### 2020-03-16 Rmd/World_Map_Breeding_Systems.Rmd
Fixing error in metadata

---
title: ""
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE}
#WORLDPLOT WITH BREEDING SYSTEMS

#Load Libraries
library(readxl)
library(ggplot2)
library(dbplyr)
library(scatterpie)
library(reshape2)
# READ LONG FORMAT DATA

setwd("~/R_Projects/Reproductive Traits")
Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")

#SUBSET UNIQUE CASES PER NETWORK
Long_format_subset <-  unique(Long_format_metawebs[,c("Plant_species","Id")])
#It seems to work fine
#and the total number of species makes sense, a bit more than the total unique cases for all the networks

#READ TRAIT DATA IN ORDER TO MERGE
data <- read.csv("Data/Data_processing/all.csv", stringsAsFactors = F)
data <- data[,c(1,4,6,7,8,15,27)]
levels(as.factor(data$Breeding_system))
#Filter data for columns of interest
data_filtered <- subset(data, Info_level=="flower"|Info_level=="capitulum"|Info_level=="inflorescence"|Info_level=="NA")
#Rename column to merge
colnames(data_filtered)[1] <- "Plant_species"
#Convert to factor 
data_filtered <- as.data.frame(data_filtered, stringsAsFactors = TRUE)

#Merge the two dataframes (trait data and the unique cases per network)
all_species_per_network <- merge(Long_format_subset, data_filtered,  by=c("Plant_species","Id"), all = T )

#Group breeding system per metaweb or web
all_summary_breeding_system <- dcast(all_species_per_network,Id~Breeding_system,value.var = "Breeding_system")

#Cleaning NA and one unfinished network
all_summary_breeding_system <- all_summary_breeding_system[-c(6,30),]

#Removing ".csv" from the Id to megere with coordinates
all_summary_breeding_system$Id <- gsub("\\..*","",all_summary_breeding_system$Id)

#Now merge with metadata to add coordinates to plot it
metadata <- read.csv("Data/Data_processing/metadata.csv", stringsAsFactors = F)
str(metadata)
metadata_sub <- metadata[,c(1:6,11)]
metadata_sub <- metadata_sub[ , -c(1)]
metadata_sub <- metadata_sub[order(metadata_sub$Id_number),] 
#Fix some coordinates manually, this locations have more than one
#fore representation purposes I will use just one
metadata_sub[6,3] <- "1.575532"
metadata_sub[6,4] <- "52.762395"
metadata_sub[7,3] <- "9.1"
metadata_sub[7,4] <- "56.1"
metadata_sub[29,3] <- "-6.16895"
metadata_sub[29,4] <- "37.234966"
metadata_sub <- metadata_sub[-14,]
colnames(metadata_sub)[1] <- "Id"

#Merge coordinates and data 
data_merged <- merge(metadata_sub, all_summary_breeding_system)

data_merged[,c(3,4,6:19)] <- sapply(data_merged[,c(3,4,6:19)],as.numeric)
sapply(data_merged, class)
data_merged$Id <- as.factor(data_merged$Id)
str(data_merged)
#Prepare data for plotting
data_merged$Hermaphroditism <- data_merged$hermaphrodite
data_merged$Dioecy <- data_merged$androdioecious + data_merged$androgynodioecious + data_merged$dioecious+
  data_merged$gynodioecious + data_merged$monoecious_dioecious + data_merged$`polygamo-dioecious`+
  data_merged$subdioecious

data_merged$Monoecy <- data_merged$andromonoecious + data_merged$gynomonoecious + data_merged$monoecious
+ data_merged$submonoecious

data_merged_sub <- data_merged[, c(1:6, 20:22)]
#Plot data
world <- map_data('world')

#network size fix

p <- ggplot(world, aes(long, lat)) +
  geom_map(map=world, aes(map_id=region), fill="white", color="black") +
  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
                     data = data_merged_sub, cols = colnames(data_merged_sub[,c(7:9)]),alpha=.8)+ 
  scale_fill_manual(breaks = colnames(data_merged_sub[,c(7:9)]),
                       labels = c("Hermaphroditism", "Dioecy", "Monoecy"),
                       values = c("Hermaphroditism" = "#4DAF4A",
                                  "Monoecy" = "#984EA3",
                                  "Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
  caption = "",fill = NULL) +
  theme(legend.position = c(0.21, 0.009),
        legend.justification = c(1, 0),
        axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm"))

```

### 2020-03-16 Rmd/World_Map_Breeding_Systems.Rmd
Playing with the coordinates to show the plot nicely

@@
 # READ LONG FORMAT DATA
-
 setwd("~/R_Projects/Reproductive Traits")
@@
 
+data_merged_sub_ord <- data_merged_sub[order(data_merged_sub$Id_number),]
+#Move coordinates manually to see all points (Improving plot visualization)
+#Manual jitter
+data_merged_sub_ord$Id_number <- seq(1, length(data_merged_sub_ord$Id_number))
+#Fixing New Zealand pies
+data_merged_sub_ord[19,4] <- -29
+data_merged_sub_ord[19,3] <- 180
+data_merged_sub_ord[20,4] <- -40
+data_merged_sub_ord[20,3] <- 180
+data_merged_sub_ord[21,4] <- -51
+data_merged_sub_ord[21,3] <- 180
+
+#Fixing Galapagos pies
+data_merged_sub_ord[18,4] <- -6
+data_merged_sub_ord[27,4] <- 5
+#Fixing Galapagos pies
+data_merged_sub_ord[13,4] <- -14
+data_merged_sub_ord[17,4] <- -25
+#Fixing Denmark pies
+data_merged_sub_ord[3,4] <- 70
+data_merged_sub_ord[4,4] <- 60
+data_merged_sub_ord[7,4] <- 50
+
 #network size fix
@@
 p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
-                     data = data_merged_sub, cols = colnames(data_merged_sub[,c(7:9)]),alpha=.8)+ 
-  scale_fill_manual(breaks = colnames(data_merged_sub[,c(7:9)]),
+                     data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:9)]),alpha=.8)+ 
+  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:9)]),
                        labels = c("Hermaphroditism", "Dioecy", "Monoecy"),
@@
         legend.justification = c(1, 0),
-        axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm"))
+        axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm"))+geom_segment(data = data_merged_sub_ord, 
+  aes(x = 174, y = -28, xend = 170, yend = -45), color = "lightblue", size = 0.3, alpha = 0.2,
+  arrow = arrow(length = unit(0.08, "inches")))
 

### 2020-03-17 Rmd/World_Map_Breeding_Systems.Rmd
Fixing error in coordinates

--- 2020-03-16 Rmd/World_Map_Breeding_Systems.Rmd
@@
 world <- map_data('world')
+data_merged_sub_ord <- data_merged_sub[order(data_merged_sub$Id_number),]
+#Move coordinates manually to see all points (Improving plot visualization)
+#Manual jitter
+data_merged_sub_ord$Id_number <- seq(1, length(data_merged_sub_ord$Id_number))
+#Fixing New Zealand pies
+data_merged_sub_ord[19,4] <- -28
+data_merged_sub_ord[19,3] <- 168
+data_merged_sub_ord[20,4] <- -52
+data_merged_sub_ord[20,3] <- 180
+data_merged_sub_ord[21,4] <- -48
+data_merged_sub_ord[21,3] <- 158
+
+#Fixing Galapagos pies
+data_merged_sub_ord[18,4] <- -7
+data_merged_sub_ord[18,3] <- -105
+
+data_merged_sub_ord[27,4] <- 6
+data_merged_sub_ord[27,3] <- -105
+
+#Fixing Mauritius pies
+data_merged_sub_ord[13,4] <- -12
+data_merged_sub_ord[13,3] <- 72
+data_merged_sub_ord[17,4] <- -28
+data_merged_sub_ord[17,3] <- 72
+
+#Fixing Denmark pies
+data_merged_sub_ord[3,4] <- 72
+data_merged_sub_ord[4,4] <- 60
+data_merged_sub_ord[7,4] <- 50
+
+#Fixing Venezuela pies
+
+data_merged_sub_ord[22,3] <- -45
+data_merged_sub_ord[22,4] <- 10
+
+#Fixing Japan pies
+
+data_merged_sub_ord[11,3] <- 154
+data_merged_sub_ord[14,3] <- 145
+data_merged_sub_ord[14,4] <- 20
+
+#Fixing Spain pies
+
+data_merged_sub_ord[28,3] <- -20
+data_merged_sub_ord[28,4] <- 28
+
+data_merged_sub_ord[1,3] <- -20
+data_merged_sub_ord[1,4] <- 52
+data_merged_sub_ord[2,3] <- -30
+data_merged_sub_ord[2,4] <- 40
 
@@
 p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
-                     data = data_merged_sub, cols = colnames(data_merged_sub[,c(7:9)]),alpha=.8)+ 
-  scale_fill_manual(breaks = colnames(data_merged_sub[,c(7:9)]),
-                       labels = c("Hermaphroditism", "Dioecy", "Monoecy"),
-                       values = c("Hermaphroditism" = "#4DAF4A",
-                                  "Monoecy" = "#984EA3",
-                                  "Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
-  caption = "",fill = NULL) +
-  theme(legend.position = c(0.21, 0.009),
-        legend.justification = c(1, 0),
-        axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm"))
-
+ data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:9)]),alpha=.8)+ 
+  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:9)]),
+ labels = c("Hermaphroditism", "Dioecy", "Monoecy"),values = c("Hermaphroditism" = "#4DAF4A",
+ "Monoecy" = "#984EA3","Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
+  caption = "",fill = NULL) + theme(legend.position = c(0.215, 0.009),legend.justification = c(1, 0),
+  axis.ticks = element_blank(),legend.key.size = unit(0.15, "cm")) +
+  geom_segment(data = data_merged_sub_ord,aes(x = 168, y = -34, xend = 172, yend = -43),color = "black", size = 0.3, alpha = 0.2) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 179, y = -46, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.2) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 164, y = -48, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.2) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = 6, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.2) +  
+  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = -7, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.2) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -12), color = "black", size = 0.3, alpha = 0.2) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -28), color = "black", size = 0.3, alpha = 0.2) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -51, y = 10, xend = -61, yend = 5.5), color = "black", size = 0.3, alpha = 0.2) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 148, y = 35, xend = 135.866667, yend = 35), color = "black", size = 0.3, alpha = 0.2) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 140, y = 22, xend = 129, yend = 28), color = "black", size = 0.3, alpha = 0.2) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -15, y = 32, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.2) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = -15, y = 50, xend = 3, yend = 43), color = "black", size = 0.3, alpha = 0.2) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -24, y = 40, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.2) 
 ```

### 2020-03-17 Scripts/Data_preparation/1_Metadata_preparation.R

@@ -939,9 +939,9 @@ robertson_1929 <- read.csv("Data/Data_networks_metawebs/25_metaweb_robertson_192
 
 BIBTEXKEY <- c("25_metaweb_robertson_1929")
 
-longitude <- c(-75.5)
+longitude <- c(-89.8968771)
 
-latitude <- c(45.4)
+latitude <- c(39.278958)
 
 country <- c("United States")
 

### 2020-03-17 Rmd/World_Map_Breeding_Systems.Rmd
Plot of breeding systems

--- 2020-03-16 Rmd/World_Map_Breeding_Systems.Rmd
@@
 
+data_merged_sub_ord <- data_merged_sub[order(data_merged_sub$Id_number),]
+#Move coordinates manually to see all points (Improving plot visualization)
+#Manual jitter
+data_merged_sub_ord$Id_number <- seq(1, length(data_merged_sub_ord$Id_number))
+#Fixing New Zealand pies
+data_merged_sub_ord[19,4] <- -28
+data_merged_sub_ord[19,3] <- 168
+data_merged_sub_ord[20,4] <- -52
+data_merged_sub_ord[20,3] <- 180
+data_merged_sub_ord[21,4] <- -48
+data_merged_sub_ord[21,3] <- 158
+
+#Fixing Galapagos pies
+data_merged_sub_ord[18,4] <- -7
+data_merged_sub_ord[18,3] <- -105
+
+data_merged_sub_ord[27,4] <- 6
+data_merged_sub_ord[27,3] <- -105
+
+#Fixing Mauritius pies
+data_merged_sub_ord[13,4] <- -12
+data_merged_sub_ord[13,3] <- 72
+data_merged_sub_ord[17,4] <- -28
+data_merged_sub_ord[17,3] <- 72
+
+#Fixing Denmark pies
+data_merged_sub_ord[3,4] <- 72
+data_merged_sub_ord[4,4] <- 60
+data_merged_sub_ord[7,4] <- 50
+
+#Fixing Venezuela pies
+
+data_merged_sub_ord[22,3] <- -45
+data_merged_sub_ord[22,4] <- 10
+data_merged_sub_ord[23,3] <- -45
+data_merged_sub_ord[23,4] <- 25
+
+#Fixing Japan pies
+
+data_merged_sub_ord[11,3] <- 154
+data_merged_sub_ord[14,3] <- 145
+data_merged_sub_ord[14,4] <- 20
+
+#Fixing Spain pies
+
+data_merged_sub_ord[28,3] <- -20
+data_merged_sub_ord[28,4] <- 28
+
+data_merged_sub_ord[1,3] <- -20
+data_merged_sub_ord[1,4] <- 52
+data_merged_sub_ord[2,3] <- -30
+data_merged_sub_ord[2,4] <- 40
+
+#Fixing Argentina pies
+
+data_merged_sub_ord[5,3] <- -90
+
+#Fixing Brazil pies
+
+data_merged_sub_ord[26,3] <- -30
+
+#Fixing Sweden pies
+
+data_merged_sub_ord[8,3] <- 40
+data_merged_sub_ord[8,4] <- 78
+
+#Fixing Denmark pies
+
+data_merged_sub_ord[3,3] <- 0
+data_merged_sub_ord[3,4] <- 80
+data_merged_sub_ord[4,3] <- 15
+data_merged_sub_ord[4,4] <- 80
+data_merged_sub_ord[7,3] <- 45
+data_merged_sub_ord[7,4] <- 60
+
+#Fixing UK pies
+
+data_merged_sub_ord[6,3] <- -8
+data_merged_sub_ord[6,4] <- 67
+
+#Fixing Australia
+
+data_merged_sub_ord[12,3] <- 120
+
+#Fixing China pie
+
+data_merged_sub_ord[10,3] <- 90
+data_merged_sub_ord[10,4] <- 0
+
+#Fixing USA pie
+
+data_merged_sub_ord[24,3] <- -60
+
+#Fixing Canada pie
+data_merged_sub_ord[25,3] <- -42
+data_merged_sub_ord[25,4] <- 52
+data_merged_sub_ord[15,3] <- -71
+data_merged_sub_ord[15,4] <- 92
+
+#Fixing Greenland pie
+
+data_merged_sub_ord[16,4] <- 92
+data_merged_sub_ord[9,4] <- 92
+
 #network size fix
@@
 p <- ggplot(world, aes(long, lat)) +
-  geom_map(map=world, aes(map_id=region), fill="white", color="black") +
+  geom_map(map=world, aes(map_id=region), fill="white", color="grey", size=0.35) +
   coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
 p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
-                     data = data_merged_sub, cols = colnames(data_merged_sub[,c(7:9)]),alpha=.8)+ 
-  scale_fill_manual(breaks = colnames(data_merged_sub[,c(7:9)]),
-                       labels = c("Hermaphroditism", "Dioecy", "Monoecy"),
-                       values = c("Hermaphroditism" = "#4DAF4A",
-                                  "Monoecy" = "#984EA3",
-                                  "Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
-  caption = "",fill = NULL) +
-  theme(legend.position = c(0.21, 0.009),
-        legend.justification = c(1, 0),
-        axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm"))
-
+ data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:9)]),alpha=.8)+ 
+  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:9)]),
+ labels = c("Hermaphroditism", "Dioecy", "Monoecy"),values = c("Hermaphroditism" = "#4DAF4A",
+ "Monoecy" = "#984EA3","Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
+  caption = "",fill = NULL) + theme(legend.position = c(0.215, 0.010),legend.justification = c(1, 0),
+  axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +
+  geom_segment(data = data_merged_sub_ord,aes(x = 168, y = -34, xend = 172, yend = -43),color = "black", size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = 179, y = -46, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = 164, y = -48, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = 6, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) +  #GALAPAGOS
+  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = -7, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) + #GALAPAGOS
+  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -12), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
+  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -28), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
+  geom_segment(data = data_merged_sub_ord, aes(x = -51, y = 10, xend = -61, yend = 5.5), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
+  geom_segment(data = data_merged_sub_ord, aes(x = -51, y =25 , xend = -67, yend = 8.9), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
+  geom_segment(data = data_merged_sub_ord, aes(x = 148, y = 35, xend = 135.8, yend = 35), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 140, y = 22, xend = 129, yend = 28), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -15.5, y = 32, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = -15, y = 50, xend = 3, yend = 43), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -24, y = 40, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -84, y = -32, xend = -68, yend = -32), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = -36, y = -21, xend = -58, yend = -21), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 34, y = 78, xend = 18.5, yend = 68), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 0, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 15, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -8, y = 61, xend = 1.5, yend = 52), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 39, y = 60, xend = 9, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 126, y = -36, xend = 148, yend = -36), color = "black", size = 0.3, alpha = 0.8) + #AUS
+  geom_segment(data = data_merged_sub_ord, aes(x = 90, y = 6, xend = 100, yend = 28), color = "black", size = 0.3, alpha = 0.8) + #CHINA
+  geom_segment(data = data_merged_sub_ord, aes(x = -66, y = 39, xend = -89, yend = 39), color = "black", size = 0.3, alpha = 0.8) + #USA
+  geom_segment(data = data_merged_sub_ord, aes(x = -48, y = 52, xend = -75, yend = 45), color = "black", size = 0.3, alpha = 0.8) + #CANADA
+  geom_segment(data = data_merged_sub_ord, aes(x = -71, y = 86, xend = -71, yend = 81), color = "black", size = 0.3, alpha = 0.8) + #CANADA
+  geom_segment(data = data_merged_sub_ord, aes(x = -52, y = 86, xend = -52, yend = 71), color = "black", size = 0.3, alpha = 0.8) + #GREENLAND
+  geom_segment(data = data_merged_sub_ord, aes(x = -20, y = 86, xend = -20, yend = 74), color = "black", size = 0.3, alpha = 0.8)
 ```

### 2020-03-18 Rmd/World_Map_Compatibility_Systems.Rmd
Compatibility system plot

--- 2020-03-17 Rmd/World_Map_Breeding_Systems.Rmd
@@
 ---
-title: ""
+title: "Untitled"
 output:
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE}
-#WORLDPLOT WITH BREEDING SYSTEMS
 
@@
 # READ LONG FORMAT DATA
+
 setwd("~/R_Projects/Reproductive Traits")
+
 Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")
@@
 data <- read.csv("Data/Data_processing/all.csv", stringsAsFactors = F)
-data <- data[,c(1,4,6,7,8,15,27)]
+data <- data[,c(1,4,6,7,8,22,27)]
 levels(as.factor(data$Breeding_system))
@@
 #Group breeding system per metaweb or web
-all_summary_breeding_system <- dcast(all_species_per_network,Id~Breeding_system,value.var = "Breeding_system")
+all_summary_compatibility_system <- dcast(all_species_per_network,Id~Compatibility,value.var = "Compatibility")
 
 #Cleaning NA and one unfinished network
-all_summary_breeding_system <- all_summary_breeding_system[-c(6,30),]
+all_summary_compatibility_system <- all_summary_compatibility_system[,c(1,5:8)]
 
+all_summary_compatibility_system$partially_self_compatible <- as.numeric(all_summary_compatibility_system$partially_self_compatible) + as.numeric(all_summary_compatibility_system$self_compatible_self_incompatible)
+all_summary_compatibility_system <- all_summary_compatibility_system[ , -4]
 #Removing ".csv" from the Id to megere with coordinates
-all_summary_breeding_system$Id <- gsub("\\..*","",all_summary_breeding_system$Id)
+all_summary_compatibility_system$Id <- gsub("\\..*","",all_summary_compatibility_system$Id)
 
@@
 #Merge coordinates and data 
-data_merged <- merge(metadata_sub, all_summary_breeding_system)
+data_merged <- merge(metadata_sub, all_summary_compatibility_system)
 
-data_merged[,c(3,4,6:19)] <- sapply(data_merged[,c(3,4,6:19)],as.numeric)
-sapply(data_merged, class)
 data_merged$Id <- as.factor(data_merged$Id)
 str(data_merged)
-#Prepare data for plotting
-data_merged$Hermaphroditism <- data_merged$hermaphrodite
-data_merged$Dioecy <- data_merged$androdioecious + data_merged$androgynodioecious + data_merged$dioecious+
-  data_merged$gynodioecious + data_merged$monoecious_dioecious + data_merged$`polygamo-dioecious`+
-  data_merged$subdioecious
 
-data_merged$Monoecy <- data_merged$andromonoecious + data_merged$gynomonoecious + data_merged$monoecious
-+ data_merged$submonoecious
-
-data_merged_sub <- data_merged[, c(1:6, 20:22)]
+#I have done this in other code for other reasons
+#I'm going to maintain it
+data_merged_sub <- data_merged
 #Plot data
@@
 
+data_merged_sub_ord[,c(3,4,7:9)] <- sapply(data_merged_sub_ord[,c(3,4,7:9)],as.numeric)
+str(data_merged_sub_ord)
+
 #network size fix
@@
   scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:9)]),
- labels = c("Hermaphroditism", "Dioecy", "Monoecy"),values = c("Hermaphroditism" = "#4DAF4A",
- "Monoecy" = "#984EA3","Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
-  caption = "",fill = NULL) + theme(legend.position = c(0.215, 0.010),legend.justification = c(1, 0),
-  axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +
+ labels = c("Partially self compatible", "Self compatible", "Self incompatible"),values = c("partially_self_compatible" = "#4DAF4A","self_compatible" = "#984EA3","self_incompatible" = "orange")) +labs(title = "Compatibility systems",subtitle = "", caption = "",fill = NULL) + theme(legend.position = c(0.18, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),
+  axis.ticks = element_blank(),legend.key.size = unit(0.16, "cm")) +
   geom_segment(data = data_merged_sub_ord,aes(x = 168, y = -34, xend = 172, yend = -43),color = "black", size = 0.3, alpha = 0.8) + #NZ
@@
   geom_segment(data = data_merged_sub_ord, aes(x = -20, y = 86, xend = -20, yend = 74), color = "black", size = 0.3, alpha = 0.8)
+
 ```

### 2020-03-19 Rmd/World_Map_Breeding_Systems.Rmd
Maps, and code for species names

@@
  labels = c("Hermaphroditism", "Dioecy", "Monoecy"),values = c("Hermaphroditism" = "#4DAF4A",
- "Monoecy" = "#984EA3","Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
-  caption = "",fill = NULL) + theme(legend.position = c(0.215, 0.010),legend.justification = c(1, 0),
-  axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +
+ "Monoecy" = "#984EA3","Dioecy" = "orange")) +labs(title = "Breeding system",subtitle = "",
+  caption = "",fill = NULL) + theme(legend.position = c(0.15, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),
+  axis.ticks = element_blank(),legend.key.size = unit(0.16, "cm")) +
   geom_segment(data = data_merged_sub_ord,aes(x = 168, y = -34, xend = 172, yend = -43),color = "black", size = 0.3, alpha = 0.8) + #NZ

### 2020-03-19 Rmd/World_Map_Life_Form.Rmd
Maps, and code for species names

--- 2020-03-18 Rmd/World_Map_Compatibility_Systems.Rmd
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE}
+#WORLDPLOT WITH LIFE FORM
 
@@
 data <- read.csv("Data/Data_processing/all.csv", stringsAsFactors = F)
-data <- data[,c(1,4,6,7,8,22,27)]
+data <- data[,c(1,4,6,7,8,51,27)]
 levels(as.factor(data$Breeding_system))
@@
 #Group breeding system per metaweb or web
-all_summary_compatibility_system <- dcast(all_species_per_network,Id~Compatibility,value.var = "Compatibility")
-
+all_summary_life_form <- dcast(all_species_per_network,Id~life_form,value.var = "life_form")
 #Cleaning NA and one unfinished network
-all_summary_compatibility_system <- all_summary_compatibility_system[,c(1,5:8)]
-
-all_summary_compatibility_system$partially_self_compatible <- as.numeric(all_summary_compatibility_system$partially_self_compatible) + as.numeric(all_summary_compatibility_system$self_compatible_self_incompatible)
-all_summary_compatibility_system <- all_summary_compatibility_system[ , -4]
+all_summary_life_form <- all_summary_life_form[-c(6,30),-c(6)]
 #Removing ".csv" from the Id to megere with coordinates
-all_summary_compatibility_system$Id <- gsub("\\..*","",all_summary_compatibility_system$Id)
+all_summary_life_form$Id <- gsub("\\..*","",all_summary_life_form$Id)
 
@@
 #Merge coordinates and data 
-data_merged <- merge(metadata_sub, all_summary_compatibility_system)
+data_merged <- merge(metadata_sub, all_summary_life_form)
 
@@
 
-data_merged_sub_ord[,c(3,4,7:9)] <- sapply(data_merged_sub_ord[,c(3,4,7:9)],as.numeric)
+data_merged_sub_ord[,c(3,4,7:10)] <- sapply(data_merged_sub_ord[,c(3,4,7:10)],as.numeric)
 str(data_merged_sub_ord)
 
-#network size fix
-
 p <- ggplot(world, aes(long, lat)) +
-  geom_map(map=world, aes(map_id=region), fill="white", color="grey", size=0.35) +
+  geom_map(map=world, aes(map_id=region), fill="white", color="black") +
   coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
 p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
- data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:9)]),alpha=.8)+ 
-  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:9)]),
- labels = c("Partially self compatible", "Self compatible", "Self incompatible"),values = c("partially_self_compatible" = "#4DAF4A","self_compatible" = "#984EA3","self_incompatible" = "orange")) +labs(title = "Compatibility systems",subtitle = "", caption = "",fill = NULL) + theme(legend.position = c(0.18, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),
-  axis.ticks = element_blank(),legend.key.size = unit(0.16, "cm")) +
+                     data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:10)]),alpha=.8)+ 
+  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:10)]),
+                    labels = c("Herb", "Shrub", "Tree", "Vine"),values = c("herb" = "#4DAF4A",
+                                                                           "shrub" = "#984EA3","tree" = "orange", "vine" = "lightblue")) +labs(title = "Life form",subtitle = "",
+                                                                                                                                               caption = "",fill = NULL) + theme(legend.position = c(0.12, 0.009),legend.justification = c(1, 0),
+                                                                                                                                                                                 axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +
   geom_segment(data = data_merged_sub_ord,aes(x = 168, y = -34, xend = 172, yend = -43),color = "black", size = 0.3, alpha = 0.8) + #NZ

### 2020-03-19 Rmd/World_Plots_Panel.Rmd
Maps, and code for species names

--- 2020-03-19 Rmd/World_Map_Breeding_Systems.Rmd
@@
 ---
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.width=40,fig.align = 'center'}
 #WORLDPLOT WITH BREEDING SYSTEMS
@@
 library(reshape2)
+library(effsize)
+library(dplyr)
+library(ggplot2)
+library(ggpubr)
+library(cowplot)
+library(gridExtra)
+library(egg)
+library(magrittr)
+library(multipanelfigure)
+library(grid)
 # READ LONG FORMAT DATA
@@
 
-p <- ggplot(world, aes(long, lat)) +
+p1 <- ggplot(world, aes(long, lat)) +
   geom_map(map=world, aes(map_id=region), fill="white", color="grey", size=0.35) +
-  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
-p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
+  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE) +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
  data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:9)]),alpha=.8)+ 
@@
  "Monoecy" = "#984EA3","Dioecy" = "orange")) +labs(title = "Breeding system",subtitle = "",
-  caption = "",fill = NULL) + theme(legend.position = c(0.15, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),
+  caption = "",fill = NULL) + theme(legend.position = c(0.15, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),legend.key.size = unit(0.16, "cm")) +
+  geom_segment(data = data_merged_sub_ord,aes(x = 168, y = -34, xend = 172, yend = -43),color = "black", size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = 179, y = -46, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = 164, y = -48, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = 6, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) +  #GALAPAGOS
+  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = -7, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) + #GALAPAGOS
+  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -12), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
+  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -28), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
+  geom_segment(data = data_merged_sub_ord, aes(x = -51, y = 10, xend = -61, yend = 5.5), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
+  geom_segment(data = data_merged_sub_ord, aes(x = -51, y =25 , xend = -67, yend = 8.9), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
+  geom_segment(data = data_merged_sub_ord, aes(x = 148, y = 35, xend = 135.8, yend = 35), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 140, y = 22, xend = 129, yend = 28), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -15.5, y = 32, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = -15, y = 50, xend = 3, yend = 43), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -24, y = 40, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -84, y = -32, xend = -68, yend = -32), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = -36, y = -21, xend = -58, yend = -21), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 34, y = 78, xend = 18.5, yend = 68), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 0, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 15, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -8, y = 61, xend = 1.5, yend = 52), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 39, y = 60, xend = 9, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 126, y = -36, xend = 148, yend = -36), color = "black", size = 0.3, alpha = 0.8) + #AUS
+  geom_segment(data = data_merged_sub_ord, aes(x = 90, y = 6, xend = 100, yend = 28), color = "black", size = 0.3, alpha = 0.8) + #CHINA
+  geom_segment(data = data_merged_sub_ord, aes(x = -66, y = 39, xend = -89, yend = 39), color = "black", size = 0.3, alpha = 0.8) + #USA
+  geom_segment(data = data_merged_sub_ord, aes(x = -48, y = 52, xend = -75, yend = 45), color = "black", size = 0.3, alpha = 0.8) + #CANADA
+  geom_segment(data = data_merged_sub_ord, aes(x = -71, y = 86, xend = -71, yend = 81), color = "black", size = 0.3, alpha = 0.8) + #CANADA
+  geom_segment(data = data_merged_sub_ord, aes(x = -52, y = 86, xend = -52, yend = 71), color = "black", size = 0.3, alpha = 0.8) + #GREENLAND
+  geom_segment(data = data_merged_sub_ord, aes(x = -20, y = 86, xend = -20, yend = 74), color = "black", size = 0.3, alpha = 0.8)
+
+#Load Libraries
+library(readxl)
+library(ggplot2)
+library(dbplyr)
+library(scatterpie)
+library(reshape2)
+# READ LONG FORMAT DATA
+
+setwd("~/R_Projects/Reproductive Traits")
+
+Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")
+
+#SUBSET UNIQUE CASES PER NETWORK
+Long_format_subset <-  unique(Long_format_metawebs[,c("Plant_species","Id")])
+#It seems to work fine
+#and the total number of species makes sense, a bit more than the total unique cases for all the networks
+
+#READ TRAIT DATA IN ORDER TO MERGE
+data <- read.csv("Data/Data_processing/all.csv", stringsAsFactors = F)
+data <- data[,c(1,4,6,7,8,22,27)]
+levels(as.factor(data$Breeding_system))
+#Filter data for columns of interest
+data_filtered <- subset(data, Info_level=="flower"|Info_level=="capitulum"|Info_level=="inflorescence"|Info_level=="NA")
+#Rename column to merge
+colnames(data_filtered)[1] <- "Plant_species"
+#Convert to factor 
+data_filtered <- as.data.frame(data_filtered, stringsAsFactors = TRUE)
+
+#Merge the two dataframes (trait data and the unique cases per network)
+all_species_per_network <- merge(Long_format_subset, data_filtered,  by=c("Plant_species","Id"), all = T )
+
+#Group breeding system per metaweb or web
+all_summary_compatibility_system <- dcast(all_species_per_network,Id~Compatibility,value.var = "Compatibility")
+
+#Cleaning NA and one unfinished network
+all_summary_compatibility_system <- all_summary_compatibility_system[,c(1,5:8)]
+
+all_summary_compatibility_system$partially_self_compatible <- as.numeric(all_summary_compatibility_system$partially_self_compatible) + as.numeric(all_summary_compatibility_system$self_compatible_self_incompatible)
+all_summary_compatibility_system <- all_summary_compatibility_system[ , -4]
+#Removing ".csv" from the Id to megere with coordinates
+all_summary_compatibility_system$Id <- gsub("\\..*","",all_summary_compatibility_system$Id)
+
+#Now merge with metadata to add coordinates to plot it
+metadata <- read.csv("Data/Data_processing/metadata.csv", stringsAsFactors = F)
+str(metadata)
+metadata_sub <- metadata[,c(1:6,11)]
+metadata_sub <- metadata_sub[ , -c(1)]
+metadata_sub <- metadata_sub[order(metadata_sub$Id_number),] 
+#Fix some coordinates manually, this locations have more than one
+#fore representation purposes I will use just one
+metadata_sub[6,3] <- "1.575532"
+metadata_sub[6,4] <- "52.762395"
+metadata_sub[7,3] <- "9.1"
+metadata_sub[7,4] <- "56.1"
+metadata_sub[29,3] <- "-6.16895"
+metadata_sub[29,4] <- "37.234966"
+metadata_sub <- metadata_sub[-14,]
+colnames(metadata_sub)[1] <- "Id"
+
+#Merge coordinates and data 
+data_merged <- merge(metadata_sub, all_summary_compatibility_system)
+
+data_merged$Id <- as.factor(data_merged$Id)
+str(data_merged)
+
+#I have done this in other code for other reasons
+#I'm going to maintain it
+data_merged_sub <- data_merged
+#Plot data
+world <- map_data('world')
+
+data_merged_sub_ord <- data_merged_sub[order(data_merged_sub$Id_number),]
+#Move coordinates manually to see all points (Improving plot visualization)
+#Manual jitter
+data_merged_sub_ord$Id_number <- seq(1, length(data_merged_sub_ord$Id_number))
+#Fixing New Zealand pies
+data_merged_sub_ord[19,4] <- -28
+data_merged_sub_ord[19,3] <- 168
+data_merged_sub_ord[20,4] <- -52
+data_merged_sub_ord[20,3] <- 180
+data_merged_sub_ord[21,4] <- -48
+data_merged_sub_ord[21,3] <- 158
+
+#Fixing Galapagos pies
+data_merged_sub_ord[18,4] <- -7
+data_merged_sub_ord[18,3] <- -105
+
+data_merged_sub_ord[27,4] <- 6
+data_merged_sub_ord[27,3] <- -105
+
+#Fixing Mauritius pies
+data_merged_sub_ord[13,4] <- -12
+data_merged_sub_ord[13,3] <- 72
+data_merged_sub_ord[17,4] <- -28
+data_merged_sub_ord[17,3] <- 72
+
+#Fixing Denmark pies
+data_merged_sub_ord[3,4] <- 72
+data_merged_sub_ord[4,4] <- 60
+data_merged_sub_ord[7,4] <- 50
+
+#Fixing Venezuela pies
+
+data_merged_sub_ord[22,3] <- -45
+data_merged_sub_ord[22,4] <- 10
+data_merged_sub_ord[23,3] <- -45
+data_merged_sub_ord[23,4] <- 25
+
+#Fixing Japan pies
+
+data_merged_sub_ord[11,3] <- 154
+data_merged_sub_ord[14,3] <- 145
+data_merged_sub_ord[14,4] <- 20
+
+#Fixing Spain pies
+
+data_merged_sub_ord[28,3] <- -20
+data_merged_sub_ord[28,4] <- 28
+
+data_merged_sub_ord[1,3] <- -20
+data_merged_sub_ord[1,4] <- 52
+data_merged_sub_ord[2,3] <- -30
+data_merged_sub_ord[2,4] <- 40
+
+#Fixing Argentina pies
+
+data_merged_sub_ord[5,3] <- -90
+
+#Fixing Brazil pies
+
+data_merged_sub_ord[26,3] <- -30
+
+#Fixing Sweden pies
+
+data_merged_sub_ord[8,3] <- 40
+data_merged_sub_ord[8,4] <- 78
+
+#Fixing Denmark pies
+
+data_merged_sub_ord[3,3] <- 0
+data_merged_sub_ord[3,4] <- 80
+data_merged_sub_ord[4,3] <- 15
+data_merged_sub_ord[4,4] <- 80
+data_merged_sub_ord[7,3] <- 45
+data_merged_sub_ord[7,4] <- 60
+
+#Fixing UK pies
+
+data_merged_sub_ord[6,3] <- -8
+data_merged_sub_ord[6,4] <- 67
+
+#Fixing Australia
+
+data_merged_sub_ord[12,3] <- 120
+
+#Fixing China pie
+
+data_merged_sub_ord[10,3] <- 90
+data_merged_sub_ord[10,4] <- 0
+
+#Fixing USA pie
+
+data_merged_sub_ord[24,3] <- -60
+
+#Fixing Canada pie
+data_merged_sub_ord[25,3] <- -42
+data_merged_sub_ord[25,4] <- 52
+data_merged_sub_ord[15,3] <- -71
+data_merged_sub_ord[15,4] <- 92
+
+#Fixing Greenland pie
+
+data_merged_sub_ord[16,4] <- 92
+data_merged_sub_ord[9,4] <- 92
+
+data_merged_sub_ord[,c(3,4,7:9)] <- sapply(data_merged_sub_ord[,c(3,4,7:9)],as.numeric)
+str(data_merged_sub_ord)
+
+#network size fix
+
+p2 <- ggplot(world, aes(long, lat)) +
+  geom_map(map=world, aes(map_id=region), fill="white", color="grey", size=0.35) +
+  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE) +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
+ data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:9)]),alpha=.8)+ 
+  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:9)]),
+ labels = c("Partially self compatible", "Self compatible", "Self incompatible"),values = c("partially_self_compatible" = "#4DAF4A","self_compatible" = "#984EA3","self_incompatible" = "orange")) +labs(title = "Compatibility system",subtitle = "", caption = "",fill = NULL) + theme(legend.position = c(0.18, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),
   axis.ticks = element_blank(),legend.key.size = unit(0.16, "cm")) +
@@
   geom_segment(data = data_merged_sub_ord, aes(x = -20, y = 86, xend = -20, yend = 74), color = "black", size = 0.3, alpha = 0.8)
+
+#Load Libraries
+library(readxl)
+library(ggplot2)
+library(dbplyr)
+library(scatterpie)
+library(reshape2)
+# READ LONG FORMAT DATA
+setwd("~/R_Projects/Reproductive Traits")
+
+Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")
+
+#SUBSET UNIQUE CASES PER NETWORK
+Long_format_subset <-  unique(Long_format_metawebs[,c("Plant_species","Id")])
+#It seems to work fine
+#and the total number of species makes sense, a bit more than the total unique cases for all the networks
+
+#READ TRAIT DATA IN ORDER TO MERGE
+data <- read.csv("Data/Data_processing/all.csv", stringsAsFactors = F)
+data <- data[,c(1,4,6,7,8,51,27)]
+levels(as.factor(data$Breeding_system))
+#Filter data for columns of interest
+data_filtered <- subset(data, Info_level=="flower"|Info_level=="capitulum"|Info_level=="inflorescence"|Info_level=="NA")
+#Rename column to merge
+colnames(data_filtered)[1] <- "Plant_species"
+#Convert to factor 
+data_filtered <- as.data.frame(data_filtered, stringsAsFactors = TRUE)
+
+#Merge the two dataframes (trait data and the unique cases per network)
+all_species_per_network <- merge(Long_format_subset, data_filtered,  by=c("Plant_species","Id"), all = T )
+
+#Group breeding system per metaweb or web
+all_summary_life_form <- dcast(all_species_per_network,Id~life_form,value.var = "life_form")
+#Cleaning NA and one unfinished network
+all_summary_life_form <- all_summary_life_form[-c(6,30),-c(6)]
+#Removing ".csv" from the Id to megere with coordinates
+all_summary_life_form$Id <- gsub("\\..*","",all_summary_life_form$Id)
+
+#Now merge with metadata to add coordinates to plot it
+metadata <- read.csv("Data/Data_processing/metadata.csv", stringsAsFactors = F)
+str(metadata)
+metadata_sub <- metadata[,c(1:6,11)]
+metadata_sub <- metadata_sub[ , -c(1)]
+metadata_sub <- metadata_sub[order(metadata_sub$Id_number),] 
+#Fix some coordinates manually, this locations have more than one
+#fore representation purposes I will use just one
+metadata_sub[6,3] <- "1.575532"
+metadata_sub[6,4] <- "52.762395"
+metadata_sub[7,3] <- "9.1"
+metadata_sub[7,4] <- "56.1"
+metadata_sub[29,3] <- "-6.16895"
+metadata_sub[29,4] <- "37.234966"
+metadata_sub <- metadata_sub[-14,]
+colnames(metadata_sub)[1] <- "Id"
+
+#Merge coordinates and data 
+data_merged <- merge(metadata_sub, all_summary_life_form)
+
+data_merged$Id <- as.factor(data_merged$Id)
+str(data_merged)
+
+#I have done this in other code for other reasons
+#I'm going to maintain it
+data_merged_sub <- data_merged
+#Plot data
+world <- map_data('world')
+
+data_merged_sub_ord <- data_merged_sub[order(data_merged_sub$Id_number),]
+#Move coordinates manually to see all points (Improving plot visualization)
+#Manual jitter
+data_merged_sub_ord$Id_number <- seq(1, length(data_merged_sub_ord$Id_number))
+#Fixing New Zealand pies
+data_merged_sub_ord[19,4] <- -28
+data_merged_sub_ord[19,3] <- 168
+data_merged_sub_ord[20,4] <- -52
+data_merged_sub_ord[20,3] <- 180
+data_merged_sub_ord[21,4] <- -48
+data_merged_sub_ord[21,3] <- 158
+
+#Fixing Galapagos pies
+data_merged_sub_ord[18,4] <- -7
+data_merged_sub_ord[18,3] <- -105
+
+data_merged_sub_ord[27,4] <- 6
+data_merged_sub_ord[27,3] <- -105
+
+#Fixing Mauritius pies
+data_merged_sub_ord[13,4] <- -12
+data_merged_sub_ord[13,3] <- 72
+data_merged_sub_ord[17,4] <- -28
+data_merged_sub_ord[17,3] <- 72
+
+#Fixing Denmark pies
+data_merged_sub_ord[3,4] <- 72
+data_merged_sub_ord[4,4] <- 60
+data_merged_sub_ord[7,4] <- 50
+
+#Fixing Venezuela pies
+
+data_merged_sub_ord[22,3] <- -45
+data_merged_sub_ord[22,4] <- 10
+data_merged_sub_ord[23,3] <- -45
+data_merged_sub_ord[23,4] <- 25
+
+#Fixing Japan pies
+
+data_merged_sub_ord[11,3] <- 154
+data_merged_sub_ord[14,3] <- 145
+data_merged_sub_ord[14,4] <- 20
+
+#Fixing Spain pies
+
+data_merged_sub_ord[28,3] <- -20
+data_merged_sub_ord[28,4] <- 28
+
+data_merged_sub_ord[1,3] <- -20
+data_merged_sub_ord[1,4] <- 52
+data_merged_sub_ord[2,3] <- -30
+data_merged_sub_ord[2,4] <- 40
+
+#Fixing Argentina pies
+
+data_merged_sub_ord[5,3] <- -90
+
+#Fixing Brazil pies
+
+data_merged_sub_ord[26,3] <- -30
+
+#Fixing Sweden pies
+
+data_merged_sub_ord[8,3] <- 40
+data_merged_sub_ord[8,4] <- 78
+
+#Fixing Denmark pies
+
+data_merged_sub_ord[3,3] <- 0
+data_merged_sub_ord[3,4] <- 80
+data_merged_sub_ord[4,3] <- 15
+data_merged_sub_ord[4,4] <- 80
+data_merged_sub_ord[7,3] <- 45
+data_merged_sub_ord[7,4] <- 60
+
+#Fixing UK pies
+
+data_merged_sub_ord[6,3] <- -8
+data_merged_sub_ord[6,4] <- 67
+
+#Fixing Australia
+
+data_merged_sub_ord[12,3] <- 120
+
+#Fixing China pie
+
+data_merged_sub_ord[10,3] <- 90
+data_merged_sub_ord[10,4] <- 0
+
+#Fixing USA pie
+
+data_merged_sub_ord[24,3] <- -60
+
+#Fixing Canada pie
+data_merged_sub_ord[25,3] <- -42
+data_merged_sub_ord[25,4] <- 52
+data_merged_sub_ord[15,3] <- -71
+data_merged_sub_ord[15,4] <- 92
+
+#Fixing Greenland pie
+
+data_merged_sub_ord[16,4] <- 92
+data_merged_sub_ord[9,4] <- 92
+
+data_merged_sub_ord[,c(3,4,7:10)] <- sapply(data_merged_sub_ord[,c(3,4,7:10)],as.numeric)
+str(data_merged_sub_ord)
+
+p3 <- ggplot(world, aes(long, lat)) +
+  geom_map(map=world, aes(map_id=region), fill="white", color="grey") +
+  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE) +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
+                     data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:10)]),alpha=.8)+ 
+  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:10)]),
+                    labels = c("Herb", "Shrub", "Tree", "Vine"),values = c("herb" = "#4DAF4A",
+                                                                           "shrub" = "#984EA3","tree" = "orange", "vine" = "lightblue")) +labs(title = "Life form",subtitle = "",
+                                                                                                                                               caption = "",fill = NULL) + theme(legend.position = c(0.12, 0.009),legend.justification = c(1, 0),
+                                                                                                                                                                                 axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +
+  geom_segment(data = data_merged_sub_ord,aes(x = 168, y = -34, xend = 172, yend = -43),color = "black", size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = 179, y = -46, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = 164, y = -48, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = 6, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) +  #GALAPAGOS
+  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = -7, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) + #GALAPAGOS
+  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -12), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
+  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -28), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
+  geom_segment(data = data_merged_sub_ord, aes(x = -51, y = 10, xend = -61, yend = 5.5), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
+  geom_segment(data = data_merged_sub_ord, aes(x = -51, y =25 , xend = -67, yend = 8.9), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
+  geom_segment(data = data_merged_sub_ord, aes(x = 148, y = 35, xend = 135.8, yend = 35), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 140, y = 22, xend = 129, yend = 28), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -15.5, y = 32, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = -15, y = 50, xend = 3, yend = 43), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -24, y = 40, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -84, y = -32, xend = -68, yend = -32), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = -36, y = -21, xend = -58, yend = -21), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 34, y = 78, xend = 18.5, yend = 68), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 0, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 15, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -8, y = 61, xend = 1.5, yend = 52), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 39, y = 60, xend = 9, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 126, y = -36, xend = 148, yend = -36), color = "black", size = 0.3, alpha = 0.8) + #AUS
+  geom_segment(data = data_merged_sub_ord, aes(x = 90, y = 6, xend = 100, yend = 28), color = "black", size = 0.3, alpha = 0.8) + #CHINA
+  geom_segment(data = data_merged_sub_ord, aes(x = -66, y = 39, xend = -89, yend = 39), color = "black", size = 0.3, alpha = 0.8) + #USA
+  geom_segment(data = data_merged_sub_ord, aes(x = -48, y = 52, xend = -75, yend = 45), color = "black", size = 0.3, alpha = 0.8) + #CANADA
+  geom_segment(data = data_merged_sub_ord, aes(x = -71, y = 86, xend = -71, yend = 81), color = "black", size = 0.3, alpha = 0.8) + #CANADA
+  geom_segment(data = data_merged_sub_ord, aes(x = -52, y = 86, xend = -52, yend = 71), color = "black", size = 0.3, alpha = 0.8) + #GREENLAND
+  geom_segment(data = data_merged_sub_ord, aes(x = -20, y = 86, xend = -20, yend = 74), color = "black", size = 0.3, alpha = 0.8)
+
+grid.arrange(p1, p2, p3, nrow=3)
+
+ #grid.draw(arrangeGrob(ggplotGrob(p1),ggplotGrob(p2),nrow=2))
+#mylegend
+ dev.off()
+
 ```

### 2020-03-19 Rmd/World_Map_Life_Form.R

@@ -1,0 +1,217 @@
+#WORLDPLOT WITH LIFE FORM
+
+#Load Libraries
+library(readxl)
+library(ggplot2)
+library(dbplyr)
+library(scatterpie)
+library(reshape2)
+
+# READ LONG FORMAT DATA
+Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")
+
+#SUBSET UNIQUE CASES PER NETWORK
+Long_format_subset <-  unique(Long_format_metawebs[,c("Plant_species","Id")])
+#It seems to work fine
+#and the total number of species makes sense, a bit more than the total unique cases for all the networks
+
+
+#READ TRAIT DATA IN ORDER TO MERGE
+data <- read.csv("Data/Data_processing/all.csv", stringsAsFactors = F)
+data <- data[,c(1,4,6,7,8,51,27)]
+levels(as.factor(data$Breeding_system))
+#Filter data for columns of interest
+data_filtered <- subset(data, Info_level=="flower"|Info_level=="capitulum"|Info_level=="inflorescence"|Info_level=="NA")
+#Rename column to merge
+colnames(data_filtered)[1] <- "Plant_species"
+#Convert to factor 
+data_filtered <- as.data.frame(data_filtered, stringsAsFactors = TRUE)
+
+#Merge the two dataframes (trait data and the unique cases per network)
+all_species_per_network <- merge(Long_format_subset, data_filtered,  by=c("Plant_species","Id"), all = T )
+
+#Group breeding system per metaweb or web
+all_summary_life_form <- dcast(all_species_per_network,Id~life_form,value.var = "life_form")
+#Cleaning NA and one unfinished network
+all_summary_life_form <- all_summary_life_form[-c(6,30),-c(6)]
+#Removing ".csv" from the Id to megere with coordinates
+all_summary_life_form$Id <- gsub("\\..*","",all_summary_life_form$Id)
+
+#Now merge with metadata to add coordinates to plot it
+metadata <- read.csv("Data/Data_processing/metadata.csv", stringsAsFactors = F)
+str(metadata)
+metadata_sub <- metadata[,c(1:6,11)]
+metadata_sub <- metadata_sub[ , -c(1)]
[…]

### 2020-03-27 Rmd/Ideas.Rmd
Adding ideas to r notebook to keep track of the meetings

---
title: "Ideas"
output: html_notebook
---

#How to proceed

- Select main floral traits

1) Flower size

2) Fower shape

3) Compatibility system

4) Style length/Ovule number

5) Selfing level

- Plot taxa/traits Barplot?

Y axis Spp richness? X Axis the grouping variables?

Consider Poll taxa here with more developped plots?

- Hypothesis

 1) Do we have matching between specific taxa and grouping traits? Maybe show this with likelihood of visitation
    1.1 Are selfers/self compatible species less relevant in the network? How can we interpretate that (generalist vs specialization/ connectance) We expect less dependency on pollinators...

 2)

 3) Possibility of testing redundancy with phylogeny

 - How to group Poll taxa.

 What to do with non-insects?

### 2020-03-27 Scripts/Data_preparation/1_Metadata_preparation.R

@@ -71,6 +71,10 @@ duration <- c("1 season", "1 season")
 
 experiment_year <- c(2005, 2005)
 
+Sampling_method <-"Plots 50*50m with 2 transects (N=3), Plots 50*50m (N=3)"
+
+Sampling_zoo_phytocentric <- "Phytocentric, Phytocentric"
+  
 unique_networks <-c(3,3)
 
 plant_species <- c(18, 13)
@@ -81,7 +85,7 @@ network_size <- c(666, 481)
 
 metadata <- data.frame(BIBTEXKEY, longitude, latitude, country, location,duration, 
                        experiment_year,unique_networks,plant_species, pollinator_species, 
-                       network_size)
+                       network_size,Sampling_method, Sampling_zoo_phytocentric)
 
 #SECOND  Bek PhD thesis 2006
 #Not much info about this network, collected in one season in Denmark and coordinates
@@ -94,13 +98,17 @@ latitude <- c(56.066667)
 
 country <- c("Denmark")
 
-location <- c(NA)
+location <- c("Moesgaard Have")
 
-duration <- c(NA)
+duration <- c("1 season")
 
-experiment_year <- c(NA)
+experiment_year <- c("2003")
 
-unique_networks <-c(NA)
+Sampling_method<-"Plots 1*1 in 1 ha"
+
+Sampling_zoo_phytocentric <- "Phytocentric"
+
+unique_networks <-c(1)
 
 plant_species <- c(37)
 
@@ -110,7 +118,7 @@ network_size <- c(8325)
 
 metadata_1 <- data.frame(BIBTEXKEY, longitude, latitude, country, location,duration, 
                        experiment_year,unique_networks,plant_species, pollinator_species, 
-                       network_size)
+                       network_size, Sampling_method, Sampling_zoo_phytocentric)
 
  metadata <- rbind(metadata, metadata_1)
  
@@ -125,13 +133,17 @@ BIBTEXKEY <- c("4_bundgaard_2003")
  
  country <- c("Denmark")
  
- location <- c(NA)
+ location <- c("Moesgaard Have")
  
- duration <- c(NA)
+ duration <- c("1 season")
  
- experiment_year <- c(NA)
+ experiment_year <- c(2003)
  
- unique_networks <-c(NA)
+ Sampling_method <-"Plots 1*1m near the trail"
+ 
+ Sampling_zoo_phytocentric <- "Phytocentric"
+ 
+ unique_networks <-c(1)
  
  plant_species <- c(16)
  
[…]

### 2020-03-30 Rmd/Ideas.Rmd
Image for ideas
Metadata almost ready, lacking info of 3 networks
EDITS

@@
 ---
+
+Abstract
+
+Plant pollinator intaractions are a keystone process for ecosystem functioning.
+However, we lack comprehensive information from both plants and pollinators that can inform from this mutualistic interaction worldwide.
+In order to tackle this, we have selected 30 networks distributed across the world and looked for key floral traits of plant-pollinator interactions for a total of 1600 species.
+Here we look how these floral traits shape the different plant-pollinator networks and the main fuctional groups of insect pollinating species.
+Giving the different nature of the data collated we do not compare across networks and we focus on the main general patterns/results within network.
+We have conducted our analysis at 3 levels, 1) unique networks, 2) metawebs and by 3) grouping both.
+We find that specific traits are associated with different guilds of floral visitors within these networks.
+We also highlight the lack of information about traits and the reproductive biology of the plant species of these networks.
+Our work shows the importance of deepen in species traits in order to understand key processes that can be seen with network metrics and highlights the importance of elemental ecology for species conservation.
+
+Hypothesis
 
@@
  1) Do we have matching between specific taxa and grouping traits? Maybe show this with likelihood of visitation
-    1.1 Are selfers/self compatible species less relevant in the network? How can we interpretate that (generalist vs specialization/ connectance) We expect less dependency on pollinators...
+    1.1 Are selfers/self compatible species less relevant in the network? How can we interpretate that (generalist vs specialization/connectance) We expect less dependency on pollinators...
+
+1.2
 

### 2020-03-30 Scripts/Spp_richness_plot.R

@@ -1,0 +1,75 @@
+#Here I'm going to show graphically the main taxa per network
+
+library(dplyr)
+library(tidyr)
+library(plyr)
+
+
+#Load data
+data <- read.csv("Data/Data_processing/Long_format_metawebs_poll_taxa_added.csv")
+
+#Unique species per network
+data_network <-  unique(data[,c("Pollinator_species","Id","Pollinator_family", "Pollinator_order")])
+#There are some mistakes in the families
+#Not very relevant at the moment, fix later
+
+#Sum unique species per network (Spp richness)
+data_network_sum <- dcast(data_network,Id~Pollinator_order,value.var = "Pollinator_order")
+
+
+data_network_main_orders <- select(data_network_sum, "Id", "Coleoptera","Lepidoptera","Hymenoptera", "Diptera") 
+str(data_network_main_orders)
+
+data_network_main_orders <- data_network_main_orders[,-1]
+str(data_network_main_orders)
+clrs <- c("darkblue", "blue", "yellow", "cornsilk")
+
+data_long <- gather(data_network_main_orders, orders, measurement, Coleoptera:Diptera, factor_key=TRUE)
+
+ggplot(data_long, aes(fill=orders, y=measurement, x=Id)) + 
+  geom_bar(position="stack", stat="identity")
+
+
+
+
+barplot(data_long, beside = FALSE, ylab = "", cex.names = 0.8
+        , las = 2, col = clrs)
+
+barplot(data_network_main_orders, main="Car Distribution by Gears and VS",
+        xlab="Number of Gears",
+        legend = rownames(counts))
+
+
+# Stacked Bar Plot with Colors and Legend
+counts <- table(mtcars$vs, mtcars$gear)
+str(counts)
+barplot(counts, main="Car Distribution by Gears and VS",
+        xlab="Number of Gears", col=c("darkblue","red"),
+        legend = rownames(counts))
+
+
+
+
+
+library(ggplot2)
+
+# create a dataset
+specie <- c(rep("sorgho" , 3) , rep("poacee" , 3) , rep("banana" , 3) , rep("triticum" , 3) )
+condition <- rep(c("normal" , "stress" , "Nitrogen") , 4)
+value <- abs(rnorm(12 , 0 , 15))
+data <- data.frame(specie,condition,value)
+
+# Stacked
+ggplot(data, aes(fill=condition, y=value, x=specie)) + 
+  geom_bar(position="stack", stat="identity")
+
+library(tidyr)
+
+# The arguments to gather():
+# - data: Data object
[…]

### 2020-04-01 Rmd/Draft.Rmd
Preparing draft of ideas

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
fontsize: 12pt
header-includes:
    - \usepackage{setspace}\doublespacing
---
Here I'm going to try to understand our data a bit better and state our hypothesis.

First I start with an abstract that could be our guide for hypothesis testing and analyses.

#Abstract

Plant pollinator intaractions are a keystone process for ecosystem functioning. However, we lack comprehensive information from both plants and pollinators that can inform from this mutualistic interaction worldwide. In order to tackle this, we have selected 30 networks distributed across the world and looked for key floral traits of plant-pollinator interactions for a total of 1600 species. Here we look how these floral traits shape the different plant-pollinator networks and the main fuctional groups of insect pollinating species. Giving the different nature of the data collated we do not compare across networks and we focus on the main general patterns/results within network. We have conducted our analysis at 3 levels, 1) unique networks, 2) metawebs and by 3) grouping both. We find that specific traits are associated with different guilds of floral visitors within these networks. We also highlight the lack of information about traits and the reproductive biology of the plant species of these networks. Our work shows the importance of deepen in species traits in order to understand key processes that can be seen with network metrics and highlights the importance of elemental ecology for species conservation.

*What sort of data do we have?*

Approximately 1600 species from 30 different networks (including metawebs and unique networks, if I split the metawebs into unique networks this number will increase quite a bit but we will lose some data because not all of them can be reduced to that level). Importantly, we do not have information for all the traits and the analyses will be with subsets of species from these networks.

This data is quantitative (visitation number) and qualitative (binary, 1's and 0's).
CHECK NUMBER OF EACH

Now I'm going to show graphically where these networks are located and how few of these traits vary across them.

\newpage

Here I show the percentage or orders from the different species without consider visitation and just richness of species. Therfore, if we have a network with 4 species from from different orders, each will appear as 25% within the stack bar of the barplot.

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center'}
setwd("~/R_Projects/Reproductive Traits")

data2 <- readRDS("Data/RData/Spp_richness_by_order.RData")
clrs <- c("darkblue", "blue", "yellow", "cornsilk", "goldenrod",
          "orange")
par(mar = c(11,6.1,4.1,8))
barplot(data2, beside = FALSE, ylab = "% visits", cex.names = 0.5
        ,las = 2, col = clrs)
abline (h = 0)
par(xpd=TRUE)
leg <- c("Hymenoptera", "Coleoptera", "Lepidoptera", "Diptera", "Hemiptera")
legend(x = 35, y = 100, legend = rev(leg), cex = 0.4, fill = rev(clrs))
par(mar = c(5,1.1,4.1,2.1))
par(xpd=FALSE)

```

\newpage

### 2020-04-01 Rmd/Draft.Rmd
Compiling figures in draft doc

@@
 
+**PLOT 1**
+
 Here I show the percentage or orders from the different species without consider visitation and just richness of species.
@@
 \newpage
+
+**PLOT 2**
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center'}
+library(ggplot2)
+library(scatterpie)
+library(sf)
+world <- map_data('world')
+setwd("~/R_Projects/Reproductive Traits")
+data_merged_sub_ord <- readRDS("Data/RData/Breeding_systems_plot.RData")
+
+p <- ggplot(world, aes(long, lat)) +
+  geom_map(map=world, aes(map_id=region), fill="white", color="black") +
+  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
+p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
+ data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:9)]),alpha=.8)+ 
+  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:9)]),
+ labels = c("Hermaphroditism", "Dioecy", "Monoecy"),values = c("Hermaphroditism" = "#4DAF4A",
+ "Monoecy" = "#984EA3","Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
+  caption = "",fill = NULL) + theme(legend.position = c(0.215, 0.009),legend.justification = c(1, 0),
+  axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +
+  geom_segment(data = data_merged_sub_ord,aes(x = 168, y = -34, xend = 172, yend = -43),color = "black", size = 0.3, alpha = 0.2) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = 179, y = -46, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.2) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = 164, y = -48, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.2) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = 6, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.2) +  #GALAPAGOS
+  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = -7, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.2) + #GALAPAGOS
+  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -12), color = "black", size = 0.3, alpha = 0.2) + #MAURITIUS
+  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -28), color = "black", size = 0.3, alpha = 0.2) + #MAURITIUS
+  geom_segment(data = data_merged_sub_ord, aes(x = -51, y = 10, xend = -61, yend = 5.5), color = "black", size = 0.3, alpha = 0.2) + #VENEZUELA
+  geom_segment(data = data_merged_sub_ord, aes(x = -51, y =25 , xend = -67, yend = 8.9), color = "black", size = 0.3, alpha = 0.2) + #VENEZUELA
+  geom_segment(data = data_merged_sub_ord, aes(x = 148, y = 35, xend = 135.8, yend = 35), color = "black", size = 0.3, alpha = 0.2) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 140, y = 22, xend = 129, yend = 28), color = "black", size = 0.3, alpha = 0.2) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -15.5, y = 32, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.2) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = -15, y = 50, xend = 3, yend = 43), color = "black", size = 0.3, alpha = 0.2) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -24, y = 40, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.2) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -84, y = -32, xend = -68, yend = -32), color = "black", size = 0.3, alpha = 0.2) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = -36, y = -21, xend = -58, yend = -21), color = "black", size = 0.3, alpha = 0.2) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 34, y = 78, xend = 18.5, yend = 68), color = "black", size = 0.3, alpha = 0.2) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 0, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.2) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 15, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.2) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -8, y = 61, xend = 1.5, yend = 52), color = "black", size = 0.3, alpha = 0.2) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 39, y = 60, xend = 9, yend = 56), color = "black", size = 0.3, alpha = 0.2) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 126, y = -36, xend = 148, yend = -36), color = "black", size = 0.3, alpha = 0.2) + #AUS
+  geom_segment(data = data_merged_sub_ord, aes(x = 90, y = 6, xend = 100, yend = 28), color = "black", size = 0.3, alpha = 0.2) + #CHINA
+  geom_segment(data = data_merged_sub_ord, aes(x = -66, y = 39, xend = -89, yend = 39), color = "black", size = 0.3, alpha = 0.2) + #USA
+  geom_segment(data = data_merged_sub_ord, aes(x = -48, y = 52, xend = -75, yend = 45), color = "black", size = 0.3, alpha = 0.2) + #CANADA
+  geom_segment(data = data_merged_sub_ord, aes(x = -71, y = 86, xend = -71, yend = 81), color = "black", size = 0.3, alpha = 0.2) + #CANADA
+  geom_segment(data = data_merged_sub_ord, aes(x = -52, y = 86, xend = -52, yend = 71), color = "black", size = 0.3, alpha = 0.2) + #GREENLAND
+  geom_segment(data = data_merged_sub_ord, aes(x = -20, y = 86, xend = -20, yend = 74), color = "black", size = 0.3, alpha = 0.2)
+```
+
+\newpage
+
+**PLOT 3**
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center'}
+library(ggplot2)
+library(scatterpie)
+library(sf)
+world <- map_data('world')
+setwd("~/R_Projects/Reproductive Traits")
+data_merged_sub_ord <- readRDS("Data/RData/Compatibility_system_plot.RData")
+
+p <- ggplot(world, aes(long, lat)) +
+  geom_map(map=world, aes(map_id=region), fill="white", color="grey", size=0.35) +
+  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
+p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
+ data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:9)]),alpha=.8)+ 
+  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:9)]),
+ labels = c("Partially self compatible", "Self compatible", "Self incompatible"),values = c("partially_self_compatible" = "#4DAF4A","self_compatible" = "#984EA3","self_incompatible" = "orange")) +labs(title = "Compatibility system",subtitle = "", caption = "",fill = NULL) + theme(legend.position = c(0.18, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),
+  axis.ticks = element_blank(),legend.key.size = unit(0.16, "cm")) +
+  geom_segment(data = data_merged_sub_ord,aes(x = 168, y = -34, xend = 172, yend = -43),color = "black", size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = 179, y = -46, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = 164, y = -48, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = 6, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) +  #GALAPAGOS
+  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = -7, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) + #GALAPAGOS
+  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -12), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
+  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -28), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
+  geom_segment(data = data_merged_sub_ord, aes(x = -51, y = 10, xend = -61, yend = 5.5), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
+  geom_segment(data = data_merged_sub_ord, aes(x = -51, y =25 , xend = -67, yend = 8.9), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
+  geom_segment(data = data_merged_sub_ord, aes(x = 148, y = 35, xend = 135.8, yend = 35), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 140, y = 22, xend = 129, yend = 28), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -15.5, y = 32, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = -15, y = 50, xend = 3, yend = 43), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -24, y = 40, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -84, y = -32, xend = -68, yend = -32), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = -36, y = -21, xend = -58, yend = -21), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 34, y = 78, xend = 18.5, yend = 68), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 0, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 15, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -8, y = 61, xend = 1.5, yend = 52), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 39, y = 60, xend = 9, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 126, y = -36, xend = 148, yend = -36), color = "black", size = 0.3, alpha = 0.8) + #AUS
+  geom_segment(data = data_merged_sub_ord, aes(x = 90, y = 6, xend = 100, yend = 28), color = "black", size = 0.3, alpha = 0.8) + #CHINA
+  geom_segment(data = data_merged_sub_ord, aes(x = -66, y = 39, xend = -89, yend = 39), color = "black", size = 0.3, alpha = 0.8) + #USA
+  geom_segment(data = data_merged_sub_ord, aes(x = -48, y = 52, xend = -75, yend = 45), color = "black", size = 0.3, alpha = 0.8) + #CANADA
+  geom_segment(data = data_merged_sub_ord, aes(x = -71, y = 86, xend = -71, yend = 81), color = "black", size = 0.3, alpha = 0.8) + #CANADA
+  geom_segment(data = data_merged_sub_ord, aes(x = -52, y = 86, xend = -52, yend = 71), color = "black", size = 0.3, alpha = 0.8) + #GREENLAND
+  geom_segment(data = data_merged_sub_ord, aes(x = -20, y = 86, xend = -20, yend = 74), color = "black", size = 0.3, alpha = 0.8)
+```

### 2020-04-01 Scripts/World_Map_Breeding_Systems.R

@@ -6,6 +6,7 @@ library(ggplot2)
 library(dbplyr)
 library(scatterpie)
 library(reshape2)
+library(sf)
 # READ LONG FORMAT DATA
 Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")
 
@@ -179,6 +180,9 @@ data_merged_sub_ord[15,4] <- 92
 
 data_merged_sub_ord[16,4] <- 92
 data_merged_sub_ord[9,4] <- 92
+
+Breeding_systems_plot <- data_merged_sub_ord
+#saveRDS(Breeding_systems_plot, "Data/RData/Breeding_systems_plot.RData")
 
 #network size fix
 

### 2020-04-01 Rmd/Draft.Rmd
Preparing draft with ideas and plots

@@
 ---
-title: "Untitled"
+title: "Draft"
 output:
@@
     - \usepackage{setspace}\doublespacing
+bibliography: 
+  - references.bib
 ---
@@
 
-#Abstract
+#Abstract (draft)
 
-Plant pollinator intaractions are a keystone process for ecosystem functioning.
+Plant pollinator interactions are a keystone process for ecosystem functioning.
 However, we lack comprehensive information from both plants and pollinators that can inform from this mutualistic interaction worldwide.
@@
 Approximately 1600 species from 30 different networks (including metawebs and unique networks, if I split the metawebs into unique networks this number will increase quite a bit but we will lose some data because not all of them can be reduced to that level).
+Metawebs inform about the regional species pool, where for our case, different years or multiple locations when the plant species are shared are combined in aunique network.
 Importantly, we do not have information for all the traits and the analyses will be with subsets of species from these networks.
 
+Noreika 2019
+
+@noreika2019
 This data is quantitative (visitation number) and qualitative (binary, 1's and 0's).
@@
 ```
+
+\newpage
+
+**PLOT 4**
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center'}
+library(ggplot2)
+library(scatterpie)
+library(sf)
+world <- map_data('world')
+setwd("~/R_Projects/Reproductive Traits")
+data_merged_sub_ord <- readRDS("Data/RData/Life_Form_plot.RData")
+
+p <- ggplot(world, aes(long, lat)) +
+  geom_map(map=world, aes(map_id=region), fill="white", color="black") +
+  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
+p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
+                     data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:10)]),alpha=.8)+ 
+  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:10)]),
+                    labels = c("Herb", "Shrub", "Tree", "Vine"),values = c("herb" = "#4DAF4A",
+                                                                           "shrub" = "#984EA3","tree" = "orange", "vine" = "lightblue")) +labs(title = "Life form",subtitle = "",
+                                                                                                                                               caption = "",fill = NULL) + theme(legend.position = c(0.12, 0.009),legend.justification = c(1, 0),
+                                                                                                                                                                                 axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +
+  geom_segment(data = data_merged_sub_ord,aes(x = 168, y = -34, xend = 172, yend = -43),color = "black", size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = 179, y = -46, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = 164, y = -48, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
+  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = 6, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) +  #GALAPAGOS
+  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = -7, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) + #GALAPAGOS
+  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -12), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
+  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -28), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
+  geom_segment(data = data_merged_sub_ord, aes(x = -51, y = 10, xend = -61, yend = 5.5), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
+  geom_segment(data = data_merged_sub_ord, aes(x = -51, y =25 , xend = -67, yend = 8.9), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
+  geom_segment(data = data_merged_sub_ord, aes(x = 148, y = 35, xend = 135.8, yend = 35), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 140, y = 22, xend = 129, yend = 28), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -15.5, y = 32, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = -15, y = 50, xend = 3, yend = 43), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -24, y = 40, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -84, y = -32, xend = -68, yend = -32), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = -36, y = -21, xend = -58, yend = -21), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 34, y = 78, xend = 18.5, yend = 68), color = "black", size = 0.3, alpha = 0.8) + 
+  geom_segment(data = data_merged_sub_ord, aes(x = 0, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 15, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = -8, y = 61, xend = 1.5, yend = 52), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 39, y = 60, xend = 9, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
+  geom_segment(data = data_merged_sub_ord, aes(x = 126, y = -36, xend = 148, yend = -36), color = "black", size = 0.3, alpha = 0.8) + #AUS
+  geom_segment(data = data_merged_sub_ord, aes(x = 90, y = 6, xend = 100, yend = 28), color = "black", size = 0.3, alpha = 0.8) + #CHINA
+  geom_segment(data = data_merged_sub_ord, aes(x = -66, y = 39, xend = -89, yend = 39), color = "black", size = 0.3, alpha = 0.8) + #USA
+  geom_segment(data = data_merged_sub_ord, aes(x = -48, y = 52, xend = -75, yend = 45), color = "black", size = 0.3, alpha = 0.8) + #CANADA
+  geom_segment(data = data_merged_sub_ord, aes(x = -71, y = 86, xend = -71, yend = 81), color = "black", size = 0.3, alpha = 0.8) + #CANADA
+  geom_segment(data = data_merged_sub_ord, aes(x = -52, y = 86, xend = -52, yend = 71), color = "black", size = 0.3, alpha = 0.8) + #GREENLAND
+  geom_segment(data = data_merged_sub_ord, aes(x = -20, y = 86, xend = -20, yend = 74), color = "black", size = 0.3, alpha = 0.8)
+
+```

### 2020-04-01 Rmd/Draft.Rmd
adding references to markdown

@@
     - \usepackage{setspace}\doublespacing
-bibliography: 
-  - references.bib
+bibliography: [references.bib]
 ---
@@
 Approximately 1600 species from 30 different networks (including metawebs and unique networks, if I split the metawebs into unique networks this number will increase quite a bit but we will lose some data because not all of them can be reduced to that level).
-Metawebs inform about the regional species pool, where for our case, different years or multiple locations when the plant species are shared are combined in aunique network.
+Metawebs inform about the regional species pool [@noreika2019pollinator], where for our case, different years or multiple locations when the plant species are shared are combined in aunique network.
 Importantly, we do not have information for all the traits and the analyses will be with subsets of species from these networks.
 
-Noreika 2019
-
-@noreika2019
 This data is quantitative (visitation number) and qualitative (binary, 1's and 0's).

### 2020-04-02 Rmd/Draft.Rmd
preparing metadata and now organizing networks

@@
 ---
-title: "Draft"
+title: "Chapter 2 Draft"
 output:
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center'}
+\vspace{4cm}
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center', fig.width=10,fig.height=7}
 setwd("~/R_Projects/Reproductive Traits")

### 2020-04-02 Scripts/Data_preparation/1_Metadata_preparation.R

@@ -186,7 +186,7 @@ BIBTEXKEY <- c("4_bundgaard_2003")
  
  unique_networks <-c(4)
  
- Data_type <- "Qualitative"
+ Data_type <- "Quantitative"
  
  plant_species <- c(59)
  

### 2020-04-03 Rmd/Draft.Rmd
Olesen 2002 added with quantitative data

@@
 par(mar = c(11,6.1,4.1,8))
-barplot(data2, beside = FALSE, ylab = "% visits", cex.names = 0.5
+barplot(data2, beside = FALSE, ylab = "% Spp per order", cex.names = 0.5
         ,las = 2, col = clrs)

### 2020-04-06 Rmd/Networks_Information.Rmd
Metadata and complementary rmd file explaining the processing of each network

---
output: html_document
fontsize: 12pt
header-includes:
    - \usepackage{setspace}\doublespacing
---

#Networks information

Here I'm going to record the processing history and adittional information, complementary to the metadata of the networks. Also I will justify when we group the networks as metaweb.

__1 carpobrotus_metaweb_Bartomeus_2008__

We have build a metaweb with three different networks that share most of the plant species.

__2_metaweb_opuntia_Bartomeus_2008__

We have build a metaweb with three different networks that share most of the plant species.

__3_bek_2006__

Master student of Jens Olesen that built an entire network for his thesis.

__4_bundgaard_2003__

Master student of Jens Olesen that built a network for his thesis, sampling on the sides of the road. Quite close to Bek's 2006 network (few hundred meters away).

__5_metaweb_chacoff_2011__

Metaweb from journal without modifications.

__6_metaweb_dicks_2002__

We have combined the two networks provided in this journal article in a unique metaweb. The meadows share a great number of species and in the article they are described as similar systems. From google maps, they seems to be 60-80 kms away from each other.

__7_metaweb_dupont_2009__

There are three networks available with three different sites (obtained from online databases). However, with quantitative data (visitation) just one from the article, seems to be an error with the supplementary material. I have no been able to get the three of them.

__8_elberling_1999__

One unique network with quantitative data. I have passed it manually from the original paper due to the online databases have mistakes in the data and binary.

__9_dupont_2009_zackenberg__

Unique network sampled during one season.

__10_metaweb_fang_huang_2012__

I have combined the data obtained from the journal article in a unique metaweb. There three networks from 3 different seasons.

__11_metaweb_inouye_1990__

Metaweb with multiple seasons. No modifications made.

__12_inouye_1988__

One unique network without modifications.

__13_metaweb_kaiser_bunbury_2009__

One unique network sampled during one season.

__14_metaweb_kaiser_bunbury_2014__

I have merged the 48 sites sampled in a heterogeneous landscape and created a metaweb. Just 6 different sites.

__15_metaweb_kato_2000__

Metaweb obtained from web of life. I have not done modifications to the dataset. Quantitative data.

__16_kevan_1970__

One unique network from one season. I have not modified the data. Obtained from web of life.

__17_lundgren_2005__

One unique network from one season. I have not modified the data.

__18_olesen_2002_mauritius__

One unique network, I have passed manually in order to have the visitation data.

__19_mcmullen_1993__

Metaweb from all the islands. From web of life.

__20_metaweb_arthurs_pass_primack_1983__

Netwrok from web of life, binary data. I have not modified it.

__21_metaweb_cass_primack_1983__

Netwrok from web of life, binary data. I have not modified it.

__22_metaweb_craigieburn_primack_1983__

Netwrok from web of life, binary data. I have not modified it.

__23_ramirez_1989__

Data from web of life. I have not modified the data.

__24_metaweb_ramirez_1992__

Metaweb from web of life without modifications.

__25_metaweb_robertson_1929__

Metaweb from web of life without modifications.

__26_small_1976__

Unique network with quantitative data without modifications.

__27_chaco_souza_2018__

Unique network with quantitative data without modifications.

__28_metaweb_traveset_2013__

Metaweb with networks from different islands from journal.

__29_metaweb_bartomeus_unpublished_data_2015__

Metaweb with networks from different sites. I made a subset of this data by transects.

__30_olesen_2002_azores__

Unique network without modifications. I have passed the data manually from source.

### 2020-04-06 Scripts/Data_preparation/1_Metadata_preparation.R

@@ -132,7 +132,7 @@ metadata_2 <- data.frame(BIBTEXKEY, longitude, latitude, country, location,durat
                        network_size,Sampling_method, Sampling_zoo_phytocentric, Data_type)
 
 
-metadata <- rbind(metadata, metadata_2)
+metadata <- rbind(metadata_1, metadata_2)
 
 
 
@@ -409,10 +409,10 @@ BIBTEXKEY <- c("7_metaweb_dupont_2009")
  metadata <- rbind(metadata, metadata_8)
  
  
- #9th  Elberling unpublished data
+ #9th  Dupont 2009
  
  
- BIBTEXKEY <- c("9_elberling_unpublished_data")
+ BIBTEXKEY <- c("9_dupont_2009_zackenberg")
  
  longitude <- c(-20.5)
  
@@ -472,7 +472,7 @@ fang_huang_3 <- melt(fang_huang_3)
  #write.csv(metaweb_fang_huang_2012, "Data_networks_metawebs/10_metaweb_fang_huang_2012.csv")
  
 
-  BIBTEXKEY <- c("10_metaweb_fang_huang_2012")
+ BIBTEXKEY <- c("10_metaweb_fang_huang_2012")
  
  longitude <- c(99.63806)
  
@@ -588,25 +588,25 @@ metadata <- rbind(metadata, metadata_12)
 
 #Carpobrutus metaweb
 
-control_kaiser_bunbury_2009 <- read.csv("Data/Data_networks/13_control_kaiser_bunbury_2009.csv")
-restored_kaiser_bunbury_2009 <- read.csv("Data/Data_networks/13_restored_kaiser_bunbury_2009.csv")
+#control_kaiser_bunbury_2009 <- read.csv("Data/Data_networks/13_control_kaiser_bunbury_2009.csv")
+#restored_kaiser_bunbury_2009 <- read.csv("Data/Data_networks/13_restored_kaiser_bunbury_2009.csv")
 
-control_kaiser_bunbury_2009 <- melt(control_kaiser_bunbury_2009)
-restored_kaiser_bunbury_2009 <- melt(restored_kaiser_bunbury_2009)
+#control_kaiser_bunbury_2009 <- melt(control_kaiser_bunbury_2009)
+#restored_kaiser_bunbury_2009 <- melt(restored_kaiser_bunbury_2009)
 
-colnames(control_kaiser_bunbury_2009) <- c("Plant_species", "Pollinator_species", "Interaction")
[…]

### 2020-04-07 Rmd/Draft.Rmd
Updating long format networks with quantitative data from some networks

@@
 Metawebs inform about the regional species pool [@noreika2019pollinator], where for our case, different years or multiple locations when the plant species are shared are combined in aunique network.
-Importantly, we do not have information for all the traits and the analyses will be with subsets of species from these networks.
+Importantly, we do not have information for all the traits and the analyses are likely to be done with subsets of species of these networks.
 
-This data is quantitative (visitation number) and qualitative (binary, 1's and 0's).
-CHECK NUMBER OF EACH
-
-Now I'm going to show graphically where these networks are located and how few of these traits vary across them.
+The type of the data of the networks is binary and qunatitative (visitation).
+We have 13 networks/metawebs with binary data and 17 with quantitative.
+All the networks where phytocentric (built from plants).
+These networks were obtained from journals/online databases or directly from the authors.
+We have selected networks from very different regions of the world to have in order to have a big picture of how these different floral traits shape the different pollinator taxa and network metrics.
 
@@
 
+\vspace{4cm}
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center', fig.width=10,fig.height=7}
+setwd("~/R_Projects/Reproductive Traits")
+
+data2 <- readRDS("Data/RData/Spp_richness_by_order.RData")
+clrs <- c("darkblue", "blue", "yellow", "cornsilk", "goldenrod",
+          "orange")
+par(mar = c(11,6.1,4.1,8))
+barplot(data2, beside = FALSE, ylab = "% Spp per order", cex.names = 0.5
+        ,las = 2, col = clrs)
+abline (h = 0)
+par(xpd=TRUE)
+leg <- c("Hymenoptera", "Coleoptera", "Lepidoptera", "Diptera", "Hemiptera")
+legend(x = 35, y = 100, legend = rev(leg), cex = 0.4, fill = rev(clrs))
+par(mar = c(5,1.1,4.1,2.1))
+par(xpd=FALSE)
+
+```
+
+\newpage
 **PLOT 2**

### 2020-04-07 Rmd/Draft.Rmd
Visitation plot

@@
 
-data2 <- readRDS("Data/RData/Spp_richness_by_order.RData")
+data2 <- readRDS("Data/RData/Spp_visitation_per_order.RData")
+
 clrs <- c("darkblue", "blue", "yellow", "cornsilk", "goldenrod",
           "orange")
+
+colnames(data2) <- c("Bartomeus unp. 2015", "Chacoff 2011","Bartomeus 2008 1", "Bartomeus 2008 2","Small 1976",
+                     "Inouye 1990", "Souza 2018", "Inouye 1988", "Dupont 2009 1", "Olesen 2002 1", "Fang huang 2012", "Olesen 2002 2", "Dicks 2002", "Elberling 1999","Kato 2000", "Kaiser-Bunbunry 2009", "Traveset 2013", "Kaiser-Bunbury 2014","Lundgren 2005")
+
 par(mar = c(11,6.1,4.1,8))

### 2020-04-09 Rmd/Visitation_stacked_barplot.Rmd
Adding images near legend

---
title: "Visitation_stacked_barplot"
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE}
library(dplyr)
library(tidyr)
library(plyr)
library(ggplot2)
library(reshape2)
library(scales)
library(devtools)
library(png)
library(grid)
dev_mode(on=T)

setwd("~/R_Projects/Reproductive Traits")

img <- readPNG(system.file("img", "Rlogo.png", package="png"))
g <- rasterGrob(img, interpolate=TRUE)

net_long_1 <- readRDS("Data/RData/Spp_visitation_per_order_long.RData")

l <- c("Bartomeus unp. 2015", "Chacoff 2011","Bartomeus 2008 1", "Bartomeus 2008 2","Small 1976",
       "Inouye 1990", "Souza 2018", "Inouye 1988", "Dupont 2009", "Olesen 2002 1", "Fang huang 2012", "Olesen 2002 2", "Dicks 2002",
       "Elberling 1999","Kato 2000", "Kaiser-Bunbunry 2009", "Traveset 2013", "Kaiser-Bunbury 2014","Lundgren 2005")
legend_title <- "Taxonomic groups"

 ggplot(net_long_1) +
  aes(x = reorder(Id,-order), 
      y = measurement, 
      fill =factor(orders, levels=c("Hemiptera","Coleoptera","Lepidoptera","Diptera", "Hymenoptera"))) +
  geom_bar(position = "fill", stat = "identity", alpha=0.6) +coord_flip() +scale_x_discrete(labels= l) + 
  scale_fill_manual(legend_title,values=c("indianred", "gray49", "seagreen", "darkgoldenrod2", "#386cb0")) + theme_classic()+xlab("Networks")+ylab("Percentage of visits") +  scale_y_continuous(labels = scales::percent)

```

### 2020-04-09 Rmd/Visitation_stacked_barplot.Rmd
visitation plot legend

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8}
 library(dplyr)
@@
 library(grid)
+library(gridExtra)
+library(jpeg)
 dev_mode(on=T)
@@
 
-l <- c("Bartomeus unp. 2015", "Chacoff 2011","Bartomeus 2008 1", "Bartomeus 2008 2","Small 1976",
+la <- c("Bartomeus unp. 2015", "Chacoff 2011","Bartomeus 2008 1", "Bartomeus 2008 2","Small 1976",
        "Inouye 1990", "Souza 2018", "Inouye 1988", "Dupont 2009", "Olesen 2002 1", "Fang huang 2012", "Olesen 2002 2", "Dicks 2002",
@@
 
- ggplot(net_long_1) +
+ get_png <- function(filename) {
+  grid::rasterGrob(png::readPNG(filename), interpolate = TRUE)
+}
+
+l <- get_png("Images/lepidoptera_2.png")
+bumb <- get_png("Images/bumblebee.png")
+dip <- get_png("Images/diptera.png")
+beet <- get_png("Images/beetle.png")
+hem<- get_png("Images/hemiptera.png")
+
+t <- grid::roundrectGrob(x=0.5, y=0.5, width=1, height=1)
+
+p<- ggplot(net_long_1) +
   aes(x = reorder(Id,-order), 
@@
       fill =factor(orders, levels=c("Hemiptera","Coleoptera","Lepidoptera","Diptera", "Hymenoptera"))) +
-  geom_bar(position = "fill", stat = "identity", alpha=0.6) +coord_flip() +scale_x_discrete(labels= l) + 
-  scale_fill_manual(legend_title,values=c("indianred", "gray49", "seagreen", "darkgoldenrod2", "#386cb0")) + theme_classic()+xlab("Networks")+ylab("Percentage of visits") +  scale_y_continuous(labels = scales::percent)
+  geom_bar(position = "fill", stat = "identity", alpha=0.6) +coord_flip() +scale_x_discrete(labels= la) + 
+  scale_fill_manual(legend_title,values=c("indianred", "gray49", "seagreen", "darkgoldenrod2", "#386cb0")) + theme_classic()+xlab("Networks")+ylab("Percentage of visits") +scale_y_continuous(labels = scales::percent) + theme(legend.background = element_rect(fill=alpha('blue', 0.0)))+
+  annotation_custom(l, xmin = 9.365, xmax = 10.0, ymin = 1.03, ymax =1.09) + annotation_custom(bumb, xmin = 7.1, xmax = 9.3, ymin = 1.03, ymax =1.09)+ annotation_custom(dip, xmin = 8.65, xmax = 9.25, ymin = 1.035, ymax =1.085)+
+  coord_cartesian(clip = "off") + annotation_custom(beet, xmin = 9.96, xmax = 10.76, ymin = 0.86, ymax =1.255)+ annotation_custom(hem, xmin = 10.86, xmax = 11.36, ymin = 0.883, ymax =1.233)+
+  coord_cartesian(clip = "off")+ coord_flip()
 
+gg_table <- ggplot_gtable(ggplot_build(p))
+gg_table$layout$clip[gg_table$layout$name=="panel"] <- "off"
+grid.draw(gg_table)
+
+#Bumblebee image credit to Melissa Broussard
 ```

### 2020-04-09 Rmd/Draft.Rmd
Adding edits to draft file

--- 2020-04-07 Rmd/Draft.Rmd
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center', fig.width=10,fig.height=7}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8}
+library(dplyr)
+library(tidyr)
+library(plyr)
+library(ggplot2)
+library(reshape2)
+library(scales)
+library(devtools)
+library(png)
+library(grid)
+library(gridExtra)
+library(jpeg)
+dev_mode(on=T)
+
 setwd("~/R_Projects/Reproductive Traits")
 
-data2 <- readRDS("Data/RData/Spp_richness_by_order.RData")
-clrs <- c("darkblue", "blue", "yellow", "cornsilk", "goldenrod",
-          "orange")
-par(mar = c(11,6.1,4.1,8))
-barplot(data2, beside = FALSE, ylab = "% Spp per order", cex.names = 0.5
-        ,las = 2, col = clrs)
-abline (h = 0)
-par(xpd=TRUE)
-leg <- c("Hymenoptera", "Coleoptera", "Lepidoptera", "Diptera", "Hemiptera")
-legend(x = 35, y = 100, legend = rev(leg), cex = 0.4, fill = rev(clrs))
-par(mar = c(5,1.1,4.1,2.1))
-par(xpd=FALSE)
+img <- readPNG(system.file("img", "Rlogo.png", package="png"))
+g <- rasterGrob(img, interpolate=TRUE)
+
+net_long_1 <- readRDS("Data/RData/Spp_visitation_per_order_long.RData")
+
+la <- c("Bartomeus unp. 2015", "Chacoff 2011","Bartomeus 2008 1", "Bartomeus 2008 2","Small 1976",
+       "Inouye 1990", "Souza 2018", "Inouye 1988", "Dupont 2009", "Olesen 2002 1", "Fang huang 2012", "Olesen 2002 2", "Dicks 2002",
+       "Elberling 1999","Kato 2000", "Kaiser-Bunbunry 2009", "Traveset 2013", "Kaiser-Bunbury 2014","Lundgren 2005")
+legend_title <- "Taxonomic groups"
+
+ get_png <- function(filename) {
+  grid::rasterGrob(png::readPNG(filename), interpolate = TRUE)
+}
+
+l <- get_png("Images/lepidoptera_2.png")
+bumb <- get_png("Images/bumblebee.png")
+dip <- get_png("Images/diptera.png")
+beet <- get_png("Images/beetle.png")
+hem<- get_png("Images/hemiptera.png")
+
+t <- grid::roundrectGrob(x=0.5, y=0.5, width=1, height=1)
+
+p<- ggplot(net_long_1) +
+  aes(x = reorder(Id,-order), 
+      y = measurement, 
+      fill =factor(orders, levels=c("Hemiptera","Coleoptera","Lepidoptera","Diptera", "Hymenoptera"))) +
+  geom_bar(position = "fill", stat = "identity", alpha=0.6) +coord_flip() +scale_x_discrete(labels= la) + 
+  scale_fill_manual(legend_title,values=c("indianred", "gray49", "seagreen", "darkgoldenrod2", "#386cb0")) + theme_classic()+xlab("Networks")+ylab("Percentage of visits") +scale_y_continuous(labels = scales::percent) + theme(legend.background = element_rect(fill=alpha('blue', 0.0)))+
+  annotation_custom(l, xmin = 9.365, xmax = 10.0, ymin = 1.03, ymax =1.09) + annotation_custom(bumb, xmin = 7.1, xmax = 9.3, ymin = 1.03, ymax =1.09)+ annotation_custom(dip, xmin = 8.65, xmax = 9.25, ymin = 1.035, ymax =1.085)+
+  coord_cartesian(clip = "off") + annotation_custom(beet, xmin = 9.96, xmax = 10.76, ymin = 0.86, ymax =1.255)+ annotation_custom(hem, xmin = 10.86, xmax = 11.36, ymin = 0.883, ymax =1.233)+
+  coord_cartesian(clip = "off")+ coord_flip()
+
+gg_table <- ggplot_gtable(ggplot_build(p))
+gg_table$layout$clip[gg_table$layout$name=="panel"] <- "off"
+grid.draw(gg_table)
+
+#Bumblebee image credit to Melissa Broussard
 

### 2020-04-10 Rmd/Draft.Rmd
Not much today, advanced a bit with the draft of ideas

@@
 
-Approximately 1600 species from 30 different networks (including metawebs and unique networks, if I split the metawebs into unique networks this number will increase quite a bit but we will lose some data because not all of them can be reduced to that level).
-Metawebs inform about the regional species pool [@noreika2019pollinator], where for our case, different years or multiple locations when the plant species are shared are combined in aunique network.
-Importantly, we do not have information for all the traits and the analyses are likely to be done with subsets of species of these networks.
+There are approximately 1600 species from 30 different networks.
+All of these networks are phytocentric (built from plants).
+The different plant-pollinator communities have been studied with very different sampling effort and methodologies.
+Therefore, our aim is not to compare across studies but to create a general picture of how floral traits shape the different pollinator taxa and network metrics.
+Here, we combine the studies with multiple years of sampling and multiple sites within an area in metawebs.
+These networks give a broader perspective of the sampling area and inform about the regional species pool [@noreika2019pollinator].
+The data of these networks is quantitative (visitation) or qualitative (binary), there are in total 19 and 11 networks/metawebs of each, respectively.
 
-The type of the data of the networks is binary and qunatitative (visitation).
-We have 13 networks/metawebs with binary data and 17 with quantitative.
-All the networks where phytocentric (built from plants).
-These networks were obtained from journals/online databases or directly from the authors.
-We have selected networks from very different regions of the world to have in order to have a big picture of how these different floral traits shape the different pollinator taxa and network metrics.
+\blandscape
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,}
+setwd("~/R_Projects/Reproductive Traits")
+library(kableExtra)
+
+m <- read.csv("Data/Data_processing/metadata.csv")
+kable(m)
+```
+
+\elandscape
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center', fig.width=10,fig.height=7}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8}
+library(dplyr)
+library(tidyr)
+library(plyr)
+library(ggplot2)
+library(reshape2)
+library(scales)
+library(devtools)
+library(png)
+library(grid)
+library(gridExtra)
+library(jpeg)
+dev_mode(on=T)
+
 setwd("~/R_Projects/Reproductive Traits")
 
-data2 <- readRDS("Data/RData/Spp_richness_by_order.RData")
-clrs <- c("darkblue", "blue", "yellow", "cornsilk", "goldenrod",
-          "orange")
-par(mar = c(11,6.1,4.1,8))
-barplot(data2, beside = FALSE, ylab = "% Spp per order", cex.names = 0.5
-        ,las = 2, col = clrs)
-abline (h = 0)
-par(xpd=TRUE)
-leg <- c("Hymenoptera", "Coleoptera", "Lepidoptera", "Diptera", "Hemiptera")
-legend(x = 35, y = 100, legend = rev(leg), cex = 0.4, fill = rev(clrs))
-par(mar = c(5,1.1,4.1,2.1))
-par(xpd=FALSE)
+img <- readPNG(system.file("img", "Rlogo.png", package="png"))
+g <- rasterGrob(img, interpolate=TRUE)
 
+net_long_1 <- readRDS("Data/RData/species_per_order_percentage.RData")
+
+legend_title <- "Taxonomic groups"
+
+la <- c("Ramirez 1989", "Ramirez 1992", "Bartomeus unp.
+2015", "Chacoff 2011","Bartomeus 2008 1", "Bartomeus 2008 2", "Robertson 1929", "Small 1976","Inouye 1990", "Souza 2018", "Bundgaard 2003", "Inouye 1988", "Dupont 2009 1", "Olesen 2002 1", "Fang huang 2012", "mcmullen 1993", "Olesen 2002 2", "Dicks 2002","Elberling 1999", "Primack 1983 1", "Primack 1983 2", "Kato 2000", "Kaiser-Bunbunry 2009", "Traveset 2013", "Kevan 1970", "Bek 2006","Primack 1983 3", "Kaiser-Bunbury 2014", "Dupont 2009 2", "Lundgren 2005")
+
+ get_png <- function(filename) {
+  grid::rasterGrob(png::readPNG(filename), interpolate = TRUE)
+}
+
+l <- get_png("Images/lepidoptera_2.png")
+bumb <- get_png("Images/bumblebee.png")
+dip <- get_png("Images/diptera.png")
+beet <- get_png("Images/beetle.png")
+hem<- get_png("Images/hemiptera.png")
+
+t <- grid::roundrectGrob(x=0.5, y=0.5, width=1, height=1)
+
+p<- ggplot(net_long_1) +
+  aes(x = reorder(Id,-order), 
+      y = measurement, 
+      fill =factor(orders, levels=c("Hemiptera","Coleoptera","Lepidoptera","Diptera", "Hymenoptera"))) +
+  geom_bar(position = "fill", stat = "identity", alpha=0.6) +coord_flip() +scale_x_discrete(labels= la) + 
+  scale_fill_manual(legend_title,values=c("indianred", "gray49", "seagreen", "darkgoldenrod2", "#386cb0")) + theme_classic()+xlab("Networks")+ylab("Species per order") +scale_y_continuous(labels = scales::percent) + theme(legend.background = element_rect(fill=alpha('blue', 0.0)))+
+  annotation_custom(l, xmin = 14.6, xmax = 15.4, ymin = 1.03, ymax =1.09) + annotation_custom(bumb, xmin = 11.6, xmax = 13.9, ymin = 1.03, ymax =1.09)+ annotation_custom(dip, xmin = 13.4, xmax = 14.4, ymin = 1.035, ymax =1.085)+
+  coord_cartesian(clip = "off") + annotation_custom(beet, xmin = 15.5, xmax = 16.7, ymin = 0.86, ymax =1.255)+ annotation_custom(hem, xmin = 16.9, xmax = 17.65, ymin = 0.883, ymax =1.233)+
+  coord_cartesian(clip = "off")+ coord_flip()
+
+gg_table <- ggplot_gtable(ggplot_build(p))
+gg_table$layout$clip[gg_table$layout$name=="panel"] <- "off"
+grid.draw(gg_table)
+
+#Bumblebee image credit to Melissa Broussard
 ```
@@
 la <- c("Bartomeus unp. 2015", "Chacoff 2011","Bartomeus 2008 1", "Bartomeus 2008 2","Small 1976",
-       "Inouye 1990", "Souza 2018", "Inouye 1988", "Dupont 2009", "Olesen 2002 1", "Fang huang 2012", "Olesen 2002 2", "Dicks 2002",
+       "Inouye 1990", "Souza 2018", "Inouye 1988", "Dupont 2009", "Olesen 2002 1", "Fang 2012", "Olesen 2002 2", "Dicks 2002",
        "Elberling 1999","Kato 2000", "Kaiser-Bunbunry 2009", "Traveset 2013", "Kaiser-Bunbury 2014","Lundgren 2005")
@@
 ```
+
+#REFERENCES

### 2020-04-10 Rmd/Draft.tex
Not much today, advanced a bit with the draft of ideas

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Chapter 2 Draft},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{setspace}\doublespacing
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{Chapter 2 Draft}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

Here I'm going to try to understand our data a bit better and state our
hypothesis.

First I start with an abstract that could be our guide for hypothesis
testing and analyses.

\section{Abstract (draft)}\label{abstract-draft}

Plant pollinator interactions are a keystone process for ecosystem
functioning. However, we lack comprehensive information from both plants
and pollinators that can inform from this mutualistic interaction
worldwide. In order to tackle this, we have selected 30 networks
distributed across the world and looked for key floral traits of
plant-pollinator interactions for a total of 1600 species. Here we look
how these floral traits shape the different plant-pollinator networks
and the main fuctional groups of insect pollinating species. Giving the
different nature of the data collated we do not compare across networks
and we focus on the main general patterns/results within network. We
have conducted our analysis at 3 levels, 1) unique networks, 2) metawebs
and by 3) grouping both. We find that specific traits are associated
with different guilds of floral visitors within these networks. We also
highlight the lack of information about traits and the reproductive
biology of the plant species of these networks. Our work shows the
importance of deepen in species traits in order to understand key
processes that can be seen with network metrics and highlights the
importance of elemental ecology for species conservation.

\emph{What sort of data do we have?}

There are approximately 1600 species from 30 different networks. All of
these networks are phytocentric (built from plants). The different
plant-pollinator communities have been studied with very different
sampling effort and methodologies. Therefore, our aim is not to compare
across studies but to create a general picture of how floral traits
shape the different pollinator taxa and network metrics. Here, we
combine the studies with multiple years of sampling and multiple sites
within an area in metawebs. These networks give a broader perspective of
the sampling area and inform about the regional species pool (Noreika et
al. 2019). The data of these networks is quantitative (visitation) or
qualitative (binary), there are in total 19 and 11 networks/metawebs of
each, respectively.

\blandscape

\begin{tabular}{r|l|r|l|l|l|l|l|r|r|r|l|l|l}
\hline
X & BIBTEXKEY & Id\_number & longitude & latitude & country & experiment\_year & unique\_networks & plant\_species & pollinator\_species & network\_size & Sampling\_method & Sampling\_zoo\_phytocentric & Data\_type\\
\hline
1 & 1\_metaweb\_carpobrotus\_Bartomeus\_2008 & 1 & 3.296797 & 42.315336 & Spain & 2005 & 3 & 18 & 37 & 666 & Plots 50*50m with 2 transects (N=3) & Phytocentric & Quantitative\\
\hline
2 & 10\_metaweb\_fang\_huang\_2012 & 10 & 99.63806 & 27.90139 & China & 2008-2010 & 3 & 130 & 247 & 32110 & plots with stratified distribution to include rare plants within 800*250m plot & Phytocentric & Quantitative\\
\hline
3 & 11\_metaweb\_inouye\_1990 & 11 & 135.866667 & 35.166667 & Japan & 1984-1987 & 4 & 114 & 883 & 100662 & Transect from stream and a bog & Phytocentric & Quantitative\\
\hline
4 & 12\_inouye\_1988 & 12 & 148.266667 & -36.45 & Australia & 1983-1984 & 1 & 40 & 85 & 3400 & 26 plots with stratified sampling of 10 minutes in each site & Phytocentric & Quantitative\\
\hline
5 & 13\_metaweb\_kaiser\_bunbury\_2009 & 13 & 57.443254 & -20.452076 & Republic of Mauritius & 2003-2004 & 2 & 96 & 184 & 17664 & 2h per sepecies within a 330*100m plot & Phytocentric & Quantitative\\
\hline
6 & 14\_metaweb\_kaiser\_bunbury\_2014 & 14 & 55.43333 & -4.666667 & Republic of Seychelles & 2007-2008 & 6 & 37 & 341 & 12617 & 2 to 4 transects of 100m, 48 networks in 6 different sites & Phytocentric & Quantitative\\
\hline
7 & 15\_metaweb\_kato\_2000 & 15 & 129.493741 & 28.377248 & Japan & 1996-1999 & 16 & 110 & 609 & 66990 & Transects from a fixed point from forest or meadow with 10 min per site & Phytocentric & Quantitative\\
\hline
8 & 16\_kevan\_1970 & 16 & -71.3 & 81.816667 & Canada & 1967 & 1 & 20 & 91 & 1820 & random walks & Phytocentric & Qualitative\\
\hline
9 & 17\_lundgren\_2005 & 17 & -52 & 71 & Greenland & 2002 & 1 & 17 & 26 & 442 & 20 mins per spp, regular walks within the plot (100*100m), max per spp 4h & Phytocentric & Quantitative\\
\hline
10 & 18\_olesen\_2002\_mauritius & 18 & 57.43 & -20.25 & Republic of Mauritius & 1998-1999 & 1 & 17 & 26 & 442 & 37 quadrats 100*100m & Phytocentric & Quantitative\\
\hline
11 & 19\_mcmullen\_1993 & 19 & -90.600747 & -0.290164 & Ecuador & NA & All islands & 105 & 54 & 5670 & Metaweb from the literature & Phytocentric & Qualitative\\
\hline
12 & 2\_metaweb\_opuntia\_Bartomeus\_2008 & 2 & 3.296797 & 42.315336 & Spain & 2005 & 3 & 13 & 37 & 481 & Plots 50*50m with 2 transects (N=3), Plots 50*50m (N=3) & Phytocentric & Quantitative\\
\hline
13 & 20\_metaweb\_arthurs\_pass\_primack\_1983 & 20 & 171.566667 & -42.95 & New Zealand & 1976-1978 & 1 & 18 & 60 & 1080 & Random census walks & Phytocentric & Qualitative\\
\hline
14 & 21\_metaweb\_cass\_primack\_1983 & 21 & 171.78466 & -43.02823 & New Zealand & 1976-1978 & 1 & 41 & 139 & 5699 & Random census walks & Phytocentric & Qualitative\\
\hline
15 & 22\_metaweb\_craigieburn\_primack\_1983 & 22 & 171.720224 & -43.099531 & New Zealand & 1976-1978 & 1 & 49 & 118 & 5782 & Random census walks & Phytocentric & Qualitative\\
\hline
16 & 23\_ramirez\_1989 & 23 & -61.716667 & 5.583333 & Venezuela & NA & 1 & 48 & 49 & 2352 & Random census walks & Phytocentric & Qualitative\\
\hline
17 & 24\_metaweb\_ramirez\_1992 & 24 & -67.416667 & 8.933333 & Venezuela & 1983,1984,1989 & 1 & 28 & 53 & 1484 & Random census walks, 16 to 20h of sampling per spp & Phytocentric & Qualitative\\
\hline
18 & 25\_metaweb\_robertson\_1929 & 25 & -89.8968771 & 39.278958 & United States & 1997-1899 & NA & 456 & 1044 & 476064 &  & Phytocentric & Qualitative\\
\hline
19 & 26\_small\_1976 & 26 & -75.5 & 45.4 & Canada & 1973 & 1 & 13 & 34 & 442 & 10 hours per spp & Phytocentric & Quantitative\\
\hline
20 & 27\_chaco\_souza\_2018 & 27 & -57.885 & -21.701111 & Brazil & 2008-2009 & 1 & 62 & 89 & 5518 & 37 plots, 15*25m (at least 50m away), spp within the plots depending sampling effort on abundance & Phytocentric & Quantitative\\
\hline
21 & 28\_metaweb\_traveset\_2013 & 28 & -91.012863 & -0.6907 & Ecuador & 2010-2011 & 1 & 60 & 220 & 13200 & Random census walks with a total of 518h & Phytocentric & Quantitative\\
\hline
22 & 29\_metaweb\_bartomeus\_unpublished\_data\_2015 & 29 & -6.16895, -6.304244, -6.280883, -6.371844, -6.43311, -6.428801, -6.555233, -6.555236, -6.506789, -6.761136, -6.660927, -6.667992, -6.680852, -6.752456, -6.675026, -6.222871 & 37.234966, 37.21781, 37.23919, 37.214279, 37.289861, 37.247223, 37.282079, 37.233157, 37.123856, 37.194957, 37.249254, 37.331447, 37.405047, 37.291937, 37.288346, 37.291091 & Spain & 2015 & 16 & 57 & 277 & 15789 & Transects & Phytocentric & Quantitative\\
\hline
23 & 3\_bek\_2006 & 3 & 10.216667 & 56.066667 & Denmark & 2003 & 1 & 37 & 225 & 8325 & Plots 1*1 in 1 ha & Phytocentric & Qualitative\\
\hline
24 & 30\_olesen\_2002\_azores & 30 & -31 & 39.4 & Azores & 2000 & 1 & 10 & 12 & 120 & 33 quadrats 100*100m & Phytocentric & Quantitative\\
\hline
25 & 4\_bundgaard\_2003 & 4 & 10.233333 & 56.066667 & Denmark & 2003 & 1 & 16 & 44 & 704 & Plots 1*1m near the trail & Phytocentric & Qualitative\\
\hline
26 & 5\_metaweb\_chacoff\_2011 & 5 & -68.015892 & -32.008985 & Argentina & 2006-2009 & 4 & 59 & 196 & 11564 & 4plots-1ha & Phytocentric & Quantitative\\
\hline
27 & 6\_metaweb\_dicks\_2002 & 6 & 1.575532; 1.097873 & 52.762395; 52.413173 & England & 2001? & 2 & 23 & 80 & 1840 & 4plots-1ha & Phytocentric & Quantitative\\
\hline
28 & 7\_metaweb\_dupont\_2009 & 7 & 9.1; 9.266667 & 56.1; 56.066667 & Denmark & 2005 & 2 & 31 & 329 & 10199 & 1*1m within 100*500m plot & Phytocentric & Quantitative\\
\hline
29 & 8\_elberling\_1999 & 8 & 18.5 & 68.35 & Sweden & 1994 & 1 & 24 & 118 & 2832 & Transects within plot of 30*50m & Phytocentric & Quantitative\\
\hline
30 & 9\_dupont\_2009\_zackenberg & 9 & -20.5 & 74.5 & Greenland & 1996-1997 & 1 & 31 & 76 & 2356 & Observation by random census walks within 25 ha & Phytocentric & Qualitative\\
\hline
\end{tabular}

\elandscape

\newpage

\textbf{PLOT 1}

Here I show the percentage or orders from the different species without
consider visitation and just richness of species. Therfore, if we have a
network with 4 species from from different orders, each will appear as
25\% within the stack bar of the barplot.

\vspace{4cm}

\includegraphics{Draft_files/figure-latex/unnamed-chunk-2-1.pdf}

\newpage

\vspace{4cm}

\includegraphics{Draft_files/figure-latex/unnamed-chunk-3-1.pdf}

\newpage
*

*PLOT 2**

\begin{center}\includegraphics{Draft_files/figure-latex/unnamed-chunk-4-1} \end{center}

\newpage

\textbf{PLOT 3}

\begin{center}\includegraphics{Draft_files/figure-latex/unnamed-chunk-5-1} \end{center}

\newpage

\textbf{PLOT 4}

\begin{center}\includegraphics{Draft_files/figure-latex/unnamed-chunk-6-1} \end{center}

\section*{REFERENCES}\label{references}
\addcontentsline{toc}{section}{REFERENCES}

\hypertarget{refs}{}
\hypertarget{ref-noreika2019pollinator}{}
Noreika, Norbertas, Ignasi Bartomeus, Marie Winsa, Riccardo Bommarco,
and Erik Öckinger. 2019. ``Pollinator Foraging Flexibility Mediates
Rapid Plant-Pollinator Network Restoration in Semi-Natural Grasslands.''
\emph{Scientific Reports} 9 (1). Nature Publishing Group: 1--11.

\end{document}

### 2020-04-11 Rmd/Draft.Rmd
Preparing metadata table

@@
 
-\blandscape
-
+\begin{landscape}
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,}
@@
 m <- read.csv("Data/Data_processing/metadata.csv")
-kable(m)
+kable(m) %>%
+  kable_styling(bootstrap_options = "striped", font_size = 7)
 ```
 
-\elandscape
+\end{landscape}
 

### 2020-04-11 Rmd/Metadata_table.Rmd
Preparing metadata table

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---

\begin{landscape}

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,}
setwd("~/R_Projects/Reproductive Traits")
library(kableExtra)

m <- read.csv("Data/Data_processing/metadata.csv")
#I will have to do some editing before knitting
#colnames(m) <- c("")
m<-m[,-c(1,3)]
colnames(m) <- c("Id","Longitude", "Latitude", "Country", "Year", "Networks", "Plant spp", "Pollinator spp", "Network size", "Sampling method", "Sampling", "Data type")

m[23,4] <-

m[1] <- c("Bartomeus 2008", "Fang 2012", "Inouye 1990", "Inouye 1988", "Kaiser-Bunbury 2009", "Kaiser-Bunbury 2014", "Kato 2000", "Kevan 1970", "Lundgren 2005", "Olesen 2002 1", "Mcmullen 1993", "Bartomeus 2008", "Primack 1983 1", "Primack 1983 2", "Primack 1983 3", "Ramirez 1989", "Ramirez 1992", "Robertson 1929", "Small 1976", "Souza 2018", "Traveset 2013", "Bartomeus 2015 unp.", "Bek 2006", "Olesen 2002 2", "Bundgaard 2003", "Chacoff 2011", "Dicks 2002", "Dupont 2009", "Elberling 1999", "Dupont 2009 2")

kable(m, "latex", longtable = T, booktabs = T) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 7, full_width=T)
```
\end{landscape}

### 2020-04-11 Scripts/Spp_richness_plot.R

@@ -29,34 +29,37 @@ str(data_network_main_orders)
 #Calculate percentage of main orders
 data_network_main_orders[,c(2:6)] <- sapply(data_network_main_orders[,c(2:6)], function(x) {x /data_network_main_orders$total_col*100})
 
+#Non-used/old I did for barplot
 #Convert to long format for plotting
-data_long <- gather(data_network_main_orders, orders, measurement, Hymenoptera:Hemiptera, factor_key=TRUE)
+#data_long <- gather(data_network_main_orders, orders, measurement, Hymenoptera:Hemiptera, factor_key=TRUE)
 
-#Convert again to wideformat for plotting with barplot/for ggplot the last format is enough
-data_long <- data_long[,c(-2)]
-data_wide <- spread(data_long, Id, measurement)
-#Select colours from a Palette that Nacho made for http://www.pnas.org/content/early/2015/11/24/1517092112.long
-clrs <- c("darkblue", "blue", "yellow", "cornsilk", "goldenrod",
-          "orange")
-data2 <- data_wide[,c(2:31)]
-data2 <- data2[,order(data2[1,], decreasing=T)]
-data2 <- as.matrix(data2)
-colnames(data2) <- c("Ramirez 1989", "Ramirez 1992", "Bartomeus unp. 2015", "Chacoff 2011","Bartomeus 2008 1", "Bartomeus 2008 2", "Robertson 1929", "Small 1976",
+#Ggplot to make it look nicer
+
+net_1 <- data_network_main_orders[order(-data_network_main_orders$Hymenoptera),]
+net_1$order <- seq(nrow(net_1))
+net_1 <- gather(net_1, orders, measurement, Hymenoptera:Hemiptera, factor_key=TRUE)
+net_1 <- net_1[,c(-2)]
+
+saveRDS(net_1, "Data/RData/species_per_order_percentage.RData")
+
+
+
+legend_title <- "Taxonomic groups"
+
+la <- c("Ramirez 1989", "Ramirez 1992", "Bartomeus unp. 2015", "Chacoff 2011","Bartomeus 2008 1", "Bartomeus 2008 2", "Robertson 1929", "Small 1976",
[…]

### 2020-04-11 Rmd/Draft.Rmd
Metadata added to draft

--- 2020-04-10 Rmd/Draft.Rmd
@@
 
-\blandscape
+\begin{landscape}
 
@@
 m <- read.csv("Data/Data_processing/metadata.csv")
-kable(m)
+#I will have to do some editing before knitting
+#colnames(m) <- c("")
+m<-m[,-c(1,3)]
+colnames(m) <- c("Id","Longitude", "Latitude", "Country", "Year", "Networks", "Plant spp", "Pollinator spp", "Network size", "Sampling method", "Sampling", "Data type")
+
+#let's select a unique network per coordinate
+#Fix Bartomeus unp 2015
+m[22,2] <- as.factor(-6.16895)
+m[22,3] <- as.factor(37.234966)
+#Dicks
+m[22,2] <- as.factor(1.575532)
+m[22,3] <- as.factor(52.762395)
+#Dupont
+m[22,2] <- as.factor(9.1)
+m[22,3] <- as.factor(56.1)
+
+m[1] <- c("Bartomeus 2008", "Fang 2012", "Inouye 1990", "Inouye 1988", "Kaiser-Bunbury 2009", "Kaiser-Bunbury 2014", "Kato 2000", "Kevan 1970", "Lundgren 2005", "Olesen 2002 1", "Mcmullen 1993", "Bartomeus 2008", "Primack 1983 1", "Primack 1983 2", "Primack 1983 3", "Ramirez 1989", "Ramirez 1992", "Robertson 1929", "Small 1976", "Souza 2018", "Traveset 2013", "Bartomeus 2015 unp.", "Bek 2006", "Olesen 2002 2", "Bundgaard 2003", "Chacoff 2011", "Dicks 2002", "Dupont 2009", "Elberling 1999", "Dupont 2009 2")
+
+m[10] <- c("Plots with transects", "Plots", "Transects", "Plots", "Plots", "Transects", "Transects", "Randow census walks", "Randow census walks", "Plots", "-", "Plots with transects", "Randow census walks", "Randow census walks", "Randow census walks", "Randow census walks", "Randow census walks", "-", "10h per spp", "Plots", "Randow census walks", "Transects", "Plots", "Plots", "Plots", "Plots", "Plots", "Plots", "Plots with transects", "Random census walks")
+
+kable(m, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T)
 ```
-
-\elandscape
+\end{landscape}
 

### 2020-04-11 Rmd/Metadata_table.Rmd
Metadata added to draft

@@
 
-m[23,4] <-
+#let's select a unique network per coordinate
+#Fix Bartomeus unp 2015
+m[22,2] <- as.factor(-6.16895)
+m[22,3] <- as.factor(37.234966)
+#Dicks
+m[22,2] <- as.factor(1.575532)
+m[22,3] <- as.factor(52.762395)
+#Dupont
+m[22,2] <- as.factor(9.1)
+m[22,3] <- as.factor(56.1)
 
@@
 
-kable(m, "latex", longtable = T, booktabs = T) %>%
-  kable_styling(latex_options = c("repeat_header"), font_size = 7, full_width=T)
+m[10] <- c("Plots with transects", "Plots", "Transects", "Plots", "Plots", "Transects", "Transects", "Randow census walks", "Randow census walks", "Plots", "-", "Plots with transects", "Randow census walks", "Randow census walks", "Randow census walks", "Randow census walks", "Randow census walks", "-", "10h per spp", "Plots", "Randow census walks", "Transects", "Plots", "Plots", "Plots", "Plots", "Plots", "Plots", "Plots with transects", "Random census walks")
+
+kable(m, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T)
 ```

### 2020-04-11 Rmd/Draft.Rmd
Adding metadata to draft

@@
 #Dicks
-m[22,2] <- as.factor(1.575532)
-m[22,3] <- as.factor(52.762395)
+m[27,2] <- as.factor(1.575532)
+m[27,3] <- as.factor(52.762395)
 #Dupont
-m[22,2] <- as.factor(9.1)
-m[22,3] <- as.factor(56.1)
+m[28,2] <- as.factor(9.1)
+m[28,3] <- as.factor(56.1)
 

### 2020-04-11 Rmd/Metadata_table.Rmd
Adding metadata to draft

@@
 
+m <- as.data.frame(m, stringsAsFactors = FALSE)
+m$Longitude<- as.numeric(m$Longitude)
+m$Latitude<- as.numeric(m$Latitude)
+
 #let's select a unique network per coordinate
 #Fix Bartomeus unp 2015
-m[22,2] <- as.factor(-6.16895)
-m[22,3] <- as.factor(37.234966)
+#m[22,2] <- as.numeric(-6.16895)
+#m[22,3] <- as.factor(37.234966)
 #Dicks
-m[22,2] <- as.factor(1.575532)
-m[22,3] <- as.factor(52.762395)
+#m[27,2] <- as.factor(1.575532)
+#m[27,3] <- as.factor(52.762395)
 #Dupont
-m[22,2] <- as.factor(9.1)
-m[22,3] <- as.factor(56.1)
+#m[28,2] <- as.factor(9.1)
+m[28,3] <- as.numeric("56.1")
 

### 2020-04-13 Rmd/Draft.Rmd
Research hypotheses.
Methods -taxsize-

@@
 
+#INTRODUCTION
+
+*Paragraph 1*
+
+*Paragraph 2*
+
+There are multiple recent studies that have considered the link between network structure and functional traits.
+@novella2019 included floral display on the interaction strength of a plant-pollinator network, finding important changes in species and network metrics.
+Moreover, @lazaro2019 shows how different traits, including flower abundance, shape, size, flowering length and nectar can influence the position in the network with important implications for community assembly.
+A more similar look to this piece is the work conducted by @carvalheiro2014 that focus on 750 networks and looks how nectar production can modulate the effects between species and found that its effect is dependent on pollinator guilds.
+The continuum from visitation to species fitness is essential to understand the relative importance of each species on the network.
+Therefore, there is a need to to include species breeding systems, compatibility level and seed/fruit set in order to fully understand the dependance on pollinators and position in the network.
+However few works have attempted this due to high demanding nature of these types of experiment [@lazaro2019] [@gomez2012fitness]
+
+  LAZARO/GOMEZ/TUR
+
+Stang papers correlations trait matching and flower size
+
+TUR --> INSECT POLLINATOR DEPENDANCE
+
+ARCEO GOMEZ NEW PAPER
+
+*Paragraph 3*
+
+*Paragraph 4*
+
+*Hypothesis*
+
+1) How the different pollinator taxonomic groups interact with the distinct plant floral traits. Are these floral traits characteristic of a pollinator syndrome?
+
+2) Are the different selected floral traits affecting the species level metrics such as generalization/specialization or centrality? What is its ecological meaning?
+
+3) Can we predict the diversity of pollinator interactions with the phylogenetic distance of a community?
+Communities with a higher number o close related species will likely have trait redundancy and less diversity of interactions.
+
+*Species/network metrics centrality/specialization
+
+#MATERIALS AND METHODS
+
+This research has collated networks from 25 different studies from very different geographical regions across the world.
+Our aim is to have a good representation of the diversity of plant-pollinator interanctions that can take place with multiple combinations of plan traits and pollinator guilds.
+The networks of these studies that were done in consecutive years or in areas close to each other with a similar species compositon were combined in metawebs.
+This makes a total of 30 different unique networks/metawebs.
+For all of these studies we have done an extensive literature and online search of different floral traits.
+These traits are breeding system, compatibility system, selfing rate (with fruit and seed set), flower shape, flower symmetry, flower size (width and length), style length and ovule number.
+Moreover, we also recorded plant height, life span and life form for these species.
+These networks have weighted and unweighted data.
+
+All plant and pollinator species names from these networks were searched through the Package taxsize from two different data sources ncbi and itis, respectively.
+Two of the main data sources for taxonomic names
+
+#DESCRIPTION OF THE DATA
+
 *What sort of data do we have?*
@@
 Therefore, our aim is not to compare across studies but to create a general picture of how floral traits shape the different pollinator taxa and network metrics.
-Here, we combine the studies with multiple years of sampling and multiple sites within an area in metawebs.
-These networks give a broader perspective of the sampling area and inform about the regional species pool [@noreika2019pollinator].
+Here, we combine studies that have multiple years of sampling and multiple sites within an area in metawebs.
+These metawebs give a broader perspective of the sampling area and inform about the regional species pool [@noreika2019pollinator].
 The data of these networks is quantitative (visitation) or qualitative (binary), there are in total 19 and 11 networks/metawebs of each, respectively.
+
+#Methods
 
@@
 
-m <- read.csv("Data/Data_processing/metadata.csv")
+m <- read.csv("Data/Data_processing/metadata.csv", stringsAsFactors = F)
 #I will have to do some editing before knitting
@@
 #Fix Bartomeus unp 2015
-m[22,2] <- as.factor(-6.16895)
-m[22,3] <- as.factor(37.234966)
+m[22,2] <- -6.16895
+m[22,3] <- 37.234966
 #Dicks
-m[27,2] <- as.factor(1.575532)
-m[27,3] <- as.factor(52.762395)
+m[27,2] <- 1.575532
+m[27,3] <- 52.762395
 #Dupont
-m[28,2] <- as.factor(9.1)
-m[28,3] <- as.factor(56.1)
+m[28,2] <- 9.1
+m[28,3] <- 56.1
 

### 2020-04-13 Rmd/Draft.Rmd
Methods

@@
 This research has collated networks from 25 different studies from very different geographical regions across the world.
-Our aim is to have a good representation of the diversity of plant-pollinator interanctions that can take place with multiple combinations of plan traits and pollinator guilds.
+All of these networks are from natural habitats or systems with a minor human intervention.
+The nature of these networks is both weighted (N) and unweighted (N) with the former just with visitation data which could serve as proxy of pollinations with limitations (REF).
+These studies have been counducted with different sampling methodologies and sampling effort and our aim is not to compare them but to get a general picture of how the traits shape these networks and the different taxonomic groups.
 The networks of these studies that were done in consecutive years or in areas close to each other with a similar species compositon were combined in metawebs.
-This makes a total of 30 different unique networks/metawebs.
+This makes a total of 30 different unique networks/metawebs when all are considered by their maximum level of organization (metaweb if possible).
+All the species names were searched with the help of the package taxsize (REF) from two different data sources ncbi and itis, that are ...
+(REF).
+We filled the not found searches manually with the help of [http://www.theplantlist.org/] and
+
  For all of these studies we have done an extensive literature and online search of different floral traits.
@@
 The data of these networks is quantitative (visitation) or qualitative (binary), there are in total 19 and 11 networks/metawebs of each, respectively.
-
-#Methods
 

### 2020-04-14 Rmd/Draft.Rmd
taxsize citation
Organizing figures and ideas

--- 2020-04-13 Rmd/Draft.Rmd
@@
 
+**Research questions**
+
 1) How the different pollinator taxonomic groups interact with the distinct plant floral traits. Are these floral traits characteristic of a pollinator syndrome?
@@
 3) Can we predict the diversity of pollinator interactions with the phylogenetic distance of a community?
-Communities with a higher number o close related species will likely have trait redundancy and less diversity of interactions.
-
-*Species/network metrics centrality/specialization
+-Hypothesis- communities with a higher number o close related species will likely have trait redundancy and less diversity of interactions.
 
@@
 This research has collated networks from 25 different studies from very different geographical regions across the world.
-Our aim is to have a good representation of the diversity of plant-pollinator interanctions that can take place with multiple combinations of plan traits and pollinator guilds.
+All of these networks are from natural habitats or systems with a minor human intervention.
+The nature of these networks is both weighted (N) and unweighted (N) with the former just with visitation data which could serve as proxy of pollination with pollinator efficiency as limitation (REF).
+These studies have been counducted with different sampling methodologies and sampling effort and our aim is not to compare them but to get a general picture of how the selected functional traits shape these networks and the different taxonomic groups.
 The networks of these studies that were done in consecutive years or in areas close to each other with a similar species compositon were combined in metawebs.
-This makes a total of 30 different unique networks/metawebs.
+This makes a total of 30 different unique networks/metawebs when all are considered by their maximum level of organization (metaweb if possible).
+All the species names were searched with the help of the package taxsize [@chamberlain2013taxize] from two different data sources ncbi and itis, for plants and floral visitors respectively.
+We filled the not found searches manually with the help of <http://www.theplantlist.org/> and <http://www.mobot.org/> for plants and  <http://www.catalogueoflife.org/> for floral visitors.
+
 For all of these studies we have done an extensive literature and online search of different floral traits.
@@
 Moreover, we also recorded plant height, life span and life form for these species.
-These networks have weighted and unweighted data.
-
-All plant and pollinator species names from these networks were searched through the Package taxsize from two different data sources ncbi and itis, respectively.
-Two of the main data sources for taxonomic names
-
-#DESCRIPTION OF THE DATA
-
-*What sort of data do we have?*
-
-There are approximately 1600 species from 30 different networks.
-All of these networks are phytocentric (built from plants).
-The different plant-pollinator communities have been studied with very different sampling effort and methodologies.
-Therefore, our aim is not to compare across studies but to create a general picture of how floral traits shape the different pollinator taxa and network metrics.
-Here, we combine studies that have multiple years of sampling and multiple sites within an area in metawebs.
-These metawebs give a broader perspective of the sampling area and inform about the regional species pool [@noreika2019pollinator].
-The data of these networks is quantitative (visitation) or qualitative (binary), there are in total 19 and 11 networks/metawebs of each, respectively.
-
-#Methods
-
-\begin{landscape}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,}
-setwd("~/R_Projects/Reproductive Traits")
-library(kableExtra)
-
-m <- read.csv("Data/Data_processing/metadata.csv", stringsAsFactors = F)
-#I will have to do some editing before knitting
-#colnames(m) <- c("")
-m<-m[,-c(1,3)]
-colnames(m) <- c("Id","Longitude", "Latitude", "Country", "Year", "Networks", "Plant spp", "Pollinator spp", "Network size", "Sampling method", "Sampling", "Data type")
-
-#let's select a unique network per coordinate
-#Fix Bartomeus unp 2015
-m[22,2] <- -6.16895
-m[22,3] <- 37.234966
-#Dicks
-m[27,2] <- 1.575532
-m[27,3] <- 52.762395
-#Dupont
-m[28,2] <- 9.1
-m[28,3] <- 56.1
-
-m[1] <- c("Bartomeus 2008", "Fang 2012", "Inouye 1990", "Inouye 1988", "Kaiser-Bunbury 2009", "Kaiser-Bunbury 2014", "Kato 2000", "Kevan 1970", "Lundgren 2005", "Olesen 2002 1", "Mcmullen 1993", "Bartomeus 2008", "Primack 1983 1", "Primack 1983 2", "Primack 1983 3", "Ramirez 1989", "Ramirez 1992", "Robertson 1929", "Small 1976", "Souza 2018", "Traveset 2013", "Bartomeus 2015 unp.", "Bek 2006", "Olesen 2002 2", "Bundgaard 2003", "Chacoff 2011", "Dicks 2002", "Dupont 2009", "Elberling 1999", "Dupont 2009 2")
-
-m[10] <- c("Plots with transects", "Plots", "Transects", "Plots", "Plots", "Transects", "Transects", "Randow census walks", "Randow census walks", "Plots", "-", "Plots with transects", "Randow census walks", "Randow census walks", "Randow census walks", "Randow census walks", "Randow census walks", "-", "10h per spp", "Plots", "Randow census walks", "Transects", "Plots", "Plots", "Plots", "Plots", "Plots", "Plots", "Plots with transects", "Random census walks")
-
-kable(m, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T)
-```
-\end{landscape}
 
@@
 
-**PLOT 1**
-
-Here I show the percentage or orders from the different species without consider visitation and just richness of species.
-Therfore, if we have a network with 4 species from from different orders, each will appear as 25% within the stack bar of the barplot.
-
 \vspace{4cm}
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8, fig.cap="Percentage of species of each order per network/metaweb (qualitative data)."}
 library(dplyr)
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8, fig.cap="Percentage of visits of each order per network/metaweb (quantitative data)."}
 library(dplyr)
@@
 \newpage
-**PLOT 2**
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center'}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center', fig.cap="Pie charts on the coordinates of each study site  with a classification of three main breeding systems (hermaphroditism, dioecy and monoecy)."}
 library(ggplot2)
@@
 
-**PLOT 3**
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center'}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center', fig.cap="Pie charts on the coordinates of each study site  with the compatibility level classified in three main groups (self compatible, partially self compatible and self incompatible)."}
 library(ggplot2)
@@
 
-**PLOT 4**
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center'}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center', fig.cap="Pie charts on the coordinates of each study site  with the life forms for all the species divided in trees, shrubs, herbs and vines."}
 library(ggplot2)
@@
 
+#DESCRIPTION OF THE DATA
+
+*What sort of data do we have?*
+
+There are approximately 1600 species from 30 different networks.
+All of these networks are phytocentric (built from plants).
+The different plant-pollinator communities have been studied with very different sampling effort and methodologies.
+Therefore, our aim is not to compare across studies but to create a general picture of how floral traits shape the different pollinator taxa and network metrics.
+Here, we combine studies that have multiple years of sampling and multiple sites within an area in metawebs.
+These metawebs give a broader perspective of the sampling area and inform about the regional species pool [@noreika2019pollinator].
+The data of these networks is quantitative (visitation) or qualitative (binary), there are in total 19 and 11 networks/metawebs of each, respectively.
+
+\begin{landscape}
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,}
+setwd("~/R_Projects/Reproductive Traits")
+library(kableExtra)
+
+m <- read.csv("Data/Data_processing/metadata.csv", stringsAsFactors = F)
+#I will have to do some editing before knitting
+#colnames(m) <- c("")
+m<-m[,-c(1,3)]
+colnames(m) <- c("Id","Longitude", "Latitude", "Country", "Year", "Networks", "Plant spp", "Pollinator spp", "Network size", "Sampling method", "Sampling", "Data type")
+
+#let's select a unique network per coordinate
+#Fix Bartomeus unp 2015
+m[22,2] <- -6.16895
+m[22,3] <- 37.234966
+#Dicks
+m[27,2] <- 1.575532
+m[27,3] <- 52.762395
+#Dupont
+m[28,2] <- 9.1
+m[28,3] <- 56.1
+
+m[1] <- c("Bartomeus 2008", "Fang 2012", "Inouye 1990", "Inouye 1988", "Kaiser-Bunbury 2009", "Kaiser-Bunbury 2014", "Kato 2000", "Kevan 1970", "Lundgren 2005", "Olesen 2002 1", "Mcmullen 1993", "Bartomeus 2008", "Primack 1983 1", "Primack 1983 2", "Primack 1983 3", "Ramirez 1989", "Ramirez 1992", "Robertson 1929", "Small 1976", "Souza 2018", "Traveset 2013", "Bartomeus 2015 unp.", "Bek 2006", "Olesen 2002 2", "Bundgaard 2003", "Chacoff 2011", "Dicks 2002", "Dupont 2009", "Elberling 1999", "Dupont 2009 2")
+
+m[10] <- c("Plots with transects", "Plots", "Transects", "Plots", "Plots", "Transects", "Transects", "Randow census walks", "Randow census walks", "Plots", "-", "Plots with transects", "Randow census walks", "Randow census walks", "Randow census walks", "Randow census walks", "Randow census walks", "-", "10h per spp", "Plots", "Randow census walks", "Transects", "Plots", "Plots", "Plots", "Plots", "Plots", "Plots", "Plots with transects", "Random census walks")
+
+kable(m, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", caption = "Metadata for all the different networks/metawebs used at their maximum level of organization (metaweb if possible).") %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T)
+```
+\end{landscape}
+
 #REFERENCES

### 2020-04-15 Rmd/Draft.Rmd
Quick comments

@@
 *Hypothesis*
+[overall, guay, pero le falta story telling]()
 
@@
 -Hypothesis- communities with a higher number o close related species will likely have trait redundancy and less diversity of interactions.
+[IB: Este ultimo punto es interesante, PERO quizas es otro paper? Mirate https://www.nature.com/articles/nature05956 Rezende tiene otros papers al respecto]()
 
@@
 grid.draw(gg_table)
+
+# IB: No me cuadra la cantidad de dipteros (y pocos hymenopteros) en mis redes, recheck colores. Ojo, quizas esta bien, pero me sorprende. 
+# IB; Para visitas hay oalgo mal seguro, no hay abejas en 2015 ¿?
 
@@
   geom_segment(data = data_merged_sub_ord, aes(x = -20, y = 86, xend = -20, yend = 74), color = "black", size = 0.3, alpha = 0.2)
+
+## Molaria compararlo con estimas a nivel mundial de que % de plantas son hermafroditas, (y igual para todos los traits).
+En otras palabras, salen estas porporciones por que reflejan las proporciones generales?
+O se desvian?)
 ```
@@
   geom_segment(data = data_merged_sub_ord, aes(x = -20, y = 86, xend = -20, yend = 74), color = "black", size = 0.3, alpha = 0.8)
+
+##Que flipe que al norte hay más self-compatible?! Esto debe estar decrito en la literatura, verdad? Hay una correlación entre la diversidad de abejas y el nivel de self incompatibility?  
 ```
@@
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T)
+
+### en 2008 por que hay 3 networks? Netiendo como puede haver 12, 6 o 2, pero 3? OK entendido, ya veo el 3+3! pon 2008a 2008b?
 ```

### 2020-04-20 Rmd/Draft.Rmd
I have to clean the code but here I have a reproducible example with on of the networks for a sankey diagram

@@
 
-la <- c("Ramirez 1989", "Ramirez 1992", "Bartomeus unp.
-2015", "Chacoff 2011","Bartomeus 2008 1", "Bartomeus 2008 2", "Robertson 1929", "Small 1976","Inouye 1990", "Souza 2018", "Bundgaard 2003", "Inouye 1988", "Dupont 2009 1", "Olesen 2002 1", "Fang huang 2012", "mcmullen 1993", "Olesen 2002 2", "Dicks 2002","Elberling 1999", "Primack 1983 1", "Primack 1983 2", "Kato 2000", "Kaiser-Bunbunry 2009", "Traveset 2013", "Kevan 1970", "Bek 2006","Primack 1983 3", "Kaiser-Bunbury 2014", "Dupont 2009 2", "Lundgren 2005")
+la <- c("Lundgren 2005", "Dupont 2009 b", "Kaiser-Bunbunry 2014",  "Primack 1983 a", "Bek 2006", "Kevan 1970","Traveset 2013", "Kaiser-Bunbunry 2009",  "Kato 2000", "Primack 1983 b", "Primack 1983 c", "Elberling 1999", "Dicks 2002", "Olesen 2002 a", "Mcmullen 1993", "Fang 2012", "Olesen 2002 b", "Dupont 2009 a", "Inouye 1988", "Bundgaard 2003","Souza 2018", "Inouye 1990", "Small 1976", "Robertson 1929", "Bartomeus 2008 b", "Bartomeus 2008 a", "Chacoff 2011","Bartomeus unp.
+2015","Ramirez 1992","Ramirez 1989")
 
@@
 # IB; Para visitas hay oalgo mal seguro, no hay abejas en 2015 ¿?
+#ARREGLADO, las nombres de las redes estaban mal ordenados
 
@@
 
-la <- c("Bartomeus unp. 2015", "Chacoff 2011","Bartomeus 2008 1", "Bartomeus 2008 2","Small 1976",
-       "Inouye 1990", "Souza 2018", "Inouye 1988", "Dupont 2009", "Olesen 2002 1", "Fang 2012", "Olesen 2002 2", "Dicks 2002",
-       "Elberling 1999","Kato 2000", "Kaiser-Bunbunry 2009", "Traveset 2013", "Kaiser-Bunbury 2014","Lundgren 2005")
+la <- c("Lundgren 2005", "Elberling 1999", "Kaiser-Bunbunry 2009", "Kato 2000", "Dupont 2009", "Olesen 2002 a", 
+       "Traveset 2013", "Bartomeus 2008 a",  "Inouye 1988", "Dicks 2002", "Inouye 1990", "Small 1976", "Bartomeus 2008 b","Chacoff 2011", "Fang 2012", "Kaiser-Bunbury 2014", "Olesen 2002 b", "Bartomeus unp.
+2015", "Souza 2018")
+
 legend_title <- "Taxonomic groups"

### 2020-04-20 Scripts/Spp_richness_plot.R

@@ -46,10 +46,15 @@ saveRDS(net_1, "Data/RData/species_per_order_percentage.RData")
 
 legend_title <- "Taxonomic groups"
 
-la <- c("Ramirez 1989", "Ramirez 1992", "Bartomeus unp. 2015", "Chacoff 2011","Bartomeus 2008 1", "Bartomeus 2008 2", "Robertson 1929", "Small 1976",
-                     "Inouye 1990", "Souza 2018", "Bundgaard 2003", "Inouye 1988", "Dupont 2009 1", "Olesen 2002 1", "Fang huang 2012", "mcmullen 1993", "Olesen 2002 2", "Dicks 2002",
-                     "Elberling 1999", "Primack 1983 1", "Primack 1983 2", "Kato 2000", "Kaiser-Bunbunry 2009", "Traveset 2013", "Kevan 1970", "Bek 2006",
-                     "Primack 1983 3", "Kaiser-Bunbury 2014", "Dupont 2009 2", "Lundgren 2005")
+
+la <- c("Lundgren 2005", "Dupont 2009 b", "Kaiser-Bunbunry 2014",  "Primack 1983 a", "Bek 2006", "Kevan 1970","Traveset 2013", 
+       "Kaiser-Bunbunry 2009",  "Kato 2000", "Primack 1983 b", "Primack 1983 c", "Elberling 1999", "Dicks 2002",
+       "Olesen 2002 a", "Mcmullen 1993", "Fang 2012", "Olesen 2002 b", "Dupont 2009 a", "Inouye 1988", "Bundgaard 2003",
+       "Souza 2018", "Inouye 1990", "Small 1976", "Robertson 1929", "Bartomeus 2008 b", "Bartomeus 2008 a", "Chacoff 2011",
+       "Bartomeus unp. 2015","Ramirez 1992","Ramirez 1989")
+
+
+
 
  ggplot(net_1) +
   aes(x = reorder(Id,-order), 
@@ -69,7 +74,8 @@ la <- c("Ramirez 1989", "Ramirez 1992", "Bartomeus unp. 2015", "Chacoff 2011","B
 
 m <- read.csv("Data/Data_processing/metadata.csv")
 data <- read.csv("Data/Data_processing/Long_format_metawebs_poll_taxa_added.csv")
-
+str(data$Interaction)
+data$Interaction[is.na(data$Interaction)] <- 0
 #Removing .csv for merging the two datasets
 data$Id <- gsub("\\..*","",data$Id)
 
[…]

### 2020-04-25 Rmd/Draft/Draft.Rmd

--- 2020-04-20 Rmd/Draft.Rmd
@@
 
+Now I'm going to explorea small subset of networks from Bartomeus 2015 to see how the analysis would be.
+Now I show graphically the networks with sankey diagrams.
+In first place the sankey diagram for the metaweb and then 4 panels in 4 different networks for the 16 different sites that were sampled in this project.
+
+*Add individual chunks to add captions, think about combining panels...*
+
+```{r, fig.align="center", echo=FALSE}
+
+library(knitr)
+
+include_graphics("Bee_fun.pdf", error = T)
+
+include_graphics("Bee_fun_x8_1.pdf", error = T)
+
+include_graphics("Bee_fun_x8_2.pdf", error = T)
+
+```
+
 #REFERENCES

### 2020-05-04 Rmd/Draft.tex

@@
 \IfFileExists{microtype.sty}{%
-\usepackage[]{microtype}
+\usepackage{microtype}
 \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
-\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
-\usepackage[unicode=true]{hyperref}
-\hypersetup{
+\usepackage[margin=1in]{geometry}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
             pdftitle={Chapter 2 Draft},
@@
 \urlstyle{same}  % don't use monospace font for urls
-\usepackage[margin=1in]{geometry}
 \usepackage{graphicx,grffile}
@@
 
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
 
-\usepackage{setspace}\doublespacing
+%%% Change title format to be more compact
+\usepackage{titling}
+
+% Create subtitle command for use in maketitle
+\providecommand{\subtitle}[1]{
+  \posttitle{
+    \begin{center}\large#1\end{center}
+    }
+}
+
+\setlength{\droptitle}{-2em}
+
+  \title{Chapter 2 Draft}
+    \pretitle{\vspace{\droptitle}\centering\huge}
+  \posttitle{\par}
+    \author{}
+    \preauthor{}\postauthor{}
+    \date{}
+    \predate{}\postdate{}
+
 \usepackage{booktabs}
@@
 
-\title{Chapter 2 Draft}
-\author{}
-\date{\vspace{-2.5em}}
+\usepackage{setspace}\doublespacing
 
@@
 
-\section{Abstract (draft)}\label{abstract-draft}
+\#Abstract (draft)
 
@@
 
-\blandscape
+\begin{landscape}
 
-\begin{tabular}{r|l|r|l|l|l|l|l|r|r|r|l|l|l}
-\hline
-X & BIBTEXKEY & Id\_number & longitude & latitude & country & experiment\_year & unique\_networks & plant\_species & pollinator\_species & network\_size & Sampling\_method & Sampling\_zoo\_phytocentric & Data\_type\\
-\hline
-1 & 1\_metaweb\_carpobrotus\_Bartomeus\_2008 & 1 & 3.296797 & 42.315336 & Spain & 2005 & 3 & 18 & 37 & 666 & Plots 50*50m with 2 transects (N=3) & Phytocentric & Quantitative\\
-\hline
-2 & 10\_metaweb\_fang\_huang\_2012 & 10 & 99.63806 & 27.90139 & China & 2008-2010 & 3 & 130 & 247 & 32110 & plots with stratified distribution to include rare plants within 800*250m plot & Phytocentric & Quantitative\\
-\hline
-3 & 11\_metaweb\_inouye\_1990 & 11 & 135.866667 & 35.166667 & Japan & 1984-1987 & 4 & 114 & 883 & 100662 & Transect from stream and a bog & Phytocentric & Quantitative\\
-\hline
-4 & 12\_inouye\_1988 & 12 & 148.266667 & -36.45 & Australia & 1983-1984 & 1 & 40 & 85 & 3400 & 26 plots with stratified sampling of 10 minutes in each site & Phytocentric & Quantitative\\
-\hline
-5 & 13\_metaweb\_kaiser\_bunbury\_2009 & 13 & 57.443254 & -20.452076 & Republic of Mauritius & 2003-2004 & 2 & 96 & 184 & 17664 & 2h per sepecies within a 330*100m plot & Phytocentric & Quantitative\\
-\hline
-6 & 14\_metaweb\_kaiser\_bunbury\_2014 & 14 & 55.43333 & -4.666667 & Republic of Seychelles & 2007-2008 & 6 & 37 & 341 & 12617 & 2 to 4 transects of 100m, 48 networks in 6 different sites & Phytocentric & Quantitative\\
-\hline
-7 & 15\_metaweb\_kato\_2000 & 15 & 129.493741 & 28.377248 & Japan & 1996-1999 & 16 & 110 & 609 & 66990 & Transects from a fixed point from forest or meadow with 10 min per site & Phytocentric & Quantitative\\
-\hline
-8 & 16\_kevan\_1970 & 16 & -71.3 & 81.816667 & Canada & 1967 & 1 & 20 & 91 & 1820 & random walks & Phytocentric & Qualitative\\
-\hline
-9 & 17\_lundgren\_2005 & 17 & -52 & 71 & Greenland & 2002 & 1 & 17 & 26 & 442 & 20 mins per spp, regular walks within the plot (100*100m), max per spp 4h & Phytocentric & Quantitative\\
-\hline
-10 & 18\_olesen\_2002\_mauritius & 18 & 57.43 & -20.25 & Republic of Mauritius & 1998-1999 & 1 & 17 & 26 & 442 & 37 quadrats 100*100m & Phytocentric & Quantitative\\
-\hline
-11 & 19\_mcmullen\_1993 & 19 & -90.600747 & -0.290164 & Ecuador & NA & All islands & 105 & 54 & 5670 & Metaweb from the literature & Phytocentric & Qualitative\\
-\hline
-12 & 2\_metaweb\_opuntia\_Bartomeus\_2008 & 2 & 3.296797 & 42.315336 & Spain & 2005 & 3 & 13 & 37 & 481 & Plots 50*50m with 2 transects (N=3), Plots 50*50m (N=3) & Phytocentric & Quantitative\\
-\hline
-13 & 20\_metaweb\_arthurs\_pass\_primack\_1983 & 20 & 171.566667 & -42.95 & New Zealand & 1976-1978 & 1 & 18 & 60 & 1080 & Random census walks & Phytocentric & Qualitative\\
-\hline
-14 & 21\_metaweb\_cass\_primack\_1983 & 21 & 171.78466 & -43.02823 & New Zealand & 1976-1978 & 1 & 41 & 139 & 5699 & Random census walks & Phytocentric & Qualitative\\
-\hline
-15 & 22\_metaweb\_craigieburn\_primack\_1983 & 22 & 171.720224 & -43.099531 & New Zealand & 1976-1978 & 1 & 49 & 118 & 5782 & Random census walks & Phytocentric & Qualitative\\
-\hline
-16 & 23\_ramirez\_1989 & 23 & -61.716667 & 5.583333 & Venezuela & NA & 1 & 48 & 49 & 2352 & Random census walks & Phytocentric & Qualitative\\
-\hline
-17 & 24\_metaweb\_ramirez\_1992 & 24 & -67.416667 & 8.933333 & Venezuela & 1983,1984,1989 & 1 & 28 & 53 & 1484 & Random census walks, 16 to 20h of sampling per spp & Phytocentric & Qualitative\\
-\hline
-18 & 25\_metaweb\_robertson\_1929 & 25 & -89.8968771 & 39.278958 & United States & 1997-1899 & NA & 456 & 1044 & 476064 &  & Phytocentric & Qualitative\\
-\hline
-19 & 26\_small\_1976 & 26 & -75.5 & 45.4 & Canada & 1973 & 1 & 13 & 34 & 442 & 10 hours per spp & Phytocentric & Quantitative\\
-\hline
-20 & 27\_chaco\_souza\_2018 & 27 & -57.885 & -21.701111 & Brazil & 2008-2009 & 1 & 62 & 89 & 5518 & 37 plots, 15*25m (at least 50m away), spp within the plots depending sampling effort on abundance & Phytocentric & Quantitative\\
-\hline
-21 & 28\_metaweb\_traveset\_2013 & 28 & -91.012863 & -0.6907 & Ecuador & 2010-2011 & 1 & 60 & 220 & 13200 & Random census walks with a total of 518h & Phytocentric & Quantitative\\
-\hline
-22 & 29\_metaweb\_bartomeus\_unpublished\_data\_2015 & 29 & -6.16895, -6.304244, -6.280883, -6.371844, -6.43311, -6.428801, -6.555233, -6.555236, -6.506789, -6.761136, -6.660927, -6.667992, -6.680852, -6.752456, -6.675026, -6.222871 & 37.234966, 37.21781, 37.23919, 37.214279, 37.289861, 37.247223, 37.282079, 37.233157, 37.123856, 37.194957, 37.249254, 37.331447, 37.405047, 37.291937, 37.288346, 37.291091 & Spain & 2015 & 16 & 57 & 277 & 15789 & Transects & Phytocentric & Quantitative\\
-\hline
-23 & 3\_bek\_2006 & 3 & 10.216667 & 56.066667 & Denmark & 2003 & 1 & 37 & 225 & 8325 & Plots 1*1 in 1 ha & Phytocentric & Qualitative\\
-\hline
-24 & 30\_olesen\_2002\_azores & 30 & -31 & 39.4 & Azores & 2000 & 1 & 10 & 12 & 120 & 33 quadrats 100*100m & Phytocentric & Quantitative\\
-\hline
-25 & 4\_bundgaard\_2003 & 4 & 10.233333 & 56.066667 & Denmark & 2003 & 1 & 16 & 44 & 704 & Plots 1*1m near the trail & Phytocentric & Qualitative\\
-\hline
-26 & 5\_metaweb\_chacoff\_2011 & 5 & -68.015892 & -32.008985 & Argentina & 2006-2009 & 4 & 59 & 196 & 11564 & 4plots-1ha & Phytocentric & Quantitative\\
-\hline
-27 & 6\_metaweb\_dicks\_2002 & 6 & 1.575532; 1.097873 & 52.762395; 52.413173 & England & 2001? & 2 & 23 & 80 & 1840 & 4plots-1ha & Phytocentric & Quantitative\\
-\hline
-28 & 7\_metaweb\_dupont\_2009 & 7 & 9.1; 9.266667 & 56.1; 56.066667 & Denmark & 2005 & 2 & 31 & 329 & 10199 & 1*1m within 100*500m plot & Phytocentric & Quantitative\\
-\hline
-29 & 8\_elberling\_1999 & 8 & 18.5 & 68.35 & Sweden & 1994 & 1 & 24 & 118 & 2832 & Transects within plot of 30*50m & Phytocentric & Quantitative\\
-\hline
-30 & 9\_dupont\_2009\_zackenberg & 9 & -20.5 & 74.5 & Greenland & 1996-1997 & 1 & 31 & 76 & 2356 & Observation by random census walks within 25 ha & Phytocentric & Qualitative\\
-\hline
-\end{tabular}
+\begingroup\fontsize{7}{9}\selectfont
 
-\elandscape
+\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
+\toprule
+Id & Longitude & Latitude & Country & Year & Networks & Plant spp & Pollinator spp & Network size & Sampling method & Sampling & Data type\\
+\midrule
+\endfirsthead
+\multicolumn{12}{@{}l}{\textit{(continued)}}\\
+\toprule
+Id & Longitude & Latitude & Country & Year & Networks & Plant spp & Pollinator spp & Network size & Sampling method & Sampling & Data type\\
+\midrule
+\endhead
+\
+\endfoot
+\bottomrule
+\endlastfoot
+\rowcolor{gray!6}  Bartomeus 2008 & 3.296797 & 42.315336 & Spain & 2005 & 3 & 18 & 37 & 666 & Plots with transects & Phytocentric & Quantitative\\
+\addlinespace
+Fang 2012 & 99.63806 & 27.90139 & China & 2008-2010 & 3 & 130 & 247 & 32110 & Plots & Phytocentric & Quantitative\\
+\addlinespace
+\rowcolor{gray!6}  Inouye 1990 & 135.866667 & 35.166667 & Japan & 1984-1987 & 4 & 114 & 883 & 100662 & Transects & Phytocentric & Quantitative\\
+\addlinespace
+Inouye 1988 & 148.266667 & -36.45 & Australia & 1983-1984 & 1 & 40 & 85 & 3400 & Plots & Phytocentric & Quantitative\\
+\addlinespace
+\rowcolor{gray!6}  Kaiser-Bunbury 2009 & 57.443254 & -20.452076 & Republic of Mauritius & 2003-2004 & 2 & 96 & 184 & 17664 & Plots & Phytocentric & Quantitative\\
+\addlinespace
+Kaiser-Bunbury 2014 & 55.43333 & -4.666667 & Republic of Seychelles & 2007-2008 & 6 & 37 & 341 & 12617 & Transects & Phytocentric & Quantitative\\
+\addlinespace
+\rowcolor{gray!6}  Kato 2000 & 129.493741 & 28.377248 & Japan & 1996-1999 & 16 & 110 & 609 & 66990 & Transects & Phytocentric & Quantitative\\
+\addlinespace
+Kevan 1970 & -71.3 & 81.816667 & Canada & 1967 & 1 & 20 & 91 & 1820 & Randow census walks & Phytocentric & Qualitative\\
+\addlinespace
+\rowcolor{gray!6}  Lundgren 2005 & -52 & 71 & Greenland & 2002 & 1 & 17 & 26 & 442 & Randow census walks & Phytocentric & Quantitative\\
+\addlinespace
+Olesen 2002 1 & 57.43 & -20.25 & Republic of Mauritius & 1998-1999 & 1 & 17 & 26 & 442 & Plots & Phytocentric & Quantitative\\
+\addlinespace
+\rowcolor{gray!6}  Mcmullen 1993 & -90.600747 & -0.290164 & Ecuador & NA & All islands & 105 & 54 & 5670 & - & Phytocentric & Qualitative\\
+\addlinespace
+Bartomeus 2008 & 3.296797 & 42.315336 & Spain & 2005 & 3 & 13 & 37 & 481 & Plots with transects & Phytocentric & Quantitative\\
+\addlinespace
+\rowcolor{gray!6}  Primack 1983 1 & 171.566667 & -42.95 & New Zealand & 1976-1978 & 1 & 18 & 60 & 1080 & Randow census walks & Phytocentric & Qualitative\\
+\addlinespace
+Primack 1983 2 & 171.78466 & -43.02823 & New Zealand & 1976-1978 & 1 & 41 & 139 & 5699 & Randow census walks & Phytocentric & Qualitative\\
+\addlinespace
+\rowcolor{gray!6}  Primack 1983 3 & 171.720224 & -43.099531 & New Zealand & 1976-1978 & 1 & 49 & 118 & 5782 & Randow census walks & Phytocentric & Qualitative\\
+\addlinespace
+Ramirez 1989 & -61.716667 & 5.583333 & Venezuela & NA & 1 & 48 & 49 & 2352 & Randow census walks & Phytocentric & Qualitative\\
+\addlinespace
+\rowcolor{gray!6}  Ramirez 1992 & -67.416667 & 8.933333 & Venezuela & 1983,1984,1989 & 1 & 28 & 53 & 1484 & Randow census walks & Phytocentric & Qualitative\\
+\addlinespace
+Robertson 1929 & -89.8968771 & 39.278958 & United States & 1997-1899 & NA & 456 & 1044 & 476064 & - & Phytocentric & Qualitative\\
+\addlinespace
+\rowcolor{gray!6}  Small 1976 & -75.5 & 45.4 & Canada & 1973 & 1 & 13 & 34 & 442 & 10h per spp & Phytocentric & Quantitative\\
+\addlinespace
+Souza 2018 & -57.885 & -21.701111 & Brazil & 2008-2009 & 1 & 62 & 89 & 5518 & Plots & Phytocentric & Quantitative\\
+\addlinespace
+\rowcolor{gray!6}  Traveset 2013 & -91.012863 & -0.6907 & Ecuador & 2010-2011 & 1 & 60 & 220 & 13200 & Randow census walks & Phytocentric & Quantitative\\
+\addlinespace
+Bartomeus 2015 unp. & -6.16895 & 37.234966 & Spain & 2015 & 16 & 57 & 277 & 15789 & Transects & Phytocentric & Quantitative\\
+\addlinespace
+\rowcolor{gray!6}  Bek 2006 & 10.216667 & 56.066667 & Denmark & 2003 & 1 & 37 & 225 & 8325 & Plots & Phytocentric & Qualitative\\
+\addlinespace
+Olesen 2002 2 & -31 & 39.4 & Azores & 2000 & 1 & 10 & 12 & 120 & Plots & Phytocentric & Quantitative\\
+\addlinespace
+\rowcolor{gray!6}  Bundgaard 2003 & 10.233333 & 56.066667 & Denmark & 2003 & 1 & 16 & 44 & 704 & Plots & Phytocentric & Qualitative\\
+\addlinespace
+Chacoff 2011 & -68.015892 & -32.008985 & Argentina & 2006-2009 & 4 & 59 & 196 & 11564 & Plots & Phytocentric & Quantitative\\
+\addlinespace
+\rowcolor{gray!6}  Dicks 2002 & 1.575532 & 52.762395 & England & 2001? & 2 & 23 & 80 & 1840 & Plots & Phytocentric & Quantitative\\
+\addlinespace
+Dupont 2009 & 9.1 & 6.1 & Denmark & 2005 & 2 & 31 & 329 & 10199 & Plots & Phytocentric & Quantitative\\
+\addlinespace
+\rowcolor{gray!6}  Elberling 1999 & 18.5 & 68.35 & Sweden & 1994 & 1 & 24 & 118 & 2832 & Plots with transects & Phytocentric & Quantitative\\
+\addlinespace
+Dupont 2009 2 & -20.5 & 74.5 & Greenland & 1996-1997 & 1 & 31 & 76 & 2356 & Random census walks & Phytocentric & Qualitative\\*
+\end{longtabu}
+\endgroup{}
+\end{landscape}
 
@@
 \newpage
-*
 
-*PLOT 2**
+\textbf{PLOT 2}
 
@@
 
-\section*{REFERENCES}\label{references}
-\addcontentsline{toc}{section}{REFERENCES}
+\#REFERENCES
 
 \hypertarget{refs}{}
-\hypertarget{ref-noreika2019pollinator}{}
+\leavevmode\hypertarget{ref-noreika2019pollinator}{}%
 Noreika, Norbertas, Ignasi Bartomeus, Marie Winsa, Riccardo Bommarco,

### 2020-05-26 Rmd/Quantitative_Data_Models_plot.Rmd
Models part 3

---
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=9,fig.width=7}
library(ds4psy)
library(ggplot2)
library(ggeffects)
library(ggplot2)
library(gridExtra)
library(egg)
library(magrittr)
library(grid)
library(Rmisc)
library(cowplot)

setwd("~/R_Projects/Reproductive Traits")

model_1 <- readRDS("Data/RData/model_1_visits_plant_height.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_plant_height.rds")

mydf <- ggpredict(model_1, terms = c("plant_height_mean_m"))

plant_height <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Plant height (m)")+ ylab("Predicted visits")+geom_point(data= all_tf, aes(x =plant_height_mean_m , y = pred))+
  geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_1 <- readRDS("Data/RData/model_1_visits_style_length.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_style_length.rds")

mydf <- ggpredict(model_1, terms = c("style_length_mm"))

style_length <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Style length (mm)")+ ylab("Predicted visits")+geom_point(data= all_tf, aes(x =style_length_mm , y = pred))+geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_1 <- readRDS("Data/RData/model_1_visits_ovule_number.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_ovule_number.rds")

mydf <- ggpredict(model_1, terms = c("ovules_mean"))

ovule_number <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") +xlab("Ovule number")+ ylab("Predicted visits")+geom_point(data= all_tf, aes(x =ovules_mean , y = pred))+
  geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_1 <- readRDS("Data/RData/model_1_visits_corolla_diameter.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_corolla_diameter.rds")

mydf <- ggpredict(model_1, terms = c("Corolla_diameter_mean"))

corolla_diameter <-ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Corolla diameter (mm)")+ ylab("Predicted visits")+geom_point(data= all_tf, aes(x =Corolla_diameter_mean , y = pred))+
  geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_1 <- readRDS("Data/RData/model_1_visits_corolla_length.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_corolla_length.rds")

mydf <- ggpredict(model_1, terms = c("Corolla_length_mean"))

corolla_length <-ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Corolla length (mm)")+ ylab("Predicted visits")+geom_point(data= all_tf, aes(x =Corolla_length_mean , y = pred))+
  geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

p <- plot_grid(plant_height, style_length, corolla_length, corolla_diameter,ovule_number,NULL, ncol = 2)

title <- ggdraw() + draw_label("VISITS ~ TRAITS", fontface='bold')

plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins

```

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=9,fig.width=7}
library(ds4psy)
library(ggplot2)
library(ggeffects)
library(ggplot2)
library(gridExtra)
library(egg)
library(magrittr)
library(grid)
library(Rmisc)
library(cowplot)

setwd("~/R_Projects/Reproductive Traits")

model_2 <- readRDS("Data/RData/model_2_visits_plant_height_2.rds")
pred <- readRDS("Data/RData/pred_plot_visits_plant_height_2.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_plant_height_2.rds")

mydf <- ggpredict(model_2, terms = c("plant_height_mean_m"))
plant_height_2 <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Plant height (m)")+ ylab("Predicted d")+geom_point(data= all_tf, aes(x =plant_height_mean_m , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_2 <- readRDS("Data/RData/model_2_visits_style_length_2.rds")
pred <- readRDS("Data/RData/pred_plot_visits_style_length_2.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_style_length_2.rds")

mydf <- ggpredict(model_2, terms = c("style_length_mm"))
style_length_2 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Style length (mm)")+ theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted d")+geom_point(data= all_tf, aes(x =style_length_mm , y = pred))+
  geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_2 <- readRDS("Data/RData/model_2_visits_corolla_length_2.rds")
pred <- readRDS("Data/RData/pred_plot_visits_corolla_length_2.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_corolla_length_2.rds")

mydf <- ggpredict(model_2, terms = c("Corolla_length_mean"))

corolla_length_2 <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Corolla length")+ ylab("Predicted d")+geom_point(data= all_tf, aes(x =Corolla_length_mean , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_2 <- readRDS("Data/RData/model_2_visitscorolla_diameter_2.rds")
pred <- readRDS("Data/RData/pred_plot_visits_corolla_diameter_2.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_corolla_diameter_2.rds")

mydf <- ggpredict(model_2, terms = c("Corolla_diameter_mean"))

corolla_diameter_2 <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Corolla diameter (mm)")+ ylab("Predicted d")+geom_point(data= all_tf, aes(x =Corolla_diameter_mean , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_2 <- readRDS("Data/RData/model_2_visits_ovule_number_2.rds")
pred <- readRDS("Data/RData/pred_plot_visits_ovule_number_2.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_ovule_number_2.rds")

mydf <- ggpredict(model_2, terms = c("ovules_mean"))
ovule_number_2 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Ovule number")+ theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted d")+geom_point(data= all_tf, aes(x =ovules_mean , y = pred))+
  geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

p <- plot_grid(plant_height_2, style_length_2, corolla_length_2, corolla_diameter_2,ovule_number_2,NULL, ncol = 2)

title <- ggdraw() + draw_label("SPECIALIZATION (d) ~ TRAITS", fontface='bold')

plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins

```

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=9,fig.width=7}
library(ds4psy)
library(ggplot2)
library(ggeffects)
library(ggplot2)
library(gridExtra)
library(egg)
library(magrittr)
library(grid)
library(Rmisc)
library(cowplot)

setwd("~/R_Projects/Reproductive Traits")

model_3 <- readRDS("Data/RData/model_3_visits_plant_height_3.rds")
pred <- readRDS("Data/RData/pred_plot_visits_plant_height_3.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_plant_height_3.rds")

mydf <- ggpredict(model_3, terms = c("plant_height_mean_m"))
plant_height_3 <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Plant height (m)")+ ylab("Predicted degree")+ geom_point(data= all_tf, aes(x =plant_height_mean_m , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_3 <- readRDS("Data/RData/model_3_visits_style_length_3.rds")
pred <- readRDS("Data/RData/pred_plot_visits_style_length_3.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_style_length_3.rds")

mydf <- ggpredict(model_3, terms = c("style_length_mm"))
style_length_3 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Style length (mm)") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted degree") + geom_point(data= all_tf, aes(x =style_length_mm , y = pred))+
  geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_3 <- readRDS("Data/RData/model_3_visits_corolla_length_3.rds")
pred <- readRDS("Data/RData/pred_plot_visits_corolla_length_3.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_corolla_length_3.rds")

mydf <- ggpredict(model_3, terms = c("Corolla_length_mean"))
corolla_length_3 <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Corolla length (mm)")+ ylab("Predicted degree")+ geom_point(data= all_tf, aes(x =Corolla_length_mean , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_3 <- readRDS("Data/RData/model_3_visits_corolla_diameter_3.rds")
pred <- readRDS("Data/RData/pred_plot_visits_corolla_diameter_3.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_corolla_diameter_3.rds")

mydf <- ggpredict(model_3, terms = c("Corolla_diameter_mean"))
corolla_diameter_3 <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Corolla diameter (mm)")+ ylab("Predicted degree")+ geom_point(data= all_tf, aes(x =Corolla_diameter_mean , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_3 <- readRDS("Data/RData/model_3_visits_ovule_number_3.rds")
pred <- readRDS("Data/RData/pred_plot_visits_ovule_number_3.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_ovule_number_3.rds")

mydf <- ggpredict(model_3, terms = c("ovules_mean"))
ovule_number_3 <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Ovule number")+ ylab("Predicted degree")+ geom_point(data= all_tf, aes(x =ovules_mean , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

p <- plot_grid(plant_height_3,style_length_3,corolla_length_3,corolla_diameter_3,ovule_number_3,NULL, ncol = 2)

title <- ggdraw() + draw_label("DEGREE ~ TRAITS", fontface='bold')

plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins

```

### 2020-05-26 Scripts/Analysis/Analysis_metric_vs_compatibility_flower_size.R

@@ -86,6 +86,9 @@ summary(model_1)
 
 resids_plot(model_1, all_df$Visits)
 
+r2(model_1)
+
+
 library(ggeffects)
 a <- ggpredict(model_1, terms = c("Corolla_diameter_mean", "Compatibility"))
 plot(a)
@@ -93,10 +96,11 @@ plot(a)
 all_tf<- all_df
 all_tf <-predict(model_1, type="subject_specific",newdata = all_tf,return_newdata = TRUE)
 
+r2(model_1)
 
 
 mydf <- ggpredict(model_1, terms = c("Corolla_diameter_mean", "Compatibility")) 
-ggplot(mydf, aes(x = x, y = predicted, colour = group)) + geom_point(data= all_tf, aes(x =Corolla_diameter_mean , y = pred, colour = Compatibility))+
+ggplot(mydf, aes(x = x, y = predicted, colour = group)) + xlab("Corolla diameter") + ylab("Predicted visits") + geom_point(data= all_tf, aes(x =Corolla_diameter_mean , y = pred, colour = Compatibility))+
   geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)+ xlab("Flower size") +
   ylab("Predicted visits")
 
@@ -116,13 +120,16 @@ hist(all_df$d)
 model_2 <- lmer(d ~ Compatibility + Corolla_diameter_mean + (1|Id) , data = all_df)
 fit<- simulateResiduals(fittedModel = model_2, plot = T)
 
+#library for r2
+library(MuMIn)
+r.squaredGLMM(model_2)
 
 mydf <- ggpredict(model_2, terms = c("Corolla_diameter_mean", "Compatibility"))
 all_tf<- all_df
 pred <-predict(model_2)
 all_tf
 
-ggplot(mydf, aes(x = x, y = predicted, colour = group)) + geom_point(data= all_tf, aes(x =Corolla_diameter_mean , y = pred, colour = Compatibility))+
+ggplot(mydf, aes(x = x, y = predicted, colour = group)) + xlab("Corolla diameter") + ylab("Predicted d") +geom_point(data= all_tf, aes(x =Corolla_diameter_mean , y = pred, colour = Compatibility))+
   geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
 
[…]

### 2020-05-26 Scripts/Analysis/Analysis_metric_vs_corolla_diameter.R

@@ -1,0 +1,155 @@
+#####################################
+###
+#### MODELS METRICS ~ OVULE NUMBER
+#####################################
+
+library(GLMMadaptive)
+library(emmeans)
+library(multcomp)
+library(ggplot2)
+library(ds4psy)
+library(dplyr)
+library(ggeffects)
+#load data
+all_df <- readRDS("Data/RData/network_metrics_main_traits.RData")
+colnames(all_df)[27]<-"Id"
+all_df <- as.data.frame(all_df) 
+all_df$Visits <- as.numeric(all_df$Visits)
+
+#Convert all NA'S to same type of NA's
+make.true.NA <- function(x) if(is.character(x)||is.factor(x)){
+  is.na(x) <- x=="NA"; x} else {
+    x}
+all_df$Corolla_diameter_mean <- make.true.NA(all_df$Corolla_diameter_mean)
+all_df <- all_df[complete.cases(all_df$Corolla_diameter_mean),]
+colnames(all_df) <- make.unique(names(all_df))
+all_df$Id <- as.factor(all_df$Id)
+all_df$Corolla_diameter_mean <- as.numeric(all_df$Corolla_diameter_mean)
+all_df$Visits <- as.numeric(all_df$Visits)
+
+
+#Funtion to check goodness of fit from https://drizopoulos.github.io/GLMMadaptive/articles/Goodness_of_Fit.html
+resids_plot <- function (object, y, nsim = 1000,
+                         type = c("subject_specific", "mean_subject"),
+                         integerResponse = NULL) {
+  if (!inherits(object, "MixMod"))
+    stop("this function works for 'MixMod' objects.\n")
+  type <- match.arg(type)
+  if (is.null(integerResponse)) {
+    integer_families <- c("binomial", "poisson", "negative binomial",
+                          "zero-inflated poisson", "zero-inflated negative binomial", 
+                          "hurdle poisson", "hurdle negative binomial")
+    numeric_families <- c("hurdle log-normal", "beta", "hurdle beta")
+    if (object$family$family %in% integer_families) {
+      integerResponse <- TRUE
+    } else if (object$family$family %in% numeric_families) {
+      integerResponse <- FALSE
+    } else {
+      stop("non build-in family object; you need to specify the 'integerResponse',\n",
[…]

### 2020-05-26 Scripts/Analysis/Analysis_metric_vs_corolla_length.R

@@ -1,0 +1,155 @@
+#####################################
+###
+#### MODELS METRICS ~ OVULE NUMBER
+#####################################
+
+library(GLMMadaptive)
+library(emmeans)
+library(multcomp)
+library(ggplot2)
+library(ds4psy)
+library(dplyr)
+library(ggeffects)
+#load data
+all_df <- readRDS("Data/RData/network_metrics_main_traits.RData")
+colnames(all_df)[27]<-"Id"
+all_df <- as.data.frame(all_df) 
+all_df$Visits <- as.numeric(all_df$Visits)
+
+#Convert all NA'S to same type of NA's
+make.true.NA <- function(x) if(is.character(x)||is.factor(x)){
+  is.na(x) <- x=="NA"; x} else {
+    x}
+all_df$Corolla_length_mean <- make.true.NA(all_df$Corolla_length_mean)
+all_df <- all_df[complete.cases(all_df$Corolla_length_mean),]
+colnames(all_df) <- make.unique(names(all_df))
+all_df$Id <- as.factor(all_df$Id)
+all_df$Corolla_length_mean <- as.numeric(all_df$Corolla_length_mean)
+all_df$Visits <- as.numeric(all_df$Visits)
+
+
+#Funtion to check goodness of fit from https://drizopoulos.github.io/GLMMadaptive/articles/Goodness_of_Fit.html
+resids_plot <- function (object, y, nsim = 1000,
+                         type = c("subject_specific", "mean_subject"),
+                         integerResponse = NULL) {
+  if (!inherits(object, "MixMod"))
+    stop("this function works for 'MixMod' objects.\n")
+  type <- match.arg(type)
+  if (is.null(integerResponse)) {
+    integer_families <- c("binomial", "poisson", "negative binomial",
+                          "zero-inflated poisson", "zero-inflated negative binomial", 
+                          "hurdle poisson", "hurdle negative binomial")
+    numeric_families <- c("hurdle log-normal", "beta", "hurdle beta")
+    if (object$family$family %in% integer_families) {
+      integerResponse <- TRUE
+    } else if (object$family$family %in% numeric_families) {
+      integerResponse <- FALSE
+    } else {
+      stop("non build-in family object; you need to specify the 'integerResponse',\n",
[…]

### 2020-05-26 Scripts/Analysis/Analysis_metric_vs_plant_height.R

@@ -24,9 +24,38 @@ all_df$plant_height_mean_m <- make.true.NA(all_df$plant_height_mean_m)
 all_df <- all_df[complete.cases(all_df$plant_height_mean_m),]
 colnames(all_df) <- make.unique(names(all_df))
 all_df$Id <- as.factor(all_df$Id)
-all_df$plant_height_mean_m <- as.integer(all_df$plant_height_mean_m)
-all_df$Visits <- as.integer(all_df$Visits)
+all_df$plant_height_mean_m <- as.numeric(all_df$plant_height_mean_m)
+all_df$Visits <- as.numeric(all_df$Visits)
 
+
+#Funtion to check goodness of fit from https://drizopoulos.github.io/GLMMadaptive/articles/Goodness_of_Fit.html
+resids_plot <- function (object, y, nsim = 1000,
+                         type = c("subject_specific", "mean_subject"),
+                         integerResponse = NULL) {
+  if (!inherits(object, "MixMod"))
+    stop("this function works for 'MixMod' objects.\n")
+  type <- match.arg(type)
+  if (is.null(integerResponse)) {
+    integer_families <- c("binomial", "poisson", "negative binomial",
+                          "zero-inflated poisson", "zero-inflated negative binomial", 
+                          "hurdle poisson", "hurdle negative binomial")
+    numeric_families <- c("hurdle log-normal", "beta", "hurdle beta")
+    if (object$family$family %in% integer_families) {
+      integerResponse <- TRUE
+    } else if (object$family$family %in% numeric_families) {
+      integerResponse <- FALSE
+    } else {
+      stop("non build-in family object; you need to specify the 'integerResponse',\n",
+           "\targument indicating whether the outcome variable is integer or not.\n")
+    }
+  }
+  sims <- simulate(object, nsim = nsim, type = type)
+  fits <- fitted(object, type = type)
+  dharmaRes <- DHARMa::createDHARMa(simulatedResponse = sims, observedResponse = y, 
+                                    fittedPredictedResponse = fits, 
+                                    integerResponse = integerResponse)
[…]

### 2020-05-26 Scripts/Analysis/Analysis_metric_vs_style_length.R

@@ -14,7 +14,7 @@ library(ggeffects)
 all_df <- readRDS("Data/RData/network_metrics_main_traits.RData")
 colnames(all_df)[27]<-"Id"
 all_df <- as.data.frame(all_df) 
-all_df$Visits <- as.integer(all_df$Visits)
+all_df$Visits <- as.numeric(all_df$Visits)
 
 #Convert all NA'S to same type of NA's
 make.true.NA <- function(x) if(is.character(x)||is.factor(x)){
@@ -24,9 +24,38 @@ all_df$style_length_mm <- make.true.NA(all_df$style_length_mm)
 all_df <- all_df[complete.cases(all_df$style_length_mm),]
 colnames(all_df) <- make.unique(names(all_df))
 all_df$Id <- as.factor(all_df$Id)
-all_df$style_length_mm <- as.integer(all_df$style_length_mm)
-all_df$Visits <- as.integer(all_df$Visits)
+all_df$style_length_mm <- as.numeric(all_df$style_length_mm)
+all_df$Visits <- as.numeric(all_df$Visits)
 
+
+#Funtion to check goodness of fit from https://drizopoulos.github.io/GLMMadaptive/articles/Goodness_of_Fit.html
+resids_plot <- function (object, y, nsim = 1000,
+                         type = c("subject_specific", "mean_subject"),
+                         integerResponse = NULL) {
+  if (!inherits(object, "MixMod"))
+    stop("this function works for 'MixMod' objects.\n")
+  type <- match.arg(type)
+  if (is.null(integerResponse)) {
+    integer_families <- c("binomial", "poisson", "negative binomial",
+                          "zero-inflated poisson", "zero-inflated negative binomial", 
+                          "hurdle poisson", "hurdle negative binomial")
+    numeric_families <- c("hurdle log-normal", "beta", "hurdle beta")
+    if (object$family$family %in% integer_families) {
+      integerResponse <- TRUE
+    } else if (object$family$family %in% numeric_families) {
+      integerResponse <- FALSE
+    } else {
+      stop("non build-in family object; you need to specify the 'integerResponse',\n",
+           "\targument indicating whether the outcome variable is integer or not.\n")
+    }
+  }
[…]

### 2020-05-26 Rmd/Quantitative_Data_Models_plot.Rmd
Models part 5

@@
 
-corolla_length_2 <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Corolla length")+ ylab("Predicted d")+geom_point(data= all_tf, aes(x =Corolla_length_mean , y = pred))+
+corolla_length_2 <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Corolla length (mm)")+ ylab("Predicted d")+geom_point(data= all_tf, aes(x =Corolla_length_mean , y = pred))+
   geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
@@
 ```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=9,fig.width=7}
+library(ds4psy)
+library(ggplot2)
+library(ggeffects)
+library(ggplot2)
+library(gridExtra)
+library(egg)
+library(magrittr)
+library(grid)
+library(Rmisc)
+library(cowplot)
+
+setwd("~/R_Projects/Reproductive Traits")
+
+model_4 <- readRDS("Data/RData/model_4_visits_plant_height_4.rds")
+pred <- readRDS("Data/RData/pred_plot_visits_plant_height_4.rds")
+all_tf <- readRDS("Data/RData/data_plot_visits_plant_height_4.rds")
+
+mydf <- ggpredict(model_4, terms = c("plant_height_mean_m"))
+plant_height_4 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Plant height") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted normalise degree") +geom_point(data= all_tf, aes(x =plant_height_mean_m , y = pred))+
+  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
+
+model_4 <- readRDS("Data/RData/model_4_visits_style_length_4.rds")
+pred <- readRDS("Data/RData/pred_plot_visits_style_length_4.rds")
+all_tf <- readRDS("Data/RData/data_plot_visits_style_length_4.rds")
+
+mydf <- ggpredict(model_4, terms = c("style_length_mm"))
+style_length_4 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Style length (mm)") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted normalise degree") +geom_point(data= all_tf, aes(x =style_length_mm , y = pred))+
+  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
+
+model_4 <- readRDS("Data/RData/model_4_visits_corolla_length_4.rds")
+pred <- readRDS("Data/RData/pred_plot_visits_corolla_length_4.rds")
+all_tf <- readRDS("Data/RData/data_plot_visits_corolla_length_4.rds")
+
+mydf <- ggpredict(model_4, terms = c("Corolla_length_mean"))
+corolla_length_4 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Corolla length (mm)") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted normalise degree") +geom_point(data= all_tf, aes(x =Corolla_length_mean , y = pred))+
+  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
+
+model_4 <- readRDS("Data/RData/model_4_visits_corolla_diameter_4.rds")
+pred <- readRDS("Data/RData/pred_plot_visits_corolla_diameter_4.rds")
+all_tf <- readRDS("Data/RData/data_plot_visits_corolla_diameter_4.rds")
+
+mydf <- ggpredict(model_4, terms = c("Corolla_diameter_mean"))
+corolla_diameter_4 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Corolla diameter (mm)") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted normalise degree") +geom_point(data= all_tf, aes(x =Corolla_diameter_mean , y = pred))+
+  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
+
+model_4 <- readRDS("Data/RData/model_4_visits_ovule_number_4.rds")
+pred <- readRDS("Data/RData/pred_plot_visits_ovule_number_4.rds")
+all_tf <- readRDS("Data/RData/data_plot_visits_ovule_number_4.rds")
+
+mydf <- ggpredict(model_4, terms = c("ovules_mean"))
+ovule_number_4 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Ovule number") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted normalise degree") +geom_point(data= all_tf, aes(x =ovules_mean , y = pred))+
+  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
+
+p <- plot_grid(plant_height_4,style_length_4, corolla_length_4,corolla_diameter_4,ovule_number_4,NULL, ncol = 2)
+
+title <- ggdraw() + draw_label("Normalise degree ~ TRAITS", fontface='bold')
+
+plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
+
+```

### 2020-05-26 Scripts/Analysis/Analysis_metric_vs_corolla_diameter.R

@@ -153,3 +153,28 @@ saveRDS(all_tf, "Data/RData/data_plot_visits_corolla_diameter_3.rds")
 saveRDS(model_3, "Data/RData/model_3_visits_corolla_diameter_3.rds")
 saveRDS(pred, "Data/RData/pred_plot_visits_corolla_diameter_3.rds")
 
+#####################################
+###
+#### MODEL 4 Normalised degree  ~ PLANT HEIGHT
+###
+#####################################
+
+
+model_4 <- mixed_model(normalised.degree ~ Corolla_diameter_mean, random = ~ 1 | Id, data = all_df,
+                       family = beta.fam(), max_phis_value=0)
+
+
+resids_plot(model_4, all_df$normalised.degree)
+#After trying with A Gaussian distribution and a Poisson, this is the family that best fit
+
+all_tf<- all_df
+all_tf <-predict(model_4, type="subject_specific",newdata = all_tf,return_newdata = TRUE)
+
+
+mydf <- ggpredict(model_4, terms = c("Corolla_diameter_mean"))
+ggplot(mydf, aes(x = x, y = predicted)) + xlab("Corolla diameter (mm)") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted normalise degree") +geom_point(data= all_tf, aes(x =Corolla_diameter_mean , y = pred))+
+  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
+
+saveRDS(all_tf, "Data/RData/data_plot_visits_corolla_diameter_4.rds")
+saveRDS(model_4, "Data/RData/model_4_visits_corolla_diameter_4.rds")
+saveRDS(pred, "Data/RData/pred_plot_visits_corolla_diameter_4.rds")

### 2020-05-26 Rmd/Quantitative_Data_Models_plot.Rmd
models

@@
 ```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=9,fig.width=7}
+library(ds4psy)
+library(ggplot2)
+library(ggeffects)
+library(ggplot2)
+library(gridExtra)
+library(egg)
+library(magrittr)
+library(grid)
+library(Rmisc)
+library(cowplot)
+
+setwd("~/R_Projects/Reproductive Traits")
+
+model_5 <- readRDS("Data/RData/model_5_visits_plant_height_5.rds")
+pred <- readRDS("Data/RData/pred_plot_visits_plant_height_5.rds")
+all_tf <- readRDS("Data/RData/data_plot_visits_plant_height_5.rds")
+
+mydf <- ggpredict(model_5, terms = c("plant_height_mean_m"))
+plant_height_5 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Plant height (m)") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted closeness") + geom_point(data= all_tf, aes(x =plant_height_mean_m , y = pred))+
+  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
+
+model_5 <- readRDS("Data/RData/model_5_visits_style_length_5.rds")
+pred <- readRDS("Data/RData/pred_plot_visits_style_length_5.rds")
+all_tf <- readRDS("Data/RData/data_plot_visits_style_length_5.rds")
+
+mydf <- ggpredict(model_5, terms = c("style_length_mm"))
+style_length_5 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("style_length (mm)")  + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted closeness") + geom_point(data= all_tf, aes(x =style_length_mm , y = pred))+
+  geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
+
+p <- plot_grid(plant_height_5,style_length_5, NULL, ncol = 2)
+
+title <- ggdraw() + draw_label("Normalise degree ~ TRAITS", fontface='bold')
+
+plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
+
+```

### 2020-05-26 Scripts/Analysis/Analysis_metric_vs_plant_height.R

@@ -213,8 +213,14 @@ all_tf$pred
 
 
 mydf <- ggpredict(model_5, terms = c("plant_height_mean_m"))
-ggplot(mydf, aes(x = x, y = predicted)) + xlab("Plant height") + ylab("Predicted closeness") + geom_point(data= all_tf, aes(x =plant_height_mean_m , y = pred))+
+ggplot(mydf, aes(x = x, y = predicted)) + xlab("Plant height (m)") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted closeness") + geom_point(data= all_tf, aes(x =plant_height_mean_m , y = pred))+
   geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
+
+saveRDS(all_tf, "Data/RData/data_plot_visits_plant_height_5.rds")
+saveRDS(model_4, "Data/RData/model_5_visits_plant_height_5.rds")
+saveRDS(pred, "Data/RData/pred_plot_visits_plant_height_5.rds")
+
+
 
 #####################################
 ###

### 2020-05-26 Scripts/Analysis/Analysis_metric_vs_style_length.R

@@ -210,8 +210,14 @@ all_tf$pred
 
 
 mydf <- ggpredict(model_5, terms = c("style_length_mm"))
-ggplot(mydf, aes(x = x, y = predicted)) + xlab("style_length_mm diameter")  + ylab("Predicted closeness") + geom_point(data= all_tf, aes(x =style_length_mm , y = pred))+
+ggplot(mydf, aes(x = x, y = predicted)) + xlab("style_length (mm)")  + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted closeness") + geom_point(data= all_tf, aes(x =style_length_mm , y = pred))+
   geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
+
+
+saveRDS(all_tf, "Data/RData/data_plot_visits_style_length_5.rds")
+saveRDS(model_5, "Data/RData/model_5_visits_style_length_5.rds")
+saveRDS(pred, "Data/RData/pred_plot_visits_style_length_5.rds")
+
 
 
 #####################################

### 2020-05-26 Rmd/Quantitative_Data_Models_plot.Rmd
models

@@
 
-p <- plot_grid(plant_height_5,style_length_5, NULL, ncol = 2)
+model_5 <- readRDS("Data/RData/model_5_visits_corolla_length_5.rds")
+pred <- readRDS("Data/RData/pred_plot_visits_corolla_length_5.rds")
+all_tf <- readRDS("Data/RData/data_plot_visits_corolla_length_5.rds")
 
-title <- ggdraw() + draw_label("Normalise degree ~ TRAITS", fontface='bold')
+mydf <- ggpredict(model_5, terms = c("Corolla_length_mean"))
+corolla_length_5 <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Corolla length (mm)")+ ylab("Predicted closeness")+geom_point(data= all_tf, aes(x =Corolla_length_mean , y = pred))+
+  geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
+
+model_5 <- readRDS("Data/RData/model_5_visits_corolla_diameter_5.rds")
+pred <- readRDS("Data/RData/pred_plot_visits_corolla_diameter_5.rds")
+all_tf <- readRDS("Data/RData/data_plot_visits_corolla_diameter_5.rds")
+
+mydf <- ggpredict(model_5, terms = c("Corolla_diameter_mean"))
+corolla_diameter_5 <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Corolla diamter (mm)")+ ylab("Predicted closeness")+geom_point(data= all_tf, aes(x =Corolla_diameter_mean , y = pred))+
+  geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
+
+model_5 <- readRDS("Data/RData/model_5_visits_ovule_number_5.rds")
+pred <- readRDS("Data/RData/pred_plot_visits_ovule_number_5.rds")
+all_tf <- readRDS("Data/RData/data_plot_visits_ovule_number_5.rds")
+
+mydf <- ggpredict(model_5, terms = c("ovules_mean"))
+ovule_number_5 <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Ovule number")+ ylab("Predicted d")+geom_point(data= all_tf, aes(x =ovules_mean , y = pred))+
+  geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)
+
+p <- plot_grid(plant_height_5,style_length_5,corolla_length_5,corolla_diameter_5, ovule_number_5, NULL, ncol = 2)
+
+title <- ggdraw() + draw_label("Closeness ~ TRAITS", fontface='bold')
 

### 2020-08-07 Rmd/Metadata_table.tex
brms model

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Untitled},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{Untitled}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\begin{landscape}

\begingroup\fontsize{7}{9}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\toprule
Id & Longitude & Latitude & Country & Year & Networks & Plant spp & Pollinator spp & Network size & Sampling method & Sampling & Data type\\
\midrule
\endfirsthead
\multicolumn{12}{@{}l}{\textit{(continued)}}\\
\toprule
Id & Longitude & Latitude & Country & Year & Networks & Plant spp & Pollinator spp & Network size & Sampling method & Sampling & Data type\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
\rowcolor{gray!6}  Bartomeus 2008 & 24 & 18.0 & Spain & 2005 & 3 & 18 & 37 & 666 & Plots with transects & Phytocentric & Quantitative\\
\addlinespace
Fang 2012 & 29 & 12.0 & China & 2008-2010 & 3 & 130 & 247 & 32110 & Plots & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Inouye 1990 & 18 & 14.0 & Japan & 1984-1987 & 4 & 114 & 883 & 100662 & Transects & Phytocentric & Quantitative\\
\addlinespace
Inouye 1988 & 19 & 7.0 & Australia & 1983-1984 & 1 & 40 & 85 & 3400 & Plots & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Kaiser-Bunbury 2009 & 27 & 4.0 & Republic of Mauritius & 2003-2004 & 2 & 96 & 184 & 17664 & Plots & Phytocentric & Quantitative\\
\addlinespace
Kaiser-Bunbury 2014 & 25 & 8.0 & Republic of Seychelles & 2007-2008 & 6 & 37 & 341 & 12617 & Transects & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Kato 2000 & 17 & 13.0 & Japan & 1996-1999 & 16 & 110 & 609 & 66990 & Transects & Phytocentric & Quantitative\\
\addlinespace
Kevan 1970 & 9 & 28.0 & Canada & 1967 & 1 & 20 & 91 & 1820 & Randow census walks & Phytocentric & Qualitative\\
\addlinespace
\rowcolor{gray!6}  Lundgren 2005 & 3 & 25.0 & Greenland & 2002 & 1 & 17 & 26 & 442 & Randow census walks & Phytocentric & Quantitative\\
\addlinespace
Olesen 2002 1 & 26 & 3.0 & Republic of Mauritius & 1998-1999 & 1 & 17 & 26 & 442 & Plots & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Mcmullen 1993 & 12 & 1.0 & Ecuador & NA & All islands & 105 & 54 & 5670 & - & Phytocentric & Qualitative\\
\addlinespace
Bartomeus 2008 & 24 & 18.0 & Spain & 2005 & 3 & 13 & 37 & 481 & Plots with transects & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Primack 1983 1 & 20 & 9.0 & New Zealand & 1976-1978 & 1 & 18 & 60 & 1080 & Randow census walks & Phytocentric & Qualitative\\
\addlinespace
Primack 1983 2 & 22 & 10.0 & New Zealand & 1976-1978 & 1 & 41 & 139 & 5699 & Randow census walks & Phytocentric & Qualitative\\
\addlinespace
\rowcolor{gray!6}  Primack 1983 3 & 21 & 11.0 & New Zealand & 1976-1978 & 1 & 49 & 118 & 5782 & Randow census walks & Phytocentric & Qualitative\\
\addlinespace
Ramirez 1989 & 6 & 20.0 & Venezuela & NA & 1 & 48 & 49 & 2352 & Randow census walks & Phytocentric & Qualitative\\
\addlinespace
\rowcolor{gray!6}  Ramirez 1992 & 7 & 27.0 & Venezuela & 1983,1984,1989 & 1 & 28 & 53 & 1484 & Randow census walks & Phytocentric & Qualitative\\
\addlinespace
Robertson 1929 & 11 & 16.0 & United States & 1997-1899 & NA & 456 & 1044 & 476064 & - & Phytocentric & Qualitative\\
\addlinespace
\rowcolor{gray!6}  Small 1976 & 10 & 19.0 & Canada & 1973 & 1 & 13 & 34 & 442 & 10h per spp & Phytocentric & Quantitative\\
\addlinespace
Souza 2018 & 4 & 5.0 & Brazil & 2008-2009 & 1 & 62 & 89 & 5518 & Plots & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Traveset 2013 & 13 & 2.0 & Ecuador & 2010-2011 & 1 & 60 & 220 & 13200 & Randow census walks & Phytocentric & Quantitative\\
\addlinespace
Bartomeus 2015 unp. & 5 & 15.0 & Spain & 2015 & 16 & 57 & 277 & 15789 & Transects & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Bek 2006 & 15 & 22.0 & Denmark & 2003 & 1 & 37 & 225 & 8325 & Plots & Phytocentric & Qualitative\\
\addlinespace
Olesen 2002 2 & 2 & 17.0 & Azores & 2000 & 1 & 10 & 12 & 120 & Plots & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Bundgaard 2003 & 16 & 22.0 & Denmark & 2003 & 1 & 16 & 44 & 704 & Plots & Phytocentric & Qualitative\\
\addlinespace
Chacoff 2011 & 8 & 6.0 & Argentina & 2006-2009 & 4 & 59 & 196 & 11564 & Plots & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Dicks 2002 & 14 & 21.0 & England & 2001? & 2 & 23 & 80 & 1840 & Plots & Phytocentric & Quantitative\\
\addlinespace
Dupont 2009 & 28 & 56.1 & Denmark & 2005 & 2 & 31 & 329 & 10199 & Plots & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Elberling 1999 & 23 & 24.0 & Sweden & 1994 & 1 & 24 & 118 & 2832 & Plots with transects & Phytocentric & Quantitative\\
\addlinespace
Dupont 2009 2 & 1 & 26.0 & Greenland & 1996-1997 & 1 & 31 & 76 & 2356 & Random census walks & Phytocentric & Qualitative\\*
\end{longtabu}
\endgroup{}
\end{landscape}

\end{document}

### 2020-08-18 Rmd/Data_organization_summary.Rmd
Removing Na's from networks that are giving issues

---
title: "Untitled"
output: html_document
---
This folder has networks of year duration with quantitative data (visitation)

# 1. Bartomeus 2008 (Network 1 in network all folder) 3 independent networks

1.1 Bartomeus 2008
1.2 Bartomeus 2008
1.3 Bartomeus 2008

# 2. Bartomeus 2008 (Network 2 in network all folder) 3 independent networks

2.1 Bartomeus 2008
2.2 Bartomeus 2008
2.3 Bartomeus 2008

# 3. Dicks 2002 (Network 6 in network all folder) 2 independent networks

3.1 Dicks 2002
3.2 Dicks 2002

# 4. Dupont 2009 (Network 7 in network all folder) 1 independent network, there are 3 but just have acces to 1 with quantitative data. I emailed Yoko Dupont but with no luck. In other published articles by their collaborator there are available two of these networks but just with qualitative data. Also it seems to be a metaweb joining these three networks with quantitative data but cannot split them.

4.1 Dupont 2009

# 5. Elberling 1999 (Network 8 in network all folder) 1 independent network.

5.1 Elberling 1999

# 6. Fang & Huang 2012 (Network 10 in network all folder) 4 independent networks but just 3 available with quantitative data.

6.1 Fang_huang_2008
6.2 Fang_huang_2009
6.3 Fang_huang_2010

# 7. Inouye 1988 (Network 12 in network all folder) 1 independent network that correspond to two sites close to each other that cannot be separated unfortunately.

7.1 Inouye 1988

# 8 Lundgren 2005 (Network 12 in network all folder) 1 independent network.

8.1 Lundgren 2005

# 9 Olesen 2002 (Network 18 and 30 in network all folder) 2 independent networks.

9.1 Olesen 2002 Mauritius

9.1 Olesen 2002 Azores

# 10 Small 2002 (Network 18 and 30 in network all folder) 2 independent networks.

10.1 Small 2002

# 11 Kaiser-bunbury 2017 (Network 30 and 30 in network all folder) 8 independent networks but 1 is from atea plantation https://doi.org/10.1038/nature21071 but also the study of 2014 https://doi.org/10.1890/14-0024.1

11.1  Kaiser-bunbury 2017 1 rosbelle

11.2  Kaiser-bunbury 2017 2 bernica

11.3  Kaiser-bunbury 2017 3 casse dent

11.4  Kaiser-bunbury 2017 4 copolia

11.5  Kaiser-bunbury 2017 5 reserve

11.6  Kaiser-bunbury 2017 6 salazie

11.7  Kaiser-bunbury 2017 7 trois freres

11.7  Kaiser-bunbury 2017 8 tea plantation

### 2020-09-09 Rmd/brms_metric_selfing.Rmd
preparing output visits inteher/selfing level

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---

# Model 1 
# $$Visits / SelfingLevel + (1|net_id) + (1|gr(phylo, cov = A))$$

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1_visits_self_all.RData")
load("Data/RData/brms_data_m1_visits_self_all.RData")

c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#Model fit
pp_check(m1) + xlim(-100,2000)+ylim(0,0.02)
#Estimates, se and ci
d <- p1[[1]][,c(1,7:10)]
kable(d, "latex")

```

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1_visits_self_all.RData")
load("Data/RData/brms_data_m1_visits_self_all.RData")

c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#Prepare example with selfing level
all_df_2 <- all_df_2 %>%
  mutate(autonomous_selfing_level = fct_relevel(autonomous_selfing_level, levels=c("high", "medium", "low", "none")))
all_df_2$autonomous_selfing_level <- as.factor(all_df_2$autonomous_selfing_level)

#Log
ggplot(data=p1[[1]], aes(x = autonomous_selfing_level, y = log(visits),color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=log(lower__), ymax=log(upper__)), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=autonomous_selfing_level, y=log(estimate__)), color="black") + ylab("Visits") + xlab("Selfing level")+
  theme(legend.position = "none")

```

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1_visits_self_all.RData")
load("Data/RData/brms_data_m1_visits_self_all.RData")

c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#ylim500
ggplot(data=p1[[1]], aes(x = autonomous_selfing_level, y = visits,color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
  theme(legend.position = "none")+ylim(0,500)

```

### 2020-09-09 Scripts/Analysis/Unique_network_analyses.R

@@ -186,11 +186,9 @@ all_df_1 <- all_df[,-c(2,3,6,7,8,13,16,63:75)]
 setnames(all_df_1, tolower(names(all_df_1)))
 #dding col named phylo for analysis
 all_df_1$phylo <- all_df_1$species
-##########################################################
-#4 CALCULATE PHYLOGENETIC DISTANCE
-##########################################################
 
-#FROM NOW ON REMEMBER TO USE THE CORRECTED SPECIES NAMES
+
+#Prepare species to calcute phylogenetic distance
 #Set these species as NA, the tree cannot find these species ad they are giving issues
 #if I leave them as NA
 all_df_1$species[all_df_1$species=="Diospyros seychellarum"] <- NA
@@ -207,8 +205,90 @@ all_df_1$species[all_df_1$fmily=="NA"] <- NA
 all_df_2 <- all_df_1[!is.na(all_df_1$species),]
 
 hist(all_df_2$visits)
-all_df_3 <- all_df_2[all_df_2$sex_or_flower_type!="separated",]
 
+
+##########################################################
+#4 Model1 (m1) VISITS~AUTONOMOUS SELFING LEVEL
+##########################################################
+
+#Prepare species, genus and family for calculating tree
+phylo <- as.data.frame(cbind(all_df_2$family, all_df_2$genus, all_df_2$species))
+colnames(phylo) <-  c("family", "genus", "species")
+
+#Select unique cases
+phylo_1 <- phylo[!duplicated(phylo$species),]
+phylo_2 <- tibble(phylo_1)
+phylo_3 <- get_tree(sp_list = phylo_2, tree = tree_plant_otl, taxon = "plant")
+
+#Convert phylogenetic tree into matrix
+A <- vcv.phylo(phylo_3)
+#Standardize to max value 1
+A <- A/max(A)
+#Unify column names; remove underscore and remove asterik
+rownames(A) <- gsub("\\*", "", rownames(A))
+colnames(A) <- gsub("\\*", "", colnames(A))
+colnames(A) <- gsub("_", " ", colnames(A))
+rownames(A) <- gsub("_", " ", rownames(A))
+
+
+#Convert all NA'S to same type of NA's
+make.true.NA <- function(x) if(is.character(x)||is.factor(x)){
+  is.na(x) <- x=="NA"; x} else {
+    x}
[…]

### 2020-09-09 Rmd/brms_metric_selfing.Rmd
d
Preparing brms visits~selfing output

@@
 ---
-title: "Untitled"
+header-includes:
+    - \usepackage{setspace}\doublespacing
 output:
@@
 
+\setlength{\abovedisplayskip}{25pt}
+\setlength{\belowdisplayskip}{25pt}
+\setlength{\abovedisplayshortskip}{25pt}
+\setlength{\belowdisplayshortskip}{25pt}
+
+```{r, echo = F}
+library(knitr)
+if(is_latex_output()) {
+  plot_default <- knit_hooks$get("plot")
+  knit_hooks$set(plot = function(x, options) { 
+    x <- c(plot_default(x, options), "\\vspace{25pt}")
+  })
+}
+```
+
 # Model 1
-# $$Visits / SelfingLevel + (1|net_id) + (1|gr(phylo, cov = A))$$
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
+```brm(visits ~ autonomous_selfing_level + (1|net_id) + (1|gr(phylo, cov = A))```
+
+This model contains both quantitative and qualitative data of selfing levels and the fixed effect is grouped in 4 categories of high, medium, low and none levels of selfing.
+The response variable is the integer of visits.
+
+Check now the fit of the model:
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=3.5, fig.height=2, fig.align='center'}
+library(brms)
+library(ggplot2)
+library(tidybayes)
+library(tidyverse)
+library(kableExtra)
+
+setwd("~/R_Projects/Reproductive traits") 
+load("Data/RData/brms_m1_visits_self_all.RData")
+load("Data/RData/brms_data_m1_visits_self_all.RData")
+
+#Model fit
+pp_check(m1) + xlim(-100,2000)+ylim(0,0.02)
+
+```
+
+The fit seems right, check now estimates, se and credible intervals:
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=3.5, fig.height=2, fig.align='center'}
+setwd("~/R_Projects/Reproductive traits") 
+load("Data/RData/brms_m1_visits_self_all.RData")
+load("Data/RData/brms_data_m1_visits_self_all.RData")
+c_e <- conditional_effects(m1)
+p1 <- plot(c_e, points=T,plot = FALSE)[[1]]
+
+#Estimates, se and ci
+d <- p1[[1]][,c(1,7:10)]
+kable(d, "latex") %>%  kable_styling(position = "center")
+
+```
+
+Plot output:
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=5, fig.height=2, fig.align='center'}
 library(brms)
@@
 
-#Model fit
-pp_check(m1) + xlim(-100,2000)+ylim(0,0.02)
-#Estimates, se and ci
-d <- p1[[1]][,c(1,7:10)]
-kable(d, "latex")
+#ylim500
+ggplot(data=p1[[1]], aes(x = autonomous_selfing_level, y = visits,color = ordered(autonomous_selfing_level))) +
+  geom_point(data = all_df_2,alpha = 1/4) + 
+  scale_fill_brewer(palette = "Greys") +
+  scale_color_brewer(palette = "Set2") + theme_bw() +
+  geom_errorbar(data=p1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
+  geom_point(data=p1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
+  theme(legend.position = "none")
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
+\newpage
+
+Set ylim max to 500 in order to improve visualization Some data points not shown.
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=5, fig.height=2, fig.align='center'}
+library(brms)
+library(ggplot2)
+library(tidybayes)
+library(tidyverse)
+library(kableExtra)
+
+setwd("~/R_Projects/Reproductive traits") 
+load("Data/RData/brms_m1_visits_self_all.RData")
+load("Data/RData/brms_data_m1_visits_self_all.RData")
+
+c_e <- conditional_effects(m1)
+p1 <- plot(c_e, points=T,plot = FALSE)[[1]]
+
+#ylim500
+ggplot(data=p1[[1]], aes(x = autonomous_selfing_level, y = visits,color = ordered(autonomous_selfing_level))) +
+  geom_point(data = all_df_2,alpha = 1/4) + 
+  scale_fill_brewer(palette = "Greys") +
+  scale_color_brewer(palette = "Set2") + theme_bw() +
+  geom_errorbar(data=p1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
+  geom_point(data=p1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
+  theme(legend.position = "none") + ylim(0,500)
+
+```
+
+Try now to logit estimates, credible intervals and points, maybe improves visualization?
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=5, fig.height=2, fig.align='center'}
 library(brms)
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
-library(brms)
-library(ggplot2)
-library(tidybayes)
-library(tidyverse)
-library(kableExtra)
+So far we haven't found big differences between groups. Also note that we have a greater number of low and none self species. This could be discussed. Keep in mind.
 
-setwd("~/R_Projects/Reproductive traits") 
-load("Data/RData/brms_m1_visits_self_all.RData")
-load("Data/RData/brms_data_m1_visits_self_all.RData")
-
-c_e <- conditional_effects(m1)
-p1 <- plot(c_e, points=T,plot = FALSE)[[1]]
-
-#ylim500
-ggplot(data=p1[[1]], aes(x = autonomous_selfing_level, y = visits,color = ordered(autonomous_selfing_level))) +
-  geom_point(data = all_df_2,alpha = 1/4) + 
-  scale_fill_brewer(palette = "Greys") +
-  scale_color_brewer(palette = "Set2") + theme_bw() +
-  geom_errorbar(data=p1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
-  geom_point(data=p1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
-  theme(legend.position = "none")+ylim(0,500)
-
-```
+Now I´m going to exclude the dioecious and monoecioues species that were considered as non-selfers.

### 2020-09-10 Rmd/brms_metric_selfing.Rmd
Preparing output

@@
 Now I´m going to exclude the dioecious and monoecioues species that were considered as non-selfers.
+
+# Model 2
+
+```brm(visits ~ autonomous_selfing_level + (1|net_id) + (1|gr(phylo, cov = A))```
+
+Check now the fit of the model:
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=3.5, fig.height=2, fig.align='center'}
+library(brms)
+library(ggplot2)
+library(tidybayes)
+library(tidyverse)
+library(kableExtra)
+
+setwd("~/R_Projects/Reproductive traits") 
+load("Data/RData/brms_m1.1_visits_self_all.RData")
+load("Data/RData/brms_data_m1.1_visits_self_all.RData")
+
+#Model fit
+pp_check(m1) + xlim(-100,2000)+ylim(0,0.02)
+```
+
+The fit seems right, check now estimates, se and credible intervals:
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=3.5, fig.height=2, fig.align='center'}
+setwd("~/R_Projects/Reproductive traits") 
+load("Data/RData/brms_m1_visits_self_all.RData")
+load("Data/RData/brms_data_m1_visits_self_all.RData")
+c_e <- conditional_effects(m1.1)
+p1 <- plot(c_e, points=T,plot = FALSE)[[1]]
+
+#Estimates, se and ci
+d <- p1[[1]][,c(1,7:10)]
+kable(d, "latex") %>%  kable_styling(position = "center")
+
+```
+
+Plot output:
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=5, fig.height=2, fig.align='center'}
+library(brms)
+library(ggplot2)
+library(tidybayes)
+library(tidyverse)
+library(kableExtra)
+
+setwd("~/R_Projects/Reproductive traits") 
+load("Data/RData/brms_m1.1_visits_self_all.RData")
+load("Data/RData/brms_data_m1.1_visits_self_all.RData")
+
+c_e <- conditional_effects(m1.1)
+p1 <- plot(c_e, points=T,plot = FALSE)[[1]]
+
+#ylim500
+ggplot(data=p1[[1]], aes(x = autonomous_selfing_level, y = visits,color = ordered(autonomous_selfing_level))) +
+  geom_point(data = all_df_2,alpha = 1/4) + 
+  scale_fill_brewer(palette = "Greys") +
+  scale_color_brewer(palette = "Set2") + theme_bw() +
+  geom_errorbar(data=p1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
+  geom_point(data=p1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
+  theme(legend.position = "none")
+
+```

### 2020-09-10 Rmd/brms_metric_selfing.Rmd
Running brms selfing models, still haver to run them again

@@
 
-This model contains both quantitative and qualitative data of selfing levels and the fixed effect is grouped in 4 categories of high, medium, low and none levels of selfing.
+This model contains both quantitative and qualitative data of selfing levels and the fixed effect is grouped in 4 categories: "high", "medium", "low" and none levels of selfing.
 The response variable is the integer of visits.
+Note that the quantitative measurement that we use is autonomous fruit production.
 

### 2020-09-11 Rmd/brms_metric_selfing.Rmd
BRMS SELFING

--- 2020-09-10 Rmd/brms_metric_selfing.Rmd
@@
 
-This model contains both quantitative and qualitative data of selfing levels and the fixed effect is grouped in 4 categories of high, medium, low and none levels of selfing.
+This model uses both quantitative and qualitative data of selfing levels which is grouped in 4 categories: "high", "medium", "low" and "none".
 The response variable is the integer of visits.
+Note that the quantitative measurement that we use is autonomous fruit production and is grouped as follows: 0=none, >0-25=low, >25-75=medium; >75-100=high.
 
@@
 
+\newpage
+
 # Model 2
@@
 
-c_e <- conditional_effects(m1.1)
-p1 <- plot(c_e, points=T,plot = FALSE)[[1]]
+c_e.1 <- conditional_effects(m1.1)
+p1.1 <- plot(c_e.1, points=T,plot = FALSE)[[1]]
 
 #ylim500
-ggplot(data=p1[[1]], aes(x = autonomous_selfing_level, y = visits,color = ordered(autonomous_selfing_level))) +
+ggplot(data=p1.1[[1]], aes(x = autonomous_selfing_level, y = visits,color = ordered(autonomous_selfing_level))) +
   geom_point(data = all_df_2,alpha = 1/4) + 
@@
   scale_color_brewer(palette = "Set2") + theme_bw() +
-  geom_errorbar(data=p1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
-  geom_point(data=p1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
+  geom_errorbar(data=p1.1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
+  geom_point(data=p1.1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
   theme(legend.position = "none")
@@
 ```
+
+\newpage
+
+Set ylim max to 500 in order to improve visualization Some data points not shown.
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=5, fig.height=2, fig.align='center'}
+library(brms)
+library(ggplot2)
+library(tidybayes)
+library(tidyverse)
+library(kableExtra)
+
+setwd("~/R_Projects/Reproductive traits") 
+load("Data/RData/brms_m1.1_visits_self_all.RData")
+load("Data/RData/brms_data_m1.1_visits_self_all.RData")
+
+c_e.1 <- conditional_effects(m1.1)
+p1.1 <- plot(c_e.1, points=T,plot = FALSE)[[1]]
+
+#ylim500
+ggplot(data=p1.1[[1]], aes(x = autonomous_selfing_level, y = visits,color = ordered(autonomous_selfing_level))) +
+  geom_point(data = all_df_2,alpha = 1/4) + 
+  scale_fill_brewer(palette = "Greys") +
+  scale_color_brewer(palette = "Set2") + theme_bw() +
+  geom_errorbar(data=p1.1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
+  geom_point(data=p1.1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
+  theme(legend.position = "none") + ylim(0,500)
+
+```

### 2020-09-14 Rmd/brms_metric_selfing.Rmd
edits

@@
 
-# Model 2
+# Model 2 Excluding species with flowers with separated sexes
 
@@
 
-The fit seems right, check now estimates, se and credible intervals:
+Again, the fit seems right, check now estimates, se and credible intervals:
 
@@
 ```
+
+Logit estimates, credible intervals and points
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=5, fig.height=2, fig.align='center'}
+library(brms)
+library(ggplot2)
+library(tidybayes)
+library(tidyverse)
+library(kableExtra)
+
+setwd("~/R_Projects/Reproductive traits") 
+load("Data/RData/brms_m1.1_visits_self_all.RData")
+load("Data/RData/brms_data_m1.1_visits_self_all.RData")
+
+c_e.1 <- conditional_effects(m1.1)
+p1.1 <- plot(c_e.1, points=T,plot = FALSE)[[1]]
+
+#Prepare example with selfing level
+all_df_2 <- all_df_2 %>%
+  mutate(autonomous_selfing_level = fct_relevel(autonomous_selfing_level, levels=c("high", "medium", "low", "none")))
+all_df_2$autonomous_selfing_level <- as.factor(all_df_2$autonomous_selfing_level)
+
+#Log
+ggplot(data=p1.1[[1]], aes(x = autonomous_selfing_level, y = log(visits),color = ordered(autonomous_selfing_level))) +
+  geom_point(data = all_df_2,alpha = 1/4) + 
+  scale_fill_brewer(palette = "Greys") +
+  scale_color_brewer(palette = "Set2") + theme_bw() +
+  geom_errorbar(data=p1.1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=log(lower__), ymax=log(upper__)), width=.1, color="black")+
+  geom_point(data=p1.1[[1]], mapping=aes(x=autonomous_selfing_level, y=log(estimate__)), color="black") + ylab("Visits") + xlab("Selfing level")+
+  theme(legend.position = "none")
+
+```
+
+Including or excluding dioecious and monoecious species does not make a very big differences in the models.
+
+BAYES R2 Model 1 including all species
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
+library(brms)
+library(ggplot2)
+library(tidybayes)
+library(tidyverse)
+library(kableExtra)
+setwd("~/R_Projects/Reproductive traits") 
+load("Data/RData/brms_m1.1_visits_self_all.RData")
+load("Data/RData/brms_m1_visits_self_all.RData")
+
+bayes_R2(m1)
+p1[[1]]
+```
+
+BAYES R2 Model 1 without monoecious and dioecious species
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
+library(brms)
+library(ggplot2)
+library(tidybayes)
+library(tidyverse)
+library(kableExtra)
+setwd("~/R_Projects/Reproductive traits") 
+load("Data/RData/brms_m1.1_visits_self_all.RData")
+load("Data/RData/brms_m1_visits_self_all.RData")
+bayes_R2(m1.1)
+p1.1[[1]]
+
+```
+
+Because the qualitative data can add some noise to the analysis now I'm going to exclude it and just consider species that have quantitative information of the auntonomous selfing level.
+
+#MODEL 3 JUST QUANTITATIVE DATA BUT GROUPED IN 4 CATEGORIES NONE, LOW, MEDIUM, HIGH.
+
+Two distributions fit the data: **Negative binomial** and **skew gaussian** with logit transformation of visits and because for the negative binomial I have to to log transform the data in order to improve visualization.
+I'm going to keep from now on with a **skew gaussian** with the logit of visits (the output is quite similar).
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
+library(brms)
+library(ggplot2)
+library(tidybayes)
+library(tidyverse)
+library(kableExtra)
+setwd("~/R_Projects/Reproductive traits") 
+load("Data/RData/brms_m1.2.1_visits_self_all.RData")
+load("Data/RData/brms_data_m1.2.1_visits_self_all.RData")
+
+c_e.1.2.1 <- conditional_effects(m1.2.1)
+p1.2.1 <- plot(c_e.1.2.1, points=T,plot = FALSE)[[1]]
+
+ggplot(data=p1.2.1[[1]], aes(x = autonomous_selfing_level, y = log(visits),color = ordered(autonomous_selfing_level))) +
+  geom_point(data = all_df_4,alpha = 1/4) + 
+  scale_fill_brewer(palette = "Greys") +
+  scale_color_brewer(palette = "Set2") + theme_bw() +
+  geom_errorbar(data=p1.2.1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
+  geom_point(data=p1.2.1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
+  theme(legend.position = "none")
+
+bayes_R2(m1.2.1)
+
+p1.2.1[[1]]
+
+```

### 2020-09-17 Visits_Traits.Rmd
Preparing summary of what I have found

---
header-includes:
    - \usepackage{setspace}\doublespacing
output:
  pdf_document: default
  html_document: default
---

\setlength{\abovedisplayskip}{25pt}
\setlength{\belowdisplayskip}{25pt}
\setlength{\abovedisplayshortskip}{25pt}
\setlength{\belowdisplayshortskip}{25pt}

```{r, echo = F}
library(knitr)
if(is_latex_output()) {
  plot_default <- knit_hooks$get("plot")
  knit_hooks$set(plot = function(x, options) { 
    x <- c(plot_default(x, options), "\\vspace{25pt}")
  })
}
```

#COMPATIBILITY

##VISITS~COMPATIBILITY

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Compatibility/brms_m1_visits_compatibility_negative_binomial.RData")
load("Data/Brms/Compatibility/brms_data_compatibility.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = compatibility, y = log(visits),color = ordered(compatibility))) +
  geom_point(data = all_df_3,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=compatibility, ymin=log(lower__), ymax=log(upper__)), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=compatibility, y=log(estimate__)), color="black") + ylab("log(Visits)") + xlab("Compatibility")+
  theme(legend.position = "none")

```

##Z-SCORES~COMPATIBILITY

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Compatibility/brms_m2_z-scores_compatibility_student.RData")
load("Data/Brms/Compatibility/brms_data_compatibility.RData")
c_e <- conditional_effects(m2)
p2 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p2[[1]], aes(x = compatibility, y = z_score_sum,color = ordered(compatibility))) +
  geom_point(data = all_df_3,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p2[[1]],mapping=aes(x=compatibility, ymin=lower__, ymax=upper__), width=.1, color="black")+
  geom_point(data=p2[[1]], mapping=aes(x=compatibility, y=estimate__), color="black") + ylab("Z-score") + xlab("Compatibility")+
  theme(legend.position = "none")

```

\newpage

#AUTONOMOUS SELFING FRUIT SET

##VISITS~SELFING:QUALITATIVE DATA

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Selfing/brms_m1_visits_selfing_negative_binomial.RData")
load("Data/Brms/Selfing/brms_data_m1_selfing.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = autonomous_selfing_level, y = log(visits),color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=log(lower__), ymax=log(upper__)), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=autonomous_selfing_level, y=log(estimate__)), color="black") + ylab("log(Visits)") + xlab("Autonomous selfing level")+
  theme(legend.position = "none")

```

##VISITS~SELFING:QUANTITATIVE DATA

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Selfing/brms_m3_visits_selfing_negative_binomial.RData")
load("Data/Brms/Selfing/brms_data_m3_selfing.RData")
c_e <- conditional_effects(m3)
p3 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p3[[1]], aes(x = autonomous_selfing_level_fruit_set, y = log(visits))) +
geom_point(data = all_df_3,alpha = 1/4) + 
scale_fill_brewer(palette = "Greys") +
scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p3[[1]],
aes(y = log(estimate__), ymin = log(lower__), ymax = log(upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

\newpage

#AUTONOMOUS SELFING FRUIT SET

##Z-SCORES~SELFING:QUALITATIVE DATA

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Selfing/brms_m4_z-scores_selfing_student.RData")
load("Data/Brms/Selfing/brms_data_m4_selfing.RData")
c_e <- conditional_effects(m4)
p4 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT
ggplot(data=p4[[1]], aes(x = autonomous_selfing_level, y = z_score_sum,color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p4[[1]],mapping=aes(x=autonomous_selfing_level, ymin=(lower__), ymax=(upper__)), width=.1, color="black")+
  geom_point(data=p4[[1]], mapping=aes(x=autonomous_selfing_level, y=(estimate__)), color="black") + ylab("Z-score") + xlab("Selfing level")+theme(legend.position = "none")

```

##Z-SCORES-SELFING:QUALITATIVE DATA

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Selfing/brms_m5_z-scores_selfing_student.RData")
load("Data/Brms/Selfing/brms_data_m5_selfing.RData")
c_e <- conditional_effects(m5)
p5 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p5[[1]], aes(x = autonomous_selfing_level_fruit_set, y = z_score_sum)) +
  geom_point(data = all_df_3,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p5[[1]],
  aes(y = estimate__, ymin = lower__, ymax = upper__),stat = "identity", color = "black", alpha = 0.1, size = 1/2)+
  ylab("Z-scores")+ xlab("Autonomous selfing-fruit set")

```

### 2020-09-18 Degree_Traits.Rmd
degree~traits

---
header-includes:
    - \usepackage{setspace}\doublespacing
output:
  pdf_document: default
  html_document: default
---

\setlength{\abovedisplayskip}{25pt}
\setlength{\belowdisplayskip}{25pt}
\setlength{\abovedisplayshortskip}{25pt}
\setlength{\belowdisplayshortskip}{25pt}

```{r, echo = F}
library(knitr)
if(is_latex_output()) {
  plot_default <- knit_hooks$get("plot")
  knit_hooks$set(plot = function(x, options) { 
    x <- c(plot_default(x, options), "\\vspace{25pt}")
  })
}
```

#COMPATIBILITY

##DEGREE~COMPATIBILITY

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Compatibility/brms_m1_degree_compatibility.RData")
load("Data/Brms/Compatibility/brms_data_degree_m1_compatibility.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT
ggplot(data=p1[[1]], aes(x = reorder(compatibility, -degree), y = degree,color = ordered(compatibility))) +
  geom_point(data = all_df_3,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=compatibility, ymin=lower__, ymax=upper__), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=compatibility, y=estimate__), color="black") + ylab("Degree") + xlab("Selfing level")+
  theme(legend.position = "none")

```

\newpage

#SELFING

##DEGREE~SELFING QUALITATIVE

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Selfing/brms_m1_degree_selfing_quant_and_quali_negative_binomial.RData")
load("Data/Brms/Selfing/brms_data_degree_m2_m3_selfing.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT
ggplot(data=p1[[1]], aes(x = autonomous_selfing_level, y = degree,color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+theme(legend.position = "none")

```

##DEGREE~SELFING QUANTITATIVE

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Selfing/brms_m3_degree_selfing_quant_negative_binomial.RData")
load("Data/Brms/Selfing/brms_data_degree_m1_selfing.RData")
c_e3 <- conditional_effects(m3)
p3 <- plot(c_e3, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT
ggplot(data=p3[[1]], aes(x = autonomous_selfing_level_fruit_set, y = log(degree))) +
  geom_point(data = all_df_3,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p3[[1]],
 aes(y = log(estimate__), ymin = log(lower__), ymax = log(upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

#FLOWER DIAMETER

##DEGREE~FLOWER DIAMETER

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Flower_size/brms_m1_visits_flower_diameter_negative_binomial.RData")
load("Data/Brms/Flower_size/brms_data_flower_diameter.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = log(corolla_diameter_mean), y = log(visits))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p1[[1]],
  aes(y = log(estimate__), ymin = log(lower__), ymax = log(upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

\newpage

#FLOWER LENGTH

##DEGREE~FLOWER LENGTH

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Flower_size/brms_m1_degree_flower_length_negative_binomial.RData")
load("Data/Brms/Flower_size/brms_data_degree_flower_length.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = log(corolla_length_mean), y = degree)) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p1[[1]],
  aes(y = log(estimate__), ymin = log(lower__), ymax = log(upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

\newpage

#STYLE LENGTH

##DEGREE~STYLE LENGTH

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Style_length/brms_m1_degree_style_length_negative_binomial.RData")
load("Data/Brms/Style_length/brms_data_degree_style_length.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = log(style_length_mm), y = degree)) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p1[[1]],
 aes(y = (estimate__), ymin = (lower__), ymax = (upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

\newpage

#OVULE NUMBER

##DEGREE~OVULE NUMBER

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Ovule_number/brms_m1_degree_ovules_mean_negative_binomial.RData")
load("Data/Brms/Ovule_number/brms_data_degree_ovules_mean.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = log(ovules_mean), y = log(visits))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p1[[1]],
 aes(y = log(estimate__), ymin = log(lower__), ymax = log(upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

\newpage

#FLOWER MORPHOLOGY

##DEGREE~FLOWER MORPHOLOGY

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Flower_morphology/brms_m1_degree_flower_morphology.RData")
load("Data/Brms/Flower_morphology/brms_data_degree_m1_flower_morphology.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = reorder(flower_morphology, -degree), y = degree,color = ordered(flower_morphology))) +
  geom_point(data = all_df_3,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=flower_morphology, ymin=lower__, ymax=upper__), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=flower_morphology, y=estimate__), color="black") + ylab("Degree") + xlab("Selfing level")+
  theme(legend.position = "none")

```

\newpage

#FLOWER SYMMETRY
##DEGREE~FLOWER SYMMETRY

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Flower_symmetry/brms_m1_degree_flower_symmetry_negative_binomial.RData")
load("Data/Brms/Flower_symmetry/brms_data_degree_flower_symmetry.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = flower_symmetry, y = degree,color = ordered(flower_symmetry))) +
  geom_point(data = all_df_3,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=flower_symmetry, ymin=(lower__), ymax=(upper__)), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=flower_symmetry, y=(estimate__)), color="black") + ylab("log(Visits)") + xlab("Flower symmetry")+theme(legend.position = "none")

```

#PLANT HEIGHT
##DEGREE~PLANT HEIGHT

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Plant_height/brms_m1_degree_plant_height_negative_binomial.RData")
load("Data/Brms/Plant_height/brms_data_degree_plant_height.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = log(plant_height_mean_m), y = degree)) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p1[[1]],
 aes(y = (estimate__), ymin = (lower__), ymax = (upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

### 2020-09-25 Rmd/Visits_Traits.Rmd
Playing with Jamies code

---
header-includes:
    - \usepackage{setspace}\doublespacing
output:
  pdf_document: default
  html_document: default
---

\setlength{\abovedisplayskip}{25pt}
\setlength{\belowdisplayskip}{25pt}
\setlength{\abovedisplayshortskip}{25pt}
\setlength{\belowdisplayshortskip}{25pt}

```{r, echo = F}
library(knitr)
if(is_latex_output()) {
  plot_default <- knit_hooks$get("plot")
  knit_hooks$set(plot = function(x, options) { 
    x <- c(plot_default(x, options), "\\vspace{25pt}")
  })
}
```

#COMPATIBILITY

##VISITS~COMPATIBILITY

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Compatibility/brms_m1_visits_compatibility_negative_binomial.RData")
load("Data/Brms/Compatibility/brms_data_compatibility.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = compatibility, y = log(visits),color = ordered(compatibility))) +
  geom_point(data = all_df_3,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=compatibility, ymin=log(lower__), ymax=log(upper__)), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=compatibility, y=log(estimate__)), color="black") + ylab("log(Visits)") + xlab("Compatibility")+
  theme(legend.position = "none")

```

##Z-SCORES~COMPATIBILITY

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Compatibility/brms_m2_z-scores_compatibility_student.RData")
load("Data/Brms/Compatibility/brms_data_compatibility.RData")
c_e <- conditional_effects(m2)
p2 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p2[[1]], aes(x = compatibility, y = z_score_sum,color = ordered(compatibility))) +
  geom_point(data = all_df_3,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p2[[1]],mapping=aes(x=compatibility, ymin=lower__, ymax=upper__), width=.1, color="black")+
  geom_point(data=p2[[1]], mapping=aes(x=compatibility, y=estimate__), color="black") + ylab("Z-score") + xlab("Compatibility")+
  theme(legend.position = "none")

```

\newpage

#AUTONOMOUS SELFING FRUIT SET

##VISITS~SELFING:QUALITATIVE DATA

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Selfing/brms_m1_visits_selfing_negative_binomial.RData")
load("Data/Brms/Selfing/brms_data_m1_selfing.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = autonomous_selfing_level, y = log(visits),color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=log(lower__), ymax=log(upper__)), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=autonomous_selfing_level, y=log(estimate__)), color="black") + ylab("log(Visits)") + xlab("Autonomous selfing level")+
  theme(legend.position = "none")

```

##VISITS~SELFING:QUANTITATIVE DATA

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Selfing/brms_m3_visits_selfing_negative_binomial.RData")
load("Data/Brms/Selfing/brms_data_m3_selfing.RData")
c_e <- conditional_effects(m3)
p3 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p3[[1]], aes(x = autonomous_selfing_level_fruit_set, y = log(visits))) +
geom_point(data = all_df_3,alpha = 1/4) + 
scale_fill_brewer(palette = "Greys") +
scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p3[[1]],
aes(y = log(estimate__), ymin = log(lower__), ymax = log(upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

\newpage

#AUTONOMOUS SELFING FRUIT SET

##Z-SCORES~SELFING:QUALITATIVE DATA

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Selfing/brms_m4_z-scores_selfing_student.RData")
load("Data/Brms/Selfing/brms_data_m4_selfing.RData")
c_e <- conditional_effects(m4)
p4 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT
ggplot(data=p4[[1]], aes(x = autonomous_selfing_level, y = z_score_sum,color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p4[[1]],mapping=aes(x=autonomous_selfing_level, ymin=(lower__), ymax=(upper__)), width=.1, color="black")+
  geom_point(data=p4[[1]], mapping=aes(x=autonomous_selfing_level, y=(estimate__)), color="black") + ylab("Z-score") + xlab("Selfing level")+theme(legend.position = "none")

```

##Z-SCORES-SELFING:QUALITATIVE DATA

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Selfing/brms_m5_z-scores_selfing_student.RData")
load("Data/Brms/Selfing/brms_data_m5_selfing.RData")
c_e <- conditional_effects(m5)
p5 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p5[[1]], aes(x = autonomous_selfing_level_fruit_set, y = z_score_sum)) +
  geom_point(data = all_df_3,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p5[[1]],
  aes(y = estimate__, ymin = lower__, ymax = upper__),stat = "identity", color = "black", alpha = 0.1, size = 1/2)+
  ylab("Z-scores")+ xlab("Autonomous selfing-fruit set")

```

#FLOWER DIAMETER

##VISITS-FLOWER DIAMETER

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Flower_size/brms_m1_visits_flower_diameter_negative_binomial.RData")
load("Data/Brms/Flower_size/brms_data_flower_diameter.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = log(corolla_diameter_mean), y = log(visits))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p1[[1]],
  aes(y = log(estimate__), ymin = log(lower__), ymax = log(upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

##Z-SCORES-FLOWER DIAMETER

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Flower_size/brms_m2_z-scores_flower_diameter_student.RData")
load("Data/Brms/Flower_size/brms_data_flower_diameter.RData")
c_e2 <- conditional_effects(m2)
p2 <- plot(c_e2, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p2[[1]], aes(x = log(corolla_diameter_mean), y = (z_score_sum))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p2[[1]],
  aes(y = (estimate__), ymin = (lower__), ymax = (upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

#FLOWER LENGTH

##VISITS-FLOWER LENGTH

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Flower_size/brms_m1_visits_flower_length_negative_binomial.RData")
load("Data/Brms/Flower_size/brms_data_flower_length.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = log(corolla_length_mean), y = log(visits))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p1[[1]],
  aes(y = log(estimate__), ymin = log(lower__), ymax = log(upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

##Z-SCORES-FLOWER LENGTH

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Flower_size/brms_m2_z-scores_flower_length_student.RData")
load("Data/Brms/Flower_size/brms_data_flower_length.RData")
c_e2 <- conditional_effects(m2)
p2 <- plot(c_e2, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p2[[1]], aes(x = log(corolla_length_mean), y = (z_score_sum))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p2[[1]],
  aes(y = (estimate__), ymin = (lower__), ymax = (upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

#STYLE LENGTH

##VISITS-STYLE LENGTH

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Style_length/brms_m1_visits_style_length_negative_binomial.RData")
load("Data/Brms/Style_length/brms_data_style_length.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = log(style_length_mm), y = log(visits))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p1[[1]],
  aes(y = log(estimate__), ymin = log(lower__), ymax = log(upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

##Z-SCORES-STYLE LENGTH

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Style_length/brms_m1_z-scores_style_length_student.RData")
load("Data/Brms/Style_length/brms_data_style_length.RData")
c_e2 <- conditional_effects(m2)
p2 <- plot(c_e2, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p2[[1]], aes(x = log(style_length_mm), y = z_score_sum)) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p2[[1]],
  aes(y = (estimate__), ymin = (lower__), ymax = (upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

#OVULE NUMBER

##VISITS-OVULE NUMBER

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Ovule_number/brms_m1_visits_ovules_mean_negative_binomial.RData")
load("Data/Brms/Ovule_number/brms_data_ovules_mean.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = log(ovules_mean), y = log(visits))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p1[[1]],
  aes(y = log(estimate__), ymin = log(lower__), ymax = log(upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

##Z-SCORES-OVULE NUMBER
```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Ovule_number/brms_m1_z-scores_ovules_mean_student.RData")
load("Data/Brms/Ovule_number/brms_data_ovules_mean.RData")
c_e2 <- conditional_effects(m2)
p2 <- plot(c_e2, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p2[[1]], aes(x = log(ovules_mean), y = z_score_sum)) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p2[[1]],
  aes(y = (estimate__), ymin = (lower__), ymax = (upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

\newpage

#FLOWER MORPHOLOGY

##VISITS-FLOWER MORPHOLOGY

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Flower_morphology/brms_m1_visits_flower_morphology_negative_binomial.RData")
load("Data/Brms/Flower_morphology/brms_data_flower_morphology.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = reorder(flower_morphology,visits), y = log(visits),color = ordered(flower_morphology))) +
  geom_point(data = all_df_3,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=flower_morphology, ymin=log(lower__), ymax=log(upper__)), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=flower_morphology, y=log(estimate__)), color="black") + ylab("log(Visits)") + xlab("Flower morphology")+
  theme(legend.position = "none")

```

##Z-SCORES-FLOWER MORPHOLOGY

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Flower_morphology/brms_m1_z-scores_flower_morphology_student.RData")
load("Data/Brms/Flower_morphology/brms_data_flower_morphology.RData")
c_e <- conditional_effects(m2)
p2 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p2[[1]], aes(x = reorder(flower_morphology,z_score_sum), y = z_score_sum,color = ordered(flower_morphology))) +
  geom_point(data = all_df_3,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p2[[1]],mapping=aes(x=flower_morphology, ymin=lower__, ymax=(upper__)), width=.1, color="black")+
  geom_point(data=p2[[1]], mapping=aes(x=flower_morphology, y=estimate__), color="black") + ylab("Z-scores") + xlab("Flower morphology")+
  theme(legend.position = "none")

```

\newpage

#FLOWER SYMMETRY

##VISITS-FLOWER SYMMETRY

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Flower_symmetry/brms_m1_visits_flower_symmetry_negative_binomial.RData")
load("Data/Brms/Flower_symmetry/brms_data_flower_symmetry.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = flower_symmetry, y = log(visits),color = ordered(flower_symmetry))) +
  geom_point(data = all_df_3,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=flower_symmetry, ymin=log(lower__), ymax=log(upper__)), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=flower_symmetry, y=log(estimate__)), color="black") + ylab("log(Visits)") + xlab("Flower symmetry")+
  theme(legend.position = "none")

```

##Z-SCORES-FLOWER SYMMETRY

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Flower_symmetry/brms_m1_z-scores_flower_symmetry_student.RData")
load("Data/Brms/Flower_symmetry/brms_data_flower_symmetry.RData")
c_e2 <- conditional_effects(m2)
p2 <- plot(c_e2, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p2[[1]], aes(x = flower_symmetry, y = z_score_sum,color = ordered(flower_symmetry))) +
  geom_point(data = all_df_3,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p2[[1]],mapping=aes(x=flower_symmetry, ymin=lower__, ymax=upper__), width=.1, color="black")+
  geom_point(data=p2[[1]], mapping=aes(x=flower_symmetry, y=estimate__), color="black") + ylab("Z-scores") + xlab("Flower symmetry")+
  theme(legend.position = "none")

```

#PLANT HEIGHT

##VISITS-PLANT HEIGHT

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Plant_height/brms_m1_visits_plant_height_negative_binomial.RData")
load("Data/Brms/Plant_height/brms_data_plant_height.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p1[[1]], aes(x = log(plant_height_mean_m), y = log(visits))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p1[[1]],
 aes(y = log(estimate__), ymin = log(lower__), ymax = log(upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

##Z-SCORES-PLANT HEIGHT

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=7, fig.height=3, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/Brms/Plant_height/brms_m1_z-scores_plant_height_student.RData")
load("Data/Brms/Plant_height/brms_data_plant_height.RData")
c_e2 <- conditional_effects(m2)
p2 <- plot(c_e2, points=T,plot = FALSE)[[1]]

#PLOT OUTPUT

ggplot(data=p2[[1]], aes(x = log(plant_height_mean_m), y = (z_score_sum))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() + geom_smooth(data = p2[[1]],
 aes(y = (estimate__), ymin = (lower__), ymax = (upper__)),stat = "identity", color = "black", alpha = 0.1, size = 1/2)

```

### 2020-09-25 Scripts/Analysis/Functional_groups/functional-groups.R

@@ -19,6 +19,7 @@ require(RANN)
 #-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
 
 e <- read.csv("traits.csv", header=TRUE, row.names=1)
+e <- read.csv("Data/Csv/long_all.csv", header=TRUE, row.names=1)
 
 #-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
 #create trait weighting vector so that all trait grouping = 1 (hairiness; phenology; activity times; bodysize; tounge length; pollen collection structure)
@@ -36,20 +37,34 @@ w <- c(0.142857143,	0.142857143,	0.142857143,	0.142857143, 0.142857143,	0.142857
 #-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
 
 e.dist <- gowdis(e, w)
+e$Compatibility
 
+e_1 <- e[c("Corolla_length_mean","Floral_unit_width","style_length_mm", "Autonomous_selfing_level_fruit_set","ovules_mean","plant_height_mean_m")]
+library(dplyr)
+e_1[,c(1:6)] <- scale(mutate_all(e_1[,c(1:6)], function(x) as.numeric(as.character(x))))
+e_1 <- e_1[complete.cases(e_1), ]
+
+str(e_1)
+e.dist <- gowdis(e_1)
+plot(noclus)
+kgs[]
+?kgs
 #-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
 #find optimal number of functional groups
 #-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+noclus <- agnes(e_1, method="ward")
+noclus <- hclust(e_1, method="ward.D")
+noclus <- hclust(e.dist, method="ward.D2")
 
-noclus <- agnes(e.dist, method="ward")
-b <- kgs(noclus, noclus$diss, maxclust=21)#6 clusters has lowest penalty score
+noclus$diss
+b <- kgs(noclus,e.dist, maxclust=21)#6 clusters has lowest penalty score
 plot(names (b), b, xlab="Number of Clusters", ylab="Penalty score")
 
 #-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
 #silhouette plot
[…]

### 2020-11-11 Rmd/PCA.Rmd
Principal component analysis of the different quantitative variables separated by qualitatie ones

---
header-includes:
    - \usepackage{setspace}\doublespacing
output:
  pdf_document: default
  html_document: default
---

\setlength{\abovedisplayskip}{25pt}
\setlength{\belowdisplayskip}{25pt}
\setlength{\abovedisplayshortskip}{25pt}
\setlength{\belowdisplayshortskip}{25pt}

```{r, echo = F}
library(knitr)
knitr::opts_chunk$set(message = FALSE)

if(is_latex_output()) {
  plot_default <- knit_hooks$get("plot")
  knit_hooks$set(plot = function(x, options) { 
    x <- c(plot_default(x, options), "\\vspace{25pt}")
  })
}
```

# PCA QUANTITATIVE DATA-SELFING LEVEL

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.width=9, fig.height=9, fig.align='center'}
#LOAD LIBRARIES
library(readxl) #read excel file (trait data)
library(dplyr) #data manipulation
library(missMDA) #For missing values
library(FactoMineR) #Produce pca biplot with individuals and variables
library(factoextra)
library(ggpubr)

#change working directory
setwd("~/R_Projects/Reproductive traits")

#LOAD DATA
trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
#select just filled rows
trait_data_1 <- trait_data[1:1701,]
#filter data, select species with flower level info and capitulum
trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
levels(as.factor(trait_filtered$Info_level))
#select columns of interest
traits <- trait_filtered %>% select(Order_all,Family_all,Genus_all,Species_all,Breeding_system,IMPUTED_Compatibility,Autonomous_selfing_level,Autonomous_selfing_level_data_type,Autonomous_selfing_level_fruit_set,Flower_morphology,Flower_symmetry,Flowers_per_plant,Flowers_per_inflorescence,Floral_unit_width,Corolla_diameter_mean,Corolla_length_mean,STYLE_IMPUTED,OVULES_IMPUTED,life_form,lifespan,IMPUTED_plant_height_mean_m)
#Remove duplicated species
t <- traits[!duplicated(traits$Species_all), ]
#check structure of the data
str(t)
#remove cases where the species is NA 
t <- t[!is.na(t$Species_all), ]

str(t)
t_trial <- t[,c(5,6,7,9:21)]
str(t_trial)
cols <- c( "Breeding_system","IMPUTED_Compatibility", "Autonomous_selfing_level","Flower_morphology","Flower_symmetry", "life_form", "lifespan")

t_trial[cols] <- lapply(t_trial[cols], factor)  ## as.factor() could also be used

colnames(t_trial) <- c("Breeding system","Compatibility system","Selfing_level", "Quantitative selfing","Flower morphology","Flower symmetry",  "Flower/plant", "Flower/inflorescence", "Inflorescence width", "Flower width",  "Flower length",  "Style length", "Ovule number", "Life form","Life span", "Plant height")

str(t_trial$`Life form`)
t_trial$Selfing_level<- as.factor(t_trial$Selfing_level)
res.impute <- imputeFAMD(t_trial, ncp=3,threshold = 1e-06)

res.impute$completeObs$Selfing_level <- factor(res.impute$completeObs$Selfing_level, levels = c("high", "medium", "low", "none"))

#from http://www.zhuoyao.net/2019/11/08/principal-component-methods-in-r-practical-guide/
fviz_pca_biplot(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="var",
              geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(3)], 
                pointshape = 19, pointsize = 1,
                palette = c("#FDE725FF","#31688EFF","#440154FF", "#35B779FF"),
                # Variables
                col.var = "black",title="",  arrowsize = 0.6,alpha.var=0.7)+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Selfing")

res.impute$completeObs$Selfing_level <- as.character(res.impute$completeObs$Selfing_level)
res.impute$completeObs$Selfing_level[res.impute$completeObs$Selfing_level=="high"] <- "selfer"
res.impute$completeObs$Selfing_level[res.impute$completeObs$Selfing_level=="medium"] <- "selfer"
res.impute$completeObs$Selfing_level[res.impute$completeObs$Selfing_level=="low"] <- "non_selfer"
res.impute$completeObs$Selfing_level[res.impute$completeObs$Selfing_level=="none"] <- "non_selfer"
res.impute$completeObs$Selfing_level <- as.factor(res.impute$completeObs$Selfing_level)

#from http://www.zhuoyao.net/2019/11/08/principal-component-methods-in-r-practical-guide/
fviz_pca_biplot(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="var",
              geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(3)], 
                pointshape = 19, pointsize = 1,
                palette = c("#35B779FF","#FDE725FF"),
                # Variables
                col.var = "black",title="",  arrowsize = 0.6,alpha.var=0.7)+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Selfing")

```

#LIFE FORM

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.width=9, fig.height=9, fig.align='center'}
#LOAD LIBRARIES
library(readxl) #read excel file (trait data)
library(dplyr) #data manipulation
library(missMDA) #For missing values
library(FactoMineR) #Produce pca biplot with individuals and variables
library(factoextra)
library(ggpubr)

#change working directory
setwd("~/R_Projects/Reproductive traits")

#LOAD DATA
trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
#select just filled rows
trait_data_1 <- trait_data[1:1701,]
#filter data, select species with flower level info and capitulum
trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
levels(as.factor(trait_filtered$Info_level))
#select columns of interest
traits <- trait_filtered %>% select(Order_all,Family_all,Genus_all,Species_all,Breeding_system,IMPUTED_Compatibility,Autonomous_selfing_level,Autonomous_selfing_level_data_type,Autonomous_selfing_level_fruit_set,Flower_morphology,Flower_symmetry,Flowers_per_plant,Flowers_per_inflorescence,Floral_unit_width,Corolla_diameter_mean,Corolla_length_mean,STYLE_IMPUTED,OVULES_IMPUTED,life_form,lifespan,IMPUTED_plant_height_mean_m)
#Remove duplicated species
t <- traits[!duplicated(traits$Species_all), ]
#check structure of the data
str(t)
#remove cases where the species is NA 
t <- t[!is.na(t$Species_all), ]

str(t)
t_trial <- t[,c(5,6,7,9:21)]
str(t_trial)
cols <- c( "Breeding_system","IMPUTED_Compatibility", "Autonomous_selfing_level","Flower_morphology","Flower_symmetry", "life_form", "lifespan")

t_trial[cols] <- lapply(t_trial[cols], factor)  ## as.factor() could also be used

colnames(t_trial) <- c("Breeding system","Compatibility system","Selfing_level", "Quantitative selfing","Flower morphology","Flower symmetry",  "Flower/plant", "Flower/inflorescence", "Inflorescence width", "Flower width",  "Flower length",  "Style length", "Ovule number", "Life form","Life span", "Plant height")

str(t_trial$`Life form`)
t_trial$Selfing_level<- as.factor(t_trial$Selfing_level)
res.impute <- imputeFAMD(t_trial, ncp=3,threshold = 1e-06)

res.impute$completeObs$Selfing_level <- factor(res.impute$completeObs$Selfing_level, levels = c("high", "medium", "low", "none"))

#from http://www.zhuoyao.net/2019/11/08/principal-component-methods-in-r-practical-guide/
fviz_pca_biplot(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="var",
              geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(14)], 
                pointshape = 19, pointsize = 1,
                palette = c("#FDE725FF","#31688EFF","#440154FF", "#35B779FF"),
                # Variables
                col.var = "black",title="",  arrowsize = 0.6,alpha.var=0.7)+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Life form")

```

# COMPATIBILITY

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.width=9, fig.height=9, fig.align='center'}
#LOAD LIBRARIES
library(readxl) #read excel file (trait data)
library(dplyr) #data manipulation
library(missMDA) #For missing values
library(FactoMineR) #Produce pca biplot with individuals and variables
library(factoextra)
library(ggpubr)

#change working directory
setwd("~/R_Projects/Reproductive traits")

#LOAD DATA
trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
#select just filled rows
trait_data_1 <- trait_data[1:1701,]
#filter data, select species with flower level info and capitulum
trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
levels(as.factor(trait_filtered$Info_level))
#select columns of interest
traits <- trait_filtered %>% select(Order_all,Family_all,Genus_all,Species_all,Breeding_system,IMPUTED_Compatibility,Autonomous_selfing_level,Autonomous_selfing_level_data_type,Autonomous_selfing_level_fruit_set,Flower_morphology,Flower_symmetry,Flowers_per_plant,Flowers_per_inflorescence,Floral_unit_width,Corolla_diameter_mean,Corolla_length_mean,STYLE_IMPUTED,OVULES_IMPUTED,life_form,lifespan,IMPUTED_plant_height_mean_m)
#Remove duplicated species
t <- traits[!duplicated(traits$Species_all), ]
#check structure of the data
str(t)
#remove cases where the species is NA 
t <- t[!is.na(t$Species_all), ]

str(t)
t_trial <- t[,c(5,6,7,9:21)]
str(t_trial)
cols <- c( "Breeding_system","IMPUTED_Compatibility", "Autonomous_selfing_level","Flower_morphology","Flower_symmetry", "life_form", "lifespan")

t_trial[cols] <- lapply(t_trial[cols], factor)  ## as.factor() could also be used

colnames(t_trial) <- c("Breeding system","Compatibility system","Selfing_level", "Quantitative selfing","Flower morphology","Flower symmetry",  "Flower/plant", "Flower/inflorescence", "Inflorescence width", "Flower width",  "Flower length",  "Style length", "Ovule number", "Life form","Life span", "Plant height")

res.impute <- imputeFAMD(t_trial, ncp=3,threshold = 1e-06) 
levels( res.impute$completeObs$IMPUTED_Compatibility)

  res.impute$completeObs$`Compatibility system` <- as.character(res.impute$completeObs$`Compatibility system`)
 res.impute$completeObs$`Compatibility system` <-  gsub("Compatibility system_", "", res.impute$completeObs$`Compatibility system`)

res.impute$completeObs$`Compatibility system` <- factor(res.impute$completeObs$`Compatibility system`, levels = c("self_compatible", "partially_self_compatible","self_incompatible", "monoecious", "dioecious"))

 #from http://www.zhuoyao.net/2019/11/08/principal-component-methods-in-r-practical-guide/
fviz_pca_biplot(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="var",
              geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(2)], 
                pointshape = 19, pointsize = 1,
                palette = c("#FDE725FF","#31688EFF","#440154FF", "#35B779FF","#21908CFF"),
                # Variables
                col.var = "black",title="",  arrowsize = 0.6,alpha.var=0.7)+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Compatibility")

```

#Life span

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.width=9, fig.height=9, fig.align='center'}
#LOAD LIBRARIES
library(readxl) #read excel file (trait data)
library(dplyr) #data manipulation
library(missMDA) #For missing values
library(FactoMineR) #Produce pca biplot with individuals and variables
library(factoextra)
library(ggpubr)

#change working directory
setwd("~/R_Projects/Reproductive traits")

#LOAD DATA
trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
#select just filled rows
trait_data_1 <- trait_data[1:1701,]
#filter data, select species with flower level info and capitulum
trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
levels(as.factor(trait_filtered$Info_level))
#select columns of interest
traits <- trait_filtered %>% select(Order_all,Family_all,Genus_all,Species_all,Breeding_system,IMPUTED_Compatibility,Autonomous_selfing_level,Autonomous_selfing_level_data_type,Autonomous_selfing_level_fruit_set,Flower_morphology,Flower_symmetry,Flowers_per_plant,Flowers_per_inflorescence,Floral_unit_width,Corolla_diameter_mean,Corolla_length_mean,STYLE_IMPUTED,OVULES_IMPUTED,life_form,lifespan,IMPUTED_plant_height_mean_m)
#Remove duplicated species
t <- traits[!duplicated(traits$Species_all), ]
#check structure of the data
str(t)
#remove cases where the species is NA 
t <- t[!is.na(t$Species_all), ]

str(t)
t_trial <- t[,c(5,6,7,9:21)]
str(t_trial)
cols <- c( "Breeding_system","IMPUTED_Compatibility", "Autonomous_selfing_level","Flower_morphology","Flower_symmetry", "life_form", "lifespan")

t_trial[cols] <- lapply(t_trial[cols], factor)  ## as.factor() could also be used

colnames(t_trial) <- c("Breeding system","Compatibility system","Selfing_level", "Quantitative selfing","Flower morphology","Flower symmetry",  "Flower/plant", "Flower/inflorescence", "Inflorescence width", "Flower width",  "Flower length",  "Style length", "Ovule number", "Life form","Life span", "Plant height")

res.impute <- imputeFAMD(t_trial, ncp=3,threshold = 1e-06)

res.impute$completeObs$`Life span` <- as.character(res.impute$completeObs$`Life span`)
res.impute$completeObs$`Life span`[res.impute$completeObs$`Life span`=="annual"] <- "short_lived"
res.impute$completeObs$`Life span`[res.impute$completeObs$`Life span`=="biennial"] <- "short_lived"
res.impute$completeObs$`Life span` <- as.factor(res.impute$completeObs$`Life span`)

 #from http://www.zhuoyao.net/2019/11/08/principal-component-methods-in-r-practical-guide/
fviz_pca_biplot(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="var",
              geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(15)], 
                pointshape = 19, pointsize = 1,
                palette = c("#35B779FF","#FDE725FF"),
                # Variables
                col.var = "black",title="",  arrowsize = 0.6,alpha.var=0.7)+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Life span")

```

#Symmetry

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.width=9, fig.height=9, fig.align='center'}
#LOAD LIBRARIES
library(readxl) #read excel file (trait data)
library(dplyr) #data manipulation
library(missMDA) #For missing values
library(FactoMineR) #Produce pca biplot with individuals and variables
library(factoextra)
library(ggpubr)

#change working directory
setwd("~/R_Projects/Reproductive traits")

#LOAD DATA
trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
#select just filled rows
trait_data_1 <- trait_data[1:1701,]
#filter data, select species with flower level info and capitulum
trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
levels(as.factor(trait_filtered$Info_level))
#select columns of interest
traits <- trait_filtered %>% select(Order_all,Family_all,Genus_all,Species_all,Breeding_system,IMPUTED_Compatibility,Autonomous_selfing_level,Autonomous_selfing_level_data_type,Autonomous_selfing_level_fruit_set,Flower_morphology,Flower_symmetry,Flowers_per_plant,Flowers_per_inflorescence,Floral_unit_width,Corolla_diameter_mean,Corolla_length_mean,STYLE_IMPUTED,OVULES_IMPUTED,life_form,lifespan,IMPUTED_plant_height_mean_m)
#Remove duplicated species
t <- traits[!duplicated(traits$Species_all), ]
#check structure of the data
str(t)
#remove cases where the species is NA 
t <- t[!is.na(t$Species_all), ]

str(t)
t_trial <- t[,c(5,6,7,9:21)]
str(t_trial)
cols <- c( "Breeding_system","IMPUTED_Compatibility", "Autonomous_selfing_level","Flower_morphology","Flower_symmetry", "life_form", "lifespan")

t_trial[cols] <- lapply(t_trial[cols], factor)  ## as.factor() could also be used

colnames(t_trial) <- c("Breeding system","Compatibility system","Selfing_level", "Quantitative selfing","Flower morphology","Flower symmetry",  "Flower/plant", "Flower/inflorescence", "Inflorescence width", "Flower width",  "Flower length",  "Style length", "Ovule number", "Life form","Life span", "Plant height")

res.impute <- imputeFAMD(t_trial, ncp=3,threshold = 1e-06)

 #from http://www.zhuoyao.net/2019/11/08/principal-component-methods-in-r-practical-guide/
fviz_pca_biplot(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="var",
              geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(6)], 
                pointshape = 19, pointsize = 1,
                palette = c("#35B779FF","#FDE725FF"),
                # Variables
                col.var = "black",title="",  arrowsize = 0.6,alpha.var=0.7)+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Symmetry")

```

#Flower morphology

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.width=9, fig.height=9, fig.align='center'}
#LOAD LIBRARIES
library(readxl) #read excel file (trait data)
library(dplyr) #data manipulation
library(missMDA) #For missing values
library(FactoMineR) #Produce pca biplot with individuals and variables
library(factoextra)
library(ggpubr)

#change working directory
setwd("~/R_Projects/Reproductive traits")

#LOAD DATA
trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
#select just filled rows
trait_data_1 <- trait_data[1:1701,]
#filter data, select species with flower level info and capitulum
trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
levels(as.factor(trait_filtered$Info_level))
#select columns of interest
traits <- trait_filtered %>% select(Order_all,Family_all,Genus_all,Species_all,Breeding_system,IMPUTED_Compatibility,Autonomous_selfing_level,Autonomous_selfing_level_data_type,Autonomous_selfing_level_fruit_set,Flower_morphology,Flower_symmetry,Flowers_per_plant,Flowers_per_inflorescence,Floral_unit_width,Corolla_diameter_mean,Corolla_length_mean,STYLE_IMPUTED,OVULES_IMPUTED,life_form,lifespan,IMPUTED_plant_height_mean_m)
#Remove duplicated species
t <- traits[!duplicated(traits$Species_all), ]
#check structure of the data
str(t)
#remove cases where the species is NA 
t <- t[!is.na(t$Species_all), ]

str(t)
t_trial <- t[,c(5,6,7,9:21)]
str(t_trial)
cols <- c( "Breeding_system","IMPUTED_Compatibility", "Autonomous_selfing_level","Flower_morphology","Flower_symmetry", "life_form", "lifespan")

t_trial[cols] <- lapply(t_trial[cols], factor)  ## as.factor() could also be used

colnames(t_trial) <- c("Breeding system","Compatibility system","Selfing_level", "Quantitative selfing","Flower morphology","Flower symmetry",  "Flower/plant", "Flower/inflorescence", "Inflorescence width", "Flower width",  "Flower length",  "Style length", "Ovule number", "Life form","Life span", "Plant height")

res.impute <- imputeFAMD(t_trial, ncp=3,threshold = 1e-06)

res.impute$completeObs$`Flower morphology` <- as.character(res.impute$completeObs$`Flower morphology`)
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="bowl"] <- "open"
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="dish"] <- "open"
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="exposed"] <- "open"
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="spadix"] <- "spike"

res.impute$completeObs$`Flower morphology` <- as.factor(res.impute$completeObs$`Flower morphology`)

 #from http://www.zhuoyao.net/2019/11/08/principal-component-methods-in-r-practical-guide/
fviz_pca_biplot(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="var",
              geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(5)], 
                pointshape = 19, pointsize = 1,
                palette = c("#440154FF", "#46337EFF", "#365C8DFF", "#277F8EFF", "#1FA187FF", "#4AC16DFF", "#9FDA3AFF", "#FDE725FF"),
                # Variables
                col.var = "black",title="",  arrowsize = 0.6,alpha.var=0.7)+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Flower shape")

```

#Breeding system

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.width=9, fig.height=9, fig.align='center'}
#LOAD LIBRARIES
library(readxl) #read excel file (trait data)
library(dplyr) #data manipulation
library(missMDA) #For missing values
library(FactoMineR) #Produce pca biplot with individuals and variables
library(factoextra)
library(ggpubr)

#change working directory
setwd("~/R_Projects/Reproductive traits")

#LOAD DATA
trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
#select just filled rows
trait_data_1 <- trait_data[1:1701,]
#filter data, select species with flower level info and capitulum
trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
levels(as.factor(trait_filtered$Info_level))
#select columns of interest
traits <- trait_filtered %>% select(Order_all,Family_all,Genus_all,Species_all,Breeding_system,IMPUTED_Compatibility,Autonomous_selfing_level,Autonomous_selfing_level_data_type,Autonomous_selfing_level_fruit_set,Flower_morphology,Flower_symmetry,Flowers_per_plant,Flowers_per_inflorescence,Floral_unit_width,Corolla_diameter_mean,Corolla_length_mean,STYLE_IMPUTED,OVULES_IMPUTED,life_form,lifespan,IMPUTED_plant_height_mean_m)
#Remove duplicated species
t <- traits[!duplicated(traits$Species_all), ]
#check structure of the data
str(t)
#remove cases where the species is NA 
t <- t[!is.na(t$Species_all), ]

str(t)
t_trial <- t[,c(5,6,7,9:21)]
str(t_trial)
cols <- c( "Breeding_system","IMPUTED_Compatibility", "Autonomous_selfing_level","Flower_morphology","Flower_symmetry", "life_form", "lifespan")

t_trial[cols] <- lapply(t_trial[cols], factor)  ## as.factor() could also be used

colnames(t_trial) <- c("Breeding system","Compatibility system","Selfing_level", "Quantitative selfing","Flower morphology","Flower symmetry",  "Flower/plant", "Flower/inflorescence", "Inflorescence width", "Flower width",  "Flower length",  "Style length", "Ovule number", "Life form","Life span", "Plant height")

res.impute <- imputeFAMD(t_trial, ncp=3,threshold = 1e-06)

res.impute$completeObs$`Breeding system` <- as.character(res.impute$completeObs$`Breeding system`)
res.impute$completeObs$`Breeding system` <- gsub("Breeding system_","", res.impute$completeObs$`Breeding system`)
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="androdioecious"] <- "dioecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="androgynodioecious"] <- "dioecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="andromonoecious"] <- "monoecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="gynodioecious"] <- "dioecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="gynoecious"] <- "monoecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="gynomonoecious"] <- "monoecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="gynomonoecious"] <- "monoecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="monoecious_dioecious"] <- "monoecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="polygamo-dioecious"] <- "dioecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="protandrous"] <- "hermaphrodite"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="protogynous"] <- "hermaphrodite"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="subdioecious"] <- "dioecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="submonoecious"] <- "monoecious"
res.impute$completeObs$`Breeding system` <- as.factor(res.impute$completeObs$`Breeding system`)

 #from http://www.zhuoyao.net/2019/11/08/principal-component-methods-in-r-practical-guide/
fviz_pca_biplot(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="var",
              geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(1)], 
                pointshape = 19, pointsize = 1,
                palette = c("#440154FF", "#21908CFF", "#FDE725FF"),
                # Variables
                col.var = "black",title="",  arrowsize = 0.6,alpha.var=0.7)+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Breeding system")

levels(res.impute$completeObs$Breeding_system)

```

### 2020-11-12 Rmd/Quantitative_metadata.Rmd
Data

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

\begin{landscape}

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,}
setwd("~/R_Projects/Reproductive Traits")
library(kableExtra)

Author <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury",
            "Bartomeus", "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard")

Year <- c("2008", "2002", "2009", "1999", "2008", "1988", "2005", "2002", "1976", "2008", "2017", "2008", "2011", "2010", "2020", "2013", "2019", "2003")

DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
"https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", 
"https://doi.org/10.1046/j.1472-4642.2002.00148.x", "/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978",
"https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData", "https://doi.org/10.1111/j.1365-2745.2010.01732.x",
"https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510", "https://doi.org/10.1126/science.1232728", 
"https://doi.org/10.1111/1365-2745.13332", "Unpublished")

Networks_used <- c("6", "2", "2", "1", "1", "1", "1", "2", "1", "1", "8", "9", "6", "2", "4", "1", "3", "1")

Sampling_method <- c("Transects", "Plots", "Plots", "Transects", "Plots", "Plots", "Random census walks", "Plots", "10h per species", "Plots", "Scattered along transects", "Transects", "30min x 4", "Transects", "5min/spp x weekly", "Random census walks", "Transects", "Plots")

m <- data.frame(Author, Year, DOI, Networks_used, Sampling_method)
colnames(m) <- c("Author", "Year", "DOI", "N. of Networks included", "Sampling method")

kable(m, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T) %>% column_spec(3,width="9cm")
```
\end{landscape}

### 2020-11-12 Scripts/Data_preparation/Networks_preparation/Processing_arroyo_correa_2019.R

@@ -1,5 +1,5 @@
 # Processing data from arroyo-correa 2019
-# DOI: https://doi.org/10.1111/j.1442-9993.2005.01474.x
+# DOI:https://doi.org/10.1111/1365-2745.13332
 #Data: 10.5281/zenodo.3011651
 # CHINA
 # Note: Same place as robertson networks but sampled in 2009-2010

### 2020-11-13 Rmd/Ideas_and_meetings/Ideas.Rmd
data org

--- 2020-03-30 Rmd/Ideas.Rmd
@@
 However, we lack comprehensive information from both plants and pollinators that can inform from this mutualistic interaction worldwide.
-In order to tackle this, we have selected 30 networks distributed across the world and looked for key floral traits of plant-pollinator interactions for a total of 1600 species.
+[frase que no significa nada, information on what?
+to inform what?]() In order to tackle this, we have selected 30 networks distributed across the world and looked for key floral traits of plant-pollinator interactions for a total of 1600 species.
 Here we look how these floral traits shape the different plant-pollinator networks and the main fuctional groups of insect pollinating species.
@@
 We also highlight the lack of information about traits and the reproductive biology of the plant species of these networks.
-Our work shows the importance of deepen in species traits in order to understand key processes that can be seen with network metrics and highlights the importance of elemental ecology for species conservation.
+Our work shows the importance to deepen in species traits in order to understand key processes that structure network metrics and highlights the importance of basic ecology for species conservation.
+[buen abstract!]()
 
@@
 5) Selfing level
+
+[ideal añadir nectar production]()
 

### 2020-11-13 Rmd/Ideas_and_meetings/meeting_24.Rmd
data org

---
header-includes:
    - \usepackage{setspace}\doublespacing
output:
  pdf_document: default
  html_document: default
---

\setlength{\abovedisplayskip}{25pt}
\setlength{\belowdisplayskip}{25pt}
\setlength{\abovedisplayshortskip}{25pt}
\setlength{\belowdisplayshortskip}{25pt}

```{r, echo = F}
library(knitr)
knitr::opts_chunk$set(message = FALSE)

if(is_latex_output()) {
  plot_default <- knit_hooks$get("plot")
  knit_hooks$set(plot = function(x, options) { 
    x <- c(plot_default(x, options), "\\vspace{25pt}")
  })
}
```

#TRAIT CORRELOGRAM

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.width=9, fig.height=9, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
merged_all_2 <- read.csv("Data/Csv/long_all.csv")

library(qad)

#qad
floral_1<-merged_all_2[c("Visits", "z_score","Corolla_length_mean","Floral_unit_width","style_length_mm", "Autonomous_selfing_level_fruit_set","ovules_mean","plant_height_mean_m")]
model <- pairwise.qad(floral_1, permutation = FALSE)
heatmap.qad(model, select = "dependence", fontsize = 5, significance = TRUE, sign.level = 0.05)

```

#PCA ALL QUATITATIVE NO AUTONOMOUS SELFING

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.width=9, fig.height=9, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
merged_all_2 <- read.csv("Data/Csv/long_all.csv")

library("FactoMineR")
library("factoextra")
floral_1<-merged_all_2[c("z_score","Floral_unit_width","style_length_mm", "ovules_mean","plant_height_mean_m")]
floral_1[,c(1:5)] <- scale(mutate_all(floral_1[,c(1:5)], function(x) as.numeric(as.character(x))))
res.pca <- PCA(floral_1, graph = FALSE)
fviz_pca_biplot(res.pca, label ="var", col.ind="cos2",repel = TRUE,col.var = "cos2",ellipse.level=0.95,gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07")) +
  theme_minimal()+ylim(-5,10)+xlim(-5,15)
```

#PCA ALL QUATITATIVE WITH AUTONOMOUS SELFING (We loss many points)

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.width=9, fig.height=9, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
merged_all_2 <- read.csv("Data/Csv/long_all.csv")

library("FactoMineR")
library("factoextra")
floral_1<-merged_all_2[c("Id", "z_score","Autonomous_selfing_level_fruit_set","Floral_unit_width","style_length_mm", "ovules_mean","plant_height_mean_m")]
res.pca <- PCA(na.omit(mutate_all(floral_1[-1], function(x) as.numeric(as.character(x)))), graph = FALSE)
fviz_pca_biplot(res.pca, label ="var", col.ind="cos2",repel = TRUE,col.var = "cos2",ellipse.level=0.95,gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07")) +
  theme_minimal()+ylim(-5,10)+xlim(-5,15)
```

### 2020-11-13 Rmd/Principal_component_analysis/PCA_individuals.Rmd
data org

---
header-includes:
    - \usepackage{setspace}\doublespacing
output:
  pdf_document: default
  html_document: default
---

\setlength{\abovedisplayskip}{25pt}
\setlength{\belowdisplayskip}{25pt}
\setlength{\abovedisplayshortskip}{25pt}
\setlength{\belowdisplayshortskip}{25pt}

```{r, echo = F}
library(knitr)
knitr::opts_chunk$set(message = FALSE)

if(is_latex_output()) {
  plot_default <- knit_hooks$get("plot")
  knit_hooks$set(plot = function(x, options) { 
    x <- c(plot_default(x, options), "\\vspace{25pt}")
  })
}
```

#PCA by individuals and coloured by qualitative variables

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.width=9, fig.height=9, fig.align='center'}
#LOAD LIBRARIES
library(readxl) #read excel file (trait data)
library(dplyr) #data manipulation
library(missMDA) #For missing values
library(FactoMineR) #Produce pca biplot with individuals and variables
library(factoextra)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)

#change working directory
setwd("~/R_Projects/Reproductive traits")

#LOAD DATA
trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
#select just filled rows
trait_data_1 <- trait_data[1:1701,]
#filter data, select species with flower level info and capitulum
trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
levels(as.factor(trait_filtered$Info_level))
#select columns of interest
traits <- trait_filtered %>% select(Order_all,Family_all,Genus_all,Species_all,Breeding_system,IMPUTED_Compatibility,Autonomous_selfing_level,Autonomous_selfing_level_data_type,Autonomous_selfing_level_fruit_set,Flower_morphology,Flower_symmetry,Flowers_per_plant,Flowers_per_inflorescence,Floral_unit_width,Corolla_diameter_mean,Corolla_length_mean,STYLE_IMPUTED,OVULES_IMPUTED,life_form,lifespan,IMPUTED_plant_height_mean_m)
#Remove duplicated species
t <- traits[!duplicated(traits$Species_all), ]
#check structure of the data
str(t)
#remove cases where the species is NA 
t <- t[!is.na(t$Species_all), ]

str(t)
t_trial <- t[,c(5,6,7,9:21)]
str(t_trial)
cols <- c( "Breeding_system","IMPUTED_Compatibility", "Autonomous_selfing_level","Flower_morphology","Flower_symmetry", "life_form", "lifespan")

t_trial[cols] <- lapply(t_trial[cols], factor)  ## as.factor() could also be used

colnames(t_trial) <- c("Breeding system","Compatibility system","Selfing_level", "Quantitative selfing","Flower morphology","Flower symmetry",  "Flower/plant", "Flower/inflorescence", "Inflorescence width", "Flower width",  "Flower length",  "Style length", "Ovule number", "Life form","Life span", "Plant height")

str(t_trial$`Life form`)
t_trial$Selfing_level<- as.factor(t_trial$Selfing_level)
res.impute <- imputeFAMD(t_trial, ncp=3,threshold = 1e-06)

  res.impute$completeObs$`Life form` <- as.character(res.impute$completeObs$`Life form`)

  res.impute$completeObs$`Life form`[res.impute$completeObs$`Life form`=="herb"] <- "Herb"
  res.impute$completeObs$`Life form`[res.impute$completeObs$`Life form`=="shrub"] <- "Shrub"
  res.impute$completeObs$`Life form`[res.impute$completeObs$`Life form`=="tree"] <- "Tree"
  res.impute$completeObs$`Life form`[res.impute$completeObs$`Life form`=="vine"] <- "Vine"

  res.impute$completeObs$`Life form` <- as.factor(res.impute$completeObs$`Life form`)

#from http://www.zhuoyao.net/2019/11/08/principal-component-methods-in-r-practical-guide/
a <- fviz_pca_ind(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="none",
              geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(14)], 
                pointshape = 19, pointsize = 1,axes.linetype=NA,title="",
                palette = c("#FDE725FF","#31688EFF","#440154FF", "#35B779FF"))+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Life form")+theme(strip.text.x = element_blank(),strip.background = element_rect(colour="white", fill="white"),legend.position=c(0.052,0.81),legend.title=element_text(size=5),legend.key.size = unit(0.5,"line"),legend.text = element_text(size = 4))+
  guides(color = guide_legend(override.aes = list(size=1.5)))+ylab("PC 2")+xlab("")

  res.impute$completeObs$`Compatibility system` <- as.character(res.impute$completeObs$`Compatibility system`)
 res.impute$completeObs$`Compatibility system` <-  gsub("Compatibility system_", "", res.impute$completeObs$`Compatibility system`)

res.impute$completeObs$`Compatibility system`[res.impute$completeObs$`Compatibility system`=="self_compatible"] <- "Self compatible"
res.impute$completeObs$`Compatibility system`[res.impute$completeObs$`Compatibility system`=="partially_self_compatible"] <- "Partially self compatible"
 res.impute$completeObs$`Compatibility system`[res.impute$completeObs$`Compatibility system`=="self_incompatible"] <- "Self incompatible"
 res.impute$completeObs$`Compatibility system`[res.impute$completeObs$`Compatibility system`=="monoecious"] <- "Monoecious"
  res.impute$completeObs$`Compatibility system`[res.impute$completeObs$`Compatibility system`=="dioecious"] <- "Dioecious"

res.impute$completeObs$`Compatibility system` <- factor(res.impute$completeObs$`Compatibility system`, levels = c("Self compatible", "Partially self compatible","Self incompatible", "Monoecious", "Dioecious"))

 #from http://www.zhuoyao.net/2019/11/08/principal-component-methods-in-r-practical-guide/
b <- fviz_pca_ind(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="var",
              geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(2)], 
                pointshape = 19, pointsize = 1,axes.linetype=NA,title="",
                palette = c("#FDE725FF","#31688EFF","#440154FF", "#35B779FF","#21908CFF"))+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Compatibility")+theme(strip.text.x = element_blank(),strip.background = element_rect(colour="white", fill="white"),legend.position=c(0.114,0.794),legend.title=element_text(size=5),legend.key.size = unit(0.5,"line"),legend.text = element_text(size = 4))+
  guides(color = guide_legend(override.aes = list(size=1.5)))+ylab("")+xlab("")

res.impute$completeObs$`Life span` <- as.character(res.impute$completeObs$`Life span`)
res.impute$completeObs$`Life span`[res.impute$completeObs$`Life span`=="annual"] <- "short_lived"
res.impute$completeObs$`Life span`[res.impute$completeObs$`Life span`=="biennial"] <- "short_lived"
res.impute$completeObs$`Life span`[res.impute$completeObs$`Life span`=="short_lived"] <- "Short lived"
res.impute$completeObs$`Life span`[res.impute$completeObs$`Life span`=="perennial"] <- "Perennial"

res.impute$completeObs$`Life span` <- as.factor(res.impute$completeObs$`Life span`)

 #from http://www.zhuoyao.net/2019/11/08/principal-component-methods-in-r-practical-guide/
c <- fviz_pca_ind(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="var",
              geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(15)], 
                pointshape = 19, pointsize = 1,axes.linetype=NA,title="",
                palette = c("#35B779FF","#FDE725FF"))+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Life span")+
theme(strip.text.x = element_blank(),strip.background = element_rect(colour="white", fill="white"),legend.position=c(0.07,0.855),legend.title=element_text(size=5),legend.key.size = unit(0.5,"line"),legend.text = element_text(size = 4))+
  guides(color = guide_legend(override.aes = list(size=1.5)))+ylab("PC 2")+xlab("")

res.impute$completeObs$`Flower symmetry` <- as.character(res.impute$completeObs$`Flower symmetry`)
res.impute$completeObs$`Flower symmetry`[res.impute$completeObs$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
res.impute$completeObs$`Flower symmetry`[res.impute$completeObs$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"
res.impute$completeObs$`Flower symmetry` <- as.factor(res.impute$completeObs$`Flower symmetry`)

 #from http://www.zhuoyao.net/2019/11/08/principal-component-methods-in-r-practical-guide/
d <- fviz_pca_ind(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="var",
              geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(6)], 
                pointshape = 19, pointsize = 1,axes.linetype=NA,title="",
                palette = c("#35B779FF","#FDE725FF"))+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Symmetry")+
theme(strip.text.x = element_blank(),strip.background = element_rect(colour="white", fill="white"),legend.position=c(0.08,0.86),legend.title=element_text(size=5),legend.key.size = unit(0.5,"line"),legend.text = element_text(size = 4))+
  guides(color = guide_legend(override.aes = list(size=1.5)))+ylab("")+xlab("")

res.impute$completeObs$`Flower morphology` <- as.character(res.impute$completeObs$`Flower morphology`)
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="bowl"] <- "open"
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="dish"] <- "open"
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="exposed"] <- "open"
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="spadix"] <- "spike"

res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="open"] <- "Open"
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="brush"] <- "Brush"
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="campanulate"] <- "Campanulate"
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="capitulum"] <- "Capitulum"
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="funnelform"] <- "Funnelform"
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="papilionaceous"] <- "Papilionaceous"
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="spike"] <- "Spike"
res.impute$completeObs$`Flower morphology`[res.impute$completeObs$`Flower morphology`=="tube"] <- "Tube"

res.impute$completeObs$`Flower morphology` <- as.factor(res.impute$completeObs$`Flower morphology`)

 #from http://www.zhuoyao.net/2019/11/08/principal-component-methods-in-r-practical-guide/
e <- fviz_pca_ind(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="none",
              geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(5)], 
                pointshape = 19, pointsize = 1,axes.linetype=NA,title="",
                palette = c("#440154FF", "#46337EFF", "#365C8DFF", "#277F8EFF", "#1FA187FF", "#4AC16DFF", "#9FDA3AFF", "#FDE725FF"))+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Flower shape")+
theme(strip.text.x = element_blank(),strip.background = element_rect(colour="white", fill="white"),legend.position=c(0.08,0.726),legend.title=element_text(size=5),legend.key.size = unit(0.5,"line"),legend.text = element_text(size = 4))+
  guides(color = guide_legend(override.aes = list(size=1.5)))+ylab("PC 2")+xlab("PC 1")

res.impute$completeObs$`Breeding system` <- as.character(res.impute$completeObs$`Breeding system`)
res.impute$completeObs$`Breeding system` <- gsub("Breeding system_","", res.impute$completeObs$`Breeding system`)
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="androdioecious"] <- "dioecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="androgynodioecious"] <- "dioecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="andromonoecious"] <- "monoecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="gynodioecious"] <- "dioecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="gynoecious"] <- "monoecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="gynomonoecious"] <- "monoecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="gynomonoecious"] <- "monoecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="monoecious_dioecious"] <- "monoecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="polygamo-dioecious"] <- "dioecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="protandrous"] <- "hermaphrodite"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="protogynous"] <- "hermaphrodite"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="subdioecious"] <- "dioecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="submonoecious"] <- "monoecious"
#Change levels to capital letters
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="monoecious"] <- "Monoecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="dioecious"] <- "Dioecious"
res.impute$completeObs$`Breeding system`[res.impute$completeObs$`Breeding system`=="hermaphrodite"] <- "Hermaphrodite"

res.impute$completeObs$`Breeding system` <- as.factor(res.impute$completeObs$`Breeding system`)

 #from http://www.zhuoyao.net/2019/11/08/principal-component-methods-in-r-practical-guide/
f <- fviz_pca_ind(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="none",
              geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(1)], 
                pointshape = 19, pointsize = 1,axes.linetype=NA,title="",
                palette = c("#440154FF", "#21908CFF", "#FDE725FF"))+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Breeding system")+
theme(strip.text.x = element_blank(),strip.background = element_rect(colour="white", fill="white"),legend.position=c(0.085,0.84),legend.title=element_text(size=5),legend.key.size = unit(0.5,"line"),legend.text = element_text(size = 4))+
  guides(color = guide_legend(override.aes = list(size=1.5)))+ylab("PC 2")+xlab("PC 1")
 #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
grid.newpage()

 grid.draw(arrangeGrob(cbind(ggplotGrob(a),ggplotGrob(b)),cbind(ggplotGrob(c),ggplotGrob(d)),cbind(ggplotGrob(e),ggplotGrob(f)),nrow=3))
#mylegend
 dev.off()

```

### 2020-11-13 Rmd/Trait_by_World_map/World_Map_Compatibility_Systems.Rmd
data org

--- 2020-03-19 Rmd/World_Map_Breeding_Systems.Rmd
@@
   scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:9)]),
- labels = c("Hermaphroditism", "Dioecy", "Monoecy"),values = c("Hermaphroditism" = "#4DAF4A",
- "Monoecy" = "#984EA3","Dioecy" = "orange")) +labs(title = "Breeding system",subtitle = "",
-  caption = "",fill = NULL) + theme(legend.position = c(0.15, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),
+ labels = c("Partially self compatible", "Self compatible", "Self incompatible"),values = c("partially_self_compatible" = "#4DAF4A","self_compatible" = "#984EA3","self_incompatible" = "orange")) +labs(title = "Compatibility system",subtitle = "", caption = "",fill = NULL) + theme(legend.position = c(0.18, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),
   axis.ticks = element_blank(),legend.key.size = unit(0.16, "cm")) +

### 2020-11-27 Scripts/6_Plot/6_Model_output_plot.Rmd
Parallel analysis excluding apis mellifera, same output.
Thinking if checking sociality levels for each genus of bees or considering it in a broad sense or analyse by family

--- 2020-04-15 Rmd/Draft.Rmd
@@
 ---
-title: "Chapter 2 Draft"
+title: "Visitation_stacked_barplot"
 output:
@@
   html_document: default
-fontsize: 12pt
-header-includes:
-    - \usepackage{setspace}\doublespacing
-bibliography: [references.bib]
 ---
-Here I'm going to try to understand our data a bit better and state our hypothesis.
 
-First I start with an abstract that could be our guide for hypothesis testing and analyses.
-
-#Abstract (draft)
-
-Plant pollinator interactions are a keystone process for ecosystem functioning.
-However, we lack comprehensive information from both plants and pollinators that can inform from this mutualistic interaction worldwide.
-In order to tackle this, we have selected 30 networks distributed across the world and looked for key floral traits of plant-pollinator interactions for a total of 1600 species.
-Here we look how these floral traits shape the different plant-pollinator networks and the main fuctional groups of insect pollinating species.
-Giving the different nature of the data collated we do not compare across networks and we focus on the main general patterns/results within network.
-We have conducted our analysis at 3 levels, 1) unique networks, 2) metawebs and by 3) grouping both.
-We find that specific traits are associated with different guilds of floral visitors within these networks.
-We also highlight the lack of information about traits and the reproductive biology of the plant species of these networks.
-Our work shows the importance of deepen in species traits in order to understand key processes that can be seen with network metrics and highlights the importance of elemental ecology for species conservation.
-
-#INTRODUCTION
-
-*Paragraph 1*
-
-*Paragraph 2*
-
-There are multiple recent studies that have considered the link between network structure and functional traits.
-@novella2019 included floral display on the interaction strength of a plant-pollinator network, finding important changes in species and network metrics.
-Moreover, @lazaro2019 shows how different traits, including flower abundance, shape, size, flowering length and nectar can influence the position in the network with important implications for community assembly.
-A more similar look to this piece is the work conducted by @carvalheiro2014 that focus on 750 networks and looks how nectar production can modulate the effects between species and found that its effect is dependent on pollinator guilds.
-The continuum from visitation to species fitness is essential to understand the relative importance of each species on the network.
-Therefore, there is a need to to include species breeding systems, compatibility level and seed/fruit set in order to fully understand the dependance on pollinators and position in the network.
-However few works have attempted this due to high demanding nature of these types of experiment [@lazaro2019] [@gomez2012fitness]
-
-  LAZARO/GOMEZ/TUR
-
-Stang papers correlations trait matching and flower size
-
-TUR --> INSECT POLLINATOR DEPENDANCE
-
-ARCEO GOMEZ NEW PAPER
-
-*Paragraph 3*
-
-*Paragraph 4*
-
-*Hypothesis*
-[overall, guay, pero le falta story telling]()
-
-**Research questions**
-
-1) How the different pollinator taxonomic groups interact with the distinct plant floral traits. Are these floral traits characteristic of a pollinator syndrome?
-
-2) Are the different selected floral traits affecting the species level metrics such as generalization/specialization or centrality? What is its ecological meaning?
-
-3) Can we predict the diversity of pollinator interactions with the phylogenetic distance of a community?
--Hypothesis- communities with a higher number o close related species will likely have trait redundancy and less diversity of interactions.
-[IB: Este ultimo punto es interesante, PERO quizas es otro paper? Mirate https://www.nature.com/articles/nature05956 Rezende tiene otros papers al respecto]()
-
-#MATERIALS AND METHODS
-
-This research has collated networks from 25 different studies from very different geographical regions across the world.
-All of these networks are from natural habitats or systems with a minor human intervention.
-The nature of these networks is both weighted (N) and unweighted (N) with the former just with visitation data which could serve as proxy of pollination with pollinator efficiency as limitation (REF).
-These studies have been counducted with different sampling methodologies and sampling effort and our aim is not to compare them but to get a general picture of how the selected functional traits shape these networks and the different taxonomic groups.
-The networks of these studies that were done in consecutive years or in areas close to each other with a similar species compositon were combined in metawebs.
-This makes a total of 30 different unique networks/metawebs when all are considered by their maximum level of organization (metaweb if possible).
-All the species names were searched with the help of the package taxsize [@chamberlain2013taxize] from two different data sources ncbi and itis, for plants and floral visitors respectively.
-We filled the not found searches manually with the help of <http://www.theplantlist.org/> and <http://www.mobot.org/> for plants and  <http://www.catalogueoflife.org/> for floral visitors.
-
-For all of these studies we have done an extensive literature and online search of different floral traits.
-These traits are breeding system, compatibility system, selfing rate (with fruit and seed set), flower shape, flower symmetry, flower size (width and length), style length and ovule number.
-Moreover, we also recorded plant height, life span and life form for these species.
-
-\newpage
-
-\vspace{4cm}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8, fig.cap="Percentage of species of each order per network/metaweb (qualitative data)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8}
 library(dplyr)
@@
 
-# IB: No me cuadra la cantidad de dipteros (y pocos hymenopteros) en mis redes, recheck colores. Ojo, quizas esta bien, pero me sorprende. 
-# IB; Para visitas hay oalgo mal seguro, no hay abejas en 2015 ¿?
-
 #Bumblebee image credit to Melissa Broussard
 ```
-
-\newpage
-
-\vspace{4cm}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8, fig.cap="Percentage of visits of each order per network/metaweb (quantitative data)."}
-library(dplyr)
-library(tidyr)
-library(plyr)
-library(ggplot2)
-library(reshape2)
-library(scales)
-library(devtools)
-library(png)
-library(grid)
-library(gridExtra)
-library(jpeg)
-dev_mode(on=T)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-img <- readPNG(system.file("img", "Rlogo.png", package="png"))
-g <- rasterGrob(img, interpolate=TRUE)
-
-net_long_1 <- readRDS("Data/RData/Spp_visitation_per_order_long.RData")
-
-la <- c("Bartomeus unp. 2015", "Chacoff 2011","Bartomeus 2008 1", "Bartomeus 2008 2","Small 1976",
-       "Inouye 1990", "Souza 2018", "Inouye 1988", "Dupont 2009", "Olesen 2002 1", "Fang 2012", "Olesen 2002 2", "Dicks 2002",
-       "Elberling 1999","Kato 2000", "Kaiser-Bunbunry 2009", "Traveset 2013", "Kaiser-Bunbury 2014","Lundgren 2005")
-legend_title <- "Taxonomic groups"
-
- get_png <- function(filename) {
-  grid::rasterGrob(png::readPNG(filename), interpolate = TRUE)
-}
-
-l <- get_png("Images/lepidoptera_2.png")
-bumb <- get_png("Images/bumblebee.png")
-dip <- get_png("Images/diptera.png")
-beet <- get_png("Images/beetle.png")
-hem<- get_png("Images/hemiptera.png")
-
-t <- grid::roundrectGrob(x=0.5, y=0.5, width=1, height=1)
-
-p<- ggplot(net_long_1) +
-  aes(x = reorder(Id,-order), 
-      y = measurement, 
-      fill =factor(orders, levels=c("Hemiptera","Coleoptera","Lepidoptera","Diptera", "Hymenoptera"))) +
-  geom_bar(position = "fill", stat = "identity", alpha=0.6) +coord_flip() +scale_x_discrete(labels= la) + 
-  scale_fill_manual(legend_title,values=c("indianred", "gray49", "seagreen", "darkgoldenrod2", "#386cb0")) + theme_classic()+xlab("Networks")+ylab("Percentage of visits") +scale_y_continuous(labels = scales::percent) + theme(legend.background = element_rect(fill=alpha('blue', 0.0)))+
-  annotation_custom(l, xmin = 9.365, xmax = 10.0, ymin = 1.03, ymax =1.09) + annotation_custom(bumb, xmin = 7.1, xmax = 9.3, ymin = 1.03, ymax =1.09)+ annotation_custom(dip, xmin = 8.65, xmax = 9.25, ymin = 1.035, ymax =1.085)+
-  coord_cartesian(clip = "off") + annotation_custom(beet, xmin = 9.96, xmax = 10.76, ymin = 0.86, ymax =1.255)+ annotation_custom(hem, xmin = 10.86, xmax = 11.36, ymin = 0.883, ymax =1.233)+
-  coord_cartesian(clip = "off")+ coord_flip()
-
-gg_table <- ggplot_gtable(ggplot_build(p))
-gg_table$layout$clip[gg_table$layout$name=="panel"] <- "off"
-grid.draw(gg_table)
-
-#Bumblebee image credit to Melissa Broussard
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center', fig.cap="Pie charts on the coordinates of each study site  with a classification of three main breeding systems (hermaphroditism, dioecy and monoecy)."}
-library(ggplot2)
-library(scatterpie)
-library(sf)
-world <- map_data('world')
-setwd("~/R_Projects/Reproductive Traits")
-data_merged_sub_ord <- readRDS("Data/RData/Breeding_systems_plot.RData")
-
-p <- ggplot(world, aes(long, lat)) +
-  geom_map(map=world, aes(map_id=region), fill="white", color="black") +
-  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
-p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
- data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:9)]),alpha=.8)+ 
-  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:9)]),
- labels = c("Hermaphroditism", "Dioecy", "Monoecy"),values = c("Hermaphroditism" = "#4DAF4A",
- "Monoecy" = "#984EA3","Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
-  caption = "",fill = NULL) + theme(legend.position = c(0.215, 0.009),legend.justification = c(1, 0),
-  axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +
-  geom_segment(data = data_merged_sub_ord,aes(x = 168, y = -34, xend = 172, yend = -43),color = "black", size = 0.3, alpha = 0.2) + #NZ
-  geom_segment(data = data_merged_sub_ord, aes(x = 179, y = -46, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.2) + #NZ
-  geom_segment(data = data_merged_sub_ord, aes(x = 164, y = -48, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.2) + #NZ
-  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = 6, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.2) +  #GALAPAGOS
-  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = -7, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.2) + #GALAPAGOS
-  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -12), color = "black", size = 0.3, alpha = 0.2) + #MAURITIUS
-  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -28), color = "black", size = 0.3, alpha = 0.2) + #MAURITIUS
-  geom_segment(data = data_merged_sub_ord, aes(x = -51, y = 10, xend = -61, yend = 5.5), color = "black", size = 0.3, alpha = 0.2) + #VENEZUELA
-  geom_segment(data = data_merged_sub_ord, aes(x = -51, y =25 , xend = -67, yend = 8.9), color = "black", size = 0.3, alpha = 0.2) + #VENEZUELA
-  geom_segment(data = data_merged_sub_ord, aes(x = 148, y = 35, xend = 135.8, yend = 35), color = "black", size = 0.3, alpha = 0.2) + 
-  geom_segment(data = data_merged_sub_ord, aes(x = 140, y = 22, xend = 129, yend = 28), color = "black", size = 0.3, alpha = 0.2) +
-  geom_segment(data = data_merged_sub_ord, aes(x = -15.5, y = 32, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.2) + 
-  geom_segment(data = data_merged_sub_ord, aes(x = -15, y = 50, xend = 3, yend = 43), color = "black", size = 0.3, alpha = 0.2) +
-  geom_segment(data = data_merged_sub_ord, aes(x = -24, y = 40, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.2) +
-  geom_segment(data = data_merged_sub_ord, aes(x = -84, y = -32, xend = -68, yend = -32), color = "black", size = 0.3, alpha = 0.2) + 
-  geom_segment(data = data_merged_sub_ord, aes(x = -36, y = -21, xend = -58, yend = -21), color = "black", size = 0.3, alpha = 0.2) +
-  geom_segment(data = data_merged_sub_ord, aes(x = 34, y = 78, xend = 18.5, yend = 68), color = "black", size = 0.3, alpha = 0.2) + 
-  geom_segment(data = data_merged_sub_ord, aes(x = 0, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.2) +
-  geom_segment(data = data_merged_sub_ord, aes(x = 15, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.2) +
-  geom_segment(data = data_merged_sub_ord, aes(x = -8, y = 61, xend = 1.5, yend = 52), color = "black", size = 0.3, alpha = 0.2) +
-  geom_segment(data = data_merged_sub_ord, aes(x = 39, y = 60, xend = 9, yend = 56), color = "black", size = 0.3, alpha = 0.2) +
-  geom_segment(data = data_merged_sub_ord, aes(x = 126, y = -36, xend = 148, yend = -36), color = "black", size = 0.3, alpha = 0.2) + #AUS
-  geom_segment(data = data_merged_sub_ord, aes(x = 90, y = 6, xend = 100, yend = 28), color = "black", size = 0.3, alpha = 0.2) + #CHINA
-  geom_segment(data = data_merged_sub_ord, aes(x = -66, y = 39, xend = -89, yend = 39), color = "black", size = 0.3, alpha = 0.2) + #USA
-  geom_segment(data = data_merged_sub_ord, aes(x = -48, y = 52, xend = -75, yend = 45), color = "black", size = 0.3, alpha = 0.2) + #CANADA
-  geom_segment(data = data_merged_sub_ord, aes(x = -71, y = 86, xend = -71, yend = 81), color = "black", size = 0.3, alpha = 0.2) + #CANADA
-  geom_segment(data = data_merged_sub_ord, aes(x = -52, y = 86, xend = -52, yend = 71), color = "black", size = 0.3, alpha = 0.2) + #GREENLAND
-  geom_segment(data = data_merged_sub_ord, aes(x = -20, y = 86, xend = -20, yend = 74), color = "black", size = 0.3, alpha = 0.2)
-
-## Molaria compararlo con estimas a nivel mundial de que % de plantas son hermafroditas, (y igual para todos los traits).
-En otras palabras, salen estas porporciones por que reflejan las proporciones generales?
-O se desvian?)
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center', fig.cap="Pie charts on the coordinates of each study site  with the compatibility level classified in three main groups (self compatible, partially self compatible and self incompatible)."}
-library(ggplot2)
-library(scatterpie)
-library(sf)
-world <- map_data('world')
-setwd("~/R_Projects/Reproductive Traits")
-data_merged_sub_ord <- readRDS("Data/RData/Compatibility_system_plot.RData")
-
-p <- ggplot(world, aes(long, lat)) +
-  geom_map(map=world, aes(map_id=region), fill="white", color="grey", size=0.35) +
-  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
-p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
- data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:9)]),alpha=.8)+ 
-  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:9)]),
- labels = c("Partially self compatible", "Self compatible", "Self incompatible"),values = c("partially_self_compatible" = "#4DAF4A","self_compatible" = "#984EA3","self_incompatible" = "orange")) +labs(title = "Compatibility system",subtitle = "", caption = "",fill = NULL) + theme(legend.position = c(0.18, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),
-  axis.ticks = element_blank(),legend.key.size = unit(0.16, "cm")) +
-  geom_segment(data = data_merged_sub_ord,aes(x = 168, y = -34, xend = 172, yend = -43),color = "black", size = 0.3, alpha = 0.8) + #NZ
-  geom_segment(data = data_merged_sub_ord, aes(x = 179, y = -46, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
-  geom_segment(data = data_merged_sub_ord, aes(x = 164, y = -48, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
-  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = 6, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) +  #GALAPAGOS
-  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = -7, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) + #GALAPAGOS
-  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -12), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
-  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -28), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
-  geom_segment(data = data_merged_sub_ord, aes(x = -51, y = 10, xend = -61, yend = 5.5), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
-  geom_segment(data = data_merged_sub_ord, aes(x = -51, y =25 , xend = -67, yend = 8.9), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
-  geom_segment(data = data_merged_sub_ord, aes(x = 148, y = 35, xend = 135.8, yend = 35), color = "black", size = 0.3, alpha = 0.8) + 
-  geom_segment(data = data_merged_sub_ord, aes(x = 140, y = 22, xend = 129, yend = 28), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = -15.5, y = 32, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) + 
-  geom_segment(data = data_merged_sub_ord, aes(x = -15, y = 50, xend = 3, yend = 43), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = -24, y = 40, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = -84, y = -32, xend = -68, yend = -32), color = "black", size = 0.3, alpha = 0.8) + 
-  geom_segment(data = data_merged_sub_ord, aes(x = -36, y = -21, xend = -58, yend = -21), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = 34, y = 78, xend = 18.5, yend = 68), color = "black", size = 0.3, alpha = 0.8) + 
-  geom_segment(data = data_merged_sub_ord, aes(x = 0, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = 15, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = -8, y = 61, xend = 1.5, yend = 52), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = 39, y = 60, xend = 9, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = 126, y = -36, xend = 148, yend = -36), color = "black", size = 0.3, alpha = 0.8) + #AUS
-  geom_segment(data = data_merged_sub_ord, aes(x = 90, y = 6, xend = 100, yend = 28), color = "black", size = 0.3, alpha = 0.8) + #CHINA
-  geom_segment(data = data_merged_sub_ord, aes(x = -66, y = 39, xend = -89, yend = 39), color = "black", size = 0.3, alpha = 0.8) + #USA
-  geom_segment(data = data_merged_sub_ord, aes(x = -48, y = 52, xend = -75, yend = 45), color = "black", size = 0.3, alpha = 0.8) + #CANADA
-  geom_segment(data = data_merged_sub_ord, aes(x = -71, y = 86, xend = -71, yend = 81), color = "black", size = 0.3, alpha = 0.8) + #CANADA
-  geom_segment(data = data_merged_sub_ord, aes(x = -52, y = 86, xend = -52, yend = 71), color = "black", size = 0.3, alpha = 0.8) + #GREENLAND
-  geom_segment(data = data_merged_sub_ord, aes(x = -20, y = 86, xend = -20, yend = 74), color = "black", size = 0.3, alpha = 0.8)
-
-##Que flipe que al norte hay más self-compatible?! Esto debe estar decrito en la literatura, verdad? Hay una correlación entre la diversidad de abejas y el nivel de self incompatibility?  
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center', fig.cap="Pie charts on the coordinates of each study site  with the life forms for all the species divided in trees, shrubs, herbs and vines."}
-library(ggplot2)
-library(scatterpie)
-library(sf)
-world <- map_data('world')
-setwd("~/R_Projects/Reproductive Traits")
-data_merged_sub_ord <- readRDS("Data/RData/Life_Form_plot.RData")
-
-p <- ggplot(world, aes(long, lat)) +
-  geom_map(map=world, aes(map_id=region), fill="white", color="black") +
-  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
-p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
-                     data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:10)]),alpha=.8)+ 
-  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:10)]),
-                    labels = c("Herb", "Shrub", "Tree", "Vine"),values = c("herb" = "#4DAF4A",
-                                                                           "shrub" = "#984EA3","tree" = "orange", "vine" = "lightblue")) +labs(title = "Life form",subtitle = "",
-                                                                                                                                               caption = "",fill = NULL) + theme(legend.position = c(0.12, 0.009),legend.justification = c(1, 0),
-                                                                                                                                                                                 axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +
-  geom_segment(data = data_merged_sub_ord,aes(x = 168, y = -34, xend = 172, yend = -43),color = "black", size = 0.3, alpha = 0.8) + #NZ
-  geom_segment(data = data_merged_sub_ord, aes(x = 179, y = -46, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
-  geom_segment(data = data_merged_sub_ord, aes(x = 164, y = -48, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
-  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = 6, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) +  #GALAPAGOS
-  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = -7, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) + #GALAPAGOS
-  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -12), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
-  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -28), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
-  geom_segment(data = data_merged_sub_ord, aes(x = -51, y = 10, xend = -61, yend = 5.5), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
-  geom_segment(data = data_merged_sub_ord, aes(x = -51, y =25 , xend = -67, yend = 8.9), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
-  geom_segment(data = data_merged_sub_ord, aes(x = 148, y = 35, xend = 135.8, yend = 35), color = "black", size = 0.3, alpha = 0.8) + 
-  geom_segment(data = data_merged_sub_ord, aes(x = 140, y = 22, xend = 129, yend = 28), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = -15.5, y = 32, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) + 
-  geom_segment(data = data_merged_sub_ord, aes(x = -15, y = 50, xend = 3, yend = 43), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = -24, y = 40, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = -84, y = -32, xend = -68, yend = -32), color = "black", size = 0.3, alpha = 0.8) + 
-  geom_segment(data = data_merged_sub_ord, aes(x = -36, y = -21, xend = -58, yend = -21), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = 34, y = 78, xend = 18.5, yend = 68), color = "black", size = 0.3, alpha = 0.8) + 
-  geom_segment(data = data_merged_sub_ord, aes(x = 0, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = 15, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = -8, y = 61, xend = 1.5, yend = 52), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = 39, y = 60, xend = 9, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
-  geom_segment(data = data_merged_sub_ord, aes(x = 126, y = -36, xend = 148, yend = -36), color = "black", size = 0.3, alpha = 0.8) + #AUS
-  geom_segment(data = data_merged_sub_ord, aes(x = 90, y = 6, xend = 100, yend = 28), color = "black", size = 0.3, alpha = 0.8) + #CHINA
-  geom_segment(data = data_merged_sub_ord, aes(x = -66, y = 39, xend = -89, yend = 39), color = "black", size = 0.3, alpha = 0.8) + #USA
-  geom_segment(data = data_merged_sub_ord, aes(x = -48, y = 52, xend = -75, yend = 45), color = "black", size = 0.3, alpha = 0.8) + #CANADA
-  geom_segment(data = data_merged_sub_ord, aes(x = -71, y = 86, xend = -71, yend = 81), color = "black", size = 0.3, alpha = 0.8) + #CANADA
-  geom_segment(data = data_merged_sub_ord, aes(x = -52, y = 86, xend = -52, yend = 71), color = "black", size = 0.3, alpha = 0.8) + #GREENLAND
-  geom_segment(data = data_merged_sub_ord, aes(x = -20, y = 86, xend = -20, yend = 74), color = "black", size = 0.3, alpha = 0.8)
-
-```
-
-#DESCRIPTION OF THE DATA
-
-*What sort of data do we have?*
-
-There are approximately 1600 species from 30 different networks.
-All of these networks are phytocentric (built from plants).
-The different plant-pollinator communities have been studied with very different sampling effort and methodologies.
-Therefore, our aim is not to compare across studies but to create a general picture of how floral traits shape the different pollinator taxa and network metrics.
-Here, we combine studies that have multiple years of sampling and multiple sites within an area in metawebs.
-These metawebs give a broader perspective of the sampling area and inform about the regional species pool [@noreika2019pollinator].
-The data of these networks is quantitative (visitation) or qualitative (binary), there are in total 19 and 11 networks/metawebs of each, respectively.
-
-\begin{landscape}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,}
-setwd("~/R_Projects/Reproductive Traits")
-library(kableExtra)
-
-m <- read.csv("Data/Data_processing/metadata.csv", stringsAsFactors = F)
-#I will have to do some editing before knitting
-#colnames(m) <- c("")
-m<-m[,-c(1,3)]
-colnames(m) <- c("Id","Longitude", "Latitude", "Country", "Year", "Networks", "Plant spp", "Pollinator spp", "Network size", "Sampling method", "Sampling", "Data type")
-
-#let's select a unique network per coordinate
-#Fix Bartomeus unp 2015
-m[22,2] <- -6.16895
-m[22,3] <- 37.234966
-#Dicks
-m[27,2] <- 1.575532
-m[27,3] <- 52.762395
-#Dupont
-m[28,2] <- 9.1
-m[28,3] <- 56.1
-
-m[1] <- c("Bartomeus 2008", "Fang 2012", "Inouye 1990", "Inouye 1988", "Kaiser-Bunbury 2009", "Kaiser-Bunbury 2014", "Kato 2000", "Kevan 1970", "Lundgren 2005", "Olesen 2002 1", "Mcmullen 1993", "Bartomeus 2008", "Primack 1983 1", "Primack 1983 2", "Primack 1983 3", "Ramirez 1989", "Ramirez 1992", "Robertson 1929", "Small 1976", "Souza 2018", "Traveset 2013", "Bartomeus 2015 unp.", "Bek 2006", "Olesen 2002 2", "Bundgaard 2003", "Chacoff 2011", "Dicks 2002", "Dupont 2009", "Elberling 1999", "Dupont 2009 2")
-
-m[10] <- c("Plots with transects", "Plots", "Transects", "Plots", "Plots", "Transects", "Transects", "Randow census walks", "Randow census walks", "Plots", "-", "Plots with transects", "Randow census walks", "Randow census walks", "Randow census walks", "Randow census walks", "Randow census walks", "-", "10h per spp", "Plots", "Randow census walks", "Transects", "Plots", "Plots", "Plots", "Plots", "Plots", "Plots", "Plots with transects", "Random census walks")
-
-kable(m, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", caption = "Metadata for all the different networks/metawebs used at their maximum level of organization (metaweb if possible).") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T)
-
-### en 2008 por que hay 3 networks? Netiendo como puede haver 12, 6 o 2, pero 3? OK entendido, ya veo el 3+3! pon 2008a 2008b?
-```
-\end{landscape}
-
-#REFERENCES

### 2020-11-27 Scripts/5_Merge_Z-scores_Trait_Data_FunctionalG.R

@@ -18,13 +18,14 @@ library(readxl) #read trait data
 #1) LOAD LONG FORMAT DATA WITH Z-SCORES, TRAIT DATA AND FUNCTIONAL GROUP DATA
 ########################################################################################################################################################
 long_d_2 <- read.csv("Data/Csv/long_format_quantitative_networks_Z_scores.csv")
+long_d_2_non_apis <- read.csv("Data/Csv/long_format_quantitative_networks_Z_scores_non_apis.csv")
 t_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx")
 hclust_d_5 <- read.csv("Data/Csv/imputed_trait_data_hclust_5_clusters.csv") #5 clusters
 ########################################################################################################################################################
 #3) MERGE WITH TRAIT DATA
 ########################################################################################################################################################
 
-#process trait data
+#process trait data all species
 t_data <- t_data[1:1701,]
 #filter data, select species with flower level info and capitulum
 t_data_filtered <- filter(t_data, Info_level == "flower" |  Info_level == "capitulum")
@@ -38,11 +39,12 @@ colnames(t)[1] <- "Plant_species"
 
 #MERGE NETWORK AND TRAIT DATA
 long_format_trait_data <- merge(long_d_2, t, by = "Plant_species", all.x =T)
-
+########################################################################################################################################################
+#repeat fo dataset witout apis mellifera
+long_format_trait_data_non_apis <- merge(long_d_2_non_apis, t, by = "Plant_species", all.x =T)
 ########################################################################################################################################################
 #4) MERGE WITH FUNCTIONAL GROUPS
 ########################################################################################################################################################
-
 #5 CLUSTERS
 #Some data processing before merging
 #colnames to merge by same id
@@ -64,14 +66,26 @@ quantitative_networks_Z_scores_with_traits_and_5_clusters <- merge(long_format_t
 head(quantitative_networks_Z_scores_with_traits_and_5_clusters)
 #remov 2 X'2 cloumn
 quantitative_networks_Z_scores_with_traits_and_5_clusters <- quantitative_networks_Z_scores_with_traits_and_5_clusters[,-c(3,4)]
-
+########################################################################################################################################################
+#repeat fo dataset witout apis mellifera
+#convert to chracters
+long_format_trait_data_non_apis$Species_all <- as.character(long_format_trait_data_non_apis$Species_all)
[…]

### 2020-11-27 Scripts/6_Analysis_Z_scores_Guilds_FunctionalG.R

@@ -104,106 +104,88 @@ pp_check(m_5_clust_stu_hclust, type='violin_grouped',group="guild")+ylim(-4,4)
 #SAVE MODEL
 setwd("~/Dropbox/PhD/R") #DROPBOX, files too large for github
 saveRDS(m_5_clust_stu_hclust, "m_5_clust_stu_hclust.RDS")
+m_5_clust_stu_hclust <- readRDS("m_5_clust_stu_hclust.RDS")
 
 
 #TRYING OTHER MODEL
 #5 clusters hclust
-m_5_clust_neg_hclust <- brm(Interaction ~ guild*Clusters + (1|Id) + (1|gr(phylo, cov = A)),
-                            data = d_5_1, family  = negbinomial(),data2 = list(A = A_5), cores = 4,chains = 4, 
+m_5_clust_zero_neg_hclust <- brm((Interaction-1) ~ guild*Clusters + (1|Id) + (1|gr(phylo, cov = A)),
+                            data = d_5_1, family  = zero_inflated_negbinomial(),data2 = list(A = A_5), cores = 4,chains = 4, 
                             sample_prior = TRUE, warmup = 500, iter = 1500,
                             control = list(adapt_delta = 0.99)) 
 
-marginal_effects(m_5_clust_neg_hclust, effects = "Clusters:guild")
-pp_check(m_5_clust_neg_hclust) +xlim(-50,200)+ylim(0,0.1)
-pp_check(m_5_clust_neg_hclust, type='violin_grouped',group="Clusters")+ylim(-4,4)
-pp_check(m_5_clust_neg_hclust, type='violin_grouped',group="guild")+ylim(-4,4)
-saveRDS(m_5_clust_neg_hclust, "m_5_clust_neg_hclust")
+marginal_effects(m_5_clust_zero_neg_hclust, effects = "Clusters:guild")
+pp_check(m_5_clust_zero_neg_hclust) +xlim(-50,200)+ylim(0,0.1)
+pp_check(m_5_clust_zero_neg_hclust, type='violin_grouped',group="Clusters")+ylim(-4,4)
+pp_check(m_5_clust_zero_neg_hclust, type='violin_grouped',group="guild")+ylim(-4,4)
+saveRDS(m_5_clust_zero_neg_hclust, "m_5_clust_zero_neg_hclust")
 
 
 
+m_5_clust_zero_neg_hclust <- readRDS("m_5_clust_zero_neg_hclust_1.RDS")
 
 
 
[…]

### 2020-11-30 Scripts/6_Plot/6_Model_output_plot.Rmd
plot

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8}
-library(dplyr)
-library(tidyr)
-library(plyr)
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=9, fig.width=10}
 library(ggplot2)
-library(reshape2)
-library(scales)
-library(devtools)
+library(brms)
 library(png)
 library(grid)
+library(grid)
 library(gridExtra)
-library(jpeg)
-dev_mode(on=T)
 
+setwd("~/Dropbox/PhD/R") #DROPBOX, files too large for github
+m_5_clust_zero_neg_hclust <- readRDS("m_5_clust_zero_neg_hclust_1.RDS")
 setwd("~/R_Projects/Reproductive Traits")
+d_5_1 <- read.csv("Data/Csv/d_5_1_brms_all_5_clusters.csv")
+#Visits
+ce_1 <- conditional_effects(m_5_clust_zero_neg_hclust, effects = "Clusters:guild",points=T) 
+#change colnames in model output to use same aesthetics
+#if not gg seems to don't like it
+colnames(ce_1[[1]])[4] <- "a"
+colnames(ce_1[[1]])[10] <- "Interaction"
+ce_1[[1]][10]<- ce_1[[1]][10]+1
+#Order levels
+#fixing label
+d_5_1$guild <- as.character(d_5_1$guild)
+d_5_1$guild[d_5_1$guild=="Bee"] <- "Bees"
+ce_1[[1]]$guild <- as.character(ce_1[[1]]$guild)
+ce_1[[1]]$guild[ce_1[[1]]$guild=="Bee"] <- "Bees"
 
-img <- readPNG(system.file("img", "Rlogo.png", package="png"))
-g <- rasterGrob(img, interpolate=TRUE)
+ce_1[[1]]$guild <- factor(ce_1[[1]]$guild, levels = c("Bees","Non-bee-Hymenoptera","Syrphids","Non-syrphids-diptera","Lepidoptera","Coleoptera"))
+d_5_1$guild <- factor(d_5_1$guild, levels = c("Bees","Non-bee-Hymenoptera","Syrphids","Non-syrphids-diptera","Lepidoptera","Coleoptera"))
 
-net_long_1 <- readRDS("Data/RData/species_per_order_percentage.RData")
-
-legend_title <- "Taxonomic groups"
-
-la <- c("Ramirez 1989", "Ramirez 1992", "Bartomeus unp.
-2015", "Chacoff 2011","Bartomeus 2008 1", "Bartomeus 2008 2", "Robertson 1929", "Small 1976","Inouye 1990", "Souza 2018", "Bundgaard 2003", "Inouye 1988", "Dupont 2009 1", "Olesen 2002 1", "Fang huang 2012", "mcmullen 1993", "Olesen 2002 2", "Dicks 2002","Elberling 1999", "Primack 1983 1", "Primack 1983 2", "Kato 2000", "Kaiser-Bunbunry 2009", "Traveset 2013", "Kevan 1970", "Bek 2006","Primack 1983 3", "Kaiser-Bunbury 2014", "Dupont 2009 2", "Lundgren 2005")
-
+#read images
  get_png <- function(filename) {
@@
 
-l <- get_png("Images/lepidoptera_2.png")
-bumb <- get_png("Images/bumblebee.png")
-dip <- get_png("Images/diptera.png")
-beet <- get_png("Images/beetle.png")
-hem<- get_png("Images/hemiptera.png")
+# 
+d_1 <- get_png("Images/dip_green_2.png")
+l <- get_png("Images/lepi_brown.png")
+b <- get_png("Images/bumble_orange.png")
+f <- get_png("Images/form_orange.png")
+s <- get_png("Images/syr_blue.png")
 
@@
 
-p<- ggplot(net_long_1) +
-  aes(x = reorder(Id,-order), 
-      y = measurement, 
-      fill =factor(orders, levels=c("Hemiptera","Coleoptera","Lepidoptera","Diptera", "Hymenoptera"))) +
-  geom_bar(position = "fill", stat = "identity", alpha=0.6) +coord_flip() +scale_x_discrete(labels= la) + 
-  scale_fill_manual(legend_title,values=c("indianred", "gray49", "seagreen", "darkgoldenrod2", "#386cb0")) + theme_classic()+xlab("Networks")+ylab("Species per order") +scale_y_continuous(labels = scales::percent) + theme(legend.background = element_rect(fill=alpha('blue', 0.0)))+
-  annotation_custom(l, xmin = 14.6, xmax = 15.4, ymin = 1.03, ymax =1.09) + annotation_custom(bumb, xmin = 11.6, xmax = 13.9, ymin = 1.03, ymax =1.09)+ annotation_custom(dip, xmin = 13.4, xmax = 14.4, ymin = 1.035, ymax =1.085)+
-  coord_cartesian(clip = "off") + annotation_custom(beet, xmin = 15.5, xmax = 16.7, ymin = 0.86, ymax =1.255)+ annotation_custom(hem, xmin = 16.9, xmax = 17.65, ymin = 0.883, ymax =1.233)+
-  coord_cartesian(clip = "off")+ coord_flip()
+t <- ggplot(ce_1[[1]], aes(x = Clusters, y = Interaction, colour = as.factor(guild), group = 
+  as.factor(guild))) +
+  geom_point(size = 1.2, position = position_dodge(width = 0.9), alpha=1) +
+  theme_bw()+ ylab("Nº of visits per plant taxa") + xlab("Plant reproductive groups")+
+  geom_point(data = d_5_1,aes(x = Clusters, y = (Interaction+1)),size = 1.2, position = position_jitterdodge(dodge.width = 0.9,   jitter.width = 0.2), alpha=0.2)+
+  geom_errorbar(data=ce_1[[1]],mapping=aes(x=Clusters, ymin=lower__, ymax=upper__,colour = as.factor(guild), group = 
+  as.factor(guild)), width=.6,alpha=0.85, size = 0.9,position = position_dodge(width = 0.9)) +ylim(0,200)+
+  scale_color_manual("Floral visitors guilds",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black"))+
+  annotation_custom(d_1, xmin = 1.02, xmax =1.15 , ymin = -5.1, ymax =-0.2) + #diptera
+  annotation_custom(l, xmin = 1.16, xmax =1.30 , ymin = -28, ymax =22) +  #lepidoptera
+  geom_vline(xintercept = c(1.5,2.5,3.5,4.5), linetype="dashed", color = "grey", size=0.5)+ #vertical lines
+  theme(panel.grid.major.x = element_blank(),panel.grid.minor.y  = element_blank())+ # remove some grids
+  annotation_custom(b, xmin = 0.46, xmax =0.79 , ymin = -4.35, ymax =-0.25) + #bees
+ annotation_custom(f, xmin = 0.67, xmax =0.87 , ymin = -4.35, ymax =-0.25) + #hymenoptera non bees
+ annotation_custom(s, xmin = 0.817, xmax =1.05 , ymin = -5.3, ymax =-0.25)
 
-gg_table <- ggplot_gtable(ggplot_build(p))
+gg_table <- ggplot_gtable(ggplot_build(t))
 gg_table$layout$clip[gg_table$layout$name=="panel"] <- "off"

### 2020-11-30 Scripts/6_Analysis_Z_scores_Guilds_FunctionalG.R

@@ -85,6 +85,10 @@ d_5_1$Clusters[d_5_1$Clusters=="5"] <- "E"
 
 d_5_1$Clusters <- as.factor(d_5_1$Clusters)
 levels(as.factor(d_5_1$Clusters))
+
+#save data
+#write.csv(d_5_1, "Data/Csv/d_5_1_brms_all_5_clusters.csv")
+
 ########################################################################################################################################################
 #3)ANALYSIS
 ########################################################################################################################################################

### 2020-12-01 Scripts/6_Plot/6_Model_output_plot.Rmd
plot with images

@@
 l <- get_png("Images/lepi_brown.png")
-b <- get_png("Images/bumble_orange.png")
-f <- get_png("Images/form_orange.png")
+b <- get_png("Images/bee_orange.png")
+f <- get_png("Images/form_2.png")
 s <- get_png("Images/syr_blue.png")
 
-t <- grid::roundrectGrob(x=0.5, y=0.5, width=1, height=1)
+t <- grid::roundrectGrob(x=10, y=10, width=10, height=10)
 
@@
   as.factor(guild)), width=.6,alpha=0.85, size = 0.9,position = position_dodge(width = 0.9)) +ylim(0,200)+
-  scale_color_manual("Floral visitors guilds",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black"))+
-  annotation_custom(d_1, xmin = 1.02, xmax =1.15 , ymin = -5.1, ymax =-0.2) + #diptera
-  annotation_custom(l, xmin = 1.16, xmax =1.30 , ymin = -28, ymax =22) +  #lepidoptera
-  geom_vline(xintercept = c(1.5,2.5,3.5,4.5), linetype="dashed", color = "grey", size=0.5)+ #vertical lines
-  theme(panel.grid.major.x = element_blank(),panel.grid.minor.y  = element_blank())+ # remove some grids
-  annotation_custom(b, xmin = 0.46, xmax =0.79 , ymin = -4.35, ymax =-0.25) + #bees
- annotation_custom(f, xmin = 0.67, xmax =0.87 , ymin = -4.35, ymax =-0.25) + #hymenoptera non bees
- annotation_custom(s, xmin = 0.817, xmax =1.05 , ymin = -5.3, ymax =-0.25)
+  scale_color_manual("Floral visitors guilds",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black"))+  theme(panel.grid.major.x = element_blank(),panel.grid.minor.y  = element_blank())+   geom_vline(xintercept = c(1.5,2.5,3.5,4.5), linetype="dashed", color = "black", size=0.5)
 
-gg_table <- ggplot_gtable(ggplot_build(t))
+t_1 <-  t + annotation_custom(l, xmin = 1.17, xmax =1.28 , ymin = -5.5, ymax =-0.5)+
+  annotation_custom(l, xmin = 1.17, xmax =1.28 , ymin = -5.75, ymax =-0.5) +  
+  annotation_custom(b, xmin = 0.55, xmax =0.70 , ymin = -5, ymax =0) + 
+ annotation_custom(f, xmin = 0.67, xmax =0.87 , ymin = -4.5, ymax =-0.65) + 
+ annotation_custom(s, xmin = 0.85, xmax =0.99 , ymin = -5.5, ymax =-0.25)+
+  annotation_custom(d_1, xmin = 1.0, xmax =1.14 , ymin = -5, ymax =0)
+
+gg_table <- ggplot_gtable(ggplot_build(t_1))
 gg_table$layout$clip[gg_table$layout$name=="panel"] <- "off"

### 2020-12-01 Rmd/Visitation_stacked_barplot.Rmd
organising clusters

@@
   coord_cartesian(clip = "off") + annotation_custom(beet, xmin = 9.96, xmax = 10.76, ymin = 0.86, ymax =1.255)+ annotation_custom(hem, xmin = 10.86, xmax = 11.36, ymin = 0.883, ymax =1.233)+
-  coord_cartesian(clip = "off")+ coord_flip()
+  coord_cartesian(clip = "off")+ coord_flip()+coord_cartesian(clip = "off")
 

### 2020-12-01 Scripts/6_Plot/6_Model_output_plot.Rmd
organising clusters

@@
 ---
-title: "Visitation_stacked_barplot"
+title: ""
 output:
@@
 s <- get_png("Images/syr_blue.png")
+beet <- get_png("Images/beet_black.png")
 
-t <- grid::roundrectGrob(x=10, y=10, width=10, height=10)
+t <- grid::roundrectGrob(x=20, y=20, width=20, height=20)
 
@@
   as.factor(guild)), width=.6,alpha=0.85, size = 0.9,position = position_dodge(width = 0.9)) +ylim(0,200)+
-  scale_color_manual("Floral visitors guilds",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black"))+  theme(panel.grid.major.x = element_blank(),panel.grid.minor.y  = element_blank())+   geom_vline(xintercept = c(1.5,2.5,3.5,4.5), linetype="dashed", color = "black", size=0.5)
+  scale_color_manual("Floral visitors guilds",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black"))+  theme(panel.grid.major.x = element_blank(),panel.grid.minor.y  = element_blank())+   geom_vline(xintercept = c(1.5,2.5,3.5,4.5), linetype="dashed", color = "black", size=0.5)+coord_cartesian(clip = "off")+theme(legend.box.margin=margin(6,6,6,6))
+  #cluster 1
+t_1 <-  t + annotation_custom(l, xmin = 1.17, xmax =1.28 , ymin = -5.75, ymax =0.5)+ #needed to colour the rest
+  annotation_custom(l, xmin = 1.17, xmax =1.28 , ymin = -5.75, ymax =0.5) +  #lepidoptera
+  annotation_custom(b, xmin = 0.55, xmax =0.70 , ymin = -5, ymax =0) + #bee
+  annotation_custom(f, xmin = 0.67, xmax =0.87 , ymin = -4.5, ymax =-0.65) + #wasp
+  annotation_custom(s, xmin = 0.85, xmax =0.99 , ymin = -5.5, ymax =-0.25)+ # syrphid
+  annotation_custom(d_1, xmin = 1.0, xmax =1.14 , ymin = -5.75, ymax =1) + #diptera
+  annotation_custom(beet, xmin = 1.265, xmax =1.485 , ymin = -4.5, ymax =-0.35) #beetle
+  #cluster 2
+t_2 <-  t_1 + annotation_custom(l, xmin = 2.17, xmax =2.28 , ymin = -5.75, ymax =0.5)+ #needed to colour the rest
+  annotation_custom(l, xmin = 2.17, xmax =2.28 , ymin = -5.75, ymax =0.5) +  #lepidoptera
+  annotation_custom(b, xmin = 1.55, xmax =1.70 , ymin = -5, ymax =0) + #bee
+  annotation_custom(f, xmin = 1.67, xmax =1.87 , ymin = -4.5, ymax =-0.65) + #wasp
+  annotation_custom(s, xmin = 1.85, xmax =1.99 , ymin = -5.5, ymax =-0.25)+ # syrphid
+  annotation_custom(d_1, xmin = 2.0, xmax =2.14 , ymin = -5.75, ymax =1) + #diptera
+  annotation_custom(beet, xmin = 2.265, xmax =2.485 , ymin = -4.5, ymax =-0.35) #beetle
+  #cluster 3
+t_3 <-  t_2 + annotation_custom(l, xmin = 3.17, xmax =3.28 , ymin = -5.75, ymax =0.5)+ #needed to colour the rest
+  annotation_custom(l, xmin = 3.17, xmax =3.28 , ymin = -5.75, ymax =0.5) +  #lepidoptera
+  annotation_custom(b, xmin = 2.55, xmax =2.70 , ymin = -5, ymax =0) + #bee
+  annotation_custom(f, xmin = 2.67, xmax =2.87 , ymin = -4.5, ymax =-0.65) + #wasp
+  annotation_custom(s, xmin = 2.85, xmax =2.99 , ymin = -5.5, ymax =-0.25)+ # syrphid
+  annotation_custom(d_1, xmin = 3.0, xmax =3.14 , ymin = -5.75, ymax =1) + #diptera
+  annotation_custom(beet, xmin = 3.265, xmax =3.485 , ymin = -4.5, ymax =-0.35) #beetle
+  #cluster 4
+t_4 <-  t_3 + annotation_custom(l, xmin = 4.17, xmax =4.28 , ymin = -5.75, ymax =0.5)+ #needed to colour the rest
+  annotation_custom(l, xmin = 4.17, xmax =4.28 , ymin = -5.75, ymax =0.5) +  #lepidoptera
+  annotation_custom(b, xmin = 3.55, xmax =3.70 , ymin = -5, ymax =0) + #bee
+  annotation_custom(f, xmin = 3.67, xmax =3.87 , ymin = -4.5, ymax =-0.65) + #wasp
+  annotation_custom(s, xmin = 3.85, xmax =3.99 , ymin = -5.5, ymax =-0.25)+ # syrphid
+  annotation_custom(d_1, xmin = 4.0, xmax =4.14 , ymin = -5.75, ymax =1) + #diptera
+  annotation_custom(beet, xmin = 4.265, xmax =4.485 , ymin = -4.5, ymax =-0.35) #beetle
+  #cluster 5
+t_5 <-  t_4 + annotation_custom(l, xmin = 5.17, xmax =5.28 , ymin = -5.75, ymax =0.5)+ #needed to colour the rest
+  annotation_custom(l, xmin = 5.17, xmax =5.28 , ymin = -5.75, ymax =0.5) +  #lepidoptera
+  annotation_custom(b, xmin = 4.55, xmax =4.70 , ymin = -5, ymax =0) + #bee
+  annotation_custom(f, xmin = 4.67, xmax =4.87 , ymin = -4.5, ymax =-0.65) + #wasp
+  annotation_custom(s, xmin = 4.85, xmax =4.99 , ymin = -5.5, ymax =-0.25)+ # syrphid
+  annotation_custom(d_1, xmin = 5.0, xmax =5.14 , ymin = -5.75, ymax =1) + #diptera
+  annotation_custom(beet, xmin = 5.265, xmax =5.485 , ymin = -4.5, ymax =-0.35) #beetle
+  #legend
+t_6 <-  t_5 + annotation_custom(l, xmin = 5.65, xmax =5.76 , ymin = 84.4, ymax =90.8)+ #lepidoptera
+              annotation_custom(b, xmin = 5.65, xmax =5.76 , ymin = 108, ymax =117.5)+ #bee
+              annotation_custom(f, xmin = 5.65, xmax =5.76 , ymin = 105, ymax =108.5)+ #wasp
+              annotation_custom(s, xmin = 5.65, xmax =5.76 , ymin = 97.5, ymax =102.5)+ #syrphid
+              annotation_custom(d_1, xmin = 5.65, xmax =5.76 , ymin = 89, ymax =99) + #diptera
+              annotation_custom(beet, xmin = 5.65, xmax =5.76 , ymin = 79.5, ymax =83.5) #beetle
 
-t_1 <-  t + annotation_custom(l, xmin = 1.17, xmax =1.28 , ymin = -5.5, ymax =-0.5)+
-  annotation_custom(l, xmin = 1.17, xmax =1.28 , ymin = -5.75, ymax =-0.5) +  
-  annotation_custom(b, xmin = 0.55, xmax =0.70 , ymin = -5, ymax =0) + 
- annotation_custom(f, xmin = 0.67, xmax =0.87 , ymin = -4.5, ymax =-0.65) + 
- annotation_custom(s, xmin = 0.85, xmax =0.99 , ymin = -5.5, ymax =-0.25)+
-  annotation_custom(d_1, xmin = 1.0, xmax =1.14 , ymin = -5, ymax =0)
-
-gg_table <- ggplot_gtable(ggplot_build(t_1))
+gg_table <- ggplot_gtable(ggplot_build(t_6))
 gg_table$layout$clip[gg_table$layout$name=="panel"] <- "off"

### 2020-12-14 Scripts/7_1_Visualize_Plant_Functional_Groups/7_plots.Rmd
edits

---
title: "Untitled"
output: pdf_document
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=6}
setwd("~/R_Projects/Reproductive Traits")
library(dplyr)
library(ggplot2)
library(viridis)
library(grid)
library(cowplot)
library(gridExtra)

#PREPARE DATA
#read unscaled trait data in order to visualize better the clusters
d <- read.csv("Data/Csv/all_species_imputed_trait_data.csv")
#read trait data with clusters
#I'll select the column of clusters and include it on the non standardize trait data
hclust_d_5 <- read.csv("Data/Csv/imputed_trait_data_hclust_5_clusters.csv") #5 clusters
#No add the cluster columns (it has the same order)
d$Clusters <- as.factor(hclust_d_5$Clusters)

#select columns of interest
t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
                        "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
                        "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
                        "IMPUTED_plant_height_mean_m", "Clusters")]

#GENERATE PLOTS
########################################################################################################################################
#Breeding system
########################################################################################################################################
breeding <- ggplot(t, aes(Clusters, Breeding_system)) +
  geom_jitter(aes(color = Clusters), size = 0.4)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "#009E73"))+
  theme_classic()+theme(legend.position = "none")+labs(x=NULL,y=NULL,subtitle = "Breeding system")+
  geom_hline(yintercept=c(1.5,2.5),color="black",linetype="longdash")
########################################################################################################################################
#Compatibility
########################################################################################################################################
t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Unisexual flowers"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Unisexual flowers"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"

Compatibility <- ggplot(t, aes(Clusters, IMPUTED_Compatibility)) +
  geom_jitter(aes(color = Clusters), size = 0.4)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "#009E73"))+
  theme_classic()+ theme_classic()+theme(legend.position = "none")+labs(x=NULL,y=NULL,subtitle = "Compatibility system")+
  geom_hline(yintercept=c(1.5,2.5,3.5),color="black",linetype="longdash")
########################################################################################################################################
#Autonomous_selfing_level
########################################################################################################################################
t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
t$Autonomous_selfing_level[t$Autonomous_selfing_level=="none"] <- "None"
t$Autonomous_selfing_level[t$Autonomous_selfing_level=="medium"] <- "Medium"
t$Autonomous_selfing_level[t$Autonomous_selfing_level=="low"] <- "Low"
t$Autonomous_selfing_level[t$Autonomous_selfing_level=="high"] <- "High"
t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels = c("None", "Low", "Medium", "High"))

Selfing <- ggplot(t, aes(Clusters, Autonomous_selfing_level)) +
  geom_jitter(aes(color = Clusters), size = 0.4)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "#009E73"))+
  theme_classic()+ theme_classic()+theme(legend.position = "none")+labs(x=NULL,y=NULL,subtitle = "Selfing level")+
  geom_hline(yintercept=c(1.5,2.5,3.5),color="black",linetype="longdash")
#######################################################################################################################################
#Flower_morphology
#######################################################################################################################################

t$Flower_morphology <- as.character(t$Flower_morphology)
t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Tube"
t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"

Flower_morphology <-  ggplot(t, aes(Clusters, Flower_morphology)) +
  geom_jitter(aes(color = Clusters), size = 0.4)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "#009E73"))+
  theme_classic()+ theme_classic()+theme(legend.position = "none")+labs(x=NULL,y=NULL,subtitle = "Flower shape")+
  geom_hline(yintercept=c(1.5,2.5,3.5,4.5,5.5),color="black",linetype="longdash")
#######################################################################################################################################
#Flower_symmetry
#######################################################################################################################################
t$Flower_symmetry <- as.character(t$Flower_symmetry)
t$Flower_symmetry[t$Flower_symmetry=="zygomorphic"] <- "Zygomorphic"
t$Flower_symmetry[t$Flower_symmetry=="actinomorphic"] <- "Actinomorphic"

Flower_symmetry <-  ggplot(t, aes(Clusters, Flower_symmetry)) +
   geom_jitter(aes(color = Clusters), size = 0.4)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "#009E73"))+
   theme_classic()+ theme_classic()+theme(legend.position = "none")+labs(x=NULL,y=NULL,subtitle = "Flower symmetry")+
  geom_hline(yintercept=c(1.5),color="black",linetype="longdash")
#######################################################################################################################################
 #life_form
#######################################################################################################################################
t$life_form <- as.character(t$life_form)
t$life_form[t$life_form=="vine"] <- "Herb"
t$life_form[t$life_form=="herb"] <- "Herb"
t$life_form[t$life_form=="shrub"] <- "Shrub"
t$life_form[t$life_form=="tree"] <- "Tree"

life_form <-  ggplot(t, aes(Clusters,life_form )) +
   geom_jitter(aes(color = Clusters), size = 0.4)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "#009E73"))+
   theme_classic()+ theme_classic()+theme(legend.position = "none")+labs(x=NULL,y=NULL,subtitle = "Life form")+
  geom_hline(yintercept=c(1.5,2.5),color="black",linetype="longdash")
#######################################################################################################################################
 #lifespan
#######################################################################################################################################
lifespan<- ggplot(t, aes(Clusters,lifespan )) +
   geom_jitter(aes(color = Clusters), size = 0.4)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "#009E73"))+
   theme_classic()+ theme_classic()+theme(legend.position = "none")+labs(x="Plant Functional groups",y=NULL,subtitle = "Life span")+
  geom_hline(yintercept=c(1.5),color="black",linetype="longdash")

#######################################################################################################################################
 plot_grid(breeding,Compatibility,Selfing,Flower_morphology,Flower_symmetry,life_form,lifespan, nrow = 7,align = 'v')

```

### 2020-12-14 Scripts/7_.R

@@ -1,439 +1,0 @@
-########################################################################################################################################################
-#SCRIPT TO EXPLORE THE TRAIT DATA OF THE DIFFERENT CLUSTERS
-
-#1)LOAD DATA 
-
-#2)PHYLOGENETIC DISTANCE OF THE SPECIES -Add them as covariable-
-
-#3)SAVE MODEL
-
-#4)PLOT OUTPUT NICELY
-########################################################################################################################################################
-library(dplyr)
-library(ggplot2)
-library(viridis)
-<<<<<<< HEAD
-library(grid)
-library(cowplot)
-library("gridExtra")
-=======
-library(tidyr)
-library(ggpubr)
->>>>>>> afbdf8ef850e818754516a1d17cb40ccfd186aa0
-########################################################################################################################################################
-#1) READ DATA
-########################################################################################################################################################
-#read unscaled trait data in order to visualize better the clusters
-d <- read.csv("Data/Csv/all_species_imputed_trait_data.csv")
-#read trait data with clusters
-#I'll select the column of clusters and include it on the non standardize trait data
-hclust_d_5 <- read.csv("Data/Csv/imputed_trait_data_hclust_5_clusters.csv") #5 clusters
-#No add the cluster columns (it has the same order)
-d$Clusters <- as.factor(hclust_d_5$Clusters)
-
-#select columns of interest
-t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
-                        "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
-                        "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
-                        "IMPUTED_plant_height_mean_m", "Clusters")]
-
-
-#Exploratory summary of the data
-summ_clusters <- t  %>% group_by(Clusters) %>% do(the_summary = summary(.))
-summ_clusters$the_summary
-
-
[…]

### 2020-12-14 Scripts/OLD/Analysis/Quantitative_networks_analysis/Principal_Component_Analysis.R

@@ -66,7 +66,7 @@ res.impute$completeObs$Selfing_level <- as.factor(res.impute$completeObs$Selfing
 fviz_pca_biplot(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="var",
                 geom.ind = "point",alpha.ind = 1, col.ind=res.impute$completeObs[-c(414,480,482,634,705,1139),c(3)], 
                 pointshape = 19, pointsize = 1,
-                palette = c("#35B779FF","#FDE725FF"),
+                palette = c("#black","#FDE725FF"),
                 # Variables
                 col.var = "black",title="",  arrowsize = 0.6,alpha.var=0.7)+xlim(-7, 10) + ylim (-8,8)+border()+labs(color="Selfing")
 
@@ -83,3 +83,151 @@ fviz_pca_ind(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,
   guides(color = guide_legend(override.aes = list(size=1.5)))
 
 
+
+fviz_pca_biplot(prcomp(res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)], scale=T), label="var",
+                geom.ind = "point",alpha.ind = 0.8, 
+                pointshape = 19, pointsize = 1,
+                palette = c("#black"),
+                # Variables
+                col.var = "#009E73",title="",  arrowsize = 1.2,alpha.var=0.7)+xlim(-7, 10)
+
+
+
+#PCA corrected by phylogeny
+
+##################################################################################################################################################################################################################
+
+#Trying phylogenetic PCA
+
+library(adephylo)
+
+res.impute$completeObs[-c(414,480,482,634,705,1139),c(4,7,8,9,10,12,13,16)]
+
+ppca(res.impute$completeObs[,c(4,7,8,9,10,12,13,16)],A_5)
+
+
+
+
+data(lizards)
+
+if(require(ape) && require(phylobase)){
[…]

### 2021-03-09 Rmd/PPCA_Qualitative_Vars.Rmd
PPCA plot panel

---
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=13, fig.width=11}

#Set working directory
setwd("~/R_Projects/Reproductive Traits")

#Load libraries
#LOAD LIBRARIES
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours

# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.3)),
            axis.text=element_text(size = rel(1.5), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(0.4, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
             panel.grid.major= element_blank()
      ))
}

#Load data
dat_cleaning_5 <- readRDS("Data/RData/Data_for_plotting_qualitative_pca_vars.rds")
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")

#CALL the output PC for simplicity
PC <- phyl_pca_forest
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots
Compatibility <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Compatibility <- dat_cleaning_5$IMPUTED_Compatibility
  dat$Compatibility <- as.character(dat$Compatibility)
  dat$Compatibility[dat$Compatibility=="dioecious"] <- "Unisexual flowers"
  dat$Compatibility[dat$Compatibility=="monoecious"] <- "Unisexual flowers"
  dat$Compatibility[dat$Compatibility=="partially_self_compatible"] <- "Partially self compatible"
  dat$Compatibility[dat$Compatibility=="self_compatible"] <- "Self compatible"
  dat$Compatibility[dat$Compatibility=="self_incompatible"] <- "Self incompatible"
  dat$Compatibility <- factor(dat$Compatibility, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))

  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Compatibility),size=1.5)+scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
                          label = PCAloadings$Variables, color="black",size=3.2)

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.185, 0.13)) +ggtitle("A)")

  plot

}

#Compatibility(PC)

#############################################################################################################################################################
#Life form
#############################################################################################################################################################
#Load plots
Life_form <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$`Life form` <- dat_cleaning_5$life_form
  dat$`Life form` <- as.character(dat$`Life form`)
  dat$`Life form`[dat$`Life form`=="herb"] <- "Herb"
  dat$`Life form`[dat$`Life form`=="shrub"] <- "Shrub"
  dat$`Life form`[dat$`Life form`=="tree"] <- "Tree"
  dat$`Life form`[dat$`Life form`=="vine"] <- "Shrub"

  dat$`Life form` <- factor( dat$`Life form`, levels = c("Herb", "Shrub", "Tree"))

  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Life form`),size=1.5)+scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
                          label = PCAloadings$Variables, color="black",size=3.2)

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("B)")

  plot

}

#Life_form(PC)

#############################################################################################################################################################
#Life span
#############################################################################################################################################################
#Load plots
Life_span <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
    dat$`Life span` <- dat_cleaning_5$lifespan
    dat$`Life span` <- as.character(dat$`Life span`)

  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Life span`),size=1.5)+scale_color_manual(values=c("sienna4","forestgreen"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
                          label = PCAloadings$Variables, color="black",size=3.2)

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.102, 0.1)) + ggtitle("C)")

  plot

}

#Life_span(PC)

#############################################################################################################################################################
#Flower symmetry
#############################################################################################################################################################
#Load plots
Flower_sym <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$`Flower symmetry` <- dat_cleaning_5$Flower_symmetry
  dat$`Flower symmetry` <- as.character(dat$`Flower symmetry`)
  dat$`Flower symmetry`[dat$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
  dat$`Flower symmetry`[dat$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"

  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower symmetry`),size=1.5)+scale_color_manual(values=c("sienna2","purple"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
                          label = PCAloadings$Variables, color="black",size=3.2)

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.165, 0.1)) + ggtitle("D)")

  plot

}

#Flower_sym(PC)

#############################################################################################################################################################
#Flower shape
#############################################################################################################################################################
#Load plots
Flower_sha <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$`Flower shape` <- dat_cleaning_5$Flower_morphology
  dat$`Flower shape` <- as.character(dat$`Flower shape`)
  dat$`Flower shape`[dat$`Flower shape`=="Funnelform"] <- "Campanulate"
  dat$`Flower shape`[dat$`Flower shape`=="Spike"] <- "Brush"

  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower shape`),size=1.5)+scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
                          label = PCAloadings$Variables, color="black",size=3.2)

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.13, 0.18)) + ggtitle("E)")

  plot

}

#Flower_sha(PC)

#############################################################################################################################################################
#Breeding system
#############################################################################################################################################################
#Load plots
Breeding_syst <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$`Breeding system` <- dat_cleaning_5$Breeding_system
  dat$`Breeding system` <- as.character(dat$`Breeding system`)
  dat$`Breeding system` <- factor(dat$`Breeding system`, levels=c("Hermaphrodite","Monoecious" ,"Dioecious"))

  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Breeding system`),size=1.5)+scale_color_manual(values=c("forestgreen","orange", "black"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
                          label = PCAloadings$Variables, color="black",size=3.2)

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.163, 0.115)) + ggtitle("F)")

  plot

}

#Breeding_syst(PC)

library(cowplot)
 plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Flower_sym(PC),Flower_sha(PC),Breeding_syst(PC), ncol=2,nrow=3,  align = "v")

```

### 2021-03-09 Rmd/PPCA_plot.Rmd
PPCA plot panel

---
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=6, fig.width=16}

#Set working directory
setwd("~/R_Projects/Reproductive Traits")

#Load libraries
#LOAD LIBRARIES
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours

# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.3)),
            axis.text=element_text(size = rel(2), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(0.9, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
             panel.grid.major= element_blank()
      ))
}

#Load data
dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca.rds")
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
dat_cleaning_5_nectar <- readRDS("Data/RData/data_subset_nectar.rds")
phyl_pca_forest_nectar <- readRDS("Data/RData/phyl_pca_forest_nectar_all.rds")
#CALL the output PC for simplicity
PC <- phyl_pca_forest
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots
all_spp <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
  dat$Nectar[dat$Nectar=="no"] <- "Absence"
  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("#fc2847", "#1cac78"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

   #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),")","%", sep = "")) #XLAB
  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
  plot <- plot + theme(panel.grid.minor = element_blank(),panel.grid.major = element_blank(),
                       panel.border = element_rect(linetype = "solid", colour = "black", size=1))

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
                          label = PCAloadings$Variables, color="black",size=5)

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.07, 0.11)) +ggtitle("")

  plot

}

#all_spp(PC)

#############################################################################################################################################################

#CALL the output PC for simplicity
PC <- phyl_pca_forest_nectar
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots

nectar_subset <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Nectar <- dat_cleaning_5_nectar$Nectar_presence_absence
  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
  dat$Nectar[dat$Nectar=="no"] <- "Absence"
  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("#fc2847", "#1cac78"))
  # plot <- plot +geom_point(data=dat, aes(-x, -y, colour = density),size=0.65,shape = 1,colour = "black",alpha=0.8)

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

   #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),")","%", sep = "")) #XLAB
  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
  plot <- plot + theme(panel.grid.minor = element_blank(),panel.grid.major = element_blank(),
                       panel.border = element_rect(linetype = "solid", colour = "black", size=1))

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height", "Nectar")

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(6,5.35,5,6,6,6,6)), y = -(PCAloadings$PC2*c(5.75,5,4.75,5.75,5.8,5.5,6)),
                          label = PCAloadings$Variables, color="black",size=5)

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.08, 0.11)) +ggtitle("")

  plot

}

library(cowplot)
 plot_grid(all_spp(phyl_pca_forest),nectar_subset(phyl_pca_forest_nectar), ncol=2,  align = "h")

```

### 2021-03-09 Scripts/3_3_PPCA_Coloured_By_Qualitative.R

@@ -115,9 +115,8 @@ rownames(final_d) <- gsub(" ", "_", rownames(final_d))
 ####
 #SAVE PHYLO PCA OUTPUT
 ####
-#saveRDS(phyl_pca_famd, "Data/RData/phyl_pca_famd.rds")
-#saveRDS(phyl_pca_forest, "Data/RData/phyl_pca_forest.rds")
-
+#saveRDS(phyl_pca_forest, "Data/RData/Data_for_plotting_qualitative_pca_vars.rds")
+#saveRDS(dat_cleaning_5, "Data/RData/data_all_species_for_rmd_plot_ppca.rds")
 ####
 #READ DATA
 ####

### 2021-03-11 Rmd/PPCA_plot_1.Rmd
Edits

--- 2021-03-09 Rmd/PPCA_plot.Rmd
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=6, fig.width=16}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=9, fig.width=9}
 
@@
   dat$Nectar[dat$Nectar=="no"] <- "Absence"
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("#fc2847", "#1cac78"))
+   dat$Nectar <- factor(dat$Nectar, levels = c("Presence","Absence"))
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("grey", "black"))
 
@@
 
-#all_spp(PC)
-
-#############################################################################################################################################################
-
-#CALL the output PC for simplicity
-PC <- phyl_pca_forest_nectar
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-nectar_subset <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Nectar <- dat_cleaning_5_nectar$Nectar_presence_absence
-  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("#fc2847", "#1cac78"))
-  # plot <- plot +geom_point(data=dat, aes(-x, -y, colour = density),size=0.65,shape = 1,colour = "black",alpha=0.8)
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),")","%", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-  plot <- plot + theme(panel.grid.minor = element_blank(),panel.grid.major = element_blank(),
-                       panel.border = element_rect(linetype = "solid", colour = "black", size=1))
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height", "Nectar")
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(6,5.35,5,6,6,6,6)), y = -(PCAloadings$PC2*c(5.75,5,4.75,5.75,5.8,5.5,6)),
-                          label = PCAloadings$Variables, color="black",size=5)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.08, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-library(cowplot)
- plot_grid(all_spp(phyl_pca_forest),nectar_subset(phyl_pca_forest_nectar), ncol=2,  align = "h")
+all_spp(PC)
 

### 2021-03-11 Scripts/7_1_Plot_Model_Output_for_Publication/6_Model_output_plot.Rmd
Edits

--- 2020-12-01 Scripts/6_Plot/6_Model_output_plot.Rmd
@@
 setwd("~/Dropbox/PhD/R") #DROPBOX, files too large for github
-m_5_clust_zero_neg_hclust <- readRDS("m_5_clust_zero_neg_hclust_1.RDS")
+m_5_clust_zero_neg_hclust <- readRDS("model_forest_data.RDS")
 setwd("~/R_Projects/Reproductive Traits")
@@
   geom_point(size = 1.2, position = position_dodge(width = 0.9), alpha=1) +
-  theme_bw()+ ylab("Nº of visits per plant taxa") + xlab("Plant reproductive groups")+
+  theme_bw()+ ylab("Nº of visits per plant taxa") + xlab("Plant functional groups")+
   geom_point(data = d_5_1,aes(x = Clusters, y = (Interaction+1)),size = 1.2, position = position_jitterdodge(dodge.width = 0.9,   jitter.width = 0.2), alpha=0.2)+
@@
 ```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=9, fig.width=13}
+library(ggplot2)
+library(brms)
+library(png)
+library(grid)
+library(grid)
+library(gridExtra)
+
+setwd("~/Dropbox/PhD/R") #DROPBOX, files too large for github
+model_forest_data <- readRDS("model_forest_data.RDS")
+setwd("~/R_Projects/Reproductive Traits")
+d_5_1 <- read.csv("Data/Csv/d_5_1_brms_all_5_clusters.csv")
+#Visits
+ce_1 <- conditional_effects(model_forest_data, effects = "Clusters:guild",points=T) 
+#change colnames in model output to use same aesthetics
+#if not gg seems to don't like it
+colnames(ce_1[[1]])[4] <- "a"
+colnames(ce_1[[1]])[10] <- "Interaction"
+ce_1[[1]][10]<- ce_1[[1]][10]+1
+ce_1[[1]][12]<- ce_1[[1]][12]+1
+ce_1[[1]][13]<- ce_1[[1]][13]+1
+
+ce_1[[1]]$guild <- as.character(ce_1[[1]]$guild)
+
+ce_1[[1]]$guild[ce_1[[1]]$guild=="Bee"] <- "Bees"
+#Order levels
+ce_1[[1]]$guild <- factor(ce_1[[1]]$guild, levels = c("Bees","Non-bee-Hymenoptera","Syrphids","Non-syrphids-diptera","Lepidoptera","Coleoptera","Other_insects"))
+d_5_1$guild <- factor(d_5_1$guild, levels = c("Bees","Non-bee-Hymenoptera","Syrphids","Non-syrphids-diptera","Lepidoptera","Coleoptera","Other_insects"))
+#plot model
+ggplot(ce_1[[1]], aes(x = Clusters, y = Interaction, colour = as.factor(guild), group = 
+                        as.factor(guild))) +
+  geom_point(size = 1.2, position = position_dodge(width = 0.8), alpha=1) +
+  theme_bw()+ ylab("Nº of visits per plant taxa") + xlab("Plant reproductive groups")+
+  geom_errorbar(data=ce_1[[1]],mapping=aes(x=Clusters, ymin=lower__, ymax=upper__,colour = as.factor(guild), group = 
+                                             as.factor(guild)), width=.6,alpha=0.8, size = 0.9,position = position_dodge(width = 0.8)) +
+  scale_color_manual("Floral visitors guilds",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black","grey"))+ylim(0,30)
+
+#Bumblebee image credit to Melissa Broussard
+```

### 2021-03-11 Scripts/7_A_Analysis_Visitation_Guilds_FunctionalG.R

@@ -25,7 +25,7 @@ library(ggplot2)
 #1) READ DATA
 ########################################################################################################################################################
 setwd("~/R_Projects/Reproductive Traits")
-d_5 <- read.csv("Data/Csv/quantitative_networks_Z_scores_with_traits_and_5_clusters_hclust_famd.csv", row.names = 1)
+d_5 <- read.csv("Data/Csv/quantitative_networks_Z_scores_with_traits_and_5_clusters_hclust_forest_data.csv", row.names = 1)
 ########################################################################################################################################################
 #2) PHYLOGENETIC DISTANCE OF THE SPECIES
 ########################################################################################################################################################
@@ -35,23 +35,10 @@ d_5$Family_all <- as.character(d_5$Family_all)
 d_5$Genus_all <- as.character(d_5$Genus_all)
 d_5$Species_all <- as.character(d_5$Species_all)
 
-#These species are not present for analysis in the matrix, remove or model cannot have phylo as covariable
-d_5$Species_all[d_5$Species_all=="Diospyros seychellarum"] <- NA
-d_5$Species_all[d_5$Species_all=="Memecylon eleagni"] <- NA
-d_5$Species_all[d_5$Species_all=="Ocotea laevigata"] <- NA
-d_5$Species_all[d_5$Species_all=="Soulamea terminaloides"] <- NA
-
-#Make these NA's as NA
-d_5$Species_all[d_5$Species_all=="NA"] <- NA
-d_5$Family_all[d_5$Family_all=="NA"] <- NA
-d_5$Genus_all[d_5$Genus_all=="NA"] <- NA
-#remove NA's
-d_5_1 <- d_5[!is.na(d_5$Family_all),]
-d_5_1 <- d_5[!is.na(d_5$Species_all),]
-d_5_1 <- d_5[!is.na(d_5$Genus_all),]
+d_5_1$Family_all[d_5_1$Plant_species=="Beta maritima"] <- "Amaranthaceae"
 
 #prepare dataframe to calculate tree
-phylo_5 <- as.data.frame(cbind(d_5_1$Family_all, d_5_1$Genus_all, d_5_1$Species_all))
+phylo_5 <- as.data.frame(cbind(d_5_1$Family_all, d_5_1$Genus_all, d_5_1$Plant_species))
 colnames(phylo_5) <-  c("family", "genus", "species")
 
 #Select unique cases
@@ -73,7 +60,7 @@ rownames(A_5) <- gsub("_", " ", rownames(A_5))
[…]

### 2021-03-15 Rmd/PPCA_Complete_Cases.Rmd
plots supplementary

--- 2021-03-11 Rmd/PPCA_plot_1.Rmd
@@
 #Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-dat_cleaning_5_nectar <- readRDS("Data/RData/data_subset_nectar.rds")
-phyl_pca_forest_nectar <- readRDS("Data/RData/phyl_pca_forest_nectar_all.rds")
+phyl_pca_forest_complete_cases <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")
 #CALL the output PC for simplicity
-PC <- phyl_pca_forest
+PC <- phyl_pca_forest_complete_cases
 #CHECK CONTENT
@@
   dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-   dat$Nectar <- factor(dat$Nectar, levels = c("Presence","Absence"))
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("grey", "black"))
+
+  plot <- plot + geom_point(data=dat, aes(x, -y),size=2, colour="grey")
 
@@
   # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
 
   #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
 
@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
+  plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,5.35,5,7.5,6.5,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
                           label = PCAloadings$Variables, color="black",size=5)

### 2021-03-15 Rmd/PPCA_Qualitative_Vars.Rmd
plots supplementary

@@
 #Load data
-dat_cleaning_5 <- readRDS("Data/RData/Data_for_plotting_qualitative_pca_vars.rds")
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca.rds")
 phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.165, 0.1)) + ggtitle("D)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.165, 0.1)) + ggtitle("F)")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.163, 0.115)) + ggtitle("F)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.163, 0.115)) + ggtitle("D)")
 
@@
 library(cowplot)
- plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Flower_sym(PC),Flower_sha(PC),Breeding_syst(PC), ncol=2,nrow=3,  align = "v")
+ plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC), ncol=2,nrow=3,  align = "v")
 

### 2021-03-15 Rmd/PPCA_Subset_Nectar.Rmd
plots supplementary

--- 2021-03-09 Rmd/PPCA_plot.Rmd
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=6, fig.width=16}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8}
 
@@
 #Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
 dat_cleaning_5_nectar <- readRDS("Data/RData/data_subset_nectar.rds")
@@
 #CALL the output PC for simplicity
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("#fc2847", "#1cac78"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),")","%", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-  plot <- plot + theme(panel.grid.minor = element_blank(),panel.grid.major = element_blank(),
-                       panel.border = element_rect(linetype = "solid", colour = "black", size=1))
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
-                          label = PCAloadings$Variables, color="black",size=5)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.07, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-#all_spp(PC)
 
@@
   dat$Nectar[dat$Nectar=="no"] <- "Absence"
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("#fc2847", "#1cac78"))
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("grey", "black"))
   # plot <- plot +geom_point(data=dat, aes(-x, -y, colour = density),size=0.65,shape = 1,colour = "black",alpha=0.8)
@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(6,5.35,5,6,6,6,6)), y = -(PCAloadings$PC2*c(5.75,5,4.75,5.75,5.8,5.5,6)),
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(6,5.35,5.2,6,6,6,6)), y = -(PCAloadings$PC2*c(5.75,5,4.3,5.75,5.8,5.5,6)),
                           label = PCAloadings$Variables, color="black",size=5)
@@
 
-library(cowplot)
- plot_grid(all_spp(phyl_pca_forest),nectar_subset(phyl_pca_forest_nectar), ncol=2,  align = "h")
+nectar_subset(phyl_pca_forest_nectar)
 

### 2021-03-15 Scripts/3_2_PPCA_Complete_Cases.R

@@ -103,12 +103,13 @@ phyl_pca_forest_complete_cases <- phyl.pca(phylo_output, final_d,method="lambda"
 ####
 #SAVE PHYLO PCA OUTPUT
 ####
-#saveRDS(phyl_pca_famd, "Data/RData/phyl_pca_famd.rds")
 saveRDS(phyl_pca_forest_complete_cases, "Data/RData/phyl_pca_forest_complete_cases.rds")
+saveRDS(dat_cleaning_5, "Data/RData/data_complete_cases.rds")
 
 ####
 #READ DATA
 ####
+
 phyl_pca_forest_complete_cases <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")
 
 
@@ -157,7 +158,7 @@ PCbiplot <- function(PC, x="PC1", y="PC2") {
   dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
   dat$Nectar[dat$Nectar=="yes"] <- "Presence"
   dat$Nectar[dat$Nectar=="no"] <- "Absence"
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=0.65)+scale_color_manual(values=c("#fc2847", "#1cac78")) #+ #scale_color_viridis_c(option = "A", direction = 1, limits = c(min(dat$density), max(dat$density)))+
+  plot <- plot + geom_point(data=dat, aes(x, -y, colour=Nectar),size=0.65)+scale_color_manual(values=c("#fc2847", "#1cac78")) #+ #scale_color_viridis_c(option = "A", direction = 1, limits = c(min(dat$density), max(dat$density)))+
   # plot <- plot +geom_point(data=dat, aes(-x, -y, colour = density),size=0.65,shape = 1,colour = "black",alpha=0.8)
   
   ########
@@ -173,7 +174,7 @@ PCbiplot <- function(PC, x="PC1", y="PC2") {
                       v2 = .5 * mult * (get(y))
   )
   # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="brown4")
[…]

### 2021-03-15 Rmd/PPCA_clusters.Rmd
funct. plot

--- 2021-03-11 Rmd/PPCA_plot_1.Rmd
@@
   dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-   dat$Nectar <- factor(dat$Nectar, levels = c("Presence","Absence"))
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("grey", "black"))
+  dat$Clusters <- dat_cleaning_5$Clusters
+ dat$Clusters <- as.factor(dat_cleaning_5$Clusters)
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Clusters),size=2)#+scale_color_manual(values=c("grey", "black"))
 

### 2021-03-15 Rmd/Plant_Functional_Groups.Rmd
funct. plot

--- 2020-12-14 Scripts/7_1_Visualize_Plant_Functional_Groups/7_plots.Rmd
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=6}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=6}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-#######################################################################################################################################
- plot_grid(breeding,Compatibility,Selfing,Flower_morphology,Flower_symmetry,life_form,lifespan, nrow = 7,align = 'v')
+library(cowplot)
+ #Plant height
+ p1 <- ggplot(t, aes(x = Clusters, y = log(IMPUTED_plant_height_mean_m)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
+ binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Plant height)")+geom_boxplot(width=0.1)+
+ theme(legend.position = "none")
+ #Flower size
+ p2 <- ggplot(t, aes(x = Clusters, y = log(Floral_unit_width)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
+ binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Flower size)")+geom_boxplot(width=0.1)+
+ theme(legend.position = "none")
+ #Ovule number
+ p3 <- ggplot(t, aes(x = Clusters, y = log(OVULES_IMPUTED)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
+ binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Ovules per flower)")+geom_boxplot(width=0.1)+
+ theme(legend.position = "none")
+ #Style length
+ p4 <- ggplot(t, aes(x = Clusters, y = log(STYLE_IMPUTED)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
+ binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Style length)")+geom_boxplot(width=0.1)+
+ theme(legend.position = "none")
+ #Flowers per plant
+ p5 <- ggplot(t, aes(x = Clusters, y = log(Flowers_per_plant)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
+ binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Flowers per plant)")+geom_boxplot(width=0.1)+
+ theme(legend.position = "none")
+ #Flowers per plant
+ p6 <- ggplot(t, aes(x = Clusters, y = Autonomous_selfing_level_fruit_set))+ geom_violin(aes(color = Clusters, fill = Clusters), 
+ binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Selfing)")+geom_boxplot(width=0.1)+
+ theme(legend.position = "none")
+
+#Load libraries
+#LOAD LIBRARIES
+library(phytools)
+library(ape) #for phylogenetic distance
+library(dplyr) #data processing
+library(rtrees) #for phylogenetic distancelibrary(MASS)
+library(reshape2)
+library(viridis) #COLOUR GGPLOT
+library(MASS)
+library(ggplot2)
+library(broman) #crayon colours
+
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+      theme(text=element_text(color="black"),
+            axis.title=element_text( size = rel(1.3)),
+            axis.text=element_text(size = rel(2), color = "black"),
+            legend.title=element_text(face="bold"),
+            legend.text=element_text(),
+            legend.background=element_rect(fill="transparent"),
+            legend.key.size = unit(0.9, 'lines'),
+            panel.border=element_rect(color="black",size=1),
+            panel.grid.minor.x =element_blank(),
+            panel.grid.minor.y= element_blank(),
+             panel.grid.major= element_blank()
+      ))
+}
+
+#Load data
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca.rds")
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+PC <- phyl_pca_forest
+#CHECK CONTENT
+#EIGENVALUES
+PC$Eval
+#PC score (POINTS)
+PC$S
+#PC loadings (ARROWS)
+PC$L
+
+#############################################################################################################################################################
+#COMPATIBILITY
+#############################################################################################################################################################
+#Load plots
+all_spp <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+  dat$Clusters <- dat_cleaning_5$Clusters
+ dat$Clusters <- as.factor(dat_cleaning_5$Clusters)
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Clusters),size=2)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "#009E73"))
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .75 * mult * (get(x)),
+                      v2 = .75 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+
+   #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+ # plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),")","%", sep = "")) #XLAB
+  #plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+  #plot <- plot + theme(panel.grid.minor = element_blank(),panel.grid.major = element_blank(),
+   #                    panel.border = element_rect(linetype = "solid", colour = "black", size=1))
+
+  #ADD LABELS
+  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
+                          label = PCAloadings$Variables, color="black",size=5)
+
+  #CHANGE THEME
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.07, 0.11)) +ggtitle("") +xlab("")+ylab("")
+
+  plot
+
+}
+
+p1 <- plot_grid(all_spp(PC))
+
+#p3 <- PCbiplot(PC)
+
+p2 <- plot_grid(breeding,Compatibility,Flower_morphology,Flower_symmetry,life_form,lifespan,
+        nrow = 3,ncol=2,align = 'h')
+
+plot_grid(p1,p2,ncol=1)
+
+#top <- plot_grid(p1,p2,p3,p4,p5,p6, nrow = 2,ncol=3,align = 'v')
+
+#plot_grid(top,bottom,nrow = 2)
 

### 2021-03-16 Figures/Graphical_Summary_Funtional_Groups.Rmd
preparing all figures

---
title: ""
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=13}

library(dplyr)
library(ggplot2)
library(cowplot)

##########################################
#Visualization of plant functional groups#
##########################################
setwd("~/R_Projects/Reproductive Traits")

#LOAD DATA
#read unscaled trait data in order to visualize better the clusters
d <- read.csv("Data/Csv/all_species_imputed_trait_data.csv")
#read trait data with clusters
#I'll select the column of clusters and include it on the non standardize trait data
hclust_d_5 <- read.csv("Data/Csv/imputed_trait_data_hclust_5_clusters.csv") #5 clusters
#No add the cluster columns (it has the same order)
d$Clusters <- as.factor(hclust_d_5$Clusters)

#select columns of interest
t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
         "IMPUTED_plant_height_mean_m", "Clusters")]

#convert character to factors
t[sapply(t, is.character)] <- lapply(t[sapply(t, is.character)], 
                                       as.factor)

#Exploratory summary of the data
summ_clusters <- t  %>% group_by(Clusters) %>% do(the_summary = summary(.))
summ_clusters$the_summary

#######################
#Qualitative variables#
#######################

#######################################################################################################
#Calculate counts per group of breeding system
breeding <- t  %>%group_by(Breeding_system, Clusters) %>%summarise(counts = n()) 
#Calculate percentage of these counts
breeding <- group_by(breeding, Clusters) %>% mutate(percent = counts/sum(counts)*100)
#Organise levels
breeding$Breeding_system <- factor(breeding$Breeding_system, levels=c("Dioecious","Monoecious","Hermaphrodite"))

#Plot BREEDING SYSTEM
p1 <- ggplot(breeding, aes(x = Clusters, y = percent)) +
  geom_bar(
  aes( fill = Breeding_system),
  stat = "identity", position = position_stack()) +theme_classic()+ylab("Percentage")+
  scale_fill_manual(values=c("black","orange","forestgreen"),name = "Breeding system")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
  legend.title = element_text(face="bold"))+guides(fill=guide_legend(title.position = "top"))+xlab("")

#######################################################################################################
#Calculate counts per group of breeding system
Compatibility <- t  %>%group_by(IMPUTED_Compatibility, Clusters) %>%summarise(counts = n()) 
Compatibility$IMPUTED_Compatibility <- as.character(Compatibility$IMPUTED_Compatibility)
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="dioecious"] <- "Unisexual f."
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="monoecious"] <- "Unisexual f."
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="self_incompatible"] <- "Self inc."
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self com."
Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="self_compatible"] <- "Self com."

#Calculate percentage of these counts
Compatibility <- group_by(Compatibility, Clusters) %>% mutate(percent = counts/sum(counts)*100)
#Organise levels

Compatibility$IMPUTED_Compatibility <- factor(Compatibility$IMPUTED_Compatibility, levels=c("Unisexual f.","Self inc.", "Partially self com.",
                                                                                            "Self com."))
#Plot Compatibility
p2 <- ggplot(Compatibility, aes(x = Clusters, y = percent)) +
  geom_bar(
  aes( fill = IMPUTED_Compatibility),
  stat = "identity", position = position_stack()) +theme_classic()+ylab("Percentage")+
  scale_fill_manual(values=c("gray7", "orange","cyan4","deepskyblue2"),name = "Compatibility system")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-0,-10,-10,0),
  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top"))+xlab("")
#######################################################################################################
#Calculate counts per group of Life form
life_form <- t  %>%group_by(life_form, Clusters) %>%summarise(counts = n()) 
life_form$life_form <- as.character(life_form$life_form)
life_form$life_form [life_form$life_form =="vine"] <- "Shrub"
life_form$life_form [life_form$life_form =="tree"] <- "Tree"
life_form$life_form [life_form$life_form =="herb"] <- "Herb"
life_form$life_form [life_form$life_form =="shrub"] <- "Shrub"

#Calculate percentage of these counts
life_form <- group_by(life_form, Clusters) %>% mutate(percent = counts/sum(counts)*100)
#Organise levels
life_form$life_form <- factor(life_form$life_form, levels=c("Tree","Shrub", "Herb"))
#Plot Compatibility
p3 <- ggplot(life_form, aes(x = Clusters, y = percent)) +
  geom_bar(
  aes( fill = life_form),
  stat = "identity", position = position_stack()) +theme_classic()+ylab("Percentage")+
  scale_fill_manual(values=c("gray7", "darkorange2","forestgreen"),name = "Life form")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
  legend.title = element_text(face="bold"))+guides(fill=guide_legend(title.position = "top"))+xlab("")
#######################################################################################################
#Calculate counts per group of Life span
lifespan <- t  %>%group_by(lifespan, Clusters) %>%summarise(counts = n()) 
#Calculate percentage of these counts
lifespan <- group_by(lifespan, Clusters) %>% mutate(percent = counts/sum(counts)*100)
#Organise levels
lifespan$lifespan <- factor(lifespan$lifespan, levels=c("Perennial","Short lived"))
#Plot Compatibility
p4 <- ggplot(lifespan, aes(x = Clusters, y = percent)) +
  geom_bar(
  aes( fill = lifespan),
  stat = "identity", position = position_stack()) +theme_classic()+ylab("Percentage")+
  scale_fill_manual(values=c("sienna4","forestgreen"),name = "Life span")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top"))+xlab("")
#######################################################################################################
#Calculate counts per group of Flower symmetry
Flower_symmetry <- t  %>%group_by(Flower_symmetry, Clusters) %>%summarise(counts = n()) 
#Calculate percentage of these counts
Flower_symmetry <- group_by(Flower_symmetry, Clusters) %>% mutate(percent = counts/sum(counts)*100)
Flower_symmetry$Flower_symmetry <- as.character(Flower_symmetry$Flower_symmetry)
Flower_symmetry$Flower_symmetry [Flower_symmetry$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
Flower_symmetry$Flower_symmetry [Flower_symmetry$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
#Organise levels
Flower_symmetry$Flower_symmetry <- factor(Flower_symmetry$Flower_symmetry, levels=c("Actinomorphic","Zygomorphic"))
#Plot Compatibility
p5 <- ggplot(Flower_symmetry, aes(x = Clusters, y = percent)) +
  geom_bar(
  aes( fill = Flower_symmetry),
  stat = "identity", position = position_stack()) +theme_classic()+ylab("Percentage")+
  scale_fill_manual(values=c("sienna2","purple"),name = "Flower symmetry")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
  legend.title = element_text(face="bold"))+guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top"))+xlab("")
#######################################################################################################
#Calculate counts per group of Flower shape
Flower_morphology <- t  %>%group_by(Flower_morphology, Clusters) %>%summarise(counts = n()) 
levels(Flower_morphology$Flower_morphology)
Flower_morphology$Flower_morphology <- as.character(Flower_morphology$Flower_morphology)
Flower_morphology$Flower_morphology[Flower_morphology$Flower_morphology=="Funnelform"] <- "Campanulate"
Flower_morphology$Flower_morphology[Flower_morphology$Flower_morphology=="Spike"] <- "Brush"

#Calculate percentage of these counts
Flower_morphology <- group_by(Flower_morphology, Clusters) %>% mutate(percent = counts/sum(counts)*100)
#Plot Compatibility
p6 <- ggplot(Flower_morphology, aes(x = Clusters, y = percent)) +
  geom_bar(
  aes( fill = Flower_morphology),
  stat = "identity", position = position_stack()) +theme_classic()+ylab("Percentage")+
  scale_fill_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"),name = "Flower shape")+
  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=3,nrow=2,byrow=TRUE,title.position = "top"))+xlab("")

top <- plot_grid(p1,p2,p3,p4,p6,p5, ncol=3,nrow=2,  align = "h")

#######################################################################################################
#######################################################################################################
#######################################################################################################

########################
#Quantitative variables#
########################

#Plant height
pp1 <- ggplot(t, aes(x = Clusters, y = log(IMPUTED_plant_height_mean_m)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
  binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Plant height)")+geom_boxplot(width=0.1)+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))+xlab("")+ggtitle("Plant height")
#Flower size
pp2 <- ggplot(t, aes(x = Clusters, y = log(Floral_unit_width)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
   binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Flower size)")+geom_boxplot(width=0.1)+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))+xlab("")+ggtitle("Flower size")
#Ovule number
pp3 <- ggplot(t, aes(x = Clusters, y = log(OVULES_IMPUTED)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
  binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Ovules per flower)")+geom_boxplot(width=0.1)+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))+xlab("")+ggtitle("Ovule number")
#Style length
pp4 <- ggplot(t, aes(x = Clusters, y = log(STYLE_IMPUTED)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
  binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Style length)")+geom_boxplot(width=0.1)+
  theme(legend.position = "none",axis.title.x = element_text(face="bold"),plot.title = element_text(face = "bold"))+xlab("")+xlab("Plant functional groups")+
  ggtitle("Style length")
#Flowers per plant
pp5 <- ggplot(t, aes(x = Clusters, y = log(Flowers_per_plant)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
  binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Flowers per plant)")+geom_boxplot(width=0.1)+
  theme(legend.position = "none",axis.title.x = element_text(face="bold"),plot.title = element_text(face = "bold"))+xlab("Plant functional groups")+
  ggtitle("Flower number")
#Flowers per plant
pp6 <- ggplot(t, aes(x = Clusters, y = Autonomous_selfing_level_fruit_set))+ geom_violin(aes(color = Clusters, fill = Clusters), 
  binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Selfing)")+geom_boxplot(width=0.1)+
  theme(legend.position = "none",axis.title.x = element_text(face="bold"),plot.title = element_text(face = "bold"))+xlab("Plant functional groups")+
  ggtitle("Selfing")

bottom <- plot_grid(pp1,pp2,pp3,pp4,pp6,pp5, ncol=3,nrow=2,  align = "v")

plot_grid(top, bottom,nrow=2, align = "hv")

```

### 2021-03-16 Figures/PPCA_Plant_Functional_Groups.Rmd
preparing all figures

---
title: ""
output: pdf_document
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10}
setwd("~/R_Projects/Reproductive Traits")

#Load libraries
#LOAD LIBRARIES
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(cowplot)
# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.2)),
            axis.text=element_text(size = rel(1.75), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(1.2, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
             panel.grid.major= element_blank()
      ))
}

#Load data
dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_CLUSTERS.rds")
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")

PC <- phyl_pca_forest
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots
all_spp <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Clusters <- dat_cleaning_5$Clusters
 dat$Clusters <- as.factor(dat_cleaning_5$Clusters)
  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Clusters),size=2.5)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "darkgreen"))+ labs(color='Functional groups')

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.4, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

   #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

 # plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),")","%", sep = "")) #XLAB
  #plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
  #plot <- plot + theme(panel.grid.minor = element_blank(),panel.grid.major = element_blank(),
   #                    panel.border = element_rect(linetype = "solid", colour = "black", size=1))

  #ADD LABELS
  rownames(PC$L) <- c("SELFING", "FLOWER N.", "FLOWER SIZE", "STYLE LENGTH", "OVULE N.", "PLANT HEIGHT" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5.2,5,7,5.8,6.5)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=5)

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("") +xlab("")+ylab("")

  plot

}

plot_grid(all_spp(PC))

```

### 2021-03-16 Figures/PPCA_Qualitative_Vars.Rmd
preparing all figures

--- 2021-03-15 Rmd/PPCA_Qualitative_Vars.Rmd
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=13, fig.width=11}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=17, fig.width=17}
 
@@
 library(broman) #crayon colours
+library(cowplot)
 
@@
 
-library(cowplot)
- plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC), ncol=2,nrow=3,  align = "v")
+#############################################################################################################################################################
+#Nectar
+#############################################################################################################################################################
+#Load plots
+Nectar <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
+  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
+  dat$Nectar[dat$Nectar=="no"] <- "Absence"
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=1.5)+scale_color_manual(values=c("black","grey"))
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .75 * mult * (get(x)),
+                      v2 = .75 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
+
+  #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+
+  #ADD LABELS
+  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
+                          label = PCAloadings$Variables, color="black",size=3.2)
+
+  #CHANGE THEME
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)")
+
+  plot
+
+}
+
+ #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")
+
+  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),NULL,Nectar(PC),NULL, ncol=3,nrow=3,  align = "hv")
 

### 2021-03-16 Scripts/4_1_Visualize_Plant_Functional_Groups/7_plots.Rmd
preparing all figures

--- 2020-12-14 Scripts/7_1_Visualize_Plant_Functional_Groups/7_plots.Rmd
@@
 ---
-title: "Untitled"
+title: ""
 output: pdf_document
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=6}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=6, fig.width=15}
 setwd("~/R_Projects/Reproductive Traits")
@@
 #######################################################################################################################################
- plot_grid(breeding,Compatibility,Selfing,Flower_morphology,Flower_symmetry,life_form,lifespan, nrow = 7,align = 'v')
+ plot_grid(breeding,Compatibility,Selfing,Flower_morphology,Flower_symmetry,life_form,lifespan, nrow = 2,ncol=3,align = 'v')
+
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca.rds")
+
+#CALL the output PC for simplicity
+PC <- phyl_pca_forest
+#CHECK CONTENT
+#EIGENVALUES
+PC$Eval
+#PC score (POINTS)
+PC$S
+#PC loadings (ARROWS)
+PC$L
+
+PCbiplot <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+  dat$Clusters <- dat_cleaning_5$Clusters
+  dat$Clusters <- as.factor(dat$Clusters)
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Clusters),size=1.5)+scale_color_manual(values=c("blue", "purple","green","orange","red")) #+ #scale_color_viridis_c(option = "A", direction = 1, limits = c(min(dat$density), max(dat$density)))+
+  # plot <- plot +geom_point(data=dat, aes(-x, -y, colour = density),size=0.65,shape = 1,colour = "black",alpha=0.8)
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .5 * mult * (get(x)),
+                      v2 = .5 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="brown4")
+
+  #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),")","%", sep = "")) #XLAB
+  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+  plot <- plot + theme(panel.grid.minor = element_blank(),panel.grid.major = element_blank(),
+                       panel.border = element_rect(linetype = "solid", colour = "black", size=1))
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+
+  #ADD LABELS
+  rownames(PC$L) <- c("Selfing", "Flower Number", "Flower size", "Style Length", "Ovule Number", "Plant Height" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(3.5,4,4,4,4,4)), y = -(PCAloadings$PC2*c(3,4,4,4,4,4)),
+                          label = PCAloadings$Variables, color="black",size=5)
+
+  #CHANGE THEME
+
+  plot <- plot + theme_bw()
+
+  #CALCULATE KERNELS
+  #mv.kde <- kde2d(data[,1], data[,2], n = 400)
+  #dx <- diff(mv.kde$x[1:2])  # lifted from emdbook::HPDregionplot()
+  #dy <- diff(mv.kde$y[1:2])
+  #sz <- sort(mv.kde$z)
+  #c1 <- cumsum(sz) * dx * dy
+
+  # specify desired contour levels:
+  #prob <- c(0.5)
+  #prob_1 <- c(0.90)
+  # plot:
+  #dimnames(mv.kde$z) <- list(mv.kde$x,mv.kde$y)
+  #dc <- melt(mv.kde$z)
+
+  #dc$prob <- approx(sz,1-c1,dc$value)$y
+
+  #plot <- plot + geom_contour(data=dc, aes(x=-Var1,y=-Var2,z=prob),colour="brown4",breaks=prob)
+  # plot:
+  #dimnames(mv.kde$z) <- list(mv.kde$x,mv.kde$y)
+  #dc <- melt(mv.kde$z)
+
+  #dc$prob_1 <- approx(sz,1-c1,dc$value)$y
+  #plot <- plot + geom_contour(data=dc, aes(x=-Var1,y=-Var2,z=prob_1),colour="black",breaks=prob_1)
+
+  plot
+
+}
+
+p3 <- PCbiplot(PC)
+
+library(patchwork)
+
+p3 / (breeding | Compatibility)
 

### 2021-03-16 Scripts/3_PPCA.R

@@ -19,8 +19,9 @@ library(broman) #crayon colours
 ########################################################################################################################################################
 #read data with missing values filled by data imputation
 dat <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-#dat <- read.csv("Data/Csv/all_species_imputed_trait_data_famd_data.csv", row.names = "X")
+dat_1 <- read.csv("Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X") 
 
+dat$Clusters <- dat_1$Clusters
 ########################################################################################################################################################
 #2) Tidy up data to get phylo distance and conduct PCA
 ########################################################################################################################################################
@@ -36,7 +37,7 @@ dat <- dat[!dat$Species_all == "Soulamea terminaloides", ]
 ########################################################################################################################################################
 #3) REMOVE OUTLIERS, OUT OF 2.5-97.5 RANGE
 ########################################################################################################################################################
-dat_cleaning <- dat[,c(2,3,4,8,11,14,16,17,20,21)]
+dat_cleaning <- dat[,c(2,3,4,8,11,14,16,17,20,22)]
 
 dat_cleaning_1 <- dat_cleaning %>%
   filter(between(Flowers_per_plant, quantile(Flowers_per_plant, 0.025), quantile(Flowers_per_plant, 0.975)))
@@ -235,5 +236,104 @@ PCbiplot <- function(PC, x="PC1", y="PC2") {
 }
 
 PCbiplot(PC)
+
+########################################################################################################################################################
+#4) PLOT PPCA BY CLUSTERS
[…]

### 2021-03-16 Scripts/4_1_Visualize_Plant_Functional_Groups/4_1_Visualize_Plant_Functional_Groups.R

@@ -210,6 +210,16 @@ ggplot(df, aes(x = Clusters, y = counts)) +
     stat = "identity", position = position_dodge(0.8),
     width = 0.7
   )+scale_fill_viridis(discrete = T)+theme_classic()
+
+
+
+
+
+
+
+
+
+
 ########################################################################################################################################################
 #Now plot the quantitative data
 ########################################################################################################################################################

### 2021-03-16 Scripts/4_1_Visualize_Plant_Functional_Groups/Funct_g.R

@@ -1,0 +1,194 @@
+##########################################
+#Visualization of plant functional groups#
+##########################################
+
+#LOAD DATA
+#read unscaled trait data in order to visualize better the clusters
+d <- read.csv("Data/Csv/all_species_imputed_trait_data.csv")
+#read trait data with clusters
+#I'll select the column of clusters and include it on the non standardize trait data
+hclust_d_5 <- read.csv("Data/Csv/imputed_trait_data_hclust_5_clusters.csv") #5 clusters
+#No add the cluster columns (it has the same order)
+d$Clusters <- as.factor(hclust_d_5$Clusters)
+
+
+#select columns of interest
+t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
+         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
+         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
+         "IMPUTED_plant_height_mean_m", "Clusters")]
+
+
+#convert character to factors
+t[sapply(t, is.character)] <- lapply(t[sapply(t, is.character)], 
+                                       as.factor)
+
+
+#Exploratory summary of the data
+summ_clusters <- t  %>% group_by(Clusters) %>% do(the_summary = summary(.))
+summ_clusters$the_summary
+
+#######################
+#Qualitative variables#
+#######################
+
+#######################################################################################################
+#Calculate counts per group of breeding system
+breeding <- t  %>%group_by(Breeding_system, Clusters) %>%summarise(counts = n()) 
+#Calculate percentage of these counts
+breeding <- group_by(breeding, Clusters) %>% mutate(percent = counts/sum(counts)*100)
+#Organise levels
+breeding$Breeding_system <- factor(breeding$Breeding_system, levels=c("Dioecious","Monoecious","Hermaphrodite"))
+
+#Plot BREEDING SYSTEM
+p1 <- ggplot(breeding, aes(x = Clusters, y = percent)) +
+  geom_bar(
+  aes( fill = Breeding_system),
+  stat = "identity", position = position_stack()) +theme_classic()+ylab("Percentage")+
[…]

### 2021-03-16 Scripts/ANALYSIS_PCA_LOADINGS.R

@@ -156,7 +156,7 @@ percentage <- round(diag(phyl_pca_2$Eval) / sum(phyl_pca_2$Eval) * 100, 2) #calc
 #save output
 #saveRDS(phyl_pca__method_C, "Data/RData/phyl_pca__method_C.rds")
 phyl_pca__method_C <- readRDS("Data/RData/phyl_pca__method_C.rds")
-
+phyl_pca__method_C$L
 #convert to dataframe
 phyl_pca <- data.frame(phyl_pca__method_C$S)
 #set same rownames
@@ -171,9 +171,10 @@ data <- read.csv("Data/Csv/metric_analysis_data_3rd_question.csv", row.names = 1
 #merge columns
 data_analysis2 <- merge(data, phyl_pca, by="Species")
 
-m1 <- lme4::lmer(d ~ PC1  +(1|Id), data=data_analysis2)
+m1 <- lme4::lmer(d ~ PC4  +(1|Id), data=data_analysis2)
 summary(m1)
 #visualizing the patterns
-jtools::effect_plot(m1, pred = PC2 , interval = TRUE, plot.points = TRUE)
+jtools::effect_plot(m1, pred = PC4 , interval = TRUE, plot.points = TRUE)
+
 
 percentage <- round(diag(phyl_pca_2$Eval) / sum(phyl_pca_2$Eval) * 100, 2) #calculate percentage

### 2021-03-17 Figures/Dendogram_Functional_Groups.Rmd
preparing figs

---
title: ""
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10}

library(dendextend)
library(ggplot2)

#Dendrogram of clusters

setwd("~/R_Projects/Reproductive Traits")

e.clust_5 <- readRDS("Data/RData/clustering_output.RDS")

newggplot.ggdend <- function (data, segments = TRUE, labels = TRUE, nodes = TRUE, 
                              horiz = FALSE, theme = theme_dendro(), offset_labels = 0, ...) {
  data <- prepare.ggdend(data)
  #angle <- ifelse(horiz, 0, 90)
  #hjust <- ifelse(horiz, 0, 1)
  p <- ggplot()
  if (segments) {
    p <- p + geom_segment(data = data$segments, aes_string(x = "x", y = "y", xend = "xend", yend = "yend", colour = "col", linetype = "lty", size = "lwd"), lineend = "square") + 
      guides(linetype = FALSE, col = FALSE) + scale_colour_identity() + 
      scale_size_identity() + scale_linetype_identity()
  }
  if (nodes) {
    p <- p + geom_point(data = data$nodes, aes_string(x = "x", y = "y", colour = "col", shape = "pch", size = "cex")) + 
      guides(shape = FALSE, col = FALSE, size = FALSE) + 
      scale_shape_identity()
  }
  if (labels) {
    data$labels$cex <- 5 * data$labels$cex
    data$labels$y <- data$labels$y + offset_labels
    p <- p + geom_text(data = data$labels, aes_string(x = "x", y = "y", label = "label", colour = "col", size = "cex", angle = "angle", hjust = "hjust", vjust = "vjust"))#edited
  }
  if (horiz) {
    p <- p + coord_flip() + scale_y_reverse(expand = c(0.2, 0))
  }
  if (!is.null(theme)) {
    p <- p + theme
  }
  p
}

assignInNamespace(x = "ggplot.ggdend", ns = "dendextend", value = newggplot.ggdend)

dendro <- as.dendrogram(e.clust_5)

gdend <- dendextend::as.ggdend(dendro %>%
                                 set('branches_k_color', k = 5) %>%
                                 set('branches_lwd', 0.25) %>%
                                 set('labels_colors', k = 5) %>%
                                 set('labels_cex', 0.037),
                               theme = theme_minimal(),
                               horiz = TRUE)
gdend$labels$angle <- seq(90, -270, length = nrow(gdend$labels))
gdend$labels$vjust <- cos(gdend$labels$angle * pi) / (180)
gdend$labels$hjust <- sin(gdend$labels$angle * pi) / (180)

ggplot(gdend,offset_labels=-0.05) + theme(panel.grid.major = element_blank(),axis.text = element_blank(),
axis.title = element_blank())+ coord_polar(theta = 'x') +  scale_y_reverse(expand = c(0.025, 0))

```

### 2021-03-17 Figures/Figure_Brms_Model.Rmd
preparing figs

---
title: ''
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=22}

library(dplyr) #data processing
library(brms)
library(cmdstanr)
library(ggplot2)
library(cowplot)

# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(1.3)),
           axis.text=element_text(size = rel(2), color = "black"),
           legend.title=element_text(face="bold"),
           legend.text=element_text(),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(0.9, 'lines'),
           panel.border=element_rect(color="black",size=1),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank()
     ))
}

#Set working directory
setwd("~/Dropbox/PhD/R") #DROPBOX, just need to run the analysis script to produce it but takes too long to have it here
#Load data
model_forest_data <- readRDS("model_forest_data.RDS")
m_5_clust_zero_neg_hclust_bees <- readRDS("m_5_clust_zero_neg_hclust_bees.RDS")

#Set working directory
setwd("~/R_Projects/Reproductive Traits")
#Load data
d_5_1 <- readRDS("Data/Csv/data_model.RDS")

ce_1 <- conditional_effects(model_forest_data, effects = "Clusters:guild",points=T) 
#change colnames in model output to use same aesthetics
#if not gg seems to don't like it
colnames(ce_1[[1]])[4] <- "a"
colnames(ce_1[[1]])[10] <- "Interaction"
ce_1[[1]][10]<- ce_1[[1]][10]+1
ce_1[[1]][12]<- ce_1[[1]][12]+1
ce_1[[1]][13]<- ce_1[[1]][13]+1

ce_1[[1]]$guild <- as.character(ce_1[[1]]$guild)

ce_1[[1]]$guild[ce_1[[1]]$guild=="Bee"] <- "Bees"
#Order levels
ce_1[[1]]$guild <- factor(ce_1[[1]]$guild, levels = c("Bees","Non-bee-Hymenoptera","Syrphids","Non-syrphids-diptera","Lepidoptera","Coleoptera","Other_insects"))
d_5_1$guild <- factor(d_5_1$guild, levels = c("Bees","Non-bee-Hymenoptera","Syrphids","Non-syrphids-diptera","Lepidoptera","Coleoptera","Other_insects"))
#plot model
p1 <- ggplot(ce_1[[1]], aes(x = Clusters, y = Interaction, colour = as.factor(guild), group = 
  as.factor(guild))) + geom_point(size = 1.5, position = position_dodge(width = 0.75), alpha=1) +
  theme_ms() + ylab("Nº of visits per plant taxa") + xlab("Plant functional groups") +
  geom_errorbar(data=ce_1[[1]],mapping=aes(x=Clusters, ymin=lower__, ymax=upper__,colour = as.factor(guild), group = 
  as.factor(guild)), width=.8,alpha=0.8, size = 1.4,position = position_dodge(width = 0.75)) +
  scale_color_manual("Floral visitors\nfunctional groups",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black","grey")) + ylim(0,30)

setwd("~/Dropbox/PhD/R") #DROPBOX, just need to run the analysis script to produce it but takes too long to have it here

d_5_1 <- readRDS("data_model_just_bees.RDS")

ce_1 <- conditional_effects(m_5_clust_zero_neg_hclust_bees, effects = "Clusters:bee_family",points=T) 
#change colnames in model output to use same aesthetics
#if not gg seems to don't like it
colnames(ce_1[[1]])[4] <- "a"
colnames(ce_1[[1]])[10] <- "Interaction"
ce_1[[1]][10]<- ce_1[[1]][10]+1

p2 <- ggplot(ce_1[[1]], aes(x = Clusters, y = Interaction, colour = as.factor(bee_family), group = 
  as.factor(bee_family))) + geom_point(size = 1.5, position = position_dodge(width = 0.75), alpha=1) +
  theme_ms() + ylab("Nº of visits per plant taxa") + xlab("Plant functional groups") +
  geom_errorbar(data=ce_1[[1]],mapping=aes(x=Clusters, ymin=lower__, ymax=upper__,colour = as.factor(bee_family), group = 
  as.factor(bee_family)), width=.8,alpha=0.8, size = 1.4,position = position_dodge(width = 0.75)) +
  scale_color_manual("Bees\nfunctional groups",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black")) + ylim(0,75)

########################################################################################################################################################

plot_grid(p1,p2, align = "hv")

```

### 2021-03-17 Figures/Graphical_Summary_Funtional_Groups.Rmd
preparing figs

@@
 setwd("~/R_Projects/Reproductive Traits")
+##########################################
+#Visualization of plant functional groups#
+##########################################
 
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           plot.title = element_text(size = 10, face = "bold"),
+           axis.title=element_text( size = rel(1)),
+           axis.text=element_text(size = rel(0.9), color = "black"),
+           legend.title=element_text(face="bold",size = 10),
+           legend.text=element_text(),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(0.9, 'lines'),
+           panel.border=element_rect(color="black",size=1),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank()
+     ))
+}
 #LOAD DATA
@@
 #Plot BREEDING SYSTEM
-p1 <- ggplot(breeding, aes(x = Clusters, y = percent)) +
+p1 <- ggplot(breeding, aes(x = percent, y = Clusters)) +
   geom_bar(
-  aes( fill = Breeding_system),
-  stat = "identity", position = position_stack()) +theme_classic()+ylab("Percentage")+
-  scale_fill_manual(values=c("black","orange","forestgreen"),name = "Breeding system")+
+  aes( fill = Breeding_system),alpha=0.85,
+  stat = "identity", position = position_stack()) +theme_ms()+xlab("")+
+  scale_fill_manual(values=c("black","orange","forestgreen"),name = "a) Breeding system")+
   theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
-  legend.title = element_text(face="bold"))+guides(fill=guide_legend(title.position = "top"))+xlab("")
+  legend.title = element_text(face="bold"))+guides(fill=guide_legend(title.position = "top")) +ylab("Functional groups")
 
@@
 #Plot Compatibility
-p2 <- ggplot(Compatibility, aes(x = Clusters, y = percent)) +
+p2 <- ggplot(Compatibility, aes(x = percent, y = Clusters)) +
   geom_bar(
-  aes( fill = IMPUTED_Compatibility),
-  stat = "identity", position = position_stack()) +theme_classic()+ylab("Percentage")+
-  scale_fill_manual(values=c("gray7", "orange","cyan4","deepskyblue2"),name = "Compatibility system")+
+  aes( fill = IMPUTED_Compatibility),alpha=0.85,
+  stat = "identity", position = position_stack()) +theme_ms()+xlab("")+
+  scale_fill_manual(values=c("gray7", "orange","cyan4","deepskyblue2"),name = "b) Compatibility system")+
   theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-0,-10,-10,0),
-  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top"))+xlab("")
+  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top")) +ylab("")
 #######################################################################################################
@@
 #Plot Compatibility
-p3 <- ggplot(life_form, aes(x = Clusters, y = percent)) +
+p3 <- ggplot(life_form, aes(x = percent, y = Clusters)) +
   geom_bar(
-  aes( fill = life_form),
-  stat = "identity", position = position_stack()) +theme_classic()+ylab("Percentage")+
-  scale_fill_manual(values=c("gray7", "darkorange2","forestgreen"),name = "Life form")+
+  aes( fill = life_form),alpha=0.85,
+  stat = "identity", position = position_stack()) +theme_ms()+xlab("")+
+  scale_fill_manual(values=c("gray7", "darkorange2","forestgreen"),name = "c) Life form")+
   theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
-  legend.title = element_text(face="bold"))+guides(fill=guide_legend(title.position = "top"))+xlab("")
+  legend.title = element_text(face="bold"))+guides(fill=guide_legend(title.position = "top"))+ylab("")
 #######################################################################################################
@@
 #Plot Compatibility
-p4 <- ggplot(lifespan, aes(x = Clusters, y = percent)) +
+p4 <- ggplot(lifespan, aes(x = percent, y = Clusters)) +
   geom_bar(
-  aes( fill = lifespan),
-  stat = "identity", position = position_stack()) +theme_classic()+ylab("Percentage")+
-  scale_fill_manual(values=c("sienna4","forestgreen"),name = "Life span")+
+  aes( fill = lifespan),alpha=0.85,
+  stat = "identity", position = position_stack()) +theme_ms()+xlab("Percentage")+
+  scale_fill_manual(values=c("sienna4","forestgreen"),name = "d) Life span")+
   theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
-  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top"))+xlab("")
+  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top")) + ylab("Functional groups")
 #######################################################################################################
@@
 #Plot Compatibility
-p5 <- ggplot(Flower_symmetry, aes(x = Clusters, y = percent)) +
+p5 <- ggplot(Flower_symmetry, aes(x = percent, y = Clusters)) +
   geom_bar(
-  aes( fill = Flower_symmetry),
-  stat = "identity", position = position_stack()) +theme_classic()+ylab("Percentage")+
-  scale_fill_manual(values=c("sienna2","purple"),name = "Flower symmetry")+
+  aes( fill = Flower_symmetry),alpha=0.85,
+  stat = "identity", position = position_stack()) +theme_ms()+xlab("Percentage")+
+  scale_fill_manual(values=c("sienna2","purple"),name = "f) Flower symmetry")+
   theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
-  legend.title = element_text(face="bold"))+guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top"))+xlab("")
+  legend.title = element_text(face="bold"))+guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top"))+ylab("")
 #######################################################################################################
@@
 #Plot Compatibility
-p6 <- ggplot(Flower_morphology, aes(x = Clusters, y = percent)) +
+p6 <- ggplot(Flower_morphology, aes(x = percent, y = Clusters)) +
   geom_bar(
-  aes( fill = Flower_morphology),
-  stat = "identity", position = position_stack()) +theme_classic()+ylab("Percentage")+
-  scale_fill_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"),name = "Flower shape")+
+  aes( fill = Flower_morphology),alpha=0.85,
+  stat = "identity", position = position_stack()) +theme_ms()+xlab("Percentage")+
+  scale_fill_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"),name = "e) Flower shape")+
   theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
-  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=3,nrow=2,byrow=TRUE,title.position = "top"))+xlab("")
+  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=3,nrow=2,byrow=TRUE,title.position = "top"))+ylab("")
 
 top <- plot_grid(p1,p2,p3,p4,p6,p5, ncol=3,nrow=2,  align = "h")
+
+# now add the title
+title <- ggdraw() + 
+  draw_label(
+    "Qualitative variables",
+    fontface = 'bold',
+    x = 0,
+    hjust = 0
+  ) +
+  theme(
+    # add margin on the left of the drawing canvas,
+    # so title is aligned with left edge of first plot
+    plot.margin = margin(0, 0, 0, 7)
+  )
+
+top_1 <- plot_grid(title,top,ncol = 1,rel_heights = c(0.1, 1))
 
@@
 
+########################
+#Try density plots#
+########################
+
 #Plant height
-pp1 <- ggplot(t, aes(x = Clusters, y = log(IMPUTED_plant_height_mean_m)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
-  binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Plant height)")+geom_boxplot(width=0.1)+
-  theme(legend.position = "none",plot.title = element_text(face = "bold"))+xlab("")+ggtitle("Plant height")
+pp1 <- ggplot(t, aes(x  = log(IMPUTED_plant_height_mean_m), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
+  ylab("Density") + xlab("log(Plant height)") + ggtitle("g) Plant height")  + ylab("Functional groups")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+
 #Flower size
-pp2 <- ggplot(t, aes(x = Clusters, y = log(Floral_unit_width)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
-   binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Flower size)")+geom_boxplot(width=0.1)+
-  theme(legend.position = "none",plot.title = element_text(face = "bold"))+xlab("")+ggtitle("Flower size")
+pp2 <- ggplot(t, aes(x  = log(Floral_unit_width), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
+  ylab("") + xlab("log(Flower size)") + ggtitle("h) Flower size") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+
 #Ovule number
-pp3 <- ggplot(t, aes(x = Clusters, y = log(OVULES_IMPUTED)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
-  binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Ovules per flower)")+geom_boxplot(width=0.1)+
-  theme(legend.position = "none",plot.title = element_text(face = "bold"))+xlab("")+ggtitle("Ovule number")
+pp3 <- ggplot(t, aes(x  = log(OVULES_IMPUTED), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
+  ylab("") + xlab("log(Ovule number)") +  ggtitle("i) Ovule number") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+
 #Style length
-pp4 <- ggplot(t, aes(x = Clusters, y = log(STYLE_IMPUTED)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
-  binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Style length)")+geom_boxplot(width=0.1)+
-  theme(legend.position = "none",axis.title.x = element_text(face="bold"),plot.title = element_text(face = "bold"))+xlab("")+xlab("Plant functional groups")+
-  ggtitle("Style length")
+pp4 <- ggplot(t, aes(x  = log(STYLE_IMPUTED), fill=Clusters)) +geom_density(alpha=0.3)+theme_ms()+theme(legend.position = "none")+
+  ylab("Density") + xlab("log(Style length)") +  ggtitle("j) Style length") + ylab("Functional groups")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+
 #Flowers per plant
-pp5 <- ggplot(t, aes(x = Clusters, y = log(Flowers_per_plant)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
-  binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Flowers per plant)")+geom_boxplot(width=0.1)+
-  theme(legend.position = "none",axis.title.x = element_text(face="bold"),plot.title = element_text(face = "bold"))+xlab("Plant functional groups")+
-  ggtitle("Flower number")
-#Flowers per plant
-pp6 <- ggplot(t, aes(x = Clusters, y = Autonomous_selfing_level_fruit_set))+ geom_violin(aes(color = Clusters, fill = Clusters), 
-  binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Selfing)")+geom_boxplot(width=0.1)+
-  theme(legend.position = "none",axis.title.x = element_text(face="bold"),plot.title = element_text(face = "bold"))+xlab("Plant functional groups")+
-  ggtitle("Selfing")
+pp5 <- ggplot(t, aes(x  = log(Flowers_per_plant), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
+  ylab("") + xlab("log(Flower number)") +  ggtitle("k) Flower number") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
 
-bottom <- plot_grid(pp1,pp2,pp3,pp4,pp6,pp5, ncol=3,nrow=2,  align = "v")
+#Selfing
+pp6 <- ggplot(t, aes(x  = Autonomous_selfing_level_fruit_set, fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
+  ylab("") + xlab("Selfing") +  ggtitle("l) Selfing") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
 
-plot_grid(top, bottom,nrow=2, align = "hv")
+#For legend
+pp7 <- ggplot(t, aes(x  = Autonomous_selfing_level_fruit_set, fill=Clusters)) +geom_density(alpha=0.2)+
+  ylab("Density") + xlab("Selfing")+theme(legend.position="bottom",legend.direction="horizontal") + guides(fill=guide_legend(title="Functional groups"))+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+
+#Extract legend
+legend_b <- get_legend(
+  pp7 + 
+    guides(color = guide_legend(nrow = 1)) +theme(legend.position="bottom",legend.direction="horizontal")
+)
+
+#generate panel of plots
+bottom <- plot_grid(pp1,pp2,pp3,pp4,pp5,pp6, ncol=3,nrow=2,  align = "hv")
+#add legend
+bottom_1 <- plot_grid(bottom,legend_b,ncol = 1, rel_heights = c(1, .1))
+
+# now add the title
+title <- ggdraw() + 
+  draw_label(
+    "Quantitative variables",
+    fontface = 'bold',
+    x = 0,
+    hjust = 0
+  ) +
+  theme(
+    # add margin on the left of the drawing canvas,
+    # so title is aligned with left edge of first plot
+    plot.margin = margin(0, 0, 0, 7)
+  )
+#add title
+bottom_2 <- plot_grid(title,bottom_1,ncol = 1,rel_heights = c(0.1, 1))
+
+####         ####
+#### P L O T ####
+####         ####
+
+plot_grid(top_1, bottom_2,nrow=2, align = "hv")
 

### 2021-03-17 Scripts/4_1_Visualize_Plant_Functional_Groups/Funct_g.R

@@ -2,6 +2,26 @@
 #Visualization of plant functional groups#
 ##########################################
 
+library(cowplot)
+library(ggplot2)
+
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           plot.title = element_text(size = 10, face = "bold"),
+           axis.title=element_text( size = rel(1)),
+           axis.text=element_text(size = rel(0.9), color = "black"),
+           legend.title=element_text(face="bold",size = 10),
+           legend.text=element_text(),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(0.9, 'lines'),
+           panel.border=element_rect(color="black",size=1),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank()
+     ))
+}
 #LOAD DATA
 #read unscaled trait data in order to visualize better the clusters
 d <- read.csv("Data/Csv/all_species_imputed_trait_data.csv")
@@ -41,13 +61,13 @@ breeding <- group_by(breeding, Clusters) %>% mutate(percent = counts/sum(counts)
 breeding$Breeding_system <- factor(breeding$Breeding_system, levels=c("Dioecious","Monoecious","Hermaphrodite"))
 
 #Plot BREEDING SYSTEM
-p1 <- ggplot(breeding, aes(x = Clusters, y = percent)) +
+p1 <- ggplot(breeding, aes(x = percent, y = Clusters)) +
   geom_bar(
-  aes( fill = Breeding_system),
-  stat = "identity", position = position_stack()) +theme_classic()+ylab("Percentage")+
-  scale_fill_manual(values=c("black","orange","forestgreen"),name = "Breeding system")+
+  aes( fill = Breeding_system),alpha=0.90,
+  stat = "identity", position = position_stack()) +theme_ms()+xlab("")+
+  scale_fill_manual(values=c("black","orange","forestgreen"),name = "a) Breeding system")+
   theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
[…]

### 2021-03-18 Figures/Graphical_Summary_Funtional_Groups.Rmd
Minor edits on plots labelling

@@
 library(cowplot)
-
 ##########################################
@@
 #read unscaled trait data in order to visualize better the clusters
-d <- read.csv("Data/Csv/all_species_imputed_trait_data.csv")
+d <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv")
 #read trait data with clusters
 #I'll select the column of clusters and include it on the non standardize trait data
-hclust_d_5 <- read.csv("Data/Csv/imputed_trait_data_hclust_5_clusters.csv") #5 clusters
+hclust_d_5 <- read.csv("Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv") #5 clusters
 #No add the cluster columns (it has the same order)
@@
 
+breeding$Clusters <- as.character(breeding$Clusters)
+
+breeding$Clusters[breeding$Clusters=="1"] <- "A"
+breeding$Clusters[breeding$Clusters=="2"] <- "B"
+breeding$Clusters[breeding$Clusters=="3"] <- "C"
+breeding$Clusters[breeding$Clusters=="4"] <- "D"
+breeding$Clusters[breeding$Clusters=="5"] <- "E"
+
+breeding$Clusters <- factor(breeding$Clusters, levels=c("E","D","C", "B", "A"))
+
 #Plot BREEDING SYSTEM
@@
 
-Compatibility$IMPUTED_Compatibility <- factor(Compatibility$IMPUTED_Compatibility, levels=c("Unisexual f.","Self inc.", "Partially self com.",
-                                                                                            "Self com."))
+Compatibility$IMPUTED_Compatibility <- factor(Compatibility$IMPUTED_Compatibility, levels=c("Unisexual f.","Self inc.", "Partially self com.",  "Self com."))
+
+Compatibility$Clusters <- as.character(Compatibility$Clusters)
+
+Compatibility$Clusters[Compatibility$Clusters=="1"] <- "A"
+Compatibility$Clusters[Compatibility$Clusters=="2"] <- "B"
+Compatibility$Clusters[Compatibility$Clusters=="3"] <- "C"
+Compatibility$Clusters[Compatibility$Clusters=="4"] <- "D"
+Compatibility$Clusters[Compatibility$Clusters=="5"] <- "E"
+
+Compatibility$Clusters <- factor(Compatibility$Clusters, levels=c("E","D","C", "B", "A"))
 #Plot Compatibility
@@
 #Plot Compatibility
+
+life_form$Clusters <- as.character(life_form$Clusters)
+
+life_form$Clusters[life_form$Clusters=="1"] <- "A"
+life_form$Clusters[life_form$Clusters=="2"] <- "B"
+life_form$Clusters[life_form$Clusters=="3"] <- "C"
+life_form$Clusters[life_form$Clusters=="4"] <- "D"
+life_form$Clusters[life_form$Clusters=="5"] <- "E"
+
+life_form$Clusters <- factor(life_form$Clusters, levels=c("E","D","C", "B", "A"))
+
 p3 <- ggplot(life_form, aes(x = percent, y = Clusters)) +
@@
 lifespan$lifespan <- factor(lifespan$lifespan, levels=c("Perennial","Short lived"))
+
+lifespan$Clusters <- as.character(lifespan$Clusters)
+
+lifespan$Clusters[lifespan$Clusters=="1"] <- "A"
+lifespan$Clusters[lifespan$Clusters=="2"] <- "B"
+lifespan$Clusters[lifespan$Clusters=="3"] <- "C"
+lifespan$Clusters[lifespan$Clusters=="4"] <- "D"
+lifespan$Clusters[lifespan$Clusters=="5"] <- "E"
+
+lifespan$Clusters <- factor(lifespan$Clusters, levels=c("E","D","C", "B", "A"))
+
 #Plot Compatibility
@@
 Flower_symmetry$Flower_symmetry <- factor(Flower_symmetry$Flower_symmetry, levels=c("Actinomorphic","Zygomorphic"))
+
+Flower_symmetry$Clusters <- as.character(Flower_symmetry$Clusters)
+
+Flower_symmetry$Clusters[Flower_symmetry$Clusters=="1"] <- "A"
+Flower_symmetry$Clusters[Flower_symmetry$Clusters=="2"] <- "B"
+Flower_symmetry$Clusters[Flower_symmetry$Clusters=="3"] <- "C"
+Flower_symmetry$Clusters[Flower_symmetry$Clusters=="4"] <- "D"
+Flower_symmetry$Clusters[Flower_symmetry$Clusters=="5"] <- "E"
+
+Flower_symmetry$Clusters <- factor(Flower_symmetry$Clusters, levels=c("E","D","C", "B", "A"))
+
 #Plot Compatibility
@@
 Flower_morphology <- group_by(Flower_morphology, Clusters) %>% mutate(percent = counts/sum(counts)*100)
+
+Flower_morphology$Clusters <- as.character(Flower_morphology$Clusters)
+
+Flower_morphology$Clusters[Flower_morphology$Clusters=="1"] <- "A"
+Flower_morphology$Clusters[Flower_morphology$Clusters=="2"] <- "B"
+Flower_morphology$Clusters[Flower_morphology$Clusters=="3"] <- "C"
+Flower_morphology$Clusters[Flower_morphology$Clusters=="4"] <- "D"
+Flower_morphology$Clusters[Flower_morphology$Clusters=="5"] <- "E"
+
+Flower_morphology$Clusters <- factor(Flower_morphology$Clusters, levels=c("E","D","C", "B", "A"))
+
 #Plot Compatibility
@@
 #For legend
+t$Clusters <- as.character(t$Clusters)
+
+t$Clusters[t$Clusters=="1"] <- "A"
+t$Clusters[t$Clusters=="2"] <- "B"
+t$Clusters[t$Clusters=="3"] <- "C"
+t$Clusters[t$Clusters=="4"] <- "D"
+t$Clusters[t$Clusters=="5"] <- "E"
+
+t$Clusters <- factor(t$Clusters, levels=c("A", "B", "C", "D", "E"))
+
 pp7 <- ggplot(t, aes(x  = Autonomous_selfing_level_fruit_set, fill=Clusters)) +geom_density(alpha=0.2)+

### 2021-03-18 Tables/Table_Summary_Functional_Groups.Rmd
Minor edits on plots labelling

---
title: ""
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}

setwd("~/R_Projects/Reproductive Traits")

library(cowplot)
library(ggplot2)
library(tidyr)
library(dplyr)
library(reshape2)
library(data.table)
library(kableExtra)

#LOAD DATA
#read unscaled trait data in order to visualize better the clusters
d <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv")

dat_1 <- read.csv("Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")

d$Clusters <- dat_1$Clusters

#select columns of interest
t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]

##############################################################################################################################
#Prepare table qualitative variables
##############################################################################################################################

##############################################################################################################################
#Breeding system
t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))

#Summary to create table
breeding <- t %>%
  group_by(Clusters,Breeding_system) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

breeding <- breeding[,-3]

breeding <- spread(breeding, Clusters, Percentage)

colnames(breeding)[1] <- "Category"

Trait <- data.frame(Trait= c(rep("Breeding system", 3)))

Breeding_system <- cbind(Trait, breeding)

##############################################################################################################################
#Compatibility
t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Unisexual flower"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Unisexual flower"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"

t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Unisexual flower", "Self incompatible", "Partially self compatible", "Self compatible"))
#Summary to create table
comp <- t %>%
  group_by(Clusters,IMPUTED_Compatibility) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

comp <- comp[,-3]

comp <- spread(comp, Clusters, Percentage)
#Replace Na's with zeros
comp[is.na(comp)] <- 0
#Set call name os categories per trait
colnames(comp)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Compatibility system", 4)))
#Add column
Compatibility_system <- cbind(Trait, comp)

############################################################################################################################################
#Life form
t$life_form <- as.character(t$life_form)
t$life_form[t$life_form =="vine"] <- "Shrub"
t$life_form[t$life_form =="tree"] <- "Tree"
t$life_form[t$life_form =="herb"] <- "Herb"
t$life_form[t$life_form =="shrub"] <- "Shrub"
#Order levels
t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
#Summary to create table
life_form <- t %>%
  group_by(Clusters,life_form) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
life_form <- life_form[,-3]
#convert to wide
life_form <- spread(life_form, Clusters, Percentage)
#Set call name os categories per trait
colnames(life_form)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Life form", 3)))
#Add column
Life_form<- cbind(Trait, life_form)

############################################################################################################################################
t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
#Summary to create table
life_span <- t %>%
  group_by(Clusters,lifespan) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
life_span <- life_span[,-3]
#convert to wide
life_span <- spread(life_span, Clusters, Percentage)
#Set call name os categories per trait
colnames(life_span)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Life span", 2)))
#Add column
Life_span<- cbind(Trait, life_span)

############################################################################################################################################
t$Flower_morphology <- as.character(t$Flower_morphology)
t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"

Flower_morphology <- t %>%
  group_by(Clusters,Flower_morphology) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
Flower_morphology <- Flower_morphology[,-3]
#convert to wide
Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
#Set call name os categories per trait
colnames(Flower_morphology)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
#Add column
Flower_morphology<- cbind(Trait, Flower_morphology)
#Replace Na's with zeros
Flower_morphology[is.na(Flower_morphology)] <- 0

############################################################################################################################################
t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"

Flower_symmetry <- t %>%
  group_by(Clusters,Flower_symmetry) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
Flower_symmetry <- Flower_symmetry[,-3]
#convert to wide
Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
#Set call name os categories per trait
colnames(Flower_symmetry)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
#Add column
Flower_symmetry<- cbind(Trait, Flower_symmetry)
############################################################################################################################################

t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"

#Order levels
t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))

Selfing <- t %>%
  group_by(Clusters,Autonomous_selfing_level) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

#delete column to convert to wide
Selfing <- Selfing[,-3]
#convert to wide
Selfing <- spread(Selfing, Clusters, Percentage)
#Set call name os categories per trait
colnames(Selfing)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
#Replace Na's with zeros
Selfing[is.na(Selfing)] <- 0
#Add column
Selfing_1 <- cbind(Trait, Selfing)

############################################################################################################################################

t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"

Nectar <- t %>%
  group_by(Clusters,Nectar_presence_absence) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

#delete column to convert to wide
Nectar <- Nectar[,-3]
#convert to wide
Nectar <- spread(Nectar, Clusters, Percentage)
#Set call name os categories per trait
colnames(Nectar)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Nectar", 2)))
#Replace Na's with zeros
Nectar[is.na(Nectar)] <- 0
#Add column
Nectar <- cbind(Trait, Nectar)

##############################################################################################################################
#Prepare table quantitative variables
##############################################################################################################################

Selfing <-  t %>% group_by(Clusters)%>% 
  select(Autonomous_selfing_level_fruit_set) %>% # select variables to summarise
  summarise_each(funs(min = min,
                     # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                    sd = sd))

s1 <- as.data.frame(t(Selfing))
#set colnames
colnames(s1) <- c("1","2","3","4","5")
#remove the cluster row
s1 <- s1[-1,]
#convert rownames to 1st columns
s1 <- setDT(s1, keep.rownames = "TRUE")[]
colnames(s1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Autonomous selfing", 5)))
#Add column
Selfing <- cbind(Trait, s1)

##############################################################################################################################
flower_number <-  t %>% group_by(Clusters)%>% 
  select(Flowers_per_plant) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

f1 <- as.data.frame(t(flower_number))
#set colnames
colnames(f1) <- c("1","2","3","4","5")
#remove the cluster row
f1 <- f1[-1,]
#convert rownames to 1st columns
f1 <- setDT(f1, keep.rownames = "TRUE")[]
colnames(f1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Flower number", 5)))
#Add column
Flower_number <- cbind(Trait, f1)

##############################################################################################################################
Flowers_per_inflorescence <-  t %>% group_by(Clusters)%>% 
  select(Flowers_per_inflorescence) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

f_i_1 <- as.data.frame(t(Flowers_per_inflorescence))
#set colnames
colnames(f_i_1) <- c("1","2","3","4","5")
#remove the cluster row
f_i_1 <- f_i_1[-1,]
#convert rownames to 1st columns
f_i_1 <- setDT(f_i_1, keep.rownames = "TRUE")[]
colnames(f_i_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Flowers per inflorescence", 5)))
#Add column
Flower_per_inflo <- cbind(Trait, f_i_1)

##############################################################################################################################
Floral_unit_width <-  t %>% group_by(Clusters)%>% 
  select(Floral_unit_width) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

f_u_w_1 <- as.data.frame(t(Floral_unit_width))
#set colnames
colnames(f_u_w_1) <- c("1","2","3","4","5")
#remove the cluster row
f_u_w_1 <- f_u_w_1[-1,]
#convert rownames to 1st columns
f_u_w_1 <- setDT(f_u_w_1, keep.rownames = "TRUE")[]
colnames(f_u_w_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Inflorescence width", 5)))
#Add column
Inflo_width <- cbind(Trait, f_u_w_1)

##############################################################################################################################
Corolla_diameter_mean <-  t %>% group_by(Clusters)%>% 
  select(Corolla_diameter_mean) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

c_w_1 <- as.data.frame(t(Corolla_diameter_mean))
#set colnames
colnames(c_w_1) <- c("1","2","3","4","5")
#remove the cluster row
c_w_1 <- c_w_1[-1,]
#convert rownames to 1st columns
c_w_1 <- setDT(c_w_1, keep.rownames = "TRUE")[]
colnames(c_w_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Flower width", 5)))
#Add column
Flower_width <- cbind(Trait, c_w_1)

##############################################################################################################################
Corolla_length_mean <-  t %>% group_by(Clusters)%>% 
  select(Corolla_length_mean) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

c_l_1 <- as.data.frame(t(Corolla_length_mean))
#set colnames
colnames(c_l_1) <- c("1","2","3","4","5")
#remove the cluster row
c_l_1 <- c_l_1[-1,]
#convert rownames to 1st columns
c_l_1 <- setDT(c_l_1, keep.rownames = "TRUE")[]
colnames(c_l_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Flower length", 5)))
#Add column
Flower_length<- cbind(Trait, c_l_1)

##############################################################################################################################
STYLE_IMPUTED <-  t %>% group_by(Clusters)%>% 
  select(STYLE_IMPUTED) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

s_l_1 <- as.data.frame(t(STYLE_IMPUTED))
#set colnames
colnames(s_l_1) <- c("1","2","3","4","5")
#remove the cluster row
s_l_1 <- s_l_1[-1,]
#convert rownames to 1st columns
s_l_1 <- setDT(s_l_1, keep.rownames = "TRUE")[]
colnames(s_l_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Style length", 5)))
#Add column
Style_length<- cbind(Trait, s_l_1)

##############################################################################################################################

OVULES_IMPUTED <-  t %>% group_by(Clusters)%>% 
  select(OVULES_IMPUTED) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

o_n_1 <- as.data.frame(t(OVULES_IMPUTED))
#set colnames
colnames(o_n_1) <- c("1","2","3","4","5")
#remove the cluster row
o_n_1 <- o_n_1[-1,]
#convert rownames to 1st columns
o_n_1 <- setDT(o_n_1, keep.rownames = "TRUE")[]
colnames(o_n_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Ovule number", 5)))
#Add column
Ovule_number <- cbind(Trait, o_n_1)

##############################################################################################################################

IMPUTED_plant_height_mean_m <-  t %>% group_by(Clusters)%>% 
  select(IMPUTED_plant_height_mean_m) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

p_h_1 <- as.data.frame(t(IMPUTED_plant_height_mean_m))
#set colnames
colnames(p_h_1) <- c("1","2","3","4","5")
#remove the cluster row
p_h_1 <- p_h_1[-1,]
#convert rownames to 1st columns
p_h_1 <- setDT(p_h_1, keep.rownames = "TRUE")[]
colnames(p_h_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Plant height", 5)))
#Add column
Plant_height <- cbind(Trait, p_h_1)

#Bind quantitative and qualitative variables
Table_all_traits <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar,
          Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length, Ovule_number, Plant_height)

#Select just two decimals
is.num <- sapply(Table_all_traits, is.numeric)
Table_all_traits[is.num] <- lapply(Table_all_traits[is.num], round, 2)

colnames(Table_all_traits) <- c("Trait", "Category", "Cluster A", "Cluster B", "Cluster C", "Cluster D", "Cluster E")

kable(Table_all_traits, "latex", longtable = T)  %>% row_spec(0,bold=TRUE) %>% group_rows(index = setNames(rle(Table_all_traits$Trait)[[1]], rle(Table_all_traits$Trait)[[2]])) %>% kable_styling(font_size = 9)  %>% kable_styling(latex_options = c("repeat_header"))

```

### 2021-03-20 Figures/Graphical_Summary_Funtional_Groups.Rmd
Functional groups

@@
 pp1 <- ggplot(t, aes(x  = log(IMPUTED_plant_height_mean_m), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
-  ylab("Density") + xlab("log(Plant height)") + ggtitle("g) Plant height")  + ylab("Functional groups")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+  ylab("Density") + xlab("log(Plant height)") + ggtitle("g) Plant height")  + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
 
@@
 pp2 <- ggplot(t, aes(x  = log(Floral_unit_width), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
-  ylab("") + xlab("log(Flower size)") + ggtitle("h) Flower size") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+  ylab("") + xlab("log(Flower size)") + ggtitle("h) Flower size") + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
 
@@
 pp3 <- ggplot(t, aes(x  = log(OVULES_IMPUTED), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
-  ylab("") + xlab("log(Ovule number)") +  ggtitle("i) Ovule number") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+  ylab("") + xlab("log(Ovule number)") +  ggtitle("i) Ovule number") +scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
 
@@
 pp4 <- ggplot(t, aes(x  = log(STYLE_IMPUTED), fill=Clusters)) +geom_density(alpha=0.3)+theme_ms()+theme(legend.position = "none")+
-  ylab("Density") + xlab("log(Style length)") +  ggtitle("j) Style length") + ylab("Functional groups")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+  ylab("Density") + xlab("log(Style length)") +  ggtitle("j) Style length") + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
 
@@
 pp5 <- ggplot(t, aes(x  = log(Flowers_per_plant), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
-  ylab("") + xlab("log(Flower number)") +  ggtitle("k) Flower number") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+  ylab("") + xlab("log(Flower number)") +  ggtitle("k) Flower number") + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
 
@@
 pp6 <- ggplot(t, aes(x  = Autonomous_selfing_level_fruit_set, fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
-  ylab("") + xlab("Selfing") +  ggtitle("l) Selfing") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+  ylab("") + xlab("Selfing") +  ggtitle("l) Selfing") + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
 

### 2021-03-20 Figures/PPCA_Plant_Functional_Groups.Rmd
Edits

@@
   dat$Clusters <- dat_cleaning_5$Clusters
- dat$Clusters <- as.factor(dat_cleaning_5$Clusters)
+  dat$Clusters <- as.character(dat$Clusters)
+  dat$Clusters[dat$Clusters=="1"] <- "A"
+  dat$Clusters[dat$Clusters=="2"] <- "B"
+  dat$Clusters[dat$Clusters=="3"] <- "C"
+  dat$Clusters[dat$Clusters=="4"] <- "D"
+  dat$Clusters[dat$Clusters=="5"] <- "E"
+
+ dat$Clusters <- factor(dat$Clusters, levels=c("A", "B", "C", "D", "E"))
+
   plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Clusters),size=2.5)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "darkgreen"))+ labs(color='Functional groups')
@@
 
- # plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),")","%", sep = "")) #XLAB
-  #plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-  #plot <- plot + theme(panel.grid.minor = element_blank(),panel.grid.major = element_blank(),
-   #                    panel.border = element_rect(linetype = "solid", colour = "black", size=1))
+  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("") +xlab("")+ylab("")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
 

### 2021-03-22 Figures/BRMS_Metric_PPCA.Rmd
Preparing plots 4 and 5 from models

---
title: ""
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=17, fig.width=17}

library(brms)
library(cmdstanr)
library(cowplot) #panel of plots
library(ggplot2)
library(data.table)

# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(1.8)),
           axis.text=element_text(size = rel(1.5), color = "black"),
           legend.title=element_text(face="bold"),
           legend.text=element_text(),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(0.4, 'lines'),
           panel.border=element_rect(color="black",size=1),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank()
     ))
}

########################################################################################################################################################################
setwd("~/R_Projects/Reproductive Traits")

#LOAD DATA
data <- read.csv("Data/Csv/metric_analysis_data_3rd_question.csv", row.names = 1) # data with specialization and integer of visits
head(data) #Check data
#Now we obtain the loadings from the global PCA which is likely to define better in the trait space the species
phyl_pca_2 <- readRDS("Data/RData/phyl_pca_forest.rds")
########################################################################################################################################################################
#PROCESS DATA BEFORE MODELLING
pca_loadings_2 <- data.frame(phyl_pca_2$S)
#prepare cols for merging
rownames(pca_loadings_2) <- gsub("_", " ", rownames(pca_loadings_2)) #remove underscores from species names
#set same colnames for merging
pca_loadings_2 <- setDT(pca_loadings_2, keep.rownames = TRUE)[]
#same colname
colnames(pca_loadings_2)[1] <- "Species"
#check data for merge
head(data)
#merge columns
data_analysis2 <- merge(data, pca_loadings_2, by="Species")

setwd("~/Dropbox/PhD/R") #DROPBOX, files too large for github
#LOAD DATA
ce_1 <- readRDS("Visits_PC1.RDS")
ce_2 <- readRDS("Visits_PC2.RDS")
spe_1 <- readRDS("Specialization_PC1.RDS")
spe_2 <- readRDS("Specialization_PC2.RDS")

colnames(ce_1[[1]])[2] <- "Interaction"

Visits_PC1 <- ggplot(ce_1[[1]], aes(x = PC1, y = (estimate__+1))) + geom_point(data = data_analysis2,aes(x = PC1, y = Visits),
              size = 1.2, alpha=0.9) + geom_line(size=1.2) + ylim(0,quantile(data_analysis2$Visits, 0.95)) +theme_ms()+
              geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1) + ylab("Number of visits")

colnames(ce_2[[1]])[2] <- "Interaction"

Visits_PC2 <- ggplot(ce_2[[1]], aes(x = PC2, y = (estimate__+1))) + geom_point(data = data_analysis2,aes(x = PC2, y = Visits),
  size = 1.2, alpha=0.9) + geom_line(size=1.2) + ylim(0,quantile(data_analysis2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1) + ylab("Number of visits")

Specialization_PC1 <- ggplot(spe_1[[1]], aes(x = PC1, y = (estimate__))) + geom_point(data = data_analysis2,aes(x = PC1, y = d),
                      size = 1.2, alpha=0.9) + geom_line(size=1.2)  +theme_ms()+
                      geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1) + ylab("Specilization (d')")

Specialization_PC2 <- ggplot(spe_2[[1]], aes(x = PC2, y = (estimate__))) + geom_point(data = data_analysis2,aes(x = PC2, y = d),
                      size = 1.2, alpha=0.9) + geom_line(size=1.2)  +theme_ms()+
                      geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1) + ylab("Specilization (d')")

plot_grid(Visits_PC1,Visits_PC2,Specialization_PC1,Specialization_PC2)

```

### 2021-03-22 Figures/Graphical_Summary_Funtional_Groups.Rmd
Preparing plots 4 and 5 from models

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=13}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=17, fig.width=13}
 
@@
 library(cowplot)
+
 ##########################################
@@
          "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
-         "IMPUTED_plant_height_mean_m", "Clusters")]
+         "IMPUTED_plant_height_mean_m","Nectar_presence_absence", "Clusters")]
 
@@
 summ_clusters$the_summary
+
+#######################################################################################################
+#######################################################################################################
+#######################################################################################################
+
+########################
+#Quantitative variables#
+########################
+
+########################
+#Try density plots#
+########################
+
+#Plant height
+pp1 <- ggplot(t, aes(x  = log(IMPUTED_plant_height_mean_m), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
+  ylab("Density") + xlab("log(Plant height)") + ggtitle("a) Plant height")  + ylab("Functional groups")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+
+#Flower size
+pp2 <- ggplot(t, aes(x  = log(Floral_unit_width), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
+  ylab("") + xlab("log(Flower size)") + ggtitle("b) Flower size") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+
+#Ovule number
+pp3 <- ggplot(t, aes(x  = log(OVULES_IMPUTED), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
+  ylab("") + xlab("log(Ovule number)") +  ggtitle("c) Ovule number") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+
+#Style length
+pp4 <- ggplot(t, aes(x  = log(STYLE_IMPUTED), fill=Clusters)) +geom_density(alpha=0.3)+theme_ms()+theme(legend.position = "none")+
+  ylab("Density") + xlab("log(Style length)") +  ggtitle("d) Style length") + ylab("Functional groups")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+
+#Flowers per plant
+pp5 <- ggplot(t, aes(x  = log(Flowers_per_plant), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
+  ylab("") + xlab("log(Flower number)") +  ggtitle("e) Flower number") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+
+#Selfing
+pp6 <- ggplot(t, aes(x  = Autonomous_selfing_level_fruit_set, fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
+  ylab("") + xlab("Selfing") +  ggtitle("f) Selfing") + ylab("")+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+
+#For legend
+t$Clusters <- as.character(t$Clusters)
+
+t$Clusters[t$Clusters=="1"] <- "A"
+t$Clusters[t$Clusters=="2"] <- "B"
+t$Clusters[t$Clusters=="3"] <- "C"
+t$Clusters[t$Clusters=="4"] <- "D"
+t$Clusters[t$Clusters=="5"] <- "E"
+
+t$Clusters <- factor(t$Clusters, levels=c("A", "B", "C", "D", "E"))
+
+pp7 <- ggplot(t, aes(x  = Autonomous_selfing_level_fruit_set, fill=Clusters)) +geom_density(alpha=0.2)+
+  ylab("Density") + xlab("Selfing")+theme(legend.position="bottom",legend.direction="horizontal") + guides(fill=guide_legend(title="Functional groups"))+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
+
+#Extract legend
+legend_b <- get_legend(
+  pp7 + 
+    guides(color = guide_legend(nrow = 1)) +theme(legend.position="bottom",legend.direction="horizontal")
+)
+
+#generate panel of plots
+top <- plot_grid(pp1,pp2,pp3,pp4,pp5,pp6, ncol=3,nrow=2,  align = "hv")
+#add legend
+top_1 <- plot_grid(top,legend_b,ncol = 1, rel_heights = c(1, .1))
+
+# now add the title
+title <- ggdraw() + 
+  draw_label(
+    "Quantitative variables",
+    fontface = 'bold',
+    x = 0,
+    hjust = 0
+  ) +
+  theme(
+    # add margin on the left of the drawing canvas,
+    # so title is aligned with left edge of first plot
+    plot.margin = margin(0, 0, 0, 7)
+  )
+#add title
+top_2 <- plot_grid(title,top_1,ncol = 1,rel_heights = c(0.1, 1))
+
+####         ####
+#### P L O T ####
+####         ####
 
@@
     stat = "identity", position = position_stack()) +theme_ms()+xlab("")+
-  scale_fill_manual(values=c("black","orange","forestgreen"),name = "a) Breeding system")+
+  scale_fill_manual(values=c("black","orange","forestgreen"),name = "g) Breeding system")+
   theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
-                                                 legend.title = element_text(face="bold"))+guides(fill=guide_legend(title.position = "top")) +ylab("Functional groups")
+  legend.title = element_text(face="bold"))+guides(fill=guide_legend(title.position = "top",reverse = TRUE)) +ylab("Functional groups")
 
@@
 Compatibility$IMPUTED_Compatibility <- as.character(Compatibility$IMPUTED_Compatibility)
-Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="dioecious"] <- "Unisexual f."
-Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="monoecious"] <- "Unisexual f."
-Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="self_incompatible"] <- "Self inc."
-Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self com."
-Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="self_compatible"] <- "Self com."
+Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="dioecious"] <- "Unisexual flowers"
+Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="monoecious"] <- "Unisexual flowers"
+Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
+Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
+Compatibility$IMPUTED_Compatibility[Compatibility$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"
 
@@
 
-Compatibility$IMPUTED_Compatibility <- factor(Compatibility$IMPUTED_Compatibility, levels=c("Unisexual f.","Self inc.", "Partially self com.",  "Self com."))
+Compatibility$IMPUTED_Compatibility <- factor(Compatibility$IMPUTED_Compatibility, levels=c("Unisexual flowers","Self incompatible", "Partially self compatible",  "Self compatible"))
 
@@
     stat = "identity", position = position_stack()) +theme_ms()+xlab("")+
-  scale_fill_manual(values=c("gray7", "orange","cyan4","deepskyblue2"),name = "b) Compatibility system")+
+  scale_fill_manual(values=c("gray7", "orange","cyan4","deepskyblue2"),name = "h) Compatibility system")+
   theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-0,-10,-10,0),
-                                                 legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top")) +ylab("")
+  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top",reverse = TRUE)) +ylab("")
 #######################################################################################################
@@
     stat = "identity", position = position_stack()) +theme_ms()+xlab("")+
-  scale_fill_manual(values=c("gray7", "darkorange2","forestgreen"),name = "c) Life form")+
+  scale_fill_manual(values=c("gray7", "darkorange2","forestgreen"),name = "i) Life form")+
   theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
-                                                 legend.title = element_text(face="bold"))+guides(fill=guide_legend(title.position = "top"))+ylab("")
+                                                 legend.title = element_text(face="bold"))+guides(fill=guide_legend(title.position = "top",reverse = TRUE))+ylab("")
 #######################################################################################################
@@
     stat = "identity", position = position_stack()) +theme_ms()+xlab("Percentage")+
-  scale_fill_manual(values=c("sienna4","forestgreen"),name = "d) Life span")+
+  scale_fill_manual(values=c("sienna4","forestgreen"),name = "j) Life span")+
   theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
-                                                 legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top")) + ylab("Functional groups")
+                                                 legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top",reverse = TRUE)) + ylab("Functional groups")
 #######################################################################################################
@@
     stat = "identity", position = position_stack()) +theme_ms()+xlab("Percentage")+
-  scale_fill_manual(values=c("sienna2","purple"),name = "f) Flower symmetry")+
+  scale_fill_manual(values=c("sienna2","purple"),name = "l) Flower symmetry")+
   theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
-                                                 legend.title = element_text(face="bold"))+guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top"))+ylab("")
+  legend.title = element_text(face="bold"))+guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE,title.position = "top",reverse = TRUE))+ylab("")
 #######################################################################################################
@@
     stat = "identity", position = position_stack()) +theme_ms()+xlab("Percentage")+
-  scale_fill_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"),name = "e) Flower shape")+
+  scale_fill_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"),name = "k) Flower shape")+
   theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
-                                                 legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=3,nrow=2,byrow=TRUE,title.position = "top"))+ylab("")
+  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=3,nrow=2,byrow=TRUE,title.position = "top",reverse = TRUE))+ylab("")
 
-top <- plot_grid(p1,p2,p3,p4,p6,p5, ncol=3,nrow=2,  align = "h")
+#######################################################################################################
+#Plot Nectar
+#Calculate counts per group of Flower shape
+Nectar_presence_absence <- t  %>% group_by(Nectar_presence_absence, Clusters) %>%summarise(counts = n()) 
+levels(Nectar_presence_absence$Nectar_presence_absence)
+Nectar_presence_absence$Nectar_presence_absence <- as.character(Nectar_presence_absence$Nectar_presence_absence)
+Nectar_presence_absence$Nectar_presence_absence[Nectar_presence_absence$Nectar_presence_absence=="yes"] <- "Yes"
+Nectar_presence_absence$Nectar_presence_absence[Nectar_presence_absence$Nectar_presence_absence=="no"] <- "No"
+
+Nectar_presence_absence$Nectar_presence_absence <- factor(Nectar_presence_absence$Nectar_presence_absence, levels=c("No","Yes"))
+
+#Calculate percentage of these counts
+Nectar_presence_absence <- group_by(Nectar_presence_absence, Clusters) %>% mutate(percent = counts/sum(counts)*100)
+
+Nectar_presence_absence$Clusters <- as.character(Nectar_presence_absence$Clusters)
+
+Nectar_presence_absence$Clusters[Nectar_presence_absence$Clusters=="1"] <- "A"
+Nectar_presence_absence$Clusters[Nectar_presence_absence$Clusters=="2"] <- "B"
+Nectar_presence_absence$Clusters[Nectar_presence_absence$Clusters=="3"] <- "C"
+Nectar_presence_absence$Clusters[Nectar_presence_absence$Clusters=="4"] <- "D"
+Nectar_presence_absence$Clusters[Nectar_presence_absence$Clusters=="5"] <- "E"
+
+Nectar_presence_absence$Clusters <- factor(Nectar_presence_absence$Clusters, levels=c("E","D","C", "B", "A"))
+
+p7 <- ggplot(Nectar_presence_absence, aes(x = percent, y = Clusters)) +
+  geom_bar(
+    aes( fill = Nectar_presence_absence),alpha=0.85,
+    stat = "identity", position = position_stack()) +theme_ms()+xlab("Percentage")+
+  scale_fill_manual(values=c("black","darkorange"),name = "m) Nectar production")+
+  theme(legend.key.size = unit(0.2, 'cm'))+theme(legend.position="top",legend.justification='left',legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,0),
+  legend.title = element_text(face="bold"))+ guides(fill=guide_legend(ncol=3,nrow=2,byrow=TRUE,title.position = "top",reverse = TRUE))+ylab("")
+
+bottom <- plot_grid(p1,p2,p3,p4,p6,p5,NULL,p7,NULL, ncol=3,nrow=3,  align = "h")
 
@@
 
-top_1 <- plot_grid(title,top,ncol = 1,rel_heights = c(0.1, 1))
+bottom_1 <- plot_grid(title,bottom,ncol = 1,rel_heights = c(0.1, 1))
 
-#######################################################################################################
-#######################################################################################################
-#######################################################################################################
-
-########################
-#Quantitative variables#
-########################
-
-########################
-#Try density plots#
-########################
-
-#Plant height
-pp1 <- ggplot(t, aes(x  = log(IMPUTED_plant_height_mean_m), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
-  ylab("Density") + xlab("log(Plant height)") + ggtitle("g) Plant height")  + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
-
-#Flower size
-pp2 <- ggplot(t, aes(x  = log(Floral_unit_width), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
-  ylab("") + xlab("log(Flower size)") + ggtitle("h) Flower size") + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
-
-#Ovule number
-pp3 <- ggplot(t, aes(x  = log(OVULES_IMPUTED), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
-  ylab("") + xlab("log(Ovule number)") +  ggtitle("i) Ovule number") +scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
-
-#Style length
-pp4 <- ggplot(t, aes(x  = log(STYLE_IMPUTED), fill=Clusters)) +geom_density(alpha=0.3)+theme_ms()+theme(legend.position = "none")+
-  ylab("Density") + xlab("log(Style length)") +  ggtitle("j) Style length") + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
-
-#Flowers per plant
-pp5 <- ggplot(t, aes(x  = log(Flowers_per_plant), fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
-  ylab("") + xlab("log(Flower number)") +  ggtitle("k) Flower number") + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
-
-#Selfing
-pp6 <- ggplot(t, aes(x  = Autonomous_selfing_level_fruit_set, fill=Clusters)) +geom_density(alpha=0.2)+theme_ms()+theme(legend.position = "none")+
-  ylab("") + xlab("Selfing") +  ggtitle("l) Selfing") + scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
-
-#For legend
-t$Clusters <- as.character(t$Clusters)
-
-t$Clusters[t$Clusters=="1"] <- "A"
-t$Clusters[t$Clusters=="2"] <- "B"
-t$Clusters[t$Clusters=="3"] <- "C"
-t$Clusters[t$Clusters=="4"] <- "D"
-t$Clusters[t$Clusters=="5"] <- "E"
-
-t$Clusters <- factor(t$Clusters, levels=c("A", "B", "C", "D", "E"))
-
-pp7 <- ggplot(t, aes(x  = Autonomous_selfing_level_fruit_set, fill=Clusters)) +geom_density(alpha=0.2)+
-  ylab("Density") + xlab("Selfing")+theme(legend.position="bottom",legend.direction="horizontal") + guides(fill=guide_legend(title="Functional groups"))+scale_fill_manual(values=c("cyan4", "red","forestgreen","purple","gold"))
-
-#Extract legend
-legend_b <- get_legend(
-  pp7 + 
-    guides(color = guide_legend(nrow = 1)) +theme(legend.position="bottom",legend.direction="horizontal")
-)
-
-#generate panel of plots
-bottom <- plot_grid(pp1,pp2,pp3,pp4,pp5,pp6, ncol=3,nrow=2,  align = "hv")
-#add legend
-bottom_1 <- plot_grid(bottom,legend_b,ncol = 1, rel_heights = c(1, .1))
-
-# now add the title
-title <- ggdraw() + 
-  draw_label(
-    "Quantitative variables",
-    fontface = 'bold',
-    x = 0,
-    hjust = 0
-  ) +
-  theme(
-    # add margin on the left of the drawing canvas,
-    # so title is aligned with left edge of first plot
-    plot.margin = margin(0, 0, 0, 7)
-  )
-#add title
-bottom_2 <- plot_grid(title,bottom_1,ncol = 1,rel_heights = c(0.1, 1))
-
-####         ####
-#### P L O T ####
-####         ####
-
-plot_grid(top_1, bottom_2,nrow=2, align = "hv")
+plot_grid(top_2, bottom_1,nrow=2, align = "hv")
 

### 2021-03-22 Scripts/7_A_Analysis_Visitation_Guilds_FunctionalG.R

@@ -72,11 +72,10 @@ d_5_1$Clusters[d_5_1$Clusters=="5"] <- "E"
 
 d_5_1$Clusters <- as.factor(d_5_1$Clusters)
 levels(as.factor(d_5_1$Clusters))
-
+levels(factor(d_5_1$guild))
 
 #exclude other insects level
-d_5_1 <- d_5_1[d_5_1$guild!="Other_insects",]
-
+d_5_1 <- subset(d_5_1, guild!="Other_insects")
 #save data
 saveRDS(d_5_1, "Data/Csv/data_model.RDS")
 ########################################################################################################################################################
@@ -86,7 +85,7 @@ saveRDS(d_5_1, "Data/Csv/data_model.RDS")
 #5 clusters hclust
 model_forest_data <- brm((Interaction-1) ~ guild*Clusters + (1|Id) + (1|gr(phylo, cov = A)),
                             data = d_5_1, family  = zero_inflated_negbinomial(),data2 = list(A = A_5), cores = 4,chains = 4, 
-                            sample_prior = TRUE, warmup = 500, iter = 1500,
+                            sample_prior = TRUE, warmup = 500, iter = 2000,
                             control = list(adapt_delta = 0.99)) 
 
 marginal_effects(m_5_clust_zero_neg_hclust_famd, effects = "Clusters:guild")
@@ -104,12 +103,16 @@ ce <- conditional_effects(m_5_clust_zero_neg_hclust_famd, effects = "Clusters:gu
 ########################################################################################################################################################
 #SAVE MODEL 1
 setwd("~/Dropbox/PhD/R") #DROPBOX, files too large for github
-saveRDS(model_forest_data, "model_forest_data.RDS")
+#saveRDS(model_forest_data, "model_forest_data.RDS")
 ########################################################################################################################################################
 #4.2)PLOT OUTPUT VISITATION DATA
 ########################################################################################################################################################
 #read model 2
-m_5_clust_zero_neg_hclust_famd <- readRDS("model_forest_data.RDS")
+model_forest_data <- readRDS("model_forest_data.RDS")
+
+setwd("~/R_Projects/Reproductive Traits")
[…]

### 2021-03-23 Figures/Figure_Brms_Model.Rmd
edits to run in the other pc

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=22}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13}
 
+#LOAD LIBRARIES
+library(ape) #for phylogenetic distance
 library(dplyr) #data processing
+library(rtrees) #for phylogenetic distance
+library(DHARMa)
 library(brms)
@@
 library(ggplot2)
-library(cowplot)
 
-# Theme for publication
 theme_ms <- function(base_size=12, base_family="Helvetica") {
@@
      theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(1.3)),
-           axis.text=element_text(size = rel(2), color = "black"),
+           axis.title=element_text( size = rel(1.8)),
+           axis.text=element_text(size = rel(1.2), color = "black"),
            legend.title=element_text(face="bold"),
-           legend.text=element_text(),
+           legend.text=element_text(size = rel(1.2)),
            legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(0.9, 'lines'),
+           legend.key.size = unit(1, 'lines'),
            panel.border=element_rect(color="black",size=1),
@@
 
-#Set working directory
-setwd("~/Dropbox/PhD/R") #DROPBOX, just need to run the analysis script to produce it but takes too long to have it here
-#Load data
+setwd("~/Dropbox/PhD/R") #DROPBOX, files too large for github
+
 model_forest_data <- readRDS("model_forest_data.RDS")
-m_5_clust_zero_neg_hclust_bees <- readRDS("m_5_clust_zero_neg_hclust_bees.RDS")
 
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-#Load data
-d_5_1 <- readRDS("Data/Csv/data_model.RDS")
+dat <- readRDS("data_model.RDS")
 
+#cond effect model visitation data
 ce_1 <- conditional_effects(model_forest_data, effects = "Clusters:guild",points=T) 
@@
 
+#Order levels
 ce_1[[1]]$guild <- as.character(ce_1[[1]]$guild)
+ce_1[[1]]$guild <- factor(ce_1[[1]]$guild, levels = c("Bees","Non-bee-Hymenoptera","Syrphids","Non-syrphids-diptera","Lepidoptera","Coleoptera"))
+dat$guild <- as.character(dat$guild)
+dat$guild <- factor(dat$guild, levels = c("Bees","Non-bee-Hymenoptera","Syrphids","Non-syrphids-diptera","Lepidoptera","Coleoptera"))
 
-ce_1[[1]]$guild[ce_1[[1]]$guild=="Bee"] <- "Bees"
-#Order levels
-ce_1[[1]]$guild <- factor(ce_1[[1]]$guild, levels = c("Bees","Non-bee-Hymenoptera","Syrphids","Non-syrphids-diptera","Lepidoptera","Coleoptera","Other_insects"))
-d_5_1$guild <- factor(d_5_1$guild, levels = c("Bees","Non-bee-Hymenoptera","Syrphids","Non-syrphids-diptera","Lepidoptera","Coleoptera","Other_insects"))
 #plot model
-p1 <- ggplot(ce_1[[1]], aes(x = Clusters, y = Interaction, colour = as.factor(guild), group = 
-  as.factor(guild))) + geom_point(size = 1.5, position = position_dodge(width = 0.75), alpha=1) +
-  theme_ms() + ylab("Nº of visits per plant taxa") + xlab("Plant functional groups") +
+ggplot(ce_1[[1]], aes(x = Clusters, y = Interaction, colour = as.factor(guild), group = 
+  as.factor(guild))) +
+  geom_point(size = 2.4, position = position_dodge(width = 0.68), alpha=1) +
+  theme_ms()+ ylab("Nº of visits per plant taxa") + xlab("Plant functional groups")+
+  geom_point(data = dat,aes(x = Clusters, y = (Interaction),group = 
+  as.factor(guild)),size = 1.2,shape=21, position = position_jitterdodge(dodge.width = 0.68, jitter.width = 0.25), alpha=0.14)+
   geom_errorbar(data=ce_1[[1]],mapping=aes(x=Clusters, ymin=lower__, ymax=upper__,colour = as.factor(guild), group = 
-  as.factor(guild)), width=.8,alpha=0.8, size = 1.4,position = position_dodge(width = 0.75)) +
-  scale_color_manual("Floral visitors\nfunctional groups",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black","grey")) + ylim(0,30)
+  as.factor(guild)), width=0.6,alpha=1, size = 1,position = position_dodge(width = 0.68)) +ylim(0,quantile(dat$Interaction, 0.95))+
+  scale_color_manual("Floral visitors guilds",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black","grey"))
 
-setwd("~/Dropbox/PhD/R") #DROPBOX, just need to run the analysis script to produce it but takes too long to have it here
-
-d_5_1 <- readRDS("data_model_just_bees.RDS")
-
-ce_1 <- conditional_effects(m_5_clust_zero_neg_hclust_bees, effects = "Clusters:bee_family",points=T) 
-#change colnames in model output to use same aesthetics
-#if not gg seems to don't like it
-colnames(ce_1[[1]])[4] <- "a"
-colnames(ce_1[[1]])[10] <- "Interaction"
-ce_1[[1]][10]<- ce_1[[1]][10]+1
-
-p2 <- ggplot(ce_1[[1]], aes(x = Clusters, y = Interaction, colour = as.factor(bee_family), group = 
-  as.factor(bee_family))) + geom_point(size = 1.5, position = position_dodge(width = 0.75), alpha=1) +
-  theme_ms() + ylab("Nº of visits per plant taxa") + xlab("Plant functional groups") +
-  geom_errorbar(data=ce_1[[1]],mapping=aes(x=Clusters, ymin=lower__, ymax=upper__,colour = as.factor(bee_family), group = 
-  as.factor(bee_family)), width=.8,alpha=0.8, size = 1.4,position = position_dodge(width = 0.75)) +
-  scale_color_manual("Bees\nfunctional groups",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black")) + ylim(0,75)
-
-########################################################################################################################################################
-
-plot_grid(p1,p2, align = "hv")
+#Values over the percentile 95 were omitted for visualization purposes
 

### 2021-03-23 Scripts/3_PPCA.R

@@ -162,10 +162,8 @@ PCbiplot <- function(PC, x="PC1", y="PC2") {
   }
   
   dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=0.65)+scale_color_manual(values=c("#fc2847", "#1cac78")) #+ #scale_color_viridis_c(option = "A", direction = 1, limits = c(min(dat$density), max(dat$density)))+
+
+  plot <- plot + geom_point(data=dat, aes(-x, -y),size=0.65)+scale_color_manual(values=c("#fc2847", "#1cac78")) #+ #scale_color_viridis_c(option = "A", direction = 1, limits = c(min(dat$density), max(dat$density)))+
  # plot <- plot +geom_point(data=dat, aes(-x, -y, colour = density),size=0.65,shape = 1,colour = "black",alpha=0.8)
   
   ########
@@ -235,105 +233,5 @@ PCbiplot <- function(PC, x="PC1", y="PC2") {
   
 }
 
-PCbiplot(PC)
-
-########################################################################################################################################################
-#4) PLOT PPCA BY CLUSTERS
-########################################################################################################################################################
-
-
-
-PCbiplot <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-  
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-  
[…]

### 2021-03-23 Scripts/6_Merge_Z-scores_Trait_Data_FunctionalG.R

@@ -108,4 +108,3 @@ write.csv(final_quant_clusters, "Data/Csv/quantitative_networks_Z_scores_with_tr
 ########################################################################################################################################################
 ########################################################################################################################################################
 
-

### 2021-03-23 Figures/Figure_Brms_Model.Rmd
Edits

@@
 library(ggplot2)
+library(patchwork)
+library(tidybayes)
+library(emmeans)
 
@@
   as.factor(guild)), width=0.6,alpha=1, size = 1,position = position_dodge(width = 0.68)) +ylim(0,quantile(dat$Interaction, 0.95))+
-  scale_color_manual("Floral visitors guilds",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black","grey"))
-
-#Values over the percentile 95 were omitted for visualization purposes
+  scale_color_manual("Floral visitors guilds",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black","grey")) + ggtitle("A")
 

### 2021-03-23 Figures/Figure_Posthoc_Brms_Model.Rmd
Edits

--- 2021-03-23 Figures/Figure_Brms_Model.Rmd
@@
 
-model_forest_data <- readRDS("model_forest_data.RDS")
+result <- readRDS("result_Tukey_model.RDS")
 
-dat <- readRDS("data_model.RDS")
-
-#cond effect model visitation data
-ce_1 <- conditional_effects(model_forest_data, effects = "Clusters:guild",points=T) 
-#change colnames in model output to use same aesthetics
-#if not gg seems to don't like it
-colnames(ce_1[[1]])[4] <- "a"
-colnames(ce_1[[1]])[10] <- "Interaction"
-ce_1[[1]][10]<- ce_1[[1]][10]+1
-ce_1[[1]][12]<- ce_1[[1]][12]+1
-ce_1[[1]][13]<- ce_1[[1]][13]+1
-
-#Order levels
-ce_1[[1]]$guild <- as.character(ce_1[[1]]$guild)
-ce_1[[1]]$guild <- factor(ce_1[[1]]$guild, levels = c("Bees","Non-bee-Hymenoptera","Syrphids","Non-syrphids-diptera","Lepidoptera","Coleoptera"))
-dat$guild <- as.character(dat$guild)
-dat$guild <- factor(dat$guild, levels = c("Bees","Non-bee-Hymenoptera","Syrphids","Non-syrphids-diptera","Lepidoptera","Coleoptera"))
-
-#plot model
- ggplot(ce_1[[1]], aes(x = Clusters, y = Interaction, colour = as.factor(guild), group = 
-  as.factor(guild))) +
-  geom_point(size = 2.4, position = position_dodge(width = 0.68), alpha=1) +
-  theme_ms()+ ylab("Nº of visits per plant taxa") + xlab("Plant functional groups")+
-  geom_point(data = dat,aes(x = Clusters, y = (Interaction),group = 
-  as.factor(guild)),size = 1.2,shape=21, position = position_jitterdodge(dodge.width = 0.68, jitter.width = 0.25), alpha=0.14)+
-  geom_errorbar(data=ce_1[[1]],mapping=aes(x=Clusters, ymin=lower__, ymax=upper__,colour = as.factor(guild), group = 
-  as.factor(guild)), width=0.6,alpha=1, size = 1,position = position_dodge(width = 0.68)) +ylim(0,quantile(dat$Interaction, 0.95))+
-  scale_color_manual("Floral visitors guilds",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black","grey")) + ggtitle("A")
+ggplot(result, aes(x = .value, y = contrast,  fill=contrast)) +
+  stat_eye( point_interval = median_qi,
+            .width = c(0.66, 0.95),alpha=0.7) +theme_ms() +theme(legend.position = "none")+geom_vline(xintercept=0,linetype="dashed") + ylab("Pairwise comparisons") + xlab("Marginal mean difference")
 

### 2021-03-23 Figures/BRMS_Metric_PPCA.Rmd
Edits

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=17, fig.width=17}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=13, fig.width=17}
 
@@
 Visits_PC1 <- ggplot(ce_1[[1]], aes(x = PC1, y = (estimate__+1))) + geom_point(data = data_analysis2,aes(x = PC1, y = Visits),
-              size = 1.2, alpha=0.9) + geom_line(size=1.2) + ylim(0,quantile(data_analysis2$Visits, 0.95)) +theme_ms()+
-              geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1) + ylab("Number of visits")
+       size = 1.5, alpha=0.9) + geom_line(colour="darkblue",size=1.2) + ylim(0,quantile(data_analysis2$Visits, 0.95)) +theme_ms()+
+  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="darkblue") + ylab("Number of visits")+ ggtitle("A")
 
@@
   size = 1.2, alpha=0.9) + geom_line(size=1.2) + ylim(0,quantile(data_analysis2$Visits, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1) + ylab("Number of visits")
+  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1) + ylab("Number of visits") + ggtitle("B")
 
@@
                       size = 1.2, alpha=0.9) + geom_line(size=1.2)  +theme_ms()+
-                      geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1) + ylab("Specilization (d')")
+                      geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1) + ylab("Specilization (d')") + ggtitle("C")
 
@@
                       size = 1.2, alpha=0.9) + geom_line(size=1.2)  +theme_ms()+
-                      geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1) + ylab("Specilization (d')")
+                      geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1) + ylab("Specilization (d')") + ggtitle("D")
 

### 2021-03-23 Figures/Figure_Brms_Model_Bees.Rmd
Edits

--- 2021-03-23 Figures/Figure_Posthoc_Brms_Model.Rmd
@@
 
+#SAVE MODEL 1
 setwd("~/Dropbox/PhD/R") #DROPBOX, files too large for github
+model_bee_families <- readRDS("model_bee_families.RDS")
+d_5_1 <- readRDS("data_model_just_bees.RDS")
 
-result <- readRDS("result_Tukey_model.RDS")
+##############
 
-ggplot(result, aes(x = .value, y = contrast,  fill=contrast)) +
-  stat_eye( point_interval = median_qi,
-            .width = c(0.66, 0.95),alpha=0.7) +theme_ms() +theme(legend.position = "none")+geom_vline(xintercept=0,linetype="dashed") + ylab("Pairwise comparisons") + xlab("Marginal mean difference")
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(1.8)),
+           axis.text=element_text(size = rel(1.2), color = "black"),
+           legend.title=element_text(face="bold"),
+           legend.text=element_text(size = rel(1.2)),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(1, 'lines'),
+           panel.border=element_rect(color="black",size=1),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank()
+     ))
+}
+
+#############
+#PLOT MODEL 1 NON APIS
+#############
+ce_1 <- conditional_effects(model_bee_families, effects = "Clusters:bee_family",points=T) 
+#change colnames in model output to use same aesthetics
+#if not gg seems to don't like it
+colnames(ce_1[[1]])[4] <- "a"
+colnames(ce_1[[1]])[10] <- "Interaction"
+ce_1[[1]][10]<- ce_1[[1]][10]+1
+
+ggplot(ce_1[[1]], aes(x = Clusters, y = Interaction, colour = as.factor(bee_family), group = 
+                        as.factor(bee_family))) +
+  geom_point(size = 2.4, position = position_dodge(width = 0.8), alpha=1) +
+  theme_ms()+ ylab("Nº of visits per plant taxa") + xlab("Plant reproductive groups")+
+  geom_point(data = d_5_1,aes(x = Clusters, y = (Interaction+1)),size = 1.2,shape=21, position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2), alpha=0.3)+
+  geom_errorbar(data=ce_1[[1]],mapping=aes(x=Clusters, ymin=lower__, ymax=upper__,colour = as.factor(bee_family), group = 
+                                             as.factor(bee_family)), width=.6,alpha=0.8, size = 0.9,position = position_dodge(width = 0.8)) +ylim(0,200)+
+  scale_color_manual("Bee families",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black"))
 

### 2021-03-23 Scripts/3_PPCA.R

@@ -112,7 +112,7 @@ phyl_pca_forest_1 <- phyl.pca(phylo_output, final_d,method="lambda",mode="cov")
 #saveRDS(phyl_pca_famd, "Data/RData/phyl_pca_famd.rds")
 saveRDS(phyl_pca_forest_1, "Data/RData/phyl_pca_forest.rds")
 #SAVE ALSO DATA TO PLOT IT IN RMD file
-#saveRDS(dat_cleaning_5, "Data/RData/data_all_species_for_rmd_plot_ppca_CLUSTERS.rds")
+saveRDS(dat_cleaning_5, "Data/RData/data_all_species_for_rmd_plot_ppca_CLUSTERS.rds")
 
 ####
 #READ DATA
@@ -131,7 +131,7 @@ PC$S
 #PC loadings (ARROWS)
 PC$L
 
-
+nrow(PC$S)
   
 ########################################################################################################################################################
 #4) PLOT PPCA

### 2021-03-30 Figures/BRMS_Funcional_Groups_X_PPCA.Rmd
edits

---
output:
  pdf_document: default
  html_document: default
classoption: landscape

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=8, fig.width=28}

#LOAD LIBRARIES 
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(tidyverse)
library(patchwork) #panel of plots
library(brms)
library(cmdstanr)

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2.2)),
           axis.text=element_text(size = rel(2), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.4)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(1.8, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank()
     ))
}

setwd("~/Dropbox/PhD/R") #DROPBOX, files too large for github

#Load data 
model_1_subset_spp_4pcs <- readRDS("model_1_subset_spp_4pcs.RDS")
dat <- readRDS("data_for_model_1_subset_spp_4pcs.RDS")

#Plot nicely PC1
ce_pc1 <- conditional_effects(model_1_subset_spp_4pcs, effects = "PC1:guild",points=T)

p1 <- ggplot(ce_pc1[[1]], aes(x = PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat,
  aes(x = PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat$Interaction, 0.95)) + ylab("Number of visits")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))

#Plot nicely PC2
ce_pc2 <- conditional_effects(model_1_subset_spp_4pcs, effects = "PC2:guild",points=T)

p2 <- ggplot(ce_pc2[[1]], aes(x = PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat,
  aes(x = PC2, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat$Interaction, 0.95)) + ylab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))

#Plot nicely PC3
ce_pc3 <- conditional_effects(model_1_subset_spp_4pcs, effects = "PC3:guild",points=T)

p3 <- ggplot(ce_pc3[[1]], aes(x = PC3, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat,
   aes(x = PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat$Interaction, 0.95)) + ylab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))

combined <- p1 + p2 + p3 & theme(legend.position = "right")
combined + plot_layout(guides = "collect")

```

### 2021-03-30 Figures/Functional_Groups.Rmd
edits

---
title: ""
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13}

#CODE TO PLOT FUNCTIONAL GROUPS
#IT CAN BE PLOT WITH MUCH LESS CODE BUT NO TIME FOR CLEANING IT

setwd("~/R_Projects/Reproductive Traits")

##########################################
#Visualization of plant functional groups#
##########################################

library(cowplot)
library(ggplot2)
library(tidyr)
library(dplyr)
library(reshape2)
library(data.table)
library(patchwork)

#LOAD DATA
#read unscaled trait data in order to visualize better the clusters
d <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv")

dat_1 <- read.csv("Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")

d$Clusters <- dat_1$Clusters

#select columns of interest
t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]

##############################################################################################################################
#Prepare table qualitative variables
##############################################################################################################################

##############################################################################################################################
#Breeding system
t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))

#Summary to create table
breeding <- t %>%
  group_by(Clusters,Breeding_system) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

breeding <- breeding[,-3]

breeding <- spread(breeding, Clusters, Percentage)

colnames(breeding)[1] <- "Category"

Trait <- data.frame(Trait= c(rep("Breeding system", 3)))

Breeding_system <- cbind(Trait, breeding)

##############################################################################################################################
#Compatibility
str(t)
t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Unisexual flower"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Unisexual flower"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"

t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Unisexual flower", "Self incompatible", "Partially self compatible", "Self compatible"))
#Summary to create table
comp <- t %>%
  group_by(Clusters,IMPUTED_Compatibility) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

comp <- comp[,-3]

comp <- spread(comp, Clusters, Percentage)
#Replace Na's with zeros
comp[is.na(comp)] <- 0
#Set call name os categories per trait
colnames(comp)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Compatibility system", 4)))
#Add column
Compatibility_system <- cbind(Trait, comp)
#Bind rows
bind_rows(Breeding_system, Compatibility_system)

############################################################################################################################################
#Life form
t$life_form <- as.character(t$life_form)
t$life_form[t$life_form =="vine"] <- "Shrub"
t$life_form[t$life_form =="tree"] <- "Tree"
t$life_form[t$life_form =="herb"] <- "Herb"
t$life_form[t$life_form =="shrub"] <- "Shrub"
#Order levels
t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
#Summary to create table
life_form <- t %>%
  group_by(Clusters,life_form) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
life_form <- life_form[,-3]
#convert to wide
life_form <- spread(life_form, Clusters, Percentage)
#Set call name os categories per trait
colnames(life_form)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Life form", 3)))
#Add column
Life_form<- cbind(Trait, life_form)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form)

############################################################################################################################################
t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
#Summary to create table
life_span <- t %>%
  group_by(Clusters,lifespan) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
life_span <- life_span[,-3]
#convert to wide
life_span <- spread(life_span, Clusters, Percentage)
#Set call name os categories per trait
colnames(life_span)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Life span", 2)))
#Add column
Life_span<- cbind(Trait, life_span)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)

############################################################################################################################################
t$Flower_morphology <- as.character(t$Flower_morphology)
t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"

Flower_morphology <- t %>%
  group_by(Clusters,Flower_morphology) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
Flower_morphology <- Flower_morphology[,-3]
#convert to wide
Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
#Set call name os categories per trait
colnames(Flower_morphology)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
#Add column
Flower_morphology<- cbind(Trait, Flower_morphology)
#Replace Na's with zeros
Flower_morphology[is.na(Flower_morphology)] <- 0
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)

############################################################################################################################################
t$Flower_symmetry <- as.character(t$Flower_symmetry)
t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"

Flower_symmetry <- t %>%
  group_by(Clusters,Flower_symmetry) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
Flower_symmetry <- Flower_symmetry[,-3]
#convert to wide
Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
#Set call name os categories per trait
colnames(Flower_symmetry)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
#Add column
Flower_symmetry<- cbind(Trait, Flower_symmetry)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
############################################################################################################################################
t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"

#Order levels
t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))

Selfing <- t %>%
  group_by(Clusters,Autonomous_selfing_level) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

#delete column to convert to wide
Selfing <- Selfing[,-3]
#convert to wide
Selfing <- spread(Selfing, Clusters, Percentage)
#Set call name os categories per trait
colnames(Selfing)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
#Replace Na's with zeros
Selfing[is.na(Selfing)] <- 0
#Add column
Selfing_1 <- cbind(Trait, Selfing)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)

############################################################################################################################################
t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"

Nectar <- t %>%
  group_by(Clusters,Nectar_presence_absence) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

#delete column to convert to wide
Nectar <- Nectar[,-3]
#convert to wide
Nectar <- spread(Nectar, Clusters, Percentage)
#Set call name os categories per trait
colnames(Nectar)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Nectar", 2)))
#Replace Na's with zeros
Nectar[is.na(Nectar)] <- 0
#Add column
Nectar <- cbind(Trait, Nectar)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar)

##############################################################################################################################
#Prepare table quantitative variables
##############################################################################################################################

Selfing <-  t %>% group_by(Clusters)%>% 
  select(Autonomous_selfing_level_fruit_set) %>% # select variables to summarise
  summarise_each(funs(min = min,
                     # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                    sd = sd))

s1 <- as.data.frame(t(Selfing))
#set colnames
colnames(s1) <- c("1","2","3","4","5")
#remove the cluster row
s1 <- s1[-1,]
#convert rownames to 1st columns
s1 <- setDT(s1, keep.rownames = "TRUE")[]
colnames(s1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Autonomous selfing", 5)))
#Add column
Selfing <- cbind(Trait, s1)

##############################################################################################################################
flower_number <-  t %>% group_by(Clusters)%>% 
  select(Flowers_per_plant) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

f1 <- as.data.frame(t(flower_number))
#set colnames
colnames(f1) <- c("1","2","3","4","5")
#remove the cluster row
f1 <- f1[-1,]
#convert rownames to 1st columns
f1 <- setDT(f1, keep.rownames = "TRUE")[]
colnames(f1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Flower number", 5)))
#Add column
Flower_number <- cbind(Trait, f1)

##############################################################################################################################
Flowers_per_inflorescence <-  t %>% group_by(Clusters)%>% 
  select(Flowers_per_inflorescence) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

f_i_1 <- as.data.frame(t(Flowers_per_inflorescence))
#set colnames
colnames(f_i_1) <- c("1","2","3","4","5")
#remove the cluster row
f_i_1 <- f_i_1[-1,]
#convert rownames to 1st columns
f_i_1 <- setDT(f_i_1, keep.rownames = "TRUE")[]
colnames(f_i_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Flowers per inflorescence", 5)))
#Add column
Flower_per_inflo <- cbind(Trait, f_i_1)

bind_rows(Selfing, Flower_number, Flower_per_inflo)

##############################################################################################################################
Floral_unit_width <-  t %>% group_by(Clusters)%>% 
  select(Floral_unit_width) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

f_u_w_1 <- as.data.frame(t(Floral_unit_width))
#set colnames
colnames(f_u_w_1) <- c("1","2","3","4","5")
#remove the cluster row
f_u_w_1 <- f_u_w_1[-1,]
#convert rownames to 1st columns
f_u_w_1 <- setDT(f_u_w_1, keep.rownames = "TRUE")[]
colnames(f_u_w_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Inflorescence width", 5)))
#Add column
Inflo_width <- cbind(Trait, f_u_w_1)

bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width)

##############################################################################################################################
Corolla_diameter_mean <-  t %>% group_by(Clusters)%>% 
  select(Corolla_diameter_mean) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

c_w_1 <- as.data.frame(t(Corolla_diameter_mean))
#set colnames
colnames(c_w_1) <- c("1","2","3","4","5")
#remove the cluster row
c_w_1 <- c_w_1[-1,]
#convert rownames to 1st columns
c_w_1 <- setDT(c_w_1, keep.rownames = "TRUE")[]
colnames(c_w_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Flower width", 5)))
#Add column
Flower_width <- cbind(Trait, c_w_1)

bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width)

##############################################################################################################################
Corolla_length_mean <-  t %>% group_by(Clusters)%>% 
  select(Corolla_length_mean) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

c_l_1 <- as.data.frame(t(Corolla_length_mean))
#set colnames
colnames(c_l_1) <- c("1","2","3","4","5")
#remove the cluster row
c_l_1 <- c_l_1[-1,]
#convert rownames to 1st columns
c_l_1 <- setDT(c_l_1, keep.rownames = "TRUE")[]
colnames(c_l_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Flower length", 5)))
#Add column
Flower_length<- cbind(Trait, c_l_1)

bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length)

##############################################################################################################################
STYLE_IMPUTED <-  t %>% group_by(Clusters)%>% 
  select(STYLE_IMPUTED) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

s_l_1 <- as.data.frame(t(STYLE_IMPUTED))
#set colnames
colnames(s_l_1) <- c("1","2","3","4","5")
#remove the cluster row
s_l_1 <- s_l_1[-1,]
#convert rownames to 1st columns
s_l_1 <- setDT(s_l_1, keep.rownames = "TRUE")[]
colnames(s_l_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Style length", 5)))
#Add column
Style_length<- cbind(Trait, s_l_1)

bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length)

##############################################################################################################################

OVULES_IMPUTED <-  t %>% group_by(Clusters)%>% 
  select(OVULES_IMPUTED) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

o_n_1 <- as.data.frame(t(OVULES_IMPUTED))
#set colnames
colnames(o_n_1) <- c("1","2","3","4","5")
#remove the cluster row
o_n_1 <- o_n_1[-1,]
#convert rownames to 1st columns
o_n_1 <- setDT(o_n_1, keep.rownames = "TRUE")[]
colnames(o_n_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Ovule number", 5)))
#Add column
Ovule_number <- cbind(Trait, o_n_1)

bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Ovule_number)

##############################################################################################################################

IMPUTED_plant_height_mean_m <-  t %>% group_by(Clusters)%>% 
  select(IMPUTED_plant_height_mean_m) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

p_h_1 <- as.data.frame(t(IMPUTED_plant_height_mean_m))
#set colnames
colnames(p_h_1) <- c("1","2","3","4","5")
#remove the cluster row
p_h_1 <- p_h_1[-1,]
#convert rownames to 1st columns
p_h_1 <- setDT(p_h_1, keep.rownames = "TRUE")[]
colnames(p_h_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Plant height", 5)))
#Add column
Plant_height <- cbind(Trait, p_h_1)

#Bind quantitative and qualitative variables
Table_all_traits <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar,
          Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length, Ovule_number, Plant_height)

#Select just two decimals
is.num <- sapply(Table_all_traits, is.numeric)
Table_all_traits[is.num] <- lapply(Table_all_traits[is.num], round, 2)

colnames(Table_all_traits) <- c("Trait", "Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")

#LOAD LIBRARIES
#devtools::install_github("ricardo-bion/ggradar", dependencies=TRUE)
suppressPackageStartupMessages(library(dplyr))
library(scales)
library(tibble)
library(ggradar)
library(janitor)
library(grid)
library(dplyr)
library(lubridate)
#QUANTITATIVVE VARIABLES

#generate subset of quantitative variables for plotting
quant_median <- subset(Table_all_traits, Category=="median")

#delete col number 2
quant_median <- quant_median[,-2]

#transpose dataframe
final_df <- as.data.frame(t(quant_median))

#rownames to colnames (1st one)
final_df_1 <- final_df %>% row_to_names(row_number = 1)

#Convert all variables to numeric
final_df_2 <- sapply(final_df_1, function(x) as.numeric(as.character(x)))

#set back the missed rownames in the processing
rownames(final_df_2) <- rownames(final_df_1)

# Convert to dataframe
final_df_2 <- as.data.frame(final_df_2)

# Scale values and set rowname as column
final_df_3 <-final_df_2 %>% rownames_to_column( var = "group" ) %>%   mutate_at(vars(-group),funs(rescale))

#Plot Radar
#ggradar(final_df_3)

#QUALITATIVE VARIABLES

#LOAD DATA
#read unscaled trait data in order to visualize better the clusters
d <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv")

dat_1 <- read.csv("Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")

d$Clusters <- dat_1$Clusters

#select columns of interest
t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]

##############################################################################################################################
#Prepare table qualitative variables
##############################################################################################################################

##############################################################################################################################
#Breeding system
t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))

#Summary to create table
breeding <- t %>%
  group_by(Clusters,Breeding_system) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

breeding <- breeding[,-3]

breeding <- spread(breeding, Clusters, Percentage)

colnames(breeding)[1] <- "Category"

Trait <- data.frame(Trait= c(rep("Breeding system", 3)))

Breeding_system <- cbind(Trait, breeding)

##############################################################################################################################
#Compatibility
str(t)
t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Self incompatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Self incompatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"

t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Self incompatible", "Partially self compatible", "Self compatible"))
#Summary to create table
comp <- t %>%
  group_by(Clusters,IMPUTED_Compatibility) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

comp <- comp[,-3]

comp <- spread(comp, Clusters, Percentage)
#Replace Na's with zeros
comp[is.na(comp)] <- 0
#Set call name os categories per trait
colnames(comp)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Compatibility system", 3)))
#Add column
Compatibility_system <- cbind(Trait, comp)
#Bind rows
bind_rows(Breeding_system, Compatibility_system)

############################################################################################################################################
#Life form
t$life_form <- as.character(t$life_form)
t$life_form[t$life_form =="vine"] <- "Shrub"
t$life_form[t$life_form =="tree"] <- "Tree"
t$life_form[t$life_form =="herb"] <- "Herb"
t$life_form[t$life_form =="shrub"] <- "Shrub"
#Order levels
t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
#Summary to create table
life_form <- t %>%
  group_by(Clusters,life_form) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
life_form <- life_form[,-3]
#convert to wide
life_form <- spread(life_form, Clusters, Percentage)
#Set call name os categories per trait
colnames(life_form)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Life form", 3)))
#Add column
Life_form<- cbind(Trait, life_form)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form)

############################################################################################################################################
t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
#Summary to create table
life_span <- t %>%
  group_by(Clusters,lifespan) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
life_span <- life_span[,-3]
#convert to wide
life_span <- spread(life_span, Clusters, Percentage)
#Set call name os categories per trait
colnames(life_span)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Life span", 2)))
#Add column
Life_span<- cbind(Trait, life_span)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)

############################################################################################################################################
#t$Flower_morphology <- as.character(t$Flower_morphology)
#t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
#t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"
#
#Flower_morphology <- t %>%
#  group_by(Clusters,Flower_morphology) %>%
#  summarise (n = n()) %>%
#  mutate(Percentage = n / sum(n)*100)
##delete column to convert to wide
#Flower_morphology <- Flower_morphology[,-3]
##convert to wide
#Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
##Set call name os categories per trait
#colnames(Flower_morphology)[1] <- "Category"
##Create new column
#Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
##Add column
#Flower_morphology<- cbind(Trait, Flower_morphology)
##Replace Na's with zeros
#Flower_morphology[is.na(Flower_morphology)] <- 0
##Bind rows
#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)
#
############################################################################################################################################
t$Flower_symmetry <- as.character(t$Flower_symmetry)
t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"

Flower_symmetry <- t %>%
  group_by(Clusters,Flower_symmetry) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
Flower_symmetry <- Flower_symmetry[,-3]
#convert to wide
Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
#Set call name os categories per trait
colnames(Flower_symmetry)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
#Add column
Flower_symmetry<- cbind(Trait, Flower_symmetry)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
############################################################################################################################################
#t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"
#
##Order levels
#t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))
#
#Selfing <- t %>%
#  group_by(Clusters,Autonomous_selfing_level) %>%
#  summarise (n = n()) %>%
#  mutate(Percentage = n / sum(n)*100)
#
##delete column to convert to wide
#Selfing <- Selfing[,-3]
##convert to wide
#Selfing <- spread(Selfing, Clusters, Percentage)
##Set call name os categories per trait
#colnames(Selfing)[1] <- "Category"
##Create new column
#Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
##Replace Na's with zeros
#Selfing[is.na(Selfing)] <- 0
##Add column
#Selfing_1 <- cbind(Trait, Selfing)
##Bind rows
#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)
#
#############################################################################################################################################
t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"

Nectar <- t %>%
  group_by(Clusters,Nectar_presence_absence) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

#delete column to convert to wide
Nectar <- Nectar[,-3]
#convert to wide
Nectar <- spread(Nectar, Clusters, Percentage)
#Set call name os categories per trait
colnames(Nectar)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Nectar", 2)))
#Replace Na's with zeros
Nectar[is.na(Nectar)] <- 0
#Add column
Nectar <- cbind(Trait, Nectar)
#Bind rows
data <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span, Flower_symmetry, Nectar)

#remove first col
data_1 <- data[,-1]
colnames(data_1) <- c("Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")

#transpose dataframe
data_2 <- as.data.frame(t(data_1))

#rownames to colnames (1st one)
data_3 <- data_2 %>% row_to_names(row_number = 1)

#Convert all variables to numeric
data_4 <- sapply(data_3, function(x) as.numeric(as.character(x)))

#set back the missed rownames in the processing
rownames(data_4) <- rownames(data_3)

# Convert to dataframe
data_4 <- as.data.frame(data_4)

# Scale values and set rowname as column
data_5 <-data_4 %>% rownames_to_column( var = "group" )

data_6 <- melt(data_5)

cluster1 <- subset(data_6, group=="Cluster 1")

cluster1$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))

#Try to achieve the desire output with plot_grid

c1 <- cluster1 %>% 
  ggplot(aes(x = variable,  y = value, fill = group))  +  
  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#00AFBB")+
  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
  theme(axis.title.x = element_blank(), axis.text.x=element_blank(),plot.title = element_text(size = 18))+ ylab("")+
  ggtitle("A) Qualitative variables")

cluster2 <- subset(data_6, group=="Cluster 2")

cluster2$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))

c2 <- cluster2 %>% 
  ggplot(aes(x = variable,  y = value, fill = group))  +  
  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#E69F00")+
  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
  theme(strip.background = element_blank(), strip.text = element_blank())+
  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+ylab("")

cluster3 <- subset(data_6, group=="Cluster 3")

cluster3$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))

c3 <- cluster3 %>% 
  ggplot(aes(x = variable,  y = value, fill = group))  +  
  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#FC4E07")+
  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+
  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("Percentage")

cluster4 <- subset(data_6, group=="Cluster 4")

cluster4$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))

c4 <- cluster4 %>% 
  ggplot(aes(x = variable,  y = value, fill = group))  +  
  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#000000")+
  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+
  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("")

cluster5 <- subset(data_6, group=="Cluster 5")

cluster5$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
c5 <- cluster5 %>% 
  ggplot(aes(x = variable,  y = value, fill = group))  +  
  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="darkgreen")+
  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
  scale_y_continuous(expand = c(0,0)) +
  theme(axis.text.x = element_text(angle = 45,vjust = 1, hjust=1))+
  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("")+xlab("")

A <- c1 + c2 + c3 + c4 + c5 + plot_layout(ncol = 1)
B <- ggradar(final_df_3, group.colours=c("#00AFBB", "#E69F00", "#FC4E07","#000000", "darkgreen"),
             legend.text.size=5, grid.label.size = 0,legend.position = "none",axis.label.size=3)+ 
  guides(shape = guide_legend(override.aes = list(size = 0.5)))+ ggtitle("B) Quantitative variables")+
  theme(plot.title = element_text(size = 18))

patch <- A | B

patch + plot_annotation(title = "Functional groups",theme = theme(plot.title = element_text(size = 20,face="bold")))

```

### 2021-03-31 Figures/BRMS_Metric_PPCA.Rmd
Plot PPCA with images, still need more edits

@@
 Visits_PC1 <- ggplot(ce_1[[1]], aes(x = PC1, y = (estimate__+1))) + geom_point(data = data_analysis2,aes(x = PC1, y = Visits),
-       size = 1.5, alpha=0.9) + geom_line(colour="darkblue",size=1.2) + ylim(0,quantile(data_analysis2$Visits, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="darkblue") + ylab("Number of visits")+ ggtitle("A")
+              size = 1.2, alpha=0.9) + geom_line(size=1.2) + ylim(0,quantile(data_analysis2$Visits, 0.95)) +theme_ms()+
+              geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1) + ylab("Number of visits") + ggtitle("A")
 

### 2021-03-31 Figures/PPCA_Plant_Functional_Groups.Rmd
Plot PPCA with images, still need more edits

@@
 
+library(magick)
+tree <- image_read("Images/PPCA_Plot/Tree.png")
+tree_1 <- as.raster(tree)
+
+style_l <- image_read("Images/PPCA_Plot/Style_Long.png")
+style_l_1 <- as.raster(style_l)
+
+style_s <- image_read("Images/PPCA_Plot/Style_Short.png")
+style_s_1 <- as.raster(style_s)
+
+ovule_h <- image_read("Images/PPCA_Plot/Ovule_High.png")
+ovule_h_1 <- as.raster(ovule_h)
+
+ovule_l <- image_read("Images/PPCA_Plot/Ovule_Low.png")
+ovule_l_1 <- as.raster(ovule_l)
+
+selfing_n <- image_read("Images/PPCA_Plot/Selfing_None.png")
+selfing_n_1 <- as.raster(selfing_n)
+
+selfing_h <- image_read("Images/PPCA_Plot/Selfing_High.png")
+selfing_h_1 <- as.raster(selfing_h)
+
+single_flower <- image_read("Images/PPCA_Plot/Single_Flower.png")
+single_flower_1 <- as.raster(single_flower)
+
+many_flowers <- image_read("Images/PPCA_Plot/Many_Flowers.png")
+many_flowers_1 <- as.raster(many_flowers)
+#many_flowers_1 <- image_rotate(many_flowers, 45)
+
+large_flower <- image_read("Images/PPCA_Plot/Large_Flower.png")
+large_flower_1 <- as.raster(large_flower)
+
+flower_small <- image_read("Images/PPCA_Plot/Flower_Small.png")
+flower_small_1 <- as.raster(flower_small)
 #############################################################################################################################################################
@@
 #Load plots
+
+#Invert axes
+PC$S[,1] <- -PC$S[,1]
+PC$S[,2] <- -PC$S[,2]
+
 all_spp <- function(PC, x="PC1", y="PC2") {
@@
   dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Clusters <- dat_cleaning_5$Clusters
-  dat$Clusters <- as.character(dat$Clusters)
-  dat$Clusters[dat$Clusters=="1"] <- "A"
-  dat$Clusters[dat$Clusters=="2"] <- "B"
-  dat$Clusters[dat$Clusters=="3"] <- "C"
-  dat$Clusters[dat$Clusters=="4"] <- "D"
-  dat$Clusters[dat$Clusters=="5"] <- "E"
 
- dat$Clusters <- factor(dat$Clusters, levels=c("A", "B", "C", "D", "E"))
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
+  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.025, 0.050, 0.075), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.85),title="Kernel density"))+
+    scale_alpha(guide = 'none')
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Clusters),size=2.5)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "darkgreen"))+ labs(color='Functional groups')
+    plot <- plot + geom_point(data=dat, aes(x, y),size=0.95, color="black")
 
@@
   datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
+                      v1 = .7 * mult * (get(x)),
+                      v2 = .7 * mult * (get(y))
   )
   # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.4, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.6, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
 
   #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.2, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, colour=c("black"))
 
@@
 
+  #CHANGE THEME
+
+  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4, xmax = -2.9,ymin = 2.45, ymax = 4.35)+
+     annotation_raster(style_l_1, xmin = 2.45, xmax = 3.25,ymin = 2.25, ymax = 3.35) +
+    annotation_raster(style_s_1, xmin = -3.25, xmax = -2.45,ymin = -2.65, ymax = -1.75) +
+    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.15,ymin = -0.65, ymax = 0.25) +
+    annotation_raster(ovule_l_1, xmin = -4.1, xmax = -3.5,ymin = -0.3, ymax = 0.6) +
+    annotation_raster(selfing_n_1, xmin = -0.2, xmax = 1.2,ymin = 2.8, ymax = 4.7) +
+    annotation_raster(selfing_h_1, xmin = -0.95, xmax = 0,ymin = -4.1, ymax = -3.25) +
+    annotation_raster(single_flower_1, xmin = 3.0, xmax = 3.7,ymin = -2, ymax = -1.1) +
+    annotation_raster(many_flowers_1, xmin = -4.60, xmax = -3.15,ymin = 1, ymax = 2.15) +
+    annotation_raster(large_flower_1, xmin = 3.4, xmax = 4.2,ymin = 1, ymax = 2.1) +
+    annotation_raster(flower_small_1, xmin = -4, xmax = -1.85,ymin = -2.4, ymax = -0.4) +
+    annotation_raster(single_flower_1, xmin = 2.8, xmax = 3.5,ymin = -3, ymax = -2.2)
+
       #ADD LABELS
-  rownames(PC$L) <- c("SELFING", "FLOWER N.", "FLOWER SIZE", "STYLE LENGTH", "OVULE N.", "PLANT HEIGHT" )
+  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
 
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5.2,5,7,5.8,6.5)),
+ plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.5,5.5,7.5,7.3,6)), y = -(PCAloadings$PC2*c(4.77,2.4,3,6.5,14,5.5)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=5)
-
-  #CHANGE THEME
 

### 2021-04-02 Main_Figures/Global_trait_spectrum.Rmd
Organizing folders and script with all the analysis

--- 2021-03-31 Figures/PPCA_Plant_Functional_Groups.Rmd
@@
 #Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_CLUSTERS.rds")
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
 phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
@@
   plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.025, 0.050, 0.075), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.85),title="Kernel density"))+
+  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
     scale_alpha(guide = 'none')
@@
      annotation_raster(style_l_1, xmin = 2.45, xmax = 3.25,ymin = 2.25, ymax = 3.35) +
-    annotation_raster(style_s_1, xmin = -3.25, xmax = -2.45,ymin = -2.65, ymax = -1.75) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.15,ymin = -0.65, ymax = 0.25) +
-    annotation_raster(ovule_l_1, xmin = -4.1, xmax = -3.5,ymin = -0.3, ymax = 0.6) +
+    annotation_raster(style_s_1, xmin = -3.05, xmax = -2.25,ymin = -2.65, ymax = -1.75) +
+    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
+    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
     annotation_raster(selfing_n_1, xmin = -0.2, xmax = 1.2,ymin = 2.8, ymax = 4.7) +
     annotation_raster(selfing_h_1, xmin = -0.95, xmax = 0,ymin = -4.1, ymax = -3.25) +
-    annotation_raster(single_flower_1, xmin = 3.0, xmax = 3.7,ymin = -2, ymax = -1.1) +
+    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
     annotation_raster(many_flowers_1, xmin = -4.60, xmax = -3.15,ymin = 1, ymax = 2.15) +
@@
     annotation_raster(flower_small_1, xmin = -4, xmax = -1.85,ymin = -2.4, ymax = -0.4) +
-    annotation_raster(single_flower_1, xmin = 2.8, xmax = 3.5,ymin = -3, ymax = -2.2)
+    annotation_raster(single_flower_1, xmin = 2.8, xmax = 3.5,ymin = -2.8, ymax = -2.2)
 
@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.5,5.5,7.5,7.3,6)), y = -(PCAloadings$PC2*c(4.77,2.4,3,6.5,14,5.5)),
+ plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.5,5.5,7.5,7.3,6)), y = -(PCAloadings$PC2*c(4.77,2.4,3,6.5,5,5.5)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=5)

### 2021-04-02 Final_Scripts/2_Trait_Data_Imputation.R

@@ -1,255 +1,0 @@
-########################################################################################################################################################
-#SCRIPT FOR DATA IMPUTATION
-########################################################################################################################################################
-#1) READ TRAIT DATA
-
-#2) CLEAN DATA AND RENAME LEVELS
-
-#3) EXPLORE PATTERNS OF MISSING DATA
-
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-
-#5) ICLUDE EIGENVALUES IN RAWDATA TO IMPROVE IMPUTATION OURPUT
-
-#6) IMPUTE DATA 
-
-#7) SAVE IMPUTED DATA 
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(missMDA) #For missing values
-library(FactoMineR) #Produce pca biplot with individuals and variables
-library(factoextra)
-library(ggpubr) 
-library(missForest) #random forst imputation
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(ape)
-library(PVR) #calculate eigen vectors and add them as a column in the imputation, seems to improve output
-library(visdat) #VISUALIZE MISSING DATA
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-str(trait_data_1)
[…]

### 2021-04-02 Final_Scripts/4_Data_Preparation_Analysis_1.R

@@ -1,51 +1,0 @@
-########################################################################################################################################################
-#SCRIPT TO PREPARE DATA FOR ANALYSIS 1) VISITS~ POLL. FUNCTIONAL GROUP*PRINCIPAL COMPONENTS
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(data.table)
-########################################################################################################################################################
-#LOAD DATA
-########################################################################################################################################################
-long_d <- read.csv("Data/Csv/long_format_quantitative_networks.csv", row.names = 1) #quantitative network data|weighted by frequency of visits per plant species
-phyl_pca <- readRDS("Data/RData/phyl_pca_forest.rds") #add PCA loadings for analysis
-dat_cleaning <- readRDS("Data/RData/data_all_species_PPCA.rds") #data for PPCA
-########################################################################################################################################################
-#PREPARE DATA
-########################################################################################################################################################
-#Select data with interaction greater than 0
-long_d_1 <- long_d[long_d$Interaction>0,]
-
-#Remove other orders/guilds that are not these ones
-long_d_2 <- long_d_1[!is.na(long_d_1$guild),] #I do it by guild because just these 6 guilds are named in this column
-
-#check levels
-levels(factor(long_d_2$guild)) #9 DIFFERENT GUILDS|After I'll select the main fucntional poll. groups for analysis
-
-#convert to dataframe the ppca data
-phyl_pca_1 <- data.frame(phyl_pca$S)
-
-#convert rownames to column
-dat_cleaning_1 <- setDT(dat_cleaning, keep.rownames = TRUE)[]
-colnames(dat_cleaning_1)[1] <- "Plant_species"
-
-phyl_pca_1$Plant_species <- dat_cleaning_1$Plant_species
-#ADD ALSO THESE OTHER 3 COLUMNS WITH SPP, GENUS AND FAMILY INFO NEEDED TO GET THE PHYLO FOR THE MODEL
-phyl_pca_1$Family_all <- dat_cleaning_1$Family_all
-phyl_pca_1$Genus_all <- dat_cleaning_1$Genus_all
-phyl_pca_1$Species_all <- dat_cleaning_1$Species_all
-
-#merge columns
-data_analysis <- merge(long_d_2, phyl_pca_1, by = "Plant_species")
-#Explore why some levels dropped
-#data_analysis <- merge(long_d_2, phyl_pca_1, by = "Plant_species", all.x = T)
-#They are just the 4 species that get_tree cannot find and then, the ones that are until genus level, and thus were not included on the ppca
[…]

### 2021-04-02 Final_Scripts/6_Data_Preparation_Analysis_2.R

@@ -1,143 +1,0 @@
-########################################################################################################################################################
-#SCRIPT TO PREPARE DATA FOR ANALYSIS 2) VISITS/SPECIALIZATION ~ PRINCIPAL COMPONENTS
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(data.table) # operate with df
-library(bipartite) #calculate metrics
-library(dplyr) #data manipulation 
-library(stringr) #remove string
-########################################################################################################################################################
-#1) LOAD NETWORK DATA
-########################################################################################################################################################
-#Set working directory to read files
-setwd("~/R_Projects/Reproductive traits/Data/Data_networks_quantitative") 
-
-#read csv files
-temp <- list.files(pattern="*.csv")
-my.list <- list(for (i in 1:length(temp)) assign(temp[i], read.csv(temp[i])))
-my_files <- list.files(pattern = "\\.csv$")
-my_data <- lapply(my_files, function(i){read.csv(i,  row.names = 1)})
-# Add id to dataframe
-names(my_data) <- stringr::str_replace(my_files, pattern = ".csv", replacement = "")
-
-########################################################################################################################################################
-#2) CALCULATE METRICS 
-########################################################################################################################################################
-
-#Function to sum visits per row and convert NA'S to 0's in the case there is any
-rs_NA <- function(x){
-  z <- as.data.frame(x)
-  z[is.na(z)] <- 0  #convert NA'S to 0's
-  z <- as.data.frame(rowSums(z)) #sum rows
-  z <- setDT(z, keep.rownames = TRUE)[] 
-  colnames(z) <- c("Species","Visits")
-  return(z)
-}
-
-
-#Calculate all metrics at once with bipartite
-met <- function(x){
-  Visits_Sum <- rs_NA(x) #previous function to sum rows 
-  #degree
-  #degree <- specieslevel(x, index="degree", level="lower")
-  #normalise degree
-  #n_degree <- specieslevel(x, index="normalised degree", level="lower")
-  #specialization
[…]

### 2021-04-02 Scripts/3_2_PPCA_Complete_Cases.R

@@ -1,18 +1,16 @@
 ########################################################################################################################################################
-#SCRIPT TO CALCULATE THE PCA
-
-#1) LOAD DATA 
-
+#SCRIPT TO CALCULATE THE PHLOGENETIC INFORMED PRINCIPAL COMPONENT ANALYSIS
+#Just filled rows for the different quantitative variables (no imputed data)
 ########################################################################################################################################################
 #LOAD LIBRARIES
-library(phytools)
+library(phytools) #ppca
 library(ape) #for phylogenetic distance
 library(dplyr) #data processing
 library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
+library(reshape2) #data processing
 library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
+library(MASS) #I think I used it for the kernel density of the plotting function; no longer used but I leave in case its handy later on
+library(ggplot2) #plotting
 library(broman) #crayon colours
 ########################################################################################################################################################
 #1) LOAD DATA
@@ -37,7 +35,9 @@ dat <- dat[!dat$Species_all == "Soulamea terminaloides", ]
 
 str(dat_cleaning)
 
-dat_cleaning <- dat[c("Family_all","Genus_all","Species_all", "Autonomous_selfing_level_fruit_set", "Flowers_per_plant","Corolla_diameter_mean","STYLE_IMPUTED","OVULES_IMPUTED", "IMPUTED_plant_height_mean_m", "Nectar_presence_absence")]
+dat_cleaning <- dat[c("Family_all","Genus_all","Species_all", "Autonomous_selfing_level_fruit_set", 
+                      "Flowers_per_plant","Corolla_diameter_mean","Style_length","Ovule_number", "Plant_height_mean_m", 
+                      "Nectar_presence_absence")]
 
 
 dat_cleaning_1 <- dat_cleaning %>%
@@ -47,18 +47,18 @@ dat_cleaning_2 <- dat_cleaning_1 %>%
   filter(between(Corolla_diameter_mean, quantile(Corolla_diameter_mean, 0.025), quantile(Corolla_diameter_mean, 0.975)))
 
[…]

### 2021-04-02 Scripts/5_Z_Scores_by_Network.R

@@ -1,61 +1,0 @@
-########################################################################################################################################################
-#SCRIPT TO CALCULATE Z-SCORES, MERGE WITH TRAIT DATA AND MERGE WITH FUNCTIONAL GROUPS (JUST SUBSET OF QUANTITATIVE NETWORKS)
-
-#1) LOAD LONG FORMAT QUANTITATIVE NETWORKS WITH POLL GUILDS (with and without apis mellifera)
-
-#2) CALCULATE Z-SCORES
-
-#3) SAVE DATA
-########################################################################################################################################################
-
-#LOAD LIBRARIES
-library(data.table)
-
-########################################################################################################################################################
-#1) LOAD LONG FORMAT DATA, TRAIT DATA AND FUNCTIONAL GROUP DATA
-########################################################################################################################################################
-long_d <- read.csv("Data/Csv/long_format_quantitative_networks.csv")
-long_d_non_apis <- read.csv("Data/Csv/long_format_quantitative_networks_non_apis.csv")
-########################################################################################################################################################
-#2) CALCULATE Z-SCORES
-########################################################################################################################################################
-
-#ALL SPECIES
-#Select data with interaction greater than 0
-long_d_1 <- long_d[long_d$Interaction>0,]
-
-#Calculate Z-scores BY NETWORK (ID)!!
-long_d_1 <- data.table(long_d_1)
-long_d_1[, Z_scores := scale(Interaction,center = TRUE, scale = TRUE), by = Id]
-
-#Remove other orders/guilds that are not these ones
-long_d_2 <- long_d_1[!is.na(long_d_1$guild),] #I do it by guild because just these 6 guilds are named in this column
-#check levels
-levels(long_d_2$guild) #6 DIFFERENT GUILDS
-
-#ALL SPECIES EXCLUDIN APIS
-#Select data with interaction greater than 0
-long_d_non_apis_1 <- long_d_non_apis[long_d_non_apis$Interaction>0,]
-
-#Calculate Z-scores BY NETWORK (ID)!!
-long_d_non_apis_1 <- data.table(long_d_non_apis_1)
-long_d_non_apis_1[, Z_scores := scale(Interaction,center = TRUE, scale = TRUE), by = Id]
-
-#Remove other orders/guilds that are not these ones
[…]

### 2021-04-02 Scripts/7_2_Analysis_Bee_Visitation/3_Merge_Z-scores_Trait_Data_FunctionalG_Bees.R

@@ -1,75 +1,0 @@
-########################################################################################################################################################
-#SCRIPT TO MERGE LONG DATA WITH Z-SCORES, TRAIT DATA AND FUNCTIONAL GROUPS
-
-#1) LOAD DATA 
-
-#3) MERGE WITH TRAIT DATA
-
-#4) MERGE WITH FUNCTIONAL GROUPS
-
-#5) SAVE DATA
-########################################################################################################################################################
-
-#LOAD LIBRARIES
-library(data.table)
-library(readxl) #read trait data
-
-########################################################################################################################################################
-#1) LOAD LONG FORMAT DATA WITH Z-SCORES, TRAIT DATA AND FUNCTIONAL GROUP DATA
-########################################################################################################################################################
-long_d_2 <- read.csv("Data/Csv/long_format_quantitative_networks_Z_scores_all_bee.csv")
-t_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx")
-hclust_d_5 <- read.csv("Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv") #5 clusters
-########################################################################################################################################################
-#3) MERGE WITH TRAIT DATA
-########################################################################################################################################################
-
-#process trait data all species
-t_data <- t_data[1:1701,]
-#filter data, select species with flower level info and capitulum
-t_data_filtered <- filter(t_data, Info_level == "flower" |  Info_level == "capitulum")
-t_data_filtered <- as.data.frame(t_data_filtered)
-colnames(t_data_filtered)[1] <- "Plant_species"
-#select columns of interest
-traits <- t_data_filtered %>% dplyr::select(Species_geonet,Order_all,Family_all,Genus_all,Species_all,Breeding_system,IMPUTED_Compatibility,Autonomous_selfing_level,Autonomous_selfing_level_data_type,Autonomous_selfing_level_fruit_set,Flower_morphology,Flower_symmetry,Flowers_per_plant,Flowers_per_inflorescence,Floral_unit_width,Corolla_diameter_mean,Corolla_length_mean,STYLE_IMPUTED,OVULES_IMPUTED,life_form,lifespan,IMPUTED_plant_height_mean_m)
-#Remove duplicated species
-t <- traits[!duplicated(traits$Species_all), ]
-colnames(t)[1] <- "Plant_species"
-
-#MERGE NETWORK AND TRAIT DATA
-long_format_trait_data <- merge(long_d_2, t, by = "Plant_species", all.x =T)
[…]

### 2021-04-02 Scripts/7_2_Analysis_Bee_Visitation/4_Analysis_Z_scores_Guilds_FunctionalG_Bees.R

@@ -1,158 +1,0 @@
-########################################################################################################################################################
-#SCRIPT FOR ANALYSIS (Z-SCORES~FUNCTIONAL GROUP*GUILD) ##HCLUST## REPEATING ANALYSIS WITHOUT APIS MELLIFERA
-
-#1)LOAD DATA 
-
-#2)PHYLOGENETIC DISTANCE OF THE SPECIES -Add them as covariable-
-
-#3)SAVE MODEL
-
-#4)PLOT OUTPUT NICELY
-########################################################################################################################################################
-
-#LOAD LIBRARIES
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distance
-library(DHARMa)
-library(brms)
-library(cmdstanr)
-library(ggplot2)
-
-########################################################################################################################################################
-#1) READ DATA
-########################################################################################################################################################
-setwd("~/R_Projects/Reproductive Traits")
-
-d_5 <- read.csv("Data/Csv/quantitative_networks_Z_scores_with_traits_and_5_clusters_hclust_all_bee.csv", row.names = 1)
-########################################################################################################################################################
-#2) PHYLOGENETIC DISTANCE OF THE SPECIES
-########################################################################################################################################################
-
-#5 CLUSTERS
-#Prepare species, genus anD_5 family for calculating phylogenetic distance
-d_5$Family_all <- as.character(d_5$Family_all)
-d_5$Genus_all <- as.character(d_5$Genus_all)
-d_5$Plant_species <- as.character(d_5$Plant_species)
-
-#Make these NA's as NA
-d_5$Plant_species[d_5$Plant_species=="NA"] <- NA
-d_5$Family_all[d_5$Family_all=="NA"] <- NA
-d_5$Genus_all[d_5$Genus_all=="NA"] <- NA
-#remove NA's
-d_5_1 <- d_5[!is.na(d_5$Family_all),]
-d_5_1 <- d_5[!is.na(d_5$Plant_species),]
-d_5_1 <- d_5[!is.na(d_5$Genus_all),]
-
-d_5_1 <- subset(d_5_1, bee_family!="Melittidae")
-d_5_1$bee_family <- factor(d_5_1$bee_family)
-levels(d_5_1$bee_family)
-
-
-#prepare dataframe to calculate tree
[…]

### 2021-04-02 Scripts/7_Analysis_All_Species_PPCA.R

@@ -1,334 +1,0 @@
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE PCA
-
-#1) LOAD DATA 
-
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(tidyverse)
-
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(1)),
-           axis.text=element_text(size = rel(0.8), color = "black"),
-           legend.title=element_text(face="bold"),
-           legend.text=element_text(),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(0.5, 'lines'),
-           panel.border=element_rect(color="black",size=1),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-
-########################################################################################################################################################
-########################################################################################################################################################
-########################################################################################################################################################
-########################################################################################################################################################
-########################################################################################################################################################
[…]

### 2021-04-02 Scripts/9_ANALYSIS_PCA_LOADINGS.R

@@ -1,150 +1,0 @@
-########################################################################################################################################################
-#Analysis of how visitation and specialization changes with the two principal components
-########################################################################################################################################################
-
-#Load libraries
-library(brms)
-library(cmdstanr)
-library(cowplot) #panel of plots
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(1.3)),
-           axis.text=element_text(size = rel(1.5), color = "black"),
-           legend.title=element_text(face="bold"),
-           legend.text=element_text(),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(0.4, 'lines'),
-           panel.border=element_rect(color="black",size=1),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-########################################################################################################################################################################
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-########################################################################################################################################################################
-#LOAD DATA
-data <- read.csv("Data/Csv/metric_analysis_data_3rd_question.csv", row.names = 1) # data with specialization and integer of visits
-head(data) #Check data
-#Now we obtain the loadings from the global PCA which is likely to define better in the trait space the species
-phyl_pca_2 <- readRDS("Data/RData/phyl_pca_forest.rds")
-########################################################################################################################################################################
-#PROCESS DATA BEFORE MODELLING
[…]

### 2021-04-02 Main_Figures/Global_trait_spectrum.Rmd
Fig 1 and fig 2

@@
 
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4, xmax = -2.9,ymin = 2.45, ymax = 4.35)+
-     annotation_raster(style_l_1, xmin = 2.45, xmax = 3.25,ymin = 2.25, ymax = 3.35) +
-    annotation_raster(style_s_1, xmin = -3.05, xmax = -2.25,ymin = -2.65, ymax = -1.75) +
+  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4, xmax = -2.85,ymin = 2.05, ymax = 3.95)+
+     annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
+    annotation_raster(style_s_1, xmin = -2.7, xmax = -2,ymin = -2.65, ymax = -1.7) +
     annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
@@
     annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.60, xmax = -3.15,ymin = 1, ymax = 2.15) +
+    annotation_raster(many_flowers_1, xmin = -4.60, xmax = -3.15,ymin = 0.9, ymax = 2.05) +
     annotation_raster(large_flower_1, xmin = 3.4, xmax = 4.2,ymin = 1, ymax = 2.1) +
@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.5,5.5,7.5,7.3,6)), y = -(PCAloadings$PC2*c(4.77,2.4,3,6.5,5,5.5)),
+ plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.5,5.5,7.25,7.3,6.15)), y = -(PCAloadings$PC2*c(4.77,2.4,3,6.2,5,5.5)+c(0,0,0,0,0.4,0)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=5)

### 2021-04-02 Main_Figures/Global_trait_spectrum_Qualitative_Vars.Rmd
Fig 1 and fig 2

--- 2021-03-16 Figures/PPCA_Qualitative_Vars.Rmd
@@
 #Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca.rds")
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
 phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
@@
   dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Compatibility <- dat_cleaning_5$IMPUTED_Compatibility
+  dat$Compatibility <- dat_cleaning_5$Compatibility_system
   dat$Compatibility <- as.character(dat$Compatibility)

### 2021-04-02 Figures/BRMS_Funcional_Groups_X_PPCA.Rmd
Fig 1, 2 and 3 ready. 1 still needs edits on the images... Waiting for the pictures to be made.

@@
   ylim(0,quantile(dat$Interaction, 0.95)) + ylab("")+
-  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))
+  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"), labels=c("Bees","Coleoptera", "Lepidoptera", "Non−bee−Hymenoptera", "Non−syrphids−Diptera", "Syrphids"))
 

### 2021-04-02 Main_Figures/Analysis_1_Visits-Poll_Func_Groups_X_Pcs.Rmd
Figures ready just waiting for image for figure 1, now results and dicussion

---
output:
  pdf_document: default
  html_document: default
classoption: landscape

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=8, fig.width=28}

#LOAD LIBRARIES 
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(tidyverse)
library(patchwork) #panel of plots
library(brms)
library(cmdstanr)

#Load theme for publication

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2.2)),
           axis.text=element_text(size = rel(2), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.4)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(1.8, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank()
     ))
}

setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github

#Plot nicely PC1
analysis_1 <- readRDS("results_analysis_1.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1.rds")

#INVERT AXES FOR PLOTTING
#ON THE GLOBAL SPECTRUM THEY ARE INVERTED SO IS GOING TO BE EASIER TO UNDERSTAND THE RESULTS IF I DO THE SAME HERE
#DOES NOT CHANGE THE RELATIONSHIPS

ce_pc1 <- conditional_effects(analysis_1, effects = "PC1:guild",points=T)

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
   aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphids-Diptera", "Syrphids"))
#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:guild",points=T)

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphids-Diptera", "Syrphids"))

#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1, effects = "PC3:guild",points=T)

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphids-Diptera", "Syrphids"))

combined <- p1 + p2 + p3 & theme(legend.position = "right")
combined + plot_layout(guides = "collect")

```

### 2021-04-02 Main_Figures/Analysis_2_Visits_Plant_Level_PCs.Rmd
Figures ready just waiting for image for figure 1, now results and dicussion

---
output:
  pdf_document: default
  html_document: default
classoption: landscape

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=20}

#LOAD LIBRARIES 
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(tidyverse)
library(patchwork) #panel of plots
library(brms)
library(cmdstanr)

#Load theme for publication

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2)),
           axis.text=element_text(size = rel(1.75), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.4)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(1.8, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank()
     ))
}

setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github

Visits_PCs <- readRDS("results_analysis_2_Visits.rds") #load model
Specialization_PCs <- readRDS("results_analysis_2_Specialization.rds") #load model

setwd("~/R_Projects/Reproductive Traits") #setwd to load data
data_analysis_2 <- readRDS("Data/RData/data_analysis_2.rds") #load data

ce_1 <- conditional_effects(Visits_PCs, effects = "PC1",points=T) 
colnames(ce_1[[1]])[3] <- "Interaction"

Visits_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = Visits),
  size = 2.5, alpha=0.5) + geom_line(colour="darkblue",size=1.2) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+ xlab("PC1") +
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="darkblue") + ylab("Number of visits")

ce_2 <- conditional_effects(Visits_PCs, effects = "PC2",points=T) 
colnames(ce_2[[1]])[3] <- "Interaction"

Visits_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = Visits),
  size = 2.5, alpha=0.5) + geom_line(colour="darkblue",size=1.2) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+ xlab("PC2") +
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="darkblue") + ylab("")

ce_3 <- conditional_effects(Visits_PCs, effects = "PC3",points=T) 
colnames(ce_3[[1]])[3] <- "Interaction"

Visits_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = Visits),
  size = 2.5, alpha=0.5) + geom_line(colour="darkblue",size=1.2) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+ xlab("PC3") +
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="darkblue") + ylab("")

#Visits_PC1 + Visits_PC2 + Visits_PC3 & theme(legend.position = "right")

ce_1 <- conditional_effects(Specialization_PCs, effects = "PC1",points=T) 
colnames(ce_1[[1]])[3] <- "Interaction"

Specialization_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = d),
  size = 2.5, alpha=0.5) + geom_line(colour="brown4",size=1.2) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+ xlab("PC1") +
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="brown4") + ylab("Specialization (d')")

ce_2 <- conditional_effects(Specialization_PCs, effects = "PC2",points=T) 
colnames(ce_2[[1]])[3] <- "Interaction"

Specialization_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = d),
  size = 2.5, alpha=0.5) + geom_line(colour="brown4",size=1.2) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+ xlab("PC2") +
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="brown4") + ylab("")

ce_3 <- conditional_effects(Specialization_PCs, effects = "PC3",points=T) 
colnames(ce_3[[1]])[3] <- "Interaction"

Specialization_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = d),
  size = 2.5, alpha=0.5) + geom_line(colour="brown4",size=1.2) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+ xlab("PC3") +
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="brown4") + ylab("")

Visits_PC1 + Visits_PC2 + Visits_PC3+Specialization_PC1 + Specialization_PC2 + Specialization_PC3 & theme(legend.position = "right")

```

### 2021-04-02 Scripts/5_Analysis_1_Visits-Poll_groups_X_PCS.R

@@ -109,18 +109,24 @@ saveRDS(dat_analysis, "Data/RData/dat_analysis_results_analysis_1.rds")
 analysis_1 <- readRDS("results_analysis_1.rds")
 dat_analysis <- readRDS("dat_analysis_results_analysis_1.rds")
 
+
+#INVERT AXES FOR PLOTTING
+#ON THE GLOBAL SPECTRUM THEY ARE INVERTED SO IS GOING TO BE EASIER TO UNDERSTAND THE RESULTS IF I DO THE SAME HERE
+#DOES NOT CHANGE THE RELATIONSHIPS 
+
+
 ce_pc1 <- conditional_effects(analysis_1, effects = "PC1:guild",points=T) 
 
 p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
    aes(x = -PC1, y = Interaction),size = 0.75, alpha=0.5) + geom_line(size=0.8) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
   theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))
 #Plot nicely PC2
 ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:guild",points=T) 
 
 p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
   aes(x = -PC2, y = Interaction),size = 0.75, alpha=0.5) + geom_line(size=0.8) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC2")+
   theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))
 
 #Plot nicely PC3
@@ -128,7 +134,11 @@ ce_pc3 <- conditional_effects(analysis_1, effects = "PC3:guild",points=T)
 
[…]

### 2021-04-07 Supplementary_Material/Table_1_List_of_Studies.Rmd
Table s1 with all studies and information about the type of networks that contains

---
title: ""
output:
  pdf_document: default
  html_document: default
---
\begin{landscape}

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,}
setwd("~/R_Projects/Reproductive Traits")
library(kableExtra)

#Create data.frame with references

`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1", "1", "1", "1", "1", "1", "1", "3", "1",
                          "1", "1")

`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))

`Network type` <- c(rep("Weighted",  18), rep("Unweighted",  4), "Weighted", "Unweighted", "Unweighted", "Unweighted", "Unweighted", "Weighted")

`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard", "Bek", "Kato", "Kevan", "Ramirez",
                    "Inouye","McMullen", "Primack", "Ramirez", "Robertson", "Traveset")

Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003,2006,2000,1970,1989,1990, 1993, 1983, 1992, 1929, 2013)

Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", "Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", "Ecuador", "New Zealand", "Venezuela",
"USA", "Ecuador")

DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
"https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
"https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
"/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
"https://doi.org/10.1111/j.1365-2745.2010.01732.x", "https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510",
"https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis", "Unpublished, Master thesis", "http://hdl.handle.net/2433/156116",
"https://doi.org/10.2307/2258569", "https://doi.org/10.2307/2388282", "http://hdl.handle.net/2433/156099", "https://biostor.org/reference/244737", "https://doi.org/10.1080/0028825X.1983.10428561",
"https://doi.org/10.1111/j.1095-8339.1992.tb00294.x", "https://doi.org/10.5962/bhl.title.11538", "https://doi.org/10.1098/rspb.2012.3040")

references <- data.frame(`First author`, `Number of networks`, `Network type`, `Network structure`, Year, Country, DOI)

colnames(references) <- c("First author", "Network N°", "Type", "Structure", "Year", "Country", "DOI")

kable(references, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 9, full_width=F)
```

\end{landscape}

### 2021-04-07 Tables/Table_List_of_Studies.R

@@ -1,0 +1,38 @@
+#####
+#Table with the list of 28 plant-pollinator studies and their network contribution 
+#####
+
+#Create data.frame with references
+
+`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1", "1", "1", "1", "1", "1", "1", "3", "1",
+                          "1", "1")
+
+`Network structure` <- c(rep("Unique", 22), rep("Metaweb",6))
+
+`Network type` <- c(rep("Weighted",  18), rep("Unweighted",  4), "Weighted", "Unweighted", "Unweighted", "Unweighted", "Unweighted", "Weighted")
+
+
+`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
+                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard", "Bek", "Kato", "Kevan", "Ramirez",
+                    "Inouye","McMullen", "Primack", "Ramirez", "Robertson", "Traveset")
+
+Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003,2006,2000,1970,1989,1990, 1993, 1983, 1992, 1929, 2013)
+
+Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", "Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
+"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", "Ecuador", "New Zealand", "Venezuela",
+"USA", "Ecuador")
+
+DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
+"https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
[…]

### 2021-04-07 Supplementary_Material/Table_1_List_of_Studies.Rmd
last edits

@@
 ---
-\begin{landscape}
 
@@
 
-Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", "Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
-"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", "Ecuador", "New Zealand", "Venezuela",
-"USA", "Ecuador")
+#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
+#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
+#"USA", "Ecuador")
 
@@
 
-references <- data.frame(`First author`, `Number of networks`, `Network type`, `Network structure`, Year, Country, DOI)
+references <- data.frame(`First author`, `Number of networks`, `Network type`, `Network structure`, Year,  DOI)
 
-colnames(references) <- c("First author", "Network N°", "Type", "Structure", "Year", "Country", "DOI")
+colnames(references) <- c("First author", "N°", "Type", "Structure", "Year",  "DOI")
 
 kable(references, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 9, full_width=F)
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 8, full_width=F)
 ```
-
-\end{landscape}

### 2021-04-07 Main_Figures/Global_trait_spectrum.Rmd
Fig 1, 2 and 3 ready. 1 still needs edits on the images... Waiting for the pictures to be made.
Last edits

@@
 library(magick)
+
+#Images were made by Paula Martin
+#Check her work on https://paulamartinart.com/
+
 tree <- image_read("Images/PPCA_Plot/Tree.png")
@@
 
-selfing_h <- image_read("Images/PPCA_Plot/Selfing_High.png")
+selfing_h <- image_read("Images/PPCA_Plot/selfing.png")
 selfing_h_1 <- as.raster(selfing_h)
@@
 
-many_flowers <- image_read("Images/PPCA_Plot/Many_Flowers.png")
+many_flowers <- image_read("Images/PPCA_Plot/Inflorescencia.png")
 many_flowers_1 <- as.raster(many_flowers)
@@
 
-large_flower <- image_read("Images/PPCA_Plot/Large_Flower.png")
+large_flower <- image_read("Images/PPCA_Plot/flower_big.png")
 large_flower_1 <- as.raster(large_flower)
 
-flower_small <- image_read("Images/PPCA_Plot/Flower_Small.png")
+flower_small <- image_read("Images/PPCA_Plot/flower_short.png")
 flower_small_1 <- as.raster(flower_small)
+
+herb <- image_read("Images/PPCA_Plot/herb.png")
+herb_1 <- as.raster(herb)
+
 #############################################################################################################################################################
@@
      annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
-    annotation_raster(style_s_1, xmin = -2.7, xmax = -2,ymin = -2.65, ymax = -1.7) +
+    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
     annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
     annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.2, xmax = 1.2,ymin = 2.8, ymax = 4.7) +
-    annotation_raster(selfing_h_1, xmin = -0.95, xmax = 0,ymin = -4.1, ymax = -3.25) +
+    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
+    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -4.1, ymax = -3.25) +
     annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.60, xmax = -3.15,ymin = 0.9, ymax = 2.05) +
-    annotation_raster(large_flower_1, xmin = 3.4, xmax = 4.2,ymin = 1, ymax = 2.1) +
-    annotation_raster(flower_small_1, xmin = -4, xmax = -1.85,ymin = -2.4, ymax = -0.4) +
-    annotation_raster(single_flower_1, xmin = 2.8, xmax = 3.5,ymin = -2.8, ymax = -2.2)
+    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.35,ymin = 0.8, ymax = 1.45) +
+    annotation_raster(large_flower_1, xmin = 3.25, xmax = 4.25,ymin = 1.2, ymax = 2.45) +
+    annotation_raster(flower_small_1, xmin = -3.60, xmax = -2.55,ymin = -2.2, ymax = -1.60) +
+    annotation_raster(herb_1, xmin = 2.6, xmax = 3.1,ymin = -2.8, ymax = -2)
 

### 2021-04-08 Main_Figures/Global_trait_spectrum.Rmd
Supp mat

@@
 
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4, xmax = -2.85,ymin = 2.05, ymax = 3.95)+
+  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
      annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
@@
     annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.35,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.25, xmax = 4.25,ymin = 1.2, ymax = 2.45) +
-    annotation_raster(flower_small_1, xmin = -3.60, xmax = -2.55,ymin = -2.2, ymax = -1.60) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3.1,ymin = -2.8, ymax = -2)
+    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
+    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
+    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
+    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
 
       #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
+  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
 

### 2021-04-09 Main_Figures/Global_trait_spectrum.Rmd
last edits

@@
   # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.6, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
 
   #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.2, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
 
@@
     annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -4.1, ymax = -3.25) +
+    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
     annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.5,5.5,7.25,7.3,6.15)), y = -(PCAloadings$PC2*c(4.77,2.4,3,6.2,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=5)
+ plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,7.25,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.4,3,6.2,5,5.5)+c(0,0,0,0,0.4,0)),
+                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
 

### 2021-04-09 Main_Figures/Global_trait_spectrum_Qualitative_Vars.Rmd
last edits

@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
-                          label = PCAloadings$Variables, color="black",size=3.2)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
+                          label = PCAloadings$Variables, color="black",size=3)
 
@@
   dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-    dat$`Life span` <- dat_cleaning_5$lifespan
-    dat$`Life span` <- as.character(dat$`Life span`)
+    dat$Lifespan <- dat_cleaning_5$lifespan
+    dat$Lifespan <- as.character(dat$Lifespan)
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Life span`),size=1.5)+scale_color_manual(values=c("sienna4","forestgreen"))
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Lifespan),size=1.5)+scale_color_manual(values=c("sienna4","forestgreen"))
 
@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
-                          label = PCAloadings$Variables, color="black",size=3.2)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
+                          label = PCAloadings$Variables, color="black",size=3)
 
+  #CHANGE THEME
   #CHANGE THEME
@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
-                          label = PCAloadings$Variables, color="black",size=3.2)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
+                          label = PCAloadings$Variables, color="black",size=3)
+
+  #CHANGE THEME
 

### 2021-04-09 Scripts/1_Merge_Spp_Names_Long_format.R

@@ -1011,19 +1011,33 @@ na <- all_long_poll_names[is.na(all_long_poll_names$guild),]
 #Aggregate by poll guild
 all_poll <- reshape2::dcast(Plant_species + guild +Id ~ "Interaction", value.var = "Interaction", fun.aggregate = sum, data = all_long_poll_names, na.rm= TRUE)
 head(all_poll)
-b <- subset(all_long_poll_names, guild=="Bee")
-table(b$genus)
-#Save for repeating analysis without apis mellifera
-all_long_poll_names_non_apis <- subset(all_long_poll_names, genus!="apis")
-all_poll_non_apis <- reshape2::dcast(Plant_species + guild +Id ~ "Interaction", value.var = "Interaction", fun.aggregate = sum, data = all_long_poll_names_non_apis, na.rm= TRUE)
+
+#Add pollinator guilds for analysis
+all_long_poll_names$bee_family[all_long_poll_names$family=="Apidae"] <- "Apidae"
+all_long_poll_names$bee_family[all_long_poll_names$family=="Megachilidae"] <- "Megachilidae"
+all_long_poll_names$bee_family[all_long_poll_names$family=="Halictidae"] <- "Halictidae"
+all_long_poll_names$bee_family[all_long_poll_names$family=="Andrenidae"] <- "Andrenidae"
+all_long_poll_names$bee_family[all_long_poll_names$family=="Colletidae"] <- "Colletidae"
+all_long_poll_names$bee_family[all_long_poll_names$family=="Melittidae"] <- "Melittidae"
+all_long_poll_names$bee_family[all_long_poll_names$family=="Stenotritidae"] <- "Stenotritidae"
+
+head(all_long_poll_names)
+all_bee_family <- all_long_poll_names[!is.na(all_long_poll_names$bee_family),]
+
+head(all_bee_family)
+levels(as.factor(all_bee_family$bee_family))
+#Aggregate by poll guild
+all_bee <- reshape2::dcast(Plant_species + bee_family +Id ~ "Interaction", value.var = "Interaction", fun.aggregate = sum, data = all_bee_family, na.rm= TRUE)
+head(all_bee)
+
 
 ########################################################################################################################################################
 #3)SAVE DATA
 ########################################################################################################################################################
 #save poll guild data
 write.csv(all_poll, "Data/Csv/long_format_quantitative_networks.csv")
-#save poll guild data without apis
[…]

### 2021-04-09 Scripts/3_PPCA.R

@@ -122,7 +122,9 @@ PC$L
 
 nrow(PC$S)
 
+percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
 
+sum(percentage[1]+percentage[2])
 ########################################################################################################################################################
 #4) PLOT PPCA
 ########################################################################################################################################################
@@ -136,6 +138,7 @@ nrow(PC$S)
 
 PC$S[,1] <- -PC$S[,1]
 PC$S[,2] <- -PC$S[,2]
+PC$S[,3] <- -PC$S[,]
 
 
 PCbiplot <- function(PC, x="PC1", y="PC2") {
@@ -244,3 +247,71 @@ PCbiplot <- function(PC, x="PC1", y="PC2") {
 
 
 PCbiplot(PC)
+
+############
+#PLOT WITH PC3
+############
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+PC$S[,1] <- -PC$S[,1]
+
+PCbiplot <- function(PC, x="PC1", y="PC3") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+  
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+  
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+  
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',colour='black') + 
+    scale_fill_continuous(low="green",high="red") 
+  
+  
+  plot <- plot + geom_point(data=dat, aes(x, y),size=0.65)+scale_color_manual(values=c("#fc2847", "#1cac78")) #+ #scale_color_viridis_c(option = "A", direction = 1, limits = c(min(dat$density), max(dat$density)))+
[…]

### 2021-04-09 Scripts/4_Data_Preparation_Analysis_1_Bees.R

@@ -1,0 +1,51 @@
+########################################################################################################################################################
+#SCRIPT TO PREPARE DATA FOR ANALYSIS 1) VISITS~ POLL. FUNCTIONAL GROUP*PRINCIPAL COMPONENTS
+########################################################################################################################################################
+#LOAD LIBRARIES
+library(data.table)
+########################################################################################################################################################
+#LOAD DATA
+########################################################################################################################################################
+long_d <- read.csv("Data/Csv/long_format_quantitative_networks_bees.csv", row.names = 1) #quantitative network data|weighted by frequency of visits per plant species
+phyl_pca <- readRDS("Data/RData/phyl_pca_forest.rds") #add PCA loadings for analysis
+dat_cleaning <- readRDS("Data/RData/data_all_species_PPCA.rds") #data for PPCA
+########################################################################################################################################################
+#PREPARE DATA
+########################################################################################################################################################
+#Select data with interaction greater than 0
+long_d_1 <- long_d[long_d$Interaction>0,]
+
+#Remove other orders/guilds that are not these ones
+long_d_2 <- long_d_1[!is.na(long_d_1$bee_family),] #I do it by guild because just these 6 guilds are named in this column
+
+#check levels
+levels(factor(long_d_2$bee_family)) #9 DIFFERENT GUILDS|After I'll select the main fucntional poll. groups for analysis
+
+#convert to dataframe the ppca data
+phyl_pca_1 <- data.frame(phyl_pca$S)
+
+#convert rownames to column
+dat_cleaning_1 <- setDT(dat_cleaning, keep.rownames = TRUE)[]
+colnames(dat_cleaning_1)[1] <- "Plant_species"
+
+phyl_pca_1$Plant_species <- dat_cleaning_1$Plant_species
+#ADD ALSO THESE OTHER 3 COLUMNS WITH SPP, GENUS AND FAMILY INFO NEEDED TO GET THE PHYLO FOR THE MODEL
+phyl_pca_1$Family_all <- dat_cleaning_1$Family_all
+phyl_pca_1$Genus_all <- dat_cleaning_1$Genus_all
+phyl_pca_1$Species_all <- dat_cleaning_1$Species_all
+
+#merge columns
+data_analysis <- merge(long_d_2, phyl_pca_1, by = "Plant_species")
+#Explore why some levels dropped
+#data_analysis <- merge(long_d_2, phyl_pca_1, by = "Plant_species", all.x = T)
[…]

### 2021-04-09 Main_Figures/Analysis_1_Separated.Rmd
Edits

---
output:
  pdf_document: default
  html_document: default
classoption: landscape

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28}

#LOAD LIBRARIES 
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(tidyverse)
library(patchwork) #panel of plots
library(brms)
library(cmdstanr)

#Load theme for publication

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2.2)),
           axis.text=element_text(size = rel(2), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.4)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(1.8, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank()
     ))
}

setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github

#Plot nicely PC1
analysis_1_just_bees <- readRDS("results_analysis_1_just_bees.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1_just_bees.rds")

ce_pc1 <- conditional_effects(analysis_1_just_bees, effects = "PC1",points=T) 
ce_pc1[[1]]$guild <- "bees"

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC2")+
  theme_ms() + theme(legend.position = "none")

#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1_just_bees, effects = "PC2",points=T) 
ce_pc1[[1]]$guild <- "bees"

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
  theme_ms() + theme(legend.position = "none") 
#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1_just_bees, effects = "PC3",points=T)
ce_pc1[[1]]$guild <- "bees"

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
  theme_ms() + theme(legend.position = "none")

#Plot nicely PC1
analysis_1_no_bees <- readRDS("results_analysis_1_no_bees.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1_no_bees.rds")

ce_pc1 <- conditional_effects(analysis_1_no_bees, effects = "PC1:guild",points=T)

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
   "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids"))

ce_pc2 <- conditional_effects(analysis_1_no_bees, effects = "PC2:guild",points=T)

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
   "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids"))
#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1_no_bees, effects = "PC3:guild",points=T)

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
  theme_ms() +theme(legend.position = "none") + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
               "Non-syrphids-diptera", "Syrphids"))

library(patchwork)

combined <- p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "right")
combined + plot_layout(guides = "collect",ncol = 3)

```

### 2021-04-09 Supplementary_Material/Figure_Analysis_Bees_Apis_Non_Apis.Rmd
Edits

---
output:
  pdf_document: default
  html_document: default

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24}

#LOAD LIBRARIES 
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(tidyverse)
library(patchwork) #panel of plots
library(brms)
library(cmdstanr)

#Load theme for publication

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2.2)),
           axis.text=element_text(size = rel(2), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.4)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(1.8, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank()
     ))
}

setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github

#Plot nicely PC1
analysis_1 <- readRDS("results_analysis_1_bee_families.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1_bee_families.rds")

ce_pc1 <- conditional_effects(analysis_1, effects = "PC1:bee_family",points=T)

a1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))+ggtitle("All bee species") + theme(plot.title = element_text(size = 36, face = "bold"))
#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:bee_family",points=T)

a2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))

#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1, effects = "PC3:bee_family",points=T)

a3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))

analysis_1_bee_families_non_apis <- readRDS("results_analysis_1_bee_families_non_apis.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1_bee_families_non_apis.rds")

ce_pc1 <- conditional_effects(analysis_1_bee_families_non_apis, effects = "PC1:bee_family",points=T)

aa1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))+ ggtitle("A. mellifera excluded") + theme(plot.title = element_text(size = 36, face = "bold"))
#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1_bee_families_non_apis, effects = "PC2:bee_family",points=T)

aa2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))

#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1_bee_families_non_apis, effects = "PC3:bee_family",points=T)

aa3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
  theme_ms() + theme(legend.position = "none")+  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))

analysis_1_just_bees <- readRDS("results_analysis_1_just_bees.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1_just_bees.rds")

ce_pc1 <- conditional_effects(analysis_1_just_bees, effects = "PC1",points=T) 
ce_pc1[[1]]$guild <- "bees"

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
  theme_ms() + theme(legend.position = "none") + ggtitle("All bee species")+
  theme(plot.title = element_text(size = 36, face = "bold"))

#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1_just_bees, effects = "PC2",points=T) 
ce_pc1[[1]]$guild <- "bees"

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
  theme_ms() + theme(legend.position = "none") 
#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1_just_bees, effects = "PC3",points=T)
ce_pc1[[1]]$guild <- "bees"

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
  theme_ms() + theme(legend.position = "none")

analysis_1_just_bees_non_apis <- readRDS("results_analysis_1_just_bees_non_apis.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1_just_bees.rds")

ce_pc1 <- conditional_effects(analysis_1_just_bees_non_apis, effects = "PC1",points=T) 
ce_pc1[[1]]$guild <- "bees"

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis,
      aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange")+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
  theme_ms() + theme(legend.position = "none") + ggtitle("A. mellifera excluded") + theme(plot.title = element_text(size = 36, face = "bold"))

#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1_just_bees_non_apis, effects = "PC2",points=T) 
ce_pc1[[1]]$guild <- "bees"

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,
                                                                          aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
  theme_ms() + theme(legend.position = "none") 
#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1_just_bees_non_apis, effects = "PC3",points=T)
ce_pc1[[1]]$guild <- "bees"

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis,
                                                                          aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
  theme_ms() + theme(legend.position = "none")

library(patchwork)

combined <- a1 + a2 + a3 + aa1 + aa2 + aa3 + p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "right")
combined + plot_layout(guides = "collect", ncol=3)

```

### 2021-04-09 Scripts/4_Data_Preparation_Analysis_1_Non_Apis.R

@@ -1,0 +1,51 @@
+########################################################################################################################################################
+#SCRIPT TO PREPARE DATA FOR ANALYSIS 1) VISITS~ POLL. FUNCTIONAL GROUP*PRINCIPAL COMPONENTS
+########################################################################################################################################################
+#LOAD LIBRARIES
+library(data.table)
+########################################################################################################################################################
+#LOAD DATA
+########################################################################################################################################################
+long_d <- read.csv("Data/Csv/long_format_quantitative_networks_non_apis.csv", row.names = 1) #quantitative network data|weighted by frequency of visits per plant species
+phyl_pca <- readRDS("Data/RData/phyl_pca_forest.rds") #add PCA loadings for analysis
+dat_cleaning <- readRDS("Data/RData/data_all_species_PPCA.rds") #data for PPCA
+########################################################################################################################################################
+#PREPARE DATA
+########################################################################################################################################################
+#Select data with interaction greater than 0
+long_d_1 <- long_d[long_d$Interaction>0,]
+
+#Remove other orders/guilds that are not these ones
+long_d_2 <- long_d_1[!is.na(long_d_1$guild),] #I do it by guild because just these 6 guilds are named in this column
+
+#check levels
+levels(factor(long_d_2$guild)) #9 DIFFERENT GUILDS|After I'll select the main fucntional poll. groups for analysis
+
+#convert to dataframe the ppca data
+phyl_pca_1 <- data.frame(phyl_pca$S)
+
+#convert rownames to column
+dat_cleaning_1 <- setDT(dat_cleaning, keep.rownames = TRUE)[]
+colnames(dat_cleaning_1)[1] <- "Plant_species"
+
+phyl_pca_1$Plant_species <- dat_cleaning_1$Plant_species
+#ADD ALSO THESE OTHER 3 COLUMNS WITH SPP, GENUS AND FAMILY INFO NEEDED TO GET THE PHYLO FOR THE MODEL
+phyl_pca_1$Family_all <- dat_cleaning_1$Family_all
+phyl_pca_1$Genus_all <- dat_cleaning_1$Genus_all
+phyl_pca_1$Species_all <- dat_cleaning_1$Species_all
+
+#merge columns
+data_analysis <- merge(long_d_2, phyl_pca_1, by = "Plant_species")
+#Explore why some levels dropped
+#data_analysis <- merge(long_d_2, phyl_pca_1, by = "Plant_species", all.x = T)
[…]

### 2021-04-09 Scripts/5_Analysis_1_Visits-Poll_groups_Non_Apis.R

@@ -1,0 +1,190 @@
+########################################################################################################################################################
+# SCRIPT FOR ANALYSIS 1 VISITS~ POLL. FUNCTIONAL GROUP*PRINCIPAL COMPONENTS
+########################################################################################################################################################
+#LOAD LIBRARIES
+library(phytools)
+library(ape) #for phylogenetic distance
+library(dplyr) #data processing
+library(rtrees) #for phylogenetic distancelibrary(MASS)
+library(reshape2)
+library(viridis) #COLOUR GGPLOT
+library(MASS)
+library(ggplot2)
+library(broman) #crayon colours
+library(tidyverse)
+library(brms)
+library(DHARMa)
+library(cmdstanr)
+library(emmeans)
+library(tidybayes)
+#LOAD THEME FOR PLOTTING
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(1.3)),
+           axis.text=element_text(size = rel(1), color = "black"),
+           legend.title=element_text(face="bold"),
+           legend.text=element_text(),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(0.9, 'lines'),
+           panel.border=element_rect(color="black",size=1),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank()
+     ))
+}
+########################################################################################################################################################
+#1) READ DATA
+########################################################################################################################################################
+d_a <- readRDS("Data/RData/data_analysis_1_non_apis.rds") #ALL SPP
+########################################################################################################################################################
+#PREPARE POLL. FUNCTIONAL GROUPS FOR MODELLING
[…]

### 2021-04-13 Supplementary_Material/Qualitative_PCA_Associations.Rmd
PPCA qualitative

---
output:
  pdf_document: default
  html_document: default

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=14}

########################################################################################################################################################
#CORRELATION BETWEEN QUALITATIVE VARIABLES AND PC's
########################################################################################################################################################
#NOTES
#I did not include the qualitative variables when I prepare the data for the PPCA
#So I have to recalculate the ata here with the qualitative variables
########################################################################################################################################################
#LOAD LIBRARIES
library(emmeans)
library(ggplot2)
library(patchwork)
library(dplyr)

theme_ms <- function(base_size=10, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(1.3)),
           axis.text=element_text(size = rel(1.1), color = "black"),
           panel.border=element_rect(color="black",size=1.2),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank(),
           legend.position = "none",
           plot.title = element_text(face = "bold",size = rel(1.45)),
           plot.subtitle = element_text(face = "bold",size = rel(1.3))
     ))
}

########################################################################################################################################################
setwd("~/R_Projects/Reproductive Traits")

#LOAD DATA
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
dat <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
########################################################################################################################################################
#remove not found species, cannot do PCA with unequal numbers of rows
cols.num <- c("Family_all","Genus_all","Species_all")
dat[cols.num] <- sapply(dat[cols.num],as.character)
dat$Species_all <- gsub("Species_all_", "", dat$Species_all)
########################################################################################################################################################
#3) REMOVE OUTLIERS, OUT OF 2.5-97.5 RANGE WHICH HELPS IMPUTATION PROCESS. SEE ARTICLE FOR REF.
########################################################################################################################################################
dat_cleaning <- dat[,]
#CHECK LEVELS

dat_cleaning_1 <- dat_cleaning %>%
  filter(between(Flowers_per_plant, quantile(Flowers_per_plant, 0.025), quantile(Flowers_per_plant, 0.975)))

dat_cleaning_2 <- dat_cleaning_1 %>%
  filter(between(Corolla_diameter_mean, quantile(Corolla_diameter_mean, 0.025), quantile(Corolla_diameter_mean, 0.975)))

dat_cleaning_3 <- dat_cleaning_2 %>%
  filter(between(Style_length, quantile(Style_length, 0.025), quantile(Style_length, 0.975)))

dat_cleaning_4 <- dat_cleaning_3 %>%
  filter(between(Ovule_number, quantile(Ovule_number, 0.025), quantile(Ovule_number, 0.975)))

dat_cleaning_5 <- dat_cleaning_4 %>%
  filter(between(Plant_height_mean_m, quantile(Plant_height_mean_m, 0.025), quantile(Plant_height_mean_m, 0.975)))

final_d <- dat_cleaning_5[,]

pca_data <- as.data.frame(phyl_pca_forest$S)

d <- cbind(final_d, pca_data)

#Prepare qualitative variables
d$Compatibility_system[d$Compatibility_system=="dioecious"] <- "Unisexual flowers"
d$Compatibility_system[d$Compatibility_system=="monoecious"] <- "Unisexual flowers"
d$Compatibility_system[d$Compatibility_system=="partially_self_compatible"] <- "Partially self compatible"
d$Compatibility_system[d$Compatibility_system=="self_compatible"] <- "Self compatible"
d$Compatibility_system[d$Compatibility_system=="self_incompatible"] <- "Self incompatible"
d$Compatibility_system <- factor(d$Compatibility_system, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))

d$life_form[d$life_form=="herb"] <- "Herb"
d$life_form[d$life_form=="shrub"] <- "Shrub"
d$life_form[d$life_form=="tree"] <- "Tree"
d$life_form[d$life_form=="vine"] <- "Shrub"

d$Flower_symmetry[d$Flower_symmetry=="actinomorphic"] <- "Actinomorphic"
d$Flower_symmetry[d$Flower_symmetry=="zygomorphic"] <- "Zygomorphic"

d$Flower_symmetry[d$Flower_symmetry=="Funnelform"] <- "Campanulate"
d$Flower_symmetry[d$Flower_symmetry=="Spike"] <- "Brush"

d$Flower_morphology[d$Flower_morphology=="Funnelform"] <- "Campanulate"
d$Flower_morphology[d$Flower_morphology=="Spike"] <- "Brush"

d$Nectar_presence_absence[d$Nectar_presence_absence=="yes"] <- "Yes"
d$Nectar_presence_absence[d$Nectar_presence_absence=="no"] <- "No"

#The other qualitative are ok

#All principal components are normally distributed
#Convert to factor before running model
d[sapply(d, is.character)] <- lapply(d[sapply(d, is.character)], as.factor)

#Run model
model1 <- lm(PC1 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
model2 <- lm(PC2 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)

####################################################################################################################################################################################################################################
#1) BREEDING SYSTEM
####################################################################################################################################################################################################################################
model_breeding_1 <- emmeans(model1, "Breeding_system")
breeding_1 <- as.data.frame(model_breeding_1[1:3])
breed1 <- multcomp::cld(model_breeding_1, alpha = 0.10, Letters = LETTERS)

breed_1 <- ggplot(breed1,aes(x= Breeding_system,y= emmean,
               label = .group)) +theme_minimal()+
  geom_point(data = breed1, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "Breeding system")+
  theme(plot.title = element_text(hjust=0.5, size=25, face="bold"))+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

model_breeding_2 <- emmeans(model2, "Breeding_system")
breeding_2 <- as.data.frame(model_breeding_2[1:3])
breed2 <- multcomp::cld(model_breeding_2, alpha = 0.10, Letters = LETTERS)

breed_2 <- ggplot(breed2,aes(x= Breeding_system,y= emmean,
             label = .group)) +theme_minimal()+
  geom_point(data = breed2, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "Breeding system")+
  theme(plot.title = element_text(hjust=0.5,size=25, face="bold") )+
  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

########################################################################################################################################################
#2) COMPATIBILITY
########################################################################################################################################################
model_com <- emmeans(model1, "Compatibility_system")

d <- as.data.frame(model_com[1:4])
comp1 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)

comp_1 <- ggplot(comp1,aes(x= Compatibility_system,y= emmean,
  label = .group)) +theme_minimal()+
  geom_point(data = comp1, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
  width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "Compatibility system")+
  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")

model_com <- emmeans(model2, "Compatibility_system")
d <- as.data.frame(model_com[1:4])
comp2 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)

comp_2 <- ggplot(comp2,aes(x= Compatibility_system,y= emmean,
  label = .group)) +theme_minimal()+
  geom_point(data = comp2, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
  width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "Compatibility system")+
  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")

########################################################################################################################################################
#3) LIFESPAN
########################################################################################################################################################
model_lif_1 <- emmeans(model1, "lifespan")
lif_1 <- as.data.frame(model_lif_1[1:2])
lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)

lifespan_1 <- ggplot(lif_1,aes(x= lifespan,y= emmean,
             label = .group)) +theme_minimal()+
  geom_point(data = lif_1, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "Lifespan")+
  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

model_lif_2 <- emmeans(model2, "lifespan")
lif_2 <- as.data.frame(model_lif_2[1:2])
lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)

lifespan_2 <- ggplot(lif_2,aes(x= lifespan,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_2, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "Lifespan")+
  geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")

########################################################################################################################################################
# 4) LIFE FORM
########################################################################################################################################################

model_lif_1 <- emmeans(model1, "life_form")
lif_1 <- as.data.frame(model_lif_1[1:3])
lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)

lifeform_1 <- ggplot(lif_1,aes(x= life_form,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_1, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "Life form")+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

model_lif_2 <- emmeans(model2, "life_form")
lif_2 <- as.data.frame(model_lif_2[1:3])
lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)

lifeform_2 <- ggplot(lif_2,aes(x= life_form,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_2, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "Life form")+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

########################################################################################################################################################
# 5) FLOWER MORPHOLOGY
########################################################################################################################################################
model_flo_1 <- emmeans(model1, "Flower_morphology")
flo_1 <- as.data.frame(model_flo_1[1:6])
flo_1 <- multcomp::cld(model_flo_1, alpha = 0.10, Letters = LETTERS)

shape_1 <- ggplot(flo_1,aes(x= Flower_morphology,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_1, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "Flower shape")+
  geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")

model_flo_2 <- emmeans(model2, "Flower_morphology")
flo_2 <- as.data.frame(model_flo_2[1:6])
flo_2 <- multcomp::cld(model_flo_2, alpha = 0.10, Letters = LETTERS)

shape_2 <- ggplot(flo_2,aes(x= Flower_morphology,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_2, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "Flower shape")+
   geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")

########################################################################################################################################################
#6) FLOWER SYMMETRY
########################################################################################################################################################
model_flo_sym_1 <- emmeans(model1, "Flower_symmetry")
flo_sym_1 <- as.data.frame(model_flo_sym_1[1:2])
flo_sym_1 <- multcomp::cld(model_flo_sym_1, alpha = 0.10, Letters = LETTERS)

symmetry_1 <-ggplot(flo_sym_1,aes(x= Flower_symmetry,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_sym_1, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")

model_flo_sym_2 <- emmeans(model2, "Flower_symmetry")
flo_sym_2 <- as.data.frame(model_flo_sym_2[1:2])
flo_sym_2 <- multcomp::cld(model_flo_sym_2, alpha = 0.10, Letters = LETTERS)

symmetry_2 <- ggplot(flo_sym_2,aes(x= Flower_symmetry,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = flo_sym_2, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna2","purple"))+labs(title = "Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

########################################################################################################################################################
#7) NECTAR
########################################################################################################################################################
model_nec <- emmeans(model1, "Nectar_presence_absence")

model_nec_1 <- emmeans(model1, "Nectar_presence_absence")
nec_1 <- as.data.frame(model_nec_1[1:2])
nec_1 <- multcomp::cld(model_nec_1, alpha = 0.10, Letters = LETTERS)

nectar_1 <- ggplot(nec_1,aes(x= Nectar_presence_absence,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = nec_1, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("black","grey"))+labs(title = "Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

model_nec_2 <- emmeans(model2, "Nectar_presence_absence")
nec_2 <- as.data.frame(model_nec_2[1:2])
nec_2 <- multcomp::cld(model_nec_2, alpha = 0.10, Letters = LETTERS)

nectar_2 <-ggplot(nec_2,aes(x= Nectar_presence_absence,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = nec_2, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("black","grey"))+labs(title = "Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")

#PLOT!

breed_1 + breed_2+ comp_1+ comp_2+ lifespan_1+ lifespan_2+ lifeform_1+ lifeform_2+ shape_1+ shape_2+
symmetry_1+ symmetry_2+ nectar_1+ nectar_2 + plot_layout(ncol = 2)+ plot_annotation(tag_levels = c('A', ')'))

```

### 2021-04-14 Supplementary_Material/Bees_and_other_func_grous_separated.Rmd
edits

---
output:
  pdf_document: default
  html_document: default

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=24}

#LOAD LIBRARIES 
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(tidyverse)
library(patchwork) #panel of plots
library(brms)
library(cmdstanr)

#Load theme for publication

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2.2)),
           axis.text=element_text(size = rel(2), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.4)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(1.8, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank()
     ))
}

setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github

#Plot nicely PC1
analysis_1_just_bees <- readRDS("results_analysis_1_just_bees.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1_just_bees.rds")

ce_pc1 <- conditional_effects(analysis_1_just_bees, effects = "PC1",points=T)

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis, aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.3, colour="orange") + geom_line(size=1.5, colour="orange") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("")+
  theme_ms() + theme(legend.position = "none")

ce_pc2 <- conditional_effects(analysis_1_just_bees, effects = "PC2",points=T)

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.3, colour="orange") + geom_line(size=1.5, colour="orange") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none")

ce_pc3 <- conditional_effects(analysis_1_just_bees, effects = "PC3",points=T)

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis,aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.3, colour="orange") + geom_line(size=1.5, colour="orange") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("")+
  theme_ms() +theme(legend.position = "none")

analysis_1_no_bees <- readRDS("results_analysis_1_no_bees.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1_no_bees.rds")

ce_pc1 <- conditional_effects(analysis_1_no_bees, effects = "PC1:guild",points=T)

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
   "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids"))

ce_pc2 <- conditional_effects(analysis_1_no_bees, effects = "PC2:guild",points=T)

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
   "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids"))
#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1_no_bees, effects = "PC3:guild",points=T)

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
  theme_ms() +theme(legend.position = "none") + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
               "Non-syrphids-diptera", "Syrphids"))

library(patchwork)

combined <- p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "right")
combined + plot_layout(guides = "collect")

```

### 2021-04-14 Supplementary_Material/Global_trait_spectrum_PC3.Rmd
edits

--- 2021-04-09 Main_Figures/Global_trait_spectrum.Rmd
@@
 
-all_spp <- function(PC, x="PC1", y="PC2") {
+pc3 <- function(PC, x="PC1", y="PC3") {
   # PC being a prcomp object
@@
 
-    plot <- plot + geom_point(data=dat, aes(x, y),size=0.95, color="black")
+    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
 
@@
   plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+  plot <- plot + ylab(paste("PC3 ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
 
@@
 
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
-    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
-    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
-    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
-    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
+  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
+ #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
+ # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
+ # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
+ # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
+ # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
+ # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
+ # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
+ # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
+ # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
+ # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
+ # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
 
@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,7.25,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.4,3,6.2,5,5.5)+c(0,0,0,0,0.4,0)),
+ plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,5.75,7.3,5.5)), y = -(PCAloadings$PC2*c(-3.5,4,3.5,8,5,5.5)+c(0,0,0,0,-0.1,0)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=4)
@@
 
-plot_grid(all_spp(PC))
+pc3(PC)
 

### 2021-04-14 Scripts/5_Analysis_1_No_Bees.R

@@ -144,7 +144,7 @@ saveRDS(dat_analysis, "dat_analysis_results_analysis_1_no_bees.rds")
 #PLOT
 ########################################################################################################################################################
 #Plot nicely PC1
-analysis_1 <- readRDS("results_analysis_1_no_bees.rds")
+analysis_1_no_bees <- readRDS("results_analysis_1_no_bees.rds")
 dat_analysis <- readRDS("dat_analysis_results_analysis_1_no_bees.rds")
 
 ce_pc1 <- conditional_effects(analysis_1_no_bees, effects = "PC1:guild",points=T) 

### 2021-04-14 Scripts/5_Analysis_1_Visits-Poll_groups_Non_Apis.R

@@ -145,8 +145,8 @@ pp_check(analysis_1_non_apis, type='violin_grouped',group="guild")+ylim(-4,4)
 #Save data
 #Save output
 setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-saveRDS(analysis_1, "results_analysis_1.rds")
-saveRDS(dat_analysis, "dat_analysis_results_analysis_1.rds")
+saveRDS(analysis_1_non_apis, "results_analysis_1_non_apis.rds")
+saveRDS(dat_analysis, "dat_analysis_results_analysis_1_non_apis.rds")
 ########################################################################################################################################################
 #PLOT
 ########################################################################################################################################################
@@ -160,14 +160,14 @@ dat_analysis <- readRDS("dat_analysis_results_analysis_1.rds")
 #DOES NOT CHANGE THE RELATIONSHIPS 
 
 
-ce_pc1 <- conditional_effects(analysis_1, effects = "PC1:guild",points=T) 
+ce_pc1 <- conditional_effects(analysis_1_non_apis, effects = "PC1:guild",points=T) 
 
 p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
   aes(x = -PC1, y = Interaction),size = 0.75, alpha=0.5) + geom_line(size=0.8) + 
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
   theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))
 #Plot nicely PC2
-ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:guild",points=T) 
+ce_pc2 <- conditional_effects(analysis_1_non_apis, effects = "PC2:guild",points=T) 
 
 p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
   aes(x = -PC2, y = Interaction),size = 0.75, alpha=0.5) + geom_line(size=0.8) + 
[…]

### 2021-04-14 Scripts/trial_all_values/Analysis_poll_groups.R

@@ -122,12 +122,15 @@ dat_analysis$System[grepl("elberling_sweeden_1999", dat_analysis$System)] <- "el
 ########################################################################################################################################################
 
 
-
+str(dat_analysis)
 
 analysis_1 <- brm((Interaction-1) ~ PC1*guild + PC2*guild + PC3*guild +(1|System/Id) + (1|gr(phylo, cov = A)),
                   data = dat_analysis, family  = zero_inflated_negbinomial(),data2 = list(A = A_5), cores = 4,chains = 4, 
                   sample_prior = TRUE, warmup = 500, iter = 2000,
                   control = list(adapt_delta = 0.99))
+
+
+all_val <- analysis_1
 
 summary(analysis_1)
 bayes_R2(analysis_1)

### 2021-04-20 Supplementary_Material/Bees_and_other_func_grous_separated.Rmd
Exploring the full model network metrics relationships

@@
            panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
+           panel.grid.major= element_blank(),
+           plot.title = element_text(size = 30, face="bold")
      ))
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("")+
-  theme_ms() + theme(legend.position = "none")
+  theme_ms() + theme(legend.position = "none") + ggtitle("(a)")
 
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("")+
-  theme_ms() + theme(legend.position = "none")
+  theme_ms() + theme(legend.position = "none")  + ggtitle("(b)")
 
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("")+
-  theme_ms() +theme(legend.position = "none")
+  theme_ms() +theme(legend.position = "none")  + ggtitle("(c)")
 
@@
    "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
-    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids"))
+    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids")) + ggtitle("(d)")
 
@@
    "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
-    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids"))
+    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids"))+ ggtitle("(e)")
 #Plot nicely PC3
@@
     limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-               "Non-syrphids-diptera", "Syrphids"))
+               "Non-syrphids-diptera", "Syrphids"))+ ggtitle("(f)")
 

### 2021-04-20 Scripts/7_Analysis_2_Visits_or_Specialization-PCS.R

@@ -6,6 +6,8 @@ library(brms) #modelling
 library(cmdstanr) #modelling
 library(cowplot) #panel of plots
 library(ggplot2) #plotting
+library(patchwork)
+
 # Theme for publication
 theme_ms <- function(base_size=12, base_family="Helvetica") {
   (theme_bw(base_size = base_size, base_family = base_family)+
@@ -26,7 +28,7 @@ theme_ms <- function(base_size=12, base_family="Helvetica") {
 #LOAD DATA
 ########################################################################################################################################################
 data_analysis_2 <- readRDS("Data/RData/data_analysis_2.rds") 
-colnames(data_analysis_2)[5] <- "Id"
+colnames(data_analysis_2)[11] <- "Id"
 ########################################################################################################################################################
 #MODEL VISITS ~ PRINCIPAL COMPONENTS
 ########################################################################################################################################################
@@ -35,154 +37,397 @@ Visits_PCs <- brm((Visits-1) ~ PC1 + PC2 + PC3 + (1|Id),
                   sample_prior = TRUE, warmup = 500, iter = 2000,
                   control = list(adapt_delta = 0.99)) 
 
-
 #looks ok
 pp_check(Visits_PCs) +xlim(-50,200)+ylim(0,0.1)
-
-#Explore conditional and marginal Bayesian r2
-bayes_R2(Visits_PCs)
-loo_R2(Visits_PCs)
-
-#Explore each of the PC's
-conditional_effects(Visits_PCs, effects = "PC1",points=T)
-conditional_effects(Visits_PCs, effects = "PC2",points=T)
-conditional_effects(Visits_PCs, effects = "PC3",points=T)
+#summary
+sumary(Visits_PCs)
 
 #Save output
 setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
 saveRDS(Visits_PCs, "results_analysis_2_Visits.rds") 
-########################################################################################################################################################
-#Plot nicely
-########################################################################################################################################################
+#read
[…]

### 2021-04-20 Scripts/7_Analysis_Metrics_Traits.R

@@ -1,0 +1,799 @@
+########################################################################################################################################################
+########################################################################################################################################################
+########################################################################################################################################################
+##SCRIPT FOR ANALYSIS 
+########################################################################################################################################################
+########################################################################################################################################################
+########################################################################################################################################################
+
+#HERE I TRY TO SELECT THE MAIN EXPLANATORY TRAITS FOR EACH TRAIT 
+
+#LOAD LIBRARIES
+library(data.table) # operate with df
+library(bipartite) #calculate metrics
+library(dplyr) #data manipulation 
+library(stringr) #remove string
+library(brms)
+library(projpred)
+library(dplyr)
+library(ggplot2)
+library(bayesplot)
+########################################################################################################################################################
+#1) LOAD NETWORK DATA
+########################################################################################################################################################
+#Set working directory to read files
+setwd("~/R_Projects/Reproductive traits/Data/Data_networks_quantitative") 
+
+#read csv files
+temp <- list.files(pattern="*.csv")
+my.list <- list(for (i in 1:length(temp)) assign(temp[i], read.csv(temp[i])))
+my_files <- list.files(pattern = "\\.csv$")
+my_data <- lapply(my_files, function(i){read.csv(i,  row.names = 1)})
+# Add id to dataframe
+names(my_data) <- stringr::str_replace(my_files, pattern = ".csv", replacement = "")
+
+########################################################################################################################################################
[…]

### 2021-04-28 Main_Figures/Analysis_1_Separated.Rmd
plot 4 of the paper, not super fan of it but good for now

@@
            panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
+           panel.grid.major= element_blank(),
+           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
+           plot.subtitle = element_text(face="bold",size=rel(2))
      ))
@@
   aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none")
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("")+
+  theme_ms() + theme(legend.position = "none") + ggtitle("PC1", subtitle = "(a)")
 
@@
   aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none") 
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("")+
+  theme_ms() + theme(legend.position = "none") + ggtitle("PC2", subtitle = "(b)")
 #Plot nicely PC3
@@
   aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none")
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("")+
+  theme_ms() + theme(legend.position = "none") + ggtitle("PC3", subtitle = "(c)")
 
@@
   aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
-  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("High Flower N.    Large flowers")+
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
-    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids"))
+    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids")) + ggtitle("(d)")
 
@@
   aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
-    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids"))
+    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids")) + ggtitle("(e)")
+
 #Plot nicely PC3
@@
   aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
-  theme_ms() +theme(legend.position = "none") + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles")+
+  theme_ms() +theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
     "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
     limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-               "Non-syrphids-diptera", "Syrphids"))
+               "Non-syrphids-diptera", "Syrphids")) + ggtitle("(f)")
 

### 2021-04-28 Main_Figures/Global_trait_spectrum_Qualitative_Vars.Rmd
plot 4 of the paper, not super fan of it but good for now

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=17, fig.width=17}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18}
 
@@
             axis.title=element_text( size = rel(1.3)),
-            axis.text=element_text(size = rel(1.5), color = "black"),
+            axis.text=element_text(size = rel(1.75), color = "black"),
             legend.title=element_text(face="bold"),
@@
             panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
+             panel.grid.major= element_blank(),
+            plot.title = element_text(size = rel(1.75), face="bold")
       ))
@@
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Compatibility),size=1.5)+scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7"))
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Compatibility),size=1.75)+scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7"))
 
@@
   # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
 
@@
   #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.185, 0.13)) +ggtitle("A)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.185, 0.13)) +ggtitle("(a)")
 
@@
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Life form`),size=1.5)+scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Life form`),size=1.75)+scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("B)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("(b)")
 
@@
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Lifespan),size=1.5)+scale_color_manual(values=c("sienna4","forestgreen"))
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Lifespan),size=1.75)+scale_color_manual(values=c("sienna4","forestgreen"))
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.102, 0.1)) + ggtitle("C)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.102, 0.1)) + ggtitle("(c)")
 
@@
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower symmetry`),size=1.5)+scale_color_manual(values=c("sienna2","purple"))
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower symmetry`),size=1.75)+scale_color_manual(values=c("sienna2","purple"))
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.165, 0.1)) + ggtitle("F)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.165, 0.1)) + ggtitle("(f)")
 
@@
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower shape`),size=1.5)+scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower shape`),size=1.75)+scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.13, 0.18)) + ggtitle("E)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.13, 0.18)) + ggtitle("(e)")
 
@@
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Breeding system`),size=1.5)+scale_color_manual(values=c("forestgreen","orange", "black"))
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Breeding system`),size=1.75)+scale_color_manual(values=c("forestgreen","orange", "black"))
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.163, 0.115)) + ggtitle("D)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.163, 0.115)) + ggtitle("(d)")
 
@@
 #Load plots
-Nectar <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
+#Nectar <- function(PC, x="PC1", y="PC2") {
+#  # PC being a prcomp object
+#  data <- data.frame(PC$S)
+#  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+#  dat <- data.frame(x = data[,x], y = data[,y])
+#  
+#  #######
+#  #DENSITY FUNCTION
+#  #######
+#  get_density <- function(x, y, ...) {
+#    dens <- MASS::kde2d(x, y, ...)
+#    ix <- findInterval(x, dens$x)
+#    iy <- findInterval(y, dens$y)
+#    ii <- cbind(ix, iy)
+#    return(dens$z[ii])
+#  }
+#  
+#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+#  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
+#  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
+#  dat$Nectar[dat$Nectar=="no"] <- "Absence"
+#  plot <- plot + geom_point(data=dat, aes(-x, -y, #colour=Nectar),size=1.75)+scale_color_manual(values=c("black","grey"))
+#  
+#  ########
+#  #ADD ARROWS 
+#  ########
+#  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+#  mult <- min(
+#    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+#    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+#  )
+#  datapc <- transform(datapc,
+#                      v1 = .75 * mult * (get(x)),
+#                      v2 = .75 * mult * (get(y))
+#  )
+#  # add arrows
+#  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, #yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
+#  
+#  #Add axis with perctentage
+#  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+#
+#  
+#  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, #arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+#  
+#  #ADD LABELS
+#  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
+#  
+#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+#  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = #-(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
+#                          label = PCAloadings$Variables, color="black",size=3)
+#  
+#  #CHANGE THEME
+#  #CHANGE THEME
+#  
+#  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)") 
+#  
+#  plot
+#  
+#}
+#
+# #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")
 
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=1.5)+scale_color_manual(values=c("black","grey"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)")
-
-  plot
-
-}
-
- #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")
-
-  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),NULL,Nectar(PC),NULL, ncol=3,nrow=3,  align = "hv")
+  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),ncol=3,nrow=2,  align = "hv")
 

### 2021-04-28 Main_Figures/Metrics_Main_Traits.Rmd
plot 4 of the paper, not super fan of it but good for now

---
title: ""
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=18}

library(ggplot2)
library(emmeans)
library(patchwork)
library(brms)

# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.3)),
            axis.text=element_text(size = rel(1.75), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(0.4, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
             panel.grid.major= element_blank(),
            plot.title = element_text(size = rel(1.75), face="bold"),
            axis.title.y = element_text(size = rel(1.5))
      ))
}

setwd("~/Dropbox/PhD/R/Chapter_2")

#Load data
df <- readRDS("df.rds")

#Model outputs
fit_v <- readRDS("results_fit_v.rds")
fit_nd <- readRDS("results_fit_nd.rds")
fit_d <- readRDS("results_fit_d.rds")

#Tukey posthoc comparisons
cld_visits_life_tukey <- readRDS("cld_visits_life_tukey.rds")
cld_nd_life_tukey <- readRDS("cld_nd_life_tukey.rds")
cld_d_life_tukey <- readRDS("cld_d_life_tukey.rds")
v_cld_comp_tukey <- readRDS("v_cld_comp_tukey.rds")
nd_cld_comp_tukey <- readRDS("nd_cld_comp_tukey.rds")
d_cld_comp_tukey <- readRDS("d_cld_comp_tukey.rds")

##################################################################
##LIFE FORM
##################################################################

#VISITATION
#merge to include in gg
life_v <- conditional_effects(fit_v, effects = "life_form",points=T) 
life_v[[1]] <- merge(life_v[[1]], cld_visits_life_tukey, by="life_form", all.x = TRUE)
#Plot
v_life <-  ggplot(life_v[[1]], aes(x = life_form, y = (estimate__),color=life_form)) + geom_jitter(width = 0.15,alpha=0.2,data = df,aes(x = life_form, y =                       Visits),size = 1, alpha=0.9) +geom_point(size=3.5) +geom_errorbar(aes(ymin=(lower__), ymax=(upper__)),width=0.2, size=1) +theme_ms()+
          xlab("") + ylab("Sum of visits") +scale_color_manual(values=c("forestgreen", "darkorange2","black")) +theme(legend.position="none")+
          scale_y_continuous(breaks = seq(0, 280, 50), limits = c(0,280),  expand = expansion(mult = c(0.05, .05))) +geom_text(data = life_v[[1]], aes(y =             270, label = .group),size=6)+ labs(title = bquote(bold('(d)')~ 'Life form'))+theme(axis.text.x = element_text(angle = 30, vjust = 1,hjust=1))

#NORMNALIZED DEGREE
#calculate posterior for life form
life_nd <- conditional_effects(fit_nd, effects = "life_form",points=T) 
life_nd[[1]] <- merge(life_nd[[1]], cld_nd_life_tukey, by="life_form", all.x = TRUE)
#Plot
nd_life <-  ggplot(life_nd[[1]], aes(x = life_form, y = (estimate__),color=life_form)) + geom_jitter(width = 0.15,alpha=0.2,data = df,aes(x = life_form, y =                       normalised.degree),size = 1, alpha=0.9) +geom_point(size=3.5) +geom_errorbar(aes(ymin=(lower__),     ymax=(upper__)),width=0.2,size=1)+theme_ms()+
          xlab("") + ylab("Normalized degree") +scale_color_manual(values=c("forestgreen", "darkorange2","black")) +theme(legend.position="none")+
          scale_y_continuous(breaks = seq(0, 0.8, 0.2), limits = c(0,0.8),  expand = expansion(mult = c(0.05, .05))) +geom_text(data = life_nd[[1]], aes(y =             0.75, label = .group),size=6)+ labs(title = bquote(bold('(e)')~ 'Life form'))+theme(axis.text.x = element_text(angle = 30, vjust = 1,hjust=1))

#SPECIALIZATION
#calculate posterior for life form
life_dd <- conditional_effects(fit_d, effects = "life_form",points=T) 
colnames(life_dd[[1]])[3] <- "Interaction"
#merge to include in gg
life_dd[[1]] <- merge(life_dd[[1]], cld_d_life_tukey, by="life_form", all.x = TRUE)
#Plot
d_life <- ggplot(life_dd[[1]], aes(x = life_form, y = (estimate__),color=life_form)) + geom_jitter(width = 0.15,alpha=0.2,data = df,aes(x = life_form, y = d),
  size = 1, alpha=0.9) +geom_point(size=3.5) +geom_errorbar(aes(ymin=(lower__), ymax=(upper__)),width=0.2, size=1)+theme_ms()+
  xlab("") + ylab("Specialization (d')") +scale_color_manual(values=c("forestgreen", "darkorange2","black"))+theme(legend.position="none")+
  scale_y_continuous(breaks = seq(0, 1, 0.2), limits = c(0,1.06),  expand = expansion(mult = c(0.05, .05))) +geom_text(data = life_dd[[1]], aes(y = 1.05, label = .group),size=6) +
  labs(title = bquote(bold('(f)')~ 'Life form'))+theme(axis.text.x = element_text(angle = 30, vjust = 1,hjust=1))

##################################################################
##COMPATIBILITY
##################################################################

#VISITATION
#calculate posterior for life form
comp_v <- conditional_effects(fit_v, effects = "Compatibility_system",points=T) 
colnames(comp_v[[1]])[3] <- "Interaction"
#merge to include in gg
comp_v[[1]] <- merge(comp_v[[1]], v_cld_comp_tukey, by="Compatibility_system", all.x = TRUE)
#Order labels for plotting
comp_v[[1]]$Compatibility_system <- factor(comp_v[[1]]$Compatibility_system, levels=c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
df$Compatibility_system <- factor(df$Compatibility_system, levels=c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
#Plot
v_comp <- ggplot(comp_v[[1]], aes(x = Compatibility_system, y = (estimate__),color=Compatibility_system)) + geom_jitter(width = 0.15,alpha=0.2,data = df,aes(x = Compatibility_system, y = Visits),
  size = 1, alpha=0.9) +geom_point(size=3.5) +geom_errorbar(aes(ymin=(lower__), ymax=(upper__)),width=0.2, size=1) +theme_ms()+
  xlab("") + ylab("Sum of visits") +scale_color_manual(values=c("deepskyblue2", "cyan4","orange","gray7")) +theme(legend.position="none")+
  scale_y_continuous(breaks = seq(0, 280, 50), limits = c(0,280),  expand = expansion(mult = c(0.05, .05))) +geom_text(data = comp_v[[1]], aes(y = 270, label = .group),size=6)+
  theme(axis.text.x = element_text(angle = 30, vjust = 1,hjust=1)) + scale_x_discrete(name=c(""),labels=c("Self-comp", "Part-selfcomp", "Self-incomp", "Uni-flow")) + 
  labs(title = bquote(bold('(g)')~ 'Compatibility'))

#NORMNALIZED DEGREE
#calculate posterior for life form
comp_nd <- conditional_effects(fit_nd, effects = "Compatibility_system",points=T) 
colnames(comp_nd[[1]])[3] <- "Interaction"
#merge to include in gg
comp_nd[[1]] <- merge(comp_nd[[1]], nd_cld_comp_tukey, by="Compatibility_system", all.x = TRUE)

comp_nd[[1]]$Compatibility_system <- factor(comp_nd[[1]]$Compatibility_system, levels=c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
df$Compatibility_system <- factor(df$Compatibility_system, levels=c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))

#Plot
nd_comp <- ggplot(comp_nd[[1]], aes(x = Compatibility_system, y = (estimate__),color=Compatibility_system)) + geom_jitter(width = 0.15,alpha=0.2,data = df,aes(x = Compatibility_system, y = normalised.degree),
  size = 1, alpha=0.9) +geom_point(size=3.5) +geom_errorbar(aes(ymin=(lower__), ymax=(upper__)),width=0.2, size=1) +theme_ms()+
  xlab("") + ylab("Normalized degree") +scale_color_manual(values=c("deepskyblue2", "cyan4","orange","gray7")) +theme(legend.position="none")+
  scale_y_continuous(breaks = seq(0, 0.8, 0.2), limits = c(0,0.8),  expand = expansion(mult = c(0.05, .05))) +geom_text(data = comp_nd[[1]], aes(y = 0.75, label = .group),size=6)+
  theme(axis.text.x = element_text(angle = 30, vjust = 1,hjust=1)) + scale_x_discrete(name=c(""), labels=c("Self-comp", "Part-selfcomp", "Self-incomp", "Uni-flow")) +
  labs(title = bquote(bold('(h)')~ 'Compatibility'))

#SPECIALIZATION
#calculate posterior for life form
#NORMNALIZED DEGREE
#calculate posterior for life form
comp_d <- conditional_effects(fit_d, effects = "Compatibility_system",points=T) 
colnames(comp_d[[1]])[3] <- "Interaction"
#merge to include in gg
comp_d[[1]] <- merge(comp_d[[1]], d_cld_comp_tukey, by="Compatibility_system", all.x = TRUE)

comp_d[[1]]$Compatibility_system <- factor(comp_d[[1]]$Compatibility_system, levels=c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
df$Compatibility_system <- factor(df$Compatibility_system, levels=c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))

#Plot
d_comp <- ggplot(comp_d[[1]], aes(x = Compatibility_system, y = (estimate__),color=Compatibility_system)) + geom_jitter(width = 0.15,alpha=0.2,data = df,aes(x = Compatibility_system, y = d),
  size = 1, alpha=0.9) +geom_point(size=3.5) +geom_errorbar(aes(ymin=(lower__), ymax=(upper__)),width=0.2, size=1) +theme_ms()+
  xlab("") + ylab("Specialization (d')") +scale_color_manual(values=c( "deepskyblue2", "cyan4","orange","gray7")) +theme(legend.position="none")+
  scale_y_continuous(breaks = seq(0, 1, 0.2), limits = c(0,1.06),  expand = expansion(mult = c(0.05, .05))) +geom_text(data = comp_d[[1]], aes(y = 1.05, label = .group),size=6)+
  theme(axis.text.x = element_text(angle = 30, vjust = 1,hjust=1)) + scale_x_discrete(name=c(""),labels=c("Self-comp", "Part-selfcomp", "Self-incomp", "Uni-flow")) +
  labs(title = bquote(bold('(i)')~ 'Compatibility'))

##################################################################
##FLOWER NUMBER
##################################################################

#VISITATION
v_flower <- conditional_effects(fit_v, effects = "Flowers_per_plant",points=T) 
colnames(v_flower[[1]])[3] <- "Interaction"

pp1 <- ggplot(v_flower[[1]], aes(x = Flowers_per_plant, y = (estimate__+1))) + geom_point(data = df,aes(x = Flowers_per_plant, y = Visits),
  size = 2, alpha=0.35,colour="darkgrey") + geom_line(colour="black",size=1.2) + ylim(0,quantile(df$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.15,fill="black") + ylab("Sum of visits") + xlab("")+
  labs(title = bquote(bold('(a)')~ 'Flower number'))

#SPECIALIZATION
d_flower <- conditional_effects(fit_d, effects = "Flowers_per_plant",points=T) 
colnames(d_flower[[1]])[3] <- "Interaction"

dd1 <- ggplot(d_flower[[1]], aes(x = Flowers_per_plant, y = (estimate__))) + geom_point(data = df,aes(x = Flowers_per_plant, y = d),
  size = 2, alpha=0.35,colour="darkgrey") + geom_line(colour="black",size=1.2)  +  theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.15,fill="black") + ylab("Specialization (d')") + xlab("")+
  labs(title = bquote(bold('(b)')~ 'Flower number'))

#NORMLAIZED DEGREE
nd_flower <- conditional_effects(fit_nd, effects = "Flowers_per_plant",points=T) 
colnames(nd_flower[[1]])[3] <- "Interaction"

ndd1 <- ggplot(nd_flower[[1]], aes(x = Flowers_per_plant, y = (estimate__))) + geom_point(data = df,aes(x = Flowers_per_plant, y = normalised.degree),
  size = 2, alpha=0.35,colour="darkgrey") + geom_line(colour="black",size=1.2)  +  theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.15,fill="black") + ylab("Normalized degree") + xlab("")+
  labs(title = bquote(bold('(c)')~ 'Flower number'))

pp1 + ndd1 + dd1 +v_life + nd_life + d_life + v_comp + nd_comp + d_comp + plot_layout(ncol = 3)

```

### 2021-04-28 Scripts/7_Analysis_2_Visits_or_Specialization-PCS.R

@@ -471,8 +471,4 @@ Visits_PC1 + Visits_PC2 + Visits_PC3 + degree_PC1 + degree_PC2 + degree_PC3+ nor
   
   
   
-betweenness_PC1 + betweenness_PC2 + betweenness_PC3 +
-PDI_PC1 + PDI_PC2 + PDI_PC3 + closeness_PC1 + closeness_PC2 + closeness_PC3 +
-  plot_layout(ncol = 3)
-
-
+#NECTAR

### 2021-04-28 Scripts/7_Analysis_Metrics_Traits.R

@@ -20,6 +20,10 @@ library(ggplot2)
 library(bayesplot)
 library(ape)
 library(rtrees)
+library(cowplot)
+library(emmeans)
+library(tidybayes)
+library(multcomp)
 ########################################################################################################################################################
 #1) LOAD NETWORK DATA
 ########################################################################################################################################################
@@ -251,12 +255,28 @@ fit_v <-  brm(Visits-1 ~ Breeding_system + Compatibility_system + Autonomous_sel
             sample_prior = TRUE, warmup = 1000, iter = 3000,
             control = list(adapt_delta = 0.99)) 
 
+summary(fit_v)
+
 pp_check(fit_v)
 
 performance::r2(fit_v)
 
 conditional_effects(fit_v)
 
+#phylo signal (lambda)
+hyp <- "sd_phylo__Intercept^2 / (sd_phylo__Intercept^2 + shape^2) = 0"
+(hyp <- hypothesis(fit_v, hyp, class = NULL))
+
+#cannot be computed for this model but should give a similar output
+performance::icc(fit_v)
+
+#Lambda (estimate of phylo signal)
+1.03^2/(1.03^2+1.05^2)
+
+
+#Save output
+setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
+saveRDS(fit_v, "results_fit_v.rds") 
 ################################################################################################################################################################
 #QUALITATIVE VARIABLES
 ################################################################################################################################################################
@@ -416,13 +436,21 @@ fit_d <-  brm(d ~ Breeding_system + Compatibility_system + Autonomous_selfing_le
               sample_prior = TRUE, warmup = 1000, iter = 3000,
               control = list(adapt_delta = 0.99)) 
 
-
+summary(fit_d)
 pp_check(fit_d)
 
 performance::r2(fit_d)
 
 conditional_effects(fit_d)
 
+hyp <- "sd_phylo__Intercept^2 / (sd_phylo__Intercept^2 + zoi^2 +coi^2) = 0"
[…]

### 2021-04-29 Supplementary_Material/Global_Trait_Spectrum_Nectar.Rmd
figure missing values supp.

--- 2021-04-09 Main_Figures/Global_trait_spectrum.Rmd
@@
 #Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+phyl_pca_forest_nectar_all <- readRDS("Data/RData/phyl_pca_forest_nectar_all.rds")
+dat_cleaning_5 <- readRDS("Data/RData/data_subset_nectar.rds")
 
-PC <- phyl_pca_forest
+PC <- phyl_pca_forest_nectar_all
 #CHECK CONTENT
@@
 
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
 all_spp <- function(PC, x="PC1", y="PC2") {
@@
 
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
+  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
+  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
+  dat$Nectar[dat$Nectar=="no"] <- "Absence"
+  # plot <- plot +geom_point(data=dat, aes(-x, -y, colour = density),size=0.65,shape = 1,colour = "black",alpha=0.8)
+
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
+    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.066),breaks = c(0.02, 0.035, 0.058), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
     scale_alpha(guide = 'none')
@@
 
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
-    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
-    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
-    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
-    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
+  plot <- plot + theme_bw()
 
   #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
+  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height", "Nectar" )
 
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,7.25,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.4,3,6.2,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(5,4.95,4.8,4.8,5.3,4.5,4.8)), y = -(PCAloadings$PC2*c(5.2,4.5,3.95,4.25,5,4.5,4.55)+c(0,0,0,0,0.2,0,0)),
+                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
 
@@
 
-plot_grid(all_spp(PC))
+all_spp(PC)
 

### 2021-04-29 Supplementary_Material/Missing_data.Rmd
figure missing values supp.

---
output:
  pdf_document: default
  html_document: default

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000}

#Set working directory
setwd("~/R_Projects/Reproductive Traits")

########################################################################################################################################################
#SCRIPT TO CHECK PATTERNS OF MISSING VALUES
########################################################################################################################################################
#1) READ TRAIT DATA

#2) CLEAN DATA

#3) EXPLORE PATTERNS OF MISSING DATA
########################################################################################################################################################
#LOAD LIBRARIES
library(readxl) #read excel file (trait data)
library(dplyr) #data manipulation
library(missMDA) #For missing values
library(FactoMineR) #Produce pca biplot with individuals and variables
library(factoextra)
library(ggpubr) 
library(missForest) #random forst imputation
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(ape)
library(PVR) #calculate eigen vectors and add them as a column in the imputation, seems to improve output
library(visdat)
library(tidyverse)

########################################################################################################################################################
#1) READ TRAIT DATA
########################################################################################################################################################
#load data
trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
########################################################################################################################################################
#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
########################################################################################################################################################
#####
#A) CLEAN DATA
#####
#select just filled rows
trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data

#str(trait_data_1)
#filter data, select species with flower level info and capitulum
trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
#levels(as.factor(trait_filtered$Info_level)) #checking levels
#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
#str(trait_filtered_2)

#Select columns to work with
t <- trait_filtered_2[c("Species_geonet","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul")]

####################################################################################################
#2) CLEAN DATA. I REPEAT THE SAME PROCEDURE OF THE DATA IMPUTATION TO GET THE SAME NUMBER OF SPECIES
####################################################################################################
#Before data imputation I need to calculate the phylo of the species
#remove not found species that do not run with get tree
cols.num <- c("Family_all","Genus_all","Species_all")
t[cols.num] <- sapply(t[cols.num],as.character)
t$Species_all <- gsub("Species_all_", "", t$Species_all)

t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species

#remove species that are not until species level
#ALL THE SPECIES WITH SP. ARE DELETD
t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
#CHECK LEVELS
#levels(factor(t$Species_all))

#Make these NA's as NA
t$Species_all[t$Species_all=="NA"] <- NA
t$Family_all[t$Family_all=="NA"] <- NA
t$Genus_all[t$Genus_all=="NA"] <- NA
#remove NA's
t <- t[!is.na(t$Family_all),]
t <- t[!is.na(t$Species_all),]
t <- t[!is.na(t$Genus_all),]

#nrow(t)

#Select just columns with traits
t <- t[c("Breeding_system","Compatibility_system",
                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul")]

#################################################
#3)SUMMARY OF THE DATA|ALL COLS CONSIDERED!
#################################################
##Number of filled cells
#nrow(t) * 16 - sum(is.na(t))#[1] 20737
##Dimension of the dataset
#nrow(t) * 16#[1] 24096
##Number of missing values
#sum(is.na(t))#[1] 3359
##Percentage of filled cells
#sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 86.87993
##Percentage of missing values
#sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 13.12007
#
#

#Function to specify number of decimals
specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))

no_missing <- specify_decimal(sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
missing <- specify_decimal(sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)

colnames(t) <- c("Breeding system","Compatibility system",
         "Autonomous selfing qualitative","Autonomous selfing quantitative", "Flower shape", "Flower symmetry", 
         "Flower number per plant", "Floral display width", "Flower width", "Flower length","Style length", "Ovule number", 
         "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar quantitative")

missing.values <- t %>%
  gather(key = "key", value = "val") %>%
  mutate(isna = is.na(val)) %>%
  group_by(key) %>%
  mutate(total = n()) %>%
  group_by(key, total, isna) %>%
  summarise(num.isna = n()) %>%
  mutate(pct = num.isna / total * 100)

levels <-
  (missing.values  %>% filter(isna == T) %>% arrange(desc(pct)))$key

percentage.plot <- missing.values %>%
  ggplot() +
  geom_bar(aes(x = reorder(key, desc(pct)), 
               y = pct, fill=isna), 
           stat = 'identity', alpha=0.8) +
  scale_x_discrete(limits = levels) + theme_bw()+
  scale_fill_manual(name = "", 
                    values = c('steelblue', 'tomato3'), labels = c("Present", "Missing")) +
  coord_flip() +
  labs(title = "Percentage of missing values", x =
         'Variables', y = "% of missing values")

percentage.plot

```

### 2021-04-29 Scripts/2_Missing_Data_Exploration.R

@@ -1,0 +1,166 @@
+########################################################################################################################################################
+#SCRIPT TO CHECK PATTERNS OF MISSING VALUES
+########################################################################################################################################################
+#1) READ TRAIT DATA
+
+#2) CLEAN DATA 
+
+#3) EXPLORE PATTERNS OF MISSING DATA
+########################################################################################################################################################
+#LOAD LIBRARIES
+library(readxl) #read excel file (trait data)
+library(dplyr) #data manipulation
+library(missMDA) #For missing values
+library(FactoMineR) #Produce pca biplot with individuals and variables
+library(factoextra)
+library(ggpubr) 
+library(missForest) #random forst imputation
+library(rtrees) #for phylogenetic distancelibrary(MASS)
+library(ape)
+library(PVR) #calculate eigen vectors and add them as a column in the imputation, seems to improve output
+library(visdat) #VISUALIZE MISSING DATA
+library(naniar)
+library(VIM)
+
+########################################################################################################################################################
+#1) READ TRAIT DATA
+########################################################################################################################################################
+#load data
+trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
+########################################################################################################################################################
+#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
+########################################################################################################################################################
+#####
+#A) CLEAN DATA
+#####
+#select just filled rows
+trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
+
+str(trait_data_1)
+#filter data, select species with flower level info and capitulum
+trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
[…]

### 2021-04-30 Supplementary_Material/Phylo_Signal_Table.Rmd
Phylogenetic signal of traits

---
title: ""
output:
  pdf_document: default
  html_document: default
header-includes:  \usepackage{soul}

---

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}

library(kableExtra)

setwd("~/R_Projects/Reproductive Traits")

#SELFING
selfing <- readRDS("Data/RData/selfing_phylo.rds")
#FLOWER NUMBER
flower_n <- readRDS("Data/RData/flower_n_phylo.rds")
#INFLO WIDTH
inflow_width <- readRDS("Data/RData/inflow_width_phylo.rds")
#FLOWER WIDTH
flower_width <- readRDS("Data/RData/flower_width_phylo.rds")
#FLOWER LENGHT
flower_length <- readRDS("Data/RData/flower_length_phylo.rds")
#STYLE LENGTH
style_n <- readRDS("Data/RData/style_n_phylo.rds")
#OVULE NUMBER
ovule_n <- readRDS("Data/RData/ovule_n_phylo.rds")
#PLANT HEIGHT
plant_height <- readRDS("Data/RData/plant_height_phylo.rds")

#Select two decimals function
specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
#LABELS
label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height")
#LAMBDA
lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda)
#P-VALUE
p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P)

tabla <- data.frame(label, specify_decimal(lambda,2), specify_decimal(p_value,2))

colnames(tabla) <- c("Variable", "Lambda", "P-value")

kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")

```

### 2021-05-04 Supplementary_Material/Missing_data.Rmd
just some edits on a plot form supp. mat

@@
          "Autonomous selfing qualitative","Autonomous selfing quantitative", "Flower shape", "Flower symmetry", 
-         "Flower number per plant", "Floral display width", "Flower width", "Flower length","Style length", "Ovule number", 
+         "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 
          "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar quantitative")
@@
   scale_fill_manual(name = "", 
-                    values = c('steelblue', 'tomato3'), labels = c("Present", "Missing")) +
+                    values = c('#57a340', '#d24513'), labels = c("Present values", "Missing values")) +
   coord_flip() +
-  labs(title = "Percentage of missing values", x =
-         'Variables', y = "% of missing values")
+  labs(title = "", x =
+         '', y = "")+  scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
+  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))
 

### 2021-05-11 Main_Figures/Traits_Table.Rmd
.

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=18}

library(kableExtra)
library(dplyr)

Trait <- c("Plant height (m)", " ", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovule number/flower",
           "Flowers per plant", "Nectar $(\\mu l)$", "Nectar (mg)", "Nectar concentration (%)", "Pollen grains per flower", "Autonomous selfing (fruit set)")

Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Autonomous selfing", "Compatibility system", "Breeding system", " ", " ", " ", " ", " ")

T.cat <- c("Short-lived, perennial", "Herb, shrub, tree", "Brush, campanulate, capitulum, open, papilionaceous, tube", "Actinomorphic, zygomorphic",
           "Presence/absence", "None, low, medium, high", "Incompatible, partially compatible, compatible", "Hermaphrodite, monoecious, dioecious"," ", " ", " ", " ", " ")

Type <- c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive")

Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Floral", "Reproductive", "Reproductive","Reproductive","","","","")

dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)

colnames(dat) <- c("Trait Type","Traits","Trait Type", "Traits", "Categories")

#dat%>%
#kbl("latex", longtable = T, booktabs = T,linesep = "\\addlinespace")

#%>%

# add_header_above(c("Quantitative traits" = 2,"Qualitative traits" = 3))

#%>%  column_spec(c(1,3), bold = T,width="2em",extra_css="transform: rotate(-90deg);") %>%
 # collapse_rows(columns = c(1,3), valign = "middle")

kable(dat,"latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "left") %>% collapse_rows(columns = c(1,3), valign = "middle")

```

### 2021-05-11 Main_Figures/Regression_Tree_Nectar_Pollen.Rmd
prepare table at home

---
title: ""
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18}

########################################################################################################################################################
#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
########################################################################################################################################################
#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)

library(rpart.plot)
library(rpart)

setwd("~/R_Projects/Reproductive Traits")

long_d <- read.csv("Data/Csv/long_format_quantitative_networks.csv", row.names = 1) #quantitative network data|weighted by frequency of visits per plant species

#Select data with interaction greater than 0
long_d_1 <- long_d[long_d$Interaction>0,]

#Remove NA'S
long_d_2 <- long_d_1[!is.na(long_d_1$guild),] #I do it by guild because just these 6 guilds are named in this column

#check levels
levels(factor(long_d_2$guild))
########################################################################################################################################################
#NOW READ NECTAR DATA
forest_data <- read.csv("Data/Csv/nectar_pollen_subset_imputed_trait_data.csv")
colnames(forest_data)[1] <- "Plant_species"
########################################################################################################################################################
#MERGE DATA
data <- merge(long_d_2, forest_data, by="Plant_species")

#SELECT COLUMNS WITH QUANTITATIVE INFORMATION
data_1 <- data[c("Interaction","Autonomous_selfing_level_fruit_set","Corolla_diameter_mean","Corolla_length_mean",
                 "Flowers_per_plant","Style_length","Ovule_number","Plant_height_mean_m","Nectar_concentration",
                 "Nectar_mg","Nectar_ul","Pollen_per_flower")]

#Set colnames for plotting
colnames(data_1) <- c("Interactions", "Aut. selfing", "Flower width","Flower length" , "Flowers per plant","Style length (mm)",
                      "Ovule number","Plant height (m)", "Nectar concentration (%)","Mg of nectar","Microlitres of nectar","Pollen grains per flower")
########################################################################################################################################################

# Create a decision tree model
tree <- rpart(Interactions~., data=data_1, cp=.007)
# Visualize the decision tree with rpart.plot
rpart.plot(tree, box.palette="GnOr",tweak = 1.20)

```

### 2021-05-11 Main_Figures/Traits_Table.Rmd
prepare table at home

@@
 ---
-title: "Untitled"
+title: ""
 output:
@@
   html_document: default
-
+header-includes:
+- \usepackage{booktabs}
+- \usepackage{longtable}
+- \usepackage{array}
+- \usepackage{multirow}
+- \usepackage{wrapfig}
+- \usepackage{float}
+- \usepackage{colortbl}
+- \usepackage{pdflscape}
+- \usepackage{tabu}
+- \usepackage{threeparttable}
+- \usepackage{threeparttablex}
+- \usepackage[normalem]{ulem}
+- \usepackage{makecell}
+- \usepackage{xcolor}
 ---
@@
 library(kableExtra)
+
 library(dplyr)
@@
 Trait <- c("Plant height (m)", " ", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovule number/flower",
-           "Flowers per plant", "Nectar $(\\mu l)$", "Nectar (mg)", "Nectar concentration (%)", "Pollen grains per flower", "Autonomous selfing (fruit set)")
+           "Flowers/plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains/flower", "Autonomous selfing (fruit set)")
 
@@
 T.cat <- c("Short-lived, perennial", "Herb, shrub, tree", "Brush, campanulate, capitulum, open, papilionaceous, tube", "Actinomorphic, zygomorphic",
-           "Presence/absence", "None, low, medium, high", "Incompatible, partially compatible, compatible", "Hermaphrodite, monoecious, dioecious"," ", " ", " ", " ", " ")
+           "Presence/absence", "None, low, medium, high", "Self-incompatible, partially self-compatible, self-compatible", "Hermaphrodite, monoecious, dioecious"," ", " ", " ", " ", " ")
 
@@
 
-Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Floral", "Reproductive", "Reproductive","Reproductive","","","","")
+Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive","","","","","")
 
@@
 
-colnames(dat) <- c("Trait Type","Traits","Trait Type", "Traits", "Categories")
+colnames(dat) <- c("Trait type","Traits","Trait type", "Traits", "Categories")
 
@@
 
-kable(dat,"latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "left") %>% collapse_rows(columns = c(1,3), valign = "middle")
+kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE) %>%
+kable_styling(full_width = T) %>%
+add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 3),bold=T)  %>%
+    column_spec(c(1,3), bold = T) %>% row_spec(0, bold=T)
 

### 2021-05-11 Supplementary_Material/Table_1_List_of_Studies.tex
prepare table at home

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\author{}
\date{\vspace{-2.5em}}

\begin{document}

\begin{landscape}

```
## [1] "latex"
```

\begingroup\fontsize{12}{14}\selectfont

\begin{longtable}[l]{lrlll}
\toprule
First author & Year & Web N. & Network type & DOI\\
\midrule
\endfirsthead
\multicolumn{5}{@{}l}{\textit{(continued)}}\\
\toprule
First author & Year & Web N. & Network type & DOI\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{Arroyo-Correa} & \cellcolor{gray!6}{2019} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1111/1365-2745.13332}\\
\addlinespace
Bartomeus & 2008 & 6 & Weighted web & https://doi.org/10.1007/s00442-007-0946-1\\
\addlinespace
\cellcolor{gray!6}{Bartomeus} & \cellcolor{gray!6}{2008} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://github.com/ibartomeus/BeeFunData}\\
\addlinespace
Bek & 2006 & 1 & Unweighted web & Unpublished, Master thesis\\
\addlinespace
\cellcolor{gray!6}{Bundgaard} & \cellcolor{gray!6}{2003} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{Unpublished, Master thesis}\\
\addlinespace
Burkle & 2013 & 1 & Weighted web & https://doi.org/10.1126/science.1232728\\
\addlinespace
\cellcolor{gray!6}{Dicks} & \cellcolor{gray!6}{2002} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1046/j.0021-8790.2001.00572.x}\\
\addlinespace
Dupont & 2003 & 3 & Weighted web & https://doi.org/10.1111/j.1365-2656.2008.01501.x\\
\addlinespace
\cellcolor{gray!6}{Elberling} & \cellcolor{gray!6}{1999} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1111/j.1600-0587.1999.tb00507.x}\\
\addlinespace
Fang & 2008 & 1 & Weighted web & https://doi.org/10.1111/1749-4877.12190\\
\addlinespace
\cellcolor{gray!6}{Inouye} & \cellcolor{gray!6}{1988} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1111/j.1442-9993.1988.tb00968.x}\\
\addlinespace
Inouye & 1990 & 1 & Weighted metaweb & http://hdl.handle.net/2433/156099\\
\addlinespace
\cellcolor{gray!6}{Kaiser-Bunbury} & \cellcolor{gray!6}{2017} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1038/nature21071}\\
\addlinespace
Kaiser-Bunbury & 2011 & 6 & Weighted web & https://doi.org/10.1111/j.1365-2745.2010.01732.x\\
\addlinespace
\cellcolor{gray!6}{Kaiser-Bunbury} & \cellcolor{gray!6}{2010} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1016/j.ppees.2009.04.001}\\
\addlinespace
Kato & 2000 & 1 & Unweighted web & http://hdl.handle.net/2433/156116\\
\addlinespace
\cellcolor{gray!6}{Kevan} & \cellcolor{gray!6}{1970} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Unweighted web} & \cellcolor{gray!6}{https://doi.org/10.2307/2258569}\\
\addlinespace
Lundgren & 2005 & 1 & Weighted web & https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2\\
\addlinespace
\cellcolor{gray!6}{McMullen} & \cellcolor{gray!6}{1993} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Unweighted metaweb} & \cellcolor{gray!6}{https://biostor.org/reference/244737}\\
\addlinespace
Olesen & 2002 & 2 & Weighted web & https://doi.org/10.1046/j.1472-4642.2002.00148.x\\
\addlinespace
\cellcolor{gray!6}{Peralta} & \cellcolor{gray!6}{2006} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1111/ele.13510}\\
\addlinespace
Primack & 1983 & 3 & Unweighted metaweb & https://doi.org/10.1080/0028825X.1983.10428561\\
\addlinespace
\cellcolor{gray!6}{Ramirez} & \cellcolor{gray!6}{1989} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Unweighted web} & \cellcolor{gray!6}{https://doi.org/10.2307/2388282}\\
\addlinespace
Ramirez & 1992 & 1 & Unweighted metaweb & https://doi.org/10.1111/j.1095-8339.1992.tb00294.x\\
\addlinespace
\cellcolor{gray!6}{Robertson} & \cellcolor{gray!6}{1929} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Unweighted metaweb} & \cellcolor{gray!6}{https://doi.org/10.5962/bhl.title.11538}\\
\addlinespace
Small & 1976 & 1 & Weighted web & /13960/t4km08d21\\
\addlinespace
\cellcolor{gray!6}{Souza} & \cellcolor{gray!6}{2017} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1111/1365-2745.12978}\\
\addlinespace
Traveset & 2013 & 1 & Weighted metaweb & https://doi.org/10.1098/rspb.2012.3040\\*
\end{longtable}
\endgroup{}

\end{landscape}

\end{document}

### 2021-05-11 Scripts/2_1_Trait_Data_Imp_Nectar_Pollen_Subset.R

@@ -50,12 +50,12 @@ trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA
 trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
 trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
 
-
+str(trait_filtered_2)
 #select columns of interest
 t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
                         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", 
                         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
-                        "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration")]
+                        "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
 
 ########################################################################################################################################################
 #2 DATA PREPARATION
@@ -121,7 +121,7 @@ t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c
 t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
          "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant",
          "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
-         "Plant_height_mean_m","Nectar_presence_absence", "Nectar_ul")]
+         "Plant_height_mean_m","Nectar_presence_absence", "Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
 
 ########################################################################################################################################################
 #3) EXPLORE PATTERNS OF MISSING DATA
@@ -172,8 +172,11 @@ t <- t[!is.na(t$Genus_all),]
 missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)*100
 sort(missing_data[missing_data >= 0], decreasing=T)
 
-#Subset just species with quantitative information about nectar
[…]

### 2021-05-12 Main_Figures/Traits_Table.Rmd
Pollen nectar pPCA added

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=18}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12}
+setwd("~/R_Projects/Reproductive Traits")
 
@@
 library(dplyr)
+library(readxl) #read excel file (trait data)
+library(dplyr) #data manipulation
+library(visdat) #VISUALIZE MISSING DATA
+library(naniar)
+library(tidyverse)
+########################################################################################################################################################
+#1) READ TRAIT DATA
+########################################################################################################################################################
+#load data
+trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
+########################################################################################################################################################
+#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
+########################################################################################################################################################
+#####
+#A) CLEAN DATA
+#####
+#select just filled rows
+trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
 
-Trait <- c("Plant height (m)", " ", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovule number/flower",
-           "Flowers/plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains/flower", "Autonomous selfing (fruit set)")
+#filter data, select species with flower level info and capitulum
+trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
+#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
+trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
+trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
+trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
 
-Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Autonomous selfing", "Compatibility system", "Breeding system", " ", " ", " ", " ", " ")
+#Select columns to work with
+t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
+                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
+                        "Flowers_per_plant","Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
+                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
 
-T.cat <- c("Short-lived, perennial", "Herb, shrub, tree", "Brush, campanulate, capitulum, open, papilionaceous, tube", "Actinomorphic, zygomorphic",
-           "Presence/absence", "None, low, medium, high", "Self-incompatible, partially self-compatible, self-compatible", "Hermaphrodite, monoecious, dioecious"," ", " ", " ", " ", " ")
+########################################################################################################################################################
+#####
+#B) RENAME LEVELS FOR IMPUTATION
+#####
+#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
+#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
+t$Breeding_system <- as.character(t$Breeding_system)
+t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
+t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
+t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
+#Change to capital letters| There are already levels with lower case
+t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
+t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
+t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
+t$Breeding_system <- as.factor(t$Breeding_system)
 
-Type <- c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive")
+#Now 3 levels
+#Flower_morphology
+t$Flower_morphology <- as.character(t$Flower_morphology)
+t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
+t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
+t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
+t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
+t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
+t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
+t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
+t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
+t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
+t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
+t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
+t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
+t$Flower_morphology <- as.factor(t$Flower_morphology)
 
-Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive","","","","","")
+#Life span
+t$lifespan <- as.character(t$lifespan )
+t$lifespan[t$lifespan=="annual"] <- "short_lived"
+t$lifespan[t$lifespan=="biennial"] <- "short_lived"
+t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
+t$lifespan[t$lifespan=="perennial"] <- "Perennial"
+t$lifespan <- as.factor(t$lifespan )
+
+########################################################################################################################################################
+#3) EXPLORE PATTERNS OF MISSING DATA
+########################################################################################################################################################
+
+#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
+#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
+t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
+t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
+t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
+t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
+
+#t$Nectar_ul adding it here just to see how many cells 
+#Now we just select presence/absence of nectar
+#select columns of interest
+t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
+         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Floral_unit_width",
+         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
+         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
+
+########################################################################################################################################################
+#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
+########################################################################################################################################################
+#Convert to factor 
+cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
+          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
+t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
+
+cols.num <- c("Family_all","Genus_all","Species_all")
+t[cols.num] <- sapply(t[cols.num],as.character)
+t$Species_all <- gsub("Species_all_", "", t$Species_all)
+
+t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
+
+#remove species that are not until species level
+#ALL THE SPECIES WITH SP. ARE DELETD
+t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
+t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
+t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
+t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
+t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
+t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
+t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
+#CHECK LEVELS
+
+#Make these NA's as NA
+t$Species_all[t$Species_all=="NA"] <- NA
+t$Family_all[t$Family_all=="NA"] <- NA
+t$Genus_all[t$Genus_all=="NA"] <- NA
+#remove NA's
+t <- t[!is.na(t$Family_all),]
+t <- t[!is.na(t$Species_all),]
+t <- t[!is.na(t$Genus_all),]
+
+missing.values <- t %>%
+  gather(key = "key", value = "val") %>%
+  mutate(isna = is.na(val)) %>%
+  group_by(key) %>%
+  mutate(total = n()) %>%
+  group_by(key, total, isna) %>%
+  summarise(num.isna = n()) %>%
+  mutate(pct = num.isna / total * 100)
+
+n_of_records <- subset(missing.values, isna=="FALSE")
+Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
+           "Flower per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")
+
+Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Autonomous selfing", "Compatibility system", "Breeding system", " ", " ", " ", " ")
+
+T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
+           "Presence \n Absence", "None \n Low \n Medium \n High", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " "),align = c("l"))
+
+Type <- c("V", "F", "F", "F", "F", "F", "F","F","F","F","F","R")
+
+Type_1 <- c("V", "V", "F", "F", "F", "R", "R", "R","","","","")
 
@@
 
-colnames(dat) <- c("Trait type","Traits","Trait type", "Traits", "Categories")
+Number_of_records_quantitative <- c(n_of_records$num.isna[n_of_records$key=="Plant_height_mean_m"], n_of_records$num.isna[n_of_records$key=="Corolla_diameter_mean"],
+  n_of_records$num.isna[n_of_records$key=="Corolla_length_mean"], n_of_records$num.isna[n_of_records$key=="Floral_unit_width"],
+  n_of_records$num.isna[n_of_records$key=="Style_length"], n_of_records$num.isna[n_of_records$key=="Ovule_number"],
+  n_of_records$num.isna[n_of_records$key=="Flowers_per_plant"], n_of_records$num.isna[n_of_records$key=="Nectar_ul"],
+  n_of_records$num.isna[n_of_records$key=="Nectar_mg"], n_of_records$num.isna[n_of_records$key=="Nectar_concentration"], n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
+  n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level_fruit_set"])
 
-#dat%>%
-#kbl("latex", longtable = T, booktabs = T,linesep = "\\addlinespace")
+Number_of_records_categorical <- c(n_of_records$num.isna[n_of_records$key=="lifespan"], n_of_records$num.isna[n_of_records$key=="life_form"],
+                                   n_of_records$num.isna[n_of_records$key=="Flower_morphology"], n_of_records$num.isna[n_of_records$key=="Flower_symmetry"],
+                                   n_of_records$num.isna[n_of_records$key=="Nectar_presence_absence"], n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level"],
+                                   n_of_records$num.isna[n_of_records$key=="Compatibility_system"], n_of_records$num.isna[n_of_records$key=="Breeding_system"],
+                                   rep("",4))
 
-#%>%
+dat <- data.frame(Type, Trait,Number_of_records_quantitative,Type_1, Trait1, T.cat,Number_of_records_categorical)
 
-# add_header_above(c("Quantitative traits" = 2,"Qualitative traits" = 3))
+colnames(dat) <- c("Trait Type","Traits", "Records","Trait Type", "Traits", "Categories", "Records")
 
-#%>%  column_spec(c(1,3), bold = T,width="2em",extra_css="transform: rotate(-90deg);") %>%
- # collapse_rows(columns = c(1,3), valign = "middle")
-
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE) %>%
+kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c")) %>%
 kable_styling(full_width = T) %>%
-add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 3),bold=T)  %>%
-    column_spec(c(1,3), bold = T) %>% row_spec(0, bold=T)
+add_header_above(c("Quantitative traits" = 3,"Categorical traits" = 4),bold=T)  %>%
+    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)
 

### 2021-05-12 Supplementary_Material/Global_Trait_Spectrum_Nectar_Pollen.Rmd
Pollen nectar pPCA added

--- 2021-04-29 Supplementary_Material/Global_Trait_Spectrum_Nectar.Rmd
@@
 #Load data
-phyl_pca_forest_nectar_all <- readRDS("Data/RData/phyl_pca_forest_nectar_all.rds")
-dat_cleaning_5 <- readRDS("Data/RData/data_subset_nectar.rds")
+phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
+dat_cleaning_7 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen.rds")
 
-PC <- phyl_pca_forest_nectar_all
+PC <- phyl_pca_forest_nectar_pollen
 #CHECK CONTENT
@@
 #Images were made by Paula Martin
-#Check her work on https://paulamartinart.com/
 
-tree <- image_read("Images/PPCA_Plot/Tree.png")
-tree_1 <- as.raster(tree)
-
-style_l <- image_read("Images/PPCA_Plot/Style_Long.png")
-style_l_1 <- as.raster(style_l)
-
-style_s <- image_read("Images/PPCA_Plot/Style_Short.png")
-style_s_1 <- as.raster(style_s)
-
-ovule_h <- image_read("Images/PPCA_Plot/Ovule_High.png")
-ovule_h_1 <- as.raster(ovule_h)
-
-ovule_l <- image_read("Images/PPCA_Plot/Ovule_Low.png")
-ovule_l_1 <- as.raster(ovule_l)
-
-selfing_n <- image_read("Images/PPCA_Plot/Selfing_None.png")
-selfing_n_1 <- as.raster(selfing_n)
-
-selfing_h <- image_read("Images/PPCA_Plot/selfing.png")
-selfing_h_1 <- as.raster(selfing_h)
-
-single_flower <- image_read("Images/PPCA_Plot/Single_Flower.png")
-single_flower_1 <- as.raster(single_flower)
-
-many_flowers <- image_read("Images/PPCA_Plot/Inflorescencia.png")
-many_flowers_1 <- as.raster(many_flowers)
-#many_flowers_1 <- image_rotate(many_flowers, 45)
-
-large_flower <- image_read("Images/PPCA_Plot/flower_big.png")
-large_flower_1 <- as.raster(large_flower)
-
-flower_small <- image_read("Images/PPCA_Plot/flower_short.png")
-flower_small_1 <- as.raster(flower_small)
-
-herb <- image_read("Images/PPCA_Plot/herb.png")
-herb_1 <- as.raster(herb)
+PC$S[,1] <- -PC$S[,1]
 
@@
 
-  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-  # plot <- plot +geom_point(data=dat, aes(-x, -y, colour = density),size=0.65,shape = 1,colour = "black",alpha=0.8)
-
   plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
-    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.066),breaks = c(0.02, 0.035, 0.058), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
+    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
     scale_alpha(guide = 'none')
@@
   # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
 
   #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=-v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
 
@@
   #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height", "Nectar" )
+  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height", "Nectar","Pollen" )
 
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(5,4.95,4.8,4.8,5.3,4.5,4.8)), y = -(PCAloadings$PC2*c(5.2,4.5,3.95,4.25,5,4.5,4.55)+c(0,0,0,0,0.2,0,0)),
-                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,5.5,5.3,5.5,6.1,5.75,5.8,6)), y = (PCAloadings$PC2*c(4.8,4.8,4.65,5.65,5,5.1,5.75,5)+c(0,0,0,0,0,0,0,0)),
+                          label = PCAloadings$Variables, color="black",fontface =2,size=4)
 

### 2021-05-12 Supplementary_Material/Missing_data.Rmd
Pollen nectar pPCA added

@@
 ########################################################################################################################################################
-#SCRIPT TO CHECK PATTERNS OF MISSING VALUES
+#SCRIPT FOR DATA IMPUTATION
 ########################################################################################################################################################
@@
 
-#2) CLEAN DATA
+#2) CLEAN DATA AND RENAME LEVELS
 
 #3) EXPLORE PATTERNS OF MISSING DATA
+
+#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
+
+#5) ICLUDE EIGENVALUES IN RAWDATA TO IMPROVE IMPUTATION OURPUT
+
+#6) IMPUTE DATA
+
+#7) SAVE IMPUTED DATA 
 ########################################################################################################################################################
@@
 library(PVR) #calculate eigen vectors and add them as a column in the imputation, seems to improve output
-library(visdat)
+library(visdat) #VISUALIZE MISSING DATA
+library(naniar)
 library(tidyverse)
-
 ########################################################################################################################################################
@@
 
-#str(trait_data_1)
+str(trait_data_1)
 #filter data, select species with flower level info and capitulum
 trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-#levels(as.factor(trait_filtered$Info_level)) #checking levels
+levels(as.factor(trait_filtered$Info_level)) #checking levels
 #remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
@@
 trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-#str(trait_filtered_2)
+str(trait_filtered_2)
 
 #Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
+t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
                         "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
                         "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul")]
+                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
+                        "Pollen_per_flower")]
 
-####################################################################################################
-#2) CLEAN DATA. I REPEAT THE SAME PROCEDURE OF THE DATA IMPUTATION TO GET THE SAME NUMBER OF SPECIES
-####################################################################################################
+########################################################################################################################################################
+#####
+#B) RENAME LEVELS FOR IMPUTATION
+#####
+#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
+#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
+t$Breeding_system <- as.character(t$Breeding_system)
+t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
+t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
+t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
+#Change to capital letters| There are already levels with lower case
+t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
+t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
+t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
+levels(as.factor(t$Breeding_system))
+t$Breeding_system <- as.factor(t$Breeding_system)
+
+#Now 3 levels
+#Flower_morphology
+t$Flower_morphology <- as.character(t$Flower_morphology)
+t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
+t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
+t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
+t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
+t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
+t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
+t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
+t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
+t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
+t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
+t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
+t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
+levels(as.factor(t$Flower_morphology))
+t$Flower_morphology <- as.factor(t$Flower_morphology)
+
+#Life span
+t$lifespan <- as.character(t$lifespan )
+t$lifespan[t$lifespan=="annual"] <- "short_lived"
+t$lifespan[t$lifespan=="biennial"] <- "short_lived"
+t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
+t$lifespan[t$lifespan=="perennial"] <- "Perennial"
+levels(as.factor(t$lifespan))
+t$lifespan <- as.factor(t$lifespan )
+
+########################################################################################################################################################
+#3) EXPLORE PATTERNS OF MISSING DATA
+########################################################################################################################################################
+#Explore patterns of missing data
+missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)
+sort(missing_data[missing_data >= 0], decreasing=T)
+#nectar values all above 50% except presence/absence
+#then, just one cololumn with 68% missing data, then one with 35% and then 20% and 10%. The rest under 5%.
+#it is recommended to remove columns over 50% but we are particulary interested in having numeric levels of quantitative selfing 
+#we are going to work just with presence/absence of nectar
+#we will perform further analysis just with a subset with the quantitative values o nectar (very interesting data and diffciult to obtain)
+
+#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
+#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
+t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
+t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
+t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
+t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
+
+#t$Nectar_ul adding it here just to see how many cells 
+#Now we just select presence/absence of nectar
+#select columns of interest
+t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
+         "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
+         "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
+         "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
+         "Pollen_per_flower")]
+
+#check missing data now
+missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)*100
+sort(missing_data[missing_data >= 0], decreasing=T)
+
+missing_data <- unlist(lapply(t, function(x) nrow(t)-sum(is.na(x))))
+sum(missing_data)
+
+#Number of missing values on the datset
+#vis_miss(t[,c(6:20)])
+#9.9% percentage of missing values]
+
+#Checking number of filled cells/ just selecting variables used in the manuscript; nectar ul should be accounted too and it has been considered but
+#not added to run this code
+
+########################################################################################################################################################
+#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
+########################################################################################################################################################
+#Convert to factor 
+cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
+          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
+t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
+str(t)
+
+#Impute data considering phylogenetic distance of species
+#it improves quality of imputation
+#https://doi.org/10.1111/2041-210X.12232 see ref for method comparisons with and without imputation
+
+#Multiple imputation process with phylogeny --> Missforest
+#https://doi.org/10.1111/2041-210X.12232
+#althought it does not have an option we are going to add it as a column
+
 #Before data imputation I need to calculate the phylo of the species
@@
 #CHECK LEVELS
-#levels(factor(t$Species_all))
+levels(factor(t$Species_all))
 
@@
 
-#nrow(t)
-
 #Select just columns with traits
@@
                         "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul")]
+                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
+         "Pollen_per_flower")]
 
@@
          "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 
-         "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar quantitative")
+         "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar per flower (microlitres)", "Nectar per flower (miligrames)", "Nectar concentration (%)", "Pollen grains per flower")
 

### 2021-05-12 Scripts/Pollen_and_nectar_traits.R

@@ -59,6 +59,8 @@ str(trait_filtered_2)
 t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all",
                         "Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_ovule_ratio","Pollen_per_flower")]
 
+
+hist(log(t$Pollen_per_flower))
 colnames(t)[1] <- "Plant_species"
 
 #Now read visitation data

### 2021-05-12 Scripts/Traits_Table.R

@@ -1,24 +1,12 @@
-
 ########################################################################################################################################################
-#SCRIPT TO PREPARE TABLE WITH TRAITS
-########################################################################################################################################################
-
+#TRAIT TABLE
 ########################################################################################################################################################
 #LOAD LIBRARIES
 library(readxl) #read excel file (trait data)
 library(dplyr) #data manipulation
-library(missMDA) #For missing values
-library(FactoMineR) #Produce pca biplot with individuals and variables
-library(factoextra)
-library(ggpubr) 
-library(missForest) #random forst imputation
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(ape)
-library(PVR) #calculate eigen vectors and add them as a column in the imputation, seems to improve output
 library(visdat) #VISUALIZE MISSING DATA
 library(naniar)
-library(VIM)
-
+library(tidyverse)
 ########################################################################################################################################################
 #1) READ TRAIT DATA
 ########################################################################################################################################################
@@ -44,17 +32,119 @@ trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
 str(trait_filtered_2)
 
 #Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
+t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
                         "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul")]
[…]

### 2021-05-13 Main_Figures/Regression_Tree_Nectar_Pollen.Rmd
regression tree

@@
 # Create a decision tree model
-tree <- rpart(Interactions~., data=data_1, cp=.007)
+tree <- rpart(Interactions~., data=data_1, cp=.004)
 # Visualize the decision tree with rpart.plot

### 2021-05-13 Scripts/2_Missing_Data_Exploration.R

@@ -1,11 +1,19 @@
 ########################################################################################################################################################
-#SCRIPT TO CHECK PATTERNS OF MISSING VALUES
+#SCRIPT FOR DATA IMPUTATION
 ########################################################################################################################################################
 #1) READ TRAIT DATA
 
-#2) CLEAN DATA 
+#2) CLEAN DATA AND RENAME LEVELS
 
 #3) EXPLORE PATTERNS OF MISSING DATA
+
+#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
+
+#5) ICLUDE EIGENVALUES IN RAWDATA TO IMPROVE IMPUTATION OURPUT
+
+#6) IMPUTE DATA 
+
+#7) SAVE IMPUTED DATA 
 ########################################################################################################################################################
 #LOAD LIBRARIES
 library(readxl) #read excel file (trait data)
@@ -20,7 +28,6 @@ library(ape)
 library(PVR) #calculate eigen vectors and add them as a column in the imputation, seems to improve output
 library(visdat) #VISUALIZE MISSING DATA
 library(naniar)
-library(VIM)
 
 ########################################################################################################################################################
 #1) READ TRAIT DATA
@@ -47,15 +54,133 @@ trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
 str(trait_filtered_2)
 
 #Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
+t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
                         "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
                         "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul")]
[…]

### 2021-05-13 Scripts/Regression_Tree_Pollen_Nectar.R

@@ -1,0 +1,264 @@
+########################################################################################################################################################
+########################################################################################################################################################
+########################################################################################################################################################
+##REGRESSION TREE FOR THE SUBSET OF SPECIES WITH INFO OF POLLEN AND NECTAR
+########################################################################################################################################################
+########################################################################################################################################################
+########################################################################################################################################################
+
+#HERE I TRY TO SELECT THE MAIN EXPLANATORY TRAITS FOR EACH TRAIT 
+
+#LOAD LIBRARIES
+library(data.table) # operate with df
+library(bipartite) #calculate metrics
+library(dplyr) #data manipulation 
+library(stringr) #remove string
+library(brms)
+library(projpred)
+library(dplyr)
+library(ggplot2)
+library(bayesplot)
+library(ape)
+library(rtrees)
+library(cowplot)
+library(emmeans)
+library(tidybayes)
+library(multcomp)
+########################################################################################################################################################
+#1) LOAD NETWORK DATA
+########################################################################################################################################################
+#Set working directory to read files
+setwd("~/R_Projects/Reproductive traits/Data/Data_networks_quantitative") 
+
+#read csv files
+temp <- list.files(pattern="*.csv")
+my.list <- list(for (i in 1:length(temp)) assign(temp[i], read.csv(temp[i])))
+my_files <- list.files(pattern = "\\.csv$")
+my_data <- lapply(my_files, function(i){read.csv(i,  row.names = 1)})
+# Add id to dataframe
+names(my_data) <- stringr::str_replace(my_files, pattern = ".csv", replacement = "")
+
[…]

### 2021-05-17 Main_Figures/Analysis_1_Separated.Rmd
supp figures

@@
      theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
+           axis.title=element_text( size = rel(2)),
+           axis.text=element_text(size = rel(1.8), color = "black"),
            legend.title=element_text(face="bold",size=rel(2)),
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("High Flower N.    Large flowers")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
    "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
    "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles")+
-  theme_ms() +theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+  theme_ms() +theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
     "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),

### 2021-05-17 Main_Figures/Traits_Table.Rmd
supp figures

@@
 Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
-           "Flower per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")
+           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")
 
@@
 T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-           "Presence \n Absence", "None \n Low \n Medium \n High", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " "),align = c("l"))
+           "Presence \n Absence", "None \n Low \n Medium \n High", "Self-incomp. \n Partially self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " "),align = c("l"))
 
@@
 
-colnames(dat) <- c("Trait Type","Traits", "Records","Trait Type", "Traits", "Categories", "Records")
+colnames(dat) <- c("Type","Traits", "Records","Type", "Traits", "Categories", "Records")
 

### 2021-05-17 Supplementary_Material/Analysis_2_Hymenoptera_Families_Separated.Rmd
supp figures

---
output:
  pdf_document: default
  html_document: default
classoption: landscape

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28}

#LOAD LIBRARIES 
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(tidyverse)
library(patchwork) #panel of plots
library(brms)
library(cmdstanr)

#Load theme for publication

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2.2)),
           axis.text=element_text(size = rel(2), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.4)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(1.8, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank()
     ))
}

setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github

#Plot nicely PC1
analysis_1 <- readRDS("results_analysis_1_bee_families.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1_bee_families.rds")

ce_pc1 <- conditional_effects(analysis_1, effects = "PC1:bee_family",points=T)

a1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))+ggtitle("(a)") + theme(plot.title = element_text(size = 28, face = "bold"))
#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:bee_family",points=T)

a2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))+ggtitle("(b)") + theme(plot.title = element_text(size = 28, face = "bold"))

#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1, effects = "PC3:bee_family",points=T)

a3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))+ggtitle("(c)") + theme(plot.title = element_text(size = 28, face = "bold"))

library(patchwork)

combined <- a1 + a2 + a3 & theme(legend.position = "right")
combined + plot_layout(guides = "collect", ncol=3)

```

### 2021-05-17 Supplementary_Material/Figure_Analysis_Bees_Apis_Non_Apis.Rmd
supp figures

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=24}
 
@@
 
-#Plot nicely PC1
-analysis_1 <- readRDS("results_analysis_1_bee_families.rds")
-dat_analysis <- readRDS("dat_analysis_results_analysis_1_bee_families.rds")
-
-ce_pc1 <- conditional_effects(analysis_1, effects = "PC1:bee_family",points=T)
-
-a1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
-  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
-  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
-   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
-    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))+ggtitle("All bee species") + theme(plot.title = element_text(size = 36, face = "bold"))
-#Plot nicely PC2
-ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:bee_family",points=T)
-
-a2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
-  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
-   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
-    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))
-
-#Plot nicely PC3
-ce_pc3 <- conditional_effects(analysis_1, effects = "PC3:bee_family",points=T)
-
-a3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
-  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
-  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
-   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
-    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))
-
-analysis_1_bee_families_non_apis <- readRDS("results_analysis_1_bee_families_non_apis.rds")
-dat_analysis <- readRDS("dat_analysis_results_analysis_1_bee_families_non_apis.rds")
-
-ce_pc1 <- conditional_effects(analysis_1_bee_families_non_apis, effects = "PC1:bee_family",points=T)
-
-aa1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
-  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
-  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
-   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
-    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))+ ggtitle("A. mellifera excluded") + theme(plot.title = element_text(size = 36, face = "bold"))
-#Plot nicely PC2
-ce_pc2 <- conditional_effects(analysis_1_bee_families_non_apis, effects = "PC2:bee_family",points=T)
-
-aa2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
-  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
-   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
-    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))
-
-#Plot nicely PC3
-ce_pc3 <- conditional_effects(analysis_1_bee_families_non_apis, effects = "PC3:bee_family",points=T)
-
-aa3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
-  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
-  theme_ms() + theme(legend.position = "none")+  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
-   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
-    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))
-
 analysis_1_just_bees <- readRDS("results_analysis_1_just_bees.rds")
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
-  theme_ms() + theme(legend.position = "none") + ggtitle("All bee species")+
-  theme(plot.title = element_text(size = 36, face = "bold"))
+  theme_ms() + theme(legend.position = "none")
 
@@
 
+my_y_title_1 <- expression("All bee species")
+
 p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none") 
+  theme_ms() + theme(legend.position = "none")  + ggtitle(my_y_title_1)+
+  theme(plot.title = element_text(size = 36, face = "bold"))
 #Plot nicely PC3
@@
 pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis,
-      aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange")+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
-  theme_ms() + theme(legend.position = "none") + ggtitle("A. mellifera excluded") + theme(plot.title = element_text(size = 36, face = "bold"))
+      aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4")+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
+  theme_ms() + theme(legend.position = "none")
 
@@
 
+my_y_title <- expression(paste(italic("Apis mellifera"), " excluded"))
+
 pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,
-                                                                          aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
+                                                                          aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none") 
+  theme_ms() + theme(legend.position = "none")  + ggtitle(my_y_title)+
+  theme(plot.title = element_text(size = 36, face = "bold"))
 #Plot nicely PC3
@@
 pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis,
-                                                                          aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
+                                                                          aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
@@
 
-combined <- a1 + a2 + a3 + aa1 + aa2 + aa3 + p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "right")
+combined <- p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "right")
 combined + plot_layout(guides = "collect", ncol=3)

### 2021-05-17 Supplementary_Material/Phylo_Signal_Table.Rmd
supp figures

@@
 plant_height <- readRDS("Data/RData/plant_height_phylo.rds")
+#POLLEN
+pollen <- readRDS("Data/RData/pollen_phylo.rds")
+#Nectar ul
+nectar_ul <- readRDS("Data/RData/Nectar_ul_phylo.rds")
+#Nectar mg
+nectar_mg <- readRDS("Data/RData/Nectar_mg_phylo.rds")
+#Nectar concentration
+nectar_con <- readRDS("Data/RData/Nectar_concentration_phylo.rds")
 
@@
 #LABELS
-label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height")
+label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Pollen grains per flower", "Nectar ($\\mu$l) per flower", "Nectar (mg) per flower", "Nectar concentration ($\\%$)")
 #LAMBDA
-lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda)
+lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, pollen$lambda, nectar_ul$lambda, nectar_mg$lambda, nectar_con$lambda)
 #P-VALUE
-p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P)
+p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P, pollen$P,nectar_ul$P,
+            nectar_mg$P,  nectar_con$P)
 
@@
 
-colnames(tabla) <- c("Variable", "Lambda", "P-value")
+colnames(tabla) <- c("Functional traits", "Lambda", "P-value")
 
-kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
+kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE) %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")

### 2021-05-17 Scripts/1_Merge_Spp_Names_Long_format.R

@@ -1060,3 +1060,23 @@ write.csv(all_bee_non_apis, "Data/Csv/long_format_quantitative_networks_bees_non
 
 
 
+#Check apis names
+apis <- subset(all_long_poll_names, genus=="Apis")
+#check levels
+levels(factor(apis$Pollinator_species))
+
+#rename dataframe
+dat <- all_long_poll_names
+
+#select interations that took place
+dat_1 <- dat[dat$Interaction>0,]
+
+#Rename all apis to calculate real proportion
+dat_1$Pollinator_species[dat_1$Pollinator_species=="Apis melifera"] <- "Apis mellifera"
+dat_1$Pollinator_species[dat_1$Pollinator_species=="Apis mellifera adansonii"] <- "Apis mellifera"
+dat_1$Pollinator_species[dat_1$Pollinator_species=="Apis cerana"] <- "Apis mellifera"
+
+#Proportion of A.mellifera visits 7.557312
+nrow(dat_1[dat_1$Pollinator_species=="Apis mellifera",])/nrow(dat_1[dat_1$Pollinator_species,])*100
+
+

### 2021-05-17 Scripts/Regression_Tree_Pollen_Nectar.R

@@ -24,6 +24,8 @@ library(cowplot)
 library(emmeans)
 library(tidybayes)
 library(multcomp)
+library(rpart)
+library(rpart.plot)
 ########################################################################################################################################################
 #1) LOAD NETWORK DATA
 ########################################################################################################################################################
@@ -189,7 +191,11 @@ df <- df[c("Visits", "Autonomous_selfing_level_fruit_set","Flowers_per_plant","C
                   "Plant_height_mean_m","Nectar_ul","Nectar_mg","Nectar_concentration", "Pollen_per_flower")]
 
 
-tree <- rpart(Visits~., data=df, cp=0.0086964) #8 divisions
+
+df$Visits <- log10(df$Visits+1)
+
+
+tree <- rpart(Visits~., data=df, cp=0.013059) #8 divisions
 rpart.plot(tree, box.palette="GnOr")
 printcp(tree)
 plotcp(tree)

### 2021-05-17 Supplementary_Material/Supplementary_Material.Rmd
edits

--- 2021-05-12 Supplementary_Material/Missing_data.Rmd
@@
 ```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10}
+setwd("~/R_Projects/Reproductive Traits")
+
+#Load libraries
+#LOAD LIBRARIES
+library(phytools)
+library(ape) #for phylogenetic distance
+library(dplyr) #data processing
+library(rtrees) #for phylogenetic distancelibrary(MASS)
+library(reshape2)
+library(viridis) #COLOUR GGPLOT
+library(MASS)
+library(ggplot2)
+library(broman) #crayon colours
+library(cowplot)
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+      theme(text=element_text(color="black"),
+            axis.title=element_text( size = rel(1.2)),
+            axis.text=element_text(size = rel(1.75), color = "black"),
+            legend.title=element_text(face="bold"),
+            legend.text=element_text(),
+            legend.background=element_rect(fill="transparent"),
+            legend.key.size = unit(1.2, 'lines'),
+            panel.border=element_rect(color="black",size=1),
+            panel.grid.minor.x =element_blank(),
+            panel.grid.minor.y= element_blank(),
+             panel.grid.major= element_blank()
+      ))
+}
+
+#Load data
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+PC <- phyl_pca_forest
+#CHECK CONTENT
+#EIGENVALUES
+PC$Eval
+#PC score (POINTS)
+PC$S
+#PC loadings (ARROWS)
+PC$L
+
+library(magick)
+
+#Images were made by Paula Martin
+#Check her work on https://paulamartinart.com/
+
+tree <- image_read("Images/PPCA_Plot/Tree.png")
+tree_1 <- as.raster(tree)
+
+style_l <- image_read("Images/PPCA_Plot/Style_Long.png")
+style_l_1 <- as.raster(style_l)
+
+style_s <- image_read("Images/PPCA_Plot/Style_Short.png")
+style_s_1 <- as.raster(style_s)
+
+ovule_h <- image_read("Images/PPCA_Plot/Ovule_High.png")
+ovule_h_1 <- as.raster(ovule_h)
+
+ovule_l <- image_read("Images/PPCA_Plot/Ovule_Low.png")
+ovule_l_1 <- as.raster(ovule_l)
+
+selfing_n <- image_read("Images/PPCA_Plot/Selfing_None.png")
+selfing_n_1 <- as.raster(selfing_n)
+
+selfing_h <- image_read("Images/PPCA_Plot/selfing.png")
+selfing_h_1 <- as.raster(selfing_h)
+
+single_flower <- image_read("Images/PPCA_Plot/Single_Flower.png")
+single_flower_1 <- as.raster(single_flower)
+
+many_flowers <- image_read("Images/PPCA_Plot/Inflorescencia.png")
+many_flowers_1 <- as.raster(many_flowers)
+#many_flowers_1 <- image_rotate(many_flowers, 45)
+
+large_flower <- image_read("Images/PPCA_Plot/flower_big.png")
+large_flower_1 <- as.raster(large_flower)
+
+flower_small <- image_read("Images/PPCA_Plot/flower_short.png")
+flower_small_1 <- as.raster(flower_small)
+
+herb <- image_read("Images/PPCA_Plot/herb.png")
+herb_1 <- as.raster(herb)
+
+#############################################################################################################################################################
+#COMPATIBILITY
+#############################################################################################################################################################
+#Load plots
+
+#Invert axes
+PC$S[,1] <- -PC$S[,1]
+PC$S[,2] <- -PC$S[,2]
+
+pc3 <- function(PC, x="PC1", y="PC3") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
+  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
+    scale_alpha(guide = 'none')
+
+    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .7 * mult * (get(x)),
+                      v2 = .7 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+
+   #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("PC3 ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
+
+  #CHANGE THEME
+
+  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
+ #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
+ # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
+ # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
+ # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
+ # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
+ # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
+ # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
+ # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
+ # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
+ # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
+ # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
+
+      #ADD LABELS
+  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+ plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,4.8,7.1,5.5)), y = -(PCAloadings$PC2*c(-3.2,4.5,3.75,8.4,5,5.5)+c(0,0,0,0,-0.08,0)),
+                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
+
+  plot
+
+}
+
+pc3(PC)
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28}
+
+library(patchwork) #panel of plots
+library(brms)
+library(ggplot2)
+#Load theme for publication
+
+theme_ms <- function(base_size=14, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(2.2)),
+           axis.text=element_text(size = rel(2), color = "black"),
+           legend.title=element_text(face="bold",size=rel(2)),
+           legend.text=element_text(size=rel(1.4)),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(1.8, 'lines'),
+           panel.border=element_rect(color="black",size=2.4),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank()
+     ))
+}
+
+setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
+
+#Plot nicely PC1
+analysis_1 <- readRDS("r_bee_families.rds")
+dat_analysis <- readRDS("dat_bee_families.rds")
+
+```

### 2021-05-17 Scripts/5_Analysis_1_Visits_Bees_Func_Groups_X_PCS.R

@@ -156,8 +156,8 @@ saveRDS(dat_analysis, "dat_analysis_results_analysis_1_bee_families.rds")
 #PLOT
 ########################################################################################################################################################
 #Plot nicely PC1
-analysis_1 <- readRDS("results_analysis_1_bee_families.rds")
-dat_analysis <- readRDS("dat_analysis_results_analysis_1_bee_families.rds")
+analysis_1 <- readRDS("r_bee_families.rds")
+dat_analysis <- readRDS("dat_bee_families.rds")
 
 
 ce_pc1 <- conditional_effects(analysis_1, effects = "PC1:bee_family",points=T) 

### 2021-05-18 Supplementary_Material/Analysis_2_Hymenoptera_Families_Separated.Rmd
edits
Preparing supplementary material

@@
   html_document: default
-classoption: landscape
 
@@
 #Plot nicely PC1
-analysis_1 <- readRDS("results_analysis_1_bee_families.rds")
-dat_analysis <- readRDS("dat_analysis_results_analysis_1_bee_families.rds")
+analysis_1 <- readRDS("r_bee_families.rds")
+dat_analysis <- readRDS("dat_bee_families.rds")
 
@@
 combined <- a1 + a2 + a3 & theme(legend.position = "right")
-combined + plot_layout(guides = "collect", ncol=3)
+combined_1 <- combined + plot_layout(guides = "collect", ncol=3)
 
+saveRDS(combined_1, "Plot_bee_families.rds")
+
+combined_2 <- readRDS("Plot_bee_families.rds")
+
+combined_2
 ```

### 2021-05-18 Supplementary_Material/Supplementary_Material.Rmd
Preparing supplementary material

@@
   html_document: default
+header-includes:
+- \usepackage{pdflscape}
+- \newcommand{\blandscape}{\begin{landscape}}
+- \newcommand{\elandscape}{\end{landscape}}
+- \usepackage{float}
+- \usepackage{caption}
+- \usepackage{setspace}\doublespacing
+- \usepackage{soul}
 
 ---
+\captionsetup[figure]{labelformat=empty}
+\captionsetup[table]{labelformat=empty}
+\captionsetup[table]{font={stretch=1.2}}
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000}
+\renewcommand{\figurename}{}
+
+#Tables
+
+\begin{landscape}
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = "left"}
+setwd("~/R_Projects/Reproductive Traits")
+library(kableExtra)
+
+#Create data.frame with references
+
+`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1", "1", "1", "1", "1", "1", "1", "3", "1",
+                          "1", "1")
+
+#`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))
+
+`Network type` <- c(rep("Weighted web",  18), rep("Unweighted web",  4), "Weighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Weighted metaweb")
+
+`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
+                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard", "Bek", "Kato", "Kevan", "Ramirez",
+                    "Inouye","McMullen", "Primack", "Ramirez", "Robertson", "Traveset")
+
+Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003,2006,2000,1970,1989,1990, 1993, 1983, 1992, 1929, 2013)
+
+#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
+#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
+#"USA", "Ecuador")
+
+DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
+"https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
+"https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
+"/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
+"https://doi.org/10.1111/j.1365-2745.2010.01732.x", "https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510",
+"https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis", "Unpublished, Master thesis", "http://hdl.handle.net/2433/156116",
+"https://doi.org/10.2307/2258569", "https://doi.org/10.2307/2388282", "http://hdl.handle.net/2433/156099", "https://biostor.org/reference/244737", "https://doi.org/10.1080/0028825X.1983.10428561",
+"https://doi.org/10.1111/j.1095-8339.1992.tb00294.x", "https://doi.org/10.5962/bhl.title.11538", "https://doi.org/10.1098/rspb.2012.3040")
+
+references <- data.frame(`First author`, Year, `Number of networks`,`Network type`,   DOI)
+
+colnames(references) <- c("First author", "Year", "Web N.",  "Network type",  "DOI")
+
+library(dplyr)
+ references %>%
+ arrange(`First author`)%>%
+kable("latex", longtable = T, booktabs = T,linesep = "\\addlinespace",
+             caption = "\\textbf{Table S1.} List of the 28 plant-pollinator studies used to build the plant trait database.
+Each study is shown with the first author that conducted the study, number of networks or metawebs that contains, type of information that contains (weighted or unweighted),  the structure (web or metaweb), year of publication and digital object identifier or permanent link for each study.") %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "left")
+
+```
+
+\end{landscape}
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
+
+library(kableExtra)
+
+setwd("~/R_Projects/Reproductive Traits")
+
+#SELFING
+selfing <- readRDS("Data/RData/selfing_phylo.rds")
+#FLOWER NUMBER
+flower_n <- readRDS("Data/RData/flower_n_phylo.rds")
+#INFLO WIDTH
+inflow_width <- readRDS("Data/RData/inflow_width_phylo.rds")
+#FLOWER WIDTH
+flower_width <- readRDS("Data/RData/flower_width_phylo.rds")
+#FLOWER LENGHT
+flower_length <- readRDS("Data/RData/flower_length_phylo.rds")
+#STYLE LENGTH
+style_n <- readRDS("Data/RData/style_n_phylo.rds")
+#OVULE NUMBER
+ovule_n <- readRDS("Data/RData/ovule_n_phylo.rds")
+#PLANT HEIGHT
+plant_height <- readRDS("Data/RData/plant_height_phylo.rds")
+#POLLEN
+pollen <- readRDS("Data/RData/pollen_phylo.rds")
+#Nectar ul
+nectar_ul <- readRDS("Data/RData/Nectar_ul_phylo.rds")
+#Nectar mg
+nectar_mg <- readRDS("Data/RData/Nectar_mg_phylo.rds")
+#Nectar concentration
+nectar_con <- readRDS("Data/RData/Nectar_concentration_phylo.rds")
+
+#Select two decimals function
+specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
+#LABELS
+label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Pollen grains per flower", "Nectar ($\\mu$l) per flower", "Nectar (mg) per flower", "Nectar concentration ($\\%$)")
+#LAMBDA
+lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, pollen$lambda, nectar_ul$lambda, nectar_mg$lambda, nectar_con$lambda)
+#P-VALUE
+p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P, pollen$P,nectar_ul$P,
+            nectar_mg$P,  nectar_con$P)
+
+tabla <- data.frame(label, specify_decimal(lambda,2), specify_decimal(p_value,2))
+
+colnames(tabla) <- c("Functional traits", "Lambda", "P-value")
+
+kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE) %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
+
+```
+
+\pagebreak
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
+
+library(dplyr)
+library(kableExtra)
+
+setwd("~/R_Projects/Reproductive Traits")
+
+PC <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+dat <- PC$L[,c(1:3)]
+
+#Create a row to add total percentage of variance explained by PC
+
+percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+percen <- percentage[1:3]
+
+dat <- rbind(dat, percen)
+
+rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Explained variation")
+
+dat <- as.data.frame(dat)
+
+dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
+
+ kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE) %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
+
+```
+
+\pagebreak
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
+
+library(dplyr)
+library(kableExtra)
+
+setwd("~/R_Projects/Reproductive Traits")
+
+PC <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
+
+dat <- PC$L[,c(1:3)]
+
+#Create a row to add total percentage of variance explained by PC
+
+percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+percen <- percentage[1:3]
+
+dat <- rbind(dat, percen)
+
+rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Microlitres of Nectar per flower" , "Pollen per flower","Explained variation")
+
+dat <- as.data.frame(dat)
+
+dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
+
+kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE) %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
+
+```
+
+\newpage
+
+#Figures
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="**Fig.
+S1**  Percentage of present and missing values on the 20 traits compiled in this study (N = 1,506 species)."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="**Fig. S2**"}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28}
+\blandscape
 
-library(patchwork) #panel of plots
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="**Fig. S3**"}
+
+library(Rcpp)
+library(patchwork)
 library(brms)
 library(ggplot2)
+library(rstan)
+library(tidyr)
+rstan_options(auto_write = TRUE)
 #Load theme for publication
@@
 
-#Plot nicely PC1
-analysis_1 <- readRDS("r_bee_families.rds")
-dat_analysis <- readRDS("dat_bee_families.rds")
+#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
+
+plot <- readRDS("Plot_bee_families.rds")
+
+plot
 
 ```
+
+\elandscape
+
+\blandscape
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28,  fig.cap="**Fig. S4**"}
+
+library(Rcpp)
+library(patchwork)
+library(brms)
+library(ggplot2)
+library(rstan)
+library(tidyr)
+rstan_options(auto_write = TRUE)
+#Load theme for publication
+
+theme_ms <- function(base_size=14, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(2.2)),
+           axis.text=element_text(size = rel(2), color = "black"),
+           legend.title=element_text(face="bold",size=rel(2)),
+           legend.text=element_text(size=rel(1.4)),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(1.8, 'lines'),
+           panel.border=element_rect(color="black",size=2.4),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank()
+     ))
+}
+
+setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
+
+#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
+
+plot_apis <- readRDS("Plot_apis.rds")
+
+plot_apis
+
+```
+
+\elandscape
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="**Fig. S5**"}
+setwd("~/R_Projects/Reproductive Traits")
+
+#Load libraries
+#LOAD LIBRARIES
+library(phytools)
+library(ape) #for phylogenetic distance
+library(dplyr) #data processing
+library(rtrees) #for phylogenetic distancelibrary(MASS)
+library(reshape2)
+library(viridis) #COLOUR GGPLOT
+library(MASS)
+library(ggplot2)
+library(broman) #crayon colours
+library(cowplot)
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+      theme(text=element_text(color="black"),
+            axis.title=element_text( size = rel(1.2)),
+            axis.text=element_text(size = rel(1.75), color = "black"),
+            legend.title=element_text(face="bold"),
+            legend.text=element_text(),
+            legend.background=element_rect(fill="transparent"),
+            legend.key.size = unit(1.2, 'lines'),
+            panel.border=element_rect(color="black",size=1),
+            panel.grid.minor.x =element_blank(),
+            panel.grid.minor.y= element_blank(),
+             panel.grid.major= element_blank()
+      ))
+}
+
+#Load data
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+PC <- phyl_pca_forest
+#CHECK CONTENT
+#EIGENVALUES
+PC$Eval
+#PC score (POINTS)
+PC$S
+#PC loadings (ARROWS)
+PC$L
+
+#############################################################################################################################################################
+#COMPATIBILITY
+#############################################################################################################################################################
+#Load plots
+
+#Invert axes
+PC$S[,1] <- -PC$S[,1]
+PC$S[,2] <- -PC$S[,2]
+
+pc3 <- function(PC, x="PC1", y="PC3") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
+  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
+    scale_alpha(guide = 'none')
+
+    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .7 * mult * (get(x)),
+                      v2 = .7 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+
+   #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("PC3 ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
+
+  #CHANGE THEME
+
+  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
+ #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
+ # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
+ # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
+ # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
+ # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
+ # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
+ # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
+ # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
+ # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
+ # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
+ # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
+
+      #ADD LABELS
+  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+ plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,4.8,7.1,5.5)), y = -(PCAloadings$PC2*c(-3.2,4.5,3.75,8.4,5,5.5)+c(0,0,0,0,-0.08,0)),
+                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
+
+  plot
+
+}
+
+pc3(PC)
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="**Fig. S6**"}
+setwd("~/R_Projects/Reproductive Traits")
+
+#Load libraries
+#LOAD LIBRARIES
+library(phytools)
+library(ape) #for phylogenetic distance
+library(dplyr) #data processing
+library(rtrees) #for phylogenetic distancelibrary(MASS)
+library(reshape2)
+library(viridis) #COLOUR GGPLOT
+library(MASS)
+library(ggplot2)
+library(broman) #crayon colours
+library(cowplot)
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+      theme(text=element_text(color="black"),
+            axis.title=element_text( size = rel(1.2)),
+            axis.text=element_text(size = rel(1.75), color = "black"),
+            legend.title=element_text(face="bold"),
+            legend.text=element_text(),
+            legend.background=element_rect(fill="transparent"),
+            legend.key.size = unit(1.2, 'lines'),
+            panel.border=element_rect(color="black",size=1),
+            panel.grid.minor.x =element_blank(),
+            panel.grid.minor.y= element_blank(),
+             panel.grid.major= element_blank()
+      ))
+}
+
+#Load data
+phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
+dat_cleaning_7 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen.rds")
+
+PC <- phyl_pca_forest_nectar_pollen
+#CHECK CONTENT
+#EIGENVALUES
+PC$Eval
+#PC score (POINTS)
+PC$S
+#PC loadings (ARROWS)
+PC$L
+
+library(magick)
+
+#Images were made by Paula Martin
+
+PC$S[,1] <- -PC$S[,1]
+
+all_spp <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
+    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
+    scale_alpha(guide = 'none')
+
+  plot <- plot + geom_point(data=dat, aes(x, y),size=0.95, color="black")
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .7 * mult * (get(x)),
+                      v2 = .7 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=-v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+
+  #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+
+  #CHANGE THEME
+
+  plot <- plot + theme_bw()
+
+  #ADD LABELS
+  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height", "Nectar","Pollen" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,5.5,5.3,5.5,6.1,5.75,5.8,6)), y = (PCAloadings$PC2*c(4.8,4.8,4.65,5.65,5,5.1,5.75,5)+c(0,0,0,0,0,0,0,0)),
+                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
+
+  plot
+
+}
+
+all_spp(PC)
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=14}
+
+########################################################################################################################################################
+#CORRELATION BETWEEN QUALITATIVE VARIABLES AND PC's
+########################################################################################################################################################
+#NOTES
+#I did not include the qualitative variables when I prepare the data for the PPCA
+#So I have to recalculate the ata here with the qualitative variables
+########################################################################################################################################################
+#LOAD LIBRARIES
+library(emmeans)
+library(ggplot2)
+library(patchwork)
+library(dplyr)
+
+theme_ms <- function(base_size=10, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(1.3)),
+           axis.text=element_text(size = rel(1.1), color = "black"),
+           panel.border=element_rect(color="black",size=1.2),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank(),
+           legend.position = "none",
+           plot.title = element_text(face = "bold",size = rel(1.45)),
+           plot.subtitle = element_text(face = "bold",size = rel(1.3))
+     ))
+}
+
+########################################################################################################################################################
+setwd("~/R_Projects/Reproductive Traits")
+
+#LOAD DATA
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+dat <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
+########################################################################################################################################################
+#remove not found species, cannot do PCA with unequal numbers of rows
+cols.num <- c("Family_all","Genus_all","Species_all")
+dat[cols.num] <- sapply(dat[cols.num],as.character)
+dat$Species_all <- gsub("Species_all_", "", dat$Species_all)
+########################################################################################################################################################
+#3) REMOVE OUTLIERS, OUT OF 2.5-97.5 RANGE WHICH HELPS IMPUTATION PROCESS. SEE ARTICLE FOR REF.
+########################################################################################################################################################
+dat_cleaning <- dat[,]
+#CHECK LEVELS
+
+dat_cleaning_1 <- dat_cleaning %>%
+  filter(between(Flowers_per_plant, quantile(Flowers_per_plant, 0.025), quantile(Flowers_per_plant, 0.975)))
+
+dat_cleaning_2 <- dat_cleaning_1 %>%
+  filter(between(Corolla_diameter_mean, quantile(Corolla_diameter_mean, 0.025), quantile(Corolla_diameter_mean, 0.975)))
+
+dat_cleaning_3 <- dat_cleaning_2 %>%
+  filter(between(Style_length, quantile(Style_length, 0.025), quantile(Style_length, 0.975)))
+
+dat_cleaning_4 <- dat_cleaning_3 %>%
+  filter(between(Ovule_number, quantile(Ovule_number, 0.025), quantile(Ovule_number, 0.975)))
+
+dat_cleaning_5 <- dat_cleaning_4 %>%
+  filter(between(Plant_height_mean_m, quantile(Plant_height_mean_m, 0.025), quantile(Plant_height_mean_m, 0.975)))
+
+final_d <- dat_cleaning_5[,]
+
+pca_data <- as.data.frame(phyl_pca_forest$S)
+
+d <- cbind(final_d, pca_data)
+
+#Prepare qualitative variables
+d$Compatibility_system[d$Compatibility_system=="dioecious"] <- "Unisexual flowers"
+d$Compatibility_system[d$Compatibility_system=="monoecious"] <- "Unisexual flowers"
+d$Compatibility_system[d$Compatibility_system=="partially_self_compatible"] <- "Partially self compatible"
+d$Compatibility_system[d$Compatibility_system=="self_compatible"] <- "Self compatible"
+d$Compatibility_system[d$Compatibility_system=="self_incompatible"] <- "Self incompatible"
+d$Compatibility_system <- factor(d$Compatibility_system, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
+
+d$life_form[d$life_form=="herb"] <- "Herb"
+d$life_form[d$life_form=="shrub"] <- "Shrub"
+d$life_form[d$life_form=="tree"] <- "Tree"
+d$life_form[d$life_form=="vine"] <- "Shrub"
+
+d$Flower_symmetry[d$Flower_symmetry=="actinomorphic"] <- "Actinomorphic"
+d$Flower_symmetry[d$Flower_symmetry=="zygomorphic"] <- "Zygomorphic"
+
+d$Flower_symmetry[d$Flower_symmetry=="Funnelform"] <- "Campanulate"
+d$Flower_symmetry[d$Flower_symmetry=="Spike"] <- "Brush"
+
+d$Flower_morphology[d$Flower_morphology=="Funnelform"] <- "Campanulate"
+d$Flower_morphology[d$Flower_morphology=="Spike"] <- "Brush"
+
+d$Nectar_presence_absence[d$Nectar_presence_absence=="yes"] <- "Yes"
+d$Nectar_presence_absence[d$Nectar_presence_absence=="no"] <- "No"
+
+#The other qualitative are ok
+
+#All principal components are normally distributed
+#Convert to factor before running model
+d[sapply(d, is.character)] <- lapply(d[sapply(d, is.character)], as.factor)
+
+#Run model
+model1 <- lm(PC1 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
+model2 <- lm(PC2 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
+
+####################################################################################################################################################################################################################################
+#1) BREEDING SYSTEM
+####################################################################################################################################################################################################################################
+model_breeding_1 <- emmeans(model1, "Breeding_system")
+breeding_1 <- as.data.frame(model_breeding_1[1:3])
+breed1 <- multcomp::cld(model_breeding_1, alpha = 0.10, Letters = LETTERS)
+
+breed_1 <- ggplot(breed1,aes(x= Breeding_system,y= emmean,
+               label = .group)) +theme_minimal()+
+  geom_point(data = breed1, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
+                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "(a) Breeding system")+
+  theme(plot.title = element_text(hjust=0.5, size=25, face="bold"))+
+  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
+
+model_breeding_2 <- emmeans(model2, "Breeding_system")
+breeding_2 <- as.data.frame(model_breeding_2[1:3])
+breed2 <- multcomp::cld(model_breeding_2, alpha = 0.10, Letters = LETTERS)
+
+breed_2 <- ggplot(breed2,aes(x= Breeding_system,y= emmean,
+             label = .group)) +theme_minimal()+
+  geom_point(data = breed2, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
+                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "(b) Breeding system")+
+  theme(plot.title = element_text(hjust=0.5,size=25, face="bold") )+
+  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
+
+########################################################################################################################################################
+#2) COMPATIBILITY
+########################################################################################################################################################
+model_com <- emmeans(model1, "Compatibility_system")
+
+d <- as.data.frame(model_com[1:4])
+comp1 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
+
+comp_1 <- ggplot(comp1,aes(x= Compatibility_system,y= emmean,
+  label = .group)) +theme_minimal()+
+  geom_point(data = comp1, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
+  width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(c) Compatibility system")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
+
+model_com <- emmeans(model2, "Compatibility_system")
+d <- as.data.frame(model_com[1:4])
+comp2 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
+
+comp_2 <- ggplot(comp2,aes(x= Compatibility_system,y= emmean,
+  label = .group)) +theme_minimal()+
+  geom_point(data = comp2, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
+  width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(d) Compatibility system")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
+
+########################################################################################################################################################
+#3) LIFESPAN
+########################################################################################################################################################
+model_lif_1 <- emmeans(model1, "lifespan")
+lif_1 <- as.data.frame(model_lif_1[1:2])
+lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
+
+lifespan_1 <- ggplot(lif_1,aes(x= lifespan,y= emmean,
+             label = .group)) +theme_minimal()+
+  geom_point(data = lif_1, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
+                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "(e) Lifespan")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
+
+model_lif_2 <- emmeans(model2, "lifespan")
+lif_2 <- as.data.frame(model_lif_2[1:2])
+lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
+
+lifespan_2 <- ggplot(lif_2,aes(x= lifespan,y= emmean,
+                 label = .group)) +theme_minimal()+
+  geom_point(data = lif_2, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
+                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "(f) Lifespan")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")
+
+########################################################################################################################################################
+# 4) LIFE FORM
+########################################################################################################################################################
+
+model_lif_1 <- emmeans(model1, "life_form")
+lif_1 <- as.data.frame(model_lif_1[1:3])
+lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
+
+lifeform_1 <- ggplot(lif_1,aes(x= life_form,y= emmean,
+                 label = .group)) +theme_minimal()+
+  geom_point(data = lif_1, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
+                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "(g) Life form")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
+
+model_lif_2 <- emmeans(model2, "life_form")
+lif_2 <- as.data.frame(model_lif_2[1:3])
+lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
+
+lifeform_2 <- ggplot(lif_2,aes(x= life_form,y= emmean,
+                 label = .group)) +theme_minimal()+
+  geom_point(data = lif_2, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
+                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "(h) Life form")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
+
+########################################################################################################################################################
+# 5) FLOWER MORPHOLOGY
+########################################################################################################################################################
+model_flo_1 <- emmeans(model1, "Flower_morphology")
+flo_1 <- as.data.frame(model_flo_1[1:6])
+flo_1 <- multcomp::cld(model_flo_1, alpha = 0.10, Letters = LETTERS)
+
+shape_1 <- ggplot(flo_1,aes(x= Flower_morphology,y= emmean,
+                 label = .group)) +theme_minimal()+
+  geom_point(data = flo_1, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
+                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(i) Flower shape")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")
+
+model_flo_2 <- emmeans(model2, "Flower_morphology")
+flo_2 <- as.data.frame(model_flo_2[1:6])
+flo_2 <- multcomp::cld(model_flo_2, alpha = 0.10, Letters = LETTERS)
+
+shape_2 <- ggplot(flo_2,aes(x= Flower_morphology,y= emmean,
+                 label = .group)) +theme_minimal()+
+  geom_point(data = flo_2, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
+                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(j) Flower shape")+
+   geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
+
+########################################################################################################################################################
+#6) FLOWER SYMMETRY
+########################################################################################################################################################
+model_flo_sym_1 <- emmeans(model1, "Flower_symmetry")
+flo_sym_1 <- as.data.frame(model_flo_sym_1[1:2])
+flo_sym_1 <- multcomp::cld(model_flo_sym_1, alpha = 0.10, Letters = LETTERS)
+
+symmetry_1 <-ggplot(flo_sym_1,aes(x= Flower_symmetry,y= emmean,
+                 label = .group)) +theme_minimal()+
+  geom_point(data = flo_sym_1, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
+                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "(k) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
+
+model_flo_sym_2 <- emmeans(model2, "Flower_symmetry")
+flo_sym_2 <- as.data.frame(model_flo_sym_2[1:2])
+flo_sym_2 <- multcomp::cld(model_flo_sym_2, alpha = 0.10, Letters = LETTERS)
+
+symmetry_2 <- ggplot(flo_sym_2,aes(x= Flower_symmetry,y= emmean,
+                     label = .group)) +theme_minimal()+
+  geom_point(data = flo_sym_2, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
+                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("sienna2","purple"))+labs(title = "(l) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
+
+########################################################################################################################################################
+#7) NECTAR
+########################################################################################################################################################
+model_nec <- emmeans(model1, "Nectar_presence_absence")
+
+model_nec_1 <- emmeans(model1, "Nectar_presence_absence")
+nec_1 <- as.data.frame(model_nec_1[1:2])
+nec_1 <- multcomp::cld(model_nec_1, alpha = 0.10, Letters = LETTERS)
+
+nectar_1 <- ggplot(nec_1,aes(x= Nectar_presence_absence,y= emmean,
+                     label = .group)) +theme_minimal()+
+  geom_point(data = nec_1, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
+                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("black","grey"))+labs(title = "(m) Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
+
+model_nec_2 <- emmeans(model2, "Nectar_presence_absence")
+nec_2 <- as.data.frame(model_nec_2[1:2])
+nec_2 <- multcomp::cld(model_nec_2, alpha = 0.10, Letters = LETTERS)
+
+nectar_2 <-ggplot(nec_2,aes(x= Nectar_presence_absence,y= emmean,
+                     label = .group)) +theme_minimal()+
+  geom_point(data = nec_2, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
+                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("black","grey"))+labs(title = "(n) Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")
+
+#PLOT!
+
+breed_1 + breed_2+ comp_1+ comp_2+ lifespan_1+ lifespan_2+ lifeform_1+ lifeform_2+ shape_1+ shape_2+
+symmetry_1+ symmetry_2+ nectar_1+ nectar_2 + plot_layout(ncol = 2)
+
+```

### 2021-05-18 Supplementary_Material/Analysis_2_Hymenoptera_Families_Separated.Rmd
Preparing supp material and now additional table with anova output with qualitative assoc.

@@
   theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
-   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
-    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))+ggtitle("(a)") + theme(plot.title = element_text(size = 28, face = "bold"))
+   "Megachilidae"),values=c("blueviolet", "orange", "limegreen","#E7298A", "cyan4"),
+    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae"))+ggtitle("(a)") + theme(plot.title = element_text(size = 28, face = "bold"))
 #Plot nicely PC2
@@
   theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
-   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
-    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))+ggtitle("(b)") + theme(plot.title = element_text(size = 28, face = "bold"))
+   "Megachilidae"),values=c("blueviolet", "orange", "limegreen","#E7298A", "cyan4"),
+    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae"))+ggtitle("(b)") + theme(plot.title = element_text(size = 28, face = "bold"))
 
@@
   theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
-   "Megachilidae", "All families"),values=c("blueviolet", "black", "limegreen","#E7298A", "cyan4","orange"),
-    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae", "All families"))+ggtitle("(c)") + theme(plot.title = element_text(size = 28, face = "bold"))
+   "Megachilidae"),values=c("blueviolet", "orange", "limegreen","#E7298A", "cyan4"),
+    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae"))+ggtitle("(c)") + theme(plot.title = element_text(size = 28, face = "bold"))
 

### 2021-05-18 Supplementary_Material/Supplementary_Material.Rmd
Preparing supp material and now additional table with anova output with qualitative assoc.

@@
 - \usepackage{soul}
+- \floatplacement{figure}{H}
+
+fontsize: 12pt
 
@@
 
-#Tables
+# Supporting information:
+
+__Authors:__ Jose B. Lanuza, Romina Rader, Jamie Stavert, Liam K. Kendall, Manu E. Saunders & Ignasi Bartomeus
+
+_The following Supporting Information is available for this article_:
+
+__Table S1.__ List of the 28 plant-pollinator studies used to build the plant trait database.
+
+__Table S2.__ Loadings of the first three principal components of the phylogenetic informed principal component analysis with all species.
+
+__Table S3.__ Loadings of the first three principal components of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.
+
+__Table S4.__ Phylogenetic signal of the different quantitative traits.
+
+__Figure S1__ Percentage of present and missing values of the different variables.
+
+__Figure S2__ Trait relationship of PC1 and PC3 with the phylogenetic informed principal component analysis with the full set of species.
+
+__Figure S3__ Fitted posterior estimates of the number of visits made by the main functional groups of bees on the main axes of trait variation.
+
+__Figure S4__ Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation.
+
+__Figure S5__ Phylogenetic informed principal component analysis for the species that did not have missing values.
+
+__Figure S6__ Phylogenetic informed principal component analysis for the imputed dataset of the subset of species with quantitative information of nectar and pollen.
+
+__Figure S7__ Statistical comparison of the different categories of the categorical traits on the main two axes of trait variation (pPCA with the full set of species).
 
@@
 Each study is shown with the first author that conducted the study, number of networks or metawebs that contains, type of information that contains (weighted or unweighted),  the structure (web or metaweb), year of publication and digital object identifier or permanent link for each study.") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "left")
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, repeat_header_method="replace" ,full_width=F,position = "left")
 
@@
 \end{landscape}
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
+
+library(dplyr)
+library(kableExtra)
+
+setwd("~/R_Projects/Reproductive Traits")
+
+PC <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+dat <- PC$L[,c(1:3)]
+
+#Create a row to add total percentage of variance explained by PC
+
+percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+percen <- percentage[1:3]
+
+dat <- rbind(dat, percen)
+
+rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Explained variation")
+
+dat <- as.data.frame(dat)
+
+dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
+
+ kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S2.} Loadings and explained variance of the first three principal components from the phylogenetically informed principal component analysis for the full set of species (N = 1,506).") %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
+
+```
+
+\pagebreak
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
+
+library(dplyr)
+library(kableExtra)
+
+setwd("~/R_Projects/Reproductive Traits")
+
+PC <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
+
+dat <- PC$L[,c(1:3)]
+
+#Create a row to add total percentage of variance explained by PC
+
+percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+percen <- percentage[1:3]
+
+dat <- rbind(dat, percen)
+
+rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Microlitres of Nectar per flower" , "Pollen per flower","Explained variation")
+
+dat <- as.data.frame(dat)
+
+dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
+
+kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S3.} Loadings and explained variance of the first three principal components from the phylogenetically informed principal component analysis for the subset of sepcies with quantitative information of nectar and pollen.") %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
+
+```
+
+\pagebreak
 
@@
 #LABELS
-label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Pollen grains per flower", "Nectar ($\\mu$l) per flower", "Nectar (mg) per flower", "Nectar concentration ($\\%$)")
+label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Nectar ($\\mu$l) per flower", "Nectar (mg) per flower", "Nectar concentration ($\\%$)","Pollen grains per flower")
 #LAMBDA
-lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, pollen$lambda, nectar_ul$lambda, nectar_mg$lambda, nectar_con$lambda)
+lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, nectar_ul$lambda, nectar_mg$lambda, nectar_con$lambda, pollen$lambda)
 #P-VALUE
-p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P, pollen$P,nectar_ul$P,
-            nectar_mg$P,  nectar_con$P)
+p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P,nectar_ul$P,
+            nectar_mg$P,  nectar_con$P, pollen$P)
 
@@
 
-kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE) %>%
+kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,caption = "\\textbf{Table S4.} Phylogenetic signal for all quantitative traits.
+Phylogenetic signal of nectar and pollen traits was calculated for the imputed dataset of the subset of species with quantitative information of nectar and pollen.") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
@@
 \pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
- kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE) %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Microlitres of Nectar per flower" , "Pollen per flower","Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
-kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE) %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-
-#Figures
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="**Fig. S2**"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="**Fig.
+S2** Phylogenetically informed principal component analysis showing the trait relationship with principal components one and three (PC1 and PC3) for the full set of species (N = 1,506)."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="**Fig. S3**"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="**Fig.
+S3** Fitted posterior estimates of the number of visits made by the different main visiting families of bees (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) in relation to the main axes of trait variation (PC1, PC2 and PC3).
+We omitted in the plotting points over percentile 95% due to extreme outliers."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28,  fig.cap="**Fig. S4**"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28,  fig.cap="**Fig.
+S4** Fitted posterior estimates of the number of visits made by the functional group of Hymenoptera-Anthophila (bees) including (superior panel) and excluding (lower panel) *Apis mellifera* in relation to the main axes of trait variation (PC, PC2 and PC3)."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="**Fig. S5**"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="**Fig.
+S5** Phylogenetic informed principal component analysis for the species that did not have missing values (non-imputed dataset; N = 723)."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="**Fig. S6**"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="**Fig.
+S6** First two main principal components from the phylogenetic informed principal component analysis for the imputed dataset of the subset of species with quantitative information of nectar and pollen (N = 467)."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=14}
+\pagenumbering{gobble}
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=14, fig.cap="**Fig.
+S7** Statistical comparison of the different categories of the categorical traits on the main two axes of trait variation (pPCA with the full set of species).
+Categories that differ significantly are denoted with a different letter."}
 

### 2021-05-18 Tables/Phylo_PPCA_Loadings_Nectar_and_Pollen.R

@@ -1,0 +1,25 @@
+
+library(dplyr)
+library(kableExtra)
+
+PC <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
+
+
+dat <- PC$L[,c(1:3)]
+
+#Create a row to add total percentage of variance explained by PC
+
+percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+percen <- percentage[1:3]
+
+dat <- rbind(dat, percen)
+
+rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Microlitres of Nectar per flower" , "Pollen per flower","Explained variation")
+
+dat <- as.data.frame(dat)
+
+dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
+
+kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE) %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center") 

### 2021-05-18 Supplementary_Material/Supplementary_Material.Rmd
supp material
still needs more work

@@
 __Table S4.__ Phylogenetic signal of the different quantitative traits.
+
+__Table S5.__ Statistical association of the different categorical variables to the principal components one and three from the pPPCA with the full set of species.
 
@@
 Phylogenetic signal of nectar and pollen traits was calculated for the imputed dataset of the subset of species with quantitative information of nectar and pollen.") %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
+
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
+
+library(dplyr)
+library(kableExtra)
+
+setwd("~/R_Projects/Reproductive Traits")
+
+d <- readRDS("Data/RData/table_categorical_tukey_test.rds")
+
+#Again im getting the same error on this rmd so I run it on another one, save the dataframe and plot it here
+
+#Plot table
+#Add latex format in markdown
+
+kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Table S5.} Statistical association of the different categorical variables to the first two principal components from the pPPCA with the full set of species.
+For each categorical trait and principal component, sum of squares, F-value and P-value are provided.") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")

### 2021-05-19 Supplementary_Material/Supplementary_Material.Rmd
.

@@
 ---
+
 \captionsetup[figure]{labelformat=empty}
@@
 
-__Table S4.__ Phylogenetic signal of the different quantitative traits.
-
-__Table S5.__ Statistical association of the different categorical variables to the principal components one and three from the pPPCA with the full set of species.
+__Table S4.__ Statistical association of the different categorical variables to the principal components one and three from the pPPCA with the full set of species.
+
+__Table S5.__ Phylogenetic signal of the different quantitative traits.
 
@@
 
-__Figure S2__ Trait relationship of PC1 and PC3 with the phylogenetic informed principal component analysis with the full set of species.
-
-__Figure S3__ Fitted posterior estimates of the number of visits made by the main functional groups of bees on the main axes of trait variation.
-
-__Figure S4__ Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation.
-
-__Figure S5__ Phylogenetic informed principal component analysis for the species that did not have missing values.
-
-__Figure S6__ Phylogenetic informed principal component analysis for the imputed dataset of the subset of species with quantitative information of nectar and pollen.
+__Figure S2__ Phylogenetic informed principal component analysis for the species that did not have missing values.
+
+__Figure S3__ Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation.
+
+__Figure S4__ Trait relationship of PC1 and PC3 with the phylogenetic informed principal component analysis with the full set of species.
+
+__Figure S5__ Phylogenetic informed principal component analysis for the imputed dataset of the subset of species with quantitative information of nectar and pollen.
+
+__Figure S6__ Fitted posterior estimates of the number of visits made by the main functional groups of bees on the main axes of trait variation.
 
@@
 \pagebreak
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
+
+library(dplyr)
+library(kableExtra)
+
+setwd("~/R_Projects/Reproductive Traits")
+
+d <- readRDS("Data/RData/table_categorical_tukey_test.rds")
+
+#Again im getting the same error on this rmd so I run it on another one, save the dataframe and plot it here
+
+#Plot table
+#Add latex format in markdown
+
+kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Table S4.} Statistical association of the different categorical variables to the first two principal components from the pPPCA with the full set of species.
+For each categorical trait and principal component, sum of squares, F-value and P-value are provided.") %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
+
+```
+
+\newpage
 
@@
 
-kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,caption = "\\textbf{Table S4.} Phylogenetic signal for all quantitative traits.
+kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,caption = "\\textbf{Table S5.} Phylogenetic signal for all quantitative traits.
 Phylogenetic signal of nectar and pollen traits was calculated for the imputed dataset of the subset of species with quantitative information of nectar and pollen.") %>%
@@
 \newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-d <- readRDS("Data/RData/table_categorical_tukey_test.rds")
-
-#Again im getting the same error on this rmd so I run it on another one, save the dataframe and plot it here
-
-#Plot table
-#Add latex format in markdown
-
-kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Table S5.} Statistical association of the different categorical variables to the first two principal components from the pPPCA with the full set of species.
-For each categorical trait and principal component, sum of squares, F-value and P-value are provided.") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
 
@@
 
+\newpage
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="**Fig.
-S2** Phylogenetically informed principal component analysis showing the trait relationship with principal components one and three (PC1 and PC3) for the full set of species (N = 1,506)."}
+S2** Phylogenetic informed principal component analysis for the species that did not have missing values (non-imputed dataset; N = 723)."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-library(magick)
-
-#Images were made by Paula Martin
-#Check her work on https://paulamartinart.com/
-
-tree <- image_read("Images/PPCA_Plot/Tree.png")
-tree_1 <- as.raster(tree)
-
-style_l <- image_read("Images/PPCA_Plot/Style_Long.png")
-style_l_1 <- as.raster(style_l)
-
-style_s <- image_read("Images/PPCA_Plot/Style_Short.png")
-style_s_1 <- as.raster(style_s)
-
-ovule_h <- image_read("Images/PPCA_Plot/Ovule_High.png")
-ovule_h_1 <- as.raster(ovule_h)
-
-ovule_l <- image_read("Images/PPCA_Plot/Ovule_Low.png")
-ovule_l_1 <- as.raster(ovule_l)
-
-selfing_n <- image_read("Images/PPCA_Plot/Selfing_None.png")
-selfing_n_1 <- as.raster(selfing_n)
-
-selfing_h <- image_read("Images/PPCA_Plot/selfing.png")
-selfing_h_1 <- as.raster(selfing_h)
-
-single_flower <- image_read("Images/PPCA_Plot/Single_Flower.png")
-single_flower_1 <- as.raster(single_flower)
-
-many_flowers <- image_read("Images/PPCA_Plot/Inflorescencia.png")
-many_flowers_1 <- as.raster(many_flowers)
-#many_flowers_1 <- image_rotate(many_flowers, 45)
-
-large_flower <- image_read("Images/PPCA_Plot/flower_big.png")
-large_flower_1 <- as.raster(large_flower)
-
-flower_small <- image_read("Images/PPCA_Plot/flower_short.png")
-flower_small_1 <- as.raster(flower_small)
-
-herb <- image_read("Images/PPCA_Plot/herb.png")
-herb_1 <- as.raster(herb)
-
 #############################################################################################################################################################
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="**Fig.
-S3** Fitted posterior estimates of the number of visits made by the different main visiting families of bees (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) in relation to the main axes of trait variation (PC1, PC2 and PC3).
-We omitted in the plotting points over percentile 95% due to extreme outliers."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28,  fig.cap="**Fig.
+S3** Fitted posterior estimates of the number of visits made by the functional group of Hymenoptera-Anthophila (bees) including (superior panel) and excluding (lower panel) *Apis mellifera* in relation to the main axes of trait variation (PC, PC2 and PC3)."}
 
@@
 library(patchwork)
-library(brms)
 library(ggplot2)
-library(rstan)
 library(tidyr)
-rstan_options(auto_write = TRUE)
 #Load theme for publication
@@
 
-plot <- readRDS("Plot_bee_families.rds")
-
-plot
+plot_apis <- readRDS("Plot_apis.rds")
+
+plot_apis
 
@@
 
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28,  fig.cap="**Fig.
-S4** Fitted posterior estimates of the number of visits made by the functional group of Hymenoptera-Anthophila (bees) including (superior panel) and excluding (lower panel) *Apis mellifera* in relation to the main axes of trait variation (PC, PC2 and PC3)."}
-
-library(Rcpp)
-library(patchwork)
-library(brms)
-library(ggplot2)
-library(rstan)
-library(tidyr)
-rstan_options(auto_write = TRUE)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot_apis <- readRDS("Plot_apis.rds")
-
-plot_apis
-
-```
-
-\elandscape
-
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="**Fig.
-S5** Phylogenetic informed principal component analysis for the species that did not have missing values (non-imputed dataset; N = 723)."}
+S4** Phylogenetically informed principal component analysis showing the trait relationship with principal components one and three (PC1 and PC3) for the full set of species (N = 1,506)."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
+\newpage
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="**Fig.
-S6** First two main principal components from the phylogenetic informed principal component analysis for the imputed dataset of the subset of species with quantitative information of nectar and pollen (N = 467)."}
+S5** First two main principal components from the phylogenetic informed principal component analysis for the imputed dataset of the subset of species with quantitative information of nectar and pollen (N = 467)."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
+\blandscape
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="**Fig.
+S6** Fitted posterior estimates of the number of visits made by the different main visiting families of bees (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) in relation to the main axes of trait variation (PC1, PC2 and PC3).
+We omitted in the plotting points over percentile 95% due to extreme outliers."}
+
+library(Rcpp)
+library(patchwork)
+library(ggplot2)
+library(tidyr)
+#Load theme for publication
+
+theme_ms <- function(base_size=14, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(2.2)),
+           axis.text=element_text(size = rel(2), color = "black"),
+           legend.title=element_text(face="bold",size=rel(2)),
+           legend.text=element_text(size=rel(1.4)),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(1.8, 'lines'),
+           panel.border=element_rect(color="black",size=2.4),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank()
+     ))
+}
+
+setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
+
+#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
+
+plot <- readRDS("Plot_bee_families.rds")
+
+plot
+
+```
+
+\elandscape
+
+\AtBeginShipout{\ifnum\value{page}=1\AtBeginShipoutDiscard\fi}
+
 \pagenumbering{gobble}
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=14, fig.cap="**Fig.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="**Fig.
 S7** Statistical comparison of the different categories of the categorical traits on the main two axes of trait variation (pPCA with the full set of species).

### 2021-05-19 Untitled/Manuscript.Rmd
.

---
title: "Plant reproductive strategies structure plant-pollinator networks"
author:
  - Jose B. Lanuza^1,2^*
  - Romina Rader^1^
  - Jamie Stavert^3^
  - Liam K. Kendall^4^
  - Manu E. Saunders^1^
  - Ignasi Bartomeus^2^

# may use lua filters for affiliations etc: see https://stackoverflow.com/a/52919256

# date: '`r Sys.Date()`'

output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_width: 7
    fig_height: 7
    df_print: kable
    keep_tex: yes
    number_sections: no
    toc: no
    includes:
      in_header: header.tex

documentclass: article
# classoption: twocolumn, landscape, etc
papersize: a4
pagestyle: plain  # plain, empty, headings
geometry: margin=1in
linestretch: 2
fontfamily: mathpazo
fontsize: 11pt

bibliography: 
  - references.bib
  - knitcitations.bib
# zotero: "My shared Zotero group"
csl: ecology.csl
# csl: https://www.zotero.org/styles/ecology

link-citations: yes
linkcolor: RoyalBlue
urlcolor: RoyalBlue
links-as-notes: false

header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

<!--# Insert author affiliations below -->

\small

^1^ School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia

^2^ Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain

^3^ Department of Conservation | Te Papa Atawhai, Auckland, New Zealand

^4^ Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden

`*` Corresponding author: barragansljose@gmail.com

\normalsize

<!--# Write Abstract and Keywords below -->

\vspace{1cm}
\hrule

#Abstract

Increasing availability of large datasets have improved our understanding of organismal life history and pollination biology. However, most attention has focused on vegetative traits when delimiting plant life strategies and overlooked key floral and reproductive traits. In addition, plant-pollinator research rarely considers the reproductive biology of the species and has overemphasized the study of highly specialized interactions. Greater knowledge of the plant reproductive trade-offs between these traits can shed light on the macroecological patterns and help our understanding of life strategies.

Here, we compiled 20 reproductive traits for 1,506 plant species from 28 plant-pollinator network studies and 18 different countries that constitute a total of 64 unique networks and 8 meta-webs. We explore the different trade-offs of floral, reproductive, and vegetative traits of the main quantitative traits in the trait space. Then, we evaluate whether the frequency of pollinator visits within networks change across the primary axes of trait variation and pollinator functional groups. Finally, we investigate if the functional role of the plant species (interaction frequency, normalized degree and specialization) in the network is associated with the primary axes of trait variation and the different plant traits.

We found that 51.8% of the trait variation was explained by two independent axes that determined plant form and function. The first axis showed the flower number versus flower size compromise (PC1, 26.72%) where species were divided in two opposed strategies with high investment in flower number and plant height on one extreme or high investment in flower size, style length and larger number of ovules on the other. The second axis showed the pollinator dependence trade-off (PC2, 25.08%) between species with high pollinator dependence with greater plant height and higher investment in floral traits on one end and low pollinator dependence with smaller height and lower investment in floral traits on the other. An additional principal component analysis with the subset of species with quantitative data of pollen and nectar showed that nectar quantity was positively associated with flower size, style length and ovule number (PC1, 24.70%) and pollen quantity was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 20.59%). The main axes of trait variation with the full set of species did not explain the overall visitation patterns but showed marked trends for the different functional groups. For instance, all pollinator functional groups had higher frequency of visits on plant species with high pollinator dependence (PC2); and bees (Anthophila), the most abundant functional group, had higher frequency of visits on species with high number of flowers and tall plant height (PC1); and, on species with longer styles and higher levels of autonomous selfing (PC3). Overall, plant species with small size, low nectar concentration and short styles showed lower visitation rates than plant species with the opposed traits; species with small amounts of floral rewards (pollen and nectar), low number of flowers and small flowers had in general lower number of visiting species (normalized degree); and species under 1.3 m, with high rewards of pollen and nectar showed the highest levels of specialization. This work highlights the need to consider essential plant reproductive and floral traits to improve understanding of plant life strategies and plant-pollinator interactions at large scales.

\vspace{3mm}
\hrule
\vspace{5mm}

*Keywords*: plant-pollinator networks | floral traits | life history strategy | functional traits

\bleft
\newpage

```{r setup, include=FALSE, cache=FALSE, message = FALSE}

library("knitr")

### Chunk options: see http://yihui.name/knitr/options/ ###
## Text results
opts_chunk$set(echo = FALSE, warning = TRUE, message = TRUE)

## Code decoration
opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)

## Cache
# opts_chunk$set(cache = 2, cache.path = "output/cache/")

## Plots
opts_chunk$set(fig.path = "output/figures/")

```

```{r knitcitations, cache = FALSE}
library(knitcitations)
cleanbib()   
cite_options(citation_format = "pandoc")
```

<!--# Start writing your paper below -->

# INTRODUCTION

Among flowering plants there is an astonishing diversity of floral structures and plant reproductive strategies [@barrett2002; @schiestl2013]. Subsequently, pollination biologists have long studied their relevance on plant-pollinator interactions. However, despite recent efforts exploring reproductive (e.g., mating and compatibility system) and floral traits (e.g., flower size or nectar provision) with large sets of species [@carvalheiro2014; @baude2016; @munoz2016; @moeller2017; @grossenbacher2017], most studies focus on the individual, community level or specific taxa and macroecological patterns remain poorly investigated. For instance, studies depicting species’ life history strategies generally focus on vegetative traits and rarely consider reproductive traits on the main axes of trait variation [@diaz2016; @salguero2016]. In addition, there is not a unified framework that explores the compromises of floral traits and their relevance on plant life strategies [@roddy2021]. Similarly, there is growing interest in understanding what determines plant-pollinator network structure. Approaches with traits range from the description of pollination syndromes [e.g., @dellinger2020], to more specific trait-matching analysis [@bartomeus2016], but again the reproductive biology of the species has received little attention [but see @tur2013 and @devaux2014] and floral traits have been overlooked beyond highly specialised plant-pollinator interactions [@dellinger2020; @roddy2021].

With increased availability of large trait databases, plant ecological strategies have begun to be examined more frequently [e.g., TRY, @kattge2011 and COMPADRE; @salguero2015], highlighting global patterns and constraints of plant form and function [@diaz2016; @salguero2016; @carmona2021]. However, these resources and their research have mainly focused on vegetative traits such as the leaf [@wright2004] or wood [@chave2009] trade-offs and neglected reproductive and floral traits that also can influence the spectrum of trait variation. For instance, short lived and perennial species tend to have high and low levels of outcrossing respectively [@barrett2003; @moeller2017] and outcrossing levels have been shown to be positively correlated with flower size [@goodwillie2010]. In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays cannot be understood without considering pollinators that are thought to be responsible for approximately 87.5% of the pollination of flowering plants [@ollerton2011]. Hence, exploring plant life strategies with reproductive and floral trade-offs, in conjunction with their known pollinators seems necessary for a correct understanding of the plant economics.

Several key studies have progressed knowledge of the link between traits and network properties [@lazaro2008; @bartomeus2013; @carvalheiro2014; @klumpers2019]. Functional traits can determine whether species interact, and thus define the species network role (e.g., specialist vs generalist). For instance, species with high investment in floral display tend to have higher visitation rates [@stang2006; @novella-fernandez2019] and greater specialization is generally associated with occupation of the trait space extremes [@junker2013; @coux2016]. In addition, the structure of the pollination network highly depends on the degree of trait-matching between plants and pollinators [@stang2009; @ibanez2012; @peralta2020]. However, little is known about the consequences of reproductive traits and floral rewards on plant species roles. In addition, although some attempts have been made to evaluate trait relationships in plant-pollinator interactions at a global scale [@carvalheiro2014; @rech2016], macroecological patterns have been little explored.

Here, we explore the major axes of plant reproductive trait variation. We investigate how these traits influence the structure of plant-pollinator networks by compiling a unique dataset comprising 20 plant functional traits for 1,506 species from 64 unique networks and 8 metawebs. First, we evaluate the major axes of reproductive trait variation and tradeoffs that determine plant form and function. Second, we investigate how plant species’ position in trait-space influences interaction strength with different  pollinator functional groups. Finally, we assess the relevance of the main axes of trait variation and traits in understanding the plant species role within the networks with complementary species level metrics (i.e., interaction strength, normalized degree and specialization).

# METHODS

##Plant-pollinator network studies

We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks. All these studies censored plant-pollinator interactions in natural systems and were selected in order to have a wide representation of geographical areas of the world. Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted) allowing us to build a database of plants that are likely to be animal pollinated. Some of these networks have been already used in past studies of plant-pollinator networks [@olesen2007; @fortuna2010; @carvalheiro2014] and are available on the online networks archives The Web of Life [@fortuna2014] and Mangal [@poisot2016]. In total, our network dataset (Table S1) constituted 60 weighted (interaction frequency) and 4 binary networks, each sampled at a unique location and year, as well as 8 meta-webs where sampled interactions were pooled across several locations and multiple years.

##Taxonomy of plants and pollinators

All plant species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) (plants) and ITIS (https://www.itis.gov/) (pollinators) using the R package taxize [version 0.9.99, @chamberlain2020]. We filled the ‘not found’ searches manually using http://www.theplantlist.org/ and http://www.mobot.org/ for plants and http://www.catalogueoflife.org/ for floral visitors.

##Functional traits

We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1). The selected traits were quantitative (12) and categorical (8) and belonged to three different trait types: vegetative, floral and reproductive. For each species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images) from a total of 30,120 cells (20 columns x 1,506 spp) we were able to fill 23,969 cells (79.6% of the dataset, see Figure S1 for missing values information per variable).

\setstretch{1.25}

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12}
setwd("~/R_Projects/Reproductive Traits")

library(kableExtra)

library(dplyr)
library(readxl) #read excel file (trait data)
library(dplyr) #data manipulation
library(visdat) #VISUALIZE MISSING DATA
library(naniar)
library(tidyverse)
########################################################################################################################################################
#1) READ TRAIT DATA
########################################################################################################################################################
#load data
trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
########################################################################################################################################################
#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
########################################################################################################################################################
#####
#A) CLEAN DATA
#####
#select just filled rows
trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data

#filter data, select species with flower level info and capitulum
trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]

#Select columns to work with
t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
                        "Flowers_per_plant","Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]

########################################################################################################################################################
#####
#B) RENAME LEVELS FOR IMPUTATION
#####
#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
t$Breeding_system <- as.character(t$Breeding_system)
t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
#Change to capital letters| There are already levels with lower case
t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
t$Breeding_system <- as.factor(t$Breeding_system)

#Now 3 levels
#Flower_morphology
t$Flower_morphology <- as.character(t$Flower_morphology)
t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
t$Flower_morphology <- as.factor(t$Flower_morphology)

#Life span
t$lifespan <- as.character(t$lifespan )
t$lifespan[t$lifespan=="annual"] <- "short_lived"
t$lifespan[t$lifespan=="biennial"] <- "short_lived"
t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
t$lifespan[t$lifespan=="perennial"] <- "Perennial"
t$lifespan <- as.factor(t$lifespan )

########################################################################################################################################################
#3) EXPLORE PATTERNS OF MISSING DATA
########################################################################################################################################################

#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)

#t$Nectar_ul adding it here just to see how many cells 
#Now we just select presence/absence of nectar
#select columns of interest
t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Floral_unit_width",
         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]

########################################################################################################################################################
#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
########################################################################################################################################################
#Convert to factor 
cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used

cols.num <- c("Family_all","Genus_all","Species_all")
t[cols.num] <- sapply(t[cols.num],as.character)
t$Species_all <- gsub("Species_all_", "", t$Species_all)

t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species

#remove species that are not until species level
#ALL THE SPECIES WITH SP. ARE DELETD
t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
#CHECK LEVELS

#Make these NA's as NA
t$Species_all[t$Species_all=="NA"] <- NA
t$Family_all[t$Family_all=="NA"] <- NA
t$Genus_all[t$Genus_all=="NA"] <- NA
#remove NA's
t <- t[!is.na(t$Family_all),]
t <- t[!is.na(t$Species_all),]
t <- t[!is.na(t$Genus_all),]

missing.values <- t %>%
  gather(key = "key", value = "val") %>%
  mutate(isna = is.na(val)) %>%
  group_by(key) %>%
  mutate(total = n()) %>%
  group_by(key, total, isna) %>%
  summarise(num.isna = n()) %>%
  mutate(pct = num.isna / total * 100)

n_of_records <- subset(missing.values, isna=="FALSE")
Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")

Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Autonomous selfing", "Compatibility system", "Breeding system", " ", " ", " ", " ")

T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
           "Presence \n Absence", "None \n Low \n Medium \n High", "Self-incomp. \n Partially self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " "),align = c("l"))

Type <- c("V", "F", "F", "F", "F", "F", "F","F","F","F","F","R")

Type_1 <- c("V", "V", "F", "F", "F", "R", "R", "R","","","","")

dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)

Number_of_records_quantitative <- c(n_of_records$num.isna[n_of_records$key=="Plant_height_mean_m"], n_of_records$num.isna[n_of_records$key=="Corolla_diameter_mean"],
  n_of_records$num.isna[n_of_records$key=="Corolla_length_mean"], n_of_records$num.isna[n_of_records$key=="Floral_unit_width"],
  n_of_records$num.isna[n_of_records$key=="Style_length"], n_of_records$num.isna[n_of_records$key=="Ovule_number"],
  n_of_records$num.isna[n_of_records$key=="Flowers_per_plant"], n_of_records$num.isna[n_of_records$key=="Nectar_ul"],
  n_of_records$num.isna[n_of_records$key=="Nectar_mg"], n_of_records$num.isna[n_of_records$key=="Nectar_concentration"], n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
  n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level_fruit_set"])

Number_of_records_categorical <- c(n_of_records$num.isna[n_of_records$key=="lifespan"], n_of_records$num.isna[n_of_records$key=="life_form"],
                                   n_of_records$num.isna[n_of_records$key=="Flower_morphology"], n_of_records$num.isna[n_of_records$key=="Flower_symmetry"],
                                   n_of_records$num.isna[n_of_records$key=="Nectar_presence_absence"], n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level"],
                                   n_of_records$num.isna[n_of_records$key=="Compatibility_system"], n_of_records$num.isna[n_of_records$key=="Breeding_system"],
                                   rep("",4))

dat <- data.frame(Type, Trait,Number_of_records_quantitative,Type_1, Trait1, T.cat,Number_of_records_categorical)

colnames(dat) <- c("Type","Traits", "Records","Type", "Traits", "Categories", "Records")

kbl(dat, booktabs = T,  linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"), caption= "List of the 20 traits compiled in this study divided in quantitative and categorical traits. The different types of trait (vegetative ‘V’, floral ‘F’ and reproductive ‘R’), total records found for the 1,506 species and categories of the qualitative traits are also provided. ") %>%
kable_styling(full_width = T,font_size = 10) %>%
add_header_above(c("Quantitative traits" = 3,"Categorical traits" = 4),bold=T)  %>%
    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)

```

\setstretch{2}

##Phylogenetic Distance

We calculated the phylogenetic distance between different plant species using the function get_tree from the package rtrees (downloaded from github, https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018] developed by @jin2019.

##Data Imputation

Missing values were imputed with the function missForest [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables. We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of missForest [@penone2014]. To extract the eigenvectors, we used the function PVRdecomp from the package PVR [@santos2018] based on the conceptual framework of @diniz-filho2012. Although the variable of autonomous selfing had a high percentage of missing values (68%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical. The categories of ‘none’, ‘low’, ‘medium’ and ‘high’ were converted to representative percentages of each category 0%, 13%, 50.8% and 80% respectively. This reduced the percentage of missing values for this column from 68% to 35% and allowed the imputation of this variable. However, we were unable to impute nectar and pollen quantity due to the high percentage of missing values (Figure S1). The imputed dataset had 9.7% of missing values with a total of 8 categorical and 8 numerical variables. Finally, we conducted an additional imputation for the subset of species with quantitative information of nectar and pollen; all variables had lower than 30% of missing values (N = 636) and the total proportion of missing values in this dataset considering all variables was 13%.

##Plant strategies

We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA). We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width (Pearson’s correlation = 0.72, p < 0.01 and Pearson’s correlation = 0.36, p < 0.01 respectively), and thus we avoided overemphasizing flower size on the spectrum of trait variation. In addition, we explored the location of different qualitative traits in the trait space. Prior to the analyses, we excluded outliers and standardized the data. Due to the high sensitivity of dimensionality reduction to outliers, we excluded values in the 2.5th-97.5th percentile range [@legendre2012]. Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range. We performed the pPCA using the function phyl.pca from the package phytools [version number 0.7-70, @revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because our variables are on the same scale after the log and z-transformation [@abdi2010]. Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Figure S2). We found little difference between the variance explained with the imputed dataset (51.08%) and the dataset without missing values (56.26%). In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non imputed dataset. Finally, we explored with the imputed dataset with quantitative information of pollen and nectar the compromises in the trait space of these two floral rewards with the other quantitative traits. For this, we considered solely one variable of nectar quantity (microlites of nectar per flower) in order to avoid overemphasizing nectar on the spectrum of trait variation.

##Phylogenetic signal of traits

We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1506) with the package phytools version 0.7-70 [@revell2012] and we used Pagel’s lambda ($\lambda$) as a measurement of the phylogenetic signal. For pollen and nectar traits, phylogenetic signal was calculated on the imputed dataset that included these traits (N = 636).

##Networks analysis

Our analyses were conducted on the subset of 60 weighted networks with interaction frequency sampled in a unique flowering season and site. Although floral visitors are not always pollinators and the frequency of visits does not consider each pollinator species efficiency [@ballantyne2015], interaction frequency provides valuable information of the impact of pollinators (Vázquez et al., 2005; Vázquez et al., 2012). Although not all networks were sampled using the same method, our aim was not to compare patterns across networks but within each network in order to obtain a general picture of associations between traits and the main axes of trait variation and plant species functional roles.

*Functional groups visitation patterns*

We explored the relevance of pollinator functional groups and the main axes of trait variation (pPCA with imputed dataset) on pollinator visitation per plant species. For this, we divided floral visitors into six main groups that differ in life form and behaviour: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Diptera-Syrphids, (iv) Diptera-Non-Syrphids, (v) Lepidoptera and (vi) Coleoptera. In addition, because Hymenoptera was the most represented group with 2,256 records counted and had the highest frequency of visits of all groups, we also explored visitation patterns of the most represented families of Hymenoptera on the trait space (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae). Apis mellifera was the species with the largest proportion of records (7.55% from the total) which is is consistent with the results of @hung2018 that showed that A. mellifera was the most frequent visiting species on a similar dataset of 80 interaction plant-pollinator networks on natural systems. Hence, to control for the relevance of Apis mellifera on the observed visitation patterns of bees, we conducted an analogous analysis excluding A. mellifera. We found that A. mellifera, was driving, in part, some of the observed trends on PC1 (Figure S3). However, we did not find major changes on PC2 and PC3.

*Plant species functional roles*

We investigated if the main axes of trait variation and traits explained plant species functional roles. We considered all uncorrelated traits apart from the principal components because this allowed us to consider quantitative and categorical traits. For this, we also used a modelling approach and conducted decision trees which help to interpret visually how the different traits determine species functional roles. We selected simple and complementary plant species level metrics with a relatively straightforward ecological interpretation relevant to our research goals: (i) sum of visits per plant species; (ii) normalized degree calculated as the number of links per plant species divided by the possible number of partners which helps comparison across networks; and (iii) specialization (d’) [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization). Normalized degree and specialization were calculated with the specieslevel function from the R package bipartite  [version 2.15, @dormann2008].

## Analyses

First, we implemented Bayesian generalized linear mixed models using the R package brms [version 2.14.6, @burkner2017]. We modelled the frequency of visits as a function of the main axes of trait variation and floral visitors functional groups (Visits~PC1xFG+PC2xFG+PC3xFG). Because we were interested in possible differences among main visitor guilds to plants with different strategies, we included the interaction between the main axes of trait variation and the distinct floral visitor functional groups. We added a nested random effect with networks nested on the study system to capture the network variability per study and within networks. We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function. Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary history of the species and therefore lack of independence across them.

Second, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation in three different models for each metric (plant species level metric~PC1+PC2+PC3). In addition we also explored how all uncorrelated traits (13) explained these metrics in three other models (plant species level metric ~ plant height + lifespan + life form + flower shape + flower symmetry + flower width + style length + ovule number + flowers per plant + nectar provision + autonomous selfing + compatibility system + breeding system). For each response variable (metric), we used different distribution families: zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization. Moreover, we included a nested random effect with networks nested on the study system and a phylogenetic random effect for species (as detailed above) in each model.

All analyses were conducted in R Version 4.0.3. In addition, all models were run for 3,000 iterations with 1000 warm up iterations. We set delta () to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function pp_check using the bayesplot package (version 1.7.2, Gabry et al., 2019).

[ADD REGRESSION TREE TO METHODS]
We conducted regression trees in order to explore the relevance of traits on the species plant functional role. We repeated the procedure as the modelling analysis and we ran a decision tree for each plant level species metric (interaction frequency, normalized degree and specialization). We used the full datase

rpart 4.1-15 (Therneau et al., 2019)
rpart.plot 3.0.9 (Milborrow 2018)

# RESULTS

## Plant strategies
The phylogenetically informed principal component analysis (pPCA) captured with the first two and three axes 51.8% and 70.97% of the trait variation respectively (Figure 1 and Figure S4) and had a phylogenetic correlation ($\lambda$) of 0.76. The first principal component (PC1) represented 26.72% of the trait variation and showed the flower number versus flower size compromise. Thus, as flower number and plant height increase, flower size, style length and ovule number decrease; and, as flower size, style length and ovule number increase, flower number and plant height decrease. The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Table S2) but style length also contributed moderately on PC1 (loading = -0.33). The second principal component (PC2) represented 25.05% of the trait variation and showed the trade-off between low and high pollinator dependence and we refer to this axis as the pollinator dependence trade-off. The main driver of trait variation of PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made a moderate contribution to PC2 (loadings from 0.27 to 0.4; Table S2). We found that high pollinator dependence was associated with larger and higher number of flowers, greater plant height and longer styles. In contrast, species with high levels of autonomous selfing had a general lower investment in flower number and size, plant height and style length. Further, PC3 also explained a considerable amount of variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51). The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S2). In addition,  the pPCA with the species subset that had nectar and pollen quantity showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 24.70%); and pollen quantity was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 20.59%; Figure S5). This pPCA also showed similar explained variance with two components (50.06%) and similar associations of traits despite some variability in the loadings (Table S3).

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,fig.cap= "Life history strategies for 1,236 plant species from 29 plant-pollinator networks studies across the first two axes of variation from a phylogenetically informed principal component analysis (pPCA). The solid arrows indicate the direction and weights of the six quantitative traits (flower number, plant height, style length, flower size, ovule number and autonomous selfing level) and the labelled icons at their end represent the extreme form of the trait continuum. The dashed lines indicate the opposed direction of trait variation and the non-labelled icons at their end illustrate the other extreme of the continuum."}
setwd("~/R_Projects/Reproductive Traits")

#Load libraries
#LOAD LIBRARIES
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(cowplot)
# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.2)),
            axis.text=element_text(size = rel(1.75), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(1.2, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
             panel.grid.major= element_blank()
      ))
}

#Load data
dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")

PC <- phyl_pca_forest
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

library(magick)

#Images were made by Paula Martin
#Check her work on https://paulamartinart.com/

tree <- image_read("Images/PPCA_Plot/Tree.png")
tree_1 <- as.raster(tree)

style_l <- image_read("Images/PPCA_Plot/Style_Long.png")
style_l_1 <- as.raster(style_l)

style_s <- image_read("Images/PPCA_Plot/Style_Short.png")
style_s_1 <- as.raster(style_s)

ovule_h <- image_read("Images/PPCA_Plot/Ovule_High.png")
ovule_h_1 <- as.raster(ovule_h)

ovule_l <- image_read("Images/PPCA_Plot/Ovule_Low.png")
ovule_l_1 <- as.raster(ovule_l)

selfing_n <- image_read("Images/PPCA_Plot/Selfing_None.png")
selfing_n_1 <- as.raster(selfing_n)

selfing_h <- image_read("Images/PPCA_Plot/selfing.png")
selfing_h_1 <- as.raster(selfing_h)

single_flower <- image_read("Images/PPCA_Plot/Single_Flower.png")
single_flower_1 <- as.raster(single_flower)

many_flowers <- image_read("Images/PPCA_Plot/Inflorescencia.png")
many_flowers_1 <- as.raster(many_flowers)
#many_flowers_1 <- image_rotate(many_flowers, 45)

large_flower <- image_read("Images/PPCA_Plot/flower_big.png")
large_flower_1 <- as.raster(large_flower)

flower_small <- image_read("Images/PPCA_Plot/flower_short.png")
flower_small_1 <- as.raster(flower_small)

herb <- image_read("Images/PPCA_Plot/herb.png")
herb_1 <- as.raster(herb)

#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots

#Invert axes
PC$S[,1] <- -PC$S[,1]
PC$S[,2] <- -PC$S[,2]

all_spp <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density

  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
    scale_alpha(guide = 'none')

    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .7 * mult * (get(x)),
                      v2 = .7 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))

   #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB

  #CHANGE THEME

  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
     annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)

      #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
 plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,7.25,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.4,3,6.2,5,5.5)+c(0,0,0,0,0.4,0)),
                         label = PCAloadings$Variables, color="black",fontface =2,size=4)

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")

  plot

}

plot_grid(all_spp(PC))

```

Evaluation of qualitative variable positions in the trait space revealed statistical association on both axes of trait variation for compatibility, breeding system, life form, lifespan and flower shape (Figure 2 and Table S4). In addition, flower symmetry was associated with PC2 (Sum of squares = 8.51, F-value = 14.72 , p < 0.01 ). Nectar provision was independent of both axes (PC1 Sum of squares = 0.37, F-value = 0.29 , p = 0.59; PC2  Sum of squares = 0.83, F-value = 1.43 , p = 0.23). Concerning self compatibility, we found larger differences in pollinator dependence the trade off  (i.e., species with unisexual flowers and self incompatibility were statistically differentiated from species with partially and fullyself compatibility in trait space; Figure S3 A and B). Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Figure S3 C and D). Consequently, lifespan also followed this gradient but perennial and short lived species just differed statistically on PC2 (Figure S3 E and F). Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of trait variation with the highest pollinator dependence and flower number investment (Figure S3 G and H). Moreover, we found that the campanulate and capitulum flower shapes were differentiated  from tube, papilionaceous, open and brush shapes in the trait space. The former morphologies tended to occupy positions with larger flowers and greater pollination dependence, while the latter positions had higher number of flowers and autonomous selfing (Figure S3 I and J). Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher pollinator dependence (Figure S3 K and L).

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, fig.cap="Location of the qualitative traits in the trait space for traits that showed a statistical association with the main axis of trait variation. These different traits included: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f)."}

#Set working directory
setwd("~/R_Projects/Reproductive Traits")

#Load libraries
#LOAD LIBRARIES
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(cowplot)

# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.3)),
            axis.text=element_text(size = rel(1.75), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(0.4, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
             panel.grid.major= element_blank(),
            plot.title = element_text(size = rel(1.75), face="bold")
      ))
}

#Load data
dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")

#CALL the output PC for simplicity
PC <- phyl_pca_forest
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots
Compatibility <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Compatibility <- dat_cleaning_5$Compatibility_system
  dat$Compatibility <- as.character(dat$Compatibility)
  dat$Compatibility[dat$Compatibility=="dioecious"] <- "Unisexual flowers"
  dat$Compatibility[dat$Compatibility=="monoecious"] <- "Unisexual flowers"
  dat$Compatibility[dat$Compatibility=="partially_self_compatible"] <- "Partially self compatible"
  dat$Compatibility[dat$Compatibility=="self_compatible"] <- "Self compatible"
  dat$Compatibility[dat$Compatibility=="self_incompatible"] <- "Self incompatible"
  dat$Compatibility <- factor(dat$Compatibility, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))

  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Compatibility),size=1.75)+scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
                          label = PCAloadings$Variables, color="black",size=3)

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.185, 0.13)) +ggtitle("(a)")

  plot

}

#Compatibility(PC)

#############################################################################################################################################################
#Life form
#############################################################################################################################################################
#Load plots
Life_form <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$`Life form` <- dat_cleaning_5$life_form
  dat$`Life form` <- as.character(dat$`Life form`)
  dat$`Life form`[dat$`Life form`=="herb"] <- "Herb"
  dat$`Life form`[dat$`Life form`=="shrub"] <- "Shrub"
  dat$`Life form`[dat$`Life form`=="tree"] <- "Tree"
  dat$`Life form`[dat$`Life form`=="vine"] <- "Shrub"

  dat$`Life form` <- factor( dat$`Life form`, levels = c("Herb", "Shrub", "Tree"))

  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Life form`),size=1.75)+scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
                          label = PCAloadings$Variables, color="black",size=3)

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("(b)")

  plot

}

#Life_form(PC)

#############################################################################################################################################################
#Life span
#############################################################################################################################################################
#Load plots
Life_span <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
    dat$Lifespan <- dat_cleaning_5$lifespan
    dat$Lifespan <- as.character(dat$Lifespan)

  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Lifespan),size=1.75)+scale_color_manual(values=c("sienna4","forestgreen"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
                          label = PCAloadings$Variables, color="black",size=3)

  #CHANGE THEME
  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.102, 0.1)) + ggtitle("(c)")

  plot

}

#Life_span(PC)

#############################################################################################################################################################
#Flower symmetry
#############################################################################################################################################################
#Load plots
Flower_sym <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$`Flower symmetry` <- dat_cleaning_5$Flower_symmetry
  dat$`Flower symmetry` <- as.character(dat$`Flower symmetry`)
  dat$`Flower symmetry`[dat$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
  dat$`Flower symmetry`[dat$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"

  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower symmetry`),size=1.75)+scale_color_manual(values=c("sienna2","purple"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
                          label = PCAloadings$Variables, color="black",size=3)

  #CHANGE THEME

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.165, 0.1)) + ggtitle("(f)")

  plot

}

#Flower_sym(PC)

#############################################################################################################################################################
#Flower shape
#############################################################################################################################################################
#Load plots
Flower_sha <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$`Flower shape` <- dat_cleaning_5$Flower_morphology
  dat$`Flower shape` <- as.character(dat$`Flower shape`)
  dat$`Flower shape`[dat$`Flower shape`=="Funnelform"] <- "Campanulate"
  dat$`Flower shape`[dat$`Flower shape`=="Spike"] <- "Brush"

  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower shape`),size=1.75)+scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
                          label = PCAloadings$Variables, color="black",size=3)

  #CHANGE THEME

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.13, 0.18)) + ggtitle("(e)")

  plot

}

#Flower_sha(PC)

#############################################################################################################################################################
#Breeding system
#############################################################################################################################################################
#Load plots
Breeding_syst <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$`Breeding system` <- dat_cleaning_5$Breeding_system
  dat$`Breeding system` <- as.character(dat$`Breeding system`)
  dat$`Breeding system` <- factor(dat$`Breeding system`, levels=c("Hermaphrodite","Monoecious" ,"Dioecious"))

  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Breeding system`),size=1.75)+scale_color_manual(values=c("forestgreen","orange", "black"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
                          label = PCAloadings$Variables, color="black",size=3)

  #CHANGE THEME
  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.163, 0.115)) + ggtitle("(d)")

  plot

}

#Breeding_syst(PC)

#############################################################################################################################################################
#Nectar
#############################################################################################################################################################
#Load plots
#Nectar <- function(PC, x="PC1", y="PC2") {
#  # PC being a prcomp object
#  data <- data.frame(PC$S)
#  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
#  dat <- data.frame(x = data[,x], y = data[,y])
#  
#  #######
#  #DENSITY FUNCTION
#  #######
#  get_density <- function(x, y, ...) {
#    dens <- MASS::kde2d(x, y, ...)
#    ix <- findInterval(x, dens$x)
#    iy <- findInterval(y, dens$y)
#    ii <- cbind(ix, iy)
#    return(dens$z[ii])
#  }
#  
#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
#  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
#  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
#  dat$Nectar[dat$Nectar=="no"] <- "Absence"
#  plot <- plot + geom_point(data=dat, aes(-x, -y, #colour=Nectar),size=1.75)+scale_color_manual(values=c("black","grey"))
#  
#  ########
#  #ADD ARROWS 
#  ########
#  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
#  mult <- min(
#    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
#    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
#  )
#  datapc <- transform(datapc,
#                      v1 = .75 * mult * (get(x)),
#                      v2 = .75 * mult * (get(y))
#  )
#  # add arrows
#  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, #yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
#  
#  #Add axis with perctentage
#  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
#
#  
#  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, #arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
#  
#  #ADD LABELS
#  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
#  
#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
#  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = #-(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
#                          label = PCAloadings$Variables, color="black",size=3)
#  
#  #CHANGE THEME
#  #CHANGE THEME
#  
#  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)") 
#  
#  plot
#  
#}
#
# #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")

  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),ncol=3,nrow=2,  align = "hv")

```

## Phylogenetic signal of traits

We found a strong phylogenetic signal with statistical association (P < 0.01) for all quantitative traits (Table S4). The traits with the highest phylogenetic signal were ovule number ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73) and flower number per plant ($\lambda$ = 0.69).  Finally the traits that showed lower phylogenetic signal were inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).

Add
*pollen and nectar traits

## Visitation patterns

The overall visitation records of functional groups differed considerably. There were 2,256 for bees, 1,768 for non-syrphid-Diptera, 845 for syrphids, 437 for Lepidoptera, 432 for Coleoptera and 362 for non-bee-Hymenoptera. The main axes of trait variation explained little of the visitation patterns (conditional R2 = 0.31; marginal R2 = 0.06) but showed interesting trends for the different functional groups (Figure 3). Furthermore, the additional model with interaction between the most represented families of Hymenoptera and the main axis of trait variation (marginal R2 = 0.30; conditional R2 = 0.03) showed that the family Apidae was the main driver of the observed patterns (Figure S2). Although Apis mellifera contributed substantially to floral visitation, the general pattern of bee visitation did not change when A. mellifera were removed (FSX).

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28}

#LOAD LIBRARIES 
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(tidyverse)
library(patchwork) #panel of plots
library(brms)
library(cmdstanr)

#Load theme for publication

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2)),
           axis.text=element_text(size = rel(1.8), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.4)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(1.8, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank(),
           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
           plot.subtitle = element_text(face="bold",size=rel(2))
     ))
}

setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github

#Plot nicely PC1
analysis_1_just_bees <- readRDS("results_analysis_1_just_bees.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1_just_bees.rds")

ce_pc1 <- conditional_effects(analysis_1_just_bees, effects = "PC1",points=T) 
ce_pc1[[1]]$guild <- "bees"

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + ggtitle("PC1", subtitle = "(a)")

#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1_just_bees, effects = "PC2",points=T) 
ce_pc1[[1]]$guild <- "bees"

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + ggtitle("PC2", subtitle = "(b)")
#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1_just_bees, effects = "PC3",points=T)
ce_pc1[[1]]$guild <- "bees"

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + ggtitle("PC3", subtitle = "(c)")

#Plot nicely PC1
analysis_1_no_bees <- readRDS("results_analysis_1_no_bees.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1_no_bees.rds")

ce_pc1 <- conditional_effects(analysis_1_no_bees, effects = "PC1:guild",points=T)

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("High Flower N.    Large flowers")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
   "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids")) + ggtitle("(d)")

ce_pc2 <- conditional_effects(analysis_1_no_bees, effects = "PC2:guild",points=T)

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
   "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids")) + ggtitle("(e)")

#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1_no_bees, effects = "PC3:guild",points=T)

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles")+
  theme_ms() +theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
    "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
               "Non-syrphids-diptera", "Syrphids")) + ggtitle("(f)")

library(patchwork)

combined <- p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "right")
combined + plot_layout(guides = "collect",ncol = 3)

```

## Plant species metrics

The three main axes of trait variation did not explain the position or role of the plant species in the network (visits ~ PCs: conditional R2 =0.11 , marginal R2 = 0.02; normalized degree ~ PCs: conditional R2 =0.24 , marginal R2 = 0.02 and specialization ~ PCs: conditional R2 =0.37 , marginal R2 = 0.03). However, the functional groups showed different visitation patterns across the three main axes of trait variation (Figure 3). On the flower number versus size compromise, all functional groups showed higher visitation rates on plant species with greater vegetative investment and more flowers except syrphids which showed the opposite trend (higher visitation on species with larger flowers and associated traits). Remarkably, on the pollinator dependence trade-off, all pollinator functional groups showed an increasing visitation pattern for species with higher pollinator dependence. Lastly, we found that bees, Lepidoptera and non-bee Hymenoptera visited more species with larger style length and Coleoptera, Non-Syrphids Diptera and Syrphids had greater visitation patterns on species with shorter styles. Furthermore, with the full model that included all traits, we found that a considerable amount of  variance for plant species network metrics was explained by the different qualitative and quantitative traits (Visits ~ Traits: conditional R2 =0.32 , marginal R2 = 0.07; Normalize degree ~ Traits: conditional R2 =0.46 , marginal R2 = 0.16; Specialization ~ Traits: conditional R2 =0.49, marginal R2 = 0.14).

# DISCUSSION

Our work highlights that in plant-pollinator networks, plant species have displayed clear trade-offs in life strategies. These trade-offs can be differentiated on two main axes of trait variation: the flower number-size trade-off and the pollinator dependence trade-off. In addition, we found that relevant qualitative traits were aggregated within trait space, showing clear delimited strategies of different plant species within plant-pollinated systems. Moreover, the distinct pollinator functional groups showed changes in their interaction strength along these axes of trait variation.  Although the main axes of trait variation explained little the variation of plant species network metrics, the full model of uncorrelated traits explained partially the plan level metrics.

# CONCLUSIONS

Wrap up

# ACKNOWLEDGEMENTS

On the shoulders of giants.

# REFERENCES

<div id ="refs"></div>

\eleft

<!--# Tables below -->

\listoftables

<!--# Figures below -->

\listoffigures

# SUPPLEMENTARY MATERIAL {-}

\beginsupplement

<!--# To have separate reference lists for main text and Suppl Mat, see https://gist.github.com/Pakillo/e1407cc0632a9202813ec2aee2434cc3 -->

### 2021-05-19 Untitled/Manuscript.tex
.

\documentclass[11pt,a4paper,]{article}
\usepackage[]{mathpazo}
\usepackage{setspace}
\setstretch{2}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{
            pdftitle={Plant reproductive strategies structure plant-pollinator networks},
            pdfauthor={Jose B. Lanuza1,2*; Romina Rader1; Jamie Stavert3; Liam K. Kendall4; Manu E. Saunders1; Ignasi Bartomeus2},
            colorlinks=true,
            linkcolor=RoyalBlue,
            citecolor=Blue,
            urlcolor=RoyalBlue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{lineno} % add 
\linenumbers % turns line numbering on

% Allowing for landscape pages
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

% Left justification of the text: see https://www.sharelatex.com/learn/Text_alignment
% \usepackage[document]{ragged2e} % already in the latex template
\newcommand{\bleft}{\begin{flushleft}}
\newcommand{\eleft}{\end{flushleft}}

% Add Supplementary Tables and Figures
% Code from https://stackoverflow.com/a/51337664
\newcommand{\beginsupplement}{
  \setcounter{table}{0}  
  \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0} 
  \renewcommand{\thefigure}{S\arabic{figure}}
}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{Plant reproductive strategies structure plant-pollinator networks}
\author{Jose B. Lanuza\textsuperscript{1,2}* \and Romina Rader\textsuperscript{1} \and Jamie Stavert\textsuperscript{3} \and Liam K. Kendall\textsuperscript{4} \and Manu E. Saunders\textsuperscript{1} \and Ignasi Bartomeus\textsuperscript{2}}
\date{}

\begin{document}
\maketitle

\small

\textsuperscript{1} School of Environmental and Rural Science,
University of New England, Armidale, New South Wales 2350, Australia

\textsuperscript{2} Estación Biológica de Doñana (EBD-CSIC), E-41092
Seville, Spain

\textsuperscript{3} Department of Conservation \textbar{} Te Papa
Atawhai, Auckland, New Zealand

\textsuperscript{4} Centre for Environmental and Climate Science, Lund
University, Sölvegatan 37, S-223 62 Lund, Sweden

\texttt{*} Corresponding author:
\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}

\normalsize

\vspace{1cm} \hrule

\section{Abstract}\label{abstract}

Increasing availability of large datasets have improved our
understanding of organismal life history and pollination biology.
However, most attention has focused on vegetative traits when delimiting
plant life strategies and overlooked key floral and reproductive traits.
In addition, plant-pollinator research rarely considers the reproductive
biology of the species and has overemphasized the study of highly
specialized interactions. Greater knowledge of the plant reproductive
trade-offs between these traits can shed light on the macroecological
patterns and help our understanding of life strategies.

Here, we compiled 20 reproductive traits for 1,506 plant species from 28
plant-pollinator network studies and 18 different countries that
constitute a total of 64 unique networks and 8 meta-webs. We explore the
different trade-offs of floral, reproductive, and vegetative traits of
the main quantitative traits in the trait space. Then, we evaluate
whether the frequency of pollinator visits within networks change across
the primary axes of trait variation and pollinator functional groups and
how individual traits contribute to the overall visitation patterns.
Finally, we investigate if the functional role of the plant species
(interaction frequency, normalized degree and specialization) in the
network is associated with the primary axes of trait variation and the
different plant traits.

We found that 51.8\% of the trait variation was explained by two
independent axes that determined plant form and function. The first axis
showed the flower number versus flower size compromise (PC1, 26.72\%)
where species were divided in two opposed strategies with high
investment in flower number and plant height on one extreme or high
investment in flower size, style length and larger number of ovules on
the other. The second axis showed the pollinator dependence trade-off
(PC2, 25.08\%) between species with high pollinator dependence with
greater plant height and higher investment in floral traits on one end
and low pollinator dependence with smaller height and lower investment
in floral traits on the other. An additional principal component
analysis with the subset of species with quantitative data of pollen and
nectar showed that nectar quantity was positively associated with flower
size, style length and ovule number (PC1, 24.70\%) and pollen quantity
was positively correlated with flower number and plant height and
negatively associated with autonomous selfing (PC2, 20.59\%). The main
axes of trait variation with the full set of species did not explain the
overall visitation patterns but showed marked trends for the different
functional groups. For instance, all pollinator functional groups had
higher frequency of visits on plant species with high pollinator
dependence (PC2); and bees (Anthophila), the most abundant functional
group, had higher frequency of visits on species with high number of
flowers and tall plant height (PC1); and, on species with longer styles
and higher levels of autonomous selfing (PC3). Overall, plant species
with small size, low nectar concentration and short styles showed lower
visitation rates than plant species with the opposed traits; species
with small amounts of floral rewards (pollen and nectar), low number of
flowers and small flowers had in general lower number of visiting
species (normalized degree); and species under 1.3 m, with high rewards
of pollen and nectar showed the highest levels of specialization. This
work highlights the need to consider essential plant reproductive and
floral traits to improve understanding of plant life strategies and
plant-pollinator interactions at large scales.

\vspace{3mm} \hrule
\vspace{5mm}

\emph{Keywords}: plant-pollinator networks \textbar{} floral traits
\textbar{} life history strategy \textbar{} functional traits

\bleft
\newpage

\section{INTRODUCTION}\label{introduction}

Among flowering plants there is an astonishing diversity of floral
structures and plant reproductive strategies (Barrett
\protect\hyperlink{ref-barrett2002}{2002}, Schiestl and Johnson
\protect\hyperlink{ref-schiestl2013}{2013}). Subsequently, pollination
biologists have long studied their relevance on plant-pollinator
interactions. However, despite recent efforts exploring reproductive
(e.g., mating and compatibility system) and floral traits (e.g., flower
size or nectar provision) with large sets of species (Carvalheiro et al.
\protect\hyperlink{ref-carvalheiro2014}{2014}, Baude et al.
\protect\hyperlink{ref-baude2016}{2016}, Munoz et al.
\protect\hyperlink{ref-munoz2016}{2016}, Grossenbacher et al.
\protect\hyperlink{ref-grossenbacher2017}{2017}, Moeller et al.
\protect\hyperlink{ref-moeller2017}{2017}), most studies focus on the
individual, community level or specific taxa and macroecological
patterns remain poorly investigated. For instance, studies depicting
species' life history strategies generally focus on vegetative traits
and rarely consider reproductive traits on the main axes of trait
variation (Díaz et al. \protect\hyperlink{ref-diaz2016}{2016},
Salguero-Gómez et al. \protect\hyperlink{ref-salguero2016}{2016}). In
addition, there is not a unified framework that explores the compromises
of floral traits and their relevance on plant life strategies (Roddy et
al. \protect\hyperlink{ref-roddy2021}{2021}). Similarly, there is
growing interest in understanding what determines plant-pollinator
network structure. Approaches with traits range from the description of
pollination syndromes (e.g., Dellinger
\protect\hyperlink{ref-dellinger2020}{2020}), to more specific
trait-matching analysis (Bartomeus et al.
\protect\hyperlink{ref-bartomeus2016}{2016}), but again the reproductive
biology of the species has received little attention (but see Tur et al.
\protect\hyperlink{ref-tur2013}{2013} and @devaux2014) and floral traits
have been overlooked beyond highly specialised plant-pollinator
interactions (Dellinger \protect\hyperlink{ref-dellinger2020}{2020},
Roddy et al. \protect\hyperlink{ref-roddy2021}{2021}).

With increased availability of large trait databases, plant ecological
strategies have begun to be examined more frequently (e.g., TRY, Kattge
et al. \protect\hyperlink{ref-kattge2011}{2011} and COMPADRE,
Salguero-Gómez et al. \protect\hyperlink{ref-salguero2015}{2015}),
highlighting global patterns and constraints of plant form and function
(Díaz et al. \protect\hyperlink{ref-diaz2016}{2016}, Salguero-Gómez et
al. \protect\hyperlink{ref-salguero2016}{2016}, Carmona et al.
\protect\hyperlink{ref-carmona2021}{2021}). However, these resources and
their research have mainly focused on vegetative traits such as the leaf
(Wright et al. \protect\hyperlink{ref-wright2004}{2004}) or wood (Chave
et al. \protect\hyperlink{ref-chave2009}{2009}) trade-offs and neglected
reproductive and floral traits that also can influence the spectrum of
trait variation. For instance, short lived and perennial species tend to
have high and low levels of outcrossing respectively (Barrett
\protect\hyperlink{ref-barrett2003}{2003}, Moeller et al.
\protect\hyperlink{ref-moeller2017}{2017}) and outcrossing levels have
been shown to be positively correlated with flower size (Goodwillie et
al. \protect\hyperlink{ref-goodwillie2010}{2010}). In addition, the
presence of costly rewards (e.g., pollen or nectar) and showy flowers or
floral displays cannot be understood without considering pollinators
that are thought to be responsible for approximately 87.5\% of the
pollination of flowering plants (Ollerton et al.
\protect\hyperlink{ref-ollerton2011}{2011}). Hence, exploring plant life
strategies with reproductive and floral trade-offs, in conjunction with
their known pollinators seems necessary for a correct understanding of
the plant economics.

Several key studies have progressed knowledge of the link between traits
and network properties (Lázaro et al.
\protect\hyperlink{ref-lazaro2008}{2008}, Bartomeus
\protect\hyperlink{ref-bartomeus2013}{2013}, Carvalheiro et al.
\protect\hyperlink{ref-carvalheiro2014}{2014}, Klumpers et al.
\protect\hyperlink{ref-klumpers2019}{2019}). Functional traits can
determine whether species interact, and thus define the species network
role (e.g., specialist vs generalist). For instance, species with high
investment in floral display tend to have higher visitation rates (Stang
et al. \protect\hyperlink{ref-stang2006}{2006}, Novella-Fernandez et al.
\protect\hyperlink{ref-novella-fernandez2019}{2019}) and greater
specialization is generally associated with occupation of the trait
space extremes (Junker et al. \protect\hyperlink{ref-junker2013}{2013},
Coux et al. \protect\hyperlink{ref-coux2016}{2016}). In addition, the
structure of the pollination network highly depends on the degree of
trait-matching between plants and pollinators (Stang et al.
\protect\hyperlink{ref-stang2009}{2009}, Ibanez
\protect\hyperlink{ref-ibanez2012}{2012}, Peralta et al.
\protect\hyperlink{ref-peralta2020}{2020}). However, little is known
about the consequences of reproductive traits and floral rewards on
plant species roles. In addition, although some attempts have been made
to evaluate trait relationships in plant-pollinator interactions at a
global scale (Carvalheiro et al.
\protect\hyperlink{ref-carvalheiro2014}{2014}, Rech et al.
\protect\hyperlink{ref-rech2016}{2016}), macroecological patterns have
been little explored.

Here, we explore the major axes of plant reproductive trait variation.
We investigate how these traits influence the structure of
plant-pollinator networks by compiling a unique dataset comprising 20
plant functional traits for 1,506 species from 64 unique networks and 8
metawebs. First, we evaluate the major axes of reproductive trait
variation and tradeoffs that determine plant form and function. Second,
we investigate how plant species' position in trait-space influences
interaction strength with different pollinator functional groups.
Finally, we assess the relevance of the main axes of trait variation and
traits in understanding the plant species role within the networks with
complementary species level metrics (i.e., interaction strength,
normalized degree and specialization).

\section{METHODS}\label{methods}

\subsection{Plant-pollinator network
studies}\label{plant-pollinator-network-studies}

We selected 28 studies from 18 different countries that constituted a
total of 64 plant-pollinator networks. All these studies censored
plant-pollinator interactions in natural systems and were selected in
order to have a wide representation of geographical areas of the world.
Although these studies differ in sampling effort and methodology, all
studies provided information about plant-pollinator interactions
(weighted and non-weighted) allowing us to build a database of plants
that are likely to be animal pollinated. Some of these networks have
been already used in past studies of plant-pollinator networks (Olesen
et al. \protect\hyperlink{ref-olesen2007}{2007}, Fortuna et al.
\protect\hyperlink{ref-fortuna2010}{2010}, Carvalheiro et al.
\protect\hyperlink{ref-carvalheiro2014}{2014}) and are available on the
online networks archives The Web of Life (Fortuna et al.
\protect\hyperlink{ref-fortuna2014}{2014}) and Mangal (Poisot et al.
\protect\hyperlink{ref-poisot2016}{2016}). In total, our network dataset
(Table S1) constituted 60 weighted (interaction frequency) and 4 binary
networks, each sampled at a unique location and year, as well as 8
meta-webs where sampled interactions were pooled across several
locations and multiple years.

\subsection{Taxonomy of plants and
pollinators}\label{taxonomy-of-plants-and-pollinators}

All plant species names, genera, families and orders were retrieved and
standardized from the taxonomy data sources NCBI
(\url{https://www.ncbi.nlm.nih.gov/taxonomy}) (plants) and ITIS
(\url{https://www.itis.gov/}) (pollinators) using the R package taxize
(version 0.9.99, Chamberlain et al.
\protect\hyperlink{ref-chamberlain2020}{2020}). We filled the `not
found' searches manually using \url{http://www.theplantlist.org/} and
\url{http://www.mobot.org/} for plants and
\url{http://www.catalogueoflife.org/} for floral visitors.

\subsection{Functional traits}\label{functional-traits}

We selected 20 different functional traits based on their relevance to
plant reproduction and data availability (Table 1). The selected traits
were quantitative (12) and categorical (8) and belonged to three
different trait types: vegetative, floral and reproductive. For each
species, we undertook an extensive literature and online search across a
wide range of resources (plant databases, online floras, books, journals
and images) from a total of 30,120 cells (20 columns x 1,506 spp) we
were able to fill 23,969 cells (79.6\% of the dataset, see Figure S1 for
missing values information per variable).

\setstretch{1.25}

\begin{table}

\caption{\label{tab:unnamed-chunk-1}List of the 20 traits compiled in this study divided in quantitative and categorical traits. The different types of trait (vegetative ‘V’, floral ‘F’ and reproductive ‘R’), total records found for the 1,506 species and categories of the qualitative traits are also provided. }
\centering
\fontsize{10}{12}\selectfont
\begin{tabu} to \linewidth {>{}c>{\raggedright}X>{\centering}X>{}c>{\raggedright}X>{\raggedright}X>{\centering}X}
\toprule
\multicolumn{3}{c}{\textbf{Quantitative traits}} & \multicolumn{4}{c}{\textbf{Categorical traits}} \\
\cmidrule(l{3pt}r{3pt}){1-3} \cmidrule(l{3pt}r{3pt}){4-7}
\textbf{Type} & \textbf{Traits} & \textbf{Records} & \textbf{Type} & \textbf{Traits} & \textbf{Categories} & \textbf{Records}\\
\midrule
\textbf{V} & Plant height (m) & 1470 & \textbf{V} & Lifepan & \makecell[l]{Short-lived \\ Perennial} & 1466\\
\addlinespace
\textbf{F} & Flower width (mm) & 1472 & \textbf{V} & Life form & \makecell[l]{Herb \\ Shrub \\ Tree} & 1472\\
\addlinespace
\textbf{F} & Flower length (mm) & 1401 & \textbf{F} & Flower shape & \makecell[l]{Brush \\ Campanulate \\ Capitulum \\ Open \\ Papilionaceous \\ Tube} & 1458\\
\addlinespace
\textbf{F} & Inflorescence width (mm) & 1496 & \textbf{F} & Flower symmetry & \makecell[l]{Actinomorphic \\ Zygomorphic} & 1478\\
\addlinespace
\textbf{F} & Style length (mm) & 1497 & \textbf{F} & Nectar & \makecell[l]{Presence \\ Absence} & 1407\\
\addlinespace
\textbf{F} & Ovules per flower & 1457 & \textbf{R} & Autonomous selfing & \makecell[l]{None \\ Low \\ Medium \\ High} & 987\\
\addlinespace
\textbf{F} & Flowers per plant & 1468 & \textbf{R} & Compatibility system & \makecell[l]{Self-incomp. \\ Partially self-comp. \\ Self-comp.} & 1253\\
\addlinespace
\textbf{F} & Nectar ($\mu$l) & 485 & \textbf{R} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious} & 1489\\
\addlinespace
\textbf{F} & Nectar (mg) & 415 & \textbf{} &  &  & \\
\addlinespace
\textbf{F} & Nectar concentration ($\%$) & 508 & \textbf{} &  &  & \\
\addlinespace
\textbf{F} & Pollen grains per flower & 298 & \textbf{} &  &  & \\
\addlinespace
\textbf{R} & Autonomous selfing (fruit set) & 992 & \textbf{} &  &  & \\
\bottomrule
\end{tabu}
\end{table}

\setstretch{2}

\subsection{Phylogenetic Distance}\label{phylogenetic-distance}

We calculated the phylogenetic distance between different plant species
using the function get\_tree from the package rtrees (downloaded from
github, \url{https://github.com/daijiang/rtrees}), which downloads
phylogenetic distances from the extended R implementation of the Open
Tree of Life (Smith and Brown \protect\hyperlink{ref-smith2018}{2018})
developed by Jin and Qian (\protect\hyperlink{ref-jin2019}{2019}).

\subsection{Data Imputation}\label{data-imputation}

Missing values were imputed with the function missForest (Stekhoven and
Bühlmann \protect\hyperlink{ref-stekhoven2012}{2012}) which allows
imputation of data sets with continuous and categorical variables. We
accounted for the phylogenetic distance among species on the imputation
process by including the eigenvectors of a principal component analysis
of the phylogenetic distance (PCoA) which has been shown to improve the
performance of missForest (Penone et al.
\protect\hyperlink{ref-penone2014}{2014}). To extract the eigenvectors,
we used the function PVRdecomp from the package PVR (Santos et al.
\protect\hyperlink{ref-santos2018}{2018}) based on the conceptual
framework of Diniz-Filho et al.
(\protect\hyperlink{ref-diniz-filho2012}{2012}). Although the variable
of autonomous selfing had a high percentage of missing values (68\%), we
were able to solve this by back transforming the qualitative column of
autonomous selfing to numerical. The categories of `none', `low',
`medium' and `high' were converted to representative percentages of each
category 0\%, 13\%, 50.8\% and 80\% respectively. This reduced the
percentage of missing values for this column from 68\% to 35\% and
allowed the imputation of this variable. However, we were unable to
impute nectar and pollen quantity due to the high percentage of missing
values (Figure S1). The imputed dataset had 9.7\% of missing values with
a total of 8 categorical and 8 numerical variables. Finally, we
conducted an additional imputation for the subset of species with
quantitative information of nectar and pollen; all variables had lower
than 30\% of missing values (N = 636) and the total proportion of
missing values in this dataset considering all variables was 13\%.

\subsection{Plant strategies}\label{plant-strategies}

We explored the trade-offs between different quantitative plant
functional traits with a phylogenetically informed Principal Component
Analysis (pPCA). We did not include the quantitative variables of flower
length and inflorescence width because they were highly and moderately
correlated to flower width (Pearson's correlation = 0.72, p \textless{}
0.01 and Pearson's correlation = 0.36, p \textless{} 0.01 respectively),
and thus we avoided overemphasizing flower size on the spectrum of trait
variation. In addition, we explored the location of different
qualitative traits in the trait space. Prior to the analyses, we
excluded outliers and standardized the data. Due to the high sensitivity
of dimensionality reduction to outliers, we excluded values in the
2.5th-97.5th percentile range (Legendre and Legendre
\protect\hyperlink{ref-legendre2012}{2012}). Then, we log transformed
the variables to reduce the influence of outliers and z-transformed (X=
0, SD=1) so that all variables were within the same numerical range. We
performed the pPCA using the function phyl.pca from the package phytools
(version number 0.7-70, Revell \protect\hyperlink{ref-revell2012}{2012})
with the method lambda (\(\lambda\)) that calculates the phylogenetic
correlation between 0 (phylogenetic independence) and 1 (shared
evolutionary history) and we implemented the mode covariance because our
variables are on the same scale after the log and z-transformation (Abdi
and Williams \protect\hyperlink{ref-abdi2010}{2010}). Moreover, to
corroborate that our imputation of missing values did not affect our
results, we conducted a pPCA on the full dataset without missing values
(Figure S2). We found little difference between the variance explained
with the imputed dataset (51.08\%) and the dataset without missing
values (56.26\%). In addition, the loadings on each principal component
had a similar contribution and correlation patterns, with the exception
of plant height which showed slight variations between the imputed and
non imputed dataset. Finally, we explored with the imputed dataset with
quantitative information of pollen and nectar the compromises in the
trait space of these two floral rewards with the other quantitative
traits. For this, we considered solely one variable of nectar quantity
(microlites of nectar per flower) in order to avoid overemphasizing
nectar on the spectrum of trait variation.

\subsection{Phylogenetic signal of
traits}\label{phylogenetic-signal-of-traits}

We calculated the phylogenetic signal of the different quantitative
traits on the imputed dataset with the full set of species (N = 1506)
with the package phytools version 0.7-70 (Revell
\protect\hyperlink{ref-revell2012}{2012}) and we used Pagel's lambda
(\(\lambda\)) as a measurement of the phylogenetic signal. For pollen
and nectar traits, phylogenetic signal was calculated on the imputed
dataset that included these traits (N = 636).

\subsection{Networks analysis}\label{networks-analysis}

Our analyses were conducted on the subset of 60 weighted networks with
interaction frequency sampled in a unique flowering season and site.
Although floral visitors are not always pollinators and the frequency of
visits does not consider each pollinator species efficiency (Ballantyne
et al. \protect\hyperlink{ref-ballantyne2015}{2015}), interaction
frequency provides valuable information of the impact of pollinators
(Vázquez et al., 2005; Vázquez et al., 2012). Although not all networks
were sampled using the same method, our aim was not to compare patterns
across networks but within each network in order to obtain a general
picture of associations between traits and the main axes of trait
variation and plant species functional roles.

\emph{Functional groups visitation patterns}

We explored the relevance of pollinator functional groups and the main
axes of trait variation (pPCA with imputed dataset) on pollinator
visitation per plant species. For this, we divided floral visitors into
six main groups that differ in life form and behaviour: (i)
Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other
non-bee Hymenoptera), (iii) Diptera-Syrphids, (iv) Diptera-Non-Syrphids,
(v) Lepidoptera and (vi) Coleoptera. In addition, because Hymenoptera
was the most represented group with 2,256 records counted and had the
highest frequency of visits of all groups, we also explored visitation
patterns of the most represented families of Hymenoptera on the trait
space (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae).
Apis mellifera was the species with the largest proportion of records
(7.55\% from the total) which is is consistent with the results of Hung
et al. (\protect\hyperlink{ref-hung2018}{2018}) that showed that A.
mellifera was the most frequent visiting species on a similar dataset of
80 interaction plant-pollinator networks on natural systems. Hence, to
control for the relevance of Apis mellifera on the observed visitation
patterns of bees, we conducted an analogous analysis excluding A.
mellifera. We found that A. mellifera, was driving, in part, some of the
observed trends on PC1 (Figure S3). However, we did not find major
changes on PC2 and PC3.

\emph{Plant species functional roles}

We investigated if the main axes of trait variation and traits explained
plant species functional roles. We considered all uncorrelated traits
apart from the principal components because this allowed us to consider
quantitative and categorical traits. For this, we also used a modelling
approach and conducted decision trees which help to interpret visually
how the different traits determine species functional roles. We selected
simple and complementary plant species level metrics with a relatively
straightforward ecological interpretation relevant to our research
goals: (i) sum of visits per plant species; (ii) normalized degree
calculated as the number of links per plant species divided by the
possible number of partners which helps comparison across networks; and
(iii) specialization (d') (Blüthgen et al.
\protect\hyperlink{ref-bluthgen2006}{2006}), which measures the
deviation of an expected random choice of the available interaction
partners and ranges between 0 (maximum generalization) and 1 (maximum
specialization). Normalized degree and specialization were calculated
with the specieslevel function from the R package bipartite (version
2.15, Dormann et al. \protect\hyperlink{ref-dormann2008}{2008}).

\subsection{Analyses}\label{analyses}

First, we implemented Bayesian generalized linear mixed models using the
R package brms (version 2.14.6, Bürkner
\protect\hyperlink{ref-burkner2017}{2017}). We modelled the frequency of
visits as a function of the main axes of trait variation and floral
visitors functional groups
(Visits\textasciitilde{}PC1xFG+PC2xFG+PC3xFG). Because we were
interested in possible differences among main visitor guilds to plants
with different strategies, we included the interaction between the main
axes of trait variation and the distinct floral visitor functional
groups. We added a nested random effect with networks nested on the
study system to capture the network variability per study and within
networks. We specified this model with a zero inflated negative binomial
distribution and weakly informative priors from the brms function.
Moreover, we included the phylogenetic covariance matrix as a random
factor due to the possible shared evolutionary history of the species
and therefore lack of independence across them.

Second, we modelled the distinct plant species metrics (sum of visits,
normalized degree and plant specialization) as a function of the three
main axes of trait variation in three different models for each metric
(plant species level metric\textasciitilde{}PC1+PC2+PC3). In addition we
also explored how all uncorrelated traits (13) explained these metrics
in three other models (plant species level metric \textasciitilde{}
plant height + lifespan + life form + flower shape + flower symmetry +
flower width + style length + ovule number + flowers per plant + nectar
provision + autonomous selfing + compatibility system + breeding
system). For each response variable (metric), we used different
distribution families: zero inflated negative binomial for the sum of
visits, weibull for normalized degree and zero one inflated beta for
specialization. Moreover, we included a nested random effect with
networks nested on the study system and a phylogenetic random effect for
species (as detailed above) in each model.

All analyses were conducted in R Version 4.0.3. In addition, all models
were run for 3,000 iterations with 1000 warm up iterations. We set delta
() to 0.99 to avoid divergent transitions and visualized the posterior
predictive checks with the function pp\_check using the bayesplot
package (version 1.7.2, Gabry et al., 2019).

{[}ADD REGRESSION TREE TO METHODS{]} We conducted regression trees in
order to explore the relevance of traits on the species plant functional
role. We repeated the procedure as the modelling analysis and we ran a
decision tree for each plant level species metric (interaction
frequency, normalized degree and specialization). We used the full
datase

rpart 4.1-15 (Therneau et al., 2019) rpart.plot 3.0.9 (Milborrow 2018)

\section{RESULTS}\label{results}

\subsection{Plant strategies}\label{plant-strategies-1}

The phylogenetically informed principal component analysis (pPCA)
captured with the first two and three axes 51.8\% and 70.97\% of the
trait variation respectively (Figure 1 and Figure S4) and had a
phylogenetic correlation (\(\lambda\)) of 0.76. The first principal
component (PC1) represented 26.72\% of the trait variation and showed
the flower number versus flower size compromise. Thus, as flower number
and plant height increase, flower size, style length and ovule number
decrease; and, as flower size, style length and ovule number increase,
flower number and plant height decrease. The main contributing traits to
PC1 were plant height, flower number, ovule number and flower size
(loadings \textgreater{} \textbar{}0.5\textbar{}; Table S2) but style
length also contributed moderately on PC1 (loading = -0.33). The second
principal component (PC2) represented 25.05\% of the trait variation and
showed the trade-off between low and high pollinator dependence and we
refer to this axis as the pollinator dependence trade-off. The main
driver of trait variation of PC2 was autonomous selfing (loading = 0.85)
but the other traits (except ovule number) also made a moderate
contribution to PC2 (loadings from 0.27 to 0.4; Table S2). We found that
high pollinator dependence was associated with larger and higher number
of flowers, greater plant height and longer styles. In contrast, species
with high levels of autonomous selfing had a general lower investment in
flower number and size, plant height and style length. Further, PC3 also
explained a considerable amount of variability (19.17\%) and the main
contributors to this axis were style length (loading = -0.66) and the
degree of autonomous selfing (loading = -0.51). The remaining traits,
apart from ovule number, were moderately correlated to changes on PC3
(loadings from -0.23 to -0.46; Table S2). In addition, the pPCA with the
species subset that had nectar and pollen quantity showed that nectar
quantity (microlitres of nectar per flower) was positively associated
with flower size, style length and ovule number (PC1, 24.70\%); and
pollen quantity was positively correlated with flower number and plant
height and negatively associated with autonomous selfing (PC2, 20.59\%;
Figure S5). This pPCA also showed similar explained variance with two
components (50.06\%) and similar associations of traits despite some
variability in the loadings (Table S3).

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
\caption{\label{fig:unnamed-chunk-2}Life history strategies for 1,236 plant
species from 29 plant-pollinator networks studies across the first two
axes of variation from a phylogenetically informed principal component
analysis (pPCA). The solid arrows indicate the direction and weights of
the six quantitative traits (flower number, plant height, style length,
flower size, ovule number and autonomous selfing level) and the labelled
icons at their end represent the extreme form of the trait continuum.
The dashed lines indicate the opposed direction of trait variation and
the non-labelled icons at their end illustrate the other extreme of the
continuum.}
\end{figure}

Evaluation of qualitative variable positions in the trait space revealed
statistical association on both axes of trait variation for
compatibility, breeding system, life form, lifespan and flower shape
(Figure 2 and Table S4). In addition, flower symmetry was associated
with PC2 (Sum of squares = 8.51, F-value = 14.72 , p \textless{} 0.01 ).
Nectar provision was independent of both axes (PC1 Sum of squares =
0.37, F-value = 0.29 , p = 0.59; PC2 Sum of squares = 0.83, F-value =
1.43 , p = 0.23). Concerning self compatibility, we found larger
differences in pollinator dependence the trade off (i.e., species with
unisexual flowers and self incompatibility were statistically
differentiated from species with partially and fullyself compatibility
in trait space; Figure S3 A and B). Life forms differed statistically
across both axes of trait variation and followed a gradient of larger
life forms (trees and shrubs) with higher pollinator dependence to
smaller ones (herbs) with lower pollinator dependence (Figure S3 C and
D). Consequently, lifespan also followed this gradient but perennial and
short lived species just differed statistically on PC2 (Figure S3 E and
F). Species with unisexual flowers (monoecious and dioecious) were
clustered on both extremes of trait variation with the highest
pollinator dependence and flower number investment (Figure S3 G and H).
Moreover, we found that the campanulate and capitulum flower shapes were
differentiated from tube, papilionaceous, open and brush shapes in the
trait space. The former morphologies tended to occupy positions with
larger flowers and greater pollination dependence, while the latter
positions had higher number of flowers and autonomous selfing (Figure S3
I and J). Regarding flower symmetry, zygomorphic flowers were associated
with lower levels of pollinator dependence, whereas actinomorphic
flowers had higher pollinator dependence (Figure S3 K and L).

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
\caption{\label{fig:unnamed-chunk-3}Location of the qualitative traits in
the trait space for traits that showed a statistical association with
the main axis of trait variation. These different traits included:
compatibility system (a), life form (b), lifespan (c), breeding system
(d), flower shape (e) and flower symmetry (f).}
\end{figure}

\subsection{Phylogenetic signal of
traits}\label{phylogenetic-signal-of-traits-1}

We found a strong phylogenetic signal with statistical association (P
\textless{} 0.01) for all quantitative traits (Table S4). The traits
with the highest phylogenetic signal were ovule number (\(\lambda\) = 1)
and plant height (\(\lambda\) = 0.96), followed by flower length
(\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73) and flower
number per plant (\(\lambda\) = 0.69). Finally the traits that showed
lower phylogenetic signal were inflorescence width (\(\lambda\) = 0.57),
style length (\(\lambda\) = 0.49) and autonomous selfing (\(\lambda\) =
0.34).

Add *pollen and nectar traits

\subsection{Visitation patterns}\label{visitation-patterns}

The overall visitation records of functional groups differed
considerably. There were 2,256 for bees, 1,768 for non-syrphid-Diptera,
845 for syrphids, 437 for Lepidoptera, 432 for Coleoptera and 362 for
non-bee-Hymenoptera. The main axes of trait variation explained little
of the visitation patterns (conditional R2 = 0.31; marginal R2 = 0.06)
but showed interesting trends for the different functional groups
(Figure 3). Furthermore, the additional model with interaction between
the most represented families of Hymenoptera and the main axis of trait
variation (marginal R2 = 0.30; conditional R2 = 0.03) showed that the
family Apidae was the main driver of the observed patterns (Figure S2).
Although Apis mellifera contributed substantially to floral visitation,
the general pattern of bee visitation did not change when A. mellifera
were removed (FSX).

\includegraphics{output/figures/unnamed-chunk-4-1.pdf}

\subsection{Plant species metrics}\label{plant-species-metrics}

The three main axes of trait variation did not explain the position or
role of the plant species in the network (visits \textasciitilde{} PCs:
conditional R2 =0.11 , marginal R2 = 0.02; normalized degree
\textasciitilde{} PCs: conditional R2 =0.24 , marginal R2 = 0.02 and
specialization \textasciitilde{} PCs: conditional R2 =0.37 , marginal R2
= 0.03). However, the functional groups showed different visitation
patterns across the three main axes of trait variation (Figure 3). On
the flower number versus size compromise, all functional groups showed
higher visitation rates on plant species with greater vegetative
investment and more flowers except syrphids which showed the opposite
trend (higher visitation on species with larger flowers and associated
traits). Remarkably, on the pollinator dependence trade-off, all
pollinator functional groups showed an increasing visitation pattern for
species with higher pollinator dependence. Lastly, we found that bees,
Lepidoptera and non-bee Hymenoptera visited more species with larger
style length and Coleoptera, Non-Syrphids Diptera and Syrphids had
greater visitation patterns on species with shorter styles. Furthermore,
with the full model that included all traits, we found that a
considerable amount of variance for plant species network metrics was
explained by the different qualitative and quantitative traits (Visits
\textasciitilde{} Traits: conditional R2 =0.32 , marginal R2 = 0.07;
Normalize degree \textasciitilde{} Traits: conditional R2 =0.46 ,
marginal R2 = 0.16; Specialization \textasciitilde{} Traits: conditional
R2 =0.49, marginal R2 = 0.14).

\section{DISCUSSION}\label{discussion}

Our work highlights that in plant-pollinator networks, plant species
have displayed clear trade-offs in life strategies. These trade-offs can
be differentiated on two main axes of trait variation: the flower
number-size trade-off and the pollinator dependence trade-off. In
addition, we found that relevant qualitative traits were aggregated
within trait space, showing clear delimited strategies of different
plant species within plant-pollinated systems. Moreover, the distinct
pollinator functional groups showed changes in their interaction
strength along these axes of trait variation. Although the main axes of
trait variation explained little the variation of plant species network
metrics, the full model of uncorrelated traits explained partially the
plan level metrics.

\section{CONCLUSIONS}\label{conclusions}

Wrap up

\section{ACKNOWLEDGEMENTS}\label{acknowledgements}

On the shoulders of giants.

\section{REFERENCES}\label{references}

\hypertarget{refs}{}
\hypertarget{ref-abdi2010}{}
Abdi, H., and L. J. Williams. 2010. Principal component analysis. WIREs
Computational Statistics 2:433--459.

\hypertarget{ref-ballantyne2015}{}
Ballantyne, G., K. C. R. Baldock, and P. G. Willmer. 2015. Constructing
more informative plantPollinator networks: Visitation and pollen
deposition networks in a heathland plant community. Proceedings of the
Royal Society B: Biological Sciences 282:20151130.

\hypertarget{ref-barrett2002}{}
Barrett, S. C. H. 2002. The evolution of plant sexual diversity. Nature
Reviews Genetics 3:274--284.

\hypertarget{ref-barrett2003}{}
Barrett, S. C. H. 2003. Mating strategies in flowering plants: The
outcrossing-selfing paradigm and beyond. Philosophical Transactions of
the Royal Society B: Biological Sciences 358:991--1004.

\hypertarget{ref-bartomeus2013}{}
Bartomeus, I. 2013. Understanding Linkage Rules in Plant-Pollinator
Networks by Using Hierarchical Models That Incorporate Pollinator
Detectability and Plant Traits. PLOS ONE 8:e69200.

\hypertarget{ref-bartomeus2016}{}
Bartomeus, I., D. Gravel, J. M. Tylianakis, M. A. Aizen, I. A. Dickie,
and M. Bernard-Verdier. 2016. A common framework for identifying linkage
rules across different types of interactions. Functional Ecology
30:1894--1903.

\hypertarget{ref-baude2016}{}
Baude, M., W. E. Kunin, N. D. Boatman, S. Conyers, N. Davies, M. A.
Gillespie, R. D. Morton, S. M. Smart, and J. Memmott. 2016. Historical
nectar assessment reveals the fall and rise of floral resources in
britain. Nature 530:85--88.

\hypertarget{ref-bluthgen2006}{}
Blüthgen, N., F. Menzel, and N. Blüthgen. 2006. Measuring specialization
in species interaction networks. BMC Ecology 6:9.

\hypertarget{ref-burkner2017}{}
Bürkner, P.-C. 2017. Brms: An R package for Bayesian multilevel models
using Stan. Journal of statistical software 80:1--28.

\hypertarget{ref-carmona2021}{}
Carmona, C. P., R. Tamme, M. Pärtel, F. de Bello, S. Brosse, P.
Capdevila, R. González-M, M. González-Suárez, R. Salguero-Gómez, M.
Vásquez-Valderrama, and A. Toussaint. 2021. Erosion of global functional
diversity across the tree of life. Science Advances 7:eabf2675.

\hypertarget{ref-carvalheiro2014}{}
Carvalheiro, L. G., J. C. Biesmeijer, G. Benadi, J. Fründ, M. Stang, I.
Bartomeus, C. N. Kaiser-Bunbury, M. Baude, S. I. F. Gomes, V. Merckx, K.
C. R. Baldock, A. T. D. Bennett, R. Boada, R. Bommarco, R. Cartar, N.
Chacoff, J. Dänhardt, L. V. Dicks, C. F. Dormann, J. Ekroos, K. S. E.
Henson, A. Holzschuh, R. R. Junker, M. Lopezaraiza-Mikel, J. Memmott, A.
Montero-Castaño, I. L. Nelson, T. Petanidou, E. F. Power, M. Rundlöf, H.
G. Smith, J. C. Stout, K. Temitope, T. Tscharntke, T. Tscheulin, M.
Vilà, and W. E. Kunin. 2014. The potential for indirect effects between
co-flowering plants via shared pollinators depends on resource
abundance, accessibility and relatedness. Ecology Letters 17:1389--1399.

\hypertarget{ref-chamberlain2020}{}
Chamberlain, S., E. Szoecs, Z. Foster, Z. Arendsee, C. Boettiger, K.
Ram, I. Bartomeus, J. Baumgartner, J. O'Donnell, J. Oksanen, B. G.
Tzovaras, P. Marchand, V. Tran, M. Salmon, G. Li, and M. Grenié. 2020.
Taxize: Taxonomic information from around the web.

\hypertarget{ref-chave2009}{}
Chave, J., D. Coomes, S. Jansen, S. L. Lewis, N. G. Swenson, and A. E.
Zanne. 2009. Towards a worldwide wood economics spectrum. Ecology
letters 12:351--366.

\hypertarget{ref-coux2016}{}
Coux, C., R. Rader, I. Bartomeus, and J. M. Tylianakis. 2016. Linking
species functional roles to their network roles. Ecology Letters
19:762--770.

\hypertarget{ref-dellinger2020}{}
Dellinger, A. S. 2020. Pollination syndromes in the 21st century: Where
do we stand and where may we go? New Phytologist 228:1193--1213.

\hypertarget{ref-devaux2014}{}
Devaux, C., C. Lepers, and E. Porcher. 2014. Constraints imposed by
pollinator behaviour on the ecology and evolution of plant mating
systems. Journal of Evolutionary Biology 27:1413--1430.

\hypertarget{ref-diniz-filho2012}{}
Diniz-Filho, J. A. F., L. M. Bini, T. F. Rangel, I. Morales-Castilla, M.
Á. Olalla-Tárraga, M. Á. Rodríguez, and B. A. Hawkins. 2012. On the
selection of phylogenetic eigenvectors for ecological analyses.
Ecography 35:239--249.

\hypertarget{ref-diaz2016}{}
Díaz, S., J. Kattge, J. H. C. Cornelissen, I. J. Wright, S. Lavorel, S.
Dray, B. Reu, M. Kleyer, C. Wirth, I. Colin Prentice, E. Garnier, G.
Bönisch, M. Westoby, H. Poorter, P. B. Reich, A. T. Moles, J. Dickie, A.
N. Gillison, A. E. Zanne, J. Chave, S. Joseph Wright, S. N. Sheremet'ev,
H. Jactel, C. Baraloto, B. Cerabolini, S. Pierce, B. Shipley, D. Kirkup,
F. Casanoves, J. S. Joswig, A. Günther, V. Falczuk, N. Rüger, M. D.
Mahecha, and L. D. Gorné. 2016. The global spectrum of plant form and
function. Nature 529:167--171.

\hypertarget{ref-dormann2008}{}
Dormann, C. F., B. Gruber, and J. Fründ. 2008. Introducing the bipartite
package: Analysing ecological networks. interaction 1.

\hypertarget{ref-fortuna2014}{}
Fortuna, M. A., R. Ortega, and J. Bascompte. 2014. The Web of Life.
arXiv:1403.2575 {[}q-bio{]}.

\hypertarget{ref-fortuna2010}{}
Fortuna, M. A., D. B. Stouffer, J. M. Olesen, P. Jordano, D. Mouillot,
B. R. Krasnov, R. Poulin, and J. Bascompte. 2010. Nestedness versus
modularity in ecological networks: Two sides of the same coin? Journal
of Animal Ecology 79:811--817.

\hypertarget{ref-goodwillie2010}{}
Goodwillie, C., R. D. Sargent, C. G. Eckert, E. Elle, M. A. Geber, M. O.
Johnston, S. Kalisz, D. A. Moeller, R. H. Ree, M. Vallejo-Marin, and A.
A. Winn. 2010. Correlated evolution of mating system and floral display
traits in flowering plants and its implications for the distribution of
mating system variation. The New Phytologist 185:311--321.

\hypertarget{ref-grossenbacher2017}{}
Grossenbacher, D. L., Y. Brandvain, J. R. Auld, M. Burd, P.-O. Cheptou,
J. K. Conner, A. G. Grant, S. M. Hovick, J. R. Pannell, A. Pauw, and
others. 2017. Self-compatibility is over-represented on islands. New
Phytologist 215:469--478.

\hypertarget{ref-hung2018}{}
Hung, K.-L. J., J. M. Kingston, M. Albrecht, D. A. Holway, and J. R.
Kohn. 2018. The worldwide importance of honey bees as pollinators in
natural habitats. Proceedings of the Royal Society B: Biological
Sciences 285:20172140.

\hypertarget{ref-ibanez2012}{}
Ibanez, S. 2012. Optimizing size thresholds in a plant-pollinator
interaction web: Towards a mechanistic understanding of ecological
networks. Oecologia 170:233--242.

\hypertarget{ref-jin2019}{}
Jin, Y., and H. Qian. 2019. V.PhyloMaker: An R package that can generate
very large phylogenies for vascular plants. Ecography 42:1353--1359.

\hypertarget{ref-junker2013}{}
Junker, R. R., N. Blüthgen, T. Brehm, J. Binkenstein, J. Paulus, H. M.
Schaefer, and M. Stang. 2013. Specialization on traits as basis for the
niche-breadth of flower visitors and as structuring mechanism of
ecological networks. Functional Ecology 27:329--341.

\hypertarget{ref-kattge2011}{}
Kattge, J., S. Díaz, S. Lavorel, I. C. Prentice, P. Leadley, G. Bönisch,
E. Garnier, M. Westoby, P. B. Reich, I. J. Wright, J. H. C. Cornelissen,
C. Violle, S. P. Harrison, P. M. V. Bodegom, M. Reichstein, B. J.
Enquist, N. A. Soudzilovskaia, D. D. Ackerly, M. Anand, O. Atkin, M.
Bahn, T. R. Baker, D. Baldocchi, R. Bekker, C. C. Blanco, B. Blonder, W.
J. Bond, R. Bradstock, D. E. Bunker, F. Casanoves, J. Cavender-Bares, J.
Q. Chambers, F. S. C. Iii, J. Chave, D. Coomes, W. K. Cornwell, J. M.
Craine, B. H. Dobrin, L. Duarte, W. Durka, J. Elser, G. Esser, M.
Estiarte, W. F. Fagan, J. Fang, F. Fernández-Méndez, A. Fidelis, B.
Finegan, O. Flores, H. Ford, D. Frank, G. T. Freschet, N. M. Fyllas, R.
V. Gallagher, W. A. Green, A. G. Gutierrez, T. Hickler, S. I. Higgins,
J. G. Hodgson, A. Jalili, S. Jansen, C. A. Joly, A. J. Kerkhoff, D.
Kirkup, K. Kitajima, M. Kleyer, S. Klotz, J. M. H. Knops, K. Kramer, I.
Kühn, H. Kurokawa, D. Laughlin, T. D. Lee, M. Leishman, F. Lens, T.
Lenz, S. L. Lewis, J. Lloyd, J. Llusià, F. Louault, S. Ma, M. D.
Mahecha, P. Manning, T. Massad, B. E. Medlyn, J. Messier, A. T. Moles,
S. C. Müller, K. Nadrowski, S. Naeem, Ü. Niinemets, S. Nöllert, A.
Nüske, R. Ogaya, J. Oleksyn, V. G. Onipchenko, Y. Onoda, J. Ordoñez, G.
Overbeck, W. A. Ozinga, S. Patiño, S. Paula, J. G. Pausas, J. Peñuelas,
O. L. Phillips, V. Pillar, H. Poorter, L. Poorter, P. Poschlod, A.
Prinzing, R. Proulx, A. Rammig, S. Reinsch, B. Reu, L. Sack, B.
Salgado-Negret, J. Sardans, S. Shiodera, B. Shipley, A. Siefert, E.
Sosinski, J.-F. Soussana, E. Swaine, N. Swenson, K. Thompson, P.
Thornton, M. Waldram, E. Weiher, M. White, S. White, S. J. Wright, B.
Yguel, S. Zaehle, A. E. Zanne, and C. Wirth. 2011. TRY a global database
of plant traits. Global Change Biology 17:2905--2935.

\hypertarget{ref-klumpers2019}{}
Klumpers, S. G. T., M. Stang, and P. G. L. Klinkhamer. 2019. Foraging
efficiency and size matching in a plantPollinator community: The
importance of sugar content and tongue length. Ecology Letters
22:469--479.

\hypertarget{ref-lazaro2008}{}
Lázaro, A., S. J. Hegland, and Ø. Totland. 2008. The relationships
between floral traits and specificity of pollination systems in three
Scandinavian plant communities. Oecologia 157:249--257.

\hypertarget{ref-legendre2012}{}
Legendre, P., and L. Legendre. 2012. Numerical ecology. Elsevier.

\hypertarget{ref-moeller2017}{}
Moeller, D. A., R. D. B. Runquist, A. M. Moe, M. A. Geber, C.
Goodwillie, P.-O. Cheptou, C. G. Eckert, E. Elle, M. O. Johnston, S.
Kalisz, R. H. Ree, R. D. Sargent, M. Vallejo-Marin, and A. A. Winn.
2017. Global biogeography of mating system variation in seed plants.
Ecology Letters 20:375--384.

\hypertarget{ref-munoz2016}{}
Munoz, F., C. Violle, and P.-O. Cheptou. 2016. CSR ecological strategies
and plant mating systems: Outcrossing increases with competitiveness but
stress-tolerance is related to mixed mating. Oikos 125:1296--1303.

\hypertarget{ref-novella-fernandez2019}{}
Novella-Fernandez, R., A. Rodrigo, X. Arnan, and J. Bosch. 2019.
Interaction strength in plant-pollinator networks: Are we using the
right measure? PLOS ONE 14:e0225930.

\hypertarget{ref-olesen2007}{}
Olesen, J. M., J. Bascompte, Y. L. Dupont, and P. Jordano. 2007. The
modularity of pollination networks. Proceedings of the National Academy
of Sciences 104:19891--19896.

\hypertarget{ref-ollerton2011}{}
Ollerton, J., R. Winfree, and S. Tarrant. 2011. How many flowering
plants are pollinated by animals? Oikos 120:321--326.

\hypertarget{ref-penone2014}{}
Penone, C., A. D. Davidson, K. T. Shoemaker, M. D. Marco, C. Rondinini,
T. M. Brooks, B. E. Young, C. H. Graham, and G. C. Costa. 2014.
Imputation of missing data in life-history trait datasets: Which
approach performs the best? Methods in Ecology and Evolution 5:961--970.

\hypertarget{ref-peralta2020}{}
Peralta, G., D. P. Vázquez, N. P. Chacoff, S. B. Lomáscolo, G. L. W.
Perry, and J. M. Tylianakis. 2020. Trait matching and phenological
overlap increase the spatio-temporal stability and functionality of
plantPollinator interactions. Ecology Letters 23:1107--1116.

\hypertarget{ref-poisot2016}{}
Poisot, T., B. Baiser, J. A. Dunne, S. Kéfi, F. Massol, N. Mouquet, T.
N. Romanuk, D. B. Stouffer, S. A. Wood, and D. Gravel. 2016. Mangal
making ecological network analysis simple. Ecography 39:384--390.

\hypertarget{ref-rech2016}{}
Rech, A. R., B. Dalsgaard, B. Sandel, J. Sonne, J.-C. Svenning, N.
Holmes, and J. Ollerton. 2016. The macroecology of animal versus wind
pollination: Ecological factors are more important than historical
climate stability. Plant Ecology \& Diversity 9:253--262.

\hypertarget{ref-revell2012}{}
Revell, L. J. 2012. Phytools: An R package for phylogenetic comparative
biology (and other things). Methods in Ecology and Evolution 3:217--223.

\hypertarget{ref-roddy2021}{}
Roddy, A. B., C. Martínez-Perez, A. L. Teixido, T. G. Cornelissen, M. E.
Olson, R. S. Oliveira, and F. A. O. Silveira. 2021. Towards the flower
economics spectrum. New Phytologist 229:665--672.

\hypertarget{ref-salguero2015}{}
Salguero-Gómez, R., O. R. Jones, C. R. Archer, Y. M. Buckley, J.
Che-Castaldo, H. Caswell, D. Hodgson, A. Scheuerlein, D. A. Conde, E.
Brinks, H. de Buhr, C. Farack, F. Gottschalk, A. Hartmann, A. Henning,
G. Hoppe, G. Römer, J. Runge, T. Ruoff, J. Wille, S. Zeh, R. Davison, D.
Vieregg, A. Baudisch, R. Altwegg, F. Colchero, M. Dong, H. de Kroon,
J.-D. Lebreton, C. J. E. Metcalf, M. M. Neel, I. M. Parker, T. Takada,
T. Valverde, L. A. Vélez-Espino, G. M. Wardle, M. Franco, and J. W.
Vaupel. 2015. The compadre Plant Matrix Database: An open online
repository for plant demography. Journal of Ecology 103:202--218.

\hypertarget{ref-salguero2016}{}
Salguero-Gómez, R., O. R. Jones, E. Jongejans, S. P. Blomberg, D. J.
Hodgson, C. Mbeau-Ache, P. A. Zuidema, H. de Kroon, and Y. M. Buckley.
2016. Fast-slow continuum and reproductive strategies structure plant
life-history variation worldwide. Proceedings of the National Academy of
Sciences of the United States of America 113:230--235.

\hypertarget{ref-santos2018}{}
Santos, T., J. A. Diniz-Filho, T. R. e Luis, M. Bini, and M. T. Santos.
2018. Package ``PVR''.

\hypertarget{ref-schiestl2013}{}
Schiestl, F. P., and S. D. Johnson. 2013. Pollinator-mediated evolution
of floral signals. Trends in Ecology \& Evolution 28:307--315.

\hypertarget{ref-smith2018}{}
Smith, S. A., and J. W. Brown. 2018. Constructing a broadly inclusive
seed plant phylogeny. American Journal of Botany 105:302--314.

\hypertarget{ref-stang2006}{}
Stang, M., P. G. L. Klinkhamer, and E. V. D. Meijden. 2006. Size
constraints and flower abundance determine the number of interactions in
a plantFlower visitor web. Oikos 112:111--121.

\hypertarget{ref-stang2009}{}
Stang, M., P. G. L. Klinkhamer, N. M. Waser, I. Stang, and E. van der
Meijden. 2009. Size-specific interaction patterns and size matching in a
plantPollinator interaction web. Annals of Botany 103:1459--1469.

\hypertarget{ref-stekhoven2012}{}
Stekhoven, D. J., and P. Bühlmann. 2012. MissForestNon-parametric
missing value imputation for mixed-type data. Bioinformatics
28:112--118.

\hypertarget{ref-tur2013}{}
Tur, C., R. Castro-Urgal, and A. Traveset. 2013. Linking Plant
Specialization to Dependence in Interactions for Seed Set in Pollination
Networks. PLoS ONE 8:e78294.

\hypertarget{ref-wright2004}{}
Wright, I. J., P. B. Reich, M. Westoby, D. D. Ackerly, Z. Baruch, F.
Bongers, J. Cavender-Bares, T. Chapin, J. H. C. Cornelissen, M. Diemer,
J. Flexas, E. Garnier, P. K. Groom, J. Gulias, K. Hikosaka, B. B.
Lamont, T. Lee, W. Lee, C. Lusk, J. J. Midgley, M.-L. Navas, Ü.
Niinemets, J. Oleksyn, N. Osada, H. Poorter, P. Poot, L. Prior, V. I.
Pyankov, C. Roumet, S. C. Thomas, M. G. Tjoelker, E. J. Veneklaas, and
R. Villar. 2004. The worldwide leaf economics spectrum. Nature
428:821--827.

\eleft

\listoftables

\listoffigures

\section*{SUPPLEMENTARY MATERIAL}\label{supplementary-material}
\addcontentsline{toc}{section}{SUPPLEMENTARY MATERIAL}

\beginsupplement

\end{document}

### 2021-05-20 Supplementary_Material/Species_Level_Metric_Pc's.Rmd
Metrics~Pc's added to supplementary

---
output:
  pdf_document: default
  html_document: default
classoption: landscape

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=28}

library(brms) #modelling
library(cmdstanr) #modelling
library(cowplot) #panel of plots
library(ggplot2) #plotting
library(patchwork)

# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2)),
           axis.text=element_text(size = rel(2.5), color = "black"),
           legend.title=element_text(face="bold"),
           legend.text=element_text(),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(0.4, 'lines'),
           panel.border=element_rect(color="black",size=2),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank()
     ))
}
#########

setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github

#read data for plotting
data_analysis_2 <- readRDS("data_analysis_2.rds")

#INTERACTION FREQUENCY
Visits_PCs <- readRDS("results_analysis_2_Visits.rds") #load model

ce_1 <- conditional_effects(Visits_PCs, effects = "PC1",points=T) 
colnames(ce_1[[1]])[3] <- "Interaction"

Visits_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = Visits),
  size = 2.5, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC1")

ce_2 <- conditional_effects(Visits_PCs, effects = "PC2",points=T) 
colnames(ce_2[[1]])[3] <- "Interaction"

Visits_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = Visits),
  size = 2.5, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC2")

ce_3 <- conditional_effects(Visits_PCs, effects = "PC3",points=T) 
colnames(ce_3[[1]])[3] <- "Interaction"

Visits_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = Visits),
  size = 2.5, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC3")

#NORMALIZED DEGREE
normalised.degree_PCs <- readRDS("results_analysis_2_normalised.degree_PCs.rds") #load model

ce_1 <- conditional_effects(normalised.degree_PCs, effects = "PC1",points=T)

normalised.degree_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = normalised.degree),
  size = 2.5, alpha=0.65, colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC1")

ce_2 <- conditional_effects(normalised.degree_PCs, effects = "PC2",points=T)

normalised.degree_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = normalised.degree),
  size = 2.5, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC2")

ce_3 <- conditional_effects(normalised.degree_PCs, effects = "PC3",points=T)

normalised.degree_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = normalised.degree),
  size = 2.5, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC3")

#SPECIALIZATION
Specialization_PCs <- readRDS("results_analysis_2_Specialization_PCs.rds") #load model

ce_1 <- conditional_effects(Specialization_PCs, effects = "PC1",points=T) 
colnames(ce_1[[1]])[3] <- "Interaction"

Specialization_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = d),
  size = 2.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1")

ce_2 <- conditional_effects(Specialization_PCs, effects = "PC2",points=T) 
colnames(ce_2[[1]])[3] <- "Interaction"

Specialization_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = d),
  size = 2.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC2")

ce_3 <- conditional_effects(Specialization_PCs, effects = "PC3",points=T) 
colnames(ce_3[[1]])[3] <- "Interaction"

Specialization_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = d),
 size = 2.5, alpha=0.65, colour="darkorange3") + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+geom_line(colour="black",size=1.5)+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC3")

Visits_PC1 + Visits_PC2 + Visits_PC3 + normalised.degree_PC1 + normalised.degree_PC2 + normalised.degree_PC3 +
  Specialization_PC1 + Specialization_PC2+ Specialization_PC3  + plot_layout(ncol = 3)

```

### 2021-05-20 Supplementary_Material/Species_Level_Metric_Pcs.Rmd
Metrics~Pc's added to supplementary

---
output:
  pdf_document: default
  html_document: default
classoption: landscape

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=28}

library(brms) #modelling
library(cmdstanr) #modelling
library(cowplot) #panel of plots
library(ggplot2) #plotting
library(patchwork)

# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(3.5)),
           axis.text=element_text(size = rel(2.75), color = "black"),
           legend.title=element_text(face="bold"),
           legend.text=element_text(),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(0.4, 'lines'),
           panel.border=element_rect(color="black",size=3),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank()
     ))
}
#########

#Note the axes are inverted because they were inverted in the pPCA for visualization purposes

setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github

#read data for plotting
data_analysis_2 <- readRDS("data_analysis_2.rds")

#INTERACTION FREQUENCY
Visits_PCs <- readRDS("results_analysis_2_Visits.rds") #load model

ce_1 <- conditional_effects(Visits_PCs, effects = "PC1",points=T) 
colnames(ce_1[[1]])[3] <- "Interaction"

Visits_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = Visits),
  size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC1")

ce_2 <- conditional_effects(Visits_PCs, effects = "PC2",points=T) 
colnames(ce_2[[1]])[3] <- "Interaction"

Visits_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = Visits),
  size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC2")

ce_3 <- conditional_effects(Visits_PCs, effects = "PC3",points=T) 
colnames(ce_3[[1]])[3] <- "Interaction"

Visits_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = Visits),
  size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC3")

#NORMALIZED DEGREE
normalised.degree_PCs <- readRDS("results_analysis_2_normalised.degree_PCs.rds") #load model

ce_1 <- conditional_effects(normalised.degree_PCs, effects = "PC1",points=T)

normalised.degree_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = normalised.degree),
  size = 3, alpha=0.65, colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC1")

ce_2 <- conditional_effects(normalised.degree_PCs, effects = "PC2",points=T)

normalised.degree_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = normalised.degree),
  size = 3, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC2")

ce_3 <- conditional_effects(normalised.degree_PCs, effects = "PC3",points=T)

normalised.degree_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = normalised.degree),
  size = 3, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC3")

#SPECIALIZATION
Specialization_PCs <- readRDS("results_analysis_2_Specialization_PCs.rds") #load model

ce_1 <- conditional_effects(Specialization_PCs, effects = "PC1",points=T) 
colnames(ce_1[[1]])[3] <- "Interaction"

Specialization_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = d),
  size = 3, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1")

ce_2 <- conditional_effects(Specialization_PCs, effects = "PC2",points=T) 
colnames(ce_2[[1]])[3] <- "Interaction"

Specialization_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = d),
  size = 3, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC2")

ce_3 <- conditional_effects(Specialization_PCs, effects = "PC3",points=T) 
colnames(ce_3[[1]])[3] <- "Interaction"

Specialization_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = d),
 size = 3, alpha=0.65, colour="darkorange3") + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+geom_line(colour="black",size=1.5)+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC3")

plot_metrics_pcs <- Visits_PC1 + Visits_PC2 + Visits_PC3 + normalised.degree_PC1 + normalised.degree_PC2 + normalised.degree_PC3 +
  Specialization_PC1 + Specialization_PC2+ Specialization_PC3  + plot_layout(ncol = 3)

plot_metrics_pcs

saveRDS(plot_metrics_pcs, "plot_metrics_pcs.rds")

```

### 2021-05-20 Supplementary_Material/Supplementary_Material.Rmd
Metrics~Pc's added to supplementary

@@
 output: 
-  pdf_document: default
-  html_document: default
+  pdf_document:
+    extra_dependencies: ["float"]
 header-includes:
@@
 - \floatplacement{figure}{H}
+- \usepackage{afterpage}
+- \usepackage{placeins}
+- \usepackage{graphicx}
 
@@
 ---
+
+```{r echo=FALSE,warning=FALSE}
+knitr::opts_chunk$set(fig.pos = "h", out.extra = "")
+
+```
 
@@
 
-__Authors:__ Jose B. Lanuza, Romina Rader, Jamie Stavert, Liam K. Kendall, Manu E. Saunders & Ignasi Bartomeus
+__Authors:__ Jose B. Lanuza, Romina Rader, Jamie Stavert, Liam K. Kendall, Manu E. Saunders, Ignasi Bartomeus
 
@@
 __Figure S7__ Statistical comparison of the different categories of the categorical traits on the main two axes of trait variation (pPCA with the full set of species).
+
+__Figure S8__  Sum of visits per plant, normalized degree and specialization modelled in function of the first three main axes of trait variation.
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="**Fig.
-S1**  Percentage of present and missing values on the 20 traits compiled in this study (N = 1,506 species)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Fig S1.}  Percentage of present and missing values on the 20 traits compiled in this study (N = 1,506 species)."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="**Fig.
-S2** Phylogenetic informed principal component analysis for the species that did not have missing values (non-imputed dataset; N = 723)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig S2.} Phylogenetic informed principal component analysis for the species that did not have missing values (non-imputed dataset; N = 723)."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28,  fig.cap="**Fig.
-S3** Fitted posterior estimates of the number of visits made by the functional group of Hymenoptera-Anthophila (bees) including (superior panel) and excluding (lower panel) *Apis mellifera* in relation to the main axes of trait variation (PC, PC2 and PC3)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28,  fig.cap="\\textbf{Fig S3.} Fitted posterior estimates of the number of visits made by the functional group of Hymenoptera-Anthophila (bees) including (superior panel) and excluding (lower panel) *Apis mellifera* in relation to the main axes of trait variation (PC, PC2 and PC3)."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="**Fig.
-S4** Phylogenetically informed principal component analysis showing the trait relationship with principal components one and three (PC1 and PC3) for the full set of species (N = 1,506)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig S4.} Phylogenetically informed principal component analysis showing the trait relationship with principal components one and three (PC1 and PC3) for the full set of species (N = 1,506)."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="**Fig.
-S5** First two main principal components from the phylogenetic informed principal component analysis for the imputed dataset of the subset of species with quantitative information of nectar and pollen (N = 467)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig S5.} First two main principal components from the phylogenetic informed principal component analysis for the imputed dataset of the subset of species with quantitative information of nectar and pollen (N = 467)."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="**Fig.
-S6** Fitted posterior estimates of the number of visits made by the different main visiting families of bees (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) in relation to the main axes of trait variation (PC1, PC2 and PC3).
-We omitted in the plotting points over percentile 95% due to extreme outliers."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="\\textbf{Fig S6.} Fitted posterior estimates of the number of visits made by the different main visiting families of bees (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) in relation to the main axes of trait variation (PC1, PC2 and PC3).
+We omitted in the plotting points over percentile 95 \\% percent due to extreme outliers."}
 
@@
 
-\AtBeginShipout{\ifnum\value{page}=1\AtBeginShipoutDiscard\fi}
-
-\pagenumbering{gobble}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="**Fig.
-S7** Statistical comparison of the different categories of the categorical traits on the main two axes of trait variation (pPCA with the full set of species).
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig S7.} Statistical comparison of the different categories of the categorical traits on the main two axes of trait variation (pPCA with the full set of species).
 Categories that differ significantly are denoted with a different letter."}
@@
 ```
+
+\blandscape
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig S8.} Sum of visits per plant, normalized degree and speciliazation modelled in function of the first three main axes of trait variation.", fig.pos= "h"}
+
+library(brms) #modelling
+library(cmdstanr) #modelling
+library(cowplot) #panel of plots
+library(ggplot2) #plotting
+library(patchwork)
+
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(3.5)),
+           axis.text=element_text(size = rel(2.75), color = "black"),
+           legend.title=element_text(face="bold"),
+           legend.text=element_text(),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(0.4, 'lines'),
+           panel.border=element_rect(color="black",size=3),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank()
+     ))
+}
+#########
+
+setwd("~/Dropbox/PhD/R/Chapter_2")
+
+#read plot generated in other rmd, bms and stan are giving trouble here... This file is created in Species_Level_Metric_Pcs
+
+plot_metrics_pcs <- readRDS("plot_metrics_pcs.rds")
+
+plot_metrics_pcs
+
+```
+
+\elandscape

### 2021-05-21 Supplementary_Material/Regression_Trees_All.Rmd
Plots with regression trees

---
title: ""
output:
  pdf_document: default
  html_document: default

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=17, fig.width=12}

########################################################################################################################################################
#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
########################################################################################################################################################
#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)

library(rpart.plot)
library(rpart)

setwd("~/R_Projects/Reproductive Traits")

v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")

#run  regression trees of the 3 metrics
set.seed(1)
tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0089891)

set.seed(1)
tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0159034)

set.seed(1)
tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0147899)

#NECTAR AND POLEN DATA
v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")

#Set correct colnames for plotting
colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")

colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")

colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")

set.seed(2)
tree1 <- rpart(Visits~., data=v_df, cp=0.0131325) #6 splits is lower than the best tree plus on sd (rule of thumb for selecting trees)

set.seed(2)
tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0109066) #6node divisons it is within on sd + error of best tree

set.seed(2)
tree3 <- rpart(Specialization~., data=d_df, cp=0.0147899) #7node divisons

par(mfrow=c(3,2))

rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency for all species", cex.main=1.75,tweak = 1.30) 
rpart.plot(tree_1, box.palette="GnOr", main="(b) Interaction frequency for subset with floral rewards", cex.main=1.75,tweak = 1.30)

rpart.plot(tree2, box.palette="GnOr", main="(c) Normalized degree for all with species", cex.main=1.75,tweak = 1.30)
rpart.plot(tree_2, box.palette="GnOr", main="(d) Normalized degree for subset with floral rewards", cex.main=1.75,tweak = 1.30)

rpart.plot(tree3, box.palette="GnOr", main="(e) Specialization for all species", cex.main=1.75,tweak = 1.30)
rpart.plot(tree_3, box.palette="GnOr", main="(f) Specialization for subset with floral rewards", cex.main=1.75,tweak = 1.30)

```

### 2021-05-21 Supplementary_Material/Regression_Trees_Subset_Nectar_Pollen.Rmd
Plots with regression trees

--- 2021-05-21 Supplementary_Material/Regression_Trees_All.Rmd
@@
   html_document: default
-
 ---
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=17, fig.width=12}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=9, fig.width=11}
 
@@
 
-v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
-nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
-d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")
-
-#run  regression trees of the 3 metrics
-set.seed(1)
-tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0089891)
-
-set.seed(1)
-tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0159034)
-
-set.seed(1)
-tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0147899)
-
-#NECTAR AND POLEN DATA
 v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
@@
 
-par(mfrow=c(3,2))
-
-rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency for all species", cex.main=1.75,tweak = 1.30) 
-rpart.plot(tree_1, box.palette="GnOr", main="(b) Interaction frequency for subset with floral rewards", cex.main=1.75,tweak = 1.30)
-
-rpart.plot(tree2, box.palette="GnOr", main="(c) Normalized degree for all with species", cex.main=1.75,tweak = 1.30)
-rpart.plot(tree_2, box.palette="GnOr", main="(d) Normalized degree for subset with floral rewards", cex.main=1.75,tweak = 1.30)
-
-rpart.plot(tree3, box.palette="GnOr", main="(e) Specialization for all species", cex.main=1.75,tweak = 1.30)
-rpart.plot(tree_3, box.palette="GnOr", main="(f) Specialization for subset with floral rewards", cex.main=1.75,tweak = 1.30)
+rpart.plot(tree1, box.palette="GnOr", main="Interaction frequency", cex.main=2,tweak = 1.20) 
+rpart.plot(tree2, box.palette="GnOr", main="Normalized degree", cex.main=2,tweak = 1.20)
+rpart.plot(tree3, box.palette="GnOr", main="Specialization", cex.main=2,tweak = 1.20)
 

### 2021-05-21 Supplementary_Material/Supplementary_Material.Rmd
Plots with regression trees

@@
 
+__Appendix S1.__ Brief description of the different traits and categories compiled in this study divided in reproductive, floral and vegetative traits.
+
 __Table S1.__ List of the 28 plant-pollinator studies used to build the plant trait database.
@@
 __Figure S8__  Sum of visits per plant, normalized degree and specialization modelled in function of the first three main axes of trait variation.
+
+\newpage
+
+__Appendix S1__
+
+Brief description of the different traits and categories compiled in this study divided in reproductive, floral and vegetative traits.
+
+_Reproductive traits_
+
+-	Breeding system: The different plant species were classified in hermaphrodite, dioecious and monoecious species.
+Intermediate breeding systems or more complex ones were also annotated but all the species were divided into these three main categories for simplicity of the analysis.
+
+-	Selfing level: We recorded the selfing level of the different species with both quantitative and qualitative data.
+The qualitative data was divided in four main categories, high selfers, medium selfers, low selfers and none which was for the species that were unable to self-pollinate.
+In addition, quantitative data was also divided into these four categories with the following criteria: from 0% to lower than 1% ‘none’, from 1% to 25% ‘low’, from 26% to 75% ‘medium’ and from 76% to 100%  ‘high’.
+We opted for the metric of autonomous selfing because it was the most abundant one in the literature and more complex metrics that were more informative were scarce.
+
+-	Compatibility system: The different species were divided in three main categories in order to know their ability to self-pollinate.
+These categories were self-compatible, partially self-compatible and self-incompatible species.
+The field of selfing level is partly complementary to the compatibility system but is important to note that not all the self-compatible species or partially self-compatible species will self-pollinate.
+
+_Floral traits_
+
+-	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape.
+We divided the flowers in 8 main different categories: open, tube, campanulate, funnelform, papilionaceous, spike and capitulum.
+See image X for the different flower morphologies.
+
+-	Flower symmetry: We also recorded if the flowers were bilaterally symmetrical “zygomorphic” or were radially symmetrical “actinomorphic”.
+
+-	Flower and inflorescence size: We searched for flower length and flower and inflorescence width (mm) for all species.
+When possible, we calculated the not found measurements with the help of online images and  the software ImageJ.
+
+-	Flower number per plant: We compiled information about the number of flowers per plant for all species.
+However, this field was rare to find and we also used online images of the different species in order to calculate rough numbers of flowers per plant.
+We referenced all the filled fields in order to be able to follow the images that were used for these counts.
+It is important to note, that these numbers are not pretended to be the exact number of flowers per species but an approximate indicator of the reproductive investment for the different species that allow the macroecological analysis of this field.
+
+-	Ovule number: We searched for the number of ovules per flower for all the different species.
+The number of ovules of Asteraceae species are considered as the total number of ovules per capitulum.
+Many species were filled by genus or family level because the number of ovules in this taxonomic groups is considered to be mostly constant (e.g., Lamiaceae Boraginaceae or Apiaceae).
+
+-	Style length: The length of the style (mm) of the different species was also included. When possible, we calculated style length from images and illustrations on the online floras.
+
+- Nectar provision: We recorded the presence and absence of nectar for all species.
+In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration.
+In general terms, nectar data was rarely present and we try to minimise the loss of information by filling some species at family level.
+For instance, Solanaceae species are described as nectarless, and species that belonged to this family were recorded with ‘absence’ of nectar.
+
+- Pollen grains per flower: We recorded pollen grains per flower for all species but this field was rarely described in the literature.
+When just the pollen:ovule ratio was found we converted it back to pollen grains by multiplying by ovule number.
+
+_Vegetative traits_
+
+- Life form, life span and plant height: We divided the different plant species in 4 main categories: herbs, vines, shrubs and trees.
+Moreover, we also divided the species between short-lived species (annual, biennial and short-lived perennials) and perennial species (long-lived).
+Finally, we also searched for the average height (m) of the different species and annotated the maximum and minimum height when possible.
+We conducted the average between the maximum and minimum height to get an approximate average height of the species when the average was not indicated.
 

### 2021-05-21 Scripts/Regression_Tree.R

@@ -1,6 +1,10 @@
 ########################################################################################################################################################
 #SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
 ########################################################################################################################################################
+
+library(rpart)
+library(rpart.plot)
+
 #READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
 long_d <- read.csv("Data/Csv/long_format_quantitative_networks.csv", row.names = 1) #quantitative network data|weighted by frequency of visits per plant species
 
@@ -22,53 +26,46 @@ colnames(forest_data)[1] <- "Plant_species"
 #MERGE DATA
 data <- merge(long_d_2, forest_data, by="Plant_species")
 nrow(data)
-#SELECT COLUMNS WITH QUANTITATIVE INFORMATION
+
+
+########################################################################################################################################################
+#VISITATION DATA REGRESSION TREE
+########################################################################################################################################################
 data_1 <- data[c("Interaction","Autonomous_selfing_level_fruit_set","Corolla_diameter_mean","Corolla_length_mean",
                  "Flowers_per_plant","Style_length","Ovule_number","Plant_height_mean_m","Nectar_concentration",
                  "Nectar_mg","Nectar_ul","Pollen_per_flower")]
 
+#Set colnames for plotting
+colnames(data_1) <- c("Interactions", "Aut. selfing", "Flower width","Flower length" , "Flowers per plant","Style length (mm)",
+                      "Ovule number","Plant height (m)", "Nectar_concentration","Mg of nectar","Microlitres of nectar","Pollen_per_flower")
+
+
+#Visitation data regression tree
+data_1$Interactions <- log10(data_1$Interactions+1) #Log transform to be able to run the tree with low error, it doesnt like non-normal dist
+
+# Create the decision tree model
+tree <- rpart(Interactions~., data=data_1, cp=.001)
+
+#check number of splits and error
+printcp(tree)
+plotcp(tree)
+
+#select optimal value for plotting cp=0.0043638, 10 splits
+tree <- rpart(Interactions~., data=data_1, cp=0.0043638)
+
+# Visualize the decision tree with green-orange pattern of color with rpart.plot
+rpart.plot(tree, box.palette="GnOr")
[…]

### 2021-05-21 Scripts/Regression_Tree_All.R

@@ -173,67 +173,81 @@ datitos_2 <- as.data.frame(datitos_1)
 
 #Now quantitative variables
 ########################################################################################################################################################
-#Visits quantitative 
+#VISITS REGRESSION TREE
 ########################################################################################################################################################
-df <- datitos_2[c("Visits", "Autonomous_selfing_level_fruit_set","Flowers_per_plant","Corolla_diameter_mean", "Style_length","Ovule_number",
+v_df_all <- datitos_2[c("Visits", "Autonomous_selfing_level_fruit_set","Flowers_per_plant","Corolla_diameter_mean", "Style_length","Ovule_number",
                   "Plant_height_mean_m")]
 
 
-tree <- rpart(Visits~., data=df, cp=0.001)
-printcp(tree)
-plotcp(tree)
-tree <- rpart(Visits~., data=df, cp=0.0077368)
-rpart.plot(tree, box.palette="GnOr")
-
-df <- df[c("Visits", "Autonomous_selfing_level_fruit_set","Flowers_per_plant","Corolla_diameter_mean","Style_length","Ovule_number",
-           "Plant_height_mean_m","Nectar_ul","Nectar_mg","Nectar_concentration", "Pollen_per_flower")]
+colnames(v_df_all) <- c("Visits", "Aut. selfing","Flowers per plant","Flower width", "Style length (mm)","Ovule number",
+                                  "Plant height (m)")
 
 
-tree <- rpart(Visits~., data=df, cp=0.0086964) #8 divisions
-rpart.plot(tree, box.palette="GnOr")
+
+v_df_all$Visits <- log10(v_df_all$Visits + 1)
+
+set.seed(1)
+tree <- rpart(Visits~., data=v_df_all, cp=0.001)
 printcp(tree)
 plotcp(tree)
 
-
-#Alternative method with poissot and lower error
-#Root node error is quite high
-
-tree <- rpart(Visits~., data=df, cp=0.016487,method = "poisson")
-printcp(tree)
-rpart.plot(tree, box.palette="GnOr", extra=100)
-
+set.seed(1)
+tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0089891)
+rpart.plot(tree_1, box.palette="GnOr")
 
 ########################################################################################################################################################
-#Visits qualitative
+#NORMALIZED DEGREE REGRESSION TREE
[…]

### 2021-05-21 Supplementary_Material/Regression_Trees_All.Rmd
edits

@@
 
-rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency for all species", cex.main=1.75,tweak = 1.30) 
-rpart.plot(tree_1, box.palette="GnOr", main="(b) Interaction frequency for subset with floral rewards", cex.main=1.75,tweak = 1.30)
+rpart.plot(tree_1, box.palette="GnOr", main="(a) Interaction frequency for all species", cex.main=1.75,tweak = 1.30) 
+rpart.plot(tree1, box.palette="GnOr", main="(b) Interaction frequency for subset with floral rewards", cex.main=1.75,tweak = 1.30)
 
-rpart.plot(tree2, box.palette="GnOr", main="(c) Normalized degree for all with species", cex.main=1.75,tweak = 1.30)
-rpart.plot(tree_2, box.palette="GnOr", main="(d) Normalized degree for subset with floral rewards", cex.main=1.75,tweak = 1.30)
+rpart.plot(tree_2, box.palette="GnOr", main="(c) Normalized degree for all species", cex.main=1.75,tweak = 1.30)
+rpart.plot(tree2, box.palette="GnOr", main="(d) Normalized degree for subset with floral rewards", cex.main=1.75,tweak = 1.30)
 
-rpart.plot(tree3, box.palette="GnOr", main="(e) Specialization for all species", cex.main=1.75,tweak = 1.30)
-rpart.plot(tree_3, box.palette="GnOr", main="(f) Specialization for subset with floral rewards", cex.main=1.75,tweak = 1.30)
+rpart.plot(tree_3, box.palette="GnOr", main="(f) Specialization for all species", cex.main=1.75,tweak = 1.30) 
+rpart.plot(tree3, box.palette="GnOr", main="(e) Specialization for subset with floral rewards", cex.main=1.75,tweak = 1.30)
 

### 2021-05-25 Main_Figures/Analysis_1_Separated.Rmd
Edits on the supplementary material

@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("High Flower N.    Large flowers")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
-   "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila-Hymenoptera (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
+   "Non-Syrphidae-Diptera", "Syrphidae-Diptera"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
     limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids")) + ggtitle("(d)")
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
-   "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila-Hymenoptera (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
+   "Non-Syrphidae-Diptera", "Syrphidae-Diptera"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
     limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids")) + ggtitle("(e)")
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles")+
-  theme_ms() +theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
-    "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
+  theme_ms() +theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila-Hymenoptera (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
+    "Non-Syrphidae-Diptera", "Syrphidae-Diptera"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
     limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",

### 2021-05-25 Supplementary_Material/Regression_Trees_All.Rmd
Edits on the supplementary material

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=17, fig.width=12}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12}
 
@@
 
-rpart.plot(tree_1, box.palette="GnOr", main="(a) Interaction frequency for all species", cex.main=1.75,tweak = 1.30) 
-rpart.plot(tree1, box.palette="GnOr", main="(b) Interaction frequency for subset with floral rewards", cex.main=1.75,tweak = 1.30)
+rpart.plot(tree_1, box.palette="GnOr", main="(a) Interaction frequency for all species", cex.main=1.75,tweak = 1.10) 
+rpart.plot(tree1, box.palette="GnOr", main="(b) Interaction frequency for subset with floral rewards", cex.main=1.75,tweak = 1.10)
 
-rpart.plot(tree_2, box.palette="GnOr", main="(c) Normalized degree for all species", cex.main=1.75,tweak = 1.30)
-rpart.plot(tree2, box.palette="GnOr", main="(d) Normalized degree for subset with floral rewards", cex.main=1.75,tweak = 1.30)
+rpart.plot(tree_2, box.palette="GnOr", main="(c) Normalized degree for all species", cex.main=1.75,tweak = 1.10)
+rpart.plot(tree2, box.palette="GnOr", main="(d) Normalized degree for subset with floral rewards", cex.main=1.75,tweak = 1.10)
 
-rpart.plot(tree_3, box.palette="GnOr", main="(f) Specialization for all species", cex.main=1.75,tweak = 1.30) 
-rpart.plot(tree3, box.palette="GnOr", main="(e) Specialization for subset with floral rewards", cex.main=1.75,tweak = 1.30)
+rpart.plot(tree_3, box.palette="GnOr", main="(e) Specialization for all species", cex.main=1.75,tweak = 1.10) 
+rpart.plot(tree3, box.palette="GnOr", main="(f) Specialization for subset with floral rewards", cex.main=1.75,tweak = 1.10)
 

### 2021-05-25 Supplementary_Material/Regression_Trees_Subset_Nectar_Pollen.Rmd
Edits on the supplementary material

@@
   html_document: default
+classoption: landscape
+
 ---
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=9, fig.width=11}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4, fig.width=11}
 
@@
 
-rpart.plot(tree1, box.palette="GnOr", main="Interaction frequency", cex.main=2,tweak = 1.20) 
-rpart.plot(tree2, box.palette="GnOr", main="Normalized degree", cex.main=2,tweak = 1.20)
-rpart.plot(tree3, box.palette="GnOr", main="Specialization", cex.main=2,tweak = 1.20)
+par(mfrow=c(1,3))
+
+rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.5,tweak = 1) 
+rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.5,tweak = 1)
+rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.5,tweak = 0.9)
 

### 2021-05-25 Supplementary_Material/Supplementary_Material.Rmd
Edits on the supplementary material

@@
 
-__Figure S4__ Trait relationship of PC1 and PC3 with the phylogenetic informed principal component analysis with the full set of species.
-
-__Figure S5__ Phylogenetic informed principal component analysis for the imputed dataset of the subset of species with quantitative information of nectar and pollen.
-
-__Figure S6__ Fitted posterior estimates of the number of visits made by the main functional groups of bees on the main axes of trait variation.
+__Figure S4__ Regression tree comparison between the regression trees with the full set of species and with the subset of species with floral rewards.
+
+__Figure S5__ Trait relationship of PC1 and PC3 with the phylogenetic informed principal component analysis with the full set of species.
+
+__Figure S6__ Phylogenetic informed principal component analysis for the imputed dataset of the subset of species with quantitative information of nectar and pollen.
 
@@
 
-__Figure S8__  Sum of visits per plant, normalized degree and specialization modelled in function of the first three main axes of trait variation.
+__Figure S8__ Fitted posterior estimates of the number of visits made by the main functional groups of bees on the main axes of trait variation.
+
+__Figure S9__  Sum of visits per plant, normalized degree and specialization modelled in function of the first three main axes of trait variation.
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig S4.} Phylogenetically informed principal component analysis showing the trait relationship with principal components one and three (PC1 and PC3) for the full set of species (N = 1,506)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig S4.} Comparison of the regression tree analysis between the full set of species and the subset of species with floral rewards for each plant species level metric (interaction frequency, nomalized degree and specialization)."}
+
+########################################################################################################################################################
+#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
+########################################################################################################################################################
+#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
+
+library(rpart.plot)
+library(rpart)
+
+setwd("~/R_Projects/Reproductive Traits")
+
+v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
+nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
+d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")
+
+#run  regression trees of the 3 metrics
+set.seed(1)
+tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0089891)
+
+set.seed(1)
+tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0159034)
+
+set.seed(1)
+tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0147899)
+
+#NECTAR AND POLEN DATA
+v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
+nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
+d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
+
+#Set correct colnames for plotting
+colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")
+
+colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")
+
+colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")
+
+set.seed(2)
+tree1 <- rpart(Visits~., data=v_df, cp=0.0131325) #6 splits is lower than the best tree plus on sd (rule of thumb for selecting trees)
+
+set.seed(2)
+tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0109066) #6node divisons it is within on sd + error of best tree
+
+set.seed(2)
+tree3 <- rpart(Specialization~., data=d_df, cp=0.0147899) #7node divisons
+
+par(mfrow=c(3,2))
+
+rpart.plot(tree_1, box.palette="GnOr", main="(a) Interaction frequency for all species", cex.main=1.75,tweak = 1.10) 
+rpart.plot(tree1, box.palette="GnOr", main="(b) Interaction frequency for subset with floral rewards", cex.main=1.75,tweak = 1.10)
+
+rpart.plot(tree_2, box.palette="GnOr", main="(c) Normalized degree for all species", cex.main=1.75,tweak = 1.10)
+rpart.plot(tree2, box.palette="GnOr", main="(d) Normalized degree for subset with floral rewards", cex.main=1.75,tweak = 1.10)
+
+rpart.plot(tree_3, box.palette="GnOr", main="(e) Specialization for all species", cex.main=1.75,tweak = 1.10) 
+rpart.plot(tree3, box.palette="GnOr", main="(f) Specialization for subset with floral rewards", cex.main=1.75,tweak = 1.10)
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig S5.} Phylogenetically informed principal component analysis showing the trait relationship with principal components one and three (PC1 and PC3) for the full set of species (N = 1,506)."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig S5.} First two main principal components from the phylogenetic informed principal component analysis for the imputed dataset of the subset of species with quantitative information of nectar and pollen (N = 467)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig S6.} First two main principal components from the phylogenetic informed principal component analysis for the imputed dataset of the subset of species with quantitative information of nectar and pollen (N = 467)."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
+\newpage
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig S7.} Statistical comparison of the different categories of the categorical traits on the main two axes of trait variation (pPCA with the full set of species).
+Categories that differ significantly are denoted with a different letter."}
+
+########################################################################################################################################################
+#CORRELATION BETWEEN QUALITATIVE VARIABLES AND PC's
+########################################################################################################################################################
+#NOTES
+#I did not include the qualitative variables when I prepare the data for the PPCA
+#So I have to recalculate the ata here with the qualitative variables
+########################################################################################################################################################
+#LOAD LIBRARIES
+library(emmeans)
+library(ggplot2)
+library(patchwork)
+library(dplyr)
+
+theme_ms <- function(base_size=10, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(1.3)),
+           axis.text=element_text(size = rel(1.1), color = "black"),
+           panel.border=element_rect(color="black",size=1.2),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank(),
+           legend.position = "none",
+           plot.title = element_text(face = "bold",size = rel(1.45)),
+           plot.subtitle = element_text(face = "bold",size = rel(1.3))
+     ))
+}
+
+########################################################################################################################################################
+setwd("~/R_Projects/Reproductive Traits")
+
+#LOAD DATA
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+dat <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
+########################################################################################################################################################
+#remove not found species, cannot do PCA with unequal numbers of rows
+cols.num <- c("Family_all","Genus_all","Species_all")
+dat[cols.num] <- sapply(dat[cols.num],as.character)
+dat$Species_all <- gsub("Species_all_", "", dat$Species_all)
+########################################################################################################################################################
+#3) REMOVE OUTLIERS, OUT OF 2.5-97.5 RANGE WHICH HELPS IMPUTATION PROCESS. SEE ARTICLE FOR REF.
+########################################################################################################################################################
+dat_cleaning <- dat[,]
+#CHECK LEVELS
+
+dat_cleaning_1 <- dat_cleaning %>%
+  filter(between(Flowers_per_plant, quantile(Flowers_per_plant, 0.025), quantile(Flowers_per_plant, 0.975)))
+
+dat_cleaning_2 <- dat_cleaning_1 %>%
+  filter(between(Corolla_diameter_mean, quantile(Corolla_diameter_mean, 0.025), quantile(Corolla_diameter_mean, 0.975)))
+
+dat_cleaning_3 <- dat_cleaning_2 %>%
+  filter(between(Style_length, quantile(Style_length, 0.025), quantile(Style_length, 0.975)))
+
+dat_cleaning_4 <- dat_cleaning_3 %>%
+  filter(between(Ovule_number, quantile(Ovule_number, 0.025), quantile(Ovule_number, 0.975)))
+
+dat_cleaning_5 <- dat_cleaning_4 %>%
+  filter(between(Plant_height_mean_m, quantile(Plant_height_mean_m, 0.025), quantile(Plant_height_mean_m, 0.975)))
+
+final_d <- dat_cleaning_5[,]
+
+pca_data <- as.data.frame(phyl_pca_forest$S)
+
+d <- cbind(final_d, pca_data)
+
+#Prepare qualitative variables
+d$Compatibility_system[d$Compatibility_system=="dioecious"] <- "Unisexual flowers"
+d$Compatibility_system[d$Compatibility_system=="monoecious"] <- "Unisexual flowers"
+d$Compatibility_system[d$Compatibility_system=="partially_self_compatible"] <- "Partially self compatible"
+d$Compatibility_system[d$Compatibility_system=="self_compatible"] <- "Self compatible"
+d$Compatibility_system[d$Compatibility_system=="self_incompatible"] <- "Self incompatible"
+d$Compatibility_system <- factor(d$Compatibility_system, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
+
+d$life_form[d$life_form=="herb"] <- "Herb"
+d$life_form[d$life_form=="shrub"] <- "Shrub"
+d$life_form[d$life_form=="tree"] <- "Tree"
+d$life_form[d$life_form=="vine"] <- "Shrub"
+
+d$Flower_symmetry[d$Flower_symmetry=="actinomorphic"] <- "Actinomorphic"
+d$Flower_symmetry[d$Flower_symmetry=="zygomorphic"] <- "Zygomorphic"
+
+d$Flower_symmetry[d$Flower_symmetry=="Funnelform"] <- "Campanulate"
+d$Flower_symmetry[d$Flower_symmetry=="Spike"] <- "Brush"
+
+d$Flower_morphology[d$Flower_morphology=="Funnelform"] <- "Campanulate"
+d$Flower_morphology[d$Flower_morphology=="Spike"] <- "Brush"
+
+d$Nectar_presence_absence[d$Nectar_presence_absence=="yes"] <- "Yes"
+d$Nectar_presence_absence[d$Nectar_presence_absence=="no"] <- "No"
+
+#The other qualitative are ok
+
+#All principal components are normally distributed
+#Convert to factor before running model
+d[sapply(d, is.character)] <- lapply(d[sapply(d, is.character)], as.factor)
+
+#Run model
+model1 <- lm(PC1 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
+model2 <- lm(PC2 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
+
+####################################################################################################################################################################################################################################
+#1) BREEDING SYSTEM
+####################################################################################################################################################################################################################################
+model_breeding_1 <- emmeans(model1, "Breeding_system")
+breeding_1 <- as.data.frame(model_breeding_1[1:3])
+breed1 <- multcomp::cld(model_breeding_1, alpha = 0.10, Letters = LETTERS)
+
+breed_1 <- ggplot(breed1,aes(x= Breeding_system,y= emmean,
+               label = .group)) +theme_minimal()+
+  geom_point(data = breed1, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
+                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "(a) Breeding system")+
+  theme(plot.title = element_text(hjust=0.5, size=25, face="bold"))+
+  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
+
+model_breeding_2 <- emmeans(model2, "Breeding_system")
+breeding_2 <- as.data.frame(model_breeding_2[1:3])
+breed2 <- multcomp::cld(model_breeding_2, alpha = 0.10, Letters = LETTERS)
+
+breed_2 <- ggplot(breed2,aes(x= Breeding_system,y= emmean,
+             label = .group)) +theme_minimal()+
+  geom_point(data = breed2, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
+                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "(b) Breeding system")+
+  theme(plot.title = element_text(hjust=0.5,size=25, face="bold") )+
+  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
+
+########################################################################################################################################################
+#2) COMPATIBILITY
+########################################################################################################################################################
+model_com <- emmeans(model1, "Compatibility_system")
+
+d <- as.data.frame(model_com[1:4])
+comp1 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
+
+comp_1 <- ggplot(comp1,aes(x= Compatibility_system,y= emmean,
+  label = .group)) +theme_minimal()+
+  geom_point(data = comp1, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
+  width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(c) Compatibility system")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
+
+model_com <- emmeans(model2, "Compatibility_system")
+d <- as.data.frame(model_com[1:4])
+comp2 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
+
+comp_2 <- ggplot(comp2,aes(x= Compatibility_system,y= emmean,
+  label = .group)) +theme_minimal()+
+  geom_point(data = comp2, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
+  width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(d) Compatibility system")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
+
+########################################################################################################################################################
+#3) LIFESPAN
+########################################################################################################################################################
+model_lif_1 <- emmeans(model1, "lifespan")
+lif_1 <- as.data.frame(model_lif_1[1:2])
+lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
+
+lifespan_1 <- ggplot(lif_1,aes(x= lifespan,y= emmean,
+             label = .group)) +theme_minimal()+
+  geom_point(data = lif_1, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
+                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "(e) Lifespan")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
+
+model_lif_2 <- emmeans(model2, "lifespan")
+lif_2 <- as.data.frame(model_lif_2[1:2])
+lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
+
+lifespan_2 <- ggplot(lif_2,aes(x= lifespan,y= emmean,
+                 label = .group)) +theme_minimal()+
+  geom_point(data = lif_2, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
+                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "(f) Lifespan")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")
+
+########################################################################################################################################################
+# 4) LIFE FORM
+########################################################################################################################################################
+
+model_lif_1 <- emmeans(model1, "life_form")
+lif_1 <- as.data.frame(model_lif_1[1:3])
+lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
+
+lifeform_1 <- ggplot(lif_1,aes(x= life_form,y= emmean,
+                 label = .group)) +theme_minimal()+
+  geom_point(data = lif_1, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
+                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "(g) Life form")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
+
+model_lif_2 <- emmeans(model2, "life_form")
+lif_2 <- as.data.frame(model_lif_2[1:3])
+lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
+
+lifeform_2 <- ggplot(lif_2,aes(x= life_form,y= emmean,
+                 label = .group)) +theme_minimal()+
+  geom_point(data = lif_2, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
+                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "(h) Life form")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
+
+########################################################################################################################################################
+# 5) FLOWER MORPHOLOGY
+########################################################################################################################################################
+model_flo_1 <- emmeans(model1, "Flower_morphology")
+flo_1 <- as.data.frame(model_flo_1[1:6])
+flo_1 <- multcomp::cld(model_flo_1, alpha = 0.10, Letters = LETTERS)
+
+shape_1 <- ggplot(flo_1,aes(x= Flower_morphology,y= emmean,
+                 label = .group)) +theme_minimal()+
+  geom_point(data = flo_1, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
+                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(i) Flower shape")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")
+
+model_flo_2 <- emmeans(model2, "Flower_morphology")
+flo_2 <- as.data.frame(model_flo_2[1:6])
+flo_2 <- multcomp::cld(model_flo_2, alpha = 0.10, Letters = LETTERS)
+
+shape_2 <- ggplot(flo_2,aes(x= Flower_morphology,y= emmean,
+                 label = .group)) +theme_minimal()+
+  geom_point(data = flo_2, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
+                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(j) Flower shape")+
+   geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
+
+########################################################################################################################################################
+#6) FLOWER SYMMETRY
+########################################################################################################################################################
+model_flo_sym_1 <- emmeans(model1, "Flower_symmetry")
+flo_sym_1 <- as.data.frame(model_flo_sym_1[1:2])
+flo_sym_1 <- multcomp::cld(model_flo_sym_1, alpha = 0.10, Letters = LETTERS)
+
+symmetry_1 <-ggplot(flo_sym_1,aes(x= Flower_symmetry,y= emmean,
+                 label = .group)) +theme_minimal()+
+  geom_point(data = flo_sym_1, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
+                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "(k) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
+
+model_flo_sym_2 <- emmeans(model2, "Flower_symmetry")
+flo_sym_2 <- as.data.frame(model_flo_sym_2[1:2])
+flo_sym_2 <- multcomp::cld(model_flo_sym_2, alpha = 0.10, Letters = LETTERS)
+
+symmetry_2 <- ggplot(flo_sym_2,aes(x= Flower_symmetry,y= emmean,
+                     label = .group)) +theme_minimal()+
+  geom_point(data = flo_sym_2, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
+                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("sienna2","purple"))+labs(title = "(l) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
+
+########################################################################################################################################################
+#7) NECTAR
+########################################################################################################################################################
+model_nec <- emmeans(model1, "Nectar_presence_absence")
+
+model_nec_1 <- emmeans(model1, "Nectar_presence_absence")
+nec_1 <- as.data.frame(model_nec_1[1:2])
+nec_1 <- multcomp::cld(model_nec_1, alpha = 0.10, Letters = LETTERS)
+
+nectar_1 <- ggplot(nec_1,aes(x= Nectar_presence_absence,y= emmean,
+                     label = .group)) +theme_minimal()+
+  geom_point(data = nec_1, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
+                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("black","grey"))+labs(title = "(m) Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
+
+model_nec_2 <- emmeans(model2, "Nectar_presence_absence")
+nec_2 <- as.data.frame(model_nec_2[1:2])
+nec_2 <- multcomp::cld(model_nec_2, alpha = 0.10, Letters = LETTERS)
+
+nectar_2 <-ggplot(nec_2,aes(x= Nectar_presence_absence,y= emmean,
+                     label = .group)) +theme_minimal()+
+  geom_point(data = nec_2, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
+                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
+  scale_color_manual(values=c("black","grey"))+labs(title = "(n) Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")
+
+#PLOT!
+
+breed_1 + breed_2+ comp_1+ comp_2+ lifespan_1+ lifespan_2+ lifeform_1+ lifeform_2+ shape_1+ shape_2+
+symmetry_1+ symmetry_2+ nectar_1+ nectar_2 + plot_layout(ncol = 2)
+
+```
+
 \blandscape
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="\\textbf{Fig S6.} Fitted posterior estimates of the number of visits made by the different main visiting families of bees (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) in relation to the main axes of trait variation (PC1, PC2 and PC3).
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="\\textbf{Fig S8.} Fitted posterior estimates of the number of visits made by the different main visiting families of bees (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) in relation to the main axes of trait variation (PC1, PC2 and PC3).
 We omitted in the plotting points over percentile 95 \\% percent due to extreme outliers."}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig S7.} Statistical comparison of the different categories of the categorical traits on the main two axes of trait variation (pPCA with the full set of species).
-Categories that differ significantly are denoted with a different letter."}
-
-########################################################################################################################################################
-#CORRELATION BETWEEN QUALITATIVE VARIABLES AND PC's
-########################################################################################################################################################
-#NOTES
-#I did not include the qualitative variables when I prepare the data for the PPCA
-#So I have to recalculate the ata here with the qualitative variables
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(emmeans)
-library(ggplot2)
-library(patchwork)
-library(dplyr)
-
-theme_ms <- function(base_size=10, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(1.3)),
-           axis.text=element_text(size = rel(1.1), color = "black"),
-           panel.border=element_rect(color="black",size=1.2),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           legend.position = "none",
-           plot.title = element_text(face = "bold",size = rel(1.45)),
-           plot.subtitle = element_text(face = "bold",size = rel(1.3))
-     ))
-}
-
-########################################################################################################################################################
-setwd("~/R_Projects/Reproductive Traits")
-
-#LOAD DATA
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-dat <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-########################################################################################################################################################
-#remove not found species, cannot do PCA with unequal numbers of rows
-cols.num <- c("Family_all","Genus_all","Species_all")
-dat[cols.num] <- sapply(dat[cols.num],as.character)
-dat$Species_all <- gsub("Species_all_", "", dat$Species_all)
-########################################################################################################################################################
-#3) REMOVE OUTLIERS, OUT OF 2.5-97.5 RANGE WHICH HELPS IMPUTATION PROCESS. SEE ARTICLE FOR REF.
-########################################################################################################################################################
-dat_cleaning <- dat[,]
-#CHECK LEVELS
-
-dat_cleaning_1 <- dat_cleaning %>%
-  filter(between(Flowers_per_plant, quantile(Flowers_per_plant, 0.025), quantile(Flowers_per_plant, 0.975)))
-
-dat_cleaning_2 <- dat_cleaning_1 %>%
-  filter(between(Corolla_diameter_mean, quantile(Corolla_diameter_mean, 0.025), quantile(Corolla_diameter_mean, 0.975)))
-
-dat_cleaning_3 <- dat_cleaning_2 %>%
-  filter(between(Style_length, quantile(Style_length, 0.025), quantile(Style_length, 0.975)))
-
-dat_cleaning_4 <- dat_cleaning_3 %>%
-  filter(between(Ovule_number, quantile(Ovule_number, 0.025), quantile(Ovule_number, 0.975)))
-
-dat_cleaning_5 <- dat_cleaning_4 %>%
-  filter(between(Plant_height_mean_m, quantile(Plant_height_mean_m, 0.025), quantile(Plant_height_mean_m, 0.975)))
-
-final_d <- dat_cleaning_5[,]
-
-pca_data <- as.data.frame(phyl_pca_forest$S)
-
-d <- cbind(final_d, pca_data)
-
-#Prepare qualitative variables
-d$Compatibility_system[d$Compatibility_system=="dioecious"] <- "Unisexual flowers"
-d$Compatibility_system[d$Compatibility_system=="monoecious"] <- "Unisexual flowers"
-d$Compatibility_system[d$Compatibility_system=="partially_self_compatible"] <- "Partially self compatible"
-d$Compatibility_system[d$Compatibility_system=="self_compatible"] <- "Self compatible"
-d$Compatibility_system[d$Compatibility_system=="self_incompatible"] <- "Self incompatible"
-d$Compatibility_system <- factor(d$Compatibility_system, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-d$life_form[d$life_form=="herb"] <- "Herb"
-d$life_form[d$life_form=="shrub"] <- "Shrub"
-d$life_form[d$life_form=="tree"] <- "Tree"
-d$life_form[d$life_form=="vine"] <- "Shrub"
-
-d$Flower_symmetry[d$Flower_symmetry=="actinomorphic"] <- "Actinomorphic"
-d$Flower_symmetry[d$Flower_symmetry=="zygomorphic"] <- "Zygomorphic"
-
-d$Flower_symmetry[d$Flower_symmetry=="Funnelform"] <- "Campanulate"
-d$Flower_symmetry[d$Flower_symmetry=="Spike"] <- "Brush"
-
-d$Flower_morphology[d$Flower_morphology=="Funnelform"] <- "Campanulate"
-d$Flower_morphology[d$Flower_morphology=="Spike"] <- "Brush"
-
-d$Nectar_presence_absence[d$Nectar_presence_absence=="yes"] <- "Yes"
-d$Nectar_presence_absence[d$Nectar_presence_absence=="no"] <- "No"
-
-#The other qualitative are ok
-
-#All principal components are normally distributed
-#Convert to factor before running model
-d[sapply(d, is.character)] <- lapply(d[sapply(d, is.character)], as.factor)
-
-#Run model
-model1 <- lm(PC1 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
-model2 <- lm(PC2 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
-
-####################################################################################################################################################################################################################################
-#1) BREEDING SYSTEM
-####################################################################################################################################################################################################################################
-model_breeding_1 <- emmeans(model1, "Breeding_system")
-breeding_1 <- as.data.frame(model_breeding_1[1:3])
-breed1 <- multcomp::cld(model_breeding_1, alpha = 0.10, Letters = LETTERS)
-
-breed_1 <- ggplot(breed1,aes(x= Breeding_system,y= emmean,
-               label = .group)) +theme_minimal()+
-  geom_point(data = breed1, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "(a) Breeding system")+
-  theme(plot.title = element_text(hjust=0.5, size=25, face="bold"))+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-model_breeding_2 <- emmeans(model2, "Breeding_system")
-breeding_2 <- as.data.frame(model_breeding_2[1:3])
-breed2 <- multcomp::cld(model_breeding_2, alpha = 0.10, Letters = LETTERS)
-
-breed_2 <- ggplot(breed2,aes(x= Breeding_system,y= emmean,
-             label = .group)) +theme_minimal()+
-  geom_point(data = breed2, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "(b) Breeding system")+
-  theme(plot.title = element_text(hjust=0.5,size=25, face="bold") )+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-########################################################################################################################################################
-#2) COMPATIBILITY
-########################################################################################################################################################
-model_com <- emmeans(model1, "Compatibility_system")
-
-d <- as.data.frame(model_com[1:4])
-comp1 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
-
-comp_1 <- ggplot(comp1,aes(x= Compatibility_system,y= emmean,
-  label = .group)) +theme_minimal()+
-  geom_point(data = comp1, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
-  width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(c) Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
-
-model_com <- emmeans(model2, "Compatibility_system")
-d <- as.data.frame(model_com[1:4])
-comp2 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
-
-comp_2 <- ggplot(comp2,aes(x= Compatibility_system,y= emmean,
-  label = .group)) +theme_minimal()+
-  geom_point(data = comp2, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
-  width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(d) Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
-
-########################################################################################################################################################
-#3) LIFESPAN
-########################################################################################################################################################
-model_lif_1 <- emmeans(model1, "lifespan")
-lif_1 <- as.data.frame(model_lif_1[1:2])
-lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
-
-lifespan_1 <- ggplot(lif_1,aes(x= lifespan,y= emmean,
-             label = .group)) +theme_minimal()+
-  geom_point(data = lif_1, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "(e) Lifespan")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-model_lif_2 <- emmeans(model2, "lifespan")
-lif_2 <- as.data.frame(model_lif_2[1:2])
-lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
-
-lifespan_2 <- ggplot(lif_2,aes(x= lifespan,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_2, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "(f) Lifespan")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")
-
-########################################################################################################################################################
-# 4) LIFE FORM
-########################################################################################################################################################
-
-model_lif_1 <- emmeans(model1, "life_form")
-lif_1 <- as.data.frame(model_lif_1[1:3])
-lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
-
-lifeform_1 <- ggplot(lif_1,aes(x= life_form,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_1, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "(g) Life form")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-model_lif_2 <- emmeans(model2, "life_form")
-lif_2 <- as.data.frame(model_lif_2[1:3])
-lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
-
-lifeform_2 <- ggplot(lif_2,aes(x= life_form,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_2, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "(h) Life form")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-########################################################################################################################################################
-# 5) FLOWER MORPHOLOGY
-########################################################################################################################################################
-model_flo_1 <- emmeans(model1, "Flower_morphology")
-flo_1 <- as.data.frame(model_flo_1[1:6])
-flo_1 <- multcomp::cld(model_flo_1, alpha = 0.10, Letters = LETTERS)
-
-shape_1 <- ggplot(flo_1,aes(x= Flower_morphology,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_1, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(i) Flower shape")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")
-
-model_flo_2 <- emmeans(model2, "Flower_morphology")
-flo_2 <- as.data.frame(model_flo_2[1:6])
-flo_2 <- multcomp::cld(model_flo_2, alpha = 0.10, Letters = LETTERS)
-
-shape_2 <- ggplot(flo_2,aes(x= Flower_morphology,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_2, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(j) Flower shape")+
-   geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
-
-########################################################################################################################################################
-#6) FLOWER SYMMETRY
-########################################################################################################################################################
-model_flo_sym_1 <- emmeans(model1, "Flower_symmetry")
-flo_sym_1 <- as.data.frame(model_flo_sym_1[1:2])
-flo_sym_1 <- multcomp::cld(model_flo_sym_1, alpha = 0.10, Letters = LETTERS)
-
-symmetry_1 <-ggplot(flo_sym_1,aes(x= Flower_symmetry,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_sym_1, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "(k) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
-
-model_flo_sym_2 <- emmeans(model2, "Flower_symmetry")
-flo_sym_2 <- as.data.frame(model_flo_sym_2[1:2])
-flo_sym_2 <- multcomp::cld(model_flo_sym_2, alpha = 0.10, Letters = LETTERS)
-
-symmetry_2 <- ggplot(flo_sym_2,aes(x= Flower_symmetry,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = flo_sym_2, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title = "(l) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-########################################################################################################################################################
-#7) NECTAR
-########################################################################################################################################################
-model_nec <- emmeans(model1, "Nectar_presence_absence")
-
-model_nec_1 <- emmeans(model1, "Nectar_presence_absence")
-nec_1 <- as.data.frame(model_nec_1[1:2])
-nec_1 <- multcomp::cld(model_nec_1, alpha = 0.10, Letters = LETTERS)
-
-nectar_1 <- ggplot(nec_1,aes(x= Nectar_presence_absence,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = nec_1, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "(m) Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-model_nec_2 <- emmeans(model2, "Nectar_presence_absence")
-nec_2 <- as.data.frame(model_nec_2[1:2])
-nec_2 <- multcomp::cld(model_nec_2, alpha = 0.10, Letters = LETTERS)
-
-nectar_2 <-ggplot(nec_2,aes(x= Nectar_presence_absence,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = nec_2, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "(n) Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")
-
-#PLOT!
-
-breed_1 + breed_2+ comp_1+ comp_2+ lifespan_1+ lifespan_2+ lifeform_1+ lifeform_2+ shape_1+ shape_2+
-symmetry_1+ symmetry_2+ nectar_1+ nectar_2 + plot_layout(ncol = 2)
-
-```
-
 \blandscape
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig S8.} Sum of visits per plant, normalized degree and speciliazation modelled in function of the first three main axes of trait variation.", fig.pos= "h"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig S9.} Sum of visits per plant, normalized degree and speciliazation modelled in function of the first three main axes of trait variation.", fig.pos= "h"}
 

### 2021-06-21 Supplementary_Material/Regression_Trees_Subset_Nectar_Pollen.Rmd
updating nectar and pollen trait analyses

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4, fig.width=11}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=17.5}
 
@@
 colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
 
 colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule number","Plant height",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
 
 colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
 
 set.seed(2)
-tree1 <- rpart(Visits~., data=v_df, cp=0.0131325) #6 splits is lower than the best tree plus on sd (rule of thumb for selecting trees)
+tree1 <- rpart(Visits~., data=v_df, cp=0.0134316) #6 splits is lower than the best tree plus on sd (rule of thumb for selecting trees)
 
 set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0109066) #6node divisons it is within on sd + error of best tree
+tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0125459) #6node divisons it is within on sd + error of best tree
 
 set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0147899) #7node divisons
+tree3 <- rpart(Specialization~., data=d_df, cp=0.0190352) #7node divisons
 
@@
 
-rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.5,tweak = 1) 
-rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.5,tweak = 1)
-rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.5,tweak = 0.9)
+rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.5,tweak = 1.15,type = 2) 
+rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.5,tweak = 1.25,type = 2)
+rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.5,tweak = 1.15,type = 2)
 

### 2021-06-21 Scripts/2_1_Trait_Data_Imp_Nectar_Pollen_Subset.R

@@ -182,8 +182,10 @@ missing_data <- unlist(lapply(t_nectar_pollen, function(x) sum(is.na(x))))/nrow(
 sort(missing_data[missing_data >= 0], decreasing=T)
 
 #mg of nectar have over 30% of missing values and thus, we do not include it in the imputation
-t_nectar_pollen <- t_nectar_pollen %>% select(-Nectar_mg)
+library(tidyverse)
+t_nectar_pollen <- t_nectar_pollen %>% select(!Nectar_mg)
 
+str(t_nectar_pollen)
 
 #################################################
 #3)SUMMARY OF THE DATA|ALL COLS CONSIDERED!

### 2021-06-21 Scripts/8_Regression_Tree_Pollen_Nectar.R

@@ -176,23 +176,24 @@ df <- as.data.frame(datitos_1)
 #Visits quantitative 
 ########################################################################################################################################################
 v_df <- df[c("Visits", "Autonomous_selfing_level_fruit_set","Flowers_per_plant","Corolla_diameter_mean","Style_length","Ovule_number",
-           "Plant_height_mean_m","Nectar_ul","Nectar_mg","Nectar_concentration", "Pollen_per_flower")]
+           "Plant_height_mean_m","Nectar_ul","Nectar_concentration", "Pollen_per_flower")]
 
 
 colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                     "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")
-
+                     "Ovule number","Plant height (m)", "Microlitres of nectar", "Nectar concentration (%)","Pollen grains per flower")
 
 
 v_df$Visits <- log10(v_df$Visits+1)
 set.seed(2)
+
 tree <- rpart(Visits~., data=v_df, cp=0.009) 
+
 
 printcp(tree)
 plotcp(tree) 
 
 set.seed(2)
-tree1 <- rpart(Visits~., data=v_df, cp=0.0161026) #4 splits is lower than the best tree plus on sd (rule of thumb for selecting trees)
+tree1 <- rpart(Visits~., data=v_df, cp=0.0134316) #7 splits is lower than the best tree plus on sd (rule of thumb for selecting trees)
 rpart.plot(tree1, box.palette="GnOr")
 
 printcp(tree1)
@@ -202,10 +203,10 @@ plotcp(tree1)
 #Normalize degree
 ########################################################################################################################################################
 nd_df <- df[c("normalised.degree", "Autonomous_selfing_level_fruit_set","Flowers_per_plant","Corolla_diameter_mean","Style_length","Ovule_number",
-                  "Plant_height_mean_m","Nectar_ul","Nectar_mg","Nectar_concentration", "Pollen_per_flower")]
+                  "Plant_height_mean_m","Nectar_ul","Nectar_concentration", "Pollen_per_flower")]
 
 colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
[…]

### 2021-06-21 Scripts/Analysis_trial.R

@@ -1,306 +1,0 @@
-########################################################################################################################################################
-#SCRIPT TO PREPARE DATA FOR ANALYSIS 1) VISITS~ POLL. FUNCTIONAL GROUP*PRINCIPAL COMPONENTS
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(data.table)
-########################################################################################################################################################
-#LOAD DATA
-########################################################################################################################################################
-long_d <- read.csv("Data/Csv/long_format_quantitative_networks.csv", row.names = 1) #quantitative network data|weighted by frequency of visits per plant species
-dat_cleaning <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv") #data for PPCA
-########################################################################################################################################################
-#PREPARE DATA
-########################################################################################################################################################
-#Select data with interaction greater than 0
-long_d_1 <- long_d[long_d$Interaction>0,]
-
-#Remove other orders/guilds that are not these ones
-long_d_2 <- long_d_1[!is.na(long_d_1$guild),] #I do it by guild because just these 6 guilds are named in this column
-
-#check levels
-levels(factor(long_d_2$guild)) #9 DIFFERENT GUILDS|After I'll select the main fucntional poll. groups for analysis
-
-
-#set 1st col name
-colnames(dat_cleaning)[1] <- "Plant_species"
-
-datos <- merge(long_d_1, dat_cleaning, by.x = "Plant_species",  by.y = "Plant_species")
-
-
[…]

### 2021-06-21 Scripts/Nectar_anal_2.R

@@ -1,287 +1,0 @@
-########################################################################################################################################################
-########################################################################################################################################################
-########################################################################################################################################################
-##SCRIPT FOR ANALYSIS 
-########################################################################################################################################################
-########################################################################################################################################################
-########################################################################################################################################################
-
-#HERE I TRY TO SELECT THE MAIN EXPLANATORY TRAITS FOR EACH TRAIT 
-
-#LOAD LIBRARIES
-library(data.table) # operate with df
-library(bipartite) #calculate metrics
-library(dplyr) #data manipulation 
-library(stringr) #remove string
-library(brms)
-library(projpred)
-library(dplyr)
-library(ggplot2)
-library(bayesplot)
-library(ape)
-library(rtrees)
-library(cowplot)
-library(emmeans)
-library(tidybayes)
-library(multcomp)
-########################################################################################################################################################
-#1) LOAD NETWORK DATA
-########################################################################################################################################################
-#Set working directory to read files
-setwd("~/R_Projects/Reproductive traits/Data/Data_networks_quantitative") 
-
-#read csv files
-temp <- list.files(pattern="*.csv")
-my.list <- list(for (i in 1:length(temp)) assign(temp[i], read.csv(temp[i])))
-my_files <- list.files(pattern = "\\.csv$")
-my_data <- lapply(my_files, function(i){read.csv(i,  row.names = 1)})
-# Add id to dataframe
-names(my_data) <- stringr::str_replace(my_files, pattern = ".csv", replacement = "")
-
[…]

### 2021-06-21 Supplementary_Material/Supplementary_Material.Rmd
edits

@@
 colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
 
 colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
 
 colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
 
 set.seed(2)
-tree1 <- rpart(Visits~., data=v_df, cp=0.0131325) #6 splits is lower than the best tree plus on sd (rule of thumb for selecting trees)
+tree1 <- rpart(Visits~., data=v_df, cp=0.0134316) #6 splits is lower than the best tree plus on sd (rule of thumb for selecting trees)
 
 set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0109066) #6node divisons it is within on sd + error of best tree
+tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0125459) #6node divisons it is within on sd + error of best tree
 
 set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0147899) #7node divisons
+tree3 <- rpart(Specialization~., data=d_df, cp=0.0171878) #7node divisons
 

### 2021-06-21 Main_Figures/Traits_Table.Rmd
edits

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=14}
 setwd("~/R_Projects/Reproductive Traits")
@@
 T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-           "Presence \n Absence", "None \n Low \n Medium \n High", "Self-incomp. \n Partially self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " "),align = c("l"))
+           "Presence \n Absence", "None \n Low \n Medium \n High", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " "),align = c("l"))
 
-Type <- c("V", "F", "F", "F", "F", "F", "F","F","F","F","F","R")
+Type <- c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive")
 
-Type_1 <- c("V", "V", "F", "F", "F", "R", "R", "R","","","","")
+Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive","","","","")
 

### 2021-06-22 Supplementary_Material/Supplementary_Material.Rmd
update sup mat

@@
 
-PC$S[,1] <- -PC$S[,1]
+PC$S[,2] <- -PC$S[,2]
 
@@
   # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
 
   #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=-v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
 
@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,5.5,5.3,5.5,6.1,5.75,5.8,6)), y = (PCAloadings$PC2*c(4.8,4.8,4.65,5.65,5,5.1,5.75,5)+c(0,0,0,0,0,0,0,0)),
+  plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.85,5.5,5.3,5.5,6.1,5.75,5.8,6)), y = -(PCAloadings$PC2*c(4.8,4.8,4.65,5.65,5,5.1,5.75,5)+c(0,0,0,0,0,0,0,0)),
                           label = PCAloadings$Variables, color="black",fontface =2,size=4.5)

### 2021-06-22 Supplementary_Material/Supplementary_Material.Rmd
minor edits on supp mat.

@@
 
- kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S2.} Loadings and explained variance of the first three principal components from the phylogenetically informed principal component analysis for the full set of species (N = 1,506).") %>%
+ kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S2.} Loadings and explained variance of the first three principal components from the phylogenetically informed principal component analysis with the full set of species after outlier processing (N = 1,236).") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
@@
 
-kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S3.} Loadings and explained variance of the first three principal components from the phylogenetically informed principal component analysis for the subset of sepcies with quantitative information of nectar and pollen.") %>%
+kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S3.} Loadings and explained variance of the first three principal components from the phylogenetically informed principal component analysis for the subset of species with quantitative information of nectar and pollen.") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")

### 2021-06-23 Supplementary_Material/Supplementary_Material.Rmd
edits

@@
 nectar_ul <- readRDS("Data/RData/Nectar_ul_phylo.rds")
+
+#Not included at the end
 #Nectar mg
-nectar_mg <- readRDS("Data/RData/Nectar_mg_phylo.rds")
+#nectar_mg <- readRDS("Data/RData/Nectar_mg_phylo.rds")
 #Nectar concentration
@@
 #LABELS
-label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Nectar ($\\mu$l) per flower", "Nectar (mg) per flower", "Nectar concentration ($\\%$)","Pollen grains per flower")
+label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Nectar per flower ($\\mu$l)", "Nectar concentration ($\\%$)","Pollen grains per flower")
 #LAMBDA
-lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, nectar_ul$lambda, nectar_mg$lambda, nectar_con$lambda, pollen$lambda)
+lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, nectar_ul$lambda, nectar_con$lambda, pollen$lambda)
 #P-VALUE
-p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P,nectar_ul$P,
-            nectar_mg$P,  nectar_con$P, pollen$P)
+p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P,nectar_ul$P,  nectar_con$P, pollen$P)
 

### 2021-06-24 Supplementary_Material/Supplementary_Material.Rmd
Edits on supp mat fig s2

@@
 
-pc3 <- function(PC, x="PC1", y="PC3") {
+pc3 <- function(PC, x="PC1", y="PC2") {
   # PC being a prcomp object
@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,4.8,7.1,5.5)), y = -(PCAloadings$PC2*c(-3.2,4.5,3.75,8.4,5,5.5)+c(0,0,0,0,-0.08,0)),
+ plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,5.25,7.1,6)), y = -(PCAloadings$PC2*c(3.8,4.3,4,5,5,5.5)+c(0,0,0,0,-0.04,0)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)

### 2021-06-24 Supplementary_Material/Supplementary_Material.Rmd
edits on fig s2

--- 2021-06-23 Supplementary_Material/Supplementary_Material.Rmd
@@
 #Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+dat_cleaning_5 <- readRDS("Data/RData/data_complete_cases.rds")
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")
 
@@
 #Invert axes
-PC$S[,1] <- -PC$S[,1]
+#PC$S[,1] <- -PC$S[,1]
 PC$S[,2] <- -PC$S[,2]
 
-pc3 <- function(PC, x="PC1", y="PC3") {
+pc3 <- function(PC, x="PC1", y="PC2") {
   # PC being a prcomp object
@@
   plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
+  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.015, 0.03, 0.07), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
     scale_alpha(guide = 'none')
@@
   # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
 
   #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
 
@@
   plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC3 ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
+  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
 
@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,4.8,7.1,5.5)), y = -(PCAloadings$PC2*c(-3.2,4.5,3.75,8.4,5,5.5)+c(0,0,0,0,-0.08,0)),
+ plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,5.2,5,5.25,6.3,6)), y = -(PCAloadings$PC2*c(4,4.75,4,4.5,5,5.5)+c(0,0,0,0,-0.04,0)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)

### 2021-06-24 Supplementary_Material/Regression_Trees_Subset_Nectar_Pollen.Rmd
edits

@@
 set.seed(2)
-tree1 <- rpart(Visits~., data=v_df, cp=0.0134316) #6 splits is lower than the best tree plus on sd (rule of thumb for selecting trees)
+tree1 <- rpart(Visits~., data=v_df, cp=0.0154001)
 
 set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0125459) #6node divisons it is within on sd + error of best tree
+tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0125459)
 
 set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0190352) #7node divisons
-
+tree3 <- rpart(Specialization~., data=d_df, cp=0.0190352) 
 par(mfrow=c(1,3))
 
-rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.5,tweak = 1.15,type = 2) 
+rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.5,tweak = 1.25,type = 2) 
 rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.5,tweak = 1.25,type = 2)

### 2021-06-24 Scripts/3_2_PPCA_Complete_Cases.R

@@ -15,7 +15,7 @@ library(broman) #crayon colours
 ########################################################################################################################################################
 #1) LOAD DATA
 ########################################################################################################################################################
-#read data with missing values filled by data imputation
+#read data with complete cases//no imputation performed despite the name of the datset
 dat <- read.csv("Data/Csv/imputed_trait_data_complete.cases.csv", row.names = "X")
 ########################################################################################################################################################
 #2) Tidy up data to get phylo distance and conduct PCA

### 2021-06-24 Scripts/trial.R

@@ -1,0 +1,88 @@
+########################################################################################################################################################
+#SCRIPT TO CALCULATE THE PHLOGENETIC INFORMED PRINCIPAL COMPONENT ANALYSIS
+########################################################################################################################################################
+#LOAD LIBRARIES
+library(phytools) #ppca
+library(ape) #for phylogenetic distance
+library(dplyr) #data processing
+library(rtrees) #for phylogenetic distancelibrary(MASS)
+library(reshape2) #data processing
+library(MASS) #I think I used it for the kernel density of the plotting function; no longer used but I leave in case its handy later on
+library(ggplot2) #plotting
+library(broman) #crayon colours
+library(magick) #add images
+########################################################################################################################################################
+#1) LOAD DATA
+########################################################################################################################################################
+#read data with missing values filled by data imputation
+dat <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
+########################################################################################################################################################
+#2) Tidy up data to get phylo distance and conduct PCA
+########################################################################################################################################################
+########################################################################################################################################################
+#remove not found species, cannot do PCA with unequal numbers of rows
+cols.num <- c("Family_all","Genus_all","Species_all")
+dat[cols.num] <- sapply(dat[cols.num],as.character)
+dat$Species_all <- gsub("Species_all_", "", dat$Species_all)
+########################################################################################################################################################
+#3) REMOVE OUTLIERS, OUT OF 2.5-97.5 RANGE WHICH HELPS IMPUTATION PROCESS. SEE ARTICLE FOR REF.
[…]

### 2021-06-25 Supplementary_Material/Regression_Trees_All.Rmd
regression trees update

@@
 set.seed(1)
-tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0089891)
+tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0054559,minbucket=50)
 
 set.seed(1)
-tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0159034)
+tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0084459,minbucket=50)
 
 set.seed(1)
-tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0147899)
+tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0072192 , minbucket=50) #10
 
@@
 colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
 
 colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
 
 colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
 
 set.seed(2)
-tree1 <- rpart(Visits~., data=v_df, cp=0.0131325) #6 splits is lower than the best tree plus on sd (rule of thumb for selecting trees)
+tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
 
 set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0109066) #6node divisons it is within on sd + error of best tree
+tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
 
 set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0147899) #7node divisons
+tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)
 

### 2021-06-25 Supplementary_Material/Regression_Trees_Subset_Nectar_Pollen.Rmd
regression trees update

@@
 colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
 
@@
 set.seed(2)
-tree1 <- rpart(Visits~., data=v_df, cp=0.0154001)
+tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
 
 set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0125459)
+tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
 
 set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0190352) 
+tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50) 
 par(mfrow=c(1,3))
@@
 rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.5,tweak = 1.25,type = 2)
-rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.5,tweak = 1.15,type = 2)
+rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.5,tweak = 1.25,type = 2)
 

### 2021-06-25 Scripts/Pollen_and_nectar_traits.R

@@ -1,418 +1,0 @@
-########################################################################################################################################################
-#Script to analyse data of pollen and nectar||Visits~Floral rewards
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(ggplot2)
-library(brms)
-library(ape) #for phylogenetic distance
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(dplyr) #data processing
-library(data.table)
-library(tidyverse)
-library(readxl)
-
-#Set publication theme
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(1.1)),
-           axis.text=element_text(size = rel(1), color = "black"),
-           legend.title=element_text(face="bold"),
-           legend.text=element_text(),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(0.4, 'lines'),
-           panel.border=element_rect(color="black",size=1),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-setwd("~/R_Projects/Reproductive Traits")
-#load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
[…]

### 2021-06-25 Scripts/Regression_Tree.R

@@ -1,71 +1,0 @@
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
-########################################################################################################################################################
-
-library(rpart)
-library(rpart.plot)
-
-#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
-long_d <- read.csv("Data/Csv/long_format_quantitative_networks.csv", row.names = 1) #quantitative network data|weighted by frequency of visits per plant species
-
-#Select data with interaction greater than 0
-long_d_1 <- long_d[long_d$Interaction>0,]
-
-#Remove NA'S
-long_d_2 <- long_d_1[!is.na(long_d_1$guild),] #I do it by guild because just these 6 guilds are named in this column
-
-#check levels
-levels(factor(long_d_2$guild))
-########################################################################################################################################################
-#NOW READ NECTAR DATA
-forest_data <- read.csv("Data/Csv/nectar_pollen_subset_imputed_trait_data.csv")
-str(forest_data)
-nrow(forest_data)
-colnames(forest_data)[1] <- "Plant_species"
-########################################################################################################################################################
-#MERGE DATA
-data <- merge(long_d_2, forest_data, by="Plant_species")
-nrow(data)
-
-
-########################################################################################################################################################
-#VISITATION DATA REGRESSION TREE
-########################################################################################################################################################
-data_1 <- data[c("Interaction","Autonomous_selfing_level_fruit_set","Corolla_diameter_mean","Corolla_length_mean",
-                 "Flowers_per_plant","Style_length","Ovule_number","Plant_height_mean_m","Nectar_concentration",
-                 "Nectar_mg","Nectar_ul","Pollen_per_flower")]
-
-#Set colnames for plotting
-colnames(data_1) <- c("Interactions", "Aut. selfing", "Flower width","Flower length" , "Flowers per plant","Style length (mm)",
-                      "Ovule number","Plant height (m)", "Nectar_concentration","Mg of nectar","Microlitres of nectar","Pollen_per_flower")
-
-
-#Visitation data regression tree
-data_1$Interactions <- log10(data_1$Interactions+1) #Log transform to be able to run the tree with low error, it doesnt like non-normal dist
-
[…]

### 2021-06-25 Scripts/trial_all_values/Analysis_1.R

@@ -1,51 +1,0 @@
-########################################################################################################################################################
-#SCRIPT TO PREPARE DATA FOR ANALYSIS 1) VISITS~ POLL. FUNCTIONAL GROUP*PRINCIPAL COMPONENTS
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(data.table)
-########################################################################################################################################################
-#LOAD DATA
-########################################################################################################################################################
-long_d <- read.csv("Data/Csv/long_format_quantitative_networks.csv", row.names = 1) #quantitative network data|weighted by frequency of visits per plant species
-phyl_pca <- readRDS("Data/RData/phyl_pca_forest_all_values.rds") #add PCA loadings for analysis
-dat_cleaning <- readRDS("Data/RData/data_all_species_PPCA.rds") #data for PPCA
-########################################################################################################################################################
-#PREPARE DATA
-########################################################################################################################################################
-#Select data with interaction greater than 0
-long_d_1 <- long_d[long_d$Interaction>0,]
-
-#Remove other orders/guilds that are not these ones
-long_d_2 <- long_d_1[!is.na(long_d_1$guild),] #I do it by guild because just these 6 guilds are named in this column
-
-#check levels
-levels(factor(long_d_2$guild)) #9 DIFFERENT GUILDS|After I'll select the main fucntional poll. groups for analysis
-
-#convert to dataframe the ppca data
-phyl_pca_1 <- data.frame(phyl_pca$S)
-
-#convert rownames to column
-dat_cleaning_1 <- setDT(dat_cleaning, keep.rownames = TRUE)[]
-colnames(dat_cleaning_1)[1] <- "Plant_species"
-
-phyl_pca_1$Plant_species <- dat_cleaning_1$Plant_species
-#ADD ALSO THESE OTHER 3 COLUMNS WITH SPP, GENUS AND FAMILY INFO NEEDED TO GET THE PHYLO FOR THE MODEL
-phyl_pca_1$Family_all <- dat_cleaning_1$Family_all
-phyl_pca_1$Genus_all <- dat_cleaning_1$Genus_all
-phyl_pca_1$Species_all <- dat_cleaning_1$Species_all
-
-#merge columns
-data_analysis <- merge(long_d_2, phyl_pca_1, by = "Plant_species")
-#Explore why some levels dropped
-#data_analysis <- merge(long_d_2, phyl_pca_1, by = "Plant_species", all.x = T)
[…]

### 2021-06-25 Scripts/trial_all_values/dat_prep_analysis_2.R

@@ -1,143 +1,0 @@
-########################################################################################################################################################
-#SCRIPT TO PREPARE DATA FOR ANALYSIS 2) VISITS/SPECIALIZATION ~ PRINCIPAL COMPONENTS
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(data.table) # operate with df
-library(bipartite) #calculate metrics
-library(dplyr) #data manipulation 
-library(stringr) #remove string
-########################################################################################################################################################
-#1) LOAD NETWORK DATA
-########################################################################################################################################################
-#Set working directory to read files
-setwd("~/R_Projects/Reproductive traits/Data/Data_networks_quantitative") 
-
-#read csv files
-temp <- list.files(pattern="*.csv")
-my.list <- list(for (i in 1:length(temp)) assign(temp[i], read.csv(temp[i])))
-my_files <- list.files(pattern = "\\.csv$")
-my_data <- lapply(my_files, function(i){read.csv(i,  row.names = 1)})
-# Add id to dataframe
-names(my_data) <- stringr::str_replace(my_files, pattern = ".csv", replacement = "")
-
-########################################################################################################################################################
-#2) CALCULATE METRICS 
-########################################################################################################################################################
-
-#Function to sum visits per row and convert NA'S to 0's in the case there is any
-rs_NA <- function(x){
-  z <- as.data.frame(x)
-  z[is.na(z)] <- 0  #convert NA'S to 0's
-  z <- as.data.frame(rowSums(z)) #sum rows
-  z <- setDT(z, keep.rownames = TRUE)[] 
-  colnames(z) <- c("Species","Visits")
-  return(z)
-}
-
-
-#Calculate all metrics at once with bipartite
-met <- function(x){
-  Visits_Sum <- rs_NA(x) #previous function to sum rows 
-  #degree
-  #degree <- specieslevel(x, index="degree", level="lower")
-  #normalise degree
-  n_degree <- specieslevel(x, index="normalised degree", level="lower")
-  #specialization
-  d_Plant <- specieslevel(x, index="d", level="lower")   # specialization from BLUTHGEN 2006
[…]

### 2021-06-25 Scripts/trial_all_values/ppca_all.R

@@ -1,202 +1,0 @@
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE PHLOGENETIC INFORMED PRINCIPAL COMPONENT ANALYSIS
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(phytools) #ppca
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2) #data processing
-library(MASS) #I think I used it for the kernel density of the plotting function; no longer used but I leave in case its handy later on
-library(ggplot2) #plotting
-library(broman) #crayon colours
-library(magick) #add images
-########################################################################################################################################################
-#1) LOAD DATA
-########################################################################################################################################################
-#read data with missing values filled by data imputation
-dat <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-########################################################################################################################################################
-#2) Tidy up data to get phylo distance and conduct PCA
-########################################################################################################################################################
-########################################################################################################################################################
-#remove not found species, cannot do PCA with unequal numbers of rows
-cols.num <- c("Family_all","Genus_all","Species_all")
-dat[cols.num] <- sapply(dat[cols.num],as.character)
-dat$Species_all <- gsub("Species_all_", "", dat$Species_all)
[…]

### 2021-08-02 Main_Figures/Analysis_1_Separated.Rmd
edits

@@
   aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("High Flower N.    Large flowers")+
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("High Flower N.    Low Flower N.\nSmall flowers       Large flowers")+
   theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila-Hymenoptera (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
@@
   aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles")+
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles\n Low selfing    High selfing")+
   theme_ms() +theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila-Hymenoptera (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",

### 2021-08-02 Supplementary_Material/Supplementary_Material.Rmd
edits

@@
 __Figure S9__  Sum of visits per plant, normalized degree and specialization modelled in function of the first three main axes of trait variation.
+
+__Figure S10__ Pearson correlation between the product of flower number-flower size and autonomous selfing level.
 
@@
 set.seed(2)
-tree1 <- rpart(Visits~., data=v_df, cp=0.0134316) #6 splits is lower than the best tree plus on sd (rule of thumb for selecting trees)
+tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
 
 set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0125459) #6node divisons it is within on sd + error of best tree
+tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
 
 set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0171878) #7node divisons
+tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)
 
@@
 \elandscape
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig S10.} Pearson correlation between the product of flower number-flower size and autonomous selfing level.", fig.pos= "h"}
+
+theme_ms <- function(base_size=18, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(2.2)),
+           axis.text=element_text(size = rel(2), color = "black"),
+           legend.title=element_text(face="bold",size=rel(2)),
+           legend.text=element_text(size=rel(2.4)),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(1.8, 'lines'),
+           panel.border=element_rect(color="black",size=2.4),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank()
+     ))
+}
+
+#LOAD LIBRARIES
+library(ggplot2)
+library(ggpubr)
+
+#LOAD DATA
+dat <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
+
+#CONDUCT PRODUCT FLOWER NUMBER-FLOWER SIZE
+dat$Product <-      log(dat$Flowers_per_plant * dat$Corolla_diameter_mean+1)
+
+ggscatter(dat, x = "Autonomous_selfing_level_fruit_set", y = "Product", 
+          add = "reg.line", conf.int = TRUE,
+          cor.coef = TRUE, cor.method = "pearson",size=5,cor.coef.size=15,
+          xlab = "Autnomous selfing", ylab = "Product flower size-number") +
+  theme_ms() +ylim(0,16)
+
+```

### 2021-08-10 Main_Figures/Global_trait_spectrum.Rmd
Update on labels and x-y axes of Figure 1

@@
       theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
+            axis.title=element_text( size = rel(1.75)),
             axis.text=element_text(size = rel(1.75), color = "black"),
@@
 
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+  plot <- plot + xlab(paste("Flower number - flower size trade-off ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("Pollinator dependence trade-off ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
 
@@
   plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
+     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
     annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
@@
     annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
+    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
     annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
@@
     annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
-    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
+    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2, ymax = -1.50) +
     annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
@@
       #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
+  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
 
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,7.25,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.4,3,6.2,5,5.5)+c(0,0,0,0,0.4,0)),
+ plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=4)
+
+ plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
+                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
 

### 2021-08-11 Draft/Manuscript.Rmd
manuscript

--- 2021-05-19 Untitled/Manuscript.Rmd
@@
 ---
-title: "Plant reproductive strategies structure plant-pollinator networks"
+title: "Trade-offs among plant floral and reproductive traits determine interactions with floral visitors"
+
 author:
@@
     number_sections: no
+    extra_dependencies: ["float"]
     toc: no
+    fig_crop: no
     includes:
@@
 fontfamily: mathpazo
-fontsize: 11pt
+fontsize: 12pt
 
@@
 - \usepackage{xcolor}
+- \usepackage{float}
+- \floatplacement{figure}{H}
+- \usepackage[skip=5pt]{caption}
 ---
@@
 
-<!--# Write Abstract and Keywords below -->
-
-\vspace{1cm}
-\hrule
-
-#Abstract
-
-Increasing availability of large datasets have improved our understanding of organismal life history and pollination biology.
-However, most attention has focused on vegetative traits when delimiting plant life strategies and overlooked key floral and reproductive traits.
-In addition, plant-pollinator research rarely considers the reproductive biology of the species and has overemphasized the study of highly specialized interactions.
-Greater knowledge of the plant reproductive trade-offs between these traits can shed light on the macroecological patterns and help our understanding of life strategies.
-
-Here, we compiled 20 reproductive traits for 1,506 plant species from 28 plant-pollinator network studies and 18 different countries that constitute a total of 64 unique networks and 8 meta-webs.
-We explore the different trade-offs of floral, reproductive, and vegetative traits of the main quantitative traits in the trait space.
-Then, we evaluate whether the frequency of pollinator visits within networks change across the primary axes of trait variation and pollinator functional groups.
-Finally, we investigate if the functional role of the plant species (interaction frequency, normalized degree and specialization) in the network is associated with the primary axes of trait variation and the different plant traits.
-
-We found that 51.8% of the trait variation was explained by two independent axes that determined plant form and function.
-The first axis showed the flower number versus flower size compromise (PC1, 26.72%) where species were divided in two opposed strategies with high investment in flower number and plant height on one extreme or high investment in flower size, style length and larger number of ovules on the other.
-The second axis showed the pollinator dependence trade-off (PC2, 25.08%) between species with high pollinator dependence with greater plant height and higher investment in floral traits on one end and low pollinator dependence with smaller height and lower investment in floral traits on the other.
-An additional principal component analysis with the subset of species with quantitative data of pollen and nectar showed that nectar quantity was positively associated with flower size, style length and ovule number (PC1, 24.70%) and pollen quantity was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 20.59%).
-The main axes of trait variation with the full set of species did not explain the overall visitation patterns but showed marked trends for the different functional groups.
-For instance, all pollinator functional groups had higher frequency of visits on plant species with high pollinator dependence (PC2); and bees (Anthophila), the most abundant functional group, had higher frequency of visits on species with high number of flowers and tall plant height (PC1); and, on species with longer styles and higher levels of autonomous selfing (PC3).
-Overall, plant species with small size, low nectar concentration and short styles showed lower visitation rates than plant species with the opposed traits; species with small amounts of floral rewards (pollen and nectar), low number of flowers and small flowers had in general lower number of visiting species (normalized degree); and species under 1.3 m, with high rewards of pollen and nectar showed the highest levels of specialization.
-This work highlights the need to consider essential plant reproductive and floral traits to improve understanding of plant life strategies and plant-pollinator interactions at large scales.
-
-\vspace{3mm}
-\hrule
+Plant life strategies are often delimited by vegetative and physiological traits but little is known about how floral and reproductive traits drive these strategies, and in turn shape plant interactions with floral visitors.
+Here, we compiled 13 floral, 4 reproductive and 3 vegetative traits for 1,506 plant species from 28 plant-pollinator network studies across 18 different countries.
+We investigated the associations among these traits, pollinator visitation and the functional role of plant species within the networks (interaction frequency, normalized degree and specialization).
+We found that 51.8% of trait variation was explained by two independent axes that encompassed plant form and function.
+Specifically, the first axis indicated the presence of a trade-off between flower number and flower size (PC1, 26.72%).
+The second axis indicated a trade-off for the level of pollinator dependency (PC2, 25.08%).
+Although the main axes of trait variation did not fully explain pollinator visitation rates, different plant life strategies were associated with visitation rates and pollinator functional groups.
+Overall, the main traits that determined plant species’ functional roles were height, nectar concentration, pollen grains per flower, number of ovules, style length, selfing level and flower width.
+Our results highlight the need to consider plant reproductive and floral traits to improve understanding of plant life strategies and plant-pollinator interactions at broader spatial scales.
+
 \vspace{5mm}
-
-*Keywords*: plant-pollinator networks | floral traits | life history strategy | functional traits
-
 \bleft
-\newpage
 
@@
 cite_options(citation_format = "pandoc")
+
 ```
 
-<!--# Start writing your paper below -->
-
-# INTRODUCTION
+```{r global_options, include=FALSE}
+knitr::opts_chunk$set(fig.pos = 'H')
+```
+
+There is an astonishing diversity of floral structures and plant reproductive strategies among flowering plants (Barrett, 2002; Schiestl & Johnson, 2013), which have long been of interest to pollination biologists in terms of their relevance to plant-pollinator interactions.
+However, most studies that have explored reproductive (e.g., mating and compatibility systems) and floral trait (e.g., flower size or nectar provision) variation have concentrated on the individual or community level and thus, broader macroecological patterns remain poorly investigated (Carvalheiro et al., 2014; Baude et al., 2016; Munoz et al., 2016; Moeller et al., 2017; Grossenbacher et al., 2017).
+Indeed, studies depicting species’ life history strategies generally focus on vegetative traits and rarely consider reproductive traits (Salguero-Gómez et al., 2016; Rüger et al., 2018).
+As a consequence, a unified framework that explores the compromises among floral traits and their relevance to plant life strategies is currently lacking (Roddy et al., 2021).
+At the same time, there is growing interest in the determinants of plant-pollinator interactions via trait-based approaches (Fenster et al., 2004) and trait-matching analyses (Bartomeus et al., 2016).
+However, floral traits have been overlooked beyond highly specialised plant-pollinator systems (Dellinger, 2020; Roddy et al., 2021) and the role of plant reproductive biology remains little explored in plant-pollinator interactions (but see Tur et al., 2013 and Devaux et al., 2014).
+
+With the recent availability of large trait databases, plant ecological strategies are increasingly being examined (e.g., TRY, Kattge et al., 2011 and COMPADRE, Salguero‐Gómez et al., 2015), and are facilitating the identification of global patterns and constraints of plant form and function (Salguero‐Gómez et al., 2015; Díaz et al., 2016; Carmona et al., 2021).
+However, the main focus has been on vegetative traits such as leaf (Wright et al., 2004) or wood (Chave et al., 2009) trade-offs with little or no attention given to reproductive and floral traits (E‐Vojtkó et al., 2020), also critical to plant form and function.
+For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively (Barrett, 2003; Moeller et al., 2017).
+Further, outcrossing levels are positively correlated with flower size (Goodwillie et al., 2010).
+In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and their role in attracting pollinators (Ollerton et al., 2011).
+Hence, exploring plant life strategies with reproductive and floral trade-offs, in conjunction with their pollinator dependence, is necessary for a balanced understanding of plant economics.
+
+Several studies have identified links between plant traits and plant-pollinator network properties (Lázaro et al., 2008; Bartomeus, 2013; Carvalheiro et al., 2014).
+Moreover, plant traits can also define species' network roles (e.g., specialists vs generalists).
+For example, species that occupy trait space extremes are more likely to exhibit higher specialization and be more reliant on trait-matching (Junker et al., 2013; Coux et al., 2016).
+This morphological matching between plant and floral visitors can determine plant-pollinator interactions, and thus shape their interaction network structure (Stang et al., 2009; Ibanez, 2012).
+Despite the increasing knowledge of the relevance of traits on the species network roles, little is known about how plant reproductive and floral traits determine plant species’ network roles at a macroecological scale.
+
+Here, we explore the potential trade-offs among plant floral and reproductive traits and how these influence the structure of plant-pollinator networks.
+First, we identify the major axes of floral and reproductive trait variation and trade-offs that determine plant form and function.
+Second, we investigate how plant species’ position in trait-space influences interaction strength with different guilds of floral visitors.
+Finally, we investigate how the main axes of trait variation and individual traits influence plant species roles within networks using complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
+
+# RESULTS
+
+**Plant strategies**
+
+The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Figure 1 and Figure S5) and had a phylogenetic correlation (**lambda**) of 0.76.
+The first principal component (PC1) represented 26.72% of the trait variation and indicated a trade-off between flower number and flower size.
+We refer to this axis as the ‘flower number - flower size trade-off as already described in previous studies (Sargent et al., 2007; Kettle et al., 2011).
+Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
+The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Table S3) but style length also contributed moderately on PC1 (loading = -0.33).
+The second principal component (PC2) represented 25.05% of the trait variation and indicated a trade-off between low and high pollinator dependence.
+We refer to this axis as the ‘pollinator dependence trade-off’.
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
+We found that high pollinator dependence was associated with larger and higher numbers of flowers, greater plant height and longer styles.
+In contrast, species with high levels of autonomous selfing tended to have fewer and smaller flowers, had shorter styles and were shorter in height.
+Further, PC3 explained a considerable amount of trait variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
+The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
+Thus, because style length was correlated with all traits on PC3 and was the main driver of variation, we refer to this axis as the ‘style length trade-off’.
+Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 23.40%); and pollen quantity (pollen grains per flower) was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 21.67%; Figure S6).
+This pPCA explained similar variance with the first two principal components (45.07%) and similar associations of traits despite some variability in the loadings (Table S4).
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,fig.pos = "!H",fig.cap= "Figure 1.
+Life history strategies for 1,236 plant species from 28 plant-pollinator networks studies across the first two axes of trait variation from a phylogenetically informed principal component analysis (pPCA).
+The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) in the 2-d plane.
+The length of the arrows indicate the weight of the variables on each principal component and the labelled icons at their end represent the extreme form of the trait continuum.
+The dashed lines show the opposed direction of trait variation and the non-labelled icons at their end illustrate the opposing extreme of the continuum."}
+
+setwd("~/R_Projects/Reproductive Traits")
+
+#Load libraries
+library(viridis) #COLOUR GGPLOT
+library(ggplot2)
+library(broman) #crayon colours
+library(cowplot)
+library(magick)
+
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+      theme(text=element_text(color="black"),
+            axis.title=element_text( size = rel(1.75)),
+            axis.text=element_text(size = rel(1.75), color = "black"),
+            legend.title=element_text(face="bold"),
+            legend.text=element_text(),
+            legend.background=element_rect(fill="transparent"),
+            legend.key.size = unit(1.2, 'lines'),
+            panel.border=element_rect(color="black",size=1),
+            panel.grid.minor.x =element_blank(),
+            panel.grid.minor.y= element_blank(),
+             panel.grid.major= element_blank()
+      ))
+}
+
+#Load data
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+PC <- phyl_pca_forest
+#CHECK CONTENT
+#EIGENVALUES
+PC$Eval
+#PC score (POINTS)
+PC$S
+#PC loadings (ARROWS)
+PC$L
+
+#Images were made by Paula Martin
+#Check her work on https://paulamartinart.com/
+
+tree <- image_read("Images/PPCA_Plot/Tree.png")
+tree_1 <- as.raster(tree)
+
+style_l <- image_read("Images/PPCA_Plot/Style_Long.png")
+style_l_1 <- as.raster(style_l)
+
+style_s <- image_read("Images/PPCA_Plot/Style_Short.png")
+style_s_1 <- as.raster(style_s)
+
+ovule_h <- image_read("Images/PPCA_Plot/Ovule_High.png")
+ovule_h_1 <- as.raster(ovule_h)
+
+ovule_l <- image_read("Images/PPCA_Plot/Ovule_Low.png")
+ovule_l_1 <- as.raster(ovule_l)
+
+selfing_n <- image_read("Images/PPCA_Plot/Selfing_None.png")
+selfing_n_1 <- as.raster(selfing_n)
+
+selfing_h <- image_read("Images/PPCA_Plot/selfing.png")
+selfing_h_1 <- as.raster(selfing_h)
+
+single_flower <- image_read("Images/PPCA_Plot/Single_Flower.png")
+single_flower_1 <- as.raster(single_flower)
+
+many_flowers <- image_read("Images/PPCA_Plot/Inflorescencia.png")
+many_flowers_1 <- as.raster(many_flowers)
+#many_flowers_1 <- image_rotate(many_flowers, 45)
+
+large_flower <- image_read("Images/PPCA_Plot/flower_big.png")
+large_flower_1 <- as.raster(large_flower)
+
+flower_small <- image_read("Images/PPCA_Plot/flower_short.png")
+flower_small_1 <- as.raster(flower_small)
+
+herb <- image_read("Images/PPCA_Plot/herb.png")
+herb_1 <- as.raster(herb)
+
+#############################################################################################################################################################
+#COMPATIBILITY
+#############################################################################################################################################################
+#Load plots
+
+#Invert axes
+PC$S[,1] <- -PC$S[,1]
+PC$S[,2] <- -PC$S[,2]
+
+all_spp <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
+  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
+    scale_alpha(guide = 'none')
+
+    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .7 * mult * (get(x)),
+                      v2 = .7 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+
+   #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  plot <- plot + xlab(paste("Flower number - flower size trade-off ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("Pollinator dependence trade-off ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+
+  #CHANGE THEME
+
+  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
+     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
+    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
+    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
+    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
+    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
+    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
+    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
+    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
+    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
+    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2, ymax = -1.50) +
+    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
+
+      #ADD LABELS
+  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+ plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
+                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
+
+ plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
+                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
+
+  plot
+
+}
+
+plot_grid(all_spp(PC))
+
+```
+
+We found that most categorical traits were statistically associated with the first two axes of trait variation (Figure 2 and Table S2).
+Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, p < 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , p = 0.59; PC2:  Sum of squares = 0.83, F-value = 1.43, p = 0.23) showed lack of statistical association.
+In addition, we found statistical differences (Tukey test) between the different levels of categorical traits in the trait space (Figure S7).
+Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatibile were statistically differentiated from species with partial or full self compatibility; Figure S7 A and B).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Figure S7 C and D).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Figure S7 E and F).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Figure S7 G and H).
+Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Figure S7 I and J).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Figure S7 K and L).
+
+\blandscape
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=13, fig.width=27, out.extra='',fig.cap="Location of the different qualitative traits that showed statistical association with the first two axes of trait variation.
+These different traits included: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f)."}
+
+#LOAD LIBRARIES 
+#library(phytools)
+#library(ape) #for phylogenetic distance
+#library(dplyr) #data processing
+#library(rtrees) #for phylogenetic distancelibrary(MASS)
+#library(reshape2)
+library(viridis) #COLOUR GGPLOT
+#library(MASS)
+library(ggplot2)
+library(broman) #crayon colours
+#library(tidyverse)
+library(patchwork) #panel of plots
+#library(brms)
+#library(cmdstanr)
+
+#Load theme for publication
+
+theme_ms <- function(base_size=14, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(2)),
+           axis.text=element_text(size = rel(1.8), color = "black"),
+           legend.title=element_text(face="bold",size=rel(2)),
+           legend.text=element_text(size=rel(1.4)),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(1.8, 'lines'),
+           panel.border=element_rect(color="black",size=2.4),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank(),
+           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
+           plot.subtitle = element_text(face="bold",size=rel(2))
+     ))
+}
+
+setwd("~/R_Projects/Reproductive Traits")
+
+p1 <- readRDS("Main_Figures/figure_2_1.rds")
+p2 <- readRDS("Main_Figures/figure_2_2.rds")
+p3 <- readRDS("Main_Figures/figure_2_3.rds")
+pp1 <- readRDS("Main_Figures/figure_2_4.rds")
+pp2 <- readRDS("Main_Figures/figure_2_5.rds")
+pp3 <- readRDS("Main_Figures/figure_2_6.rds")
+
+library(patchwork)
+
+combined <- p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "right")
+combined + plot_layout(guides = "collect",ncol = 3)
+
+```
+
+\elandscape
+
+**Phylogenetic signal of traits**
+
+###OLD
 

### 2021-08-11 Draft/Manuscript.tex
manuscript

--- 2021-05-19 Untitled/Manuscript.tex
@@
-\documentclass[11pt,a4paper,]{article}
+\documentclass[12pt,a4paper,]{article}
 \usepackage[]{mathpazo}
@@
 \hypersetup{
-            pdftitle={Plant reproductive strategies structure plant-pollinator networks},
+            pdftitle={Trade-offs among plant floral and reproductive traits determine interactions with floral visitors},
             pdfauthor={Jose B. Lanuza1,2*; Romina Rader1; Jamie Stavert3; Liam K. Kendall4; Manu E. Saunders1; Ignasi Bartomeus2},
@@
 \usepackage{xcolor}
+\usepackage{float}
+\floatplacement{figure}{H}
+\usepackage[skip=5pt]{caption}
+\usepackage{float}
 \usepackage{booktabs}
@@
 \usepackage{wrapfig}
-\usepackage{float}
 \usepackage{colortbl}
@@
 
-\title{Plant reproductive strategies structure plant-pollinator networks}
+\title{Trade-offs among plant floral and reproductive traits determine
+interactions with floral visitors}
 \author{Jose B.
@@
 
-\vspace{1cm} \hrule
-
-\section{Abstract}\label{abstract}
-
-Increasing availability of large datasets have improved our
-understanding of organismal life history and pollination biology.
-However, most attention has focused on vegetative traits when delimiting
-plant life strategies and overlooked key floral and reproductive traits.
-In addition, plant-pollinator research rarely considers the reproductive
-biology of the species and has overemphasized the study of highly
-specialized interactions. Greater knowledge of the plant reproductive
-trade-offs between these traits can shed light on the macroecological
-patterns and help our understanding of life strategies.
-
-Here, we compiled 20 reproductive traits for 1,506 plant species from 28
-plant-pollinator network studies and 18 different countries that
-constitute a total of 64 unique networks and 8 meta-webs. We explore the
-different trade-offs of floral, reproductive, and vegetative traits of
-the main quantitative traits in the trait space. Then, we evaluate
-whether the frequency of pollinator visits within networks change across
-the primary axes of trait variation and pollinator functional groups and
-how individual traits contribute to the overall visitation patterns.
-Finally, we investigate if the functional role of the plant species
-(interaction frequency, normalized degree and specialization) in the
-network is associated with the primary axes of trait variation and the
-different plant traits.
-
-We found that 51.8\% of the trait variation was explained by two
-independent axes that determined plant form and function. The first axis
-showed the flower number versus flower size compromise (PC1, 26.72\%)
-where species were divided in two opposed strategies with high
-investment in flower number and plant height on one extreme or high
-investment in flower size, style length and larger number of ovules on
-the other. The second axis showed the pollinator dependence trade-off
-(PC2, 25.08\%) between species with high pollinator dependence with
-greater plant height and higher investment in floral traits on one end
-and low pollinator dependence with smaller height and lower investment
-in floral traits on the other. An additional principal component
-analysis with the subset of species with quantitative data of pollen and
-nectar showed that nectar quantity was positively associated with flower
-size, style length and ovule number (PC1, 24.70\%) and pollen quantity
-was positively correlated with flower number and plant height and
-negatively associated with autonomous selfing (PC2, 20.59\%). The main
-axes of trait variation with the full set of species did not explain the
-overall visitation patterns but showed marked trends for the different
-functional groups. For instance, all pollinator functional groups had
-higher frequency of visits on plant species with high pollinator
-dependence (PC2); and bees (Anthophila), the most abundant functional
-group, had higher frequency of visits on species with high number of
-flowers and tall plant height (PC1); and, on species with longer styles
-and higher levels of autonomous selfing (PC3). Overall, plant species
-with small size, low nectar concentration and short styles showed lower
-visitation rates than plant species with the opposed traits; species
-with small amounts of floral rewards (pollen and nectar), low number of
-flowers and small flowers had in general lower number of visiting
-species (normalized degree); and species under 1.3 m, with high rewards
-of pollen and nectar showed the highest levels of specialization. This
-work highlights the need to consider essential plant reproductive and
-floral traits to improve understanding of plant life strategies and
-plant-pollinator interactions at large scales.
-
-\vspace{3mm} \hrule
-\vspace{5mm}
-
-\emph{Keywords}: plant-pollinator networks \textbar{} floral traits
-\textbar{} life history strategy \textbar{} functional traits
-
-\bleft
-\newpage
-
-\section{INTRODUCTION}\label{introduction}
+Plant life strategies are often delimited by vegetative and
+physiological traits but little is known about how floral and
+reproductive traits drive these strategies, and in turn shape plant
+interactions with floral visitors. Here, we compiled 13 floral, 4
+reproductive and 3 vegetative traits for 1,506 plant species from 28
+plant-pollinator network studies across 18 different countries. We
+investigated the associations among these traits, pollinator visitation
+and the functional role of plant species within the networks
+(interaction frequency, normalized degree and specialization). We found
+that 51.8\% of trait variation was explained by two independent axes
+that encompassed plant form and function. Specifically, the first axis
+indicated the presence of a trade-off between flower number and flower
+size (PC1, 26.72\%). The second axis indicated a trade-off for the level
+of pollinator dependency (PC2, 25.08\%). Although the main axes of trait
+variation did not fully explain pollinator visitation rates, different
+plant life strategies were associated with visitation rates and
+pollinator functional groups. Overall, the main traits that determined
+plant species' functional roles were height, nectar concentration,
+pollen grains per flower, number of ovules, style length, selfing level
+and flower width. Our results highlight the need to consider plant
+reproductive and floral traits to improve understanding of plant life
+strategies and plant-pollinator interactions at broader spatial scales.
+
+\vspace{5mm} \bleft
+
+There is an astonishing diversity of floral structures and plant
+reproductive strategies among flowering plants (Barrett, 2002; Schiestl
+\& Johnson, 2013), which have long been of interest to pollination
+biologists in terms of their relevance to plant-pollinator interactions.
+However, most studies that have explored reproductive (e.g., mating and
+compatibility systems) and floral trait (e.g., flower size or nectar
+provision) variation have concentrated on the individual or community
+level and thus, broader macroecological patterns remain poorly
+investigated (Carvalheiro et al., 2014; Baude et al., 2016; Munoz et
+al., 2016; Moeller et al., 2017; Grossenbacher et al., 2017). Indeed,
+studies depicting species' life history strategies generally focus on
+vegetative traits and rarely consider reproductive traits
+(Salguero-Gómez et al., 2016; Rüger et al., 2018). As a consequence, a
+unified framework that explores the compromises among floral traits and
+their relevance to plant life strategies is currently lacking (Roddy et
+al., 2021). At the same time, there is growing interest in the
+determinants of plant-pollinator interactions via trait-based approaches
+(Fenster et al., 2004) and trait-matching analyses (Bartomeus et al.,
+2016). However, floral traits have been overlooked beyond highly
+specialised plant-pollinator systems (Dellinger, 2020; Roddy et al.,
+2021) and the role of plant reproductive biology remains little explored
+in plant-pollinator interactions (but see Tur et al., 2013 and Devaux et
+al., 2014).
+
+With the recent availability of large trait databases, plant ecological
+strategies are increasingly being examined (e.g., TRY, Kattge et al.,
+2011 and COMPADRE, Salguero‐Gómez et al., 2015), and are facilitating
+the identification of global patterns and constraints of plant form and
+function (Salguero‐Gómez et al., 2015; Díaz et al., 2016; Carmona et
+al., 2021). However, the main focus has been on vegetative traits such
+as leaf (Wright et al., 2004) or wood (Chave et al., 2009) trade-offs
+with little or no attention given to reproductive and floral traits
+(E‐Vojtkó et al., 2020), also critical to plant form and function. For
+instance, short lived versus perennial species tend to have low versus
+high levels of outcrossing, respectively (Barrett, 2003; Moeller et al.,
+2017). Further, outcrossing levels are positively correlated with flower
+size (Goodwillie et al., 2010). In addition, the presence of costly
+rewards (e.g., pollen or nectar) and showy flowers or floral displays
+can only be understood through consideration of plant species' reliance
+upon animal pollination (pollinator dependence) and their role in
+attracting pollinators (Ollerton et al., 2011). Hence, exploring plant
+life strategies with reproductive and floral trade-offs, in conjunction
+with their pollinator dependence, is necessary for a balanced
+understanding of plant economics.
+
+Several studies have identified links between plant traits and
+plant-pollinator network properties (Lázaro et al., 2008; Bartomeus,
+2013; Carvalheiro et al., 2014). Moreover, plant traits can also define
+species' network roles (e.g., specialists vs generalists). For example,
+species that occupy trait space extremes are more likely to exhibit
+higher specialization and be more reliant on trait-matching (Junker et
+al., 2013; Coux et al., 2016). This morphological matching between plant
+and floral visitors can determine plant-pollinator interactions, and
+thus shape their interaction network structure (Stang et al., 2009;
+Ibanez, 2012). Despite the increasing knowledge of the relevance of
+traits on the species network roles, little is known about how plant
+reproductive and floral traits determine plant species' network roles at
+a macroecological scale.
+
+Here, we explore the potential trade-offs among plant floral and
+reproductive traits and how these influence the structure of
+plant-pollinator networks. First, we identify the major axes of floral
+and reproductive trait variation and trade-offs that determine plant
+form and function. Second, we investigate how plant species' position in
+trait-space influences interaction strength with different guilds of
+floral visitors. Finally, we investigate how the main axes of trait
+variation and individual traits influence plant species roles within
+networks using complementary interaction network metrics (i.e.,
+interaction strength, normalized degree and specialization).
+
+\section{RESULTS}\label{results}
+
+\textbf{Plant strategies}
+
+The phylogenetically informed principal component analysis (pPCA)
+captured by the first two and three axes 51.8\% and 70.97\% of trait
+variation, respectively (Figure 1 and Figure S5) and had a phylogenetic
+correlation (\textbf{lambda}) of 0.76. The first principal component
+(PC1) represented 26.72\% of the trait variation and indicated a
+trade-off between flower number and flower size. We refer to this axis
+as the `flower number - flower size trade-off as already described in
+previous studies (Sargent et al., 2007; Kettle et al., 2011). Hence, one
+end of the spectrum comprised species with high investment in flower
+number and plant height but small flower size, short style length and
+low ovule number. The other end of this spectrum comprised species that
+were short in height and invested in large flowers, long styles, many
+ovules, but few flowers. The main contributing traits to PC1 were plant
+height, flower number, ovule number and flower size (loadings
+\textgreater{} \textbar{}0.5\textbar{}; Table S3) but style length also
+contributed moderately on PC1 (loading = -0.33). The second principal
+component (PC2) represented 25.05\% of the trait variation and indicated
+a trade-off between low and high pollinator dependence. We refer to this
+axis as the `pollinator dependence trade-off'. The main driver of trait
+variation on PC2 was autonomous selfing (loading = 0.85) but the other
+traits (except ovule number) also made moderate contributions (loadings
+from 0.27 to 0.4; Table S3). We found that high pollinator dependence
+was associated with larger and higher numbers of flowers, greater plant
+height and longer styles. In contrast, species with high levels of
+autonomous selfing tended to have fewer and smaller flowers, had shorter
+styles and were shorter in height. Further, PC3 explained a considerable
+amount of trait variability (19.17\%) and the main contributors to this
+axis were style length (loading = -0.66) and the degree of autonomous
+selfing (loading = -0.51). The remaining traits, apart from ovule
+number, were moderately correlated to changes on PC3 (loadings from
+-0.23 to -0.46; Table S3). Thus, because style length was correlated
+with all traits on PC3 and was the main driver of variation, we refer to
+this axis as the `style length trade-off'. Further, the pPCA with the
+subset of species that had nectar and pollen quantity data showed that
+nectar quantity (microlitres of nectar per flower) was positively
+associated with flower size, style length and ovule number (PC1,
+23.40\%); and pollen quantity (pollen grains per flower) was positively
+correlated with flower number and plant height and negatively associated
+with autonomous selfing (PC2, 21.67\%; Figure S6). This pPCA explained
+similar variance with the first two principal components (45.07\%) and
+similar associations of traits despite some variability in the loadings
+(Table S4).
+
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-1-1.pdf}
+\caption{\label{fig:unnamed-chunk-1}Figure 1. Life history strategies for
+1,236 plant species from 28 plant-pollinator networks studies across the
+first two axes of trait variation from a phylogenetically informed
+principal component analysis (pPCA). The solid arrows indicate the
+direction of the different quantitative traits (flower number, plant
+height, style length, flower size, ovule number and level of autonomous
+selfing) in the 2-d plane. The length of the arrows indicate the weight
+of the variables on each principal component and the labelled icons at
+their end represent the extreme form of the trait continuum. The dashed
+lines show the opposed direction of trait variation and the non-labelled
+icons at their end illustrate the opposing extreme of the continuum.}
+\end{figure}
+
+We found that most categorical traits were statistically associated with
+the first two axes of trait variation (Figure 2 and Table S2). Flower
+symmetry, which was only associated with PC2 (Sum of squares = 8.51,
+F-value = 14.72, p \textless{} 0.01 ), and nectar provision, which was
+independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 ,
+p = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, p = 0.23) showed
+lack of statistical association. In addition, we found statistical
+differences (Tukey test) between the different levels of categorical
+traits in the trait space (Figure S7). Regarding self compatibility, we
+found larger differences on PC2 (i.e., species with unisexual flowers
+that were self incompatibile were statistically differentiated from
+species with partial or full self compatibility; Figure S7 A and B).
+Life forms differed statistically across both axes of trait variation
+and followed a gradient of larger life forms (trees and shrubs) with
+higher pollinator dependence to smaller ones (herbs) with lower
+pollinator dependence (Figure S7 C and D). Consequently, lifespan also
+followed this gradient but perennial and short lived species only
+differed statistically on PC2 (Figure S7 E and F). Species with
+unisexual flowers (monoecious and dioecious) were clustered on both
+extremes of the first two principal components and had the highest
+pollinator dependence and highest number of flowers (Figure S7 G and H).
+Moreover, we found that the campanulate and capitulum flower shapes were
+differentiated from tube, papilionaceous, open and brush shapes in the
+trait space. The former morphologies had larger flowers and greater
+pollinator dependence, while the latter had higher flower number and
+greater autonomous selfing (Figure S7 I and J). Regarding flower
+symmetry, zygomorphic flowers were associated with lower levels of
+pollinator dependence, whereas actinomorphic flowers had higher levels
+of pollinator dependence (Figure S7 K and L).
+
+\blandscape
+
+\begin{figure}[H]
+\includegraphics{output/figures/unnamed-chunk-2-1} \caption{Location of the different qualitative traits that showed statistical association with the first two axes of trait variation.
+These different traits included: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).}\label{fig:unnamed-chunk-2}
+\end{figure}
+
+\elandscape
+
+\textbf{Phylogenetic signal of traits}
+
+\subsubsection{OLD}\label{old}
 
@@
 
-\caption{\label{tab:unnamed-chunk-1}List of the 20 traits compiled in this study divided in quantitative and categorical traits.
+\caption{\label{tab:unnamed-chunk-3}List of the 20 traits compiled in this study divided in quantitative and categorical traits.
 The different types of trait (vegetative ‘V’, floral ‘F’ and reproductive ‘R’), total records found for the 1,506 species and categories of the qualitative traits are also provided.
@@
 \addlinespace
-\textbf{F} & Style length (mm) & 1497 & \textbf{F} & Nectar & \makecell[l]{Presence \\ Absence} & 1407\\
+\textbf{F} & Style length (mm) & 1497 & \textbf{F} & Nectar & \makecell[l]{Presence \\ Absence} & 1408\\
 \addlinespace
@@
 \addlinespace
-\textbf{F} & Nectar ($\mu$l) & 485 & \textbf{R} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious} & 1489\\
+\textbf{F} & Nectar ($\mu$l) & 531 & \textbf{R} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious} & 1489\\
 \addlinespace
-\textbf{F} & Nectar (mg) & 415 & \textbf{} &  &  & \\
+\textbf{F} & Nectar (mg) & 455 & \textbf{} &  &  & \\
 \addlinespace
-\textbf{F} & Nectar concentration ($\%$) & 508 & \textbf{} &  &  & \\
+\textbf{F} & Nectar concentration ($\%$) & 558 & \textbf{} &  &  & \\
 \addlinespace
-\textbf{F} & Pollen grains per flower & 298 & \textbf{} &  &  & \\
+\textbf{F} & Pollen grains per flower & 533 & \textbf{} &  &  & \\
 \addlinespace
@@
 
-\section{RESULTS}\label{results}
+\section{RESULTS}\label{results-1}
 
@@
 \centering
-\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
-\caption{\label{fig:unnamed-chunk-2}Life history strategies for 1,236 plant
+\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
+\caption{\label{fig:unnamed-chunk-4}Life history strategies for 1,236 plant
 species from 29 plant-pollinator networks studies across the first two
@@
 \centering
-\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}Location of the qualitative traits in
+\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
+\caption{\label{fig:unnamed-chunk-5}Location of the qualitative traits in
 the trait space for traits that showed a statistical association with
@@
 
-\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
 

### 2021-08-11 Untitled/Untitled.tex
manuscript

% !TeX program = pdfLaTeX
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}

\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%

%% load any required packages here

% Pandoc citation processing

\begin{document}

\title{Title here \thanks{Grants or other notes about the article that should go on the front page
should be placed here. General acknowledgments should be placed at the
end of the article.} }
 \subtitle{Do you have a subtitle? If so, write it here}

    \titlerunning{Short form of title (if too long for head)}

\author{  Äüthör 1 \and  Âuthóř 2 \and  }

    \authorrunning{ Short form of author list if too long for running head }

\institute{
        Äüthör 1 \at
     Department of YYY, University of XXX \\
     \email{\href{mailto:abc@def}{\nolinkurl{abc@def}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Âuthóř 2 \at
     Department of ZZZ, University of WWW \\
     \email{\href{mailto:djf@wef}{\nolinkurl{djf@wef}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
    }

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
The text of your abstract. 150 -- 250 words.
\\
\keywords{
        key \and
        dictionary \and
        word \and
    }

    \subclass{
                    MSC code 1 \and
                    MSC code 2 \and
            }

\end{abstract}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

\section{Introduction}\label{intro}

Your text comes here. Separate text sections with \cite{Mislevy06Cog}.

\section{Section title}\label{sec:1}

Text with citations by \cite{Galyardt14mmm}.

\subsection{Subsection title}\label{sec:2}

as required. Don't forget to give each section and subsection a unique
label (see Sect. \ref{sec:1}).

\paragraph{Paragraph headings}\label{paragraph-headings}

Use paragraph headings as needed.

\begin{align}
a^2+b^2=c^2
\end{align}

\bibliographystyle{spphys}
\bibliography{bibliography.bib}

\end{document}

### 2021-08-11 Draft/Manuscript.Rmd
edits on manuscript

@@
 - \floatplacement{figure}{H}
-- \usepackage[skip=5pt]{caption}
+- \usepackage[skip=3pt]{caption}
+- \captionsetup[figure]{labelformat=empty}
+- \usepackage{setspace}
+
 ---
@@
 \small
+\doublespacing
 
@@
 \normalsize
-
-Plant life strategies are often delimited by vegetative and physiological traits but little is known about how floral and reproductive traits drive these strategies, and in turn shape plant interactions with floral visitors.
+\singlespacing
+
+__Plant life strategies are often delimited by vegetative and physiological traits but little is known about how floral and reproductive traits drive these strategies, and in turn shape plant interactions with floral visitors.
 Here, we compiled 13 floral, 4 reproductive and 3 vegetative traits for 1,506 plant species from 28 plant-pollinator network studies across 18 different countries.
@@
 Overall, the main traits that determined plant species’ functional roles were height, nectar concentration, pollen grains per flower, number of ovules, style length, selfing level and flower width.
-Our results highlight the need to consider plant reproductive and floral traits to improve understanding of plant life strategies and plant-pollinator interactions at broader spatial scales.
-
+Our results highlight the need to consider plant reproductive and floral traits to improve understanding of plant life strategies and plant-pollinator interactions at broader spatial scales.__
+
+\doublespacing
 \vspace{5mm}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,fig.pos = "!H",fig.cap= "Figure 1.
-Life history strategies for 1,236 plant species from 28 plant-pollinator networks studies across the first two axes of trait variation from a phylogenetically informed principal component analysis (pPCA).
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,fig.pos = "t",fig.cap= "**Fig.
+1 |** Life history strategies for 1,236 plant species from 28 plant-pollinator networks studies across the first two axes of trait variation from a phylogenetically informed principal component analysis (pPCA).
 The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) in the 2-d plane.
@@
 Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Figure S7 K and L).
+
+\blandscape
+
+\vspace*{-28mm}
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18,fig.pos = "!H",fig.cap= "**Fig.
+2 | Location of the different qualitative traits on the trait space.** The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f)."}
+
+#Set working directory
+setwd("~/R_Projects/Reproductive Traits")
+
+#Load libraries
+#LOAD LIBRARIES
+#library(phytools)
+#library(ape) #for phylogenetic distance
+#library(dplyr) #data processing
+#library(rtrees) #for phylogenetic distancelibrary(MASS)
+#library(reshape2)
+library(viridis) #COLOUR GGPLOT
+#library(MASS)
+library(ggplot2)
+library(broman) #crayon colours
+#library(cowplot)
+
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+      theme(text=element_text(color="black"),
+            axis.title=element_text( size = rel(1.75)),
+            axis.text=element_text(size = rel(1.75), color = "black"),
+            legend.title=element_text(face="bold"),
+            legend.text=element_text(),
+            legend.background=element_rect(fill="transparent"),
+            legend.key.size = unit(0.55, 'lines'),
+            panel.border=element_rect(color="black",size=1),
+            panel.grid.minor.x =element_blank(),
+            panel.grid.minor.y= element_blank(),
+             panel.grid.major= element_blank(),
+            plot.title = element_text(size = rel(1.65), face="bold")
+      ))
+}
+
+#Load data
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+#CALL the output PC for simplicity
+PC <- phyl_pca_forest
+#CHECK CONTENT
+#EIGENVALUES
+PC$Eval
+#PC score (POINTS)
+PC$S
+#PC loadings (ARROWS)
+PC$L
+
+#############################################################################################################################################################
+#COMPATIBILITY
+#############################################################################################################################################################
+#Load plots
+Compatibility <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+  dat$Compatibility <- dat_cleaning_5$Compatibility_system
+  dat$Compatibility <- as.character(dat$Compatibility)
+  dat$Compatibility[dat$Compatibility=="dioecious"] <- "Unisexual flowers"
+  dat$Compatibility[dat$Compatibility=="monoecious"] <- "Unisexual flowers"
+  dat$Compatibility[dat$Compatibility=="partially_self_compatible"] <- "Partially self compatible"
+  dat$Compatibility[dat$Compatibility=="self_compatible"] <- "Self compatible"
+  dat$Compatibility[dat$Compatibility=="self_incompatible"] <- "Self incompatible"
+  dat$Compatibility <- factor(dat$Compatibility, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
+
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Compatibility),size=1.75)+scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7"))
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .75 * mult * (get(x)),
+                      v2 = .75 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
+
+  #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+
+  #ADD LABELS
+  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
+                          label = PCAloadings$Variables, color="black",size=3)
+
+  #CHANGE THEME
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.185, 0.13)) +ggtitle("(a)")
+
+  plot
+
+}
+
+#Compatibility(PC)
+
+#############################################################################################################################################################
+#Life form
+#############################################################################################################################################################
+#Load plots
+Life_form <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+  dat$`Life form` <- dat_cleaning_5$life_form
+  dat$`Life form` <- as.character(dat$`Life form`)
+  dat$`Life form`[dat$`Life form`=="herb"] <- "Herb"
+  dat$`Life form`[dat$`Life form`=="shrub"] <- "Shrub"
+  dat$`Life form`[dat$`Life form`=="tree"] <- "Tree"
+  dat$`Life form`[dat$`Life form`=="vine"] <- "Shrub"
+
+  dat$`Life form` <- factor( dat$`Life form`, levels = c("Herb", "Shrub", "Tree"))
+
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Life form`),size=1.75)+scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .75 * mult * (get(x)),
+                      v2 = .75 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
+
+  #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+
+  #ADD LABELS
+  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
+                          label = PCAloadings$Variables, color="black",size=3)
+
+  #CHANGE THEME
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("(b)")
+
+  plot
+
+}
+
+#Life_form(PC)
+
+#############################################################################################################################################################
+#Life span
+#############################################################################################################################################################
+#Load plots
+Life_span <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+    dat$Lifespan <- dat_cleaning_5$lifespan
+    dat$Lifespan <- as.character(dat$Lifespan)
+
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Lifespan),size=1.75)+scale_color_manual(values=c("sienna4","forestgreen"))
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .75 * mult * (get(x)),
+                      v2 = .75 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
+
+  #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+
+  #ADD LABELS
+  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
+                          label = PCAloadings$Variables, color="black",size=3)
+
+  #CHANGE THEME
+  #CHANGE THEME
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.102, 0.1)) + ggtitle("(c)")
+
+  plot
+
+}
+
+#Life_span(PC)
+
+#############################################################################################################################################################
+#Flower symmetry
+#############################################################################################################################################################
+#Load plots
+Flower_sym <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+  dat$`Flower symmetry` <- dat_cleaning_5$Flower_symmetry
+  dat$`Flower symmetry` <- as.character(dat$`Flower symmetry`)
+  dat$`Flower symmetry`[dat$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
+  dat$`Flower symmetry`[dat$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"
+
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower symmetry`),size=1.75)+scale_color_manual(values=c("sienna2","purple"))
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .75 * mult * (get(x)),
+                      v2 = .75 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
+
+  #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+
+  #ADD LABELS
+  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
+                          label = PCAloadings$Variables, color="black",size=3)
+
+  #CHANGE THEME
+
+  #CHANGE THEME
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.165, 0.1)) + ggtitle("(f)")
+
+  plot
+
+}
+
+#Flower_sym(PC)
+
+#############################################################################################################################################################
+#Flower shape
+#############################################################################################################################################################
+#Load plots
+Flower_sha <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+  dat$`Flower shape` <- dat_cleaning_5$Flower_morphology
+  dat$`Flower shape` <- as.character(dat$`Flower shape`)
+  dat$`Flower shape`[dat$`Flower shape`=="Funnelform"] <- "Campanulate"
+  dat$`Flower shape`[dat$`Flower shape`=="Spike"] <- "Brush"
+
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower shape`),size=1.75)+scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .75 * mult * (get(x)),
+                      v2 = .75 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
+
+  #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+
+  #ADD LABELS
+  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
+                          label = PCAloadings$Variables, color="black",size=3)
+
+  #CHANGE THEME
+
+  #CHANGE THEME
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.13, 0.18)) + ggtitle("(e)")
+
+  plot
+
+}
+
+#Flower_sha(PC)
+
+#############################################################################################################################################################
+#Breeding system
+#############################################################################################################################################################
+#Load plots
+Breeding_syst <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+  dat$`Breeding system` <- dat_cleaning_5$Breeding_system
+  dat$`Breeding system` <- as.character(dat$`Breeding system`)
+  dat$`Breeding system` <- factor(dat$`Breeding system`, levels=c("Hermaphrodite","Monoecious" ,"Dioecious"))
+
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Breeding system`),size=1.75)+scale_color_manual(values=c("forestgreen","orange", "black"))
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .75 * mult * (get(x)),
+                      v2 = .75 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
+
+  #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+
+  #ADD LABELS
+  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
+                          label = PCAloadings$Variables, color="black",size=3)
+
+  #CHANGE THEME
+  #CHANGE THEME
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.163, 0.115)) + ggtitle("(d)")
+
+  plot
+
+}
+
+#Breeding_syst(PC)
+
+#############################################################################################################################################################
+#Nectar
+#############################################################################################################################################################
+#Load plots
+#Nectar <- function(PC, x="PC1", y="PC2") {
+#  # PC being a prcomp object
+#  data <- data.frame(PC$S)
+#  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+#  dat <- data.frame(x = data[,x], y = data[,y])
+#  
+#  #######
+#  #DENSITY FUNCTION
+#  #######
+#  get_density <- function(x, y, ...) {
+#    dens <- MASS::kde2d(x, y, ...)
+#    ix <- findInterval(x, dens$x)
+#    iy <- findInterval(y, dens$y)
+#    ii <- cbind(ix, iy)
+#    return(dens$z[ii])
+#  }
+#  
+#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+#  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
+#  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
+#  dat$Nectar[dat$Nectar=="no"] <- "Absence"
+#  plot <- plot + geom_point(data=dat, aes(-x, -y, #colour=Nectar),size=1.75)+scale_color_manual(values=c("black","grey"))
+#  
+#  ########
+#  #ADD ARROWS 
+#  ########
+#  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+#  mult <- min(
+#    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+#    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+#  )
+#  datapc <- transform(datapc,
+#                      v1 = .75 * mult * (get(x)),
+#                      v2 = .75 * mult * (get(y))
+#  )
+#  # add arrows
+#  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, #yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
+#  
+#  #Add axis with perctentage
+#  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+#
+#  
+#  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, #arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+#  
+#  #ADD LABELS
+#  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
+#  
+#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+#  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = #-(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
+#                          label = PCAloadings$Variables, color="black",size=3)
+#  
+#  #CHANGE THEME
+#  #CHANGE THEME
+#  
+#  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)") 
+#  
+#  plot
+#  
+#}
+#
+# #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")
+
+#  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flowe#r_sym(PC),ncol=3,nrow=2,  align = "hv")
+
+library(patchwork)
+Compatibility(PC) + Life_form(PC) + Life_span(PC) + Breeding_syst(PC) + Flower_sha(PC) + Flower_sym(PC) + plot_layout(ncol=3)
+
+```
+
+\elandscape
+
+\vspace{5mm}
 

### 2021-08-11 Draft/Manuscript.tex
edits on manuscript

@@
 \floatplacement{figure}{H}
-\usepackage[skip=5pt]{caption}
+\usepackage[skip=3pt]{caption}
+\captionsetup[figure]{labelformat=empty}
+\usepackage{setspace}
 \usepackage{float}
@@
 \normalsize
-
-Plant life strategies are often delimited by vegetative and
+\singlespacing
+
+\textbf{Plant life strategies are often delimited by vegetative and
 physiological traits but little is known about how floral and
@@
 reproductive and floral traits to improve understanding of plant life
-strategies and plant-pollinator interactions at broader spatial scales.
-
+strategies and plant-pollinator interactions at broader spatial scales.}
+
+\doublespacing
 \vspace{5mm} \bleft
@@
 \includegraphics{output/figures/unnamed-chunk-1-1.pdf}
-\caption{\label{fig:unnamed-chunk-1}Figure 1. Life history strategies for
-1,236 plant species from 28 plant-pollinator networks studies across the
-first two axes of trait variation from a phylogenetically informed
-principal component analysis (pPCA). The solid arrows indicate the
-direction of the different quantitative traits (flower number, plant
-height, style length, flower size, ovule number and level of autonomous
-selfing) in the 2-d plane. The length of the arrows indicate the weight
-of the variables on each principal component and the labelled icons at
-their end represent the extreme form of the trait continuum. The dashed
-lines show the opposed direction of trait variation and the non-labelled
-icons at their end illustrate the opposing extreme of the continuum.}
+\caption{\label{fig:unnamed-chunk-1}\textbf{Fig. 1 \textbar{}} Life history
+strategies for 1,236 plant species from 28 plant-pollinator networks
+studies across the first two axes of trait variation from a
+phylogenetically informed principal component analysis (pPCA). The solid
+arrows indicate the direction of the different quantitative traits
+(flower number, plant height, style length, flower size, ovule number
+and level of autonomous selfing) in the 2-d plane. The length of the
+arrows indicate the weight of the variables on each principal component
+and the labelled icons at their end represent the extreme form of the
+trait continuum. The dashed lines show the opposed direction of trait
+variation and the non-labelled icons at their end illustrate the
+opposing extreme of the continuum.}
 \end{figure}
@@
 
+\vspace*{-28mm}
+
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
+\caption{\label{fig:unnamed-chunk-2}\textbf{Fig. 2 \textbar{} Location of
+the different qualitative traits on the trait space.} The panel is
+composed by the traits that showed statistical association with the
+first two axes of trait variation: compatibility system (a), life form
+(b), lifespan (c), breeding system (d), flower shape (e) and flower
+symmetry (f).}
+\end{figure}
+
+\elandscape
+
+\vspace{5mm}
+
+\blandscape
+
 \begin{figure}[H]
-\includegraphics{output/figures/unnamed-chunk-2-1} \caption{Location of the different qualitative traits that showed statistical association with the first two axes of trait variation.
-These different traits included: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).}\label{fig:unnamed-chunk-2}
+\includegraphics{output/figures/unnamed-chunk-3-1} \caption{Location of the different qualitative traits that showed statistical association with the first two axes of trait variation.
+These different traits included: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 
-\caption{\label{tab:unnamed-chunk-3}List of the 20 traits compiled in this study divided in quantitative and categorical traits.
+\caption{\label{tab:unnamed-chunk-4}List of the 20 traits compiled in this study divided in quantitative and categorical traits.
 The different types of trait (vegetative ‘V’, floral ‘F’ and reproductive ‘R’), total records found for the 1,506 species and categories of the qualitative traits are also provided.
@@
 \centering
-\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}Life history strategies for 1,236 plant
+\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
+\caption{\label{fig:unnamed-chunk-5}Life history strategies for 1,236 plant
 species from 29 plant-pollinator networks studies across the first two
@@
 \centering
-\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
-\caption{\label{fig:unnamed-chunk-5}Location of the qualitative traits in
+\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
+\caption{\label{fig:unnamed-chunk-6}Location of the qualitative traits in
 the trait space for traits that showed a statistical association with
@@
 
-\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-7-1.pdf}
 

### 2021-08-12 Draft/Manuscript.Rmd
Paper almost ready

@@
 ---
-title: "Trade-offs among plant floral and reproductive traits determine interactions with floral visitors"
-
-author:
-  - Jose B. Lanuza^1,2^*
-  - Romina Rader^1^
-  - Jamie Stavert^3^
-  - Liam K. Kendall^4^
-  - Manu E. Saunders^1^
-  - Ignasi Bartomeus^2^
+title: \singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant floral and reproductive traits determine interactions with floral visitors
+
+#author: 
+#  - Jose B. Lanuza^1,2^*
+#  - Romina Rader^1^
+#  - Jamie Stavert^3^
+#  - Liam K. Kendall^4^
+#  - Manu E. Saunders^1^
+#  - Ignasi Bartomeus^2^
 
@@
 links-as-notes: false
+subparagraph: yes
 
@@
 - \usepackage{setspace}
+- \usepackage{titlesec}
+- \titlespacing{\title}{0pt}{\parskip}{-\parskip}
+- \usepackage[style=nature]{biblatex}
 
@@
 
-<!--# Insert author affiliations below -->
-
-\small
-\doublespacing
-
-^1^ School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia
-
-^2^ Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain
-
-^3^ Department of Conservation | Te Papa Atawhai, Auckland, New Zealand
-
-^4^ Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden
-
-`*` Corresponding author: barragansljose@gmail.com
+\vspace{-2.2cm}
+\singlespacing
+\large 
+\textbf{Jose B. Lanuza$^{1,2}*$, Romina Rader$^{1}$, Jamie Stavert$^{3}$, Liam K. Kendall$^{4}$, Manu E. Saunders$^{1}$ and Ignasi Bartomeus$^{2}$}
 
 \normalsize
-\singlespacing
 
@@
 
+\small
+\vspace{-0.5cm}
+
+\noindent\rule{\textwidth}{1pt}
+
+^1^ School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
+^2^ Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
+^3^ Department of Conservation | Te Papa Atawhai, Auckland, New Zealand.
+^4^ Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden.
+`*` e-mail: barragansljose@gmail.com
+
 \doublespacing
@@
 \bleft
+\normalsize
 
@@
 
-There is an astonishing diversity of floral structures and plant reproductive strategies among flowering plants (Barrett, 2002; Schiestl & Johnson, 2013), which have long been of interest to pollination biologists in terms of their relevance to plant-pollinator interactions.
-However, most studies that have explored reproductive (e.g., mating and compatibility systems) and floral trait (e.g., flower size or nectar provision) variation have concentrated on the individual or community level and thus, broader macroecological patterns remain poorly investigated (Carvalheiro et al., 2014; Baude et al., 2016; Munoz et al., 2016; Moeller et al., 2017; Grossenbacher et al., 2017).
-Indeed, studies depicting species’ life history strategies generally focus on vegetative traits and rarely consider reproductive traits (Salguero-Gómez et al., 2016; Rüger et al., 2018).
-As a consequence, a unified framework that explores the compromises among floral traits and their relevance to plant life strategies is currently lacking (Roddy et al., 2021).
-At the same time, there is growing interest in the determinants of plant-pollinator interactions via trait-based approaches (Fenster et al., 2004) and trait-matching analyses (Bartomeus et al., 2016).
-However, floral traits have been overlooked beyond highly specialised plant-pollinator systems (Dellinger, 2020; Roddy et al., 2021) and the role of plant reproductive biology remains little explored in plant-pollinator interactions (but see Tur et al., 2013 and Devaux et al., 2014).
-
-With the recent availability of large trait databases, plant ecological strategies are increasingly being examined (e.g., TRY, Kattge et al., 2011 and COMPADRE, Salguero‐Gómez et al., 2015), and are facilitating the identification of global patterns and constraints of plant form and function (Salguero‐Gómez et al., 2015; Díaz et al., 2016; Carmona et al., 2021).
-However, the main focus has been on vegetative traits such as leaf (Wright et al., 2004) or wood (Chave et al., 2009) trade-offs with little or no attention given to reproductive and floral traits (E‐Vojtkó et al., 2020), also critical to plant form and function.
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively (Barrett, 2003; Moeller et al., 2017).
-Further, outcrossing levels are positively correlated with flower size (Goodwillie et al., 2010).
-In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and their role in attracting pollinators (Ollerton et al., 2011).
+There is an astonishing diversity of floral structures and plant reproductive strategies among flowering plants [@barrett2002; @schiestl2013], which have long been of interest to pollination biologists in terms of their relevance to plant-pollinator interactions.
+However, most studies that have explored reproductive (e.g., mating and compatibility systems) and floral trait (e.g., flower size or nectar provision) variation have concentrated on the individual or community level and thus, broader macroecological patterns remain poorly investigated [@carvalheiro2014; @baude2016; @munoz2016; @moeller2017; @grossenbacher2017].
+Indeed, studies depicting species’ life history strategies generally focus on vegetative traits and rarely consider reproductive traits [@salguero2016, @ruger2018].
+As a consequence, a unified framework that explores the compromises among floral traits and their relevance to plant life strategies is currently lacking [@roddy2021].
+At the same time, there is growing interest in the determinants of plant-pollinator interactions via trait-based approaches [@fenster2004] and trait-matching analyses [@bartomeus2016].
+However, floral traits have been overlooked beyond highly specialised plant-pollinator systems [@dellinger2020; @roddy2021] and the role of plant reproductive biology remains little explored in plant-pollinator interactions (but see references [@tur2013; @devaux2014]).
+
+  With the recent availability of large trait databases, plant ecological strategies are increasingly being examined [e.g., TRY; @kattge2011 and COMPADRE; @salguero2015], and are facilitating the identification of global patterns and constraints of plant form and function [@salguero2016; @diaz2016; @carmona2021].
+However, the main focus has been on vegetative traits such as leaf [@wright2004] or wood [@chave2009] trade-offs with little or no attention given to reproductive and floral traits [@evojtko2020], also critical to plant form and function.
+For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively [@barrett2003; @moeller2017].
+Further, outcrossing levels are positively correlated with flower size [@goodwillie2010].
+In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and their role in attracting pollinators [@ollerton2011].
 Hence, exploring plant life strategies with reproductive and floral trade-offs, in conjunction with their pollinator dependence, is necessary for a balanced understanding of plant economics.
 
-Several studies have identified links between plant traits and plant-pollinator network properties (Lázaro et al., 2008; Bartomeus, 2013; Carvalheiro et al., 2014).
+  Several studies have identified links between plant traits and plant-pollinator network properties [@lazaro2008; @bartomeus2013; @carvalheiro2014].
 Moreover, plant traits can also define species' network roles (e.g., specialists vs generalists).
-For example, species that occupy trait space extremes are more likely to exhibit higher specialization and be more reliant on trait-matching (Junker et al., 2013; Coux et al., 2016).
-This morphological matching between plant and floral visitors can determine plant-pollinator interactions, and thus shape their interaction network structure (Stang et al., 2009; Ibanez, 2012).
+For example, species that occupy trait space extremes are more likely to exhibit higher specialization and be more reliant on trait-matching [@junker2013; @coux2016].
+This morphological matching between plant and floral visitors can determine plant-pollinator interactions, and thus shape their interaction network structure [@stang2009; @ibanez2012].
 Despite the increasing knowledge of the relevance of traits on the species network roles, little is known about how plant reproductive and floral traits determine plant species’ network roles at a macroecological scale.
@@
 
-**Plant strategies**
-
-The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Figure 1 and Figure S5) and had a phylogenetic correlation (**lambda**) of 0.76.
+**Plant strategies.** The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Fig.
+1 and Supplementary Fig.
+S5) and had a phylogenetic correlation ($\lambda$) of 0.76.
 The first principal component (PC1) represented 26.72% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the ‘flower number - flower size trade-off as already described in previous studies (Sargent et al., 2007; Kettle et al., 2011).
+We refer to this axis as the ‘flower number - flower size trade-off as already described in previous studies [@sargent2007; @kettle2011].
 Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
 The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Table S3) but style length also contributed moderately on PC1 (loading = -0.33).
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Supplementary Table S3) but style length also contributed moderately on PC1 (loading = -0.33).
 The second principal component (PC2) represented 25.05% of the trait variation and indicated a trade-off between low and high pollinator dependence.
 We refer to this axis as the ‘pollinator dependence trade-off’.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Supplementary Table S3).
 We found that high pollinator dependence was associated with larger and higher numbers of flowers, greater plant height and longer styles.
@@
 Further, PC3 explained a considerable amount of trait variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
-The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
+The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Supplementary Table S3).
 Thus, because style length was correlated with all traits on PC3 and was the main driver of variation, we refer to this axis as the ‘style length trade-off’.
-Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 23.40%); and pollen quantity (pollen grains per flower) was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 21.67%; Figure S6).
-This pPCA explained similar variance with the first two principal components (45.07%) and similar associations of traits despite some variability in the loadings (Table S4).
+Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 23.40%); and pollen quantity (pollen grains per flower) was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 21.67%; Supplementary Fig.
+S6).
+This pPCA explained similar variance with the first two principal components (45.07%) and similar associations of traits despite some variability in the loadings (Supplementary Table S4).
 
@@
 
-We found that most categorical traits were statistically associated with the first two axes of trait variation (Figure 2 and Table S2).
+We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
+2 and Supplementary Table S2).
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, p < 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , p = 0.59; PC2:  Sum of squares = 0.83, F-value = 1.43, p = 0.23) showed lack of statistical association.
-In addition, we found statistical differences (Tukey test) between the different levels of categorical traits in the trait space (Figure S7).
-Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatibile were statistically differentiated from species with partial or full self compatibility; Figure S7 A and B).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Figure S7 C and D).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Figure S7 E and F).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Figure S7 G and H).
+In addition, we found statistical differences (Tukey test) between the different levels of categorical traits in the trait space (Supplementary Fig.
+S7).
+Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatibile were statistically differentiated from species with partial or full self compatibility; Supplementary Fig.
+S7 A and B).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Supplementary Fig.
+S7 C and D).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Supplementary Fig.
+S7 E and F).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Supplementary Fig.
+S7 G and H).
 Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Figure S7 I and J).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Figure S7 K and L).
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Supplementary Fig.
+S7 I and J).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Supplementary Fig.
+S7 K and L).
 
@@
 
+**Phylogenetic signal of traits.** We found a strong phylogenetic signal (P < 0.01) in all quantitative traits (Supplementary Table S5).
+The traits that showed the highest phylogenetic signal were ovule number ($\lambda = 1$), pollen grains per flower ($\lambda = 1$) and plant height ($\lambda = 0.96$), followed by flower length ($\lambda = 0.75$), flower width ($\lambda = 0.73$), number of flowers per plant ($\lambda = 0.69$) and nectar concentration ($\lambda = 0.65$).
+The traits that showed a moderate phylogenetic signal were inflorescence width ($\lambda = 0.57$), style length ($\lambda = 0.49$) and autonomous selfing ($\lambda = 0.34$).
+Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits ($\lambda = 0.14$).
+
+**Visitation patterns.** The main axes of trait variation explained little of the overall visitation rates (conditional $R2 = 0.31$; marginal $R2 = 0.06$) but showed relevant trends when we explored the interaction with the different floral visitors guilds (Fig.
+3).
+All floral visitors guilds visited plant species with higher pollinator dependence more frequently (PC2; Fig.
+3b and Fig.
+3e).
+In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig.
+3a and Fig.
+3d).
+On the style length trade-off (PC3), Anthophila-Hymenoptera, Lepidoptera and Non-Anthophila-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
+3c and Fig.
+3f).
+Furthermore, when running an additional model that separates the most represented families of Anthophila-Hymenoptera (bees; $marginal R2 = 0.30$; $conditional R2 = 0.03$) showed that the family Apidae was the main driver of the observed patterns (Supplementary Fig.
+S8).
+
 \blandscape
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=13, fig.width=27, out.extra='',fig.cap="Location of the different qualitative traits that showed statistical association with the first two axes of trait variation.
-These different traits included: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap= "**Fig.
+2 | Fitted posterior estimates of the number of visits made by the different floral visitors guilds in relation to the three main axes of trait variation (PC1, PC2 and PC3)**.
+Bees (a, b and c) and the rest of guilds (d, e and f) were plotted separately for visualization purposes.
+In addition, we trimmed the plotting area that was over the 95th percentile to improve visualisation.
+PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off."}
 
@@
            legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
+           legend.key.size = unit(2, 'lines'),
            panel.border=element_rect(color="black",size=2.4),
@@
 
-combined <- p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "right")
+combined <- p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "bottom")
 combined + plot_layout(guides = "collect",ncol = 3)
@@
 
-**Phylogenetic signal of traits**
-
-###OLD
-
-Among flowering plants there is an astonishing diversity of floral structures and plant reproductive strategies [@barrett2002; @schiestl2013].
-Subsequently, pollination biologists have long studied their relevance on plant-pollinator interactions.
-However, despite recent efforts exploring reproductive (e.g., mating and compatibility system) and floral traits (e.g., flower size or nectar provision) with large sets of species [@carvalheiro2014; @baude2016; @munoz2016; @moeller2017; @grossenbacher2017], most studies focus on the individual, community level or specific taxa and macroecological patterns remain poorly investigated.
-For instance, studies depicting species’ life history strategies generally focus on vegetative traits and rarely consider reproductive traits on the main axes of trait variation [@diaz2016; @salguero2016].
-In addition, there is not a unified framework that explores the compromises of floral traits and their relevance on plant life strategies [@roddy2021].
-Similarly, there is growing interest in understanding what determines plant-pollinator network structure.
-Approaches with traits range from the description of pollination syndromes [e.g., @dellinger2020], to more specific trait-matching analysis [@bartomeus2016], but again the reproductive biology of the species has received little attention [but see @tur2013 and @devaux2014] and floral traits have been overlooked beyond highly specialised plant-pollinator interactions [@dellinger2020; @roddy2021].
-
-With increased availability of large trait databases, plant ecological strategies have begun to be examined more frequently [e.g., TRY, @kattge2011 and COMPADRE; @salguero2015], highlighting global patterns and constraints of plant form and function [@diaz2016; @salguero2016; @carmona2021].
-However, these resources and their research have mainly focused on vegetative traits such as the leaf [@wright2004] or wood [@chave2009] trade-offs and neglected reproductive and floral traits that also can influence the spectrum of trait variation.
-For instance, short lived and perennial species tend to have high and low levels of outcrossing respectively [@barrett2003; @moeller2017] and outcrossing levels have been shown to be positively correlated with flower size [@goodwillie2010].
-In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays cannot be understood without considering pollinators that are thought to be responsible for approximately 87.5% of the pollination of flowering plants [@ollerton2011].
-Hence, exploring plant life strategies with reproductive and floral trade-offs, in conjunction with their known pollinators seems necessary for a correct understanding of the plant economics.
-
-Several key studies have progressed knowledge of the link between traits and network properties [@lazaro2008; @bartomeus2013; @carvalheiro2014; @klumpers2019].
-Functional traits can determine whether species interact, and thus define the species network role (e.g., specialist vs generalist).
-For instance, species with high investment in floral display tend to have higher visitation rates [@stang2006; @novella-fernandez2019] and greater specialization is generally associated with occupation of the trait space extremes [@junker2013; @coux2016].
-In addition, the structure of the pollination network highly depends on the degree of trait-matching between plants and pollinators [@stang2009; @ibanez2012; @peralta2020].
-However, little is known about the consequences of reproductive traits and floral rewards on plant species roles.
-In addition, although some attempts have been made to evaluate trait relationships in plant-pollinator interactions at a global scale [@carvalheiro2014; @rech2016], macroecological patterns have been little explored.
-
-Here, we explore the major axes of plant reproductive trait variation.
-We investigate how these traits influence the structure of plant-pollinator networks by compiling a unique dataset comprising 20 plant functional traits for 1,506 species from 64 unique networks and 8 metawebs.
-First, we evaluate the major axes of reproductive trait variation and tradeoffs that determine plant form and function.
-Second, we investigate how plant species’ position in trait-space influences interaction strength with different  pollinator functional groups.
-Finally, we assess the relevance of the main axes of trait variation and traits in understanding the plant species role within the networks with complementary species level metrics (i.e., interaction strength, normalized degree and specialization).
-
-# METHODS
-
-##Plant-pollinator network studies
-
-We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
-All these studies censored plant-pollinator interactions in natural systems and were selected in order to have a wide representation of geographical areas of the world.
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted) allowing us to build a database of plants that are likely to be animal pollinated.
-Some of these networks have been already used in past studies of plant-pollinator networks [@olesen2007; @fortuna2010; @carvalheiro2014] and are available on the online networks archives The Web of Life [@fortuna2014] and Mangal [@poisot2016].
-In total, our network dataset (Table S1) constituted 60 weighted (interaction frequency) and 4 binary networks, each sampled at a unique location and year, as well as 8 meta-webs where sampled interactions were pooled across several locations and multiple years.
-
-##Taxonomy of plants and pollinators
-
-All plant species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) (plants) and ITIS (https://www.itis.gov/) (pollinators) using the R package taxize [version 0.9.99, @chamberlain2020].
+**Plant species functional roles.** The three main axes of trait variation poorly explain the variance of the different plant species level metrics (Supplementary Fig.
+S9; interaction frequency ~ PCs, $conditional R2 = 0.11$, $marginal R2 = 0.02$; normalized degree ~ PCs, $conditional R2 = 0.24$, $marginal R2 = 0.02$; and, specialization ~ PCs, $conditional R2 = 0.37$, $marginal R2 = 0.03$).
+Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
+On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers.
+On PC1, specialization showed the opposite trend.
+On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower selfing and higher for species with long styles and higher levels of selfing.
+Again, specialization showed the opposite trend to interaction frequency.
+
+When we further investigate which combination of traits drive plant network roles, we show that the regression tree for visitation frequency was best explained by plant height, nectar concentration and style length (Fig.
+4a).
+Specifically, species taller than 3.9 m had the highest interaction frequency, while species that were shorter than 3.9 m and had a nectar concentration lower than 16% had the lowest interaction frequency.
+Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
+4b).
+Species with a nectar concentration over 49% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49%, more than 21,000 pollen grains per flower and height less than 0.78 m had the lowest normalized degree.
+Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
+4c).
+Overall, plant species with the highest specialization were shorter than 1.3 m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11% of their fruits.
+In contrast, species taller or equal than 5.1 m and with lower than 14 ovules per flower had the lowest specialization values.
+
+\blandscape
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=12,fig.pos = "!H",fig.cap= "**Fig.
+4 | Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits**.
+The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
+Thus, the top node has the mean value of the named trait for the 100% of species.
+Each node has a yes/no question and when the condition is fulfilled, the branch turns to the ‘yes’ direction and when not, to the ‘no’ direction.
+This rationale is followed in all the regression trees as indicated in the first branch division of the topmost node of each tree."}
+
+########################################################################################################################################################
+#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
+########################################################################################################################################################
+#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
+
+library(rpart.plot)
+library(rpart)
+
+setwd("~/R_Projects/Reproductive Traits")
+
+v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
+nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
+d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
+
+#Set correct colnames for plotting
+colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
+
+colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
+
+colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
+
+set.seed(2)
+tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
+
+set.seed(2)
+tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
+
+set.seed(2)
+tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50) 
+par(mfrow=c(1,3))
+
+rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.5,tweak = 1.25,type = 2) 
+rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.5,tweak = 1.25,type = 2)
+rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.5,tweak = 1.25,type = 2)
+
+```
+
+\elandscape
+
+# DISCUSSION
+
+Here, we show that plant species exhibit clear trade-offs in their floral, reproductive and vegetative traits.
+These trade-offs are differentiated on three main axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
+Although these axes of trait variation did not explain overall visitation rates, we found that plant life strategies were clearly associated with different floral visitors guilds.
+Interestingly, pollen and nectar related traits were better than all other traits for characterizing plant species functional roles within their interaction networks.
+
+Over 50% of plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
+Variation in these two axes of trait variation appears to be associated with the commonly described ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life history strategies as indicated by the different floral and reproductive traits associated with plant height, life form and lifespan.
+The “slow” part of the continuum (i.e., tall trees and shrubs) had plant species with many flowers, few ovules, higher pollinator dependence, greater occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
+In contrast, species that employed the “fast” strategy (i.e., short herbs), had fewer flowers, more ovules, greater occurrence of self compatibility and lower pollinator dependence.
+Further, on the first two axes of trait variation, we found additional support for the positive association between outcrossing rate and floral display, in accordance with @goodwillie2010.
+This trend was further confirmed when looking at the specific correlation between floral display and autonomous selfing for our dataset (see Supplementary Fig.
+S10).
+
+Despite the low predictive power of the main axes of trait variation on overall visitation patterns, we found commonalities among and within floral visitors guilds across these axes that indicate the influence of life history strategies on floral visitation rate.
+For example, all guilds showed an increasing trend of visitation on plant species with higher pollinator dependence, which were also associated with larger floral displays and greater pollen quantity (Fig.
+1 and Supplementary Fig.
+S6).
+This trend is consistent with previous plant-pollinator studies that show higher visitation rates on species that make greater reproductive investment [@hegland2005; @lazaro2013; @kaiser2014].
+In regard to the flower number - flower size and style length trade-offs, different guilds showed contrasting visitation rates, which could be associated with different pollination syndromes at a macroecological scale.
+For instance, the guilds of bees and syrphids were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
+3) indicating a possible niche partitioning among these two guilds [@palmer2003; @phillips2020].
+However, these plant-pollinator associations do not account for some of the traits (i.e., pollen and nectar quantity) that had greater relevance on the species network roles (Fig.
+4) because of insufficient data availability and lack of pollinator efficiency measurements for more complete descriptions of the pollination syndromes [@dellinger2020].
+In any case, it is worth noting that this general pattern emerges in field-measured plant-pollinator networks, where other local factors such as species relative abundances, will surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016].
+
+To conclude, we provide the first description of plant floral and reproductive trade-offs using a large global dataset of plant traits and interactions with floral visitors.
+This allowed us to identify the major reproductive strategies of flowering plants and how plant life strategies determine their interaction with floral visitor guilds.
+Although the percentage of explained variation found with the first two axes (~50%) is lower than other studies that have evaluated life histories with vegetative traits [@diaz2016; @carmona2021], this percentage is consistent with @salguero2016 which characterized life strategies with both vegetative and reproductive traits (i.e., semelparity and iteroparity).
+Future work needs to integrate these floral and reproductive compromises with the already described vegetative and physiological trade-offs @diaz2016 to create a more comprehensive spectra of trait variation [@roddy2021].
+Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators [@gervasi2017; @mackin2021].
+Finally, a more complete description of the macroecological patterns of plant-pollinator interactions including unrepresented areas of the world [@poisot2021] and traits that have been largely ignored (e.g., floral rewards and plant mating system) are needed to progress in our understanding of the global patterns in plant-pollinator interactions.
+
+# MATERIALS AND METHODS
+
+**Plant-pollinator network studies.** We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
+These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
+Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
+Many of these networks are freely available either as published studies [(Olesen et al., 2007; @fortuna2010; @carvalheiro2014] or available in online archives (e.g., “The Web of Life” [@fortuna2010] and “Mangal” [@poisot2016].
+In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+
+**Taxonomy of plants and pollinators.** All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [version _0.9.99_; @chamberlain2020].
 We filled the ‘not found’ searches manually using http://www.theplantlist.org/ and http://www.mobot.org/ for plants and http://www.catalogueoflife.org/ for floral visitors.
 
-##Functional traits
-
-We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
-The selected traits were quantitative (12) and categorical (8) and belonged to three different trait types: vegetative, floral and reproductive.
-For each species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images) from a total of 30,120 cells (20 columns x 1,506 spp) we were able to fill 23,969 cells (79.6% of the dataset, see Figure S1 for missing values information per variable).
-
-\setstretch{1.25}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12}
+**Functional traits.** We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
+These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive and 3 vegetative).
+For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
+From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Supplementary Fig.
+S1 for missing values information for each trait).
+
+**Phylogenetic Distance.** We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package _rtrees_ (https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018] developed by @jin2019.
+
+\singlespacing
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=1, fig.width=14}
 setwd("~/R_Projects/Reproductive Traits")
@@
 T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-           "Presence \n Absence", "None \n Low \n Medium \n High", "Self-incomp. \n Partially self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " "),align = c("l"))
-
-Type <- c("V", "F", "F", "F", "F", "F", "F","F","F","F","F","R")
-
-Type_1 <- c("V", "V", "F", "F", "F", "R", "R", "R","","","","")
+           "Presence \n Absence", "None \n Low \n Medium \n High", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " "),align = c("l"))
+
+Type <- c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive")
+
+Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive","","","","")
 
@@
 
-kbl(dat, booktabs = T,  linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"), caption= "List of the 20 traits compiled in this study divided in quantitative and categorical traits.
-The different types of trait (vegetative ‘V’, floral ‘F’ and reproductive ‘R’), total records found for the 1,506 species and categories of the qualitative traits are also provided.
-") %>%
+kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c")) %>%
 kable_styling(full_width = T,font_size = 10) %>%
@@
 
-\setstretch{2}
-
-##Phylogenetic Distance
-
-We calculated the phylogenetic distance between different plant species using the function get_tree from the package rtrees (downloaded from github, https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018] developed by @jin2019.
-
-##Data Imputation
-
-Missing values were imputed with the function missForest [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of missForest [@penone2014].
-To extract the eigenvectors, we used the function PVRdecomp from the package PVR [@santos2018] based on the conceptual framework of @diniz-filho2012.
+\doublespacing
+
+**Data Imputation.** Trait missing values were imputed with the function _missForest_ [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of _missForest_ [@penone2014].
+To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on the conceptual framework of [@diniz-filho2012].
 Although the variable of autonomous selfing had a high percentage of missing values (68%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
-The categories of ‘none’, ‘low’, ‘medium’ and ‘high’ were converted to representative percentages of each category 0%, 13%, 50.8% and 80% respectively.
+The categories of ‘none’, ‘low’, ‘medium’ and ‘high’ were converted to representative percentages of each category 0%, 13%, 50.5% and 88% respectively.
 This reduced the percentage of missing values for this column from 68% to 35% and allowed the imputation of this variable.
-However, we were unable to impute nectar and pollen quantity due to the high percentage of missing values (Figure S1).
-The imputed dataset had 9.7% of missing values with a total of 8 categorical and 8 numerical variables.
-Finally, we conducted an additional imputation for the subset of species with quantitative information of nectar and pollen; all variables had lower than 30% of missing values (N = 636) and the total proportion of missing values in this dataset considering all variables was 13%.
-
-##Plant strategies
-
-We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width (Pearson’s correlation = 0.72, p < 0.01 and Pearson’s correlation = 0.36, p < 0.01 respectively), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-In addition, we explored the location of different qualitative traits in the trait space.
+However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Supplementary Fig.
+S1).
+Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79% of missing values.
+Further, we conducted an additional imputation on the filtered raw data by filled cells of either pollen grains per flower or microlitres of nectar.
+This subset comprised 755 species, 8.01% missing values and all traits but milligrams of nectar (~50% of missing values) were included in the imputation process.
+
+**Plant strategies.** We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, p < 0.01 and Pearson’s correlation = 0.36, p < 0.01 respectively), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
 Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values in the 2.5th-97.5th percentile range [@legendre2012].
+Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th–97.5th percentile range [@legendre2012], and thus our final dataset had 1,236 species.
 Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function phyl.pca from the package phytools [version number 0.7-70, @revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because our variables are on the same scale after the log and z-transformation [@abdi2010].
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Figure S2).
-We found little difference between the variance explained with the imputed dataset (51.08%) and the dataset without missing values (56.26%).
-In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non imputed dataset.
-Finally, we explored with the imputed dataset with quantitative information of pollen and nectar the compromises in the trait space of these two floral rewards with the other quantitative traits.
-For this, we considered solely one variable of nectar quantity (microlites of nectar per flower) in order to avoid overemphasizing nectar on the spectrum of trait variation.
-
-##Phylogenetic signal of traits
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1506) with the package phytools version 0.7-70 [@revell2012] and we used Pagel’s lambda ($\lambda$) as a measurement of the phylogenetic signal.
-For pollen and nectar traits, phylogenetic signal was calculated on the imputed dataset that included these traits (N = 636).
-
-##Networks analysis
-
-Our analyses were conducted on the subset of 60 weighted networks with interaction frequency sampled in a unique flowering season and site.
-Although floral visitors are not always pollinators and the frequency of visits does not consider each pollinator species efficiency [@ballantyne2015], interaction frequency provides valuable information of the impact of pollinators (Vázquez et al., 2005; Vázquez et al., 2012).
-Although not all networks were sampled using the same method, our aim was not to compare patterns across networks but within each network in order to obtain a general picture of associations between traits and the main axes of trait variation and plant species functional roles.
-
-*Functional groups visitation patterns*
-
-We explored the relevance of pollinator functional groups and the main axes of trait variation (pPCA with imputed dataset) on pollinator visitation per plant species.
-For this, we divided floral visitors into six main groups that differ in life form and behaviour: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Diptera-Syrphids, (iv) Diptera-Non-Syrphids, (v) Lepidoptera and (vi) Coleoptera.
-In addition, because Hymenoptera was the most represented group with 2,256 records counted and had the highest frequency of visits of all groups, we also explored visitation patterns of the most represented families of Hymenoptera on the trait space (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae).
-Apis mellifera was the species with the largest proportion of records (7.55% from the total) which is is consistent with the results of @hung2018 that showed that A.
-mellifera was the most frequent visiting species on a similar dataset of 80 interaction plant-pollinator networks on natural systems.
-Hence, to control for the relevance of Apis mellifera on the observed visitation patterns of bees, we conducted an analogous analysis excluding A.
+We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [version _0.7-70_; revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
+Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
+S2).
+We found little difference between the explained variance with the imputed dataset (51.08%) and the dataset without missing values (52.87%).
+In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
+Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
+For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
+
+**Phylogenetic signal of traits.** We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ version _0.7-70_ (Revell, 2012a) and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
+However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
+
+**Networks analyses.** Analyses were conducted on the subset of 60 weighted networks with interaction frequency sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+In total, our weighted network dataset (excluding meta-webs) included 2,256 interactions of bees (i.e.
+Anthophila-Hymenoptera) with plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-Anthophila-Hymenoptera interactions.
+Although floral visitors are not always pollinators and the frequency of visits does not consider each pollinator species efficiency [@ballantyne2015], visitation rate provides valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
+Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
+All analyses were conducted in R version _4.0.3_.
+
+**Visitation patterns.** We used Bayesian modelling (see below for details) to explore the effect of floral visitors groups and the main axes of trait variation (pPCA with imputed dataset) on floral visits per plant species.
+For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
+Moreover, because Hymenoptera-Anthophila was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the visitation rate of the main Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+In addition, we found that Apis mellifera was the floral visitor with the largest proportion of records counted (7.55% of the total).
+This is consistent with @hung2018 who showed that A.
+mellifera was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems.
+Hence, to control for the effect of Apis mellifera on the observed visitation patterns of bees, we conducted an analogous analysis excluding A.
 mellifera.
 We found that A.
-mellifera, was driving, in part, some of the observed trends on PC1 (Figure S3).
-However, we did not find major changes on PC2 and PC3.
-
-*Plant species functional roles*
-
-We investigated if the main axes of trait variation and traits explained plant species functional roles.
-We considered all uncorrelated traits apart from the principal components because this allowed us to consider quantitative and categorical traits.
-For this, we also used a modelling approach and conducted decision trees which help to interpret visually how the different traits determine species functional roles.
-We selected simple and complementary plant species level metrics with a relatively straightforward ecological interpretation relevant to our research goals: (i) sum of visits per plant species; (ii) normalized degree calculated as the number of links per plant species divided by the possible number of partners which helps comparison across networks; and (iii) specialization (d’) [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the specieslevel function from the R package bipartite  [version 2.15, @dormann2008].
-
-## Analyses
-
-First, we implemented Bayesian generalized linear mixed models using the R package brms [version 2.14.6, @burkner2017].
-We modelled the frequency of visits as a function of the main axes of trait variation and floral visitors functional groups (Visits~PC1xFG+PC2xFG+PC3xFG).
-Because we were interested in possible differences among main visitor guilds to plants with different strategies, we included the interaction between the main axes of trait variation and the distinct floral visitor functional groups.
-We added a nested random effect with networks nested on the study system to capture the network variability per study and within networks.
+mellifera, was partly driving some of the observed trends on PC1 (Supplementary Fig.
+S3).
+However, we did not detect major differences on PC2 and PC3.
+
+We implemented Bayesian generalized linear mixed models using the R package _brms_ [version _2.14.6_; @burkner2017].
+We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
+In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
+Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
 We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary history of the species and therefore lack of independence across them.
-
-Second, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation in three different models for each metric (plant species level metric~PC1+PC2+PC3).
-In addition we also explored how all uncorrelated traits (13) explained these metrics in three other models (plant species level metric ~ plant height + lifespan + life form + flower shape + flower symmetry + flower width + style length + ovule number + flowers per plant + nectar provision + autonomous selfing + compatibility system + breeding system).
-For each response variable (metric), we used different distribution families: zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization.
-Moreover, we included a nested random effect with networks nested on the study system and a phylogenetic random effect for species (as detailed above) in each model.
-
-All analyses were conducted in R Version 4.0.3.
-In addition, all models were run for 3,000 iterations with 1000 warm up iterations.
-We set delta () to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function pp_check using the bayesplot package (version 1.7.2, Gabry et al., 2019).
-
-[ADD REGRESSION TREE TO METHODS]
-We conducted regression trees in order to explore the relevance of traits on the species plant functional role.
-We repeated the procedure as the modelling analysis and we ran a decision tree for each plant level species metric (interaction frequency, normalized degree and specialization).
-We used the full datase
-
-rpart 4.1-15 (Therneau et al., 2019)
-rpart.plot 3.0.9 (Milborrow 2018)
-
-# RESULTS
-
-## Plant strategies
-The phylogenetically informed principal component analysis (pPCA) captured with the first two and three axes 51.8% and 70.97% of the trait variation respectively (Figure 1 and Figure S4) and had a phylogenetic correlation ($\lambda$) of 0.76.
-The first principal component (PC1) represented 26.72% of the trait variation and showed the flower number versus flower size compromise.
-Thus, as flower number and plant height increase, flower size, style length and ovule number decrease; and, as flower size, style length and ovule number increase, flower number and plant height decrease.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Table S2) but style length also contributed moderately on PC1 (loading = -0.33).
-The second principal component (PC2) represented 25.05% of the trait variation and showed the trade-off between low and high pollinator dependence and we refer to this axis as the pollinator dependence trade-off.
-The main driver of trait variation of PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made a moderate contribution to PC2 (loadings from 0.27 to 0.4; Table S2).
-We found that high pollinator dependence was associated with larger and higher number of flowers, greater plant height and longer styles.
-In contrast, species with high levels of autonomous selfing had a general lower investment in flower number and size, plant height and style length.
-Further, PC3 also explained a considerable amount of variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
-The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S2).
-In addition,  the pPCA with the species subset that had nectar and pollen quantity showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 24.70%); and pollen quantity was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 20.59%; Figure S5).
-This pPCA also showed similar explained variance with two components (50.06%) and similar associations of traits despite some variability in the loadings (Table S3).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,fig.cap= "Life history strategies for 1,236 plant species from 29 plant-pollinator networks studies across the first two axes of variation from a phylogenetically informed principal component analysis (pPCA).
-The solid arrows indicate the direction and weights of the six quantitative traits (flower number, plant height, style length, flower size, ovule number and autonomous selfing level) and the labelled icons at their end represent the extreme form of the trait continuum.
-The dashed lines indicate the opposed direction of trait variation and the non-labelled icons at their end illustrate the other extreme of the continuum."}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-library(magick)
-
-#Images were made by Paula Martin
-#Check her work on https://paulamartinart.com/
-
-tree <- image_read("Images/PPCA_Plot/Tree.png")
-tree_1 <- as.raster(tree)
-
-style_l <- image_read("Images/PPCA_Plot/Style_Long.png")
-style_l_1 <- as.raster(style_l)
-
-style_s <- image_read("Images/PPCA_Plot/Style_Short.png")
-style_s_1 <- as.raster(style_s)
-
-ovule_h <- image_read("Images/PPCA_Plot/Ovule_High.png")
-ovule_h_1 <- as.raster(ovule_h)
-
-ovule_l <- image_read("Images/PPCA_Plot/Ovule_Low.png")
-ovule_l_1 <- as.raster(ovule_l)
-
-selfing_n <- image_read("Images/PPCA_Plot/Selfing_None.png")
-selfing_n_1 <- as.raster(selfing_n)
-
-selfing_h <- image_read("Images/PPCA_Plot/selfing.png")
-selfing_h_1 <- as.raster(selfing_h)
-
-single_flower <- image_read("Images/PPCA_Plot/Single_Flower.png")
-single_flower_1 <- as.raster(single_flower)
-
-many_flowers <- image_read("Images/PPCA_Plot/Inflorescencia.png")
-many_flowers_1 <- as.raster(many_flowers)
-#many_flowers_1 <- image_rotate(many_flowers, 45)
-
-large_flower <- image_read("Images/PPCA_Plot/flower_big.png")
-large_flower_1 <- as.raster(large_flower)
-
-flower_small <- image_read("Images/PPCA_Plot/flower_short.png")
-flower_small_1 <- as.raster(flower_small)
-
-herb <- image_read("Images/PPCA_Plot/herb.png")
-herb_1 <- as.raster(herb)
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
-    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
-    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
-    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
-    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,7.25,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.4,3,6.2,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-plot_grid(all_spp(PC))
-
-```
-
-Evaluation of qualitative variable positions in the trait space revealed statistical association on both axes of trait variation for compatibility, breeding system, life form, lifespan and flower shape (Figure 2 and Table S4).
-In addition, flower symmetry was associated with PC2 (Sum of squares = 8.51, F-value = 14.72 , p < 0.01 ).
-Nectar provision was independent of both axes (PC1 Sum of squares = 0.37, F-value = 0.29 , p = 0.59; PC2  Sum of squares = 0.83, F-value = 1.43 , p = 0.23).
-Concerning self compatibility, we found larger differences in pollinator dependence the trade off  (i.e., species with unisexual flowers and self incompatibility were statistically differentiated from species with partially and fullyself compatibility in trait space; Figure S3 A and B).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Figure S3 C and D).
-Consequently, lifespan also followed this gradient but perennial and short lived species just differed statistically on PC2 (Figure S3 E and F).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of trait variation with the highest pollinator dependence and flower number investment (Figure S3 G and H).
-Moreover, we found that the campanulate and capitulum flower shapes were differentiated  from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies tended to occupy positions with larger flowers and greater pollination dependence, while the latter positions had higher number of flowers and autonomous selfing (Figure S3 I and J).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher pollinator dependence (Figure S3 K and L).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, fig.cap="Location of the qualitative traits in the trait space for traits that showed a statistical association with the main axis of trait variation.
-These different traits included: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f)."}
-
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.3)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.4, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank(),
-            plot.title = element_text(size = rel(1.75), face="bold")
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-#CALL the output PC for simplicity
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-Compatibility <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Compatibility <- dat_cleaning_5$Compatibility_system
-  dat$Compatibility <- as.character(dat$Compatibility)
-  dat$Compatibility[dat$Compatibility=="dioecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="monoecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-  dat$Compatibility[dat$Compatibility=="self_compatible"] <- "Self compatible"
-  dat$Compatibility[dat$Compatibility=="self_incompatible"] <- "Self incompatible"
-  dat$Compatibility <- factor(dat$Compatibility, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Compatibility),size=1.75)+scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.185, 0.13)) +ggtitle("(a)")
-
-  plot
-
-}
-
-#Compatibility(PC)
-
-#############################################################################################################################################################
-#Life form
-#############################################################################################################################################################
-#Load plots
-Life_form <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Life form` <- dat_cleaning_5$life_form
-  dat$`Life form` <- as.character(dat$`Life form`)
-  dat$`Life form`[dat$`Life form`=="herb"] <- "Herb"
-  dat$`Life form`[dat$`Life form`=="shrub"] <- "Shrub"
-  dat$`Life form`[dat$`Life form`=="tree"] <- "Tree"
-  dat$`Life form`[dat$`Life form`=="vine"] <- "Shrub"
-
-  dat$`Life form` <- factor( dat$`Life form`, levels = c("Herb", "Shrub", "Tree"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Life form`),size=1.75)+scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("(b)")
-
-  plot
-
-}
-
-#Life_form(PC)
-
-#############################################################################################################################################################
-#Life span
-#############################################################################################################################################################
-#Load plots
-Life_span <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-    dat$Lifespan <- dat_cleaning_5$lifespan
-    dat$Lifespan <- as.character(dat$Lifespan)
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Lifespan),size=1.75)+scale_color_manual(values=c("sienna4","forestgreen"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.102, 0.1)) + ggtitle("(c)")
-
-  plot
-
-}
-
-#Life_span(PC)
-
-#############################################################################################################################################################
-#Flower symmetry
-#############################################################################################################################################################
-#Load plots
-Flower_sym <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower symmetry` <- dat_cleaning_5$Flower_symmetry
-  dat$`Flower symmetry` <- as.character(dat$`Flower symmetry`)
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower symmetry`),size=1.75)+scale_color_manual(values=c("sienna2","purple"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.165, 0.1)) + ggtitle("(f)")
-
-  plot
-
-}
-
-#Flower_sym(PC)
-
-#############################################################################################################################################################
-#Flower shape
-#############################################################################################################################################################
-#Load plots
-Flower_sha <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower shape` <- dat_cleaning_5$Flower_morphology
-  dat$`Flower shape` <- as.character(dat$`Flower shape`)
-  dat$`Flower shape`[dat$`Flower shape`=="Funnelform"] <- "Campanulate"
-  dat$`Flower shape`[dat$`Flower shape`=="Spike"] <- "Brush"
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower shape`),size=1.75)+scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.13, 0.18)) + ggtitle("(e)")
-
-  plot
-
-}
-
-#Flower_sha(PC)
-
-#############################################################################################################################################################
-#Breeding system
-#############################################################################################################################################################
-#Load plots
-Breeding_syst <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Breeding system` <- dat_cleaning_5$Breeding_system
-  dat$`Breeding system` <- as.character(dat$`Breeding system`)
-  dat$`Breeding system` <- factor(dat$`Breeding system`, levels=c("Hermaphrodite","Monoecious" ,"Dioecious"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Breeding system`),size=1.75)+scale_color_manual(values=c("forestgreen","orange", "black"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.163, 0.115)) + ggtitle("(d)")
-
-  plot
-
-}
-
-#Breeding_syst(PC)
-
-#############################################################################################################################################################
-#Nectar
-#############################################################################################################################################################
-#Load plots
-#Nectar <- function(PC, x="PC1", y="PC2") {
-#  # PC being a prcomp object
-#  data <- data.frame(PC$S)
-#  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-#  dat <- data.frame(x = data[,x], y = data[,y])
-#  
-#  #######
-#  #DENSITY FUNCTION
-#  #######
-#  get_density <- function(x, y, ...) {
-#    dens <- MASS::kde2d(x, y, ...)
-#    ix <- findInterval(x, dens$x)
-#    iy <- findInterval(y, dens$y)
-#    ii <- cbind(ix, iy)
-#    return(dens$z[ii])
-#  }
-#  
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-#  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-#  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-#  plot <- plot + geom_point(data=dat, aes(-x, -y, #colour=Nectar),size=1.75)+scale_color_manual(values=c("black","grey"))
-#  
-#  ########
-#  #ADD ARROWS 
-#  ########
-#  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-#  mult <- min(
-#    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-#    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-#  )
-#  datapc <- transform(datapc,
-#                      v1 = .75 * mult * (get(x)),
-#                      v2 = .75 * mult * (get(y))
-#  )
-#  # add arrows
-#  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, #yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-#  
-#  #Add axis with perctentage
-#  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-#
-#  
-#  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, #arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-#  
-#  #ADD LABELS
-#  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-#  
-#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-#  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = #-(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-#                          label = PCAloadings$Variables, color="black",size=3)
-#  
-#  #CHANGE THEME
-#  #CHANGE THEME
-#  
-#  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)") 
-#  
-#  plot
-#  
-#}
-#
-# #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")
-
-  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),ncol=3,nrow=2,  align = "hv")
-
-```
-
-## Phylogenetic signal of traits
-
-We found a strong phylogenetic signal with statistical association (P < 0.01) for all quantitative traits (Table S4).
-The traits with the highest phylogenetic signal were ovule number ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73) and flower number per plant ($\lambda$ = 0.69).
-Finally the traits that showed lower phylogenetic signal were inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
-
-Add
-*pollen and nectar traits
-
-## Visitation patterns
-
-The overall visitation records of functional groups differed considerably.
-There were 2,256 for bees, 1,768 for non-syrphid-Diptera, 845 for syrphids, 437 for Lepidoptera, 432 for Coleoptera and 362 for non-bee-Hymenoptera.
-The main axes of trait variation explained little of the visitation patterns (conditional R2 = 0.31; marginal R2 = 0.06) but showed interesting trends for the different functional groups (Figure 3).
-Furthermore, the additional model with interaction between the most represented families of Hymenoptera and the main axis of trait variation (marginal R2 = 0.30; conditional R2 = 0.03) showed that the family Apidae was the main driver of the observed patterns (Figure S2).
-Although Apis mellifera contributed substantially to floral visitation, the general pattern of bee visitation did not change when A.
-mellifera were removed (FSX).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28}
-
-#LOAD LIBRARIES 
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(tidyverse)
-library(patchwork) #panel of plots
-library(brms)
-library(cmdstanr)
-
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2)),
-           axis.text=element_text(size = rel(1.8), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
-           plot.subtitle = element_text(face="bold",size=rel(2))
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#Plot nicely PC1
-analysis_1_just_bees <- readRDS("results_analysis_1_just_bees.rds")
-dat_analysis <- readRDS("dat_analysis_results_analysis_1_just_bees.rds")
-
-ce_pc1 <- conditional_effects(analysis_1_just_bees, effects = "PC1",points=T) 
-ce_pc1[[1]]$guild <- "bees"
-
-p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis,
-  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("")+
-  theme_ms() + theme(legend.position = "none") + ggtitle("PC1", subtitle = "(a)")
-
-#Plot nicely PC2
-ce_pc2 <- conditional_effects(analysis_1_just_bees, effects = "PC2",points=T) 
-ce_pc1[[1]]$guild <- "bees"
-
-p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,
-  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("")+
-  theme_ms() + theme(legend.position = "none") + ggtitle("PC2", subtitle = "(b)")
-#Plot nicely PC3
-ce_pc3 <- conditional_effects(analysis_1_just_bees, effects = "PC3",points=T)
-ce_pc1[[1]]$guild <- "bees"
-
-p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis,
-  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("")+
-  theme_ms() + theme(legend.position = "none") + ggtitle("PC3", subtitle = "(c)")
-
-#Plot nicely PC1
-analysis_1_no_bees <- readRDS("results_analysis_1_no_bees.rds")
-dat_analysis <- readRDS("dat_analysis_results_analysis_1_no_bees.rds")
-
-ce_pc1 <- conditional_effects(analysis_1_no_bees, effects = "PC1:guild",points=T)
-
-pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
-  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("High Flower N.    Large flowers")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
-   "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
-    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids")) + ggtitle("(d)")
-
-ce_pc2 <- conditional_effects(analysis_1_no_bees, effects = "PC2:guild",points=T)
-
-pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
-  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
-   "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
-    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids")) + ggtitle("(e)")
-
-#Plot nicely PC3
-ce_pc3 <- conditional_effects(analysis_1_no_bees, effects = "PC3:guild",points=T)
-
-pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
-  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles")+
-  theme_ms() +theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",labels=c("Anthophila (bees)","Coleoptera", "Lepidoptera", "Non-Anthophila-Hymenoptera",
-    "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
-    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-               "Non-syrphids-diptera", "Syrphids")) + ggtitle("(f)")
-
-library(patchwork)
-
-combined <- p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "right")
-combined + plot_layout(guides = "collect",ncol = 3)
-
-```
-
-## Plant species metrics
-
-The three main axes of trait variation did not explain the position or role of the plant species in the network (visits ~ PCs: conditional R2 =0.11 , marginal R2 = 0.02; normalized degree ~ PCs: conditional R2 =0.24 , marginal R2 = 0.02 and specialization ~ PCs: conditional R2 =0.37 , marginal R2 = 0.03).
-However, the functional groups showed different visitation patterns across the three main axes of trait variation (Figure 3).
-On the flower number versus size compromise, all functional groups showed higher visitation rates on plant species with greater vegetative investment and more flowers except syrphids which showed the opposite trend (higher visitation on species with larger flowers and associated traits).
-Remarkably, on the pollinator dependence trade-off, all pollinator functional groups showed an increasing visitation pattern for species with higher pollinator dependence.
-Lastly, we found that bees, Lepidoptera and non-bee Hymenoptera visited more species with larger style length and Coleoptera, Non-Syrphids Diptera and Syrphids had greater visitation patterns on species with shorter styles.
-Furthermore, with the full model that included all traits, we found that a considerable amount of  variance for plant species network metrics was explained by the different qualitative and quantitative traits (Visits ~ Traits: conditional R2 =0.32 , marginal R2 = 0.07; Normalize degree ~ Traits: conditional R2 =0.46 , marginal R2 = 0.16; Specialization ~ Traits: conditional R2 =0.49, marginal R2 = 0.14).
-
-# DISCUSSION
-
-Our work highlights that in plant-pollinator networks, plant species have displayed clear trade-offs in life strategies.
-These trade-offs can be differentiated on two main axes of trait variation: the flower number-size trade-off and the pollinator dependence trade-off.
-In addition, we found that relevant qualitative traits were aggregated within trait space, showing clear delimited strategies of different plant species within plant-pollinated systems.
-Moreover, the distinct pollinator functional groups showed changes in their interaction strength along these axes of trait variation.
-Although the main axes of trait variation explained little the variation of plant species network metrics, the full model of uncorrelated traits explained partially the plan level metrics.
-
-# CONCLUSIONS
-
-Wrap up
-
-# ACKNOWLEDGEMENTS
-
-On the shoulders of giants.
-
-# REFERENCES
+We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
+We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [version _1.7.2_; @gabry2019].
+
+**Plant species functional roles.** We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization [d’; @bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the specieslevel function from the R package _bipartite_ [version _2.15_; @dormann2008].
+
+First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric~PC1+PC2+PC3).
+For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
+Finally, we used the same random factors (networks nested within study system and phylogeny) and model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns section’.
+
+Second, to better understand these complex trait relationships, we used regression trees.
+Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
+We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
+We conducted this analysis using the _rpart_ package version _4.1-15_ (Therneau et al., 2015) with method _‘anova’_ with a minimum of 50 observations per terminal node and we used _rpart.plot_ version _3.0.9_ [@milborrow2015] to plot the regression trees.
+We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
+We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
+We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig.
+S4).
+
+# References
 
@@
 \eleft
-
-<!--# Tables below -->
-
-\listoftables
-
-<!--# Figures below -->
-
-\listoffigures
-
-# SUPPLEMENTARY MATERIAL {-}
-
-\beginsupplement
-
-<!--# To have separate reference lists for main text and Suppl Mat, see https://gist.github.com/Pakillo/e1407cc0632a9202813ec2aee2434cc3 -->

### 2021-08-12 Draft/Manuscript.tex
Paper almost ready

@@
 \hypersetup{
-            pdftitle={Trade-offs among plant floral and reproductive traits determine interactions with floral visitors},
-            pdfauthor={Jose B. Lanuza1,2*; Romina Rader1; Jamie Stavert3; Liam K. Kendall4; Manu E. Saunders1; Ignasi Bartomeus2},
+            pdftitle={ Trade-offs among plant floral and reproductive traits determine interactions with floral visitors},
             colorlinks=true,
@@
 \setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
 
@@
 \usepackage{setspace}
+\usepackage{titlesec}
+\titlespacing{\title}{0pt}{\parskip}{-\parskip}
+\usepackage[style=nature]{biblatex}
 \usepackage{float}
@@
 
-\title{Trade-offs among plant floral and reproductive traits determine
-interactions with floral visitors}
-\author{Jose B.
-Lanuza\textsuperscript{1,2}* \and Romina Rader\textsuperscript{1} \and Jamie Stavert\textsuperscript{3} \and Liam K.
-Kendall\textsuperscript{4} \and Manu E.
-Saunders\textsuperscript{1} \and Ignasi Bartomeus\textsuperscript{2}}
-\date{}
+\title{\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant floral and
+reproductive traits determine interactions with floral visitors}
+\author{}
+\date{\vspace{-2.5em}}
 
@@
 
-\small
-\doublespacing
-
-\textsuperscript{1} School of Environmental and Rural Science,
-University of New England, Armidale, New South Wales 2350, Australia
-
-\textsuperscript{2} Estación Biológica de Doñana (EBD-CSIC), E-41092
-Seville, Spain
-
-\textsuperscript{3} Department of Conservation \textbar{} Te Papa
-Atawhai, Auckland, New Zealand
-
-\textsuperscript{4} Centre for Environmental and Climate Science, Lund
-University, Sölvegatan 37, S-223 62 Lund, Sweden
-
-\texttt{*} Corresponding author:
-\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
+\vspace{-2.2cm} \singlespacing
+\large 
+\textbf{Jose B. Lanuza$^{1,2}*$, Romina Rader$^{1}$, Jamie Stavert$^{3}$, Liam K. Kendall$^{4}$, Manu E. Saunders$^{1}$ and Ignasi Bartomeus$^{2}$}
 
 \normalsize
-\singlespacing
 
@@
 
+\small
+\vspace{-0.5cm}
+
+\noindent\rule{\textwidth}{1pt}
+
+\textsuperscript{1} School of Environmental and Rural Science,
+University of New England, Armidale, New South Wales 2350, Australia.
+\textsuperscript{2} Estación Biológica de Doñana (EBD-CSIC), E-41092
+Seville, Spain. \textsuperscript{3} Department of Conservation
+\textbar{} Te Papa Atawhai, Auckland, New Zealand. \textsuperscript{4}
+Centre for Environmental and Climate Science, Lund University,
+Sölvegatan 37, S-223 62 Lund, Sweden. \texttt{*} e-mail:
+\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
+
 \doublespacing
 \vspace{5mm} \bleft
+\normalsize
 
 There is an astonishing diversity of floral structures and plant
-reproductive strategies among flowering plants (Barrett, 2002; Schiestl
-\& Johnson, 2013), which have long been of interest to pollination
-biologists in terms of their relevance to plant-pollinator interactions.
-However, most studies that have explored reproductive (e.g., mating and
-compatibility systems) and floral trait (e.g., flower size or nectar
-provision) variation have concentrated on the individual or community
-level and thus, broader macroecological patterns remain poorly
-investigated (Carvalheiro et al., 2014; Baude et al., 2016; Munoz et
-al., 2016; Moeller et al., 2017; Grossenbacher et al., 2017). Indeed,
-studies depicting species' life history strategies generally focus on
-vegetative traits and rarely consider reproductive traits
-(Salguero-Gómez et al., 2016; Rüger et al., 2018). As a consequence, a
-unified framework that explores the compromises among floral traits and
-their relevance to plant life strategies is currently lacking (Roddy et
-al., 2021). At the same time, there is growing interest in the
-determinants of plant-pollinator interactions via trait-based approaches
-(Fenster et al., 2004) and trait-matching analyses (Bartomeus et al.,
-2016). However, floral traits have been overlooked beyond highly
-specialised plant-pollinator systems (Dellinger, 2020; Roddy et al.,
-2021) and the role of plant reproductive biology remains little explored
-in plant-pollinator interactions (but see Tur et al., 2013 and Devaux et
-al., 2014).
+reproductive strategies among flowering
+plants\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}},
+which have long been of interest to pollination biologists in terms of
+their relevance to plant-pollinator interactions. However, most studies
+that have explored reproductive (e.g., mating and compatibility systems)
+and floral trait (e.g., flower size or nectar provision) variation have
+concentrated on the individual or community level and thus, broader
+macroecological patterns remain poorly
+investigated\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3}--\protect\hyperlink{ref-grossenbacher2017}{7}}.
+Indeed, studies depicting species' life history strategies generally
+focus on vegetative traits and rarely consider reproductive
+traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}}. As a
+consequence, a unified framework that explores the compromises among
+floral traits and their relevance to plant life strategies is currently
+lacking\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}}. At the
+same time, there is growing interest in the determinants of
+plant-pollinator interactions via trait-based
+approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{11}} and
+trait-matching
+analyses\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{12}}.
+However, floral traits have been overlooked beyond highly specialised
+plant-pollinator
+systems\textsuperscript{\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-dellinger2020}{13}}
+and the role of plant reproductive biology remains little explored in
+plant-pollinator interactions (but see
+references\textsuperscript{\protect\hyperlink{ref-tur2013}{14},\protect\hyperlink{ref-devaux2014}{15}}).
 
 With the recent availability of large trait databases, plant ecological
-strategies are increasingly being examined (e.g., TRY, Kattge et al.,
-2011 and COMPADRE, Salguero‐Gómez et al., 2015), and are facilitating
-the identification of global patterns and constraints of plant form and
-function (Salguero‐Gómez et al., 2015; Díaz et al., 2016; Carmona et
-al., 2021). However, the main focus has been on vegetative traits such
-as leaf (Wright et al., 2004) or wood (Chave et al., 2009) trade-offs
-with little or no attention given to reproductive and floral traits
-(E‐Vojtkó et al., 2020), also critical to plant form and function. For
-instance, short lived versus perennial species tend to have low versus
-high levels of outcrossing, respectively (Barrett, 2003; Moeller et al.,
-2017). Further, outcrossing levels are positively correlated with flower
-size (Goodwillie et al., 2010). In addition, the presence of costly
-rewards (e.g., pollen or nectar) and showy flowers or floral displays
-can only be understood through consideration of plant species' reliance
-upon animal pollination (pollinator dependence) and their role in
-attracting pollinators (Ollerton et al., 2011). Hence, exploring plant
-life strategies with reproductive and floral trade-offs, in conjunction
-with their pollinator dependence, is necessary for a balanced
-understanding of plant economics.
+strategies are increasingly being
+examined\textsuperscript{\protect\hyperlink{ref-kattge2011}{16},\protect\hyperlink{ref-salguero2015}{17}},
+and are facilitating the identification of global patterns and
+constraints of plant form and
+function\textsuperscript{\protect\hyperlink{ref-salguero2016}{8},\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}}.
+However, the main focus has been on vegetative traits such as
+leaf\textsuperscript{\protect\hyperlink{ref-wright2004}{20}} or
+wood\textsuperscript{\protect\hyperlink{ref-chave2009}{21}} trade-offs
+with little or no attention given to reproductive and floral
+traits\textsuperscript{\protect\hyperlink{ref-evojtko2020}{22}}, also
+critical to plant form and function. For instance, short lived versus
+perennial species tend to have low versus high levels of outcrossing,
+respectively\textsuperscript{\protect\hyperlink{ref-moeller2017}{6},\protect\hyperlink{ref-barrett2003}{23}}.
+Further, outcrossing levels are positively correlated with flower
+size\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{24}}. In
+addition, the presence of costly rewards (e.g., pollen or nectar) and
+showy flowers or floral displays can only be understood through
+consideration of plant species' reliance upon animal pollination
+(pollinator dependence) and their role in attracting
+pollinators\textsuperscript{\protect\hyperlink{ref-ollerton2011}{25}}.
+Hence, exploring plant life strategies with reproductive and floral
+trade-offs, in conjunction with their pollinator dependence, is
+necessary for a balanced understanding of plant economics.
 
 Several studies have identified links between plant traits and
-plant-pollinator network properties (Lázaro et al., 2008; Bartomeus,
-2013; Carvalheiro et al., 2014). Moreover, plant traits can also define
-species' network roles (e.g., specialists vs generalists). For example,
-species that occupy trait space extremes are more likely to exhibit
-higher specialization and be more reliant on trait-matching (Junker et
-al., 2013; Coux et al., 2016). This morphological matching between plant
-and floral visitors can determine plant-pollinator interactions, and
-thus shape their interaction network structure (Stang et al., 2009;
-Ibanez, 2012). Despite the increasing knowledge of the relevance of
-traits on the species network roles, little is known about how plant
-reproductive and floral traits determine plant species' network roles at
-a macroecological scale.
+plant-pollinator network
+properties\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3},\protect\hyperlink{ref-lazaro2008}{26},\protect\hyperlink{ref-bartomeus2013}{27}}.
+Moreover, plant traits can also define species' network roles (e.g.,
+specialists vs generalists). For example, species that occupy trait
+space extremes are more likely to exhibit higher specialization and be
+more reliant on
+trait-matching\textsuperscript{\protect\hyperlink{ref-junker2013}{28},\protect\hyperlink{ref-coux2016}{29}}.
+This morphological matching between plant and floral visitors can
+determine plant-pollinator interactions, and thus shape their
+interaction network
+structure\textsuperscript{\protect\hyperlink{ref-stang2009}{30},\protect\hyperlink{ref-ibanez2012}{31}}.
+Despite the increasing knowledge of the relevance of traits on the
+species network roles, little is known about how plant reproductive and
+floral traits determine plant species' network roles at a
+macroecological scale.
 
@@
 
-\textbf{Plant strategies}
-
-The phylogenetically informed principal component analysis (pPCA)
-captured by the first two and three axes 51.8\% and 70.97\% of trait
-variation, respectively (Figure 1 and Figure S5) and had a phylogenetic
-correlation (\textbf{lambda}) of 0.76. The first principal component
-(PC1) represented 26.72\% of the trait variation and indicated a
-trade-off between flower number and flower size. We refer to this axis
-as the `flower number - flower size trade-off as already described in
-previous studies (Sargent et al., 2007; Kettle et al., 2011). Hence, one
-end of the spectrum comprised species with high investment in flower
-number and plant height but small flower size, short style length and
-low ovule number. The other end of this spectrum comprised species that
-were short in height and invested in large flowers, long styles, many
-ovules, but few flowers. The main contributing traits to PC1 were plant
-height, flower number, ovule number and flower size (loadings
-\textgreater{} \textbar{}0.5\textbar{}; Table S3) but style length also
-contributed moderately on PC1 (loading = -0.33). The second principal
-component (PC2) represented 25.05\% of the trait variation and indicated
-a trade-off between low and high pollinator dependence. We refer to this
-axis as the `pollinator dependence trade-off'. The main driver of trait
-variation on PC2 was autonomous selfing (loading = 0.85) but the other
-traits (except ovule number) also made moderate contributions (loadings
-from 0.27 to 0.4; Table S3). We found that high pollinator dependence
-was associated with larger and higher numbers of flowers, greater plant
-height and longer styles. In contrast, species with high levels of
-autonomous selfing tended to have fewer and smaller flowers, had shorter
-styles and were shorter in height. Further, PC3 explained a considerable
-amount of trait variability (19.17\%) and the main contributors to this
-axis were style length (loading = -0.66) and the degree of autonomous
-selfing (loading = -0.51). The remaining traits, apart from ovule
-number, were moderately correlated to changes on PC3 (loadings from
--0.23 to -0.46; Table S3). Thus, because style length was correlated
-with all traits on PC3 and was the main driver of variation, we refer to
-this axis as the `style length trade-off'. Further, the pPCA with the
-subset of species that had nectar and pollen quantity data showed that
-nectar quantity (microlitres of nectar per flower) was positively
-associated with flower size, style length and ovule number (PC1,
-23.40\%); and pollen quantity (pollen grains per flower) was positively
-correlated with flower number and plant height and negatively associated
-with autonomous selfing (PC2, 21.67\%; Figure S6). This pPCA explained
-similar variance with the first two principal components (45.07\%) and
-similar associations of traits despite some variability in the loadings
-(Table S4).
+\textbf{Plant strategies.} The phylogenetically informed principal
+component analysis (pPCA) captured by the first two and three axes
+51.8\% and 70.97\% of trait variation, respectively (Fig. 1 and
+Supplementary Fig. S5) and had a phylogenetic correlation (\(\lambda\))
+of 0.76. The first principal component (PC1) represented 26.72\% of the
+trait variation and indicated a trade-off between flower number and
+flower size. We refer to this axis as the `flower number - flower size
+trade-off as already described in previous
+studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{32},\protect\hyperlink{ref-kettle2011}{33}}.
+Hence, one end of the spectrum comprised species with high investment in
+flower number and plant height but small flower size, short style length
+and low ovule number. The other end of this spectrum comprised species
+that were short in height and invested in large flowers, long styles,
+many ovules, but few flowers. The main contributing traits to PC1 were
+plant height, flower number, ovule number and flower size (loadings
+\textgreater{} \textbar{}0.5\textbar{}; Supplementary Table S3) but
+style length also contributed moderately on PC1 (loading = -0.33). The
+second principal component (PC2) represented 25.05\% of the trait
+variation and indicated a trade-off between low and high pollinator
+dependence. We refer to this axis as the `pollinator dependence
+trade-off'. The main driver of trait variation on PC2 was autonomous
+selfing (loading = 0.85) but the other traits (except ovule number) also
+made moderate contributions (loadings from 0.27 to 0.4; Supplementary
+Table S3). We found that high pollinator dependence was associated with
+larger and higher numbers of flowers, greater plant height and longer
+styles. In contrast, species with high levels of autonomous selfing
+tended to have fewer and smaller flowers, had shorter styles and were
+shorter in height. Further, PC3 explained a considerable amount of trait
+variability (19.17\%) and the main contributors to this axis were style
+length (loading = -0.66) and the degree of autonomous selfing (loading =
+-0.51). The remaining traits, apart from ovule number, were moderately
+correlated to changes on PC3 (loadings from -0.23 to -0.46;
+Supplementary Table S3). Thus, because style length was correlated with
+all traits on PC3 and was the main driver of variation, we refer to this
+axis as the `style length trade-off'. Further, the pPCA with the subset
+of species that had nectar and pollen quantity data showed that nectar
+quantity (microlitres of nectar per flower) was positively associated
+with flower size, style length and ovule number (PC1, 23.40\%); and
+pollen quantity (pollen grains per flower) was positively correlated
+with flower number and plant height and negatively associated with
+autonomous selfing (PC2, 21.67\%; Supplementary Fig. S6). This pPCA
+explained similar variance with the first two principal components
+(45.07\%) and similar associations of traits despite some variability in
+the loadings (Supplementary Table S4).
 
@@
 We found that most categorical traits were statistically associated with
-the first two axes of trait variation (Figure 2 and Table S2). Flower
-symmetry, which was only associated with PC2 (Sum of squares = 8.51,
-F-value = 14.72, p \textless{} 0.01 ), and nectar provision, which was
-independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 ,
-p = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, p = 0.23) showed
-lack of statistical association. In addition, we found statistical
-differences (Tukey test) between the different levels of categorical
-traits in the trait space (Figure S7). Regarding self compatibility, we
-found larger differences on PC2 (i.e., species with unisexual flowers
-that were self incompatibile were statistically differentiated from
-species with partial or full self compatibility; Figure S7 A and B).
-Life forms differed statistically across both axes of trait variation
-and followed a gradient of larger life forms (trees and shrubs) with
-higher pollinator dependence to smaller ones (herbs) with lower
-pollinator dependence (Figure S7 C and D). Consequently, lifespan also
-followed this gradient but perennial and short lived species only
-differed statistically on PC2 (Figure S7 E and F). Species with
-unisexual flowers (monoecious and dioecious) were clustered on both
-extremes of the first two principal components and had the highest
-pollinator dependence and highest number of flowers (Figure S7 G and H).
-Moreover, we found that the campanulate and capitulum flower shapes were
+the first two axes of trait variation (Fig. 2 and Supplementary Table
+S2). Flower symmetry, which was only associated with PC2 (Sum of squares
+= 8.51, F-value = 14.72, p \textless{} 0.01 ), and nectar provision,
+which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37,
+F-value = 0.29 , p = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, p
+= 0.23) showed lack of statistical association. In addition, we found
+statistical differences (Tukey test) between the different levels of
+categorical traits in the trait space (Supplementary Fig. S7). Regarding
+self compatibility, we found larger differences on PC2 (i.e., species
+with unisexual flowers that were self incompatibile were statistically
+differentiated from species with partial or full self compatibility;
+Supplementary Fig. S7 A and B). Life forms differed statistically across
+both axes of trait variation and followed a gradient of larger life
+forms (trees and shrubs) with higher pollinator dependence to smaller
+ones (herbs) with lower pollinator dependence (Supplementary Fig. S7 C
+and D). Consequently, lifespan also followed this gradient but perennial
+and short lived species only differed statistically on PC2
+(Supplementary Fig. S7 E and F). Species with unisexual flowers
+(monoecious and dioecious) were clustered on both extremes of the first
+two principal components and had the highest pollinator dependence and
+highest number of flowers (Supplementary Fig. S7 G and H). Moreover, we
+found that the campanulate and capitulum flower shapes were
 differentiated from tube, papilionaceous, open and brush shapes in the
@@
 pollinator dependence, while the latter had higher flower number and
-greater autonomous selfing (Figure S7 I and J). Regarding flower
-symmetry, zygomorphic flowers were associated with lower levels of
-pollinator dependence, whereas actinomorphic flowers had higher levels
-of pollinator dependence (Figure S7 K and L).
+greater autonomous selfing (Supplementary Fig. S7 I and J). Regarding
+flower symmetry, zygomorphic flowers were associated with lower levels
+of pollinator dependence, whereas actinomorphic flowers had higher
+levels of pollinator dependence (Supplementary Fig. S7 K and L).
 
@@
 
+\textbf{Phylogenetic signal of traits.} We found a strong phylogenetic
+signal (P \textless{} 0.01) in all quantitative traits (Supplementary
+Table S5). The traits that showed the highest phylogenetic signal were
+ovule number (\(\lambda = 1\)), pollen grains per flower
+(\(\lambda = 1\)) and plant height (\(\lambda = 0.96\)), followed by
+flower length (\(\lambda = 0.75\)), flower width (\(\lambda = 0.73\)),
+number of flowers per plant (\(\lambda = 0.69\)) and nectar
+concentration (\(\lambda = 0.65\)). The traits that showed a moderate
+phylogenetic signal were inflorescence width (\(\lambda = 0.57\)), style
+length (\(\lambda = 0.49\)) and autonomous selfing (\(\lambda = 0.34\)).
+Finally, microliters of nectar per flower showed the lowest phylogenetic
+signal of all traits (\(\lambda = 0.14\)).
+
+\textbf{Visitation patterns.} The main axes of trait variation explained
+little of the overall visitation rates (conditional \(R2 = 0.31\);
+marginal \(R2 = 0.06\)) but showed relevant trends when we explored the
+interaction with the different floral visitors guilds (Fig. 3). All
+floral visitors guilds visited plant species with higher pollinator
+dependence more frequently (PC2; Fig. 3b and Fig. 3e). In addition, all
+guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera,
+non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on
+species with small numerous flowers (PC1; Fig. 3a and Fig. 3d). On the
+style length trade-off (PC3), Anthophila-Hymenoptera, Lepidoptera and
+Non-Anthophila-Hymenoptera showed greater visitation rates on plant
+species with larger styles and higher levels of selfing; while
+Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation
+rates on species with shorter styles and lower selfing (Fig. 3c and Fig.
+3f). Furthermore, when running an additional model that separates the
+most represented families of Anthophila-Hymenoptera (bees;
+\(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) showed that the
+family Apidae was the main driver of the observed patterns
+(Supplementary Fig. S8).
+
 \blandscape
 
-\begin{figure}[H]
-\includegraphics{output/figures/unnamed-chunk-3-1} \caption{Location of the different qualitative traits that showed statistical association with the first two axes of trait variation.
-These different traits included: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).}\label{fig:unnamed-chunk-3}
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
+\caption{\label{fig:unnamed-chunk-3}\textbf{Fig. 2 \textbar{} Fitted
+posterior estimates of the number of visits made by the different floral
+visitors guilds in relation to the three main axes of trait variation
+(PC1, PC2 and PC3)}. Bees (a, b and c) and the rest of guilds (d, e and
+f) were plotted separately for visualization purposes. In addition, we
+trimmed the plotting area that was over the 95th percentile to improve
+visualisation. PC1 represents the flower number - flower size trade-off,
+PC2 represents the pollinator dependence trade-off and PC3, the style
+length trade-off.}
 \end{figure}
@@
 
-\textbf{Phylogenetic signal of traits}
-
-\subsubsection{OLD}\label{old}
-
-Among flowering plants there is an astonishing diversity of floral
-structures and plant reproductive strategies (Barrett
-\protect\hyperlink{ref-barrett2002}{2002}, Schiestl and Johnson
-\protect\hyperlink{ref-schiestl2013}{2013}). Subsequently, pollination
-biologists have long studied their relevance on plant-pollinator
-interactions. However, despite recent efforts exploring reproductive
-(e.g., mating and compatibility system) and floral traits (e.g., flower
-size or nectar provision) with large sets of species (Carvalheiro et al.
-\protect\hyperlink{ref-carvalheiro2014}{2014}, Baude et al.
-\protect\hyperlink{ref-baude2016}{2016}, Munoz et al.
-\protect\hyperlink{ref-munoz2016}{2016}, Grossenbacher et al.
-\protect\hyperlink{ref-grossenbacher2017}{2017}, Moeller et al.
-\protect\hyperlink{ref-moeller2017}{2017}), most studies focus on the
-individual, community level or specific taxa and macroecological
-patterns remain poorly investigated. For instance, studies depicting
-species' life history strategies generally focus on vegetative traits
-and rarely consider reproductive traits on the main axes of trait
-variation (Díaz et al. \protect\hyperlink{ref-diaz2016}{2016},
-Salguero-Gómez et al. \protect\hyperlink{ref-salguero2016}{2016}). In
-addition, there is not a unified framework that explores the compromises
-of floral traits and their relevance on plant life strategies (Roddy et
-al. \protect\hyperlink{ref-roddy2021}{2021}). Similarly, there is
-growing interest in understanding what determines plant-pollinator
-network structure. Approaches with traits range from the description of
-pollination syndromes (e.g., Dellinger
-\protect\hyperlink{ref-dellinger2020}{2020}), to more specific
-trait-matching analysis (Bartomeus et al.
-\protect\hyperlink{ref-bartomeus2016}{2016}), but again the reproductive
-biology of the species has received little attention (but see Tur et al.
-\protect\hyperlink{ref-tur2013}{2013} and @devaux2014) and floral traits
-have been overlooked beyond highly specialised plant-pollinator
-interactions (Dellinger \protect\hyperlink{ref-dellinger2020}{2020},
-Roddy et al. \protect\hyperlink{ref-roddy2021}{2021}).
-
-With increased availability of large trait databases, plant ecological
-strategies have begun to be examined more frequently (e.g., TRY, Kattge
-et al. \protect\hyperlink{ref-kattge2011}{2011} and COMPADRE,
-Salguero-Gómez et al. \protect\hyperlink{ref-salguero2015}{2015}),
-highlighting global patterns and constraints of plant form and function
-(Díaz et al. \protect\hyperlink{ref-diaz2016}{2016}, Salguero-Gómez et
-al. \protect\hyperlink{ref-salguero2016}{2016}, Carmona et al.
-\protect\hyperlink{ref-carmona2021}{2021}). However, these resources and
-their research have mainly focused on vegetative traits such as the leaf
-(Wright et al. \protect\hyperlink{ref-wright2004}{2004}) or wood (Chave
-et al. \protect\hyperlink{ref-chave2009}{2009}) trade-offs and neglected
-reproductive and floral traits that also can influence the spectrum of
-trait variation. For instance, short lived and perennial species tend to
-have high and low levels of outcrossing respectively (Barrett
-\protect\hyperlink{ref-barrett2003}{2003}, Moeller et al.
-\protect\hyperlink{ref-moeller2017}{2017}) and outcrossing levels have
-been shown to be positively correlated with flower size (Goodwillie et
-al. \protect\hyperlink{ref-goodwillie2010}{2010}). In addition, the
-presence of costly rewards (e.g., pollen or nectar) and showy flowers or
-floral displays cannot be understood without considering pollinators
-that are thought to be responsible for approximately 87.5\% of the
-pollination of flowering plants (Ollerton et al.
-\protect\hyperlink{ref-ollerton2011}{2011}). Hence, exploring plant life
-strategies with reproductive and floral trade-offs, in conjunction with
-their known pollinators seems necessary for a correct understanding of
-the plant economics.
-
-Several key studies have progressed knowledge of the link between traits
-and network properties (Lázaro et al.
-\protect\hyperlink{ref-lazaro2008}{2008}, Bartomeus
-\protect\hyperlink{ref-bartomeus2013}{2013}, Carvalheiro et al.
-\protect\hyperlink{ref-carvalheiro2014}{2014}, Klumpers et al.
-\protect\hyperlink{ref-klumpers2019}{2019}). Functional traits can
-determine whether species interact, and thus define the species network
-role (e.g., specialist vs generalist). For instance, species with high
-investment in floral display tend to have higher visitation rates (Stang
-et al. \protect\hyperlink{ref-stang2006}{2006}, Novella-Fernandez et al.
-\protect\hyperlink{ref-novella-fernandez2019}{2019}) and greater
-specialization is generally associated with occupation of the trait
-space extremes (Junker et al. \protect\hyperlink{ref-junker2013}{2013},
-Coux et al. \protect\hyperlink{ref-coux2016}{2016}). In addition, the
-structure of the pollination network highly depends on the degree of
-trait-matching between plants and pollinators (Stang et al.
-\protect\hyperlink{ref-stang2009}{2009}, Ibanez
-\protect\hyperlink{ref-ibanez2012}{2012}, Peralta et al.
-\protect\hyperlink{ref-peralta2020}{2020}). However, little is known
-about the consequences of reproductive traits and floral rewards on
-plant species roles. In addition, although some attempts have been made
-to evaluate trait relationships in plant-pollinator interactions at a
-global scale (Carvalheiro et al.
-\protect\hyperlink{ref-carvalheiro2014}{2014}, Rech et al.
-\protect\hyperlink{ref-rech2016}{2016}), macroecological patterns have
-been little explored.
-
-Here, we explore the major axes of plant reproductive trait variation.
-We investigate how these traits influence the structure of
-plant-pollinator networks by compiling a unique dataset comprising 20
-plant functional traits for 1,506 species from 64 unique networks and 8
-metawebs. First, we evaluate the major axes of reproductive trait
-variation and tradeoffs that determine plant form and function. Second,
-we investigate how plant species' position in trait-space influences
-interaction strength with different pollinator functional groups.
-Finally, we assess the relevance of the main axes of trait variation and
-traits in understanding the plant species role within the networks with
-complementary species level metrics (i.e., interaction strength,
-normalized degree and specialization).
-
-\section{METHODS}\label{methods}
-
-\subsection{Plant-pollinator network
-studies}\label{plant-pollinator-network-studies}
-
-We selected 28 studies from 18 different countries that constituted a
-total of 64 plant-pollinator networks. All these studies censored
-plant-pollinator interactions in natural systems and were selected in
-order to have a wide representation of geographical areas of the world.
-Although these studies differ in sampling effort and methodology, all
-studies provided information about plant-pollinator interactions
-(weighted and non-weighted) allowing us to build a database of plants
-that are likely to be animal pollinated. Some of these networks have
-been already used in past studies of plant-pollinator networks (Olesen
-et al. \protect\hyperlink{ref-olesen2007}{2007}, Fortuna et al.
-\protect\hyperlink{ref-fortuna2010}{2010}, Carvalheiro et al.
-\protect\hyperlink{ref-carvalheiro2014}{2014}) and are available on the
-online networks archives The Web of Life (Fortuna et al.
-\protect\hyperlink{ref-fortuna2014}{2014}) and Mangal (Poisot et al.
-\protect\hyperlink{ref-poisot2016}{2016}). In total, our network dataset
-(Table S1) constituted 60 weighted (interaction frequency) and 4 binary
-networks, each sampled at a unique location and year, as well as 8
-meta-webs where sampled interactions were pooled across several
+\textbf{Plant species functional roles.} The three main axes of trait
+variation poorly explain the variance of the different plant species
+level metrics (Supplementary Fig. S9; interaction frequency
+\textasciitilde{} PCs, \(conditional R2 = 0.11\),
+\(marginal R2 = 0.02\); normalized degree \textasciitilde{} PCs,
+\(conditional R2 = 0.24\), \(marginal R2 = 0.02\); and, specialization
+\textasciitilde{} PCs, \(conditional R2 = 0.37\),
+\(marginal R2 = 0.03\)). Overall, the most notable trends were found on
+PC1 and PC3 for interaction frequency and specialization. On the flower
+number - flower size trade-off (PC1), interaction frequency was higher
+for plant species with more flowers but was lower for plant species with
+larger flowers. On PC1, specialization showed the opposite trend. On the
+style length trade-off (PC3), interaction frequency was lower for plants
+with shorter styles and lower selfing and higher for species with long
+styles and higher levels of selfing. Again, specialization showed the
+opposite trend to interaction frequency.
+
+When we further investigate which combination of traits drive plant
+network roles, we show that the regression tree for visitation frequency
+was best explained by plant height, nectar concentration and style
+length (Fig. 4a). Specifically, species taller than 3.9 m had the
+highest interaction frequency, while species that were shorter than 3.9
+m and had a nectar concentration lower than 16\% had the lowest
+interaction frequency. Normalized degree was best explained by nectar
+concentration, pollen grains per flower, plant height, flower width and
+autonomous selfing (Fig. 4b). Species with a nectar concentration over
+49\% had the highest levels of normalized degree, whereas species with
+nectar concentration lower than 49\%, more than 21,000 pollen grains per
+flower and height less than 0.78 m had the lowest normalized degree.
+Finally, specialization was best explained by plant height, ovule
+number, pollen grains per flower and autonomous selfing (Fig. 4c).
+Overall, plant species with the highest specialization were shorter than
+1.3 m, had more than 14,000 pollen grains per flower and autonomously
+self-pollinated less than 11\% of their fruits. In contrast, species
+taller or equal than 5.1 m and with lower than 14 ovules per flower had
+the lowest specialization values.
+
+\blandscape
+
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
+\caption{\label{fig:unnamed-chunk-4}\textbf{Fig. 4 \textbar{} Regression
+tree analysis of interaction frequency (log-transformed), normalized
+degree and specialization for the subset of species with quantitative
+data for pollen and nectar traits}. The superior value inside the node
+indicates the mean value of the different species-level metric and the
+lower value, the percentage of species that are considered in each node.
+Thus, the top node has the mean value of the named trait for the 100\%
+of species. Each node has a yes/no question and when the condition is
+fulfilled, the branch turns to the `yes' direction and when not, to the
+`no' direction. This rationale is followed in all the regression trees
+as indicated in the first branch division of the topmost node of each
+tree.}
+\end{figure}
+
+\elandscape
+
+\section{DISCUSSION}\label{discussion}
+
+Here, we show that plant species exhibit clear trade-offs in their
+floral, reproductive and vegetative traits. These trade-offs are
+differentiated on three main axes of trait variation: (i) flower number
+- flower size, (ii) pollinator dependence and (iii) style length.
+Although these axes of trait variation did not explain overall
+visitation rates, we found that plant life strategies were clearly
+associated with different floral visitors guilds. Interestingly, pollen
+and nectar related traits were better than all other traits for
+characterizing plant species functional roles within their interaction
+networks.
+
+Over 50\% of plant trait variation was captured by the flower number -
+flower size and pollinator dependence trade-offs. Variation in these two
+axes of trait variation appears to be associated with the commonly
+described `fast-slow continuum' in
+plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}} and
+animal\textsuperscript{\protect\hyperlink{ref-healy2019}{34}} life
+history strategies as indicated by the different floral and reproductive
+traits associated with plant height, life form and lifespan. The
+``slow'' part of the continuum (i.e., tall trees and shrubs) had plant
+species with many flowers, few ovules, higher pollinator dependence,
+greater occurrence of self-incompatibility and more complex breeding
+systems (e.g., monoecious and dioecious species). In contrast, species
+that employed the ``fast'' strategy (i.e., short herbs), had fewer
+flowers, more ovules, greater occurrence of self compatibility and lower
+pollinator dependence. Further, on the first two axes of trait
+variation, we found additional support for the positive association
+between outcrossing rate and floral display, in accordance with
+\protect\hyperlink{ref-goodwillie2010}{24}. This trend was further
+confirmed when looking at the specific correlation between floral
+display and autonomous selfing for our dataset (see Supplementary Fig.
+S10).
+
+Despite the low predictive power of the main axes of trait variation on
+overall visitation patterns, we found commonalities among and within
+floral visitors guilds across these axes that indicate the influence of
+life history strategies on floral visitation rate. For example, all
+guilds showed an increasing trend of visitation on plant species with
+higher pollinator dependence, which were also associated with larger
+floral displays and greater pollen quantity (Fig. 1 and Supplementary
+Fig. S6). This trend is consistent with previous plant-pollinator
+studies that show higher visitation rates on species that make greater
+reproductive
+investment\textsuperscript{\protect\hyperlink{ref-hegland2005}{35}--\protect\hyperlink{ref-kaiser2014}{37}}.
+In regard to the flower number - flower size and style length
+trade-offs, different guilds showed contrasting visitation rates, which
+could be associated with different pollination syndromes at a
+macroecological scale. For instance, the guilds of bees and syrphids
+were clearly associated with opposing life-strategies on PC1 and PC3
+(Fig. 3) indicating a possible niche partitioning among these two
+guilds\textsuperscript{\protect\hyperlink{ref-palmer2003}{38},\protect\hyperlink{ref-phillips2020}{39}}.
+However, these plant-pollinator associations do not account for some of
+the traits (i.e., pollen and nectar quantity) that had greater relevance
+on the species network roles (Fig. 4) because of insufficient data
+availability and lack of pollinator efficiency measurements for more
+complete descriptions of the pollination
+syndromes\textsuperscript{\protect\hyperlink{ref-dellinger2020}{13}}. In
+any case, it is worth noting that this general pattern emerges in
+field-measured plant-pollinator networks, where other local factors such
+as species relative abundances, will surely explain part of the observed
+variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{12},\protect\hyperlink{ref-vazquez2007}{40},\protect\hyperlink{ref-encinas2012}{41}}.
+
+To conclude, we provide the first description of plant floral and
+reproductive trade-offs using a large global dataset of plant traits and
+interactions with floral visitors. This allowed us to identify the major
+reproductive strategies of flowering plants and how plant life
+strategies determine their interaction with floral visitor guilds.
+Although the percentage of explained variation found with the first two
+axes (\textasciitilde{}50\%) is lower than other studies that have
+evaluated life histories with vegetative
+traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}},
+this percentage is consistent with
+\protect\hyperlink{ref-salguero2016}{8} which characterized life
+strategies with both vegetative and reproductive traits (i.e.,
+semelparity and iteroparity). Future work needs to integrate these
+floral and reproductive compromises with the already described
+vegetative and physiological trade-offs
+\protect\hyperlink{ref-diaz2016}{18} to create a more comprehensive
+spectra of trait
+variation\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}}.
+Further, the varying level of phylogenetic signal among traits deserves
+further attention to understand evolutionary changes on mating and
+flower morphology in response to
+pollinators\textsuperscript{\protect\hyperlink{ref-gervasi2017}{42},\protect\hyperlink{ref-mackin2021}{43}}.
+Finally, a more complete description of the macroecological patterns of
+plant-pollinator interactions including unrepresented areas of the
+world\textsuperscript{\protect\hyperlink{ref-poisot2021}{44}} and traits
+that have been largely ignored (e.g., floral rewards and plant mating
+system) are needed to progress in our understanding of the global
+patterns in plant-pollinator interactions.
+
+\section{MATERIALS AND METHODS}\label{materials-and-methods}
+
+\textbf{Plant-pollinator network studies.} We selected 28 studies from
+18 different countries that constituted a total of 64 plant-pollinator
+networks. These studies recorded plant-pollinator interactions in
+natural systems and were selected so that we had broad geographical
+representation. Although these studies differ in sampling effort and
+methodology, all studies provided information about plant-pollinator
+interactions (weighted and non-weighted), which we used to build a
+database of plant species that are likely to be animal pollinated. Many
+of these networks are freely available either as published
+studies\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3},\protect\hyperlink{ref-fortuna2010}{45}}
+or available in online archives (e.g., ``The Web of
+Life''\textsuperscript{\protect\hyperlink{ref-fortuna2010}{45}} and
+``Mangal''\textsuperscript{\protect\hyperlink{ref-poisot2016}{46}}. In
+total, our network dataset (see Supplementary Table S1) constituted 60
+weighted (interaction frequency) and 4 unweighted (presence/absence of
+the interaction) networks, each sampled at a unique location and year,
+as well as eight meta-webs where interactions were pooled across several
 locations and multiple years.
 
-\subsection{Taxonomy of plants and
-pollinators}\label{taxonomy-of-plants-and-pollinators}
-
-All plant species names, genera, families and orders were retrieved and
-standardized from the taxonomy data sources NCBI
-(\url{https://www.ncbi.nlm.nih.gov/taxonomy}) (plants) and ITIS
-(\url{https://www.itis.gov/}) (pollinators) using the R package taxize
-(version 0.9.99, Chamberlain et al.
-\protect\hyperlink{ref-chamberlain2020}{2020}). We filled the `not
-found' searches manually using \url{http://www.theplantlist.org/} and
-\url{http://www.mobot.org/} for plants and
-\url{http://www.catalogueoflife.org/} for floral visitors.
-
-\subsection{Functional traits}\label{functional-traits}
-
-We selected 20 different functional traits based on their relevance to
-plant reproduction and data availability (Table 1). The selected traits
-were quantitative (12) and categorical (8) and belonged to three
-different trait types: vegetative, floral and reproductive. For each
-species, we undertook an extensive literature and online search across a
-wide range of resources (plant databases, online floras, books, journals
-and images) from a total of 30,120 cells (20 columns x 1,506 spp) we
-were able to fill 23,969 cells (79.6\% of the dataset, see Figure S1 for
-missing values information per variable).
-
-\setstretch{1.25}
-
-\begin{table}
-
-\caption{\label{tab:unnamed-chunk-4}List of the 20 traits compiled in this study divided in quantitative and categorical traits.
-The different types of trait (vegetative ‘V’, floral ‘F’ and reproductive ‘R’), total records found for the 1,506 species and categories of the qualitative traits are also provided.
-}
-\centering
-\fontsize{10}{12}\selectfont
+\textbf{Taxonomy of plants and pollinators.} All species names, genera,
+families and orders were retrieved and standardized from the taxonomy
+data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for
+plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the
+R package
+\emph{taxize}\textsuperscript{\protect\hyperlink{ref-chamberlain2020}{47}}.
+We filled the `not found' searches manually using
+\url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for
+plants and \url{http://www.catalogueoflife.org/} for floral visitors.
+
+\textbf{Functional traits.} We selected 20 different functional traits
+based on their relevance to plant reproduction and data availability
+(Table 1). These included twelve quantitative and eight categorical
+traits belonging to three broader trait groupings (13 floral, 4
+reproductive and 3 vegetative). For each plant species, we undertook an
+extensive literature and online search across a wide range of resources
+(plant databases, online floras, books, journals and images). From a
+total of 30,120 cells (20 columns × 1,506 species) we were able to fill
+24,341 cells (80.8\% of the dataset, see Supplementary Fig. S1 for
+missing values information for each trait).
+
+\textbf{Phylogenetic Distance.} We calculated the phylogenetic distance
+between different plant species using the function \emph{get\_tree} from
+the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}),
+which downloads phylogenetic distances from the extended R
+implementation of the Open Tree of
+Life\textsuperscript{\protect\hyperlink{ref-smith2018}{48}} developed by
+\protect\hyperlink{ref-jin2019}{49}.
+
+\singlespacing
+
+\begingroup\fontsize{10}{12}\selectfont
+
 \begin{tabu} to \linewidth {>{}c>{\raggedright}X>{\centering}X>{}c>{\raggedright}X>{\raggedright}X>{\centering}X}
@@
 \midrule
-\textbf{V} & Plant height (m) & 1470 & \textbf{V} & Lifepan & \makecell[l]{Short-lived \\ Perennial} & 1466\\
+\textbf{Vegetative} & Plant height (m) & 1470 & \textbf{Vegetative} & Lifepan & \makecell[l]{Short-lived \\ Perennial} & 1466\\
 \addlinespace
-\textbf{F} & Flower width (mm) & 1472 & \textbf{V} & Life form & \makecell[l]{Herb \\ Shrub \\ Tree} & 1472\\
+\textbf{Floral} & Flower width (mm) & 1472 & \textbf{Vegetative} & Life form & \makecell[l]{Herb \\ Shrub \\ Tree} & 1472\\
 \addlinespace
-\textbf{F} & Flower length (mm) & 1401 & \textbf{F} & Flower shape & \makecell[l]{Brush \\ Campanulate \\ Capitulum \\ Open \\ Papilionaceous \\ Tube} & 1458\\
+\textbf{Floral} & Flower length (mm) & 1401 & \textbf{Floral} & Flower shape & \makecell[l]{Brush \\ Campanulate \\ Capitulum \\ Open \\ Papilionaceous \\ Tube} & 1458\\
 \addlinespace
-\textbf{F} & Inflorescence width (mm) & 1496 & \textbf{F} & Flower symmetry & \makecell[l]{Actinomorphic \\ Zygomorphic} & 1478\\
+\textbf{Floral} & Inflorescence width (mm) & 1496 & \textbf{Floral} & Flower symmetry & \makecell[l]{Actinomorphic \\ Zygomorphic} & 1478\\
 \addlinespace
-\textbf{F} & Style length (mm) & 1497 & \textbf{F} & Nectar & \makecell[l]{Presence \\ Absence} & 1408\\
+\textbf{Floral} & Style length (mm) & 1497 & \textbf{Floral} & Nectar & \makecell[l]{Presence \\ Absence} & 1408\\
 \addlinespace
-\textbf{F} & Ovules per flower & 1457 & \textbf{R} & Autonomous selfing & \makecell[l]{None \\ Low \\ Medium \\ High} & 987\\
+\textbf{Floral} & Ovules per flower & 1457 & \textbf{Reproductive} & Autonomous selfing & \makecell[l]{None \\ Low \\ Medium \\ High} & 987\\
 \addlinespace
-\textbf{F} & Flowers per plant & 1468 & \textbf{R} & Compatibility system & \makecell[l]{Self-incomp. \\ Partially self-comp. \\ Self-comp.} & 1253\\
+\textbf{Floral} & Flowers per plant & 1468 & \textbf{Reproductive} & Compatibility system & \makecell[l]{Self-incomp. \\ Part. self-comp. \\ Self-comp.} & 1253\\
 \addlinespace
-\textbf{F} & Nectar ($\mu$l) & 531 & \textbf{R} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious} & 1489\\
+\textbf{Floral} & Nectar ($\mu$l) & 531 & \textbf{Reproductive} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious} & 1489\\
 \addlinespace
-\textbf{F} & Nectar (mg) & 455 & \textbf{} &  &  & \\
+\textbf{Floral} & Nectar (mg) & 455 & \textbf{} &  &  & \\
 \addlinespace
-\textbf{F} & Nectar concentration ($\%$) & 558 & \textbf{} &  &  & \\
+\textbf{Floral} & Nectar concentration ($\%$) & 558 & \textbf{} &  &  & \\
 \addlinespace
-\textbf{F} & Pollen grains per flower & 533 & \textbf{} &  &  & \\
+\textbf{Floral} & Pollen grains per flower & 533 & \textbf{} &  &  & \\
 \addlinespace
-\textbf{R} & Autonomous selfing (fruit set) & 992 & \textbf{} &  &  & \\
+\textbf{Reproductive} & Autonomous selfing (fruit set) & 992 & \textbf{} &  &  & \\
 \bottomrule
 \end{tabu}
-\end{table}
-
-\setstretch{2}
-
-\subsection{Phylogenetic Distance}\label{phylogenetic-distance}
-
-We calculated the phylogenetic distance between different plant species
-using the function get\_tree from the package rtrees (downloaded from
-github, \url{https://github.com/daijiang/rtrees}), which downloads
-phylogenetic distances from the extended R implementation of the Open
-Tree of Life (Smith and Brown \protect\hyperlink{ref-smith2018}{2018})
-developed by Jin and Qian (\protect\hyperlink{ref-jin2019}{2019}).
-
-\subsection{Data Imputation}\label{data-imputation}
-
-Missing values were imputed with the function missForest (Stekhoven and
-Bühlmann \protect\hyperlink{ref-stekhoven2012}{2012}) which allows
-imputation of data sets with continuous and categorical variables. We
-accounted for the phylogenetic distance among species on the imputation
-process by including the eigenvectors of a principal component analysis
-of the phylogenetic distance (PCoA) which has been shown to improve the
-performance of missForest (Penone et al.
-\protect\hyperlink{ref-penone2014}{2014}). To extract the eigenvectors,
-we used the function PVRdecomp from the package PVR (Santos et al.
-\protect\hyperlink{ref-santos2018}{2018}) based on the conceptual
-framework of Diniz-Filho et al.
-(\protect\hyperlink{ref-diniz-filho2012}{2012}). Although the variable
-of autonomous selfing had a high percentage of missing values (68\%), we
-were able to solve this by back transforming the qualitative column of
-autonomous selfing to numerical. The categories of `none', `low',
-`medium' and `high' were converted to representative percentages of each
-category 0\%, 13\%, 50.8\% and 80\% respectively. This reduced the
-percentage of missing values for this column from 68\% to 35\% and
-allowed the imputation of this variable. However, we were unable to
-impute nectar and pollen quantity due to the high percentage of missing
-values (Figure S1). The imputed dataset had 9.7\% of missing values with
-a total of 8 categorical and 8 numerical variables. Finally, we
-conducted an additional imputation for the subset of species with
-quantitative information of nectar and pollen; all variables had lower
-than 30\% of missing values (N = 636) and the total proportion of
-missing values in this dataset considering all variables was 13\%.
-
-\subsection{Plant strategies}\label{plant-strategies}
-
-We explored the trade-offs between different quantitative plant
-functional traits with a phylogenetically informed Principal Component
-Analysis (pPCA). We did not include the quantitative variables of flower
-length and inflorescence width because they were highly and moderately
-correlated to flower width (Pearson's correlation = 0.72, p \textless{}
-0.01 and Pearson's correlation = 0.36, p \textless{} 0.01 respectively),
-and thus we avoided overemphasizing flower size on the spectrum of trait
-variation. In addition, we explored the location of different
-qualitative traits in the trait space. Prior to the analyses, we
+
+\endgroup{}
+
+\doublespacing
+
+\textbf{Data Imputation.} Trait missing values were imputed with the
+function
+\emph{missForest}\textsuperscript{\protect\hyperlink{ref-stekhoven2012}{50}}
+which allows imputation of data sets with continuous and categorical
+variables. We accounted for the phylogenetic distance among species on
+the imputation process by including the eigenvectors of a principal
+component analysis of the phylogenetic distance (PCoA) which has been
+shown to improve the performance of
+\emph{missForest}\textsuperscript{\protect\hyperlink{ref-penone2014}{51}}.
+To extract the eigenvectors, we used the function \emph{PVRdecomp} from
+the package
+\emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{52}} based
+on the conceptual framework
+of\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{53}}.
+Although the variable of autonomous selfing had a high percentage of
+missing values (68\%), we were able to solve this by back transforming
+the qualitative column of autonomous selfing to numerical. The
+categories of `none', `low', `medium' and `high' were converted to
+representative percentages of each category 0\%, 13\%, 50.5\% and 88\%
+respectively. This reduced the percentage of missing values for this
+column from 68\% to 35\% and allowed the imputation of this variable.
+However, we were unable to include nectar and pollen traits on the
+imputation process because of the high percentage of missing values
+(Supplementary Fig. S1). Hence, the imputed dataset had 1,506 species,
+seven categorical and eight numerical variables and 5.79\% of missing
+values. Further, we conducted an additional imputation on the filtered
+raw data by filled cells of either pollen grains per flower or
+microlitres of nectar. This subset comprised 755 species, 8.01\% missing
+values and all traits but milligrams of nectar (\textasciitilde{}50\% of
+missing values) were included in the imputation process.
+
+\textbf{Plant strategies.} We explored the trade-offs between different
+quantitative plant functional traits with a phylogenetically informed
+Principal Component Analysis (pPCA). We did not include the quantitative
+variables of flower length and inflorescence width because they were
+highly and moderately correlated to flower width respectively (Pearson's
+correlation = 0.72, p \textless{} 0.01 and Pearson's correlation = 0.36,
+p \textless{} 0.01 respectively), and thus we avoided overemphasizing
+flower size on the spectrum of trait variation. Although qualitative
+traits were not included in the dimensionality reduction analysis, we
+also investigated the association of the different qualitative traits
+with the main axes of trait variation. Prior to the analyses, we
 excluded outliers and standardized the data. Due to the high sensitivity
-of dimensionality reduction to outliers, we excluded values in the
-2.5th-97.5th percentile range (Legendre and Legendre
-\protect\hyperlink{ref-legendre2012}{2012}). Then, we log transformed
-the variables to reduce the influence of outliers and z-transformed (X=
-0, SD=1) so that all variables were within the same numerical range. We
-performed the pPCA using the function phyl.pca from the package phytools
-(version number 0.7-70, Revell \protect\hyperlink{ref-revell2012}{2012})
-with the method lambda (\(\lambda\)) that calculates the phylogenetic
-correlation between 0 (phylogenetic independence) and 1 (shared
-evolutionary history) and we implemented the mode covariance because our
-variables are on the same scale after the log and z-transformation (Abdi
-and Williams \protect\hyperlink{ref-abdi2010}{2010}). Moreover, to
-corroborate that our imputation of missing values did not affect our
-results, we conducted a pPCA on the full dataset without missing values
-(Figure S2). We found little difference between the variance explained
-with the imputed dataset (51.08\%) and the dataset without missing
-values (56.26\%). In addition, the loadings on each principal component
-had a similar contribution and correlation patterns, with the exception
-of plant height which showed slight variations between the imputed and
-non imputed dataset. Finally, we explored with the imputed dataset with
-quantitative information of pollen and nectar the compromises in the
-trait space of these two floral rewards with the other quantitative
-traits. For this, we considered solely one variable of nectar quantity
-(microlites of nectar per flower) in order to avoid overemphasizing
-nectar on the spectrum of trait variation.
-
-\subsection{Phylogenetic signal of
-traits}\label{phylogenetic-signal-of-traits}
-
-We calculated the phylogenetic signal of the different quantitative
-traits on the imputed dataset with the full set of species (N = 1506)
-with the package phytools version 0.7-70 (Revell
-\protect\hyperlink{ref-revell2012}{2012}) and we used Pagel's lambda
-(\(\lambda\)) as a measurement of the phylogenetic signal. For pollen
-and nectar traits, phylogenetic signal was calculated on the imputed
-dataset that included these traits (N = 636).
-
-\subsection{Networks analysis}\label{networks-analysis}
-
-Our analyses were conducted on the subset of 60 weighted networks with
-interaction frequency sampled in a unique flowering season and site.
-Although floral visitors are not always pollinators and the frequency of
-visits does not consider each pollinator species efficiency (Ballantyne
-et al. \protect\hyperlink{ref-ballantyne2015}{2015}), interaction
-frequency provides valuable information of the impact of pollinators
-(Vázquez et al., 2005; Vázquez et al., 2012). Although not all networks
-were sampled using the same method, our aim was not to compare patterns
-across networks but within each network in order to obtain a general
-picture of associations between traits and the main axes of trait
-variation and plant species functional roles.
-
-\emph{Functional groups visitation patterns}
-
-We explored the relevance of pollinator functional groups and the main
-axes of trait variation (pPCA with imputed dataset) on pollinator
-visitation per plant species. For this, we divided floral visitors into
-six main groups that differ in life form and behaviour: (i)
-Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other
-non-bee Hymenoptera), (iii) Diptera-Syrphids, (iv) Diptera-Non-Syrphids,
-(v) Lepidoptera and (vi) Coleoptera. In addition, because Hymenoptera
-was the most represented group with 2,256 records counted and had the
-highest frequency of visits of all groups, we also explored visitation
-patterns of the most represented families of Hymenoptera on the trait
-space (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae).
-Apis mellifera was the species with the largest proportion of records
-(7.55\% from the total) which is is consistent with the results of Hung
-et al. (\protect\hyperlink{ref-hung2018}{2018}) that showed that A.
-mellifera was the most frequent visiting species on a similar dataset of
-80 interaction plant-pollinator networks on natural systems. Hence, to
-control for the relevance of Apis mellifera on the observed visitation
-patterns of bees, we conducted an analogous analysis excluding A.
-mellifera. We found that A. mellifera, was driving, in part, some of the
-observed trends on PC1 (Figure S3). However, we did not find major
-changes on PC2 and PC3.
-
-\emph{Plant species functional roles}
-
-We investigated if the main axes of trait variation and traits explained
-plant species functional roles. We considered all uncorrelated traits
-apart from the principal components because this allowed us to consider
-quantitative and categorical traits. For this, we also used a modelling
-approach and conducted decision trees which help to interpret visually
-how the different traits determine species functional roles. We selected
-simple and complementary plant species level metrics with a relatively
+of dimensionality reduction to outliers, we excluded values within the
+2.5th--97.5th percentile
+range\textsuperscript{\protect\hyperlink{ref-legendre2012}{54}}, and
+thus our final dataset had 1,236 species. Then, we log transformed the
+variables to reduce the influence of outliers and z-transformed (X= 0,
+SD=1) so that all variables were within the same numerical range. We
+performed the pPCA using the function \emph{phyl.pca} from the package
+\emph{phytools} {[}version \emph{0.7-70}; revell2012{]} with the method
+lambda (\(\lambda\)) that calculates the phylogenetic correlation
+between 0 (phylogenetic independence) and 1 (shared evolutionary
+history) and we implemented the mode covariance because values for each
+variables were on the same scale following
+transformation\textsuperscript{\protect\hyperlink{ref-abdi2010}{55}}.
+Moreover, to corroborate that our imputation of missing values did not
+affect our results, we conducted a pPCA on the full dataset without
+missing values (see Supplementary Fig. S2). We found little difference
+between the explained variance with the imputed dataset (51.08\%) and
+the dataset without missing values (52.87\%). In addition, the loadings
+on each principal component had a similar contribution and correlation
+patterns, with the exception of plant height which showed slight
+variations between the imputed and non-imputed dataset. Finally, we
+conducted an additional phylogenetic informed principal component
+analysis for the subset of species with pollen and nectar quantity. For
+this, we included all quantitative traits considered in the main pPCA
+plus pollen grains and microlitres of nectar per flower.
+
+\textbf{Phylogenetic signal of traits.} We calculated the phylogenetic
+signal of the different quantitative traits on the imputed dataset with
+the full set of species (N = 1,506) with the package \emph{phytools}
+version \emph{0.7-70} (Revell, 2012a) and we used Pagel's \(\lambda\) as
+a measurement of the phylogenetic signal. However, for pollen and nectar
+traits, phylogenetic signal was calculated only on the subset of species
+that had quantitative information for these traits (N = 755).
+
+\textbf{Networks analyses.} Analyses were conducted on the subset of 60
+weighted networks with interaction frequency sampled in a unique
+flowering season and site, which included 556 plant and 1,126 pollinator
+species. In total, our weighted network dataset (excluding meta-webs)
+included 2,256 interactions of bees (i.e.~Anthophila-Hymenoptera) with
+plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae
+interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions
+and 362 non-Anthophila-Hymenoptera interactions. Although floral
+visitors are not always pollinators and the frequency of visits does not
+consider each pollinator species
+efficiency\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{56}},
+visitation rate provides valuable information of the contribution of
+floral visitors to
+pollination\textsuperscript{\protect\hyperlink{ref-vazquez2005}{57},\protect\hyperlink{ref-vazquez2012}{58}}.
+Sampling methods varied across networks but this was accounted for in
+analyses by considering them in the random effects of the modelling
+process. All analyses were conducted in R version \emph{4.0.3}.
+
+\textbf{Visitation patterns.} We used Bayesian modelling (see below for
+details) to explore the effect of floral visitors groups and the main
+axes of trait variation (pPCA with imputed dataset) on floral visits per
+plant species. For this, we divided floral visitors into six main guilds
+that differ in life form, behaviour and are likely to play a similar
+ecological role: (i) Hymenoptera-Anthophila (bees), (ii)
+Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii)
+Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi)
+Coleoptera. Moreover, because Hymenoptera-Anthophila was the most
+represented group with 2,256 records and had the highest frequency of
+visits of all groups, we also explored the visitation rate of the main
+Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae,
+Halictidae and Megachilidae) on the trait space. In addition, we found
+that Apis mellifera was the floral visitor with the largest proportion
+of records counted (7.55\% of the total). This is consistent with
+\protect\hyperlink{ref-hung2018}{59} who showed that A. mellifera was
+the most frequent floral visitor in a similar dataset of 80
+plant-pollinator networks in natural ecosystems. Hence, to control for
+the effect of Apis mellifera on the observed visitation patterns of
+bees, we conducted an analogous analysis excluding A. mellifera. We
+found that A. mellifera, was partly driving some of the observed trends
+on PC1 (Supplementary Fig. S3). However, we did not detect major
+differences on PC2 and PC3.
+
+We implemented Bayesian generalized linear mixed models using the R
+package
+\emph{brms}\textsuperscript{\protect\hyperlink{ref-burkner2017}{60}}. We
+modelled the frequency of visits as a function of the main axes of plant
+trait variation and their interactions with floral visitor functional
+groups (Visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation
+patterns among floral visitors groups to plants with different
+strategies, we included interactions between the main axes of trait
+variation (PC1, PC2 and PC3) and the floral visitor guilds. In this
+model, we added a nested random effect of networks nested within the
+study system to capture the variation in networks among studies and
+within networks. Moreover, we included the phylogenetic covariance
+matrix as a random factor due to the possible shared evolutionary
+histories of species and therefore lack of independence across them. We
+specified this model with a zero inflated negative binomial distribution
+and weakly informative priors from the brms function. We run this model
+for 3,000 iterations and with previous 1,000 warm up iterations. We set
+delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized
+the posterior predictive checks with the function \emph{pp\_check} using
+the \emph{bayesplot}
+package\textsuperscript{\protect\hyperlink{ref-gabry2019}{61}}.
+
+\textbf{Plant species functional roles.} We investigated whether
+different quantitative traits determined plant species functional roles
+using Bayesian modelling and regression trees. For this, we selected
+simple and complementary species-level network metrics commonly applied
+in bipartite network
+studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{62}} with a
 straightforward ecological interpretation relevant to our research
-goals: (i) sum of visits per plant species; (ii) normalized degree
-calculated as the number of links per plant species divided by the
-possible number of partners which helps comparison across networks; and
-(iii) specialization (d') (Blüthgen et al.
-\protect\hyperlink{ref-bluthgen2006}{2006}), which measures the
-deviation of an expected random choice of the available interaction
-partners and ranges between 0 (maximum generalization) and 1 (maximum
-specialization). Normalized degree and specialization were calculated
-with the specieslevel function from the R package bipartite (version
-2.15, Dormann et al. \protect\hyperlink{ref-dormann2008}{2008}).
-
-\subsection{Analyses}\label{analyses}
-
-First, we implemented Bayesian generalized linear mixed models using the
-R package brms (version 2.14.6, Bürkner
-\protect\hyperlink{ref-burkner2017}{2017}). We modelled the frequency of
-visits as a function of the main axes of trait variation and floral
-visitors functional groups
-(Visits\textasciitilde{}PC1xFG+PC2xFG+PC3xFG). Because we were
-interested in possible differences among main visitor guilds to plants
-with different strategies, we included the interaction between the main
-axes of trait variation and the distinct floral visitor functional
-groups. We added a nested random effect with networks nested on the
-study system to capture the network variability per study and within
-networks. We specified this model with a zero inflated negative binomial
-distribution and weakly informative priors from the brms function.
-Moreover, we included the phylogenetic covariance matrix as a random
-factor due to the possible shared evolutionary history of the species
-and therefore lack of independence across them.
-
-Second, we modelled the distinct plant species metrics (sum of visits,
+goals. The different plant species-level metrics were: (i) sum of visits
+per plant species; (ii) normalized degree, calculated as the number of
+links per plant species divided by the total possible number of
+partners; and (iii)
+specialization\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{63}},
+which measures the deviation of an expected random choice of the
+available interaction partners and ranges between 0 (maximum
+generalization) and 1 (maximum specialization). Normalized degree and
+specialization were calculated with the specieslevel function from the R
+package
+\emph{bipartite}\textsuperscript{\protect\hyperlink{ref-dormann2008}{62}}.
+
+First, we modelled the distinct plant species metrics (sum of visits,
 normalized degree and plant specialization) as a function of the three
-main axes of trait variation in three different models for each metric
-(plant species level metric\textasciitilde{}PC1+PC2+PC3). In addition we
-also explored how all uncorrelated traits (13) explained these metrics
-in three other models (plant species level metric \textasciitilde{}
-plant height + lifespan + life form + flower shape + flower symmetry +
-flower width + style length + ovule number + flowers per plant + nectar
-provision + autonomous selfing + compatibility system + breeding
-system). For each response variable (metric), we used different
-distribution families: zero inflated negative binomial for the sum of
-visits, weibull for normalized degree and zero one inflated beta for
-specialization. Moreover, we included a nested random effect with
-networks nested on the study system and a phylogenetic random effect for
-species (as detailed above) in each model.
-
-All analyses were conducted in R Version 4.0.3. In addition, all models
-were run for 3,000 iterations with 1000 warm up iterations. We set delta
-() to 0.99 to avoid divergent transitions and visualized the posterior
-predictive checks with the function pp\_check using the bayesplot
-package (version 1.7.2, Gabry et al., 2019).
-
-{[}ADD REGRESSION TREE TO METHODS{]} We conducted regression trees in
-order to explore the relevance of traits on the species plant functional
-role. We repeated the procedure as the modelling analysis and we ran a
-decision tree for each plant level species metric (interaction
-frequency, normalized degree and specialization). We used the full
-datase
-
-rpart 4.1-15 (Therneau et al., 2019) rpart.plot 3.0.9 (Milborrow 2018)
-
-\section{RESULTS}\label{results-1}
-
-\subsection{Plant strategies}\label{plant-strategies-1}
-
-The phylogenetically informed principal component analysis (pPCA)
-captured with the first two and three axes 51.8\% and 70.97\% of the
-trait variation respectively (Figure 1 and Figure S4) and had a
-phylogenetic correlation (\(\lambda\)) of 0.76. The first principal
-component (PC1) represented 26.72\% of the trait variation and showed
-the flower number versus flower size compromise. Thus, as flower number
-and plant height increase, flower size, style length and ovule number
-decrease; and, as flower size, style length and ovule number increase,
-flower number and plant height decrease. The main contributing traits to
-PC1 were plant height, flower number, ovule number and flower size
-(loadings \textgreater{} \textbar{}0.5\textbar{}; Table S2) but style
-length also contributed moderately on PC1 (loading = -0.33). The second
-principal component (PC2) represented 25.05\% of the trait variation and
-showed the trade-off between low and high pollinator dependence and we
-refer to this axis as the pollinator dependence trade-off. The main
-driver of trait variation of PC2 was autonomous selfing (loading = 0.85)
-but the other traits (except ovule number) also made a moderate
-contribution to PC2 (loadings from 0.27 to 0.4; Table S2). We found that
-high pollinator dependence was associated with larger and higher number
-of flowers, greater plant height and longer styles. In contrast, species
-with high levels of autonomous selfing had a general lower investment in
-flower number and size, plant height and style length. Further, PC3 also
-explained a considerable amount of variability (19.17\%) and the main
-contributors to this axis were style length (loading = -0.66) and the
-degree of autonomous selfing (loading = -0.51). The remaining traits,
-apart from ovule number, were moderately correlated to changes on PC3
-(loadings from -0.23 to -0.46; Table S2). In addition, the pPCA with the
-species subset that had nectar and pollen quantity showed that nectar
-quantity (microlitres of nectar per flower) was positively associated
-with flower size, style length and ovule number (PC1, 24.70\%); and
-pollen quantity was positively correlated with flower number and plant
-height and negatively associated with autonomous selfing (PC2, 20.59\%;
-Figure S5). This pPCA also showed similar explained variance with two
-components (50.06\%) and similar associations of traits despite some
-variability in the loadings (Table S3).
-
-\begin{figure}
-\centering
-\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
-\caption{\label{fig:unnamed-chunk-5}Life history strategies for 1,236 plant
-species from 29 plant-pollinator networks studies across the first two
-axes of variation from a phylogenetically informed principal component
-analysis (pPCA). The solid arrows indicate the direction and weights of
-the six quantitative traits (flower number, plant height, style length,
-flower size, ovule number and autonomous selfing level) and the labelled
-icons at their end represent the extreme form of the trait continuum.
-The dashed lines indicate the opposed direction of trait variation and
-the non-labelled icons at their end illustrate the other extreme of the
-continuum.}
-\end{figure}
-
-Evaluation of qualitative variable positions in the trait space revealed
-statistical association on both axes of trait variation for
-compatibility, breeding system, life form, lifespan and flower shape
-(Figure 2 and Table S4). In addition, flower symmetry was associated
-with PC2 (Sum of squares = 8.51, F-value = 14.72 , p \textless{} 0.01 ).
-Nectar provision was independent of both axes (PC1 Sum of squares =
-0.37, F-value = 0.29 , p = 0.59; PC2 Sum of squares = 0.83, F-value =
-1.43 , p = 0.23). Concerning self compatibility, we found larger
-differences in pollinator dependence the trade off (i.e., species with
-unisexual flowers and self incompatibility were statistically
-differentiated from species with partially and fullyself compatibility
-in trait space; Figure S3 A and B). Life forms differed statistically
-across both axes of trait variation and followed a gradient of larger
-life forms (trees and shrubs) with higher pollinator dependence to
-smaller ones (herbs) with lower pollinator dependence (Figure S3 C and
-D). Consequently, lifespan also followed this gradient but perennial and
-short lived species just differed statistically on PC2 (Figure S3 E and
-F). Species with unisexual flowers (monoecious and dioecious) were
-clustered on both extremes of trait variation with the highest
-pollinator dependence and flower number investment (Figure S3 G and H).
-Moreover, we found that the campanulate and capitulum flower shapes were
-differentiated from tube, papilionaceous, open and brush shapes in the
-trait space. The former morphologies tended to occupy positions with
-larger flowers and greater pollination dependence, while the latter
-positions had higher number of flowers and autonomous selfing (Figure S3
-I and J). Regarding flower symmetry, zygomorphic flowers were associated
-with lower levels of pollinator dependence, whereas actinomorphic
-flowers had higher pollinator dependence (Figure S3 K and L).
-
-\begin{figure}
-\centering
-\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
-\caption{\label{fig:unnamed-chunk-6}Location of the qualitative traits in
-the trait space for traits that showed a statistical association with
-the main axis of trait variation. These different traits included:
-compatibility system (a), life form (b), lifespan (c), breeding system
-(d), flower shape (e) and flower symmetry (f).}
-\end{figure}
-
-\subsection{Phylogenetic signal of
-traits}\label{phylogenetic-signal-of-traits-1}
-
-We found a strong phylogenetic signal with statistical association (P
-\textless{} 0.01) for all quantitative traits (Table S4). The traits
-with the highest phylogenetic signal were ovule number (\(\lambda\) = 1)
-and plant height (\(\lambda\) = 0.96), followed by flower length
-(\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73) and flower
-number per plant (\(\lambda\) = 0.69). Finally the traits that showed
-lower phylogenetic signal were inflorescence width (\(\lambda\) = 0.57),
-style length (\(\lambda\) = 0.49) and autonomous selfing (\(\lambda\) =
-0.34).
-
-Add *pollen and nectar traits
-
-\subsection{Visitation patterns}\label{visitation-patterns}
-
-The overall visitation records of functional groups differed
-considerably. There were 2,256 for bees, 1,768 for non-syrphid-Diptera,
-845 for syrphids, 437 for Lepidoptera, 432 for Coleoptera and 362 for
-non-bee-Hymenoptera. The main axes of trait variation explained little
-of the visitation patterns (conditional R2 = 0.31; marginal R2 = 0.06)
-but showed interesting trends for the different functional groups
-(Figure 3). Furthermore, the additional model with interaction between
-the most represented families of Hymenoptera and the main axis of trait
-variation (marginal R2 = 0.30; conditional R2 = 0.03) showed that the
-family Apidae was the main driver of the observed patterns (Figure S2).
-Although Apis mellifera contributed substantially to floral visitation,
-the general pattern of bee visitation did not change when A. mellifera
-were removed (FSX).
-
-\includegraphics{output/figures/unnamed-chunk-7-1.pdf}
-
-\subsection{Plant species metrics}\label{plant-species-metrics}
-
-The three main axes of trait variation did not explain the position or
-role of the plant species in the network (visits \textasciitilde{} PCs:
-conditional R2 =0.11 , marginal R2 = 0.02; normalized degree
-\textasciitilde{} PCs: conditional R2 =0.24 , marginal R2 = 0.02 and
-specialization \textasciitilde{} PCs: conditional R2 =0.37 , marginal R2
-= 0.03). However, the functional groups showed different visitation
-patterns across the three main axes of trait variation (Figure 3). On
-the flower number versus size compromise, all functional groups showed
-higher visitation rates on plant species with greater vegetative
-investment and more flowers except syrphids which showed the opposite
-trend (higher visitation on species with larger flowers and associated
-traits). Remarkably, on the pollinator dependence trade-off, all
-pollinator functional groups showed an increasing visitation pattern for
-species with higher pollinator dependence. Lastly, we found that bees,
-Lepidoptera and non-bee Hymenoptera visited more species with larger
-style length and Coleoptera, Non-Syrphids Diptera and Syrphids had
-greater visitation patterns on species with shorter styles. Furthermore,
-with the full model that included all traits, we found that a
-considerable amount of variance for plant species network metrics was
-explained by the different qualitative and quantitative traits (Visits
-\textasciitilde{} Traits: conditional R2 =0.32 , marginal R2 = 0.07;
-Normalize degree \textasciitilde{} Traits: conditional R2 =0.46 ,
-marginal R2 = 0.16; Specialization \textasciitilde{} Traits: conditional
-R2 =0.49, marginal R2 = 0.14).
-
-\section{DISCUSSION}\label{discussion}
-
-Our work highlights that in plant-pollinator networks, plant species
-have displayed clear trade-offs in life strategies. These trade-offs can
-be differentiated on two main axes of trait variation: the flower
-number-size trade-off and the pollinator dependence trade-off. In
-addition, we found that relevant qualitative traits were aggregated
-within trait space, showing clear delimited strategies of different
-plant species within plant-pollinated systems. Moreover, the distinct
-pollinator functional groups showed changes in their interaction
-strength along these axes of trait variation. Although the main axes of
-trait variation explained little the variation of plant species network
-metrics, the full model of uncorrelated traits explained partially the
-plan level metrics.
-
-\section{CONCLUSIONS}\label{conclusions}
-
-Wrap up
-
-\section{ACKNOWLEDGEMENTS}\label{acknowledgements}
-
-On the shoulders of giants.
-
-\section{REFERENCES}\label{references}
+main axes of trait variation (plant species level
+metric\textasciitilde{}PC1+PC2+PC3). For each response variable (i.e.,
+each plant species level metric), we used different distribution
+families (zero inflated negative binomial for the sum of visits, weibull
+for normalized degree and zero one inflated beta for specialization).
+Finally, we used the same random factors (networks nested within study
+system and phylogeny) and model settings and conducted the same
+posterior predictive checks for each model as detailed above in the
+`visitation patterns section'.
+
+Second, to better understand these complex trait relationships, we used
+regression trees. Regression trees are recursive algorithms which can
+detect complex relationships among predictors and allow identification
+of the relevance of specific trait combinations on species functional
+roles. We focused exclusively on quantitative traits because almost all
+categorical traits were statistically associated with the first two axes
+of trait variation (Supplementary Table S2). We conducted this analysis
+using the \emph{rpart} package version \emph{4.1-15} (Therneau et al.,
+2015) with method \emph{`anova'} with a minimum of 50 observations per
+terminal node and we used \emph{rpart.plot} version
+\emph{3.0.9}\textsuperscript{\protect\hyperlink{ref-milborrow2015}{64}}
+to plot the regression trees. We considered the species level indices as
+response variables (interaction frequency, normalized degree and
+specialization) and we performed one regression tree per metric using
+the different quantitative traits as predictors. We calculated two
+regression trees per plant species-level metric, one for the full set of
+species and another for the subset of species for which we had pollen
+and nectar traits. We focused on regression trees that included floral
+rewards because they consistently showed pollen and nectar traits as
+being the best for explaining the different species-level metrics (see
+Supplementary Fig. S4).
+
+\section{References}\label{references}
 
 \hypertarget{refs}{}
+\hypertarget{ref-barrett2002}{}
+1. Barrett, S. C. H. The evolution of plant sexual diversity.
+\emph{Nature Reviews Genetics} \textbf{3}, 274--284 (2002).
+
+\hypertarget{ref-schiestl2013}{}
+2. Schiestl, F. P. \& Johnson, S. D. Pollinator-mediated evolution of
+floral signals. \emph{Trends in Ecology \& Evolution} \textbf{28},
+307--315 (2013).
+
+\hypertarget{ref-carvalheiro2014}{}
+3. Carvalheiro, L. G. \emph{et al.} The potential for indirect effects
+between co-flowering plants via shared pollinators depends on resource
+abundance, accessibility and relatedness. \emph{Ecology Letters}
+\textbf{17}, 1389--1399 (2014).
+
+\hypertarget{ref-baude2016}{}
+4. Baude, M. \emph{et al.} Historical nectar assessment reveals the fall
+and rise of floral resources in britain. \emph{Nature} \textbf{530},
+85--88 (2016).
+
+\hypertarget{ref-munoz2016}{}
+5. Munoz, F., Violle, C. \& Cheptou, P.-O. CSR ecological strategies and
+plant mating systems: Outcrossing increases with competitiveness but
+stress-tolerance is related to mixed mating. \emph{Oikos} \textbf{125},
+1296--1303 (2016).
+
+\hypertarget{ref-moeller2017}{}
+6. Moeller, D. A. \emph{et al.} Global biogeography of mating system
+variation in seed plants. \emph{Ecology Letters} \textbf{20}, 375--384
+(2017).
+
+\hypertarget{ref-grossenbacher2017}{}
+7. Grossenbacher, D. L. \emph{et al.} Self-compatibility is
+over-represented on islands. \emph{New Phytologist} \textbf{215},
+469--478 (2017).
+
+\hypertarget{ref-salguero2016}{}
+8. Salguero-Gómez, R. \emph{et al.} Fast-slow continuum and reproductive
+strategies structure plant life-history variation worldwide.
+\emph{Proceedings of the National Academy of Sciences of the United
+States of America} \textbf{113}, 230--235 (2016).
+
+\hypertarget{ref-ruger2018}{}
+9. Rüger, N. \emph{et al.} Beyond the fastSlow continuum: Demographic
+dimensions structuring a tropical tree community. \emph{Ecology Letters}
+\textbf{21}, 1075--1084 (2018).
+
+\hypertarget{ref-roddy2021}{}
+10. Roddy, A. B. \emph{et al.} Towards the flower economics spectrum.
+\emph{New Phytologist} \textbf{229}, 665--672 (2021).
+
+\hypertarget{ref-fenster2004}{}
+11. Fenster, C. B., Armbruster, W. S., Wilson, P., Dudash, M. R. \&
+Thomson, J. D. Pollination Syndromes and Floral Specialization.
+\emph{Annual Review of Ecology, Evolution, and Systematics} \textbf{35},
+375--403 (2004).
+
+\hypertarget{ref-bartomeus2016}{}
+12. Bartomeus, I. \emph{et al.} A common framework for identifying
+linkage rules across different types of interactions. \emph{Functional
+Ecology} \textbf{30}, 1894--1903 (2016).
+
+\hypertarget{ref-dellinger2020}{}
+13. Dellinger, A. S. Pollination syndromes in the 21st century: Where do
+we stand and where may we go? \emph{New Phytologist} \textbf{228},
+1193--1213 (2020).
+
+\hypertarget{ref-tur2013}{}
+14. Tur, C., Castro-Urgal, R. \& Traveset, A. Linking Plant
+Specialization to Dependence in Interactions for Seed Set in Pollination
+Networks. \emph{PLoS ONE} \textbf{8}, e78294 (2013).
+
+\hypertarget{ref-devaux2014}{}
+15. Devaux, C., Lepers, C. \& Porcher, E. Constraints imposed by
+pollinator behaviour on the ecology and evolution of plant mating
+systems. \emph{Journal of Evolutionary Biology} \textbf{27}, 1413--1430
+(2014).
+
+\hypertarget{ref-kattge2011}{}
+16. Kattge, J. \emph{et al.} TRY a global database of plant traits.
+\emph{Global Change Biology} \textbf{17}, 2905--2935 (2011).
+
+\hypertarget{ref-salguero2015}{}
+17. Salguero-Gómez, R. \emph{et al.} The compadre Plant Matrix Database:
+An open online repository for plant demography. \emph{Journal of
+Ecology} \textbf{103}, 202--218 (2015).
+
+\hypertarget{ref-diaz2016}{}
+18. Díaz, S. \emph{et al.} The global spectrum of plant form and
+function. \emph{Nature} \textbf{529}, 167--171 (2016).
+
+\hypertarget{ref-carmona2021}{}
+19. Carmona, C. P. \emph{et al.} Erosion of global functional diversity
+across the tree of life. \emph{Science Advances} \textbf{7}, eabf2675
+(2021).
+
+\hypertarget{ref-wright2004}{}
+20. Wright, I. J. \emph{et al.} The worldwide leaf economics spectrum.
+\emph{Nature} \textbf{428}, 821--827 (2004).
+
+\hypertarget{ref-chave2009}{}
+21. Chave, J. \emph{et al.} Towards a worldwide wood economics spectrum.
+\emph{Ecology letters} \textbf{12}, 351--366 (2009).
+
+\hypertarget{ref-evojtko2020}{}
+22. E-Vojtkó, A., Bello, F. de, Durka, W., Kühn, I. \& Götzenberger, L.
+The neglected importance of floral traits in trait-based plant community
+assembly. \emph{Journal of Vegetation Science} \textbf{31}, 529--539
+(2020).
+
+\hypertarget{ref-barrett2003}{}
+23. Barrett, S. C. H. Mating strategies in flowering plants: The
+outcrossing-selfing paradigm and beyond. \emph{Philosophical
+Transactions of the Royal Society B: Biological Sciences} \textbf{358},
+991--1004 (2003).
+
+\hypertarget{ref-goodwillie2010}{}
+24. Goodwillie, C. \emph{et al.} Correlated evolution of mating system
+and floral display traits in flowering plants and its implications for
+the distribution of mating system variation. \emph{The New Phytologist}
+\textbf{185}, 311--321 (2010).
+
+\hypertarget{ref-ollerton2011}{}
+25. Ollerton, J., Winfree, R. \& Tarrant, S. How many flowering plants
+are pollinated by animals? \emph{Oikos} \textbf{120}, 321--326 (2011).
+
+\hypertarget{ref-lazaro2008}{}
+26. Lázaro, A., Hegland, S. J. \& Totland, Ø. The relationships between
+floral traits and specificity of pollination systems in three
+Scandinavian plant communities. \emph{Oecologia} \textbf{157}, 249--257
+(2008).
+
+\hypertarget{ref-bartomeus2013}{}
+27. Bartomeus, I. Understanding Linkage Rules in Plant-Pollinator
+Networks by Using Hierarchical Models That Incorporate Pollinator
+Detectability and Plant Traits. \emph{PLOS ONE} \textbf{8}, e69200
+(2013).
+
+\hypertarget{ref-junker2013}{}
+28. Junker, R. R. \emph{et al.} Specialization on traits as basis for
+the niche-breadth of flower visitors and as structuring mechanism of
+ecological networks. \emph{Functional Ecology} \textbf{27}, 329--341
+(2013).
+
+\hypertarget{ref-coux2016}{}
+29. Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking
+species functional roles to their network roles. \emph{Ecology Letters}
+\textbf{19}, 762--770 (2016).
+
+\hypertarget{ref-stang2009}{}
+30. Stang, M., Klinkhamer, P. G. L., Waser, N. M., Stang, I. \& van der
+Meijden, E. Size-specific interaction patterns and size matching in a
+plantPollinator interaction web. \emph{Annals of Botany} \textbf{103},
+1459--1469 (2009).
+
+\hypertarget{ref-ibanez2012}{}
+31. Ibanez, S. Optimizing size thresholds in a plant-pollinator
+interaction web: Towards a mechanistic understanding of ecological
+networks. \emph{Oecologia} \textbf{170}, 233--242 (2012).
+
+\hypertarget{ref-sargent2007}{}
+32. Sargent, R. D., Goodwillie, C., Kalisz, S. \& Ree, R. H.
+Phylogenetic evidence for a flower size and number trade-off.
+\emph{American Journal of Botany} \textbf{94}, 2059--2062 (2007).
+
+\hypertarget{ref-kettle2011}{}
+33. Kettle, C. J. \emph{et al.} Ecological Implications of a Flower
+Size/Number Trade-Off in Tropical Forest Trees. \emph{PLOS ONE}
+\textbf{6}, e16111 (2011).
+
+\hypertarget{ref-healy2019}{}
+34. Healy, K., Ezard, T. H. G., Jones, O. R., Salguero-Gómez, R. \&
+Buckley, Y. M. Animal life history is shaped by the pace of life and the
+distribution of age-specific mortality and reproduction. \emph{Nature
+Ecology \& Evolution} \textbf{3}, 1217--1224 (2019).
+
+\hypertarget{ref-hegland2005}{}
+35. Hegland, S. J. \& Totland, Ø. Relationships between species' floral
+traits and pollinator visitation in a temperate grassland.
+\emph{Oecologia} \textbf{145}, 586--594 (2005).
+
+\hypertarget{ref-lazaro2013}{}
+36. Lázaro, A., Jakobsson, A. \& Totland, Ø. How do pollinator
+visitation rate and seed set relate to species' floral traits and
+community context? \emph{Oecologia} \textbf{173}, 881--893 (2013).
+
+\hypertarget{ref-kaiser2014}{}
+37. Kaiser-Bunbury, C. N., Vázquez, D. P., Stang, M. \& Ghazoul, J.
+Determinants of the microstructure of plantPollinator networks.
+\emph{Ecology} \textbf{95}, 3314--3324 (2014).
+
+\hypertarget{ref-palmer2003}{}
+38. Palmer, T. M., Stanton, M. L. \& Young, T. P. Competition and
+coexistence: Exploring mechanisms that restrict and maintain diversity
+within mutualist guilds. \emph{the american naturalist} \textbf{162},
+S63--S79 (2003).
+
+\hypertarget{ref-phillips2020}{}
+39. Phillips, R. D., Peakall, R., van der Niet, T. \& Johnson, S. D.
+Niche perspectives on plantPollinator interactions. \emph{Trends in
+Plant Science} \textbf{25}, 779--793 (2020).
+
+\hypertarget{ref-vazquez2007}{}
+40. Vázquez, D. P. \emph{et al.} Species abundance and asymmetric
+interaction strength in ecological networks. \emph{Oikos} \textbf{116},
+1120--1127 (2007).
+
+\hypertarget{ref-encinas2012}{}
+41. Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives
+mutualistic network structure and diversity. \emph{Ecology letters}
+\textbf{15}, 198--208 (2012).
+
+\hypertarget{ref-gervasi2017}{}
+42. Gervasi, D. D. L. \& Schiestl, F. P. Real-time divergent evolution
+in plants driven by pollinators. \emph{Nature Communications}
+\textbf{8}, 14691 (2017).
+
+\hypertarget{ref-mackin2021}{}
+43. Mackin, C. R., Peña, J. F., Blanco, M. A., Balfour, N. J. \&
+Castellanos, M. C. Rapid evolution of a floral trait following
+acquisition of novel pollinators. \emph{Journal of Ecology}
+\textbf{109}, 2234--2246 (2021).
+
+\hypertarget{ref-poisot2021}{}
+44. Poisot, T. \emph{et al.} Global knowledge gaps in species
+interaction networks data. \emph{Journal of Biogeography} \textbf{48},
+1552--1563 (2021).
+
+\hypertarget{ref-fortuna2010}{}
+45. Fortuna, M. A. \emph{et al.} Nestedness versus modularity in
+ecological networks: Two sides of the same coin? \emph{Journal of Animal
+Ecology} \textbf{79}, 811--817 (2010).
+
+\hypertarget{ref-poisot2016}{}
+46. Poisot, T. \emph{et al.} Mangal making ecological network analysis
+simple. \emph{Ecography} \textbf{39}, 384--390 (2016).
+
+\hypertarget{ref-chamberlain2020}{}
+47. Chamberlain, S. \emph{et al.} \emph{Taxize: Taxonomic information
+from around the web}. (2020).
+
+\hypertarget{ref-smith2018}{}
+48. Smith, S. A. \& Brown, J. W. Constructing a broadly inclusive seed
+plant phylogeny. \emph{American Journal of Botany} \textbf{105},
+302--314 (2018).
+
+\hypertarget{ref-jin2019}{}
+49. Jin, Y. \& Qian, H. V.PhyloMaker: An R package that can generate
+very large phylogenies for vascular plants. \emph{Ecography}
+\textbf{42}, 1353--1359 (2019).
+
+\hypertarget{ref-stekhoven2012}{}
+50. Stekhoven, D. J. \& Bühlmann, P. MissForestNon-parametric missing
+value imputation for mixed-type data. \emph{Bioinformatics} \textbf{28},
+112--118 (2012).
+
+\hypertarget{ref-penone2014}{}
+51. Penone, C. \emph{et al.} Imputation of missing data in life-history
+trait datasets: Which approach performs the best? \emph{Methods in
+Ecology and Evolution} \textbf{5}, 961--970 (2014).
+
+\hypertarget{ref-santos2018}{}
+52. Santos, T., Diniz-Filho, J. A., e Luis, T. R., Bini, M. \& Santos,
+M. T. Package `PVR'. (2018).
+
+\hypertarget{ref-diniz-filho2012}{}
+53. Diniz-Filho, J. A. F. \emph{et al.} On the selection of phylogenetic
+eigenvectors for ecological analyses. \emph{Ecography} \textbf{35},
+239--249 (2012).
+
+\hypertarget{ref-legendre2012}{}
+54. Legendre, P. \& Legendre, L. \emph{Numerical ecology}. (Elsevier,
+2012).
+
 \hypertarget{ref-abdi2010}{}
-Abdi, H., and L. J. Williams. 2010. Principal component analysis. WIREs
-Computational Statistics 2:433--459.
+55. Abdi, H. \& Williams, L. J. Principal component analysis.
+\emph{WIREs Computational Statistics} \textbf{2}, 433--459 (2010).
 
 \hypertarget{ref-ballantyne2015}{}
-Ballantyne, G., K. C. R. Baldock, and P. G. Willmer. 2015. Constructing
+56. Ballantyne, G., Baldock, K. C. R. \& Willmer, P. G. Constructing
 more informative plantPollinator networks: Visitation and pollen
-deposition networks in a heathland plant community. Proceedings of the
-Royal Society B: Biological Sciences 282:20151130.
-
-\hypertarget{ref-barrett2002}{}
-Barrett, S. C. H. 2002. The evolution of plant sexual diversity. Nature
-Reviews Genetics 3:274--284.
-
-\hypertarget{ref-barrett2003}{}
-Barrett, S. C. H. 2003. Mating strategies in flowering plants: The
-outcrossing-selfing paradigm and beyond. Philosophical Transactions of
-the Royal Society B: Biological Sciences 358:991--1004.
-
-\hypertarget{ref-bartomeus2013}{}
-Bartomeus, I. 2013. Understanding Linkage Rules in Plant-Pollinator
-Networks by Using Hierarchical Models That Incorporate Pollinator
-Detectability and Plant Traits. PLOS ONE 8:e69200.
-
-\hypertarget{ref-bartomeus2016}{}
-Bartomeus, I., D. Gravel, J. M. Tylianakis, M. A. Aizen, I. A. Dickie,
-and M. Bernard-Verdier. 2016. A common framework for identifying linkage
-rules across different types of interactions. Functional Ecology
-30:1894--1903.
-
-\hypertarget{ref-baude2016}{}
-Baude, M., W. E. Kunin, N. D. Boatman, S. Conyers, N. Davies, M. A.
-Gillespie, R. D. Morton, S. M. Smart, and J. Memmott. 2016. Historical
-nectar assessment reveals the fall and rise of floral resources in
-britain. Nature 530:85--88.
+deposition networks in a heathland plant community. \emph{Proceedings of
+the Royal Society B: Biological Sciences} \textbf{282}, 20151130 (2015).
+
+\hypertarget{ref-vazquez2005}{}
+57. Vázquez, D. P., Morris, W. F. \& Jordano, P. Interaction frequency
+as a surrogate for the total effect of animal mutualists on plants.
+\emph{Ecology Letters} \textbf{8}, 1088--1094 (2005).
+
+\hypertarget{ref-vazquez2012}{}
+58. Vázquez, D. P. \emph{et al.} The strength of plantPollinator
+interactions. \emph{Ecology} \textbf{93}, 719--725 (2012).
+
+\hypertarget{ref-hung2018}{}
+59. Hung, K.-L. J., Kingston, J. M., Albrecht, M., Holway, D. A. \&
+Kohn, J. R. The worldwide importance of honey bees as pollinators in
+natural habitats. \emph{Proceedings of the Royal Society B: Biological
+Sciences} \textbf{285}, 20172140 (2018).
+
+\hypertarget{ref-burkner2017}{}
+60. Bürkner, P.-C. Brms: An R package for Bayesian multilevel models
+using Stan. \emph{Journal of statistical software} \textbf{80}, 1--28
+(2017).
+
+\hypertarget{ref-gabry2019}{}
+61. Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A.
+Visualization in Bayesian workflow. \emph{Journal of the Royal
+Statistical Society: Series A (Statistics in Society)} \textbf{182},
+389--402 (2019).
+
+\hypertarget{ref-dormann2008}{}
+62. Dormann, C. F., Gruber, B. \& Fründ, J. Introducing the bipartite
+package: Analysing ecological networks. \emph{interaction} \textbf{1},
+(2008).
 
 \hypertarget{ref-bluthgen2006}{}
-Blüthgen, N., F. Menzel, and N. Blüthgen. 2006. Measuring specialization
-in species interaction networks. BMC Ecology 6:9.
-
-\hypertarget{ref-burkner2017}{}
-Bürkner, P.-C. 2017. Brms: An R package for Bayesian multilevel models
-using Stan. Journal of statistical software 80:1--28.
-
-\hypertarget{ref-carmona2021}{}
-Carmona, C. P., R. Tamme, M. Pärtel, F. de Bello, S. Brosse, P.
-Capdevila, R. González-M, M. González-Suárez, R. Salguero-Gómez, M.
-Vásquez-Valderrama, and A. Toussaint. 2021. Erosion of global functional
-diversity across the tree of life. Science Advances 7:eabf2675.
-
-\hypertarget{ref-carvalheiro2014}{}
-Carvalheiro, L. G., J. C. Biesmeijer, G. Benadi, J. Fründ, M. Stang, I.
-Bartomeus, C. N. Kaiser-Bunbury, M. Baude, S. I. F. Gomes, V. Merckx, K.
-C. R. Baldock, A. T. D. Bennett, R. Boada, R. Bommarco, R. Cartar, N.
-Chacoff, J. Dänhardt, L. V. Dicks, C. F. Dormann, J. Ekroos, K. S. E.
-Henson, A. Holzschuh, R. R. Junker, M. Lopezaraiza-Mikel, J. Memmott, A.
-Montero-Castaño, I. L. Nelson, T. Petanidou, E. F. Power, M. Rundlöf, H.
-G. Smith, J. C. Stout, K. Temitope, T. Tscharntke, T. Tscheulin, M.
-Vilà, and W. E. Kunin. 2014. The potential for indirect effects between
-co-flowering plants via shared pollinators depends on resource
-abundance, accessibility and relatedness. Ecology Letters 17:1389--1399.
-
-\hypertarget{ref-chamberlain2020}{}
-Chamberlain, S., E. Szoecs, Z. Foster, Z. Arendsee, C. Boettiger, K.
-Ram, I. Bartomeus, J. Baumgartner, J. O'Donnell, J. Oksanen, B. G.
-Tzovaras, P. Marchand, V. Tran, M. Salmon, G. Li, and M. Grenié. 2020.
-Taxize: Taxonomic information from around the web.
-
-\hypertarget{ref-chave2009}{}
-Chave, J., D. Coomes, S. Jansen, S. L. Lewis, N. G. Swenson, and A. E.
-Zanne. 2009. Towards a worldwide wood economics spectrum. Ecology
-letters 12:351--366.
-
-\hypertarget{ref-coux2016}{}
-Coux, C., R. Rader, I. Bartomeus, and J. M. Tylianakis. 2016. Linking
-species functional roles to their network roles. Ecology Letters
-19:762--770.
-
-\hypertarget{ref-dellinger2020}{}
-Dellinger, A. S. 2020. Pollination syndromes in the 21st century: Where
-do we stand and where may we go? New Phytologist 228:1193--1213.
-
-\hypertarget{ref-devaux2014}{}
-Devaux, C., C. Lepers, and E. Porcher. 2014. Constraints imposed by
-pollinator behaviour on the ecology and evolution of plant mating
-systems. Journal of Evolutionary Biology 27:1413--1430.
-
-\hypertarget{ref-diniz-filho2012}{}
-Diniz-Filho, J. A. F., L. M. Bini, T. F. Rangel, I. Morales-Castilla, M.
-Á. Olalla-Tárraga, M. Á. Rodríguez, and B. A. Hawkins. 2012. On the
-selection of phylogenetic eigenvectors for ecological analyses.
-Ecography 35:239--249.
-
-\hypertarget{ref-diaz2016}{}
-Díaz, S., J. Kattge, J. H. C. Cornelissen, I. J. Wright, S. Lavorel, S.
-Dray, B. Reu, M. Kleyer, C. Wirth, I. Colin Prentice, E. Garnier, G.
-Bönisch, M. Westoby, H. Poorter, P. B. Reich, A. T. Moles, J. Dickie, A.
-N. Gillison, A. E. Zanne, J. Chave, S. Joseph Wright, S. N. Sheremet'ev,
-H. Jactel, C. Baraloto, B. Cerabolini, S. Pierce, B. Shipley, D. Kirkup,
-F. Casanoves, J. S. Joswig, A. Günther, V. Falczuk, N. Rüger, M. D.
-Mahecha, and L. D. Gorné. 2016. The global spectrum of plant form and
-function. Nature 529:167--171.
-
-\hypertarget{ref-dormann2008}{}
-Dormann, C. F., B. Gruber, and J. Fründ. 2008. Introducing the bipartite
-package: Analysing ecological networks. interaction 1.
-
-\hypertarget{ref-fortuna2014}{}
-Fortuna, M. A., R. Ortega, and J. Bascompte. 2014. The Web of Life.
-arXiv:1403.2575 {[}q-bio{]}.
-
-\hypertarget{ref-fortuna2010}{}
-Fortuna, M. A., D. B. Stouffer, J. M. Olesen, P. Jordano, D. Mouillot,
-B. R. Krasnov, R. Poulin, and J. Bascompte. 2010. Nestedness versus
-modularity in ecological networks: Two sides of the same coin? Journal
-of Animal Ecology 79:811--817.
-
-\hypertarget{ref-goodwillie2010}{}
-Goodwillie, C., R. D. Sargent, C. G. Eckert, E. Elle, M. A. Geber, M. O.
-Johnston, S. Kalisz, D. A. Moeller, R. H. Ree, M. Vallejo-Marin, and A.
-A. Winn. 2010. Correlated evolution of mating system and floral display
-traits in flowering plants and its implications for the distribution of
-mating system variation. The New Phytologist 185:311--321.
-
-\hypertarget{ref-grossenbacher2017}{}
-Grossenbacher, D. L., Y. Brandvain, J. R. Auld, M. Burd, P.-O. Cheptou,
-J. K. Conner, A. G. Grant, S. M. Hovick, J. R. Pannell, A. Pauw, and
-others. 2017. Self-compatibility is over-represented on islands. New
-Phytologist 215:469--478.
-
-\hypertarget{ref-hung2018}{}
-Hung, K.-L. J., J. M. Kingston, M. Albrecht, D. A. Holway, and J. R.
-Kohn. 2018. The worldwide importance of honey bees as pollinators in
-natural habitats. Proceedings of the Royal Society B: Biological
-Sciences 285:20172140.
-
-\hypertarget{ref-ibanez2012}{}
-Ibanez, S. 2012. Optimizing size thresholds in a plant-pollinator
-interaction web: Towards a mechanistic understanding of ecological
-networks. Oecologia 170:233--242.
-
-\hypertarget{ref-jin2019}{}
-Jin, Y., and H. Qian. 2019. V.PhyloMaker: An R package that can generate
-very large phylogenies for vascular plants. Ecography 42:1353--1359.
-
-\hypertarget{ref-junker2013}{}
-Junker, R. R., N. Blüthgen, T. Brehm, J. Binkenstein, J. Paulus, H. M.
-Schaefer, and M. Stang. 2013. Specialization on traits as basis for the
-niche-breadth of flower visitors and as structuring mechanism of
-ecological networks. Functional Ecology 27:329--341.
-
-\hypertarget{ref-kattge2011}{}
-Kattge, J., S. Díaz, S. Lavorel, I. C. Prentice, P. Leadley, G. Bönisch,
-E. Garnier, M. Westoby, P. B. Reich, I. J. Wright, J. H. C. Cornelissen,
-C. Violle, S. P. Harrison, P. M. V. Bodegom, M. Reichstein, B. J.
-Enquist, N. A. Soudzilovskaia, D. D. Ackerly, M. Anand, O. Atkin, M.
-Bahn, T. R. Baker, D. Baldocchi, R. Bekker, C. C. Blanco, B. Blonder, W.
-J. Bond, R. Bradstock, D. E. Bunker, F. Casanoves, J. Cavender-Bares, J.
-Q. Chambers, F. S. C. Iii, J. Chave, D. Coomes, W. K. Cornwell, J. M.
-Craine, B. H. Dobrin, L. Duarte, W. Durka, J. Elser, G. Esser, M.
-Estiarte, W. F. Fagan, J. Fang, F. Fernández-Méndez, A. Fidelis, B.
-Finegan, O. Flores, H. Ford, D. Frank, G. T. Freschet, N. M. Fyllas, R.
-V. Gallagher, W. A. Green, A. G. Gutierrez, T. Hickler, S. I. Higgins,
-J. G. Hodgson, A. Jalili, S. Jansen, C. A. Joly, A. J. Kerkhoff, D.
-Kirkup, K. Kitajima, M. Kleyer, S. Klotz, J. M. H. Knops, K. Kramer, I.
-Kühn, H. Kurokawa, D. Laughlin, T. D. Lee, M. Leishman, F. Lens, T.
-Lenz, S. L. Lewis, J. Lloyd, J. Llusià, F. Louault, S. Ma, M. D.
-Mahecha, P. Manning, T. Massad, B. E. Medlyn, J. Messier, A. T. Moles,
-S. C. Müller, K. Nadrowski, S. Naeem, Ü. Niinemets, S. Nöllert, A.
-Nüske, R. Ogaya, J. Oleksyn, V. G. Onipchenko, Y. Onoda, J. Ordoñez, G.
-Overbeck, W. A. Ozinga, S. Patiño, S. Paula, J. G. Pausas, J. Peñuelas,
-O. L. Phillips, V. Pillar, H. Poorter, L. Poorter, P. Poschlod, A.
-Prinzing, R. Proulx, A. Rammig, S. Reinsch, B. Reu, L. Sack, B.
-Salgado-Negret, J. Sardans, S. Shiodera, B. Shipley, A. Siefert, E.
-Sosinski, J.-F. Soussana, E. Swaine, N. Swenson, K. Thompson, P.
-Thornton, M. Waldram, E. Weiher, M. White, S. White, S. J. Wright, B.
-Yguel, S. Zaehle, A. E. Zanne, and C. Wirth. 2011. TRY a global database
-of plant traits. Global Change Biology 17:2905--2935.
-
-\hypertarget{ref-klumpers2019}{}
-Klumpers, S. G. T., M. Stang, and P. G. L. Klinkhamer. 2019. Foraging
-efficiency and size matching in a plantPollinator community: The
-importance of sugar content and tongue length. Ecology Letters
-22:469--479.
-
-\hypertarget{ref-lazaro2008}{}
-Lázaro, A., S. J. Hegland, and Ø. Totland. 2008. The relationships
-between floral traits and specificity of pollination systems in three
-Scandinavian plant communities. Oecologia 157:249--257.
-
-\hypertarget{ref-legendre2012}{}
-Legendre, P., and L. Legendre. 2012. Numerical ecology. Elsevier.
-
-\hypertarget{ref-moeller2017}{}
-Moeller, D. A., R. D. B. Runquist, A. M. Moe, M. A. Geber, C.
-Goodwillie, P.-O. Cheptou, C. G. Eckert, E. Elle, M. O. Johnston, S.
-Kalisz, R. H. Ree, R. D. Sargent, M. Vallejo-Marin, and A. A. Winn.
-2017. Global biogeography of mating system variation in seed plants.
-Ecology Letters 20:375--384.
-
-\hypertarget{ref-munoz2016}{}
-Munoz, F., C. Violle, and P.-O. Cheptou. 2016. CSR ecological strategies
-and plant mating systems: Outcrossing increases with competitiveness but
-stress-tolerance is related to mixed mating. Oikos 125:1296--1303.
-
-\hypertarget{ref-novella-fernandez2019}{}
-Novella-Fernandez, R., A. Rodrigo, X. Arnan, and J. Bosch. 2019.
-Interaction strength in plant-pollinator networks: Are we using the
-right measure? PLOS ONE 14:e0225930.
-
-\hypertarget{ref-olesen2007}{}
-Olesen, J. M., J. Bascompte, Y. L. Dupont, and P. Jordano. 2007. The
-modularity of pollination networks. Proceedings of the National Academy
-of Sciences 104:19891--19896.
-
-\hypertarget{ref-ollerton2011}{}
-Ollerton, J., R. Winfree, and S. Tarrant. 2011. How many flowering
-plants are pollinated by animals? Oikos 120:321--326.
-
-\hypertarget{ref-penone2014}{}
-Penone, C., A. D. Davidson, K. T. Shoemaker, M. D. Marco, C. Rondinini,
-T. M. Brooks, B. E. Young, C. H. Graham, and G. C. Costa. 2014.
-Imputation of missing data in life-history trait datasets: Which
-approach performs the best? Methods in Ecology and Evolution 5:961--970.
-
-\hypertarget{ref-peralta2020}{}
-Peralta, G., D. P. Vázquez, N. P. Chacoff, S. B. Lomáscolo, G. L. W.
-Perry, and J. M. Tylianakis. 2020. Trait matching and phenological
-overlap increase the spatio-temporal stability and functionality of
-plantPollinator interactions. Ecology Letters 23:1107--1116.
-
-\hypertarget{ref-poisot2016}{}
-Poisot, T., B. Baiser, J. A. Dunne, S. Kéfi, F. Massol, N. Mouquet, T.
-N. Romanuk, D. B. Stouffer, S. A. Wood, and D. Gravel. 2016. Mangal
-making ecological network analysis simple. Ecography 39:384--390.
-
-\hypertarget{ref-rech2016}{}
-Rech, A. R., B. Dalsgaard, B. Sandel, J. Sonne, J.-C. Svenning, N.
-Holmes, and J. Ollerton. 2016. The macroecology of animal versus wind
-pollination: Ecological factors are more important than historical
-climate stability. Plant Ecology \& Diversity 9:253--262.
-
-\hypertarget{ref-revell2012}{}
-Revell, L. J. 2012. Phytools: An R package for phylogenetic comparative
-biology (and other things). Methods in Ecology and Evolution 3:217--223.
-
-\hypertarget{ref-roddy2021}{}
-Roddy, A. B., C. Martínez-Perez, A. L. Teixido, T. G. Cornelissen, M. E.
-Olson, R. S. Oliveira, and F. A. O. Silveira. 2021. Towards the flower
-economics spectrum. New Phytologist 229:665--672.
-
-\hypertarget{ref-salguero2015}{}
-Salguero-Gómez, R., O. R. Jones, C. R. Archer, Y. M. Buckley, J.
-Che-Castaldo, H. Caswell, D. Hodgson, A. Scheuerlein, D. A. Conde, E.
-Brinks, H. de Buhr, C. Farack, F. Gottschalk, A. Hartmann, A. Henning,
-G. Hoppe, G. Römer, J. Runge, T. Ruoff, J. Wille, S. Zeh, R. Davison, D.
-Vieregg, A. Baudisch, R. Altwegg, F. Colchero, M. Dong, H. de Kroon,
-J.-D. Lebreton, C. J. E. Metcalf, M. M. Neel, I. M. Parker, T. Takada,
-T. Valverde, L. A. Vélez-Espino, G. M. Wardle, M. Franco, and J. W.
-Vaupel. 2015. The compadre Plant Matrix Database: An open online
-repository for plant demography. Journal of Ecology 103:202--218.
-
-\hypertarget{ref-salguero2016}{}
-Salguero-Gómez, R., O. R. Jones, E. Jongejans, S. P. Blomberg, D. J.
-Hodgson, C. Mbeau-Ache, P. A. Zuidema, H. de Kroon, and Y. M. Buckley.
-2016. Fast-slow continuum and reproductive strategies structure plant
-life-history variation worldwide. Proceedings of the National Academy of
-Sciences of the United States of America 113:230--235.
-
-\hypertarget{ref-santos2018}{}
-Santos, T., J. A. Diniz-Filho, T. R. e Luis, M. Bini, and M. T. Santos.
-2018. Package ``PVR''.
-
-\hypertarget{ref-schiestl2013}{}
-Schiestl, F. P., and S. D. Johnson. 2013. Pollinator-mediated evolution
-of floral signals. Trends in Ecology \& Evolution 28:307--315.
-
-\hypertarget{ref-smith2018}{}
-Smith, S. A., and J. W. Brown. 2018. Constructing a broadly inclusive
-seed plant phylogeny. American Journal of Botany 105:302--314.
-
-\hypertarget{ref-stang2006}{}
-Stang, M., P. G. L. Klinkhamer, and E. V. D. Meijden. 2006. Size
-constraints and flower abundance determine the number of interactions in
-a plantFlower visitor web. Oikos 112:111--121.
-
-\hypertarget{ref-stang2009}{}
-Stang, M., P. G. L. Klinkhamer, N. M. Waser, I. Stang, and E. van der
-Meijden. 2009. Size-specific interaction patterns and size matching in a
-plantPollinator interaction web. Annals of Botany 103:1459--1469.
-
-\hypertarget{ref-stekhoven2012}{}
-Stekhoven, D. J., and P. Bühlmann. 2012. MissForestNon-parametric
-missing value imputation for mixed-type data. Bioinformatics
-28:112--118.
-
-\hypertarget{ref-tur2013}{}
-Tur, C., R. Castro-Urgal, and A. Traveset. 2013. Linking Plant
-Specialization to Dependence in Interactions for Seed Set in Pollination
-Networks. PLoS ONE 8:e78294.
-
-\hypertarget{ref-wright2004}{}
-Wright, I. J., P. B. Reich, M. Westoby, D. D. Ackerly, Z. Baruch, F.
-Bongers, J. Cavender-Bares, T. Chapin, J. H. C. Cornelissen, M. Diemer,
-J. Flexas, E. Garnier, P. K. Groom, J. Gulias, K. Hikosaka, B. B.
-Lamont, T. Lee, W. Lee, C. Lusk, J. J. Midgley, M.-L. Navas, Ü.
-Niinemets, J. Oleksyn, N. Osada, H. Poorter, P. Poot, L. Prior, V. I.
-Pyankov, C. Roumet, S. C. Thomas, M. G. Tjoelker, E. J. Veneklaas, and
-R. Villar. 2004. The worldwide leaf economics spectrum. Nature
-428:821--827.
+63. Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in
+species interaction networks. \emph{BMC Ecology} \textbf{6}, 9 (2006).
+
+\hypertarget{ref-milborrow2015}{}
+64. Milborrow, S. Rpart. plot: Plot rpart Models. An Enhanced Version of
+plot. rpart. \emph{R package version} \textbf{1}, (2015).
 
@@
 
-\listoftables
-
-\listoffigures
-
-\section*{SUPPLEMENTARY MATERIAL}\label{supplementary-material}
-\addcontentsline{toc}{section}{SUPPLEMENTARY MATERIAL}
-
-\beginsupplement
-
 \end{document}

### 2021-08-12 Untitled/Untitled.tex
Paper almost ready

@@
-% !TeX program = pdfLaTeX
-\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
-%
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage[utf8]{inputenc}
+\documentclass[9pt,twocolumn,twoside,]{pnas-new}
 
-\usepackage[hyphens]{url} % not crucial - just used below for the URL
-\usepackage{hyperref}
+%% Some pieces required from the pandoc template
 \providecommand{\tightlist}{%
@@
 
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
+% Use the lineno option to display guide line numbers if required.
+% Note that the use of elements such as single-column equations
+% may affect the guide line number alignment.
 
-%% load any required packages here
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
 
@@
 
+\templatetype{pnasresearcharticle}  % Choose template
+
+\title{Template for preparing your research report submission to PNAS using
+RMarkdown}
+
+\author[a,1,2]{Alice Anonymous}
+\author[a,b]{Bob Security}
+
+  \affil[a]{Some Institute of Technology, Department, Street, City, State, Zip}
+  \affil[b]{Another University Department, Street, City, State, Zip}
+
+% Please give the surname of the lead author for the running footer
+\leadauthor{Anonymous}
+
+% Please add here a significance statement to explain the relevance of your work
+\significancestatement{Authors must submit a 120-word maximum statement about the significance
+of their research paper written at a level understandable to an
+undergraduate educated scientist outside their field of speciality. The
+primary goal of the Significance Statement is to explain the relevance
+of the work in broad context to a broad readership. The Significance
+Statement appears in the paper itself and is required for all research
+papers.}
+
+\authorcontributions{Please provide details of author contributions here.}
+
+\authordeclaration{Please declare any conflict of interest here.}
+
+\equalauthors{\textsuperscript{1} A.O.(Author One) and A.T. (Author Two) contributed equally to this work
+(remove if not applicable).}
+
+\correspondingauthor{\textsuperscript{2} To whom correspondence should be addressed. E-mail:
+\href{mailto:bob@email.com}{\nolinkurl{bob@email.com}}}
+
+% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
+ \keywords{  one |  two |  optional |  optional |  optional  }
+
+\begin{abstract}
+Please provide an abstract of no more than 250 words in a single
+paragraph. Abstracts should explain to the general reader the major
+contributions of the article. References in the abstract must be cited
+in full within the abstract itself and cited in the text.
+\end{abstract}
+
+\dates{This manuscript was compiled on \today}
+\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
+
 \begin{document}
 
-\title{Title here \thanks{Grants or other notes about the article that should go on the front page
-should be placed here. General acknowledgments should be placed at the
-end of the article.} }
- \subtitle{Do you have a subtitle? If so, write it here}
-
-    \titlerunning{Short form of title (if too long for head)}
-
-\author{  Äüthör 1 \and  Âuthóř 2 \and  }
-
-    \authorrunning{ Short form of author list if too long for running head }
-
-\institute{
-        Äüthör 1 \at
-     Department of YYY, University of XXX \\
-     \email{\href{mailto:abc@def}{\nolinkurl{abc@def}}}  %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-    \and
-        Âuthóř 2 \at
-     Department of ZZZ, University of WWW \\
-     \email{\href{mailto:djf@wef}{\nolinkurl{djf@wef}}}  %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-    \and
-    }
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
+% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
+% You should only change this length when you've finalised the article contents.
+\verticaladjustment{-2pt}
 
 \maketitle
+\thispagestyle{firststyle}
+\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
 
-\begin{abstract}
-The text of your abstract. 150 -- 250 words.
-\\
-\keywords{
-        key \and
-        dictionary \and
-        word \and
-    }
+% If your first paragraph (i.e.
+with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation.
+If this is the case, add \parshape=0 to the end of the list environment.
 
-    \subclass{
-                    MSC code 1 \and
-                    MSC code 2 \and
-            }
+\acknow{Please include your acknowledgments here, set in a single paragraph.
+Please do not include any acknowledgments in the Supporting Information,
+or anywhere else in the manuscript.}
 
-\end{abstract}
+This PNAS journal template is provided to help you write your work in
+the correct journal format. Instructions for use are provided below.
 
-\def\spacingset#1{\renewcommand{\baselinestretch}%
-{#1}\small\normalsize} \spacingset{1}
+Note: please start your introduction without including the word
+``Introduction'' as a section heading (except for math articles in the
+Physical Sciences section); this heading is implied in the first
+paragraphs.
 
-\section{Introduction}\label{intro}
+\section*{Guide to using this
+template}\label{guide-to-using-this-template}
+\addcontentsline{toc}{section}{Guide to using this template}
 
-Your text comes here. Separate text sections with \cite{Mislevy06Cog}.
+Please note that whilst this template provides a preview of the typeset
+manuscript for submission, to help in this preparation, it will not
+necessarily be the final publication layout. For more detailed
+information please see the
+\href{http://www.pnas.org/site/authors/format.xhtml}{PNAS Information
+for Authors}.
 
-\section{Section title}\label{sec:1}
+\subsection*{Author Affiliations}\label{author-affiliations}
+\addcontentsline{toc}{subsection}{Author Affiliations}
 
-Text with citations by \cite{Galyardt14mmm}.
+Include department, institution, and complete address, with the
+ZIP/postal code, for each author. Use lower case letters to match
+authors with institutions, as shown in the example. Authors with an
+ORCID ID may supply this information at submission.
 
-\subsection{Subsection title}\label{sec:2}
+\subsection*{Submitting Manuscripts}\label{submitting-manuscripts}
+\addcontentsline{toc}{subsection}{Submitting Manuscripts}
 
-as required. Don't forget to give each section and subsection a unique
-label (see Sect. \ref{sec:1}).
+All authors must submit their articles at
+\href{http://www.pnascentral.org/cgi-bin/main.plex}{PNAScentral}. If you
+are using Overleaf to write your article, you can use the ``Submit to
+PNAS'' option in the top bar of the editor window.
 
-\paragraph{Paragraph headings}\label{paragraph-headings}
+\subsection*{Format}\label{format}
+\addcontentsline{toc}{subsection}{Format}
 
-Use paragraph headings as needed.
+Many authors find it useful to organize their manuscripts with the
+following order of sections; Title, Author Affiliation, Keywords,
+Abstract, Significance Statement, Results, Discussion, Materials and
+methods, Acknowledgments, and References. Other orders and headings are
+permitted.
 
-\begin{align}
-a^2+b^2=c^2
-\end{align}
+\subsection*{Manuscript Length}\label{manuscript-length}
+\addcontentsline{toc}{subsection}{Manuscript Length}
 
-\bibliographystyle{spphys}
-\bibliography{bibliography.bib}
+PNAS generally uses a two-column format averaging 67 characters,
+including spaces, per line. The maximum length of a Direct Submission
+research article is six pages and a PNAS PLUS research article is ten
+pages including all text, spaces, and the number of characters displaced
+by figures, tables, and equations. When submitting tables, figures,
+and/or equations in addition to text, keep the text for your manuscript
+under 39,000 characters (including spaces) for Direct Submissions and
+72,000 characters (including spaces) for PNAS PLUS.
+
+\subsection*{References}\label{references}
+\addcontentsline{toc}{subsection}{References}
+
+References should be cited in numerical order as they appear in text;
+this will be done automatically via bibtex, e.g. (1) and (2, 3). All
+references, including for the SI, should be included in the main
+manuscript file. References appearing in both sections should not be
+duplicated. SI references included in tables should be included with the
+main reference section.
+
+\subsection*{Data Archival}\label{data-archival}
+\addcontentsline{toc}{subsection}{Data Archival}
+
+PNAS must be able to archive the data essential to a published article.
+Where such archiving is not possible, deposition of data in public
+databases, such as GenBank, ArrayExpress, Protein Data Bank, Unidata,
+and others outlined in the Information for Authors, is acceptable.
+
+\subsection*{Language-Editing Services}\label{language-editing-services}
+\addcontentsline{toc}{subsection}{Language-Editing Services}
+
+Prior to submission, authors who believe their manuscripts would benefit
+from professional editing are encouraged to use a language-editing
+service (see list at www.pnas.org/site/authors/language-editing.xhtml).
+PNAS does not take responsibility for or endorse these services, and
+their use has no bearing on acceptance of a manuscript for publication.
+
+\begin{figure}
+\centering
+\includegraphics{frog.png}
+\caption{Placeholder image of a frog with a long example caption to show
+justification setting.{}}
+\end{figure}
+
+\subsection*{Digital Figures}\label{sec:figures}
+\addcontentsline{toc}{subsection}{Digital Figures}
+
+Only TIFF, EPS, and high-resolution PDF for Mac or PC are allowed for
+figures that will appear in the main text, and images must be final
+size. Authors may submit U3D or PRC files for 3D images; these must be
+accompanied by 2D representations in TIFF, EPS, or high-resolution PDF
+format. Color images must be in RGB (red, green, blue) mode. Include the
+font files for any text.
+
+Figures and Tables should be labelled and referenced in the standard way
+using the \texttt{\textbackslash{}label\{\}} and
+\texttt{\textbackslash{}ref\{\}} commands.
+
+Figure \[fig:frog\] shows an example of how to insert a column-wide
+figure. To insert a figure wider than one column, please use the
+\texttt{\textbackslash{}begin\{figure*\}...\textbackslash{}end\{figure*\}}
+environment. Figures wider than one column should be sized to 11.4 cm or
+17.8 cm wide.
+
+\subsection*{Single column equations}\label{single-column-equations}
+\addcontentsline{toc}{subsection}{Single column equations}
+
+Authors may use 1- or 2-column equations in their article, according to
+their preference.
+
+To allow an equation to span both columns, options are to use the
+\texttt{\textbackslash{}begin\{figure*\}...\textbackslash{}end\{figure*\}}
+environment mentioned above for figures, or to use the
+\texttt{\textbackslash{}begin\{widetext\}...\textbackslash{}end\{widetext\}}
+environment as shown in equation \[eqn:example\] below.
+
+Please note that this option may run into problems with floats and
+footnotes, as mentioned in the \href{http://texdoc.net/pkg/cuted}{cuted
+package documentation}. In the case of problems with footnotes, it may
+be possible to correct the situation using commands
+\texttt{\textbackslash{}footnotemark} and
+\texttt{\textbackslash{}footnotetext}.
+
+\[\begin{aligned}
+(x+y)^3&=(x+y)(x+y)^2\\
+       &=(x+y)(x^2+2xy+y^2) \label{eqn:example} \\
+       &=x^3+3x^2y+3xy^3+x^3. 
+\end{aligned}\]
+
+\subsection*{Supporting Information
+(SI)}\label{supporting-information-si}
+\addcontentsline{toc}{subsection}{Supporting Information (SI)}
+
+The main text of the paper must stand on its own without the SI. Refer
+to SI in the manuscript at an appropriate point in the text. Number
+supporting figures and tables starting with S1, S2, etc. Authors are
+limited to no more than 10 SI files, not including movie files. Authors
+who place detailed materials and methods in SI must provide sufficient
+detail in the main text methods to enable a reader to follow the logic
+of the procedures and results and also must reference the online
+methods. If a paper is fundamentally a study of a new method or
+technique, then the methods must be described completely in the main
+text. Because PNAS edits SI and composes it into a single PDF, authors
+must provide the following file formats only.
+
+\subsubsection*{SI Text}\label{si-text}
+\addcontentsline{toc}{subsubsection}{SI Text}
+
+Supply Word, RTF, or LaTeX files (LaTeX files must be accompanied by a
+PDF with the same file name for visual reference).
+
+\subsubsection*{SI Figures}\label{si-figures}
+\addcontentsline{toc}{subsubsection}{SI Figures}
+
+Provide a brief legend for each supporting figure after the supporting
+text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or
+GIF format; figures may not be embedded in manuscript text. When saving
+TIFF files, use only LZW compression; do not use JPEG compression. Do
+not save figure numbers, legends, or author names as part of the image.
+Composite figures must be pre-assembled.
+
+\subsubsection*{3D Figures}\label{d-figures}
+\addcontentsline{toc}{subsubsection}{3D Figures}
+
+Supply a composable U3D or PRC file so that it may be edited and
+composed. Authors may submit a PDF file but please note it will be
+published in raw format and will not be edited or composed.
+
+\subsubsection*{SI Tables}\label{si-tables}
+\addcontentsline{toc}{subsubsection}{SI Tables}
+
+Supply Word, RTF, or LaTeX files (LaTeX files must be accompanied by a
+PDF with the same file name for visual reference); include only one
+table per file. Do not use tabs or spaces to separate columns in Word
+tables.
+
+\subsubsection*{SI Datasets}\label{si-datasets}
+\addcontentsline{toc}{subsubsection}{SI Datasets}
+
+Supply Excel (.xls), RTF, or PDF files. This file type will be published
+in raw format and will not be edited or composed.
+
+\subsubsection*{SI Movies}\label{si-movies}
+\addcontentsline{toc}{subsubsection}{SI Movies}
+
+Supply Audio Video Interleave (avi), Quicktime (mov), Windows Media
+(wmv), animated GIF (gif), or MPEG files and submit a brief legend for
+each movie in a Word or RTF file. All movies should be submitted at the
+desired reproduction size and length. Movies should be no more than 10
+MB in size.
+
+\subsubsection*{Still images}\label{still-images}
+\addcontentsline{toc}{subsubsection}{Still images}
+
+Authors must provide a still image from each video file. Supply TIFF,
+EPS, high-resolution PDF, JPEG, or GIF files.
+
+\subsubsection*{Appendices}\label{appendices}
+\addcontentsline{toc}{subsubsection}{Appendices}
+
+PNAS prefers that authors submit individual source files to ensure
+readability. If this is not possible, supply a single PDF file that
+contains all of the SI associated with the paper. This file type will be
+published in raw format and will not be edited or composed.
+
+\showmatmethods
+\showacknow
+\pnasbreak
+
+\hypertarget{refs}{}
+\hypertarget{ref-belkin2002using}{}
+1. Belkin M, Niyogi P (2002) Using manifold stucture for partially
+labeled classification. \emph{Advances in Neural Information Processing
+Systems}, pp 929--936.
+
+\hypertarget{ref-berard1994embedding}{}
+2. Bérard P, Besson G, Gallot S (1994) Embedding riemannian manifolds by
+their heat kernel. \emph{Geometric \& Functional Analysis GAFA}
+4(4):373--398.
+
+\hypertarget{ref-coifman2005geometric}{}
+3. Coifman RR, et al. (2005) Geometric diffusions as a tool for harmonic
+analysis and structure definition of data: Diffusion maps.
+\emph{Proceedings of the National Academy of Sciences of the United
+States of America} 102(21):7426--7431.
+
+% Bibliography
+% \bibliography{pnas-sample}
 

### 2021-08-13 Draft/Manuscript.Rmd
editys

@@
 The first principal component (PC1) represented 26.72% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the ‘flower number - flower size trade-off as already described in previous studies [@sargent2007; @kettle2011].
+We refer to this axis as the ‘flower number - flower size trade-off’ as already described in previous studies [@sargent2007; @kettle2011].
 Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
@@
 The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Supplementary Table S3).
-We found that high pollinator dependence was associated with larger and higher numbers of flowers, greater plant height and longer styles.
+We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
 In contrast, species with high levels of autonomous selfing tended to have fewer and smaller flowers, had shorter styles and were shorter in height.
@@
 The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Supplementary Table S3).
-Thus, because style length was correlated with all traits on PC3 and was the main driver of variation, we refer to this axis as the ‘style length trade-off’.
+Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the ‘style length trade-off’.
 Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 23.40%); and pollen quantity (pollen grains per flower) was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 21.67%; Supplementary Fig.
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,fig.pos = "t",fig.cap= "**Fig.
-1 |** Life history strategies for 1,236 plant species from 28 plant-pollinator networks studies across the first two axes of trait variation from a phylogenetically informed principal component analysis (pPCA).
-The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) in the 2-d plane.
+1 | Plant life-history strategies.** Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator networks studies.
+The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
 The length of the arrows indicate the weight of the variables on each principal component and the labelled icons at their end represent the extreme form of the trait continuum.
@@
 2 and Supplementary Table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, p < 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , p = 0.59; PC2:  Sum of squares = 0.83, F-value = 1.43, p = 0.23) showed lack of statistical association.
-In addition, we found statistical differences (Tukey test) between the different levels of categorical traits in the trait space (Supplementary Fig.
+Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, _P_ < 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , _P_ = 0.59; PC2:  Sum of squares = 0.83, F-value = 1.43, _P_ = 0.23) showed lack of statistical association.
+In addition, we found with Tukey test statistical differences between the different levels of categorical traits in the trait space (Supplementary Fig.
 S7).
 Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatibile were statistically differentiated from species with partial or full self compatibility; Supplementary Fig.
-S7 A and B).
+S7a and Fig.
+S7b).
 Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Supplementary Fig.
-S7 C and D).
+S7c and Fig.
+S7d).
 Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Supplementary Fig.
-S7 E and F).
+S7e and Fig.
+S7f).
 Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Supplementary Fig.
-S7 G and H).
+S7g and Fig.
+S7h).
 Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
 The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Supplementary Fig.
-S7 I and J).
+S7i and Fig.
+S7j).
 Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Supplementary Fig.
-S7 K and L).
+S7k and Fig.
+S7l).
 
@@
 
-**Phylogenetic signal of traits.** We found a strong phylogenetic signal (P < 0.01) in all quantitative traits (Supplementary Table S5).
+**Phylogenetic signal of traits.** We found a strong phylogenetic signal (*P* < 0.01) in all quantitative traits (Supplementary Table S5).
 The traits that showed the highest phylogenetic signal were ovule number ($\lambda = 1$), pollen grains per flower ($\lambda = 1$) and plant height ($\lambda = 0.96$), followed by flower length ($\lambda = 0.75$), flower width ($\lambda = 0.73$), number of flowers per plant ($\lambda = 0.69$) and nectar concentration ($\lambda = 0.65$).
@@
 
-**Visitation patterns.** The main axes of trait variation explained little of the overall visitation rates (conditional $R2 = 0.31$; marginal $R2 = 0.06$) but showed relevant trends when we explored the interaction with the different floral visitors guilds (Fig.
+**Visitation patterns.** The main axes of trait variation explained little of the overall visitation rates ($conditional R2 = 0.31$; $marginal R2 = 0.06$) but showed relevant trends when we explored the interaction with the different floral visitors guilds (Fig.
 3).
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap= "**Fig.
-2 | Fitted posterior estimates of the number of visits made by the different floral visitors guilds in relation to the three main axes of trait variation (PC1, PC2 and PC3)**.
+3 | Visitation rates across the three main axes of trait variation.** Fitted posterior estimates of the number of visits made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
 Bees (a, b and c) and the rest of guilds (d, e and f) were plotted separately for visualization purposes.
@@
 
-**Plant species functional roles.** The three main axes of trait variation poorly explain the variance of the different plant species level metrics (Supplementary Fig.
+**Plant species functional roles.** The variance of the different plant species level metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
 S9; interaction frequency ~ PCs, $conditional R2 = 0.11$, $marginal R2 = 0.02$; normalized degree ~ PCs, $conditional R2 = 0.24$, $marginal R2 = 0.02$; and, specialization ~ PCs, $conditional R2 = 0.37$, $marginal R2 = 0.03$).
@@
 On PC1, specialization showed the opposite trend.
-On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower selfing and higher for species with long styles and higher levels of selfing.
+On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing.
 Again, specialization showed the opposite trend to interaction frequency.
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=12,fig.pos = "!H",fig.cap= "**Fig.
-4 | Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits**.
+4 | Trait relevance on the plant species’ functional roles.** Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
 The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
@@
 colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
 
 colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
 
 colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
 
@@
 
-rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.5,tweak = 1.25,type = 2) 
-rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.5,tweak = 1.25,type = 2)
-rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.5,tweak = 1.25,type = 2)
+rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.45,tweak = 1.25,type = 2) 
+rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.45,tweak = 1.25,type = 2)
+rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.45,tweak = 1.25,type = 2)
 
@@
 Over 50% of plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
-Variation in these two axes of trait variation appears to be associated with the commonly described ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life history strategies as indicated by the different floral and reproductive traits associated with plant height, life form and lifespan.
-The “slow” part of the continuum (i.e., tall trees and shrubs) had plant species with many flowers, few ovules, higher pollinator dependence, greater occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, species that employed the “fast” strategy (i.e., short herbs), had fewer flowers, more ovules, greater occurrence of self compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the positive association between outcrossing rate and floral display, in accordance with @goodwillie2010.
+Variation in these two axes of trait variation appears to be associated with the commonly described ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life-history strategies as indicated by the different floral and reproductive traits associated with plant height, life form and lifespan.
+The ‘slow’ part of the continuum (i.e., tall trees and shrubs) had plant species with many flowers, few ovules, higher pollinator dependence, greater occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
+In contrast, species that employed the ‘fast’ strategy (i.e., short herbs), had fewer flowers, more ovules, greater occurrence of self compatibility and lower pollinator dependence.
+Further, on the first two axes of trait variation, we found additional support for the **previously described** positive association between outcrossing rate and floral display [@goodwillie2010].
 This trend was further confirmed when looking at the specific correlation between floral display and autonomous selfing for our dataset (see Supplementary Fig.
@@
 
-Despite the low predictive power of the main axes of trait variation on overall visitation patterns, we found commonalities among and within floral visitors guilds across these axes that indicate the influence of life history strategies on floral visitation rate.
+Despite the low predictive power of the main axes of trait variation on overall visitation patterns, we found commonalities among and within floral visitors guilds across these axes that indicate the influence of life-history strategies on floral visitation rate.
 For example, all guilds showed an increasing trend of visitation on plant species with higher pollinator dependence, which were also associated with larger floral displays and greater pollen quantity (Fig.

### 2021-08-13 Draft/Manuscript.tex
editys

@@
 flower size. We refer to this axis as the `flower number - flower size
-trade-off as already described in previous
+trade-off' as already described in previous
 studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{32},\protect\hyperlink{ref-kettle2011}{33}}.
@@
 Table S3). We found that high pollinator dependence was associated with
-larger and higher numbers of flowers, greater plant height and longer
+larger and a higher number of flowers, greater plant height and longer
 styles. In contrast, species with high levels of autonomous selfing
@@
 Supplementary Table S3). Thus, because style length was correlated with
-all traits on PC3 and was the main driver of variation, we refer to this
-axis as the `style length trade-off'. Further, the pPCA with the subset
-of species that had nectar and pollen quantity data showed that nectar
-quantity (microlitres of nectar per flower) was positively associated
-with flower size, style length and ovule number (PC1, 23.40\%); and
-pollen quantity (pollen grains per flower) was positively correlated
-with flower number and plant height and negatively associated with
-autonomous selfing (PC2, 21.67\%; Supplementary Fig. S6). This pPCA
+all traits on PC3 and was the main driver of trait variation, we refer
+to this axis as the `style length trade-off'. Further, the pPCA with the
+subset of species that had nectar and pollen quantity data showed that
+nectar quantity (microlitres of nectar per flower) was positively
+associated with flower size, style length and ovule number (PC1,
+23.40\%); and pollen quantity (pollen grains per flower) was positively
+correlated with flower number and plant height and negatively associated
+with autonomous selfing (PC2, 21.67\%; Supplementary Fig. S6). This pPCA
 explained similar variance with the first two principal components
@@
 \includegraphics{output/figures/unnamed-chunk-1-1.pdf}
-\caption{\label{fig:unnamed-chunk-1}\textbf{Fig. 1 \textbar{}} Life history
-strategies for 1,236 plant species from 28 plant-pollinator networks
-studies across the first two axes of trait variation from a
-phylogenetically informed principal component analysis (pPCA). The solid
-arrows indicate the direction of the different quantitative traits
-(flower number, plant height, style length, flower size, ovule number
-and level of autonomous selfing) in the 2-d plane. The length of the
-arrows indicate the weight of the variables on each principal component
-and the labelled icons at their end represent the extreme form of the
-trait continuum. The dashed lines show the opposed direction of trait
-variation and the non-labelled icons at their end illustrate the
-opposing extreme of the continuum.}
+\caption{\label{fig:unnamed-chunk-1}\textbf{Fig. 1 \textbar{} Plant
+life-history strategies.} Phylogenetically informed principal component
+analysis (pPCA) of 1,236 plant species from 28 plant-pollinator networks
+studies. The solid arrows indicate the direction of the different
+quantitative traits (flower number, plant height, style length, flower
+size, ovule number and level of autonomous selfing) across the two main
+axes of trait variation. The length of the arrows indicate the weight of
+the variables on each principal component and the labelled icons at
+their end represent the extreme form of the trait continuum. The dashed
+lines show the opposed direction of trait variation and the non-labelled
+icons at their end illustrate the opposing extreme of the continuum.}
 \end{figure}
@@
 S2). Flower symmetry, which was only associated with PC2 (Sum of squares
-= 8.51, F-value = 14.72, p \textless{} 0.01 ), and nectar provision,
-which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37,
-F-value = 0.29 , p = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, p
-= 0.23) showed lack of statistical association. In addition, we found
-statistical differences (Tukey test) between the different levels of
-categorical traits in the trait space (Supplementary Fig. S7). Regarding
-self compatibility, we found larger differences on PC2 (i.e., species
-with unisexual flowers that were self incompatibile were statistically
-differentiated from species with partial or full self compatibility;
-Supplementary Fig. S7 A and B). Life forms differed statistically across
-both axes of trait variation and followed a gradient of larger life
-forms (trees and shrubs) with higher pollinator dependence to smaller
-ones (herbs) with lower pollinator dependence (Supplementary Fig. S7 C
-and D). Consequently, lifespan also followed this gradient but perennial
-and short lived species only differed statistically on PC2
-(Supplementary Fig. S7 E and F). Species with unisexual flowers
-(monoecious and dioecious) were clustered on both extremes of the first
-two principal components and had the highest pollinator dependence and
-highest number of flowers (Supplementary Fig. S7 G and H). Moreover, we
-found that the campanulate and capitulum flower shapes were
-differentiated from tube, papilionaceous, open and brush shapes in the
-trait space. The former morphologies had larger flowers and greater
-pollinator dependence, while the latter had higher flower number and
-greater autonomous selfing (Supplementary Fig. S7 I and J). Regarding
+= 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar
+provision, which was independent of PC1 and PC2 (PC1: Sum of squares =
+0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83,
+F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
+In addition, we found with Tukey test statistical differences between
+the different levels of categorical traits in the trait space
+(Supplementary Fig. S7). Regarding self compatibility, we found larger
+differences on PC2 (i.e., species with unisexual flowers that were self
+incompatibile were statistically differentiated from species with
+partial or full self compatibility; Supplementary Fig. S7a and Fig.
+S7b). Life forms differed statistically across both axes of trait
+variation and followed a gradient of larger life forms (trees and
+shrubs) with higher pollinator dependence to smaller ones (herbs) with
+lower pollinator dependence (Supplementary Fig. S7c and Fig. S7d).
+Consequently, lifespan also followed this gradient but perennial and
+short lived species only differed statistically on PC2 (Supplementary
+Fig. S7e and Fig. S7f). Species with unisexual flowers (monoecious and
+dioecious) were clustered on both extremes of the first two principal
+components and had the highest pollinator dependence and highest number
+of flowers (Supplementary Fig. S7g and Fig. S7h). Moreover, we found
+that the campanulate and capitulum flower shapes were differentiated
+from tube, papilionaceous, open and brush shapes in the trait space. The
+former morphologies had larger flowers and greater pollinator
+dependence, while the latter had higher flower number and greater
+autonomous selfing (Supplementary Fig. S7i and Fig. S7j). Regarding
 flower symmetry, zygomorphic flowers were associated with lower levels
 of pollinator dependence, whereas actinomorphic flowers had higher
-levels of pollinator dependence (Supplementary Fig. S7 K and L).
+levels of pollinator dependence (Supplementary Fig. S7k and Fig. S7l).
 
@@
 \textbf{Phylogenetic signal of traits.} We found a strong phylogenetic
-signal (P \textless{} 0.01) in all quantitative traits (Supplementary
-Table S5). The traits that showed the highest phylogenetic signal were
-ovule number (\(\lambda = 1\)), pollen grains per flower
-(\(\lambda = 1\)) and plant height (\(\lambda = 0.96\)), followed by
-flower length (\(\lambda = 0.75\)), flower width (\(\lambda = 0.73\)),
-number of flowers per plant (\(\lambda = 0.69\)) and nectar
-concentration (\(\lambda = 0.65\)). The traits that showed a moderate
-phylogenetic signal were inflorescence width (\(\lambda = 0.57\)), style
-length (\(\lambda = 0.49\)) and autonomous selfing (\(\lambda = 0.34\)).
-Finally, microliters of nectar per flower showed the lowest phylogenetic
-signal of all traits (\(\lambda = 0.14\)).
+signal (\emph{P} \textless{} 0.01) in all quantitative traits
+(Supplementary Table S5). The traits that showed the highest
+phylogenetic signal were ovule number (\(\lambda = 1\)), pollen grains
+per flower (\(\lambda = 1\)) and plant height (\(\lambda = 0.96\)),
+followed by flower length (\(\lambda = 0.75\)), flower width
+(\(\lambda = 0.73\)), number of flowers per plant (\(\lambda = 0.69\))
+and nectar concentration (\(\lambda = 0.65\)). The traits that showed a
+moderate phylogenetic signal were inflorescence width
+(\(\lambda = 0.57\)), style length (\(\lambda = 0.49\)) and autonomous
+selfing (\(\lambda = 0.34\)). Finally, microliters of nectar per flower
+showed the lowest phylogenetic signal of all traits
+(\(\lambda = 0.14\)).
 
 \textbf{Visitation patterns.} The main axes of trait variation explained
-little of the overall visitation rates (conditional \(R2 = 0.31\);
-marginal \(R2 = 0.06\)) but showed relevant trends when we explored the
+little of the overall visitation rates (\(conditional R2 = 0.31\);
+\(marginal R2 = 0.06\)) but showed relevant trends when we explored the
 interaction with the different floral visitors guilds (Fig. 3). All
@@
 \includegraphics{output/figures/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}\textbf{Fig. 2 \textbar{} Fitted
-posterior estimates of the number of visits made by the different floral
-visitors guilds in relation to the three main axes of trait variation
-(PC1, PC2 and PC3)}. Bees (a, b and c) and the rest of guilds (d, e and
-f) were plotted separately for visualization purposes. In addition, we
-trimmed the plotting area that was over the 95th percentile to improve
-visualisation. PC1 represents the flower number - flower size trade-off,
-PC2 represents the pollinator dependence trade-off and PC3, the style
-length trade-off.}
+\caption{\label{fig:unnamed-chunk-3}\textbf{Fig. 3 \textbar{} Visitation
+rates across the three main axes of trait variation.} Fitted posterior
+estimates of the number of visits made by the different floral visitors
+guilds in relation to PC1, PC2 and PC3. Bees (a, b and c) and the rest
+of guilds (d, e and f) were plotted separately for visualization
+purposes. In addition, we trimmed the plotting area that was over the
+95th percentile to improve visualisation. PC1 represents the flower
+number - flower size trade-off, PC2 represents the pollinator dependence
+trade-off and PC3, the style length trade-off.}
 \end{figure}
@@
 
-\textbf{Plant species functional roles.} The three main axes of trait
-variation poorly explain the variance of the different plant species
-level metrics (Supplementary Fig. S9; interaction frequency
+\textbf{Plant species functional roles.} The variance of the different
+plant species level metrics was poorly explained by the three main axes
+of trait variation (Supplementary Fig. S9; interaction frequency
 \textasciitilde{} PCs, \(conditional R2 = 0.11\),
@@
 style length trade-off (PC3), interaction frequency was lower for plants
-with shorter styles and lower selfing and higher for species with long
-styles and higher levels of selfing. Again, specialization showed the
-opposite trend to interaction frequency.
+with shorter styles and lower autonomous selfing and higher for species
+with longer styles and higher autonomous selfing. Again, specialization
+showed the opposite trend to interaction frequency.
 
@@
 \includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\textbf{Fig. 4 \textbar{} Regression
-tree analysis of interaction frequency (log-transformed), normalized
-degree and specialization for the subset of species with quantitative
-data for pollen and nectar traits}. The superior value inside the node
-indicates the mean value of the different species-level metric and the
-lower value, the percentage of species that are considered in each node.
-Thus, the top node has the mean value of the named trait for the 100\%
-of species. Each node has a yes/no question and when the condition is
+\caption{\label{fig:unnamed-chunk-4}\textbf{Fig. 4 \textbar{} Trait
+relevance on the plant species' functional roles.} Regression tree
+analysis of interaction frequency (log-transformed), normalized degree
+and specialization for the subset of species with quantitative data for
+pollen and nectar traits. The superior value inside the node indicates
+the mean value of the different species-level metric and the lower
+value, the percentage of species that are considered in each node. Thus,
+the top node has the mean value of the named trait for the 100\% of
+species. Each node has a yes/no question and when the condition is
 fulfilled, the branch turns to the `yes' direction and when not, to the
@@
 plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}} and
-animal\textsuperscript{\protect\hyperlink{ref-healy2019}{34}} life
-history strategies as indicated by the different floral and reproductive
-traits associated with plant height, life form and lifespan. The
-``slow'' part of the continuum (i.e., tall trees and shrubs) had plant
-species with many flowers, few ovules, higher pollinator dependence,
-greater occurrence of self-incompatibility and more complex breeding
-systems (e.g., monoecious and dioecious species). In contrast, species
-that employed the ``fast'' strategy (i.e., short herbs), had fewer
+animal\textsuperscript{\protect\hyperlink{ref-healy2019}{34}}
+life-history strategies as indicated by the different floral and
+reproductive traits associated with plant height, life form and
+lifespan. The `slow' part of the continuum (i.e., tall trees and shrubs)
+had plant species with many flowers, few ovules, higher pollinator
+dependence, greater occurrence of self-incompatibility and more complex
+breeding systems (e.g., monoecious and dioecious species). In contrast,
+species that employed the `fast' strategy (i.e., short herbs), had fewer
 flowers, more ovules, greater occurrence of self compatibility and lower
 pollinator dependence. Further, on the first two axes of trait
-variation, we found additional support for the positive association
-between outcrossing rate and floral display, in accordance with
-\protect\hyperlink{ref-goodwillie2010}{24}. This trend was further
-confirmed when looking at the specific correlation between floral
-display and autonomous selfing for our dataset (see Supplementary Fig.
-S10).
+variation, we found additional support for the previously described
+positive association between outcrossing rate and floral
+display\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{24}}.
+This trend was further confirmed when looking at the specific
+correlation between floral display and autonomous selfing for our
+dataset (see Supplementary Fig. S10).
 
@@
 floral visitors guilds across these axes that indicate the influence of
-life history strategies on floral visitation rate. For example, all
+life-history strategies on floral visitation rate. For example, all
 guilds showed an increasing trend of visitation on plant species with

### 2021-08-13 Draft/Manuscript.Rmd
Minor edit to clarify numeric ref

@@
 In contrast, species that employed the ‘fast’ strategy (i.e., short herbs), had fewer flowers, more ovules, greater occurrence of self compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the **previously described** positive association between outcrossing rate and floral display [@goodwillie2010].
+Further, on the first two axes of trait variation, we found additional support for the positive association already described in a previous study between outcrossing rate and floral display [@goodwillie2010].
 This trend was further confirmed when looking at the specific correlation between floral display and autonomous selfing for our dataset (see Supplementary Fig.

### 2021-08-13 Draft/Manuscript.Rmd
minor correctionsstyle corrections on main text

@@
 - \usepackage[style=nature]{biblatex}
+- \usepackage[labelformat = empty]{caption}
 
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=12,fig.pos = "!H",fig.cap= "**Fig.
-4 | Trait relevance on the plant species’ functional roles.** Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
+4 | contribution of traits in plant's network roles.** Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
 The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
@@
 Despite the low predictive power of the main axes of trait variation on overall visitation patterns, we found commonalities among and within floral visitors guilds across these axes that indicate the influence of life-history strategies on floral visitation rate.
-For example, all guilds showed an increasing trend of visitation on plant species with higher pollinator dependence, which were also associated with larger floral displays and greater pollen quantity (Fig.
+For example, all guilds showed an increasing trend of visitation on plant species with higher pollinator dependence, which were also associated with larger floral displays and greater pollen quantities (Fig.
 1 and Supplementary Fig.
@@
 This allowed us to identify the major reproductive strategies of flowering plants and how plant life strategies determine their interaction with floral visitor guilds.
-Although the percentage of explained variation found with the first two axes (~50%) is lower than other studies that have evaluated life histories with vegetative traits [@diaz2016; @carmona2021], this percentage is consistent with @salguero2016 which characterized life strategies with both vegetative and reproductive traits (i.e., semelparity and iteroparity).
-Future work needs to integrate these floral and reproductive compromises with the already described vegetative and physiological trade-offs @diaz2016 to create a more comprehensive spectra of trait variation [@roddy2021].
+Although the percentage of explained variation found with the first two axes (~50%) is lower than other studies that have evaluated life histories with vegetative traits [@diaz2016; @carmona2021], this percentage is consistent with the largest and most recent study that have characterized life strategies with both vegetative and reproductive (i.e., semelparity and iteroparity) traits [@salguero2016].
+Future work needs to integrate these floral and reproductive compromises with the already described vegetative and physiological trade-offs [@diaz2016] to create a more comprehensive spectra of trait variation [@roddy2021].
 Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators [@gervasi2017; @mackin2021].
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies [(Olesen et al., 2007; @fortuna2010; @carvalheiro2014] or available in online archives (e.g., “The Web of Life” [@fortuna2010] and “Mangal” [@poisot2016].
+Many of these networks are freely available either as published studies [(Olesen et al., 2007; @fortuna2010; @carvalheiro2014] or available in online archives (e.g., ‘The Web of Life’ [@fortuna2010] and ‘Mangal’ [@poisot2016].
 In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
@@
 
-**Phylogenetic Distance.** We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package _rtrees_ (https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018] developed by @jin2019.
+**Phylogenetic Distance.** We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package _rtrees_ (https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
 
@@
 
-dat <- data.frame(Type, Trait,Number_of_records_quantitative,Type_1, Trait1, T.cat,Number_of_records_categorical)
-
-colnames(dat) <- c("Type","Traits", "Records","Type", "Traits", "Categories", "Records")
-
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c")) %>%
+dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
+
+colnames(dat) <- c("Type","Traits", "Type", "Traits", "Categories")
+
+kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table 1 | Quantitative and categorical traits used in this study.}") %>%
 kable_styling(full_width = T,font_size = 10) %>%
-add_header_above(c("Quantitative traits" = 3,"Categorical traits" = 4),bold=T)  %>%
-    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)
+add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 3),bold=T)  %>%
+    column_spec(c(1,3), bold = T) %>% row_spec(0, bold=T)
 
@@
 We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of _missForest_ [@penone2014].
-To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on the conceptual framework of [@diniz-filho2012].
+To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
 Although the variable of autonomous selfing had a high percentage of missing values (68%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
@@
 **Plant strategies.** We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, p < 0.01 and Pearson’s correlation = 0.36, p < 0.01 respectively), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01 respectively), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
@@
 Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [version _0.7-70_; revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
+We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [version _0.7-70_; @revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
 Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
@@
 
-**Phylogenetic signal of traits.** We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ version _0.7-70_ (Revell, 2012a) and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
+**Phylogenetic signal of traits.** We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ version _0.7-70_ [@revell2012] and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
@@
 **Networks analyses.** Analyses were conducted on the subset of 60 weighted networks with interaction frequency sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our weighted network dataset (excluding meta-webs) included 2,256 interactions of bees (i.e.
-Anthophila-Hymenoptera) with plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-Anthophila-Hymenoptera interactions.
+In total, our weighted network dataset (excluding meta-webs) included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-Anthophila-Hymenoptera interactions.
 Although floral visitors are not always pollinators and the frequency of visits does not consider each pollinator species efficiency [@ballantyne2015], visitation rate provides valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
@@
 Moreover, because Hymenoptera-Anthophila was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the visitation rate of the main Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that Apis mellifera was the floral visitor with the largest proportion of records counted (7.55% of the total).
-This is consistent with @hung2018 who showed that A.
-mellifera was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems.
-Hence, to control for the effect of Apis mellifera on the observed visitation patterns of bees, we conducted an analogous analysis excluding A.
-mellifera.
-We found that A.
-mellifera, was partly driving some of the observed trends on PC1 (Supplementary Fig.
+In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
+This finding is consistent with previous research showing that _A.
+mellifera_ was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
+Hence, to control for the effect of _A.
+mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis excluding _A.
+mellifera_.
+We found that _A.
+mellifera_, was partly driving some of the observed trends on PC1 (Supplementary Fig.
 S3).
@@
 The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization [d’; @bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the specieslevel function from the R package _bipartite_ [version _2.15_; @dormann2008].
-
-First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric~PC1+PC2+PC3).
+Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [version _2.15_; @dormann2008].
+
+First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric ~ PC1 + PC2 + PC3).
 For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors (networks nested within study system and phylogeny) and model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns section’.
+Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns section’.
 
@@
 We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
-We conducted this analysis using the _rpart_ package version _4.1-15_ (Therneau et al., 2015) with method _‘anova’_ with a minimum of 50 observations per terminal node and we used _rpart.plot_ version _3.0.9_ [@milborrow2015] to plot the regression trees.
+We conducted this analysis using the _rpart_ package [@therneau2015] version _4.1-15_ with method _‘anova’_ with a minimum of 50 observations per terminal node and we used _rpart.plot_ [@milborrow2015] version _3.0.9_ to plot the regression trees.
 We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.

### 2021-08-13 Draft/Manuscript.tex
minor correctionsstyle corrections on main text

@@
 \usepackage[style=nature]{biblatex}
+\usepackage[labelformat = empty]{caption}
 \usepackage{float}
@@
 \includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\textbf{Fig. 4 \textbar{} Trait
-relevance on the plant species' functional roles.} Regression tree
-analysis of interaction frequency (log-transformed), normalized degree
-and specialization for the subset of species with quantitative data for
+\caption{\label{fig:unnamed-chunk-4}\textbf{Fig. 4 \textbar{} contribution
+of traits in plant's network roles.} Regression tree analysis of
+interaction frequency (log-transformed), normalized degree and
+specialization for the subset of species with quantitative data for
 pollen and nectar traits. The superior value inside the node indicates
@@
 pollinator dependence. Further, on the first two axes of trait
-variation, we found additional support for the previously described
-positive association between outcrossing rate and floral
+variation, we found additional support for the positive association
+already described in a previous study between outcrossing rate and
+floral
 display\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{24}}.
@@
 higher pollinator dependence, which were also associated with larger
-floral displays and greater pollen quantity (Fig. 1 and Supplementary
+floral displays and greater pollen quantities (Fig. 1 and Supplementary
 Fig. S6). This trend is consistent with previous plant-pollinator
@@
 traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}},
-this percentage is consistent with
-\protect\hyperlink{ref-salguero2016}{8} which characterized life
-strategies with both vegetative and reproductive traits (i.e.,
-semelparity and iteroparity). Future work needs to integrate these
-floral and reproductive compromises with the already described
-vegetative and physiological trade-offs
-\protect\hyperlink{ref-diaz2016}{18} to create a more comprehensive
-spectra of trait
+this percentage is consistent with the largest and most recent study
+that have characterized life strategies with both vegetative and
+reproductive (i.e., semelparity and iteroparity)
+traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}}. Future
+work needs to integrate these floral and reproductive compromises with
+the already described vegetative and physiological
+trade-offs\textsuperscript{\protect\hyperlink{ref-diaz2016}{18}} to
+create a more comprehensive spectra of trait
 variation\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}}.
@@
 studies\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3},\protect\hyperlink{ref-fortuna2010}{45}}
-or available in online archives (e.g., ``The Web of
-Life''\textsuperscript{\protect\hyperlink{ref-fortuna2010}{45}} and
-``Mangal''\textsuperscript{\protect\hyperlink{ref-poisot2016}{46}}. In
+or available in online archives (e.g., `The Web of
+Life'\textsuperscript{\protect\hyperlink{ref-fortuna2010}{45}} and
+`Mangal'\textsuperscript{\protect\hyperlink{ref-poisot2016}{46}}. In
 total, our network dataset (see Supplementary Table S1) constituted 60
@@
 implementation of the Open Tree of
-Life\textsuperscript{\protect\hyperlink{ref-smith2018}{48}} developed by
-\protect\hyperlink{ref-jin2019}{49}.
+Life\textsuperscript{\protect\hyperlink{ref-smith2018}{48},\protect\hyperlink{ref-jin2019}{49}}.
 
@@
 
-\begingroup\fontsize{10}{12}\selectfont
-
-\begin{tabu} to \linewidth {>{}c>{\raggedright}X>{\centering}X>{}c>{\raggedright}X>{\raggedright}X>{\centering}X}
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-5}\textbf{Table 1 | Quantitative and categorical traits used in this study.}}
+\centering
+\fontsize{10}{12}\selectfont
+\begin{tabu} to \linewidth {>{}c>{\raggedright}X>{}c>{\centering}X>{\raggedright}X}
 \toprule
-\multicolumn{3}{c}{\textbf{Quantitative traits}} & \multicolumn{4}{c}{\textbf{Categorical traits}} \\
-\cmidrule(l{3pt}r{3pt}){1-3} \cmidrule(l{3pt}r{3pt}){4-7}
-\textbf{Type} & \textbf{Traits} & \textbf{Records} & \textbf{Type} & \textbf{Traits} & \textbf{Categories} & \textbf{Records}\\
+\multicolumn{2}{c}{\textbf{Quantitative traits}} & \multicolumn{3}{c}{\textbf{Categorical traits}} \\
+\cmidrule(l{3pt}r{3pt}){1-2} \cmidrule(l{3pt}r{3pt}){3-5}
+\textbf{Type} & \textbf{Traits} & \textbf{Type} & \textbf{Traits} & \textbf{Categories}\\
 \midrule
-\textbf{Vegetative} & Plant height (m) & 1470 & \textbf{Vegetative} & Lifepan & \makecell[l]{Short-lived \\ Perennial} & 1466\\
+\textbf{Vegetative} & Plant height (m) & \textbf{Vegetative} & Lifepan & \makecell[l]{Short-lived \\ Perennial}\\
 \addlinespace
-\textbf{Floral} & Flower width (mm) & 1472 & \textbf{Vegetative} & Life form & \makecell[l]{Herb \\ Shrub \\ Tree} & 1472\\
+\textbf{Floral} & Flower width (mm) & \textbf{Vegetative} & Life form & \makecell[l]{Herb \\ Shrub \\ Tree}\\
 \addlinespace
-\textbf{Floral} & Flower length (mm) & 1401 & \textbf{Floral} & Flower shape & \makecell[l]{Brush \\ Campanulate \\ Capitulum \\ Open \\ Papilionaceous \\ Tube} & 1458\\
+\textbf{Floral} & Flower length (mm) & \textbf{Floral} & Flower shape & \makecell[l]{Brush \\ Campanulate \\ Capitulum \\ Open \\ Papilionaceous \\ Tube}\\
 \addlinespace
-\textbf{Floral} & Inflorescence width (mm) & 1496 & \textbf{Floral} & Flower symmetry & \makecell[l]{Actinomorphic \\ Zygomorphic} & 1478\\
+\textbf{Floral} & Inflorescence width (mm) & \textbf{Floral} & Flower symmetry & \makecell[l]{Actinomorphic \\ Zygomorphic}\\
 \addlinespace
-\textbf{Floral} & Style length (mm) & 1497 & \textbf{Floral} & Nectar & \makecell[l]{Presence \\ Absence} & 1408\\
+\textbf{Floral} & Style length (mm) & \textbf{Floral} & Nectar & \makecell[l]{Presence \\ Absence}\\
 \addlinespace
-\textbf{Floral} & Ovules per flower & 1457 & \textbf{Reproductive} & Autonomous selfing & \makecell[l]{None \\ Low \\ Medium \\ High} & 987\\
+\textbf{Floral} & Ovules per flower & \textbf{Reproductive} & Autonomous selfing & \makecell[l]{None \\ Low \\ Medium \\ High}\\
 \addlinespace
-\textbf{Floral} & Flowers per plant & 1468 & \textbf{Reproductive} & Compatibility system & \makecell[l]{Self-incomp. \\ Part. self-comp. \\ Self-comp.} & 1253\\
+\textbf{Floral} & Flowers per plant & \textbf{Reproductive} & Compatibility system & \makecell[l]{Self-incomp. \\ Part. self-comp. \\ Self-comp.}\\
 \addlinespace
-\textbf{Floral} & Nectar ($\mu$l) & 531 & \textbf{Reproductive} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious} & 1489\\
+\textbf{Floral} & Nectar ($\mu$l) & \textbf{Reproductive} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious}\\
 \addlinespace
-\textbf{Floral} & Nectar (mg) & 455 & \textbf{} &  &  & \\
+\textbf{Floral} & Nectar (mg) & \textbf{} &  & \\
 \addlinespace
-\textbf{Floral} & Nectar concentration ($\%$) & 558 & \textbf{} &  &  & \\
+\textbf{Floral} & Nectar concentration ($\%$) & \textbf{} &  & \\
 \addlinespace
-\textbf{Floral} & Pollen grains per flower & 533 & \textbf{} &  &  & \\
+\textbf{Floral} & Pollen grains per flower & \textbf{} &  & \\
 \addlinespace
-\textbf{Reproductive} & Autonomous selfing (fruit set) & 992 & \textbf{} &  &  & \\
+\textbf{Reproductive} & Autonomous selfing (fruit set) & \textbf{} &  & \\
 \bottomrule
 \end{tabu}
-
-\endgroup{}
+\end{table}
 
@@
 \emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{52}} based
-on the conceptual framework
-of\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{53}}.
+on a previous conceptual framework that considers phylogenetic
+eigenvectors\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{53}}.
 Although the variable of autonomous selfing had a high percentage of
@@
 highly and moderately correlated to flower width respectively (Pearson's
-correlation = 0.72, p \textless{} 0.01 and Pearson's correlation = 0.36,
-p \textless{} 0.01 respectively), and thus we avoided overemphasizing
-flower size on the spectrum of trait variation. Although qualitative
-traits were not included in the dimensionality reduction analysis, we
-also investigated the association of the different qualitative traits
-with the main axes of trait variation. Prior to the analyses, we
-excluded outliers and standardized the data. Due to the high sensitivity
-of dimensionality reduction to outliers, we excluded values within the
-2.5th--97.5th percentile
+correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation
+= 0.36, \emph{P} \textless{} 0.01 respectively), and thus we avoided
+overemphasizing flower size on the spectrum of trait variation. Although
+qualitative traits were not included in the dimensionality reduction
+analysis, we also investigated the association of the different
+qualitative traits with the main axes of trait variation. Prior to the
+analyses, we excluded outliers and standardized the data. Due to the
+high sensitivity of dimensionality reduction to outliers, we excluded
+values within the 2.5th--97.5th percentile
 range\textsuperscript{\protect\hyperlink{ref-legendre2012}{54}}, and
@@
 performed the pPCA using the function \emph{phyl.pca} from the package
-\emph{phytools} {[}version \emph{0.7-70}; revell2012{]} with the method
-lambda (\(\lambda\)) that calculates the phylogenetic correlation
-between 0 (phylogenetic independence) and 1 (shared evolutionary
-history) and we implemented the mode covariance because values for each
-variables were on the same scale following
-transformation\textsuperscript{\protect\hyperlink{ref-abdi2010}{55}}.
+\emph{phytools}\textsuperscript{\protect\hyperlink{ref-revell2012}{55}}
+with the method lambda (\(\lambda\)) that calculates the phylogenetic
+correlation between 0 (phylogenetic independence) and 1 (shared
+evolutionary history) and we implemented the mode covariance because
+values for each variables were on the same scale following
+transformation\textsuperscript{\protect\hyperlink{ref-abdi2010}{56}}.
 Moreover, to corroborate that our imputation of missing values did not
@@
 the full set of species (N = 1,506) with the package \emph{phytools}
-version \emph{0.7-70} (Revell, 2012a) and we used Pagel's \(\lambda\) as
-a measurement of the phylogenetic signal. However, for pollen and nectar
-traits, phylogenetic signal was calculated only on the subset of species
-that had quantitative information for these traits (N = 755).
+version
+\emph{0.7-70}\textsuperscript{\protect\hyperlink{ref-revell2012}{55}}
+and we used Pagel's \(\lambda\) as a measurement of the phylogenetic
+signal. However, for pollen and nectar traits, phylogenetic signal was
+calculated only on the subset of species that had quantitative
+information for these traits (N = 755).
 
@@
 species. In total, our weighted network dataset (excluding meta-webs)
-included 2,256 interactions of bees (i.e.~Anthophila-Hymenoptera) with
+included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with
 plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae
@@
 consider each pollinator species
-efficiency\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{56}},
+efficiency\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{57}},
 visitation rate provides valuable information of the contribution of
 floral visitors to
-pollination\textsuperscript{\protect\hyperlink{ref-vazquez2005}{57},\protect\hyperlink{ref-vazquez2012}{58}}.
+pollination\textsuperscript{\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}}.
 Sampling methods varied across networks but this was accounted for in
@@
 Halictidae and Megachilidae) on the trait space. In addition, we found
-that Apis mellifera was the floral visitor with the largest proportion
-of records counted (7.55\% of the total). This is consistent with
-\protect\hyperlink{ref-hung2018}{59} who showed that A. mellifera was
+that \emph{Apis mellifera} was the floral visitor with the largest
+proportion of records counted (7.55\% of the total). This finding is
+consistent with previous research showing that \emph{A. mellifera} was
 the most frequent floral visitor in a similar dataset of 80
-plant-pollinator networks in natural ecosystems. Hence, to control for
-the effect of Apis mellifera on the observed visitation patterns of
-bees, we conducted an analogous analysis excluding A. mellifera. We
-found that A. mellifera, was partly driving some of the observed trends
-on PC1 (Supplementary Fig. S3). However, we did not detect major
-differences on PC2 and PC3.
+plant-pollinator networks in natural
+ecosystems\textsuperscript{\protect\hyperlink{ref-hung2018}{60}}. Hence,
+to control for the effect of \emph{A. mellifera} on the observed
+visitation patterns of bees, we conducted an analogous analysis
+excluding \emph{A. mellifera}. We found that \emph{A. mellifera}, was
+partly driving some of the observed trends on PC1 (Supplementary Fig.
+S3). However, we did not detect major differences on PC2 and PC3.
 
@@
 package
-\emph{brms}\textsuperscript{\protect\hyperlink{ref-burkner2017}{60}}. We
+\emph{brms}\textsuperscript{\protect\hyperlink{ref-burkner2017}{61}}. We
 modelled the frequency of visits as a function of the main axes of plant
@@
 the \emph{bayesplot}
-package\textsuperscript{\protect\hyperlink{ref-gabry2019}{61}}.
+package\textsuperscript{\protect\hyperlink{ref-gabry2019}{62}}.
 
@@
 in bipartite network
-studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{62}} with a
+studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{63}} with a
 straightforward ecological interpretation relevant to our research
@@
 partners; and (iii)
-specialization\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{63}},
+specialization\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{64}},
 which measures the deviation of an expected random choice of the
@@
 generalization) and 1 (maximum specialization). Normalized degree and
-specialization were calculated with the specieslevel function from the R
-package
-\emph{bipartite}\textsuperscript{\protect\hyperlink{ref-dormann2008}{62}}.
+specialization were calculated with the \emph{specieslevel} function
+from the R package
+\emph{bipartite}\textsuperscript{\protect\hyperlink{ref-dormann2008}{63}}.
 
@@
 normalized degree and plant specialization) as a function of the three
-main axes of trait variation (plant species level
-metric\textasciitilde{}PC1+PC2+PC3). For each response variable (i.e.,
+main axes of trait variation (plant species level metric
+\textasciitilde{} PC1 + PC2 + PC3). For each response variable (i.e.,
 each plant species level metric), we used different distribution
@@
 for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors (networks nested within study
-system and phylogeny) and model settings and conducted the same
-posterior predictive checks for each model as detailed above in the
-`visitation patterns section'.
+Finally, we used the same random factors, model settings and conducted
+the same posterior predictive checks for each model as detailed above in
+the `visitation patterns section'.
 
@@
 of trait variation (Supplementary Table S2). We conducted this analysis
-using the \emph{rpart} package version \emph{4.1-15} (Therneau et al.,
-2015) with method \emph{`anova'} with a minimum of 50 observations per
-terminal node and we used \emph{rpart.plot} version
-\emph{3.0.9}\textsuperscript{\protect\hyperlink{ref-milborrow2015}{64}}
-to plot the regression trees. We considered the species level indices as
-response variables (interaction frequency, normalized degree and
-specialization) and we performed one regression tree per metric using
-the different quantitative traits as predictors. We calculated two
-regression trees per plant species-level metric, one for the full set of
-species and another for the subset of species for which we had pollen
-and nectar traits. We focused on regression trees that included floral
-rewards because they consistently showed pollen and nectar traits as
-being the best for explaining the different species-level metrics (see
-Supplementary Fig. S4).
+using the \emph{rpart}
+package\textsuperscript{\protect\hyperlink{ref-therneau2015}{65}}
+version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50
+observations per terminal node and we used
+\emph{rpart.plot}\textsuperscript{\protect\hyperlink{ref-milborrow2015}{66}}
+version \emph{3.0.9} to plot the regression trees. We considered the
+species level indices as response variables (interaction frequency,
+normalized degree and specialization) and we performed one regression
+tree per metric using the different quantitative traits as predictors.
+We calculated two regression trees per plant species-level metric, one
+for the full set of species and another for the subset of species for
+which we had pollen and nectar traits. We focused on regression trees
+that included floral rewards because they consistently showed pollen and
+nectar traits as being the best for explaining the different
+species-level metrics (see Supplementary Fig. S4).
 
@@
 
+\hypertarget{ref-revell2012}{}
+55. Revell, L. J. Phytools: An R package for phylogenetic comparative
+biology (and other things). \emph{Methods in Ecology and Evolution}
+\textbf{3}, 217--223 (2012).
+
 \hypertarget{ref-abdi2010}{}
-55. Abdi, H. \& Williams, L. J. Principal component analysis.
+56. Abdi, H. \& Williams, L. J. Principal component analysis.
 \emph{WIREs Computational Statistics} \textbf{2}, 433--459 (2010).
@@
 \hypertarget{ref-ballantyne2015}{}
-56. Ballantyne, G., Baldock, K. C. R. \& Willmer, P. G. Constructing
+57. Ballantyne, G., Baldock, K. C. R. \& Willmer, P. G. Constructing
 more informative plantPollinator networks: Visitation and pollen
@@
 \hypertarget{ref-vazquez2005}{}
-57. Vázquez, D. P., Morris, W. F. \& Jordano, P. Interaction frequency
+58. Vázquez, D. P., Morris, W. F. \& Jordano, P. Interaction frequency
 as a surrogate for the total effect of animal mutualists on plants.
@@
 \hypertarget{ref-vazquez2012}{}
-58. Vázquez, D. P. \emph{et al.} The strength of plantPollinator
+59. Vázquez, D. P. \emph{et al.} The strength of plantPollinator
 interactions. \emph{Ecology} \textbf{93}, 719--725 (2012).
@@
 \hypertarget{ref-hung2018}{}
-59. Hung, K.-L. J., Kingston, J. M., Albrecht, M., Holway, D. A. \&
+60. Hung, K.-L. J., Kingston, J. M., Albrecht, M., Holway, D. A. \&
 Kohn, J. R. The worldwide importance of honey bees as pollinators in
@@
 \hypertarget{ref-burkner2017}{}
-60. Bürkner, P.-C. Brms: An R package for Bayesian multilevel models
+61. Bürkner, P.-C. Brms: An R package for Bayesian multilevel models
 using Stan. \emph{Journal of statistical software} \textbf{80}, 1--28
@@
 \hypertarget{ref-gabry2019}{}
-61. Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A.
+62. Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A.
 Visualization in Bayesian workflow. \emph{Journal of the Royal
@@
 \hypertarget{ref-dormann2008}{}
-62. Dormann, C. F., Gruber, B. \& Fründ, J. Introducing the bipartite
+63. Dormann, C. F., Gruber, B. \& Fründ, J. Introducing the bipartite
 package: Analysing ecological networks. \emph{interaction} \textbf{1},
@@
 \hypertarget{ref-bluthgen2006}{}
-63. Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in
+64. Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in
 species interaction networks. \emph{BMC Ecology} \textbf{6}, 9 (2006).
 
+\hypertarget{ref-therneau2015}{}
+65. Therneau, T., Atkinson, B., Ripley, B. \& Ripley, M. B. Package
+`rpart'. \emph{Available online: cran. ma. ic. ac.
+uk/web/packages/rpart/rpart. pdf (accessed on 20 April 2016)} (2015).
+
 \hypertarget{ref-milborrow2015}{}
-64. Milborrow, S. Rpart. plot: Plot rpart Models. An Enhanced Version of
+66. Milborrow, S. Rpart. plot: Plot rpart Models. An Enhanced Version of
 plot. rpart. \emph{R package version} \textbf{1}, (2015).

### 2021-08-13 Draft/Manuscript.Rmd
abbreviation of journal refs

@@
 We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
-We conducted this analysis using the _rpart_ package [@therneau2015] version _4.1-15_ with method _‘anova’_ with a minimum of 50 observations per terminal node and we used _rpart.plot_ [@milborrow2015] version _3.0.9_ to plot the regression trees.
+We conducted this analysis using the _rpart_ package [@therneau2015] version _4.1-15_ with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] version _3.0.9_ to plot the regression trees.
 We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.

### 2021-08-13 Draft/Manuscript.tex
abbreviation of journal refs

@@
 version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50
-observations per terminal node and we used
-\emph{rpart.plot}\textsuperscript{\protect\hyperlink{ref-milborrow2015}{66}}
+observations per terminal node and we used the \emph{rpart.plot}
+package\textsuperscript{\protect\hyperlink{ref-milborrow2015}{66}}
 version \emph{3.0.9} to plot the regression trees. We considered the
@@
 \hypertarget{ref-barrett2002}{}
-1. Barrett, S. C. H. The evolution of plant sexual diversity.
-\emph{Nature Reviews Genetics} \textbf{3}, 274--284 (2002).
+1. Barrett, S. C. H. The evolution of plant sexual diversity. \emph{Nat.
+Rev. Genet.} \textbf{3}, 274--284 (2002).
 
@@
 2. Schiestl, F. P. \& Johnson, S. D. Pollinator-mediated evolution of
-floral signals. \emph{Trends in Ecology \& Evolution} \textbf{28},
-307--315 (2013).
+floral signals. \emph{Trends Ecol. Evol.} \textbf{28}, 307--315 (2013).
 
@@
 between co-flowering plants via shared pollinators depends on resource
-abundance, accessibility and relatedness. \emph{Ecology Letters}
+abundance, accessibility and relatedness. \emph{Ecol. Lett.}
 \textbf{17}, 1389--1399 (2014).
@@
 6. Moeller, D. A. \emph{et al.} Global biogeography of mating system
-variation in seed plants. \emph{Ecology Letters} \textbf{20}, 375--384
+variation in seed plants. \emph{Ecol. Lett.} \textbf{20}, 375--384
 (2017).
@@
 7. Grossenbacher, D. L. \emph{et al.} Self-compatibility is
-over-represented on islands. \emph{New Phytologist} \textbf{215},
-469--478 (2017).
+over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478
+(2017).
 
@@
 9. Rüger, N. \emph{et al.} Beyond the fastSlow continuum: Demographic
-dimensions structuring a tropical tree community. \emph{Ecology Letters}
+dimensions structuring a tropical tree community. \emph{Ecol. Lett.}
 \textbf{21}, 1075--1084 (2018).
@@
 10. Roddy, A. B. \emph{et al.} Towards the flower economics spectrum.
-\emph{New Phytologist} \textbf{229}, 665--672 (2021).
+\emph{New Phytol.} \textbf{229}, 665--672 (2021).
 
@@
 13. Dellinger, A. S. Pollination syndromes in the 21st century: Where do
-we stand and where may we go? \emph{New Phytologist} \textbf{228},
+we stand and where may we go? \emph{New Phytol.} \textbf{228},
 1193--1213 (2020).
@@
 21. Chave, J. \emph{et al.} Towards a worldwide wood economics spectrum.
-\emph{Ecology letters} \textbf{12}, 351--366 (2009).
+\emph{Ecol. Lett.} \textbf{12}, 351--366 (2009).
 
@@
 and floral display traits in flowering plants and its implications for
-the distribution of mating system variation. \emph{The New Phytologist}
+the distribution of mating system variation. \emph{New Phytol.}
 \textbf{185}, 311--321 (2010).
@@
 29. Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking
-species functional roles to their network roles. \emph{Ecology Letters}
+species functional roles to their network roles. \emph{Ecol. Lett.}
 \textbf{19}, 762--770 (2016).
@@
 41. Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives
-mutualistic network structure and diversity. \emph{Ecology letters}
+mutualistic network structure and diversity. \emph{Ecol. Lett.}
 \textbf{15}, 198--208 (2012).
@@
 as a surrogate for the total effect of animal mutualists on plants.
-\emph{Ecology Letters} \textbf{8}, 1088--1094 (2005).
+\emph{Ecol. Lett.} \textbf{8}, 1088--1094 (2005).
 

### 2021-08-14 Draft/Manuscript.Rmd
journal abbreviations of refs

@@
 - \usepackage{colortbl}
-- \usepackage{pdflscape}
 - \usepackage{tabu}
@@
 - \usepackage[labelformat = empty]{caption}
+- \usepackage{pdflscape}
 
@@
 \vspace{5mm}
-\bleft
 \normalsize
@@
 kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table 1 | Quantitative and categorical traits used in this study.}") %>%
-kable_styling(full_width = T,font_size = 10) %>%
+kable_styling(full_width = F,font_size = 10) %>%
 add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 3),bold=T)  %>%
@@
 <div id ="refs"></div>
-
-\eleft

### 2021-08-14 Draft/Manuscript.tex
journal abbreviations of refs

@@
-\documentclass[12pt,a4paper,]{article}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
+%
+\documentclass[
+  12pt,
+  a4paper,
+]{article}
 \usepackage[]{mathpazo}
 \usepackage{setspace}
-\setstretch{2}
 \usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
+\IfFileExists{microtype.sty}{% use microtype if available
   \usepackage[]{microtype}
@@
 }{}
-\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
-\usepackage[unicode=true]{hyperref}
-\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
 \hypersetup{
@@
   linkcolor=RoyalBlue,
+  filecolor=Maroon,
   citecolor=Blue,
   urlcolor=RoyalBlue,
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
 \usepackage{longtable,booktabs}
-% Fix footnotes in tables (requires footnote package)
-\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\pagestyle{plain}
 \usepackage{lineno} % add 
@@
 \usepackage{colortbl}
-\usepackage{pdflscape}
 \usepackage{tabu}
@@
 \usepackage[labelformat = empty]{caption}
+\usepackage{pdflscape}
 \usepackage{float}
@@
 
-\title{\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant floral and
-reproductive traits determine interactions with floral visitors}
+\title{\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant floral and reproductive traits determine interactions with floral visitors}
 \author{}
@@
 
-\vspace{-2.2cm} \singlespacing
+\setstretch{2}
+\vspace{-2.2cm}
+\singlespacing
 \large
+
 \textbf{Jose B. Lanuza$^{1,2}*$, Romina Rader$^{1}$, Jamie Stavert$^{3}$, Liam K. Kendall$^{4}$, Manu E. Saunders$^{1}$ and Ignasi Bartomeus$^{2}$}
@@
 
-\textbf{Plant life strategies are often delimited by vegetative and
-physiological traits but little is known about how floral and
-reproductive traits drive these strategies, and in turn shape plant
-interactions with floral visitors. Here, we compiled 13 floral, 4
-reproductive and 3 vegetative traits for 1,506 plant species from 28
-plant-pollinator network studies across 18 different countries. We
-investigated the associations among these traits, pollinator visitation
-and the functional role of plant species within the networks
-(interaction frequency, normalized degree and specialization). We found
-that 51.8\% of trait variation was explained by two independent axes
-that encompassed plant form and function. Specifically, the first axis
-indicated the presence of a trade-off between flower number and flower
-size (PC1, 26.72\%). The second axis indicated a trade-off for the level
-of pollinator dependency (PC2, 25.08\%). Although the main axes of trait
-variation did not fully explain pollinator visitation rates, different
-plant life strategies were associated with visitation rates and
-pollinator functional groups. Overall, the main traits that determined
-plant species' functional roles were height, nectar concentration,
-pollen grains per flower, number of ovules, style length, selfing level
-and flower width. Our results highlight the need to consider plant
-reproductive and floral traits to improve understanding of plant life
-strategies and plant-pollinator interactions at broader spatial scales.}
+\textbf{Plant life strategies are often delimited by vegetative and physiological traits but little is known about how floral and reproductive traits drive these strategies, and in turn shape plant interactions with floral visitors.
+Here, we compiled 13 floral, 4 reproductive and 3 vegetative traits for 1,506 plant species from 28 plant-pollinator network studies across 18 different countries.
+We investigated the associations among these traits, pollinator visitation and the functional role of plant species within the networks (interaction frequency, normalized degree and specialization).
+We found that 51.8\% of trait variation was explained by two independent axes that encompassed plant form and function.
+Specifically, the first axis indicated the presence of a trade-off between flower number and flower size (PC1, 26.72\%).
+The second axis indicated a trade-off for the level of pollinator dependency (PC2, 25.08\%).
+Although the main axes of trait variation did not fully explain pollinator visitation rates, different plant life strategies were associated with visitation rates and pollinator functional groups.
+Overall, the main traits that determined plant species' functional roles were height, nectar concentration, pollen grains per flower, number of ovules, style length, selfing level and flower width.
+Our results highlight the need to consider plant reproductive and floral traits to improve understanding of plant life strategies and plant-pollinator interactions at broader spatial scales.}
 
@@
 
-\noindent\rule{\textwidth}{1pt}
+\noindent
 
-\textsuperscript{1} School of Environmental and Rural Science,
-University of New England, Armidale, New South Wales 2350, Australia.
-\textsuperscript{2} Estación Biológica de Doñana (EBD-CSIC), E-41092
-Seville, Spain. \textsuperscript{3} Department of Conservation
-\textbar{} Te Papa Atawhai, Auckland, New Zealand. \textsuperscript{4}
-Centre for Environmental and Climate Science, Lund University,
-Sölvegatan 37, S-223 62 Lund, Sweden. \texttt{*} e-mail:
-\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
+\rule{\textwidth}{1pt}
+
+\textsuperscript{1} School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
+\textsuperscript{2} Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
+\textsuperscript{3} Department of Conservation \textbar{} Te Papa Atawhai, Auckland, New Zealand.
+\textsuperscript{4} Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden.
+\texttt{*} e-mail: \href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
 
 \doublespacing
-\vspace{5mm} \bleft
+\vspace{5mm}
 \normalsize
 
-There is an astonishing diversity of floral structures and plant
-reproductive strategies among flowering
-plants\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}},
-which have long been of interest to pollination biologists in terms of
-their relevance to plant-pollinator interactions. However, most studies
-that have explored reproductive (e.g., mating and compatibility systems)
-and floral trait (e.g., flower size or nectar provision) variation have
-concentrated on the individual or community level and thus, broader
-macroecological patterns remain poorly
-investigated\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3}--\protect\hyperlink{ref-grossenbacher2017}{7}}.
-Indeed, studies depicting species' life history strategies generally
-focus on vegetative traits and rarely consider reproductive
-traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}}. As a
-consequence, a unified framework that explores the compromises among
-floral traits and their relevance to plant life strategies is currently
-lacking\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}}. At the
-same time, there is growing interest in the determinants of
-plant-pollinator interactions via trait-based
-approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{11}} and
-trait-matching
-analyses\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{12}}.
-However, floral traits have been overlooked beyond highly specialised
-plant-pollinator
-systems\textsuperscript{\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-dellinger2020}{13}}
-and the role of plant reproductive biology remains little explored in
-plant-pollinator interactions (but see
-references\textsuperscript{\protect\hyperlink{ref-tur2013}{14},\protect\hyperlink{ref-devaux2014}{15}}).
+There is an astonishing diversity of floral structures and plant reproductive strategies among flowering plants,\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}} which have long been of interest to pollination biologists in terms of their relevance to plant-pollinator interactions.
+However, most studies that have explored reproductive (e.g., mating and compatibility systems) and floral trait (e.g., flower size or nectar provision) variation have concentrated on the individual or community level and thus, broader macroecological patterns remain poorly investigated.\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3}--\protect\hyperlink{ref-grossenbacher2017}{7}} Indeed, studies depicting species' life history strategies generally focus on vegetative traits and rarely consider reproductive traits.\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}} As a consequence, a unified framework that explores the compromises among floral traits and their relevance to plant life strategies is currently lacking.\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}} At the same time, there is growing interest in the determinants of plant-pollinator interactions via trait-based approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{11}} and trait-matching analyses.\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{12}} However, floral traits have been overlooked beyond highly specialised plant-pollinator systems\textsuperscript{\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-dellinger2020}{13}} and the role of plant reproductive biology remains little explored in plant-pollinator interactions (but see references\textsuperscript{\protect\hyperlink{ref-tur2013}{14},\protect\hyperlink{ref-devaux2014}{15}}).
 
-With the recent availability of large trait databases, plant ecological
-strategies are increasingly being
-examined\textsuperscript{\protect\hyperlink{ref-kattge2011}{16},\protect\hyperlink{ref-salguero2015}{17}},
-and are facilitating the identification of global patterns and
-constraints of plant form and
-function\textsuperscript{\protect\hyperlink{ref-salguero2016}{8},\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}}.
-However, the main focus has been on vegetative traits such as
-leaf\textsuperscript{\protect\hyperlink{ref-wright2004}{20}} or
-wood\textsuperscript{\protect\hyperlink{ref-chave2009}{21}} trade-offs
-with little or no attention given to reproductive and floral
-traits\textsuperscript{\protect\hyperlink{ref-evojtko2020}{22}}, also
-critical to plant form and function. For instance, short lived versus
-perennial species tend to have low versus high levels of outcrossing,
-respectively\textsuperscript{\protect\hyperlink{ref-moeller2017}{6},\protect\hyperlink{ref-barrett2003}{23}}.
-Further, outcrossing levels are positively correlated with flower
-size\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{24}}. In
-addition, the presence of costly rewards (e.g., pollen or nectar) and
-showy flowers or floral displays can only be understood through
-consideration of plant species' reliance upon animal pollination
-(pollinator dependence) and their role in attracting
-pollinators\textsuperscript{\protect\hyperlink{ref-ollerton2011}{25}}.
-Hence, exploring plant life strategies with reproductive and floral
-trade-offs, in conjunction with their pollinator dependence, is
-necessary for a balanced understanding of plant economics.
+With the recent availability of large trait databases, plant ecological strategies are increasingly being examined,\textsuperscript{\protect\hyperlink{ref-kattge2011}{16},\protect\hyperlink{ref-salguero2015}{17}} and are facilitating the identification of global patterns and constraints of plant form and function.\textsuperscript{\protect\hyperlink{ref-salguero2016}{8},\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}} However, the main focus has been on vegetative traits such as leaf\textsuperscript{\protect\hyperlink{ref-wright2004}{20}} or wood\textsuperscript{\protect\hyperlink{ref-chave2009}{21}} trade-offs with little or no attention given to reproductive and floral traits,\textsuperscript{\protect\hyperlink{ref-evojtko2020}{22}} also critical to plant form and function.
+For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively.\textsuperscript{\protect\hyperlink{ref-moeller2017}{6},\protect\hyperlink{ref-barrett2003}{23}} Further, outcrossing levels are positively correlated with flower size.\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{24}} In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species' reliance upon animal pollination (pollinator dependence) and their role in attracting pollinators.\textsuperscript{\protect\hyperlink{ref-ollerton2011}{25}} Hence, exploring plant life strategies with reproductive and floral trade-offs, in conjunction with their pollinator dependence, is necessary for a balanced understanding of plant economics.
 
-Several studies have identified links between plant traits and
-plant-pollinator network
-properties\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3},\protect\hyperlink{ref-lazaro2008}{26},\protect\hyperlink{ref-bartomeus2013}{27}}.
-Moreover, plant traits can also define species' network roles (e.g.,
-specialists vs generalists). For example, species that occupy trait
-space extremes are more likely to exhibit higher specialization and be
-more reliant on
-trait-matching\textsuperscript{\protect\hyperlink{ref-junker2013}{28},\protect\hyperlink{ref-coux2016}{29}}.
-This morphological matching between plant and floral visitors can
-determine plant-pollinator interactions, and thus shape their
-interaction network
-structure\textsuperscript{\protect\hyperlink{ref-stang2009}{30},\protect\hyperlink{ref-ibanez2012}{31}}.
-Despite the increasing knowledge of the relevance of traits on the
-species network roles, little is known about how plant reproductive and
-floral traits determine plant species' network roles at a
-macroecological scale.
+Several studies have identified links between plant traits and plant-pollinator network properties.\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3},\protect\hyperlink{ref-lazaro2008}{26},\protect\hyperlink{ref-bartomeus2013}{27}} Moreover, plant traits can also define species' network roles (e.g., specialists vs generalists).
+For example, species that occupy trait space extremes are more likely to exhibit higher specialization and be more reliant on trait-matching.\textsuperscript{\protect\hyperlink{ref-junker2013}{28},\protect\hyperlink{ref-coux2016}{29}} This morphological matching between plant and floral visitors can determine plant-pollinator interactions, and thus shape their interaction network structure.\textsuperscript{\protect\hyperlink{ref-stang2009}{30},\protect\hyperlink{ref-ibanez2012}{31}} Despite the increasing knowledge of the relevance of traits on the species network roles, little is known about how plant reproductive and floral traits determine plant species' network roles at a macroecological scale.
 
-Here, we explore the potential trade-offs among plant floral and
-reproductive traits and how these influence the structure of
-plant-pollinator networks. First, we identify the major axes of floral
-and reproductive trait variation and trade-offs that determine plant
-form and function. Second, we investigate how plant species' position in
-trait-space influences interaction strength with different guilds of
-floral visitors. Finally, we investigate how the main axes of trait
-variation and individual traits influence plant species roles within
-networks using complementary interaction network metrics (i.e.,
-interaction strength, normalized degree and specialization).
+Here, we explore the potential trade-offs among plant floral and reproductive traits and how these influence the structure of plant-pollinator networks.
+First, we identify the major axes of floral and reproductive trait variation and trade-offs that determine plant form and function.
+Second, we investigate how plant species' position in trait-space influences interaction strength with different guilds of floral visitors.
+Finally, we investigate how the main axes of trait variation and individual traits influence plant species roles within networks using complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
 
-\section{RESULTS}\label{results}
+\hypertarget{results}{%
+\section{RESULTS}\label{results}}
 
-\textbf{Plant strategies.} The phylogenetically informed principal
-component analysis (pPCA) captured by the first two and three axes
-51.8\% and 70.97\% of trait variation, respectively (Fig. 1 and
-Supplementary Fig. S5) and had a phylogenetic correlation (\(\lambda\))
-of 0.76. The first principal component (PC1) represented 26.72\% of the
-trait variation and indicated a trade-off between flower number and
-flower size. We refer to this axis as the `flower number - flower size
-trade-off' as already described in previous
-studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{32},\protect\hyperlink{ref-kettle2011}{33}}.
-Hence, one end of the spectrum comprised species with high investment in
-flower number and plant height but small flower size, short style length
-and low ovule number. The other end of this spectrum comprised species
-that were short in height and invested in large flowers, long styles,
-many ovules, but few flowers. The main contributing traits to PC1 were
-plant height, flower number, ovule number and flower size (loadings
-\textgreater{} \textbar{}0.5\textbar{}; Supplementary Table S3) but
-style length also contributed moderately on PC1 (loading = -0.33). The
-second principal component (PC2) represented 25.05\% of the trait
-variation and indicated a trade-off between low and high pollinator
-dependence. We refer to this axis as the `pollinator dependence
-trade-off'. The main driver of trait variation on PC2 was autonomous
-selfing (loading = 0.85) but the other traits (except ovule number) also
-made moderate contributions (loadings from 0.27 to 0.4; Supplementary
-Table S3). We found that high pollinator dependence was associated with
-larger and a higher number of flowers, greater plant height and longer
-styles. In contrast, species with high levels of autonomous selfing
-tended to have fewer and smaller flowers, had shorter styles and were
-shorter in height. Further, PC3 explained a considerable amount of trait
-variability (19.17\%) and the main contributors to this axis were style
-length (loading = -0.66) and the degree of autonomous selfing (loading =
--0.51). The remaining traits, apart from ovule number, were moderately
-correlated to changes on PC3 (loadings from -0.23 to -0.46;
-Supplementary Table S3). Thus, because style length was correlated with
-all traits on PC3 and was the main driver of trait variation, we refer
-to this axis as the `style length trade-off'. Further, the pPCA with the
-subset of species that had nectar and pollen quantity data showed that
-nectar quantity (microlitres of nectar per flower) was positively
-associated with flower size, style length and ovule number (PC1,
-23.40\%); and pollen quantity (pollen grains per flower) was positively
-correlated with flower number and plant height and negatively associated
-with autonomous selfing (PC2, 21.67\%; Supplementary Fig. S6). This pPCA
-explained similar variance with the first two principal components
-(45.07\%) and similar associations of traits despite some variability in
-the loadings (Supplementary Table S4).
+\textbf{Plant strategies.} The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8\% and 70.97\% of trait variation, respectively (Fig.
+1 and Supplementary Fig.
+S5) and had a phylogenetic correlation (\(\lambda\)) of 0.76.
+The first principal component (PC1) represented 26.72\% of the trait variation and indicated a trade-off between flower number and flower size.
+We refer to this axis as the `flower number - flower size trade-off' as already described in previous studies.\textsuperscript{\protect\hyperlink{ref-sargent2007}{32},\protect\hyperlink{ref-kettle2011}{33}} Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
+The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Supplementary Table S3) but style length also contributed moderately on PC1 (loading = -0.33).
+The second principal component (PC2) represented 25.05\% of the trait variation and indicated a trade-off between low and high pollinator dependence.
+We refer to this axis as the `pollinator dependence trade-off'.
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Supplementary Table S3).
+We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
+In contrast, species with high levels of autonomous selfing tended to have fewer and smaller flowers, had shorter styles and were shorter in height.
+Further, PC3 explained a considerable amount of trait variability (19.17\%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
+The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Supplementary Table S3).
+Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the `style length trade-off'.
+Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 23.40\%); and pollen quantity (pollen grains per flower) was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 21.67\%; Supplementary Fig.
+S6).
+This pPCA explained similar variance with the first two principal components (45.07\%) and similar associations of traits despite some variability in the loadings (Supplementary Table S4).
 
@@
 \includegraphics{output/figures/unnamed-chunk-1-1.pdf}
-\caption{\label{fig:unnamed-chunk-1}\textbf{Fig. 1 \textbar{} Plant
-life-history strategies.} Phylogenetically informed principal component
-analysis (pPCA) of 1,236 plant species from 28 plant-pollinator networks
-studies. The solid arrows indicate the direction of the different
-quantitative traits (flower number, plant height, style length, flower
-size, ovule number and level of autonomous selfing) across the two main
-axes of trait variation. The length of the arrows indicate the weight of
-the variables on each principal component and the labelled icons at
-their end represent the extreme form of the trait continuum. The dashed
-lines show the opposed direction of trait variation and the non-labelled
-icons at their end illustrate the opposing extreme of the continuum.}
+\caption{\label{fig:unnamed-chunk-1}\textbf{Fig.
+1 \textbar{} Plant life-history strategies.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator networks studies.
+The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
+The length of the arrows indicate the weight of the variables on each principal component and the labelled icons at their end represent the extreme form of the trait continuum.
+The dashed lines show the opposed direction of trait variation and the non-labelled icons at their end illustrate the opposing extreme of the continuum.}
 \end{figure}
 
-We found that most categorical traits were statistically associated with
-the first two axes of trait variation (Fig. 2 and Supplementary Table
-S2). Flower symmetry, which was only associated with PC2 (Sum of squares
-= 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar
-provision, which was independent of PC1 and PC2 (PC1: Sum of squares =
-0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83,
-F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
-In addition, we found with Tukey test statistical differences between
-the different levels of categorical traits in the trait space
-(Supplementary Fig. S7). Regarding self compatibility, we found larger
-differences on PC2 (i.e., species with unisexual flowers that were self
-incompatibile were statistically differentiated from species with
-partial or full self compatibility; Supplementary Fig. S7a and Fig.
-S7b). Life forms differed statistically across both axes of trait
-variation and followed a gradient of larger life forms (trees and
-shrubs) with higher pollinator dependence to smaller ones (herbs) with
-lower pollinator dependence (Supplementary Fig. S7c and Fig. S7d).
-Consequently, lifespan also followed this gradient but perennial and
-short lived species only differed statistically on PC2 (Supplementary
-Fig. S7e and Fig. S7f). Species with unisexual flowers (monoecious and
-dioecious) were clustered on both extremes of the first two principal
-components and had the highest pollinator dependence and highest number
-of flowers (Supplementary Fig. S7g and Fig. S7h). Moreover, we found
-that the campanulate and capitulum flower shapes were differentiated
-from tube, papilionaceous, open and brush shapes in the trait space. The
-former morphologies had larger flowers and greater pollinator
-dependence, while the latter had higher flower number and greater
-autonomous selfing (Supplementary Fig. S7i and Fig. S7j). Regarding
-flower symmetry, zygomorphic flowers were associated with lower levels
-of pollinator dependence, whereas actinomorphic flowers had higher
-levels of pollinator dependence (Supplementary Fig. S7k and Fig. S7l).
+We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
+2 and Supplementary Table S2).
+Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
+In addition, we found with Tukey test statistical differences between the different levels of categorical traits in the trait space (Supplementary Fig.
+S7).
+Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatibile were statistically differentiated from species with partial or full self compatibility; Supplementary Fig.
+S7a and Fig.
+S7b).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Supplementary Fig.
+S7c and Fig.
+S7d).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Supplementary Fig.
+S7e and Fig.
+S7f).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Supplementary Fig.
+S7g and Fig.
+S7h).
+Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Supplementary Fig.
+S7i and Fig.
+S7j).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Supplementary Fig.
+S7k and Fig.
+S7l).
 
@@
 \includegraphics{output/figures/unnamed-chunk-2-1.pdf}
-\caption{\label{fig:unnamed-chunk-2}\textbf{Fig. 2 \textbar{} Location of
-the different qualitative traits on the trait space.} The panel is
-composed by the traits that showed statistical association with the
-first two axes of trait variation: compatibility system (a), life form
-(b), lifespan (c), breeding system (d), flower shape (e) and flower
-symmetry (f).}
+\caption{\label{fig:unnamed-chunk-2}\textbf{Fig.
+2 \textbar{} Location of the different qualitative traits on the trait space.} The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).}
 \end{figure}
@@
 
-\textbf{Phylogenetic signal of traits.} We found a strong phylogenetic
-signal (\emph{P} \textless{} 0.01) in all quantitative traits
-(Supplementary Table S5). The traits that showed the highest
-phylogenetic signal were ovule number (\(\lambda = 1\)), pollen grains
-per flower (\(\lambda = 1\)) and plant height (\(\lambda = 0.96\)),
-followed by flower length (\(\lambda = 0.75\)), flower width
-(\(\lambda = 0.73\)), number of flowers per plant (\(\lambda = 0.69\))
-and nectar concentration (\(\lambda = 0.65\)). The traits that showed a
-moderate phylogenetic signal were inflorescence width
-(\(\lambda = 0.57\)), style length (\(\lambda = 0.49\)) and autonomous
-selfing (\(\lambda = 0.34\)). Finally, microliters of nectar per flower
-showed the lowest phylogenetic signal of all traits
-(\(\lambda = 0.14\)).
+\textbf{Phylogenetic signal of traits.} We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) in all quantitative traits (Supplementary Table S5).
+The traits that showed the highest phylogenetic signal were ovule number (\(\lambda = 1\)), pollen grains per flower (\(\lambda = 1\)) and plant height (\(\lambda = 0.96\)), followed by flower length (\(\lambda = 0.75\)), flower width (\(\lambda = 0.73\)), number of flowers per plant (\(\lambda = 0.69\)) and nectar concentration (\(\lambda = 0.65\)).
+The traits that showed a moderate phylogenetic signal were inflorescence width (\(\lambda = 0.57\)), style length (\(\lambda = 0.49\)) and autonomous selfing (\(\lambda = 0.34\)).
+Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits (\(\lambda = 0.14\)).
 
-\textbf{Visitation patterns.} The main axes of trait variation explained
-little of the overall visitation rates (\(conditional R2 = 0.31\);
-\(marginal R2 = 0.06\)) but showed relevant trends when we explored the
-interaction with the different floral visitors guilds (Fig. 3). All
-floral visitors guilds visited plant species with higher pollinator
-dependence more frequently (PC2; Fig. 3b and Fig. 3e). In addition, all
-guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera,
-non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on
-species with small numerous flowers (PC1; Fig. 3a and Fig. 3d). On the
-style length trade-off (PC3), Anthophila-Hymenoptera, Lepidoptera and
-Non-Anthophila-Hymenoptera showed greater visitation rates on plant
-species with larger styles and higher levels of selfing; while
-Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation
-rates on species with shorter styles and lower selfing (Fig. 3c and Fig.
-3f). Furthermore, when running an additional model that separates the
-most represented families of Anthophila-Hymenoptera (bees;
-\(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) showed that the
-family Apidae was the main driver of the observed patterns
-(Supplementary Fig. S8).
+\textbf{Visitation patterns.} The main axes of trait variation explained little of the overall visitation rates (\(conditional R2 = 0.31\); \(marginal R2 = 0.06\)) but showed relevant trends when we explored the interaction with the different floral visitors guilds (Fig.
+3).
+All floral visitors guilds visited plant species with higher pollinator dependence more frequently (PC2; Fig.
+3b and Fig.
+3e).
+In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig.
+3a and Fig.
+3d).
+On the style length trade-off (PC3), Anthophila-Hymenoptera, Lepidoptera and Non-Anthophila-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
+3c and Fig.
+3f).
+Furthermore, when running an additional model that separates the most represented families of Anthophila-Hymenoptera (bees; \(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) showed that the family Apidae was the main driver of the observed patterns (Supplementary Fig.
+S8).
 
@@
 \includegraphics{output/figures/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}\textbf{Fig. 3 \textbar{} Visitation
-rates across the three main axes of trait variation.} Fitted posterior
-estimates of the number of visits made by the different floral visitors
-guilds in relation to PC1, PC2 and PC3. Bees (a, b and c) and the rest
-of guilds (d, e and f) were plotted separately for visualization
-purposes. In addition, we trimmed the plotting area that was over the
-95th percentile to improve visualisation. PC1 represents the flower
-number - flower size trade-off, PC2 represents the pollinator dependence
-trade-off and PC3, the style length trade-off.}
+\caption{\label{fig:unnamed-chunk-3}\textbf{Fig.
+3 \textbar{} Visitation rates across the three main axes of trait variation.} Fitted posterior estimates of the number of visits made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
+Bees (a, b and c) and the rest of guilds (d, e and f) were plotted separately for visualization purposes.
+In addition, we trimmed the plotting area that was over the 95th percentile to improve visualisation.
+PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.}
 \end{figure}
@@
 
-\textbf{Plant species functional roles.} The variance of the different
-plant species level metrics was poorly explained by the three main axes
-of trait variation (Supplementary Fig. S9; interaction frequency
-\textasciitilde{} PCs, \(conditional R2 = 0.11\),
-\(marginal R2 = 0.02\); normalized degree \textasciitilde{} PCs,
-\(conditional R2 = 0.24\), \(marginal R2 = 0.02\); and, specialization
-\textasciitilde{} PCs, \(conditional R2 = 0.37\),
-\(marginal R2 = 0.03\)). Overall, the most notable trends were found on
-PC1 and PC3 for interaction frequency and specialization. On the flower
-number - flower size trade-off (PC1), interaction frequency was higher
-for plant species with more flowers but was lower for plant species with
-larger flowers. On PC1, specialization showed the opposite trend. On the
-style length trade-off (PC3), interaction frequency was lower for plants
-with shorter styles and lower autonomous selfing and higher for species
-with longer styles and higher autonomous selfing. Again, specialization
-showed the opposite trend to interaction frequency.
+\textbf{Plant species functional roles.} The variance of the different plant species level metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
+S9; interaction frequency \textasciitilde{} PCs, \(conditional R2 = 0.11\), \(marginal R2 = 0.02\); normalized degree \textasciitilde{} PCs, \(conditional R2 = 0.24\), \(marginal R2 = 0.02\); and, specialization \textasciitilde{} PCs, \(conditional R2 = 0.37\), \(marginal R2 = 0.03\)).
+Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
+On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers.
+On PC1, specialization showed the opposite trend.
+On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing.
+Again, specialization showed the opposite trend to interaction frequency.
 
-When we further investigate which combination of traits drive plant
-network roles, we show that the regression tree for visitation frequency
-was best explained by plant height, nectar concentration and style
-length (Fig. 4a). Specifically, species taller than 3.9 m had the
-highest interaction frequency, while species that were shorter than 3.9
-m and had a nectar concentration lower than 16\% had the lowest
-interaction frequency. Normalized degree was best explained by nectar
-concentration, pollen grains per flower, plant height, flower width and
-autonomous selfing (Fig. 4b). Species with a nectar concentration over
-49\% had the highest levels of normalized degree, whereas species with
-nectar concentration lower than 49\%, more than 21,000 pollen grains per
-flower and height less than 0.78 m had the lowest normalized degree.
-Finally, specialization was best explained by plant height, ovule
-number, pollen grains per flower and autonomous selfing (Fig. 4c).
-Overall, plant species with the highest specialization were shorter than
-1.3 m, had more than 14,000 pollen grains per flower and autonomously
-self-pollinated less than 11\% of their fruits. In contrast, species
-taller or equal than 5.1 m and with lower than 14 ovules per flower had
-the lowest specialization values.
+When we further investigate which combination of traits drive plant network roles, we show that the regression tree for visitation frequency was best explained by plant height, nectar concentration and style length (Fig.
+4a).
+Specifically, species taller than 3.9 m had the highest interaction frequency, while species that were shorter than 3.9 m and had a nectar concentration lower than 16\% had the lowest interaction frequency.
+Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
+4b).
+Species with a nectar concentration over 49\% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49\%, more than 21,000 pollen grains per flower and height less than 0.78 m had the lowest normalized degree.
+Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
+4c).
+Overall, plant species with the highest specialization were shorter than 1.3 m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11\% of their fruits.
+In contrast, species taller or equal than 5.1 m and with lower than 14 ovules per flower had the lowest specialization values.
 
@@
 \includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\textbf{Fig. 4 \textbar{} contribution
-of traits in plant's network roles.} Regression tree analysis of
-interaction frequency (log-transformed), normalized degree and
-specialization for the subset of species with quantitative data for
-pollen and nectar traits. The superior value inside the node indicates
-the mean value of the different species-level metric and the lower
-value, the percentage of species that are considered in each node. Thus,
-the top node has the mean value of the named trait for the 100\% of
-species. Each node has a yes/no question and when the condition is
-fulfilled, the branch turns to the `yes' direction and when not, to the
-`no' direction. This rationale is followed in all the regression trees
-as indicated in the first branch division of the topmost node of each
-tree.}
+\caption{\label{fig:unnamed-chunk-4}\textbf{Fig.
+4 \textbar{} contribution of traits in plant's network roles.} Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
+The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
+Thus, the top node has the mean value of the named trait for the 100\% of species.
+Each node has a yes/no question and when the condition is fulfilled, the branch turns to the `yes' direction and when not, to the `no' direction.
+This rationale is followed in all the regression trees as indicated in the first branch division of the topmost node of each tree.}
 \end{figure}
@@
 
-\section{DISCUSSION}\label{discussion}
+\hypertarget{discussion}{%
+\section{DISCUSSION}\label{discussion}}
 
-Here, we show that plant species exhibit clear trade-offs in their
-floral, reproductive and vegetative traits. These trade-offs are
-differentiated on three main axes of trait variation: (i) flower number
-- flower size, (ii) pollinator dependence and (iii) style length.
-Although these axes of trait variation did not explain overall
-visitation rates, we found that plant life strategies were clearly
-associated with different floral visitors guilds. Interestingly, pollen
-and nectar related traits were better than all other traits for
-characterizing plant species functional roles within their interaction
-networks.
+Here, we show that plant species exhibit clear trade-offs in their floral, reproductive and vegetative traits.
+These trade-offs are differentiated on three main axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
+Although these axes of trait variation did not explain overall visitation rates, we found that plant life strategies were clearly associated with different floral visitors guilds.
+Interestingly, pollen and nectar related traits were better than all other traits for characterizing plant species functional roles within their interaction networks.
 
-Over 50\% of plant trait variation was captured by the flower number -
-flower size and pollinator dependence trade-offs. Variation in these two
-axes of trait variation appears to be associated with the commonly
-described `fast-slow continuum' in
-plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}} and
-animal\textsuperscript{\protect\hyperlink{ref-healy2019}{34}}
-life-history strategies as indicated by the different floral and
-reproductive traits associated with plant height, life form and
-lifespan. The `slow' part of the continuum (i.e., tall trees and shrubs)
-had plant species with many flowers, few ovules, higher pollinator
-dependence, greater occurrence of self-incompatibility and more complex
-breeding systems (e.g., monoecious and dioecious species). In contrast,
-species that employed the `fast' strategy (i.e., short herbs), had fewer
-flowers, more ovules, greater occurrence of self compatibility and lower
-pollinator dependence. Further, on the first two axes of trait
-variation, we found additional support for the positive association
-already described in a previous study between outcrossing rate and
-floral
-display\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{24}}.
-This trend was further confirmed when looking at the specific
-correlation between floral display and autonomous selfing for our
-dataset (see Supplementary Fig. S10).
+Over 50\% of plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
+Variation in these two axes of trait variation appears to be associated with the commonly described `fast-slow continuum' in plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}} and animal\textsuperscript{\protect\hyperlink{ref-healy2019}{34}} life-history strategies as indicated by the different floral and reproductive traits associated with plant height, life form and lifespan.
+The `slow' part of the continuum (i.e., tall trees and shrubs) had plant species with many flowers, few ovules, higher pollinator dependence, greater occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
+In contrast, species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, greater occurrence of self compatibility and lower pollinator dependence.
+Further, on the first two axes of trait variation, we found additional support for the positive association already described in a previous study between outcrossing rate and floral display.\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{24}} This trend was further confirmed when looking at the specific correlation between floral display and autonomous selfing for our dataset (see Supplementary Fig.
+S10).
 
-Despite the low predictive power of the main axes of trait variation on
-overall visitation patterns, we found commonalities among and within
-floral visitors guilds across these axes that indicate the influence of
-life-history strategies on floral visitation rate. For example, all
-guilds showed an increasing trend of visitation on plant species with
-higher pollinator dependence, which were also associated with larger
-floral displays and greater pollen quantities (Fig. 1 and Supplementary
-Fig. S6). This trend is consistent with previous plant-pollinator
-studies that show higher visitation rates on species that make greater
-reproductive
-investment\textsuperscript{\protect\hyperlink{ref-hegland2005}{35}--\protect\hyperlink{ref-kaiser2014}{37}}.
-In regard to the flower number - flower size and style length
-trade-offs, different guilds showed contrasting visitation rates, which
-could be associated with different pollination syndromes at a
-macroecological scale. For instance, the guilds of bees and syrphids
-were clearly associated with opposing life-strategies on PC1 and PC3
-(Fig. 3) indicating a possible niche partitioning among these two
-guilds\textsuperscript{\protect\hyperlink{ref-palmer2003}{38},\protect\hyperlink{ref-phillips2020}{39}}.
-However, these plant-pollinator associations do not account for some of
-the traits (i.e., pollen and nectar quantity) that had greater relevance
-on the species network roles (Fig. 4) because of insufficient data
-availability and lack of pollinator efficiency measurements for more
-complete descriptions of the pollination
-syndromes\textsuperscript{\protect\hyperlink{ref-dellinger2020}{13}}. In
-any case, it is worth noting that this general pattern emerges in
-field-measured plant-pollinator networks, where other local factors such
-as species relative abundances, will surely explain part of the observed
-variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{12},\protect\hyperlink{ref-vazquez2007}{40},\protect\hyperlink{ref-encinas2012}{41}}.
+Despite the low predictive power of the main axes of trait variation on overall visitation patterns, we found commonalities among and within floral visitors guilds across these axes that indicate the influence of life-history strategies on floral visitation rate.
+For example, all guilds showed an increasing trend of visitation on plant species with higher pollinator dependence, which were also associated with larger floral displays and greater pollen quantities (Fig.
+1 and Supplementary Fig.
+S6).
+This trend is consistent with previous plant-pollinator studies that show higher visitation rates on species that make greater reproductive investment.\textsuperscript{\protect\hyperlink{ref-hegland2005}{35}--\protect\hyperlink{ref-kaiser2014}{37}} In regard to the flower number - flower size and style length trade-offs, different guilds showed contrasting visitation rates, which could be associated with different pollination syndromes at a macroecological scale.
+For instance, the guilds of bees and syrphids were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
+3) indicating a possible niche partitioning among these two guilds.\textsuperscript{\protect\hyperlink{ref-palmer2003}{38},\protect\hyperlink{ref-phillips2020}{39}} However, these plant-pollinator associations do not account for some of the traits (i.e., pollen and nectar quantity) that had greater relevance on the species network roles (Fig.
+4) because of insufficient data availability and lack of pollinator efficiency measurements for more complete descriptions of the pollination syndromes.\textsuperscript{\protect\hyperlink{ref-dellinger2020}{13}} In any case, it is worth noting that this general pattern emerges in field-measured plant-pollinator networks, where other local factors such as species relative abundances, will surely explain part of the observed variability.\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{12},\protect\hyperlink{ref-vazquez2007}{40},\protect\hyperlink{ref-encinas2012}{41}}
 
-To conclude, we provide the first description of plant floral and
-reproductive trade-offs using a large global dataset of plant traits and
-interactions with floral visitors. This allowed us to identify the major
-reproductive strategies of flowering plants and how plant life
-strategies determine their interaction with floral visitor guilds.
-Although the percentage of explained variation found with the first two
-axes (\textasciitilde{}50\%) is lower than other studies that have
-evaluated life histories with vegetative
-traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}},
-this percentage is consistent with the largest and most recent study
-that have characterized life strategies with both vegetative and
-reproductive (i.e., semelparity and iteroparity)
-traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}}. Future
-work needs to integrate these floral and reproductive compromises with
-the already described vegetative and physiological
-trade-offs\textsuperscript{\protect\hyperlink{ref-diaz2016}{18}} to
-create a more comprehensive spectra of trait
-variation\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}}.
-Further, the varying level of phylogenetic signal among traits deserves
-further attention to understand evolutionary changes on mating and
-flower morphology in response to
-pollinators\textsuperscript{\protect\hyperlink{ref-gervasi2017}{42},\protect\hyperlink{ref-mackin2021}{43}}.
-Finally, a more complete description of the macroecological patterns of
-plant-pollinator interactions including unrepresented areas of the
-world\textsuperscript{\protect\hyperlink{ref-poisot2021}{44}} and traits
-that have been largely ignored (e.g., floral rewards and plant mating
-system) are needed to progress in our understanding of the global
-patterns in plant-pollinator interactions.
+To conclude, we provide the first description of plant floral and reproductive trade-offs using a large global dataset of plant traits and interactions with floral visitors.
+This allowed us to identify the major reproductive strategies of flowering plants and how plant life strategies determine their interaction with floral visitor guilds.
+Although the percentage of explained variation found with the first two axes (\textasciitilde50\%) is lower than other studies that have evaluated life histories with vegetative traits,\textsuperscript{\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}} this percentage is consistent with the largest and most recent study that have characterized life strategies with both vegetative and reproductive (i.e., semelparity and iteroparity) traits.\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}} Future work needs to integrate these floral and reproductive compromises with the already described vegetative and physiological trade-offs\textsuperscript{\protect\hyperlink{ref-diaz2016}{18}} to create a more comprehensive spectra of trait variation.\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}} Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators.\textsuperscript{\protect\hyperlink{ref-gervasi2017}{42},\protect\hyperlink{ref-mackin2021}{43}} Finally, a more complete description of the macroecological patterns of plant-pollinator interactions including unrepresented areas of the world\textsuperscript{\protect\hyperlink{ref-poisot2021}{44}} and traits that have been largely ignored (e.g., floral rewards and plant mating system) are needed to progress in our understanding of the global patterns in plant-pollinator interactions.
 
-\section{MATERIALS AND METHODS}\label{materials-and-methods}
+\hypertarget{materials-and-methods}{%
+\section{MATERIALS AND METHODS}\label{materials-and-methods}}
 
-\textbf{Plant-pollinator network studies.} We selected 28 studies from
-18 different countries that constituted a total of 64 plant-pollinator
-networks. These studies recorded plant-pollinator interactions in
-natural systems and were selected so that we had broad geographical
-representation. Although these studies differ in sampling effort and
-methodology, all studies provided information about plant-pollinator
-interactions (weighted and non-weighted), which we used to build a
-database of plant species that are likely to be animal pollinated. Many
-of these networks are freely available either as published
-studies\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3},\protect\hyperlink{ref-fortuna2010}{45}}
-or available in online archives (e.g., `The Web of
-Life'\textsuperscript{\protect\hyperlink{ref-fortuna2010}{45}} and
-`Mangal'\textsuperscript{\protect\hyperlink{ref-poisot2016}{46}}. In
-total, our network dataset (see Supplementary Table S1) constituted 60
-weighted (interaction frequency) and 4 unweighted (presence/absence of
-the interaction) networks, each sampled at a unique location and year,
-as well as eight meta-webs where interactions were pooled across several
-locations and multiple years.
+\textbf{Plant-pollinator network studies.} We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
+These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
+Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
+Many of these networks are freely available either as published studies\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3},\protect\hyperlink{ref-fortuna2010}{45}} or available in online archives (e.g., `The Web of Life'\textsuperscript{\protect\hyperlink{ref-fortuna2010}{45}} and `Mangal'.\textsuperscript{\protect\hyperlink{ref-poisot2016}{46}} In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
 
-\textbf{Taxonomy of plants and pollinators.} All species names, genera,
-families and orders were retrieved and standardized from the taxonomy
-data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for
-plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the
-R package
-\emph{taxize}\textsuperscript{\protect\hyperlink{ref-chamberlain2020}{47}}.
-We filled the `not found' searches manually using
-\url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for
-plants and \url{http://www.catalogueoflife.org/} for floral visitors.
+\textbf{Taxonomy of plants and pollinators.} All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize}.\textsuperscript{\protect\hyperlink{ref-chamberlain2020}{47}} We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
 
-\textbf{Functional traits.} We selected 20 different functional traits
-based on their relevance to plant reproduction and data availability
-(Table 1). These included twelve quantitative and eight categorical
-traits belonging to three broader trait groupings (13 floral, 4
-reproductive and 3 vegetative). For each plant species, we undertook an
-extensive literature and online search across a wide range of resources
-(plant databases, online floras, books, journals and images). From a
-total of 30,120 cells (20 columns × 1,506 species) we were able to fill
-24,341 cells (80.8\% of the dataset, see Supplementary Fig. S1 for
-missing values information for each trait).
+\textbf{Functional traits.} We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
+These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive and 3 vegetative).
+For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
+From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8\% of the dataset, see Supplementary Fig.
+S1 for missing values information for each trait).
 
-\textbf{Phylogenetic Distance.} We calculated the phylogenetic distance
-between different plant species using the function \emph{get\_tree} from
-the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}),
-which downloads phylogenetic distances from the extended R
-implementation of the Open Tree of
-Life\textsuperscript{\protect\hyperlink{ref-smith2018}{48},\protect\hyperlink{ref-jin2019}{49}}.
+\textbf{Phylogenetic Distance.} We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life.\textsuperscript{\protect\hyperlink{ref-smith2018}{48},\protect\hyperlink{ref-jin2019}{49}}
 
@@
 \fontsize{10}{12}\selectfont
-\begin{tabu} to \linewidth {>{}c>{\raggedright}X>{}c>{\centering}X>{\raggedright}X}
+\begin{tabular}[t]{>{}cl>{}ccl}
 \toprule
@@
 \bottomrule
-\end{tabu}
+\end{tabular}
 \end{table}
@@
 
-\textbf{Data Imputation.} Trait missing values were imputed with the
-function
-\emph{missForest}\textsuperscript{\protect\hyperlink{ref-stekhoven2012}{50}}
-which allows imputation of data sets with continuous and categorical
-variables. We accounted for the phylogenetic distance among species on
-the imputation process by including the eigenvectors of a principal
-component analysis of the phylogenetic distance (PCoA) which has been
-shown to improve the performance of
-\emph{missForest}\textsuperscript{\protect\hyperlink{ref-penone2014}{51}}.
-To extract the eigenvectors, we used the function \emph{PVRdecomp} from
-the package
-\emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{52}} based
-on a previous conceptual framework that considers phylogenetic
-eigenvectors\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{53}}.
-Although the variable of autonomous selfing had a high percentage of
-missing values (68\%), we were able to solve this by back transforming
-the qualitative column of autonomous selfing to numerical. The
-categories of `none', `low', `medium' and `high' were converted to
-representative percentages of each category 0\%, 13\%, 50.5\% and 88\%
-respectively. This reduced the percentage of missing values for this
-column from 68\% to 35\% and allowed the imputation of this variable.
-However, we were unable to include nectar and pollen traits on the
-imputation process because of the high percentage of missing values
-(Supplementary Fig. S1). Hence, the imputed dataset had 1,506 species,
-seven categorical and eight numerical variables and 5.79\% of missing
-values. Further, we conducted an additional imputation on the filtered
-raw data by filled cells of either pollen grains per flower or
-microlitres of nectar. This subset comprised 755 species, 8.01\% missing
-values and all traits but milligrams of nectar (\textasciitilde{}50\% of
-missing values) were included in the imputation process.
+\textbf{Data Imputation.} Trait missing values were imputed with the function \emph{missForest}\textsuperscript{\protect\hyperlink{ref-stekhoven2012}{50}} which allows imputation of data sets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest}.\textsuperscript{\protect\hyperlink{ref-penone2014}{51}} To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{52}} based on a previous conceptual framework that considers phylogenetic eigenvectors.\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{53}} Although the variable of autonomous selfing had a high percentage of missing values (68\%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
+The categories of `none', `low', `medium' and `high' were converted to representative percentages of each category 0\%, 13\%, 50.5\% and 88\% respectively.
+This reduced the percentage of missing values for this column from 68\% to 35\% and allowed the imputation of this variable.
+However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Supplementary Fig.
+S1).
+Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79\% of missing values.
+Further, we conducted an additional imputation on the filtered raw data by filled cells of either pollen grains per flower or microlitres of nectar.
+This subset comprised 755 species, 8.01\% missing values and all traits but milligrams of nectar (\textasciitilde50\% of missing values) were included in the imputation process.
 
-\textbf{Plant strategies.} We explored the trade-offs between different
-quantitative plant functional traits with a phylogenetically informed
-Principal Component Analysis (pPCA). We did not include the quantitative
-variables of flower length and inflorescence width because they were
-highly and moderately correlated to flower width respectively (Pearson's
-correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation
-= 0.36, \emph{P} \textless{} 0.01 respectively), and thus we avoided
-overemphasizing flower size on the spectrum of trait variation. Although
-qualitative traits were not included in the dimensionality reduction
-analysis, we also investigated the association of the different
-qualitative traits with the main axes of trait variation. Prior to the
-analyses, we excluded outliers and standardized the data. Due to the
-high sensitivity of dimensionality reduction to outliers, we excluded
-values within the 2.5th--97.5th percentile
-range\textsuperscript{\protect\hyperlink{ref-legendre2012}{54}}, and
-thus our final dataset had 1,236 species. Then, we log transformed the
-variables to reduce the influence of outliers and z-transformed (X= 0,
-SD=1) so that all variables were within the same numerical range. We
-performed the pPCA using the function \emph{phyl.pca} from the package
-\emph{phytools}\textsuperscript{\protect\hyperlink{ref-revell2012}{55}}
-with the method lambda (\(\lambda\)) that calculates the phylogenetic
-correlation between 0 (phylogenetic independence) and 1 (shared
-evolutionary history) and we implemented the mode covariance because
-values for each variables were on the same scale following
-transformation\textsuperscript{\protect\hyperlink{ref-abdi2010}{56}}.
-Moreover, to corroborate that our imputation of missing values did not
-affect our results, we conducted a pPCA on the full dataset without
-missing values (see Supplementary Fig. S2). We found little difference
-between the explained variance with the imputed dataset (51.08\%) and
-the dataset without missing values (52.87\%). In addition, the loadings
-on each principal component had a similar contribution and correlation
-patterns, with the exception of plant height which showed slight
-variations between the imputed and non-imputed dataset. Finally, we
-conducted an additional phylogenetic informed principal component
-analysis for the subset of species with pollen and nectar quantity. For
-this, we included all quantitative traits considered in the main pPCA
-plus pollen grains and microlitres of nectar per flower.
+\textbf{Plant strategies.} We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01 respectively), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
+Prior to the analyses, we excluded outliers and standardized the data.
+Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th--97.5th percentile range,\textsuperscript{\protect\hyperlink{ref-legendre2012}{54}} and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools}\textsuperscript{\protect\hyperlink{ref-revell2012}{55}} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation.\textsuperscript{\protect\hyperlink{ref-abdi2010}{56}} Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
+S2).
+We found little difference between the explained variance with the imputed dataset (51.08\%) and the dataset without missing values (52.87\%).
+In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
+Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
+For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
 
-\textbf{Phylogenetic signal of traits.} We calculated the phylogenetic
-signal of the different quantitative traits on the imputed dataset with
-the full set of species (N = 1,506) with the package \emph{phytools}
-version
-\emph{0.7-70}\textsuperscript{\protect\hyperlink{ref-revell2012}{55}}
-and we used Pagel's \(\lambda\) as a measurement of the phylogenetic
-signal. However, for pollen and nectar traits, phylogenetic signal was
-calculated only on the subset of species that had quantitative
-information for these traits (N = 755).
+\textbf{Phylogenetic signal of traits.} We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} version \emph{0.7-70}\textsuperscript{\protect\hyperlink{ref-revell2012}{55}} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
 
-\textbf{Networks analyses.} Analyses were conducted on the subset of 60
-weighted networks with interaction frequency sampled in a unique
-flowering season and site, which included 556 plant and 1,126 pollinator
-species. In total, our weighted network dataset (excluding meta-webs)
-included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with
-plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae
-interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions
-and 362 non-Anthophila-Hymenoptera interactions. Although floral
-visitors are not always pollinators and the frequency of visits does not
-consider each pollinator species
-efficiency\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{57}},
-visitation rate provides valuable information of the contribution of
-floral visitors to
-pollination\textsuperscript{\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}}.
-Sampling methods varied across networks but this was accounted for in
-analyses by considering them in the random effects of the modelling
-process. All analyses were conducted in R version \emph{4.0.3}.
+\textbf{Networks analyses.} Analyses were conducted on the subset of 60 weighted networks with interaction frequency sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+In total, our weighted network dataset (excluding meta-webs) included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-Anthophila-Hymenoptera interactions.
+Although floral visitors are not always pollinators and the frequency of visits does not consider each pollinator species efficiency,\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{57}} visitation rate provides valuable information of the contribution of floral visitors to pollination.\textsuperscript{\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}} Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
+All analyses were conducted in R version \emph{4.0.3}.
 
-\textbf{Visitation patterns.} We used Bayesian modelling (see below for
-details) to explore the effect of floral visitors groups and the main
-axes of trait variation (pPCA with imputed dataset) on floral visits per
-plant species. For this, we divided floral visitors into six main guilds
-that differ in life form, behaviour and are likely to play a similar
-ecological role: (i) Hymenoptera-Anthophila (bees), (ii)
-Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii)
-Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi)
-Coleoptera. Moreover, because Hymenoptera-Anthophila was the most
-represented group with 2,256 records and had the highest frequency of
-visits of all groups, we also explored the visitation rate of the main
-Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae,
-Halictidae and Megachilidae) on the trait space. In addition, we found
-that \emph{Apis mellifera} was the floral visitor with the largest
-proportion of records counted (7.55\% of the total). This finding is
-consistent with previous research showing that \emph{A. mellifera} was
-the most frequent floral visitor in a similar dataset of 80
-plant-pollinator networks in natural
-ecosystems\textsuperscript{\protect\hyperlink{ref-hung2018}{60}}. Hence,
-to control for the effect of \emph{A. mellifera} on the observed
-visitation patterns of bees, we conducted an analogous analysis
-excluding \emph{A. mellifera}. We found that \emph{A. mellifera}, was
-partly driving some of the observed trends on PC1 (Supplementary Fig.
-S3). However, we did not detect major differences on PC2 and PC3.
+\textbf{Visitation patterns.} We used Bayesian modelling (see below for details) to explore the effect of floral visitors groups and the main axes of trait variation (pPCA with imputed dataset) on floral visits per plant species.
+For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
+Moreover, because Hymenoptera-Anthophila was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the visitation rate of the main Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total).
+This finding is consistent with previous research showing that \emph{A.
+mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems.\textsuperscript{\protect\hyperlink{ref-hung2018}{60}} Hence, to control for the effect of \emph{A.
+mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis excluding \emph{A.
+mellifera}.
+We found that \emph{A.
+mellifera}, was partly driving some of the observed trends on PC1 (Supplementary Fig.
+S3).
+However, we did not detect major differences on PC2 and PC3.
 
-We implemented Bayesian generalized linear mixed models using the R
-package
-\emph{brms}\textsuperscript{\protect\hyperlink{ref-burkner2017}{61}}. We
-modelled the frequency of visits as a function of the main axes of plant
-trait variation and their interactions with floral visitor functional
-groups (Visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation
-patterns among floral visitors groups to plants with different
-strategies, we included interactions between the main axes of trait
-variation (PC1, PC2 and PC3) and the floral visitor guilds. In this
-model, we added a nested random effect of networks nested within the
-study system to capture the variation in networks among studies and
-within networks. Moreover, we included the phylogenetic covariance
-matrix as a random factor due to the possible shared evolutionary
-histories of species and therefore lack of independence across them. We
-specified this model with a zero inflated negative binomial distribution
-and weakly informative priors from the brms function. We run this model
-for 3,000 iterations and with previous 1,000 warm up iterations. We set
-delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized
-the posterior predictive checks with the function \emph{pp\_check} using
-the \emph{bayesplot}
-package\textsuperscript{\protect\hyperlink{ref-gabry2019}{62}}.
+We implemented Bayesian generalized linear mixed models using the R package \emph{brms}.\textsuperscript{\protect\hyperlink{ref-burkner2017}{61}} We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
+In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
+Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
+We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
+We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package.\textsuperscript{\protect\hyperlink{ref-gabry2019}{62}}
 
-\textbf{Plant species functional roles.} We investigated whether
-different quantitative traits determined plant species functional roles
-using Bayesian modelling and regression trees. For this, we selected
-simple and complementary species-level network metrics commonly applied
-in bipartite network
-studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{63}} with a
-straightforward ecological interpretation relevant to our research
-goals. The different plant species-level metrics were: (i) sum of visits
-per plant species; (ii) normalized degree, calculated as the number of
-links per plant species divided by the total possible number of
-partners; and (iii)
-specialization\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{64}},
-which measures the deviation of an expected random choice of the
-available interaction partners and ranges between 0 (maximum
-generalization) and 1 (maximum specialization). Normalized degree and
-specialization were calculated with the \emph{specieslevel} function
-from the R package
-\emph{bipartite}\textsuperscript{\protect\hyperlink{ref-dormann2008}{63}}.
+\textbf{Plant species functional roles.} We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{63}} with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization,\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{64}} which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite}.\textsuperscript{\protect\hyperlink{ref-dormann2008}{63}}
 
-First, we modelled the distinct plant species metrics (sum of visits,
-normalized degree and plant specialization) as a function of the three
-main axes of trait variation (plant species level metric
-\textasciitilde{} PC1 + PC2 + PC3). For each response variable (i.e.,
-each plant species level metric), we used different distribution
-families (zero inflated negative binomial for the sum of visits, weibull
-for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted
-the same posterior predictive checks for each model as detailed above in
-the `visitation patterns section'.
+First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
+For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
+Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns section'.
 
-Second, to better understand these complex trait relationships, we used
-regression trees. Regression trees are recursive algorithms which can
-detect complex relationships among predictors and allow identification
-of the relevance of specific trait combinations on species functional
-roles. We focused exclusively on quantitative traits because almost all
-categorical traits were statistically associated with the first two axes
-of trait variation (Supplementary Table S2). We conducted this analysis
-using the \emph{rpart}
-package\textsuperscript{\protect\hyperlink{ref-therneau2015}{65}}
-version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50
-observations per terminal node and we used the \emph{rpart.plot}
-package\textsuperscript{\protect\hyperlink{ref-milborrow2015}{66}}
-version \emph{3.0.9} to plot the regression trees. We considered the
-species level indices as response variables (interaction frequency,
-normalized degree and specialization) and we performed one regression
-tree per metric using the different quantitative traits as predictors.
-We calculated two regression trees per plant species-level metric, one
-for the full set of species and another for the subset of species for
-which we had pollen and nectar traits. We focused on regression trees
-that included floral rewards because they consistently showed pollen and
-nectar traits as being the best for explaining the different
-species-level metrics (see Supplementary Fig. S4).
+Second, to better understand these complex trait relationships, we used regression trees.
+Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
+We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
+We conducted this analysis using the \emph{rpart} package\textsuperscript{\protect\hyperlink{ref-therneau2015}{65}} version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package\textsuperscript{\protect\hyperlink{ref-milborrow2015}{66}} version \emph{3.0.9} to plot the regression trees.
+We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
+We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
+We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig.
+S4).
 
-\section{References}\label{references}
+\hypertarget{references}{%
+\section{References}\label{references}}
 
 \hypertarget{refs}{}
-\hypertarget{ref-barrett2002}{}
-1. Barrett, S. C. H. The evolution of plant sexual diversity. \emph{Nat.
-Rev. Genet.} \textbf{3}, 274--284 (2002).
+\leavevmode\hypertarget{ref-barrett2002}{}%
+1. Barrett, S. C. H. The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.} \textbf{3}, 274--284 (2002).
 
-\hypertarget{ref-schiestl2013}{}
-2. Schiestl, F. P. \& Johnson, S. D. Pollinator-mediated evolution of
-floral signals. \emph{Trends Ecol. Evol.} \textbf{28}, 307--315 (2013).
+\leavevmode\hypertarget{ref-schiestl2013}{}%
+2. Schiestl, F. P. \& Johnson, S. D. Pollinator-mediated evolution of floral signals. \emph{Trends Ecol. Evol.} \textbf{28}, 307--315 (2013).
 
-\hypertarget{ref-carvalheiro2014}{}
-3. Carvalheiro, L. G. \emph{et al.} The potential for indirect effects
-between co-flowering plants via shared pollinators depends on resource
-abundance, accessibility and relatedness. \emph{Ecol. Lett.}
-\textbf{17}, 1389--1399 (2014).
+\leavevmode\hypertarget{ref-carvalheiro2014}{}%
+3.
+Carvalheiro, L.
+G.
+\emph{et al.} The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
+\emph{Ecol.
+Lett.} \textbf{17}, 1389--1399 (2014).
 
-\hypertarget{ref-baude2016}{}
-4. Baude, M. \emph{et al.} Historical nectar assessment reveals the fall
-and rise of floral resources in britain. \emph{Nature} \textbf{530},
-85--88 (2016).
+\leavevmode\hypertarget{ref-baude2016}{}%
+4. Baude, M. \emph{et al.} Historical nectar assessment reveals the fall and rise of floral resources in britain. \emph{Nature} \textbf{530}, 85--88 (2016).
 
-\hypertarget{ref-munoz2016}{}
-5. Munoz, F., Violle, C. \& Cheptou, P.-O. CSR ecological strategies and
-plant mating systems: Outcrossing increases with competitiveness but
-stress-tolerance is related to mixed mating. \emph{Oikos} \textbf{125},
-1296--1303 (2016).
+\leavevmode\hypertarget{ref-munoz2016}{}%
+5.
+Munoz, F., Violle, C.
+\& Cheptou, P.-O.
+CSR ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
+\emph{Oikos} \textbf{125}, 1296--1303 (2016).
 
-\hypertarget{ref-moeller2017}{}
-6. Moeller, D. A. \emph{et al.} Global biogeography of mating system
-variation in seed plants. \emph{Ecol. Lett.} \textbf{20}, 375--384
-(2017).
+\leavevmode\hypertarget{ref-moeller2017}{}%
+6. Moeller, D. A. \emph{et al.} Global biogeography of mating system variation in seed plants. \emph{Ecol. Lett.} \textbf{20}, 375--384 (2017).
 
-\hypertarget{ref-grossenbacher2017}{}
-7. Grossenbacher, D. L. \emph{et al.} Self-compatibility is
-over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478
-(2017).
+\leavevmode\hypertarget{ref-grossenbacher2017}{}%
+7. Grossenbacher, D. L. \emph{et al.} Self-compatibility is over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478 (2017).
 
-\hypertarget{ref-salguero2016}{}
-8. Salguero-Gómez, R. \emph{et al.} Fast-slow continuum and reproductive
-strategies structure plant life-history variation worldwide.
-\emph{Proceedings of the National Academy of Sciences of the United
-States of America} \textbf{113}, 230--235 (2016).
+\leavevmode\hypertarget{ref-salguero2016}{}%
+8.
+Salguero-Gómez, R.
+\emph{et al.} Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
+\emph{Proc.
+Natl.
+Acad.
+Sci.
+U.S.A.} \textbf{113}, 230--235 (2016).
 
-\hypertarget{ref-ruger2018}{}
-9. Rüger, N. \emph{et al.} Beyond the fastSlow continuum: Demographic
-dimensions structuring a tropical tree community. \emph{Ecol. Lett.}
-\textbf{21}, 1075--1084 (2018).
+\leavevmode\hypertarget{ref-ruger2018}{}%
+9. Rüger, N. \emph{et al.} Beyond the fastSlow continuum: Demographic dimensions structuring a tropical tree community. \emph{Ecol. Lett.} \textbf{21}, 1075--1084 (2018).
 
-\hypertarget{ref-roddy2021}{}
-10. Roddy, A. B. \emph{et al.} Towards the flower economics spectrum.
-\emph{New Phytol.} \textbf{229}, 665--672 (2021).
+\leavevmode\hypertarget{ref-roddy2021}{}%
+10. Roddy, A. B. \emph{et al.} Towards the flower economics spectrum. \emph{New Phytol.} \textbf{229}, 665--672 (2021).
 
-\hypertarget{ref-fenster2004}{}
-11. Fenster, C. B., Armbruster, W. S., Wilson, P., Dudash, M. R. \&
-Thomson, J. D. Pollination Syndromes and Floral Specialization.
-\emph{Annual Review of Ecology, Evolution, and Systematics} \textbf{35},
-375--403 (2004).
+\leavevmode\hypertarget{ref-fenster2004}{}%
+11. Fenster, C. B., Armbruster, W. S., Wilson, P., Dudash, M. R. \& Thomson, J. D. Pollination Syndromes and Floral Specialization. \emph{Annu. Rev. Ecol. Evol. Syst.} \textbf{35}, 375--403 (2004).
 
-\hypertarget{ref-bartomeus2016}{}
-12. Bartomeus, I. \emph{et al.} A common framework for identifying
-linkage rules across different types of interactions. \emph{Functional
-Ecology} \textbf{30}, 1894--1903 (2016).
+\leavevmode\hypertarget{ref-bartomeus2016}{}%
+12. Bartomeus, I. \emph{et al.} A common framework for identifying linkage rules across different types of interactions. \emph{Funct. Ecol.} \textbf{30}, 1894--1903 (2016).
 
-\hypertarget{ref-dellinger2020}{}
-13. Dellinger, A. S. Pollination syndromes in the 21st century: Where do
-we stand and where may we go? \emph{New Phytol.} \textbf{228},
-1193--1213 (2020).
+\leavevmode\hypertarget{ref-dellinger2020}{}%
+13. Dellinger, A. S. Pollination syndromes in the 21st century: Where do we stand and where may we go? \emph{New Phytol.} \textbf{228}, 1193--1213 (2020).
 
-\hypertarget{ref-tur2013}{}
-14. Tur, C., Castro-Urgal, R. \& Traveset, A. Linking Plant
-Specialization to Dependence in Interactions for Seed Set in Pollination
-Networks. \emph{PLoS ONE} \textbf{8}, e78294 (2013).
+\leavevmode\hypertarget{ref-tur2013}{}%
+14. Tur, C., Castro-Urgal, R. \& Traveset, A. Linking Plant Specialization to Dependence in Interactions for Seed Set in Pollination Networks. \emph{PLoS ONE} \textbf{8}, e78294 (2013).
 
-\hypertarget{ref-devaux2014}{}
-15. Devaux, C., Lepers, C. \& Porcher, E. Constraints imposed by
-pollinator behaviour on the ecology and evolution of plant mating
-systems. \emph{Journal of Evolutionary Biology} \textbf{27}, 1413--1430
-(2014).
+\leavevmode\hypertarget{ref-devaux2014}{}%
+15. Devaux, C., Lepers, C. \& Porcher, E. Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems. \emph{J. Evol. Biol.} \textbf{27}, 1413--1430 (2014).
 
-\hypertarget{ref-kattge2011}{}
-16. Kattge, J. \emph{et al.} TRY a global database of plant traits.
-\emph{Global Change Biology} \textbf{17}, 2905--2935 (2011).
+\leavevmode\hypertarget{ref-kattge2011}{}%
+16. Kattge, J. \emph{et al.} TRY a global database of plant traits. \emph{Glob. Chang. Biol.} \textbf{17}, 2905--2935 (2011).
 
-\hypertarget{ref-salguero2015}{}
-17. Salguero-Gómez, R. \emph{et al.} The compadre Plant Matrix Database:
-An open online repository for plant demography. \emph{Journal of
-Ecology} \textbf{103}, 202--218 (2015).
+\leavevmode\hypertarget{ref-salguero2015}{}%
+17. Salguero-Gómez, R. \emph{et al.} The compadre Plant Matrix Database: An open online repository for plant demography. \emph{J. Ecol.} \textbf{103}, 202--218 (2015).
 
-\hypertarget{ref-diaz2016}{}
-18. Díaz, S. \emph{et al.} The global spectrum of plant form and
-function. \emph{Nature} \textbf{529}, 167--171 (2016).
+\leavevmode\hypertarget{ref-diaz2016}{}%
+18. Díaz, S. \emph{et al.} The global spectrum of plant form and function. \emph{Nature} \textbf{529}, 167--171 (2016).
 
-\hypertarget{ref-carmona2021}{}
-19. Carmona, C. P. \emph{et al.} Erosion of global functional diversity
-across the tree of life. \emph{Science Advances} \textbf{7}, eabf2675
-(2021).
+\leavevmode\hypertarget{ref-carmona2021}{}%
+19. Carmona, C. P. \emph{et al.} Erosion of global functional diversity across the tree of life. \emph{Sci. Adv.} \textbf{7}, eabf2675 (2021).
 
-\hypertarget{ref-wright2004}{}
-20. Wright, I. J. \emph{et al.} The worldwide leaf economics spectrum.
-\emph{Nature} \textbf{428}, 821--827 (2004).
+\leavevmode\hypertarget{ref-wright2004}{}%
+20. Wright, I. J. \emph{et al.} The worldwide leaf economics spectrum. \emph{Nature} \textbf{428}, 821--827 (2004).
 
-\hypertarget{ref-chave2009}{}
-21. Chave, J. \emph{et al.} Towards a worldwide wood economics spectrum.
-\emph{Ecol. Lett.} \textbf{12}, 351--366 (2009).
+\leavevmode\hypertarget{ref-chave2009}{}%
+21. Chave, J. \emph{et al.} Towards a worldwide wood economics spectrum. \emph{Ecol. Lett.} \textbf{12}, 351--366 (2009).
 
-\hypertarget{ref-evojtko2020}{}
-22. E-Vojtkó, A., Bello, F. de, Durka, W., Kühn, I. \& Götzenberger, L.
-The neglected importance of floral traits in trait-based plant community
-assembly. \emph{Journal of Vegetation Science} \textbf{31}, 529--539
-(2020).
+\leavevmode\hypertarget{ref-evojtko2020}{}%
+22.
+E-Vojtkó, A., Bello, F.
+de, Durka, W., Kühn, I.
+\& Götzenberger, L.
+The neglected importance of floral traits in trait-based plant community assembly.
+\emph{J.
+Veg.
+Sci.} \textbf{31}, 529--539 (2020).
 
-\hypertarget{ref-barrett2003}{}
-23. Barrett, S. C. H. Mating strategies in flowering plants: The
-outcrossing-selfing paradigm and beyond. \emph{Philosophical
-Transactions of the Royal Society B: Biological Sciences} \textbf{358},
-991--1004 (2003).
+\leavevmode\hypertarget{ref-barrett2003}{}%
+23. Barrett, S. C. H. Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond. \emph{Philos. Trans. R. Soc. Lond., B, Biol. Sci.} \textbf{358}, 991--1004 (2003).
 
-\hypertarget{ref-goodwillie2010}{}
-24. Goodwillie, C. \emph{et al.} Correlated evolution of mating system
-and floral display traits in flowering plants and its implications for
-the distribution of mating system variation. \emph{New Phytol.}
-\textbf{185}, 311--321 (2010).
+\leavevmode\hypertarget{ref-goodwillie2010}{}%
+24.
+Goodwillie, C.
+\emph{et al.} Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
+\emph{New Phytol.} \textbf{185}, 311--321 (2010).
 
-\hypertarget{ref-ollerton2011}{}
-25. Ollerton, J., Winfree, R. \& Tarrant, S. How many flowering plants
-are pollinated by animals? \emph{Oikos} \textbf{120}, 321--326 (2011).
+\leavevmode\hypertarget{ref-ollerton2011}{}%
+25. Ollerton, J., Winfree, R. \& Tarrant, S. How many flowering plants are pollinated by animals? \emph{Oikos} \textbf{120}, 321--326 (2011).
 
-\hypertarget{ref-lazaro2008}{}
-26. Lázaro, A., Hegland, S. J. \& Totland, Ø. The relationships between
-floral traits and specificity of pollination systems in three
-Scandinavian plant communities. \emph{Oecologia} \textbf{157}, 249--257
-(2008).
+\leavevmode\hypertarget{ref-lazaro2008}{}%
+26.
+Lázaro, A., Hegland, S.
+J.
+\& Totland, Ø.
+The relationships between floral traits and specificity of pollination systems in three Scandinavian plant communities.
+\emph{Oecologia} \textbf{157}, 249--257 (2008).
 
-\hypertarget{ref-bartomeus2013}{}
-27. Bartomeus, I. Understanding Linkage Rules in Plant-Pollinator
-Networks by Using Hierarchical Models That Incorporate Pollinator
-Detectability and Plant Traits. \emph{PLOS ONE} \textbf{8}, e69200
-(2013).
+\leavevmode\hypertarget{ref-bartomeus2013}{}%
+27.
+Bartomeus, I.
+Understanding Linkage Rules in Plant-Pollinator Networks by Using Hierarchical Models That Incorporate Pollinator Detectability and Plant Traits.
+\emph{PLOS ONE} \textbf{8}, e69200 (2013).
 
-\hypertarget{ref-junker2013}{}
-28. Junker, R. R. \emph{et al.} Specialization on traits as basis for
-the niche-breadth of flower visitors and as structuring mechanism of
-ecological networks. \emph{Functional Ecology} \textbf{27}, 329--341
-(2013).
+\leavevmode\hypertarget{ref-junker2013}{}%
+28.
+Junker, R.
+R.
+\emph{et al.} Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
+\emph{Funct.
+Ecol.} \textbf{27}, 329--341 (2013).
 
-\hypertarget{ref-coux2016}{}
-29. Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking
-species functional roles to their network roles. \emph{Ecol. Lett.}
-\textbf{19}, 762--770 (2016).
+\leavevmode\hypertarget{ref-coux2016}{}%
+29. Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking species functional roles to their network roles. \emph{Ecol. Lett.} \textbf{19}, 762--770 (2016).
 
-\hypertarget{ref-stang2009}{}
-30. Stang, M., Klinkhamer, P. G. L., Waser, N. M., Stang, I. \& van der
-Meijden, E. Size-specific interaction patterns and size matching in a
-plantPollinator interaction web. \emph{Annals of Botany} \textbf{103},
-1459--1469 (2009).
+\leavevmode\hypertarget{ref-stang2009}{}%
+30.
+Stang, M., Klinkhamer, P.
+G.
+L., Waser, N.
+M., Stang, I.
+\& van der Meijden, E.
+Size-specific interaction patterns and size matching in a plantPollinator interaction web.
+\emph{Ann.
+Bot.} \textbf{103}, 1459--1469 (2009).
 
-\hypertarget{ref-ibanez2012}{}
-31. Ibanez, S. Optimizing size thresholds in a plant-pollinator
-interaction web: Towards a mechanistic understanding of ecological
-networks. \emph{Oecologia} \textbf{170}, 233--242 (2012).
+\leavevmode\hypertarget{ref-ibanez2012}{}%
+31. Ibanez, S. Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks. \emph{Oecologia} \textbf{170}, 233--242 (2012).
 
-\hypertarget{ref-sargent2007}{}
-32. Sargent, R. D., Goodwillie, C., Kalisz, S. \& Ree, R. H.
-Phylogenetic evidence for a flower size and number trade-off.
-\emph{American Journal of Botany} \textbf{94}, 2059--2062 (2007).
+\leavevmode\hypertarget{ref-sargent2007}{}%
+32. Sargent, R. D., Goodwillie, C., Kalisz, S. \& Ree, R. H. Phylogenetic evidence for a flower size and number trade-off. \emph{Am. J. Bot.} \textbf{94}, 2059--2062 (2007).
 
-\hypertarget{ref-kettle2011}{}
-33. Kettle, C. J. \emph{et al.} Ecological Implications of a Flower
-Size/Number Trade-Off in Tropical Forest Trees. \emph{PLOS ONE}
-\textbf{6}, e16111 (2011).
+\leavevmode\hypertarget{ref-kettle2011}{}%
+33. Kettle, C. J. \emph{et al.} Ecological Implications of a Flower Size/Number Trade-Off in Tropical Forest Trees. \emph{PLOS ONE} \textbf{6}, e16111 (2011).
 
-\hypertarget{ref-healy2019}{}
-34. Healy, K., Ezard, T. H. G., Jones, O. R., Salguero-Gómez, R. \&
-Buckley, Y. M. Animal life history is shaped by the pace of life and the
-distribution of age-specific mortality and reproduction. \emph{Nature
-Ecology \& Evolution} \textbf{3}, 1217--1224 (2019).
+\leavevmode\hypertarget{ref-healy2019}{}%
+34.
+Healy, K., Ezard, T.
+H.
+G., Jones, O.
+R., Salguero-Gómez, R.
+\& Buckley, Y.
+M.
+Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
+\emph{Nat.
+Ecol.
+Evol} \textbf{3}, 1217--1224 (2019).
 
-\hypertarget{ref-hegland2005}{}
-35. Hegland, S. J. \& Totland, Ø. Relationships between species' floral
-traits and pollinator visitation in a temperate grassland.
-\emph{Oecologia} \textbf{145}, 586--594 (2005).
+\leavevmode\hypertarget{ref-hegland2005}{}%
+35. Hegland, S. J. \& Totland, Ø. Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia} \textbf{145}, 586--594 (2005).
 
-\hypertarget{ref-lazaro2013}{}
-36. Lázaro, A., Jakobsson, A. \& Totland, Ø. How do pollinator
-visitation rate and seed set relate to species' floral traits and
-community context? \emph{Oecologia} \textbf{173}, 881--893 (2013).
+\leavevmode\hypertarget{ref-lazaro2013}{}%
+36. Lázaro, A., Jakobsson, A. \& Totland, Ø. How do pollinator visitation rate and seed set relate to species' floral traits and community context? \emph{Oecologia} \textbf{173}, 881--893 (2013).
 
-\hypertarget{ref-kaiser2014}{}
-37. Kaiser-Bunbury, C. N., Vázquez, D. P., Stang, M. \& Ghazoul, J.
-Determinants of the microstructure of plantPollinator networks.
-\emph{Ecology} \textbf{95}, 3314--3324 (2014).
+\leavevmode\hypertarget{ref-kaiser2014}{}%
+37. Kaiser-Bunbury, C. N., Vázquez, D. P., Stang, M. \& Ghazoul, J. Determinants of the microstructure of plantPollinator networks. \emph{Ecology} \textbf{95}, 3314--3324 (2014).
 
-\hypertarget{ref-palmer2003}{}
-38. Palmer, T. M., Stanton, M. L. \& Young, T. P. Competition and
-coexistence: Exploring mechanisms that restrict and maintain diversity
-within mutualist guilds. \emph{the american naturalist} \textbf{162},
-S63--S79 (2003).
+\leavevmode\hypertarget{ref-palmer2003}{}%
+38.
+Palmer, T.
+M., Stanton, M.
+L.
+\& Young, T.
+P.
+Competition and coexistence: Exploring mechanisms that restrict and maintain diversity within mutualist guilds.
+\emph{Am.
+Nat.} \textbf{162}, S63--S79 (2003).
 
-\hypertarget{ref-phillips2020}{}
-39. Phillips, R. D., Peakall, R., van der Niet, T. \& Johnson, S. D.
-Niche perspectives on plantPollinator interactions. \emph{Trends in
-Plant Science} \textbf{25}, 779--793 (2020).
+\leavevmode\hypertarget{ref-phillips2020}{}%
+39. Phillips, R. D., Peakall, R., van der Niet, T. \& Johnson, S. D. Niche perspectives on plantPollinator interactions. \emph{Trends Plant Sci.} \textbf{25}, 779--793 (2020).
 
-\hypertarget{ref-vazquez2007}{}
-40. Vázquez, D. P. \emph{et al.} Species abundance and asymmetric
-interaction strength in ecological networks. \emph{Oikos} \textbf{116},
-1120--1127 (2007).
+\leavevmode\hypertarget{ref-vazquez2007}{}%
+40. Vázquez, D. P. \emph{et al.} Species abundance and asymmetric interaction strength in ecological networks. \emph{Oikos} \textbf{116}, 1120--1127 (2007).
 
-\hypertarget{ref-encinas2012}{}
-41. Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives
-mutualistic network structure and diversity. \emph{Ecol. Lett.}
-\textbf{15}, 198--208 (2012).
+\leavevmode\hypertarget{ref-encinas2012}{}%
+41. Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.} \textbf{15}, 198--208 (2012).
 
-\hypertarget{ref-gervasi2017}{}
-42. Gervasi, D. D. L. \& Schiestl, F. P. Real-time divergent evolution
-in plants driven by pollinators. \emph{Nature Communications}
-\textbf{8}, 14691 (2017).
+\leavevmode\hypertarget{ref-gervasi2017}{}%
+42. Gervasi, D. D. L. \& Schiestl, F. P. Real-time divergent evolution in plants driven by pollinators. \emph{Nat. Commun.} \textbf{8}, 14691 (2017).
 
-\hypertarget{ref-mackin2021}{}
-43. Mackin, C. R., Peña, J. F., Blanco, M. A., Balfour, N. J. \&
-Castellanos, M. C. Rapid evolution of a floral trait following
-acquisition of novel pollinators. \emph{Journal of Ecology}
-\textbf{109}, 2234--2246 (2021).
+\leavevmode\hypertarget{ref-mackin2021}{}%
+43.
+Mackin, C.
+R., Peña, J.
+F., Blanco, M.
+A., Balfour, N.
+J.
+\& Castellanos, M.
+C.
+Rapid evolution of a floral trait following acquisition of novel pollinators.
+\emph{J.
+Ecol.} \textbf{109}, 2234--2246 (2021).
 
-\hypertarget{ref-poisot2021}{}
-44. Poisot, T. \emph{et al.} Global knowledge gaps in species
-interaction networks data. \emph{Journal of Biogeography} \textbf{48},
-1552--1563 (2021).
+\leavevmode\hypertarget{ref-poisot2021}{}%
+44. Poisot, T. \emph{et al.} Global knowledge gaps in species interaction networks data. \emph{J. Biogeogr.} \textbf{48}, 1552--1563 (2021).
 
-\hypertarget{ref-fortuna2010}{}
-45. Fortuna, M. A. \emph{et al.} Nestedness versus modularity in
-ecological networks: Two sides of the same coin? \emph{Journal of Animal
-Ecology} \textbf{79}, 811--817 (2010).
+\leavevmode\hypertarget{ref-fortuna2010}{}%
+45. Fortuna, M. A. \emph{et al.} Nestedness versus modularity in ecological networks: Two sides of the same coin? \emph{J. Anim. Ecol.} \textbf{79}, 811--817 (2010).
 
-\hypertarget{ref-poisot2016}{}
-46. Poisot, T. \emph{et al.} Mangal making ecological network analysis
-simple. \emph{Ecography} \textbf{39}, 384--390 (2016).
+\leavevmode\hypertarget{ref-poisot2016}{}%
+46. Poisot, T. \emph{et al.} Mangal making ecological network analysis simple. \emph{Ecography} \textbf{39}, 384--390 (2016).
 
-\hypertarget{ref-chamberlain2020}{}
-47. Chamberlain, S. \emph{et al.} \emph{Taxize: Taxonomic information
-from around the web}. (2020).
+\leavevmode\hypertarget{ref-chamberlain2020}{}%
+47. Chamberlain, S. \emph{et al.} \emph{Taxize: Taxonomic information from around the web}. (2020).
 
-\hypertarget{ref-smith2018}{}
-48. Smith, S. A. \& Brown, J. W. Constructing a broadly inclusive seed
-plant phylogeny. \emph{American Journal of Botany} \textbf{105},
-302--314 (2018).
+\leavevmode\hypertarget{ref-smith2018}{}%
+48. Smith, S. A. \& Brown, J. W. Constructing a broadly inclusive seed plant phylogeny. \emph{Am. J. Bot.} \textbf{105}, 302--314 (2018).
 
-\hypertarget{ref-jin2019}{}
-49. Jin, Y. \& Qian, H. V.PhyloMaker: An R package that can generate
-very large phylogenies for vascular plants. \emph{Ecography}
-\textbf{42}, 1353--1359 (2019).
+\leavevmode\hypertarget{ref-jin2019}{}%
+49. Jin, Y. \& Qian, H. V.PhyloMaker: An R package that can generate very large phylogenies for vascular plants. \emph{Ecography} \textbf{42}, 1353--1359 (2019).
 
-\hypertarget{ref-stekhoven2012}{}
-50. Stekhoven, D. J. \& Bühlmann, P. MissForestNon-parametric missing
-value imputation for mixed-type data. \emph{Bioinformatics} \textbf{28},
-112--118 (2012).
+\leavevmode\hypertarget{ref-stekhoven2012}{}%
+50. Stekhoven, D. J. \& Bühlmann, P. MissForestNon-parametric missing value imputation for mixed-type data. \emph{Bioinformatics} \textbf{28}, 112--118 (2012).
 
-\hypertarget{ref-penone2014}{}
-51. Penone, C. \emph{et al.} Imputation of missing data in life-history
-trait datasets: Which approach performs the best? \emph{Methods in
-Ecology and Evolution} \textbf{5}, 961--970 (2014).
+\leavevmode\hypertarget{ref-penone2014}{}%
+51. Penone, C. \emph{et al.} Imputation of missing data in life-history trait datasets: Which approach performs the best? \emph{Methods Ecol. Evol.} \textbf{5}, 961--970 (2014).
 
-\hypertarget{ref-santos2018}{}
-52. Santos, T., Diniz-Filho, J. A., e Luis, T. R., Bini, M. \& Santos,
-M. T. Package `PVR'. (2018).
+\leavevmode\hypertarget{ref-santos2018}{}%
+52. Santos, T., Diniz-Filho, J. A., e Luis, T. R., Bini, M. \& Santos, M. T. Package `PVR'. (2018).
 
-\hypertarget{ref-diniz-filho2012}{}
-53. Diniz-Filho, J. A. F. \emph{et al.} On the selection of phylogenetic
-eigenvectors for ecological analyses. \emph{Ecography} \textbf{35},
-239--249 (2012).
+\leavevmode\hypertarget{ref-diniz-filho2012}{}%
+53. Diniz-Filho, J. A. F. \emph{et al.} On the selection of phylogenetic eigenvectors for ecological analyses. \emph{Ecography} \textbf{35}, 239--249 (2012).
 
-\hypertarget{ref-legendre2012}{}
-54. Legendre, P. \& Legendre, L. \emph{Numerical ecology}. (Elsevier,
-2012).
+\leavevmode\hypertarget{ref-legendre2012}{}%
+54. Legendre, P. \& Legendre, L. \emph{Numerical ecology}. (Elsevier, 2012).
 
-\hypertarget{ref-revell2012}{}
-55. Revell, L. J. Phytools: An R package for phylogenetic comparative
-biology (and other things). \emph{Methods in Ecology and Evolution}
-\textbf{3}, 217--223 (2012).
+\leavevmode\hypertarget{ref-revell2012}{}%
+55. Revell, L. J. Phytools: An R package for phylogenetic comparative biology (and other things). \emph{Methods Ecol. Evol.} \textbf{3}, 217--223 (2012).
 
-\hypertarget{ref-abdi2010}{}
-56. Abdi, H. \& Williams, L. J. Principal component analysis.
-\emph{WIREs Computational Statistics} \textbf{2}, 433--459 (2010).
+\leavevmode\hypertarget{ref-abdi2010}{}%
+56. Abdi, H. \& Williams, L. J. Principal component analysis. \emph{WIREs Computational Statistics} \textbf{2}, 433--459 (2010).
 
-\hypertarget{ref-ballantyne2015}{}
-57. Ballantyne, G., Baldock, K. C. R. \& Willmer, P. G. Constructing
-more informative plantPollinator networks: Visitation and pollen
-deposition networks in a heathland plant community. \emph{Proceedings of
-the Royal Society B: Biological Sciences} \textbf{282}, 20151130 (2015).
+\leavevmode\hypertarget{ref-ballantyne2015}{}%
+57.
+Ballantyne, G., Baldock, K.
+C.
+R.
+\& Willmer, P.
+G.
+Constructing more informative plantPollinator networks: Visitation and pollen deposition networks in a heathland plant community.
+\emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{282}, 20151130 (2015).
 
-\hypertarget{ref-vazquez2005}{}
-58. Vázquez, D. P., Morris, W. F. \& Jordano, P. Interaction frequency
-as a surrogate for the total effect of animal mutualists on plants.
-\emph{Ecol. Lett.} \textbf{8}, 1088--1094 (2005).
+\leavevmode\hypertarget{ref-vazquez2005}{}%
+58. Vázquez, D. P., Morris, W. F. \& Jordano, P. Interaction frequency as a surrogate for the total effect of animal mutualists on plants. \emph{Ecol. Lett.} \textbf{8}, 1088--1094 (2005).
 
-\hypertarget{ref-vazquez2012}{}
-59. Vázquez, D. P. \emph{et al.} The strength of plantPollinator
-interactions. \emph{Ecology} \textbf{93}, 719--725 (2012).
+\leavevmode\hypertarget{ref-vazquez2012}{}%
+59. Vázquez, D. P. \emph{et al.} The strength of plantPollinator interactions. \emph{Ecology} \textbf{93}, 719--725 (2012).
 
-\hypertarget{ref-hung2018}{}
-60. Hung, K.-L. J., Kingston, J. M., Albrecht, M., Holway, D. A. \&
-Kohn, J. R. The worldwide importance of honey bees as pollinators in
-natural habitats. \emph{Proceedings of the Royal Society B: Biological
-Sciences} \textbf{285}, 20172140 (2018).
+\leavevmode\hypertarget{ref-hung2018}{}%
+60.
+Hung, K.-L.
+J., Kingston, J.
+M., Albrecht, M., Holway, D.
+A.
+\& Kohn, J.
+R.
+The worldwide importance of honey bees as pollinators in natural habitats.
+\emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{285}, 20172140 (2018).
 
-\hypertarget{ref-burkner2017}{}
-61. Bürkner, P.-C. Brms: An R package for Bayesian multilevel models
-using Stan. \emph{Journal of statistical software} \textbf{80}, 1--28
-(2017).
+\leavevmode\hypertarget{ref-burkner2017}{}%
+61. Bürkner, P.-C. Brms: An R package for Bayesian multilevel models using Stan. \emph{Journal of statistical software} \textbf{80}, 1--28 (2017).
 
-\hypertarget{ref-gabry2019}{}
-62. Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A.
-Visualization in Bayesian workflow. \emph{Journal of the Royal
-Statistical Society: Series A (Statistics in Society)} \textbf{182},
-389--402 (2019).
+\leavevmode\hypertarget{ref-gabry2019}{}%
+62.
+Gabry, J., Simpson, D., Vehtari, A., Betancourt, M.
+\& Gelman, A.
+Visualization in Bayesian workflow.
+\emph{Journal of the Royal Statistical Society: Series A (Statistics in Society)} \textbf{182}, 389--402 (2019).
 
-\hypertarget{ref-dormann2008}{}
-63. Dormann, C. F., Gruber, B. \& Fründ, J. Introducing the bipartite
-package: Analysing ecological networks. \emph{interaction} \textbf{1},
-(2008).
+\leavevmode\hypertarget{ref-dormann2008}{}%
+63. Dormann, C. F., Gruber, B. \& Fründ, J. Introducing the bipartite package: Analysing ecological networks. \emph{interaction} \textbf{1}, (2008).
 
-\hypertarget{ref-bluthgen2006}{}
-64. Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in
-species interaction networks. \emph{BMC Ecology} \textbf{6}, 9 (2006).
+\leavevmode\hypertarget{ref-bluthgen2006}{}%
+64. Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in species interaction networks. \emph{BMC Ecology} \textbf{6}, 9 (2006).
 
-\hypertarget{ref-therneau2015}{}
-65. Therneau, T., Atkinson, B., Ripley, B. \& Ripley, M. B. Package
-`rpart'. \emph{Available online: cran. ma. ic. ac.
-uk/web/packages/rpart/rpart. pdf (accessed on 20 April 2016)} (2015).
+\leavevmode\hypertarget{ref-therneau2015}{}%
+65. Therneau, T., Atkinson, B., Ripley, B. \& Ripley, M. B. Package `rpart'. \emph{Available online: cran. ma. ic. ac. uk/web/packages/rpart/rpart. pdf (accessed on 20 April 2016)} (2015).
 
-\hypertarget{ref-milborrow2015}{}
-66. Milborrow, S. Rpart. plot: Plot rpart Models. An Enhanced Version of
-plot. rpart. \emph{R package version} \textbf{1}, (2015).
-
-\eleft
+\leavevmode\hypertarget{ref-milborrow2015}{}%
+66. Milborrow, S. Rpart. Plot: Plot rpart Models. An Enhanced Version of plot. Rpart. \emph{R package version} \textbf{1}, (2015).
 

### 2021-08-14 Main_Figures/Traits_Table.Rmd
journal abbreviations of refs

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=14}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=5, fig.width=8}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-dat <- data.frame(Type, Trait,Number_of_records_quantitative,Type_1, Trait1, T.cat,Number_of_records_categorical)
+dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
 
-colnames(dat) <- c("Type","Traits", "Records","Type", "Traits", "Categories", "Records")
+colnames(dat) <- c("Type","Traits","Type", "Traits", "Categories")
 
 kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c")) %>%
-kable_styling(full_width = T) %>%
-add_header_above(c("Quantitative traits" = 3,"Categorical traits" = 4),bold=T)  %>%
-    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)
+kable_styling(full_width = F)
 

### 2021-08-14 Draft/Manuscript.tex
edits

@@
 \leavevmode\hypertarget{ref-tur2013}{}%
-14. Tur, C., Castro-Urgal, R. \& Traveset, A. Linking Plant Specialization to Dependence in Interactions for Seed Set in Pollination Networks. \emph{PLoS ONE} \textbf{8}, e78294 (2013).
+14. Tur, C., Castro-Urgal, R. \& Traveset, A. Linking Plant Specialization to Dependence in Interactions for Seed Set in Pollination Networks. \emph{PLoS One} \textbf{8}, e78294 (2013).
 
@@
 \leavevmode\hypertarget{ref-barrett2003}{}%
-23. Barrett, S. C. H. Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond. \emph{Philos. Trans. R. Soc. Lond., B, Biol. Sci.} \textbf{358}, 991--1004 (2003).
+23. Barrett, S. C. H. Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond. \emph{Philos. Trans. R. Soc. Lond. B Biol. Sci.} \textbf{358}, 991--1004 (2003).
 
@@
 Understanding Linkage Rules in Plant-Pollinator Networks by Using Hierarchical Models That Incorporate Pollinator Detectability and Plant Traits.
-\emph{PLOS ONE} \textbf{8}, e69200 (2013).
+\emph{PLoS One} \textbf{8}, e69200 (2013).
 
@@
 \leavevmode\hypertarget{ref-kettle2011}{}%
-33. Kettle, C. J. \emph{et al.} Ecological Implications of a Flower Size/Number Trade-Off in Tropical Forest Trees. \emph{PLOS ONE} \textbf{6}, e16111 (2011).
+33. Kettle, C. J. \emph{et al.} Ecological Implications of a Flower Size/Number Trade-Off in Tropical Forest Trees. \emph{PLoS One} \textbf{6}, e16111 (2011).
 
@@
 \leavevmode\hypertarget{ref-chamberlain2020}{}%
-47. Chamberlain, S. \emph{et al.} \emph{Taxize: Taxonomic information from around the web}. (2020).
+47. Chamberlain, S. \emph{et al.} \emph{Taxize: Taxonomic information from around the web. R package version 0.9.99}. (2020).
 
@@
 \leavevmode\hypertarget{ref-abdi2010}{}%
-56. Abdi, H. \& Williams, L. J. Principal component analysis. \emph{WIREs Computational Statistics} \textbf{2}, 433--459 (2010).
+56. Abdi, H. \& Williams, L. J. Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459 (2010).
 
@@
 Constructing more informative plantPollinator networks: Visitation and pollen deposition networks in a heathland plant community.
-\emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{282}, 20151130 (2015).
+\emph{Proc.
+Royal Soc.
+B} \textbf{282}, 20151130 (2015).
 
@@
 The worldwide importance of honey bees as pollinators in natural habitats.
-\emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{285}, 20172140 (2018).
+\emph{Proc.
+Royal Soc.
+B} \textbf{285}, 20172140 (2018).
 
 \leavevmode\hypertarget{ref-burkner2017}{}%
-61. Bürkner, P.-C. Brms: An R package for Bayesian multilevel models using Stan. \emph{Journal of statistical software} \textbf{80}, 1--28 (2017).
+61. Bürkner, P.-C. Brms: An R package for Bayesian multilevel models using Stan. \emph{J. Stat. Softw.} \textbf{80}, 1--28 (2017).
 
 \leavevmode\hypertarget{ref-gabry2019}{}%
-62.
-Gabry, J., Simpson, D., Vehtari, A., Betancourt, M.
-\& Gelman, A.
-Visualization in Bayesian workflow.
-\emph{Journal of the Royal Statistical Society: Series A (Statistics in Society)} \textbf{182}, 389--402 (2019).
+62. Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A. Visualization in Bayesian workflow. \emph{J. R. Stat. Soc. Ser. A Stat. Soc.} \textbf{182}, 389--402 (2019).
 
@@
 \leavevmode\hypertarget{ref-bluthgen2006}{}%
-64. Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in species interaction networks. \emph{BMC Ecology} \textbf{6}, 9 (2006).
+64. Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in species interaction networks. \emph{BMC Ecol.} \textbf{6}, 9 (2006).
 

### 2021-08-15 Draft/Manuscript.tex
edits

@@
 \leavevmode\hypertarget{ref-chamberlain2020}{}%
-47. Chamberlain, S. \emph{et al.} \emph{Taxize: Taxonomic information from around the web. R package version 0.9.99}. (2020).
+47.
+Chamberlain, S.
+\emph{et al.} Taxize: Taxonomic information from around the web.
+R package version 0.9.99 (2020).~at \href{https://CRAN.R-project.org/package=taxize}{https://cran.r-project.org/package=taxize}.
 
@@
 \leavevmode\hypertarget{ref-santos2018}{}%
-52. Santos, T., Diniz-Filho, J. A., e Luis, T. R., Bini, M. \& Santos, M. T. Package `PVR'. (2018).
+52. Chamberlain, S. \emph{et al.} Package `PVR'. R package version 0.3 (2018).~at \href{https://CRAN.R-project.org/package=PVR}{https://cran.r-project.org/package=PVR}.
 
@@
 \leavevmode\hypertarget{ref-legendre2012}{}%
-54. Legendre, P. \& Legendre, L. \emph{Numerical ecology}. (Elsevier, 2012).
+54. Legendre, P. \& Legendre, L. \emph{Numerical ecology}. (Elsevier, Amsterdam, 2012).
 
@@
 \leavevmode\hypertarget{ref-therneau2015}{}%
-65. Therneau, T., Atkinson, B., Ripley, B. \& Ripley, M. B. Package `rpart'. \emph{Available online: cran. ma. ic. ac. uk/web/packages/rpart/rpart. pdf (accessed on 20 April 2016)} (2015).
+65.
+Therneau, T., Atkinson, B., Ripley, B.
+\& Ripley, M.
+B.
+Package `rpart'.
+R package version 4.1-15 (2015).~at \href{https://CRAN.R-project.org/package=rpart}{https://cran.r-project.org/package=rpart}.
 
 \leavevmode\hypertarget{ref-milborrow2015}{}%
-66. Milborrow, S. Rpart. Plot: Plot rpart Models. An Enhanced Version of plot. Rpart. \emph{R package version} \textbf{1}, (2015).
+66.
+Milborrow, S.
+Rpart.
+Plot: Plot rpart Models.
+An Enhanced Version of plot.
+Rpart.
+R package version 3.0.9 (2015).~at \href{https://CRAN.R-project.org/package=rpart.plot}{https://cran.r-project.org/package=rpart.plot}.
 

### 2021-08-16 Manuscript/Manuscript.Rmd
edits

--- 2021-08-14 Draft/Manuscript.Rmd
@@
 **Functional traits.** We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
-These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive and 3 vegetative).
+These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive and 3 vegetative, Supplementary Information).
 For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).

### 2021-08-16 Manuscript/Manuscript.tex
edits

--- 2021-08-14 Draft/Manuscript.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
-%
-\documentclass[
-  12pt,
-  a4paper,
-]{article}
+\documentclass[12pt,a4paper,]{article}
 \usepackage[]{mathpazo}
 \usepackage{setspace}
+\setstretch{2}
 \usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
   \fi
-% Use upquote if available, for straight quotes in verbatim environments
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
+% use microtype if available
+\IfFileExists{microtype.sty}{%
 \usepackage[]{microtype}
@@
 }{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
+\usepackage[unicode=true]{hyperref}
+\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
 \hypersetup{
@@
             linkcolor=RoyalBlue,
-  filecolor=Maroon,
             citecolor=Blue,
             urlcolor=RoyalBlue,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
 \usepackage[margin=1in]{geometry}
 \usepackage{longtable,booktabs}
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
+% Fix footnotes in tables (requires footnote package)
+\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+
+% set default figure placement to htbp
 \makeatletter
@@
 \makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-\pagestyle{plain}
+
 \usepackage{lineno} % add 
@@
 
-\title{\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant floral and reproductive traits determine interactions with floral visitors}
+\title{\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant floral and
+reproductive traits determine interactions with floral visitors}
 \author{}
@@
 
-\setstretch{2}
-\vspace{-2.2cm}
-\singlespacing
+\vspace{-2.2cm} \singlespacing
 \large 
-
 \textbf{Jose B. Lanuza$^{1,2}*$, Romina Rader$^{1}$, Jamie Stavert$^{3}$, Liam K. Kendall$^{4}$, Manu E. Saunders$^{1}$ and Ignasi Bartomeus$^{2}$}
@@
 
-\textbf{Plant life strategies are often delimited by vegetative and physiological traits but little is known about how floral and reproductive traits drive these strategies, and in turn shape plant interactions with floral visitors.
-Here, we compiled 13 floral, 4 reproductive and 3 vegetative traits for 1,506 plant species from 28 plant-pollinator network studies across 18 different countries.
-We investigated the associations among these traits, pollinator visitation and the functional role of plant species within the networks (interaction frequency, normalized degree and specialization).
-We found that 51.8\% of trait variation was explained by two independent axes that encompassed plant form and function.
-Specifically, the first axis indicated the presence of a trade-off between flower number and flower size (PC1, 26.72\%).
-The second axis indicated a trade-off for the level of pollinator dependency (PC2, 25.08\%).
-Although the main axes of trait variation did not fully explain pollinator visitation rates, different plant life strategies were associated with visitation rates and pollinator functional groups.
-Overall, the main traits that determined plant species' functional roles were height, nectar concentration, pollen grains per flower, number of ovules, style length, selfing level and flower width.
-Our results highlight the need to consider plant reproductive and floral traits to improve understanding of plant life strategies and plant-pollinator interactions at broader spatial scales.}
+\textbf{Plant life strategies are often delimited by vegetative and
+physiological traits but little is known about how floral and
+reproductive traits drive these strategies, and in turn shape plant
+interactions with floral visitors. Here, we compiled 13 floral, 4
+reproductive and 3 vegetative traits for 1,506 plant species from 28
+plant-pollinator network studies across 18 different countries. We
+investigated the associations among these traits, pollinator visitation
+and the functional role of plant species within the networks
+(interaction frequency, normalized degree and specialization). We found
+that 51.8\% of trait variation was explained by two independent axes
+that encompassed plant form and function. Specifically, the first axis
+indicated the presence of a trade-off between flower number and flower
+size (PC1, 26.72\%). The second axis indicated a trade-off for the level
+of pollinator dependency (PC2, 25.08\%). Although the main axes of trait
+variation did not fully explain pollinator visitation rates, different
+plant life strategies were associated with visitation rates and
+pollinator functional groups. Overall, the main traits that determined
+plant species' functional roles were height, nectar concentration,
+pollen grains per flower, number of ovules, style length, selfing level
+and flower width. Our results highlight the need to consider plant
+reproductive and floral traits to improve understanding of plant life
+strategies and plant-pollinator interactions at broader spatial scales.}
 
@@
 
-\noindent
+\noindent\rule{\textwidth}{1pt}
 
-\rule{\textwidth}{1pt}
-
-\textsuperscript{1} School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-\textsuperscript{2} Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-\textsuperscript{3} Department of Conservation \textbar{} Te Papa Atawhai, Auckland, New Zealand.
-\textsuperscript{4} Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden.
-\texttt{*} e-mail: \href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
+\textsuperscript{1} School of Environmental and Rural Science,
+University of New England, Armidale, New South Wales 2350, Australia.
+\textsuperscript{2} Estación Biológica de Doñana (EBD-CSIC), E-41092
+Seville, Spain. \textsuperscript{3} Department of Conservation
+\textbar{} Te Papa Atawhai, Auckland, New Zealand. \textsuperscript{4}
+Centre for Environmental and Climate Science, Lund University,
+Sölvegatan 37, S-223 62 Lund, Sweden. \texttt{*} e-mail:
+\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
 
 \doublespacing
-\vspace{5mm}
-\normalsize
+\vspace{5mm} \normalsize
 
-There is an astonishing diversity of floral structures and plant reproductive strategies among flowering plants,\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}} which have long been of interest to pollination biologists in terms of their relevance to plant-pollinator interactions.
-However, most studies that have explored reproductive (e.g., mating and compatibility systems) and floral trait (e.g., flower size or nectar provision) variation have concentrated on the individual or community level and thus, broader macroecological patterns remain poorly investigated.\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3}--\protect\hyperlink{ref-grossenbacher2017}{7}} Indeed, studies depicting species' life history strategies generally focus on vegetative traits and rarely consider reproductive traits.\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}} As a consequence, a unified framework that explores the compromises among floral traits and their relevance to plant life strategies is currently lacking.\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}} At the same time, there is growing interest in the determinants of plant-pollinator interactions via trait-based approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{11}} and trait-matching analyses.\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{12}} However, floral traits have been overlooked beyond highly specialised plant-pollinator systems\textsuperscript{\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-dellinger2020}{13}} and the role of plant reproductive biology remains little explored in plant-pollinator interactions (but see references\textsuperscript{\protect\hyperlink{ref-tur2013}{14},\protect\hyperlink{ref-devaux2014}{15}}).
+There is an astonishing diversity of floral structures and plant
+reproductive strategies among flowering
+plants\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}},
+which have long been of interest to pollination biologists in terms of
+their relevance to plant-pollinator interactions. However, most studies
+that have explored reproductive (e.g., mating and compatibility systems)
+and floral trait (e.g., flower size or nectar provision) variation have
+concentrated on the individual or community level and thus, broader
+macroecological patterns remain poorly
+investigated\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3}--\protect\hyperlink{ref-grossenbacher2017}{7}}.
+Indeed, studies depicting species' life history strategies generally
+focus on vegetative traits and rarely consider reproductive
+traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}}. As a
+consequence, a unified framework that explores the compromises among
+floral traits and their relevance to plant life strategies is currently
+lacking\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}}. At the
+same time, there is growing interest in the determinants of
+plant-pollinator interactions via trait-based
+approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{11}} and
+trait-matching
+analyses\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{12}}.
+However, floral traits have been overlooked beyond highly specialised
+plant-pollinator
+systems\textsuperscript{\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-dellinger2020}{13}}
+and the role of plant reproductive biology remains little explored in
+plant-pollinator interactions (but see
+references\textsuperscript{\protect\hyperlink{ref-tur2013}{14},\protect\hyperlink{ref-devaux2014}{15}}).
 
-With the recent availability of large trait databases, plant ecological strategies are increasingly being examined,\textsuperscript{\protect\hyperlink{ref-kattge2011}{16},\protect\hyperlink{ref-salguero2015}{17}} and are facilitating the identification of global patterns and constraints of plant form and function.\textsuperscript{\protect\hyperlink{ref-salguero2016}{8},\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}} However, the main focus has been on vegetative traits such as leaf\textsuperscript{\protect\hyperlink{ref-wright2004}{20}} or wood\textsuperscript{\protect\hyperlink{ref-chave2009}{21}} trade-offs with little or no attention given to reproductive and floral traits,\textsuperscript{\protect\hyperlink{ref-evojtko2020}{22}} also critical to plant form and function.
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively.\textsuperscript{\protect\hyperlink{ref-moeller2017}{6},\protect\hyperlink{ref-barrett2003}{23}} Further, outcrossing levels are positively correlated with flower size.\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{24}} In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species' reliance upon animal pollination (pollinator dependence) and their role in attracting pollinators.\textsuperscript{\protect\hyperlink{ref-ollerton2011}{25}} Hence, exploring plant life strategies with reproductive and floral trade-offs, in conjunction with their pollinator dependence, is necessary for a balanced understanding of plant economics.
+With the recent availability of large trait databases, plant ecological
+strategies are increasingly being
+examined\textsuperscript{\protect\hyperlink{ref-kattge2011}{16},\protect\hyperlink{ref-salguero2015}{17}},
+and are facilitating the identification of global patterns and
+constraints of plant form and
+function\textsuperscript{\protect\hyperlink{ref-salguero2016}{8},\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}}.
+However, the main focus has been on vegetative traits such as
+leaf\textsuperscript{\protect\hyperlink{ref-wright2004}{20}} or
+wood\textsuperscript{\protect\hyperlink{ref-chave2009}{21}} trade-offs
+with little or no attention given to reproductive and floral
+traits\textsuperscript{\protect\hyperlink{ref-evojtko2020}{22}}, also
+critical to plant form and function. For instance, short lived versus
+perennial species tend to have low versus high levels of outcrossing,
+respectively\textsuperscript{\protect\hyperlink{ref-moeller2017}{6},\protect\hyperlink{ref-barrett2003}{23}}.
+Further, outcrossing levels are positively correlated with flower
+size\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{24}}. In
+addition, the presence of costly rewards (e.g., pollen or nectar) and
+showy flowers or floral displays can only be understood through
+consideration of plant species' reliance upon animal pollination
+(pollinator dependence) and their role in attracting
+pollinators\textsuperscript{\protect\hyperlink{ref-ollerton2011}{25}}.
+Hence, exploring plant life strategies with reproductive and floral
+trade-offs, in conjunction with their pollinator dependence, is
+necessary for a balanced understanding of plant economics.
 
-Several studies have identified links between plant traits and plant-pollinator network properties.\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3},\protect\hyperlink{ref-lazaro2008}{26},\protect\hyperlink{ref-bartomeus2013}{27}} Moreover, plant traits can also define species' network roles (e.g., specialists vs generalists).
-For example, species that occupy trait space extremes are more likely to exhibit higher specialization and be more reliant on trait-matching.\textsuperscript{\protect\hyperlink{ref-junker2013}{28},\protect\hyperlink{ref-coux2016}{29}} This morphological matching between plant and floral visitors can determine plant-pollinator interactions, and thus shape their interaction network structure.\textsuperscript{\protect\hyperlink{ref-stang2009}{30},\protect\hyperlink{ref-ibanez2012}{31}} Despite the increasing knowledge of the relevance of traits on the species network roles, little is known about how plant reproductive and floral traits determine plant species' network roles at a macroecological scale.
+Several studies have identified links between plant traits and
+plant-pollinator network
+properties\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3},\protect\hyperlink{ref-lazaro2008}{26},\protect\hyperlink{ref-bartomeus2013}{27}}.
+Moreover, plant traits can also define species' network roles (e.g.,
+specialists vs generalists). For example, species that occupy trait
+space extremes are more likely to exhibit higher specialization and be
+more reliant on
+trait-matching\textsuperscript{\protect\hyperlink{ref-junker2013}{28},\protect\hyperlink{ref-coux2016}{29}}.
+This morphological matching between plant and floral visitors can
+determine plant-pollinator interactions, and thus shape their
+interaction network
+structure\textsuperscript{\protect\hyperlink{ref-stang2009}{30},\protect\hyperlink{ref-ibanez2012}{31}}.
+Despite the increasing knowledge of the relevance of traits on the
+species network roles, little is known about how plant reproductive and
+floral traits determine plant species' network roles at a
+macroecological scale.
 
-Here, we explore the potential trade-offs among plant floral and reproductive traits and how these influence the structure of plant-pollinator networks.
-First, we identify the major axes of floral and reproductive trait variation and trade-offs that determine plant form and function.
-Second, we investigate how plant species' position in trait-space influences interaction strength with different guilds of floral visitors.
-Finally, we investigate how the main axes of trait variation and individual traits influence plant species roles within networks using complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
+Here, we explore the potential trade-offs among plant floral and
+reproductive traits and how these influence the structure of
+plant-pollinator networks. First, we identify the major axes of floral
+and reproductive trait variation and trade-offs that determine plant
+form and function. Second, we investigate how plant species' position in
+trait-space influences interaction strength with different guilds of
+floral visitors. Finally, we investigate how the main axes of trait
+variation and individual traits influence plant species roles within
+networks using complementary interaction network metrics (i.e.,
+interaction strength, normalized degree and specialization).
 
-\hypertarget{results}{%
-\section{RESULTS}\label{results}}
+\section{RESULTS}\label{results}
 
-\textbf{Plant strategies.} The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8\% and 70.97\% of trait variation, respectively (Fig.
-1 and Supplementary Fig.
-S5) and had a phylogenetic correlation (\(\lambda\)) of 0.76.
-The first principal component (PC1) represented 26.72\% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the `flower number - flower size trade-off' as already described in previous studies.\textsuperscript{\protect\hyperlink{ref-sargent2007}{32},\protect\hyperlink{ref-kettle2011}{33}} Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Supplementary Table S3) but style length also contributed moderately on PC1 (loading = -0.33).
-The second principal component (PC2) represented 25.05\% of the trait variation and indicated a trade-off between low and high pollinator dependence.
-We refer to this axis as the `pollinator dependence trade-off'.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Supplementary Table S3).
-We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
-In contrast, species with high levels of autonomous selfing tended to have fewer and smaller flowers, had shorter styles and were shorter in height.
-Further, PC3 explained a considerable amount of trait variability (19.17\%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
-The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Supplementary Table S3).
-Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the `style length trade-off'.
-Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 23.40\%); and pollen quantity (pollen grains per flower) was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 21.67\%; Supplementary Fig.
-S6).
-This pPCA explained similar variance with the first two principal components (45.07\%) and similar associations of traits despite some variability in the loadings (Supplementary Table S4).
+\textbf{Plant strategies.} The phylogenetically informed principal
+component analysis (pPCA) captured by the first two and three axes
+51.8\% and 70.97\% of trait variation, respectively (Fig. 1 and
+Supplementary Fig. S5) and had a phylogenetic correlation (\(\lambda\))
+of 0.76. The first principal component (PC1) represented 26.72\% of the
+trait variation and indicated a trade-off between flower number and
+flower size. We refer to this axis as the `flower number - flower size
+trade-off' as already described in previous
+studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{32},\protect\hyperlink{ref-kettle2011}{33}}.
+Hence, one end of the spectrum comprised species with high investment in
+flower number and plant height but small flower size, short style length
+and low ovule number. The other end of this spectrum comprised species
+that were short in height and invested in large flowers, long styles,
+many ovules, but few flowers. The main contributing traits to PC1 were
+plant height, flower number, ovule number and flower size (loadings
+\textgreater{} \textbar{}0.5\textbar{}; Supplementary Table S3) but
+style length also contributed moderately on PC1 (loading = -0.33). The
+second principal component (PC2) represented 25.05\% of the trait
+variation and indicated a trade-off between low and high pollinator
+dependence. We refer to this axis as the `pollinator dependence
+trade-off'. The main driver of trait variation on PC2 was autonomous
+selfing (loading = 0.85) but the other traits (except ovule number) also
+made moderate contributions (loadings from 0.27 to 0.4; Supplementary
+Table S3). We found that high pollinator dependence was associated with
+larger and a higher number of flowers, greater plant height and longer
+styles. In contrast, species with high levels of autonomous selfing
+tended to have fewer and smaller flowers, had shorter styles and were
+shorter in height. Further, PC3 explained a considerable amount of trait
+variability (19.17\%) and the main contributors to this axis were style
+length (loading = -0.66) and the degree of autonomous selfing (loading =
+-0.51). The remaining traits, apart from ovule number, were moderately
+correlated to changes on PC3 (loadings from -0.23 to -0.46;
+Supplementary Table S3). Thus, because style length was correlated with
+all traits on PC3 and was the main driver of trait variation, we refer
+to this axis as the `style length trade-off'. Further, the pPCA with the
+subset of species that had nectar and pollen quantity data showed that
+nectar quantity (microlitres of nectar per flower) was positively
+associated with flower size, style length and ovule number (PC1,
+23.40\%); and pollen quantity (pollen grains per flower) was positively
+correlated with flower number and plant height and negatively associated
+with autonomous selfing (PC2, 21.67\%; Supplementary Fig. S6). This pPCA
+explained similar variance with the first two principal components
+(45.07\%) and similar associations of traits despite some variability in
+the loadings (Supplementary Table S4).
 
@@
 \includegraphics{output/figures/unnamed-chunk-1-1.pdf}
-\caption{\label{fig:unnamed-chunk-1}\textbf{Fig.
-1 \textbar{} Plant life-history strategies.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator networks studies.
-The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
-The length of the arrows indicate the weight of the variables on each principal component and the labelled icons at their end represent the extreme form of the trait continuum.
-The dashed lines show the opposed direction of trait variation and the non-labelled icons at their end illustrate the opposing extreme of the continuum.}
+\caption{\label{fig:unnamed-chunk-1}\textbf{Fig. 1 \textbar{} Plant
+life-history strategies.} Phylogenetically informed principal component
+analysis (pPCA) of 1,236 plant species from 28 plant-pollinator networks
+studies. The solid arrows indicate the direction of the different
+quantitative traits (flower number, plant height, style length, flower
+size, ovule number and level of autonomous selfing) across the two main
+axes of trait variation. The length of the arrows indicate the weight of
+the variables on each principal component and the labelled icons at
+their end represent the extreme form of the trait continuum. The dashed
+lines show the opposed direction of trait variation and the non-labelled
+icons at their end illustrate the opposing extreme of the continuum.}
 \end{figure}
 
-We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
-2 and Supplementary Table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
-In addition, we found with Tukey test statistical differences between the different levels of categorical traits in the trait space (Supplementary Fig.
-S7).
-Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatibile were statistically differentiated from species with partial or full self compatibility; Supplementary Fig.
-S7a and Fig.
-S7b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Supplementary Fig.
-S7c and Fig.
-S7d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Supplementary Fig.
-S7e and Fig.
-S7f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Supplementary Fig.
-S7g and Fig.
-S7h).
-Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Supplementary Fig.
-S7i and Fig.
-S7j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Supplementary Fig.
-S7k and Fig.
-S7l).
+We found that most categorical traits were statistically associated with
+the first two axes of trait variation (Fig. 2 and Supplementary Table
+S2). Flower symmetry, which was only associated with PC2 (Sum of squares
+= 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar
+provision, which was independent of PC1 and PC2 (PC1: Sum of squares =
+0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83,
+F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
+In addition, we found with Tukey test statistical differences between
+the different levels of categorical traits in the trait space
+(Supplementary Fig. S7). Regarding self compatibility, we found larger
+differences on PC2 (i.e., species with unisexual flowers that were self
+incompatibile were statistically differentiated from species with
+partial or full self compatibility; Supplementary Fig. S7a and Fig.
+S7b). Life forms differed statistically across both axes of trait
+variation and followed a gradient of larger life forms (trees and
+shrubs) with higher pollinator dependence to smaller ones (herbs) with
+lower pollinator dependence (Supplementary Fig. S7c and Fig. S7d).
+Consequently, lifespan also followed this gradient but perennial and
+short lived species only differed statistically on PC2 (Supplementary
+Fig. S7e and Fig. S7f). Species with unisexual flowers (monoecious and
+dioecious) were clustered on both extremes of the first two principal
+components and had the highest pollinator dependence and highest number
+of flowers (Supplementary Fig. S7g and Fig. S7h). Moreover, we found
+that the campanulate and capitulum flower shapes were differentiated
+from tube, papilionaceous, open and brush shapes in the trait space. The
+former morphologies had larger flowers and greater pollinator
+dependence, while the latter had higher flower number and greater
+autonomous selfing (Supplementary Fig. S7i and Fig. S7j). Regarding
+flower symmetry, zygomorphic flowers were associated with lower levels
+of pollinator dependence, whereas actinomorphic flowers had higher
+levels of pollinator dependence (Supplementary Fig. S7k and Fig. S7l).
 
@@
 \includegraphics{output/figures/unnamed-chunk-2-1.pdf}
-\caption{\label{fig:unnamed-chunk-2}\textbf{Fig.
-2 \textbar{} Location of the different qualitative traits on the trait space.} The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).}
+\caption{\label{fig:unnamed-chunk-2}\textbf{Fig. 2 \textbar{} Location of
+the different qualitative traits on the trait space.} The panel is
+composed by the traits that showed statistical association with the
+first two axes of trait variation: compatibility system (a), life form
+(b), lifespan (c), breeding system (d), flower shape (e) and flower
+symmetry (f).}
 \end{figure}
@@
 
-\textbf{Phylogenetic signal of traits.} We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) in all quantitative traits (Supplementary Table S5).
-The traits that showed the highest phylogenetic signal were ovule number (\(\lambda = 1\)), pollen grains per flower (\(\lambda = 1\)) and plant height (\(\lambda = 0.96\)), followed by flower length (\(\lambda = 0.75\)), flower width (\(\lambda = 0.73\)), number of flowers per plant (\(\lambda = 0.69\)) and nectar concentration (\(\lambda = 0.65\)).
-The traits that showed a moderate phylogenetic signal were inflorescence width (\(\lambda = 0.57\)), style length (\(\lambda = 0.49\)) and autonomous selfing (\(\lambda = 0.34\)).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits (\(\lambda = 0.14\)).
+\textbf{Phylogenetic signal of traits.} We found a strong phylogenetic
+signal (\emph{P} \textless{} 0.01) in all quantitative traits
+(Supplementary Table S5). The traits that showed the highest
+phylogenetic signal were ovule number (\(\lambda = 1\)), pollen grains
+per flower (\(\lambda = 1\)) and plant height (\(\lambda = 0.96\)),
+followed by flower length (\(\lambda = 0.75\)), flower width
+(\(\lambda = 0.73\)), number of flowers per plant (\(\lambda = 0.69\))
+and nectar concentration (\(\lambda = 0.65\)). The traits that showed a
+moderate phylogenetic signal were inflorescence width
+(\(\lambda = 0.57\)), style length (\(\lambda = 0.49\)) and autonomous
+selfing (\(\lambda = 0.34\)). Finally, microliters of nectar per flower
+showed the lowest phylogenetic signal of all traits
+(\(\lambda = 0.14\)).
 
-\textbf{Visitation patterns.} The main axes of trait variation explained little of the overall visitation rates (\(conditional R2 = 0.31\); \(marginal R2 = 0.06\)) but showed relevant trends when we explored the interaction with the different floral visitors guilds (Fig.
-3).
-All floral visitors guilds visited plant species with higher pollinator dependence more frequently (PC2; Fig.
-3b and Fig.
-3e).
-In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig.
-3a and Fig.
-3d).
-On the style length trade-off (PC3), Anthophila-Hymenoptera, Lepidoptera and Non-Anthophila-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
-3c and Fig.
-3f).
-Furthermore, when running an additional model that separates the most represented families of Anthophila-Hymenoptera (bees; \(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) showed that the family Apidae was the main driver of the observed patterns (Supplementary Fig.
-S8).
+\textbf{Visitation patterns.} The main axes of trait variation explained
+little of the overall visitation rates (\(conditional R2 = 0.31\);
+\(marginal R2 = 0.06\)) but showed relevant trends when we explored the
+interaction with the different floral visitors guilds (Fig. 3). All
+floral visitors guilds visited plant species with higher pollinator
+dependence more frequently (PC2; Fig. 3b and Fig. 3e). In addition, all
+guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera,
+non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on
+species with small numerous flowers (PC1; Fig. 3a and Fig. 3d). On the
+style length trade-off (PC3), Anthophila-Hymenoptera, Lepidoptera and
+Non-Anthophila-Hymenoptera showed greater visitation rates on plant
+species with larger styles and higher levels of selfing; while
+Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation
+rates on species with shorter styles and lower selfing (Fig. 3c and Fig.
+3f). Furthermore, when running an additional model that separates the
+most represented families of Anthophila-Hymenoptera (bees;
+\(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) showed that the
+family Apidae was the main driver of the observed patterns
+(Supplementary Fig. S8).
 
@@
 \includegraphics{output/figures/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}\textbf{Fig.
-3 \textbar{} Visitation rates across the three main axes of trait variation.} Fitted posterior estimates of the number of visits made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
-Bees (a, b and c) and the rest of guilds (d, e and f) were plotted separately for visualization purposes.
-In addition, we trimmed the plotting area that was over the 95th percentile to improve visualisation.
-PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.}
+\caption{\label{fig:unnamed-chunk-3}\textbf{Fig. 3 \textbar{} Visitation
+rates across the three main axes of trait variation.} Fitted posterior
+estimates of the number of visits made by the different floral visitors
+guilds in relation to PC1, PC2 and PC3. Bees (a, b and c) and the rest
+of guilds (d, e and f) were plotted separately for visualization
+purposes. In addition, we trimmed the plotting area that was over the
+95th percentile to improve visualisation. PC1 represents the flower
+number - flower size trade-off, PC2 represents the pollinator dependence
+trade-off and PC3, the style length trade-off.}
 \end{figure}
@@
 
-\textbf{Plant species functional roles.} The variance of the different plant species level metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
-S9; interaction frequency \textasciitilde{} PCs, \(conditional R2 = 0.11\), \(marginal R2 = 0.02\); normalized degree \textasciitilde{} PCs, \(conditional R2 = 0.24\), \(marginal R2 = 0.02\); and, specialization \textasciitilde{} PCs, \(conditional R2 = 0.37\), \(marginal R2 = 0.03\)).
-Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
-On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers.
-On PC1, specialization showed the opposite trend.
-On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing.
-Again, specialization showed the opposite trend to interaction frequency.
+\textbf{Plant species functional roles.} The variance of the different
+plant species level metrics was poorly explained by the three main axes
+of trait variation (Supplementary Fig. S9; interaction frequency
+\textasciitilde{} PCs, \(conditional R2 = 0.11\),
+\(marginal R2 = 0.02\); normalized degree \textasciitilde{} PCs,
+\(conditional R2 = 0.24\), \(marginal R2 = 0.02\); and, specialization
+\textasciitilde{} PCs, \(conditional R2 = 0.37\),
+\(marginal R2 = 0.03\)). Overall, the most notable trends were found on
+PC1 and PC3 for interaction frequency and specialization. On the flower
+number - flower size trade-off (PC1), interaction frequency was higher
+for plant species with more flowers but was lower for plant species with
+larger flowers. On PC1, specialization showed the opposite trend. On the
+style length trade-off (PC3), interaction frequency was lower for plants
+with shorter styles and lower autonomous selfing and higher for species
+with longer styles and higher autonomous selfing. Again, specialization
+showed the opposite trend to interaction frequency.
 
-When we further investigate which combination of traits drive plant network roles, we show that the regression tree for visitation frequency was best explained by plant height, nectar concentration and style length (Fig.
-4a).
-Specifically, species taller than 3.9 m had the highest interaction frequency, while species that were shorter than 3.9 m and had a nectar concentration lower than 16\% had the lowest interaction frequency.
-Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
-4b).
-Species with a nectar concentration over 49\% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49\%, more than 21,000 pollen grains per flower and height less than 0.78 m had the lowest normalized degree.
-Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
-4c).
-Overall, plant species with the highest specialization were shorter than 1.3 m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11\% of their fruits.
-In contrast, species taller or equal than 5.1 m and with lower than 14 ovules per flower had the lowest specialization values.
+When we further investigate which combination of traits drive plant
+network roles, we show that the regression tree for visitation frequency
+was best explained by plant height, nectar concentration and style
+length (Fig. 4a). Specifically, species taller than 3.9 m had the
+highest interaction frequency, while species that were shorter than 3.9
+m and had a nectar concentration lower than 16\% had the lowest
+interaction frequency. Normalized degree was best explained by nectar
+concentration, pollen grains per flower, plant height, flower width and
+autonomous selfing (Fig. 4b). Species with a nectar concentration over
+49\% had the highest levels of normalized degree, whereas species with
+nectar concentration lower than 49\%, more than 21,000 pollen grains per
+flower and height less than 0.78 m had the lowest normalized degree.
+Finally, specialization was best explained by plant height, ovule
+number, pollen grains per flower and autonomous selfing (Fig. 4c).
+Overall, plant species with the highest specialization were shorter than
+1.3 m, had more than 14,000 pollen grains per flower and autonomously
+self-pollinated less than 11\% of their fruits. In contrast, species
+taller or equal than 5.1 m and with lower than 14 ovules per flower had
+the lowest specialization values.
 
@@
 \includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\textbf{Fig.
-4 \textbar{} contribution of traits in plant's network roles.} Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
-The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
-Thus, the top node has the mean value of the named trait for the 100\% of species.
-Each node has a yes/no question and when the condition is fulfilled, the branch turns to the `yes' direction and when not, to the `no' direction.
-This rationale is followed in all the regression trees as indicated in the first branch division of the topmost node of each tree.}
+\caption{\label{fig:unnamed-chunk-4}\textbf{Fig. 4 \textbar{} contribution
+of traits in plant's network roles.} Regression tree analysis of
+interaction frequency (log-transformed), normalized degree and
+specialization for the subset of species with quantitative data for
+pollen and nectar traits. The superior value inside the node indicates
+the mean value of the different species-level metric and the lower
+value, the percentage of species that are considered in each node. Thus,
+the top node has the mean value of the named trait for the 100\% of
+species. Each node has a yes/no question and when the condition is
+fulfilled, the branch turns to the `yes' direction and when not, to the
+`no' direction. This rationale is followed in all the regression trees
+as indicated in the first branch division of the topmost node of each
+tree.}
 \end{figure}
@@
 
-\hypertarget{discussion}{%
-\section{DISCUSSION}\label{discussion}}
+\section{DISCUSSION}\label{discussion}
 
-Here, we show that plant species exhibit clear trade-offs in their floral, reproductive and vegetative traits.
-These trade-offs are differentiated on three main axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-Although these axes of trait variation did not explain overall visitation rates, we found that plant life strategies were clearly associated with different floral visitors guilds.
-Interestingly, pollen and nectar related traits were better than all other traits for characterizing plant species functional roles within their interaction networks.
+Here, we show that plant species exhibit clear trade-offs in their
+floral, reproductive and vegetative traits. These trade-offs are
+differentiated on three main axes of trait variation: (i) flower number
+- flower size, (ii) pollinator dependence and (iii) style length.
+Although these axes of trait variation did not explain overall
+visitation rates, we found that plant life strategies were clearly
+associated with different floral visitors guilds. Interestingly, pollen
+and nectar related traits were better than all other traits for
+characterizing plant species functional roles within their interaction
+networks.
 
-Over 50\% of plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
-Variation in these two axes of trait variation appears to be associated with the commonly described `fast-slow continuum' in plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}} and animal\textsuperscript{\protect\hyperlink{ref-healy2019}{34}} life-history strategies as indicated by the different floral and reproductive traits associated with plant height, life form and lifespan.
-The `slow' part of the continuum (i.e., tall trees and shrubs) had plant species with many flowers, few ovules, higher pollinator dependence, greater occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, greater occurrence of self compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the positive association already described in a previous study between outcrossing rate and floral display.\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{24}} This trend was further confirmed when looking at the specific correlation between floral display and autonomous selfing for our dataset (see Supplementary Fig.
-S10).
+Over 50\% of plant trait variation was captured by the flower number -
+flower size and pollinator dependence trade-offs. Variation in these two
+axes of trait variation appears to be associated with the commonly
+described `fast-slow continuum' in
+plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}} and
+animal\textsuperscript{\protect\hyperlink{ref-healy2019}{34}}
+life-history strategies as indicated by the different floral and
+reproductive traits associated with plant height, life form and
+lifespan. The `slow' part of the continuum (i.e., tall trees and shrubs)
+had plant species with many flowers, few ovules, higher pollinator
+dependence, greater occurrence of self-incompatibility and more complex
+breeding systems (e.g., monoecious and dioecious species). In contrast,
+species that employed the `fast' strategy (i.e., short herbs), had fewer
+flowers, more ovules, greater occurrence of self compatibility and lower
+pollinator dependence. Further, on the first two axes of trait
+variation, we found additional support for the positive association
+already described in a previous study between outcrossing rate and
+floral
+display\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{24}}.
+This trend was further confirmed when looking at the specific
+correlation between floral display and autonomous selfing for our
+dataset (see Supplementary Fig. S10).
 
-Despite the low predictive power of the main axes of trait variation on overall visitation patterns, we found commonalities among and within floral visitors guilds across these axes that indicate the influence of life-history strategies on floral visitation rate.
-For example, all guilds showed an increasing trend of visitation on plant species with higher pollinator dependence, which were also associated with larger floral displays and greater pollen quantities (Fig.
-1 and Supplementary Fig.
-S6).
-This trend is consistent with previous plant-pollinator studies that show higher visitation rates on species that make greater reproductive investment.\textsuperscript{\protect\hyperlink{ref-hegland2005}{35}--\protect\hyperlink{ref-kaiser2014}{37}} In regard to the flower number - flower size and style length trade-offs, different guilds showed contrasting visitation rates, which could be associated with different pollination syndromes at a macroecological scale.
-For instance, the guilds of bees and syrphids were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
-3) indicating a possible niche partitioning among these two guilds.\textsuperscript{\protect\hyperlink{ref-palmer2003}{38},\protect\hyperlink{ref-phillips2020}{39}} However, these plant-pollinator associations do not account for some of the traits (i.e., pollen and nectar quantity) that had greater relevance on the species network roles (Fig.
-4) because of insufficient data availability and lack of pollinator efficiency measurements for more complete descriptions of the pollination syndromes.\textsuperscript{\protect\hyperlink{ref-dellinger2020}{13}} In any case, it is worth noting that this general pattern emerges in field-measured plant-pollinator networks, where other local factors such as species relative abundances, will surely explain part of the observed variability.\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{12},\protect\hyperlink{ref-vazquez2007}{40},\protect\hyperlink{ref-encinas2012}{41}}
+Despite the low predictive power of the main axes of trait variation on
+overall visitation patterns, we found commonalities among and within
+floral visitors guilds across these axes that indicate the influence of
+life-history strategies on floral visitation rate. For example, all
+guilds showed an increasing trend of visitation on plant species with
+higher pollinator dependence, which were also associated with larger
+floral displays and greater pollen quantities (Fig. 1 and Supplementary
+Fig. S6). This trend is consistent with previous plant-pollinator
+studies that show higher visitation rates on species that make greater
+reproductive
+investment\textsuperscript{\protect\hyperlink{ref-hegland2005}{35}--\protect\hyperlink{ref-kaiser2014}{37}}.
+In regard to the flower number - flower size and style length
+trade-offs, different guilds showed contrasting visitation rates, which
+could be associated with different pollination syndromes at a
+macroecological scale. For instance, the guilds of bees and syrphids
+were clearly associated with opposing life-strategies on PC1 and PC3
+(Fig. 3) indicating a possible niche partitioning among these two
+guilds\textsuperscript{\protect\hyperlink{ref-palmer2003}{38},\protect\hyperlink{ref-phillips2020}{39}}.
+However, these plant-pollinator associations do not account for some of
+the traits (i.e., pollen and nectar quantity) that had greater relevance
+on the species network roles (Fig. 4) because of insufficient data
+availability and lack of pollinator efficiency measurements for more
+complete descriptions of the pollination
+syndromes\textsuperscript{\protect\hyperlink{ref-dellinger2020}{13}}. In
+any case, it is worth noting that this general pattern emerges in
+field-measured plant-pollinator networks, where other local factors such
+as species relative abundances, will surely explain part of the observed
+variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{12},\protect\hyperlink{ref-vazquez2007}{40},\protect\hyperlink{ref-encinas2012}{41}}.
 
-To conclude, we provide the first description of plant floral and reproductive trade-offs using a large global dataset of plant traits and interactions with floral visitors.
-This allowed us to identify the major reproductive strategies of flowering plants and how plant life strategies determine their interaction with floral visitor guilds.
-Although the percentage of explained variation found with the first two axes (\textasciitilde50\%) is lower than other studies that have evaluated life histories with vegetative traits,\textsuperscript{\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}} this percentage is consistent with the largest and most recent study that have characterized life strategies with both vegetative and reproductive (i.e., semelparity and iteroparity) traits.\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}} Future work needs to integrate these floral and reproductive compromises with the already described vegetative and physiological trade-offs\textsuperscript{\protect\hyperlink{ref-diaz2016}{18}} to create a more comprehensive spectra of trait variation.\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}} Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators.\textsuperscript{\protect\hyperlink{ref-gervasi2017}{42},\protect\hyperlink{ref-mackin2021}{43}} Finally, a more complete description of the macroecological patterns of plant-pollinator interactions including unrepresented areas of the world\textsuperscript{\protect\hyperlink{ref-poisot2021}{44}} and traits that have been largely ignored (e.g., floral rewards and plant mating system) are needed to progress in our understanding of the global patterns in plant-pollinator interactions.
+To conclude, we provide the first description of plant floral and
+reproductive trade-offs using a large global dataset of plant traits and
+interactions with floral visitors. This allowed us to identify the major
+reproductive strategies of flowering plants and how plant life
+strategies determine their interaction with floral visitor guilds.
+Although the percentage of explained variation found with the first two
+axes (\textasciitilde{}50\%) is lower than other studies that have
+evaluated life histories with vegetative
+traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}},
+this percentage is consistent with the largest and most recent study
+that have characterized life strategies with both vegetative and
+reproductive (i.e., semelparity and iteroparity)
+traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}}. Future
+work needs to integrate these floral and reproductive compromises with
+the already described vegetative and physiological
+trade-offs\textsuperscript{\protect\hyperlink{ref-diaz2016}{18}} to
+create a more comprehensive spectra of trait
+variation\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}}.
+Further, the varying level of phylogenetic signal among traits deserves
+further attention to understand evolutionary changes on mating and
+flower morphology in response to
+pollinators\textsuperscript{\protect\hyperlink{ref-gervasi2017}{42},\protect\hyperlink{ref-mackin2021}{43}}.
+Finally, a more complete description of the macroecological patterns of
+plant-pollinator interactions including unrepresented areas of the
+world\textsuperscript{\protect\hyperlink{ref-poisot2021}{44}} and traits
+that have been largely ignored (e.g., floral rewards and plant mating
+system) are needed to progress in our understanding of the global
+patterns in plant-pollinator interactions.
 
-\hypertarget{materials-and-methods}{%
-\section{MATERIALS AND METHODS}\label{materials-and-methods}}
+\section{MATERIALS AND METHODS}\label{materials-and-methods}
 
-\textbf{Plant-pollinator network studies.} We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3},\protect\hyperlink{ref-fortuna2010}{45}} or available in online archives (e.g., `The Web of Life'\textsuperscript{\protect\hyperlink{ref-fortuna2010}{45}} and `Mangal'.\textsuperscript{\protect\hyperlink{ref-poisot2016}{46}} In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+\textbf{Plant-pollinator network studies.} We selected 28 studies from
+18 different countries that constituted a total of 64 plant-pollinator
+networks. These studies recorded plant-pollinator interactions in
+natural systems and were selected so that we had broad geographical
+representation. Although these studies differ in sampling effort and
+methodology, all studies provided information about plant-pollinator
+interactions (weighted and non-weighted), which we used to build a
+database of plant species that are likely to be animal pollinated. Many
+of these networks are freely available either as published
+studies\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3},\protect\hyperlink{ref-fortuna2010}{45}}
+or available in online archives (e.g., `The Web of
+Life'\textsuperscript{\protect\hyperlink{ref-fortuna2010}{45}} and
+`Mangal'\textsuperscript{\protect\hyperlink{ref-poisot2016}{46}}. In
+total, our network dataset (see Supplementary Table S1) constituted 60
+weighted (interaction frequency) and 4 unweighted (presence/absence of
+the interaction) networks, each sampled at a unique location and year,
+as well as eight meta-webs where interactions were pooled across several
+locations and multiple years.
 
-\textbf{Taxonomy of plants and pollinators.} All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize}.\textsuperscript{\protect\hyperlink{ref-chamberlain2020}{47}} We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
+\textbf{Taxonomy of plants and pollinators.} All species names, genera,
+families and orders were retrieved and standardized from the taxonomy
+data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for
+plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the
+R package
+\emph{taxize}\textsuperscript{\protect\hyperlink{ref-chamberlain2020}{47}}.
+We filled the `not found' searches manually using
+\url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for
+plants and \url{http://www.catalogueoflife.org/} for floral visitors.
 
-\textbf{Functional traits.} We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
-These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive and 3 vegetative).
-For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8\% of the dataset, see Supplementary Fig.
-S1 for missing values information for each trait).
+\textbf{Functional traits.} We selected 20 different functional traits
+based on their relevance to plant reproduction and data availability
+(Table 1). These included twelve quantitative and eight categorical
+traits belonging to three broader trait groupings (13 floral, 4
+reproductive and 3 vegetative, Supplementary Information). For each
+plant species, we undertook an extensive literature and online search
+across a wide range of resources (plant databases, online floras, books,
+journals and images). From a total of 30,120 cells (20 columns × 1,506
+species) we were able to fill 24,341 cells (80.8\% of the dataset, see
+Supplementary Fig. S1 for missing values information for each trait).
 
-\textbf{Phylogenetic Distance.} We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life.\textsuperscript{\protect\hyperlink{ref-smith2018}{48},\protect\hyperlink{ref-jin2019}{49}}
+\textbf{Phylogenetic Distance.} We calculated the phylogenetic distance
+between different plant species using the function \emph{get\_tree} from
+the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}),
+which downloads phylogenetic distances from the extended R
+implementation of the Open Tree of
+Life\textsuperscript{\protect\hyperlink{ref-smith2018}{48},\protect\hyperlink{ref-jin2019}{49}}.
 
@@
 
-\textbf{Data Imputation.} Trait missing values were imputed with the function \emph{missForest}\textsuperscript{\protect\hyperlink{ref-stekhoven2012}{50}} which allows imputation of data sets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest}.\textsuperscript{\protect\hyperlink{ref-penone2014}{51}} To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{52}} based on a previous conceptual framework that considers phylogenetic eigenvectors.\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{53}} Although the variable of autonomous selfing had a high percentage of missing values (68\%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
-The categories of `none', `low', `medium' and `high' were converted to representative percentages of each category 0\%, 13\%, 50.5\% and 88\% respectively.
-This reduced the percentage of missing values for this column from 68\% to 35\% and allowed the imputation of this variable.
-However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Supplementary Fig.
-S1).
-Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79\% of missing values.
-Further, we conducted an additional imputation on the filtered raw data by filled cells of either pollen grains per flower or microlitres of nectar.
-This subset comprised 755 species, 8.01\% missing values and all traits but milligrams of nectar (\textasciitilde50\% of missing values) were included in the imputation process.
+\textbf{Data Imputation.} Trait missing values were imputed with the
+function
+\emph{missForest}\textsuperscript{\protect\hyperlink{ref-stekhoven2012}{50}}
+which allows imputation of data sets with continuous and categorical
+variables. We accounted for the phylogenetic distance among species on
+the imputation process by including the eigenvectors of a principal
+component analysis of the phylogenetic distance (PCoA) which has been
+shown to improve the performance of
+\emph{missForest}\textsuperscript{\protect\hyperlink{ref-penone2014}{51}}.
+To extract the eigenvectors, we used the function \emph{PVRdecomp} from
+the package
+\emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{52}} based
+on a previous conceptual framework that considers phylogenetic
+eigenvectors\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{53}}.
+Although the variable of autonomous selfing had a high percentage of
+missing values (68\%), we were able to solve this by back transforming
+the qualitative column of autonomous selfing to numerical. The
+categories of `none', `low', `medium' and `high' were converted to
+representative percentages of each category 0\%, 13\%, 50.5\% and 88\%
+respectively. This reduced the percentage of missing values for this
+column from 68\% to 35\% and allowed the imputation of this variable.
+However, we were unable to include nectar and pollen traits on the
+imputation process because of the high percentage of missing values
+(Supplementary Fig. S1). Hence, the imputed dataset had 1,506 species,
+seven categorical and eight numerical variables and 5.79\% of missing
+values. Further, we conducted an additional imputation on the filtered
+raw data by filled cells of either pollen grains per flower or
+microlitres of nectar. This subset comprised 755 species, 8.01\% missing
+values and all traits but milligrams of nectar (\textasciitilde{}50\% of
+missing values) were included in the imputation process.
 
-\textbf{Plant strategies.} We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01 respectively), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th--97.5th percentile range,\textsuperscript{\protect\hyperlink{ref-legendre2012}{54}} and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools}\textsuperscript{\protect\hyperlink{ref-revell2012}{55}} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation.\textsuperscript{\protect\hyperlink{ref-abdi2010}{56}} Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
-S2).
-We found little difference between the explained variance with the imputed dataset (51.08\%) and the dataset without missing values (52.87\%).
-In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
-For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
+\textbf{Plant strategies.} We explored the trade-offs between different
+quantitative plant functional traits with a phylogenetically informed
+Principal Component Analysis (pPCA). We did not include the quantitative
+variables of flower length and inflorescence width because they were
+highly and moderately correlated to flower width respectively (Pearson's
+correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation
+= 0.36, \emph{P} \textless{} 0.01 respectively), and thus we avoided
+overemphasizing flower size on the spectrum of trait variation. Although
+qualitative traits were not included in the dimensionality reduction
+analysis, we also investigated the association of the different
+qualitative traits with the main axes of trait variation. Prior to the
+analyses, we excluded outliers and standardized the data. Due to the
+high sensitivity of dimensionality reduction to outliers, we excluded
+values within the 2.5th--97.5th percentile
+range\textsuperscript{\protect\hyperlink{ref-legendre2012}{54}}, and
+thus our final dataset had 1,236 species. Then, we log transformed the
+variables to reduce the influence of outliers and z-transformed (X= 0,
+SD=1) so that all variables were within the same numerical range. We
+performed the pPCA using the function \emph{phyl.pca} from the package
+\emph{phytools}\textsuperscript{\protect\hyperlink{ref-revell2012}{55}}
+with the method lambda (\(\lambda\)) that calculates the phylogenetic
+correlation between 0 (phylogenetic independence) and 1 (shared
+evolutionary history) and we implemented the mode covariance because
+values for each variables were on the same scale following
+transformation\textsuperscript{\protect\hyperlink{ref-abdi2010}{56}}.
+Moreover, to corroborate that our imputation of missing values did not
+affect our results, we conducted a pPCA on the full dataset without
+missing values (see Supplementary Fig. S2). We found little difference
+between the explained variance with the imputed dataset (51.08\%) and
+the dataset without missing values (52.87\%). In addition, the loadings
+on each principal component had a similar contribution and correlation
+patterns, with the exception of plant height which showed slight
+variations between the imputed and non-imputed dataset. Finally, we
+conducted an additional phylogenetic informed principal component
+analysis for the subset of species with pollen and nectar quantity. For
+this, we included all quantitative traits considered in the main pPCA
+plus pollen grains and microlitres of nectar per flower.
 
-\textbf{Phylogenetic signal of traits.} We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} version \emph{0.7-70}\textsuperscript{\protect\hyperlink{ref-revell2012}{55}} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
+\textbf{Phylogenetic signal of traits.} We calculated the phylogenetic
+signal of the different quantitative traits on the imputed dataset with
+the full set of species (N = 1,506) with the package \emph{phytools}
+version
+\emph{0.7-70}\textsuperscript{\protect\hyperlink{ref-revell2012}{55}}
+and we used Pagel's \(\lambda\) as a measurement of the phylogenetic
+signal. However, for pollen and nectar traits, phylogenetic signal was
+calculated only on the subset of species that had quantitative
+information for these traits (N = 755).
 
-\textbf{Networks analyses.} Analyses were conducted on the subset of 60 weighted networks with interaction frequency sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our weighted network dataset (excluding meta-webs) included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-Anthophila-Hymenoptera interactions.
-Although floral visitors are not always pollinators and the frequency of visits does not consider each pollinator species efficiency,\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{57}} visitation rate provides valuable information of the contribution of floral visitors to pollination.\textsuperscript{\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}} Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
-All analyses were conducted in R version \emph{4.0.3}.
+\textbf{Networks analyses.} Analyses were conducted on the subset of 60
+weighted networks with interaction frequency sampled in a unique
+flowering season and site, which included 556 plant and 1,126 pollinator
+species. In total, our weighted network dataset (excluding meta-webs)
+included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with
+plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae
+interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions
+and 362 non-Anthophila-Hymenoptera interactions. Although floral
+visitors are not always pollinators and the frequency of visits does not
+consider each pollinator species
+efficiency\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{57}},
+visitation rate provides valuable information of the contribution of
+floral visitors to
+pollination\textsuperscript{\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}}.
+Sampling methods varied across networks but this was accounted for in
+analyses by considering them in the random effects of the modelling
+process. All analyses were conducted in R version \emph{4.0.3}.
 
-\textbf{Visitation patterns.} We used Bayesian modelling (see below for details) to explore the effect of floral visitors groups and the main axes of trait variation (pPCA with imputed dataset) on floral visits per plant species.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because Hymenoptera-Anthophila was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the visitation rate of the main Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total).
-This finding is consistent with previous research showing that \emph{A.
-mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems.\textsuperscript{\protect\hyperlink{ref-hung2018}{60}} Hence, to control for the effect of \emph{A.
-mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis excluding \emph{A.
-mellifera}.
-We found that \emph{A.
-mellifera}, was partly driving some of the observed trends on PC1 (Supplementary Fig.
-S3).
-However, we did not detect major differences on PC2 and PC3.
+\textbf{Visitation patterns.} We used Bayesian modelling (see below for
+details) to explore the effect of floral visitors groups and the main
+axes of trait variation (pPCA with imputed dataset) on floral visits per
+plant species. For this, we divided floral visitors into six main guilds
+that differ in life form, behaviour and are likely to play a similar
+ecological role: (i) Hymenoptera-Anthophila (bees), (ii)
+Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii)
+Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi)
+Coleoptera. Moreover, because Hymenoptera-Anthophila was the most
+represented group with 2,256 records and had the highest frequency of
+visits of all groups, we also explored the visitation rate of the main
+Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae,
+Halictidae and Megachilidae) on the trait space. In addition, we found
+that \emph{Apis mellifera} was the floral visitor with the largest
+proportion of records counted (7.55\% of the total). This finding is
+consistent with previous research showing that \emph{A. mellifera} was
+the most frequent floral visitor in a similar dataset of 80
+plant-pollinator networks in natural
+ecosystems\textsuperscript{\protect\hyperlink{ref-hung2018}{60}}. Hence,
+to control for the effect of \emph{A. mellifera} on the observed
+visitation patterns of bees, we conducted an analogous analysis
+excluding \emph{A. mellifera}. We found that \emph{A. mellifera}, was
+partly driving some of the observed trends on PC1 (Supplementary Fig.
+S3). However, we did not detect major differences on PC2 and PC3.
 
-We implemented Bayesian generalized linear mixed models using the R package \emph{brms}.\textsuperscript{\protect\hyperlink{ref-burkner2017}{61}} We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
-In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
-We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package.\textsuperscript{\protect\hyperlink{ref-gabry2019}{62}}
+We implemented Bayesian generalized linear mixed models using the R
+package
+\emph{brms}\textsuperscript{\protect\hyperlink{ref-burkner2017}{61}}. We
+modelled the frequency of visits as a function of the main axes of plant
+trait variation and their interactions with floral visitor functional
+groups (Visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation
+patterns among floral visitors groups to plants with different
+strategies, we included interactions between the main axes of trait
+variation (PC1, PC2 and PC3) and the floral visitor guilds. In this
+model, we added a nested random effect of networks nested within the
+study system to capture the variation in networks among studies and
+within networks. Moreover, we included the phylogenetic covariance
+matrix as a random factor due to the possible shared evolutionary
+histories of species and therefore lack of independence across them. We
+specified this model with a zero inflated negative binomial distribution
+and weakly informative priors from the brms function. We run this model
+for 3,000 iterations and with previous 1,000 warm up iterations. We set
+delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized
+the posterior predictive checks with the function \emph{pp\_check} using
+the \emph{bayesplot}
+package\textsuperscript{\protect\hyperlink{ref-gabry2019}{62}}.
 
-\textbf{Plant species functional roles.} We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{63}} with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization,\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{64}} which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite}.\textsuperscript{\protect\hyperlink{ref-dormann2008}{63}}
+\textbf{Plant species functional roles.} We investigated whether
+different quantitative traits determined plant species functional roles
+using Bayesian modelling and regression trees. For this, we selected
+simple and complementary species-level network metrics commonly applied
+in bipartite network
+studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{63}} with a
+straightforward ecological interpretation relevant to our research
+goals. The different plant species-level metrics were: (i) sum of visits
+per plant species; (ii) normalized degree, calculated as the number of
+links per plant species divided by the total possible number of
+partners; and (iii)
+specialization\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{64}},
+which measures the deviation of an expected random choice of the
+available interaction partners and ranges between 0 (maximum
+generalization) and 1 (maximum specialization). Normalized degree and
+specialization were calculated with the \emph{specieslevel} function
+from the R package
+\emph{bipartite}\textsuperscript{\protect\hyperlink{ref-dormann2008}{63}}.
 
-First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
-For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns section'.
+First, we modelled the distinct plant species metrics (sum of visits,
+normalized degree and plant specialization) as a function of the three
+main axes of trait variation (plant species level metric
+\textasciitilde{} PC1 + PC2 + PC3). For each response variable (i.e.,
+each plant species level metric), we used different distribution
+families (zero inflated negative binomial for the sum of visits, weibull
+for normalized degree and zero one inflated beta for specialization).
+Finally, we used the same random factors, model settings and conducted
+the same posterior predictive checks for each model as detailed above in
+the `visitation patterns section'.
 
-Second, to better understand these complex trait relationships, we used regression trees.
-Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
-We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
-We conducted this analysis using the \emph{rpart} package\textsuperscript{\protect\hyperlink{ref-therneau2015}{65}} version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package\textsuperscript{\protect\hyperlink{ref-milborrow2015}{66}} version \emph{3.0.9} to plot the regression trees.
-We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
-We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig.
-S4).
+Second, to better understand these complex trait relationships, we used
+regression trees. Regression trees are recursive algorithms which can
+detect complex relationships among predictors and allow identification
+of the relevance of specific trait combinations on species functional
+roles. We focused exclusively on quantitative traits because almost all
+categorical traits were statistically associated with the first two axes
+of trait variation (Supplementary Table S2). We conducted this analysis
+using the \emph{rpart}
+package\textsuperscript{\protect\hyperlink{ref-therneau2015}{65}}
+version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50
+observations per terminal node and we used the \emph{rpart.plot}
+package\textsuperscript{\protect\hyperlink{ref-milborrow2015}{66}}
+version \emph{3.0.9} to plot the regression trees. We considered the
+species level indices as response variables (interaction frequency,
+normalized degree and specialization) and we performed one regression
+tree per metric using the different quantitative traits as predictors.
+We calculated two regression trees per plant species-level metric, one
+for the full set of species and another for the subset of species for
+which we had pollen and nectar traits. We focused on regression trees
+that included floral rewards because they consistently showed pollen and
+nectar traits as being the best for explaining the different
+species-level metrics (see Supplementary Fig. S4).
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\section{References}\label{references}
 
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-barrett2002}{}%
-1. Barrett, S. C. H. The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.} \textbf{3}, 274--284 (2002).
+\hypertarget{ref-barrett2002}{}
+1. Barrett, S. C. H. The evolution of plant sexual diversity. \emph{Nat.
+Rev. Genet.} \textbf{3}, 274--284 (2002).
 
-\leavevmode\hypertarget{ref-schiestl2013}{}%
-2. Schiestl, F. P. \& Johnson, S. D. Pollinator-mediated evolution of floral signals. \emph{Trends Ecol. Evol.} \textbf{28}, 307--315 (2013).
+\hypertarget{ref-schiestl2013}{}
+2. Schiestl, F. P. \& Johnson, S. D. Pollinator-mediated evolution of
+floral signals. \emph{Trends Ecol. Evol.} \textbf{28}, 307--315 (2013).
 
-\leavevmode\hypertarget{ref-carvalheiro2014}{}%
-3.
-Carvalheiro, L.
-G.
-\emph{et al.} The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
-\emph{Ecol.
-Lett.} \textbf{17}, 1389--1399 (2014).
+\hypertarget{ref-carvalheiro2014}{}
+3. Carvalheiro, L. G. \emph{et al.} The potential for indirect effects
+between co-flowering plants via shared pollinators depends on resource
+abundance, accessibility and relatedness. \emph{Ecol. Lett.}
+\textbf{17}, 1389--1399 (2014).
 
-\leavevmode\hypertarget{ref-baude2016}{}%
-4. Baude, M. \emph{et al.} Historical nectar assessment reveals the fall and rise of floral resources in britain. \emph{Nature} \textbf{530}, 85--88 (2016).
+\hypertarget{ref-baude2016}{}
+4. Baude, M. \emph{et al.} Historical nectar assessment reveals the fall
+and rise of floral resources in britain. \emph{Nature} \textbf{530},
+85--88 (2016).
 
-\leavevmode\hypertarget{ref-munoz2016}{}%
-5.
-Munoz, F., Violle, C.
-\& Cheptou, P.-O.
-CSR ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
-\emph{Oikos} \textbf{125}, 1296--1303 (2016).
+\hypertarget{ref-munoz2016}{}
+5. Munoz, F., Violle, C. \& Cheptou, P.-O. CSR ecological strategies and
+plant mating systems: Outcrossing increases with competitiveness but
+stress-tolerance is related to mixed mating. \emph{Oikos} \textbf{125},
+1296--1303 (2016).
 
-\leavevmode\hypertarget{ref-moeller2017}{}%
-6. Moeller, D. A. \emph{et al.} Global biogeography of mating system variation in seed plants. \emph{Ecol. Lett.} \textbf{20}, 375--384 (2017).
+\hypertarget{ref-moeller2017}{}
+6. Moeller, D. A. \emph{et al.} Global biogeography of mating system
+variation in seed plants. \emph{Ecol. Lett.} \textbf{20}, 375--384
+(2017).
 
-\leavevmode\hypertarget{ref-grossenbacher2017}{}%
-7. Grossenbacher, D. L. \emph{et al.} Self-compatibility is over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478 (2017).
+\hypertarget{ref-grossenbacher2017}{}
+7. Grossenbacher, D. L. \emph{et al.} Self-compatibility is
+over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478
+(2017).
 
-\leavevmode\hypertarget{ref-salguero2016}{}%
-8.
-Salguero-Gómez, R.
-\emph{et al.} Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
-\emph{Proc.
-Natl.
-Acad.
-Sci.
-U.S.A.} \textbf{113}, 230--235 (2016).
+\hypertarget{ref-salguero2016}{}
+8. Salguero-Gómez, R. \emph{et al.} Fast-slow continuum and reproductive
+strategies structure plant life-history variation worldwide. \emph{Proc.
+Natl. Acad. Sci. U.S.A.} \textbf{113}, 230--235 (2016).
 
-\leavevmode\hypertarget{ref-ruger2018}{}%
-9. Rüger, N. \emph{et al.} Beyond the fastSlow continuum: Demographic dimensions structuring a tropical tree community. \emph{Ecol. Lett.} \textbf{21}, 1075--1084 (2018).
+\hypertarget{ref-ruger2018}{}
+9. Rüger, N. \emph{et al.} Beyond the fastSlow continuum: Demographic
+dimensions structuring a tropical tree community. \emph{Ecol. Lett.}
+\textbf{21}, 1075--1084 (2018).
 
-\leavevmode\hypertarget{ref-roddy2021}{}%
-10. Roddy, A. B. \emph{et al.} Towards the flower economics spectrum. \emph{New Phytol.} \textbf{229}, 665--672 (2021).
+\hypertarget{ref-roddy2021}{}
+10. Roddy, A. B. \emph{et al.} Towards the flower economics spectrum.
+\emph{New Phytol.} \textbf{229}, 665--672 (2021).
 
-\leavevmode\hypertarget{ref-fenster2004}{}%
-11. Fenster, C. B., Armbruster, W. S., Wilson, P., Dudash, M. R. \& Thomson, J. D. Pollination Syndromes and Floral Specialization. \emph{Annu. Rev. Ecol. Evol. Syst.} \textbf{35}, 375--403 (2004).
+\hypertarget{ref-fenster2004}{}
+11. Fenster, C. B., Armbruster, W. S., Wilson, P., Dudash, M. R. \&
+Thomson, J. D. Pollination Syndromes and Floral Specialization.
+\emph{Annu. Rev. Ecol. Evol. Syst.} \textbf{35}, 375--403 (2004).
 
-\leavevmode\hypertarget{ref-bartomeus2016}{}%
-12. Bartomeus, I. \emph{et al.} A common framework for identifying linkage rules across different types of interactions. \emph{Funct. Ecol.} \textbf{30}, 1894--1903 (2016).
+\hypertarget{ref-bartomeus2016}{}
+12. Bartomeus, I. \emph{et al.} A common framework for identifying
+linkage rules across different types of interactions. \emph{Funct.
+Ecol.} \textbf{30}, 1894--1903 (2016).
 
-\leavevmode\hypertarget{ref-dellinger2020}{}%
-13. Dellinger, A. S. Pollination syndromes in the 21st century: Where do we stand and where may we go? \emph{New Phytol.} \textbf{228}, 1193--1213 (2020).
+\hypertarget{ref-dellinger2020}{}
+13. Dellinger, A. S. Pollination syndromes in the 21st century: Where do
+we stand and where may we go? \emph{New Phytol.} \textbf{228},
+1193--1213 (2020).
 
-\leavevmode\hypertarget{ref-tur2013}{}%
-14. Tur, C., Castro-Urgal, R. \& Traveset, A. Linking Plant Specialization to Dependence in Interactions for Seed Set in Pollination Networks. \emph{PLoS One} \textbf{8}, e78294 (2013).
+\hypertarget{ref-tur2013}{}
+14. Tur, C., Castro-Urgal, R. \& Traveset, A. Linking Plant
+Specialization to Dependence in Interactions for Seed Set in Pollination
+Networks. \emph{PLoS One} \textbf{8}, e78294 (2013).
 
-\leavevmode\hypertarget{ref-devaux2014}{}%
-15. Devaux, C., Lepers, C. \& Porcher, E. Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems. \emph{J. Evol. Biol.} \textbf{27}, 1413--1430 (2014).
+\hypertarget{ref-devaux2014}{}
+15. Devaux, C., Lepers, C. \& Porcher, E. Constraints imposed by
+pollinator behaviour on the ecology and evolution of plant mating
+systems. \emph{J. Evol. Biol.} \textbf{27}, 1413--1430 (2014).
 
-\leavevmode\hypertarget{ref-kattge2011}{}%
-16. Kattge, J. \emph{et al.} TRY a global database of plant traits. \emph{Glob. Chang. Biol.} \textbf{17}, 2905--2935 (2011).
+\hypertarget{ref-kattge2011}{}
+16. Kattge, J. \emph{et al.} TRY a global database of plant traits.
+\emph{Glob. Chang. Biol.} \textbf{17}, 2905--2935 (2011).
 
-\leavevmode\hypertarget{ref-salguero2015}{}%
-17. Salguero-Gómez, R. \emph{et al.} The compadre Plant Matrix Database: An open online repository for plant demography. \emph{J. Ecol.} \textbf{103}, 202--218 (2015).
+\hypertarget{ref-salguero2015}{}
+17. Salguero-Gómez, R. \emph{et al.} The compadre Plant Matrix Database:
+An open online repository for plant demography. \emph{J. Ecol.}
+\textbf{103}, 202--218 (2015).
 
-\leavevmode\hypertarget{ref-diaz2016}{}%
-18. Díaz, S. \emph{et al.} The global spectrum of plant form and function. \emph{Nature} \textbf{529}, 167--171 (2016).
+\hypertarget{ref-diaz2016}{}
+18. Díaz, S. \emph{et al.} The global spectrum of plant form and
+function. \emph{Nature} \textbf{529}, 167--171 (2016).
 
-\leavevmode\hypertarget{ref-carmona2021}{}%
-19. Carmona, C. P. \emph{et al.} Erosion of global functional diversity across the tree of life. \emph{Sci. Adv.} \textbf{7}, eabf2675 (2021).
+\hypertarget{ref-carmona2021}{}
+19. Carmona, C. P. \emph{et al.} Erosion of global functional diversity
+across the tree of life. \emph{Sci. Adv.} \textbf{7}, eabf2675 (2021).
 
-\leavevmode\hypertarget{ref-wright2004}{}%
-20. Wright, I. J. \emph{et al.} The worldwide leaf economics spectrum. \emph{Nature} \textbf{428}, 821--827 (2004).
+\hypertarget{ref-wright2004}{}
+20. Wright, I. J. \emph{et al.} The worldwide leaf economics spectrum.
+\emph{Nature} \textbf{428}, 821--827 (2004).
 
-\leavevmode\hypertarget{ref-chave2009}{}%
-21. Chave, J. \emph{et al.} Towards a worldwide wood economics spectrum. \emph{Ecol. Lett.} \textbf{12}, 351--366 (2009).
+\hypertarget{ref-chave2009}{}
+21. Chave, J. \emph{et al.} Towards a worldwide wood economics spectrum.
+\emph{Ecol. Lett.} \textbf{12}, 351--366 (2009).
 
-\leavevmode\hypertarget{ref-evojtko2020}{}%
-22.
-E-Vojtkó, A., Bello, F.
-de, Durka, W., Kühn, I.
-\& Götzenberger, L.
-The neglected importance of floral traits in trait-based plant community assembly.
-\emph{J.
-Veg.
-Sci.} \textbf{31}, 529--539 (2020).
+\hypertarget{ref-evojtko2020}{}
+22. E-Vojtkó, A., Bello, F. de, Durka, W., Kühn, I. \& Götzenberger, L.
+The neglected importance of floral traits in trait-based plant community
+assembly. \emph{J. Veg. Sci.} \textbf{31}, 529--539 (2020).
 
-\leavevmode\hypertarget{ref-barrett2003}{}%
-23. Barrett, S. C. H. Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond. \emph{Philos. Trans. R. Soc. Lond. B Biol. Sci.} \textbf{358}, 991--1004 (2003).
+\hypertarget{ref-barrett2003}{}
+23. Barrett, S. C. H. Mating strategies in flowering plants: The
+outcrossing-selfing paradigm and beyond. \emph{Philos. Trans. R. Soc.
+Lond. B Biol. Sci.} \textbf{358}, 991--1004 (2003).
 
-\leavevmode\hypertarget{ref-goodwillie2010}{}%
-24.
-Goodwillie, C.
-\emph{et al.} Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
-\emph{New Phytol.} \textbf{185}, 311--321 (2010).
+\hypertarget{ref-goodwillie2010}{}
+24. Goodwillie, C. \emph{et al.} Correlated evolution of mating system
+and floral display traits in flowering plants and its implications for
+the distribution of mating system variation. \emph{New Phytol.}
+\textbf{185}, 311--321 (2010).
 
-\leavevmode\hypertarget{ref-ollerton2011}{}%
-25. Ollerton, J., Winfree, R. \& Tarrant, S. How many flowering plants are pollinated by animals? \emph{Oikos} \textbf{120}, 321--326 (2011).
+\hypertarget{ref-ollerton2011}{}
+25. Ollerton, J., Winfree, R. \& Tarrant, S. How many flowering plants
+are pollinated by animals? \emph{Oikos} \textbf{120}, 321--326 (2011).
 
-\leavevmode\hypertarget{ref-lazaro2008}{}%
-26.
-Lázaro, A., Hegland, S.
-J.
-\& Totland, Ø.
-The relationships between floral traits and specificity of pollination systems in three Scandinavian plant communities.
-\emph{Oecologia} \textbf{157}, 249--257 (2008).
+\hypertarget{ref-lazaro2008}{}
+26. Lázaro, A., Hegland, S. J. \& Totland, Ø. The relationships between
+floral traits and specificity of pollination systems in three
+Scandinavian plant communities. \emph{Oecologia} \textbf{157}, 249--257
+(2008).
 
-\leavevmode\hypertarget{ref-bartomeus2013}{}%
-27.
-Bartomeus, I.
-Understanding Linkage Rules in Plant-Pollinator Networks by Using Hierarchical Models That Incorporate Pollinator Detectability and Plant Traits.
-\emph{PLoS One} \textbf{8}, e69200 (2013).
+\hypertarget{ref-bartomeus2013}{}
+27. Bartomeus, I. Understanding Linkage Rules in Plant-Pollinator
+Networks by Using Hierarchical Models That Incorporate Pollinator
+Detectability and Plant Traits. \emph{PLoS One} \textbf{8}, e69200
+(2013).
 
-\leavevmode\hypertarget{ref-junker2013}{}%
-28.
-Junker, R.
-R.
-\emph{et al.} Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
-\emph{Funct.
-Ecol.} \textbf{27}, 329--341 (2013).
+\hypertarget{ref-junker2013}{}
+28. Junker, R. R. \emph{et al.} Specialization on traits as basis for
+the niche-breadth of flower visitors and as structuring mechanism of
+ecological networks. \emph{Funct. Ecol.} \textbf{27}, 329--341 (2013).
 
-\leavevmode\hypertarget{ref-coux2016}{}%
-29. Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking species functional roles to their network roles. \emph{Ecol. Lett.} \textbf{19}, 762--770 (2016).
+\hypertarget{ref-coux2016}{}
+29. Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking
+species functional roles to their network roles. \emph{Ecol. Lett.}
+\textbf{19}, 762--770 (2016).
 
-\leavevmode\hypertarget{ref-stang2009}{}%
-30.
-Stang, M., Klinkhamer, P.
-G.
-L., Waser, N.
-M., Stang, I.
-\& van der Meijden, E.
-Size-specific interaction patterns and size matching in a plantPollinator interaction web.
-\emph{Ann.
-Bot.} \textbf{103}, 1459--1469 (2009).
+\hypertarget{ref-stang2009}{}
+30. Stang, M., Klinkhamer, P. G. L., Waser, N. M., Stang, I. \& van der
+Meijden, E. Size-specific interaction patterns and size matching in a
+plantPollinator interaction web. \emph{Ann. Bot.} \textbf{103},
+1459--1469 (2009).
 
-\leavevmode\hypertarget{ref-ibanez2012}{}%
-31. Ibanez, S. Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks. \emph{Oecologia} \textbf{170}, 233--242 (2012).
+\hypertarget{ref-ibanez2012}{}
+31. Ibanez, S. Optimizing size thresholds in a plant-pollinator
+interaction web: Towards a mechanistic understanding of ecological
+networks. \emph{Oecologia} \textbf{170}, 233--242 (2012).
 
-\leavevmode\hypertarget{ref-sargent2007}{}%
-32. Sargent, R. D., Goodwillie, C., Kalisz, S. \& Ree, R. H. Phylogenetic evidence for a flower size and number trade-off. \emph{Am. J. Bot.} \textbf{94}, 2059--2062 (2007).
+\hypertarget{ref-sargent2007}{}
+32. Sargent, R. D., Goodwillie, C., Kalisz, S. \& Ree, R. H.
+Phylogenetic evidence for a flower size and number trade-off. \emph{Am.
+J. Bot.} \textbf{94}, 2059--2062 (2007).
 
-\leavevmode\hypertarget{ref-kettle2011}{}%
-33. Kettle, C. J. \emph{et al.} Ecological Implications of a Flower Size/Number Trade-Off in Tropical Forest Trees. \emph{PLoS One} \textbf{6}, e16111 (2011).
+\hypertarget{ref-kettle2011}{}
+33. Kettle, C. J. \emph{et al.} Ecological Implications of a Flower
+Size/Number Trade-Off in Tropical Forest Trees. \emph{PLoS One}
+\textbf{6}, e16111 (2011).
 
-\leavevmode\hypertarget{ref-healy2019}{}%
-34.
-Healy, K., Ezard, T.
-H.
-G., Jones, O.
-R., Salguero-Gómez, R.
-\& Buckley, Y.
-M.
-Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
-\emph{Nat.
-Ecol.
-Evol} \textbf{3}, 1217--1224 (2019).
+\hypertarget{ref-healy2019}{}
+34. Healy, K., Ezard, T. H. G., Jones, O. R., Salguero-Gómez, R. \&
+Buckley, Y. M. Animal life history is shaped by the pace of life and the
+distribution of age-specific mortality and reproduction. \emph{Nat.
+Ecol. Evol} \textbf{3}, 1217--1224 (2019).
 
-\leavevmode\hypertarget{ref-hegland2005}{}%
-35. Hegland, S. J. \& Totland, Ø. Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia} \textbf{145}, 586--594 (2005).
+\hypertarget{ref-hegland2005}{}
+35. Hegland, S. J. \& Totland, Ø. Relationships between species' floral
+traits and pollinator visitation in a temperate grassland.
+\emph{Oecologia} \textbf{145}, 586--594 (2005).
 
-\leavevmode\hypertarget{ref-lazaro2013}{}%
-36. Lázaro, A., Jakobsson, A. \& Totland, Ø. How do pollinator visitation rate and seed set relate to species' floral traits and community context? \emph{Oecologia} \textbf{173}, 881--893 (2013).
+\hypertarget{ref-lazaro2013}{}
+36. Lázaro, A., Jakobsson, A. \& Totland, Ø. How do pollinator
+visitation rate and seed set relate to species' floral traits and
+community context? \emph{Oecologia} \textbf{173}, 881--893 (2013).
 
-\leavevmode\hypertarget{ref-kaiser2014}{}%
-37. Kaiser-Bunbury, C. N., Vázquez, D. P., Stang, M. \& Ghazoul, J. Determinants of the microstructure of plantPollinator networks. \emph{Ecology} \textbf{95}, 3314--3324 (2014).
+\hypertarget{ref-kaiser2014}{}
+37. Kaiser-Bunbury, C. N., Vázquez, D. P., Stang, M. \& Ghazoul, J.
+Determinants of the microstructure of plantPollinator networks.
+\emph{Ecology} \textbf{95}, 3314--3324 (2014).
 
-\leavevmode\hypertarget{ref-palmer2003}{}%
-38.
-Palmer, T.
-M., Stanton, M.
-L.
-\& Young, T.
-P.
-Competition and coexistence: Exploring mechanisms that restrict and maintain diversity within mutualist guilds.
-\emph{Am.
-Nat.} \textbf{162}, S63--S79 (2003).
+\hypertarget{ref-palmer2003}{}
+38. Palmer, T. M., Stanton, M. L. \& Young, T. P. Competition and
+coexistence: Exploring mechanisms that restrict and maintain diversity
+within mutualist guilds. \emph{Am. Nat.} \textbf{162}, S63--S79 (2003).
 
-\leavevmode\hypertarget{ref-phillips2020}{}%
-39. Phillips, R. D., Peakall, R., van der Niet, T. \& Johnson, S. D. Niche perspectives on plantPollinator interactions. \emph{Trends Plant Sci.} \textbf{25}, 779--793 (2020).
+\hypertarget{ref-phillips2020}{}
+39. Phillips, R. D., Peakall, R., van der Niet, T. \& Johnson, S. D.
+Niche perspectives on plantPollinator interactions. \emph{Trends Plant
+Sci.} \textbf{25}, 779--793 (2020).
 
-\leavevmode\hypertarget{ref-vazquez2007}{}%
-40. Vázquez, D. P. \emph{et al.} Species abundance and asymmetric interaction strength in ecological networks. \emph{Oikos} \textbf{116}, 1120--1127 (2007).
+\hypertarget{ref-vazquez2007}{}
+40. Vázquez, D. P. \emph{et al.} Species abundance and asymmetric
+interaction strength in ecological networks. \emph{Oikos} \textbf{116},
+1120--1127 (2007).
 
-\leavevmode\hypertarget{ref-encinas2012}{}%
-41. Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.} \textbf{15}, 198--208 (2012).
+\hypertarget{ref-encinas2012}{}
+41. Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives
+mutualistic network structure and diversity. \emph{Ecol. Lett.}
+\textbf{15}, 198--208 (2012).
 
-\leavevmode\hypertarget{ref-gervasi2017}{}%
-42. Gervasi, D. D. L. \& Schiestl, F. P. Real-time divergent evolution in plants driven by pollinators. \emph{Nat. Commun.} \textbf{8}, 14691 (2017).
+\hypertarget{ref-gervasi2017}{}
+42. Gervasi, D. D. L. \& Schiestl, F. P. Real-time divergent evolution
+in plants driven by pollinators. \emph{Nat. Commun.} \textbf{8}, 14691
+(2017).
 
-\leavevmode\hypertarget{ref-mackin2021}{}%
-43.
-Mackin, C.
-R., Peña, J.
-F., Blanco, M.
-A., Balfour, N.
-J.
-\& Castellanos, M.
-C.
-Rapid evolution of a floral trait following acquisition of novel pollinators.
-\emph{J.
-Ecol.} \textbf{109}, 2234--2246 (2021).
+\hypertarget{ref-mackin2021}{}
+43. Mackin, C. R., Peña, J. F., Blanco, M. A., Balfour, N. J. \&
+Castellanos, M. C. Rapid evolution of a floral trait following
+acquisition of novel pollinators. \emph{J. Ecol.} \textbf{109},
+2234--2246 (2021).
 
-\leavevmode\hypertarget{ref-poisot2021}{}%
-44. Poisot, T. \emph{et al.} Global knowledge gaps in species interaction networks data. \emph{J. Biogeogr.} \textbf{48}, 1552--1563 (2021).
+\hypertarget{ref-poisot2021}{}
+44. Poisot, T. \emph{et al.} Global knowledge gaps in species
+interaction networks data. \emph{J. Biogeogr.} \textbf{48}, 1552--1563
+(2021).
 
-\leavevmode\hypertarget{ref-fortuna2010}{}%
-45. Fortuna, M. A. \emph{et al.} Nestedness versus modularity in ecological networks: Two sides of the same coin? \emph{J. Anim. Ecol.} \textbf{79}, 811--817 (2010).
+\hypertarget{ref-fortuna2010}{}
+45. Fortuna, M. A. \emph{et al.} Nestedness versus modularity in
+ecological networks: Two sides of the same coin? \emph{J. Anim. Ecol.}
+\textbf{79}, 811--817 (2010).
 
-\leavevmode\hypertarget{ref-poisot2016}{}%
-46. Poisot, T. \emph{et al.} Mangal making ecological network analysis simple. \emph{Ecography} \textbf{39}, 384--390 (2016).
+\hypertarget{ref-poisot2016}{}
+46. Poisot, T. \emph{et al.} Mangal making ecological network analysis
+simple. \emph{Ecography} \textbf{39}, 384--390 (2016).
 
-\leavevmode\hypertarget{ref-chamberlain2020}{}%
-47. Chamberlain, S. \emph{et al.} \emph{Taxize: Taxonomic information from around the web. R package version 0.9.99}. (2020).
+\hypertarget{ref-chamberlain2020}{}
+47. Chamberlain, S. \emph{et al.} Taxize: Taxonomic information from
+around the web. r package version 0.9.99 (2020).~at
+\href{https://CRAN.R-project.org/package=taxize}{https://cran.R-project.org/package=taxize}.
 
-\leavevmode\hypertarget{ref-smith2018}{}%
-48. Smith, S. A. \& Brown, J. W. Constructing a broadly inclusive seed plant phylogeny. \emph{Am. J. Bot.} \textbf{105}, 302--314 (2018).
+\hypertarget{ref-smith2018}{}
+48. Smith, S. A. \& Brown, J. W. Constructing a broadly inclusive seed
+plant phylogeny. \emph{Am. J. Bot.} \textbf{105}, 302--314 (2018).
 
-\leavevmode\hypertarget{ref-jin2019}{}%
-49. Jin, Y. \& Qian, H. V.PhyloMaker: An R package that can generate very large phylogenies for vascular plants. \emph{Ecography} \textbf{42}, 1353--1359 (2019).
+\hypertarget{ref-jin2019}{}
+49. Jin, Y. \& Qian, H. V.PhyloMaker: An R package that can generate
+very large phylogenies for vascular plants. \emph{Ecography}
+\textbf{42}, 1353--1359 (2019).
 
-\leavevmode\hypertarget{ref-stekhoven2012}{}%
-50. Stekhoven, D. J. \& Bühlmann, P. MissForestNon-parametric missing value imputation for mixed-type data. \emph{Bioinformatics} \textbf{28}, 112--118 (2012).
+\hypertarget{ref-stekhoven2012}{}
+50. Stekhoven, D. J. \& Bühlmann, P. MissForestNon-parametric missing
+value imputation for mixed-type data. \emph{Bioinformatics} \textbf{28},
+112--118 (2012).
 
-\leavevmode\hypertarget{ref-penone2014}{}%
-51. Penone, C. \emph{et al.} Imputation of missing data in life-history trait datasets: Which approach performs the best? \emph{Methods Ecol. Evol.} \textbf{5}, 961--970 (2014).
+\hypertarget{ref-penone2014}{}
+51. Penone, C. \emph{et al.} Imputation of missing data in life-history
+trait datasets: Which approach performs the best? \emph{Methods Ecol.
+Evol.} \textbf{5}, 961--970 (2014).
 
-\leavevmode\hypertarget{ref-santos2018}{}%
-52. Santos, T., Diniz-Filho, J. A., e Luis, T. R., Bini, M. \& Santos, M. T. Package `PVR'. (2018).
+\hypertarget{ref-santos2018}{}
+52. Chamberlain, S. \emph{et al.} Package `PVR'. r package version 0.3
+(2018).~at
+\href{https://CRAN.R-project.org/package=PVR}{https://cran.R-project.org/package=PVR}.
 
-\leavevmode\hypertarget{ref-diniz-filho2012}{}%
-53. Diniz-Filho, J. A. F. \emph{et al.} On the selection of phylogenetic eigenvectors for ecological analyses. \emph{Ecography} \textbf{35}, 239--249 (2012).
+\hypertarget{ref-diniz-filho2012}{}
+53. Diniz-Filho, J. A. F. \emph{et al.} On the selection of phylogenetic
+eigenvectors for ecological analyses. \emph{Ecography} \textbf{35},
+239--249 (2012).
 
-\leavevmode\hypertarget{ref-legendre2012}{}%
-54. Legendre, P. \& Legendre, L. \emph{Numerical ecology}. (Elsevier, 2012).
+\hypertarget{ref-legendre2012}{}
+54. Legendre, P. \& Legendre, L. \emph{Numerical ecology}. (Elsevier,
+Amsterdam, 2012).
 
-\leavevmode\hypertarget{ref-revell2012}{}%
-55. Revell, L. J. Phytools: An R package for phylogenetic comparative biology (and other things). \emph{Methods Ecol. Evol.} \textbf{3}, 217--223 (2012).
+\hypertarget{ref-revell2012}{}
+55. Revell, L. J. Phytools: An R package for phylogenetic comparative
+biology (and other things). \emph{Methods Ecol. Evol.} \textbf{3},
+217--223 (2012).
 
-\leavevmode\hypertarget{ref-abdi2010}{}%
-56. Abdi, H. \& Williams, L. J. Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459 (2010).
+\hypertarget{ref-abdi2010}{}
+56. Abdi, H. \& Williams, L. J. Principal component analysis.
+\emph{WIREs Comp. Stats.} \textbf{2}, 433--459 (2010).
 
-\leavevmode\hypertarget{ref-ballantyne2015}{}%
-57.
-Ballantyne, G., Baldock, K.
-C.
-R.
-\& Willmer, P.
-G.
-Constructing more informative plantPollinator networks: Visitation and pollen deposition networks in a heathland plant community.
-\emph{Proc.
-Royal Soc.
-B} \textbf{282}, 20151130 (2015).
+\hypertarget{ref-ballantyne2015}{}
+57. Ballantyne, G., Baldock, K. C. R. \& Willmer, P. G. Constructing
+more informative plantPollinator networks: Visitation and pollen
+deposition networks in a heathland plant community. \emph{Proc. Royal
+Soc. B} \textbf{282}, 20151130 (2015).
 
-\leavevmode\hypertarget{ref-vazquez2005}{}%
-58. Vázquez, D. P., Morris, W. F. \& Jordano, P. Interaction frequency as a surrogate for the total effect of animal mutualists on plants. \emph{Ecol. Lett.} \textbf{8}, 1088--1094 (2005).
+\hypertarget{ref-vazquez2005}{}
+58. Vázquez, D. P., Morris, W. F. \& Jordano, P. Interaction frequency
+as a surrogate for the total effect of animal mutualists on plants.
+\emph{Ecol. Lett.} \textbf{8}, 1088--1094 (2005).
 
-\leavevmode\hypertarget{ref-vazquez2012}{}%
-59. Vázquez, D. P. \emph{et al.} The strength of plantPollinator interactions. \emph{Ecology} \textbf{93}, 719--725 (2012).
+\hypertarget{ref-vazquez2012}{}
+59. Vázquez, D. P. \emph{et al.} The strength of plantPollinator
+interactions. \emph{Ecology} \textbf{93}, 719--725 (2012).
 
-\leavevmode\hypertarget{ref-hung2018}{}%
-60.
-Hung, K.-L.
-J., Kingston, J.
-M., Albrecht, M., Holway, D.
-A.
-\& Kohn, J.
-R.
-The worldwide importance of honey bees as pollinators in natural habitats.
-\emph{Proc.
-Royal Soc.
-B} \textbf{285}, 20172140 (2018).
+\hypertarget{ref-hung2018}{}
+60. Hung, K.-L. J., Kingston, J. M., Albrecht, M., Holway, D. A. \&
+Kohn, J. R. The worldwide importance of honey bees as pollinators in
+natural habitats. \emph{Proc. Royal Soc. B} \textbf{285}, 20172140
+(2018).
 
-\leavevmode\hypertarget{ref-burkner2017}{}%
-61. Bürkner, P.-C. Brms: An R package for Bayesian multilevel models using Stan. \emph{J. Stat. Softw.} \textbf{80}, 1--28 (2017).
+\hypertarget{ref-burkner2017}{}
+61. Bürkner, P.-C. Brms: An R package for Bayesian multilevel models
+using Stan. \emph{J. Stat. Softw.} \textbf{80}, 1--28 (2017).
 
-\leavevmode\hypertarget{ref-gabry2019}{}%
-62. Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A. Visualization in Bayesian workflow. \emph{J. R. Stat. Soc. Ser. A Stat. Soc.} \textbf{182}, 389--402 (2019).
+\hypertarget{ref-gabry2019}{}
+62. Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A.
+Visualization in Bayesian workflow. \emph{J. R. Stat. Soc. Ser. A Stat.
+Soc.} \textbf{182}, 389--402 (2019).
 
-\leavevmode\hypertarget{ref-dormann2008}{}%
-63. Dormann, C. F., Gruber, B. \& Fründ, J. Introducing the bipartite package: Analysing ecological networks. \emph{interaction} \textbf{1}, (2008).
+\hypertarget{ref-dormann2008}{}
+63. Dormann, C. F., Gruber, B. \& Fründ, J. Introducing the bipartite
+package: Analysing ecological networks. \emph{interaction} \textbf{1},
+(2008).
 
-\leavevmode\hypertarget{ref-bluthgen2006}{}%
-64. Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in species interaction networks. \emph{BMC Ecol.} \textbf{6}, 9 (2006).
+\hypertarget{ref-bluthgen2006}{}
+64. Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in
+species interaction networks. \emph{BMC Ecol.} \textbf{6}, 9 (2006).
 
-\leavevmode\hypertarget{ref-therneau2015}{}%
-65. Therneau, T., Atkinson, B., Ripley, B. \& Ripley, M. B. Package `rpart'. \emph{Available online: cran. ma. ic. ac. uk/web/packages/rpart/rpart. pdf (accessed on 20 April 2016)} (2015).
+\hypertarget{ref-therneau2015}{}
+65. Therneau, T., Atkinson, B., Ripley, B. \& Ripley, M. B. Package
+`rpart'. r package version 4.1-15 (2015).~at
+\href{https://CRAN.R-project.org/package=rpart}{https://cran.R-project.org/package=rpart}.
 
-\leavevmode\hypertarget{ref-milborrow2015}{}%
-66. Milborrow, S. Rpart. Plot: Plot rpart Models. An Enhanced Version of plot. Rpart. \emph{R package version} \textbf{1}, (2015).
+\hypertarget{ref-milborrow2015}{}
+66. Milborrow, S. Rpart. plot: Plot rpart Models. An Enhanced Version of
+plot. rpart. r package version 3.0.9 (2015).~at
+\href{https://CRAN.R-project.org/package=rpart.plot}{https://cran.R-project.org/package=rpart.plot}.
 

### 2021-08-16 Supplementary_Material/Figure_Analysis_Bees_Apis_Non_Apis.Rmd
Preparing supplementary material
edits

@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
-  theme_ms() + theme(legend.position = "none")
+  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = "(a)")
 
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none")  + ggtitle(my_y_title_1)+
-  theme(plot.title = element_text(size = 36, face = "bold"))
+  theme_ms() + theme(legend.position = "none")  + 
+  theme(plot.title = element_text(size = 36, face = "bold"),plot.subtitle=element_text(size=30,face="bold"))+labs(title = my_y_title_1, subtitle = "(b)")
+
 #Plot nicely PC3
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
-  theme_ms() + theme(legend.position = "none")
+  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) +labs(title = "", subtitle = "(c)")
 
@@
       aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4")+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
-  theme_ms() + theme(legend.position = "none")
+  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = "(d)")
 
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none")  + ggtitle(my_y_title)+
-  theme(plot.title = element_text(size = 36, face = "bold"))
+  theme_ms() + theme(legend.position = "none")  +
+  theme(plot.title = element_text(size = 36, face = "bold"),plot.subtitle=element_text(size=30,face="bold"))+ labs(title = my_y_title, subtitle = "(e)")
 #Plot nicely PC3
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
-  theme_ms() + theme(legend.position = "none")
+  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = "(f)")
 
@@
 combined <- p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "right")
-combined + plot_layout(guides = "collect", ncol=3)
+combined <- combined + plot_layout(guides = "collect", ncol=3)
+
+saveRDS(combined, "Plot_apis.rds")
+
+combined
 

### 2021-08-16 Supplementary_Material/Supplementary_Material.Rmd
edits

@@
 ---
+title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant floral and reproductive traits determine interactions with floral visitors}
+
 output: 
@@
 - \usepackage{graphicx}
+- \usepackage{floatpag}
 
@@
 
-# Supporting information:
-
-__Authors:__ Jose B. Lanuza, Romina Rader, Jamie Stavert, Liam K. Kendall, Manu E. Saunders, Ignasi Bartomeus
-
-_The following Supporting Information is available for this article_:
-
-__Appendix S1.__ Brief description of the different traits and categories compiled in this study divided in reproductive, floral and vegetative traits.
-
-__Table S1.__ List of the 28 plant-pollinator studies used to build the plant trait database.
-
-__Table S2.__ Loadings of the first three principal components of the phylogenetic informed principal component analysis with all species.
-
-__Table S3.__ Loadings of the first three principal components of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.
-
-__Table S4.__ Statistical association of the different categorical variables to the principal components one and three from the pPPCA with the full set of species.
-
-__Table S5.__ Phylogenetic signal of the different quantitative traits.
-
-__Figure S1__ Percentage of present and missing values of the different variables.
-
-__Figure S2__ Phylogenetic informed principal component analysis for the species that did not have missing values.
-
-__Figure S3__ Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation.
-
-__Figure S4__ Regression tree comparison between the regression trees with the full set of species and with the subset of species with floral rewards.
-
-__Figure S5__ Trait relationship of PC1 and PC3 with the phylogenetic informed principal component analysis with the full set of species.
-
-__Figure S6__ Phylogenetic informed principal component analysis for the imputed dataset of the subset of species with quantitative information of nectar and pollen.
-
-__Figure S7__ Statistical comparison of the different categories of the categorical traits on the main two axes of trait variation (pPCA with the full set of species).
-
-__Figure S8__ Fitted posterior estimates of the number of visits made by the main functional groups of bees on the main axes of trait variation.
-
-__Figure S9__  Sum of visits per plant, normalized degree and specialization modelled in function of the first three main axes of trait variation.
-
-__Figure S10__ Pearson correlation between the product of flower number-flower size and autonomous selfing level.
+\singlespacing
+\vspace{-1.6cm}
+
+Jose B. Lanuza$^{1,2}*$, Romina Rader$^{1}$, Jamie Stavert$^{3}$, Liam K. Kendall$^{4}$, Manu E. Saunders$^{1}$ and Ignasi Bartomeus$^{2}$
+
+\vspace{-0.6cm}
+
+\section*{\hfil Supplementary information\hfil}
+
+# Contents:
+
+__Supplementary text__
+
+Description of the traits compiled in this study
+
+\doublespacing
+\singlespacing
+
+__Supplementary Tables__
+
+Supplementary Table S1: List of the 28 plant-pollinator studies used to build the plant trait database
+
+Supplementary Table S2: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species
+
+Supplementary Table S3: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity
+
+Supplementary Table S4: Statistical association between the different categorical variables and the fisrt three main axes of trait variation with the full set of species
+
+Supplementary Table S5: Phylogenetic signal of the different quantitative traits
+
+\doublespacing
+\singlespacing
+
+__Supplementary Figures__
+
+Supplementary Fig. S1: Percentage of present and missing values of the different traits
+
+Supplementary Fig. S2: Phylogenetic informed principal component analysis for the species that did not have missing values
+
+Supplementary Fig. S3: Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation
+
+Supplementary Fig. S4: Regression tree analyses
+
+Supplementary Fig. S5: PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species
+
+Supplementary Fig. S6: Phylogenetic informed principal component analysis for the subset of species with floral rewards.
+
+Supplementary Fig. S7: Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species
+
+Supplementary Fig. S8: Visitation rate of the main bee families on the main axes of trait variation
+
+Supplementary Fig. S9:  Plant species level metrics across the three main axes of trait variation
+
+Supplementary Fig. S10: Pearson correlation between the product of flower number-flower size and autonomous selfing level
 
@@
 
-__Appendix S1__
-
-Brief description of the different traits and categories compiled in this study divided in reproductive, floral and vegetative traits.
+__Description of the traits compiled in this study__
 
@@
 In addition, quantitative data was also divided into these four categories with the following criteria: from 0% to lower than 1% ‘none’, from 1% to 25% ‘low’, from 26% to 75% ‘medium’ and from 76% to 100%  ‘high’.
-We opted for the metric of autonomous selfing because it was the most abundant one in the literature and more complex metrics that were more informative were scarce.
 
@@
 We divided the flowers in 8 main different categories: open, tube, campanulate, funnelform, papilionaceous, spike and capitulum.
-See image X for the different flower morphologies.
 
@@
 kable("latex", longtable = T, booktabs = T,linesep = "\\addlinespace",
-             caption = "\\textbf{Table S1.} List of the 28 plant-pollinator studies used to build the plant trait database.
-Each study is shown with the first author that conducted the study, number of networks or metawebs that contains, type of information that contains (weighted or unweighted),  the structure (web or metaweb), year of publication and digital object identifier or permanent link for each study.") %>%
+             caption = "\\textbf{Supplementary Table S1 | List of the 28 plant-pollinator studies used to build the plant trait database.} Each study is shown with the first author that conducted the study, number of networks or metawebs that contains, type of information that contains (weighted or unweighted),  the structure (web or metaweb), year of publication and digital object identifier or permanent link for each study.") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, repeat_header_method="replace" ,full_width=F,position = "left")
@@
 
- kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S2.} Loadings and explained variance of the first three principal components from the phylogenetically informed principal component analysis with the full set of species after outlier processing (N = 1,236).") %>%
+ kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Supplementary Table S2 | Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species.}") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
@@
 
-kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S3.} Loadings and explained variance of the first three principal components from the phylogenetically informed principal component analysis for the subset of species with quantitative information of nectar and pollen.") %>%
+kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Supplementary Table S3 | Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.}") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
@@
 
-kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Table S4.} Statistical association of the different categorical variables to the first two principal components from the pPPCA with the full set of species.
-For each categorical trait and principal component, sum of squares, F-value and P-value are provided.") %>%
+kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Supplementary Table S4 | Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species.}") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
@@
 
-kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,caption = "\\textbf{Table S5.} Phylogenetic signal for all quantitative traits.
-Phylogenetic signal of nectar and pollen traits was calculated for the imputed dataset of the subset of species with quantitative information of nectar and pollen.") %>%
+kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,caption = "\\textbf{Supplementary Table S5 | Phylogenetic signal of the different quantitative traits.}") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Fig S1.}  Percentage of present and missing values on the 20 traits compiled in this study (N = 1,506 species)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Supplementary Fig. S1 | Percentage of present and missing values of the different traits.}"}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig S2.} Phylogenetic informed principal component analysis for the species that did not have missing values (non-imputed dataset; N = 723)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Supplementary Fig.
+S2 |  Phylogenetic informed principal component analysis for the species that did not have missing values.}"}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28,  fig.cap="\\textbf{Fig S3.} Fitted posterior estimates of the number of visits made by the functional group of Hymenoptera-Anthophila (bees) including (superior panel) and excluding (lower panel) *Apis mellifera* in relation to the main axes of trait variation (PC, PC2 and PC3)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28,  fig.cap="\\textbf{Supplementary Fig.
+S3 | Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation.} The superior (plots a, b and c) and lower (plots d, e and f) panels show visitation rates on the main axes of trait variation with and without \\emph{Apis mellifera}, respectively."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig S4.} Comparison of the regression tree analysis between the full set of species and the subset of species with floral rewards for each plant species level metric (interaction frequency, nomalized degree and specialization)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Supplementary Fig.
+S4 | Regression tree analyses.} Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
+"}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig S5.} Phylogenetically informed principal component analysis showing the trait relationship with principal components one and three (PC1 and PC3) for the full set of species (N = 1,506)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Supplementary Fig.
+S5 | PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species.}"}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig S6.} First two main principal components from the phylogenetic informed principal component analysis for the imputed dataset of the subset of species with quantitative information of nectar and pollen (N = 467)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Supplementary Fig.
+S6 | Phylogenetic informed principal component analysis for the subset of species with floral rewards.}"}
 setwd("~/R_Projects/Reproductive Traits")
@@
 \newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig S7.} Statistical comparison of the different categories of the categorical traits on the main two axes of trait variation (pPCA with the full set of species).
-Categories that differ significantly are denoted with a different letter."}
+\thispagestyle{empty}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Supplementary Fig.
+S7 | Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species.} Categories that differ significantly are denoted with a different letter."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="\\textbf{Fig S8.} Fitted posterior estimates of the number of visits made by the different main visiting families of bees (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) in relation to the main axes of trait variation (PC1, PC2 and PC3).
-We omitted in the plotting points over percentile 95 \\% percent due to extreme outliers."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="\\textbf{Supplementary Fig.
+S8 | Visitation rate of the main bee families on the main axes of trait variation.} Fitted posterior estimates of the visitation rate of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
+We omitted in the plotting area points over percentile 95 \\% percent due to extreme outliers."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig S9.} Sum of visits per plant, normalized degree and speciliazation modelled in function of the first three main axes of trait variation.", fig.pos= "h"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Supplementary Fig.
+S9 | Plant species level metrics across the three main axes of trait variation.}", fig.pos= "h"}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig S10.} Pearson correlation between the product of flower number-flower size and autonomous selfing level.", fig.pos= "h"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Supplementary Fig.
+S10 | Pearson correlation between the product of flower number-flower size and autonomous selfing level.}", fig.pos= "h"}
 

### 2021-08-16 Supplementary_Material/Supplementary_Material_LK.Rmd
proof-reading LK

--- 2021-08-16 Supplementary_Material/Supplementary_Material.Rmd
@@
 
-Supplementary Table S2: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species
-
-Supplementary Table S3: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity
-
-Supplementary Table S4: Statistical association between the different categorical variables and the fisrt three main axes of trait variation with the full set of species
+Supplementary Table S2: Loadings of the first three axes of trait variation of the phylogenetically informed principal component analysis with the full set of species
+
+Supplementary Table S3: Loadings of the first three axes of trait variation of the phylogenetically informed principal component analysis with the subset of species with data of nectar and pollen quantity
+
+Supplementary Table S4: Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species
 
@@
 
-Supplementary Fig. S2: Phylogenetic informed principal component analysis for the species that did not have missing values
-
-Supplementary Fig. S3: Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation
+Supplementary Fig. S2: Phylogenetically informed principal component analysis for the species that did not have missing values
+
+Supplementary Fig. S3: Fitted posterior estimates of the number of visits made by bees including and excluding honey bees on the main axes of trait variation
 
@@
 
-Supplementary Fig. S6: Phylogenetic informed principal component analysis for the subset of species with floral rewards.
+Supplementary Fig. S6: Phylogenetically informed principal component analysis for the subset of species with floral rewards.
 
@@
 
-Supplementary Fig. S8: Visitation rate of the main bee families on the main axes of trait variation
+Supplementary Fig. S8: Visitation rate of the main bee families in relation to the main axes of trait variation
 
@@
 -	Selfing level: We recorded the selfing level of the different species with both quantitative and qualitative data.
-The qualitative data was divided in four main categories, high selfers, medium selfers, low selfers and none which was for the species that were unable to self-pollinate.
-In addition, quantitative data was also divided into these four categories with the following criteria: from 0% to lower than 1% ‘none’, from 1% to 25% ‘low’, from 26% to 75% ‘medium’ and from 76% to 100%  ‘high’.
+The qualitative data were divided in four main categories, high selfers, medium selfers, low selfers and none which was for the species that were unable to self-pollinate.
+In addition, quantitative data were also divided into these four categories with the following criteria: from 0% to lower than 1% ‘none’, from 1% to 25% ‘low’, from 26% to 75% ‘medium’ and from 76% to 100%  ‘high’.
 
@@
 -	Flower and inflorescence size: We searched for flower length and flower and inflorescence width (mm) for all species.
-When possible, we calculated the not found measurements with the help of online images and  the software ImageJ.
+When possible, we measured this trait with the help of online images and the software ImageJ.
 
@@
 We referenced all the filled fields in order to be able to follow the images that were used for these counts.
-It is important to note, that these numbers are not pretended to be the exact number of flowers per species but an approximate indicator of the reproductive investment for the different species that allow the macroecological analysis of this field.
-
--	Ovule number: We searched for the number of ovules per flower for all the different species.
+It is important to note, that these numbers are not predicted to be the exact number of flowers per plant in each species but an approximate indicator of the reproductive investment in each species that will allow for its use in macroecological analysis.
+
+-	Ovule number: We searched for the number of ovules per flower for all species.
 The number of ovules of Asteraceae species are considered as the total number of ovules per capitulum.
-Many species were filled by genus or family level because the number of ovules in this taxonomic groups is considered to be mostly constant (e.g., Lamiaceae Boraginaceae or Apiaceae).
-
--	Style length: The length of the style (mm) of the different species was also included. When possible, we calculated style length from images and illustrations on the online floras.
+Many species were filled at either the genus or family level because the number of ovules in this taxonomic groups is considered to be mostly constant (e.g., Lamiaceae, Boraginaceae, or Apiaceae).
+
+-	Style length: The length of the style (mm) of the different species. When possible, we calculated style length from online images and illustrations.
 
@@
 In general terms, nectar data was rarely present and we try to minimise the loss of information by filling some species at family level.
-For instance, Solanaceae species are described as nectarless, and species that belonged to this family were recorded with ‘absence’ of nectar.
+For instance, Solanaceae species are described as nectarless.
+Therefore, all Solanaceae species were recorded with having an ‘absence’ of nectar.
 
 - Pollen grains per flower: We recorded pollen grains per flower for all species but this field was rarely described in the literature.
-When just the pollen:ovule ratio was found we converted it back to pollen grains by multiplying by ovule number.
+When we could only find the pollen:ovule ratio, we converted it back to pollen grains by multiplying by ovule number.
 
@@
 Finally, we also searched for the average height (m) of the different species and annotated the maximum and minimum height when possible.
-We conducted the average between the maximum and minimum height to get an approximate average height of the species when the average was not indicated.
+We calculated the average between the maximum and minimum height to get an approximate average height of the species when the average was not indicated.
 
@@
 
- kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Supplementary Table S2 | Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species.}") %>%
+ kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Supplementary Table S2 | Loadings of the first three axes of trait variation of the phylogenetically informed principal component analysis with the full set of species.}") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
@@
 
-kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Supplementary Table S3 | Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.}") %>%
+kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Supplementary Table S3 | Loadings of the first three axes of trait variation of the phylogenetically informed principal component analysis with the subset of species with data of nectar and pollen quantity.}") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Supplementary Fig.
-S2 |  Phylogenetic informed principal component analysis for the species that did not have missing values.}"}
+S2 |  Phylogenetically informed principal component analysis for the species that did not have missing values.}"}
 setwd("~/R_Projects/Reproductive Traits")
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Supplementary Fig.
-S6 | Phylogenetic informed principal component analysis for the subset of species with floral rewards.}"}
+S6 | Phylogenetically informed principal component analysis for the subset of species with floral rewards.}"}
 setwd("~/R_Projects/Reproductive Traits")
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="\\textbf{Supplementary Fig.
-S8 | Visitation rate of the main bee families on the main axes of trait variation.} Fitted posterior estimates of the visitation rate of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
+S8 | Visitation rate of the main bee families in relation to the main axes of trait variation.} Fitted posterior estimates of the visitation rate of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
 We omitted in the plotting area points over percentile 95 \\% percent due to extreme outliers."}

### 2021-08-16 Supplementary_Material/Supplementary_Material.Rmd
Some additions to supp mat

@@
 -	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape.
-We divided the flowers in 8 main different categories: open, tube, campanulate, funnelform, papilionaceous, spike and capitulum.
+We divided the flowers in 8 main different categories: open, bowl, tube, campanulate, funnelform, papilionaceous, brush and capitulum.
+Finally, because some of the flower shapes were rare in our dataset, we grouped them within the closest flower morphologies (e.g., bowl shape was included within in the open shape).
+Thus, we ended with 6 distinct morphological groups for analyses: tube, papilonaceous, open, capitulum, campanulate and brush (see scheme of the different flower morphologies below).
 

### 2021-08-23 Supplementary_Material/Supplementary_Material.Rmd
Figure of flower morphologies added to supplementary text

--- 2021-08-16 Supplementary_Material/Supplementary_Material.Rmd
@@
 
-Description of the traits compiled in this study
+Description of the traits compiled in this study with an illustrative figure of the main flower morphologies (Supplementary text Fig 1)
 
@@
 _Floral traits_
-
--	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape.
-We divided the flowers in 8 main different categories: open, tube, campanulate, funnelform, papilionaceous, spike and capitulum.
 
@@
 Many species were filled by genus or family level because the number of ovules in this taxonomic groups is considered to be mostly constant (e.g., Lamiaceae Boraginaceae or Apiaceae).
+
+-	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape.
+We divided the flowers in 8 main different categories: open, bowl, tube, campanulate, funnelform, papilionaceous, brush and capitulum.
+However, we ended up groupping all flowers on the following 6  morphological groups for analyses: tube, papilonaceous, open, capitulum, campanulate and brush (Supplementary text Fig.
+1).
+
+```{r pressure, echo=FALSE, fig.cap="", out.width = '65%',fig.align='center', fig.cap="\\textbf{Supplementary text Fig.
+1 | Main floral morphologies considered in this study.} All species were groupped within these categories for analysis: tube (a), papilonaceous (b), open (c), capitulum (d), campanulate (e) and brush (f)."}
+knitr::include_graphics("../Images/flower_shapes.png")
+```
 

### 2021-09-15 Main_Figures/Figure3.Rmd
Ddding presence absence model to ms

---
output:
  pdf_document: default
  html_document: default
classoption: landscape

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap= "**Fig. 3 | Visitation rates across the three main axes of trait variation.** Fitted posterior estimates of the number of visits made by the different floral visitors guilds in relation to PC1, PC2 and PC3. Bees (a, b and c) and the rest of guilds (d, e and f) were plotted separately for visualization purposes. In addition, we trimmed the plotting area that was over the 95th percentile to improve visualisation. PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off."}

#LOAD LIBRARIES 
#library(phytools)
#library(ape) #for phylogenetic distance
#library(dplyr) #data processing
#library(rtrees) #for phylogenetic distancelibrary(MASS)
#library(reshape2)
library(viridis) #COLOUR GGPLOT
#library(MASS)
library(ggplot2)
library(broman) #crayon colours
#library(tidyverse)
library(patchwork) #panel of plots
library(brms)
library(cmdstanr)

#Load theme for publication

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2)),
           axis.text=element_text(size = rel(1.8), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.4)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(1.8, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank(),
           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
           plot.subtitle = element_text(face="bold",size=rel(2))
     ))
}

#decimal places for ggplot

scaleFUN <- function(x) sprintf("%.1f", x)

#Prepare plot with presence absence and interaction frequency
setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
#Plot nicely PC1
analysis_1 <- readRDS("results_analysis_1_presence_absence.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_presence_absence.rds")

ce_pc1 <- conditional_effects(analysis_1, effects = "PC1:guild",points=T)

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:guild",points=T)

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

ce_pc3 <- conditional_effects(analysis_1, effects = "PC3:guild",points=T)

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
 aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
#Plot nicely PC1
analysis_1 <- readRDS("results_analysis_1.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1.rds")
########################################################################################################################

########################################################################################################################
ce_pc1 <- conditional_effects(analysis_1, effects = "PC1:guild",points=T)

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+
  scale_y_log10()+ggtitle("(d)")
#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:guild",points=T)

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", 
  "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10()+ggtitle("(e)")

#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1, effects = "PC3:guild",points=T)

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles\n Low selfing    High selfing")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold"))+ 
  scale_color_manual(name="Functional groups",values=c("orange", 
  "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ scale_y_log10()+ggtitle("(f)")

combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
combined + plot_layout(guides = "collect",ncol = 3)

setwd("~/R_Projects/Reproductive Traits")

saveRDS(p1,"Main_Figures/figure_3_1.rds")
saveRDS(p2,"Main_Figures/figure_3_2.rds")
saveRDS(p3,"Main_Figures/figure_3_3.rds")
saveRDS(pp1,"Main_Figures/figure_3_4.rds")
saveRDS(pp2,"Main_Figures/figure_3_5.rds")
saveRDS(pp3,"Main_Figures/figure_3_6.rds")

```

### 2021-09-15 Manuscript/Manuscript.Rmd
Ddding presence absence model to ms

@@
 ---
-title: \singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant floral and reproductive traits determine interactions with floral visitors
+title: \singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors
 
@@
 First, we identify the major axes of floral and reproductive trait variation and trade-offs that determine plant form and function.
-Second, we investigate how plant species’ position in trait-space influences interaction strength with different guilds of floral visitors.
-Finally, we investigate how the main axes of trait variation and individual traits influence plant species roles within networks using complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
+Second, we investigate how plant species’ position in trait-space influences their interaction strength with different guilds of floral visitors.
+Finally, we investigate how the main axes of trait variation and individual traits influence plant species roles within networks.
 
@@
 The first principal component (PC1) represented 26.72% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the ‘flower number - flower size trade-off’ as already described in previous studies [@sargent2007; @kettle2011].
+We refer to this axis as the ‘flower number - flower size trade-off’, as already described in previous studies [@sargent2007; @kettle2011].
 Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,fig.pos = "t",fig.cap= "**Fig.
-1 | Plant life-history strategies.** Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator networks studies.
+1 | Plant life-history strategies.** Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
 The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
-The length of the arrows indicate the weight of the variables on each principal component and the labelled icons at their end represent the extreme form of the trait continuum.
-The dashed lines show the opposed direction of trait variation and the non-labelled icons at their end illustrate the opposing extreme of the continuum."}
+The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation.
+The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}
 
@@
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, _P_ < 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , _P_ = 0.59; PC2:  Sum of squares = 0.83, F-value = 1.43, _P_ = 0.23) showed lack of statistical association.
-In addition, we found with Tukey test statistical differences between the different levels of categorical traits in the trait space (Supplementary Fig.
+In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Supplementary Fig.
 S7).
-Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatibile were statistically differentiated from species with partial or full self compatibility; Supplementary Fig.
+Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Supplementary Fig.
 S7a and Fig.
@@
 
-**Visitation patterns.** The main axes of trait variation explained little of the overall visitation rates ($conditional R2 = 0.31$; $marginal R2 = 0.06$) but showed relevant trends when we explored the interaction with the different floral visitors guilds (Fig.
+**Visitation patterns.** The main axes of trait variation explained little of the overall visitation rates ($conditional R2 = 0.31$; $marginal R2 = 0.06$) but showed relevant trends when we explored the interaction with the different floral visitor guilds (Fig.
 3).
-All floral visitors guilds visited plant species with higher pollinator dependence more frequently (PC2; Fig.
+All floral visitor guilds visited plant species with higher pollinator dependence more frequently (PC2; Fig.
 3b and Fig.
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap= "**Fig.
-3 | Visitation rates across the three main axes of trait variation.** Fitted posterior estimates of the number of visits made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
-Bees (a, b and c) and the rest of guilds (d, e and f) were plotted separately for visualization purposes.
-In addition, we trimmed the plotting area that was over the 95th percentile to improve visualisation.
+3 | Interaction (yes/no) and visitation rates across the three main axes of trait variation per floral visitor guild.** Fitted posterior estimates of the presence/absence of interaction (a, b and c) and number of visits (d, e and f) made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
 PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off."}
@@
 
-p1 <- readRDS("Main_Figures/figure_2_1.rds")
-p2 <- readRDS("Main_Figures/figure_2_2.rds")
-p3 <- readRDS("Main_Figures/figure_2_3.rds")
-pp1 <- readRDS("Main_Figures/figure_2_4.rds")
-pp2 <- readRDS("Main_Figures/figure_2_5.rds")
-pp3 <- readRDS("Main_Figures/figure_2_6.rds")
+p1 <- readRDS("Main_Figures/figure_3_1.rds")
+p2 <- readRDS("Main_Figures/figure_3_2.rds")
+p3 <- readRDS("Main_Figures/figure_3_3.rds")
+pp1 <- readRDS("Main_Figures/figure_3_4.rds")
+pp2 <- readRDS("Main_Figures/figure_3_5.rds")
+pp3 <- readRDS("Main_Figures/figure_3_6.rds")
 
@@
 
-combined <- p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "bottom")
+combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
 combined + plot_layout(guides = "collect",ncol = 3)
@@
 
-**Plant species functional roles.** The variance of the different plant species level metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
+**Plant species functional roles.** The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
 S9; interaction frequency ~ PCs, $conditional R2 = 0.11$, $marginal R2 = 0.02$; normalized degree ~ PCs, $conditional R2 = 0.24$, $marginal R2 = 0.02$; and, specialization ~ PCs, $conditional R2 = 0.37$, $marginal R2 = 0.03$).
@@
 These trade-offs are differentiated on three main axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-Although these axes of trait variation did not explain overall visitation rates, we found that plant life strategies were clearly associated with different floral visitors guilds.
+Although these axes of trait variation did not explain overall visitation rates, we found that plant life strategies were clearly associated with different floral visitor guilds.
 Interestingly, pollen and nectar related traits were better than all other traits for characterizing plant species functional roles within their interaction networks.
@@
 This allowed us to identify the major reproductive strategies of flowering plants and how plant life strategies determine their interaction with floral visitor guilds.
-Although the percentage of explained variation found with the first two axes (~50%) is lower than other studies that have evaluated life histories with vegetative traits [@diaz2016; @carmona2021], this percentage is consistent with the largest and most recent study that have characterized life strategies with both vegetative and reproductive (i.e., semelparity and iteroparity) traits [@salguero2016].
-Future work needs to integrate these floral and reproductive compromises with the already described vegetative and physiological trade-offs [@diaz2016] to create a more comprehensive spectra of trait variation [@roddy2021].
+Although the percentage of explained variation found with the first two axes (~50%) is lower than other studies that have evaluated life histories with vegetative traits [@diaz2016; @carmona2021], this percentage is consistent with the largest and most recent study that has characterized life strategies with both vegetative and reproductive (i.e., semelparity and iteroparity) traits [@salguero2016].
+Future work needs to integrate these floral and reproductive compromises with the already described vegetative and physiological trade-offs [@diaz2016] to create a more comprehensive spectrum of trait variation [@roddy2021].
 Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators [@gervasi2017; @mackin2021].
@@
 
-**Networks analyses.** Analyses were conducted on the subset of 60 weighted networks with interaction frequency sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+**Network analyses.** Analyses were conducted on the subset of 60 weighted networks with interaction frequency sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
 In total, our weighted network dataset (excluding meta-webs) included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-Anthophila-Hymenoptera interactions.
@@
 
-**Visitation patterns.** We used Bayesian modelling (see below for details) to explore the effect of floral visitors groups and the main axes of trait variation (pPCA with imputed dataset) on floral visits per plant species.
+**Visitation patterns.** We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on floral visits per plant species.
 For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.

### 2021-09-15 Manuscript/Manuscript.tex
Ddding presence absence model to ms

@@
 \hypersetup{
-            pdftitle={ Trade-offs among plant floral and reproductive traits determine interactions with floral visitors},
+            pdftitle={ Trade-offs among plant reproductive traits determine interactions with floral visitors},
             colorlinks=true,
@@
 
-\title{\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant floral and
+\title{\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant
 reproductive traits determine interactions with floral visitors}
@@
 form and function. Second, we investigate how plant species' position in
-trait-space influences interaction strength with different guilds of
-floral visitors. Finally, we investigate how the main axes of trait
+trait-space influences their interaction strength with different guilds
+of floral visitors. Finally, we investigate how the main axes of trait
 variation and individual traits influence plant species roles within
-networks using complementary interaction network metrics (i.e.,
-interaction strength, normalized degree and specialization).
+networks.
 
@@
 flower size. We refer to this axis as the `flower number - flower size
-trade-off' as already described in previous
+trade-off', as already described in previous
 studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{32},\protect\hyperlink{ref-kettle2011}{33}}.
@@
 life-history strategies.} Phylogenetically informed principal component
-analysis (pPCA) of 1,236 plant species from 28 plant-pollinator networks
+analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network
 studies. The solid arrows indicate the direction of the different
@@
 axes of trait variation. The length of the arrows indicate the weight of
-the variables on each principal component and the labelled icons at
-their end represent the extreme form of the trait continuum. The dashed
-lines show the opposed direction of trait variation and the non-labelled
-icons at their end illustrate the opposing extreme of the continuum.}
+the variables on each principal component and the dashed lines show the
+opposed direction of trait variation. The icons at both ends of arrows
+and dashed lines illustrate the extreme form of the trait continuum.}
 \end{figure}
@@
 F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
-In addition, we found with Tukey test statistical differences between
-the different levels of categorical traits in the trait space
+In addition, we found (with a Tukey test) statistical differences
+between the different levels of categorical traits in the trait space
 (Supplementary Fig. S7). Regarding self compatibility, we found larger
 differences on PC2 (i.e., species with unisexual flowers that were self
-incompatibile were statistically differentiated from species with
-partial or full self compatibility; Supplementary Fig. S7a and Fig.
-S7b). Life forms differed statistically across both axes of trait
-variation and followed a gradient of larger life forms (trees and
-shrubs) with higher pollinator dependence to smaller ones (herbs) with
-lower pollinator dependence (Supplementary Fig. S7c and Fig. S7d).
-Consequently, lifespan also followed this gradient but perennial and
-short lived species only differed statistically on PC2 (Supplementary
-Fig. S7e and Fig. S7f). Species with unisexual flowers (monoecious and
-dioecious) were clustered on both extremes of the first two principal
-components and had the highest pollinator dependence and highest number
-of flowers (Supplementary Fig. S7g and Fig. S7h). Moreover, we found
-that the campanulate and capitulum flower shapes were differentiated
-from tube, papilionaceous, open and brush shapes in the trait space. The
-former morphologies had larger flowers and greater pollinator
-dependence, while the latter had higher flower number and greater
-autonomous selfing (Supplementary Fig. S7i and Fig. S7j). Regarding
-flower symmetry, zygomorphic flowers were associated with lower levels
-of pollinator dependence, whereas actinomorphic flowers had higher
-levels of pollinator dependence (Supplementary Fig. S7k and Fig. S7l).
+incompatible were statistically differentiated from species with partial
+or full self compatibility; Supplementary Fig. S7a and Fig. S7b). Life
+forms differed statistically across both axes of trait variation and
+followed a gradient of larger life forms (trees and shrubs) with higher
+pollinator dependence to smaller ones (herbs) with lower pollinator
+dependence (Supplementary Fig. S7c and Fig. S7d). Consequently, lifespan
+also followed this gradient but perennial and short lived species only
+differed statistically on PC2 (Supplementary Fig. S7e and Fig. S7f).
+Species with unisexual flowers (monoecious and dioecious) were clustered
+on both extremes of the first two principal components and had the
+highest pollinator dependence and highest number of flowers
+(Supplementary Fig. S7g and Fig. S7h). Moreover, we found that the
+campanulate and capitulum flower shapes were differentiated from tube,
+papilionaceous, open and brush shapes in the trait space. The former
+morphologies had larger flowers and greater pollinator dependence, while
+the latter had higher flower number and greater autonomous selfing
+(Supplementary Fig. S7i and Fig. S7j). Regarding flower symmetry,
+zygomorphic flowers were associated with lower levels of pollinator
+dependence, whereas actinomorphic flowers had higher levels of
+pollinator dependence (Supplementary Fig. S7k and Fig. S7l).
 
@@
 \(marginal R2 = 0.06\)) but showed relevant trends when we explored the
-interaction with the different floral visitors guilds (Fig. 3). All
-floral visitors guilds visited plant species with higher pollinator
+interaction with the different floral visitor guilds (Fig. 3). All
+floral visitor guilds visited plant species with higher pollinator
 dependence more frequently (PC2; Fig. 3b and Fig. 3e). In addition, all
@@
 \includegraphics{output/figures/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}\textbf{Fig. 3 \textbar{} Visitation
-rates across the three main axes of trait variation.} Fitted posterior
-estimates of the number of visits made by the different floral visitors
-guilds in relation to PC1, PC2 and PC3. Bees (a, b and c) and the rest
-of guilds (d, e and f) were plotted separately for visualization
-purposes. In addition, we trimmed the plotting area that was over the
-95th percentile to improve visualisation. PC1 represents the flower
-number - flower size trade-off, PC2 represents the pollinator dependence
-trade-off and PC3, the style length trade-off.}
+\caption{\label{fig:unnamed-chunk-3}\textbf{Fig. 3 \textbar{} Interaction
+(yes/no) and visitation rates across the three main axes of trait
+variation per floral visitor guild.} Fitted posterior estimates of the
+presence/absence of interaction (a, b and c) and number of visits (d, e
+and f) made by the different floral visitors guilds in relation to PC1,
+PC2 and PC3. PC1 represents the flower number - flower size trade-off,
+PC2 represents the pollinator dependence trade-off and PC3, the style
+length trade-off.}
 \end{figure}
@@
 \textbf{Plant species functional roles.} The variance of the different
-plant species level metrics was poorly explained by the three main axes
-of trait variation (Supplementary Fig. S9; interaction frequency
-\textasciitilde{} PCs, \(conditional R2 = 0.11\),
+plant species-level network metrics was poorly explained by the three
+main axes of trait variation (Supplementary Fig. S9; interaction
+frequency \textasciitilde{} PCs, \(conditional R2 = 0.11\),
 \(marginal R2 = 0.02\); normalized degree \textasciitilde{} PCs,
@@
 visitation rates, we found that plant life strategies were clearly
-associated with different floral visitors guilds. Interestingly, pollen
+associated with different floral visitor guilds. Interestingly, pollen
 and nectar related traits were better than all other traits for
@@
 this percentage is consistent with the largest and most recent study
-that have characterized life strategies with both vegetative and
+that has characterized life strategies with both vegetative and
 reproductive (i.e., semelparity and iteroparity)
@@
 trade-offs\textsuperscript{\protect\hyperlink{ref-diaz2016}{18}} to
-create a more comprehensive spectra of trait
+create a more comprehensive spectrum of trait
 variation\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}}.
@@
 
-\textbf{Networks analyses.} Analyses were conducted on the subset of 60
+\textbf{Network analyses.} Analyses were conducted on the subset of 60
 weighted networks with interaction frequency sampled in a unique
@@
 \textbf{Visitation patterns.} We used Bayesian modelling (see below for
-details) to explore the effect of floral visitors groups and the main
+details) to explore the effect of floral visitor groups and the main
 axes of trait variation (pPCA with imputed dataset) on floral visits per

### 2021-09-15 Scripts/5_Analysis_Presence_Absesence_PCs.R

@@ -152,7 +152,10 @@ pp_check(analysis_1, type='violin_grouped',group="guild")+ylim(-4,4)
 setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
 saveRDS(analysis_1, "results_analysis_1_presence_absence.rds")
 saveRDS(dat_analysis, "dat_analysis_results_analysis_presence_absence.rds")
-##############
+################################################################################################################
+#Plot nicely PC1
+analysis_1 <- readRDS("results_analysis_1_presence_absence.rds")
+dat_analysis <- readRDS("dat_analysis_results_analysis_presence_absence.rds")
 
 ce_pc1 <- conditional_effects(analysis_1, effects = "PC1:guild",points=T) 
 

### 2021-09-16 Manuscript/Manuscript.Rmd
wording edit from reproductive to reproductive biology;
and

describing new model with prsence absence. Now I have to redo analysis of supp. mat to match all analyses

@@
 
-__Plant life strategies are often delimited by vegetative and physiological traits but little is known about how floral and reproductive traits drive these strategies, and in turn shape plant interactions with floral visitors.
-Here, we compiled 13 floral, 4 reproductive and 3 vegetative traits for 1,506 plant species from 28 plant-pollinator network studies across 18 different countries.
+__Plant life strategies are often delimited by vegetative and physiological traits but little is known about how floral and reproductive biology traits drive these strategies, and in turn shape plant interactions with floral visitors.
+Here, we compiled 13 floral, 4 reproductive biology and 3 vegetative traits for 1,506 plant species from 28 plant-pollinator network studies across 18 different countries.
 We investigated the associations among these traits, pollinator visitation and the functional role of plant species within the networks (interaction frequency, normalized degree and specialization).
@@
 There is an astonishing diversity of floral structures and plant reproductive strategies among flowering plants [@barrett2002; @schiestl2013], which have long been of interest to pollination biologists in terms of their relevance to plant-pollinator interactions.
-However, most studies that have explored reproductive (e.g., mating and compatibility systems) and floral trait (e.g., flower size or nectar provision) variation have concentrated on the individual or community level and thus, broader macroecological patterns remain poorly investigated [@carvalheiro2014; @baude2016; @munoz2016; @moeller2017; @grossenbacher2017].
-Indeed, studies depicting species’ life history strategies generally focus on vegetative traits and rarely consider reproductive traits [@salguero2016, @ruger2018].
+However, most studies that have explored plant reproductive biology (e.g., mating and compatibility systems) and floral trait (e.g., flower size or nectar provision) variation have concentrated on the individual or community level and thus, broader macroecological patterns remain poorly investigated [@carvalheiro2014; @baude2016; @munoz2016; @moeller2017; @grossenbacher2017].
+Indeed, studies depicting species’ life history strategies generally focus on vegetative traits and rarely consider reproductive biology traits [@salguero2016, @ruger2018].
 As a consequence, a unified framework that explores the compromises among floral traits and their relevance to plant life strategies is currently lacking [@roddy2021].
@@
   With the recent availability of large trait databases, plant ecological strategies are increasingly being examined [e.g., TRY; @kattge2011 and COMPADRE; @salguero2015], and are facilitating the identification of global patterns and constraints of plant form and function [@salguero2016; @diaz2016; @carmona2021].
-However, the main focus has been on vegetative traits such as leaf [@wright2004] or wood [@chave2009] trade-offs with little or no attention given to reproductive and floral traits [@evojtko2020], also critical to plant form and function.
+However, the main focus has been on vegetative traits such as leaf [@wright2004] or wood [@chave2009] trade-offs with little or no attention given to reproductive biology and floral traits [@evojtko2020], also critical to plant form and function.
 For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively [@barrett2003; @moeller2017].
@@
 In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and their role in attracting pollinators [@ollerton2011].
-Hence, exploring plant life strategies with reproductive and floral trade-offs, in conjunction with their pollinator dependence, is necessary for a balanced understanding of plant economics.
+Hence, exploring plant life strategies with reproductive biology and floral trade-offs, in conjunction with their pollinator dependence, is necessary for a balanced understanding of plant economics.
 
@@
 
-Here, we explore the potential trade-offs among plant floral and reproductive traits and how these influence the structure of plant-pollinator networks.
-First, we identify the major axes of floral and reproductive trait variation and trade-offs that determine plant form and function.
+Here, we explore the potential trade-offs among plant floral and reproductive biology traits and how these influence the structure of plant-pollinator networks.
+First, we identify the major axes of trait variation and trade-offs that determine plant form and function.
 Second, we investigate how plant species’ position in trait-space influences their interaction strength with different guilds of floral visitors.
@@
 3 | Interaction (yes/no) and visitation rates across the three main axes of trait variation per floral visitor guild.** Fitted posterior estimates of the presence/absence of interaction (a, b and c) and number of visits (d, e and f) made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
-PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off."}
+PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.
+For visualization purposes, due to large differences between the visitation rates of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
 
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=12,fig.pos = "!H",fig.cap= "**Fig.
-4 | contribution of traits in plant's network roles.** Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
+4 | Contribution of traits in plant's network roles.** Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
 The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
@@
 
-Here, we show that plant species exhibit clear trade-offs in their floral, reproductive and vegetative traits.
+Here, we show that plant species exhibit clear trade-offs in their floral, reproductive biology and vegetative traits.
 These trade-offs are differentiated on three main axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
@@
 Over 50% of plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
-Variation in these two axes of trait variation appears to be associated with the commonly described ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life-history strategies as indicated by the different floral and reproductive traits associated with plant height, life form and lifespan.
+Variation in these two axes of trait variation appears to be associated with the commonly described ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life-history strategies as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
 The ‘slow’ part of the continuum (i.e., tall trees and shrubs) had plant species with many flowers, few ovules, higher pollinator dependence, greater occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
@@
 
-To conclude, we provide the first description of plant floral and reproductive trade-offs using a large global dataset of plant traits and interactions with floral visitors.
+To conclude, we provide the first description of plant floral and reproductive biology trade-offs using a large global dataset of plant traits and interactions with floral visitors.
 This allowed us to identify the major reproductive strategies of flowering plants and how plant life strategies determine their interaction with floral visitor guilds.
@@
 **Functional traits.** We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
-These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive and 3 vegetative, Supplementary Information).
+These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive biology and 3 vegetative, Supplementary Information).
 For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
@@
 
-Type <- c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive")
-
-Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive","","","","")
+Type <- linebreak(c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive \n biology"),align = c("c"))
+
+Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology", "Reproductive \n biology","","","",""),align = c("c"))
 

### 2021-09-16 Manuscript/Manuscript.tex
wording edit from reproductive to reproductive biology;
and

describing new model with prsence absence. Now I have to redo analysis of supp. mat to match all analyses

@@
 physiological traits but little is known about how floral and
-reproductive traits drive these strategies, and in turn shape plant
-interactions with floral visitors. Here, we compiled 13 floral, 4
-reproductive and 3 vegetative traits for 1,506 plant species from 28
-plant-pollinator network studies across 18 different countries. We
-investigated the associations among these traits, pollinator visitation
-and the functional role of plant species within the networks
+reproductive biology traits drive these strategies, and in turn shape
+plant interactions with floral visitors. Here, we compiled 13 floral, 4
+reproductive biology and 3 vegetative traits for 1,506 plant species
+from 28 plant-pollinator network studies across 18 different countries.
+We investigated the associations among these traits, pollinator
+visitation and the functional role of plant species within the networks
 (interaction frequency, normalized degree and specialization). We found
@@
 their relevance to plant-pollinator interactions. However, most studies
-that have explored reproductive (e.g., mating and compatibility systems)
-and floral trait (e.g., flower size or nectar provision) variation have
-concentrated on the individual or community level and thus, broader
-macroecological patterns remain poorly
+that have explored plant reproductive biology (e.g., mating and
+compatibility systems) and floral trait (e.g., flower size or nectar
+provision) variation have concentrated on the individual or community
+level and thus, broader macroecological patterns remain poorly
 investigated\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3}--\protect\hyperlink{ref-grossenbacher2017}{7}}.
 Indeed, studies depicting species' life history strategies generally
-focus on vegetative traits and rarely consider reproductive
+focus on vegetative traits and rarely consider reproductive biology
 traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}}. As a
@@
 wood\textsuperscript{\protect\hyperlink{ref-chave2009}{21}} trade-offs
-with little or no attention given to reproductive and floral
+with little or no attention given to reproductive biology and floral
 traits\textsuperscript{\protect\hyperlink{ref-evojtko2020}{22}}, also
@@
 pollinators\textsuperscript{\protect\hyperlink{ref-ollerton2011}{25}}.
-Hence, exploring plant life strategies with reproductive and floral
-trade-offs, in conjunction with their pollinator dependence, is
+Hence, exploring plant life strategies with reproductive biology and
+floral trade-offs, in conjunction with their pollinator dependence, is
 necessary for a balanced understanding of plant economics.
@@
 Here, we explore the potential trade-offs among plant floral and
-reproductive traits and how these influence the structure of
-plant-pollinator networks. First, we identify the major axes of floral
-and reproductive trait variation and trade-offs that determine plant
-form and function. Second, we investigate how plant species' position in
-trait-space influences their interaction strength with different guilds
-of floral visitors. Finally, we investigate how the main axes of trait
-variation and individual traits influence plant species roles within
-networks.
+reproductive biology traits and how these influence the structure of
+plant-pollinator networks. First, we identify the major axes of trait
+variation and trade-offs that determine plant form and function. Second,
+we investigate how plant species' position in trait-space influences
+their interaction strength with different guilds of floral visitors.
+Finally, we investigate how the main axes of trait variation and
+individual traits influence plant species roles within networks.
 
@@
 PC2 represents the pollinator dependence trade-off and PC3, the style
-length trade-off.}
+length trade-off. For visualization purposes, due to large differences
+between the visitation rates of bees and the rest of guilds, the number
+of visits was log-transformed (Y-axis of lower panel).}
 \end{figure}
@@
 Here, we show that plant species exhibit clear trade-offs in their
-floral, reproductive and vegetative traits. These trade-offs are
+floral, reproductive biology and vegetative traits. These trade-offs are
 differentiated on three main axes of trait variation: (i) flower number
@@
 life-history strategies as indicated by the different floral and
-reproductive traits associated with plant height, life form and
+reproductive biology traits associated with plant height, life form and
 lifespan. The `slow' part of the continuum (i.e., tall trees and shrubs)
@@
 To conclude, we provide the first description of plant floral and
-reproductive trade-offs using a large global dataset of plant traits and
-interactions with floral visitors. This allowed us to identify the major
-reproductive strategies of flowering plants and how plant life
-strategies determine their interaction with floral visitor guilds.
-Although the percentage of explained variation found with the first two
-axes (\textasciitilde{}50\%) is lower than other studies that have
-evaluated life histories with vegetative
+reproductive biology trade-offs using a large global dataset of plant
+traits and interactions with floral visitors. This allowed us to
+identify the major reproductive strategies of flowering plants and how
+plant life strategies determine their interaction with floral visitor
+guilds. Although the percentage of explained variation found with the
+first two axes (\textasciitilde{}50\%) is lower than other studies that
+have evaluated life histories with vegetative
 traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}},
@@
 traits belonging to three broader trait groupings (13 floral, 4
-reproductive and 3 vegetative, Supplementary Information). For each
-plant species, we undertook an extensive literature and online search
-across a wide range of resources (plant databases, online floras, books,
-journals and images). From a total of 30,120 cells (20 columns × 1,506
-species) we were able to fill 24,341 cells (80.8\% of the dataset, see
-Supplementary Fig. S1 for missing values information for each trait).
+reproductive biology and 3 vegetative, Supplementary Information). For
+each plant species, we undertook an extensive literature and online
+search across a wide range of resources (plant databases, online floras,
+books, journals and images). From a total of 30,120 cells (20 columns ×
+1,506 species) we were able to fill 24,341 cells (80.8\% of the dataset,
+see Supplementary Fig. S1 for missing values information for each
+trait).
 
@@
 \addlinespace
-\textbf{Floral} & Ovules per flower & \textbf{Reproductive} & Autonomous selfing & \makecell[l]{None \\ Low \\ Medium \\ High}\\
+\textbf{Floral} & Ovules per flower & \textbf{\makecell[c]{Reproductive \\ biology}} & Autonomous selfing & \makecell[l]{None \\ Low \\ Medium \\ High}\\
 \addlinespace
-\textbf{Floral} & Flowers per plant & \textbf{Reproductive} & Compatibility system & \makecell[l]{Self-incomp. \\ Part. self-comp. \\ Self-comp.}\\
+\textbf{Floral} & Flowers per plant & \textbf{\makecell[c]{Reproductive \\ biology}} & Compatibility system & \makecell[l]{Self-incomp. \\ Part. self-comp. \\ Self-comp.}\\
 \addlinespace
-\textbf{Floral} & Nectar ($\mu$l) & \textbf{Reproductive} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious}\\
+\textbf{Floral} & Nectar ($\mu$l) & \textbf{\makecell[c]{Reproductive \\ biology}} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious}\\
 \addlinespace
@@
 \addlinespace
-\textbf{Reproductive} & Autonomous selfing (fruit set) & \textbf{} &  & \\
+\textbf{\makecell[c]{Reproductive \\ biology}} & Autonomous selfing (fruit set) & \textbf{} &  & \\
 \bottomrule

### 2021-09-16 Scripts/4_Data_Preparation_Analysis_1_Bees_Non_Apis.R

@@ -44,8 +44,34 @@ data_analysis <- merge(long_d_2, phyl_pca_1, by = "Plant_species")
 ########################################################################################################################################################
 saveRDS(data_analysis, "Data/RData/data_analysis_1_bees_non_apis.rds") 
 ########################################################################################################################################################
+#Now save it for presence/absence analysis
 ########################################################################################################################################################
+#Select data with interaction greater than 0
+long_d_1 <- long_d
 
+#Remove other orders/guilds that are not these ones
+long_d_2 <- long_d_1[!is.na(long_d_1$bee_family),] #I do it by guild because just these 6 guilds are named in this column
+
+#check levels
+levels(factor(long_d_2$bee_family)) #9 DIFFERENT GUILDS|After I'll select the main fucntional poll. groups for analysis
+
+#convert to dataframe the ppca data
+phyl_pca_1 <- data.frame(phyl_pca$S)
+
+#convert rownames to column
+dat_cleaning_1 <- setDT(dat_cleaning, keep.rownames = TRUE)[]
+colnames(dat_cleaning_1)[1] <- "Plant_species"
+
+phyl_pca_1$Plant_species <- dat_cleaning_1$Plant_species
+#ADD ALSO THESE OTHER 3 COLUMNS WITH SPP, GENUS AND FAMILY INFO NEEDED TO GET THE PHYLO FOR THE MODEL
+phyl_pca_1$Family_all <- dat_cleaning_1$Family_all
+phyl_pca_1$Genus_all <- dat_cleaning_1$Genus_all
+phyl_pca_1$Species_all <- dat_cleaning_1$Species_all
+
+#merge columns
+data_analysis <- merge(long_d_2, phyl_pca_1, by = "Plant_species")
+#Explore why some levels dropped
+saveRDS(data_analysis, "Data/RData/data_analysis_1_bees_non_apis_presence_absence.rds") 
 
 
 

### 2021-09-16 Manuscript/Manuscript.Rmd
Edits

@@
 
-**Visitation patterns.** We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on floral visits per plant species.
+**Visitation patterns.** We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
 For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.

### 2021-09-16 Supplementary_Material/Analysis_2_Hymenoptera_Families_Separated.Rmd
Update of figure 8 of supplementary material with new analysis

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap= ""}
 
-#LOAD LIBRARIES 
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
 library(reshape2)
 library(viridis) #COLOUR GGPLOT
-library(MASS)
+#library(MASS)
 library(ggplot2)
 library(broman) #crayon colours
-library(tidyverse)
+#library(tidyverse)
 library(patchwork) #panel of plots
@@
 
+#decimal places for ggplot
+
+scaleFUN <- function(x) sprintf("%.1f", x)
+
+#Prepare plot with presence absence and interaction frequency
 setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
+#Plot nicely PC1
+analysis_1 <- readRDS("results_analysis_1_bee_families_presence_absence.rds")
+dat_analysis <- readRDS("dat_analysis_results_analysis_1_bee_families_presence_absence.rds")
 
+ce_pc1 <- conditional_effects(analysis_1, effects = "PC1:bee_family",points=T)
+
+pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
+aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
+  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+
+ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:bee_family",points=T)
+
+pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
+aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
+  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+
+ce_pc3 <- conditional_effects(analysis_1, effects = "PC3:bee_family",points=T)
+
+pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
+ aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
+  theme_ms() + theme(legend.position = "none") + 
+  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 #Plot nicely PC1
@@
 dat_analysis <- readRDS("dat_bee_families.rds")
+########################################################################################################################
 
+########################################################################################################################
 ce_pc1 <- conditional_effects(analysis_1, effects = "PC1:bee_family",points=T)
 
-a1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
-  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
-  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
-   "Megachilidae"),values=c("blueviolet", "orange", "limegreen","#E7298A", "cyan4"),
-    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae"))+ggtitle("(a)") + theme(plot.title = element_text(size = 28, face = "bold"))
+p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
+  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
+  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+
+  scale_y_log10()+ggtitle("(d)")
 #Plot nicely PC2
@@
 
-a2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
-  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
-   "Megachilidae"),values=c("blueviolet", "orange", "limegreen","#E7298A", "cyan4"),
-    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae"))+ggtitle("(b)") + theme(plot.title = element_text(size = 28, face = "bold"))
+p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
+  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + 
+  scale_color_manual(name="Functional groups",values=c("orange", "black", 
+  "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10()+ggtitle("(e)")
 
@@
 
-a3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
-  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.4) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
-  theme_ms() + theme(legend.position = "none") +  scale_color_manual(name="Functional groups",labels=c("Andrenidae","Apidae", "Colletidae", "Halictidae",
-   "Megachilidae"),values=c("blueviolet", "orange", "limegreen","#E7298A", "cyan4"),
-    limits = c("Andrenidae","Apidae", "Colletidae", "Halictidae","Megachilidae"))+ggtitle("(c)") + theme(plot.title = element_text(size = 28, face = "bold"))
+p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
+  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles\n Low selfing    High selfing")+
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold"))+ 
+  scale_color_manual(name="Functional groups",values=c("orange", 
+  "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ scale_y_log10()+ggtitle("(f)")
 
-library(patchwork)
-
-combined <- a1 + a2 + a3 & theme(legend.position = "right")
-combined_1 <- combined + plot_layout(guides = "collect", ncol=3)
+combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
+combined_1 <- combined + plot_layout(guides = "collect",ncol = 3)
 

### 2021-09-16 Supplementary_Material/Supplementary_Material.Rmd
Update of figure 8 of supplementary material with new analysis

@@
 
-Supplementary Fig. S8: Visitation rate of the main bee families on the main axes of trait variation
+Supplementary Fig. S8: Presence/absence of interaction and visitation rate of the main bee families on the main axes of trait variation
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="\\textbf{Supplementary Fig.
-S8 | Visitation rate of the main bee families on the main axes of trait variation.} Fitted posterior estimates of the visitation rate of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
-We omitted in the plotting area points over percentile 95 \\% percent due to extreme outliers."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Supplementary Fig.
+S8 | Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation.} Fitted posterior estimates of the presence/absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
+For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)"}
 

### 2021-09-16 Manuscript/Manuscript.Rmd
Update text with new analysis.
I have to do the last analysis to complete the suup mat with the new presence-absence model

- With and without apis comparison

@@
 First, we identify the major axes of trait variation and trade-offs that determine plant form and function.
-Second, we investigate how plant species’ position in trait-space influences their interaction strength with different guilds of floral visitors.
+Second, we investigate how plant species’ position in trait-space influences their interaction patterns with different guilds of floral visitors.
 Finally, we investigate how the main axes of trait variation and individual traits influence plant species roles within networks.
@@
 
-**Network analyses.** Analyses were conducted on the subset of 60 weighted networks with interaction frequency sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our weighted network dataset (excluding meta-webs) included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-Anthophila-Hymenoptera interactions.
-Although floral visitors are not always pollinators and the frequency of visits does not consider each pollinator species efficiency [@ballantyne2015], visitation rate provides valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
+**Network analyses.** Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+These networks were analysed in their qualitative (presence-absence) and quantitative (interaction frequency) form.
+First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
+Second, we analysed the untransformed weighted networks with interaction frequency that accounts for the intensity of the interaction.
+Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency [@ballantyne2015], interaction frequency can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
+In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-Anthophila-Hymenoptera interactions.
 Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
@@
 For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because Hymenoptera-Anthophila was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the visitation rate of the main Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+Moreover, because Hymenoptera-Anthophila was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
 In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
@@
 Hence, to control for the effect of _A.
-mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis excluding _A.
+mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of interaction and visitation rate excluding _A.
 mellifera_.

### 2021-09-16 Manuscript/Manuscript.tex
Update text with new analysis.
I have to do the last analysis to complete the suup mat with the new presence-absence model

- With and without apis comparison

@@
 \includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\textbf{Fig. 4 \textbar{} contribution
+\caption{\label{fig:unnamed-chunk-4}\textbf{Fig. 4 \textbar{} Contribution
 of traits in plant's network roles.} Regression tree analysis of
@@
 details) to explore the effect of floral visitor groups and the main
-axes of trait variation (pPCA with imputed dataset) on floral visits per
-plant species. For this, we divided floral visitors into six main guilds
-that differ in life form, behaviour and are likely to play a similar
-ecological role: (i) Hymenoptera-Anthophila (bees), (ii)
-Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii)
+axes of trait variation (pPCA with imputed dataset) on both qualitative
+(presence/absence) and quantitative (visitation rate) floral
+interactions per plant species. For this, we divided floral visitors
+into six main guilds that differ in life form, behaviour and are likely
+to play a similar ecological role: (i) Hymenoptera-Anthophila (bees),
+(ii) Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii)
 Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi)
@@
 represented group with 2,256 records and had the highest frequency of
-visits of all groups, we also explored the visitation rate of the main
-Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae,
-Halictidae and Megachilidae) on the trait space. In addition, we found
-that \emph{Apis mellifera} was the floral visitor with the largest
-proportion of records counted (7.55\% of the total). This finding is
-consistent with previous research showing that \emph{A. mellifera} was
-the most frequent floral visitor in a similar dataset of 80
-plant-pollinator networks in natural
+visits of all groups, we also explored the presence-absence of
+interaction and visitation rate of the main Hymenoptera-Anthophila
+families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae)
+on the trait space. In addition, we found that \emph{Apis mellifera} was
+the floral visitor with the largest proportion of records counted
+(7.55\% of the total). This finding is consistent with previous research
+showing that \emph{A. mellifera} was the most frequent floral visitor in
+a similar dataset of 80 plant-pollinator networks in natural
 ecosystems\textsuperscript{\protect\hyperlink{ref-hung2018}{60}}. Hence,

### 2021-09-16 Supplementary_Material/Supplementary_Material.Rmd
Update text with new analysis.
I have to do the last analysis to complete the suup mat with the new presence-absence model

- With and without apis comparison

@@
 
-Supplementary Fig. S8: Presence/absence of interaction and visitation rate of the main bee families on the main axes of trait variation
+Supplementary Fig. S8: Presence-absence of interaction and visitation rate of the main bee families on the main axes of trait variation
 
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Supplementary Fig.
-S8 | Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation.} Fitted posterior estimates of the presence/absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
+S8 | Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation.} Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
 For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)"}

### 2021-09-19 Supplementary_Material/Apis_Non_Apis_Bees_Presence_Absence.Rmd
Update in figure and figure caption of supp mat

---
title: ""
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap= ""}

library(reshape2)
library(viridis) #color GGPLOT
#library(MASS)
library(ggplot2)
library(broman) #crayon colors
#library(tidyverse)
library(patchwork) #panel of plots
library(brms)
#library(cmdstanr)

#Load theme for publication

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2)),
           axis.text=element_text(size = rel(1.8), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.4)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(1.8, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank(),
           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
           plot.subtitle = element_text(face="bold",size=rel(2))
     ))
}

#decimal places for ggplot

scaleFUN <- function(x) sprintf("%.1f", x)

#Prepare plot with presence absence and interaction frequency
setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
#Plot nicely PC1
analysis_1 <- readRDS("results_analysis_1_bee_apis_presence_absence.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1_bee_apis_presence_absence.rds")

ce_pc1 <- conditional_effects(analysis_1, effects = "PC1",points=T)

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4,  colour="orange") + geom_line(size=1.5,  colour="orange")  + ylab("Interaction")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

ce_pc2 <- conditional_effects(analysis_1, effects = "PC2",points=T)

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = dat_analysis,
aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4,  colour="orange") + geom_line(size=1.5, colour="orange")  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

ce_pc3 <- conditional_effects(analysis_1, effects = "PC3",points=T)

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = dat_analysis,
 aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4,  colour="orange") + geom_line(size=1.5,  colour="orange")  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

#Plot nicely PC1
analysis_1 <- readRDS("results_analysis_1_bee_non_apis_presence_absence.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1_bee_non_apis_presence_absence.rds")

ce_pc1 <- conditional_effects(analysis_1, effects = "PC1",points=T)

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4,  colour="orange") + geom_line(size=1.5,  colour="orange")  + ylab("Interaction")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

ce_pc2 <- conditional_effects(analysis_1, effects = "PC2",points=T)

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = dat_analysis,
aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4,  colour="orange") + geom_line(size=1.5,  colour="orange")  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

ce_pc3 <- conditional_effects(analysis_1, effects = "PC3",points=T)

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = dat_analysis,
 aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4,  colour="orange") + geom_line(size=1.5,  colour="orange")  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
 combined + plot_layout(guides = "collect",ncol = 3)

```

### 2021-09-19 Supplementary_Material/Bees_and_other_func_grous_separated.Rmd
Update in figure and figure caption of supp mat

--- 2021-04-14 Supplementary_Material/Bees_and_other_func_grous_separated.Rmd
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=24}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24}
 
@@
 library(brms)
-library(cmdstanr)
 
@@
 
+#decimal places for ggplot
+
+scaleFUN <- function(x) sprintf("%.1f", x)
+
+#Prepare plot with presence absence and interaction frequency
 setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
+#Plot nicely PC1
+analysis_1 <- readRDS("results_analysis_1_bee_apis_presence_absence.rds")
+dat_analysis <- readRDS("dat_analysis_results_analysis_1_bee_apis_presence_absence.rds")
+
+ce_pc1 <- conditional_effects(analysis_1, effects = "PC1",points=T)
+
+my_y_title_1 <- expression(paste(bold("(a) "), "All bee species"))
+
+a1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = dat_analysis,
+aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4,  colour="orange") + geom_line(size=1.5,  colour="orange")  + ylab("Interaction")+ xlab("")+
+  theme_ms() + theme(legend.position = "none") +scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes")) + labs(title = "PC1", subtitle = my_y_title_1)
+
+ce_pc2 <- conditional_effects(analysis_1, effects = "PC2",points=T)
+
+my_y_title_1 <- expression(paste(bold("(b) "), "All bee species"))
+
+a2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = dat_analysis,
+aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4,  colour="orange") + geom_line(size=1.5, colour="orange")  + ylab("")+ xlab("")+
+  theme_ms() + theme(legend.position = "none") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes")) + labs(title = "PC2", subtitle = my_y_title_1)
+
+ce_pc3 <- conditional_effects(analysis_1, effects = "PC3",points=T)
+
+my_y_title_1 <- expression(paste(bold("(c) "), "All bee species"))
+
+a3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = dat_analysis,
+ aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4,  colour="orange") + geom_line(size=1.5,  colour="orange")  + ylab("")+ xlab("")+
+  theme_ms() + theme(legend.position = "none") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))+ labs(title = "PC3", subtitle = my_y_title_1)
 
 #Plot nicely PC1
+analysis_1 <- readRDS("results_analysis_1_bee_non_apis_presence_absence.rds")
+dat_analysis <- readRDS("dat_analysis_results_analysis_1_bee_non_apis_presence_absence.rds")
+
+my_y_title <- expression(paste(bold("(d) "), italic("Apis mellifera"), " excluded"))
+
+ce_pc1 <- conditional_effects(analysis_1, effects = "PC1",points=T)
+
+b1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = dat_analysis,
+aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4,  colour="brown4") + geom_line(size=1.5,  colour="brown4")  + ylab("Interaction")+ xlab("")+
+  theme_ms() + theme(legend.position = "none") + ggtitle("PC1", subtitle = "(d)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))+
+   labs(title = "", subtitle = my_y_title)
+
+ce_pc2 <- conditional_effects(analysis_1, effects = "PC2",points=T)
+
+my_y_title <- expression(paste(bold("(e) "), italic("Apis mellifera"), " excluded"))
+
+b2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = dat_analysis,
+aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4,  colour="brown4") + geom_line(size=1.5,  colour="brown4")  + ylab("")+ xlab("")+
+  theme_ms() + theme(legend.position = "none") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes")) +
+ labs(title = "", subtitle =my_y_title)
+
+ce_pc3 <- conditional_effects(analysis_1, effects = "PC3",points=T)
+
+my_y_title <- expression(paste(bold("(f) "), italic("Apis mellifera"), " excluded"))
+
+b3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = dat_analysis,
+ aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4,  colour="brown4") + geom_line(size=1.5,  colour="brown4")  + ylab("")+ xlab("")+
+  theme_ms() + theme(legend.position = "none") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))+
+ labs(title = "", subtitle =my_y_title)
+
 analysis_1_just_bees <- readRDS("results_analysis_1_just_bees.rds")
@@
 ce_pc1 <- conditional_effects(analysis_1_just_bees, effects = "PC1",points=T) 
+ce_pc1[[1]]$guild <- "bees"
 
-p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis, aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.3, colour="orange") + geom_line(size=1.5, colour="orange") +
+my_y_title_1 <- expression(paste(bold("(g) "), "All bee species"))
+
+c1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis,
+  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("")+
-  theme_ms() + theme(legend.position = "none")
+  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) +
+ labs(title = "", subtitle =my_y_title_1)
 
+#Plot nicely PC2
 ce_pc2 <- conditional_effects(analysis_1_just_bees, effects = "PC2",points=T) 
+ce_pc1[[1]]$guild <- "bees"
 
-p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.3, colour="orange") + geom_line(size=1.5, colour="orange") +
+my_y_title_1 <- expression(paste(bold("(h) "), "All bee species"))
+
+c2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,
+  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("")+
-  theme_ms() + theme(legend.position = "none")
+  theme_ms() + theme(legend.position = "none")  + 
+  theme(plot.title = element_text(size = 36, face = "bold"),plot.subtitle=element_text(size=30,face="bold"))+
+ labs(title = "", subtitle =my_y_title_1)
 
+#Plot nicely PC3
 ce_pc3 <- conditional_effects(analysis_1_just_bees, effects = "PC3",points=T)
+ce_pc1[[1]]$guild <- "bees"
 
-p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis,aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.3, colour="orange") + geom_line(size=1.5, colour="orange") +
+my_y_title_1 <- expression(paste(bold("(i) "), "All bee species"))
+
+c3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis,
+  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("")+
-  theme_ms() +theme(legend.position = "none")
+  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) +
+ labs(title = "", subtitle =my_y_title_1)
 
-analysis_1_no_bees <- readRDS("results_analysis_1_no_bees.rds")
-dat_analysis <- readRDS("dat_analysis_results_analysis_1_no_bees.rds")
+analysis_1_just_bees_non_apis <- readRDS("results_analysis_1_just_bees_non_apis.rds")
+dat_analysis <- readRDS("dat_analysis_results_analysis_1_just_bees.rds")
 
-ce_pc1 <- conditional_effects(analysis_1_no_bees, effects = "PC1:guild",points=T)
+ce_pc1 <- conditional_effects(analysis_1_just_bees_non_apis, effects = "PC1",points=T) 
+ce_pc1[[1]]$guild <- "bees"
 
-pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
-  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.5) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
-  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-   "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
-    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids"))
+my_y_title <- expression(paste(bold("(j) "), italic("Apis mellifera"), " excluded"))
 
-ce_pc2 <- conditional_effects(analysis_1_no_bees, effects = "PC2:guild",points=T)
+d1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis,
+      aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4")+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
+  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) +
+ labs(title = "", subtitle =my_y_title)
 
-pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
-  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.5) + 
+#Plot nicely PC2
+ce_pc2 <- conditional_effects(analysis_1_just_bees_non_apis, effects = "PC2",points=T) 
+ce_pc1[[1]]$guild <- "bees"
+
+my_y_title <- expression(paste(bold("(k) "), italic("Apis mellifera"), " excluded"))
+
+d2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,
+                                                                          aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-   "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
-    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphids-diptera", "Syrphids"))
+  theme_ms() + theme(legend.position = "none")  +
+  theme(plot.title = element_text(size = 36, face = "bold"),plot.subtitle=element_text(size=30,face="bold"))+ labs(title = "", subtitle = my_y_title)
 #Plot nicely PC3
-ce_pc3 <- conditional_effects(analysis_1_no_bees, effects = "PC3:guild",points=T)
+ce_pc3 <- conditional_effects(analysis_1_just_bees_non_apis, effects = "PC3",points=T)
+ce_pc1[[1]]$guild <- "bees"
 
-pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
-  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5) + geom_line(size=1.5) + 
+my_y_title <- expression(paste(bold("(l) "), italic("Apis mellifera"), " excluded"))
+
+d3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis,
+                                                                          aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
-  theme_ms() +theme(legend.position = "none") + scale_color_manual(name="Functional groups",labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-    "Non-syrphids-diptera", "Syrphids"),values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),
-    limits = c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-               "Non-syrphids-diptera", "Syrphids"))
+  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = my_y_title)
 
@@
 
-combined <- p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "right")
-combined + plot_layout(guides = "collect")
+combined <- a1 + a2 + a3 + b1 + b2 + b3 + c1 + c2 + c3 + d1 + d2 + d3 & theme(legend.position = "right")
+combined <- combined + plot_layout(guides = "collect",ncol = 3)
+
+setwd("~/Dropbox/PhD/R/Chapter_2")
+
+saveRDS(combined, "Plot_apis_non_apis.rds")
 

### 2021-09-19 Supplementary_Material/Supplementary_Material.Rmd
Update in figure and figure caption of supp mat

@@
 
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28,  fig.cap="\\textbf{Supplementary Fig.
-S3 | Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation.} The superior (plots a, b and c) and lower (plots d, e and f) panels show visitation rates on the main axes of trait variation with and without \\emph{Apis mellifera}, respectively."}
+\newpage
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24,  fig.cap="\\textbf{Supplementary Fig.
+S3 | Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation.} The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates."}
 
@@
 
-plot_apis <- readRDS("Plot_apis.rds")
+plot_apis <- readRDS("Plot_apis_non_apis.rds")
 
@@
 ```
-
-\elandscape
 
@@
 library(brms) #modelling
-library(cmdstanr) #modelling
 library(cowplot) #panel of plots

### 2021-10-05 Manuscript/Manuscript.Rmd
edits

@@
 
-__Plant life strategies are often delimited by vegetative and physiological traits but little is known about how floral and reproductive biology traits drive these strategies, and in turn shape plant interactions with floral visitors.
-Here, we compiled 13 floral, 4 reproductive biology and 3 vegetative traits for 1,506 plant species from 28 plant-pollinator network studies across 18 different countries.
-We investigated the associations among these traits, pollinator visitation and the functional role of plant species within the networks (interaction frequency, normalized degree and specialization).
+__Plant life strategies are constrained by cost-benefit trade-offs that determine plant form and function.
+Despite the recent advances in the understanding of plant trade-offs with vegetative and physiological traits, little is known about the plant reproductive economics and how they constrain plant life strategies and shape interactions with floral visitors.
+Here, we investigated plant reproductive trade-offs and their association with floral visitors with a dataset of 1506 plant species with 17 reproductive and 3 vegetative traits from 28 plant-pollinator network studies across 18 countries.
+Then, we tested whether a species reproductive strategy predicted plant-pollinator interactions (presence-absence and visitation rate) and if the interaction strategy (its role in a pollination network) was predicted by individual traits.
 We found that 51.8% of trait variation was explained by two independent axes that encompassed plant form and function.
-Specifically, the first axis indicated the presence of a trade-off between flower number and flower size (PC1, 26.72%).
-The second axis indicated a trade-off for the level of pollinator dependency (PC2, 25.08%).
-Although the main axes of trait variation did not fully explain pollinator visitation rates, different plant life strategies were associated with visitation rates and pollinator functional groups.
-Overall, the main traits that determined plant species’ functional roles were height, nectar concentration, pollen grains per flower, number of ovules, style length, selfing level and flower width.
-Our results highlight the need to consider plant reproductive and floral traits to improve understanding of plant life strategies and plant-pollinator interactions at broader spatial scales.__
+Specifically, the first axis indicated the presence of a trade-off between flower number and flower size (PC1, 26.72%) and the second axis indicated a trade-off for the level of pollinator dependency (PC2, 25.08%).
+The reproductive trade-offs explained some of the qualitative interaction with pollinators (presence-absence) but none of the variability of visitation rates.
+However, noteworthy differences across pollinator guilds were found in both cases.
+Finally, we found that specific traits with special relevance of floral rewards were key in the understanding of the species network role.
+Our results highlight the need to consider plant reproductive trade-offs to improve our understanding of plant life strategies and plant-pollinator interactions at broader spatial scales.__
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,fig.pos = "t",fig.cap= "**Fig.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.align='center',fig.width=10,fig.cap= "**Fig.
 1 | Plant life-history strategies.** Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18,fig.pos = "!H",fig.cap= "**Fig.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18,fig.cap= "**Fig.
 2 | Location of the different qualitative traits on the trait space.** The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f)."}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap= "**Fig.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Fig.
 3 | Interaction (yes/no) and visitation rates across the three main axes of trait variation per floral visitor guild.** Fitted posterior estimates of the presence/absence of interaction (a, b and c) and number of visits (d, e and f) made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=12,fig.pos = "!H",fig.cap= "**Fig.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=12,fig.cap= "**Fig.
 4 | Contribution of traits in plant's network roles.** Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.

### 2021-10-05 Manuscript/Manuscript.tex
edits

@@
 
-\textbf{Plant life strategies are often delimited by vegetative and
-physiological traits but little is known about how floral and
-reproductive biology traits drive these strategies, and in turn shape
-plant interactions with floral visitors. Here, we compiled 13 floral, 4
-reproductive biology and 3 vegetative traits for 1,506 plant species
-from 28 plant-pollinator network studies across 18 different countries.
-We investigated the associations among these traits, pollinator
-visitation and the functional role of plant species within the networks
-(interaction frequency, normalized degree and specialization). We found
-that 51.8\% of trait variation was explained by two independent axes
-that encompassed plant form and function. Specifically, the first axis
-indicated the presence of a trade-off between flower number and flower
-size (PC1, 26.72\%). The second axis indicated a trade-off for the level
-of pollinator dependency (PC2, 25.08\%). Although the main axes of trait
-variation did not fully explain pollinator visitation rates, different
-plant life strategies were associated with visitation rates and
-pollinator functional groups. Overall, the main traits that determined
-plant species' functional roles were height, nectar concentration,
-pollen grains per flower, number of ovules, style length, selfing level
-and flower width. Our results highlight the need to consider plant
-reproductive and floral traits to improve understanding of plant life
+\textbf{Plant life strategies are constrained by cost-benefit trade-offs
+that determine plant form and function. Despite the recent advances in
+the understanding of plant trade-offs with vegetative and physiological
+traits, little is known about the plant reproductive economics and how
+they constrain plant life strategies and shape interactions with floral
+visitors. Here, we investigated plant reproductive trade-offs and their
+association with floral visitors with a dataset of 1506 plant species
+with 17 reproductive and 3 vegetative traits from 28 plant-pollinator
+network studies across 18 countries. Then, we tested whether a species
+reproductive strategy predicted plant-pollinator interactions
+(presence-absence and visitation rate) and if the interaction strategy
+(its role in a pollination network) was predicted by individual traits.
+We found that 51.8\% of trait variation was explained by two independent
+axes that encompassed plant form and function. Specifically, the first
+axis indicated the presence of a trade-off between flower number and
+flower size (PC1, 26.72\%) and the second axis indicated a trade-off for
+the level of pollinator dependency (PC2, 25.08\%). The reproductive
+trade-offs explained some of the qualitative interaction with
+pollinators (presence-absence) but none of the variability of visitation
+rates. However, noteworthy differences across pollinator guilds were
+found in both cases. Finally, we found that specific traits with special
+relevance of floral rewards were key in the understanding of the species
+network role. Our results highlight the need to consider plant
+reproductive trade-offs to improve our understanding of plant life
 strategies and plant-pollinator interactions at broader spatial scales.}
@@
 we investigate how plant species' position in trait-space influences
-their interaction strength with different guilds of floral visitors.
+their interaction patterns with different guilds of floral visitors.
 Finally, we investigate how the main axes of trait variation and
@@
 
-\begin{figure}
-\centering
-\includegraphics{output/figures/unnamed-chunk-1-1.pdf}
-\caption{\label{fig:unnamed-chunk-1}\textbf{Fig. 1 \textbar{} Plant
-life-history strategies.} Phylogenetically informed principal component
-analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network
-studies. The solid arrows indicate the direction of the different
-quantitative traits (flower number, plant height, style length, flower
-size, ovule number and level of autonomous selfing) across the two main
-axes of trait variation. The length of the arrows indicate the weight of
-the variables on each principal component and the dashed lines show the
-opposed direction of trait variation. The icons at both ends of arrows
-and dashed lines illustrate the extreme form of the trait continuum.}
+\begin{figure}[H]
+
+{\centering \includegraphics{output/figures/unnamed-chunk-1-1}
+
+}
+
+\caption{**Fig.
+1 | Plant life-history strategies.** Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
+The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
+The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation.
+The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum.}\label{fig:unnamed-chunk-1}
 \end{figure}
@@
 \textbf{Network analyses.} Analyses were conducted on the subset of 60
-weighted networks with interaction frequency sampled in a unique
-flowering season and site, which included 556 plant and 1,126 pollinator
-species. In total, our weighted network dataset (excluding meta-webs)
-included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with
-plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae
-interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions
-and 362 non-Anthophila-Hymenoptera interactions. Although floral
-visitors are not always pollinators and the frequency of visits does not
-consider each pollinator species
+weighted networks sampled in a unique flowering season and site, which
+included 556 plant and 1,126 pollinator species. These networks were
+analysed in their qualitative (presence-absence) and quantitative
+(interaction frequency) form. First, we analysed the binary version of
+these weighted networks with presence-absence information that assumes
+equal weight across interactions. Second, we analysed the untransformed
+weighted networks with interaction frequency that accounts for the
+intensity of the interaction. Although floral visitors are not always
+pollinators and interaction frequency does not consider each pollinator
+species
 efficiency\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{57}},
-visitation rate provides valuable information of the contribution of
-floral visitors to
+interaction frequency can provide valuable information of the
+contribution of floral visitors to
 pollination\textsuperscript{\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}}.
-Sampling methods varied across networks but this was accounted for in
-analyses by considering them in the random effects of the modelling
-process. All analyses were conducted in R version \emph{4.0.3}.
+In total, our network dataset (excluding meta-webs and non-weighted
+networks) included 2,256 interactions of Anthophila-Hymenoptera (i.e.,
+bees) with plants, 1,768 non-Syrphidae-Diptera interactions, 845
+Syrphidae interactions, 437 Lepidoptera interactions, 432 Coleoptera
+interactions and 362 non-Anthophila-Hymenoptera interactions. Sampling
+methods varied across networks but this was accounted for in analyses by
+considering them in the random effects of the modelling process. All
+analyses were conducted in R version \emph{4.0.3}.
 
@@
 to control for the effect of \emph{A. mellifera} on the observed
-visitation patterns of bees, we conducted an analogous analysis
-excluding \emph{A. mellifera}. We found that \emph{A. mellifera}, was
-partly driving some of the observed trends on PC1 (Supplementary Fig.
-S3). However, we did not detect major differences on PC2 and PC3.
+visitation patterns of bees, we conducted an analogous analysis with
+presence-absence of interaction and visitation rate excluding \emph{A.
+mellifera}. We found that \emph{A. mellifera}, was partly driving some
+of the observed trends on PC1 (Supplementary Fig. S3). However, we did
+not detect major differences on PC2 and PC3.
 

### 2021-10-05 Supplementary_Material/Supplementary_Material.Rmd
edits

@@
 ---
-title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant floral and reproductive traits determine interactions with floral visitors}
+title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant reproductive traits determine interactions with floral visitors}
 
@@
 ```{r pressure, echo=FALSE, fig.cap="", out.width = '65%',fig.align='center', fig.cap="\\textbf{Supplementary text Fig.
-1 | Main floral morphologies considered in this study.} All species were groupped within these categories for analysis: tube (a), papilonaceous (b), open (c), capitulum (d), campanulate (e) and brush (f)."}
+1 | Main floral morphologies considered in this study.} All species were groupped within these categories for analysis: (a) tube, (b) papilonaceous, (c) open, (d) capitulum, (e) campanulate and (f) brush."}
 knitr::include_graphics("../Images/flower_shapes.png")

### 2021-10-06 Manuscript/Manuscript.Rmd
update on ms

@@
 
-There is an astonishing diversity of floral structures and plant reproductive strategies among flowering plants [@barrett2002; @schiestl2013], which have long been of interest to pollination biologists in terms of their relevance to plant-pollinator interactions.
-However, most studies that have explored plant reproductive biology (e.g., mating and compatibility systems) and floral trait (e.g., flower size or nectar provision) variation have concentrated on the individual or community level and thus, broader macroecological patterns remain poorly investigated [@carvalheiro2014; @baude2016; @munoz2016; @moeller2017; @grossenbacher2017].
-Indeed, studies depicting species’ life history strategies generally focus on vegetative traits and rarely consider reproductive biology traits [@salguero2016, @ruger2018].
-As a consequence, a unified framework that explores the compromises among floral traits and their relevance to plant life strategies is currently lacking [@roddy2021].
-At the same time, there is growing interest in the determinants of plant-pollinator interactions via trait-based approaches [@fenster2004] and trait-matching analyses [@bartomeus2016].
-However, floral traits have been overlooked beyond highly specialised plant-pollinator systems [@dellinger2020; @roddy2021] and the role of plant reproductive biology remains little explored in plant-pollinator interactions (but see references [@tur2013; @devaux2014]).
-
-  With the recent availability of large trait databases, plant ecological strategies are increasingly being examined [e.g., TRY; @kattge2011 and COMPADRE; @salguero2015], and are facilitating the identification of global patterns and constraints of plant form and function [@salguero2016; @diaz2016; @carmona2021].
-However, the main focus has been on vegetative traits such as leaf [@wright2004] or wood [@chave2009] trade-offs with little or no attention given to reproductive biology and floral traits [@evojtko2020], also critical to plant form and function.
+Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their relevance to understand plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that explores plant reproductive compromises is currently lacking [@roddy2021].
+In addition, macroecological studies regarding specific reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and as a consequence studies that link reproductive traits to plant-pollinator interactions at large scales are poorly explored [@sargent2008; @rech2016; @salguero2016; @ruger2018].
+Linking the position in the trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
+At the same time, there is increasing interest in the understanding of the determinants of plant-pollinator interactions via trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
+However, reproductive traits have been overlooked beyond highly specialised systems [@dellinger2020] despite the apparent generalist nature of plant-pollinator interactions [@waser1996; @olesen2002].
+In addition, it is yet unclear how the different reproductive biology traits influence plant-pollinator associations [@tur2013; @devaux2014].
+
+Species can optimize their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can employ.
+With the recent availability of large trait databases (e.g., TRY [@kattge2011] and COMPADRE [@salguero2015]), plant ecological strategies are increasingly being examined, and are facilitating the identification of global patterns and constraints of plant form and function [@salguero2016; @diaz2016; bruelheide2018; @carmona2021].
+However, the main focus has been on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits
+[@evojtko2020; @roddy2021], also critical to plant life strategies that shape plant interactions with pollinators and ultimately impact plant reproductive success.
 For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively [@barrett2003; @moeller2017].
@@
 In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and their role in attracting pollinators [@ollerton2011].
-Hence, exploring plant life strategies with reproductive biology and floral trade-offs, in conjunction with their pollinator dependence, is necessary for a balanced understanding of plant economics.
-
-  Several studies have identified links between plant traits and plant-pollinator network properties [@lazaro2008; @bartomeus2013; @carvalheiro2014].
-Moreover, plant traits can also define species' network roles (e.g., specialists vs generalists).
+However, it is still unknown to what extent these different  reproductive compromises determine plant-pollinator associations.
+
+Several studies have identified links between plant traits and plant-pollinator network properties [@bartomeus2013; @olito2015; @rowe2020].
+Moreover, plant traits can also define species' network roles (@lazaro2013; @tur2013)(e.g., specialists vs generalists).
 For example, species that occupy trait space extremes are more likely to exhibit higher specialization and be more reliant on trait-matching [@junker2013; @coux2016].
 This morphological matching between plant and floral visitors can determine plant-pollinator interactions, and thus shape their interaction network structure [@stang2009; @ibanez2012].
-Despite the increasing knowledge of the relevance of traits on the species network roles, little is known about how plant reproductive and floral traits determine plant species’ network roles at a macroecological scale.
-
-Here, we explore the potential trade-offs among plant floral and reproductive biology traits and how these influence the structure of plant-pollinator networks.
-First, we identify the major axes of trait variation and trade-offs that determine plant form and function.
-Second, we investigate how plant species’ position in trait-space influences their interaction patterns with different guilds of floral visitors.
-Finally, we investigate how the main axes of trait variation and individual traits influence plant species roles within networks.
+Remarkably, the combination of traits have shown to increase the predictive power of the network interactions [@eklof2013].
+Therefore, considering the different plant reproductive trade-offs which represent the species strategy within the network [@dehling2016] could progress our understanding of plant-pollinator interactions.
+Further, we know little if the different network patterns generally studied at the community level are maintained when we scale up at macroecological scale.
+
+Here, we explore the potential trade-offs among plant floral and reproductive biology traits and how these influence plant-pollinator interactions.
+First, we identify the major axes of reproductive trait variation and trade-offs that determine plant form and function.
+Second, we investigate how plant species’ position in trait-space influences plant-pollinator interactions (presence-absence and visitation rate).
+Finally, we investigate how the main axes of trait variation and individual traits influence plant species roles within networks using complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
 

### 2021-10-06 Manuscript/Manuscript.tex
update on ms

@@
 
-There is an astonishing diversity of floral structures and plant
-reproductive strategies among flowering
-plants\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}},
-which have long been of interest to pollination biologists in terms of
-their relevance to plant-pollinator interactions. However, most studies
-that have explored plant reproductive biology (e.g., mating and
-compatibility systems) and floral trait (e.g., flower size or nectar
-provision) variation have concentrated on the individual or community
-level and thus, broader macroecological patterns remain poorly
-investigated\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3}--\protect\hyperlink{ref-grossenbacher2017}{7}}.
-Indeed, studies depicting species' life history strategies generally
-focus on vegetative traits and rarely consider reproductive biology
-traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}}. As a
-consequence, a unified framework that explores the compromises among
-floral traits and their relevance to plant life strategies is currently
-lacking\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}}. At the
-same time, there is growing interest in the determinants of
-plant-pollinator interactions via trait-based
-approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{11}} and
-trait-matching
-analyses\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{12}}.
-However, floral traits have been overlooked beyond highly specialised
-plant-pollinator
-systems\textsuperscript{\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-dellinger2020}{13}}
-and the role of plant reproductive biology remains little explored in
-plant-pollinator interactions (but see
-references\textsuperscript{\protect\hyperlink{ref-tur2013}{14},\protect\hyperlink{ref-devaux2014}{15}}).
-
-With the recent availability of large trait databases, plant ecological
-strategies are increasingly being
-examined\textsuperscript{\protect\hyperlink{ref-kattge2011}{16},\protect\hyperlink{ref-salguero2015}{17}},
-and are facilitating the identification of global patterns and
-constraints of plant form and
-function\textsuperscript{\protect\hyperlink{ref-salguero2016}{8},\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}}.
+Despite the astonishing diversity of floral structures among flowering
+plants\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}}
+and their relevance to understand plant-pollinator
+interactions\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}},
+a unified framework that explores plant reproductive compromises is
+currently lacking\textsuperscript{\protect\hyperlink{ref-roddy2021}{5}}.
+In addition, macroecological studies regarding specific reproductive
+traits are
+scarce\textsuperscript{\protect\hyperlink{ref-baude2016}{6}--\protect\hyperlink{ref-moeller2017}{9}}
+and as a consequence studies that link reproductive traits to
+plant-pollinator interactions at large scales are poorly
+explored\textsuperscript{\protect\hyperlink{ref-sargent2008}{10}--\protect\hyperlink{ref-ruger2018}{13}}.
+Linking the position in the trait-space with the different pollinator
+groups could help to improve our understanding of plant-pollinator
+associations\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}}.
+At the same time, there is increasing interest in the understanding of
+the determinants of plant-pollinator interactions via trait-based
+approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{15}}
+and trait-matching
+analyses\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-bartomeus2016}{17}}.
+However, reproductive traits have been overlooked beyond highly
+specialised
+systems\textsuperscript{\protect\hyperlink{ref-dellinger2020}{4}}
+despite the apparent generalist nature of plant-pollinator
+interactions\textsuperscript{\protect\hyperlink{ref-waser1996}{18},\protect\hyperlink{ref-olesen2002}{19}}.
+In addition, it is yet unclear how the different reproductive biology
+traits influence plant-pollinator
+associations\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-devaux2014}{21}}.
+
+Species can optimize their fitness through various life-history traits,
+yet trade-offs among those traits constrain the range of potential
+strategies that a species can employ. With the recent availability of
+large trait databases (e.g.,
+TRY\textsuperscript{\protect\hyperlink{ref-kattge2011}{22}} and
+COMPADRE\textsuperscript{\protect\hyperlink{ref-salguero2015}{23}}),
+plant ecological strategies are increasingly being examined, and are
+facilitating the identification of global patterns and constraints of
+plant form and
+function\textsuperscript{\protect\hyperlink{ref-salguero2016}{12},\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{25}}.
 However, the main focus has been on vegetative traits such as
-leaf\textsuperscript{\protect\hyperlink{ref-wright2004}{20}} or
-wood\textsuperscript{\protect\hyperlink{ref-chave2009}{21}} trade-offs
-with little or no attention given to reproductive biology and floral
-traits\textsuperscript{\protect\hyperlink{ref-evojtko2020}{22}}, also
-critical to plant form and function. For instance, short lived versus
-perennial species tend to have low versus high levels of outcrossing,
-respectively\textsuperscript{\protect\hyperlink{ref-moeller2017}{6},\protect\hyperlink{ref-barrett2003}{23}}.
+leaf\textsuperscript{\protect\hyperlink{ref-wright2004}{26}},
+wood\textsuperscript{\protect\hyperlink{ref-chave2009}{27}}, or
+root\textsuperscript{\protect\hyperlink{ref-laughlin2021}{28}}
+trade-offs with little or no attention given to reproductive
+traits\textsuperscript{\protect\hyperlink{ref-roddy2021}{5},\protect\hyperlink{ref-evojtko2020}{29}},
+also critical to plant life strategies that shape plant interactions
+with pollinators and ultimately impact plant reproductive success. For
+instance, short lived versus perennial species tend to have low versus
+high levels of outcrossing,
+respectively\textsuperscript{\protect\hyperlink{ref-moeller2017}{9},\protect\hyperlink{ref-barrett2003}{30}}.
 Further, outcrossing levels are positively correlated with flower
-size\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{24}}. In
+size\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{31}}. In
 addition, the presence of costly rewards (e.g., pollen or nectar) and
@@
 (pollinator dependence) and their role in attracting
-pollinators\textsuperscript{\protect\hyperlink{ref-ollerton2011}{25}}.
-Hence, exploring plant life strategies with reproductive biology and
-floral trade-offs, in conjunction with their pollinator dependence, is
-necessary for a balanced understanding of plant economics.
+pollinators\textsuperscript{\protect\hyperlink{ref-ollerton2011}{32}}.
+However, it is still unknown to what extent these different reproductive
+compromises determine plant-pollinator associations.
 
@@
 plant-pollinator network
-properties\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3},\protect\hyperlink{ref-lazaro2008}{26},\protect\hyperlink{ref-bartomeus2013}{27}}.
-Moreover, plant traits can also define species' network roles (e.g.,
-specialists vs generalists). For example, species that occupy trait
-space extremes are more likely to exhibit higher specialization and be
-more reliant on
-trait-matching\textsuperscript{\protect\hyperlink{ref-junker2013}{28},\protect\hyperlink{ref-coux2016}{29}}.
+properties\textsuperscript{\protect\hyperlink{ref-bartomeus2013}{33}--\protect\hyperlink{ref-rowe2020}{35}}.
+Moreover, plant traits can also define species' network roles
+(\protect\hyperlink{ref-lazaro2013}{36};
+\protect\hyperlink{ref-tur2013}{20})(e.g., specialists vs generalists).
+For example, species that occupy trait space extremes are more likely to
+exhibit higher specialization and be more reliant on
+trait-matching\textsuperscript{\protect\hyperlink{ref-junker2013}{37},\protect\hyperlink{ref-coux2016}{38}}.
 This morphological matching between plant and floral visitors can
@@
 interaction network
-structure\textsuperscript{\protect\hyperlink{ref-stang2009}{30},\protect\hyperlink{ref-ibanez2012}{31}}.
-Despite the increasing knowledge of the relevance of traits on the
-species network roles, little is known about how plant reproductive and
-floral traits determine plant species' network roles at a
-macroecological scale.
+structure\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-ibanez2012}{39}}.
+Remarkably, the combination of traits have shown to increase the
+predictive power of the network
+interactions\textsuperscript{\protect\hyperlink{ref-eklof2013}{40}}.
+Therefore, considering the different plant reproductive trade-offs which
+represent the species strategy within the
+network\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}} could
+progress our understanding of plant-pollinator interactions. Further, we
+know little if the different network patterns generally studied at the
+community level are maintained when we scale up at macroecological
+scale.
 
 Here, we explore the potential trade-offs among plant floral and
-reproductive biology traits and how these influence the structure of
-plant-pollinator networks. First, we identify the major axes of trait
+reproductive biology traits and how these influence plant-pollinator
+interactions. First, we identify the major axes of reproductive trait
 variation and trade-offs that determine plant form and function. Second,
 we investigate how plant species' position in trait-space influences
-their interaction patterns with different guilds of floral visitors.
+plant-pollinator interactions (presence-absence and visitation rate).
 Finally, we investigate how the main axes of trait variation and
-individual traits influence plant species roles within networks.
+individual traits influence plant species roles within networks using
+complementary interaction network metrics (i.e., interaction strength,
+normalized degree and specialization).
 
@@
 trade-off', as already described in previous
-studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{32},\protect\hyperlink{ref-kettle2011}{33}}.
+studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{41},\protect\hyperlink{ref-kettle2011}{42}}.
 Hence, one end of the spectrum comprised species with high investment in
@@
 described `fast-slow continuum' in
-plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}} and
-animal\textsuperscript{\protect\hyperlink{ref-healy2019}{34}}
+plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}} and
+animal\textsuperscript{\protect\hyperlink{ref-healy2019}{43}}
 life-history strategies as indicated by the different floral and
@@
 floral
-display\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{24}}.
+display\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{31}}.
 This trend was further confirmed when looking at the specific
@@
 reproductive
-investment\textsuperscript{\protect\hyperlink{ref-hegland2005}{35}--\protect\hyperlink{ref-kaiser2014}{37}}.
+investment\textsuperscript{\protect\hyperlink{ref-lazaro2013}{36},\protect\hyperlink{ref-hegland2005}{44},\protect\hyperlink{ref-kaiser2014}{45}}.
 In regard to the flower number - flower size and style length
@@
 (Fig. 3) indicating a possible niche partitioning among these two
-guilds\textsuperscript{\protect\hyperlink{ref-palmer2003}{38},\protect\hyperlink{ref-phillips2020}{39}}.
+guilds\textsuperscript{\protect\hyperlink{ref-palmer2003}{46},\protect\hyperlink{ref-phillips2020}{47}}.
 However, these plant-pollinator associations do not account for some of
@@
 complete descriptions of the pollination
-syndromes\textsuperscript{\protect\hyperlink{ref-dellinger2020}{13}}. In
+syndromes\textsuperscript{\protect\hyperlink{ref-dellinger2020}{4}}. In
 any case, it is worth noting that this general pattern emerges in
@@
 as species relative abundances, will surely explain part of the observed
-variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{12},\protect\hyperlink{ref-vazquez2007}{40},\protect\hyperlink{ref-encinas2012}{41}}.
+variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{17},\protect\hyperlink{ref-vazquez2007}{48},\protect\hyperlink{ref-encinas2012}{49}}.
 
@@
 have evaluated life histories with vegetative
-traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}},
+traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{25}},
 this percentage is consistent with the largest and most recent study
@@
 reproductive (i.e., semelparity and iteroparity)
-traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}}. Future
+traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}}. Future
 work needs to integrate these floral and reproductive compromises with
 the already described vegetative and physiological
-trade-offs\textsuperscript{\protect\hyperlink{ref-diaz2016}{18}} to
+trade-offs\textsuperscript{\protect\hyperlink{ref-diaz2016}{24}} to
 create a more comprehensive spectrum of trait
-variation\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}}.
+variation\textsuperscript{\protect\hyperlink{ref-roddy2021}{5}}.
 Further, the varying level of phylogenetic signal among traits deserves
@@
 flower morphology in response to
-pollinators\textsuperscript{\protect\hyperlink{ref-gervasi2017}{42},\protect\hyperlink{ref-mackin2021}{43}}.
+pollinators\textsuperscript{\protect\hyperlink{ref-gervasi2017}{50},\protect\hyperlink{ref-mackin2021}{51}}.
 Finally, a more complete description of the macroecological patterns of
 plant-pollinator interactions including unrepresented areas of the
-world\textsuperscript{\protect\hyperlink{ref-poisot2021}{44}} and traits
+world\textsuperscript{\protect\hyperlink{ref-poisot2021}{52}} and traits
 that have been largely ignored (e.g., floral rewards and plant mating
@@
 of these networks are freely available either as published
-studies\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{3},\protect\hyperlink{ref-fortuna2010}{45}}
+studies\textsuperscript{\protect\hyperlink{ref-fortuna2010}{53},\protect\hyperlink{ref-carvalheiro2014}{54}}
 or available in online archives (e.g., `The Web of
-Life'\textsuperscript{\protect\hyperlink{ref-fortuna2010}{45}} and
-`Mangal'\textsuperscript{\protect\hyperlink{ref-poisot2016}{46}}. In
+Life'\textsuperscript{\protect\hyperlink{ref-fortuna2010}{53}} and
+`Mangal'\textsuperscript{\protect\hyperlink{ref-poisot2016}{55}}. In
 total, our network dataset (see Supplementary Table S1) constituted 60
@@
 R package
-\emph{taxize}\textsuperscript{\protect\hyperlink{ref-chamberlain2020}{47}}.
+\emph{taxize}\textsuperscript{\protect\hyperlink{ref-chamberlain2020}{56}}.
 We filled the `not found' searches manually using
@@
 implementation of the Open Tree of
-Life\textsuperscript{\protect\hyperlink{ref-smith2018}{48},\protect\hyperlink{ref-jin2019}{49}}.
+Life\textsuperscript{\protect\hyperlink{ref-smith2018}{57},\protect\hyperlink{ref-jin2019}{58}}.
 
@@
 function
-\emph{missForest}\textsuperscript{\protect\hyperlink{ref-stekhoven2012}{50}}
+\emph{missForest}\textsuperscript{\protect\hyperlink{ref-stekhoven2012}{59}}
 which allows imputation of data sets with continuous and categorical
@@
 shown to improve the performance of
-\emph{missForest}\textsuperscript{\protect\hyperlink{ref-penone2014}{51}}.
+\emph{missForest}\textsuperscript{\protect\hyperlink{ref-penone2014}{60}}.
 To extract the eigenvectors, we used the function \emph{PVRdecomp} from
 the package
-\emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{52}} based
+\emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{61}} based
 on a previous conceptual framework that considers phylogenetic
-eigenvectors\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{53}}.
+eigenvectors\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{62}}.
 Although the variable of autonomous selfing had a high percentage of
@@
 values within the 2.5th--97.5th percentile
-range\textsuperscript{\protect\hyperlink{ref-legendre2012}{54}}, and
+range\textsuperscript{\protect\hyperlink{ref-legendre2012}{63}}, and
 thus our final dataset had 1,236 species. Then, we log transformed the
@@
 performed the pPCA using the function \emph{phyl.pca} from the package
-\emph{phytools}\textsuperscript{\protect\hyperlink{ref-revell2012}{55}}
+\emph{phytools}\textsuperscript{\protect\hyperlink{ref-revell2012}{64}}
 with the method lambda (\(\lambda\)) that calculates the phylogenetic
@@
 values for each variables were on the same scale following
-transformation\textsuperscript{\protect\hyperlink{ref-abdi2010}{56}}.
+transformation\textsuperscript{\protect\hyperlink{ref-abdi2010}{65}}.
 Moreover, to corroborate that our imputation of missing values did not
@@
 version
-\emph{0.7-70}\textsuperscript{\protect\hyperlink{ref-revell2012}{55}}
+\emph{0.7-70}\textsuperscript{\protect\hyperlink{ref-revell2012}{64}}
 and we used Pagel's \(\lambda\) as a measurement of the phylogenetic
@@
 species
-efficiency\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{57}},
+efficiency\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{66}},
 interaction frequency can provide valuable information of the
 contribution of floral visitors to
-pollination\textsuperscript{\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}}.
+pollination\textsuperscript{\protect\hyperlink{ref-vazquez2005}{67},\protect\hyperlink{ref-vazquez2012}{68}}.
 In total, our network dataset (excluding meta-webs and non-weighted
@@
 a similar dataset of 80 plant-pollinator networks in natural
-ecosystems\textsuperscript{\protect\hyperlink{ref-hung2018}{60}}. Hence,
+ecosystems\textsuperscript{\protect\hyperlink{ref-hung2018}{69}}. Hence,
 to control for the effect of \emph{A. mellifera} on the observed
@@
 package
-\emph{brms}\textsuperscript{\protect\hyperlink{ref-burkner2017}{61}}. We
+\emph{brms}\textsuperscript{\protect\hyperlink{ref-burkner2017}{70}}. We
 modelled the frequency of visits as a function of the main axes of plant
@@
 the \emph{bayesplot}
-package\textsuperscript{\protect\hyperlink{ref-gabry2019}{62}}.
+package\textsuperscript{\protect\hyperlink{ref-gabry2019}{71}}.
 
@@
 in bipartite network
-studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{63}} with a
+studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{72}} with a
 straightforward ecological interpretation relevant to our research
@@
 partners; and (iii)
-specialization\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{64}},
+specialization\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{73}},
 which measures the deviation of an expected random choice of the
@@
 from the R package
-\emph{bipartite}\textsuperscript{\protect\hyperlink{ref-dormann2008}{63}}.
+\emph{bipartite}\textsuperscript{\protect\hyperlink{ref-dormann2008}{72}}.
 
@@
 using the \emph{rpart}
-package\textsuperscript{\protect\hyperlink{ref-therneau2015}{65}}
+package\textsuperscript{\protect\hyperlink{ref-therneau2015}{74}}
 version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50
 observations per terminal node and we used the \emph{rpart.plot}
-package\textsuperscript{\protect\hyperlink{ref-milborrow2015}{66}}
+package\textsuperscript{\protect\hyperlink{ref-milborrow2015}{75}}
 version \emph{3.0.9} to plot the regression trees. We considered the
@@
 
-\hypertarget{ref-carvalheiro2014}{}
-3. Carvalheiro, L. G. \emph{et al.} The potential for indirect effects
-between co-flowering plants via shared pollinators depends on resource
-abundance, accessibility and relatedness. \emph{Ecol. Lett.}
-\textbf{17}, 1389--1399 (2014).
+\hypertarget{ref-fenster2004}{}
+3. Fenster, C. B., Armbruster, W. S., Wilson, P., Dudash, M. R. \&
+Thomson, J. D. Pollination Syndromes and Floral Specialization.
+\emph{Annu. Rev. Ecol. Evol. Syst.} \textbf{35}, 375--403 (2004).
+
+\hypertarget{ref-dellinger2020}{}
+4. Dellinger, A. S. Pollination syndromes in the 21st century: Where do
+we stand and where may we go? \emph{New Phytol.} \textbf{228},
+1193--1213 (2020).
+
+\hypertarget{ref-roddy2021}{}
+5. Roddy, A. B. \emph{et al.} Towards the flower economics spectrum.
+\emph{New Phytol.} \textbf{229}, 665--672 (2021).
 
 \hypertarget{ref-baude2016}{}
-4. Baude, M. \emph{et al.} Historical nectar assessment reveals the fall
+6. Baude, M. \emph{et al.} Historical nectar assessment reveals the fall
 and rise of floral resources in britain. \emph{Nature} \textbf{530},
@@
 \hypertarget{ref-munoz2016}{}
-5. Munoz, F., Violle, C. \& Cheptou, P.-O. CSR ecological strategies and
+7. Munoz, F., Violle, C. \& Cheptou, P.-O. CSR ecological strategies and
 plant mating systems: Outcrossing increases with competitiveness but
@@
 
+\hypertarget{ref-grossenbacher2017}{}
+8. Grossenbacher, D. L. \emph{et al.} Self-compatibility is
+over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478
+(2017).
+
 \hypertarget{ref-moeller2017}{}
-6. Moeller, D. A. \emph{et al.} Global biogeography of mating system
+9. Moeller, D. A. \emph{et al.} Global biogeography of mating system
 variation in seed plants. \emph{Ecol. Lett.} \textbf{20}, 375--384
@@
 
-\hypertarget{ref-grossenbacher2017}{}
-7. Grossenbacher, D. L. \emph{et al.} Self-compatibility is
-over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478
-(2017).
+\hypertarget{ref-sargent2008}{}
+10. Sargent, R. D. \& Ackerly, D. D. Plant--pollinator interactions and
+the assembly of plant communities. \emph{Trends in Ecology \& Evolution}
+\textbf{23}, 123--130 (2008).
+
+\hypertarget{ref-rech2016}{}
+11. Rech, A. R. \emph{et al.} The macroecology of animal versus wind
+pollination: Ecological factors are more important than historical
+climate stability. \emph{Plant Ecology \& Diversity} \textbf{9},
+253--262 (2016).
 
 \hypertarget{ref-salguero2016}{}
-8. Salguero-Gómez, R. \emph{et al.} Fast-slow continuum and reproductive
-strategies structure plant life-history variation worldwide. \emph{Proc.
-Natl. Acad. Sci. U.S.A.} \textbf{113}, 230--235 (2016).
+12. Salguero-Gómez, R. \emph{et al.} Fast-slow continuum and
+reproductive strategies structure plant life-history variation
+worldwide. \emph{Proc. Natl. Acad. Sci. U.S.A.} \textbf{113}, 230--235
+(2016).
 
 \hypertarget{ref-ruger2018}{}
-9. Rüger, N. \emph{et al.} Beyond the fastSlow continuum: Demographic
+13. Rüger, N. \emph{et al.} Beyond the fastSlow continuum: Demographic
 dimensions structuring a tropical tree community. \emph{Ecol. Lett.}
@@
 
-\hypertarget{ref-roddy2021}{}
-10. Roddy, A. B. \emph{et al.} Towards the flower economics spectrum.
-\emph{New Phytol.} \textbf{229}, 665--672 (2021).
-
-\hypertarget{ref-fenster2004}{}
-11. Fenster, C. B., Armbruster, W. S., Wilson, P., Dudash, M. R. \&
-Thomson, J. D. Pollination Syndromes and Floral Specialization.
-\emph{Annu. Rev. Ecol. Evol. Syst.} \textbf{35}, 375--403 (2004).
+\hypertarget{ref-dehling2016}{}
+14. Dehling, D. M., Jordano, P., Schaefer, H. M., Böhning-Gaese, K. \&
+Schleuning, M. Morphology predicts species' functional roles and their
+degree of specialization in plant--frugivore interactions.
+\emph{Proceedings of the Royal Society B: Biological Sciences}
+\textbf{283}, 20152444 (2016).
+
+\hypertarget{ref-rosas2014}{}
+15. Rosas-Guerrero, V. \emph{et al.} A quantitative review of
+pollination syndromes: Do floral traits predict effective pollinators?
+\emph{Ecology letters} \textbf{17}, 388--400 (2014).
+
+\hypertarget{ref-stang2009}{}
+16. Stang, M., Klinkhamer, P. G. L., Waser, N. M., Stang, I. \& van der
+Meijden, E. Size-specific interaction patterns and size matching in a
+plantPollinator interaction web. \emph{Ann. Bot.} \textbf{103},
+1459--1469 (2009).
 
 \hypertarget{ref-bartomeus2016}{}
-12. Bartomeus, I. \emph{et al.} A common framework for identifying
+17. Bartomeus, I. \emph{et al.} A common framework for identifying
 linkage rules across different types of interactions. \emph{Funct.
@@
 
-\hypertarget{ref-dellinger2020}{}
-13. Dellinger, A. S. Pollination syndromes in the 21st century: Where do
-we stand and where may we go? \emph{New Phytol.} \textbf{228},
-1193--1213 (2020).
+\hypertarget{ref-waser1996}{}
+18. Waser, N. M., Chittka, L., Price, M. V., Williams, N. M. \&
+Ollerton, J. Generalization in pollination systems, and why it matters.
+\emph{Ecology} \textbf{77}, 1043--1060 (1996).
+
+\hypertarget{ref-olesen2002}{}
+19. Olesen, J. M. \& Jordano, P. Geographic patterns in
+plant--pollinator mutualistic networks. \emph{Ecology} \textbf{83},
+2416--2424 (2002).
 
 \hypertarget{ref-tur2013}{}
-14. Tur, C., Castro-Urgal, R. \& Traveset, A. Linking Plant
+20. Tur, C., Castro-Urgal, R. \& Traveset, A. Linking Plant
 Specialization to Dependence in Interactions for Seed Set in Pollination
@@
 \hypertarget{ref-devaux2014}{}
-15. Devaux, C., Lepers, C. \& Porcher, E. Constraints imposed by
+21. Devaux, C., Lepers, C. \& Porcher, E. Constraints imposed by
 pollinator behaviour on the ecology and evolution of plant mating
@@
 \hypertarget{ref-kattge2011}{}
-16. Kattge, J. \emph{et al.} TRY a global database of plant traits.
+22. Kattge, J. \emph{et al.} TRY a global database of plant traits.
 \emph{Glob. Chang. Biol.} \textbf{17}, 2905--2935 (2011).
@@
 \hypertarget{ref-salguero2015}{}
-17. Salguero-Gómez, R. \emph{et al.} The compadre Plant Matrix Database:
+23. Salguero-Gómez, R. \emph{et al.} The compadre Plant Matrix Database:
 An open online repository for plant demography. \emph{J. Ecol.}
@@
 \hypertarget{ref-diaz2016}{}
-18. Díaz, S. \emph{et al.} The global spectrum of plant form and
+24. Díaz, S. \emph{et al.} The global spectrum of plant form and
 function. \emph{Nature} \textbf{529}, 167--171 (2016).
@@
 \hypertarget{ref-carmona2021}{}
-19. Carmona, C. P. \emph{et al.} Erosion of global functional diversity
+25. Carmona, C. P. \emph{et al.} Erosion of global functional diversity
 across the tree of life. \emph{Sci. Adv.} \textbf{7}, eabf2675 (2021).
@@
 \hypertarget{ref-wright2004}{}
-20. Wright, I. J. \emph{et al.} The worldwide leaf economics spectrum.
+26. Wright, I. J. \emph{et al.} The worldwide leaf economics spectrum.
 \emph{Nature} \textbf{428}, 821--827 (2004).
@@
 \hypertarget{ref-chave2009}{}
-21. Chave, J. \emph{et al.} Towards a worldwide wood economics spectrum.
+27. Chave, J. \emph{et al.} Towards a worldwide wood economics spectrum.
 \emph{Ecol. Lett.} \textbf{12}, 351--366 (2009).
 
+\hypertarget{ref-laughlin2021}{}
+28. Laughlin, D. C. \emph{et al.} Root traits explain plant species
+distributions along climatic gradients yet challenge the nature of
+ecological trade-offs. \emph{Nature Ecology \& Evolution} 1--12 (2021).
+
 \hypertarget{ref-evojtko2020}{}
-22. E-Vojtkó, A., Bello, F. de, Durka, W., Kühn, I. \& Götzenberger, L.
+29. E-Vojtkó, A., Bello, F. de, Durka, W., Kühn, I. \& Götzenberger, L.
 The neglected importance of floral traits in trait-based plant community
@@
 \hypertarget{ref-barrett2003}{}
-23. Barrett, S. C. H. Mating strategies in flowering plants: The
+30. Barrett, S. C. H. Mating strategies in flowering plants: The
 outcrossing-selfing paradigm and beyond. \emph{Philos. Trans. R. Soc.
@@
 \hypertarget{ref-goodwillie2010}{}
-24. Goodwillie, C. \emph{et al.} Correlated evolution of mating system
+31. Goodwillie, C. \emph{et al.} Correlated evolution of mating system
 and floral display traits in flowering plants and its implications for
@@
 \hypertarget{ref-ollerton2011}{}
-25. Ollerton, J., Winfree, R. \& Tarrant, S. How many flowering plants
+32. Ollerton, J., Winfree, R. \& Tarrant, S. How many flowering plants
 are pollinated by animals? \emph{Oikos} \textbf{120}, 321--326 (2011).
 
-\hypertarget{ref-lazaro2008}{}
-26. Lázaro, A., Hegland, S. J. \& Totland, Ø. The relationships between
-floral traits and specificity of pollination systems in three
-Scandinavian plant communities. \emph{Oecologia} \textbf{157}, 249--257
-(2008).
-
 \hypertarget{ref-bartomeus2013}{}
-27. Bartomeus, I. Understanding Linkage Rules in Plant-Pollinator
+33. Bartomeus, I. Understanding Linkage Rules in Plant-Pollinator
 Networks by Using Hierarchical Models That Incorporate Pollinator
@@
 
-\hypertarget{ref-junker2013}{}
-28. Junker, R. R. \emph{et al.} Specialization on traits as basis for
-the niche-breadth of flower visitors and as structuring mechanism of
-ecological networks. \emph{Funct. Ecol.} \textbf{27}, 329--341 (2013).
-
-\hypertarget{ref-coux2016}{}
-29. Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking
-species functional roles to their network roles. \emph{Ecol. Lett.}
-\textbf{19}, 762--770 (2016).
-
-\hypertarget{ref-stang2009}{}
-30. Stang, M., Klinkhamer, P. G. L., Waser, N. M., Stang, I. \& van der
-Meijden, E. Size-specific interaction patterns and size matching in a
-plantPollinator interaction web. \emph{Ann. Bot.} \textbf{103},
-1459--1469 (2009).
-
-\hypertarget{ref-ibanez2012}{}
-31. Ibanez, S. Optimizing size thresholds in a plant-pollinator
-interaction web: Towards a mechanistic understanding of ecological
-networks. \emph{Oecologia} \textbf{170}, 233--242 (2012).
-
-\hypertarget{ref-sargent2007}{}
-32. Sargent, R. D., Goodwillie, C., Kalisz, S. \& Ree, R. H.
-Phylogenetic evidence for a flower size and number trade-off. \emph{Am.
-J. Bot.} \textbf{94}, 2059--2062 (2007).
-
-\hypertarget{ref-kettle2011}{}
-33. Kettle, C. J. \emph{et al.} Ecological Implications of a Flower
-Size/Number Trade-Off in Tropical Forest Trees. \emph{PLoS One}
-\textbf{6}, e16111 (2011).
-
-\hypertarget{ref-healy2019}{}
-34. Healy, K., Ezard, T. H. G., Jones, O. R., Salguero-Gómez, R. \&
-Buckley, Y. M. Animal life history is shaped by the pace of life and the
-distribution of age-specific mortality and reproduction. \emph{Nat.
-Ecol. Evol} \textbf{3}, 1217--1224 (2019).
-
-\hypertarget{ref-hegland2005}{}
-35. Hegland, S. J. \& Totland, Ø. Relationships between species' floral
-traits and pollinator visitation in a temperate grassland.
-\emph{Oecologia} \textbf{145}, 586--594 (2005).
+\hypertarget{ref-olito2015}{}
+34. Olito, C. \& Fox, J. W. Species traits and abundances predict
+metrics of plantPollinator network structure, but not pairwise
+interactions. \emph{Oikos} \textbf{124}, 428--436 (2015).
+
+\hypertarget{ref-rowe2020}{}
+35. Rowe, L. \emph{et al.} Flower traits associated with the visitation
+patterns of bees. \emph{Oecologia} \textbf{193}, 511--522 (2020).
 
@@
 
+\hypertarget{ref-junker2013}{}
+37. Junker, R. R. \emph{et al.} Specialization on traits as basis for
+the niche-breadth of flower visitors and as structuring mechanism of
+ecological networks. \emph{Funct. Ecol.} \textbf{27}, 329--341 (2013).
+
+\hypertarget{ref-coux2016}{}
+38. Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking
+species functional roles to their network roles. \emph{Ecol. Lett.}
+\textbf{19}, 762--770 (2016).
+
+\hypertarget{ref-ibanez2012}{}
+39. Ibanez, S. Optimizing size thresholds in a plant-pollinator
+interaction web: Towards a mechanistic understanding of ecological
+networks. \emph{Oecologia} \textbf{170}, 233--242 (2012).
+
+\hypertarget{ref-eklof2013}{}
+40. Eklöf, A. \emph{et al.} The dimensionality of ecological networks.
+\emph{Ecology letters} \textbf{16}, 577--583 (2013).
+
+\hypertarget{ref-sargent2007}{}
+41. Sargent, R. D., Goodwillie, C., Kalisz, S. \& Ree, R. H.
+Phylogenetic evidence for a flower size and number trade-off. \emph{Am.
+J. Bot.} \textbf{94}, 2059--2062 (2007).
+
+\hypertarget{ref-kettle2011}{}
+42. Kettle, C. J. \emph{et al.} Ecological Implications of a Flower
+Size/Number Trade-Off in Tropical Forest Trees. \emph{PLoS One}
+\textbf{6}, e16111 (2011).
+
+\hypertarget{ref-healy2019}{}
+43. Healy, K., Ezard, T. H. G., Jones, O. R., Salguero-Gómez, R. \&
+Buckley, Y. M. Animal life history is shaped by the pace of life and the
+distribution of age-specific mortality and reproduction. \emph{Nat.
+Ecol. Evol} \textbf{3}, 1217--1224 (2019).
+
+\hypertarget{ref-hegland2005}{}
+44. Hegland, S. J. \& Totland, Ø. Relationships between species' floral
+traits and pollinator visitation in a temperate grassland.
+\emph{Oecologia} \textbf{145}, 586--594 (2005).
+
 \hypertarget{ref-kaiser2014}{}
-37. Kaiser-Bunbury, C. N., Vázquez, D. P., Stang, M. \& Ghazoul, J.
+45. Kaiser-Bunbury, C. N., Vázquez, D. P., Stang, M. \& Ghazoul, J.
 Determinants of the microstructure of plantPollinator networks.
@@
 \hypertarget{ref-palmer2003}{}
-38. Palmer, T. M., Stanton, M. L. \& Young, T. P. Competition and
+46. Palmer, T. M., Stanton, M. L. \& Young, T. P. Competition and
 coexistence: Exploring mechanisms that restrict and maintain diversity
@@
 \hypertarget{ref-phillips2020}{}
-39. Phillips, R. D., Peakall, R., van der Niet, T. \& Johnson, S. D.
+47. Phillips, R. D., Peakall, R., van der Niet, T. \& Johnson, S. D.
 Niche perspectives on plantPollinator interactions. \emph{Trends Plant
@@
 \hypertarget{ref-vazquez2007}{}
-40. Vázquez, D. P. \emph{et al.} Species abundance and asymmetric
+48. Vázquez, D. P. \emph{et al.} Species abundance and asymmetric
 interaction strength in ecological networks. \emph{Oikos} \textbf{116},
@@
 \hypertarget{ref-encinas2012}{}
-41. Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives
+49. Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives
 mutualistic network structure and diversity. \emph{Ecol. Lett.}
@@
 \hypertarget{ref-gervasi2017}{}
-42. Gervasi, D. D. L. \& Schiestl, F. P. Real-time divergent evolution
+50. Gervasi, D. D. L. \& Schiestl, F. P. Real-time divergent evolution
 in plants driven by pollinators. \emph{Nat. Commun.} \textbf{8}, 14691
@@
 \hypertarget{ref-mackin2021}{}
-43. Mackin, C. R., Peña, J. F., Blanco, M. A., Balfour, N. J. \&
+51. Mackin, C. R., Peña, J. F., Blanco, M. A., Balfour, N. J. \&
 Castellanos, M. C. Rapid evolution of a floral trait following
@@
 \hypertarget{ref-poisot2021}{}
-44. Poisot, T. \emph{et al.} Global knowledge gaps in species
+52. Poisot, T. \emph{et al.} Global knowledge gaps in species
 interaction networks data. \emph{J. Biogeogr.} \textbf{48}, 1552--1563
@@
 \hypertarget{ref-fortuna2010}{}
-45. Fortuna, M. A. \emph{et al.} Nestedness versus modularity in
+53. Fortuna, M. A. \emph{et al.} Nestedness versus modularity in
 ecological networks: Two sides of the same coin? \emph{J. Anim. Ecol.}
@@
 
+\hypertarget{ref-carvalheiro2014}{}
+54. Carvalheiro, L. G. \emph{et al.} The potential for indirect effects
+between co-flowering plants via shared pollinators depends on resource
+abundance, accessibility and relatedness. \emph{Ecol. Lett.}
+\textbf{17}, 1389--1399 (2014).
+
 \hypertarget{ref-poisot2016}{}
-46. Poisot, T. \emph{et al.} Mangal making ecological network analysis
+55. Poisot, T. \emph{et al.} Mangal making ecological network analysis
 simple. \emph{Ecography} \textbf{39}, 384--390 (2016).
@@
 \hypertarget{ref-chamberlain2020}{}
-47. Chamberlain, S. \emph{et al.} Taxize: Taxonomic information from
+56. Chamberlain, S. \emph{et al.} Taxize: Taxonomic information from
 around the web. r package version 0.9.99 (2020).~at
@@
 \hypertarget{ref-smith2018}{}
-48. Smith, S. A. \& Brown, J. W. Constructing a broadly inclusive seed
+57. Smith, S. A. \& Brown, J. W. Constructing a broadly inclusive seed
 plant phylogeny. \emph{Am. J. Bot.} \textbf{105}, 302--314 (2018).
@@
 \hypertarget{ref-jin2019}{}
-49. Jin, Y. \& Qian, H. V.PhyloMaker: An R package that can generate
+58. Jin, Y. \& Qian, H. V.PhyloMaker: An R package that can generate
 very large phylogenies for vascular plants. \emph{Ecography}
@@
 \hypertarget{ref-stekhoven2012}{}
-50. Stekhoven, D. J. \& Bühlmann, P. MissForestNon-parametric missing
+59. Stekhoven, D. J. \& Bühlmann, P. MissForestNon-parametric missing
 value imputation for mixed-type data. \emph{Bioinformatics} \textbf{28},
@@
 \hypertarget{ref-penone2014}{}
-51. Penone, C. \emph{et al.} Imputation of missing data in life-history
+60. Penone, C. \emph{et al.} Imputation of missing data in life-history
 trait datasets: Which approach performs the best? \emph{Methods Ecol.
@@
 \hypertarget{ref-santos2018}{}
-52. Chamberlain, S. \emph{et al.} Package `PVR'. r package version 0.3
+61. Chamberlain, S. \emph{et al.} Package `PVR'. r package version 0.3
 (2018).~at
@@
 \hypertarget{ref-diniz-filho2012}{}
-53. Diniz-Filho, J. A. F. \emph{et al.} On the selection of phylogenetic
+62. Diniz-Filho, J. A. F. \emph{et al.} On the selection of phylogenetic
 eigenvectors for ecological analyses. \emph{Ecography} \textbf{35},
@@
 \hypertarget{ref-legendre2012}{}
-54. Legendre, P. \& Legendre, L. \emph{Numerical ecology}. (Elsevier,
+63. Legendre, P. \& Legendre, L. \emph{Numerical ecology}. (Elsevier,
 Amsterdam, 2012).
@@
 \hypertarget{ref-revell2012}{}
-55. Revell, L. J. Phytools: An R package for phylogenetic comparative
+64. Revell, L. J. Phytools: An R package for phylogenetic comparative
 biology (and other things). \emph{Methods Ecol. Evol.} \textbf{3},
@@
 \hypertarget{ref-abdi2010}{}
-56. Abdi, H. \& Williams, L. J. Principal component analysis.
+65. Abdi, H. \& Williams, L. J. Principal component analysis.
 \emph{WIREs Comp. Stats.} \textbf{2}, 433--459 (2010).
@@
 \hypertarget{ref-ballantyne2015}{}
-57. Ballantyne, G., Baldock, K. C. R. \& Willmer, P. G. Constructing
+66. Ballantyne, G., Baldock, K. C. R. \& Willmer, P. G. Constructing
 more informative plantPollinator networks: Visitation and pollen
@@
 \hypertarget{ref-vazquez2005}{}
-58. Vázquez, D. P., Morris, W. F. \& Jordano, P. Interaction frequency
+67. Vázquez, D. P., Morris, W. F. \& Jordano, P. Interaction frequency
 as a surrogate for the total effect of animal mutualists on plants.
@@
 \hypertarget{ref-vazquez2012}{}
-59. Vázquez, D. P. \emph{et al.} The strength of plantPollinator
+68. Vázquez, D. P. \emph{et al.} The strength of plantPollinator
 interactions. \emph{Ecology} \textbf{93}, 719--725 (2012).
@@
 \hypertarget{ref-hung2018}{}
-60. Hung, K.-L. J., Kingston, J. M., Albrecht, M., Holway, D. A. \&
+69. Hung, K.-L. J., Kingston, J. M., Albrecht, M., Holway, D. A. \&
 Kohn, J. R. The worldwide importance of honey bees as pollinators in
@@
 \hypertarget{ref-burkner2017}{}
-61. Bürkner, P.-C. Brms: An R package for Bayesian multilevel models
+70. Bürkner, P.-C. Brms: An R package for Bayesian multilevel models
 using Stan. \emph{J. Stat. Softw.} \textbf{80}, 1--28 (2017).
@@
 \hypertarget{ref-gabry2019}{}
-62. Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A.
+71. Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A.
 Visualization in Bayesian workflow. \emph{J. R. Stat. Soc. Ser. A Stat.
@@
 \hypertarget{ref-dormann2008}{}
-63. Dormann, C. F., Gruber, B. \& Fründ, J. Introducing the bipartite
+72. Dormann, C. F., Gruber, B. \& Fründ, J. Introducing the bipartite
 package: Analysing ecological networks. \emph{interaction} \textbf{1},
@@
 \hypertarget{ref-bluthgen2006}{}
-64. Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in
+73. Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in
 species interaction networks. \emph{BMC Ecol.} \textbf{6}, 9 (2006).
@@
 \hypertarget{ref-therneau2015}{}
-65. Therneau, T., Atkinson, B., Ripley, B. \& Ripley, M. B. Package
+74. Therneau, T., Atkinson, B., Ripley, B. \& Ripley, M. B. Package
 `rpart'. r package version 4.1-15 (2015).~at
@@
 \hypertarget{ref-milborrow2015}{}
-66. Milborrow, S. Rpart. plot: Plot rpart Models. An Enhanced Version of
+75. Milborrow, S. Rpart. plot: Plot rpart Models. An Enhanced Version of
 plot. rpart. r package version 3.0.9 (2015).~at

### 2021-10-06 Manuscript/Manuscript.Rmd
edits

@@
 Several studies have identified links between plant traits and plant-pollinator network properties [@bartomeus2013; @olito2015; @rowe2020].
-Moreover, plant traits can also define species' network roles (@lazaro2013; @tur2013)(e.g., specialists vs generalists).
+Moreover, plant traits can also define species' network roles [@lazaro2013; @tur2013] (e.g., specialists vs generalists).
 For example, species that occupy trait space extremes are more likely to exhibit higher specialization and be more reliant on trait-matching [@junker2013; @coux2016].
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.align='center',fig.width=10,fig.cap= "**Fig.
-1 | Plant life-history strategies.** Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Fig.
+1 | Plant life-history strategies.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
 The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
@@
 
-**Visitation patterns.** The main axes of trait variation explained little of the overall visitation rates ($conditional R2 = 0.31$; $marginal R2 = 0.06$) but showed relevant trends when we explored the interaction with the different floral visitor guilds (Fig.
+**Visitation patterns.** The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors ($conditional R2 = 0.26$; $marginal R2 = 0.20$) but little of the overall visitation rates ($conditional R2 = 0.31$; $marginal R2 = 0.06$).
+However, we found relevant trends across the different floral visitor guilds on both presence-absence and visitation interactions (Fig.
 3).
-All floral visitor guilds visited plant species with higher pollinator dependence more frequently (PC2; Fig.
+On the pollinator dependence trade-off, all floral visitor guilds interacted more frequently with plant species with higher pollinator dependence (PC2; Fig.
 3b and Fig.
 3e).
+For presence-absence interactions we found that all Diptera, Coleoptera and non-bee Hymenoptera guilds interacted more frequently with plants with high flower number and small flowers (flower number - flower size trade-off, PC1; Fig.
+3a) but bees and Lepidoptera interacted slightly more frequently with plant species with low flower number but large flowers.
+For presence-absence interactions on PC3 (style length trade-off; Fig.
+3c), we found that bees interacted clearly more with plant species with long styles and high selfing and the rest of the guilds interacted slightly more with plant species with short styles and low selfing.
 In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig.
+3d).
+On the style length trade-off, bees, Lepidoptera and Non-Anthophila-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
+3f).
+
+The additional model for both presence-absence ($marginal R2 = 0.29$; $conditional R2 = 0.19$) and visitation rate ($marginal R2 = 0.30$; $conditional R2 = 0.03$) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns and that the contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
 3a and Fig.
-3d).
-On the style length trade-off (PC3), Anthophila-Hymenoptera, Lepidoptera and Non-Anthophila-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
-3c and Fig.
-3f).
-Furthermore, when running an additional model that separates the most represented families of Anthophila-Hymenoptera (bees; $marginal R2 = 0.30$; $conditional R2 = 0.03$) showed that the family Apidae was the main driver of the observed patterns (Supplementary Fig.
+3d) were driven by the family Andrenidae which interacted more frequently on presence-absence interactions with plant species with low number of flower but large (Supplementary Fig.
 S8).
@@
 These trade-offs are differentiated on three main axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-Although these axes of trait variation did not explain overall visitation rates, we found that plant life strategies were clearly associated with different floral visitor guilds.
+These axes of trait variation explained partly the presence-absence interactions between plants and floral visitors but did not explain the overall visitation rates.
+However, on both qualitative and quantitative interactions floral visitor guilds showed associations with the different reproductive trade-offs.
 Interestingly, pollen and nectar related traits were better than all other traits for characterizing plant species functional roles within their interaction networks.
@@
 
-Despite the low predictive power of the main axes of trait variation on overall visitation patterns, we found commonalities among and within floral visitors guilds across these axes that indicate the influence of life-history strategies on floral visitation rate.
+Despite the low predictive power of the main axes of trait variation on overall interaction patterns (presence-absence and visitation rate), we found commonalities among and within floral visitors guilds across these axes that indicate the influence of life-history strategies on plant-pollinator interactions.
 For example, all guilds showed an increasing trend of visitation on plant species with higher pollinator dependence, which were also associated with larger floral displays and greater pollen quantities (Fig.

### 2021-10-06 Manuscript/Manuscript.tex
edits

@@
 properties\textsuperscript{\protect\hyperlink{ref-bartomeus2013}{33}--\protect\hyperlink{ref-rowe2020}{35}}.
-Moreover, plant traits can also define species' network roles
-(\protect\hyperlink{ref-lazaro2013}{36};
-\protect\hyperlink{ref-tur2013}{20})(e.g., specialists vs generalists).
-For example, species that occupy trait space extremes are more likely to
-exhibit higher specialization and be more reliant on
+Moreover, plant traits can also define species' network
+roles\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-lazaro2013}{36}}
+(e.g., specialists vs generalists). For example, species that occupy
+trait space extremes are more likely to exhibit higher specialization
+and be more reliant on
 trait-matching\textsuperscript{\protect\hyperlink{ref-junker2013}{37},\protect\hyperlink{ref-coux2016}{38}}.
@@
 
-\caption{**Fig.
-1 | Plant life-history strategies.** Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
+\caption{\textbf{Fig.
+1 | Plant life-history strategies.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
 The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
@@
 \textbf{Visitation patterns.} The main axes of trait variation explained
-little of the overall visitation rates (\(conditional R2 = 0.31\);
-\(marginal R2 = 0.06\)) but showed relevant trends when we explored the
-interaction with the different floral visitor guilds (Fig. 3). All
-floral visitor guilds visited plant species with higher pollinator
-dependence more frequently (PC2; Fig. 3b and Fig. 3e). In addition, all
-guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera,
-non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on
-species with small numerous flowers (PC1; Fig. 3a and Fig. 3d). On the
-style length trade-off (PC3), Anthophila-Hymenoptera, Lepidoptera and
+partly presence-absence interactions between plant and floral visitors
+(\(conditional R2 = 0.26\); \(marginal R2 = 0.20\)) but little of the
+overall visitation rates (\(conditional R2 = 0.31\);
+\(marginal R2 = 0.06\)). However, we found relevant trends across the
+different floral visitor guilds on both presence-absence and visitation
+interactions (Fig. 3). On the pollinator dependence trade-off, all
+floral visitor guilds interacted more frequently with plant species with
+higher pollinator dependence (PC2; Fig. 3b and Fig. 3e). For
+presence-absence interactions we found that all Diptera, Coleoptera and
+non-bee Hymenoptera guilds interacted more frequently with plants with
+high flower number and small flowers (flower number - flower size
+trade-off, PC1; Fig. 3a) but bees and Lepidoptera interacted slightly
+more frequently with plant species with low flower number but large
+flowers. For presence-absence interactions on PC3 (style length
+trade-off; Fig. 3c), we found that bees interacted clearly more with
+plant species with long styles and high selfing and the rest of the
+guilds interacted slightly more with plant species with short styles and
+low selfing. In addition, all guilds other than Syrphids and Lepidoptera
+(i.e., all Hymenoptera, non-Syrphidae-Diptera and Coleoptera) showed
+greater visitation rates on species with small numerous flowers (PC1;
+Fig. 3d). On the style length trade-off, bees, Lepidoptera and
 Non-Anthophila-Hymenoptera showed greater visitation rates on plant
@@
 Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation
-rates on species with shorter styles and lower selfing (Fig. 3c and Fig.
-3f). Furthermore, when running an additional model that separates the
-most represented families of Anthophila-Hymenoptera (bees;
-\(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) showed that the
-family Apidae was the main driver of the observed patterns
-(Supplementary Fig. S8).
+rates on species with shorter styles and lower selfing (Fig. 3f).
+
+The additional model for both presence-absence (\(marginal R2 = 0.29\);
+\(conditional R2 = 0.19\)) and visitation rate (\(marginal R2 = 0.30\);
+\(conditional R2 = 0.03\)) for the most represented families of bees
+showed that the family Apidae was the main driver of the observed
+patterns and that the contrasting differences between presence-absence
+and visitation rate for bees on PC1 (Fig. 3a and Fig. 3d) were driven by
+the family Andrenidae which interacted more frequently on
+presence-absence interactions with plant species with low number of
+flower but large (Supplementary Fig. S8).
 
@@
 differentiated on three main axes of trait variation: (i) flower number
-- flower size, (ii) pollinator dependence and (iii) style length.
-Although these axes of trait variation did not explain overall
-visitation rates, we found that plant life strategies were clearly
-associated with different floral visitor guilds. Interestingly, pollen
-and nectar related traits were better than all other traits for
-characterizing plant species functional roles within their interaction
-networks.
+- flower size, (ii) pollinator dependence and (iii) style length. These
+axes of trait variation explained partly the presence-absence
+interactions between plants and floral visitors but did not explain the
+overall visitation rates. However, on both qualitative and quantitative
+interactions floral visitor guilds showed associations with the
+different reproductive trade-offs. Interestingly, pollen and nectar
+related traits were better than all other traits for characterizing
+plant species functional roles within their interaction networks.
 
@@
 Despite the low predictive power of the main axes of trait variation on
-overall visitation patterns, we found commonalities among and within
-floral visitors guilds across these axes that indicate the influence of
-life-history strategies on floral visitation rate. For example, all
-guilds showed an increasing trend of visitation on plant species with
-higher pollinator dependence, which were also associated with larger
-floral displays and greater pollen quantities (Fig. 1 and Supplementary
-Fig. S6). This trend is consistent with previous plant-pollinator
-studies that show higher visitation rates on species that make greater
-reproductive
+overall interaction patterns (presence-absence and visitation rate), we
+found commonalities among and within floral visitors guilds across these
+axes that indicate the influence of life-history strategies on
+plant-pollinator interactions. For example, all guilds showed an
+increasing trend of visitation on plant species with higher pollinator
+dependence, which were also associated with larger floral displays and
+greater pollen quantities (Fig. 1 and Supplementary Fig. S6). This trend
+is consistent with previous plant-pollinator studies that show higher
+visitation rates on species that make greater reproductive
 investment\textsuperscript{\protect\hyperlink{ref-lazaro2013}{36},\protect\hyperlink{ref-hegland2005}{44},\protect\hyperlink{ref-kaiser2014}{45}}.
@@
 10. Sargent, R. D. \& Ackerly, D. D. Plant--pollinator interactions and
-the assembly of plant communities. \emph{Trends in Ecology \& Evolution}
+the assembly of plant communities. \emph{Trends Ecol. Evol.}
 \textbf{23}, 123--130 (2008).
@@
 pollination: Ecological factors are more important than historical
-climate stability. \emph{Plant Ecology \& Diversity} \textbf{9},
-253--262 (2016).
+climate stability. \emph{Plant Ecol. Divers.} \textbf{9}, 253--262
+(2016).
 
@@
 Schleuning, M. Morphology predicts species' functional roles and their
-degree of specialization in plant--frugivore interactions.
-\emph{Proceedings of the Royal Society B: Biological Sciences}
-\textbf{283}, 20152444 (2016).
+degree of specialization in plant--frugivore interactions. \emph{Proc.
+Royal Soc. B} \textbf{283}, 20152444 (2016).
 
@@
 pollination syndromes: Do floral traits predict effective pollinators?
-\emph{Ecology letters} \textbf{17}, 388--400 (2014).
+\emph{Ecol. Lett.} \textbf{17}, 388--400 (2014).
 
@@
 distributions along climatic gradients yet challenge the nature of
-ecological trade-offs. \emph{Nature Ecology \& Evolution} 1--12 (2021).
+ecological trade-offs. \emph{Nat. Ecol. Evol.} 1--12 (2021).
 
@@
 40. Eklöf, A. \emph{et al.} The dimensionality of ecological networks.
-\emph{Ecology letters} \textbf{16}, 577--583 (2013).
+\emph{Ecol. Lett.} \textbf{16}, 577--583 (2013).
 
@@
 distribution of age-specific mortality and reproduction. \emph{Nat.
-Ecol. Evol} \textbf{3}, 1217--1224 (2019).
+Ecol. Evol.} \textbf{3}, 1217--1224 (2019).
 

### 2021-10-06 Manuscript/Manuscript.Rmd
edits

@@
 <div id ="refs"></div>
+
+# Acknowledgements
+
+We thank all researchers that made their data available for our analysis.
+We thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
+We also thank Jason Tylianakis for his comments on the manuscript before submission.
+JBL thanks the University of New England for the funding provided to carry out this work.

### 2021-10-06 Manuscript/Manuscript.tex
edits

@@
 
+\section{Acknowledgements}\label{acknowledgements}
+
+We thank all researchers that made their data available for our
+analysis. We thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza
+and David Ragel for their help with data collection. We also thank Jason
+Tylianakis for his comments on the manuscript before submission. JBL
+thanks the University of New England for the funding provided to carry
+out this work.
+
 \end{document}

### 2021-10-19 Manuscript/Manuscript.Rmd
edits

@@
 __Plant life strategies are constrained by cost-benefit trade-offs that determine plant form and function.
-Despite the recent advances in the understanding of plant trade-offs with vegetative and physiological traits, little is known about the plant reproductive economics and how they constrain plant life strategies and shape interactions with floral visitors.
-Here, we investigated plant reproductive trade-offs and their association with floral visitors with a dataset of 1506 plant species with 17 reproductive and 3 vegetative traits from 28 plant-pollinator network studies across 18 countries.
-Then, we tested whether a species reproductive strategy predicted plant-pollinator interactions (presence-absence and visitation rate) and if the interaction strategy (its role in a pollination network) was predicted by individual traits.
-We found that 51.8% of trait variation was explained by two independent axes that encompassed plant form and function.
-Specifically, the first axis indicated the presence of a trade-off between flower number and flower size (PC1, 26.72%) and the second axis indicated a trade-off for the level of pollinator dependency (PC2, 25.08%).
-The reproductive trade-offs explained some of the qualitative interaction with pollinators (presence-absence) but none of the variability of visitation rates.
-However, noteworthy differences across pollinator guilds were found in both cases.
-Finally, we found that specific traits with special relevance of floral rewards were key in the understanding of the species network role.
-Our results highlight the need to consider plant reproductive trade-offs to improve our understanding of plant life strategies and plant-pollinator interactions at broader spatial scales.__
+However, despite recent advances in the understanding of trade-offs for vegetative and physiological traits, little is known about plant reproductive economics and how they constrain plant life strategies and shape interactions with floral visitors.
+Here, we investigate plant reproductive trade-offs and how these reproductive compromises drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species from 28 plant-pollinator studies across 18 countries.
+We tested whether a plant’s reproductive strategy predicts its interactions with floral visitors and if the different reproductive traits predict the plant’s role within the pollination network.
+We found that over half of all plant reproductive trait variation was explained by two independent axes that encompassed plant form and function.
+Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
+Plant reproductive trade-offs somewhat explained the presence or absence of interactions with floral visitors, but not differences in visitation rate.
+However, we did find important differences in the interaction level among floral visitor guilds on the different axes of trait variation.
+Finally, we found that plant size and floral rewards were the most important traits in the understanding of the species network role.
+Our results highlight the importance of plant reproductive trade-offs in determining plant life strategies and plant-pollinator interactions in a global context.__
 
@@
 
-Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their relevance to understand plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that explores plant reproductive compromises is currently lacking [@roddy2021].
-In addition, macroecological studies regarding specific reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and as a consequence studies that link reproductive traits to plant-pollinator interactions at large scales are poorly explored [@sargent2008; @rech2016; @salguero2016; @ruger2018].
+Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that explores plant reproductive compromises is currently lacking [@roddy2021].
+In addition, macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
 Linking the position in the trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
-At the same time, there is increasing interest in the understanding of the determinants of plant-pollinator interactions via trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
-However, reproductive traits have been overlooked beyond highly specialised systems [@dellinger2020] despite the apparent generalist nature of plant-pollinator interactions [@waser1996; @olesen2002].
-In addition, it is yet unclear how the different reproductive biology traits influence plant-pollinator associations [@tur2013; @devaux2014].
-
-Species can optimize their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can employ.
-With the recent availability of large trait databases (e.g., TRY [@kattge2011] and COMPADRE [@salguero2015]), plant ecological strategies are increasingly being examined, and are facilitating the identification of global patterns and constraints of plant form and function [@salguero2016; @diaz2016; bruelheide2018; @carmona2021].
-However, the main focus has been on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits
-[@evojtko2020; @roddy2021], also critical to plant life strategies that shape plant interactions with pollinators and ultimately impact plant reproductive success.
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively [@barrett2003; @moeller2017].
-Further, outcrossing levels are positively correlated with flower size [@goodwillie2010].
-In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and their role in attracting pollinators [@ollerton2011].
-However, it is still unknown to what extent these different  reproductive compromises determine plant-pollinator associations.
+Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
+However, reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020] despite the apparent generalist nature of plant-pollinator interactions [@waser1996; @olesen2002].
+In addition, it is unclear how specific plant reproductive biology traits influence plant-pollinator interactions [@tur2013; @devaux2014].
+
+Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
+With the recent availability of large trait databases (e.g., TRY [@kattge2011] and COMPADRE [@salguero2015]), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; bruelheide2018; @carmona2021].
+However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
+For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively [@barrett2003; @moeller2017] and outcrossing levels are positively correlated with flower size [@goodwillie2010].
+In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators [@ollerton2011; @rodger2021].
+However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.
 
 Several studies have identified links between plant traits and plant-pollinator network properties [@bartomeus2013; @olito2015; @rowe2020].
-Moreover, plant traits can also define species' network roles [@lazaro2013; @tur2013] (e.g., specialists vs generalists).
-For example, species that occupy trait space extremes are more likely to exhibit higher specialization and be more reliant on trait-matching [@junker2013; @coux2016].
-This morphological matching between plant and floral visitors can determine plant-pollinator interactions, and thus shape their interaction network structure [@stang2009; @ibanez2012].
+Moreover, plant traits can define species’ network roles (e.g., specialists vs generalists) [@lazaro2013; @tur2013].
+For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
+Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
 Remarkably, the combination of traits have shown to increase the predictive power of the network interactions [@eklof2013].
@@
 
-Here, we explore the potential trade-offs among plant floral and reproductive biology traits and how these influence plant-pollinator interactions.
+Here, we aim to explore the potential trade-offs among reproductive traits and how these influence plant-pollinator interactions.
 First, we identify the major axes of reproductive trait variation and trade-offs that determine plant form and function.
-Second, we investigate how plant species’ position in trait-space influences plant-pollinator interactions (presence-absence and visitation rate).
-Finally, we investigate how the main axes of trait variation and individual traits influence plant species roles within networks using complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
+Second, we investigate how plant species’ position in trait-space interactions with floral visitors.
+Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species’ roles within networks using a set of complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
 
@@
 
-Here, we show that plant species exhibit clear trade-offs in their floral, reproductive biology and vegetative traits.
+Here, we show that plant species exhibit clear trade-offs among their vegetative and reproductive traits that determined different interaction levels with floral visitor guilds.
 These trade-offs are differentiated on three main axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-These axes of trait variation explained partly the presence-absence interactions between plants and floral visitors but did not explain the overall visitation rates.
-However, on both qualitative and quantitative interactions floral visitor guilds showed associations with the different reproductive trade-offs.
-Interestingly, pollen and nectar related traits were better than all other traits for characterizing plant species functional roles within their interaction networks.
-
-Over 50% of plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
-Variation in these two axes of trait variation appears to be associated with the commonly described ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life-history strategies as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-The ‘slow’ part of the continuum (i.e., tall trees and shrubs) had plant species with many flowers, few ovules, higher pollinator dependence, greater occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, species that employed the ‘fast’ strategy (i.e., short herbs), had fewer flowers, more ovules, greater occurrence of self compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the positive association already described in a previous study between outcrossing rate and floral display [@goodwillie2010].
-This trend was further confirmed when looking at the specific correlation between floral display and autonomous selfing for our dataset (see Supplementary Fig.
+These reproductive trade-offs somewhat explained the presence or absence of interactions with floral visitors, but not differences in visitation rate.
+However, on both qualitative and quantitative interactions we found marked associations of floral visitor guilds with the main axes of trait variation.
+Further, we found that plant height and floral reward related traits were best at characterising plant species functional roles within pollination networks.
+
+Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
+Trait variation on these two axes was associated with the ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+The ‘slow’ part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
+In contrast, plant species that employed the ‘fast’ strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
+Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
+The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Supplementary Fig.
 S10).
 
-Despite the low predictive power of the main axes of trait variation on overall interaction patterns (presence-absence and visitation rate), we found commonalities among and within floral visitors guilds across these axes that indicate the influence of life-history strategies on plant-pollinator interactions.
-For example, all guilds showed an increasing trend of visitation on plant species with higher pollinator dependence, which were also associated with larger floral displays and greater pollen quantities (Fig.
+Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (presence-absence of interactions and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies strongly influence plant-pollinator interactions.
+For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
 1 and Supplementary Fig.
 S6).
-This trend is consistent with previous plant-pollinator studies that show higher visitation rates on species that make greater reproductive investment [@hegland2005; @lazaro2013; @kaiser2014].
-In regard to the flower number - flower size and style length trade-offs, different guilds showed contrasting visitation rates, which could be associated with different pollination syndromes at a macroecological scale.
-For instance, the guilds of bees and syrphids were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
-3) indicating a possible niche partitioning among these two guilds [@palmer2003; @phillips2020].
-However, these plant-pollinator associations do not account for some of the traits (i.e., pollen and nectar quantity) that had greater relevance on the species network roles (Fig.
-4) because of insufficient data availability and lack of pollinator efficiency measurements for more complete descriptions of the pollination syndromes [@dellinger2020].
-In any case, it is worth noting that this general pattern emerges in field-measured plant-pollinator networks, where other local factors such as species relative abundances, will surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016].
-
-To conclude, we provide the first description of plant floral and reproductive biology trade-offs using a large global dataset of plant traits and interactions with floral visitors.
-This allowed us to identify the major reproductive strategies of flowering plants and how plant life strategies determine their interaction with floral visitor guilds.
-Although the percentage of explained variation found with the first two axes (~50%) is lower than other studies that have evaluated life histories with vegetative traits [@diaz2016; @carmona2021], this percentage is consistent with the largest and most recent study that has characterized life strategies with both vegetative and reproductive (i.e., semelparity and iteroparity) traits [@salguero2016].
-Future work needs to integrate these floral and reproductive compromises with the already described vegetative and physiological trade-offs [@diaz2016] to create a more comprehensive spectrum of trait variation [@roddy2021].
+This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently [@hegland2005; @lazaro2013; @kaiser2014].
+In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation rates across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
+For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
+3) suggesting possible niche partitioning [@palmer2003; @phillips2020] between these two guilds.
+However, despite floral rewards, related traits were among the best at characterising species functional roles (Fig.
+4), yet the association between reproductive trade-offs and floral visitors did not account for floral rewards because there was insufficient data available.
+More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive trade-offs do not.
+
+To conclude, we provide the first description of plant reproductive trade-offs using a large global dataset of plant traits.
+We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
+Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits [@diaz2016; @carmona2021] it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits [@salguero2016].
+Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
 Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators [@gervasi2017; @mackin2021].
-Finally, a more complete description of the macroecological patterns of plant-pollinator interactions including unrepresented areas of the world [@poisot2021] and traits that have been largely ignored (e.g., floral rewards and plant mating system) are needed to progress in our understanding of the global patterns in plant-pollinator interactions.
+Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
 

### 2021-10-19 Manuscript/Manuscript.tex
edits

@@
 \textbf{Plant life strategies are constrained by cost-benefit trade-offs
-that determine plant form and function. Despite the recent advances in
-the understanding of plant trade-offs with vegetative and physiological
-traits, little is known about the plant reproductive economics and how
-they constrain plant life strategies and shape interactions with floral
-visitors. Here, we investigated plant reproductive trade-offs and their
-association with floral visitors with a dataset of 1506 plant species
-with 17 reproductive and 3 vegetative traits from 28 plant-pollinator
-network studies across 18 countries. Then, we tested whether a species
-reproductive strategy predicted plant-pollinator interactions
-(presence-absence and visitation rate) and if the interaction strategy
-(its role in a pollination network) was predicted by individual traits.
-We found that 51.8\% of trait variation was explained by two independent
-axes that encompassed plant form and function. Specifically, the first
-axis indicated the presence of a trade-off between flower number and
-flower size (PC1, 26.72\%) and the second axis indicated a trade-off for
-the level of pollinator dependency (PC2, 25.08\%). The reproductive
-trade-offs explained some of the qualitative interaction with
-pollinators (presence-absence) but none of the variability of visitation
-rates. However, noteworthy differences across pollinator guilds were
-found in both cases. Finally, we found that specific traits with special
-relevance of floral rewards were key in the understanding of the species
-network role. Our results highlight the need to consider plant
-reproductive trade-offs to improve our understanding of plant life
-strategies and plant-pollinator interactions at broader spatial scales.}
+that determine plant form and function. However, despite recent advances
+in the understanding of trade-offs for vegetative and physiological
+traits, little is known about plant reproductive economics and how they
+constrain plant life strategies and shape interactions with floral
+visitors. Here, we investigate plant reproductive trade-offs and how
+these reproductive compromises drive interactions with floral visitors
+using a dataset of 17 reproductive traits for 1,506 plant species from
+28 plant-pollinator studies across 18 countries. We tested whether a
+plant's reproductive strategy predicts its interactions with floral
+visitors and if the different reproductive traits predict the plant's
+role within the pollination network. We found that over half of all
+plant reproductive trait variation was explained by two independent axes
+that encompassed plant form and function. Specifically, the first axis
+indicated the presence of a trade-off between flower number and flower
+size, while the second axis indicated a pollinator dependency trade-off.
+Plant reproductive trade-offs somewhat explained the presence or absence
+of interactions with floral visitors, but not differences in visitation
+rate. However, we did find important differences in the interaction
+level among floral visitor guilds on the different axes of trait
+variation. Finally, we found that plant size and floral rewards were the
+most important traits in the understanding of the species network role.
+Our results highlight the importance of plant reproductive trade-offs in
+determining plant life strategies and plant-pollinator interactions in a
+global context.}
 
@@
 plants\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}}
-and their relevance to understand plant-pollinator
+and their importance in shaping plant-pollinator
 interactions\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}},
@@
 currently lacking\textsuperscript{\protect\hyperlink{ref-roddy2021}{5}}.
-In addition, macroecological studies regarding specific reproductive
+In addition, macroecological studies that investigate plant reproductive
 traits are
 scarce\textsuperscript{\protect\hyperlink{ref-baude2016}{6}--\protect\hyperlink{ref-moeller2017}{9}}
-and as a consequence studies that link reproductive traits to
-plant-pollinator interactions at large scales are poorly
-explored\textsuperscript{\protect\hyperlink{ref-sargent2008}{10}--\protect\hyperlink{ref-ruger2018}{13}}.
+and consequently, there is poor understanding of how reproductive traits
+drive interactions with floral visitors at large
+scales\textsuperscript{\protect\hyperlink{ref-sargent2008}{10}--\protect\hyperlink{ref-ruger2018}{13}}.
 Linking the position in the trait-space with the different pollinator
@@
 associations\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}}.
-At the same time, there is increasing interest in the understanding of
-the determinants of plant-pollinator interactions via trait-based
+Further, there is increasing interest in understanding drivers of
+plant-pollinator interactions using trait-based
 approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{15}}
@@
 However, reproductive traits have been overlooked beyond highly
-specialised
+specialised pollination
 systems\textsuperscript{\protect\hyperlink{ref-dellinger2020}{4}}
@@
 interactions\textsuperscript{\protect\hyperlink{ref-waser1996}{18},\protect\hyperlink{ref-olesen2002}{19}}.
-In addition, it is yet unclear how the different reproductive biology
+In addition, it is unclear how specific plant reproductive biology
 traits influence plant-pollinator
-associations\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-devaux2014}{21}}.
-
-Species can optimize their fitness through various life-history traits,
+interactions\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-devaux2014}{21}}.
+
+Species can optimise their fitness through various life-history traits,
 yet trade-offs among those traits constrain the range of potential
-strategies that a species can employ. With the recent availability of
-large trait databases (e.g.,
+strategies that a species can use. With the recent availability of large
+trait databases (e.g.,
 TRY\textsuperscript{\protect\hyperlink{ref-kattge2011}{22}} and
 COMPADRE\textsuperscript{\protect\hyperlink{ref-salguero2015}{23}}),
-plant ecological strategies are increasingly being examined, and are
-facilitating the identification of global patterns and constraints of
+plant ecological strategies are being increasingly examined, and are
+facilitating the identification of global patterns and constraints in
 plant form and
 function\textsuperscript{\protect\hyperlink{ref-salguero2016}{12},\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{25}}.
-However, the main focus has been on vegetative traits such as
+However, most studies have focused on vegetative traits such as
 leaf\textsuperscript{\protect\hyperlink{ref-wright2004}{26}},
@@
 trade-offs with little or no attention given to reproductive
-traits\textsuperscript{\protect\hyperlink{ref-roddy2021}{5},\protect\hyperlink{ref-evojtko2020}{29}},
-also critical to plant life strategies that shape plant interactions
-with pollinators and ultimately impact plant reproductive success. For
+traits\textsuperscript{\protect\hyperlink{ref-roddy2021}{5},\protect\hyperlink{ref-evojtko2020}{29}}
+which are critical to plant life strategies that shape interactions with
+pollinators and ultimately determine plant reproductive success. For
 instance, short lived versus perennial species tend to have low versus
 high levels of outcrossing,
-respectively\textsuperscript{\protect\hyperlink{ref-moeller2017}{9},\protect\hyperlink{ref-barrett2003}{30}}.
-Further, outcrossing levels are positively correlated with flower
+respectively\textsuperscript{\protect\hyperlink{ref-moeller2017}{9},\protect\hyperlink{ref-barrett2003}{30}}
+and outcrossing levels are positively correlated with flower
 size\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{31}}. In
@@
 consideration of plant species' reliance upon animal pollination
-(pollinator dependence) and their role in attracting
-pollinators\textsuperscript{\protect\hyperlink{ref-ollerton2011}{32}}.
+(pollinator dependence) and its role in attracting
+pollinators\textsuperscript{\protect\hyperlink{ref-ollerton2011}{32},\protect\hyperlink{ref-rodger2021}{33}}.
 However, it is still unknown to what extent these different reproductive
-compromises determine plant-pollinator associations.
+compromises determine plant-pollinator interactions.
 
@@
 plant-pollinator network
-properties\textsuperscript{\protect\hyperlink{ref-bartomeus2013}{33}--\protect\hyperlink{ref-rowe2020}{35}}.
-Moreover, plant traits can also define species' network
-roles\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-lazaro2013}{36}}
-(e.g., specialists vs generalists). For example, species that occupy
-trait space extremes are more likely to exhibit higher specialization
-and be more reliant on
-trait-matching\textsuperscript{\protect\hyperlink{ref-junker2013}{37},\protect\hyperlink{ref-coux2016}{38}}.
-This morphological matching between plant and floral visitors can
-determine plant-pollinator interactions, and thus shape their
-interaction network
-structure\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-ibanez2012}{39}}.
+properties\textsuperscript{\protect\hyperlink{ref-bartomeus2013}{34}--\protect\hyperlink{ref-rowe2020}{36}}.
+Moreover, plant traits can define species' network roles (e.g.,
+specialists vs
+generalists)\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-lazaro2013}{37}}.
+For example, plant species that occupy reproductive trait space extremes
+are more likely to exhibit higher levels of specialisation and be more
+reliant on the trait-matching with
+pollinators\textsuperscript{\protect\hyperlink{ref-junker2013}{38},\protect\hyperlink{ref-coux2016}{39}}.
+Morphological matching between plant and floral visitors often
+determines plant-pollinator interactions, and can thus strongly
+influence interaction network
+structure\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-ibanez2012}{40}}.
 Remarkably, the combination of traits have shown to increase the
 predictive power of the network
-interactions\textsuperscript{\protect\hyperlink{ref-eklof2013}{40}}.
+interactions\textsuperscript{\protect\hyperlink{ref-eklof2013}{41}}.
 Therefore, considering the different plant reproductive trade-offs which
@@
 
-Here, we explore the potential trade-offs among plant floral and
-reproductive biology traits and how these influence plant-pollinator
-interactions. First, we identify the major axes of reproductive trait
-variation and trade-offs that determine plant form and function. Second,
-we investigate how plant species' position in trait-space influences
-plant-pollinator interactions (presence-absence and visitation rate).
-Finally, we investigate how the main axes of trait variation and
-individual traits influence plant species roles within networks using
-complementary interaction network metrics (i.e., interaction strength,
-normalized degree and specialization).
+Here, we aim to explore the potential trade-offs among reproductive
+traits and how these influence plant-pollinator interactions. First, we
+identify the major axes of reproductive trait variation and trade-offs
+that determine plant form and function. Second, we investigate how plant
+species' position in trait-space interactions with floral visitors.
+Finally, we investigate how both the main axes of trait variation, and
+individual traits, influence plant species' roles within networks using
+a set of complementary interaction network metrics (i.e., interaction
+strength, normalized degree and specialization).
 
@@
 trade-off', as already described in previous
-studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{41},\protect\hyperlink{ref-kettle2011}{42}}.
+studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{42},\protect\hyperlink{ref-kettle2011}{43}}.
 Hence, one end of the spectrum comprised species with high investment in
@@
 
-Here, we show that plant species exhibit clear trade-offs in their
-floral, reproductive biology and vegetative traits. These trade-offs are
-differentiated on three main axes of trait variation: (i) flower number
-- flower size, (ii) pollinator dependence and (iii) style length. These
-axes of trait variation explained partly the presence-absence
-interactions between plants and floral visitors but did not explain the
-overall visitation rates. However, on both qualitative and quantitative
-interactions floral visitor guilds showed associations with the
-different reproductive trade-offs. Interestingly, pollen and nectar
-related traits were better than all other traits for characterizing
-plant species functional roles within their interaction networks.
-
-Over 50\% of plant trait variation was captured by the flower number -
-flower size and pollinator dependence trade-offs. Variation in these two
-axes of trait variation appears to be associated with the commonly
-described `fast-slow continuum' in
+Here, we show that plant species exhibit clear trade-offs among their
+vegetative and reproductive traits that determined different interaction
+levels with floral visitor guilds. These trade-offs are differentiated
+on three main axes of trait variation: (i) flower number - flower size,
+(ii) pollinator dependence and (iii) style length. These reproductive
+trade-offs somewhat explained the presence or absence of interactions
+with floral visitors, but not differences in visitation rate. However,
+on both qualitative and quantitative interactions we found marked
+associations of floral visitor guilds with the main axes of trait
+variation. Further, we found that plant height and floral reward related
+traits were best at characterising plant species functional roles within
+pollination networks.
+
+Over half of all plant trait variation was captured by the flower number
+- flower size and pollinator dependence trade-offs. Trait variation on
+these two axes was associated with the `fast-slow continuum' in
 plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}} and
-animal\textsuperscript{\protect\hyperlink{ref-healy2019}{43}}
-life-history strategies as indicated by the different floral and
+animal\textsuperscript{\protect\hyperlink{ref-healy2019}{44}}
+life-history strategies, as indicated by the different floral and
 reproductive biology traits associated with plant height, life form and
-lifespan. The `slow' part of the continuum (i.e., tall trees and shrubs)
-had plant species with many flowers, few ovules, higher pollinator
-dependence, greater occurrence of self-incompatibility and more complex
-breeding systems (e.g., monoecious and dioecious species). In contrast,
-species that employed the `fast' strategy (i.e., short herbs), had fewer
-flowers, more ovules, greater occurrence of self compatibility and lower
-pollinator dependence. Further, on the first two axes of trait
-variation, we found additional support for the positive association
-already described in a previous study between outcrossing rate and
-floral
-display\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{31}}.
-This trend was further confirmed when looking at the specific
-correlation between floral display and autonomous selfing for our
-dataset (see Supplementary Fig. S10).
-
-Despite the low predictive power of the main axes of trait variation on
-overall interaction patterns (presence-absence and visitation rate), we
-found commonalities among and within floral visitors guilds across these
-axes that indicate the influence of life-history strategies on
-plant-pollinator interactions. For example, all guilds showed an
-increasing trend of visitation on plant species with higher pollinator
-dependence, which were also associated with larger floral displays and
+lifespan. The `slow' part of this continuum (i.e., tall trees and
+shrubs) included plant species with many flowers, few ovules, higher
+pollinator dependence, frequent occurrence of self-incompatibility and
+more complex breeding systems (e.g., monoecious and dioecious species).
+In contrast, plant species that employed the `fast' strategy (i.e.,
+short herbs), had fewer flowers, more ovules, frequent occurrence of
+self-compatibility and lower pollinator dependence. Further, on the
+first two axes of trait variation, we found additional support for the
+previously described positive association between higher outcrossing
+rate and larger floral
+display\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{31}}. The
+positive correlation between larger floral display and higher pollinator
+dependence in our dataset further confirmed this trend (see
+Supplementary Fig. S10).
+
+Despite the low predictive power of the main trait variation axes for
+broad-level interaction patterns (presence-absence of interactions and
+visitation rate), we found changes in the interaction patterns among and
+within floral visitor guilds across these axes that suggest plant
+life-history strategies strongly influence plant-pollinator
+interactions. For example, all floral visitor guilds visited plant
+species with higher pollinator dependence more frequently, and high
+pollinator dependence was associated with large floral displays and
 greater pollen quantities (Fig. 1 and Supplementary Fig. S6). This trend
-is consistent with previous plant-pollinator studies that show higher
-visitation rates on species that make greater reproductive
-investment\textsuperscript{\protect\hyperlink{ref-lazaro2013}{36},\protect\hyperlink{ref-hegland2005}{44},\protect\hyperlink{ref-kaiser2014}{45}}.
+is consistent with previous studies that show plant species with higher
+reproductive investment tend to be visited by pollinators more
+frequently\textsuperscript{\protect\hyperlink{ref-lazaro2013}{37},\protect\hyperlink{ref-hegland2005}{45},\protect\hyperlink{ref-kaiser2014}{46}}.
 In regard to the flower number - flower size and style length
-trade-offs, different guilds showed contrasting visitation rates, which
-could be associated with different pollination syndromes at a
-macroecological scale. For instance, the guilds of bees and syrphids
-were clearly associated with opposing life-strategies on PC1 and PC3
-(Fig. 3) indicating a possible niche partitioning among these two
-guilds\textsuperscript{\protect\hyperlink{ref-palmer2003}{46},\protect\hyperlink{ref-phillips2020}{47}}.
-However, these plant-pollinator associations do not account for some of
-the traits (i.e., pollen and nectar quantity) that had greater relevance
-on the species network roles (Fig. 4) because of insufficient data
-availability and lack of pollinator efficiency measurements for more
-complete descriptions of the pollination
-syndromes\textsuperscript{\protect\hyperlink{ref-dellinger2020}{4}}. In
-any case, it is worth noting that this general pattern emerges in
-field-measured plant-pollinator networks, where other local factors such
-as species relative abundances, will surely explain part of the observed
-variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{17},\protect\hyperlink{ref-vazquez2007}{48},\protect\hyperlink{ref-encinas2012}{49}}.
-
-To conclude, we provide the first description of plant floral and
-reproductive biology trade-offs using a large global dataset of plant
-traits and interactions with floral visitors. This allowed us to
-identify the major reproductive strategies of flowering plants and how
-plant life strategies determine their interaction with floral visitor
-guilds. Although the percentage of explained variation found with the
-first two axes (\textasciitilde{}50\%) is lower than other studies that
-have evaluated life histories with vegetative
-traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{25}},
-this percentage is consistent with the largest and most recent study
-that has characterized life strategies with both vegetative and
-reproductive (i.e., semelparity and iteroparity)
+trade-offs, different pollinator guilds showed contrasting visitation
+rates across the continuum of trait variation, which could be associated
+with different pollination syndromes at a macroecological scale. For
+instance, bees and syrphid flies were clearly associated with opposing
+life-strategies on PC1 and PC3 (Fig. 3) suggesting possible niche
+partitioning\textsuperscript{\protect\hyperlink{ref-palmer2003}{47},\protect\hyperlink{ref-phillips2020}{48}}
+between these two guilds. However, despite floral rewards, related
+traits were among the best at characterising species functional roles
+(Fig. 4), yet the association between reproductive trade-offs and floral
+visitors did not account for floral rewards because there was
+insufficient data available. More detailed exploration of reproductive
+trade-offs in conjunction with floral rewards is needed to help
+elucidate plant-pollinator associations. In any case, it is worth noting
+that other local factors such as species relative abundances, surely
+explain part of the observed
+variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{17},\protect\hyperlink{ref-vazquez2007}{49},\protect\hyperlink{ref-encinas2012}{50}}
+that reproductive trade-offs do not.
+
+To conclude, we provide the first description of plant reproductive
+trade-offs using a large global dataset of plant traits. We identified
+the major reproductive strategies of flowering plants and how these
+strategies influence interactions with different floral visitor guilds.
+Although the explained variation that we found in the first two axes is
+lower than previous studies of vegetative
+traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{25}}
+it is consistent with the largest and most recent study that has
+characterised plant life strategies with vegetative and reproductive
 traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}}. Future
-work needs to integrate these floral and reproductive compromises with
-the already described vegetative and physiological
-trade-offs\textsuperscript{\protect\hyperlink{ref-diaz2016}{24}} to
-create a more comprehensive spectrum of trait
-variation\textsuperscript{\protect\hyperlink{ref-roddy2021}{5}}.
-Further, the varying level of phylogenetic signal among traits deserves
-further attention to understand evolutionary changes on mating and
-flower morphology in response to
-pollinators\textsuperscript{\protect\hyperlink{ref-gervasi2017}{50},\protect\hyperlink{ref-mackin2021}{51}}.
-Finally, a more complete description of the macroecological patterns of
-plant-pollinator interactions including unrepresented areas of the
-world\textsuperscript{\protect\hyperlink{ref-poisot2021}{52}} and traits
-that have been largely ignored (e.g., floral rewards and plant mating
-system) are needed to progress in our understanding of the global
+work needs to integrate the reproductive compromises that we have
+identified with vegetative and physiological trade-offs to create a more
+comprehensive spectrum of plant trait variation. Further, the varying
+level of phylogenetic signal among traits deserves further attention to
+understand evolutionary changes on mating and flower morphology in
+response to
+pollinators\textsuperscript{\protect\hyperlink{ref-gervasi2017}{51},\protect\hyperlink{ref-mackin2021}{52}}.
+Finally, including plant-pollinator networks from unrepresented areas of
+the world and a more complete description of plant reproductive
+trade-offs is essential for a better understanding of the global
 patterns in plant-pollinator interactions.
@@
 
+\hypertarget{ref-rodger2021}{}
+33. Rodger, J. G. \emph{et al.} Widespread vulnerability of flowering
+plant seed production to pollinator declines. \emph{Science Advances}
+\textbf{7}, eabd3524 (2021).
+
 \hypertarget{ref-bartomeus2013}{}
-33. Bartomeus, I. Understanding Linkage Rules in Plant-Pollinator
+34. Bartomeus, I. Understanding Linkage Rules in Plant-Pollinator
 Networks by Using Hierarchical Models That Incorporate Pollinator
@@
 \hypertarget{ref-olito2015}{}
-34. Olito, C. \& Fox, J. W. Species traits and abundances predict
+35. Olito, C. \& Fox, J. W. Species traits and abundances predict
 metrics of plantPollinator network structure, but not pairwise
@@
 \hypertarget{ref-rowe2020}{}
-35. Rowe, L. \emph{et al.} Flower traits associated with the visitation
+36. Rowe, L. \emph{et al.} Flower traits associated with the visitation
 patterns of bees. \emph{Oecologia} \textbf{193}, 511--522 (2020).
@@
 \hypertarget{ref-lazaro2013}{}
-36. Lázaro, A., Jakobsson, A. \& Totland, Ø. How do pollinator
+37. Lázaro, A., Jakobsson, A. \& Totland, Ø. How do pollinator
 visitation rate and seed set relate to species' floral traits and
@@
 \hypertarget{ref-junker2013}{}
-37. Junker, R. R. \emph{et al.} Specialization on traits as basis for
+38. Junker, R. R. \emph{et al.} Specialization on traits as basis for
 the niche-breadth of flower visitors and as structuring mechanism of
@@
 \hypertarget{ref-coux2016}{}
-38. Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking
+39. Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking
 species functional roles to their network roles. \emph{Ecol. Lett.}
@@
 \hypertarget{ref-ibanez2012}{}
-39. Ibanez, S. Optimizing size thresholds in a plant-pollinator
+40. Ibanez, S. Optimizing size thresholds in a plant-pollinator
 interaction web: Towards a mechanistic understanding of ecological
@@
 \hypertarget{ref-eklof2013}{}
-40. Eklöf, A. \emph{et al.} The dimensionality of ecological networks.
+41. Eklöf, A. \emph{et al.} The dimensionality of ecological networks.
 \emph{Ecol. Lett.} \textbf{16}, 577--583 (2013).
@@
 \hypertarget{ref-sargent2007}{}
-41. Sargent, R. D., Goodwillie, C., Kalisz, S. \& Ree, R. H.
+42. Sargent, R. D., Goodwillie, C., Kalisz, S. \& Ree, R. H.
 Phylogenetic evidence for a flower size and number trade-off. \emph{Am.
@@
 \hypertarget{ref-kettle2011}{}
-42. Kettle, C. J. \emph{et al.} Ecological Implications of a Flower
+43. Kettle, C. J. \emph{et al.} Ecological Implications of a Flower
 Size/Number Trade-Off in Tropical Forest Trees. \emph{PLoS One}
@@
 \hypertarget{ref-healy2019}{}
-43. Healy, K., Ezard, T. H. G., Jones, O. R., Salguero-Gómez, R. \&
+44. Healy, K., Ezard, T. H. G., Jones, O. R., Salguero-Gómez, R. \&
 Buckley, Y. M. Animal life history is shaped by the pace of life and the
@@
 \hypertarget{ref-hegland2005}{}
-44. Hegland, S. J. \& Totland, Ø. Relationships between species' floral
+45. Hegland, S. J. \& Totland, Ø. Relationships between species' floral
 traits and pollinator visitation in a temperate grassland.
@@
 \hypertarget{ref-kaiser2014}{}
-45. Kaiser-Bunbury, C. N., Vázquez, D. P., Stang, M. \& Ghazoul, J.
+46. Kaiser-Bunbury, C. N., Vázquez, D. P., Stang, M. \& Ghazoul, J.
 Determinants of the microstructure of plantPollinator networks.
@@
 \hypertarget{ref-palmer2003}{}
-46. Palmer, T. M., Stanton, M. L. \& Young, T. P. Competition and
+47. Palmer, T. M., Stanton, M. L. \& Young, T. P. Competition and
 coexistence: Exploring mechanisms that restrict and maintain diversity
@@
 \hypertarget{ref-phillips2020}{}
-47. Phillips, R. D., Peakall, R., van der Niet, T. \& Johnson, S. D.
+48. Phillips, R. D., Peakall, R., van der Niet, T. \& Johnson, S. D.
 Niche perspectives on plantPollinator interactions. \emph{Trends Plant
@@
 \hypertarget{ref-vazquez2007}{}
-48. Vázquez, D. P. \emph{et al.} Species abundance and asymmetric
+49. Vázquez, D. P. \emph{et al.} Species abundance and asymmetric
 interaction strength in ecological networks. \emph{Oikos} \textbf{116},
@@
 \hypertarget{ref-encinas2012}{}
-49. Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives
+50. Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives
 mutualistic network structure and diversity. \emph{Ecol. Lett.}
@@
 \hypertarget{ref-gervasi2017}{}
-50. Gervasi, D. D. L. \& Schiestl, F. P. Real-time divergent evolution
+51. Gervasi, D. D. L. \& Schiestl, F. P. Real-time divergent evolution
 in plants driven by pollinators. \emph{Nat. Commun.} \textbf{8}, 14691
@@
 \hypertarget{ref-mackin2021}{}
-51. Mackin, C. R., Peña, J. F., Blanco, M. A., Balfour, N. J. \&
+52. Mackin, C. R., Peña, J. F., Blanco, M. A., Balfour, N. J. \&
 Castellanos, M. C. Rapid evolution of a floral trait following
@@
 2234--2246 (2021).
-
-\hypertarget{ref-poisot2021}{}
-52. Poisot, T. \emph{et al.} Global knowledge gaps in species
-interaction networks data. \emph{J. Biogeogr.} \textbf{48}, 1552--1563
-(2021).
 

### 2021-10-19 Manuscript/Manuscript.Rmd
parenthesis edit

@@
 Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY [@kattge2011] and COMPADRE [@salguero2015]), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; bruelheide2018; @carmona2021].
+With the recent availability of large trait databases (e.g., TRY @kattge2011 and COMPADRE @salguero2015), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; bruelheide2018; @carmona2021].
 However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
@@
 
-The additional model for both presence-absence ($marginal R2 = 0.29$; $conditional R2 = 0.19$) and visitation rate ($marginal R2 = 0.30$; $conditional R2 = 0.03$) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns and that the contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
+The additional model for both presence-absence of interactions ($marginal R2 = 0.29$; $conditional R2 = 0.19$) and visitation rate ($marginal R2 = 0.30$; $conditional R2 = 0.03$) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns and that the contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
 3a and Fig.

### 2021-10-19 Manuscript/Manuscript.tex
parenthesis edit

@@
 strategies that a species can use. With the recent availability of large
-trait databases (e.g.,
-TRY\textsuperscript{\protect\hyperlink{ref-kattge2011}{22}} and
-COMPADRE\textsuperscript{\protect\hyperlink{ref-salguero2015}{23}}),
-plant ecological strategies are being increasingly examined, and are
-facilitating the identification of global patterns and constraints in
-plant form and
+trait databases (e.g., TRY \protect\hyperlink{ref-kattge2011}{22} and
+COMPADRE \protect\hyperlink{ref-salguero2015}{23}), plant ecological
+strategies are being increasingly examined, and are facilitating the
+identification of global patterns and constraints in plant form and
 function\textsuperscript{\protect\hyperlink{ref-salguero2016}{12},\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{25}}.
@@
 
-The additional model for both presence-absence (\(marginal R2 = 0.29\);
-\(conditional R2 = 0.19\)) and visitation rate (\(marginal R2 = 0.30\);
-\(conditional R2 = 0.03\)) for the most represented families of bees
-showed that the family Apidae was the main driver of the observed
-patterns and that the contrasting differences between presence-absence
-and visitation rate for bees on PC1 (Fig. 3a and Fig. 3d) were driven by
-the family Andrenidae which interacted more frequently on
-presence-absence interactions with plant species with low number of
-flower but large (Supplementary Fig. S8).
+The additional model for both presence-absence of interactions
+(\(marginal R2 = 0.29\); \(conditional R2 = 0.19\)) and visitation rate
+(\(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) for the most
+represented families of bees showed that the family Apidae was the main
+driver of the observed patterns and that the contrasting differences
+between presence-absence and visitation rate for bees on PC1 (Fig. 3a
+and Fig. 3d) were driven by the family Andrenidae which interacted more
+frequently on presence-absence interactions with plant species with low
+number of flower but large (Supplementary Fig. S8).
 

### 2021-11-18 Main_Figures/Graphical abstract plot.Rmd
graph

--- 2021-08-10 Main_Figures/Global_trait_spectrum.Rmd
@@
             legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
+            panel.border=element_rect(color="black",size=3),
             panel.grid.minor.x =element_blank(),
@@
 
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
+  #plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
+  #scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
+  #  scale_alpha(guide = 'none')
 
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
+    plot <- plot + geom_point(data=dat, aes(x, y),size=2.5, color="azure4")
 
@@
   # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=5.5, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
 
   #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
 
@@
 
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
-    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
-    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
-    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
-    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2, ymax = -1.50) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
+#  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, #ymax = 4.05)+
+#     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
+#    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
+#    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
+#    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
+#    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
+#    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
+#    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
+#    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
+#    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
+#    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2, ymax = -1.50) +
+#    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2) 
+#
 
       #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
+#  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
 
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
+ # PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+ #plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
+  #                       label = PCAloadings$Variables, color="black",fontface =2,size=4)
 
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
-                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
+ #plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
+   #                      label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
+  plot <- plot + theme_ms() +ylim(-3.5,3) + xlim(-3.5,3) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("") +theme(axis.line=element_blank(),axis.text.x=element_blank(),
+          axis.text.y=element_blank(),axis.ticks=element_blank(),
+          axis.title.x=element_blank(),
+          axis.title.y=element_blank(),legend.position="none",
+          panel.background=element_blank(),panel.grid.major=element_blank(),
+          panel.grid.minor=element_blank(),plot.background=element_blank())
 

### 2021-11-18 Manuscript/Manuscript.Rmd
graph

@@
 First, we identify the major axes of reproductive trait variation and trade-offs that determine plant form and function.
-Second, we investigate how plant species’ position in trait-space interactions with floral visitors.
+Second, we investigate how plant species’ position in trait-space influence interactions with floral visitors.
 Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species’ roles within networks using a set of complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
@@
 
-Here, we show that plant species exhibit clear trade-offs among their vegetative and reproductive traits that determined different interaction levels with floral visitor guilds.
-These trade-offs are differentiated on three main axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-These reproductive trade-offs somewhat explained the presence or absence of interactions with floral visitors, but not differences in visitation rate.
-However, on both qualitative and quantitative interactions we found marked associations of floral visitor guilds with the main axes of trait variation.
-Further, we found that plant height and floral reward related traits were best at characterising plant species functional roles within pollination networks.
+Here, we show that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
+These trade-offs are differentiated along three axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
+These reproductive trade-offs helped explain the presence of floral visitor interactions, but not their visitation rates.
+Floral visitor guilds formed distinct relationships with the main axes of trait variation.
+Moreover, we found that the plant species functional roles within pollination networks were best explained by plant size and floral reward related traits.
 

### 2021-11-18 Manuscript/Manuscript.tex
graph

@@
-\documentclass[12pt,a4paper,]{article}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  12pt,
+  a4paper,
+]{article}
+\title{\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors}
+\author{}
+\date{\vspace{-2.5em}}
+
+\usepackage{amsmath,amssymb}
 \usepackage[]{mathpazo}
 \usepackage{setspace}
-\setstretch{2}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
   \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
+\IfFileExists{microtype.sty}{% use microtype if available
   \usepackage[]{microtype}
@@
   colorlinks=true,
-            linkcolor=RoyalBlue,
-            citecolor=Blue,
-            urlcolor=RoyalBlue,
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  linkcolor={RoyalBlue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={RoyalBlue},
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs}
-% Fix footnotes in tables (requires footnote package)
-\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
-\usepackage{graphicx,grffile}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
 \makeatletter
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\pagestyle{plain}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 \usepackage{lineno} % add 
@@
 }
+
 \usepackage{booktabs}
@@
 \usepackage{xcolor}
-
-\title{\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant
-reproductive traits determine interactions with floral visitors}
-\author{}
-\date{\vspace{-2.5em}}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 
@@
 
-\textbf{Plant life strategies are constrained by cost-benefit trade-offs
-that determine plant form and function. However, despite recent advances
-in the understanding of trade-offs for vegetative and physiological
-traits, little is known about plant reproductive economics and how they
-constrain plant life strategies and shape interactions with floral
-visitors. Here, we investigate plant reproductive trade-offs and how
-these reproductive compromises drive interactions with floral visitors
-using a dataset of 17 reproductive traits for 1,506 plant species from
-28 plant-pollinator studies across 18 countries. We tested whether a
-plant's reproductive strategy predicts its interactions with floral
-visitors and if the different reproductive traits predict the plant's
-role within the pollination network. We found that over half of all
-plant reproductive trait variation was explained by two independent axes
-that encompassed plant form and function. Specifically, the first axis
-indicated the presence of a trade-off between flower number and flower
-size, while the second axis indicated a pollinator dependency trade-off.
-Plant reproductive trade-offs somewhat explained the presence or absence
-of interactions with floral visitors, but not differences in visitation
-rate. However, we did find important differences in the interaction
-level among floral visitor guilds on the different axes of trait
-variation. Finally, we found that plant size and floral rewards were the
-most important traits in the understanding of the species network role.
-Our results highlight the importance of plant reproductive trade-offs in
-determining plant life strategies and plant-pollinator interactions in a
-global context.}
+\textbf{Plant life strategies are constrained by cost-benefit trade-offs that determine plant form and function.
+However, despite recent advances in the understanding of trade-offs for vegetative and physiological traits, little is known about plant reproductive economics and how they constrain plant life strategies and shape interactions with floral visitors.
+Here, we investigate plant reproductive trade-offs and how these reproductive compromises drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species from 28 plant-pollinator studies across 18 countries.
+We tested whether a plant's reproductive strategy predicts its interactions with floral visitors and if the different reproductive traits predict the plant's role within the pollination network.
+We found that over half of all plant reproductive trait variation was explained by two independent axes that encompassed plant form and function.
+Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
+Plant reproductive trade-offs somewhat explained the presence or absence of interactions with floral visitors, but not differences in visitation rate.
+However, we did find important differences in the interaction level among floral visitor guilds on the different axes of trait variation.
+Finally, we found that plant size and floral rewards were the most important traits in the understanding of the species network role.
+Our results highlight the importance of plant reproductive trade-offs in determining plant life strategies and plant-pollinator interactions in a global context.}
 
@@
 
-\noindent\rule{\textwidth}{1pt}
-
-\textsuperscript{1} School of Environmental and Rural Science,
-University of New England, Armidale, New South Wales 2350, Australia.
-\textsuperscript{2} Estación Biológica de Doñana (EBD-CSIC), E-41092
-Seville, Spain. \textsuperscript{3} Department of Conservation
-\textbar{} Te Papa Atawhai, Auckland, New Zealand. \textsuperscript{4}
-Centre for Environmental and Climate Science, Lund University,
-Sölvegatan 37, S-223 62 Lund, Sweden. \texttt{*} e-mail:
-\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
+\noindent
+
+\rule{\textwidth}{1pt}
+
+\textsuperscript{1} School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
+\textsuperscript{2} Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
+\textsuperscript{3} Department of Conservation \textbar{} Te Papa Atawhai, Auckland, New Zealand.
+\textsuperscript{4} Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden.
+\texttt{*} e-mail: \href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
 
 \doublespacing
-\vspace{5mm} \normalsize
-
-Despite the astonishing diversity of floral structures among flowering
-plants\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}}
-and their importance in shaping plant-pollinator
-interactions\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}},
-a unified framework that explores plant reproductive compromises is
-currently lacking\textsuperscript{\protect\hyperlink{ref-roddy2021}{5}}.
-In addition, macroecological studies that investigate plant reproductive
-traits are
-scarce\textsuperscript{\protect\hyperlink{ref-baude2016}{6}--\protect\hyperlink{ref-moeller2017}{9}}
-and consequently, there is poor understanding of how reproductive traits
-drive interactions with floral visitors at large
-scales\textsuperscript{\protect\hyperlink{ref-sargent2008}{10}--\protect\hyperlink{ref-ruger2018}{13}}.
-Linking the position in the trait-space with the different pollinator
-groups could help to improve our understanding of plant-pollinator
-associations\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}}.
-Further, there is increasing interest in understanding drivers of
-plant-pollinator interactions using trait-based
-approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{15}}
-and trait-matching
-analyses\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-bartomeus2016}{17}}.
-However, reproductive traits have been overlooked beyond highly
-specialised pollination
-systems\textsuperscript{\protect\hyperlink{ref-dellinger2020}{4}}
-despite the apparent generalist nature of plant-pollinator
-interactions\textsuperscript{\protect\hyperlink{ref-waser1996}{18},\protect\hyperlink{ref-olesen2002}{19}}.
-In addition, it is unclear how specific plant reproductive biology
-traits influence plant-pollinator
-interactions\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-devaux2014}{21}}.
-
-Species can optimise their fitness through various life-history traits,
-yet trade-offs among those traits constrain the range of potential
-strategies that a species can use. With the recent availability of large
-trait databases (e.g., TRY \protect\hyperlink{ref-kattge2011}{22} and
-COMPADRE \protect\hyperlink{ref-salguero2015}{23}), plant ecological
-strategies are being increasingly examined, and are facilitating the
-identification of global patterns and constraints in plant form and
-function\textsuperscript{\protect\hyperlink{ref-salguero2016}{12},\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{25}}.
-However, most studies have focused on vegetative traits such as
-leaf\textsuperscript{\protect\hyperlink{ref-wright2004}{26}},
-wood\textsuperscript{\protect\hyperlink{ref-chave2009}{27}}, or
-root\textsuperscript{\protect\hyperlink{ref-laughlin2021}{28}}
-trade-offs with little or no attention given to reproductive
-traits\textsuperscript{\protect\hyperlink{ref-roddy2021}{5},\protect\hyperlink{ref-evojtko2020}{29}}
-which are critical to plant life strategies that shape interactions with
-pollinators and ultimately determine plant reproductive success. For
-instance, short lived versus perennial species tend to have low versus
-high levels of outcrossing,
-respectively\textsuperscript{\protect\hyperlink{ref-moeller2017}{9},\protect\hyperlink{ref-barrett2003}{30}}
-and outcrossing levels are positively correlated with flower
-size\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{31}}. In
-addition, the presence of costly rewards (e.g., pollen or nectar) and
-showy flowers or floral displays can only be understood through
-consideration of plant species' reliance upon animal pollination
-(pollinator dependence) and its role in attracting
-pollinators\textsuperscript{\protect\hyperlink{ref-ollerton2011}{32},\protect\hyperlink{ref-rodger2021}{33}}.
-However, it is still unknown to what extent these different reproductive
-compromises determine plant-pollinator interactions.
-
-Several studies have identified links between plant traits and
-plant-pollinator network
-properties\textsuperscript{\protect\hyperlink{ref-bartomeus2013}{34}--\protect\hyperlink{ref-rowe2020}{36}}.
-Moreover, plant traits can define species' network roles (e.g.,
-specialists vs
-generalists)\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-lazaro2013}{37}}.
-For example, plant species that occupy reproductive trait space extremes
-are more likely to exhibit higher levels of specialisation and be more
-reliant on the trait-matching with
-pollinators\textsuperscript{\protect\hyperlink{ref-junker2013}{38},\protect\hyperlink{ref-coux2016}{39}}.
-Morphological matching between plant and floral visitors often
-determines plant-pollinator interactions, and can thus strongly
-influence interaction network
-structure\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-ibanez2012}{40}}.
-Remarkably, the combination of traits have shown to increase the
-predictive power of the network
-interactions\textsuperscript{\protect\hyperlink{ref-eklof2013}{41}}.
-Therefore, considering the different plant reproductive trade-offs which
-represent the species strategy within the
-network\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}} could
-progress our understanding of plant-pollinator interactions. Further, we
-know little if the different network patterns generally studied at the
-community level are maintained when we scale up at macroecological
-scale.
-
-Here, we aim to explore the potential trade-offs among reproductive
-traits and how these influence plant-pollinator interactions. First, we
-identify the major axes of reproductive trait variation and trade-offs
-that determine plant form and function. Second, we investigate how plant
-species' position in trait-space interactions with floral visitors.
-Finally, we investigate how both the main axes of trait variation, and
-individual traits, influence plant species' roles within networks using
-a set of complementary interaction network metrics (i.e., interaction
-strength, normalized degree and specialization).
-
-\section{RESULTS}\label{results}
-
-\textbf{Plant strategies.} The phylogenetically informed principal
-component analysis (pPCA) captured by the first two and three axes
-51.8\% and 70.97\% of trait variation, respectively (Fig. 1 and
-Supplementary Fig. S5) and had a phylogenetic correlation (\(\lambda\))
-of 0.76. The first principal component (PC1) represented 26.72\% of the
-trait variation and indicated a trade-off between flower number and
-flower size. We refer to this axis as the `flower number - flower size
-trade-off', as already described in previous
-studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{42},\protect\hyperlink{ref-kettle2011}{43}}.
-Hence, one end of the spectrum comprised species with high investment in
-flower number and plant height but small flower size, short style length
-and low ovule number. The other end of this spectrum comprised species
-that were short in height and invested in large flowers, long styles,
-many ovules, but few flowers. The main contributing traits to PC1 were
-plant height, flower number, ovule number and flower size (loadings
-\textgreater{} \textbar{}0.5\textbar{}; Supplementary Table S3) but
-style length also contributed moderately on PC1 (loading = -0.33). The
-second principal component (PC2) represented 25.05\% of the trait
-variation and indicated a trade-off between low and high pollinator
-dependence. We refer to this axis as the `pollinator dependence
-trade-off'. The main driver of trait variation on PC2 was autonomous
-selfing (loading = 0.85) but the other traits (except ovule number) also
-made moderate contributions (loadings from 0.27 to 0.4; Supplementary
-Table S3). We found that high pollinator dependence was associated with
-larger and a higher number of flowers, greater plant height and longer
-styles. In contrast, species with high levels of autonomous selfing
-tended to have fewer and smaller flowers, had shorter styles and were
-shorter in height. Further, PC3 explained a considerable amount of trait
-variability (19.17\%) and the main contributors to this axis were style
-length (loading = -0.66) and the degree of autonomous selfing (loading =
--0.51). The remaining traits, apart from ovule number, were moderately
-correlated to changes on PC3 (loadings from -0.23 to -0.46;
-Supplementary Table S3). Thus, because style length was correlated with
-all traits on PC3 and was the main driver of trait variation, we refer
-to this axis as the `style length trade-off'. Further, the pPCA with the
-subset of species that had nectar and pollen quantity data showed that
-nectar quantity (microlitres of nectar per flower) was positively
-associated with flower size, style length and ovule number (PC1,
-23.40\%); and pollen quantity (pollen grains per flower) was positively
-correlated with flower number and plant height and negatively associated
-with autonomous selfing (PC2, 21.67\%; Supplementary Fig. S6). This pPCA
-explained similar variance with the first two principal components
-(45.07\%) and similar associations of traits despite some variability in
-the loadings (Supplementary Table S4).
+\vspace{5mm}
+\normalsize
+
+Despite the astonishing diversity of floral structures among flowering plants\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}} and their importance in shaping plant-pollinator interactions,\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}} a unified framework that explores plant reproductive compromises is currently lacking.\textsuperscript{\protect\hyperlink{ref-roddy2021}{5}} In addition, macroecological studies that investigate plant reproductive traits are scarce\textsuperscript{\protect\hyperlink{ref-baude2016}{6}--\protect\hyperlink{ref-moeller2017}{9}} and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales.\textsuperscript{\protect\hyperlink{ref-sargent2008}{10}--\protect\hyperlink{ref-ruger2018}{13}} Linking the position in the trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations.\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}} Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{15}} and trait-matching analyses.\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-bartomeus2016}{17}} However, reproductive traits have been overlooked beyond highly specialised pollination systems\textsuperscript{\protect\hyperlink{ref-dellinger2020}{4}} despite the apparent generalist nature of plant-pollinator interactions.\textsuperscript{\protect\hyperlink{ref-waser1996}{18},\protect\hyperlink{ref-olesen2002}{19}} In addition, it is unclear how specific plant reproductive biology traits influence plant-pollinator interactions.\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-devaux2014}{21}}
+
+Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
+With the recent availability of large trait databases (e.g., TRY\textsuperscript{\protect\hyperlink{ref-kattge2011}{22}} and COMPADRE),\textsuperscript{\protect\hyperlink{ref-salguero2015}{23}} plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function {[}\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}};;\textsuperscript{\protect\hyperlink{ref-diaz2016}{24}} bruelheide2018;{]}.\textsuperscript{\protect\hyperlink{ref-carmona2021}{25}} However, most studies have focused on vegetative traits such as leaf,\textsuperscript{\protect\hyperlink{ref-wright2004}{26}} wood,\textsuperscript{\protect\hyperlink{ref-chave2009}{27}} or root\textsuperscript{\protect\hyperlink{ref-laughlin2021}{28}} trade-offs with little or no attention given to reproductive traits\textsuperscript{\protect\hyperlink{ref-roddy2021}{5},\protect\hyperlink{ref-evojtko2020}{29}} which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
+For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively\textsuperscript{\protect\hyperlink{ref-moeller2017}{9},\protect\hyperlink{ref-barrett2003}{30}} and outcrossing levels are positively correlated with flower size.\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{31}} In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species' reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators.\textsuperscript{\protect\hyperlink{ref-ollerton2011}{32},\protect\hyperlink{ref-rodger2021}{33}} However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.
+
+Several studies have identified links between plant traits and plant-pollinator network properties.\textsuperscript{\protect\hyperlink{ref-bartomeus2013}{34}--\protect\hyperlink{ref-rowe2020}{36}} Moreover, plant traits can define species' network roles (e.g., specialists vs generalists).\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-lazaro2013}{37}} For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators.\textsuperscript{\protect\hyperlink{ref-junker2013}{38},\protect\hyperlink{ref-coux2016}{39}} Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure.\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-ibanez2012}{40}} Remarkably, the combination of traits have shown to increase the predictive power of the network interactions.\textsuperscript{\protect\hyperlink{ref-eklof2013}{41}} Therefore, considering the different plant reproductive trade-offs which represent the species strategy within the network\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}} could progress our understanding of plant-pollinator interactions.
+Further, we know little if the different network patterns generally studied at the community level are maintained when we scale up at macroecological scale.
+
+Here, we aim to explore the potential trade-offs among reproductive traits and how these influence plant-pollinator interactions.
+First, we identify the major axes of reproductive trait variation and trade-offs that determine plant form and function.
+Second, we investigate how plant species' position in trait-space interactions with floral visitors.
+Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' roles within networks using a set of complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
+
+\hypertarget{results}{%
+\section{RESULTS}\label{results}}
+
+\textbf{Plant strategies.} The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8\% and 70.97\% of trait variation, respectively (Fig.
+1 and Supplementary Fig.
+S5) and had a phylogenetic correlation (\(\lambda\)) of 0.76.
+The first principal component (PC1) represented 26.72\% of the trait variation and indicated a trade-off between flower number and flower size.
+We refer to this axis as the `flower number - flower size trade-off', as already described in previous studies.\textsuperscript{\protect\hyperlink{ref-sargent2007}{42},\protect\hyperlink{ref-kettle2011}{43}} Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
+The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Supplementary Table S3) but style length also contributed moderately on PC1 (loading = -0.33).
+The second principal component (PC2) represented 25.05\% of the trait variation and indicated a trade-off between low and high pollinator dependence.
+We refer to this axis as the `pollinator dependence trade-off'.
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Supplementary Table S3).
+We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
+In contrast, species with high levels of autonomous selfing tended to have fewer and smaller flowers, had shorter styles and were shorter in height.
+Further, PC3 explained a considerable amount of trait variability (19.17\%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
+The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Supplementary Table S3).
+Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the `style length trade-off'.
+Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 23.40\%); and pollen quantity (pollen grains per flower) was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 21.67\%; Supplementary Fig.
+S6).
+This pPCA explained similar variance with the first two principal components (45.07\%) and similar associations of traits despite some variability in the loadings (Supplementary Table S4).
 
@@
 
-We found that most categorical traits were statistically associated with
-the first two axes of trait variation (Fig. 2 and Supplementary Table
-S2). Flower symmetry, which was only associated with PC2 (Sum of squares
-= 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar
-provision, which was independent of PC1 and PC2 (PC1: Sum of squares =
-0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83,
-F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences
-between the different levels of categorical traits in the trait space
-(Supplementary Fig. S7). Regarding self compatibility, we found larger
-differences on PC2 (i.e., species with unisexual flowers that were self
-incompatible were statistically differentiated from species with partial
-or full self compatibility; Supplementary Fig. S7a and Fig. S7b). Life
-forms differed statistically across both axes of trait variation and
-followed a gradient of larger life forms (trees and shrubs) with higher
-pollinator dependence to smaller ones (herbs) with lower pollinator
-dependence (Supplementary Fig. S7c and Fig. S7d). Consequently, lifespan
-also followed this gradient but perennial and short lived species only
-differed statistically on PC2 (Supplementary Fig. S7e and Fig. S7f).
-Species with unisexual flowers (monoecious and dioecious) were clustered
-on both extremes of the first two principal components and had the
-highest pollinator dependence and highest number of flowers
-(Supplementary Fig. S7g and Fig. S7h). Moreover, we found that the
-campanulate and capitulum flower shapes were differentiated from tube,
-papilionaceous, open and brush shapes in the trait space. The former
-morphologies had larger flowers and greater pollinator dependence, while
-the latter had higher flower number and greater autonomous selfing
-(Supplementary Fig. S7i and Fig. S7j). Regarding flower symmetry,
-zygomorphic flowers were associated with lower levels of pollinator
-dependence, whereas actinomorphic flowers had higher levels of
-pollinator dependence (Supplementary Fig. S7k and Fig. S7l).
+We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
+2 and Supplementary Table S2).
+Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
+In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Supplementary Fig.
+S7).
+Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Supplementary Fig.
+S7a and Fig.
+S7b).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Supplementary Fig.
+S7c and Fig.
+S7d).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Supplementary Fig.
+S7e and Fig.
+S7f).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Supplementary Fig.
+S7g and Fig.
+S7h).
+Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Supplementary Fig.
+S7i and Fig.
+S7j).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Supplementary Fig.
+S7k and Fig.
+S7l).
 
@@
 
-\textbf{Phylogenetic signal of traits.} We found a strong phylogenetic
-signal (\emph{P} \textless{} 0.01) in all quantitative traits
-(Supplementary Table S5). The traits that showed the highest
-phylogenetic signal were ovule number (\(\lambda = 1\)), pollen grains
-per flower (\(\lambda = 1\)) and plant height (\(\lambda = 0.96\)),
-followed by flower length (\(\lambda = 0.75\)), flower width
-(\(\lambda = 0.73\)), number of flowers per plant (\(\lambda = 0.69\))
-and nectar concentration (\(\lambda = 0.65\)). The traits that showed a
-moderate phylogenetic signal were inflorescence width
-(\(\lambda = 0.57\)), style length (\(\lambda = 0.49\)) and autonomous
-selfing (\(\lambda = 0.34\)). Finally, microliters of nectar per flower
-showed the lowest phylogenetic signal of all traits
-(\(\lambda = 0.14\)).
-
-\textbf{Visitation patterns.} The main axes of trait variation explained
-partly presence-absence interactions between plant and floral visitors
-(\(conditional R2 = 0.26\); \(marginal R2 = 0.20\)) but little of the
-overall visitation rates (\(conditional R2 = 0.31\);
-\(marginal R2 = 0.06\)). However, we found relevant trends across the
-different floral visitor guilds on both presence-absence and visitation
-interactions (Fig. 3). On the pollinator dependence trade-off, all
-floral visitor guilds interacted more frequently with plant species with
-higher pollinator dependence (PC2; Fig. 3b and Fig. 3e). For
-presence-absence interactions we found that all Diptera, Coleoptera and
-non-bee Hymenoptera guilds interacted more frequently with plants with
-high flower number and small flowers (flower number - flower size
-trade-off, PC1; Fig. 3a) but bees and Lepidoptera interacted slightly
-more frequently with plant species with low flower number but large
-flowers. For presence-absence interactions on PC3 (style length
-trade-off; Fig. 3c), we found that bees interacted clearly more with
-plant species with long styles and high selfing and the rest of the
-guilds interacted slightly more with plant species with short styles and
-low selfing. In addition, all guilds other than Syrphids and Lepidoptera
-(i.e., all Hymenoptera, non-Syrphidae-Diptera and Coleoptera) showed
-greater visitation rates on species with small numerous flowers (PC1;
-Fig. 3d). On the style length trade-off, bees, Lepidoptera and
-Non-Anthophila-Hymenoptera showed greater visitation rates on plant
-species with larger styles and higher levels of selfing; while
-Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation
-rates on species with shorter styles and lower selfing (Fig. 3f).
-
-The additional model for both presence-absence of interactions
-(\(marginal R2 = 0.29\); \(conditional R2 = 0.19\)) and visitation rate
-(\(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) for the most
-represented families of bees showed that the family Apidae was the main
-driver of the observed patterns and that the contrasting differences
-between presence-absence and visitation rate for bees on PC1 (Fig. 3a
-and Fig. 3d) were driven by the family Andrenidae which interacted more
-frequently on presence-absence interactions with plant species with low
-number of flower but large (Supplementary Fig. S8).
+\textbf{Phylogenetic signal of traits.} We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) in all quantitative traits (Supplementary Table S5).
+The traits that showed the highest phylogenetic signal were ovule number (\(\lambda = 1\)), pollen grains per flower (\(\lambda = 1\)) and plant height (\(\lambda = 0.96\)), followed by flower length (\(\lambda = 0.75\)), flower width (\(\lambda = 0.73\)), number of flowers per plant (\(\lambda = 0.69\)) and nectar concentration (\(\lambda = 0.65\)).
+The traits that showed a moderate phylogenetic signal were inflorescence width (\(\lambda = 0.57\)), style length (\(\lambda = 0.49\)) and autonomous selfing (\(\lambda = 0.34\)).
+Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits (\(\lambda = 0.14\)).
+
+\textbf{Visitation patterns.} The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors (\(conditional R2 = 0.26\); \(marginal R2 = 0.20\)) but little of the overall visitation rates (\(conditional R2 = 0.31\); \(marginal R2 = 0.06\)).
+However, we found relevant trends across the different floral visitor guilds on both presence-absence and visitation interactions (Fig.
+3).
+On the pollinator dependence trade-off, all floral visitor guilds interacted more frequently with plant species with higher pollinator dependence (PC2; Fig.
+3b and Fig.
+3e).
+For presence-absence interactions we found that all Diptera, Coleoptera and non-bee Hymenoptera guilds interacted more frequently with plants with high flower number and small flowers (flower number - flower size trade-off, PC1; Fig.
+3a) but bees and Lepidoptera interacted slightly more frequently with plant species with low flower number but large flowers.
+For presence-absence interactions on PC3 (style length trade-off; Fig.
+3c), we found that bees interacted clearly more with plant species with long styles and high selfing and the rest of the guilds interacted slightly more with plant species with short styles and low selfing.
+In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig.
+3d).
+On the style length trade-off, bees, Lepidoptera and Non-Anthophila-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
+3f).
+
+The additional model for both presence-absence of interactions (\(marginal R2 = 0.29\); \(conditional R2 = 0.19\)) and visitation rate (\(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns and that the contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
+3a and Fig.
+3d) were driven by the family Andrenidae which interacted more frequently on presence-absence interactions with plant species with low number of flower but large (Supplementary Fig.
+S8).
 
@@
 \includegraphics{output/figures/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}\textbf{Fig. 3 \textbar{} Interaction
-(yes/no) and visitation rates across the three main axes of trait
-variation per floral visitor guild.} Fitted posterior estimates of the
-presence/absence of interaction (a, b and c) and number of visits (d, e
-and f) made by the different floral visitors guilds in relation to PC1,
-PC2 and PC3. PC1 represents the flower number - flower size trade-off,
-PC2 represents the pollinator dependence trade-off and PC3, the style
-length trade-off. For visualization purposes, due to large differences
-between the visitation rates of bees and the rest of guilds, the number
-of visits was log-transformed (Y-axis of lower panel).}
+\caption{\label{fig:unnamed-chunk-3}\textbf{Fig.
+3 \textbar{} Interaction (yes/no) and visitation rates across the three main axes of trait variation per floral visitor guild.} Fitted posterior estimates of the presence/absence of interaction (a, b and c) and number of visits (d, e and f) made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
+PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.
+For visualization purposes, due to large differences between the visitation rates of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel).}
 \end{figure}
@@
 
-\textbf{Plant species functional roles.} The variance of the different
-plant species-level network metrics was poorly explained by the three
-main axes of trait variation (Supplementary Fig. S9; interaction
-frequency \textasciitilde{} PCs, \(conditional R2 = 0.11\),
-\(marginal R2 = 0.02\); normalized degree \textasciitilde{} PCs,
-\(conditional R2 = 0.24\), \(marginal R2 = 0.02\); and, specialization
-\textasciitilde{} PCs, \(conditional R2 = 0.37\),
-\(marginal R2 = 0.03\)). Overall, the most notable trends were found on
-PC1 and PC3 for interaction frequency and specialization. On the flower
-number - flower size trade-off (PC1), interaction frequency was higher
-for plant species with more flowers but was lower for plant species with
-larger flowers. On PC1, specialization showed the opposite trend. On the
-style length trade-off (PC3), interaction frequency was lower for plants
-with shorter styles and lower autonomous selfing and higher for species
-with longer styles and higher autonomous selfing. Again, specialization
-showed the opposite trend to interaction frequency.
-
-When we further investigate which combination of traits drive plant
-network roles, we show that the regression tree for visitation frequency
-was best explained by plant height, nectar concentration and style
-length (Fig. 4a). Specifically, species taller than 3.9 m had the
-highest interaction frequency, while species that were shorter than 3.9
-m and had a nectar concentration lower than 16\% had the lowest
-interaction frequency. Normalized degree was best explained by nectar
-concentration, pollen grains per flower, plant height, flower width and
-autonomous selfing (Fig. 4b). Species with a nectar concentration over
-49\% had the highest levels of normalized degree, whereas species with
-nectar concentration lower than 49\%, more than 21,000 pollen grains per
-flower and height less than 0.78 m had the lowest normalized degree.
-Finally, specialization was best explained by plant height, ovule
-number, pollen grains per flower and autonomous selfing (Fig. 4c).
-Overall, plant species with the highest specialization were shorter than
-1.3 m, had more than 14,000 pollen grains per flower and autonomously
-self-pollinated less than 11\% of their fruits. In contrast, species
-taller or equal than 5.1 m and with lower than 14 ovules per flower had
-the lowest specialization values.
+\textbf{Plant species functional roles.} The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
+S9; interaction frequency \textasciitilde{} PCs, \(conditional R2 = 0.11\), \(marginal R2 = 0.02\); normalized degree \textasciitilde{} PCs, \(conditional R2 = 0.24\), \(marginal R2 = 0.02\); and, specialization \textasciitilde{} PCs, \(conditional R2 = 0.37\), \(marginal R2 = 0.03\)).
+Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
+On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers.
+On PC1, specialization showed the opposite trend.
+On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing.
+Again, specialization showed the opposite trend to interaction frequency.
+
+When we further investigate which combination of traits drive plant network roles, we show that the regression tree for visitation frequency was best explained by plant height, nectar concentration and style length (Fig.
+4a).
+Specifically, species taller than 3.9 m had the highest interaction frequency, while species that were shorter than 3.9 m and had a nectar concentration lower than 16\% had the lowest interaction frequency.
+Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
+4b).
+Species with a nectar concentration over 49\% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49\%, more than 21,000 pollen grains per flower and height less than 0.78 m had the lowest normalized degree.
+Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
+4c).
+Overall, plant species with the highest specialization were shorter than 1.3 m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11\% of their fruits.
+In contrast, species taller or equal than 5.1 m and with lower than 14 ovules per flower had the lowest specialization values.
 
@@
 \includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\textbf{Fig. 4 \textbar{} Contribution
-of traits in plant's network roles.} Regression tree analysis of
-interaction frequency (log-transformed), normalized degree and
-specialization for the subset of species with quantitative data for
-pollen and nectar traits. The superior value inside the node indicates
-the mean value of the different species-level metric and the lower
-value, the percentage of species that are considered in each node. Thus,
-the top node has the mean value of the named trait for the 100\% of
-species. Each node has a yes/no question and when the condition is
-fulfilled, the branch turns to the `yes' direction and when not, to the
-`no' direction. This rationale is followed in all the regression trees
-as indicated in the first branch division of the topmost node of each
-tree.}
+\caption{\label{fig:unnamed-chunk-4}\textbf{Fig.
+4 \textbar{} Contribution of traits in plant's network roles.} Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
+The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
+Thus, the top node has the mean value of the named trait for the 100\% of species.
+Each node has a yes/no question and when the condition is fulfilled, the branch turns to the `yes' direction and when not, to the `no' direction.
+This rationale is followed in all the regression trees as indicated in the first branch division of the topmost node of each tree.}
 \end{figure}
@@
 
-\section{DISCUSSION}\label{discussion}
-
-Here, we show that plant species exhibit clear trade-offs among their
-vegetative and reproductive traits that determined different interaction
-levels with floral visitor guilds. These trade-offs are differentiated
-on three main axes of trait variation: (i) flower number - flower size,
-(ii) pollinator dependence and (iii) style length. These reproductive
-trade-offs somewhat explained the presence or absence of interactions
-with floral visitors, but not differences in visitation rate. However,
-on both qualitative and quantitative interactions we found marked
-associations of floral visitor guilds with the main axes of trait
-variation. Further, we found that plant height and floral reward related
-traits were best at characterising plant species functional roles within
-pollination networks.
-
-Over half of all plant trait variation was captured by the flower number
-- flower size and pollinator dependence trade-offs. Trait variation on
-these two axes was associated with the `fast-slow continuum' in
-plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}} and
-animal\textsuperscript{\protect\hyperlink{ref-healy2019}{44}}
-life-history strategies, as indicated by the different floral and
-reproductive biology traits associated with plant height, life form and
-lifespan. The `slow' part of this continuum (i.e., tall trees and
-shrubs) included plant species with many flowers, few ovules, higher
-pollinator dependence, frequent occurrence of self-incompatibility and
-more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, plant species that employed the `fast' strategy (i.e.,
-short herbs), had fewer flowers, more ovules, frequent occurrence of
-self-compatibility and lower pollinator dependence. Further, on the
-first two axes of trait variation, we found additional support for the
-previously described positive association between higher outcrossing
-rate and larger floral
-display\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{31}}. The
-positive correlation between larger floral display and higher pollinator
-dependence in our dataset further confirmed this trend (see
-Supplementary Fig. S10).
-
-Despite the low predictive power of the main trait variation axes for
-broad-level interaction patterns (presence-absence of interactions and
-visitation rate), we found changes in the interaction patterns among and
-within floral visitor guilds across these axes that suggest plant
-life-history strategies strongly influence plant-pollinator
-interactions. For example, all floral visitor guilds visited plant
-species with higher pollinator dependence more frequently, and high
-pollinator dependence was associated with large floral displays and
-greater pollen quantities (Fig. 1 and Supplementary Fig. S6). This trend
-is consistent with previous studies that show plant species with higher
-reproductive investment tend to be visited by pollinators more
-frequently\textsuperscript{\protect\hyperlink{ref-lazaro2013}{37},\protect\hyperlink{ref-hegland2005}{45},\protect\hyperlink{ref-kaiser2014}{46}}.
-In regard to the flower number - flower size and style length
-trade-offs, different pollinator guilds showed contrasting visitation
-rates across the continuum of trait variation, which could be associated
-with different pollination syndromes at a macroecological scale. For
-instance, bees and syrphid flies were clearly associated with opposing
-life-strategies on PC1 and PC3 (Fig. 3) suggesting possible niche
-partitioning\textsuperscript{\protect\hyperlink{ref-palmer2003}{47},\protect\hyperlink{ref-phillips2020}{48}}
-between these two guilds. However, despite floral rewards, related
-traits were among the best at characterising species functional roles
-(Fig. 4), yet the association between reproductive trade-offs and floral
-visitors did not account for floral rewards because there was
-insufficient data available. More detailed exploration of reproductive
-trade-offs in conjunction with floral rewards is needed to help
-elucidate plant-pollinator associations. In any case, it is worth noting
-that other local factors such as species relative abundances, surely
-explain part of the observed
-variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{17},\protect\hyperlink{ref-vazquez2007}{49},\protect\hyperlink{ref-encinas2012}{50}}
-that reproductive trade-offs do not.
-
-To conclude, we provide the first description of plant reproductive
-trade-offs using a large global dataset of plant traits. We identified
-the major reproductive strategies of flowering plants and how these
-strategies influence interactions with different floral visitor guilds.
-Although the explained variation that we found in the first two axes is
-lower than previous studies of vegetative
-traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{25}}
-it is consistent with the largest and most recent study that has
-characterised plant life strategies with vegetative and reproductive
-traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}}. Future
-work needs to integrate the reproductive compromises that we have
-identified with vegetative and physiological trade-offs to create a more
-comprehensive spectrum of plant trait variation. Further, the varying
-level of phylogenetic signal among traits deserves further attention to
-understand evolutionary changes on mating and flower morphology in
-response to
-pollinators\textsuperscript{\protect\hyperlink{ref-gervasi2017}{51},\protect\hyperlink{ref-mackin2021}{52}}.
-Finally, including plant-pollinator networks from unrepresented areas of
-the world and a more complete description of plant reproductive
-trade-offs is essential for a better understanding of the global
-patterns in plant-pollinator interactions.
-
-\section{MATERIALS AND METHODS}\label{materials-and-methods}
-
-\textbf{Plant-pollinator network studies.} We selected 28 studies from
-18 different countries that constituted a total of 64 plant-pollinator
-networks. These studies recorded plant-pollinator interactions in
-natural systems and were selected so that we had broad geographical
-representation. Although these studies differ in sampling effort and
-methodology, all studies provided information about plant-pollinator
-interactions (weighted and non-weighted), which we used to build a
-database of plant species that are likely to be animal pollinated. Many
-of these networks are freely available either as published
-studies\textsuperscript{\protect\hyperlink{ref-fortuna2010}{53},\protect\hyperlink{ref-carvalheiro2014}{54}}
-or available in online archives (e.g., `The Web of
-Life'\textsuperscript{\protect\hyperlink{ref-fortuna2010}{53}} and
-`Mangal'\textsuperscript{\protect\hyperlink{ref-poisot2016}{55}}. In
-total, our network dataset (see Supplementary Table S1) constituted 60
-weighted (interaction frequency) and 4 unweighted (presence/absence of
-the interaction) networks, each sampled at a unique location and year,
-as well as eight meta-webs where interactions were pooled across several
-locations and multiple years.
-
-\textbf{Taxonomy of plants and pollinators.} All species names, genera,
-families and orders were retrieved and standardized from the taxonomy
-data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for
-plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the
-R package
-\emph{taxize}\textsuperscript{\protect\hyperlink{ref-chamberlain2020}{56}}.
-We filled the `not found' searches manually using
-\url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for
-plants and \url{http://www.catalogueoflife.org/} for floral visitors.
-
-\textbf{Functional traits.} We selected 20 different functional traits
-based on their relevance to plant reproduction and data availability
-(Table 1). These included twelve quantitative and eight categorical
-traits belonging to three broader trait groupings (13 floral, 4
-reproductive biology and 3 vegetative, Supplementary Information). For
-each plant species, we undertook an extensive literature and online
-search across a wide range of resources (plant databases, online floras,
-books, journals and images). From a total of 30,120 cells (20 columns ×
-1,506 species) we were able to fill 24,341 cells (80.8\% of the dataset,
-see Supplementary Fig. S1 for missing values information for each
-trait).
-
-\textbf{Phylogenetic Distance.} We calculated the phylogenetic distance
-between different plant species using the function \emph{get\_tree} from
-the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}),
-which downloads phylogenetic distances from the extended R
-implementation of the Open Tree of
-Life\textsuperscript{\protect\hyperlink{ref-smith2018}{57},\protect\hyperlink{ref-jin2019}{58}}.
+\hypertarget{discussion}{%
+\section{DISCUSSION}\label{discussion}}
+
+Here, we show that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
+These trade-offs are differentiated along three axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
+These reproductive trade-offs helped explain the presence of floral visitor interactions, but not their visitation rates.
+Floral visitor guilds formed distinct relationships with the main axes of trait variation.
+Moreover, we found that the plant species functional roles within pollination networks were best explained by plant size and floral reward related traits.
+
+Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
+Trait variation on these two axes was associated with the `fast-slow continuum' in plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}} and animal\textsuperscript{\protect\hyperlink{ref-healy2019}{44}} life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+The `slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
+In contrast, plant species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
+Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display.\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{31}} The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Supplementary Fig.
+S10).
+
+Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (presence-absence of interactions and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies strongly influence plant-pollinator interactions.
+For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
+1 and Supplementary Fig.
+S6).
+This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently.\textsuperscript{\protect\hyperlink{ref-lazaro2013}{37},\protect\hyperlink{ref-hegland2005}{45},\protect\hyperlink{ref-kaiser2014}{46}} In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation rates across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
+For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
+3) suggesting possible niche partitioning\textsuperscript{\protect\hyperlink{ref-palmer2003}{47},\protect\hyperlink{ref-phillips2020}{48}} between these two guilds.
+However, despite floral rewards, related traits were among the best at characterising species functional roles (Fig.
+4), yet the association between reproductive trade-offs and floral visitors did not account for floral rewards because there was insufficient data available.
+More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{17},\protect\hyperlink{ref-vazquez2007}{49},\protect\hyperlink{ref-encinas2012}{50}} that reproductive trade-offs do not.
+
+To conclude, we provide the first description of plant reproductive trade-offs using a large global dataset of plant traits.
+We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
+Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{25}} it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits.\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}} Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
+Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators.\textsuperscript{\protect\hyperlink{ref-gervasi2017}{51},\protect\hyperlink{ref-mackin2021}{52}} Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
+
+\hypertarget{materials-and-methods}{%
+\section{MATERIALS AND METHODS}\label{materials-and-methods}}
+
+\textbf{Plant-pollinator network studies.} We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
+These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
+Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
+Many of these networks are freely available either as published studies {[}(Olesen et al., 2007;;\textsuperscript{\protect\hyperlink{ref-fortuna2010}{53}}{]}\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{54}} or available in online archives (e.g., `The Web of Life'\textsuperscript{\protect\hyperlink{ref-fortuna2010}{53}} and `Mangal'.\textsuperscript{\protect\hyperlink{ref-poisot2016}{55}} In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+
+\textbf{Taxonomy of plants and pollinators.} All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} {[}version \emph{0.9.99};{]}.\textsuperscript{\protect\hyperlink{ref-chamberlain2020}{56}} We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
+
+\textbf{Functional traits.} We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
+These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive biology and 3 vegetative, Supplementary Information).
+For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
+From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8\% of the dataset, see Supplementary Fig.
+S1 for missing values information for each trait).
+
+\textbf{Phylogenetic Distance.} We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life.\textsuperscript{\protect\hyperlink{ref-smith2018}{57},\protect\hyperlink{ref-jin2019}{58}}
 
@@
 
-\textbf{Data Imputation.} Trait missing values were imputed with the
-function
-\emph{missForest}\textsuperscript{\protect\hyperlink{ref-stekhoven2012}{59}}
-which allows imputation of data sets with continuous and categorical
-variables. We accounted for the phylogenetic distance among species on
-the imputation process by including the eigenvectors of a principal
-component analysis of the phylogenetic distance (PCoA) which has been
-shown to improve the performance of
-\emph{missForest}\textsuperscript{\protect\hyperlink{ref-penone2014}{60}}.
-To extract the eigenvectors, we used the function \emph{PVRdecomp} from
-the package
-\emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{61}} based
-on a previous conceptual framework that considers phylogenetic
-eigenvectors\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{62}}.
-Although the variable of autonomous selfing had a high percentage of
-missing values (68\%), we were able to solve this by back transforming
-the qualitative column of autonomous selfing to numerical. The
-categories of `none', `low', `medium' and `high' were converted to
-representative percentages of each category 0\%, 13\%, 50.5\% and 88\%
-respectively. This reduced the percentage of missing values for this
-column from 68\% to 35\% and allowed the imputation of this variable.
-However, we were unable to include nectar and pollen traits on the
-imputation process because of the high percentage of missing values
-(Supplementary Fig. S1). Hence, the imputed dataset had 1,506 species,
-seven categorical and eight numerical variables and 5.79\% of missing
-values. Further, we conducted an additional imputation on the filtered
-raw data by filled cells of either pollen grains per flower or
-microlitres of nectar. This subset comprised 755 species, 8.01\% missing
-values and all traits but milligrams of nectar (\textasciitilde{}50\% of
-missing values) were included in the imputation process.
-
-\textbf{Plant strategies.} We explored the trade-offs between different
-quantitative plant functional traits with a phylogenetically informed
-Principal Component Analysis (pPCA). We did not include the quantitative
-variables of flower length and inflorescence width because they were
-highly and moderately correlated to flower width respectively (Pearson's
-correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation
-= 0.36, \emph{P} \textless{} 0.01 respectively), and thus we avoided
-overemphasizing flower size on the spectrum of trait variation. Although
-qualitative traits were not included in the dimensionality reduction
-analysis, we also investigated the association of the different
-qualitative traits with the main axes of trait variation. Prior to the
-analyses, we excluded outliers and standardized the data. Due to the
-high sensitivity of dimensionality reduction to outliers, we excluded
-values within the 2.5th--97.5th percentile
-range\textsuperscript{\protect\hyperlink{ref-legendre2012}{63}}, and
-thus our final dataset had 1,236 species. Then, we log transformed the
-variables to reduce the influence of outliers and z-transformed (X= 0,
-SD=1) so that all variables were within the same numerical range. We
-performed the pPCA using the function \emph{phyl.pca} from the package
-\emph{phytools}\textsuperscript{\protect\hyperlink{ref-revell2012}{64}}
-with the method lambda (\(\lambda\)) that calculates the phylogenetic
-correlation between 0 (phylogenetic independence) and 1 (shared
-evolutionary history) and we implemented the mode covariance because
-values for each variables were on the same scale following
-transformation\textsuperscript{\protect\hyperlink{ref-abdi2010}{65}}.
-Moreover, to corroborate that our imputation of missing values did not
-affect our results, we conducted a pPCA on the full dataset without
-missing values (see Supplementary Fig. S2). We found little difference
-between the explained variance with the imputed dataset (51.08\%) and
-the dataset without missing values (52.87\%). In addition, the loadings
-on each principal component had a similar contribution and correlation
-patterns, with the exception of plant height which showed slight
-variations between the imputed and non-imputed dataset. Finally, we
-conducted an additional phylogenetic informed principal component
-analysis for the subset of species with pollen and nectar quantity. For
-this, we included all quantitative traits considered in the main pPCA
-plus pollen grains and microlitres of nectar per flower.
-
-\textbf{Phylogenetic signal of traits.} We calculated the phylogenetic
-signal of the different quantitative traits on the imputed dataset with
-the full set of species (N = 1,506) with the package \emph{phytools}
-version
-\emph{0.7-70}\textsuperscript{\protect\hyperlink{ref-revell2012}{64}}
-and we used Pagel's \(\lambda\) as a measurement of the phylogenetic
-signal. However, for pollen and nectar traits, phylogenetic signal was
-calculated only on the subset of species that had quantitative
-information for these traits (N = 755).
-
-\textbf{Network analyses.} Analyses were conducted on the subset of 60
-weighted networks sampled in a unique flowering season and site, which
-included 556 plant and 1,126 pollinator species. These networks were
-analysed in their qualitative (presence-absence) and quantitative
-(interaction frequency) form. First, we analysed the binary version of
-these weighted networks with presence-absence information that assumes
-equal weight across interactions. Second, we analysed the untransformed
-weighted networks with interaction frequency that accounts for the
-intensity of the interaction. Although floral visitors are not always
-pollinators and interaction frequency does not consider each pollinator
-species
-efficiency\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{66}},
-interaction frequency can provide valuable information of the
-contribution of floral visitors to
-pollination\textsuperscript{\protect\hyperlink{ref-vazquez2005}{67},\protect\hyperlink{ref-vazquez2012}{68}}.
-In total, our network dataset (excluding meta-webs and non-weighted
-networks) included 2,256 interactions of Anthophila-Hymenoptera (i.e.,
-bees) with plants, 1,768 non-Syrphidae-Diptera interactions, 845
-Syrphidae interactions, 437 Lepidoptera interactions, 432 Coleoptera
-interactions and 362 non-Anthophila-Hymenoptera interactions. Sampling
-methods varied across networks but this was accounted for in analyses by
-considering them in the random effects of the modelling process. All
-analyses were conducted in R version \emph{4.0.3}.
-
-\textbf{Visitation patterns.} We used Bayesian modelling (see below for
-details) to explore the effect of floral visitor groups and the main
-axes of trait variation (pPCA with imputed dataset) on both qualitative
-(presence/absence) and quantitative (visitation rate) floral
-interactions per plant species. For this, we divided floral visitors
-into six main guilds that differ in life form, behaviour and are likely
-to play a similar ecological role: (i) Hymenoptera-Anthophila (bees),
-(ii) Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii)
-Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi)
-Coleoptera. Moreover, because Hymenoptera-Anthophila was the most
-represented group with 2,256 records and had the highest frequency of
-visits of all groups, we also explored the presence-absence of
-interaction and visitation rate of the main Hymenoptera-Anthophila
-families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae)
-on the trait space. In addition, we found that \emph{Apis mellifera} was
-the floral visitor with the largest proportion of records counted
-(7.55\% of the total). This finding is consistent with previous research
-showing that \emph{A. mellifera} was the most frequent floral visitor in
-a similar dataset of 80 plant-pollinator networks in natural
-ecosystems\textsuperscript{\protect\hyperlink{ref-hung2018}{69}}. Hence,
-to control for the effect of \emph{A. mellifera} on the observed
-visitation patterns of bees, we conducted an analogous analysis with
-presence-absence of interaction and visitation rate excluding \emph{A.
-mellifera}. We found that \emph{A. mellifera}, was partly driving some
-of the observed trends on PC1 (Supplementary Fig. S3). However, we did
-not detect major differences on PC2 and PC3.
-
-We implemented Bayesian generalized linear mixed models using the R
-package
-\emph{brms}\textsuperscript{\protect\hyperlink{ref-burkner2017}{70}}. We
-modelled the frequency of visits as a function of the main axes of plant
-trait variation and their interactions with floral visitor functional
-groups (Visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation
-patterns among floral visitors groups to plants with different
-strategies, we included interactions between the main axes of trait
-variation (PC1, PC2 and PC3) and the floral visitor guilds. In this
-model, we added a nested random effect of networks nested within the
-study system to capture the variation in networks among studies and
-within networks. Moreover, we included the phylogenetic covariance
-matrix as a random factor due to the possible shared evolutionary
-histories of species and therefore lack of independence across them. We
-specified this model with a zero inflated negative binomial distribution
-and weakly informative priors from the brms function. We run this model
-for 3,000 iterations and with previous 1,000 warm up iterations. We set
-delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized
-the posterior predictive checks with the function \emph{pp\_check} using
-the \emph{bayesplot}
-package\textsuperscript{\protect\hyperlink{ref-gabry2019}{71}}.
-
-\textbf{Plant species functional roles.} We investigated whether
-different quantitative traits determined plant species functional roles
-using Bayesian modelling and regression trees. For this, we selected
-simple and complementary species-level network metrics commonly applied
-in bipartite network
-studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{72}} with a
-straightforward ecological interpretation relevant to our research
-goals. The different plant species-level metrics were: (i) sum of visits
-per plant species; (ii) normalized degree, calculated as the number of
-links per plant species divided by the total possible number of
-partners; and (iii)
-specialization\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{73}},
-which measures the deviation of an expected random choice of the
-available interaction partners and ranges between 0 (maximum
-generalization) and 1 (maximum specialization). Normalized degree and
-specialization were calculated with the \emph{specieslevel} function
-from the R package
-\emph{bipartite}\textsuperscript{\protect\hyperlink{ref-dormann2008}{72}}.
-
-First, we modelled the distinct plant species metrics (sum of visits,
-normalized degree and plant specialization) as a function of the three
-main axes of trait variation (plant species level metric
-\textasciitilde{} PC1 + PC2 + PC3). For each response variable (i.e.,
-each plant species level metric), we used different distribution
-families (zero inflated negative binomial for the sum of visits, weibull
-for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted
-the same posterior predictive checks for each model as detailed above in
-the `visitation patterns section'.
-
-Second, to better understand these complex trait relationships, we used
-regression trees. Regression trees are recursive algorithms which can
-detect complex relationships among predictors and allow identification
-of the relevance of specific trait combinations on species functional
-roles. We focused exclusively on quantitative traits because almost all
-categorical traits were statistically associated with the first two axes
-of trait variation (Supplementary Table S2). We conducted this analysis
-using the \emph{rpart}
-package\textsuperscript{\protect\hyperlink{ref-therneau2015}{74}}
-version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50
-observations per terminal node and we used the \emph{rpart.plot}
-package\textsuperscript{\protect\hyperlink{ref-milborrow2015}{75}}
-version \emph{3.0.9} to plot the regression trees. We considered the
-species level indices as response variables (interaction frequency,
-normalized degree and specialization) and we performed one regression
-tree per metric using the different quantitative traits as predictors.
-We calculated two regression trees per plant species-level metric, one
-for the full set of species and another for the subset of species for
-which we had pollen and nectar traits. We focused on regression trees
-that included floral rewards because they consistently showed pollen and
-nectar traits as being the best for explaining the different
-species-level metrics (see Supplementary Fig. S4).
-
-\section{References}\label{references}
+\textbf{Data Imputation.} Trait missing values were imputed with the function \emph{missForest}\textsuperscript{\protect\hyperlink{ref-stekhoven2012}{59}} which allows imputation of data sets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest}.\textsuperscript{\protect\hyperlink{ref-penone2014}{60}} To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{61}} based on a previous conceptual framework that considers phylogenetic eigenvectors.\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{62}} Although the variable of autonomous selfing had a high percentage of missing values (68\%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
+The categories of `none', `low', `medium' and `high' were converted to representative percentages of each category 0\%, 13\%, 50.5\% and 88\% respectively.
+This reduced the percentage of missing values for this column from 68\% to 35\% and allowed the imputation of this variable.
+However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Supplementary Fig.
+S1).
+Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79\% of missing values.
+Further, we conducted an additional imputation on the filtered raw data by filled cells of either pollen grains per flower or microlitres of nectar.
+This subset comprised 755 species, 8.01\% missing values and all traits but milligrams of nectar (\textasciitilde50\% of missing values) were included in the imputation process.
+
+\textbf{Plant strategies.} We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01 respectively), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
+Prior to the analyses, we excluded outliers and standardized the data.
+Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th--97.5th percentile range,\textsuperscript{\protect\hyperlink{ref-legendre2012}{63}} and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}version \emph{0.7-70};{]}\textsuperscript{\protect\hyperlink{ref-revell2012}{64}} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation.\textsuperscript{\protect\hyperlink{ref-abdi2010}{65}} Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
+S2).
+We found little difference between the explained variance with the imputed dataset (51.08\%) and the dataset without missing values (52.87\%).
+In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
+Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
+For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
+
+\textbf{Phylogenetic signal of traits.} We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} version \emph{0.7-70}\textsuperscript{\protect\hyperlink{ref-revell2012}{64}} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
+
+\textbf{Network analyses.} Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+These networks were analysed in their qualitative (presence-absence) and quantitative (interaction frequency) form.
+First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
+Second, we analysed the untransformed weighted networks with interaction frequency that accounts for the intensity of the interaction.
+Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency,\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{66}} interaction frequency can provide valuable information of the contribution of floral visitors to pollination.\textsuperscript{\protect\hyperlink{ref-vazquez2005}{67},\protect\hyperlink{ref-vazquez2012}{68}} In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-Anthophila-Hymenoptera interactions.
+Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
+All analyses were conducted in R version \emph{4.0.3}.
+
+\textbf{Visitation patterns.} We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
+For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
+Moreover, because Hymenoptera-Anthophila was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total).
+This finding is consistent with previous research showing that \emph{A.
+mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems.\textsuperscript{\protect\hyperlink{ref-hung2018}{69}} Hence, to control for the effect of \emph{A.
+mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of interaction and visitation rate excluding \emph{A.
+mellifera}.
+We found that \emph{A.
+mellifera}, was partly driving some of the observed trends on PC1 (Supplementary Fig.
+S3).
+However, we did not detect major differences on PC2 and PC3.
+
+We implemented Bayesian generalized linear mixed models using the R package \emph{brms} {[}version \emph{2.14.6};{]}.\textsuperscript{\protect\hyperlink{ref-burkner2017}{70}} We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
+In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
+Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
+We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
+We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}version \emph{1.7.2};{]}.\textsuperscript{\protect\hyperlink{ref-gabry2019}{71}}
+
+\textbf{Plant species functional roles.} We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{72}} with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization {[}d';{]},\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{73}} which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} {[}version \emph{2.15};{]}.\textsuperscript{\protect\hyperlink{ref-dormann2008}{72}}
+
+First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
+For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
+Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns section'.
+
+Second, to better understand these complex trait relationships, we used regression trees.
+Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
+We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
+We conducted this analysis using the \emph{rpart} package\textsuperscript{\protect\hyperlink{ref-therneau2015}{74}} version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package\textsuperscript{\protect\hyperlink{ref-milborrow2015}{75}} version \emph{3.0.9} to plot the regression trees.
+We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
+We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
+We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig.
+S4).
+
+\hypertarget{references}{%
+\section{References}\label{references}}
 
 \hypertarget{refs}{}
-\hypertarget{ref-barrett2002}{}
-1. Barrett, S. C. H. The evolution of plant sexual diversity. \emph{Nat.
-Rev. Genet.} \textbf{3}, 274--284 (2002).
-
-\hypertarget{ref-schiestl2013}{}
-2. Schiestl, F. P. \& Johnson, S. D. Pollinator-mediated evolution of
-floral signals. \emph{Trends Ecol. Evol.} \textbf{28}, 307--315 (2013).
-
-\hypertarget{ref-fenster2004}{}
-3. Fenster, C. B., Armbruster, W. S., Wilson, P., Dudash, M. R. \&
-Thomson, J. D. Pollination Syndromes and Floral Specialization.
-\emph{Annu. Rev. Ecol. Evol. Syst.} \textbf{35}, 375--403 (2004).
-
-\hypertarget{ref-dellinger2020}{}
-4. Dellinger, A. S. Pollination syndromes in the 21st century: Where do
-we stand and where may we go? \emph{New Phytol.} \textbf{228},
-1193--1213 (2020).
-
-\hypertarget{ref-roddy2021}{}
-5. Roddy, A. B. \emph{et al.} Towards the flower economics spectrum.
-\emph{New Phytol.} \textbf{229}, 665--672 (2021).
-
-\hypertarget{ref-baude2016}{}
-6. Baude, M. \emph{et al.} Historical nectar assessment reveals the fall
-and rise of floral resources in britain. \emph{Nature} \textbf{530},
-85--88 (2016).
-
-\hypertarget{ref-munoz2016}{}
-7. Munoz, F., Violle, C. \& Cheptou, P.-O. CSR ecological strategies and
-plant mating systems: Outcrossing increases with competitiveness but
-stress-tolerance is related to mixed mating. \emph{Oikos} \textbf{125},
-1296--1303 (2016).
-
-\hypertarget{ref-grossenbacher2017}{}
-8. Grossenbacher, D. L. \emph{et al.} Self-compatibility is
-over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478
-(2017).
-
-\hypertarget{ref-moeller2017}{}
-9. Moeller, D. A. \emph{et al.} Global biogeography of mating system
-variation in seed plants. \emph{Ecol. Lett.} \textbf{20}, 375--384
-(2017).
-
-\hypertarget{ref-sargent2008}{}
-10. Sargent, R. D. \& Ackerly, D. D. Plant--pollinator interactions and
-the assembly of plant communities. \emph{Trends Ecol. Evol.}
-\textbf{23}, 123--130 (2008).
-
-\hypertarget{ref-rech2016}{}
-11. Rech, A. R. \emph{et al.} The macroecology of animal versus wind
-pollination: Ecological factors are more important than historical
-climate stability. \emph{Plant Ecol. Divers.} \textbf{9}, 253--262
-(2016).
-
-\hypertarget{ref-salguero2016}{}
-12. Salguero-Gómez, R. \emph{et al.} Fast-slow continuum and
-reproductive strategies structure plant life-history variation
-worldwide. \emph{Proc. Natl. Acad. Sci. U.S.A.} \textbf{113}, 230--235
-(2016).
-
-\hypertarget{ref-ruger2018}{}
-13. Rüger, N. \emph{et al.} Beyond the fastSlow continuum: Demographic
-dimensions structuring a tropical tree community. \emph{Ecol. Lett.}
-\textbf{21}, 1075--1084 (2018).
-
-\hypertarget{ref-dehling2016}{}
-14. Dehling, D. M., Jordano, P., Schaefer, H. M., Böhning-Gaese, K. \&
-Schleuning, M. Morphology predicts species' functional roles and their
-degree of specialization in plant--frugivore interactions. \emph{Proc.
-Royal Soc. B} \textbf{283}, 20152444 (2016).
-
-\hypertarget{ref-rosas2014}{}
-15. Rosas-Guerrero, V. \emph{et al.} A quantitative review of
-pollination syndromes: Do floral traits predict effective pollinators?
-\emph{Ecol. Lett.} \textbf{17}, 388--400 (2014).
-
-\hypertarget{ref-stang2009}{}
-16. Stang, M., Klinkhamer, P. G. L., Waser, N. M., Stang, I. \& van der
-Meijden, E. Size-specific interaction patterns and size matching in a
-plantPollinator interaction web. \emph{Ann. Bot.} \textbf{103},
-1459--1469 (2009).
-
-\hypertarget{ref-bartomeus2016}{}
-17. Bartomeus, I. \emph{et al.} A common framework for identifying
-linkage rules across different types of interactions. \emph{Funct.
-Ecol.} \textbf{30}, 1894--1903 (2016).
-
-\hypertarget{ref-waser1996}{}
-18. Waser, N. M., Chittka, L., Price, M. V., Williams, N. M. \&
-Ollerton, J. Generalization in pollination systems, and why it matters.
-\emph{Ecology} \textbf{77}, 1043--1060 (1996).
-
-\hypertarget{ref-olesen2002}{}
-19. Olesen, J. M. \& Jordano, P. Geographic patterns in
-plant--pollinator mutualistic networks. \emph{Ecology} \textbf{83},
-2416--2424 (2002).
-
-\hypertarget{ref-tur2013}{}
-20. Tur, C., Castro-Urgal, R. \& Traveset, A. Linking Plant
-Specialization to Dependence in Interactions for Seed Set in Pollination
-Networks. \emph{PLoS One} \textbf{8}, e78294 (2013).
-
-\hypertarget{ref-devaux2014}{}
-21. Devaux, C., Lepers, C. \& Porcher, E. Constraints imposed by
-pollinator behaviour on the ecology and evolution of plant mating
-systems. \emph{J. Evol. Biol.} \textbf{27}, 1413--1430 (2014).
-
-\hypertarget{ref-kattge2011}{}
-22. Kattge, J. \emph{et al.} TRY a global database of plant traits.
-\emph{Glob. Chang. Biol.} \textbf{17}, 2905--2935 (2011).
-
-\hypertarget{ref-salguero2015}{}
-23. Salguero-Gómez, R. \emph{et al.} The compadre Plant Matrix Database:
-An open online repository for plant demography. \emph{J. Ecol.}
-\textbf{103}, 202--218 (2015).
-
-\hypertarget{ref-diaz2016}{}
-24. Díaz, S. \emph{et al.} The global spectrum of plant form and
-function. \emph{Nature} \textbf{529}, 167--171 (2016).
-
-\hypertarget{ref-carmona2021}{}
-25. Carmona, C. P. \emph{et al.} Erosion of global functional diversity
-across the tree of life. \emph{Sci. Adv.} \textbf{7}, eabf2675 (2021).
-
-\hypertarget{ref-wright2004}{}
-26. Wright, I. J. \emph{et al.} The worldwide leaf economics spectrum.
-\emph{Nature} \textbf{428}, 821--827 (2004).
-
-\hypertarget{ref-chave2009}{}
-27. Chave, J. \emph{et al.} Towards a worldwide wood economics spectrum.
-\emph{Ecol. Lett.} \textbf{12}, 351--366 (2009).
-
-\hypertarget{ref-laughlin2021}{}
-28. Laughlin, D. C. \emph{et al.} Root traits explain plant species
-distributions along climatic gradients yet challenge the nature of
-ecological trade-offs. \emph{Nat. Ecol. Evol.} 1--12 (2021).
-
-\hypertarget{ref-evojtko2020}{}
-29. E-Vojtkó, A., Bello, F. de, Durka, W., Kühn, I. \& Götzenberger, L.
-The neglected importance of floral traits in trait-based plant community
-assembly. \emph{J. Veg. Sci.} \textbf{31}, 529--539 (2020).
-
-\hypertarget{ref-barrett2003}{}
-30. Barrett, S. C. H. Mating strategies in flowering plants: The
-outcrossing-selfing paradigm and beyond. \emph{Philos. Trans. R. Soc.
-Lond. B Biol. Sci.} \textbf{358}, 991--1004 (2003).
-
-\hypertarget{ref-goodwillie2010}{}
-31. Goodwillie, C. \emph{et al.} Correlated evolution of mating system
-and floral display traits in flowering plants and its implications for
-the distribution of mating system variation. \emph{New Phytol.}
-\textbf{185}, 311--321 (2010).
-
-\hypertarget{ref-ollerton2011}{}
-32. Ollerton, J., Winfree, R. \& Tarrant, S. How many flowering plants
-are pollinated by animals? \emph{Oikos} \textbf{120}, 321--326 (2011).
-
-\hypertarget{ref-rodger2021}{}
-33. Rodger, J. G. \emph{et al.} Widespread vulnerability of flowering
-plant seed production to pollinator declines. \emph{Science Advances}
-\textbf{7}, eabd3524 (2021).
-
-\hypertarget{ref-bartomeus2013}{}
-34. Bartomeus, I. Understanding Linkage Rules in Plant-Pollinator
-Networks by Using Hierarchical Models That Incorporate Pollinator
-Detectability and Plant Traits. \emph{PLoS One} \textbf{8}, e69200
-(2013).
-
-\hypertarget{ref-olito2015}{}
-35. Olito, C. \& Fox, J. W. Species traits and abundances predict
-metrics of plantPollinator network structure, but not pairwise
-interactions. \emph{Oikos} \textbf{124}, 428--436 (2015).
-
-\hypertarget{ref-rowe2020}{}
-36. Rowe, L. \emph{et al.} Flower traits associated with the visitation
-patterns of bees. \emph{Oecologia} \textbf{193}, 511--522 (2020).
-
-\hypertarget{ref-lazaro2013}{}
-37. Lázaro, A., Jakobsson, A. \& Totland, Ø. How do pollinator
-visitation rate and seed set relate to species' floral traits and
-community context? \emph{Oecologia} \textbf{173}, 881--893 (2013).
-
-\hypertarget{ref-junker2013}{}
-38. Junker, R. R. \emph{et al.} Specialization on traits as basis for
-the niche-breadth of flower visitors and as structuring mechanism of
-ecological networks. \emph{Funct. Ecol.} \textbf{27}, 329--341 (2013).
-
-\hypertarget{ref-coux2016}{}
-39. Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking
-species functional roles to their network roles. \emph{Ecol. Lett.}
-\textbf{19}, 762--770 (2016).
-
-\hypertarget{ref-ibanez2012}{}
-40. Ibanez, S. Optimizing size thresholds in a plant-pollinator
-interaction web: Towards a mechanistic understanding of ecological
-networks. \emph{Oecologia} \textbf{170}, 233--242 (2012).
-
-\hypertarget{ref-eklof2013}{}
-41. Eklöf, A. \emph{et al.} The dimensionality of ecological networks.
-\emph{Ecol. Lett.} \textbf{16}, 577--583 (2013).
-
-\hypertarget{ref-sargent2007}{}
-42. Sargent, R. D., Goodwillie, C., Kalisz, S. \& Ree, R. H.
-Phylogenetic evidence for a flower size and number trade-off. \emph{Am.
-J. Bot.} \textbf{94}, 2059--2062 (2007).
-
-\hypertarget{ref-kettle2011}{}
-43. Kettle, C. J. \emph{et al.} Ecological Implications of a Flower
-Size/Number Trade-Off in Tropical Forest Trees. \emph{PLoS One}
-\textbf{6}, e16111 (2011).
-
-\hypertarget{ref-healy2019}{}
-44. Healy, K., Ezard, T. H. G., Jones, O. R., Salguero-Gómez, R. \&
-Buckley, Y. M. Animal life history is shaped by the pace of life and the
-distribution of age-specific mortality and reproduction. \emph{Nat.
-Ecol. Evol.} \textbf{3}, 1217--1224 (2019).
-
-\hypertarget{ref-hegland2005}{}
-45. Hegland, S. J. \& Totland, Ø. Relationships between species' floral
-traits and pollinator visitation in a temperate grassland.
-\emph{Oecologia} \textbf{145}, 586--594 (2005).
-
-\hypertarget{ref-kaiser2014}{}
-46. Kaiser-Bunbury, C. N., Vázquez, D. P., Stang, M. \& Ghazoul, J.
-Determinants of the microstructure of plantPollinator networks.
-\emph{Ecology} \textbf{95}, 3314--3324 (2014).
-
-\hypertarget{ref-palmer2003}{}
-47. Palmer, T. M., Stanton, M. L. \& Young, T. P. Competition and
-coexistence: Exploring mechanisms that restrict and maintain diversity
-within mutualist guilds. \emph{Am. Nat.} \textbf{162}, S63--S79 (2003).
-
-\hypertarget{ref-phillips2020}{}
-48. Phillips, R. D., Peakall, R., van der Niet, T. \& Johnson, S. D.
-Niche perspectives on plantPollinator interactions. \emph{Trends Plant
-Sci.} \textbf{25}, 779--793 (2020).
-
-\hypertarget{ref-vazquez2007}{}
-49. Vázquez, D. P. \emph{et al.} Species abundance and asymmetric
-interaction strength in ecological networks. \emph{Oikos} \textbf{116},
-1120--1127 (2007).
-
-\hypertarget{ref-encinas2012}{}
-50. Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives
-mutualistic network structure and diversity. \emph{Ecol. Lett.}
-\textbf{15}, 198--208 (2012).
-
-\hypertarget{ref-gervasi2017}{}
-51. Gervasi, D. D. L. \& Schiestl, F. P. Real-time divergent evolution
-in plants driven by pollinators. \emph{Nat. Commun.} \textbf{8}, 14691
-(2017).
-
-\hypertarget{ref-mackin2021}{}
-52. Mackin, C. R., Peña, J. F., Blanco, M. A., Balfour, N. J. \&
-Castellanos, M. C. Rapid evolution of a floral trait following
-acquisition of novel pollinators. \emph{J. Ecol.} \textbf{109},
-2234--2246 (2021).
-
-\hypertarget{ref-fortuna2010}{}
-53. Fortuna, M. A. \emph{et al.} Nestedness versus modularity in
-ecological networks: Two sides of the same coin? \emph{J. Anim. Ecol.}
-\textbf{79}, 811--817 (2010).
-
-\hypertarget{ref-carvalheiro2014}{}
-54. Carvalheiro, L. G. \emph{et al.} The potential for indirect effects
-between co-flowering plants via shared pollinators depends on resource
-abundance, accessibility and relatedness. \emph{Ecol. Lett.}
-\textbf{17}, 1389--1399 (2014).
-
-\hypertarget{ref-poisot2016}{}
-55. Poisot, T. \emph{et al.} Mangal making ecological network analysis
-simple. \emph{Ecography} \textbf{39}, 384--390 (2016).
-
-\hypertarget{ref-chamberlain2020}{}
-56. Chamberlain, S. \emph{et al.} Taxize: Taxonomic information from
-around the web. r package version 0.9.99 (2020).~at
-\href{https://CRAN.R-project.org/package=taxize}{https://cran.R-project.org/package=taxize}.
-
-\hypertarget{ref-smith2018}{}
-57. Smith, S. A. \& Brown, J. W. Constructing a broadly inclusive seed
-plant phylogeny. \emph{Am. J. Bot.} \textbf{105}, 302--314 (2018).
-
-\hypertarget{ref-jin2019}{}
-58. Jin, Y. \& Qian, H. V.PhyloMaker: An R package that can generate
-very large phylogenies for vascular plants. \emph{Ecography}
-\textbf{42}, 1353--1359 (2019).
-
-\hypertarget{ref-stekhoven2012}{}
-59. Stekhoven, D. J. \& Bühlmann, P. MissForestNon-parametric missing
-value imputation for mixed-type data. \emph{Bioinformatics} \textbf{28},
-112--118 (2012).
-
-\hypertarget{ref-penone2014}{}
-60. Penone, C. \emph{et al.} Imputation of missing data in life-history
-trait datasets: Which approach performs the best? \emph{Methods Ecol.
-Evol.} \textbf{5}, 961--970 (2014).
-
-\hypertarget{ref-santos2018}{}
-61. Chamberlain, S. \emph{et al.} Package `PVR'. r package version 0.3
-(2018).~at
-\href{https://CRAN.R-project.org/package=PVR}{https://cran.R-project.org/package=PVR}.
-
-\hypertarget{ref-diniz-filho2012}{}
-62. Diniz-Filho, J. A. F. \emph{et al.} On the selection of phylogenetic
-eigenvectors for ecological analyses. \emph{Ecography} \textbf{35},
-239--249 (2012).
-
-\hypertarget{ref-legendre2012}{}
-63. Legendre, P. \& Legendre, L. \emph{Numerical ecology}. (Elsevier,
-Amsterdam, 2012).
-
-\hypertarget{ref-revell2012}{}
-64. Revell, L. J. Phytools: An R package for phylogenetic comparative
-biology (and other things). \emph{Methods Ecol. Evol.} \textbf{3},
-217--223 (2012).
-
-\hypertarget{ref-abdi2010}{}
-65. Abdi, H. \& Williams, L. J. Principal component analysis.
-\emph{WIREs Comp. Stats.} \textbf{2}, 433--459 (2010).
-
-\hypertarget{ref-ballantyne2015}{}
-66. Ballantyne, G., Baldock, K. C. R. \& Willmer, P. G. Constructing
-more informative plantPollinator networks: Visitation and pollen
-deposition networks in a heathland plant community. \emph{Proc. Royal
-Soc. B} \textbf{282}, 20151130 (2015).
-
-\hypertarget{ref-vazquez2005}{}
-67. Vázquez, D. P., Morris, W. F. \& Jordano, P. Interaction frequency
-as a surrogate for the total effect of animal mutualists on plants.
-\emph{Ecol. Lett.} \textbf{8}, 1088--1094 (2005).
-
-\hypertarget{ref-vazquez2012}{}
-68. Vázquez, D. P. \emph{et al.} The strength of plantPollinator
-interactions. \emph{Ecology} \textbf{93}, 719--725 (2012).
-
-\hypertarget{ref-hung2018}{}
-69. Hung, K.-L. J., Kingston, J. M., Albrecht, M., Holway, D. A. \&
-Kohn, J. R. The worldwide importance of honey bees as pollinators in
-natural habitats. \emph{Proc. Royal Soc. B} \textbf{285}, 20172140
-(2018).
-
-\hypertarget{ref-burkner2017}{}
-70. Bürkner, P.-C. Brms: An R package for Bayesian multilevel models
-using Stan. \emph{J. Stat. Softw.} \textbf{80}, 1--28 (2017).
-
-\hypertarget{ref-gabry2019}{}
-71. Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A.
-Visualization in Bayesian workflow. \emph{J. R. Stat. Soc. Ser. A Stat.
-Soc.} \textbf{182}, 389--402 (2019).
-
-\hypertarget{ref-dormann2008}{}
-72. Dormann, C. F., Gruber, B. \& Fründ, J. Introducing the bipartite
-package: Analysing ecological networks. \emph{interaction} \textbf{1},
-(2008).
-
-\hypertarget{ref-bluthgen2006}{}
-73. Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in
-species interaction networks. \emph{BMC Ecol.} \textbf{6}, 9 (2006).
-
-\hypertarget{ref-therneau2015}{}
-74. Therneau, T., Atkinson, B., Ripley, B. \& Ripley, M. B. Package
-`rpart'. r package version 4.1-15 (2015).~at
-\href{https://CRAN.R-project.org/package=rpart}{https://cran.R-project.org/package=rpart}.
-
-\hypertarget{ref-milborrow2015}{}
-75. Milborrow, S. Rpart. plot: Plot rpart Models. An Enhanced Version of
-plot. rpart. r package version 3.0.9 (2015).~at
-\href{https://CRAN.R-project.org/package=rpart.plot}{https://cran.R-project.org/package=rpart.plot}.
-
-\section{Acknowledgements}\label{acknowledgements}
-
-We thank all researchers that made their data available for our
-analysis. We thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza
-and David Ragel for their help with data collection. We also thank Jason
-Tylianakis for his comments on the manuscript before submission. JBL
-thanks the University of New England for the funding provided to carry
-out this work.
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-barrett2002}{}}%
+\CSLLeftMargin{1. }
+\CSLRightInline{Barrett, S. C. H. The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.} \textbf{3}, 274--284 (2002).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schiestl2013}{}}%
+\CSLLeftMargin{2. }
+\CSLRightInline{Schiestl, F. P. \& Johnson, S. D. Pollinator-mediated evolution of floral signals. \emph{Trends Ecol. Evol.} \textbf{28}, 307--315 (2013).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fenster2004}{}}%
+\CSLLeftMargin{3. }
+\CSLRightInline{Fenster, C.
+B., Armbruster, W.
+S., Wilson, P., Dudash, M.
+R.
+\& Thomson, J.
+D.
+Pollination {Syndromes} and {Floral Specialization}.
+\emph{Annu.
+Rev.
+Ecol.
+Evol.
+Syst.} \textbf{35}, 375--403 (2004).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dellinger2020}{}}%
+\CSLLeftMargin{4. }
+\CSLRightInline{Dellinger, A. S. Pollination syndromes in the 21st century: Where do we stand and where may we go? \emph{New Phytol.} \textbf{228}, 1193--1213 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-roddy2021}{}}%
+\CSLLeftMargin{5. }
+\CSLRightInline{Roddy, A. B. \emph{et al.} Towards the flower economics spectrum. \emph{New Phytol.} \textbf{229}, 665--672 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-baude2016}{}}%
+\CSLLeftMargin{6. }
+\CSLRightInline{Baude, M. \emph{et al.} Historical nectar assessment reveals the fall and rise of floral resources in britain. \emph{Nature} \textbf{530}, 85--88 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
+\CSLLeftMargin{7. }
+\CSLRightInline{Munoz, F., Violle, C.
+\& Cheptou, P.-O.
+{CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
+\emph{Oikos} \textbf{125}, 1296--1303 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-grossenbacher2017}{}}%
+\CSLLeftMargin{8. }
+\CSLRightInline{Grossenbacher, D. L. \emph{et al.} Self-compatibility is over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
+\CSLLeftMargin{9. }
+\CSLRightInline{Moeller, D. A. \emph{et al.} Global biogeography of mating system variation in seed plants. \emph{Ecol. Lett.} \textbf{20}, 375--384 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
+\CSLLeftMargin{10. }
+\CSLRightInline{Sargent, R. D. \& Ackerly, D. D. Plant--pollinator interactions and the assembly of plant communities. \emph{Trends Ecol. Evol.} \textbf{23}, 123--130 (2008).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rech2016}{}}%
+\CSLLeftMargin{11. }
+\CSLRightInline{Rech, A.
+R.
+\emph{et al.} The macroecology of animal versus wind pollination: Ecological factors are more important than historical climate stability.
+\emph{Plant Ecol.
+Divers.} \textbf{9}, 253--262 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-salguero2016}{}}%
+\CSLLeftMargin{12. }
+\CSLRightInline{Salguero-Gómez, R.
+\emph{et al.} Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
+\emph{Proc.
+Natl.
+Acad.
+Sci.
+U.S.A.} \textbf{113}, 230--235 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
+\CSLLeftMargin{13. }
+\CSLRightInline{Rüger, N. \emph{et al.} Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community. \emph{Ecol. Lett.} \textbf{21}, 1075--1084 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
+\CSLLeftMargin{14. }
+\CSLRightInline{Dehling, D.
+M., Jordano, P., Schaefer, H.
+M., Böhning-Gaese, K.
+\& Schleuning, M.
+Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
+\emph{Proc.
+Royal Soc.
+B} \textbf{283}, 20152444 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
+\CSLLeftMargin{15. }
+\CSLRightInline{Rosas-Guerrero, V. \emph{et al.} A quantitative review of pollination syndromes: Do floral traits predict effective pollinators? \emph{Ecol. Lett.} \textbf{17}, 388--400 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
+\CSLLeftMargin{16. }
+\CSLRightInline{Stang, M., Klinkhamer, P.
+G.
+L., Waser, N.
+M., Stang, I.
+\& van der Meijden, E.
+Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
+\emph{Ann.
+Bot.} \textbf{103}, 1459--1469 (2009).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
+\CSLLeftMargin{17. }
+\CSLRightInline{Bartomeus, I. \emph{et al.} A common framework for identifying linkage rules across different types of interactions. \emph{Funct. Ecol.} \textbf{30}, 1894--1903 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-waser1996}{}}%
+\CSLLeftMargin{18. }
+\CSLRightInline{Waser, N. M., Chittka, L., Price, M. V., Williams, N. M. \& Ollerton, J. Generalization in pollination systems, and why it matters. \emph{Ecology} \textbf{77}, 1043--1060 (1996).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-olesen2002}{}}%
+\CSLLeftMargin{19. }
+\CSLRightInline{Olesen, J. M. \& Jordano, P. Geographic patterns in plant--pollinator mutualistic networks. \emph{Ecology} \textbf{83}, 2416--2424 (2002).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
+\CSLLeftMargin{20. }
+\CSLRightInline{Tur, C., Castro-Urgal, R.
+\& Traveset, A.
+Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}.
+\emph{PLoS One} \textbf{8}, e78294 (2013).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
+\CSLLeftMargin{21. }
+\CSLRightInline{Devaux, C., Lepers, C.
+\& Porcher, E.
+Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems.
+\emph{J.
+Evol.
+Biol.} \textbf{27}, 1413--1430 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
+\CSLLeftMargin{22. }
+\CSLRightInline{Kattge, J. \emph{et al.} {TRY} \textendash{} a global database of plant traits. \emph{Glob. Chang. Biol.} \textbf{17}, 2905--2935 (2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
+\CSLLeftMargin{23. }
+\CSLRightInline{Salguero-Gómez, R. \emph{et al.} The compadre {Plant Matrix Database}: An open online repository for plant demography. \emph{J. Ecol.} \textbf{103}, 202--218 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
+\CSLLeftMargin{24. }
+\CSLRightInline{Díaz, S. \emph{et al.} The global spectrum of plant form and function. \emph{Nature} \textbf{529}, 167--171 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
+\CSLLeftMargin{25. }
+\CSLRightInline{Carmona, C. P. \emph{et al.} Erosion of global functional diversity across the tree of life. \emph{Sci. Adv.} \textbf{7}, eabf2675 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%
+\CSLLeftMargin{26. }
+\CSLRightInline{Wright, I. J. \emph{et al.} The worldwide leaf economics spectrum. \emph{Nature} \textbf{428}, 821--827 (2004).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
+\CSLLeftMargin{27. }
+\CSLRightInline{Chave, J. \emph{et al.} Towards a worldwide wood economics spectrum. \emph{Ecol. Lett.} \textbf{12}, 351--366 (2009).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
+\CSLLeftMargin{28. }
+\CSLRightInline{Laughlin, D.
+C.
+\emph{et al.} Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
+\emph{Nat.
+Ecol.
+Evol.} 1--12 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
+\CSLLeftMargin{29. }
+\CSLRightInline{E-Vojtkó, A., Bello, F.
+de, Durka, W., Kühn, I.
+\& Götzenberger, L.
+The neglected importance of floral traits in trait-based plant community assembly.
+\emph{J.
+Veg.
+Sci.} \textbf{31}, 529--539 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
+\CSLLeftMargin{30. }
+\CSLRightInline{Barrett, S. C. H. Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond. \emph{Philos. Trans. R. Soc. Lond. B Biol. Sci.} \textbf{358}, 991--1004 (2003).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
+\CSLLeftMargin{31. }
+\CSLRightInline{Goodwillie, C.
+\emph{et al.} Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
+\emph{New Phytol.} \textbf{185}, 311--321 (2010).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ollerton2011}{}}%
+\CSLLeftMargin{32. }
+\CSLRightInline{Ollerton, J., Winfree, R. \& Tarrant, S. How many flowering plants are pollinated by animals? \emph{Oikos} \textbf{120}, 321--326 (2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rodger2021}{}}%
+\CSLLeftMargin{33. }
+\CSLRightInline{Rodger, J. G. \emph{et al.} Widespread vulnerability of flowering plant seed production to pollinator declines. \emph{Science Advances} \textbf{7}, eabd3524 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2013}{}}%
+\CSLLeftMargin{34. }
+\CSLRightInline{Bartomeus, I.
+Understanding {Linkage Rules} in {Plant}-{Pollinator Networks} by {Using Hierarchical Models That Incorporate Pollinator Detectability} and {Plant Traits}.
+\emph{PLoS One} \textbf{8}, e69200 (2013).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-olito2015}{}}%
+\CSLLeftMargin{35. }
+\CSLRightInline{Olito, C.
+\& Fox, J.
+W.
+Species traits and abundances predict metrics of plant\textendash pollinator network structure, but not pairwise interactions.
+\emph{Oikos} \textbf{124}, 428--436 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rowe2020}{}}%
+\CSLLeftMargin{36. }
+\CSLRightInline{Rowe, L. \emph{et al.} Flower traits associated with the visitation patterns of bees. \emph{Oecologia} \textbf{193}, 511--522 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
+\CSLLeftMargin{37. }
+\CSLRightInline{Lázaro, A., Jakobsson, A.
+\& Totland, Ø.
+How do pollinator visitation rate and seed set relate to species' floral traits and community context?
+\emph{Oecologia} \textbf{173}, 881--893 (2013).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
+\CSLLeftMargin{38. }
+\CSLRightInline{Junker, R.
+R.
+\emph{et al.} Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
+\emph{Funct.
+Ecol.} \textbf{27}, 329--341 (2013).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
+\CSLLeftMargin{39. }
+\CSLRightInline{Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking species functional roles to their network roles. \emph{Ecol. Lett.} \textbf{19}, 762--770 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
+\CSLLeftMargin{40. }
+\CSLRightInline{Ibanez, S.
+Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks.
+\emph{Oecologia} \textbf{170}, 233--242 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
+\CSLLeftMargin{41. }
+\CSLRightInline{Eklöf, A. \emph{et al.} The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583 (2013).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
+\CSLLeftMargin{42. }
+\CSLRightInline{Sargent, R. D., Goodwillie, C., Kalisz, S. \& Ree, R. H. Phylogenetic evidence for a flower size and number trade-off. \emph{Am. J. Bot.} \textbf{94}, 2059--2062 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
+\CSLLeftMargin{43. }
+\CSLRightInline{Kettle, C. J. \emph{et al.} Ecological {Implications} of a {Flower Size}/{Number Trade}-{Off} in {Tropical Forest Trees}. \emph{PLoS One} \textbf{6}, e16111 (2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
+\CSLLeftMargin{44. }
+\CSLRightInline{Healy, K., Ezard, T.
+H.
+G., Jones, O.
+R., Salguero-Gómez, R.
+\& Buckley, Y.
+M.
+Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
+\emph{Nat.
+Ecol.
+Evol.} \textbf{3}, 1217--1224 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
+\CSLLeftMargin{45. }
+\CSLRightInline{Hegland, S. J. \& Totland, Ø. Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia} \textbf{145}, 586--594 (2005).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
+\CSLLeftMargin{46. }
+\CSLRightInline{Kaiser-Bunbury, C.
+N., Vázquez, D.
+P., Stang, M.
+\& Ghazoul, J.
+Determinants of the microstructure of plant\textendash pollinator networks.
+\emph{Ecology} \textbf{95}, 3314--3324 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-palmer2003}{}}%
+\CSLLeftMargin{47. }
+\CSLRightInline{Palmer, T.
+M., Stanton, M.
+L.
+\& Young, T.
+P.
+Competition and coexistence: Exploring mechanisms that restrict and maintain diversity within mutualist guilds.
+\emph{Am.
+Nat.} \textbf{162}, S63--S79 (2003).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-phillips2020}{}}%
+\CSLLeftMargin{48. }
+\CSLRightInline{Phillips, R. D., Peakall, R., van der Niet, T. \& Johnson, S. D. Niche perspectives on plant\textendash pollinator interactions. \emph{Trends Plant Sci.} \textbf{25}, 779--793 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
+\CSLLeftMargin{49. }
+\CSLRightInline{Vázquez, D. P. \emph{et al.} Species abundance and asymmetric interaction strength in ecological networks. \emph{Oikos} \textbf{116}, 1120--1127 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
+\CSLLeftMargin{50. }
+\CSLRightInline{Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.} \textbf{15}, 198--208 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gervasi2017}{}}%
+\CSLLeftMargin{51. }
+\CSLRightInline{Gervasi, D. D. L. \& Schiestl, F. P. Real-time divergent evolution in plants driven by pollinators. \emph{Nat. Commun.} \textbf{8}, 14691 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mackin2021}{}}%
+\CSLLeftMargin{52. }
+\CSLRightInline{Mackin, C.
+R., Peña, J.
+F., Blanco, M.
+A., Balfour, N.
+J.
+\& Castellanos, M.
+C.
+Rapid evolution of a floral trait following acquisition of novel pollinators.
+\emph{J.
+Ecol.} \textbf{109}, 2234--2246 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
+\CSLLeftMargin{53. }
+\CSLRightInline{Fortuna, M. A. \emph{et al.} Nestedness versus modularity in ecological networks: Two sides of the same coin? \emph{J. Anim. Ecol.} \textbf{79}, 811--817 (2010).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
+\CSLLeftMargin{54. }
+\CSLRightInline{Carvalheiro, L.
+G.
+\emph{et al.} The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
+\emph{Ecol.
+Lett.} \textbf{17}, 1389--1399 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
+\CSLLeftMargin{55. }
+\CSLRightInline{Poisot, T. \emph{et al.} Mangal \textendash{} making ecological network analysis simple. \emph{Ecography} \textbf{39}, 384--390 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
+\CSLLeftMargin{56. }
+\CSLRightInline{Chamberlain, S.
+\emph{et al.} Taxize: {Taxonomic} information from around the web.
+R package version 0.9.99 (2020).~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
+\CSLLeftMargin{57. }
+\CSLRightInline{Smith, S. A. \& Brown, J. W. Constructing a broadly inclusive seed plant phylogeny. \emph{Am. J. Bot.} \textbf{105}, 302--314 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
+\CSLLeftMargin{58. }
+\CSLRightInline{Jin, Y. \& Qian, H. V.{PhyloMaker}: An {R} package that can generate very large phylogenies for vascular plants. \emph{Ecography} \textbf{42}, 1353--1359 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
+\CSLLeftMargin{59. }
+\CSLRightInline{Stekhoven, D. J. \& Bühlmann, P. {MissForest}\textemdash non-parametric missing value imputation for mixed-type data. \emph{Bioinformatics} \textbf{28}, 112--118 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
+\CSLLeftMargin{60. }
+\CSLRightInline{Penone, C. \emph{et al.} Imputation of missing data in life-history trait datasets: Which approach performs the best? \emph{Methods Ecol. Evol.} \textbf{5}, 961--970 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
+\CSLLeftMargin{61. }
+\CSLRightInline{Chamberlain, S. \emph{et al.} Package {``{PVR}''}. R package version 0.3 (2018).~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
+\CSLLeftMargin{62. }
+\CSLRightInline{Diniz-Filho, J. A. F. \emph{et al.} On the selection of phylogenetic eigenvectors for ecological analyses. \emph{Ecography} \textbf{35}, 239--249 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
+\CSLLeftMargin{63. }
+\CSLRightInline{Legendre, P. \& Legendre, L. \emph{Numerical ecology}. ({Elsevier, Amsterdam}, 2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
+\CSLLeftMargin{64. }
+\CSLRightInline{Revell, L. J. Phytools: An {R} package for phylogenetic comparative biology (and other things). \emph{Methods Ecol. Evol.} \textbf{3}, 217--223 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
+\CSLLeftMargin{65. }
+\CSLRightInline{Abdi, H. \& Williams, L. J. Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459 (2010).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
+\CSLLeftMargin{66. }
+\CSLRightInline{Ballantyne, G., Baldock, K.
+C.
+R.
+\& Willmer, P.
+G.
+Constructing more informative plant\textendash pollinator networks: Visitation and pollen deposition networks in a heathland plant community.
+\emph{Proc.
+Royal Soc.
+B} \textbf{282}, 20151130 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
+\CSLLeftMargin{67. }
+\CSLRightInline{Vázquez, D.
+P., Morris, W.
+F.
+\& Jordano, P.
+Interaction frequency as a surrogate for the total effect of animal mutualists on plants.
+\emph{Ecol.
+Lett.} \textbf{8}, 1088--1094 (2005).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
+\CSLLeftMargin{68. }
+\CSLRightInline{Vázquez, D. P. \emph{et al.} The strength of plant\textendash pollinator interactions. \emph{Ecology} \textbf{93}, 719--725 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
+\CSLLeftMargin{69. }
+\CSLRightInline{Hung, K.-L.
+J., Kingston, J.
+M., Albrecht, M., Holway, D.
+A.
+\& Kohn, J.
+R.
+The worldwide importance of honey bees as pollinators in natural habitats.
+\emph{Proc.
+Royal Soc.
+B} \textbf{285}, 20172140 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
+\CSLLeftMargin{70. }
+\CSLRightInline{Bürkner, P.-C. Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.} \textbf{80}, 1--28 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
+\CSLLeftMargin{71. }
+\CSLRightInline{Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A. Visualization in {Bayesian} workflow. \emph{J. R. Stat. Soc. Ser. A Stat. Soc.} \textbf{182}, 389--402 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
+\CSLLeftMargin{72. }
+\CSLRightInline{Dormann, C. F., Gruber, B. \& Fründ, J. Introducing the bipartite package: Analysing ecological networks. \emph{R News} \textbf{8/2}, (2008).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
+\CSLLeftMargin{73. }
+\CSLRightInline{Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in species interaction networks. \emph{BMC Ecol.} \textbf{6}, 9 (2006).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-therneau2015}{}}%
+\CSLLeftMargin{74. }
+\CSLRightInline{Therneau, T., Atkinson, B., Ripley, B.
+\& Ripley, M.
+B.
+Package {``rpart''}.
+R package version 4.1-15 (2015).~At \href{https://CRAN.R-project.org/package=rpart}{https://CRAN.r-project.org/package=rpart}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-milborrow2015}{}}%
+\CSLLeftMargin{75. }
+\CSLRightInline{Milborrow, S.
+Rpart.
+Plot: {Plot} rpart {Models}.
+{An Enhanced Version} of plot.
+Rpart.
+R package version 3.0.9 (2015).~At \href{https://CRAN.R-project.org/package=rpart.plot}{https://CRAN.r-project.org/package=rpart.plot}.}
+
+\end{CSLReferences}
+
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+We thank all researchers that made their data available for our analysis.
+We thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
+We also thank Jason Tylianakis for his comments on the manuscript before submission.
+JBL thanks the University of New England for the funding provided to carry out this work.
 

### 2021-11-20 Manuscript/MS_word.Rmd
graphical abstract plots

--- 2021-10-19 Manuscript/Manuscript.Rmd
@@
 ---
-title: \singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors
-
-#author: 
-#  - Jose B. Lanuza^1,2^*
-#  - Romina Rader^1^
-#  - Jamie Stavert^3^
-#  - Liam K. Kendall^4^
-#  - Manu E. Saunders^1^
-#  - Ignasi Bartomeus^2^
-
-# may use lua filters for affiliations etc: see https://stackoverflow.com/a/52919256
-
-# date: '`r Sys.Date()`'
-
-output:
-  bookdown::pdf_document2:
-    fig_caption: yes
-    fig_width: 7
-    fig_height: 7
-    df_print: kable
-    keep_tex: yes
-    number_sections: no
-    extra_dependencies: ["float"]
-    toc: no
-    fig_crop: no
-    includes:
-      in_header: header.tex
-
+title: "Untitled"
+output: word_document
 documentclass: article
@@
 fontsize: 12pt
+always_allow_html: true
 
@@
 - \usepackage{pdflscape}
+---
+---
+title: \singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors
+
+#author: 
+#  - Jose B. Lanuza^1,2^*
+#  - Romina Rader^1^
+#  - Jamie Stavert^3^
+#  - Liam K. Kendall^4^
+#  - Manu E. Saunders^1^
+#  - Ignasi Bartomeus^2^
+
+# may use lua filters for affiliations etc: see https://stackoverflow.com/a/52919256
+
+# date: '`r Sys.Date()`'
+
+output:
+  word_document: default
+  bookdown::word_document2: default  # for cross-references
+    fig_caption: yes
+    fig_width: 7
+    fig_height: 7
+    df_print: kable
+    keep_tex: yes
+    number_sections: no
+    extra_dependencies: ["float"]
+    toc: no
+    fig_crop: no
+    includes:
+      in_header: header.tex
+
+documentclass: article
+# classoption: twocolumn, landscape, etc
+papersize: a4
+pagestyle: plain  # plain, empty, headings
+geometry: margin=1in
+linestretch: 2
+fontfamily: mathpazo
+fontsize: 12pt
+
+bibliography: 
+  - references.bib
+  - knitcitations.bib
+# zotero: "My shared Zotero group"
+csl: ecology.csl
+# csl: https://www.zotero.org/styles/ecology
+
+link-citations: yes
+linkcolor: RoyalBlue
+urlcolor: RoyalBlue
+links-as-notes: false
+subparagraph: yes
+
+header-includes:
+- \usepackage{booktabs}
+- \usepackage{longtable}
+- \usepackage{array}
+- \usepackage{multirow}
+- \usepackage{wrapfig}
+- \usepackage{float}
+- \usepackage{colortbl}
+- \usepackage{tabu}
+- \usepackage{threeparttable}
+- \usepackage{threeparttablex}
+- \usepackage[normalem]{ulem}
+- \usepackage{makecell}
+- \usepackage{xcolor}
+- \usepackage{float}
+- \floatplacement{figure}{H}
+- \usepackage[skip=3pt]{caption}
+- \captionsetup[figure]{labelformat=empty}
+- \usepackage{setspace}
+- \usepackage{titlesec}
+- \titlespacing{\title}{0pt}{\parskip}{-\parskip}
+- \usepackage[style=nature]{biblatex}
+- \usepackage[labelformat = empty]{caption}
+- \usepackage{pdflscape}
 
@@
 __Plant life strategies are constrained by cost-benefit trade-offs that determine plant form and function.
-However, despite recent advances in the understanding of trade-offs for vegetative and physiological traits, little is known about plant reproductive economics and how they constrain plant life strategies and shape interactions with floral visitors.
-Here, we investigate plant reproductive trade-offs and how these reproductive compromises drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species from 28 plant-pollinator studies across 18 countries.
-We tested whether a plant’s reproductive strategy predicts its interactions with floral visitors and if the different reproductive traits predict the plant’s role within the pollination network.
-We found that over half of all plant reproductive trait variation was explained by two independent axes that encompassed plant form and function.
-Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
-Plant reproductive trade-offs somewhat explained the presence or absence of interactions with floral visitors, but not differences in visitation rate.
-However, we did find important differences in the interaction level among floral visitor guilds on the different axes of trait variation.
-Finally, we found that plant size and floral rewards were the most important traits in the understanding of the species network role.
-Our results highlight the importance of plant reproductive trade-offs in determining plant life strategies and plant-pollinator interactions in a global context.__
+Despite the recent advances in the understanding of plant trade-offs with vegetative and physiological traits, little is known about the plant reproductive economics and how they constrain plant life strategies and shape interactions with floral visitors.
+Here, we investigated plant reproductive trade-offs and their association with floral visitors with a dataset of 1506 plant species with 17 reproductive and 3 vegetative traits from 28 plant-pollinator network studies across 18 countries.
+Then, we tested whether a species reproductive strategy predicted plant-pollinator interactions (presence-absence and visitation rate) and if the interaction strategy (its role in a pollination network) was predicted by individual traits.
+We found that 51.8% of trait variation was explained by two independent axes that encompassed plant form and function.
+Specifically, the first axis indicated the presence of a trade-off between flower number and flower size (PC1, 26.72%) and the second axis indicated a trade-off for the level of pollinator dependency (PC2, 25.08%).
+The reproductive trade-offs explained some of the qualitative interaction with pollinators (presence-absence) but none of the variability of visitation rates.
+However, noteworthy differences across pollinator guilds were found in both cases.
+Finally, we found that specific traits with special relevance of floral rewards were key in the understanding of the species network role.
+Our results highlight the need to consider plant reproductive trade-offs to improve our understanding of plant life strategies and plant-pollinator interactions at broader spatial scales.__
 
@@
 
-Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that explores plant reproductive compromises is currently lacking [@roddy2021].
-In addition, macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
+Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their relevance to understand plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that explores plant reproductive compromises is currently lacking [@roddy2021].
+In addition, macroecological studies regarding specific reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and as a consequence studies that link reproductive traits to plant-pollinator interactions at large scales are poorly explored [@sargent2008; @rech2016; @salguero2016; @ruger2018].
 Linking the position in the trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
-Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
-However, reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020] despite the apparent generalist nature of plant-pollinator interactions [@waser1996; @olesen2002].
-In addition, it is unclear how specific plant reproductive biology traits influence plant-pollinator interactions [@tur2013; @devaux2014].
-
-Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY [@kattge2011] and COMPADRE [@salguero2015]), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; bruelheide2018; @carmona2021].
-However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively [@barrett2003; @moeller2017] and outcrossing levels are positively correlated with flower size [@goodwillie2010].
-In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators [@ollerton2011; @rodger2021].
-However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.
+At the same time, there is increasing interest in the understanding of the determinants of plant-pollinator interactions via trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
+However, reproductive traits have been overlooked beyond highly specialised systems [@dellinger2020] despite the apparent generalist nature of plant-pollinator interactions [@waser1996; @olesen2002].
+In addition, it is yet unclear how the different reproductive biology traits influence plant-pollinator associations [@tur2013; @devaux2014].
+
+Species can optimize their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can employ.
+With the recent availability of large trait databases (e.g., TRY [@kattge2011] and COMPADRE [@salguero2015]), plant ecological strategies are increasingly being examined, and are facilitating the identification of global patterns and constraints of plant form and function [@salguero2016; @diaz2016; bruelheide2018; @carmona2021].
+However, the main focus has been on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits
+[@evojtko2020; @roddy2021], also critical to plant life strategies that shape plant interactions with pollinators and ultimately impact plant reproductive success.
+For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively [@barrett2003; @moeller2017].
+Further, outcrossing levels are positively correlated with flower size [@goodwillie2010].
+In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and their role in attracting pollinators [@ollerton2011].
+However, it is still unknown to what extent these different  reproductive compromises determine plant-pollinator associations.
 
 Several studies have identified links between plant traits and plant-pollinator network properties [@bartomeus2013; @olito2015; @rowe2020].
-Moreover, plant traits can define species’ network roles (e.g., specialists vs generalists) [@lazaro2013; @tur2013].
-For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
-Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
+Moreover, plant traits can also define species' network roles [@lazaro2013; @tur2013] (e.g., specialists vs generalists).
+For example, species that occupy trait space extremes are more likely to exhibit higher specialization and be more reliant on trait-matching [@junker2013; @coux2016].
+This morphological matching between plant and floral visitors can determine plant-pollinator interactions, and thus shape their interaction network structure [@stang2009; @ibanez2012].
 Remarkably, the combination of traits have shown to increase the predictive power of the network interactions [@eklof2013].
@@
 
-Here, we aim to explore the potential trade-offs among reproductive traits and how these influence plant-pollinator interactions.
+Here, we explore the potential trade-offs among plant floral and reproductive biology traits and how these influence plant-pollinator interactions.
 First, we identify the major axes of reproductive trait variation and trade-offs that determine plant form and function.
-Second, we investigate how plant species’ position in trait-space interactions with floral visitors.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species’ roles within networks using a set of complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
+Second, we investigate how plant species’ position in trait-space influences plant-pollinator interactions (presence-absence and visitation rate).
+Finally, we investigate how the main axes of trait variation and individual traits influence plant species roles within networks using complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
 
@@
 
-Here, we show that plant species exhibit clear trade-offs among their vegetative and reproductive traits that determined different interaction levels with floral visitor guilds.
+Here, we show that plant species exhibit clear trade-offs in their floral, reproductive biology and vegetative traits.
 These trade-offs are differentiated on three main axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-These reproductive trade-offs somewhat explained the presence or absence of interactions with floral visitors, but not differences in visitation rate.
-However, on both qualitative and quantitative interactions we found marked associations of floral visitor guilds with the main axes of trait variation.
-Further, we found that plant height and floral reward related traits were best at characterising plant species functional roles within pollination networks.
-
-Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
-Trait variation on these two axes was associated with the ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-The ‘slow’ part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, plant species that employed the ‘fast’ strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
-The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Supplementary Fig.
+These axes of trait variation explained partly the presence-absence interactions between plants and floral visitors but did not explain the overall visitation rates.
+However, on both qualitative and quantitative interactions floral visitor guilds showed associations with the different reproductive trade-offs.
+Interestingly, pollen and nectar related traits were better than all other traits for characterizing plant species functional roles within their interaction networks.
+
+Over 50% of plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
+Variation in these two axes of trait variation appears to be associated with the commonly described ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life-history strategies as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+The ‘slow’ part of the continuum (i.e., tall trees and shrubs) had plant species with many flowers, few ovules, higher pollinator dependence, greater occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
+In contrast, species that employed the ‘fast’ strategy (i.e., short herbs), had fewer flowers, more ovules, greater occurrence of self compatibility and lower pollinator dependence.
+Further, on the first two axes of trait variation, we found additional support for the positive association already described in a previous study between outcrossing rate and floral display [@goodwillie2010].
+This trend was further confirmed when looking at the specific correlation between floral display and autonomous selfing for our dataset (see Supplementary Fig.
 S10).
 
-Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (presence-absence of interactions and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies strongly influence plant-pollinator interactions.
-For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
+Despite the low predictive power of the main axes of trait variation on overall interaction patterns (presence-absence and visitation rate), we found commonalities among and within floral visitors guilds across these axes that indicate the influence of life-history strategies on plant-pollinator interactions.
+For example, all guilds showed an increasing trend of visitation on plant species with higher pollinator dependence, which were also associated with larger floral displays and greater pollen quantities (Fig.
 1 and Supplementary Fig.
 S6).
-This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently [@hegland2005; @lazaro2013; @kaiser2014].
-In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation rates across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
-For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
-3) suggesting possible niche partitioning [@palmer2003; @phillips2020] between these two guilds.
-However, despite floral rewards, related traits were among the best at characterising species functional roles (Fig.
-4), yet the association between reproductive trade-offs and floral visitors did not account for floral rewards because there was insufficient data available.
-More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive trade-offs do not.
-
-To conclude, we provide the first description of plant reproductive trade-offs using a large global dataset of plant traits.
-We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
-Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits [@diaz2016; @carmona2021] it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits [@salguero2016].
-Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
+This trend is consistent with previous plant-pollinator studies that show higher visitation rates on species that make greater reproductive investment [@hegland2005; @lazaro2013; @kaiser2014].
+In regard to the flower number - flower size and style length trade-offs, different guilds showed contrasting visitation rates, which could be associated with different pollination syndromes at a macroecological scale.
+For instance, the guilds of bees and syrphids were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
+3) indicating a possible niche partitioning among these two guilds [@palmer2003; @phillips2020].
+However, these plant-pollinator associations do not account for some of the traits (i.e., pollen and nectar quantity) that had greater relevance on the species network roles (Fig.
+4) because of insufficient data availability and lack of pollinator efficiency measurements for more complete descriptions of the pollination syndromes [@dellinger2020].
+In any case, it is worth noting that this general pattern emerges in field-measured plant-pollinator networks, where other local factors such as species relative abundances, will surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016].
+
+To conclude, we provide the first description of plant floral and reproductive biology trade-offs using a large global dataset of plant traits and interactions with floral visitors.
+This allowed us to identify the major reproductive strategies of flowering plants and how plant life strategies determine their interaction with floral visitor guilds.
+Although the percentage of explained variation found with the first two axes (~50%) is lower than other studies that have evaluated life histories with vegetative traits [@diaz2016; @carmona2021], this percentage is consistent with the largest and most recent study that has characterized life strategies with both vegetative and reproductive (i.e., semelparity and iteroparity) traits [@salguero2016].
+Future work needs to integrate these floral and reproductive compromises with the already described vegetative and physiological trade-offs [@diaz2016] to create a more comprehensive spectrum of trait variation [@roddy2021].
 Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators [@gervasi2017; @mackin2021].
-Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
+Finally, a more complete description of the macroecological patterns of plant-pollinator interactions including unrepresented areas of the world [@poisot2021] and traits that have been largely ignored (e.g., floral rewards and plant mating system) are needed to progress in our understanding of the global patterns in plant-pollinator interactions.
 

### 2021-11-20 OLD/World_Map_Sampling_Location.Rmd
graphical abstract plots

---
title: ""
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE}
#WORLDPLOT WITH LIFE FORM

#Load Libraries
library(readxl)
library(ggplot2)
library(dbplyr)
library(scatterpie)
library(reshape2)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)

# READ LONG FORMAT DATA 
world <- ne_countries(scale = "medium", returnclass = "sf")

# READ LONG FORMAT DATA

Long_format_metawebs <- readRDS("Long_format_metawebs.RData")

#SUBSET UNIQUE CASES PER NETWORK
Long_format_subset <-  unique(Long_format_metawebs[,c("Plant_species","Id")])
#It seems to work fine
#and the total number of species makes sense, a bit more than the total unique cases for all the networks

#READ TRAIT DATA IN ORDER TO MERGE
data <- read.csv("../Data/Data_processing/Pollinator_species_names/all.csv", stringsAsFactors = F)
data <- data[,c(1,4,6,7,8,51,27)]
levels(as.factor(data$Breeding_system))
#Filter data for columns of interest
data_filtered <- subset(data, Info_level=="flower"|Info_level=="capitulum"|Info_level=="inflorescence"|Info_level=="NA")
#Rename column to merge
colnames(data_filtered)[1] <- "Plant_species"
#Convert to factor 
data_filtered <- as.data.frame(data_filtered, stringsAsFactors = TRUE)

#Merge the two dataframes (trait data and the unique cases per network)
all_species_per_network <- merge(Long_format_subset, data_filtered,  by=c("Plant_species","Id"), all = T )

#Group breeding system per metaweb or web
all_summary_life_form <- dcast(all_species_per_network,Id~life_form,value.var = "life_form")
#Cleaning NA and one unfinished network
all_summary_life_form <- all_summary_life_form[-c(6,30),-c(6)]
#Removing ".csv" from the Id to megere with coordinates
all_summary_life_form$Id <- gsub("\\..*","",all_summary_life_form$Id)

#Now merge with metadata to add coordinates to plot it
metadata <- read.csv("../Data/Data_processing/Metadata/metadata.csv", stringsAsFactors = F)
str(metadata)
metadata_sub <- metadata[,c(1:6,11)]
metadata_sub <- metadata_sub[ , -c(1)]
metadata_sub <- metadata_sub[order(metadata_sub$Id_number),] 
#Fix some coordinates manually, this locations have more than one
#fore representation purposes I will use just one
metadata_sub[6,3] <- "1.575532"
metadata_sub[6,4] <- "52.762395"
metadata_sub[7,3] <- "9.1"
metadata_sub[7,4] <- "56.1"
metadata_sub[29,3] <- "-6.16895"
metadata_sub[29,4] <- "37.234966"
metadata_sub <- metadata_sub[-14,]
colnames(metadata_sub)[1] <- "Id"

str(metadata_sub)

metadata_sub$longitude <- as.numeric(metadata_sub$longitude)
metadata_sub$latitude <- as.numeric(metadata_sub$latitude)

ggplot(data = world) + 
  geom_sf(color = "#E0E0E0", fill = "#EEEEEE", size=0.1,lwd = 0)+
  theme(axis.line = element_line(color='aliceblue'),
        plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())+
  geom_point(data=metadata_sub, aes(longitude,latitude), shape = 16, colour = "#74c365",size = 2.35, alpha=0.9)+
  theme(panel.grid.major = element_line(color = gray(.5), 
  linetype = "dashed", size = 0), panel.background = element_rect(fill = "aliceblue"))+
  xlab("")+ylab("")+
  coord_sf(expand = FALSE)+
  theme(axis.text.x=element_blank(), #remove x axis labels
        axis.ticks.x=element_blank(), #remove x axis ticks
        axis.text.y=element_blank(),  #remove y axis labels
        axis.ticks.y=element_blank(),
        panel.border = element_blank()
  )

```

### 2021-11-20 OLD/trial.R

@@ -1,0 +1,102 @@
+
+#Load Libraries
+library(readxl)
+library(ggplot2)
+library(dbplyr)
+library(scatterpie)
+library(reshape2)
+library(sf)
+library(rnaturalearth)
+library(rnaturalearthdata)
+# READ LONG FORMAT DATA 
+world <- ne_countries(returnclass = "sf")
+
+Long_format_metawebs <- readRDS("OLD/Long_format_metawebs.RData")
+
+#SUBSET UNIQUE CASES PER NETWORK
+Long_format_subset <-  unique(Long_format_metawebs[,c("Plant_species","Id")])
+#It seems to work fine
+#and the total number of species makes sense, a bit more than the total unique cases for all the networks
+
+
+#READ TRAIT DATA IN ORDER TO MERGE
+data <- read.csv("Data/Data_processing/Pollinator_species_names/all.csv", stringsAsFactors = F)
+data <- data[,c(1,4,6,7,8,51,27)]
+levels(as.factor(data$Breeding_system))
+#Filter data for columns of interest
+data_filtered <- subset(data, Info_level=="flower"|Info_level=="capitulum"|Info_level=="inflorescence"|Info_level=="NA")
+#Rename column to merge
+colnames(data_filtered)[1] <- "Plant_species"
+#Convert to factor 
+data_filtered <- as.data.frame(data_filtered, stringsAsFactors = TRUE)
+
+#Merge the two dataframes (trait data and the unique cases per network)
+all_species_per_network <- merge(Long_format_subset, data_filtered,  by=c("Plant_species","Id"), all = T )
+
+#Group breeding system per metaweb or web
+all_summary_life_form <- dcast(all_species_per_network,Id~life_form,value.var = "life_form")
+#Cleaning NA and one unfinished network
+all_summary_life_form <- all_summary_life_form[-c(6,30),-c(6)]
+#Removing ".csv" from the Id to megere with coordinates
+all_summary_life_form$Id <- gsub("\\..*","",all_summary_life_form$Id)
+
+#Now merge with metadata to add coordinates to plot it
+metadata <- read.csv("Data/Data_processing/Metadata/metadata.csv", stringsAsFactors = F)
+str(metadata)
+metadata_sub <- metadata[,c(1:6,11)]
+metadata_sub <- metadata_sub[ , -c(1)]
+metadata_sub <- metadata_sub[order(metadata_sub$Id_number),] 
[…]

### 2021-11-26 Manuscript/Manuscript.Rmd
wording edit

@@
 
-\vspace{-2.2cm}
+\vspace{-1.8cm}
 \singlespacing
@@
 Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
-Plant reproductive trade-offs somewhat explained the presence or absence of interactions with floral visitors, but not differences in visitation rate.
+Plant reproductive trade-offs helped explain partly the presence or absence of interactions with floral visitors, but not differences in visitation rate.
 However, we did find important differences in the interaction level among floral visitor guilds on the different axes of trait variation.
@@
 These trade-offs are differentiated along three axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-These reproductive trade-offs helped explain the presence of floral visitor interactions, but not their visitation rates.
-Floral visitor guilds formed distinct relationships with the main axes of trait variation.
+These reproductive trade-offs helped explain partly the presence of floral visitor interactions, but not their visitation rates.
+However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
 Moreover, we found that the plant species functional roles within pollination networks were best explained by plant size and floral reward related traits.

### 2021-11-26 Manuscript/Manuscript.tex
wording edit

@@
 \setstretch{2}
-\vspace{-2.2cm}
+\vspace{-1.8cm}
 \singlespacing
@@
 First, we identify the major axes of reproductive trait variation and trade-offs that determine plant form and function.
-Second, we investigate how plant species' position in trait-space interactions with floral visitors.
+Second, we investigate how plant species' position in trait-space influence interactions with floral visitors.
 Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' roles within networks using a set of complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).

### 2021-11-26 Main_Figures/Graphical_abstract_trait_spectra.Rmd

--- 2021-11-18 Main_Figures/Graphical abstract plot.Rmd
@@
 
-    plot <- plot + geom_point(data=dat, aes(x, y),size=2.5, color="azure4")
+    plot <- plot + geom_point(data=dat, aes(x, y),size=3, color="grey69")
 
@@
   # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=5.5, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=5.5, arrow=arrow(length=unit(0.5,"cm")), alpha=0.5, colour=c("#74c365"))
 
@@
           panel.background=element_blank(),panel.grid.major=element_blank(),
-          panel.grid.minor=element_blank(),plot.background=element_blank())
+          panel.grid.minor=element_blank(),plot.background=element_blank(), panel.border = element_blank()
+)
 

### 2021-12-02 Main_Figures/Figure3.Rmd
edits before submission

@@
 aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
-  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 
@@
 aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
-  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 
@@
   theme_ms() + theme(legend.position = "none") + 
-  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 #Plot nicely PC1
@@
   theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
-  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+
+  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+    "Non-syrphid-Diptera", "Syrphids"))+
   scale_y_log10()+ggtitle("(d)")
@@
   scale_color_manual(name="Functional groups",values=c("orange", "black", 
-  "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10()+ggtitle("(e)")
+  "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+    "Non-syrphid-Diptera", "Syrphids")) + scale_y_log10()+ggtitle("(e)")
 
@@
   scale_color_manual(name="Functional groups",values=c("orange", 
-  "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ scale_y_log10()+ggtitle("(f)")
+  "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+    "Non-syrphid-Diptera", "Syrphids"))+ scale_y_log10()+ggtitle("(f)")
 

### 2021-12-02 Manuscript/Manuscript.Rmd
edits before submission

@@
 ---
-title: \singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors
+title: \singlespacing \vspace{-1.6cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors
 
@@
 
-\vspace{-1.8cm}
+\vspace{-1.7cm}
 \singlespacing
@@
 
+\vspace{0.3cm}
+
 \normalsize
@@
 However, despite recent advances in the understanding of trade-offs for vegetative and physiological traits, little is known about plant reproductive economics and how they constrain plant life strategies and shape interactions with floral visitors.
-Here, we investigate plant reproductive trade-offs and how these reproductive compromises drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species from 28 plant-pollinator studies across 18 countries.
+Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species from 28 plant-pollinator studies across 18 countries.
 We tested whether a plant’s reproductive strategy predicts its interactions with floral visitors and if the different reproductive traits predict the plant’s role within the pollination network.
@@
 Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY @kattge2011 and COMPADRE @salguero2015), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; bruelheide2018; @carmona2021].
+With the recent availability of large trait databases (e.g., TRY @kattge2011 and COMPADRE @salguero2015), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
 However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
@@
 **Phylogenetic signal of traits.** We found a strong phylogenetic signal (*P* < 0.01) in all quantitative traits (Supplementary Table S5).
-The traits that showed the highest phylogenetic signal were ovule number ($\lambda = 1$), pollen grains per flower ($\lambda = 1$) and plant height ($\lambda = 0.96$), followed by flower length ($\lambda = 0.75$), flower width ($\lambda = 0.73$), number of flowers per plant ($\lambda = 0.69$) and nectar concentration ($\lambda = 0.65$).
-The traits that showed a moderate phylogenetic signal were inflorescence width ($\lambda = 0.57$), style length ($\lambda = 0.49$) and autonomous selfing ($\lambda = 0.34$).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits ($\lambda = 0.14$).
-
-**Visitation patterns.** The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors ($conditional R2 = 0.26$; $marginal R2 = 0.20$) but little of the overall visitation rates ($conditional R2 = 0.31$; $marginal R2 = 0.06$).
+The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
+The traits that showed a moderate phylogenetic signal were inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
+Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits ($\lambda$ = 0.14).
+
+**Visitation patterns.** The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall visitation rates (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
 However, we found relevant trends across the different floral visitor guilds on both presence-absence and visitation interactions (Fig.
@@
 3e).
-For presence-absence interactions we found that all Diptera, Coleoptera and non-bee Hymenoptera guilds interacted more frequently with plants with high flower number and small flowers (flower number - flower size trade-off, PC1; Fig.
+For presence-absence interactions we found that all Diptera, Coleoptera and non-bee-Hymenoptera guilds interacted more frequently with plants with high flower number and small flowers (flower number - flower size trade-off, PC1; Fig.
 3a) but bees and Lepidoptera interacted slightly more frequently with plant species with low flower number but large flowers.
@@
 3c), we found that bees interacted clearly more with plant species with long styles and high selfing and the rest of the guilds interacted slightly more with plant species with short styles and low selfing.
-In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig.
+In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-syrphid-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig.
 3d).
-On the style length trade-off, bees, Lepidoptera and Non-Anthophila-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
+On the style length trade-off, bees, Lepidoptera and non-bee-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while syrphids, non-syrphid-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
 3f).
 
-The additional model for both presence-absence of interactions ($marginal R2 = 0.29$; $conditional R2 = 0.19$) and visitation rate ($marginal R2 = 0.30$; $conditional R2 = 0.03$) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns and that the contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
+The additional model for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and visitation rate (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns and that the contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
 3a and Fig.
-3d) were driven by the family Andrenidae which interacted more frequently on presence-absence interactions with plant species with low number of flower but large (Supplementary Fig.
+3d) were driven by the family Andrenidae which interacted more frequently on presence-absence interactions with plant species with low number of flowers but large (Supplementary Fig.
 S8).
@@
 **Plant species functional roles.** The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
-S9; interaction frequency ~ PCs, $conditional R2 = 0.11$, $marginal R2 = 0.02$; normalized degree ~ PCs, $conditional R2 = 0.24$, $marginal R2 = 0.02$; and, specialization ~ PCs, $conditional R2 = 0.37$, $marginal R2 = 0.03$).
+S9; interaction frequency ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
 Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
@@
 4a).
-Specifically, species taller than 3.9 m had the highest interaction frequency, while species that were shorter than 3.9 m and had a nectar concentration lower than 16% had the lowest interaction frequency.
+Specifically, species taller than 3.9m had the highest interaction frequency, while species that were shorter than 3.9m and had a nectar concentration lower than 16% had the lowest interaction frequency.
 Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
 4b).
-Species with a nectar concentration over 49% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49%, more than 21,000 pollen grains per flower and height less than 0.78 m had the lowest normalized degree.
+Species with a nectar concentration over 49% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49%, more than 21,000 pollen grains per flower and height less than 0.78m had the lowest normalized degree.
 Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
 4c).
-Overall, plant species with the highest specialization were shorter than 1.3 m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11% of their fruits.
-In contrast, species taller or equal than 5.1 m and with lower than 14 ovules per flower had the lowest specialization values.
+Overall, plant species with the highest specialization were shorter than 1.3m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11% of their fruits.
+In contrast, species taller or equal than 5.1m and with lower than 14 ovules per flower had the lowest specialization values.
 
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies [(Olesen et al., 2007; @fortuna2010; @carvalheiro2014] or available in online archives (e.g., ‘The Web of Life’ [@fortuna2010] and ‘Mangal’ [@poisot2016].
+Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives (e.g., ‘The Web of Life’ [@fortuna2010] and ‘Mangal’ [@poisot2016].
 In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
 
-**Taxonomy of plants and pollinators.** All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [version _0.9.99_; @chamberlain2020].
+**Taxonomy of plants and pollinators.** All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020] version _0.9.99_.
 We filled the ‘not found’ searches manually using http://www.theplantlist.org/ and http://www.mobot.org/ for plants and http://www.catalogueoflife.org/ for floral visitors.
@@
 Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [version _0.7-70_; @revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
+We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [@revell2012] (version _0.7-70_) with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
 Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
@@
 
-**Phylogenetic signal of traits.** We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ version _0.7-70_ [@revell2012] and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
+**Phylogenetic signal of traits.** We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] version _0.7-70_ and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
@@
 Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency [@ballantyne2015], interaction frequency can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-Anthophila-Hymenoptera interactions.
+In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
 Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
@@
 **Visitation patterns.** We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because Hymenoptera-Anthophila was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
+Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
 In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
@@
 
-We implemented Bayesian generalized linear mixed models using the R package _brms_ [version _2.14.6_; @burkner2017].
+We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017] (version _2.14.6_).
 We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
@@
 We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [version _1.7.2_; @gabry2019].
+We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019] (version _1.7.2_).
 
@@
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization [d’; @bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [version _2.15_; @dormann2008].
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d’) [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008] (version _2.15_).
 

### 2021-12-02 Manuscript/Manuscript.tex
edits before submission

@@
 ]{article}
-\title{\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors}
+\title{\singlespacing \vspace{-1.6cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors}
 \author{}
@@
 \setstretch{2}
-\vspace{-1.8cm}
+\vspace{-1.7cm}
 \singlespacing
@@
 However, despite recent advances in the understanding of trade-offs for vegetative and physiological traits, little is known about plant reproductive economics and how they constrain plant life strategies and shape interactions with floral visitors.
-Here, we investigate plant reproductive trade-offs and how these reproductive compromises drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species from 28 plant-pollinator studies across 18 countries.
+Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species from 28 plant-pollinator studies across 18 countries.
 We tested whether a plant's reproductive strategy predicts its interactions with floral visitors and if the different reproductive traits predict the plant's role within the pollination network.
@@
 Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY\textsuperscript{\protect\hyperlink{ref-kattge2011}{22}} and COMPADRE),\textsuperscript{\protect\hyperlink{ref-salguero2015}{23}} plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function {[}\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}};;\textsuperscript{\protect\hyperlink{ref-diaz2016}{24}} bruelheide2018;{]}.\textsuperscript{\protect\hyperlink{ref-carmona2021}{25}} However, most studies have focused on vegetative traits such as leaf,\textsuperscript{\protect\hyperlink{ref-wright2004}{26}} wood,\textsuperscript{\protect\hyperlink{ref-chave2009}{27}} or root\textsuperscript{\protect\hyperlink{ref-laughlin2021}{28}} trade-offs with little or no attention given to reproductive traits\textsuperscript{\protect\hyperlink{ref-roddy2021}{5},\protect\hyperlink{ref-evojtko2020}{29}} which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively\textsuperscript{\protect\hyperlink{ref-moeller2017}{9},\protect\hyperlink{ref-barrett2003}{30}} and outcrossing levels are positively correlated with flower size.\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{31}} In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species' reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators.\textsuperscript{\protect\hyperlink{ref-ollerton2011}{32},\protect\hyperlink{ref-rodger2021}{33}} However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.
+With the recent availability of large trait databases (e.g., TRY\textsuperscript{\protect\hyperlink{ref-kattge2011}{22}} and COMPADRE),\textsuperscript{\protect\hyperlink{ref-salguero2015}{23}} plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function.\textsuperscript{\protect\hyperlink{ref-salguero2016}{12},\protect\hyperlink{ref-diaz2016}{24}--\protect\hyperlink{ref-carmona2021}{26}} However, most studies have focused on vegetative traits such as leaf,\textsuperscript{\protect\hyperlink{ref-wright2004}{27}} wood,\textsuperscript{\protect\hyperlink{ref-chave2009}{28}} or root\textsuperscript{\protect\hyperlink{ref-laughlin2021}{29}} trade-offs with little or no attention given to reproductive traits\textsuperscript{\protect\hyperlink{ref-roddy2021}{5},\protect\hyperlink{ref-evojtko2020}{30}} which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
+For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively\textsuperscript{\protect\hyperlink{ref-moeller2017}{9},\protect\hyperlink{ref-barrett2003}{31}} and outcrossing levels are positively correlated with flower size.\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{32}} In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species' reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators.\textsuperscript{\protect\hyperlink{ref-ollerton2011}{33},\protect\hyperlink{ref-rodger2021}{34}} However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.
 
-Several studies have identified links between plant traits and plant-pollinator network properties.\textsuperscript{\protect\hyperlink{ref-bartomeus2013}{34}--\protect\hyperlink{ref-rowe2020}{36}} Moreover, plant traits can define species' network roles (e.g., specialists vs generalists).\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-lazaro2013}{37}} For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators.\textsuperscript{\protect\hyperlink{ref-junker2013}{38},\protect\hyperlink{ref-coux2016}{39}} Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure.\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-ibanez2012}{40}} Remarkably, the combination of traits have shown to increase the predictive power of the network interactions.\textsuperscript{\protect\hyperlink{ref-eklof2013}{41}} Therefore, considering the different plant reproductive trade-offs which represent the species strategy within the network\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}} could progress our understanding of plant-pollinator interactions.
+Several studies have identified links between plant traits and plant-pollinator network properties.\textsuperscript{\protect\hyperlink{ref-bartomeus2013}{35}--\protect\hyperlink{ref-rowe2020}{37}} Moreover, plant traits can define species' network roles (e.g., specialists vs generalists).\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-lazaro2013}{38}} For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators.\textsuperscript{\protect\hyperlink{ref-junker2013}{39},\protect\hyperlink{ref-coux2016}{40}} Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure.\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-ibanez2012}{41}} Remarkably, the combination of traits have shown to increase the predictive power of the network interactions.\textsuperscript{\protect\hyperlink{ref-eklof2013}{42}} Therefore, considering the different plant reproductive trade-offs which represent the species strategy within the network\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}} could progress our understanding of plant-pollinator interactions.
 Further, we know little if the different network patterns generally studied at the community level are maintained when we scale up at macroecological scale.
@@
 The first principal component (PC1) represented 26.72\% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the `flower number - flower size trade-off', as already described in previous studies.\textsuperscript{\protect\hyperlink{ref-sargent2007}{42},\protect\hyperlink{ref-kettle2011}{43}} Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
+We refer to this axis as the `flower number - flower size trade-off', as already described in previous studies.\textsuperscript{\protect\hyperlink{ref-sargent2007}{43},\protect\hyperlink{ref-kettle2011}{44}} Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
 The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
@@
 \textbf{Phylogenetic signal of traits.} We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) in all quantitative traits (Supplementary Table S5).
-The traits that showed the highest phylogenetic signal were ovule number (\(\lambda = 1\)), pollen grains per flower (\(\lambda = 1\)) and plant height (\(\lambda = 0.96\)), followed by flower length (\(\lambda = 0.75\)), flower width (\(\lambda = 0.73\)), number of flowers per plant (\(\lambda = 0.69\)) and nectar concentration (\(\lambda = 0.65\)).
-The traits that showed a moderate phylogenetic signal were inflorescence width (\(\lambda = 0.57\)), style length (\(\lambda = 0.49\)) and autonomous selfing (\(\lambda = 0.34\)).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits (\(\lambda = 0.14\)).
+The traits that showed the highest phylogenetic signal were ovule number (\(\lambda\) = 1), pollen grains per flower (\(\lambda\) = 1) and plant height (\(\lambda\) = 0.96), followed by flower length (\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73), number of flowers per plant (\(\lambda\) = 0.69) and nectar concentration (\(\lambda\) = 0.65).
+The traits that showed a moderate phylogenetic signal were inflorescence width (\(\lambda\) = 0.57), style length (\(\lambda\) = 0.49) and autonomous selfing (\(\lambda\) = 0.34).
+Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits (\(\lambda\) = 0.14).
 
-\textbf{Visitation patterns.} The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors (\(conditional R2 = 0.26\); \(marginal R2 = 0.20\)) but little of the overall visitation rates (\(conditional R2 = 0.31\); \(marginal R2 = 0.06\)).
+\textbf{Visitation patterns.} The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the overall visitation rates (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
 However, we found relevant trends across the different floral visitor guilds on both presence-absence and visitation interactions (Fig.
@@
 3c), we found that bees interacted clearly more with plant species with long styles and high selfing and the rest of the guilds interacted slightly more with plant species with short styles and low selfing.
-In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig.
+In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-syrphid-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig.
 3d).
-On the style length trade-off, bees, Lepidoptera and Non-Anthophila-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
+On the style length trade-off, bees, Lepidoptera and non-bee-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while syrphids, non-syrphid-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
 3f).
 
-The additional model for both presence-absence of interactions (\(marginal R2 = 0.29\); \(conditional R2 = 0.19\)) and visitation rate (\(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns and that the contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
+The additional model for both presence-absence of interactions (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and visitation rate (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns and that the contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
 3a and Fig.
-3d) were driven by the family Andrenidae which interacted more frequently on presence-absence interactions with plant species with low number of flower but large (Supplementary Fig.
+3d) were driven by the family Andrenidae which interacted more frequently on presence-absence interactions with plant species with low number of flowers but large (Supplementary Fig.
 S8).
@@
 \textbf{Plant species functional roles.} The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
-S9; interaction frequency \textasciitilde{} PCs, \(conditional R2 = 0.11\), \(marginal R2 = 0.02\); normalized degree \textasciitilde{} PCs, \(conditional R2 = 0.24\), \(marginal R2 = 0.02\); and, specialization \textasciitilde{} PCs, \(conditional R2 = 0.37\), \(marginal R2 = 0.03\)).
+S9; interaction frequency \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
 Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
@@
 4a).
-Specifically, species taller than 3.9 m had the highest interaction frequency, while species that were shorter than 3.9 m and had a nectar concentration lower than 16\% had the lowest interaction frequency.
+Specifically, species taller than 3.9m had the highest interaction frequency, while species that were shorter than 3.9m and had a nectar concentration lower than 16\% had the lowest interaction frequency.
 Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
 4b).
-Species with a nectar concentration over 49\% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49\%, more than 21,000 pollen grains per flower and height less than 0.78 m had the lowest normalized degree.
+Species with a nectar concentration over 49\% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49\%, more than 21,000 pollen grains per flower and height less than 0.78m had the lowest normalized degree.
 Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
 4c).
-Overall, plant species with the highest specialization were shorter than 1.3 m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11\% of their fruits.
-In contrast, species taller or equal than 5.1 m and with lower than 14 ovules per flower had the lowest specialization values.
+Overall, plant species with the highest specialization were shorter than 1.3m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11\% of their fruits.
+In contrast, species taller or equal than 5.1m and with lower than 14 ovules per flower had the lowest specialization values.
 
@@
 Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
-Trait variation on these two axes was associated with the `fast-slow continuum' in plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}} and animal\textsuperscript{\protect\hyperlink{ref-healy2019}{44}} life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+Trait variation on these two axes was associated with the `fast-slow continuum' in plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}} and animal\textsuperscript{\protect\hyperlink{ref-healy2019}{45}} life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
 The `slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
 In contrast, plant species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display.\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{31}} The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Supplementary Fig.
+Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display.\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{32}} The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Supplementary Fig.
 S10).
@@
 S6).
-This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently.\textsuperscript{\protect\hyperlink{ref-lazaro2013}{37},\protect\hyperlink{ref-hegland2005}{45},\protect\hyperlink{ref-kaiser2014}{46}} In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation rates across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
+This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently.\textsuperscript{\protect\hyperlink{ref-lazaro2013}{38},\protect\hyperlink{ref-hegland2005}{46},\protect\hyperlink{ref-kaiser2014}{47}} In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation rates across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
 For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
-3) suggesting possible niche partitioning\textsuperscript{\protect\hyperlink{ref-palmer2003}{47},\protect\hyperlink{ref-phillips2020}{48}} between these two guilds.
+3) suggesting possible niche partitioning\textsuperscript{\protect\hyperlink{ref-palmer2003}{48},\protect\hyperlink{ref-phillips2020}{49}} between these two guilds.
 However, despite floral rewards, related traits were among the best at characterising species functional roles (Fig.
@@
 More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{17},\protect\hyperlink{ref-vazquez2007}{49},\protect\hyperlink{ref-encinas2012}{50}} that reproductive trade-offs do not.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{17},\protect\hyperlink{ref-vazquez2007}{50},\protect\hyperlink{ref-encinas2012}{51}} that reproductive trade-offs do not.
 
@@
 We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
-Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{25}} it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits.\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}} Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
-Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators.\textsuperscript{\protect\hyperlink{ref-gervasi2017}{51},\protect\hyperlink{ref-mackin2021}{52}} Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
+Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{26}} it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits.\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}} Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
+Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators.\textsuperscript{\protect\hyperlink{ref-gervasi2017}{52},\protect\hyperlink{ref-mackin2021}{53}} Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
 
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies {[}(Olesen et al., 2007;;\textsuperscript{\protect\hyperlink{ref-fortuna2010}{53}}{]}\textsuperscript{\protect\hyperlink{ref-carvalheiro2014}{54}} or available in online archives (e.g., `The Web of Life'\textsuperscript{\protect\hyperlink{ref-fortuna2010}{53}} and `Mangal'.\textsuperscript{\protect\hyperlink{ref-poisot2016}{55}} In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+Many of these networks are freely available either as published studies\textsuperscript{\protect\hyperlink{ref-olesen2007}{54}--\protect\hyperlink{ref-carvalheiro2014}{56}} or available in online archives (e.g., `The Web of Life'\textsuperscript{\protect\hyperlink{ref-fortuna2010}{55}} and `Mangal'.\textsuperscript{\protect\hyperlink{ref-poisot2016}{57}} In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
 
-\textbf{Taxonomy of plants and pollinators.} All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} {[}version \emph{0.9.99};{]}.\textsuperscript{\protect\hyperlink{ref-chamberlain2020}{56}} We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
+\textbf{Taxonomy of plants and pollinators.} All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize}\textsuperscript{\protect\hyperlink{ref-chamberlain2020}{58}} version \emph{0.9.99}.
+We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
 
@@
 
-\textbf{Phylogenetic Distance.} We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life.\textsuperscript{\protect\hyperlink{ref-smith2018}{57},\protect\hyperlink{ref-jin2019}{58}}
+\textbf{Phylogenetic Distance.} We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life.\textsuperscript{\protect\hyperlink{ref-smith2018}{59},\protect\hyperlink{ref-jin2019}{60}}
 
@@
 
-\textbf{Data Imputation.} Trait missing values were imputed with the function \emph{missForest}\textsuperscript{\protect\hyperlink{ref-stekhoven2012}{59}} which allows imputation of data sets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest}.\textsuperscript{\protect\hyperlink{ref-penone2014}{60}} To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{61}} based on a previous conceptual framework that considers phylogenetic eigenvectors.\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{62}} Although the variable of autonomous selfing had a high percentage of missing values (68\%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
+\textbf{Data Imputation.} Trait missing values were imputed with the function \emph{missForest}\textsuperscript{\protect\hyperlink{ref-stekhoven2012}{61}} which allows imputation of data sets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest}.\textsuperscript{\protect\hyperlink{ref-penone2014}{62}} To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{63}} based on a previous conceptual framework that considers phylogenetic eigenvectors.\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{64}} Although the variable of autonomous selfing had a high percentage of missing values (68\%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
 The categories of `none', `low', `medium' and `high' were converted to representative percentages of each category 0\%, 13\%, 50.5\% and 88\% respectively.
@@
 Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th--97.5th percentile range,\textsuperscript{\protect\hyperlink{ref-legendre2012}{63}} and thus our final dataset had 1,236 species.
+Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th--97.5th percentile range,\textsuperscript{\protect\hyperlink{ref-legendre2012}{65}} and thus our final dataset had 1,236 species.
 Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}version \emph{0.7-70};{]}\textsuperscript{\protect\hyperlink{ref-revell2012}{64}} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation.\textsuperscript{\protect\hyperlink{ref-abdi2010}{65}} Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools}\textsuperscript{\protect\hyperlink{ref-revell2012}{66}} (version \emph{0.7-70}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation.\textsuperscript{\protect\hyperlink{ref-abdi2010}{67}} Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
 S2).
@@
 
-\textbf{Phylogenetic signal of traits.} We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} version \emph{0.7-70}\textsuperscript{\protect\hyperlink{ref-revell2012}{64}} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+\textbf{Phylogenetic signal of traits.} We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools}\textsuperscript{\protect\hyperlink{ref-revell2012}{66}} version \emph{0.7-70} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
@@
 Second, we analysed the untransformed weighted networks with interaction frequency that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency,\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{66}} interaction frequency can provide valuable information of the contribution of floral visitors to pollination.\textsuperscript{\protect\hyperlink{ref-vazquez2005}{67},\protect\hyperlink{ref-vazquez2012}{68}} In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-Anthophila-Hymenoptera interactions.
+Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency,\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{68}} interaction frequency can provide valuable information of the contribution of floral visitors to pollination.\textsuperscript{\protect\hyperlink{ref-vazquez2005}{69},\protect\hyperlink{ref-vazquez2012}{70}} In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
 Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
@@
 \textbf{Visitation patterns.} We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because Hymenoptera-Anthophila was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
+Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
 In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total).
 This finding is consistent with previous research showing that \emph{A.
-mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems.\textsuperscript{\protect\hyperlink{ref-hung2018}{69}} Hence, to control for the effect of \emph{A.
+mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems.\textsuperscript{\protect\hyperlink{ref-hung2018}{71}} Hence, to control for the effect of \emph{A.
 mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of interaction and visitation rate excluding \emph{A.
@@
 
-We implemented Bayesian generalized linear mixed models using the R package \emph{brms} {[}version \emph{2.14.6};{]}.\textsuperscript{\protect\hyperlink{ref-burkner2017}{70}} We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
+We implemented Bayesian generalized linear mixed models using the R package \emph{brms}\textsuperscript{\protect\hyperlink{ref-burkner2017}{72}} (version \emph{2.14.6}).
+We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
 Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
@@
 We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}version \emph{1.7.2};{]}.\textsuperscript{\protect\hyperlink{ref-gabry2019}{71}}
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package\textsuperscript{\protect\hyperlink{ref-gabry2019}{73}} (version \emph{1.7.2}).
 
 \textbf{Plant species functional roles.} We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{72}} with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization {[}d';{]},\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{73}} which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} {[}version \emph{2.15};{]}.\textsuperscript{\protect\hyperlink{ref-dormann2008}{72}}
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{74}} with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d'),\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{75}} which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite}\textsuperscript{\protect\hyperlink{ref-dormann2008}{74}} (version \emph{2.15}).
 
@@
 We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
-We conducted this analysis using the \emph{rpart} package\textsuperscript{\protect\hyperlink{ref-therneau2015}{74}} version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package\textsuperscript{\protect\hyperlink{ref-milborrow2015}{75}} version \emph{3.0.9} to plot the regression trees.
+We conducted this analysis using the \emph{rpart} package\textsuperscript{\protect\hyperlink{ref-therneau2015}{76}} version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package\textsuperscript{\protect\hyperlink{ref-milborrow2015}{77}} version \emph{3.0.9} to plot the regression trees.
 We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
+\CSLLeftMargin{25. }
+\CSLRightInline{Bruelheide, H. \emph{et al.} Global trait--environment relationships of plant communities. \emph{Nat. Ecol. Evol.} \textbf{2}, 1906--1917 (2018).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{26. }
 \CSLRightInline{Carmona, C. P. \emph{et al.} Erosion of global functional diversity across the tree of life. \emph{Sci. Adv.} \textbf{7}, eabf2675 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{27. }
 \CSLRightInline{Wright, I. J. \emph{et al.} The worldwide leaf economics spectrum. \emph{Nature} \textbf{428}, 821--827 (2004).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{28. }
 \CSLRightInline{Chave, J. \emph{et al.} Towards a worldwide wood economics spectrum. \emph{Ecol. Lett.} \textbf{12}, 351--366 (2009).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Laughlin, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{30. }
 \CSLRightInline{E-Vojtkó, A., Bello, F.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Barrett, S. C. H. Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond. \emph{Philos. Trans. R. Soc. Lond. B Biol. Sci.} \textbf{358}, 991--1004 (2003).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{32. }
 \CSLRightInline{Goodwillie, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ollerton2011}{}}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{33. }
 \CSLRightInline{Ollerton, J., Winfree, R. \& Tarrant, S. How many flowering plants are pollinated by animals? \emph{Oikos} \textbf{120}, 321--326 (2011).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rodger2021}{}}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{34. }
 \CSLRightInline{Rodger, J. G. \emph{et al.} Widespread vulnerability of flowering plant seed production to pollinator declines. \emph{Science Advances} \textbf{7}, eabd3524 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bartomeus2013}{}}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{35. }
 \CSLRightInline{Bartomeus, I.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-olito2015}{}}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{36. }
 \CSLRightInline{Olito, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rowe2020}{}}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Rowe, L. \emph{et al.} Flower traits associated with the visitation patterns of bees. \emph{Oecologia} \textbf{193}, 511--522 (2020).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Lázaro, A., Jakobsson, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Junker, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking species functional roles to their network roles. \emph{Ecol. Lett.} \textbf{19}, 762--770 (2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Ibanez, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Eklöf, A. \emph{et al.} The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583 (2013).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Sargent, R. D., Goodwillie, C., Kalisz, S. \& Ree, R. H. Phylogenetic evidence for a flower size and number trade-off. \emph{Am. J. Bot.} \textbf{94}, 2059--2062 (2007).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Kettle, C. J. \emph{et al.} Ecological {Implications} of a {Flower Size}/{Number Trade}-{Off} in {Tropical Forest Trees}. \emph{PLoS One} \textbf{6}, e16111 (2011).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Healy, K., Ezard, T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Hegland, S. J. \& Totland, Ø. Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia} \textbf{145}, 586--594 (2005).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Kaiser-Bunbury, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-palmer2003}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Palmer, T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-phillips2020}{}}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Phillips, R. D., Peakall, R., van der Niet, T. \& Johnson, S. D. Niche perspectives on plant\textendash pollinator interactions. \emph{Trends Plant Sci.} \textbf{25}, 779--793 (2020).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Vázquez, D. P. \emph{et al.} Species abundance and asymmetric interaction strength in ecological networks. \emph{Oikos} \textbf{116}, 1120--1127 (2007).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.} \textbf{15}, 198--208 (2012).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gervasi2017}{}}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Gervasi, D. D. L. \& Schiestl, F. P. Real-time divergent evolution in plants driven by pollinators. \emph{Nat. Commun.} \textbf{8}, 14691 (2017).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-mackin2021}{}}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Mackin, C.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
+\CSLLeftMargin{54. }
+\CSLRightInline{Olesen, J. M., Bascompte, J., Dupont, Y. L. \& Jordano, P. The modularity of pollination networks. \emph{PNAS} \textbf{104}, 19891--19896 (2007).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Fortuna, M. A. \emph{et al.} Nestedness versus modularity in ecological networks: Two sides of the same coin? \emph{J. Anim. Ecol.} \textbf{79}, 811--817 (2010).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Carvalheiro, L.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{57. }
 \CSLRightInline{Poisot, T. \emph{et al.} Mangal \textendash{} making ecological network analysis simple. \emph{Ecography} \textbf{39}, 384--390 (2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{58. }
 \CSLRightInline{Chamberlain, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
-\CSLLeftMargin{57. }
+\CSLLeftMargin{59. }
 \CSLRightInline{Smith, S. A. \& Brown, J. W. Constructing a broadly inclusive seed plant phylogeny. \emph{Am. J. Bot.} \textbf{105}, 302--314 (2018).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
-\CSLLeftMargin{58. }
+\CSLLeftMargin{60. }
 \CSLRightInline{Jin, Y. \& Qian, H. V.{PhyloMaker}: An {R} package that can generate very large phylogenies for vascular plants. \emph{Ecography} \textbf{42}, 1353--1359 (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
-\CSLLeftMargin{59. }
+\CSLLeftMargin{61. }
 \CSLRightInline{Stekhoven, D. J. \& Bühlmann, P. {MissForest}\textemdash non-parametric missing value imputation for mixed-type data. \emph{Bioinformatics} \textbf{28}, 112--118 (2012).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
-\CSLLeftMargin{60. }
+\CSLLeftMargin{62. }
 \CSLRightInline{Penone, C. \emph{et al.} Imputation of missing data in life-history trait datasets: Which approach performs the best? \emph{Methods Ecol. Evol.} \textbf{5}, 961--970 (2014).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
-\CSLLeftMargin{61. }
+\CSLLeftMargin{63. }
 \CSLRightInline{Chamberlain, S. \emph{et al.} Package {``{PVR}''}. R package version 0.3 (2018).~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
-\CSLLeftMargin{62. }
+\CSLLeftMargin{64. }
 \CSLRightInline{Diniz-Filho, J. A. F. \emph{et al.} On the selection of phylogenetic eigenvectors for ecological analyses. \emph{Ecography} \textbf{35}, 239--249 (2012).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
-\CSLLeftMargin{63. }
+\CSLLeftMargin{65. }
 \CSLRightInline{Legendre, P. \& Legendre, L. \emph{Numerical ecology}. ({Elsevier, Amsterdam}, 2012).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
-\CSLLeftMargin{64. }
+\CSLLeftMargin{66. }
 \CSLRightInline{Revell, L. J. Phytools: An {R} package for phylogenetic comparative biology (and other things). \emph{Methods Ecol. Evol.} \textbf{3}, 217--223 (2012).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
-\CSLLeftMargin{65. }
+\CSLLeftMargin{67. }
 \CSLRightInline{Abdi, H. \& Williams, L. J. Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459 (2010).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
-\CSLLeftMargin{66. }
+\CSLLeftMargin{68. }
 \CSLRightInline{Ballantyne, G., Baldock, K.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
-\CSLLeftMargin{67. }
+\CSLLeftMargin{69. }
 \CSLRightInline{Vázquez, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
-\CSLLeftMargin{68. }
+\CSLLeftMargin{70. }
 \CSLRightInline{Vázquez, D. P. \emph{et al.} The strength of plant\textendash pollinator interactions. \emph{Ecology} \textbf{93}, 719--725 (2012).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
-\CSLLeftMargin{69. }
+\CSLLeftMargin{71. }
 \CSLRightInline{Hung, K.-L.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
-\CSLLeftMargin{70. }
+\CSLLeftMargin{72. }
 \CSLRightInline{Bürkner, P.-C. Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.} \textbf{80}, 1--28 (2017).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
-\CSLLeftMargin{71. }
+\CSLLeftMargin{73. }
 \CSLRightInline{Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A. Visualization in {Bayesian} workflow. \emph{J. R. Stat. Soc. Ser. A Stat. Soc.} \textbf{182}, 389--402 (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
-\CSLLeftMargin{72. }
+\CSLLeftMargin{74. }
 \CSLRightInline{Dormann, C. F., Gruber, B. \& Fründ, J. Introducing the bipartite package: Analysing ecological networks. \emph{R News} \textbf{8/2}, (2008).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
-\CSLLeftMargin{73. }
+\CSLLeftMargin{75. }
 \CSLRightInline{Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in species interaction networks. \emph{BMC Ecol.} \textbf{6}, 9 (2006).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-therneau2015}{}}%
-\CSLLeftMargin{74. }
+\CSLLeftMargin{76. }
 \CSLRightInline{Therneau, T., Atkinson, B., Ripley, B.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-milborrow2015}{}}%
-\CSLLeftMargin{75. }
+\CSLLeftMargin{77. }
 \CSLRightInline{Milborrow, S.

### 2021-12-06 Manuscript/Manuscript.Rmd
edits of Nacho

@@
 # csl: https://www.zotero.org/styles/ecology
-
+notes-after-punctuation: false
 link-citations: yes
@@
 However, we did find important differences in the interaction level among floral visitor guilds on the different axes of trait variation.
-Finally, we found that plant size and floral rewards were the most important traits in the understanding of the species network role.
+Finally, we found that plant size and floral rewards were the most important traits in the understanding of the plant species network role.
 Our results highlight the importance of plant reproductive trade-offs in determining plant life strategies and plant-pollinator interactions in a global context.__
@@
 In addition, macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
-Linking the position in the trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
+Linking the plant's position in the trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
 Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
-However, reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020] despite the apparent generalist nature of plant-pollinator interactions [@waser1996; @olesen2002].
-In addition, it is unclear how specific plant reproductive biology traits influence plant-pollinator interactions [@tur2013; @devaux2014].
+However, reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020] despite the generalist nature of plant-pollinator interactions [@waser1996; @olesen2002].
+Overall, it is unclear how specific plant reproductive biology traits shape plant-pollinator interactions [@tur2013; @devaux2014].
 
@@
 However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively [@barrett2003; @moeller2017] and outcrossing levels are positively correlated with flower size [@goodwillie2010].
+For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively, [@barrett2003; @moeller2017] and outcrossing levels are positively correlated with flower size [@goodwillie2010].
 In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators [@ollerton2011; @rodger2021].
@@
 Remarkably, the combination of traits have shown to increase the predictive power of the network interactions [@eklof2013].
-Therefore, considering the different plant reproductive trade-offs which represent the species strategy within the network [@dehling2016] could progress our understanding of plant-pollinator interactions.
-Further, we know little if the different network patterns generally studied at the community level are maintained when we scale up at macroecological scale.
+Therefore, considering the different plant reproductive trade-offs which represent the species reproductive strategy within the network [@dehling2016] could progress our understanding of plant-pollinator interactions.
+Further, we know little if those patterns generally studied at the community level are representative at wider macroecological scales.
 
@@
 Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
-On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers.
-On PC1, specialization showed the opposite trend.
-On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing.
-Again, specialization showed the opposite trend to interaction frequency.
+On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers (Supplementary Fig.
+S9a).
+On PC1, specialization showed the opposite trend (Supplementary Fig.
+S9g).
+On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Supplementary Fig.
+S9c).
+Again, specialization showed the opposite trend to interaction frequency (Supplementary Fig.
+S9i).
 
@@
 
-Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (presence-absence of interactions and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies strongly influence plant-pollinator interactions.
+Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (presence-absence of interactions and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies influence plant-pollinator interactions.
 For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
@@
 3) suggesting possible niche partitioning [@palmer2003; @phillips2020] between these two guilds.
-However, despite floral rewards, related traits were among the best at characterising species functional roles (Fig.
+However, despite floral rewards were not included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species functional roles (Fig.
 4), yet the association between reproductive trade-offs and floral visitors did not account for floral rewards because there was insufficient data available.
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives (e.g., ‘The Web of Life’ [@fortuna2010] and ‘Mangal’ [@poisot2016].
+Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives (e.g., The Web of Life [@fortuna2010] and Mangal [@poisot2016]).
 In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
@@
 Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79% of missing values.
-Further, we conducted an additional imputation on the filtered raw data by filled cells of either pollen grains per flower or microlitres of nectar.
+Further, we conducted an additional imputation process on the subset of species with data for pollen per flower and microliters of nectar.
 This subset comprised 755 species, 8.01% missing values and all traits but milligrams of nectar (~50% of missing values) were included in the imputation process.
@@
 **Plant strategies.** We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01 respectively), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
@@
 
+This is study was supported by project SAFEGUARD (101003476 H2020-SFS-2019-2).
 We thank all researchers that made their data available for our analysis.

### 2021-12-06 Manuscript/Manuscript.tex
edits of Nacho

@@
 However, we did find important differences in the interaction level among floral visitor guilds on the different axes of trait variation.
-Finally, we found that plant size and floral rewards were the most important traits in the understanding of the species network role.
+Finally, we found that plant size and floral rewards were the most important traits in the understanding of the plant species network role.
 Our results highlight the importance of plant reproductive trade-offs in determining plant life strategies and plant-pollinator interactions in a global context.}
@@
 
-Despite the astonishing diversity of floral structures among flowering plants\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}} and their importance in shaping plant-pollinator interactions,\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}} a unified framework that explores plant reproductive compromises is currently lacking.\textsuperscript{\protect\hyperlink{ref-roddy2021}{5}} In addition, macroecological studies that investigate plant reproductive traits are scarce\textsuperscript{\protect\hyperlink{ref-baude2016}{6}--\protect\hyperlink{ref-moeller2017}{9}} and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales.\textsuperscript{\protect\hyperlink{ref-sargent2008}{10}--\protect\hyperlink{ref-ruger2018}{13}} Linking the position in the trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations.\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}} Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{15}} and trait-matching analyses.\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-bartomeus2016}{17}} However, reproductive traits have been overlooked beyond highly specialised pollination systems\textsuperscript{\protect\hyperlink{ref-dellinger2020}{4}} despite the apparent generalist nature of plant-pollinator interactions.\textsuperscript{\protect\hyperlink{ref-waser1996}{18},\protect\hyperlink{ref-olesen2002}{19}} In addition, it is unclear how specific plant reproductive biology traits influence plant-pollinator interactions.\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-devaux2014}{21}}
+Despite the astonishing diversity of floral structures among flowering plants\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}} and their importance in shaping plant-pollinator interactions\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}}, a unified framework that explores plant reproductive compromises is currently lacking\textsuperscript{\protect\hyperlink{ref-roddy2021}{5}}.
+In addition, macroecological studies that investigate plant reproductive traits are scarce\textsuperscript{\protect\hyperlink{ref-baude2016}{6}--\protect\hyperlink{ref-moeller2017}{9}} and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales\textsuperscript{\protect\hyperlink{ref-sargent2008}{10}--\protect\hyperlink{ref-ruger2018}{13}}.
+Linking the plant's position in the trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}}.
+Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{15}} and trait-matching analyses\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-bartomeus2016}{17}}.
+However, reproductive traits have been overlooked beyond highly specialised pollination systems\textsuperscript{\protect\hyperlink{ref-dellinger2020}{4}} despite the generalist nature of plant-pollinator interactions\textsuperscript{\protect\hyperlink{ref-waser1996}{18},\protect\hyperlink{ref-olesen2002}{19}}.
+Overall, it is unclear how specific plant reproductive biology traits shape plant-pollinator interactions\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-devaux2014}{21}}.
 
 Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY\textsuperscript{\protect\hyperlink{ref-kattge2011}{22}} and COMPADRE),\textsuperscript{\protect\hyperlink{ref-salguero2015}{23}} plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function.\textsuperscript{\protect\hyperlink{ref-salguero2016}{12},\protect\hyperlink{ref-diaz2016}{24}--\protect\hyperlink{ref-carmona2021}{26}} However, most studies have focused on vegetative traits such as leaf,\textsuperscript{\protect\hyperlink{ref-wright2004}{27}} wood,\textsuperscript{\protect\hyperlink{ref-chave2009}{28}} or root\textsuperscript{\protect\hyperlink{ref-laughlin2021}{29}} trade-offs with little or no attention given to reproductive traits\textsuperscript{\protect\hyperlink{ref-roddy2021}{5},\protect\hyperlink{ref-evojtko2020}{30}} which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively\textsuperscript{\protect\hyperlink{ref-moeller2017}{9},\protect\hyperlink{ref-barrett2003}{31}} and outcrossing levels are positively correlated with flower size.\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{32}} In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species' reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators.\textsuperscript{\protect\hyperlink{ref-ollerton2011}{33},\protect\hyperlink{ref-rodger2021}{34}} However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.
-
-Several studies have identified links between plant traits and plant-pollinator network properties.\textsuperscript{\protect\hyperlink{ref-bartomeus2013}{35}--\protect\hyperlink{ref-rowe2020}{37}} Moreover, plant traits can define species' network roles (e.g., specialists vs generalists).\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-lazaro2013}{38}} For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators.\textsuperscript{\protect\hyperlink{ref-junker2013}{39},\protect\hyperlink{ref-coux2016}{40}} Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure.\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-ibanez2012}{41}} Remarkably, the combination of traits have shown to increase the predictive power of the network interactions.\textsuperscript{\protect\hyperlink{ref-eklof2013}{42}} Therefore, considering the different plant reproductive trade-offs which represent the species strategy within the network\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}} could progress our understanding of plant-pollinator interactions.
-Further, we know little if the different network patterns generally studied at the community level are maintained when we scale up at macroecological scale.
+With the recent availability of large trait databases (e.g., TRY\textsuperscript{\protect\hyperlink{ref-kattge2011}{22}} and COMPADRE\textsuperscript{\protect\hyperlink{ref-salguero2015}{23}}), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function\textsuperscript{\protect\hyperlink{ref-salguero2016}{12},\protect\hyperlink{ref-diaz2016}{24}--\protect\hyperlink{ref-carmona2021}{26}}.
+However, most studies have focused on vegetative traits such as leaf\textsuperscript{\protect\hyperlink{ref-wright2004}{27}}, wood\textsuperscript{\protect\hyperlink{ref-chave2009}{28}}, or root\textsuperscript{\protect\hyperlink{ref-laughlin2021}{29}} trade-offs with little or no attention given to reproductive traits\textsuperscript{\protect\hyperlink{ref-roddy2021}{5},\protect\hyperlink{ref-evojtko2020}{30}} which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
+For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively,\textsuperscript{\protect\hyperlink{ref-moeller2017}{9},\protect\hyperlink{ref-barrett2003}{31}} and outcrossing levels are positively correlated with flower size\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{32}}.
+In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species' reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators\textsuperscript{\protect\hyperlink{ref-ollerton2011}{33},\protect\hyperlink{ref-rodger2021}{34}}.
+However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.
+
+Several studies have identified links between plant traits and plant-pollinator network properties\textsuperscript{\protect\hyperlink{ref-bartomeus2013}{35}--\protect\hyperlink{ref-rowe2020}{37}}.
+Moreover, plant traits can define species' network roles (e.g., specialists vs generalists)\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-lazaro2013}{38}}.
+For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators\textsuperscript{\protect\hyperlink{ref-junker2013}{39},\protect\hyperlink{ref-coux2016}{40}}.
+Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-ibanez2012}{41}}.
+Remarkably, the combination of traits have shown to increase the predictive power of the network interactions\textsuperscript{\protect\hyperlink{ref-eklof2013}{42}}.
+Therefore, considering the different plant reproductive trade-offs which represent the species reproductive strategy within the network\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}} could progress our understanding of plant-pollinator interactions.
+Further, we know little if those patterns generally studied at the community level are representative at wider macroecological scales.
 
@@
 The first principal component (PC1) represented 26.72\% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the `flower number - flower size trade-off', as already described in previous studies.\textsuperscript{\protect\hyperlink{ref-sargent2007}{43},\protect\hyperlink{ref-kettle2011}{44}} Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
+We refer to this axis as the `flower number - flower size trade-off', as already described in previous studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{43},\protect\hyperlink{ref-kettle2011}{44}}.
+Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
 The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
@@
 In contrast, plant species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display.\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{32}} The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Supplementary Fig.
+Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{32}}.
+The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Supplementary Fig.
 S10).
 
-Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (presence-absence of interactions and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies strongly influence plant-pollinator interactions.
+Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (presence-absence of interactions and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies influence plant-pollinator interactions.
 For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
@@
 S6).
-This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently.\textsuperscript{\protect\hyperlink{ref-lazaro2013}{38},\protect\hyperlink{ref-hegland2005}{46},\protect\hyperlink{ref-kaiser2014}{47}} In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation rates across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
+This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently\textsuperscript{\protect\hyperlink{ref-lazaro2013}{38},\protect\hyperlink{ref-hegland2005}{46},\protect\hyperlink{ref-kaiser2014}{47}}.
+In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation rates across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
 For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
 3) suggesting possible niche partitioning\textsuperscript{\protect\hyperlink{ref-palmer2003}{48},\protect\hyperlink{ref-phillips2020}{49}} between these two guilds.
-However, despite floral rewards, related traits were among the best at characterising species functional roles (Fig.
+However, despite floral rewards were not included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species functional roles (Fig.
 4), yet the association between reproductive trade-offs and floral visitors did not account for floral rewards because there was insufficient data available.
@@
 We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
-Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{26}} it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits.\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}} Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
-Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators.\textsuperscript{\protect\hyperlink{ref-gervasi2017}{52},\protect\hyperlink{ref-mackin2021}{53}} Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
+Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{26}} it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}}.
+Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
+Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators\textsuperscript{\protect\hyperlink{ref-gervasi2017}{52},\protect\hyperlink{ref-mackin2021}{53}}.
+Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
 
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies\textsuperscript{\protect\hyperlink{ref-olesen2007}{54}--\protect\hyperlink{ref-carvalheiro2014}{56}} or available in online archives (e.g., `The Web of Life'\textsuperscript{\protect\hyperlink{ref-fortuna2010}{55}} and `Mangal'.\textsuperscript{\protect\hyperlink{ref-poisot2016}{57}} In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+Many of these networks are freely available either as published studies\textsuperscript{\protect\hyperlink{ref-olesen2007}{54}--\protect\hyperlink{ref-carvalheiro2014}{56}} or available in online archives (e.g., The Web of Life\textsuperscript{\protect\hyperlink{ref-fortuna2010}{55}} and Mangal\textsuperscript{\protect\hyperlink{ref-poisot2016}{57}}).
+In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
 
@@
 
-\textbf{Phylogenetic Distance.} We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life.\textsuperscript{\protect\hyperlink{ref-smith2018}{59},\protect\hyperlink{ref-jin2019}{60}}
+\textbf{Phylogenetic Distance.} We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life\textsuperscript{\protect\hyperlink{ref-smith2018}{59},\protect\hyperlink{ref-jin2019}{60}}.
 
@@
 \textbf{Data Imputation.} Trait missing values were imputed with the function \emph{missForest}\textsuperscript{\protect\hyperlink{ref-stekhoven2012}{61}} which allows imputation of data sets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest}.\textsuperscript{\protect\hyperlink{ref-penone2014}{62}} To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{63}} based on a previous conceptual framework that considers phylogenetic eigenvectors.\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{64}} Although the variable of autonomous selfing had a high percentage of missing values (68\%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest}\textsuperscript{\protect\hyperlink{ref-penone2014}{62}}.
+To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{63}} based on a previous conceptual framework that considers phylogenetic eigenvectors\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{64}}.
+Although the variable of autonomous selfing had a high percentage of missing values (68\%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
 The categories of `none', `low', `medium' and `high' were converted to representative percentages of each category 0\%, 13\%, 50.5\% and 88\% respectively.
@@
 Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79\% of missing values.
-Further, we conducted an additional imputation on the filtered raw data by filled cells of either pollen grains per flower or microlitres of nectar.
+Further, we conducted an additional imputation process on the subset of species with data for pollen per flower and microliters of nectar.
 This subset comprised 755 species, 8.01\% missing values and all traits but milligrams of nectar (\textasciitilde50\% of missing values) were included in the imputation process.
@@
 \textbf{Plant strategies.} We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01 respectively), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
 Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th--97.5th percentile range,\textsuperscript{\protect\hyperlink{ref-legendre2012}{65}} and thus our final dataset had 1,236 species.
+Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th--97.5th percentile range\textsuperscript{\protect\hyperlink{ref-legendre2012}{65}}, and thus our final dataset had 1,236 species.
 Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools}\textsuperscript{\protect\hyperlink{ref-revell2012}{66}} (version \emph{0.7-70}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation.\textsuperscript{\protect\hyperlink{ref-abdi2010}{67}} Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools}\textsuperscript{\protect\hyperlink{ref-revell2012}{66}} (version \emph{0.7-70}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation\textsuperscript{\protect\hyperlink{ref-abdi2010}{67}}.
+Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
 S2).
@@
 Second, we analysed the untransformed weighted networks with interaction frequency that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency,\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{68}} interaction frequency can provide valuable information of the contribution of floral visitors to pollination.\textsuperscript{\protect\hyperlink{ref-vazquez2005}{69},\protect\hyperlink{ref-vazquez2012}{70}} In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
+Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{68}}, interaction frequency can provide valuable information of the contribution of floral visitors to pollination\textsuperscript{\protect\hyperlink{ref-vazquez2005}{69},\protect\hyperlink{ref-vazquez2012}{70}}.
+In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
 Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
@@
 This finding is consistent with previous research showing that \emph{A.
-mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems.\textsuperscript{\protect\hyperlink{ref-hung2018}{71}} Hence, to control for the effect of \emph{A.
+mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems\textsuperscript{\protect\hyperlink{ref-hung2018}{71}}.
+Hence, to control for the effect of \emph{A.
 mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of interaction and visitation rate excluding \emph{A.
@@
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{74}} with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d'),\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{75}} which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d')\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{75}}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
 Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite}\textsuperscript{\protect\hyperlink{ref-dormann2008}{74}} (version \emph{2.15}).

### 2021-12-06 Supplementary_Material/Species_Level_Metric_Pcs.Rmd
edits of Nacho

@@
            axis.text=element_text(size = rel(2.75), color = "black"),
+           plot.title = element_text(size = 40),
            legend.title=element_text(face="bold"),
@@
   size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC1")
+  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC1")+ggtitle("(a)")
 
@@
   size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC2")
+  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC2")+ggtitle("(b)")
 
@@
   size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC3")
+  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC3") +ggtitle("(c)")
 
@@
   size = 3, alpha=0.65, colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC1")
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC1")+ggtitle("(d)")
 
@@
   size = 3, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC2")
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC2")+ggtitle("(e)")
 
@@
   size = 3, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC3")
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC3")+ggtitle("(f)")
 
@@
   size = 3, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1")
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1")+ggtitle("(g)")
 
@@
   size = 3, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC2")
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC2")+ggtitle("(h)")
 
@@
  size = 3, alpha=0.65, colour="darkorange3") + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+geom_line(colour="black",size=1.5)+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC3")
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC3")+ggtitle("(i)")
 

### 2021-12-06 OLD/trial.R

@@ -9,7 +9,7 @@ library(sf)
 library(rnaturalearth)
 library(rnaturalearthdata)
 # READ LONG FORMAT DATA 
-world <- ne_countries(returnclass = "sf")
+world <- ne_countries(scale = "medium", returnclass = "sf")
 
 Long_format_metawebs <- readRDS("OLD/Long_format_metawebs.RData")
 
@@ -81,22 +81,24 @@ ggplot(data = world) +
  linetype = "dashed", size = 0.5), panel.background = element_rect(fill = "aliceblue"))
 
 
-
-
-
-ggplot(world, aes(long, lat)) +
-  geom_map(map=world, aes(map_id=region), fill="antiquewhite", color="grey49") +
-  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + 
-  coord_sf( ylim = c(-60, 100), expand = FALSE)+
-  geom_jitter(data=metadata_sub, aes(longitude,latitude), shape = 10, colour = "black", 
-              fill = "white",size = 2, stroke = 1,width = 0.2, height = 3)+
-  theme(panel.grid.major = element_line(color = gray(.5), 
-linetype = "dashed", size = 0.5), panel.background = element_rect(fill = "aliceblue"))
-
-ggplot() + 
-  geom_sf(data = world, show.legend = F) 
-
 ggplot(data = world) + 
-  geom_sf(color = "black", fill = "lightgreen")+
+  geom_sf(color = "grey25", fill = "grey80", size=0.1,lwd = 0)+
+  theme(axis.line = element_line(color='aliceblue'),
+        plot.background = element_blank(),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.border = element_blank())+
+  geom_point(data=metadata_sub, aes(longitude,latitude), shape = 21, colour = "black", 
+              fill = "#74c365",size = 2.35)+
   theme(panel.grid.major = element_line(color = gray(.5), 
-                                                                                      linetype = "dashed", size = 0.5), panel.background = element_rect(fill = "aliceblue"))
+  linetype = "dashed", size = 0), panel.background = element_rect(fill = "aliceblue"))+
+  xlab("")+ylab("")+
+  coord_sf(expand = FALSE)+
+  theme(axis.text.x=element_blank(), #remove x axis labels
+        axis.ticks.x=element_blank(), #remove x axis ticks
[…]

### 2021-12-07 Manuscript/Manuscript.Rmd
final edits, acknowledgements, and few style edits

@@
 Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
-However, reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020] despite the generalist nature of plant-pollinator interactions [@waser1996; @olesen2002].
+However, despite the generalist nature of most plant-pollinator interactions [@waser1996; @olesen2002], reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020].
 Overall, it is unclear how specific plant reproductive biology traits shape plant-pollinator interactions [@tur2013; @devaux2014].
@@
 
-This is study was supported by project SAFEGUARD (101003476 H2020-SFS-2019-2).
+This is study was supported by the project SAFEGUARD (101003476 H2020-SFS-2019-2).
 We thank all researchers that made their data available for our analysis.

### 2021-12-07 Manuscript/Manuscript.tex
final edits, acknowledgements, and few style edits

@@
 Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{15}} and trait-matching analyses\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-bartomeus2016}{17}}.
-However, reproductive traits have been overlooked beyond highly specialised pollination systems\textsuperscript{\protect\hyperlink{ref-dellinger2020}{4}} despite the generalist nature of plant-pollinator interactions\textsuperscript{\protect\hyperlink{ref-waser1996}{18},\protect\hyperlink{ref-olesen2002}{19}}.
+However, despite the generalist nature of most plant-pollinator interactions\textsuperscript{\protect\hyperlink{ref-waser1996}{18},\protect\hyperlink{ref-olesen2002}{19}}, reproductive traits have been overlooked beyond highly specialised pollination systems\textsuperscript{\protect\hyperlink{ref-dellinger2020}{4}}.
 Overall, it is unclear how specific plant reproductive biology traits shape plant-pollinator interactions\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-devaux2014}{21}}.
@@
 \CSLLeftMargin{34. }
-\CSLRightInline{Rodger, J. G. \emph{et al.} Widespread vulnerability of flowering plant seed production to pollinator declines. \emph{Science Advances} \textbf{7}, eabd3524 (2021).}
+\CSLRightInline{Rodger, J. G. \emph{et al.} Widespread vulnerability of flowering plant seed production to pollinator declines. \emph{Sci. Adv.} \textbf{7}, eabd3524 (2021).}
 

### 2021-12-07 Supplementary_Material/Analysis_2_Hymenoptera_Families_Separated.Rmd
edits on sup mat

@@
            panel.grid.major= element_blank(),
-           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
-           plot.subtitle = element_text(face="bold",size=rel(2))
+           plot.title = element_text(hjust = 0.5,size=rel(2.75)),
+           plot.subtitle = element_text(size=rel(2.5))
      ))
@@
 aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
-  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 
@@
 aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
-  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 
@@
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
-  theme_ms() + theme(legend.position = "none") + 
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + 
   scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0)) + scale_color_manual(name="Functional groups",
   values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + 
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0)) + 
   scale_color_manual(name="Functional groups",values=c("orange", "black", 
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles\n Low selfing    High selfing")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold"))+ 
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0))+ 
   scale_color_manual(name="Functional groups",values=c("orange", 

### 2021-12-07 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
edits on sup mat

--- 2021-10-05 Supplementary_Material/Supplementary_Material.Rmd
@@
 
-Jose B. Lanuza$^{1,2}*$, Romina Rader$^{1}$, Jamie Stavert$^{3}$, Liam K. Kendall$^{4}$, Manu E. Saunders$^{1}$ and Ignasi Bartomeus$^{2}$
+Jose B. Lanuza, Romina Rader, Jamie Stavert, Liam K. Kendall, Manu E. Saunders and Ignasi Bartomeus
 
@@
 
-Supplementary Fig. S1: Percentage of present and missing values of the different traits
+Supplementary Fig. S1: Percentage of present and missing values of the different plant traits
 
@@
 In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration.
-In general terms, nectar data was rarely present and we try to minimise the loss of information by filling some species at family level.
+In general terms, nectar data was rarely present and we tried to minimise the loss of information by filling some species at family level.
 For instance, Solanaceae species are described as nectarless, and species that belonged to this family were recorded with ‘absence’ of nectar.
@@
 - Pollen grains per flower: We recorded pollen grains per flower for all species but this field was rarely described in the literature.
-When just the pollen:ovule ratio was found we converted it back to pollen grains by multiplying by ovule number.
+When just the pollen:ovule ratio was found we converted it back to pollen grains by multiplying it by the average ovule number found for each species.
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Supplementary Fig. S1 | Percentage of present and missing values of the different traits.}"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Supplementary Fig.
+S1 | Percentage of present and missing values of the different plant traits.}"}
 

### 2021-12-09 Manuscript/Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
edits

--- 2021-12-07 Manuscript/Manuscript.Rmd
@@
 
-__Plant life strategies are constrained by cost-benefit trade-offs that determine plant form and function.
-However, despite recent advances in the understanding of trade-offs for vegetative and physiological traits, little is known about plant reproductive economics and how they constrain plant life strategies and shape interactions with floral visitors.
+__Plant life-history strategies are constrained by cost-benefit trade-offs that determine plant form and function.
+However, despite recent advances in the understanding of trade-offs for vegetative and physiological traits, little is known about plant reproductive economics and how they constrain plant life-history strategies and shape interactions with floral visitors.
 Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species from 28 plant-pollinator studies across 18 countries.
@@
 Finally, we found that plant size and floral rewards were the most important traits in the understanding of the plant species network role.
-Our results highlight the importance of plant reproductive trade-offs in determining plant life strategies and plant-pollinator interactions in a global context.__
+Our results highlight the importance of plant reproductive trade-offs in determining plant life-history strategies and plant-pollinator interactions in a global context.__
 
@@
 
-Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that explores plant reproductive compromises is currently lacking [@roddy2021].
+Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that explores plant reproductive trade-offs is currently lacking [@roddy2021].
 In addition, macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
-Linking the plant's position in the trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
+Linking the plant's position in trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
 Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
@@
 Therefore, considering the different plant reproductive trade-offs which represent the species reproductive strategy within the network [@dehling2016] could progress our understanding of plant-pollinator interactions.
-Further, we know little if those patterns generally studied at the community level are representative at wider macroecological scales.
+Further, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.
 
@@
 The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Supplementary Table S3) but style length also contributed moderately on PC1 (loading = -0.33).
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Supplementary Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
 The second principal component (PC2) represented 25.05% of the trait variation and indicated a trade-off between low and high pollinator dependence.
@@
 
-The additional model for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and visitation rate (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns and that the contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
+The additional model for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and visitation rate (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
+The contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
 3a and Fig.
-3d) were driven by the family Andrenidae which interacted more frequently on presence-absence interactions with plant species with low number of flowers but large (Supplementary Fig.
+3d) were driven by the family Andrenidae, which interacted more frequently on presence-absence interactions with plant species with low number of large flowers (Supplementary Fig.
 S8).
@@
 
-When we further investigate which combination of traits drive plant network roles, we show that the regression tree for visitation frequency was best explained by plant height, nectar concentration and style length (Fig.
+When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for visitation frequency was best explained by plant height, nectar concentration and style length (Fig.
 4a).
@@
 
-Here, we show that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
+This study demonstrates that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
 These trade-offs are differentiated along three axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-These reproductive trade-offs helped explain partly the presence of floral visitor interactions, but not their visitation rates.
+These reproductive trade-offs helped partly explain the presence of floral visitor interactions, but not their visitation rates.
 However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
@@
 3) suggesting possible niche partitioning [@palmer2003; @phillips2020] between these two guilds.
-However, despite floral rewards were not included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species functional roles (Fig.
-4), yet the association between reproductive trade-offs and floral visitors did not account for floral rewards because there was insufficient data available.
+However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species functional roles (Fig.
+4).
 More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.

### 2021-12-09 Manuscript/Lanuza_et_al_2021_Nat_Eco_Evo.tex
edits

--- 2021-12-07 Manuscript/Manuscript.tex
@@
 
-\textbf{Plant life strategies are constrained by cost-benefit trade-offs that determine plant form and function.
-However, despite recent advances in the understanding of trade-offs for vegetative and physiological traits, little is known about plant reproductive economics and how they constrain plant life strategies and shape interactions with floral visitors.
+\textbf{Plant life-history strategies are constrained by cost-benefit trade-offs that determine plant form and function.
+However, despite recent advances in the understanding of trade-offs for vegetative and physiological traits, little is known about plant reproductive economics and how they constrain plant life-history strategies and shape interactions with floral visitors.
 Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species from 28 plant-pollinator studies across 18 countries.
@@
 Finally, we found that plant size and floral rewards were the most important traits in the understanding of the plant species network role.
-Our results highlight the importance of plant reproductive trade-offs in determining plant life strategies and plant-pollinator interactions in a global context.}
+Our results highlight the importance of plant reproductive trade-offs in determining plant life-history strategies and plant-pollinator interactions in a global context.}
 
@@
 
-Despite the astonishing diversity of floral structures among flowering plants\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}} and their importance in shaping plant-pollinator interactions\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}}, a unified framework that explores plant reproductive compromises is currently lacking\textsuperscript{\protect\hyperlink{ref-roddy2021}{5}}.
+Despite the astonishing diversity of floral structures among flowering plants\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}} and their importance in shaping plant-pollinator interactions\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}}, a unified framework that explores plant reproductive trade-offs is currently lacking\textsuperscript{\protect\hyperlink{ref-roddy2021}{5}}.
 In addition, macroecological studies that investigate plant reproductive traits are scarce\textsuperscript{\protect\hyperlink{ref-baude2016}{6}--\protect\hyperlink{ref-moeller2017}{9}} and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales\textsuperscript{\protect\hyperlink{ref-sargent2008}{10}--\protect\hyperlink{ref-ruger2018}{13}}.
-Linking the plant's position in the trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}}.
+Linking the plant's position in trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}}.
 Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{15}} and trait-matching analyses\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-bartomeus2016}{17}}.
@@
 Therefore, considering the different plant reproductive trade-offs which represent the species reproductive strategy within the network\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}} could progress our understanding of plant-pollinator interactions.
-Further, we know little if those patterns generally studied at the community level are representative at wider macroecological scales.
+Further, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.
 
@@
 The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Supplementary Table S3) but style length also contributed moderately on PC1 (loading = -0.33).
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Supplementary Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
 The second principal component (PC2) represented 25.05\% of the trait variation and indicated a trade-off between low and high pollinator dependence.
@@
 
-The additional model for both presence-absence of interactions (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and visitation rate (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns and that the contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
+The additional model for both presence-absence of interactions (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and visitation rate (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
+The contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
 3a and Fig.
-3d) were driven by the family Andrenidae which interacted more frequently on presence-absence interactions with plant species with low number of flowers but large (Supplementary Fig.
+3d) were driven by the family Andrenidae, which interacted more frequently on presence-absence interactions with plant species with low number of large flowers (Supplementary Fig.
 S8).
@@
 3) suggesting possible niche partitioning\textsuperscript{\protect\hyperlink{ref-palmer2003}{48},\protect\hyperlink{ref-phillips2020}{49}} between these two guilds.
-However, despite floral rewards were not included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species functional roles (Fig.
-4), yet the association between reproductive trade-offs and floral visitors did not account for floral rewards because there was insufficient data available.
+However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species functional roles (Fig.
+4).
 More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.

### 2021-12-09 Manuscript/MS_word.Rmd
edits

--- 2021-11-18 Manuscript/Manuscript.Rmd
@@
 - \usepackage{pdflscape}
-
 ---
-
-\vspace{-2.2cm}
+---
+title: \singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors
+
+#author: 
+#  - Jose B. Lanuza^1,2^*
+#  - Romina Rader^1^
+#  - Jamie Stavert^3^
+#  - Liam K. Kendall^4^
+#  - Manu E. Saunders^1^
+#  - Ignasi Bartomeus^2^
+
+# may use lua filters for affiliations etc: see https://stackoverflow.com/a/52919256
+
+# date: '`r Sys.Date()`'
+
+output:
+  word_document: default
+  bookdown::word_document2: default  # for cross-references
+    fig_caption: yes
+    fig_width: 7
+    fig_height: 7
+    df_print: kable
+    keep_tex: yes
+    number_sections: no
+    extra_dependencies: ["float"]
+    toc: no
+    fig_crop: no
+    includes:
+      in_header: header.tex
+
+documentclass: article
+# classoption: twocolumn, landscape, etc
+papersize: a4
+pagestyle: plain  # plain, empty, headings
+geometry: margin=1in
+linestretch: 2
+fontfamily: mathpazo
+fontsize: 12pt
+
+bibliography: 
+  - references.bib
+  - knitcitations.bib
+# zotero: "My shared Zotero group"
+csl: ecology.csl
+# csl: https://www.zotero.org/styles/ecology
+
+link-citations: yes
+linkcolor: RoyalBlue
+urlcolor: RoyalBlue
+links-as-notes: false
+subparagraph: yes
+
+header-includes:
+- \usepackage{booktabs}
+- \usepackage{longtable}
+- \usepackage{array}
+- \usepackage{multirow}
+- \usepackage{wrapfig}
+- \usepackage{float}
+- \usepackage{colortbl}
+- \usepackage{tabu}
+- \usepackage{threeparttable}
+- \usepackage{threeparttablex}
+- \usepackage[normalem]{ulem}
+- \usepackage{makecell}
+- \usepackage{xcolor}
+- \usepackage{float}
+- \floatplacement{figure}{H}
+- \usepackage[skip=3pt]{caption}
+- \captionsetup[figure]{labelformat=empty}
+- \usepackage{setspace}
+- \usepackage{titlesec}
+- \titlespacing{\title}{0pt}{\parskip}{-\parskip}
+- \usepackage[style=nature]{biblatex}
+- \usepackage[labelformat = empty]{caption}
+- \usepackage{pdflscape}
+
+---
+
+\vspace{-1.7cm}
 \singlespacing

### 2021-12-16 Main_Figures/Figure3.Rmd
edits

--- 2021-09-15 Main_Figures/Figure3.Rmd
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap= "**Fig.
-3 | Visitation rates across the three main axes of trait variation.** Fitted posterior estimates of the number of visits made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
-Bees (a, b and c) and the rest of guilds (d, e and f) were plotted separately for visualization purposes.
-In addition, we trimmed the plotting area that was over the 95th percentile to improve visualisation.
-PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off."}
+\pagenumbering{gobble}
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27}
 
@@
            plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
-           plot.subtitle = element_text(face="bold",size=rel(2))
+           plot.subtitle = element_text(face="bold",size=rel(2.5))
      ))
@@
 aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
-  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC1", subtitle = "A")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 
@@
 aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
-  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC2", subtitle = "B") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 
@@
   theme_ms() + theme(legend.position = "none") + 
-  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC3", subtitle = "C")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 #Plot nicely PC1
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
-  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+
-  scale_y_log10()+ggtitle("(d)")
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
+  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+    "Non-syrphid-Diptera", "Syrphids"))+
+  scale_y_log10()+ggtitle("D")
 #Plot nicely PC2
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + 
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + 
   scale_color_manual(name="Functional groups",values=c("orange", "black", 
-  "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10()+ggtitle("(e)")
+  "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+    "Non-syrphid-Diptera", "Syrphids")) + scale_y_log10()+ggtitle("E")
 
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles\n Low selfing    High selfing")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold"))+ 
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold"))+ 
   scale_color_manual(name="Functional groups",values=c("orange", 
-  "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ scale_y_log10()+ggtitle("(f)")
+  "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
+    "Non-syrphid-Diptera", "Syrphids"))+ scale_y_log10()+ggtitle("F")
 

### 2021-12-16 Main_Figures/Traits_Table.Rmd
edits

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=5, fig.width=8}
+\pagenumbering{gobble}
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=1, fig.width=14}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-Type <- c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive")
+Type <- linebreak(c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive \n biology"),align = c("c"))
 
-Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive","","","","")
+Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology", "Reproductive \n biology","","","",""),align = c("c"))
 
@@
 
-dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
+dat <- data.frame( Trait, Trait1, T.cat)
 
-colnames(dat) <- c("Type","Traits","Type", "Traits", "Categories")
+colnames(dat) <- c(" ", "Traits", "Categories")
 
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c")) %>%
-kable_styling(full_width = F)
+kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("l","l","l")) %>%
+  kable_styling(full_width = F,font_size = 10) %>%
+  add_header_above(c("Quantitative traits" = 1,"Qualitative traits" = 2),bold=T)   %>% row_spec(0, bold=T)
 

### 2021-12-16 Supplementary_Material/Regression_Trees_Subset_Nectar_Pollen.Rmd
edits

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=17.5}
+\pagenumbering{gobble}
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.3, fig.width=15, out.width="105%"}
 
@@
 colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
 
 colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
 
 colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
 
@@
 
-rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.5,tweak = 1.25,type = 2) 
-rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.5,tweak = 1.25,type = 2)
-rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.5,tweak = 1.25,type = 2)
+rpart.plot(tree1, box.palette="GnOr", main="A Interaction frequency", cex.main=2.25,tweak = 1.50,type = 2) 
+rpart.plot(tree2, box.palette="GnOr", main="B Normalized degree", cex.main=2.25,tweak = 1.50,type = 2)
+rpart.plot(tree3, box.palette="GnOr", main="C Specialization", cex.main=2.25,tweak = 1.50,type = 2)
 

### 2021-12-17 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
edits on supp mat to match pnas format

@@
 ---
-title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant reproductive traits determine interactions with floral visitors}
+#title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant reproductive traits determine interactions with floral visitors}
 
@@
 
+```{r echo=FALSE, out.width='100%', fig.align='center'}
+knitr::include_graphics('../Images/pnas-logo.png')
+```
+
 \singlespacing
-\vspace{-1.6cm}
-
-Jose B. Lanuza, Romina Rader, Jamie Stavert, Liam K. Kendall, Manu E. Saunders and Ignasi Bartomeus
-
-\vspace{-0.6cm}
-
-\section*{\hfil Supplementary information\hfil}
-
-# Contents:
+
+\vspace{2cm}
+
+# Supplementary information for:
+
+## Trade-offs among plant reproductive traits determine interactions with floral visitors
+
+\textbf{Jose B. Lanuza*, Romina Rader, Jamie Stavert, Liam K. Kendall, Manu E. Saunders and Ignasi Bartomeus}
+
+\textbf{*Corresponding author}
+**E-mail: barragansljose@gmail.com**
+
+**This pdf includes:**
+
+Supplementary text
+
+Tables S1 to S5
+
+Figures S1 to S10
+
+\doublespacing
+
+<!--
 
@@
 
+-->
+
 \newpage
+
+## Supplementary Information Text
 
@@
 We divided the flowers in 8 main different categories: open, bowl, tube, campanulate, funnelform, papilionaceous, brush and capitulum.
-However, we ended up groupping all flowers on the following 6  morphological groups for analyses: tube, papilonaceous, open, capitulum, campanulate and brush (Supplementary text Fig.
+However, we ended up groupping all flowers on the following 6  morphological groups for analyses: tube, papilonaceous, open, capitulum, campanulate and brush (Supplementary Information Text Fig.
 1).
 
-```{r pressure, echo=FALSE, fig.cap="", out.width = '65%',fig.align='center', fig.cap="\\textbf{Supplementary text Fig.
-1 | Main floral morphologies considered in this study.} All species were groupped within these categories for analysis: (a) tube, (b) papilonaceous, (c) open, (d) capitulum, (e) campanulate and (f) brush."}
+```{r pressure, echo=FALSE, fig.cap="", out.width = '65%',fig.align='center', fig.cap="\\textbf{Supplementary Information Text Fig.
+1.}  Main floral morphologies considered in this study.
+All species were groupped within these categories for analysis: (a) tube, (b) papilonaceous, (c) open, (d) capitulum, (e) campanulate and (f) brush."}
 knitr::include_graphics("../Images/flower_shapes.png")
@@
 kable("latex", longtable = T, booktabs = T,linesep = "\\addlinespace",
-             caption = "\\textbf{Supplementary Table S1 | List of the 28 plant-pollinator studies used to build the plant trait database.} Each study is shown with the first author that conducted the study, number of networks or metawebs that contains, type of information that contains (weighted or unweighted),  the structure (web or metaweb), year of publication and digital object identifier or permanent link for each study.") %>%
+             caption = "\\textbf{Table S1.
+List of the 28 plant-pollinator studies used to build the plant trait database.
+Each study is shown with the first author that conducted the study, number of networks or metawebs that contains, type of information that contains (weighted or unweighted),  the structure (web or metaweb), year of publication and digital object identifier or permanent link for each study.}") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, repeat_header_method="replace" ,full_width=F,position = "left")
@@
 
- kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Supplementary Table S2 | Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species.}") %>%
+ kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S2.
+Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species.}") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
@@
 
-kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Supplementary Table S3 | Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.}") %>%
+kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S3.
+Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.}") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
@@
 
-kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Supplementary Table S4 | Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species.}") %>%
+kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Table S4.
+Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species.}") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
@@
 
-kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,caption = "\\textbf{Supplementary Table S5 | Phylogenetic signal of the different quantitative traits.}") %>%
+kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,caption = "\\textbf{Table S5. Phylogenetic signal of the different quantitative traits.}") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Supplementary Fig.
-S1 | Percentage of present and missing values of the different plant traits.}"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Fig. S1.} Percentage of present and missing values of the different plant traits."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Supplementary Fig.
-S2 |  Phylogenetic informed principal component analysis for the species that did not have missing values.}"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig.
+S2.}  Phylogenetic informed principal component analysis for the species that did not have missing values."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24,  fig.cap="\\textbf{Supplementary Fig.
-S3 | Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation.} The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24,  fig.cap="\\textbf{Fig.
+S3.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation.
+The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Supplementary Fig.
-S4 | Regression tree analyses.} Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig.
+S4.} Regression tree analyses.
+Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
 "}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Supplementary Fig.
-S5 | PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species.}"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig.
+S5.} PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Supplementary Fig.
-S6 | Phylogenetic informed principal component analysis for the subset of species with floral rewards.}"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig.
+S6.} Phylogenetic informed principal component analysis for the subset of species with floral rewards."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 \thispagestyle{empty}
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Supplementary Fig.
-S7 | Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species.} Categories that differ significantly are denoted with a different letter."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig.
+S7.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species.
+Categories that differ significantly are denoted with a different letter."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Supplementary Fig.
-S8 | Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation.} Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Fig.
+S8.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation.
+Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
 For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)"}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Supplementary Fig.
-S9 | Plant species level metrics across the three main axes of trait variation.}", fig.pos= "h"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
+S9.} Plant species level metrics across the three main axes of trait variation.", fig.pos= "h"}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Supplementary Fig.
-S10 | Pearson correlation between the product of flower number-flower size and autonomous selfing level.}", fig.pos= "h"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
+S10.} Pearson correlation between the product of flower number-flower size and autonomous selfing level.", fig.pos= "h"}
 

### 2021-12-20 Supplementary_Material/Bees_and_other_func_grous_separated.Rmd
Cap letters in supp to match the journal formattin of PNAS

@@
            plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
-           plot.subtitle = element_text(face="bold",size=rel(2))
+           plot.subtitle = element_text(face="bold",size=rel(2.2))
      ))
@@
 
-my_y_title_1 <- expression(paste(bold("(a) "), "All bee species"))
+my_y_title_1 <- expression(paste(bold("A "), "All bee species"))
 
@@
 
-my_y_title_1 <- expression(paste(bold("(b) "), "All bee species"))
+my_y_title_1 <- expression(paste(bold("B "), "All bee species"))
 
@@
 
-my_y_title_1 <- expression(paste(bold("(c) "), "All bee species"))
+my_y_title_1 <- expression(paste(bold("C "), "All bee species"))
 
@@
 
-my_y_title <- expression(paste(bold("(d) "), italic("Apis mellifera"), " excluded"))
+my_y_title <- expression(paste(bold("D "), italic("Apis mellifera"), " excluded"))
 
@@
 
-my_y_title <- expression(paste(bold("(e) "), italic("Apis mellifera"), " excluded"))
+my_y_title <- expression(paste(bold("E "), italic("Apis mellifera"), " excluded"))
 
@@
 
-my_y_title <- expression(paste(bold("(f) "), italic("Apis mellifera"), " excluded"))
+my_y_title <- expression(paste(bold("F "), italic("Apis mellifera"), " excluded"))
 
@@
 
-my_y_title_1 <- expression(paste(bold("(g) "), "All bee species"))
+my_y_title_1 <- expression(paste(bold("G "), "All bee species"))
 
@@
 
-my_y_title_1 <- expression(paste(bold("(h) "), "All bee species"))
+my_y_title_1 <- expression(paste(bold("H "), "All bee species"))
 
@@
 
-my_y_title_1 <- expression(paste(bold("(i) "), "All bee species"))
+my_y_title_1 <- expression(paste(bold("I "), "All bee species"))
 
@@
 
-my_y_title <- expression(paste(bold("(j) "), italic("Apis mellifera"), " excluded"))
+my_y_title <- expression(paste(bold("J "), italic("Apis mellifera"), " excluded"))
 
@@
 
-my_y_title <- expression(paste(bold("(k) "), italic("Apis mellifera"), " excluded"))
+my_y_title <- expression(paste(bold("K "), italic("Apis mellifera"), " excluded"))
 
@@
 
-my_y_title <- expression(paste(bold("(l) "), italic("Apis mellifera"), " excluded"))
+my_y_title <- expression(paste(bold("L "), italic("Apis mellifera"), " excluded"))
 
@@
 
+combined
+
 setwd("~/Dropbox/PhD/R/Chapter_2")

### 2021-12-20 Supplementary_Material/Species_Level_Metric_Pcs.Rmd
Cap letters in supp to match the journal formattin of PNAS

@@
            axis.text=element_text(size = rel(2.75), color = "black"),
-           plot.title = element_text(size = 40),
+           plot.title = element_text(size = 40,face="bold"),
            legend.title=element_text(face="bold"),
@@
   size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC1")+ggtitle("(a)")
+  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC1")+ggtitle("A")
 
@@
   size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC2")+ggtitle("(b)")
+  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC2")+ggtitle("B")
 
@@
   size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC3") +ggtitle("(c)")
+  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC3") +ggtitle("C")
 
@@
   size = 3, alpha=0.65, colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC1")+ggtitle("(d)")
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC1")+ggtitle("D")
 
@@
   size = 3, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC2")+ggtitle("(e)")
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC2")+ggtitle("E")
 
@@
   size = 3, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC3")+ggtitle("(f)")
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC3")+ggtitle("F")
 
@@
   size = 3, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1")+ggtitle("(g)")
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1")+ggtitle("G")
 
@@
   size = 3, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC2")+ggtitle("(h)")
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC2")+ggtitle("H")
 
@@
  size = 3, alpha=0.65, colour="darkorange3") + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+geom_line(colour="black",size=1.5)+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC3")+ggtitle("(i)")
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC3")+ggtitle("I")
 

### 2021-12-20 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
Cap letters in supp to match the journal formattin of PNAS

@@
 
-rpart.plot(tree_1, box.palette="GnOr", main="(a) Interaction frequency for all species", cex.main=1.75,tweak = 1.10) 
-rpart.plot(tree1, box.palette="GnOr", main="(b) Interaction frequency for subset with floral rewards", cex.main=1.75,tweak = 1.10)
-
-rpart.plot(tree_2, box.palette="GnOr", main="(c) Normalized degree for all species", cex.main=1.75,tweak = 1.10)
-rpart.plot(tree2, box.palette="GnOr", main="(d) Normalized degree for subset with floral rewards", cex.main=1.75,tweak = 1.10)
-
-rpart.plot(tree_3, box.palette="GnOr", main="(e) Specialization for all species", cex.main=1.75,tweak = 1.10) 
-rpart.plot(tree3, box.palette="GnOr", main="(f) Specialization for subset with floral rewards", cex.main=1.75,tweak = 1.10)
+rpart.plot(tree_1, box.palette="GnOr", main="A Interaction frequency for all species", cex.main=1.85,tweak = 1.10) 
+rpart.plot(tree1, box.palette="GnOr", main="B Interaction frequency for subset with floral rewards", cex.main=1.85,tweak = 1.10)
+
+rpart.plot(tree_2, box.palette="GnOr", main="C Normalized degree for all species", cex.main=1.85,tweak = 1.10)
+rpart.plot(tree2, box.palette="GnOr", main="D Normalized degree for subset with floral rewards", cex.main=1.85,tweak = 1.10)
+
+rpart.plot(tree_3, box.palette="GnOr", main="E Specialization for all species", cex.main=1.85,tweak = 1.10) 
+rpart.plot(tree3, box.palette="GnOr", main="F Specialization for subset with floral rewards", cex.main=1.85,tweak = 1.10)
 
@@
            legend.position = "none",
-           plot.title = element_text(face = "bold",size = rel(1.45)),
-           plot.subtitle = element_text(face = "bold",size = rel(1.3))
+           plot.title = element_text(face = "bold",size = rel(1.55)),
+           plot.subtitle = element_text(face = "bold",size = rel(1.4))
      ))
@@
                 width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "(a) Breeding system")+
+  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "A Breeding system")+
   theme(plot.title = element_text(hjust=0.5, size=25, face="bold"))+
@@
                 width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "(b) Breeding system")+
+  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "B Breeding system")+
   theme(plot.title = element_text(hjust=0.5,size=25, face="bold") )+
@@
   width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(c) Compatibility system")+
+  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "C Compatibility system")+
   geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
@@
   width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(d) Compatibility system")+
+  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "D Compatibility system")+
   geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
@@
                 width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "(e) Lifespan")+
+  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "E Lifespan")+
   geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
@@
                 width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "(f) Lifespan")+
+  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "F Lifespan")+
   geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")
@@
                 width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "(g) Life form")+
+  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "G Life form")+
   geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
@@
                 width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "(h) Life form")+
+  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "H Life form")+
   geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
@@
                 width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(i) Flower shape")+
+  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "I Flower shape")+
   geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")
@@
                 width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(j) Flower shape")+
+  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "J Flower shape")+
    geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
@@
                 width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "(k) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
+  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "K Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
 
@@
                 width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title = "(l) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
+  scale_color_manual(values=c("sienna2","purple"))+labs(title = "L Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
 
@@
                 width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "(m) Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
+  scale_color_manual(values=c("black","grey"))+labs(title = "M Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
 
@@
                 width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "(n) Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")
+  scale_color_manual(values=c("black","grey"))+labs(title = "N Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")
 

### 2021-12-20 OLD/trial.R

@@ -75,7 +75,7 @@ ggplot(data = world) +
   geom_sf(fill="antiquewhite", color="grey49") +
   xlab("Longitude") + ylab("Latitude") +
   geom_jitter(data=metadata_sub, aes(longitude,latitude), 
-  shape = 10, colour = "black", fill = "white",size = 2, 
+  shape = 10, colour = "black", fill = "white",size = 4, 
   stroke = 1,width = 0.2, height = 3)+ 
   theme(panel.grid.major = element_line(color = gray(.5), 
  linetype = "dashed", size = 0.5), panel.background = element_rect(fill = "aliceblue"))
@@ -83,13 +83,13 @@ ggplot(data = world) +
 
 ggplot(data = world) + 
   geom_sf(color = "grey25", fill = "grey80", size=0.1,lwd = 0)+
-  theme(axis.line = element_line(color='aliceblue'),
+  theme(axis.line = element_line(color='white'),
         plot.background = element_blank(),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.border = element_blank())+
-  geom_point(data=metadata_sub, aes(longitude,latitude), shape = 21, colour = "black", 
-              fill = "#74c365",size = 2.35)+
+  geom_jitter(data=metadata_sub, aes(longitude,latitude), shape = 21, colour = "black", 
+              fill = "#74c365",size = 3,stroke = 1,width = 0.2, height = 3)+
   theme(panel.grid.major = element_line(color = gray(.5), 
   linetype = "dashed", size = 0), panel.background = element_rect(fill = "aliceblue"))+
   xlab("")+ylab("")+

### 2022-01-04 Manuscript/Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
Editing table to fit on one column on overleaf

@@
 
-This is study was supported by the project SAFEGUARD (101003476 H2020-SFS-2019-2).
-We thank all researchers that made their data available for our analysis.
-We thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
+This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
+We thank all researchers that made their data openly available and sent it upon request.
+We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
 We also thank Jason Tylianakis for his comments on the manuscript before submission.
-JBL thanks the University of New England for the funding provided to carry out this work.
+Finally, JBL thanks the University of New England for the funding provided to carry out this work.

### 2022-01-14 Main_Figures/Presentation_1_plot_qualitative_trait.Rmd
Adding figure for presentation at EBD

--- 2021-12-09 Manuscript/Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
@@
 ---
-title: \singlespacing \vspace{-1.6cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors
-
-#author: 
-#  - Jose B. Lanuza^1,2^*
-#  - Romina Rader^1^
-#  - Jamie Stavert^3^
-#  - Liam K. Kendall^4^
-#  - Manu E. Saunders^1^
-#  - Ignasi Bartomeus^2^
-
-# may use lua filters for affiliations etc: see https://stackoverflow.com/a/52919256
-
-# date: '`r Sys.Date()`'
-
 output:
-  bookdown::pdf_document2:
-    fig_caption: yes
-    fig_width: 7
-    fig_height: 7
-    df_print: kable
-    keep_tex: yes
-    number_sections: no
-    extra_dependencies: ["float"]
-    toc: no
-    fig_crop: no
-    includes:
-      in_header: header.tex
-
-documentclass: article
-# classoption: twocolumn, landscape, etc
-papersize: a4
-pagestyle: plain  # plain, empty, headings
-geometry: margin=1in
-linestretch: 2
-fontfamily: mathpazo
-fontsize: 12pt
-
-bibliography: 
-  - references.bib
-  - knitcitations.bib
-# zotero: "My shared Zotero group"
-csl: ecology.csl
-# csl: https://www.zotero.org/styles/ecology
-notes-after-punctuation: false
-link-citations: yes
-linkcolor: RoyalBlue
-urlcolor: RoyalBlue
-links-as-notes: false
-subparagraph: yes
-
-header-includes:
-- \usepackage{booktabs}
-- \usepackage{longtable}
-- \usepackage{array}
-- \usepackage{multirow}
-- \usepackage{wrapfig}
-- \usepackage{float}
-- \usepackage{colortbl}
-- \usepackage{tabu}
-- \usepackage{threeparttable}
-- \usepackage{threeparttablex}
-- \usepackage[normalem]{ulem}
-- \usepackage{makecell}
-- \usepackage{xcolor}
-- \usepackage{float}
-- \floatplacement{figure}{H}
-- \usepackage[skip=3pt]{caption}
-- \captionsetup[figure]{labelformat=empty}
-- \usepackage{setspace}
-- \usepackage{titlesec}
-- \titlespacing{\title}{0pt}{\parskip}{-\parskip}
-- \usepackage[style=nature]{biblatex}
-- \usepackage[labelformat = empty]{caption}
-- \usepackage{pdflscape}
+  pdf_document: default
+  html_document: default
+classoption: landscape
 
@@
 
-\vspace{-1.7cm}
-\singlespacing
-\large 
-\textbf{Jose B. Lanuza$^{1,2}*$, Romina Rader$^{1}$, Jamie Stavert$^{3}$, Liam K. Kendall$^{4}$, Manu E. Saunders$^{1}$ and Ignasi Bartomeus$^{2}$}
+\pagenumbering{gobble}
 
-\vspace{0.3cm}
-
-\normalsize
-
-__Plant life-history strategies are constrained by cost-benefit trade-offs that determine plant form and function.
-However, despite recent advances in the understanding of trade-offs for vegetative and physiological traits, little is known about plant reproductive economics and how they constrain plant life-history strategies and shape interactions with floral visitors.
-Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species from 28 plant-pollinator studies across 18 countries.
-We tested whether a plant’s reproductive strategy predicts its interactions with floral visitors and if the different reproductive traits predict the plant’s role within the pollination network.
-We found that over half of all plant reproductive trait variation was explained by two independent axes that encompassed plant form and function.
-Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
-Plant reproductive trade-offs helped explain partly the presence or absence of interactions with floral visitors, but not differences in visitation rate.
-However, we did find important differences in the interaction level among floral visitor guilds on the different axes of trait variation.
-Finally, we found that plant size and floral rewards were the most important traits in the understanding of the plant species network role.
-Our results highlight the importance of plant reproductive trade-offs in determining plant life-history strategies and plant-pollinator interactions in a global context.__
-
-\small
-\vspace{-0.5cm}
-
-\noindent\rule{\textwidth}{1pt}
-
-^1^ School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-^2^ Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-^3^ Department of Conservation | Te Papa Atawhai, Auckland, New Zealand.
-^4^ Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden.
-`*` e-mail: barragansljose@gmail.com
-
-\doublespacing
-\vspace{5mm}
-\normalsize
-
-```{r setup, include=FALSE, cache=FALSE, message = FALSE}
-
-library("knitr")
-
-### Chunk options: see http://yihui.name/knitr/options/ ###
-## Text results
-opts_chunk$set(echo = FALSE, warning = TRUE, message = TRUE)
-
-## Code decoration
-opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)
-
-## Cache
-# opts_chunk$set(cache = 2, cache.path = "output/cache/")
-
-## Plots
-opts_chunk$set(fig.path = "output/figures/")
-
-```
-
-```{r knitcitations, cache = FALSE}
-library(knitcitations)
-cleanbib()   
-cite_options(citation_format = "pandoc")
-
-```
-
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.pos = 'H')
-```
-
-Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that explores plant reproductive trade-offs is currently lacking [@roddy2021].
-In addition, macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
-Linking the plant's position in trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
-Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
-However, despite the generalist nature of most plant-pollinator interactions [@waser1996; @olesen2002], reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020].
-Overall, it is unclear how specific plant reproductive biology traits shape plant-pollinator interactions [@tur2013; @devaux2014].
-
-Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY @kattge2011 and COMPADRE @salguero2015), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
-However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively, [@barrett2003; @moeller2017] and outcrossing levels are positively correlated with flower size [@goodwillie2010].
-In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators [@ollerton2011; @rodger2021].
-However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.
-
-Several studies have identified links between plant traits and plant-pollinator network properties [@bartomeus2013; @olito2015; @rowe2020].
-Moreover, plant traits can define species’ network roles (e.g., specialists vs generalists) [@lazaro2013; @tur2013].
-For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
-Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
-Remarkably, the combination of traits have shown to increase the predictive power of the network interactions [@eklof2013].
-Therefore, considering the different plant reproductive trade-offs which represent the species reproductive strategy within the network [@dehling2016] could progress our understanding of plant-pollinator interactions.
-Further, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.
-
-Here, we aim to explore the potential trade-offs among reproductive traits and how these influence plant-pollinator interactions.
-First, we identify the major axes of reproductive trait variation and trade-offs that determine plant form and function.
-Second, we investigate how plant species’ position in trait-space influence interactions with floral visitors.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species’ roles within networks using a set of complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
-
-# RESULTS
-
-**Plant strategies.** The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Fig.
-1 and Supplementary Fig.
-S5) and had a phylogenetic correlation ($\lambda$) of 0.76.
-The first principal component (PC1) represented 26.72% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the ‘flower number - flower size trade-off’, as already described in previous studies [@sargent2007; @kettle2011].
-Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Supplementary Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
-The second principal component (PC2) represented 25.05% of the trait variation and indicated a trade-off between low and high pollinator dependence.
-We refer to this axis as the ‘pollinator dependence trade-off’.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Supplementary Table S3).
-We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
-In contrast, species with high levels of autonomous selfing tended to have fewer and smaller flowers, had shorter styles and were shorter in height.
-Further, PC3 explained a considerable amount of trait variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
-The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Supplementary Table S3).
-Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the ‘style length trade-off’.
-Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 23.40%); and pollen quantity (pollen grains per flower) was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 21.67%; Supplementary Fig.
-S6).
-This pPCA explained similar variance with the first two principal components (45.07%) and similar associations of traits despite some variability in the loadings (Supplementary Table S4).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Fig.
-1 | Plant life-history strategies.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
-The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
-The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation.
-The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}
-
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-library(viridis) #COLOUR GGPLOT
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(magick)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#Images were made by Paula Martin
-#Check her work on https://paulamartinart.com/
-
-tree <- image_read("Images/PPCA_Plot/Tree.png")
-tree_1 <- as.raster(tree)
-
-style_l <- image_read("Images/PPCA_Plot/Style_Long.png")
-style_l_1 <- as.raster(style_l)
-
-style_s <- image_read("Images/PPCA_Plot/Style_Short.png")
-style_s_1 <- as.raster(style_s)
-
-ovule_h <- image_read("Images/PPCA_Plot/Ovule_High.png")
-ovule_h_1 <- as.raster(ovule_h)
-
-ovule_l <- image_read("Images/PPCA_Plot/Ovule_Low.png")
-ovule_l_1 <- as.raster(ovule_l)
-
-selfing_n <- image_read("Images/PPCA_Plot/Selfing_None.png")
-selfing_n_1 <- as.raster(selfing_n)
-
-selfing_h <- image_read("Images/PPCA_Plot/selfing.png")
-selfing_h_1 <- as.raster(selfing_h)
-
-single_flower <- image_read("Images/PPCA_Plot/Single_Flower.png")
-single_flower_1 <- as.raster(single_flower)
-
-many_flowers <- image_read("Images/PPCA_Plot/Inflorescencia.png")
-many_flowers_1 <- as.raster(many_flowers)
-#many_flowers_1 <- image_rotate(many_flowers, 45)
-
-large_flower <- image_read("Images/PPCA_Plot/flower_big.png")
-large_flower_1 <- as.raster(large_flower)
-
-flower_small <- image_read("Images/PPCA_Plot/flower_short.png")
-flower_small_1 <- as.raster(flower_small)
-
-herb <- image_read("Images/PPCA_Plot/herb.png")
-herb_1 <- as.raster(herb)
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("Flower number - flower size trade-off ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Pollinator dependence trade-off ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
-    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
-    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
-    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
-    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2, ymax = -1.50) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
-
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
-                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-plot_grid(all_spp(PC))
-
-```
-
-We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
-2 and Supplementary Table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, _P_ < 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , _P_ = 0.59; PC2:  Sum of squares = 0.83, F-value = 1.43, _P_ = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Supplementary Fig.
-S7).
-Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Supplementary Fig.
-S7a and Fig.
-S7b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Supplementary Fig.
-S7c and Fig.
-S7d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Supplementary Fig.
-S7e and Fig.
-S7f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Supplementary Fig.
-S7g and Fig.
-S7h).
-Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Supplementary Fig.
-S7i and Fig.
-S7j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Supplementary Fig.
-S7k and Fig.
-S7l).
-
-\blandscape
-
-\vspace*{-28mm}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18,fig.cap= "**Fig.
-2 | Location of the different qualitative traits on the trait space.** The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=12}
 
@@
 #LOAD LIBRARIES
-#library(phytools)
-#library(ape) #for phylogenetic distance
-#library(dplyr) #data processing
+library(phytools)
+library(ape) #for phylogenetic distance
+library(dplyr) #data processing
 #library(rtrees) #for phylogenetic distancelibrary(MASS)
-#library(reshape2)
+library(reshape2)
 library(viridis) #COLOUR GGPLOT
-#library(MASS)
+library(MASS)
 library(ggplot2)
 library(broman) #crayon colours
-#library(cowplot)
+library(cowplot)
 
@@
       theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
+            axis.title=element_text( size = rel(2.5)),
             axis.text=element_text(size = rel(1.75), color = "black"),
             legend.title=element_text(face="bold"),
-            legend.text=element_text(),
+            legend.text=element_text(size = rel(1.8)),
             legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.55, 'lines'),
+            legend.key.size = unit(2.6, 'lines'),
             panel.border=element_rect(color="black",size=1),
@@
              panel.grid.major= element_blank(),
-            plot.title = element_text(size = rel(1.65), face="bold")
+            plot.title = element_text(size = rel(2), face="bold")
       ))
@@
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Compatibility),size=1.75)+scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7"))
+  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Compatibility),size=3.5)+scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7"))
 
@@
   # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=2.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
 
@@
   #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.4, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
 
   #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
+#  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
+#  
+#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+#  plot <- plot + annotate("text", x = #-(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = #-(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
+#                          label = PCAloadings$Variables, #color="black",size=12, fontface=2)
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.185, 0.13)) +ggtitle("(a)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.20, 0.14),legend.title=element_text(size=24)) +ggtitle("")
 
@@
   #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
+  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
 
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
+                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("(b)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.090, 0.115)) + ggtitle("B")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.102, 0.1)) + ggtitle("(c)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.12, 0.1)) + ggtitle("C")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.165, 0.1)) + ggtitle("(f)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("F")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.13, 0.18)) + ggtitle("(e)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("E")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.163, 0.115)) + ggtitle("(d)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("D")
 
@@
 
-#  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flowe#r_sym(PC),ncol=3,nrow=2,  align = "hv")
-
-library(patchwork)
-Compatibility(PC) + Life_form(PC) + Life_span(PC) + Breeding_syst(PC) + Flower_sha(PC) + Flower_sym(PC) + plot_layout(ncol=3)
+  plot_grid(Compatibility(PC),ncol=1,nrow=1,  align = "hv")
 
 ```
-
-\elandscape
-
-\vspace{5mm}
-
-**Phylogenetic signal of traits.** We found a strong phylogenetic signal (*P* < 0.01) in all quantitative traits (Supplementary Table S5).
-The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
-The traits that showed a moderate phylogenetic signal were inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits ($\lambda$ = 0.14).
-
-**Visitation patterns.** The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall visitation rates (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant trends across the different floral visitor guilds on both presence-absence and visitation interactions (Fig.
-3).
-On the pollinator dependence trade-off, all floral visitor guilds interacted more frequently with plant species with higher pollinator dependence (PC2; Fig.
-3b and Fig.
-3e).
-For presence-absence interactions we found that all Diptera, Coleoptera and non-bee-Hymenoptera guilds interacted more frequently with plants with high flower number and small flowers (flower number - flower size trade-off, PC1; Fig.
-3a) but bees and Lepidoptera interacted slightly more frequently with plant species with low flower number but large flowers.
-For presence-absence interactions on PC3 (style length trade-off; Fig.
-3c), we found that bees interacted clearly more with plant species with long styles and high selfing and the rest of the guilds interacted slightly more with plant species with short styles and low selfing.
-In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-syrphid-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig.
-3d).
-On the style length trade-off, bees, Lepidoptera and non-bee-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while syrphids, non-syrphid-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
-3f).
-
-The additional model for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and visitation rate (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
-3a and Fig.
-3d) were driven by the family Andrenidae, which interacted more frequently on presence-absence interactions with plant species with low number of large flowers (Supplementary Fig.
-S8).
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Fig.
-3 | Interaction (yes/no) and visitation rates across the three main axes of trait variation per floral visitor guild.** Fitted posterior estimates of the presence/absence of interaction (a, b and c) and number of visits (d, e and f) made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
-PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.
-For visualization purposes, due to large differences between the visitation rates of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
-
-#LOAD LIBRARIES 
-#library(phytools)
-#library(ape) #for phylogenetic distance
-#library(dplyr) #data processing
-#library(rtrees) #for phylogenetic distancelibrary(MASS)
-#library(reshape2)
-library(viridis) #COLOUR GGPLOT
-#library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-#library(tidyverse)
-library(patchwork) #panel of plots
-#library(brms)
-#library(cmdstanr)
-
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2)),
-           axis.text=element_text(size = rel(1.8), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(2, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
-           plot.subtitle = element_text(face="bold",size=rel(2))
-     ))
-}
-
-setwd("~/R_Projects/Reproductive Traits")
-
-p1 <- readRDS("Main_Figures/figure_3_1.rds")
-p2 <- readRDS("Main_Figures/figure_3_2.rds")
-p3 <- readRDS("Main_Figures/figure_3_3.rds")
-pp1 <- readRDS("Main_Figures/figure_3_4.rds")
-pp2 <- readRDS("Main_Figures/figure_3_5.rds")
-pp3 <- readRDS("Main_Figures/figure_3_6.rds")
-
-library(patchwork)
-
-combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
-combined + plot_layout(guides = "collect",ncol = 3)
-
-```
-
-\elandscape
-
-**Plant species functional roles.** The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
-S9; interaction frequency ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
-On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers (Supplementary Fig.
-S9a).
-On PC1, specialization showed the opposite trend (Supplementary Fig.
-S9g).
-On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Supplementary Fig.
-S9c).
-Again, specialization showed the opposite trend to interaction frequency (Supplementary Fig.
-S9i).
-
-When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for visitation frequency was best explained by plant height, nectar concentration and style length (Fig.
-4a).
-Specifically, species taller than 3.9m had the highest interaction frequency, while species that were shorter than 3.9m and had a nectar concentration lower than 16% had the lowest interaction frequency.
-Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
-4b).
-Species with a nectar concentration over 49% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49%, more than 21,000 pollen grains per flower and height less than 0.78m had the lowest normalized degree.
-Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
-4c).
-Overall, plant species with the highest specialization were shorter than 1.3m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11% of their fruits.
-In contrast, species taller or equal than 5.1m and with lower than 14 ovules per flower had the lowest specialization values.
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=12,fig.cap= "**Fig.
-4 | Contribution of traits in plant's network roles.** Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
-The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
-Thus, the top node has the mean value of the named trait for the 100% of species.
-Each node has a yes/no question and when the condition is fulfilled, the branch turns to the ‘yes’ direction and when not, to the ‘no’ direction.
-This rationale is followed in all the regression trees as indicated in the first branch division of the topmost node of each tree."}
-
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
-########################################################################################################################################################
-#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
-
-library(rpart.plot)
-library(rpart)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
-nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
-d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
-
-#Set correct colnames for plotting
-colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
-
-colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
-
-colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
-
-set.seed(2)
-tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
-
-set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
-
-set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50) 
-par(mfrow=c(1,3))
-
-rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.45,tweak = 1.25,type = 2) 
-rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.45,tweak = 1.25,type = 2)
-rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.45,tweak = 1.25,type = 2)
-
-```
-
-\elandscape
-
-# DISCUSSION
-
-This study demonstrates that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
-These trade-offs are differentiated along three axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-These reproductive trade-offs helped partly explain the presence of floral visitor interactions, but not their visitation rates.
-However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
-Moreover, we found that the plant species functional roles within pollination networks were best explained by plant size and floral reward related traits.
-
-Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
-Trait variation on these two axes was associated with the ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-The ‘slow’ part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, plant species that employed the ‘fast’ strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
-The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Supplementary Fig.
-S10).
-
-Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (presence-absence of interactions and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies influence plant-pollinator interactions.
-For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
-1 and Supplementary Fig.
-S6).
-This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently [@hegland2005; @lazaro2013; @kaiser2014].
-In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation rates across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
-For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
-3) suggesting possible niche partitioning [@palmer2003; @phillips2020] between these two guilds.
-However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species functional roles (Fig.
-4).
-More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive trade-offs do not.
-
-To conclude, we provide the first description of plant reproductive trade-offs using a large global dataset of plant traits.
-We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
-Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits [@diaz2016; @carmona2021] it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits [@salguero2016].
-Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
-Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators [@gervasi2017; @mackin2021].
-Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
-
-# MATERIALS AND METHODS
-
-**Plant-pollinator network studies.** We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives (e.g., The Web of Life [@fortuna2010] and Mangal [@poisot2016]).
-In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
-
-**Taxonomy of plants and pollinators.** All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020] version _0.9.99_.
-We filled the ‘not found’ searches manually using http://www.theplantlist.org/ and http://www.mobot.org/ for plants and http://www.catalogueoflife.org/ for floral visitors.
-
-**Functional traits.** We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
-These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive biology and 3 vegetative, Supplementary Information).
-For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Supplementary Fig.
-S1 for missing values information for each trait).
-
-**Phylogenetic Distance.** We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package _rtrees_ (https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
-
-\singlespacing
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=1, fig.width=14}
-setwd("~/R_Projects/Reproductive Traits")
-
-library(kableExtra)
-
-library(dplyr)
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant","Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Floral_unit_width",
-         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
-         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-n_of_records <- subset(missing.values, isna=="FALSE")
-Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
-           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")
-
-Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Autonomous selfing", "Compatibility system", "Breeding system", " ", " ", " ", " ")
-
-T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-           "Presence \n Absence", "None \n Low \n Medium \n High", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " "),align = c("l"))
-
-Type <- linebreak(c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive \n biology"),align = c("c"))
-
-Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology", "Reproductive \n biology","","","",""),align = c("c"))
-
-dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
-
-Number_of_records_quantitative <- c(n_of_records$num.isna[n_of_records$key=="Plant_height_mean_m"], n_of_records$num.isna[n_of_records$key=="Corolla_diameter_mean"],
-  n_of_records$num.isna[n_of_records$key=="Corolla_length_mean"], n_of_records$num.isna[n_of_records$key=="Floral_unit_width"],
-  n_of_records$num.isna[n_of_records$key=="Style_length"], n_of_records$num.isna[n_of_records$key=="Ovule_number"],
-  n_of_records$num.isna[n_of_records$key=="Flowers_per_plant"], n_of_records$num.isna[n_of_records$key=="Nectar_ul"],
-  n_of_records$num.isna[n_of_records$key=="Nectar_mg"], n_of_records$num.isna[n_of_records$key=="Nectar_concentration"], n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
-  n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level_fruit_set"])
-
-Number_of_records_categorical <- c(n_of_records$num.isna[n_of_records$key=="lifespan"], n_of_records$num.isna[n_of_records$key=="life_form"],
-                                   n_of_records$num.isna[n_of_records$key=="Flower_morphology"], n_of_records$num.isna[n_of_records$key=="Flower_symmetry"],
-                                   n_of_records$num.isna[n_of_records$key=="Nectar_presence_absence"], n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level"],
-                                   n_of_records$num.isna[n_of_records$key=="Compatibility_system"], n_of_records$num.isna[n_of_records$key=="Breeding_system"],
-                                   rep("",4))
-
-dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
-
-colnames(dat) <- c("Type","Traits", "Type", "Traits", "Categories")
-
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table 1 | Quantitative and categorical traits used in this study.}") %>%
-kable_styling(full_width = F,font_size = 10) %>%
-add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 3),bold=T)  %>%
-    column_spec(c(1,3), bold = T) %>% row_spec(0, bold=T)
-
-```
-
-\doublespacing
-
-**Data Imputation.** Trait missing values were imputed with the function _missForest_ [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of _missForest_ [@penone2014].
-To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-Although the variable of autonomous selfing had a high percentage of missing values (68%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
-The categories of ‘none’, ‘low’, ‘medium’ and ‘high’ were converted to representative percentages of each category 0%, 13%, 50.5% and 88% respectively.
-This reduced the percentage of missing values for this column from 68% to 35% and allowed the imputation of this variable.
-However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Supplementary Fig.
-S1).
-Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79% of missing values.
-Further, we conducted an additional imputation process on the subset of species with data for pollen per flower and microliters of nectar.
-This subset comprised 755 species, 8.01% missing values and all traits but milligrams of nectar (~50% of missing values) were included in the imputation process.
-
-**Plant strategies.** We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th–97.5th percentile range [@legendre2012], and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [@revell2012] (version _0.7-70_) with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
-S2).
-We found little difference between the explained variance with the imputed dataset (51.08%) and the dataset without missing values (52.87%).
-In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
-For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
-
-**Phylogenetic signal of traits.** We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] version _0.7-70_ and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-**Network analyses.** Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-These networks were analysed in their qualitative (presence-absence) and quantitative (interaction frequency) form.
-First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
-Second, we analysed the untransformed weighted networks with interaction frequency that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency [@ballantyne2015], interaction frequency can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
-All analyses were conducted in R version _4.0.3_.
-
-**Visitation patterns.** We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
-This finding is consistent with previous research showing that _A.
-mellifera_ was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
-Hence, to control for the effect of _A.
-mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of interaction and visitation rate excluding _A.
-mellifera_.
-We found that _A.
-mellifera_, was partly driving some of the observed trends on PC1 (Supplementary Fig.
-S3).
-However, we did not detect major differences on PC2 and PC3.
-
-We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017] (version _2.14.6_).
-We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
-In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
-We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019] (version _1.7.2_).
-
-**Plant species functional roles.** We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d’) [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008] (version _2.15_).
-
-First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric ~ PC1 + PC2 + PC3).
-For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns section’.
-
-Second, to better understand these complex trait relationships, we used regression trees.
-Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
-We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
-We conducted this analysis using the _rpart_ package [@therneau2015] version _4.1-15_ with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] version _3.0.9_ to plot the regression trees.
-We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
-We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig.
-S4).
-
-# References
-
-<div id ="refs"></div>
-
-# Acknowledgements
-
-This is study was supported by the project SAFEGUARD (101003476 H2020-SFS-2019-2).
-We thank all researchers that made their data available for our analysis.
-We thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
-We also thank Jason Tylianakis for his comments on the manuscript before submission.
-JBL thanks the University of New England for the funding provided to carry out this work.

### 2022-01-17 Main_Figures/Figure3_b.Rmd
Some figures for presentation at ebd

--- 2021-12-16 Main_Figures/Figure3.Rmd
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=14}
 
@@
      theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2)),
-           axis.text=element_text(size = rel(1.8), color = "black"),
+           axis.title=element_text( size = rel(2.2)),
+           axis.text=element_text(size = rel(2), color = "black"),
            legend.title=element_text(face="bold",size=rel(2)),
@@
 pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
-aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
+aes(x = -PC1, y = Interaction),size = 2.8, alpha=0.4) + geom_line(size=1.8)  + ylab("Interaction")+ xlab("")+
   theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC1", subtitle = "A")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+    "Non-syrphid-Diptera", "Syrphids"))+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 
@@
 pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
-aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
+aes(x = -PC2, y = Interaction),size = 2.8, alpha=0.4) + geom_line(size=1.8)  + ylab("Interaction")+ xlab("")+
   theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC2", subtitle = "B") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+    "Non-syrphid-Diptera", "Syrphids"))+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 
@@
 
-combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
-combined + plot_layout(guides = "collect",ncol = 3)
+pp2 + theme(legend.position = "bottom")
 
-setwd("~/R_Projects/Reproductive Traits")
-
-saveRDS(p1,"Main_Figures/figure_3_1.rds")
-saveRDS(p2,"Main_Figures/figure_3_2.rds")
-saveRDS(p3,"Main_Figures/figure_3_3.rds")
-saveRDS(pp1,"Main_Figures/figure_3_4.rds")
-saveRDS(pp2,"Main_Figures/figure_3_5.rds")
-saveRDS(pp3,"Main_Figures/figure_3_6.rds")
+#combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
+#combined + plot_layout(guides = "collect",ncol = 3)
 

### 2022-01-24 Manuscript/Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
Editing for Ecol Letters

@@
 # zotero: "My shared Zotero group"
-csl: ecology.csl
-# csl: https://www.zotero.org/styles/ecology
+csl: ecology.csl #ecology letters
 notes-after-punctuation: false
@@
 - \usepackage{pdflscape}
+#- \DeclareUnicodeCharacter{0301}{*************************************}
 
@@
 
-\vspace{-1.7cm}
+\vspace{-1.4cm}
+
 \singlespacing
-\large 
-\textbf{Jose B. Lanuza$^{1,2}*$, Romina Rader$^{1}$, Jamie Stavert$^{3}$, Liam K. Kendall$^{4}$, Manu E. Saunders$^{1}$ and Ignasi Bartomeus$^{2}$}
-
-\vspace{0.3cm}
-
-\normalsize
-
-__Plant life-history strategies are constrained by cost-benefit trade-offs that determine plant form and function.
-However, despite recent advances in the understanding of trade-offs for vegetative and physiological traits, little is known about plant reproductive economics and how they constrain plant life-history strategies and shape interactions with floral visitors.
-Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species from 28 plant-pollinator studies across 18 countries.
-We tested whether a plant’s reproductive strategy predicts its interactions with floral visitors and if the different reproductive traits predict the plant’s role within the pollination network.
-We found that over half of all plant reproductive trait variation was explained by two independent axes that encompassed plant form and function.
-Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
-Plant reproductive trade-offs helped explain partly the presence or absence of interactions with floral visitors, but not differences in visitation rate.
-However, we did find important differences in the interaction level among floral visitor guilds on the different axes of trait variation.
-Finally, we found that plant size and floral rewards were the most important traits in the understanding of the plant species network role.
-Our results highlight the importance of plant reproductive trade-offs in determining plant life-history strategies and plant-pollinator interactions in a global context.__
+
+\textbf{Jose B.
+Lanuza$^{1,2}$} <barragansljose@gmail.com>, \textbf{Romina Rader$^{1}$} <rrader@une.edu.au>, \textbf{Jamie Stavert$^{3}$} <jamie.stavert@gmail.com>, \textbf{Liam K.
+Kendall$^{4}$} <liam.k.kendall@gmail.com>, \textbf{Manu E.
+Saunders$^{1}$} <Manu.Saunders@une.edu.au> \textbf{and Ignasi Bartomeus$^{2}$} <nacho.bartomeus@gmail.com>
 
 \small
-\vspace{-0.5cm}
-
-\noindent\rule{\textwidth}{1pt}
 
@@
 ^4^ Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden.
-`*` e-mail: barragansljose@gmail.com
+
+\doublespacing
+\normalsize
+
+\textbf{Statement of authorship:} JBL, RR and IB designed the study.
+JBL collated the data and conducted analysis with guidance of JS, LKK and IB.
+JBL wrote the manuscript with contributions of all authors.
+
+\textbf{Data accessibility statement:} All data and code used to conduct this study will be deposited in the public repository Dryad upon acceptance.
+
+\textbf{Short title:} Plant reproductive trade-offs.
+
+\textbf{Keywords:} life-history strategies | plant reproductive trade-offs | plant-pollinator interactions.
+
+\textbf{Type of article:} Letter.
+
+\textbf{Number of words:} Abstract  (146 words), main text (XXXX).
+
+\textbf{Number of references:} 77.
+
+\textbf{Number of figures and tables:} 4 figures and 1 table.
+
+\textbf{Corresponding author:} Jose B. Lanuza | +34 616375981| <barragansljose@gmail.com>
+
+\newpage
+
+# ABSTRACT
+
+Plant life-history strategies are constrained by cost-benefit trade-offs that determine plant form and function.
+However, despite recent advances in the understanding of plant trait variation, little is known about plant reproductive trade-offs and how these constrain life-history strategies and shape interactions with floral visitors.
+Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species.
+We found that over half of all plant reproductive trait variation was explained by two independent axes.
+Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
+In addition, plant reproductive trade-offs determined important differences in the interaction level among floral visitor guilds.
+Our study shows the main plant reproductive trade-offs and their relevance to understand plant-pollinator interactions in a global context.
+
+\newpage
 
@@
 
-Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that explores plant reproductive trade-offs is currently lacking [@roddy2021].
+**In bold PNAS editor's comments.**
+
+- 1st explores is an ambiguous term.
+Maybe changing it for describe/determine?
+2nd.
+Last phrase of the 1st paragraph lacks clarity.
+3rd.
+Conceptual focus is unclear (3rd paragraph).
+General comment: What do we need to understand, and how will this information relate to broader problems in ecology/evolution?
+It is not sufficient to suggest that we need to improve our understanding without giving specifics regarding the impact of these studies.
+
+- There is insufficient justification/discussion of the traits used (Table 1).
+For example, what is the expected relevance of plant height?
+In addition, some of the traits are classified as both quantitative and qualitative.
+How can this work?
+For example, the selfing level was given as four categories of quantitative estimates as well as four categories of qualitative estimates.
+Aren't these the same thing?
+Finally, it is not clear why some traits were included, such as ovule number, whole others were not, such as flower color.
+
+- I am not convinced that the imputation process for missing trait values is accurate.
+There are many examples of very closely related plant species that differ dramatically in traits such as nectar volume and other traits relevant to pollinator interactions, so using a phylogenetic signal to estimate missing values may often give the wrong answer.
+In the Supplement you state: "In general terms, nectar data was rarely present and we tried to minimise the loss of information by filling some species at family level." Seems preferable to simply exclude nectar as one of your traits.
+
+- A major issue with network data from studies of plant-visitor interactions is that there is rarely enough information to distinguish pollinators from pollen predators or nectar thieves.
+
+- It is not clear that the broad phylogenetic scale investigated in the paper is appropriate for investigating the importance of trade-offs that evolve at the level of populations and species.
+I realize that the data at a finer micro-evolutionary scale are generally not available, but this is the level where constraints emerge.
+
+# INTRODUCTION
+
+Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that **explores** plant reproductive trade-offs is currently lacking [@roddy2021].
 In addition, macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
@@
 However, despite the generalist nature of most plant-pollinator interactions [@waser1996; @olesen2002], reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020].
-Overall, it is unclear how specific plant reproductive biology traits shape plant-pollinator interactions [@tur2013; @devaux2014].
+**Overall, it is unclear how specific plant reproductive biology traits shape plant-pollinator interactions [@tur2013; @devaux2014].**
 
@@
 Remarkably, the combination of traits have shown to increase the predictive power of the network interactions [@eklof2013].
-Therefore, considering the different plant reproductive trade-offs which represent the species reproductive strategy within the network [@dehling2016] could progress our understanding of plant-pollinator interactions.
+**Therefore, considering the different plant reproductive trade-offs which represent the species reproductive strategy within the network [@dehling2016] could progress our understanding of plant-pollinator interactions**.
 Further, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.
@@
 Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species’ roles within networks using a set of complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
+
+# MATERIALS AND METHODS
+
+**Plant-pollinator network studies.** We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
+These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
+Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
+Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives (e.g., The Web of Life [@fortuna2010] and Mangal [@poisot2016]).
+In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+
+**Taxonomy of plants and pollinators.** All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020] version _0.9.99_.
+We filled the ‘not found’ searches manually using http://www.theplantlist.org/ and http://www.mobot.org/ for plants and http://www.catalogueoflife.org/ for floral visitors.
+
+**Functional traits.** We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
+These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive biology and 3 vegetative, Supplementary Information).
+For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
+From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Supplementary Fig.
+S1 for missing values information for each trait).
+
+**Phylogenetic Distance.** We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package _rtrees_ (https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
+
+\singlespacing
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=1, fig.width=14}
+setwd("~/R_Projects/Reproductive Traits")
+
+library(kableExtra)
+
+library(dplyr)
+library(readxl) #read excel file (trait data)
+library(dplyr) #data manipulation
+library(visdat) #VISUALIZE MISSING DATA
+library(naniar)
+library(tidyverse)
+########################################################################################################################################################
+#1) READ TRAIT DATA
+########################################################################################################################################################
+#load data
+trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
+########################################################################################################################################################
+#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
+########################################################################################################################################################
+#####
+#A) CLEAN DATA
+#####
+#select just filled rows
+trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
+
+#filter data, select species with flower level info and capitulum
+trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
+#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
+trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
+trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
+trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
+
+#Select columns to work with
+t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
+                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
+                        "Flowers_per_plant","Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
+                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
+
+########################################################################################################################################################
+#####
+#B) RENAME LEVELS FOR IMPUTATION
+#####
+#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
+#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
+t$Breeding_system <- as.character(t$Breeding_system)
+t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
+t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
+t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
+t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
+t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
+#Change to capital letters| There are already levels with lower case
+t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
+t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
+t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
+t$Breeding_system <- as.factor(t$Breeding_system)
+
+#Now 3 levels
+#Flower_morphology
+t$Flower_morphology <- as.character(t$Flower_morphology)
+t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
+t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
+t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
+t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
+t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
+t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
+t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
+t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
+t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
+t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
+t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
+t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
+t$Flower_morphology <- as.factor(t$Flower_morphology)
+
+#Life span
+t$lifespan <- as.character(t$lifespan )
+t$lifespan[t$lifespan=="annual"] <- "short_lived"
+t$lifespan[t$lifespan=="biennial"] <- "short_lived"
+t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
+t$lifespan[t$lifespan=="perennial"] <- "Perennial"
+t$lifespan <- as.factor(t$lifespan )
+
+########################################################################################################################################################
+#3) EXPLORE PATTERNS OF MISSING DATA
+########################################################################################################################################################
+
+#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
+#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
+t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
+t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
+t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
+t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
+
+#t$Nectar_ul adding it here just to see how many cells 
+#Now we just select presence/absence of nectar
+#select columns of interest
+t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
+         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Floral_unit_width",
+         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
+         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
+
+########################################################################################################################################################
+#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
+########################################################################################################################################################
+#Convert to factor 
+cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
+          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
+t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
+
+cols.num <- c("Family_all","Genus_all","Species_all")
+t[cols.num] <- sapply(t[cols.num],as.character)
+t$Species_all <- gsub("Species_all_", "", t$Species_all)
+
+t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
+
+#remove species that are not until species level
+#ALL THE SPECIES WITH SP. ARE DELETD
+t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
+t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
+t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
+t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
+t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
+t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
+t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
+#CHECK LEVELS
+
+#Make these NA's as NA
+t$Species_all[t$Species_all=="NA"] <- NA
+t$Family_all[t$Family_all=="NA"] <- NA
+t$Genus_all[t$Genus_all=="NA"] <- NA
+#remove NA's
+t <- t[!is.na(t$Family_all),]
+t <- t[!is.na(t$Species_all),]
+t <- t[!is.na(t$Genus_all),]
+
+missing.values <- t %>%
+  gather(key = "key", value = "val") %>%
+  mutate(isna = is.na(val)) %>%
+  group_by(key) %>%
+  mutate(total = n()) %>%
+  group_by(key, total, isna) %>%
+  summarise(num.isna = n()) %>%
+  mutate(pct = num.isna / total * 100)
+
+n_of_records <- subset(missing.values, isna=="FALSE")
+Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
+           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")
+
+Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Autonomous selfing", "Compatibility system", "Breeding system", " ", " ", " ", " ")
+
+T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
+           "Presence \n Absence", "None \n Low \n Medium \n High", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " "),align = c("l"))
+
+Type <- linebreak(c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive \n biology"),align = c("c"))
+
+Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology", "Reproductive \n biology","","","",""),align = c("c"))
+
+dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
+
+Number_of_records_quantitative <- c(n_of_records$num.isna[n_of_records$key=="Plant_height_mean_m"], n_of_records$num.isna[n_of_records$key=="Corolla_diameter_mean"],
+  n_of_records$num.isna[n_of_records$key=="Corolla_length_mean"], n_of_records$num.isna[n_of_records$key=="Floral_unit_width"],
+  n_of_records$num.isna[n_of_records$key=="Style_length"], n_of_records$num.isna[n_of_records$key=="Ovule_number"],
+  n_of_records$num.isna[n_of_records$key=="Flowers_per_plant"], n_of_records$num.isna[n_of_records$key=="Nectar_ul"],
+  n_of_records$num.isna[n_of_records$key=="Nectar_mg"], n_of_records$num.isna[n_of_records$key=="Nectar_concentration"], n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
+  n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level_fruit_set"])
+
+Number_of_records_categorical <- c(n_of_records$num.isna[n_of_records$key=="lifespan"], n_of_records$num.isna[n_of_records$key=="life_form"],
+                                   n_of_records$num.isna[n_of_records$key=="Flower_morphology"], n_of_records$num.isna[n_of_records$key=="Flower_symmetry"],
+                                   n_of_records$num.isna[n_of_records$key=="Nectar_presence_absence"], n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level"],
+                                   n_of_records$num.isna[n_of_records$key=="Compatibility_system"], n_of_records$num.isna[n_of_records$key=="Breeding_system"],
+                                   rep("",4))
+
+dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
+
+colnames(dat) <- c("Type","Traits", "Type", "Traits", "Categories")
+
+kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table 1 | Quantitative and categorical traits used in this study.}") %>%
+kable_styling(full_width = F,font_size = 10) %>%
+add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 3),bold=T)  %>%
+    column_spec(c(1,3), bold = T) %>% row_spec(0, bold=T)
+
+```
+
+\doublespacing
+
+**Data Imputation.** Trait missing values were imputed with the function _missForest_ [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of _missForest_ [@penone2014].
+To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
+Although the variable of autonomous selfing had a high percentage of missing values (68%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
+The categories of ‘none’, ‘low’, ‘medium’ and ‘high’ were converted to representative percentages of each category 0%, 13%, 50.5% and 88% respectively.
+This reduced the percentage of missing values for this column from 68% to 35% and allowed the imputation of this variable.
+However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Supplementary Fig.
+S1).
+Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79% of missing values.
+Further, we conducted an additional imputation process on the subset of species with data for pollen per flower and microliters of nectar.
+This subset comprised 755 species, 8.01% missing values and all traits but milligrams of nectar (~50% of missing values) were included in the imputation process.
+
+**Plant strategies.** We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
+Prior to the analyses, we excluded outliers and standardized the data.
+Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th–97.5th percentile range [@legendre2012], and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
+We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [@revell2012] (version _0.7-70_) with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
+Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
+S2).
+We found little difference between the explained variance with the imputed dataset (51.08%) and the dataset without missing values (52.87%).
+In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
+Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
+For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
+
+**Phylogenetic signal of traits.** We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] version _0.7-70_ and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
+However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
+
+**Network analyses.** Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+These networks were analysed in their qualitative (presence-absence) and quantitative (interaction frequency) form.
+First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
+Second, we analysed the untransformed weighted networks with interaction frequency that accounts for the intensity of the interaction.
+Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency [@ballantyne2015], interaction frequency can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
+In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
+Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
+All analyses were conducted in R version _4.0.3_.
+
+**Visitation patterns.** We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
+For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
+Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
+This finding is consistent with previous research showing that _A.
+mellifera_ was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
+Hence, to control for the effect of _A.
+mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of interaction and visitation rate excluding _A.
+mellifera_.
+We found that _A.
+mellifera_, was partly driving some of the observed trends on PC1 (Supplementary Fig.
+S3).
+However, we did not detect major differences on PC2 and PC3.
+
+We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017] (version _2.14.6_).
+We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
+In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
+Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
+We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
+We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
+We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019] (version _1.7.2_).
+
+**Plant species functional roles.** We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d’) [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008] (version _2.15_).
+
+First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric ~ PC1 + PC2 + PC3).
+For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
+Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns section’.
+
+Second, to better understand these complex trait relationships, we used regression trees.
+Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
+We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
+We conducted this analysis using the _rpart_ package [@therneau2015] version _4.1-15_ with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] version _3.0.9_ to plot the regression trees.
+We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
+We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
+We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig.
+S4).
 
@@
 
-# MATERIALS AND METHODS
-
-**Plant-pollinator network studies.** We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives (e.g., The Web of Life [@fortuna2010] and Mangal [@poisot2016]).
-In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
-
-**Taxonomy of plants and pollinators.** All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020] version _0.9.99_.
-We filled the ‘not found’ searches manually using http://www.theplantlist.org/ and http://www.mobot.org/ for plants and http://www.catalogueoflife.org/ for floral visitors.
-
-**Functional traits.** We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
-These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive biology and 3 vegetative, Supplementary Information).
-For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Supplementary Fig.
-S1 for missing values information for each trait).
-
-**Phylogenetic Distance.** We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package _rtrees_ (https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
-
-\singlespacing
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=1, fig.width=14}
-setwd("~/R_Projects/Reproductive Traits")
-
-library(kableExtra)
-
-library(dplyr)
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant","Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Floral_unit_width",
-         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
-         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-n_of_records <- subset(missing.values, isna=="FALSE")
-Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
-           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")
-
-Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Autonomous selfing", "Compatibility system", "Breeding system", " ", " ", " ", " ")
-
-T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-           "Presence \n Absence", "None \n Low \n Medium \n High", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " "),align = c("l"))
-
-Type <- linebreak(c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive \n biology"),align = c("c"))
-
-Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology", "Reproductive \n biology","","","",""),align = c("c"))
-
-dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
-
-Number_of_records_quantitative <- c(n_of_records$num.isna[n_of_records$key=="Plant_height_mean_m"], n_of_records$num.isna[n_of_records$key=="Corolla_diameter_mean"],
-  n_of_records$num.isna[n_of_records$key=="Corolla_length_mean"], n_of_records$num.isna[n_of_records$key=="Floral_unit_width"],
-  n_of_records$num.isna[n_of_records$key=="Style_length"], n_of_records$num.isna[n_of_records$key=="Ovule_number"],
-  n_of_records$num.isna[n_of_records$key=="Flowers_per_plant"], n_of_records$num.isna[n_of_records$key=="Nectar_ul"],
-  n_of_records$num.isna[n_of_records$key=="Nectar_mg"], n_of_records$num.isna[n_of_records$key=="Nectar_concentration"], n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
-  n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level_fruit_set"])
-
-Number_of_records_categorical <- c(n_of_records$num.isna[n_of_records$key=="lifespan"], n_of_records$num.isna[n_of_records$key=="life_form"],
-                                   n_of_records$num.isna[n_of_records$key=="Flower_morphology"], n_of_records$num.isna[n_of_records$key=="Flower_symmetry"],
-                                   n_of_records$num.isna[n_of_records$key=="Nectar_presence_absence"], n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level"],
-                                   n_of_records$num.isna[n_of_records$key=="Compatibility_system"], n_of_records$num.isna[n_of_records$key=="Breeding_system"],
-                                   rep("",4))
-
-dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
-
-colnames(dat) <- c("Type","Traits", "Type", "Traits", "Categories")
-
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table 1 | Quantitative and categorical traits used in this study.}") %>%
-kable_styling(full_width = F,font_size = 10) %>%
-add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 3),bold=T)  %>%
-    column_spec(c(1,3), bold = T) %>% row_spec(0, bold=T)
-
-```
-
-\doublespacing
-
-**Data Imputation.** Trait missing values were imputed with the function _missForest_ [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of _missForest_ [@penone2014].
-To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-Although the variable of autonomous selfing had a high percentage of missing values (68%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
-The categories of ‘none’, ‘low’, ‘medium’ and ‘high’ were converted to representative percentages of each category 0%, 13%, 50.5% and 88% respectively.
-This reduced the percentage of missing values for this column from 68% to 35% and allowed the imputation of this variable.
-However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Supplementary Fig.
-S1).
-Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79% of missing values.
-Further, we conducted an additional imputation process on the subset of species with data for pollen per flower and microliters of nectar.
-This subset comprised 755 species, 8.01% missing values and all traits but milligrams of nectar (~50% of missing values) were included in the imputation process.
-
-**Plant strategies.** We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th–97.5th percentile range [@legendre2012], and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [@revell2012] (version _0.7-70_) with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
-S2).
-We found little difference between the explained variance with the imputed dataset (51.08%) and the dataset without missing values (52.87%).
-In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
-For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
-
-**Phylogenetic signal of traits.** We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] version _0.7-70_ and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-**Network analyses.** Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-These networks were analysed in their qualitative (presence-absence) and quantitative (interaction frequency) form.
-First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
-Second, we analysed the untransformed weighted networks with interaction frequency that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency [@ballantyne2015], interaction frequency can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
-All analyses were conducted in R version _4.0.3_.
-
-**Visitation patterns.** We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
-This finding is consistent with previous research showing that _A.
-mellifera_ was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
-Hence, to control for the effect of _A.
-mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of interaction and visitation rate excluding _A.
-mellifera_.
-We found that _A.
-mellifera_, was partly driving some of the observed trends on PC1 (Supplementary Fig.
-S3).
-However, we did not detect major differences on PC2 and PC3.
-
-We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017] (version _2.14.6_).
-We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
-In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
-We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019] (version _1.7.2_).
-
-**Plant species functional roles.** We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d’) [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008] (version _2.15_).
-
-First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric ~ PC1 + PC2 + PC3).
-For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns section’.
-
-Second, to better understand these complex trait relationships, we used regression trees.
-Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
-We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
-We conducted this analysis using the _rpart_ package [@therneau2015] version _4.1-15_ with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] version _3.0.9_ to plot the regression trees.
-We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
-We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig.
-S4).
-
 # References

### 2022-01-24 Manuscript/Lanuza_et_al_2021_Nat_Eco_Evo.tex
Editing for Ecol Letters

@@
 \setstretch{2}
-\vspace{-1.7cm}
+\vspace{-1.4cm}
+
 \singlespacing
-\large
-
-\textbf{Jose B. Lanuza$^{1,2}*$, Romina Rader$^{1}$, Jamie Stavert$^{3}$, Liam K. Kendall$^{4}$, Manu E. Saunders$^{1}$ and Ignasi Bartomeus$^{2}$}
-
-\vspace{0.3cm}
-
-\normalsize
-
-\textbf{Plant life-history strategies are constrained by cost-benefit trade-offs that determine plant form and function.
-However, despite recent advances in the understanding of trade-offs for vegetative and physiological traits, little is known about plant reproductive economics and how they constrain plant life-history strategies and shape interactions with floral visitors.
-Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species from 28 plant-pollinator studies across 18 countries.
-We tested whether a plant's reproductive strategy predicts its interactions with floral visitors and if the different reproductive traits predict the plant's role within the pollination network.
-We found that over half of all plant reproductive trait variation was explained by two independent axes that encompassed plant form and function.
-Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
-Plant reproductive trade-offs helped explain partly the presence or absence of interactions with floral visitors, but not differences in visitation rate.
-However, we did find important differences in the interaction level among floral visitor guilds on the different axes of trait variation.
-Finally, we found that plant size and floral rewards were the most important traits in the understanding of the plant species network role.
-Our results highlight the importance of plant reproductive trade-offs in determining plant life-history strategies and plant-pollinator interactions in a global context.}
+
+\textbf{Jose B.
+Lanuza$^{1,2}$} \href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}, \textbf{Romina Rader$^{1}$} \href{mailto:rrader@une.edu.au}{\nolinkurl{rrader@une.edu.au}}, \textbf{Jamie Stavert$^{3}$} \href{mailto:jamie.stavert@gmail.com}{\nolinkurl{jamie.stavert@gmail.com}}, \textbf{Liam K.
+Kendall$^{4}$} \href{mailto:liam.k.kendall@gmail.com}{\nolinkurl{liam.k.kendall@gmail.com}}, \textbf{Manu E.
+Saunders$^{1}$} \href{mailto:Manu.Saunders@une.edu.au}{\nolinkurl{Manu.Saunders@une.edu.au}} \textbf{and Ignasi Bartomeus$^{2}$} \href{mailto:nacho.bartomeus@gmail.com}{\nolinkurl{nacho.bartomeus@gmail.com}}
 
 \small
-\vspace{-0.5cm}
-
-\noindent
-
-\rule{\textwidth}{1pt}
 
@@
 \textsuperscript{4} Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden.
-\texttt{*} e-mail: \href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
+
+\doublespacing
+\normalsize
+
+\textbf{Statement of authorship:} JBL, RR and IB designed the study.
+JBL collated the data and conducted analysis with guidance of JS, LKK and IB.
+JBL wrote the manuscript with contributions of all authors.
+
+\textbf{Data accessibility statement:} All data and code used to conduct this study will be deposited in the public repository Dryad upon acceptance.
+
+\textbf{Short title:} Plant reproductive trade-offs.
+
+\textbf{Keywords:} life-history strategies \textbar{} plant reproductive trade-offs \textbar{} plant-pollinator interactions.
+
+\textbf{Type of article:} Letter.
+
+\textbf{Number of words:} Abstract (146 words), main text (XXXX).
+
+\textbf{Number of references:} 77.
+
+\textbf{Number of figures and tables:} 4 figures and 1 table.
+
+\textbf{Corresponding author:} Jose B. Lanuza \textbar{} +34 616375981\textbar{} \href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
+
+\newpage
+
+\hypertarget{abstract}{%
+\section{ABSTRACT}\label{abstract}}
+
+Plant life-history strategies are constrained by cost-benefit trade-offs that determine plant form and function.
+However, despite recent advances in the understanding of plant trait variation, little is known about plant reproductive trade-offs and how these constrain life-history strategies and shape interactions with floral visitors.
+Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species.
+We found that over half of all plant reproductive trait variation was explained by two independent axes.
+Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
+In addition, plant reproductive trade-offs determined important differences in the interaction level among floral visitor guilds.
+Our study shows the main plant reproductive trade-offs and their relevance to understand plant-pollinator interactions in a global context.
+
+\newpage
 
@@
 
-Despite the astonishing diversity of floral structures among flowering plants\textsuperscript{\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}} and their importance in shaping plant-pollinator interactions\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}}, a unified framework that explores plant reproductive trade-offs is currently lacking\textsuperscript{\protect\hyperlink{ref-roddy2021}{5}}.
-In addition, macroecological studies that investigate plant reproductive traits are scarce\textsuperscript{\protect\hyperlink{ref-baude2016}{6}--\protect\hyperlink{ref-moeller2017}{9}} and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales\textsuperscript{\protect\hyperlink{ref-sargent2008}{10}--\protect\hyperlink{ref-ruger2018}{13}}.
-Linking the plant's position in trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}}.
-Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches\textsuperscript{\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{15}} and trait-matching analyses\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-bartomeus2016}{17}}.
-However, despite the generalist nature of most plant-pollinator interactions\textsuperscript{\protect\hyperlink{ref-waser1996}{18},\protect\hyperlink{ref-olesen2002}{19}}, reproductive traits have been overlooked beyond highly specialised pollination systems\textsuperscript{\protect\hyperlink{ref-dellinger2020}{4}}.
-Overall, it is unclear how specific plant reproductive biology traits shape plant-pollinator interactions\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-devaux2014}{21}}.
+\textbf{In bold PNAS editor's comments.}
+
+\begin{itemize}
+\item
+  1st explores is an ambiguous term.
+Maybe changing it for describe/determine?
+2nd.
+Last phrase of the 1st paragraph lacks clarity.
+3rd.
+Conceptual focus is unclear (3rd paragraph).
+General comment: What do we need to understand, and how will this information relate to broader problems in ecology/evolution?
+It is not sufficient to suggest that we need to improve our understanding without giving specifics regarding the impact of these studies.
+\item
+  There is insufficient justification/discussion of the traits used (Table 1).
+For example, what is the expected relevance of plant height?
+In addition, some of the traits are classified as both quantitative and qualitative.
+How can this work?
+For example, the selfing level was given as four categories of quantitative estimates as well as four categories of qualitative estimates.
+Aren't these the same thing?
+Finally, it is not clear why some traits were included, such as ovule number, whole others were not, such as flower color.
+\item
+  I am not convinced that the imputation process for missing trait values is accurate.
+There are many examples of very closely related plant species that differ dramatically in traits such as nectar volume and other traits relevant to pollinator interactions, so using a phylogenetic signal to estimate missing values may often give the wrong answer.
+In the Supplement you state: ``In general terms, nectar data was rarely present and we tried to minimise the loss of information by filling some species at family level.'' Seems preferable to simply exclude nectar as one of your traits.
+\item
+  A major issue with network data from studies of plant-visitor interactions is that there is rarely enough information to distinguish pollinators from pollen predators or nectar thieves.
+\item
+  It is not clear that the broad phylogenetic scale investigated in the paper is appropriate for investigating the importance of tradeoffs that evolve at the level of populations and species.
+I realize that the data at a finer micro-evolutionary scale are generally not available, but this is the level where constraints emerge.
+\end{itemize}
+
+\hypertarget{introduction}{%
+\section{INTRODUCTION}\label{introduction}}
+
+Despite the astonishing diversity of floral structures among flowering plants (\protect\hyperlink{ref-barrett2002}{Barrett 2002}; \protect\hyperlink{ref-schiestl2013}{Schiestl \& Johnson 2013}) and their importance in shaping plant-pollinator interactions (\protect\hyperlink{ref-fenster2004}{Fenster \emph{et al.} 2004}; \protect\hyperlink{ref-dellinger2020}{Dellinger 2020}), a unified framework that \textbf{explores} plant reproductive trade-offs is currently lacking (\protect\hyperlink{ref-roddy2021}{Roddy \emph{et al.} 2021}).
+In addition, macroecological studies that investigate plant reproductive traits are scarce (\protect\hyperlink{ref-baude2016}{Baude \emph{et al.} 2016}; \protect\hyperlink{ref-munoz2016}{Munoz \emph{et al.} 2016}; \protect\hyperlink{ref-grossenbacher2017}{Grossenbacher \emph{et al.} 2017}; \protect\hyperlink{ref-moeller2017}{Moeller \emph{et al.} 2017}) and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales (\protect\hyperlink{ref-sargent2008}{Sargent \& Ackerly 2008}; \protect\hyperlink{ref-rech2016}{Rech \emph{et al.} 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}; \protect\hyperlink{ref-ruger2018}{Rüger \emph{et al.} 2018}).
+Linking the plant's position in trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations (\protect\hyperlink{ref-dehling2016}{Dehling \emph{et al.} 2016}).
+Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches (\protect\hyperlink{ref-fenster2004}{Fenster \emph{et al.} 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero \emph{et al.} 2014}) and trait-matching analyses (\protect\hyperlink{ref-stang2009}{Stang \emph{et al.} 2009}; \protect\hyperlink{ref-bartomeus2016}{Bartomeus \emph{et al.} 2016}).
+However, despite the generalist nature of most plant-pollinator interactions (\protect\hyperlink{ref-waser1996}{Waser \emph{et al.} 1996}; \protect\hyperlink{ref-olesen2002}{Olesen \& Jordano 2002}), reproductive traits have been overlooked beyond highly specialised pollination systems (\protect\hyperlink{ref-dellinger2020}{Dellinger 2020}).
+\textbf{Overall, it is unclear how specific plant reproductive biology traits shape plant-pollinator interactions (\protect\hyperlink{ref-tur2013}{Tur \emph{et al.} 2013}; \protect\hyperlink{ref-devaux2014}{Devaux \emph{et al.} 2014}).}
 
 Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY\textsuperscript{\protect\hyperlink{ref-kattge2011}{22}} and COMPADRE\textsuperscript{\protect\hyperlink{ref-salguero2015}{23}}), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function\textsuperscript{\protect\hyperlink{ref-salguero2016}{12},\protect\hyperlink{ref-diaz2016}{24}--\protect\hyperlink{ref-carmona2021}{26}}.
-However, most studies have focused on vegetative traits such as leaf\textsuperscript{\protect\hyperlink{ref-wright2004}{27}}, wood\textsuperscript{\protect\hyperlink{ref-chave2009}{28}}, or root\textsuperscript{\protect\hyperlink{ref-laughlin2021}{29}} trade-offs with little or no attention given to reproductive traits\textsuperscript{\protect\hyperlink{ref-roddy2021}{5},\protect\hyperlink{ref-evojtko2020}{30}} which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively,\textsuperscript{\protect\hyperlink{ref-moeller2017}{9},\protect\hyperlink{ref-barrett2003}{31}} and outcrossing levels are positively correlated with flower size\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{32}}.
-In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species' reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators\textsuperscript{\protect\hyperlink{ref-ollerton2011}{33},\protect\hyperlink{ref-rodger2021}{34}}.
+With the recent availability of large trait databases (e.g., TRY \protect\hyperlink{ref-kattge2011}{Kattge \emph{et al.}} (\protect\hyperlink{ref-kattge2011}{2011}) and COMPADRE \protect\hyperlink{ref-salguero2015}{Salguero-Gómez \emph{et al.}} (\protect\hyperlink{ref-salguero2015}{2015})), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function (\protect\hyperlink{ref-diaz2016}{Díaz \emph{et al.} 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}; \protect\hyperlink{ref-bruelheide2018}{Bruelheide \emph{et al.} 2018}; \protect\hyperlink{ref-carmona2021}{Carmona \emph{et al.} 2021}).
+However, most studies have focused on vegetative traits such as leaf (\protect\hyperlink{ref-wright2004}{Wright \emph{et al.} 2004}), wood (\protect\hyperlink{ref-chave2009}{Chave \emph{et al.} 2009}), or root (\protect\hyperlink{ref-laughlin2021}{Laughlin \emph{et al.} 2021}) trade-offs with little or no attention given to reproductive traits (\protect\hyperlink{ref-evojtko2020}{E-Vojtkó \emph{et al.} 2020}; \protect\hyperlink{ref-roddy2021}{Roddy \emph{et al.} 2021}) which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
+For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively, (\protect\hyperlink{ref-barrett2003}{Barrett 2003}; \protect\hyperlink{ref-moeller2017}{Moeller \emph{et al.} 2017}) and outcrossing levels are positively correlated with flower size (\protect\hyperlink{ref-goodwillie2010}{Goodwillie \emph{et al.} 2010}).
+In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species' reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators (\protect\hyperlink{ref-ollerton2011}{Ollerton \emph{et al.} 2011}; \protect\hyperlink{ref-rodger2021}{Rodger \emph{et al.} 2021}).
 However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.
 
-Several studies have identified links between plant traits and plant-pollinator network properties\textsuperscript{\protect\hyperlink{ref-bartomeus2013}{35}--\protect\hyperlink{ref-rowe2020}{37}}.
-Moreover, plant traits can define species' network roles (e.g., specialists vs generalists)\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-lazaro2013}{38}}.
-For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators\textsuperscript{\protect\hyperlink{ref-junker2013}{39},\protect\hyperlink{ref-coux2016}{40}}.
-Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-ibanez2012}{41}}.
-Remarkably, the combination of traits have shown to increase the predictive power of the network interactions\textsuperscript{\protect\hyperlink{ref-eklof2013}{42}}.
-Therefore, considering the different plant reproductive trade-offs which represent the species reproductive strategy within the network\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}} could progress our understanding of plant-pollinator interactions.
+Several studies have identified links between plant traits and plant-pollinator network properties (\protect\hyperlink{ref-bartomeus2013}{Bartomeus 2013}; \protect\hyperlink{ref-olito2015}{Olito \& Fox 2015}; \protect\hyperlink{ref-rowe2020}{Rowe \emph{et al.} 2020}).
+Moreover, plant traits can define species' network roles (e.g., specialists vs generalists) (\protect\hyperlink{ref-lazaro2013}{Lázaro \emph{et al.} 2013}; \protect\hyperlink{ref-tur2013}{Tur \emph{et al.} 2013}).
+For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators (\protect\hyperlink{ref-junker2013}{Junker \emph{et al.} 2013}; \protect\hyperlink{ref-coux2016}{Coux \emph{et al.} 2016}).
+Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure (\protect\hyperlink{ref-stang2009}{Stang \emph{et al.} 2009}; \protect\hyperlink{ref-ibanez2012}{Ibanez 2012}).
+Remarkably, the combination of traits have shown to increase the predictive power of the network interactions (\protect\hyperlink{ref-eklof2013}{Eklöf \emph{et al.} 2013}).
+\textbf{Therefore, considering the different plant reproductive trade-offs which represent the species reproductive strategy within the network (\protect\hyperlink{ref-dehling2016}{Dehling \emph{et al.} 2016}) could progress our understanding of plant-pollinator interactions}.
 Further, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.
@@
 
+\hypertarget{materials-and-methods}{%
+\section{MATERIALS AND METHODS}\label{materials-and-methods}}
+
+\textbf{Plant-pollinator network studies.} We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
+These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
+Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
+Many of these networks are freely available either as published studies (\protect\hyperlink{ref-olesen2007}{Olesen \emph{et al.} 2007}; \protect\hyperlink{ref-fortuna2010}{Fortuna \emph{et al.} 2010}; \protect\hyperlink{ref-carvalheiro2014}{Carvalheiro \emph{et al.} 2014}) or available in online archives (e.g., The Web of Life (\protect\hyperlink{ref-fortuna2010}{Fortuna \emph{et al.} 2010}) and Mangal (\protect\hyperlink{ref-poisot2016}{Poisot \emph{et al.} 2016})).
+In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+
+\textbf{Taxonomy of plants and pollinators.} All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain \emph{et al.} n.d.b}) version \emph{0.9.99}.
+We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
+
+\textbf{Functional traits.} We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
+These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive biology and 3 vegetative, Supplementary Information).
+For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
+From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8\% of the dataset, see Supplementary Fig.
+S1 for missing values information for each trait).
+
+\textbf{Phylogenetic Distance.} We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life (\protect\hyperlink{ref-smith2018}{Smith \& Brown 2018}; \protect\hyperlink{ref-jin2019}{Jin \& Qian 2019}).
+
+\singlespacing
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-1}\textbf{Table 1 | Quantitative and categorical traits used in this study.}}
+\centering
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{>{}cl>{}ccl}
+\toprule
+\multicolumn{2}{c}{\textbf{Quantitative traits}} & \multicolumn{3}{c}{\textbf{Categorical traits}} \\
+\cmidrule(l{3pt}r{3pt}){1-2} \cmidrule(l{3pt}r{3pt}){3-5}
+\textbf{Type} & \textbf{Traits} & \textbf{Type} & \textbf{Traits} & \textbf{Categories}\\
+\midrule
+\textbf{Vegetative} & Plant height (m) & \textbf{Vegetative} & Lifepan & \makecell[l]{Short-lived \\ Perennial}\\
+\addlinespace
+\textbf{Floral} & Flower width (mm) & \textbf{Vegetative} & Life form & \makecell[l]{Herb \\ Shrub \\ Tree}\\
+\addlinespace
+\textbf{Floral} & Flower length (mm) & \textbf{Floral} & Flower shape & \makecell[l]{Brush \\ Campanulate \\ Capitulum \\ Open \\ Papilionaceous \\ Tube}\\
+\addlinespace
+\textbf{Floral} & Inflorescence width (mm) & \textbf{Floral} & Flower symmetry & \makecell[l]{Actinomorphic \\ Zygomorphic}\\
+\addlinespace
+\textbf{Floral} & Style length (mm) & \textbf{Floral} & Nectar & \makecell[l]{Presence \\ Absence}\\
+\addlinespace
+\textbf{Floral} & Ovules per flower & \textbf{\makecell[c]{Reproductive \\ biology}} & Autonomous selfing & \makecell[l]{None \\ Low \\ Medium \\ High}\\
+\addlinespace
+\textbf{Floral} & Flowers per plant & \textbf{\makecell[c]{Reproductive \\ biology}} & Compatibility system & \makecell[l]{Self-incomp. \\ Part. self-comp. \\ Self-comp.}\\
+\addlinespace
+\textbf{Floral} & Nectar ($\mu$l) & \textbf{\makecell[c]{Reproductive \\ biology}} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious}\\
+\addlinespace
+\textbf{Floral} & Nectar (mg) & \textbf{} &  & \\
+\addlinespace
+\textbf{Floral} & Nectar concentration ($\%$) & \textbf{} &  & \\
+\addlinespace
+\textbf{Floral} & Pollen grains per flower & \textbf{} &  & \\
+\addlinespace
+\textbf{\makecell[c]{Reproductive \\ biology}} & Autonomous selfing (fruit set) & \textbf{} &  & \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\doublespacing
+
+\textbf{Data Imputation.} Trait missing values were imputed with the function \emph{missForest} (\protect\hyperlink{ref-stekhoven2012}{Stekhoven \& Bühlmann 2012}) which allows imputation of data sets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} (\protect\hyperlink{ref-penone2014}{Penone \emph{et al.} 2014}).
+To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} (\protect\hyperlink{ref-santos2018}{Chamberlain \emph{et al.} n.d.a}) based on a previous conceptual framework that considers phylogenetic eigenvectors (\protect\hyperlink{ref-diniz-filho2012}{Diniz-Filho \emph{et al.} 2012}).
+Although the variable of autonomous selfing had a high percentage of missing values (68\%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
+The categories of `none,' `low,' `medium' and `high' were converted to representative percentages of each category 0\%, 13\%, 50.5\% and 88\% respectively.
+This reduced the percentage of missing values for this column from 68\% to 35\% and allowed the imputation of this variable.
+However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Supplementary Fig.
+S1).
+Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79\% of missing values.
+Further, we conducted an additional imputation process on the subset of species with data for pollen per flower and microliters of nectar.
+This subset comprised 755 species, 8.01\% missing values and all traits but milligrams of nectar (\textasciitilde50\% of missing values) were included in the imputation process.
+
+\textbf{Plant strategies.} We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
+Prior to the analyses, we excluded outliers and standardized the data.
+Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th--97.5th percentile range (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre 2012}), and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell 2012}) (version \emph{0.7-70}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams 2010}).
+Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
+S2).
+We found little difference between the explained variance with the imputed dataset (51.08\%) and the dataset without missing values (52.87\%).
+In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
+Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
+For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
+
+\textbf{Phylogenetic signal of traits.} We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell 2012}) version \emph{0.7-70} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
+
+\textbf{Network analyses.} Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+These networks were analysed in their qualitative (presence-absence) and quantitative (interaction frequency) form.
+First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
+Second, we analysed the untransformed weighted networks with interaction frequency that accounts for the intensity of the interaction.
+Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency (\protect\hyperlink{ref-ballantyne2015}{Ballantyne \emph{et al.} 2015}), interaction frequency can provide valuable information of the contribution of floral visitors to pollination (\protect\hyperlink{ref-vazquez2005}{Vázquez \emph{et al.} 2005}, \protect\hyperlink{ref-vazquez2012}{2012}).
+In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
+Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
+All analyses were conducted in R version \emph{4.0.3}.
+
+\textbf{Visitation patterns.} We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
+For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
+Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total).
+This finding is consistent with previous research showing that \emph{A.
+mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems (\protect\hyperlink{ref-hung2018}{Hung \emph{et al.} 2018}).
+Hence, to control for the effect of \emph{A.
+mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of interaction and visitation rate excluding \emph{A.
+mellifera}.
+We found that \emph{A.
+mellifera}, was partly driving some of the observed trends on PC1 (Supplementary Fig.
+S3).
+However, we did not detect major differences on PC2 and PC3.
+
+We implemented Bayesian generalized linear mixed models using the R package \emph{brms} (\protect\hyperlink{ref-burkner2017}{Bürkner 2017}) (version \emph{2.14.6}).
+We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
+In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
+Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
+We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
+We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package (\protect\hyperlink{ref-gabry2019}{Gabry \emph{et al.} 2019}) (version \emph{1.7.2}).
+
+\textbf{Plant species functional roles.} We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies (\protect\hyperlink{ref-dormann2008}{Dormann \emph{et al.} 2008}) with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') (\protect\hyperlink{ref-bluthgen2006}{Blüthgen \emph{et al.} 2006}), which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} (\protect\hyperlink{ref-dormann2008}{Dormann \emph{et al.} 2008}) (version \emph{2.15}).
+
+First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
+For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
+Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns section.'
+
+Second, to better understand these complex trait relationships, we used regression trees.
+Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
+We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
+We conducted this analysis using the \emph{rpart} package (\protect\hyperlink{ref-therneau2015}{Therneau \emph{et al.} n.d.}) version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package (\protect\hyperlink{ref-milborrow2015}{Milborrow n.d.}) version \emph{3.0.9} to plot the regression trees.
+We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
+We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
+We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig.
+S4).
+
 \hypertarget{results}{%
@@
 The first principal component (PC1) represented 26.72\% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the `flower number - flower size trade-off', as already described in previous studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{43},\protect\hyperlink{ref-kettle2011}{44}}.
+We refer to this axis as the `flower number - flower size trade-off,' as already described in previous studies (\protect\hyperlink{ref-sargent2007}{Sargent \emph{et al.} 2007}; \protect\hyperlink{ref-kettle2011}{Kettle \emph{et al.} 2011}).
 Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
@@
 The second principal component (PC2) represented 25.05\% of the trait variation and indicated a trade-off between low and high pollinator dependence.
-We refer to this axis as the `pollinator dependence trade-off'.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Supplementary Table S3).
+We refer to this axis as the `pollinator dependence trade-off.' The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Supplementary Table S3).
 We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
@@
 The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Supplementary Table S3).
-Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the `style length trade-off'.
-Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 23.40\%); and pollen quantity (pollen grains per flower) was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 21.67\%; Supplementary Fig.
+Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the `style length trade-off.' Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 23.40\%); and pollen quantity (pollen grains per flower) was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 21.67\%; Supplementary Fig.
 S6).
@@
 
-{\centering \includegraphics{output/figures/unnamed-chunk-1-1}
+{\centering \includegraphics{output/figures/unnamed-chunk-2-1}
 
@@
 The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation.
-The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum.}\label{fig:unnamed-chunk-1}
+The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum.}\label{fig:unnamed-chunk-2}
 \end{figure}
@@
 \centering
-\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
-\caption{\label{fig:unnamed-chunk-2}\textbf{Fig.
+\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
+\caption{\label{fig:unnamed-chunk-3}\textbf{Fig.
 2 \textbar{} Location of the different qualitative traits on the trait space.} The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).}
@@
 \centering
-\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}\textbf{Fig.
+\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
+\caption{\label{fig:unnamed-chunk-4}\textbf{Fig.
 3 \textbar{} Interaction (yes/no) and visitation rates across the three main axes of trait variation per floral visitor guild.} Fitted posterior estimates of the presence/absence of interaction (a, b and c) and number of visits (d, e and f) made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
@@
 \centering
-\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\textbf{Fig.
+\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
+\caption{\label{fig:unnamed-chunk-5}\textbf{Fig.
 4 \textbar{} Contribution of traits in plant's network roles.} Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
@@
 Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
-Trait variation on these two axes was associated with the `fast-slow continuum' in plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}} and animal\textsuperscript{\protect\hyperlink{ref-healy2019}{45}} life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+Trait variation on these two axes was associated with the `fast-slow continuum' in plant (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}) and animal (\protect\hyperlink{ref-healy2019}{Healy \emph{et al.} 2019}) life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
 The `slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
 In contrast, plant species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{32}}.
+Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie \emph{et al.} 2010}).
 The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Supplementary Fig.
@@
 S6).
-This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently\textsuperscript{\protect\hyperlink{ref-lazaro2013}{38},\protect\hyperlink{ref-hegland2005}{46},\protect\hyperlink{ref-kaiser2014}{47}}.
+This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently (\protect\hyperlink{ref-hegland2005}{Hegland \& Totland 2005}; \protect\hyperlink{ref-lazaro2013}{Lázaro \emph{et al.} 2013}; \protect\hyperlink{ref-kaiser2014}{Kaiser-Bunbury \emph{et al.} 2014}).
 In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation rates across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
 For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
-3) suggesting possible niche partitioning\textsuperscript{\protect\hyperlink{ref-palmer2003}{48},\protect\hyperlink{ref-phillips2020}{49}} between these two guilds.
+3) suggesting possible niche partitioning (\protect\hyperlink{ref-palmer2003}{Palmer \emph{et al.} 2003}; \protect\hyperlink{ref-phillips2020}{Phillips \emph{et al.} 2020}) between these two guilds.
 However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species functional roles (Fig.
@@
 More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{17},\protect\hyperlink{ref-vazquez2007}{50},\protect\hyperlink{ref-encinas2012}{51}} that reproductive trade-offs do not.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability (\protect\hyperlink{ref-vazquez2007}{Vázquez \emph{et al.} 2007}; \protect\hyperlink{ref-encinas2012}{Encinas-Viso \emph{et al.} 2012}; \protect\hyperlink{ref-bartomeus2016}{Bartomeus \emph{et al.} 2016}) that reproductive trade-offs do not.
 
@@
 We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
-Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{26}} it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{12}}.
+Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits (\protect\hyperlink{ref-diaz2016}{Díaz \emph{et al.} 2016}; \protect\hyperlink{ref-carmona2021}{Carmona \emph{et al.} 2021}) it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}).
 Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
-Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators\textsuperscript{\protect\hyperlink{ref-gervasi2017}{52},\protect\hyperlink{ref-mackin2021}{53}}.
+Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators (\protect\hyperlink{ref-gervasi2017}{Gervasi \& Schiestl 2017}; \protect\hyperlink{ref-mackin2021}{Mackin \emph{et al.} 2021}).
 Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
-
-\hypertarget{materials-and-methods}{%
-\section{MATERIALS AND METHODS}\label{materials-and-methods}}
-
-\textbf{Plant-pollinator network studies.} We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies\textsuperscript{\protect\hyperlink{ref-olesen2007}{54}--\protect\hyperlink{ref-carvalheiro2014}{56}} or available in online archives (e.g., The Web of Life\textsuperscript{\protect\hyperlink{ref-fortuna2010}{55}} and Mangal\textsuperscript{\protect\hyperlink{ref-poisot2016}{57}}).
-In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
-
-\textbf{Taxonomy of plants and pollinators.} All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize}\textsuperscript{\protect\hyperlink{ref-chamberlain2020}{58}} version \emph{0.9.99}.
-We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
-
-\textbf{Functional traits.} We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
-These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive biology and 3 vegetative, Supplementary Information).
-For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8\% of the dataset, see Supplementary Fig.
-S1 for missing values information for each trait).
-
-\textbf{Phylogenetic Distance.} We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life\textsuperscript{\protect\hyperlink{ref-smith2018}{59},\protect\hyperlink{ref-jin2019}{60}}.
-
-\singlespacing
-
-\begin{table}
-
-\caption{\label{tab:unnamed-chunk-5}\textbf{Table 1 | Quantitative and categorical traits used in this study.}}
-\centering
-\fontsize{10}{12}\selectfont
-\begin{tabular}[t]{>{}cl>{}ccl}
-\toprule
-\multicolumn{2}{c}{\textbf{Quantitative traits}} & \multicolumn{3}{c}{\textbf{Categorical traits}} \\
-\cmidrule(l{3pt}r{3pt}){1-2} \cmidrule(l{3pt}r{3pt}){3-5}
-\textbf{Type} & \textbf{Traits} & \textbf{Type} & \textbf{Traits} & \textbf{Categories}\\
-\midrule
-\textbf{Vegetative} & Plant height (m) & \textbf{Vegetative} & Lifepan & \makecell[l]{Short-lived \\ Perennial}\\
-\addlinespace
-\textbf{Floral} & Flower width (mm) & \textbf{Vegetative} & Life form & \makecell[l]{Herb \\ Shrub \\ Tree}\\
-\addlinespace
-\textbf{Floral} & Flower length (mm) & \textbf{Floral} & Flower shape & \makecell[l]{Brush \\ Campanulate \\ Capitulum \\ Open \\ Papilionaceous \\ Tube}\\
-\addlinespace
-\textbf{Floral} & Inflorescence width (mm) & \textbf{Floral} & Flower symmetry & \makecell[l]{Actinomorphic \\ Zygomorphic}\\
-\addlinespace
-\textbf{Floral} & Style length (mm) & \textbf{Floral} & Nectar & \makecell[l]{Presence \\ Absence}\\
-\addlinespace
-\textbf{Floral} & Ovules per flower & \textbf{\makecell[c]{Reproductive \\ biology}} & Autonomous selfing & \makecell[l]{None \\ Low \\ Medium \\ High}\\
-\addlinespace
-\textbf{Floral} & Flowers per plant & \textbf{\makecell[c]{Reproductive \\ biology}} & Compatibility system & \makecell[l]{Self-incomp. \\ Part. self-comp. \\ Self-comp.}\\
-\addlinespace
-\textbf{Floral} & Nectar ($\mu$l) & \textbf{\makecell[c]{Reproductive \\ biology}} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious}\\
-\addlinespace
-\textbf{Floral} & Nectar (mg) & \textbf{} &  & \\
-\addlinespace
-\textbf{Floral} & Nectar concentration ($\%$) & \textbf{} &  & \\
-\addlinespace
-\textbf{Floral} & Pollen grains per flower & \textbf{} &  & \\
-\addlinespace
-\textbf{\makecell[c]{Reproductive \\ biology}} & Autonomous selfing (fruit set) & \textbf{} &  & \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\doublespacing
-
-\textbf{Data Imputation.} Trait missing values were imputed with the function \emph{missForest}\textsuperscript{\protect\hyperlink{ref-stekhoven2012}{61}} which allows imputation of data sets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest}\textsuperscript{\protect\hyperlink{ref-penone2014}{62}}.
-To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR}\textsuperscript{\protect\hyperlink{ref-santos2018}{63}} based on a previous conceptual framework that considers phylogenetic eigenvectors\textsuperscript{\protect\hyperlink{ref-diniz-filho2012}{64}}.
-Although the variable of autonomous selfing had a high percentage of missing values (68\%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
-The categories of `none', `low', `medium' and `high' were converted to representative percentages of each category 0\%, 13\%, 50.5\% and 88\% respectively.
-This reduced the percentage of missing values for this column from 68\% to 35\% and allowed the imputation of this variable.
-However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Supplementary Fig.
-S1).
-Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79\% of missing values.
-Further, we conducted an additional imputation process on the subset of species with data for pollen per flower and microliters of nectar.
-This subset comprised 755 species, 8.01\% missing values and all traits but milligrams of nectar (\textasciitilde50\% of missing values) were included in the imputation process.
-
-\textbf{Plant strategies.} We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th--97.5th percentile range\textsuperscript{\protect\hyperlink{ref-legendre2012}{65}}, and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools}\textsuperscript{\protect\hyperlink{ref-revell2012}{66}} (version \emph{0.7-70}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation\textsuperscript{\protect\hyperlink{ref-abdi2010}{67}}.
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
-S2).
-We found little difference between the explained variance with the imputed dataset (51.08\%) and the dataset without missing values (52.87\%).
-In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
-For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
-
-\textbf{Phylogenetic signal of traits.} We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools}\textsuperscript{\protect\hyperlink{ref-revell2012}{66}} version \emph{0.7-70} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-\textbf{Network analyses.} Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-These networks were analysed in their qualitative (presence-absence) and quantitative (interaction frequency) form.
-First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
-Second, we analysed the untransformed weighted networks with interaction frequency that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{68}}, interaction frequency can provide valuable information of the contribution of floral visitors to pollination\textsuperscript{\protect\hyperlink{ref-vazquez2005}{69},\protect\hyperlink{ref-vazquez2012}{70}}.
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
-All analyses were conducted in R version \emph{4.0.3}.
-
-\textbf{Visitation patterns.} We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total).
-This finding is consistent with previous research showing that \emph{A.
-mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems\textsuperscript{\protect\hyperlink{ref-hung2018}{71}}.
-Hence, to control for the effect of \emph{A.
-mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of interaction and visitation rate excluding \emph{A.
-mellifera}.
-We found that \emph{A.
-mellifera}, was partly driving some of the observed trends on PC1 (Supplementary Fig.
-S3).
-However, we did not detect major differences on PC2 and PC3.
-
-We implemented Bayesian generalized linear mixed models using the R package \emph{brms}\textsuperscript{\protect\hyperlink{ref-burkner2017}{72}} (version \emph{2.14.6}).
-We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
-In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
-We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package\textsuperscript{\protect\hyperlink{ref-gabry2019}{73}} (version \emph{1.7.2}).
-
-\textbf{Plant species functional roles.} We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies\textsuperscript{\protect\hyperlink{ref-dormann2008}{74}} with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d')\textsuperscript{\protect\hyperlink{ref-bluthgen2006}{75}}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite}\textsuperscript{\protect\hyperlink{ref-dormann2008}{74}} (version \emph{2.15}).
-
-First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
-For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns section'.
-
-Second, to better understand these complex trait relationships, we used regression trees.
-Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
-We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
-We conducted this analysis using the \emph{rpart} package\textsuperscript{\protect\hyperlink{ref-therneau2015}{76}} version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package\textsuperscript{\protect\hyperlink{ref-milborrow2015}{77}} version \emph{3.0.9} to plot the regression trees.
-We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
-We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig.
-S4).
 
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
+Abdi, H. \& Williams, L.J. (2010). Principal component analysis. \emph{WIREs Comp. Stats.}, 2, 433--459.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
+Ballantyne, G., Baldock, K.C.R.
+\& Willmer, P.G.
+(2015).
+Constructing more informative plant\textendash pollinator networks: Visitation and pollen deposition networks in a heathland plant community.
+\emph{Proc.
+Royal Soc.
+B}, 282, 20151130.
+
 \leavevmode\vadjust pre{\hypertarget{ref-barrett2002}{}}%
-\CSLLeftMargin{1. }
-\CSLRightInline{Barrett, S. C. H. The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.} \textbf{3}, 274--284 (2002).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schiestl2013}{}}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Schiestl, F. P. \& Johnson, S. D. Pollinator-mediated evolution of floral signals. \emph{Trends Ecol. Evol.} \textbf{28}, 307--315 (2013).}
+Barrett, S.C.H. (2002). The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.}, 3, 274--284.
+
+\leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
+Barrett, S.C.H. (2003). Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond. \emph{Philos. Trans. R. Soc. Lond. B Biol. Sci.}, 358, 991--1004.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2013}{}}%
+Bartomeus, I.
+(2013).
+Understanding {Linkage Rules} in {Plant}-{Pollinator Networks} by {Using Hierarchical Models That Incorporate Pollinator Detectability} and {Plant Traits}.
+\emph{PLoS One}, 8, e69200.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
+Bartomeus, I., Gravel, D., Tylianakis, J.M., Aizen, M.A., Dickie, I.A.
+\& Bernard-Verdier, M.
+(2016).
+A common framework for identifying linkage rules across different types of interactions.
+\emph{Funct.
+Ecol.}, 30, 1894--1903.
+
+\leavevmode\vadjust pre{\hypertarget{ref-baude2016}{}}%
+Baude, M., Kunin, W.E., Boatman, N.D., Conyers, S., Davies, N., Gillespie, M.A., \emph{et al.} (2016).
+Historical nectar assessment reveals the fall and rise of floral resources in britain.
+\emph{Nature}, 530, 85--88.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
+Blüthgen, N., Menzel, F. \& Blüthgen, N. (2006). Measuring specialization in species interaction networks. \emph{BMC Ecol.}, 6, 9.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
+Bruelheide, H., Dengler, J., Purschke, O., Lenoir, J., Jiménez-Alfaro, B., Hennekens, S.M., \emph{et al.} (2018).
+Global trait--environment relationships of plant communities.
+\emph{Nat.
+Ecol.
+Evol.}, 2, 1906--1917.
+
+\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
+Bürkner, P.-C. (2017). Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.}, 80, 1--28.
+
+\leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
+Carmona, C.P., Tamme, R., Pärtel, M., Bello, F. de, Brosse, S., Capdevila, P., \emph{et al.} (2021). Erosion of global functional diversity across the tree of life. \emph{Sci. Adv.}, 7, eabf2675.
+
+\leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
+Carvalheiro, L.G., Biesmeijer, J.C., Benadi, G., Fründ, J., Stang, M., Bartomeus, I., \emph{et al.} (2014).
+The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
+\emph{Ecol.
+Lett.}, 17, 1389--1399.
+
+\leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
+Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., \emph{et al.} (n.d.a).
+Package {`{PVR}.'} R package version 0.3 (2018).~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
+Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., \emph{et al.} (n.d.b).
+Taxize: {Taxonomic} information from around the web.
+R package version 0.9.99 (2020).~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
+Chave, J., Coomes, D., Jansen, S., Lewis, S.L., Swenson, N.G. \& Zanne, A.E. (2009). Towards a worldwide wood economics spectrum. \emph{Ecol. Lett.}, 12, 351--366.
+
+\leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
+Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J.M. (2016). Linking species functional roles to their network roles. \emph{Ecol. Lett.}, 19, 762--770.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
+Dehling, D.M., Jordano, P., Schaefer, H.M., Böhning-Gaese, K.
+\& Schleuning, M.
+(2016).
+Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
+\emph{Proc.
+Royal Soc.
+B}, 283, 20152444.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dellinger2020}{}}%
+Dellinger, A.S. (2020). Pollination syndromes in the 21st century: Where do we stand and where may we go? \emph{New Phytol.}, 228, 1193--1213.
+
+\leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
+Devaux, C., Lepers, C. \& Porcher, E. (2014). Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems. \emph{J. Evol. Biol.}, 27, 1413--1430.
+
+\leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
+Díaz, S., Kattge, J., Cornelissen, J.H.C., Wright, I.J., Lavorel, S., Dray, S., \emph{et al.} (2016). The global spectrum of plant form and function. \emph{Nature}, 529, 167--171.
+
+\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
+Diniz-Filho, J.A.F., Bini, L.M., Rangel, T.F., Morales-Castilla, I., Olalla-Tárraga, M.Á., Rodríguez, M.Á., \emph{et al.} (2012).
+On the selection of phylogenetic eigenvectors for ecological analyses.
+\emph{Ecography}, 35, 239--249.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
+Dormann, C.F., Gruber, B. \& Fründ, J. (2008). Introducing the bipartite package: Analysing ecological networks. \emph{R News}, 8/2.
+
+\leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
+Eklöf, A., Jacob, U., Kopp, J., Bosch, J., Castro-Urgal, R., Chacoff, N.P., \emph{et al.} (2013). The dimensionality of ecological networks. \emph{Ecol. Lett.}, 16, 577--583.
+
+\leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
+Encinas-Viso, F., Revilla, T.A. \& Etienne, R.S. (2012). Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.}, 15, 198--208.
+
+\leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
+E-Vojtkó, A., Bello, F. de, Durka, W., Kühn, I. \& Götzenberger, L. (2020). The neglected importance of floral traits in trait-based plant community assembly. \emph{J. Veg. Sci.}, 31, 529--539.
 
 \leavevmode\vadjust pre{\hypertarget{ref-fenster2004}{}}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Fenster, C.
-B., Armbruster, W.
-S., Wilson, P., Dudash, M.
-R.
-\& Thomson, J.
-D.
-Pollination {Syndromes} and {Floral Specialization}.
-\emph{Annu.
-Rev.
+Fenster, C.B., Armbruster, W.S., Wilson, P., Dudash, M.R. \& Thomson, J.D. (2004). Pollination {Syndromes} and {Floral Specialization}. \emph{Annu. Rev. Ecol. Evol. Syst.}, 35, 375--403.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
+Fortuna, M.A., Stouffer, D.B., Olesen, J.M., Jordano, P., Mouillot, D., Krasnov, B.R., \emph{et al.} (2010).
+Nestedness versus modularity in ecological networks: Two sides of the same coin?
+\emph{J.
+Anim.
+Ecol.}, 79, 811--817.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
+Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A. (2019). Visualization in {Bayesian} workflow. \emph{J. R. Stat. Soc. Ser. A Stat. Soc.}, 182, 389--402.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gervasi2017}{}}%
+Gervasi, D.D.L. \& Schiestl, F.P. (2017). Real-time divergent evolution in plants driven by pollinators. \emph{Nat. Commun.}, 8, 14691.
+
+\leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
+Goodwillie, C., Sargent, R.D., Eckert, C.G., Elle, E., Geber, M.A., Johnston, M.O., \emph{et al.} (2010).
+Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
+\emph{New Phytol.}, 185, 311--321.
+
+\leavevmode\vadjust pre{\hypertarget{ref-grossenbacher2017}{}}%
+Grossenbacher, D.L., Brandvain, Y., Auld, J.R., Burd, M., Cheptou, P.-O., Conner, J.K., \emph{et al.} (2017). Self-compatibility is over-represented on islands. \emph{New Phytol.}, 215, 469--478.
+
+\leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
+Healy, K., Ezard, T.H.G., Jones, O.R., Salguero-Gómez, R.
+\& Buckley, Y.M.
+(2019).
+Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
+\emph{Nat.
 Ecol.
-Evol.
-Syst.} \textbf{35}, 375--403 (2004).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dellinger2020}{}}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Dellinger, A. S. Pollination syndromes in the 21st century: Where do we stand and where may we go? \emph{New Phytol.} \textbf{228}, 1193--1213 (2020).}
+Evol.}, 3, 1217--1224.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
+Hegland, S.J. \& Totland, Ø. (2005). Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia}, 145, 586--594.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
+Hung, K.-L.J., Kingston, J.M., Albrecht, M., Holway, D.A. \& Kohn, J.R. (2018). The worldwide importance of honey bees as pollinators in natural habitats. \emph{Proc. Royal Soc. B}, 285, 20172140.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
+Ibanez, S. (2012). Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks. \emph{Oecologia}, 170, 233--242.
+
+\leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
+Jin, Y. \& Qian, H. (2019). V.{PhyloMaker}: An {R} package that can generate very large phylogenies for vascular plants. \emph{Ecography}, 42, 1353--1359.
+
+\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
+Junker, R.R., Blüthgen, N., Brehm, T., Binkenstein, J., Paulus, J., Schaefer, H.M., \emph{et al.} (2013).
+Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
+\emph{Funct.
+Ecol.}, 27, 329--341.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
+Kaiser-Bunbury, C.N., Vázquez, D.P., Stang, M. \& Ghazoul, J. (2014). Determinants of the microstructure of plant\textendash pollinator networks. \emph{Ecology}, 95, 3314--3324.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
+Kattge, J., Díaz, S., Lavorel, S., Prentice, I.C., Leadley, P., Bönisch, G., \emph{et al.} (2011). {TRY} \textendash{} a global database of plant traits. \emph{Glob. Chang. Biol.}, 17, 2905--2935.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
+Kettle, C.J., Maycock, C.R., Ghazoul, J., Hollingsworth, P.M., Khoo, E., Sukri, R.S.H., \emph{et al.} (2011).
+Ecological {Implications} of a {Flower Size}/{Number Trade}-{Off} in {Tropical Forest Trees}.
+\emph{PLoS One}, 6, e16111.
+
+\leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
+Laughlin, D.C., Mommer, L., Sabatini, F.M., Bruelheide, H., Kuyper, T.W., McCormack, M.L., \emph{et al.} (2021).
+Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
+\emph{Nat.
+Ecol.
+Evol.}, 1--12.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
+Lázaro, A., Jakobsson, A. \& Totland, Ø. (2013). How do pollinator visitation rate and seed set relate to species' floral traits and community context? \emph{Oecologia}, 173, 881--893.
+
+\leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
+Legendre, P. \& Legendre, L. (2012). \emph{Numerical ecology}. {2nd edn}. {Elsevier, Amsterdam}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mackin2021}{}}%
+Mackin, C.R., Peña, J.F., Blanco, M.A., Balfour, N.J. \& Castellanos, M.C. (2021). Rapid evolution of a floral trait following acquisition of novel pollinators. \emph{J. Ecol.}, 109, 2234--2246.
+
+\leavevmode\vadjust pre{\hypertarget{ref-milborrow2015}{}}%
+Milborrow, S.
+(n.d.).
+Rpart.
+Plot: {Plot} rpart {Models}.
+{An Enhanced Version} of plot.
+Rpart.
+R package version 3.0.9 (2015).~At \href{https://CRAN.R-project.org/package=rpart.plot}{https://CRAN.r-project.org/package=rpart.plot}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
+Moeller, D.A., Runquist, R.D.B., Moe, A.M., Geber, M.A., Goodwillie, C., Cheptou, P.-O., \emph{et al.} (2017).
+Global biogeography of mating system variation in seed plants.
+\emph{Ecol.
+Lett.}, 20, 375--384.
+
+\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
+Munoz, F., Violle, C.
+\& Cheptou, P.-O.
+(2016).
+{CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
+\emph{Oikos}, 125, 1296--1303.
+
+\leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
+Olesen, J.M., Bascompte, J., Dupont, Y.L. \& Jordano, P. (2007). The modularity of pollination networks. \emph{PNAS}, 104, 19891--19896.
+
+\leavevmode\vadjust pre{\hypertarget{ref-olesen2002}{}}%
+Olesen, J.M. \& Jordano, P. (2002). Geographic patterns in plant--pollinator mutualistic networks. \emph{Ecology}, 83, 2416--2424.
+
+\leavevmode\vadjust pre{\hypertarget{ref-olito2015}{}}%
+Olito, C. \& Fox, J.W. (2015). Species traits and abundances predict metrics of plant\textendash pollinator network structure, but not pairwise interactions. \emph{Oikos}, 124, 428--436.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ollerton2011}{}}%
+Ollerton, J., Winfree, R. \& Tarrant, S. (2011). How many flowering plants are pollinated by animals? \emph{Oikos}, 120, 321--326.
+
+\leavevmode\vadjust pre{\hypertarget{ref-palmer2003}{}}%
+Palmer, T.M., Stanton, M.L. \& Young, T.P. (2003). Competition and coexistence: Exploring mechanisms that restrict and maintain diversity within mutualist guilds. \emph{Am. Nat.}, 162, S63--S79.
+
+\leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
+Penone, C., Davidson, A.D., Shoemaker, K.T., Marco, M.D., Rondinini, C., Brooks, T.M., \emph{et al.} (2014).
+Imputation of missing data in life-history trait datasets: Which approach performs the best?
+\emph{Methods Ecol.
+Evol.}, 5, 961--970.
+
+\leavevmode\vadjust pre{\hypertarget{ref-phillips2020}{}}%
+Phillips, R.D., Peakall, R., van der Niet, T. \& Johnson, S.D. (2020). Niche perspectives on plant\textendash pollinator interactions. \emph{Trends Plant Sci.}, 25, 779--793.
+
+\leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
+Poisot, T., Baiser, B., Dunne, J.A., Kéfi, S., Massol, F., Mouquet, N., \emph{et al.} (2016). Mangal \textendash{} making ecological network analysis simple. \emph{Ecography}, 39, 384--390.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rech2016}{}}%
+Rech, A.R., Dalsgaard, B., Sandel, B., Sonne, J., Svenning, J.-C., Holmes, N., \emph{et al.} (2016).
+The macroecology of animal versus wind pollination: Ecological factors are more important than historical climate stability.
+\emph{Plant Ecol.
+Divers.}, 9, 253--262.
+
+\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
+Revell, L.J. (2012). Phytools: An {R} package for phylogenetic comparative biology (and other things). \emph{Methods Ecol. Evol.}, 3, 217--223.
 
 \leavevmode\vadjust pre{\hypertarget{ref-roddy2021}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Roddy, A. B. \emph{et al.} Towards the flower economics spectrum. \emph{New Phytol.} \textbf{229}, 665--672 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-baude2016}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{Baude, M. \emph{et al.} Historical nectar assessment reveals the fall and rise of floral resources in britain. \emph{Nature} \textbf{530}, 85--88 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{Munoz, F., Violle, C.
-\& Cheptou, P.-O.
-{CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
-\emph{Oikos} \textbf{125}, 1296--1303 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-grossenbacher2017}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Grossenbacher, D. L. \emph{et al.} Self-compatibility is over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Moeller, D. A. \emph{et al.} Global biogeography of mating system variation in seed plants. \emph{Ecol. Lett.} \textbf{20}, 375--384 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{Sargent, R. D. \& Ackerly, D. D. Plant--pollinator interactions and the assembly of plant communities. \emph{Trends Ecol. Evol.} \textbf{23}, 123--130 (2008).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rech2016}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{Rech, A.
-R.
-\emph{et al.} The macroecology of animal versus wind pollination: Ecological factors are more important than historical climate stability.
-\emph{Plant Ecol.
-Divers.} \textbf{9}, 253--262 (2016).}
+Roddy, A.B., Martínez-Perez, C., Teixido, A.L., Cornelissen, T.G., Olson, M.E., Oliveira, R.S., \emph{et al.} (2021). Towards the flower economics spectrum. \emph{New Phytol.}, 229, 665--672.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rodger2021}{}}%
+Rodger, J.G., Bennett, J.M., Razanajatovo, M., Knight, T.M., Kleunen, M.
+van, Ashman, T.-L., \emph{et al.} (2021).
+Widespread vulnerability of flowering plant seed production to pollinator declines.
+\emph{Sci.
+Adv.}, 7, eabd3524.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
+Rosas-Guerrero, V., Aguilar, R., Martén-Rodríguez, S., Ashworth, L., Lopezaraiza-Mikel, M., Bastida, J.M., \emph{et al.} (2014).
+A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
+\emph{Ecol.
+Lett.}, 17, 388--400.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rowe2020}{}}%
+Rowe, L., Gibson, D., Bahlai, C.A., Gibbs, J., Landis, D.A. \& Isaacs, R. (2020). Flower traits associated with the visitation patterns of bees. \emph{Oecologia}, 193, 511--522.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
+Rüger, N., Comita, L.S., Condit, R., Purves, D., Rosenbaum, B., Visser, M.D., \emph{et al.} (2018).
+Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
+\emph{Ecol.
+Lett.}, 21, 1075--1084.
+
+\leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
+Salguero-Gómez, R., Jones, O.R., Archer, C.R., Buckley, Y.M., Che-Castaldo, J., Caswell, H., \emph{et al.} (2015).
+The compadre {Plant Matrix Database}: An open online repository for plant demography.
+\emph{J.
+Ecol.}, 103, 202--218.
 
 \leavevmode\vadjust pre{\hypertarget{ref-salguero2016}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Salguero-Gómez, R.
-\emph{et al.} Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
+Salguero-Gómez, R., Jones, O.R., Jongejans, E., Blomberg, S.P., Hodgson, D.J., Mbeau-Ache, C., \emph{et al.} (2016).
+Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
 \emph{Proc.
@@
 Sci.
-U.S.A.} \textbf{113}, 230--235 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Rüger, N. \emph{et al.} Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community. \emph{Ecol. Lett.} \textbf{21}, 1075--1084 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Dehling, D.
-M., Jordano, P., Schaefer, H.
-M., Böhning-Gaese, K.
-\& Schleuning, M.
-Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
-\emph{Proc.
-Royal Soc.
-B} \textbf{283}, 20152444 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Rosas-Guerrero, V. \emph{et al.} A quantitative review of pollination syndromes: Do floral traits predict effective pollinators? \emph{Ecol. Lett.} \textbf{17}, 388--400 (2014).}
+U.S.A.}, 113, 230--235.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
+Sargent, R.D. \& Ackerly, D.D. (2008). Plant--pollinator interactions and the assembly of plant communities. \emph{Trends Ecol. Evol.}, 23, 123--130.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
+Sargent, R.D., Goodwillie, C., Kalisz, S. \& Ree, R.H. (2007). Phylogenetic evidence for a flower size and number trade-off. \emph{Am. J. Bot.}, 94, 2059--2062.
+
+\leavevmode\vadjust pre{\hypertarget{ref-schiestl2013}{}}%
+Schiestl, F.P. \& Johnson, S.D. (2013). Pollinator-mediated evolution of floral signals. \emph{Trends Ecol. Evol.}, 28, 307--315.
+
+\leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
+Smith, S.A. \& Brown, J.W. (2018). Constructing a broadly inclusive seed plant phylogeny. \emph{Am. J. Bot.}, 105, 302--314.
 
 \leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Stang, M., Klinkhamer, P.
-G.
-L., Waser, N.
-M., Stang, I.
+Stang, M., Klinkhamer, P.G.L., Waser, N.M., Stang, I.
 \& van der Meijden, E.
+(2009).
 Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
 \emph{Ann.
-Bot.} \textbf{103}, 1459--1469 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{Bartomeus, I. \emph{et al.} A common framework for identifying linkage rules across different types of interactions. \emph{Funct. Ecol.} \textbf{30}, 1894--1903 (2016).}
+Bot.}, 103, 1459--1469.
+
+\leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
+Stekhoven, D.J. \& Bühlmann, P. (2012). {MissForest}\textemdash non-parametric missing value imputation for mixed-type data. \emph{Bioinformatics}, 28, 112--118.
+
+\leavevmode\vadjust pre{\hypertarget{ref-therneau2015}{}}%
+Therneau, T., Atkinson, B., Ripley, B.
+\& Ripley, M.B.
+(n.d.).
+Package {`rpart.'} R package version 4.1-15 (2015).~At \href{https://CRAN.R-project.org/package=rpart}{https://CRAN.r-project.org/package=rpart}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
+Tur, C., Castro-Urgal, R. \& Traveset, A. (2013). Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}. \emph{PLoS One}, 8, e78294.
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
+Vázquez, D.P., Lomáscolo, S.B., Maldonado, M.B., Chacoff, N.P., Dorado, J., Stevani, E.L., \emph{et al.} (2012). The strength of plant\textendash pollinator interactions. \emph{Ecology}, 93, 719--725.
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
+Vázquez, D.P., Melián, C.J., Williams, N.M., Blüthgen, N., Krasnov, B.R.
+\& Poulin, R.
+(2007).
+Species abundance and asymmetric interaction strength in ecological networks.
+\emph{Oikos}, 116, 1120--1127.
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
+Vázquez, D.P., Morris, W.F. \& Jordano, P. (2005). Interaction frequency as a surrogate for the total effect of animal mutualists on plants. \emph{Ecol. Lett.}, 8, 1088--1094.
 
 \leavevmode\vadjust pre{\hypertarget{ref-waser1996}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Waser, N. M., Chittka, L., Price, M. V., Williams, N. M. \& Ollerton, J. Generalization in pollination systems, and why it matters. \emph{Ecology} \textbf{77}, 1043--1060 (1996).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-olesen2002}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Olesen, J. M. \& Jordano, P. Geographic patterns in plant--pollinator mutualistic networks. \emph{Ecology} \textbf{83}, 2416--2424 (2002).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Tur, C., Castro-Urgal, R.
-\& Traveset, A.
-Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}.
-\emph{PLoS One} \textbf{8}, e78294 (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Devaux, C., Lepers, C.
-\& Porcher, E.
-Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems.
-\emph{J.
-Evol.
-Biol.} \textbf{27}, 1413--1430 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{Kattge, J. \emph{et al.} {TRY} \textendash{} a global database of plant traits. \emph{Glob. Chang. Biol.} \textbf{17}, 2905--2935 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Salguero-Gómez, R. \emph{et al.} The compadre {Plant Matrix Database}: An open online repository for plant demography. \emph{J. Ecol.} \textbf{103}, 202--218 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{Díaz, S. \emph{et al.} The global spectrum of plant form and function. \emph{Nature} \textbf{529}, 167--171 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Bruelheide, H. \emph{et al.} Global trait--environment relationships of plant communities. \emph{Nat. Ecol. Evol.} \textbf{2}, 1906--1917 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Carmona, C. P. \emph{et al.} Erosion of global functional diversity across the tree of life. \emph{Sci. Adv.} \textbf{7}, eabf2675 (2021).}
+Waser, N.M., Chittka, L., Price, M.V., Williams, N.M. \& Ollerton, J. (1996). Generalization in pollination systems, and why it matters. \emph{Ecology}, 77, 1043--1060.
 
 \leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Wright, I. J. \emph{et al.} The worldwide leaf economics spectrum. \emph{Nature} \textbf{428}, 821--827 (2004).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{Chave, J. \emph{et al.} Towards a worldwide wood economics spectrum. \emph{Ecol. Lett.} \textbf{12}, 351--366 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{Laughlin, D.
-C.
-\emph{et al.} Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
-\emph{Nat.
-Ecol.
-Evol.} 1--12 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{E-Vojtkó, A., Bello, F.
-de, Durka, W., Kühn, I.
-\& Götzenberger, L.
-The neglected importance of floral traits in trait-based plant community assembly.
-\emph{J.
-Veg.
-Sci.} \textbf{31}, 529--539 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Barrett, S. C. H. Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond. \emph{Philos. Trans. R. Soc. Lond. B Biol. Sci.} \textbf{358}, 991--1004 (2003).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Goodwillie, C.
-\emph{et al.} Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
-\emph{New Phytol.} \textbf{185}, 311--321 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ollerton2011}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{Ollerton, J., Winfree, R. \& Tarrant, S. How many flowering plants are pollinated by animals? \emph{Oikos} \textbf{120}, 321--326 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rodger2021}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{Rodger, J. G. \emph{et al.} Widespread vulnerability of flowering plant seed production to pollinator declines. \emph{Sci. Adv.} \textbf{7}, eabd3524 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2013}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Bartomeus, I.
-Understanding {Linkage Rules} in {Plant}-{Pollinator Networks} by {Using Hierarchical Models That Incorporate Pollinator Detectability} and {Plant Traits}.
-\emph{PLoS One} \textbf{8}, e69200 (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-olito2015}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Olito, C.
-\& Fox, J.
-W.
-Species traits and abundances predict metrics of plant\textendash pollinator network structure, but not pairwise interactions.
-\emph{Oikos} \textbf{124}, 428--436 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rowe2020}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Rowe, L. \emph{et al.} Flower traits associated with the visitation patterns of bees. \emph{Oecologia} \textbf{193}, 511--522 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{Lázaro, A., Jakobsson, A.
-\& Totland, Ø.
-How do pollinator visitation rate and seed set relate to species' floral traits and community context?
-\emph{Oecologia} \textbf{173}, 881--893 (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Junker, R.
-R.
-\emph{et al.} Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
-\emph{Funct.
-Ecol.} \textbf{27}, 329--341 (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
-\CSLLeftMargin{40. }
-\CSLRightInline{Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking species functional roles to their network roles. \emph{Ecol. Lett.} \textbf{19}, 762--770 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Ibanez, S.
-Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks.
-\emph{Oecologia} \textbf{170}, 233--242 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
-\CSLLeftMargin{42. }
-\CSLRightInline{Eklöf, A. \emph{et al.} The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583 (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
-\CSLLeftMargin{43. }
-\CSLRightInline{Sargent, R. D., Goodwillie, C., Kalisz, S. \& Ree, R. H. Phylogenetic evidence for a flower size and number trade-off. \emph{Am. J. Bot.} \textbf{94}, 2059--2062 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Kettle, C. J. \emph{et al.} Ecological {Implications} of a {Flower Size}/{Number Trade}-{Off} in {Tropical Forest Trees}. \emph{PLoS One} \textbf{6}, e16111 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
-\CSLLeftMargin{45. }
-\CSLRightInline{Healy, K., Ezard, T.
-H.
-G., Jones, O.
-R., Salguero-Gómez, R.
-\& Buckley, Y.
-M.
-Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
-\emph{Nat.
-Ecol.
-Evol.} \textbf{3}, 1217--1224 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
-\CSLLeftMargin{46. }
-\CSLRightInline{Hegland, S. J. \& Totland, Ø. Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia} \textbf{145}, 586--594 (2005).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Kaiser-Bunbury, C.
-N., Vázquez, D.
-P., Stang, M.
-\& Ghazoul, J.
-Determinants of the microstructure of plant\textendash pollinator networks.
-\emph{Ecology} \textbf{95}, 3314--3324 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-palmer2003}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Palmer, T.
-M., Stanton, M.
-L.
-\& Young, T.
-P.
-Competition and coexistence: Exploring mechanisms that restrict and maintain diversity within mutualist guilds.
-\emph{Am.
-Nat.} \textbf{162}, S63--S79 (2003).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-phillips2020}{}}%
-\CSLLeftMargin{49. }
-\CSLRightInline{Phillips, R. D., Peakall, R., van der Niet, T. \& Johnson, S. D. Niche perspectives on plant\textendash pollinator interactions. \emph{Trends Plant Sci.} \textbf{25}, 779--793 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
-\CSLLeftMargin{50. }
-\CSLRightInline{Vázquez, D. P. \emph{et al.} Species abundance and asymmetric interaction strength in ecological networks. \emph{Oikos} \textbf{116}, 1120--1127 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.} \textbf{15}, 198--208 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gervasi2017}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Gervasi, D. D. L. \& Schiestl, F. P. Real-time divergent evolution in plants driven by pollinators. \emph{Nat. Commun.} \textbf{8}, 14691 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mackin2021}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Mackin, C.
-R., Peña, J.
-F., Blanco, M.
-A., Balfour, N.
-J.
-\& Castellanos, M.
-C.
-Rapid evolution of a floral trait following acquisition of novel pollinators.
-\emph{J.
-Ecol.} \textbf{109}, 2234--2246 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Olesen, J. M., Bascompte, J., Dupont, Y. L. \& Jordano, P. The modularity of pollination networks. \emph{PNAS} \textbf{104}, 19891--19896 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Fortuna, M. A. \emph{et al.} Nestedness versus modularity in ecological networks: Two sides of the same coin? \emph{J. Anim. Ecol.} \textbf{79}, 811--817 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Carvalheiro, L.
-G.
-\emph{et al.} The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
-\emph{Ecol.
-Lett.} \textbf{17}, 1389--1399 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Poisot, T. \emph{et al.} Mangal \textendash{} making ecological network analysis simple. \emph{Ecography} \textbf{39}, 384--390 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
-\CSLLeftMargin{58. }
-\CSLRightInline{Chamberlain, S.
-\emph{et al.} Taxize: {Taxonomic} information from around the web.
-R package version 0.9.99 (2020).~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
-\CSLLeftMargin{59. }
-\CSLRightInline{Smith, S. A. \& Brown, J. W. Constructing a broadly inclusive seed plant phylogeny. \emph{Am. J. Bot.} \textbf{105}, 302--314 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
-\CSLLeftMargin{60. }
-\CSLRightInline{Jin, Y. \& Qian, H. V.{PhyloMaker}: An {R} package that can generate very large phylogenies for vascular plants. \emph{Ecography} \textbf{42}, 1353--1359 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
-\CSLLeftMargin{61. }
-\CSLRightInline{Stekhoven, D. J. \& Bühlmann, P. {MissForest}\textemdash non-parametric missing value imputation for mixed-type data. \emph{Bioinformatics} \textbf{28}, 112--118 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
-\CSLLeftMargin{62. }
-\CSLRightInline{Penone, C. \emph{et al.} Imputation of missing data in life-history trait datasets: Which approach performs the best? \emph{Methods Ecol. Evol.} \textbf{5}, 961--970 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
-\CSLLeftMargin{63. }
-\CSLRightInline{Chamberlain, S. \emph{et al.} Package {``{PVR}''}. R package version 0.3 (2018).~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
-\CSLLeftMargin{64. }
-\CSLRightInline{Diniz-Filho, J. A. F. \emph{et al.} On the selection of phylogenetic eigenvectors for ecological analyses. \emph{Ecography} \textbf{35}, 239--249 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
-\CSLLeftMargin{65. }
-\CSLRightInline{Legendre, P. \& Legendre, L. \emph{Numerical ecology}. ({Elsevier, Amsterdam}, 2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
-\CSLLeftMargin{66. }
-\CSLRightInline{Revell, L. J. Phytools: An {R} package for phylogenetic comparative biology (and other things). \emph{Methods Ecol. Evol.} \textbf{3}, 217--223 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
-\CSLLeftMargin{67. }
-\CSLRightInline{Abdi, H. \& Williams, L. J. Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
-\CSLLeftMargin{68. }
-\CSLRightInline{Ballantyne, G., Baldock, K.
-C.
-R.
-\& Willmer, P.
-G.
-Constructing more informative plant\textendash pollinator networks: Visitation and pollen deposition networks in a heathland plant community.
-\emph{Proc.
-Royal Soc.
-B} \textbf{282}, 20151130 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
-\CSLLeftMargin{69. }
-\CSLRightInline{Vázquez, D.
-P., Morris, W.
-F.
-\& Jordano, P.
-Interaction frequency as a surrogate for the total effect of animal mutualists on plants.
-\emph{Ecol.
-Lett.} \textbf{8}, 1088--1094 (2005).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
-\CSLLeftMargin{70. }
-\CSLRightInline{Vázquez, D. P. \emph{et al.} The strength of plant\textendash pollinator interactions. \emph{Ecology} \textbf{93}, 719--725 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
-\CSLLeftMargin{71. }
-\CSLRightInline{Hung, K.-L.
-J., Kingston, J.
-M., Albrecht, M., Holway, D.
-A.
-\& Kohn, J.
-R.
-The worldwide importance of honey bees as pollinators in natural habitats.
-\emph{Proc.
-Royal Soc.
-B} \textbf{285}, 20172140 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
-\CSLLeftMargin{72. }
-\CSLRightInline{Bürkner, P.-C. Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.} \textbf{80}, 1--28 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
-\CSLLeftMargin{73. }
-\CSLRightInline{Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A. Visualization in {Bayesian} workflow. \emph{J. R. Stat. Soc. Ser. A Stat. Soc.} \textbf{182}, 389--402 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
-\CSLLeftMargin{74. }
-\CSLRightInline{Dormann, C. F., Gruber, B. \& Fründ, J. Introducing the bipartite package: Analysing ecological networks. \emph{R News} \textbf{8/2}, (2008).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
-\CSLLeftMargin{75. }
-\CSLRightInline{Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in species interaction networks. \emph{BMC Ecol.} \textbf{6}, 9 (2006).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-therneau2015}{}}%
-\CSLLeftMargin{76. }
-\CSLRightInline{Therneau, T., Atkinson, B., Ripley, B.
-\& Ripley, M.
-B.
-Package {``rpart''}.
-R package version 4.1-15 (2015).~At \href{https://CRAN.R-project.org/package=rpart}{https://CRAN.r-project.org/package=rpart}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-milborrow2015}{}}%
-\CSLLeftMargin{77. }
-\CSLRightInline{Milborrow, S.
-Rpart.
-Plot: {Plot} rpart {Models}.
-{An Enhanced Version} of plot.
-Rpart.
-R package version 3.0.9 (2015).~At \href{https://CRAN.R-project.org/package=rpart.plot}{https://CRAN.r-project.org/package=rpart.plot}.}
+Wright, I.J., Reich, P.B., Westoby, M., Ackerly, D.D., Baruch, Z., Bongers, F., \emph{et al.} (2004). The worldwide leaf economics spectrum. \emph{Nature}, 428, 821--827.
 
@@
 
-This is study was supported by the project SAFEGUARD (101003476 H2020-SFS-2019-2).
-We thank all researchers that made their data available for our analysis.
-We thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
+This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
+We thank all researchers that made their data openly available and sent it upon request.
+We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
 We also thank Jason Tylianakis for his comments on the manuscript before submission.
-JBL thanks the University of New England for the funding provided to carry out this work.
+Finally, JBL thanks the University of New England for the funding provided to carry out this work.
 

### 2022-01-24 Main_Figures/Figure3_a.Rmd

--- 2022-01-17 Main_Figures/Figure3_b.Rmd
@@
 pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
-aes(x = -PC2, y = Interaction),size = 2.8, alpha=0.4) + geom_line(size=1.8)  + ylab("Interaction")+ xlab("")+
+aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
   theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-    "Non-syrphid-Diptera", "Syrphids"))+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC2", subtitle = "B") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 
@@
 
-pp2 + theme(legend.position = "bottom")
+pp1 + theme(legend.position = "bottom")
 

### 2022-01-24 Main_Figures/Global_trait_spectrum.Rmd

@@
   plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
+     annotation_raster(style_l_1, xmin = 2.10, xmax = 2.90,ymin = 2.55, ymax = 3.7) +
     annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
+ plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,4.95,5.6,7.45,7.2,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.2,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
+                         label = PCAloadings$Variables, color="black",fontface =2,size=5)
 
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
-                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
+ plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.2,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
+                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=5)
 

### 2022-01-24 Main_Figures/Global_trait_spectrum_Qualitative_Vars.Rmd
Pollen nectar pPCA added

@@
   html_document: default
+classoption: landscape
+
 ---
+
+\pagenumbering{gobble}
 
@@
       theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.3)),
+            axis.title=element_text( size = rel(1.75)),
             axis.text=element_text(size = rel(1.75), color = "black"),
             legend.title=element_text(face="bold"),
-            legend.text=element_text(),
+            legend.text=element_text(size = rel(1.1)),
             legend.background=element_rect(fill="transparent"),
@@
              panel.grid.major= element_blank(),
-            plot.title = element_text(size = rel(1.75), face="bold")
+            plot.title = element_text(size = rel(2), face="bold")
       ))
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.185, 0.13)) +ggtitle("(a)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("A")
 

### 2022-01-24 Main_Figures/figure3_abcd.Rmd

--- 2022-01-17 Main_Figures/Figure3_b.Rmd
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=14}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=17, fig.width=27}
 
@@
   aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("")+
   theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
@@
     "Non-syrphid-Diptera", "Syrphids"))+
-  scale_y_log10()+ggtitle("D")
+  scale_y_log10()
 #Plot nicely PC2
@@
   aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("")+
   theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + 
@@
   "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-    "Non-syrphid-Diptera", "Syrphids")) + scale_y_log10()+ggtitle("E")
+    "Non-syrphid-Diptera", "Syrphids")) + scale_y_log10()
 
@@
 
-pp2 + theme(legend.position = "bottom")
+pp1+pp2+p1 +p2 + theme(legend.position = "none")+ plot_layout(ncol = 2)
 

### 2022-01-24 Manuscript/Lanuza_et_al_2021_Nat_Eco_Evo.tex

@@
 \item
-  It is not clear that the broad phylogenetic scale investigated in the paper is appropriate for investigating the importance of tradeoffs that evolve at the level of populations and species.
+  It is not clear that the broad phylogenetic scale investigated in the paper is appropriate for investigating the importance of trade-offs that evolve at the level of populations and species.
 I realize that the data at a finer micro-evolutionary scale are generally not available, but this is the level where constraints emerge.

### 2022-01-24 Supplementary_Material/Analysis_2_Hymenoptera_Families_Separated.Rmd

@@
      theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2)),
-           axis.text=element_text(size = rel(1.8), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
+           axis.title=element_text( size = rel(2.2)),
+           axis.text=element_text(size = rel(1.85), color = "black"),
+           legend.title=element_text(face="bold",size=rel(2.4)),
+           legend.text=element_text(size=rel(1.8)),
            legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
+           legend.key.size = unit(2, 'lines'),
            panel.border=element_rect(color="black",size=2.4),
@@
            panel.grid.major= element_blank(),
-           plot.title = element_text(hjust = 0.5,size=rel(2.75)),
-           plot.subtitle = element_text(size=rel(2.5))
-     ))
+           plot.title = element_text(hjust = 0.5,size=rel(2.95), face="bold"),
+           plot.subtitle = element_text(size=rel(2.7),face="bold")))
 }
@@
 aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC1", subtitle = "A")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 
@@
 aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC2", subtitle = "B") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 
@@
   theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + 
-  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC3", subtitle = "C")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 #Plot nicely PC1
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0)) + scale_color_manual(name="Functional groups",
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.95),hjust = 0)) + scale_color_manual(name="Functional groups",
   values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+
-  scale_y_log10()+ggtitle("(d)")
+  scale_y_log10()+ggtitle("D")
 #Plot nicely PC2
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0)) + 
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.95),hjust = 0)) + 
   scale_color_manual(name="Functional groups",values=c("orange", "black", 
-  "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10()+ggtitle("(e)")
+  "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10()+ggtitle("E")
 
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles\n Low selfing    High selfing")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0))+ 
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.95),hjust = 0))+ 
   scale_color_manual(name="Functional groups",values=c("orange", 
-  "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ scale_y_log10()+ggtitle("(f)")
+  "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ scale_y_log10()+ggtitle("F")
 

### 2022-01-24 Supplementary_Material/Analysis_2_Hymenoptera_a.Rmd

--- 2022-01-24 Supplementary_Material/Analysis_2_Hymenoptera_Families_Separated.Rmd
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap= ""}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=14,fig.pos = "!H",fig.cap= ""}
 
@@
 aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC1", subtitle = "A")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 
@@
 
-combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
-combined_1 <- combined + plot_layout(guides = "collect",ncol = 3)
+pp1 + theme(legend.position = "bottom")
 
-saveRDS(combined_1, "Plot_bee_families.rds")
+#combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
+#combined_1 <- combined + plot_layout(guides = "collect",ncol = 3)
 
-combined_2 <- readRDS("Plot_bee_families.rds")
-
-combined_2
 ```

### 2022-01-26 Main_Figures/Figure3.Rmd
Ms update based on editor comment

--- 2021-12-02 Main_Figures/Figure3.Rmd
@@
            legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
+           legend.text=element_text(size=rel(1.7)),
            legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
+           legend.key.size = unit(1.9, 'lines'),
            panel.border=element_rect(color="black",size=2.4),
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
   values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + 
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + 
   scale_color_manual(name="Functional groups",values=c("orange", "black", 
@@
   ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles\n Low selfing    High selfing")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold"))+ 
+  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold"))+ 
   scale_color_manual(name="Functional groups",values=c("orange", 

### 2022-01-26 Manuscript/Lanuza_et_al_2021_Ecol_Letters.Rmd
Ms update based on editor comment

--- 2022-01-24 Manuscript/Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
@@
 
-\textbf{Number of references:} 77.
+\textbf{Number of references:} 77 (CHECK! Probably less now)
 
@@
 However, despite recent advances in the understanding of plant trait variation, little is known about plant reproductive trade-offs and how these constrain life-history strategies and shape interactions with floral visitors.
-Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species.
+Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
 We found that over half of all plant reproductive trait variation was explained by two independent axes.
@@
 
-**In bold PNAS editor's comments.**
-
-- 1st explores is an ambiguous term.
-Maybe changing it for describe/determine?
-2nd.
-Last phrase of the 1st paragraph lacks clarity.
-3rd.
-Conceptual focus is unclear (3rd paragraph).
-General comment: What do we need to understand, and how will this information relate to broader problems in ecology/evolution?
-It is not sufficient to suggest that we need to improve our understanding without giving specifics regarding the impact of these studies.
-
-- There is insufficient justification/discussion of the traits used (Table 1).
-For example, what is the expected relevance of plant height?
-In addition, some of the traits are classified as both quantitative and qualitative.
-How can this work?
-For example, the selfing level was given as four categories of quantitative estimates as well as four categories of qualitative estimates.
-Aren't these the same thing?
-Finally, it is not clear why some traits were included, such as ovule number, whole others were not, such as flower color.
-
-- I am not convinced that the imputation process for missing trait values is accurate.
-There are many examples of very closely related plant species that differ dramatically in traits such as nectar volume and other traits relevant to pollinator interactions, so using a phylogenetic signal to estimate missing values may often give the wrong answer.
-In the Supplement you state: "In general terms, nectar data was rarely present and we tried to minimise the loss of information by filling some species at family level." Seems preferable to simply exclude nectar as one of your traits.
-
-- A major issue with network data from studies of plant-visitor interactions is that there is rarely enough information to distinguish pollinators from pollen predators or nectar thieves.
-
-- It is not clear that the broad phylogenetic scale investigated in the paper is appropriate for investigating the importance of trade-offs that evolve at the level of populations and species.
-I realize that the data at a finer micro-evolutionary scale are generally not available, but this is the level where constraints emerge.
-
 # INTRODUCTION
 
-Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that **explores** plant reproductive trade-offs is currently lacking [@roddy2021].
+Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that **describes the major** plant reproductive trade-offs is currently lacking [@roddy2021].
 In addition, macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
@@
 Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
-However, despite the generalist nature of most plant-pollinator interactions [@waser1996; @olesen2002], reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020].
-**Overall, it is unclear how specific plant reproductive biology traits shape plant-pollinator interactions [@tur2013; @devaux2014].**
+**However, plant reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020] and remains unclear how specific plant reproductive biology traits (e.g., mating or compatibility system) influence plant-pollinator associations [@tur2013; @devaux2014].**
 
 Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY @kattge2011 and COMPADRE @salguero2015), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
+With the recent availability of large trait databases [e.g., TRY @kattge2011; and COMPADRE @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
 However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
@@
 Several studies have identified links between plant traits and plant-pollinator network properties [@bartomeus2013; @olito2015; @rowe2020].
-Moreover, plant traits can define species’ network roles (e.g., specialists vs generalists) [@lazaro2013; @tur2013].
+Moreover, plant traits can define species’ network roles [e.g., specialists vs generalists\; @lazaro2013; @tur2013].
 For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
 Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
-Remarkably, the combination of traits have shown to increase the predictive power of the network interactions [@eklof2013].
-**Therefore, considering the different plant reproductive trade-offs which represent the species reproductive strategy within the network [@dehling2016] could progress our understanding of plant-pollinator interactions**.
-Further, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.
+Remarkably, the combination of traits has shown to increase the predictive power of the network interactions [@eklof2013].
+**Moreover, the position in the trait space can determine plant and pollinator species functional roles [@dehling2016].
+Therefore, by considering the position in the reproductive trait space we could progress our understanding of the plant species functional roles within plant-pollinator interaction networks.
+Nonetheless, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.**
 
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives (e.g., The Web of Life [@fortuna2010] and Mangal [@poisot2016]).
-In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives [e.g., The Web of Life, @fortuna2010; and Mangal, @poisot2016].
+In total, our network dataset (see Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
 
@@
 
-**Functional traits.** We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
-These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive biology and 3 vegetative, Supplementary Information).
+**Functional traits.** We selected a total of 19 different functional traits that included both reproductive and vegetative traits (see Table 1 and Supplementary Information).
+From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
+The 3 remaining traits, were vegetative traits that are commonly used to characterize the global spectrum of plant form and function and represent the fast-slow continuum of trait variation (e.g., short-lived versus perennial species).
 For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Supplementary Fig.
+From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Fig.
 S1 for missing values information for each trait).
@@
 
-Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Autonomous selfing", "Compatibility system", "Breeding system", " ", " ", " ", " ")
+Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Compatibility system", "Breeding system", " ", " ", " ", " ", " ")
 
 T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-           "Presence \n Absence", "None \n Low \n Medium \n High", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " "),align = c("l"))
+           "Presence \n Absence", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " ", ""),align = c("l"))
 
@@
 
-Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology", "Reproductive \n biology","","","",""),align = c("c"))
+Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology","","","","", ""),align = c("c"))
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Fig.
-1 | Plant life-history strategies.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
 The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18,fig.cap= "**Fig.
-2 | Location of the different qualitative traits on the trait space.** The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="90%",fig.align='center',fig.cap= "\\textbf{Figure 2} Location of the different qualitative traits on the trait space.
+The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
+The solid arrows indicate the direction of variation of the different quantitative traits showed in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S)."}
 
@@
 #LOAD LIBRARIES
-#library(phytools)
-#library(ape) #for phylogenetic distance
-#library(dplyr) #data processing
-#library(rtrees) #for phylogenetic distancelibrary(MASS)
-#library(reshape2)
+library(phytools)
+library(ape) #for phylogenetic distance
+library(dplyr) #data processing
+library(rtrees) #for phylogenetic distancelibrary(MASS)
+library(reshape2)
 library(viridis) #COLOUR GGPLOT
-#library(MASS)
+library(MASS)
 library(ggplot2)
 library(broman) #crayon colours
-#library(cowplot)
+library(cowplot)
 
@@
             legend.title=element_text(face="bold"),
-            legend.text=element_text(),
+            legend.text=element_text(size = rel(1.1)),
             legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.55, 'lines'),
+            legend.key.size = unit(0.4, 'lines'),
             panel.border=element_rect(color="black",size=1),
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.185, 0.13)) +ggtitle("(a)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("(b)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.090, 0.115)) + ggtitle("(b)")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.102, 0.1)) + ggtitle("(c)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.12, 0.1)) + ggtitle("(c)")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.165, 0.1)) + ggtitle("(f)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.13, 0.18)) + ggtitle("(e)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.163, 0.115)) + ggtitle("(d)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("(d)")
 
@@
 
-#  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flowe#r_sym(PC),ncol=3,nrow=2,  align = "hv")
-
-library(patchwork)
-Compatibility(PC) + Life_form(PC) + Life_span(PC) + Breeding_syst(PC) + Flower_sha(PC) + Flower_sym(PC) + plot_layout(ncol=3)
+  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),ncol=3,nrow=2,  align = "hv")
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Fig.
-3 | Interaction (yes/no) and visitation rates across the three main axes of trait variation per floral visitor guild.** Fitted posterior estimates of the presence/absence of interaction (a, b and c) and number of visits (d, e and f) made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3** Interaction (yes/no) and visitation rates across the three main axes of trait variation per floral visitor guild.
+Fitted posterior estimates of the presence/absence of interaction (a, b and c) and number of visits (d, e and f) made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
 PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=12,fig.cap= "**Fig.
-4 | Contribution of traits in plant's network roles.** Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=12,fig.cap= "**Figure 4** Contribution of traits in plant's network roles.
+Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
 The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
@@
 
-rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.45,tweak = 1.25,type = 2) 
-rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.45,tweak = 1.25,type = 2)
-rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.45,tweak = 1.25,type = 2)
+rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.75,tweak = 1.25,type = 2) 
+rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.75,tweak = 1.25,type = 2)
+rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.75,tweak = 1.25,type = 2)
 

### 2022-01-26 Manuscript/Lanuza_et_al_2021_Ecol_Letters.tex
Ms update based on editor comment

--- 2022-01-24 Manuscript/Lanuza_et_al_2021_Nat_Eco_Evo.tex
@@
 
-\textbf{In bold PNAS editor's comments.}
-
-\begin{itemize}
-\item
-  1st explores is an ambiguous term.
-Maybe changing it for describe/determine?
-2nd.
-Last phrase of the 1st paragraph lacks clarity.
-3rd.
-Conceptual focus is unclear (3rd paragraph).
-General comment: What do we need to understand, and how will this information relate to broader problems in ecology/evolution?
-It is not sufficient to suggest that we need to improve our understanding without giving specifics regarding the impact of these studies.
-\item
-  There is insufficient justification/discussion of the traits used (Table 1).
-For example, what is the expected relevance of plant height?
-In addition, some of the traits are classified as both quantitative and qualitative.
-How can this work?
-For example, the selfing level was given as four categories of quantitative estimates as well as four categories of qualitative estimates.
-Aren't these the same thing?
-Finally, it is not clear why some traits were included, such as ovule number, whole others were not, such as flower color.
-\item
-  I am not convinced that the imputation process for missing trait values is accurate.
-There are many examples of very closely related plant species that differ dramatically in traits such as nectar volume and other traits relevant to pollinator interactions, so using a phylogenetic signal to estimate missing values may often give the wrong answer.
-In the Supplement you state: ``In general terms, nectar data was rarely present and we tried to minimise the loss of information by filling some species at family level.'' Seems preferable to simply exclude nectar as one of your traits.
-\item
-  A major issue with network data from studies of plant-visitor interactions is that there is rarely enough information to distinguish pollinators from pollen predators or nectar thieves.
-\item
-  It is not clear that the broad phylogenetic scale investigated in the paper is appropriate for investigating the importance of tradeoffs that evolve at the level of populations and species.
-I realize that the data at a finer micro-evolutionary scale are generally not available, but this is the level where constraints emerge.
-\end{itemize}
-
 \hypertarget{introduction}{%
@@
 
-Despite the astonishing diversity of floral structures among flowering plants (\protect\hyperlink{ref-barrett2002}{Barrett 2002}; \protect\hyperlink{ref-schiestl2013}{Schiestl \& Johnson 2013}) and their importance in shaping plant-pollinator interactions (\protect\hyperlink{ref-fenster2004}{Fenster \emph{et al.} 2004}; \protect\hyperlink{ref-dellinger2020}{Dellinger 2020}), a unified framework that \textbf{explores} plant reproductive trade-offs is currently lacking (\protect\hyperlink{ref-roddy2021}{Roddy \emph{et al.} 2021}).
+Despite the astonishing diversity of floral structures among flowering plants (\protect\hyperlink{ref-barrett2002}{Barrett 2002}; \protect\hyperlink{ref-schiestl2013}{Schiestl \& Johnson 2013}) and their importance in shaping plant-pollinator interactions (\protect\hyperlink{ref-fenster2004}{Fenster \emph{et al.} 2004}; \protect\hyperlink{ref-dellinger2020}{Dellinger 2020}), a unified framework that \textbf{describes the major} plant reproductive trade-offs is currently lacking (\protect\hyperlink{ref-roddy2021}{Roddy \emph{et al.} 2021}).
 In addition, macroecological studies that investigate plant reproductive traits are scarce (\protect\hyperlink{ref-baude2016}{Baude \emph{et al.} 2016}; \protect\hyperlink{ref-munoz2016}{Munoz \emph{et al.} 2016}; \protect\hyperlink{ref-grossenbacher2017}{Grossenbacher \emph{et al.} 2017}; \protect\hyperlink{ref-moeller2017}{Moeller \emph{et al.} 2017}) and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales (\protect\hyperlink{ref-sargent2008}{Sargent \& Ackerly 2008}; \protect\hyperlink{ref-rech2016}{Rech \emph{et al.} 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}; \protect\hyperlink{ref-ruger2018}{Rüger \emph{et al.} 2018}).
@@
 Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches (\protect\hyperlink{ref-fenster2004}{Fenster \emph{et al.} 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero \emph{et al.} 2014}) and trait-matching analyses (\protect\hyperlink{ref-stang2009}{Stang \emph{et al.} 2009}; \protect\hyperlink{ref-bartomeus2016}{Bartomeus \emph{et al.} 2016}).
-However, despite the generalist nature of most plant-pollinator interactions (\protect\hyperlink{ref-waser1996}{Waser \emph{et al.} 1996}; \protect\hyperlink{ref-olesen2002}{Olesen \& Jordano 2002}), reproductive traits have been overlooked beyond highly specialised pollination systems (\protect\hyperlink{ref-dellinger2020}{Dellinger 2020}).
-\textbf{Overall, it is unclear how specific plant reproductive biology traits shape plant-pollinator interactions (\protect\hyperlink{ref-tur2013}{Tur \emph{et al.} 2013}; \protect\hyperlink{ref-devaux2014}{Devaux \emph{et al.} 2014}).}
+\textbf{However, plant reproductive traits have been overlooked beyond highly specialised pollination systems (\protect\hyperlink{ref-dellinger2020}{Dellinger 2020}) and remains unclear how specific plant reproductive biology traits (e.g., mating or compatibility system) influence plant-pollinator associations (\protect\hyperlink{ref-tur2013}{Tur \emph{et al.} 2013}; \protect\hyperlink{ref-devaux2014}{Devaux \emph{et al.} 2014}).}
 
 Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY \protect\hyperlink{ref-kattge2011}{Kattge \emph{et al.}} (\protect\hyperlink{ref-kattge2011}{2011}) and COMPADRE \protect\hyperlink{ref-salguero2015}{Salguero-Gómez \emph{et al.}} (\protect\hyperlink{ref-salguero2015}{2015})), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function (\protect\hyperlink{ref-diaz2016}{Díaz \emph{et al.} 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}; \protect\hyperlink{ref-bruelheide2018}{Bruelheide \emph{et al.} 2018}; \protect\hyperlink{ref-carmona2021}{Carmona \emph{et al.} 2021}).
+With the recent availability of large trait databases (e.g., TRY \protect\hyperlink{ref-kattge2011}{Kattge \emph{et al.} 2011}; and COMPADRE \protect\hyperlink{ref-salguero2015}{Salguero-Gómez \emph{et al.} 2015}), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function (\protect\hyperlink{ref-diaz2016}{Díaz \emph{et al.} 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}; \protect\hyperlink{ref-bruelheide2018}{Bruelheide \emph{et al.} 2018}; \protect\hyperlink{ref-carmona2021}{Carmona \emph{et al.} 2021}).
 However, most studies have focused on vegetative traits such as leaf (\protect\hyperlink{ref-wright2004}{Wright \emph{et al.} 2004}), wood (\protect\hyperlink{ref-chave2009}{Chave \emph{et al.} 2009}), or root (\protect\hyperlink{ref-laughlin2021}{Laughlin \emph{et al.} 2021}) trade-offs with little or no attention given to reproductive traits (\protect\hyperlink{ref-evojtko2020}{E-Vojtkó \emph{et al.} 2020}; \protect\hyperlink{ref-roddy2021}{Roddy \emph{et al.} 2021}) which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
@@
 Several studies have identified links between plant traits and plant-pollinator network properties (\protect\hyperlink{ref-bartomeus2013}{Bartomeus 2013}; \protect\hyperlink{ref-olito2015}{Olito \& Fox 2015}; \protect\hyperlink{ref-rowe2020}{Rowe \emph{et al.} 2020}).
-Moreover, plant traits can define species' network roles (e.g., specialists vs generalists) (\protect\hyperlink{ref-lazaro2013}{Lázaro \emph{et al.} 2013}; \protect\hyperlink{ref-tur2013}{Tur \emph{et al.} 2013}).
+Moreover, plant traits can define species' network roles (e.g., specialists vs generalists; \protect\hyperlink{ref-lazaro2013}{Lázaro \emph{et al.} 2013}; \protect\hyperlink{ref-tur2013}{Tur \emph{et al.} 2013}).
 For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators (\protect\hyperlink{ref-junker2013}{Junker \emph{et al.} 2013}; \protect\hyperlink{ref-coux2016}{Coux \emph{et al.} 2016}).
 Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure (\protect\hyperlink{ref-stang2009}{Stang \emph{et al.} 2009}; \protect\hyperlink{ref-ibanez2012}{Ibanez 2012}).
-Remarkably, the combination of traits have shown to increase the predictive power of the network interactions (\protect\hyperlink{ref-eklof2013}{Eklöf \emph{et al.} 2013}).
-\textbf{Therefore, considering the different plant reproductive trade-offs which represent the species reproductive strategy within the network (\protect\hyperlink{ref-dehling2016}{Dehling \emph{et al.} 2016}) could progress our understanding of plant-pollinator interactions}.
-Further, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.
+Remarkably, the combination of traits has shown to increase the predictive power of the network interactions (\protect\hyperlink{ref-eklof2013}{Eklöf \emph{et al.} 2013}).
+\textbf{Moreover, the position in the trait space can determine plant and pollinator species functional roles (\protect\hyperlink{ref-dehling2016}{Dehling \emph{et al.} 2016}).
+Therefore, by considering the position in the reproductive trait space we could progress our understanding of the plant species functional roles within plant-pollinator interaction networks.
+Nonetheless, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.}
 
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies (\protect\hyperlink{ref-olesen2007}{Olesen \emph{et al.} 2007}; \protect\hyperlink{ref-fortuna2010}{Fortuna \emph{et al.} 2010}; \protect\hyperlink{ref-carvalheiro2014}{Carvalheiro \emph{et al.} 2014}) or available in online archives (e.g., The Web of Life (\protect\hyperlink{ref-fortuna2010}{Fortuna \emph{et al.} 2010}) and Mangal (\protect\hyperlink{ref-poisot2016}{Poisot \emph{et al.} 2016})).
-In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+Many of these networks are freely available either as published studies (\protect\hyperlink{ref-olesen2007}{Olesen \emph{et al.} 2007}; \protect\hyperlink{ref-fortuna2010}{Fortuna \emph{et al.} 2010}; \protect\hyperlink{ref-carvalheiro2014}{Carvalheiro \emph{et al.} 2014}) or available in online archives (e.g., The Web of Life, \protect\hyperlink{ref-fortuna2010}{Fortuna \emph{et al.} 2010}; and Mangal, \protect\hyperlink{ref-poisot2016}{Poisot \emph{et al.} 2016}).
+In total, our network dataset (see Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
 
@@
 
-\textbf{Functional traits.} We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
-These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive biology and 3 vegetative, Supplementary Information).
+\textbf{Functional traits.} We selected a total of 19 different functional traits that included both reproductive and vegetative traits (see Table 1 and Supplementary Information).
+From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
+The 3 remaining traits, were vegetative traits that are commonly used to characterize the global spectrum of plant form and function and represent the fast-slow continuum of trait variation (e.g., short-lived versus perennial species).
 For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8\% of the dataset, see Supplementary Fig.
+From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8\% of the dataset, see Fig.
 S1 for missing values information for each trait).
@@
 \addlinespace
-\textbf{Floral} & Ovules per flower & \textbf{\makecell[c]{Reproductive \\ biology}} & Autonomous selfing & \makecell[l]{None \\ Low \\ Medium \\ High}\\
+\textbf{Floral} & Ovules per flower & \textbf{\makecell[c]{Reproductive \\ biology}} & Compatibility system & \makecell[l]{Self-incomp. \\ Part. self-comp. \\ Self-comp.}\\
 \addlinespace
-\textbf{Floral} & Flowers per plant & \textbf{\makecell[c]{Reproductive \\ biology}} & Compatibility system & \makecell[l]{Self-incomp. \\ Part. self-comp. \\ Self-comp.}\\
+\textbf{Floral} & Flowers per plant & \textbf{\makecell[c]{Reproductive \\ biology}} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious}\\
 \addlinespace
-\textbf{Floral} & Nectar ($\mu$l) & \textbf{\makecell[c]{Reproductive \\ biology}} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious}\\
+\textbf{Floral} & Nectar ($\mu$l) & \textbf{} &  & \\
 \addlinespace
@@
 
-\caption{\textbf{Fig.
-1 | Plant life-history strategies.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
+\caption{\textbf{Figure 1} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
 The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
@@
 
-\begin{figure}
-\centering
-\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}\textbf{Fig.
-2 \textbar{} Location of the different qualitative traits on the trait space.} The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=0.9\linewidth]{output/figures/unnamed-chunk-3-1}
+
+}
+
+\caption{\textbf{Figure 2} Location of the different qualitative traits on the trait space.
+The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
+The solid arrows indicate the direction of variation of the different quantitative traits showed in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S).}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 \includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\textbf{Fig.
-3 \textbar{} Interaction (yes/no) and visitation rates across the three main axes of trait variation per floral visitor guild.} Fitted posterior estimates of the presence/absence of interaction (a, b and c) and number of visits (d, e and f) made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
+\caption{\label{fig:unnamed-chunk-4}\textbf{Figure 3} Interaction (yes/no) and visitation rates across the three main axes of trait variation per floral visitor guild.
+Fitted posterior estimates of the presence/absence of interaction (a, b and c) and number of visits (d, e and f) made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
 PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.
@@
 \includegraphics{output/figures/unnamed-chunk-5-1.pdf}
-\caption{\label{fig:unnamed-chunk-5}\textbf{Fig.
-4 \textbar{} Contribution of traits in plant's network roles.} Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
+\caption{\label{fig:unnamed-chunk-5}\textbf{Figure 4} Contribution of traits in plant's network roles.
+Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
 The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-olesen2002}{}}%
-Olesen, J.M. \& Jordano, P. (2002). Geographic patterns in plant--pollinator mutualistic networks. \emph{Ecology}, 83, 2416--2424.
-
 \leavevmode\vadjust pre{\hypertarget{ref-olito2015}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-waser1996}{}}%
-Waser, N.M., Chittka, L., Price, M.V., Williams, N.M. \& Ollerton, J. (1996). Generalization in pollination systems, and why it matters. \emph{Ecology}, 77, 1043--1060.
-
 \leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%

### 2022-01-26 Manuscript/MS_word.Rmd
Ms update based on editor comment

@@
 Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY @kattge2011 and COMPADRE @salguero2015), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
+With the recent availability of large trait databases [e.g., TRY @kattge2011; and COMPADRE @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
 However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.

### 2022-01-26 Manuscript/trial.Rmd
Ms update based on editor comment

--- 2021-12-09 Manuscript/Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
@@
 ---
-title: \singlespacing \vspace{-1.6cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors
-
-#author: 
-#  - Jose B. Lanuza^1,2^*
-#  - Romina Rader^1^
-#  - Jamie Stavert^3^
-#  - Liam K. Kendall^4^
-#  - Manu E. Saunders^1^
-#  - Ignasi Bartomeus^2^
-
-# may use lua filters for affiliations etc: see https://stackoverflow.com/a/52919256
-
-# date: '`r Sys.Date()`'
-
-output:
-  bookdown::pdf_document2:
-    fig_caption: yes
-    fig_width: 7
-    fig_height: 7
-    df_print: kable
-    keep_tex: yes
-    number_sections: no
-    extra_dependencies: ["float"]
-    toc: no
-    fig_crop: no
-    includes:
-      in_header: header.tex
-
-documentclass: article
-# classoption: twocolumn, landscape, etc
-papersize: a4
-pagestyle: plain  # plain, empty, headings
-geometry: margin=1in
-linestretch: 2
-fontfamily: mathpazo
-fontsize: 12pt
-
-bibliography: 
-  - references.bib
-  - knitcitations.bib
-# zotero: "My shared Zotero group"
-csl: ecology.csl
-# csl: https://www.zotero.org/styles/ecology
-notes-after-punctuation: false
-link-citations: yes
-linkcolor: RoyalBlue
-urlcolor: RoyalBlue
-links-as-notes: false
-subparagraph: yes
-
-header-includes:
-- \usepackage{booktabs}
-- \usepackage{longtable}
-- \usepackage{array}
-- \usepackage{multirow}
-- \usepackage{wrapfig}
-- \usepackage{float}
-- \usepackage{colortbl}
-- \usepackage{tabu}
-- \usepackage{threeparttable}
-- \usepackage{threeparttablex}
-- \usepackage[normalem]{ulem}
-- \usepackage{makecell}
-- \usepackage{xcolor}
-- \usepackage{float}
-- \floatplacement{figure}{H}
-- \usepackage[skip=3pt]{caption}
-- \captionsetup[figure]{labelformat=empty}
-- \usepackage{setspace}
-- \usepackage{titlesec}
-- \titlespacing{\title}{0pt}{\parskip}{-\parskip}
-- \usepackage[style=nature]{biblatex}
-- \usepackage[labelformat = empty]{caption}
-- \usepackage{pdflscape}
-
+title: "Untitled"
+output: html_document
 ---
-
-\vspace{-1.7cm}
-\singlespacing
-\large 
-\textbf{Jose B. Lanuza$^{1,2}*$, Romina Rader$^{1}$, Jamie Stavert$^{3}$, Liam K. Kendall$^{4}$, Manu E. Saunders$^{1}$ and Ignasi Bartomeus$^{2}$}
-
-\vspace{0.3cm}
-
-\normalsize
-
-__Plant life-history strategies are constrained by cost-benefit trade-offs that determine plant form and function.
-However, despite recent advances in the understanding of trade-offs for vegetative and physiological traits, little is known about plant reproductive economics and how they constrain plant life-history strategies and shape interactions with floral visitors.
-Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species from 28 plant-pollinator studies across 18 countries.
-We tested whether a plant’s reproductive strategy predicts its interactions with floral visitors and if the different reproductive traits predict the plant’s role within the pollination network.
-We found that over half of all plant reproductive trait variation was explained by two independent axes that encompassed plant form and function.
-Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
-Plant reproductive trade-offs helped explain partly the presence or absence of interactions with floral visitors, but not differences in visitation rate.
-However, we did find important differences in the interaction level among floral visitor guilds on the different axes of trait variation.
-Finally, we found that plant size and floral rewards were the most important traits in the understanding of the plant species network role.
-Our results highlight the importance of plant reproductive trade-offs in determining plant life-history strategies and plant-pollinator interactions in a global context.__
-
-\small
-\vspace{-0.5cm}
-
-\noindent\rule{\textwidth}{1pt}
-
-^1^ School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-^2^ Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-^3^ Department of Conservation | Te Papa Atawhai, Auckland, New Zealand.
-^4^ Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden.
-`*` e-mail: barragansljose@gmail.com
-
-\doublespacing
-\vspace{5mm}
-\normalsize
-
-```{r setup, include=FALSE, cache=FALSE, message = FALSE}
-
-library("knitr")
-
-### Chunk options: see http://yihui.name/knitr/options/ ###
-## Text results
-opts_chunk$set(echo = FALSE, warning = TRUE, message = TRUE)
-
-## Code decoration
-opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)
-
-## Cache
-# opts_chunk$set(cache = 2, cache.path = "output/cache/")
-
-## Plots
-opts_chunk$set(fig.path = "output/figures/")
-
-```
-
-```{r knitcitations, cache = FALSE}
-library(knitcitations)
-cleanbib()   
-cite_options(citation_format = "pandoc")
-
-```
-
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.pos = 'H')
-```
-
-Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that explores plant reproductive trade-offs is currently lacking [@roddy2021].
-In addition, macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
-Linking the plant's position in trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
-Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
-However, despite the generalist nature of most plant-pollinator interactions [@waser1996; @olesen2002], reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020].
-Overall, it is unclear how specific plant reproductive biology traits shape plant-pollinator interactions [@tur2013; @devaux2014].
-
-Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY @kattge2011 and COMPADRE @salguero2015), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
-However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively, [@barrett2003; @moeller2017] and outcrossing levels are positively correlated with flower size [@goodwillie2010].
-In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators [@ollerton2011; @rodger2021].
-However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.
-
-Several studies have identified links between plant traits and plant-pollinator network properties [@bartomeus2013; @olito2015; @rowe2020].
-Moreover, plant traits can define species’ network roles (e.g., specialists vs generalists) [@lazaro2013; @tur2013].
-For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
-Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
-Remarkably, the combination of traits have shown to increase the predictive power of the network interactions [@eklof2013].
-Therefore, considering the different plant reproductive trade-offs which represent the species reproductive strategy within the network [@dehling2016] could progress our understanding of plant-pollinator interactions.
-Further, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.
-
-Here, we aim to explore the potential trade-offs among reproductive traits and how these influence plant-pollinator interactions.
-First, we identify the major axes of reproductive trait variation and trade-offs that determine plant form and function.
-Second, we investigate how plant species’ position in trait-space influence interactions with floral visitors.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species’ roles within networks using a set of complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
-
-# RESULTS
-
-**Plant strategies.** The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Fig.
-1 and Supplementary Fig.
-S5) and had a phylogenetic correlation ($\lambda$) of 0.76.
-The first principal component (PC1) represented 26.72% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the ‘flower number - flower size trade-off’, as already described in previous studies [@sargent2007; @kettle2011].
-Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Supplementary Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
-The second principal component (PC2) represented 25.05% of the trait variation and indicated a trade-off between low and high pollinator dependence.
-We refer to this axis as the ‘pollinator dependence trade-off’.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Supplementary Table S3).
-We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
-In contrast, species with high levels of autonomous selfing tended to have fewer and smaller flowers, had shorter styles and were shorter in height.
-Further, PC3 explained a considerable amount of trait variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
-The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Supplementary Table S3).
-Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the ‘style length trade-off’.
-Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 23.40%); and pollen quantity (pollen grains per flower) was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 21.67%; Supplementary Fig.
-S6).
-This pPCA explained similar variance with the first two principal components (45.07%) and similar associations of traits despite some variability in the loadings (Supplementary Table S4).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Fig.
-1 | Plant life-history strategies.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
-The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
-The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation.
-The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}
-
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-library(viridis) #COLOUR GGPLOT
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(magick)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#Images were made by Paula Martin
-#Check her work on https://paulamartinart.com/
-
-tree <- image_read("Images/PPCA_Plot/Tree.png")
-tree_1 <- as.raster(tree)
-
-style_l <- image_read("Images/PPCA_Plot/Style_Long.png")
-style_l_1 <- as.raster(style_l)
-
-style_s <- image_read("Images/PPCA_Plot/Style_Short.png")
-style_s_1 <- as.raster(style_s)
-
-ovule_h <- image_read("Images/PPCA_Plot/Ovule_High.png")
-ovule_h_1 <- as.raster(ovule_h)
-
-ovule_l <- image_read("Images/PPCA_Plot/Ovule_Low.png")
-ovule_l_1 <- as.raster(ovule_l)
-
-selfing_n <- image_read("Images/PPCA_Plot/Selfing_None.png")
-selfing_n_1 <- as.raster(selfing_n)
-
-selfing_h <- image_read("Images/PPCA_Plot/selfing.png")
-selfing_h_1 <- as.raster(selfing_h)
-
-single_flower <- image_read("Images/PPCA_Plot/Single_Flower.png")
-single_flower_1 <- as.raster(single_flower)
-
-many_flowers <- image_read("Images/PPCA_Plot/Inflorescencia.png")
-many_flowers_1 <- as.raster(many_flowers)
-#many_flowers_1 <- image_rotate(many_flowers, 45)
-
-large_flower <- image_read("Images/PPCA_Plot/flower_big.png")
-large_flower_1 <- as.raster(large_flower)
-
-flower_small <- image_read("Images/PPCA_Plot/flower_short.png")
-flower_small_1 <- as.raster(flower_small)
-
-herb <- image_read("Images/PPCA_Plot/herb.png")
-herb_1 <- as.raster(herb)
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("Flower number - flower size trade-off ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Pollinator dependence trade-off ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
-    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
-    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
-    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
-    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2, ymax = -1.50) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
-
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
-                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-plot_grid(all_spp(PC))
-
-```
-
-We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
-2 and Supplementary Table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, _P_ < 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , _P_ = 0.59; PC2:  Sum of squares = 0.83, F-value = 1.43, _P_ = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Supplementary Fig.
-S7).
-Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Supplementary Fig.
-S7a and Fig.
-S7b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Supplementary Fig.
-S7c and Fig.
-S7d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Supplementary Fig.
-S7e and Fig.
-S7f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Supplementary Fig.
-S7g and Fig.
-S7h).
-Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Supplementary Fig.
-S7i and Fig.
-S7j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Supplementary Fig.
-S7k and Fig.
-S7l).
-
-\blandscape
-
-\vspace*{-28mm}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18,fig.cap= "**Fig.
-2 | Location of the different qualitative traits on the trait space.** The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f)."}
-
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-#library(phytools)
-#library(ape) #for phylogenetic distance
-#library(dplyr) #data processing
-#library(rtrees) #for phylogenetic distancelibrary(MASS)
-#library(reshape2)
-library(viridis) #COLOUR GGPLOT
-#library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-#library(cowplot)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.55, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank(),
-            plot.title = element_text(size = rel(1.65), face="bold")
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-#CALL the output PC for simplicity
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-Compatibility <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Compatibility <- dat_cleaning_5$Compatibility_system
-  dat$Compatibility <- as.character(dat$Compatibility)
-  dat$Compatibility[dat$Compatibility=="dioecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="monoecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-  dat$Compatibility[dat$Compatibility=="self_compatible"] <- "Self compatible"
-  dat$Compatibility[dat$Compatibility=="self_incompatible"] <- "Self incompatible"
-  dat$Compatibility <- factor(dat$Compatibility, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Compatibility),size=1.75)+scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.185, 0.13)) +ggtitle("(a)")
-
-  plot
-
-}
-
-#Compatibility(PC)
-
-#############################################################################################################################################################
-#Life form
-#############################################################################################################################################################
-#Load plots
-Life_form <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Life form` <- dat_cleaning_5$life_form
-  dat$`Life form` <- as.character(dat$`Life form`)
-  dat$`Life form`[dat$`Life form`=="herb"] <- "Herb"
-  dat$`Life form`[dat$`Life form`=="shrub"] <- "Shrub"
-  dat$`Life form`[dat$`Life form`=="tree"] <- "Tree"
-  dat$`Life form`[dat$`Life form`=="vine"] <- "Shrub"
-
-  dat$`Life form` <- factor( dat$`Life form`, levels = c("Herb", "Shrub", "Tree"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Life form`),size=1.75)+scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("(b)")
-
-  plot
-
-}
-
-#Life_form(PC)
-
-#############################################################################################################################################################
-#Life span
-#############################################################################################################################################################
-#Load plots
-Life_span <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-    dat$Lifespan <- dat_cleaning_5$lifespan
-    dat$Lifespan <- as.character(dat$Lifespan)
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Lifespan),size=1.75)+scale_color_manual(values=c("sienna4","forestgreen"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.102, 0.1)) + ggtitle("(c)")
-
-  plot
-
-}
-
-#Life_span(PC)
-
-#############################################################################################################################################################
-#Flower symmetry
-#############################################################################################################################################################
-#Load plots
-Flower_sym <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower symmetry` <- dat_cleaning_5$Flower_symmetry
-  dat$`Flower symmetry` <- as.character(dat$`Flower symmetry`)
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower symmetry`),size=1.75)+scale_color_manual(values=c("sienna2","purple"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.165, 0.1)) + ggtitle("(f)")
-
-  plot
-
-}
-
-#Flower_sym(PC)
-
-#############################################################################################################################################################
-#Flower shape
-#############################################################################################################################################################
-#Load plots
-Flower_sha <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower shape` <- dat_cleaning_5$Flower_morphology
-  dat$`Flower shape` <- as.character(dat$`Flower shape`)
-  dat$`Flower shape`[dat$`Flower shape`=="Funnelform"] <- "Campanulate"
-  dat$`Flower shape`[dat$`Flower shape`=="Spike"] <- "Brush"
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower shape`),size=1.75)+scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.13, 0.18)) + ggtitle("(e)")
-
-  plot
-
-}
-
-#Flower_sha(PC)
-
-#############################################################################################################################################################
-#Breeding system
-#############################################################################################################################################################
-#Load plots
-Breeding_syst <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Breeding system` <- dat_cleaning_5$Breeding_system
-  dat$`Breeding system` <- as.character(dat$`Breeding system`)
-  dat$`Breeding system` <- factor(dat$`Breeding system`, levels=c("Hermaphrodite","Monoecious" ,"Dioecious"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Breeding system`),size=1.75)+scale_color_manual(values=c("forestgreen","orange", "black"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.163, 0.115)) + ggtitle("(d)")
-
-  plot
-
-}
-
-#Breeding_syst(PC)
-
-#############################################################################################################################################################
-#Nectar
-#############################################################################################################################################################
-#Load plots
-#Nectar <- function(PC, x="PC1", y="PC2") {
-#  # PC being a prcomp object
-#  data <- data.frame(PC$S)
-#  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-#  dat <- data.frame(x = data[,x], y = data[,y])
-#  
-#  #######
-#  #DENSITY FUNCTION
-#  #######
-#  get_density <- function(x, y, ...) {
-#    dens <- MASS::kde2d(x, y, ...)
-#    ix <- findInterval(x, dens$x)
-#    iy <- findInterval(y, dens$y)
-#    ii <- cbind(ix, iy)
-#    return(dens$z[ii])
-#  }
-#  
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-#  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-#  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-#  plot <- plot + geom_point(data=dat, aes(-x, -y, #colour=Nectar),size=1.75)+scale_color_manual(values=c("black","grey"))
-#  
-#  ########
-#  #ADD ARROWS 
-#  ########
-#  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-#  mult <- min(
-#    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-#    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-#  )
-#  datapc <- transform(datapc,
-#                      v1 = .75 * mult * (get(x)),
-#                      v2 = .75 * mult * (get(y))
-#  )
-#  # add arrows
-#  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, #yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-#  
-#  #Add axis with perctentage
-#  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-#
-#  
-#  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, #arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-#  
-#  #ADD LABELS
-#  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-#  
-#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-#  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = #-(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-#                          label = PCAloadings$Variables, color="black",size=3)
-#  
-#  #CHANGE THEME
-#  #CHANGE THEME
-#  
-#  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)") 
-#  
-#  plot
-#  
-#}
-#
-# #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")
-
-#  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flowe#r_sym(PC),ncol=3,nrow=2,  align = "hv")
-
-library(patchwork)
-Compatibility(PC) + Life_form(PC) + Life_span(PC) + Breeding_syst(PC) + Flower_sha(PC) + Flower_sym(PC) + plot_layout(ncol=3)
-
-```
-
-\elandscape
-
-\vspace{5mm}
-
-**Phylogenetic signal of traits.** We found a strong phylogenetic signal (*P* < 0.01) in all quantitative traits (Supplementary Table S5).
-The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
-The traits that showed a moderate phylogenetic signal were inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits ($\lambda$ = 0.14).
-
-**Visitation patterns.** The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall visitation rates (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant trends across the different floral visitor guilds on both presence-absence and visitation interactions (Fig.
-3).
-On the pollinator dependence trade-off, all floral visitor guilds interacted more frequently with plant species with higher pollinator dependence (PC2; Fig.
-3b and Fig.
-3e).
-For presence-absence interactions we found that all Diptera, Coleoptera and non-bee-Hymenoptera guilds interacted more frequently with plants with high flower number and small flowers (flower number - flower size trade-off, PC1; Fig.
-3a) but bees and Lepidoptera interacted slightly more frequently with plant species with low flower number but large flowers.
-For presence-absence interactions on PC3 (style length trade-off; Fig.
-3c), we found that bees interacted clearly more with plant species with long styles and high selfing and the rest of the guilds interacted slightly more with plant species with short styles and low selfing.
-In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-syrphid-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig.
-3d).
-On the style length trade-off, bees, Lepidoptera and non-bee-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while syrphids, non-syrphid-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
-3f).
-
-The additional model for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and visitation rate (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
-3a and Fig.
-3d) were driven by the family Andrenidae, which interacted more frequently on presence-absence interactions with plant species with low number of large flowers (Supplementary Fig.
-S8).
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Fig.
-3 | Interaction (yes/no) and visitation rates across the three main axes of trait variation per floral visitor guild.** Fitted posterior estimates of the presence/absence of interaction (a, b and c) and number of visits (d, e and f) made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
-PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.
-For visualization purposes, due to large differences between the visitation rates of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
-
-#LOAD LIBRARIES 
-#library(phytools)
-#library(ape) #for phylogenetic distance
-#library(dplyr) #data processing
-#library(rtrees) #for phylogenetic distancelibrary(MASS)
-#library(reshape2)
-library(viridis) #COLOUR GGPLOT
-#library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-#library(tidyverse)
-library(patchwork) #panel of plots
-#library(brms)
-#library(cmdstanr)
-
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2)),
-           axis.text=element_text(size = rel(1.8), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(2, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
-           plot.subtitle = element_text(face="bold",size=rel(2))
-     ))
-}
-
-setwd("~/R_Projects/Reproductive Traits")
-
-p1 <- readRDS("Main_Figures/figure_3_1.rds")
-p2 <- readRDS("Main_Figures/figure_3_2.rds")
-p3 <- readRDS("Main_Figures/figure_3_3.rds")
-pp1 <- readRDS("Main_Figures/figure_3_4.rds")
-pp2 <- readRDS("Main_Figures/figure_3_5.rds")
-pp3 <- readRDS("Main_Figures/figure_3_6.rds")
-
-library(patchwork)
-
-combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
-combined + plot_layout(guides = "collect",ncol = 3)
-
-```
-
-\elandscape
-
-**Plant species functional roles.** The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
-S9; interaction frequency ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
-On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers (Supplementary Fig.
-S9a).
-On PC1, specialization showed the opposite trend (Supplementary Fig.
-S9g).
-On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Supplementary Fig.
-S9c).
-Again, specialization showed the opposite trend to interaction frequency (Supplementary Fig.
-S9i).
-
-When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for visitation frequency was best explained by plant height, nectar concentration and style length (Fig.
-4a).
-Specifically, species taller than 3.9m had the highest interaction frequency, while species that were shorter than 3.9m and had a nectar concentration lower than 16% had the lowest interaction frequency.
-Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
-4b).
-Species with a nectar concentration over 49% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49%, more than 21,000 pollen grains per flower and height less than 0.78m had the lowest normalized degree.
-Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
-4c).
-Overall, plant species with the highest specialization were shorter than 1.3m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11% of their fruits.
-In contrast, species taller or equal than 5.1m and with lower than 14 ovules per flower had the lowest specialization values.
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=12,fig.cap= "**Fig.
-4 | Contribution of traits in plant's network roles.** Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
-The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
-Thus, the top node has the mean value of the named trait for the 100% of species.
-Each node has a yes/no question and when the condition is fulfilled, the branch turns to the ‘yes’ direction and when not, to the ‘no’ direction.
-This rationale is followed in all the regression trees as indicated in the first branch division of the topmost node of each tree."}
-
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
-########################################################################################################################################################
-#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
-
-library(rpart.plot)
-library(rpart)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
-nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
-d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
-
-#Set correct colnames for plotting
-colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
-
-colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
-
-colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
-
-set.seed(2)
-tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
-
-set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
-
-set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50) 
-par(mfrow=c(1,3))
-
-rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.45,tweak = 1.25,type = 2) 
-rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.45,tweak = 1.25,type = 2)
-rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.45,tweak = 1.25,type = 2)
-
-```
-
-\elandscape
-
-# DISCUSSION
-
-This study demonstrates that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
-These trade-offs are differentiated along three axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-These reproductive trade-offs helped partly explain the presence of floral visitor interactions, but not their visitation rates.
-However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
-Moreover, we found that the plant species functional roles within pollination networks were best explained by plant size and floral reward related traits.
-
-Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
-Trait variation on these two axes was associated with the ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-The ‘slow’ part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, plant species that employed the ‘fast’ strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
-The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Supplementary Fig.
-S10).
-
-Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (presence-absence of interactions and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies influence plant-pollinator interactions.
-For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
-1 and Supplementary Fig.
-S6).
-This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently [@hegland2005; @lazaro2013; @kaiser2014].
-In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation rates across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
-For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
-3) suggesting possible niche partitioning [@palmer2003; @phillips2020] between these two guilds.
-However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species functional roles (Fig.
-4).
-More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive trade-offs do not.
-
-To conclude, we provide the first description of plant reproductive trade-offs using a large global dataset of plant traits.
-We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
-Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits [@diaz2016; @carmona2021] it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits [@salguero2016].
-Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
-Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators [@gervasi2017; @mackin2021].
-Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
-
-# MATERIALS AND METHODS
-
-**Plant-pollinator network studies.** We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives (e.g., The Web of Life [@fortuna2010] and Mangal [@poisot2016]).
-In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
-
-**Taxonomy of plants and pollinators.** All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020] version _0.9.99_.
-We filled the ‘not found’ searches manually using http://www.theplantlist.org/ and http://www.mobot.org/ for plants and http://www.catalogueoflife.org/ for floral visitors.
-
-**Functional traits.** We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
-These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive biology and 3 vegetative, Supplementary Information).
-For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Supplementary Fig.
-S1 for missing values information for each trait).
-
-**Phylogenetic Distance.** We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package _rtrees_ (https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
-
-\singlespacing
 
@@
 ```
-
-\doublespacing
-
-**Data Imputation.** Trait missing values were imputed with the function _missForest_ [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of _missForest_ [@penone2014].
-To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-Although the variable of autonomous selfing had a high percentage of missing values (68%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
-The categories of ‘none’, ‘low’, ‘medium’ and ‘high’ were converted to representative percentages of each category 0%, 13%, 50.5% and 88% respectively.
-This reduced the percentage of missing values for this column from 68% to 35% and allowed the imputation of this variable.
-However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Supplementary Fig.
-S1).
-Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79% of missing values.
-Further, we conducted an additional imputation process on the subset of species with data for pollen per flower and microliters of nectar.
-This subset comprised 755 species, 8.01% missing values and all traits but milligrams of nectar (~50% of missing values) were included in the imputation process.
-
-**Plant strategies.** We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th–97.5th percentile range [@legendre2012], and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [@revell2012] (version _0.7-70_) with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
-S2).
-We found little difference between the explained variance with the imputed dataset (51.08%) and the dataset without missing values (52.87%).
-In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
-For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
-
-**Phylogenetic signal of traits.** We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] version _0.7-70_ and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-**Network analyses.** Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-These networks were analysed in their qualitative (presence-absence) and quantitative (interaction frequency) form.
-First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
-Second, we analysed the untransformed weighted networks with interaction frequency that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency [@ballantyne2015], interaction frequency can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
-All analyses were conducted in R version _4.0.3_.
-
-**Visitation patterns.** We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
-This finding is consistent with previous research showing that _A.
-mellifera_ was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
-Hence, to control for the effect of _A.
-mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of interaction and visitation rate excluding _A.
-mellifera_.
-We found that _A.
-mellifera_, was partly driving some of the observed trends on PC1 (Supplementary Fig.
-S3).
-However, we did not detect major differences on PC2 and PC3.
-
-We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017] (version _2.14.6_).
-We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
-In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
-We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019] (version _1.7.2_).
-
-**Plant species functional roles.** We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d’) [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008] (version _2.15_).
-
-First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric ~ PC1 + PC2 + PC3).
-For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns section’.
-
-Second, to better understand these complex trait relationships, we used regression trees.
-Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
-We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
-We conducted this analysis using the _rpart_ package [@therneau2015] version _4.1-15_ with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] version _3.0.9_ to plot the regression trees.
-We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
-We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig.
-S4).
-
-# References
-
-<div id ="refs"></div>
-
-# Acknowledgements
-
-This is study was supported by the project SAFEGUARD (101003476 H2020-SFS-2019-2).
-We thank all researchers that made their data available for our analysis.
-We thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
-We also thank Jason Tylianakis for his comments on the manuscript before submission.
-JBL thanks the University of New England for the funding provided to carry out this work.

### 2022-01-26 Manuscript/Lanuza_et_al_2021_Ecol_Letters.Rmd
edits

@@
 
-**Plant-pollinator network studies.** We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
+**Plant-pollinator network studies**
+
+We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
 These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
@@
 
-**Taxonomy of plants and pollinators.** All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020] version _0.9.99_.
+**Taxonomy of plants and pollinators**
+
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020] version _0.9.99_.
 We filled the ‘not found’ searches manually using http://www.theplantlist.org/ and http://www.mobot.org/ for plants and http://www.catalogueoflife.org/ for floral visitors.
 
-**Functional traits.** We selected a total of 19 different functional traits that included both reproductive and vegetative traits (see Table 1 and Supplementary Information).
+**Functional traits**
+
+We selected a total of 19 different functional traits that included both reproductive and vegetative traits (see Table 1 and Supplementary Information).
 From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
@@
 
-**Phylogenetic Distance.** We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package _rtrees_ (https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
+**Phylogenetic Distance**
+
+We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package _rtrees_ (https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
 
@@
 
-**Data Imputation.** Trait missing values were imputed with the function _missForest_ [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
+**Data Imputation**
+
+Trait missing values were imputed with the function _missForest_ [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
 We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of _missForest_ [@penone2014].
@@
 
-**Plant strategies.** We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
+**Plant strategies**
+
+We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
 We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
@@
 
-**Phylogenetic signal of traits.** We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] version _0.7-70_ and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
+**Phylogenetic signal of traits**
+
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] version _0.7-70_ and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
 
-**Network analyses.** Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+**Network analyses**
+
+Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
 These networks were analysed in their qualitative (presence-absence) and quantitative (interaction frequency) form.
@@
 
-**Visitation patterns.** We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
+**Visitation patterns**
+
+We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
 For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
@@
 
-**Plant species functional roles.** We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
+**Plant species functional roles**
+
+We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
@@
 
-**Plant strategies.** The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Fig.
+**Plant strategies**
+
+The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Fig.
 1 and Supplementary Fig.
@@
 
-**Phylogenetic signal of traits.** We found a strong phylogenetic signal (*P* < 0.01) in all quantitative traits (Supplementary Table S5).
+**Phylogenetic signal of traits**
+
+We found a strong phylogenetic signal (*P* < 0.01) in all quantitative traits (Supplementary Table S5).
 The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
@@
 
-**Visitation patterns.** The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall visitation rates (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
+**Visitation patterns**
+
+The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall visitation rates (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
 However, we found relevant trends across the different floral visitor guilds on both presence-absence and visitation interactions (Fig.
@@
 
-**Plant species functional roles.** The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
+**Plant species functional roles**
+
+The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
 S9; interaction frequency ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).

### 2022-01-26 Manuscript/Lanuza_et_al_2021_Ecol_Letters.tex
edits

@@
 
-\textbf{Plant-pollinator network studies.} We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
+\textbf{Plant-pollinator network studies}
+
+We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
 These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
@@
 
-\textbf{Taxonomy of plants and pollinators.} All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain \emph{et al.} n.d.b}) version \emph{0.9.99}.
+\textbf{Taxonomy of plants and pollinators}
+
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain \emph{et al.} n.d.b}) version \emph{0.9.99}.
 We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
 
-\textbf{Functional traits.} We selected a total of 19 different functional traits that included both reproductive and vegetative traits (see Table 1 and Supplementary Information).
+\textbf{Functional traits}
+
+We selected a total of 19 different functional traits that included both reproductive and vegetative traits (see Table 1 and Supplementary Information).
 From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
@@
 
-\textbf{Phylogenetic Distance.} We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life (\protect\hyperlink{ref-smith2018}{Smith \& Brown 2018}; \protect\hyperlink{ref-jin2019}{Jin \& Qian 2019}).
+\textbf{Phylogenetic Distance}
+
+We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life (\protect\hyperlink{ref-smith2018}{Smith \& Brown 2018}; \protect\hyperlink{ref-jin2019}{Jin \& Qian 2019}).
 
@@
 
-\textbf{Data Imputation.} Trait missing values were imputed with the function \emph{missForest} (\protect\hyperlink{ref-stekhoven2012}{Stekhoven \& Bühlmann 2012}) which allows imputation of data sets with continuous and categorical variables.
+\textbf{Data Imputation}
+
+Trait missing values were imputed with the function \emph{missForest} (\protect\hyperlink{ref-stekhoven2012}{Stekhoven \& Bühlmann 2012}) which allows imputation of data sets with continuous and categorical variables.
 We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} (\protect\hyperlink{ref-penone2014}{Penone \emph{et al.} 2014}).
@@
 
-\textbf{Plant strategies.} We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
+\textbf{Plant strategies}
+
+We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
 We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
@@
 
-\textbf{Phylogenetic signal of traits.} We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell 2012}) version \emph{0.7-70} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+\textbf{Phylogenetic signal of traits}
+
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell 2012}) version \emph{0.7-70} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
 
-\textbf{Network analyses.} Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+\textbf{Network analyses}
+
+Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
 These networks were analysed in their qualitative (presence-absence) and quantitative (interaction frequency) form.
@@
 
-\textbf{Visitation patterns.} We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
+\textbf{Visitation patterns}
+
+We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
 For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
@@
 
-\textbf{Plant species functional roles.} We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
+\textbf{Plant species functional roles}
+
+We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies (\protect\hyperlink{ref-dormann2008}{Dormann \emph{et al.} 2008}) with a straightforward ecological interpretation relevant to our research goals.
@@
 
-\textbf{Plant strategies.} The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8\% and 70.97\% of trait variation, respectively (Fig.
+\textbf{Plant strategies}
+
+The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8\% and 70.97\% of trait variation, respectively (Fig.
 1 and Supplementary Fig.
@@
 
-\textbf{Phylogenetic signal of traits.} We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) in all quantitative traits (Supplementary Table S5).
+\textbf{Phylogenetic signal of traits}
+
+We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) in all quantitative traits (Supplementary Table S5).
 The traits that showed the highest phylogenetic signal were ovule number (\(\lambda\) = 1), pollen grains per flower (\(\lambda\) = 1) and plant height (\(\lambda\) = 0.96), followed by flower length (\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73), number of flowers per plant (\(\lambda\) = 0.69) and nectar concentration (\(\lambda\) = 0.65).
@@
 
-\textbf{Visitation patterns.} The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the overall visitation rates (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
+\textbf{Visitation patterns}
+
+The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the overall visitation rates (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
 However, we found relevant trends across the different floral visitor guilds on both presence-absence and visitation interactions (Fig.
@@
 
-\textbf{Plant species functional roles.} The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
+\textbf{Plant species functional roles}
+
+The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
 S9; interaction frequency \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).

### 2022-01-26 Manuscript/Lanuza_et_al_2021_Ecol_Letters.Rmd
edits for Ecol Letters

@@
 Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases [e.g., TRY @kattge2011; and COMPADRE @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
+With the recent availability of large trait databases [e.g., TRY, @kattge2011; and COMPADRE, @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
 However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
@@
 Remarkably, the combination of traits has shown to increase the predictive power of the network interactions [@eklof2013].
-**Moreover, the position in the trait space can determine plant and pollinator species functional roles [@dehling2016].
-Therefore, by considering the position in the reproductive trait space we could progress our understanding of the plant species functional roles within plant-pollinator interaction networks.
-Nonetheless, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.**
+**Moreover, the position in the trait space can determine plant and pollinator species’ functional roles [@dehling2016].
+Therefore, by considering the multidimensional reproductive trait space we could progress our understanding of plant-pollinator associations.
+Importantly, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.**
 
@@
 From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
+Note that autonomous selfing was recorded quantitatively (fruit set) and qualitatively because this trait was rarely available in its numerical form.
 The 3 remaining traits, were vegetative traits that are commonly used to characterize the global spectrum of plant form and function and represent the fast-slow continuum of trait variation (e.g., short-lived versus perennial species).
 For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Fig.
+From a total of 30,120 cells (20 columns x 1506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Fig.
 S1 for missing values information for each trait).
@@
 n_of_records <- subset(missing.values, isna=="FALSE")
-Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
-           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")
-
-Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Compatibility system", "Breeding system", " ", " ", " ", " ", " ")
+Trait <- linebreak(c("Plant height \n (m)", "Flower width \n (mm)", "Flower length \n (mm)", "Inflorescence width \n (mm)", "Style length \n (mm)", "Ovules per flower",
+           "Flowers per plant", "Nectar \n ($\\mu$l)", "Nectar \n (mg)", "Nectar concentration \n ($\\%$)", "Pollen grains \n per flower", "Autonomous selfing \n (fruit set)"),align = c("c"))
+
+Trait1 <- linebreak(c("Lifepan", "Life form", "Flower \n shape", "Flower \n symmetry", "Nectar", "Compatibility \n system", "Breeding \n system", "Autonomous \n selfing", " ", " ", " ", " "),align = c("c"))
 
 T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-           "Presence \n Absence", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " ", ""),align = c("l"))
+           "Presence \n Absence", "Self-incompatible \n Part.
+self-compatible \n Self-compatible", "Hermaphrodite \n Monoecious \n Dioecious","None \n Low \n Medium \n High", " ", " ", " ", ""),align = c("l"))
 
@@
 
-Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology","","","","", ""),align = c("c"))
+Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology","Reproductive \n biology","","","", ""),align = c("c"))
 
@@
 
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table 1 | Quantitative and categorical traits used in this study.}") %>%
+kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table 1} Plant functional traits used in this study.") %>%
 kable_styling(full_width = F,font_size = 10) %>%
@@
 To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-Although the variable of autonomous selfing had a high percentage of missing values (68%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
-The categories of ‘none’, ‘low’, ‘medium’ and ‘high’ were converted to representative percentages of each category 0%, 13%, 50.5% and 88% respectively.
+Although the variable of autonomous selfing had a high percentage of missing values (68%), we were able to solve this by back transforming a complementary qualitative column of autonomous selfing to numerical.
+The categories of ‘none’, ‘low’, ‘medium’ and ‘high’ were converted to representative percentages of each category 0%, 13%, 50.5% and 88%, respectively.
 This reduced the percentage of missing values for this column from 68% to 35% and allowed the imputation of this variable.
-However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Supplementary Fig.
+However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Fig.
 S1).
@@
 We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the reproductive spectrum of trait variation.
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
@@
 Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [@revell2012] (version _0.7-70_) with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
+We performed the pPCA using the function _phyl.pca_ from the package _phytools_ version _0.7-70_ [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
+Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
 S2).

### 2022-01-26 Manuscript/Lanuza_et_al_2021_Ecol_Letters.tex
edits for Ecol Letters

@@
 Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY \protect\hyperlink{ref-kattge2011}{Kattge \emph{et al.} 2011}; and COMPADRE \protect\hyperlink{ref-salguero2015}{Salguero-Gómez \emph{et al.} 2015}), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function (\protect\hyperlink{ref-diaz2016}{Díaz \emph{et al.} 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}; \protect\hyperlink{ref-bruelheide2018}{Bruelheide \emph{et al.} 2018}; \protect\hyperlink{ref-carmona2021}{Carmona \emph{et al.} 2021}).
+With the recent availability of large trait databases (e.g., TRY, \protect\hyperlink{ref-kattge2011}{Kattge \emph{et al.} 2011}; and COMPADRE, \protect\hyperlink{ref-salguero2015}{Salguero-Gómez \emph{et al.} 2015}), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function (\protect\hyperlink{ref-diaz2016}{Díaz \emph{et al.} 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}; \protect\hyperlink{ref-bruelheide2018}{Bruelheide \emph{et al.} 2018}; \protect\hyperlink{ref-carmona2021}{Carmona \emph{et al.} 2021}).
 However, most studies have focused on vegetative traits such as leaf (\protect\hyperlink{ref-wright2004}{Wright \emph{et al.} 2004}), wood (\protect\hyperlink{ref-chave2009}{Chave \emph{et al.} 2009}), or root (\protect\hyperlink{ref-laughlin2021}{Laughlin \emph{et al.} 2021}) trade-offs with little or no attention given to reproductive traits (\protect\hyperlink{ref-evojtko2020}{E-Vojtkó \emph{et al.} 2020}; \protect\hyperlink{ref-roddy2021}{Roddy \emph{et al.} 2021}) which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
@@
 Remarkably, the combination of traits has shown to increase the predictive power of the network interactions (\protect\hyperlink{ref-eklof2013}{Eklöf \emph{et al.} 2013}).
-\textbf{Moreover, the position in the trait space can determine plant and pollinator species functional roles (\protect\hyperlink{ref-dehling2016}{Dehling \emph{et al.} 2016}).
-Therefore, by considering the position in the reproductive trait space we could progress our understanding of the plant species functional roles within plant-pollinator interaction networks.
-Nonetheless, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.}
+\textbf{Moreover, the position in the trait space can determine plant and pollinator species' functional roles (\protect\hyperlink{ref-dehling2016}{Dehling \emph{et al.} 2016}).
+Therefore, by considering the multidimensional reproductive trait space we could progress our understanding of plant-pollinator associations.
+Importantly, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.}
 
@@
 
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain \emph{et al.} n.d.b}) version \emph{0.9.99}.
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain \emph{et al.} n.d.}) version \emph{0.9.99}.
 We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
@@
 From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
+Note that autonomous selfing was recorded quantitatively (fruit set) and qualitatively because this trait was rarely available in its numerical form.
 The 3 remaining traits, were vegetative traits that are commonly used to characterize the global spectrum of plant form and function and represent the fast-slow continuum of trait variation (e.g., short-lived versus perennial species).
 For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8\% of the dataset, see Fig.
+From a total of 30,120 cells (20 columns x 1506 species) we were able to fill 24,341 cells (80.8\% of the dataset, see Fig.
 S1 for missing values information for each trait).
@@
 
-\caption{\label{tab:unnamed-chunk-1}\textbf{Table 1 | Quantitative and categorical traits used in this study.}}
+\caption{\label{tab:unnamed-chunk-1}\textbf{Table 1} Plant functional traits used in this study.}
 \centering
@@
 \midrule
-\textbf{Vegetative} & Plant height (m) & \textbf{Vegetative} & Lifepan & \makecell[l]{Short-lived \\ Perennial}\\
+\textbf{Vegetative} & \makecell[c]{Plant height \\ (m)} & \textbf{Vegetative} & Lifepan & \makecell[l]{Short-lived \\ Perennial}\\
 \addlinespace
-\textbf{Floral} & Flower width (mm) & \textbf{Vegetative} & Life form & \makecell[l]{Herb \\ Shrub \\ Tree}\\
+\textbf{Floral} & \makecell[c]{Flower width \\ (mm)} & \textbf{Vegetative} & Life form & \makecell[l]{Herb \\ Shrub \\ Tree}\\
 \addlinespace
-\textbf{Floral} & Flower length (mm) & \textbf{Floral} & Flower shape & \makecell[l]{Brush \\ Campanulate \\ Capitulum \\ Open \\ Papilionaceous \\ Tube}\\
+\textbf{Floral} & \makecell[c]{Flower length \\ (mm)} & \textbf{Floral} & \makecell[c]{Flower \\ shape} & \makecell[l]{Brush \\ Campanulate \\ Capitulum \\ Open \\ Papilionaceous \\ Tube}\\
 \addlinespace
-\textbf{Floral} & Inflorescence width (mm) & \textbf{Floral} & Flower symmetry & \makecell[l]{Actinomorphic \\ Zygomorphic}\\
+\textbf{Floral} & \makecell[c]{Inflorescence width \\ (mm)} & \textbf{Floral} & \makecell[c]{Flower \\ symmetry} & \makecell[l]{Actinomorphic \\ Zygomorphic}\\
 \addlinespace
-\textbf{Floral} & Style length (mm) & \textbf{Floral} & Nectar & \makecell[l]{Presence \\ Absence}\\
+\textbf{Floral} & \makecell[c]{Style length \\ (mm)} & \textbf{Floral} & Nectar & \makecell[l]{Presence \\ Absence}\\
 \addlinespace
-\textbf{Floral} & Ovules per flower & \textbf{\makecell[c]{Reproductive \\ biology}} & Compatibility system & \makecell[l]{Self-incomp. \\ Part. self-comp. \\ Self-comp.}\\
+\textbf{Floral} & Ovules per flower & \textbf{\makecell[c]{Reproductive \\ biology}} & \makecell[c]{Compatibility \\ system} & \makecell[l]{Self-incompatible \\ Part.
+self-compatible \\ Self-compatible}\\
 \addlinespace
-\textbf{Floral} & Flowers per plant & \textbf{\makecell[c]{Reproductive \\ biology}} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious}\\
+\textbf{Floral} & Flowers per plant & \textbf{\makecell[c]{Reproductive \\ biology}} & \makecell[c]{Breeding \\ system} & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious}\\
 \addlinespace
-\textbf{Floral} & Nectar ($\mu$l) & \textbf{} &  & \\
+\textbf{Floral} & \makecell[c]{Nectar \\ ($\mu$l)} & \textbf{\makecell[c]{Reproductive \\ biology}} & \makecell[c]{Autonomous \\ selfing} & \makecell[l]{None \\ Low \\ Medium \\ High}\\
 \addlinespace
-\textbf{Floral} & Nectar (mg) & \textbf{} &  & \\
+\textbf{Floral} & \makecell[c]{Nectar \\ (mg)} & \textbf{} &  & \\
 \addlinespace
-\textbf{Floral} & Nectar concentration ($\%$) & \textbf{} &  & \\
+\textbf{Floral} & \makecell[c]{Nectar concentration \\ ($\%$)} & \textbf{} &  & \\
 \addlinespace
-\textbf{Floral} & Pollen grains per flower & \textbf{} &  & \\
+\textbf{Floral} & \makecell[c]{Pollen grains \\ per flower} & \textbf{} &  & \\
 \addlinespace
-\textbf{\makecell[c]{Reproductive \\ biology}} & Autonomous selfing (fruit set) & \textbf{} &  & \\
+\textbf{\makecell[c]{Reproductive \\ biology}} & \makecell[c]{Autonomous selfing \\ (fruit set)} & \textbf{} &  & \\
 \bottomrule
@@
 We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} (\protect\hyperlink{ref-penone2014}{Penone \emph{et al.} 2014}).
-To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} (\protect\hyperlink{ref-santos2018}{Chamberlain \emph{et al.} n.d.a}) based on a previous conceptual framework that considers phylogenetic eigenvectors (\protect\hyperlink{ref-diniz-filho2012}{Diniz-Filho \emph{et al.} 2012}).
-Although the variable of autonomous selfing had a high percentage of missing values (68\%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
-The categories of `none,' `low,' `medium' and `high' were converted to representative percentages of each category 0\%, 13\%, 50.5\% and 88\% respectively.
+To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} (\protect\hyperlink{ref-santos2018}{Chamberlain \emph{et al.} 2018}) based on a previous conceptual framework that considers phylogenetic eigenvectors (\protect\hyperlink{ref-diniz-filho2012}{Diniz-Filho \emph{et al.} 2012}).
+Although the variable of autonomous selfing had a high percentage of missing values (68\%), we were able to solve this by back transforming a complementary qualitative column of autonomous selfing to numerical.
+The categories of `none,' `low,' `medium' and `high' were converted to representative percentages of each category 0\%, 13\%, 50.5\% and 88\%, respectively.
 This reduced the percentage of missing values for this column from 68\% to 35\% and allowed the imputation of this variable.
-However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Supplementary Fig.
+However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Fig.
 S1).
@@
 We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the reproductive spectrum of trait variation.
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
@@
 Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell 2012}) (version \emph{0.7-70}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams 2010}).
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} version \emph{0.7-70} (\protect\hyperlink{ref-revell2012}{Revell 2012}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams 2010}).
+Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
 S2).
@@
 \leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
-Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., \emph{et al.} (n.d.a).
-Package {`{PVR}.'} R package version 0.3 (2018).~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}.
+Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., \emph{et al.} (2018).
+Package {`{PVR}.'} R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
-Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., \emph{et al.} (n.d.b).
+Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., \emph{et al.} (n.d.).
 Taxize: {Taxonomic} information from around the web.

### 2022-01-27 Manuscript/Lanuza_et_al_2021_Ecol_Letters.tex
edits

@@
 
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain \emph{et al.} n.d.}) version \emph{0.9.99}.
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain \emph{et al.} 2020}) version \emph{0.9.99}.
 We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
+
+\newpage
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
-Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., \emph{et al.} (n.d.).
+Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., \emph{et al.} (2020).
 Taxize: {Taxonomic} information from around the web.
-R package version 0.9.99 (2020).~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}.
+R package version 0.9.99.~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}.
 

### 2022-01-27 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
edits for Ecol Letters
edits

@@
 \captionsetup[table]{font={stretch=1.2}}
-
-\renewcommand{\figurename}{}
-
-```{r echo=FALSE, out.width='100%', fig.align='center'}
-knitr::include_graphics('../Images/pnas-logo.png')
-```
 
@@
 #Images were made by Paula Martin
+PC$S[,1] <- -PC$S[,1]
 
@@
 
-  plot <- plot + geom_point(data=dat, aes(x, y),size=0.95, color="black")
+  plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
 
@@
   # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
 
   #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
 
@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.85,5.5,5.3,5.5,6.1,5.75,5.8,6)), y = -(PCAloadings$PC2*c(4.8,4.8,4.65,5.65,5,5.1,5.75,5)+c(0,0,0,0,0,0,0,0)),
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,4.8,4.8,5.5,5,5.5,5.8,6.5)), y = -(PCAloadings$PC2*c(4.8,4.4,4.15,5.35,5,4.7,5.75,6)+c(0,0,0,0,0,0,0,0)),
                           label = PCAloadings$Variables, color="black",fontface =2,size=4.5)

### 2022-01-27 Supplementary_Material/trial.Rmd
edits

--- 2022-01-27 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
@@
 ---
-#title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant reproductive traits determine interactions with floral visitors}
-
-output: 
-  pdf_document:
-    extra_dependencies: ["float"]
-header-includes:
-- \usepackage{pdflscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
-- \usepackage{float}
-- \usepackage{caption}
-- \usepackage{setspace}\doublespacing
-- \usepackage{soul}
-- \floatplacement{figure}{H}
-- \usepackage{afterpage}
-- \usepackage{placeins}
-- \usepackage{graphicx}
-- \usepackage{floatpag}
-
-fontsize: 12pt
-
+title: "Untitled"
+output: html_document
 ---
-
-```{r echo=FALSE,warning=FALSE}
-knitr::opts_chunk$set(fig.pos = "h", out.extra = "")
-
-```
-
-\captionsetup[figure]{labelformat=empty}
-\captionsetup[table]{labelformat=empty}
-\captionsetup[table]{font={stretch=1.2}}
-
-\singlespacing
-
-\vspace{2cm}
-
-# Supplementary information for:
-
-## Trade-offs among plant reproductive traits determine interactions with floral visitors
-
-\textbf{Jose B. Lanuza*, Romina Rader, Jamie Stavert, Liam K. Kendall, Manu E. Saunders and Ignasi Bartomeus}
-
-\textbf{*Corresponding author}
-**E-mail: barragansljose@gmail.com**
-
-**This pdf includes:**
-
-Supplementary text
-
-Tables S1 to S5
-
-Figures S1 to S10
-
-\doublespacing
-
-<!--
-
-__Supplementary text__
-
-Description of the traits compiled in this study with an illustrative figure of the main flower morphologies (Supplementary text Fig 1)
-
-\doublespacing
-\singlespacing
-
-__Supplementary Tables__
-
-Supplementary Table S1: List of the 28 plant-pollinator studies used to build the plant trait database
-
-Supplementary Table S2: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species
-
-Supplementary Table S3: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity
-
-Supplementary Table S4: Statistical association between the different categorical variables and the fisrt three main axes of trait variation with the full set of species
-
-Supplementary Table S5: Phylogenetic signal of the different quantitative traits
-
-\doublespacing
-\singlespacing
-
-__Supplementary Figures__
-
-Supplementary Fig. S1: Percentage of present and missing values of the different plant traits
-
-Supplementary Fig. S2: Phylogenetic informed principal component analysis for the species that did not have missing values
-
-Supplementary Fig. S3: Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation
-
-Supplementary Fig. S4: Regression tree analyses
-
-Supplementary Fig. S5: PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species
-
-Supplementary Fig. S6: Phylogenetic informed principal component analysis for the subset of species with floral rewards.
-
-Supplementary Fig. S7: Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species
-
-Supplementary Fig. S8: Presence-absence of interaction and visitation rate of the main bee families on the main axes of trait variation
-
-Supplementary Fig. S9:  Plant species level metrics across the three main axes of trait variation
-
-Supplementary Fig. S10: Pearson correlation between the product of flower number-flower size and autonomous selfing level
-
--->
-
-\newpage
-
-## Supplementary Information Text
-
-__Description of the traits compiled in this study__
-
-_Reproductive traits_
-
--	Breeding system: The different plant species were classified in hermaphrodite, dioecious and monoecious species.
-Intermediate breeding systems or more complex ones were also annotated but all the species were divided into these three main categories for simplicity of the analysis.
-
--	Selfing level: We recorded the selfing level of the different species with both quantitative and qualitative data.
-The qualitative data was divided in four main categories, high selfers, medium selfers, low selfers and none which was for the species that were unable to self-pollinate.
-In addition, quantitative data was also divided into these four categories with the following criteria: from 0% to lower than 1% ‘none’, from 1% to 25% ‘low’, from 26% to 75% ‘medium’ and from 76% to 100%  ‘high’.
-
--	Compatibility system: The different species were divided in three main categories in order to know their ability to self-pollinate.
-These categories were self-compatible, partially self-compatible and self-incompatible species.
-The field of selfing level is partly complementary to the compatibility system but is important to note that not all the self-compatible species or partially self-compatible species will self-pollinate.
-
-_Floral traits_
-
--	Flower symmetry: We also recorded if the flowers were bilaterally symmetrical “zygomorphic” or were radially symmetrical “actinomorphic”.
-
--	Flower and inflorescence size: We searched for flower length and flower and inflorescence width (mm) for all species.
-When possible, we calculated the not found measurements with the help of online images and  the software ImageJ.
-
--	Flower number per plant: We compiled information about the number of flowers per plant for all species.
-However, this field was rare to find and we also used online images of the different species in order to calculate rough numbers of flowers per plant.
-We referenced all the filled fields in order to be able to follow the images that were used for these counts.
-It is important to note, that these numbers are not pretended to be the exact number of flowers per species but an approximate indicator of the reproductive investment for the different species that allow the macroecological analysis of this field.
-
--	Ovule number: We searched for the number of ovules per flower for all the different species.
-The number of ovules of Asteraceae species are considered as the total number of ovules per capitulum.
-Many species were filled by genus or family level because the number of ovules in this taxonomic groups is considered to be mostly constant (e.g., Lamiaceae Boraginaceae or Apiaceae).
-
--	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape.
-We divided the flowers in 8 main different categories: open, bowl, tube, campanulate, funnelform, papilionaceous, brush and capitulum.
-However, we ended up groupping all flowers on the following 6  morphological groups for analyses: tube, papilonaceous, open, capitulum, campanulate and brush (Supplementary Information Text Fig.
-1).
-
-```{r pressure, echo=FALSE, fig.cap="", out.width = '65%',fig.align='center', fig.cap="\\textbf{Supplementary Information Text Fig.
-1.}  Main floral morphologies considered in this study.
-All species were groupped within these categories for analysis: (a) tube, (b) papilonaceous, (c) open, (d) capitulum, (e) campanulate and (f) brush."}
-knitr::include_graphics("../Images/flower_shapes.png")
-```
-
--	Style length: The length of the style (mm) of the different species was also included. When possible, we calculated style length from images and illustrations on the online floras.
-
-- Nectar provision: We recorded the presence and absence of nectar for all species.
-In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration.
-In general terms, nectar data was rarely present and we tried to minimise the loss of information by filling some species at family level.
-For instance, Solanaceae species are described as nectarless, and species that belonged to this family were recorded with ‘absence’ of nectar.
-
-- Pollen grains per flower: We recorded pollen grains per flower for all species but this field was rarely described in the literature.
-When just the pollen:ovule ratio was found we converted it back to pollen grains by multiplying it by the average ovule number found for each species.
-
-_Vegetative traits_
-
-- Life form, life span and plant height: We divided the different plant species in 4 main categories: herbs, vines, shrubs and trees.
-Moreover, we also divided the species between short-lived species (annual, biennial and short-lived perennials) and perennial species (long-lived).
-Finally, we also searched for the average height (m) of the different species and annotated the maximum and minimum height when possible.
-We conducted the average between the maximum and minimum height to get an approximate average height of the species when the average was not indicated.
-
-\begin{landscape}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = "left"}
-setwd("~/R_Projects/Reproductive Traits")
-library(kableExtra)
-
-#Create data.frame with references
-
-`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1", "1", "1", "1", "1", "1", "1", "3", "1",
-                          "1", "1")
-
-#`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))
-
-`Network type` <- c(rep("Weighted web",  18), rep("Unweighted web",  4), "Weighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Weighted metaweb")
-
-`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
-                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard", "Bek", "Kato", "Kevan", "Ramirez",
-                    "Inouye","McMullen", "Primack", "Ramirez", "Robertson", "Traveset")
-
-Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003,2006,2000,1970,1989,1990, 1993, 1983, 1992, 1929, 2013)
-
-#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
-#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
-#"USA", "Ecuador")
-
-DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
-"https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
-"https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
-"/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
-"https://doi.org/10.1111/j.1365-2745.2010.01732.x", "https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510",
-"https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis", "Unpublished, Master thesis", "http://hdl.handle.net/2433/156116",
-"https://doi.org/10.2307/2258569", "https://doi.org/10.2307/2388282", "http://hdl.handle.net/2433/156099", "https://biostor.org/reference/244737", "https://doi.org/10.1080/0028825X.1983.10428561",
-"https://doi.org/10.1111/j.1095-8339.1992.tb00294.x", "https://doi.org/10.5962/bhl.title.11538", "https://doi.org/10.1098/rspb.2012.3040")
-
-references <- data.frame(`First author`, Year, `Number of networks`,`Network type`,   DOI)
-
-colnames(references) <- c("First author", "Year", "Web N.",  "Network type",  "DOI")
-
-library(dplyr)
- references %>%
- arrange(`First author`)%>%
-kable("latex", longtable = T, booktabs = T,linesep = "\\addlinespace",
-             caption = "\\textbf{Table S1.
-List of the 28 plant-pollinator studies used to build the plant trait database.
-Each study is shown with the first author that conducted the study, number of networks or metawebs that contains, type of information that contains (weighted or unweighted),  the structure (web or metaweb), year of publication and digital object identifier or permanent link for each study.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, repeat_header_method="replace" ,full_width=F,position = "left")
-
-```
-
-\end{landscape}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
- kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S2.
-Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Microlitres of Nectar per flower" , "Pollen per flower","Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
-kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S3.
-Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-d <- readRDS("Data/RData/table_categorical_tukey_test.rds")
-
-#Again im getting the same error on this rmd so I run it on another one, save the dataframe and plot it here
-
-#Plot table
-#Add latex format in markdown
-
-kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Table S4.
-Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-#SELFING
-selfing <- readRDS("Data/RData/selfing_phylo.rds")
-#FLOWER NUMBER
-flower_n <- readRDS("Data/RData/flower_n_phylo.rds")
-#INFLO WIDTH
-inflow_width <- readRDS("Data/RData/inflow_width_phylo.rds")
-#FLOWER WIDTH
-flower_width <- readRDS("Data/RData/flower_width_phylo.rds")
-#FLOWER LENGHT
-flower_length <- readRDS("Data/RData/flower_length_phylo.rds")
-#STYLE LENGTH
-style_n <- readRDS("Data/RData/style_n_phylo.rds")
-#OVULE NUMBER
-ovule_n <- readRDS("Data/RData/ovule_n_phylo.rds")
-#PLANT HEIGHT
-plant_height <- readRDS("Data/RData/plant_height_phylo.rds")
-#POLLEN
-pollen <- readRDS("Data/RData/pollen_phylo.rds")
-#Nectar ul
-nectar_ul <- readRDS("Data/RData/Nectar_ul_phylo.rds")
-
-#Not included at the end
-#Nectar mg
-#nectar_mg <- readRDS("Data/RData/Nectar_mg_phylo.rds")
-#Nectar concentration
-nectar_con <- readRDS("Data/RData/Nectar_concentration_phylo.rds")
-
-#Select two decimals function
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-#LABELS
-label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Nectar per flower ($\\mu$l)", "Nectar concentration ($\\%$)","Pollen grains per flower")
-#LAMBDA
-lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, nectar_ul$lambda, nectar_con$lambda, pollen$lambda)
-#P-VALUE
-p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P,nectar_ul$P,  nectar_con$P, pollen$P)
-
-tabla <- data.frame(label, specify_decimal(lambda,2), specify_decimal(p_value,2))
-
-colnames(tabla) <- c("Functional traits", "Lambda", "P-value")
-
-kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,caption = "\\textbf{Table S5. Phylogenetic signal of the different quantitative traits.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Fig. S1.} Percentage of present and missing values of the different plant traits."}
-
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-
-########################################################################################################################################################
-#SCRIPT FOR DATA IMPUTATION
-########################################################################################################################################################
-#1) READ TRAIT DATA
-
-#2) CLEAN DATA AND RENAME LEVELS
-
-#3) EXPLORE PATTERNS OF MISSING DATA
-
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-
-#5) ICLUDE EIGENVALUES IN RAWDATA TO IMPROVE IMPUTATION OURPUT
-
-#6) IMPUTE DATA
-
-#7) SAVE IMPUTED DATA 
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(missMDA) #For missing values
-library(FactoMineR) #Produce pca biplot with individuals and variables
-library(factoextra)
-library(ggpubr) 
-library(missForest) #random forst imputation
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(ape)
-library(PVR) #calculate eigen vectors and add them as a column in the imputation, seems to improve output
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-str(trait_data_1)
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-levels(as.factor(trait_filtered$Info_level)) #checking levels
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-str(trait_filtered_2)
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-                        "Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-levels(as.factor(t$Breeding_system))
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-levels(as.factor(t$Flower_morphology))
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-levels(as.factor(t$lifespan))
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-#Explore patterns of missing data
-missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)
-sort(missing_data[missing_data >= 0], decreasing=T)
-#nectar values all above 50% except presence/absence
-#then, just one cololumn with 68% missing data, then one with 35% and then 20% and 10%. The rest under 5%.
-#it is recommended to remove columns over 50% but we are particulary interested in having numeric levels of quantitative selfing 
-#we are going to work just with presence/absence of nectar
-#we will perform further analysis just with a subset with the quantitative values o nectar (very interesting data and diffciult to obtain)
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-         "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-         "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-         "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-         "Pollen_per_flower")]
-
-#check missing data now
-missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)*100
-sort(missing_data[missing_data >= 0], decreasing=T)
-
-missing_data <- unlist(lapply(t, function(x) nrow(t)-sum(is.na(x))))
-sum(missing_data)
-
-#Number of missing values on the datset
-#vis_miss(t[,c(6:20)])
-#9.9% percentage of missing values]
-
-#Checking number of filled cells/ just selecting variables used in the manuscript; nectar ul should be accounted too and it has been considered but
-#not added to run this code
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-str(t)
-
-#Impute data considering phylogenetic distance of species
-#it improves quality of imputation
-#https://doi.org/10.1111/2041-210X.12232 see ref for method comparisons with and without imputation
-
-#Multiple imputation process with phylogeny --> Missforest
-#https://doi.org/10.1111/2041-210X.12232
-#althought it does not have an option we are going to add it as a column
-
-#Before data imputation I need to calculate the phylo of the species
-#remove not found species that do not run with get tree
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-levels(factor(t$Species_all))
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-#Select just columns with traits
-t <- t[c("Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-         "Pollen_per_flower")]
-
-#################################################
-#3)SUMMARY OF THE DATA|ALL COLS CONSIDERED!
-#################################################
-##Number of filled cells
-#nrow(t) * 16 - sum(is.na(t))#[1] 20737
-##Dimension of the dataset
-#nrow(t) * 16#[1] 24096
-##Number of missing values
-#sum(is.na(t))#[1] 3359
-##Percentage of filled cells
-#sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 86.87993
-##Percentage of missing values
-#sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 13.12007
-#
-#
-
-#Function to specify number of decimals
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-no_missing <- specify_decimal(sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
-missing <- specify_decimal(sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
-
-colnames(t) <- c("Breeding system","Compatibility system",
-         "Autonomous selfing qualitative","Autonomous selfing quantitative", "Flower shape", "Flower symmetry", 
-         "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 
-         "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar per flower (microlitres)", "Nectar per flower (miligrames)", "Nectar concentration (%)", "Pollen grains per flower")
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-levels <-
-  (missing.values  %>% filter(isna == T) %>% arrange(desc(pct)))$key
-
-percentage.plot <- missing.values %>%
-  ggplot() +
-  geom_bar(aes(x = reorder(key, desc(pct)), 
-               y = pct, fill=isna), 
-           stat = 'identity', alpha=0.8) +
-  scale_x_discrete(limits = levels) + theme_bw()+
-  scale_fill_manual(name = "", 
-                    values = c('#57a340', '#d24513'), labels = c("Present values", "Missing values")) +
-  coord_flip() +
-  labs(title = "", x =
-         '', y = "")+  scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
-  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))
-
-percentage.plot
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig.
-S2.}  Phylogenetic informed principal component analysis for the species that did not have missing values."}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_complete_cases.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-#PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-pc3 <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.015, 0.03, 0.07), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,5.2,5,5.25,6.3,6)), y = -(PCAloadings$PC2*c(4,4.75,4,4.5,5,5.5)+c(0,0,0,0,-0.04,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-pc3(PC)
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24,  fig.cap="\\textbf{Fig.
-S3.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation.
-The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates."}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot_apis <- readRDS("Plot_apis_non_apis.rds")
-
-plot_apis
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig.
-S4.} Regression tree analyses.
-Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
-"}
-
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
-########################################################################################################################################################
-#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
-
-library(rpart.plot)
-library(rpart)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
-nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
-d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")
-
-#run  regression trees of the 3 metrics
-set.seed(1)
-tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0054559,minbucket=50)
-
-set.seed(1)
-tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0084459,minbucket=50)
-
-set.seed(1)
-tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0072192 , minbucket=50) #10
-
-#NECTAR AND POLEN DATA
-v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
-nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
-d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
-
-#Set correct colnames for plotting
-colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-set.seed(2)
-tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
-
-set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
-
-set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)
-
-par(mfrow=c(3,2))
-
-rpart.plot(tree_1, box.palette="GnOr", main="A Interaction frequency for all species", cex.main=1.85,tweak = 1.10) 
-rpart.plot(tree1, box.palette="GnOr", main="B Interaction frequency for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-rpart.plot(tree_2, box.palette="GnOr", main="C Normalized degree for all species", cex.main=1.85,tweak = 1.10)
-rpart.plot(tree2, box.palette="GnOr", main="D Normalized degree for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-rpart.plot(tree_3, box.palette="GnOr", main="E Specialization for all species", cex.main=1.85,tweak = 1.10) 
-rpart.plot(tree3, box.palette="GnOr", main="F Specialization for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig.
-S5.} PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species."}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-pc3 <- function(PC, x="PC1", y="PC3") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC3 ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,4.8,7.1,5.5)), y = -(PCAloadings$PC2*c(-3.2,4.5,3.75,8.4,5,5.5)+c(0,0,0,0,-0.08,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-pc3(PC)
-
-```
-
-\newpage
 
@@
 ```
-
-\newpage
-\thispagestyle{empty}
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig.
-S7.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species.
-Categories that differ significantly are denoted with a different letter."}
-
-########################################################################################################################################################
-#CORRELATION BETWEEN QUALITATIVE VARIABLES AND PC's
-########################################################################################################################################################
-#NOTES
-#I did not include the qualitative variables when I prepare the data for the PPCA
-#So I have to recalculate the ata here with the qualitative variables
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(emmeans)
-library(ggplot2)
-library(patchwork)
-library(dplyr)
-
-theme_ms <- function(base_size=10, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(1.3)),
-           axis.text=element_text(size = rel(1.1), color = "black"),
-           panel.border=element_rect(color="black",size=1.2),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           legend.position = "none",
-           plot.title = element_text(face = "bold",size = rel(1.55)),
-           plot.subtitle = element_text(face = "bold",size = rel(1.4))
-     ))
-}
-
-########################################################################################################################################################
-setwd("~/R_Projects/Reproductive Traits")
-
-#LOAD DATA
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-dat <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-########################################################################################################################################################
-#remove not found species, cannot do PCA with unequal numbers of rows
-cols.num <- c("Family_all","Genus_all","Species_all")
-dat[cols.num] <- sapply(dat[cols.num],as.character)
-dat$Species_all <- gsub("Species_all_", "", dat$Species_all)
-########################################################################################################################################################
-#3) REMOVE OUTLIERS, OUT OF 2.5-97.5 RANGE WHICH HELPS IMPUTATION PROCESS. SEE ARTICLE FOR REF.
-########################################################################################################################################################
-dat_cleaning <- dat[,]
-#CHECK LEVELS
-
-dat_cleaning_1 <- dat_cleaning %>%
-  filter(between(Flowers_per_plant, quantile(Flowers_per_plant, 0.025), quantile(Flowers_per_plant, 0.975)))
-
-dat_cleaning_2 <- dat_cleaning_1 %>%
-  filter(between(Corolla_diameter_mean, quantile(Corolla_diameter_mean, 0.025), quantile(Corolla_diameter_mean, 0.975)))
-
-dat_cleaning_3 <- dat_cleaning_2 %>%
-  filter(between(Style_length, quantile(Style_length, 0.025), quantile(Style_length, 0.975)))
-
-dat_cleaning_4 <- dat_cleaning_3 %>%
-  filter(between(Ovule_number, quantile(Ovule_number, 0.025), quantile(Ovule_number, 0.975)))
-
-dat_cleaning_5 <- dat_cleaning_4 %>%
-  filter(between(Plant_height_mean_m, quantile(Plant_height_mean_m, 0.025), quantile(Plant_height_mean_m, 0.975)))
-
-final_d <- dat_cleaning_5[,]
-
-pca_data <- as.data.frame(phyl_pca_forest$S)
-
-d <- cbind(final_d, pca_data)
-
-#Prepare qualitative variables
-d$Compatibility_system[d$Compatibility_system=="dioecious"] <- "Unisexual flowers"
-d$Compatibility_system[d$Compatibility_system=="monoecious"] <- "Unisexual flowers"
-d$Compatibility_system[d$Compatibility_system=="partially_self_compatible"] <- "Partially self compatible"
-d$Compatibility_system[d$Compatibility_system=="self_compatible"] <- "Self compatible"
-d$Compatibility_system[d$Compatibility_system=="self_incompatible"] <- "Self incompatible"
-d$Compatibility_system <- factor(d$Compatibility_system, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-d$life_form[d$life_form=="herb"] <- "Herb"
-d$life_form[d$life_form=="shrub"] <- "Shrub"
-d$life_form[d$life_form=="tree"] <- "Tree"
-d$life_form[d$life_form=="vine"] <- "Shrub"
-
-d$Flower_symmetry[d$Flower_symmetry=="actinomorphic"] <- "Actinomorphic"
-d$Flower_symmetry[d$Flower_symmetry=="zygomorphic"] <- "Zygomorphic"
-
-d$Flower_symmetry[d$Flower_symmetry=="Funnelform"] <- "Campanulate"
-d$Flower_symmetry[d$Flower_symmetry=="Spike"] <- "Brush"
-
-d$Flower_morphology[d$Flower_morphology=="Funnelform"] <- "Campanulate"
-d$Flower_morphology[d$Flower_morphology=="Spike"] <- "Brush"
-
-d$Nectar_presence_absence[d$Nectar_presence_absence=="yes"] <- "Yes"
-d$Nectar_presence_absence[d$Nectar_presence_absence=="no"] <- "No"
-
-#The other qualitative are ok
-
-#All principal components are normally distributed
-#Convert to factor before running model
-d[sapply(d, is.character)] <- lapply(d[sapply(d, is.character)], as.factor)
-
-#Run model
-model1 <- lm(PC1 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
-model2 <- lm(PC2 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
-
-####################################################################################################################################################################################################################################
-#1) BREEDING SYSTEM
-####################################################################################################################################################################################################################################
-model_breeding_1 <- emmeans(model1, "Breeding_system")
-breeding_1 <- as.data.frame(model_breeding_1[1:3])
-breed1 <- multcomp::cld(model_breeding_1, alpha = 0.10, Letters = LETTERS)
-
-breed_1 <- ggplot(breed1,aes(x= Breeding_system,y= emmean,
-               label = .group)) +theme_minimal()+
-  geom_point(data = breed1, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "A Breeding system")+
-  theme(plot.title = element_text(hjust=0.5, size=25, face="bold"))+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-model_breeding_2 <- emmeans(model2, "Breeding_system")
-breeding_2 <- as.data.frame(model_breeding_2[1:3])
-breed2 <- multcomp::cld(model_breeding_2, alpha = 0.10, Letters = LETTERS)
-
-breed_2 <- ggplot(breed2,aes(x= Breeding_system,y= emmean,
-             label = .group)) +theme_minimal()+
-  geom_point(data = breed2, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "B Breeding system")+
-  theme(plot.title = element_text(hjust=0.5,size=25, face="bold") )+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-########################################################################################################################################################
-#2) COMPATIBILITY
-########################################################################################################################################################
-model_com <- emmeans(model1, "Compatibility_system")
-
-d <- as.data.frame(model_com[1:4])
-comp1 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
-
-comp_1 <- ggplot(comp1,aes(x= Compatibility_system,y= emmean,
-  label = .group)) +theme_minimal()+
-  geom_point(data = comp1, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
-  width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "C Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
-
-model_com <- emmeans(model2, "Compatibility_system")
-d <- as.data.frame(model_com[1:4])
-comp2 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
-
-comp_2 <- ggplot(comp2,aes(x= Compatibility_system,y= emmean,
-  label = .group)) +theme_minimal()+
-  geom_point(data = comp2, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
-  width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "D Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
-
-########################################################################################################################################################
-#3) LIFESPAN
-########################################################################################################################################################
-model_lif_1 <- emmeans(model1, "lifespan")
-lif_1 <- as.data.frame(model_lif_1[1:2])
-lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
-
-lifespan_1 <- ggplot(lif_1,aes(x= lifespan,y= emmean,
-             label = .group)) +theme_minimal()+
-  geom_point(data = lif_1, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "E Lifespan")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-model_lif_2 <- emmeans(model2, "lifespan")
-lif_2 <- as.data.frame(model_lif_2[1:2])
-lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
-
-lifespan_2 <- ggplot(lif_2,aes(x= lifespan,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_2, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "F Lifespan")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")
-
-########################################################################################################################################################
-# 4) LIFE FORM
-########################################################################################################################################################
-
-model_lif_1 <- emmeans(model1, "life_form")
-lif_1 <- as.data.frame(model_lif_1[1:3])
-lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
-
-lifeform_1 <- ggplot(lif_1,aes(x= life_form,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_1, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "G Life form")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-model_lif_2 <- emmeans(model2, "life_form")
-lif_2 <- as.data.frame(model_lif_2[1:3])
-lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
-
-lifeform_2 <- ggplot(lif_2,aes(x= life_form,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_2, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "H Life form")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-########################################################################################################################################################
-# 5) FLOWER MORPHOLOGY
-########################################################################################################################################################
-model_flo_1 <- emmeans(model1, "Flower_morphology")
-flo_1 <- as.data.frame(model_flo_1[1:6])
-flo_1 <- multcomp::cld(model_flo_1, alpha = 0.10, Letters = LETTERS)
-
-shape_1 <- ggplot(flo_1,aes(x= Flower_morphology,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_1, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "I Flower shape")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")
-
-model_flo_2 <- emmeans(model2, "Flower_morphology")
-flo_2 <- as.data.frame(model_flo_2[1:6])
-flo_2 <- multcomp::cld(model_flo_2, alpha = 0.10, Letters = LETTERS)
-
-shape_2 <- ggplot(flo_2,aes(x= Flower_morphology,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_2, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "J Flower shape")+
-   geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
-
-########################################################################################################################################################
-#6) FLOWER SYMMETRY
-########################################################################################################################################################
-model_flo_sym_1 <- emmeans(model1, "Flower_symmetry")
-flo_sym_1 <- as.data.frame(model_flo_sym_1[1:2])
-flo_sym_1 <- multcomp::cld(model_flo_sym_1, alpha = 0.10, Letters = LETTERS)
-
-symmetry_1 <-ggplot(flo_sym_1,aes(x= Flower_symmetry,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_sym_1, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "K Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
-
-model_flo_sym_2 <- emmeans(model2, "Flower_symmetry")
-flo_sym_2 <- as.data.frame(model_flo_sym_2[1:2])
-flo_sym_2 <- multcomp::cld(model_flo_sym_2, alpha = 0.10, Letters = LETTERS)
-
-symmetry_2 <- ggplot(flo_sym_2,aes(x= Flower_symmetry,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = flo_sym_2, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title = "L Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-########################################################################################################################################################
-#7) NECTAR
-########################################################################################################################################################
-model_nec <- emmeans(model1, "Nectar_presence_absence")
-
-model_nec_1 <- emmeans(model1, "Nectar_presence_absence")
-nec_1 <- as.data.frame(model_nec_1[1:2])
-nec_1 <- multcomp::cld(model_nec_1, alpha = 0.10, Letters = LETTERS)
-
-nectar_1 <- ggplot(nec_1,aes(x= Nectar_presence_absence,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = nec_1, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "M Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-model_nec_2 <- emmeans(model2, "Nectar_presence_absence")
-nec_2 <- as.data.frame(model_nec_2[1:2])
-nec_2 <- multcomp::cld(model_nec_2, alpha = 0.10, Letters = LETTERS)
-
-nectar_2 <-ggplot(nec_2,aes(x= Nectar_presence_absence,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = nec_2, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "N Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")
-
-#PLOT!
-
-breed_1 + breed_2+ comp_1+ comp_2+ lifespan_1+ lifespan_2+ lifeform_1+ lifeform_2+ shape_1+ shape_2+
-symmetry_1+ symmetry_2+ nectar_1+ nectar_2 + plot_layout(ncol = 2)
-
-```
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Fig.
-S8.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation.
-Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
-For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)"}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot <- readRDS("Plot_bee_families.rds")
-
-plot
-
-```
-
-\elandscape
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S9.} Plant species level metrics across the three main axes of trait variation.", fig.pos= "h"}
-
-library(brms) #modelling
-library(cowplot) #panel of plots
-library(ggplot2) #plotting
-library(patchwork)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(3.5)),
-           axis.text=element_text(size = rel(2.75), color = "black"),
-           legend.title=element_text(face="bold"),
-           legend.text=element_text(),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(0.4, 'lines'),
-           panel.border=element_rect(color="black",size=3),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-#########
-
-setwd("~/Dropbox/PhD/R/Chapter_2")
-
-#read plot generated in other rmd, bms and stan are giving trouble here... This file is created in Species_Level_Metric_Pcs
-
-plot_metrics_pcs <- readRDS("plot_metrics_pcs.rds")
-
-plot_metrics_pcs
-
-```
-
-\elandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S10.} Pearson correlation between the product of flower number-flower size and autonomous selfing level.", fig.pos= "h"}
-
-theme_ms <- function(base_size=18, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(2.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-#LOAD LIBRARIES
-library(ggplot2)
-library(ggpubr)
-
-#LOAD DATA
-dat <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-
-#CONDUCT PRODUCT FLOWER NUMBER-FLOWER SIZE
-dat$Product <-      log(dat$Flowers_per_plant * dat$Corolla_diameter_mean+1)
-
-ggscatter(dat, x = "Autonomous_selfing_level_fruit_set", y = "Product", 
-          add = "reg.line", conf.int = TRUE,
-          cor.coef = TRUE, cor.method = "pearson",size=5,cor.coef.size=15,
-          xlab = "Autnomous selfing", ylab = "Product flower size-number") +
-  theme_ms() +ylim(0,16)
-
-```

### 2022-01-27 Scripts/2_1_Trait_Data_Imp_Nectar_Pollen_Subset.R

@@ -185,8 +185,6 @@ sort(missing_data[missing_data >= 0], decreasing=T)
 library(tidyverse)
 t_nectar_pollen <- t_nectar_pollen %>% select(!Nectar_mg)
 
-str(t_nectar_pollen)
-
 #################################################
 #3)SUMMARY OF THE DATA|ALL COLS CONSIDERED!
 #################################################

### 2022-01-27 Scripts/3_PPCA_Nectar_Pollen.R

@@ -46,6 +46,7 @@ dat_cleaning_4 <- dat_cleaning_3 %>%
 dat_cleaning_5 <- dat_cleaning_4 %>%
   filter(between(Plant_height_mean_m, quantile(Plant_height_mean_m, 0.025), quantile(Plant_height_mean_m, 0.975)))
 
+
 dat_cleaning_6 <- dat_cleaning_5 %>%
   filter(between(Nectar_ul, quantile(Nectar_ul, 0.025), quantile(Nectar_ul, 0.975)))
 
@@ -204,7 +205,7 @@ all_spp <- function(PC, x="PC1", y="PC2") {
   plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,5.5,6.25,6.3,6.15,6,6)), y = (PCAloadings$PC2*c(4.693,2.4,3,6.2,5,5.5,6,5)+c(0,0,0,0,0.4,0,0,0)),
                           label = PCAloadings$Variables, color="black",fontface =2,size=4)
   
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("") 
+  plot <- plot + theme_bw() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("") 
   
   
   

### 2022-01-27 Manuscript/Lanuza_et_al_2021_Ecol_Letters.Rmd
edits

@@
 
-\textbf{Number of words:} Abstract  (146 words), main text (XXXX).
+\textbf{Number of words:} Abstract  (146 words), main text (5097 words).
 
@@
 Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives [e.g., The Web of Life, @fortuna2010; and Mangal, @poisot2016].
-In total, our network dataset (see Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+In total, our network dataset (Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
 
@@
 
+\newpage
+
 **Functional traits**
 
-We selected a total of 19 different functional traits that included both reproductive and vegetative traits (see Table 1 and Supplementary Information).
+We selected a total of 19 different functional traits that included both reproductive and vegetative traits (Table 1 and Supplementary Information).
 From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
@@
 To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-Although the variable of autonomous selfing had a high percentage of missing values (68%), we were able to solve this by back transforming a complementary qualitative column of autonomous selfing to numerical.
-The categories of ‘none’, ‘low’, ‘medium’ and ‘high’ were converted to representative percentages of each category 0%, 13%, 50.5% and 88%, respectively.
-This reduced the percentage of missing values for this column from 68% to 35% and allowed the imputation of this variable.
 However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Fig.
@@
 We found that _A.
-mellifera_, was partly driving some of the observed trends on PC1 (Supplementary Fig.
+mellifera_, was partly driving some of the observed trends on PC1 (Fig.
 S3).
@@
 
-We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017] (version _2.14.6_).
+We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017] version _2.14.6_.
 We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
@@
 We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019] (version _1.7.2_).
+We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019] version _1.7.2_.
 
@@
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d’) [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008] (version _2.15_).
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization [d’\; @bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008] version _2.15_.
 
@@
 Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
-We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
+We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
 We conducted this analysis using the _rpart_ package [@therneau2015] version _4.1-15_ with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] version _3.0.9_ to plot the regression trees.
@@
 We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig.
+We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (Fig.
 S4).
@@
 The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Fig.
-1 and Supplementary Fig.
+1 and Fig.
 S5) and had a phylogenetic correlation ($\lambda$) of 0.76.
@@
 The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Supplementary Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
 The second principal component (PC2) represented 25.05% of the trait variation and indicated a trade-off between low and high pollinator dependence.
 We refer to this axis as the ‘pollinator dependence trade-off’.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Supplementary Table S3).
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
 We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
@@
 Further, PC3 explained a considerable amount of trait variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
-The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Supplementary Table S3).
+The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
 Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the ‘style length trade-off’.
-Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 23.40%); and pollen quantity (pollen grains per flower) was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 21.67%; Supplementary Fig.
+Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82%; Fig.
 S6).
-This pPCA explained similar variance with the first two principal components (45.07%) and similar associations of traits despite some variability in the loadings (Supplementary Table S4).
+This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (Table S4).
 
@@
 We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
-2 and Supplementary Table S2).
+2 and Table S2).
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, _P_ < 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , _P_ = 0.59; PC2:  Sum of squares = 0.83, F-value = 1.43, _P_ = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Supplementary Fig.
+In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
 S7).
-Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Supplementary Fig.
+Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Fig.
 S7a and Fig.
 S7b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Supplementary Fig.
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
 S7c and Fig.
 S7d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Supplementary Fig.
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
 S7e and Fig.
 S7f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Supplementary Fig.
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
 S7g and Fig.
@@
 Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Supplementary Fig.
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Fig.
 S7i and Fig.
 S7j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Supplementary Fig.
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Fig.
 S7k and Fig.
@@
 
-We found a strong phylogenetic signal (*P* < 0.01) in all quantitative traits (Supplementary Table S5).
+We found a strong phylogenetic signal (*P* < 0.01) in all quantitative traits (Table S5).
 The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
@@
 3a and Fig.
-3d) were driven by the family Andrenidae, which interacted more frequently on presence-absence interactions with plant species with low number of large flowers (Supplementary Fig.
+3d) were driven by the family Andrenidae, which interacted more frequently on presence-absence interactions with plant species with low number of large flowers (Fig.
 S8).
@@
 
-The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
+The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
 S9; interaction frequency ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
 Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
-On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers (Supplementary Fig.
+On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
 S9a).
-On PC1, specialization showed the opposite trend (Supplementary Fig.
+On PC1, specialization showed the opposite trend (Fig.
 S9g).
-On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Supplementary Fig.
+On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
 S9c).
-Again, specialization showed the opposite trend to interaction frequency (Supplementary Fig.
+Again, specialization showed the opposite trend to interaction frequency (Fig.
 S9i).
@@
 Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
-The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Supplementary Fig.
+The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
 S10).
@@
 For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
-1 and Supplementary Fig.
+1 and Fig.
 S6).

### 2022-01-27 Manuscript/Lanuza_et_al_2021_Ecol_Letters.tex
edits

@@
 
-\textbf{Number of words:} Abstract (146 words), main text (XXXX).
+\textbf{Number of words:} Abstract (146 words), main text (5097 words).
 
@@
 Many of these networks are freely available either as published studies (\protect\hyperlink{ref-olesen2007}{Olesen \emph{et al.} 2007}; \protect\hyperlink{ref-fortuna2010}{Fortuna \emph{et al.} 2010}; \protect\hyperlink{ref-carvalheiro2014}{Carvalheiro \emph{et al.} 2014}) or available in online archives (e.g., The Web of Life, \protect\hyperlink{ref-fortuna2010}{Fortuna \emph{et al.} 2010}; and Mangal, \protect\hyperlink{ref-poisot2016}{Poisot \emph{et al.} 2016}).
-In total, our network dataset (see Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+In total, our network dataset (Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
 
@@
 
-We selected a total of 19 different functional traits that included both reproductive and vegetative traits (see Table 1 and Supplementary Information).
+We selected a total of 19 different functional traits that included both reproductive and vegetative traits (Table 1 and Supplementary Information).
 From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
@@
 To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} (\protect\hyperlink{ref-santos2018}{Chamberlain \emph{et al.} 2018}) based on a previous conceptual framework that considers phylogenetic eigenvectors (\protect\hyperlink{ref-diniz-filho2012}{Diniz-Filho \emph{et al.} 2012}).
-Although the variable of autonomous selfing had a high percentage of missing values (68\%), we were able to solve this by back transforming a complementary qualitative column of autonomous selfing to numerical.
-The categories of `none,' `low,' `medium' and `high' were converted to representative percentages of each category 0\%, 13\%, 50.5\% and 88\%, respectively.
-This reduced the percentage of missing values for this column from 68\% to 35\% and allowed the imputation of this variable.
 However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Fig.
@@
 We found that \emph{A.
-mellifera}, was partly driving some of the observed trends on PC1 (Supplementary Fig.
+mellifera}, was partly driving some of the observed trends on PC1 (Fig.
 S3).
@@
 
-We implemented Bayesian generalized linear mixed models using the R package \emph{brms} (\protect\hyperlink{ref-burkner2017}{Bürkner 2017}) (version \emph{2.14.6}).
+We implemented Bayesian generalized linear mixed models using the R package \emph{brms} (\protect\hyperlink{ref-burkner2017}{Bürkner 2017}) version \emph{2.14.6}.
 We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
@@
 We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package (\protect\hyperlink{ref-gabry2019}{Gabry \emph{et al.} 2019}) (version \emph{1.7.2}).
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package (\protect\hyperlink{ref-gabry2019}{Gabry \emph{et al.} 2019}) version \emph{1.7.2}.
 
@@
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies (\protect\hyperlink{ref-dormann2008}{Dormann \emph{et al.} 2008}) with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') (\protect\hyperlink{ref-bluthgen2006}{Blüthgen \emph{et al.} 2006}), which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} (\protect\hyperlink{ref-dormann2008}{Dormann \emph{et al.} 2008}) (version \emph{2.15}).
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d'; \protect\hyperlink{ref-bluthgen2006}{Blüthgen \emph{et al.} 2006}), which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} (\protect\hyperlink{ref-dormann2008}{Dormann \emph{et al.} 2008}) version \emph{2.15}.
 
@@
 Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
-We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
-We conducted this analysis using the \emph{rpart} package (\protect\hyperlink{ref-therneau2015}{Therneau \emph{et al.} n.d.}) version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package (\protect\hyperlink{ref-milborrow2015}{Milborrow n.d.}) version \emph{3.0.9} to plot the regression trees.
+We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
+We conducted this analysis using the \emph{rpart} package (\protect\hyperlink{ref-therneau2015}{Therneau \emph{et al.} 2015}) version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package (\protect\hyperlink{ref-milborrow2015}{Milborrow 2015}) version \emph{3.0.9} to plot the regression trees.
 We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
 We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig.
+We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (Fig.
 S4).
@@
 The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8\% and 70.97\% of trait variation, respectively (Fig.
-1 and Supplementary Fig.
+1 and Fig.
 S5) and had a phylogenetic correlation (\(\lambda\)) of 0.76.
@@
 The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Supplementary Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
 The second principal component (PC2) represented 25.05\% of the trait variation and indicated a trade-off between low and high pollinator dependence.
-We refer to this axis as the `pollinator dependence trade-off.' The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Supplementary Table S3).
+We refer to this axis as the `pollinator dependence trade-off.' The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
 We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
@@
 Further, PC3 explained a considerable amount of trait variability (19.17\%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
-The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Supplementary Table S3).
-Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the `style length trade-off.' Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 23.40\%); and pollen quantity (pollen grains per flower) was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 21.67\%; Supplementary Fig.
+The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
+Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the `style length trade-off.' Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82\%; Fig.
 S6).
-This pPCA explained similar variance with the first two principal components (45.07\%) and similar associations of traits despite some variability in the loadings (Supplementary Table S4).
+This pPCA explained similar variance with the first two principal components (45.52\%) and similar associations of traits despite some variability in the loadings (Table S4).
 
@@
 We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
-2 and Supplementary Table S2).
+2 and Table S2).
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Supplementary Fig.
+In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
 S7).
-Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Supplementary Fig.
+Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Fig.
 S7a and Fig.
 S7b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Supplementary Fig.
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
 S7c and Fig.
 S7d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Supplementary Fig.
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
 S7e and Fig.
 S7f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Supplementary Fig.
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
 S7g and Fig.
@@
 
-We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) in all quantitative traits (Supplementary Table S5).
+We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) in all quantitative traits (Table S5).
 The traits that showed the highest phylogenetic signal were ovule number (\(\lambda\) = 1), pollen grains per flower (\(\lambda\) = 1) and plant height (\(\lambda\) = 0.96), followed by flower length (\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73), number of flowers per plant (\(\lambda\) = 0.69) and nectar concentration (\(\lambda\) = 0.65).
@@
 
-The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
+The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
 S9; interaction frequency \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
 Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
-On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers (Supplementary Fig.
+On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
 S9a).
-On PC1, specialization showed the opposite trend (Supplementary Fig.
+On PC1, specialization showed the opposite trend (Fig.
 S9g).
-On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Supplementary Fig.
+On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
 S9c).
-Again, specialization showed the opposite trend to interaction frequency (Supplementary Fig.
+Again, specialization showed the opposite trend to interaction frequency (Fig.
 S9i).
@@
 Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie \emph{et al.} 2010}).
-The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Supplementary Fig.
+The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
 S10).
@@
 Milborrow, S.
-(n.d.).
+(2015).
 Rpart.
@@
 Rpart.
-R package version 3.0.9 (2015).~At \href{https://CRAN.R-project.org/package=rpart.plot}{https://CRAN.r-project.org/package=rpart.plot}.
+R package version 3.0.9.~At \href{https://CRAN.R-project.org/package=rpart.plot}{https://CRAN.r-project.org/package=rpart.plot}.
 
@@
 \& Ripley, M.B.
-(n.d.).
-Package {`rpart.'} R package version 4.1-15 (2015).~At \href{https://CRAN.R-project.org/package=rpart}{https://CRAN.r-project.org/package=rpart}.
+(2015).
+Package {`rpart.'} R package version 4.1-15.~At \href{https://CRAN.R-project.org/package=rpart}{https://CRAN.r-project.org/package=rpart}.
 

### 2022-01-27 Manuscript/MS_word.Rmd
edits

--- 2021-12-09 Manuscript/MS_word.Rmd
@@
 
-\vspace{-1.7cm}
+\vspace{-1.4cm}
+
 \singlespacing
-\large 
-\textbf{Jose B. Lanuza$^{1,2}*$, Romina Rader$^{1}$, Jamie Stavert$^{3}$, Liam K. Kendall$^{4}$, Manu E. Saunders$^{1}$ and Ignasi Bartomeus$^{2}$}
 
-\vspace{0.3cm}
-
-\normalsize
-
-__Plant life strategies are constrained by cost-benefit trade-offs that determine plant form and function.
-However, despite recent advances in the understanding of trade-offs for vegetative and physiological traits, little is known about plant reproductive economics and how they constrain plant life strategies and shape interactions with floral visitors.
-Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 17 reproductive traits for 1,506 plant species from 28 plant-pollinator studies across 18 countries.
-We tested whether a plant’s reproductive strategy predicts its interactions with floral visitors and if the different reproductive traits predict the plant’s role within the pollination network.
-We found that over half of all plant reproductive trait variation was explained by two independent axes that encompassed plant form and function.
-Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
-Plant reproductive trade-offs helped explain partly the presence or absence of interactions with floral visitors, but not differences in visitation rate.
-However, we did find important differences in the interaction level among floral visitor guilds on the different axes of trait variation.
-Finally, we found that plant size and floral rewards were the most important traits in the understanding of the species network role.
-Our results highlight the importance of plant reproductive trade-offs in determining plant life strategies and plant-pollinator interactions in a global context.__
+\textbf{Jose B.
+Lanuza$^{1,2}$} <barragansljose@gmail.com>, \textbf{Romina Rader$^{1}$} <rrader@une.edu.au>, \textbf{Jamie Stavert$^{3}$} <jamie.stavert@gmail.com>, \textbf{Liam K.
+Kendall$^{4}$} <liam.k.kendall@gmail.com>, \textbf{Manu E.
+Saunders$^{1}$} <Manu.Saunders@une.edu.au> \textbf{and Ignasi Bartomeus$^{2}$} <nacho.bartomeus@gmail.com>
 
 \small
-\vspace{-0.5cm}
-
-\noindent\rule{\textwidth}{1pt}
 
@@
 ^4^ Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden.
-`*` e-mail: barragansljose@gmail.com
+
+\doublespacing
+\normalsize
+
+\textbf{Statement of authorship:} JBL, RR and IB designed the study.
+JBL collated the data and conducted analysis with guidance of JS, LKK and IB.
+JBL wrote the manuscript with contributions of all authors.
+
+\textbf{Data accessibility statement:} All data and code used to conduct this study will be deposited in the public repository Dryad upon acceptance.
+
+\textbf{Short title:} Plant reproductive trade-offs.
+
+\textbf{Keywords:} life-history strategies | plant reproductive trade-offs | plant-pollinator interactions.
+
+\textbf{Type of article:} Letter.
+
+\textbf{Number of words:} Abstract  (146 words), main text (XXXX).
+
+\textbf{Number of references:} 77 (CHECK! Probably less now)
+
+\textbf{Number of figures and tables:} 4 figures and 1 table.
+
+\textbf{Corresponding author:} Jose B. Lanuza | +34 616375981| <barragansljose@gmail.com>
+
+\newpage
+
+# ABSTRACT
+
+Plant life-history strategies are constrained by cost-benefit trade-offs that determine plant form and function.
+However, despite recent advances in the understanding of plant trait variation, little is known about plant reproductive trade-offs and how these constrain life-history strategies and shape interactions with floral visitors.
+Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
+We found that over half of all plant reproductive trait variation was explained by two independent axes.
+Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
+In addition, plant reproductive trade-offs determined important differences in the interaction level among floral visitor guilds.
+Our study shows the main plant reproductive trade-offs and their relevance to understand plant-pollinator interactions in a global context.
+
+\newpage
 
@@
 
-Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that explores plant reproductive compromises is currently lacking [@roddy2021].
+# INTRODUCTION
+
+Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that **describes the major** plant reproductive trade-offs is currently lacking [@roddy2021].
 In addition, macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
-Linking the position in the trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
+Linking the plant's position in trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
 Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
-However, reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020] despite the apparent generalist nature of plant-pollinator interactions [@waser1996; @olesen2002].
-In addition, it is unclear how specific plant reproductive biology traits influence plant-pollinator interactions [@tur2013; @devaux2014].
+**However, plant reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020] and remains unclear how specific plant reproductive biology traits (e.g., mating or compatibility system) influence plant-pollinator associations [@tur2013; @devaux2014].**
 
 Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY @kattge2011 and COMPADRE @salguero2015), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
+With the recent availability of large trait databases [e.g., TRY, @kattge2011; and COMPADRE, @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
 However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively [@barrett2003; @moeller2017] and outcrossing levels are positively correlated with flower size [@goodwillie2010].
+For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively, [@barrett2003; @moeller2017] and outcrossing levels are positively correlated with flower size [@goodwillie2010].
 In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators [@ollerton2011; @rodger2021].
@@
 Several studies have identified links between plant traits and plant-pollinator network properties [@bartomeus2013; @olito2015; @rowe2020].
-Moreover, plant traits can define species’ network roles (e.g., specialists vs generalists) [@lazaro2013; @tur2013].
+Moreover, plant traits can define species’ network roles [e.g., specialists vs generalists\; @lazaro2013; @tur2013].
 For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
 Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
-Remarkably, the combination of traits have shown to increase the predictive power of the network interactions [@eklof2013].
-Therefore, considering the different plant reproductive trade-offs which represent the species strategy within the network [@dehling2016] could progress our understanding of plant-pollinator interactions.
-Further, we know little if the different network patterns generally studied at the community level are maintained when we scale up at macroecological scale.
+Remarkably, the combination of traits has shown to increase the predictive power of the network interactions [@eklof2013].
+**Moreover, the position in the trait space can determine plant and pollinator species’ functional roles [@dehling2016].
+Therefore, by considering the multidimensional reproductive trait space we could progress our understanding of plant-pollinator associations.
+Importantly, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.**
 
@@
 
+# MATERIALS AND METHODS
+
+**Plant-pollinator network studies**
+
+We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
+These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
+Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
+Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives [e.g., The Web of Life, @fortuna2010; and Mangal, @poisot2016].
+In total, our network dataset (see Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+
+**Taxonomy of plants and pollinators**
+
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020] version _0.9.99_.
+We filled the ‘not found’ searches manually using http://www.theplantlist.org/ and http://www.mobot.org/ for plants and http://www.catalogueoflife.org/ for floral visitors.
+
+\newpage
+
+**Functional traits**
+
+We selected a total of 19 different functional traits that included both reproductive and vegetative traits (see Table 1 and Supplementary Information).
+From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
+Note that autonomous selfing was recorded quantitatively (fruit set) and qualitatively because this trait was rarely available in its numerical form.
+The 3 remaining traits, were vegetative traits that are commonly used to characterize the global spectrum of plant form and function and represent the fast-slow continuum of trait variation (e.g., short-lived versus perennial species).
+For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
+From a total of 30,120 cells (20 columns x 1506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Fig.
+S1 for missing values information for each trait).
+
+**Phylogenetic Distance**
+
+We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package _rtrees_ (https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
+
+\singlespacing
+
+\doublespacing
+
+**Data Imputation**
+
+Trait missing values were imputed with the function _missForest_ [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of _missForest_ [@penone2014].
+To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
+However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Fig.
+S1).
+Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79% of missing values.
+Further, we conducted an additional imputation process on the subset of species with data for pollen per flower and microliters of nectar.
+This subset comprised 755 species, 8.01% missing values and all traits but milligrams of nectar (~50% of missing values) were included in the imputation process.
+
+**Plant strategies**
+
+We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the reproductive spectrum of trait variation.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
+Prior to the analyses, we excluded outliers and standardized the data.
+Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th–97.5th percentile range [@legendre2012], and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
+We performed the pPCA using the function _phyl.pca_ from the package _phytools_ version _0.7-70_ [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
+Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
+S2).
+We found little difference between the explained variance with the imputed dataset (51.08%) and the dataset without missing values (52.87%).
+In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
+Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
+For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
+
+**Phylogenetic signal of traits**
+
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] version _0.7-70_ and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
+However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
+
+**Network analyses**
+
+Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+These networks were analysed in their qualitative (presence-absence) and quantitative (interaction frequency) form.
+First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
+Second, we analysed the untransformed weighted networks with interaction frequency that accounts for the intensity of the interaction.
+Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency [@ballantyne2015], interaction frequency can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
+In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
+Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
+All analyses were conducted in R version _4.0.3_.
+
+**Visitation patterns**
+
+We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
+For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
+Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
+This finding is consistent with previous research showing that _A.
+mellifera_ was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
+Hence, to control for the effect of _A.
+mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of interaction and visitation rate excluding _A.
+mellifera_.
+We found that _A.
+mellifera_, was partly driving some of the observed trends on PC1 (Fig.
+S3).
+However, we did not detect major differences on PC2 and PC3.
+
+We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017] version _2.14.6_.
+We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
+In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
+Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
+We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
+We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
+We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019] version _1.7.2_.
+
+**Plant species functional roles**
+
+We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization [d’\; @bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008] version _2.15_.
+
+First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric ~ PC1 + PC2 + PC3).
+For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
+Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns section’.
+
+Second, to better understand these complex trait relationships, we used regression trees.
+Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
+We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
+We conducted this analysis using the _rpart_ package [@therneau2015] version _4.1-15_ with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] version _3.0.9_ to plot the regression trees.
+We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
+We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
+We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Fig.
+S4).
+
 # RESULTS
 
-**Plant strategies.** The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Fig.
-1 and Supplementary Fig.
+**Plant strategies**
+
+The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Fig.
+1 and Fig.
 S5) and had a phylogenetic correlation ($\lambda$) of 0.76.
@@
 The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Supplementary Table S3) but style length also contributed moderately on PC1 (loading = -0.33).
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
 The second principal component (PC2) represented 25.05% of the trait variation and indicated a trade-off between low and high pollinator dependence.
 We refer to this axis as the ‘pollinator dependence trade-off’.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Supplementary Table S3).
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
 We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
@@
 Further, PC3 explained a considerable amount of trait variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
-The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Supplementary Table S3).
+The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
 Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the ‘style length trade-off’.
-Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) was positively associated with flower size, style length and ovule number (PC1, 23.40%); and pollen quantity (pollen grains per flower) was positively correlated with flower number and plant height and negatively associated with autonomous selfing (PC2, 21.67%; Supplementary Fig.
+Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82%; Fig.
 S6).
-This pPCA explained similar variance with the first two principal components (45.07%) and similar associations of traits despite some variability in the loadings (Supplementary Table S4).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Fig.
-1 | Plant life-history strategies.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
-The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
-The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation.
-The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}
-
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-library(viridis) #COLOUR GGPLOT
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(magick)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#Images were made by Paula Martin
-#Check her work on https://paulamartinart.com/
-
-tree <- image_read("Images/PPCA_Plot/Tree.png")
-tree_1 <- as.raster(tree)
-
-style_l <- image_read("Images/PPCA_Plot/Style_Long.png")
-style_l_1 <- as.raster(style_l)
-
-style_s <- image_read("Images/PPCA_Plot/Style_Short.png")
-style_s_1 <- as.raster(style_s)
-
-ovule_h <- image_read("Images/PPCA_Plot/Ovule_High.png")
-ovule_h_1 <- as.raster(ovule_h)
-
-ovule_l <- image_read("Images/PPCA_Plot/Ovule_Low.png")
-ovule_l_1 <- as.raster(ovule_l)
-
-selfing_n <- image_read("Images/PPCA_Plot/Selfing_None.png")
-selfing_n_1 <- as.raster(selfing_n)
-
-selfing_h <- image_read("Images/PPCA_Plot/selfing.png")
-selfing_h_1 <- as.raster(selfing_h)
-
-single_flower <- image_read("Images/PPCA_Plot/Single_Flower.png")
-single_flower_1 <- as.raster(single_flower)
-
-many_flowers <- image_read("Images/PPCA_Plot/Inflorescencia.png")
-many_flowers_1 <- as.raster(many_flowers)
-#many_flowers_1 <- image_rotate(many_flowers, 45)
-
-large_flower <- image_read("Images/PPCA_Plot/flower_big.png")
-large_flower_1 <- as.raster(large_flower)
-
-flower_small <- image_read("Images/PPCA_Plot/flower_short.png")
-flower_small_1 <- as.raster(flower_small)
-
-herb <- image_read("Images/PPCA_Plot/herb.png")
-herb_1 <- as.raster(herb)
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("Flower number - flower size trade-off ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Pollinator dependence trade-off ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
-    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
-    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
-    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
-    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2, ymax = -1.50) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
-
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
-                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-plot_grid(all_spp(PC))
-
-```
+This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (Table S4).
 
 We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
-2 and Supplementary Table S2).
+2 and Table S2).
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, _P_ < 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , _P_ = 0.59; PC2:  Sum of squares = 0.83, F-value = 1.43, _P_ = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Supplementary Fig.
+In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
 S7).
-Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Supplementary Fig.
+Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Fig.
 S7a and Fig.
 S7b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Supplementary Fig.
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
 S7c and Fig.
 S7d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Supplementary Fig.
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
 S7e and Fig.
 S7f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Supplementary Fig.
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
 S7g and Fig.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18,fig.cap= "**Fig.
-2 | Location of the different qualitative traits on the trait space.** The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f)."}
-
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-#library(phytools)
-#library(ape) #for phylogenetic distance
-#library(dplyr) #data processing
-#library(rtrees) #for phylogenetic distancelibrary(MASS)
-#library(reshape2)
-library(viridis) #COLOUR GGPLOT
-#library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-#library(cowplot)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.55, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank(),
-            plot.title = element_text(size = rel(1.65), face="bold")
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-#CALL the output PC for simplicity
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-Compatibility <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Compatibility <- dat_cleaning_5$Compatibility_system
-  dat$Compatibility <- as.character(dat$Compatibility)
-  dat$Compatibility[dat$Compatibility=="dioecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="monoecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-  dat$Compatibility[dat$Compatibility=="self_compatible"] <- "Self compatible"
-  dat$Compatibility[dat$Compatibility=="self_incompatible"] <- "Self incompatible"
-  dat$Compatibility <- factor(dat$Compatibility, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Compatibility),size=1.75)+scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.185, 0.13)) +ggtitle("(a)")
-
-  plot
-
-}
-
-#Compatibility(PC)
-
-#############################################################################################################################################################
-#Life form
-#############################################################################################################################################################
-#Load plots
-Life_form <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Life form` <- dat_cleaning_5$life_form
-  dat$`Life form` <- as.character(dat$`Life form`)
-  dat$`Life form`[dat$`Life form`=="herb"] <- "Herb"
-  dat$`Life form`[dat$`Life form`=="shrub"] <- "Shrub"
-  dat$`Life form`[dat$`Life form`=="tree"] <- "Tree"
-  dat$`Life form`[dat$`Life form`=="vine"] <- "Shrub"
-
-  dat$`Life form` <- factor( dat$`Life form`, levels = c("Herb", "Shrub", "Tree"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Life form`),size=1.75)+scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("(b)")
-
-  plot
-
-}
-
-#Life_form(PC)
-
-#############################################################################################################################################################
-#Life span
-#############################################################################################################################################################
-#Load plots
-Life_span <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-    dat$Lifespan <- dat_cleaning_5$lifespan
-    dat$Lifespan <- as.character(dat$Lifespan)
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Lifespan),size=1.75)+scale_color_manual(values=c("sienna4","forestgreen"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.102, 0.1)) + ggtitle("(c)")
-
-  plot
-
-}
-
-#Life_span(PC)
-
-#############################################################################################################################################################
-#Flower symmetry
-#############################################################################################################################################################
-#Load plots
-Flower_sym <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower symmetry` <- dat_cleaning_5$Flower_symmetry
-  dat$`Flower symmetry` <- as.character(dat$`Flower symmetry`)
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower symmetry`),size=1.75)+scale_color_manual(values=c("sienna2","purple"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.165, 0.1)) + ggtitle("(f)")
-
-  plot
-
-}
-
-#Flower_sym(PC)
-
-#############################################################################################################################################################
-#Flower shape
-#############################################################################################################################################################
-#Load plots
-Flower_sha <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower shape` <- dat_cleaning_5$Flower_morphology
-  dat$`Flower shape` <- as.character(dat$`Flower shape`)
-  dat$`Flower shape`[dat$`Flower shape`=="Funnelform"] <- "Campanulate"
-  dat$`Flower shape`[dat$`Flower shape`=="Spike"] <- "Brush"
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower shape`),size=1.75)+scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.13, 0.18)) + ggtitle("(e)")
-
-  plot
-
-}
-
-#Flower_sha(PC)
-
-#############################################################################################################################################################
-#Breeding system
-#############################################################################################################################################################
-#Load plots
-Breeding_syst <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Breeding system` <- dat_cleaning_5$Breeding_system
-  dat$`Breeding system` <- as.character(dat$`Breeding system`)
-  dat$`Breeding system` <- factor(dat$`Breeding system`, levels=c("Hermaphrodite","Monoecious" ,"Dioecious"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Breeding system`),size=1.75)+scale_color_manual(values=c("forestgreen","orange", "black"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-                          label = PCAloadings$Variables, color="black",size=3)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.163, 0.115)) + ggtitle("(d)")
-
-  plot
-
-}
-
-#Breeding_syst(PC)
-
-#############################################################################################################################################################
-#Nectar
-#############################################################################################################################################################
-#Load plots
-#Nectar <- function(PC, x="PC1", y="PC2") {
-#  # PC being a prcomp object
-#  data <- data.frame(PC$S)
-#  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-#  dat <- data.frame(x = data[,x], y = data[,y])
-#  
-#  #######
-#  #DENSITY FUNCTION
-#  #######
-#  get_density <- function(x, y, ...) {
-#    dens <- MASS::kde2d(x, y, ...)
-#    ix <- findInterval(x, dens$x)
-#    iy <- findInterval(y, dens$y)
-#    ii <- cbind(ix, iy)
-#    return(dens$z[ii])
-#  }
-#  
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-#  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-#  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-#  plot <- plot + geom_point(data=dat, aes(-x, -y, #colour=Nectar),size=1.75)+scale_color_manual(values=c("black","grey"))
-#  
-#  ########
-#  #ADD ARROWS 
-#  ########
-#  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-#  mult <- min(
-#    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-#    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-#  )
-#  datapc <- transform(datapc,
-#                      v1 = .75 * mult * (get(x)),
-#                      v2 = .75 * mult * (get(y))
-#  )
-#  # add arrows
-#  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, #yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-#  
-#  #Add axis with perctentage
-#  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-#
-#  
-#  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, #arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-#  
-#  #ADD LABELS
-#  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-#  
-#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-#  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = #-(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-#                          label = PCAloadings$Variables, color="black",size=3)
-#  
-#  #CHANGE THEME
-#  #CHANGE THEME
-#  
-#  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)") 
-#  
-#  plot
-#  
-#}
-#
-# #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")
-
-#  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flowe#r_sym(PC),ncol=3,nrow=2,  align = "hv")
-
-library(patchwork)
-Compatibility(PC) + Life_form(PC) + Life_span(PC) + Breeding_syst(PC) + Flower_sha(PC) + Flower_sym(PC) + plot_layout(ncol=3)
-
-```
-
-\elandscape
-
 \vspace{5mm}
 
-**Phylogenetic signal of traits.** We found a strong phylogenetic signal (*P* < 0.01) in all quantitative traits (Supplementary Table S5).
+**Phylogenetic signal of traits**
+
+We found a strong phylogenetic signal (*P* < 0.01) in all quantitative traits (Table S5).
 The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
@@
 
-The additional model for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and visitation rate (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns and that the contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
+The additional model for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and visitation rate (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
+The contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
 3a and Fig.
-3d) were driven by the family Andrenidae which interacted more frequently on presence-absence interactions with plant species with low number of flowers but large (Supplementary Fig.
+3d) were driven by the family Andrenidae, which interacted more frequently on presence-absence interactions with plant species with low number of large flowers (Fig.
 S8).
 
-\blandscape
+**Plant species functional roles**
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Fig.
-3 | Interaction (yes/no) and visitation rates across the three main axes of trait variation per floral visitor guild.** Fitted posterior estimates of the presence/absence of interaction (a, b and c) and number of visits (d, e and f) made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
-PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.
-For visualization purposes, due to large differences between the visitation rates of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
-
-#LOAD LIBRARIES 
-#library(phytools)
-#library(ape) #for phylogenetic distance
-#library(dplyr) #data processing
-#library(rtrees) #for phylogenetic distancelibrary(MASS)
-#library(reshape2)
-library(viridis) #COLOUR GGPLOT
-#library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-#library(tidyverse)
-library(patchwork) #panel of plots
-#library(brms)
-#library(cmdstanr)
-
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2)),
-           axis.text=element_text(size = rel(1.8), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(2, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
-           plot.subtitle = element_text(face="bold",size=rel(2))
-     ))
-}
-
-setwd("~/R_Projects/Reproductive Traits")
-
-p1 <- readRDS("Main_Figures/figure_3_1.rds")
-p2 <- readRDS("Main_Figures/figure_3_2.rds")
-p3 <- readRDS("Main_Figures/figure_3_3.rds")
-pp1 <- readRDS("Main_Figures/figure_3_4.rds")
-pp2 <- readRDS("Main_Figures/figure_3_5.rds")
-pp3 <- readRDS("Main_Figures/figure_3_6.rds")
-
-library(patchwork)
-
-combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
-combined + plot_layout(guides = "collect",ncol = 3)
-
-```
-
-\elandscape
-
-**Plant species functional roles.** The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Supplementary Fig.
+The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
 S9; interaction frequency ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
 Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
-On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers.
-On PC1, specialization showed the opposite trend.
-On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing.
-Again, specialization showed the opposite trend to interaction frequency.
+On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
+S9a).
+On PC1, specialization showed the opposite trend (Fig.
+S9g).
+On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
+S9c).
+Again, specialization showed the opposite trend to interaction frequency (Fig.
+S9i).
 
-When we further investigate which combination of traits drive plant network roles, we show that the regression tree for visitation frequency was best explained by plant height, nectar concentration and style length (Fig.
+When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for visitation frequency was best explained by plant height, nectar concentration and style length (Fig.
 4a).
@@
 
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=12,fig.cap= "**Fig.
-4 | Contribution of traits in plant's network roles.** Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
-The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
-Thus, the top node has the mean value of the named trait for the 100% of species.
-Each node has a yes/no question and when the condition is fulfilled, the branch turns to the ‘yes’ direction and when not, to the ‘no’ direction.
-This rationale is followed in all the regression trees as indicated in the first branch division of the topmost node of each tree."}
-
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
-########################################################################################################################################################
-#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
-
-library(rpart.plot)
-library(rpart)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
-nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
-d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
-
-#Set correct colnames for plotting
-colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
-
-colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
-
-colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
-
-set.seed(2)
-tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
-
-set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
-
-set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50) 
-par(mfrow=c(1,3))
-
-rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.45,tweak = 1.25,type = 2) 
-rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.45,tweak = 1.25,type = 2)
-rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.45,tweak = 1.25,type = 2)
-
-```
-
-\elandscape
-
 # DISCUSSION
 
-Here, we show that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
+This study demonstrates that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
 These trade-offs are differentiated along three axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-These reproductive trade-offs helped explain partly the presence of floral visitor interactions, but not their visitation rates.
+These reproductive trade-offs helped partly explain the presence of floral visitor interactions, but not their visitation rates.
 However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
@@
 Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
-The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Supplementary Fig.
+The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Fig.
 S10).
 
-Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (presence-absence of interactions and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies strongly influence plant-pollinator interactions.
+Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (presence-absence of interactions and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies influence plant-pollinator interactions.
 For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
-1 and Supplementary Fig.
+1 and Fig.
 S6).
@@
 3) suggesting possible niche partitioning [@palmer2003; @phillips2020] between these two guilds.
-However, despite floral rewards, related traits were among the best at characterising species functional roles (Fig.
-4), yet the association between reproductive trade-offs and floral visitors did not account for floral rewards because there was insufficient data available.
+However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species functional roles (Fig.
+4).
 More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
@@
 
-# MATERIALS AND METHODS
-
-**Plant-pollinator network studies.** We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives (e.g., ‘The Web of Life’ [@fortuna2010] and ‘Mangal’ [@poisot2016].
-In total, our network dataset (see Supplementary Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
-
-**Taxonomy of plants and pollinators.** All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020] version _0.9.99_.
-We filled the ‘not found’ searches manually using http://www.theplantlist.org/ and http://www.mobot.org/ for plants and http://www.catalogueoflife.org/ for floral visitors.
-
-**Functional traits.** We selected 20 different functional traits based on their relevance to plant reproduction and data availability (Table 1).
-These included twelve quantitative and eight categorical traits belonging to three broader trait groupings (13 floral, 4 reproductive biology and 3 vegetative, Supplementary Information).
-For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Supplementary Fig.
-S1 for missing values information for each trait).
-
-**Phylogenetic Distance.** We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package _rtrees_ (https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
-
-\singlespacing
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=1, fig.width=14}
-setwd("~/R_Projects/Reproductive Traits")
-
-library(kableExtra)
-
-library(dplyr)
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant","Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Floral_unit_width",
-         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
-         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-n_of_records <- subset(missing.values, isna=="FALSE")
-Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
-           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")
-
-Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Autonomous selfing", "Compatibility system", "Breeding system", " ", " ", " ", " ")
-
-T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-           "Presence \n Absence", "None \n Low \n Medium \n High", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " "),align = c("l"))
-
-Type <- linebreak(c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive \n biology"),align = c("c"))
-
-Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology", "Reproductive \n biology","","","",""),align = c("c"))
-
-dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
-
-Number_of_records_quantitative <- c(n_of_records$num.isna[n_of_records$key=="Plant_height_mean_m"], n_of_records$num.isna[n_of_records$key=="Corolla_diameter_mean"],
-  n_of_records$num.isna[n_of_records$key=="Corolla_length_mean"], n_of_records$num.isna[n_of_records$key=="Floral_unit_width"],
-  n_of_records$num.isna[n_of_records$key=="Style_length"], n_of_records$num.isna[n_of_records$key=="Ovule_number"],
-  n_of_records$num.isna[n_of_records$key=="Flowers_per_plant"], n_of_records$num.isna[n_of_records$key=="Nectar_ul"],
-  n_of_records$num.isna[n_of_records$key=="Nectar_mg"], n_of_records$num.isna[n_of_records$key=="Nectar_concentration"], n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
-  n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level_fruit_set"])
-
-Number_of_records_categorical <- c(n_of_records$num.isna[n_of_records$key=="lifespan"], n_of_records$num.isna[n_of_records$key=="life_form"],
-                                   n_of_records$num.isna[n_of_records$key=="Flower_morphology"], n_of_records$num.isna[n_of_records$key=="Flower_symmetry"],
-                                   n_of_records$num.isna[n_of_records$key=="Nectar_presence_absence"], n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level"],
-                                   n_of_records$num.isna[n_of_records$key=="Compatibility_system"], n_of_records$num.isna[n_of_records$key=="Breeding_system"],
-                                   rep("",4))
-
-dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
-
-colnames(dat) <- c("Type","Traits", "Type", "Traits", "Categories")
-
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table 1 | Quantitative and categorical traits used in this study.}") %>%
-kable_styling(full_width = F,font_size = 10) %>%
-add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 3),bold=T)  %>%
-    column_spec(c(1,3), bold = T) %>% row_spec(0, bold=T)
-
-```
-
-\doublespacing
-
-**Data Imputation.** Trait missing values were imputed with the function _missForest_ [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of _missForest_ [@penone2014].
-To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-Although the variable of autonomous selfing had a high percentage of missing values (68%), we were able to solve this by back transforming the qualitative column of autonomous selfing to numerical.
-The categories of ‘none’, ‘low’, ‘medium’ and ‘high’ were converted to representative percentages of each category 0%, 13%, 50.5% and 88% respectively.
-This reduced the percentage of missing values for this column from 68% to 35% and allowed the imputation of this variable.
-However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Supplementary Fig.
-S1).
-Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79% of missing values.
-Further, we conducted an additional imputation on the filtered raw data by filled cells of either pollen grains per flower or microlitres of nectar.
-This subset comprised 755 species, 8.01% missing values and all traits but milligrams of nectar (~50% of missing values) were included in the imputation process.
-
-**Plant strategies.** We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01 respectively), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th–97.5th percentile range [@legendre2012], and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [@revell2012] (version _0.7-70_) with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Supplementary Fig.
-S2).
-We found little difference between the explained variance with the imputed dataset (51.08%) and the dataset without missing values (52.87%).
-In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
-For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
-
-**Phylogenetic signal of traits.** We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] version _0.7-70_ and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-**Network analyses.** Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-These networks were analysed in their qualitative (presence-absence) and quantitative (interaction frequency) form.
-First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
-Second, we analysed the untransformed weighted networks with interaction frequency that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency [@ballantyne2015], interaction frequency can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
-All analyses were conducted in R version _4.0.3_.
-
-**Visitation patterns.** We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
-This finding is consistent with previous research showing that _A.
-mellifera_ was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
-Hence, to control for the effect of _A.
-mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of interaction and visitation rate excluding _A.
-mellifera_.
-We found that _A.
-mellifera_, was partly driving some of the observed trends on PC1 (Supplementary Fig.
-S3).
-However, we did not detect major differences on PC2 and PC3.
-
-We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017] (version _2.14.6_).
-We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
-In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
-We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019] (version _1.7.2_).
-
-**Plant species functional roles.** We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d’) [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008] (version _2.15_).
-
-First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric ~ PC1 + PC2 + PC3).
-For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns section’.
-
-Second, to better understand these complex trait relationships, we used regression trees.
-Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
-We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2).
-We conducted this analysis using the _rpart_ package [@therneau2015] version _4.1-15_ with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] version _3.0.9_ to plot the regression trees.
-We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
-We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig.
-S4).
-
 # References
@@
 
-We thank all researchers that made their data available for our analysis.
-We thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
+This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
+We thank all researchers that made their data openly available and sent it upon request.
+We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
 We also thank Jason Tylianakis for his comments on the manuscript before submission.
-JBL thanks the University of New England for the funding provided to carry out this work.
+Finally, JBL thanks the University of New England for the funding provided to carry out this work.

### 2022-01-31 Manuscript/Lanuza_et_al_2021_Ecol_Letters.Rmd
Edits to fit the max of 5000 words

@@
 
-\textbf{Number of words:} Abstract  (146 words), main text (5097 words).
-
-\textbf{Number of references:} 77 (CHECK! Probably less now)
+\textbf{Number of words:} Abstract  (146 words), main text (4999 words).
+
+\textbf{Number of references:} 75
 
@@
 In addition, plant reproductive trade-offs determined important differences in the interaction level among floral visitor guilds.
-Our study shows the main plant reproductive trade-offs and their relevance to understand plant-pollinator interactions in a global context.
+Our study shows the main reproductive trade-offs of flowering plants and their relevance to understand plant-pollinator interactions in a global context.
 
@@
 Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that **describes the major** plant reproductive trade-offs is currently lacking [@roddy2021].
-In addition, macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
+In addition, macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with pollinators at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
 Linking the plant's position in trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
@@
 Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases [e.g., TRY, @kattge2011; and COMPADRE, @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
+With the recent availability of large trait databases [e.g., TRY @kattge2011; and COMPADRE @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
 However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
@@
 Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
-Remarkably, the combination of traits has shown to increase the predictive power of the network interactions [@eklof2013].
-**Moreover, the position in the trait space can determine plant and pollinator species’ functional roles [@dehling2016].
-Therefore, by considering the multidimensional reproductive trait space we could progress our understanding of plant-pollinator associations.
-Importantly, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.**
+**Importantly, the combination of traits has shown to increase the predictive power of the network interactions [@eklof2013] and by considering the position in the multidimensional trait space we can determine species’ functional roles within plant-pollinator networks [@dehling2016].
+Nonetheless, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.**
 
@@
 
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020] version _0.9.99_.
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020].
 We filled the ‘not found’ searches manually using http://www.theplantlist.org/ and http://www.mobot.org/ for plants and http://www.catalogueoflife.org/ for floral visitors.
 
-\newpage
-
 **Functional traits**
 
-We selected a total of 19 different functional traits that included both reproductive and vegetative traits (Table 1 and Supplementary Information).
+We selected a total of 19 different functional traits that included both reproductive and vegetative traits (see Table 1 and Supplementary Information).
 From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
-Note that autonomous selfing was recorded quantitatively (fruit set) and qualitatively because this trait was rarely available in its numerical form.
 The 3 remaining traits, were vegetative traits that are commonly used to characterize the global spectrum of plant form and function and represent the fast-slow continuum of trait variation (e.g., short-lived versus perennial species).
 For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns x 1506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Fig.
+From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Fig.
 S1 for missing values information for each trait).
@@
 n_of_records <- subset(missing.values, isna=="FALSE")
-Trait <- linebreak(c("Plant height \n (m)", "Flower width \n (mm)", "Flower length \n (mm)", "Inflorescence width \n (mm)", "Style length \n (mm)", "Ovules per flower",
-           "Flowers per plant", "Nectar \n ($\\mu$l)", "Nectar \n (mg)", "Nectar concentration \n ($\\%$)", "Pollen grains \n per flower", "Autonomous selfing \n (fruit set)"),align = c("c"))
-
-Trait1 <- linebreak(c("Lifepan", "Life form", "Flower \n shape", "Flower \n symmetry", "Nectar", "Compatibility \n system", "Breeding \n system", "Autonomous \n selfing", " ", " ", " ", " "),align = c("c"))
+Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
+           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")
+
+Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Compatibility system", "Breeding system", " ", " ", " ", " ", " ")
 
 T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-           "Presence \n Absence", "Self-incompatible \n Part.
-self-compatible \n Self-compatible", "Hermaphrodite \n Monoecious \n Dioecious","None \n Low \n Medium \n High", " ", " ", " ", ""),align = c("l"))
+           "Presence \n Absence", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " ", ""),align = c("l"))
 
@@
 
-Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology","Reproductive \n biology","","","", ""),align = c("c"))
+Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology","","","","", ""),align = c("c"))
 
@@
 
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table 1} Plant functional traits used in this study.") %>%
+kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table 1 | Quantitative and categorical traits used in this study.}") %>%
 kable_styling(full_width = F,font_size = 10) %>%
@@
 To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Fig.
-S1).
-Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79% of missing values.
-Further, we conducted an additional imputation process on the subset of species with data for pollen per flower and microliters of nectar.
-This subset comprised 755 species, 8.01% missing values and all traits but milligrams of nectar (~50% of missing values) were included in the imputation process.
+We conducted two different imputations, one for the full set of species (1,506 species, 5.79% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
+S1) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01% of missing values).
 
@@
 We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the reproductive spectrum of trait variation.
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
@@
 Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function _phyl.pca_ from the package _phytools_ version _0.7-70_ [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
+We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
+Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Fig.
 S2).
@@
 
-**Phylogenetic signal of traits**
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] version _0.7-70_ and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
+**Phylogenetic signal**
+
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
@@
 Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-These networks were analysed in their qualitative (presence-absence) and quantitative (interaction frequency) form.
+These networks were analysed in their qualitative and quantitative form.
 First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
@@
 
-We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
+We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species.
 For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
 In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
@@
 
-We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017] version _2.14.6_.
+We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017].
 We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
@@
 We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019] version _1.7.2_.
+We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019].
 
@@
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization [d’\; @bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008] version _2.15_.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d’) [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008].
 
@@
 We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
-We conducted this analysis using the _rpart_ package [@therneau2015] version _4.1-15_ with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] version _3.0.9_ to plot the regression trees.
+We conducted this analysis using the _rpart_ package [@therneau2015] with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] to plot the regression trees.
 We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
@@
 
-The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Fig.
+The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Fig.
 1 and Fig.
@@
 
-**Phylogenetic signal of traits**
+**Phylogenetic signal**
 

### 2022-01-31 Manuscript/Lanuza_et_al_2021_Ecol_Letters.tex
Edits to fit the max of 5000 words

@@
 
-\textbf{Number of words:} Abstract (146 words), main text (5097 words).
+\textbf{Number of words:} Abstract (146 words), main text (4999 words).
 
-\textbf{Number of references:} 77 (CHECK! Probably less now)
+\textbf{Number of references:} 75
 
@@
 Despite the astonishing diversity of floral structures among flowering plants (\protect\hyperlink{ref-barrett2002}{Barrett 2002}; \protect\hyperlink{ref-schiestl2013}{Schiestl \& Johnson 2013}) and their importance in shaping plant-pollinator interactions (\protect\hyperlink{ref-fenster2004}{Fenster \emph{et al.} 2004}; \protect\hyperlink{ref-dellinger2020}{Dellinger 2020}), a unified framework that \textbf{describes the major} plant reproductive trade-offs is currently lacking (\protect\hyperlink{ref-roddy2021}{Roddy \emph{et al.} 2021}).
-In addition, macroecological studies that investigate plant reproductive traits are scarce (\protect\hyperlink{ref-baude2016}{Baude \emph{et al.} 2016}; \protect\hyperlink{ref-munoz2016}{Munoz \emph{et al.} 2016}; \protect\hyperlink{ref-grossenbacher2017}{Grossenbacher \emph{et al.} 2017}; \protect\hyperlink{ref-moeller2017}{Moeller \emph{et al.} 2017}) and consequently, there is poor understanding of how reproductive traits drive interactions with floral visitors at large scales (\protect\hyperlink{ref-sargent2008}{Sargent \& Ackerly 2008}; \protect\hyperlink{ref-rech2016}{Rech \emph{et al.} 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}; \protect\hyperlink{ref-ruger2018}{Rüger \emph{et al.} 2018}).
+In addition, macroecological studies that investigate plant reproductive traits are scarce (\protect\hyperlink{ref-baude2016}{Baude \emph{et al.} 2016}; \protect\hyperlink{ref-munoz2016}{Munoz \emph{et al.} 2016}; \protect\hyperlink{ref-grossenbacher2017}{Grossenbacher \emph{et al.} 2017}; \protect\hyperlink{ref-moeller2017}{Moeller \emph{et al.} 2017}) and consequently, there is poor understanding of how reproductive traits drive interactions with pollinators at large scales (\protect\hyperlink{ref-sargent2008}{Sargent \& Ackerly 2008}; \protect\hyperlink{ref-rech2016}{Rech \emph{et al.} 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}; \protect\hyperlink{ref-ruger2018}{Rüger \emph{et al.} 2018}).
 Linking the plant's position in trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations (\protect\hyperlink{ref-dehling2016}{Dehling \emph{et al.} 2016}).
@@
 Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY, \protect\hyperlink{ref-kattge2011}{Kattge \emph{et al.} 2011}; and COMPADRE, \protect\hyperlink{ref-salguero2015}{Salguero-Gómez \emph{et al.} 2015}), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function (\protect\hyperlink{ref-diaz2016}{Díaz \emph{et al.} 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}; \protect\hyperlink{ref-bruelheide2018}{Bruelheide \emph{et al.} 2018}; \protect\hyperlink{ref-carmona2021}{Carmona \emph{et al.} 2021}).
+With the recent availability of large trait databases (e.g., TRY \protect\hyperlink{ref-kattge2011}{Kattge \emph{et al.} 2011}; and COMPADRE \protect\hyperlink{ref-salguero2015}{Salguero-Gómez \emph{et al.} 2015}), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function (\protect\hyperlink{ref-diaz2016}{Díaz \emph{et al.} 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}; \protect\hyperlink{ref-bruelheide2018}{Bruelheide \emph{et al.} 2018}; \protect\hyperlink{ref-carmona2021}{Carmona \emph{et al.} 2021}).
 However, most studies have focused on vegetative traits such as leaf (\protect\hyperlink{ref-wright2004}{Wright \emph{et al.} 2004}), wood (\protect\hyperlink{ref-chave2009}{Chave \emph{et al.} 2009}), or root (\protect\hyperlink{ref-laughlin2021}{Laughlin \emph{et al.} 2021}) trade-offs with little or no attention given to reproductive traits (\protect\hyperlink{ref-evojtko2020}{E-Vojtkó \emph{et al.} 2020}; \protect\hyperlink{ref-roddy2021}{Roddy \emph{et al.} 2021}) which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
@@
 Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure (\protect\hyperlink{ref-stang2009}{Stang \emph{et al.} 2009}; \protect\hyperlink{ref-ibanez2012}{Ibanez 2012}).
-Remarkably, the combination of traits has shown to increase the predictive power of the network interactions (\protect\hyperlink{ref-eklof2013}{Eklöf \emph{et al.} 2013}).
-\textbf{Moreover, the position in the trait space can determine plant and pollinator species' functional roles (\protect\hyperlink{ref-dehling2016}{Dehling \emph{et al.} 2016}).
-Therefore, by considering the multidimensional reproductive trait space we could progress our understanding of plant-pollinator associations.
-Importantly, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.}
+\textbf{Importantly, the combination of traits has shown to increase the predictive power of the network interactions (\protect\hyperlink{ref-eklof2013}{Eklöf \emph{et al.} 2013}) and by considering the position in the multidimensional trait space we can determine species' functional roles within plant-pollinator networks (\protect\hyperlink{ref-dehling2016}{Dehling \emph{et al.} 2016}).
+Nonetheless, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.}
 
@@
 
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain \emph{et al.} 2020}) version \emph{0.9.99}.
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain \emph{et al.} 2020}).
 We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
-
-\newpage
 
@@
 
-We selected a total of 19 different functional traits that included both reproductive and vegetative traits (Table 1 and Supplementary Information).
+We selected a total of 19 different functional traits that included both reproductive and vegetative traits (see Table 1 and Supplementary Information).
 From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
-Note that autonomous selfing was recorded quantitatively (fruit set) and qualitatively because this trait was rarely available in its numerical form.
 The 3 remaining traits, were vegetative traits that are commonly used to characterize the global spectrum of plant form and function and represent the fast-slow continuum of trait variation (e.g., short-lived versus perennial species).
 For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns x 1506 species) we were able to fill 24,341 cells (80.8\% of the dataset, see Fig.
+From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8\% of the dataset, see Fig.
 S1 for missing values information for each trait).
@@
 
-\caption{\label{tab:unnamed-chunk-1}\textbf{Table 1} Plant functional traits used in this study.}
+\caption{\label{tab:unnamed-chunk-1}\textbf{Table 1 | Quantitative and categorical traits used in this study.}}
 \centering
@@
 \midrule
-\textbf{Vegetative} & \makecell[c]{Plant height \\ (m)} & \textbf{Vegetative} & Lifepan & \makecell[l]{Short-lived \\ Perennial}\\
+\textbf{Vegetative} & Plant height (m) & \textbf{Vegetative} & Lifepan & \makecell[l]{Short-lived \\ Perennial}\\
 \addlinespace
-\textbf{Floral} & \makecell[c]{Flower width \\ (mm)} & \textbf{Vegetative} & Life form & \makecell[l]{Herb \\ Shrub \\ Tree}\\
+\textbf{Floral} & Flower width (mm) & \textbf{Vegetative} & Life form & \makecell[l]{Herb \\ Shrub \\ Tree}\\
 \addlinespace
-\textbf{Floral} & \makecell[c]{Flower length \\ (mm)} & \textbf{Floral} & \makecell[c]{Flower \\ shape} & \makecell[l]{Brush \\ Campanulate \\ Capitulum \\ Open \\ Papilionaceous \\ Tube}\\
+\textbf{Floral} & Flower length (mm) & \textbf{Floral} & Flower shape & \makecell[l]{Brush \\ Campanulate \\ Capitulum \\ Open \\ Papilionaceous \\ Tube}\\
 \addlinespace
-\textbf{Floral} & \makecell[c]{Inflorescence width \\ (mm)} & \textbf{Floral} & \makecell[c]{Flower \\ symmetry} & \makecell[l]{Actinomorphic \\ Zygomorphic}\\
+\textbf{Floral} & Inflorescence width (mm) & \textbf{Floral} & Flower symmetry & \makecell[l]{Actinomorphic \\ Zygomorphic}\\
 \addlinespace
-\textbf{Floral} & \makecell[c]{Style length \\ (mm)} & \textbf{Floral} & Nectar & \makecell[l]{Presence \\ Absence}\\
+\textbf{Floral} & Style length (mm) & \textbf{Floral} & Nectar & \makecell[l]{Presence \\ Absence}\\
 \addlinespace
-\textbf{Floral} & Ovules per flower & \textbf{\makecell[c]{Reproductive \\ biology}} & \makecell[c]{Compatibility \\ system} & \makecell[l]{Self-incompatible \\ Part.
-self-compatible \\ Self-compatible}\\
+\textbf{Floral} & Ovules per flower & \textbf{\makecell[c]{Reproductive \\ biology}} & Compatibility system & \makecell[l]{Self-incomp. \\ Part. self-comp. \\ Self-comp.}\\
 \addlinespace
-\textbf{Floral} & Flowers per plant & \textbf{\makecell[c]{Reproductive \\ biology}} & \makecell[c]{Breeding \\ system} & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious}\\
+\textbf{Floral} & Flowers per plant & \textbf{\makecell[c]{Reproductive \\ biology}} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious}\\
 \addlinespace
-\textbf{Floral} & \makecell[c]{Nectar \\ ($\mu$l)} & \textbf{\makecell[c]{Reproductive \\ biology}} & \makecell[c]{Autonomous \\ selfing} & \makecell[l]{None \\ Low \\ Medium \\ High}\\
+\textbf{Floral} & Nectar ($\mu$l) & \textbf{} &  & \\
 \addlinespace
-\textbf{Floral} & \makecell[c]{Nectar \\ (mg)} & \textbf{} &  & \\
+\textbf{Floral} & Nectar (mg) & \textbf{} &  & \\
 \addlinespace
-\textbf{Floral} & \makecell[c]{Nectar concentration \\ ($\%$)} & \textbf{} &  & \\
+\textbf{Floral} & Nectar concentration ($\%$) & \textbf{} &  & \\
 \addlinespace
-\textbf{Floral} & \makecell[c]{Pollen grains \\ per flower} & \textbf{} &  & \\
+\textbf{Floral} & Pollen grains per flower & \textbf{} &  & \\
 \addlinespace
-\textbf{\makecell[c]{Reproductive \\ biology}} & \makecell[c]{Autonomous selfing \\ (fruit set)} & \textbf{} &  & \\
+\textbf{\makecell[c]{Reproductive \\ biology}} & Autonomous selfing (fruit set) & \textbf{} &  & \\
 \bottomrule
@@
 To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} (\protect\hyperlink{ref-santos2018}{Chamberlain \emph{et al.} 2018}) based on a previous conceptual framework that considers phylogenetic eigenvectors (\protect\hyperlink{ref-diniz-filho2012}{Diniz-Filho \emph{et al.} 2012}).
-However, we were unable to include nectar and pollen traits on the imputation process because of the high percentage of missing values (Fig.
-S1).
-Hence, the imputed dataset had 1,506 species, seven categorical and eight numerical variables and 5.79\% of missing values.
-Further, we conducted an additional imputation process on the subset of species with data for pollen per flower and microliters of nectar.
-This subset comprised 755 species, 8.01\% missing values and all traits but milligrams of nectar (\textasciitilde50\% of missing values) were included in the imputation process.
+We conducted two different imputations, one for the full set of species (1,506 species, 5.79\% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
+S1) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01\% of missing values).
 
@@
 We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the reproductive spectrum of trait variation.
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
@@
 Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} version \emph{0.7-70} (\protect\hyperlink{ref-revell2012}{Revell 2012}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams 2010}).
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell 2012}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams 2010}).
+Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Fig.
 S2).
@@
 
-\textbf{Phylogenetic signal of traits}
+\textbf{Phylogenetic signal}
 
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell 2012}) version \emph{0.7-70} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell 2012}) and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
@@
 
-We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative (presence/absence) and quantitative (visitation rate) floral interactions per plant species.
+We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species.
 For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits of all groups, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
 In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total).
@@
 
-We implemented Bayesian generalized linear mixed models using the R package \emph{brms} (\protect\hyperlink{ref-burkner2017}{Bürkner 2017}) version \emph{2.14.6}.
+We implemented Bayesian generalized linear mixed models using the R package \emph{brms} (\protect\hyperlink{ref-burkner2017}{Bürkner 2017}).
 We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
@@
 We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package (\protect\hyperlink{ref-gabry2019}{Gabry \emph{et al.} 2019}) version \emph{1.7.2}.
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package (\protect\hyperlink{ref-gabry2019}{Gabry \emph{et al.} 2019}).
 
@@
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies (\protect\hyperlink{ref-dormann2008}{Dormann \emph{et al.} 2008}) with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d'; \protect\hyperlink{ref-bluthgen2006}{Blüthgen \emph{et al.} 2006}), which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} (\protect\hyperlink{ref-dormann2008}{Dormann \emph{et al.} 2008}) version \emph{2.15}.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') (\protect\hyperlink{ref-bluthgen2006}{Blüthgen \emph{et al.} 2006}), which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} (\protect\hyperlink{ref-dormann2008}{Dormann \emph{et al.} 2008}).
 
@@
 We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
-We conducted this analysis using the \emph{rpart} package (\protect\hyperlink{ref-therneau2015}{Therneau \emph{et al.} 2015}) version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package (\protect\hyperlink{ref-milborrow2015}{Milborrow 2015}) version \emph{3.0.9} to plot the regression trees.
+We conducted this analysis using the \emph{rpart} package (\protect\hyperlink{ref-therneau2015}{Therneau \emph{et al.} 2015}) with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package (\protect\hyperlink{ref-milborrow2015}{Milborrow 2015}) to plot the regression trees.
 We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
@@
 
-The phylogenetically informed principal component analysis (pPCA) captured by the first two and three axes 51.8\% and 70.97\% of trait variation, respectively (Fig.
+The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of trait variation, respectively (Fig.
 1 and Fig.
@@
 
-\textbf{Phylogenetic signal of traits}
+\textbf{Phylogenetic signal}
 

### 2022-01-31 Manuscript/MS_word.Rmd
Edits to fit the max of 5000 words

@@
 ---
-title: \singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors
+---
+title: \singlespacing \vspace{-1.6cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors
 
@@
 output:
-  word_document: default
-  bookdown::word_document2: default  # for cross-references
+  bookdown::pdf_document2:
     fig_caption: yes
@@
 # zotero: "My shared Zotero group"
-csl: ecology.csl
-# csl: https://www.zotero.org/styles/ecology
-
+csl: ecology.csl #ecology letters
+notes-after-punctuation: false
 link-citations: yes
@@
 - \usepackage{pdflscape}
+#- \DeclareUnicodeCharacter{0301}{*************************************}
 
 ---
-
-\vspace{-1.4cm}
-
-\singlespacing
-
-\textbf{Jose B.
-Lanuza$^{1,2}$} <barragansljose@gmail.com>, \textbf{Romina Rader$^{1}$} <rrader@une.edu.au>, \textbf{Jamie Stavert$^{3}$} <jamie.stavert@gmail.com>, \textbf{Liam K.
-Kendall$^{4}$} <liam.k.kendall@gmail.com>, \textbf{Manu E.
-Saunders$^{1}$} <Manu.Saunders@une.edu.au> \textbf{and Ignasi Bartomeus$^{2}$} <nacho.bartomeus@gmail.com>
-
-\small
-
-^1^ School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-^2^ Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-^3^ Department of Conservation | Te Papa Atawhai, Auckland, New Zealand.
-^4^ Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden.
-
-\doublespacing
-\normalsize
-
-\textbf{Statement of authorship:} JBL, RR and IB designed the study.
-JBL collated the data and conducted analysis with guidance of JS, LKK and IB.
-JBL wrote the manuscript with contributions of all authors.
-
-\textbf{Data accessibility statement:} All data and code used to conduct this study will be deposited in the public repository Dryad upon acceptance.
-
-\textbf{Short title:} Plant reproductive trade-offs.
-
-\textbf{Keywords:} life-history strategies | plant reproductive trade-offs | plant-pollinator interactions.
-
-\textbf{Type of article:} Letter.
-
-\textbf{Number of words:} Abstract  (146 words), main text (XXXX).
-
-\textbf{Number of references:} 77 (CHECK! Probably less now)
-
-\textbf{Number of figures and tables:} 4 figures and 1 table.
-
-\textbf{Corresponding author:} Jose B. Lanuza | +34 616375981| <barragansljose@gmail.com>
-
-\newpage
-
-# ABSTRACT
-
-Plant life-history strategies are constrained by cost-benefit trade-offs that determine plant form and function.
-However, despite recent advances in the understanding of plant trait variation, little is known about plant reproductive trade-offs and how these constrain life-history strategies and shape interactions with floral visitors.
-Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
-We found that over half of all plant reproductive trait variation was explained by two independent axes.
-Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
-In addition, plant reproductive trade-offs determined important differences in the interaction level among floral visitor guilds.
-Our study shows the main plant reproductive trade-offs and their relevance to understand plant-pollinator interactions in a global context.
-
-\newpage
-
-\doublespacing
-\vspace{5mm}
-\normalsize
 
@@
 
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020] version _0.9.99_.
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020].
 We filled the ‘not found’ searches manually using http://www.theplantlist.org/ and http://www.mobot.org/ for plants and http://www.catalogueoflife.org/ for floral visitors.
-
-\newpage
 
@@
 From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
-Note that autonomous selfing was recorded quantitatively (fruit set) and qualitatively because this trait was rarely available in its numerical form.
 The 3 remaining traits, were vegetative traits that are commonly used to characterize the global spectrum of plant form and function and represent the fast-slow continuum of trait variation (e.g., short-lived versus perennial species).
 For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns x 1506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Fig.
+From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Fig.
 S1 for missing values information for each trait).
@@
 
-\singlespacing
-
-\doublespacing
-
 **Data Imputation**
@@
 
-**Phylogenetic signal of traits**
+**Phylogenetic signal**
 
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] version _0.7-70_ and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
@@
 We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
-We conducted this analysis using the _rpart_ package [@therneau2015] version _4.1-15_ with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] version _3.0.9_ to plot the regression trees.
+We conducted this analysis using the _rpart_ package [@therneau2015] with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] to plot the regression trees.
 We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
 We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Fig.
+We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (Fig.
 S4).
@@
 
-\blandscape
-
-\vspace*{-28mm}
-
-\vspace{5mm}
-
-**Phylogenetic signal of traits**
+**Phylogenetic signal**
 
@@
 Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
-The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (see Fig.
+The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
 S10).
@@
 Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
-
-# References
-
-<div id ="refs"></div>
-
-# Acknowledgements
-
-This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-We thank all researchers that made their data openly available and sent it upon request.
-We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
-We also thank Jason Tylianakis for his comments on the manuscript before submission.
-Finally, JBL thanks the University of New England for the funding provided to carry out this work.

### 2022-02-01 Manuscript/Lanuza_et_al_2021_Ecol_Letters.Rmd
Ecol Letters

@@
 
-\textbf{Number of words:} Abstract  (146 words), main text (4999 words).
+\textbf{Number of words:} Abstract  (146 words), main text excluding references, acknowledgements and captions (4983 words).
 
@@
 
-Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that **describes the major** plant reproductive trade-offs is currently lacking [@roddy2021].
+Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that describes the major plant reproductive trade-offs is currently lacking [@roddy2021].
 In addition, macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with pollinators at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
@@
 Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
-**However, plant reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020] and remains unclear how specific plant reproductive biology traits (e.g., mating or compatibility system) influence plant-pollinator associations [@tur2013; @devaux2014].**
+However, plant reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020] and remains unclear how specific plant reproductive biology traits (e.g., mating or compatibility system) influence plant-pollinator associations [@tur2013; @devaux2014].
 
@@
 Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
-**Importantly, the combination of traits has shown to increase the predictive power of the network interactions [@eklof2013] and by considering the position in the multidimensional trait space we can determine species’ functional roles within plant-pollinator networks [@dehling2016].
-Nonetheless, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.**
+Importantly, the combination of traits has shown to increase the predictive power of the network interactions [@eklof2013] and by considering the position in the multidimensional trait space we can determine species’ roles within plant-pollinator interaction networks [@dehling2016].
+Nonetheless, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.
 
@@
 Second, we investigate how plant species’ position in trait-space influence interactions with floral visitors.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species’ roles within networks using a set of complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
+Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species’ roles within networks using a set of complementary interaction network metrics (i.e., visitation rate, normalized degree and specialization).
 
@@
 Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives [e.g., The Web of Life, @fortuna2010; and Mangal, @poisot2016].
-In total, our network dataset (Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+In total, our network dataset (Table S1) constituted 60 weighted (visitation rate) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
 
@@
 
-**Functional traits**
+**Plant traits**
 
@@
 
-We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
+We explored the trade-offs between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
 We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
@@
 We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Fig.
+Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
 S2).
@@
 First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
-Second, we analysed the untransformed weighted networks with interaction frequency that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency [@ballantyne2015], interaction frequency can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
+Second, we analysed the untransformed weighted networks with visitation rate that accounts for the intensity of the interaction.
+Although floral visitors are not always pollinators and visitation rate does not consider each pollinator species efficiency [@ballantyne2015], visitation rate can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
 In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
@@
 For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
 In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
@@
 Hence, to control for the effect of _A.
-mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of interaction and visitation rate excluding _A.
+mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and visitation rate excluding _A.
 mellifera_.
@@
 We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017].
-We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
-In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
+We modelled presence-absence of observed interactions and visitation rate as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., visitation rate ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
+We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
 Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
-We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
+We specified for presence-absence of interaction and visitation rate a Bernoulli and a zero inflated negative binomial distribution, respectively.
+The models were run with weakly informative priors from the brms function, 3,000 iterations and with previous 1,000 warm up iterations.
 We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019].
 
-**Plant species functional roles**
-
-We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
+**Plant species network roles**
+
+We investigated whether different quantitative traits determined plant species network roles using Bayesian modelling and regression trees.
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
@@
 For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns section’.
-
-Second, to better understand these complex trait relationships, we used regression trees.
-Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
+Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns’ section.
+
+Second, to better understand complex trait relationships, we used regression trees.
+Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction.
 We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
 We conducted this analysis using the _rpart_ package [@therneau2015] with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] to plot the regression trees.
-We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
+We considered the species level indices as response variables (visitation rate, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
 We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
@@
 
-The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall visitation rates (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant trends across the different floral visitor guilds on both presence-absence and visitation interactions (Fig.
+The main axes of trait variation explained partly presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall visitation rates (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
+However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and visitation rates (Fig.
 3).
-On the pollinator dependence trade-off, all floral visitor guilds interacted more frequently with plant species with higher pollinator dependence (PC2; Fig.
+We found that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds (flower number - flower size trade-off, PC1; Fig.
+3a).
+However, plant species with high flower number but small flowers had higher visitation rates of bees and syrphids guilds (PC1; Fig.
+3d).
+Remarkably, all plant species with higher pollinator dependence had higher number of interacting partners and visitation rates for all floral visitor guilds (PC2; Fig.
 3b and Fig.
 3e).
-For presence-absence interactions we found that all Diptera, Coleoptera and non-bee-Hymenoptera guilds interacted more frequently with plants with high flower number and small flowers (flower number - flower size trade-off, PC1; Fig.
-3a) but bees and Lepidoptera interacted slightly more frequently with plant species with low flower number but large flowers.
-For presence-absence interactions on PC3 (style length trade-off; Fig.
-3c), we found that bees interacted clearly more with plant species with long styles and high selfing and the rest of the guilds interacted slightly more with plant species with short styles and low selfing.
-In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-syrphid-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig.
-3d).
-On the style length trade-off, bees, Lepidoptera and non-bee-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while syrphids, non-syrphid-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
+Finally, plant species with short styles and low selfing had higher interaction partners of all guilds but bees that interacted clearly more with plant species with long styles and high selfing (style length trade-off; Fig.
+3c).
+However, for visitation rate, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
 3f).
 
-The additional model for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and visitation rate (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
+The additional model for both presence-absence of interaction (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and visitation rate (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
+The contrasting differences between presence-absence of interaction and visitation rate for bees on PC1 (Fig.
 3a and Fig.
-3d) were driven by the family Andrenidae, which interacted more frequently on presence-absence interactions with plant species with low number of large flowers (Fig.
+3d) were driven by the family Andrenidae that had higher number of interacting partners but lower visitation rates on plant species with low number of large flowers (Fig.
 S8).
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3** Interaction (yes/no) and visitation rates across the three main axes of trait variation per floral visitor guild.
-Fitted posterior estimates of the presence/absence of interaction (a, b and c) and number of visits (d, e and f) made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and visitation rate (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
 PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.
@@
 
-**Plant species functional roles**
+**Plant species network roles**
 
 The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
-S9; interaction frequency ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
-On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
+S9; visitation rate ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
+Overall, the most notable trends were found on PC1 and PC3 for visitation rate and specialization.
+On the flower number - flower size trade-off (PC1), visitation rate was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
 S9a).
@@
 S9g).
-On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
+On the style length trade-off (PC3), visitation rate was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
 S9c).
-Again, specialization showed the opposite trend to interaction frequency (Fig.
+Again, specialization showed the opposite trend to visitation rate (Fig.
 S9i).
 
-When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for visitation frequency was best explained by plant height, nectar concentration and style length (Fig.
+When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for visitation rate was best explained by plant height, nectar concentration and style length (Fig.
 4a).
-Specifically, species taller than 3.9m had the highest interaction frequency, while species that were shorter than 3.9m and had a nectar concentration lower than 16% had the lowest interaction frequency.
+Specifically, species taller than 3.9m had the highest visitation rate, while species that were shorter than 3.9m and had a nectar concentration lower than 16% had the lowest visitation rate.
 Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=12,fig.cap= "**Figure 4** Contribution of traits in plant's network roles.
-Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
+Regression tree analysis of visitation rate (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
 The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
@@
 
-rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.75,tweak = 1.25,type = 2) 
+rpart.plot(tree1, box.palette="GnOr", main="(a) Visitation rate", cex.main=1.75,tweak = 1.25,type = 2) 
 rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.75,tweak = 1.25,type = 2)
@@
 However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
-Moreover, we found that the plant species functional roles within pollination networks were best explained by plant size and floral reward related traits.
+Moreover, we found that the plant species network roles were best explained by plant size and floral reward related traits.
 
@@
 
-Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (presence-absence of interactions and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies influence plant-pollinator interactions.
+Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (number of interaction partners and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies influence plant-pollinator interactions.
 For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
@@
 3) suggesting possible niche partitioning [@palmer2003; @phillips2020] between these two guilds.
-However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species functional roles (Fig.
+However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species network roles (Fig.
 4).
@@
 
-To conclude, we provide the first description of plant reproductive trade-offs using a large global dataset of plant traits.
+To conclude, we provide a robust description of plant reproductive trade-offs using a large global dataset of plant traits.
 We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.

### 2022-02-01 Manuscript/Lanuza_et_al_2021_Ecol_Letters.tex
Ecol Letters

@@
 
-\textbf{Number of words:} Abstract (146 words), main text (4999 words).
+\textbf{Number of words:} Abstract (146 words), main text excluding references, acknowledgements and captions (4983 words).
 
@@
 
-Despite the astonishing diversity of floral structures among flowering plants (\protect\hyperlink{ref-barrett2002}{Barrett 2002}; \protect\hyperlink{ref-schiestl2013}{Schiestl \& Johnson 2013}) and their importance in shaping plant-pollinator interactions (\protect\hyperlink{ref-fenster2004}{Fenster \emph{et al.} 2004}; \protect\hyperlink{ref-dellinger2020}{Dellinger 2020}), a unified framework that \textbf{describes the major} plant reproductive trade-offs is currently lacking (\protect\hyperlink{ref-roddy2021}{Roddy \emph{et al.} 2021}).
+Despite the astonishing diversity of floral structures among flowering plants (\protect\hyperlink{ref-barrett2002}{Barrett 2002}; \protect\hyperlink{ref-schiestl2013}{Schiestl \& Johnson 2013}) and their importance in shaping plant-pollinator interactions (\protect\hyperlink{ref-fenster2004}{Fenster \emph{et al.} 2004}; \protect\hyperlink{ref-dellinger2020}{Dellinger 2020}), a unified framework that describes the major plant reproductive trade-offs is currently lacking (\protect\hyperlink{ref-roddy2021}{Roddy \emph{et al.} 2021}).
 In addition, macroecological studies that investigate plant reproductive traits are scarce (\protect\hyperlink{ref-baude2016}{Baude \emph{et al.} 2016}; \protect\hyperlink{ref-munoz2016}{Munoz \emph{et al.} 2016}; \protect\hyperlink{ref-grossenbacher2017}{Grossenbacher \emph{et al.} 2017}; \protect\hyperlink{ref-moeller2017}{Moeller \emph{et al.} 2017}) and consequently, there is poor understanding of how reproductive traits drive interactions with pollinators at large scales (\protect\hyperlink{ref-sargent2008}{Sargent \& Ackerly 2008}; \protect\hyperlink{ref-rech2016}{Rech \emph{et al.} 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}; \protect\hyperlink{ref-ruger2018}{Rüger \emph{et al.} 2018}).
@@
 Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches (\protect\hyperlink{ref-fenster2004}{Fenster \emph{et al.} 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero \emph{et al.} 2014}) and trait-matching analyses (\protect\hyperlink{ref-stang2009}{Stang \emph{et al.} 2009}; \protect\hyperlink{ref-bartomeus2016}{Bartomeus \emph{et al.} 2016}).
-\textbf{However, plant reproductive traits have been overlooked beyond highly specialised pollination systems (\protect\hyperlink{ref-dellinger2020}{Dellinger 2020}) and remains unclear how specific plant reproductive biology traits (e.g., mating or compatibility system) influence plant-pollinator associations (\protect\hyperlink{ref-tur2013}{Tur \emph{et al.} 2013}; \protect\hyperlink{ref-devaux2014}{Devaux \emph{et al.} 2014}).}
+However, plant reproductive traits have been overlooked beyond highly specialised pollination systems (\protect\hyperlink{ref-dellinger2020}{Dellinger 2020}) and remains unclear how specific plant reproductive biology traits (e.g., mating or compatibility system) influence plant-pollinator associations (\protect\hyperlink{ref-tur2013}{Tur \emph{et al.} 2013}; \protect\hyperlink{ref-devaux2014}{Devaux \emph{et al.} 2014}).
 
@@
 Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure (\protect\hyperlink{ref-stang2009}{Stang \emph{et al.} 2009}; \protect\hyperlink{ref-ibanez2012}{Ibanez 2012}).
-\textbf{Importantly, the combination of traits has shown to increase the predictive power of the network interactions (\protect\hyperlink{ref-eklof2013}{Eklöf \emph{et al.} 2013}) and by considering the position in the multidimensional trait space we can determine species' functional roles within plant-pollinator networks (\protect\hyperlink{ref-dehling2016}{Dehling \emph{et al.} 2016}).
-Nonetheless, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.}
+Importantly, the combination of traits has shown to increase the predictive power of the network interactions (\protect\hyperlink{ref-eklof2013}{Eklöf \emph{et al.} 2013}) and by considering the position in the multidimensional trait space we can determine species' roles within plant-pollinator interaction networks (\protect\hyperlink{ref-dehling2016}{Dehling \emph{et al.} 2016}).
+Nonetheless, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.
 
@@
 Second, we investigate how plant species' position in trait-space influence interactions with floral visitors.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' roles within networks using a set of complementary interaction network metrics (i.e., interaction strength, normalized degree and specialization).
+Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' roles within networks using a set of complementary interaction network metrics (i.e., visitation rate, normalized degree and specialization).
 
@@
 Many of these networks are freely available either as published studies (\protect\hyperlink{ref-olesen2007}{Olesen \emph{et al.} 2007}; \protect\hyperlink{ref-fortuna2010}{Fortuna \emph{et al.} 2010}; \protect\hyperlink{ref-carvalheiro2014}{Carvalheiro \emph{et al.} 2014}) or available in online archives (e.g., The Web of Life, \protect\hyperlink{ref-fortuna2010}{Fortuna \emph{et al.} 2010}; and Mangal, \protect\hyperlink{ref-poisot2016}{Poisot \emph{et al.} 2016}).
-In total, our network dataset (Table S1) constituted 60 weighted (interaction frequency) and 4 unweighted (presence/absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+In total, our network dataset (Table S1) constituted 60 weighted (visitation rate) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
 
@@
 
-\textbf{Functional traits}
+\textbf{Plant traits}
 
@@
 
-We explored the trade-offs between different quantitative plant functional traits with a phylogenetically informed Principal Component Analysis (pPCA).
+We explored the trade-offs between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
 We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
@@
 We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell 2012}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams 2010}).
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (see Fig.
+Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
 S2).
@@
 First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
-Second, we analysed the untransformed weighted networks with interaction frequency that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and interaction frequency does not consider each pollinator species efficiency (\protect\hyperlink{ref-ballantyne2015}{Ballantyne \emph{et al.} 2015}), interaction frequency can provide valuable information of the contribution of floral visitors to pollination (\protect\hyperlink{ref-vazquez2005}{Vázquez \emph{et al.} 2005}, \protect\hyperlink{ref-vazquez2012}{2012}).
+Second, we analysed the untransformed weighted networks with visitation rate that accounts for the intensity of the interaction.
+Although floral visitors are not always pollinators and visitation rate does not consider each pollinator species efficiency (\protect\hyperlink{ref-ballantyne2015}{Ballantyne \emph{et al.} 2015}), visitation rate can provide valuable information of the contribution of floral visitors to pollination (\protect\hyperlink{ref-vazquez2005}{Vázquez \emph{et al.} 2005}, \protect\hyperlink{ref-vazquez2012}{2012}).
 In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
@@
 For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored the presence-absence of interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
 In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total).
@@
 Hence, to control for the effect of \emph{A.
-mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of interaction and visitation rate excluding \emph{A.
+mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and visitation rate excluding \emph{A.
 mellifera}.
@@
 We implemented Bayesian generalized linear mixed models using the R package \emph{brms} (\protect\hyperlink{ref-burkner2017}{Bürkner 2017}).
-We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
-In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
+We modelled presence-absence of observed interactions and visitation rate as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., visitation rate \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
+We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
 Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
-We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
+We specified for presence-absence of interaction and visitation rate a Bernoulli and a zero inflated negative binomial distribution, respectively.
+The models were run with weakly informative priors from the brms function, 3,000 iterations and with previous 1,000 warm up iterations.
 We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package (\protect\hyperlink{ref-gabry2019}{Gabry \emph{et al.} 2019}).
 
-\textbf{Plant species functional roles}
+\textbf{Plant species network roles}
 
-We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
+We investigated whether different quantitative traits determined plant species network roles using Bayesian modelling and regression trees.
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies (\protect\hyperlink{ref-dormann2008}{Dormann \emph{et al.} 2008}) with a straightforward ecological interpretation relevant to our research goals.
@@
 For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns section.'
+Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns' section.
 
-Second, to better understand these complex trait relationships, we used regression trees.
-Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
+Second, to better understand complex trait relationships, we used regression trees.
+Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction.
 We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
 We conducted this analysis using the \emph{rpart} package (\protect\hyperlink{ref-therneau2015}{Therneau \emph{et al.} 2015}) with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package (\protect\hyperlink{ref-milborrow2015}{Milborrow 2015}) to plot the regression trees.
-We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
+We considered the species level indices as response variables (visitation rate, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
 We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
@@
 
-The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the overall visitation rates (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
-However, we found relevant trends across the different floral visitor guilds on both presence-absence and visitation interactions (Fig.
+The main axes of trait variation explained partly presence-absence of interaction partners (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the overall visitation rates (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
+However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and visitation rates (Fig.
 3).
-On the pollinator dependence trade-off, all floral visitor guilds interacted more frequently with plant species with higher pollinator dependence (PC2; Fig.
+We found that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds (flower number - flower size trade-off, PC1; Fig.
+3a).
+However, plant species with high flower number but small flowers had higher visitation rates of bees and syrphids guilds (PC1; Fig.
+3d).
+Remarkably, all plant species with higher pollinator dependence had higher number of interacting partners and visitation rates for all floral visitor guilds (PC2; Fig.
 3b and Fig.
 3e).
-For presence-absence interactions we found that all Diptera, Coleoptera and non-bee-Hymenoptera guilds interacted more frequently with plants with high flower number and small flowers (flower number - flower size trade-off, PC1; Fig.
-3a) but bees and Lepidoptera interacted slightly more frequently with plant species with low flower number but large flowers.
-For presence-absence interactions on PC3 (style length trade-off; Fig.
-3c), we found that bees interacted clearly more with plant species with long styles and high selfing and the rest of the guilds interacted slightly more with plant species with short styles and low selfing.
-In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-syrphid-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig.
-3d).
-On the style length trade-off, bees, Lepidoptera and non-bee-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while syrphids, non-syrphid-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
+Finally, plant species with short styles and low selfing had higher interaction partners of all guilds but bees that interacted clearly more with plant species with long styles and high selfing (style length trade-off; Fig.
+3c).
+However, for visitation rate, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
 3f).
 
-The additional model for both presence-absence of interactions (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and visitation rate (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
+The additional model for both presence-absence of interaction (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and visitation rate (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
+The contrasting differences between presence-absence of interaction and visitation rate for bees on PC1 (Fig.
 3a and Fig.
-3d) were driven by the family Andrenidae, which interacted more frequently on presence-absence interactions with plant species with low number of large flowers (Fig.
+3d) were driven by the family Andrenidae that had higher number of interacting partners but lower visitation rates on plant species with low number of large flowers (Fig.
 S8).
@@
 \includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\textbf{Figure 3} Interaction (yes/no) and visitation rates across the three main axes of trait variation per floral visitor guild.
-Fitted posterior estimates of the presence/absence of interaction (a, b and c) and number of visits (d, e and f) made by the different floral visitors guilds in relation to PC1, PC2 and PC3.
+\caption{\label{fig:unnamed-chunk-4}\textbf{Figure 3} Fitted posterior estimates of the presence-absence of interaction (a, b and c) and visitation rate (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
 PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.
@@
 
-\textbf{Plant species functional roles}
+\textbf{Plant species network roles}
 
 The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
-S9; interaction frequency \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
-Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
-On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
+S9; visitation rate \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
+Overall, the most notable trends were found on PC1 and PC3 for visitation rate and specialization.
+On the flower number - flower size trade-off (PC1), visitation rate was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
 S9a).
@@
 S9g).
-On the style length trade-off (PC3), interaction frequency was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
+On the style length trade-off (PC3), visitation rate was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
 S9c).
-Again, specialization showed the opposite trend to interaction frequency (Fig.
+Again, specialization showed the opposite trend to visitation rate (Fig.
 S9i).
 
-When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for visitation frequency was best explained by plant height, nectar concentration and style length (Fig.
+When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for visitation rate was best explained by plant height, nectar concentration and style length (Fig.
 4a).
-Specifically, species taller than 3.9m had the highest interaction frequency, while species that were shorter than 3.9m and had a nectar concentration lower than 16\% had the lowest interaction frequency.
+Specifically, species taller than 3.9m had the highest visitation rate, while species that were shorter than 3.9m and had a nectar concentration lower than 16\% had the lowest visitation rate.
 Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
@@
 \caption{\label{fig:unnamed-chunk-5}\textbf{Figure 4} Contribution of traits in plant's network roles.
-Regression tree analysis of interaction frequency (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
+Regression tree analysis of visitation rate (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
 The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
@@
 3) suggesting possible niche partitioning (\protect\hyperlink{ref-palmer2003}{Palmer \emph{et al.} 2003}; \protect\hyperlink{ref-phillips2020}{Phillips \emph{et al.} 2020}) between these two guilds.
-However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species functional roles (Fig.
+However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species network roles (Fig.
 4).

### 2022-02-01 Manuscript/MS_word.Rmd
Ecol Letters

@@
 ---
----
----
-title: \singlespacing \vspace{-1.6cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors
 
-#author: 
-#  - Jose B. Lanuza^1,2^*
-#  - Romina Rader^1^
-#  - Jamie Stavert^3^
-#  - Liam K. Kendall^4^
-#  - Manu E. Saunders^1^
-#  - Ignasi Bartomeus^2^
-
-# may use lua filters for affiliations etc: see https://stackoverflow.com/a/52919256
-
-# date: '`r Sys.Date()`'
-
-output:
-  bookdown::pdf_document2:
-    fig_caption: yes
-    fig_width: 7
-    fig_height: 7
-    df_print: kable
-    keep_tex: yes
-    number_sections: no
-    extra_dependencies: ["float"]
-    toc: no
-    fig_crop: no
-    includes:
-      in_header: header.tex
-
-documentclass: article
-# classoption: twocolumn, landscape, etc
-papersize: a4
-pagestyle: plain  # plain, empty, headings
-geometry: margin=1in
-linestretch: 2
-fontfamily: mathpazo
-fontsize: 12pt
-
-bibliography: 
-  - references.bib
-  - knitcitations.bib
-# zotero: "My shared Zotero group"
-csl: ecology.csl #ecology letters
-notes-after-punctuation: false
-link-citations: yes
-linkcolor: RoyalBlue
-urlcolor: RoyalBlue
-links-as-notes: false
-subparagraph: yes
-
-header-includes:
-- \usepackage{booktabs}
-- \usepackage{longtable}
-- \usepackage{array}
-- \usepackage{multirow}
-- \usepackage{wrapfig}
-- \usepackage{float}
-- \usepackage{colortbl}
-- \usepackage{tabu}
-- \usepackage{threeparttable}
-- \usepackage{threeparttablex}
-- \usepackage[normalem]{ulem}
-- \usepackage{makecell}
-- \usepackage{xcolor}
-- \usepackage{float}
-- \floatplacement{figure}{H}
-- \usepackage[skip=3pt]{caption}
-- \captionsetup[figure]{labelformat=empty}
-- \usepackage{setspace}
-- \usepackage{titlesec}
-- \titlespacing{\title}{0pt}{\parskip}{-\parskip}
-- \usepackage[style=nature]{biblatex}
-- \usepackage[labelformat = empty]{caption}
-- \usepackage{pdflscape}
-#- \DeclareUnicodeCharacter{0301}{*************************************}
-
----
+\doublespacing
+\vspace{5mm}
+\normalsize
 
@@
 We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017].
-We modelled the frequency of visits as a function of the main axes of plant trait variation and their interactions with floral visitor functional groups (Visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the floral visitor guilds.
-In this model, we added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
+We modelled presence-absence of observed interactions and visitation rate as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., visitation rate ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
+We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
 Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified this model with a zero inflated negative binomial distribution and weakly informative priors from the brms function.
-We run this model for 3,000 iterations and with previous 1,000 warm up iterations.
+We specified for presence-absence of interaction and visitation rate a Bernoulli and a zero inflated negative binomial distribution, respectively.
+The models were run with weakly informative priors from the brms function, 3,000 iterations and with previous 1,000 warm up iterations.
 We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019].
 
-**Plant species functional roles**
+**Plant species network roles**
 
-We investigated whether different quantitative traits determined plant species functional roles using Bayesian modelling and regression trees.
+We investigated whether different quantitative traits determined plant species network roles using Bayesian modelling and regression trees.
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
@@
 For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns section’.
+Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns’ section.
 
-Second, to better understand these complex trait relationships, we used regression trees.
-Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles.
+Second, to better understand complex trait relationships, we used regression trees.
+Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction.
 We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
 We conducted this analysis using the _rpart_ package [@therneau2015] with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] to plot the regression trees.
-We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
+We considered the species level indices as response variables (visitation rate, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
 We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
@@
 
-The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall visitation rates (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant trends across the different floral visitor guilds on both presence-absence and visitation interactions (Fig.
+The main axes of trait variation explained partly presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall visitation rates (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
+However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and visitation rates (Fig.
 3).
-On the pollinator dependence trade-off, all floral visitor guilds interacted more frequently with plant species with higher pollinator dependence (PC2; Fig.
+We found that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds (flower number - flower size trade-off, PC1; Fig.
+3a).
+However, plant species with high flower number but small flowers had higher visitation rates of bees and syrphids guilds (PC1; Fig.
+3d).
+Remarkably, all plant species with higher pollinator dependence had higher number of interacting partners and visitation rates for all floral visitor guilds (PC2; Fig.
 3b and Fig.
 3e).
-For presence-absence interactions we found that all Diptera, Coleoptera and non-bee-Hymenoptera guilds interacted more frequently with plants with high flower number and small flowers (flower number - flower size trade-off, PC1; Fig.
-3a) but bees and Lepidoptera interacted slightly more frequently with plant species with low flower number but large flowers.
-For presence-absence interactions on PC3 (style length trade-off; Fig.
-3c), we found that bees interacted clearly more with plant species with long styles and high selfing and the rest of the guilds interacted slightly more with plant species with short styles and low selfing.
-In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-syrphid-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig.
-3d).
-On the style length trade-off, bees, Lepidoptera and non-bee-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while syrphids, non-syrphid-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig.
+Finally, plant species with short styles and low selfing had higher interaction partners of all guilds but bees that interacted clearly more with plant species with long styles and high selfing (style length trade-off; Fig.
+3c).
+However, for visitation rate, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
 3f).
 
-The additional model for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and visitation rate (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig.
+The additional model for both presence-absence of interaction (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and visitation rate (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
+The contrasting differences between presence-absence of interaction and visitation rate for bees on PC1 (Fig.
 3a and Fig.
-3d) were driven by the family Andrenidae, which interacted more frequently on presence-absence interactions with plant species with low number of large flowers (Fig.
+3d) were driven by the family Andrenidae that had higher number of interacting partners but lower visitation rates on plant species with low number of large flowers (Fig.
 S8).
 
-**Plant species functional roles**
+**Plant species network roles**
 
 The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
-S9; interaction frequency ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on PC1 and PC3 for interaction frequency and specialization.
-On the flower number - flower size trade-off (PC1), interaction frequency was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
+S9; visitation rate ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
+Overall, the most notable trends were found on PC1 and PC3 for visitation rate and specialization.
+On the flower number - flower size trade-off (PC1), visitation rate was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
 S9a).

### 2022-02-01 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
Ecol Letters

--- 2022-01-27 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
@@
 In addition, quantitative data was also divided into these four categories with the following criteria: from 0% to lower than 1% ‘none’, from 1% to 25% ‘low’, from 26% to 75% ‘medium’ and from 76% to 100%  ‘high’.
+Because quantitative selfing had a high percentage of missing values (68%), we were able to solve this by converting these four categories to representative percentages of each category 0%, 13%, 50.5% and 88%.
+This reduced the percentage of missing values for this quantitative trait from 68% to 35% and allowed the imputation of this variable.
 
@@
 In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration.
-In general terms, nectar data was rarely present and we tried to minimise the loss of information by filling some species at family level.
-For instance, Solanaceae species are described as nectarless, and species that belonged to this family were recorded with ‘absence’ of nectar.
+For species that did not have nectar information but belonged to a family that is considered as ‘nectarless’, this trait was recorded at family level and the species was recorded with ‘absence’ of nectar.
+This was done exclusively for well documented nectarless taxonomical groups.
 
@@
 
+\pagebreak
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
@@
 
+d <- readRDS("Data/RData/table_categorical_tukey_test.rds")
+
+#Again im getting the same error on this rmd so I run it on another one, save the dataframe and plot it here
+
+#Plot table
+#Add latex format in markdown
+
+kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Table S2.
+Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species.}") %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
+
+```
+
+\pagebreak
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
+
+library(dplyr)
+library(kableExtra)
+
+setwd("~/R_Projects/Reproductive Traits")
+
 PC <- readRDS("Data/RData/phyl_pca_forest.rds")
@@
 
- kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S2.
+ kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S3.
 Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species.}") %>%
@@
 
-kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S3.
+kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S4.
 Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-d <- readRDS("Data/RData/table_categorical_tukey_test.rds")
-
-#Again im getting the same error on this rmd so I run it on another one, save the dataframe and plot it here
-
-#Plot table
-#Add latex format in markdown
-
-kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Table S4.
-Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species.}") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")

### 2022-04-15 Manuscript/Lanuza_et_al_2021_Ecol_Letters.Rmd
edits
Working on 1st paragraph

@@
 
-Despite the astonishing diversity of floral structures among flowering plants [@barrett2002; @schiestl2013] and their importance in shaping plant-pollinator interactions [@fenster2004; @dellinger2020], a unified framework that describes the major plant reproductive trade-offs is currently lacking [@roddy2021].
-In addition, macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with pollinators at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
+Flowering plants have an astonishing diversity of floral structures [@barrett2002; @schiestl2013] that shape plant-pollinator associations [@fenster2004; @dellinger2020].
+However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [REF].
+Despite the recent advances in the theoretical understanding of the major floral trade-offs (e.g., floral economic spectrum; REF), we lack empirical evidence that helps to elucidate the spectrum of reproductive trait variation at a global scale as done recently for other vegetative and physiological traits [REF].
+
+Macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with pollinators at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
 Linking the plant's position in trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
@@
 Second, we investigate how plant species’ position in trait-space influence interactions with floral visitors.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species’ roles within networks using a set of complementary interaction network metrics (i.e., visitation rate, normalized degree and specialization).
+Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species’ roles within networks using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
 
@@
 Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives [e.g., The Web of Life, @fortuna2010; and Mangal, @poisot2016].
-In total, our network dataset (Table S1) constituted 60 weighted (visitation rate) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+In total, our network dataset (Table S1) constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
 
@@
 We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package _rtrees_ (https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
+
+**Data Imputation**
+
+Trait missing values were imputed with the function _missForest_ [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of _missForest_ [@penone2014].
+To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
+We conducted two different imputations, one for the full set of species (1,506 species, 5.79% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
+S1) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01% of missing values).
+
+**Plant strategies**
+
+We explored the trade-offs between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
+Prior to the analyses, we excluded outliers and standardized the data.
+Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th–97.5th percentile range [@legendre2012], and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
+We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
+Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
+S2).
+We found little difference between the explained variance with the imputed dataset (51.08%) and the dataset without missing values (52.87%).
+In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
+Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
+For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
+
+**Phylogenetic signal**
+
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
+However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
+
+**Network analyses**
+
+Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+These networks were analysed in their qualitative and quantitative form.
+First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
+Second, we analysed the untransformed weighted networks with the number of visits of floral visitors to individual flowers that account for the intensity of the interaction.
+Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency [@ballantyne2015], the number of visits can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
+In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
+Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
+All analyses were conducted in R version _4.0.3_.
+
+**Visitation patterns**
+
+We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species.
+For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
+Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
+This finding is consistent with previous research showing that _A.
+mellifera_ was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
+Hence, to control for the effect of _A.
+mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding _A.
+mellifera_.
+We found that _A.
+mellifera_, was partly driving some of the observed trends on PC1 (Fig.
+S3).
+However, we did not detect major differences on PC2 and PC3.
+
+We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017].
+We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
+We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
+Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
+We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
+The models were run with weakly informative priors from the brms function, 3,000 iterations and with previous 1,000 warm up iterations.
+We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019].
+
+**Plant species network roles**
+
+We investigated whether different quantitative traits determined plant species network roles using Bayesian modelling and regression trees.
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d’) [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008].
+
+First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric ~ PC1 + PC2 + PC3).
+For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
+Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns’ section.
+
+Second, to better understand complex trait relationships, we used regression trees.
+Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction.
+We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
+We conducted this analysis using the _rpart_ package [@therneau2015] with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] to plot the regression trees.
+We considered the species level indices as response variables (number of visits, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
+We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
+We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (Fig.
+S4).
+
+# RESULTS
+
+**Plant strategies**
+
+The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Fig.
+1 and Fig.
+S5) and had a phylogenetic correlation ($\lambda$) of 0.76.
+The first principal component (PC1) represented 26.72% of the trait variation and indicated a trade-off between flower number and flower size.
+We refer to this axis as the ‘flower number - flower size trade-off’, as already described in previous studies [@sargent2007; @kettle2011].
+Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
+The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
+The second principal component (PC2) represented 25.05% of the trait variation and indicated a trade-off between low and high pollinator dependence.
+We refer to this axis as the ‘pollinator dependence trade-off’.
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
+We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
+In contrast, species with high levels of autonomous selfing tended to have fewer and smaller flowers, had shorter styles and were shorter in height.
+Further, PC3 explained a considerable amount of trait variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
+The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
+Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the ‘style length trade-off’.
+Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82%; Fig.
+S6).
+This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (Table S4).
+
+We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
+2 and Table S2).
+Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, _P_ < 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , _P_ = 0.59; PC2:  Sum of squares = 0.83, F-value = 1.43, _P_ = 0.23) showed lack of statistical association.
+In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
+S7).
+Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Fig.
+S7a and Fig.
+S7b).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
+S7c and Fig.
+S7d).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
+S7e and Fig.
+S7f).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
+S7g and Fig.
+S7h).
+Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Fig.
+S7i and Fig.
+S7j).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Fig.
+S7k and Fig.
+S7l).
+
+**Phylogenetic signal**
+
+We found a strong phylogenetic signal (*P* < 0.01) in all quantitative traits (Table S5).
+The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
+The traits that showed a moderate phylogenetic signal were inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
+Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits ($\lambda$ = 0.14).
+
+**Visitation patterns**
+
+The main axes of trait variation explained partly presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
+However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (Fig.
+3).
+We found that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds (flower number - flower size trade-off, PC1; Fig.
+3a).
+However, plant species with high flower number but small flowers had higher number of visits of bees and syrphids guilds (PC1; Fig.
+3d).
+Remarkably, all plant species with higher pollinator dependence had higher number of interacting partners and number of visits for all floral visitor guilds (PC2; Fig.
+3b and Fig.
+3e).
+Finally, plant species with short styles and low selfing had higher interaction partners of all guilds but bees that interacted clearly more with plant species with long styles and high selfing (style length trade-off; Fig.
+3c).
+However, for number of visits, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
+3f).
+
+The additional model for both presence-absence of interaction (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
+The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (Fig.
+3a and Fig.
+3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (Fig.
+S8).
+
+**Plant species network roles**
+
+The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
+S9; number of visits ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
+Overall, the most notable trends were found on PC1 and PC3 for number of visits and specialization.
+On the flower number - flower size trade-off (PC1), number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
+S9a).
+On PC1, specialization showed the opposite trend (Fig.
+S9g).
+On the style length trade-off (PC3), number of visits was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
+S9c).
+Again, specialization showed the opposite trend to number of visits (Fig.
+S9i).
+
+When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for number of visits was best explained by plant height, nectar concentration and style length (Fig.
+4a).
+Specifically, species taller than 3.9m had the highest number of visits, while species that were shorter than 3.9m and had a nectar concentration lower than 16% had the lowest number of visits.
+Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
+4b).
+Species with a nectar concentration over 49% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49%, more than 21,000 pollen grains per flower and height less than 0.78m had the lowest normalized degree.
+Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
+4c).
+Overall, plant species with the highest specialization were shorter than 1.3m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11% of their fruits.
+In contrast, species taller or equal than 5.1m and with lower than 14 ovules per flower had the lowest specialization values.
+
+# DISCUSSION
+
+This study demonstrates that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
+These trade-offs are differentiated along three axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
+These reproductive trade-offs helped partly explain the presence of floral visitor interactions, but not their number of visits.
+However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
+Moreover, we found that the plant species network roles were best explained by plant size and floral reward related traits.
+
+Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
+Trait variation on these two axes was associated with the ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+The ‘slow’ part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
+In contrast, plant species that employed the ‘fast’ strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
+Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
+The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
+S10).
+
+Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (number of interaction partners and number of visits), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies influence plant-pollinator interactions.
+For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
+1 and Fig.
+S6).
+This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently [@hegland2005; @lazaro2013; @kaiser2014].
+In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation patterns across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
+For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
+3) suggesting possible niche partitioning [@palmer2003; @phillips2020] between these two guilds.
+However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species network roles (Fig.
+4).
+More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive trade-offs do not.
+
+To conclude, we provide a robust description of plant reproductive trade-offs using a large global dataset of plant traits.
+We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
+Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits [@diaz2016; @carmona2021] it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits [@salguero2016].
+Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
+Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators [@gervasi2017; @mackin2021].
+Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
+
+# References
+
+<div id ="refs"></div>
+
+# Acknowledgements
+
+This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
+We thank all researchers that made their data openly available and sent it upon request.
+We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
+We also thank Jason Tylianakis for his comments on the manuscript before submission.
+Finally, JBL thanks the University of New England for the funding provided to carry out this work.
 
@@
 
-**Data Imputation**
-
-Trait missing values were imputed with the function _missForest_ [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of _missForest_ [@penone2014].
-To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-We conducted two different imputations, one for the full set of species (1,506 species, 5.79% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
-S1) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01% of missing values).
-
-**Plant strategies**
-
-We explored the trade-offs between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th–97.5th percentile range [@legendre2012], and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
-S2).
-We found little difference between the explained variance with the imputed dataset (51.08%) and the dataset without missing values (52.87%).
-In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
-For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
-
-**Phylogenetic signal**
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-**Network analyses**
-
-Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-These networks were analysed in their qualitative and quantitative form.
-First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
-Second, we analysed the untransformed weighted networks with visitation rate that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and visitation rate does not consider each pollinator species efficiency [@ballantyne2015], visitation rate can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
-All analyses were conducted in R version _4.0.3_.
-
-**Visitation patterns**
-
-We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
-This finding is consistent with previous research showing that _A.
-mellifera_ was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
-Hence, to control for the effect of _A.
-mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and visitation rate excluding _A.
-mellifera_.
-We found that _A.
-mellifera_, was partly driving some of the observed trends on PC1 (Fig.
-S3).
-However, we did not detect major differences on PC2 and PC3.
-
-We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017].
-We modelled presence-absence of observed interactions and visitation rate as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., visitation rate ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
-We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified for presence-absence of interaction and visitation rate a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with weakly informative priors from the brms function, 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019].
-
-**Plant species network roles**
-
-We investigated whether different quantitative traits determined plant species network roles using Bayesian modelling and regression trees.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d’) [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008].
-
-First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric ~ PC1 + PC2 + PC3).
-For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns’ section.
-
-Second, to better understand complex trait relationships, we used regression trees.
-Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction.
-We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
-We conducted this analysis using the _rpart_ package [@therneau2015] with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] to plot the regression trees.
-We considered the species level indices as response variables (visitation rate, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
-We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (Fig.
-S4).
-
-# RESULTS
-
-**Plant strategies**
-
-The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Fig.
-1 and Fig.
-S5) and had a phylogenetic correlation ($\lambda$) of 0.76.
-The first principal component (PC1) represented 26.72% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the ‘flower number - flower size trade-off’, as already described in previous studies [@sargent2007; @kettle2011].
-Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
-The second principal component (PC2) represented 25.05% of the trait variation and indicated a trade-off between low and high pollinator dependence.
-We refer to this axis as the ‘pollinator dependence trade-off’.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
-We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
-In contrast, species with high levels of autonomous selfing tended to have fewer and smaller flowers, had shorter styles and were shorter in height.
-Further, PC3 explained a considerable amount of trait variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
-The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
-Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the ‘style length trade-off’.
-Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82%; Fig.
-S6).
-This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (Table S4).
-
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
@@
 ```
-
-We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
-2 and Table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, _P_ < 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , _P_ = 0.59; PC2:  Sum of squares = 0.83, F-value = 1.43, _P_ = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
-S7).
-Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Fig.
-S7a and Fig.
-S7b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
-S7c and Fig.
-S7d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
-S7e and Fig.
-S7f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
-S7g and Fig.
-S7h).
-Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Fig.
-S7i and Fig.
-S7j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Fig.
-S7k and Fig.
-S7l).
 
@@
 \vspace{5mm}
-
-**Phylogenetic signal**
-
-We found a strong phylogenetic signal (*P* < 0.01) in all quantitative traits (Table S5).
-The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
-The traits that showed a moderate phylogenetic signal were inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits ($\lambda$ = 0.14).
-
-**Visitation patterns**
-
-The main axes of trait variation explained partly presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall visitation rates (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and visitation rates (Fig.
-3).
-We found that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds (flower number - flower size trade-off, PC1; Fig.
-3a).
-However, plant species with high flower number but small flowers had higher visitation rates of bees and syrphids guilds (PC1; Fig.
-3d).
-Remarkably, all plant species with higher pollinator dependence had higher number of interacting partners and visitation rates for all floral visitor guilds (PC2; Fig.
-3b and Fig.
-3e).
-Finally, plant species with short styles and low selfing had higher interaction partners of all guilds but bees that interacted clearly more with plant species with long styles and high selfing (style length trade-off; Fig.
-3c).
-However, for visitation rate, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
-3f).
-
-The additional model for both presence-absence of interaction (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and visitation rate (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence of interaction and visitation rate for bees on PC1 (Fig.
-3a and Fig.
-3d) were driven by the family Andrenidae that had higher number of interacting partners but lower visitation rates on plant species with low number of large flowers (Fig.
-S8).
-
 \blandscape
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and visitation rate (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
 PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.
-For visualization purposes, due to large differences between the visitation rates of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
+For visualization purposes, due to large differences between number of visits of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
 
@@
 
-**Plant species network roles**
-
-The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
-S9; visitation rate ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on PC1 and PC3 for visitation rate and specialization.
-On the flower number - flower size trade-off (PC1), visitation rate was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
-S9a).
-On PC1, specialization showed the opposite trend (Fig.
-S9g).
-On the style length trade-off (PC3), visitation rate was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
-S9c).
-Again, specialization showed the opposite trend to visitation rate (Fig.
-S9i).
-
-When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for visitation rate was best explained by plant height, nectar concentration and style length (Fig.
-4a).
-Specifically, species taller than 3.9m had the highest visitation rate, while species that were shorter than 3.9m and had a nectar concentration lower than 16% had the lowest visitation rate.
-Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
-4b).
-Species with a nectar concentration over 49% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49%, more than 21,000 pollen grains per flower and height less than 0.78m had the lowest normalized degree.
-Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
-4c).
-Overall, plant species with the highest specialization were shorter than 1.3m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11% of their fruits.
-In contrast, species taller or equal than 5.1m and with lower than 14 ovules per flower had the lowest specialization values.
-
 \blandscape
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=12,fig.cap= "**Figure 4** Contribution of traits in plant's network roles.
-Regression tree analysis of visitation rate (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
+Regression tree analysis of number of visits (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
 The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
@@
 
-rpart.plot(tree1, box.palette="GnOr", main="(a) Visitation rate", cex.main=1.75,tweak = 1.25,type = 2) 
+rpart.plot(tree1, box.palette="GnOr", main="(a) Number of visits", cex.main=1.75,tweak = 1.25,type = 2) 
 rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.75,tweak = 1.25,type = 2)
@@
 \elandscape
-
-# DISCUSSION
-
-This study demonstrates that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
-These trade-offs are differentiated along three axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-These reproductive trade-offs helped partly explain the presence of floral visitor interactions, but not their visitation rates.
-However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
-Moreover, we found that the plant species network roles were best explained by plant size and floral reward related traits.
-
-Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
-Trait variation on these two axes was associated with the ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-The ‘slow’ part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, plant species that employed the ‘fast’ strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
-The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
-S10).
-
-Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (number of interaction partners and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies influence plant-pollinator interactions.
-For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
-1 and Fig.
-S6).
-This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently [@hegland2005; @lazaro2013; @kaiser2014].
-In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation rates across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
-For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
-3) suggesting possible niche partitioning [@palmer2003; @phillips2020] between these two guilds.
-However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species network roles (Fig.
-4).
-More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive trade-offs do not.
-
-To conclude, we provide a robust description of plant reproductive trade-offs using a large global dataset of plant traits.
-We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
-Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits [@diaz2016; @carmona2021] it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits [@salguero2016].
-Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
-Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators [@gervasi2017; @mackin2021].
-Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
-
-# References
-
-<div id ="refs"></div>
-
-# Acknowledgements
-
-This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-We thank all researchers that made their data openly available and sent it upon request.
-We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
-We also thank Jason Tylianakis for his comments on the manuscript before submission.
-Finally, JBL thanks the University of New England for the funding provided to carry out this work.

### 2022-04-15 Manuscript/Lanuza_et_al_2021_Ecol_Letters.Rmd
Edits on ms

@@
 
-Macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with pollinators at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
-Linking the plant's position in trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
+Although there is an increasing number of macroecological studies that investigate plant reproductive traits [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017], we still have poor understanding of how reproductive traits drive interactions with pollinators at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
+Because the species' morphology can determine the species' functional role, by linking the plant's position in the reproductive trait-space with the different pollinator groups (as done similarly in @dehling2016), we could help to improve our understanding of plant-pollinator associations.
 Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
-However, plant reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020] and remains unclear how specific plant reproductive biology traits (e.g., mating or compatibility system) influence plant-pollinator associations [@tur2013; @devaux2014].
+However, plant reproductive traits have been overlooked for most pollination systems [@dellinger2020] and remains unclear how specific plant reproductive biology traits (e.g., mating or compatibility system) influence plant-pollinator associations [@tur2013; @devaux2014].
 

### 2022-04-18 Manuscript/Lanuza_et_al_2021_Ecol_Letters.Rmd
edits

@@
 However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [REF].
-Despite the recent advances in the theoretical understanding of the major floral trade-offs (e.g., floral economic spectrum; REF), we lack empirical evidence that helps to elucidate the spectrum of reproductive trait variation at a global scale as done recently for other vegetative and physiological traits [REF].
+Despite the recent advances in the theoretical understanding of the major floral trade-offs [e.g., floral economic spectrum; @roddy2021], we lack empirical evidence that helps to elucidate the spectrum of reproductive trait variation at a global scale as done recently for other vegetative and physiological traits [REF].
 
 Although there is an increasing number of macroecological studies that investigate plant reproductive traits [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017], we still have poor understanding of how reproductive traits drive interactions with pollinators at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
-Because the species' morphology can determine the species' functional role, by linking the plant's position in the reproductive trait-space with the different pollinator groups (as done similarly in @dehling2016), we could help to improve our understanding of plant-pollinator associations.
+Because the species' morphology can determine the species' functional role, by linking the plant's position in the reproductive trait-space with the different pollinator groups [as done similarly in @dehling2016], we could help to improve our understanding of plant-pollinator associations.
 Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
@@
 In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators [@ollerton2011; @rodger2021].
-However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.
+However, it is still unknown to what extent these different reproductive strategies determine plant-pollinator interactions.
 
@@
 
-Here, we aim to explore the potential trade-offs among reproductive traits and how these influence plant-pollinator interactions.
+Here, we aim to explore the potential trade-offs among plant reproductive traits and their association with the different floral visitor guilds.
 First, we identify the major axes of reproductive trait variation and trade-offs that determine plant form and function.
-Second, we investigate how plant species’ position in trait-space influence interactions with floral visitors.
+Second, we investigate the association between the plant species’ position in trait-space and the different floral visitor guilds with the help of qualitative (presence-absence of interaction) and quantitative (number of visits) information.
 Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species’ roles within networks using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
@@
 
-We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
+We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see Table S1 and Fig.
+S1).
 These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
@@
 Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives [e.g., The Web of Life, @fortuna2010; and Mangal, @poisot2016].
-In total, our network dataset (Table S1) constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
 
@@
 From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Fig.
-S1 for missing values information for each trait).
+S2 for missing values information for each trait).
 
@@
 We conducted two different imputations, one for the full set of species (1,506 species, 5.79% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
-S1) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01% of missing values).
+S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01% of missing values).
 
@@
 Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
-S2).
+S3).
 We found little difference between the explained variance with the imputed dataset (51.08%) and the dataset without missing values (52.87%).
@@
 mellifera_, was partly driving some of the observed trends on PC1 (Fig.
-S3).
+S4).
 However, we did not detect major differences on PC2 and PC3.
@@
 We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with weakly informative priors from the brms function, 3,000 iterations and with previous 1,000 warm up iterations.
+The models were run with non or very weakly informative informative priors from the brm function so they have neglible influence on the results [@burkner2017], 3,000 iterations and with previous 1,000 warm up iterations.
 We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019].
@@
 We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (Fig.
-S4).
+S5).
 
@@
 1 and Fig.
-S5) and had a phylogenetic correlation ($\lambda$) of 0.76.
+S6) and had a phylogenetic correlation ($\lambda$) of 0.76.
 The first principal component (PC1) represented 26.72% of the trait variation and indicated a trade-off between flower number and flower size.
@@
 Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82%; Fig.
-S6).
+S7).
 This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (Table S4).
@@
 In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
-S7).
+S8).
 Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Fig.
-S7a and Fig.
-S7b).
+S8a and Fig.
+S8b).
 Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
-S7c and Fig.
-S7d).
+S8c and Fig.
+S8d).
 Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
-S7e and Fig.
-S7f).
+S8e and Fig.
+S8f).
 Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
-S7g and Fig.
-S7h).
+S8g and Fig.
+S8h).
 Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
 The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Fig.
-S7i and Fig.
-S7j).
+S8i and Fig.
+S8j).
 Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Fig.
-S7k and Fig.
-S7l).
+S8k and Fig.
+S8l).
 
@@
 3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (Fig.
-S8).
+S9).
 
@@
 The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
-S9; number of visits ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
+S10; number of visits ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
 Overall, the most notable trends were found on PC1 and PC3 for number of visits and specialization.
 On the flower number - flower size trade-off (PC1), number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
-S9a).
+S10a).
 On PC1, specialization showed the opposite trend (Fig.
-S9g).
+S10g).
 On the style length trade-off (PC3), number of visits was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
-S9c).
+S10c).
 Again, specialization showed the opposite trend to number of visits (Fig.
-S9i).
+S10i).
 
@@
 The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
-S10).
+S11).
 

### 2022-04-18 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
edits

@@
 When possible, we calculated the not found measurements with the help of online images and  the software ImageJ.
+Note that for species with compound flowers (e.g., Asteraceae) or similar floral structures we considered the actual inflorescence as the floral unit and the inflorescence or group of inflorescences as the inflorescence.
+For each species this is indicated in the dataset with the field of "info_level".
+For analysis just flower and capitulum level were considered but for some Asteraceae species information about ray and disc florets were also annotated.
 
@@
 This was done exclusively for well documented nectarless taxonomical groups.
+For analysis, we considered exclusively microlitres of nectar measured in a given moment of time which was generally associated with the peak of nectar production.
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Fig. S1.} Percentage of present and missing values of the different plant traits."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.cap="\\textbf{Fig.
+S1.} Map with the different locations of the plant-pollinator studies used in this work to explore woldwide patterns at the meso-scale level.
+For each study just one location is shown except for the study of Olesen that was conducted in two very different locations (Mauritius and Azores)."}
+
+#Create coordinate dataset for plotting
+
+longitude <- c("3.296797",  #1
+               "1.575532", #2
+               "9.275556", 
+               "18.5", #4
+               "99.63806", #5
+               "148.266667",
+               "-52", 
+               "-31", "57.43", #8
+               "-75.5", #9
+               "-57.885", #10
+               "55.447778",
+               "-6.16895", #12bart
+               "55.43333", #13
+               "57.733333",
+               "-68.015892", #15
+               "-89.8968771",
+               "171.756111",
+               "10.233333",
+               "-90.35",
+               "-93.8968771",#Robertson
+               "-67.4292900",
+               "-61.71666666666667",
+               "175.756111",
+               "-71.3",
+               "129.387359", #Kevan
+               "135.75385",
+               "-93.35",
+               "10.219072")
+
+latitude <- c("42.315336", #1
+              "52.762395", #2
+              "56.0725",
+              "68.35", #4
+              "27.90139", #5
+              "-36.45", #6
+              "71", #7
+              "39.4", "-23.25", #8 #modified for visibility of ovelapping
+              "45.4", #9
+              "-21.701111", #10
+              "-7.67",#11 #modified for visibility of ovelapping
+              "37.234966", #12bart
+              "-4.666667", #13
+              "-20.4538",
+              "-32.008985", #15
+              "39.278958",
+              "-43.035889",
+              "59.066667",#18 #modified for visibility of ovelapping
+              "-0.533333",
+              "39.278958", #Robertson 
+              "8.9241600",
+              "5.5833333",
+              "-43.035889",
+              "81.8166667",
+              "28.288661", #Kevan 
+              "35.02107",
+              "-0.533333",
+              "56.069108")
+
+id <- c("Bartomeus1", #1
+        "Dicks", #2
+        "Dupont", 
+        "Elberling", #4
+        "Fang", #5
+        "Inouye1", #6
+        "Lundgren", #7
+        "Olesen", "Olesen", #8
+        "Small", #9
+        "Souza", #10
+        "Kaiser-Bunbury1", #
+        "Bartomeus2", #12
+        "Kaiser-Bunbury2", #13
+        "Kaiser-Bunbury3", #14
+        "Peralta", #15
+        "Burkle",
+        "Arroyo-Correa",
+        "Bundgaard",
+        "Traveset",
+        "Robertson",
+        "Ramirez1",
+        "Ramirez2",
+        "Primack",
+        "Kevan",
+        "Kato",
+        "Inouye2",
+        "McMullen",
+        "Baek")
+
+d <- data.frame(longitude, latitude, id)
+
+library("ggplot2")
+library("sf")
+library("rnaturalearth")
+library("rnaturalearthdata")
+
+world <- ne_countries(scale = "medium", returnclass = "sf")
+class(world)
+
+d$longitude <- as.numeric(d$longitude)
+d$latitude <- as.numeric(d$latitude)
+
+sf::sf_use_s2(FALSE)
+
+#these colors come from the library(pals)- labs = c('alphabet')
+
+colors <- c("red4", "#0075DC", "#4C005C", "#4C005C", "#993F00",  "#5EF1F2", 
+        "#005C31", "#2BCE48", "black", "lightblue", "darkorange3", "darkorange3","#8F7C00",
+        "#8F7C00","#8F7C00", "#9DCC00", "#C20088", "gold1","#FFA8BB","#426600","94FFB5","#003380",  
+         "#FF0010","#FF0010", "salmon", "seashell3","greenyellow","mediumaquamarine")
+
+set.seed(12)
+ggplot(data = world) +
+  geom_sf(fill="antiquewhite", color="grey49") +
+  xlab("Longitude") + ylab("Latitude") +
+  geom_point(data=d , aes(longitude,latitude,  color=id),  shape=10,
+           size = 3.5, stroke=1)+ 
+  theme(panel.grid.major = element_line(color = gray(.5), 
+linetype = "dashed", size = 0), panel.background = element_rect(fill = "aliceblue"))+
+  coord_sf(expand = FALSE) +  scale_y_continuous(breaks = c(-50,0, 50)) +
+  scale_x_continuous(breaks = c(-100,0, 100)) +
+  theme(legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=6),
+         legend.title = element_text(size=12))+
+  scale_colour_discrete(name = "Study \n locations") +   scale_colour_manual(
+    values = colors)
+
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Fig. S2.} Percentage of present and missing values of the different plant traits."}
 
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig.
-S2.}  Phylogenetic informed principal component analysis for the species that did not have missing values."}
+S3.}  Phylogenetic informed principal component analysis for the species that did not have missing values."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24,  fig.cap="\\textbf{Fig.
-S3.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation.
+S4.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation.
 The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates."}
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig.
-S4.} Regression tree analyses.
+S5.} Regression tree analyses.
 Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig.
-S5.} PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species."}
+S6.} PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig.
-S6.} Phylogenetic informed principal component analysis for the subset of species with floral rewards."}
+S7.} Phylogenetic informed principal component analysis for the subset of species with floral rewards."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig.
-S7.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species.
+S8.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species.
 Categories that differ significantly are denoted with a different letter."}
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Fig.
-S8.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation.
+S9.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation.
 Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S9.} Plant species level metrics across the three main axes of trait variation.", fig.pos= "h"}
-
-library(brms) #modelling
+S10.} Plant species level metrics across the three main axes of trait variation.", fig.pos= "h"}
+
+#library(brms) #modelling
 library(cowplot) #panel of plots
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S10.} Pearson correlation between the product of flower number-flower size and autonomous selfing level.", fig.pos= "h"}
+S11.} Pearson correlation between the product of flower number-flower size and autonomous selfing level.", fig.pos= "h"}
 

### 2022-04-22 Manuscript/Lanuza_et_al_2021.Rmd
edits

--- 2022-04-18 Manuscript/Lanuza_et_al_2021_Ecol_Letters.Rmd
@@
 - \usepackage{pdflscape}
-#- \DeclareUnicodeCharacter{0301}{*************************************}
+- \usepackage[T1]{fontenc}
+- \DeclareUnicodeCharacter{0301}{*************************************}
+- \DeclareUnicodeCharacter{1EF3}{*************************************}
 
@@
 Flowering plants have an astonishing diversity of floral structures [@barrett2002; @schiestl2013] that shape plant-pollinator associations [@fenster2004; @dellinger2020].
-However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [REF].
-Despite the recent advances in the theoretical understanding of the major floral trade-offs [e.g., floral economic spectrum; @roddy2021], we lack empirical evidence that helps to elucidate the spectrum of reproductive trait variation at a global scale as done recently for other vegetative and physiological traits [REF].
+However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [@salguero2016].
+Despite the recent advances in the theoretical understanding of the major floral trade-offs [e.g., floral economic spectrum; @roddy2021], we lack empirical evidence that helps to elucidate the spectrum of reproductive trait variation at a global scale as done recently for other vegetative and physiological traits [@diaz2016; @onoda2017].
 
@@
 Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
-However, plant reproductive traits have been overlooked for most pollination systems [@dellinger2020] and remains unclear how specific plant reproductive biology traits (e.g., mating or compatibility system) influence plant-pollinator associations [@tur2013; @devaux2014].
+However, plant reproductive traits have been overlooked for most pollination systems [@dellinger2020] and remains unclear how specific plant reproductive biology traits (i.e., mating or compatibility system) influence plant-pollinator associations [@tur2013; @devaux2014].
 
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives [e.g., The Web of Life, @fortuna2010; and Mangal, @poisot2016].
+Many of these networks are freely available either as published studies [e.g.,\ @carvalheiro2014; @olesen2007; @fortuna2010] or available in online archives [e.g., The Web of Life, @fortuna2010; and Mangal, @poisot2016].
 In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
@@
 We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
-We conducted this analysis using the _rpart_ package [@therneau2015] with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] to plot the regression trees.
+We conducted this analysis using the _rpart_ function from the _rtrees_ package [@therneau2015] with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] to plot the regression trees.
 We considered the species level indices as response variables (number of visits, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
@@
 When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for number of visits was best explained by plant height, nectar concentration and style length (Fig.
-4a).
+4a; root node error = 1%).
 Specifically, species taller than 3.9m had the highest number of visits, while species that were shorter than 3.9m and had a nectar concentration lower than 16% had the lowest number of visits.
 Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
-4b).
+4b; root node error = 2%).
 Species with a nectar concentration over 49% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49%, more than 21,000 pollen grains per flower and height less than 0.78m had the lowest normalized degree.
 Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
-4c).
+4c; root node error = 7%).
 Overall, plant species with the highest specialization were shorter than 1.3m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11% of their fruits.

### 2022-04-22 Manuscript/Lanuza_et_al_2021.tex
edits

--- 2022-02-01 Manuscript/Lanuza_et_al_2021_Ecol_Letters.tex
@@
 \usepackage{pdflscape}
+\usepackage[T1]{fontenc}
+\DeclareUnicodeCharacter{0301}{*************************************}
+\DeclareUnicodeCharacter{1EF3}{*************************************}
 \usepackage{float}
@@
 
-Despite the astonishing diversity of floral structures among flowering plants (\protect\hyperlink{ref-barrett2002}{Barrett 2002}; \protect\hyperlink{ref-schiestl2013}{Schiestl \& Johnson 2013}) and their importance in shaping plant-pollinator interactions (\protect\hyperlink{ref-fenster2004}{Fenster \emph{et al.} 2004}; \protect\hyperlink{ref-dellinger2020}{Dellinger 2020}), a unified framework that describes the major plant reproductive trade-offs is currently lacking (\protect\hyperlink{ref-roddy2021}{Roddy \emph{et al.} 2021}).
-In addition, macroecological studies that investigate plant reproductive traits are scarce (\protect\hyperlink{ref-baude2016}{Baude \emph{et al.} 2016}; \protect\hyperlink{ref-munoz2016}{Munoz \emph{et al.} 2016}; \protect\hyperlink{ref-grossenbacher2017}{Grossenbacher \emph{et al.} 2017}; \protect\hyperlink{ref-moeller2017}{Moeller \emph{et al.} 2017}) and consequently, there is poor understanding of how reproductive traits drive interactions with pollinators at large scales (\protect\hyperlink{ref-sargent2008}{Sargent \& Ackerly 2008}; \protect\hyperlink{ref-rech2016}{Rech \emph{et al.} 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}; \protect\hyperlink{ref-ruger2018}{Rüger \emph{et al.} 2018}).
-Linking the plant's position in trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations (\protect\hyperlink{ref-dehling2016}{Dehling \emph{et al.} 2016}).
-Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches (\protect\hyperlink{ref-fenster2004}{Fenster \emph{et al.} 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero \emph{et al.} 2014}) and trait-matching analyses (\protect\hyperlink{ref-stang2009}{Stang \emph{et al.} 2009}; \protect\hyperlink{ref-bartomeus2016}{Bartomeus \emph{et al.} 2016}).
-However, plant reproductive traits have been overlooked beyond highly specialised pollination systems (\protect\hyperlink{ref-dellinger2020}{Dellinger 2020}) and remains unclear how specific plant reproductive biology traits (e.g., mating or compatibility system) influence plant-pollinator associations (\protect\hyperlink{ref-tur2013}{Tur \emph{et al.} 2013}; \protect\hyperlink{ref-devaux2014}{Devaux \emph{et al.} 2014}).
+Flowering plants have an astonishing diversity of floral structures (\protect\hyperlink{ref-barrett2002}{Barrett, 2002}; \protect\hyperlink{ref-schiestl2013}{Schiestl \& Johnson, 2013}) that shape plant-pollinator associations (\protect\hyperlink{ref-dellinger2020}{Dellinger, 2020}; \protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}).
+However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
+Despite the recent advances in the theoretical understanding of the major floral trade-offs {[}e.g., floral economic spectrum; \protect\hyperlink{ref-roddy2021}{Roddy et al.} (\protect\hyperlink{ref-roddy2021}{2021}){]}, we lack empirical evidence that helps to elucidate the spectrum of reproductive trait variation at a global scale as done recently for other vegetative and physiological traits (\protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}; \protect\hyperlink{ref-onoda2017}{Onoda et al., 2017}).
+
+Although there is an increasing number of macroecological studies that investigate plant reproductive traits (\protect\hyperlink{ref-baude2016}{Baude et al., 2016}; \protect\hyperlink{ref-grossenbacher2017}{Grossenbacher et al., 2017}; \protect\hyperlink{ref-moeller2017}{Moeller et al., 2017}; \protect\hyperlink{ref-munoz2016}{Munoz et al., 2016}), we still have poor understanding of how reproductive traits drive interactions with pollinators at large scales (\protect\hyperlink{ref-rech2016}{Rech et al., 2016}; \protect\hyperlink{ref-ruger2018}{Rüger et al., 2018}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}; \protect\hyperlink{ref-sargent2008}{Sargent \& Ackerly, 2008}).
+Because the species' morphology can determine the species' functional role, by linking the plant's position in the reproductive trait-space with the different pollinator groups (as done similarly in \protect\hyperlink{ref-dehling2016}{Dehling et al., 2016}), we could help to improve our understanding of plant-pollinator associations.
+Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches (\protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero et al., 2014}) and trait-matching analyses (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}).
+However, plant reproductive traits have been overlooked for most pollination systems (\protect\hyperlink{ref-dellinger2020}{Dellinger, 2020}) and remains unclear how specific plant reproductive biology traits (i.e., mating or compatibility system) influence plant-pollinator associations (\protect\hyperlink{ref-devaux2014}{Devaux et al., 2014}; \protect\hyperlink{ref-tur2013}{Tur et al., 2013}).
 
 Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases (e.g., TRY \protect\hyperlink{ref-kattge2011}{Kattge \emph{et al.} 2011}; and COMPADRE \protect\hyperlink{ref-salguero2015}{Salguero-Gómez \emph{et al.} 2015}), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function (\protect\hyperlink{ref-diaz2016}{Díaz \emph{et al.} 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}; \protect\hyperlink{ref-bruelheide2018}{Bruelheide \emph{et al.} 2018}; \protect\hyperlink{ref-carmona2021}{Carmona \emph{et al.} 2021}).
-However, most studies have focused on vegetative traits such as leaf (\protect\hyperlink{ref-wright2004}{Wright \emph{et al.} 2004}), wood (\protect\hyperlink{ref-chave2009}{Chave \emph{et al.} 2009}), or root (\protect\hyperlink{ref-laughlin2021}{Laughlin \emph{et al.} 2021}) trade-offs with little or no attention given to reproductive traits (\protect\hyperlink{ref-evojtko2020}{E-Vojtkó \emph{et al.} 2020}; \protect\hyperlink{ref-roddy2021}{Roddy \emph{et al.} 2021}) which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively, (\protect\hyperlink{ref-barrett2003}{Barrett 2003}; \protect\hyperlink{ref-moeller2017}{Moeller \emph{et al.} 2017}) and outcrossing levels are positively correlated with flower size (\protect\hyperlink{ref-goodwillie2010}{Goodwillie \emph{et al.} 2010}).
-In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species' reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators (\protect\hyperlink{ref-ollerton2011}{Ollerton \emph{et al.} 2011}; \protect\hyperlink{ref-rodger2021}{Rodger \emph{et al.} 2021}).
-However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.
-
-Several studies have identified links between plant traits and plant-pollinator network properties (\protect\hyperlink{ref-bartomeus2013}{Bartomeus 2013}; \protect\hyperlink{ref-olito2015}{Olito \& Fox 2015}; \protect\hyperlink{ref-rowe2020}{Rowe \emph{et al.} 2020}).
-Moreover, plant traits can define species' network roles (e.g., specialists vs generalists; \protect\hyperlink{ref-lazaro2013}{Lázaro \emph{et al.} 2013}; \protect\hyperlink{ref-tur2013}{Tur \emph{et al.} 2013}).
-For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators (\protect\hyperlink{ref-junker2013}{Junker \emph{et al.} 2013}; \protect\hyperlink{ref-coux2016}{Coux \emph{et al.} 2016}).
-Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure (\protect\hyperlink{ref-stang2009}{Stang \emph{et al.} 2009}; \protect\hyperlink{ref-ibanez2012}{Ibanez 2012}).
-Importantly, the combination of traits has shown to increase the predictive power of the network interactions (\protect\hyperlink{ref-eklof2013}{Eklöf \emph{et al.} 2013}) and by considering the position in the multidimensional trait space we can determine species' roles within plant-pollinator interaction networks (\protect\hyperlink{ref-dehling2016}{Dehling \emph{et al.} 2016}).
+With the recent availability of large trait databases (e.g., TRY \protect\hyperlink{ref-kattge2011}{Kattge et al., 2011}; and COMPADRE \protect\hyperlink{ref-salguero2015}{Salguero-Gómez et al., 2015}), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function (\protect\hyperlink{ref-bruelheide2018}{Bruelheide et al., 2018}; \protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
+However, most studies have focused on vegetative traits such as leaf (\protect\hyperlink{ref-wright2004}{Wright et al., 2004}), wood (\protect\hyperlink{ref-chave2009}{Chave et al., 2009}), or root (\protect\hyperlink{ref-laughlin2021}{Laughlin et al., 2021}) trade-offs with little or no attention given to reproductive traits (\protect\hyperlink{ref-evojtko2020}{E-Vojtkó et al., 2020}; \protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}) which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
+For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively, (\protect\hyperlink{ref-barrett2003}{Barrett, 2003}; \protect\hyperlink{ref-moeller2017}{Moeller et al., 2017}) and outcrossing levels are positively correlated with flower size (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}).
+In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species' reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators (\protect\hyperlink{ref-ollerton2011}{Ollerton et al., 2011}; \protect\hyperlink{ref-rodger2021}{Rodger et al., 2021}).
+However, it is still unknown to what extent these different reproductive strategies determine plant-pollinator interactions.
+
+Several studies have identified links between plant traits and plant-pollinator network properties (\protect\hyperlink{ref-bartomeus2013}{Bartomeus, 2013}; \protect\hyperlink{ref-olito2015}{Olito \& Fox, 2015}; \protect\hyperlink{ref-rowe2020}{Rowe et al., 2020}).
+Moreover, plant traits can define species' network roles (e.g., specialists vs generalists; \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}; \protect\hyperlink{ref-tur2013}{Tur et al., 2013}).
+For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators (\protect\hyperlink{ref-coux2016}{Coux et al., 2016}; \protect\hyperlink{ref-junker2013}{Junker et al., 2013}).
+Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure (\protect\hyperlink{ref-ibanez2012}{Ibanez, 2012}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}).
+Importantly, the combination of traits has shown to increase the predictive power of the network interactions (\protect\hyperlink{ref-eklof2013}{Eklöf et al., 2013}) and by considering the position in the multidimensional trait space we can determine species' roles within plant-pollinator interaction networks (\protect\hyperlink{ref-dehling2016}{Dehling et al., 2016}).
 Nonetheless, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.
 
-Here, we aim to explore the potential trade-offs among reproductive traits and how these influence plant-pollinator interactions.
+Here, we aim to explore the potential trade-offs among plant reproductive traits and their association with the different floral visitor guilds.
 First, we identify the major axes of reproductive trait variation and trade-offs that determine plant form and function.
-Second, we investigate how plant species' position in trait-space influence interactions with floral visitors.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' roles within networks using a set of complementary interaction network metrics (i.e., visitation rate, normalized degree and specialization).
+Second, we investigate the association between the plant species' position in trait-space and the different floral visitor guilds with the help of qualitative (presence-absence of interaction) and quantitative (number of visits) information.
+Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' roles within networks using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
 
@@
 
-We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
+We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see Table S1 and Fig.
+S1).
 These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies (\protect\hyperlink{ref-olesen2007}{Olesen \emph{et al.} 2007}; \protect\hyperlink{ref-fortuna2010}{Fortuna \emph{et al.} 2010}; \protect\hyperlink{ref-carvalheiro2014}{Carvalheiro \emph{et al.} 2014}) or available in online archives (e.g., The Web of Life, \protect\hyperlink{ref-fortuna2010}{Fortuna \emph{et al.} 2010}; and Mangal, \protect\hyperlink{ref-poisot2016}{Poisot \emph{et al.} 2016}).
-In total, our network dataset (Table S1) constituted 60 weighted (visitation rate) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+Many of these networks are freely available either as published studies (e.g.,~ \protect\hyperlink{ref-carvalheiro2014}{Carvalheiro et al., 2014}; \protect\hyperlink{ref-fortuna2010}{Fortuna et al., 2010}; \protect\hyperlink{ref-olesen2007}{Olesen et al., 2007}) or available in online archives (e.g., The Web of Life, \protect\hyperlink{ref-fortuna2010}{Fortuna et al., 2010}; and Mangal, \protect\hyperlink{ref-poisot2016}{Poisot et al., 2016}).
+In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
 
@@
 
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain \emph{et al.} 2020}).
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain et al., 2020}).
 We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
@@
 From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8\% of the dataset, see Fig.
-S1 for missing values information for each trait).
+S2 for missing values information for each trait).
 
@@
 
-We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life (\protect\hyperlink{ref-smith2018}{Smith \& Brown 2018}; \protect\hyperlink{ref-jin2019}{Jin \& Qian 2019}).
+We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life (\protect\hyperlink{ref-jin2019}{Jin \& Qian, 2019}; \protect\hyperlink{ref-smith2018}{Smith \& Brown, 2018}).
+
+\textbf{Data Imputation}
+
+Trait missing values were imputed with the function \emph{missForest} (\protect\hyperlink{ref-stekhoven2012}{Stekhoven \& Bühlmann, 2012}) which allows imputation of data sets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} (\protect\hyperlink{ref-penone2014}{Penone et al., 2014}).
+To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} (\protect\hyperlink{ref-santos2018}{Chamberlain et al., 2018}) based on a previous conceptual framework that considers phylogenetic eigenvectors (\protect\hyperlink{ref-diniz-filho2012}{Diniz-Filho et al., 2012}).
+We conducted two different imputations, one for the full set of species (1,506 species, 5.79\% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
+S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01\% of missing values).
+
+\textbf{Plant strategies}
+
+We explored the trade-offs between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
+Prior to the analyses, we excluded outliers and standardized the data.
+Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th--97.5th percentile range (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}), and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell, 2012}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams, 2010}).
+Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
+S3).
+We found little difference between the explained variance with the imputed dataset (51.08\%) and the dataset without missing values (52.87\%).
+In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
+Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
+For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
+
+\textbf{Phylogenetic signal}
+
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell, 2012}) and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
+
+\textbf{Network analyses}
+
+Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+These networks were analysed in their qualitative and quantitative form.
+First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
+Second, we analysed the untransformed weighted networks with the number of visits of floral visitors to individual flowers that account for the intensity of the interaction.
+Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency (\protect\hyperlink{ref-ballantyne2015}{Ballantyne et al., 2015}), the number of visits can provide valuable information of the contribution of floral visitors to pollination (\protect\hyperlink{ref-vazquez2005}{Vázquez et al., 2005}, \protect\hyperlink{ref-vazquez2012}{2012}).
+In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
+Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
+All analyses were conducted in R version \emph{4.0.3}.
+
+\textbf{Visitation patterns}
+
+We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species.
+For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
+Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total).
+This finding is consistent with previous research showing that \emph{A.
+mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems (\protect\hyperlink{ref-hung2018}{Hung et al., 2018}).
+Hence, to control for the effect of \emph{A.
+mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding \emph{A.
+mellifera}.
+We found that \emph{A.
+mellifera}, was partly driving some of the observed trends on PC1 (Fig.
+S4).
+However, we did not detect major differences on PC2 and PC3.
+
+We implemented Bayesian generalized linear mixed models using the R package \emph{brms} (\protect\hyperlink{ref-burkner2017}{Bürkner, 2017}).
+We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
+We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
+Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
+We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
+The models were run with non or very weakly informative informative priors from the brm function so they have neglible influence on the results (\protect\hyperlink{ref-burkner2017}{Bürkner, 2017}), 3,000 iterations and with previous 1,000 warm up iterations.
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package (\protect\hyperlink{ref-gabry2019}{Gabry et al., 2019}).
+
+\textbf{Plant species network roles}
+
+We investigated whether different quantitative traits determined plant species network roles using Bayesian modelling and regression trees.
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies (\protect\hyperlink{ref-dormann2008}{Dormann et al., 2008}) with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') (\protect\hyperlink{ref-bluthgen2006}{Blüthgen et al., 2006}), which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} (\protect\hyperlink{ref-dormann2008}{Dormann et al., 2008}).
+
+First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
+For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
+Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns' section.
+
+Second, to better understand complex trait relationships, we used regression trees.
+Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction.
+We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
+We conducted this analysis using the \emph{rpart} function from the \emph{rtrees} package (\protect\hyperlink{ref-therneau2015}{Therneau et al., 2015}) with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package (\protect\hyperlink{ref-milborrow2015}{Milborrow, 2015}) to plot the regression trees.
+We considered the species level indices as response variables (number of visits, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
+We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
+We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (Fig.
+S5).
+
+\hypertarget{results}{%
+\section{RESULTS}\label{results}}
+
+\textbf{Plant strategies}
+
+The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of trait variation, respectively (Fig.
+1 and Fig.
+S6) and had a phylogenetic correlation (\(\lambda\)) of 0.76.
+The first principal component (PC1) represented 26.72\% of the trait variation and indicated a trade-off between flower number and flower size.
+We refer to this axis as the `flower number - flower size trade-off,' as already described in previous studies (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}).
+Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
+The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
+The second principal component (PC2) represented 25.05\% of the trait variation and indicated a trade-off between low and high pollinator dependence.
+We refer to this axis as the `pollinator dependence trade-off.' The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
+We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
+In contrast, species with high levels of autonomous selfing tended to have fewer and smaller flowers, had shorter styles and were shorter in height.
+Further, PC3 explained a considerable amount of trait variability (19.17\%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
+The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
+Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the `style length trade-off.' Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82\%; Fig.
+S7).
+This pPCA explained similar variance with the first two principal components (45.52\%) and similar associations of traits despite some variability in the loadings (Table S4).
+
+We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
+2 and Table S2).
+Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
+In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
+S8).
+Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Fig.
+S8a and Fig.
+S8b).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
+S8c and Fig.
+S8d).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
+S8e and Fig.
+S8f).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
+S8g and Fig.
+S8h).
+Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Fig.
+S8i and Fig.
+S8j).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Fig.
+S8k and Fig.
+S8l).
+
+\textbf{Phylogenetic signal}
+
+We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) in all quantitative traits (Table S5).
+The traits that showed the highest phylogenetic signal were ovule number (\(\lambda\) = 1), pollen grains per flower (\(\lambda\) = 1) and plant height (\(\lambda\) = 0.96), followed by flower length (\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73), number of flowers per plant (\(\lambda\) = 0.69) and nectar concentration (\(\lambda\) = 0.65).
+The traits that showed a moderate phylogenetic signal were inflorescence width (\(\lambda\) = 0.57), style length (\(\lambda\) = 0.49) and autonomous selfing (\(\lambda\) = 0.34).
+Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits (\(\lambda\) = 0.14).
+
+\textbf{Visitation patterns}
+
+The main axes of trait variation explained partly presence-absence of interaction partners (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the overall number of visits (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
+However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (Fig.
+3).
+We found that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds (flower number - flower size trade-off, PC1; Fig.
+3a).
+However, plant species with high flower number but small flowers had higher number of visits of bees and syrphids guilds (PC1; Fig.
+3d).
+Remarkably, all plant species with higher pollinator dependence had higher number of interacting partners and number of visits for all floral visitor guilds (PC2; Fig.
+3b and Fig.
+3e).
+Finally, plant species with short styles and low selfing had higher interaction partners of all guilds but bees that interacted clearly more with plant species with long styles and high selfing (style length trade-off; Fig.
+3c).
+However, for number of visits, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
+3f).
+
+The additional model for both presence-absence of interaction (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and number of visits (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
+The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (Fig.
+3a and Fig.
+3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (Fig.
+S9).
+
+\textbf{Plant species network roles}
+
+The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
+S10; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
+Overall, the most notable trends were found on PC1 and PC3 for number of visits and specialization.
+On the flower number - flower size trade-off (PC1), number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
+S10a).
+On PC1, specialization showed the opposite trend (Fig.
+S10g).
+On the style length trade-off (PC3), number of visits was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
+S10c).
+Again, specialization showed the opposite trend to number of visits (Fig.
+S10i).
+
+When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for number of visits was best explained by plant height, nectar concentration and style length (Fig.
+4a).
+Specifically, species taller than 3.9m had the highest number of visits, while species that were shorter than 3.9m and had a nectar concentration lower than 16\% had the lowest number of visits.
+Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
+4b).
+Species with a nectar concentration over 49\% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49\%, more than 21,000 pollen grains per flower and height less than 0.78m had the lowest normalized degree.
+Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
+4c).
+Overall, plant species with the highest specialization were shorter than 1.3m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11\% of their fruits.
+In contrast, species taller or equal than 5.1m and with lower than 14 ovules per flower had the lowest specialization values.
+
+\hypertarget{discussion}{%
+\section{DISCUSSION}\label{discussion}}
+
+This study demonstrates that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
+These trade-offs are differentiated along three axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
+These reproductive trade-offs helped partly explain the presence of floral visitor interactions, but not their number of visits.
+However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
+Moreover, we found that the plant species network roles were best explained by plant size and floral reward related traits.
+
+Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
+Trait variation on these two axes was associated with the `fast-slow continuum' in plant (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}) and animal (\protect\hyperlink{ref-healy2019}{Healy et al., 2019}) life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+The `slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
+In contrast, plant species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
+Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}).
+The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
+S11).
+
+Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (number of interaction partners and number of visits), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies influence plant-pollinator interactions.
+For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
+1 and Fig.
+S6).
+This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently (\protect\hyperlink{ref-hegland2005}{Hegland \& Totland, 2005}; \protect\hyperlink{ref-kaiser2014}{Kaiser-Bunbury et al., 2014}; \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}).
+In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation patterns across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
+For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
+3) suggesting possible niche partitioning (\protect\hyperlink{ref-palmer2003}{Palmer et al., 2003}; \protect\hyperlink{ref-phillips2020}{Phillips et al., 2020}) between these two guilds.
+However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species network roles (Fig.
+4).
+More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-encinas2012}{Encinas-Viso et al., 2012}; \protect\hyperlink{ref-vazquez2007}{Vázquez et al., 2007}) that reproductive trade-offs do not.
+
+To conclude, we provide a robust description of plant reproductive trade-offs using a large global dataset of plant traits.
+We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
+Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}) it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
+Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
+Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators (\protect\hyperlink{ref-gervasi2017}{Gervasi \& Schiestl, 2017}; \protect\hyperlink{ref-mackin2021}{Mackin et al., 2021}).
+Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
+Abdi, H., \& Williams, L. J. (2010). Principal component analysis. \emph{WIREs Comp. Stats.}, \emph{2}(4), 433--459. \url{https://doi.org/10.1002/wics.101}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
+Ballantyne, G., Baldock, K.
+C.
+R., \& Willmer, P.
+G.
+(2015).
+Constructing more informative plant\textendash pollinator networks: Visitation and pollen deposition networks in a heathland plant community.
+\emph{Proc.
+Royal Soc.
+B}, \emph{282}(1814), 20151130.
+\url{https://doi.org/10.1098/rspb.2015.1130}
+
+\leavevmode\vadjust pre{\hypertarget{ref-barrett2002}{}}%
+Barrett, S. C. H. (2002). The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.}, \emph{3}(4), 274--284. \url{https://doi.org/10.1038/nrg776}
+
+\leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
+Barrett, S.
+C.
+H.
+(2003).
+Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond.
+\emph{Philos.
+Trans.
+R.
+Soc.
+Lond.
+B Biol.
+Sci.}, \emph{358}(1434), 991--1004.
+\url{https://doi.org/10.1098/rstb.2003.1301}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2013}{}}%
+Bartomeus, I.
+(2013).
+Understanding {Linkage Rules} in {Plant}-{Pollinator Networks} by {Using Hierarchical Models That Incorporate Pollinator Detectability} and {Plant Traits}.
+\emph{PLoS One}, \emph{8}(7), e69200.
+\url{https://doi.org/10.1371/journal.pone.0069200}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
+Bartomeus, I., Gravel, D., Tylianakis, J.
+M., Aizen, M.
+A., Dickie, I.
+A., \& Bernard-Verdier, M.
+(2016).
+A common framework for identifying linkage rules across different types of interactions.
+\emph{Funct.
+Ecol.}, \emph{30}(12), 1894--1903.
+\url{https://doi.org/10.1111/1365-2435.12666}
+
+\leavevmode\vadjust pre{\hypertarget{ref-baude2016}{}}%
+Baude, M., Kunin, W.
+E., Boatman, N.
+D., Conyers, S., Davies, N., Gillespie, M.
+A., Morton, R.
+D., Smart, S.
+M., \& Memmott, J.
+(2016).
+Historical nectar assessment reveals the fall and rise of floral resources in britain.
+\emph{Nature}, \emph{530}(7588), 85--88.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
+Blüthgen, N., Menzel, F., \& Blüthgen, N. (2006). Measuring specialization in species interaction networks. \emph{BMC Ecol.}, \emph{6}(1), 9. \url{https://doi.org/10.1186/1472-6785-6-9}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
+Bruelheide, H., Dengler, J., Purschke, O., Lenoir, J., Jiménez-Alfaro, B., Hennekens, S.
+M., Botta-Dukát, Z., Chytry, M., Field, R., Jansen, F.others.
+(2018).
+Global trait--environment relationships of plant communities.
+\emph{Nat.
+Ecol.
+Evol.}, \emph{2}(12), 1906--1917.
+
+\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
+Bürkner, P.-C. (2017). Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.}, \emph{80}(1), 1--28.
+
+\leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
+Carmona, C.
+P., Tamme, R., Pärtel, M., Bello, F.
+de, Brosse, S., Capdevila, P., González-M, R., González-Suárez, M., Salguero-Gómez, R., Vásquez-Valderrama, M., \& Toussaint, A.
+(2021).
+Erosion of global functional diversity across the tree of life.
+\emph{Sci.
+Adv.}, \emph{7}(13), eabf2675.
+\url{https://doi.org/10.1126/sciadv.abf2675}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
+Carvalheiro, L.
+G., Biesmeijer, J.
+C., Benadi, G., Fründ, J., Stang, M., Bartomeus, I., Kaiser-Bunbury, C.
+N., Baude, M., Gomes, S.
+I.
+F., Merckx, V., Baldock, K.
+C.
+R., Bennett, A.
+T.
+D., Boada, R., Bommarco, R., Cartar, R., Chacoff, N., Dänhardt, J., Dicks, L.
+V., Dormann, C.
+F., \ldots{} Kunin, W.
+E.
+(2014).
+The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
+\emph{Ecol.
+Lett.}, \emph{17}(11), 1389--1399.
+\url{https://doi.org/10.1111/ele.12342}
+
+\leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
+Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., Bartomeus, I., Baumgartner, J., O'Donnell, J., Oksanen, J., Tzovaras, B.
+G., Marchand, P., Tran, V., Salmon, M., Li, G., \& Grenié, M.
+(2018).
+\emph{Package {`{PVR}.'} R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
+Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., Bartomeus, I., Baumgartner, J., O'Donnell, J., Oksanen, J., Tzovaras, B.
+G., Marchand, P., Tran, V., Salmon, M., Li, G., \& Grenié, M.
+(2020).
+\emph{Taxize: {Taxonomic} information from around the web.
+R package version 0.9.99.~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
+Chave, J., Coomes, D., Jansen, S., Lewis, S. L., Swenson, N. G., \& Zanne, A. E. (2009). Towards a worldwide wood economics spectrum. \emph{Ecol. Lett.}, \emph{12}(4), 351--366.
+
+\leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
+Coux, C., Rader, R., Bartomeus, I., \& Tylianakis, J.
+M.
+(2016).
+Linking species functional roles to their network roles.
+\emph{Ecol.
+Lett.}, \emph{19}(7), 762--770.
+\url{https://doi.org/10.1111/ele.12612}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
+Dehling, D.
+M., Jordano, P., Schaefer, H.
+M., Böhning-Gaese, K., \& Schleuning, M.
+(2016).
+Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
+\emph{Proc.
+Royal Soc.
+B}, \emph{283}(1823), 20152444.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dellinger2020}{}}%
+Dellinger, A. S. (2020). Pollination syndromes in the 21st century: Where do we stand and where may we go? \emph{New Phytol.}, \emph{228}(4), 1193--1213. \url{https://doi.org/10.1111/nph.16793}
+
+\leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
+Devaux, C., Lepers, C., \& Porcher, E.
+(2014).
+Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems.
+\emph{J.
+Evol.
+Biol.}, \emph{27}(7), 1413--1430.
+\url{https://doi.org/10.1111/jeb.12380}
+
+\leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
+Díaz, S., Kattge, J., Cornelissen, J.
+H.
+C., Wright, I.
+J., Lavorel, S., Dray, S., Reu, B., Kleyer, M., Wirth, C., Colin Prentice, I., Garnier, E., Bönisch, G., Westoby, M., Poorter, H., Reich, P.
+B., Moles, A.
+T., Dickie, J., Gillison, A.
+N., Zanne, A.
+E., \ldots{} Gorné, L.
+D.
+(2016).
+The global spectrum of plant form and function.
+\emph{Nature}, \emph{529}(7585), 167--171.
+\url{https://doi.org/10.1038/nature16489}
+
+\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
+Diniz-Filho, J.
+A.
+F., Bini, L.
+M., Rangel, T.
+F., Morales-Castilla, I., Olalla-Tárraga, M.
+Á., Rodríguez, M.
+Á., \& Hawkins, B.
+A.
+(2012).
+On the selection of phylogenetic eigenvectors for ecological analyses.
+\emph{Ecography}, \emph{35}(3), 239--249.
+\url{https://doi.org/10.1111/j.1600-0587.2011.06949.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
+Dormann, C. F., Gruber, B., \& Fründ, J. (2008). Introducing the bipartite package: Analysing ecological networks. \emph{R News}, \emph{8/2}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
+Eklöf, A., Jacob, U., Kopp, J., Bosch, J., Castro-Urgal, R., Chacoff, N.
+P., Dalsgaard, B., Sassi, C.
+de, Galetti, M., Guimaraes, P.
+R.others.
+(2013).
+The dimensionality of ecological networks.
+\emph{Ecol.
+Lett.}, \emph{16}(5), 577--583.
+
+\leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
+Encinas-Viso, F., Revilla, T. A., \& Etienne, R. S. (2012). Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.}, \emph{15}(3), 198--208.
+
+\leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
+E-Vojtkó, A., Bello, F.
+de, Durka, W., Kühn, I., \& Götzenberger, L.
+(2020).
+The neglected importance of floral traits in trait-based plant community assembly.
+\emph{J.
+Veg.
+Sci.}, \emph{31}(4), 529--539.
+\url{https://doi.org/10.1111/jvs.12877}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fenster2004}{}}%
+Fenster, C.
+B., Armbruster, W.
+S., Wilson, P., Dudash, M.
+R., \& Thomson, J.
+D.
+(2004).
+Pollination {Syndromes} and {Floral Specialization}.
+\emph{Annu.
+Rev.
+Ecol.
+Evol.
+Syst.}, \emph{35}(1), 375--403.
+\url{https://doi.org/10.1146/annurev.ecolsys.34.011802.132347}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
+Fortuna, M.
+A., Stouffer, D.
+B., Olesen, J.
+M., Jordano, P., Mouillot, D., Krasnov, B.
+R., Poulin, R., \& Bascompte, J.
+(2010).
+Nestedness versus modularity in ecological networks: Two sides of the same coin?
+\emph{J.
+Anim.
+Ecol.}, \emph{79}(4), 811--817.
+\url{https://doi.org/10.1111/j.1365-2656.2010.01688.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
+Gabry, J., Simpson, D., Vehtari, A., Betancourt, M., \& Gelman, A.
+(2019).
+Visualization in {Bayesian} workflow.
+\emph{J.
+R.
+Stat.
+Soc.
+Ser.
+A Stat.
+Soc.}, \emph{182}(2), 389--402.
+\url{https://doi.org/10.1111/rssa.12378}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gervasi2017}{}}%
+Gervasi, D. D. L., \& Schiestl, F. P. (2017). Real-time divergent evolution in plants driven by pollinators. \emph{Nat. Commun.}, \emph{8}(1), 14691. \url{https://doi.org/10.1038/ncomms14691}
+
+\leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
+Goodwillie, C., Sargent, R.
+D., Eckert, C.
+G., Elle, E., Geber, M.
+A., Johnston, M.
+O., Kalisz, S., Moeller, D.
+A., Ree, R.
+H., Vallejo-Marin, M., \& Winn, A.
+A.
+(2010).
+Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
+\emph{New Phytol.}, \emph{185}(1), 311--321.
+\url{https://doi.org/10.1111/j.1469-8137.2009.03043.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-grossenbacher2017}{}}%
+Grossenbacher, D.
+L., Brandvain, Y., Auld, J.
+R., Burd, M., Cheptou, P.-O., Conner, J.
+K., Grant, A.
+G., Hovick, S.
+M., Pannell, J.
+R., Pauw, A.others.
+(2017).
+Self-compatibility is over-represented on islands.
+\emph{New Phytol.}, \emph{215}(1), 469--478.
+
+\leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
+Healy, K., Ezard, T.
+H.
+G., Jones, O.
+R., Salguero-Gómez, R., \& Buckley, Y.
+M.
+(2019).
+Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
+\emph{Nat.
+Ecol.
+Evol.}, \emph{3}(8), 1217--1224.
+\url{https://doi.org/10.1038/s41559-019-0938-7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
+Hegland, S. J., \& Totland, Ø. (2005). Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia}, \emph{145}(4), 586--594.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
+Hung, K.-L.
+J., Kingston, J.
+M., Albrecht, M., Holway, D.
+A., \& Kohn, J.
+R.
+(2018).
+The worldwide importance of honey bees as pollinators in natural habitats.
+\emph{Proc.
+Royal Soc.
+B}, \emph{285}(1870), 20172140.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
+Ibanez, S.
+(2012).
+Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks.
+\emph{Oecologia}, \emph{170}(1), 233--242.
+\url{https://doi.org/10.1007/s00442-012-2290-3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
+Jin, Y., \& Qian, H.
+(2019).
+V.{PhyloMaker}: An {R} package that can generate very large phylogenies for vascular plants.
+\emph{Ecography}, \emph{42}(8), 1353--1359.
+\url{https://doi.org/10.1111/ecog.04434}
+
+\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
+Junker, R.
+R., Blüthgen, N., Brehm, T., Binkenstein, J., Paulus, J., Schaefer, H.
+M., \& Stang, M.
+(2013).
+Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
+\emph{Funct.
+Ecol.}, \emph{27}(2), 329--341.
+\url{https://doi.org/10.1111/1365-2435.12005}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
+Kaiser-Bunbury, C.
+N., Vázquez, D.
+P., Stang, M., \& Ghazoul, J.
+(2014).
+Determinants of the microstructure of plant\textendash pollinator networks.
+\emph{Ecology}, \emph{95}(12), 3314--3324.
+\url{https://doi.org/10.1890/14-0024.1}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
+Kattge, J., Díaz, S., Lavorel, S., Prentice, I.
+C., Leadley, P., Bönisch, G., Garnier, E., Westoby, M., Reich, P.
+B., Wright, I.
+J., Cornelissen, J.
+H.
+C., Violle, C., Harrison, S.
+P., Bodegom, P.
+M.
+V., Reichstein, M., Enquist, B.
+J., Soudzilovskaia, N.
+A., Ackerly, D.
+D., Anand, M., \ldots{} Wirth, C.
+(2011).
+{TRY} \textendash{} a global database of plant traits.
+\emph{Glob.
+Chang.
+Biol.}, \emph{17}(9), 2905--2935.
+\url{https://doi.org/10.1111/j.1365-2486.2011.02451.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
+Kettle, C.
+J., Maycock, C.
+R., Ghazoul, J., Hollingsworth, P.
+M., Khoo, E., Sukri, R.
+S.
+H., \& Burslem, D.
+F.
+R.
+P.
+(2011).
+Ecological {Implications} of a {Flower Size}/{Number Trade}-{Off} in {Tropical Forest Trees}.
+\emph{PLoS One}, \emph{6}(2), e16111.
+\url{https://doi.org/10.1371/journal.pone.0016111}
+
+\leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
+Laughlin, D.
+C., Mommer, L., Sabatini, F.
+M., Bruelheide, H., Kuyper, T.
+W., McCormack, M.
+L., Bergmann, J., Freschet, G.
+T., Guerrero-Ramírez, N.
+R., Iversen, C.
+M.others.
+(2021).
+Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
+\emph{Nat.
+Ecol.
+Evol.}, 1--12.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
+Lázaro, A., Jakobsson, A., \& Totland, Ø.
+(2013).
+How do pollinator visitation rate and seed set relate to species' floral traits and community context?
+\emph{Oecologia}, \emph{173}(3), 881--893.
+\url{https://doi.org/10.1007/s00442-013-2652-5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
+Legendre, P., \& Legendre, L. (2012). \emph{Numerical ecology} ({2nd edn}). {Elsevier, Amsterdam}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mackin2021}{}}%
+Mackin, C.
+R., Peña, J.
+F., Blanco, M.
+A., Balfour, N.
+J., \& Castellanos, M.
+C.
+(2021).
+Rapid evolution of a floral trait following acquisition of novel pollinators.
+\emph{J.
+Ecol.}, \emph{109}(5), 2234--2246.
+\url{https://doi.org/10.1111/1365-2745.13636}
+
+\leavevmode\vadjust pre{\hypertarget{ref-milborrow2015}{}}%
+Milborrow, S.
+(2015).
+\emph{Rpart.
+Plot: {Plot} rpart {Models}.
+{An Enhanced Version} of plot.
+Rpart.
+R package version 3.0.9.~At \href{https://CRAN.R-project.org/package=rpart.plot}{https://CRAN.r-project.org/package=rpart.plot}}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
+Moeller, D.
+A., Runquist, R.
+D.
+B., Moe, A.
+M., Geber, M.
+A., Goodwillie, C., Cheptou, P.-O., Eckert, C.
+G., Elle, E., Johnston, M.
+O., Kalisz, S., Ree, R.
+H., Sargent, R.
+D., Vallejo-Marin, M., \& Winn, A.
+A.
+(2017).
+Global biogeography of mating system variation in seed plants.
+\emph{Ecol.
+Lett.}, \emph{20}(3), 375--384.
+\url{https://doi.org/10.1111/ele.12738}
+
+\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
+Munoz, F., Violle, C., \& Cheptou, P.-O.
+(2016).
+{CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
+\emph{Oikos}, \emph{125}(9), 1296--1303.
+\url{https://doi.org/10.1111/oik.02328}
+
+\leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
+Olesen, J. M., Bascompte, J., Dupont, Y. L., \& Jordano, P. (2007). The modularity of pollination networks. \emph{PNAS}, \emph{104}(50), 19891--19896. \url{https://doi.org/10.1073/pnas.0706375104}
+
+\leavevmode\vadjust pre{\hypertarget{ref-olito2015}{}}%
+Olito, C., \& Fox, J.
+W.
+(2015).
+Species traits and abundances predict metrics of plant\textendash pollinator network structure, but not pairwise interactions.
+\emph{Oikos}, \emph{124}(4), 428--436.
+\url{https://doi.org/10.1111/oik.01439}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ollerton2011}{}}%
+Ollerton, J., Winfree, R., \& Tarrant, S. (2011). How many flowering plants are pollinated by animals? \emph{Oikos}, \emph{120}(3), 321--326.
+
+\leavevmode\vadjust pre{\hypertarget{ref-onoda2017}{}}%
+Onoda, Y., Wright, I.
+J., Evans, J.
+R., Hikosaka, K., Kitajima, K., Niinemets, Ü., Poorter, H., Tosens, T., \& Westoby, M.
+(2017).
+Physiological and structural tradeoffs underlying the leaf economics spectrum.
+\emph{New Phytologist}, \emph{214}(4), 1447--1463.
+
+\leavevmode\vadjust pre{\hypertarget{ref-palmer2003}{}}%
+Palmer, T.
+M., Stanton, M.
+L., \& Young, T.
+P.
+(2003).
+Competition and coexistence: Exploring mechanisms that restrict and maintain diversity within mutualist guilds.
+\emph{Am.
+Nat.}, \emph{162}(S4), S63--S79.
+
+\leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
+Penone, C., Davidson, A.
+D., Shoemaker, K.
+T., Marco, M.
+D., Rondinini, C., Brooks, T.
+M., Young, B.
+E., Graham, C.
+H., \& Costa, G.
+C.
+(2014).
+Imputation of missing data in life-history trait datasets: Which approach performs the best?
+\emph{Methods Ecol.
+Evol.}, \emph{5}(9), 961--970.
+\url{https://doi.org/10.1111/2041-210X.12232}
+
+\leavevmode\vadjust pre{\hypertarget{ref-phillips2020}{}}%
+Phillips, R. D., Peakall, R., van der Niet, T., \& Johnson, S. D. (2020). Niche perspectives on plant\textendash pollinator interactions. \emph{Trends Plant Sci.}, \emph{25}(8), 779--793.
+
+\leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
+Poisot, T., Baiser, B., Dunne, J.
+A., Kéfi, S., Massol, F., Mouquet, N., Romanuk, T.
+N., Stouffer, D.
+B., Wood, S.
+A., \& Gravel, D.
+(2016).
+Mangal \textendash{} making ecological network analysis simple.
+\emph{Ecography}, \emph{39}(4), 384--390.
+\url{https://doi.org/10.1111/ecog.00976}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rech2016}{}}%
+Rech, A.
+R., Dalsgaard, B., Sandel, B., Sonne, J., Svenning, J.-C., Holmes, N., \& Ollerton, J.
+(2016).
+The macroecology of animal versus wind pollination: Ecological factors are more important than historical climate stability.
+\emph{Plant Ecol.
+Divers.}, \emph{9}(3), 253--262.
+\url{https://doi.org/10.1080/17550874.2016.1207722}
+
+\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
+Revell, L.
+J.
+(2012).
+Phytools: An {R} package for phylogenetic comparative biology (and other things).
+\emph{Methods Ecol.
+Evol.}, \emph{3}(2), 217--223.
+\url{https://doi.org/10.1111/j.2041-210X.2011.00169.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-roddy2021}{}}%
+Roddy, A.
+B., Martínez-Perez, C., Teixido, A.
+L., Cornelissen, T.
+G., Olson, M.
+E., Oliveira, R.
+S., \& Silveira, F.
+A.
+O.
+(2021).
+Towards the flower economics spectrum.
+\emph{New Phytol.}, \emph{229}(2), 665--672.
+\url{https://doi.org/10.1111/nph.16823}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rodger2021}{}}%
+Rodger, J.
+G., Bennett, J.
+M., Razanajatovo, M., Knight, T.
+M., Kleunen, M.
+van, Ashman, T.-L., Steets, J.
+A., Hui, C., Arceo-Gómez, G., Burd, M.others.
+(2021).
+Widespread vulnerability of flowering plant seed production to pollinator declines.
+\emph{Sci.
+Adv.}, \emph{7}(42), eabd3524.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
+Rosas-Guerrero, V., Aguilar, R., Martén-Rodríguez, S., Ashworth, L., Lopezaraiza-Mikel, M., Bastida, J.
+M., \& Quesada, M.
+(2014).
+A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
+\emph{Ecol.
+Lett.}, \emph{17}(3), 388--400.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rowe2020}{}}%
+Rowe, L., Gibson, D., Bahlai, C.
+A., Gibbs, J., Landis, D.
+A., \& Isaacs, R.
+(2020).
+Flower traits associated with the visitation patterns of bees.
+\emph{Oecologia}, \emph{193}(2), 511--522.
+\url{https://doi.org/10.1007/s00442-020-04674-0}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
+Rüger, N., Comita, L.
+S., Condit, R., Purves, D., Rosenbaum, B., Visser, M.
+D., Wright, S.
+J., \& Wirth, C.
+(2018).
+Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
+\emph{Ecol.
+Lett.}, \emph{21}(7), 1075--1084.
+\url{https://doi.org/10.1111/ele.12974}
+
+\leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
+Salguero-Gómez, R., Jones, O.
+R., Archer, C.
+R., Buckley, Y.
+M., Che-Castaldo, J., Caswell, H., Hodgson, D., Scheuerlein, A., Conde, D.
+A., Brinks, E., Buhr, H.
+de, Farack, C., Gottschalk, F., Hartmann, A., Henning, A., Hoppe, G., Römer, G., Runge, J., Ruoff, T., \ldots{} Vaupel, J.
+W.
+(2015).
+The compadre {Plant Matrix Database}: An open online repository for plant demography.
+\emph{J.
+Ecol.}, \emph{103}(1), 202--218.
+\url{https://doi.org/10.1111/1365-2745.12334}
+
+\leavevmode\vadjust pre{\hypertarget{ref-salguero2016}{}}%
+Salguero-Gómez, R., Jones, O.
+R., Jongejans, E., Blomberg, S.
+P., Hodgson, D.
+J., Mbeau-Ache, C., Zuidema, P.
+A., de Kroon, H., \& Buckley, Y.
+M.
+(2016).
+Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
+\emph{Proc.
+Natl.
+Acad.
+Sci.
+U.S.A.}, \emph{113}(1), 230--235.
+\url{https://doi.org/10.1073/pnas.1506215112}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
+Sargent, R. D., \& Ackerly, D. D. (2008). Plant--pollinator interactions and the assembly of plant communities. \emph{Trends Ecol. Evol.}, \emph{23}(3), 123--130.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
+Sargent, R.
+D., Goodwillie, C., Kalisz, S., \& Ree, R.
+H.
+(2007).
+Phylogenetic evidence for a flower size and number trade-off.
+\emph{Am.
+J.
+Bot.}, \emph{94}(12), 2059--2062.
+\url{https://doi.org/10.3732/ajb.94.12.2059}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schiestl2013}{}}%
+Schiestl, F. P., \& Johnson, S. D. (2013). Pollinator-mediated evolution of floral signals. \emph{Trends Ecol. Evol.}, \emph{28}(5), 307--315. \url{https://doi.org/10.1016/j.tree.2013.01.019}
+
+\leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
+Smith, S. A., \& Brown, J. W. (2018). Constructing a broadly inclusive seed plant phylogeny. \emph{Am. J. Bot.}, \emph{105}(3), 302--314. \url{https://doi.org/10.1002/ajb2.1019}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
+Stang, M., Klinkhamer, P.
+G.
+L., Waser, N.
+M., Stang, I., \& van der Meijden, E.
+(2009).
+Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
+\emph{Ann.
+Bot.}, \emph{103}(9), 1459--1469.
+\url{https://doi.org/10.1093/aob/mcp027}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
+Stekhoven, D.
+J., \& Bühlmann, P.
+(2012).
+{MissForest}\textemdash non-parametric missing value imputation for mixed-type data.
+\emph{Bioinformatics}, \emph{28}(1), 112--118.
+\url{https://doi.org/10.1093/bioinformatics/btr597}
+
+\leavevmode\vadjust pre{\hypertarget{ref-therneau2015}{}}%
+Therneau, T., Atkinson, B., Ripley, B., \& Ripley, M.
+B.
+(2015).
+\emph{Package {`rpart.'} R package version 4.1-15.~At \href{https://CRAN.R-project.org/package=rpart}{https://CRAN.r-project.org/package=rpart}}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
+Tur, C., Castro-Urgal, R., \& Traveset, A.
+(2013).
+Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}.
+\emph{PLoS One}, \emph{8}(10), e78294.
+\url{https://doi.org/10.1371/journal.pone.0078294}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
+Vázquez, D.
+P., Lomáscolo, S.
+B., Maldonado, M.
+B., Chacoff, N.
+P., Dorado, J., Stevani, E.
+L., \& Vitale, N.
+L.
+(2012).
+The strength of plant\textendash pollinator interactions.
+\emph{Ecology}, \emph{93}(4), 719--725.
+\url{https://doi.org/10.1890/11-1356.1}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
+Vázquez, D.
+P., Melián, C.
+J., Williams, N.
+M., Blüthgen, N., Krasnov, B.
+R., \& Poulin, R.
+(2007).
+Species abundance and asymmetric interaction strength in ecological networks.
+\emph{Oikos}, \emph{116}(7), 1120--1127.
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
+Vázquez, D.
+P., Morris, W.
+F., \& Jordano, P.
+(2005).
+Interaction frequency as a surrogate for the total effect of animal mutualists on plants.
+\emph{Ecol.
+Lett.}, \emph{8}(10), 1088--1094.
+\url{https://doi.org/10.1111/j.1461-0248.2005.00810.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%
+Wright, I.
+J., Reich, P.
+B., Westoby, M., Ackerly, D.
+D., Baruch, Z., Bongers, F., Cavender-Bares, J., Chapin, T., Cornelissen, J.
+H.
+C., Diemer, M., Flexas, J., Garnier, E., Groom, P.
+K., Gulias, J., Hikosaka, K., Lamont, B.
+B., Lee, T., Lee, W., Lusk, C., \ldots{} Villar, R.
+(2004).
+The worldwide leaf economics spectrum.
+\emph{Nature}, \emph{428}(6985), 821--827.
+\url{https://doi.org/10.1038/nature02403}
+
+\end{CSLReferences}
+
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
+We thank all researchers that made their data openly available and sent it upon request.
+We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
+We also thank Jason Tylianakis for his comments on the manuscript before submission.
+Finally, JBL thanks the University of New England for the funding provided to carry out this work.
 
@@
 
-\textbf{Data Imputation}
-
-Trait missing values were imputed with the function \emph{missForest} (\protect\hyperlink{ref-stekhoven2012}{Stekhoven \& Bühlmann 2012}) which allows imputation of data sets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} (\protect\hyperlink{ref-penone2014}{Penone \emph{et al.} 2014}).
-To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} (\protect\hyperlink{ref-santos2018}{Chamberlain \emph{et al.} 2018}) based on a previous conceptual framework that considers phylogenetic eigenvectors (\protect\hyperlink{ref-diniz-filho2012}{Diniz-Filho \emph{et al.} 2012}).
-We conducted two different imputations, one for the full set of species (1,506 species, 5.79\% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
-S1) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01\% of missing values).
-
-\textbf{Plant strategies}
-
-We explored the trade-offs between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th--97.5th percentile range (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre 2012}), and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell 2012}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams 2010}).
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
-S2).
-We found little difference between the explained variance with the imputed dataset (51.08\%) and the dataset without missing values (52.87\%).
-In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
-For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
-
-\textbf{Phylogenetic signal}
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell 2012}) and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-\textbf{Network analyses}
-
-Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-These networks were analysed in their qualitative and quantitative form.
-First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
-Second, we analysed the untransformed weighted networks with visitation rate that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and visitation rate does not consider each pollinator species efficiency (\protect\hyperlink{ref-ballantyne2015}{Ballantyne \emph{et al.} 2015}), visitation rate can provide valuable information of the contribution of floral visitors to pollination (\protect\hyperlink{ref-vazquez2005}{Vázquez \emph{et al.} 2005}, \protect\hyperlink{ref-vazquez2012}{2012}).
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
-All analyses were conducted in R version \emph{4.0.3}.
-
-\textbf{Visitation patterns}
-
-We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and visitation rate of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total).
-This finding is consistent with previous research showing that \emph{A.
-mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems (\protect\hyperlink{ref-hung2018}{Hung \emph{et al.} 2018}).
-Hence, to control for the effect of \emph{A.
-mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and visitation rate excluding \emph{A.
-mellifera}.
-We found that \emph{A.
-mellifera}, was partly driving some of the observed trends on PC1 (Fig.
-S3).
-However, we did not detect major differences on PC2 and PC3.
-
-We implemented Bayesian generalized linear mixed models using the R package \emph{brms} (\protect\hyperlink{ref-burkner2017}{Bürkner 2017}).
-We modelled presence-absence of observed interactions and visitation rate as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., visitation rate \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
-We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified for presence-absence of interaction and visitation rate a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with weakly informative priors from the brms function, 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package (\protect\hyperlink{ref-gabry2019}{Gabry \emph{et al.} 2019}).
-
-\textbf{Plant species network roles}
-
-We investigated whether different quantitative traits determined plant species network roles using Bayesian modelling and regression trees.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies (\protect\hyperlink{ref-dormann2008}{Dormann \emph{et al.} 2008}) with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') (\protect\hyperlink{ref-bluthgen2006}{Blüthgen \emph{et al.} 2006}), which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} (\protect\hyperlink{ref-dormann2008}{Dormann \emph{et al.} 2008}).
-
-First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
-For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns' section.
-
-Second, to better understand complex trait relationships, we used regression trees.
-Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction.
-We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
-We conducted this analysis using the \emph{rpart} package (\protect\hyperlink{ref-therneau2015}{Therneau \emph{et al.} 2015}) with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package (\protect\hyperlink{ref-milborrow2015}{Milborrow 2015}) to plot the regression trees.
-We considered the species level indices as response variables (visitation rate, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
-We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (Fig.
-S4).
-
-\hypertarget{results}{%
-\section{RESULTS}\label{results}}
-
-\textbf{Plant strategies}
-
-The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of trait variation, respectively (Fig.
-1 and Fig.
-S5) and had a phylogenetic correlation (\(\lambda\)) of 0.76.
-The first principal component (PC1) represented 26.72\% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the `flower number - flower size trade-off,' as already described in previous studies (\protect\hyperlink{ref-sargent2007}{Sargent \emph{et al.} 2007}; \protect\hyperlink{ref-kettle2011}{Kettle \emph{et al.} 2011}).
-Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
-The second principal component (PC2) represented 25.05\% of the trait variation and indicated a trade-off between low and high pollinator dependence.
-We refer to this axis as the `pollinator dependence trade-off.' The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
-We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
-In contrast, species with high levels of autonomous selfing tended to have fewer and smaller flowers, had shorter styles and were shorter in height.
-Further, PC3 explained a considerable amount of trait variability (19.17\%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
-The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
-Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the `style length trade-off.' Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82\%; Fig.
-S6).
-This pPCA explained similar variance with the first two principal components (45.52\%) and similar associations of traits despite some variability in the loadings (Table S4).
-
 \begin{figure}[H]
@@
 
-We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
-2 and Table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
-S7).
-Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Fig.
-S7a and Fig.
-S7b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
-S7c and Fig.
-S7d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
-S7e and Fig.
-S7f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
-S7g and Fig.
-S7h).
-Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Fig.
-S7i and Fig.
-S7j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Fig.
-S7k and Fig.
-S7l).
-
 \blandscape
@@
 \vspace{5mm}
-
-\textbf{Phylogenetic signal}
-
-We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) in all quantitative traits (Table S5).
-The traits that showed the highest phylogenetic signal were ovule number (\(\lambda\) = 1), pollen grains per flower (\(\lambda\) = 1) and plant height (\(\lambda\) = 0.96), followed by flower length (\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73), number of flowers per plant (\(\lambda\) = 0.69) and nectar concentration (\(\lambda\) = 0.65).
-The traits that showed a moderate phylogenetic signal were inflorescence width (\(\lambda\) = 0.57), style length (\(\lambda\) = 0.49) and autonomous selfing (\(\lambda\) = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits (\(\lambda\) = 0.14).
-
-\textbf{Visitation patterns}
-
-The main axes of trait variation explained partly presence-absence of interaction partners (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the overall visitation rates (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
-However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and visitation rates (Fig.
-3).
-We found that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds (flower number - flower size trade-off, PC1; Fig.
-3a).
-However, plant species with high flower number but small flowers had higher visitation rates of bees and syrphids guilds (PC1; Fig.
-3d).
-Remarkably, all plant species with higher pollinator dependence had higher number of interacting partners and visitation rates for all floral visitor guilds (PC2; Fig.
-3b and Fig.
-3e).
-Finally, plant species with short styles and low selfing had higher interaction partners of all guilds but bees that interacted clearly more with plant species with long styles and high selfing (style length trade-off; Fig.
-3c).
-However, for visitation rate, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
-3f).
-
-The additional model for both presence-absence of interaction (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and visitation rate (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence of interaction and visitation rate for bees on PC1 (Fig.
-3a and Fig.
-3d) were driven by the family Andrenidae that had higher number of interacting partners but lower visitation rates on plant species with low number of large flowers (Fig.
-S8).
-
 \blandscape
@@
 \includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\textbf{Figure 3} Fitted posterior estimates of the presence-absence of interaction (a, b and c) and visitation rate (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
+\caption{\label{fig:unnamed-chunk-4}\textbf{Figure 3} Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
 PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.
-For visualization purposes, due to large differences between the visitation rates of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel).}
+For visualization purposes, due to large differences between number of visits of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel).}
 \end{figure}
@@
 \elandscape
-
-\textbf{Plant species network roles}
-
-The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
-S9; visitation rate \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
-Overall, the most notable trends were found on PC1 and PC3 for visitation rate and specialization.
-On the flower number - flower size trade-off (PC1), visitation rate was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
-S9a).
-On PC1, specialization showed the opposite trend (Fig.
-S9g).
-On the style length trade-off (PC3), visitation rate was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
-S9c).
-Again, specialization showed the opposite trend to visitation rate (Fig.
-S9i).
-
-When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for visitation rate was best explained by plant height, nectar concentration and style length (Fig.
-4a).
-Specifically, species taller than 3.9m had the highest visitation rate, while species that were shorter than 3.9m and had a nectar concentration lower than 16\% had the lowest visitation rate.
-Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
-4b).
-Species with a nectar concentration over 49\% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49\%, more than 21,000 pollen grains per flower and height less than 0.78m had the lowest normalized degree.
-Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
-4c).
-Overall, plant species with the highest specialization were shorter than 1.3m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11\% of their fruits.
-In contrast, species taller or equal than 5.1m and with lower than 14 ovules per flower had the lowest specialization values.
 
@@
 \caption{\label{fig:unnamed-chunk-5}\textbf{Figure 4} Contribution of traits in plant's network roles.
-Regression tree analysis of visitation rate (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
+Regression tree analysis of number of visits (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
 The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
@@
 
-\hypertarget{discussion}{%
-\section{DISCUSSION}\label{discussion}}
-
-This study demonstrates that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
-These trade-offs are differentiated along three axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-These reproductive trade-offs helped partly explain the presence of floral visitor interactions, but not their visitation rates.
-However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
-Moreover, we found that the plant species network roles were best explained by plant size and floral reward related traits.
-
-Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
-Trait variation on these two axes was associated with the `fast-slow continuum' in plant (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}) and animal (\protect\hyperlink{ref-healy2019}{Healy \emph{et al.} 2019}) life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-The `slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, plant species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie \emph{et al.} 2010}).
-The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
-S10).
-
-Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (number of interaction partners and visitation rate), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies influence plant-pollinator interactions.
-For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
-1 and Fig.
-S6).
-This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently (\protect\hyperlink{ref-hegland2005}{Hegland \& Totland 2005}; \protect\hyperlink{ref-lazaro2013}{Lázaro \emph{et al.} 2013}; \protect\hyperlink{ref-kaiser2014}{Kaiser-Bunbury \emph{et al.} 2014}).
-In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation rates across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
-For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
-3) suggesting possible niche partitioning (\protect\hyperlink{ref-palmer2003}{Palmer \emph{et al.} 2003}; \protect\hyperlink{ref-phillips2020}{Phillips \emph{et al.} 2020}) between these two guilds.
-However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species network roles (Fig.
-4).
-More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability (\protect\hyperlink{ref-vazquez2007}{Vázquez \emph{et al.} 2007}; \protect\hyperlink{ref-encinas2012}{Encinas-Viso \emph{et al.} 2012}; \protect\hyperlink{ref-bartomeus2016}{Bartomeus \emph{et al.} 2016}) that reproductive trade-offs do not.
-
-To conclude, we provide a robust description of plant reproductive trade-offs using a large global dataset of plant traits.
-We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
-Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits (\protect\hyperlink{ref-diaz2016}{Díaz \emph{et al.} 2016}; \protect\hyperlink{ref-carmona2021}{Carmona \emph{et al.} 2021}) it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez \emph{et al.} 2016}).
-Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
-Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators (\protect\hyperlink{ref-gervasi2017}{Gervasi \& Schiestl 2017}; \protect\hyperlink{ref-mackin2021}{Mackin \emph{et al.} 2021}).
-Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
-Abdi, H. \& Williams, L.J. (2010). Principal component analysis. \emph{WIREs Comp. Stats.}, 2, 433--459.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
-Ballantyne, G., Baldock, K.C.R.
-\& Willmer, P.G.
-(2015).
-Constructing more informative plant\textendash pollinator networks: Visitation and pollen deposition networks in a heathland plant community.
-\emph{Proc.
-Royal Soc.
-B}, 282, 20151130.
-
-\leavevmode\vadjust pre{\hypertarget{ref-barrett2002}{}}%
-Barrett, S.C.H. (2002). The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.}, 3, 274--284.
-
-\leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
-Barrett, S.C.H. (2003). Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond. \emph{Philos. Trans. R. Soc. Lond. B Biol. Sci.}, 358, 991--1004.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2013}{}}%
-Bartomeus, I.
-(2013).
-Understanding {Linkage Rules} in {Plant}-{Pollinator Networks} by {Using Hierarchical Models That Incorporate Pollinator Detectability} and {Plant Traits}.
-\emph{PLoS One}, 8, e69200.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
-Bartomeus, I., Gravel, D., Tylianakis, J.M., Aizen, M.A., Dickie, I.A.
-\& Bernard-Verdier, M.
-(2016).
-A common framework for identifying linkage rules across different types of interactions.
-\emph{Funct.
-Ecol.}, 30, 1894--1903.
-
-\leavevmode\vadjust pre{\hypertarget{ref-baude2016}{}}%
-Baude, M., Kunin, W.E., Boatman, N.D., Conyers, S., Davies, N., Gillespie, M.A., \emph{et al.} (2016).
-Historical nectar assessment reveals the fall and rise of floral resources in britain.
-\emph{Nature}, 530, 85--88.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
-Blüthgen, N., Menzel, F. \& Blüthgen, N. (2006). Measuring specialization in species interaction networks. \emph{BMC Ecol.}, 6, 9.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
-Bruelheide, H., Dengler, J., Purschke, O., Lenoir, J., Jiménez-Alfaro, B., Hennekens, S.M., \emph{et al.} (2018).
-Global trait--environment relationships of plant communities.
-\emph{Nat.
-Ecol.
-Evol.}, 2, 1906--1917.
-
-\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
-Bürkner, P.-C. (2017). Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.}, 80, 1--28.
-
-\leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
-Carmona, C.P., Tamme, R., Pärtel, M., Bello, F. de, Brosse, S., Capdevila, P., \emph{et al.} (2021). Erosion of global functional diversity across the tree of life. \emph{Sci. Adv.}, 7, eabf2675.
-
-\leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
-Carvalheiro, L.G., Biesmeijer, J.C., Benadi, G., Fründ, J., Stang, M., Bartomeus, I., \emph{et al.} (2014).
-The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
-\emph{Ecol.
-Lett.}, 17, 1389--1399.
-
-\leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
-Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., \emph{et al.} (2018).
-Package {`{PVR}.'} R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
-Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., \emph{et al.} (2020).
-Taxize: {Taxonomic} information from around the web.
-R package version 0.9.99.~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
-Chave, J., Coomes, D., Jansen, S., Lewis, S.L., Swenson, N.G. \& Zanne, A.E. (2009). Towards a worldwide wood economics spectrum. \emph{Ecol. Lett.}, 12, 351--366.
-
-\leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
-Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J.M. (2016). Linking species functional roles to their network roles. \emph{Ecol. Lett.}, 19, 762--770.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
-Dehling, D.M., Jordano, P., Schaefer, H.M., Böhning-Gaese, K.
-\& Schleuning, M.
-(2016).
-Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
-\emph{Proc.
-Royal Soc.
-B}, 283, 20152444.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dellinger2020}{}}%
-Dellinger, A.S. (2020). Pollination syndromes in the 21st century: Where do we stand and where may we go? \emph{New Phytol.}, 228, 1193--1213.
-
-\leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
-Devaux, C., Lepers, C. \& Porcher, E. (2014). Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems. \emph{J. Evol. Biol.}, 27, 1413--1430.
-
-\leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
-Díaz, S., Kattge, J., Cornelissen, J.H.C., Wright, I.J., Lavorel, S., Dray, S., \emph{et al.} (2016). The global spectrum of plant form and function. \emph{Nature}, 529, 167--171.
-
-\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
-Diniz-Filho, J.A.F., Bini, L.M., Rangel, T.F., Morales-Castilla, I., Olalla-Tárraga, M.Á., Rodríguez, M.Á., \emph{et al.} (2012).
-On the selection of phylogenetic eigenvectors for ecological analyses.
-\emph{Ecography}, 35, 239--249.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
-Dormann, C.F., Gruber, B. \& Fründ, J. (2008). Introducing the bipartite package: Analysing ecological networks. \emph{R News}, 8/2.
-
-\leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
-Eklöf, A., Jacob, U., Kopp, J., Bosch, J., Castro-Urgal, R., Chacoff, N.P., \emph{et al.} (2013). The dimensionality of ecological networks. \emph{Ecol. Lett.}, 16, 577--583.
-
-\leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
-Encinas-Viso, F., Revilla, T.A. \& Etienne, R.S. (2012). Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.}, 15, 198--208.
-
-\leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
-E-Vojtkó, A., Bello, F. de, Durka, W., Kühn, I. \& Götzenberger, L. (2020). The neglected importance of floral traits in trait-based plant community assembly. \emph{J. Veg. Sci.}, 31, 529--539.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fenster2004}{}}%
-Fenster, C.B., Armbruster, W.S., Wilson, P., Dudash, M.R. \& Thomson, J.D. (2004). Pollination {Syndromes} and {Floral Specialization}. \emph{Annu. Rev. Ecol. Evol. Syst.}, 35, 375--403.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
-Fortuna, M.A., Stouffer, D.B., Olesen, J.M., Jordano, P., Mouillot, D., Krasnov, B.R., \emph{et al.} (2010).
-Nestedness versus modularity in ecological networks: Two sides of the same coin?
-\emph{J.
-Anim.
-Ecol.}, 79, 811--817.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
-Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A. (2019). Visualization in {Bayesian} workflow. \emph{J. R. Stat. Soc. Ser. A Stat. Soc.}, 182, 389--402.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gervasi2017}{}}%
-Gervasi, D.D.L. \& Schiestl, F.P. (2017). Real-time divergent evolution in plants driven by pollinators. \emph{Nat. Commun.}, 8, 14691.
-
-\leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
-Goodwillie, C., Sargent, R.D., Eckert, C.G., Elle, E., Geber, M.A., Johnston, M.O., \emph{et al.} (2010).
-Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
-\emph{New Phytol.}, 185, 311--321.
-
-\leavevmode\vadjust pre{\hypertarget{ref-grossenbacher2017}{}}%
-Grossenbacher, D.L., Brandvain, Y., Auld, J.R., Burd, M., Cheptou, P.-O., Conner, J.K., \emph{et al.} (2017). Self-compatibility is over-represented on islands. \emph{New Phytol.}, 215, 469--478.
-
-\leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
-Healy, K., Ezard, T.H.G., Jones, O.R., Salguero-Gómez, R.
-\& Buckley, Y.M.
-(2019).
-Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
-\emph{Nat.
-Ecol.
-Evol.}, 3, 1217--1224.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
-Hegland, S.J. \& Totland, Ø. (2005). Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia}, 145, 586--594.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
-Hung, K.-L.J., Kingston, J.M., Albrecht, M., Holway, D.A. \& Kohn, J.R. (2018). The worldwide importance of honey bees as pollinators in natural habitats. \emph{Proc. Royal Soc. B}, 285, 20172140.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
-Ibanez, S. (2012). Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks. \emph{Oecologia}, 170, 233--242.
-
-\leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
-Jin, Y. \& Qian, H. (2019). V.{PhyloMaker}: An {R} package that can generate very large phylogenies for vascular plants. \emph{Ecography}, 42, 1353--1359.
-
-\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
-Junker, R.R., Blüthgen, N., Brehm, T., Binkenstein, J., Paulus, J., Schaefer, H.M., \emph{et al.} (2013).
-Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
-\emph{Funct.
-Ecol.}, 27, 329--341.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
-Kaiser-Bunbury, C.N., Vázquez, D.P., Stang, M. \& Ghazoul, J. (2014). Determinants of the microstructure of plant\textendash pollinator networks. \emph{Ecology}, 95, 3314--3324.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
-Kattge, J., Díaz, S., Lavorel, S., Prentice, I.C., Leadley, P., Bönisch, G., \emph{et al.} (2011). {TRY} \textendash{} a global database of plant traits. \emph{Glob. Chang. Biol.}, 17, 2905--2935.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
-Kettle, C.J., Maycock, C.R., Ghazoul, J., Hollingsworth, P.M., Khoo, E., Sukri, R.S.H., \emph{et al.} (2011).
-Ecological {Implications} of a {Flower Size}/{Number Trade}-{Off} in {Tropical Forest Trees}.
-\emph{PLoS One}, 6, e16111.
-
-\leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
-Laughlin, D.C., Mommer, L., Sabatini, F.M., Bruelheide, H., Kuyper, T.W., McCormack, M.L., \emph{et al.} (2021).
-Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
-\emph{Nat.
-Ecol.
-Evol.}, 1--12.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
-Lázaro, A., Jakobsson, A. \& Totland, Ø. (2013). How do pollinator visitation rate and seed set relate to species' floral traits and community context? \emph{Oecologia}, 173, 881--893.
-
-\leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
-Legendre, P. \& Legendre, L. (2012). \emph{Numerical ecology}. {2nd edn}. {Elsevier, Amsterdam}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-mackin2021}{}}%
-Mackin, C.R., Peña, J.F., Blanco, M.A., Balfour, N.J. \& Castellanos, M.C. (2021). Rapid evolution of a floral trait following acquisition of novel pollinators. \emph{J. Ecol.}, 109, 2234--2246.
-
-\leavevmode\vadjust pre{\hypertarget{ref-milborrow2015}{}}%
-Milborrow, S.
-(2015).
-Rpart.
-Plot: {Plot} rpart {Models}.
-{An Enhanced Version} of plot.
-Rpart.
-R package version 3.0.9.~At \href{https://CRAN.R-project.org/package=rpart.plot}{https://CRAN.r-project.org/package=rpart.plot}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
-Moeller, D.A., Runquist, R.D.B., Moe, A.M., Geber, M.A., Goodwillie, C., Cheptou, P.-O., \emph{et al.} (2017).
-Global biogeography of mating system variation in seed plants.
-\emph{Ecol.
-Lett.}, 20, 375--384.
-
-\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
-Munoz, F., Violle, C.
-\& Cheptou, P.-O.
-(2016).
-{CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
-\emph{Oikos}, 125, 1296--1303.
-
-\leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
-Olesen, J.M., Bascompte, J., Dupont, Y.L. \& Jordano, P. (2007). The modularity of pollination networks. \emph{PNAS}, 104, 19891--19896.
-
-\leavevmode\vadjust pre{\hypertarget{ref-olito2015}{}}%
-Olito, C. \& Fox, J.W. (2015). Species traits and abundances predict metrics of plant\textendash pollinator network structure, but not pairwise interactions. \emph{Oikos}, 124, 428--436.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ollerton2011}{}}%
-Ollerton, J., Winfree, R. \& Tarrant, S. (2011). How many flowering plants are pollinated by animals? \emph{Oikos}, 120, 321--326.
-
-\leavevmode\vadjust pre{\hypertarget{ref-palmer2003}{}}%
-Palmer, T.M., Stanton, M.L. \& Young, T.P. (2003). Competition and coexistence: Exploring mechanisms that restrict and maintain diversity within mutualist guilds. \emph{Am. Nat.}, 162, S63--S79.
-
-\leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
-Penone, C., Davidson, A.D., Shoemaker, K.T., Marco, M.D., Rondinini, C., Brooks, T.M., \emph{et al.} (2014).
-Imputation of missing data in life-history trait datasets: Which approach performs the best?
-\emph{Methods Ecol.
-Evol.}, 5, 961--970.
-
-\leavevmode\vadjust pre{\hypertarget{ref-phillips2020}{}}%
-Phillips, R.D., Peakall, R., van der Niet, T. \& Johnson, S.D. (2020). Niche perspectives on plant\textendash pollinator interactions. \emph{Trends Plant Sci.}, 25, 779--793.
-
-\leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
-Poisot, T., Baiser, B., Dunne, J.A., Kéfi, S., Massol, F., Mouquet, N., \emph{et al.} (2016). Mangal \textendash{} making ecological network analysis simple. \emph{Ecography}, 39, 384--390.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rech2016}{}}%
-Rech, A.R., Dalsgaard, B., Sandel, B., Sonne, J., Svenning, J.-C., Holmes, N., \emph{et al.} (2016).
-The macroecology of animal versus wind pollination: Ecological factors are more important than historical climate stability.
-\emph{Plant Ecol.
-Divers.}, 9, 253--262.
-
-\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
-Revell, L.J. (2012). Phytools: An {R} package for phylogenetic comparative biology (and other things). \emph{Methods Ecol. Evol.}, 3, 217--223.
-
-\leavevmode\vadjust pre{\hypertarget{ref-roddy2021}{}}%
-Roddy, A.B., Martínez-Perez, C., Teixido, A.L., Cornelissen, T.G., Olson, M.E., Oliveira, R.S., \emph{et al.} (2021). Towards the flower economics spectrum. \emph{New Phytol.}, 229, 665--672.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rodger2021}{}}%
-Rodger, J.G., Bennett, J.M., Razanajatovo, M., Knight, T.M., Kleunen, M.
-van, Ashman, T.-L., \emph{et al.} (2021).
-Widespread vulnerability of flowering plant seed production to pollinator declines.
-\emph{Sci.
-Adv.}, 7, eabd3524.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
-Rosas-Guerrero, V., Aguilar, R., Martén-Rodríguez, S., Ashworth, L., Lopezaraiza-Mikel, M., Bastida, J.M., \emph{et al.} (2014).
-A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
-\emph{Ecol.
-Lett.}, 17, 388--400.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rowe2020}{}}%
-Rowe, L., Gibson, D., Bahlai, C.A., Gibbs, J., Landis, D.A. \& Isaacs, R. (2020). Flower traits associated with the visitation patterns of bees. \emph{Oecologia}, 193, 511--522.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
-Rüger, N., Comita, L.S., Condit, R., Purves, D., Rosenbaum, B., Visser, M.D., \emph{et al.} (2018).
-Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
-\emph{Ecol.
-Lett.}, 21, 1075--1084.
-
-\leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
-Salguero-Gómez, R., Jones, O.R., Archer, C.R., Buckley, Y.M., Che-Castaldo, J., Caswell, H., \emph{et al.} (2015).
-The compadre {Plant Matrix Database}: An open online repository for plant demography.
-\emph{J.
-Ecol.}, 103, 202--218.
-
-\leavevmode\vadjust pre{\hypertarget{ref-salguero2016}{}}%
-Salguero-Gómez, R., Jones, O.R., Jongejans, E., Blomberg, S.P., Hodgson, D.J., Mbeau-Ache, C., \emph{et al.} (2016).
-Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
-\emph{Proc.
-Natl.
-Acad.
-Sci.
-U.S.A.}, 113, 230--235.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
-Sargent, R.D. \& Ackerly, D.D. (2008). Plant--pollinator interactions and the assembly of plant communities. \emph{Trends Ecol. Evol.}, 23, 123--130.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
-Sargent, R.D., Goodwillie, C., Kalisz, S. \& Ree, R.H. (2007). Phylogenetic evidence for a flower size and number trade-off. \emph{Am. J. Bot.}, 94, 2059--2062.
-
-\leavevmode\vadjust pre{\hypertarget{ref-schiestl2013}{}}%
-Schiestl, F.P. \& Johnson, S.D. (2013). Pollinator-mediated evolution of floral signals. \emph{Trends Ecol. Evol.}, 28, 307--315.
-
-\leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
-Smith, S.A. \& Brown, J.W. (2018). Constructing a broadly inclusive seed plant phylogeny. \emph{Am. J. Bot.}, 105, 302--314.
-
-\leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
-Stang, M., Klinkhamer, P.G.L., Waser, N.M., Stang, I.
-\& van der Meijden, E.
-(2009).
-Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
-\emph{Ann.
-Bot.}, 103, 1459--1469.
-
-\leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
-Stekhoven, D.J. \& Bühlmann, P. (2012). {MissForest}\textemdash non-parametric missing value imputation for mixed-type data. \emph{Bioinformatics}, 28, 112--118.
-
-\leavevmode\vadjust pre{\hypertarget{ref-therneau2015}{}}%
-Therneau, T., Atkinson, B., Ripley, B.
-\& Ripley, M.B.
-(2015).
-Package {`rpart.'} R package version 4.1-15.~At \href{https://CRAN.R-project.org/package=rpart}{https://CRAN.r-project.org/package=rpart}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
-Tur, C., Castro-Urgal, R. \& Traveset, A. (2013). Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}. \emph{PLoS One}, 8, e78294.
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
-Vázquez, D.P., Lomáscolo, S.B., Maldonado, M.B., Chacoff, N.P., Dorado, J., Stevani, E.L., \emph{et al.} (2012). The strength of plant\textendash pollinator interactions. \emph{Ecology}, 93, 719--725.
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
-Vázquez, D.P., Melián, C.J., Williams, N.M., Blüthgen, N., Krasnov, B.R.
-\& Poulin, R.
-(2007).
-Species abundance and asymmetric interaction strength in ecological networks.
-\emph{Oikos}, 116, 1120--1127.
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
-Vázquez, D.P., Morris, W.F. \& Jordano, P. (2005). Interaction frequency as a surrogate for the total effect of animal mutualists on plants. \emph{Ecol. Lett.}, 8, 1088--1094.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%
-Wright, I.J., Reich, P.B., Westoby, M., Ackerly, D.D., Baruch, Z., Bongers, F., \emph{et al.} (2004). The worldwide leaf economics spectrum. \emph{Nature}, 428, 821--827.
-
-\end{CSLReferences}
-
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
-
-This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-We thank all researchers that made their data openly available and sent it upon request.
-We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
-We also thank Jason Tylianakis for his comments on the manuscript before submission.
-Finally, JBL thanks the University of New England for the funding provided to carry out this work.
-
 \end{document}

### 2022-04-22 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
edits

@@
 
+Here we describe the different traits of the database used in this study to explore the reproductive spectrum of trait variation and plant-pollinator associations.
+Note that all species have references or links providing the original source of the information.
+
 _Reproductive traits_
@@
 When possible, we calculated the not found measurements with the help of online images and the software ImageJ.
-Note that for species with compound flowers (e.g., Asteraceae) or similar floral structures we considered the actual inflorescence as the floral unit and the inflorescence or group of inflorescences as the inflorescence.
-For each species this is indicated in the dataset with the field of "info_level".
-For analysis just flower and capitulum level were considered but for some Asteraceae species information about ray and disc florets were also annotated.
+Note that for species with compound flowers (e.g., Asteraceae) or similar floral structures with flower heads with many small flowers we considered the inflorescence as the floral unit.
+For each species this is indicated in the dataset with the field of "info_level" where the measurement level is specified as capitulum or flower level.
+Note that for some Asteraceae species information about the disc and ray floret is also provided in the database but these were not included in our analyses.
 
@@
 This was done exclusively for well documented nectarless taxonomical groups.
-For analysis, we considered exclusively microlitres of nectar measured in a given moment of time which was generally associated with the peak of nectar production.
+For the field of microlitres of nectar, we considered single measurements of nectar standing crop.
+In general terms, the timming of the measurement and methodology differed across studies.
+For instance, some studies measured nectar in freshly opened flowers while others in flowers that were bagged for 24 hours.
+Despite the different methodologies to measure nectar provision, we believe that this is an interesting field that allows the macroecological exploration of this important floral reward in relation with the rest of reproductive traits at a global scale.
 

### 2022-04-23 Manuscript/Lanuza_et_al_2021.Rmd
More edits on main text

@@
 
+We first investigated how the different groups of floral visitors interacted along the main axes of trait variation (see below ‘visitation patterns’ section).
+This was done for the binary version of the networks that assumes equal weight across interactions and for the weighted version with the number of visits of floral visitors to individual flowers that account for the intensity of the interaction.
+Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency [@ballantyne2015], the number of visits can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
+Second, we investigated how the main axes of trait variation and individual traits influence plant species’ roles within networks using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below ‘plant species network roles’ section).
+
 Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-These networks were analysed in their qualitative and quantitative form.
-First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
-Second, we analysed the untransformed weighted networks with the number of visits of floral visitors to individual flowers that account for the intensity of the interaction.
-Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency [@ballantyne2015], the number of visits can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
 In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.

### 2022-04-27 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
minor edit on supp mat

@@
 For instance, some studies measured nectar in freshly opened flowers while others in flowers that were bagged for 24 hours.
-Despite the different methodologies to measure nectar provision, we believe that this is an interesting field that allows the macroecological exploration of this important floral reward in relation with the rest of reproductive traits at a global scale.
+Despite the different methodologies to measure nectar provision, we believe that this is an appropriate way to collate measurements of nectar to explore trait associations at a macroecological scale.
 

### 2022-05-11 Manuscript/Lanuza_et_al_2021.Rmd
keep from here

@@
 ---
-title: \singlespacing \vspace{-1.6cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors
+title: \singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors
 
@@
 However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [@salguero2016].
-Despite the recent advances in the theoretical understanding of the major floral trade-offs [e.g., floral economic spectrum; @roddy2021], we lack empirical evidence that helps to elucidate the spectrum of reproductive trait variation at a global scale as done recently for other vegetative and physiological traits [@diaz2016; @onoda2017].
-
-Although there is an increasing number of macroecological studies that investigate plant reproductive traits [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017], we still have poor understanding of how reproductive traits drive interactions with pollinators at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
-Because the species' morphology can determine the species' functional role, by linking the plant's position in the reproductive trait-space with the different pollinator groups [as done similarly in @dehling2016], we could help to improve our understanding of plant-pollinator associations.
-Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
-However, plant reproductive traits have been overlooked for most pollination systems [@dellinger2020] and remains unclear how specific plant reproductive biology traits (i.e., mating or compatibility system) influence plant-pollinator associations [@tur2013; @devaux2014].
+Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@friedman2020; @roddy2021], their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
+Thus, in order to progress towards a comprehensive understanding of the reproductive spectrum of trait variation as done recently for other vegetative and physiological plant traits [@wright2004; @chave2009; @diaz2016; @onoda2017; @laughlin2021], there is a need to acquire a multitrait perspective with broad geographical coverage that allows elucidating the reproductive spectrum of trait variation of flowering plants.
+
+Although there is an increasing number of macroecological studies that investigate plant reproductive traits [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017], we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
+The use of
+trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
+Interestingly, because the species' morphology can determine the species' functional role,
+
+because the species' morphology can determine the species' functional role, by linking the plant's position in the reproductive trait-space with the different floral visitor groups [as done in @dehling2016], we can investigate how the different reproductive trait correlations from the reproductive spectrum associate with the distinct floral visitor groups.
+However, plant reproductive traits remain overlooked for a great number of plant species [@dellinger2020] and is still unclear how specific reproductive traits like mating or compatibility system influence plant-pollinator associations [@tur2013; @devaux2014].
 

### 2022-05-11 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
keep from here

@@
 ---
-#title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant reproductive traits determine interactions with floral visitors}
+#title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Covariation among reproductive traits in flowering plants determine interactions with floral visitors}
 
@@
 
-## Trade-offs among plant reproductive traits determine interactions with floral visitors
+## Covariation among reproductive traits in flowering plants determine interactions with floral visitors
 

### 2022-05-12 Manuscript/Lanuza_et_al_2021.Rmd
Update on intro

@@
 Although there is an increasing number of macroecological studies that investigate plant reproductive traits [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017], we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
-The use of
-trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-Interestingly, because the species' morphology can determine the species' functional role,
-
-because the species' morphology can determine the species' functional role, by linking the plant's position in the reproductive trait-space with the different floral visitor groups [as done in @dehling2016], we can investigate how the different reproductive trait correlations from the reproductive spectrum associate with the distinct floral visitor groups.
-However, plant reproductive traits remain overlooked for a great number of plant species [@dellinger2020] and is still unclear how specific reproductive traits like mating or compatibility system influence plant-pollinator associations [@tur2013; @devaux2014].
-
-Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
+In addition, the pollination system of a great number of plant species remains unexplored and is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations [@tur2013; @devaux2014].
+Interestingly, the use of trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
+Because the species' morphology can determine the species' functional role, an interesting novel approach to investigate plant-pollinator interactions is to examine how traits in the multidimensional trait space determine species interaction patterns [see @dehling2016].
+Thus, by defining the reproductive spectrum of trait variation is possible to investigate how the different reproductive strategies are associated worldwide with the interaction patterns of the different floral visitors.
+
+[Keep from here](Jose)
+
 With the recent availability of large trait databases [e.g., TRY @kattge2011; and COMPADRE @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
-However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
+However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with floral visitors and ultimately determine plant reproductive success.
+
 For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively, [@barrett2003; @moeller2017] and outcrossing levels are positively correlated with flower size [@goodwillie2010].

### 2022-05-12 Manuscript/Lanuza_et_al_2021.Rmd
edits

@@
 Interestingly, the use of trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-Because the species' morphology can determine the species' functional role, an interesting novel approach to investigate plant-pollinator interactions is to examine how traits in the multidimensional trait space determine species interaction patterns [see @dehling2016].
-Thus, by defining the reproductive spectrum of trait variation is possible to investigate how the different reproductive strategies are associated worldwide with the interaction patterns of the different floral visitors.
-
-[Keep from here](Jose)
+Because the species' morphology can determine the species' functional role in the pollination network, an interesting novel approach to investigate plant-pollinator interactions is to examine how traits in the multidimensional trait space determine species interaction patterns [see @dehling2016].
+Thus, by defining the reproductive spectrum of trait variation is possible to investigate how the different plant reproductive strategies are associated with the interaction patterns of the different floral visitors.
+
+[Keep from here but remember to read again all coments, just in case I'm mssing something important](Jose)
 

### 2022-05-13 Manuscript/Lanuza_et_al_2021.Rmd
keep from here

@@
 Because the species' morphology can determine the species' functional role in the pollination network, an interesting novel approach to investigate plant-pollinator interactions is to examine how traits in the multidimensional trait space determine species interaction patterns [see @dehling2016].
-Thus, by defining the reproductive spectrum of trait variation is possible to investigate how the different plant reproductive strategies are associated with the interaction patterns of the different floral visitors.
-
-[Keep from here but remember to read again all coments, just in case I'm mssing something important](Jose)
+Thus, by defining the reproductive spectrum of trait variation is possible to investigate how the different plant reproductive strategies are associated with the interaction patterns of the different floral visitors at global scale.
 
 With the recent availability of large trait databases [e.g., TRY @kattge2011; and COMPADRE @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
-However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with floral visitors and ultimately determine plant reproductive success.
+However, most studies have focused on trait correlations of vegetative and physiological traits from the leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] related traits with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are also critical to plant life strategies as they shape interactions with floral visitors and ultimately impact plant reproductive success.
 

### 2022-05-21 Manuscript/Lanuza_et_al_2021.tex
intro update

@@
 ]{article}
-\title{\singlespacing \vspace{-1.6cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors}
-\author{}
-\date{\vspace{-2.5em}}
-
 \usepackage{amsmath,amssymb}
@@
 \hypersetup{
-  pdftitle={ Trade-offs among plant reproductive traits determine interactions with floral visitors},
+  pdftitle={ Covariation among reproductive traits in flowering plants determine interactions with floral visitors},
   colorlinks=true,
@@
 
+\title{\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors}
+\author{}
+\date{\vspace{-2.5em}}
+
 \begin{document}
@@
 Flowering plants have an astonishing diversity of floral structures (\protect\hyperlink{ref-barrett2002}{Barrett, 2002}; \protect\hyperlink{ref-schiestl2013}{Schiestl \& Johnson, 2013}) that shape plant-pollinator associations (\protect\hyperlink{ref-dellinger2020}{Dellinger, 2020}; \protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}).
-However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
-Despite the recent advances in the theoretical understanding of the major floral trade-offs {[}e.g., floral economic spectrum; \protect\hyperlink{ref-roddy2021}{Roddy et al.} (\protect\hyperlink{ref-roddy2021}{2021}){]}, we lack empirical evidence that helps to elucidate the spectrum of reproductive trait variation at a global scale as done recently for other vegetative and physiological traits (\protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}; \protect\hyperlink{ref-onoda2017}{Onoda et al., 2017}).
-
-Although there is an increasing number of macroecological studies that investigate plant reproductive traits (\protect\hyperlink{ref-baude2016}{Baude et al., 2016}; \protect\hyperlink{ref-grossenbacher2017}{Grossenbacher et al., 2017}; \protect\hyperlink{ref-moeller2017}{Moeller et al., 2017}; \protect\hyperlink{ref-munoz2016}{Munoz et al., 2016}), we still have poor understanding of how reproductive traits drive interactions with pollinators at large scales (\protect\hyperlink{ref-rech2016}{Rech et al., 2016}; \protect\hyperlink{ref-ruger2018}{Rüger et al., 2018}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}; \protect\hyperlink{ref-sargent2008}{Sargent \& Ackerly, 2008}).
-Because the species' morphology can determine the species' functional role, by linking the plant's position in the reproductive trait-space with the different pollinator groups (as done similarly in \protect\hyperlink{ref-dehling2016}{Dehling et al., 2016}), we could help to improve our understanding of plant-pollinator associations.
-Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches (\protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero et al., 2014}) and trait-matching analyses (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}).
-However, plant reproductive traits have been overlooked for most pollination systems (\protect\hyperlink{ref-dellinger2020}{Dellinger, 2020}) and remains unclear how specific plant reproductive biology traits (i.e., mating or compatibility system) influence plant-pollinator associations (\protect\hyperlink{ref-devaux2014}{Devaux et al., 2014}; \protect\hyperlink{ref-tur2013}{Tur et al., 2013}).
-
-Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
+However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints (\protect\hyperlink{ref-stearns1989}{Stearns, 1989}).
+Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}), their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
+Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other vegetative and physiological plant traits (\protect\hyperlink{ref-chave2009}{Chave et al., 2009}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}; \protect\hyperlink{ref-laughlin2021}{Laughlin et al., 2021}; \protect\hyperlink{ref-onoda2017}{Onoda et al., 2017}; \protect\hyperlink{ref-wright2004}{Wright et al., 2004}), there is a need to acquire a multitrait perspective with broad geographical coverage.
+Importantly, the characterization of the reproductive trait covariation patterns can help to further understand the different plant ecological strategies (\protect\hyperlink{ref-agrawal2020}{Agrawal, 2020}) and improve our knowledge on plant-pollinator associations (\protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}).
+
+Although there is an increasing number of macroecological studies that investigate plant reproductive traits (\protect\hyperlink{ref-baude2016}{Baude et al., 2016}; \protect\hyperlink{ref-grossenbacher2017}{Grossenbacher et al., 2017}; \protect\hyperlink{ref-moeller2017}{Moeller et al., 2017}; \protect\hyperlink{ref-munoz2016}{Munoz et al., 2016}), we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales (\protect\hyperlink{ref-rech2016}{Rech et al., 2016}; \protect\hyperlink{ref-ruger2018}{Rüger et al., 2018}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}; \protect\hyperlink{ref-sargent2008}{Sargent \& Ackerly, 2008}).
+In addition, the pollination system of a great number of plant species remains unexplored and is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations (\protect\hyperlink{ref-devaux2014}{Devaux et al., 2014}; \protect\hyperlink{ref-tur2013}{Tur et al., 2013}).
+Interestingly, the use of trait-based approaches (\protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero et al., 2014}) and trait-matching analyses (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}) has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
+For example, plant traits can define species' network roles {[}e.g., specialists vs generalists; Lázaro et al.
+(\protect\hyperlink{ref-lazaro2013}{2013}); Tur et al.
+(\protect\hyperlink{ref-tur2013}{2013}){]} and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators (\protect\hyperlink{ref-coux2016}{Coux et al., 2016}; \protect\hyperlink{ref-junker2013}{Junker et al., 2013}).
+Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure (\protect\hyperlink{ref-ibanez2012}{Ibanez, 2012}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}).
+Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network interactions (\protect\hyperlink{ref-eklof2013}{Eklöf et al., 2013}), an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns (see \protect\hyperlink{ref-dehling2016}{Dehling et al., 2016}).
+Thus, by exploring the reproductive spectrum of trait variation is possible to delimit the different plant reproductive strategies and explore how these are associated with the interaction patterns of the different floral visitors.
+
 With the recent availability of large trait databases (e.g., TRY \protect\hyperlink{ref-kattge2011}{Kattge et al., 2011}; and COMPADRE \protect\hyperlink{ref-salguero2015}{Salguero-Gómez et al., 2015}), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function (\protect\hyperlink{ref-bruelheide2018}{Bruelheide et al., 2018}; \protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
-However, most studies have focused on vegetative traits such as leaf (\protect\hyperlink{ref-wright2004}{Wright et al., 2004}), wood (\protect\hyperlink{ref-chave2009}{Chave et al., 2009}), or root (\protect\hyperlink{ref-laughlin2021}{Laughlin et al., 2021}) trade-offs with little or no attention given to reproductive traits (\protect\hyperlink{ref-evojtko2020}{E-Vojtkó et al., 2020}; \protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}) which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively, (\protect\hyperlink{ref-barrett2003}{Barrett, 2003}; \protect\hyperlink{ref-moeller2017}{Moeller et al., 2017}) and outcrossing levels are positively correlated with flower size (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}).
-In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species' reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators (\protect\hyperlink{ref-ollerton2011}{Ollerton et al., 2011}; \protect\hyperlink{ref-rodger2021}{Rodger et al., 2021}).
-However, it is still unknown to what extent these different reproductive strategies determine plant-pollinator interactions.
-
-Several studies have identified links between plant traits and plant-pollinator network properties (\protect\hyperlink{ref-bartomeus2013}{Bartomeus, 2013}; \protect\hyperlink{ref-olito2015}{Olito \& Fox, 2015}; \protect\hyperlink{ref-rowe2020}{Rowe et al., 2020}).
-Moreover, plant traits can define species' network roles (e.g., specialists vs generalists; \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}; \protect\hyperlink{ref-tur2013}{Tur et al., 2013}).
-For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators (\protect\hyperlink{ref-coux2016}{Coux et al., 2016}; \protect\hyperlink{ref-junker2013}{Junker et al., 2013}).
-Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure (\protect\hyperlink{ref-ibanez2012}{Ibanez, 2012}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}).
-Importantly, the combination of traits has shown to increase the predictive power of the network interactions (\protect\hyperlink{ref-eklof2013}{Eklöf et al., 2013}) and by considering the position in the multidimensional trait space we can determine species' roles within plant-pollinator interaction networks (\protect\hyperlink{ref-dehling2016}{Dehling et al., 2016}).
-Nonetheless, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.
-
-Here, we aim to explore the potential trade-offs among plant reproductive traits and their association with the different floral visitor guilds.
-First, we identify the major axes of reproductive trait variation and trade-offs that determine plant form and function.
-Second, we investigate the association between the plant species' position in trait-space and the different floral visitor guilds with the help of qualitative (presence-absence of interaction) and quantitative (number of visits) information.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' roles within networks using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
+However, most studies with a multitrait perspective have focused on trait correlations from the leaf (\protect\hyperlink{ref-wright2004}{Wright et al., 2004}), wood (\protect\hyperlink{ref-chave2009}{Chave et al., 2009}), or root (\protect\hyperlink{ref-laughlin2021}{Laughlin et al., 2021}) related traits with little or no attention given to reproductive traits (\protect\hyperlink{ref-evojtko2020}{E-Vojtkó et al., 2020}; \protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}).
+Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}), the positive association between flower size and outcrossing rate (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}) or the association between outcrossing rate and lifespan where short lived versus perennial species tend to have low versus high levels of outcrossing (\protect\hyperlink{ref-barrett2003}{Barrett, 2003}; \protect\hyperlink{ref-moeller2017}{Moeller et al., 2017}), respectively.
+Although these different trait associations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships (\protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}), we still lack empirical evidence that investigates jointly these different reproductive trait associations.
+
+Here, we aim to progress knowledge on the reproductive trait covariation patterns and their association with the different floral visitor guilds by exploring at a broad geographical scale the reproductive trait associations of entomophilous plant species from plant-pollination networks.
+First, we investigate what are the major axes of reproductive trait variation for the different plant species.
+Second, we investigate the association between the plant species' position in the multidimensional trait-space and the different floral visitor guilds with the help of qualitative (presence-absence of interaction) and quantitative (number of visits) information about plant-pollinator interactions.
+Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' functional role in the pollination network using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
 
@@
 
+We first investigated how the different groups of floral visitors interacted along the main axes of trait variation (see below `visitation patterns' section).
+This was done for the binary version of the networks that assumes equal weight across interactions and for the weighted version with the number of visits of floral visitors to individual flowers that account for the intensity of the interaction.
+Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency (\protect\hyperlink{ref-ballantyne2015}{Ballantyne et al., 2015}), the number of visits can provide valuable information of the contribution of floral visitors to pollination (\protect\hyperlink{ref-vazquez2005}{Vázquez et al., 2005}, \protect\hyperlink{ref-vazquez2012}{2012}).
+Second, we investigated how the main axes of trait variation and individual traits influence plant species' roles within networks using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below `plant species network roles' section).
+
 Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-These networks were analysed in their qualitative and quantitative form.
-First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
-Second, we analysed the untransformed weighted networks with the number of visits of floral visitors to individual flowers that account for the intensity of the interaction.
-Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency (\protect\hyperlink{ref-ballantyne2015}{Ballantyne et al., 2015}), the number of visits can provide valuable information of the contribution of floral visitors to pollination (\protect\hyperlink{ref-vazquez2005}{Vázquez et al., 2005}, \protect\hyperlink{ref-vazquez2012}{2012}).
 In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
@@
 The first principal component (PC1) represented 26.72\% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the `flower number - flower size trade-off,' as already described in previous studies (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}).
+We refer to this axis as the `flower number - flower size trade-off', as already described in previous studies (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}).
 Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
@@
 The second principal component (PC2) represented 25.05\% of the trait variation and indicated a trade-off between low and high pollinator dependence.
-We refer to this axis as the `pollinator dependence trade-off.' The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
+We refer to this axis as the `pollinator dependence trade-off'.
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
 We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
@@
 The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
-Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the `style length trade-off.' Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82\%; Fig.
+Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the `style length trade-off'.
+Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82\%; Fig.
 S7).
@@
 When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for number of visits was best explained by plant height, nectar concentration and style length (Fig.
-4a).
+4a; root node error = 1\%).
 Specifically, species taller than 3.9m had the highest number of visits, while species that were shorter than 3.9m and had a nectar concentration lower than 16\% had the lowest number of visits.
 Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
-4b).
+4b; root node error = 2\%).
 Species with a nectar concentration over 49\% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49\%, more than 21,000 pollen grains per flower and height less than 0.78m had the lowest normalized degree.
 Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
-4c).
+4c; root node error = 7\%).
 Overall, plant species with the highest specialization were shorter than 1.3m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11\% of their fruits.
@@
 Abdi, H., \& Williams, L. J. (2010). Principal component analysis. \emph{WIREs Comp. Stats.}, \emph{2}(4), 433--459. \url{https://doi.org/10.1002/wics.101}
+
+\leavevmode\vadjust pre{\hypertarget{ref-agrawal2020}{}}%
+Agrawal, A. A. (2020). A scale-dependent framework for trade-offs, syndromes, and specialization in organismal biology. \emph{Ecology}, \emph{101}(2), e02924.
 
@@
 \url{https://doi.org/10.1098/rstb.2003.1301}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2013}{}}%
-Bartomeus, I.
-(2013).
-Understanding {Linkage Rules} in {Plant}-{Pollinator Networks} by {Using Hierarchical Models That Incorporate Pollinator Detectability} and {Plant Traits}.
-\emph{PLoS One}, \emph{8}(7), e69200.
-\url{https://doi.org/10.1371/journal.pone.0069200}
 
@@
 (2018).
-\emph{Package {`{PVR}.'} R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}}.
+\emph{Package {``{PVR}.''} R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}}.
 
@@
 \url{https://doi.org/10.1111/j.1365-2656.2010.01688.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-friedman2020}{}}%
+Friedman, J.
+(2020).
+The evolution of annual and perennial plant life histories: Ecological correlates and genetic mechanisms.
+\emph{Annual Review of Ecology, Evolution, and Systematics}, \emph{51}, 461--481.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-olito2015}{}}%
-Olito, C., \& Fox, J.
-W.
-(2015).
-Species traits and abundances predict metrics of plant\textendash pollinator network structure, but not pairwise interactions.
-\emph{Oikos}, \emph{124}(4), 428--436.
-\url{https://doi.org/10.1111/oik.01439}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ollerton2011}{}}%
-Ollerton, J., Winfree, R., \& Tarrant, S. (2011). How many flowering plants are pollinated by animals? \emph{Oikos}, \emph{120}(3), 321--326.
-
 \leavevmode\vadjust pre{\hypertarget{ref-onoda2017}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-rodger2021}{}}%
-Rodger, J.
-G., Bennett, J.
-M., Razanajatovo, M., Knight, T.
-M., Kleunen, M.
-van, Ashman, T.-L., Steets, J.
-A., Hui, C., Arceo-Gómez, G., Burd, M.others.
-(2021).
-Widespread vulnerability of flowering plant seed production to pollinator declines.
-\emph{Sci.
-Adv.}, \emph{7}(42), eabd3524.
-
 \leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
@@
 Lett.}, \emph{17}(3), 388--400.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rowe2020}{}}%
-Rowe, L., Gibson, D., Bahlai, C.
-A., Gibbs, J., Landis, D.
-A., \& Isaacs, R.
-(2020).
-Flower traits associated with the visitation patterns of bees.
-\emph{Oecologia}, \emph{193}(2), 511--522.
-\url{https://doi.org/10.1007/s00442-020-04674-0}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-stearns1989}{}}%
+Stearns, S. C. (1989). Trade-offs in life-history evolution. \emph{Functional Ecology}, \emph{3}(3), 259--268.
+
 \leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
@@
 (2015).
-\emph{Package {`rpart.'} R package version 4.1-15.~At \href{https://CRAN.R-project.org/package=rpart}{https://CRAN.r-project.org/package=rpart}}.
+\emph{Package {``rpart.''} R package version 4.1-15.~At \href{https://CRAN.R-project.org/package=rpart}{https://CRAN.r-project.org/package=rpart}}.
 
@@
 
-\vspace*{-28mm}
+\vspace{-28mm}
 

### 2022-05-21 Manuscript/Lanuza_et_al_2021.Rmd
edits intro

--- 2022-05-12 Manuscript/Lanuza_et_al_2021.Rmd
@@
 - \DeclareUnicodeCharacter{1EF3}{*************************************}
-
 ---
@@
 \textbf{Jose B.
-Lanuza$^{1,2}$} <barragansljose@gmail.com>, \textbf{Romina Rader$^{1}$} <rrader@une.edu.au>, \textbf{Jamie Stavert$^{3}$} <jamie.stavert@gmail.com>, \textbf{Liam K.
-Kendall$^{4}$} <liam.k.kendall@gmail.com>, \textbf{Manu E.
-Saunders$^{1}$} <Manu.Saunders@une.edu.au> \textbf{and Ignasi Bartomeus$^{2}$} <nacho.bartomeus@gmail.com>
+Lanuza$^{1,2}$} [barragansljose\@gmail.com](mailto:barragansljose@gmail.com){.email}, \textbf{Romina Rader$^{1}$} [rrader\@une.edu.au](mailto:rrader@une.edu.au){.email}, \textbf{Jamie Stavert$^{3}$} [jamie.stavert\@gmail.com](mailto:jamie.stavert@gmail.com){.email}, \textbf{Liam K.
+Kendall$^{4}$} [liam.k.kendall\@gmail.com](mailto:liam.k.kendall@gmail.com){.email}, \textbf{Manu E.
+Saunders$^{1}$} [Manu.Saunders\@une.edu.au](mailto:Manu.Saunders@une.edu.au){.email} \textbf{and Ignasi Bartomeus$^{2}$} [nacho.bartomeus\@gmail.com](mailto:nacho.bartomeus@gmail.com){.email}
 
@@
 ^2^ Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-^3^ Department of Conservation | Te Papa Atawhai, Auckland, New Zealand.
+^3^ Department of Conservation \| Te Papa Atawhai, Auckland, New Zealand.
 ^4^ Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden.
 
+```{=tex}
 \doublespacing
 \normalsize
-
+```
 \textbf{Statement of authorship:} JBL, RR and IB designed the study.
@@
 
-\textbf{Keywords:} life-history strategies | plant reproductive trade-offs | plant-pollinator interactions.
+\textbf{Keywords:} life-history strategies \| plant reproductive trade-offs \| plant-pollinator interactions.
 
@@
 
-\textbf{Corresponding author:} Jose B. Lanuza | +34 616375981| <barragansljose@gmail.com>
+\textbf{Corresponding author:} Jose B. Lanuza \| +34 616375981\| [barragansljose\@gmail.com](mailto:barragansljose@gmail.com){.email}
 
@@
 
+```{=tex}
 \doublespacing
@@
 \normalsize
-
+```
 ```{r setup, include=FALSE, cache=FALSE, message = FALSE}
@@
 Flowering plants have an astonishing diversity of floral structures [@barrett2002; @schiestl2013] that shape plant-pollinator associations [@fenster2004; @dellinger2020].
-However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [@salguero2016].
-Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@friedman2020; @roddy2021], their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
-Thus, in order to progress towards a comprehensive understanding of the reproductive spectrum of trait variation as done recently for other vegetative and physiological plant traits [@wright2004; @chave2009; @diaz2016; @onoda2017; @laughlin2021], there is a need to acquire a multitrait perspective with broad geographical coverage that allows elucidating the reproductive spectrum of trait variation of flowering plants.
+However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [@stearns1989].
+Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@salguero2016; @friedman2020; @roddy2021], their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
+Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other vegetative and physiological plant traits [@wright2004; @chave2009; @diaz2016; @onoda2017; @laughlin2021], there is a need to acquire a multitrait perspective with broad geographical coverage.
+Importantly, the characterization of the reproductive trait covariation patterns can help to further understand the different plant ecological strategies [@agrawal2020] and improve our knowledge on plant-pollinator associations [@roddy2021].
 
@@
 Interestingly, the use of trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-Because the species' morphology can determine the species' functional role, an interesting novel approach to investigate plant-pollinator interactions is to examine how traits in the multidimensional trait space determine species interaction patterns [see @dehling2016].
-Thus, by defining the reproductive spectrum of trait variation is possible to investigate how the different reproductive strategies are associated worldwide with the interaction patterns of the different floral visitors.
-
-[Keep from here](Jose)
+For example, plant traits can define species' network roles [e.g., specialists vs generalists; @lazaro2013; @tur2013] and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
+Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
+Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network interactions [@eklof2013], an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns [see @dehling2016].
+Thus, by exploring the reproductive spectrum of trait variation is possible to delimit the different plant reproductive strategies and explore how these are associated with the interaction patterns of the different floral visitors.
 
 With the recent availability of large trait databases [e.g., TRY @kattge2011; and COMPADRE @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
-However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with floral visitors and ultimately determine plant reproductive success.
-
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively, [@barrett2003; @moeller2017] and outcrossing levels are positively correlated with flower size [@goodwillie2010].
-In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators [@ollerton2011; @rodger2021].
-However, it is still unknown to what extent these different reproductive strategies determine plant-pollinator interactions.
-
-Several studies have identified links between plant traits and plant-pollinator network properties [@bartomeus2013; @olito2015; @rowe2020].
-Moreover, plant traits can define species’ network roles [e.g., specialists vs generalists\; @lazaro2013; @tur2013].
-For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
-Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
-Importantly, the combination of traits has shown to increase the predictive power of the network interactions [@eklof2013] and by considering the position in the multidimensional trait space we can determine species’ roles within plant-pollinator interaction networks [@dehling2016].
-Nonetheless, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.
-
-Here, we aim to explore the potential trade-offs among plant reproductive traits and their association with the different floral visitor guilds.
-First, we identify the major axes of reproductive trait variation and trade-offs that determine plant form and function.
-Second, we investigate the association between the plant species’ position in trait-space and the different floral visitor guilds with the help of qualitative (presence-absence of interaction) and quantitative (number of visits) information.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species’ roles within networks using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
+However, most studies with a multitrait perspective have focused on trait correlations from the leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] related traits with little or no attention given to reproductive traits [@evojtko2020; @roddy2021].
+Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number [@sargent2007; @kettle2011], the positive association between flower size and outcrossing rate [@goodwillie2010] or the association between outcrossing rate and lifespan where short lived versus perennial species tend to have low versus high levels of outcrossing [@barrett2003; @moeller2017], respectively.
+Although these different trait associations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships [@roddy2021], we still lack empirical evidence that investigates jointly these different reproductive trait associations.
+
+Here, we aim to progress knowledge on the reproductive trait covariation patterns and their association with the different floral visitor guilds by exploring at a broad geographical scale the reproductive trait associations of entomophilous plant species from plant-pollination networks.
+First, we investigate what are the major axes of reproductive trait variation for the different plant species.
+Second, we investigate the association between the plant species' position in the multidimensional trait-space and the different floral visitor guilds with the help of qualitative (presence-absence of interaction) and quantitative (number of visits) information about plant-pollinator interactions.
+Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' functional role in the pollination network using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
 
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies [e.g.,\ @carvalheiro2014; @olesen2007; @fortuna2010] or available in online archives [e.g., The Web of Life, @fortuna2010; and Mangal, @poisot2016].
+Many of these networks are freely available either as published studies [e.g.,  @carvalheiro2014; @olesen2007; @fortuna2010] or available in online archives [e.g., The Web of Life, @fortuna2010; and Mangal, @poisot2016].
 In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
@@
 
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020].
-We filled the ‘not found’ searches manually using http://www.theplantlist.org/ and http://www.mobot.org/ for plants and http://www.catalogueoflife.org/ for floral visitors.
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (<https://www.ncbi.nlm.nih.gov/taxonomy>) for plants and ITIS (<https://www.itis.gov/>) for pollinators, using the R package *taxize* [@chamberlain2020].
+We filled the 'not found' searches manually using <http://www.theplantlist.org/> and <http://www.mobot.org/> for plants and <http://www.catalogueoflife.org/> for floral visitors.
 
@@
 
-We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package _rtrees_ (https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
+We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package *rtrees* (<https://github.com/daijiang/rtrees>), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
 
@@
 
-Trait missing values were imputed with the function _missForest_ [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of _missForest_ [@penone2014].
-To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
+Trait missing values were imputed with the function *missForest* [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of *missForest* [@penone2014].
+To extract the eigenvectors, we used the function *PVRdecomp* from the package *PVR* [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
 We conducted two different imputations, one for the full set of species (1,506 species, 5.79% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
@@
 We explored the trade-offs between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
 Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th–97.5th percentile range [@legendre2012], and thus our final dataset had 1,236 species.
+Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th--97.5th percentile range [@legendre2012], and thus our final dataset had 1,236 species.
 Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
+We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
 Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
@@
 
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package *phytools* [@revell2012] and we used Pagel's $\lambda$ as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
@@
 
-We first investigated how the different groups of floral visitors interacted along the main axes of trait variation (see below ‘visitation patterns’ section).
+We first investigated how the different groups of floral visitors interacted along the main axes of trait variation (see below 'visitation patterns' section).
 This was done for the binary version of the networks that assumes equal weight across interactions and for the weighted version with the number of visits of floral visitors to individual flowers that account for the intensity of the interaction.
 Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency [@ballantyne2015], the number of visits can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
-Second, we investigated how the main axes of trait variation and individual traits influence plant species’ roles within networks using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below ‘plant species network roles’ section).
+Second, we investigated how the main axes of trait variation and individual traits influence plant species' roles within networks using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below 'plant species network roles' section).
 
@@
 Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
-All analyses were conducted in R version _4.0.3_.
+All analyses were conducted in R version *4.0.3*.
 
@@
 Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
-This finding is consistent with previous research showing that _A.
-mellifera_ was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
-Hence, to control for the effect of _A.
-mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding _A.
-mellifera_.
-We found that _A.
-mellifera_, was partly driving some of the observed trends on PC1 (Fig.
+In addition, we found that *Apis mellifera* was the floral visitor with the largest proportion of records counted (7.55% of the total).
+This finding is consistent with previous research showing that *A.
+mellifera* was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
+Hence, to control for the effect of *A.
+mellifera* on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding *A.
+mellifera*.
+We found that *A.
+mellifera*, was partly driving some of the observed trends on PC1 (Fig.
 S4).
@@
 
-We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017].
-We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
+We implemented Bayesian generalized linear mixed models using the R package *brms* [@burkner2017].
+We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
 Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
@@
 The models were run with non or very weakly informative informative priors from the brm function so they have neglible influence on the results [@burkner2017], 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019].
+We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the *bayesplot* package [@gabry2019].
 
@@
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d’) [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008].
-
-First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric ~ PC1 + PC2 + PC3).
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the *specieslevel* function from the R package *bipartite* [@dormann2008].
+
+First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
 For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns’ section.
+Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the 'visitation patterns' section.
 
@@
 We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
-We conducted this analysis using the _rpart_ function from the _rtrees_ package [@therneau2015] with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] to plot the regression trees.
+We conducted this analysis using the *rpart* function from the *rtrees* package [@therneau2015] with method *'anova'* with a minimum of 50 observations per terminal node and we used the *rpart.plot* package [@milborrow2015] to plot the regression trees.
 We considered the species level indices as response variables (number of visits, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
@@
 The first principal component (PC1) represented 26.72% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the ‘flower number - flower size trade-off’, as already described in previous studies [@sargent2007; @kettle2011].
+We refer to this axis as the 'flower number - flower size trade-off', as already described in previous studies [@sargent2007; @kettle2011].
 Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
 The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
 The second principal component (PC2) represented 25.05% of the trait variation and indicated a trade-off between low and high pollinator dependence.
-We refer to this axis as the ‘pollinator dependence trade-off’.
+We refer to this axis as the 'pollinator dependence trade-off'.
 The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
@@
 The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
-Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the ‘style length trade-off’.
+Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the 'style length trade-off'.
 Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82%; Fig.
@@
 2 and Table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, _P_ < 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , _P_ = 0.59; PC2:  Sum of squares = 0.83, F-value = 1.43, _P_ = 0.23) showed lack of statistical association.
+Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed lack of statistical association.
 In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
@@
 
-We found a strong phylogenetic signal (*P* < 0.01) in all quantitative traits (Table S5).
+We found a strong phylogenetic signal (*P* \< 0.01) in all quantitative traits (Table S5).
 The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
@@
 The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
-S10; number of visits ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
+S10; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
 Overall, the most notable trends were found on PC1 and PC3 for number of visits and specialization.
@@
 Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
-Trait variation on these two axes was associated with the ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-The ‘slow’ part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, plant species that employed the ‘fast’ strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
+Trait variation on these two axes was associated with the 'fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+The 'slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
+In contrast, plant species that employed the 'fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
 Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
@@
 
-<div id ="refs"></div>
+::: {#refs}
+:::
 
@@
 
+```{=tex}
 \vspace{5mm}
 \blandscape
-
+```
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).

### 2022-05-23 Manuscript/Lanuza_et_al_2021.Rmd
edits methods

@@
 
-\textbf{Short title:} Plant reproductive trade-offs.
-
-\textbf{Keywords:} life-history strategies \| plant reproductive trade-offs \| plant-pollinator interactions.
+\textbf{Short title:} Covariation among plant reproductive traits.
+
+\textbf{Keywords:} life-history strategies \| plant reproductive traits \| plant-pollinator interactions.
 
@@
 Interestingly, the use of trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-For example, plant traits can define species' network roles [e.g., specialists vs generalists; @lazaro2013; @tur2013] and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
+For example, plant traits can define species' network roles [e.g., specialists vs generalists;\ @lazaro2013; @tur2013] and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
 Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
 Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network interactions [@eklof2013], an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns [see @dehling2016].
-Thus, by exploring the reproductive spectrum of trait variation is possible to delimit the different plant reproductive strategies and explore how these are associated with the interaction patterns of the different floral visitors.
+Thus, by exploring the reproductive spectrum of trait variation is possible to delimit the different plant reproductive strategies and explore how these are associated with the different floral visitors.
 
@@
 Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number [@sargent2007; @kettle2011], the positive association between flower size and outcrossing rate [@goodwillie2010] or the association between outcrossing rate and lifespan where short lived versus perennial species tend to have low versus high levels of outcrossing [@barrett2003; @moeller2017], respectively.
-Although these different trait associations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships [@roddy2021], we still lack empirical evidence that investigates jointly these different reproductive trait associations.
-
-Here, we aim to progress knowledge on the reproductive trait covariation patterns and their association with the different floral visitor guilds by exploring at a broad geographical scale the reproductive trait associations of entomophilous plant species from plant-pollination networks.
-First, we investigate what are the major axes of reproductive trait variation for the different plant species.
+Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships [@roddy2021], we still lack empirical evidence that investigates jointly these different reproductive trait associations.
+
+Here, we aim to progress knowledge on the reproductive trait covariation patterns and their association with the different floral visitor guilds by exploring at a broad geographical scale the reproductive spectrum of trait variation of entomophilous plant species from plant-pollination networks.
+First, we investigate what are the major axes of reproductive trait variation and trait correlations for the different plant species.
 Second, we investigate the association between the plant species' position in the multidimensional trait-space and the different floral visitor guilds with the help of qualitative (presence-absence of interaction) and quantitative (number of visits) information about plant-pollinator interactions.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' functional role in the pollination network using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
+Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
 
@@
 S1).
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
+These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different biological communities.
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
@@
 
-We selected a total of 19 different functional traits that included both reproductive and vegetative traits (see Table 1 and Supplementary Information).
-From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
-The 3 remaining traits, were vegetative traits that are commonly used to characterize the global spectrum of plant form and function and represent the fast-slow continuum of trait variation (e.g., short-lived versus perennial species).
-For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Fig.
+We selected a total of 19 different functional traits that comprised both reproductive and life history traits (see Table 1).
+From these, 16 were reproductive traits that consisted of 13 floral traits and 3 reproductive biology traits.
+Floral traits included morphological traits (e.g., style length) but also floral reward (e.g., pollen quantity) and floral display (e.g., number of flowers) related traits.
+Reproductive biology traits indicated the reproductive system of the plant and included breeding, mating and compatibility system.
+The 3 remaining traits were life history traits that included plant height, lifespan and life form and are commonly used to characterize the fast-slow continuum of plant trait variation (e.g., short-lived versus perennial species).
+For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
+From a total of 30,120 possible cells considering all traits and plant species (20 columns × 1,506 species), we were able to fill 24,341 cells (80.8% of the dataset, see Fig.
 S2 for missing values information for each trait).
+An extended description of each trait and how it was obtained can be found in Appendix S1.
 

### 2022-05-23 Manuscript/Lanuza_et_al_2021.tex
edits methods

@@
 ]{article}
+\title{\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors}
+\author{}
+\date{\vspace{-2.5em}}
+
 \usepackage{amsmath,amssymb}
@@
 
-\title{\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors}
-\author{}
-\date{\vspace{-2.5em}}
-
 \begin{document}
@@
 
-\textbf{Short title:} Plant reproductive trade-offs.
-
-\textbf{Keywords:} life-history strategies \textbar{} plant reproductive trade-offs \textbar{} plant-pollinator interactions.
+\textbf{Short title:} Covariation among plant reproductive traits.
+
+\textbf{Keywords:} life-history strategies \textbar{} plant reproductive traits \textbar{} plant-pollinator interactions.
 
@@
 Interestingly, the use of trait-based approaches (\protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero et al., 2014}) and trait-matching analyses (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}) has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-For example, plant traits can define species' network roles {[}e.g., specialists vs generalists; Lázaro et al.
-(\protect\hyperlink{ref-lazaro2013}{2013}); Tur et al.
-(\protect\hyperlink{ref-tur2013}{2013}){]} and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators (\protect\hyperlink{ref-coux2016}{Coux et al., 2016}; \protect\hyperlink{ref-junker2013}{Junker et al., 2013}).
+For example, plant traits can define species' network roles (e.g., specialists vs generalists;~ \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}; \protect\hyperlink{ref-tur2013}{Tur et al., 2013}) and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators (\protect\hyperlink{ref-coux2016}{Coux et al., 2016}; \protect\hyperlink{ref-junker2013}{Junker et al., 2013}).
 Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure (\protect\hyperlink{ref-ibanez2012}{Ibanez, 2012}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}).
 Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network interactions (\protect\hyperlink{ref-eklof2013}{Eklöf et al., 2013}), an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns (see \protect\hyperlink{ref-dehling2016}{Dehling et al., 2016}).
-Thus, by exploring the reproductive spectrum of trait variation is possible to delimit the different plant reproductive strategies and explore how these are associated with the interaction patterns of the different floral visitors.
+Thus, by exploring the reproductive spectrum of trait variation is possible to delimit the different plant reproductive strategies and explore how these are associated with the different floral visitors.
 
@@
 Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}), the positive association between flower size and outcrossing rate (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}) or the association between outcrossing rate and lifespan where short lived versus perennial species tend to have low versus high levels of outcrossing (\protect\hyperlink{ref-barrett2003}{Barrett, 2003}; \protect\hyperlink{ref-moeller2017}{Moeller et al., 2017}), respectively.
-Although these different trait associations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships (\protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}), we still lack empirical evidence that investigates jointly these different reproductive trait associations.
-
-Here, we aim to progress knowledge on the reproductive trait covariation patterns and their association with the different floral visitor guilds by exploring at a broad geographical scale the reproductive trait associations of entomophilous plant species from plant-pollination networks.
-First, we investigate what are the major axes of reproductive trait variation for the different plant species.
+Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships (\protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}), we still lack empirical evidence that investigates jointly these different reproductive trait associations.
+
+Here, we aim to progress knowledge on the reproductive trait covariation patterns and their association with the different floral visitor guilds by exploring at a broad geographical scale the reproductive spectrum of trait variation of entomophilous plant species from plant-pollination networks.
+First, we investigate what are the major axes of reproductive trait variation and trait correlations for the different plant species.
 Second, we investigate the association between the plant species' position in the multidimensional trait-space and the different floral visitor guilds with the help of qualitative (presence-absence of interaction) and quantitative (number of visits) information about plant-pollinator interactions.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' functional role in the pollination network using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
+Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
 
@@
 
-We selected a total of 19 different functional traits that included both reproductive and vegetative traits (see Table 1 and Supplementary Information).
-From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
-The 3 remaining traits, were vegetative traits that are commonly used to characterize the global spectrum of plant form and function and represent the fast-slow continuum of trait variation (e.g., short-lived versus perennial species).
-For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8\% of the dataset, see Fig.
+We selected a total of 19 different functional traits that comprised both reproductive and life history traits (see Table 1).
+From these, 16 were reproductive traits that consisted of 13 floral traits and 3 reproductive biology traits.
+Floral traits included morphological traits (e.g., style length) but also floral reward (e.g., pollen quantity) and floral display (e.g., number of flowers) related traits.
+Reproductive biology traits indicated the reproductive system of the plant and included breeding, mating and compatibility system.
+The 3 remaining traits were life history traits that included plant height, lifespan and life form and are commonly used to characterize the fast-slow continuum of plant trait variation (e.g., short-lived versus perennial species).
+For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
+From a total of 30,120 possible cells considering all traits and plant species (20 columns × 1,506 species), we were able to fill 24,341 cells (80.8\% of the dataset, see Fig.
 S2 for missing values information for each trait).
+An extended description of each trait and how it was obtained can be found in Appendix S1.
 
@@
 The first principal component (PC1) represented 26.72\% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the `flower number - flower size trade-off', as already described in previous studies (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}).
+We refer to this axis as the `flower number - flower size trade-off,' as already described in previous studies (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}).
 Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
@@
 The second principal component (PC2) represented 25.05\% of the trait variation and indicated a trade-off between low and high pollinator dependence.
-We refer to this axis as the `pollinator dependence trade-off'.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
+We refer to this axis as the `pollinator dependence trade-off.' The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
 We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
@@
 The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
-Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the `style length trade-off'.
-Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82\%; Fig.
+Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the `style length trade-off.' Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82\%; Fig.
 S7).
@@
 (2018).
-\emph{Package {``{PVR}.''} R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}}.
+\emph{Package {`{PVR}.'} R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}}.
 
@@
 (2015).
-\emph{Package {``rpart.''} R package version 4.1-15.~At \href{https://CRAN.R-project.org/package=rpart}{https://CRAN.r-project.org/package=rpart}}.
+\emph{Package {`rpart.'} R package version 4.1-15.~At \href{https://CRAN.R-project.org/package=rpart}{https://CRAN.r-project.org/package=rpart}}.
 

### 2022-05-23 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
edits methods

@@
 
-Supplementary text
+Appendix S1 (text)
 
@@
 
-## Supplementary Information Text
+## Appendix S1
 
@@
 S1.} Map with the different locations of the plant-pollinator studies used in this work to explore woldwide patterns at the meso-scale level.
-For each study just one location is shown except for the study of Olesen that was conducted in two very different locations (Mauritius and Azores)."}
+Note that for visualization purposes studies from the same authors are shown with the same colour."}
 
@@
   theme(legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=6),
-         legend.title = element_text(size=12))+
-  scale_colour_discrete(name = "Study \n locations") +   scale_colour_manual(
-    values = colors)
+         legend.title = element_text(size=12)) +   scale_colour_manual(values = colors) + labs(colour="Plant-pollinator studies")
 

### 2022-05-24 Manuscript/Lanuza_et_al_2021.Rmd
m

@@
 Interestingly, the use of trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-For example, plant traits can define species' network roles [e.g., specialists vs generalists;\ @lazaro2013; @tur2013] and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
+For example, plant traits can define species' network roles [e.g., specialists vs generalists;  @lazaro2013; @tur2013] and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
 Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
@@
 Reproductive biology traits indicated the reproductive system of the plant and included breeding, mating and compatibility system.
-The 3 remaining traits were life history traits that included plant height, lifespan and life form and are commonly used to characterize the fast-slow continuum of plant trait variation (e.g., short-lived versus perennial species).
+The 3 remaining traits were life history traits that are commonly used to characterize the fast-slow continuum of plant trait variation (i.e., plant height, lifespan and life form).
 For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
@@
 
-We explored the trade-offs between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
+We explored the association between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
 We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with an Anova and a Tukey test.
+For this, we first implemented a linear model (one for each PC) were the principal components were the response variables and the qualitative variables the predictors.
 Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th--97.5th percentile range [@legendre2012], and thus our final dataset had 1,236 species.
+Due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values within the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
 Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.

### 2022-05-26 Manuscript/Lanuza_et_al_2021.Rmd
updating results

@@
 We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with an Anova and a Tukey test.
-For this, we first implemented a linear model (one for each PC) were the principal components were the response variables and the qualitative variables the predictors.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
+For this, we first implemented a linear model (one for each principal component) where they were the response variable and the different qualitative variables the predictors.
 Prior to the analyses, we excluded outliers and standardized the data.
@@
 
-We first investigated how the different groups of floral visitors interacted along the main axes of trait variation (see below 'visitation patterns' section).
-This was done for the binary version of the networks that assumes equal weight across interactions and for the weighted version with the number of visits of floral visitors to individual flowers that account for the intensity of the interaction.
+First, we investigated how the different groups of floral visitors interacted along the main axes of reproductive trait variation (see below 'visitation patterns' section) with the help of qualitative and quantitative information of plant-pollinator interactions.
+For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that account for the intensity of the interaction.
 Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency [@ballantyne2015], the number of visits can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
-Second, we investigated how the main axes of trait variation and individual traits influence plant species' roles within networks using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below 'plant species network roles' section).
+Second, we investigated how the main axes of trait variation and individual traits influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below 'plant species network roles' section).
 
@@
 
-We investigated whether different quantitative traits determined plant species network roles using Bayesian modelling and regression trees.
+We investigated whether different quantitative traits determined different plant species' functional roles in the pollination network using Bayesian modelling and regression trees.
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
@@
 
-The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Fig.
+The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of the reproductive trait variation, respectively (Fig.
 1 and Fig.
-S6) and had a phylogenetic correlation ($\lambda$) of 0.76.
-The first principal component (PC1) represented 26.72% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the 'flower number - flower size trade-off', as already described in previous studies [@sargent2007; @kettle2011].
-Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
+S6).
+The first principal component (PC1) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
+One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
+For instance, on this end of the spectrum we find the species *Cornus florida* which has approximately a total of 10.000 flowers, an average height of 7.5m, flowers of 3mm wide, a style length of 3.5mm and a total of 2 ovules per flower.
 The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
-The second principal component (PC2) represented 25.05% of the trait variation and indicated a trade-off between low and high pollinator dependence.
-We refer to this axis as the 'pollinator dependence trade-off'.
+For instance, on this side of the spectrum we find the species *Petunia axillaris* which has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
+The second principal component (PC2) represented 25.05% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
 The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
+
 We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.

### 2022-05-30 Manuscript/Lanuza_et_al_2021.Rmd
Some edits
edits

@@
 We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+Prior to the analyses, we excluded outliers and standardized the data.
+Due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as indicated for principal component analysis [@legendre2012].
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
-For this, we first implemented a linear model (one for each principal component) where they were the response variable and the different qualitative variables the predictors.
-Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values within the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
 We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
@@
 S6).
-The first principal component (PC1) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
+The first principal component (PC1) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size ('flower number - flower size').
 The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
@@
 The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-For instance, on this side of the spectrum we find the species *Petunia axillaris* which has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
+For instance, on this side of the axis we find the species *Petunia axillaris* that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
 The second principal component (PC2) represented 25.05% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
 The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
-
-We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
-In contrast, species with high levels of autonomous selfing tended to have fewer and smaller flowers, had shorter styles and were shorter in height.
+In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles.
+A species example of this side of the spectrum is *Zuccagnia punctata* that is a self incompatible shrub which depends totally on floral visitors, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm.
+In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
+For instance, on this side of the spectrum we find the species *Veronica peregrina* which is a self compatible herb that is thought to be almost a complete selfer, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
 Further, PC3 explained a considerable amount of trait variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
 The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
-Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the 'style length trade-off'.
-Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82%; Fig.
+In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82%; Fig.
 S7).
@@
 
-We found a strong phylogenetic signal (*P* \< 0.01) in all quantitative traits (Table S5).
+We found a strong phylogenetic signal (*P* \< 0.01) for most quantitative traits (Table S5).
 The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
@@
 
-  plot <- plot + xlab(paste("Flower number - flower size trade-off ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Pollinator dependence trade-off ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+  plot <- plot + xlab(paste("Flower number - flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("Pollinator dependence axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
 
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
-PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.
+PC1 represents the flower number - flower size axis, PC2 represents the pollinator dependence axis and PC3, the style length - pollinator dependence axis.
 For visualization purposes, due to large differences between number of visits of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel)."}

### 2022-05-30 Manuscript/Lanuza_et_al_2021.tex
edits

@@
 
-We explored the trade-offs between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
+We explored the association between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
 We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation.
+For this, we first implemented a linear model (one for each principal component) where the principal components were the response variable and the different qualitative variables the predictors.
+Finally, we explore the statistical association with an Anova and the differences between categories for each categorical variable with a Tukey test.
 Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th--97.5th percentile range (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}), and thus our final dataset had 1,236 species.
+Due to the high sensitivity of dimensionality reduction to outliers (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}; \protect\hyperlink{ref-serneels2008}{Serneels \& Verdonck, 2008}), we excluded values within the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
 Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
@@
 
-We first investigated how the different groups of floral visitors interacted along the main axes of trait variation (see below `visitation patterns' section).
-This was done for the binary version of the networks that assumes equal weight across interactions and for the weighted version with the number of visits of floral visitors to individual flowers that account for the intensity of the interaction.
+First, we investigated how the different groups of floral visitors interacted along the main axes of reproductive trait variation (see below `visitation patterns' section) with the help of qualitative and quantitative information of plant-pollinator interactions.
+For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that account for the intensity of the interaction.
 Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency (\protect\hyperlink{ref-ballantyne2015}{Ballantyne et al., 2015}), the number of visits can provide valuable information of the contribution of floral visitors to pollination (\protect\hyperlink{ref-vazquez2005}{Vázquez et al., 2005}, \protect\hyperlink{ref-vazquez2012}{2012}).
-Second, we investigated how the main axes of trait variation and individual traits influence plant species' roles within networks using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below `plant species network roles' section).
+Second, we investigated how the main axes of trait variation and individual traits influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below `plant species network roles' section).
 
@@
 
-We investigated whether different quantitative traits determined plant species network roles using Bayesian modelling and regression trees.
+We investigated whether different quantitative traits determined different plant species' functional roles in the pollination network using Bayesian modelling and regression trees.
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies (\protect\hyperlink{ref-dormann2008}{Dormann et al., 2008}) with a straightforward ecological interpretation relevant to our research goals.
@@
 
-The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of trait variation, respectively (Fig.
+The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of the reproductive trait variation, respectively (Fig.
 1 and Fig.
-S6) and had a phylogenetic correlation (\(\lambda\)) of 0.76.
-The first principal component (PC1) represented 26.72\% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the `flower number - flower size trade-off,' as already described in previous studies (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}).
-Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
+S6).
+The first principal component (PC1) represented 26.72\% of the trait variation and indicated a negative correlation between flower number and flower size (`flower number - flower size').
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
+One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
+For instance, on this end of the spectrum we find the species \emph{Cornus florida} which has approximately a total of 10.000 flowers, an average height of 7.5m, flowers of 3mm wide, a style length of 3.5mm and a total of 2 ovules per flower.
 The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
-The second principal component (PC2) represented 25.05\% of the trait variation and indicated a trade-off between low and high pollinator dependence.
-We refer to this axis as the `pollinator dependence trade-off.' The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
-We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
-In contrast, species with high levels of autonomous selfing tended to have fewer and smaller flowers, had shorter styles and were shorter in height.
+For instance, on this side of the axis we find the species \emph{Petunia axillaris} that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
+The second principal component (PC2) represented 25.05\% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
+In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles.
+A species example of this side of the spectrum is \emph{Zuccagnia punctata} that is a self incompatible shrub which depends totally on floral visitors, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm.
+In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
+For instance, on this side of the spectrum we find the species \emph{Veronica peregrina} which is a self compatible herb that is thought to be almost a complete selfer, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
 Further, PC3 explained a considerable amount of trait variability (19.17\%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
 The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
-Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the `style length trade-off.' Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82\%; Fig.
+In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82\%; Fig.
 S7).
@@
 
-We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) in all quantitative traits (Table S5).
+We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) for most quantitative traits (Table S5).
 The traits that showed the highest phylogenetic signal were ovule number (\(\lambda\) = 1), pollen grains per flower (\(\lambda\) = 1) and plant height (\(\lambda\) = 0.96), followed by flower length (\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73), number of flowers per plant (\(\lambda\) = 0.69) and nectar concentration (\(\lambda\) = 0.65).
@@
 Schiestl, F. P., \& Johnson, S. D. (2013). Pollinator-mediated evolution of floral signals. \emph{Trends Ecol. Evol.}, \emph{28}(5), 307--315. \url{https://doi.org/10.1016/j.tree.2013.01.019}
+
+\leavevmode\vadjust pre{\hypertarget{ref-serneels2008}{}}%
+Serneels, S., \& Verdonck, T. (2008). Principal component analysis for data containing outliers and missing elements. \emph{Computational Statistics \& Data Analysis}, \emph{52}(3), 1712--1727.
 
@@
 \caption{\label{fig:unnamed-chunk-4}\textbf{Figure 3} Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
-PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.
+PC1 represents the flower number - flower size axis, PC2 represents the pollinator dependence axis and PC3, the style length - pollinator dependence axis.
 For visualization purposes, due to large differences between number of visits of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel).}

### 2022-05-31 Manuscript/Lanuza_et_al_2021.Rmd
edits

@@
 
-Trait missing values were imputed with the function *missForest* [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
+To avoid the loss of relevant ecological information that can lead to invalid inferences [@kleinke2020], we imputed trait missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
 We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of *missForest* [@penone2014].
@@
 S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01% of missing values).
+To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without missing values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
+
+[Esta última parte intenta justificar la validación de nuestros resultados, le vendría bien ojo crítico, antes estaba en el siguiente párrafo pero la maldad mental para criticarnos se genera en este y pienso que ya no llega al siguiente con buenos ojos](Jose)
 
@@
 We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
-S3).
-We found little difference between the explained variance with the imputed dataset (51.08%) and the dataset without missing values (52.87%).
-In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
 Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.

### 2022-05-31 Manuscript/Lanuza_et_al_2021.tex
edits

@@
 We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation.
-For this, we first implemented a linear model (one for each principal component) where the principal components were the response variable and the different qualitative variables the predictors.
-Finally, we explore the statistical association with an Anova and the differences between categories for each categorical variable with a Tukey test.
 Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}; \protect\hyperlink{ref-serneels2008}{Serneels \& Verdonck, 2008}), we excluded values within the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
+Due to the high sensitivity of dimensionality reduction to outliers (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}; \protect\hyperlink{ref-serneels2008}{Serneels \& Verdonck, 2008}), we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as indicated for principal component analysis (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}).
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
 We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell, 2012}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams, 2010}).

### 2022-05-31 Supplementary_Material/trial.Rmd
edits

@@
 title: "Untitled"
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
 ---
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig.
-S6.} Phylogenetic informed principal component analysis for the subset of species with floral rewards."}
+S3.}  Phylogenetic informed principal component analysis for the species that did not have missing values."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 #Load data
-phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-dat_cleaning_7 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen.rds")
+phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen_complete_cases.rds")
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen_complete_cases.rds")
 
@@
 
-library(magick)
-
-#Images were made by Paula Martin
-PC$S[,1] <- -PC$S[,1]
+#############################################################################################################################################################
+#COMPATIBILITY
+#############################################################################################################################################################
+#Load plots
 
@@
 
-  plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
+  plot <- plot + geom_point(data=dat, aes(x, y),size=0.95, color="black")
 
@@
   # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
 
   #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=-v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
 
@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,4.8,4.8,5.5,5,5.5,5.8,6.5)), y = -(PCAloadings$PC2*c(4.8,4.4,4.15,5.35,5,4.7,5.75,6)+c(0,0,0,0,0,0,0,0)),
-                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
+  plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,5.5,6.25,6.3,4.2,6,6)), y = -(PCAloadings$PC2*c(4.693,3.5,3,6.2,3.5,4.15,6,7.5)+c(0,0,0,0,2,0,0,0)),
+                          label = PCAloadings$Variables, color="black",fontface =2,size=4)
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
+  plot <- plot + theme_bw() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
 

### 2022-05-31 Scripts/3_PPCA_Nectar_Pollen_Complete_Cases.R

@@ -260,8 +260,8 @@ saveRDS(dat_cleaning_7, "Data/RData/data_all_species_PPCA_nectar_pollen_complete
 ####
 #READ DATA
 ####
-#phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-#dat_cleaning_7 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen.rds")
+phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen_complete_cases.rds")
+dat_cleaning_7 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen_complete_cases.rds")
 
 
 #CALL the output PC for simplicity

### 2022-06-02 Manuscript/Lanuza_et_al_2021.Rmd
edit

@@
 
-To avoid the loss of relevant ecological information that can lead to invalid inferences [@kleinke2020], we imputed trait missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
+To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
 We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of *missForest* [@penone2014].

### 2022-06-02 Manuscript/Lanuza_et_al_2021.tex
edit

@@
 
-Trait missing values were imputed with the function \emph{missForest} (\protect\hyperlink{ref-stekhoven2012}{Stekhoven \& Bühlmann, 2012}) which allows imputation of data sets with continuous and categorical variables.
+To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} (\protect\hyperlink{ref-stekhoven2012}{Stekhoven \& Bühlmann, 2012}) which allows imputation of data sets with continuous and categorical variables.
 We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} (\protect\hyperlink{ref-penone2014}{Penone et al., 2014}).
@@
 S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01\% of missing values).
+To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without missing values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
+
+\href{Jose}{Esta última parte intenta justificar la validación de nuestros resultados, le vendría bien ojo crítico, antes estaba en el siguiente párrafo pero la maldad mental para criticarnos se genera en este y pienso que ya no llega al siguiente con buenos ojos}
 
@@
 We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell, 2012}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams, 2010}).
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
-S3).
-We found little difference between the explained variance with the imputed dataset (51.08\%) and the dataset without missing values (52.87\%).
-In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
 Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.

### 2022-06-02 Supplementary_Material/All_spp_and_completecasesPPCA.Rmd
edit

--- 2022-05-23 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
@@
 ---
-#title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Covariation among reproductive traits in flowering plants determine interactions with floral visitors}
-
 output:
-  pdf_document:
-    extra_dependencies: ["float"]
-header-includes:
-- \usepackage{pdflscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
-- \usepackage{float}
-- \usepackage{caption}
-- \usepackage{setspace}\doublespacing
-- \usepackage{soul}
-- \floatplacement{figure}{H}
-- \usepackage{afterpage}
-- \usepackage{placeins}
-- \usepackage{graphicx}
-- \usepackage{floatpag}
-
-fontsize: 12pt
-
+  pdf_document: default
+  html_document: default
 ---
 
-```{r echo=FALSE,warning=FALSE}
-knitr::opts_chunk$set(fig.pos = "h", out.extra = "")
-
-```
-
-\captionsetup[figure]{labelformat=empty}
-\captionsetup[table]{labelformat=empty}
-\captionsetup[table]{font={stretch=1.2}}
-
-\singlespacing
-
-\vspace{2cm}
-
-# Supplementary information for:
-
-## Covariation among reproductive traits in flowering plants determine interactions with floral visitors
-
-\textbf{Jose B. Lanuza*, Romina Rader, Jamie Stavert, Liam K. Kendall, Manu E. Saunders and Ignasi Bartomeus}
-
-\textbf{*Corresponding author}
-**E-mail: barragansljose@gmail.com**
-
-**This pdf includes:**
-
-Appendix S1 (text)
-
-Tables S1 to S5
-
-Figures S1 to S10
-
-\doublespacing
-
-<!--
-
-__Supplementary text__
-
-Description of the traits compiled in this study with an illustrative figure of the main flower morphologies (Supplementary text Fig 1)
-
-\doublespacing
-\singlespacing
-
-__Supplementary Tables__
-
-Supplementary Table S1: List of the 28 plant-pollinator studies used to build the plant trait database
-
-Supplementary Table S2: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species
-
-Supplementary Table S3: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity
-
-Supplementary Table S4: Statistical association between the different categorical variables and the fisrt three main axes of trait variation with the full set of species
-
-Supplementary Table S5: Phylogenetic signal of the different quantitative traits
-
-\doublespacing
-\singlespacing
-
-__Supplementary Figures__
-
-Supplementary Fig. S1: Percentage of present and missing values of the different plant traits
-
-Supplementary Fig. S2: Phylogenetic informed principal component analysis for the species that did not have missing values
-
-Supplementary Fig. S3: Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation
-
-Supplementary Fig. S4: Regression tree analyses
-
-Supplementary Fig. S5: PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species
-
-Supplementary Fig. S6: Phylogenetic informed principal component analysis for the subset of species with floral rewards.
-
-Supplementary Fig. S7: Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species
-
-Supplementary Fig. S8: Presence-absence of interaction and visitation rate of the main bee families on the main axes of trait variation
-
-Supplementary Fig. S9:  Plant species level metrics across the three main axes of trait variation
-
-Supplementary Fig. S10: Pearson correlation between the product of flower number-flower size and autonomous selfing level
-
--->
-
-\newpage
-
-## Appendix S1
-
-__Description of the traits compiled in this study__
-
-Here we describe the different traits of the database used in this study to explore the reproductive spectrum of trait variation and plant-pollinator associations.
-Note that all species have references or links providing the original source of the information.
-
-_Reproductive traits_
-
--	Breeding system: The different plant species were classified in hermaphrodite, dioecious and monoecious species.
-Intermediate breeding systems or more complex ones were also annotated but all the species were divided into these three main categories for simplicity of the analysis.
-
--	Selfing level: We recorded the selfing level of the different species with both quantitative and qualitative data.
-The qualitative data was divided in four main categories, high selfers, medium selfers, low selfers and none which was for the species that were unable to self-pollinate.
-In addition, quantitative data was also divided into these four categories with the following criteria: from 0% to lower than 1% ‘none’, from 1% to 25% ‘low’, from 26% to 75% ‘medium’ and from 76% to 100%  ‘high’.
-Because quantitative selfing had a high percentage of missing values (68%), we were able to solve this by converting these four categories to representative percentages of each category 0%, 13%, 50.5% and 88%.
-This reduced the percentage of missing values for this quantitative trait from 68% to 35% and allowed the imputation of this variable.
-
--	Compatibility system: The different species were divided in three main categories in order to know their ability to self-pollinate.
-These categories were self-compatible, partially self-compatible and self-incompatible species.
-The field of selfing level is partly complementary to the compatibility system but is important to note that not all the self-compatible species or partially self-compatible species will self-pollinate.
-
-_Floral traits_
-
--	Flower symmetry: We also recorded if the flowers were bilaterally symmetrical “zygomorphic” or were radially symmetrical “actinomorphic”.
-
--	Flower and inflorescence size: We searched for flower length and flower and inflorescence width (mm) for all species.
-When possible, we calculated the not found measurements with the help of online images and the software ImageJ.
-Note that for species with compound flowers (e.g., Asteraceae) or similar floral structures with flower heads with many small flowers we considered the inflorescence as the floral unit.
-For each species this is indicated in the dataset with the field of "info_level" where the measurement level is specified as capitulum or flower level.
-Note that for some Asteraceae species information about the disc and ray floret is also provided in the database but these were not included in our analyses.
-
--	Flower number per plant: We compiled information about the number of flowers per plant for all species.
-However, this field was rare to find and we also used online images of the different species in order to calculate rough numbers of flowers per plant.
-We referenced all the filled fields in order to be able to follow the images that were used for these counts.
-It is important to note, that these numbers are not pretended to be the exact number of flowers per species but an approximate indicator of the reproductive investment for the different species that allow the macroecological analysis of this field.
-
--	Ovule number: We searched for the number of ovules per flower for all the different species.
-The number of ovules of Asteraceae species are considered as the total number of ovules per capitulum.
-Many species were filled by genus or family level because the number of ovules in this taxonomic groups is considered to be mostly constant (e.g., Lamiaceae Boraginaceae or Apiaceae).
-
--	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape.
-We divided the flowers in 8 main different categories: open, bowl, tube, campanulate, funnelform, papilionaceous, brush and capitulum.
-However, we ended up groupping all flowers on the following 6  morphological groups for analyses: tube, papilonaceous, open, capitulum, campanulate and brush (Supplementary Information Text Fig.
-1).
-
-```{r pressure, echo=FALSE, fig.cap="", out.width = '65%',fig.align='center', fig.cap="\\textbf{Supplementary Information Text Fig.
-1.}  Main floral morphologies considered in this study.
-All species were groupped within these categories for analysis: (a) tube, (b) papilonaceous, (c) open, (d) capitulum, (e) campanulate and (f) brush."}
-knitr::include_graphics("../Images/flower_shapes.png")
-```
-
--	Style length: The length of the style (mm) of the different species was also included. When possible, we calculated style length from images and illustrations on the online floras.
-
-- Nectar provision: We recorded the presence and absence of nectar for all species.
-In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration.
-For species that did not have nectar information but belonged to a family that is considered as ‘nectarless’, this trait was recorded at family level and the species was recorded with ‘absence’ of nectar.
-This was done exclusively for well documented nectarless taxonomical groups.
-For the field of microlitres of nectar, we considered single measurements of nectar standing crop.
-In general terms, the timming of the measurement and methodology differed across studies.
-For instance, some studies measured nectar in freshly opened flowers while others in flowers that were bagged for 24 hours.
-Despite the different methodologies to measure nectar provision, we believe that this is an appropriate way to collate measurements of nectar to explore trait associations at a macroecological scale.
-
-- Pollen grains per flower: We recorded pollen grains per flower for all species but this field was rarely described in the literature.
-When just the pollen:ovule ratio was found we converted it back to pollen grains by multiplying it by the average ovule number found for each species.
-
-_Vegetative traits_
-
-- Life form, life span and plant height: We divided the different plant species in 4 main categories: herbs, vines, shrubs and trees.
-Moreover, we also divided the species between short-lived species (annual, biennial and short-lived perennials) and perennial species (long-lived).
-Finally, we also searched for the average height (m) of the different species and annotated the maximum and minimum height when possible.
-We conducted the average between the maximum and minimum height to get an approximate average height of the species when the average was not indicated.
-
-\begin{landscape}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = "left"}
-setwd("~/R_Projects/Reproductive Traits")
-library(kableExtra)
-
-#Create data.frame with references
-
-`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1", "1", "1", "1", "1", "1", "1", "3", "1",
-                          "1", "1")
-
-#`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))
-
-`Network type` <- c(rep("Weighted web",  18), rep("Unweighted web",  4), "Weighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Weighted metaweb")
-
-`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
-                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard", "Bek", "Kato", "Kevan", "Ramirez",
-                    "Inouye","McMullen", "Primack", "Ramirez", "Robertson", "Traveset")
-
-Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003,2006,2000,1970,1989,1990, 1993, 1983, 1992, 1929, 2013)
-
-#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
-#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
-#"USA", "Ecuador")
-
-DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
-"https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
-"https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
-"/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
-"https://doi.org/10.1111/j.1365-2745.2010.01732.x", "https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510",
-"https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis", "Unpublished, Master thesis", "http://hdl.handle.net/2433/156116",
-"https://doi.org/10.2307/2258569", "https://doi.org/10.2307/2388282", "http://hdl.handle.net/2433/156099", "https://biostor.org/reference/244737", "https://doi.org/10.1080/0028825X.1983.10428561",
-"https://doi.org/10.1111/j.1095-8339.1992.tb00294.x", "https://doi.org/10.5962/bhl.title.11538", "https://doi.org/10.1098/rspb.2012.3040")
-
-references <- data.frame(`First author`, Year, `Number of networks`,`Network type`,   DOI)
-
-colnames(references) <- c("First author", "Year", "Web N.",  "Network type",  "DOI")
-
-library(dplyr)
- references %>%
- arrange(`First author`)%>%
-kable("latex", longtable = T, booktabs = T,linesep = "\\addlinespace",
-             caption = "\\textbf{Table S1.
-List of the 28 plant-pollinator studies used to build the plant trait database.
-Each study is shown with the first author that conducted the study, number of networks or metawebs that contains, type of information that contains (weighted or unweighted),  the structure (web or metaweb), year of publication and digital object identifier or permanent link for each study.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, repeat_header_method="replace" ,full_width=F,position = "left")
-
-```
-
-\end{landscape}
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=20, fig.width=10,out.width="85%",fig.align='center',fig.cap= ""}
 
@@
 
-d <- readRDS("Data/RData/table_categorical_tukey_test.rds")
-
-#Again im getting the same error on this rmd so I run it on another one, save the dataframe and plot it here
-
-#Plot table
-#Add latex format in markdown
-
-kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Table S2.
-Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
- kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S3.
-Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Microlitres of Nectar per flower" , "Pollen per flower","Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
-kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S4.
-Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-#SELFING
-selfing <- readRDS("Data/RData/selfing_phylo.rds")
-#FLOWER NUMBER
-flower_n <- readRDS("Data/RData/flower_n_phylo.rds")
-#INFLO WIDTH
-inflow_width <- readRDS("Data/RData/inflow_width_phylo.rds")
-#FLOWER WIDTH
-flower_width <- readRDS("Data/RData/flower_width_phylo.rds")
-#FLOWER LENGHT
-flower_length <- readRDS("Data/RData/flower_length_phylo.rds")
-#STYLE LENGTH
-style_n <- readRDS("Data/RData/style_n_phylo.rds")
-#OVULE NUMBER
-ovule_n <- readRDS("Data/RData/ovule_n_phylo.rds")
-#PLANT HEIGHT
-plant_height <- readRDS("Data/RData/plant_height_phylo.rds")
-#POLLEN
-pollen <- readRDS("Data/RData/pollen_phylo.rds")
-#Nectar ul
-nectar_ul <- readRDS("Data/RData/Nectar_ul_phylo.rds")
-
-#Not included at the end
-#Nectar mg
-#nectar_mg <- readRDS("Data/RData/Nectar_mg_phylo.rds")
-#Nectar concentration
-nectar_con <- readRDS("Data/RData/Nectar_concentration_phylo.rds")
-
-#Select two decimals function
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-#LABELS
-label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Nectar per flower ($\\mu$l)", "Nectar concentration ($\\%$)","Pollen grains per flower")
-#LAMBDA
-lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, nectar_ul$lambda, nectar_con$lambda, pollen$lambda)
-#P-VALUE
-p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P,nectar_ul$P,  nectar_con$P, pollen$P)
-
-tabla <- data.frame(label, specify_decimal(lambda,2), specify_decimal(p_value,2))
-
-colnames(tabla) <- c("Functional traits", "Lambda", "P-value")
-
-kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,caption = "\\textbf{Table S5. Phylogenetic signal of the different quantitative traits.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.cap="\\textbf{Fig.
-S1.} Map with the different locations of the plant-pollinator studies used in this work to explore woldwide patterns at the meso-scale level.
-Note that for visualization purposes studies from the same authors are shown with the same colour."}
-
-#Create coordinate dataset for plotting
-
-longitude <- c("3.296797",  #1
-               "1.575532", #2
-               "9.275556", 
-               "18.5", #4
-               "99.63806", #5
-               "148.266667",
-               "-52", 
-               "-31", "57.43", #8
-               "-75.5", #9
-               "-57.885", #10
-               "55.447778",
-               "-6.16895", #12bart
-               "55.43333", #13
-               "57.733333",
-               "-68.015892", #15
-               "-89.8968771",
-               "171.756111",
-               "10.233333",
-               "-90.35",
-               "-93.8968771",#Robertson
-               "-67.4292900",
-               "-61.71666666666667",
-               "175.756111",
-               "-71.3",
-               "129.387359", #Kevan
-               "135.75385",
-               "-93.35",
-               "10.219072")
-
-latitude <- c("42.315336", #1
-              "52.762395", #2
-              "56.0725",
-              "68.35", #4
-              "27.90139", #5
-              "-36.45", #6
-              "71", #7
-              "39.4", "-23.25", #8 #modified for visibility of ovelapping
-              "45.4", #9
-              "-21.701111", #10
-              "-7.67",#11 #modified for visibility of ovelapping
-              "37.234966", #12bart
-              "-4.666667", #13
-              "-20.4538",
-              "-32.008985", #15
-              "39.278958",
-              "-43.035889",
-              "59.066667",#18 #modified for visibility of ovelapping
-              "-0.533333",
-              "39.278958", #Robertson 
-              "8.9241600",
-              "5.5833333",
-              "-43.035889",
-              "81.8166667",
-              "28.288661", #Kevan 
-              "35.02107",
-              "-0.533333",
-              "56.069108")
-
-id <- c("Bartomeus1", #1
-        "Dicks", #2
-        "Dupont", 
-        "Elberling", #4
-        "Fang", #5
-        "Inouye1", #6
-        "Lundgren", #7
-        "Olesen", "Olesen", #8
-        "Small", #9
-        "Souza", #10
-        "Kaiser-Bunbury1", #
-        "Bartomeus2", #12
-        "Kaiser-Bunbury2", #13
-        "Kaiser-Bunbury3", #14
-        "Peralta", #15
-        "Burkle",
-        "Arroyo-Correa",
-        "Bundgaard",
-        "Traveset",
-        "Robertson",
-        "Ramirez1",
-        "Ramirez2",
-        "Primack",
-        "Kevan",
-        "Kato",
-        "Inouye2",
-        "McMullen",
-        "Baek")
-
-d <- data.frame(longitude, latitude, id)
-
-library("ggplot2")
-library("sf")
-library("rnaturalearth")
-library("rnaturalearthdata")
-
-world <- ne_countries(scale = "medium", returnclass = "sf")
-class(world)
-
-d$longitude <- as.numeric(d$longitude)
-d$latitude <- as.numeric(d$latitude)
-
-sf::sf_use_s2(FALSE)
-
-#these colors come from the library(pals)- labs = c('alphabet')
-
-colors <- c("red4", "#0075DC", "#4C005C", "#4C005C", "#993F00",  "#5EF1F2", 
-        "#005C31", "#2BCE48", "black", "lightblue", "darkorange3", "darkorange3","#8F7C00",
-        "#8F7C00","#8F7C00", "#9DCC00", "#C20088", "gold1","#FFA8BB","#426600","94FFB5","#003380",  
-         "#FF0010","#FF0010", "salmon", "seashell3","greenyellow","mediumaquamarine")
-
-set.seed(12)
-ggplot(data = world) +
-  geom_sf(fill="antiquewhite", color="grey49") +
-  xlab("Longitude") + ylab("Latitude") +
-  geom_point(data=d , aes(longitude,latitude,  color=id),  shape=10,
-           size = 3.5, stroke=1)+ 
-  theme(panel.grid.major = element_line(color = gray(.5), 
-linetype = "dashed", size = 0), panel.background = element_rect(fill = "aliceblue"))+
-  coord_sf(expand = FALSE) +  scale_y_continuous(breaks = c(-50,0, 50)) +
-  scale_x_continuous(breaks = c(-100,0, 100)) +
-  theme(legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=6),
-         legend.title = element_text(size=12)) +   scale_colour_manual(values = colors) + labs(colour="Plant-pollinator studies")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Fig. S2.} Percentage of present and missing values of the different plant traits."}
-
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-
-########################################################################################################################################################
-#SCRIPT FOR DATA IMPUTATION
-########################################################################################################################################################
-#1) READ TRAIT DATA
-
-#2) CLEAN DATA AND RENAME LEVELS
-
-#3) EXPLORE PATTERNS OF MISSING DATA
-
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-
-#5) ICLUDE EIGENVALUES IN RAWDATA TO IMPROVE IMPUTATION OURPUT
-
-#6) IMPUTE DATA
-
-#7) SAVE IMPUTED DATA 
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(missMDA) #For missing values
-library(FactoMineR) #Produce pca biplot with individuals and variables
-library(factoextra)
-library(ggpubr) 
-library(missForest) #random forst imputation
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(ape)
-library(PVR) #calculate eigen vectors and add them as a column in the imputation, seems to improve output
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-str(trait_data_1)
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-levels(as.factor(trait_filtered$Info_level)) #checking levels
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-str(trait_filtered_2)
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-                        "Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-levels(as.factor(t$Breeding_system))
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-levels(as.factor(t$Flower_morphology))
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-levels(as.factor(t$lifespan))
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-#Explore patterns of missing data
-missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)
-sort(missing_data[missing_data >= 0], decreasing=T)
-#nectar values all above 50% except presence/absence
-#then, just one cololumn with 68% missing data, then one with 35% and then 20% and 10%. The rest under 5%.
-#it is recommended to remove columns over 50% but we are particulary interested in having numeric levels of quantitative selfing 
-#we are going to work just with presence/absence of nectar
-#we will perform further analysis just with a subset with the quantitative values o nectar (very interesting data and diffciult to obtain)
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-         "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-         "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-         "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-         "Pollen_per_flower")]
-
-#check missing data now
-missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)*100
-sort(missing_data[missing_data >= 0], decreasing=T)
-
-missing_data <- unlist(lapply(t, function(x) nrow(t)-sum(is.na(x))))
-sum(missing_data)
-
-#Number of missing values on the datset
-#vis_miss(t[,c(6:20)])
-#9.9% percentage of missing values]
-
-#Checking number of filled cells/ just selecting variables used in the manuscript; nectar ul should be accounted too and it has been considered but
-#not added to run this code
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-str(t)
-
-#Impute data considering phylogenetic distance of species
-#it improves quality of imputation
-#https://doi.org/10.1111/2041-210X.12232 see ref for method comparisons with and without imputation
-
-#Multiple imputation process with phylogeny --> Missforest
-#https://doi.org/10.1111/2041-210X.12232
-#althought it does not have an option we are going to add it as a column
-
-#Before data imputation I need to calculate the phylo of the species
-#remove not found species that do not run with get tree
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-levels(factor(t$Species_all))
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-#Select just columns with traits
-t <- t[c("Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-         "Pollen_per_flower")]
-
-#################################################
-#3)SUMMARY OF THE DATA|ALL COLS CONSIDERED!
-#################################################
-##Number of filled cells
-#nrow(t) * 16 - sum(is.na(t))#[1] 20737
-##Dimension of the dataset
-#nrow(t) * 16#[1] 24096
-##Number of missing values
-#sum(is.na(t))#[1] 3359
-##Percentage of filled cells
-#sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 86.87993
-##Percentage of missing values
-#sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 13.12007
-#
-#
-
-#Function to specify number of decimals
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-no_missing <- specify_decimal(sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
-missing <- specify_decimal(sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
-
-colnames(t) <- c("Breeding system","Compatibility system",
-         "Autonomous selfing qualitative","Autonomous selfing quantitative", "Flower shape", "Flower symmetry", 
-         "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 
-         "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar per flower (microlitres)", "Nectar per flower (miligrames)", "Nectar concentration (%)", "Pollen grains per flower")
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-levels <-
-  (missing.values  %>% filter(isna == T) %>% arrange(desc(pct)))$key
-
-percentage.plot <- missing.values %>%
-  ggplot() +
-  geom_bar(aes(x = reorder(key, desc(pct)), 
-               y = pct, fill=isna), 
-           stat = 'identity', alpha=0.8) +
-  scale_x_discrete(limits = levels) + theme_bw()+
-  scale_fill_manual(name = "", 
-                    values = c('#57a340', '#d24513'), labels = c("Present values", "Missing values")) +
-  coord_flip() +
-  labs(title = "", x =
-         '', y = "")+  scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
-  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))
-
-percentage.plot
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig.
-S3.}  Phylogenetic informed principal component analysis for the species that did not have missing values."}
-setwd("~/R_Projects/Reproductive Traits")
-
 #Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
 library(viridis) #COLOUR GGPLOT
-library(MASS)
 library(ggplot2)
@@
 library(cowplot)
+library(magick)
+
 # Theme for publication
@@
 }
+
+#Load data
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+PC <- phyl_pca_forest
+#CHECK CONTENT
+#EIGENVALUES
+PC$Eval
+#PC score (POINTS)
+PC$S
+#PC loadings (ARROWS)
+PC$L
+
+#Images were made by Paula Martin
+#Check her work on https://paulamartinart.com/
+
+#############################################################################################################################################################
+#COMPATIBILITY
+#############################################################################################################################################################
+#Load plots
+
+#Invert axes
+PC$S[,1] <- -PC$S[,1]
+PC$S[,2] <- -PC$S[,2]
+
+all_spp <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
+  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
+    scale_alpha(guide = 'none')
+
+    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .7 * mult * (get(x)),
+                      v2 = .7 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+
+   #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+
+#ADD LABELS
+  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+ plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
+                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
+
+# plot <- plot + annotate("text", x = #(PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = #(PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0))#,
+#                         label =c("Low selfing", "Few flowers", #"Small flowers", "Short styles", "Few ovules", "Short plants" ), #color="black",fontface =2,size=4)
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
+
+  plot
+
+}
+
+p1 <- all_spp(PC)
 
@@
 
-pc3 <- function(PC, x="PC1", y="PC2") {
+all_complete_cases <- function(PC, x="PC1", y="PC2") {
   # PC being a prcomp object
@@
 
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
+  plot <- plot + theme_bw() 
       #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
+  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
 
@@
 
-pc3(PC)
+p2 <- all_complete_cases(PC)
+
+library(patchwork)
+
+p1 / p2 + plot_annotation(tag_levels = 'A') & 
+  theme(plot.tag = element_text(size = 24, face="bold"))
 
 ```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24,  fig.cap="\\textbf{Fig.
-S4.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation.
-The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates."}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot_apis <- readRDS("Plot_apis_non_apis.rds")
-
-plot_apis
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig.
-S5.} Regression tree analyses.
-Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
-"}
-
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
-########################################################################################################################################################
-#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
-
-library(rpart.plot)
-library(rpart)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
-nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
-d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")
-
-#run  regression trees of the 3 metrics
-set.seed(1)
-tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0054559,minbucket=50)
-
-set.seed(1)
-tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0084459,minbucket=50)
-
-set.seed(1)
-tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0072192 , minbucket=50) #10
-
-#NECTAR AND POLEN DATA
-v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
-nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
-d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
-
-#Set correct colnames for plotting
-colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-set.seed(2)
-tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
-
-set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
-
-set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)
-
-par(mfrow=c(3,2))
-
-rpart.plot(tree_1, box.palette="GnOr", main="A Interaction frequency for all species", cex.main=1.85,tweak = 1.10) 
-rpart.plot(tree1, box.palette="GnOr", main="B Interaction frequency for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-rpart.plot(tree_2, box.palette="GnOr", main="C Normalized degree for all species", cex.main=1.85,tweak = 1.10)
-rpart.plot(tree2, box.palette="GnOr", main="D Normalized degree for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-rpart.plot(tree_3, box.palette="GnOr", main="E Specialization for all species", cex.main=1.85,tweak = 1.10) 
-rpart.plot(tree3, box.palette="GnOr", main="F Specialization for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig.
-S6.} PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species."}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-pc3 <- function(PC, x="PC1", y="PC3") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC3 ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,4.8,7.1,5.5)), y = -(PCAloadings$PC2*c(-3.2,4.5,3.75,8.4,5,5.5)+c(0,0,0,0,-0.08,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-pc3(PC)
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig.
-S7.} Phylogenetic informed principal component analysis for the subset of species with floral rewards."}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-dat_cleaning_7 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen.rds")
-
-PC <- phyl_pca_forest_nectar_pollen
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-library(magick)
-
-#Images were made by Paula Martin
-PC$S[,1] <- -PC$S[,1]
-
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
-    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-  plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw()
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height", "Nectar","Pollen" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,4.8,4.8,5.5,5,5.5,5.8,6.5)), y = -(PCAloadings$PC2*c(4.8,4.4,4.15,5.35,5,4.7,5.75,6)+c(0,0,0,0,0,0,0,0)),
-                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-all_spp(PC)
-
-```
-
-\newpage
-\thispagestyle{empty}
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig.
-S8.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species.
-Categories that differ significantly are denoted with a different letter."}
-
-########################################################################################################################################################
-#CORRELATION BETWEEN QUALITATIVE VARIABLES AND PC's
-########################################################################################################################################################
-#NOTES
-#I did not include the qualitative variables when I prepare the data for the PPCA
-#So I have to recalculate the ata here with the qualitative variables
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(emmeans)
-library(ggplot2)
-library(patchwork)
-library(dplyr)
-
-theme_ms <- function(base_size=10, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(1.3)),
-           axis.text=element_text(size = rel(1.1), color = "black"),
-           panel.border=element_rect(color="black",size=1.2),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           legend.position = "none",
-           plot.title = element_text(face = "bold",size = rel(1.55)),
-           plot.subtitle = element_text(face = "bold",size = rel(1.4))
-     ))
-}
-
-########################################################################################################################################################
-setwd("~/R_Projects/Reproductive Traits")
-
-#LOAD DATA
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-dat <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-########################################################################################################################################################
-#remove not found species, cannot do PCA with unequal numbers of rows
-cols.num <- c("Family_all","Genus_all","Species_all")
-dat[cols.num] <- sapply(dat[cols.num],as.character)
-dat$Species_all <- gsub("Species_all_", "", dat$Species_all)
-########################################################################################################################################################
-#3) REMOVE OUTLIERS, OUT OF 2.5-97.5 RANGE WHICH HELPS IMPUTATION PROCESS. SEE ARTICLE FOR REF.
-########################################################################################################################################################
-dat_cleaning <- dat[,]
-#CHECK LEVELS
-
-dat_cleaning_1 <- dat_cleaning %>%
-  filter(between(Flowers_per_plant, quantile(Flowers_per_plant, 0.025), quantile(Flowers_per_plant, 0.975)))
-
-dat_cleaning_2 <- dat_cleaning_1 %>%
-  filter(between(Corolla_diameter_mean, quantile(Corolla_diameter_mean, 0.025), quantile(Corolla_diameter_mean, 0.975)))
-
-dat_cleaning_3 <- dat_cleaning_2 %>%
-  filter(between(Style_length, quantile(Style_length, 0.025), quantile(Style_length, 0.975)))
-
-dat_cleaning_4 <- dat_cleaning_3 %>%
-  filter(between(Ovule_number, quantile(Ovule_number, 0.025), quantile(Ovule_number, 0.975)))
-
-dat_cleaning_5 <- dat_cleaning_4 %>%
-  filter(between(Plant_height_mean_m, quantile(Plant_height_mean_m, 0.025), quantile(Plant_height_mean_m, 0.975)))
-
-final_d <- dat_cleaning_5[,]
-
-pca_data <- as.data.frame(phyl_pca_forest$S)
-
-d <- cbind(final_d, pca_data)
-
-#Prepare qualitative variables
-d$Compatibility_system[d$Compatibility_system=="dioecious"] <- "Unisexual flowers"
-d$Compatibility_system[d$Compatibility_system=="monoecious"] <- "Unisexual flowers"
-d$Compatibility_system[d$Compatibility_system=="partially_self_compatible"] <- "Partially self compatible"
-d$Compatibility_system[d$Compatibility_system=="self_compatible"] <- "Self compatible"
-d$Compatibility_system[d$Compatibility_system=="self_incompatible"] <- "Self incompatible"
-d$Compatibility_system <- factor(d$Compatibility_system, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-d$life_form[d$life_form=="herb"] <- "Herb"
-d$life_form[d$life_form=="shrub"] <- "Shrub"
-d$life_form[d$life_form=="tree"] <- "Tree"
-d$life_form[d$life_form=="vine"] <- "Shrub"
-
-d$Flower_symmetry[d$Flower_symmetry=="actinomorphic"] <- "Actinomorphic"
-d$Flower_symmetry[d$Flower_symmetry=="zygomorphic"] <- "Zygomorphic"
-
-d$Flower_symmetry[d$Flower_symmetry=="Funnelform"] <- "Campanulate"
-d$Flower_symmetry[d$Flower_symmetry=="Spike"] <- "Brush"
-
-d$Flower_morphology[d$Flower_morphology=="Funnelform"] <- "Campanulate"
-d$Flower_morphology[d$Flower_morphology=="Spike"] <- "Brush"
-
-d$Nectar_presence_absence[d$Nectar_presence_absence=="yes"] <- "Yes"
-d$Nectar_presence_absence[d$Nectar_presence_absence=="no"] <- "No"
-
-#The other qualitative are ok
-
-#All principal components are normally distributed
-#Convert to factor before running model
-d[sapply(d, is.character)] <- lapply(d[sapply(d, is.character)], as.factor)
-
-#Run model
-model1 <- lm(PC1 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
-model2 <- lm(PC2 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
-
-####################################################################################################################################################################################################################################
-#1) BREEDING SYSTEM
-####################################################################################################################################################################################################################################
-model_breeding_1 <- emmeans(model1, "Breeding_system")
-breeding_1 <- as.data.frame(model_breeding_1[1:3])
-breed1 <- multcomp::cld(model_breeding_1, alpha = 0.10, Letters = LETTERS)
-
-breed_1 <- ggplot(breed1,aes(x= Breeding_system,y= emmean,
-               label = .group)) +theme_minimal()+
-  geom_point(data = breed1, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "A Breeding system")+
-  theme(plot.title = element_text(hjust=0.5, size=25, face="bold"))+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-model_breeding_2 <- emmeans(model2, "Breeding_system")
-breeding_2 <- as.data.frame(model_breeding_2[1:3])
-breed2 <- multcomp::cld(model_breeding_2, alpha = 0.10, Letters = LETTERS)
-
-breed_2 <- ggplot(breed2,aes(x= Breeding_system,y= emmean,
-             label = .group)) +theme_minimal()+
-  geom_point(data = breed2, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "B Breeding system")+
-  theme(plot.title = element_text(hjust=0.5,size=25, face="bold") )+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-########################################################################################################################################################
-#2) COMPATIBILITY
-########################################################################################################################################################
-model_com <- emmeans(model1, "Compatibility_system")
-
-d <- as.data.frame(model_com[1:4])
-comp1 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
-
-comp_1 <- ggplot(comp1,aes(x= Compatibility_system,y= emmean,
-  label = .group)) +theme_minimal()+
-  geom_point(data = comp1, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
-  width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "C Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
-
-model_com <- emmeans(model2, "Compatibility_system")
-d <- as.data.frame(model_com[1:4])
-comp2 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
-
-comp_2 <- ggplot(comp2,aes(x= Compatibility_system,y= emmean,
-  label = .group)) +theme_minimal()+
-  geom_point(data = comp2, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
-  width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "D Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
-
-########################################################################################################################################################
-#3) LIFESPAN
-########################################################################################################################################################
-model_lif_1 <- emmeans(model1, "lifespan")
-lif_1 <- as.data.frame(model_lif_1[1:2])
-lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
-
-lifespan_1 <- ggplot(lif_1,aes(x= lifespan,y= emmean,
-             label = .group)) +theme_minimal()+
-  geom_point(data = lif_1, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "E Lifespan")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-model_lif_2 <- emmeans(model2, "lifespan")
-lif_2 <- as.data.frame(model_lif_2[1:2])
-lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
-
-lifespan_2 <- ggplot(lif_2,aes(x= lifespan,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_2, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "F Lifespan")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")
-
-########################################################################################################################################################
-# 4) LIFE FORM
-########################################################################################################################################################
-
-model_lif_1 <- emmeans(model1, "life_form")
-lif_1 <- as.data.frame(model_lif_1[1:3])
-lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
-
-lifeform_1 <- ggplot(lif_1,aes(x= life_form,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_1, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "G Life form")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-model_lif_2 <- emmeans(model2, "life_form")
-lif_2 <- as.data.frame(model_lif_2[1:3])
-lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
-
-lifeform_2 <- ggplot(lif_2,aes(x= life_form,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_2, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "H Life form")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-########################################################################################################################################################
-# 5) FLOWER MORPHOLOGY
-########################################################################################################################################################
-model_flo_1 <- emmeans(model1, "Flower_morphology")
-flo_1 <- as.data.frame(model_flo_1[1:6])
-flo_1 <- multcomp::cld(model_flo_1, alpha = 0.10, Letters = LETTERS)
-
-shape_1 <- ggplot(flo_1,aes(x= Flower_morphology,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_1, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "I Flower shape")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")
-
-model_flo_2 <- emmeans(model2, "Flower_morphology")
-flo_2 <- as.data.frame(model_flo_2[1:6])
-flo_2 <- multcomp::cld(model_flo_2, alpha = 0.10, Letters = LETTERS)
-
-shape_2 <- ggplot(flo_2,aes(x= Flower_morphology,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_2, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "J Flower shape")+
-   geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
-
-########################################################################################################################################################
-#6) FLOWER SYMMETRY
-########################################################################################################################################################
-model_flo_sym_1 <- emmeans(model1, "Flower_symmetry")
-flo_sym_1 <- as.data.frame(model_flo_sym_1[1:2])
-flo_sym_1 <- multcomp::cld(model_flo_sym_1, alpha = 0.10, Letters = LETTERS)
-
-symmetry_1 <-ggplot(flo_sym_1,aes(x= Flower_symmetry,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_sym_1, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "K Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
-
-model_flo_sym_2 <- emmeans(model2, "Flower_symmetry")
-flo_sym_2 <- as.data.frame(model_flo_sym_2[1:2])
-flo_sym_2 <- multcomp::cld(model_flo_sym_2, alpha = 0.10, Letters = LETTERS)
-
-symmetry_2 <- ggplot(flo_sym_2,aes(x= Flower_symmetry,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = flo_sym_2, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title = "L Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-########################################################################################################################################################
-#7) NECTAR
-########################################################################################################################################################
-model_nec <- emmeans(model1, "Nectar_presence_absence")
-
-model_nec_1 <- emmeans(model1, "Nectar_presence_absence")
-nec_1 <- as.data.frame(model_nec_1[1:2])
-nec_1 <- multcomp::cld(model_nec_1, alpha = 0.10, Letters = LETTERS)
-
-nectar_1 <- ggplot(nec_1,aes(x= Nectar_presence_absence,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = nec_1, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "M Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-model_nec_2 <- emmeans(model2, "Nectar_presence_absence")
-nec_2 <- as.data.frame(model_nec_2[1:2])
-nec_2 <- multcomp::cld(model_nec_2, alpha = 0.10, Letters = LETTERS)
-
-nectar_2 <-ggplot(nec_2,aes(x= Nectar_presence_absence,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = nec_2, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "N Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")
-
-#PLOT!
-
-breed_1 + breed_2+ comp_1+ comp_2+ lifespan_1+ lifespan_2+ lifeform_1+ lifeform_2+ shape_1+ shape_2+
-symmetry_1+ symmetry_2+ nectar_1+ nectar_2 + plot_layout(ncol = 2)
-
-```
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Fig.
-S9.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation.
-Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
-For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)"}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot <- readRDS("Plot_bee_families.rds")
-
-plot
-
-```
-
-\elandscape
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S10.} Plant species level metrics across the three main axes of trait variation.", fig.pos= "h"}
-
-#library(brms) #modelling
-library(cowplot) #panel of plots
-library(ggplot2) #plotting
-library(patchwork)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(3.5)),
-           axis.text=element_text(size = rel(2.75), color = "black"),
-           legend.title=element_text(face="bold"),
-           legend.text=element_text(),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(0.4, 'lines'),
-           panel.border=element_rect(color="black",size=3),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-#########
-
-setwd("~/Dropbox/PhD/R/Chapter_2")
-
-#read plot generated in other rmd, bms and stan are giving trouble here... This file is created in Species_Level_Metric_Pcs
-
-plot_metrics_pcs <- readRDS("plot_metrics_pcs.rds")
-
-plot_metrics_pcs
-
-```
-
-\elandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S11.} Pearson correlation between the product of flower number-flower size and autonomous selfing level.", fig.pos= "h"}
-
-theme_ms <- function(base_size=18, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(2.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-#LOAD LIBRARIES
-library(ggplot2)
-library(ggpubr)
-
-#LOAD DATA
-dat <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-
-#CONDUCT PRODUCT FLOWER NUMBER-FLOWER SIZE
-dat$Product <-      log(dat$Flowers_per_plant * dat$Corolla_diameter_mean+1)
-
-ggscatter(dat, x = "Autonomous_selfing_level_fruit_set", y = "Product", 
-          add = "reg.line", conf.int = TRUE,
-          cor.coef = TRUE, cor.method = "pearson",size=5,cor.coef.size=15,
-          xlab = "Autnomous selfing", ylab = "Product flower size-number") +
-  theme_ms() +ylim(0,16)
-
-```

### 2022-06-02 Supplementary_Material/Subset_spp_floral_rewards_and_completecases_PPCA.Rmd
edit

--- 2022-05-23 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
@@
 ---
-#title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Covariation among reproductive traits in flowering plants determine interactions with floral visitors}
-
 output:
-  pdf_document:
-    extra_dependencies: ["float"]
-header-includes:
-- \usepackage{pdflscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
-- \usepackage{float}
-- \usepackage{caption}
-- \usepackage{setspace}\doublespacing
-- \usepackage{soul}
-- \floatplacement{figure}{H}
-- \usepackage{afterpage}
-- \usepackage{placeins}
-- \usepackage{graphicx}
-- \usepackage{floatpag}
-
-fontsize: 12pt
-
+  pdf_document: default
+  html_document: default
 ---
 
-```{r echo=FALSE,warning=FALSE}
-knitr::opts_chunk$set(fig.pos = "h", out.extra = "")
-
-```
-
-\captionsetup[figure]{labelformat=empty}
-\captionsetup[table]{labelformat=empty}
-\captionsetup[table]{font={stretch=1.2}}
-
-\singlespacing
-
-\vspace{2cm}
-
-# Supplementary information for:
-
-## Covariation among reproductive traits in flowering plants determine interactions with floral visitors
-
-\textbf{Jose B. Lanuza*, Romina Rader, Jamie Stavert, Liam K. Kendall, Manu E. Saunders and Ignasi Bartomeus}
-
-\textbf{*Corresponding author}
-**E-mail: barragansljose@gmail.com**
-
-**This pdf includes:**
-
-Appendix S1 (text)
-
-Tables S1 to S5
-
-Figures S1 to S10
-
-\doublespacing
-
-<!--
-
-__Supplementary text__
-
-Description of the traits compiled in this study with an illustrative figure of the main flower morphologies (Supplementary text Fig 1)
-
-\doublespacing
-\singlespacing
-
-__Supplementary Tables__
-
-Supplementary Table S1: List of the 28 plant-pollinator studies used to build the plant trait database
-
-Supplementary Table S2: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species
-
-Supplementary Table S3: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity
-
-Supplementary Table S4: Statistical association between the different categorical variables and the fisrt three main axes of trait variation with the full set of species
-
-Supplementary Table S5: Phylogenetic signal of the different quantitative traits
-
-\doublespacing
-\singlespacing
-
-__Supplementary Figures__
-
-Supplementary Fig. S1: Percentage of present and missing values of the different plant traits
-
-Supplementary Fig. S2: Phylogenetic informed principal component analysis for the species that did not have missing values
-
-Supplementary Fig. S3: Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation
-
-Supplementary Fig. S4: Regression tree analyses
-
-Supplementary Fig. S5: PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species
-
-Supplementary Fig. S6: Phylogenetic informed principal component analysis for the subset of species with floral rewards.
-
-Supplementary Fig. S7: Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species
-
-Supplementary Fig. S8: Presence-absence of interaction and visitation rate of the main bee families on the main axes of trait variation
-
-Supplementary Fig. S9:  Plant species level metrics across the three main axes of trait variation
-
-Supplementary Fig. S10: Pearson correlation between the product of flower number-flower size and autonomous selfing level
-
--->
-
-\newpage
-
-## Appendix S1
-
-__Description of the traits compiled in this study__
-
-Here we describe the different traits of the database used in this study to explore the reproductive spectrum of trait variation and plant-pollinator associations.
-Note that all species have references or links providing the original source of the information.
-
-_Reproductive traits_
-
--	Breeding system: The different plant species were classified in hermaphrodite, dioecious and monoecious species.
-Intermediate breeding systems or more complex ones were also annotated but all the species were divided into these three main categories for simplicity of the analysis.
-
--	Selfing level: We recorded the selfing level of the different species with both quantitative and qualitative data.
-The qualitative data was divided in four main categories, high selfers, medium selfers, low selfers and none which was for the species that were unable to self-pollinate.
-In addition, quantitative data was also divided into these four categories with the following criteria: from 0% to lower than 1% ‘none’, from 1% to 25% ‘low’, from 26% to 75% ‘medium’ and from 76% to 100%  ‘high’.
-Because quantitative selfing had a high percentage of missing values (68%), we were able to solve this by converting these four categories to representative percentages of each category 0%, 13%, 50.5% and 88%.
-This reduced the percentage of missing values for this quantitative trait from 68% to 35% and allowed the imputation of this variable.
-
--	Compatibility system: The different species were divided in three main categories in order to know their ability to self-pollinate.
-These categories were self-compatible, partially self-compatible and self-incompatible species.
-The field of selfing level is partly complementary to the compatibility system but is important to note that not all the self-compatible species or partially self-compatible species will self-pollinate.
-
-_Floral traits_
-
--	Flower symmetry: We also recorded if the flowers were bilaterally symmetrical “zygomorphic” or were radially symmetrical “actinomorphic”.
-
--	Flower and inflorescence size: We searched for flower length and flower and inflorescence width (mm) for all species.
-When possible, we calculated the not found measurements with the help of online images and the software ImageJ.
-Note that for species with compound flowers (e.g., Asteraceae) or similar floral structures with flower heads with many small flowers we considered the inflorescence as the floral unit.
-For each species this is indicated in the dataset with the field of "info_level" where the measurement level is specified as capitulum or flower level.
-Note that for some Asteraceae species information about the disc and ray floret is also provided in the database but these were not included in our analyses.
-
--	Flower number per plant: We compiled information about the number of flowers per plant for all species.
-However, this field was rare to find and we also used online images of the different species in order to calculate rough numbers of flowers per plant.
-We referenced all the filled fields in order to be able to follow the images that were used for these counts.
-It is important to note, that these numbers are not pretended to be the exact number of flowers per species but an approximate indicator of the reproductive investment for the different species that allow the macroecological analysis of this field.
-
--	Ovule number: We searched for the number of ovules per flower for all the different species.
-The number of ovules of Asteraceae species are considered as the total number of ovules per capitulum.
-Many species were filled by genus or family level because the number of ovules in this taxonomic groups is considered to be mostly constant (e.g., Lamiaceae Boraginaceae or Apiaceae).
-
--	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape.
-We divided the flowers in 8 main different categories: open, bowl, tube, campanulate, funnelform, papilionaceous, brush and capitulum.
-However, we ended up groupping all flowers on the following 6  morphological groups for analyses: tube, papilonaceous, open, capitulum, campanulate and brush (Supplementary Information Text Fig.
-1).
-
-```{r pressure, echo=FALSE, fig.cap="", out.width = '65%',fig.align='center', fig.cap="\\textbf{Supplementary Information Text Fig.
-1.}  Main floral morphologies considered in this study.
-All species were groupped within these categories for analysis: (a) tube, (b) papilonaceous, (c) open, (d) capitulum, (e) campanulate and (f) brush."}
-knitr::include_graphics("../Images/flower_shapes.png")
-```
-
--	Style length: The length of the style (mm) of the different species was also included. When possible, we calculated style length from images and illustrations on the online floras.
-
-- Nectar provision: We recorded the presence and absence of nectar for all species.
-In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration.
-For species that did not have nectar information but belonged to a family that is considered as ‘nectarless’, this trait was recorded at family level and the species was recorded with ‘absence’ of nectar.
-This was done exclusively for well documented nectarless taxonomical groups.
-For the field of microlitres of nectar, we considered single measurements of nectar standing crop.
-In general terms, the timming of the measurement and methodology differed across studies.
-For instance, some studies measured nectar in freshly opened flowers while others in flowers that were bagged for 24 hours.
-Despite the different methodologies to measure nectar provision, we believe that this is an appropriate way to collate measurements of nectar to explore trait associations at a macroecological scale.
-
-- Pollen grains per flower: We recorded pollen grains per flower for all species but this field was rarely described in the literature.
-When just the pollen:ovule ratio was found we converted it back to pollen grains by multiplying it by the average ovule number found for each species.
-
-_Vegetative traits_
-
-- Life form, life span and plant height: We divided the different plant species in 4 main categories: herbs, vines, shrubs and trees.
-Moreover, we also divided the species between short-lived species (annual, biennial and short-lived perennials) and perennial species (long-lived).
-Finally, we also searched for the average height (m) of the different species and annotated the maximum and minimum height when possible.
-We conducted the average between the maximum and minimum height to get an approximate average height of the species when the average was not indicated.
-
-\begin{landscape}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = "left"}
-setwd("~/R_Projects/Reproductive Traits")
-library(kableExtra)
-
-#Create data.frame with references
-
-`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1", "1", "1", "1", "1", "1", "1", "3", "1",
-                          "1", "1")
-
-#`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))
-
-`Network type` <- c(rep("Weighted web",  18), rep("Unweighted web",  4), "Weighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Weighted metaweb")
-
-`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
-                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard", "Bek", "Kato", "Kevan", "Ramirez",
-                    "Inouye","McMullen", "Primack", "Ramirez", "Robertson", "Traveset")
-
-Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003,2006,2000,1970,1989,1990, 1993, 1983, 1992, 1929, 2013)
-
-#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
-#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
-#"USA", "Ecuador")
-
-DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
-"https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
-"https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
-"/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
-"https://doi.org/10.1111/j.1365-2745.2010.01732.x", "https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510",
-"https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis", "Unpublished, Master thesis", "http://hdl.handle.net/2433/156116",
-"https://doi.org/10.2307/2258569", "https://doi.org/10.2307/2388282", "http://hdl.handle.net/2433/156099", "https://biostor.org/reference/244737", "https://doi.org/10.1080/0028825X.1983.10428561",
-"https://doi.org/10.1111/j.1095-8339.1992.tb00294.x", "https://doi.org/10.5962/bhl.title.11538", "https://doi.org/10.1098/rspb.2012.3040")
-
-references <- data.frame(`First author`, Year, `Number of networks`,`Network type`,   DOI)
-
-colnames(references) <- c("First author", "Year", "Web N.",  "Network type",  "DOI")
-
-library(dplyr)
- references %>%
- arrange(`First author`)%>%
-kable("latex", longtable = T, booktabs = T,linesep = "\\addlinespace",
-             caption = "\\textbf{Table S1.
-List of the 28 plant-pollinator studies used to build the plant trait database.
-Each study is shown with the first author that conducted the study, number of networks or metawebs that contains, type of information that contains (weighted or unweighted),  the structure (web or metaweb), year of publication and digital object identifier or permanent link for each study.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, repeat_header_method="replace" ,full_width=F,position = "left")
-
-```
-
-\end{landscape}
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-d <- readRDS("Data/RData/table_categorical_tukey_test.rds")
-
-#Again im getting the same error on this rmd so I run it on another one, save the dataframe and plot it here
-
-#Plot table
-#Add latex format in markdown
-
-kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Table S2.
-Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
- kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S3.
-Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Microlitres of Nectar per flower" , "Pollen per flower","Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
-kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S4.
-Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-#SELFING
-selfing <- readRDS("Data/RData/selfing_phylo.rds")
-#FLOWER NUMBER
-flower_n <- readRDS("Data/RData/flower_n_phylo.rds")
-#INFLO WIDTH
-inflow_width <- readRDS("Data/RData/inflow_width_phylo.rds")
-#FLOWER WIDTH
-flower_width <- readRDS("Data/RData/flower_width_phylo.rds")
-#FLOWER LENGHT
-flower_length <- readRDS("Data/RData/flower_length_phylo.rds")
-#STYLE LENGTH
-style_n <- readRDS("Data/RData/style_n_phylo.rds")
-#OVULE NUMBER
-ovule_n <- readRDS("Data/RData/ovule_n_phylo.rds")
-#PLANT HEIGHT
-plant_height <- readRDS("Data/RData/plant_height_phylo.rds")
-#POLLEN
-pollen <- readRDS("Data/RData/pollen_phylo.rds")
-#Nectar ul
-nectar_ul <- readRDS("Data/RData/Nectar_ul_phylo.rds")
-
-#Not included at the end
-#Nectar mg
-#nectar_mg <- readRDS("Data/RData/Nectar_mg_phylo.rds")
-#Nectar concentration
-nectar_con <- readRDS("Data/RData/Nectar_concentration_phylo.rds")
-
-#Select two decimals function
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-#LABELS
-label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Nectar per flower ($\\mu$l)", "Nectar concentration ($\\%$)","Pollen grains per flower")
-#LAMBDA
-lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, nectar_ul$lambda, nectar_con$lambda, pollen$lambda)
-#P-VALUE
-p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P,nectar_ul$P,  nectar_con$P, pollen$P)
-
-tabla <- data.frame(label, specify_decimal(lambda,2), specify_decimal(p_value,2))
-
-colnames(tabla) <- c("Functional traits", "Lambda", "P-value")
-
-kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,caption = "\\textbf{Table S5. Phylogenetic signal of the different quantitative traits.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.cap="\\textbf{Fig.
-S1.} Map with the different locations of the plant-pollinator studies used in this work to explore woldwide patterns at the meso-scale level.
-Note that for visualization purposes studies from the same authors are shown with the same colour."}
-
-#Create coordinate dataset for plotting
-
-longitude <- c("3.296797",  #1
-               "1.575532", #2
-               "9.275556", 
-               "18.5", #4
-               "99.63806", #5
-               "148.266667",
-               "-52", 
-               "-31", "57.43", #8
-               "-75.5", #9
-               "-57.885", #10
-               "55.447778",
-               "-6.16895", #12bart
-               "55.43333", #13
-               "57.733333",
-               "-68.015892", #15
-               "-89.8968771",
-               "171.756111",
-               "10.233333",
-               "-90.35",
-               "-93.8968771",#Robertson
-               "-67.4292900",
-               "-61.71666666666667",
-               "175.756111",
-               "-71.3",
-               "129.387359", #Kevan
-               "135.75385",
-               "-93.35",
-               "10.219072")
-
-latitude <- c("42.315336", #1
-              "52.762395", #2
-              "56.0725",
-              "68.35", #4
-              "27.90139", #5
-              "-36.45", #6
-              "71", #7
-              "39.4", "-23.25", #8 #modified for visibility of ovelapping
-              "45.4", #9
-              "-21.701111", #10
-              "-7.67",#11 #modified for visibility of ovelapping
-              "37.234966", #12bart
-              "-4.666667", #13
-              "-20.4538",
-              "-32.008985", #15
-              "39.278958",
-              "-43.035889",
-              "59.066667",#18 #modified for visibility of ovelapping
-              "-0.533333",
-              "39.278958", #Robertson 
-              "8.9241600",
-              "5.5833333",
-              "-43.035889",
-              "81.8166667",
-              "28.288661", #Kevan 
-              "35.02107",
-              "-0.533333",
-              "56.069108")
-
-id <- c("Bartomeus1", #1
-        "Dicks", #2
-        "Dupont", 
-        "Elberling", #4
-        "Fang", #5
-        "Inouye1", #6
-        "Lundgren", #7
-        "Olesen", "Olesen", #8
-        "Small", #9
-        "Souza", #10
-        "Kaiser-Bunbury1", #
-        "Bartomeus2", #12
-        "Kaiser-Bunbury2", #13
-        "Kaiser-Bunbury3", #14
-        "Peralta", #15
-        "Burkle",
-        "Arroyo-Correa",
-        "Bundgaard",
-        "Traveset",
-        "Robertson",
-        "Ramirez1",
-        "Ramirez2",
-        "Primack",
-        "Kevan",
-        "Kato",
-        "Inouye2",
-        "McMullen",
-        "Baek")
-
-d <- data.frame(longitude, latitude, id)
-
-library("ggplot2")
-library("sf")
-library("rnaturalearth")
-library("rnaturalearthdata")
-
-world <- ne_countries(scale = "medium", returnclass = "sf")
-class(world)
-
-d$longitude <- as.numeric(d$longitude)
-d$latitude <- as.numeric(d$latitude)
-
-sf::sf_use_s2(FALSE)
-
-#these colors come from the library(pals)- labs = c('alphabet')
-
-colors <- c("red4", "#0075DC", "#4C005C", "#4C005C", "#993F00",  "#5EF1F2", 
-        "#005C31", "#2BCE48", "black", "lightblue", "darkorange3", "darkorange3","#8F7C00",
-        "#8F7C00","#8F7C00", "#9DCC00", "#C20088", "gold1","#FFA8BB","#426600","94FFB5","#003380",  
-         "#FF0010","#FF0010", "salmon", "seashell3","greenyellow","mediumaquamarine")
-
-set.seed(12)
-ggplot(data = world) +
-  geom_sf(fill="antiquewhite", color="grey49") +
-  xlab("Longitude") + ylab("Latitude") +
-  geom_point(data=d , aes(longitude,latitude,  color=id),  shape=10,
-           size = 3.5, stroke=1)+ 
-  theme(panel.grid.major = element_line(color = gray(.5), 
-linetype = "dashed", size = 0), panel.background = element_rect(fill = "aliceblue"))+
-  coord_sf(expand = FALSE) +  scale_y_continuous(breaks = c(-50,0, 50)) +
-  scale_x_continuous(breaks = c(-100,0, 100)) +
-  theme(legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=6),
-         legend.title = element_text(size=12)) +   scale_colour_manual(values = colors) + labs(colour="Plant-pollinator studies")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Fig. S2.} Percentage of present and missing values of the different plant traits."}
-
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-
-########################################################################################################################################################
-#SCRIPT FOR DATA IMPUTATION
-########################################################################################################################################################
-#1) READ TRAIT DATA
-
-#2) CLEAN DATA AND RENAME LEVELS
-
-#3) EXPLORE PATTERNS OF MISSING DATA
-
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-
-#5) ICLUDE EIGENVALUES IN RAWDATA TO IMPROVE IMPUTATION OURPUT
-
-#6) IMPUTE DATA
-
-#7) SAVE IMPUTED DATA 
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(missMDA) #For missing values
-library(FactoMineR) #Produce pca biplot with individuals and variables
-library(factoextra)
-library(ggpubr) 
-library(missForest) #random forst imputation
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(ape)
-library(PVR) #calculate eigen vectors and add them as a column in the imputation, seems to improve output
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-str(trait_data_1)
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-levels(as.factor(trait_filtered$Info_level)) #checking levels
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-str(trait_filtered_2)
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-                        "Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-levels(as.factor(t$Breeding_system))
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-levels(as.factor(t$Flower_morphology))
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-levels(as.factor(t$lifespan))
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-#Explore patterns of missing data
-missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)
-sort(missing_data[missing_data >= 0], decreasing=T)
-#nectar values all above 50% except presence/absence
-#then, just one cololumn with 68% missing data, then one with 35% and then 20% and 10%. The rest under 5%.
-#it is recommended to remove columns over 50% but we are particulary interested in having numeric levels of quantitative selfing 
-#we are going to work just with presence/absence of nectar
-#we will perform further analysis just with a subset with the quantitative values o nectar (very interesting data and diffciult to obtain)
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-         "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-         "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-         "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-         "Pollen_per_flower")]
-
-#check missing data now
-missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)*100
-sort(missing_data[missing_data >= 0], decreasing=T)
-
-missing_data <- unlist(lapply(t, function(x) nrow(t)-sum(is.na(x))))
-sum(missing_data)
-
-#Number of missing values on the datset
-#vis_miss(t[,c(6:20)])
-#9.9% percentage of missing values]
-
-#Checking number of filled cells/ just selecting variables used in the manuscript; nectar ul should be accounted too and it has been considered but
-#not added to run this code
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-str(t)
-
-#Impute data considering phylogenetic distance of species
-#it improves quality of imputation
-#https://doi.org/10.1111/2041-210X.12232 see ref for method comparisons with and without imputation
-
-#Multiple imputation process with phylogeny --> Missforest
-#https://doi.org/10.1111/2041-210X.12232
-#althought it does not have an option we are going to add it as a column
-
-#Before data imputation I need to calculate the phylo of the species
-#remove not found species that do not run with get tree
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-levels(factor(t$Species_all))
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-#Select just columns with traits
-t <- t[c("Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-         "Pollen_per_flower")]
-
-#################################################
-#3)SUMMARY OF THE DATA|ALL COLS CONSIDERED!
-#################################################
-##Number of filled cells
-#nrow(t) * 16 - sum(is.na(t))#[1] 20737
-##Dimension of the dataset
-#nrow(t) * 16#[1] 24096
-##Number of missing values
-#sum(is.na(t))#[1] 3359
-##Percentage of filled cells
-#sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 86.87993
-##Percentage of missing values
-#sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 13.12007
-#
-#
-
-#Function to specify number of decimals
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-no_missing <- specify_decimal(sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
-missing <- specify_decimal(sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
-
-colnames(t) <- c("Breeding system","Compatibility system",
-         "Autonomous selfing qualitative","Autonomous selfing quantitative", "Flower shape", "Flower symmetry", 
-         "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 
-         "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar per flower (microlitres)", "Nectar per flower (miligrames)", "Nectar concentration (%)", "Pollen grains per flower")
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-levels <-
-  (missing.values  %>% filter(isna == T) %>% arrange(desc(pct)))$key
-
-percentage.plot <- missing.values %>%
-  ggplot() +
-  geom_bar(aes(x = reorder(key, desc(pct)), 
-               y = pct, fill=isna), 
-           stat = 'identity', alpha=0.8) +
-  scale_x_discrete(limits = levels) + theme_bw()+
-  scale_fill_manual(name = "", 
-                    values = c('#57a340', '#d24513'), labels = c("Present values", "Missing values")) +
-  coord_flip() +
-  labs(title = "", x =
-         '', y = "")+  scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
-  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))
-
-percentage.plot
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig.
-S3.}  Phylogenetic informed principal component analysis for the species that did not have missing values."}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_complete_cases.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-#PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-pc3 <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.015, 0.03, 0.07), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,5.2,5,5.25,6.3,6)), y = -(PCAloadings$PC2*c(4,4.75,4,4.5,5,5.5)+c(0,0,0,0,-0.04,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-pc3(PC)
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24,  fig.cap="\\textbf{Fig.
-S4.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation.
-The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates."}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot_apis <- readRDS("Plot_apis_non_apis.rds")
-
-plot_apis
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig.
-S5.} Regression tree analyses.
-Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
-"}
-
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
-########################################################################################################################################################
-#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
-
-library(rpart.plot)
-library(rpart)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
-nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
-d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")
-
-#run  regression trees of the 3 metrics
-set.seed(1)
-tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0054559,minbucket=50)
-
-set.seed(1)
-tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0084459,minbucket=50)
-
-set.seed(1)
-tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0072192 , minbucket=50) #10
-
-#NECTAR AND POLEN DATA
-v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
-nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
-d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
-
-#Set correct colnames for plotting
-colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-set.seed(2)
-tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
-
-set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
-
-set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)
-
-par(mfrow=c(3,2))
-
-rpart.plot(tree_1, box.palette="GnOr", main="A Interaction frequency for all species", cex.main=1.85,tweak = 1.10) 
-rpart.plot(tree1, box.palette="GnOr", main="B Interaction frequency for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-rpart.plot(tree_2, box.palette="GnOr", main="C Normalized degree for all species", cex.main=1.85,tweak = 1.10)
-rpart.plot(tree2, box.palette="GnOr", main="D Normalized degree for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-rpart.plot(tree_3, box.palette="GnOr", main="E Specialization for all species", cex.main=1.85,tweak = 1.10) 
-rpart.plot(tree3, box.palette="GnOr", main="F Specialization for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig.
-S6.} PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species."}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-pc3 <- function(PC, x="PC1", y="PC3") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC3 ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,4.8,7.1,5.5)), y = -(PCAloadings$PC2*c(-3.2,4.5,3.75,8.4,5,5.5)+c(0,0,0,0,-0.08,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-pc3(PC)
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=10,out.width="85%",fig.align='center',fig.cap="\\textbf{Fig.
 S7.} Phylogenetic informed principal component analysis for the subset of species with floral rewards."}
@@
   #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height", "Nectar","Pollen" )
+  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants", "Copious nectar","Copious pollen")
 
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,4.8,4.8,5.5,5,5.5,5.8,6.5)), y = -(PCAloadings$PC2*c(4.8,4.4,4.15,5.35,5,4.7,5.75,6)+c(0,0,0,0,0,0,0,0)),
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,4.8,4.8,5.5,5.5,5.5,5.8,6.5)), y = -(PCAloadings$PC2*c(4.8,4.4,4.15,5.35,4.2,4.7,5.75,6)+c(0,0,0,0,0,0,0,0)),
                           label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
@@
 
-all_spp(PC)
+p1 <- all_spp(PC)
 
-```
+#Load data
+phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen_complete_cases.rds")
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen_complete_cases.rds")
 
-\newpage
-\thispagestyle{empty}
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig.
-S8.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species.
-Categories that differ significantly are denoted with a different letter."}
+PC <- phyl_pca_forest_nectar_pollen
+#CHECK CONTENT
+#EIGENVALUES
+PC$Eval
+#PC score (POINTS)
+PC$S
+#PC loadings (ARROWS)
+PC$L
 
-########################################################################################################################################################
-#CORRELATION BETWEEN QUALITATIVE VARIABLES AND PC's
-########################################################################################################################################################
-#NOTES
-#I did not include the qualitative variables when I prepare the data for the PPCA
-#So I have to recalculate the ata here with the qualitative variables
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(emmeans)
-library(ggplot2)
-library(patchwork)
-library(dplyr)
+#############################################################################################################################################################
+#COMPATIBILITY
+#############################################################################################################################################################
+#Load plots
+PC$S[,1] <- -PC$S[,1]
+PC$S[,2] <- -PC$S[,2]
 
-theme_ms <- function(base_size=10, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(1.3)),
-           axis.text=element_text(size = rel(1.1), color = "black"),
-           panel.border=element_rect(color="black",size=1.2),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           legend.position = "none",
-           plot.title = element_text(face = "bold",size = rel(1.55)),
-           plot.subtitle = element_text(face = "bold",size = rel(1.4))
-     ))
+all_spp_complete <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
   }
 
-########################################################################################################################################################
-setwd("~/R_Projects/Reproductive Traits")
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
 
-#LOAD DATA
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-dat <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-########################################################################################################################################################
-#remove not found species, cannot do PCA with unequal numbers of rows
-cols.num <- c("Family_all","Genus_all","Species_all")
-dat[cols.num] <- sapply(dat[cols.num],as.character)
-dat$Species_all <- gsub("Species_all_", "", dat$Species_all)
-########################################################################################################################################################
-#3) REMOVE OUTLIERS, OUT OF 2.5-97.5 RANGE WHICH HELPS IMPUTATION PROCESS. SEE ARTICLE FOR REF.
-########################################################################################################################################################
-dat_cleaning <- dat[,]
-#CHECK LEVELS
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
+    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
+    scale_alpha(guide = 'none')
 
-dat_cleaning_1 <- dat_cleaning %>%
-  filter(between(Flowers_per_plant, quantile(Flowers_per_plant, 0.025), quantile(Flowers_per_plant, 0.975)))
+  plot <- plot + geom_point(data=dat, aes(x, y),size=0.95, color="black")
 
-dat_cleaning_2 <- dat_cleaning_1 %>%
-  filter(between(Corolla_diameter_mean, quantile(Corolla_diameter_mean, 0.025), quantile(Corolla_diameter_mean, 0.975)))
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .7 * mult * (get(x)),
+                      v2 = .7 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
 
-dat_cleaning_3 <- dat_cleaning_2 %>%
-  filter(between(Style_length, quantile(Style_length, 0.025), quantile(Style_length, 0.975)))
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=-v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
 
-dat_cleaning_4 <- dat_cleaning_3 %>%
-  filter(between(Ovule_number, quantile(Ovule_number, 0.025), quantile(Ovule_number, 0.975)))
+  #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
 
-dat_cleaning_5 <- dat_cleaning_4 %>%
-  filter(between(Plant_height_mean_m, quantile(Plant_height_mean_m, 0.025), quantile(Plant_height_mean_m, 0.975)))
+  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
 
-final_d <- dat_cleaning_5[,]
+  #CHANGE THEME
 
-pca_data <- as.data.frame(phyl_pca_forest$S)
+  plot <- plot + theme_bw()
 
-d <- cbind(final_d, pca_data)
+  #ADD LABELS
+  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants", "Copious nectar","Copious pollen")
 
-#Prepare qualitative variables
-d$Compatibility_system[d$Compatibility_system=="dioecious"] <- "Unisexual flowers"
-d$Compatibility_system[d$Compatibility_system=="monoecious"] <- "Unisexual flowers"
-d$Compatibility_system[d$Compatibility_system=="partially_self_compatible"] <- "Partially self compatible"
-d$Compatibility_system[d$Compatibility_system=="self_compatible"] <- "Self compatible"
-d$Compatibility_system[d$Compatibility_system=="self_incompatible"] <- "Self incompatible"
-d$Compatibility_system <- factor(d$Compatibility_system, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,4.8,5.4,5,4.2,5.8,3.4)+c(0,0,0,0,0,0,0,0)), y = -(PCAloadings$PC2*c(4.693,3.5,4,4,3,4.15,4.2,6.2)),
+                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
 
-d$life_form[d$life_form=="herb"] <- "Herb"
-d$life_form[d$life_form=="shrub"] <- "Shrub"
-d$life_form[d$life_form=="tree"] <- "Tree"
-d$life_form[d$life_form=="vine"] <- "Shrub"
-
-d$Flower_symmetry[d$Flower_symmetry=="actinomorphic"] <- "Actinomorphic"
-d$Flower_symmetry[d$Flower_symmetry=="zygomorphic"] <- "Zygomorphic"
-
-d$Flower_symmetry[d$Flower_symmetry=="Funnelform"] <- "Campanulate"
-d$Flower_symmetry[d$Flower_symmetry=="Spike"] <- "Brush"
-
-d$Flower_morphology[d$Flower_morphology=="Funnelform"] <- "Campanulate"
-d$Flower_morphology[d$Flower_morphology=="Spike"] <- "Brush"
-
-d$Nectar_presence_absence[d$Nectar_presence_absence=="yes"] <- "Yes"
-d$Nectar_presence_absence[d$Nectar_presence_absence=="no"] <- "No"
-
-#The other qualitative are ok
-
-#All principal components are normally distributed
-#Convert to factor before running model
-d[sapply(d, is.character)] <- lapply(d[sapply(d, is.character)], as.factor)
-
-#Run model
-model1 <- lm(PC1 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
-model2 <- lm(PC2 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
-
-####################################################################################################################################################################################################################################
-#1) BREEDING SYSTEM
-####################################################################################################################################################################################################################################
-model_breeding_1 <- emmeans(model1, "Breeding_system")
-breeding_1 <- as.data.frame(model_breeding_1[1:3])
-breed1 <- multcomp::cld(model_breeding_1, alpha = 0.10, Letters = LETTERS)
-
-breed_1 <- ggplot(breed1,aes(x= Breeding_system,y= emmean,
-               label = .group)) +theme_minimal()+
-  geom_point(data = breed1, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "A Breeding system")+
-  theme(plot.title = element_text(hjust=0.5, size=25, face="bold"))+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-model_breeding_2 <- emmeans(model2, "Breeding_system")
-breeding_2 <- as.data.frame(model_breeding_2[1:3])
-breed2 <- multcomp::cld(model_breeding_2, alpha = 0.10, Letters = LETTERS)
-
-breed_2 <- ggplot(breed2,aes(x= Breeding_system,y= emmean,
-             label = .group)) +theme_minimal()+
-  geom_point(data = breed2, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "B Breeding system")+
-  theme(plot.title = element_text(hjust=0.5,size=25, face="bold") )+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-########################################################################################################################################################
-#2) COMPATIBILITY
-########################################################################################################################################################
-model_com <- emmeans(model1, "Compatibility_system")
-
-d <- as.data.frame(model_com[1:4])
-comp1 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
-
-comp_1 <- ggplot(comp1,aes(x= Compatibility_system,y= emmean,
-  label = .group)) +theme_minimal()+
-  geom_point(data = comp1, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
-  width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "C Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
-
-model_com <- emmeans(model2, "Compatibility_system")
-d <- as.data.frame(model_com[1:4])
-comp2 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
-
-comp_2 <- ggplot(comp2,aes(x= Compatibility_system,y= emmean,
-  label = .group)) +theme_minimal()+
-  geom_point(data = comp2, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
-  width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "D Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
-
-########################################################################################################################################################
-#3) LIFESPAN
-########################################################################################################################################################
-model_lif_1 <- emmeans(model1, "lifespan")
-lif_1 <- as.data.frame(model_lif_1[1:2])
-lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
-
-lifespan_1 <- ggplot(lif_1,aes(x= lifespan,y= emmean,
-             label = .group)) +theme_minimal()+
-  geom_point(data = lif_1, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "E Lifespan")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-model_lif_2 <- emmeans(model2, "lifespan")
-lif_2 <- as.data.frame(model_lif_2[1:2])
-lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
-
-lifespan_2 <- ggplot(lif_2,aes(x= lifespan,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_2, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "F Lifespan")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")
-
-########################################################################################################################################################
-# 4) LIFE FORM
-########################################################################################################################################################
-
-model_lif_1 <- emmeans(model1, "life_form")
-lif_1 <- as.data.frame(model_lif_1[1:3])
-lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
-
-lifeform_1 <- ggplot(lif_1,aes(x= life_form,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_1, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "G Life form")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-model_lif_2 <- emmeans(model2, "life_form")
-lif_2 <- as.data.frame(model_lif_2[1:3])
-lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
-
-lifeform_2 <- ggplot(lif_2,aes(x= life_form,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_2, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "H Life form")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-########################################################################################################################################################
-# 5) FLOWER MORPHOLOGY
-########################################################################################################################################################
-model_flo_1 <- emmeans(model1, "Flower_morphology")
-flo_1 <- as.data.frame(model_flo_1[1:6])
-flo_1 <- multcomp::cld(model_flo_1, alpha = 0.10, Letters = LETTERS)
-
-shape_1 <- ggplot(flo_1,aes(x= Flower_morphology,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_1, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "I Flower shape")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")
-
-model_flo_2 <- emmeans(model2, "Flower_morphology")
-flo_2 <- as.data.frame(model_flo_2[1:6])
-flo_2 <- multcomp::cld(model_flo_2, alpha = 0.10, Letters = LETTERS)
-
-shape_2 <- ggplot(flo_2,aes(x= Flower_morphology,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_2, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "J Flower shape")+
-   geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
-
-########################################################################################################################################################
-#6) FLOWER SYMMETRY
-########################################################################################################################################################
-model_flo_sym_1 <- emmeans(model1, "Flower_symmetry")
-flo_sym_1 <- as.data.frame(model_flo_sym_1[1:2])
-flo_sym_1 <- multcomp::cld(model_flo_sym_1, alpha = 0.10, Letters = LETTERS)
-
-symmetry_1 <-ggplot(flo_sym_1,aes(x= Flower_symmetry,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_sym_1, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "K Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
-
-model_flo_sym_2 <- emmeans(model2, "Flower_symmetry")
-flo_sym_2 <- as.data.frame(model_flo_sym_2[1:2])
-flo_sym_2 <- multcomp::cld(model_flo_sym_2, alpha = 0.10, Letters = LETTERS)
-
-symmetry_2 <- ggplot(flo_sym_2,aes(x= Flower_symmetry,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = flo_sym_2, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title = "L Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-########################################################################################################################################################
-#7) NECTAR
-########################################################################################################################################################
-model_nec <- emmeans(model1, "Nectar_presence_absence")
-
-model_nec_1 <- emmeans(model1, "Nectar_presence_absence")
-nec_1 <- as.data.frame(model_nec_1[1:2])
-nec_1 <- multcomp::cld(model_nec_1, alpha = 0.10, Letters = LETTERS)
-
-nectar_1 <- ggplot(nec_1,aes(x= Nectar_presence_absence,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = nec_1, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "M Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-model_nec_2 <- emmeans(model2, "Nectar_presence_absence")
-nec_2 <- as.data.frame(model_nec_2[1:2])
-nec_2 <- multcomp::cld(model_nec_2, alpha = 0.10, Letters = LETTERS)
-
-nectar_2 <-ggplot(nec_2,aes(x= Nectar_presence_absence,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = nec_2, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "N Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")
-
-#PLOT!
-
-breed_1 + breed_2+ comp_1+ comp_2+ lifespan_1+ lifespan_2+ lifeform_1+ lifeform_2+ shape_1+ shape_2+
-symmetry_1+ symmetry_2+ nectar_1+ nectar_2 + plot_layout(ncol = 2)
-
-```
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Fig.
-S9.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation.
-Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
-For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)"}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot <- readRDS("Plot_bee_families.rds")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
 
@@
 
-```
+}
 
-\elandscape
+p2 <- all_spp_complete(PC)
 
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S10.} Plant species level metrics across the three main axes of trait variation.", fig.pos= "h"}
-
-#library(brms) #modelling
-library(cowplot) #panel of plots
-library(ggplot2) #plotting
 library(patchwork)
 
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(3.5)),
-           axis.text=element_text(size = rel(2.75), color = "black"),
-           legend.title=element_text(face="bold"),
-           legend.text=element_text(),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(0.4, 'lines'),
-           panel.border=element_rect(color="black",size=3),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-#########
-
-setwd("~/Dropbox/PhD/R/Chapter_2")
-
-#read plot generated in other rmd, bms and stan are giving trouble here... This file is created in Species_Level_Metric_Pcs
-
-plot_metrics_pcs <- readRDS("plot_metrics_pcs.rds")
-
-plot_metrics_pcs
+p1 / p2 + plot_annotation(tag_levels = 'A') & 
+  theme(plot.tag = element_text(size = 24, face="bold"))
 
 ```
-
-\elandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S11.} Pearson correlation between the product of flower number-flower size and autonomous selfing level.", fig.pos= "h"}
-
-theme_ms <- function(base_size=18, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(2.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-#LOAD LIBRARIES
-library(ggplot2)
-library(ggpubr)
-
-#LOAD DATA
-dat <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-
-#CONDUCT PRODUCT FLOWER NUMBER-FLOWER SIZE
-dat$Product <-      log(dat$Flowers_per_plant * dat$Corolla_diameter_mean+1)
-
-ggscatter(dat, x = "Autonomous_selfing_level_fruit_set", y = "Product", 
-          add = "reg.line", conf.int = TRUE,
-          cor.coef = TRUE, cor.method = "pearson",size=5,cor.coef.size=15,
-          xlab = "Autnomous selfing", ylab = "Product flower size-number") +
-  theme_ms() +ylim(0,16)
-
-```

### 2022-06-02 Supplementary_Material/Subset_spp_floral_rewards_and_completecases_PPCA.Rmd
Supp mat update

@@
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,4.8,5.4,5,4.2,5.8,3.4)+c(0,0,0,0,0,0,0,0)), y = -(PCAloadings$PC2*c(4.693,3.5,4,4,3,4.15,4.2,6.2)),
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,4.8,5.4,5,4.2,5.8,3.4)+c(0,0,0,0,0,0,0,0)), y = -(PCAloadings$PC2*c(4.693,3.5,4,4,3,4.15,4.2,6.5)),
                           label = PCAloadings$Variables, color="black",fontface =2,size=4.5)

### 2022-06-02 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
Supp mat update

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig.
-S3.}  Phylogenetic informed principal component analysis for the species that did not have missing values."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=20, fig.width=10,out.width="80%",fig.align='center',fig.cap= "\\textbf{Fig.
+S3.} Comparison of the phylogenetic informed principal component analysis for the dataset with data imputation and without data imputation.
+Panel A shows the reproductive spectrum of trait variation for the full dataset with data imputation and panel B shows the reproductive spectrum for the dataset without data imputation where the species with missing trait data were excluded from the analysis."}
+
+setwd("~/R_Projects/Reproductive Traits")
+
+#Load libraries
+library(viridis) #COLOUR GGPLOT
+library(ggplot2)
+library(broman) #crayon colours
+library(cowplot)
+library(magick)
+
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+      theme(text=element_text(color="black"),
+            axis.title=element_text( size = rel(1.75)),
+            axis.text=element_text(size = rel(1.75), color = "black"),
+            legend.title=element_text(face="bold"),
+            legend.text=element_text(),
+            legend.background=element_rect(fill="transparent"),
+            legend.key.size = unit(1.2, 'lines'),
+            panel.border=element_rect(color="black",size=1),
+            panel.grid.minor.x =element_blank(),
+            panel.grid.minor.y= element_blank(),
+             panel.grid.major= element_blank()
+      ))
+}
+
+#Load data
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+PC <- phyl_pca_forest
+#CHECK CONTENT
+#EIGENVALUES
+PC$Eval
+#PC score (POINTS)
+PC$S
+#PC loadings (ARROWS)
+PC$L
+
+#Images were made by Paula Martin
+#Check her work on https://paulamartinart.com/
+
+#############################################################################################################################################################
+#COMPATIBILITY
+#############################################################################################################################################################
+#Load plots
+
+#Invert axes
+PC$S[,1] <- -PC$S[,1]
+PC$S[,2] <- -PC$S[,2]
+
+all_spp <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
+  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
+    scale_alpha(guide = 'none')
+
+    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .7 * mult * (get(x)),
+                      v2 = .7 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+
+   #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+
+#ADD LABELS
+  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+ plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
+                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
+
+# plot <- plot + annotate("text", x = #(PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = #(PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0))#,
+#                         label =c("Low selfing", "Few flowers", #"Small flowers", "Short styles", "Few ovules", "Short plants" ), #color="black",fontface =2,size=4)
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
+
+  plot
+
+}
+
+p1 <- all_spp(PC)
+
+#Load data
+dat_cleaning_5 <- readRDS("Data/RData/data_complete_cases.rds")
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")
+
+PC <- phyl_pca_forest
+#CHECK CONTENT
+#EIGENVALUES
+PC$Eval
+#PC score (POINTS)
+PC$S
+#PC loadings (ARROWS)
+PC$L
+
+#############################################################################################################################################################
+#COMPATIBILITY
+#############################################################################################################################################################
+#Load plots
+
+#Invert axes
+#PC$S[,1] <- -PC$S[,1]
+PC$S[,2] <- -PC$S[,2]
+
+all_complete_cases <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
+  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.015, 0.03, 0.07), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
+    scale_alpha(guide = 'none')
+
+    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .7 * mult * (get(x)),
+                      v2 = .7 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+
+   #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+
+  #CHANGE THEME
+
+  plot <- plot + theme_bw() 
+      #ADD LABELS
+  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+ plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,5.2,5,5.25,6.3,6)), y = -(PCAloadings$PC2*c(4,4.75,4,4.5,5,5.5)+c(0,0,0,0,-0.04,0)),
+                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
+
+  plot
+
+}
+
+p2 <- all_complete_cases(PC)
+
+library(patchwork)
+
+p1 / p2 + plot_annotation(tag_levels = 'A') & 
+  theme(plot.tag = element_text(size = 24, face="bold"))
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=10,out.width="80%",fig.align='center',fig.cap="\\textbf{Fig.
+S4.} Comparison of the phylogenetic informed principal component analysis for the subset of species that had information of floral rewards with data imputation and without data imputation.
+Panel A shows the reproductive spectrum of trait variation for the dataset with data imputation and panel B shows the reproductive spectrum for the dataset excluding species with missing trait data"}
 setwd("~/R_Projects/Reproductive Traits")
@@
 #Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_complete_cases.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")
-
-PC <- phyl_pca_forest
+phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
+dat_cleaning_7 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen.rds")
+
+PC <- phyl_pca_forest_nectar_pollen
 #CHECK CONTENT
@@
 
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-#PC$S[,1] <- -PC$S[,1]
+library(magick)
+
+#Images were made by Paula Martin
+PC$S[,1] <- -PC$S[,1]
+
 PC$S[,2] <- -PC$S[,2]
 
-pc3 <- function(PC, x="PC1", y="PC2") {
+all_spp <- function(PC, x="PC1", y="PC2") {
   # PC being a prcomp object
@@
 
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.015, 0.03, 0.07), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
+    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
     scale_alpha(guide = 'none')
@@
 
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
+  plot <- plot + theme_bw()
 
   #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
+  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants", "Copious nectar","Copious pollen")
 
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,5.2,5,5.25,6.3,6)), y = -(PCAloadings$PC2*c(4,4.75,4,4.5,5,5.5)+c(0,0,0,0,-0.04,0)),
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,4.8,4.8,5.5,5.5,5.5,5.8,6.5)), y = -(PCAloadings$PC2*c(4.8,4.4,4.15,5.35,4.2,4.7,5.75,6)+c(0,0,0,0,0,0,0,0)),
                           label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
@@
 
-pc3(PC)
+p1 <- all_spp(PC)
+
+#Load data
+phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen_complete_cases.rds")
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen_complete_cases.rds")
+
+PC <- phyl_pca_forest_nectar_pollen
+#CHECK CONTENT
+#EIGENVALUES
+PC$Eval
+#PC score (POINTS)
+PC$S
+#PC loadings (ARROWS)
+PC$L
+
+#############################################################################################################################################################
+#COMPATIBILITY
+#############################################################################################################################################################
+#Load plots
+PC$S[,1] <- -PC$S[,1]
+PC$S[,2] <- -PC$S[,2]
+
+all_spp_complete <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
+    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
+    scale_alpha(guide = 'none')
+
+  plot <- plot + geom_point(data=dat, aes(x, y),size=0.95, color="black")
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .7 * mult * (get(x)),
+                      v2 = .7 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=-v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+
+  #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+
+  #CHANGE THEME
+
+  plot <- plot + theme_bw()
+
+  #ADD LABELS
+  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants", "Copious nectar","Copious pollen")
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,4.8,5.4,5,4.2,5.8,3.4)+c(0,0,0,0,0,0,0,0)), y = -(PCAloadings$PC2*c(4.693,3.5,4,4,3,4.15,4.2,6.5)),
+                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
+
+  plot
+
+}
+
+p2 <- all_spp_complete(PC)
+
+library(patchwork)
+
+p1 / p2 + plot_annotation(tag_levels = 'A') & 
+  theme(plot.tag = element_text(size = 24, face="bold"))
 
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24,  fig.cap="\\textbf{Fig.
-S4.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation.
+S5.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation.
 The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates."}
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig.
-S5.} Regression tree analyses.
+S6.} Regression tree analyses.
 Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
@@
 
+\newpage
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig.
-S6.} PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species."}
+S7.} Phylogenetic informed principal component analysis for the subset of species with floral rewards."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 #Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-pc3 <- function(PC, x="PC1", y="PC3") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC3 ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,4.8,7.1,5.5)), y = -(PCAloadings$PC2*c(-3.2,4.5,3.75,8.4,5,5.5)+c(0,0,0,0,-0.08,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-pc3(PC)
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig.
-S7.} Phylogenetic informed principal component analysis for the subset of species with floral rewards."}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
 phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")

### 2022-06-03 Manuscript/Lanuza_et_al_2021.Rmd
edit

@@
 
-To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
+To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of datasets with continuous and categorical variables.
 We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of *missForest* [@penone2014].
@@
 First, we investigated how the different groups of floral visitors interacted along the main axes of reproductive trait variation (see below 'visitation patterns' section) with the help of qualitative and quantitative information of plant-pollinator interactions.
-For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that account for the intensity of the interaction.
+For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
 Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency [@ballantyne2015], the number of visits can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
@@
 We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with non or very weakly informative informative priors from the brm function so they have neglible influence on the results [@burkner2017], 3,000 iterations and with previous 1,000 warm up iterations.
+The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results [@burkner2017].
 We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the *bayesplot* package [@gabry2019].
@@
 Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the 'visitation patterns' section.
+
+[Aqui hay que convencer que usar el dataset de floral rewards es lo mas adecuado]()
 

### 2022-06-03 Manuscript/Lanuza_et_al_2021.tex
edit

@@
 
-To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} (\protect\hyperlink{ref-stekhoven2012}{Stekhoven \& Bühlmann, 2012}) which allows imputation of data sets with continuous and categorical variables.
+To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} (\protect\hyperlink{ref-stekhoven2012}{Stekhoven \& Bühlmann, 2012}) which allows imputation of datasets with continuous and categorical variables.
 We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} (\protect\hyperlink{ref-penone2014}{Penone et al., 2014}).
@@
 First, we investigated how the different groups of floral visitors interacted along the main axes of reproductive trait variation (see below `visitation patterns' section) with the help of qualitative and quantitative information of plant-pollinator interactions.
-For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that account for the intensity of the interaction.
+For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
 Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency (\protect\hyperlink{ref-ballantyne2015}{Ballantyne et al., 2015}), the number of visits can provide valuable information of the contribution of floral visitors to pollination (\protect\hyperlink{ref-vazquez2005}{Vázquez et al., 2005}, \protect\hyperlink{ref-vazquez2012}{2012}).
@@
 We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with non or very weakly informative informative priors from the brm function so they have neglible influence on the results (\protect\hyperlink{ref-burkner2017}{Bürkner, 2017}), 3,000 iterations and with previous 1,000 warm up iterations.
+The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results (\protect\hyperlink{ref-burkner2017}{Bürkner, 2017}).
 We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package (\protect\hyperlink{ref-gabry2019}{Gabry et al., 2019}).

### 2022-06-06 Manuscript/Lanuza_et_al_2021.Rmd
edits

@@
 
-[Esta última parte intenta justificar la validación de nuestros resultados, le vendría bien ojo crítico, antes estaba en el siguiente párrafo pero la maldad mental para criticarnos se genera en este y pienso que ya no llega al siguiente con buenos ojos](Jose)
-
 **Plant strategies**
@@
 mellifera*, was partly driving some of the observed trends on PC1 (Fig.
-S4).
+S5).
 However, we did not detect major differences on PC2 and PC3.
@@
 
-[Aqui hay que convencer que usar el dataset de floral rewards es lo mas adecuado]()
-
 Second, to better understand complex trait relationships, we used regression trees.
@@
 We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (Fig.
-S5).
+Because pollen and nectar traits are essential to understand plant-pollinator interactions [@heinrich1972; @johnson2008; @vaudo2015], we focused in the main text on the regression trees that included floral rewards.
+Indeed, we found that nectar and pollen traits were among the best traits for explaining the different species-level metrics (Fig.
+S6).
 
@@
 1 and Fig.
-S6).
+S7).
 The first principal component (PC1) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size ('flower number - flower size').
@@
 In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82%; Fig.
-S7).
+S4).
 This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (Table S4).

### 2022-06-06 Manuscript/Lanuza_et_al_2021.tex
edits

@@
 
-\href{Jose}{Esta última parte intenta justificar la validación de nuestros resultados, le vendría bien ojo crítico, antes estaba en el siguiente párrafo pero la maldad mental para criticarnos se genera en este y pienso que ya no llega al siguiente con buenos ojos}
-
 \textbf{Plant strategies}
@@
 mellifera}, was partly driving some of the observed trends on PC1 (Fig.
-S4).
+S5).
 However, we did not detect major differences on PC2 and PC3.
@@
 We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (Fig.
-S5).
+Because pollen and nectar traits are essential to understand plant-pollinator interactions (\protect\hyperlink{ref-heinrich1972}{Heinrich \& Raven, 1972}; \protect\hyperlink{ref-johnson2008}{Johnson \& Nicolson, 2008}; \protect\hyperlink{ref-vaudo2015}{Vaudo et al., 2015}), we focused in the main text on the regression trees that included floral rewards.
+Indeed, we found that nectar and pollen traits were among the best traits for explaining the different species-level metrics (Fig.
+S6).
 
@@
 1 and Fig.
-S6).
+S7).
 The first principal component (PC1) represented 26.72\% of the trait variation and indicated a negative correlation between flower number and flower size (`flower number - flower size').
@@
 In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82\%; Fig.
-S7).
+S4).
 This pPCA explained similar variance with the first two principal components (45.52\%) and similar associations of traits despite some variability in the loadings (Table S4).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-heinrich1972}{}}%
+Heinrich, B., \& Raven, P.
+H.
+(1972).
+Energetics and pollination ecology: The energetics of pollinators may have wide implications in floral biology and community ecology.
+\emph{Science}, \emph{176}(4035), 597--602.
+
 \leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
@@
 \url{https://doi.org/10.1111/ecog.04434}
+
+\leavevmode\vadjust pre{\hypertarget{ref-johnson2008}{}}%
+Johnson, S. D., \& Nicolson, S. W. (2008). Evolutionary associations between nectar properties and specificity in bird pollination systems. \emph{Biology Letters}, \emph{4}(1), 49--52.
 
@@
 \url{https://doi.org/10.1371/journal.pone.0078294}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vaudo2015}{}}%
+Vaudo, A. D., Tooker, J. F., Grozinger, C. M., \& Patch, H. M. (2015). Bee nutrition and floral resource restoration. \emph{Current Opinion in Insect Science}, \emph{10}, 133--141.
 

### 2022-06-06 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
edits

@@
 \newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.cap="\\textbf{Fig.
+\blandscape
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.width=12, fig.height=6, fig.cap="\\textbf{Fig.
 S1.} Map with the different locations of the plant-pollinator studies used in this work to explore woldwide patterns at the meso-scale level.
@@
   geom_point(data=d , aes(longitude,latitude,  color=id),  shape=10,
-           size = 3.5, stroke=1)+ 
+           size = 4.5, stroke=1)+ 
   theme(panel.grid.major = element_line(color = gray(.5), 
@@
   scale_x_continuous(breaks = c(-100,0, 100)) +
-  theme(legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=6),
+  theme(legend.key.size = unit(0.6, 'cm'), legend.text = element_text(size=10),
          legend.title = element_text(size=12)) +   scale_colour_manual(values = colors) + labs(colour="Plant-pollinator studies")
@@
 ```
+
+\elandscape
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=20, fig.width=10,out.width="80%",fig.align='center',fig.cap= "\\textbf{Fig.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=20, fig.width=10,out.width="60%",fig.align='center',fig.cap= "\\textbf{Fig.
 S3.} Comparison of the phylogenetic informed principal component analysis for the dataset with data imputation and without data imputation.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=10,out.width="80%",fig.align='center',fig.cap="\\textbf{Fig.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=10,out.width="60%",fig.align='center',fig.cap="\\textbf{Fig.
 S4.} Comparison of the phylogenetic informed principal component analysis for the subset of species that had information of floral rewards with data imputation and without data imputation.
 Panel A shows the reproductive spectrum of trait variation for the dataset with data imputation and panel B shows the reproductive spectrum for the dataset excluding species with missing trait data"}
+setwd("~/R_Projects/Reproductive Traits")
+
+#Load libraries
+#LOAD LIBRARIES
+library(phytools)
+library(ape) #for phylogenetic distance
+library(dplyr) #data processing
+library(rtrees) #for phylogenetic distancelibrary(MASS)
+library(reshape2)
+library(viridis) #COLOUR GGPLOT
+library(MASS)
+library(ggplot2)
+library(broman) #crayon colours
+library(cowplot)
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+      theme(text=element_text(color="black"),
+            axis.title=element_text( size = rel(1.75)),
+            axis.text=element_text(size = rel(1.75), color = "black"),
+            legend.title=element_text(face="bold"),
+            legend.text=element_text(),
+            legend.background=element_rect(fill="transparent"),
+            legend.key.size = unit(1.2, 'lines'),
+            panel.border=element_rect(color="black",size=1),
+            panel.grid.minor.x =element_blank(),
+            panel.grid.minor.y= element_blank(),
+             panel.grid.major= element_blank()
+      ))
+}
+
+#Load data
+phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
+dat_cleaning_7 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen.rds")
+
+PC <- phyl_pca_forest_nectar_pollen
+#CHECK CONTENT
+#EIGENVALUES
+PC$Eval
+#PC score (POINTS)
+PC$S
+#PC loadings (ARROWS)
+PC$L
+
+library(magick)
+
+#Images were made by Paula Martin
+PC$S[,1] <- -PC$S[,1]
+
+PC$S[,2] <- -PC$S[,2]
+
+all_spp <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
+    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
+    scale_alpha(guide = 'none')
+
+  plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .7 * mult * (get(x)),
+                      v2 = .7 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+
+  #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+
+  #CHANGE THEME
+
+  plot <- plot + theme_bw()
+
+  #ADD LABELS
+  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants", "Copious nectar","Copious pollen")
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,4.8,4.8,5.5,5.5,5.5,5.8,6.5)), y = -(PCAloadings$PC2*c(4.8,4.4,4.15,5.35,4.2,4.7,5.75,6)+c(0,0,0,0,0,0,0,0)),
+                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
+
+  plot
+
+}
+
+p1 <- all_spp(PC)
+
+#Load data
+phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen_complete_cases.rds")
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen_complete_cases.rds")
+
+PC <- phyl_pca_forest_nectar_pollen
+#CHECK CONTENT
+#EIGENVALUES
+PC$Eval
+#PC score (POINTS)
+PC$S
+#PC loadings (ARROWS)
+PC$L
+
+#############################################################################################################################################################
+#COMPATIBILITY
+#############################################################################################################################################################
+#Load plots
+PC$S[,1] <- -PC$S[,1]
+PC$S[,2] <- -PC$S[,2]
+
+all_spp_complete <- function(PC, x="PC1", y="PC2") {
+  # PC being a prcomp object
+  data <- data.frame(PC$S)
+  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
+  dat <- data.frame(x = data[,x], y = data[,y])
+
+  #######
+  #DENSITY FUNCTION
+  #######
+  get_density <- function(x, y, ...) {
+    dens <- MASS::kde2d(x, y, ...)
+    ix <- findInterval(x, dens$x)
+    iy <- findInterval(y, dens$y)
+    ii <- cbind(ix, iy)
+    return(dens$z[ii])
+  }
+
+  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
+
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
+    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
+    scale_alpha(guide = 'none')
+
+  plot <- plot + geom_point(data=dat, aes(x, y),size=0.95, color="black")
+
+  ########
+  #ADD ARROWS 
+  ########
+  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
+  mult <- min(
+    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
+    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
+  )
+  datapc <- transform(datapc,
+                      v1 = .7 * mult * (get(x)),
+                      v2 = .7 * mult * (get(y))
+  )
+  # add arrows
+  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
+
+  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=-v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+
+  #Add axis with perctentage
+  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
+
+  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+
+  #CHANGE THEME
+
+  plot <- plot + theme_bw()
+
+  #ADD LABELS
+  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants", "Copious nectar","Copious pollen")
+
+  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
+  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,4.8,5.4,5,4.2,5.8,3.4)+c(0,0,0,0,0,0,0,0)), y = -(PCAloadings$PC2*c(4.693,3.5,4,4,3,4.15,4.2,6.5)),
+                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
+
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
+
+  plot
+
+}
+
+p2 <- all_spp_complete(PC)
+
+library(patchwork)
+
+p1 / p2 + plot_annotation(tag_levels = 'A') & 
+  theme(plot.tag = element_text(size = 24, face="bold"))
+
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24,  fig.cap="\\textbf{Fig.
+S5.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation.
+The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates."}
+
+library(Rcpp)
+library(patchwork)
+library(ggplot2)
+library(tidyr)
+#Load theme for publication
+
+theme_ms <- function(base_size=14, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(2.2)),
+           axis.text=element_text(size = rel(2), color = "black"),
+           legend.title=element_text(face="bold",size=rel(2)),
+           legend.text=element_text(size=rel(1.4)),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(1.8, 'lines'),
+           panel.border=element_rect(color="black",size=2.4),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank()
+     ))
+}
+
+setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
+
+#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
+
+plot_apis <- readRDS("Plot_apis_non_apis.rds")
+
+plot_apis
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig.
+S6.} Regression tree analyses.
+Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
+"}
+
+########################################################################################################################################################
+#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
+########################################################################################################################################################
+#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
+
+library(rpart.plot)
+library(rpart)
+
+setwd("~/R_Projects/Reproductive Traits")
+
+v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
+nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
+d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")
+
+#run  regression trees of the 3 metrics
+set.seed(1)
+tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0054559,minbucket=50)
+
+set.seed(1)
+tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0084459,minbucket=50)
+
+set.seed(1)
+tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0072192 , minbucket=50) #10
+
+#NECTAR AND POLEN DATA
+v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
+nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
+d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
+
+#Set correct colnames for plotting
+colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
+
+colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
+
+colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
+
+set.seed(2)
+tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
+
+set.seed(2)
+tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
+
+set.seed(2)
+tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)
+
+par(mfrow=c(3,2))
+
+rpart.plot(tree_1, box.palette="GnOr", main="A Interaction frequency for all species", cex.main=1.85,tweak = 1.10) 
+rpart.plot(tree1, box.palette="GnOr", main="B Interaction frequency for subset with floral rewards", cex.main=1.85,tweak = 1.10)
+
+rpart.plot(tree_2, box.palette="GnOr", main="C Normalized degree for all species", cex.main=1.85,tweak = 1.10)
+rpart.plot(tree2, box.palette="GnOr", main="D Normalized degree for subset with floral rewards", cex.main=1.85,tweak = 1.10)
+
+rpart.plot(tree_3, box.palette="GnOr", main="E Specialization for all species", cex.main=1.85,tweak = 1.10) 
+rpart.plot(tree3, box.palette="GnOr", main="F Specialization for subset with floral rewards", cex.main=1.85,tweak = 1.10)
+
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig.
+S7.} Phylogenetic informed principal component analysis for the subset of species with floral rewards."}
 setwd("~/R_Projects/Reproductive Traits")
@@
   #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants", "Copious nectar","Copious pollen")
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,4.8,4.8,5.5,5.5,5.5,5.8,6.5)), y = -(PCAloadings$PC2*c(4.8,4.4,4.15,5.35,4.2,4.7,5.75,6)+c(0,0,0,0,0,0,0,0)),
-                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-p1 <- all_spp(PC)
-
-#Load data
-phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen_complete_cases.rds")
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen_complete_cases.rds")
-
-PC <- phyl_pca_forest_nectar_pollen
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_spp_complete <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
-    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-  plot <- plot + geom_point(data=dat, aes(x, y),size=0.95, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=-v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw()
-
-  #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants", "Copious nectar","Copious pollen")
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,4.8,5.4,5,4.2,5.8,3.4)+c(0,0,0,0,0,0,0,0)), y = -(PCAloadings$PC2*c(4.693,3.5,4,4,3,4.15,4.2,6.5)),
-                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-p2 <- all_spp_complete(PC)
-
-library(patchwork)
-
-p1 / p2 + plot_annotation(tag_levels = 'A') & 
-  theme(plot.tag = element_text(size = 24, face="bold"))
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24,  fig.cap="\\textbf{Fig.
-S5.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation.
-The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates."}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot_apis <- readRDS("Plot_apis_non_apis.rds")
-
-plot_apis
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig.
-S6.} Regression tree analyses.
-Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
-"}
-
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
-########################################################################################################################################################
-#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
-
-library(rpart.plot)
-library(rpart)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
-nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
-d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")
-
-#run  regression trees of the 3 metrics
-set.seed(1)
-tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0054559,minbucket=50)
-
-set.seed(1)
-tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0084459,minbucket=50)
-
-set.seed(1)
-tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0072192 , minbucket=50) #10
-
-#NECTAR AND POLEN DATA
-v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
-nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
-d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
-
-#Set correct colnames for plotting
-colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-set.seed(2)
-tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
-
-set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
-
-set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)
-
-par(mfrow=c(3,2))
-
-rpart.plot(tree_1, box.palette="GnOr", main="A Interaction frequency for all species", cex.main=1.85,tweak = 1.10) 
-rpart.plot(tree1, box.palette="GnOr", main="B Interaction frequency for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-rpart.plot(tree_2, box.palette="GnOr", main="C Normalized degree for all species", cex.main=1.85,tweak = 1.10)
-rpart.plot(tree2, box.palette="GnOr", main="D Normalized degree for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-rpart.plot(tree_3, box.palette="GnOr", main="E Specialization for all species", cex.main=1.85,tweak = 1.10) 
-rpart.plot(tree3, box.palette="GnOr", main="F Specialization for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig.
-S7.} Phylogenetic informed principal component analysis for the subset of species with floral rewards."}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-dat_cleaning_7 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen.rds")
-
-PC <- phyl_pca_forest_nectar_pollen
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-library(magick)
-
-#Images were made by Paula Martin
-PC$S[,1] <- -PC$S[,1]
-
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
-    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-  plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw()
-
-  #ADD LABELS
   rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height", "Nectar","Pollen" )

### 2022-06-07 Manuscript/Lanuza_et_al_2021.Rmd
edit

@@
 S7).
-The first principal component (PC1) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size ('flower number - flower size').
+The first principal component (PC1 or the flower number - flower size axis) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
 The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
@@
 For instance, on this side of the axis we find the species *Petunia axillaris* that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
-The second principal component (PC2) represented 25.05% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
+The second principal component (PC2 or the pollinator dependence axis) represented 25.05% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
 The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
 In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles.
-A species example of this side of the spectrum is *Zuccagnia punctata* that is a self incompatible shrub which depends totally on floral visitors, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm.
+On this extreme of the spectrum we find the species *Zuccagnia punctata* that is a self-incompatible shrub that depends completely on floral visitors for seed production, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm.
 In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
-For instance, on this side of the spectrum we find the species *Veronica peregrina* which is a self compatible herb that is thought to be almost a complete selfer, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
-Further, PC3 explained a considerable amount of trait variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
-The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
+For instance, on this end of the spectrum we find the species *Veronica peregrina* which is a self compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
+Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = |-0.51|) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
+The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; Table S3).
 In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82%; Fig.
@@
 
-We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
+We found (with an Anova) that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
 2 and Table S2).
@@
 3).
-We found that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds (flower number - flower size trade-off, PC1; Fig.
-3a).
-However, plant species with high flower number but small flowers had higher number of visits of bees and syrphids guilds (PC1; Fig.
+We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (Fig.
+3a) but plants on the other extreme of the spectrum with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
+Regarding visitation rates, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number and small flowers (Fig.
 3d).
-Remarkably, all plant species with higher pollinator dependence had higher number of interacting partners and number of visits for all floral visitor guilds (PC2; Fig.
+On the pollinator dependence axis, we found that all species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (Fig.
 3b and Fig.
 3e).
-Finally, plant species with short styles and low selfing had higher interaction partners of all guilds but bees that interacted clearly more with plant species with long styles and high selfing (style length trade-off; Fig.
+Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (Fig.
 3c).
-However, for number of visits, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
+However, regarding number of visits, plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
 3f).

### 2022-06-07 Manuscript/Lanuza_et_al_2021.tex
edit

@@
 S7).
-The first principal component (PC1) represented 26.72\% of the trait variation and indicated a negative correlation between flower number and flower size (`flower number - flower size').
+The first principal component (PC1 or the flower number - flower size axis) represented 26.72\% of the trait variation and indicated a negative correlation between flower number and flower size.
 The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
@@
 For instance, on this side of the axis we find the species \emph{Petunia axillaris} that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
-The second principal component (PC2) represented 25.05\% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
+The second principal component (PC2 or the pollinator dependence axis) represented 25.05\% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
 The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
 In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles.
-A species example of this side of the spectrum is \emph{Zuccagnia punctata} that is a self incompatible shrub which depends totally on floral visitors, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm.
+On this extreme of the spectrum we find the species \emph{Zuccagnia punctata} that is a self-incompatible shrub that depends completely on floral visitors for seed production, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm.
 In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
-For instance, on this side of the spectrum we find the species \emph{Veronica peregrina} which is a self compatible herb that is thought to be almost a complete selfer, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
-Further, PC3 explained a considerable amount of trait variability (19.17\%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
-The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
+For instance, on this end of the spectrum we find the species \emph{Veronica peregrina} which is a self compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
+Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17\%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \textbar-0.51\textbar) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
+The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; Table S3).
 In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82\%; Fig.
@@
 3d).
-Remarkably, all plant species with higher pollinator dependence had higher number of interacting partners and number of visits for all floral visitor guilds (PC2; Fig.
+All plant species with higher pollinator dependence had higher number of interacting partners and number of visits for all floral visitor guilds (PC2; Fig.
 3b and Fig.
 3e).
-Finally, plant species with short styles and low selfing had higher interaction partners of all guilds but bees that interacted clearly more with plant species with long styles and high selfing (style length trade-off; Fig.
+Finally, plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees that interacted clearly more with plant species with long styles and low pollinator dependence (style length trade-off; Fig.
 3c).

### 2022-06-07 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
edit

@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig.
-S7.} Phylogenetic informed principal component analysis for the subset of species with floral rewards."}
+S7.} Phylogenetically informed principal component analysis (pPCA) for all plant species with the first (flower number - flower size axis) and third (style length - pollinator dependence axis) principal component that explained most trait variation."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 #Load data
-phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-dat_cleaning_7 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen.rds")
-
-PC <- phyl_pca_forest_nectar_pollen
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+PC <- phyl_pca_forest
 #CHECK CONTENT
@@
 
-library(magick)
-
-#Images were made by Paula Martin
+#############################################################################################################################################################
+#COMPATIBILITY
+#############################################################################################################################################################
+#Load plots
+
+#Invert axes
 PC$S[,1] <- -PC$S[,1]
-
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
+PC$S[,3] <- -PC$S[,3]
+
+pc3 <- function(PC, x="PC1", y="PC3") {
   # PC being a prcomp object
@@
 
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
-    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
+  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
+  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
     scale_alpha(guide = 'none')
@@
 
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+  plot <- plot + xlab(paste("Flower number - flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("Style length - pollinator dependence axis ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
 
@@
 
-  plot <- plot + theme_bw()
+  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
+ #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
+ # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
+ # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
+ # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
+ # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
+ # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
+ # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
+ # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
+ # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
+ # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
+ # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
 
       #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height", "Nectar","Pollen" )
+  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
 
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,4.8,4.8,5.5,5,5.5,5.8,6.5)), y = -(PCAloadings$PC2*c(4.8,4.4,4.15,5.35,5,4.7,5.75,6)+c(0,0,0,0,0,0,0,0)),
+ plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,4.8,7.1,5.5)), y = -(PCAloadings$PC2*c(-3.2,4.5,3.75,8.4,5,5.5)+c(0,0,0,0,-0.08,0)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
@@
 
-all_spp(PC)
+pc3(PC)
 
@@
   scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "A Breeding system")+
-  theme(plot.title = element_text(hjust=0.5, size=25, face="bold"))+
+  theme(plot.title = element_text(hjust=0.5, size=26, face="bold"), plot.subtitle=element_text(size=16))+
   geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
@@
   scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "B Breeding system")+
-  theme(plot.title = element_text(hjust=0.5,size=25, face="bold") )+
+  theme(plot.title = element_text(hjust=0.5,size=26, face="bold"),plot.subtitle=element_text(size=16))+
   geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

### 2022-06-08 Manuscript/Lanuza_et_al_2021.Rmd
edits

@@
 In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
-For instance, on this end of the spectrum we find the species *Veronica peregrina* which is a self compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
+For instance, on this end of the spectrum we find the species *Veronica peregrina* which is a self-compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
 Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = |-0.51|) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
 The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; Table S3).
-In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82%; Fig.
+In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (Fig.
 S4).
@@
 S8).
-Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Fig.
+Regarding self-compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility; Fig.
 S8a and Fig.
@@
 Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Fig.
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (Fig.
 S8i and Fig.
@@
 
-The main axes of trait variation explained partly presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
+The main axes of trait variation (PC1, PC2 and PC3) explained partly presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
 However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (Fig.
@@
 We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (Fig.
-3a) but plants on the other extreme of the spectrum with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
-Regarding visitation rates, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number and small flowers (Fig.
+3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
+Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number but small (Fig.
 3d).
-On the pollinator dependence axis, we found that all species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (Fig.
+On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (Fig.
 3b and Fig.
@@
 3c).
-However, regarding number of visits, plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
+However, regarding number of visits on the style length - pollinator dependence axis, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
 3f).
@@
 S10; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on PC1 and PC3 for number of visits and specialization.
-On the flower number - flower size trade-off (PC1), number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
+Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
+On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
 S10a).
-On PC1, specialization showed the opposite trend (Fig.
+However, specialization showed the opposite trend on this axis (Fig.
 S10g).
-On the style length trade-off (PC3), number of visits was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
+On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (Fig.
 S10c).
@@
 
-This study demonstrates that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
-These trade-offs are differentiated along three axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-These reproductive trade-offs helped partly explain the presence of floral visitor interactions, but not their number of visits.
+This study investigates the reproductive spectrum of flowering plants from plant-pollinator networks and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
+We found that there are three reproductive axes that capture over 70% of the reproductive trait variation: (i) the flower number - flower size axis, (ii) the pollinator dependence axis and (iii) the style length - pollinator dependence axis.
+These reproductive axes helped partly explain the presence of floral visitor interactions, but not their number of visits.
 However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
-Moreover, we found that the plant species network roles were best explained by plant size and floral reward related traits.
+Finally, we found that the plant species network roles were best explained by plant size and floral reward related traits.
 

### 2022-06-08 Manuscript/Lanuza_et_al_2021.tex
edits

@@
 In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
-For instance, on this end of the spectrum we find the species \emph{Veronica peregrina} which is a self compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
+For instance, on this end of the spectrum we find the species \emph{Veronica peregrina} which is a self-compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
 Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17\%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \textbar-0.51\textbar) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
 The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; Table S3).
-In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82\%; Fig.
+In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (Fig.
 S4).
@@
 
-The main axes of trait variation explained partly presence-absence of interaction partners (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the overall number of visits (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
+The main axes of trait variation (PC1, PC2 and PC3) explained partly presence-absence of interaction partners (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the overall number of visits (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
 However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (Fig.
 3).
-We found that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds (flower number - flower size trade-off, PC1; Fig.
-3a).
-However, plant species with high flower number but small flowers had higher number of visits of bees and syrphids guilds (PC1; Fig.
+We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (Fig.
+3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
+Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number but small (Fig.
 3d).
-All plant species with higher pollinator dependence had higher number of interacting partners and number of visits for all floral visitor guilds (PC2; Fig.
+On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (Fig.
 3b and Fig.
 3e).
-Finally, plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees that interacted clearly more with plant species with long styles and low pollinator dependence (style length trade-off; Fig.
+Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (Fig.
 3c).
-However, for number of visits, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
+However, regarding number of visits on the style length - pollinator dependence axis, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
 3f).
@@
 S10; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
-Overall, the most notable trends were found on PC1 and PC3 for number of visits and specialization.
-On the flower number - flower size trade-off (PC1), number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
+Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
+On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
 S10a).
-On PC1, specialization showed the opposite trend (Fig.
+However, specialization showed the opposite trend on this axis (Fig.
 S10g).
-On the style length trade-off (PC3), number of visits was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
+On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (Fig.
 S10c).
@@
 
-This study demonstrates that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
-These trade-offs are differentiated along three axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-These reproductive trade-offs helped partly explain the presence of floral visitor interactions, but not their number of visits.
+This study investigates the reproductive spectrum of flowering plants from plant-pollinator networks and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
+We found that there are three reproductive axes that capture over 70\% of the reproductive trait variation: (i) the flower number - flower size axis, (ii) the pollinator dependence axis and (iii) the style length - pollinator dependence axis.
+These reproductive axes helped partly explain the presence of floral visitor interactions, but not their number of visits.
 However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
-Moreover, we found that the plant species network roles were best explained by plant size and floral reward related traits.
+Finally, we found that the plant species network roles were best explained by plant size and floral reward related traits.
 

### 2022-06-09 Manuscript/Lanuza_et_al_2021.Rmd
edit

@@
 However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [@stearns1989].
-Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@salguero2016; @friedman2020; @roddy2021], their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
+Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@salguero2016; @friedman2020; @paterno2020; @roddy2021], their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
 Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other vegetative and physiological plant traits [@wright2004; @chave2009; @diaz2016; @onoda2017; @laughlin2021], there is a need to acquire a multitrait perspective with broad geographical coverage.
@@
 
-This study investigates the reproductive spectrum of flowering plants from plant-pollinator networks and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
+This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
+Despite the enormous variability of plant reproductive structures, three axes were able to capture over 70% of reproductive trait variation.
+The first axis was the flower number - flower size and described the negative association between flower number and flower size.
+Although this negative correlation has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species and without a multitrait perspective.
+Here, we provide support to this evidence and show that also key reproductive traits to plant reproduction like ovule number and style length are positively correlated with flower size and negatively correlated with flower number.
+The second axis organized the species by the degree of pollinator dependence where species with higher pollinator dependence showed greater floral display.
+
+As expected... quizas hilar aqui con un par de refs para que quede menos results
+
+it has been investigated empirically only just with few hundreds of Angiosperm species and without a multitrait perspective.
+The second axis of reproductive trait variation was the pollinator dependence axis and showed the variation
+
+main covariation pattern of the reproductive trait space was the negative correlation between flower number and flower size that is a widely described association across [@sargent2007; @kettle2011] and within [@delph2004] Angiosperms species.
+Our study explore this association beyond a two-trait correlation and shows that other fundamental traits to plant reproduction are also negatively correlated to flower number like ovule number and style length.
+
+The second axis that explained most variation was the pollinator dependence one
+
 We found that there are three reproductive axes that capture over 70% of the reproductive trait variation: (i) the flower number - flower size axis, (ii) the pollinator dependence axis and (iii) the style length - pollinator dependence axis.

### 2022-06-09 Manuscript/Lanuza_et_al_2021.tex
edit

@@
 However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints (\protect\hyperlink{ref-stearns1989}{Stearns, 1989}).
-Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}), their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
+Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-paterno2020}{Paterno et al., 2020}; \protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}), their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
 Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other vegetative and physiological plant traits (\protect\hyperlink{ref-chave2009}{Chave et al., 2009}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}; \protect\hyperlink{ref-laughlin2021}{Laughlin et al., 2021}; \protect\hyperlink{ref-onoda2017}{Onoda et al., 2017}; \protect\hyperlink{ref-wright2004}{Wright et al., 2004}), there is a need to acquire a multitrait perspective with broad geographical coverage.
@@
 
-This study investigates the reproductive spectrum of flowering plants from plant-pollinator networks and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
+This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
+Despite the enormous variability of plant reproductive structures, three axes were able to capture over 70\% of reproductive trait variation.
+One of the major covariation patterns of the reproductive trait space was the negative correlation between flower number and flower size that is a widely described association across (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}) and within (\protect\hyperlink{ref-delph2004}{Delph et al., 2004}) Angiosperms species.
+Our study explore this association beyond a two-trait correlation and shows that other fundamental traits to plant reproduction are also negatively correlated to flower number like ovule number and style length.
+
+The second axis that explained most variation was the pollinator dependence one
+
 We found that there are three reproductive axes that capture over 70\% of the reproductive trait variation: (i) the flower number - flower size axis, (ii) the pollinator dependence axis and (iii) the style length - pollinator dependence axis.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-delph2004}{}}%
+Delph, L.
+F., Gehring, J.
+L., Frey, F.
+M., Arntz, A.
+M., \& Levri, M.
+(2004).
+Genetic constraints on floral evolution in a sexually dimorphic plant revealed by artificial selection.
+\emph{Evolution}, \emph{58}(9), 1936--1946.
+
 \leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
@@
 Nat.}, \emph{162}(S4), S63--S79.
+
+\leavevmode\vadjust pre{\hypertarget{ref-paterno2020}{}}%
+Paterno, G.
+B., Silveira, C.
+L., Kollmann, J., Westoby, M., \& Fonseca, C.
+R.
+(2020).
+The maleness of larger angiosperm flowers.
+\emph{Proceedings of the National Academy of Sciences}, \emph{117}(20), 10921--10926.
 

### 2022-06-10 Manuscript/Lanuza_et_al_2021.Rmd
edit

@@
 
-We selected a total of 19 different functional traits that comprised both reproductive and life history traits (see Table 1).
+We selected a total of 19 different functional traits that comprised reproductive traits and plant form and size related traits (see Table 1).
 From these, 16 were reproductive traits that consisted of 13 floral traits and 3 reproductive biology traits.
-Floral traits included morphological traits (e.g., style length) but also floral reward (e.g., pollen quantity) and floral display (e.g., number of flowers) related traits.
+Floral traits included traits related to the size of floral organs (e.g., style length), floral display (e.g., number of flowers) and floral rewards (e.g., pollen quantity).
 Reproductive biology traits indicated the reproductive system of the plant and included breeding, mating and compatibility system.
-The 3 remaining traits were life history traits that are commonly used to characterize the fast-slow continuum of plant trait variation (i.e., plant height, lifespan and life form).
+The 3 remaining traits were plant size and form related traits that are commonly used to characterize the fast-slow continuum of plant trait variation (i.e., plant height, lifespan and life form).
 For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
@@
 This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
-Despite the enormous variability of plant reproductive structures, three axes were able to capture over 70% of reproductive trait variation.
-The first axis was the flower number - flower size and described the negative association between flower number and flower size.
+Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50% and 70% of reproductive trait variation, respectively.
+These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
+Although the explained trait variation that we found in the first two axes is lower than previous studies that consider morphological and physiological traits [@diaz2016; @carmona2021], it is consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits [@salguero2016].
+Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds but insufficient to capture their visitation rates.
+This highlights the need to account for other factors such as species abundances [@ref] or biological mistmatches [@ref] to better capture the intensity of species interactions at a macroecological scale.
+
+The first axis described the negative association between flower number and flower size.
 Although this negative correlation has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species and without a multitrait perspective.
 Here, we provide support to this evidence and show that also key reproductive traits to plant reproduction like ovule number and style length are positively correlated with flower size and negatively correlated with flower number.
-The second axis organized the species by the degree of pollinator dependence where species with higher pollinator dependence showed greater floral display.
+The second axis organized the different species by the degree of pollinator dependence where species with higher pollinator dependence showed greater floral display.
 
@@
 The second axis that explained most variation was the pollinator dependence one
-
-We found that there are three reproductive axes that capture over 70% of the reproductive trait variation: (i) the flower number - flower size axis, (ii) the pollinator dependence axis and (iii) the style length - pollinator dependence axis.
-These reproductive axes helped partly explain the presence of floral visitor interactions, but not their number of visits.
-However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
-Finally, we found that the plant species network roles were best explained by plant size and floral reward related traits.
 
@@
 We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
-Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits [@diaz2016; @carmona2021] it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits [@salguero2016].
 Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
@@
 Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
+
+[Lo guardo aqui por si hay que rescatarlo](Jose)
+
+[We found that there are three reproductive axes that capture over 70% of the reproductive trait variation: (i) the flower number - flower size axis, (ii) the pollinator dependence axis and (iii) the style length - pollinator dependence axis.
+These reproductive axes helped partly explain the presence of floral visitor interactions, but not their number of visits.
+However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
+Finally, we found that the plant species network roles were best explained by plant size and floral reward related traits.](old text)
 
@@
   plot <- plot + xlab(paste("Flower number - flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Pollinator dependence axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+  plot <- plot + ylab(paste("Pollinator dependence - floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
 

### 2022-06-10 Manuscript/Lanuza_et_al_2021.tex
edit

@@
 This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
-Despite the enormous variability of plant reproductive structures, three axes were able to capture over 70\% of reproductive trait variation.
-One of the major covariation patterns of the reproductive trait space was the negative correlation between flower number and flower size that is a widely described association across (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}) and within (\protect\hyperlink{ref-delph2004}{Delph et al., 2004}) Angiosperms species.
+Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively.
+These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
+Although the explained trait variation that we found in the first two axes is lower than previous studies that consider morphological and physiological traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}), it is consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
+Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds but insufficient to capture their visitation rates.
+This highlights the need to account for other factors (e.g., species abundances or biological mistmatch) to better capture the intensity of species interactions at a macroecological scale.
+
+The first axis described the negative association between flower number and flower size.
+Although this negative correlation has received substantial attention {[}worley2000; \protect\hyperlink{ref-sargent2007}{Sargent et al.} (\protect\hyperlink{ref-sargent2007}{2007}); \protect\hyperlink{ref-kettle2011}{Kettle et al.} (\protect\hyperlink{ref-kettle2011}{2011}){]}, it has only been investigated across a few hundred of Angiosperm species and without a multitrait perspective.
+Here, we provide support to this evidence and show that also key reproductive traits to plant reproduction like ovule number and style length are positively correlated with flower size and negatively correlated with flower number.
+The second axis organized the different species by the degree of pollinator dependence where species with higher pollinator dependence showed greater floral display.
+
+As expected\ldots{} quizas hilar aqui con un par de refs para que quede menos results
+
+it has been investigated empirically only just with few hundreds of Angiosperm species and without a multitrait perspective.
+The second axis of reproductive trait variation was the pollinator dependence axis and showed the variation
+
+main covariation pattern of the reproductive trait space was the negative correlation between flower number and flower size that is a widely described association across (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}) and within (\protect\hyperlink{ref-delph2004}{Delph et al., 2004}) Angiosperms species.
 Our study explore this association beyond a two-trait correlation and shows that other fundamental traits to plant reproduction are also negatively correlated to flower number like ovule number and style length.
@@
 The second axis that explained most variation was the pollinator dependence one
-
-We found that there are three reproductive axes that capture over 70\% of the reproductive trait variation: (i) the flower number - flower size axis, (ii) the pollinator dependence axis and (iii) the style length - pollinator dependence axis.
-These reproductive axes helped partly explain the presence of floral visitor interactions, but not their number of visits.
-However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
-Finally, we found that the plant species network roles were best explained by plant size and floral reward related traits.
 
@@
 We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
-Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}) it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
 Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
@@
 Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
+
+\href{Jose}{Lo guardo aqui por si hay que rescatarlo}
+
+\href{old\%20text}{We found that there are three reproductive axes that capture over 70\% of the reproductive trait variation: (i) the flower number - flower size axis, (ii) the pollinator dependence axis and (iii) the style length - pollinator dependence axis.
+These reproductive axes helped partly explain the presence of floral visitor interactions, but not their number of visits.
+However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
+Finally, we found that the plant species network roles were best explained by plant size and floral reward related traits.}
 

### 2022-06-10 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
edit

@@
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
+                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
 

### 2022-06-11 Manuscript/Lanuza_et_al_2021.Rmd
edit

@@
 Although the explained trait variation that we found in the first two axes is lower than previous studies that consider morphological and physiological traits [@diaz2016; @carmona2021], it is consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits [@salguero2016].
-Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds but insufficient to capture their visitation rates.
-This highlights the need to account for other factors such as species abundances [@ref] or biological mistmatches [@ref] to better capture the intensity of species interactions at a macroecological scale.
+Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
+However, they were insufficient to capture their visitation rates which highlights the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
+
+Although the negative correlation between flower number and flower size has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
+Here, we provide support to this evidence with a great diversity of phylogenetic lineages (170 families and over 1000 species) and show that other important traits like ovule number, style length and plant height also covariate along this reproductive axis.
+
+quizas citar aqui el paper de maleness...
+
+Hablar de los otros ejes ahora
 
@@
 
-it has been investigated empirically only just with few hundreds of Angiosperm species and without a multitrait perspective.
-The second axis of reproductive trait variation was the pollinator dependence axis and showed the variation
-
-main covariation pattern of the reproductive trait space was the negative correlation between flower number and flower size that is a widely described association across [@sargent2007; @kettle2011] and within [@delph2004] Angiosperms species.
-Our study explore this association beyond a two-trait correlation and shows that other fundamental traits to plant reproduction are also negatively correlated to flower number like ovule number and style length.
-
-The second axis that explained most variation was the pollinator dependence one
-
-Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
  Trait variation on these two axes was associated with the 'fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.

### 2022-06-11 Manuscript/Lanuza_et_al_2021.tex
edit

@@
 Although the explained trait variation that we found in the first two axes is lower than previous studies that consider morphological and physiological traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}), it is consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
-Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds but insufficient to capture their visitation rates.
-This highlights the need to account for other factors (e.g., species abundances or biological mistmatch) to better capture the intensity of species interactions at a macroecological scale.
+Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
+However, they were insufficient to capture their visitation rates which highlights the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
+
+Although the negative correlation between flower number and flower size has received substantial attention {[}worley2000; \protect\hyperlink{ref-sargent2007}{Sargent et al.} (\protect\hyperlink{ref-sargent2007}{2007}); \protect\hyperlink{ref-kettle2011}{Kettle et al.} (\protect\hyperlink{ref-kettle2011}{2011}){]}, it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
+Here, we provide support to this evidence with a great diversity of phylogenetic lineages (170 families and over 1000 species) and show that other important traits like ovule number, style length and plant height also covariate along this axis.
+
+quizas citar aqui el paper de maleness\ldots{}
+
+Hablar de los otros ejes ahora
 
@@
 
-it has been investigated empirically only just with few hundreds of Angiosperm species and without a multitrait perspective.
-The second axis of reproductive trait variation was the pollinator dependence axis and showed the variation
-
-main covariation pattern of the reproductive trait space was the negative correlation between flower number and flower size that is a widely described association across (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}) and within (\protect\hyperlink{ref-delph2004}{Delph et al., 2004}) Angiosperms species.
-Our study explore this association beyond a two-trait correlation and shows that other fundamental traits to plant reproduction are also negatively correlated to flower number like ovule number and style length.
-
-The second axis that explained most variation was the pollinator dependence one
-
-Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
 Trait variation on these two axes was associated with the `fast-slow continuum' in plant (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}) and animal (\protect\hyperlink{ref-healy2019}{Healy et al., 2019}) life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
@@
 Dellinger, A. S. (2020). Pollination syndromes in the 21st century: Where do we stand and where may we go? \emph{New Phytol.}, \emph{228}(4), 1193--1213. \url{https://doi.org/10.1111/nph.16793}
-
-\leavevmode\vadjust pre{\hypertarget{ref-delph2004}{}}%
-Delph, L.
-F., Gehring, J.
-L., Frey, F.
-M., Arntz, A.
-M., \& Levri, M.
-(2004).
-Genetic constraints on floral evolution in a sexually dimorphic plant revealed by artificial selection.
-\emph{Evolution}, \emph{58}(9), 1936--1946.
 

### 2022-06-13 Manuscript/Lanuza_et_al_2021.Rmd
edits

@@
 Flowering plants have an astonishing diversity of floral structures [@barrett2002; @schiestl2013] that shape plant-pollinator associations [@fenster2004; @dellinger2020].
-However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [@stearns1989].
+However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
 Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@salguero2016; @friedman2020; @paterno2020; @roddy2021], their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
@@
 Although the negative correlation between flower number and flower size has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
-Here, we provide support to this evidence with a great diversity of phylogenetic lineages (170 families and over 1000 species) and show that other important traits like ovule number, style length and plant height also covariate along this reproductive axis.
-
-quizas citar aqui el paper de maleness...
-
-Hablar de los otros ejes ahora
-
-The first axis described the negative association between flower number and flower size.
-Although this negative correlation has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species and without a multitrait perspective.
-Here, we provide support to this evidence and show that also key reproductive traits to plant reproduction like ovule number and style length are positively correlated with flower size and negatively correlated with flower number.
-The second axis organized the different species by the degree of pollinator dependence where species with higher pollinator dependence showed greater floral display.
-
-As expected... quizas hilar aqui con un par de refs para que quede menos results
+Here, we provide support to this evidence with a great diversity of phylogenetic lineages (170 families and over 1000 species) and show that other reproductive and plant size and form related traits also covariate along this axis.
+For example, most species with unisexual flowers (14% of all species) were concentrated in the trait space and were associated with species with woddy life forms (i.e., trees and shrubs) with high flower number.
+This empirical evidence corroborates the idea that approximately 10% of species have separation of sexes [@barrett2002] and that breeding systems are associated with specific life forms [@petit2006].
+The pollinator dependence - floral display axis
+
+check number of species of goodwillie and what we offer that is new...
+
+Further, the pollinator dependence - floral display axis provided additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
+
+Style length...
 
@@
 In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive trade-offs do not.
+
+[Plant scientists’ research attention is skewed towards colourful, conspicuous and broadly distributed flowers](May be interesting to comment on)
 

### 2022-06-13 Manuscript/Lanuza_et_al_2021.tex
edits

@@
 Flowering plants have an astonishing diversity of floral structures (\protect\hyperlink{ref-barrett2002}{Barrett, 2002}; \protect\hyperlink{ref-schiestl2013}{Schiestl \& Johnson, 2013}) that shape plant-pollinator associations (\protect\hyperlink{ref-dellinger2020}{Dellinger, 2020}; \protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}).
-However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints (\protect\hyperlink{ref-stearns1989}{Stearns, 1989}).
+However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints (\protect\hyperlink{ref-agrawal2020}{Agrawal, 2020}; \protect\hyperlink{ref-stearns1989}{Stearns, 1989}).
 Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-paterno2020}{Paterno et al., 2020}; \protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}), their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
@@
 Although the negative correlation between flower number and flower size has received substantial attention {[}worley2000; \protect\hyperlink{ref-sargent2007}{Sargent et al.} (\protect\hyperlink{ref-sargent2007}{2007}); \protect\hyperlink{ref-kettle2011}{Kettle et al.} (\protect\hyperlink{ref-kettle2011}{2011}){]}, it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
-Here, we provide support to this evidence with a great diversity of phylogenetic lineages (170 families and over 1000 species) and show that other important traits like ovule number, style length and plant height also covariate along this axis.
-
-quizas citar aqui el paper de maleness\ldots{}
-
-Hablar de los otros ejes ahora
-
-The first axis described the negative association between flower number and flower size.
-Although this negative correlation has received substantial attention {[}worley2000; \protect\hyperlink{ref-sargent2007}{Sargent et al.} (\protect\hyperlink{ref-sargent2007}{2007}); \protect\hyperlink{ref-kettle2011}{Kettle et al.} (\protect\hyperlink{ref-kettle2011}{2011}){]}, it has only been investigated across a few hundred of Angiosperm species and without a multitrait perspective.
-Here, we provide support to this evidence and show that also key reproductive traits to plant reproduction like ovule number and style length are positively correlated with flower size and negatively correlated with flower number.
+Here, we provide support to this evidence with a great diversity of phylogenetic lineages (170 families and over 1000 species) and show that other reproductive and plant size and form related traits also covariate along this axis.
+For instance, most unisexual species (14\% of plant species of our dataset) were associated with woody species with high flower number.
+This concurs well with the previous idea that approximately 10\% of flowering plants have separation of sexes (\protect\hyperlink{ref-barrett2002}{Barrett, 2002}) and that species with unisexual flowers tend to be associated with woody/tree life forms (\protect\hyperlink{ref-petit2006}{Petit \& Hampe, 2006}).
+
 The second axis organized the different species by the degree of pollinator dependence where species with higher pollinator dependence showed greater floral display.
@@
 In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-encinas2012}{Encinas-Viso et al., 2012}; \protect\hyperlink{ref-vazquez2007}{Vázquez et al., 2007}) that reproductive trade-offs do not.
+
+\href{May\%20be\%20interesting\%20to\%20comment\%20on}{Plant scientists' research attention is skewed towards colourful, conspicuous and broadly distributed flowers}
 
@@
 \url{https://doi.org/10.1111/2041-210X.12232}
+
+\leavevmode\vadjust pre{\hypertarget{ref-petit2006}{}}%
+Petit, R. J., \& Hampe, A. (2006). Some evolutionary consequences of being a tree. \emph{Annu. Rev. Ecol. Evol. Syst.}, \emph{37}, 187--214.
 

### 2022-06-14 Manuscript/Lanuza_et_al_2021.Rmd
edits

@@
 
+Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1000 species) within a multitrait context.
+Although the negative correlation between flower number and flower size has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
+We found support to this trait association and show that other reproductive and plant size and form related traits also covariate along this axis.
+For example, our study complements previous evidence that links breeding systems and life forms [@petit2006; friedman2020] by showing that most species with unisexual flowers were concentrated in the trait space with woody life forms with high flower number.
+Similarly, the second axis of reproductive trait variation also confirmed the previously described positive association between outcrossing rate and floral display [@goodwillie2010].
+Thus, as expected species with higher pollination dependende had greater allocation to flower number or flower size.
+
 Although the negative correlation between flower number and flower size has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
 Here, we provide support to this evidence with a great diversity of phylogenetic lineages (170 families and over 1000 species) and show that other reproductive and plant size and form related traits also covariate along this axis.
-For example, most species with unisexual flowers (14% of all species) were concentrated in the trait space and were associated with species with woddy life forms (i.e., trees and shrubs) with high flower number.
+For example, our study complements previous evidence that links breeding systems and life forms [@petit2006; friedman2020] by showing that most species with unisexual flowers were concentrated in the trait space with woody life forms with high flower number.
+Similarly, the second axis of reproductive trait variation also provided solid evidence for the previously described positive association between outcrossing rate and floral display [@goodwillie2010].
+
+Despite floral rewards not being included in the main analysis because there was insufficient data, we found on an additional exploration that as expected
+
+we found that most species with unisexual flowers (14% of all species) were concentrated in the trait space and were associated with woody life forms with high flower number.
+These findings are consistent with the idea that approximately 10% of Angiosperms have separation of sexes [@barrett2002] and that breeding systems are associated with specific life forms [@petit2006; friedman2020].
+Moreover, our findings of the positive association between pollinator dependence and floral display confirms previous evidence that shows across 154 flowering plants that species with higher outcrossing rates allocate more resources to attraction [@goodwillie2010].
+
+greater allocation of resources to attraction for species with higher outcrossing rates [@goodwillie2010].
+
+14% of plant species in our dataset had unisexual flowers
+
+14% of plant species in our dataset had unisexual flowers and they were concentrated in the trait space and associated with woody life forms with high flower number.
+Our findings of the positive association between pollinator dependence and floral display confirms previous evidence that shows greater allocation of resources for species with higher outcrossing rates [@goodwillie2010].
+
+provide additional support to the positive correlation between pollinator dependence and floral display [@]
+
+For example, most species with unisexual flowers (14% of species of our dataset) were concentrated in the trait space and were associated with woody life forms and high flower number.
+These findings support the idea that approximately 10% of Angiosperms have separation of sexes [@barrett2002] and that breeding systems are associated with specific life forms [@petit2006].
+Our results also highlight the existence of a reproductive axis where floral display and pollinator dependence are positively correlated
+
+with species with woddy life forms (i.e., trees and shrubs) with high flower number.
 This empirical evidence corroborates the idea that approximately 10% of species have separation of sexes [@barrett2002] and that breeding systems are associated with specific life forms [@petit2006].

### 2022-06-14 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
edits

@@
   #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=-v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
+  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
 
@@
 \elandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S11.} Pearson correlation between the product of flower number-flower size and autonomous selfing level.", fig.pos= "h"}
-
-theme_ms <- function(base_size=18, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(2.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-#LOAD LIBRARIES
-library(ggplot2)
-library(ggpubr)
-
-#LOAD DATA
-dat <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-
-#CONDUCT PRODUCT FLOWER NUMBER-FLOWER SIZE
-dat$Product <-      log(dat$Flowers_per_plant * dat$Corolla_diameter_mean+1)
-
-ggscatter(dat, x = "Autonomous_selfing_level_fruit_set", y = "Product", 
-          add = "reg.line", conf.int = TRUE,
-          cor.coef = TRUE, cor.method = "pearson",size=5,cor.coef.size=15,
-          xlab = "Autnomous selfing", ylab = "Product flower size-number") +
-  theme_ms() +ylim(0,16)
-
-```

### 2022-06-15 Manuscript/Lanuza_et_al_2021.Rmd
edits

--- 2022-06-13 Manuscript/Lanuza_et_al_2021.Rmd
@@
 
+Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1000 species) within a multitrait context.
 Although the negative correlation between flower number and flower size has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
-Here, we provide support to this evidence with a great diversity of phylogenetic lineages (170 families and over 1000 species) and show that other reproductive and plant size and form related traits also covariate along this axis.
-For example, most species with unisexual flowers (14% of all species) were concentrated in the trait space and were associated with species with woddy life forms (i.e., trees and shrubs) with high flower number.
-This empirical evidence corroborates the idea that approximately 10% of species have separation of sexes [@barrett2002] and that breeding systems are associated with specific life forms [@petit2006].
-The pollinator dependence - floral display axis
-
-check number of species of goodwillie and what we offer that is new...
-
-Further, the pollinator dependence - floral display axis provided additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
-
-Style length...
+We found support to this trait association and show that other reproductive and plant size and form related traits also covariate along this axis.
+For example, our study complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers were concentrated in the trait space with woody life forms with high flower number.
+Moreover, our work also confirms the previously described positive association between outcrossing rate and larger floral display [@goodwillie2010] that has been reviewed several times as one of the most common mechanisms to promote pollen transfer and guarantee reproductive success.
+
+Our work also confirms the previously described positive association between outcrossing rate and floral display
+
+Plants with larger floral displays can ensure pollen transfer
+
+A common strategy of flowering plants to ensure pollen transfer by allocating more resources to floral display
+
+Flowering plants have developed multiple strategies to influence pollinator behaviour and ensure pollen transfer [@minnaar2019].
+One of the most well known trait associations is the greater allocation of resources from oucrossing species to floral display
+
+Plants in order to ensure reproductive success have developed a broad range of reproductive strategies.
+
+Because most flowering plants rely on pollinators to ensure reproductive success [@ollerton2011], plants have developed multiple strategies to influence pollinator behaviour and ensure pollen transfer [@minnaar2019].
+We found support to the idea that
+
+Resource allocation to attraction has been shown to influence pollinator visitation and impact reproductive success
+
+Our work also confirms the previously described positive association between outcrossing rate and floral display [@goodwillie2010] where species with larger floral displays
+
+Similarly, the second axis of reproductive trait variation also confirmed the previously described positive association between outcrossing rate and floral display [@goodwillie2010].
+Resource allocation to attraction has been shown to influence pollinator visitation and impact reproductive success [@minnaar2019]
+
+Plants with larger floral displays have been shown to attract more floral visitors and ensure reproductive success
+
+that is thought to be one of the mechanisms to ensure pollen transfer [@minnaar2019].
+
+As expected, species with higher pollinator dependence showed greater allocation of resources to attraction that has been  in order to ensure pollen transfer
+
+species with higher pollination dependende had greater allocation to flower number or flower size.
 
@@
 
-\vspace{-28mm}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="90%",fig.align='center',fig.cap= "\\textbf{Figure 2} Location of the different qualitative traits on the trait space.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="80%",fig.align='center',fig.cap= "\\textbf{Figure 2} Location of the different qualitative traits on the trait space.
 The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).

### 2022-06-15 Manuscript/Lanuza_et_al_2021.tex
edits

@@
 
+Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1000 species) within a multitrait context.
 Although the negative correlation between flower number and flower size has received substantial attention {[}worley2000; \protect\hyperlink{ref-sargent2007}{Sargent et al.} (\protect\hyperlink{ref-sargent2007}{2007}); \protect\hyperlink{ref-kettle2011}{Kettle et al.} (\protect\hyperlink{ref-kettle2011}{2011}){]}, it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
-Here, we provide support to this evidence with a great diversity of phylogenetic lineages (170 families and over 1000 species) and show that other reproductive and plant size and form related traits also covariate along this axis.
-For instance, most unisexual species (14\% of plant species of our dataset) were associated with woody species with high flower number.
-This concurs well with the previous idea that approximately 10\% of flowering plants have separation of sexes (\protect\hyperlink{ref-barrett2002}{Barrett, 2002}) and that species with unisexual flowers tend to be associated with woody/tree life forms (\protect\hyperlink{ref-petit2006}{Petit \& Hampe, 2006}).
-
-The second axis organized the different species by the degree of pollinator dependence where species with higher pollinator dependence showed greater floral display.
-
-As expected\ldots{} quizas hilar aqui con un par de refs para que quede menos results
+We found support to this trait association and show that other reproductive and plant size and form related traits also covariate along this axis.
+For example, our study complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-petit2006}{Petit \& Hampe} (\protect\hyperlink{ref-petit2006}{2006}); friedman2020{]} by showing that most species with unisexual flowers were concentrated in the trait space with woody life forms with high flower number.
+Similarly, the second axis of reproductive trait variation also confirmed the previously described positive association between outcrossing rate and floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}).
+
+that is thought to be one of the mechanisms to ensure pollen transfer (\protect\hyperlink{ref-minnaar2019}{Minnaar et al., 2019}).
+
+As expected, species with higher pollinator dependence showed greater allocation of resources to attraction that has been in order to ensure pollen transfer
+
+species with higher pollination dependende had greater allocation to flower number or flower size.
 
@@
 R package version 3.0.9.~At \href{https://CRAN.R-project.org/package=rpart.plot}{https://CRAN.r-project.org/package=rpart.plot}}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-minnaar2019}{}}%
+Minnaar, C., Anderson, B., Jager, M. L. de, \& Karron, J. D. (2019). Plant--pollinator interactions along the pathway to paternity. \emph{Annals of Botany}, \emph{123}(2), 225--245.
 
@@
 
-\vspace{-28mm}
-
 \begin{figure}[H]
 
-{\centering \includegraphics[width=0.9\linewidth]{output/figures/unnamed-chunk-3-1}
+{\centering \includegraphics[width=0.8\linewidth]{output/figures/unnamed-chunk-3-1}
 

### 2022-06-16 Manuscript/Lanuza_et_al_2021.Rmd
edits

--- 2022-06-13 Manuscript/Lanuza_et_al_2021.Rmd
@@
 These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
-Although the explained trait variation that we found in the first two axes is lower than previous studies that consider morphological and physiological traits [@diaz2016; @carmona2021], it is consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits [@salguero2016].
+Although the explained trait variation that we found in the first two axes is lower than previous studies that consider other morphological and physiological traits [@diaz2016; @carmona2021], our results are consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits [@salguero2016].
 Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
@@
 
-Although the negative correlation between flower number and flower size has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
-Here, we provide support to this evidence with a great diversity of phylogenetic lineages (170 families and over 1000 species) and show that other reproductive and plant size and form related traits also covariate along this axis.
-For example, most species with unisexual flowers (14% of all species) were concentrated in the trait space and were associated with species with woddy life forms (i.e., trees and shrubs) with high flower number.
-This empirical evidence corroborates the idea that approximately 10% of species have separation of sexes [@barrett2002] and that breeding systems are associated with specific life forms [@petit2006].
-The pollinator dependence - floral display axis
-
-check number of species of goodwillie and what we offer that is new...
-
-Further, the pollinator dependence - floral display axis provided additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
-
-Style length...
-
- Trait variation on these two axes was associated with the 'fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-The 'slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, plant species that employed the 'fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
-The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
-S11).
+Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1000 species) within a multitrait context.
+Although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
+We found support to this trait association and show that other reproductive and plant size and form related traits also covariate along this axis.
+For example, our study complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
+Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attraction of floral visitors.
+Therefore, our results highlight the presence of reproductive trait covariation patterns that are in part mediated by floral visitors in order to ensure plant reproductive success.
+
+Cosas que se pueden mencionar:
+
+- Hablar algo de las main trends
+
+- Factores que puden afectar que no son al número de parejas interactuantes y tasa de visitas: Quizás mencionar en detalle
+
+- Floral rewards
 
@@
 Finally, we found that the plant species network roles were best explained by plant size and floral reward related traits.](old text)
+
+[Trait variation on these two axes was associated with the 'fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+The 'slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
+In contrast, plant species that employed the 'fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
+Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
+The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
+S11)]()
 

### 2022-06-16 Manuscript/Lanuza_et_al_2021.tex
edits

@@
 These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
-Although the explained trait variation that we found in the first two axes is lower than previous studies that consider morphological and physiological traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}), it is consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
+Although the explained trait variation that we found in the first two axes is lower than previous studies that consider other morphological and physiological traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}), our results are consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
 Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
@@
 Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1000 species) within a multitrait context.
-Although the negative correlation between flower number and flower size has received substantial attention {[}worley2000; \protect\hyperlink{ref-sargent2007}{Sargent et al.} (\protect\hyperlink{ref-sargent2007}{2007}); \protect\hyperlink{ref-kettle2011}{Kettle et al.} (\protect\hyperlink{ref-kettle2011}{2011}){]}, it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
+Although the negative correlation between flower number and flower size has received substantial attention (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}; \protect\hyperlink{ref-worley2000}{Worley et al., 2000}), it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
 We found support to this trait association and show that other reproductive and plant size and form related traits also covariate along this axis.
-For example, our study complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-petit2006}{Petit \& Hampe} (\protect\hyperlink{ref-petit2006}{2006}); friedman2020{]} by showing that most species with unisexual flowers were concentrated in the trait space with woody life forms with high flower number.
-Similarly, the second axis of reproductive trait variation also confirmed the previously described positive association between outcrossing rate and floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}).
-
-that is thought to be one of the mechanisms to ensure pollen transfer (\protect\hyperlink{ref-minnaar2019}{Minnaar et al., 2019}).
-
-As expected, species with higher pollinator dependence showed greater allocation of resources to attraction that has been in order to ensure pollen transfer
-
-species with higher pollination dependende had greater allocation to flower number or flower size.
-
-Trait variation on these two axes was associated with the `fast-slow continuum' in plant (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}) and animal (\protect\hyperlink{ref-healy2019}{Healy et al., 2019}) life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-The `slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, plant species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}).
-The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
-S11).
+For example, our study complements previous evidence that links breeding systems and life forms (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-petit2006}{Petit \& Hampe, 2006}) by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
+Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}) where species with high pollinator dependence have greater allocation of resources to attraction of floral visitors.
+Therefore, our results highlight the presence of reproductive trait covariation patterns that are in part mediated by floral visitors in order to ensure plant reproductive success.
+
+Cosas que se pueden mencionar:
+
+\begin{itemize}
+\item
+  Hablar algo de las main trends
+\item
+  Factores que puden afectar que no son al número de parejas interactuantes y tasa de visitas: Quizás mencionar en detalle
+\item
+  Floral rewards
+\end{itemize}
 
@@
 Finally, we found that the plant species network roles were best explained by plant size and floral reward related traits.}
+
+\href{}{Trait variation on these two axes was associated with the `fast-slow continuum' in plant (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}) and animal (\protect\hyperlink{ref-healy2019}{Healy et al., 2019}) life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+The `slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
+In contrast, plant species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
+Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}).
+The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
+S11)}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-minnaar2019}{}}%
-Minnaar, C., Anderson, B., Jager, M. L. de, \& Karron, J. D. (2019). Plant--pollinator interactions along the pathway to paternity. \emph{Annals of Botany}, \emph{123}(2), 225--245.
-
 \leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
@@
 \url{https://doi.org/10.1111/j.1461-0248.2005.00810.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-worley2000}{}}%
+Worley, A.
+C., Baker, A.
+M., Thompson, J.
+D., \& Barrett, S.
+C.
+(2000).
+Floral display in narcissus: Variation in flower size and number at the species, population, and individual levels.
+\emph{International Journal of Plant Sciences}, \emph{161}(1), 69--79.
 

### 2022-06-16 Manuscript/Lanuza_et_al_2021.Rmd
edits

@@
 These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
-Although the explained trait variation that we found in the first two axes is lower than previous studies that consider other morphological and physiological traits [@diaz2016; @carmona2021], our results are consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits [@salguero2016].
+Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits [@diaz2016; @carmona2021], our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits [@salguero2016].
 Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
-However, they were insufficient to capture their visitation rates which highlights the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
+However, they were insufficient to capture their visitation rates which highlight the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
 
@@
 Although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
-We found support to this trait association and show that other reproductive and plant size and form related traits also covariate along this axis.
+We found support to this trait association and show that other reproductive traits and plant form and size related traits also covariate along this axis.
 For example, our study complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
-Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attraction of floral visitors.
-Therefore, our results highlight the presence of reproductive trait covariation patterns that are in part mediated by floral visitors in order to ensure plant reproductive success.
+Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
+Therefore, our results highlight the presence of worldwide reproductive trait covariation patterns that are mediated by floral visitors.
+
+Quizas frase para conclusion:
+
+Therefore, our results highlight the need to account in the global spectrum of plant trait variation the overlook reproductive trait covariation patterns that are ultimately impacted by their interaction with floral visitors.
+
+that life history strategies in flowering plants are constraint by reproductive trait covariation patterns that are mediated by floral visitors.
+
+the presence of worldwide reproductive trait covariation patterns that are mediated by floral visitors.
 

### 2022-06-16 Manuscript/Lanuza_et_al_2021.tex
edits

@@
 ]{article}
-\title{\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors}
-\author{}
-\date{\vspace{-2.5em}}
-
 \usepackage{amsmath,amssymb}
@@
 Interestingly, the use of trait-based approaches (\protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero et al., 2014}) and trait-matching analyses (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}) has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-For example, plant traits can define species' network roles (e.g., specialists vs generalists;~ \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}; \protect\hyperlink{ref-tur2013}{Tur et al., 2013}) and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators (\protect\hyperlink{ref-coux2016}{Coux et al., 2016}; \protect\hyperlink{ref-junker2013}{Junker et al., 2013}).
+For example, plant traits can define species' network roles {[}e.g., specialists vs generalists;~ Lázaro et al.
+(\protect\hyperlink{ref-lazaro2013}{2013}); Tur et al.
+(\protect\hyperlink{ref-tur2013}{2013}){]} and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators (\protect\hyperlink{ref-coux2016}{Coux et al., 2016}; \protect\hyperlink{ref-junker2013}{Junker et al., 2013}).
 Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure (\protect\hyperlink{ref-ibanez2012}{Ibanez, 2012}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}).
@@
 These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
-Although the explained trait variation that we found in the first two axes is lower than previous studies that consider other morphological and physiological traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}), our results are consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
+Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}), our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
 Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
-However, they were insufficient to capture their visitation rates which highlights the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
+However, they were insufficient to capture their visitation rates which highlight the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
 
@@
 Although the negative correlation between flower number and flower size has received substantial attention (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}; \protect\hyperlink{ref-worley2000}{Worley et al., 2000}), it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
-We found support to this trait association and show that other reproductive and plant size and form related traits also covariate along this axis.
+We found support to this trait association and show that other reproductive traits and plant form and size related traits also covariate along this axis.
 For example, our study complements previous evidence that links breeding systems and life forms (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-petit2006}{Petit \& Hampe, 2006}) by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
-Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}) where species with high pollinator dependence have greater allocation of resources to attraction of floral visitors.
-Therefore, our results highlight the presence of reproductive trait covariation patterns that are in part mediated by floral visitors in order to ensure plant reproductive success.
+Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}) where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
+Therefore, our results highlight the presence of worldwide reproductive trait covariation patterns that are mediated by floral visitors.
 

### 2022-06-16 Manuscript/Lanuza_et_al_2021.Rmd
edits

@@
 Although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
-We found support to this trait association and show that other reproductive traits and plant form and size related traits also covariate along this axis.
+We found support to this trait association and show that other life history traits also covariate along this axis.
 For example, our study complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
 Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Therefore, our results highlight the presence of worldwide reproductive trait covariation patterns that are mediated by floral visitors.
+Thus, our results highlight the presence of global reproductive trait covariation patterns across flowering plants that are shaped by floral visitors and are likely to impose constraints to the whole spectrum of trait variation.
 

### 2022-06-16 Manuscript/Lanuza_et_al_2021.tex
edits

@@
 Although the negative correlation between flower number and flower size has received substantial attention (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}; \protect\hyperlink{ref-worley2000}{Worley et al., 2000}), it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
-We found support to this trait association and show that other reproductive traits and plant form and size related traits also covariate along this axis.
+We found support to this trait association and show that other life history traits also covariate along this axis.
 For example, our study complements previous evidence that links breeding systems and life forms (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-petit2006}{Petit \& Hampe, 2006}) by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
 Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}) where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Therefore, our results highlight the presence of worldwide reproductive trait covariation patterns that are mediated by floral visitors.
+Thus, our results highlight the presence of global reproductive trait covariation patterns across flowering plants that are shaped by floral visitors and are likely to impose constraints to the whole spectrum of trait variation.
+
+that are shaped by the interaction between plants and floral visitors.
+
+that is mediated by the interaction with floral visitors wich ultimately
+
+need to be included when exploring the global spectrum of trait variation of flowering plants.
+
+are mediated by floral visitors.
+
+Quizas frase para conclusion:
+
+Therefore, our results highlight the need to account in the global spectrum of plant trait variation the overlook reproductive trait covariation patterns that are ultimately impacted by their interaction with floral visitors.
+
+that life history strategies in flowering plants are constraint by reproductive trait covariation patterns that are mediated by floral visitors.
+
+the presence of worldwide reproductive trait covariation patterns that are mediated by floral visitors.
 

### 2022-06-17 Main_Figures/Figure3.Rmd
edit

@@
   aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles\n Low selfing    High selfing")+
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles      Long styles\n High poll. depend.   Low poll. depend.")+
   theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold"))+ 

### 2022-06-17 Manuscript/Lanuza_et_al_2021.Rmd
edit

@@
 
-Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1000 species) within a multitrait context.
+Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context.
 Although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
@@
 Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Thus, our results highlight the presence of global reproductive trait covariation patterns across flowering plants that are shaped by floral visitors and are likely to impose constraints to the whole spectrum of trait variation.
+Thus, our results highlight the presence of reproductive trait covariation patterns across flowering plants that are shaped by floral visitors and are likely to impose constraints to the global spectrum of trait variation.
+
+Overall, our models showed that the main reproductive axes of trait variation have low predictive power for broad-level interaction patterns between plants and floral visitors.
+However, we found changes in the interaction patterns among and within floral visitor guilds that suggest that plant reproductive strategies partly mediate these associations at large ecological scales.
+As expected, the extreme of the spectrum that was associated with larger floral displays
+
+For example, all floral visitor guilds interacted more with plant species with larger floral displays.
+
+This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently [@hegland2005; @lazaro2013; @kaiser2014].
+
+plant species with high pollinator dependence and grater investment in floral display had higher number of
+
+on the axis of pollinator dependence - floral display, species with larger investment of floral displays and grater pollinator dependence had
+
+For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
+1 and Fig.
+S6).
 
@@
 Therefore, our results highlight the need to account in the global spectrum of plant trait variation the overlook reproductive trait covariation patterns that are ultimately impacted by their interaction with floral visitors.
-
-that life history strategies in flowering plants are constraint by reproductive trait covariation patterns that are mediated by floral visitors.
-
-the presence of worldwide reproductive trait covariation patterns that are mediated by floral visitors.
 
@@
 
-To conclude, we provide a robust description of plant reproductive trade-offs using a large global dataset of plant traits.
+To conclude, we provide a robust description of plant reproductive covariation patterns using a large global dataset of plant traits.
 We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
@@
 
-[Lo guardo aqui por si hay que rescatarlo](Jose)
-
-[We found that there are three reproductive axes that capture over 70% of the reproductive trait variation: (i) the flower number - flower size axis, (ii) the pollinator dependence axis and (iii) the style length - pollinator dependence axis.
-These reproductive axes helped partly explain the presence of floral visitor interactions, but not their number of visits.
-However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
-Finally, we found that the plant species network roles were best explained by plant size and floral reward related traits.](old text)
-
 [Trait variation on these two axes was associated with the 'fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
@@
 In contrast, plant species that employed the 'fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
-The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
-S11)]()
 
@@
 
-flower_small <- image_read("Images/PPCA_Plot/flower_short.png")
+#"Images/PPCA_Plot/flower_short.png"
+flower_small <- image_read("Images/PPCA_Plot/flower_big.png")
 flower_small_1 <- as.raster(flower_small)
@@
     annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
-    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2, ymax = -1.50) +
+    annotation_raster(large_flower_1, xmin = 3.18, xmax = 4.13,ymin = 1.3, ymax = 2.4) +
+    annotation_raster(flower_small_1, xmin = -3.21, xmax = -2.81,ymin = -2, ymax = -1.45) +
     annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
@@
              panel.grid.major= element_blank(),
-            plot.title = element_text(size = rel(2), face="bold")
+            plot.title = element_text(size = rel(2.5), face="bold")
       ))

### 2022-06-17 Manuscript/Lanuza_et_al_2021.tex
edit

--- 2022-06-16 Manuscript/Lanuza_et_al_2021.tex
@@
 Interestingly, the use of trait-based approaches (\protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero et al., 2014}) and trait-matching analyses (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}) has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-For example, plant traits can define species' network roles {[}e.g., specialists vs generalists;~ Lázaro et al.
-(\protect\hyperlink{ref-lazaro2013}{2013}); Tur et al.
-(\protect\hyperlink{ref-tur2013}{2013}){]} and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators (\protect\hyperlink{ref-coux2016}{Coux et al., 2016}; \protect\hyperlink{ref-junker2013}{Junker et al., 2013}).
+For example, plant traits can define species' network roles (e.g., specialists vs generalists;~ \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}; \protect\hyperlink{ref-tur2013}{Tur et al., 2013}) and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators (\protect\hyperlink{ref-coux2016}{Coux et al., 2016}; \protect\hyperlink{ref-junker2013}{Junker et al., 2013}).
 Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure (\protect\hyperlink{ref-ibanez2012}{Ibanez, 2012}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}).
@@
 
-Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1000 species) within a multitrait context.
+Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context.
 Although the negative correlation between flower number and flower size has received substantial attention (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}; \protect\hyperlink{ref-worley2000}{Worley et al., 2000}), it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
-We found support to this trait association and show that other reproductive traits and plant form and size related traits also covariate along this axis.
+We found support to this trait association and show that other life history traits also covariate along this axis.
 For example, our study complements previous evidence that links breeding systems and life forms (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-petit2006}{Petit \& Hampe, 2006}) by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
 Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}) where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Therefore, our results highlight the presence of worldwide reproductive trait covariation patterns that are mediated by floral visitors.
+Thus, our results highlight the presence of reproductive trait covariation patterns across flowering plants that are shaped by floral visitors and are likely to impose constraints to the global spectrum of trait variation.
+
+Overall, our models showed that the main axes of reproductive trait variation have low predictive power for broad-level interaction patterns between plants and floral visitors.
+However, we found changes in the interaction patterns among and within floral visitor guilds that suggest that plant reproductive strategies partly mediate these associations at large ecological scales.
+For example, all floral visitor guilds interacted more with plant species with larger floral displays.
+
+plant species with high pollinator dependence and grater investment in floral display had higher number of
+
+on the axis of pollinator dependence - floral display, species with larger investment of floral displays and grater pollinator dependence had
+
+For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
+1 and Fig.
+S6).
+
+Quizas frase para conclusion:
+
+Therefore, our results highlight the need to account in the global spectrum of plant trait variation the overlook reproductive trait covariation patterns that are ultimately impacted by their interaction with floral visitors.
 
@@
 
-\href{Jose}{Lo guardo aqui por si hay que rescatarlo}
-
-\href{old\%20text}{We found that there are three reproductive axes that capture over 70\% of the reproductive trait variation: (i) the flower number - flower size axis, (ii) the pollinator dependence axis and (iii) the style length - pollinator dependence axis.
-These reproductive axes helped partly explain the presence of floral visitor interactions, but not their number of visits.
-However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
-Finally, we found that the plant species network roles were best explained by plant size and floral reward related traits.}
-
-\href{}{Trait variation on these two axes was associated with the `fast-slow continuum' in plant (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}) and animal (\protect\hyperlink{ref-healy2019}{Healy et al., 2019}) life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+{[}Trait variation on these two axes was associated with the `fast-slow continuum' in plant (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}) and animal (\protect\hyperlink{ref-healy2019}{Healy et al., 2019}) life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
 The `slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
 In contrast, plant species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}).
-The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
-S11)}
 

### 2022-06-17 Manuscript/Lanuza_et_al_2021.Rmd
edit

@@
 Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Thus, our results highlight the presence of reproductive trait covariation patterns across flowering plants that are shaped by floral visitors and are likely to impose constraints to the global spectrum of trait variation.
-
-Overall, our models showed that the main reproductive axes of trait variation have low predictive power for broad-level interaction patterns between plants and floral visitors.
+Thus, our results highlight the presence of reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of trait variation.
+
+Overall, our models showed that the main plant reproductive trait correlations have low predictive power for broad-level interaction patterns between plants and floral visitors.
 However, we found changes in the interaction patterns among and within floral visitor guilds that suggest that plant reproductive strategies partly mediate these associations at large ecological scales.
-As expected, the extreme of the spectrum that was associated with larger floral displays
-
-For example, all floral visitor guilds interacted more with plant species with larger floral displays.
-
-This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently [@hegland2005; @lazaro2013; @kaiser2014].
-
-plant species with high pollinator dependence and grater investment in floral display had higher number of
-
-on the axis of pollinator dependence - floral display, species with larger investment of floral displays and grater pollinator dependence had
-
-For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
-1 and Fig.
-S6).
-
-Quizas frase para conclusion:
-
-Therefore, our results highlight the need to account in the global spectrum of plant trait variation the overlook reproductive trait covariation patterns that are ultimately impacted by their interaction with floral visitors.
+For example, we found that all floral visitor guilds interacted more frequently with plant species with larger floral displays in agreement with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
+In regard to the other trait correlations, floral visitor guilds showed contrasting visitation patterns across the continuum of reproductive trait variation.
+Different floral visitor guilds have been shown to exert different selective pressures and lead to distinct set of reproductive trait that can be identified as pollination syndromes
+
+@dellinger2020
+
+@fenster2004
+
+that suggests possible adaptations and different selective pressures from specific floral visitor guilds to different set of plant reproductive traits.
+
+These different floral visitor guilds
+
+suggesting possible adaptations from specific floral visitor guilds to different set of plant reproductive traits.
+
+ In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation patterns across the continuum of trait variation
 
@@
 
-Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (number of interaction partners and number of visits), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies influence plant-pollinator interactions.
  For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
@@
 In contrast, plant species that employed the 'fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
+
+Quizas frase para conclusion:
+
+Therefore, our results highlight the need to account in the global spectrum of plant trait variation the overlook reproductive trait covariation patterns that are ultimately impacted by their interaction with floral visitors.
 

### 2022-06-20 Manuscript/Lanuza_et_al_2021.Rmd
edits

@@
 Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context.
+In addition, our work links the reproductive trait variation with the previously described fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
 Although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
@@
 Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Thus, our results highlight the presence of reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of trait variation.
+Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral display.
+Thus, our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
 
@@
 For example, we found that all floral visitor guilds interacted more frequently with plant species with larger floral displays in agreement with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
-In regard to the other trait correlations, floral visitor guilds showed contrasting visitation patterns across the continuum of reproductive trait variation.
-Different floral visitor guilds have been shown to exert different selective pressures and lead to distinct set of reproductive trait that can be identified as pollination syndromes
-
-@dellinger2020
-
-@fenster2004
-
-that suggests possible adaptations and different selective pressures from specific floral visitor guilds to different set of plant reproductive traits.
-
-These different floral visitor guilds
-
-suggesting possible adaptations from specific floral visitor guilds to different set of plant reproductive traits.
-
- In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation patterns across the continuum of trait variation
-
-Cosas que se pueden mencionar:
-
-- Hablar algo de las main trends
-
-- Factores que puden afectar que no son al número de parejas interactuantes y tasa de visitas: Quizás mencionar en detalle
-
-- Floral rewards
-
- For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
-1 and Fig.
-S6).
-This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently [@hegland2005; @lazaro2013; @kaiser2014].
-In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation patterns across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
-For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
-3) suggesting possible niche partitioning [@palmer2003; @phillips2020] between these two guilds.
-However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species network roles (Fig.
-4).
-More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive trade-offs do not.
-
-[Plant scientists’ research attention is skewed towards colourful, conspicuous and broadly distributed flowers](May be interesting to comment on)
-
-To conclude, we provide a robust description of plant reproductive covariation patterns using a large global dataset of plant traits.
-We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
+Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes.
+For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour [rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive correlations do not.
+
+To conclude, we provide a robust description of the reproductive covariation patterns of animal pollinated species from plant-pollinator networks with the help of a global dataset of plant reproductive traits.
+Our work is a first step to elucidate the reproductive spectrum of flowering plants and highlights the relevance of floral visitors in the understanding of the different reproductive trait correlations.
+
+To better understand the reproductive spectrum of plant trait variation, there are several other reproductive traits that
+
+Future work needs to provide a more detailed description of the reproductive trait correlations by including other key reproductive traits that may affect these covariation patterns.
+
+Despite we provide a detailed exploration with numerous reproductive traits, other reproductive traits that can affect these trait correlations need to be also accounted (e.g., flower colour and life span or more detailed exploration of floral rewards).
+Future work needs to integrate these reproductive correlations with the already described morphological and physiological plant correlations in order to better understand the global spectrum of plant form and function.
+
 Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
@@
 Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
-
-[Trait variation on these two axes was associated with the 'fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-The 'slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, plant species that employed the 'fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-
-Quizas frase para conclusion:
-
-Therefore, our results highlight the need to account in the global spectrum of plant trait variation the overlook reproductive trait covariation patterns that are ultimately impacted by their interaction with floral visitors.
 

### 2022-06-20 Manuscript/Lanuza_et_al_2021.tex
edits

@@
 Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context.
+In addition, our work links the reproductive trait variation with the previously described fast-slow continuum' in plant (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}) and animal (\protect\hyperlink{ref-healy2019}{Healy et al., 2019}) life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
 Although the negative correlation between flower number and flower size has received substantial attention (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}; \protect\hyperlink{ref-worley2000}{Worley et al., 2000}), it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
@@
 Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}) where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Thus, our results highlight the presence of reproductive trait covariation patterns across flowering plants that are shaped by floral visitors and are likely to impose constraints to the global spectrum of trait variation.
-
-Overall, our models showed that the main axes of reproductive trait variation have low predictive power for broad-level interaction patterns between plants and floral visitors.
+Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral display.
+Thus, our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
+
+Overall, our models showed that the main plant reproductive trait correlations have low predictive power for broad-level interaction patterns between plants and floral visitors.
 However, we found changes in the interaction patterns among and within floral visitor guilds that suggest that plant reproductive strategies partly mediate these associations at large ecological scales.
-For example, all floral visitor guilds interacted more with plant species with larger floral displays.
-
-plant species with high pollinator dependence and grater investment in floral display had higher number of
-
-on the axis of pollinator dependence - floral display, species with larger investment of floral displays and grater pollinator dependence had
-
-For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
-1 and Fig.
-S6).
-
-Quizas frase para conclusion:
-
-Therefore, our results highlight the need to account in the global spectrum of plant trait variation the overlook reproductive trait covariation patterns that are ultimately impacted by their interaction with floral visitors.
-
-Cosas que se pueden mencionar:
-
-\begin{itemize}
-\item
-  Hablar algo de las main trends
-\item
-  Factores que puden afectar que no son al número de parejas interactuantes y tasa de visitas: Quizás mencionar en detalle
-\item
-  Floral rewards
-\end{itemize}
-
-Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (number of interaction partners and number of visits), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies influence plant-pollinator interactions.
-For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
-1 and Fig.
-S6).
-This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently (\protect\hyperlink{ref-hegland2005}{Hegland \& Totland, 2005}; \protect\hyperlink{ref-kaiser2014}{Kaiser-Bunbury et al., 2014}; \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}).
-In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation patterns across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
-For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
-3) suggesting possible niche partitioning (\protect\hyperlink{ref-palmer2003}{Palmer et al., 2003}; \protect\hyperlink{ref-phillips2020}{Phillips et al., 2020}) between these two guilds.
-However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species network roles (Fig.
-4).
-More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-encinas2012}{Encinas-Viso et al., 2012}; \protect\hyperlink{ref-vazquez2007}{Vázquez et al., 2007}) that reproductive trade-offs do not.
-
-\href{May\%20be\%20interesting\%20to\%20comment\%20on}{Plant scientists' research attention is skewed towards colourful, conspicuous and broadly distributed flowers}
-
-To conclude, we provide a robust description of plant reproductive covariation patterns using a large global dataset of plant traits.
+For example, we found that all floral visitor guilds interacted more frequently with plant species with larger floral displays in agreement with previous findings (\protect\hyperlink{ref-hegland2005}{Hegland \& Totland, 2005}; \protect\hyperlink{ref-kaiser2014}{Kaiser-Bunbury et al., 2014}; \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}).
+Because plants can adapt to the most efficient floral visitors (\protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}), the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes.
+For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour {[}rader2020; \protect\hyperlink{ref-foldesi2021}{Földesi et al.} (\protect\hyperlink{ref-foldesi2021}{2021}){]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-encinas2012}{Encinas-Viso et al., 2012}; \protect\hyperlink{ref-vazquez2007}{Vázquez et al., 2007}) that reproductive correlations do not.
+
+To conclude, we provide a robust description of the reproductive covariation patterns of flowering plants with the help of a large global dataset of plant reproductive traits.
+
 We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
+
 Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
@@
 In contrast, plant species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
+
+Quizas frase para conclusion:
+
+Therefore, our results highlight the need to account in the global spectrum of plant trait variation the overlook reproductive trait covariation patterns that are ultimately impacted by their interaction with floral visitors.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
+Földesi, R., Howlett, B.
+G., Grass, I., \& Batáry, P.
+(2021).
+Larger pollinators deposit more pollen on stigmas across multiple plant species---a meta-analysis.
+\emph{Journal of Applied Ecology}, \emph{58}(4), 699--707.
+
 \leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-palmer2003}{}}%
-Palmer, T.
-M., Stanton, M.
-L., \& Young, T.
-P.
-(2003).
-Competition and coexistence: Exploring mechanisms that restrict and maintain diversity within mutualist guilds.
-\emph{Am.
-Nat.}, \emph{162}(S4), S63--S79.
-
 \leavevmode\vadjust pre{\hypertarget{ref-paterno2020}{}}%
@@
 Petit, R. J., \& Hampe, A. (2006). Some evolutionary consequences of being a tree. \emph{Annu. Rev. Ecol. Evol. Syst.}, \emph{37}, 187--214.
-
-\leavevmode\vadjust pre{\hypertarget{ref-phillips2020}{}}%
-Phillips, R. D., Peakall, R., van der Niet, T., \& Johnson, S. D. (2020). Niche perspectives on plant\textendash pollinator interactions. \emph{Trends Plant Sci.}, \emph{25}(8), 779--793.
 

### 2022-06-21 Manuscript/Lanuza_et_al_2021.Rmd
edits

@@
 
-# ABSTRACT
-
-Plant life-history strategies are constrained by cost-benefit trade-offs that determine plant form and function.
-However, despite recent advances in the understanding of plant trait variation, little is known about plant reproductive trade-offs and how these constrain life-history strategies and shape interactions with floral visitors.
-Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
-We found that over half of all plant reproductive trait variation was explained by two independent axes.
-Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
-In addition, plant reproductive trade-offs determined important differences in the interaction level among floral visitor guilds.
-Our study shows the main reproductive trade-offs of flowering plants and their relevance to understand plant-pollinator interactions in a global context.
+# Abstract
+
+Plants have an enormous variation of life history strategies and trait combinations.
+However, there is strong evidence that there are evolutionary and physiological constraints that limit the number of plant ecological strategies.
+Despite recent advances in the understanding of plant trait variation, little is known about reproductive trait correlations and how these affect plant life-history strategies and shape interactions with floral visitors.
+Here, we investigate the reproductive spectrum of flowering plants and how this drive interactions with floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
+We found that over 50% and 70% of all trait variation was explained by the first two and three reproductive axes, respectively.
+Specifically, the first axis indicated the presence of a negative correlation between flower number and flower size; the second axis showed a positive correlation between pollinator dependence and floral display; and the third axis indicated a negative correlation between style length and pollinator dependence.
+These different reproductive axes determined important differences in the interaction level among floral visitor guilds but were insufficient to fully capture plant-pollinator associations.
+Our study shows the major reproductive trait correlations and highlights their relevance to understand plant-pollinator interactions in a global context.
 
@@
 
-# INTRODUCTION
+# 1. Introduction
 
@@
 
-# MATERIALS AND METHODS
-
-**Plant-pollinator network studies**
+# 2. Methods
+
+## (a) Plant-pollinator network studies
 
@@
 
-**Taxonomy of plants and pollinators**
+## (b) Taxonomy of plants and pollinators
 
@@
 
-**Plant traits**
+## (c) Plant traits
 
@@
 
-**Phylogenetic Distance**
+## (d) Phylogenetic Distance
 
@@
 
-**Data Imputation**
+## (e) Data Imputation
 
@@
 
-**Plant strategies**
+## (f) Plant strategies
 
@@
 
-**Phylogenetic signal**
+## (g) Phylogenetic signal
 
@@
 
-**Network analyses**
+## (h) Network analyses
 
@@
 
-**Visitation patterns**
+### (i) Visitation patterns
 
@@
 
-**Plant species network roles**
-
-We investigated whether different quantitative traits determined different plant species' functional roles in the pollination network using Bayesian modelling and regression trees.
+### (ii) Plant species network roles
+
+We investigated whether different quantitative traits determined different plant species' functional roles in the pollination network using Bayesian modelling.
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
@@
 
-First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
+We modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
 For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
@@
 
-Second, to better understand complex trait relationships, we used regression trees.
-Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction.
-We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
-We conducted this analysis using the *rpart* function from the *rtrees* package [@therneau2015] with method *'anova'* with a minimum of 50 observations per terminal node and we used the *rpart.plot* package [@milborrow2015] to plot the regression trees.
-We considered the species level indices as response variables (number of visits, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
-We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-Because pollen and nectar traits are essential to understand plant-pollinator interactions [@heinrich1972; @johnson2008; @vaudo2015], we focused in the main text on the regression trees that included floral rewards.
-Indeed, we found that nectar and pollen traits were among the best traits for explaining the different species-level metrics (Fig.
-S6).
-
-# RESULTS
-
-**Plant strategies**
+# 3. Results
+
+## (a) Plant strategies
 
@@
 
-**Phylogenetic signal**
+## (b) Phylogenetic signal
 
@@
 
-**Visitation patterns**
+## (c) Visitation patterns
 
@@
 
-**Plant species network roles**
+## (d) Plant species network roles
 
@@
 
-When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for number of visits was best explained by plant height, nectar concentration and style length (Fig.
-4a; root node error = 1%).
-Specifically, species taller than 3.9m had the highest number of visits, while species that were shorter than 3.9m and had a nectar concentration lower than 16% had the lowest number of visits.
-Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
-4b; root node error = 2%).
-Species with a nectar concentration over 49% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49%, more than 21,000 pollen grains per flower and height less than 0.78m had the lowest normalized degree.
-Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
-4c; root node error = 7%).
-Overall, plant species with the highest specialization were shorter than 1.3m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11% of their fruits.
-In contrast, species taller or equal than 5.1m and with lower than 14 ovules per flower had the lowest specialization values.
-
-# DISCUSSION
+# 4. Discussion
 
@@
 
-To conclude, we provide a robust description of the reproductive covariation patterns of animal pollinated species from plant-pollinator networks with the help of a global dataset of plant reproductive traits.
-Our work is a first step to elucidate the reproductive spectrum of flowering plants and highlights the relevance of floral visitors in the understanding of the different reproductive trait correlations.
-
-To better understand the reproductive spectrum of plant trait variation, there are several other reproductive traits that
-
-Future work needs to provide a more detailed description of the reproductive trait correlations by including other key reproductive traits that may affect these covariation patterns.
-
-Despite we provide a detailed exploration with numerous reproductive traits, other reproductive traits that can affect these trait correlations need to be also accounted (e.g., flower colour and life span or more detailed exploration of floral rewards).
-Future work needs to integrate these reproductive correlations with the already described morphological and physiological plant correlations in order to better understand the global spectrum of plant form and function.
-
-Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
-Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators [@gervasi2017; @mackin2021].
-Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
+To conclude, we provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of plant reproductive traits from species that belong to plant-pollinator networks.
+Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider other factors beyond plant reproductive strategies to better capture broad scale patterns of interactions with floral visitors.
+Our work provides empirical evidence that complements previous studies that have explored trait correlations with other plant organs and highlights the need to include these reproductive correlations in the global spectrum of plant form and function [@diaz2016] as reproductive strategies involve clear cost and benefits that can affect the trait space of the whole plant.
+Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and plant-pollinator associations.
 
@@
 ```
+
+\clearpage
 
@@
 
-```{=tex}
 \vspace{5mm}
 \blandscape
-```
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
@@
 \elandscape
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=4.25, fig.width=12,fig.cap= "**Figure 4** Contribution of traits in plant's network roles.
-Regression tree analysis of number of visits (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
-The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
-Thus, the top node has the mean value of the named trait for the 100% of species.
-Each node has a yes/no question and when the condition is fulfilled, the branch turns to the ‘yes’ direction and when not, to the ‘no’ direction.
-This rationale is followed in all the regression trees as indicated in the first branch division of the topmost node of each tree."}
-
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
-########################################################################################################################################################
-#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
-
-library(rpart.plot)
-library(rpart)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
-nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
-d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
-
-#Set correct colnames for plotting
-colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
-
-colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
-
-colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule n.","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen g. per flower")
-
-set.seed(2)
-tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
-
-set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
-
-set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50) 
-par(mfrow=c(1,3))
-
-rpart.plot(tree1, box.palette="GnOr", main="(a) Number of visits", cex.main=1.75,tweak = 1.25,type = 2) 
-rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.75,tweak = 1.25,type = 2)
-rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.75,tweak = 1.25,type = 2)
-
-```
-
-\elandscape

### 2022-06-21 Manuscript/Lanuza_et_al_2021.tex
edits

@@
 \hypertarget{abstract}{%
-\section{ABSTRACT}\label{abstract}}
-
-Plant life-history strategies are constrained by cost-benefit trade-offs that determine plant form and function.
-However, despite recent advances in the understanding of plant trait variation, little is known about plant reproductive trade-offs and how these constrain life-history strategies and shape interactions with floral visitors.
-Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
-We found that over half of all plant reproductive trait variation was explained by two independent axes.
-Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
-In addition, plant reproductive trade-offs determined important differences in the interaction level among floral visitor guilds.
-Our study shows the main reproductive trade-offs of flowering plants and their relevance to understand plant-pollinator interactions in a global context.
+\section{Abstract}\label{abstract}}
+
+Plants have an enormous variation of life history strategies and trait combinations.
+However, there is strong evidence that there are evolutionary and physiological constraints that limit the number of plant ecological strategies.
+Despite recent advances in the understanding of plant trait variation, little is known about reproductive trait correlations and how these affect plant life-history strategies and shape interactions with floral visitors.
+Here, we investigate the reproductive spectrum of flowering plants and how this drive interactions with floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
+We found that over 50\% and 70\% of all trait variation was explained by the first two and three reproductive axes, respectively.
+Specifically, the first axis indicated the presence of a negative correlation between flower number and flower size; the second axis showed a positive correlation between pollinator dependence and floral display; and the third axis indicated a negative correlation between style length and pollinator dependence.
+These different reproductive axes determined important differences in the interaction level among floral visitor guilds but were insufficient to fully capture plant-pollinator associations.
+Our study shows the major reproductive trait correlations and highlights their relevance to understand plant-pollinator interactions in a global context.
 
@@
 \hypertarget{introduction}{%
-\section{INTRODUCTION}\label{introduction}}
-
-Flowering plants have an astonishing diversity of floral structures (\protect\hyperlink{ref-barrett2002}{Barrett, 2002}; \protect\hyperlink{ref-schiestl2013}{Schiestl \& Johnson, 2013}) that shape plant-pollinator associations (\protect\hyperlink{ref-dellinger2020}{Dellinger, 2020}; \protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}).
-However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints (\protect\hyperlink{ref-agrawal2020}{Agrawal, 2020}; \protect\hyperlink{ref-stearns1989}{Stearns, 1989}).
-Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-paterno2020}{Paterno et al., 2020}; \protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}), their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
-Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other vegetative and physiological plant traits (\protect\hyperlink{ref-chave2009}{Chave et al., 2009}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}; \protect\hyperlink{ref-laughlin2021}{Laughlin et al., 2021}; \protect\hyperlink{ref-onoda2017}{Onoda et al., 2017}; \protect\hyperlink{ref-wright2004}{Wright et al., 2004}), there is a need to acquire a multitrait perspective with broad geographical coverage.
-Importantly, the characterization of the reproductive trait covariation patterns can help to further understand the different plant ecological strategies (\protect\hyperlink{ref-agrawal2020}{Agrawal, 2020}) and improve our knowledge on plant-pollinator associations (\protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}).
-
-Although there is an increasing number of macroecological studies that investigate plant reproductive traits (\protect\hyperlink{ref-baude2016}{Baude et al., 2016}; \protect\hyperlink{ref-grossenbacher2017}{Grossenbacher et al., 2017}; \protect\hyperlink{ref-moeller2017}{Moeller et al., 2017}; \protect\hyperlink{ref-munoz2016}{Munoz et al., 2016}), we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales (\protect\hyperlink{ref-rech2016}{Rech et al., 2016}; \protect\hyperlink{ref-ruger2018}{Rüger et al., 2018}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}; \protect\hyperlink{ref-sargent2008}{Sargent \& Ackerly, 2008}).
-In addition, the pollination system of a great number of plant species remains unexplored and is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations (\protect\hyperlink{ref-devaux2014}{Devaux et al., 2014}; \protect\hyperlink{ref-tur2013}{Tur et al., 2013}).
-Interestingly, the use of trait-based approaches (\protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero et al., 2014}) and trait-matching analyses (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}) has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-For example, plant traits can define species' network roles (e.g., specialists vs generalists;~ \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}; \protect\hyperlink{ref-tur2013}{Tur et al., 2013}) and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators (\protect\hyperlink{ref-coux2016}{Coux et al., 2016}; \protect\hyperlink{ref-junker2013}{Junker et al., 2013}).
-Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure (\protect\hyperlink{ref-ibanez2012}{Ibanez, 2012}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}).
-Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network interactions (\protect\hyperlink{ref-eklof2013}{Eklöf et al., 2013}), an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns (see \protect\hyperlink{ref-dehling2016}{Dehling et al., 2016}).
+\section{1. Introduction}\label{introduction}}
+
+Flowering plants have an astonishing diversity of floral structures {[}\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}{]} that shape plant-pollinator associations {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}{]}.
+However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints {[}\protect\hyperlink{ref-stearns1989}{5},\protect\hyperlink{ref-agrawal2020}{6}{]}.
+Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits {[}\protect\hyperlink{ref-salguero2016}{7}--\protect\hyperlink{ref-roddy2021}{10}{]}, their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
+Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other vegetative and physiological plant traits {[}\protect\hyperlink{ref-wright2004}{11}--\protect\hyperlink{ref-laughlin2021}{15}{]}, there is a need to acquire a multitrait perspective with broad geographical coverage.
+Importantly, the characterization of the reproductive trait covariation patterns can help to further understand the different plant ecological strategies {[}\protect\hyperlink{ref-agrawal2020}{6}{]} and improve our knowledge on plant-pollinator associations {[}\protect\hyperlink{ref-roddy2021}{10}{]}.
+
+Although there is an increasing number of macroecological studies that investigate plant reproductive traits {[}\protect\hyperlink{ref-baude2016}{16}--\protect\hyperlink{ref-moeller2017}{19}{]}, we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-sargent2008}{20}--\protect\hyperlink{ref-ruger2018}{22}{]}.
+In addition, the pollination system of a great number of plant species remains unexplored and is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations {[}\protect\hyperlink{ref-tur2013}{23},\protect\hyperlink{ref-devaux2014}{24}{]}.
+Interestingly, the use of trait-based approaches {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{25}{]} and trait-matching analyses {[}\protect\hyperlink{ref-stang2009}{26},\protect\hyperlink{ref-bartomeus2016}{27}{]} has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
+For example, plant traits can define species' network roles {[}\protect\hyperlink{ref-tur2013}{23},e.g., specialists vs generalists;~ \protect\hyperlink{ref-lazaro2013}{28}{]} and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators {[}\protect\hyperlink{ref-junker2013}{29},\protect\hyperlink{ref-coux2016}{30}{]}.
+Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure {[}\protect\hyperlink{ref-stang2009}{26},\protect\hyperlink{ref-ibanez2012}{31}{]}.
+Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network interactions {[}\protect\hyperlink{ref-eklof2013}{32}{]}, an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns {[}see \protect\hyperlink{ref-dehling2016}{33}{]}.
 Thus, by exploring the reproductive spectrum of trait variation is possible to delimit the different plant reproductive strategies and explore how these are associated with the different floral visitors.
 
-With the recent availability of large trait databases (e.g., TRY \protect\hyperlink{ref-kattge2011}{Kattge et al., 2011}; and COMPADRE \protect\hyperlink{ref-salguero2015}{Salguero-Gómez et al., 2015}), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function (\protect\hyperlink{ref-bruelheide2018}{Bruelheide et al., 2018}; \protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
-However, most studies with a multitrait perspective have focused on trait correlations from the leaf (\protect\hyperlink{ref-wright2004}{Wright et al., 2004}), wood (\protect\hyperlink{ref-chave2009}{Chave et al., 2009}), or root (\protect\hyperlink{ref-laughlin2021}{Laughlin et al., 2021}) related traits with little or no attention given to reproductive traits (\protect\hyperlink{ref-evojtko2020}{E-Vojtkó et al., 2020}; \protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}).
-Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}), the positive association between flower size and outcrossing rate (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}) or the association between outcrossing rate and lifespan where short lived versus perennial species tend to have low versus high levels of outcrossing (\protect\hyperlink{ref-barrett2003}{Barrett, 2003}; \protect\hyperlink{ref-moeller2017}{Moeller et al., 2017}), respectively.
-Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships (\protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}), we still lack empirical evidence that investigates jointly these different reproductive trait associations.
+With the recent availability of large trait databases {[}e.g., TRY \protect\hyperlink{ref-kattge2011}{34},and COMPADRE \protect\hyperlink{ref-salguero2015}{35}{]}, plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-diaz2016}{13},\protect\hyperlink{ref-bruelheide2018}{36},\protect\hyperlink{ref-carmona2021}{37}{]}.
+However, most studies with a multitrait perspective have focused on trait correlations from the leaf {[}\protect\hyperlink{ref-wright2004}{11}{]}, wood {[}\protect\hyperlink{ref-chave2009}{12}{]}, or root {[}\protect\hyperlink{ref-laughlin2021}{15}{]} related traits with little or no attention given to reproductive traits {[}\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-evojtko2020}{38}{]}.
+Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{39},\protect\hyperlink{ref-kettle2011}{40}{]}, the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{41}{]} or the association between outcrossing rate and lifespan where short lived versus perennial species tend to have low versus high levels of outcrossing {[}\protect\hyperlink{ref-moeller2017}{19},\protect\hyperlink{ref-barrett2003}{42}{]}, respectively.
+Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships {[}\protect\hyperlink{ref-roddy2021}{10}{]}, we still lack empirical evidence that investigates jointly these different reproductive trait associations.
 
@@
 
-\hypertarget{materials-and-methods}{%
-\section{MATERIALS AND METHODS}\label{materials-and-methods}}
-
-\textbf{Plant-pollinator network studies}
+\hypertarget{methods}{%
+\section{2. Methods}\label{methods}}
+
+\hypertarget{a-plant-pollinator-network-studies}{%
+\subsection{(a) Plant-pollinator network studies}\label{a-plant-pollinator-network-studies}}
 
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies (e.g.,~ \protect\hyperlink{ref-carvalheiro2014}{Carvalheiro et al., 2014}; \protect\hyperlink{ref-fortuna2010}{Fortuna et al., 2010}; \protect\hyperlink{ref-olesen2007}{Olesen et al., 2007}) or available in online archives (e.g., The Web of Life, \protect\hyperlink{ref-fortuna2010}{Fortuna et al., 2010}; and Mangal, \protect\hyperlink{ref-poisot2016}{Poisot et al., 2016}).
+Many of these networks are freely available either as published studies {[}e.g.,~ \protect\hyperlink{ref-carvalheiro2014}{43},\protect\hyperlink{ref-olesen2007}{44},\protect\hyperlink{ref-fortuna2010}{45}{]} or available in online archives {[}e.g., The Web of Life, \protect\hyperlink{ref-fortuna2010}{45},and Mangal, \protect\hyperlink{ref-poisot2016}{46}{]}.
 In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
 
-\textbf{Taxonomy of plants and pollinators}
-
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain et al., 2020}).
+\hypertarget{b-taxonomy-of-plants-and-pollinators}{%
+\subsection{(b) Taxonomy of plants and pollinators}\label{b-taxonomy-of-plants-and-pollinators}}
+
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} {[}\protect\hyperlink{ref-chamberlain2020}{47}{]}.
 We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
 
-\textbf{Plant traits}
+\hypertarget{c-plant-traits}{%
+\subsection{(c) Plant traits}\label{c-plant-traits}}
 
@@
 
-\textbf{Phylogenetic Distance}
-
-We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life (\protect\hyperlink{ref-jin2019}{Jin \& Qian, 2019}; \protect\hyperlink{ref-smith2018}{Smith \& Brown, 2018}).
-
-\textbf{Data Imputation}
-
-To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} (\protect\hyperlink{ref-stekhoven2012}{Stekhoven \& Bühlmann, 2012}) which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} (\protect\hyperlink{ref-penone2014}{Penone et al., 2014}).
-To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} (\protect\hyperlink{ref-santos2018}{Chamberlain et al., 2018}) based on a previous conceptual framework that considers phylogenetic eigenvectors (\protect\hyperlink{ref-diniz-filho2012}{Diniz-Filho et al., 2012}).
+\hypertarget{d-phylogenetic-distance}{%
+\subsection{(d) Phylogenetic Distance}\label{d-phylogenetic-distance}}
+
+We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{48},\protect\hyperlink{ref-jin2019}{49}{]}.
+
+\hypertarget{e-data-imputation}{%
+\subsection{(e) Data Imputation}\label{e-data-imputation}}
+
+To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{50}{]} which allows imputation of datasets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{51}{]}.
+To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} {[}\protect\hyperlink{ref-santos2018}{52}{]} based on a previous conceptual framework that considers phylogenetic eigenvectors {[}\protect\hyperlink{ref-diniz-filho2012}{53}{]}.
 We conducted two different imputations, one for the full set of species (1,506 species, 5.79\% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
@@
 
-\textbf{Plant strategies}
+\hypertarget{f-plant-strategies}{%
+\subsection{(f) Plant strategies}\label{f-plant-strategies}}
 
@@
 Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}; \protect\hyperlink{ref-serneels2008}{Serneels \& Verdonck, 2008}), we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as indicated for principal component analysis (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}).
+Due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{54},\protect\hyperlink{ref-legendre2012}{55}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as indicated for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{55}{]}.
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell, 2012}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams, 2010}).
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{56}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{57}{]}.
 Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
@@
 
-\textbf{Phylogenetic signal}
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell, 2012}) and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+\hypertarget{g-phylogenetic-signal}{%
+\subsection{(g) Phylogenetic signal}\label{g-phylogenetic-signal}}
+
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{56}{]} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
 
-\textbf{Network analyses}
+\hypertarget{h-network-analyses}{%
+\subsection{(h) Network analyses}\label{h-network-analyses}}
 
@@
 For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency (\protect\hyperlink{ref-ballantyne2015}{Ballantyne et al., 2015}), the number of visits can provide valuable information of the contribution of floral visitors to pollination (\protect\hyperlink{ref-vazquez2005}{Vázquez et al., 2005}, \protect\hyperlink{ref-vazquez2012}{2012}).
+Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency {[}\protect\hyperlink{ref-ballantyne2015}{58}{]}, the number of visits can provide valuable information of the contribution of floral visitors to pollination {[}\protect\hyperlink{ref-vazquez2005}{59},\protect\hyperlink{ref-vazquez2012}{60}{]}.
 Second, we investigated how the main axes of trait variation and individual traits influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below `plant species network roles' section).
@@
 
-\textbf{Visitation patterns}
+\hypertarget{i-visitation-patterns}{%
+\subsubsection{(i) Visitation patterns}\label{i-visitation-patterns}}
 
@@
 This finding is consistent with previous research showing that \emph{A.
-mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems (\protect\hyperlink{ref-hung2018}{Hung et al., 2018}).
+mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems {[}\protect\hyperlink{ref-hung2018}{61}{]}.
 Hence, to control for the effect of \emph{A.
@@
 
-We implemented Bayesian generalized linear mixed models using the R package \emph{brms} (\protect\hyperlink{ref-burkner2017}{Bürkner, 2017}).
+We implemented Bayesian generalized linear mixed models using the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{62}{]}.
 We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
@@
 We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results (\protect\hyperlink{ref-burkner2017}{Bürkner, 2017}).
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package (\protect\hyperlink{ref-gabry2019}{Gabry et al., 2019}).
-
-\textbf{Plant species network roles}
-
-We investigated whether different quantitative traits determined different plant species' functional roles in the pollination network using Bayesian modelling and regression trees.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies (\protect\hyperlink{ref-dormann2008}{Dormann et al., 2008}) with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') (\protect\hyperlink{ref-bluthgen2006}{Blüthgen et al., 2006}), which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} (\protect\hyperlink{ref-dormann2008}{Dormann et al., 2008}).
-
-First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
+The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results {[}\protect\hyperlink{ref-burkner2017}{62}{]}.
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}\protect\hyperlink{ref-gabry2019}{63}{]}.
+
+\hypertarget{ii-plant-species-network-roles}{%
+\subsubsection{(ii) Plant species network roles}\label{ii-plant-species-network-roles}}
+
+We investigated whether different quantitative traits determined different plant species' functional roles in the pollination network using Bayesian modelling.
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{64}{]} with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{65}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{64}{]}.
+
+We modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
 For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
@@
 
-Second, to better understand complex trait relationships, we used regression trees.
-Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction.
-We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
-We conducted this analysis using the \emph{rpart} function from the \emph{rtrees} package (\protect\hyperlink{ref-therneau2015}{Therneau et al., 2015}) with method \emph{`anova'} with a minimum of 50 observations per terminal node and we used the \emph{rpart.plot} package (\protect\hyperlink{ref-milborrow2015}{Milborrow, 2015}) to plot the regression trees.
-We considered the species level indices as response variables (number of visits, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
-We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-Because pollen and nectar traits are essential to understand plant-pollinator interactions (\protect\hyperlink{ref-heinrich1972}{Heinrich \& Raven, 1972}; \protect\hyperlink{ref-johnson2008}{Johnson \& Nicolson, 2008}; \protect\hyperlink{ref-vaudo2015}{Vaudo et al., 2015}), we focused in the main text on the regression trees that included floral rewards.
-Indeed, we found that nectar and pollen traits were among the best traits for explaining the different species-level metrics (Fig.
-S6).
-
 \hypertarget{results}{%
-\section{RESULTS}\label{results}}
-
-\textbf{Plant strategies}
+\section{3. Results}\label{results}}
+
+\hypertarget{a-plant-strategies}{%
+\subsection{(a) Plant strategies}\label{a-plant-strategies}}
 
@@
 
-\textbf{Phylogenetic signal}
+\hypertarget{b-phylogenetic-signal}{%
+\subsection{(b) Phylogenetic signal}\label{b-phylogenetic-signal}}
 
@@
 
-\textbf{Visitation patterns}
+\hypertarget{c-visitation-patterns}{%
+\subsection{(c) Visitation patterns}\label{c-visitation-patterns}}
 
@@
 
-\textbf{Plant species network roles}
+\hypertarget{d-plant-species-network-roles}{%
+\subsection{(d) Plant species network roles}\label{d-plant-species-network-roles}}
 
@@
 
-When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for number of visits was best explained by plant height, nectar concentration and style length (Fig.
-4a; root node error = 1\%).
-Specifically, species taller than 3.9m had the highest number of visits, while species that were shorter than 3.9m and had a nectar concentration lower than 16\% had the lowest number of visits.
-Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
-4b; root node error = 2\%).
-Species with a nectar concentration over 49\% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49\%, more than 21,000 pollen grains per flower and height less than 0.78m had the lowest normalized degree.
-Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
-4c; root node error = 7\%).
-Overall, plant species with the highest specialization were shorter than 1.3m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11\% of their fruits.
-In contrast, species taller or equal than 5.1m and with lower than 14 ovules per flower had the lowest specialization values.
-
 \hypertarget{discussion}{%
-\section{DISCUSSION}\label{discussion}}
+\section{4. Discussion}\label{discussion}}
 
@@
 These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
-Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}), our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
+Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{13},\protect\hyperlink{ref-carmona2021}{37}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
 Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
@@
 Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context.
-In addition, our work links the reproductive trait variation with the previously described fast-slow continuum' in plant (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}) and animal (\protect\hyperlink{ref-healy2019}{Healy et al., 2019}) life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-Although the negative correlation between flower number and flower size has received substantial attention (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}; \protect\hyperlink{ref-worley2000}{Worley et al., 2000}), it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
+In addition, our work links the reproductive trait variation with the previously described fast-slow continuum' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{66}{]} life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+Although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{39},\protect\hyperlink{ref-kettle2011}{40},\protect\hyperlink{ref-worley2000}{67}{]}, it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
 We found support to this trait association and show that other life history traits also covariate along this axis.
-For example, our study complements previous evidence that links breeding systems and life forms (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-petit2006}{Petit \& Hampe, 2006}) by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
-Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}) where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
+For example, our study complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{68}{]} by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
+Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{41}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
 Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral display.
@@
 However, we found changes in the interaction patterns among and within floral visitor guilds that suggest that plant reproductive strategies partly mediate these associations at large ecological scales.
-For example, we found that all floral visitor guilds interacted more frequently with plant species with larger floral displays in agreement with previous findings (\protect\hyperlink{ref-hegland2005}{Hegland \& Totland, 2005}; \protect\hyperlink{ref-kaiser2014}{Kaiser-Bunbury et al., 2014}; \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}).
-Because plants can adapt to the most efficient floral visitors (\protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}), the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes.
-For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour {[}rader2020; \protect\hyperlink{ref-foldesi2021}{Földesi et al.} (\protect\hyperlink{ref-foldesi2021}{2021}){]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-encinas2012}{Encinas-Viso et al., 2012}; \protect\hyperlink{ref-vazquez2007}{Vázquez et al., 2007}) that reproductive correlations do not.
-
-To conclude, we provide a robust description of the reproductive covariation patterns of flowering plants with the help of a large global dataset of plant reproductive traits.
-
-We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
-
-Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
-Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators (\protect\hyperlink{ref-gervasi2017}{Gervasi \& Schiestl, 2017}; \protect\hyperlink{ref-mackin2021}{Mackin et al., 2021}).
-Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
-
-{[}Trait variation on these two axes was associated with the `fast-slow continuum' in plant (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}) and animal (\protect\hyperlink{ref-healy2019}{Healy et al., 2019}) life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-The `slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, plant species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-
-Quizas frase para conclusion:
-
-Therefore, our results highlight the need to account in the global spectrum of plant trait variation the overlook reproductive trait covariation patterns that are ultimately impacted by their interaction with floral visitors.
+For example, we found that all floral visitor guilds interacted more frequently with plant species with larger floral displays in agreement with previous findings {[}\protect\hyperlink{ref-lazaro2013}{28},\protect\hyperlink{ref-hegland2005}{69},\protect\hyperlink{ref-kaiser2014}{70}{]}.
+Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes.
+For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour {[}rader2020; {[}\protect\hyperlink{ref-foldesi2021}{71}{]}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{27},\protect\hyperlink{ref-vazquez2007}{72},\protect\hyperlink{ref-encinas2012}{73}{]} that reproductive correlations do not.
+
+To conclude, we provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of plant reproductive traits from species that belong to plant-pollinator networks.
+Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider other factors beyond plant reproductive strategies to better capture broad scale patterns of interactions with floral visitors.
+Our work provides empirical evidence that complements previous studies that have explored trait correlations with other plant organs and highlights the need to include these reproductive correlations in the global spectrum of plant form and function {[}\protect\hyperlink{ref-diaz2016}{13}{]} as reproductive strategies involve clear cost and benefits that can affect the trait space of the whole plant.
+Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and plant-pollinator associations.
 
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
-Abdi, H., \& Williams, L. J. (2010). Principal component analysis. \emph{WIREs Comp. Stats.}, \emph{2}(4), 433--459. \url{https://doi.org/10.1002/wics.101}
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-barrett2002}{}}%
+\CSLLeftMargin{1. }
+\CSLRightInline{Barrett SCH. 2002 The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.} \textbf{3}, 274--284. (doi:\href{https://doi.org/10.1038/nrg776}{10.1038/nrg776})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schiestl2013}{}}%
+\CSLLeftMargin{2. }
+\CSLRightInline{Schiestl FP, Johnson SD.
+2013 Pollinator-mediated evolution of floral signals.
+\emph{Trends Ecol.
+Evol.} \textbf{28}, 307--315.
+(doi:\href{https://doi.org/10.1016/j.tree.2013.01.019}{10.1016/j.tree.2013.01.019})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fenster2004}{}}%
+\CSLLeftMargin{3. }
+\CSLRightInline{Fenster CB, Armbruster WS, Wilson P, Dudash MR, Thomson JD.
+2004 Pollination {Syndromes} and {Floral Specialization}.
+\emph{Annu.
+Rev.
+Ecol.
+Evol.
+Syst.} \textbf{35}, 375--403.
+(doi:\href{https://doi.org/10.1146/annurev.ecolsys.34.011802.132347}{10.1146/annurev.ecolsys.34.011802.132347})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dellinger2020}{}}%
+\CSLLeftMargin{4. }
+\CSLRightInline{Dellinger AS.
+2020 Pollination syndromes in the 21st century: Where do we stand and where may we go?
+\emph{New Phytol.} \textbf{228}, 1193--1213.
+(doi:\href{https://doi.org/10.1111/nph.16793}{10.1111/nph.16793})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stearns1989}{}}%
+\CSLLeftMargin{5. }
+\CSLRightInline{Stearns SC. 1989 Trade-offs in life-history evolution. \emph{Functional ecology} \textbf{3}, 259--268.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-agrawal2020}{}}%
-Agrawal, A. A. (2020). A scale-dependent framework for trade-offs, syndromes, and specialization in organismal biology. \emph{Ecology}, \emph{101}(2), e02924.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
-Ballantyne, G., Baldock, K.
-C.
-R., \& Willmer, P.
-G.
-(2015).
-Constructing more informative plant\textendash pollinator networks: Visitation and pollen deposition networks in a heathland plant community.
+\CSLLeftMargin{6. }
+\CSLRightInline{Agrawal AA. 2020 A scale-dependent framework for trade-offs, syndromes, and specialization in organismal biology. \emph{Ecology} \textbf{101}, e02924.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-salguero2016}{}}%
+\CSLLeftMargin{7. }
+\CSLRightInline{Salguero-Gómez R, Jones OR, Jongejans E, Blomberg SP, Hodgson DJ, Mbeau-Ache C, Zuidema PA, de Kroon H, Buckley YM.
+2016 Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
+\emph{Proc.
+Natl.
+Acad.
+Sci.
+U.S.A.} \textbf{113}, 230--235.
+(doi:\href{https://doi.org/10.1073/pnas.1506215112}{10.1073/pnas.1506215112})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-friedman2020}{}}%
+\CSLLeftMargin{8. }
+\CSLRightInline{Friedman J.
+2020 The evolution of annual and perennial plant life histories: Ecological correlates and genetic mechanisms.
+\emph{Annual Review of Ecology, Evolution, and Systematics} \textbf{51}, 461--481.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-paterno2020}{}}%
+\CSLLeftMargin{9. }
+\CSLRightInline{Paterno GB, Silveira CL, Kollmann J, Westoby M, Fonseca CR.
+2020 The maleness of larger angiosperm flowers.
+\emph{Proceedings of the National Academy of Sciences} \textbf{117}, 10921--10926.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-roddy2021}{}}%
+\CSLLeftMargin{10. }
+\CSLRightInline{Roddy AB, Martínez-Perez C, Teixido AL, Cornelissen TG, Olson ME, Oliveira RS, Silveira FAO.
+2021 Towards the flower economics spectrum.
+\emph{New Phytol.} \textbf{229}, 665--672.
+(doi:\href{https://doi.org/10.1111/nph.16823}{10.1111/nph.16823})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%
+\CSLLeftMargin{11. }
+\CSLRightInline{Wright IJ \emph{et al.} 2004 The worldwide leaf economics spectrum. \emph{Nature} \textbf{428}, 821--827. (doi:\href{https://doi.org/10.1038/nature02403}{10.1038/nature02403})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
+\CSLLeftMargin{12. }
+\CSLRightInline{Chave J, Coomes D, Jansen S, Lewis SL, Swenson NG, Zanne AE. 2009 Towards a worldwide wood economics spectrum. \emph{Ecol. Lett.} \textbf{12}, 351--366.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
+\CSLLeftMargin{13. }
+\CSLRightInline{Díaz S \emph{et al.} 2016 The global spectrum of plant form and function. \emph{Nature} \textbf{529}, 167--171. (doi:\href{https://doi.org/10.1038/nature16489}{10.1038/nature16489})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-onoda2017}{}}%
+\CSLLeftMargin{14. }
+\CSLRightInline{Onoda Y, Wright IJ, Evans JR, Hikosaka K, Kitajima K, Niinemets Ü, Poorter H, Tosens T, Westoby M.
+2017 Physiological and structural tradeoffs underlying the leaf economics spectrum.
+\emph{New Phytologist} \textbf{214}, 1447--1463.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
+\CSLLeftMargin{15. }
+\CSLRightInline{Laughlin DC \emph{et al.} 2021 Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
+\emph{Nat.
+Ecol.
+Evol.}, 1--12.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-baude2016}{}}%
+\CSLLeftMargin{16. }
+\CSLRightInline{Baude M, Kunin WE, Boatman ND, Conyers S, Davies N, Gillespie MA, Morton RD, Smart SM, Memmott J.
+2016 Historical nectar assessment reveals the fall and rise of floral resources in britain.
+\emph{Nature} \textbf{530}, 85--88.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
+\CSLLeftMargin{17. }
+\CSLRightInline{Munoz F, Violle C, Cheptou P-O.
+2016 {CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
+\emph{Oikos} \textbf{125}, 1296--1303.
+(doi:\href{https://doi.org/10.1111/oik.02328}{10.1111/oik.02328})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-grossenbacher2017}{}}%
+\CSLLeftMargin{18. }
+\CSLRightInline{Grossenbacher DL \emph{et al.} 2017 Self-compatibility is over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
+\CSLLeftMargin{19. }
+\CSLRightInline{Moeller DA \emph{et al.} 2017 Global biogeography of mating system variation in seed plants.
+\emph{Ecol.
+Lett.} \textbf{20}, 375--384.
+(doi:\href{https://doi.org/10.1111/ele.12738}{10.1111/ele.12738})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
+\CSLLeftMargin{20. }
+\CSLRightInline{Sargent RD, Ackerly DD. 2008 Plant--pollinator interactions and the assembly of plant communities. \emph{Trends Ecol. Evol.} \textbf{23}, 123--130.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rech2016}{}}%
+\CSLLeftMargin{21. }
+\CSLRightInline{Rech AR, Dalsgaard B, Sandel B, Sonne J, Svenning J-C, Holmes N, Ollerton J.
+2016 The macroecology of animal versus wind pollination: Ecological factors are more important than historical climate stability.
+\emph{Plant Ecol.
+Divers.} \textbf{9}, 253--262.
+(doi:\href{https://doi.org/10.1080/17550874.2016.1207722}{10.1080/17550874.2016.1207722})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
+\CSLLeftMargin{22. }
+\CSLRightInline{Rüger N, Comita LS, Condit R, Purves D, Rosenbaum B, Visser MD, Wright SJ, Wirth C.
+2018 Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
+\emph{Ecol.
+Lett.} \textbf{21}, 1075--1084.
+(doi:\href{https://doi.org/10.1111/ele.12974}{10.1111/ele.12974})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
+\CSLLeftMargin{23. }
+\CSLRightInline{Tur C, Castro-Urgal R, Traveset A.
+2013 Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}.
+\emph{PLoS One} \textbf{8}, e78294.
+(doi:\href{https://doi.org/10.1371/journal.pone.0078294}{10.1371/journal.pone.0078294})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
+\CSLLeftMargin{24. }
+\CSLRightInline{Devaux C, Lepers C, Porcher E.
+2014 Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems.
+\emph{J.
+Evol.
+Biol.} \textbf{27}, 1413--1430.
+(doi:\href{https://doi.org/10.1111/jeb.12380}{10.1111/jeb.12380})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
+\CSLLeftMargin{25. }
+\CSLRightInline{Rosas-Guerrero V, Aguilar R, Martén-Rodríguez S, Ashworth L, Lopezaraiza-Mikel M, Bastida JM, Quesada M.
+2014 A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
+\emph{Ecol.
+Lett.} \textbf{17}, 388--400.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
+\CSLLeftMargin{26. }
+\CSLRightInline{Stang M, Klinkhamer PGL, Waser NM, Stang I, van der Meijden E.
+2009 Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
+\emph{Ann.
+Bot.} \textbf{103}, 1459--1469.
+(doi:\href{https://doi.org/10.1093/aob/mcp027}{10.1093/aob/mcp027})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
+\CSLLeftMargin{27. }
+\CSLRightInline{Bartomeus I, Gravel D, Tylianakis JM, Aizen MA, Dickie IA, Bernard-Verdier M.
+2016 A common framework for identifying linkage rules across different types of interactions.
+\emph{Funct.
+Ecol.} \textbf{30}, 1894--1903.
+(doi:\href{https://doi.org/10.1111/1365-2435.12666}{10.1111/1365-2435.12666})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
+\CSLLeftMargin{28. }
+\CSLRightInline{Lázaro A, Jakobsson A, Totland Ø.
+2013 How do pollinator visitation rate and seed set relate to species' floral traits and community context?
+\emph{Oecologia} \textbf{173}, 881--893.
+(doi:\href{https://doi.org/10.1007/s00442-013-2652-5}{10.1007/s00442-013-2652-5})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
+\CSLLeftMargin{29. }
+\CSLRightInline{Junker RR, Blüthgen N, Brehm T, Binkenstein J, Paulus J, Schaefer HM, Stang M.
+2013 Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
+\emph{Funct.
+Ecol.} \textbf{27}, 329--341.
+(doi:\href{https://doi.org/10.1111/1365-2435.12005}{10.1111/1365-2435.12005})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
+\CSLLeftMargin{30. }
+\CSLRightInline{Coux C, Rader R, Bartomeus I, Tylianakis JM.
+2016 Linking species functional roles to their network roles.
+\emph{Ecol.
+Lett.} \textbf{19}, 762--770.
+(doi:\href{https://doi.org/10.1111/ele.12612}{10.1111/ele.12612})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
+\CSLLeftMargin{31. }
+\CSLRightInline{Ibanez S.
+2012 Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks.
+\emph{Oecologia} \textbf{170}, 233--242.
+(doi:\href{https://doi.org/10.1007/s00442-012-2290-3}{10.1007/s00442-012-2290-3})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
+\CSLLeftMargin{32. }
+\CSLRightInline{Eklöf A \emph{et al.} 2013 The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
+\CSLLeftMargin{33. }
+\CSLRightInline{Dehling DM, Jordano P, Schaefer HM, Böhning-Gaese K, Schleuning M.
+2016 Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
 \emph{Proc.
 Royal Soc.
-B}, \emph{282}(1814), 20151130.
-\url{https://doi.org/10.1098/rspb.2015.1130}
-
-\leavevmode\vadjust pre{\hypertarget{ref-barrett2002}{}}%
-Barrett, S. C. H. (2002). The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.}, \emph{3}(4), 274--284. \url{https://doi.org/10.1038/nrg776}
+B} \textbf{283}, 20152444.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
+\CSLLeftMargin{34. }
+\CSLRightInline{Kattge J \emph{et al.} 2011 {TRY} \textendash{} a global database of plant traits.
+\emph{Glob.
+Chang.
+Biol.} \textbf{17}, 2905--2935.
+(doi:\href{https://doi.org/10.1111/j.1365-2486.2011.02451.x}{10.1111/j.1365-2486.2011.02451.x})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
+\CSLLeftMargin{35. }
+\CSLRightInline{Salguero-Gómez R \emph{et al.} 2015 The compadre {Plant Matrix Database}: An open online repository for plant demography.
+\emph{J.
+Ecol.} \textbf{103}, 202--218.
+(doi:\href{https://doi.org/10.1111/1365-2745.12334}{10.1111/1365-2745.12334})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
+\CSLLeftMargin{36. }
+\CSLRightInline{Bruelheide H \emph{et al.} 2018 Global trait--environment relationships of plant communities. \emph{Nat. Ecol. Evol.} \textbf{2}, 1906--1917.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
+\CSLLeftMargin{37. }
+\CSLRightInline{Carmona CP \emph{et al.} 2021 Erosion of global functional diversity across the tree of life.
+\emph{Sci.
+Adv.} \textbf{7}, eabf2675.
+(doi:\href{https://doi.org/10.1126/sciadv.abf2675}{10.1126/sciadv.abf2675})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
+\CSLLeftMargin{38. }
+\CSLRightInline{E-Vojtkó A, Bello F de, Durka W, Kühn I, Götzenberger L.
+2020 The neglected importance of floral traits in trait-based plant community assembly.
+\emph{J.
+Veg.
+Sci.} \textbf{31}, 529--539.
+(doi:\href{https://doi.org/10.1111/jvs.12877}{10.1111/jvs.12877})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
+\CSLLeftMargin{39. }
+\CSLRightInline{Sargent RD, Goodwillie C, Kalisz S, Ree RH.
+2007 Phylogenetic evidence for a flower size and number trade-off.
+\emph{Am.
+J.
+Bot.} \textbf{94}, 2059--2062.
+(doi:\href{https://doi.org/10.3732/ajb.94.12.2059}{10.3732/ajb.94.12.2059})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
+\CSLLeftMargin{40. }
+\CSLRightInline{Kettle CJ, Maycock CR, Ghazoul J, Hollingsworth PM, Khoo E, Sukri RSH, Burslem DFRP.
+2011 Ecological {Implications} of a {Flower Size}/{Number Trade}-{Off} in {Tropical Forest Trees}.
+\emph{PLoS One} \textbf{6}, e16111.
+(doi:\href{https://doi.org/10.1371/journal.pone.0016111}{10.1371/journal.pone.0016111})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
+\CSLLeftMargin{41. }
+\CSLRightInline{Goodwillie C \emph{et al.} 2010 Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
+\emph{New Phytol.} \textbf{185}, 311--321.
+(doi:\href{https://doi.org/10.1111/j.1469-8137.2009.03043.x}{10.1111/j.1469-8137.2009.03043.x})}
 
 \leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
-Barrett, S.
-C.
-H.
-(2003).
-Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond.
+\CSLLeftMargin{42. }
+\CSLRightInline{Barrett SCH.
+2003 Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond.
 \emph{Philos.
@@
 B Biol.
-Sci.}, \emph{358}(1434), 991--1004.
-\url{https://doi.org/10.1098/rstb.2003.1301}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
-Bartomeus, I., Gravel, D., Tylianakis, J.
-M., Aizen, M.
-A., Dickie, I.
-A., \& Bernard-Verdier, M.
-(2016).
-A common framework for identifying linkage rules across different types of interactions.
-\emph{Funct.
-Ecol.}, \emph{30}(12), 1894--1903.
-\url{https://doi.org/10.1111/1365-2435.12666}
-
-\leavevmode\vadjust pre{\hypertarget{ref-baude2016}{}}%
-Baude, M., Kunin, W.
-E., Boatman, N.
-D., Conyers, S., Davies, N., Gillespie, M.
-A., Morton, R.
-D., Smart, S.
-M., \& Memmott, J.
-(2016).
-Historical nectar assessment reveals the fall and rise of floral resources in britain.
-\emph{Nature}, \emph{530}(7588), 85--88.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
-Blüthgen, N., Menzel, F., \& Blüthgen, N. (2006). Measuring specialization in species interaction networks. \emph{BMC Ecol.}, \emph{6}(1), 9. \url{https://doi.org/10.1186/1472-6785-6-9}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
-Bruelheide, H., Dengler, J., Purschke, O., Lenoir, J., Jiménez-Alfaro, B., Hennekens, S.
-M., Botta-Dukát, Z., Chytry, M., Field, R., Jansen, F.others.
-(2018).
-Global trait--environment relationships of plant communities.
-\emph{Nat.
-Ecol.
-Evol.}, \emph{2}(12), 1906--1917.
-
-\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
-Bürkner, P.-C. (2017). Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.}, \emph{80}(1), 1--28.
-
-\leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
-Carmona, C.
-P., Tamme, R., Pärtel, M., Bello, F.
-de, Brosse, S., Capdevila, P., González-M, R., González-Suárez, M., Salguero-Gómez, R., Vásquez-Valderrama, M., \& Toussaint, A.
-(2021).
-Erosion of global functional diversity across the tree of life.
-\emph{Sci.
-Adv.}, \emph{7}(13), eabf2675.
-\url{https://doi.org/10.1126/sciadv.abf2675}
+Sci.} \textbf{358}, 991--1004.
+(doi:\href{https://doi.org/10.1098/rstb.2003.1301}{10.1098/rstb.2003.1301})}
 
 \leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
-Carvalheiro, L.
-G., Biesmeijer, J.
-C., Benadi, G., Fründ, J., Stang, M., Bartomeus, I., Kaiser-Bunbury, C.
-N., Baude, M., Gomes, S.
-I.
-F., Merckx, V., Baldock, K.
-C.
-R., Bennett, A.
-T.
-D., Boada, R., Bommarco, R., Cartar, R., Chacoff, N., Dänhardt, J., Dicks, L.
-V., Dormann, C.
-F., \ldots{} Kunin, W.
-E.
-(2014).
-The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
+\CSLLeftMargin{43. }
+\CSLRightInline{Carvalheiro LG \emph{et al.} 2014 The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
 \emph{Ecol.
-Lett.}, \emph{17}(11), 1389--1399.
-\url{https://doi.org/10.1111/ele.12342}
+Lett.} \textbf{17}, 1389--1399.
+(doi:\href{https://doi.org/10.1111/ele.12342}{10.1111/ele.12342})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
+\CSLLeftMargin{44. }
+\CSLRightInline{Olesen JM, Bascompte J, Dupont YL, Jordano P.
+2007 The modularity of pollination networks.
+\emph{PNAS} \textbf{104}, 19891--19896.
+(doi:\href{https://doi.org/10.1073/pnas.0706375104}{10.1073/pnas.0706375104})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
+\CSLLeftMargin{45. }
+\CSLRightInline{Fortuna MA, Stouffer DB, Olesen JM, Jordano P, Mouillot D, Krasnov BR, Poulin R, Bascompte J.
+2010 Nestedness versus modularity in ecological networks: Two sides of the same coin?
+\emph{J.
+Anim.
+Ecol.} \textbf{79}, 811--817.
+(doi:\href{https://doi.org/10.1111/j.1365-2656.2010.01688.x}{10.1111/j.1365-2656.2010.01688.x})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
+\CSLLeftMargin{46. }
+\CSLRightInline{Poisot T \emph{et al.} 2016 Mangal \textendash{} making ecological network analysis simple.
+\emph{Ecography} \textbf{39}, 384--390.
+(doi:\href{https://doi.org/10.1111/ecog.00976}{10.1111/ecog.00976})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
+\CSLLeftMargin{47. }
+\CSLRightInline{Chamberlain S \emph{et al.} 2020 Taxize: {Taxonomic} information from around the web.
+R package version 0.9.99.~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}.
+}
+
+\leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
+\CSLLeftMargin{48. }
+\CSLRightInline{Smith SA, Brown JW.
+2018 Constructing a broadly inclusive seed plant phylogeny.
+\emph{Am.
+J.
+Bot.} \textbf{105}, 302--314.
+(doi:\href{https://doi.org/10.1002/ajb2.1019}{10.1002/ajb2.1019})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
+\CSLLeftMargin{49. }
+\CSLRightInline{Jin Y, Qian H.
+2019 V.{PhyloMaker}: An {R} package that can generate very large phylogenies for vascular plants.
+\emph{Ecography} \textbf{42}, 1353--1359.
+(doi:\href{https://doi.org/10.1111/ecog.04434}{10.1111/ecog.04434})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
+\CSLLeftMargin{50. }
+\CSLRightInline{Stekhoven DJ, Bühlmann P.
+2012 {MissForest}\textemdash non-parametric missing value imputation for mixed-type data.
+\emph{Bioinformatics} \textbf{28}, 112--118.
+(doi:\href{https://doi.org/10.1093/bioinformatics/btr597}{10.1093/bioinformatics/btr597})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
+\CSLLeftMargin{51. }
+\CSLRightInline{Penone C, Davidson AD, Shoemaker KT, Marco MD, Rondinini C, Brooks TM, Young BE, Graham CH, Costa GC.
+2014 Imputation of missing data in life-history trait datasets: Which approach performs the best?
+\emph{Methods Ecol.
+Evol.} \textbf{5}, 961--970.
+(doi:\href{https://doi.org/10.1111/2041-210X.12232}{10.1111/2041-210X.12232})}
 
 \leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
-Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., Bartomeus, I., Baumgartner, J., O'Donnell, J., Oksanen, J., Tzovaras, B.
-G., Marchand, P., Tran, V., Salmon, M., Li, G., \& Grenié, M.
-(2018).
-\emph{Package {`{PVR}.'} R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
-Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., Bartomeus, I., Baumgartner, J., O'Donnell, J., Oksanen, J., Tzovaras, B.
-G., Marchand, P., Tran, V., Salmon, M., Li, G., \& Grenié, M.
-(2020).
-\emph{Taxize: {Taxonomic} information from around the web.
-R package version 0.9.99.~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
-Chave, J., Coomes, D., Jansen, S., Lewis, S. L., Swenson, N. G., \& Zanne, A. E. (2009). Towards a worldwide wood economics spectrum. \emph{Ecol. Lett.}, \emph{12}(4), 351--366.
-
-\leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
-Coux, C., Rader, R., Bartomeus, I., \& Tylianakis, J.
-M.
-(2016).
-Linking species functional roles to their network roles.
-\emph{Ecol.
-Lett.}, \emph{19}(7), 762--770.
-\url{https://doi.org/10.1111/ele.12612}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
-Dehling, D.
-M., Jordano, P., Schaefer, H.
-M., Böhning-Gaese, K., \& Schleuning, M.
-(2016).
-Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
+\CSLLeftMargin{52. }
+\CSLRightInline{Chamberlain S \emph{et al.} 2018 Package {``{PVR}''}. R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
+\CSLLeftMargin{53. }
+\CSLRightInline{Diniz-Filho JAF, Bini LM, Rangel TF, Morales-Castilla I, Olalla-Tárraga MÁ, Rodríguez MÁ, Hawkins BA.
+2012 On the selection of phylogenetic eigenvectors for ecological analyses.
+\emph{Ecography} \textbf{35}, 239--249.
+(doi:\href{https://doi.org/10.1111/j.1600-0587.2011.06949.x}{10.1111/j.1600-0587.2011.06949.x})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-serneels2008}{}}%
+\CSLLeftMargin{54. }
+\CSLRightInline{Serneels S, Verdonck T. 2008 Principal component analysis for data containing outliers and missing elements. \emph{Computational Statistics \& Data Analysis} \textbf{52}, 1712--1727.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
+\CSLLeftMargin{55. }
+\CSLRightInline{Legendre P, Legendre L. 2012 \emph{Numerical ecology}. {2nd edn}. {Elsevier, Amsterdam}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
+\CSLLeftMargin{56. }
+\CSLRightInline{Revell LJ.
+2012 Phytools: An {R} package for phylogenetic comparative biology (and other things).
+\emph{Methods Ecol.
+Evol.} \textbf{3}, 217--223.
+(doi:\href{https://doi.org/10.1111/j.2041-210X.2011.00169.x}{10.1111/j.2041-210X.2011.00169.x})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
+\CSLLeftMargin{57. }
+\CSLRightInline{Abdi H, Williams LJ. 2010 Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459. (doi:\href{https://doi.org/10.1002/wics.101}{10.1002/wics.101})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
+\CSLLeftMargin{58. }
+\CSLRightInline{Ballantyne G, Baldock KCR, Willmer PG.
+2015 Constructing more informative plant\textendash pollinator networks: Visitation and pollen deposition networks in a heathland plant community.
 \emph{Proc.
 Royal Soc.
-B}, \emph{283}(1823), 20152444.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dellinger2020}{}}%
-Dellinger, A. S. (2020). Pollination syndromes in the 21st century: Where do we stand and where may we go? \emph{New Phytol.}, \emph{228}(4), 1193--1213. \url{https://doi.org/10.1111/nph.16793}
-
-\leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
-Devaux, C., Lepers, C., \& Porcher, E.
-(2014).
-Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems.
-\emph{J.
-Evol.
-Biol.}, \emph{27}(7), 1413--1430.
-\url{https://doi.org/10.1111/jeb.12380}
-
-\leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
-Díaz, S., Kattge, J., Cornelissen, J.
-H.
-C., Wright, I.
-J., Lavorel, S., Dray, S., Reu, B., Kleyer, M., Wirth, C., Colin Prentice, I., Garnier, E., Bönisch, G., Westoby, M., Poorter, H., Reich, P.
-B., Moles, A.
-T., Dickie, J., Gillison, A.
-N., Zanne, A.
-E., \ldots{} Gorné, L.
-D.
-(2016).
-The global spectrum of plant form and function.
-\emph{Nature}, \emph{529}(7585), 167--171.
-\url{https://doi.org/10.1038/nature16489}
-
-\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
-Diniz-Filho, J.
-A.
-F., Bini, L.
-M., Rangel, T.
-F., Morales-Castilla, I., Olalla-Tárraga, M.
-Á., Rodríguez, M.
-Á., \& Hawkins, B.
-A.
-(2012).
-On the selection of phylogenetic eigenvectors for ecological analyses.
-\emph{Ecography}, \emph{35}(3), 239--249.
-\url{https://doi.org/10.1111/j.1600-0587.2011.06949.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
-Dormann, C. F., Gruber, B., \& Fründ, J. (2008). Introducing the bipartite package: Analysing ecological networks. \emph{R News}, \emph{8/2}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
-Eklöf, A., Jacob, U., Kopp, J., Bosch, J., Castro-Urgal, R., Chacoff, N.
-P., Dalsgaard, B., Sassi, C.
-de, Galetti, M., Guimaraes, P.
-R.others.
-(2013).
-The dimensionality of ecological networks.
+B} \textbf{282}, 20151130.
+(doi:\href{https://doi.org/10.1098/rspb.2015.1130}{10.1098/rspb.2015.1130})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
+\CSLLeftMargin{59. }
+\CSLRightInline{Vázquez DP, Morris WF, Jordano P.
+2005 Interaction frequency as a surrogate for the total effect of animal mutualists on plants.
 \emph{Ecol.
-Lett.}, \emph{16}(5), 577--583.
-
-\leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
-Encinas-Viso, F., Revilla, T. A., \& Etienne, R. S. (2012). Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.}, \emph{15}(3), 198--208.
-
-\leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
-E-Vojtkó, A., Bello, F.
-de, Durka, W., Kühn, I., \& Götzenberger, L.
-(2020).
-The neglected importance of floral traits in trait-based plant community assembly.
-\emph{J.
-Veg.
-Sci.}, \emph{31}(4), 529--539.
-\url{https://doi.org/10.1111/jvs.12877}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fenster2004}{}}%
-Fenster, C.
-B., Armbruster, W.
-S., Wilson, P., Dudash, M.
-R., \& Thomson, J.
-D.
-(2004).
-Pollination {Syndromes} and {Floral Specialization}.
-\emph{Annu.
-Rev.
-Ecol.
-Evol.
-Syst.}, \emph{35}(1), 375--403.
-\url{https://doi.org/10.1146/annurev.ecolsys.34.011802.132347}
-
-\leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
-Földesi, R., Howlett, B.
-G., Grass, I., \& Batáry, P.
-(2021).
-Larger pollinators deposit more pollen on stigmas across multiple plant species---a meta-analysis.
-\emph{Journal of Applied Ecology}, \emph{58}(4), 699--707.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
-Fortuna, M.
-A., Stouffer, D.
-B., Olesen, J.
-M., Jordano, P., Mouillot, D., Krasnov, B.
-R., Poulin, R., \& Bascompte, J.
-(2010).
-Nestedness versus modularity in ecological networks: Two sides of the same coin?
-\emph{J.
-Anim.
-Ecol.}, \emph{79}(4), 811--817.
-\url{https://doi.org/10.1111/j.1365-2656.2010.01688.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-friedman2020}{}}%
-Friedman, J.
-(2020).
-The evolution of annual and perennial plant life histories: Ecological correlates and genetic mechanisms.
-\emph{Annual Review of Ecology, Evolution, and Systematics}, \emph{51}, 461--481.
+Lett.} \textbf{8}, 1088--1094.
+(doi:\href{https://doi.org/10.1111/j.1461-0248.2005.00810.x}{10.1111/j.1461-0248.2005.00810.x})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
+\CSLLeftMargin{60. }
+\CSLRightInline{Vázquez DP, Lomáscolo SB, Maldonado MB, Chacoff NP, Dorado J, Stevani EL, Vitale NL.
+2012 The strength of plant\textendash pollinator interactions.
+\emph{Ecology} \textbf{93}, 719--725.
+(doi:\href{https://doi.org/10.1890/11-1356.1}{10.1890/11-1356.1})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
+\CSLLeftMargin{61. }
+\CSLRightInline{Hung K-LJ, Kingston JM, Albrecht M, Holway DA, Kohn JR.
+2018 The worldwide importance of honey bees as pollinators in natural habitats.
+\emph{Proc.
+Royal Soc.
+B} \textbf{285}, 20172140.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
+\CSLLeftMargin{62. }
+\CSLRightInline{Bürkner P-C. 2017 Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.} \textbf{80}, 1--28.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
-Gabry, J., Simpson, D., Vehtari, A., Betancourt, M., \& Gelman, A.
-(2019).
-Visualization in {Bayesian} workflow.
+\CSLLeftMargin{63. }
+\CSLRightInline{Gabry J, Simpson D, Vehtari A, Betancourt M, Gelman A.
+2019 Visualization in {Bayesian} workflow.
 \emph{J.
@@
 A Stat.
-Soc.}, \emph{182}(2), 389--402.
-\url{https://doi.org/10.1111/rssa.12378}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gervasi2017}{}}%
-Gervasi, D. D. L., \& Schiestl, F. P. (2017). Real-time divergent evolution in plants driven by pollinators. \emph{Nat. Commun.}, \emph{8}(1), 14691. \url{https://doi.org/10.1038/ncomms14691}
-
-\leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
-Goodwillie, C., Sargent, R.
-D., Eckert, C.
-G., Elle, E., Geber, M.
-A., Johnston, M.
-O., Kalisz, S., Moeller, D.
-A., Ree, R.
-H., Vallejo-Marin, M., \& Winn, A.
-A.
-(2010).
-Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
-\emph{New Phytol.}, \emph{185}(1), 311--321.
-\url{https://doi.org/10.1111/j.1469-8137.2009.03043.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-grossenbacher2017}{}}%
-Grossenbacher, D.
-L., Brandvain, Y., Auld, J.
-R., Burd, M., Cheptou, P.-O., Conner, J.
-K., Grant, A.
-G., Hovick, S.
-M., Pannell, J.
-R., Pauw, A.others.
-(2017).
-Self-compatibility is over-represented on islands.
-\emph{New Phytol.}, \emph{215}(1), 469--478.
+Soc.} \textbf{182}, 389--402.
+(doi:\href{https://doi.org/10.1111/rssa.12378}{10.1111/rssa.12378})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
+\CSLLeftMargin{64. }
+\CSLRightInline{Dormann CF, Gruber B, Fründ J. 2008 Introducing the bipartite package: Analysing ecological networks. \emph{R News} \textbf{8/2}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
+\CSLLeftMargin{65. }
+\CSLRightInline{Blüthgen N, Menzel F, Blüthgen N.
+2006 Measuring specialization in species interaction networks.
+\emph{BMC Ecol.} \textbf{6}, 9.
+(doi:\href{https://doi.org/10.1186/1472-6785-6-9}{10.1186/1472-6785-6-9})}
 
 \leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
-Healy, K., Ezard, T.
-H.
-G., Jones, O.
-R., Salguero-Gómez, R., \& Buckley, Y.
-M.
-(2019).
-Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
+\CSLLeftMargin{66. }
+\CSLRightInline{Healy K, Ezard THG, Jones OR, Salguero-Gómez R, Buckley YM.
+2019 Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
 \emph{Nat.
 Ecol.
-Evol.}, \emph{3}(8), 1217--1224.
-\url{https://doi.org/10.1038/s41559-019-0938-7}
+Evol.} \textbf{3}, 1217--1224.
+(doi:\href{https://doi.org/10.1038/s41559-019-0938-7}{10.1038/s41559-019-0938-7})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-worley2000}{}}%
+\CSLLeftMargin{67. }
+\CSLRightInline{Worley AC, Baker AM, Thompson JD, Barrett SC.
+2000 Floral display in narcissus: Variation in flower size and number at the species, population, and individual levels.
+\emph{International Journal of Plant Sciences} \textbf{161}, 69--79.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-petit2006}{}}%
+\CSLLeftMargin{68. }
+\CSLRightInline{Petit RJ, Hampe A. 2006 Some evolutionary consequences of being a tree. \emph{Annu. Rev. Ecol. Evol. Syst.} \textbf{37}, 187--214.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
-Hegland, S. J., \& Totland, Ø. (2005). Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia}, \emph{145}(4), 586--594.
-
-\leavevmode\vadjust pre{\hypertarget{ref-heinrich1972}{}}%
-Heinrich, B., \& Raven, P.
-H.
-(1972).
-Energetics and pollination ecology: The energetics of pollinators may have wide implications in floral biology and community ecology.
-\emph{Science}, \emph{176}(4035), 597--602.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
-Hung, K.-L.
-J., Kingston, J.
-M., Albrecht, M., Holway, D.
-A., \& Kohn, J.
-R.
-(2018).
-The worldwide importance of honey bees as pollinators in natural habitats.
-\emph{Proc.
-Royal Soc.
-B}, \emph{285}(1870), 20172140.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
-Ibanez, S.
-(2012).
-Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks.
-\emph{Oecologia}, \emph{170}(1), 233--242.
-\url{https://doi.org/10.1007/s00442-012-2290-3}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
-Jin, Y., \& Qian, H.
-(2019).
-V.{PhyloMaker}: An {R} package that can generate very large phylogenies for vascular plants.
-\emph{Ecography}, \emph{42}(8), 1353--1359.
-\url{https://doi.org/10.1111/ecog.04434}
-
-\leavevmode\vadjust pre{\hypertarget{ref-johnson2008}{}}%
-Johnson, S. D., \& Nicolson, S. W. (2008). Evolutionary associations between nectar properties and specificity in bird pollination systems. \emph{Biology Letters}, \emph{4}(1), 49--52.
-
-\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
-Junker, R.
-R., Blüthgen, N., Brehm, T., Binkenstein, J., Paulus, J., Schaefer, H.
-M., \& Stang, M.
-(2013).
-Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
-\emph{Funct.
-Ecol.}, \emph{27}(2), 329--341.
-\url{https://doi.org/10.1111/1365-2435.12005}
+\CSLLeftMargin{69. }
+\CSLRightInline{Hegland SJ, Totland Ø. 2005 Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia} \textbf{145}, 586--594.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
-Kaiser-Bunbury, C.
-N., Vázquez, D.
-P., Stang, M., \& Ghazoul, J.
-(2014).
-Determinants of the microstructure of plant\textendash pollinator networks.
-\emph{Ecology}, \emph{95}(12), 3314--3324.
-\url{https://doi.org/10.1890/14-0024.1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
-Kattge, J., Díaz, S., Lavorel, S., Prentice, I.
-C., Leadley, P., Bönisch, G., Garnier, E., Westoby, M., Reich, P.
-B., Wright, I.
-J., Cornelissen, J.
-H.
-C., Violle, C., Harrison, S.
-P., Bodegom, P.
-M.
-V., Reichstein, M., Enquist, B.
-J., Soudzilovskaia, N.
-A., Ackerly, D.
-D., Anand, M., \ldots{} Wirth, C.
-(2011).
-{TRY} \textendash{} a global database of plant traits.
-\emph{Glob.
-Chang.
-Biol.}, \emph{17}(9), 2905--2935.
-\url{https://doi.org/10.1111/j.1365-2486.2011.02451.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
-Kettle, C.
-J., Maycock, C.
-R., Ghazoul, J., Hollingsworth, P.
-M., Khoo, E., Sukri, R.
-S.
-H., \& Burslem, D.
-F.
-R.
-P.
-(2011).
-Ecological {Implications} of a {Flower Size}/{Number Trade}-{Off} in {Tropical Forest Trees}.
-\emph{PLoS One}, \emph{6}(2), e16111.
-\url{https://doi.org/10.1371/journal.pone.0016111}
-
-\leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
-Laughlin, D.
-C., Mommer, L., Sabatini, F.
-M., Bruelheide, H., Kuyper, T.
-W., McCormack, M.
-L., Bergmann, J., Freschet, G.
-T., Guerrero-Ramírez, N.
-R., Iversen, C.
-M.others.
-(2021).
-Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
-\emph{Nat.
-Ecol.
-Evol.}, 1--12.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
-Lázaro, A., Jakobsson, A., \& Totland, Ø.
-(2013).
-How do pollinator visitation rate and seed set relate to species' floral traits and community context?
-\emph{Oecologia}, \emph{173}(3), 881--893.
-\url{https://doi.org/10.1007/s00442-013-2652-5}
-
-\leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
-Legendre, P., \& Legendre, L. (2012). \emph{Numerical ecology} ({2nd edn}). {Elsevier, Amsterdam}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-mackin2021}{}}%
-Mackin, C.
-R., Peña, J.
-F., Blanco, M.
-A., Balfour, N.
-J., \& Castellanos, M.
-C.
-(2021).
-Rapid evolution of a floral trait following acquisition of novel pollinators.
-\emph{J.
-Ecol.}, \emph{109}(5), 2234--2246.
-\url{https://doi.org/10.1111/1365-2745.13636}
-
-\leavevmode\vadjust pre{\hypertarget{ref-milborrow2015}{}}%
-Milborrow, S.
-(2015).
-\emph{Rpart.
-Plot: {Plot} rpart {Models}.
-{An Enhanced Version} of plot.
-Rpart.
-R package version 3.0.9.~At \href{https://CRAN.R-project.org/package=rpart.plot}{https://CRAN.r-project.org/package=rpart.plot}}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
-Moeller, D.
-A., Runquist, R.
-D.
-B., Moe, A.
-M., Geber, M.
-A., Goodwillie, C., Cheptou, P.-O., Eckert, C.
-G., Elle, E., Johnston, M.
-O., Kalisz, S., Ree, R.
-H., Sargent, R.
-D., Vallejo-Marin, M., \& Winn, A.
-A.
-(2017).
-Global biogeography of mating system variation in seed plants.
-\emph{Ecol.
-Lett.}, \emph{20}(3), 375--384.
-\url{https://doi.org/10.1111/ele.12738}
-
-\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
-Munoz, F., Violle, C., \& Cheptou, P.-O.
-(2016).
-{CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
-\emph{Oikos}, \emph{125}(9), 1296--1303.
-\url{https://doi.org/10.1111/oik.02328}
-
-\leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
-Olesen, J. M., Bascompte, J., Dupont, Y. L., \& Jordano, P. (2007). The modularity of pollination networks. \emph{PNAS}, \emph{104}(50), 19891--19896. \url{https://doi.org/10.1073/pnas.0706375104}
-
-\leavevmode\vadjust pre{\hypertarget{ref-onoda2017}{}}%
-Onoda, Y., Wright, I.
-J., Evans, J.
-R., Hikosaka, K., Kitajima, K., Niinemets, Ü., Poorter, H., Tosens, T., \& Westoby, M.
-(2017).
-Physiological and structural tradeoffs underlying the leaf economics spectrum.
-\emph{New Phytologist}, \emph{214}(4), 1447--1463.
-
-\leavevmode\vadjust pre{\hypertarget{ref-paterno2020}{}}%
-Paterno, G.
-B., Silveira, C.
-L., Kollmann, J., Westoby, M., \& Fonseca, C.
-R.
-(2020).
-The maleness of larger angiosperm flowers.
-\emph{Proceedings of the National Academy of Sciences}, \emph{117}(20), 10921--10926.
-
-\leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
-Penone, C., Davidson, A.
-D., Shoemaker, K.
-T., Marco, M.
-D., Rondinini, C., Brooks, T.
-M., Young, B.
-E., Graham, C.
-H., \& Costa, G.
-C.
-(2014).
-Imputation of missing data in life-history trait datasets: Which approach performs the best?
-\emph{Methods Ecol.
-Evol.}, \emph{5}(9), 961--970.
-\url{https://doi.org/10.1111/2041-210X.12232}
-
-\leavevmode\vadjust pre{\hypertarget{ref-petit2006}{}}%
-Petit, R. J., \& Hampe, A. (2006). Some evolutionary consequences of being a tree. \emph{Annu. Rev. Ecol. Evol. Syst.}, \emph{37}, 187--214.
-
-\leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
-Poisot, T., Baiser, B., Dunne, J.
-A., Kéfi, S., Massol, F., Mouquet, N., Romanuk, T.
-N., Stouffer, D.
-B., Wood, S.
-A., \& Gravel, D.
-(2016).
-Mangal \textendash{} making ecological network analysis simple.
-\emph{Ecography}, \emph{39}(4), 384--390.
-\url{https://doi.org/10.1111/ecog.00976}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rech2016}{}}%
-Rech, A.
-R., Dalsgaard, B., Sandel, B., Sonne, J., Svenning, J.-C., Holmes, N., \& Ollerton, J.
-(2016).
-The macroecology of animal versus wind pollination: Ecological factors are more important than historical climate stability.
-\emph{Plant Ecol.
-Divers.}, \emph{9}(3), 253--262.
-\url{https://doi.org/10.1080/17550874.2016.1207722}
-
-\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
-Revell, L.
-J.
-(2012).
-Phytools: An {R} package for phylogenetic comparative biology (and other things).
-\emph{Methods Ecol.
-Evol.}, \emph{3}(2), 217--223.
-\url{https://doi.org/10.1111/j.2041-210X.2011.00169.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-roddy2021}{}}%
-Roddy, A.
-B., Martínez-Perez, C., Teixido, A.
-L., Cornelissen, T.
-G., Olson, M.
-E., Oliveira, R.
-S., \& Silveira, F.
-A.
-O.
-(2021).
-Towards the flower economics spectrum.
-\emph{New Phytol.}, \emph{229}(2), 665--672.
-\url{https://doi.org/10.1111/nph.16823}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
-Rosas-Guerrero, V., Aguilar, R., Martén-Rodríguez, S., Ashworth, L., Lopezaraiza-Mikel, M., Bastida, J.
-M., \& Quesada, M.
-(2014).
-A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
-\emph{Ecol.
-Lett.}, \emph{17}(3), 388--400.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
-Rüger, N., Comita, L.
-S., Condit, R., Purves, D., Rosenbaum, B., Visser, M.
-D., Wright, S.
-J., \& Wirth, C.
-(2018).
-Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
-\emph{Ecol.
-Lett.}, \emph{21}(7), 1075--1084.
-\url{https://doi.org/10.1111/ele.12974}
-
-\leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
-Salguero-Gómez, R., Jones, O.
-R., Archer, C.
-R., Buckley, Y.
-M., Che-Castaldo, J., Caswell, H., Hodgson, D., Scheuerlein, A., Conde, D.
-A., Brinks, E., Buhr, H.
-de, Farack, C., Gottschalk, F., Hartmann, A., Henning, A., Hoppe, G., Römer, G., Runge, J., Ruoff, T., \ldots{} Vaupel, J.
-W.
-(2015).
-The compadre {Plant Matrix Database}: An open online repository for plant demography.
-\emph{J.
-Ecol.}, \emph{103}(1), 202--218.
-\url{https://doi.org/10.1111/1365-2745.12334}
-
-\leavevmode\vadjust pre{\hypertarget{ref-salguero2016}{}}%
-Salguero-Gómez, R., Jones, O.
-R., Jongejans, E., Blomberg, S.
-P., Hodgson, D.
-J., Mbeau-Ache, C., Zuidema, P.
-A., de Kroon, H., \& Buckley, Y.
-M.
-(2016).
-Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
-\emph{Proc.
-Natl.
-Acad.
-Sci.
-U.S.A.}, \emph{113}(1), 230--235.
-\url{https://doi.org/10.1073/pnas.1506215112}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
-Sargent, R. D., \& Ackerly, D. D. (2008). Plant--pollinator interactions and the assembly of plant communities. \emph{Trends Ecol. Evol.}, \emph{23}(3), 123--130.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
-Sargent, R.
-D., Goodwillie, C., Kalisz, S., \& Ree, R.
-H.
-(2007).
-Phylogenetic evidence for a flower size and number trade-off.
-\emph{Am.
-J.
-Bot.}, \emph{94}(12), 2059--2062.
-\url{https://doi.org/10.3732/ajb.94.12.2059}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schiestl2013}{}}%
-Schiestl, F. P., \& Johnson, S. D. (2013). Pollinator-mediated evolution of floral signals. \emph{Trends Ecol. Evol.}, \emph{28}(5), 307--315. \url{https://doi.org/10.1016/j.tree.2013.01.019}
-
-\leavevmode\vadjust pre{\hypertarget{ref-serneels2008}{}}%
-Serneels, S., \& Verdonck, T. (2008). Principal component analysis for data containing outliers and missing elements. \emph{Computational Statistics \& Data Analysis}, \emph{52}(3), 1712--1727.
-
-\leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
-Smith, S. A., \& Brown, J. W. (2018). Constructing a broadly inclusive seed plant phylogeny. \emph{Am. J. Bot.}, \emph{105}(3), 302--314. \url{https://doi.org/10.1002/ajb2.1019}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
-Stang, M., Klinkhamer, P.
-G.
-L., Waser, N.
-M., Stang, I., \& van der Meijden, E.
-(2009).
-Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
-\emph{Ann.
-Bot.}, \emph{103}(9), 1459--1469.
-\url{https://doi.org/10.1093/aob/mcp027}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stearns1989}{}}%
-Stearns, S. C. (1989). Trade-offs in life-history evolution. \emph{Functional Ecology}, \emph{3}(3), 259--268.
-
-\leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
-Stekhoven, D.
-J., \& Bühlmann, P.
-(2012).
-{MissForest}\textemdash non-parametric missing value imputation for mixed-type data.
-\emph{Bioinformatics}, \emph{28}(1), 112--118.
-\url{https://doi.org/10.1093/bioinformatics/btr597}
-
-\leavevmode\vadjust pre{\hypertarget{ref-therneau2015}{}}%
-Therneau, T., Atkinson, B., Ripley, B., \& Ripley, M.
-B.
-(2015).
-\emph{Package {`rpart.'} R package version 4.1-15.~At \href{https://CRAN.R-project.org/package=rpart}{https://CRAN.r-project.org/package=rpart}}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
-Tur, C., Castro-Urgal, R., \& Traveset, A.
-(2013).
-Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}.
-\emph{PLoS One}, \emph{8}(10), e78294.
-\url{https://doi.org/10.1371/journal.pone.0078294}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vaudo2015}{}}%
-Vaudo, A. D., Tooker, J. F., Grozinger, C. M., \& Patch, H. M. (2015). Bee nutrition and floral resource restoration. \emph{Current Opinion in Insect Science}, \emph{10}, 133--141.
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
-Vázquez, D.
-P., Lomáscolo, S.
-B., Maldonado, M.
-B., Chacoff, N.
-P., Dorado, J., Stevani, E.
-L., \& Vitale, N.
-L.
-(2012).
-The strength of plant\textendash pollinator interactions.
-\emph{Ecology}, \emph{93}(4), 719--725.
-\url{https://doi.org/10.1890/11-1356.1}
+\CSLLeftMargin{70. }
+\CSLRightInline{Kaiser-Bunbury CN, Vázquez DP, Stang M, Ghazoul J.
+2014 Determinants of the microstructure of plant\textendash pollinator networks.
+\emph{Ecology} \textbf{95}, 3314--3324.
+(doi:\href{https://doi.org/10.1890/14-0024.1}{10.1890/14-0024.1})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
+\CSLLeftMargin{71. }
+\CSLRightInline{Földesi R, Howlett BG, Grass I, Batáry P.
+2021 Larger pollinators deposit more pollen on stigmas across multiple plant species---a meta-analysis.
+\emph{Journal of Applied Ecology} \textbf{58}, 699--707.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
-Vázquez, D.
-P., Melián, C.
-J., Williams, N.
-M., Blüthgen, N., Krasnov, B.
-R., \& Poulin, R.
-(2007).
-Species abundance and asymmetric interaction strength in ecological networks.
-\emph{Oikos}, \emph{116}(7), 1120--1127.
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
-Vázquez, D.
-P., Morris, W.
-F., \& Jordano, P.
-(2005).
-Interaction frequency as a surrogate for the total effect of animal mutualists on plants.
-\emph{Ecol.
-Lett.}, \emph{8}(10), 1088--1094.
-\url{https://doi.org/10.1111/j.1461-0248.2005.00810.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-worley2000}{}}%
-Worley, A.
-C., Baker, A.
-M., Thompson, J.
-D., \& Barrett, S.
-C.
-(2000).
-Floral display in narcissus: Variation in flower size and number at the species, population, and individual levels.
-\emph{International Journal of Plant Sciences}, \emph{161}(1), 69--79.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%
-Wright, I.
-J., Reich, P.
-B., Westoby, M., Ackerly, D.
-D., Baruch, Z., Bongers, F., Cavender-Bares, J., Chapin, T., Cornelissen, J.
-H.
-C., Diemer, M., Flexas, J., Garnier, E., Groom, P.
-K., Gulias, J., Hikosaka, K., Lamont, B.
-B., Lee, T., Lee, W., Lusk, C., \ldots{} Villar, R.
-(2004).
-The worldwide leaf economics spectrum.
-\emph{Nature}, \emph{428}(6985), 821--827.
-\url{https://doi.org/10.1038/nature02403}
+\CSLLeftMargin{72. }
+\CSLRightInline{Vázquez DP, Melián CJ, Williams NM, Blüthgen N, Krasnov BR, Poulin R.
+2007 Species abundance and asymmetric interaction strength in ecological networks.
+\emph{Oikos} \textbf{116}, 1120--1127.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
+\CSLLeftMargin{73. }
+\CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS. 2012 Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.} \textbf{15}, 198--208.}
 
@@
 
+\clearpage
+
 \doublespacing
@@
 
-\blandscape
-
-\begin{figure}
-\centering
-\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
-\caption{\label{fig:unnamed-chunk-5}\textbf{Figure 4} Contribution of traits in plant's network roles.
-Regression tree analysis of number of visits (log-transformed), normalized degree and specialization for the subset of species with quantitative data for pollen and nectar traits.
-The superior value inside the node indicates the mean value of the different species-level metric and the lower value, the percentage of species that are considered in each node.
-Thus, the top node has the mean value of the named trait for the 100\% of species.
-Each node has a yes/no question and when the condition is fulfilled, the branch turns to the `yes' direction and when not, to the `no' direction.
-This rationale is followed in all the regression trees as indicated in the first branch division of the topmost node of each tree.}
-\end{figure}
-
-\elandscape
-
 \end{document}

### 2022-06-21 Manuscript/Regression_trees.Rmd
edits

--- 2022-04-15 Manuscript/Lanuza_et_al_2021_Ecol_Letters.Rmd
@@
 ---
-title: \singlespacing \vspace{-1.6cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors
-
-#author: 
-#  - Jose B. Lanuza^1,2^*
-#  - Romina Rader^1^
-#  - Jamie Stavert^3^
-#  - Liam K. Kendall^4^
-#  - Manu E. Saunders^1^
-#  - Ignasi Bartomeus^2^
-
-# may use lua filters for affiliations etc: see https://stackoverflow.com/a/52919256
-
-# date: '`r Sys.Date()`'
-
-output:
-  bookdown::pdf_document2:
-    fig_caption: yes
-    fig_width: 7
-    fig_height: 7
-    df_print: kable
-    keep_tex: yes
-    number_sections: no
-    extra_dependencies: ["float"]
-    toc: no
-    fig_crop: no
-    includes:
-      in_header: header.tex
-
-documentclass: article
-# classoption: twocolumn, landscape, etc
-papersize: a4
-pagestyle: plain  # plain, empty, headings
-geometry: margin=1in
-linestretch: 2
-fontfamily: mathpazo
-fontsize: 12pt
-
-bibliography: 
-  - references.bib
-  - knitcitations.bib
-# zotero: "My shared Zotero group"
-csl: ecology.csl #ecology letters
-notes-after-punctuation: false
-link-citations: yes
-linkcolor: RoyalBlue
-urlcolor: RoyalBlue
-links-as-notes: false
-subparagraph: yes
-
-header-includes:
-- \usepackage{booktabs}
-- \usepackage{longtable}
-- \usepackage{array}
-- \usepackage{multirow}
-- \usepackage{wrapfig}
-- \usepackage{float}
-- \usepackage{colortbl}
-- \usepackage{tabu}
-- \usepackage{threeparttable}
-- \usepackage{threeparttablex}
-- \usepackage[normalem]{ulem}
-- \usepackage{makecell}
-- \usepackage{xcolor}
-- \usepackage{float}
-- \floatplacement{figure}{H}
-- \usepackage[skip=3pt]{caption}
-- \captionsetup[figure]{labelformat=empty}
-- \usepackage{setspace}
-- \usepackage{titlesec}
-- \titlespacing{\title}{0pt}{\parskip}{-\parskip}
-- \usepackage[style=nature]{biblatex}
-- \usepackage[labelformat = empty]{caption}
-- \usepackage{pdflscape}
-#- \DeclareUnicodeCharacter{0301}{*************************************}
-
+title: "Untitled"
+output: html_document
 ---
-
-\vspace{-1.4cm}
-
-\singlespacing
-
-\textbf{Jose B.
-Lanuza$^{1,2}$} <barragansljose@gmail.com>, \textbf{Romina Rader$^{1}$} <rrader@une.edu.au>, \textbf{Jamie Stavert$^{3}$} <jamie.stavert@gmail.com>, \textbf{Liam K.
-Kendall$^{4}$} <liam.k.kendall@gmail.com>, \textbf{Manu E.
-Saunders$^{1}$} <Manu.Saunders@une.edu.au> \textbf{and Ignasi Bartomeus$^{2}$} <nacho.bartomeus@gmail.com>
-
-\small
-
-^1^ School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-^2^ Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-^3^ Department of Conservation | Te Papa Atawhai, Auckland, New Zealand.
-^4^ Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden.
-
-\doublespacing
-\normalsize
-
-\textbf{Statement of authorship:} JBL, RR and IB designed the study.
-JBL collated the data and conducted analysis with guidance of JS, LKK and IB.
-JBL wrote the manuscript with contributions of all authors.
-
-\textbf{Data accessibility statement:} All data and code used to conduct this study will be deposited in the public repository Dryad upon acceptance.
-
-\textbf{Short title:} Plant reproductive trade-offs.
-
-\textbf{Keywords:} life-history strategies | plant reproductive trade-offs | plant-pollinator interactions.
-
-\textbf{Type of article:} Letter.
-
-\textbf{Number of words:} Abstract  (146 words), main text excluding references, acknowledgements and captions (4983 words).
-
-\textbf{Number of references:} 75
-
-\textbf{Number of figures and tables:} 4 figures and 1 table.
-
-\textbf{Corresponding author:} Jose B. Lanuza | +34 616375981| <barragansljose@gmail.com>
-
-\newpage
-
-# ABSTRACT
-
-Plant life-history strategies are constrained by cost-benefit trade-offs that determine plant form and function.
-However, despite recent advances in the understanding of plant trait variation, little is known about plant reproductive trade-offs and how these constrain life-history strategies and shape interactions with floral visitors.
-Here, we investigate plant reproductive trade-offs and how these drive interactions with floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
-We found that over half of all plant reproductive trait variation was explained by two independent axes.
-Specifically, the first axis indicated the presence of a trade-off between flower number and flower size, while the second axis indicated a pollinator dependency trade-off.
-In addition, plant reproductive trade-offs determined important differences in the interaction level among floral visitor guilds.
-Our study shows the main reproductive trade-offs of flowering plants and their relevance to understand plant-pollinator interactions in a global context.
-
-\newpage
-
-\doublespacing
-\vspace{5mm}
-\normalsize
-
-```{r setup, include=FALSE, cache=FALSE, message = FALSE}
-
-library("knitr")
-
-### Chunk options: see http://yihui.name/knitr/options/ ###
-## Text results
-opts_chunk$set(echo = FALSE, warning = TRUE, message = TRUE)
-
-## Code decoration
-opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)
-
-## Cache
-# opts_chunk$set(cache = 2, cache.path = "output/cache/")
-
-## Plots
-opts_chunk$set(fig.path = "output/figures/")
-
-```
-
-```{r knitcitations, cache = FALSE}
-library(knitcitations)
-cleanbib()   
-cite_options(citation_format = "pandoc")
-
-```
-
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.pos = 'H')
-```
-
-# INTRODUCTION
-
-Flowering plants have an astonishing diversity of floral structures [@barrett2002; @schiestl2013] that shape plant-pollinator associations [@fenster2004; @dellinger2020].
-However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [REF].
-Despite the recent advances in the theoretical understanding of the major floral trade-offs (e.g., floral economic spectrum; REF), we lack empirical evidence that helps to elucidate the spectrum of reproductive trait variation at a global scale as done recently for other vegetative and physiological traits [REF].
-
-Macroecological studies that investigate plant reproductive traits are scarce [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017] and consequently, there is poor understanding of how reproductive traits drive interactions with pollinators at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
-Linking the plant's position in trait-space with the different pollinator groups could help to improve our understanding of plant-pollinator associations [@dehling2016].
-Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016].
-However, plant reproductive traits have been overlooked beyond highly specialised pollination systems [@dellinger2020] and remains unclear how specific plant reproductive biology traits (e.g., mating or compatibility system) influence plant-pollinator associations [@tur2013; @devaux2014].
-
-Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use.
-With the recent availability of large trait databases [e.g., TRY @kattge2011; and COMPADRE @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
-However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success.
-For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively, [@barrett2003; @moeller2017] and outcrossing levels are positively correlated with flower size [@goodwillie2010].
-In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators [@ollerton2011; @rodger2021].
-However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.
-
-Several studies have identified links between plant traits and plant-pollinator network properties [@bartomeus2013; @olito2015; @rowe2020].
-Moreover, plant traits can define species’ network roles [e.g., specialists vs generalists\; @lazaro2013; @tur2013].
-For example, plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
-Morphological matching between plant and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
-Importantly, the combination of traits has shown to increase the predictive power of the network interactions [@eklof2013] and by considering the position in the multidimensional trait space we can determine species’ roles within plant-pollinator interaction networks [@dehling2016].
-Nonetheless, we know little if those patterns generally studied at the community level are representative of wider macroecological scales.
-
-Here, we aim to explore the potential trade-offs among reproductive traits and how these influence plant-pollinator interactions.
-First, we identify the major axes of reproductive trait variation and trade-offs that determine plant form and function.
-Second, we investigate how plant species’ position in trait-space influence interactions with floral visitors.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species’ roles within networks using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
-
-# MATERIALS AND METHODS
-
-**Plant-pollinator network studies**
-
-We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks.
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation.
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies [@olesen2007; @fortuna2010; @carvalheiro2014] or available in online archives [e.g., The Web of Life, @fortuna2010; and Mangal, @poisot2016].
-In total, our network dataset (Table S1) constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
-
-**Taxonomy of plants and pollinators**
-
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (https://www.ncbi.nlm.nih.gov/taxonomy) for plants and ITIS (https://www.itis.gov/) for pollinators, using the R package _taxize_ [@chamberlain2020].
-We filled the ‘not found’ searches manually using http://www.theplantlist.org/ and http://www.mobot.org/ for plants and http://www.catalogueoflife.org/ for floral visitors.
-
-**Plant traits**
-
-We selected a total of 19 different functional traits that included both reproductive and vegetative traits (see Table 1 and Supplementary Information).
-From these, 16 were reproductive traits (13 floral and 3 reproductive biology traits) and were selected based on their relevance to plant reproduction and data availability.
-The 3 remaining traits, were vegetative traits that are commonly used to characterize the global spectrum of plant form and function and represent the fast-slow continuum of trait variation (e.g., short-lived versus perennial species).
-For each plant species, we undertook an extensive literature and online search across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 cells (20 columns × 1,506 species) we were able to fill 24,341 cells (80.8% of the dataset, see Fig.
-S1 for missing values information for each trait).
-
-**Phylogenetic Distance**
-
-We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package _rtrees_ (https://github.com/daijiang/rtrees), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
-
-**Data Imputation**
-
-Trait missing values were imputed with the function _missForest_ [@stekhoven2012] which allows imputation of data sets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of _missForest_ [@penone2014].
-To extract the eigenvectors, we used the function _PVRdecomp_ from the package _PVR_ [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-We conducted two different imputations, one for the full set of species (1,506 species, 5.79% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
-S1) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01% of missing values).
-
-**Plant strategies**
-
-We explored the trade-offs between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson’s correlation = 0.72, _P_ < 0.01 and Pearson’s correlation = 0.36, _P_ < 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the association of the different qualitative traits with the main axes of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers, we excluded values within the 2.5th–97.5th percentile range [@legendre2012], and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range.
-We performed the pPCA using the function _phyl.pca_ from the package _phytools_ [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
-Moreover, to corroborate that our imputation of missing values did not affect our results, we conducted a pPCA on the full dataset without missing values (Fig.
-S2).
-We found little difference between the explained variance with the imputed dataset (51.08%) and the dataset without missing values (52.87%).
-In addition, the loadings on each principal component had a similar contribution and correlation patterns, with the exception of plant height which showed slight variations between the imputed and non-imputed dataset.
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
-For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
-
-**Phylogenetic signal**
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package _phytools_ [@revell2012] and we used Pagel’s $\lambda$ as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-**Network analyses**
-
-Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-These networks were analysed in their qualitative and quantitative form.
-First, we analysed the binary version of these weighted networks with presence-absence information that assumes equal weight across interactions.
-Second, we analysed the untransformed weighted networks with the number of visits of floral visitors to individual flowers that account for the intensity of the interaction.
-Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency [@ballantyne2015], the number of visits can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
-All analyses were conducted in R version _4.0.3_.
-
-**Visitation patterns**
-
-We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that _Apis mellifera_ was the floral visitor with the largest proportion of records counted (7.55% of the total).
-This finding is consistent with previous research showing that _A.
-mellifera_ was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
-Hence, to control for the effect of _A.
-mellifera_ on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding _A.
-mellifera_.
-We found that _A.
-mellifera_, was partly driving some of the observed trends on PC1 (Fig.
-S3).
-However, we did not detect major differences on PC2 and PC3.
-
-We implemented Bayesian generalized linear mixed models using the R package _brms_ [@burkner2017].
-We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits ~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
-We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with weakly informative priors from the brms function, 3,000 iterations and with previous 1,000 warm up iterations.
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the _bayesplot_ package [@gabry2019].
-
-**Plant species network roles**
-
-We investigated whether different quantitative traits determined plant species network roles using Bayesian modelling and regression trees.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d’) [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the _specieslevel_ function from the R package _bipartite_ [@dormann2008].
-
-First, we modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric ~ PC1 + PC2 + PC3).
-For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the ‘visitation patterns’ section.
-
-Second, to better understand complex trait relationships, we used regression trees.
-Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction.
-We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
-We conducted this analysis using the _rpart_ package [@therneau2015] with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] to plot the regression trees.
-We considered the species level indices as response variables (number of visits, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
-We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
-We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (Fig.
-S4).
-
-# RESULTS
-
-**Plant strategies**
-
-The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of trait variation, respectively (Fig.
-1 and Fig.
-S5) and had a phylogenetic correlation ($\lambda$) of 0.76.
-The first principal component (PC1) represented 26.72% of the trait variation and indicated a trade-off between flower number and flower size.
-We refer to this axis as the ‘flower number - flower size trade-off’, as already described in previous studies [@sargent2007; @kettle2011].
-Hence, one end of the spectrum comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings > |0.5|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
-The second principal component (PC2) represented 25.05% of the trait variation and indicated a trade-off between low and high pollinator dependence.
-We refer to this axis as the ‘pollinator dependence trade-off’.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
-We found that high pollinator dependence was associated with larger and a higher number of flowers, greater plant height and longer styles.
-In contrast, species with high levels of autonomous selfing tended to have fewer and smaller flowers, had shorter styles and were shorter in height.
-Further, PC3 explained a considerable amount of trait variability (19.17%) and the main contributors to this axis were style length (loading = -0.66) and the degree of autonomous selfing (loading = -0.51).
-The remaining traits, apart from ovule number, were moderately correlated to changes on PC3 (loadings from -0.23 to -0.46; Table S3).
-Thus, because style length was correlated with all traits on PC3 and was the main driver of trait variation, we refer to this axis as the ‘style length trade-off’.
-Further, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (PC1, 26.82%; Fig.
-S6).
-This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (Table S4).
-
-We found that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
-2 and Table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, _P_ < 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , _P_ = 0.59; PC2:  Sum of squares = 0.83, F-value = 1.43, _P_ = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
-S7).
-Regarding self compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self incompatible were statistically differentiated from species with partial or full self compatibility; Fig.
-S7a and Fig.
-S7b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
-S7c and Fig.
-S7d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
-S7e and Fig.
-S7f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
-S7g and Fig.
-S7h).
-Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and greater autonomous selfing (Fig.
-S7i and Fig.
-S7j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Fig.
-S7k and Fig.
-S7l).
-
-**Phylogenetic signal**
-
-We found a strong phylogenetic signal (*P* < 0.01) in all quantitative traits (Table S5).
-The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
-The traits that showed a moderate phylogenetic signal were inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits ($\lambda$ = 0.14).
-
-**Visitation patterns**
-
-The main axes of trait variation explained partly presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (Fig.
-3).
-We found that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds (flower number - flower size trade-off, PC1; Fig.
-3a).
-However, plant species with high flower number but small flowers had higher number of visits of bees and syrphids guilds (PC1; Fig.
-3d).
-Remarkably, all plant species with higher pollinator dependence had higher number of interacting partners and number of visits for all floral visitor guilds (PC2; Fig.
-3b and Fig.
-3e).
-Finally, plant species with short styles and low selfing had higher interaction partners of all guilds but bees that interacted clearly more with plant species with long styles and high selfing (style length trade-off; Fig.
-3c).
-However, for number of visits, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
-3f).
-
-The additional model for both presence-absence of interaction (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (Fig.
-3a and Fig.
-3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (Fig.
-S8).
-
-**Plant species network roles**
-
-The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
-S9; number of visits ~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree ~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization ~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on PC1 and PC3 for number of visits and specialization.
-On the flower number - flower size trade-off (PC1), number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
-S9a).
-On PC1, specialization showed the opposite trend (Fig.
-S9g).
-On the style length trade-off (PC3), number of visits was lower for plants with shorter styles and lower autonomous selfing and higher for species with longer styles and higher autonomous selfing (Fig.
-S9c).
-Again, specialization showed the opposite trend to number of visits (Fig.
-S9i).
-
-When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for number of visits was best explained by plant height, nectar concentration and style length (Fig.
-4a).
-Specifically, species taller than 3.9m had the highest number of visits, while species that were shorter than 3.9m and had a nectar concentration lower than 16% had the lowest number of visits.
-Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
-4b).
-Species with a nectar concentration over 49% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49%, more than 21,000 pollen grains per flower and height less than 0.78m had the lowest normalized degree.
-Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
-4c).
-Overall, plant species with the highest specialization were shorter than 1.3m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11% of their fruits.
-In contrast, species taller or equal than 5.1m and with lower than 14 ovules per flower had the lowest specialization values.
-
-# DISCUSSION
-
-This study demonstrates that plant species exhibit clear trade-offs among their vegetative and reproductive traits and that these trade-offs determine interactions with floral visitors.
-These trade-offs are differentiated along three axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length.
-These reproductive trade-offs helped partly explain the presence of floral visitor interactions, but not their number of visits.
-However, floral visitor guilds formed distinct relationships with the main axes of trait variation.
-Moreover, we found that the plant species network roles were best explained by plant size and floral reward related traits.
-
-Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs.
-Trait variation on these two axes was associated with the ‘fast-slow continuum’ in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-The ‘slow’ part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species).
-In contrast, plant species that employed the ‘fast’ strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence.
-Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010].
-The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig.
-S10).
-
-Despite the low predictive power of the main trait variation axes for broad-level interaction patterns (number of interaction partners and number of visits), we found changes in the interaction patterns among and within floral visitor guilds across these axes that suggest plant life-history strategies influence plant-pollinator interactions.
-For example, all floral visitor guilds visited plant species with higher pollinator dependence more frequently, and high pollinator dependence was associated with large floral displays and greater pollen quantities (Fig.
-1 and Fig.
-S6).
-This trend is consistent with previous studies that show plant species with higher reproductive investment tend to be visited by pollinators more frequently [@hegland2005; @lazaro2013; @kaiser2014].
-In regard to the flower number - flower size and style length trade-offs, different pollinator guilds showed contrasting visitation patterns across the continuum of trait variation, which could be associated with different pollination syndromes at a macroecological scale.
-For instance, bees and syrphid flies were clearly associated with opposing life-strategies on PC1 and PC3 (Fig.
-3) suggesting possible niche partitioning [@palmer2003; @phillips2020] between these two guilds.
-However, despite floral rewards not being included in the main analysis because there was insufficient data available, floral reward related traits were among the best at characterising species network roles (Fig.
-4).
-More detailed exploration of reproductive trade-offs in conjunction with floral rewards is needed to help elucidate plant-pollinator associations.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive trade-offs do not.
-
-To conclude, we provide a robust description of plant reproductive trade-offs using a large global dataset of plant traits.
-We identified the major reproductive strategies of flowering plants and how these strategies influence interactions with different floral visitor guilds.
-Although the explained variation that we found in the first two axes is lower than previous studies of vegetative traits [@diaz2016; @carmona2021] it is consistent with the largest and most recent study that has characterised plant life strategies with vegetative and reproductive traits [@salguero2016].
-Future work needs to integrate the reproductive compromises that we have identified with vegetative and physiological trade-offs to create a more comprehensive spectrum of plant trait variation.
-Further, the varying level of phylogenetic signal among traits deserves further attention to understand evolutionary changes on mating and flower morphology in response to pollinators [@gervasi2017; @mackin2021].
-Finally, including plant-pollinator networks from unrepresented areas of the world and a more complete description of plant reproductive trade-offs is essential for a better understanding of the global patterns in plant-pollinator interactions.
-
-# References
-
-<div id ="refs"></div>
-
-# Acknowledgements
-
-This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-We thank all researchers that made their data openly available and sent it upon request.
-We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
-We also thank Jason Tylianakis for his comments on the manuscript before submission.
-Finally, JBL thanks the University of New England for the funding provided to carry out this work.
-
-\singlespacing
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=1, fig.width=14}
-setwd("~/R_Projects/Reproductive Traits")
-
-library(kableExtra)
-
-library(dplyr)
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant","Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Floral_unit_width",
-         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
-         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-n_of_records <- subset(missing.values, isna=="FALSE")
-Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
-           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")
-
-Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Compatibility system", "Breeding system", " ", " ", " ", " ", " ")
-
-T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-           "Presence \n Absence", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " ", ""),align = c("l"))
-
-Type <- linebreak(c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive \n biology"),align = c("c"))
-
-Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology","","","","", ""),align = c("c"))
-
-dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
-
-Number_of_records_quantitative <- c(n_of_records$num.isna[n_of_records$key=="Plant_height_mean_m"], n_of_records$num.isna[n_of_records$key=="Corolla_diameter_mean"],
-  n_of_records$num.isna[n_of_records$key=="Corolla_length_mean"], n_of_records$num.isna[n_of_records$key=="Floral_unit_width"],
-  n_of_records$num.isna[n_of_records$key=="Style_length"], n_of_records$num.isna[n_of_records$key=="Ovule_number"],
-  n_of_records$num.isna[n_of_records$key=="Flowers_per_plant"], n_of_records$num.isna[n_of_records$key=="Nectar_ul"],
-  n_of_records$num.isna[n_of_records$key=="Nectar_mg"], n_of_records$num.isna[n_of_records$key=="Nectar_concentration"], n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
-  n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level_fruit_set"])
-
-Number_of_records_categorical <- c(n_of_records$num.isna[n_of_records$key=="lifespan"], n_of_records$num.isna[n_of_records$key=="life_form"],
-                                   n_of_records$num.isna[n_of_records$key=="Flower_morphology"], n_of_records$num.isna[n_of_records$key=="Flower_symmetry"],
-                                   n_of_records$num.isna[n_of_records$key=="Nectar_presence_absence"], n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level"],
-                                   n_of_records$num.isna[n_of_records$key=="Compatibility_system"], n_of_records$num.isna[n_of_records$key=="Breeding_system"],
-                                   rep("",4))
-
-dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
-
-colnames(dat) <- c("Type","Traits", "Type", "Traits", "Categories")
-
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table 1 | Quantitative and categorical traits used in this study.}") %>%
-kable_styling(full_width = F,font_size = 10) %>%
-add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 3),bold=T)  %>%
-    column_spec(c(1,3), bold = T) %>% row_spec(0, bold=T)
-
-```
-
-\doublespacing
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
-The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
-The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation.
-The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}
-
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-library(viridis) #COLOUR GGPLOT
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(magick)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#Images were made by Paula Martin
-#Check her work on https://paulamartinart.com/
-
-tree <- image_read("Images/PPCA_Plot/Tree.png")
-tree_1 <- as.raster(tree)
-
-style_l <- image_read("Images/PPCA_Plot/Style_Long.png")
-style_l_1 <- as.raster(style_l)
-
-style_s <- image_read("Images/PPCA_Plot/Style_Short.png")
-style_s_1 <- as.raster(style_s)
-
-ovule_h <- image_read("Images/PPCA_Plot/Ovule_High.png")
-ovule_h_1 <- as.raster(ovule_h)
-
-ovule_l <- image_read("Images/PPCA_Plot/Ovule_Low.png")
-ovule_l_1 <- as.raster(ovule_l)
-
-selfing_n <- image_read("Images/PPCA_Plot/Selfing_None.png")
-selfing_n_1 <- as.raster(selfing_n)
-
-selfing_h <- image_read("Images/PPCA_Plot/selfing.png")
-selfing_h_1 <- as.raster(selfing_h)
-
-single_flower <- image_read("Images/PPCA_Plot/Single_Flower.png")
-single_flower_1 <- as.raster(single_flower)
-
-many_flowers <- image_read("Images/PPCA_Plot/Inflorescencia.png")
-many_flowers_1 <- as.raster(many_flowers)
-#many_flowers_1 <- image_rotate(many_flowers, 45)
-
-large_flower <- image_read("Images/PPCA_Plot/flower_big.png")
-large_flower_1 <- as.raster(large_flower)
-
-flower_small <- image_read("Images/PPCA_Plot/flower_short.png")
-flower_small_1 <- as.raster(flower_small)
-
-herb <- image_read("Images/PPCA_Plot/herb.png")
-herb_1 <- as.raster(herb)
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("Flower number - flower size trade-off ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Pollinator dependence trade-off ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
-    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
-    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
-    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
-    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2, ymax = -1.50) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
-
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
-                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-plot_grid(all_spp(PC))
-
-```
-
-\blandscape
-
-\vspace*{-28mm}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="90%",fig.align='center',fig.cap= "\\textbf{Figure 2} Location of the different qualitative traits on the trait space.
-The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
-The solid arrows indicate the direction of variation of the different quantitative traits showed in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S)."}
-
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(size = rel(1.1)),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.4, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank(),
-            plot.title = element_text(size = rel(2), face="bold")
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-#CALL the output PC for simplicity
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-Compatibility <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Compatibility <- dat_cleaning_5$Compatibility_system
-  dat$Compatibility <- as.character(dat$Compatibility)
-  dat$Compatibility[dat$Compatibility=="dioecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="monoecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-  dat$Compatibility[dat$Compatibility=="self_compatible"] <- "Self compatible"
-  dat$Compatibility[dat$Compatibility=="self_incompatible"] <- "Self incompatible"
-  dat$Compatibility <- factor(dat$Compatibility, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Compatibility),size=1.75)+scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)")
-
-  plot
-
-}
-
-#Compatibility(PC)
-
-#############################################################################################################################################################
-#Life form
-#############################################################################################################################################################
-#Load plots
-Life_form <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Life form` <- dat_cleaning_5$life_form
-  dat$`Life form` <- as.character(dat$`Life form`)
-  dat$`Life form`[dat$`Life form`=="herb"] <- "Herb"
-  dat$`Life form`[dat$`Life form`=="shrub"] <- "Shrub"
-  dat$`Life form`[dat$`Life form`=="tree"] <- "Tree"
-  dat$`Life form`[dat$`Life form`=="vine"] <- "Shrub"
-
-  dat$`Life form` <- factor( dat$`Life form`, levels = c("Herb", "Shrub", "Tree"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Life form`),size=1.75)+scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.090, 0.115)) + ggtitle("(b)")
-
-  plot
-
-}
-
-#Life_form(PC)
-
-#############################################################################################################################################################
-#Life span
-#############################################################################################################################################################
-#Load plots
-Life_span <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-    dat$Lifespan <- dat_cleaning_5$lifespan
-    dat$Lifespan <- as.character(dat$Lifespan)
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Lifespan),size=1.75)+scale_color_manual(values=c("sienna4","forestgreen"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.12, 0.1)) + ggtitle("(c)")
-
-  plot
-
-}
-
-#Life_span(PC)
-
-#############################################################################################################################################################
-#Flower symmetry
-#############################################################################################################################################################
-#Load plots
-Flower_sym <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower symmetry` <- dat_cleaning_5$Flower_symmetry
-  dat$`Flower symmetry` <- as.character(dat$`Flower symmetry`)
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower symmetry`),size=1.75)+scale_color_manual(values=c("sienna2","purple"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)")
-
-  plot
-
-}
-
-#Flower_sym(PC)
-
-#############################################################################################################################################################
-#Flower shape
-#############################################################################################################################################################
-#Load plots
-Flower_sha <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower shape` <- dat_cleaning_5$Flower_morphology
-  dat$`Flower shape` <- as.character(dat$`Flower shape`)
-  dat$`Flower shape`[dat$`Flower shape`=="Funnelform"] <- "Campanulate"
-  dat$`Flower shape`[dat$`Flower shape`=="Spike"] <- "Brush"
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower shape`),size=1.75)+scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)")
-
-  plot
-
-}
-
-#Flower_sha(PC)
-
-#############################################################################################################################################################
-#Breeding system
-#############################################################################################################################################################
-#Load plots
-Breeding_syst <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Breeding system` <- dat_cleaning_5$Breeding_system
-  dat$`Breeding system` <- as.character(dat$`Breeding system`)
-  dat$`Breeding system` <- factor(dat$`Breeding system`, levels=c("Hermaphrodite","Monoecious" ,"Dioecious"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Breeding system`),size=1.75)+scale_color_manual(values=c("forestgreen","orange", "black"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("(d)")
-
-  plot
-
-}
-
-#Breeding_syst(PC)
-
-#############################################################################################################################################################
-#Nectar
-#############################################################################################################################################################
-#Load plots
-#Nectar <- function(PC, x="PC1", y="PC2") {
-#  # PC being a prcomp object
-#  data <- data.frame(PC$S)
-#  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-#  dat <- data.frame(x = data[,x], y = data[,y])
-#  
-#  #######
-#  #DENSITY FUNCTION
-#  #######
-#  get_density <- function(x, y, ...) {
-#    dens <- MASS::kde2d(x, y, ...)
-#    ix <- findInterval(x, dens$x)
-#    iy <- findInterval(y, dens$y)
-#    ii <- cbind(ix, iy)
-#    return(dens$z[ii])
-#  }
-#  
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-#  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-#  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-#  plot <- plot + geom_point(data=dat, aes(-x, -y, #colour=Nectar),size=1.75)+scale_color_manual(values=c("black","grey"))
-#  
-#  ########
-#  #ADD ARROWS 
-#  ########
-#  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-#  mult <- min(
-#    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-#    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-#  )
-#  datapc <- transform(datapc,
-#                      v1 = .75 * mult * (get(x)),
-#                      v2 = .75 * mult * (get(y))
-#  )
-#  # add arrows
-#  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, #yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-#  
-#  #Add axis with perctentage
-#  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-#
-#  
-#  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, #arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-#  
-#  #ADD LABELS
-#  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-#  
-#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-#  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = #-(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-#                          label = PCAloadings$Variables, color="black",size=3)
-#  
-#  #CHANGE THEME
-#  #CHANGE THEME
-#  
-#  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)") 
-#  
-#  plot
-#  
-#}
-#
-# #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")
-
-  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),ncol=3,nrow=2,  align = "hv")
-
-```
-
-\elandscape
-
-\vspace{5mm}
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
-PC1 represents the flower number - flower size trade-off, PC2 represents the pollinator dependence trade-off and PC3, the style length trade-off.
-For visualization purposes, due to large differences between number of visits of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
-
-#LOAD LIBRARIES 
-#library(phytools)
-#library(ape) #for phylogenetic distance
-#library(dplyr) #data processing
-#library(rtrees) #for phylogenetic distancelibrary(MASS)
-#library(reshape2)
-library(viridis) #COLOUR GGPLOT
-#library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-#library(tidyverse)
-library(patchwork) #panel of plots
-#library(brms)
-#library(cmdstanr)
-
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2)),
-           axis.text=element_text(size = rel(1.8), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(2, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
-           plot.subtitle = element_text(face="bold",size=rel(2))
-     ))
-}
-
-setwd("~/R_Projects/Reproductive Traits")
-
-p1 <- readRDS("Main_Figures/figure_3_1.rds")
-p2 <- readRDS("Main_Figures/figure_3_2.rds")
-p3 <- readRDS("Main_Figures/figure_3_3.rds")
-pp1 <- readRDS("Main_Figures/figure_3_4.rds")
-pp2 <- readRDS("Main_Figures/figure_3_5.rds")
-pp3 <- readRDS("Main_Figures/figure_3_6.rds")
-
-library(patchwork)
-
-combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
-combined + plot_layout(guides = "collect",ncol = 3)
-
-```
-
-\elandscape
+# Regression trees
 
@@
 \elandscape
+
+# Methods
+
+Second, to better understand complex trait relationships, we used regression trees.
+Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on explaining species roles within the network of interaction.
+We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Table S2).
+We conducted this analysis using the *rpart* function from the *rtrees* package [@therneau2015] with method *'anova'* with a minimum of 50 observations per terminal node and we used the *rpart.plot* package [@milborrow2015] to plot the regression trees.
+We considered the species level indices as response variables (number of visits, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors.
+We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits.
+Because pollen and nectar traits are essential to understand plant-pollinator interactions [@heinrich1972; @johnson2008; @vaudo2015], we focused in the main text on the regression trees that included floral rewards.
+Indeed, we found that nectar and pollen traits were among the best traits for explaining the different species-level metrics (Fig.
+S6).
+
+# Results
+
+When we further investigated the combination of traits that drive plant network roles, we found that the regression tree for number of visits was best explained by plant height, nectar concentration and style length (Fig.
+4a; root node error = 1%).
+Specifically, species taller than 3.9m had the highest number of visits, while species that were shorter than 3.9m and had a nectar concentration lower than 16% had the lowest number of visits.
+Normalized degree was best explained by nectar concentration, pollen grains per flower, plant height, flower width and autonomous selfing (Fig.
+4b; root node error = 2%).
+Species with a nectar concentration over 49% had the highest levels of normalized degree, whereas species with nectar concentration lower than 49%, more than 21,000 pollen grains per flower and height less than 0.78m had the lowest normalized degree.
+Finally, specialization was best explained by plant height, ovule number, pollen grains per flower and autonomous selfing (Fig.
+4c; root node error = 7%).
+Overall, plant species with the highest specialization were shorter than 1.3m, had more than 14,000 pollen grains per flower and autonomously self-pollinated less than 11% of their fruits.
+In contrast, species taller or equal than 5.1m and with lower than 14 ovules per flower had the lowest specialization values.
+
+# Supplemetary material
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig.
+S6.} Regression tree analyses.
+Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
+"}
+
+########################################################################################################################################################
+#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
+########################################################################################################################################################
+#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
+
+library(rpart.plot)
+library(rpart)
+
+setwd("~/R_Projects/Reproductive Traits")
+
+v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
+nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
+d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")
+
+#run  regression trees of the 3 metrics
+set.seed(1)
+tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0054559,minbucket=50)
+
+set.seed(1)
+tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0084459,minbucket=50)
+
+set.seed(1)
+tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0072192 , minbucket=50) #10
+
+#NECTAR AND POLEN DATA
+v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
+nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
+d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
+
+#Set correct colnames for plotting
+colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
+
+colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
+
+colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
+                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
+
+set.seed(2)
+tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
+
+set.seed(2)
+tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
+
+set.seed(2)
+tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)
+
+par(mfrow=c(3,2))
+
+rpart.plot(tree_1, box.palette="GnOr", main="A Interaction frequency for all species", cex.main=1.85,tweak = 1.10) 
+rpart.plot(tree1, box.palette="GnOr", main="B Interaction frequency for subset with floral rewards", cex.main=1.85,tweak = 1.10)
+
+rpart.plot(tree_2, box.palette="GnOr", main="C Normalized degree for all species", cex.main=1.85,tweak = 1.10)
+rpart.plot(tree2, box.palette="GnOr", main="D Normalized degree for subset with floral rewards", cex.main=1.85,tweak = 1.10)
+
+rpart.plot(tree_3, box.palette="GnOr", main="E Specialization for all species", cex.main=1.85,tweak = 1.10) 
+rpart.plot(tree3, box.palette="GnOr", main="F Specialization for subset with floral rewards", cex.main=1.85,tweak = 1.10)
+
+```

### 2022-06-22 Manuscript/Lanuza_et_al_2021.Rmd
Edits

@@
 
-# Acknowledgements
-
-This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-We thank all researchers that made their data openly available and sent it upon request.
+**Data accessibility.** All data and code used to conduct this study will is deposited at Zenodo
+
+**Authors’contributions.**
+
+**Conflict of interest declaration.** We declare we have no competing interests.
+
+**Funding.** This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
+
+**Acknowledgements.** We thank all researchers that made their data openly available and sent it upon request.
 We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.

### 2022-06-22 Manuscript/Lanuza_et_al_2021.Rmd
edits on manuscript

@@
 ```
-\textbf{Statement of authorship:} JBL, RR and IB designed the study.
-JBL collated the data and conducted analysis with guidance of JS, LKK and IB.
-JBL wrote the manuscript with contributions of all authors.
-
-\textbf{Data accessibility statement:} All data and code used to conduct this study will be deposited in the public repository Dryad upon acceptance.
-
-\textbf{Short title:} Covariation among plant reproductive traits.
-
-\textbf{Keywords:} life-history strategies \| plant reproductive traits \| plant-pollinator interactions.
-
-\textbf{Type of article:} Letter.
-
-\textbf{Number of words:} Abstract (146 words), main text excluding references, acknowledgements and captions (4983 words).
-
-\textbf{Number of references:} 75
-
-\textbf{Number of figures and tables:} 4 figures and 1 table.
 
 \textbf{Corresponding author:} Jose B. Lanuza \| +34 616375981\| [barragansljose\@gmail.com](mailto:barragansljose@gmail.com){.email}
-
-\newpage
 
@@
 Our study shows the major reproductive trait correlations and highlights their relevance to understand plant-pollinator interactions in a global context.
-
-\newpage
 
@@
 An extended description of each trait and how it was obtained can be found in Appendix S1.
-
-## (d) Phylogenetic Distance
-
-We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package *rtrees* (<https://github.com/daijiang/rtrees>), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
-
-## (e) Data Imputation
-
-To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of *missForest* [@penone2014].
-To extract the eigenvectors, we used the function *PVRdecomp* from the package *PVR* [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-We conducted two different imputations, one for the full set of species (1,506 species, 5.79% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
-S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without missing values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
-
-## (f) Plant strategies
-
-We explored the association between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as indicated for principal component analysis [@legendre2012].
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
-We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
-For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
-
-## (g) Phylogenetic signal
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package *phytools* [@revell2012] and we used Pagel's $\lambda$ as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-## (h) Network analyses
-
-First, we investigated how the different groups of floral visitors interacted along the main axes of reproductive trait variation (see below 'visitation patterns' section) with the help of qualitative and quantitative information of plant-pollinator interactions.
-For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency [@ballantyne2015], the number of visits can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
-Second, we investigated how the main axes of trait variation and individual traits influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below 'plant species network roles' section).
-
-Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
-All analyses were conducted in R version *4.0.3*.
-
-### (i) Visitation patterns
-
-We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that *Apis mellifera* was the floral visitor with the largest proportion of records counted (7.55% of the total).
-This finding is consistent with previous research showing that *A.
-mellifera* was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
-Hence, to control for the effect of *A.
-mellifera* on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding *A.
-mellifera*.
-We found that *A.
-mellifera*, was partly driving some of the observed trends on PC1 (Fig.
-S5).
-However, we did not detect major differences on PC2 and PC3.
-
-We implemented Bayesian generalized linear mixed models using the R package *brms* [@burkner2017].
-We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
-We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results [@burkner2017].
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the *bayesplot* package [@gabry2019].
-
-### (ii) Plant species network roles
-
-We investigated whether different quantitative traits determined different plant species' functional roles in the pollination network using Bayesian modelling.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the *specieslevel* function from the R package *bipartite* [@dormann2008].
-
-We modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
-For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the 'visitation patterns' section.
-
-# 3. Results
-
-## (a) Plant strategies
-
-The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of the reproductive trait variation, respectively (Fig.
-1 and Fig.
-S7).
-The first principal component (PC1 or the flower number - flower size axis) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
-One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-For instance, on this end of the spectrum we find the species *Cornus florida* which has approximately a total of 10.000 flowers, an average height of 7.5m, flowers of 3mm wide, a style length of 3.5mm and a total of 2 ovules per flower.
-The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-For instance, on this side of the axis we find the species *Petunia axillaris* that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
-The second principal component (PC2 or the pollinator dependence axis) represented 25.05% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
-In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles.
-On this extreme of the spectrum we find the species *Zuccagnia punctata* that is a self-incompatible shrub that depends completely on floral visitors for seed production, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm.
-In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
-For instance, on this end of the spectrum we find the species *Veronica peregrina* which is a self-compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
-Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = |-0.51|) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
-The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; Table S3).
-In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (Fig.
-S4).
-This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (Table S4).
-
-We found (with an Anova) that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
-2 and Table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
-S8).
-Regarding self-compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility; Fig.
-S8a and Fig.
-S8b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
-S8c and Fig.
-S8d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
-S8e and Fig.
-S8f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
-S8g and Fig.
-S8h).
-Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (Fig.
-S8i and Fig.
-S8j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Fig.
-S8k and Fig.
-S8l).
-
-## (b) Phylogenetic signal
-
-We found a strong phylogenetic signal (*P* \< 0.01) for most quantitative traits (Table S5).
-The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
-The traits that showed a moderate phylogenetic signal were inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits ($\lambda$ = 0.14).
-
-## (c) Visitation patterns
-
-The main axes of trait variation (PC1, PC2 and PC3) explained partly presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (Fig.
-3).
-We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (Fig.
-3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
-Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number but small (Fig.
-3d).
-On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (Fig.
-3b and Fig.
-3e).
-Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (Fig.
-3c).
-However, regarding number of visits on the style length - pollinator dependence axis, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
-3f).
-
-The additional model for both presence-absence of interaction (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (Fig.
-3a and Fig.
-3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (Fig.
-S9).
-
-## (d) Plant species network roles
-
-The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
-S10; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
-On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
-S10a).
-However, specialization showed the opposite trend on this axis (Fig.
-S10g).
-On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (Fig.
-S10c).
-Again, specialization showed the opposite trend to number of visits (Fig.
-S10i).
-
-# 4. Discussion
-
-This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
-Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50% and 70% of reproductive trait variation, respectively.
-These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
-Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits [@diaz2016; @carmona2021], our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits [@salguero2016].
-Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
-However, they were insufficient to capture their visitation rates which highlight the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
-
-Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context.
-In addition, our work links the reproductive trait variation with the previously described fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-Although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
-We found support to this trait association and show that other life history traits also covariate along this axis.
-For example, our study complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
-Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral display.
-Thus, our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
-
-Overall, our models showed that the main plant reproductive trait correlations have low predictive power for broad-level interaction patterns between plants and floral visitors.
-However, we found changes in the interaction patterns among and within floral visitor guilds that suggest that plant reproductive strategies partly mediate these associations at large ecological scales.
-For example, we found that all floral visitor guilds interacted more frequently with plant species with larger floral displays in agreement with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
-Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes.
-For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour [rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive correlations do not.
-
-To conclude, we provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of plant reproductive traits from species that belong to plant-pollinator networks.
-Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider other factors beyond plant reproductive strategies to better capture broad scale patterns of interactions with floral visitors.
-Our work provides empirical evidence that complements previous studies that have explored trait correlations with other plant organs and highlights the need to include these reproductive correlations in the global spectrum of plant form and function [@diaz2016] as reproductive strategies involve clear cost and benefits that can affect the trait space of the whole plant.
-Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and plant-pollinator associations.
-
-# References
-
-::: {#refs}
-:::
-
-**Data accessibility.** All data and code used to conduct this study will is deposited at Zenodo
-
-**Authors’contributions.**
-
-**Conflict of interest declaration.** We declare we have no competing interests.
-
-**Funding.** This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-
-**Acknowledgements.** We thank all researchers that made their data openly available and sent it upon request.
-We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
-We also thank Jason Tylianakis for his comments on the manuscript before submission.
-Finally, JBL thanks the University of New England for the funding provided to carry out this work.
 
@@
 
-\clearpage
-
 \doublespacing
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
+## (d) Phylogenetic Distance
+
+We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package *rtrees* (<https://github.com/daijiang/rtrees>), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
+
+## (e) Data Imputation
+
+To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of datasets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of *missForest* [@penone2014].
+To extract the eigenvectors, we used the function *PVRdecomp* from the package *PVR* [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
+We conducted two different imputations, one for the full set of species (1,506 species, 5.79% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
+S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01% of missing values).
+To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without missing values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
+
+## (f) Plant strategies
+
+We explored the association between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+Prior to the analyses, we excluded outliers and standardized the data.
+Due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as indicated for principal component analysis [@legendre2012].
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
+We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
+Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
+For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
+
+## (g) Phylogenetic signal
+
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package *phytools* [@revell2012] and we used Pagel's $\lambda$ as a measurement of the phylogenetic signal.
+However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
+
+## (h) Network analyses
+
+First, we investigated how the different groups of floral visitors interacted along the main axes of reproductive trait variation (see below 'visitation patterns' section) with the help of qualitative and quantitative information of plant-pollinator interactions.
+For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
+Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency [@ballantyne2015], the number of visits can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
+Second, we investigated how the main axes of trait variation and individual traits influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below 'plant species network roles' section).
+
+Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
+Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
+All analyses were conducted in R version *4.0.3*.
+
+### (i) Visitation patterns
+
+We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species.
+For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
+Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+In addition, we found that *Apis mellifera* was the floral visitor with the largest proportion of records counted (7.55% of the total).
+This finding is consistent with previous research showing that *A.
+mellifera* was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
+Hence, to control for the effect of *A.
+mellifera* on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding *A.
+mellifera*.
+We found that *A.
+mellifera*, was partly driving some of the observed trends on PC1 (Fig.
+S5).
+However, we did not detect major differences on PC2 and PC3.
+
+We implemented Bayesian generalized linear mixed models using the R package *brms* [@burkner2017].
+We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
+We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
+Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
+We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
+The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results [@burkner2017].
+We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the *bayesplot* package [@gabry2019].
+
+### (ii) Plant species network roles
+
+We investigated whether different quantitative traits determined different plant species' functional roles in the pollination network using Bayesian modelling.
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the *specieslevel* function from the R package *bipartite* [@dormann2008].
+
+We modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
+For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
+Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the 'visitation patterns' section.
+
+# 3. Results
+
+## (a) Plant strategies
+
+The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of the reproductive trait variation, respectively (Fig.
+1 and Fig.
+S7).
+The first principal component (PC1 or the flower number - flower size axis) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
+One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
+For instance, on this end of the spectrum we find the species *Cornus florida* which has approximately a total of 10.000 flowers, an average height of 7.5m, flowers of 3mm wide, a style length of 3.5mm and a total of 2 ovules per flower.
+The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
+For instance, on this side of the axis we find the species *Petunia axillaris* that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
+The second principal component (PC2 or the pollinator dependence axis) represented 25.05% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
+In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles.
+On this extreme of the spectrum we find the species *Zuccagnia punctata* that is a self-incompatible shrub that depends completely on floral visitors for seed production, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm.
+In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
+For instance, on this end of the spectrum we find the species *Veronica peregrina* which is a self-compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
+Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = |-0.51|) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
+The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; Table S3).
+In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (Fig.
+S4).
+This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (Table S4).
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="95%", fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
 The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
@@
 ```
+
+We found (with an Anova) that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
+2 and Table S2).
+Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed lack of statistical association.
+In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
+S8).
+Regarding self-compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility; Fig.
+S8a and Fig.
+S8b).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
+S8c and Fig.
+S8d).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
+S8e and Fig.
+S8f).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
+S8g and Fig.
+S8h).
+Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (Fig.
+S8i and Fig.
+S8j).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Fig.
+S8k and Fig.
+S8l).
 
@@
 
+## (b) Phylogenetic signal
+
+We found a strong phylogenetic signal (*P* \< 0.01) for most quantitative traits (Table S5).
+The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
+The traits that showed a moderate phylogenetic signal were inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
+Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits ($\lambda$ = 0.14).
+
+## (c) Visitation patterns
+
+The main axes of trait variation (PC1, PC2 and PC3) explained partly presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
+However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (Fig.
+3).
+We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (Fig.
+3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
+Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number but small (Fig.
+3d).
+On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (Fig.
+3b and Fig.
+3e).
+Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (Fig.
+3c).
+However, regarding number of visits on the style length - pollinator dependence axis, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
+3f).
+
+The additional model for both presence-absence of interaction (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
+The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (Fig.
+3a and Fig.
+3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (Fig.
+S9).
+
 \vspace{5mm}
@@
 \elandscape
+
+## (d) Plant species network roles
+
+The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
+S10; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
+Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
+On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
+S10a).
+However, specialization showed the opposite trend on this axis (Fig.
+S10g).
+On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (Fig.
+S10c).
+Again, specialization showed the opposite trend to number of visits (Fig.
+S10i).
+
+# 4. Discussion
+
+This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
+Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50% and 70% of reproductive trait variation, respectively.
+These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
+Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits [@diaz2016; @carmona2021], our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits [@salguero2016].
+Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
+However, they were insufficient to capture their visitation rates which highlight the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
+
+Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context.
+In addition, our work links the reproductive trait variation with the previously described fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+Although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
+We found support to this trait association and show that other life history traits also covariate along this axis.
+For example, our study complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
+Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
+Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral display.
+Thus, our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
+
+Overall, our models showed that the main plant reproductive trait correlations have low predictive power for broad-level interaction patterns between plants and floral visitors.
+However, we found changes in the interaction patterns among and within floral visitor guilds that suggest that plant reproductive strategies partly mediate these associations at large ecological scales.
+For example, we found that all floral visitor guilds interacted more frequently with plant species with larger floral displays in agreement with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
+Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes.
+For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour [rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive correlations do not.
+
+To conclude, we provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of plant reproductive traits from species that belong to plant-pollinator networks.
+Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider other factors beyond plant reproductive strategies to better capture broad scale patterns of interactions with floral visitors.
+Our work provides empirical evidence that complements previous studies that have explored trait correlations with other plant organs and highlights the need to include these reproductive correlations in the global spectrum of plant form and function [@diaz2016] as reproductive strategies involve clear cost and benefits that can affect the trait space of the whole plant.
+Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and plant-pollinator associations.
+
+# References
+
+::: {#refs}
+:::
+
+**Data accessibility.** All data and code used to conduct this study will is deposited at Zenodo
+
+**Authors’contributions.** JBL, RR and IB designed the study. JBL collated the data and conducted analysis with guidance of JS, LKK and IB. JBL wrote the manuscript with contributions of all authors.
+
+**Conflict of interest declaration.** We declare we have no competing interests.
+
+**Funding.** This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
+
+**Acknowledgements.** We thank all researchers that made their data openly available and sent it upon request.
+We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
+We also thank Jason Tylianakis for his comments on the manuscript before submission.
+Finally, JBL thanks the University of New England for the funding provided to carry out this work.

### 2022-06-22 Manuscript/Lanuza_et_al_2021.tex
edits on manuscript

@@
 
-\textbf{Statement of authorship:} JBL, RR and IB designed the study.
-JBL collated the data and conducted analysis with guidance of JS, LKK and IB.
-JBL wrote the manuscript with contributions of all authors.
-
-\textbf{Data accessibility statement:} All data and code used to conduct this study will be deposited in the public repository Dryad upon acceptance.
-
-\textbf{Short title:} Covariation among plant reproductive traits.
-
-\textbf{Keywords:} life-history strategies \textbar{} plant reproductive traits \textbar{} plant-pollinator interactions.
-
-\textbf{Type of article:} Letter.
-
-\textbf{Number of words:} Abstract (146 words), main text excluding references, acknowledgements and captions (4983 words).
-
-\textbf{Number of references:} 75
-
-\textbf{Number of figures and tables:} 4 figures and 1 table.
-
 \textbf{Corresponding author:} Jose B. Lanuza \textbar{} +34 616375981\textbar{} \href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
-
-\newpage
 
@@
 An extended description of each trait and how it was obtained can be found in Appendix S1.
-
-\hypertarget{d-phylogenetic-distance}{%
-\subsection{(d) Phylogenetic Distance}\label{d-phylogenetic-distance}}
-
-We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{48},\protect\hyperlink{ref-jin2019}{49}{]}.
-
-\hypertarget{e-data-imputation}{%
-\subsection{(e) Data Imputation}\label{e-data-imputation}}
-
-To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{50}{]} which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{51}{]}.
-To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} {[}\protect\hyperlink{ref-santos2018}{52}{]} based on a previous conceptual framework that considers phylogenetic eigenvectors {[}\protect\hyperlink{ref-diniz-filho2012}{53}{]}.
-We conducted two different imputations, one for the full set of species (1,506 species, 5.79\% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
-S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01\% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without missing values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
-
-\hypertarget{f-plant-strategies}{%
-\subsection{(f) Plant strategies}\label{f-plant-strategies}}
-
-We explored the association between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{54},\protect\hyperlink{ref-legendre2012}{55}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as indicated for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{55}{]}.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{56}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{57}{]}.
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
-For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
-
-\hypertarget{g-phylogenetic-signal}{%
-\subsection{(g) Phylogenetic signal}\label{g-phylogenetic-signal}}
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{56}{]} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-\hypertarget{h-network-analyses}{%
-\subsection{(h) Network analyses}\label{h-network-analyses}}
-
-First, we investigated how the different groups of floral visitors interacted along the main axes of reproductive trait variation (see below `visitation patterns' section) with the help of qualitative and quantitative information of plant-pollinator interactions.
-For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency {[}\protect\hyperlink{ref-ballantyne2015}{58}{]}, the number of visits can provide valuable information of the contribution of floral visitors to pollination {[}\protect\hyperlink{ref-vazquez2005}{59},\protect\hyperlink{ref-vazquez2012}{60}{]}.
-Second, we investigated how the main axes of trait variation and individual traits influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below `plant species network roles' section).
-
-Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
-All analyses were conducted in R version \emph{4.0.3}.
-
-\hypertarget{i-visitation-patterns}{%
-\subsubsection{(i) Visitation patterns}\label{i-visitation-patterns}}
-
-We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total).
-This finding is consistent with previous research showing that \emph{A.
-mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems {[}\protect\hyperlink{ref-hung2018}{61}{]}.
-Hence, to control for the effect of \emph{A.
-mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding \emph{A.
-mellifera}.
-We found that \emph{A.
-mellifera}, was partly driving some of the observed trends on PC1 (Fig.
-S5).
-However, we did not detect major differences on PC2 and PC3.
-
-We implemented Bayesian generalized linear mixed models using the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{62}{]}.
-We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
-We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results {[}\protect\hyperlink{ref-burkner2017}{62}{]}.
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}\protect\hyperlink{ref-gabry2019}{63}{]}.
-
-\hypertarget{ii-plant-species-network-roles}{%
-\subsubsection{(ii) Plant species network roles}\label{ii-plant-species-network-roles}}
-
-We investigated whether different quantitative traits determined different plant species' functional roles in the pollination network using Bayesian modelling.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{64}{]} with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{65}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{64}{]}.
-
-We modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
-For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns' section.
-
-\hypertarget{results}{%
-\section{3. Results}\label{results}}
-
-\hypertarget{a-plant-strategies}{%
-\subsection{(a) Plant strategies}\label{a-plant-strategies}}
-
-The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of the reproductive trait variation, respectively (Fig.
-1 and Fig.
-S7).
-The first principal component (PC1 or the flower number - flower size axis) represented 26.72\% of the trait variation and indicated a negative correlation between flower number and flower size.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
-One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-For instance, on this end of the spectrum we find the species \emph{Cornus florida} which has approximately a total of 10.000 flowers, an average height of 7.5m, flowers of 3mm wide, a style length of 3.5mm and a total of 2 ovules per flower.
-The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-For instance, on this side of the axis we find the species \emph{Petunia axillaris} that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
-The second principal component (PC2 or the pollinator dependence axis) represented 25.05\% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
-In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles.
-On this extreme of the spectrum we find the species \emph{Zuccagnia punctata} that is a self-incompatible shrub that depends completely on floral visitors for seed production, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm.
-In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
-For instance, on this end of the spectrum we find the species \emph{Veronica peregrina} which is a self-compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
-Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17\%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \textbar-0.51\textbar) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
-The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; Table S3).
-In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (Fig.
-S4).
-This pPCA explained similar variance with the first two principal components (45.52\%) and similar associations of traits despite some variability in the loadings (Table S4).
-
-We found (with an Anova) that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
-2 and Table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
-S8).
-Regarding self-compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility; Fig.
-S8a and Fig.
-S8b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
-S8c and Fig.
-S8d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
-S8e and Fig.
-S8f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
-S8g and Fig.
-S8h).
-Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (Fig.
-S8i and Fig.
-S8j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Fig.
-S8k and Fig.
-S8l).
-
-\hypertarget{b-phylogenetic-signal}{%
-\subsection{(b) Phylogenetic signal}\label{b-phylogenetic-signal}}
-
-We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) for most quantitative traits (Table S5).
-The traits that showed the highest phylogenetic signal were ovule number (\(\lambda\) = 1), pollen grains per flower (\(\lambda\) = 1) and plant height (\(\lambda\) = 0.96), followed by flower length (\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73), number of flowers per plant (\(\lambda\) = 0.69) and nectar concentration (\(\lambda\) = 0.65).
-The traits that showed a moderate phylogenetic signal were inflorescence width (\(\lambda\) = 0.57), style length (\(\lambda\) = 0.49) and autonomous selfing (\(\lambda\) = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits (\(\lambda\) = 0.14).
-
-\hypertarget{c-visitation-patterns}{%
-\subsection{(c) Visitation patterns}\label{c-visitation-patterns}}
-
-The main axes of trait variation (PC1, PC2 and PC3) explained partly presence-absence of interaction partners (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the overall number of visits (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
-However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (Fig.
-3).
-We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (Fig.
-3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
-Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number but small (Fig.
-3d).
-On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (Fig.
-3b and Fig.
-3e).
-Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (Fig.
-3c).
-However, regarding number of visits on the style length - pollinator dependence axis, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
-3f).
-
-The additional model for both presence-absence of interaction (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and number of visits (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (Fig.
-3a and Fig.
-3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (Fig.
-S9).
-
-\hypertarget{d-plant-species-network-roles}{%
-\subsection{(d) Plant species network roles}\label{d-plant-species-network-roles}}
-
-The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
-S10; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
-On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
-S10a).
-However, specialization showed the opposite trend on this axis (Fig.
-S10g).
-On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (Fig.
-S10c).
-Again, specialization showed the opposite trend to number of visits (Fig.
-S10i).
-
-\hypertarget{discussion}{%
-\section{4. Discussion}\label{discussion}}
-
-This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
-Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively.
-These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
-Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{13},\protect\hyperlink{ref-carmona2021}{37}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
-Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
-However, they were insufficient to capture their visitation rates which highlight the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
-
-Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context.
-In addition, our work links the reproductive trait variation with the previously described fast-slow continuum' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{66}{]} life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-Although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{39},\protect\hyperlink{ref-kettle2011}{40},\protect\hyperlink{ref-worley2000}{67}{]}, it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
-We found support to this trait association and show that other life history traits also covariate along this axis.
-For example, our study complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{68}{]} by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
-Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{41}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral display.
-Thus, our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
-
-Overall, our models showed that the main plant reproductive trait correlations have low predictive power for broad-level interaction patterns between plants and floral visitors.
-However, we found changes in the interaction patterns among and within floral visitor guilds that suggest that plant reproductive strategies partly mediate these associations at large ecological scales.
-For example, we found that all floral visitor guilds interacted more frequently with plant species with larger floral displays in agreement with previous findings {[}\protect\hyperlink{ref-lazaro2013}{28},\protect\hyperlink{ref-hegland2005}{69},\protect\hyperlink{ref-kaiser2014}{70}{]}.
-Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes.
-For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour {[}rader2020; {[}\protect\hyperlink{ref-foldesi2021}{71}{]}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{27},\protect\hyperlink{ref-vazquez2007}{72},\protect\hyperlink{ref-encinas2012}{73}{]} that reproductive correlations do not.
-
-To conclude, we provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of plant reproductive traits from species that belong to plant-pollinator networks.
-Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider other factors beyond plant reproductive strategies to better capture broad scale patterns of interactions with floral visitors.
-Our work provides empirical evidence that complements previous studies that have explored trait correlations with other plant organs and highlights the need to include these reproductive correlations in the global spectrum of plant form and function {[}\protect\hyperlink{ref-diaz2016}{13}{]} as reproductive strategies involve clear cost and benefits that can affect the trait space of the whole plant.
-Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and plant-pollinator associations.
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-barrett2002}{}}%
-\CSLLeftMargin{1. }
-\CSLRightInline{Barrett SCH. 2002 The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.} \textbf{3}, 274--284. (doi:\href{https://doi.org/10.1038/nrg776}{10.1038/nrg776})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schiestl2013}{}}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Schiestl FP, Johnson SD.
-2013 Pollinator-mediated evolution of floral signals.
-\emph{Trends Ecol.
-Evol.} \textbf{28}, 307--315.
-(doi:\href{https://doi.org/10.1016/j.tree.2013.01.019}{10.1016/j.tree.2013.01.019})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fenster2004}{}}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Fenster CB, Armbruster WS, Wilson P, Dudash MR, Thomson JD.
-2004 Pollination {Syndromes} and {Floral Specialization}.
-\emph{Annu.
-Rev.
-Ecol.
-Evol.
-Syst.} \textbf{35}, 375--403.
-(doi:\href{https://doi.org/10.1146/annurev.ecolsys.34.011802.132347}{10.1146/annurev.ecolsys.34.011802.132347})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dellinger2020}{}}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Dellinger AS.
-2020 Pollination syndromes in the 21st century: Where do we stand and where may we go?
-\emph{New Phytol.} \textbf{228}, 1193--1213.
-(doi:\href{https://doi.org/10.1111/nph.16793}{10.1111/nph.16793})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stearns1989}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Stearns SC. 1989 Trade-offs in life-history evolution. \emph{Functional ecology} \textbf{3}, 259--268.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-agrawal2020}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{Agrawal AA. 2020 A scale-dependent framework for trade-offs, syndromes, and specialization in organismal biology. \emph{Ecology} \textbf{101}, e02924.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-salguero2016}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{Salguero-Gómez R, Jones OR, Jongejans E, Blomberg SP, Hodgson DJ, Mbeau-Ache C, Zuidema PA, de Kroon H, Buckley YM.
-2016 Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
-\emph{Proc.
-Natl.
-Acad.
-Sci.
-U.S.A.} \textbf{113}, 230--235.
-(doi:\href{https://doi.org/10.1073/pnas.1506215112}{10.1073/pnas.1506215112})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-friedman2020}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Friedman J.
-2020 The evolution of annual and perennial plant life histories: Ecological correlates and genetic mechanisms.
-\emph{Annual Review of Ecology, Evolution, and Systematics} \textbf{51}, 461--481.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-paterno2020}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Paterno GB, Silveira CL, Kollmann J, Westoby M, Fonseca CR.
-2020 The maleness of larger angiosperm flowers.
-\emph{Proceedings of the National Academy of Sciences} \textbf{117}, 10921--10926.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-roddy2021}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{Roddy AB, Martínez-Perez C, Teixido AL, Cornelissen TG, Olson ME, Oliveira RS, Silveira FAO.
-2021 Towards the flower economics spectrum.
-\emph{New Phytol.} \textbf{229}, 665--672.
-(doi:\href{https://doi.org/10.1111/nph.16823}{10.1111/nph.16823})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{Wright IJ \emph{et al.} 2004 The worldwide leaf economics spectrum. \emph{Nature} \textbf{428}, 821--827. (doi:\href{https://doi.org/10.1038/nature02403}{10.1038/nature02403})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Chave J, Coomes D, Jansen S, Lewis SL, Swenson NG, Zanne AE. 2009 Towards a worldwide wood economics spectrum. \emph{Ecol. Lett.} \textbf{12}, 351--366.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Díaz S \emph{et al.} 2016 The global spectrum of plant form and function. \emph{Nature} \textbf{529}, 167--171. (doi:\href{https://doi.org/10.1038/nature16489}{10.1038/nature16489})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-onoda2017}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Onoda Y, Wright IJ, Evans JR, Hikosaka K, Kitajima K, Niinemets Ü, Poorter H, Tosens T, Westoby M.
-2017 Physiological and structural tradeoffs underlying the leaf economics spectrum.
-\emph{New Phytologist} \textbf{214}, 1447--1463.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Laughlin DC \emph{et al.} 2021 Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
-\emph{Nat.
-Ecol.
-Evol.}, 1--12.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-baude2016}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Baude M, Kunin WE, Boatman ND, Conyers S, Davies N, Gillespie MA, Morton RD, Smart SM, Memmott J.
-2016 Historical nectar assessment reveals the fall and rise of floral resources in britain.
-\emph{Nature} \textbf{530}, 85--88.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{Munoz F, Violle C, Cheptou P-O.
-2016 {CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
-\emph{Oikos} \textbf{125}, 1296--1303.
-(doi:\href{https://doi.org/10.1111/oik.02328}{10.1111/oik.02328})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-grossenbacher2017}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Grossenbacher DL \emph{et al.} 2017 Self-compatibility is over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Moeller DA \emph{et al.} 2017 Global biogeography of mating system variation in seed plants.
-\emph{Ecol.
-Lett.} \textbf{20}, 375--384.
-(doi:\href{https://doi.org/10.1111/ele.12738}{10.1111/ele.12738})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Sargent RD, Ackerly DD. 2008 Plant--pollinator interactions and the assembly of plant communities. \emph{Trends Ecol. Evol.} \textbf{23}, 123--130.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rech2016}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Rech AR, Dalsgaard B, Sandel B, Sonne J, Svenning J-C, Holmes N, Ollerton J.
-2016 The macroecology of animal versus wind pollination: Ecological factors are more important than historical climate stability.
-\emph{Plant Ecol.
-Divers.} \textbf{9}, 253--262.
-(doi:\href{https://doi.org/10.1080/17550874.2016.1207722}{10.1080/17550874.2016.1207722})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{Rüger N, Comita LS, Condit R, Purves D, Rosenbaum B, Visser MD, Wright SJ, Wirth C.
-2018 Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
-\emph{Ecol.
-Lett.} \textbf{21}, 1075--1084.
-(doi:\href{https://doi.org/10.1111/ele.12974}{10.1111/ele.12974})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Tur C, Castro-Urgal R, Traveset A.
-2013 Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}.
-\emph{PLoS One} \textbf{8}, e78294.
-(doi:\href{https://doi.org/10.1371/journal.pone.0078294}{10.1371/journal.pone.0078294})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{Devaux C, Lepers C, Porcher E.
-2014 Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems.
-\emph{J.
-Evol.
-Biol.} \textbf{27}, 1413--1430.
-(doi:\href{https://doi.org/10.1111/jeb.12380}{10.1111/jeb.12380})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Rosas-Guerrero V, Aguilar R, Martén-Rodríguez S, Ashworth L, Lopezaraiza-Mikel M, Bastida JM, Quesada M.
-2014 A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
-\emph{Ecol.
-Lett.} \textbf{17}, 388--400.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Stang M, Klinkhamer PGL, Waser NM, Stang I, van der Meijden E.
-2009 Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
-\emph{Ann.
-Bot.} \textbf{103}, 1459--1469.
-(doi:\href{https://doi.org/10.1093/aob/mcp027}{10.1093/aob/mcp027})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Bartomeus I, Gravel D, Tylianakis JM, Aizen MA, Dickie IA, Bernard-Verdier M.
-2016 A common framework for identifying linkage rules across different types of interactions.
-\emph{Funct.
-Ecol.} \textbf{30}, 1894--1903.
-(doi:\href{https://doi.org/10.1111/1365-2435.12666}{10.1111/1365-2435.12666})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{Lázaro A, Jakobsson A, Totland Ø.
-2013 How do pollinator visitation rate and seed set relate to species' floral traits and community context?
-\emph{Oecologia} \textbf{173}, 881--893.
-(doi:\href{https://doi.org/10.1007/s00442-013-2652-5}{10.1007/s00442-013-2652-5})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{Junker RR, Blüthgen N, Brehm T, Binkenstein J, Paulus J, Schaefer HM, Stang M.
-2013 Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
-\emph{Funct.
-Ecol.} \textbf{27}, 329--341.
-(doi:\href{https://doi.org/10.1111/1365-2435.12005}{10.1111/1365-2435.12005})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Coux C, Rader R, Bartomeus I, Tylianakis JM.
-2016 Linking species functional roles to their network roles.
-\emph{Ecol.
-Lett.} \textbf{19}, 762--770.
-(doi:\href{https://doi.org/10.1111/ele.12612}{10.1111/ele.12612})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Ibanez S.
-2012 Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks.
-\emph{Oecologia} \textbf{170}, 233--242.
-(doi:\href{https://doi.org/10.1007/s00442-012-2290-3}{10.1007/s00442-012-2290-3})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Eklöf A \emph{et al.} 2013 The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{Dehling DM, Jordano P, Schaefer HM, Böhning-Gaese K, Schleuning M.
-2016 Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
-\emph{Proc.
-Royal Soc.
-B} \textbf{283}, 20152444.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{Kattge J \emph{et al.} 2011 {TRY} \textendash{} a global database of plant traits.
-\emph{Glob.
-Chang.
-Biol.} \textbf{17}, 2905--2935.
-(doi:\href{https://doi.org/10.1111/j.1365-2486.2011.02451.x}{10.1111/j.1365-2486.2011.02451.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Salguero-Gómez R \emph{et al.} 2015 The compadre {Plant Matrix Database}: An open online repository for plant demography.
-\emph{J.
-Ecol.} \textbf{103}, 202--218.
-(doi:\href{https://doi.org/10.1111/1365-2745.12334}{10.1111/1365-2745.12334})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Bruelheide H \emph{et al.} 2018 Global trait--environment relationships of plant communities. \emph{Nat. Ecol. Evol.} \textbf{2}, 1906--1917.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Carmona CP \emph{et al.} 2021 Erosion of global functional diversity across the tree of life.
-\emph{Sci.
-Adv.} \textbf{7}, eabf2675.
-(doi:\href{https://doi.org/10.1126/sciadv.abf2675}{10.1126/sciadv.abf2675})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{E-Vojtkó A, Bello F de, Durka W, Kühn I, Götzenberger L.
-2020 The neglected importance of floral traits in trait-based plant community assembly.
-\emph{J.
-Veg.
-Sci.} \textbf{31}, 529--539.
-(doi:\href{https://doi.org/10.1111/jvs.12877}{10.1111/jvs.12877})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Sargent RD, Goodwillie C, Kalisz S, Ree RH.
-2007 Phylogenetic evidence for a flower size and number trade-off.
-\emph{Am.
-J.
-Bot.} \textbf{94}, 2059--2062.
-(doi:\href{https://doi.org/10.3732/ajb.94.12.2059}{10.3732/ajb.94.12.2059})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
-\CSLLeftMargin{40. }
-\CSLRightInline{Kettle CJ, Maycock CR, Ghazoul J, Hollingsworth PM, Khoo E, Sukri RSH, Burslem DFRP.
-2011 Ecological {Implications} of a {Flower Size}/{Number Trade}-{Off} in {Tropical Forest Trees}.
-\emph{PLoS One} \textbf{6}, e16111.
-(doi:\href{https://doi.org/10.1371/journal.pone.0016111}{10.1371/journal.pone.0016111})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Goodwillie C \emph{et al.} 2010 Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
-\emph{New Phytol.} \textbf{185}, 311--321.
-(doi:\href{https://doi.org/10.1111/j.1469-8137.2009.03043.x}{10.1111/j.1469-8137.2009.03043.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
-\CSLLeftMargin{42. }
-\CSLRightInline{Barrett SCH.
-2003 Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond.
-\emph{Philos.
-Trans.
-R.
-Soc.
-Lond.
-B Biol.
-Sci.} \textbf{358}, 991--1004.
-(doi:\href{https://doi.org/10.1098/rstb.2003.1301}{10.1098/rstb.2003.1301})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
-\CSLLeftMargin{43. }
-\CSLRightInline{Carvalheiro LG \emph{et al.} 2014 The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
-\emph{Ecol.
-Lett.} \textbf{17}, 1389--1399.
-(doi:\href{https://doi.org/10.1111/ele.12342}{10.1111/ele.12342})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Olesen JM, Bascompte J, Dupont YL, Jordano P.
-2007 The modularity of pollination networks.
-\emph{PNAS} \textbf{104}, 19891--19896.
-(doi:\href{https://doi.org/10.1073/pnas.0706375104}{10.1073/pnas.0706375104})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
-\CSLLeftMargin{45. }
-\CSLRightInline{Fortuna MA, Stouffer DB, Olesen JM, Jordano P, Mouillot D, Krasnov BR, Poulin R, Bascompte J.
-2010 Nestedness versus modularity in ecological networks: Two sides of the same coin?
-\emph{J.
-Anim.
-Ecol.} \textbf{79}, 811--817.
-(doi:\href{https://doi.org/10.1111/j.1365-2656.2010.01688.x}{10.1111/j.1365-2656.2010.01688.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
-\CSLLeftMargin{46. }
-\CSLRightInline{Poisot T \emph{et al.} 2016 Mangal \textendash{} making ecological network analysis simple.
-\emph{Ecography} \textbf{39}, 384--390.
-(doi:\href{https://doi.org/10.1111/ecog.00976}{10.1111/ecog.00976})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Chamberlain S \emph{et al.} 2020 Taxize: {Taxonomic} information from around the web.
-R package version 0.9.99.~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Smith SA, Brown JW.
-2018 Constructing a broadly inclusive seed plant phylogeny.
-\emph{Am.
-J.
-Bot.} \textbf{105}, 302--314.
-(doi:\href{https://doi.org/10.1002/ajb2.1019}{10.1002/ajb2.1019})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
-\CSLLeftMargin{49. }
-\CSLRightInline{Jin Y, Qian H.
-2019 V.{PhyloMaker}: An {R} package that can generate very large phylogenies for vascular plants.
-\emph{Ecography} \textbf{42}, 1353--1359.
-(doi:\href{https://doi.org/10.1111/ecog.04434}{10.1111/ecog.04434})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
-\CSLLeftMargin{50. }
-\CSLRightInline{Stekhoven DJ, Bühlmann P.
-2012 {MissForest}\textemdash non-parametric missing value imputation for mixed-type data.
-\emph{Bioinformatics} \textbf{28}, 112--118.
-(doi:\href{https://doi.org/10.1093/bioinformatics/btr597}{10.1093/bioinformatics/btr597})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Penone C, Davidson AD, Shoemaker KT, Marco MD, Rondinini C, Brooks TM, Young BE, Graham CH, Costa GC.
-2014 Imputation of missing data in life-history trait datasets: Which approach performs the best?
-\emph{Methods Ecol.
-Evol.} \textbf{5}, 961--970.
-(doi:\href{https://doi.org/10.1111/2041-210X.12232}{10.1111/2041-210X.12232})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Chamberlain S \emph{et al.} 2018 Package {``{PVR}''}. R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Diniz-Filho JAF, Bini LM, Rangel TF, Morales-Castilla I, Olalla-Tárraga MÁ, Rodríguez MÁ, Hawkins BA.
-2012 On the selection of phylogenetic eigenvectors for ecological analyses.
-\emph{Ecography} \textbf{35}, 239--249.
-(doi:\href{https://doi.org/10.1111/j.1600-0587.2011.06949.x}{10.1111/j.1600-0587.2011.06949.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-serneels2008}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Serneels S, Verdonck T. 2008 Principal component analysis for data containing outliers and missing elements. \emph{Computational Statistics \& Data Analysis} \textbf{52}, 1712--1727.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Legendre P, Legendre L. 2012 \emph{Numerical ecology}. {2nd edn}. {Elsevier, Amsterdam}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Revell LJ.
-2012 Phytools: An {R} package for phylogenetic comparative biology (and other things).
-\emph{Methods Ecol.
-Evol.} \textbf{3}, 217--223.
-(doi:\href{https://doi.org/10.1111/j.2041-210X.2011.00169.x}{10.1111/j.2041-210X.2011.00169.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Abdi H, Williams LJ. 2010 Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459. (doi:\href{https://doi.org/10.1002/wics.101}{10.1002/wics.101})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
-\CSLLeftMargin{58. }
-\CSLRightInline{Ballantyne G, Baldock KCR, Willmer PG.
-2015 Constructing more informative plant\textendash pollinator networks: Visitation and pollen deposition networks in a heathland plant community.
-\emph{Proc.
-Royal Soc.
-B} \textbf{282}, 20151130.
-(doi:\href{https://doi.org/10.1098/rspb.2015.1130}{10.1098/rspb.2015.1130})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
-\CSLLeftMargin{59. }
-\CSLRightInline{Vázquez DP, Morris WF, Jordano P.
-2005 Interaction frequency as a surrogate for the total effect of animal mutualists on plants.
-\emph{Ecol.
-Lett.} \textbf{8}, 1088--1094.
-(doi:\href{https://doi.org/10.1111/j.1461-0248.2005.00810.x}{10.1111/j.1461-0248.2005.00810.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
-\CSLLeftMargin{60. }
-\CSLRightInline{Vázquez DP, Lomáscolo SB, Maldonado MB, Chacoff NP, Dorado J, Stevani EL, Vitale NL.
-2012 The strength of plant\textendash pollinator interactions.
-\emph{Ecology} \textbf{93}, 719--725.
-(doi:\href{https://doi.org/10.1890/11-1356.1}{10.1890/11-1356.1})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
-\CSLLeftMargin{61. }
-\CSLRightInline{Hung K-LJ, Kingston JM, Albrecht M, Holway DA, Kohn JR.
-2018 The worldwide importance of honey bees as pollinators in natural habitats.
-\emph{Proc.
-Royal Soc.
-B} \textbf{285}, 20172140.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
-\CSLLeftMargin{62. }
-\CSLRightInline{Bürkner P-C. 2017 Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.} \textbf{80}, 1--28.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
-\CSLLeftMargin{63. }
-\CSLRightInline{Gabry J, Simpson D, Vehtari A, Betancourt M, Gelman A.
-2019 Visualization in {Bayesian} workflow.
-\emph{J.
-R.
-Stat.
-Soc.
-Ser.
-A Stat.
-Soc.} \textbf{182}, 389--402.
-(doi:\href{https://doi.org/10.1111/rssa.12378}{10.1111/rssa.12378})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
-\CSLLeftMargin{64. }
-\CSLRightInline{Dormann CF, Gruber B, Fründ J. 2008 Introducing the bipartite package: Analysing ecological networks. \emph{R News} \textbf{8/2}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
-\CSLLeftMargin{65. }
-\CSLRightInline{Blüthgen N, Menzel F, Blüthgen N.
-2006 Measuring specialization in species interaction networks.
-\emph{BMC Ecol.} \textbf{6}, 9.
-(doi:\href{https://doi.org/10.1186/1472-6785-6-9}{10.1186/1472-6785-6-9})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
-\CSLLeftMargin{66. }
-\CSLRightInline{Healy K, Ezard THG, Jones OR, Salguero-Gómez R, Buckley YM.
-2019 Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
-\emph{Nat.
-Ecol.
-Evol.} \textbf{3}, 1217--1224.
-(doi:\href{https://doi.org/10.1038/s41559-019-0938-7}{10.1038/s41559-019-0938-7})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-worley2000}{}}%
-\CSLLeftMargin{67. }
-\CSLRightInline{Worley AC, Baker AM, Thompson JD, Barrett SC.
-2000 Floral display in narcissus: Variation in flower size and number at the species, population, and individual levels.
-\emph{International Journal of Plant Sciences} \textbf{161}, 69--79.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-petit2006}{}}%
-\CSLLeftMargin{68. }
-\CSLRightInline{Petit RJ, Hampe A. 2006 Some evolutionary consequences of being a tree. \emph{Annu. Rev. Ecol. Evol. Syst.} \textbf{37}, 187--214.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
-\CSLLeftMargin{69. }
-\CSLRightInline{Hegland SJ, Totland Ø. 2005 Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia} \textbf{145}, 586--594.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
-\CSLLeftMargin{70. }
-\CSLRightInline{Kaiser-Bunbury CN, Vázquez DP, Stang M, Ghazoul J.
-2014 Determinants of the microstructure of plant\textendash pollinator networks.
-\emph{Ecology} \textbf{95}, 3314--3324.
-(doi:\href{https://doi.org/10.1890/14-0024.1}{10.1890/14-0024.1})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
-\CSLLeftMargin{71. }
-\CSLRightInline{Földesi R, Howlett BG, Grass I, Batáry P.
-2021 Larger pollinators deposit more pollen on stigmas across multiple plant species---a meta-analysis.
-\emph{Journal of Applied Ecology} \textbf{58}, 699--707.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
-\CSLLeftMargin{72. }
-\CSLRightInline{Vázquez DP, Melián CJ, Williams NM, Blüthgen N, Krasnov BR, Poulin R.
-2007 Species abundance and asymmetric interaction strength in ecological networks.
-\emph{Oikos} \textbf{116}, 1120--1127.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
-\CSLLeftMargin{73. }
-\CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS. 2012 Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.} \textbf{15}, 198--208.}
-
-\end{CSLReferences}
-
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
-
-This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-We thank all researchers that made their data openly available and sent it upon request.
-We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
-We also thank Jason Tylianakis for his comments on the manuscript before submission.
-Finally, JBL thanks the University of New England for the funding provided to carry out this work.
 
@@
 
-\clearpage
-
 \doublespacing
 
+\hypertarget{d-phylogenetic-distance}{%
+\subsection{(d) Phylogenetic Distance}\label{d-phylogenetic-distance}}
+
+We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{48},\protect\hyperlink{ref-jin2019}{49}{]}.
+
+\hypertarget{e-data-imputation}{%
+\subsection{(e) Data Imputation}\label{e-data-imputation}}
+
+To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{50}{]} which allows imputation of datasets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{51}{]}.
+To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} {[}\protect\hyperlink{ref-santos2018}{52}{]} based on a previous conceptual framework that considers phylogenetic eigenvectors {[}\protect\hyperlink{ref-diniz-filho2012}{53}{]}.
+We conducted two different imputations, one for the full set of species (1,506 species, 5.79\% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
+S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01\% of missing values).
+To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without missing values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
+
+\hypertarget{f-plant-strategies}{%
+\subsection{(f) Plant strategies}\label{f-plant-strategies}}
+
+We explored the association between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+Prior to the analyses, we excluded outliers and standardized the data.
+Due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{54},\protect\hyperlink{ref-legendre2012}{55}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as indicated for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{55}{]}.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{56}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{57}{]}.
+Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
+For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
+
+\hypertarget{g-phylogenetic-signal}{%
+\subsection{(g) Phylogenetic signal}\label{g-phylogenetic-signal}}
+
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{56}{]} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
+
+\hypertarget{h-network-analyses}{%
+\subsection{(h) Network analyses}\label{h-network-analyses}}
+
+First, we investigated how the different groups of floral visitors interacted along the main axes of reproductive trait variation (see below `visitation patterns' section) with the help of qualitative and quantitative information of plant-pollinator interactions.
+For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
+Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency {[}\protect\hyperlink{ref-ballantyne2015}{58}{]}, the number of visits can provide valuable information of the contribution of floral visitors to pollination {[}\protect\hyperlink{ref-vazquez2005}{59},\protect\hyperlink{ref-vazquez2012}{60}{]}.
+Second, we investigated how the main axes of trait variation and individual traits influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below `plant species network roles' section).
+
+Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
+Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
+All analyses were conducted in R version \emph{4.0.3}.
+
+\hypertarget{i-visitation-patterns}{%
+\subsubsection{(i) Visitation patterns}\label{i-visitation-patterns}}
+
+We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species.
+For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
+Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
+In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total).
+This finding is consistent with previous research showing that \emph{A.
+mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems {[}\protect\hyperlink{ref-hung2018}{61}{]}.
+Hence, to control for the effect of \emph{A.
+mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding \emph{A.
+mellifera}.
+We found that \emph{A.
+mellifera}, was partly driving some of the observed trends on PC1 (Fig.
+S5).
+However, we did not detect major differences on PC2 and PC3.
+
+We implemented Bayesian generalized linear mixed models using the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{62}{]}.
+We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
+We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
+Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
+We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
+The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results {[}\protect\hyperlink{ref-burkner2017}{62}{]}.
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}\protect\hyperlink{ref-gabry2019}{63}{]}.
+
+\hypertarget{ii-plant-species-network-roles}{%
+\subsubsection{(ii) Plant species network roles}\label{ii-plant-species-network-roles}}
+
+We investigated whether different quantitative traits determined different plant species' functional roles in the pollination network using Bayesian modelling.
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{64}{]} with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{65}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{64}{]}.
+
+We modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
+For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
+Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns' section.
+
+\hypertarget{results}{%
+\section{3. Results}\label{results}}
+
+\hypertarget{a-plant-strategies}{%
+\subsection{(a) Plant strategies}\label{a-plant-strategies}}
+
+The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of the reproductive trait variation, respectively (Fig.
+1 and Fig.
+S7).
+The first principal component (PC1 or the flower number - flower size axis) represented 26.72\% of the trait variation and indicated a negative correlation between flower number and flower size.
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
+One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
+For instance, on this end of the spectrum we find the species \emph{Cornus florida} which has approximately a total of 10.000 flowers, an average height of 7.5m, flowers of 3mm wide, a style length of 3.5mm and a total of 2 ovules per flower.
+The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
+For instance, on this side of the axis we find the species \emph{Petunia axillaris} that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
+The second principal component (PC2 or the pollinator dependence axis) represented 25.05\% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
+In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles.
+On this extreme of the spectrum we find the species \emph{Zuccagnia punctata} that is a self-incompatible shrub that depends completely on floral visitors for seed production, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm.
+In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
+For instance, on this end of the spectrum we find the species \emph{Veronica peregrina} which is a self-compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
+Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17\%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \textbar-0.51\textbar) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
+The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; Table S3).
+In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (Fig.
+S4).
+This pPCA explained similar variance with the first two principal components (45.52\%) and similar associations of traits despite some variability in the loadings (Table S4).
+
 \begin{figure}[H]
 
-{\centering \includegraphics{output/figures/unnamed-chunk-2-1}
+{\centering \includegraphics[width=0.95\linewidth]{output/figures/unnamed-chunk-2-1}
 
@@
 
+We found (with an Anova) that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
+2 and Table S2).
+Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
+In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
+S8).
+Regarding self-compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility; Fig.
+S8a and Fig.
+S8b).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
+S8c and Fig.
+S8d).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
+S8e and Fig.
+S8f).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
+S8g and Fig.
+S8h).
+Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (Fig.
+S8i and Fig.
+S8j).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Fig.
+S8k and Fig.
+S8l).
+
 \blandscape
@@
 \elandscape
+
+\hypertarget{b-phylogenetic-signal}{%
+\subsection{(b) Phylogenetic signal}\label{b-phylogenetic-signal}}
+
+We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) for most quantitative traits (Table S5).
+The traits that showed the highest phylogenetic signal were ovule number (\(\lambda\) = 1), pollen grains per flower (\(\lambda\) = 1) and plant height (\(\lambda\) = 0.96), followed by flower length (\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73), number of flowers per plant (\(\lambda\) = 0.69) and nectar concentration (\(\lambda\) = 0.65).
+The traits that showed a moderate phylogenetic signal were inflorescence width (\(\lambda\) = 0.57), style length (\(\lambda\) = 0.49) and autonomous selfing (\(\lambda\) = 0.34).
+Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits (\(\lambda\) = 0.14).
+
+\hypertarget{c-visitation-patterns}{%
+\subsection{(c) Visitation patterns}\label{c-visitation-patterns}}
+
+The main axes of trait variation (PC1, PC2 and PC3) explained partly presence-absence of interaction partners (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the overall number of visits (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
+However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (Fig.
+3).
+We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (Fig.
+3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
+Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number but small (Fig.
+3d).
+On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (Fig.
+3b and Fig.
+3e).
+Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (Fig.
+3c).
+However, regarding number of visits on the style length - pollinator dependence axis, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
+3f).
+
+The additional model for both presence-absence of interaction (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and number of visits (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
+The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (Fig.
+3a and Fig.
+3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (Fig.
+S9).
 
@@
 
+\hypertarget{d-plant-species-network-roles}{%
+\subsection{(d) Plant species network roles}\label{d-plant-species-network-roles}}
+
+The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
+S10; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
+Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
+On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
+S10a).
+However, specialization showed the opposite trend on this axis (Fig.
+S10g).
+On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (Fig.
+S10c).
+Again, specialization showed the opposite trend to number of visits (Fig.
+S10i).
+
+\hypertarget{discussion}{%
+\section{4. Discussion}\label{discussion}}
+
+This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
+Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively.
+These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
+Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{13},\protect\hyperlink{ref-carmona2021}{37}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
+Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
+However, they were insufficient to capture their visitation rates which highlight the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
+
+Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context.
+In addition, our work links the reproductive trait variation with the previously described fast-slow continuum' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{66}{]} life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+Although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{39},\protect\hyperlink{ref-kettle2011}{40},\protect\hyperlink{ref-worley2000}{67}{]}, it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
+We found support to this trait association and show that other life history traits also covariate along this axis.
+For example, our study complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{68}{]} by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
+Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{41}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
+Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral display.
+Thus, our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
+
+Overall, our models showed that the main plant reproductive trait correlations have low predictive power for broad-level interaction patterns between plants and floral visitors.
+However, we found changes in the interaction patterns among and within floral visitor guilds that suggest that plant reproductive strategies partly mediate these associations at large ecological scales.
+For example, we found that all floral visitor guilds interacted more frequently with plant species with larger floral displays in agreement with previous findings {[}\protect\hyperlink{ref-lazaro2013}{28},\protect\hyperlink{ref-hegland2005}{69},\protect\hyperlink{ref-kaiser2014}{70}{]}.
+Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes.
+For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour {[}rader2020; {[}\protect\hyperlink{ref-foldesi2021}{71}{]}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{27},\protect\hyperlink{ref-vazquez2007}{72},\protect\hyperlink{ref-encinas2012}{73}{]} that reproductive correlations do not.
+
+To conclude, we provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of plant reproductive traits from species that belong to plant-pollinator networks.
+Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider other factors beyond plant reproductive strategies to better capture broad scale patterns of interactions with floral visitors.
+Our work provides empirical evidence that complements previous studies that have explored trait correlations with other plant organs and highlights the need to include these reproductive correlations in the global spectrum of plant form and function {[}\protect\hyperlink{ref-diaz2016}{13}{]} as reproductive strategies involve clear cost and benefits that can affect the trait space of the whole plant.
+Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and plant-pollinator associations.
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-barrett2002}{}}%
+\CSLLeftMargin{1. }
+\CSLRightInline{Barrett SCH. 2002 The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.} \textbf{3}, 274--284. (doi:\href{https://doi.org/10.1038/nrg776}{10.1038/nrg776})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schiestl2013}{}}%
+\CSLLeftMargin{2. }
+\CSLRightInline{Schiestl FP, Johnson SD.
+2013 Pollinator-mediated evolution of floral signals.
+\emph{Trends Ecol.
+Evol.} \textbf{28}, 307--315.
+(doi:\href{https://doi.org/10.1016/j.tree.2013.01.019}{10.1016/j.tree.2013.01.019})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fenster2004}{}}%
+\CSLLeftMargin{3. }
+\CSLRightInline{Fenster CB, Armbruster WS, Wilson P, Dudash MR, Thomson JD.
+2004 Pollination {Syndromes} and {Floral Specialization}.
+\emph{Annu.
+Rev.
+Ecol.
+Evol.
+Syst.} \textbf{35}, 375--403.
+(doi:\href{https://doi.org/10.1146/annurev.ecolsys.34.011802.132347}{10.1146/annurev.ecolsys.34.011802.132347})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dellinger2020}{}}%
+\CSLLeftMargin{4. }
+\CSLRightInline{Dellinger AS.
+2020 Pollination syndromes in the 21st century: Where do we stand and where may we go?
+\emph{New Phytol.} \textbf{228}, 1193--1213.
+(doi:\href{https://doi.org/10.1111/nph.16793}{10.1111/nph.16793})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stearns1989}{}}%
+\CSLLeftMargin{5. }
+\CSLRightInline{Stearns SC. 1989 Trade-offs in life-history evolution. \emph{Functional ecology} \textbf{3}, 259--268.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-agrawal2020}{}}%
+\CSLLeftMargin{6. }
+\CSLRightInline{Agrawal AA. 2020 A scale-dependent framework for trade-offs, syndromes, and specialization in organismal biology. \emph{Ecology} \textbf{101}, e02924.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-salguero2016}{}}%
+\CSLLeftMargin{7. }
+\CSLRightInline{Salguero-Gómez R, Jones OR, Jongejans E, Blomberg SP, Hodgson DJ, Mbeau-Ache C, Zuidema PA, de Kroon H, Buckley YM.
+2016 Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
+\emph{Proc.
+Natl.
+Acad.
+Sci.
+U.S.A.} \textbf{113}, 230--235.
+(doi:\href{https://doi.org/10.1073/pnas.1506215112}{10.1073/pnas.1506215112})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-friedman2020}{}}%
+\CSLLeftMargin{8. }
+\CSLRightInline{Friedman J.
+2020 The evolution of annual and perennial plant life histories: Ecological correlates and genetic mechanisms.
+\emph{Annual Review of Ecology, Evolution, and Systematics} \textbf{51}, 461--481.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-paterno2020}{}}%
+\CSLLeftMargin{9. }
+\CSLRightInline{Paterno GB, Silveira CL, Kollmann J, Westoby M, Fonseca CR.
+2020 The maleness of larger angiosperm flowers.
+\emph{Proceedings of the National Academy of Sciences} \textbf{117}, 10921--10926.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-roddy2021}{}}%
+\CSLLeftMargin{10. }
+\CSLRightInline{Roddy AB, Martínez-Perez C, Teixido AL, Cornelissen TG, Olson ME, Oliveira RS, Silveira FAO.
+2021 Towards the flower economics spectrum.
+\emph{New Phytol.} \textbf{229}, 665--672.
+(doi:\href{https://doi.org/10.1111/nph.16823}{10.1111/nph.16823})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%
+\CSLLeftMargin{11. }
+\CSLRightInline{Wright IJ \emph{et al.} 2004 The worldwide leaf economics spectrum. \emph{Nature} \textbf{428}, 821--827. (doi:\href{https://doi.org/10.1038/nature02403}{10.1038/nature02403})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
+\CSLLeftMargin{12. }
+\CSLRightInline{Chave J, Coomes D, Jansen S, Lewis SL, Swenson NG, Zanne AE. 2009 Towards a worldwide wood economics spectrum. \emph{Ecol. Lett.} \textbf{12}, 351--366.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
+\CSLLeftMargin{13. }
+\CSLRightInline{Díaz S \emph{et al.} 2016 The global spectrum of plant form and function. \emph{Nature} \textbf{529}, 167--171. (doi:\href{https://doi.org/10.1038/nature16489}{10.1038/nature16489})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-onoda2017}{}}%
+\CSLLeftMargin{14. }
+\CSLRightInline{Onoda Y, Wright IJ, Evans JR, Hikosaka K, Kitajima K, Niinemets Ü, Poorter H, Tosens T, Westoby M.
+2017 Physiological and structural tradeoffs underlying the leaf economics spectrum.
+\emph{New Phytologist} \textbf{214}, 1447--1463.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
+\CSLLeftMargin{15. }
+\CSLRightInline{Laughlin DC \emph{et al.} 2021 Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
+\emph{Nat.
+Ecol.
+Evol.}, 1--12.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-baude2016}{}}%
+\CSLLeftMargin{16. }
+\CSLRightInline{Baude M, Kunin WE, Boatman ND, Conyers S, Davies N, Gillespie MA, Morton RD, Smart SM, Memmott J.
+2016 Historical nectar assessment reveals the fall and rise of floral resources in britain.
+\emph{Nature} \textbf{530}, 85--88.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
+\CSLLeftMargin{17. }
+\CSLRightInline{Munoz F, Violle C, Cheptou P-O.
+2016 {CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
+\emph{Oikos} \textbf{125}, 1296--1303.
+(doi:\href{https://doi.org/10.1111/oik.02328}{10.1111/oik.02328})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-grossenbacher2017}{}}%
+\CSLLeftMargin{18. }
+\CSLRightInline{Grossenbacher DL \emph{et al.} 2017 Self-compatibility is over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
+\CSLLeftMargin{19. }
+\CSLRightInline{Moeller DA \emph{et al.} 2017 Global biogeography of mating system variation in seed plants.
+\emph{Ecol.
+Lett.} \textbf{20}, 375--384.
+(doi:\href{https://doi.org/10.1111/ele.12738}{10.1111/ele.12738})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
+\CSLLeftMargin{20. }
+\CSLRightInline{Sargent RD, Ackerly DD. 2008 Plant--pollinator interactions and the assembly of plant communities. \emph{Trends Ecol. Evol.} \textbf{23}, 123--130.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rech2016}{}}%
+\CSLLeftMargin{21. }
+\CSLRightInline{Rech AR, Dalsgaard B, Sandel B, Sonne J, Svenning J-C, Holmes N, Ollerton J.
+2016 The macroecology of animal versus wind pollination: Ecological factors are more important than historical climate stability.
+\emph{Plant Ecol.
+Divers.} \textbf{9}, 253--262.
+(doi:\href{https://doi.org/10.1080/17550874.2016.1207722}{10.1080/17550874.2016.1207722})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
+\CSLLeftMargin{22. }
+\CSLRightInline{Rüger N, Comita LS, Condit R, Purves D, Rosenbaum B, Visser MD, Wright SJ, Wirth C.
+2018 Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
+\emph{Ecol.
+Lett.} \textbf{21}, 1075--1084.
+(doi:\href{https://doi.org/10.1111/ele.12974}{10.1111/ele.12974})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
+\CSLLeftMargin{23. }
+\CSLRightInline{Tur C, Castro-Urgal R, Traveset A.
+2013 Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}.
+\emph{PLoS One} \textbf{8}, e78294.
+(doi:\href{https://doi.org/10.1371/journal.pone.0078294}{10.1371/journal.pone.0078294})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
+\CSLLeftMargin{24. }
+\CSLRightInline{Devaux C, Lepers C, Porcher E.
+2014 Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems.
+\emph{J.
+Evol.
+Biol.} \textbf{27}, 1413--1430.
+(doi:\href{https://doi.org/10.1111/jeb.12380}{10.1111/jeb.12380})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
+\CSLLeftMargin{25. }
+\CSLRightInline{Rosas-Guerrero V, Aguilar R, Martén-Rodríguez S, Ashworth L, Lopezaraiza-Mikel M, Bastida JM, Quesada M.
+2014 A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
+\emph{Ecol.
+Lett.} \textbf{17}, 388--400.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
+\CSLLeftMargin{26. }
+\CSLRightInline{Stang M, Klinkhamer PGL, Waser NM, Stang I, van der Meijden E.
+2009 Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
+\emph{Ann.
+Bot.} \textbf{103}, 1459--1469.
+(doi:\href{https://doi.org/10.1093/aob/mcp027}{10.1093/aob/mcp027})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
+\CSLLeftMargin{27. }
+\CSLRightInline{Bartomeus I, Gravel D, Tylianakis JM, Aizen MA, Dickie IA, Bernard-Verdier M.
+2016 A common framework for identifying linkage rules across different types of interactions.
+\emph{Funct.
+Ecol.} \textbf{30}, 1894--1903.
+(doi:\href{https://doi.org/10.1111/1365-2435.12666}{10.1111/1365-2435.12666})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
+\CSLLeftMargin{28. }
+\CSLRightInline{Lázaro A, Jakobsson A, Totland Ø.
+2013 How do pollinator visitation rate and seed set relate to species' floral traits and community context?
+\emph{Oecologia} \textbf{173}, 881--893.
+(doi:\href{https://doi.org/10.1007/s00442-013-2652-5}{10.1007/s00442-013-2652-5})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
+\CSLLeftMargin{29. }
+\CSLRightInline{Junker RR, Blüthgen N, Brehm T, Binkenstein J, Paulus J, Schaefer HM, Stang M.
+2013 Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
+\emph{Funct.
+Ecol.} \textbf{27}, 329--341.
+(doi:\href{https://doi.org/10.1111/1365-2435.12005}{10.1111/1365-2435.12005})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
+\CSLLeftMargin{30. }
+\CSLRightInline{Coux C, Rader R, Bartomeus I, Tylianakis JM.
+2016 Linking species functional roles to their network roles.
+\emph{Ecol.
+Lett.} \textbf{19}, 762--770.
+(doi:\href{https://doi.org/10.1111/ele.12612}{10.1111/ele.12612})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
+\CSLLeftMargin{31. }
+\CSLRightInline{Ibanez S.
+2012 Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks.
+\emph{Oecologia} \textbf{170}, 233--242.
+(doi:\href{https://doi.org/10.1007/s00442-012-2290-3}{10.1007/s00442-012-2290-3})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
+\CSLLeftMargin{32. }
+\CSLRightInline{Eklöf A \emph{et al.} 2013 The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
+\CSLLeftMargin{33. }
+\CSLRightInline{Dehling DM, Jordano P, Schaefer HM, Böhning-Gaese K, Schleuning M.
+2016 Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
+\emph{Proc.
+Royal Soc.
+B} \textbf{283}, 20152444.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
+\CSLLeftMargin{34. }
+\CSLRightInline{Kattge J \emph{et al.} 2011 {TRY} \textendash{} a global database of plant traits.
+\emph{Glob.
+Chang.
+Biol.} \textbf{17}, 2905--2935.
+(doi:\href{https://doi.org/10.1111/j.1365-2486.2011.02451.x}{10.1111/j.1365-2486.2011.02451.x})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
+\CSLLeftMargin{35. }
+\CSLRightInline{Salguero-Gómez R \emph{et al.} 2015 The compadre {Plant Matrix Database}: An open online repository for plant demography.
+\emph{J.
+Ecol.} \textbf{103}, 202--218.
+(doi:\href{https://doi.org/10.1111/1365-2745.12334}{10.1111/1365-2745.12334})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
+\CSLLeftMargin{36. }
+\CSLRightInline{Bruelheide H \emph{et al.} 2018 Global trait--environment relationships of plant communities. \emph{Nat. Ecol. Evol.} \textbf{2}, 1906--1917.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
+\CSLLeftMargin{37. }
+\CSLRightInline{Carmona CP \emph{et al.} 2021 Erosion of global functional diversity across the tree of life.
+\emph{Sci.
+Adv.} \textbf{7}, eabf2675.
+(doi:\href{https://doi.org/10.1126/sciadv.abf2675}{10.1126/sciadv.abf2675})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
+\CSLLeftMargin{38. }
+\CSLRightInline{E-Vojtkó A, Bello F de, Durka W, Kühn I, Götzenberger L.
+2020 The neglected importance of floral traits in trait-based plant community assembly.
+\emph{J.
+Veg.
+Sci.} \textbf{31}, 529--539.
+(doi:\href{https://doi.org/10.1111/jvs.12877}{10.1111/jvs.12877})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
+\CSLLeftMargin{39. }
+\CSLRightInline{Sargent RD, Goodwillie C, Kalisz S, Ree RH.
+2007 Phylogenetic evidence for a flower size and number trade-off.
+\emph{Am.
+J.
+Bot.} \textbf{94}, 2059--2062.
+(doi:\href{https://doi.org/10.3732/ajb.94.12.2059}{10.3732/ajb.94.12.2059})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
+\CSLLeftMargin{40. }
+\CSLRightInline{Kettle CJ, Maycock CR, Ghazoul J, Hollingsworth PM, Khoo E, Sukri RSH, Burslem DFRP.
+2011 Ecological {Implications} of a {Flower Size}/{Number Trade}-{Off} in {Tropical Forest Trees}.
+\emph{PLoS One} \textbf{6}, e16111.
+(doi:\href{https://doi.org/10.1371/journal.pone.0016111}{10.1371/journal.pone.0016111})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
+\CSLLeftMargin{41. }
+\CSLRightInline{Goodwillie C \emph{et al.} 2010 Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
+\emph{New Phytol.} \textbf{185}, 311--321.
+(doi:\href{https://doi.org/10.1111/j.1469-8137.2009.03043.x}{10.1111/j.1469-8137.2009.03043.x})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
+\CSLLeftMargin{42. }
+\CSLRightInline{Barrett SCH.
+2003 Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond.
+\emph{Philos.
+Trans.
+R.
+Soc.
+Lond.
+B Biol.
+Sci.} \textbf{358}, 991--1004.
+(doi:\href{https://doi.org/10.1098/rstb.2003.1301}{10.1098/rstb.2003.1301})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
+\CSLLeftMargin{43. }
+\CSLRightInline{Carvalheiro LG \emph{et al.} 2014 The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
+\emph{Ecol.
+Lett.} \textbf{17}, 1389--1399.
+(doi:\href{https://doi.org/10.1111/ele.12342}{10.1111/ele.12342})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
+\CSLLeftMargin{44. }
+\CSLRightInline{Olesen JM, Bascompte J, Dupont YL, Jordano P.
+2007 The modularity of pollination networks.
+\emph{PNAS} \textbf{104}, 19891--19896.
+(doi:\href{https://doi.org/10.1073/pnas.0706375104}{10.1073/pnas.0706375104})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
+\CSLLeftMargin{45. }
+\CSLRightInline{Fortuna MA, Stouffer DB, Olesen JM, Jordano P, Mouillot D, Krasnov BR, Poulin R, Bascompte J.
+2010 Nestedness versus modularity in ecological networks: Two sides of the same coin?
+\emph{J.
+Anim.
+Ecol.} \textbf{79}, 811--817.
+(doi:\href{https://doi.org/10.1111/j.1365-2656.2010.01688.x}{10.1111/j.1365-2656.2010.01688.x})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
+\CSLLeftMargin{46. }
+\CSLRightInline{Poisot T \emph{et al.} 2016 Mangal \textendash{} making ecological network analysis simple.
+\emph{Ecography} \textbf{39}, 384--390.
+(doi:\href{https://doi.org/10.1111/ecog.00976}{10.1111/ecog.00976})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
+\CSLLeftMargin{47. }
+\CSLRightInline{Chamberlain S \emph{et al.} 2020 Taxize: {Taxonomic} information from around the web.
+R package version 0.9.99.~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}.
+}
+
+\leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
+\CSLLeftMargin{48. }
+\CSLRightInline{Smith SA, Brown JW.
+2018 Constructing a broadly inclusive seed plant phylogeny.
+\emph{Am.
+J.
+Bot.} \textbf{105}, 302--314.
+(doi:\href{https://doi.org/10.1002/ajb2.1019}{10.1002/ajb2.1019})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
+\CSLLeftMargin{49. }
+\CSLRightInline{Jin Y, Qian H.
+2019 V.{PhyloMaker}: An {R} package that can generate very large phylogenies for vascular plants.
+\emph{Ecography} \textbf{42}, 1353--1359.
+(doi:\href{https://doi.org/10.1111/ecog.04434}{10.1111/ecog.04434})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
+\CSLLeftMargin{50. }
+\CSLRightInline{Stekhoven DJ, Bühlmann P.
+2012 {MissForest}\textemdash non-parametric missing value imputation for mixed-type data.
+\emph{Bioinformatics} \textbf{28}, 112--118.
+(doi:\href{https://doi.org/10.1093/bioinformatics/btr597}{10.1093/bioinformatics/btr597})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
+\CSLLeftMargin{51. }
+\CSLRightInline{Penone C, Davidson AD, Shoemaker KT, Marco MD, Rondinini C, Brooks TM, Young BE, Graham CH, Costa GC.
+2014 Imputation of missing data in life-history trait datasets: Which approach performs the best?
+\emph{Methods Ecol.
+Evol.} \textbf{5}, 961--970.
+(doi:\href{https://doi.org/10.1111/2041-210X.12232}{10.1111/2041-210X.12232})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
+\CSLLeftMargin{52. }
+\CSLRightInline{Chamberlain S \emph{et al.} 2018 Package {``{PVR}''}. R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
+\CSLLeftMargin{53. }
+\CSLRightInline{Diniz-Filho JAF, Bini LM, Rangel TF, Morales-Castilla I, Olalla-Tárraga MÁ, Rodríguez MÁ, Hawkins BA.
+2012 On the selection of phylogenetic eigenvectors for ecological analyses.
+\emph{Ecography} \textbf{35}, 239--249.
+(doi:\href{https://doi.org/10.1111/j.1600-0587.2011.06949.x}{10.1111/j.1600-0587.2011.06949.x})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-serneels2008}{}}%
+\CSLLeftMargin{54. }
+\CSLRightInline{Serneels S, Verdonck T. 2008 Principal component analysis for data containing outliers and missing elements. \emph{Computational Statistics \& Data Analysis} \textbf{52}, 1712--1727.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
+\CSLLeftMargin{55. }
+\CSLRightInline{Legendre P, Legendre L. 2012 \emph{Numerical ecology}. {2nd edn}. {Elsevier, Amsterdam}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
+\CSLLeftMargin{56. }
+\CSLRightInline{Revell LJ.
+2012 Phytools: An {R} package for phylogenetic comparative biology (and other things).
+\emph{Methods Ecol.
+Evol.} \textbf{3}, 217--223.
+(doi:\href{https://doi.org/10.1111/j.2041-210X.2011.00169.x}{10.1111/j.2041-210X.2011.00169.x})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
+\CSLLeftMargin{57. }
+\CSLRightInline{Abdi H, Williams LJ. 2010 Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459. (doi:\href{https://doi.org/10.1002/wics.101}{10.1002/wics.101})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
+\CSLLeftMargin{58. }
+\CSLRightInline{Ballantyne G, Baldock KCR, Willmer PG.
+2015 Constructing more informative plant\textendash pollinator networks: Visitation and pollen deposition networks in a heathland plant community.
+\emph{Proc.
+Royal Soc.
+B} \textbf{282}, 20151130.
+(doi:\href{https://doi.org/10.1098/rspb.2015.1130}{10.1098/rspb.2015.1130})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
+\CSLLeftMargin{59. }
+\CSLRightInline{Vázquez DP, Morris WF, Jordano P.
+2005 Interaction frequency as a surrogate for the total effect of animal mutualists on plants.
+\emph{Ecol.
+Lett.} \textbf{8}, 1088--1094.
+(doi:\href{https://doi.org/10.1111/j.1461-0248.2005.00810.x}{10.1111/j.1461-0248.2005.00810.x})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
+\CSLLeftMargin{60. }
+\CSLRightInline{Vázquez DP, Lomáscolo SB, Maldonado MB, Chacoff NP, Dorado J, Stevani EL, Vitale NL.
+2012 The strength of plant\textendash pollinator interactions.
+\emph{Ecology} \textbf{93}, 719--725.
+(doi:\href{https://doi.org/10.1890/11-1356.1}{10.1890/11-1356.1})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
+\CSLLeftMargin{61. }
+\CSLRightInline{Hung K-LJ, Kingston JM, Albrecht M, Holway DA, Kohn JR.
+2018 The worldwide importance of honey bees as pollinators in natural habitats.
+\emph{Proc.
+Royal Soc.
+B} \textbf{285}, 20172140.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
+\CSLLeftMargin{62. }
+\CSLRightInline{Bürkner P-C. 2017 Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.} \textbf{80}, 1--28.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
+\CSLLeftMargin{63. }
+\CSLRightInline{Gabry J, Simpson D, Vehtari A, Betancourt M, Gelman A.
+2019 Visualization in {Bayesian} workflow.
+\emph{J.
+R.
+Stat.
+Soc.
+Ser.
+A Stat.
+Soc.} \textbf{182}, 389--402.
+(doi:\href{https://doi.org/10.1111/rssa.12378}{10.1111/rssa.12378})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
+\CSLLeftMargin{64. }
+\CSLRightInline{Dormann CF, Gruber B, Fründ J. 2008 Introducing the bipartite package: Analysing ecological networks. \emph{R News} \textbf{8/2}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
+\CSLLeftMargin{65. }
+\CSLRightInline{Blüthgen N, Menzel F, Blüthgen N.
+2006 Measuring specialization in species interaction networks.
+\emph{BMC Ecol.} \textbf{6}, 9.
+(doi:\href{https://doi.org/10.1186/1472-6785-6-9}{10.1186/1472-6785-6-9})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
+\CSLLeftMargin{66. }
+\CSLRightInline{Healy K, Ezard THG, Jones OR, Salguero-Gómez R, Buckley YM.
+2019 Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
+\emph{Nat.
+Ecol.
+Evol.} \textbf{3}, 1217--1224.
+(doi:\href{https://doi.org/10.1038/s41559-019-0938-7}{10.1038/s41559-019-0938-7})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-worley2000}{}}%
+\CSLLeftMargin{67. }
+\CSLRightInline{Worley AC, Baker AM, Thompson JD, Barrett SC.
+2000 Floral display in narcissus: Variation in flower size and number at the species, population, and individual levels.
+\emph{International Journal of Plant Sciences} \textbf{161}, 69--79.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-petit2006}{}}%
+\CSLLeftMargin{68. }
+\CSLRightInline{Petit RJ, Hampe A. 2006 Some evolutionary consequences of being a tree. \emph{Annu. Rev. Ecol. Evol. Syst.} \textbf{37}, 187--214.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
+\CSLLeftMargin{69. }
+\CSLRightInline{Hegland SJ, Totland Ø. 2005 Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia} \textbf{145}, 586--594.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
+\CSLLeftMargin{70. }
+\CSLRightInline{Kaiser-Bunbury CN, Vázquez DP, Stang M, Ghazoul J.
+2014 Determinants of the microstructure of plant\textendash pollinator networks.
+\emph{Ecology} \textbf{95}, 3314--3324.
+(doi:\href{https://doi.org/10.1890/14-0024.1}{10.1890/14-0024.1})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
+\CSLLeftMargin{71. }
+\CSLRightInline{Földesi R, Howlett BG, Grass I, Batáry P.
+2021 Larger pollinators deposit more pollen on stigmas across multiple plant species---a meta-analysis.
+\emph{Journal of Applied Ecology} \textbf{58}, 699--707.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
+\CSLLeftMargin{72. }
+\CSLRightInline{Vázquez DP, Melián CJ, Williams NM, Blüthgen N, Krasnov BR, Poulin R.
+2007 Species abundance and asymmetric interaction strength in ecological networks.
+\emph{Oikos} \textbf{116}, 1120--1127.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
+\CSLLeftMargin{73. }
+\CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS. 2012 Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.} \textbf{15}, 198--208.}
+
+\end{CSLReferences}
+
+\textbf{Data accessibility.} All data and code used to conduct this study will is deposited at Zenodo
+
+\textbf{Authors'contributions.} JBL, RR and IB designed the study.
+JBL collated the data and conducted analysis with guidance of JS, LKK and IB.
+JBL wrote the manuscript with contributions of all authors.
+
+\textbf{Conflict of interest declaration.} We declare we have no competing interests.
+
+\textbf{Funding.} This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
+
+\textbf{Acknowledgements.} We thank all researchers that made their data openly available and sent it upon request.
+We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
+We also thank Jason Tylianakis for his comments on the manuscript before submission.
+Finally, JBL thanks the University of New England for the funding provided to carry out this work.
+
 \end{document}

### 2022-06-22 Manuscript/Lanuza_et_al_2021.Rmd
edits

@@
 # zotero: "My shared Zotero group"
-csl: ecology.csl #ecology letters
+csl: proceedingsb.csl #ecology letters
 notes-after-punctuation: false
@@
 n_of_records <- subset(missing.values, isna=="FALSE")
-Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
-           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")
-
-Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Compatibility system", "Breeding system", " ", " ", " ", " ", " ")
-
-T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-           "Presence \n Absence", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " ", ""),align = c("l"))
-
-Type <- linebreak(c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive \n biology"),align = c("c"))
-
-Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology","","","","", ""),align = c("c"))
-
-dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
+
+Trait <- c("Plant height", "Flower width", "Flower length", "Inflorescence width", "Style length", "Ovules per flower",
+           "Flowers per plant", "Microliters of nectar", "Milligrams of nectar", "Nectar concentration", "Pollen grains per flower", "Autonomous selfing (fruit set)")
+
+Trait1 <- linebreak(c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Compatibility system", "Breeding system"),align = c("l"))
+
+#T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub #\n Tree", "Brush \n Campanulate \n Capitulum \n Open \n #Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
+#           "Presence \n Absence", "Self-incomp. \n Part. #self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n #Dioecious"),align = c("l"))
+#
+T.cat <- linebreak(c("Short-lived and perennial", "Herb, shrub and tree", "Brush, campanulate, capitulum,\n open, papilionaceous and tube",  "Actinomorphic and zygomorphic",
+           "Presence and absence", "Self-incompatible, partially self-compabtile \n and self-compatible", "Hermaphrodite, monoecious and dioecious"), align = c("l"))
 
@@
 
-dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
-
-colnames(dat) <- c("Type","Traits", "Type", "Traits", "Categories")
-
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table 1 | Quantitative and categorical traits used in this study.}") %>%
-kable_styling(full_width = F,font_size = 10) %>%
-add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 3),bold=T)  %>%
-    column_spec(c(1,3), bold = T) %>% row_spec(0, bold=T)
+T.range <- c("0.01-30m", "0.50-205mm", "0.20-195mm", "0.80-300mm", "0-138mm", "1-25 x $10^3$", "1-18 x $10^4$", "0-160$\\mu$l", "0-6.1mg", "0-100$\\%$", "13-2 x $10^8$", "0-100$\\%$")
+
+dat_1 <- data.frame(Trait,T.range)
+dat_2 <- data.frame(Trait1, T.cat)
+
+colnames(dat_1) <- c("Quantitative traits", "Numerical range")
+colnames(dat_2) <- c("Categorical traits", "Categories")
+
+#kable(list(dat_1, dat_2), booktabs = T, linesep = #"\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1 | #Quantitative and categorical traits used in this study.}") %>%
+#  kable_styling(full_width = F,font_size = 10) %>%  #column_spec(1:4, 
+#              width = "3in", 
+#              latex_valign = "m")
+#
+#
+
+colnames(dat_1) <- c("Traits", "Numerical range/Categories")
+colnames(dat_2) <- c("Traits", "Numerical range/Categories")
+
+d <- rbind(dat_1,dat_2)
+
+kable(d, booktabs = T, linesep = "\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1 | Quantitative and categorical traits used in this study.}") %>%
+  kable_styling(full_width = F,font_size = 10) %>% row_spec(0, bold=T) %>% pack_rows("Quantitative", 1, 12) %>%
+pack_rows("Categorical", 13, 19)
 
@@
 
-**Data accessibility.** All data and code used to conduct this study will is deposited at Zenodo
+**Data accessibility.** All data and code used to conduct this study is deposited at Zenodo
 
@@
 
-**Funding.** This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
+**Funding.** This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2) and JBL was supported by a University of New England postgraduate scholarship.
 

### 2022-06-22 Manuscript/Lanuza_et_al_2021.tex
edits

@@
 \fontsize{10}{12}\selectfont
-\begin{tabular}[t]{>{}cl>{}ccl}
+\begin{tabular}[t]{ll}
 \toprule
-\multicolumn{2}{c}{\textbf{Quantitative traits}} & \multicolumn{3}{c}{\textbf{Categorical traits}} \\
-\cmidrule(l{3pt}r{3pt}){1-2} \cmidrule(l{3pt}r{3pt}){3-5}
-\textbf{Type} & \textbf{Traits} & \textbf{Type} & \textbf{Traits} & \textbf{Categories}\\
+\textbf{Traits} & \textbf{Numerical range/Categories}\\
 \midrule
-\textbf{Vegetative} & Plant height (m) & \textbf{Vegetative} & Lifepan & \makecell[l]{Short-lived \\ Perennial}\\
-\addlinespace
-\textbf{Floral} & Flower width (mm) & \textbf{Vegetative} & Life form & \makecell[l]{Herb \\ Shrub \\ Tree}\\
-\addlinespace
-\textbf{Floral} & Flower length (mm) & \textbf{Floral} & Flower shape & \makecell[l]{Brush \\ Campanulate \\ Capitulum \\ Open \\ Papilionaceous \\ Tube}\\
-\addlinespace
-\textbf{Floral} & Inflorescence width (mm) & \textbf{Floral} & Flower symmetry & \makecell[l]{Actinomorphic \\ Zygomorphic}\\
-\addlinespace
-\textbf{Floral} & Style length (mm) & \textbf{Floral} & Nectar & \makecell[l]{Presence \\ Absence}\\
-\addlinespace
-\textbf{Floral} & Ovules per flower & \textbf{\makecell[c]{Reproductive \\ biology}} & Compatibility system & \makecell[l]{Self-incomp. \\ Part. self-comp. \\ Self-comp.}\\
-\addlinespace
-\textbf{Floral} & Flowers per plant & \textbf{\makecell[c]{Reproductive \\ biology}} & Breeding system & \makecell[l]{Hermaphrodite \\ Monoecious \\ Dioecious}\\
-\addlinespace
-\textbf{Floral} & Nectar ($\mu$l) & \textbf{} &  & \\
-\addlinespace
-\textbf{Floral} & Nectar (mg) & \textbf{} &  & \\
-\addlinespace
-\textbf{Floral} & Nectar concentration ($\%$) & \textbf{} &  & \\
-\addlinespace
-\textbf{Floral} & Pollen grains per flower & \textbf{} &  & \\
-\addlinespace
-\textbf{\makecell[c]{Reproductive \\ biology}} & Autonomous selfing (fruit set) & \textbf{} &  & \\
+\addlinespace[0.3em]
+\multicolumn{2}{l}{\textbf{Quantitative}}\\
+\hspace{1em}Plant height & 0.01-30m\\
+\hspace{1em}Flower width & 0.50-205mm\\
+\hspace{1em}Flower length & 0.20-195mm\\
+\hspace{1em}Inflorescence width & 0.80-300mm\\
+\hspace{1em}Style length & 0-138mm\\
+\hspace{1em}Ovules per flower & 1-25 x $10^3$\\
+\hspace{1em}Flowers per plant & 1-18 x $10^4$\\
+\hspace{1em}Microliters of nectar & 0-160$\mu$l\\
+\hspace{1em}Milligrams of nectar & 0-6.1mg\\
+\hspace{1em}Nectar concentration & 0-100$\%$\\
+\hspace{1em}Pollen grains per flower & 13-2 x $10^8$\\
+\hspace{1em}Autonomous selfing (fruit set) & 0-100$\%$\\
+\addlinespace[0.3em]
+\multicolumn{2}{l}{\textbf{Categorical}}\\
+\hspace{1em}Lifepan & Short-lived and perennial\\
+\hspace{1em}Life form & Herb, shrub and tree\\
+\hspace{1em}Flower shape & \makecell[l]{Brush, campanulate, capitulum,\\ open, papilionaceous and tube}\\
+\hspace{1em}Flower symmetry & Actinomorphic and zygomorphic\\
+\hspace{1em}Nectar & Presence and absence\\
+\hspace{1em}Compatibility system & \makecell[l]{Self-incompatible, partially self-compabtile \\ and self-compatible}\\
+\hspace{1em}Breeding system & Hermaphrodite, monoecious and dioecious\\
 \bottomrule
@@
 
-\textbf{Funding.} This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
+\textbf{Funding.} This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2) and JBL was supported by a University of New England postgraduate scholarship.
 

### 2022-06-22 Manuscript/trial.Rmd
edits

@@
 ---
-title: "Untitled"
-output: html_document
+title: ""
+output:
+  pdf_document: default
+  html_document: default
+
+header-includes:
+- \usepackage{booktabs}
+- \usepackage{longtable}
+- \usepackage{array}
+- \usepackage{multirow}
+- \usepackage{wrapfig}
+- \usepackage{float}
+- \usepackage{colortbl}
+- \usepackage{tabu}
+- \usepackage{threeparttable}
+- \usepackage{threeparttablex}
+- \usepackage[normalem]{ulem}
+- \usepackage{makecell}
+- \usepackage{xcolor}
+- \usepackage{float}
+- \floatplacement{figure}{H}
+- \usepackage[skip=3pt]{caption}
+- \captionsetup[figure]{labelformat=empty}
+- \usepackage{setspace}
+- \usepackage{titlesec}
+- \titlespacing{\title}{0pt}{\parskip}{-\parskip}
+- \usepackage[style=nature]{biblatex}
+- \usepackage[labelformat = empty]{caption}
+- \usepackage{pdflscape}
+- \usepackage[T1]{fontenc}
+- \DeclareUnicodeCharacter{0301}{*************************************}
+- \DeclareUnicodeCharacter{1EF3}{*************************************}
 ---
+
+\singlespacing
 
@@
 n_of_records <- subset(missing.values, isna=="FALSE")
-Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
-           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")
 
-Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Autonomous selfing", "Compatibility system", "Breeding system", " ", " ", " ", " ")
+Trait <- c("Plant height", "Flower width", "Flower length", "Inflorescence width", "Style length", "Ovules per flower",
+           "Flowers per plant", "Microliters of nectar", "Milligrams of nectar", "Nectar concentration", "Pollen grains per flower", "Autonomous selfing (fruit set)")
 
-T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-           "Presence \n Absence", "None \n Low \n Medium \n High", "Self-incomp. \n Part. self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious"," ", " ", " ", " "),align = c("l"))
+Trait1 <- linebreak(c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Compatibility system", "Breeding system"),align = c("l"))
 
-Type <- linebreak(c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Floral","Floral","Floral","Floral","Reproductive \n biology"),align = c("c"))
-
-Type_1 <- linebreak(c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive \n biology", "Reproductive \n biology", "Reproductive \n biology","","","",""),align = c("c"))
-
-dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
+#T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub #\n Tree", "Brush \n Campanulate \n Capitulum \n Open \n #Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
+#           "Presence \n Absence", "Self-incomp. \n Part. #self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n #Dioecious"),align = c("l"))
+#
+T.cat <- linebreak(c("Short-lived and perennial", "Herb, shrub and tree", "Brush, campanulate, capitulum,\n open, papilionaceous and tube",  "Actinomorphic and zygomorphic",
+           "Presence and absence", "Self-incompatible, partially self-compabtile \n and self-compatible", "Hermaphrodite, monoecious and dioecious"), align = c("l"))
 
@@
 
-dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
+T.range <- c("0.01-30m", "0.50-205mm", "0.20-195mm", "0.80-300mm", "0-138mm", "1-25 x $10^3$", "1-18 x $10^4$", "0-160$\\mu$l", "0-6.1mg", "0-100$\\%$", "13-2 x $10^8$", "0-100$\\%$")
 
-colnames(dat) <- c("Type","Traits", "Type", "Traits", "Categories")
+dat_1 <- data.frame(Trait,T.range)
+dat_2 <- data.frame(Trait1, T.cat)
 
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table 1 | Quantitative and categorical traits used in this study.}") %>%
-kable_styling(full_width = F,font_size = 10) %>%
-add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 3),bold=T)  %>%
-    column_spec(c(1,3), bold = T) %>% row_spec(0, bold=T)
+colnames(dat_1) <- c("Quantitative traits", "Numerical range")
+colnames(dat_2) <- c("Categorical traits", "Categories")
+
+#kable(list(dat_1, dat_2), booktabs = T, linesep = #"\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1 | #Quantitative and categorical traits used in this study.}") %>%
+#  kable_styling(full_width = F,font_size = 10) %>%  #column_spec(1:4, 
+#              width = "3in", 
+#              latex_valign = "m")
+#
+#
+
+colnames(dat_1) <- c("Traits", "Numerical range/Categories")
+colnames(dat_2) <- c("Traits", "Numerical range/Categories")
+
+d <- rbind(dat_1,dat_2)
+
+kable(d, booktabs = T, linesep = "\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1 | Quantitative and categorical traits used in this study.}") %>%
+  kable_styling(full_width = F,font_size = 10) %>% row_spec(0, bold=T) %>% pack_rows("Quantitative", 1, 12) %>%
+pack_rows("Categorical", 13, 19) %>%   column_spec(1, width = "10em") %>% 
+  collapse_rows(columns = 1:2, valign = "top", latex_hline = "major")
 

### 2022-06-22 Manuscript/Lanuza_et_al_2021.Rmd
edits

@@
 
-\textbf{Corresponding author:} Jose B. Lanuza \| +34 616375981\| [barragansljose\@gmail.com](mailto:barragansljose@gmail.com){.email}
+\textbf{Keywords:} life-history strategies \| plant reproductive traits \| plant-pollinator interactions
+
+\textbf{Author for correspondence:} Jose B. Lanuza \| [barragansljose\@gmail.com](mailto:barragansljose@gmail.com){.email}
 
@@
 Interestingly, the use of trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-For example, plant traits can define species' network roles [e.g., specialists vs generalists;  @lazaro2013; @tur2013] and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
+For example, plant traits can define species' network roles [e.g., specialists vs generalists @tur2013] and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
 Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
@@
 
-With the recent availability of large trait databases [e.g., TRY @kattge2011; and COMPADRE @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
+With the recent availability of large trait databases [e.g., TRY @kattge2011;\ COMPADRE @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
 However, most studies with a multitrait perspective have focused on trait correlations from the leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] related traits with little or no attention given to reproductive traits [@evojtko2020; @roddy2021].
@@
 
-We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see Table S1 and Fig.
-S1).
+We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see table S1 and figure S1).
 These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different biological communities.
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies [e.g.,  @carvalheiro2014; @olesen2007; @fortuna2010] or available in online archives [e.g., The Web of Life, @fortuna2010; and Mangal, @poisot2016].
+Many of these networks are freely available either as published studies [e.g., @carvalheiro2014; @olesen2007; @fortuna2010] or available in online archives [e.g., Mangal @poisot2016;\ The Web of Life @fortuna2010].
 In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
@@
 
-We selected a total of 19 different functional traits that comprised reproductive traits and plant form and size related traits (see Table 1).
+We selected a total of 19 different functional traits that comprised reproductive traits and plant form and size related traits (see table 1).
 From these, 16 were reproductive traits that consisted of 13 floral traits and 3 reproductive biology traits.
@@
 For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 possible cells considering all traits and plant species (20 columns × 1,506 species), we were able to fill 24,341 cells (80.8% of the dataset, see Fig.
-S2 for missing values information for each trait).
+From a total of 30,120 possible cells considering all traits and plant species (20 columns × 1,506 species), we were able to fill 24,341 cells (80.8% of the dataset, see figure S2 for missing values information for each trait).
 An extended description of each trait and how it was obtained can be found in Appendix S1.
@@
 
-kable(d, booktabs = T, linesep = "\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1 | Quantitative and categorical traits used in this study.}") %>%
-  kable_styling(full_width = F,font_size = 10) %>% row_spec(0, bold=T) %>% pack_rows("Quantitative", 1, 12) %>%
+kable(d, booktabs = T, linesep = "\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1.} Quantitative and categorical traits used in this study.") %>%
+  kable_styling(full_width = F,font_size = 12) %>% row_spec(0, bold=T) %>% pack_rows("Quantitative", 1, 12) %>%
 pack_rows("Categorical", 13, 19)
@@
 To extract the eigenvectors, we used the function *PVRdecomp* from the package *PVR* [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-We conducted two different imputations, one for the full set of species (1,506 species, 5.79% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
-S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01% of missing values).
+We conducted two different imputations, one for the full set of species (1,506 species, 5.79% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (figure S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01% of missing values).
 To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without missing values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
@@
 We found that *A.
-mellifera*, was partly driving some of the observed trends on PC1 (Fig.
-S5).
+mellifera*, was partly driving some of the observed trends on PC1 (figure S5).
 However, we did not detect major differences on PC2 and PC3.
@@
 
-The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of the reproductive trait variation, respectively (Fig.
-1 and Fig.
-S7).
+The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of the reproductive trait variation, respectively (figure 1 and figure S7).
 The first principal component (PC1 or the flower number - flower size axis) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; table S3) but style length also contributed moderately to PC1 (loading = -0.33).
 One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
@@
 The second principal component (PC2 or the pollinator dependence axis) represented 25.05% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; table S3).
 In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles.
@@
 Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = |-0.51|) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
-The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; Table S3).
-In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (Fig.
-S4).
-This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (Table S4).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="95%", fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
+The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; table S3).
+In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (figure S4).
+This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (table S4).
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="95%", fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
 The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
@@
 
-We found (with an Anova) that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
-2 and Table S2).
+We found (with an Anova) that most categorical traits were statistically associated with the first two axes of trait variation (figure 2 and table S2).
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
-S8).
-Regarding self-compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility; Fig.
-S8a and Fig.
-S8b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
-S8c and Fig.
-S8d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
-S8e and Fig.
-S8f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
-S8g and Fig.
-S8h).
+In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (figure S8).
+Regarding self-compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility; figure S8a and figure S8b).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S8c and figure S8d).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S8e and figure S8f).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S8g and figure S8h).
 Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (Fig.
-S8i and Fig.
-S8j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Fig.
-S8k and Fig.
-S8l).
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S8i and figure S8j).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S8k and figure S8l).
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="80%",fig.align='center',fig.cap= "\\textbf{Figure 2} Location of the different qualitative traits on the trait space.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="80%",fig.align='center',fig.cap= "\\textbf{Figure 2.} Location of the different qualitative traits on the trait space.
 The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
@@
 
-We found a strong phylogenetic signal (*P* \< 0.01) for most quantitative traits (Table S5).
+We found a strong phylogenetic signal (*P* \< 0.01) for most quantitative traits (table S5).
 The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
@@
 The main axes of trait variation (PC1, PC2 and PC3) explained partly presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (Fig.
-3).
-We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (Fig.
-3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
-Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number but small (Fig.
-3d).
-On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (Fig.
-3b and Fig.
-3e).
-Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (Fig.
-3c).
-However, regarding number of visits on the style length - pollinator dependence axis, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
-3f).
+However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (figure 3).
+We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (figure 3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
+Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number but small (figure 3d).
+On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (figure 3b and figure 3e).
+Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (figure 3c).
+However, regarding number of visits on the style length - pollinator dependence axis, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (figure 3f).
 
 The additional model for both presence-absence of interaction (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (Fig.
-3a and Fig.
-3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (Fig.
-S9).
+The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (figure 3a and figure 3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (figure S9).
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
 PC1 represents the flower number - flower size axis, PC2 represents the pollinator dependence axis and PC3, the style length - pollinator dependence axis.
@@
 
-The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
-S10; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
+The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S10; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
 Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
-On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
-S10a).
-However, specialization showed the opposite trend on this axis (Fig.
-S10g).
-On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (Fig.
-S10c).
-Again, specialization showed the opposite trend to number of visits (Fig.
-S10i).
+On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S10a).
+However, specialization showed the opposite trend on this axis (figure S10g).
+On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S10c).
+Again, specialization showed the opposite trend to number of visits (figure S10i).
 

### 2022-06-22 Manuscript/Lanuza_et_al_2021.tex
edits

@@
 
-\textbf{Corresponding author:} Jose B. Lanuza \textbar{} +34 616375981\textbar{} \href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
+\textbf{Keywords:} life-history strategies \textbar{} plant reproductive traits \textbar{} plant-pollinator interactions
+
+\textbf{Author for correspondence:} Jose B. Lanuza \textbar{} \href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
 
@@
 Interestingly, the use of trait-based approaches {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{25}{]} and trait-matching analyses {[}\protect\hyperlink{ref-stang2009}{26},\protect\hyperlink{ref-bartomeus2016}{27}{]} has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-For example, plant traits can define species' network roles {[}\protect\hyperlink{ref-tur2013}{23},e.g., specialists vs generalists;~ \protect\hyperlink{ref-lazaro2013}{28}{]} and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators {[}\protect\hyperlink{ref-junker2013}{29},\protect\hyperlink{ref-coux2016}{30}{]}.
-Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure {[}\protect\hyperlink{ref-stang2009}{26},\protect\hyperlink{ref-ibanez2012}{31}{]}.
-Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network interactions {[}\protect\hyperlink{ref-eklof2013}{32}{]}, an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns {[}see \protect\hyperlink{ref-dehling2016}{33}{]}.
+For example, plant traits can define species' network roles {[}e.g., specialists vs generalists \protect\hyperlink{ref-tur2013}{23}{]} and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators {[}\protect\hyperlink{ref-junker2013}{28},\protect\hyperlink{ref-coux2016}{29}{]}.
+Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure {[}\protect\hyperlink{ref-stang2009}{26},\protect\hyperlink{ref-ibanez2012}{30}{]}.
+Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network interactions {[}\protect\hyperlink{ref-eklof2013}{31}{]}, an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns {[}see \protect\hyperlink{ref-dehling2016}{32}{]}.
 Thus, by exploring the reproductive spectrum of trait variation is possible to delimit the different plant reproductive strategies and explore how these are associated with the different floral visitors.
 
-With the recent availability of large trait databases {[}e.g., TRY \protect\hyperlink{ref-kattge2011}{34},and COMPADRE \protect\hyperlink{ref-salguero2015}{35}{]}, plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-diaz2016}{13},\protect\hyperlink{ref-bruelheide2018}{36},\protect\hyperlink{ref-carmona2021}{37}{]}.
-However, most studies with a multitrait perspective have focused on trait correlations from the leaf {[}\protect\hyperlink{ref-wright2004}{11}{]}, wood {[}\protect\hyperlink{ref-chave2009}{12}{]}, or root {[}\protect\hyperlink{ref-laughlin2021}{15}{]} related traits with little or no attention given to reproductive traits {[}\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-evojtko2020}{38}{]}.
-Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{39},\protect\hyperlink{ref-kettle2011}{40}{]}, the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{41}{]} or the association between outcrossing rate and lifespan where short lived versus perennial species tend to have low versus high levels of outcrossing {[}\protect\hyperlink{ref-moeller2017}{19},\protect\hyperlink{ref-barrett2003}{42}{]}, respectively.
+With the recent availability of large trait databases {[}e.g., TRY \protect\hyperlink{ref-kattge2011}{33},~COMPADRE \protect\hyperlink{ref-salguero2015}{34}{]}, plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-diaz2016}{13},\protect\hyperlink{ref-bruelheide2018}{35},\protect\hyperlink{ref-carmona2021}{36}{]}.
+However, most studies with a multitrait perspective have focused on trait correlations from the leaf {[}\protect\hyperlink{ref-wright2004}{11}{]}, wood {[}\protect\hyperlink{ref-chave2009}{12}{]}, or root {[}\protect\hyperlink{ref-laughlin2021}{15}{]} related traits with little or no attention given to reproductive traits {[}\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-evojtko2020}{37}{]}.
+Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{38},\protect\hyperlink{ref-kettle2011}{39}{]}, the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{40}{]} or the association between outcrossing rate and lifespan where short lived versus perennial species tend to have low versus high levels of outcrossing {[}\protect\hyperlink{ref-moeller2017}{19},\protect\hyperlink{ref-barrett2003}{41}{]}, respectively.
 Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships {[}\protect\hyperlink{ref-roddy2021}{10}{]}, we still lack empirical evidence that investigates jointly these different reproductive trait associations.
@@
 
-We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see Table S1 and Fig.
-S1).
+We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see table S1 and figure S1).
 These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different biological communities.
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies {[}e.g.,~ \protect\hyperlink{ref-carvalheiro2014}{43},\protect\hyperlink{ref-olesen2007}{44},\protect\hyperlink{ref-fortuna2010}{45}{]} or available in online archives {[}e.g., The Web of Life, \protect\hyperlink{ref-fortuna2010}{45},and Mangal, \protect\hyperlink{ref-poisot2016}{46}{]}.
+Many of these networks are freely available either as published studies {[}e.g., \protect\hyperlink{ref-carvalheiro2014}{42},\protect\hyperlink{ref-olesen2007}{43},\protect\hyperlink{ref-fortuna2010}{44}{]} or available in online archives {[}e.g., Mangal \protect\hyperlink{ref-poisot2016}{45},~The Web of Life \protect\hyperlink{ref-fortuna2010}{44}{]}.
 In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
@@
 
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} {[}\protect\hyperlink{ref-chamberlain2020}{47}{]}.
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} {[}\protect\hyperlink{ref-chamberlain2020}{46}{]}.
 We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
@@
 For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 possible cells considering all traits and plant species (20 columns × 1,506 species), we were able to fill 24,341 cells (80.8\% of the dataset, see Fig.
-S2 for missing values information for each trait).
+From a total of 30,120 possible cells considering all traits and plant species (20 columns × 1,506 species), we were able to fill 24,341 cells (80.8\% of the dataset, see figure S2 for missing values information for each trait).
 An extended description of each trait and how it was obtained can be found in Appendix S1.
@@
 
-\caption{\label{tab:unnamed-chunk-1}\textbf{Table 1 | Quantitative and categorical traits used in this study.}}
+\caption{\label{tab:unnamed-chunk-1}\textbf{Table 1.} Quantitative and categorical traits used in this study.}
 \centering
-\fontsize{10}{12}\selectfont
+\fontsize{12}{14}\selectfont
 \begin{tabular}[t]{ll}
@@
 
-We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{48},\protect\hyperlink{ref-jin2019}{49}{]}.
+We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{47},\protect\hyperlink{ref-jin2019}{48}{]}.
 
@@
 
-To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{50}{]} which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{51}{]}.
-To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} {[}\protect\hyperlink{ref-santos2018}{52}{]} based on a previous conceptual framework that considers phylogenetic eigenvectors {[}\protect\hyperlink{ref-diniz-filho2012}{53}{]}.
-We conducted two different imputations, one for the full set of species (1,506 species, 5.79\% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (Fig.
-S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01\% of missing values).
+To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{49}{]} which allows imputation of datasets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{50}{]}.
+To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} {[}\protect\hyperlink{ref-santos2018}{51}{]} based on a previous conceptual framework that considers phylogenetic eigenvectors {[}\protect\hyperlink{ref-diniz-filho2012}{52}{]}.
+We conducted two different imputations, one for the full set of species (1,506 species, 5.79\% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (figure S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01\% of missing values).
 To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without missing values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
@@
 Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{54},\protect\hyperlink{ref-legendre2012}{55}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as indicated for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{55}{]}.
+Due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{53},\protect\hyperlink{ref-legendre2012}{54}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as indicated for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{54}{]}.
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{56}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{57}{]}.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{55}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{56}{]}.
 Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
@@
 
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{56}{]} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{55}{]} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
@@
 For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency {[}\protect\hyperlink{ref-ballantyne2015}{58}{]}, the number of visits can provide valuable information of the contribution of floral visitors to pollination {[}\protect\hyperlink{ref-vazquez2005}{59},\protect\hyperlink{ref-vazquez2012}{60}{]}.
+Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency {[}\protect\hyperlink{ref-ballantyne2015}{57}{]}, the number of visits can provide valuable information of the contribution of floral visitors to pollination {[}\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}{]}.
 Second, we investigated how the main axes of trait variation and individual traits influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below `plant species network roles' section).
@@
 This finding is consistent with previous research showing that \emph{A.
-mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems {[}\protect\hyperlink{ref-hung2018}{61}{]}.
+mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems {[}\protect\hyperlink{ref-hung2018}{60}{]}.
 Hence, to control for the effect of \emph{A.
@@
 We found that \emph{A.
-mellifera}, was partly driving some of the observed trends on PC1 (Fig.
-S5).
+mellifera}, was partly driving some of the observed trends on PC1 (figure S5).
 However, we did not detect major differences on PC2 and PC3.
 
-We implemented Bayesian generalized linear mixed models using the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{62}{]}.
+We implemented Bayesian generalized linear mixed models using the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{61}{]}.
 We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
@@
 We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results {[}\protect\hyperlink{ref-burkner2017}{62}{]}.
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}\protect\hyperlink{ref-gabry2019}{63}{]}.
+The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results {[}\protect\hyperlink{ref-burkner2017}{61}{]}.
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}\protect\hyperlink{ref-gabry2019}{62}{]}.
 
@@
 We investigated whether different quantitative traits determined different plant species' functional roles in the pollination network using Bayesian modelling.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{64}{]} with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{65}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{64}{]}.
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{63}{]} with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{64}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{63}{]}.
 
@@
 
-The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of the reproductive trait variation, respectively (Fig.
-1 and Fig.
-S7).
+The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of the reproductive trait variation, respectively (figure 1 and figure S7).
 The first principal component (PC1 or the flower number - flower size axis) represented 26.72\% of the trait variation and indicated a negative correlation between flower number and flower size.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; Table S3) but style length also contributed moderately to PC1 (loading = -0.33).
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; table S3) but style length also contributed moderately to PC1 (loading = -0.33).
 One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
@@
 The second principal component (PC2 or the pollinator dependence axis) represented 25.05\% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; Table S3).
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; table S3).
 In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles.
@@
 Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17\%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \textbar-0.51\textbar) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
-The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; Table S3).
-In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (Fig.
-S4).
-This pPCA explained similar variance with the first two principal components (45.52\%) and similar associations of traits despite some variability in the loadings (Table S4).
+The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; table S3).
+In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (figure S4).
+This pPCA explained similar variance with the first two principal components (45.52\%) and similar associations of traits despite some variability in the loadings (table S4).
 
@@
 
-\caption{\textbf{Figure 1} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
+\caption{\textbf{Figure 1.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
 The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
@@
 
-We found (with an Anova) that most categorical traits were statistically associated with the first two axes of trait variation (Fig.
-2 and Table S2).
+We found (with an Anova) that most categorical traits were statistically associated with the first two axes of trait variation (figure 2 and table S2).
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (Fig.
-S8).
-Regarding self-compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility; Fig.
-S8a and Fig.
-S8b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (Fig.
-S8c and Fig.
-S8d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (Fig.
-S8e and Fig.
-S8f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (Fig.
-S8g and Fig.
-S8h).
+In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (figure S8).
+Regarding self-compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility; figure S8a and figure S8b).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S8c and figure S8d).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S8e and figure S8f).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S8g and figure S8h).
 Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (Fig.
-S8i and Fig.
-S8j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (Fig.
-S8k and Fig.
-S8l).
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S8i and figure S8j).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S8k and figure S8l).
 
@@
 
-\caption{\textbf{Figure 2} Location of the different qualitative traits on the trait space.
+\caption{\textbf{Figure 2.} Location of the different qualitative traits on the trait space.
 The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
@@
 
-We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) for most quantitative traits (Table S5).
+We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) for most quantitative traits (table S5).
 The traits that showed the highest phylogenetic signal were ovule number (\(\lambda\) = 1), pollen grains per flower (\(\lambda\) = 1) and plant height (\(\lambda\) = 0.96), followed by flower length (\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73), number of flowers per plant (\(\lambda\) = 0.69) and nectar concentration (\(\lambda\) = 0.65).
@@
 The main axes of trait variation (PC1, PC2 and PC3) explained partly presence-absence of interaction partners (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the overall number of visits (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
-However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (Fig.
-3).
-We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (Fig.
-3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
-Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number but small (Fig.
-3d).
-On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (Fig.
-3b and Fig.
-3e).
-Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (Fig.
-3c).
-However, regarding number of visits on the style length - pollinator dependence axis, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (Fig.
-3f).
+However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (figure 3).
+We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (figure 3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
+Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number but small (figure 3d).
+On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (figure 3b and figure 3e).
+Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (figure 3c).
+However, regarding number of visits on the style length - pollinator dependence axis, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (figure 3f).
 
 The additional model for both presence-absence of interaction (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and number of visits (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (Fig.
-3a and Fig.
-3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (Fig.
-S9).
+The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (figure 3a and figure 3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (figure S9).
 
@@
 \includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\textbf{Figure 3} Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
+\caption{\label{fig:unnamed-chunk-4}\textbf{Figure 3.} Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
 PC1 represents the flower number - flower size axis, PC2 represents the pollinator dependence axis and PC3, the style length - pollinator dependence axis.
@@
 
-The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (Fig.
-S10; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
+The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S10; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
 Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
-On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (Fig.
-S10a).
-However, specialization showed the opposite trend on this axis (Fig.
-S10g).
-On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (Fig.
-S10c).
-Again, specialization showed the opposite trend to number of visits (Fig.
-S10i).
+On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S10a).
+However, specialization showed the opposite trend on this axis (figure S10g).
+On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S10c).
+Again, specialization showed the opposite trend to number of visits (figure S10i).
 
@@
 These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
-Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{13},\protect\hyperlink{ref-carmona2021}{37}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
+Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{13},\protect\hyperlink{ref-carmona2021}{36}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
 Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
@@
 Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context.
-In addition, our work links the reproductive trait variation with the previously described fast-slow continuum' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{66}{]} life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-Although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{39},\protect\hyperlink{ref-kettle2011}{40},\protect\hyperlink{ref-worley2000}{67}{]}, it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
+In addition, our work links the reproductive trait variation with the previously described fast-slow continuum' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{65}{]} life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
+Although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{38},\protect\hyperlink{ref-kettle2011}{39},\protect\hyperlink{ref-worley2000}{66}{]}, it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
 We found support to this trait association and show that other life history traits also covariate along this axis.
-For example, our study complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{68}{]} by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
-Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{41}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
+For example, our study complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{67}{]} by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
+Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{40}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
 Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral display.
@@
 However, we found changes in the interaction patterns among and within floral visitor guilds that suggest that plant reproductive strategies partly mediate these associations at large ecological scales.
-For example, we found that all floral visitor guilds interacted more frequently with plant species with larger floral displays in agreement with previous findings {[}\protect\hyperlink{ref-lazaro2013}{28},\protect\hyperlink{ref-hegland2005}{69},\protect\hyperlink{ref-kaiser2014}{70}{]}.
+For example, we found that all floral visitor guilds interacted more frequently with plant species with larger floral displays in agreement with previous findings {[}\protect\hyperlink{ref-hegland2005}{68}--\protect\hyperlink{ref-kaiser2014}{70}{]}.
 Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
 \CSLLeftMargin{28. }
-\CSLRightInline{Lázaro A, Jakobsson A, Totland Ø.
-2013 How do pollinator visitation rate and seed set relate to species' floral traits and community context?
-\emph{Oecologia} \textbf{173}, 881--893.
-(doi:\href{https://doi.org/10.1007/s00442-013-2652-5}{10.1007/s00442-013-2652-5})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
-\CSLLeftMargin{29. }
 \CSLRightInline{Junker RR, Blüthgen N, Brehm T, Binkenstein J, Paulus J, Schaefer HM, Stang M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Coux C, Rader R, Bartomeus I, Tylianakis JM.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Ibanez S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
+\CSLLeftMargin{31. }
+\CSLRightInline{Eklöf A \emph{et al.} 2013 The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
 \CSLLeftMargin{32. }
-\CSLRightInline{Eklöf A \emph{et al.} 2013 The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
-\CSLLeftMargin{33. }
 \CSLRightInline{Dehling DM, Jordano P, Schaefer HM, Böhning-Gaese K, Schleuning M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{33. }
 \CSLRightInline{Kattge J \emph{et al.} 2011 {TRY} \textendash{} a global database of plant traits.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{34. }
 \CSLRightInline{Salguero-Gómez R \emph{et al.} 2015 The compadre {Plant Matrix Database}: An open online repository for plant demography.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
+\CSLLeftMargin{35. }
+\CSLRightInline{Bruelheide H \emph{et al.} 2018 Global trait--environment relationships of plant communities. \emph{Nat. Ecol. Evol.} \textbf{2}, 1906--1917.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
 \CSLLeftMargin{36. }
-\CSLRightInline{Bruelheide H \emph{et al.} 2018 Global trait--environment relationships of plant communities. \emph{Nat. Ecol. Evol.} \textbf{2}, 1906--1917.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
-\CSLLeftMargin{37. }
 \CSLRightInline{Carmona CP \emph{et al.} 2021 Erosion of global functional diversity across the tree of life.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{37. }
 \CSLRightInline{E-Vojtkó A, Bello F de, Durka W, Kühn I, Götzenberger L.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Sargent RD, Goodwillie C, Kalisz S, Ree RH.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Kettle CJ, Maycock CR, Ghazoul J, Hollingsworth PM, Khoo E, Sukri RSH, Burslem DFRP.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Goodwillie C \emph{et al.} 2010 Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Barrett SCH.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Carvalheiro LG \emph{et al.} 2014 The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Olesen JM, Bascompte J, Dupont YL, Jordano P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Fortuna MA, Stouffer DB, Olesen JM, Jordano P, Mouillot D, Krasnov BR, Poulin R, Bascompte J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Poisot T \emph{et al.} 2016 Mangal \textendash{} making ecological network analysis simple.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Chamberlain S \emph{et al.} 2020 Taxize: {Taxonomic} information from around the web.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Smith SA, Brown JW.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Jin Y, Qian H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Stekhoven DJ, Bühlmann P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Penone C, Davidson AD, Shoemaker KT, Marco MD, Rondinini C, Brooks TM, Young BE, Graham CH, Costa GC.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
+\CSLLeftMargin{51. }
+\CSLRightInline{Chamberlain S \emph{et al.} 2018 Package {`{PVR}'}. R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
 \CSLLeftMargin{52. }
-\CSLRightInline{Chamberlain S \emph{et al.} 2018 Package {``{PVR}''}. R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
-\CSLLeftMargin{53. }
 \CSLRightInline{Diniz-Filho JAF, Bini LM, Rangel TF, Morales-Castilla I, Olalla-Tárraga MÁ, Rodríguez MÁ, Hawkins BA.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-serneels2008}{}}%
+\CSLLeftMargin{53. }
+\CSLRightInline{Serneels S, Verdonck T. 2008 Principal component analysis for data containing outliers and missing elements. \emph{Computational Statistics \& Data Analysis} \textbf{52}, 1712--1727.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
 \CSLLeftMargin{54. }
-\CSLRightInline{Serneels S, Verdonck T. 2008 Principal component analysis for data containing outliers and missing elements. \emph{Computational Statistics \& Data Analysis} \textbf{52}, 1712--1727.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
+\CSLRightInline{Legendre P, Legendre L. 2012 \emph{Numerical ecology}. {2nd edn}. {Elsevier, Amsterdam}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
 \CSLLeftMargin{55. }
-\CSLRightInline{Legendre P, Legendre L. 2012 \emph{Numerical ecology}. {2nd edn}. {Elsevier, Amsterdam}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
-\CSLLeftMargin{56. }
 \CSLRightInline{Revell LJ.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
+\CSLLeftMargin{56. }
+\CSLRightInline{Abdi H, Williams LJ. 2010 Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459. (doi:\href{https://doi.org/10.1002/wics.101}{10.1002/wics.101})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
 \CSLLeftMargin{57. }
-\CSLRightInline{Abdi H, Williams LJ. 2010 Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459. (doi:\href{https://doi.org/10.1002/wics.101}{10.1002/wics.101})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
-\CSLLeftMargin{58. }
 \CSLRightInline{Ballantyne G, Baldock KCR, Willmer PG.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
-\CSLLeftMargin{59. }
+\CSLLeftMargin{58. }
 \CSLRightInline{Vázquez DP, Morris WF, Jordano P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
-\CSLLeftMargin{60. }
+\CSLLeftMargin{59. }
 \CSLRightInline{Vázquez DP, Lomáscolo SB, Maldonado MB, Chacoff NP, Dorado J, Stevani EL, Vitale NL.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
-\CSLLeftMargin{61. }
+\CSLLeftMargin{60. }
 \CSLRightInline{Hung K-LJ, Kingston JM, Albrecht M, Holway DA, Kohn JR.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
+\CSLLeftMargin{61. }
+\CSLRightInline{Bürkner P-C. 2017 Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.} \textbf{80}, 1--28.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
 \CSLLeftMargin{62. }
-\CSLRightInline{Bürkner P-C. 2017 Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.} \textbf{80}, 1--28.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
-\CSLLeftMargin{63. }
 \CSLRightInline{Gabry J, Simpson D, Vehtari A, Betancourt M, Gelman A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
+\CSLLeftMargin{63. }
+\CSLRightInline{Dormann CF, Gruber B, Fründ J. 2008 Introducing the bipartite package: Analysing ecological networks. \emph{R News} \textbf{8/2}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
 \CSLLeftMargin{64. }
-\CSLRightInline{Dormann CF, Gruber B, Fründ J. 2008 Introducing the bipartite package: Analysing ecological networks. \emph{R News} \textbf{8/2}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
-\CSLLeftMargin{65. }
 \CSLRightInline{Blüthgen N, Menzel F, Blüthgen N.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
-\CSLLeftMargin{66. }
+\CSLLeftMargin{65. }
 \CSLRightInline{Healy K, Ezard THG, Jones OR, Salguero-Gómez R, Buckley YM.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-worley2000}{}}%
-\CSLLeftMargin{67. }
+\CSLLeftMargin{66. }
 \CSLRightInline{Worley AC, Baker AM, Thompson JD, Barrett SC.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-petit2006}{}}%
+\CSLLeftMargin{67. }
+\CSLRightInline{Petit RJ, Hampe A. 2006 Some evolutionary consequences of being a tree. \emph{Annu. Rev. Ecol. Evol. Syst.} \textbf{37}, 187--214.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
 \CSLLeftMargin{68. }
-\CSLRightInline{Petit RJ, Hampe A. 2006 Some evolutionary consequences of being a tree. \emph{Annu. Rev. Ecol. Evol. Syst.} \textbf{37}, 187--214.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
+\CSLRightInline{Hegland SJ, Totland Ø. 2005 Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia} \textbf{145}, 586--594.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
 \CSLLeftMargin{69. }
-\CSLRightInline{Hegland SJ, Totland Ø. 2005 Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia} \textbf{145}, 586--594.}
+\CSLRightInline{Lázaro A, Jakobsson A, Totland Ø.
+2013 How do pollinator visitation rate and seed set relate to species' floral traits and community context?
+\emph{Oecologia} \textbf{173}, 881--893.
+(doi:\href{https://doi.org/10.1007/s00442-013-2652-5}{10.1007/s00442-013-2652-5})}
 
@@
 
-\textbf{Data accessibility.} All data and code used to conduct this study will is deposited at Zenodo
+\textbf{Data accessibility.} All data and code used to conduct this study is deposited at Zenodo
 

### 2022-06-23 Manuscript/Lanuza_et_al_2021.Rmd
manuscript update

@@
 Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@salguero2016; @friedman2020; @paterno2020; @roddy2021], their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
-Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other vegetative and physiological plant traits [@wright2004; @chave2009; @diaz2016; @onoda2017; @laughlin2021], there is a need to acquire a multitrait perspective with broad geographical coverage.
-Importantly, the characterization of the reproductive trait covariation patterns can help to further understand the different plant ecological strategies [@agrawal2020] and improve our knowledge on plant-pollinator associations [@roddy2021].
+Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other morphological and physiological plant traits [@wright2004; @chave2009; @diaz2016; @onoda2017; @laughlin2021], there is a need to acquire a multitrait perspective with broad geographical coverage.
+Importantly, the characterization of the reproductive spectrum can help to further understand the different plant ecological strategies [@agrawal2020] and improve our knowledge on plant-pollinator associations [@roddy2021].
 
@@
 Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
-Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network interactions [@eklof2013], an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns [see @dehling2016].
-Thus, by exploring the reproductive spectrum of trait variation is possible to delimit the different plant reproductive strategies and explore how these are associated with the different floral visitors.
+Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network of interactions [@eklof2013], an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns [see @dehling2016].
+Thus, by exploring the plant reproductive spectrum of trait variation is possible to delimit the different reproductive strategies and explore how these are associated with the different floral visitors.
 
@@
 However, most studies with a multitrait perspective have focused on trait correlations from the leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] related traits with little or no attention given to reproductive traits [@evojtko2020; @roddy2021].
-Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number [@sargent2007; @kettle2011], the positive association between flower size and outcrossing rate [@goodwillie2010] or the association between outcrossing rate and lifespan where short lived versus perennial species tend to have low versus high levels of outcrossing [@barrett2003; @moeller2017], respectively.
-Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships [@roddy2021], we still lack empirical evidence that investigates jointly these different reproductive trait associations.
-
-Here, we aim to progress knowledge on the reproductive trait covariation patterns and their association with the different floral visitor guilds by exploring at a broad geographical scale the reproductive spectrum of trait variation of entomophilous plant species from plant-pollination networks.
+Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number [@sargent2007; @kettle2011], the positive association between flower size and outcrossing rate [@goodwillie2010] or the positive association between outcrossing rate and lifespan [@barrett2003; @moeller2017].
+Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships [@roddy2021], we still lack empirical evidence that investigates jointly how these different reproductive trait associations shape plant life history strategies.
+
+Here, we aim to progress knowledge on the reproductive trait covariation patterns and their association with the different floral visitor guilds by exploring at a broad geographical scale the reproductive spectrum of trait variation of flowering plants from plant-pollination networks.
 First, we investigate what are the major axes of reproductive trait variation and trait correlations for the different plant species.
 Second, we investigate the association between the plant species' position in the multidimensional trait-space and the different floral visitor guilds with the help of qualitative (presence-absence of interaction) and quantitative (number of visits) information about plant-pollinator interactions.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
+Finally, we investigate how the main axes of trait variation influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
 
@@
 
-We selected a total of 19 different functional traits that comprised reproductive traits and plant form and size related traits (see table 1).
-From these, 16 were reproductive traits that consisted of 13 floral traits and 3 reproductive biology traits.
-Floral traits included traits related to the size of floral organs (e.g., style length), floral display (e.g., number of flowers) and floral rewards (e.g., pollen quantity).
-Reproductive biology traits indicated the reproductive system of the plant and included breeding, mating and compatibility system.
-The 3 remaining traits were plant size and form related traits that are commonly used to characterize the fast-slow continuum of plant trait variation (i.e., plant height, lifespan and life form).
+We selected a total of 19 different quantitative and categorical functional traits that comprised reproductive traits and plant form and size related traits (see table 1).
+Reproductive traits consisted of floral traits and reproductive biology traits: (i) floral traits included traits related to the size of floral organs (e.g., style length), floral display (e.g., flower number) or floral rewards (e.g., pollen quantity) while (ii) reproductive biology traits indicated the reproductive system of the plant (i.e., breeding, mating and compatibility system).
+The remaining traits were plant size and form related traits that are commonly used to characterize the fast-slow continuum of plant trait variation (i.e., plant height, lifespan and life form).
 For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
@@
 
-The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of the reproductive trait variation, respectively (figure 1 and figure S7).
+The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of the reproductive trait variation, respectively (figure 1 and figure S6).
 The first principal component (PC1 or the flower number - flower size axis) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
@@
 The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-For instance, on this side of the axis we find the species *Petunia axillaris* that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
+For instance, on this other end, we find the species *Petunia axillaris* that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
 The second principal component (PC2 or the pollinator dependence axis) represented 25.05% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
@@
 In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
-For instance, on this end of the spectrum we find the species *Veronica peregrina* which is a self-compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
+As an example of this reproductive extreme, we find the species *Veronica peregrina* which is a self-compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
 Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = |-0.51|) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
 The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; table S3).
-In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (figure S4).
+In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with floral display.
+Floral rewards were specially strongly correlated with flower size but slightly correlated with flower number (figure S4).
 This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (table S4).
@@
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (figure S8).
-Regarding self-compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility; figure S8a and figure S8b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S8c and figure S8d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S8e and figure S8f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S8g and figure S8h).
+In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (figure S7).
+Regarding self-compatibility, we found larger differences on PC2.
+For instance, species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility on this vertical axis (figure S7a and figure S7b).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S7c and figure S7d).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h).
 Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S8i and figure S8j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S8k and figure S8l).
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S7i and figure S7j).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S7k and figure S7l).
 
@@
 
-The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S10; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
+The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
 Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
-On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S10a).
-However, specialization showed the opposite trend on this axis (figure S10g).
-On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S10c).
-Again, specialization showed the opposite trend to number of visits (figure S10i).
+On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
+However, specialization showed the opposite trend on this axis (figure S9g).
+On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S9c).
+Again, specialization showed the opposite trend to number of visits (figure S9i).
 
@@
 
-This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
+This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that shape interactions with floral visitors at a global scale.
 Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50% and 70% of reproductive trait variation, respectively.
@@
 Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits [@diaz2016; @carmona2021], our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits [@salguero2016].
-Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
+Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
 However, they were insufficient to capture their visitation rates which highlight the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
 
-Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context.
-In addition, our work links the reproductive trait variation with the previously described fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-Although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
+Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and links the reproductive spectrum with the previously described fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
+For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
 We found support to this trait association and show that other life history traits also covariate along this axis.
-For example, our study complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
+Our study also complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
 Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral display.
-Thus, our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
+Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral displays.
+Our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
 
@@
 Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes.
-For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour [rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies.
+For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour [@rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies.
 In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive correlations do not.
 
-To conclude, we provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of plant reproductive traits from species that belong to plant-pollinator networks.
+To conclude, we provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of reproductive traits from plant species that belong to plant-pollinator networks.
 Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider other factors beyond plant reproductive strategies to better capture broad scale patterns of interactions with floral visitors.
-Our work provides empirical evidence that complements previous studies that have explored trait correlations with other plant organs and highlights the need to include these reproductive correlations in the global spectrum of plant form and function [@diaz2016] as reproductive strategies involve clear cost and benefits that can affect the trait space of the whole plant.
-Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and plant-pollinator associations.
+In addition, we provide empirical evidence that complements previous studies that have explored trait correlations with other plant organs and highlights the need to include these reproductive trait correlations in the global spectrum of plant form and function [@diaz2016], as the different plant reproductive strategies involve clear cost and benefits that can affect resource allocation to other morphological and physiological traits.
+Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and understanding of the different plant-pollinator associations.
 
@@
 
-**Funding.** This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2) and JBL was supported by a University of New England postgraduate scholarship.
+**Funding.** This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2) and JBL was supported by a University of New England IPRA postgraduate scholarship.
 
@@
 We also thank Jason Tylianakis for his comments on the manuscript before submission.
-Finally, JBL thanks the University of New England for the funding provided to carry out this work.
+Finally, we thank Marcos Méndez, Susan Kalisz, Amanda Benoit, May Berenbaum and an anonimous reviewer for thoughtful feedback and useful comments on earlier versions of this manuscript.

### 2022-06-23 Manuscript/Lanuza_et_al_2021.tex
manuscript update

@@
 Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits {[}\protect\hyperlink{ref-salguero2016}{7}--\protect\hyperlink{ref-roddy2021}{10}{]}, their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
-Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other vegetative and physiological plant traits {[}\protect\hyperlink{ref-wright2004}{11}--\protect\hyperlink{ref-laughlin2021}{15}{]}, there is a need to acquire a multitrait perspective with broad geographical coverage.
-Importantly, the characterization of the reproductive trait covariation patterns can help to further understand the different plant ecological strategies {[}\protect\hyperlink{ref-agrawal2020}{6}{]} and improve our knowledge on plant-pollinator associations {[}\protect\hyperlink{ref-roddy2021}{10}{]}.
+Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other morphological and physiological plant traits {[}\protect\hyperlink{ref-wright2004}{11}--\protect\hyperlink{ref-laughlin2021}{15}{]}, there is a need to acquire a multitrait perspective with broad geographical coverage.
+Importantly, the characterization of the reproductive spectrum can help to further understand the different plant ecological strategies {[}\protect\hyperlink{ref-agrawal2020}{6}{]} and improve our knowledge on plant-pollinator associations {[}\protect\hyperlink{ref-roddy2021}{10}{]}.
 
@@
 Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure {[}\protect\hyperlink{ref-stang2009}{26},\protect\hyperlink{ref-ibanez2012}{30}{]}.
-Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network interactions {[}\protect\hyperlink{ref-eklof2013}{31}{]}, an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns {[}see \protect\hyperlink{ref-dehling2016}{32}{]}.
-Thus, by exploring the reproductive spectrum of trait variation is possible to delimit the different plant reproductive strategies and explore how these are associated with the different floral visitors.
+Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network of interactions {[}\protect\hyperlink{ref-eklof2013}{31}{]}, an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns {[}see \protect\hyperlink{ref-dehling2016}{32}{]}.
+Thus, by exploring the plant reproductive spectrum of trait variation is possible to delimit the different reproductive strategies and explore how these are associated with the different floral visitors.
 
@@
 However, most studies with a multitrait perspective have focused on trait correlations from the leaf {[}\protect\hyperlink{ref-wright2004}{11}{]}, wood {[}\protect\hyperlink{ref-chave2009}{12}{]}, or root {[}\protect\hyperlink{ref-laughlin2021}{15}{]} related traits with little or no attention given to reproductive traits {[}\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-evojtko2020}{37}{]}.
-Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{38},\protect\hyperlink{ref-kettle2011}{39}{]}, the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{40}{]} or the association between outcrossing rate and lifespan where short lived versus perennial species tend to have low versus high levels of outcrossing {[}\protect\hyperlink{ref-moeller2017}{19},\protect\hyperlink{ref-barrett2003}{41}{]}, respectively.
-Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships {[}\protect\hyperlink{ref-roddy2021}{10}{]}, we still lack empirical evidence that investigates jointly these different reproductive trait associations.
-
-Here, we aim to progress knowledge on the reproductive trait covariation patterns and their association with the different floral visitor guilds by exploring at a broad geographical scale the reproductive spectrum of trait variation of entomophilous plant species from plant-pollination networks.
+Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{38},\protect\hyperlink{ref-kettle2011}{39}{]}, the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{40}{]} or the positive association between outcrossing rate and lifespan {[}\protect\hyperlink{ref-moeller2017}{19},\protect\hyperlink{ref-barrett2003}{41}{]}.
+Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships {[}\protect\hyperlink{ref-roddy2021}{10}{]}, we still lack empirical evidence that investigates jointly how these different reproductive trait associations shape plant life history strategies.
+
+Here, we aim to progress knowledge on the reproductive trait covariation patterns and their association with the different floral visitor guilds by exploring at a broad geographical scale the reproductive spectrum of trait variation of flowering plants from plant-pollination networks.
 First, we investigate what are the major axes of reproductive trait variation and trait correlations for the different plant species.
 Second, we investigate the association between the plant species' position in the multidimensional trait-space and the different floral visitor guilds with the help of qualitative (presence-absence of interaction) and quantitative (number of visits) information about plant-pollinator interactions.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
+Finally, we investigate how the main axes of trait variation influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
 
@@
 
-The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of the reproductive trait variation, respectively (figure 1 and figure S7).
+The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of the reproductive trait variation, respectively (figure 1 and figure S6).
 The first principal component (PC1 or the flower number - flower size axis) represented 26.72\% of the trait variation and indicated a negative correlation between flower number and flower size.
@@
 The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-For instance, on this side of the axis we find the species \emph{Petunia axillaris} that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
+For instance, on this other end, we find the species \emph{Petunia axillaris} that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
 The second principal component (PC2 or the pollinator dependence axis) represented 25.05\% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
@@
 In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
-For instance, on this end of the spectrum we find the species \emph{Veronica peregrina} which is a self-compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
+As an example of this reproductive extreme, we find the species \emph{Veronica peregrina} which is a self-compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
 Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17\%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \textbar-0.51\textbar) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
 The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; table S3).
-In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (figure S4).
+In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with floral display.
+Floral rewards were specially strongly correlated with flower size but slightly correlated with flower number (figure S4).
 This pPCA explained similar variance with the first two principal components (45.52\%) and similar associations of traits despite some variability in the loadings (table S4).
@@
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (figure S8).
-Regarding self-compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility; figure S8a and figure S8b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S8c and figure S8d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S8e and figure S8f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S8g and figure S8h).
+In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (figure S7).
+Regarding self-compatibility, we found larger differences on PC2.
+For instance, species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility on this vertical axis (figure S7a and figure S7b).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S7c and figure S7d).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h).
 Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S8i and figure S8j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S8k and figure S8l).
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S7i and figure S7j).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S7k and figure S7l).
 
@@
 
-The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S10; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
+The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
 Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
-On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S10a).
-However, specialization showed the opposite trend on this axis (figure S10g).
-On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S10c).
-Again, specialization showed the opposite trend to number of visits (figure S10i).
+On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
+However, specialization showed the opposite trend on this axis (figure S9g).
+On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S9c).
+Again, specialization showed the opposite trend to number of visits (figure S9i).
 
@@
 
-This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
+This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that shape interactions with floral visitors at a global scale.
 Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively.
@@
 Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{13},\protect\hyperlink{ref-carmona2021}{36}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
-Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
+Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
 However, they were insufficient to capture their visitation rates which highlight the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
 
-Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context.
-In addition, our work links the reproductive trait variation with the previously described fast-slow continuum' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{65}{]} life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-Although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{38},\protect\hyperlink{ref-kettle2011}{39},\protect\hyperlink{ref-worley2000}{66}{]}, it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
+Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and links the reproductive spectrum with the previously described fast-slow continuum' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{65}{]} life-history strategies, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
+For instance, although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{38},\protect\hyperlink{ref-kettle2011}{39},\protect\hyperlink{ref-worley2000}{66}{]}, it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
 We found support to this trait association and show that other life history traits also covariate along this axis.
-For example, our study complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{67}{]} by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
+Our study also complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{67}{]} by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
 Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{40}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral display.
-Thus, our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
+Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral displays.
+Our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
 
@@
 Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes.
-For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour {[}rader2020; {[}\protect\hyperlink{ref-foldesi2021}{71}{]}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{27},\protect\hyperlink{ref-vazquez2007}{72},\protect\hyperlink{ref-encinas2012}{73}{]} that reproductive correlations do not.
-
-To conclude, we provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of plant reproductive traits from species that belong to plant-pollinator networks.
+For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour {[}\protect\hyperlink{ref-rader2020}{71},\protect\hyperlink{ref-foldesi2021}{72}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{27},\protect\hyperlink{ref-vazquez2007}{73},\protect\hyperlink{ref-encinas2012}{74}{]} that reproductive correlations do not.
+
+To conclude, we provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of reproductive traits from plant species that belong to plant-pollinator networks.
 Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider other factors beyond plant reproductive strategies to better capture broad scale patterns of interactions with floral visitors.
-Our work provides empirical evidence that complements previous studies that have explored trait correlations with other plant organs and highlights the need to include these reproductive correlations in the global spectrum of plant form and function {[}\protect\hyperlink{ref-diaz2016}{13}{]} as reproductive strategies involve clear cost and benefits that can affect the trait space of the whole plant.
-Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and plant-pollinator associations.
+In addition, we provide empirical evidence that complements previous studies that have explored trait correlations with other plant organs and highlights the need to include these reproductive trait correlations in the global spectrum of plant form and function {[}\protect\hyperlink{ref-diaz2016}{13}{]}, as the different plant reproductive strategies involve clear cost and benefits that can affect resource allocation to other morphological and physiological traits.
+Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and understanding of the different plant-pollinator associations.
 
@@
 \CSLLeftMargin{5. }
-\CSLRightInline{Stearns SC. 1989 Trade-offs in life-history evolution. \emph{Functional ecology} \textbf{3}, 259--268.}
+\CSLRightInline{Stearns SC. 1989 Trade-offs in life-history evolution. \emph{Funct. Ecol.} \textbf{3}, 259--268. (doi:\href{https://doi.org/10.2307/2389364}{10.2307/2389364})}
 
@@
 \CSLLeftMargin{6. }
-\CSLRightInline{Agrawal AA. 2020 A scale-dependent framework for trade-offs, syndromes, and specialization in organismal biology. \emph{Ecology} \textbf{101}, e02924.}
+\CSLRightInline{Agrawal AA.
+2020 A scale-dependent framework for trade-offs, syndromes, and specialization in organismal biology.
+\emph{Ecology} \textbf{101}, e02924.
+(doi:\href{https://doi.org/10.1002/ecy.2924}{10.1002/ecy.2924})}
 
@@
 2020 The evolution of annual and perennial plant life histories: Ecological correlates and genetic mechanisms.
-\emph{Annual Review of Ecology, Evolution, and Systematics} \textbf{51}, 461--481.}
+\emph{Annu.
+Rev.
+Ecol.
+Evol.
+Syst.} \textbf{51}, 461--481.
+(doi:\href{https://doi.org/10.1146/annurev-ecolsys-110218-024638}{10.1146/annurev-ecolsys-110218-024638})}
 
@@
 2020 The maleness of larger angiosperm flowers.
-\emph{Proceedings of the National Academy of Sciences} \textbf{117}, 10921--10926.}
+\emph{Proc.
+Natl.
+Acad.
+Sci.} \textbf{117}, 10921--10926.
+(doi:\href{https://doi.org/10.1073/pnas.1910631117}{10.1073/pnas.1910631117})}
 
@@
 \CSLLeftMargin{12. }
-\CSLRightInline{Chave J, Coomes D, Jansen S, Lewis SL, Swenson NG, Zanne AE. 2009 Towards a worldwide wood economics spectrum. \emph{Ecol. Lett.} \textbf{12}, 351--366.}
+\CSLRightInline{Chave J, Coomes D, Jansen S, Lewis SL, Swenson NG, Zanne AE.
+2009 Towards a worldwide wood economics spectrum.
+\emph{Ecol.
+Lett.} \textbf{12}, 351--366.
+(doi:\href{https://doi.org/10.1111/j.1461-0248.2009.01285.x}{10.1111/j.1461-0248.2009.01285.x})}
 
@@
 2017 Physiological and structural tradeoffs underlying the leaf economics spectrum.
-\emph{New Phytologist} \textbf{214}, 1447--1463.}
+\emph{New Phytol.} \textbf{214}, 1447--1463.
+(doi:\href{https://doi.org/10.1111/nph.14496}{10.1111/nph.14496})}
 
@@
 Ecol.
-Evol.}, 1--12.}
+Evol.}, 1--12.
+(doi:\href{https://doi.org/10.1038/s41559-021-01471-7}{10.1038/s41559-021-01471-7})}
 
@@
 2016 Historical nectar assessment reveals the fall and rise of floral resources in britain.
-\emph{Nature} \textbf{530}, 85--88.}
+\emph{Nature} \textbf{530}, 85--88.
+(doi:\href{https://doi.org/10.1038/nature16532}{10.1038/nature16532})}
 
@@
 \CSLLeftMargin{18. }
-\CSLRightInline{Grossenbacher DL \emph{et al.} 2017 Self-compatibility is over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478.}
+\CSLRightInline{Grossenbacher DL \emph{et al.} 2017 Self-compatibility is over-represented on islands.
+\emph{New Phytol.} \textbf{215}, 469--478.
+(doi:\href{https://doi.org/10.1111/nph.14534}{10.1111/nph.14534})}
 
@@
 \CSLLeftMargin{20. }
-\CSLRightInline{Sargent RD, Ackerly DD. 2008 Plant--pollinator interactions and the assembly of plant communities. \emph{Trends Ecol. Evol.} \textbf{23}, 123--130.}
+\CSLRightInline{Sargent RD, Ackerly DD.
+2008 Plant--pollinator interactions and the assembly of plant communities.
+\emph{Trends Ecol.
+Evol.} \textbf{23}, 123--130.
+(doi:\href{https://doi.org/10.1016/j.tree.2007.11.003}{10.1016/j.tree.2007.11.003})}
 
@@
 \emph{Ecol.
-Lett.} \textbf{17}, 388--400.}
+Lett.} \textbf{17}, 388--400.
+(doi:\href{https://doi.org/10.1111/ele.12224}{10.1111/ele.12224})}
 
@@
 \CSLLeftMargin{31. }
-\CSLRightInline{Eklöf A \emph{et al.} 2013 The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583.}
+\CSLRightInline{Eklöf A \emph{et al.} 2013 The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583. (doi:\href{https://doi.org/10.1111/ele.12081}{10.1111/ele.12081})}
 
@@
 Royal Soc.
-B} \textbf{283}, 20152444.}
+B} \textbf{283}, 20152444.
+(doi:\href{https://doi.org/10.1098/rspb.2015.2444}{10.1098/rspb.2015.2444})}
 
@@
 \CSLLeftMargin{35. }
-\CSLRightInline{Bruelheide H \emph{et al.} 2018 Global trait--environment relationships of plant communities. \emph{Nat. Ecol. Evol.} \textbf{2}, 1906--1917.}
+\CSLRightInline{Bruelheide H \emph{et al.} 2018 Global trait--environment relationships of plant communities.
+\emph{Nat.
+Ecol.
+Evol.} \textbf{2}, 1906--1917.
+(doi:\href{https://doi.org/10.1038/s41559-018-0699-8}{10.1038/s41559-018-0699-8})}
 
@@
 \CSLLeftMargin{53. }
-\CSLRightInline{Serneels S, Verdonck T. 2008 Principal component analysis for data containing outliers and missing elements. \emph{Computational Statistics \& Data Analysis} \textbf{52}, 1712--1727.}
+\CSLRightInline{Serneels S, Verdonck T.
+2008 Principal component analysis for data containing outliers and missing elements.
+\emph{Comput.
+Stat.
+Data Anal.} \textbf{52}, 1712--1727.
+(doi:\href{https://doi.org/10.1016/j.csda.2007.05.024}{10.1016/j.csda.2007.05.024})}
 
@@
 Royal Soc.
-B} \textbf{285}, 20172140.}
+B} \textbf{285}, 20172140.
+(doi:\href{https://doi.org/10.1098/rspb.2017.2140}{10.1098/rspb.2017.2140})}
 
@@
 \CSLLeftMargin{61. }
-\CSLRightInline{Bürkner P-C. 2017 Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.} \textbf{80}, 1--28.}
+\CSLRightInline{Bürkner P-C.
+2017 Brms: {An R} package for {Bayesian} multilevel models using {Stan}.
+\emph{J.
+Stat.
+Softw.} \textbf{80}, 1--28.
+(doi:\href{https://doi.org/10.18637/jss.v080.i01}{10.18637/jss.v080.i01})}
 
@@
 2000 Floral display in narcissus: Variation in flower size and number at the species, population, and individual levels.
-\emph{International Journal of Plant Sciences} \textbf{161}, 69--79.}
+\emph{Int.
+J.
+Plant Sci.} \textbf{161}, 69--79.
+(doi:\href{https://doi.org/10.1086/314225}{10.1086/314225})}
 
@@
 \CSLLeftMargin{67. }
-\CSLRightInline{Petit RJ, Hampe A. 2006 Some evolutionary consequences of being a tree. \emph{Annu. Rev. Ecol. Evol. Syst.} \textbf{37}, 187--214.}
+\CSLRightInline{Petit RJ, Hampe A.
+2006 Some evolutionary consequences of being a tree.
+\emph{Annu.
+Rev.
+Ecol.
+Evol.
+Syst.} \textbf{37}, 187--214.
+(doi:\href{https://doi.org/10.1146/annurev.ecolsys.37.091305.110215}{10.1146/annurev.ecolsys.37.091305.110215})}
 
@@
 \CSLLeftMargin{68. }
-\CSLRightInline{Hegland SJ, Totland Ø. 2005 Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia} \textbf{145}, 586--594.}
+\CSLRightInline{Hegland SJ, Totland Ø.
+2005 Relationships between species' floral traits and pollinator visitation in a temperate grassland.
+\emph{Oecologia} \textbf{145}, 586--594.
+(doi:\href{https://doi.org/10.1007/s00442-005-0165-6}{10.1007/s00442-005-0165-6})}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-rader2020}{}}%
+\CSLLeftMargin{71. }
+\CSLRightInline{Rader R, Cunningham S, Howlett B, Inouye D.
+2020 Non-bee insects as visitors and pollinators of crops: Biology, ecology, and management.
+\emph{Annu.
+Rev.
+Entomol.} \textbf{65}, 391--407.
+(doi:\href{https://doi.org/10.1146/annurev-ento-011019-025055}{10.1146/annurev-ento-011019-025055})}
+
 \leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
-\CSLLeftMargin{71. }
+\CSLLeftMargin{72. }
 \CSLRightInline{Földesi R, Howlett BG, Grass I, Batáry P.
 2021 Larger pollinators deposit more pollen on stigmas across multiple plant species---a meta-analysis.
-\emph{Journal of Applied Ecology} \textbf{58}, 699--707.}
+\emph{J.
+Appl.
+Ecol.} \textbf{58}, 699--707.
+(doi:\href{https://doi.org/10.1111/1365-2664.13798}{10.1111/1365-2664.13798})}
 
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
-\CSLLeftMargin{72. }
+\CSLLeftMargin{73. }
 \CSLRightInline{Vázquez DP, Melián CJ, Williams NM, Blüthgen N, Krasnov BR, Poulin R.
 2007 Species abundance and asymmetric interaction strength in ecological networks.
-\emph{Oikos} \textbf{116}, 1120--1127.}
+\emph{Oikos} \textbf{116}, 1120--1127.
+(doi:\href{https://doi.org/10.1111/j.0030-1299.2007.15828.x}{10.1111/j.0030-1299.2007.15828.x})}
 
 \leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
-\CSLLeftMargin{73. }
-\CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS. 2012 Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.} \textbf{15}, 198--208.}
+\CSLLeftMargin{74. }
+\CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS.
+2012 Phenology drives mutualistic network structure and diversity.
+\emph{Ecol.
+Lett.} \textbf{15}, 198--208.
+(doi:\href{https://doi.org/10.1111/j.1461-0248.2011.01726.x}{10.1111/j.1461-0248.2011.01726.x})}
 
@@
 
-\textbf{Funding.} This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2) and JBL was supported by a University of New England postgraduate scholarship.
+\textbf{Funding.} This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2) and JBL was supported by a University of New England IPRA postgraduate scholarship.
 
@@
 We also thank Jason Tylianakis for his comments on the manuscript before submission.
-Finally, JBL thanks the University of New England for the funding provided to carry out this work.
+Finally, we thank Marcos Méndez, Susan Kalisz, Amanda Benoit, May Berenbaum and an anonimous reviewer for thoughtful feedback and useful comments on earlier versions of this manuscript.
 

### 2022-06-23 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021.Rmd
manuscript update

--- 2022-06-14 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
@@
 
-Figures S1 to S10
+Figures S1 to S9
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig.
-S6.} Regression tree analyses.
-Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
-"}
-
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
-########################################################################################################################################################
-#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
-
-library(rpart.plot)
-library(rpart)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
-nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
-d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")
-
-#run  regression trees of the 3 metrics
-set.seed(1)
-tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0054559,minbucket=50)
-
-set.seed(1)
-tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0084459,minbucket=50)
-
-set.seed(1)
-tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0072192 , minbucket=50) #10
-
-#NECTAR AND POLEN DATA
-v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
-nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
-d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
-
-#Set correct colnames for plotting
-colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-set.seed(2)
-tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
-
-set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
-
-set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)
-
-par(mfrow=c(3,2))
-
-rpart.plot(tree_1, box.palette="GnOr", main="A Interaction frequency for all species", cex.main=1.85,tweak = 1.10) 
-rpart.plot(tree1, box.palette="GnOr", main="B Interaction frequency for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-rpart.plot(tree_2, box.palette="GnOr", main="C Normalized degree for all species", cex.main=1.85,tweak = 1.10)
-rpart.plot(tree2, box.palette="GnOr", main="D Normalized degree for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-rpart.plot(tree_3, box.palette="GnOr", main="E Specialization for all species", cex.main=1.85,tweak = 1.10) 
-rpart.plot(tree3, box.palette="GnOr", main="F Specialization for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-```
-
 \newpage
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig.
-S7.} Phylogenetically informed principal component analysis (pPCA) for all plant species with the first (flower number - flower size axis) and third (style length - pollinator dependence axis) principal component that explained most trait variation."}
+S6.} Phylogenetically informed principal component analysis (pPCA) for all plant species with the first (flower number - flower size axis) and third (style length - pollinator dependence axis) principal component that explained most trait variation."}
 setwd("~/R_Projects/Reproductive Traits")
@@
 \thispagestyle{empty}
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig.
-S8.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species.
+S7.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species.
 Categories that differ significantly are denoted with a different letter."}
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Fig.
-S9.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation.
+S8.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation.
 Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S10.} Plant species level metrics across the three main axes of trait variation.", fig.pos= "h"}
+S9.} Plant species level metrics across the three main axes of trait variation.", fig.pos= "h"}
 

### 2022-06-23 Manuscript/Lanuza_et_al_2021.tex
manuscript update with orcid

@@
 \DeclareUnicodeCharacter{1EF3}{*************************************}
+\usepackage{orcidlink}
 \usepackage{float}
@@
 \textbf{Jose B.
-Lanuza$^{1,2}$} \href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}, \textbf{Romina Rader$^{1}$} \href{mailto:rrader@une.edu.au}{\nolinkurl{rrader@une.edu.au}}, \textbf{Jamie Stavert$^{3}$} \href{mailto:jamie.stavert@gmail.com}{\nolinkurl{jamie.stavert@gmail.com}}, \textbf{Liam K.
-Kendall$^{4}$} \href{mailto:liam.k.kendall@gmail.com}{\nolinkurl{liam.k.kendall@gmail.com}}, \textbf{Manu E.
-Saunders$^{1}$} \href{mailto:Manu.Saunders@une.edu.au}{\nolinkurl{Manu.Saunders@une.edu.au}} \textbf{and Ignasi Bartomeus$^{2}$} \href{mailto:nacho.bartomeus@gmail.com}{\nolinkurl{nacho.bartomeus@gmail.com}}
+Lanuza$^{1,2}$} \orcidlink{0000-0002-0287-409X}, \textbf{Romina Rader$^{1}$} \orcidlink{0000-0001-9056-9118}, \textbf{Jamie Stavert$^{3}$} \orcidlink{0000-0002-2103-5320}, \textbf{Liam K.
+Kendall$^{4}$} \orcidlink{0000-0002-0671-0121}, \textbf{Manu E.
+Saunders$^{1}$} \orcidlink{0000-0003-0645-8277}
+\textbf{and Ignasi Bartomeus$^{2}$}
+\orcidlink{0000-0001-7893-4389}
 
@@
 
-\textbf{Data accessibility.} All data and code used to conduct this study is deposited at Zenodo
+\textbf{Data accessibility.} All data and code used to conduct this study is available at Zenodo (\url{https://doi.org/10.5281/zenodo.6705621}) and Github (\url{https://github.com/JoseBSL/Reproductive-traits}).
 

### 2022-06-23 Manuscript/Lanuza_et_al_2022.Rmd
edits

--- 2022-06-23 Manuscript/Lanuza_et_al_2021.Rmd
@@
 - \DeclareUnicodeCharacter{1EF3}{*************************************}
+- \usepackage{orcidlink}
+
 ---
@@
 \textbf{Jose B.
-Lanuza$^{1,2}$} [barragansljose\@gmail.com](mailto:barragansljose@gmail.com){.email}, \textbf{Romina Rader$^{1}$} [rrader\@une.edu.au](mailto:rrader@une.edu.au){.email}, \textbf{Jamie Stavert$^{3}$} [jamie.stavert\@gmail.com](mailto:jamie.stavert@gmail.com){.email}, \textbf{Liam K.
-Kendall$^{4}$} [liam.k.kendall\@gmail.com](mailto:liam.k.kendall@gmail.com){.email}, \textbf{Manu E.
-Saunders$^{1}$} [Manu.Saunders\@une.edu.au](mailto:Manu.Saunders@une.edu.au){.email} \textbf{and Ignasi Bartomeus$^{2}$} [nacho.bartomeus\@gmail.com](mailto:nacho.bartomeus@gmail.com){.email}
+Lanuza$^{1,2}$} \orcidlink{0000-0002-0287-409X}, \textbf{Romina Rader$^{1}$} \orcidlink{0000-0001-9056-9118}, \textbf{Jamie Stavert$^{3}$} \orcidlink{0000-0002-2103-5320}, \textbf{Liam K.
+Kendall$^{4}$} \orcidlink{0000-0002-0671-0121}, \textbf{Manu E.
+Saunders$^{1}$} \orcidlink{0000-0003-0645-8277}
+\textbf{and Ignasi Bartomeus$^{2}$}
+\orcidlink{0000-0001-7893-4389}
 
@@
 
-**Data accessibility.** All data and code used to conduct this study is deposited at Zenodo
+**Data accessibility.** All data and code used to conduct this study is available at Zenodo (https://doi.org/10.5281/zenodo.6705621) and Github (https://github.com/JoseBSL/Reproductive-traits).
 

### 2022-06-26 Manuscript/Lanuza_et_al_2022.Rmd
Revision

@@
 However, there is strong evidence that there are evolutionary and physiological constraints that limit the number of plant ecological strategies.
-Despite recent advances in the understanding of plant trait variation, little is known about reproductive trait correlations and how these affect plant life-history strategies and shape interactions with floral visitors.
-Here, we investigate the reproductive spectrum of flowering plants and how this drive interactions with floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
+Despite recent advances in the understanding of the plant trait variation spectrum, reproductive traits are often not considered despite its key role in shaping both plant life-history strategies and plants interactions with floral visitors.
+Here, we investigate the reproductive spectrum of flowering plants and how this drive the establishment of interactions with their floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
 We found that over 50% and 70% of all trait variation was explained by the first two and three reproductive axes, respectively.
@@
 These different reproductive axes determined important differences in the interaction level among floral visitor guilds but were insufficient to fully capture plant-pollinator associations.
-Our study shows the major reproductive trait correlations and highlights their relevance to understand plant-pollinator interactions in a global context.
+Our study shows the general reproductive trait correlations observed and highlights their relevance to understand plant-pollinator interactions in a global context.
 
@@
 
-Flowering plants have an astonishing diversity of floral structures [@barrett2002; @schiestl2013] that shape plant-pollinator associations [@fenster2004; @dellinger2020].
+Flowering plants have an astonishing diversity of floral structures [@barrett2002; @schiestl2013] that shape their interactions with animal pollinators [@fenster2004; @dellinger2020].
+The variety of reproductive strategies followed by different plant species, from specialized reliance on a single pollinator, to full self-pollination, is incredibly rich.
 However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
-Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@salguero2016; @friedman2020; @paterno2020; @roddy2021], their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
-Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other morphological and physiological plant traits [@wright2004; @chave2009; @diaz2016; @onoda2017; @laughlin2021], there is a need to acquire a multitrait perspective with broad geographical coverage.
+Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@salguero2016; @friedman2020; @paterno2020; @roddy2021], their study is often limited to a limited number of reproductive traits that are rarely studied in combination.
+Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other morphological and physiological plant traits such as roots (REF) or leafs (REF) Etc..
+[@wright2004; @chave2009; @diaz2016; @onoda2017; @laughlin2021], there is a need to acquire a multitrait perspective with broad geographical coverage.
 Importantly, the characterization of the reproductive spectrum can help to further understand the different plant ecological strategies [@agrawal2020] and improve our knowledge on plant-pollinator associations [@roddy2021].
-
-Although there is an increasing number of macroecological studies that investigate plant reproductive traits [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017], we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
-In addition, the pollination system of a great number of plant species remains unexplored and is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations [@tur2013; @devaux2014].
-Interestingly, the use of trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-For example, plant traits can define species' network roles [e.g., specialists vs generalists @tur2013] and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
-Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
-Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network of interactions [@eklof2013], an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns [see @dehling2016].
-Thus, by exploring the plant reproductive spectrum of trait variation is possible to delimit the different reproductive strategies and explore how these are associated with the different floral visitors.
 
@@
 Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships [@roddy2021], we still lack empirical evidence that investigates jointly how these different reproductive trait associations shape plant life history strategies.
+
+Despite this increasing number of macroecological studies that investigate some plant reproductive traits [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017], we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
+The use of trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
+For example, plant traits can define species' network roles [e.g., specialists vs generalists @tur2013] and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
+Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
+However, is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations [@tur2013; @devaux2014].
+Indeed, the pollination system of a great number of plant species remains unexplored.
+Because both the species' morphology and  mating system can determine the species' functional role in the pollination network and a combination of traits has shown to increase the predictive [predictive whith respect to what??
+what do you want to predict?]() power of the network of interactions [@eklof2013], an interesting novel approach is to investigate how a complete set of reproductive traits in the multidimensional trait space determine species interaction patterns [see @dehling2016 for a morphological approach].
+Thus, by exploring the plant reproductive spectrum of trait variation is possible to delimit the different reproductive strategies and explore how these are associated with the different floral visitors.
 
@@
 An extended description of each trait and how it was obtained can be found in Appendix S1.
+
+[Table 1 has a 10^3 which should be 1000]()
 
@@
 We conducted two different imputations, one for the full set of species (1,506 species, 5.79% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (figure S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without missing values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
+To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
 
@@
 Due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as indicated for principal component analysis [@legendre2012].
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as recomended for principal component analysis [@legendre2012].
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
@@
 Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency [@ballantyne2015], the number of visits can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
-Second, we investigated how the main axes of trait variation and individual traits influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below 'plant species network roles' section).
+[Yo aqui meteria los analysis bayesianos.
+AHora me parece que rompee el flujo]() Second, we investigated how the main axes of trait variation and individual traits influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below 'plant species network roles' section).
+[Y aqui su analsys]()
 
@@
 In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
+Sampling methods varied across networks [or studies?]() but this was accounted for in analyses by considering them in the random effects of the modelling process (see below).
 All analyses were conducted in R version *4.0.3*.
+[Y esto es un gran cierre d emetodos]()
 
@@
 
-We found (with an Anova) that most categorical traits were statistically associated with the first two axes of trait variation (figure 2 and table S2).
+We found that most categorical traits were statistically associated with the first two axes of trait variation (figure 2 and table S2).
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (figure S7).
+In addition, we found statistical differences between the different levels of categorical traits in the trait space (figure S7).
 Regarding self-compatibility, we found larger differences on PC2.
-For instance, species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility on this vertical axis (figure S7a and figure S7b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S7c and figure S7d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h).
+For instance, species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility on this vertical axis (figure S7a and figure S7b; Tukey test *P* < 0.05).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S7c and figure S7d; Tukey test *P* < 0.05).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f; Tukey test *P* < 0.05).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h; Tukey test *P* < 0.05).
 Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S7i and figure S7j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S7k and figure S7l).
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S7i and figure S7j; Tukey test *P* < 0.05).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S7k and figure S7l; Tukey test *P* < 0.05).
 
@@
 ## (c) Visitation patterns 
+[asegurate que cuadran los subtitulos de metodos con esto si los modificas]()
 
@@
 We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (figure 3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
-Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number but small (figure 3d).
+Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high number of small flowers (figure 3d).
 On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (figure 3b and figure 3e).
 Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (figure 3c).
-However, regarding number of visits on the style length - pollinator dependence axis, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (figure 3f).
-
-The additional model for both presence-absence of interaction (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
+Plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (figure 3f).
+
+The additional model for the most represented families of bees for both presence-absence of interaction (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) showed that the family Apidae was the main driver of the observed patterns.
 The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (figure 3a and figure 3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (figure S9).
@@
 Again, specialization showed the opposite trend to number of visits (figure S9i).
+[crees que podemos meter una figura de este resultado en main text?
+Si no esta ahi, no lo va a ver nadie]()
 
@@
 
-This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that shape interactions with floral visitors at a global scale.
+The reproductive spectrum of flowering plants show clear positive and negative covariations between reproductive traits that shape the interactions of angiosperms with their floral visitors at a global scale.
 Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50% and 70% of reproductive trait variation, respectively.
-These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
+These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence [que opinas de que pol dep salga en dos ejes?
+No es raro?]().
 Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits [@diaz2016; @carmona2021], our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits [@salguero2016].
-Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
-However, they were insufficient to capture their visitation rates which highlight the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
-
-Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and links the reproductive spectrum with the previously described fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
-For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
+Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds.
+However, they were insufficient to capture the visitation rates, which highlight the need to account for other local factors, such as local relative abuncances [REF?
+a malas mi Fun Ecol de 2016](), to better capture the strength of these mutualistic interactions at a macroecological scale.
+
+We provide solid evidence for the generality of several hypothesized trait associations across a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and linked the reproductive spectrum with previously described fast-slow continuum' life-history strategies in plants [@salguero2016] and animals [@healy2019], as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
+For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a pair-wise trait approach.
 We found support to this trait association and show that other life history traits also covariate along this axis.
-Our study also complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
+Our study also complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers [are concentrated in the trait space](no pillo esto) and are associated with woody life forms with high flower number.
 Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
@@
 
-Overall, our models showed that the main plant reproductive trait correlations have low predictive power for broad-level interaction patterns between plants and floral visitors.
-However, we found changes in the interaction patterns among and within floral visitor guilds that suggest that plant reproductive strategies partly mediate these associations at large ecological scales.
-For example, we found that all floral visitor guilds interacted more frequently with plant species with larger floral displays in agreement with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
-Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes.
-For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour [@rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies.
+Overall, plant reproductive trait covariation axes help explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales.
+For example, as predicted by [evolutionary?
+life-history?]() theory, larger investments floral size and rewards to attract pollinators makes sense when pollinator dependence is higher, but this might trade off with the resources allocated to ovule production [mirate la literatura de esto...
+seguro que hay papers.
+Además, si esto que digo l apoyan los datos, puede ser algo que la gente querra citar (YO QUIEREO!) asi que dejalo explicito](Anne Leonard tenia algo de eso, creo).
+Interestingly, by combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings [@hegland2005; @lazaro2013; @kaiser2014].
+Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes [ref, van der pijl, como clasico, no?
+Ollerton tiene cosas recientes]().
+For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies [name which ones]() and because these two guilds are likely to differ in ecology and behaviour [@rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies.
 In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive correlations do not.
 
-To conclude, we provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of reproductive traits from plant species that belong to plant-pollinator networks.
-Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider other factors beyond plant reproductive strategies to better capture broad scale patterns of interactions with floral visitors.
-In addition, we provide empirical evidence that complements previous studies that have explored trait correlations with other plant organs and highlights the need to include these reproductive trait correlations in the global spectrum of plant form and function [@diaz2016], as the different plant reproductive strategies involve clear cost and benefits that can affect resource allocation to other morphological and physiological traits.
+We provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of reproductive traits from plant species that belong to plant-pollinator networks.
+Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider factors such as plant reproductive strategies, and not only flower morphology, to better capture broad scale patterns of interactions with floral visitors.
+In addition, we provide empirical evidence that complements previous trait correlation studies along other plant organs and highlights the need to include reproductive trait correlations in the global spectrum of plant form and function [@diaz2016], as the different plant reproductive strategies involve clear cost and benefits that can affect resource allocation to other morphological and physiological traits.
 Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and understanding of the different plant-pollinator associations.
+
+[Me falta un parrafo de por que esto es importante o que puede hacer la gente con esto.
+Seria el penultimo parrafo, por ejemplo, como afecta esto a la gente haciendo coexistencia (e.g.
+el paper de Pauw y el tuyo).
+Como afecta esto a la gente hacienco estabilidad y estructura de polinizadores.
+Como afecta esto a ecologos evolutivos?]()
 

### 2022-06-28 Manuscript/Lanuza_et_al_2022.Rmd
edits

@@
 However, there is strong evidence that there are evolutionary and physiological constraints that limit the number of plant ecological strategies.
-Despite recent advances in the understanding of the plant trait variation spectrum, reproductive traits are often not considered despite its key role in shaping both plant life-history strategies and plants interactions with floral visitors.
+Despite recent advances in the understanding of plant trait correlations, reproductive traits are often not considered despite its key role in shaping both plant life-history strategies and plants interactions with floral visitors.
 Here, we investigate the reproductive spectrum of flowering plants and how this drive the establishment of interactions with their floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
-We found that over 50% and 70% of all trait variation was explained by the first two and three reproductive axes, respectively.
-Specifically, the first axis indicated the presence of a negative correlation between flower number and flower size; the second axis showed a positive correlation between pollinator dependence and floral display; and the third axis indicated a negative correlation between style length and pollinator dependence.
+We found that over 50% of all trait variation was explained by the first two reproductive axes.
+Specifically, the first axis indicated the presence of a negative correlation between flower number and flower size while the second axis showed a positive correlation between pollinator dependence and floral display.
 These different reproductive axes determined important differences in the interaction level among floral visitor guilds but were insufficient to fully capture plant-pollinator associations.
-Our study shows the general reproductive trait correlations observed and highlights their relevance to understand plant-pollinator interactions in a global context.
+Our study shows the main reproductive trait correlations of flowering plants and highlights their relevance to understand plant-pollinator interactions in a global context.
 
@@
 However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
-Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@salguero2016; @friedman2020; @paterno2020; @roddy2021], their study is often limited to a limited number of reproductive traits that are rarely studied in combination.
-Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other morphological and physiological plant traits such as roots (REF) or leafs (REF) Etc..
-[@wright2004; @chave2009; @diaz2016; @onoda2017; @laughlin2021], there is a need to acquire a multitrait perspective with broad geographical coverage.
-Importantly, the characterization of the reproductive spectrum can help to further understand the different plant ecological strategies [@agrawal2020] and improve our knowledge on plant-pollinator associations [@roddy2021].
+Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@salguero2016; @friedman2020; @paterno2020; @roddy2021], their study is often limited to a few number of reproductive traits that are rarely studied in combination.
+Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other root [@laughlin2021], leaf [@wright2004] or wood [@chave2009] related traits, there is a need to acquire a multitrait perspective with broad geographical coverage.
+Importantly, the characterization of the plant reproductive spectrum can help to further understand the different plant ecological strategies [@agrawal2020] and improve our knowledge on plant-pollinator associations [@roddy2021].
 
 With the recent availability of large trait databases [e.g., TRY @kattge2011;\ COMPADRE @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
-However, most studies with a multitrait perspective have focused on trait correlations from the leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] related traits with little or no attention given to reproductive traits [@evojtko2020; @roddy2021].
+However, most studies with a multitrait perspective have overlooked plant reproductive traits [@evojtko2020; @roddy2021] and focused on trait correlations from other plant organs.
 Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number [@sargent2007; @kettle2011], the positive association between flower size and outcrossing rate [@goodwillie2010] or the positive association between outcrossing rate and lifespan [@barrett2003; @moeller2017].
@@
 
-Despite this increasing number of macroecological studies that investigate some plant reproductive traits [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017], we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
+Despite this increasing number of macroecological studies that investigate specific plant reproductive traits [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017], we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
 The use of trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
@@
 However, is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations [@tur2013; @devaux2014].
-Indeed, the pollination system of a great number of plant species remains unexplored.
-Because both the species' morphology and  mating system can determine the species' functional role in the pollination network and a combination of traits has shown to increase the predictive [predictive whith respect to what??
-what do you want to predict?]() power of the network of interactions [@eklof2013], an interesting novel approach is to investigate how a complete set of reproductive traits in the multidimensional trait space determine species interaction patterns [see @dehling2016 for a morphological approach].
+Indeed, the pollination system of a great number of plant species remains unexplored [@dellinger2020].
+Because both the species' morphology and mating system can determine the species' functional role in the pollination network and the combination of several traits has shown to increase the predictive power of the structure of ecological networks [@eklof2013], an interesting novel approach is to investigate how a complete set of reproductive traits in the multidimensional trait space determine species interaction patterns [see @dehling2016 for a morphological approach].
 Thus, by exploring the plant reproductive spectrum of trait variation is possible to delimit the different reproductive strategies and explore how these are associated with the different floral visitors.
@@
 An extended description of each trait and how it was obtained can be found in Appendix S1.
-
-[Table 1 has a 10^3 which should be 1000]()
 
@@
 
-T.range <- c("0.01-30m", "0.50-205mm", "0.20-195mm", "0.80-300mm", "0-138mm", "1-25 x $10^3$", "1-18 x $10^4$", "0-160$\\mu$l", "0-6.1mg", "0-100$\\%$", "13-2 x $10^8$", "0-100$\\%$")
+T.range <- c("0.01-30m", "0.50-205mm", "0.20-195mm", "0.80-300mm", "0-138mm", "1-25000", "1-1.8 x $10^5$", "0-160$\\mu$l", "0-6.1mg", "0-100$\\%$", "13-2 x $10^8$", "0-100$\\%$")
 
@@
 
-First, we investigated how the different groups of floral visitors interacted along the main axes of reproductive trait variation (see below 'visitation patterns' section) with the help of qualitative and quantitative information of plant-pollinator interactions.
+### (i) Visitation patterns
+
+First, we used Bayesian modelling (see below for details) to investigate how the different groups of floral visitors interacted along the main axes of reproductive trait variation with the help of qualitative and quantitative information of plant-pollinator interactions.
 For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
 Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency [@ballantyne2015], the number of visits can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
-[Yo aqui meteria los analysis bayesianos.
-AHora me parece que rompee el flujo]() Second, we investigated how the main axes of trait variation and individual traits influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below 'plant species network roles' section).
-[Y aqui su analsys]()
-
-Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across networks [or studies?]() but this was accounted for in analyses by considering them in the random effects of the modelling process (see below).
-All analyses were conducted in R version *4.0.3*.
-[Y esto es un gran cierre d emetodos]()
-
-### (i) Visitation patterns
-
-We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species.
 For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
@@
 
-We investigated whether different quantitative traits determined different plant species' functional roles in the pollination network using Bayesian modelling.
+Second, we investigated with Bayesian modelling how the main axes of trait variation determined different plant species' functional roles in the pollination network.
 For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+The different plant species-level metrics that summarize species' functional roles were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
 Normalized degree and specialization were calculated with the *specieslevel* function from the R package *bipartite* [@dormann2008].
-
 We modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
@@
 Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the 'visitation patterns' section.
+
+Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
+Sampling methods varied across studies but this was accounted for in analyses by considering them in the random effects of the modelling process.
+All analyses were conducted in R version *4.0.3*.
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="95%", fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="85%", fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
 The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
@@
 ## (c) Visitation patterns
-[asegurate que cuadran los subtitulos de metodos con esto si los modificas]()
 
@@
 The additional model for the most represented families of bees for both presence-absence of interaction (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (figure 3a and figure 3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (figure S9).
+The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (figure 3a and figure 3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (figure S8).
 
@@
 
-The reproductive spectrum of flowering plants show clear positive and negative covariations between reproductive traits that shape the interactions of angiosperms with their floral visitors at a global scale.
+The reproductive spectrum of flowering plants show clear positive and negative covariations between reproductive traits that shape the interactions of Angiosperms with their floral visitors at a global scale.
 Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50% and 70% of reproductive trait variation, respectively.
@@
 Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds.
-However, they were insufficient to capture the visitation rates, which highlight the need to account for other local factors, such as local relative abuncances [REF?
-a malas mi Fun Ecol de 2016](), to better capture the strength of these mutualistic interactions at a macroecological scale.
+However, they were insufficient to capture the visitation rates, which highlight the need to account for other local factors, such as local relative abuncances [@bartomeus2016], to better capture the strength of these mutualistic interactions at a macroecological scale.
 

### 2022-06-28 Manuscript/Lanuza_et_al_2022.tex
edits

--- 2022-06-23 Manuscript/Lanuza_et_al_2021.tex
@@
 However, there is strong evidence that there are evolutionary and physiological constraints that limit the number of plant ecological strategies.
-Despite recent advances in the understanding of plant trait variation, little is known about reproductive trait correlations and how these affect plant life-history strategies and shape interactions with floral visitors.
-Here, we investigate the reproductive spectrum of flowering plants and how this drive interactions with floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
-We found that over 50\% and 70\% of all trait variation was explained by the first two and three reproductive axes, respectively.
-Specifically, the first axis indicated the presence of a negative correlation between flower number and flower size; the second axis showed a positive correlation between pollinator dependence and floral display; and the third axis indicated a negative correlation between style length and pollinator dependence.
+Despite recent advances in the understanding of plant trait correlations, reproductive traits are often not considered despite its key role in shaping both plant life-history strategies and plants interactions with floral visitors.
+Here, we investigate the reproductive spectrum of flowering plants and how this drive the establishment of interactions with their floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
+We found that over 50\% of all trait variation was explained by the first two reproductive axes.
+Specifically, the first axis indicated the presence of a negative correlation between flower number and flower size while the second axis showed a positive correlation between pollinator dependence and floral display.
 These different reproductive axes determined important differences in the interaction level among floral visitor guilds but were insufficient to fully capture plant-pollinator associations.
-Our study shows the major reproductive trait correlations and highlights their relevance to understand plant-pollinator interactions in a global context.
+Our study shows the main reproductive trait correlations of flowering plants and highlights their relevance to understand plant-pollinator interactions in a global context.
 
@@
 
-Flowering plants have an astonishing diversity of floral structures {[}\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}{]} that shape plant-pollinator associations {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}{]}.
+Flowering plants have an astonishing diversity of floral structures {[}\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}{]} that shape their interactions with animal pollinators {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}{]}.
+The variety of reproductive strategies followed by different plant species, from specialized reliance on a single pollinator, to full self-pollination, is incredibly rich.
 However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints {[}\protect\hyperlink{ref-stearns1989}{5},\protect\hyperlink{ref-agrawal2020}{6}{]}.
-Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits {[}\protect\hyperlink{ref-salguero2016}{7}--\protect\hyperlink{ref-roddy2021}{10}{]}, their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
-Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other morphological and physiological plant traits {[}\protect\hyperlink{ref-wright2004}{11}--\protect\hyperlink{ref-laughlin2021}{15}{]}, there is a need to acquire a multitrait perspective with broad geographical coverage.
-Importantly, the characterization of the reproductive spectrum can help to further understand the different plant ecological strategies {[}\protect\hyperlink{ref-agrawal2020}{6}{]} and improve our knowledge on plant-pollinator associations {[}\protect\hyperlink{ref-roddy2021}{10}{]}.
-
-Although there is an increasing number of macroecological studies that investigate plant reproductive traits {[}\protect\hyperlink{ref-baude2016}{16}--\protect\hyperlink{ref-moeller2017}{19}{]}, we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-sargent2008}{20}--\protect\hyperlink{ref-ruger2018}{22}{]}.
-In addition, the pollination system of a great number of plant species remains unexplored and is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations {[}\protect\hyperlink{ref-tur2013}{23},\protect\hyperlink{ref-devaux2014}{24}{]}.
-Interestingly, the use of trait-based approaches {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{25}{]} and trait-matching analyses {[}\protect\hyperlink{ref-stang2009}{26},\protect\hyperlink{ref-bartomeus2016}{27}{]} has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-For example, plant traits can define species' network roles {[}e.g., specialists vs generalists \protect\hyperlink{ref-tur2013}{23}{]} and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators {[}\protect\hyperlink{ref-junker2013}{28},\protect\hyperlink{ref-coux2016}{29}{]}.
-Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure {[}\protect\hyperlink{ref-stang2009}{26},\protect\hyperlink{ref-ibanez2012}{30}{]}.
-Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network of interactions {[}\protect\hyperlink{ref-eklof2013}{31}{]}, an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns {[}see \protect\hyperlink{ref-dehling2016}{32}{]}.
+Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits {[}\protect\hyperlink{ref-salguero2016}{7}--\protect\hyperlink{ref-roddy2021}{10}{]}, their study is often limited to a few number of reproductive traits that are rarely studied in combination.
+Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other root {[}\protect\hyperlink{ref-laughlin2021}{11}{]}, leaf {[}\protect\hyperlink{ref-wright2004}{12}{]} or wood {[}\protect\hyperlink{ref-chave2009}{13}{]} related traits, there is a need to acquire a multitrait perspective with broad geographical coverage.
+Importantly, the characterization of the plant reproductive spectrum can help to further understand the different plant ecological strategies {[}\protect\hyperlink{ref-agrawal2020}{6}{]} and improve our knowledge on plant-pollinator associations {[}\protect\hyperlink{ref-roddy2021}{10}{]}.
+
+With the recent availability of large trait databases {[}e.g., TRY \protect\hyperlink{ref-kattge2011}{14},~COMPADRE \protect\hyperlink{ref-salguero2015}{15}{]}, plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-diaz2016}{16}--\protect\hyperlink{ref-carmona2021}{18}{]}.
+However, most studies with a multitrait perspective have overlooked plant reproductive traits {[}\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-evojtko2020}{19}{]} and focused on trait correlations from other plant organs.
+Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{20},\protect\hyperlink{ref-kettle2011}{21}{]}, the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{22}{]} or the positive association between outcrossing rate and lifespan {[}\protect\hyperlink{ref-barrett2003}{23},\protect\hyperlink{ref-moeller2017}{24}{]}.
+Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships {[}\protect\hyperlink{ref-roddy2021}{10}{]}, we still lack empirical evidence that investigates jointly how these different reproductive trait associations shape plant life history strategies.
+
+Despite this increasing number of macroecological studies that investigate specific plant reproductive traits {[}\protect\hyperlink{ref-moeller2017}{24}--\protect\hyperlink{ref-grossenbacher2017}{27}{]}, we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-sargent2008}{28}--\protect\hyperlink{ref-ruger2018}{30}{]}.
+The use of trait-based approaches {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{31}{]} and trait-matching analyses {[}\protect\hyperlink{ref-stang2009}{32},\protect\hyperlink{ref-bartomeus2016}{33}{]} has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
+For example, plant traits can define species' network roles {[}e.g., specialists vs generalists \protect\hyperlink{ref-tur2013}{34}{]} and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators {[}\protect\hyperlink{ref-junker2013}{35},\protect\hyperlink{ref-coux2016}{36}{]}.
+Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure {[}\protect\hyperlink{ref-stang2009}{32},\protect\hyperlink{ref-ibanez2012}{37}{]}.
+However, is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations {[}\protect\hyperlink{ref-tur2013}{34},\protect\hyperlink{ref-devaux2014}{38}{]}.
+Indeed, the pollination system of a great number of plant species remains unexplored {[}\protect\hyperlink{ref-dellinger2020}{4}{]}.
+Because both the species' morphology and mating system can determine the species' functional role in the pollination network and the combination of several traits has shown to increase the predictive power of the structure of ecological networks {[}\protect\hyperlink{ref-eklof2013}{39}{]}, an interesting novel approach is to investigate how a complete set of reproductive traits in the multidimensional trait space determine species interaction patterns {[}see \protect\hyperlink{ref-dehling2016}{40} for a morphological approach{]}.
 Thus, by exploring the plant reproductive spectrum of trait variation is possible to delimit the different reproductive strategies and explore how these are associated with the different floral visitors.
-
-With the recent availability of large trait databases {[}e.g., TRY \protect\hyperlink{ref-kattge2011}{33},~COMPADRE \protect\hyperlink{ref-salguero2015}{34}{]}, plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-diaz2016}{13},\protect\hyperlink{ref-bruelheide2018}{35},\protect\hyperlink{ref-carmona2021}{36}{]}.
-However, most studies with a multitrait perspective have focused on trait correlations from the leaf {[}\protect\hyperlink{ref-wright2004}{11}{]}, wood {[}\protect\hyperlink{ref-chave2009}{12}{]}, or root {[}\protect\hyperlink{ref-laughlin2021}{15}{]} related traits with little or no attention given to reproductive traits {[}\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-evojtko2020}{37}{]}.
-Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{38},\protect\hyperlink{ref-kettle2011}{39}{]}, the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{40}{]} or the positive association between outcrossing rate and lifespan {[}\protect\hyperlink{ref-moeller2017}{19},\protect\hyperlink{ref-barrett2003}{41}{]}.
-Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships {[}\protect\hyperlink{ref-roddy2021}{10}{]}, we still lack empirical evidence that investigates jointly how these different reproductive trait associations shape plant life history strategies.
 
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies {[}e.g., \protect\hyperlink{ref-carvalheiro2014}{42},\protect\hyperlink{ref-olesen2007}{43},\protect\hyperlink{ref-fortuna2010}{44}{]} or available in online archives {[}e.g., Mangal \protect\hyperlink{ref-poisot2016}{45},~The Web of Life \protect\hyperlink{ref-fortuna2010}{44}{]}.
+Many of these networks are freely available either as published studies {[}e.g., \protect\hyperlink{ref-carvalheiro2014}{41},\protect\hyperlink{ref-olesen2007}{42},\protect\hyperlink{ref-fortuna2010}{43}{]} or available in online archives {[}e.g., Mangal \protect\hyperlink{ref-poisot2016}{44},~The Web of Life \protect\hyperlink{ref-fortuna2010}{43}{]}.
 In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
@@
 
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} {[}\protect\hyperlink{ref-chamberlain2020}{46}{]}.
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} {[}\protect\hyperlink{ref-chamberlain2020}{45}{]}.
 We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
@@
 \hspace{1em}Style length & 0-138mm\\
-\hspace{1em}Ovules per flower & 1-25 x $10^3$\\
-\hspace{1em}Flowers per plant & 1-18 x $10^4$\\
+\hspace{1em}Ovules per flower & 1-25000\\
+\hspace{1em}Flowers per plant & 1-1.8 x $10^5$\\
 \hspace{1em}Microliters of nectar & 0-160$\mu$l\\
@@
 
-We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{47},\protect\hyperlink{ref-jin2019}{48}{]}.
+We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{46},\protect\hyperlink{ref-jin2019}{47}{]}.
 
@@
 
-To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{49}{]} which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{50}{]}.
-To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} {[}\protect\hyperlink{ref-santos2018}{51}{]} based on a previous conceptual framework that considers phylogenetic eigenvectors {[}\protect\hyperlink{ref-diniz-filho2012}{52}{]}.
+To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{48}{]} which allows imputation of datasets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{49}{]}.
+To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} {[}\protect\hyperlink{ref-santos2018}{50}{]} based on a previous conceptual framework that considers phylogenetic eigenvectors {[}\protect\hyperlink{ref-diniz-filho2012}{51}{]}.
 We conducted two different imputations, one for the full set of species (1,506 species, 5.79\% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (figure S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01\% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without missing values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
+To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
 
@@
 Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{53},\protect\hyperlink{ref-legendre2012}{54}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as indicated for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{54}{]}.
+Due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{52},\protect\hyperlink{ref-legendre2012}{53}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as recomended for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{53}{]}.
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{55}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{56}{]}.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{54}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{55}{]}.
 Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
@@
 
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{55}{]} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{54}{]} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
@@
 
-First, we investigated how the different groups of floral visitors interacted along the main axes of reproductive trait variation (see below `visitation patterns' section) with the help of qualitative and quantitative information of plant-pollinator interactions.
-For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency {[}\protect\hyperlink{ref-ballantyne2015}{57}{]}, the number of visits can provide valuable information of the contribution of floral visitors to pollination {[}\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}{]}.
-Second, we investigated how the main axes of trait variation and individual traits influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below `plant species network roles' section).
-
-Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
-All analyses were conducted in R version \emph{4.0.3}.
-
 \hypertarget{i-visitation-patterns}{%
@@
 
-We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species.
+First, we used Bayesian modelling (see below for details) to investigate how the different groups of floral visitors interacted along the main axes of reproductive trait variation with the help of qualitative and quantitative information of plant-pollinator interactions.
+For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
+Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency {[}\protect\hyperlink{ref-ballantyne2015}{56}{]}, the number of visits can provide valuable information of the contribution of floral visitors to pollination {[}\protect\hyperlink{ref-vazquez2005}{57},\protect\hyperlink{ref-vazquez2012}{58}{]}.
 For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
@@
 This finding is consistent with previous research showing that \emph{A.
-mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems {[}\protect\hyperlink{ref-hung2018}{60}{]}.
+mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems {[}\protect\hyperlink{ref-hung2018}{59}{]}.
 Hence, to control for the effect of \emph{A.
@@
 
-We implemented Bayesian generalized linear mixed models using the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{61}{]}.
+We implemented Bayesian generalized linear mixed models using the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{60}{]}.
 We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
@@
 We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results {[}\protect\hyperlink{ref-burkner2017}{61}{]}.
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}\protect\hyperlink{ref-gabry2019}{62}{]}.
+The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results {[}\protect\hyperlink{ref-burkner2017}{60}{]}.
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}\protect\hyperlink{ref-gabry2019}{61}{]}.
 
@@
 
-We investigated whether different quantitative traits determined different plant species' functional roles in the pollination network using Bayesian modelling.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{63}{]} with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{64}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{63}{]}.
-
+Second, we investigated with Bayesian modelling how the main axes of trait variation determined different plant species' functional roles in the pollination network.
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{62}{]} with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics that summarize species' functional roles were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{63}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{62}{]}.
 We modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
@@
 Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns' section.
+
+Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
+Sampling methods varied across studies but this was accounted for in analyses by considering them in the random effects of the modelling process.
+All analyses were conducted in R version \emph{4.0.3}.
 
@@
 
-{\centering \includegraphics[width=0.95\linewidth]{output/figures/unnamed-chunk-2-1}
+{\centering \includegraphics[width=0.85\linewidth]{output/figures/unnamed-chunk-2-1}
 
@@
 
-We found (with an Anova) that most categorical traits were statistically associated with the first two axes of trait variation (figure 2 and table S2).
+We found that most categorical traits were statistically associated with the first two axes of trait variation (figure 2 and table S2).
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (figure S7).
+In addition, we found statistical differences between the different levels of categorical traits in the trait space (figure S7).
 Regarding self-compatibility, we found larger differences on PC2.
-For instance, species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility on this vertical axis (figure S7a and figure S7b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S7c and figure S7d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h).
+For instance, species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility on this vertical axis (figure S7a and figure S7b; Tukey test \emph{P} \textless{} 0.05).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S7c and figure S7d; Tukey test \emph{P} \textless{} 0.05).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f; Tukey test \emph{P} \textless{} 0.05).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h; Tukey test \emph{P} \textless{} 0.05).
 Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S7i and figure S7j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S7k and figure S7l).
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S7i and figure S7j; Tukey test \emph{P} \textless{} 0.05).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S7k and figure S7l; Tukey test \emph{P} \textless{} 0.05).
 
@@
 We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (figure 3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
-Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number but small (figure 3d).
+Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high number of small flowers (figure 3d).
 On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (figure 3b and figure 3e).
 Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (figure 3c).
-However, regarding number of visits on the style length - pollinator dependence axis, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (figure 3f).
-
-The additional model for both presence-absence of interaction (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and number of visits (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (figure 3a and figure 3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (figure S9).
+Plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (figure 3f).
+
+The additional model for the most represented families of bees for both presence-absence of interaction (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and number of visits (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03) showed that the family Apidae was the main driver of the observed patterns.
+The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (figure 3a and figure 3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (figure S8).
 
@@
 Again, specialization showed the opposite trend to number of visits (figure S9i).
+\href{}{crees que podemos meter una figura de este resultado en main text?
+Si no esta ahi, no lo va a ver nadie}
 
@@
 
-This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that shape interactions with floral visitors at a global scale.
+The reproductive spectrum of flowering plants show clear positive and negative covariations between reproductive traits that shape the interactions of angiosperms with their floral visitors at a global scale.
 Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively.
-These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
-Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{13},\protect\hyperlink{ref-carmona2021}{36}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
-Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
-However, they were insufficient to capture their visitation rates which highlight the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
-
-Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and links the reproductive spectrum with the previously described fast-slow continuum' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{65}{]} life-history strategies, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
-For instance, although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{38},\protect\hyperlink{ref-kettle2011}{39},\protect\hyperlink{ref-worley2000}{66}{]}, it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
+These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence \href{}{que opinas de que pol dep salga en dos ejes?
+No es raro?}.
+Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{16},\protect\hyperlink{ref-carmona2021}{18}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
+Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds.
+However, they were insufficient to capture the visitation rates, which highlight the need to account for other local factors, such as local relative abuncances \href{}{REF?
+a malas mi Fun Ecol de 2016}, to better capture the strength of these mutualistic interactions at a macroecological scale.
+
+We provide solid evidence for the generality of several hypothesized trait associations across a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and linked the reproductive spectrum with previously described fast-slow continuum' life-history strategies in plants {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animals {[}\protect\hyperlink{ref-healy2019}{64}{]}, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
+For instance, although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{20},\protect\hyperlink{ref-kettle2011}{21},\protect\hyperlink{ref-worley2000}{65}{]}, it has only been investigated across a few hundred of Angiosperm species with a pair-wise trait approach.
 We found support to this trait association and show that other life history traits also covariate along this axis.
-Our study also complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{67}{]} by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
-Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{40}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
+Our study also complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{66}{]} by showing that most species with unisexual flowers \href{no\%20pillo\%20esto}{are concentrated in the trait space} and are associated with woody life forms with high flower number.
+Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{22}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
 Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral displays.
@@
 
-Overall, our models showed that the main plant reproductive trait correlations have low predictive power for broad-level interaction patterns between plants and floral visitors.
-However, we found changes in the interaction patterns among and within floral visitor guilds that suggest that plant reproductive strategies partly mediate these associations at large ecological scales.
-For example, we found that all floral visitor guilds interacted more frequently with plant species with larger floral displays in agreement with previous findings {[}\protect\hyperlink{ref-hegland2005}{68}--\protect\hyperlink{ref-kaiser2014}{70}{]}.
-Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes.
-For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour {[}\protect\hyperlink{ref-rader2020}{71},\protect\hyperlink{ref-foldesi2021}{72}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{27},\protect\hyperlink{ref-vazquez2007}{73},\protect\hyperlink{ref-encinas2012}{74}{]} that reproductive correlations do not.
-
-To conclude, we provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of reproductive traits from plant species that belong to plant-pollinator networks.
-Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider other factors beyond plant reproductive strategies to better capture broad scale patterns of interactions with floral visitors.
-In addition, we provide empirical evidence that complements previous studies that have explored trait correlations with other plant organs and highlights the need to include these reproductive trait correlations in the global spectrum of plant form and function {[}\protect\hyperlink{ref-diaz2016}{13}{]}, as the different plant reproductive strategies involve clear cost and benefits that can affect resource allocation to other morphological and physiological traits.
+Overall, plant reproductive trait covariation axes help explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales.
+For example, as predicted by \href{}{evolutionary?
+life-history?} theory, larger investments floral size and rewards to attract pollinators makes sense when pollinator dependence is higher, but this might trade off with the resources allocated to ovule production \href{Anne\%20Leonard\%20tenia\%20algo\%20de\%20eso,\%20creo}{mirate la literatura de esto\ldots{} seguro que hay papers.
+Además, si esto que digo l apoyan los datos, puede ser algo que la gente querra citar (YO QUIEREO!) asi que dejalo explicito}.
+Interestingly, by combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings {[}\protect\hyperlink{ref-hegland2005}{67}--\protect\hyperlink{ref-kaiser2014}{69}{]}.
+Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes \href{}{ref, van der pijl, como clasico, no?
+Ollerton tiene cosas recientes}.
+For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies \href{}{name which ones} and because these two guilds are likely to differ in ecology and behaviour {[}\protect\hyperlink{ref-rader2020}{70},\protect\hyperlink{ref-foldesi2021}{71}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{33},\protect\hyperlink{ref-vazquez2007}{72},\protect\hyperlink{ref-encinas2012}{73}{]} that reproductive correlations do not.
+
+We provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of reproductive traits from plant species that belong to plant-pollinator networks.
+Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider factors such as plant reproductive strategies, and not only flower morphology, to better capture broad scale patterns of interactions with floral visitors.
+In addition, we provide empirical evidence that complements previous trait correlation studies along other plant organs and highlights the need to include reproductive trait correlations in the global spectrum of plant form and function {[}\protect\hyperlink{ref-diaz2016}{16}{]}, as the different plant reproductive strategies involve clear cost and benefits that can affect resource allocation to other morphological and physiological traits.
 Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and understanding of the different plant-pollinator associations.
+
+\href{}{Me falta un parrafo de por que esto es importante o que puede hacer la gente con esto.
+Seria el penultimo parrafo, por ejemplo, como afecta esto a la gente haciendo coexistencia (e.g.~el paper de Pauw y el tuyo).
+Como afecta esto a la gente hacienco estabilidad y estructura de polinizadores.
+Como afecta esto a ecologos evolutivos?}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
+\CSLLeftMargin{11. }
+\CSLRightInline{Laughlin DC \emph{et al.} 2021 Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
+\emph{Nat.
+Ecol.
+Evol.}, 1--12.
+(doi:\href{https://doi.org/10.1038/s41559-021-01471-7}{10.1038/s41559-021-01471-7})}
+
 \leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%
-\CSLLeftMargin{11. }
+\CSLLeftMargin{12. }
 \CSLRightInline{Wright IJ \emph{et al.} 2004 The worldwide leaf economics spectrum. \emph{Nature} \textbf{428}, 821--827. (doi:\href{https://doi.org/10.1038/nature02403}{10.1038/nature02403})}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
-\CSLLeftMargin{12. }
+\CSLLeftMargin{13. }
 \CSLRightInline{Chave J, Coomes D, Jansen S, Lewis SL, Swenson NG, Zanne AE.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Díaz S \emph{et al.} 2016 The global spectrum of plant form and function. \emph{Nature} \textbf{529}, 167--171. (doi:\href{https://doi.org/10.1038/nature16489}{10.1038/nature16489})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-onoda2017}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
 \CSLLeftMargin{14. }
-\CSLRightInline{Onoda Y, Wright IJ, Evans JR, Hikosaka K, Kitajima K, Niinemets Ü, Poorter H, Tosens T, Westoby M.
-2017 Physiological and structural tradeoffs underlying the leaf economics spectrum.
-\emph{New Phytol.} \textbf{214}, 1447--1463.
-(doi:\href{https://doi.org/10.1111/nph.14496}{10.1111/nph.14496})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Laughlin DC \emph{et al.} 2021 Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
-\emph{Nat.
-Ecol.
-Evol.}, 1--12.
-(doi:\href{https://doi.org/10.1038/s41559-021-01471-7}{10.1038/s41559-021-01471-7})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-baude2016}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Baude M, Kunin WE, Boatman ND, Conyers S, Davies N, Gillespie MA, Morton RD, Smart SM, Memmott J.
-2016 Historical nectar assessment reveals the fall and rise of floral resources in britain.
-\emph{Nature} \textbf{530}, 85--88.
-(doi:\href{https://doi.org/10.1038/nature16532}{10.1038/nature16532})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{Munoz F, Violle C, Cheptou P-O.
-2016 {CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
-\emph{Oikos} \textbf{125}, 1296--1303.
-(doi:\href{https://doi.org/10.1111/oik.02328}{10.1111/oik.02328})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-grossenbacher2017}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Grossenbacher DL \emph{et al.} 2017 Self-compatibility is over-represented on islands.
-\emph{New Phytol.} \textbf{215}, 469--478.
-(doi:\href{https://doi.org/10.1111/nph.14534}{10.1111/nph.14534})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Moeller DA \emph{et al.} 2017 Global biogeography of mating system variation in seed plants.
-\emph{Ecol.
-Lett.} \textbf{20}, 375--384.
-(doi:\href{https://doi.org/10.1111/ele.12738}{10.1111/ele.12738})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Sargent RD, Ackerly DD.
-2008 Plant--pollinator interactions and the assembly of plant communities.
-\emph{Trends Ecol.
-Evol.} \textbf{23}, 123--130.
-(doi:\href{https://doi.org/10.1016/j.tree.2007.11.003}{10.1016/j.tree.2007.11.003})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rech2016}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Rech AR, Dalsgaard B, Sandel B, Sonne J, Svenning J-C, Holmes N, Ollerton J.
-2016 The macroecology of animal versus wind pollination: Ecological factors are more important than historical climate stability.
-\emph{Plant Ecol.
-Divers.} \textbf{9}, 253--262.
-(doi:\href{https://doi.org/10.1080/17550874.2016.1207722}{10.1080/17550874.2016.1207722})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{Rüger N, Comita LS, Condit R, Purves D, Rosenbaum B, Visser MD, Wright SJ, Wirth C.
-2018 Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
-\emph{Ecol.
-Lett.} \textbf{21}, 1075--1084.
-(doi:\href{https://doi.org/10.1111/ele.12974}{10.1111/ele.12974})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Tur C, Castro-Urgal R, Traveset A.
-2013 Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}.
-\emph{PLoS One} \textbf{8}, e78294.
-(doi:\href{https://doi.org/10.1371/journal.pone.0078294}{10.1371/journal.pone.0078294})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{Devaux C, Lepers C, Porcher E.
-2014 Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems.
-\emph{J.
-Evol.
-Biol.} \textbf{27}, 1413--1430.
-(doi:\href{https://doi.org/10.1111/jeb.12380}{10.1111/jeb.12380})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Rosas-Guerrero V, Aguilar R, Martén-Rodríguez S, Ashworth L, Lopezaraiza-Mikel M, Bastida JM, Quesada M.
-2014 A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
-\emph{Ecol.
-Lett.} \textbf{17}, 388--400.
-(doi:\href{https://doi.org/10.1111/ele.12224}{10.1111/ele.12224})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Stang M, Klinkhamer PGL, Waser NM, Stang I, van der Meijden E.
-2009 Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
-\emph{Ann.
-Bot.} \textbf{103}, 1459--1469.
-(doi:\href{https://doi.org/10.1093/aob/mcp027}{10.1093/aob/mcp027})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Bartomeus I, Gravel D, Tylianakis JM, Aizen MA, Dickie IA, Bernard-Verdier M.
-2016 A common framework for identifying linkage rules across different types of interactions.
-\emph{Funct.
-Ecol.} \textbf{30}, 1894--1903.
-(doi:\href{https://doi.org/10.1111/1365-2435.12666}{10.1111/1365-2435.12666})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{Junker RR, Blüthgen N, Brehm T, Binkenstein J, Paulus J, Schaefer HM, Stang M.
-2013 Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
-\emph{Funct.
-Ecol.} \textbf{27}, 329--341.
-(doi:\href{https://doi.org/10.1111/1365-2435.12005}{10.1111/1365-2435.12005})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{Coux C, Rader R, Bartomeus I, Tylianakis JM.
-2016 Linking species functional roles to their network roles.
-\emph{Ecol.
-Lett.} \textbf{19}, 762--770.
-(doi:\href{https://doi.org/10.1111/ele.12612}{10.1111/ele.12612})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Ibanez S.
-2012 Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks.
-\emph{Oecologia} \textbf{170}, 233--242.
-(doi:\href{https://doi.org/10.1007/s00442-012-2290-3}{10.1007/s00442-012-2290-3})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Eklöf A \emph{et al.} 2013 The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583. (doi:\href{https://doi.org/10.1111/ele.12081}{10.1111/ele.12081})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Dehling DM, Jordano P, Schaefer HM, Böhning-Gaese K, Schleuning M.
-2016 Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
-\emph{Proc.
-Royal Soc.
-B} \textbf{283}, 20152444.
-(doi:\href{https://doi.org/10.1098/rspb.2015.2444}{10.1098/rspb.2015.2444})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
-\CSLLeftMargin{33. }
 \CSLRightInline{Kattge J \emph{et al.} 2011 {TRY} \textendash{} a global database of plant traits.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{15. }
 \CSLRightInline{Salguero-Gómez R \emph{et al.} 2015 The compadre {Plant Matrix Database}: An open online repository for plant demography.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
+\CSLLeftMargin{16. }
+\CSLRightInline{Díaz S \emph{et al.} 2016 The global spectrum of plant form and function. \emph{Nature} \textbf{529}, 167--171. (doi:\href{https://doi.org/10.1038/nature16489}{10.1038/nature16489})}
+
 \leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{17. }
 \CSLRightInline{Bruelheide H \emph{et al.} 2018 Global trait--environment relationships of plant communities.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{18. }
 \CSLRightInline{Carmona CP \emph{et al.} 2021 Erosion of global functional diversity across the tree of life.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{19. }
 \CSLRightInline{E-Vojtkó A, Bello F de, Durka W, Kühn I, Götzenberger L.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{20. }
 \CSLRightInline{Sargent RD, Goodwillie C, Kalisz S, Ree RH.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{21. }
 \CSLRightInline{Kettle CJ, Maycock CR, Ghazoul J, Hollingsworth PM, Khoo E, Sukri RSH, Burslem DFRP.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{22. }
 \CSLRightInline{Goodwillie C \emph{et al.} 2010 Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{23. }
 \CSLRightInline{Barrett SCH.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
+\CSLLeftMargin{24. }
+\CSLRightInline{Moeller DA \emph{et al.} 2017 Global biogeography of mating system variation in seed plants.
+\emph{Ecol.
+Lett.} \textbf{20}, 375--384.
+(doi:\href{https://doi.org/10.1111/ele.12738}{10.1111/ele.12738})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-baude2016}{}}%
+\CSLLeftMargin{25. }
+\CSLRightInline{Baude M, Kunin WE, Boatman ND, Conyers S, Davies N, Gillespie MA, Morton RD, Smart SM, Memmott J.
+2016 Historical nectar assessment reveals the fall and rise of floral resources in britain.
+\emph{Nature} \textbf{530}, 85--88.
+(doi:\href{https://doi.org/10.1038/nature16532}{10.1038/nature16532})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
+\CSLLeftMargin{26. }
+\CSLRightInline{Munoz F, Violle C, Cheptou P-O.
+2016 {CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
+\emph{Oikos} \textbf{125}, 1296--1303.
+(doi:\href{https://doi.org/10.1111/oik.02328}{10.1111/oik.02328})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-grossenbacher2017}{}}%
+\CSLLeftMargin{27. }
+\CSLRightInline{Grossenbacher DL \emph{et al.} 2017 Self-compatibility is over-represented on islands.
+\emph{New Phytol.} \textbf{215}, 469--478.
+(doi:\href{https://doi.org/10.1111/nph.14534}{10.1111/nph.14534})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
+\CSLLeftMargin{28. }
+\CSLRightInline{Sargent RD, Ackerly DD.
+2008 Plant--pollinator interactions and the assembly of plant communities.
+\emph{Trends Ecol.
+Evol.} \textbf{23}, 123--130.
+(doi:\href{https://doi.org/10.1016/j.tree.2007.11.003}{10.1016/j.tree.2007.11.003})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rech2016}{}}%
+\CSLLeftMargin{29. }
+\CSLRightInline{Rech AR, Dalsgaard B, Sandel B, Sonne J, Svenning J-C, Holmes N, Ollerton J.
+2016 The macroecology of animal versus wind pollination: Ecological factors are more important than historical climate stability.
+\emph{Plant Ecol.
+Divers.} \textbf{9}, 253--262.
+(doi:\href{https://doi.org/10.1080/17550874.2016.1207722}{10.1080/17550874.2016.1207722})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
+\CSLLeftMargin{30. }
+\CSLRightInline{Rüger N, Comita LS, Condit R, Purves D, Rosenbaum B, Visser MD, Wright SJ, Wirth C.
+2018 Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
+\emph{Ecol.
+Lett.} \textbf{21}, 1075--1084.
+(doi:\href{https://doi.org/10.1111/ele.12974}{10.1111/ele.12974})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
+\CSLLeftMargin{31. }
+\CSLRightInline{Rosas-Guerrero V, Aguilar R, Martén-Rodríguez S, Ashworth L, Lopezaraiza-Mikel M, Bastida JM, Quesada M.
+2014 A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
+\emph{Ecol.
+Lett.} \textbf{17}, 388--400.
+(doi:\href{https://doi.org/10.1111/ele.12224}{10.1111/ele.12224})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
+\CSLLeftMargin{32. }
+\CSLRightInline{Stang M, Klinkhamer PGL, Waser NM, Stang I, van der Meijden E.
+2009 Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
+\emph{Ann.
+Bot.} \textbf{103}, 1459--1469.
+(doi:\href{https://doi.org/10.1093/aob/mcp027}{10.1093/aob/mcp027})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
+\CSLLeftMargin{33. }
+\CSLRightInline{Bartomeus I, Gravel D, Tylianakis JM, Aizen MA, Dickie IA, Bernard-Verdier M.
+2016 A common framework for identifying linkage rules across different types of interactions.
+\emph{Funct.
+Ecol.} \textbf{30}, 1894--1903.
+(doi:\href{https://doi.org/10.1111/1365-2435.12666}{10.1111/1365-2435.12666})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
+\CSLLeftMargin{34. }
+\CSLRightInline{Tur C, Castro-Urgal R, Traveset A.
+2013 Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}.
+\emph{PLoS One} \textbf{8}, e78294.
+(doi:\href{https://doi.org/10.1371/journal.pone.0078294}{10.1371/journal.pone.0078294})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
+\CSLLeftMargin{35. }
+\CSLRightInline{Junker RR, Blüthgen N, Brehm T, Binkenstein J, Paulus J, Schaefer HM, Stang M.
+2013 Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
+\emph{Funct.
+Ecol.} \textbf{27}, 329--341.
+(doi:\href{https://doi.org/10.1111/1365-2435.12005}{10.1111/1365-2435.12005})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
+\CSLLeftMargin{36. }
+\CSLRightInline{Coux C, Rader R, Bartomeus I, Tylianakis JM.
+2016 Linking species functional roles to their network roles.
+\emph{Ecol.
+Lett.} \textbf{19}, 762--770.
+(doi:\href{https://doi.org/10.1111/ele.12612}{10.1111/ele.12612})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
+\CSLLeftMargin{37. }
+\CSLRightInline{Ibanez S.
+2012 Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks.
+\emph{Oecologia} \textbf{170}, 233--242.
+(doi:\href{https://doi.org/10.1007/s00442-012-2290-3}{10.1007/s00442-012-2290-3})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
+\CSLLeftMargin{38. }
+\CSLRightInline{Devaux C, Lepers C, Porcher E.
+2014 Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems.
+\emph{J.
+Evol.
+Biol.} \textbf{27}, 1413--1430.
+(doi:\href{https://doi.org/10.1111/jeb.12380}{10.1111/jeb.12380})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
+\CSLLeftMargin{39. }
+\CSLRightInline{Eklöf A \emph{et al.} 2013 The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583. (doi:\href{https://doi.org/10.1111/ele.12081}{10.1111/ele.12081})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
+\CSLLeftMargin{40. }
+\CSLRightInline{Dehling DM, Jordano P, Schaefer HM, Böhning-Gaese K, Schleuning M.
+2016 Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
+\emph{Proc.
+Royal Soc.
+B} \textbf{283}, 20152444.
+(doi:\href{https://doi.org/10.1098/rspb.2015.2444}{10.1098/rspb.2015.2444})}
+
 \leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Carvalheiro LG \emph{et al.} 2014 The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Olesen JM, Bascompte J, Dupont YL, Jordano P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Fortuna MA, Stouffer DB, Olesen JM, Jordano P, Mouillot D, Krasnov BR, Poulin R, Bascompte J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Poisot T \emph{et al.} 2016 Mangal \textendash{} making ecological network analysis simple.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Chamberlain S \emph{et al.} 2020 Taxize: {Taxonomic} information from around the web.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Smith SA, Brown JW.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Jin Y, Qian H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Stekhoven DJ, Bühlmann P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Penone C, Davidson AD, Shoemaker KT, Marco MD, Rondinini C, Brooks TM, Young BE, Graham CH, Costa GC.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
+\CSLLeftMargin{50. }
+\CSLRightInline{Chamberlain S \emph{et al.} 2018 Package {``{PVR}''}. R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
 \CSLLeftMargin{51. }
-\CSLRightInline{Chamberlain S \emph{et al.} 2018 Package {`{PVR}'}. R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
-\CSLLeftMargin{52. }
 \CSLRightInline{Diniz-Filho JAF, Bini LM, Rangel TF, Morales-Castilla I, Olalla-Tárraga MÁ, Rodríguez MÁ, Hawkins BA.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-serneels2008}{}}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Serneels S, Verdonck T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
+\CSLLeftMargin{53. }
+\CSLRightInline{Legendre P, Legendre L. 2012 \emph{Numerical ecology}. {2nd edn}. {Elsevier, Amsterdam}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
 \CSLLeftMargin{54. }
-\CSLRightInline{Legendre P, Legendre L. 2012 \emph{Numerical ecology}. {2nd edn}. {Elsevier, Amsterdam}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
-\CSLLeftMargin{55. }
 \CSLRightInline{Revell LJ.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
+\CSLLeftMargin{55. }
+\CSLRightInline{Abdi H, Williams LJ. 2010 Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459. (doi:\href{https://doi.org/10.1002/wics.101}{10.1002/wics.101})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
 \CSLLeftMargin{56. }
-\CSLRightInline{Abdi H, Williams LJ. 2010 Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459. (doi:\href{https://doi.org/10.1002/wics.101}{10.1002/wics.101})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
-\CSLLeftMargin{57. }
 \CSLRightInline{Ballantyne G, Baldock KCR, Willmer PG.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
-\CSLLeftMargin{58. }
+\CSLLeftMargin{57. }
 \CSLRightInline{Vázquez DP, Morris WF, Jordano P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
-\CSLLeftMargin{59. }
+\CSLLeftMargin{58. }
 \CSLRightInline{Vázquez DP, Lomáscolo SB, Maldonado MB, Chacoff NP, Dorado J, Stevani EL, Vitale NL.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
-\CSLLeftMargin{60. }
+\CSLLeftMargin{59. }
 \CSLRightInline{Hung K-LJ, Kingston JM, Albrecht M, Holway DA, Kohn JR.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
-\CSLLeftMargin{61. }
+\CSLLeftMargin{60. }
 \CSLRightInline{Bürkner P-C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
-\CSLLeftMargin{62. }
+\CSLLeftMargin{61. }
 \CSLRightInline{Gabry J, Simpson D, Vehtari A, Betancourt M, Gelman A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
+\CSLLeftMargin{62. }
+\CSLRightInline{Dormann CF, Gruber B, Fründ J. 2008 Introducing the bipartite package: Analysing ecological networks. \emph{R News} \textbf{8/2}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
 \CSLLeftMargin{63. }
-\CSLRightInline{Dormann CF, Gruber B, Fründ J. 2008 Introducing the bipartite package: Analysing ecological networks. \emph{R News} \textbf{8/2}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
-\CSLLeftMargin{64. }
 \CSLRightInline{Blüthgen N, Menzel F, Blüthgen N.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
-\CSLLeftMargin{65. }
+\CSLLeftMargin{64. }
 \CSLRightInline{Healy K, Ezard THG, Jones OR, Salguero-Gómez R, Buckley YM.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-worley2000}{}}%
-\CSLLeftMargin{66. }
+\CSLLeftMargin{65. }
 \CSLRightInline{Worley AC, Baker AM, Thompson JD, Barrett SC.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-petit2006}{}}%
-\CSLLeftMargin{67. }
+\CSLLeftMargin{66. }
 \CSLRightInline{Petit RJ, Hampe A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
-\CSLLeftMargin{68. }
+\CSLLeftMargin{67. }
 \CSLRightInline{Hegland SJ, Totland Ø.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
-\CSLLeftMargin{69. }
+\CSLLeftMargin{68. }
 \CSLRightInline{Lázaro A, Jakobsson A, Totland Ø.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
-\CSLLeftMargin{70. }
+\CSLLeftMargin{69. }
 \CSLRightInline{Kaiser-Bunbury CN, Vázquez DP, Stang M, Ghazoul J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rader2020}{}}%
-\CSLLeftMargin{71. }
+\CSLLeftMargin{70. }
 \CSLRightInline{Rader R, Cunningham S, Howlett B, Inouye D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
-\CSLLeftMargin{72. }
+\CSLLeftMargin{71. }
 \CSLRightInline{Földesi R, Howlett BG, Grass I, Batáry P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
-\CSLLeftMargin{73. }
+\CSLLeftMargin{72. }
 \CSLRightInline{Vázquez DP, Melián CJ, Williams NM, Blüthgen N, Krasnov BR, Poulin R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
-\CSLLeftMargin{74. }
+\CSLLeftMargin{73. }
 \CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS.

### 2022-06-28 Manuscript/Lanuza_et_al_2022.Rmd
edits

@@
 Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50% and 70% of reproductive trait variation, respectively.
-These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence [que opinas de que pol dep salga en dos ejes?
-No es raro?]().
+These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
 Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits [@diaz2016; @carmona2021], our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits [@salguero2016].
@@
 Interestingly, by combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings [@hegland2005; @lazaro2013; @kaiser2014].
-Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes [ref, van der pijl, como clasico, no?
-Ollerton tiene cosas recientes]().
+Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes [@faegri2013; @rosas2014; @dellinger2020].
 For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies [name which ones]() and because these two guilds are likely to differ in ecology and behaviour [@rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies.

### 2022-06-28 Manuscript/Lanuza_et_al_2022.tex
edits

@@
 
-The reproductive spectrum of flowering plants show clear positive and negative covariations between reproductive traits that shape the interactions of angiosperms with their floral visitors at a global scale.
+The reproductive spectrum of flowering plants show clear positive and negative covariations between reproductive traits that shape the interactions of Angiosperms with their floral visitors at a global scale.
 Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively.
@@
 Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds.
-However, they were insufficient to capture the visitation rates, which highlight the need to account for other local factors, such as local relative abuncances \href{}{REF?
-a malas mi Fun Ecol de 2016}, to better capture the strength of these mutualistic interactions at a macroecological scale.
+However, they were insufficient to capture the visitation rates, which highlight the need to account for other local factors, such as local relative abuncances {[}\protect\hyperlink{ref-bartomeus2016}{33}{]}, to better capture the strength of these mutualistic interactions at a macroecological scale.
 
@@
 Interestingly, by combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings {[}\protect\hyperlink{ref-hegland2005}{67}--\protect\hyperlink{ref-kaiser2014}{69}{]}.
-Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes \href{}{ref, van der pijl, como clasico, no?
-Ollerton tiene cosas recientes}.
-For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies \href{}{name which ones} and because these two guilds are likely to differ in ecology and behaviour {[}\protect\hyperlink{ref-rader2020}{70},\protect\hyperlink{ref-foldesi2021}{71}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{33},\protect\hyperlink{ref-vazquez2007}{72},\protect\hyperlink{ref-encinas2012}{73}{]} that reproductive correlations do not.
+Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes {[}\protect\hyperlink{ref-dellinger2020}{4},\protect\hyperlink{ref-rosas2014}{31},\protect\hyperlink{ref-faegri2013}{70}{]}.
+For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies \href{}{name which ones} and because these two guilds are likely to differ in ecology and behaviour {[}\protect\hyperlink{ref-rader2020}{71},\protect\hyperlink{ref-foldesi2021}{72}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{33},\protect\hyperlink{ref-vazquez2007}{73},\protect\hyperlink{ref-encinas2012}{74}{]} that reproductive correlations do not.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-faegri2013}{}}%
+\CSLLeftMargin{70. }
+\CSLRightInline{Faegri K, Van Der Pijl L. 2013 Principles of pollination ecology. }
+
 \leavevmode\vadjust pre{\hypertarget{ref-rader2020}{}}%
-\CSLLeftMargin{70. }
+\CSLLeftMargin{71. }
 \CSLRightInline{Rader R, Cunningham S, Howlett B, Inouye D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
-\CSLLeftMargin{71. }
+\CSLLeftMargin{72. }
 \CSLRightInline{Földesi R, Howlett BG, Grass I, Batáry P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
-\CSLLeftMargin{72. }
+\CSLLeftMargin{73. }
 \CSLRightInline{Vázquez DP, Melián CJ, Williams NM, Blüthgen N, Krasnov BR, Poulin R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
-\CSLLeftMargin{73. }
+\CSLLeftMargin{74. }
 \CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS.

### 2022-07-04 Main_Figures/Figure3.Rmd
edits

@@
 pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
-aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
+aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab(NULL)+
   theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
@@
 pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
-aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
+aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab(NULL)+ xlab(NULL)+
   theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
@@
 pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
- aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
+ aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab(NULL)+ xlab(NULL)+
   theme_ms() + theme(legend.position = "none") + 
@@
   aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend.   High poll. depend.")+
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab(NULL)+ xlab("Low poll. depend.   High poll. depend.")+
   theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + 
@@
   aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles      Long styles\n High poll. depend.   Low poll. depend.")+
+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab(NULL)+ xlab("Short styles      Long styles\n High poll. depend.   Low poll. depend.")+
   theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold"))+ 

### 2022-07-04 Manuscript/Lanuza_et_al_2022.Rmd
edits

@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.090, 0.115)) + ggtitle("(b)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.090, 0.115)) + ggtitle("(b)") +
+    xlab(NULL) + ylab(NULL)
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.12, 0.1)) + ggtitle("(c)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.12, 0.1)) + ggtitle("(c)") +
+    xlab(NULL) + ylab(NULL)
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL)
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL)
 
@@
 
+\blandscape
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=28,out.width="90%",fig.align='center',fig.cap="\\textbf{Fig.
+S9.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows).
+The x-axis shows the most illustrative trait extremes of the trait continuum.
+Note that the plots are coloured by the different network metrics.", fig.pos= "h"}
+
+#library(brms) #modelling
+library(cowplot) #panel of plots
+library(ggplot2) #plotting
+library(patchwork)
+
+setwd("~/Dropbox/PhD/R/Chapter_2")
+
+#read plot generated in other rmd, bms and stan are giving trouble here... This file is created in Species_Level_Metric_Pcs
+
+plot_metrics_pcs <- readRDS("plot_metrics_pcs.rds")
+
+plot_metrics_pcs
+
+```
+
+\elandscape
+
 # 4. Discussion

### 2022-07-04 Manuscript/Lanuza_et_al_2022.tex
edits

@@
 
+\blandscape
+
+\begin{figure}[h]
+
+{\centering \includegraphics[width=0.9\linewidth]{output/figures/unnamed-chunk-5-1}
+
+}
+
+\caption{\textbf{Fig.
+S9.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows).
+The x-axis shows the most illustrative trait extremes of the trait continuum.
+Note that the plots are coloured by the different network metrics.}\label{fig:unnamed-chunk-5}
+\end{figure}
+
+\elandscape
+
 \hypertarget{discussion}{%
@@
 Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively.
-These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence \href{}{que opinas de que pol dep salga en dos ejes?
-No es raro?}.
+These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
 Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{16},\protect\hyperlink{ref-carmona2021}{18}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.

### 2022-07-04 Supplementary_Material/Species_Level_Metric_Pcs.Rmd
edits

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=28}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=22, fig.width=28, fig.align='center'}
 
@@
 # Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
+
+theme_ms <- function(base_size=14, base_family="Helvetica") {
   (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(3.5)),
-           axis.text=element_text(size = rel(2.75), color = "black"),
-           plot.title = element_text(size = 40,face="bold"),
-           legend.title=element_text(face="bold"),
-           legend.text=element_text(),
+           axis.title=element_text( size = rel(2.2)),
+           axis.text=element_text(size = rel(1.9), color = "black"),
+           legend.title=element_text(face="bold",size=rel(2)),
+           legend.text=element_text(size=rel(1.7)),
            legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(0.4, 'lines'),
-           panel.border=element_rect(color="black",size=3),
+           legend.key.size = unit(1.9, 'lines'),
+           panel.border=element_rect(color="black",size=2.4),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
+           panel.grid.major= element_blank(),
+           plot.title = element_text(hjust = 0.5,size=rel(3.05),face="bold"),
+           plot.subtitle = element_text(face="bold",size=rel(2.7))
      ))
@@
   size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC1")+ggtitle("A")
+  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC1")+ggtitle("PC1", subtitle = "(a)")+ xlab(NULL)
 
@@
   size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC2")+ggtitle("B")
+  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("") + xlab("PC2")+ggtitle("PC2", subtitle = "(b)")+ xlab(NULL)
 
@@
 Visits_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = Visits),
-  size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC3") +ggtitle("C")
+  size = 3.5, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
+  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab(NULL) + xlab("PC3") +ggtitle("PC3", subtitle = "(c)")+ xlab(NULL)
 
@@
 normalised.degree_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = normalised.degree),
-  size = 3, alpha=0.65, colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC1")+ggtitle("D")
+  size = 3.5, alpha=0.65, colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC1") + ggtitle(NULL, subtitle = "(d)")+ xlab(NULL)
 
@@
 normalised.degree_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = normalised.degree),
-  size = 3, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC2")+ggtitle("E")
+  size = 3.5, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5) +theme_ms()+
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab(NULL) + xlab("PC2") + ggtitle(NULL, subtitle = "(e)")+ xlab(NULL)
 
@@
 normalised.degree_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = normalised.degree),
-  size = 3, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC3")+ggtitle("F")
+  size = 3.5, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab(NULL) + xlab("PC3") + ggtitle(NULL, subtitle = "(f)")+ xlab(NULL)
 
@@
 Specialization_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = d),
-  size = 3, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1")+ggtitle("G")
+  size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1") + ggtitle(NULL, subtitle = "(g)") +  xlab("High flower N.
+Low flower N.\nSmall flowers    Large flowers")
 
@@
 Specialization_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = d),
-  size = 3, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC2")+ggtitle("H")
+  size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab(NULL) + xlab("PC2") + ggtitle(NULL, subtitle = "(h)") + xlab("Low poll. depend.   High poll. depend.")
 
@@
 Specialization_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = d),
- size = 3, alpha=0.65, colour="darkorange3") + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+geom_line(colour="black",size=1.5)+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC3")+ggtitle("I")
+ size = 3.5, alpha=0.65, colour="darkorange3") + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+geom_line(colour="black",size=1.5)+
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab(NULL) + xlab("PC3") + ggtitle(NULL, subtitle = "(i)")+ xlab("Short styles      Long styles\n High poll.
+depend.
+Low poll.
+depend.")
 

### 2022-07-05 Main_Figures/Figure3.Rmd
figs

@@
 library(broman) #crayon colours
-#library(tidyverse)
+library(tidyverse)
 library(patchwork) #panel of plots
@@
            legend.key.size = unit(1.9, 'lines'),
+           legend.box.margin=margin(20,20,20,20),
            panel.border=element_rect(color="black",size=2.4),
@@
            plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
+           plot.margin = margin(1,1,1,1, unit = "cm"),
            plot.subtitle = element_text(face="bold",size=rel(2.5))
+
      ))
@@
 
-pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
-aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab(NULL)+
-  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=guild, colour=guild)) + 
+geom_point(data = dat_analysis,
+aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + 
+ylab("Interaction") + 
+xlab(NULL) +
+theme_ms() + 
+theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A","cyan4","blueviolet"),           labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphid-Diptera", "Syrphids")) + ggtitle("PC1", subtitle = "(a)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
 
@@
 
-p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
+dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)
+
+p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + 
+geom_point(data = dat_analysis,
 aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
+coord_cartesian(ylim=c(1,100),clip="off") + 
+ylab("Number of visits") +  
+theme_ms() + 
+theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
   values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-    "Non-syrphid-Diptera", "Syrphids"))+
-  scale_y_log10()+ggtitle("(d)")
+    "Non-syrphid-Diptera", "Syrphids")) +
+scale_y_log10() +
+ggtitle(NULL, subtitle = "(d)") +
+annotate(geom = "text", x = -1.7, y =0.2 , label = "High flower N.", size = 8) +
+annotate(geom = "text", x = -1.7, y =0.12 , label = "Small flowers", size = 8) + 
+annotate(geom = "text", x = 1.8, y =0.2 , label = "Low flower N.", size = 8) + 
+annotate(geom = "text", x = 1.8, y =0.12 , label = "Large flowers", size = 8) +
+xlab("") +
+annotate(geom = "text", x = -0.1, y =0.35 , label = "Flower number - Flower size axis", size = 8.5, fontface =2) + xlab("") + theme(panel.border=element_rect(color="black",size=1.2))
+
 #Plot nicely PC2
@@
 
-p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
-  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab(NULL)+ xlab("Low poll. depend.   High poll. depend.")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + 
-  scale_color_manual(name="Functional groups",values=c("orange", "black", 
-  "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-    "Non-syrphid-Diptera", "Syrphids")) + scale_y_log10()+ggtitle("(e)")
+dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)
+
+p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + 
+geom_point(data = dat_analysis, aes(x = -PC2, y = Interaction), size = 2.5, alpha=0.4) + 
+geom_line(size=1.5) + 
+coord_cartesian(ylim=c(1,100),clip="off") + 
+ylab(NULL)  +
+theme_ms() + 
+theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + 
+scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"), labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphid-Diptera", "Syrphids")) + scale_y_log10()+
+ggtitle(NULL, subtitle = "(e)") +
+annotate(geom = "text", x = -1.7, y =0.2 , label = "Low poll. depend.", size = 8) +
+annotate(geom = "text", x = -1.65, y =0.12 , label = "Small floral display", size = 8) + 
+annotate(geom = "text", x = 1.8, y =0.2 , label = "High poll. depend.", size = 8) + 
+annotate(geom = "text", x = 1.85, y =0.12 , label = "Large floral display", size = 8) +
+xlab("") +
+annotate(geom = "text", x = -0.1, y =0.35 , label = "Pollinator dependence - Floral display axis", size = 8.5, fontface =2) +
+theme(panel.border=element_rect(color="black",size=1.2))
 
@@
 
+dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)
+
 p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
   aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab(NULL)+ xlab("Short styles      Long styles\n High poll. depend.   Low poll. depend.")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold"))+ 
+coord_cartesian(ylim=c(1,100),clip="off") +
+ylab(NULL) +
+theme_ms() + 
+theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + 
 scale_color_manual(name="Functional groups",values=c("orange", 
-  "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
-    "Non-syrphid-Diptera", "Syrphids"))+ scale_y_log10()+ggtitle("(f)")
+  "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphid-Diptera", "Syrphids")) + 
+scale_y_log10() + 
+ggtitle(NULL, subtitle = "(f)") +
+annotate(geom = "text", x = -1.6, y =0.2 , label = "Short styles", size = 8) +
+annotate(geom = "text", x = -1.25, y =0.12 , label = "High poll. depend.", size = 8) + 
+annotate(geom = "text", x = 2.15, y =0.2 , label = "Long styles", size = 8) + 
+annotate(geom = "text", x = 2.5, y =0.12 , label = "Low poll. depend.", size = 8) +
+xlab(" \n \n  ") +
+annotate(geom = "text", x = 0.25, y =0.35 , label = "Style length - Pollinator dependence axis", size = 8.5, fontface =2) +
+theme(panel.border=element_rect(color="black",size=1.2))
 

### 2022-07-05 Manuscript/Lanuza_et_al_2022.Rmd
figs

@@
       theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
+            axis.title=element_text( size = rel(1.6)),
+            axis.text=element_text(size = rel(1.6), color = "black"),
             legend.title=element_text(face="bold"),
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)  + ylab("Pollinator dependence - floral display axis")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL)
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL) + xlab("Flower number - flower size axis")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL)
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL) + xlab("Flower number - flower size axis")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("(d)")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("(d)") +
+    xlab("Flower number - flower size axis") +
+    ylab("Pollinator dependence - floral display axis")
 

### 2022-07-06 Manuscript/Lanuza_et_al_2022.Rmd
sup mat edits

@@
 Again, specialization showed the opposite trend to number of visits (figure S9i).
-[crees que podemos meter una figura de este resultado en main text?
-Si no esta ahi, no lo va a ver nadie]()
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=28,out.width="90%",fig.align='center',fig.cap="\\textbf{Fig.
-S9.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows).
-The x-axis shows the most illustrative trait extremes of the trait continuum.
-Note that the plots are coloured by the different network metrics.", fig.pos= "h"}
-
-#library(brms) #modelling
-library(cowplot) #panel of plots
-library(ggplot2) #plotting
-library(patchwork)
-
-setwd("~/Dropbox/PhD/R/Chapter_2")
-
-#read plot generated in other rmd, bms and stan are giving trouble here... This file is created in Species_Level_Metric_Pcs
-
-plot_metrics_pcs <- readRDS("plot_metrics_pcs.rds")
-
-plot_metrics_pcs
-
-```
-
-\elandscape
 

### 2022-07-06 Supplementary_Material/Analysis_2_Hymenoptera_Families_Separated.Rmd
sup mat edits

--- 2021-12-07 Supplementary_Material/Analysis_2_Hymenoptera_Families_Separated.Rmd
@@
 
-pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
- aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + 
-  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__), group=bee_family, colour=bee_family)) + 
+geom_point(data = dat_analysis,
+ aes(x = -PC3, y = Interaction), size = 2.5, alpha=0.4) + geom_line(size=1.5)  + 
+ylab("") + 
+xlab("") +
+theme_ms() + 
+theme(legend.position = "none",plot.title = element_text(face="bold")) + 
+scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet")) + ggtitle("PC3", subtitle = "(c)") +
+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
+
 #Plot nicely PC1
@@
 
-p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
-  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0)) + scale_color_manual(name="Functional groups",
-  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+
-  scale_y_log10()+ggtitle("(d)")
+p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=bee_family, colour=bee_family)) + 
+geom_point(data = dat_analysis, aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + 
+geom_line(size=1.5) + 
+coord_cartesian(ylim=c(1,100),clip="off")+ 
+ylab("Number of visits") + 
+xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers") +
+theme_ms() + 
+theme(legend.position = "none",plot.title = element_text(size=rel(2.95),hjust = 0)) + scale_color_manual(name="Functional groups",
+values = c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet")) +
+scale_y_log10() + ggtitle("(d)") +
+annotate(geom = "text", x = -1.7, y =0.2 , label = "High flower N.", size = 8) +
+annotate(geom = "text", x = -1.7, y =0.12 , label = "Small flowers", size = 8) + 
+annotate(geom = "text", x = 1.8, y =0.2 , label = "Low flower N.", size = 8) + 
+annotate(geom = "text", x = 1.8, y =0.12 , label = "Large flowers", size = 8) +
+xlab("") +
+annotate(geom = "text", x = -0.1, y =0.35 , label = "Flower number - Flower size axis", size = 8.5, fontface =2) + xlab("") + theme(panel.border=element_rect(color="black",size=1.2))
+
 #Plot nicely PC2
@@
 
-p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
-  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0)) + 
-  scale_color_manual(name="Functional groups",values=c("orange", "black", 
-  "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10()+ggtitle("(e)")
+dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)
+
+p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=bee_family, colour=bee_family)) + 
+geom_point(data = dat_analysis, aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + 
+geom_line(size=1.5) + 
+coord_cartesian(ylim=c(1,100),clip="off")+ 
+ylab("") + 
+xlab("Low poll. depend. High poll. depend.") +
+theme_ms() + 
+theme(legend.position = "none",plot.title = element_text(size=rel(2.95),hjust = 0)) + 
+scale_color_manual(name="Functional groups",values=c("orange", 
+        "black", "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10() +
+ggtitle("(e)") +
+annotate(geom = "text", x = -1.7, y =0.2 , label = "Low poll. depend.", size = 8) +
+annotate(geom = "text", x = -1.65, y =0.12 , label = "Small floral display", size = 8) + 
+annotate(geom = "text", x = 1.8, y =0.2 , label = "High poll. depend.", size = 8) + 
+annotate(geom = "text", x = 1.85, y =0.12 , label = "Large floral display", size = 8) +
+xlab(NULL) +
+annotate(geom = "text", x = -0.1, y =0.35 , label = "Pollinator dependence - Floral display axis", size = 8.5, fontface =2) +
+theme(panel.border=element_rect(color="black",size=1.2))
 
@@
 
-p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
-  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles\n Low selfing    High selfing")+
-  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0))+ 
+dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)
+
+p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=bee_family, colour=bee_family)) + 
+geom_point(data = dat_analysis, aes(x = -PC3, 
+          y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
+coord_cartesian(ylim=c(1,100),clip="off") + 
+ylab("") +
+theme_ms() + 
+theme(legend.position = "none",plot.title = 
+        element_text(size=rel(2.95),hjust = 0)) + 
 scale_color_manual(name="Functional groups",values=c("orange", 
-  "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ scale_y_log10()+ggtitle("(f)")
+        "black", "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10() + 
+ggtitle("(f)") +
+annotate(geom = "text", x = -1.6, y =0.2 , label = "Short styles", size = 8) +
+annotate(geom = "text", x = -1.25, y =0.12 , label = "High poll. depend.", size = 8) + 
+annotate(geom = "text", x = 1.95, y =0.2 , label = "Long styles", size = 8) + 
+annotate(geom = "text", x = 2.3, y =0.12 , label = "Low poll. depend.", size = 8) +
+xlab(" \n \n  ") +
+annotate(geom = "text", x = 0.25, y =0.35 , label = "Style length - Pollinator dependence axis", size = 8.5, fontface =2) +
+theme(panel.border=element_rect(color="black",size=1.2))
 

### 2022-07-06 Supplementary_Material/Bees_and_other_func_grous_separated.Rmd
sup mat edits

--- 2021-09-19 Supplementary_Material/Bees_and_other_func_grous_separated.Rmd
@@
 
-d1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis,
-      aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4")+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
-  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) +
- labs(title = "", subtitle =my_y_title)
+dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)
+
+d1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis, aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") +  coord_cartesian(ylim=c(1,100),clip="off") +
+ylab("Number of visits") +
+theme_ms() + 
+theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) +
+labs(title = "", subtitle =my_y_title) +
+annotate(geom = "text", x = -1.7, y =-32 , label = "High flower N.", size = 8) +
+annotate(geom = "text", x = -1.72, y =-42 , label = "Small flowers", size = 8) + 
+annotate(geom = "text", x = 1.8, y =-32 , label = "Low flower N.", size = 8) + 
+annotate(geom = "text", x = 1.8, y =-42 , label = "Large flowers", size = 8) +
+xlab("") +
+annotate(geom = "text", x = -0.1, y =-20 , label = "Flower number - Flower size axis", size = 8.5, fontface =2) + xlab("") + theme(panel.border=element_rect(color="black",size=1.2))
 
@@
 
-d2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,
-                                                                          aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none")  +
-  theme(plot.title = element_text(size = 36, face = "bold"),plot.subtitle=element_text(size=30,face="bold"))+ labs(title = "", subtitle = my_y_title)
+dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)
+
+d2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis, aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") +
+coord_cartesian(ylim=c(1,100),clip="off") +
+ylab("") + 
+theme_ms() + 
+theme(legend.position = "none")  +
+theme(plot.title = element_text(size = 36, face = "bold"),plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = my_y_title) +
+annotate(geom = "text", x = -1.7, y =-32 , label = "Low poll. depend.", size = 8) +
+annotate(geom = "text", x = -1.65, y =-42 , label = "Small floral display", size = 8) + 
+annotate(geom = "text", x = 1.75, y =-32 , label = "High poll. depend.", size = 8) + 
+annotate(geom = "text", x = 1.8, y =-42 , label = "Large floral display", size = 8) +
+xlab(NULL) +
+annotate(geom = "text", x = -0.1, y =-20 , label = "Pollinator dependence - Floral display axis", size = 8.5, fontface =2) +
+theme(panel.border=element_rect(color="black",size=1.2))
+
 #Plot nicely PC3
@@
 
-d3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis,
-                                                                          aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
-  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = my_y_title)
+dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)
+
+d3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis, aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") +
+coord_cartesian(ylim=c(1,100),clip="off") +
+ylab("") + 
+theme_ms() + 
+theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = my_y_title) +
+annotate(geom = "text", x = -1.6, y =-32 , label = "Short styles", size = 8) +
+annotate(geom = "text", x = -1.2, y =-42 , label = "High poll. depend.", size = 8) + 
+annotate(geom = "text", x = 1.95, y =-32 , label = "Long styles", size = 8) + 
+annotate(geom = "text", x = 2.3, y =-42 , label = "Low poll. depend.", size = 8) +
+xlab(" \n \n  ") +
+annotate(geom = "text", x = 0.25, y =-20 , label = "Style length - Pollinator dependence axis", size = 8.5, fontface =2) +
+theme(panel.border=element_rect(color="black",size=1.2))
 

### 2022-07-06 Supplementary_Material/Species_Level_Metric_Pcs.Rmd
sup mat edits

@@
 
-Specialization_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = d),
-  size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1") + ggtitle(NULL, subtitle = "(g)") +  xlab("High flower N.
-Low flower N.\nSmall flowers    Large flowers")
+Specialization_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + 
+geom_point(data = data_analysis_2,aes(x = -PC1, y = d),
+           size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + coord_cartesian(ylim=c(0,quantile(data_analysis_2$d, 0.95)), 
+            clip="off") + 
+           theme_ms() +
+geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, 
+            alpha=0.1,fill="black") + ylab("Specialization (d')") + 
+xlab("PC1") + 
+ggtitle(NULL, subtitle = "(g)") +  
+annotate(geom = "text", x = -1.6, y =-0.3 , 
+               label = "High flower N.", size = 8) +
+annotate(geom = "text", x = -1.7, y =-0.41 ,
+               label = "Small flowers", size = 8) + 
+annotate(geom = "text", x = 1.75, y =-0.3 , 
+               label = "Low flower N.", size = 8) + 
+annotate(geom = "text", x = 1.75, y =-0.41 ,
+               label = "Large flowers", size = 8) +
+annotate(geom = "text", x = 0.10, y =-0.19 , 
+    label = "Flower number - Flower size axis", size = 8.5, fontface =2) +
+theme(panel.border=element_rect(color="black",size=1.2)) +
+xlab(" \n \n  ")
 
@@
 
-Specialization_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = d),
-  size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab(NULL) + xlab("PC2") + ggtitle(NULL, subtitle = "(h)") + xlab("Low poll. depend.   High poll. depend.")
+Specialization_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y =
+(estimate__))) + 
+geom_point(data = data_analysis_2,aes(x = -PC2, y = d),
+           size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + coord_cartesian(ylim=c(0,quantile(data_analysis_2$d, 0.95)), 
+                clip="off") +
+theme_ms() +
+geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + 
+ylab(NULL) + 
+xlab("PC2") + 
+ggtitle(NULL, subtitle = "(h)") + 
+xlab(NULL) +
+annotate(geom = "text", x = -1.57, y =-0.3 , 
+               label = "Low poll. depend.", size = 8) +
+annotate(geom = "text", x = -1.5, y =-0.41 ,
+               label = "Small floral display", size = 8) + 
+annotate(geom = "text", x = 1.75, y =-0.3 , 
+               label = "High poll. depend.", size = 8) + 
+annotate(geom = "text", x = 1.8, y =-0.41 ,
+               label = "Large floral display", size = 8) +
+annotate(geom = "text", x = 0.10, y =-0.19 , 
+    label = "Pollinator dependence - Floral display axis", size = 8.5, fontface =2) +
+theme(panel.border=element_rect(color="black",size=1.2))
 
@@
 
-Specialization_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = d),
- size = 3.5, alpha=0.65, colour="darkorange3") + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+geom_line(colour="black",size=1.5)+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab(NULL) + xlab("PC3") + ggtitle(NULL, subtitle = "(i)")+ xlab("Short styles      Long styles\n High poll.
-depend.
-Low poll.
-depend.")
+Specialization_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y =             (estimate__))) + 
+geom_point(data = data_analysis_2,aes(x = -PC3, y = d),
+           size = 3.5, alpha=0.65, colour="darkorange3")  +
+theme_ms() + 
+geom_line(colour="black",size=1.5) +
+geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2,    
+            alpha=0.1,fill="black") +
+ylab(NULL) + 
+xlab("PC3") + 
+coord_cartesian(ylim=c(0,quantile(data_analysis_2$d, 0.95)), 
+                clip="off") +
+ggtitle(NULL, subtitle = "(i)") + 
+annotate(geom = "text", x = -1.57, y =-0.3 , 
+         label = "Short styles", size = 8) +
+annotate(geom = "text", x = -1.25, y =-0.41 ,
+         label = "High poll. depend.", size = 8) + 
+annotate(geom = "text", x = 2.05, y =-0.3 , 
+         label = "Long styles", size = 8) + 
+annotate(geom = "text", x = 2.4, y =-0.41 ,
+         label = "Low poll. depend.", size = 8) +
+annotate(geom = "text", x = 0.25, y =-0.19 , 
+         label = "Style length - Pollinator dependence axis", 
+         size = 8.5, fontface =2) +
+theme(panel.border=element_rect(color="black",size=1.2)) +
+xlab(NULL)
 

### 2022-07-06 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
sup mat edits

--- 2022-06-23 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021.Rmd
@@
 S3.} Comparison of the phylogenetic informed principal component analysis for the dataset with data imputation and without data imputation.
-Panel A shows the reproductive spectrum of trait variation for the full dataset with data imputation and panel B shows the reproductive spectrum for the dataset without data imputation where the species with missing trait data were excluded from the analysis."}
+Panel 'a' shows the reproductive spectrum of trait variation for the full dataset with data imputation and panel 'b' shows the reproductive spectrum for the dataset without data imputation where the species with missing trait data were excluded from the analysis."}
 
@@
 
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("Pollinator dependence - Floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
 
@@
 
-p1 / p2 + plot_annotation(tag_levels = 'A') & 
-  theme(plot.tag = element_text(size = 24, face="bold"))
+p1 / p2 + plot_annotation(tag_levels = c('a'), tag_prefix = '(', tag_sep = '', tag_suffix = ')')  & theme(plot.tag = element_text(size = 24, face="bold"))
 
@@
 
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("Pollinator dependence - Floral display ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
 
@@
 
-p1 / p2 + plot_annotation(tag_levels = 'A') & 
+p1 / p2 + plot_annotation(tag_levels = c('a'), tag_prefix = '(', tag_sep = '', tag_suffix = ')') & 
   theme(plot.tag = element_text(size = 24, face="bold"))
@@
 
-  plot <- plot + xlab(paste("Flower number - flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Style length - pollinator dependence axis ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
+  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("Style length - Pollinator dependence axis ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
 
@@
                 width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "A Breeding system")+
+  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "(a) Breeding system")+
   theme(plot.title = element_text(hjust=0.5, size=26, face="bold"), plot.subtitle=element_text(size=16))+
@@
                 width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "B Breeding system")+
+  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "(b) Breeding system")+
   theme(plot.title = element_text(hjust=0.5,size=26, face="bold"),plot.subtitle=element_text(size=16))+
@@
   width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "C Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
+  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(c) Compatibility system")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black") + theme(axis.text = element_text( size = rel(1)))
 
@@
   width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "D Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
+  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(d) Compatibility system")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black") + theme(axis.text = element_text( size = rel(1)))
 
@@
                 width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "E Lifespan")+
+  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "(e) Lifespan")+
   geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
@@
                 width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "F Lifespan")+
+  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "(f) Lifespan")+
   geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")
@@
                 width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "G Life form")+
+  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "(g) Life form")+
   geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
@@
                 width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "H Life form")+
+  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "(h) Life form")+
   geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
@@
                 width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "I Flower shape")+
+  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(i) Flower shape")+
   geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")
@@
                 width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "J Flower shape")+
+  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(j) Flower shape")+
    geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
@@
                 width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "K Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
+  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "(k) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
 
@@
                 width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title = "L Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
+  scale_color_manual(values=c("sienna2","purple"))+labs(title = "(l) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
 
@@
                 width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "M Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
+  scale_color_manual(values=c("black","grey"))+labs(title = "(m) Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
 
@@
                 width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "N Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")
+  scale_color_manual(values=c("black","grey"))+labs(title = "(n) Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")
 
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S9.} Plant species level metrics across the three main axes of trait variation.", fig.pos= "h"}
+S9.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows).
+The x-axis shows the most illustrative trait extremes of the trait continuum.
+Note that the plots are coloured by the different network metrics.", fig.pos= "h"}
 

### 2022-07-06 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
some edits on sup mat

@@
 
-Here we describe the different traits of the database used in this study to explore the reproductive spectrum of trait variation and plant-pollinator associations.
-Note that all species have references or links providing the original source of the information.
+Here we describe the different individual traits that have been included in the database:
 
@@
 
--	Breeding system: The different plant species were classified in hermaphrodite, dioecious and monoecious species.
+-	Breeding system: All species were classified in hermaphrodite, dioecious and monoecious species.
 Intermediate breeding systems or more complex ones were also annotated but all the species were divided into these three main categories for simplicity of the analysis.
@@
 -	Selfing level: We recorded the selfing level of the different species with both quantitative and qualitative data.
-The qualitative data was divided in four main categories, high selfers, medium selfers, low selfers and none which was for the species that were unable to self-pollinate.
-In addition, quantitative data was also divided into these four categories with the following criteria: from 0% to lower than 1% ‘none’, from 1% to 25% ‘low’, from 26% to 75% ‘medium’ and from 76% to 100%  ‘high’.
-Because quantitative selfing had a high percentage of missing values (68%), we were able to solve this by converting these four categories to representative percentages of each category 0%, 13%, 50.5% and 88%.
-This reduced the percentage of missing values for this quantitative trait from 68% to 35% and allowed the imputation of this variable.
+The qualitative data was divided in four main categories, high selfers (76% to 100% of selfing), medium selfers (26% to 75%), low selfers (1% to 25%) and none (0%) which was for the species that were unable to self-pollinate.
+The quantitative column of selfing had a high percentage of missing values (68%) but we were able to solve this by converting the four categories from the qualitative column to numerical.
+For this, we considered the mean value of the different categories, that is the categories of ‘none’, ‘low’, ‘medium’ and ‘high’ represented 0%, 13%, 50.5% and 88% of selfing, respectively.
+This reduced the percentage of missing of this column from 68% to 35% and allowed the imputation of this variable.
 
@@
 
--	Flower symmetry: We also recorded if the flowers were bilaterally symmetrical “zygomorphic” or were radially symmetrical “actinomorphic”.
+-	Flower symmetry: Depending on the possible number of identical divisions of a flower, plant species were classified into zygomorphic (bilaterally symmetrical with only two identical parts) and actinomorphic (radially symmetrical with more than three identical parts).
 
@@
 Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
-For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)"}
+For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)."}
 

### 2022-07-07 Main_Figures/Figure3.Rmd
edit

@@
 annotate(geom = "text", x = -1.7, y =0.2 , label = "High flower N.", size = 8) +
-annotate(geom = "text", x = -1.7, y =0.12 , label = "Small flowers", size = 8) + 
+annotate(geom = "text", x = -1.75, y =0.12 , label = "Small flowers", size = 8) + 
 annotate(geom = "text", x = 1.8, y =0.2 , label = "Low flower N.", size = 8) + 

### 2022-07-07 Manuscript/Lanuza_et_al_2022.Rmd
edit

@@
 
-  plot <- plot + xlab(paste("Flower number - flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Pollinator dependence - floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
+  plot <- plot + ylab(paste("Pollinator dependence - Floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)  + ylab("Pollinator dependence - floral display axis")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)  + ylab("Pollinator dependence - Floral display axis")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL) + xlab("Flower number - flower size axis")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL) + xlab("Flower number - Flower size axis")
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL) + xlab("Flower number - flower size axis")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL) + xlab("Flower number - Flower size axis")
 
@@
   plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("(d)") +
-    xlab("Flower number - flower size axis") +
-    ylab("Pollinator dependence - floral display axis")
+    xlab("Flower number - Flower size axis") +
+    ylab("Pollinator dependence - Floral display axis")
 
@@
 Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds.
-However, they were insufficient to capture the visitation rates, which highlight the need to account for other local factors, such as local relative abuncances [@bartomeus2016], to better capture the strength of these mutualistic interactions at a macroecological scale.
-
-We provide solid evidence for the generality of several hypothesized trait associations across a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and linked the reproductive spectrum with previously described fast-slow continuum' life-history strategies in plants [@salguero2016] and animals [@healy2019], as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
+However, they were insufficient to capture the visitation rates by guild or other species-level network metrics, which highlight the need to account for other local factors, such as species relative abuncances [@bartomeus2016], to better understand the association of these mutualistic interactions at a macroecological scale.
+
+Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and links the reproductive spectrum with the previously described fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
 For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a pair-wise trait approach.
 We found support to this trait association and show that other life history traits also covariate along this axis.
-Our study also complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers [are concentrated in the trait space](no pillo esto) and are associated with woody life forms with high flower number.
+Our study also complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers are associated with woody life forms with high flower number.
 Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
@@
 Overall, plant reproductive trait covariation axes help explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales.
-For example, as predicted by [evolutionary?
-life-history?]() theory, larger investments floral size and rewards to attract pollinators makes sense when pollinator dependence is higher, but this might trade off with the resources allocated to ovule production [mirate la literatura de esto...
-seguro que hay papers.
-Además, si esto que digo l apoyan los datos, puede ser algo que la gente querra citar (YO QUIEREO!) asi que dejalo explicito](Anne Leonard tenia algo de eso, creo).
-Interestingly, by combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings [@hegland2005; @lazaro2013; @kaiser2014].
+For example, we found that all floral visitor guilds interacted more frequently with plant species with larger flowers in agreement with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
+As predicted by evolutionary life-history theory [@stebbins1970], larger investments on floral display and rewards to attract pollinators makes sense when pollinator dependence is higher but there are compromises (as the flower number - floral display) that can affect the reproductive investment to other organs such as ovule number and affect pollen transfer and seed production
+
+However, the investment in floral display has evident compromises between flower number and flower size
+
+there are evident compromises as the one showed between flower number and flower size that affect the reproductive investment in ovules and pollen transfer as also shown for other wind pollinated species [@friedman2011]
+
+  By combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings [@hegland2005; @lazaro2013; @kaiser2014].
 Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes [@faegri2013; @rosas2014; @dellinger2020].

### 2022-07-07 Manuscript/Lanuza_et_al_2022.tex
edit

--- 2022-06-28 Manuscript/Lanuza_et_al_2022.tex
@@
 Again, specialization showed the opposite trend to number of visits (figure S9i).
-\href{}{crees que podemos meter una figura de este resultado en main text?
-Si no esta ahi, no lo va a ver nadie}
 
@@
 Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively.
-These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence \href{}{que opinas de que pol dep salga en dos ejes?
-No es raro?}.
+These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
 Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{16},\protect\hyperlink{ref-carmona2021}{18}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
 Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds.
-However, they were insufficient to capture the visitation rates, which highlight the need to account for other local factors, such as local relative abuncances {[}\protect\hyperlink{ref-bartomeus2016}{33}{]}, to better capture the strength of these mutualistic interactions at a macroecological scale.
-
-We provide solid evidence for the generality of several hypothesized trait associations across a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and linked the reproductive spectrum with previously described fast-slow continuum' life-history strategies in plants {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animals {[}\protect\hyperlink{ref-healy2019}{64}{]}, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
+However, they were insufficient to capture the visitation rates by guild or other species-level network metrics, which highlight the need to account for other local factors, such as species relative abuncances {[}\protect\hyperlink{ref-bartomeus2016}{33}{]}, to better understand the association of these mutualistic interactions at a macroecological scale.
+
+Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and links the reproductive spectrum with the previously described fast-slow continuum' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{64}{]} life-history strategies, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
 For instance, although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{20},\protect\hyperlink{ref-kettle2011}{21},\protect\hyperlink{ref-worley2000}{65}{]}, it has only been investigated across a few hundred of Angiosperm species with a pair-wise trait approach.
 We found support to this trait association and show that other life history traits also covariate along this axis.
-Our study also complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{66}{]} by showing that most species with unisexual flowers \href{no\%20pillo\%20esto}{are concentrated in the trait space} and are associated with woody life forms with high flower number.
+Our study also complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{66}{]} by showing that most species with unisexual flowers are associated with woody life forms with high flower number.
 Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{22}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
@@
 Overall, plant reproductive trait covariation axes help explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales.
-For example, as predicted by \href{}{evolutionary?
-life-history?} theory, larger investments floral size and rewards to attract pollinators makes sense when pollinator dependence is higher, but this might trade off with the resources allocated to ovule production \href{Anne\%20Leonard\%20tenia\%20algo\%20de\%20eso,\%20creo}{mirate la literatura de esto\ldots{} seguro que hay papers.
+For example, as predicted by evolutionary life-history theory {[}\protect\hyperlink{ref-stebbins1970}{67}{]}, larger investments floral size and rewards to attract pollinators makes sense when pollinator dependence is higher, but this might trade off with the resources allocated to ovule production \href{Anne\%20Leonard\%20tenia\%20algo\%20de\%20eso,\%20creo}{mirate la literatura de esto\ldots{} seguro que hay papers.
 Además, si esto que digo l apoyan los datos, puede ser algo que la gente querra citar (YO QUIEREO!) asi que dejalo explicito}.
-Interestingly, by combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings {[}\protect\hyperlink{ref-hegland2005}{67}--\protect\hyperlink{ref-kaiser2014}{69}{]}.
-Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes {[}\protect\hyperlink{ref-dellinger2020}{4},\protect\hyperlink{ref-rosas2014}{31},\protect\hyperlink{ref-faegri2013}{70}{]}.
-For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies \href{}{name which ones} and because these two guilds are likely to differ in ecology and behaviour {[}\protect\hyperlink{ref-rader2020}{71},\protect\hyperlink{ref-foldesi2021}{72}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{33},\protect\hyperlink{ref-vazquez2007}{73},\protect\hyperlink{ref-encinas2012}{74}{]} that reproductive correlations do not.
+Interestingly, by combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings {[}\protect\hyperlink{ref-hegland2005}{68}--\protect\hyperlink{ref-kaiser2014}{70}{]}.
+Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes {[}\protect\hyperlink{ref-dellinger2020}{4},\protect\hyperlink{ref-rosas2014}{31},\protect\hyperlink{ref-faegri2013}{71}{]}.
+For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies \href{}{name which ones} and because these two guilds are likely to differ in ecology and behaviour {[}\protect\hyperlink{ref-rader2020}{72},\protect\hyperlink{ref-foldesi2021}{73}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
+In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{33},\protect\hyperlink{ref-vazquez2007}{74},\protect\hyperlink{ref-encinas2012}{75}{]} that reproductive correlations do not.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-stebbins1970}{}}%
+\CSLLeftMargin{67. }
+\CSLRightInline{Stebbins GL.
+1970 Adaptive radiation of reproductive characteristics in angiosperms, i: Pollination mechanisms.
+\emph{Annual Review of Ecology and Systematics}, 307--326.
+(doi:\href{https://doi.org/10.1146/annurev.es.01.110170.001515}{10.1146/annurev.es.01.110170.001515})}
+
 \leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
-\CSLLeftMargin{67. }
+\CSLLeftMargin{68. }
 \CSLRightInline{Hegland SJ, Totland Ø.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
-\CSLLeftMargin{68. }
+\CSLLeftMargin{69. }
 \CSLRightInline{Lázaro A, Jakobsson A, Totland Ø.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
-\CSLLeftMargin{69. }
+\CSLLeftMargin{70. }
 \CSLRightInline{Kaiser-Bunbury CN, Vázquez DP, Stang M, Ghazoul J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-faegri2013}{}}%
-\CSLLeftMargin{70. }
+\CSLLeftMargin{71. }
 \CSLRightInline{Faegri K, Van Der Pijl L. 2013 Principles of pollination ecology. }
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rader2020}{}}%
-\CSLLeftMargin{71. }
+\CSLLeftMargin{72. }
 \CSLRightInline{Rader R, Cunningham S, Howlett B, Inouye D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
-\CSLLeftMargin{72. }
+\CSLLeftMargin{73. }
 \CSLRightInline{Földesi R, Howlett BG, Grass I, Batáry P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
-\CSLLeftMargin{73. }
+\CSLLeftMargin{74. }
 \CSLRightInline{Vázquez DP, Melián CJ, Williams NM, Blüthgen N, Krasnov BR, Poulin R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
-\CSLLeftMargin{74. }
+\CSLLeftMargin{75. }
 \CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS.

### 2022-07-07 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
edit

@@
 
-_Reproductive traits_
+_Reproductive biology traits_
 
@@
 The number of ovules of Asteraceae species are considered as the total number of ovules per capitulum.
-Many species were filled by genus or family level because the number of ovules in this taxonomic groups is considered to be mostly constant (e.g., Lamiaceae Boraginaceae or Apiaceae).
+Many species were filled by genus or family level because the number of ovules of some taxonomic groups is considered to be mostly constant (e.g., Lamiaceae, Boraginaceae or Apiaceae).
 
@@
 
--	Style length: The length of the style (mm) of the different species was also included. When possible, we calculated style length from images and illustrations on the online floras.
+-	Style length: We searched for the length of the style (the pistil excluding the ovary and the stigma) in millimeters for all plant species.
+When the information about style length was missing, we tried to calculate it from images and illustrations from online resources (e.g., floras).
 
@@
 For the field of microlitres of nectar, we considered single measurements of nectar standing crop.
-In general terms, the timming of the measurement and methodology differed across studies.
-For instance, some studies measured nectar in freshly opened flowers while others in flowers that were bagged for 24 hours.
-Despite the different methodologies to measure nectar provision, we believe that this is an appropriate way to collate measurements of nectar to explore trait associations at a macroecological scale.
-
-- Pollen grains per flower: We recorded pollen grains per flower for all species but this field was rarely described in the literature.
-When just the pollen:ovule ratio was found we converted it back to pollen grains by multiplying it by the average ovule number found for each species.
-
-_Vegetative traits_
+Despite the timing and methodology of the different quantitative measurements of nectar differed across studies, these fields allowed us to have an approximate idea of the reproductive investment of the different plant species.
+
+- Pollen grains per flower: For each species, we searched for the total number of pollen grains per flower.
+Because this fields was rarely available, we also tried to recover from pollen:ovule ratio information the total number of pollen grains by multiplying it by the average ovule number found for each species.
+
+_Other life history traits_
 

### 2022-07-08 Manuscript/Lanuza_et_al_2022.Rmd
edits

@@
 Overall, plant reproductive trait covariation axes help explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales.
-For example, we found that all floral visitor guilds interacted more frequently with plant species with larger flowers in agreement with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
-As predicted by evolutionary life-history theory [@stebbins1970], larger investments on floral display and rewards to attract pollinators makes sense when pollinator dependence is higher but there are compromises (as the flower number - floral display) that can affect the reproductive investment to other organs such as ovule number and affect pollen transfer and seed production
-
-However, the investment in floral display has evident compromises between flower number and flower size
-
-there are evident compromises as the one showed between flower number and flower size that affect the reproductive investment in ovules and pollen transfer as also shown for other wind pollinated species [@friedman2011]
-
-  By combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings [@hegland2005; @lazaro2013; @kaiser2014].
-Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes [@faegri2013; @rosas2014; @dellinger2020].
+For example, we found that all floral visitor guilds interacted more frequently with plant species with larger flowers and higher pollinator dependence in agreement with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
+As predicted by evolutionary life-history theory [@stebbins1970], larger investments on floral display and rewards to attract pollinators makes sense when pollinator dependence is higher but this investment is compromised by the cost of the different reproductive structures, trait associations and the distinct selective pressures such as the one exerted by the different floral visitor guilds [@galen1999].
+For instance, smaller flowers were less visited overall, but they are inexpensive (e.g., low ovule number) and can counterpart this lack of visitation at the flower level by increasing the chances of visitation at the whole individual level with larger displays as suggested for wind pollinated species which can optimise the probabilities of pollen capture and seed production with numerous small flowers [@friedman2011].
+Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations found between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes [@faegri2013; @rosas2014; @dellinger2020].
 For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies [name which ones]() and because these two guilds are likely to differ in ecology and behaviour [@rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies.

### 2022-07-11 Manuscript/Lanuza_et_al_2022.Rmd
edits

@@
 - \usepackage{orcidlink}
-
 ---
@@
 Kendall$^{4}$} \orcidlink{0000-0002-0671-0121}, \textbf{Manu E.
-Saunders$^{1}$} \orcidlink{0000-0003-0645-8277}
-\textbf{and Ignasi Bartomeus$^{2}$}
-\orcidlink{0000-0001-7893-4389}
+Saunders$^{1}$} \orcidlink{0000-0003-0645-8277} \textbf{and Ignasi Bartomeus$^{2}$} \orcidlink{0000-0001-7893-4389}
 
@@
 ```
-
 \textbf{Keywords:} life-history strategies \| plant reproductive traits \| plant-pollinator interactions
@@
 However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
-Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@salguero2016; @friedman2020; @paterno2020; @roddy2021], their study is often limited to a few number of reproductive traits that are rarely studied in combination.
+Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@salguero2016; @friedman2020; @paterno2020; @roddy2021; @song2022], their study is often limited to a few number of reproductive traits that are rarely studied in combination.
 Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other root [@laughlin2021], leaf [@wright2004] or wood [@chave2009] related traits, there is a need to acquire a multitrait perspective with broad geographical coverage.
@@
 
-With the recent availability of large trait databases [e.g., TRY @kattge2011;\ COMPADRE @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
+With the recent availability of large trait databases [e.g., TRY @kattge2011;  COMPADRE @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
 However, most studies with a multitrait perspective have overlooked plant reproductive traits [@evojtko2020; @roddy2021] and focused on trait correlations from other plant organs.
@@
 Because both the species' morphology and mating system can determine the species' functional role in the pollination network and the combination of several traits has shown to increase the predictive power of the structure of ecological networks [@eklof2013], an interesting novel approach is to investigate how a complete set of reproductive traits in the multidimensional trait space determine species interaction patterns [see @dehling2016 for a morphological approach].
-Thus, by exploring the plant reproductive spectrum of trait variation is possible to delimit the different reproductive strategies and explore how these are associated with the different floral visitors.
+Thus, by exploring the plant reproductive spectrum of trait variation it is possible to delimit the different reproductive strategies and explore how these are associated with the different floral visitors.
 
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies [e.g., @carvalheiro2014; @olesen2007; @fortuna2010] or available in online archives [e.g., Mangal @poisot2016;\ The Web of Life @fortuna2010].
+Many of these networks are freely available either as published studies [e.g., @carvalheiro2014; @olesen2007; @fortuna2010] or available in online archives [e.g., Mangal @poisot2016;  The Web of Life @fortuna2010].
 In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
@@
 Due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as recomended for principal component analysis [@legendre2012].
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as recommended for principal component analysis [@legendre2012].
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
@@
 We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results [@burkner2017].
+The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so they have neglible influence on the results [@burkner2017].
 We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the *bayesplot* package [@gabry2019].
@@
 As an example of this reproductive extreme, we find the species *Veronica peregrina* which is a self-compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
-Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = |-0.51|) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
+Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \|-0.51\|) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
 The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; table S3).
@@
 Regarding self-compatibility, we found larger differences on PC2.
-For instance, species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility on this vertical axis (figure S7a and figure S7b; Tukey test *P* < 0.05).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S7c and figure S7d; Tukey test *P* < 0.05).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f; Tukey test *P* < 0.05).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h; Tukey test *P* < 0.05).
+For instance, species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility on this vertical axis (figure S7a and figure S7b; Tukey test *P* \< 0.05).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S7c and figure S7d; Tukey test *P* \< 0.05).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f; Tukey test *P* \< 0.05).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h; Tukey test *P* \< 0.05).
 Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S7i and figure S7j; Tukey test *P* < 0.05).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S7k and figure S7l; Tukey test *P* < 0.05).
+The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S7i and figure S7j; Tukey test *P* \< 0.05).
+Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S7k and figure S7l; Tukey test *P* \< 0.05).
 
@@
 
+```{=tex}
 \vspace{5mm}
 \blandscape
-
+```
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
@@
 Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
-On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
+On PC1, the number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
 However, specialization showed the opposite trend on this axis (figure S9g).
@@
 
-The reproductive spectrum of flowering plants show clear positive and negative covariations between reproductive traits that shape the interactions of Angiosperms with their floral visitors at a global scale.
+The reproductive spectrum of flowering plants showed clear reproductive trait covariation patterns that shaped interactions with floral visitors at a global scale.
 Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50% and 70% of reproductive trait variation, respectively.
@@
 Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds.
-However, they were insufficient to capture the visitation rates by guild or other species-level network metrics, which highlight the need to account for other local factors, such as species relative abuncances [@bartomeus2016], to better understand the association of these mutualistic interactions at a macroecological scale.
+However, they were insufficient to capture the visitation rates by guild or the other species-level network metrics considered in this study, which highlights the need to account for other local factors, such as species relative abundances [@bartomeus2016], to better understand the association of plant-pollinator interactions at a macroecological scale.
 
 Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and links the reproductive spectrum with the previously described fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
-For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a pair-wise trait approach.
+For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred Angiosperm species with a pair-wise trait approach.
 We found support to this trait association and show that other life history traits also covariate along this axis.
@@
 Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral displays.
+Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral displays but in particular with species with larger flowers.
 Our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
 
-Overall, plant reproductive trait covariation axes help explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales.
+Overall, plant reproductive trait covariation axes helped explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales.
 For example, we found that all floral visitor guilds interacted more frequently with plant species with larger flowers and higher pollinator dependence in agreement with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
-As predicted by evolutionary life-history theory [@stebbins1970], larger investments on floral display and rewards to attract pollinators makes sense when pollinator dependence is higher but this investment is compromised by the cost of the different reproductive structures, trait associations and the distinct selective pressures such as the one exerted by the different floral visitor guilds [@galen1999].
-For instance, smaller flowers were less visited overall, but they are inexpensive (e.g., low ovule number) and can counterpart this lack of visitation at the flower level by increasing the chances of visitation at the whole individual level with larger displays as suggested for wind pollinated species which can optimise the probabilities of pollen capture and seed production with numerous small flowers [@friedman2011].
-Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations found between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes [@faegri2013; @rosas2014; @dellinger2020].
-For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies [name which ones]() and because these two guilds are likely to differ in ecology and behaviour [@rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive correlations do not.
-
-We provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of reproductive traits from plant species that belong to plant-pollinator networks.
-Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider factors such as plant reproductive strategies, and not only flower morphology, to better capture broad scale patterns of interactions with floral visitors.
-In addition, we provide empirical evidence that complements previous trait correlation studies along other plant organs and highlights the need to include reproductive trait correlations in the global spectrum of plant form and function [@diaz2016], as the different plant reproductive strategies involve clear cost and benefits that can affect resource allocation to other morphological and physiological traits.
+As predicted by evolutionary life-history theory [@stebbins1970], larger investment on floral display and rewards to attract pollinators makes sense when pollinator dependence is higher, but this investment is compromised by the cost of the different reproductive structures, trait associations and the distinct selective pressures such as the one exerted by the different floral visitor guilds [@galen1999].
+For instance, smaller flowers were less visited overall, but they are inexpensive (e.g., low ovule number) and can counterpart this lack of visitation at the flower level by increasing the chances of visitation at the whole individual level with larger displays as suggested for wind pollinated species where small numerous flowers can increase the chances of pollen capture and seed production [@friedman2011].
+In addition, because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations found between reproductive traits and floral visitor guilds also may indicate the existence of large scale pollination syndromes [@faegri2013; @rosas2014; @dellinger2020].
+For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies on all axes and because these two guilds are likely to differ in ecology and behaviour [@rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies.
+In any case, it is worth noting that other local factors such as species relative abundances, phenology or trait matching, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive trait correlations do not.
+
+Our study provides a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of reproductive traits from plant species that belong to plant-pollinator networks.
+Additionally, we highlight the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider factors such as plant reproductive strategies, and not only flower morphology, to better capture broad scale patterns of interactions with floral visitors.
+Further, we provide empirical evidence that complements previous trait correlation studies along other plant organs and we highlights the need to include reproductive trait correlations in the global spectrum of plant form and function [@diaz2016], as the different plant reproductive strategies involve clear cost and benefits that can affect resource allocation to other morphological and physiological traits.
 Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and understanding of the different plant-pollinator associations.
-
-[Me falta un parrafo de por que esto es importante o que puede hacer la gente con esto.
-Seria el penultimo parrafo, por ejemplo, como afecta esto a la gente haciendo coexistencia (e.g.
-el paper de Pauw y el tuyo).
-Como afecta esto a la gente hacienco estabilidad y estructura de polinizadores.
-Como afecta esto a ecologos evolutivos?]()
 
@@
 
-**Data accessibility.** All data and code used to conduct this study is available at Zenodo (https://doi.org/10.5281/zenodo.6705621) and Github (https://github.com/JoseBSL/Reproductive-traits).
-
-**Authors’contributions.** JBL, RR and IB designed the study. JBL collated the data and conducted analysis with guidance of JS, LKK and IB. JBL wrote the manuscript with contributions of all authors.
+**Data accessibility.** All data and code used to conduct this study are available in the online repositories of Zenodo (<https://doi.org/10.5281/zenodo.6705621>) and Github (<https://github.com/JoseBSL/Reproductive-traits>).
+
+**Authors' contributions.** JBL, RR and IB designed the study. JBL collated the data and conducted analysis with guidance of JS, LKK and IB. JBL wrote the manuscript with contributions of all authors.
 
@@
 We also thank Jason Tylianakis for his comments on the manuscript before submission.
-Finally, we thank Marcos Méndez, Susan Kalisz, Amanda Benoit, May Berenbaum and an anonimous reviewer for thoughtful feedback and useful comments on earlier versions of this manuscript.
+Finally, we thank Marcos Méndez, Susan Kalisz, Amanda Benoit, May Berenbaum and an anonymous reviewer for thoughtful feedback and useful comments on earlier versions of this manuscript.

### 2022-07-11 Manuscript/Lanuza_et_al_2022.tex
edits

@@
 However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints {[}\protect\hyperlink{ref-stearns1989}{5},\protect\hyperlink{ref-agrawal2020}{6}{]}.
-Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits {[}\protect\hyperlink{ref-salguero2016}{7}--\protect\hyperlink{ref-roddy2021}{10}{]}, their study is often limited to a few number of reproductive traits that are rarely studied in combination.
-Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other root {[}\protect\hyperlink{ref-laughlin2021}{11}{]}, leaf {[}\protect\hyperlink{ref-wright2004}{12}{]} or wood {[}\protect\hyperlink{ref-chave2009}{13}{]} related traits, there is a need to acquire a multitrait perspective with broad geographical coverage.
+Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits {[}\protect\hyperlink{ref-salguero2016}{7}--\protect\hyperlink{ref-song2022}{11}{]}, their study is often limited to a few number of reproductive traits that are rarely studied in combination.
+Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other root {[}\protect\hyperlink{ref-laughlin2021}{12}{]}, leaf {[}\protect\hyperlink{ref-wright2004}{13}{]} or wood {[}\protect\hyperlink{ref-chave2009}{14}{]} related traits, there is a need to acquire a multitrait perspective with broad geographical coverage.
 Importantly, the characterization of the plant reproductive spectrum can help to further understand the different plant ecological strategies {[}\protect\hyperlink{ref-agrawal2020}{6}{]} and improve our knowledge on plant-pollinator associations {[}\protect\hyperlink{ref-roddy2021}{10}{]}.
 
-With the recent availability of large trait databases {[}e.g., TRY \protect\hyperlink{ref-kattge2011}{14},~COMPADRE \protect\hyperlink{ref-salguero2015}{15}{]}, plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-diaz2016}{16}--\protect\hyperlink{ref-carmona2021}{18}{]}.
-However, most studies with a multitrait perspective have overlooked plant reproductive traits {[}\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-evojtko2020}{19}{]} and focused on trait correlations from other plant organs.
-Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{20},\protect\hyperlink{ref-kettle2011}{21}{]}, the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{22}{]} or the positive association between outcrossing rate and lifespan {[}\protect\hyperlink{ref-barrett2003}{23},\protect\hyperlink{ref-moeller2017}{24}{]}.
+With the recent availability of large trait databases {[}e.g., TRY \protect\hyperlink{ref-kattge2011}{15},~COMPADRE \protect\hyperlink{ref-salguero2015}{16}{]}, plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-diaz2016}{17}--\protect\hyperlink{ref-carmona2021}{19}{]}.
+However, most studies with a multitrait perspective have overlooked plant reproductive traits {[}\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-evojtko2020}{20}{]} and focused on trait correlations from other plant organs.
+Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{21},\protect\hyperlink{ref-kettle2011}{22}{]}, the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{23}{]} or the positive association between outcrossing rate and lifespan {[}\protect\hyperlink{ref-barrett2003}{24},\protect\hyperlink{ref-moeller2017}{25}{]}.
 Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships {[}\protect\hyperlink{ref-roddy2021}{10}{]}, we still lack empirical evidence that investigates jointly how these different reproductive trait associations shape plant life history strategies.
 
-Despite this increasing number of macroecological studies that investigate specific plant reproductive traits {[}\protect\hyperlink{ref-moeller2017}{24}--\protect\hyperlink{ref-grossenbacher2017}{27}{]}, we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-sargent2008}{28}--\protect\hyperlink{ref-ruger2018}{30}{]}.
-The use of trait-based approaches {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{31}{]} and trait-matching analyses {[}\protect\hyperlink{ref-stang2009}{32},\protect\hyperlink{ref-bartomeus2016}{33}{]} has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-For example, plant traits can define species' network roles {[}e.g., specialists vs generalists \protect\hyperlink{ref-tur2013}{34}{]} and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators {[}\protect\hyperlink{ref-junker2013}{35},\protect\hyperlink{ref-coux2016}{36}{]}.
-Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure {[}\protect\hyperlink{ref-stang2009}{32},\protect\hyperlink{ref-ibanez2012}{37}{]}.
-However, is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations {[}\protect\hyperlink{ref-tur2013}{34},\protect\hyperlink{ref-devaux2014}{38}{]}.
+Despite this increasing number of macroecological studies that investigate specific plant reproductive traits {[}\protect\hyperlink{ref-moeller2017}{25}--\protect\hyperlink{ref-grossenbacher2017}{28}{]}, we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-sargent2008}{29}--\protect\hyperlink{ref-ruger2018}{31}{]}.
+The use of trait-based approaches {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{32}{]} and trait-matching analyses {[}\protect\hyperlink{ref-stang2009}{33},\protect\hyperlink{ref-bartomeus2016}{34}{]} has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
+For example, plant traits can define species' network roles {[}e.g., specialists vs generalists \protect\hyperlink{ref-tur2013}{35}{]} and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators {[}\protect\hyperlink{ref-junker2013}{36},\protect\hyperlink{ref-coux2016}{37}{]}.
+Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure {[}\protect\hyperlink{ref-stang2009}{33},\protect\hyperlink{ref-ibanez2012}{38}{]}.
+However, is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations {[}\protect\hyperlink{ref-tur2013}{35},\protect\hyperlink{ref-devaux2014}{39}{]}.
 Indeed, the pollination system of a great number of plant species remains unexplored {[}\protect\hyperlink{ref-dellinger2020}{4}{]}.
-Because both the species' morphology and mating system can determine the species' functional role in the pollination network and the combination of several traits has shown to increase the predictive power of the structure of ecological networks {[}\protect\hyperlink{ref-eklof2013}{39}{]}, an interesting novel approach is to investigate how a complete set of reproductive traits in the multidimensional trait space determine species interaction patterns {[}see \protect\hyperlink{ref-dehling2016}{40} for a morphological approach{]}.
-Thus, by exploring the plant reproductive spectrum of trait variation is possible to delimit the different reproductive strategies and explore how these are associated with the different floral visitors.
+Because both the species' morphology and mating system can determine the species' functional role in the pollination network and the combination of several traits has shown to increase the predictive power of the structure of ecological networks {[}\protect\hyperlink{ref-eklof2013}{40}{]}, an interesting novel approach is to investigate how a complete set of reproductive traits in the multidimensional trait space determine species interaction patterns {[}see \protect\hyperlink{ref-dehling2016}{41} for a morphological approach{]}.
+Thus, by exploring the plant reproductive spectrum of trait variation it is possible to delimit the different reproductive strategies and explore how these are associated with the different floral visitors.
 
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies {[}e.g., \protect\hyperlink{ref-carvalheiro2014}{41},\protect\hyperlink{ref-olesen2007}{42},\protect\hyperlink{ref-fortuna2010}{43}{]} or available in online archives {[}e.g., Mangal \protect\hyperlink{ref-poisot2016}{44},~The Web of Life \protect\hyperlink{ref-fortuna2010}{43}{]}.
+Many of these networks are freely available either as published studies {[}e.g., \protect\hyperlink{ref-carvalheiro2014}{42},\protect\hyperlink{ref-olesen2007}{43},\protect\hyperlink{ref-fortuna2010}{44}{]} or available in online archives {[}e.g., Mangal \protect\hyperlink{ref-poisot2016}{45},~The Web of Life \protect\hyperlink{ref-fortuna2010}{44}{]}.
 In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
@@
 
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} {[}\protect\hyperlink{ref-chamberlain2020}{45}{]}.
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} {[}\protect\hyperlink{ref-chamberlain2020}{46}{]}.
 We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
@@
 
-We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{46},\protect\hyperlink{ref-jin2019}{47}{]}.
+We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{47},\protect\hyperlink{ref-jin2019}{48}{]}.
 
@@
 
-To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{48}{]} which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{49}{]}.
-To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} {[}\protect\hyperlink{ref-santos2018}{50}{]} based on a previous conceptual framework that considers phylogenetic eigenvectors {[}\protect\hyperlink{ref-diniz-filho2012}{51}{]}.
+To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{49}{]} which allows imputation of datasets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{50}{]}.
+To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} {[}\protect\hyperlink{ref-santos2018}{51}{]} based on a previous conceptual framework that considers phylogenetic eigenvectors {[}\protect\hyperlink{ref-diniz-filho2012}{52}{]}.
 We conducted two different imputations, one for the full set of species (1,506 species, 5.79\% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (figure S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01\% of missing values).
@@
 Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{52},\protect\hyperlink{ref-legendre2012}{53}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as recomended for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{53}{]}.
+Due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{53},\protect\hyperlink{ref-legendre2012}{54}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
+Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as recommended for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{54}{]}.
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{54}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{55}{]}.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{55}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{56}{]}.
 Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
@@
 
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{54}{]} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{55}{]} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
@@
 For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency {[}\protect\hyperlink{ref-ballantyne2015}{56}{]}, the number of visits can provide valuable information of the contribution of floral visitors to pollination {[}\protect\hyperlink{ref-vazquez2005}{57},\protect\hyperlink{ref-vazquez2012}{58}{]}.
+Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency {[}\protect\hyperlink{ref-ballantyne2015}{57}{]}, the number of visits can provide valuable information of the contribution of floral visitors to pollination {[}\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}{]}.
 For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
@@
 This finding is consistent with previous research showing that \emph{A.
-mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems {[}\protect\hyperlink{ref-hung2018}{59}{]}.
+mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems {[}\protect\hyperlink{ref-hung2018}{60}{]}.
 Hence, to control for the effect of \emph{A.
@@
 
-We implemented Bayesian generalized linear mixed models using the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{60}{]}.
+We implemented Bayesian generalized linear mixed models using the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{61}{]}.
 We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
@@
 We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results {[}\protect\hyperlink{ref-burkner2017}{60}{]}.
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}\protect\hyperlink{ref-gabry2019}{61}{]}.
+The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so they have neglible influence on the results {[}\protect\hyperlink{ref-burkner2017}{61}{]}.
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}\protect\hyperlink{ref-gabry2019}{62}{]}.
 
@@
 Second, we investigated with Bayesian modelling how the main axes of trait variation determined different plant species' functional roles in the pollination network.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{62}{]} with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics that summarize species' functional roles were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{63}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{62}{]}.
+For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{63}{]} with a straightforward ecological interpretation relevant to our research goals.
+The different plant species-level metrics that summarize species' functional roles were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{64}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{63}{]}.
 We modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
@@
 
-The reproductive spectrum of flowering plants show clear positive and negative covariations between reproductive traits that shape the interactions of Angiosperms with their floral visitors at a global scale.
+The reproductive spectrum of flowering plants showed clear reproductive trait covariation patterns that shaped interactions with floral visitors at a global scale.
 Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively.
 These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
-Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{16},\protect\hyperlink{ref-carmona2021}{18}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
+Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{17},\protect\hyperlink{ref-carmona2021}{19}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
 Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds.
-However, they were insufficient to capture the visitation rates by guild or other species-level network metrics, which highlight the need to account for other local factors, such as species relative abuncances {[}\protect\hyperlink{ref-bartomeus2016}{33}{]}, to better understand the association of these mutualistic interactions at a macroecological scale.
-
-Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and links the reproductive spectrum with the previously described fast-slow continuum' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{64}{]} life-history strategies, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
-For instance, although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{20},\protect\hyperlink{ref-kettle2011}{21},\protect\hyperlink{ref-worley2000}{65}{]}, it has only been investigated across a few hundred of Angiosperm species with a pair-wise trait approach.
+However, they were insufficient to capture the visitation rates by guild or the other species-level network metrics considered in this study, which highlights the need to account for other local factors, such as species relative abundances {[}\protect\hyperlink{ref-bartomeus2016}{34}{]}, to better understand the association of plant-pollinator interactions at a macroecological scale.
+
+Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and links the reproductive spectrum with the previously described fast-slow continuum' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{65}{]} life-history strategies, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
+For instance, although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{21},\protect\hyperlink{ref-kettle2011}{22},\protect\hyperlink{ref-worley2000}{66}{]}, it has only been investigated across a few hundred Angiosperm species with a pair-wise trait approach.
 We found support to this trait association and show that other life history traits also covariate along this axis.
-Our study also complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{66}{]} by showing that most species with unisexual flowers are associated with woody life forms with high flower number.
-Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{22}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral displays.
+Our study also complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{67}{]} by showing that most species with unisexual flowers are associated with woody life forms with high flower number.
+Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{23}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
+Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral displays but in particular with species with larger flowers.
 Our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
 
-Overall, plant reproductive trait covariation axes help explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales.
-For example, as predicted by evolutionary life-history theory {[}\protect\hyperlink{ref-stebbins1970}{67}{]}, larger investments floral size and rewards to attract pollinators makes sense when pollinator dependence is higher, but this might trade off with the resources allocated to ovule production \href{Anne\%20Leonard\%20tenia\%20algo\%20de\%20eso,\%20creo}{mirate la literatura de esto\ldots{} seguro que hay papers.
-Además, si esto que digo l apoyan los datos, puede ser algo que la gente querra citar (YO QUIEREO!) asi que dejalo explicito}.
-Interestingly, by combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings {[}\protect\hyperlink{ref-hegland2005}{68}--\protect\hyperlink{ref-kaiser2014}{70}{]}.
-Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes {[}\protect\hyperlink{ref-dellinger2020}{4},\protect\hyperlink{ref-rosas2014}{31},\protect\hyperlink{ref-faegri2013}{71}{]}.
-For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies \href{}{name which ones} and because these two guilds are likely to differ in ecology and behaviour {[}\protect\hyperlink{ref-rader2020}{72},\protect\hyperlink{ref-foldesi2021}{73}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{33},\protect\hyperlink{ref-vazquez2007}{74},\protect\hyperlink{ref-encinas2012}{75}{]} that reproductive correlations do not.
-
-We provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of reproductive traits from plant species that belong to plant-pollinator networks.
-Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider factors such as plant reproductive strategies, and not only flower morphology, to better capture broad scale patterns of interactions with floral visitors.
-In addition, we provide empirical evidence that complements previous trait correlation studies along other plant organs and highlights the need to include reproductive trait correlations in the global spectrum of plant form and function {[}\protect\hyperlink{ref-diaz2016}{16}{]}, as the different plant reproductive strategies involve clear cost and benefits that can affect resource allocation to other morphological and physiological traits.
+Overall, plant reproductive trait covariation axes helped explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales.
+For example, we found that all floral visitor guilds interacted more frequently with plant species with larger flowers and higher pollinator dependence in agreement with previous findings {[}\protect\hyperlink{ref-hegland2005}{68}--\protect\hyperlink{ref-kaiser2014}{70}{]}.
+As predicted by evolutionary life-history theory {[}\protect\hyperlink{ref-stebbins1970}{71}{]}, larger investment on floral display and rewards to attract pollinators makes sense when pollinator dependence is higher, but this investment is compromised by the cost of the different reproductive structures, trait associations and the distinct selective pressures such as the one exerted by the different floral visitor guilds {[}\protect\hyperlink{ref-galen1999}{72}{]}.
+For instance, smaller flowers were less visited overall, but they are inexpensive (e.g., low ovule number) and can counterpart this lack of visitation at the flower level by increasing the chances of visitation at the whole individual level with larger displays as suggested for wind pollinated species where small numerous flowers can increase the chances of pollen capture and seed production {[}\protect\hyperlink{ref-friedman2011}{73}{]}.
+In addition, because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations found between reproductive traits and floral visitor guilds also may indicate the existence of large scale pollination syndromes {[}\protect\hyperlink{ref-dellinger2020}{4},\protect\hyperlink{ref-rosas2014}{32},\protect\hyperlink{ref-faegri2013}{74}{]}.
+For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies on all axes and because these two guilds are likely to differ in ecology and behaviour {[}\protect\hyperlink{ref-rader2020}{75},\protect\hyperlink{ref-foldesi2021}{76}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
+In any case, it is worth noting that other local factors such as species relative abundances, phenology or trait matching, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{34},\protect\hyperlink{ref-vazquez2007}{77},\protect\hyperlink{ref-encinas2012}{78}{]} that reproductive trait correlations do not.
+
+Our study provides a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of reproductive traits from plant species that belong to plant-pollinator networks.
+Additionally, we highlight the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider factors such as plant reproductive strategies, and not only flower morphology, to better capture broad scale patterns of interactions with floral visitors.
+Further, we provide empirical evidence that complements previous trait correlation studies along other plant organs and we highlights the need to include reproductive trait correlations in the global spectrum of plant form and function {[}\protect\hyperlink{ref-diaz2016}{17}{]}, as the different plant reproductive strategies involve clear cost and benefits that can affect resource allocation to other morphological and physiological traits.
 Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and understanding of the different plant-pollinator associations.
-
-\href{}{Me falta un parrafo de por que esto es importante o que puede hacer la gente con esto.
-Seria el penultimo parrafo, por ejemplo, como afecta esto a la gente haciendo coexistencia (e.g.~el paper de Pauw y el tuyo).
-Como afecta esto a la gente hacienco estabilidad y estructura de polinizadores.
-Como afecta esto a ecologos evolutivos?}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-song2022}{}}%
+\CSLLeftMargin{11. }
+\CSLRightInline{Song B \emph{et al.} 2022 Global analysis of floral longevity reveals latitudinal gradients and biotic and abiotic correlates.
+\emph{New Phytologist} (doi:\href{https://doi.org/10.1111/nph.18271}{10.1111/nph.18271})}
+
 \leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
-\CSLLeftMargin{11. }
+\CSLLeftMargin{12. }
 \CSLRightInline{Laughlin DC \emph{et al.} 2021 Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%
-\CSLLeftMargin{12. }
+\CSLLeftMargin{13. }
 \CSLRightInline{Wright IJ \emph{et al.} 2004 The worldwide leaf economics spectrum. \emph{Nature} \textbf{428}, 821--827. (doi:\href{https://doi.org/10.1038/nature02403}{10.1038/nature02403})}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
-\CSLLeftMargin{13. }
+\CSLLeftMargin{14. }
 \CSLRightInline{Chave J, Coomes D, Jansen S, Lewis SL, Swenson NG, Zanne AE.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
-\CSLLeftMargin{14. }
+\CSLLeftMargin{15. }
 \CSLRightInline{Kattge J \emph{et al.} 2011 {TRY} \textendash{} a global database of plant traits.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
-\CSLLeftMargin{15. }
+\CSLLeftMargin{16. }
 \CSLRightInline{Salguero-Gómez R \emph{et al.} 2015 The compadre {Plant Matrix Database}: An open online repository for plant demography.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
-\CSLLeftMargin{16. }
+\CSLLeftMargin{17. }
 \CSLRightInline{Díaz S \emph{et al.} 2016 The global spectrum of plant form and function. \emph{Nature} \textbf{529}, 167--171. (doi:\href{https://doi.org/10.1038/nature16489}{10.1038/nature16489})}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
-\CSLLeftMargin{17. }
+\CSLLeftMargin{18. }
 \CSLRightInline{Bruelheide H \emph{et al.} 2018 Global trait--environment relationships of plant communities.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
-\CSLLeftMargin{18. }
+\CSLLeftMargin{19. }
 \CSLRightInline{Carmona CP \emph{et al.} 2021 Erosion of global functional diversity across the tree of life.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
-\CSLLeftMargin{19. }
+\CSLLeftMargin{20. }
 \CSLRightInline{E-Vojtkó A, Bello F de, Durka W, Kühn I, Götzenberger L.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
-\CSLLeftMargin{20. }
+\CSLLeftMargin{21. }
 \CSLRightInline{Sargent RD, Goodwillie C, Kalisz S, Ree RH.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
-\CSLLeftMargin{21. }
+\CSLLeftMargin{22. }
 \CSLRightInline{Kettle CJ, Maycock CR, Ghazoul J, Hollingsworth PM, Khoo E, Sukri RSH, Burslem DFRP.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{23. }
 \CSLRightInline{Goodwillie C \emph{et al.} 2010 Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{24. }
 \CSLRightInline{Barrett SCH.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{25. }
 \CSLRightInline{Moeller DA \emph{et al.} 2017 Global biogeography of mating system variation in seed plants.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-baude2016}{}}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{26. }
 \CSLRightInline{Baude M, Kunin WE, Boatman ND, Conyers S, Davies N, Gillespie MA, Morton RD, Smart SM, Memmott J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{27. }
 \CSLRightInline{Munoz F, Violle C, Cheptou P-O.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-grossenbacher2017}{}}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{28. }
 \CSLRightInline{Grossenbacher DL \emph{et al.} 2017 Self-compatibility is over-represented on islands.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Sargent RD, Ackerly DD.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rech2016}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Rech AR, Dalsgaard B, Sandel B, Sonne J, Svenning J-C, Holmes N, Ollerton J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Rüger N, Comita LS, Condit R, Purves D, Rosenbaum B, Visser MD, Wright SJ, Wirth C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{32. }
 \CSLRightInline{Rosas-Guerrero V, Aguilar R, Martén-Rodríguez S, Ashworth L, Lopezaraiza-Mikel M, Bastida JM, Quesada M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{33. }
 \CSLRightInline{Stang M, Klinkhamer PGL, Waser NM, Stang I, van der Meijden E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{34. }
 \CSLRightInline{Bartomeus I, Gravel D, Tylianakis JM, Aizen MA, Dickie IA, Bernard-Verdier M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{35. }
 \CSLRightInline{Tur C, Castro-Urgal R, Traveset A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{36. }
 \CSLRightInline{Junker RR, Blüthgen N, Brehm T, Binkenstein J, Paulus J, Schaefer HM, Stang M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Coux C, Rader R, Bartomeus I, Tylianakis JM.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Ibanez S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Devaux C, Lepers C, Porcher E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Eklöf A \emph{et al.} 2013 The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583. (doi:\href{https://doi.org/10.1111/ele.12081}{10.1111/ele.12081})}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Dehling DM, Jordano P, Schaefer HM, Böhning-Gaese K, Schleuning M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Carvalheiro LG \emph{et al.} 2014 The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Olesen JM, Bascompte J, Dupont YL, Jordano P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Fortuna MA, Stouffer DB, Olesen JM, Jordano P, Mouillot D, Krasnov BR, Poulin R, Bascompte J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Poisot T \emph{et al.} 2016 Mangal \textendash{} making ecological network analysis simple.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Chamberlain S \emph{et al.} 2020 Taxize: {Taxonomic} information from around the web.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Smith SA, Brown JW.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Jin Y, Qian H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Stekhoven DJ, Bühlmann P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Penone C, Davidson AD, Shoemaker KT, Marco MD, Rondinini C, Brooks TM, Young BE, Graham CH, Costa GC.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Chamberlain S \emph{et al.} 2018 Package {``{PVR}''}. R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}. }
@@
 \leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Diniz-Filho JAF, Bini LM, Rangel TF, Morales-Castilla I, Olalla-Tárraga MÁ, Rodríguez MÁ, Hawkins BA.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-serneels2008}{}}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Serneels S, Verdonck T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Legendre P, Legendre L. 2012 \emph{Numerical ecology}. {2nd edn}. {Elsevier, Amsterdam}. }
@@
 \leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Revell LJ.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Abdi H, Williams LJ. 2010 Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459. (doi:\href{https://doi.org/10.1002/wics.101}{10.1002/wics.101})}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{57. }
 \CSLRightInline{Ballantyne G, Baldock KCR, Willmer PG.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
-\CSLLeftMargin{57. }
+\CSLLeftMargin{58. }
 \CSLRightInline{Vázquez DP, Morris WF, Jordano P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
-\CSLLeftMargin{58. }
+\CSLLeftMargin{59. }
 \CSLRightInline{Vázquez DP, Lomáscolo SB, Maldonado MB, Chacoff NP, Dorado J, Stevani EL, Vitale NL.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
-\CSLLeftMargin{59. }
+\CSLLeftMargin{60. }
 \CSLRightInline{Hung K-LJ, Kingston JM, Albrecht M, Holway DA, Kohn JR.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
-\CSLLeftMargin{60. }
+\CSLLeftMargin{61. }
 \CSLRightInline{Bürkner P-C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
-\CSLLeftMargin{61. }
+\CSLLeftMargin{62. }
 \CSLRightInline{Gabry J, Simpson D, Vehtari A, Betancourt M, Gelman A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
-\CSLLeftMargin{62. }
+\CSLLeftMargin{63. }
 \CSLRightInline{Dormann CF, Gruber B, Fründ J. 2008 Introducing the bipartite package: Analysing ecological networks. \emph{R News} \textbf{8/2}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
-\CSLLeftMargin{63. }
+\CSLLeftMargin{64. }
 \CSLRightInline{Blüthgen N, Menzel F, Blüthgen N.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
-\CSLLeftMargin{64. }
+\CSLLeftMargin{65. }
 \CSLRightInline{Healy K, Ezard THG, Jones OR, Salguero-Gómez R, Buckley YM.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-worley2000}{}}%
-\CSLLeftMargin{65. }
+\CSLLeftMargin{66. }
 \CSLRightInline{Worley AC, Baker AM, Thompson JD, Barrett SC.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-petit2006}{}}%
-\CSLLeftMargin{66. }
+\CSLLeftMargin{67. }
 \CSLRightInline{Petit RJ, Hampe A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-stebbins1970}{}}%
-\CSLLeftMargin{67. }
-\CSLRightInline{Stebbins GL.
-1970 Adaptive radiation of reproductive characteristics in angiosperms, i: Pollination mechanisms.
-\emph{Annual Review of Ecology and Systematics}, 307--326.
-(doi:\href{https://doi.org/10.1146/annurev.es.01.110170.001515}{10.1146/annurev.es.01.110170.001515})}
-
 \leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-stebbins1970}{}}%
+\CSLLeftMargin{71. }
+\CSLRightInline{Stebbins GL.
+1970 Adaptive radiation of reproductive characteristics in angiosperms, i: Pollination mechanisms.
+\emph{Annual Review of Ecology and Systematics}, 307--326.
+(doi:\href{https://doi.org/10.1146/annurev.es.01.110170.001515}{10.1146/annurev.es.01.110170.001515})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-galen1999}{}}%
+\CSLLeftMargin{72. }
+\CSLRightInline{Galen C.
+1999 Why do flowers vary?
+The functional ecology of variation in flower size and form within natural plant populations.
+\emph{Bioscience} \textbf{49}, 631--640.
+(doi:\href{https://doi.org/10.2307/1313439}{10.2307/1313439})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-friedman2011}{}}%
+\CSLLeftMargin{73. }
+\CSLRightInline{Friedman J, Barrett SC.
+2011 The evolution of ovule number and flower size in wind-pollinated plants.
+\emph{The American Naturalist} \textbf{177}, 246--257.
+(doi:\href{https://doi.org/10.1086/657954}{10.1086/657954})}
+
 \leavevmode\vadjust pre{\hypertarget{ref-faegri2013}{}}%
-\CSLLeftMargin{71. }
+\CSLLeftMargin{74. }
 \CSLRightInline{Faegri K, Van Der Pijl L. 2013 Principles of pollination ecology. }
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rader2020}{}}%
-\CSLLeftMargin{72. }
+\CSLLeftMargin{75. }
 \CSLRightInline{Rader R, Cunningham S, Howlett B, Inouye D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
-\CSLLeftMargin{73. }
+\CSLLeftMargin{76. }
 \CSLRightInline{Földesi R, Howlett BG, Grass I, Batáry P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
-\CSLLeftMargin{74. }
+\CSLLeftMargin{77. }
 \CSLRightInline{Vázquez DP, Melián CJ, Williams NM, Blüthgen N, Krasnov BR, Poulin R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
-\CSLLeftMargin{75. }
+\CSLLeftMargin{78. }
 \CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS.
@@
 
-\textbf{Data accessibility.} All data and code used to conduct this study is available at Zenodo (\url{https://doi.org/10.5281/zenodo.6705621}) and Github (\url{https://github.com/JoseBSL/Reproductive-traits}).
-
-\textbf{Authors'contributions.} JBL, RR and IB designed the study.
+\textbf{Data accessibility.} All data and code used to conduct this study are available in the online repositories of Zenodo (\url{https://doi.org/10.5281/zenodo.6705621}) and Github (\url{https://github.com/JoseBSL/Reproductive-traits}).
+
+\textbf{Authors' contributions.} JBL, RR and IB designed the study.
 JBL collated the data and conducted analysis with guidance of JS, LKK and IB.
@@
 We also thank Jason Tylianakis for his comments on the manuscript before submission.
-Finally, we thank Marcos Méndez, Susan Kalisz, Amanda Benoit, May Berenbaum and an anonimous reviewer for thoughtful feedback and useful comments on earlier versions of this manuscript.
+Finally, we thank Marcos Méndez, Susan Kalisz, Amanda Benoit, May Berenbaum and an anonymous reviewer for thoughtful feedback and useful comments on earlier versions of this manuscript.
 

### 2022-07-11 Google_drive.R

@@ -1,0 +1,21 @@
+
+
+#Upload files to google drive
+#install packages
+remotes::install_github("claudiozandonella/trackdown",
+                        build_vignettes = TRUE, force=T)
+
+install.packages("googledrive")
+
+#set google doc
+googledrive::drive_auth()
+
+#load libraries
+library(googledrive)
+library(trackdown)
+
+#upload file
+upload_file(
+  file = "Manuscript/Lanuza_et_al_2022.Rmd", 
+  gfile = "Untitled"
+)

### 2022-07-19 Manuscript/Lanuza_et_al_2022.Rmd
style edits

@@
 ---
-title: \singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors
+title: \singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shapes interactions with floral visitors
 
@@
 
-Plants have an enormous variation of life history strategies and trait combinations.
-However, there is strong evidence that there are evolutionary and physiological constraints that limit the number of plant ecological strategies.
-Despite recent advances in the understanding of plant trait correlations, reproductive traits are often not considered despite its key role in shaping both plant life-history strategies and plants interactions with floral visitors.
-Here, we investigate the reproductive spectrum of flowering plants and how this drive the establishment of interactions with their floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
-We found that over 50% of all trait variation was explained by the first two reproductive axes.
-Specifically, the first axis indicated the presence of a negative correlation between flower number and flower size while the second axis showed a positive correlation between pollinator dependence and floral display.
-These different reproductive axes determined important differences in the interaction level among floral visitor guilds but were insufficient to fully capture plant-pollinator associations.
-Our study shows the main reproductive trait correlations of flowering plants and highlights their relevance to understand plant-pollinator interactions in a global context.
+Globally, plants display enormous variation in life history strategies and trait combinations.
+However, evidence suggests that evolutionary and physiological constraints limit the number of plant ecological strategies.
+Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with floral visitors.
+Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with floral visitors.
+We show that over 50% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the positive correlation between pollinator dependence and floral display size.
+In empirical plant-pollinator networks, the plant position within these axes was associated with the number of interacting partners and the visitation rates of the distinct floral visitor guilds, but the unexplained variability found highlights the need to incorporate other factors along with reproductive traits to fully explain plant-pollinator interactions.
+Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping networks of plant-pollinator interactions at a global scale.
 
@@
 
-Flowering plants have an astonishing diversity of floral structures [@barrett2002; @schiestl2013] that shape their interactions with animal pollinators [@fenster2004; @dellinger2020].
-The variety of reproductive strategies followed by different plant species, from specialized reliance on a single pollinator, to full self-pollination, is incredibly rich.
-However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
-Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@salguero2016; @friedman2020; @paterno2020; @roddy2021; @song2022], their study is often limited to a few number of reproductive traits that are rarely studied in combination.
-Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other root [@laughlin2021], leaf [@wright2004] or wood [@chave2009] related traits, there is a need to acquire a multitrait perspective with broad geographical coverage.
-Importantly, the characterization of the plant reproductive spectrum can help to further understand the different plant ecological strategies [@agrawal2020] and improve our knowledge on plant-pollinator associations [@roddy2021].
-
-With the recent availability of large trait databases [e.g., TRY @kattge2011;  COMPADRE @salguero2015], plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
-However, most studies with a multitrait perspective have overlooked plant reproductive traits [@evojtko2020; @roddy2021] and focused on trait correlations from other plant organs.
-Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number [@sargent2007; @kettle2011], the positive association between flower size and outcrossing rate [@goodwillie2010] or the positive association between outcrossing rate and lifespan [@barrett2003; @moeller2017].
-Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships [@roddy2021], we still lack empirical evidence that investigates jointly how these different reproductive trait associations shape plant life history strategies.
-
-Despite this increasing number of macroecological studies that investigate specific plant reproductive traits [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017], we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales [@sargent2008; @rech2016; @salguero2016; @ruger2018].
-The use of trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-For example, plant traits can define species' network roles [e.g., specialists vs generalists @tur2013] and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators [@junker2013; @coux2016].
-Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure [@stang2009; @ibanez2012].
-However, is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations [@tur2013; @devaux2014].
-Indeed, the pollination system of a great number of plant species remains unexplored [@dellinger2020].
-Because both the species' morphology and mating system can determine the species' functional role in the pollination network and the combination of several traits has shown to increase the predictive power of the structure of ecological networks [@eklof2013], an interesting novel approach is to investigate how a complete set of reproductive traits in the multidimensional trait space determine species interaction patterns [see @dehling2016 for a morphological approach].
-Thus, by exploring the plant reproductive spectrum of trait variation it is possible to delimit the different reproductive strategies and explore how these are associated with the different floral visitors.
-
-Here, we aim to progress knowledge on the reproductive trait covariation patterns and their association with the different floral visitor guilds by exploring at a broad geographical scale the reproductive spectrum of trait variation of flowering plants from plant-pollination networks.
-First, we investigate what are the major axes of reproductive trait variation and trait correlations for the different plant species.
-Second, we investigate the association between the plant species' position in the multidimensional trait-space and the different floral visitor guilds with the help of qualitative (presence-absence of interaction) and quantitative (number of visits) information about plant-pollinator interactions.
-Finally, we investigate how the main axes of trait variation influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
+Flowering plants display an astonishing diversity of reproductive structures [@barrett2002; @schiestl2013] that shape their interactions with animal pollinators [@fenster2004; @dellinger2020].
+The variety of reproductive strategies used by different plant species, from specialized reliance on a single pollinator, to full self-pollination, is incredibly rich.
+However, not all reproductive trait combinations in plants are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
+Despite recent advances in theoretical and empirical understanding of correlations between plant reproductive traits at large ecological scales [@salguero2016; @friedman2020; @paterno2020; @roddy2021; @song2022], studies typically focus on just a few traits, often in isolation.
+Thus, to develop a comprehensive understanding of the plant reproductive spectrum of trait variation, as done recently for root [@laughlin2021], leaf [@wright2004] and wood [@chave2009] related traits, we require a multi-trait perspective with broad geographical coverage.
+Importantly, characterization of the plant reproductive spectrum could reveal key reproductive strategies among different species [@agrawal2020] and improve knowledge of associations between specific reproductive traits and pollinators [@roddy2021].
+
+With the recent availability of large trait databases [e.g., TRY @kattge2011;  COMPADRE @salguero2015], there has been increased research on plant ecological strategies, which has produced identification of global patterns in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
+However, studies that look at multiple traits tend to overlook plant reproductive traits [@evojtko2020; @ruger2018; @roddy2021], and focus on trait correlations in other plant organs such as morphological and physiological leaf traits [@wright2004; @shipley2006; @donovan2011; @osnas2013].
+Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs (e.g., the negative correlation between flower size and flower number [@sargent2007; @kettle2011]; the positive association between flower size and outcrossing rate [@goodwillie2010]; or the positive correlation between outcrossing rate and lifespan [@barrett2003; @munoz2016; @moeller2017]).
+Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships [@roddy2021], we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
+
+Trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] are powerful for exploring the underlying mechanisms driving plant-pollinator interactions.
+For example, plant traits can define species' network roles [e.g., specialists vs generalists @tur2013] and plant species that occupy reproductive trait space extremes are likely to be more specialized and display tighter trait-matching with pollinators [@junker2013; @coux2016].
+Indeed, the degree of morphological matching between plants and floral visitors often determines whether or not interactions occur, and consequently influences  the broader network structure [@stang2009; @ibanez2012].
+However, it is still unclear how specific reproductive traits (e.g., mating or compatibility system) influence plant-pollinator associations [@sargent2008; @tur2013; @devaux2014].
+Indeed, both morphology and mating system can determine a species' functional role within pollination networks, and the combination of several traits increases power for predicting network structure [@eklof2013].
+Because the species position within the multidimensional trait space can result in different interaction patterns or adaptations to pollinators [see @dehling2016 for a purely morphological approach], the use of the reproductive trait space to explore plant-pollinator interactions could help to identify species functional roles and associations of traits with specific pollinators (i.e., pollination syndromes).
+
+Here, we explore the spectrum of reproductive traits in flowering plants, within a global set of plant-pollinator networks, to identify reproductive trait covariation and how this influences the network of interactions between plants and floral visitors.
+First, we identify the major axes of reproductive trait variation and correlations among traits for plant species.
+Then, we investigate the associations between plant species’ positions in reproductive trait space and the strength of their interactions with different floral visitor guilds within networks.
+Finally, we determine how the main axes of reproductive trait variation influence plant species' functional roles within pollination networks, using a range of complementary interaction network metrics.
 
@@
 We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see table S1 and figure S1).
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different biological communities.
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies [e.g., @carvalheiro2014; @olesen2007; @fortuna2010] or available in online archives [e.g., Mangal @poisot2016;  The Web of Life @fortuna2010].
-In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different ecological communities.
+Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to benefit, to some degree, from animal pollination.
+Many of these networks are freely available either as published studies [e.g., @carvalheiro2014; @olesen2007; @fortuna2010] or in online archives [e.g., Mangal @poisot2016;  The Web of Life @fortuna2010].
+In total, our network dataset constituted 60 weighted (number of visits) and four unweighted (interaction presence-absence) networks, each sampled at a unique location and year, as well as eight meta-networks where interactions were pooled across several locations and multiple years.
 
@@
 
-We selected a total of 19 different quantitative and categorical functional traits that comprised reproductive traits and plant form and size related traits (see table 1).
-Reproductive traits consisted of floral traits and reproductive biology traits: (i) floral traits included traits related to the size of floral organs (e.g., style length), floral display (e.g., flower number) or floral rewards (e.g., pollen quantity) while (ii) reproductive biology traits indicated the reproductive system of the plant (i.e., breeding, mating and compatibility system).
-The remaining traits were plant size and form related traits that are commonly used to characterize the fast-slow continuum of plant trait variation (i.e., plant height, lifespan and life form).
+We selected a total of 19 quantitative and categorical functional traits that included reproductive traits and traits related with plant form and size (see table 1).
+Reproductive traits consisted of those related to floral and reproductive biology: (i) floral traits included those related to the size of floral organs (e.g., style length), floral display size (e.g., flower number) and floral rewards (e.g., pollen quantity), while (ii) reproductive biology traits represented the plant reproductive system (i.e., the breeding, mating and compatibility system).
+The remaining traits were related to plant size and form (i.e., plant height, lifespan and life form), which are commonly used to characterize the fast-slow continuum of plant trait variation [@salguero2016].
 For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 possible cells considering all traits and plant species (20 columns × 1,506 species), we were able to fill 24,341 cells (80.8% of the dataset, see figure S2 for missing values information for each trait).
+From a matrix comprising a total of 28,614 possible cells (considering all traits and plant species: 19 columns × 1,506 species), we were able to fill 23,354 cells (81.6% of the dataset, see figure S2 for missing value information for each trait).
 An extended description of each trait and how it was obtained can be found in Appendix S1.
@@
 
-We calculated the phylogenetic distance between different plant species using the function *get_tree* from the package *rtrees* (<https://github.com/daijiang/rtrees>), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
+We calculated the phylogenetic distance between all plant species considered using the function *get_tree* from the package *rtrees* (<https://github.com/daijiang/rtrees>), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
 
@@
 
-To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of *missForest* [@penone2014].
+To avoid excluding species with trait missing values, we imputed trait missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of datasets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors from principal component analysis of the phylogenetic distance (PCoA), which has been shown to improve the performance of *missForest* [@penone2014].
 To extract the eigenvectors, we used the function *PVRdecomp* from the package *PVR* [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-We conducted two different imputations, one for the full set of species (1,506 species, 5.79% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (figure S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
+We conducted two different imputations, one for the full set of species (1,506 species: 5.79% of missing values), and excluded nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01% of missing values).
+To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and results for the two datasets were consitent (Fig S3 and Fig S4).
 
@@
 
-We explored the association between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+We explored the association between the different quantitative plant traits using a phylogenetically informed Principal Component Analysis (pPCA).
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
 Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as recommended for principal component analysis [@legendre2012].
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
-We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation [@abdi2010].
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
-For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
+Specifically, due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
+Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis [@legendre2012].
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
+We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode “covariance” because values for each variables were on the same scale following transformation [@abdi2010].
+Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity data.
+For this, we included all quantitative traits included in the main pPCA, plus pollen grains and microlitres of nectar per flower.
 
@@
 
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package *phytools* [@revell2012] and we used Pagel's $\lambda$ as a measurement of the phylogenetic signal.
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package *phytools* [@revell2012] and used Pagel's $\lambda$ as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
@@
 
-First, we used Bayesian modelling (see below for details) to investigate how the different groups of floral visitors interacted along the main axes of reproductive trait variation with the help of qualitative and quantitative information of plant-pollinator interactions.
-For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency [@ballantyne2015], the number of visits can provide valuable information of the contribution of floral visitors to pollination [@vazquez2005; @vazquez2012].
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that *Apis mellifera* was the floral visitor with the largest proportion of records counted (7.55% of the total).
-This finding is consistent with previous research showing that *A.
+We used Bayesian modeling (see details below) to investigate how the different guilds of floral visitors interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
+Specifically, interactions between plants and floral visitors in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
+Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species [@ballantyne2015], the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination [@vazquez2005; @vazquez2012].
+We divided floral visitors into six main taxonomical guilds that differ in life form, behaviour and thus likely play similar ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
+Moreover, because bees had the greatest number of occurrences in networks  (2,256 records) and the highest frequency of visits, we further broke this group down into the main bee families (Andrenidae, Apidae, Colletidae, Halictidae, and Megachilidae).
+In addition, we found that *Apis mellifera* was the floral visitor with the largest proportion of occurrences in networks (7.55% of the total).
+This is consistent with previous research showing that *A.
 mellifera* was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
 Hence, to control for the effect of *A.
-mellifera* on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding *A.
+mellifera* on observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding *A.
 mellifera*.
@@
 
-We implemented Bayesian generalized linear mixed models using the R package *brms* [@burkner2017].
-We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
-We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so they have neglible influence on the results [@burkner2017].
+We used Bayesian generalized linear mixed models in the R package *brms* [@burkner2017] to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in visitation patterns among floral visitor guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds in the model.
+We added a nested random effect of networks within the study system to capture the variation in networks among studies and within networks.
+Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence among them.
+We specified for the presence or absence of an interaction and number of visits with Bernoulli and a zero inflated negative binomial distributions, respectively.
+The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results [@burkner2017].
 We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the *bayesplot* package [@gabry2019].
@@
 
-Second, we investigated with Bayesian modelling how the main axes of trait variation determined different plant species' functional roles in the pollination network.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies [@dormann2008] with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics that summarize species' functional roles were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the *specieslevel* function from the R package *bipartite* [@dormann2008].
-We modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
-For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
+We also used Bayesian modeling to investigate how the main axes of trait variation determined different plant species' functional roles within pollination networks.
+For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies [@dormann2008], with clear ecological interpretations and are relevant for defining species' functional roles in networks.
+Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the *specieslevel* function in the R package *bipartite* [@dormann2008].
+We modeled each plant species metric (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
+For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree, and zero-one inflated beta for specialization).
 Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the 'visitation patterns' section.
 
-Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across studies but this was accounted for in analyses by considering them in the random effects of the modelling process.
+Our analyses were conducted on the subset of 60 weighted networks (out of a total of 64 networks) sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+In total, our network dataset (excluding meta- and non-weighted networks) included 2,256 interactions for bees, 1,768 for non-syrphid-dipterans, 845 for syrphids, 437 for lepidopterans, 432 for coleopterans, and 362 for non-bee-hymenopterans.
+Sampling methods varied across studies but this was accounted for in analyses by including study identity as a  random effect in our models.
 All analyses were conducted in R version *4.0.3*.
@@
 
-The phylogenetically informed principal component analysis captured by the first two and three axes 51.8% and 70.97% of the reproductive trait variation, respectively (figure 1 and figure S6).
-The first principal component (PC1 or the flower number - flower size axis) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; table S3) but style length also contributed moderately to PC1 (loading = -0.33).
+Our phylogenetically informed principal component analysis captured  51.8% and 70.97% of the reproductive trait variation in the first two and three axes, respectively (figure 1 and figure S6).
+The first principal component (PC1; the flower number - flower size axis) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; table S3) but style length also contributed moderately (loading = -0.33).
 One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-For instance, on this end of the spectrum we find the species *Cornus florida* which has approximately a total of 10.000 flowers, an average height of 7.5m, flowers of 3mm wide, a style length of 3.5mm and a total of 2 ovules per flower.
-The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-For instance, on this other end, we find the species *Petunia axillaris* that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
-The second principal component (PC2 or the pollinator dependence axis) represented 25.05% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; table S3).
-In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles.
-On this extreme of the spectrum we find the species *Zuccagnia punctata* that is a self-incompatible shrub that depends completely on floral visitors for seed production, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm.
-In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
-As an example of this reproductive extreme, we find the species *Veronica peregrina* which is a self-compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
-Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \|-0.51\|) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
-The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; table S3).
-In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with floral display.
-Floral rewards were specially strongly correlated with flower size but slightly correlated with flower number (figure S4).
-This pPCA explained similar variance with the first two principal components (45.52%) and similar associations of traits despite some variability in the loadings (table S4).
+For instance, *Cornus florida* occurred at this end of the spectrum, which, on average, has approximately 10,000 flowers, is 7.5 m high, has flowers that are 3 mm wide, styles 3.5 mm long and  two ovules per flower.
+The other end of this spectrum had species that were short in height, with few large flowers that had long styles and many ovules.
+For example, *Petunia axillaris* on average, is 0.5 m high and has approximately 10 flowers per plant that are over 50 mm wide with 25 mm long styles and over 200 ovules.
+The second principal component (PC2; the pollinator dependence axis) encompassed 25.05% of the trait variation and represented variation from low to high autonomous selfing (i.e., high to low pollinator dependence).
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but all other traits (except ovule number) made moderate contributions (loadings ranging between 0.27 to 0.4; table S3).
+Generally speaking, species with high pollinator dependence had larger and many flowers with long styles, and were tall.
+*Zuccagnia punctata* occurred at this extreme of the spectrum, which is a self-incompatible species, completely dependent on animal pollination for seed production, producing  approximately 1,500 flowers per plant with an average height of 3 m and 20 mm long styles.
+In contrast, species with low pollinator dependence tended to have fewer and smaller flowers with shorter styles, and were shorter in height.
+*Veronica peregrina* occurred at this end of the spectrum, and is a self-compatible plant that requires little or no pollination by animals, it has approximately 20 flowers per plant, is 0.2 m high and has 0.25 mm long styles.
+The third principal component (PC3; the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \|-0.51\|), where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
+The remaining traits, apart from ovule number, were all positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; table S3).
+In addition, the pPCA with the subset of species that we had nectar and pollen quantity data for showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with floral display size.
+Floral rewards were particularly strongly correlated with flower size but weakly correlated with flower number (figure S4).
+The first two principal components for this pPCA explained similar variance  (45.52%) and similar associations of traits, despite some variability in the loadings (table S4).
 
@@
 We found that most categorical traits were statistically associated with the first two axes of trait variation (figure 2 and table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed lack of statistical association.
-In addition, we found statistical differences between the different levels of categorical traits in the trait space (figure S7).
+Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed a lack of statistical association.
+In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S7).
 Regarding self-compatibility, we found larger differences on PC2.
-For instance, species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility on this vertical axis (figure S7a and figure S7b; Tukey test *P* \< 0.05).
+For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S7a and figure S7b; Tukey test *P* \< 0.05).
 Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S7c and figure S7d; Tukey test *P* \< 0.05).
 Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f; Tukey test *P* \< 0.05).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h; Tukey test *P* \< 0.05).
-Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S7i and figure S7j; Tukey test *P* \< 0.05).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S7k and figure S7l; Tukey test *P* \< 0.05).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h; Tukey test *P* \< 0.05).
+Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and high pollinator dependence, while the latter had more flowers and lower pollinator dependence (figure S7i and figure S7j; Tukey test *P* \< 0.05).
+Finally, in terms of flower symmetry, zygomorphic flowers were associated with lower pollinator dependence, whereas actinomorphic flowers were more dependent on pollinators (figure S7k and figure S7l; Tukey test *P* \< 0.05).
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="80%",fig.align='center',fig.cap= "\\textbf{Figure 2.} Location of the different qualitative traits on the trait space.
-The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
-The solid arrows indicate the direction of variation of the different quantitative traits showed in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="80%",fig.align='center',fig.cap= "\\textbf{Figure 2.} Location of the different qualitative traits in the trait space.
+The figure panel is composed of the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
+The solid arrows indicate the direction of variation of the different quantitative traits shown in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S)."}
 
@@
 The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
-The traits that showed a moderate phylogenetic signal were inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits ($\lambda$ = 0.14).
+The traits that had a moderate phylogenetic signal included inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
+Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all the traits we measured ($\lambda$ = 0.14).
 
@@
 
-The main axes of trait variation (PC1, PC2 and PC3) explained partly presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the overall number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (figure 3).
-We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (figure 3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
-Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high number of small flowers (figure 3d).
-On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (figure 3b and figure 3e).
-Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (figure 3c).
-Plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (figure 3f).
-
-The additional model for the most represented families of bees for both presence-absence of interaction (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03) showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (figure 3a and figure 3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (figure S8).
+The main axes of trait variation (PC1, PC2 and PC3) partly explained the presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the total number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
+However, we found relevant differences across the different floral visitor guilds for both the presence-absence of interactions and number of visits (figure 3).
+On the flower number - flower size axis, we found  that plants with many small flowers tended to have interaction partners that were Coleoptera, non-bee-Hymenoptera and Diptera (figure 3a), whereas plants with few large flowers mostly had interaction partners that were bees and Lepidoptera.
+We found similar trends for visitation rates on the flower number - flower size axis,  but bees and syrphids visited plant species with many small flowers more frequently (figure 3d).
+On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had many interaction partners and recieved many visits from all floral visitor guilds (figure 3b and figure 3e).
+Finally, on the style length - pollinator dependence axis, plant species with short styles and high pollinator dependence had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and low pollinator dependence (figure 3c).
+Plants with long styles and low pollinator dependence interacted more frequently with Lepidoptera and non-bee-Hymenoptera (figure 3f).
+
+The additional models for the most represented bee families, for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and the number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03), showed that the Apidae family was the main driver of the observed patterns.
+The contrast between interaction presence/absence  and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S8).
 
@@
 ```
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
-PC1 represents the flower number - flower size axis, PC2 represents the pollinator dependence axis and PC3, the style length - pollinator dependence axis.
-For visualization purposes, due to large differences between number of visits of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
+PC1 represents the flower number - flower size axis, PC2 represents the pollinator dependence axis and PC3 represents the style length - pollinator dependence axis.
+For visualization purposes due to large differences between number of visits from bees and the rest of the pollinator guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
 
@@
 
-The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
+Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
 Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
-On PC1, the number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
-However, specialization showed the opposite trend on this axis (figure S9g).
+On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
+However, specialization (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
 On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S9c).
-Again, specialization showed the opposite trend to number of visits (figure S9i).
+Again, specialization showed the opposite trend to the number of visits (figure S9i).
 
@@
 
-The reproductive spectrum of flowering plants showed clear reproductive trait covariation patterns that shaped interactions with floral visitors at a global scale.
-Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50% and 70% of reproductive trait variation, respectively.
-These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
-Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits [@diaz2016; @carmona2021], our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits [@salguero2016].
-Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds.
-However, they were insufficient to capture the visitation rates by guild or the other species-level network metrics considered in this study, which highlights the need to account for other local factors, such as species relative abundances [@bartomeus2016], to better understand the association of plant-pollinator interactions at a macroecological scale.
-
-Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and links the reproductive spectrum with the previously described fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
-For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred Angiosperm species with a pair-wise trait approach.
-We found support to this trait association and show that other life history traits also covariate along this axis.
-Our study also complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers are associated with woody life forms with high flower number.
-Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral displays but in particular with species with larger flowers.
-Our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
-
-Overall, plant reproductive trait covariation axes helped explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales.
-For example, we found that all floral visitor guilds interacted more frequently with plant species with larger flowers and higher pollinator dependence in agreement with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
-As predicted by evolutionary life-history theory [@stebbins1970], larger investment on floral display and rewards to attract pollinators makes sense when pollinator dependence is higher, but this investment is compromised by the cost of the different reproductive structures, trait associations and the distinct selective pressures such as the one exerted by the different floral visitor guilds [@galen1999].
-For instance, smaller flowers were less visited overall, but they are inexpensive (e.g., low ovule number) and can counterpart this lack of visitation at the flower level by increasing the chances of visitation at the whole individual level with larger displays as suggested for wind pollinated species where small numerous flowers can increase the chances of pollen capture and seed production [@friedman2011].
-In addition, because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations found between reproductive traits and floral visitor guilds also may indicate the existence of large scale pollination syndromes [@faegri2013; @rosas2014; @dellinger2020].
-For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies on all axes and because these two guilds are likely to differ in ecology and behaviour [@rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies.
-In any case, it is worth noting that other local factors such as species relative abundances, phenology or trait matching, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive trait correlations do not.
-
-Our study provides a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of reproductive traits from plant species that belong to plant-pollinator networks.
-Additionally, we highlight the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider factors such as plant reproductive strategies, and not only flower morphology, to better capture broad scale patterns of interactions with floral visitors.
-Further, we provide empirical evidence that complements previous trait correlation studies along other plant organs and we highlights the need to include reproductive trait correlations in the global spectrum of plant form and function [@diaz2016], as the different plant reproductive strategies involve clear cost and benefits that can affect resource allocation to other morphological and physiological traits.
-Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and understanding of the different plant-pollinator associations.
+We found strong covariation among traits within the flowering plant reproductive spectrum, which shapes interactions with floral visitors at a global scale.
+Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50% and 70% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, pollinator dependence and floral display, and style length and pollinator dependence.
+Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits [@diaz2016; @carmona2021], our results align with the largest and most recent study of plant life strategies that included reproductive, form and size related traits [@salguero2016].
+The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct floral visitor guilds.
+However, the unexplained variability found highlights the need to account for other local factors, such as species relative abundances [@bartomeus2016], along with reproductive traits, to better explain plant-pollinator associations.
+
+Our study provides strong evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1,200 species).
+Specifically, by using a multitrait approach, we are able to link the reproductive spectrum of plant trait variation with the previously described “fast-slow continuum” in plant [@salguero2016] and animal [@healy2019] life-history strategies.
+This fast-slow continuum was illustrated by the associations between reproductive traits and plant height, life form and lifespan traits.
+For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred Angiosperm species in the absence of a multitrait perspective.
+We found support for this trait association and show that other reproductive traits (e.g., style length or ovule number) covary along this flower number - flower size axis.
+Our study also complements previous work linking plant breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers also have woody life forms and many flowers.
+Moreover, we identify the previously documented positive association between outcrossing rate and floral display size [@goodwillie2010], where species with high pollinator dependence also allocate large resource quantities to attract floral visitors.
+Although we did not include floral rewards in our main analysis due to insufficient data, we did find that plant species with large floral displays and, in particular, large flowers, tended to have higher pollen and nectar quantity.
+Thus, we demonstrate that globally, reproductive trait covariation in flowering plants likely imposes constraints on the broader spectrum of plant trait variation.
+
+Overall, plant reproductive traits explained interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations across spatial large scales.
+For example, we found that all floral visitor guilds interacted more frequently with large flowered and pollinator dependent plant species, which aligns with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
+As predicted by evolutionary life-history theory [@stebbins1970], larger investment in floral display and rewards to attract pollinators occurs when pollinator dependence is high.
+However,  the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different floral visitor guilds [@galen1999].
+For instance, smaller flowers are visited less overall, but they are inexpensive to produce (e.g., have a low ovule number) and low visitation rate at the individual flower level can be compensated by overall visitation at the plant level by producing many flowers resulting in a larger quantity of small fruits [@kettle2011].
+In addition, because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and floral visitor guilds could indicate the existence of pollination syndromes [@fenster2004; @faegri2013; @rosas2014; @dellinger2020].
+For instance, bees had a higher number of interacting partners on plant species with large flowers but interacted more frequently with species with small flowers while syrphid flies showed the opposite trend.
+This could be reflective of differences in the ecology and behaviour between these pollinator guilds [@rader2020; @foldesi2021] that ultimately exert different selective pressures, leading divergent plant reproductive strategies.
+In any case, it is worth noting that local factors (e.g., species relative abundances or phenologies) likely contribute to the variability in the association between the plant reproductive spectrum and floral visitors [@vazquez2007; @encinas2012; @bartomeus2016].
+
+Our study provides a comprehensive assessment of  reproductive trait covariation patterns in flowering plants, using a global dataset of traits for plant species within plant-pollinator networks.
+We show the importance of floral visitors in mediating reproductive trait correlations and identify the need to consider broader plant reproductive strategies, rather than just flower morphology, to understand patterns of plant-pollinator interactions.
+Further, we provide empirical evidence of reproductive trait associations that complements trait covariation studies for other plant organs, highlighting the need to include reproductive traits in the global spectrum of plant form and function.
+Future work incorporating underrepresented areas of the world and additional relevant reproductive traits (e.g., flower life span and colour) will be valuable for enhancing our understanding of the plant reproductive spectrum and associated plant-pollinator interactions.
 
@@
 We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
-We also thank Jason Tylianakis for his comments on the manuscript before submission.
+We thank Jason Tylianakis for his insightful comments on the manuscript before submission.
 Finally, we thank Marcos Méndez, Susan Kalisz, Amanda Benoit, May Berenbaum and an anonymous reviewer for thoughtful feedback and useful comments on earlier versions of this manuscript.

### 2022-07-19 Manuscript/Lanuza_et_al_2022.tex
style edits

@@
 ]{article}
-\title{\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors}
+\title{\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shapes interactions with floral visitors}
 \author{}
@@
 \hypersetup{
-  pdftitle={ Covariation among reproductive traits in flowering plants determine interactions with floral visitors},
+  pdftitle={ Covariation among reproductive traits in flowering plants shapes interactions with floral visitors},
   colorlinks=true,
@@
 
-Plants have an enormous variation of life history strategies and trait combinations.
-However, there is strong evidence that there are evolutionary and physiological constraints that limit the number of plant ecological strategies.
-Despite recent advances in the understanding of plant trait correlations, reproductive traits are often not considered despite its key role in shaping both plant life-history strategies and plants interactions with floral visitors.
-Here, we investigate the reproductive spectrum of flowering plants and how this drive the establishment of interactions with their floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
-We found that over 50\% of all trait variation was explained by the first two reproductive axes.
-Specifically, the first axis indicated the presence of a negative correlation between flower number and flower size while the second axis showed a positive correlation between pollinator dependence and floral display.
-These different reproductive axes determined important differences in the interaction level among floral visitor guilds but were insufficient to fully capture plant-pollinator associations.
-Our study shows the main reproductive trait correlations of flowering plants and highlights their relevance to understand plant-pollinator interactions in a global context.
+Globally, plants display enormous variation in life history strategies and trait combinations.
+However, evidence suggests that evolutionary and physiological constraints limit the number of plant ecological strategies.
+Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with floral visitors.
+Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with floral visitors.
+We show that over 50\% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the positive correlation between pollinator dependence and floral display size.
+In empirical plant-pollinator networks, the plant position within these axes was associated with the number of interacting partners and the visitation rates of the distinct floral visitor guilds, but the unexplained variability found highlights the need to incorporate other factors along with reproductive traits to fully explain plant-pollinator interactions.
+Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping networks of plant-pollinator interactions at a global scale.
 
@@
 
-Flowering plants have an astonishing diversity of floral structures {[}\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}{]} that shape their interactions with animal pollinators {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}{]}.
-The variety of reproductive strategies followed by different plant species, from specialized reliance on a single pollinator, to full self-pollination, is incredibly rich.
-However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints {[}\protect\hyperlink{ref-stearns1989}{5},\protect\hyperlink{ref-agrawal2020}{6}{]}.
-Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits {[}\protect\hyperlink{ref-salguero2016}{7}--\protect\hyperlink{ref-song2022}{11}{]}, their study is often limited to a few number of reproductive traits that are rarely studied in combination.
-Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other root {[}\protect\hyperlink{ref-laughlin2021}{12}{]}, leaf {[}\protect\hyperlink{ref-wright2004}{13}{]} or wood {[}\protect\hyperlink{ref-chave2009}{14}{]} related traits, there is a need to acquire a multitrait perspective with broad geographical coverage.
-Importantly, the characterization of the plant reproductive spectrum can help to further understand the different plant ecological strategies {[}\protect\hyperlink{ref-agrawal2020}{6}{]} and improve our knowledge on plant-pollinator associations {[}\protect\hyperlink{ref-roddy2021}{10}{]}.
-
-With the recent availability of large trait databases {[}e.g., TRY \protect\hyperlink{ref-kattge2011}{15},~COMPADRE \protect\hyperlink{ref-salguero2015}{16}{]}, plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-diaz2016}{17}--\protect\hyperlink{ref-carmona2021}{19}{]}.
-However, most studies with a multitrait perspective have overlooked plant reproductive traits {[}\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-evojtko2020}{20}{]} and focused on trait correlations from other plant organs.
-Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{21},\protect\hyperlink{ref-kettle2011}{22}{]}, the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{23}{]} or the positive association between outcrossing rate and lifespan {[}\protect\hyperlink{ref-barrett2003}{24},\protect\hyperlink{ref-moeller2017}{25}{]}.
-Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships {[}\protect\hyperlink{ref-roddy2021}{10}{]}, we still lack empirical evidence that investigates jointly how these different reproductive trait associations shape plant life history strategies.
-
-Despite this increasing number of macroecological studies that investigate specific plant reproductive traits {[}\protect\hyperlink{ref-moeller2017}{25}--\protect\hyperlink{ref-grossenbacher2017}{28}{]}, we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-sargent2008}{29}--\protect\hyperlink{ref-ruger2018}{31}{]}.
-The use of trait-based approaches {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{32}{]} and trait-matching analyses {[}\protect\hyperlink{ref-stang2009}{33},\protect\hyperlink{ref-bartomeus2016}{34}{]} has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-For example, plant traits can define species' network roles {[}e.g., specialists vs generalists \protect\hyperlink{ref-tur2013}{35}{]} and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators {[}\protect\hyperlink{ref-junker2013}{36},\protect\hyperlink{ref-coux2016}{37}{]}.
-Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure {[}\protect\hyperlink{ref-stang2009}{33},\protect\hyperlink{ref-ibanez2012}{38}{]}.
-However, is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations {[}\protect\hyperlink{ref-tur2013}{35},\protect\hyperlink{ref-devaux2014}{39}{]}.
-Indeed, the pollination system of a great number of plant species remains unexplored {[}\protect\hyperlink{ref-dellinger2020}{4}{]}.
-Because both the species' morphology and mating system can determine the species' functional role in the pollination network and the combination of several traits has shown to increase the predictive power of the structure of ecological networks {[}\protect\hyperlink{ref-eklof2013}{40}{]}, an interesting novel approach is to investigate how a complete set of reproductive traits in the multidimensional trait space determine species interaction patterns {[}see \protect\hyperlink{ref-dehling2016}{41} for a morphological approach{]}.
-Thus, by exploring the plant reproductive spectrum of trait variation it is possible to delimit the different reproductive strategies and explore how these are associated with the different floral visitors.
-
-Here, we aim to progress knowledge on the reproductive trait covariation patterns and their association with the different floral visitor guilds by exploring at a broad geographical scale the reproductive spectrum of trait variation of flowering plants from plant-pollination networks.
-First, we investigate what are the major axes of reproductive trait variation and trait correlations for the different plant species.
-Second, we investigate the association between the plant species' position in the multidimensional trait-space and the different floral visitor guilds with the help of qualitative (presence-absence of interaction) and quantitative (number of visits) information about plant-pollinator interactions.
-Finally, we investigate how the main axes of trait variation influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
+Flowering plants display an astonishing diversity of reproductive structures {[}\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}{]} that shape their interactions with animal pollinators {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}{]}.
+The variety of reproductive strategies used by different plant species, from specialized reliance on a single pollinator, to full self-pollination, is incredibly rich.
+However, not all reproductive trait combinations in plants are possible due to evolutionary and ecological constraints {[}\protect\hyperlink{ref-stearns1989}{5},\protect\hyperlink{ref-agrawal2020}{6}{]}.
+Despite recent advances in theoretical and empirical understanding of correlations between plant reproductive traits at large ecological scales {[}\protect\hyperlink{ref-salguero2016}{7}--\protect\hyperlink{ref-song2022}{11}{]}, studies typically focus on just a few traits, often in isolation.
+Thus, to develop a comprehensive understanding of the plant reproductive spectrum of trait variation, as done recently for root {[}\protect\hyperlink{ref-laughlin2021}{12}{]}, leaf {[}\protect\hyperlink{ref-wright2004}{13}{]} and wood {[}\protect\hyperlink{ref-chave2009}{14}{]} related traits, we require a multi-trait perspective with broad geographical coverage.
+Importantly, characterization of the plant reproductive spectrum could reveal key reproductive strategies among different species {[}\protect\hyperlink{ref-agrawal2020}{6}{]} and improve knowledge of associations between specific reproductive traits and pollinators {[}\protect\hyperlink{ref-roddy2021}{10}{]}.
+
+With the recent availability of large trait databases {[}e.g., TRY \protect\hyperlink{ref-kattge2011}{15},COMPADRE \protect\hyperlink{ref-salguero2015}{16}{]}, there has been increased research on plant ecological strategies, which has produced identification of global patterns in plant form and function {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-diaz2016}{17}--\protect\hyperlink{ref-carmona2021}{19}{]}.
+However, studies that look at multiple traits tend to overlook plant reproductive traits {[}\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-evojtko2020}{20},\protect\hyperlink{ref-ruger2018}{21}{]}, and focus on trait correlations in other plant organs such as morphological and physiological leaf traits {[}\protect\hyperlink{ref-wright2004}{13},\protect\hyperlink{ref-shipley2006}{22}--\protect\hyperlink{ref-osnas2013}{24}{]}.
+Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs (e.g., the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{25},\protect\hyperlink{ref-kettle2011}{26}{]}; the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{27}{]}; or the positive correlation between outcrossing rate and lifespan {[}\protect\hyperlink{ref-barrett2003}{28}--\protect\hyperlink{ref-moeller2017}{30}{]}).
+Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships {[}\protect\hyperlink{ref-roddy2021}{10}{]}, we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
+
+Trait-based approaches {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{31}{]} and trait-matching analyses {[}\protect\hyperlink{ref-stang2009}{32},\protect\hyperlink{ref-bartomeus2016}{33}{]} are powerful for exploring the underlying mechanisms driving plant-pollinator interactions.
+For example, plant traits can define species' network roles {[}e.g., specialists vs generalists \protect\hyperlink{ref-tur2013}{34}{]} and plant species that occupy reproductive trait space extremes are likely to be more specialized and display tighter trait-matching with pollinators {[}\protect\hyperlink{ref-junker2013}{35},\protect\hyperlink{ref-coux2016}{36}{]}.
+Indeed, the degree of morphological matching between plants and floral visitors often determines whether or not interactions occur, and consequently influences the broader network structure {[}\protect\hyperlink{ref-stang2009}{32},\protect\hyperlink{ref-ibanez2012}{37}{]}.
+However, it is still unclear how specific reproductive traits (e.g., mating or compatibility system) influence plant-pollinator associations {[}\protect\hyperlink{ref-tur2013}{34},\protect\hyperlink{ref-sargent2008}{38},\protect\hyperlink{ref-devaux2014}{39}{]}.
+Indeed, both morphology and mating system can determine a species' functional role within pollination networks, and the combination of several traits increases power for predicting network structure {[}\protect\hyperlink{ref-eklof2013}{40}{]}.
+Because the species position within the multidimensional trait space can result in different interaction patterns or adaptations to pollinators {[}see \protect\hyperlink{ref-dehling2016}{41} for a purely morphological approach{]}, the use of the reproductive trait space to explore plant-pollinator interactions could help to identify species functional roles and associations of traits with specific pollinators (i.e., pollination syndromes).
+
+Here, we explore the spectrum of reproductive traits in flowering plants, within a global set of plant-pollinator networks, to identify reproductive trait covariation and how this influences the network of interactions between plants and floral visitors.
+First, we identify the major axes of reproductive trait variation and correlations among traits for plant species.
+Then, we investigate the associations between plant species' positions in reproductive trait space and the strength of their interactions with different floral visitor guilds within networks.
+Finally, we determine how the main axes of reproductive trait variation influence plant species' functional roles within pollination networks, using a range of complementary interaction network metrics.
 
@@
 We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see table S1 and figure S1).
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different biological communities.
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies {[}e.g., \protect\hyperlink{ref-carvalheiro2014}{42},\protect\hyperlink{ref-olesen2007}{43},\protect\hyperlink{ref-fortuna2010}{44}{]} or available in online archives {[}e.g., Mangal \protect\hyperlink{ref-poisot2016}{45},~The Web of Life \protect\hyperlink{ref-fortuna2010}{44}{]}.
-In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
+These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different ecological communities.
+Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to benefit, to some degree, from animal pollination.
+Many of these networks are freely available either as published studies {[}e.g., \protect\hyperlink{ref-carvalheiro2014}{42},\protect\hyperlink{ref-olesen2007}{43},\protect\hyperlink{ref-fortuna2010}{44}{]} or in online archives {[}e.g., Mangal \protect\hyperlink{ref-poisot2016}{45},The Web of Life \protect\hyperlink{ref-fortuna2010}{44}{]}.
+In total, our network dataset constituted 60 weighted (number of visits) and four unweighted (interaction presence-absence) networks, each sampled at a unique location and year, as well as eight meta-networks where interactions were pooled across several locations and multiple years.
 
@@
 
-We selected a total of 19 different quantitative and categorical functional traits that comprised reproductive traits and plant form and size related traits (see table 1).
-Reproductive traits consisted of floral traits and reproductive biology traits: (i) floral traits included traits related to the size of floral organs (e.g., style length), floral display (e.g., flower number) or floral rewards (e.g., pollen quantity) while (ii) reproductive biology traits indicated the reproductive system of the plant (i.e., breeding, mating and compatibility system).
-The remaining traits were plant size and form related traits that are commonly used to characterize the fast-slow continuum of plant trait variation (i.e., plant height, lifespan and life form).
+We selected a total of 19 quantitative and categorical functional traits that included reproductive traits and traits related with plant form and size (see table 1).
+Reproductive traits consisted of those related to floral and reproductive biology: (i) floral traits included those related to the size of floral organs (e.g., style length), floral display size (e.g., flower number) and floral rewards (e.g., pollen quantity), while (ii) reproductive biology traits represented the plant reproductive system (i.e., the breeding, mating and compatibility system).
+The remaining traits were related to plant size and form (i.e., plant height, lifespan and life form), which are commonly used to characterize the fast-slow continuum of plant trait variation {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
 For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 possible cells considering all traits and plant species (20 columns × 1,506 species), we were able to fill 24,341 cells (80.8\% of the dataset, see figure S2 for missing values information for each trait).
+From a matrix comprising a total of 28,614 possible cells (considering all traits and plant species: 19 columns × 1,506 species), we were able to fill 23,354 cells (81.6\% of the dataset, see figure S2 for missing value information for each trait).
 An extended description of each trait and how it was obtained can be found in Appendix S1.
@@
 
-We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{47},\protect\hyperlink{ref-jin2019}{48}{]}.
+We calculated the phylogenetic distance between all plant species considered using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{47},\protect\hyperlink{ref-jin2019}{48}{]}.
 
@@
 
-To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{49}{]} which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{50}{]}.
+To avoid excluding species with trait missing values, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{49}{]} which allows imputation of datasets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors from principal component analysis of the phylogenetic distance (PCoA), which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{50}{]}.
 To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} {[}\protect\hyperlink{ref-santos2018}{51}{]} based on a previous conceptual framework that considers phylogenetic eigenvectors {[}\protect\hyperlink{ref-diniz-filho2012}{52}{]}.
-We conducted two different imputations, one for the full set of species (1,506 species, 5.79\% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (figure S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01\% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
+We conducted two different imputations, one for the full set of species (1,506 species: 5.79\% of missing values), and excluded nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01\% of missing values).
+To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and results for the two datasets were consitent (Fig S3 and Fig S4).
 
@@
 
-We explored the association between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
+We explored the association between the different quantitative plant traits using a phylogenetically informed Principal Component Analysis (pPCA).
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
 Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{53},\protect\hyperlink{ref-legendre2012}{54}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as recommended for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{54}{]}.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{55}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{56}{]}.
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
-For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
+Specifically, due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{53},\protect\hyperlink{ref-legendre2012}{54}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
+Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{54}{]}.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{55}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode ``covariance'' because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{56}{]}.
+Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity data.
+For this, we included all quantitative traits included in the main pPCA, plus pollen grains and microlitres of nectar per flower.
 
@@
 
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{55}{]} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{55}{]} and used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
@@
 
-First, we used Bayesian modelling (see below for details) to investigate how the different groups of floral visitors interacted along the main axes of reproductive trait variation with the help of qualitative and quantitative information of plant-pollinator interactions.
-For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency {[}\protect\hyperlink{ref-ballantyne2015}{57}{]}, the number of visits can provide valuable information of the contribution of floral visitors to pollination {[}\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}{]}.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total).
-This finding is consistent with previous research showing that \emph{A.
+We used Bayesian modeling (see details below) to investigate how the different guilds of floral visitors interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
+Specifically, interactions between plants and floral visitors in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
+Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species {[}\protect\hyperlink{ref-ballantyne2015}{57}{]}, the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination {[}\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}{]}.
+We divided floral visitors into six main taxonomical guilds that differ in life form, behaviour and thus likely play similar ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
+Moreover, because bees had the greatest number of occurrences in networks (2,256 records) and the highest frequency of visits, we further broke this group down into the main bee families (Andrenidae, Apidae, Colletidae, Halictidae, and Megachilidae).
+In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of occurrences in networks (7.55\% of the total).
+This is consistent with previous research showing that \emph{A.
 mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems {[}\protect\hyperlink{ref-hung2018}{60}{]}.
 Hence, to control for the effect of \emph{A.
-mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding \emph{A.
+mellifera} on observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding \emph{A.
 mellifera}.
@@
 
-We implemented Bayesian generalized linear mixed models using the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{61}{]}.
-We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
-We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so they have neglible influence on the results {[}\protect\hyperlink{ref-burkner2017}{61}{]}.
+We used Bayesian generalized linear mixed models in the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{61}{]} to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in visitation patterns among floral visitor guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds in the model.
+We added a nested random effect of networks within the study system to capture the variation in networks among studies and within networks.
+Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence among them.
+We specified for the presence or absence of an interaction and number of visits with Bernoulli and a zero inflated negative binomial distributions, respectively.
+The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results {[}\protect\hyperlink{ref-burkner2017}{61}{]}.
 We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}\protect\hyperlink{ref-gabry2019}{62}{]}.
@@
 
-Second, we investigated with Bayesian modelling how the main axes of trait variation determined different plant species' functional roles in the pollination network.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{63}{]} with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics that summarize species' functional roles were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{64}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{63}{]}.
-We modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
-For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
+We also used Bayesian modeling to investigate how the main axes of trait variation determined different plant species' functional roles within pollination networks.
+For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{63}{]}, with clear ecological interpretations and are relevant for defining species' functional roles in networks.
+Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{64}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the \emph{specieslevel} function in the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{63}{]}.
+We modeled each plant species metric (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
+For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree, and zero-one inflated beta for specialization).
 Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns' section.
 
-Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across studies but this was accounted for in analyses by considering them in the random effects of the modelling process.
+Our analyses were conducted on the subset of 60 weighted networks (out of a total of 64 networks) sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
+In total, our network dataset (excluding meta- and non-weighted networks) included 2,256 interactions for bees, 1,768 for non-syrphid-dipterans, 845 for syrphids, 437 for lepidopterans, 432 for coleopterans, and 362 for non-bee-hymenopterans.
+Sampling methods varied across studies but this was accounted for in analyses by including study identity as a random effect in our models.
 All analyses were conducted in R version \emph{4.0.3}.
@@
 
-The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of the reproductive trait variation, respectively (figure 1 and figure S6).
-The first principal component (PC1 or the flower number - flower size axis) represented 26.72\% of the trait variation and indicated a negative correlation between flower number and flower size.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; table S3) but style length also contributed moderately to PC1 (loading = -0.33).
+Our phylogenetically informed principal component analysis captured 51.8\% and 70.97\% of the reproductive trait variation in the first two and three axes, respectively (figure 1 and figure S6).
+The first principal component (PC1; the flower number - flower size axis) represented 26.72\% of the trait variation and indicated a negative correlation between flower number and flower size.
+The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; table S3) but style length also contributed moderately (loading = -0.33).
 One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-For instance, on this end of the spectrum we find the species \emph{Cornus florida} which has approximately a total of 10.000 flowers, an average height of 7.5m, flowers of 3mm wide, a style length of 3.5mm and a total of 2 ovules per flower.
-The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-For instance, on this other end, we find the species \emph{Petunia axillaris} that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
-The second principal component (PC2 or the pollinator dependence axis) represented 25.05\% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; table S3).
-In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles.
-On this extreme of the spectrum we find the species \emph{Zuccagnia punctata} that is a self-incompatible shrub that depends completely on floral visitors for seed production, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm.
-In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
-As an example of this reproductive extreme, we find the species \emph{Veronica peregrina} which is a self-compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
-Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17\%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \textbar-0.51\textbar) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
-The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; table S3).
-In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with floral display.
-Floral rewards were specially strongly correlated with flower size but slightly correlated with flower number (figure S4).
-This pPCA explained similar variance with the first two principal components (45.52\%) and similar associations of traits despite some variability in the loadings (table S4).
+For instance, \emph{Cornus florida} occurred at this end of the spectrum, which, on average, has approximately 10,000 flowers, is 7.5 m high, has flowers that are 3 mm wide, styles 3.5 mm long and two ovules per flower.
+The other end of this spectrum had species that were short in height, with few large flowers that had long styles and many ovules.
+For example, \emph{Petunia axillaris} on average, is 0.5 m high and has approximately 10 flowers per plant that are over 50 mm wide with 25 mm long styles and over 200 ovules.
+The second principal component (PC2; the pollinator dependence axis) encompassed 25.05\% of the trait variation and represented variation from low to high autonomous selfing (i.e., high to low pollinator dependence).
+The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but all other traits (except ovule number) made moderate contributions (loadings ranging between 0.27 to 0.4; table S3).
+Generally speaking, species with high pollinator dependence had larger and many flowers with long styles, and were tall.
+\emph{Zuccagnia punctata} occurred at this extreme of the spectrum, which is a self-incompatible species, completely dependent on animal pollination for seed production, producing approximately 1,500 flowers per plant with an average height of 3 m and 20 mm long styles.
+In contrast, species with low pollinator dependence tended to have fewer and smaller flowers with shorter styles, and were shorter in height.
+\emph{Veronica peregrina} occurred at this end of the spectrum, and is a self-compatible plant that requires little or no pollination by animals, it has approximately 20 flowers per plant, is 0.2 m high and has 0.25 mm long styles.
+The third principal component (PC3; the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17\%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \textbar-0.51\textbar), where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
+The remaining traits, apart from ovule number, were all positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; table S3).
+In addition, the pPCA with the subset of species that we had nectar and pollen quantity data for showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with floral display size.
+Floral rewards were particularly strongly correlated with flower size but weakly correlated with flower number (figure S4).
+The first two principal components for this pPCA explained similar variance (45.52\%) and similar associations of traits, despite some variability in the loadings (table S4).
 
@@
 We found that most categorical traits were statistically associated with the first two axes of trait variation (figure 2 and table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
-In addition, we found statistical differences between the different levels of categorical traits in the trait space (figure S7).
+Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed a lack of statistical association.
+In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S7).
 Regarding self-compatibility, we found larger differences on PC2.
-For instance, species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility on this vertical axis (figure S7a and figure S7b; Tukey test \emph{P} \textless{} 0.05).
+For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S7a and figure S7b; Tukey test \emph{P} \textless{} 0.05).
 Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S7c and figure S7d; Tukey test \emph{P} \textless{} 0.05).
 Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f; Tukey test \emph{P} \textless{} 0.05).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h; Tukey test \emph{P} \textless{} 0.05).
-Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S7i and figure S7j; Tukey test \emph{P} \textless{} 0.05).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S7k and figure S7l; Tukey test \emph{P} \textless{} 0.05).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h; Tukey test \emph{P} \textless{} 0.05).
+Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and high pollinator dependence, while the latter had more flowers and lower pollinator dependence (figure S7i and figure S7j; Tukey test \emph{P} \textless{} 0.05).
+Finally, in terms of flower symmetry, zygomorphic flowers were associated with lower pollinator dependence, whereas actinomorphic flowers were more dependent on pollinators (figure S7k and figure S7l; Tukey test \emph{P} \textless{} 0.05).
 
@@
 
-\caption{\textbf{Figure 2.} Location of the different qualitative traits on the trait space.
-The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
-The solid arrows indicate the direction of variation of the different quantitative traits showed in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S).}\label{fig:unnamed-chunk-3}
+\caption{\textbf{Figure 2.} Location of the different qualitative traits in the trait space.
+The figure panel is composed of the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
+The solid arrows indicate the direction of variation of the different quantitative traits shown in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S).}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 The traits that showed the highest phylogenetic signal were ovule number (\(\lambda\) = 1), pollen grains per flower (\(\lambda\) = 1) and plant height (\(\lambda\) = 0.96), followed by flower length (\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73), number of flowers per plant (\(\lambda\) = 0.69) and nectar concentration (\(\lambda\) = 0.65).
-The traits that showed a moderate phylogenetic signal were inflorescence width (\(\lambda\) = 0.57), style length (\(\lambda\) = 0.49) and autonomous selfing (\(\lambda\) = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits (\(\lambda\) = 0.14).
+The traits that had a moderate phylogenetic signal included inflorescence width (\(\lambda\) = 0.57), style length (\(\lambda\) = 0.49) and autonomous selfing (\(\lambda\) = 0.34).
+Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all the traits we measured (\(\lambda\) = 0.14).
 
@@
 
-The main axes of trait variation (PC1, PC2 and PC3) explained partly presence-absence of interaction partners (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the overall number of visits (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
-However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (figure 3).
-We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (figure 3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
-Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high number of small flowers (figure 3d).
-On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (figure 3b and figure 3e).
-Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (figure 3c).
-Plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (figure 3f).
-
-The additional model for the most represented families of bees for both presence-absence of interaction (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and number of visits (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03) showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (figure 3a and figure 3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (figure S8).
+The main axes of trait variation (PC1, PC2 and PC3) partly explained the presence-absence of interaction partners (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the total number of visits (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
+However, we found relevant differences across the different floral visitor guilds for both the presence-absence of interactions and number of visits (figure 3).
+On the flower number - flower size axis, we found that plants with many small flowers tended to have interaction partners that were Coleoptera, non-bee-Hymenoptera and Diptera (figure 3a), whereas plants with few large flowers mostly had interaction partners that were bees and Lepidoptera.
+We found similar trends for visitation rates on the flower number - flower size axis, but bees and syrphids visited plant species with many small flowers more frequently (figure 3d).
+On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had many interaction partners and recieved many visits from all floral visitor guilds (figure 3b and figure 3e).
+Finally, on the style length - pollinator dependence axis, plant species with short styles and high pollinator dependence had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and low pollinator dependence (figure 3c).
+Plants with long styles and low pollinator dependence interacted more frequently with Lepidoptera and non-bee-Hymenoptera (figure 3f).
+
+The additional models for the most represented bee families, for both presence-absence of interactions (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and the number of visits (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03), showed that the Apidae family was the main driver of the observed patterns.
+The contrast between interaction presence/absence and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S8).
 
@@
 \includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\textbf{Figure 3.} Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
-PC1 represents the flower number - flower size axis, PC2 represents the pollinator dependence axis and PC3, the style length - pollinator dependence axis.
-For visualization purposes, due to large differences between number of visits of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel).}
+\caption{\label{fig:unnamed-chunk-4}\textbf{Figure 3.} Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
+PC1 represents the flower number - flower size axis, PC2 represents the pollinator dependence axis and PC3 represents the style length - pollinator dependence axis.
+For visualization purposes due to large differences between number of visits from bees and the rest of the pollinator guilds, the number of visits was log-transformed (Y-axis of lower panel).}
 \end{figure}
@@
 
-The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
+Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
 Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
-On PC1, the number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
-However, specialization showed the opposite trend on this axis (figure S9g).
+On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
+However, specialization (d') was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
 On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S9c).
-Again, specialization showed the opposite trend to number of visits (figure S9i).
+Again, specialization showed the opposite trend to the number of visits (figure S9i).
 
@@
 
-The reproductive spectrum of flowering plants showed clear reproductive trait covariation patterns that shaped interactions with floral visitors at a global scale.
-Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively.
-These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
-Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{17},\protect\hyperlink{ref-carmona2021}{19}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
-Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds.
-However, they were insufficient to capture the visitation rates by guild or the other species-level network metrics considered in this study, which highlights the need to account for other local factors, such as species relative abundances {[}\protect\hyperlink{ref-bartomeus2016}{34}{]}, to better understand the association of plant-pollinator interactions at a macroecological scale.
-
-Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and links the reproductive spectrum with the previously described fast-slow continuum' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{65}{]} life-history strategies, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan.
-For instance, although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{21},\protect\hyperlink{ref-kettle2011}{22},\protect\hyperlink{ref-worley2000}{66}{]}, it has only been investigated across a few hundred Angiosperm species with a pair-wise trait approach.
-We found support to this trait association and show that other life history traits also covariate along this axis.
-Our study also complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{67}{]} by showing that most species with unisexual flowers are associated with woody life forms with high flower number.
-Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{23}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral displays but in particular with species with larger flowers.
-Our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
-
-Overall, plant reproductive trait covariation axes helped explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales.
-For example, we found that all floral visitor guilds interacted more frequently with plant species with larger flowers and higher pollinator dependence in agreement with previous findings {[}\protect\hyperlink{ref-hegland2005}{68}--\protect\hyperlink{ref-kaiser2014}{70}{]}.
-As predicted by evolutionary life-history theory {[}\protect\hyperlink{ref-stebbins1970}{71}{]}, larger investment on floral display and rewards to attract pollinators makes sense when pollinator dependence is higher, but this investment is compromised by the cost of the different reproductive structures, trait associations and the distinct selective pressures such as the one exerted by the different floral visitor guilds {[}\protect\hyperlink{ref-galen1999}{72}{]}.
-For instance, smaller flowers were less visited overall, but they are inexpensive (e.g., low ovule number) and can counterpart this lack of visitation at the flower level by increasing the chances of visitation at the whole individual level with larger displays as suggested for wind pollinated species where small numerous flowers can increase the chances of pollen capture and seed production {[}\protect\hyperlink{ref-friedman2011}{73}{]}.
-In addition, because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations found between reproductive traits and floral visitor guilds also may indicate the existence of large scale pollination syndromes {[}\protect\hyperlink{ref-dellinger2020}{4},\protect\hyperlink{ref-rosas2014}{32},\protect\hyperlink{ref-faegri2013}{74}{]}.
-For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies on all axes and because these two guilds are likely to differ in ecology and behaviour {[}\protect\hyperlink{ref-rader2020}{75},\protect\hyperlink{ref-foldesi2021}{76}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
-In any case, it is worth noting that other local factors such as species relative abundances, phenology or trait matching, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{34},\protect\hyperlink{ref-vazquez2007}{77},\protect\hyperlink{ref-encinas2012}{78}{]} that reproductive trait correlations do not.
-
-Our study provides a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of reproductive traits from plant species that belong to plant-pollinator networks.
-Additionally, we highlight the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider factors such as plant reproductive strategies, and not only flower morphology, to better capture broad scale patterns of interactions with floral visitors.
-Further, we provide empirical evidence that complements previous trait correlation studies along other plant organs and we highlights the need to include reproductive trait correlations in the global spectrum of plant form and function {[}\protect\hyperlink{ref-diaz2016}{17}{]}, as the different plant reproductive strategies involve clear cost and benefits that can affect resource allocation to other morphological and physiological traits.
-Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and understanding of the different plant-pollinator associations.
+We found strong covariation among traits within the flowering plant reproductive spectrum, which shapes interactions with floral visitors at a global scale.
+Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50\% and 70\% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, pollinator dependence and floral display, and style length and pollinator dependence.
+Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{17},\protect\hyperlink{ref-carmona2021}{19}{]}, our results align with the largest and most recent study of plant life strategies that included reproductive, form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
+The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct floral visitor guilds.
+However, the unexplained variability found highlights the need to account for other local factors, such as species relative abundances {[}\protect\hyperlink{ref-bartomeus2016}{33}{]}, along with reproductive traits, to better explain plant-pollinator associations.
+
+Our study provides strong evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1,200 species).
+Specifically, by using a multitrait approach, we are able to link the reproductive spectrum of plant trait variation with the previously described ``fast-slow continuum'' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{65}{]} life-history strategies.
+This fast-slow continuum was illustrated by the associations between reproductive traits and plant height, life form and lifespan traits.
+For instance, although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{25},\protect\hyperlink{ref-kettle2011}{26},\protect\hyperlink{ref-worley2000}{66}{]}, it has only been investigated across a few hundred Angiosperm species in the absence of a multitrait perspective.
+We found support for this trait association and show that other reproductive traits (e.g., style length or ovule number) covary along this flower number - flower size axis.
+Our study also complements previous work linking plant breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{67}{]} by showing that most species with unisexual flowers also have woody life forms and many flowers.
+Moreover, we identify the previously documented positive association between outcrossing rate and floral display size {[}\protect\hyperlink{ref-goodwillie2010}{27}{]}, where species with high pollinator dependence also allocate large resource quantities to attract floral visitors.
+Although we did not include floral rewards in our main analysis due to insufficient data, we did find that plant species with large floral displays and, in particular, large flowers, tended to have higher pollen and nectar quantity.
+Thus, we demonstrate that globally, reproductive trait covariation in flowering plants likely imposes constraints on the broader spectrum of plant trait variation.
+
+Overall, plant reproductive traits explained interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations across spatial large scales.
+For example, we found that all floral visitor guilds interacted more frequently with large flowered and pollinator dependent plant species, which aligns with previous findings {[}\protect\hyperlink{ref-hegland2005}{68}--\protect\hyperlink{ref-kaiser2014}{70}{]}.
+As predicted by evolutionary life-history theory {[}\protect\hyperlink{ref-stebbins1970}{71}{]}, larger investment in floral display and rewards to attract pollinators occurs when pollinator dependence is high.
+However, the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different floral visitor guilds {[}\protect\hyperlink{ref-galen1999}{72}{]}.
+For instance, smaller flowers are visited less overall, but they are inexpensive to produce (e.g., have a low ovule number) and low visitation rate at the individual flower level can be compensated by overall visitation at the plant level by producing many flowers resulting in a larger quantity of small fruits {[}\protect\hyperlink{ref-kettle2011}{26}{]}.
+In addition, because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and floral visitor guilds could indicate the existence of pollination syndromes {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4},\protect\hyperlink{ref-rosas2014}{31},\protect\hyperlink{ref-faegri2013}{73}{]}.
+For instance, bees had a higher number of interacting partners on plant species with large flowers but interacted more frequently with species with small flowers while syrphid flies showed the opposite trend.
+This could be reflective of differences in the ecology and behaviour between these pollinator guilds {[}\protect\hyperlink{ref-rader2020}{74},\protect\hyperlink{ref-foldesi2021}{75}{]} that ultimately exert different selective pressures, leading divergent plant reproductive strategies.
+In any case, it is worth noting that local factors (e.g., species relative abundances or phenologies) likely contribute to the variability in the association between the plant reproductive spectrum and floral visitors {[}\protect\hyperlink{ref-bartomeus2016}{33},\protect\hyperlink{ref-vazquez2007}{76},\protect\hyperlink{ref-encinas2012}{77}{]}.
+
+Our study provides a comprehensive assessment of reproductive trait covariation patterns in flowering plants, using a global dataset of traits for plant species within plant-pollinator networks.
+We show the importance of floral visitors in mediating reproductive trait correlations and identify the need to consider broader plant reproductive strategies, rather than just flower morphology, to understand patterns of plant-pollinator interactions.
+Further, we provide empirical evidence of reproductive trait associations that complements trait covariation studies for other plant organs, highlighting the need to include reproductive traits in the global spectrum of plant form and function.
+Future work incorporating underrepresented areas of the world and additional relevant reproductive traits (e.g., flower life span and colour) will be valuable for enhancing our understanding of the plant reproductive spectrum and associated plant-pollinator interactions.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
+\CSLLeftMargin{21. }
+\CSLRightInline{Rüger N, Comita LS, Condit R, Purves D, Rosenbaum B, Visser MD, Wright SJ, Wirth C.
+2018 Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
+\emph{Ecol.
+Lett.} \textbf{21}, 1075--1084.
+(doi:\href{https://doi.org/10.1111/ele.12974}{10.1111/ele.12974})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-shipley2006}{}}%
+\CSLLeftMargin{22. }
+\CSLRightInline{Shipley B, Lechowicz MJ, Wright I, Reich PB.
+2006 Fundamental trade-offs generating the worldwide leaf economics spectrum.
+\emph{Ecology} \textbf{87}, 535--541.
+(doi:\href{https://doi.org/10.1890/05-1051}{10.1890/05-1051})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-donovan2011}{}}%
+\CSLLeftMargin{23. }
+\CSLRightInline{Donovan LA, Maherali H, Caruso CM, Huber H, Kroon H de.
+2011 The evolution of the worldwide leaf economics spectrum.
+\emph{Trends in Ecology \& Evolution} \textbf{26}, 88--95.
+(doi:\href{https://doi.org/10.1016/j.tree.2010.11.011}{10.1016/j.tree.2010.11.011})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-osnas2013}{}}%
+\CSLLeftMargin{24. }
+\CSLRightInline{Osnas JL, Lichstein JW, Reich PB, Pacala SW.
+2013 Global leaf trait relationships: Mass, area, and the leaf economics spectrum.
+\emph{Science} \textbf{340}, 741--744.
+(doi:\href{https://doi.org/10.1126/science.1231574}{10.1126/science.1231574})}
+
 \leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
-\CSLLeftMargin{21. }
+\CSLLeftMargin{25. }
 \CSLRightInline{Sargent RD, Goodwillie C, Kalisz S, Ree RH.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{26. }
 \CSLRightInline{Kettle CJ, Maycock CR, Ghazoul J, Hollingsworth PM, Khoo E, Sukri RSH, Burslem DFRP.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{27. }
 \CSLRightInline{Goodwillie C \emph{et al.} 2010 Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{28. }
 \CSLRightInline{Barrett SCH.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
+\CSLLeftMargin{29. }
+\CSLRightInline{Munoz F, Violle C, Cheptou P-O.
+2016 {CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
+\emph{Oikos} \textbf{125}, 1296--1303.
+(doi:\href{https://doi.org/10.1111/oik.02328}{10.1111/oik.02328})}
+
 \leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Moeller DA \emph{et al.} 2017 Global biogeography of mating system variation in seed plants.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-baude2016}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Baude M, Kunin WE, Boatman ND, Conyers S, Davies N, Gillespie MA, Morton RD, Smart SM, Memmott J.
-2016 Historical nectar assessment reveals the fall and rise of floral resources in britain.
-\emph{Nature} \textbf{530}, 85--88.
-(doi:\href{https://doi.org/10.1038/nature16532}{10.1038/nature16532})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Munoz F, Violle C, Cheptou P-O.
-2016 {CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
-\emph{Oikos} \textbf{125}, 1296--1303.
-(doi:\href{https://doi.org/10.1111/oik.02328}{10.1111/oik.02328})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-grossenbacher2017}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{Grossenbacher DL \emph{et al.} 2017 Self-compatibility is over-represented on islands.
-\emph{New Phytol.} \textbf{215}, 469--478.
-(doi:\href{https://doi.org/10.1111/nph.14534}{10.1111/nph.14534})}
+\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
+\CSLLeftMargin{31. }
+\CSLRightInline{Rosas-Guerrero V, Aguilar R, Martén-Rodríguez S, Ashworth L, Lopezaraiza-Mikel M, Bastida JM, Quesada M.
+2014 A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
+\emph{Ecol.
+Lett.} \textbf{17}, 388--400.
+(doi:\href{https://doi.org/10.1111/ele.12224}{10.1111/ele.12224})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
+\CSLLeftMargin{32. }
+\CSLRightInline{Stang M, Klinkhamer PGL, Waser NM, Stang I, van der Meijden E.
+2009 Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
+\emph{Ann.
+Bot.} \textbf{103}, 1459--1469.
+(doi:\href{https://doi.org/10.1093/aob/mcp027}{10.1093/aob/mcp027})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
+\CSLLeftMargin{33. }
+\CSLRightInline{Bartomeus I, Gravel D, Tylianakis JM, Aizen MA, Dickie IA, Bernard-Verdier M.
+2016 A common framework for identifying linkage rules across different types of interactions.
+\emph{Funct.
+Ecol.} \textbf{30}, 1894--1903.
+(doi:\href{https://doi.org/10.1111/1365-2435.12666}{10.1111/1365-2435.12666})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
+\CSLLeftMargin{34. }
+\CSLRightInline{Tur C, Castro-Urgal R, Traveset A.
+2013 Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}.
+\emph{PLoS One} \textbf{8}, e78294.
+(doi:\href{https://doi.org/10.1371/journal.pone.0078294}{10.1371/journal.pone.0078294})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
+\CSLLeftMargin{35. }
+\CSLRightInline{Junker RR, Blüthgen N, Brehm T, Binkenstein J, Paulus J, Schaefer HM, Stang M.
+2013 Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
+\emph{Funct.
+Ecol.} \textbf{27}, 329--341.
+(doi:\href{https://doi.org/10.1111/1365-2435.12005}{10.1111/1365-2435.12005})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
+\CSLLeftMargin{36. }
+\CSLRightInline{Coux C, Rader R, Bartomeus I, Tylianakis JM.
+2016 Linking species functional roles to their network roles.
+\emph{Ecol.
+Lett.} \textbf{19}, 762--770.
+(doi:\href{https://doi.org/10.1111/ele.12612}{10.1111/ele.12612})}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
+\CSLLeftMargin{37. }
+\CSLRightInline{Ibanez S.
+2012 Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks.
+\emph{Oecologia} \textbf{170}, 233--242.
+(doi:\href{https://doi.org/10.1007/s00442-012-2290-3}{10.1007/s00442-012-2290-3})}
 
 \leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Sargent RD, Ackerly DD.
@@
 (doi:\href{https://doi.org/10.1016/j.tree.2007.11.003}{10.1016/j.tree.2007.11.003})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rech2016}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Rech AR, Dalsgaard B, Sandel B, Sonne J, Svenning J-C, Holmes N, Ollerton J.
-2016 The macroecology of animal versus wind pollination: Ecological factors are more important than historical climate stability.
-\emph{Plant Ecol.
-Divers.} \textbf{9}, 253--262.
-(doi:\href{https://doi.org/10.1080/17550874.2016.1207722}{10.1080/17550874.2016.1207722})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Rüger N, Comita LS, Condit R, Purves D, Rosenbaum B, Visser MD, Wright SJ, Wirth C.
-2018 Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
-\emph{Ecol.
-Lett.} \textbf{21}, 1075--1084.
-(doi:\href{https://doi.org/10.1111/ele.12974}{10.1111/ele.12974})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Rosas-Guerrero V, Aguilar R, Martén-Rodríguez S, Ashworth L, Lopezaraiza-Mikel M, Bastida JM, Quesada M.
-2014 A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
-\emph{Ecol.
-Lett.} \textbf{17}, 388--400.
-(doi:\href{https://doi.org/10.1111/ele.12224}{10.1111/ele.12224})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{Stang M, Klinkhamer PGL, Waser NM, Stang I, van der Meijden E.
-2009 Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
-\emph{Ann.
-Bot.} \textbf{103}, 1459--1469.
-(doi:\href{https://doi.org/10.1093/aob/mcp027}{10.1093/aob/mcp027})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{Bartomeus I, Gravel D, Tylianakis JM, Aizen MA, Dickie IA, Bernard-Verdier M.
-2016 A common framework for identifying linkage rules across different types of interactions.
-\emph{Funct.
-Ecol.} \textbf{30}, 1894--1903.
-(doi:\href{https://doi.org/10.1111/1365-2435.12666}{10.1111/1365-2435.12666})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Tur C, Castro-Urgal R, Traveset A.
-2013 Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}.
-\emph{PLoS One} \textbf{8}, e78294.
-(doi:\href{https://doi.org/10.1371/journal.pone.0078294}{10.1371/journal.pone.0078294})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Junker RR, Blüthgen N, Brehm T, Binkenstein J, Paulus J, Schaefer HM, Stang M.
-2013 Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
-\emph{Funct.
-Ecol.} \textbf{27}, 329--341.
-(doi:\href{https://doi.org/10.1111/1365-2435.12005}{10.1111/1365-2435.12005})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Coux C, Rader R, Bartomeus I, Tylianakis JM.
-2016 Linking species functional roles to their network roles.
-\emph{Ecol.
-Lett.} \textbf{19}, 762--770.
-(doi:\href{https://doi.org/10.1111/ele.12612}{10.1111/ele.12612})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{Ibanez S.
-2012 Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks.
-\emph{Oecologia} \textbf{170}, 233--242.
-(doi:\href{https://doi.org/10.1007/s00442-012-2290-3}{10.1007/s00442-012-2290-3})}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-friedman2011}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-faegri2013}{}}%
 \CSLLeftMargin{73. }
-\CSLRightInline{Friedman J, Barrett SC.
-2011 The evolution of ovule number and flower size in wind-pollinated plants.
-\emph{The American Naturalist} \textbf{177}, 246--257.
-(doi:\href{https://doi.org/10.1086/657954}{10.1086/657954})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-faegri2013}{}}%
+\CSLRightInline{Faegri K, Van Der Pijl L. 2013 \emph{Principles of pollination ecology}. {3rd edn}. {Elsevier}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-rader2020}{}}%
 \CSLLeftMargin{74. }
-\CSLRightInline{Faegri K, Van Der Pijl L. 2013 Principles of pollination ecology. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-rader2020}{}}%
-\CSLLeftMargin{75. }
 \CSLRightInline{Rader R, Cunningham S, Howlett B, Inouye D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
-\CSLLeftMargin{76. }
+\CSLLeftMargin{75. }
 \CSLRightInline{Földesi R, Howlett BG, Grass I, Batáry P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
-\CSLLeftMargin{77. }
+\CSLLeftMargin{76. }
 \CSLRightInline{Vázquez DP, Melián CJ, Williams NM, Blüthgen N, Krasnov BR, Poulin R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
-\CSLLeftMargin{78. }
+\CSLLeftMargin{77. }
 \CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS.

### 2022-07-19 Google_drive.R

@@ -17,5 +17,12 @@ library(trackdown)
 #upload file
 upload_file(
   file = "Manuscript/Lanuza_et_al_2022.Rmd", 
-  gfile = "Untitled"
+  gfile = "Reproductive_traits"
+)
+
+
+#download file 
+download_file(
+  file = "Manuscript/Lanuza_et_al_2022.Rmd", 
+  gfile = "Reproductive_traits"
 )

### 2022-07-19 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
updating fig s1

@@
 
-colnames(t) <- c("Breeding system","Compatibility system",
-         "Autonomous selfing qualitative","Autonomous selfing quantitative", "Flower shape", "Flower symmetry", 
+t = t %>% select(!Autonomous_selfing_level)
+
+colnames(t) <- c("Breeding system","Compatibility system","Autonomous selfing level", "Flower shape", "Flower symmetry", 
                  "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 

### 2022-09-26 Main_Figures/Figure3.Rmd
updates on ms with rwcomments

@@
 ggtitle(NULL, subtitle = "(e)") +
-annotate(geom = "text", x = -1.7, y =0.2 , label = "Low poll. depend.", size = 8) +
+annotate(geom = "text", x = -1.78, y =0.2 , label = "High aut. selfing", size = 8) +
 annotate(geom = "text", x = -1.65, y =0.12 , label = "Small floral display", size = 8) + 
-annotate(geom = "text", x = 1.8, y =0.2 , label = "High poll. depend.", size = 8) + 
+annotate(geom = "text", x = 1.665, y =0.2 , label = "Low aut. selfing", size = 8) + 
 annotate(geom = "text", x = 1.85, y =0.12 , label = "Large floral display", size = 8) +
 xlab("") +
-annotate(geom = "text", x = -0.1, y =0.35 , label = "Pollinator dependence - Floral display axis", size = 8.5, fontface =2) +
+annotate(geom = "text", x = -0.1, y =0.35 , label = "Autonomous selfing - Floral display axis", size = 8.5, fontface =2) +
 theme(panel.border=element_rect(color="black",size=1.2))
@@
 ggtitle(NULL, subtitle = "(f)") +
-annotate(geom = "text", x = -1.6, y =0.2 , label = "Short styles", size = 8) +
-annotate(geom = "text", x = -1.25, y =0.12 , label = "High poll. depend.", size = 8) + 
-annotate(geom = "text", x = 2.15, y =0.2 , label = "Long styles", size = 8) + 
-annotate(geom = "text", x = 2.5, y =0.12 , label = "Low poll. depend.", size = 8) +
+annotate(geom = "text", x = -1.48, y =0.2 , label = "Short styles", size = 8) +
+annotate(geom = "text", x = -1.25, y =0.12 , label = "Low aut. selfing", size = 8) + 
+annotate(geom = "text", x = 2.24, y =0.2 , label = "Long styles", size = 8) + 
+annotate(geom = "text", x = 2.5, y =0.12 , label = "High aut. selfing", size = 8) +
 xlab(" \n \n  ") +
-annotate(geom = "text", x = 0.25, y =0.35 , label = "Style length - Pollinator dependence axis", size = 8.5, fontface =2) +
+annotate(geom = "text", x = 0.25, y =0.35 , label = "Style length - Autonomous selfing axis", size = 8.5, fontface =2) +
 theme(panel.border=element_rect(color="black",size=1.2))

### 2022-09-26 Manuscript/Lanuza_et_al_2022.Rmd
updates on ms with rwcomments

@@
 Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with floral visitors.
-We show that over 50% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the positive correlation between pollinator dependence and floral display size.
-In empirical plant-pollinator networks, the plant position within these axes was associated with the number of interacting partners and the visitation rates of the distinct floral visitor guilds, but the unexplained variability found highlights the need to incorporate other factors along with reproductive traits to fully explain plant-pollinator interactions.
+We show that over 50% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the negative correlation between autonomous selfing and floral display size.
+In addition, these reproductive axes were associated with different numbers of interacting partners and visitation rates of the distinct floral visitor guilds.
+However, the relatively small amount of variance explained by the different reproductive axes highlight the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
 Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping networks of plant-pollinator interactions at a global scale.
@@
 However, studies that look at multiple traits tend to overlook plant reproductive traits [@evojtko2020; @ruger2018; @roddy2021], and focus on trait correlations in other plant organs such as morphological and physiological leaf traits [@wright2004; @shipley2006; @donovan2011; @osnas2013].
-Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs (e.g., the negative correlation between flower size and flower number [@sargent2007; @kettle2011]; the positive association between flower size and outcrossing rate [@goodwillie2010]; or the positive correlation between outcrossing rate and lifespan [@barrett2003; @munoz2016; @moeller2017]).
+Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs (e.g., the negative correlation between flower size and flower number [@sargent2007; @kettle2011; @vojtko2022]; the positive association between flower size and outcrossing rate [@goodwillie2010]; or the positive correlation between outcrossing rate and lifespan [@barrett2003; @munoz2016; @moeller2017]).
 Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships [@roddy2021], we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
@@
 We conducted two different imputations, one for the full set of species (1,506 species: 5.79% of missing values), and excluded nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and results for the two datasets were consitent (Fig S3 and Fig S4).
-
-## (f) Plant strategies
+To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and results for the two datasets were consistent (Fig S3 and Fig S4).
+
+## (f) Plant strategies analysis
 
@@
 Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species [@ballantyne2015], the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination [@vazquez2005; @vazquez2012].
-We divided floral visitors into six main taxonomical guilds that differ in life form, behaviour and thus likely play similar ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
+We divided floral visitors into six main taxonomical guilds that differ in life form, behaviour and thus likely play different ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
 Moreover, because bees had the greatest number of occurrences in networks  (2,256 records) and the highest frequency of visits, we further broke this group down into the main bee families (Andrenidae, Apidae, Colletidae, Halictidae, and Megachilidae).
@@
 
-## (a) Plant strategies
+## (a) Plant strategies analysis
 
@@
 For example, *Petunia axillaris* on average, is 0.5 m high and has approximately 10 flowers per plant that are over 50 mm wide with 25 mm long styles and over 200 ovules.
-The second principal component (PC2; the pollinator dependence axis) encompassed 25.05% of the trait variation and represented variation from low to high autonomous selfing (i.e., high to low pollinator dependence).
+The second principal component (PC2; the autonomous selfing - floral display axis) encompassed 25.05% of the trait variation and represented variation from low to high autonomous selfing (i.e., high to low pollinator dependence).
 The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but all other traits (except ovule number) made moderate contributions (loadings ranging between 0.27 to 0.4; table S3).
-Generally speaking, species with high pollinator dependence had larger and many flowers with long styles, and were tall.
+Generally speaking, species with low autonomous selfing had larger and many flowers with long styles, and were tall.
 *Zuccagnia punctata* occurred at this extreme of the spectrum, which is a self-incompatible species, completely dependent on animal pollination for seed production, producing  approximately 1,500 flowers per plant with an average height of 3 m and 20 mm long styles.
-In contrast, species with low pollinator dependence tended to have fewer and smaller flowers with shorter styles, and were shorter in height.
+In contrast, species with high autonomous selfing tended to have fewer and smaller flowers with shorter styles, and were shorter in height.
 *Veronica peregrina* occurred at this end of the spectrum, and is a self-compatible plant that requires little or no pollination by animals, it has approximately 20 flowers per plant, is 0.2 m high and has 0.25 mm long styles.
-The third principal component (PC3; the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \|-0.51\|), where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
-The remaining traits, apart from ovule number, were all positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; table S3).
+The third principal component (PC3; the style length - autonomous selfing axis) explained a considerable amount of trait variability (19.17%) and represented a positive correlation between style length (loading = -0.66) and autonomous selfing (loading = \|-0.51\|), where species with short styles had low autonomous selfing and species with long styles high autonomous selfing.
+The remaining traits, apart from ovule number, were all positively correlated with style length and autonomous selfing (loadings from -0.23 to -0.46; table S3).
 In addition, the pPCA with the subset of species that we had nectar and pollen quantity data for showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with floral display size.
@@
   plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Pollinator dependence - Floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+  plot <- plot + ylab(paste("Autonomous selfing - Floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
 
@@
 For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S7a and figure S7b; Tukey test *P* \< 0.05).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S7c and figure S7d; Tukey test *P* \< 0.05).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S7c and figure S7d; Tukey test *P* \< 0.05).
 Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f; Tukey test *P* \< 0.05).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h; Tukey test *P* \< 0.05).
-Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and high pollinator dependence, while the latter had more flowers and lower pollinator dependence (figure S7i and figure S7j; Tukey test *P* \< 0.05).
-Finally, in terms of flower symmetry, zygomorphic flowers were associated with lower pollinator dependence, whereas actinomorphic flowers were more dependent on pollinators (figure S7k and figure S7l; Tukey test *P* \< 0.05).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S7g and figure S7h; Tukey test *P* \< 0.05).
+Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S7i and figure S7j; Tukey test *P* \< 0.05).
+Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S7k and figure S7l; Tukey test *P* \< 0.05).
 
@@
 
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)  + ylab("Pollinator dependence - Floral display axis")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)  + ylab("Autonomous selfing - Floral display axis")
 
@@
     xlab("Flower number - Flower size axis") +
-    ylab("Pollinator dependence - Floral display axis")
+    ylab("Autonomous selfing - Floral display axis")
 
@@
 We found similar trends for visitation rates on the flower number - flower size axis,  but bees and syrphids visited plant species with many small flowers more frequently (figure 3d).
-On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had many interaction partners and recieved many visits from all floral visitor guilds (figure 3b and figure 3e).
-Finally, on the style length - pollinator dependence axis, plant species with short styles and high pollinator dependence had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and low pollinator dependence (figure 3c).
-Plants with long styles and low pollinator dependence interacted more frequently with Lepidoptera and non-bee-Hymenoptera (figure 3f).
+On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and recieved many visits from all floral visitor guilds (figure 3b and figure 3e).
+Finally, on the style length - autonomous selfing axis, plant species with short styles and low autonomous selfing had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and high autonomous selfing (figure 3c).
+Plants with long styles and high autonomous selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera (figure 3f).
 
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
-PC1 represents the flower number - flower size axis, PC2 represents the pollinator dependence axis and PC3 represents the style length - pollinator dependence axis.
+PC1 represents the flower number - flower size axis, PC2 represents the autonomous selfing - floral display axis and PC3 represents the style length - autonomous selfing axis.
 For visualization purposes due to large differences between number of visits from bees and the rest of the pollinator guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
@@
 Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
+Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and specialization.
 On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
 However, specialization (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
-On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S9c).
+On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S9c).
 Again, specialization showed the opposite trend to the number of visits (figure S9i).
@@
 We found strong covariation among traits within the flowering plant reproductive spectrum, which shapes interactions with floral visitors at a global scale.
-Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50% and 70% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, pollinator dependence and floral display, and style length and pollinator dependence.
-Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits [@diaz2016; @carmona2021], our results align with the largest and most recent study of plant life strategies that included reproductive, form and size related traits [@salguero2016].
+Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50% and 70% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, autonomous selfing and floral display, and style length and autonomous selfing.
+Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits [@diaz2016; @carmona2021], our results align with the two largest and most recent studies of plant life strategies that included reproductive, form and size related traits [@salguero2016; @vojtko2022].
 The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct floral visitor guilds.
@@
 Our study also complements previous work linking plant breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers also have woody life forms and many flowers.
-Moreover, we identify the previously documented positive association between outcrossing rate and floral display size [@goodwillie2010], where species with high pollinator dependence also allocate large resource quantities to attract floral visitors.
+Moreover, we identify the previously documented positive association between outcrossing rate and floral display size [@goodwillie2010], where species with low autonomous selfing levels also allocate large resource quantities to attract floral visitors.
 Although we did not include floral rewards in our main analysis due to insufficient data, we did find that plant species with large floral displays and, in particular, large flowers, tended to have higher pollen and nectar quantity.
@@
 Overall, plant reproductive traits explained interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations across spatial large scales.
-For example, we found that all floral visitor guilds interacted more frequently with large flowered and pollinator dependent plant species, which aligns with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
+For example, we found that all floral visitor guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
 As predicted by evolutionary life-history theory [@stebbins1970], larger investment in floral display and rewards to attract pollinators occurs when pollinator dependence is high.
@@
 We show the importance of floral visitors in mediating reproductive trait correlations and identify the need to consider broader plant reproductive strategies, rather than just flower morphology, to understand patterns of plant-pollinator interactions.
-Further, we provide empirical evidence of reproductive trait associations that complements trait covariation studies for other plant organs, highlighting the need to include reproductive traits in the global spectrum of plant form and function.
+Further, we provide empirical evidence of reproductive trait associations that complement trait covariation studies for other plant organs, highlighting the need to include reproductive traits in the global spectrum of plant form and function.
 Future work incorporating underrepresented areas of the world and additional relevant reproductive traits (e.g., flower life span and colour) will be valuable for enhancing our understanding of the plant reproductive spectrum and associated plant-pollinator interactions.

### 2022-09-26 Manuscript/Lanuza_et_al_2022.tex
updates on ms with rwcomments

@@
 Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with floral visitors.
-We show that over 50\% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the positive correlation between pollinator dependence and floral display size.
-In empirical plant-pollinator networks, the plant position within these axes was associated with the number of interacting partners and the visitation rates of the distinct floral visitor guilds, but the unexplained variability found highlights the need to incorporate other factors along with reproductive traits to fully explain plant-pollinator interactions.
+We show that over 50\% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the negative correlation between autonomous selfing and floral display size.
+In addition, these reproductive axes were associated with different numbers of interacting partners and visitation rates of the distinct floral visitor guilds.
+However, the relatively small amount of variance explained by the different reproductive axes highlight the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
 Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping networks of plant-pollinator interactions at a global scale.
@@
 However, studies that look at multiple traits tend to overlook plant reproductive traits {[}\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-evojtko2020}{20},\protect\hyperlink{ref-ruger2018}{21}{]}, and focus on trait correlations in other plant organs such as morphological and physiological leaf traits {[}\protect\hyperlink{ref-wright2004}{13},\protect\hyperlink{ref-shipley2006}{22}--\protect\hyperlink{ref-osnas2013}{24}{]}.
-Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs (e.g., the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{25},\protect\hyperlink{ref-kettle2011}{26}{]}; the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{27}{]}; or the positive correlation between outcrossing rate and lifespan {[}\protect\hyperlink{ref-barrett2003}{28}--\protect\hyperlink{ref-moeller2017}{30}{]}).
+Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs (e.g., the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{25}--\protect\hyperlink{ref-vojtko2022}{27}{]}; the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{28}{]}; or the positive correlation between outcrossing rate and lifespan {[}\protect\hyperlink{ref-barrett2003}{29}--\protect\hyperlink{ref-moeller2017}{31}{]}).
 Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships {[}\protect\hyperlink{ref-roddy2021}{10}{]}, we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
 
-Trait-based approaches {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{31}{]} and trait-matching analyses {[}\protect\hyperlink{ref-stang2009}{32},\protect\hyperlink{ref-bartomeus2016}{33}{]} are powerful for exploring the underlying mechanisms driving plant-pollinator interactions.
-For example, plant traits can define species' network roles {[}e.g., specialists vs generalists \protect\hyperlink{ref-tur2013}{34}{]} and plant species that occupy reproductive trait space extremes are likely to be more specialized and display tighter trait-matching with pollinators {[}\protect\hyperlink{ref-junker2013}{35},\protect\hyperlink{ref-coux2016}{36}{]}.
-Indeed, the degree of morphological matching between plants and floral visitors often determines whether or not interactions occur, and consequently influences the broader network structure {[}\protect\hyperlink{ref-stang2009}{32},\protect\hyperlink{ref-ibanez2012}{37}{]}.
-However, it is still unclear how specific reproductive traits (e.g., mating or compatibility system) influence plant-pollinator associations {[}\protect\hyperlink{ref-tur2013}{34},\protect\hyperlink{ref-sargent2008}{38},\protect\hyperlink{ref-devaux2014}{39}{]}.
-Indeed, both morphology and mating system can determine a species' functional role within pollination networks, and the combination of several traits increases power for predicting network structure {[}\protect\hyperlink{ref-eklof2013}{40}{]}.
-Because the species position within the multidimensional trait space can result in different interaction patterns or adaptations to pollinators {[}see \protect\hyperlink{ref-dehling2016}{41} for a purely morphological approach{]}, the use of the reproductive trait space to explore plant-pollinator interactions could help to identify species functional roles and associations of traits with specific pollinators (i.e., pollination syndromes).
+Trait-based approaches {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{32}{]} and trait-matching analyses {[}\protect\hyperlink{ref-stang2009}{33},\protect\hyperlink{ref-bartomeus2016}{34}{]} are powerful for exploring the underlying mechanisms driving plant-pollinator interactions.
+For example, plant traits can define species' network roles {[}e.g., specialists vs generalists \protect\hyperlink{ref-tur2013}{35}{]} and plant species that occupy reproductive trait space extremes are likely to be more specialized and display tighter trait-matching with pollinators {[}\protect\hyperlink{ref-junker2013}{36},\protect\hyperlink{ref-coux2016}{37}{]}.
+Indeed, the degree of morphological matching between plants and floral visitors often determines whether or not interactions occur, and consequently influences the broader network structure {[}\protect\hyperlink{ref-stang2009}{33},\protect\hyperlink{ref-ibanez2012}{38}{]}.
+However, it is still unclear how specific reproductive traits (e.g., mating or compatibility system) influence plant-pollinator associations {[}\protect\hyperlink{ref-tur2013}{35},\protect\hyperlink{ref-sargent2008}{39},\protect\hyperlink{ref-devaux2014}{40}{]}.
+Indeed, both morphology and mating system can determine a species' functional role within pollination networks, and the combination of several traits increases power for predicting network structure {[}\protect\hyperlink{ref-eklof2013}{41}{]}.
+Because the species position within the multidimensional trait space can result in different interaction patterns or adaptations to pollinators {[}see \protect\hyperlink{ref-dehling2016}{42} for a purely morphological approach{]}, the use of the reproductive trait space to explore plant-pollinator interactions could help to identify species functional roles and associations of traits with specific pollinators (i.e., pollination syndromes).
 
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to benefit, to some degree, from animal pollination.
-Many of these networks are freely available either as published studies {[}e.g., \protect\hyperlink{ref-carvalheiro2014}{42},\protect\hyperlink{ref-olesen2007}{43},\protect\hyperlink{ref-fortuna2010}{44}{]} or in online archives {[}e.g., Mangal \protect\hyperlink{ref-poisot2016}{45},The Web of Life \protect\hyperlink{ref-fortuna2010}{44}{]}.
+Many of these networks are freely available either as published studies {[}e.g., \protect\hyperlink{ref-carvalheiro2014}{43},\protect\hyperlink{ref-olesen2007}{44},\protect\hyperlink{ref-fortuna2010}{45}{]} or in online archives {[}e.g., Mangal \protect\hyperlink{ref-poisot2016}{46},The Web of Life \protect\hyperlink{ref-fortuna2010}{45}{]}.
 In total, our network dataset constituted 60 weighted (number of visits) and four unweighted (interaction presence-absence) networks, each sampled at a unique location and year, as well as eight meta-networks where interactions were pooled across several locations and multiple years.
@@
 
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} {[}\protect\hyperlink{ref-chamberlain2020}{46}{]}.
+All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} {[}\protect\hyperlink{ref-chamberlain2020}{47}{]}.
 We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
@@
 
-We calculated the phylogenetic distance between all plant species considered using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{47},\protect\hyperlink{ref-jin2019}{48}{]}.
+We calculated the phylogenetic distance between all plant species considered using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{48},\protect\hyperlink{ref-jin2019}{49}{]}.
 
@@
 
-To avoid excluding species with trait missing values, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{49}{]} which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors from principal component analysis of the phylogenetic distance (PCoA), which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{50}{]}.
-To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} {[}\protect\hyperlink{ref-santos2018}{51}{]} based on a previous conceptual framework that considers phylogenetic eigenvectors {[}\protect\hyperlink{ref-diniz-filho2012}{52}{]}.
+To avoid excluding species with trait missing values, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{50}{]} which allows imputation of datasets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors from principal component analysis of the phylogenetic distance (PCoA), which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{51}{]}.
+To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} {[}\protect\hyperlink{ref-santos2018}{52}{]} based on a previous conceptual framework that considers phylogenetic eigenvectors {[}\protect\hyperlink{ref-diniz-filho2012}{53}{]}.
 We conducted two different imputations, one for the full set of species (1,506 species: 5.79\% of missing values), and excluded nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01\% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and results for the two datasets were consitent (Fig S3 and Fig S4).
-
-\hypertarget{f-plant-strategies}{%
-\subsection{(f) Plant strategies}\label{f-plant-strategies}}
+To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and results for the two datasets were consistent (Fig S3 and Fig S4).
+
+\hypertarget{f-plant-strategies-analysis}{%
+\subsection{(f) Plant strategies analysis}\label{f-plant-strategies-analysis}}
 
@@
 Prior to the analyses, we excluded outliers and standardized the data.
-Specifically, due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{53},\protect\hyperlink{ref-legendre2012}{54}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{54}{]}.
+Specifically, due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{54},\protect\hyperlink{ref-legendre2012}{55}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
+Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{55}{]}.
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{55}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode ``covariance'' because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{56}{]}.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{56}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode ``covariance'' because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{57}{]}.
 Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity data.
@@
 
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{55}{]} and used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{56}{]} and used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
@@
 Specifically, interactions between plants and floral visitors in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
-Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species {[}\protect\hyperlink{ref-ballantyne2015}{57}{]}, the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination {[}\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}{]}.
-We divided floral visitors into six main taxonomical guilds that differ in life form, behaviour and thus likely play similar ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
+Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species {[}\protect\hyperlink{ref-ballantyne2015}{58}{]}, the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination {[}\protect\hyperlink{ref-vazquez2005}{59},\protect\hyperlink{ref-vazquez2012}{60}{]}.
+We divided floral visitors into six main taxonomical guilds that differ in life form, behaviour and thus likely play different ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
 Moreover, because bees had the greatest number of occurrences in networks (2,256 records) and the highest frequency of visits, we further broke this group down into the main bee families (Andrenidae, Apidae, Colletidae, Halictidae, and Megachilidae).
@@
 This is consistent with previous research showing that \emph{A.
-mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems {[}\protect\hyperlink{ref-hung2018}{60}{]}.
+mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems {[}\protect\hyperlink{ref-hung2018}{61}{]}.
 Hence, to control for the effect of \emph{A.
@@
 
-We used Bayesian generalized linear mixed models in the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{61}{]} to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
+We used Bayesian generalized linear mixed models in the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{62}{]} to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
 Because we were interested in possible differences in visitation patterns among floral visitor guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds in the model.
@@
 We specified for the presence or absence of an interaction and number of visits with Bernoulli and a zero inflated negative binomial distributions, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results {[}\protect\hyperlink{ref-burkner2017}{61}{]}.
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}\protect\hyperlink{ref-gabry2019}{62}{]}.
+The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results {[}\protect\hyperlink{ref-burkner2017}{62}{]}.
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}\protect\hyperlink{ref-gabry2019}{63}{]}.
 
@@
 We also used Bayesian modeling to investigate how the main axes of trait variation determined different plant species' functional roles within pollination networks.
-For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{63}{]}, with clear ecological interpretations and are relevant for defining species' functional roles in networks.
-Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{64}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function in the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{63}{]}.
+For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{64}{]}, with clear ecological interpretations and are relevant for defining species' functional roles in networks.
+Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{65}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
+Normalized degree and specialization were calculated with the \emph{specieslevel} function in the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{64}{]}.
 We modeled each plant species metric (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
@@
 
-\hypertarget{a-plant-strategies}{%
-\subsection{(a) Plant strategies}\label{a-plant-strategies}}
+\hypertarget{a-plant-strategies-analysis}{%
+\subsection{(a) Plant strategies analysis}\label{a-plant-strategies-analysis}}
 
@@
 For example, \emph{Petunia axillaris} on average, is 0.5 m high and has approximately 10 flowers per plant that are over 50 mm wide with 25 mm long styles and over 200 ovules.
-The second principal component (PC2; the pollinator dependence axis) encompassed 25.05\% of the trait variation and represented variation from low to high autonomous selfing (i.e., high to low pollinator dependence).
+The second principal component (PC2; the autonomous selfing - floral display axis) encompassed 25.05\% of the trait variation and represented variation from low to high autonomous selfing (i.e., high to low pollinator dependence).
 The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but all other traits (except ovule number) made moderate contributions (loadings ranging between 0.27 to 0.4; table S3).
-Generally speaking, species with high pollinator dependence had larger and many flowers with long styles, and were tall.
+Generally speaking, species with low autonomous selfing had larger and many flowers with long styles, and were tall.
 \emph{Zuccagnia punctata} occurred at this extreme of the spectrum, which is a self-incompatible species, completely dependent on animal pollination for seed production, producing approximately 1,500 flowers per plant with an average height of 3 m and 20 mm long styles.
-In contrast, species with low pollinator dependence tended to have fewer and smaller flowers with shorter styles, and were shorter in height.
+In contrast, species with high autonomous selfing tended to have fewer and smaller flowers with shorter styles, and were shorter in height.
 \emph{Veronica peregrina} occurred at this end of the spectrum, and is a self-compatible plant that requires little or no pollination by animals, it has approximately 20 flowers per plant, is 0.2 m high and has 0.25 mm long styles.
-The third principal component (PC3; the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17\%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \textbar-0.51\textbar), where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
-The remaining traits, apart from ovule number, were all positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; table S3).
+The third principal component (PC3; the style length - autonomous selfing axis) explained a considerable amount of trait variability (19.17\%) and represented a positive correlation between style length (loading = -0.66) and autonomous selfing (loading = \textbar-0.51\textbar), where species with short styles had low autonomous selfing and species with long styles high autonomous selfing.
+The remaining traits, apart from ovule number, were all positively correlated with style length and autonomous selfing (loadings from -0.23 to -0.46; table S3).
 In addition, the pPCA with the subset of species that we had nectar and pollen quantity data for showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with floral display size.
@@
 For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S7a and figure S7b; Tukey test \emph{P} \textless{} 0.05).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S7c and figure S7d; Tukey test \emph{P} \textless{} 0.05).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S7c and figure S7d; Tukey test \emph{P} \textless{} 0.05).
 Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f; Tukey test \emph{P} \textless{} 0.05).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h; Tukey test \emph{P} \textless{} 0.05).
-Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and high pollinator dependence, while the latter had more flowers and lower pollinator dependence (figure S7i and figure S7j; Tukey test \emph{P} \textless{} 0.05).
-Finally, in terms of flower symmetry, zygomorphic flowers were associated with lower pollinator dependence, whereas actinomorphic flowers were more dependent on pollinators (figure S7k and figure S7l; Tukey test \emph{P} \textless{} 0.05).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S7g and figure S7h; Tukey test \emph{P} \textless{} 0.05).
+Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S7i and figure S7j; Tukey test \emph{P} \textless{} 0.05).
+Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S7k and figure S7l; Tukey test \emph{P} \textless{} 0.05).
 
@@
 We found similar trends for visitation rates on the flower number - flower size axis, but bees and syrphids visited plant species with many small flowers more frequently (figure 3d).
-On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had many interaction partners and recieved many visits from all floral visitor guilds (figure 3b and figure 3e).
-Finally, on the style length - pollinator dependence axis, plant species with short styles and high pollinator dependence had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and low pollinator dependence (figure 3c).
-Plants with long styles and low pollinator dependence interacted more frequently with Lepidoptera and non-bee-Hymenoptera (figure 3f).
+On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and recieved many visits from all floral visitor guilds (figure 3b and figure 3e).
+Finally, on the style length - autonomous selfing axis, plant species with short styles and low autonomous selfing had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and high autonomous selfing (figure 3c).
+Plants with long styles and high autonomous selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera (figure 3f).
 
@@
 \caption{\label{fig:unnamed-chunk-4}\textbf{Figure 3.} Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
-PC1 represents the flower number - flower size axis, PC2 represents the pollinator dependence axis and PC3 represents the style length - pollinator dependence axis.
+PC1 represents the flower number - flower size axis, PC2 represents the autonomous selfing - floral display axis and PC3 represents the style length - autonomous selfing axis.
 For visualization purposes due to large differences between number of visits from bees and the rest of the pollinator guilds, the number of visits was log-transformed (Y-axis of lower panel).}
@@
 Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
+Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and specialization.
 On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
 However, specialization (d') was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
-On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S9c).
+On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S9c).
 Again, specialization showed the opposite trend to the number of visits (figure S9i).
@@
 We found strong covariation among traits within the flowering plant reproductive spectrum, which shapes interactions with floral visitors at a global scale.
-Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50\% and 70\% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, pollinator dependence and floral display, and style length and pollinator dependence.
-Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{17},\protect\hyperlink{ref-carmona2021}{19}{]}, our results align with the largest and most recent study of plant life strategies that included reproductive, form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
+Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50\% and 70\% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, autonomous selfing and floral display, and style length and autonomous selfing.
+Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{17},\protect\hyperlink{ref-carmona2021}{19}{]}, our results align with the two largest and most recent studies of plant life strategies that included reproductive, form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-vojtko2022}{27}{]}.
 The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct floral visitor guilds.
-However, the unexplained variability found highlights the need to account for other local factors, such as species relative abundances {[}\protect\hyperlink{ref-bartomeus2016}{33}{]}, along with reproductive traits, to better explain plant-pollinator associations.
+However, the unexplained variability found highlights the need to account for other local factors, such as species relative abundances {[}\protect\hyperlink{ref-bartomeus2016}{34}{]}, along with reproductive traits, to better explain plant-pollinator associations.
 
 Our study provides strong evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1,200 species).
-Specifically, by using a multitrait approach, we are able to link the reproductive spectrum of plant trait variation with the previously described ``fast-slow continuum'' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{65}{]} life-history strategies.
+Specifically, by using a multitrait approach, we are able to link the reproductive spectrum of plant trait variation with the previously described ``fast-slow continuum'' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{66}{]} life-history strategies.
 This fast-slow continuum was illustrated by the associations between reproductive traits and plant height, life form and lifespan traits.
-For instance, although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{25},\protect\hyperlink{ref-kettle2011}{26},\protect\hyperlink{ref-worley2000}{66}{]}, it has only been investigated across a few hundred Angiosperm species in the absence of a multitrait perspective.
+For instance, although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{25},\protect\hyperlink{ref-kettle2011}{26},\protect\hyperlink{ref-worley2000}{67}{]}, it has only been investigated across a few hundred Angiosperm species in the absence of a multitrait perspective.
 We found support for this trait association and show that other reproductive traits (e.g., style length or ovule number) covary along this flower number - flower size axis.
-Our study also complements previous work linking plant breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{67}{]} by showing that most species with unisexual flowers also have woody life forms and many flowers.
-Moreover, we identify the previously documented positive association between outcrossing rate and floral display size {[}\protect\hyperlink{ref-goodwillie2010}{27}{]}, where species with high pollinator dependence also allocate large resource quantities to attract floral visitors.
+Our study also complements previous work linking plant breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{68}{]} by showing that most species with unisexual flowers also have woody life forms and many flowers.
+Moreover, we identify the previously documented positive association between outcrossing rate and floral display size {[}\protect\hyperlink{ref-goodwillie2010}{28}{]}, where species with low autonomous selfing levels also allocate large resource quantities to attract floral visitors.
 Although we did not include floral rewards in our main analysis due to insufficient data, we did find that plant species with large floral displays and, in particular, large flowers, tended to have higher pollen and nectar quantity.
@@
 Overall, plant reproductive traits explained interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations across spatial large scales.
-For example, we found that all floral visitor guilds interacted more frequently with large flowered and pollinator dependent plant species, which aligns with previous findings {[}\protect\hyperlink{ref-hegland2005}{68}--\protect\hyperlink{ref-kaiser2014}{70}{]}.
-As predicted by evolutionary life-history theory {[}\protect\hyperlink{ref-stebbins1970}{71}{]}, larger investment in floral display and rewards to attract pollinators occurs when pollinator dependence is high.
-However, the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different floral visitor guilds {[}\protect\hyperlink{ref-galen1999}{72}{]}.
+For example, we found that all floral visitor guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings {[}\protect\hyperlink{ref-hegland2005}{69}--\protect\hyperlink{ref-kaiser2014}{71}{]}.
+As predicted by evolutionary life-history theory {[}\protect\hyperlink{ref-stebbins1970}{72}{]}, larger investment in floral display and rewards to attract pollinators occurs when pollinator dependence is high.
+However, the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different floral visitor guilds {[}\protect\hyperlink{ref-galen1999}{73}{]}.
 For instance, smaller flowers are visited less overall, but they are inexpensive to produce (e.g., have a low ovule number) and low visitation rate at the individual flower level can be compensated by overall visitation at the plant level by producing many flowers resulting in a larger quantity of small fruits {[}\protect\hyperlink{ref-kettle2011}{26}{]}.
-In addition, because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and floral visitor guilds could indicate the existence of pollination syndromes {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4},\protect\hyperlink{ref-rosas2014}{31},\protect\hyperlink{ref-faegri2013}{73}{]}.
+In addition, because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and floral visitor guilds could indicate the existence of pollination syndromes {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4},\protect\hyperlink{ref-rosas2014}{32},\protect\hyperlink{ref-faegri2013}{74}{]}.
 For instance, bees had a higher number of interacting partners on plant species with large flowers but interacted more frequently with species with small flowers while syrphid flies showed the opposite trend.
-This could be reflective of differences in the ecology and behaviour between these pollinator guilds {[}\protect\hyperlink{ref-rader2020}{74},\protect\hyperlink{ref-foldesi2021}{75}{]} that ultimately exert different selective pressures, leading divergent plant reproductive strategies.
-In any case, it is worth noting that local factors (e.g., species relative abundances or phenologies) likely contribute to the variability in the association between the plant reproductive spectrum and floral visitors {[}\protect\hyperlink{ref-bartomeus2016}{33},\protect\hyperlink{ref-vazquez2007}{76},\protect\hyperlink{ref-encinas2012}{77}{]}.
+This could be reflective of differences in the ecology and behaviour between these pollinator guilds {[}\protect\hyperlink{ref-rader2020}{75},\protect\hyperlink{ref-foldesi2021}{76}{]} that ultimately exert different selective pressures, leading divergent plant reproductive strategies.
+In any case, it is worth noting that local factors (e.g., species relative abundances or phenologies) likely contribute to the variability in the association between the plant reproductive spectrum and floral visitors {[}\protect\hyperlink{ref-bartomeus2016}{34},\protect\hyperlink{ref-vazquez2007}{77},\protect\hyperlink{ref-encinas2012}{78}{]}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-vojtko2022}{}}%
+\CSLLeftMargin{27. }
+\CSLRightInline{E-Vojtkó A, Junker RR, Bello F de, Götzenberger L.
+2022 Floral and reproductive traits are an independent dimension within the plant economic spectrum of temperate central europe.
+\emph{New Phytologist} (doi:\url{https://doi.org/10.1111/nph.18386})}
+
 \leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{28. }
 \CSLRightInline{Goodwillie C \emph{et al.} 2010 Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Barrett SCH.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Munoz F, Violle C, Cheptou P-O.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Moeller DA \emph{et al.} 2017 Global biogeography of mating system variation in seed plants.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Sargent RD, Ackerly DD.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Devaux C, Lepers C, Porcher E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Eklöf A \emph{et al.} 2013 The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583. (doi:\href{https://doi.org/10.1111/ele.12081}{10.1111/ele.12081})}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Dehling DM, Jordano P, Schaefer HM, Böhning-Gaese K, Schleuning M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Carvalheiro LG \emph{et al.} 2014 The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Olesen JM, Bascompte J, Dupont YL, Jordano P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Fortuna MA, Stouffer DB, Olesen JM, Jordano P, Mouillot D, Krasnov BR, Poulin R, Bascompte J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Poisot T \emph{et al.} 2016 Mangal \textendash{} making ecological network analysis simple.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Chamberlain S \emph{et al.} 2020 Taxize: {Taxonomic} information from around the web.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Smith SA, Brown JW.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Jin Y, Qian H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Stekhoven DJ, Bühlmann P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Penone C, Davidson AD, Shoemaker KT, Marco MD, Rondinini C, Brooks TM, Young BE, Graham CH, Costa GC.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Chamberlain S \emph{et al.} 2018 Package {``{PVR}''}. R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}. }
@@
 \leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Diniz-Filho JAF, Bini LM, Rangel TF, Morales-Castilla I, Olalla-Tárraga MÁ, Rodríguez MÁ, Hawkins BA.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-serneels2008}{}}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Serneels S, Verdonck T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Legendre P, Legendre L. 2012 \emph{Numerical ecology}. {2nd edn}. {Elsevier, Amsterdam}. }
@@
 \leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Revell LJ.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{57. }
 \CSLRightInline{Abdi H, Williams LJ. 2010 Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459. (doi:\href{https://doi.org/10.1002/wics.101}{10.1002/wics.101})}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
-\CSLLeftMargin{57. }
+\CSLLeftMargin{58. }
 \CSLRightInline{Ballantyne G, Baldock KCR, Willmer PG.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
-\CSLLeftMargin{58. }
+\CSLLeftMargin{59. }
 \CSLRightInline{Vázquez DP, Morris WF, Jordano P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
-\CSLLeftMargin{59. }
+\CSLLeftMargin{60. }
 \CSLRightInline{Vázquez DP, Lomáscolo SB, Maldonado MB, Chacoff NP, Dorado J, Stevani EL, Vitale NL.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
-\CSLLeftMargin{60. }
+\CSLLeftMargin{61. }
 \CSLRightInline{Hung K-LJ, Kingston JM, Albrecht M, Holway DA, Kohn JR.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
-\CSLLeftMargin{61. }
+\CSLLeftMargin{62. }
 \CSLRightInline{Bürkner P-C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
-\CSLLeftMargin{62. }
+\CSLLeftMargin{63. }
 \CSLRightInline{Gabry J, Simpson D, Vehtari A, Betancourt M, Gelman A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
-\CSLLeftMargin{63. }
+\CSLLeftMargin{64. }
 \CSLRightInline{Dormann CF, Gruber B, Fründ J. 2008 Introducing the bipartite package: Analysing ecological networks. \emph{R News} \textbf{8/2}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
-\CSLLeftMargin{64. }
+\CSLLeftMargin{65. }
 \CSLRightInline{Blüthgen N, Menzel F, Blüthgen N.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
-\CSLLeftMargin{65. }
+\CSLLeftMargin{66. }
 \CSLRightInline{Healy K, Ezard THG, Jones OR, Salguero-Gómez R, Buckley YM.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-worley2000}{}}%
-\CSLLeftMargin{66. }
+\CSLLeftMargin{67. }
 \CSLRightInline{Worley AC, Baker AM, Thompson JD, Barrett SC.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-petit2006}{}}%
-\CSLLeftMargin{67. }
+\CSLLeftMargin{68. }
 \CSLRightInline{Petit RJ, Hampe A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
-\CSLLeftMargin{68. }
+\CSLLeftMargin{69. }
 \CSLRightInline{Hegland SJ, Totland Ø.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
-\CSLLeftMargin{69. }
+\CSLLeftMargin{70. }
 \CSLRightInline{Lázaro A, Jakobsson A, Totland Ø.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
-\CSLLeftMargin{70. }
+\CSLLeftMargin{71. }
 \CSLRightInline{Kaiser-Bunbury CN, Vázquez DP, Stang M, Ghazoul J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-stebbins1970}{}}%
-\CSLLeftMargin{71. }
+\CSLLeftMargin{72. }
 \CSLRightInline{Stebbins GL.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-galen1999}{}}%
-\CSLLeftMargin{72. }
+\CSLLeftMargin{73. }
 \CSLRightInline{Galen C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-faegri2013}{}}%
-\CSLLeftMargin{73. }
+\CSLLeftMargin{74. }
 \CSLRightInline{Faegri K, Van Der Pijl L. 2013 \emph{Principles of pollination ecology}. {3rd edn}. {Elsevier}. }
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rader2020}{}}%
-\CSLLeftMargin{74. }
+\CSLLeftMargin{75. }
 \CSLRightInline{Rader R, Cunningham S, Howlett B, Inouye D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
-\CSLLeftMargin{75. }
+\CSLLeftMargin{76. }
 \CSLRightInline{Földesi R, Howlett BG, Grass I, Batáry P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
-\CSLLeftMargin{76. }
+\CSLLeftMargin{77. }
 \CSLRightInline{Vázquez DP, Melián CJ, Williams NM, Blüthgen N, Krasnov BR, Poulin R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
-\CSLLeftMargin{77. }
+\CSLLeftMargin{78. }
 \CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS.

### 2022-09-26 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
updates on ms with rwcomments

@@
                 width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "(a) Breeding system")+
-  theme(plot.title = element_text(hjust=0.5, size=26, face="bold"), plot.subtitle=element_text(size=16))+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
+  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title =  "(g) Breeding system")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black") + theme(axis.text = element_text( size = rel(0.9)))
 
@@
                 width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "(b) Breeding system")+
-  theme(plot.title = element_text(hjust=0.5,size=26, face="bold"),plot.subtitle=element_text(size=16))+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
+  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title =  "(h) Breeding system")+
+  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black") + theme(axis.text = element_text( size = rel(0.9)))
 
@@
   width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(c) Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black") + theme(axis.text = element_text( size = rel(1)))
+  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +
+    labs(title = "PC2",subtitle = "(a) Compatibility system")+
+  theme(plot.title = element_text(hjust=0.5,size=26, face="bold"),plot.subtitle=element_text(size=16))+
+  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
 
@@
   width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(d) Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black") + theme(axis.text = element_text( size = rel(1)))
+  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) + 
+    labs(title = "PC2",subtitle = "(b) Compatibility system")+
+  theme(plot.title = element_text(hjust=0.5,size=26, face="bold"),plot.subtitle=element_text(size=16))+
+  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
 
@@
                 width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "(g) Life form")+
+  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "(c) Life form")+
   geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
@@
                 width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "(h) Life form")+
+  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "(d) Life form")+
   geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
@@
 #PLOT!
-
-breed_1 + breed_2+ comp_1+ comp_2+ lifespan_1+ lifespan_2+ lifeform_1+ lifeform_2+ shape_1+ shape_2+
-symmetry_1+ symmetry_2+ nectar_1+ nectar_2 + plot_layout(ncol = 2)
+comp_1 + comp_2  + lifeform_1 + lifeform_2+ lifespan_1 + lifespan_2 + breed_1 + breed_2+ shape_1 + shape_2 +
+symmetry_1 + symmetry_2 + nectar_1 + nectar_2 + plot_layout(ncol = 2)
 

### 2022-09-29 Supplementary_Material/Bees_and_other_func_grous_separated.Rmd
edits

@@
 labs(title = "", subtitle =my_y_title) +
-annotate(geom = "text", x = -1.7, y =-32 , label = "High flower N.", size = 8) +
+annotate(geom = "text", x = -1.69, y =-32 , label = "High flower N.", size = 8) +
 annotate(geom = "text", x = -1.72, y =-42 , label = "Small flowers", size = 8) + 
@@
 theme(plot.title = element_text(size = 36, face = "bold"),plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = my_y_title) +
-annotate(geom = "text", x = -1.7, y =-32 , label = "Low poll. depend.", size = 8) +
+annotate(geom = "text", x = -1.77, y =-32 , label = "High aut. selfing", size = 8) +
 annotate(geom = "text", x = -1.65, y =-42 , label = "Small floral display", size = 8) + 
-annotate(geom = "text", x = 1.75, y =-32 , label = "High poll. depend.", size = 8) + 
+annotate(geom = "text", x = 1.6, y =-32 , label = "Low aut. selfing", size = 8) + 
 annotate(geom = "text", x = 1.8, y =-42 , label = "Large floral display", size = 8) +
 xlab(NULL) +
-annotate(geom = "text", x = -0.1, y =-20 , label = "Pollinator dependence - Floral display axis", size = 8.5, fontface =2) +
+annotate(geom = "text", x = -0.1, y =-20 , label = "Autonomous selfing - Floral display axis", size = 8.5, fontface =2) +
 theme(panel.border=element_rect(color="black",size=1.2))
@@
 annotate(geom = "text", x = -1.6, y =-32 , label = "Short styles", size = 8) +
-annotate(geom = "text", x = -1.2, y =-42 , label = "High poll. depend.", size = 8) + 
+annotate(geom = "text", x = -1.35, y =-42 , label = "Low aut. selfing", size = 8) + 
 annotate(geom = "text", x = 1.95, y =-32 , label = "Long styles", size = 8) + 
-annotate(geom = "text", x = 2.3, y =-42 , label = "Low poll. depend.", size = 8) +
+annotate(geom = "text", x = 2.25, y =-42 , label = "High aut. selfing", size = 8) +
 xlab(" \n \n  ") +
-annotate(geom = "text", x = 0.25, y =-20 , label = "Style length - Pollinator dependence axis", size = 8.5, fontface =2) +
+annotate(geom = "text", x = 0.25, y =-20 , label = "Style length - Autonomous selfing axis", size = 8.5, fontface =2) +
 theme(panel.border=element_rect(color="black",size=1.2))

### 2022-09-29 Supplementary_Material/Species_Level_Metric_Pcs.Rmd
edits

--- 2022-07-04 Supplementary_Material/Species_Level_Metric_Pcs.Rmd
@@
 
-Specialization_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = d),
-  size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1") + ggtitle(NULL, subtitle = "(g)") +  xlab("High flower N.
-Low flower N.\nSmall flowers    Large flowers")
+Specialization_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + 
+geom_point(data = data_analysis_2,aes(x = -PC1, y = d),
+           size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + coord_cartesian(ylim=c(0,quantile(data_analysis_2$d, 0.95)), 
+            clip="off") + 
+           theme_ms() +
+geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, 
+            alpha=0.1,fill="black") + ylab("Specialization (d')") + 
+xlab("PC1") + 
+ggtitle(NULL, subtitle = "(g)") +  
+annotate(geom = "text", x = -1.6, y =-0.3 , 
+               label = "High flower N.", size = 8) +
+annotate(geom = "text", x = -1.65, y =-0.41 ,
+               label = "Small flowers", size = 8) + 
+annotate(geom = "text", x = 1.75, y =-0.3 , 
+               label = "Low flower N.", size = 8) + 
+annotate(geom = "text", x = 1.75, y =-0.41 ,
+               label = "Large flowers", size = 8) +
+annotate(geom = "text", x = 0.10, y =-0.19 , 
+    label = "Flower number - Flower size axis", size = 8.5, fontface =2) +
+theme(panel.border=element_rect(color="black",size=1.2)) +
+xlab(" \n \n  ")
 
@@
 
-Specialization_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = d),
-  size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab(NULL) + xlab("PC2") + ggtitle(NULL, subtitle = "(h)") + xlab("Low poll. depend.   High poll. depend.")
+Specialization_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y =
+(estimate__))) + 
+geom_point(data = data_analysis_2,aes(x = -PC2, y = d),
+           size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + coord_cartesian(ylim=c(0,quantile(data_analysis_2$d, 0.95)), 
+                clip="off") +
+theme_ms() +
+geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + 
+ylab(NULL) + 
+xlab("PC2") + 
+ggtitle(NULL, subtitle = "(h)") + 
+xlab(NULL) +
+annotate(geom = "text", x = -1.57, y =-0.3 , 
+               label = "High aut. selfing", size = 8) +
+annotate(geom = "text", x = -1.45, y =-0.41 ,
+               label = "Small floral display", size = 8) + 
+annotate(geom = "text", x = 1.75, y =-0.3 , 
+               label = "Low aut. selfing", size = 8) + 
+annotate(geom = "text", x = 1.9, y =-0.41 ,
+               label = "Large floral display", size = 8) +
+annotate(geom = "text", x = 0.10, y =-0.19 , 
+    label = "Autonomous selfing - Floral display axis", size = 8.5, fontface =2) +
+theme(panel.border=element_rect(color="black",size=1.2))
 
@@
 
-Specialization_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = d),
- size = 3.5, alpha=0.65, colour="darkorange3") + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+geom_line(colour="black",size=1.5)+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab(NULL) + xlab("PC3") + ggtitle(NULL, subtitle = "(i)")+ xlab("Short styles      Long styles\n High poll.
-depend.
-Low poll.
-depend.")
+Specialization_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y =             (estimate__))) + 
+geom_point(data = data_analysis_2,aes(x = -PC3, y = d),
+           size = 3.5, alpha=0.65, colour="darkorange3")  +
+theme_ms() + 
+geom_line(colour="black",size=1.5) +
+geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2,    
+            alpha=0.1,fill="black") +
+ylab(NULL) + 
+xlab("PC3") + 
+coord_cartesian(ylim=c(0,quantile(data_analysis_2$d, 0.95)), 
+                clip="off") +
+ggtitle(NULL, subtitle = "(i)") + 
+annotate(geom = "text", x = -1.57, y =-0.3 , 
+         label = "Short styles", size = 8) +
+annotate(geom = "text", x = -1.35, y =-0.41 ,
+         label = "Low aut. selfing", size = 8) + 
+annotate(geom = "text", x = 2.05, y =-0.3 , 
+         label = "Long styles", size = 8) + 
+annotate(geom = "text", x = 2.3, y =-0.41 ,
+         label = "High aut. selfing", size = 8) +
+annotate(geom = "text", x = 0.25, y =-0.19 , 
+         label = "Style length - Autonomous selfing axis", 
+         size = 8.5, fontface =2) +
+theme(panel.border=element_rect(color="black",size=1.2)) +
+xlab(NULL)
 

### 2022-09-29 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
edits

@@
   plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Pollinator dependence - Floral display ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
+  plot <- plot + ylab(paste("Autonomous selfing - Floral display ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
 
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig.
-S6.} Phylogenetically informed principal component analysis (pPCA) for all plant species with the first (flower number - flower size axis) and third (style length - pollinator dependence axis) principal component that explained most trait variation."}
+S6.} Phylogenetically informed principal component analysis (pPCA) for all plant species with the first (flower number - flower size axis) and third (style length - autonomous selfing) principal component that explained most trait variation."}
 setwd("~/R_Projects/Reproductive Traits")
@@
   plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Style length - Pollinator dependence axis ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
+  plot <- plot + ylab(paste("Style length - Autnomous selfing axis ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
 

### 2022-10-04 Manuscript/Lanuza_et_al_2022.Rmd
edits

@@
 
-\vspace{-1.4cm}
-
-\singlespacing
-
-\textbf{Jose B.
-Lanuza$^{1,2}$} \orcidlink{0000-0002-0287-409X}, \textbf{Romina Rader$^{1}$} \orcidlink{0000-0001-9056-9118}, \textbf{Jamie Stavert$^{3}$} \orcidlink{0000-0002-2103-5320}, \textbf{Liam K.
-Kendall$^{4}$} \orcidlink{0000-0002-0671-0121}, \textbf{Manu E.
-Saunders$^{1}$} \orcidlink{0000-0003-0645-8277} \textbf{and Ignasi Bartomeus$^{2}$} \orcidlink{0000-0001-7893-4389}
-
-\small
-
-^1^ School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-^2^ Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-^3^ Department of Conservation \| Te Papa Atawhai, Auckland, New Zealand.
-^4^ Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden.
-
 ```{=tex}
@@
 ```
-\textbf{Keywords:} life-history strategies \| plant reproductive traits \| plant-pollinator interactions
-
-\textbf{Author for correspondence:} Jose B. Lanuza \| [barragansljose\@gmail.com](mailto:barragansljose@gmail.com){.email}
 
@@
 
+\textbf{Keywords:} life-history strategies \| plant reproductive traits \| plant-pollinator interactions
+
 ```{=tex}
@@
 Flowering plants display an astonishing diversity of reproductive structures [@barrett2002; @schiestl2013] that shape their interactions with animal pollinators [@fenster2004; @dellinger2020].
-The variety of reproductive strategies used by different plant species, from specialized reliance on a single pollinator, to full self-pollination, is incredibly rich.
+The variety of reproductive strategies used by different plant species, from specialised reliance on a single pollinator, to full self-pollination, is incredibly rich.
 However, not all reproductive trait combinations in plants are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
@@
 However, studies that look at multiple traits tend to overlook plant reproductive traits [@evojtko2020; @ruger2018; @roddy2021], and focus on trait correlations in other plant organs such as morphological and physiological leaf traits [@wright2004; @shipley2006; @donovan2011; @osnas2013].
-Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs (e.g., the negative correlation between flower size and flower number [@sargent2007; @kettle2011; @vojtko2022]; the positive association between flower size and outcrossing rate [@goodwillie2010]; or the positive correlation between outcrossing rate and lifespan [@barrett2003; @munoz2016; @moeller2017]).
+Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs such as the negative correlation between flower size and flower number [@sargent2007; @kettle2011; @vojtko2022]; the positive association between flower size and outcrossing rate [@goodwillie2010]; or the positive correlation between outcrossing rate and lifespan [@barrett2003; @munoz2016; @moeller2017]).
 Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships [@roddy2021], we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
@@
 Trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] are powerful for exploring the underlying mechanisms driving plant-pollinator interactions.
-For example, plant traits can define species' network roles [e.g., specialists vs generalists @tur2013] and plant species that occupy reproductive trait space extremes are likely to be more specialized and display tighter trait-matching with pollinators [@junker2013; @coux2016].
+For example, plant traits can define species' network roles [e.g., specialists vs generalists @tur2013] and plant species that occupy reproductive trait space extremes are likely to be more specialised and display tighter trait-matching with pollinators [@junker2013; @coux2016].
 Indeed, the degree of morphological matching between plants and floral visitors often determines whether or not interactions occur, and consequently influences  the broader network structure [@stang2009; @ibanez2012].
@@
 
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (<https://www.ncbi.nlm.nih.gov/taxonomy>) for plants and ITIS (<https://www.itis.gov/>) for pollinators, using the R package *taxize* [@chamberlain2020].
+All species names, genera, families and orders were retrieved and standardised from the taxonomy data sources NCBI (<https://www.ncbi.nlm.nih.gov/taxonomy>) for plants and ITIS (<https://www.itis.gov/>) for pollinators, using the R package *taxize* [@chamberlain2020].
 We filled the 'not found' searches manually using <http://www.theplantlist.org/> and <http://www.mobot.org/> for plants and <http://www.catalogueoflife.org/> for floral visitors.
@@
 Reproductive traits consisted of those related to floral and reproductive biology: (i) floral traits included those related to the size of floral organs (e.g., style length), floral display size (e.g., flower number) and floral rewards (e.g., pollen quantity), while (ii) reproductive biology traits represented the plant reproductive system (i.e., the breeding, mating and compatibility system).
-The remaining traits were related to plant size and form (i.e., plant height, lifespan and life form), which are commonly used to characterize the fast-slow continuum of plant trait variation [@salguero2016].
+The remaining traits were related to plant size and form (i.e., plant height, lifespan and life form), which are commonly used to characterise the fast-slow continuum of plant trait variation [@salguero2016].
 For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
@@
 We explored the association between the different quantitative plant traits using a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasise flower size on the spectrum of trait variation.
+Prior to the analyses, we excluded outliers and standardised the data.
 Specifically, due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
@@
 
-We used Bayesian modeling (see details below) to investigate how the different guilds of floral visitors interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
+We used Bayesian modelling (see details below) to investigate how the different guilds of floral visitors interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
 Specifically, interactions between plants and floral visitors in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
@@
 
-We used Bayesian generalized linear mixed models in the R package *brms* [@burkner2017] to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
+We used Bayesian generalised linear mixed models in the R package *brms* [@burkner2017] to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
 Because we were interested in possible differences in visitation patterns among floral visitor guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds in the model.
@@
 
-We also used Bayesian modeling to investigate how the main axes of trait variation determined different plant species' functional roles within pollination networks.
+We also used Bayesian modelling to investigate how the main axes of trait variation determined different plant species' functional roles within pollination networks.
 For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies [@dormann2008], with clear ecological interpretations and are relevant for defining species' functional roles in networks.
-Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the *specieslevel* function in the R package *bipartite* [@dormann2008].
-We modeled each plant species metric (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
-For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree, and zero-one inflated beta for specialization).
+Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalised degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialisation (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalisation) and 1 (maximum specialisation).
+Normalised degree and specialisation were calculated with the *specieslevel* function in the R package *bipartite* [@dormann2008].
+We modelled each plant species metric (sum of visits, normalised degree and plant specialisation) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
+For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalised degree, and zero-one inflated beta for specialisation).
 Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the 'visitation patterns' section.
@@
 
-Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and specialization.
+Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalised degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialisation \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
+Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and specialisation.
 On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
-However, specialization (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
+However, specialisation (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
 On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S9c).
-Again, specialization showed the opposite trend to the number of visits (figure S9i).
+Again, specialisation showed the opposite trend to the number of visits (figure S9i).
 
@@
 This fast-slow continuum was illustrated by the associations between reproductive traits and plant height, life form and lifespan traits.
-For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred Angiosperm species in the absence of a multitrait perspective.
+For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred Angiosperm species and generally lacking a multitrait perspective.
 We found support for this trait association and show that other reproductive traits (e.g., style length or ovule number) covary along this flower number - flower size axis.
@@
 As predicted by evolutionary life-history theory [@stebbins1970], larger investment in floral display and rewards to attract pollinators occurs when pollinator dependence is high.
-However,  the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different floral visitor guilds [@galen1999].
+Indeed, the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different floral visitor guilds [@galen1999].
 For instance, smaller flowers are visited less overall, but they are inexpensive to produce (e.g., have a low ovule number) and low visitation rate at the individual flower level can be compensated by overall visitation at the plant level by producing many flowers resulting in a larger quantity of small fruits [@kettle2011].
-In addition, because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and floral visitor guilds could indicate the existence of pollination syndromes [@fenster2004; @faegri2013; @rosas2014; @dellinger2020].
+In addition, we found that a substantial number of species with high autonomous selfing had large styles and were associated with a high number of interactions with bees.
+These species seem to rely on animal pollinators as indicated by their high investment in sizable styles that can help prevent pollen competition [@ramesha2011; @ashman2013; @lanuza2021] while having reproductive assurance in their absence.
+Similarly, zygomorphic flowers are specialised floral structures that promote precise pollen transfer [sargent2004; @gong2009] but they were associated with high levels of autogamy.
+Our findings are consistent with the idea that reproductive assurance is not rare within specialised pollination systems [@fenster2007] and highlight the need to explore the timing (e.g., early versus delayed) and selfing mechanisms [see @goodwillie2018] in relation to other reproductive traits to better understand reproductive trait correlations and plant-pollinator interactions.
+
+Because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and floral visitor guilds could indicate the existence of pollination syndromes [@fenster2004; @faegri2013; @rosas2014; @dellinger2020].
 For instance, bees had a higher number of interacting partners on plant species with large flowers but interacted more frequently with species with small flowers while syrphid flies showed the opposite trend.
@@
 :::
-
-**Data accessibility.** All data and code used to conduct this study are available in the online repositories of Zenodo (<https://doi.org/10.5281/zenodo.6705621>) and Github (<https://github.com/JoseBSL/Reproductive-traits>).
-
-**Authors' contributions.** JBL, RR and IB designed the study. JBL collated the data and conducted analysis with guidance of JS, LKK and IB. JBL wrote the manuscript with contributions of all authors.
-
-**Conflict of interest declaration.** We declare we have no competing interests.
-
-**Funding.** This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2) and JBL was supported by a University of New England IPRA postgraduate scholarship.
-
-**Acknowledgements.** We thank all researchers that made their data openly available and sent it upon request.
-We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
-We thank Jason Tylianakis for his insightful comments on the manuscript before submission.
-Finally, we thank Marcos Méndez, Susan Kalisz, Amanda Benoit, May Berenbaum and an anonymous reviewer for thoughtful feedback and useful comments on earlier versions of this manuscript.

### 2022-10-04 Manuscript/Lanuza_et_al_2022.tex
edits

@@
 \setstretch{2}
-\vspace{-1.4cm}
-
-\singlespacing
-
-\textbf{Jose B.
-Lanuza$^{1,2}$} \orcidlink{0000-0002-0287-409X}, \textbf{Romina Rader$^{1}$} \orcidlink{0000-0001-9056-9118}, \textbf{Jamie Stavert$^{3}$} \orcidlink{0000-0002-2103-5320}, \textbf{Liam K.
-Kendall$^{4}$} \orcidlink{0000-0002-0671-0121}, \textbf{Manu E.
-Saunders$^{1}$} \orcidlink{0000-0003-0645-8277} \textbf{and Ignasi Bartomeus$^{2}$} \orcidlink{0000-0001-7893-4389}
-
-\small
-
-\textsuperscript{1} School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-\textsuperscript{2} Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-\textsuperscript{3} Department of Conservation \textbar{} Te Papa Atawhai, Auckland, New Zealand.
-\textsuperscript{4} Centre for Environmental and Climate Science, Lund University, Sölvegatan 37, S-223 62 Lund, Sweden.
-
 \doublespacing
 \normalsize
-
-\textbf{Keywords:} life-history strategies \textbar{} plant reproductive traits \textbar{} plant-pollinator interactions
-
-\textbf{Author for correspondence:} Jose B. Lanuza \textbar{} \href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
 
@@
 
+\textbf{Keywords:} life-history strategies \textbar{} plant reproductive traits \textbar{} plant-pollinator interactions
+
 \doublespacing
@@
 
-Flowering plants display an astonishing diversity of reproductive structures {[}\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}{]} that shape their interactions with animal pollinators {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}{]}.
-The variety of reproductive strategies used by different plant species, from specialized reliance on a single pollinator, to full self-pollination, is incredibly rich.
-However, not all reproductive trait combinations in plants are possible due to evolutionary and ecological constraints {[}\protect\hyperlink{ref-stearns1989}{5},\protect\hyperlink{ref-agrawal2020}{6}{]}.
-Despite recent advances in theoretical and empirical understanding of correlations between plant reproductive traits at large ecological scales {[}\protect\hyperlink{ref-salguero2016}{7}--\protect\hyperlink{ref-song2022}{11}{]}, studies typically focus on just a few traits, often in isolation.
-Thus, to develop a comprehensive understanding of the plant reproductive spectrum of trait variation, as done recently for root {[}\protect\hyperlink{ref-laughlin2021}{12}{]}, leaf {[}\protect\hyperlink{ref-wright2004}{13}{]} and wood {[}\protect\hyperlink{ref-chave2009}{14}{]} related traits, we require a multi-trait perspective with broad geographical coverage.
-Importantly, characterization of the plant reproductive spectrum could reveal key reproductive strategies among different species {[}\protect\hyperlink{ref-agrawal2020}{6}{]} and improve knowledge of associations between specific reproductive traits and pollinators {[}\protect\hyperlink{ref-roddy2021}{10}{]}.
-
-With the recent availability of large trait databases {[}e.g., TRY \protect\hyperlink{ref-kattge2011}{15},COMPADRE \protect\hyperlink{ref-salguero2015}{16}{]}, there has been increased research on plant ecological strategies, which has produced identification of global patterns in plant form and function {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-diaz2016}{17}--\protect\hyperlink{ref-carmona2021}{19}{]}.
-However, studies that look at multiple traits tend to overlook plant reproductive traits {[}\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-evojtko2020}{20},\protect\hyperlink{ref-ruger2018}{21}{]}, and focus on trait correlations in other plant organs such as morphological and physiological leaf traits {[}\protect\hyperlink{ref-wright2004}{13},\protect\hyperlink{ref-shipley2006}{22}--\protect\hyperlink{ref-osnas2013}{24}{]}.
-Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs (e.g., the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{25}--\protect\hyperlink{ref-vojtko2022}{27}{]}; the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{28}{]}; or the positive correlation between outcrossing rate and lifespan {[}\protect\hyperlink{ref-barrett2003}{29}--\protect\hyperlink{ref-moeller2017}{31}{]}).
-Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships {[}\protect\hyperlink{ref-roddy2021}{10}{]}, we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
-
-Trait-based approaches {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{32}{]} and trait-matching analyses {[}\protect\hyperlink{ref-stang2009}{33},\protect\hyperlink{ref-bartomeus2016}{34}{]} are powerful for exploring the underlying mechanisms driving plant-pollinator interactions.
-For example, plant traits can define species' network roles {[}e.g., specialists vs generalists \protect\hyperlink{ref-tur2013}{35}{]} and plant species that occupy reproductive trait space extremes are likely to be more specialized and display tighter trait-matching with pollinators {[}\protect\hyperlink{ref-junker2013}{36},\protect\hyperlink{ref-coux2016}{37}{]}.
-Indeed, the degree of morphological matching between plants and floral visitors often determines whether or not interactions occur, and consequently influences the broader network structure {[}\protect\hyperlink{ref-stang2009}{33},\protect\hyperlink{ref-ibanez2012}{38}{]}.
-However, it is still unclear how specific reproductive traits (e.g., mating or compatibility system) influence plant-pollinator associations {[}\protect\hyperlink{ref-tur2013}{35},\protect\hyperlink{ref-sargent2008}{39},\protect\hyperlink{ref-devaux2014}{40}{]}.
-Indeed, both morphology and mating system can determine a species' functional role within pollination networks, and the combination of several traits increases power for predicting network structure {[}\protect\hyperlink{ref-eklof2013}{41}{]}.
-Because the species position within the multidimensional trait space can result in different interaction patterns or adaptations to pollinators {[}see \protect\hyperlink{ref-dehling2016}{42} for a purely morphological approach{]}, the use of the reproductive trait space to explore plant-pollinator interactions could help to identify species functional roles and associations of traits with specific pollinators (i.e., pollination syndromes).
+Flowering plants display an astonishing diversity of reproductive structures (\protect\hyperlink{ref-barrett2002}{Barrett, 2002}; \protect\hyperlink{ref-schiestl2013}{Schiestl \& Johnson, 2013}) that shape their interactions with animal pollinators (\protect\hyperlink{ref-dellinger2020}{Dellinger, 2020}; \protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}).
+The variety of reproductive strategies used by different plant species, from specialised reliance on a single pollinator, to full self-pollination, is incredibly rich.
+However, not all reproductive trait combinations in plants are possible due to evolutionary and ecological constraints (\protect\hyperlink{ref-agrawal2020}{Agrawal, 2020}; \protect\hyperlink{ref-stearns1989}{Stearns, 1989}).
+Despite recent advances in theoretical and empirical understanding of correlations between plant reproductive traits at large ecological scales (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-paterno2020}{Paterno et al., 2020}; \protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}; \protect\hyperlink{ref-song2022}{Song et al., 2022}), studies typically focus on just a few traits, often in isolation.
+Thus, to develop a comprehensive understanding of the plant reproductive spectrum of trait variation, as done recently for root (\protect\hyperlink{ref-laughlin2021}{Laughlin et al., 2021}), leaf (\protect\hyperlink{ref-wright2004}{Wright et al., 2004}) and wood (\protect\hyperlink{ref-chave2009}{Chave et al., 2009}) related traits, we require a multi-trait perspective with broad geographical coverage.
+Importantly, characterization of the plant reproductive spectrum could reveal key reproductive strategies among different species (\protect\hyperlink{ref-agrawal2020}{Agrawal, 2020}) and improve knowledge of associations between specific reproductive traits and pollinators (\protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}).
+
+With the recent availability of large trait databases (e.g., TRY \protect\hyperlink{ref-kattge2011}{Kattge et al., 2011}; COMPADRE \protect\hyperlink{ref-salguero2015}{Salguero-Gómez et al., 2015}), there has been increased research on plant ecological strategies, which has produced identification of global patterns in plant form and function (\protect\hyperlink{ref-bruelheide2018}{Bruelheide et al., 2018}; \protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
+However, studies that look at multiple traits tend to overlook plant reproductive traits (\protect\hyperlink{ref-evojtko2020}{E-Vojtkó et al., 2020}; \protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}; \protect\hyperlink{ref-ruger2018}{Rüger et al., 2018}), and focus on trait correlations in other plant organs such as morphological and physiological leaf traits (\protect\hyperlink{ref-donovan2011}{Donovan et al., 2011}; \protect\hyperlink{ref-osnas2013}{Osnas et al., 2013}; \protect\hyperlink{ref-shipley2006}{Shipley et al., 2006}; \protect\hyperlink{ref-wright2004}{Wright et al., 2004}).
+Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs such as the negative correlation between flower size and flower number (\protect\hyperlink{ref-vojtko2022}{E-Vojtkó et al., 2022}; \protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}); the positive association between flower size and outcrossing rate (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}); or the positive correlation between outcrossing rate and lifespan (\protect\hyperlink{ref-barrett2003}{Barrett, 2003}; \protect\hyperlink{ref-moeller2017}{Moeller et al., 2017}; \protect\hyperlink{ref-munoz2016}{Munoz et al., 2016})).
+Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships (\protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}), we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
+
+Trait-based approaches (\protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero et al., 2014}) and trait-matching analyses (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}) are powerful for exploring the underlying mechanisms driving plant-pollinator interactions.
+For example, plant traits can define species' network roles (e.g., specialists vs generalists \protect\hyperlink{ref-tur2013}{Tur et al., 2013}) and plant species that occupy reproductive trait space extremes are likely to be more specialised and display tighter trait-matching with pollinators (\protect\hyperlink{ref-coux2016}{Coux et al., 2016}; \protect\hyperlink{ref-junker2013}{Junker et al., 2013}).
+Indeed, the degree of morphological matching between plants and floral visitors often determines whether or not interactions occur, and consequently influences the broader network structure (\protect\hyperlink{ref-ibanez2012}{Ibanez, 2012}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}).
+However, it is still unclear how specific reproductive traits (e.g., mating or compatibility system) influence plant-pollinator associations (\protect\hyperlink{ref-devaux2014}{Devaux et al., 2014}; \protect\hyperlink{ref-sargent2008}{Sargent \& Ackerly, 2008}; \protect\hyperlink{ref-tur2013}{Tur et al., 2013}).
+Indeed, both morphology and mating system can determine a species' functional role within pollination networks, and the combination of several traits increases power for predicting network structure (\protect\hyperlink{ref-eklof2013}{Eklöf et al., 2013}).
+Because the species position within the multidimensional trait space can result in different interaction patterns or adaptations to pollinators (see \protect\hyperlink{ref-dehling2016}{Dehling et al., 2016} for a purely morphological approach), the use of the reproductive trait space to explore plant-pollinator interactions could help to identify species functional roles and associations of traits with specific pollinators (i.e., pollination syndromes).
 
@@
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to benefit, to some degree, from animal pollination.
-Many of these networks are freely available either as published studies {[}e.g., \protect\hyperlink{ref-carvalheiro2014}{43},\protect\hyperlink{ref-olesen2007}{44},\protect\hyperlink{ref-fortuna2010}{45}{]} or in online archives {[}e.g., Mangal \protect\hyperlink{ref-poisot2016}{46},The Web of Life \protect\hyperlink{ref-fortuna2010}{45}{]}.
+Many of these networks are freely available either as published studies (e.g., \protect\hyperlink{ref-carvalheiro2014}{Carvalheiro et al., 2014}; \protect\hyperlink{ref-fortuna2010}{Fortuna et al., 2010}; \protect\hyperlink{ref-olesen2007}{Olesen et al., 2007}) or in online archives (e.g., Mangal \protect\hyperlink{ref-poisot2016}{Poisot et al., 2016}; The Web of Life \protect\hyperlink{ref-fortuna2010}{Fortuna et al., 2010}).
 In total, our network dataset constituted 60 weighted (number of visits) and four unweighted (interaction presence-absence) networks, each sampled at a unique location and year, as well as eight meta-networks where interactions were pooled across several locations and multiple years.
@@
 
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} {[}\protect\hyperlink{ref-chamberlain2020}{47}{]}.
+All species names, genera, families and orders were retrieved and standardised from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain et al., 2020}).
 We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
@@
 Reproductive traits consisted of those related to floral and reproductive biology: (i) floral traits included those related to the size of floral organs (e.g., style length), floral display size (e.g., flower number) and floral rewards (e.g., pollen quantity), while (ii) reproductive biology traits represented the plant reproductive system (i.e., the breeding, mating and compatibility system).
-The remaining traits were related to plant size and form (i.e., plant height, lifespan and life form), which are commonly used to characterize the fast-slow continuum of plant trait variation {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
+The remaining traits were related to plant size and form (i.e., plant height, lifespan and life form), which are commonly used to characterise the fast-slow continuum of plant trait variation (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
 For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
@@
 
-We calculated the phylogenetic distance between all plant species considered using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{48},\protect\hyperlink{ref-jin2019}{49}{]}.
+We calculated the phylogenetic distance between all plant species considered using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life (\protect\hyperlink{ref-jin2019}{Jin \& Qian, 2019}; \protect\hyperlink{ref-smith2018}{Smith \& Brown, 2018}).
 
@@
 
-To avoid excluding species with trait missing values, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{50}{]} which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors from principal component analysis of the phylogenetic distance (PCoA), which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{51}{]}.
-To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} {[}\protect\hyperlink{ref-santos2018}{52}{]} based on a previous conceptual framework that considers phylogenetic eigenvectors {[}\protect\hyperlink{ref-diniz-filho2012}{53}{]}.
+To avoid excluding species with trait missing values, we imputed trait missing values with the help of the function \emph{missForest} (\protect\hyperlink{ref-stekhoven2012}{Stekhoven \& Bühlmann, 2012}) which allows imputation of datasets with continuous and categorical variables.
+We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors from principal component analysis of the phylogenetic distance (PCoA), which has been shown to improve the performance of \emph{missForest} (\protect\hyperlink{ref-penone2014}{Penone et al., 2014}).
+To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} (\protect\hyperlink{ref-santos2018}{Chamberlain et al., 2018}) based on a previous conceptual framework that considers phylogenetic eigenvectors (\protect\hyperlink{ref-diniz-filho2012}{Diniz-Filho et al., 2012}).
 We conducted two different imputations, one for the full set of species (1,506 species: 5.79\% of missing values), and excluded nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01\% of missing values).
@@
 We explored the association between the different quantitative plant traits using a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
-Specifically, due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{54},\protect\hyperlink{ref-legendre2012}{55}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{55}{]}.
+We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasise flower size on the spectrum of trait variation.
+Prior to the analyses, we excluded outliers and standardised the data.
+Specifically, due to the high sensitivity of dimensionality reduction to outliers (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}; \protect\hyperlink{ref-serneels2008}{Serneels \& Verdonck, 2008}), we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
+Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}).
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{56}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode ``covariance'' because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{57}{]}.
+We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell, 2012}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode ``covariance'' because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams, 2010}).
 Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity data.
@@
 
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{56}{]} and used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
+We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell, 2012}) and used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
 However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
@@
 
-We used Bayesian modeling (see details below) to investigate how the different guilds of floral visitors interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
+We used Bayesian modelling (see details below) to investigate how the different guilds of floral visitors interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
 Specifically, interactions between plants and floral visitors in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
-Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species {[}\protect\hyperlink{ref-ballantyne2015}{58}{]}, the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination {[}\protect\hyperlink{ref-vazquez2005}{59},\protect\hyperlink{ref-vazquez2012}{60}{]}.
+Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species (\protect\hyperlink{ref-ballantyne2015}{Ballantyne et al., 2015}), the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination (\protect\hyperlink{ref-vazquez2005}{Vázquez et al., 2005}, \protect\hyperlink{ref-vazquez2012}{2012}).
 We divided floral visitors into six main taxonomical guilds that differ in life form, behaviour and thus likely play different ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
@@
 This is consistent with previous research showing that \emph{A.
-mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems {[}\protect\hyperlink{ref-hung2018}{61}{]}.
+mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems (\protect\hyperlink{ref-hung2018}{Hung et al., 2018}).
 Hence, to control for the effect of \emph{A.
@@
 
-We used Bayesian generalized linear mixed models in the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{62}{]} to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
+We used Bayesian generalised linear mixed models in the R package \emph{brms} (\protect\hyperlink{ref-burkner2017}{Bürkner, 2017}) to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
 Because we were interested in possible differences in visitation patterns among floral visitor guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds in the model.
@@
 We specified for the presence or absence of an interaction and number of visits with Bernoulli and a zero inflated negative binomial distributions, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results {[}\protect\hyperlink{ref-burkner2017}{62}{]}.
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}\protect\hyperlink{ref-gabry2019}{63}{]}.
+The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results (\protect\hyperlink{ref-burkner2017}{Bürkner, 2017}).
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package (\protect\hyperlink{ref-gabry2019}{Gabry et al., 2019}).
 
@@
 
-We also used Bayesian modeling to investigate how the main axes of trait variation determined different plant species' functional roles within pollination networks.
-For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{64}{]}, with clear ecological interpretations and are relevant for defining species' functional roles in networks.
-Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{65}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function in the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{64}{]}.
-We modeled each plant species metric (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
-For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree, and zero-one inflated beta for specialization).
+We also used Bayesian modelling to investigate how the main axes of trait variation determined different plant species' functional roles within pollination networks.
+For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies (\protect\hyperlink{ref-dormann2008}{Dormann et al., 2008}), with clear ecological interpretations and are relevant for defining species' functional roles in networks.
+Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalised degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialisation (d') (\protect\hyperlink{ref-bluthgen2006}{Blüthgen et al., 2006}), which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalisation) and 1 (maximum specialisation).
+Normalised degree and specialisation were calculated with the \emph{specieslevel} function in the R package \emph{bipartite} (\protect\hyperlink{ref-dormann2008}{Dormann et al., 2008}).
+We modelled each plant species metric (sum of visits, normalised degree and plant specialisation) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
+For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalised degree, and zero-one inflated beta for specialisation).
 Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns' section.
@@
 
-Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and specialization.
+Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalised degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialisation \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
+Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and specialisation.
 On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
-However, specialization (d') was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
+However, specialisation (d') was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
 On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S9c).
-Again, specialization showed the opposite trend to the number of visits (figure S9i).
+Again, specialisation showed the opposite trend to the number of visits (figure S9i).
 
@@
 Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50\% and 70\% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, autonomous selfing and floral display, and style length and autonomous selfing.
-Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{17},\protect\hyperlink{ref-carmona2021}{19}{]}, our results align with the two largest and most recent studies of plant life strategies that included reproductive, form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-vojtko2022}{27}{]}.
+Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}), our results align with the two largest and most recent studies of plant life strategies that included reproductive, form and size related traits (\protect\hyperlink{ref-vojtko2022}{E-Vojtkó et al., 2022}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
 The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct floral visitor guilds.
-However, the unexplained variability found highlights the need to account for other local factors, such as species relative abundances {[}\protect\hyperlink{ref-bartomeus2016}{34}{]}, along with reproductive traits, to better explain plant-pollinator associations.
+However, the unexplained variability found highlights the need to account for other local factors, such as species relative abundances (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}), along with reproductive traits, to better explain plant-pollinator associations.
 
 Our study provides strong evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1,200 species).
-Specifically, by using a multitrait approach, we are able to link the reproductive spectrum of plant trait variation with the previously described ``fast-slow continuum'' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{66}{]} life-history strategies.
+Specifically, by using a multitrait approach, we are able to link the reproductive spectrum of plant trait variation with the previously described ``fast-slow continuum'' in plant (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}) and animal (\protect\hyperlink{ref-healy2019}{Healy et al., 2019}) life-history strategies.
 This fast-slow continuum was illustrated by the associations between reproductive traits and plant height, life form and lifespan traits.
-For instance, although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{25},\protect\hyperlink{ref-kettle2011}{26},\protect\hyperlink{ref-worley2000}{67}{]}, it has only been investigated across a few hundred Angiosperm species in the absence of a multitrait perspective.
+For instance, although the negative correlation between flower number and flower size has received substantial attention (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}; \protect\hyperlink{ref-worley2000}{Worley et al., 2000}), it has only been investigated across a few hundred Angiosperm species and generally lacking a multitrait perspective.
 We found support for this trait association and show that other reproductive traits (e.g., style length or ovule number) covary along this flower number - flower size axis.
-Our study also complements previous work linking plant breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{68}{]} by showing that most species with unisexual flowers also have woody life forms and many flowers.
-Moreover, we identify the previously documented positive association between outcrossing rate and floral display size {[}\protect\hyperlink{ref-goodwillie2010}{28}{]}, where species with low autonomous selfing levels also allocate large resource quantities to attract floral visitors.
+Our study also complements previous work linking plant breeding systems and life forms (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-petit2006}{Petit \& Hampe, 2006}) by showing that most species with unisexual flowers also have woody life forms and many flowers.
+Moreover, we identify the previously documented positive association between outcrossing rate and floral display size (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}), where species with low autonomous selfing levels also allocate large resource quantities to attract floral visitors.
 Although we did not include floral rewards in our main analysis due to insufficient data, we did find that plant species with large floral displays and, in particular, large flowers, tended to have higher pollen and nectar quantity.
@@
 Overall, plant reproductive traits explained interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations across spatial large scales.
-For example, we found that all floral visitor guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings {[}\protect\hyperlink{ref-hegland2005}{69}--\protect\hyperlink{ref-kaiser2014}{71}{]}.
-As predicted by evolutionary life-history theory {[}\protect\hyperlink{ref-stebbins1970}{72}{]}, larger investment in floral display and rewards to attract pollinators occurs when pollinator dependence is high.
-However, the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different floral visitor guilds {[}\protect\hyperlink{ref-galen1999}{73}{]}.
-For instance, smaller flowers are visited less overall, but they are inexpensive to produce (e.g., have a low ovule number) and low visitation rate at the individual flower level can be compensated by overall visitation at the plant level by producing many flowers resulting in a larger quantity of small fruits {[}\protect\hyperlink{ref-kettle2011}{26}{]}.
-In addition, because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and floral visitor guilds could indicate the existence of pollination syndromes {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4},\protect\hyperlink{ref-rosas2014}{32},\protect\hyperlink{ref-faegri2013}{74}{]}.
+For example, we found that all floral visitor guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings (\protect\hyperlink{ref-hegland2005}{Hegland \& Totland, 2005}; \protect\hyperlink{ref-kaiser2014}{Kaiser-Bunbury et al., 2014}; \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}).
+As predicted by evolutionary life-history theory (\protect\hyperlink{ref-stebbins1970}{Stebbins, 1970}), larger investment in floral display and rewards to attract pollinators occurs when pollinator dependence is high.
+Indeed, the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different floral visitor guilds (\protect\hyperlink{ref-galen1999}{Galen, 1999}).
+For instance, smaller flowers are visited less overall, but they are inexpensive to produce (e.g., have a low ovule number) and low visitation rate at the individual flower level can be compensated by overall visitation at the plant level by producing many flowers resulting in a larger quantity of small fruits (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}).
+In addition, we found that a substantial number of species with high autonomous selfing had large styles and were associated with a high number of interactions with bees.
+These species seem to rely on animal pollinators as indicated by their high investment in sizable styles that can help prevent pollen competition (\protect\hyperlink{ref-ashman2013}{Ashman \& Arceo-Gómez, 2013}; \protect\hyperlink{ref-lanuza2021}{Lanuza et al., 2021}; \protect\hyperlink{ref-ramesha2011}{Ramesha et al., 2011}) while having reproductive assurance in their absence.
+Similarly, zygomorphic flowers are specialised floral structures that promote precise pollen transfer {[}sargent2004; \protect\hyperlink{ref-gong2009}{Gong \& Huang} (\protect\hyperlink{ref-gong2009}{2009}){]} but they were associated with high levels of autogamy.
+Our findings are consistent with the idea that reproductive assurance is not rare within specialised pollination systems (\protect\hyperlink{ref-fenster2007}{Fenster \& Marten-Rodriguez, 2007}) and highlight the need to explore the timing (e.g., early versus delayed) and selfing mechanisms (see \protect\hyperlink{ref-goodwillie2018}{Goodwillie \& Weber, 2018}) in relation to other reproductive traits to better understand reproductive trait correlations and plant-pollinator interactions.
+
+Because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and floral visitor guilds could indicate the existence of pollination syndromes (\protect\hyperlink{ref-dellinger2020}{Dellinger, 2020}; \protect\hyperlink{ref-faegri2013}{Faegri \& Van Der Pijl, 2013}; \protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero et al., 2014}).
 For instance, bees had a higher number of interacting partners on plant species with large flowers but interacted more frequently with species with small flowers while syrphid flies showed the opposite trend.
-This could be reflective of differences in the ecology and behaviour between these pollinator guilds {[}\protect\hyperlink{ref-rader2020}{75},\protect\hyperlink{ref-foldesi2021}{76}{]} that ultimately exert different selective pressures, leading divergent plant reproductive strategies.
-In any case, it is worth noting that local factors (e.g., species relative abundances or phenologies) likely contribute to the variability in the association between the plant reproductive spectrum and floral visitors {[}\protect\hyperlink{ref-bartomeus2016}{34},\protect\hyperlink{ref-vazquez2007}{77},\protect\hyperlink{ref-encinas2012}{78}{]}.
+This could be reflective of differences in the ecology and behaviour between these pollinator guilds (\protect\hyperlink{ref-foldesi2021}{Földesi et al., 2021}; \protect\hyperlink{ref-rader2020}{Rader et al., 2020}) that ultimately exert different selective pressures, leading divergent plant reproductive strategies.
+In any case, it is worth noting that local factors (e.g., species relative abundances or phenologies) likely contribute to the variability in the association between the plant reproductive spectrum and floral visitors (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-encinas2012}{Encinas-Viso et al., 2012}; \protect\hyperlink{ref-vazquez2007}{Vázquez et al., 2007}).
 
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
+Abdi, H., \& Williams, L. J. (2010). Principal component analysis. \emph{WIREs Comp. Stats.}, \emph{2}(4), 433--459. \url{https://doi.org/10.1002/wics.101}
+
+\leavevmode\vadjust pre{\hypertarget{ref-agrawal2020}{}}%
+Agrawal, A. A. (2020). A scale-dependent framework for trade-offs, syndromes, and specialization in organismal biology. \emph{Ecology}, \emph{101}(2), e02924. \url{https://doi.org/10.1002/ecy.2924}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ashman2013}{}}%
+Ashman, T.-L., \& Arceo-Gómez, G.
+(2013).
+Toward a predictive understanding of the fitness costs of heterospecific pollen receipt and its importance in co-flowering communities.
+\emph{American Journal of Botany}, \emph{100}(6), 1061--1070.
+\url{https://doi.org/10.3732/ajb.1200496}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
+Ballantyne, G., Baldock, K.
+C.
+R., \& Willmer, P.
+G.
+(2015).
+Constructing more informative plant\textendash pollinator networks: Visitation and pollen deposition networks in a heathland plant community.
+\emph{Proc.
+Royal Soc.
+B}, \emph{282}(1814), 20151130.
+\url{https://doi.org/10.1098/rspb.2015.1130}
+
 \leavevmode\vadjust pre{\hypertarget{ref-barrett2002}{}}%
-\CSLLeftMargin{1. }
-\CSLRightInline{Barrett SCH. 2002 The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.} \textbf{3}, 274--284. (doi:\href{https://doi.org/10.1038/nrg776}{10.1038/nrg776})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schiestl2013}{}}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Schiestl FP, Johnson SD.
-2013 Pollinator-mediated evolution of floral signals.
-\emph{Trends Ecol.
-Evol.} \textbf{28}, 307--315.
-(doi:\href{https://doi.org/10.1016/j.tree.2013.01.019}{10.1016/j.tree.2013.01.019})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fenster2004}{}}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Fenster CB, Armbruster WS, Wilson P, Dudash MR, Thomson JD.
-2004 Pollination {Syndromes} and {Floral Specialization}.
-\emph{Annu.
-Rev.
-Ecol.
-Evol.
-Syst.} \textbf{35}, 375--403.
-(doi:\href{https://doi.org/10.1146/annurev.ecolsys.34.011802.132347}{10.1146/annurev.ecolsys.34.011802.132347})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dellinger2020}{}}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Dellinger AS.
-2020 Pollination syndromes in the 21st century: Where do we stand and where may we go?
-\emph{New Phytol.} \textbf{228}, 1193--1213.
-(doi:\href{https://doi.org/10.1111/nph.16793}{10.1111/nph.16793})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stearns1989}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Stearns SC. 1989 Trade-offs in life-history evolution. \emph{Funct. Ecol.} \textbf{3}, 259--268. (doi:\href{https://doi.org/10.2307/2389364}{10.2307/2389364})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-agrawal2020}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{Agrawal AA.
-2020 A scale-dependent framework for trade-offs, syndromes, and specialization in organismal biology.
-\emph{Ecology} \textbf{101}, e02924.
-(doi:\href{https://doi.org/10.1002/ecy.2924}{10.1002/ecy.2924})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-salguero2016}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{Salguero-Gómez R, Jones OR, Jongejans E, Blomberg SP, Hodgson DJ, Mbeau-Ache C, Zuidema PA, de Kroon H, Buckley YM.
-2016 Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
-\emph{Proc.
-Natl.
-Acad.
-Sci.
-U.S.A.} \textbf{113}, 230--235.
-(doi:\href{https://doi.org/10.1073/pnas.1506215112}{10.1073/pnas.1506215112})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-friedman2020}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Friedman J.
-2020 The evolution of annual and perennial plant life histories: Ecological correlates and genetic mechanisms.
-\emph{Annu.
-Rev.
-Ecol.
-Evol.
-Syst.} \textbf{51}, 461--481.
-(doi:\href{https://doi.org/10.1146/annurev-ecolsys-110218-024638}{10.1146/annurev-ecolsys-110218-024638})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-paterno2020}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Paterno GB, Silveira CL, Kollmann J, Westoby M, Fonseca CR.
-2020 The maleness of larger angiosperm flowers.
-\emph{Proc.
-Natl.
-Acad.
-Sci.} \textbf{117}, 10921--10926.
-(doi:\href{https://doi.org/10.1073/pnas.1910631117}{10.1073/pnas.1910631117})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-roddy2021}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{Roddy AB, Martínez-Perez C, Teixido AL, Cornelissen TG, Olson ME, Oliveira RS, Silveira FAO.
-2021 Towards the flower economics spectrum.
-\emph{New Phytol.} \textbf{229}, 665--672.
-(doi:\href{https://doi.org/10.1111/nph.16823}{10.1111/nph.16823})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-song2022}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{Song B \emph{et al.} 2022 Global analysis of floral longevity reveals latitudinal gradients and biotic and abiotic correlates.
-\emph{New Phytologist} (doi:\href{https://doi.org/10.1111/nph.18271}{10.1111/nph.18271})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Laughlin DC \emph{et al.} 2021 Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
-\emph{Nat.
-Ecol.
-Evol.}, 1--12.
-(doi:\href{https://doi.org/10.1038/s41559-021-01471-7}{10.1038/s41559-021-01471-7})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Wright IJ \emph{et al.} 2004 The worldwide leaf economics spectrum. \emph{Nature} \textbf{428}, 821--827. (doi:\href{https://doi.org/10.1038/nature02403}{10.1038/nature02403})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Chave J, Coomes D, Jansen S, Lewis SL, Swenson NG, Zanne AE.
-2009 Towards a worldwide wood economics spectrum.
-\emph{Ecol.
-Lett.} \textbf{12}, 351--366.
-(doi:\href{https://doi.org/10.1111/j.1461-0248.2009.01285.x}{10.1111/j.1461-0248.2009.01285.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Kattge J \emph{et al.} 2011 {TRY} \textendash{} a global database of plant traits.
-\emph{Glob.
-Chang.
-Biol.} \textbf{17}, 2905--2935.
-(doi:\href{https://doi.org/10.1111/j.1365-2486.2011.02451.x}{10.1111/j.1365-2486.2011.02451.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Salguero-Gómez R \emph{et al.} 2015 The compadre {Plant Matrix Database}: An open online repository for plant demography.
-\emph{J.
-Ecol.} \textbf{103}, 202--218.
-(doi:\href{https://doi.org/10.1111/1365-2745.12334}{10.1111/1365-2745.12334})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{Díaz S \emph{et al.} 2016 The global spectrum of plant form and function. \emph{Nature} \textbf{529}, 167--171. (doi:\href{https://doi.org/10.1038/nature16489}{10.1038/nature16489})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Bruelheide H \emph{et al.} 2018 Global trait--environment relationships of plant communities.
-\emph{Nat.
-Ecol.
-Evol.} \textbf{2}, 1906--1917.
-(doi:\href{https://doi.org/10.1038/s41559-018-0699-8}{10.1038/s41559-018-0699-8})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Carmona CP \emph{et al.} 2021 Erosion of global functional diversity across the tree of life.
-\emph{Sci.
-Adv.} \textbf{7}, eabf2675.
-(doi:\href{https://doi.org/10.1126/sciadv.abf2675}{10.1126/sciadv.abf2675})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{E-Vojtkó A, Bello F de, Durka W, Kühn I, Götzenberger L.
-2020 The neglected importance of floral traits in trait-based plant community assembly.
-\emph{J.
-Veg.
-Sci.} \textbf{31}, 529--539.
-(doi:\href{https://doi.org/10.1111/jvs.12877}{10.1111/jvs.12877})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Rüger N, Comita LS, Condit R, Purves D, Rosenbaum B, Visser MD, Wright SJ, Wirth C.
-2018 Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
-\emph{Ecol.
-Lett.} \textbf{21}, 1075--1084.
-(doi:\href{https://doi.org/10.1111/ele.12974}{10.1111/ele.12974})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shipley2006}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{Shipley B, Lechowicz MJ, Wright I, Reich PB.
-2006 Fundamental trade-offs generating the worldwide leaf economics spectrum.
-\emph{Ecology} \textbf{87}, 535--541.
-(doi:\href{https://doi.org/10.1890/05-1051}{10.1890/05-1051})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-donovan2011}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Donovan LA, Maherali H, Caruso CM, Huber H, Kroon H de.
-2011 The evolution of the worldwide leaf economics spectrum.
-\emph{Trends in Ecology \& Evolution} \textbf{26}, 88--95.
-(doi:\href{https://doi.org/10.1016/j.tree.2010.11.011}{10.1016/j.tree.2010.11.011})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-osnas2013}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{Osnas JL, Lichstein JW, Reich PB, Pacala SW.
-2013 Global leaf trait relationships: Mass, area, and the leaf economics spectrum.
-\emph{Science} \textbf{340}, 741--744.
-(doi:\href{https://doi.org/10.1126/science.1231574}{10.1126/science.1231574})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Sargent RD, Goodwillie C, Kalisz S, Ree RH.
-2007 Phylogenetic evidence for a flower size and number trade-off.
-\emph{Am.
-J.
-Bot.} \textbf{94}, 2059--2062.
-(doi:\href{https://doi.org/10.3732/ajb.94.12.2059}{10.3732/ajb.94.12.2059})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Kettle CJ, Maycock CR, Ghazoul J, Hollingsworth PM, Khoo E, Sukri RSH, Burslem DFRP.
-2011 Ecological {Implications} of a {Flower Size}/{Number Trade}-{Off} in {Tropical Forest Trees}.
-\emph{PLoS One} \textbf{6}, e16111.
-(doi:\href{https://doi.org/10.1371/journal.pone.0016111}{10.1371/journal.pone.0016111})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vojtko2022}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{E-Vojtkó A, Junker RR, Bello F de, Götzenberger L.
-2022 Floral and reproductive traits are an independent dimension within the plant economic spectrum of temperate central europe.
-\emph{New Phytologist} (doi:\url{https://doi.org/10.1111/nph.18386})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{Goodwillie C \emph{et al.} 2010 Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
-\emph{New Phytol.} \textbf{185}, 311--321.
-(doi:\href{https://doi.org/10.1111/j.1469-8137.2009.03043.x}{10.1111/j.1469-8137.2009.03043.x})}
+Barrett, S. C. H. (2002). The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.}, \emph{3}(4), 274--284. \url{https://doi.org/10.1038/nrg776}
 
 \leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{Barrett SCH.
-2003 Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond.
+Barrett, S.
+C.
+H.
+(2003).
+Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond.
 \emph{Philos.
@@
 B Biol.
-Sci.} \textbf{358}, 991--1004.
-(doi:\href{https://doi.org/10.1098/rstb.2003.1301}{10.1098/rstb.2003.1301})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Munoz F, Violle C, Cheptou P-O.
-2016 {CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
-\emph{Oikos} \textbf{125}, 1296--1303.
-(doi:\href{https://doi.org/10.1111/oik.02328}{10.1111/oik.02328})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Moeller DA \emph{et al.} 2017 Global biogeography of mating system variation in seed plants.
+Sci.}, \emph{358}(1434), 991--1004.
+\url{https://doi.org/10.1098/rstb.2003.1301}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
+Bartomeus, I., Gravel, D., Tylianakis, J.
+M., Aizen, M.
+A., Dickie, I.
+A., \& Bernard-Verdier, M.
+(2016).
+A common framework for identifying linkage rules across different types of interactions.
+\emph{Funct.
+Ecol.}, \emph{30}(12), 1894--1903.
+\url{https://doi.org/10.1111/1365-2435.12666}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
+Blüthgen, N., Menzel, F., \& Blüthgen, N. (2006). Measuring specialization in species interaction networks. \emph{BMC Ecol.}, \emph{6}(1), 9. \url{https://doi.org/10.1186/1472-6785-6-9}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
+Bruelheide, H., Dengler, J., Purschke, O., Lenoir, J., Jiménez-Alfaro, B., Hennekens, S.
+M., Botta-Dukát, Z., Chytry, M., Field, R., Jansen, F.others.
+(2018).
+Global trait--environment relationships of plant communities.
+\emph{Nat.
+Ecol.
+Evol.}, \emph{2}(12), 1906--1917.
+\url{https://doi.org/10.1038/s41559-018-0699-8}
+
+\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
+Bürkner, P.-C. (2017). Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
+Carmona, C.
+P., Tamme, R., Pärtel, M., Bello, F.
+de, Brosse, S., Capdevila, P., González-M, R., González-Suárez, M., Salguero-Gómez, R., Vásquez-Valderrama, M., \& Toussaint, A.
+(2021).
+Erosion of global functional diversity across the tree of life.
+\emph{Sci.
+Adv.}, \emph{7}(13), eabf2675.
+\url{https://doi.org/10.1126/sciadv.abf2675}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
+Carvalheiro, L.
+G., Biesmeijer, J.
+C., Benadi, G., Fründ, J., Stang, M., Bartomeus, I., Kaiser-Bunbury, C.
+N., Baude, M., Gomes, S.
+I.
+F., Merckx, V., Baldock, K.
+C.
+R., Bennett, A.
+T.
+D., Boada, R., Bommarco, R., Cartar, R., Chacoff, N., Dänhardt, J., Dicks, L.
+V., Dormann, C.
+F., \ldots{} Kunin, W.
+E.
+(2014).
+The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
 \emph{Ecol.
-Lett.} \textbf{20}, 375--384.
-(doi:\href{https://doi.org/10.1111/ele.12738}{10.1111/ele.12738})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Rosas-Guerrero V, Aguilar R, Martén-Rodríguez S, Ashworth L, Lopezaraiza-Mikel M, Bastida JM, Quesada M.
-2014 A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
+Lett.}, \emph{17}(11), 1389--1399.
+\url{https://doi.org/10.1111/ele.12342}
+
+\leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
+Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., Bartomeus, I., Baumgartner, J., O'Donnell, J., Oksanen, J., Tzovaras, B.
+G., Marchand, P., Tran, V., Salmon, M., Li, G., \& Grenié, M.
+(2018).
+\emph{Package {`{PVR}.'} R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
+Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., Bartomeus, I., Baumgartner, J., O'Donnell, J., Oksanen, J., Tzovaras, B.
+G., Marchand, P., Tran, V., Salmon, M., Li, G., \& Grenié, M.
+(2020).
+\emph{Taxize: {Taxonomic} information from around the web.
+R package version 0.9.99.~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
+Chave, J., Coomes, D., Jansen, S., Lewis, S.
+L., Swenson, N.
+G., \& Zanne, A.
+E.
+(2009).
+Towards a worldwide wood economics spectrum.
 \emph{Ecol.
-Lett.} \textbf{17}, 388--400.
-(doi:\href{https://doi.org/10.1111/ele.12224}{10.1111/ele.12224})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{Stang M, Klinkhamer PGL, Waser NM, Stang I, van der Meijden E.
-2009 Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
-\emph{Ann.
-Bot.} \textbf{103}, 1459--1469.
-(doi:\href{https://doi.org/10.1093/aob/mcp027}{10.1093/aob/mcp027})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{Bartomeus I, Gravel D, Tylianakis JM, Aizen MA, Dickie IA, Bernard-Verdier M.
-2016 A common framework for identifying linkage rules across different types of interactions.
-\emph{Funct.
-Ecol.} \textbf{30}, 1894--1903.
-(doi:\href{https://doi.org/10.1111/1365-2435.12666}{10.1111/1365-2435.12666})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Tur C, Castro-Urgal R, Traveset A.
-2013 Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}.
-\emph{PLoS One} \textbf{8}, e78294.
-(doi:\href{https://doi.org/10.1371/journal.pone.0078294}{10.1371/journal.pone.0078294})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Junker RR, Blüthgen N, Brehm T, Binkenstein J, Paulus J, Schaefer HM, Stang M.
-2013 Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
-\emph{Funct.
-Ecol.} \textbf{27}, 329--341.
-(doi:\href{https://doi.org/10.1111/1365-2435.12005}{10.1111/1365-2435.12005})}
+Lett.}, \emph{12}(4), 351--366.
+\url{https://doi.org/10.1111/j.1461-0248.2009.01285.x}
 
 \leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Coux C, Rader R, Bartomeus I, Tylianakis JM.
-2016 Linking species functional roles to their network roles.
+Coux, C., Rader, R., Bartomeus, I., \& Tylianakis, J.
+M.
+(2016).
+Linking species functional roles to their network roles.
 \emph{Ecol.
-Lett.} \textbf{19}, 762--770.
-(doi:\href{https://doi.org/10.1111/ele.12612}{10.1111/ele.12612})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{Ibanez S.
-2012 Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks.
-\emph{Oecologia} \textbf{170}, 233--242.
-(doi:\href{https://doi.org/10.1007/s00442-012-2290-3}{10.1007/s00442-012-2290-3})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Sargent RD, Ackerly DD.
-2008 Plant--pollinator interactions and the assembly of plant communities.
-\emph{Trends Ecol.
-Evol.} \textbf{23}, 123--130.
-(doi:\href{https://doi.org/10.1016/j.tree.2007.11.003}{10.1016/j.tree.2007.11.003})}
+Lett.}, \emph{19}(7), 762--770.
+\url{https://doi.org/10.1111/ele.12612}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
+Dehling, D.
+M., Jordano, P., Schaefer, H.
+M., Böhning-Gaese, K., \& Schleuning, M.
+(2016).
+Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
+\emph{Proc.
+Royal Soc.
+B}, \emph{283}(1823), 20152444.
+\url{https://doi.org/10.1098/rspb.2015.2444}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dellinger2020}{}}%
+Dellinger, A. S. (2020). Pollination syndromes in the 21st century: Where do we stand and where may we go? \emph{New Phytol.}, \emph{228}(4), 1193--1213. \url{https://doi.org/10.1111/nph.16793}
 
 \leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
-\CSLLeftMargin{40. }
-\CSLRightInline{Devaux C, Lepers C, Porcher E.
-2014 Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems.
+Devaux, C., Lepers, C., \& Porcher, E.
+(2014).
+Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems.
 \emph{J.
 Evol.
-Biol.} \textbf{27}, 1413--1430.
-(doi:\href{https://doi.org/10.1111/jeb.12380}{10.1111/jeb.12380})}
+Biol.}, \emph{27}(7), 1413--1430.
+\url{https://doi.org/10.1111/jeb.12380}
+
+\leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
+Díaz, S., Kattge, J., Cornelissen, J.
+H.
+C., Wright, I.
+J., Lavorel, S., Dray, S., Reu, B., Kleyer, M., Wirth, C., Colin Prentice, I., Garnier, E., Bönisch, G., Westoby, M., Poorter, H., Reich, P.
+B., Moles, A.
+T., Dickie, J., Gillison, A.
+N., Zanne, A.
+E., \ldots{} Gorné, L.
+D.
+(2016).
+The global spectrum of plant form and function.
+\emph{Nature}, \emph{529}(7585), 167--171.
+\url{https://doi.org/10.1038/nature16489}
+
+\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
+Diniz-Filho, J.
+A.
+F., Bini, L.
+M., Rangel, T.
+F., Morales-Castilla, I., Olalla-Tárraga, M.
+Á., Rodríguez, M.
+Á., \& Hawkins, B.
+A.
+(2012).
+On the selection of phylogenetic eigenvectors for ecological analyses.
+\emph{Ecography}, \emph{35}(3), 239--249.
+\url{https://doi.org/10.1111/j.1600-0587.2011.06949.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-donovan2011}{}}%
+Donovan, L.
+A., Maherali, H., Caruso, C.
+M., Huber, H., \& Kroon, H.
+de.
+(2011).
+The evolution of the worldwide leaf economics spectrum.
+\emph{Trends in Ecology \& Evolution}, \emph{26}(2), 88--95.
+\url{https://doi.org/10.1016/j.tree.2010.11.011}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
+Dormann, C. F., Gruber, B., \& Fründ, J. (2008). Introducing the bipartite package: Analysing ecological networks. \emph{R News}, \emph{8/2}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Eklöf A \emph{et al.} 2013 The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583. (doi:\href{https://doi.org/10.1111/ele.12081}{10.1111/ele.12081})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
-\CSLLeftMargin{42. }
-\CSLRightInline{Dehling DM, Jordano P, Schaefer HM, Böhning-Gaese K, Schleuning M.
-2016 Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
-\emph{Proc.
-Royal Soc.
-B} \textbf{283}, 20152444.
-(doi:\href{https://doi.org/10.1098/rspb.2015.2444}{10.1098/rspb.2015.2444})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
-\CSLLeftMargin{43. }
-\CSLRightInline{Carvalheiro LG \emph{et al.} 2014 The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
+Eklöf, A., Jacob, U., Kopp, J., Bosch, J., Castro-Urgal, R., Chacoff, N.
+P., Dalsgaard, B., Sassi, C.
+de, Galetti, M., Guimaraes, P.
+R.others.
+(2013).
+The dimensionality of ecological networks.
 \emph{Ecol.
-Lett.} \textbf{17}, 1389--1399.
-(doi:\href{https://doi.org/10.1111/ele.12342}{10.1111/ele.12342})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Olesen JM, Bascompte J, Dupont YL, Jordano P.
-2007 The modularity of pollination networks.
-\emph{PNAS} \textbf{104}, 19891--19896.
-(doi:\href{https://doi.org/10.1073/pnas.0706375104}{10.1073/pnas.0706375104})}
+Lett.}, \emph{16}(5), 577--583.
+\url{https://doi.org/10.1111/ele.12081}
+
+\leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
+Encinas-Viso, F., Revilla, T.
+A., \& Etienne, R.
+S.
+(2012).
+Phenology drives mutualistic network structure and diversity.
+\emph{Ecol.
+Lett.}, \emph{15}(3), 198--208.
+\url{https://doi.org/10.1111/j.1461-0248.2011.01726.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
+E-Vojtkó, A., Bello, F.
+de, Durka, W., Kühn, I., \& Götzenberger, L.
+(2020).
+The neglected importance of floral traits in trait-based plant community assembly.
+\emph{J.
+Veg.
+Sci.}, \emph{31}(4), 529--539.
+\url{https://doi.org/10.1111/jvs.12877}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vojtko2022}{}}%
+E-Vojtkó, A., Junker, R.
+R., Bello, F.
+de, \& Götzenberger, L.
+(2022).
+Floral and reproductive traits are an independent dimension within the plant economic spectrum of temperate central europe.
+\emph{New Phytologist}.
+\url{https://doi.org/10.1111/nph.18386}
+
+\leavevmode\vadjust pre{\hypertarget{ref-faegri2013}{}}%
+Faegri, K., \& Van Der Pijl, L. (2013). \emph{Principles of pollination ecology} ({3rd edn}). {Elsevier}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fenster2004}{}}%
+Fenster, C.
+B., Armbruster, W.
+S., Wilson, P., Dudash, M.
+R., \& Thomson, J.
+D.
+(2004).
+Pollination {Syndromes} and {Floral Specialization}.
+\emph{Annu.
+Rev.
+Ecol.
+Evol.
+Syst.}, \emph{35}(1), 375--403.
+\url{https://doi.org/10.1146/annurev.ecolsys.34.011802.132347}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fenster2007}{}}%
+Fenster, C.
+B., \& Marten-Rodriguez, S.
+(2007).
+Reproductive assurance and the evolution of pollination specialization.
+\emph{International Journal of Plant Sciences}, \emph{168}(2), 215--228.
+\url{https://doi.org/10.1086/509647}
+
+\leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
+Földesi, R., Howlett, B.
+G., Grass, I., \& Batáry, P.
+(2021).
+Larger pollinators deposit more pollen on stigmas across multiple plant species---a meta-analysis.
+\emph{J.
+Appl.
+Ecol.}, \emph{58}(4), 699--707.
+\url{https://doi.org/10.1111/1365-2664.13798}
 
 \leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
-\CSLLeftMargin{45. }
-\CSLRightInline{Fortuna MA, Stouffer DB, Olesen JM, Jordano P, Mouillot D, Krasnov BR, Poulin R, Bascompte J.
-2010 Nestedness versus modularity in ecological networks: Two sides of the same coin?
+Fortuna, M.
+A., Stouffer, D.
+B., Olesen, J.
+M., Jordano, P., Mouillot, D., Krasnov, B.
+R., Poulin, R., \& Bascompte, J.
+(2010).
+Nestedness versus modularity in ecological networks: Two sides of the same coin?
 \emph{J.
 Anim.
-Ecol.} \textbf{79}, 811--817.
-(doi:\href{https://doi.org/10.1111/j.1365-2656.2010.01688.x}{10.1111/j.1365-2656.2010.01688.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
-\CSLLeftMargin{46. }
-\CSLRightInline{Poisot T \emph{et al.} 2016 Mangal \textendash{} making ecological network analysis simple.
-\emph{Ecography} \textbf{39}, 384--390.
-(doi:\href{https://doi.org/10.1111/ecog.00976}{10.1111/ecog.00976})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Chamberlain S \emph{et al.} 2020 Taxize: {Taxonomic} information from around the web.
-R package version 0.9.99.~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Smith SA, Brown JW.
-2018 Constructing a broadly inclusive seed plant phylogeny.
-\emph{Am.
-J.
-Bot.} \textbf{105}, 302--314.
-(doi:\href{https://doi.org/10.1002/ajb2.1019}{10.1002/ajb2.1019})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
-\CSLLeftMargin{49. }
-\CSLRightInline{Jin Y, Qian H.
-2019 V.{PhyloMaker}: An {R} package that can generate very large phylogenies for vascular plants.
-\emph{Ecography} \textbf{42}, 1353--1359.
-(doi:\href{https://doi.org/10.1111/ecog.04434}{10.1111/ecog.04434})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
-\CSLLeftMargin{50. }
-\CSLRightInline{Stekhoven DJ, Bühlmann P.
-2012 {MissForest}\textemdash non-parametric missing value imputation for mixed-type data.
-\emph{Bioinformatics} \textbf{28}, 112--118.
-(doi:\href{https://doi.org/10.1093/bioinformatics/btr597}{10.1093/bioinformatics/btr597})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Penone C, Davidson AD, Shoemaker KT, Marco MD, Rondinini C, Brooks TM, Young BE, Graham CH, Costa GC.
-2014 Imputation of missing data in life-history trait datasets: Which approach performs the best?
-\emph{Methods Ecol.
-Evol.} \textbf{5}, 961--970.
-(doi:\href{https://doi.org/10.1111/2041-210X.12232}{10.1111/2041-210X.12232})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Chamberlain S \emph{et al.} 2018 Package {``{PVR}''}. R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Diniz-Filho JAF, Bini LM, Rangel TF, Morales-Castilla I, Olalla-Tárraga MÁ, Rodríguez MÁ, Hawkins BA.
-2012 On the selection of phylogenetic eigenvectors for ecological analyses.
-\emph{Ecography} \textbf{35}, 239--249.
-(doi:\href{https://doi.org/10.1111/j.1600-0587.2011.06949.x}{10.1111/j.1600-0587.2011.06949.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-serneels2008}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Serneels S, Verdonck T.
-2008 Principal component analysis for data containing outliers and missing elements.
-\emph{Comput.
-Stat.
-Data Anal.} \textbf{52}, 1712--1727.
-(doi:\href{https://doi.org/10.1016/j.csda.2007.05.024}{10.1016/j.csda.2007.05.024})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Legendre P, Legendre L. 2012 \emph{Numerical ecology}. {2nd edn}. {Elsevier, Amsterdam}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Revell LJ.
-2012 Phytools: An {R} package for phylogenetic comparative biology (and other things).
-\emph{Methods Ecol.
-Evol.} \textbf{3}, 217--223.
-(doi:\href{https://doi.org/10.1111/j.2041-210X.2011.00169.x}{10.1111/j.2041-210X.2011.00169.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Abdi H, Williams LJ. 2010 Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459. (doi:\href{https://doi.org/10.1002/wics.101}{10.1002/wics.101})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
-\CSLLeftMargin{58. }
-\CSLRightInline{Ballantyne G, Baldock KCR, Willmer PG.
-2015 Constructing more informative plant\textendash pollinator networks: Visitation and pollen deposition networks in a heathland plant community.
-\emph{Proc.
-Royal Soc.
-B} \textbf{282}, 20151130.
-(doi:\href{https://doi.org/10.1098/rspb.2015.1130}{10.1098/rspb.2015.1130})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
-\CSLLeftMargin{59. }
-\CSLRightInline{Vázquez DP, Morris WF, Jordano P.
-2005 Interaction frequency as a surrogate for the total effect of animal mutualists on plants.
-\emph{Ecol.
-Lett.} \textbf{8}, 1088--1094.
-(doi:\href{https://doi.org/10.1111/j.1461-0248.2005.00810.x}{10.1111/j.1461-0248.2005.00810.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
-\CSLLeftMargin{60. }
-\CSLRightInline{Vázquez DP, Lomáscolo SB, Maldonado MB, Chacoff NP, Dorado J, Stevani EL, Vitale NL.
-2012 The strength of plant\textendash pollinator interactions.
-\emph{Ecology} \textbf{93}, 719--725.
-(doi:\href{https://doi.org/10.1890/11-1356.1}{10.1890/11-1356.1})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
-\CSLLeftMargin{61. }
-\CSLRightInline{Hung K-LJ, Kingston JM, Albrecht M, Holway DA, Kohn JR.
-2018 The worldwide importance of honey bees as pollinators in natural habitats.
-\emph{Proc.
-Royal Soc.
-B} \textbf{285}, 20172140.
-(doi:\href{https://doi.org/10.1098/rspb.2017.2140}{10.1098/rspb.2017.2140})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
-\CSLLeftMargin{62. }
-\CSLRightInline{Bürkner P-C.
-2017 Brms: {An R} package for {Bayesian} multilevel models using {Stan}.
-\emph{J.
-Stat.
-Softw.} \textbf{80}, 1--28.
-(doi:\href{https://doi.org/10.18637/jss.v080.i01}{10.18637/jss.v080.i01})}
+Ecol.}, \emph{79}(4), 811--817.
+\url{https://doi.org/10.1111/j.1365-2656.2010.01688.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-friedman2020}{}}%
+Friedman, J.
+(2020).
+The evolution of annual and perennial plant life histories: Ecological correlates and genetic mechanisms.
+\emph{Annu.
+Rev.
+Ecol.
+Evol.
+Syst.}, \emph{51}, 461--481.
+\url{https://doi.org/10.1146/annurev-ecolsys-110218-024638}
 
 \leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
-\CSLLeftMargin{63. }
-\CSLRightInline{Gabry J, Simpson D, Vehtari A, Betancourt M, Gelman A.
-2019 Visualization in {Bayesian} workflow.
+Gabry, J., Simpson, D., Vehtari, A., Betancourt, M., \& Gelman, A.
+(2019).
+Visualization in {Bayesian} workflow.
 \emph{J.
@@
 A Stat.
-Soc.} \textbf{182}, 389--402.
-(doi:\href{https://doi.org/10.1111/rssa.12378}{10.1111/rssa.12378})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
-\CSLLeftMargin{64. }
-\CSLRightInline{Dormann CF, Gruber B, Fründ J. 2008 Introducing the bipartite package: Analysing ecological networks. \emph{R News} \textbf{8/2}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
-\CSLLeftMargin{65. }
-\CSLRightInline{Blüthgen N, Menzel F, Blüthgen N.
-2006 Measuring specialization in species interaction networks.
-\emph{BMC Ecol.} \textbf{6}, 9.
-(doi:\href{https://doi.org/10.1186/1472-6785-6-9}{10.1186/1472-6785-6-9})}
+Soc.}, \emph{182}(2), 389--402.
+\url{https://doi.org/10.1111/rssa.12378}
+
+\leavevmode\vadjust pre{\hypertarget{ref-galen1999}{}}%
+Galen, C.
+(1999).
+Why do flowers vary?
+The functional ecology of variation in flower size and form within natural plant populations.
+\emph{Bioscience}, \emph{49}(8), 631--640.
+\url{https://doi.org/10.2307/1313439}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gong2009}{}}%
+Gong, Y.-B., \& Huang, S.-Q.
+(2009).
+Floral symmetry: Pollinator-mediated stabilizing selection on flower size in bilateral species.
+\emph{Proceedings of the Royal Society B: Biological Sciences}, \emph{276}(1675), 4013--4020.
+\url{https://doi.org/10.1098/rspb.2009.1254}
+
+\leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
+Goodwillie, C., Sargent, R.
+D., Eckert, C.
+G., Elle, E., Geber, M.
+A., Johnston, M.
+O., Kalisz, S., Moeller, D.
+A., Ree, R.
+H., Vallejo-Marin, M., \& Winn, A.
+A.
+(2010).
+Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
+\emph{New Phytol.}, \emph{185}(1), 311--321.
+\url{https://doi.org/10.1111/j.1469-8137.2009.03043.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-goodwillie2018}{}}%
+Goodwillie, C., \& Weber, J.
+J.
+(2018).
+The best of both worlds?
+A review of delayed selfing in flowering plants.
+\emph{American Journal of Botany}, \emph{105}(4), 641--655.
+\url{https://doi.org/10.1002/ajb2.1045}
 
 \leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
-\CSLLeftMargin{66. }
-\CSLRightInline{Healy K, Ezard THG, Jones OR, Salguero-Gómez R, Buckley YM.
-2019 Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
+Healy, K., Ezard, T.
+H.
+G., Jones, O.
+R., Salguero-Gómez, R., \& Buckley, Y.
+M.
+(2019).
+Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
 \emph{Nat.
 Ecol.
-Evol.} \textbf{3}, 1217--1224.
-(doi:\href{https://doi.org/10.1038/s41559-019-0938-7}{10.1038/s41559-019-0938-7})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-worley2000}{}}%
-\CSLLeftMargin{67. }
-\CSLRightInline{Worley AC, Baker AM, Thompson JD, Barrett SC.
-2000 Floral display in narcissus: Variation in flower size and number at the species, population, and individual levels.
-\emph{Int.
-J.
-Plant Sci.} \textbf{161}, 69--79.
-(doi:\href{https://doi.org/10.1086/314225}{10.1086/314225})}
+Evol.}, \emph{3}(8), 1217--1224.
+\url{https://doi.org/10.1038/s41559-019-0938-7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
+Hegland, S.
+J., \& Totland, Ø.
+(2005).
+Relationships between species' floral traits and pollinator visitation in a temperate grassland.
+\emph{Oecologia}, \emph{145}(4), 586--594.
+\url{https://doi.org/10.1007/s00442-005-0165-6}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
+Hung, K.-L.
+J., Kingston, J.
+M., Albrecht, M., Holway, D.
+A., \& Kohn, J.
+R.
+(2018).
+The worldwide importance of honey bees as pollinators in natural habitats.
+\emph{Proc.
+Royal Soc.
+B}, \emph{285}(1870), 20172140.
+\url{https://doi.org/10.1098/rspb.2017.2140}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
+Ibanez, S.
+(2012).
+Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks.
+\emph{Oecologia}, \emph{170}(1), 233--242.
+\url{https://doi.org/10.1007/s00442-012-2290-3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
+Jin, Y., \& Qian, H.
+(2019).
+V.{PhyloMaker}: An {R} package that can generate very large phylogenies for vascular plants.
+\emph{Ecography}, \emph{42}(8), 1353--1359.
+\url{https://doi.org/10.1111/ecog.04434}
+
+\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
+Junker, R.
+R., Blüthgen, N., Brehm, T., Binkenstein, J., Paulus, J., Schaefer, H.
+M., \& Stang, M.
+(2013).
+Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
+\emph{Funct.
+Ecol.}, \emph{27}(2), 329--341.
+\url{https://doi.org/10.1111/1365-2435.12005}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
+Kaiser-Bunbury, C.
+N., Vázquez, D.
+P., Stang, M., \& Ghazoul, J.
+(2014).
+Determinants of the microstructure of plant\textendash pollinator networks.
+\emph{Ecology}, \emph{95}(12), 3314--3324.
+\url{https://doi.org/10.1890/14-0024.1}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
+Kattge, J., Díaz, S., Lavorel, S., Prentice, I.
+C., Leadley, P., Bönisch, G., Garnier, E., Westoby, M., Reich, P.
+B., Wright, I.
+J., Cornelissen, J.
+H.
+C., Violle, C., Harrison, S.
+P., Bodegom, P.
+M.
+V., Reichstein, M., Enquist, B.
+J., Soudzilovskaia, N.
+A., Ackerly, D.
+D., Anand, M., \ldots{} Wirth, C.
+(2011).
+{TRY} \textendash{} a global database of plant traits.
+\emph{Glob.
+Chang.
+Biol.}, \emph{17}(9), 2905--2935.
+\url{https://doi.org/10.1111/j.1365-2486.2011.02451.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
+Kettle, C.
+J., Maycock, C.
+R., Ghazoul, J., Hollingsworth, P.
+M., Khoo, E., Sukri, R.
+S.
+H., \& Burslem, D.
+F.
+R.
+P.
+(2011).
+Ecological {Implications} of a {Flower Size}/{Number Trade}-{Off} in {Tropical Forest Trees}.
+\emph{PLoS One}, \emph{6}(2), e16111.
+\url{https://doi.org/10.1371/journal.pone.0016111}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lanuza2021}{}}%
+Lanuza, J.
+B., Bartomeus, I., Ashman, T.-L., Bible, G., \& Rader, R.
+(2021).
+Recipient and donor characteristics govern the hierarchical structure of heterospecific pollen competition networks.
+\emph{Journal of Ecology}, \emph{109}(6), 2329--2341.
+\url{https://doi.org/10.1111/1365-2745.13640}
+
+\leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
+Laughlin, D.
+C., Mommer, L., Sabatini, F.
+M., Bruelheide, H., Kuyper, T.
+W., McCormack, M.
+L., Bergmann, J., Freschet, G.
+T., Guerrero-Ramírez, N.
+R., Iversen, C.
+M.others.
+(2021).
+Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
+\emph{Nat.
+Ecol.
+Evol.}, 1--12.
+\url{https://doi.org/10.1038/s41559-021-01471-7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
+Lázaro, A., Jakobsson, A., \& Totland, Ø.
+(2013).
+How do pollinator visitation rate and seed set relate to species' floral traits and community context?
+\emph{Oecologia}, \emph{173}(3), 881--893.
+\url{https://doi.org/10.1007/s00442-013-2652-5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
+Legendre, P., \& Legendre, L. (2012). \emph{Numerical ecology} ({2nd edn}). {Elsevier, Amsterdam}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
+Moeller, D.
+A., Runquist, R.
+D.
+B., Moe, A.
+M., Geber, M.
+A., Goodwillie, C., Cheptou, P.-O., Eckert, C.
+G., Elle, E., Johnston, M.
+O., Kalisz, S., Ree, R.
+H., Sargent, R.
+D., Vallejo-Marin, M., \& Winn, A.
+A.
+(2017).
+Global biogeography of mating system variation in seed plants.
+\emph{Ecol.
+Lett.}, \emph{20}(3), 375--384.
+\url{https://doi.org/10.1111/ele.12738}
+
+\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
+Munoz, F., Violle, C., \& Cheptou, P.-O.
+(2016).
+{CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
+\emph{Oikos}, \emph{125}(9), 1296--1303.
+\url{https://doi.org/10.1111/oik.02328}
+
+\leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
+Olesen, J. M., Bascompte, J., Dupont, Y. L., \& Jordano, P. (2007). The modularity of pollination networks. \emph{PNAS}, \emph{104}(50), 19891--19896. \url{https://doi.org/10.1073/pnas.0706375104}
+
+\leavevmode\vadjust pre{\hypertarget{ref-osnas2013}{}}%
+Osnas, J.
+L., Lichstein, J.
+W., Reich, P.
+B., \& Pacala, S.
+W.
+(2013).
+Global leaf trait relationships: Mass, area, and the leaf economics spectrum.
+\emph{Science}, \emph{340}(6133), 741--744.
+\url{https://doi.org/10.1126/science.1231574}
+
+\leavevmode\vadjust pre{\hypertarget{ref-paterno2020}{}}%
+Paterno, G.
+B., Silveira, C.
+L., Kollmann, J., Westoby, M., \& Fonseca, C.
+R.
+(2020).
+The maleness of larger angiosperm flowers.
+\emph{Proc.
+Natl.
+Acad.
+Sci.}, \emph{117}(20), 10921--10926.
+\url{https://doi.org/10.1073/pnas.1910631117}
+
+\leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
+Penone, C., Davidson, A.
+D., Shoemaker, K.
+T., Marco, M.
+D., Rondinini, C., Brooks, T.
+M., Young, B.
+E., Graham, C.
+H., \& Costa, G.
+C.
+(2014).
+Imputation of missing data in life-history trait datasets: Which approach performs the best?
+\emph{Methods Ecol.
+Evol.}, \emph{5}(9), 961--970.
+\url{https://doi.org/10.1111/2041-210X.12232}
 
 \leavevmode\vadjust pre{\hypertarget{ref-petit2006}{}}%
-\CSLLeftMargin{68. }
-\CSLRightInline{Petit RJ, Hampe A.
-2006 Some evolutionary consequences of being a tree.
+Petit, R.
+J., \& Hampe, A.
+(2006).
+Some evolutionary consequences of being a tree.
 \emph{Annu.
@@
 Evol.
-Syst.} \textbf{37}, 187--214.
-(doi:\href{https://doi.org/10.1146/annurev.ecolsys.37.091305.110215}{10.1146/annurev.ecolsys.37.091305.110215})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
-\CSLLeftMargin{69. }
-\CSLRightInline{Hegland SJ, Totland Ø.
-2005 Relationships between species' floral traits and pollinator visitation in a temperate grassland.
-\emph{Oecologia} \textbf{145}, 586--594.
-(doi:\href{https://doi.org/10.1007/s00442-005-0165-6}{10.1007/s00442-005-0165-6})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
-\CSLLeftMargin{70. }
-\CSLRightInline{Lázaro A, Jakobsson A, Totland Ø.
-2013 How do pollinator visitation rate and seed set relate to species' floral traits and community context?
-\emph{Oecologia} \textbf{173}, 881--893.
-(doi:\href{https://doi.org/10.1007/s00442-013-2652-5}{10.1007/s00442-013-2652-5})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
-\CSLLeftMargin{71. }
-\CSLRightInline{Kaiser-Bunbury CN, Vázquez DP, Stang M, Ghazoul J.
-2014 Determinants of the microstructure of plant\textendash pollinator networks.
-\emph{Ecology} \textbf{95}, 3314--3324.
-(doi:\href{https://doi.org/10.1890/14-0024.1}{10.1890/14-0024.1})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stebbins1970}{}}%
-\CSLLeftMargin{72. }
-\CSLRightInline{Stebbins GL.
-1970 Adaptive radiation of reproductive characteristics in angiosperms, i: Pollination mechanisms.
-\emph{Annual Review of Ecology and Systematics}, 307--326.
-(doi:\href{https://doi.org/10.1146/annurev.es.01.110170.001515}{10.1146/annurev.es.01.110170.001515})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-galen1999}{}}%
-\CSLLeftMargin{73. }
-\CSLRightInline{Galen C.
-1999 Why do flowers vary?
-The functional ecology of variation in flower size and form within natural plant populations.
-\emph{Bioscience} \textbf{49}, 631--640.
-(doi:\href{https://doi.org/10.2307/1313439}{10.2307/1313439})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-faegri2013}{}}%
-\CSLLeftMargin{74. }
-\CSLRightInline{Faegri K, Van Der Pijl L. 2013 \emph{Principles of pollination ecology}. {3rd edn}. {Elsevier}. }
+Syst.}, \emph{37}, 187--214.
+\url{https://doi.org/10.1146/annurev.ecolsys.37.091305.110215}
+
+\leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
+Poisot, T., Baiser, B., Dunne, J.
+A., Kéfi, S., Massol, F., Mouquet, N., Romanuk, T.
+N., Stouffer, D.
+B., Wood, S.
+A., \& Gravel, D.
+(2016).
+Mangal \textendash{} making ecological network analysis simple.
+\emph{Ecography}, \emph{39}(4), 384--390.
+\url{https://doi.org/10.1111/ecog.00976}
 
 \leavevmode\vadjust pre{\hypertarget{ref-rader2020}{}}%
-\CSLLeftMargin{75. }
-\CSLRightInline{Rader R, Cunningham S, Howlett B, Inouye D.
-2020 Non-bee insects as visitors and pollinators of crops: Biology, ecology, and management.
+Rader, R., Cunningham, S., Howlett, B., \& Inouye, D.
+(2020).
+Non-bee insects as visitors and pollinators of crops: Biology, ecology, and management.
 \emph{Annu.
 Rev.
-Entomol.} \textbf{65}, 391--407.
-(doi:\href{https://doi.org/10.1146/annurev-ento-011019-025055}{10.1146/annurev-ento-011019-025055})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
-\CSLLeftMargin{76. }
-\CSLRightInline{Földesi R, Howlett BG, Grass I, Batáry P.
-2021 Larger pollinators deposit more pollen on stigmas across multiple plant species---a meta-analysis.
+Entomol.}, \emph{65}, 391--407.
+\url{https://doi.org/10.1146/annurev-ento-011019-025055}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ramesha2011}{}}%
+Ramesha, B., Yetish, M., Ravikanth, G., Ganeshaiah, K., Ghazoul, J., \& Shaanker, R.
+U.
+(2011).
+Stylish lengths: Mate choice in flowers.
+\emph{Journal of Biosciences}, \emph{36}(2), 229--234.
+\url{https://doi.org/10.1007/s12038-011-9057-6}
+
+\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
+Revell, L.
+J.
+(2012).
+Phytools: An {R} package for phylogenetic comparative biology (and other things).
+\emph{Methods Ecol.
+Evol.}, \emph{3}(2), 217--223.
+\url{https://doi.org/10.1111/j.2041-210X.2011.00169.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-roddy2021}{}}%
+Roddy, A.
+B., Martínez-Perez, C., Teixido, A.
+L., Cornelissen, T.
+G., Olson, M.
+E., Oliveira, R.
+S., \& Silveira, F.
+A.
+O.
+(2021).
+Towards the flower economics spectrum.
+\emph{New Phytol.}, \emph{229}(2), 665--672.
+\url{https://doi.org/10.1111/nph.16823}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
+Rosas-Guerrero, V., Aguilar, R., Martén-Rodríguez, S., Ashworth, L., Lopezaraiza-Mikel, M., Bastida, J.
+M., \& Quesada, M.
+(2014).
+A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
+\emph{Ecol.
+Lett.}, \emph{17}(3), 388--400.
+\url{https://doi.org/10.1111/ele.12224}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
+Rüger, N., Comita, L.
+S., Condit, R., Purves, D., Rosenbaum, B., Visser, M.
+D., Wright, S.
+J., \& Wirth, C.
+(2018).
+Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
+\emph{Ecol.
+Lett.}, \emph{21}(7), 1075--1084.
+\url{https://doi.org/10.1111/ele.12974}
+
+\leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
+Salguero-Gómez, R., Jones, O.
+R., Archer, C.
+R., Buckley, Y.
+M., Che-Castaldo, J., Caswell, H., Hodgson, D., Scheuerlein, A., Conde, D.
+A., Brinks, E., Buhr, H.
+de, Farack, C., Gottschalk, F., Hartmann, A., Henning, A., Hoppe, G., Römer, G., Runge, J., Ruoff, T., \ldots{} Vaupel, J.
+W.
+(2015).
+The compadre {Plant Matrix Database}: An open online repository for plant demography.
 \emph{J.
-Appl.
-Ecol.} \textbf{58}, 699--707.
-(doi:\href{https://doi.org/10.1111/1365-2664.13798}{10.1111/1365-2664.13798})}
+Ecol.}, \emph{103}(1), 202--218.
+\url{https://doi.org/10.1111/1365-2745.12334}
+
+\leavevmode\vadjust pre{\hypertarget{ref-salguero2016}{}}%
+Salguero-Gómez, R., Jones, O.
+R., Jongejans, E., Blomberg, S.
+P., Hodgson, D.
+J., Mbeau-Ache, C., Zuidema, P.
+A., de Kroon, H., \& Buckley, Y.
+M.
+(2016).
+Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
+\emph{Proc.
+Natl.
+Acad.
+Sci.
+U.S.A.}, \emph{113}(1), 230--235.
+\url{https://doi.org/10.1073/pnas.1506215112}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
+Sargent, R.
+D., \& Ackerly, D.
+D.
+(2008).
+Plant--pollinator interactions and the assembly of plant communities.
+\emph{Trends Ecol.
+Evol.}, \emph{23}(3), 123--130.
+\url{https://doi.org/10.1016/j.tree.2007.11.003}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
+Sargent, R.
+D., Goodwillie, C., Kalisz, S., \& Ree, R.
+H.
+(2007).
+Phylogenetic evidence for a flower size and number trade-off.
+\emph{Am.
+J.
+Bot.}, \emph{94}(12), 2059--2062.
+\url{https://doi.org/10.3732/ajb.94.12.2059}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schiestl2013}{}}%
+Schiestl, F. P., \& Johnson, S. D. (2013). Pollinator-mediated evolution of floral signals. \emph{Trends Ecol. Evol.}, \emph{28}(5), 307--315. \url{https://doi.org/10.1016/j.tree.2013.01.019}
+
+\leavevmode\vadjust pre{\hypertarget{ref-serneels2008}{}}%
+Serneels, S., \& Verdonck, T.
+(2008).
+Principal component analysis for data containing outliers and missing elements.
+\emph{Comput.
+Stat.
+Data Anal.}, \emph{52}(3), 1712--1727.
+\url{https://doi.org/10.1016/j.csda.2007.05.024}
+
+\leavevmode\vadjust pre{\hypertarget{ref-shipley2006}{}}%
+Shipley, B., Lechowicz, M.
+J., Wright, I., \& Reich, P.
+B.
+(2006).
+Fundamental trade-offs generating the worldwide leaf economics spectrum.
+\emph{Ecology}, \emph{87}(3), 535--541.
+\url{https://doi.org/10.1890/05-1051}
+
+\leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
+Smith, S. A., \& Brown, J. W. (2018). Constructing a broadly inclusive seed plant phylogeny. \emph{Am. J. Bot.}, \emph{105}(3), 302--314. \url{https://doi.org/10.1002/ajb2.1019}
+
+\leavevmode\vadjust pre{\hypertarget{ref-song2022}{}}%
+Song, B., Sun, L., Barrett, S.
+C., Moles, A.
+T., Luo, Y.-H., Armbruster, W.
+S., Gao, Y.-Q., Zhang, S., Zhang, Z.-Q., \& Sun, H.
+(2022).
+Global analysis of floral longevity reveals latitudinal gradients and biotic and abiotic correlates.
+\emph{New Phytologist}.
+\url{https://doi.org/10.1111/nph.18271}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
+Stang, M., Klinkhamer, P.
+G.
+L., Waser, N.
+M., Stang, I., \& van der Meijden, E.
+(2009).
+Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
+\emph{Ann.
+Bot.}, \emph{103}(9), 1459--1469.
+\url{https://doi.org/10.1093/aob/mcp027}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stearns1989}{}}%
+Stearns, S. C. (1989). Trade-offs in life-history evolution. \emph{Funct. Ecol.}, \emph{3}(3), 259--268. \url{https://doi.org/10.2307/2389364}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stebbins1970}{}}%
+Stebbins, G.
+L.
+(1970).
+Adaptive radiation of reproductive characteristics in angiosperms, i: Pollination mechanisms.
+\emph{Annual Review of Ecology and Systematics}, 307--326.
+\url{https://doi.org/10.1146/annurev.es.01.110170.001515}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
+Stekhoven, D.
+J., \& Bühlmann, P.
+(2012).
+{MissForest}\textemdash non-parametric missing value imputation for mixed-type data.
+\emph{Bioinformatics}, \emph{28}(1), 112--118.
+\url{https://doi.org/10.1093/bioinformatics/btr597}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
+Tur, C., Castro-Urgal, R., \& Traveset, A.
+(2013).
+Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}.
+\emph{PLoS One}, \emph{8}(10), e78294.
+\url{https://doi.org/10.1371/journal.pone.0078294}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
+Vázquez, D.
+P., Lomáscolo, S.
+B., Maldonado, M.
+B., Chacoff, N.
+P., Dorado, J., Stevani, E.
+L., \& Vitale, N.
+L.
+(2012).
+The strength of plant\textendash pollinator interactions.
+\emph{Ecology}, \emph{93}(4), 719--725.
+\url{https://doi.org/10.1890/11-1356.1}
 
 \leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
-\CSLLeftMargin{77. }
-\CSLRightInline{Vázquez DP, Melián CJ, Williams NM, Blüthgen N, Krasnov BR, Poulin R.
-2007 Species abundance and asymmetric interaction strength in ecological networks.
-\emph{Oikos} \textbf{116}, 1120--1127.
-(doi:\href{https://doi.org/10.1111/j.0030-1299.2007.15828.x}{10.1111/j.0030-1299.2007.15828.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
-\CSLLeftMargin{78. }
-\CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS.
-2012 Phenology drives mutualistic network structure and diversity.
+Vázquez, D.
+P., Melián, C.
+J., Williams, N.
+M., Blüthgen, N., Krasnov, B.
+R., \& Poulin, R.
+(2007).
+Species abundance and asymmetric interaction strength in ecological networks.
+\emph{Oikos}, \emph{116}(7), 1120--1127.
+\url{https://doi.org/10.1111/j.0030-1299.2007.15828.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
+Vázquez, D.
+P., Morris, W.
+F., \& Jordano, P.
+(2005).
+Interaction frequency as a surrogate for the total effect of animal mutualists on plants.
 \emph{Ecol.
-Lett.} \textbf{15}, 198--208.
-(doi:\href{https://doi.org/10.1111/j.1461-0248.2011.01726.x}{10.1111/j.1461-0248.2011.01726.x})}
+Lett.}, \emph{8}(10), 1088--1094.
+\url{https://doi.org/10.1111/j.1461-0248.2005.00810.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-worley2000}{}}%
+Worley, A.
+C., Baker, A.
+M., Thompson, J.
+D., \& Barrett, S.
+C.
+(2000).
+Floral display in narcissus: Variation in flower size and number at the species, population, and individual levels.
+\emph{Int.
+J.
+Plant Sci.}, \emph{161}(1), 69--79.
+\url{https://doi.org/10.1086/314225}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%
+Wright, I.
+J., Reich, P.
+B., Westoby, M., Ackerly, D.
+D., Baruch, Z., Bongers, F., Cavender-Bares, J., Chapin, T., Cornelissen, J.
+H.
+C., Diemer, M., Flexas, J., Garnier, E., Groom, P.
+K., Gulias, J., Hikosaka, K., Lamont, B.
+B., Lee, T., Lee, W., Lusk, C., \ldots{} Villar, R.
+(2004).
+The worldwide leaf economics spectrum.
+\emph{Nature}, \emph{428}(6985), 821--827.
+\url{https://doi.org/10.1038/nature02403}
 
@@
 
-\textbf{Data accessibility.} All data and code used to conduct this study are available in the online repositories of Zenodo (\url{https://doi.org/10.5281/zenodo.6705621}) and Github (\url{https://github.com/JoseBSL/Reproductive-traits}).
-
-\textbf{Authors' contributions.} JBL, RR and IB designed the study.
-JBL collated the data and conducted analysis with guidance of JS, LKK and IB.
-JBL wrote the manuscript with contributions of all authors.
-
-\textbf{Conflict of interest declaration.} We declare we have no competing interests.
-
-\textbf{Funding.} This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2) and JBL was supported by a University of New England IPRA postgraduate scholarship.
-
-\textbf{Acknowledgements.} We thank all researchers that made their data openly available and sent it upon request.
-We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
-We thank Jason Tylianakis for his insightful comments on the manuscript before submission.
-Finally, we thank Marcos Méndez, Susan Kalisz, Amanda Benoit, May Berenbaum and an anonymous reviewer for thoughtful feedback and useful comments on earlier versions of this manuscript.
-
 \end{document}

### 2022-10-04 Manuscript/Title_Page.Rmd
edits

--- 2022-07-19 Manuscript/Lanuza_et_al_2022.Rmd
@@
 
-```{=tex}
-\doublespacing
-\normalsize
-```
-\textbf{Keywords:} life-history strategies \| plant reproductive traits \| plant-pollinator interactions
-
 \textbf{Author for correspondence:} Jose B. Lanuza \| [barragansljose\@gmail.com](mailto:barragansljose@gmail.com){.email}
-
-# Abstract
-
-Globally, plants display enormous variation in life history strategies and trait combinations.
-However, evidence suggests that evolutionary and physiological constraints limit the number of plant ecological strategies.
-Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with floral visitors.
-Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with floral visitors.
-We show that over 50% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the positive correlation between pollinator dependence and floral display size.
-In empirical plant-pollinator networks, the plant position within these axes was associated with the number of interacting partners and the visitation rates of the distinct floral visitor guilds, but the unexplained variability found highlights the need to incorporate other factors along with reproductive traits to fully explain plant-pollinator interactions.
-Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping networks of plant-pollinator interactions at a global scale.
-
-```{=tex}
-\doublespacing
-\vspace{5mm}
-\normalsize
-```
-```{r setup, include=FALSE, cache=FALSE, message = FALSE}
-
-library("knitr")
-
-### Chunk options: see http://yihui.name/knitr/options/ ###
-## Text results
-opts_chunk$set(echo = FALSE, warning = TRUE, message = TRUE)
-
-## Code decoration
-opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)
-
-## Cache
-# opts_chunk$set(cache = 2, cache.path = "output/cache/")
-
-## Plots
-opts_chunk$set(fig.path = "output/figures/")
-
-```
-
-```{r knitcitations, cache = FALSE}
-library(knitcitations)
-cleanbib()   
-cite_options(citation_format = "pandoc")
-
-```
-
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.pos = 'H')
-```
-
-# 1. Introduction
-
-Flowering plants display an astonishing diversity of reproductive structures [@barrett2002; @schiestl2013] that shape their interactions with animal pollinators [@fenster2004; @dellinger2020].
-The variety of reproductive strategies used by different plant species, from specialized reliance on a single pollinator, to full self-pollination, is incredibly rich.
-However, not all reproductive trait combinations in plants are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
-Despite recent advances in theoretical and empirical understanding of correlations between plant reproductive traits at large ecological scales [@salguero2016; @friedman2020; @paterno2020; @roddy2021; @song2022], studies typically focus on just a few traits, often in isolation.
-Thus, to develop a comprehensive understanding of the plant reproductive spectrum of trait variation, as done recently for root [@laughlin2021], leaf [@wright2004] and wood [@chave2009] related traits, we require a multi-trait perspective with broad geographical coverage.
-Importantly, characterization of the plant reproductive spectrum could reveal key reproductive strategies among different species [@agrawal2020] and improve knowledge of associations between specific reproductive traits and pollinators [@roddy2021].
-
-With the recent availability of large trait databases [e.g., TRY @kattge2011;  COMPADRE @salguero2015], there has been increased research on plant ecological strategies, which has produced identification of global patterns in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
-However, studies that look at multiple traits tend to overlook plant reproductive traits [@evojtko2020; @ruger2018; @roddy2021], and focus on trait correlations in other plant organs such as morphological and physiological leaf traits [@wright2004; @shipley2006; @donovan2011; @osnas2013].
-Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs (e.g., the negative correlation between flower size and flower number [@sargent2007; @kettle2011]; the positive association between flower size and outcrossing rate [@goodwillie2010]; or the positive correlation between outcrossing rate and lifespan [@barrett2003; @munoz2016; @moeller2017]).
-Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships [@roddy2021], we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
-
-Trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] are powerful for exploring the underlying mechanisms driving plant-pollinator interactions.
-For example, plant traits can define species' network roles [e.g., specialists vs generalists @tur2013] and plant species that occupy reproductive trait space extremes are likely to be more specialized and display tighter trait-matching with pollinators [@junker2013; @coux2016].
-Indeed, the degree of morphological matching between plants and floral visitors often determines whether or not interactions occur, and consequently influences  the broader network structure [@stang2009; @ibanez2012].
-However, it is still unclear how specific reproductive traits (e.g., mating or compatibility system) influence plant-pollinator associations [@sargent2008; @tur2013; @devaux2014].
-Indeed, both morphology and mating system can determine a species' functional role within pollination networks, and the combination of several traits increases power for predicting network structure [@eklof2013].
-Because the species position within the multidimensional trait space can result in different interaction patterns or adaptations to pollinators [see @dehling2016 for a purely morphological approach], the use of the reproductive trait space to explore plant-pollinator interactions could help to identify species functional roles and associations of traits with specific pollinators (i.e., pollination syndromes).
-
-Here, we explore the spectrum of reproductive traits in flowering plants, within a global set of plant-pollinator networks, to identify reproductive trait covariation and how this influences the network of interactions between plants and floral visitors.
-First, we identify the major axes of reproductive trait variation and correlations among traits for plant species.
-Then, we investigate the associations between plant species’ positions in reproductive trait space and the strength of their interactions with different floral visitor guilds within networks.
-Finally, we determine how the main axes of reproductive trait variation influence plant species' functional roles within pollination networks, using a range of complementary interaction network metrics.
-
-# 2. Methods
-
-## (a) Plant-pollinator network studies
-
-We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see table S1 and figure S1).
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different ecological communities.
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to benefit, to some degree, from animal pollination.
-Many of these networks are freely available either as published studies [e.g., @carvalheiro2014; @olesen2007; @fortuna2010] or in online archives [e.g., Mangal @poisot2016;  The Web of Life @fortuna2010].
-In total, our network dataset constituted 60 weighted (number of visits) and four unweighted (interaction presence-absence) networks, each sampled at a unique location and year, as well as eight meta-networks where interactions were pooled across several locations and multiple years.
-
-## (b) Taxonomy of plants and pollinators
-
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (<https://www.ncbi.nlm.nih.gov/taxonomy>) for plants and ITIS (<https://www.itis.gov/>) for pollinators, using the R package *taxize* [@chamberlain2020].
-We filled the 'not found' searches manually using <http://www.theplantlist.org/> and <http://www.mobot.org/> for plants and <http://www.catalogueoflife.org/> for floral visitors.
-
-## (c) Plant traits
-
-We selected a total of 19 quantitative and categorical functional traits that included reproductive traits and traits related with plant form and size (see table 1).
-Reproductive traits consisted of those related to floral and reproductive biology: (i) floral traits included those related to the size of floral organs (e.g., style length), floral display size (e.g., flower number) and floral rewards (e.g., pollen quantity), while (ii) reproductive biology traits represented the plant reproductive system (i.e., the breeding, mating and compatibility system).
-The remaining traits were related to plant size and form (i.e., plant height, lifespan and life form), which are commonly used to characterize the fast-slow continuum of plant trait variation [@salguero2016].
-For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
-From a matrix comprising a total of 28,614 possible cells (considering all traits and plant species: 19 columns × 1,506 species), we were able to fill 23,354 cells (81.6% of the dataset, see figure S2 for missing value information for each trait).
-An extended description of each trait and how it was obtained can be found in Appendix S1.
-
-\singlespacing
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=1, fig.width=14}
-setwd("~/R_Projects/Reproductive Traits")
-
-library(kableExtra)
-
-library(dplyr)
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant","Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Floral_unit_width",
-         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
-         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-n_of_records <- subset(missing.values, isna=="FALSE")
-
-Trait <- c("Plant height", "Flower width", "Flower length", "Inflorescence width", "Style length", "Ovules per flower",
-           "Flowers per plant", "Microliters of nectar", "Milligrams of nectar", "Nectar concentration", "Pollen grains per flower", "Autonomous selfing (fruit set)")
-
-Trait1 <- linebreak(c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Compatibility system", "Breeding system"),align = c("l"))
-
-#T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub #\n Tree", "Brush \n Campanulate \n Capitulum \n Open \n #Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-#           "Presence \n Absence", "Self-incomp. \n Part. #self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n #Dioecious"),align = c("l"))
-#
-T.cat <- linebreak(c("Short-lived and perennial", "Herb, shrub and tree", "Brush, campanulate, capitulum,\n open, papilionaceous and tube",  "Actinomorphic and zygomorphic",
-           "Presence and absence", "Self-incompatible, partially self-compabtile \n and self-compatible", "Hermaphrodite, monoecious and dioecious"), align = c("l"))
-
-Number_of_records_quantitative <- c(n_of_records$num.isna[n_of_records$key=="Plant_height_mean_m"], n_of_records$num.isna[n_of_records$key=="Corolla_diameter_mean"],
-  n_of_records$num.isna[n_of_records$key=="Corolla_length_mean"], n_of_records$num.isna[n_of_records$key=="Floral_unit_width"],
-  n_of_records$num.isna[n_of_records$key=="Style_length"], n_of_records$num.isna[n_of_records$key=="Ovule_number"],
-  n_of_records$num.isna[n_of_records$key=="Flowers_per_plant"], n_of_records$num.isna[n_of_records$key=="Nectar_ul"],
-  n_of_records$num.isna[n_of_records$key=="Nectar_mg"], n_of_records$num.isna[n_of_records$key=="Nectar_concentration"], n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
-  n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level_fruit_set"])
-
-Number_of_records_categorical <- c(n_of_records$num.isna[n_of_records$key=="lifespan"], n_of_records$num.isna[n_of_records$key=="life_form"],
-                                   n_of_records$num.isna[n_of_records$key=="Flower_morphology"], n_of_records$num.isna[n_of_records$key=="Flower_symmetry"],
-                                   n_of_records$num.isna[n_of_records$key=="Nectar_presence_absence"], n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level"],
-                                   n_of_records$num.isna[n_of_records$key=="Compatibility_system"], n_of_records$num.isna[n_of_records$key=="Breeding_system"],
-                                   rep("",4))
-
-T.range <- c("0.01-30m", "0.50-205mm", "0.20-195mm", "0.80-300mm", "0-138mm", "1-25000", "1-1.8 x $10^5$", "0-160$\\mu$l", "0-6.1mg", "0-100$\\%$", "13-2 x $10^8$", "0-100$\\%$")
-
-dat_1 <- data.frame(Trait,T.range)
-dat_2 <- data.frame(Trait1, T.cat)
-
-colnames(dat_1) <- c("Quantitative traits", "Numerical range")
-colnames(dat_2) <- c("Categorical traits", "Categories")
-
-#kable(list(dat_1, dat_2), booktabs = T, linesep = #"\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1 | #Quantitative and categorical traits used in this study.}") %>%
-#  kable_styling(full_width = F,font_size = 10) %>%  #column_spec(1:4, 
-#              width = "3in", 
-#              latex_valign = "m")
-#
-#
-
-colnames(dat_1) <- c("Traits", "Numerical range/Categories")
-colnames(dat_2) <- c("Traits", "Numerical range/Categories")
-
-d <- rbind(dat_1,dat_2)
-
-kable(d, booktabs = T, linesep = "\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1.} Quantitative and categorical traits used in this study.") %>%
-  kable_styling(full_width = F,font_size = 12) %>% row_spec(0, bold=T) %>% pack_rows("Quantitative", 1, 12) %>%
-pack_rows("Categorical", 13, 19)
-
-```
-
-\doublespacing
-
-## (d) Phylogenetic Distance
-
-We calculated the phylogenetic distance between all plant species considered using the function *get_tree* from the package *rtrees* (<https://github.com/daijiang/rtrees>), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
-
-## (e) Data Imputation
-
-To avoid excluding species with trait missing values, we imputed trait missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors from principal component analysis of the phylogenetic distance (PCoA), which has been shown to improve the performance of *missForest* [@penone2014].
-To extract the eigenvectors, we used the function *PVRdecomp* from the package *PVR* [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-We conducted two different imputations, one for the full set of species (1,506 species: 5.79% of missing values), and excluded nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and results for the two datasets were consitent (Fig S3 and Fig S4).
-
-## (f) Plant strategies
-
-We explored the association between the different quantitative plant traits using a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
-Specifically, due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis [@legendre2012].
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
-We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode “covariance” because values for each variables were on the same scale following transformation [@abdi2010].
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity data.
-For this, we included all quantitative traits included in the main pPCA, plus pollen grains and microlitres of nectar per flower.
-
-## (g) Phylogenetic signal
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package *phytools* [@revell2012] and used Pagel's $\lambda$ as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-## (h) Network analyses
-
-### (i) Visitation patterns
-
-We used Bayesian modeling (see details below) to investigate how the different guilds of floral visitors interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
-Specifically, interactions between plants and floral visitors in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
-Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species [@ballantyne2015], the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination [@vazquez2005; @vazquez2012].
-We divided floral visitors into six main taxonomical guilds that differ in life form, behaviour and thus likely play similar ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
-Moreover, because bees had the greatest number of occurrences in networks  (2,256 records) and the highest frequency of visits, we further broke this group down into the main bee families (Andrenidae, Apidae, Colletidae, Halictidae, and Megachilidae).
-In addition, we found that *Apis mellifera* was the floral visitor with the largest proportion of occurrences in networks (7.55% of the total).
-This is consistent with previous research showing that *A.
-mellifera* was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
-Hence, to control for the effect of *A.
-mellifera* on observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding *A.
-mellifera*.
-We found that *A.
-mellifera*, was partly driving some of the observed trends on PC1 (figure S5).
-However, we did not detect major differences on PC2 and PC3.
-
-We used Bayesian generalized linear mixed models in the R package *brms* [@burkner2017] to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in visitation patterns among floral visitor guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds in the model.
-We added a nested random effect of networks within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence among them.
-We specified for the presence or absence of an interaction and number of visits with Bernoulli and a zero inflated negative binomial distributions, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results [@burkner2017].
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the *bayesplot* package [@gabry2019].
-
-### (ii) Plant species network roles
-
-We also used Bayesian modeling to investigate how the main axes of trait variation determined different plant species' functional roles within pollination networks.
-For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies [@dormann2008], with clear ecological interpretations and are relevant for defining species' functional roles in networks.
-Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the *specieslevel* function in the R package *bipartite* [@dormann2008].
-We modeled each plant species metric (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
-For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree, and zero-one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the 'visitation patterns' section.
-
-Our analyses were conducted on the subset of 60 weighted networks (out of a total of 64 networks) sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our network dataset (excluding meta- and non-weighted networks) included 2,256 interactions for bees, 1,768 for non-syrphid-dipterans, 845 for syrphids, 437 for lepidopterans, 432 for coleopterans, and 362 for non-bee-hymenopterans.
-Sampling methods varied across studies but this was accounted for in analyses by including study identity as a  random effect in our models.
-All analyses were conducted in R version *4.0.3*.
-
-# 3. Results
-
-## (a) Plant strategies
-
-Our phylogenetically informed principal component analysis captured  51.8% and 70.97% of the reproductive trait variation in the first two and three axes, respectively (figure 1 and figure S6).
-The first principal component (PC1; the flower number - flower size axis) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; table S3) but style length also contributed moderately (loading = -0.33).
-One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-For instance, *Cornus florida* occurred at this end of the spectrum, which, on average, has approximately 10,000 flowers, is 7.5 m high, has flowers that are 3 mm wide, styles 3.5 mm long and  two ovules per flower.
-The other end of this spectrum had species that were short in height, with few large flowers that had long styles and many ovules.
-For example, *Petunia axillaris* on average, is 0.5 m high and has approximately 10 flowers per plant that are over 50 mm wide with 25 mm long styles and over 200 ovules.
-The second principal component (PC2; the pollinator dependence axis) encompassed 25.05% of the trait variation and represented variation from low to high autonomous selfing (i.e., high to low pollinator dependence).
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but all other traits (except ovule number) made moderate contributions (loadings ranging between 0.27 to 0.4; table S3).
-Generally speaking, species with high pollinator dependence had larger and many flowers with long styles, and were tall.
-*Zuccagnia punctata* occurred at this extreme of the spectrum, which is a self-incompatible species, completely dependent on animal pollination for seed production, producing  approximately 1,500 flowers per plant with an average height of 3 m and 20 mm long styles.
-In contrast, species with low pollinator dependence tended to have fewer and smaller flowers with shorter styles, and were shorter in height.
-*Veronica peregrina* occurred at this end of the spectrum, and is a self-compatible plant that requires little or no pollination by animals, it has approximately 20 flowers per plant, is 0.2 m high and has 0.25 mm long styles.
-The third principal component (PC3; the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \|-0.51\|), where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
-The remaining traits, apart from ovule number, were all positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; table S3).
-In addition, the pPCA with the subset of species that we had nectar and pollen quantity data for showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with floral display size.
-Floral rewards were particularly strongly correlated with flower size but weakly correlated with flower number (figure S4).
-The first two principal components for this pPCA explained similar variance  (45.52%) and similar associations of traits, despite some variability in the loadings (table S4).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="85%", fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
-The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
-The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation.
-The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}
-
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-library(viridis) #COLOUR GGPLOT
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(magick)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#Images were made by Paula Martin
-#Check her work on https://paulamartinart.com/
-
-tree <- image_read("Images/PPCA_Plot/Tree.png")
-tree_1 <- as.raster(tree)
-
-style_l <- image_read("Images/PPCA_Plot/Style_Long.png")
-style_l_1 <- as.raster(style_l)
-
-style_s <- image_read("Images/PPCA_Plot/Style_Short.png")
-style_s_1 <- as.raster(style_s)
-
-ovule_h <- image_read("Images/PPCA_Plot/Ovule_High.png")
-ovule_h_1 <- as.raster(ovule_h)
-
-ovule_l <- image_read("Images/PPCA_Plot/Ovule_Low.png")
-ovule_l_1 <- as.raster(ovule_l)
-
-selfing_n <- image_read("Images/PPCA_Plot/Selfing_None.png")
-selfing_n_1 <- as.raster(selfing_n)
-
-selfing_h <- image_read("Images/PPCA_Plot/selfing.png")
-selfing_h_1 <- as.raster(selfing_h)
-
-single_flower <- image_read("Images/PPCA_Plot/Single_Flower.png")
-single_flower_1 <- as.raster(single_flower)
-
-many_flowers <- image_read("Images/PPCA_Plot/Inflorescencia.png")
-many_flowers_1 <- as.raster(many_flowers)
-#many_flowers_1 <- image_rotate(many_flowers, 45)
-
-large_flower <- image_read("Images/PPCA_Plot/flower_big.png")
-large_flower_1 <- as.raster(large_flower)
-
-#"Images/PPCA_Plot/flower_short.png"
-flower_small <- image_read("Images/PPCA_Plot/flower_big.png")
-flower_small_1 <- as.raster(flower_small)
-
-herb <- image_read("Images/PPCA_Plot/herb.png")
-herb_1 <- as.raster(herb)
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Pollinator dependence - Floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
-    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
-    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
-    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.18, xmax = 4.13,ymin = 1.3, ymax = 2.4) +
-    annotation_raster(flower_small_1, xmin = -3.21, xmax = -2.81,ymin = -2, ymax = -1.45) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
-
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
-                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-plot_grid(all_spp(PC))
-
-```
-
-We found that most categorical traits were statistically associated with the first two axes of trait variation (figure 2 and table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed a lack of statistical association.
-In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S7).
-Regarding self-compatibility, we found larger differences on PC2.
-For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S7a and figure S7b; Tukey test *P* \< 0.05).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S7c and figure S7d; Tukey test *P* \< 0.05).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f; Tukey test *P* \< 0.05).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the highest pollinator dependence and highest number of flowers (figure S7g and figure S7h; Tukey test *P* \< 0.05).
-Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and high pollinator dependence, while the latter had more flowers and lower pollinator dependence (figure S7i and figure S7j; Tukey test *P* \< 0.05).
-Finally, in terms of flower symmetry, zygomorphic flowers were associated with lower pollinator dependence, whereas actinomorphic flowers were more dependent on pollinators (figure S7k and figure S7l; Tukey test *P* \< 0.05).
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="80%",fig.align='center',fig.cap= "\\textbf{Figure 2.} Location of the different qualitative traits in the trait space.
-The figure panel is composed of the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
-The solid arrows indicate the direction of variation of the different quantitative traits shown in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S)."}
-
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.6)),
-            axis.text=element_text(size = rel(1.6), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(size = rel(1.1)),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.4, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank(),
-            plot.title = element_text(size = rel(2.5), face="bold")
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-#CALL the output PC for simplicity
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-Compatibility <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Compatibility <- dat_cleaning_5$Compatibility_system
-  dat$Compatibility <- as.character(dat$Compatibility)
-  dat$Compatibility[dat$Compatibility=="dioecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="monoecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-  dat$Compatibility[dat$Compatibility=="self_compatible"] <- "Self compatible"
-  dat$Compatibility[dat$Compatibility=="self_incompatible"] <- "Self incompatible"
-  dat$Compatibility <- factor(dat$Compatibility, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Compatibility),size=1.75)+scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)  + ylab("Pollinator dependence - Floral display axis")
-
-  plot
-
-}
-
-#Compatibility(PC)
-
-#############################################################################################################################################################
-#Life form
-#############################################################################################################################################################
-#Load plots
-Life_form <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Life form` <- dat_cleaning_5$life_form
-  dat$`Life form` <- as.character(dat$`Life form`)
-  dat$`Life form`[dat$`Life form`=="herb"] <- "Herb"
-  dat$`Life form`[dat$`Life form`=="shrub"] <- "Shrub"
-  dat$`Life form`[dat$`Life form`=="tree"] <- "Tree"
-  dat$`Life form`[dat$`Life form`=="vine"] <- "Shrub"
-
-  dat$`Life form` <- factor( dat$`Life form`, levels = c("Herb", "Shrub", "Tree"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Life form`),size=1.75)+scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.090, 0.115)) + ggtitle("(b)") +
-    xlab(NULL) + ylab(NULL)
-
-  plot
-
-}
-
-#Life_form(PC)
-
-#############################################################################################################################################################
-#Life span
-#############################################################################################################################################################
-#Load plots
-Life_span <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-    dat$Lifespan <- dat_cleaning_5$lifespan
-    dat$Lifespan <- as.character(dat$Lifespan)
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Lifespan),size=1.75)+scale_color_manual(values=c("sienna4","forestgreen"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.12, 0.1)) + ggtitle("(c)") +
-    xlab(NULL) + ylab(NULL)
-
-  plot
-
-}
-
-#Life_span(PC)
-
-#############################################################################################################################################################
-#Flower symmetry
-#############################################################################################################################################################
-#Load plots
-Flower_sym <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower symmetry` <- dat_cleaning_5$Flower_symmetry
-  dat$`Flower symmetry` <- as.character(dat$`Flower symmetry`)
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower symmetry`),size=1.75)+scale_color_manual(values=c("sienna2","purple"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL) + xlab("Flower number - Flower size axis")
-
-  plot
-
-}
-
-#Flower_sym(PC)
-
-#############################################################################################################################################################
-#Flower shape
-#############################################################################################################################################################
-#Load plots
-Flower_sha <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower shape` <- dat_cleaning_5$Flower_morphology
-  dat$`Flower shape` <- as.character(dat$`Flower shape`)
-  dat$`Flower shape`[dat$`Flower shape`=="Funnelform"] <- "Campanulate"
-  dat$`Flower shape`[dat$`Flower shape`=="Spike"] <- "Brush"
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower shape`),size=1.75)+scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL) + xlab("Flower number - Flower size axis")
-
-  plot
-
-}
-
-#Flower_sha(PC)
-
-#############################################################################################################################################################
-#Breeding system
-#############################################################################################################################################################
-#Load plots
-Breeding_syst <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Breeding system` <- dat_cleaning_5$Breeding_system
-  dat$`Breeding system` <- as.character(dat$`Breeding system`)
-  dat$`Breeding system` <- factor(dat$`Breeding system`, levels=c("Hermaphrodite","Monoecious" ,"Dioecious"))
-
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Breeding system`),size=1.75)+scale_color_manual(values=c("forestgreen","orange", "black"))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("(d)") +
-    xlab("Flower number - Flower size axis") +
-    ylab("Pollinator dependence - Floral display axis")
-
-  plot
-
-}
-
-#Breeding_syst(PC)
-
-#############################################################################################################################################################
-#Nectar
-#############################################################################################################################################################
-#Load plots
-#Nectar <- function(PC, x="PC1", y="PC2") {
-#  # PC being a prcomp object
-#  data <- data.frame(PC$S)
-#  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-#  dat <- data.frame(x = data[,x], y = data[,y])
-#  
-#  #######
-#  #DENSITY FUNCTION
-#  #######
-#  get_density <- function(x, y, ...) {
-#    dens <- MASS::kde2d(x, y, ...)
-#    ix <- findInterval(x, dens$x)
-#    iy <- findInterval(y, dens$y)
-#    ii <- cbind(ix, iy)
-#    return(dens$z[ii])
-#  }
-#  
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-#  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-#  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-#  plot <- plot + geom_point(data=dat, aes(-x, -y, #colour=Nectar),size=1.75)+scale_color_manual(values=c("black","grey"))
-#  
-#  ########
-#  #ADD ARROWS 
-#  ########
-#  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-#  mult <- min(
-#    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-#    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-#  )
-#  datapc <- transform(datapc,
-#                      v1 = .75 * mult * (get(x)),
-#                      v2 = .75 * mult * (get(y))
-#  )
-#  # add arrows
-#  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, #yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-#  
-#  #Add axis with perctentage
-#  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-#
-#  
-#  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, #arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-#  
-#  #ADD LABELS
-#  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-#  
-#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-#  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = #-(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-#                          label = PCAloadings$Variables, color="black",size=3)
-#  
-#  #CHANGE THEME
-#  #CHANGE THEME
-#  
-#  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)") 
-#  
-#  plot
-#  
-#}
-#
-# #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")
-
-  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),ncol=3,nrow=2,  align = "hv")
-
-```
-
-\elandscape
-
-## (b) Phylogenetic signal
-
-We found a strong phylogenetic signal (*P* \< 0.01) for most quantitative traits (table S5).
-The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
-The traits that had a moderate phylogenetic signal included inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all the traits we measured ($\lambda$ = 0.14).
-
-## (c) Visitation patterns
-
-The main axes of trait variation (PC1, PC2 and PC3) partly explained the presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the total number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant differences across the different floral visitor guilds for both the presence-absence of interactions and number of visits (figure 3).
-On the flower number - flower size axis, we found  that plants with many small flowers tended to have interaction partners that were Coleoptera, non-bee-Hymenoptera and Diptera (figure 3a), whereas plants with few large flowers mostly had interaction partners that were bees and Lepidoptera.
-We found similar trends for visitation rates on the flower number - flower size axis,  but bees and syrphids visited plant species with many small flowers more frequently (figure 3d).
-On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had many interaction partners and recieved many visits from all floral visitor guilds (figure 3b and figure 3e).
-Finally, on the style length - pollinator dependence axis, plant species with short styles and high pollinator dependence had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and low pollinator dependence (figure 3c).
-Plants with long styles and low pollinator dependence interacted more frequently with Lepidoptera and non-bee-Hymenoptera (figure 3f).
-
-The additional models for the most represented bee families, for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and the number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03), showed that the Apidae family was the main driver of the observed patterns.
-The contrast between interaction presence/absence  and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S8).
-
-```{=tex}
-\vspace{5mm}
-\blandscape
-```
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
-PC1 represents the flower number - flower size axis, PC2 represents the pollinator dependence axis and PC3 represents the style length - pollinator dependence axis.
-For visualization purposes due to large differences between number of visits from bees and the rest of the pollinator guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
-
-#LOAD LIBRARIES 
-#library(phytools)
-#library(ape) #for phylogenetic distance
-#library(dplyr) #data processing
-#library(rtrees) #for phylogenetic distancelibrary(MASS)
-#library(reshape2)
-library(viridis) #COLOUR GGPLOT
-#library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-#library(tidyverse)
-library(patchwork) #panel of plots
-#library(brms)
-#library(cmdstanr)
-
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2)),
-           axis.text=element_text(size = rel(1.8), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(2, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
-           plot.subtitle = element_text(face="bold",size=rel(2))
-     ))
-}
-
-setwd("~/R_Projects/Reproductive Traits")
-
-p1 <- readRDS("Main_Figures/figure_3_1.rds")
-p2 <- readRDS("Main_Figures/figure_3_2.rds")
-p3 <- readRDS("Main_Figures/figure_3_3.rds")
-pp1 <- readRDS("Main_Figures/figure_3_4.rds")
-pp2 <- readRDS("Main_Figures/figure_3_5.rds")
-pp3 <- readRDS("Main_Figures/figure_3_6.rds")
-
-library(patchwork)
-
-combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
-combined + plot_layout(guides = "collect",ncol = 3)
-
-```
-
-\elandscape
-
-## (d) Plant species network roles
-
-Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
-On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
-However, specialization (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
-On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S9c).
-Again, specialization showed the opposite trend to the number of visits (figure S9i).
-
-# 4. Discussion
-
-We found strong covariation among traits within the flowering plant reproductive spectrum, which shapes interactions with floral visitors at a global scale.
-Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50% and 70% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, pollinator dependence and floral display, and style length and pollinator dependence.
-Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits [@diaz2016; @carmona2021], our results align with the largest and most recent study of plant life strategies that included reproductive, form and size related traits [@salguero2016].
-The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct floral visitor guilds.
-However, the unexplained variability found highlights the need to account for other local factors, such as species relative abundances [@bartomeus2016], along with reproductive traits, to better explain plant-pollinator associations.
-
-Our study provides strong evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1,200 species).
-Specifically, by using a multitrait approach, we are able to link the reproductive spectrum of plant trait variation with the previously described “fast-slow continuum” in plant [@salguero2016] and animal [@healy2019] life-history strategies.
-This fast-slow continuum was illustrated by the associations between reproductive traits and plant height, life form and lifespan traits.
-For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred Angiosperm species in the absence of a multitrait perspective.
-We found support for this trait association and show that other reproductive traits (e.g., style length or ovule number) covary along this flower number - flower size axis.
-Our study also complements previous work linking plant breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers also have woody life forms and many flowers.
-Moreover, we identify the previously documented positive association between outcrossing rate and floral display size [@goodwillie2010], where species with high pollinator dependence also allocate large resource quantities to attract floral visitors.
-Although we did not include floral rewards in our main analysis due to insufficient data, we did find that plant species with large floral displays and, in particular, large flowers, tended to have higher pollen and nectar quantity.
-Thus, we demonstrate that globally, reproductive trait covariation in flowering plants likely imposes constraints on the broader spectrum of plant trait variation.
-
-Overall, plant reproductive traits explained interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations across spatial large scales.
-For example, we found that all floral visitor guilds interacted more frequently with large flowered and pollinator dependent plant species, which aligns with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
-As predicted by evolutionary life-history theory [@stebbins1970], larger investment in floral display and rewards to attract pollinators occurs when pollinator dependence is high.
-However,  the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different floral visitor guilds [@galen1999].
-For instance, smaller flowers are visited less overall, but they are inexpensive to produce (e.g., have a low ovule number) and low visitation rate at the individual flower level can be compensated by overall visitation at the plant level by producing many flowers resulting in a larger quantity of small fruits [@kettle2011].
-In addition, because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and floral visitor guilds could indicate the existence of pollination syndromes [@fenster2004; @faegri2013; @rosas2014; @dellinger2020].
-For instance, bees had a higher number of interacting partners on plant species with large flowers but interacted more frequently with species with small flowers while syrphid flies showed the opposite trend.
-This could be reflective of differences in the ecology and behaviour between these pollinator guilds [@rader2020; @foldesi2021] that ultimately exert different selective pressures, leading divergent plant reproductive strategies.
-In any case, it is worth noting that local factors (e.g., species relative abundances or phenologies) likely contribute to the variability in the association between the plant reproductive spectrum and floral visitors [@vazquez2007; @encinas2012; @bartomeus2016].
-
-Our study provides a comprehensive assessment of  reproductive trait covariation patterns in flowering plants, using a global dataset of traits for plant species within plant-pollinator networks.
-We show the importance of floral visitors in mediating reproductive trait correlations and identify the need to consider broader plant reproductive strategies, rather than just flower morphology, to understand patterns of plant-pollinator interactions.
-Further, we provide empirical evidence of reproductive trait associations that complements trait covariation studies for other plant organs, highlighting the need to include reproductive traits in the global spectrum of plant form and function.
-Future work incorporating underrepresented areas of the world and additional relevant reproductive traits (e.g., flower life span and colour) will be valuable for enhancing our understanding of the plant reproductive spectrum and associated plant-pollinator interactions.
-
-# References
-
-::: {#refs}
-:::
-
-**Data accessibility.** All data and code used to conduct this study are available in the online repositories of Zenodo (<https://doi.org/10.5281/zenodo.6705621>) and Github (<https://github.com/JoseBSL/Reproductive-traits>).
-
-**Authors' contributions.** JBL, RR and IB designed the study. JBL collated the data and conducted analysis with guidance of JS, LKK and IB. JBL wrote the manuscript with contributions of all authors.
-
-**Conflict of interest declaration.** We declare we have no competing interests.
-
-**Funding.** This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2) and JBL was supported by a University of New England IPRA postgraduate scholarship.
 
@@
 Finally, we thank Marcos Méndez, Susan Kalisz, Amanda Benoit, May Berenbaum and an anonymous reviewer for thoughtful feedback and useful comments on earlier versions of this manuscript.
+
+**Conflict of interest declaration.** We declare we have no competing interests.
+
+**Authors' contributions.** JBL, RR and IB designed the study. JBL collated the data and conducted analysis with guidance of JS, LKK and IB. JBL wrote the manuscript with contributions of all authors.
+
+**Data accessibility.** All data and code used to conduct this study are available in the online repositories of Zenodo (<https://doi.org/10.5281/zenodo.6705621>) and Github (<https://github.com/JoseBSL/Reproductive-traits>).

### 2022-10-04 Manuscript/Title_Page.tex
edits

--- 2022-06-22 Manuscript/Lanuza_et_al_2021.tex
@@
 ]{article}
+\title{\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shapes interactions with floral visitors}
+\author{}
+\date{\vspace{-2.5em}}
+
 \usepackage{amsmath,amssymb}
@@
 \pagestyle{plain}
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 \usepackage{lineno} % add 
@@
 \DeclareUnicodeCharacter{1EF3}{*************************************}
+\usepackage{orcidlink}
 \usepackage{float}
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
 \ifLuaTeX
@@
 \fi
-
-\title{\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors}
-\author{}
-\date{\vspace{-2.5em}}
 
@@
 \textbf{Jose B.
-Lanuza$^{1,2}$} \href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}, \textbf{Romina Rader$^{1}$} \href{mailto:rrader@une.edu.au}{\nolinkurl{rrader@une.edu.au}}, \textbf{Jamie Stavert$^{3}$} \href{mailto:jamie.stavert@gmail.com}{\nolinkurl{jamie.stavert@gmail.com}}, \textbf{Liam K.
-Kendall$^{4}$} \href{mailto:liam.k.kendall@gmail.com}{\nolinkurl{liam.k.kendall@gmail.com}}, \textbf{Manu E.
-Saunders$^{1}$} \href{mailto:Manu.Saunders@une.edu.au}{\nolinkurl{Manu.Saunders@une.edu.au}} \textbf{and Ignasi Bartomeus$^{2}$} \href{mailto:nacho.bartomeus@gmail.com}{\nolinkurl{nacho.bartomeus@gmail.com}}
+Lanuza$^{1,2}$} \orcidlink{0000-0002-0287-409X}, \textbf{Romina Rader$^{1}$} \orcidlink{0000-0001-9056-9118}, \textbf{Jamie Stavert$^{3}$} \orcidlink{0000-0002-2103-5320}, \textbf{Liam K.
+Kendall$^{4}$} \orcidlink{0000-0002-0671-0121}, \textbf{Manu E.
+Saunders$^{1}$} \orcidlink{0000-0003-0645-8277} \textbf{and Ignasi Bartomeus$^{2}$} \orcidlink{0000-0001-7893-4389}
 
@@
 
-\doublespacing
-\normalsize
-
-\textbf{Keywords:} life-history strategies \textbar{} plant reproductive traits \textbar{} plant-pollinator interactions
-
-\textbf{Author for correspondence:} Jose B. Lanuza \textbar{} \href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
-
-\hypertarget{abstract}{%
-\section{Abstract}\label{abstract}}
-
-Plants have an enormous variation of life history strategies and trait combinations.
-However, there is strong evidence that there are evolutionary and physiological constraints that limit the number of plant ecological strategies.
-Despite recent advances in the understanding of plant trait variation, little is known about reproductive trait correlations and how these affect plant life-history strategies and shape interactions with floral visitors.
-Here, we investigate the reproductive spectrum of flowering plants and how this drive interactions with floral visitors using a dataset of 16 reproductive traits for 1,506 plant species.
-We found that over 50\% and 70\% of all trait variation was explained by the first two and three reproductive axes, respectively.
-Specifically, the first axis indicated the presence of a negative correlation between flower number and flower size; the second axis showed a positive correlation between pollinator dependence and floral display; and the third axis indicated a negative correlation between style length and pollinator dependence.
-These different reproductive axes determined important differences in the interaction level among floral visitor guilds but were insufficient to fully capture plant-pollinator associations.
-Our study shows the major reproductive trait correlations and highlights their relevance to understand plant-pollinator interactions in a global context.
-
-\doublespacing
-\vspace{5mm}
-\normalsize
-
-\hypertarget{introduction}{%
-\section{1. Introduction}\label{introduction}}
-
-Flowering plants have an astonishing diversity of floral structures {[}\protect\hyperlink{ref-barrett2002}{1},\protect\hyperlink{ref-schiestl2013}{2}{]} that shape plant-pollinator associations {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-dellinger2020}{4}{]}.
-However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints {[}\protect\hyperlink{ref-stearns1989}{5},\protect\hyperlink{ref-agrawal2020}{6}{]}.
-Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits {[}\protect\hyperlink{ref-salguero2016}{7}--\protect\hyperlink{ref-roddy2021}{10}{]}, their study is often limited to a handful number of reproductive traits that are rarely studied jointly.
-Thus, in order to progress towards a comprehensive understanding of the plant reproductive spectrum of trait variation as done recently for other vegetative and physiological plant traits {[}\protect\hyperlink{ref-wright2004}{11}--\protect\hyperlink{ref-laughlin2021}{15}{]}, there is a need to acquire a multitrait perspective with broad geographical coverage.
-Importantly, the characterization of the reproductive trait covariation patterns can help to further understand the different plant ecological strategies {[}\protect\hyperlink{ref-agrawal2020}{6}{]} and improve our knowledge on plant-pollinator associations {[}\protect\hyperlink{ref-roddy2021}{10}{]}.
-
-Although there is an increasing number of macroecological studies that investigate plant reproductive traits {[}\protect\hyperlink{ref-baude2016}{16}--\protect\hyperlink{ref-moeller2017}{19}{]}, we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-sargent2008}{20}--\protect\hyperlink{ref-ruger2018}{22}{]}.
-In addition, the pollination system of a great number of plant species remains unexplored and is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations {[}\protect\hyperlink{ref-tur2013}{23},\protect\hyperlink{ref-devaux2014}{24}{]}.
-Interestingly, the use of trait-based approaches {[}\protect\hyperlink{ref-fenster2004}{3},\protect\hyperlink{ref-rosas2014}{25}{]} and trait-matching analyses {[}\protect\hyperlink{ref-stang2009}{26},\protect\hyperlink{ref-bartomeus2016}{27}{]} has shown to be of great importance when exploring the drivers of plant-pollinator interactions.
-For example, plant traits can define species' network roles {[}e.g., specialists vs generalists \protect\hyperlink{ref-tur2013}{23}{]} and plant species that occupy reproductive trait space extremes are more likely to exhibit higher levels of specialisation and be more reliant on the trait-matching with pollinators {[}\protect\hyperlink{ref-junker2013}{28},\protect\hyperlink{ref-coux2016}{29}{]}.
-Indeed, morphological matching between plants and floral visitors often determines plant-pollinator interactions, and can thus strongly influence interaction network structure {[}\protect\hyperlink{ref-stang2009}{26},\protect\hyperlink{ref-ibanez2012}{30}{]}.
-Because the species' morphology can determine the species' functional role in the pollination network and the combination of traits has shown to increase the predictive power of the network interactions {[}\protect\hyperlink{ref-eklof2013}{31}{]}, an interesting novel approach is to investigate how traits in the multidimensional trait space determine species interaction patterns {[}see \protect\hyperlink{ref-dehling2016}{32}{]}.
-Thus, by exploring the reproductive spectrum of trait variation is possible to delimit the different plant reproductive strategies and explore how these are associated with the different floral visitors.
-
-With the recent availability of large trait databases {[}e.g., TRY \protect\hyperlink{ref-kattge2011}{33},~COMPADRE \protect\hyperlink{ref-salguero2015}{34}{]}, plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function {[}\protect\hyperlink{ref-salguero2016}{7},\protect\hyperlink{ref-diaz2016}{13},\protect\hyperlink{ref-bruelheide2018}{35},\protect\hyperlink{ref-carmona2021}{36}{]}.
-However, most studies with a multitrait perspective have focused on trait correlations from the leaf {[}\protect\hyperlink{ref-wright2004}{11}{]}, wood {[}\protect\hyperlink{ref-chave2009}{12}{]}, or root {[}\protect\hyperlink{ref-laughlin2021}{15}{]} related traits with little or no attention given to reproductive traits {[}\protect\hyperlink{ref-roddy2021}{10},\protect\hyperlink{ref-evojtko2020}{37}{]}.
-Despite the lack of an holistic view that depict reproductive trait covariation patterns, there are widely recognized reproductive trait associations between pair of traits such as the negative correlation between flower size and flower number {[}\protect\hyperlink{ref-sargent2007}{38},\protect\hyperlink{ref-kettle2011}{39}{]}, the positive association between flower size and outcrossing rate {[}\protect\hyperlink{ref-goodwillie2010}{40}{]} or the association between outcrossing rate and lifespan where short lived versus perennial species tend to have low versus high levels of outcrossing {[}\protect\hyperlink{ref-moeller2017}{19},\protect\hyperlink{ref-barrett2003}{41}{]}, respectively.
-Although these different trait correlations (and others) have recently allowed to progress towards a conceptual framework that integrates the different floral trait relationships {[}\protect\hyperlink{ref-roddy2021}{10}{]}, we still lack empirical evidence that investigates jointly these different reproductive trait associations.
-
-Here, we aim to progress knowledge on the reproductive trait covariation patterns and their association with the different floral visitor guilds by exploring at a broad geographical scale the reproductive spectrum of trait variation of entomophilous plant species from plant-pollination networks.
-First, we investigate what are the major axes of reproductive trait variation and trait correlations for the different plant species.
-Second, we investigate the association between the plant species' position in the multidimensional trait-space and the different floral visitor guilds with the help of qualitative (presence-absence of interaction) and quantitative (number of visits) information about plant-pollinator interactions.
-Finally, we investigate how both the main axes of trait variation, and individual traits, influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics (i.e., number of visits, normalized degree and specialization).
-
-\hypertarget{methods}{%
-\section{2. Methods}\label{methods}}
-
-\hypertarget{a-plant-pollinator-network-studies}{%
-\subsection{(a) Plant-pollinator network studies}\label{a-plant-pollinator-network-studies}}
-
-We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see table S1 and figure S1).
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different biological communities.
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to be animal pollinated.
-Many of these networks are freely available either as published studies {[}e.g., \protect\hyperlink{ref-carvalheiro2014}{42},\protect\hyperlink{ref-olesen2007}{43},\protect\hyperlink{ref-fortuna2010}{44}{]} or available in online archives {[}e.g., Mangal \protect\hyperlink{ref-poisot2016}{45},~The Web of Life \protect\hyperlink{ref-fortuna2010}{44}{]}.
-In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (presence-absence of the interaction) networks, each sampled at a unique location and year, as well as eight meta-webs where interactions were pooled across several locations and multiple years.
-
-\hypertarget{b-taxonomy-of-plants-and-pollinators}{%
-\subsection{(b) Taxonomy of plants and pollinators}\label{b-taxonomy-of-plants-and-pollinators}}
-
-All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} {[}\protect\hyperlink{ref-chamberlain2020}{46}{]}.
-We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
-
-\hypertarget{c-plant-traits}{%
-\subsection{(c) Plant traits}\label{c-plant-traits}}
-
-We selected a total of 19 different functional traits that comprised reproductive traits and plant form and size related traits (see table 1).
-From these, 16 were reproductive traits that consisted of 13 floral traits and 3 reproductive biology traits.
-Floral traits included traits related to the size of floral organs (e.g., style length), floral display (e.g., number of flowers) and floral rewards (e.g., pollen quantity).
-Reproductive biology traits indicated the reproductive system of the plant and included breeding, mating and compatibility system.
-The 3 remaining traits were plant size and form related traits that are commonly used to characterize the fast-slow continuum of plant trait variation (i.e., plant height, lifespan and life form).
-For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
-From a total of 30,120 possible cells considering all traits and plant species (20 columns × 1,506 species), we were able to fill 24,341 cells (80.8\% of the dataset, see figure S2 for missing values information for each trait).
-An extended description of each trait and how it was obtained can be found in Appendix S1.
-
-\singlespacing
-
-\begin{table}
-
-\caption{\label{tab:unnamed-chunk-1}\textbf{Table 1.} Quantitative and categorical traits used in this study.}
-\centering
-\fontsize{12}{14}\selectfont
-\begin{tabular}[t]{ll}
-\toprule
-\textbf{Traits} & \textbf{Numerical range/Categories}\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{2}{l}{\textbf{Quantitative}}\\
-\hspace{1em}Plant height & 0.01-30m\\
-\hspace{1em}Flower width & 0.50-205mm\\
-\hspace{1em}Flower length & 0.20-195mm\\
-\hspace{1em}Inflorescence width & 0.80-300mm\\
-\hspace{1em}Style length & 0-138mm\\
-\hspace{1em}Ovules per flower & 1-25 x $10^3$\\
-\hspace{1em}Flowers per plant & 1-18 x $10^4$\\
-\hspace{1em}Microliters of nectar & 0-160$\mu$l\\
-\hspace{1em}Milligrams of nectar & 0-6.1mg\\
-\hspace{1em}Nectar concentration & 0-100$\%$\\
-\hspace{1em}Pollen grains per flower & 13-2 x $10^8$\\
-\hspace{1em}Autonomous selfing (fruit set) & 0-100$\%$\\
-\addlinespace[0.3em]
-\multicolumn{2}{l}{\textbf{Categorical}}\\
-\hspace{1em}Lifepan & Short-lived and perennial\\
-\hspace{1em}Life form & Herb, shrub and tree\\
-\hspace{1em}Flower shape & \makecell[l]{Brush, campanulate, capitulum,\\ open, papilionaceous and tube}\\
-\hspace{1em}Flower symmetry & Actinomorphic and zygomorphic\\
-\hspace{1em}Nectar & Presence and absence\\
-\hspace{1em}Compatibility system & \makecell[l]{Self-incompatible, partially self-compabtile \\ and self-compatible}\\
-\hspace{1em}Breeding system & Hermaphrodite, monoecious and dioecious\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\doublespacing
-
-\hypertarget{d-phylogenetic-distance}{%
-\subsection{(d) Phylogenetic Distance}\label{d-phylogenetic-distance}}
-
-We calculated the phylogenetic distance between different plant species using the function \emph{get\_tree} from the package \emph{rtrees} (\url{https://github.com/daijiang/rtrees}), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life {[}\protect\hyperlink{ref-smith2018}{47},\protect\hyperlink{ref-jin2019}{48}{]}.
-
-\hypertarget{e-data-imputation}{%
-\subsection{(e) Data Imputation}\label{e-data-imputation}}
-
-To avoid the loss of relevant ecological information, we imputed trait missing values with the help of the function \emph{missForest} {[}\protect\hyperlink{ref-stekhoven2012}{49}{]} which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors of a principal component analysis of the phylogenetic distance (PCoA) which has been shown to improve the performance of \emph{missForest} {[}\protect\hyperlink{ref-penone2014}{50}{]}.
-To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} {[}\protect\hyperlink{ref-santos2018}{51}{]} based on a previous conceptual framework that considers phylogenetic eigenvectors {[}\protect\hyperlink{ref-diniz-filho2012}{52}{]}.
-We conducted two different imputations, one for the full set of species (1,506 species, 5.79\% of missing values) excluding nectar and pollen traits because of the high percentage of missing values (figure S2) and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species, 8.01\% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without missing values and we found consistent similar results on both analyses (Fig S3 and Fig S4).
-
-\hypertarget{f-plant-strategies}{%
-\subsection{(f) Plant strategies}\label{f-plant-strategies}}
-
-We explored the association between the different quantitative plant traits with a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasizing flower size on the spectrum of trait variation.
-Prior to the analyses, we excluded outliers and standardized the data.
-Due to the high sensitivity of dimensionality reduction to outliers {[}\protect\hyperlink{ref-serneels2008}{53},\protect\hyperlink{ref-legendre2012}{54}{]}, we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed the variables to reduce the influence of outliers and z-transformed (X= 0, SD=1) so that all variables were within the same numerical range as indicated for principal component analysis {[}\protect\hyperlink{ref-legendre2012}{54}{]}.
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation with the help of an Anova and a Tukey test.
-We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{55}{]} with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode covariance because values for each variables were on the same scale following transformation {[}\protect\hyperlink{ref-abdi2010}{56}{]}.
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity.
-For this, we included all quantitative traits considered in the main pPCA plus pollen grains and microlitres of nectar per flower.
-
-\hypertarget{g-phylogenetic-signal}{%
-\subsection{(g) Phylogenetic signal}\label{g-phylogenetic-signal}}
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package \emph{phytools} {[}\protect\hyperlink{ref-revell2012}{55}{]} and we used Pagel's \(\lambda\) as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-\hypertarget{h-network-analyses}{%
-\subsection{(h) Network analyses}\label{h-network-analyses}}
-
-First, we investigated how the different groups of floral visitors interacted along the main axes of reproductive trait variation (see below `visitation patterns' section) with the help of qualitative and quantitative information of plant-pollinator interactions.
-For this, we used as qualitative information the binary version of the networks (presence-absence of interaction) that assumes equal weight across interactions and as quantitative information the number of visits of floral visitors to individual flowers that accounts for the intensity of the interaction.
-Although floral visitors are not always pollinators and number of visits does not consider each pollinator species efficiency {[}\protect\hyperlink{ref-ballantyne2015}{57}{]}, the number of visits can provide valuable information of the contribution of floral visitors to pollination {[}\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}{]}.
-Second, we investigated how the main axes of trait variation and individual traits influence plant species' functional roles in the pollination network using a set of complementary interaction network metrics: number of visits, normalized degree and specialization (see below `plant species network roles' section).
-
-Analyses were conducted on the subset of 60 weighted networks sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our network dataset (excluding meta-webs and non-weighted networks) included 2,256 interactions of bees with plants, 1,768 non-syrphid-Diptera interactions, 845 syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee-Hymenoptera interactions.
-Sampling methods varied across networks but this was accounted for in analyses by considering them in the random effects of the modelling process.
-All analyses were conducted in R version \emph{4.0.3}.
-
-\hypertarget{i-visitation-patterns}{%
-\subsubsection{(i) Visitation patterns}\label{i-visitation-patterns}}
-
-We used Bayesian modelling (see below for details) to explore the effect of floral visitor groups and the main axes of trait variation (pPCA with imputed dataset) on both qualitative and quantitative floral interactions per plant species.
-For this, we divided floral visitors into six main guilds that differ in life form, behaviour and are likely to play a similar ecological role: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera and (vi) Coleoptera.
-Moreover, because the guild of bees was the most represented group with 2,256 records and had the highest frequency of visits, we also explored presence-absence of the interaction and number of visits of the main bee families (Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae) on the trait space.
-In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of records counted (7.55\% of the total).
-This finding is consistent with previous research showing that \emph{A.
-mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems {[}\protect\hyperlink{ref-hung2018}{60}{]}.
-Hence, to control for the effect of \emph{A.
-mellifera} on the observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding \emph{A.
-mellifera}.
-We found that \emph{A.
-mellifera}, was partly driving some of the observed trends on PC1 (figure S5).
-However, we did not detect major differences on PC2 and PC3.
-
-We implemented Bayesian generalized linear mixed models using the R package \emph{brms} {[}\protect\hyperlink{ref-burkner2017}{61}{]}.
-We modelled presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in the visitation patterns among floral visitors groups to plants with different strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds.
-We added a nested random effect of networks nested within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence across them.
-We specified for presence-absence of interaction and number of visits a Bernoulli and a zero inflated negative binomial distribution, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative informative priors from the brm function so they have neglible influence on the results {[}\protect\hyperlink{ref-burkner2017}{61}{]}.
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package {[}\protect\hyperlink{ref-gabry2019}{62}{]}.
-
-\hypertarget{ii-plant-species-network-roles}{%
-\subsubsection{(ii) Plant species network roles}\label{ii-plant-species-network-roles}}
-
-We investigated whether different quantitative traits determined different plant species' functional roles in the pollination network using Bayesian modelling.
-For this, we selected simple and complementary species-level network metrics commonly applied in bipartite network studies {[}\protect\hyperlink{ref-dormann2008}{63}{]} with a straightforward ecological interpretation relevant to our research goals.
-The different plant species-level metrics were: (i) sum of visits per plant species; (ii) normalized degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialization (d') {[}\protect\hyperlink{ref-bluthgen2006}{64}{]}, which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalization) and 1 (maximum specialization).
-Normalized degree and specialization were calculated with the \emph{specieslevel} function from the R package \emph{bipartite} {[}\protect\hyperlink{ref-dormann2008}{63}{]}.
-
-We modelled the distinct plant species metrics (sum of visits, normalized degree and plant specialization) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
-For each response variable (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalized degree and zero one inflated beta for specialization).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns' section.
-
-\hypertarget{results}{%
-\section{3. Results}\label{results}}
-
-\hypertarget{a-plant-strategies}{%
-\subsection{(a) Plant strategies}\label{a-plant-strategies}}
-
-The phylogenetically informed principal component analysis captured by the first two and three axes 51.8\% and 70.97\% of the reproductive trait variation, respectively (figure 1 and figure S7).
-The first principal component (PC1 or the flower number - flower size axis) represented 26.72\% of the trait variation and indicated a negative correlation between flower number and flower size.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \textgreater{} \textbar0.5\textbar; table S3) but style length also contributed moderately to PC1 (loading = -0.33).
-One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-For instance, on this end of the spectrum we find the species \emph{Cornus florida} which has approximately a total of 10.000 flowers, an average height of 7.5m, flowers of 3mm wide, a style length of 3.5mm and a total of 2 ovules per flower.
-The other end of this spectrum comprised species that were short in height and invested in large flowers, long styles, many ovules, but few flowers.
-For instance, on this side of the axis we find the species \emph{Petunia axillaris} that has approximately 10 flowers per plant, a height of 0.5m, flowers over 50mm wide, styles of 25mm and over 200 ovules per flower.
-The second principal component (PC2 or the pollinator dependence axis) represented 25.05\% of the trait variation and indicated the variation from low to high autonomous selfing, or in other words, high to low pollinator dependence, respectively.
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but the other traits (except ovule number) also made moderate contributions (loadings from 0.27 to 0.4; table S3).
-In general terms, species with high pollinator dependence were associated with larger and a higher number of flowers, greater plant height and longer styles.
-On this extreme of the spectrum we find the species \emph{Zuccagnia punctata} that is a self-incompatible shrub that depends completely on floral visitors for seed production, it has approximately 1500 flowers per plant, 3m height and a style length of 20mm.
-In contrast, species with low pollinator dependence tended to have fewer and smaller flowers, shorter plant height and shorter styles.
-For instance, on this end of the spectrum we find the species \emph{Veronica peregrina} which is a self-compatible herb that is thought to be almost a complete selfer that relies none or little on floral visitors, it has around 20 flowers per plant, a height of 0.2m and a style length of 0.25mm.
-Further, the third principal component (PC3 or the style length - pollinator dependence axis) explained a considerable amount of trait variability (19.17\%) and represented a negative correlation between style length (loading = -0.66) and pollinator dependence (autonomous selfing loading = \textbar-0.51\textbar) where species with short styles had high pollinator dependence and species with long styles low pollinator dependence.
-The remaining traits, apart from ovule number, were positively correlated with style length and negatively correlated with pollinator dependence (loadings from -0.23 to -0.46; table S3).
-In addition, the pPCA with the subset of species that had nectar and pollen quantity data showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with flower size, style length and ovule number but negatively associated with flower number (figure S4).
-This pPCA explained similar variance with the first two principal components (45.52\%) and similar associations of traits despite some variability in the loadings (table S4).
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=0.95\linewidth]{output/figures/unnamed-chunk-2-1}
-
-}
-
-\caption{\textbf{Figure 1.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
-The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
-The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation.
-The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum.}\label{fig:unnamed-chunk-2}
-\end{figure}
-
-We found (with an Anova) that most categorical traits were statistically associated with the first two axes of trait variation (figure 2 and table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
-In addition, we found (with a Tukey test) statistical differences between the different levels of categorical traits in the trait space (figure S8).
-Regarding self-compatibility, we found larger differences on PC2 (i.e., species with unisexual flowers that were self-incompatible were statistically differentiated from species with partial or full self-compatibility; figure S8a and figure S8b).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with higher pollinator dependence to smaller ones (herbs) with lower pollinator dependence (figure S8c and figure S8d).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S8e and figure S8f).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had the highest pollinator dependence and highest number of flowers (figure S8g and figure S8h).
-Moreover, we found that the campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space.
-The former morphologies had larger flowers and greater pollinator dependence, while the latter had higher flower number and lower pollinator dependence (figure S8i and figure S8j).
-Regarding flower symmetry, zygomorphic flowers were associated with lower levels of pollinator dependence, whereas actinomorphic flowers had higher levels of pollinator dependence (figure S8k and figure S8l).
-
-\blandscape
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=0.8\linewidth]{output/figures/unnamed-chunk-3-1}
-
-}
-
-\caption{\textbf{Figure 2.} Location of the different qualitative traits on the trait space.
-The panel is composed by the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
-The solid arrows indicate the direction of variation of the different quantitative traits showed in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S).}\label{fig:unnamed-chunk-3}
-\end{figure}
-
-\elandscape
-
-\hypertarget{b-phylogenetic-signal}{%
-\subsection{(b) Phylogenetic signal}\label{b-phylogenetic-signal}}
-
-We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) for most quantitative traits (table S5).
-The traits that showed the highest phylogenetic signal were ovule number (\(\lambda\) = 1), pollen grains per flower (\(\lambda\) = 1) and plant height (\(\lambda\) = 0.96), followed by flower length (\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73), number of flowers per plant (\(\lambda\) = 0.69) and nectar concentration (\(\lambda\) = 0.65).
-The traits that showed a moderate phylogenetic signal were inflorescence width (\(\lambda\) = 0.57), style length (\(\lambda\) = 0.49) and autonomous selfing (\(\lambda\) = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all traits (\(\lambda\) = 0.14).
-
-\hypertarget{c-visitation-patterns}{%
-\subsection{(c) Visitation patterns}\label{c-visitation-patterns}}
-
-The main axes of trait variation (PC1, PC2 and PC3) explained partly presence-absence of interaction partners (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the overall number of visits (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
-However, we found relevant differences across the different floral visitor guilds on both presence-absence of interactions and number of visits (figure 3).
-We found on the flower number - flower size axis that plants with high flower number and small flowers had higher interaction partners of Coleoptera, non-bee-Hymenoptera and all Diptera guilds (figure 3a) but plants with low flower number but large flowers had higher interaction partners of bees and Lepidoptera guilds.
-Regarding visitation rates on the flower number - flower size axis, we found similar trends but bees and syrphids guilds in this case showed higher number of visits to plant species with high flower number but small (figure 3d).
-On the pollinator dependence axis, we found that all plant species with higher pollinator dependence had higher number of interacting partners and number of visits from all floral visitor guilds (figure 3b and figure 3e).
-Finally, on the style length - pollinator dependence axis plant species with short styles and high pollinator dependence had higher interaction partners of all guilds but bees, that interacted clearly more with plant species with long styles and low pollinator dependence (figure 3c).
-However, regarding number of visits on the style length - pollinator dependence axis, we found that plants with long styles and high selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera guilds (figure 3f).
-
-The additional model for both presence-absence of interaction (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and number of visits (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns.
-The contrasting differences between presence-absence of interaction and number of visits for bees on PC1 (figure 3a and figure 3d) were driven by the family Andrenidae that had higher number of interacting partners but lower number of visits on plant species with low number of large flowers (figure S9).
-
-\vspace{5mm}
-\blandscape
-
-\begin{figure}
-\centering
-\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\textbf{Figure 3.} Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of trait variation (PC1, PC2 and PC3).
-PC1 represents the flower number - flower size axis, PC2 represents the pollinator dependence axis and PC3, the style length - pollinator dependence axis.
-For visualization purposes, due to large differences between number of visits of bees and the rest of guilds, the number of visits was log-transformed (Y-axis of lower panel).}
-\end{figure}
-
-\elandscape
-
-\hypertarget{d-plant-species-network-roles}{%
-\subsection{(d) Plant species network roles}\label{d-plant-species-network-roles}}
-
-The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S10; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization.
-On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S10a).
-However, specialization showed the opposite trend on this axis (figure S10g).
-On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S10c).
-Again, specialization showed the opposite trend to number of visits (figure S10i).
-
-\hypertarget{discussion}{%
-\section{4. Discussion}\label{discussion}}
-
-This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale.
-Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively.
-These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence.
-Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{13},\protect\hyperlink{ref-carmona2021}{36}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}.
-Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds.
-However, they were insufficient to capture their visitation rates which highlight the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.
-
-Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context.
-In addition, our work links the reproductive trait variation with the previously described fast-slow continuum' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{65}{]} life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan.
-Although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{38},\protect\hyperlink{ref-kettle2011}{39},\protect\hyperlink{ref-worley2000}{66}{]}, it has only been investigated across a few hundred of Angiosperm species with a two-trait approach.
-We found support to this trait association and show that other life history traits also covariate along this axis.
-For example, our study complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{67}{]} by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number.
-Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{40}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors.
-Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral display.
-Thus, our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.
-
-Overall, our models showed that the main plant reproductive trait correlations have low predictive power for broad-level interaction patterns between plants and floral visitors.
-However, we found changes in the interaction patterns among and within floral visitor guilds that suggest that plant reproductive strategies partly mediate these associations at large ecological scales.
-For example, we found that all floral visitor guilds interacted more frequently with plant species with larger floral displays in agreement with previous findings {[}\protect\hyperlink{ref-hegland2005}{68}--\protect\hyperlink{ref-kaiser2014}{70}{]}.
-Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes.
-For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies and because these two guilds are likely to differ in ecology and behaviour {[}rader2020; {[}\protect\hyperlink{ref-foldesi2021}{71}{]}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies.
-In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{27},\protect\hyperlink{ref-vazquez2007}{72},\protect\hyperlink{ref-encinas2012}{73}{]} that reproductive correlations do not.
-
-To conclude, we provide a robust description of the main reproductive trait covariation patterns of flowering plants by using a global dataset of plant reproductive traits from species that belong to plant-pollinator networks.
-Our work highlights the relevance of floral visitors in mediating these reproductive trait correlations and the need to consider other factors beyond plant reproductive strategies to better capture broad scale patterns of interactions with floral visitors.
-Our work provides empirical evidence that complements previous studies that have explored trait correlations with other plant organs and highlights the need to include these reproductive correlations in the global spectrum of plant form and function {[}\protect\hyperlink{ref-diaz2016}{13}{]} as reproductive strategies involve clear cost and benefits that can affect the trait space of the whole plant.
-Finally, the future incorporation of unrepresented areas of the world and other relevant reproductive traits such as flower life span or flower colour will definitely help to provide better descriptions of the reproductive spectrum of plant trait variation and plant-pollinator associations.
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-barrett2002}{}}%
-\CSLLeftMargin{1. }
-\CSLRightInline{Barrett SCH. 2002 The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.} \textbf{3}, 274--284. (doi:\href{https://doi.org/10.1038/nrg776}{10.1038/nrg776})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schiestl2013}{}}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Schiestl FP, Johnson SD.
-2013 Pollinator-mediated evolution of floral signals.
-\emph{Trends Ecol.
-Evol.} \textbf{28}, 307--315.
-(doi:\href{https://doi.org/10.1016/j.tree.2013.01.019}{10.1016/j.tree.2013.01.019})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fenster2004}{}}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Fenster CB, Armbruster WS, Wilson P, Dudash MR, Thomson JD.
-2004 Pollination {Syndromes} and {Floral Specialization}.
-\emph{Annu.
-Rev.
-Ecol.
-Evol.
-Syst.} \textbf{35}, 375--403.
-(doi:\href{https://doi.org/10.1146/annurev.ecolsys.34.011802.132347}{10.1146/annurev.ecolsys.34.011802.132347})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dellinger2020}{}}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Dellinger AS.
-2020 Pollination syndromes in the 21st century: Where do we stand and where may we go?
-\emph{New Phytol.} \textbf{228}, 1193--1213.
-(doi:\href{https://doi.org/10.1111/nph.16793}{10.1111/nph.16793})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stearns1989}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Stearns SC. 1989 Trade-offs in life-history evolution. \emph{Functional ecology} \textbf{3}, 259--268.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-agrawal2020}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{Agrawal AA. 2020 A scale-dependent framework for trade-offs, syndromes, and specialization in organismal biology. \emph{Ecology} \textbf{101}, e02924.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-salguero2016}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{Salguero-Gómez R, Jones OR, Jongejans E, Blomberg SP, Hodgson DJ, Mbeau-Ache C, Zuidema PA, de Kroon H, Buckley YM.
-2016 Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
-\emph{Proc.
-Natl.
-Acad.
-Sci.
-U.S.A.} \textbf{113}, 230--235.
-(doi:\href{https://doi.org/10.1073/pnas.1506215112}{10.1073/pnas.1506215112})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-friedman2020}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Friedman J.
-2020 The evolution of annual and perennial plant life histories: Ecological correlates and genetic mechanisms.
-\emph{Annual Review of Ecology, Evolution, and Systematics} \textbf{51}, 461--481.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-paterno2020}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Paterno GB, Silveira CL, Kollmann J, Westoby M, Fonseca CR.
-2020 The maleness of larger angiosperm flowers.
-\emph{Proceedings of the National Academy of Sciences} \textbf{117}, 10921--10926.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-roddy2021}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{Roddy AB, Martínez-Perez C, Teixido AL, Cornelissen TG, Olson ME, Oliveira RS, Silveira FAO.
-2021 Towards the flower economics spectrum.
-\emph{New Phytol.} \textbf{229}, 665--672.
-(doi:\href{https://doi.org/10.1111/nph.16823}{10.1111/nph.16823})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wright2004}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{Wright IJ \emph{et al.} 2004 The worldwide leaf economics spectrum. \emph{Nature} \textbf{428}, 821--827. (doi:\href{https://doi.org/10.1038/nature02403}{10.1038/nature02403})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chave2009}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Chave J, Coomes D, Jansen S, Lewis SL, Swenson NG, Zanne AE. 2009 Towards a worldwide wood economics spectrum. \emph{Ecol. Lett.} \textbf{12}, 351--366.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-diaz2016}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Díaz S \emph{et al.} 2016 The global spectrum of plant form and function. \emph{Nature} \textbf{529}, 167--171. (doi:\href{https://doi.org/10.1038/nature16489}{10.1038/nature16489})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-onoda2017}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Onoda Y, Wright IJ, Evans JR, Hikosaka K, Kitajima K, Niinemets Ü, Poorter H, Tosens T, Westoby M.
-2017 Physiological and structural tradeoffs underlying the leaf economics spectrum.
-\emph{New Phytologist} \textbf{214}, 1447--1463.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-laughlin2021}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Laughlin DC \emph{et al.} 2021 Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
-\emph{Nat.
-Ecol.
-Evol.}, 1--12.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-baude2016}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Baude M, Kunin WE, Boatman ND, Conyers S, Davies N, Gillespie MA, Morton RD, Smart SM, Memmott J.
-2016 Historical nectar assessment reveals the fall and rise of floral resources in britain.
-\emph{Nature} \textbf{530}, 85--88.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-munoz2016}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{Munoz F, Violle C, Cheptou P-O.
-2016 {CSR} ecological strategies and plant mating systems: Outcrossing increases with competitiveness but stress-tolerance is related to mixed mating.
-\emph{Oikos} \textbf{125}, 1296--1303.
-(doi:\href{https://doi.org/10.1111/oik.02328}{10.1111/oik.02328})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-grossenbacher2017}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Grossenbacher DL \emph{et al.} 2017 Self-compatibility is over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-moeller2017}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Moeller DA \emph{et al.} 2017 Global biogeography of mating system variation in seed plants.
-\emph{Ecol.
-Lett.} \textbf{20}, 375--384.
-(doi:\href{https://doi.org/10.1111/ele.12738}{10.1111/ele.12738})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Sargent RD, Ackerly DD. 2008 Plant--pollinator interactions and the assembly of plant communities. \emph{Trends Ecol. Evol.} \textbf{23}, 123--130.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rech2016}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Rech AR, Dalsgaard B, Sandel B, Sonne J, Svenning J-C, Holmes N, Ollerton J.
-2016 The macroecology of animal versus wind pollination: Ecological factors are more important than historical climate stability.
-\emph{Plant Ecol.
-Divers.} \textbf{9}, 253--262.
-(doi:\href{https://doi.org/10.1080/17550874.2016.1207722}{10.1080/17550874.2016.1207722})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ruger2018}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{Rüger N, Comita LS, Condit R, Purves D, Rosenbaum B, Visser MD, Wright SJ, Wirth C.
-2018 Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
-\emph{Ecol.
-Lett.} \textbf{21}, 1075--1084.
-(doi:\href{https://doi.org/10.1111/ele.12974}{10.1111/ele.12974})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Tur C, Castro-Urgal R, Traveset A.
-2013 Linking {Plant Specialization} to {Dependence} in {Interactions} for {Seed Set} in {Pollination Networks}.
-\emph{PLoS One} \textbf{8}, e78294.
-(doi:\href{https://doi.org/10.1371/journal.pone.0078294}{10.1371/journal.pone.0078294})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-devaux2014}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{Devaux C, Lepers C, Porcher E.
-2014 Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems.
-\emph{J.
-Evol.
-Biol.} \textbf{27}, 1413--1430.
-(doi:\href{https://doi.org/10.1111/jeb.12380}{10.1111/jeb.12380})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rosas2014}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Rosas-Guerrero V, Aguilar R, Martén-Rodríguez S, Ashworth L, Lopezaraiza-Mikel M, Bastida JM, Quesada M.
-2014 A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
-\emph{Ecol.
-Lett.} \textbf{17}, 388--400.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stang2009}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Stang M, Klinkhamer PGL, Waser NM, Stang I, van der Meijden E.
-2009 Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
-\emph{Ann.
-Bot.} \textbf{103}, 1459--1469.
-(doi:\href{https://doi.org/10.1093/aob/mcp027}{10.1093/aob/mcp027})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bartomeus2016}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Bartomeus I, Gravel D, Tylianakis JM, Aizen MA, Dickie IA, Bernard-Verdier M.
-2016 A common framework for identifying linkage rules across different types of interactions.
-\emph{Funct.
-Ecol.} \textbf{30}, 1894--1903.
-(doi:\href{https://doi.org/10.1111/1365-2435.12666}{10.1111/1365-2435.12666})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-junker2013}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{Junker RR, Blüthgen N, Brehm T, Binkenstein J, Paulus J, Schaefer HM, Stang M.
-2013 Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
-\emph{Funct.
-Ecol.} \textbf{27}, 329--341.
-(doi:\href{https://doi.org/10.1111/1365-2435.12005}{10.1111/1365-2435.12005})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-coux2016}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{Coux C, Rader R, Bartomeus I, Tylianakis JM.
-2016 Linking species functional roles to their network roles.
-\emph{Ecol.
-Lett.} \textbf{19}, 762--770.
-(doi:\href{https://doi.org/10.1111/ele.12612}{10.1111/ele.12612})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ibanez2012}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Ibanez S.
-2012 Optimizing size thresholds in a plant-pollinator interaction web: Towards a mechanistic understanding of ecological networks.
-\emph{Oecologia} \textbf{170}, 233--242.
-(doi:\href{https://doi.org/10.1007/s00442-012-2290-3}{10.1007/s00442-012-2290-3})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-eklof2013}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Eklöf A \emph{et al.} 2013 The dimensionality of ecological networks. \emph{Ecol. Lett.} \textbf{16}, 577--583.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dehling2016}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Dehling DM, Jordano P, Schaefer HM, Böhning-Gaese K, Schleuning M.
-2016 Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
-\emph{Proc.
-Royal Soc.
-B} \textbf{283}, 20152444.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kattge2011}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{Kattge J \emph{et al.} 2011 {TRY} \textendash{} a global database of plant traits.
-\emph{Glob.
-Chang.
-Biol.} \textbf{17}, 2905--2935.
-(doi:\href{https://doi.org/10.1111/j.1365-2486.2011.02451.x}{10.1111/j.1365-2486.2011.02451.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-salguero2015}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{Salguero-Gómez R \emph{et al.} 2015 The compadre {Plant Matrix Database}: An open online repository for plant demography.
-\emph{J.
-Ecol.} \textbf{103}, 202--218.
-(doi:\href{https://doi.org/10.1111/1365-2745.12334}{10.1111/1365-2745.12334})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bruelheide2018}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Bruelheide H \emph{et al.} 2018 Global trait--environment relationships of plant communities. \emph{Nat. Ecol. Evol.} \textbf{2}, 1906--1917.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carmona2021}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Carmona CP \emph{et al.} 2021 Erosion of global functional diversity across the tree of life.
-\emph{Sci.
-Adv.} \textbf{7}, eabf2675.
-(doi:\href{https://doi.org/10.1126/sciadv.abf2675}{10.1126/sciadv.abf2675})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-evojtko2020}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{E-Vojtkó A, Bello F de, Durka W, Kühn I, Götzenberger L.
-2020 The neglected importance of floral traits in trait-based plant community assembly.
-\emph{J.
-Veg.
-Sci.} \textbf{31}, 529--539.
-(doi:\href{https://doi.org/10.1111/jvs.12877}{10.1111/jvs.12877})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sargent2007}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{Sargent RD, Goodwillie C, Kalisz S, Ree RH.
-2007 Phylogenetic evidence for a flower size and number trade-off.
-\emph{Am.
-J.
-Bot.} \textbf{94}, 2059--2062.
-(doi:\href{https://doi.org/10.3732/ajb.94.12.2059}{10.3732/ajb.94.12.2059})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kettle2011}{}}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Kettle CJ, Maycock CR, Ghazoul J, Hollingsworth PM, Khoo E, Sukri RSH, Burslem DFRP.
-2011 Ecological {Implications} of a {Flower Size}/{Number Trade}-{Off} in {Tropical Forest Trees}.
-\emph{PLoS One} \textbf{6}, e16111.
-(doi:\href{https://doi.org/10.1371/journal.pone.0016111}{10.1371/journal.pone.0016111})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-goodwillie2010}{}}%
-\CSLLeftMargin{40. }
-\CSLRightInline{Goodwillie C \emph{et al.} 2010 Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
-\emph{New Phytol.} \textbf{185}, 311--321.
-(doi:\href{https://doi.org/10.1111/j.1469-8137.2009.03043.x}{10.1111/j.1469-8137.2009.03043.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-barrett2003}{}}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Barrett SCH.
-2003 Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond.
-\emph{Philos.
-Trans.
-R.
-Soc.
-Lond.
-B Biol.
-Sci.} \textbf{358}, 991--1004.
-(doi:\href{https://doi.org/10.1098/rstb.2003.1301}{10.1098/rstb.2003.1301})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carvalheiro2014}{}}%
-\CSLLeftMargin{42. }
-\CSLRightInline{Carvalheiro LG \emph{et al.} 2014 The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
-\emph{Ecol.
-Lett.} \textbf{17}, 1389--1399.
-(doi:\href{https://doi.org/10.1111/ele.12342}{10.1111/ele.12342})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
-\CSLLeftMargin{43. }
-\CSLRightInline{Olesen JM, Bascompte J, Dupont YL, Jordano P.
-2007 The modularity of pollination networks.
-\emph{PNAS} \textbf{104}, 19891--19896.
-(doi:\href{https://doi.org/10.1073/pnas.0706375104}{10.1073/pnas.0706375104})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Fortuna MA, Stouffer DB, Olesen JM, Jordano P, Mouillot D, Krasnov BR, Poulin R, Bascompte J.
-2010 Nestedness versus modularity in ecological networks: Two sides of the same coin?
-\emph{J.
-Anim.
-Ecol.} \textbf{79}, 811--817.
-(doi:\href{https://doi.org/10.1111/j.1365-2656.2010.01688.x}{10.1111/j.1365-2656.2010.01688.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-poisot2016}{}}%
-\CSLLeftMargin{45. }
-\CSLRightInline{Poisot T \emph{et al.} 2016 Mangal \textendash{} making ecological network analysis simple.
-\emph{Ecography} \textbf{39}, 384--390.
-(doi:\href{https://doi.org/10.1111/ecog.00976}{10.1111/ecog.00976})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
-\CSLLeftMargin{46. }
-\CSLRightInline{Chamberlain S \emph{et al.} 2020 Taxize: {Taxonomic} information from around the web.
-R package version 0.9.99.~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Smith SA, Brown JW.
-2018 Constructing a broadly inclusive seed plant phylogeny.
-\emph{Am.
-J.
-Bot.} \textbf{105}, 302--314.
-(doi:\href{https://doi.org/10.1002/ajb2.1019}{10.1002/ajb2.1019})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jin2019}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Jin Y, Qian H.
-2019 V.{PhyloMaker}: An {R} package that can generate very large phylogenies for vascular plants.
-\emph{Ecography} \textbf{42}, 1353--1359.
-(doi:\href{https://doi.org/10.1111/ecog.04434}{10.1111/ecog.04434})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stekhoven2012}{}}%
-\CSLLeftMargin{49. }
-\CSLRightInline{Stekhoven DJ, Bühlmann P.
-2012 {MissForest}\textemdash non-parametric missing value imputation for mixed-type data.
-\emph{Bioinformatics} \textbf{28}, 112--118.
-(doi:\href{https://doi.org/10.1093/bioinformatics/btr597}{10.1093/bioinformatics/btr597})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-penone2014}{}}%
-\CSLLeftMargin{50. }
-\CSLRightInline{Penone C, Davidson AD, Shoemaker KT, Marco MD, Rondinini C, Brooks TM, Young BE, Graham CH, Costa GC.
-2014 Imputation of missing data in life-history trait datasets: Which approach performs the best?
-\emph{Methods Ecol.
-Evol.} \textbf{5}, 961--970.
-(doi:\href{https://doi.org/10.1111/2041-210X.12232}{10.1111/2041-210X.12232})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-santos2018}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Chamberlain S \emph{et al.} 2018 Package {`{PVR}'}. R package version 0.3.~At \href{https://CRAN.R-project.org/package=PVR}{https://CRAN.r-project.org/package=PVR}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-diniz-filho2012}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Diniz-Filho JAF, Bini LM, Rangel TF, Morales-Castilla I, Olalla-Tárraga MÁ, Rodríguez MÁ, Hawkins BA.
-2012 On the selection of phylogenetic eigenvectors for ecological analyses.
-\emph{Ecography} \textbf{35}, 239--249.
-(doi:\href{https://doi.org/10.1111/j.1600-0587.2011.06949.x}{10.1111/j.1600-0587.2011.06949.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-serneels2008}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Serneels S, Verdonck T. 2008 Principal component analysis for data containing outliers and missing elements. \emph{Computational Statistics \& Data Analysis} \textbf{52}, 1712--1727.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-legendre2012}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Legendre P, Legendre L. 2012 \emph{Numerical ecology}. {2nd edn}. {Elsevier, Amsterdam}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-revell2012}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Revell LJ.
-2012 Phytools: An {R} package for phylogenetic comparative biology (and other things).
-\emph{Methods Ecol.
-Evol.} \textbf{3}, 217--223.
-(doi:\href{https://doi.org/10.1111/j.2041-210X.2011.00169.x}{10.1111/j.2041-210X.2011.00169.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Abdi H, Williams LJ. 2010 Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459. (doi:\href{https://doi.org/10.1002/wics.101}{10.1002/wics.101})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ballantyne2015}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Ballantyne G, Baldock KCR, Willmer PG.
-2015 Constructing more informative plant\textendash pollinator networks: Visitation and pollen deposition networks in a heathland plant community.
-\emph{Proc.
-Royal Soc.
-B} \textbf{282}, 20151130.
-(doi:\href{https://doi.org/10.1098/rspb.2015.1130}{10.1098/rspb.2015.1130})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2005}{}}%
-\CSLLeftMargin{58. }
-\CSLRightInline{Vázquez DP, Morris WF, Jordano P.
-2005 Interaction frequency as a surrogate for the total effect of animal mutualists on plants.
-\emph{Ecol.
-Lett.} \textbf{8}, 1088--1094.
-(doi:\href{https://doi.org/10.1111/j.1461-0248.2005.00810.x}{10.1111/j.1461-0248.2005.00810.x})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2012}{}}%
-\CSLLeftMargin{59. }
-\CSLRightInline{Vázquez DP, Lomáscolo SB, Maldonado MB, Chacoff NP, Dorado J, Stevani EL, Vitale NL.
-2012 The strength of plant\textendash pollinator interactions.
-\emph{Ecology} \textbf{93}, 719--725.
-(doi:\href{https://doi.org/10.1890/11-1356.1}{10.1890/11-1356.1})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hung2018}{}}%
-\CSLLeftMargin{60. }
-\CSLRightInline{Hung K-LJ, Kingston JM, Albrecht M, Holway DA, Kohn JR.
-2018 The worldwide importance of honey bees as pollinators in natural habitats.
-\emph{Proc.
-Royal Soc.
-B} \textbf{285}, 20172140.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
-\CSLLeftMargin{61. }
-\CSLRightInline{Bürkner P-C. 2017 Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.} \textbf{80}, 1--28.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gabry2019}{}}%
-\CSLLeftMargin{62. }
-\CSLRightInline{Gabry J, Simpson D, Vehtari A, Betancourt M, Gelman A.
-2019 Visualization in {Bayesian} workflow.
-\emph{J.
-R.
-Stat.
-Soc.
-Ser.
-A Stat.
-Soc.} \textbf{182}, 389--402.
-(doi:\href{https://doi.org/10.1111/rssa.12378}{10.1111/rssa.12378})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dormann2008}{}}%
-\CSLLeftMargin{63. }
-\CSLRightInline{Dormann CF, Gruber B, Fründ J. 2008 Introducing the bipartite package: Analysing ecological networks. \emph{R News} \textbf{8/2}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
-\CSLLeftMargin{64. }
-\CSLRightInline{Blüthgen N, Menzel F, Blüthgen N.
-2006 Measuring specialization in species interaction networks.
-\emph{BMC Ecol.} \textbf{6}, 9.
-(doi:\href{https://doi.org/10.1186/1472-6785-6-9}{10.1186/1472-6785-6-9})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-healy2019}{}}%
-\CSLLeftMargin{65. }
-\CSLRightInline{Healy K, Ezard THG, Jones OR, Salguero-Gómez R, Buckley YM.
-2019 Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
-\emph{Nat.
-Ecol.
-Evol.} \textbf{3}, 1217--1224.
-(doi:\href{https://doi.org/10.1038/s41559-019-0938-7}{10.1038/s41559-019-0938-7})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-worley2000}{}}%
-\CSLLeftMargin{66. }
-\CSLRightInline{Worley AC, Baker AM, Thompson JD, Barrett SC.
-2000 Floral display in narcissus: Variation in flower size and number at the species, population, and individual levels.
-\emph{International Journal of Plant Sciences} \textbf{161}, 69--79.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-petit2006}{}}%
-\CSLLeftMargin{67. }
-\CSLRightInline{Petit RJ, Hampe A. 2006 Some evolutionary consequences of being a tree. \emph{Annu. Rev. Ecol. Evol. Syst.} \textbf{37}, 187--214.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
-\CSLLeftMargin{68. }
-\CSLRightInline{Hegland SJ, Totland Ø. 2005 Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia} \textbf{145}, 586--594.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
-\CSLLeftMargin{69. }
-\CSLRightInline{Lázaro A, Jakobsson A, Totland Ø.
-2013 How do pollinator visitation rate and seed set relate to species' floral traits and community context?
-\emph{Oecologia} \textbf{173}, 881--893.
-(doi:\href{https://doi.org/10.1007/s00442-013-2652-5}{10.1007/s00442-013-2652-5})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
-\CSLLeftMargin{70. }
-\CSLRightInline{Kaiser-Bunbury CN, Vázquez DP, Stang M, Ghazoul J.
-2014 Determinants of the microstructure of plant\textendash pollinator networks.
-\emph{Ecology} \textbf{95}, 3314--3324.
-(doi:\href{https://doi.org/10.1890/14-0024.1}{10.1890/14-0024.1})}
-
-\leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
-\CSLLeftMargin{71. }
-\CSLRightInline{Földesi R, Howlett BG, Grass I, Batáry P.
-2021 Larger pollinators deposit more pollen on stigmas across multiple plant species---a meta-analysis.
-\emph{Journal of Applied Ecology} \textbf{58}, 699--707.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
-\CSLLeftMargin{72. }
-\CSLRightInline{Vázquez DP, Melián CJ, Williams NM, Blüthgen N, Krasnov BR, Poulin R.
-2007 Species abundance and asymmetric interaction strength in ecological networks.
-\emph{Oikos} \textbf{116}, 1120--1127.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
-\CSLLeftMargin{73. }
-\CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS. 2012 Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.} \textbf{15}, 198--208.}
-
-\end{CSLReferences}
-
-\textbf{Data accessibility.} All data and code used to conduct this study is deposited at Zenodo
-
-\textbf{Authors'contributions.} JBL, RR and IB designed the study.
-JBL collated the data and conducted analysis with guidance of JS, LKK and IB.
-JBL wrote the manuscript with contributions of all authors.
-
-\textbf{Conflict of interest declaration.} We declare we have no competing interests.
-
-\textbf{Funding.} This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2) and JBL was supported by a University of New England postgraduate scholarship.
-
-\textbf{Acknowledgements.} We thank all researchers that made their data openly available and sent it upon request.
-We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
-We also thank Jason Tylianakis for his comments on the manuscript before submission.
-Finally, JBL thanks the University of New England for the funding provided to carry out this work.
-
 \end{document}

### 2022-10-04 Supplementary_Material/Species_Level_Metric_Pc's.Rmd
edits

@@
   size = 2.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
-  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1")
+  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Selectivity (d')") + xlab("PC1")
 

### 2022-10-05 Manuscript/Lanuza_et_al_2022.Rmd
Title page and MS update

@@
 ---
-title: \singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shapes interactions with floral visitors
+title: \singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shape their interactions with pollinators
 
@@
 However, evidence suggests that evolutionary and physiological constraints limit the number of plant ecological strategies.
-Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with floral visitors.
-Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with floral visitors.
+Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with pollinators.
+Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
 We show that over 50% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the negative correlation between autonomous selfing and floral display size.
-In addition, these reproductive axes were associated with different numbers of interacting partners and visitation rates of the distinct floral visitor guilds.
-However, the relatively small amount of variance explained by the different reproductive axes highlight the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
+In addition, these reproductive axes were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
+However, reproductive axes explain a relatively small amount of variance in pollinator interactions highlighting the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
 Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping networks of plant-pollinator interactions at a global scale.
@@
 However, studies that look at multiple traits tend to overlook plant reproductive traits [@evojtko2020; @ruger2018; @roddy2021], and focus on trait correlations in other plant organs such as morphological and physiological leaf traits [@wright2004; @shipley2006; @donovan2011; @osnas2013].
-Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs such as the negative correlation between flower size and flower number [@sargent2007; @kettle2011; @vojtko2022]; the positive association between flower size and outcrossing rate [@goodwillie2010]; or the positive correlation between outcrossing rate and lifespan [@barrett2003; @munoz2016; @moeller2017]).
+Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs such as the negative correlation between flower size and flower number [@sargent2007; @kettle2011; @vojtko2022]; the positive association between flower size and outcrossing rate [@goodwillie2010]; or the positive correlation between outcrossing rate and lifespan [@barrett2003; @munoz2016; @moeller2017].
 Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships [@roddy2021], we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
@@
 For example, plant traits can define species' network roles [e.g., specialists vs generalists @tur2013] and plant species that occupy reproductive trait space extremes are likely to be more specialised and display tighter trait-matching with pollinators [@junker2013; @coux2016].
-Indeed, the degree of morphological matching between plants and floral visitors often determines whether or not interactions occur, and consequently influences  the broader network structure [@stang2009; @ibanez2012].
+Indeed, the degree of morphological matching between plants and pollinators often determines whether or not interactions occur, and consequently influences  the broader network structure [@stang2009; @ibanez2012].
 However, it is still unclear how specific reproductive traits (e.g., mating or compatibility system) influence plant-pollinator associations [@sargent2008; @tur2013; @devaux2014].
+For example, species with high selfing rates may evolve to invest less in floral rewards resulting in a lower number of pollinator visits [@devaux2014].
 Indeed, both morphology and mating system can determine a species' functional role within pollination networks, and the combination of several traits increases power for predicting network structure [@eklof2013].
@@
 
-Here, we explore the spectrum of reproductive traits in flowering plants, within a global set of plant-pollinator networks, to identify reproductive trait covariation and how this influences the network of interactions between plants and floral visitors.
+Here, we explore the spectrum of reproductive traits in flowering plants, within a global set of plant-pollinator networks, to identify reproductive trait covariation and how this influences the network of interactions between plants and pollinators.
 First, we identify the major axes of reproductive trait variation and correlations among traits for plant species.
-Then, we investigate the associations between plant species’ positions in reproductive trait space and the strength of their interactions with different floral visitor guilds within networks.
+Then, we investigate the associations between plant species’ positions in reproductive trait space and the strength of their interactions with different pollinator guilds within networks.
 Finally, we determine how the main axes of reproductive trait variation influence plant species' functional roles within pollination networks, using a range of complementary interaction network metrics.
@@
 All species names, genera, families and orders were retrieved and standardised from the taxonomy data sources NCBI (<https://www.ncbi.nlm.nih.gov/taxonomy>) for plants and ITIS (<https://www.itis.gov/>) for pollinators, using the R package *taxize* [@chamberlain2020].
-We filled the 'not found' searches manually using <http://www.theplantlist.org/> and <http://www.mobot.org/> for plants and <http://www.catalogueoflife.org/> for floral visitors.
+We filled the 'not found' searches manually using <http://www.theplantlist.org/> and <http://www.mobot.org/> for plants and <http://www.catalogueoflife.org/> for pollinators.
 
@@
 To extract the eigenvectors, we used the function *PVRdecomp* from the package *PVR* [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-We conducted two different imputations, one for the full set of species (1,506 species: 5.79% of missing values), and excluded nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01% of missing values).
+We conducted two different imputations, one for the full set of species (1,506 species: 5.79% of missing values), and excluding nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01% of missing values).
 To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and results for the two datasets were consistent (Fig S3 and Fig S4).
@@
 
-We used Bayesian modelling (see details below) to investigate how the different guilds of floral visitors interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
-Specifically, interactions between plants and floral visitors in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
+We used Bayesian modelling (see details below) to investigate how the different guilds of pollinators interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
+Specifically, interactions between plants and pollinators in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
 Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species [@ballantyne2015], the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination [@vazquez2005; @vazquez2012].
-We divided floral visitors into six main taxonomical guilds that differ in life form, behaviour and thus likely play different ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
+Therefore, despite the fact that we do not evaluate pollinator effectiveness we refer to the different floral visitors as pollinators.
+
+We divided pollinators into six main taxonomical guilds that differ in life form, behaviour and thus likely play different ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
 Moreover, because bees had the greatest number of occurrences in networks  (2,256 records) and the highest frequency of visits, we further broke this group down into the main bee families (Andrenidae, Apidae, Colletidae, Halictidae, and Megachilidae).
-In addition, we found that *Apis mellifera* was the floral visitor with the largest proportion of occurrences in networks (7.55% of the total).
+In addition, we found that *Apis mellifera* was the pollinator with the largest proportion of occurrences in networks (7.55% of the total).
 This is consistent with previous research showing that *A.
-mellifera* was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
+mellifera* was the most frequent pollinator in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
 Hence, to control for the effect of *A.
@@
 
-We used Bayesian generalised linear mixed models in the R package *brms* [@burkner2017] to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in visitation patterns among floral visitor guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds in the model.
+We used Bayesian generalised linear mixed models in the R package *brms* [@burkner2017] to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with pollinator guilds (e.g., number of visits \~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in visitation patterns among pollinator guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different pollinator guilds in the model.
 We added a nested random effect of networks within the study system to capture the variation in networks among studies and within networks.
@@
 The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results [@burkner2017].
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function *pp_check* using the *bayesplot* package [@gabry2019].
+We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualised the posterior predictive checks with the function *pp_check* using the *bayesplot* package [@gabry2019].
 
@@
 For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies [@dormann2008], with clear ecological interpretations and are relevant for defining species' functional roles in networks.
-Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalised degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialisation (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalisation) and 1 (maximum specialisation).
-Normalised degree and specialisation were calculated with the *specieslevel* function in the R package *bipartite* [@dormann2008].
-We modelled each plant species metric (sum of visits, normalised degree and plant specialisation) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
-For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalised degree, and zero-one inflated beta for specialisation).
+Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalised degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) selectivity (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalisation) and 1 (maximum specialisation).
+Normalised degree and selectivity were calculated with the *specieslevel* function in the R package *bipartite* [@dormann2008].
+We modelled each plant species metric (sum of visits, normalised degree and plant selectivity) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
+For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalised degree, and zero-one inflated beta for selectivity).
 Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the 'visitation patterns' section.
@@
 The main axes of trait variation (PC1, PC2 and PC3) partly explained the presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the total number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant differences across the different floral visitor guilds for both the presence-absence of interactions and number of visits (figure 3).
+However, we found relevant differences across the different pollinator guilds for both the presence-absence of interactions and number of visits (figure 3).
 On the flower number - flower size axis, we found  that plants with many small flowers tended to have interaction partners that were Coleoptera, non-bee-Hymenoptera and Diptera (figure 3a), whereas plants with few large flowers mostly had interaction partners that were bees and Lepidoptera.
 We found similar trends for visitation rates on the flower number - flower size axis,  but bees and syrphids visited plant species with many small flowers more frequently (figure 3d).
-On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and recieved many visits from all floral visitor guilds (figure 3b and figure 3e).
+On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and recieved many visits from all pollinator guilds (figure 3b and figure 3e).
 Finally, on the style length - autonomous selfing axis, plant species with short styles and low autonomous selfing had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and high autonomous selfing (figure 3c).
@@
 ```
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different pollinator guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
 PC1 represents the flower number - flower size axis, PC2 represents the autonomous selfing - floral display axis and PC3 represents the style length - autonomous selfing axis.
@@
 
-Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalised degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialisation \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and specialisation.
+Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalised degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, selectivity \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
+Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and selectivity.
 On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
-However, specialisation (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
+However, selectivity (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
 On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S9c).
-Again, specialisation showed the opposite trend to the number of visits (figure S9i).
+Again, selectivity showed the opposite trend to the number of visits (figure S9i).
 
@@
 
-We found strong covariation among traits within the flowering plant reproductive spectrum, which shapes interactions with floral visitors at a global scale.
+We found strong covariation among traits within the flowering plant reproductive spectrum, which shapes interactions with pollinators at a global scale.
 Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50% and 70% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, autonomous selfing and floral display, and style length and autonomous selfing.
 Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits [@diaz2016; @carmona2021], our results align with the two largest and most recent studies of plant life strategies that included reproductive, form and size related traits [@salguero2016; @vojtko2022].
-The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct floral visitor guilds.
+The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
 However, the unexplained variability found highlights the need to account for other local factors, such as species relative abundances [@bartomeus2016], along with reproductive traits, to better explain plant-pollinator associations.
@@
 Our study also complements previous work linking plant breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers also have woody life forms and many flowers.
-Moreover, we identify the previously documented positive association between outcrossing rate and floral display size [@goodwillie2010], where species with low autonomous selfing levels also allocate large resource quantities to attract floral visitors.
+Moreover, we identify the previously documented positive association between outcrossing rate and floral display size [@goodwillie2010], where species with low autonomous selfing levels also allocate large resource quantities to attract pollinators.
+
 Although we did not include floral rewards in our main analysis due to insufficient data, we did find that plant species with large floral displays and, in particular, large flowers, tended to have higher pollen and nectar quantity.
@@
 
-Overall, plant reproductive traits explained interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations across spatial large scales.
-For example, we found that all floral visitor guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
+Overall, plant reproductive traits explained interaction patterns among and within pollinator guilds suggesting that plant reproductive strategies partly mediate these associations across spatial large scales.
+For example, we found that all pollinator guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
 As predicted by evolutionary life-history theory [@stebbins1970], larger investment in floral display and rewards to attract pollinators occurs when pollinator dependence is high.
-Indeed, the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different floral visitor guilds [@galen1999].
+Indeed, the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different pollinator guilds [@galen1999].
 For instance, smaller flowers are visited less overall, but they are inexpensive to produce (e.g., have a low ovule number) and low visitation rate at the individual flower level can be compensated by overall visitation at the plant level by producing many flowers resulting in a larger quantity of small fruits [@kettle2011].
@@
 These species seem to rely on animal pollinators as indicated by their high investment in sizable styles that can help prevent pollen competition [@ramesha2011; @ashman2013; @lanuza2021] while having reproductive assurance in their absence.
-Similarly, zygomorphic flowers are specialised floral structures that promote precise pollen transfer [sargent2004; @gong2009] but they were associated with high levels of autogamy.
+For instance, the annual herb _Scabiosa atropurpurea_ has flowers grouped in clusters with relatively long styles and a single ovule per flower that is likely to be fertilised with a single legitimate floral visit but avoids reproductive failure with autonomous self pollination.
+Similarly, zygomorphic flowers are specialised floral structures that promote precise pollen transfer [@sargent2004; @gong2009] but they were associated with high levels of autogamy.
 Our findings are consistent with the idea that reproductive assurance is not rare within specialised pollination systems [@fenster2007] and highlight the need to explore the timing (e.g., early versus delayed) and selfing mechanisms [see @goodwillie2018] in relation to other reproductive traits to better understand reproductive trait correlations and plant-pollinator interactions.
 
-Because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and floral visitor guilds could indicate the existence of pollination syndromes [@fenster2004; @faegri2013; @rosas2014; @dellinger2020].
+Because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and pollinator guilds could indicate the existence of pollination syndromes [@fenster2004; @faegri2013; @rosas2014; @dellinger2020].
 For instance, bees had a higher number of interacting partners on plant species with large flowers but interacted more frequently with species with small flowers while syrphid flies showed the opposite trend.
 This could be reflective of differences in the ecology and behaviour between these pollinator guilds [@rader2020; @foldesi2021] that ultimately exert different selective pressures, leading divergent plant reproductive strategies.
-In any case, it is worth noting that local factors (e.g., species relative abundances or phenologies) likely contribute to the variability in the association between the plant reproductive spectrum and floral visitors [@vazquez2007; @encinas2012; @bartomeus2016].
+In any case, it is worth noting that local factors (e.g., species relative abundances or phenologies) likely contribute to the variability in the association between the plant reproductive spectrum and pollinators [@vazquez2007; @encinas2012; @bartomeus2016].
+Taking both aspects together, we suggest that while plant reproductive traits do shape their interactions with pollinators, pollinator syndromes at a macroecological scale are not distinct compartmentalised items, but form part of a multifaceted context dependent continuum.
 
 Our study provides a comprehensive assessment of  reproductive trait covariation patterns in flowering plants, using a global dataset of traits for plant species within plant-pollinator networks.
-We show the importance of floral visitors in mediating reproductive trait correlations and identify the need to consider broader plant reproductive strategies, rather than just flower morphology, to understand patterns of plant-pollinator interactions.
+We show the importance of pollinators in mediating reproductive trait correlations and identify the need to consider broader plant reproductive strategies, rather than just flower morphology, to understand patterns of plant-pollinator interactions.
 Further, we provide empirical evidence of reproductive trait associations that complement trait covariation studies for other plant organs, highlighting the need to include reproductive traits in the global spectrum of plant form and function.
@@
 
+\newpage
+
 # References

### 2022-10-05 Manuscript/Lanuza_et_al_2022.tex
Title page and MS update

@@
 ]{article}
-\title{\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shapes interactions with floral visitors}
+\title{\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shape their interactions with pollinators}
 \author{}
@@
 \hypersetup{
-  pdftitle={ Covariation among reproductive traits in flowering plants shapes interactions with floral visitors},
+  pdftitle={ Covariation among reproductive traits in flowering plants shape their interactions with pollinators},
   colorlinks=true,
@@
 However, evidence suggests that evolutionary and physiological constraints limit the number of plant ecological strategies.
-Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with floral visitors.
-Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with floral visitors.
+Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with pollinators.
+Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
 We show that over 50\% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the negative correlation between autonomous selfing and floral display size.
-In addition, these reproductive axes were associated with different numbers of interacting partners and visitation rates of the distinct floral visitor guilds.
-However, the relatively small amount of variance explained by the different reproductive axes highlight the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
+In addition, these reproductive axes were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
+However, reproductive axes explain a relatively small amount of variance in pollinator interactions highlighting the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
 Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping networks of plant-pollinator interactions at a global scale.
@@
 However, studies that look at multiple traits tend to overlook plant reproductive traits (\protect\hyperlink{ref-evojtko2020}{E-Vojtkó et al., 2020}; \protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}; \protect\hyperlink{ref-ruger2018}{Rüger et al., 2018}), and focus on trait correlations in other plant organs such as morphological and physiological leaf traits (\protect\hyperlink{ref-donovan2011}{Donovan et al., 2011}; \protect\hyperlink{ref-osnas2013}{Osnas et al., 2013}; \protect\hyperlink{ref-shipley2006}{Shipley et al., 2006}; \protect\hyperlink{ref-wright2004}{Wright et al., 2004}).
-Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs such as the negative correlation between flower size and flower number (\protect\hyperlink{ref-vojtko2022}{E-Vojtkó et al., 2022}; \protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}); the positive association between flower size and outcrossing rate (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}); or the positive correlation between outcrossing rate and lifespan (\protect\hyperlink{ref-barrett2003}{Barrett, 2003}; \protect\hyperlink{ref-moeller2017}{Moeller et al., 2017}; \protect\hyperlink{ref-munoz2016}{Munoz et al., 2016})).
+Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs such as the negative correlation between flower size and flower number (\protect\hyperlink{ref-vojtko2022}{E-Vojtkó et al., 2022}; \protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}); the positive association between flower size and outcrossing rate (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}); or the positive correlation between outcrossing rate and lifespan (\protect\hyperlink{ref-barrett2003}{Barrett, 2003}; \protect\hyperlink{ref-moeller2017}{Moeller et al., 2017}; \protect\hyperlink{ref-munoz2016}{Munoz et al., 2016}).
 Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships (\protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}), we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
@@
 For example, plant traits can define species' network roles (e.g., specialists vs generalists \protect\hyperlink{ref-tur2013}{Tur et al., 2013}) and plant species that occupy reproductive trait space extremes are likely to be more specialised and display tighter trait-matching with pollinators (\protect\hyperlink{ref-coux2016}{Coux et al., 2016}; \protect\hyperlink{ref-junker2013}{Junker et al., 2013}).
-Indeed, the degree of morphological matching between plants and floral visitors often determines whether or not interactions occur, and consequently influences the broader network structure (\protect\hyperlink{ref-ibanez2012}{Ibanez, 2012}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}).
+Indeed, the degree of morphological matching between plants and pollinators often determines whether or not interactions occur, and consequently influences the broader network structure (\protect\hyperlink{ref-ibanez2012}{Ibanez, 2012}; \protect\hyperlink{ref-stang2009}{Stang et al., 2009}).
 However, it is still unclear how specific reproductive traits (e.g., mating or compatibility system) influence plant-pollinator associations (\protect\hyperlink{ref-devaux2014}{Devaux et al., 2014}; \protect\hyperlink{ref-sargent2008}{Sargent \& Ackerly, 2008}; \protect\hyperlink{ref-tur2013}{Tur et al., 2013}).
+For example, species with high selfing rates may evolve to invest less in floral rewards resulting in a lower number of pollinator visits (\protect\hyperlink{ref-devaux2014}{Devaux et al., 2014}).
 Indeed, both morphology and mating system can determine a species' functional role within pollination networks, and the combination of several traits increases power for predicting network structure (\protect\hyperlink{ref-eklof2013}{Eklöf et al., 2013}).
@@
 
-Here, we explore the spectrum of reproductive traits in flowering plants, within a global set of plant-pollinator networks, to identify reproductive trait covariation and how this influences the network of interactions between plants and floral visitors.
+Here, we explore the spectrum of reproductive traits in flowering plants, within a global set of plant-pollinator networks, to identify reproductive trait covariation and how this influences the network of interactions between plants and pollinators.
 First, we identify the major axes of reproductive trait variation and correlations among traits for plant species.
-Then, we investigate the associations between plant species' positions in reproductive trait space and the strength of their interactions with different floral visitor guilds within networks.
+Then, we investigate the associations between plant species' positions in reproductive trait space and the strength of their interactions with different pollinator guilds within networks.
 Finally, we determine how the main axes of reproductive trait variation influence plant species' functional roles within pollination networks, using a range of complementary interaction network metrics.
@@
 All species names, genera, families and orders were retrieved and standardised from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain et al., 2020}).
-We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.
+We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for pollinators.
 
@@
 To extract the eigenvectors, we used the function \emph{PVRdecomp} from the package \emph{PVR} (\protect\hyperlink{ref-santos2018}{Chamberlain et al., 2018}) based on a previous conceptual framework that considers phylogenetic eigenvectors (\protect\hyperlink{ref-diniz-filho2012}{Diniz-Filho et al., 2012}).
-We conducted two different imputations, one for the full set of species (1,506 species: 5.79\% of missing values), and excluded nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01\% of missing values).
+We conducted two different imputations, one for the full set of species (1,506 species: 5.79\% of missing values), and excluding nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01\% of missing values).
 To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and results for the two datasets were consistent (Fig S3 and Fig S4).
@@
 
-We used Bayesian modelling (see details below) to investigate how the different guilds of floral visitors interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
-Specifically, interactions between plants and floral visitors in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
+We used Bayesian modelling (see details below) to investigate how the different guilds of pollinators interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
+Specifically, interactions between plants and pollinators in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
 Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species (\protect\hyperlink{ref-ballantyne2015}{Ballantyne et al., 2015}), the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination (\protect\hyperlink{ref-vazquez2005}{Vázquez et al., 2005}, \protect\hyperlink{ref-vazquez2012}{2012}).
-We divided floral visitors into six main taxonomical guilds that differ in life form, behaviour and thus likely play different ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
+Therefore, despite the fact that we do not evaluate pollinator effectiveness we refer to the different floral visitors as pollinators.
+
+We divided pollinators into six main taxonomical guilds that differ in life form, behaviour and thus likely play different ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
 Moreover, because bees had the greatest number of occurrences in networks (2,256 records) and the highest frequency of visits, we further broke this group down into the main bee families (Andrenidae, Apidae, Colletidae, Halictidae, and Megachilidae).
-In addition, we found that \emph{Apis mellifera} was the floral visitor with the largest proportion of occurrences in networks (7.55\% of the total).
+In addition, we found that \emph{Apis mellifera} was the pollinator with the largest proportion of occurrences in networks (7.55\% of the total).
 This is consistent with previous research showing that \emph{A.
-mellifera} was the most frequent floral visitor in a similar dataset of 80 plant-pollinator networks in natural ecosystems (\protect\hyperlink{ref-hung2018}{Hung et al., 2018}).
+mellifera} was the most frequent pollinator in a similar dataset of 80 plant-pollinator networks in natural ecosystems (\protect\hyperlink{ref-hung2018}{Hung et al., 2018}).
 Hence, to control for the effect of \emph{A.
@@
 
-We used Bayesian generalised linear mixed models in the R package \emph{brms} (\protect\hyperlink{ref-burkner2017}{Bürkner, 2017}) to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with floral visitor guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in visitation patterns among floral visitor guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different floral visitor guilds in the model.
+We used Bayesian generalised linear mixed models in the R package \emph{brms} (\protect\hyperlink{ref-burkner2017}{Bürkner, 2017}) to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with pollinator guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
+Because we were interested in possible differences in visitation patterns among pollinator guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different pollinator guilds in the model.
 We added a nested random effect of networks within the study system to capture the variation in networks among studies and within networks.
@@
 The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results (\protect\hyperlink{ref-burkner2017}{Bürkner, 2017}).
-We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualized the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package (\protect\hyperlink{ref-gabry2019}{Gabry et al., 2019}).
+We set delta (\(\Delta\)) to 0.99 to avoid divergent transitions and visualised the posterior predictive checks with the function \emph{pp\_check} using the \emph{bayesplot} package (\protect\hyperlink{ref-gabry2019}{Gabry et al., 2019}).
 
@@
 For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies (\protect\hyperlink{ref-dormann2008}{Dormann et al., 2008}), with clear ecological interpretations and are relevant for defining species' functional roles in networks.
-Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalised degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) specialisation (d') (\protect\hyperlink{ref-bluthgen2006}{Blüthgen et al., 2006}), which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalisation) and 1 (maximum specialisation).
-Normalised degree and specialisation were calculated with the \emph{specieslevel} function in the R package \emph{bipartite} (\protect\hyperlink{ref-dormann2008}{Dormann et al., 2008}).
-We modelled each plant species metric (sum of visits, normalised degree and plant specialisation) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
-For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalised degree, and zero-one inflated beta for specialisation).
+Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalised degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) selectivity (d') (\protect\hyperlink{ref-bluthgen2006}{Blüthgen et al., 2006}), which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalisation) and 1 (maximum specialisation).
+Normalised degree and selectivity were calculated with the \emph{specieslevel} function in the R package \emph{bipartite} (\protect\hyperlink{ref-dormann2008}{Dormann et al., 2008}).
+We modelled each plant species metric (sum of visits, normalised degree and plant selectivity) as a function of the three main axes of trait variation (plant species level metric \textasciitilde{} PC1 + PC2 + PC3).
+For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalised degree, and zero-one inflated beta for selectivity).
 Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the `visitation patterns' section.
@@
 The main axes of trait variation (PC1, PC2 and PC3) partly explained the presence-absence of interaction partners (conditional \(R^{2}\) = 0.26; marginal \(R^{2}\) = 0.20) but little of the total number of visits (conditional \(R^{2}\) = 0.31; marginal \(R^{2}\) = 0.06).
-However, we found relevant differences across the different floral visitor guilds for both the presence-absence of interactions and number of visits (figure 3).
+However, we found relevant differences across the different pollinator guilds for both the presence-absence of interactions and number of visits (figure 3).
 On the flower number - flower size axis, we found that plants with many small flowers tended to have interaction partners that were Coleoptera, non-bee-Hymenoptera and Diptera (figure 3a), whereas plants with few large flowers mostly had interaction partners that were bees and Lepidoptera.
 We found similar trends for visitation rates on the flower number - flower size axis, but bees and syrphids visited plant species with many small flowers more frequently (figure 3d).
-On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and recieved many visits from all floral visitor guilds (figure 3b and figure 3e).
+On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and recieved many visits from all pollinator guilds (figure 3b and figure 3e).
 Finally, on the style length - autonomous selfing axis, plant species with short styles and low autonomous selfing had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and high autonomous selfing (figure 3c).
@@
 \includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\textbf{Figure 3.} Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different floral visitor guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
+\caption{\label{fig:unnamed-chunk-4}\textbf{Figure 3.} Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different pollinator guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
 PC1 represents the flower number - flower size axis, PC2 represents the autonomous selfing - floral display axis and PC3 represents the style length - autonomous selfing axis.
@@
 
-Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalised degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialisation \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and specialisation.
+Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalised degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, selectivity \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
+Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and selectivity.
 On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
-However, specialisation (d') was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
+However, selectivity (d') was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
 On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S9c).
-Again, specialisation showed the opposite trend to the number of visits (figure S9i).
+Again, selectivity showed the opposite trend to the number of visits (figure S9i).
 
@@
 
-We found strong covariation among traits within the flowering plant reproductive spectrum, which shapes interactions with floral visitors at a global scale.
+We found strong covariation among traits within the flowering plant reproductive spectrum, which shapes interactions with pollinators at a global scale.
 Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50\% and 70\% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, autonomous selfing and floral display, and style length and autonomous selfing.
 Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}), our results align with the two largest and most recent studies of plant life strategies that included reproductive, form and size related traits (\protect\hyperlink{ref-vojtko2022}{E-Vojtkó et al., 2022}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}).
-The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct floral visitor guilds.
+The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
 However, the unexplained variability found highlights the need to account for other local factors, such as species relative abundances (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}), along with reproductive traits, to better explain plant-pollinator associations.
@@
 Our study also complements previous work linking plant breeding systems and life forms (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-petit2006}{Petit \& Hampe, 2006}) by showing that most species with unisexual flowers also have woody life forms and many flowers.
-Moreover, we identify the previously documented positive association between outcrossing rate and floral display size (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}), where species with low autonomous selfing levels also allocate large resource quantities to attract floral visitors.
+Moreover, we identify the previously documented positive association between outcrossing rate and floral display size (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}), where species with low autonomous selfing levels also allocate large resource quantities to attract pollinators.
+
 Although we did not include floral rewards in our main analysis due to insufficient data, we did find that plant species with large floral displays and, in particular, large flowers, tended to have higher pollen and nectar quantity.
@@
 
-Overall, plant reproductive traits explained interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations across spatial large scales.
-For example, we found that all floral visitor guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings (\protect\hyperlink{ref-hegland2005}{Hegland \& Totland, 2005}; \protect\hyperlink{ref-kaiser2014}{Kaiser-Bunbury et al., 2014}; \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}).
+Overall, plant reproductive traits explained interaction patterns among and within pollinator guilds suggesting that plant reproductive strategies partly mediate these associations across spatial large scales.
+For example, we found that all pollinator guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings (\protect\hyperlink{ref-hegland2005}{Hegland \& Totland, 2005}; \protect\hyperlink{ref-kaiser2014}{Kaiser-Bunbury et al., 2014}; \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}).
 As predicted by evolutionary life-history theory (\protect\hyperlink{ref-stebbins1970}{Stebbins, 1970}), larger investment in floral display and rewards to attract pollinators occurs when pollinator dependence is high.
-Indeed, the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different floral visitor guilds (\protect\hyperlink{ref-galen1999}{Galen, 1999}).
+Indeed, the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different pollinator guilds (\protect\hyperlink{ref-galen1999}{Galen, 1999}).
 For instance, smaller flowers are visited less overall, but they are inexpensive to produce (e.g., have a low ovule number) and low visitation rate at the individual flower level can be compensated by overall visitation at the plant level by producing many flowers resulting in a larger quantity of small fruits (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}).
@@
 These species seem to rely on animal pollinators as indicated by their high investment in sizable styles that can help prevent pollen competition (\protect\hyperlink{ref-ashman2013}{Ashman \& Arceo-Gómez, 2013}; \protect\hyperlink{ref-lanuza2021}{Lanuza et al., 2021}; \protect\hyperlink{ref-ramesha2011}{Ramesha et al., 2011}) while having reproductive assurance in their absence.
-Similarly, zygomorphic flowers are specialised floral structures that promote precise pollen transfer {[}sargent2004; \protect\hyperlink{ref-gong2009}{Gong \& Huang} (\protect\hyperlink{ref-gong2009}{2009}){]} but they were associated with high levels of autogamy.
+For instance, the annual herb \emph{Scabiosa atropurpurea} has flowers grouped in clusters with relatively long styles and a single ovule per flower that is likely to be fertilised with a single legitimate floral visit but avoids reproductive failure with autonomous self pollination.
+Similarly, zygomorphic flowers are specialised floral structures that promote precise pollen transfer (\protect\hyperlink{ref-gong2009}{Gong \& Huang, 2009}; \protect\hyperlink{ref-sargent2004}{Sargent, 2004}) but they were associated with high levels of autogamy.
 Our findings are consistent with the idea that reproductive assurance is not rare within specialised pollination systems (\protect\hyperlink{ref-fenster2007}{Fenster \& Marten-Rodriguez, 2007}) and highlight the need to explore the timing (e.g., early versus delayed) and selfing mechanisms (see \protect\hyperlink{ref-goodwillie2018}{Goodwillie \& Weber, 2018}) in relation to other reproductive traits to better understand reproductive trait correlations and plant-pollinator interactions.
 
-Because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and floral visitor guilds could indicate the existence of pollination syndromes (\protect\hyperlink{ref-dellinger2020}{Dellinger, 2020}; \protect\hyperlink{ref-faegri2013}{Faegri \& Van Der Pijl, 2013}; \protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero et al., 2014}).
+Because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and pollinator guilds could indicate the existence of pollination syndromes (\protect\hyperlink{ref-dellinger2020}{Dellinger, 2020}; \protect\hyperlink{ref-faegri2013}{Faegri \& Van Der Pijl, 2013}; \protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero et al., 2014}).
 For instance, bees had a higher number of interacting partners on plant species with large flowers but interacted more frequently with species with small flowers while syrphid flies showed the opposite trend.
 This could be reflective of differences in the ecology and behaviour between these pollinator guilds (\protect\hyperlink{ref-foldesi2021}{Földesi et al., 2021}; \protect\hyperlink{ref-rader2020}{Rader et al., 2020}) that ultimately exert different selective pressures, leading divergent plant reproductive strategies.
-In any case, it is worth noting that local factors (e.g., species relative abundances or phenologies) likely contribute to the variability in the association between the plant reproductive spectrum and floral visitors (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-encinas2012}{Encinas-Viso et al., 2012}; \protect\hyperlink{ref-vazquez2007}{Vázquez et al., 2007}).
+In any case, it is worth noting that local factors (e.g., species relative abundances or phenologies) likely contribute to the variability in the association between the plant reproductive spectrum and pollinators (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-encinas2012}{Encinas-Viso et al., 2012}; \protect\hyperlink{ref-vazquez2007}{Vázquez et al., 2007}).
+Taking both aspects together, we suggest that while plant reproductive traits do shape their interactions with pollinators, pollinator syndromes at a macroecological scale are not distinct compartmentalised items, but form part of a multifaceted context dependent continuum.
 
 Our study provides a comprehensive assessment of reproductive trait covariation patterns in flowering plants, using a global dataset of traits for plant species within plant-pollinator networks.
-We show the importance of floral visitors in mediating reproductive trait correlations and identify the need to consider broader plant reproductive strategies, rather than just flower morphology, to understand patterns of plant-pollinator interactions.
+We show the importance of pollinators in mediating reproductive trait correlations and identify the need to consider broader plant reproductive strategies, rather than just flower morphology, to understand patterns of plant-pollinator interactions.
 Further, we provide empirical evidence of reproductive trait associations that complement trait covariation studies for other plant organs, highlighting the need to include reproductive traits in the global spectrum of plant form and function.
 Future work incorporating underrepresented areas of the world and additional relevant reproductive traits (e.g., flower life span and colour) will be valuable for enhancing our understanding of the plant reproductive spectrum and associated plant-pollinator interactions.
+
+\newpage
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-sargent2004}{}}%
+Sargent, R.
+D.
+(2004).
+Floral symmetry affects speciation rates in angiosperms.
+\emph{Proceedings of the Royal Society of London.
+Series B: Biological Sciences}, \emph{271}(1539), 603--608.
+\url{https://doi.org/10.1098/rspb.2003.2644}
+
 \leavevmode\vadjust pre{\hypertarget{ref-sargent2008}{}}%

### 2022-10-05 Manuscript/Title_Page.tex
Title page and MS update

@@
 
+\textbf{Author for correspondence:} Jose B. Lanuza \textbar{} \href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
+
+\textbf{Acknowledgements.} We thank all researchers that made their data openly available and sent it upon request.
+We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
+We thank Jason Tylianakis for his insightful comments on the manuscript before submission.
+Finally, we thank Marcos Méndez, Susan Kalisz, Amanda Benoit, May Berenbaum and an anonymous reviewer for thoughtful feedback and useful comments on earlier versions of this manuscript.
+
+\textbf{Conflict of interest declaration.} We declare we have no competing interests.
+
+\textbf{Authors' contributions.} JBL, RR and IB designed the study.
+JBL collated the data and conducted analysis with guidance of JS, LKK and IB.
+JBL wrote the manuscript with contributions of all authors.
+
+\textbf{Data accessibility.} All data and code used to conduct this study are available in the online repositories of Zenodo (\url{https://doi.org/10.5281/zenodo.6705621}) and Github (\url{https://github.com/JoseBSL/Reproductive-traits}).
+
 \end{document}

### 2022-10-05 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
Final edits on supp mat

@@
 ---
-#title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Covariation among reproductive traits in flowering plants determine interactions with floral visitors}
+#title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Covariation among reproductive traits in flowering plants shape their interactions with pollinators}
 
@@
 
-## Covariation among reproductive traits in flowering plants determine interactions with floral visitors
+## Covariation among reproductive traits in flowering plants shape their interactions with pollinators
 

### 2023-01-18 Manuscript/Lanuza_et_al_2022.Rmd
Adding symbols to figures of the main text

@@
 
+1.
 Globally, plants display enormous variation in life history strategies and trait combinations.
@@
 Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with pollinators.
-Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
+
+2. Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
+
+3.
 We show that over 50% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the negative correlation between autonomous selfing and floral display size.
@@
 However, reproductive axes explain a relatively small amount of variance in pollinator interactions highlighting the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
-Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping networks of plant-pollinator interactions at a global scale.
+
+4. Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping networks of plant-pollinator interactions at a global scale.
 
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=1, fig.width=14}
-setwd("~/R_Projects/Reproductive Traits")
 
@@
 #load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
+trait_data <- read_excel("../Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
 ########################################################################################################################################################
@@
 
-setwd("~/R_Projects/Reproductive Traits")
-
 #Load libraries
@@
 #Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+dat_cleaning_5 <- readRDS("../Data/RData/data_all_species_PPCA.rds")
+phyl_pca_forest <- readRDS("../Data/RData/phyl_pca_forest.rds")
 
@@
 
-tree <- image_read("Images/PPCA_Plot/Tree.png")
+tree <- image_read("../Images/PPCA_Plot/Tree.png")
 tree_1 <- as.raster(tree)
 
-style_l <- image_read("Images/PPCA_Plot/Style_Long.png")
+style_l <- image_read("../Images/PPCA_Plot/Style_Long.png")
 style_l_1 <- as.raster(style_l)
 
-style_s <- image_read("Images/PPCA_Plot/Style_Short.png")
+style_s <- image_read("../Images/PPCA_Plot/Style_Short.png")
 style_s_1 <- as.raster(style_s)
 
-ovule_h <- image_read("Images/PPCA_Plot/Ovule_High.png")
+ovule_h <- image_read("../Images/PPCA_Plot/Ovule_High.png")
 ovule_h_1 <- as.raster(ovule_h)
 
-ovule_l <- image_read("Images/PPCA_Plot/Ovule_Low.png")
+ovule_l <- image_read("../Images/PPCA_Plot/Ovule_Low.png")
 ovule_l_1 <- as.raster(ovule_l)
 
-selfing_n <- image_read("Images/PPCA_Plot/Selfing_None.png")
+selfing_n <- image_read("../Images/PPCA_Plot/Selfing_None.png")
 selfing_n_1 <- as.raster(selfing_n)
 
-selfing_h <- image_read("Images/PPCA_Plot/selfing.png")
+selfing_h <- image_read("../Images/PPCA_Plot/selfing.png")
 selfing_h_1 <- as.raster(selfing_h)
 
-single_flower <- image_read("Images/PPCA_Plot/Single_Flower.png")
+single_flower <- image_read("../Images/PPCA_Plot/Single_Flower.png")
 single_flower_1 <- as.raster(single_flower)
 
-many_flowers <- image_read("Images/PPCA_Plot/Inflorescencia.png")
+many_flowers <- image_read("../Images/PPCA_Plot/Inflorescencia.png")
 many_flowers_1 <- as.raster(many_flowers)
@@
 
-large_flower <- image_read("Images/PPCA_Plot/flower_big.png")
+large_flower <- image_read("../Images/PPCA_Plot/flower_big.png")
 large_flower_1 <- as.raster(large_flower)
@@
 #"Images/PPCA_Plot/flower_short.png"
-flower_small <- image_read("Images/PPCA_Plot/flower_big.png")
+flower_small <- image_read("../Images/PPCA_Plot/flower_big.png")
 flower_small_1 <- as.raster(flower_small)
 
-herb <- image_read("Images/PPCA_Plot/herb.png")
+herb <- image_read("../Images/PPCA_Plot/herb.png")
 herb_1 <- as.raster(herb)
@@
 
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-
 #Load libraries
@@
 library(cowplot)
+library(ggstar)
 
@@
 #Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+dat_cleaning_5 <- readRDS("../Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
+phyl_pca_forest <- readRDS("../Data/RData/phyl_pca_forest.rds")
 
@@
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Compatibility),size=1.75)+scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7"))
+  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=Compatibility, fill=Compatibility), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("deepskyblue2", "purple2","goldenrod","gray7")) +
+scale_starshape_manual(values = c(13, 15, 28, 5))
 
@@
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Life form`),size=1.75)+scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))
+plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Life form`, fill=`Life form`), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("forestgreen", "darkorange2","black")) +
+scale_starshape_manual(values = c(13, 15, 28))
 
@@
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Lifespan),size=1.75)+scale_color_manual(values=c("sienna4","forestgreen"))
+  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=Lifespan, fill=Lifespan), size=2.25, color= NA, alpha = 0.9)+ scale_fill_manual(values=c("sienna4","forestgreen")) +
+scale_starshape_manual(values = c(13, 15))
 
@@
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower symmetry`),size=1.75)+scale_color_manual(values=c("sienna2","purple"))
+  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Flower symmetry`, fill=`Flower symmetry`), size=2.25, color= NA, alpha = 0.9) + scale_fill_manual(values=c("goldenrod","purple2")) +
+scale_starshape_manual(values = c(13, 15))
 
@@
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Flower shape`),size=1.75)+scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))
+  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Flower shape`, fill=`Flower shape`), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("black","goldenrod", "deepskyblue2","forestgreen","purple2","darkorange2")) +
+scale_starshape_manual(values = c(13, 15, 28, 5, 9, 14))
 
@@
 
-  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=`Breeding system`),size=1.75)+scale_color_manual(values=c("forestgreen","orange", "black"))
+  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Breeding system`, fill=`Breeding system`), size=2.25, color= NA, alpha = 0.9) + scale_fill_manual(values=c("forestgreen","darkorange2", "black")) +
+scale_starshape_manual(values = c(13, 15, 28))
 
@@
 
-setwd("~/R_Projects/Reproductive Traits")
-
-p1 <- readRDS("Main_Figures/figure_3_1.rds")
-p2 <- readRDS("Main_Figures/figure_3_2.rds")
-p3 <- readRDS("Main_Figures/figure_3_3.rds")
-pp1 <- readRDS("Main_Figures/figure_3_4.rds")
-pp2 <- readRDS("Main_Figures/figure_3_5.rds")
-pp3 <- readRDS("Main_Figures/figure_3_6.rds")
+p1 <- readRDS("../Main_Figures/figure_3_1.rds")
+p2 <- readRDS("../Main_Figures/figure_3_2.rds")
+p3 <- readRDS("../Main_Figures/figure_3_3.rds")
+pp1 <- readRDS("../Main_Figures/figure_3_4.rds")
+pp2 <- readRDS("../Main_Figures/figure_3_5.rds")
+pp3 <- readRDS("../Main_Figures/figure_3_6.rds")
 
@@
 
-combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
+combined <- pp1 + pp2 + pp3 + p1 + p2 + p3  & theme(legend.position = "bottom") &  guides(color = guide_legend(override.aes = list(size=6.5), keywidth=1.8,
+                 keyheight=0.1,
+                 default.unit="inch"))
+
 combined + plot_layout(guides = "collect",ncol = 3)
-
 ```

### 2023-01-18 Manuscript/Lanuza_et_al_2022.tex
Adding symbols to figures of the main text

@@
 ]{article}
-\title{\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shape their interactions with pollinators}
-\author{}
-\date{\vspace{-2.5em}}
-
 \usepackage{amsmath,amssymb}
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={ Covariation among reproductive traits in flowering plants shape their interactions with pollinators},
-  colorlinks=true,
-  linkcolor={RoyalBlue},
-  filecolor={Maroon},
-  citecolor={Blue},
-  urlcolor={RoyalBlue},
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={ Covariation among reproductive traits in flowering plants shape their interactions with pollinators},
+  colorlinks=true,
+  linkcolor={RoyalBlue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={RoyalBlue},
+  pdfcreator={LaTeX via pandoc}}
+
+\title{\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shape their interactions with pollinators}
+\author{}
+\date{\vspace{-2.5em}}
 
@@
 
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
   Globally, plants display enormous variation in life history strategies and trait combinations.
@@
 Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with pollinators.
+\item
   Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
+\item
   We show that over 50\% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the negative correlation between autonomous selfing and floral display size.
@@
 However, reproductive axes explain a relatively small amount of variance in pollinator interactions highlighting the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
+\item
   Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping networks of plant-pollinator interactions at a global scale.
+\end{enumerate}
 
@@
 Bruelheide, H., Dengler, J., Purschke, O., Lenoir, J., Jiménez-Alfaro, B., Hennekens, S.
-M., Botta-Dukát, Z., Chytry, M., Field, R., Jansen, F.others.
+M., Botta-Dukát, Z., Chytry, M., Field, R., Jansen, F., et al.
 (2018).
@@
 de, Galetti, M., Guimaraes, P.
-R.others.
+R., et al.
 (2013).
@@
 R., Iversen, C.
-M.others.
+M., et al.
 (2021).

### 2023-01-18 Manuscript/Trial.Rmd
Adding symbols to figures of the main text

--- 2023-01-18 Manuscript/Lanuza_et_al_2022.Rmd
@@
 ---
-title: \singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shape their interactions with pollinators
-
-#author: 
-#  - Jose B. Lanuza^1,2^*
-#  - Romina Rader^1^
-#  - Jamie Stavert^3^
-#  - Liam K. Kendall^4^
-#  - Manu E. Saunders^1^
-#  - Ignasi Bartomeus^2^
-
-# may use lua filters for affiliations etc: see https://stackoverflow.com/a/52919256
-
-# date: '`r Sys.Date()`'
-
-output:
-  bookdown::pdf_document2:
-    fig_caption: yes
-    fig_width: 7
-    fig_height: 7
-    df_print: kable
-    keep_tex: yes
-    number_sections: no
-    extra_dependencies: ["float"]
-    toc: no
-    fig_crop: no
-    includes:
-      in_header: header.tex
-
-documentclass: article
-# classoption: twocolumn, landscape, etc
-papersize: a4
-pagestyle: plain  # plain, empty, headings
-geometry: margin=1in
-linestretch: 2
-fontfamily: mathpazo
-fontsize: 12pt
-
-bibliography: 
-  - references.bib
-  - knitcitations.bib
-# zotero: "My shared Zotero group"
-csl: proceedingsb.csl #ecology letters
-notes-after-punctuation: false
-link-citations: yes
-linkcolor: RoyalBlue
-urlcolor: RoyalBlue
-links-as-notes: false
-subparagraph: yes
-
-header-includes:
-- \usepackage{booktabs}
-- \usepackage{longtable}
-- \usepackage{array}
-- \usepackage{multirow}
-- \usepackage{wrapfig}
-- \usepackage{float}
-- \usepackage{colortbl}
-- \usepackage{tabu}
-- \usepackage{threeparttable}
-- \usepackage{threeparttablex}
-- \usepackage[normalem]{ulem}
-- \usepackage{makecell}
-- \usepackage{xcolor}
-- \usepackage{float}
-- \floatplacement{figure}{H}
-- \usepackage[skip=3pt]{caption}
-- \captionsetup[figure]{labelformat=empty}
-- \usepackage{setspace}
-- \usepackage{titlesec}
-- \titlespacing{\title}{0pt}{\parskip}{-\parskip}
-- \usepackage[style=nature]{biblatex}
-- \usepackage[labelformat = empty]{caption}
-- \usepackage{pdflscape}
-- \usepackage[T1]{fontenc}
-- \DeclareUnicodeCharacter{0301}{*************************************}
-- \DeclareUnicodeCharacter{1EF3}{*************************************}
-- \usepackage{orcidlink}
+output: pdf_document
+classoption: landscape
 ---
-
-```{=tex}
-\doublespacing
-\normalsize
-```
-
-# Abstract
-
-1.
-Globally, plants display enormous variation in life history strategies and trait combinations.
-However, evidence suggests that evolutionary and physiological constraints limit the number of plant ecological strategies.
-Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with pollinators.
-
-2. Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
-
-3.
-We show that over 50% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the negative correlation between autonomous selfing and floral display size.
-In addition, these reproductive axes were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
-However, reproductive axes explain a relatively small amount of variance in pollinator interactions highlighting the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
-
-4. Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping networks of plant-pollinator interactions at a global scale.
-
-\textbf{Keywords:} life-history strategies \| plant reproductive traits \| plant-pollinator interactions
-
-```{=tex}
-\doublespacing
-\vspace{5mm}
-\normalsize
-```
-```{r setup, include=FALSE, cache=FALSE, message = FALSE}
-
-library("knitr")
-
-### Chunk options: see http://yihui.name/knitr/options/ ###
-## Text results
-opts_chunk$set(echo = FALSE, warning = TRUE, message = TRUE)
-
-## Code decoration
-opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)
-
-## Cache
-# opts_chunk$set(cache = 2, cache.path = "output/cache/")
-
-## Plots
-opts_chunk$set(fig.path = "output/figures/")
-
-```
-
-```{r knitcitations, cache = FALSE}
-library(knitcitations)
-cleanbib()   
-cite_options(citation_format = "pandoc")
-
-```
-
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.pos = 'H')
-```
-
-# 1. Introduction
-
-Flowering plants display an astonishing diversity of reproductive structures [@barrett2002; @schiestl2013] that shape their interactions with animal pollinators [@fenster2004; @dellinger2020].
-The variety of reproductive strategies used by different plant species, from specialised reliance on a single pollinator, to full self-pollination, is incredibly rich.
-However, not all reproductive trait combinations in plants are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
-Despite recent advances in theoretical and empirical understanding of correlations between plant reproductive traits at large ecological scales [@salguero2016; @friedman2020; @paterno2020; @roddy2021; @song2022], studies typically focus on just a few traits, often in isolation.
-Thus, to develop a comprehensive understanding of the plant reproductive spectrum of trait variation, as done recently for root [@laughlin2021], leaf [@wright2004] and wood [@chave2009] related traits, we require a multi-trait perspective with broad geographical coverage.
-Importantly, characterization of the plant reproductive spectrum could reveal key reproductive strategies among different species [@agrawal2020] and improve knowledge of associations between specific reproductive traits and pollinators [@roddy2021].
-
-With the recent availability of large trait databases [e.g., TRY @kattge2011;  COMPADRE @salguero2015], there has been increased research on plant ecological strategies, which has produced identification of global patterns in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
-However, studies that look at multiple traits tend to overlook plant reproductive traits [@evojtko2020; @ruger2018; @roddy2021], and focus on trait correlations in other plant organs such as morphological and physiological leaf traits [@wright2004; @shipley2006; @donovan2011; @osnas2013].
-Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs such as the negative correlation between flower size and flower number [@sargent2007; @kettle2011; @vojtko2022]; the positive association between flower size and outcrossing rate [@goodwillie2010]; or the positive correlation between outcrossing rate and lifespan [@barrett2003; @munoz2016; @moeller2017].
-Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships [@roddy2021], we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
-
-Trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] are powerful for exploring the underlying mechanisms driving plant-pollinator interactions.
-For example, plant traits can define species' network roles [e.g., specialists vs generalists @tur2013] and plant species that occupy reproductive trait space extremes are likely to be more specialised and display tighter trait-matching with pollinators [@junker2013; @coux2016].
-Indeed, the degree of morphological matching between plants and pollinators often determines whether or not interactions occur, and consequently influences  the broader network structure [@stang2009; @ibanez2012].
-However, it is still unclear how specific reproductive traits (e.g., mating or compatibility system) influence plant-pollinator associations [@sargent2008; @tur2013; @devaux2014].
-For example, species with high selfing rates may evolve to invest less in floral rewards resulting in a lower number of pollinator visits [@devaux2014].
-Indeed, both morphology and mating system can determine a species' functional role within pollination networks, and the combination of several traits increases power for predicting network structure [@eklof2013].
-Because the species position within the multidimensional trait space can result in different interaction patterns or adaptations to pollinators [see @dehling2016 for a purely morphological approach], the use of the reproductive trait space to explore plant-pollinator interactions could help to identify species functional roles and associations of traits with specific pollinators (i.e., pollination syndromes).
-
-Here, we explore the spectrum of reproductive traits in flowering plants, within a global set of plant-pollinator networks, to identify reproductive trait covariation and how this influences the network of interactions between plants and pollinators.
-First, we identify the major axes of reproductive trait variation and correlations among traits for plant species.
-Then, we investigate the associations between plant species’ positions in reproductive trait space and the strength of their interactions with different pollinator guilds within networks.
-Finally, we determine how the main axes of reproductive trait variation influence plant species' functional roles within pollination networks, using a range of complementary interaction network metrics.
-
-# 2. Methods
-
-## (a) Plant-pollinator network studies
-
-We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see table S1 and figure S1).
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different ecological communities.
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to benefit, to some degree, from animal pollination.
-Many of these networks are freely available either as published studies [e.g., @carvalheiro2014; @olesen2007; @fortuna2010] or in online archives [e.g., Mangal @poisot2016;  The Web of Life @fortuna2010].
-In total, our network dataset constituted 60 weighted (number of visits) and four unweighted (interaction presence-absence) networks, each sampled at a unique location and year, as well as eight meta-networks where interactions were pooled across several locations and multiple years.
-
-## (b) Taxonomy of plants and pollinators
-
-All species names, genera, families and orders were retrieved and standardised from the taxonomy data sources NCBI (<https://www.ncbi.nlm.nih.gov/taxonomy>) for plants and ITIS (<https://www.itis.gov/>) for pollinators, using the R package *taxize* [@chamberlain2020].
-We filled the 'not found' searches manually using <http://www.theplantlist.org/> and <http://www.mobot.org/> for plants and <http://www.catalogueoflife.org/> for pollinators.
-
-## (c) Plant traits
-
-We selected a total of 19 quantitative and categorical functional traits that included reproductive traits and traits related with plant form and size (see table 1).
-Reproductive traits consisted of those related to floral and reproductive biology: (i) floral traits included those related to the size of floral organs (e.g., style length), floral display size (e.g., flower number) and floral rewards (e.g., pollen quantity), while (ii) reproductive biology traits represented the plant reproductive system (i.e., the breeding, mating and compatibility system).
-The remaining traits were related to plant size and form (i.e., plant height, lifespan and life form), which are commonly used to characterise the fast-slow continuum of plant trait variation [@salguero2016].
-For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
-From a matrix comprising a total of 28,614 possible cells (considering all traits and plant species: 19 columns × 1,506 species), we were able to fill 23,354 cells (81.6% of the dataset, see figure S2 for missing value information for each trait).
-An extended description of each trait and how it was obtained can be found in Appendix S1.
-
-\singlespacing
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=1, fig.width=14}
-
-library(kableExtra)
-
-library(dplyr)
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("../Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant","Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Floral_unit_width",
-         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
-         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-n_of_records <- subset(missing.values, isna=="FALSE")
-
-Trait <- c("Plant height", "Flower width", "Flower length", "Inflorescence width", "Style length", "Ovules per flower",
-           "Flowers per plant", "Microliters of nectar", "Milligrams of nectar", "Nectar concentration", "Pollen grains per flower", "Autonomous selfing (fruit set)")
-
-Trait1 <- linebreak(c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Compatibility system", "Breeding system"),align = c("l"))
-
-#T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub #\n Tree", "Brush \n Campanulate \n Capitulum \n Open \n #Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-#           "Presence \n Absence", "Self-incomp. \n Part. #self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n #Dioecious"),align = c("l"))
-#
-T.cat <- linebreak(c("Short-lived and perennial", "Herb, shrub and tree", "Brush, campanulate, capitulum,\n open, papilionaceous and tube",  "Actinomorphic and zygomorphic",
-           "Presence and absence", "Self-incompatible, partially self-compabtile \n and self-compatible", "Hermaphrodite, monoecious and dioecious"), align = c("l"))
-
-Number_of_records_quantitative <- c(n_of_records$num.isna[n_of_records$key=="Plant_height_mean_m"], n_of_records$num.isna[n_of_records$key=="Corolla_diameter_mean"],
-  n_of_records$num.isna[n_of_records$key=="Corolla_length_mean"], n_of_records$num.isna[n_of_records$key=="Floral_unit_width"],
-  n_of_records$num.isna[n_of_records$key=="Style_length"], n_of_records$num.isna[n_of_records$key=="Ovule_number"],
-  n_of_records$num.isna[n_of_records$key=="Flowers_per_plant"], n_of_records$num.isna[n_of_records$key=="Nectar_ul"],
-  n_of_records$num.isna[n_of_records$key=="Nectar_mg"], n_of_records$num.isna[n_of_records$key=="Nectar_concentration"], n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
-  n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level_fruit_set"])
-
-Number_of_records_categorical <- c(n_of_records$num.isna[n_of_records$key=="lifespan"], n_of_records$num.isna[n_of_records$key=="life_form"],
-                                   n_of_records$num.isna[n_of_records$key=="Flower_morphology"], n_of_records$num.isna[n_of_records$key=="Flower_symmetry"],
-                                   n_of_records$num.isna[n_of_records$key=="Nectar_presence_absence"], n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level"],
-                                   n_of_records$num.isna[n_of_records$key=="Compatibility_system"], n_of_records$num.isna[n_of_records$key=="Breeding_system"],
-                                   rep("",4))
-
-T.range <- c("0.01-30m", "0.50-205mm", "0.20-195mm", "0.80-300mm", "0-138mm", "1-25000", "1-1.8 x $10^5$", "0-160$\\mu$l", "0-6.1mg", "0-100$\\%$", "13-2 x $10^8$", "0-100$\\%$")
-
-dat_1 <- data.frame(Trait,T.range)
-dat_2 <- data.frame(Trait1, T.cat)
-
-colnames(dat_1) <- c("Quantitative traits", "Numerical range")
-colnames(dat_2) <- c("Categorical traits", "Categories")
-
-#kable(list(dat_1, dat_2), booktabs = T, linesep = #"\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1 | #Quantitative and categorical traits used in this study.}") %>%
-#  kable_styling(full_width = F,font_size = 10) %>%  #column_spec(1:4, 
-#              width = "3in", 
-#              latex_valign = "m")
-#
-#
-
-colnames(dat_1) <- c("Traits", "Numerical range/Categories")
-colnames(dat_2) <- c("Traits", "Numerical range/Categories")
-
-d <- rbind(dat_1,dat_2)
-
-kable(d, booktabs = T, linesep = "\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1.} Quantitative and categorical traits used in this study.") %>%
-  kable_styling(full_width = F,font_size = 12) %>% row_spec(0, bold=T) %>% pack_rows("Quantitative", 1, 12) %>%
-pack_rows("Categorical", 13, 19)
-
-```
-
-\doublespacing
-
-## (d) Phylogenetic Distance
-
-We calculated the phylogenetic distance between all plant species considered using the function *get_tree* from the package *rtrees* (<https://github.com/daijiang/rtrees>), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
-
-## (e) Data Imputation
-
-To avoid excluding species with trait missing values, we imputed trait missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors from principal component analysis of the phylogenetic distance (PCoA), which has been shown to improve the performance of *missForest* [@penone2014].
-To extract the eigenvectors, we used the function *PVRdecomp* from the package *PVR* [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-We conducted two different imputations, one for the full set of species (1,506 species: 5.79% of missing values), and excluding nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and results for the two datasets were consistent (Fig S3 and Fig S4).
-
-## (f) Plant strategies analysis
-
-We explored the association between the different quantitative plant traits using a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasise flower size on the spectrum of trait variation.
-Prior to the analyses, we excluded outliers and standardised the data.
-Specifically, due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis [@legendre2012].
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
-We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode “covariance” because values for each variables were on the same scale following transformation [@abdi2010].
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity data.
-For this, we included all quantitative traits included in the main pPCA, plus pollen grains and microlitres of nectar per flower.
-
-## (g) Phylogenetic signal
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package *phytools* [@revell2012] and used Pagel's $\lambda$ as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-## (h) Network analyses
-
-### (i) Visitation patterns
-
-We used Bayesian modelling (see details below) to investigate how the different guilds of pollinators interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
-Specifically, interactions between plants and pollinators in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
-Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species [@ballantyne2015], the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination [@vazquez2005; @vazquez2012].
-Therefore, despite the fact that we do not evaluate pollinator effectiveness we refer to the different floral visitors as pollinators.
-
-We divided pollinators into six main taxonomical guilds that differ in life form, behaviour and thus likely play different ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
-Moreover, because bees had the greatest number of occurrences in networks  (2,256 records) and the highest frequency of visits, we further broke this group down into the main bee families (Andrenidae, Apidae, Colletidae, Halictidae, and Megachilidae).
-In addition, we found that *Apis mellifera* was the pollinator with the largest proportion of occurrences in networks (7.55% of the total).
-This is consistent with previous research showing that *A.
-mellifera* was the most frequent pollinator in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
-Hence, to control for the effect of *A.
-mellifera* on observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding *A.
-mellifera*.
-We found that *A.
-mellifera*, was partly driving some of the observed trends on PC1 (figure S5).
-However, we did not detect major differences on PC2 and PC3.
-
-We used Bayesian generalised linear mixed models in the R package *brms* [@burkner2017] to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with pollinator guilds (e.g., number of visits \~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
-Because we were interested in possible differences in visitation patterns among pollinator guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different pollinator guilds in the model.
-We added a nested random effect of networks within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence among them.
-We specified for the presence or absence of an interaction and number of visits with Bernoulli and a zero inflated negative binomial distributions, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results [@burkner2017].
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualised the posterior predictive checks with the function *pp_check* using the *bayesplot* package [@gabry2019].
-
-### (ii) Plant species network roles
-
-We also used Bayesian modelling to investigate how the main axes of trait variation determined different plant species' functional roles within pollination networks.
-For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies [@dormann2008], with clear ecological interpretations and are relevant for defining species' functional roles in networks.
-Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalised degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) selectivity (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalisation) and 1 (maximum specialisation).
-Normalised degree and selectivity were calculated with the *specieslevel* function in the R package *bipartite* [@dormann2008].
-We modelled each plant species metric (sum of visits, normalised degree and plant selectivity) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
-For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalised degree, and zero-one inflated beta for selectivity).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the 'visitation patterns' section.
-
-Our analyses were conducted on the subset of 60 weighted networks (out of a total of 64 networks) sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our network dataset (excluding meta- and non-weighted networks) included 2,256 interactions for bees, 1,768 for non-syrphid-dipterans, 845 for syrphids, 437 for lepidopterans, 432 for coleopterans, and 362 for non-bee-hymenopterans.
-Sampling methods varied across studies but this was accounted for in analyses by including study identity as a  random effect in our models.
-All analyses were conducted in R version *4.0.3*.
-
-# 3. Results
-
-## (a) Plant strategies analysis
-
-Our phylogenetically informed principal component analysis captured  51.8% and 70.97% of the reproductive trait variation in the first two and three axes, respectively (figure 1 and figure S6).
-The first principal component (PC1; the flower number - flower size axis) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; table S3) but style length also contributed moderately (loading = -0.33).
-One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-For instance, *Cornus florida* occurred at this end of the spectrum, which, on average, has approximately 10,000 flowers, is 7.5 m high, has flowers that are 3 mm wide, styles 3.5 mm long and  two ovules per flower.
-The other end of this spectrum had species that were short in height, with few large flowers that had long styles and many ovules.
-For example, *Petunia axillaris* on average, is 0.5 m high and has approximately 10 flowers per plant that are over 50 mm wide with 25 mm long styles and over 200 ovules.
-The second principal component (PC2; the autonomous selfing - floral display axis) encompassed 25.05% of the trait variation and represented variation from low to high autonomous selfing (i.e., high to low pollinator dependence).
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but all other traits (except ovule number) made moderate contributions (loadings ranging between 0.27 to 0.4; table S3).
-Generally speaking, species with low autonomous selfing had larger and many flowers with long styles, and were tall.
-*Zuccagnia punctata* occurred at this extreme of the spectrum, which is a self-incompatible species, completely dependent on animal pollination for seed production, producing  approximately 1,500 flowers per plant with an average height of 3 m and 20 mm long styles.
-In contrast, species with high autonomous selfing tended to have fewer and smaller flowers with shorter styles, and were shorter in height.
-*Veronica peregrina* occurred at this end of the spectrum, and is a self-compatible plant that requires little or no pollination by animals, it has approximately 20 flowers per plant, is 0.2 m high and has 0.25 mm long styles.
-The third principal component (PC3; the style length - autonomous selfing axis) explained a considerable amount of trait variability (19.17%) and represented a positive correlation between style length (loading = -0.66) and autonomous selfing (loading = \|-0.51\|), where species with short styles had low autonomous selfing and species with long styles high autonomous selfing.
-The remaining traits, apart from ovule number, were all positively correlated with style length and autonomous selfing (loadings from -0.23 to -0.46; table S3).
-In addition, the pPCA with the subset of species that we had nectar and pollen quantity data for showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with floral display size.
-Floral rewards were particularly strongly correlated with flower size but weakly correlated with flower number (figure S4).
-The first two principal components for this pPCA explained similar variance  (45.52%) and similar associations of traits, despite some variability in the loadings (table S4).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="85%", fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
-The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
-The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation.
-The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}
-
-#Load libraries
-library(viridis) #COLOUR GGPLOT
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(magick)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("../Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("../Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#Images were made by Paula Martin
-#Check her work on https://paulamartinart.com/
-
-tree <- image_read("../Images/PPCA_Plot/Tree.png")
-tree_1 <- as.raster(tree)
-
-style_l <- image_read("../Images/PPCA_Plot/Style_Long.png")
-style_l_1 <- as.raster(style_l)
-
-style_s <- image_read("../Images/PPCA_Plot/Style_Short.png")
-style_s_1 <- as.raster(style_s)
-
-ovule_h <- image_read("../Images/PPCA_Plot/Ovule_High.png")
-ovule_h_1 <- as.raster(ovule_h)
-
-ovule_l <- image_read("../Images/PPCA_Plot/Ovule_Low.png")
-ovule_l_1 <- as.raster(ovule_l)
-
-selfing_n <- image_read("../Images/PPCA_Plot/Selfing_None.png")
-selfing_n_1 <- as.raster(selfing_n)
-
-selfing_h <- image_read("../Images/PPCA_Plot/selfing.png")
-selfing_h_1 <- as.raster(selfing_h)
-
-single_flower <- image_read("../Images/PPCA_Plot/Single_Flower.png")
-single_flower_1 <- as.raster(single_flower)
-
-many_flowers <- image_read("../Images/PPCA_Plot/Inflorescencia.png")
-many_flowers_1 <- as.raster(many_flowers)
-#many_flowers_1 <- image_rotate(many_flowers, 45)
-
-large_flower <- image_read("../Images/PPCA_Plot/flower_big.png")
-large_flower_1 <- as.raster(large_flower)
-
-#"Images/PPCA_Plot/flower_short.png"
-flower_small <- image_read("../Images/PPCA_Plot/flower_big.png")
-flower_small_1 <- as.raster(flower_small)
-
-herb <- image_read("../Images/PPCA_Plot/herb.png")
-herb_1 <- as.raster(herb)
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Autonomous selfing - Floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
-    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
-    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
-    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.18, xmax = 4.13,ymin = 1.3, ymax = 2.4) +
-    annotation_raster(flower_small_1, xmin = -3.21, xmax = -2.81,ymin = -2, ymax = -1.45) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
-
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
-                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-plot_grid(all_spp(PC))
-
-```
-
-We found that most categorical traits were statistically associated with the first two axes of trait variation (figure 2 and table S2).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed a lack of statistical association.
-In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S7).
-Regarding self-compatibility, we found larger differences on PC2.
-For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S7a and figure S7b; Tukey test *P* \< 0.05).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S7c and figure S7d; Tukey test *P* \< 0.05).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f; Tukey test *P* \< 0.05).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S7g and figure S7h; Tukey test *P* \< 0.05).
-Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S7i and figure S7j; Tukey test *P* \< 0.05).
-Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S7k and figure S7l; Tukey test *P* \< 0.05).
-
-\blandscape
 
@@
 ```
-
-\elandscape
-
-## (b) Phylogenetic signal
-
-We found a strong phylogenetic signal (*P* \< 0.01) for most quantitative traits (table S5).
-The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
-The traits that had a moderate phylogenetic signal included inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all the traits we measured ($\lambda$ = 0.14).
-
-## (c) Visitation patterns
-
-The main axes of trait variation (PC1, PC2 and PC3) partly explained the presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the total number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant differences across the different pollinator guilds for both the presence-absence of interactions and number of visits (figure 3).
-On the flower number - flower size axis, we found  that plants with many small flowers tended to have interaction partners that were Coleoptera, non-bee-Hymenoptera and Diptera (figure 3a), whereas plants with few large flowers mostly had interaction partners that were bees and Lepidoptera.
-We found similar trends for visitation rates on the flower number - flower size axis,  but bees and syrphids visited plant species with many small flowers more frequently (figure 3d).
-On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and recieved many visits from all pollinator guilds (figure 3b and figure 3e).
-Finally, on the style length - autonomous selfing axis, plant species with short styles and low autonomous selfing had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and high autonomous selfing (figure 3c).
-Plants with long styles and high autonomous selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera (figure 3f).
-
-The additional models for the most represented bee families, for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and the number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03), showed that the Apidae family was the main driver of the observed patterns.
-The contrast between interaction presence/absence  and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S8).
-
-```{=tex}
-\vspace{5mm}
-\blandscape
-```
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different pollinator guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
-PC1 represents the flower number - flower size axis, PC2 represents the autonomous selfing - floral display axis and PC3 represents the style length - autonomous selfing axis.
-For visualization purposes due to large differences between number of visits from bees and the rest of the pollinator guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
-
-#LOAD LIBRARIES 
-#library(phytools)
-#library(ape) #for phylogenetic distance
-#library(dplyr) #data processing
-#library(rtrees) #for phylogenetic distancelibrary(MASS)
-#library(reshape2)
-library(viridis) #COLOUR GGPLOT
-#library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-#library(tidyverse)
-library(patchwork) #panel of plots
-#library(brms)
-#library(cmdstanr)
-
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2)),
-           axis.text=element_text(size = rel(1.8), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(2, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
-           plot.subtitle = element_text(face="bold",size=rel(2))
-     ))
-}
-
-p1 <- readRDS("../Main_Figures/figure_3_1.rds")
-p2 <- readRDS("../Main_Figures/figure_3_2.rds")
-p3 <- readRDS("../Main_Figures/figure_3_3.rds")
-pp1 <- readRDS("../Main_Figures/figure_3_4.rds")
-pp2 <- readRDS("../Main_Figures/figure_3_5.rds")
-pp3 <- readRDS("../Main_Figures/figure_3_6.rds")
-
-library(patchwork)
-
-combined <- pp1 + pp2 + pp3 + p1 + p2 + p3  & theme(legend.position = "bottom") &  guides(color = guide_legend(override.aes = list(size=6.5), keywidth=1.8,
-                 keyheight=0.1,
-                 default.unit="inch"))
-
-combined + plot_layout(guides = "collect",ncol = 3)
-```
-
-\elandscape
-
-## (d) Plant species network roles
-
-Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalised degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, selectivity \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and selectivity.
-On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
-However, selectivity (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
-On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S9c).
-Again, selectivity showed the opposite trend to the number of visits (figure S9i).
-
-# 4. Discussion
-
-We found strong covariation among traits within the flowering plant reproductive spectrum, which shapes interactions with pollinators at a global scale.
-Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50% and 70% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, autonomous selfing and floral display, and style length and autonomous selfing.
-Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits [@diaz2016; @carmona2021], our results align with the two largest and most recent studies of plant life strategies that included reproductive, form and size related traits [@salguero2016; @vojtko2022].
-The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
-However, the unexplained variability found highlights the need to account for other local factors, such as species relative abundances [@bartomeus2016], along with reproductive traits, to better explain plant-pollinator associations.
-
-Our study provides strong evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1,200 species).
-Specifically, by using a multitrait approach, we are able to link the reproductive spectrum of plant trait variation with the previously described “fast-slow continuum” in plant [@salguero2016] and animal [@healy2019] life-history strategies.
-This fast-slow continuum was illustrated by the associations between reproductive traits and plant height, life form and lifespan traits.
-For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred Angiosperm species and generally lacking a multitrait perspective.
-We found support for this trait association and show that other reproductive traits (e.g., style length or ovule number) covary along this flower number - flower size axis.
-Our study also complements previous work linking plant breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers also have woody life forms and many flowers.
-Moreover, we identify the previously documented positive association between outcrossing rate and floral display size [@goodwillie2010], where species with low autonomous selfing levels also allocate large resource quantities to attract pollinators.
-
-Although we did not include floral rewards in our main analysis due to insufficient data, we did find that plant species with large floral displays and, in particular, large flowers, tended to have higher pollen and nectar quantity.
-Thus, we demonstrate that globally, reproductive trait covariation in flowering plants likely imposes constraints on the broader spectrum of plant trait variation.
-
-Overall, plant reproductive traits explained interaction patterns among and within pollinator guilds suggesting that plant reproductive strategies partly mediate these associations across spatial large scales.
-For example, we found that all pollinator guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
-As predicted by evolutionary life-history theory [@stebbins1970], larger investment in floral display and rewards to attract pollinators occurs when pollinator dependence is high.
-Indeed, the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different pollinator guilds [@galen1999].
-For instance, smaller flowers are visited less overall, but they are inexpensive to produce (e.g., have a low ovule number) and low visitation rate at the individual flower level can be compensated by overall visitation at the plant level by producing many flowers resulting in a larger quantity of small fruits [@kettle2011].
-In addition, we found that a substantial number of species with high autonomous selfing had large styles and were associated with a high number of interactions with bees.
-These species seem to rely on animal pollinators as indicated by their high investment in sizable styles that can help prevent pollen competition [@ramesha2011; @ashman2013; @lanuza2021] while having reproductive assurance in their absence.
-For instance, the annual herb _Scabiosa atropurpurea_ has flowers grouped in clusters with relatively long styles and a single ovule per flower that is likely to be fertilised with a single legitimate floral visit but avoids reproductive failure with autonomous self pollination.
-Similarly, zygomorphic flowers are specialised floral structures that promote precise pollen transfer [@sargent2004; @gong2009] but they were associated with high levels of autogamy.
-Our findings are consistent with the idea that reproductive assurance is not rare within specialised pollination systems [@fenster2007] and highlight the need to explore the timing (e.g., early versus delayed) and selfing mechanisms [see @goodwillie2018] in relation to other reproductive traits to better understand reproductive trait correlations and plant-pollinator interactions.
-
-Because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and pollinator guilds could indicate the existence of pollination syndromes [@fenster2004; @faegri2013; @rosas2014; @dellinger2020].
-For instance, bees had a higher number of interacting partners on plant species with large flowers but interacted more frequently with species with small flowers while syrphid flies showed the opposite trend.
-This could be reflective of differences in the ecology and behaviour between these pollinator guilds [@rader2020; @foldesi2021] that ultimately exert different selective pressures, leading divergent plant reproductive strategies.
-In any case, it is worth noting that local factors (e.g., species relative abundances or phenologies) likely contribute to the variability in the association between the plant reproductive spectrum and pollinators [@vazquez2007; @encinas2012; @bartomeus2016].
-Taking both aspects together, we suggest that while plant reproductive traits do shape their interactions with pollinators, pollinator syndromes at a macroecological scale are not distinct compartmentalised items, but form part of a multifaceted context dependent continuum.
-
-Our study provides a comprehensive assessment of  reproductive trait covariation patterns in flowering plants, using a global dataset of traits for plant species within plant-pollinator networks.
-We show the importance of pollinators in mediating reproductive trait correlations and identify the need to consider broader plant reproductive strategies, rather than just flower morphology, to understand patterns of plant-pollinator interactions.
-Further, we provide empirical evidence of reproductive trait associations that complement trait covariation studies for other plant organs, highlighting the need to include reproductive traits in the global spectrum of plant form and function.
-Future work incorporating underrepresented areas of the world and additional relevant reproductive traits (e.g., flower life span and colour) will be valuable for enhancing our understanding of the plant reproductive spectrum and associated plant-pollinator interactions.
-
-\newpage
-
-# References
-
-::: {#refs}
-:::

### 2023-01-31 Manuscript/Lanuza_et_al_2022.Rmd
Adding more context about the plant and pollinators of our study.

@@
 These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different ecological communities.
+The pollinators documented by these studies are primarily insect pollinators and the plants are characterised by a clear dominance of smaller life forms (i.e., 61% of herbs, 28% of shrubs and 11% of trees).
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to benefit, to some degree, from animal pollination.
@@
 
-We used Bayesian generalised linear mixed models in the R package *brms* [@burkner2017] to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with pollinator guilds (e.g., number of visits \~ PC1 x FGs + PC2 x FGs + PC3 x FGs).
+We used Bayesian generalised linear mixed models in the R package *brms* [@burkner2017] to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation (i.e., PC) and their interactions with pollinator guilds (i.e., PGs; e.g., number of visits \~ PC1 x PGs + PC2 x PGs + PC3 x PGs).
 Because we were interested in possible differences in visitation patterns among pollinator guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different pollinator guilds in the model.
@@
 Further, we provide empirical evidence of reproductive trait associations that complement trait covariation studies for other plant organs, highlighting the need to include reproductive traits in the global spectrum of plant form and function.
-Future work incorporating underrepresented areas of the world and additional relevant reproductive traits (e.g., flower life span and colour) will be valuable for enhancing our understanding of the plant reproductive spectrum and associated plant-pollinator interactions.
+Future work incorporating underrepresented areas of the world and additional relevant reproductive traits (e.g., flower life span and colour) from a broader range of life forms will be valuable for enhancing our understanding of the plant reproductive spectrum and associated plant-pollinator interactions.
 

### 2023-01-31 Manuscript/Lanuza_et_al_2022.tex
Adding more context about the plant and pollinators of our study.

@@
 These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different ecological communities.
+The pollinators documented by these studies are primarily insect pollinators and the plants are characterised by a clear dominance of smaller life forms (i.e., 61\% of herbs, 28\% of shrubs and 11\% of trees).
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to benefit, to some degree, from animal pollination.
@@
 
-We used Bayesian generalised linear mixed models in the R package \emph{brms} (\protect\hyperlink{ref-burkner2017}{Bürkner, 2017}) to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation and their interactions with pollinator guilds (e.g., number of visits \textasciitilde{} PC1 x FGs + PC2 x FGs + PC3 x FGs).
+We used Bayesian generalised linear mixed models in the R package \emph{brms} (\protect\hyperlink{ref-burkner2017}{Bürkner, 2017}) to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation (i.e., PC) and their interactions with pollinator guilds (i.e., PGs; e.g., number of visits \textasciitilde{} PC1 x PGs + PC2 x PGs + PC3 x PGs).
 Because we were interested in possible differences in visitation patterns among pollinator guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different pollinator guilds in the model.

### 2023-02-01 Manuscript/Lanuza_et_al_2022.Rmd
Edits

@@
 These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different ecological communities.
-The pollinators documented by these studies are primarily insect pollinators and the plants are characterised by a clear dominance of smaller life forms (i.e., 61% of herbs, 28% of shrubs and 11% of trees).
+The pollinators documented by these studies are primarily insect pollinators (97.8% of the total visits recorded) and the plants are characterised by a clear dominance of smaller life forms (i.e., 61% of herbs, 28% of shrubs and 11% of trees).
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to benefit, to some degree, from animal pollination.
@@
 Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis [@legendre2012].
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated their position in the trait space and the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
 We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode “covariance” because values for each variables were on the same scale following transformation [@abdi2010].
@@
 We divided pollinators into six main taxonomical guilds that differ in life form, behaviour and thus likely play different ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
+Note that we excluded non-insect pollinators from our analyses as they comprised only a 2.2% of the total visits recorded in our set of studies.
 Moreover, because bees had the greatest number of occurrences in networks  (2,256 records) and the highest frequency of visits, we further broke this group down into the main bee families (Andrenidae, Apidae, Colletidae, Halictidae, and Megachilidae).
@@
 
-We found that most categorical traits were statistically associated with the first two axes of trait variation (figure 2 and table S2).
+As expected, due to individual trait correlations between qualitative and quantitative traits (e.g., life form and plant height), we found that most categorical traits were clustered on the trait space and statistically associated with the first two axes of trait variation (figure s2 and table s2).
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed a lack of statistical association.

### 2023-02-01 Manuscript/Lanuza_et_al_2022.tex
Edits

@@
 These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different ecological communities.
-The pollinators documented by these studies are primarily insect pollinators and the plants are characterised by a clear dominance of smaller life forms (i.e., 61\% of herbs, 28\% of shrubs and 11\% of trees).
+The pollinators documented by these studies are primarily insect pollinators (97.8\% of the total visits recorded) and the plants are characterised by a clear dominance of smaller life forms (i.e., 61\% of herbs, 28\% of shrubs and 11\% of trees).
 Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to benefit, to some degree, from animal pollination.
@@
 Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}).
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
+Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated their position in the trait space and the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
 We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell, 2012}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode ``covariance'' because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams, 2010}).
@@
 We divided pollinators into six main taxonomical guilds that differ in life form, behaviour and thus likely play different ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
+Note that we excluded non-insect pollinators from our analyses as they comprised only a 2.2\% of the total visits recorded in our set of studies.
 Moreover, because bees had the greatest number of occurrences in networks (2,256 records) and the highest frequency of visits, we further broke this group down into the main bee families (Andrenidae, Apidae, Colletidae, Halictidae, and Megachilidae).
@@
 
-We found that most categorical traits were statistically associated with the first two axes of trait variation (figure 2 and table S2).
+As expected, due to individual trait correlations between qualitative and quantitative traits (e.g., life form and plant height), we found that most categorical traits were clustered on the trait space and statistically associated with the first two axes of trait variation (figure s2 and table s2).
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed a lack of statistical association.

### 2023-02-01 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
Edits

@@
 - Nectar provision: We recorded the presence and absence of nectar for all species.
-In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration.
+In addition, we also searched for microlitres and milligrams of nectar per flower.
 For species that did not have nectar information but belonged to a family that is considered as ‘nectarless’, this trait was recorded at family level and the species was recorded with ‘absence’ of nectar.
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = "left"}
-setwd("~/R_Projects/Reproductive Traits")
+setwd("~/R_Projects/Reproductive-Traits")
 library(kableExtra)
@@
 
-setwd("~/R_Projects/Reproductive Traits")
-
-d <- readRDS("Data/RData/table_categorical_tukey_test.rds")
+d <- readRDS("../Data/RData/table_categorical_tukey_test.rds")
 
@@
 
-setwd("~/R_Projects/Reproductive Traits")
+setwd("~/R_Projects/Reproductive-Traits")
 
@@
 #Set working directory
-setwd("~/R_Projects/Reproductive Traits")
+setwd("~/R_Projects/Reproductive-Traits")
 
@@
 Panel A shows the reproductive spectrum of trait variation for the dataset with data imputation and panel B shows the reproductive spectrum for the dataset excluding species with missing trait data"}
-setwd("~/R_Projects/Reproductive Traits")
+setwd("~/R_Projects/Reproductive-Traits")
 
@@
 
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
 #This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
 
-plot_apis <- readRDS("Plot_apis_non_apis.rds")
+plot_apis <- readRDS("../Data/RData/Plot_apis_non_apis.rds")
 
@@
 S6.} Phylogenetically informed principal component analysis (pPCA) for all plant species with the first (flower number - flower size axis) and third (style length - autonomous selfing) principal component that explained most trait variation."}
-setwd("~/R_Projects/Reproductive Traits")
+setwd("~/R_Projects/Reproductive-Traits")
 
@@
 ########################################################################################################################################################
-setwd("~/R_Projects/Reproductive Traits")
 
 #LOAD DATA
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-dat <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
+phyl_pca_forest <- readRDS("../Data/RData/phyl_pca_forest.rds")
+dat <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
 ########################################################################################################################################################
@@
 
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
 #This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
 
-plot <- readRDS("Plot_bee_families.rds")
+plot <- readRDS("../Data/RData/Plot_bee_families.rds")
 
@@
 
-setwd("~/Dropbox/PhD/R/Chapter_2")
-
 #read plot generated in other rmd, bms and stan are giving trouble here... This file is created in Species_Level_Metric_Pcs
 
-plot_metrics_pcs <- readRDS("plot_metrics_pcs.rds")
+plot_metrics_pcs <- readRDS("../Data/RData/plot_metrics_pcs.rds")
 

### 2023-02-01 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.tex
Edits

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage{float}
\usepackage{caption}
\usepackage{setspace}\doublespacing
\usepackage{soul}
\floatplacement{figure}{H}
\usepackage{afterpage}
\usepackage{placeins}
\usepackage{graphicx}
\usepackage{floatpag}
\usepackage{float}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{\vspace{-2.5em}}

\begin{document}

\captionsetup[figure]{labelformat=empty}
\captionsetup[table]{labelformat=empty}
\captionsetup[table]{font={stretch=1.2}}

\singlespacing

\vspace{2cm}

\hypertarget{supplementary-information-for}{%
\section{Supplementary information
for:}\label{supplementary-information-for}}

\hypertarget{covariation-among-reproductive-traits-in-flowering-plants-shape-their-interactions-with-pollinators}{%
\subsection{Covariation among reproductive traits in flowering plants
shape their interactions with
pollinators}\label{covariation-among-reproductive-traits-in-flowering-plants-shape-their-interactions-with-pollinators}}

\textbf{Jose B. Lanuza*, Romina Rader, Jamie Stavert, Liam K. Kendall, Manu E. Saunders and Ignasi Bartomeus}

\textbf{*Corresponding author} \textbf{E-mail:
\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}}

\textbf{This pdf includes:}

Appendix S1 (text)

Tables S1 to S5

Figures S1 to S9

\doublespacing

\newpage

\hypertarget{appendix-s1}{%
\subsection{Appendix S1}\label{appendix-s1}}

\textbf{Description of the traits compiled in this study}

Here we describe the different individual traits that have been included
in the database:

\emph{Reproductive biology traits}

\begin{itemize}
\item
  Breeding system: All species were classified in hermaphrodite,
  dioecious and monoecious species. Intermediate breeding systems or
  more complex ones were also annotated but all the species were divided
  into these three main categories for simplicity of the analysis.
\item
  Selfing level: We recorded the selfing level of the different species
  with both quantitative and qualitative data. The qualitative data was
  divided in four main categories, high selfers (76\% to 100\% of
  selfing), medium selfers (26\% to 75\%), low selfers (1\% to 25\%) and
  none (0\%) which was for the species that were unable to
  self-pollinate. The quantitative column of selfing had a high
  percentage of missing values (68\%) but we were able to solve this by
  converting the four categories from the qualitative column to
  numerical. For this, we considered the mean value of the different
  categories, that is the categories of `none', `low', `medium' and
  `high' represented 0\%, 13\%, 50.5\% and 88\% of selfing,
  respectively. This reduced the percentage of missing of this column
  from 68\% to 35\% and allowed the imputation of this variable.
\item
  Compatibility system: The different species were divided in three main
  categories in order to know their ability to self-pollinate. These
  categories were self-compatible, partially self-compatible and
  self-incompatible species. The field of selfing level is partly
  complementary to the compatibility system but is important to note
  that not all the self-compatible species or partially self-compatible
  species will self-pollinate.
\end{itemize}

\emph{Floral traits}

\begin{itemize}
\item
  Flower symmetry: Depending on the possible number of identical
  divisions of a flower, plant species were classified into zygomorphic
  (bilaterally symmetrical with only two identical parts) and
  actinomorphic (radially symmetrical with more than three identical
  parts).
\item
  Flower and inflorescence size: We searched for flower length and
  flower and inflorescence width (mm) for all species. When possible, we
  calculated the not found measurements with the help of online images
  and the software ImageJ. Note that for species with compound flowers
  (e.g., Asteraceae) or similar floral structures with flower heads with
  many small flowers we considered the inflorescence as the floral unit.
  For each species this is indicated in the dataset with the field of
  ``info\_level'' where the measurement level is specified as capitulum
  or flower level. Note that for some Asteraceae species information
  about the disc and ray floret is also provided in the database but
  these were not included in our analyses.
\item
  Flower number per plant: We compiled information about the number of
  flowers per plant for all species. However, this field was rare to
  find and we also used online images of the different species in order
  to calculate rough numbers of flowers per plant. We referenced all the
  filled fields in order to be able to follow the images that were used
  for these counts. It is important to note, that these numbers are not
  pretended to be the exact number of flowers per species but an
  approximate indicator of the reproductive investment for the different
  species that allow the macroecological analysis of this field.
\item
  Ovule number: We searched for the number of ovules per flower for all
  the different species. The number of ovules of Asteraceae species are
  considered as the total number of ovules per capitulum. Many species
  were filled by genus or family level because the number of ovules of
  some taxonomic groups is considered to be mostly constant (e.g.,
  Lamiaceae, Boraginaceae or Apiaceae).
\item
  Flower morphology: We looked for images and illustrations of the
  flowers from the different species on the floras and available
  resources in order to categorize the flower shape. We divided the
  flowers in 8 main different categories: open, bowl, tube, campanulate,
  funnelform, papilionaceous, brush and capitulum. However, we ended up
  groupping all flowers on the following 6 morphological groups for
  analyses: tube, papilonaceous, open, capitulum, campanulate and brush
  (Supplementary Information Text Fig. 1).
\end{itemize}

\begin{figure}[h]

{\centering \includegraphics[width=0.65\linewidth,]{../Images/flower_shapes}

}

\caption{\textbf{Supplementary Information Text Fig. 1.}  Main floral morphologies considered in this study. All species were groupped within these categories for analysis: (a) tube, (b) papilonaceous, (c) open, (d) capitulum, (e) campanulate and (f) brush.}\label{fig:pressure}
\end{figure}

\begin{itemize}
\item
  Style length: We searched for the length of the style (the pistil
  excluding the ovary and the stigma) in millimeters for all plant
  species. When the information about style length was missing, we tried
  to calculate it from images and illustrations from online resources
  (e.g., floras).
\item
  Nectar provision: We recorded the presence and absence of nectar for
  all species. In addition, we also searched for microlitres and
  milligrams of nectar per flower. For species that did not have nectar
  information but belonged to a family that is considered as
  `nectarless', this trait was recorded at family level and the species
  was recorded with `absence' of nectar. This was done exclusively for
  well documented nectarless taxonomical groups. For the field of
  microlitres of nectar, we considered single measurements of nectar
  standing crop. Despite the timing and methodology of the different
  quantitative measurements of nectar differed across studies, these
  fields allowed us to have an approximate idea of the reproductive
  investment of the different plant species.
\item
  Pollen grains per flower: For each species, we searched for the total
  number of pollen grains per flower. Because this fields was rarely
  available, we also tried to recover from pollen:ovule ratio
  information the total number of pollen grains by multiplying it by the
  average ovule number found for each species.
\end{itemize}

\emph{Other life history traits}

\begin{itemize}
\tightlist
\item
  Life form, life span and plant height: We divided the different plant
  species in 4 main categories: herbs, vines, shrubs and trees.
  Moreover, we also divided the species between short-lived species
  (annual, biennial and short-lived perennials) and perennial species
  (long-lived). Finally, we also searched for the average height (m) of
  the different species and annotated the maximum and minimum height
  when possible. We conducted the average between the maximum and
  minimum height to get an approximate average height of the species
  when the average was not indicated.
\end{itemize}

\begin{landscape}

\begingroup\fontsize{12}{14}\selectfont

\begin{longtable}[l]{lrlll}
\caption{\label{tab:unnamed-chunk-2}\textbf{Table S1. List of the 28 plant-pollinator studies used to build the plant trait database. Each study is shown with the first author that conducted the study, number of networks or metawebs that contains, type of information that contains (weighted or unweighted),  the structure (web or metaweb), year of publication and digital object identifier or permanent link for each study.}}\\
\toprule
First author & Year & Web N. & Network type & DOI\\
\midrule
\endfirsthead
\caption[]{\textit{(continued)}}\\
\toprule
First author & Year & Web N. & Network type & DOI\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{Arroyo-Correa} & \cellcolor{gray!6}{2019} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1111/1365-2745.13332}\\
\addlinespace
Bartomeus & 2008 & 6 & Weighted web & https://doi.org/10.1007/s00442-007-0946-1\\
\addlinespace
\cellcolor{gray!6}{Bartomeus} & \cellcolor{gray!6}{2008} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://github.com/ibartomeus/BeeFunData}\\
\addlinespace
Bek & 2006 & 1 & Unweighted web & Unpublished, Master thesis\\
\addlinespace
\cellcolor{gray!6}{Bundgaard} & \cellcolor{gray!6}{2003} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{Unpublished, Master thesis}\\
\addlinespace
Burkle & 2013 & 1 & Weighted web & https://doi.org/10.1126/science.1232728\\
\addlinespace
\cellcolor{gray!6}{Dicks} & \cellcolor{gray!6}{2002} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1046/j.0021-8790.2001.00572.x}\\
\addlinespace
Dupont & 2003 & 3 & Weighted web & https://doi.org/10.1111/j.1365-2656.2008.01501.x\\
\addlinespace
\cellcolor{gray!6}{Elberling} & \cellcolor{gray!6}{1999} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1111/j.1600-0587.1999.tb00507.x}\\
\addlinespace
Fang & 2008 & 1 & Weighted web & https://doi.org/10.1111/1749-4877.12190\\
\addlinespace
\cellcolor{gray!6}{Inouye} & \cellcolor{gray!6}{1988} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1111/j.1442-9993.1988.tb00968.x}\\
\addlinespace
Inouye & 1990 & 1 & Weighted metaweb & http://hdl.handle.net/2433/156099\\
\addlinespace
\cellcolor{gray!6}{Kaiser-Bunbury} & \cellcolor{gray!6}{2017} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1038/nature21071}\\
\addlinespace
Kaiser-Bunbury & 2011 & 6 & Weighted web & https://doi.org/10.1111/j.1365-2745.2010.01732.x\\
\addlinespace
\cellcolor{gray!6}{Kaiser-Bunbury} & \cellcolor{gray!6}{2010} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1016/j.ppees.2009.04.001}\\
\addlinespace
Kato & 2000 & 1 & Unweighted web & http://hdl.handle.net/2433/156116\\
\addlinespace
\cellcolor{gray!6}{Kevan} & \cellcolor{gray!6}{1970} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Unweighted web} & \cellcolor{gray!6}{https://doi.org/10.2307/2258569}\\
\addlinespace
Lundgren & 2005 & 1 & Weighted web & https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2\\
\addlinespace
\cellcolor{gray!6}{McMullen} & \cellcolor{gray!6}{1993} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Unweighted metaweb} & \cellcolor{gray!6}{https://biostor.org/reference/244737}\\
\addlinespace
Olesen & 2002 & 2 & Weighted web & https://doi.org/10.1046/j.1472-4642.2002.00148.x\\
\addlinespace
\cellcolor{gray!6}{Peralta} & \cellcolor{gray!6}{2006} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1111/ele.13510}\\
\addlinespace
Primack & 1983 & 3 & Unweighted metaweb & https://doi.org/10.1080/0028825X.1983.10428561\\
\addlinespace
\cellcolor{gray!6}{Ramirez} & \cellcolor{gray!6}{1989} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Unweighted web} & \cellcolor{gray!6}{https://doi.org/10.2307/2388282}\\
\addlinespace
Ramirez & 1992 & 1 & Unweighted metaweb & https://doi.org/10.1111/j.1095-8339.1992.tb00294.x\\
\addlinespace
\cellcolor{gray!6}{Robertson} & \cellcolor{gray!6}{1929} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Unweighted metaweb} & \cellcolor{gray!6}{https://doi.org/10.5962/bhl.title.11538}\\
\addlinespace
Small & 1976 & 1 & Weighted web & /13960/t4km08d21\\
\addlinespace
\cellcolor{gray!6}{Souza} & \cellcolor{gray!6}{2017} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{Weighted web} & \cellcolor{gray!6}{https://doi.org/10.1111/1365-2745.12978}\\
\addlinespace
Traveset & 2013 & 1 & Weighted metaweb & https://doi.org/10.1098/rspb.2012.3040\\*
\end{longtable}
\endgroup{}

\end{landscape}

\pagebreak

\begingroup\fontsize{12}{14}\selectfont

\begin{longtable}[t]{lrrrl}
\caption{\label{tab:unnamed-chunk-3}\textbf{Table S2. Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species.}}\\
\toprule
Functional traits & Sum Sq & F value & Pr(>F) & PC\\
\midrule
\endfirsthead
\caption[]{\textbf{Table S2. Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species.} \textit{(continued)}}\\
\toprule
Functional traits & Sum Sq & F value & Pr(>F) & PC\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{Breeding system} & \cellcolor{gray!6}{304.59} & \cellcolor{gray!6}{119.50} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{PC1}\\
\addlinespace
Compatibility system & 89.12 & 23.31 & 0.00 & PC1\\
\addlinespace
\cellcolor{gray!6}{Lifespan} & \cellcolor{gray!6}{35.65} & \cellcolor{gray!6}{27.97} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{PC1}\\
\addlinespace
Life form & 565.87 & 222.00 & 0.00 & PC1\\
\addlinespace
\cellcolor{gray!6}{Flower shape} & \cellcolor{gray!6}{132.24} & \cellcolor{gray!6}{20.75} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{PC1}\\
\addlinespace
Flower symmetry & 0.37 & 0.29 & 0.59 & PC1\\
\addlinespace
\cellcolor{gray!6}{Nectar provision} & \cellcolor{gray!6}{0.38} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{0.59} & \cellcolor{gray!6}{PC1}\\
\addlinespace
Breeding system & 304.59 & 119.50 & 0.00 & PC2\\
\addlinespace
\cellcolor{gray!6}{Compatibility system} & \cellcolor{gray!6}{89.12} & \cellcolor{gray!6}{23.31} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{PC2}\\
\addlinespace
Lifespan & 35.65 & 27.97 & 0.00 & PC2\\
\addlinespace
\cellcolor{gray!6}{Life form} & \cellcolor{gray!6}{565.87} & \cellcolor{gray!6}{222.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{PC2}\\
\addlinespace
Flower shape & 132.24 & 20.75 & 0.00 & PC2\\
\addlinespace
\cellcolor{gray!6}{Flower symmetry} & \cellcolor{gray!6}{0.37} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{0.59} & \cellcolor{gray!6}{PC2}\\
\addlinespace
Nectar provision & 0.38 & 0.29 & 0.59 & PC2\\*
\end{longtable}
\endgroup{}

\pagebreak

\begingroup\fontsize{12}{14}\selectfont

\begin{longtable}[t]{lrrr}
\caption{\label{tab:unnamed-chunk-4}\textbf{Table S3. Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species.}}\\
\toprule
  & PC1 & PC2 & PC3\\
\midrule
\endfirsthead
\caption[]{\textbf{Table S3. Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species.} \textit{(continued)}}\\
\toprule
  & PC1 & PC2 & PC3\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{Autonomous selfing} & \cellcolor{gray!6}{0.03} & \cellcolor{gray!6}{0.85} & \cellcolor{gray!6}{-0.51}\\
\addlinespace
Flowers per plant & 0.75 & -0.27 & -0.24\\
\addlinespace
\cellcolor{gray!6}{Flower width} & \cellcolor{gray!6}{-0.67} & \cellcolor{gray!6}{-0.38} & \cellcolor{gray!6}{-0.30}\\
\addlinespace
Style length & -0.34 & -0.37 & -0.66\\
\addlinespace
\cellcolor{gray!6}{Ovule number} & \cellcolor{gray!6}{-0.53} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{-0.02}\\
\addlinespace
Plant height & 0.56 & -0.40 & -0.46\\
\addlinespace
\cellcolor{gray!6}{Explained variation} & \cellcolor{gray!6}{26.72} & \cellcolor{gray!6}{25.08} & \cellcolor{gray!6}{19.17}\\*
\end{longtable}
\endgroup{}

\pagebreak

\begingroup\fontsize{12}{14}\selectfont

\begin{longtable}[t]{lrrr}
\caption{\label{tab:unnamed-chunk-5}\textbf{Table S4. Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.}}\\
\toprule
  & PC1 & PC2 & PC3\\
\midrule
\endfirsthead
\caption[]{\textbf{Table S4. Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.} \textit{(continued)}}\\
\toprule
  & PC1 & PC2 & PC3\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{Autonomous selfing} & \cellcolor{gray!6}{-0.05} & \cellcolor{gray!6}{0.78} & \cellcolor{gray!6}{0.37}\\
\addlinespace
Flowers per plant & 0.53 & -0.49 & 0.42\\
\addlinespace
\cellcolor{gray!6}{Flower width} & \cellcolor{gray!6}{-0.74} & \cellcolor{gray!6}{-0.27} & \cellcolor{gray!6}{-0.13}\\
\addlinespace
Style length & -0.60 & -0.30 & 0.11\\
\addlinespace
\cellcolor{gray!6}{Ovule number} & \cellcolor{gray!6}{-0.59} & \cellcolor{gray!6}{0.11} & \cellcolor{gray!6}{-0.08}\\
\addlinespace
Plant height & 0.26 & -0.60 & 0.47\\
\addlinespace
\cellcolor{gray!6}{Microlitres of Nectar per flower} & \cellcolor{gray!6}{-0.49} & \cellcolor{gray!6}{0.05} & \cellcolor{gray!6}{0.71}\\
\addlinespace
Pollen per flower & -0.29 & -0.45 & -0.13\\
\addlinespace
\cellcolor{gray!6}{Explained variation} & \cellcolor{gray!6}{23.42} & \cellcolor{gray!6}{21.13} & \cellcolor{gray!6}{14.84}\\*
\end{longtable}
\endgroup{}

\newpage

\begingroup\fontsize{12}{14}\selectfont

\begin{longtable}[t]{lll}
\caption{\label{tab:unnamed-chunk-6}\textbf{Table S5. Phylogenetic signal of the different quantitative traits.}}\\
\toprule
Functional traits & Lambda & P-value\\
\midrule
\endfirsthead
\caption[]{\textbf{Table S5. Phylogenetic signal of the different quantitative traits.} \textit{(continued)}}\\
\toprule
Functional traits & Lambda & P-value\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{Autonomous selfing} & \cellcolor{gray!6}{0.34} & \cellcolor{gray!6}{0.00}\\
\addlinespace
Flower number & 0.69 & 0.00\\
\addlinespace
\cellcolor{gray!6}{Inflorescence width} & \cellcolor{gray!6}{0.57} & \cellcolor{gray!6}{0.00}\\
\addlinespace
Flower width & 0.73 & 0.00\\
\addlinespace
\cellcolor{gray!6}{Flower length} & \cellcolor{gray!6}{0.75} & \cellcolor{gray!6}{0.00}\\
\addlinespace
Style length & 0.49 & 0.00\\
\addlinespace
\cellcolor{gray!6}{Ovule number} & \cellcolor{gray!6}{1.00} & \cellcolor{gray!6}{0.00}\\
\addlinespace
Plant height & 0.96 & 0.00\\
\addlinespace
\cellcolor{gray!6}{Nectar per flower ($\mu$l)} & \cellcolor{gray!6}{0.14} & \cellcolor{gray!6}{0.00}\\
\addlinespace
Nectar concentration ($\%$) & 0.65 & 0.00\\
\addlinespace
\cellcolor{gray!6}{Pollen grains per flower} & \cellcolor{gray!6}{1.00} & \cellcolor{gray!6}{0.00}\\*
\end{longtable}
\endgroup{}

\newpage
\begin{landscape}

\begin{figure}[h]
\includegraphics{Sup_Mat_Lanuza_et_al_2022_files/figure-latex/unnamed-chunk-7-1} \caption{\textbf{Fig. S1.} Map with the different locations of the plant-pollinator studies used in this work to explore woldwide patterns at the meso-scale level. Note that for visualization purposes studies from the same authors are shown with the same colour.}\label{fig:unnamed-chunk-7}
\end{figure}

\end{landscape}

\newpage

\begin{figure}[h]
\includegraphics{Sup_Mat_Lanuza_et_al_2022_files/figure-latex/unnamed-chunk-8-1} \caption{\textbf{Fig. S2.} Percentage of present and missing values of the different plant traits.}\label{fig:unnamed-chunk-8}
\end{figure}

\newpage

\begin{figure}[h]

{\centering \includegraphics[width=0.6\linewidth,]{Sup_Mat_Lanuza_et_al_2022_files/figure-latex/unnamed-chunk-9-1}

}

\caption{\textbf{Fig. S3.} Comparison of the phylogenetic informed principal component analysis for the dataset with data imputation and without data imputation. Panel 'a' shows the reproductive spectrum of trait variation for the full dataset with data imputation and panel 'b' shows the reproductive spectrum for the dataset without data imputation where the species with missing trait data were excluded from the analysis.}\label{fig:unnamed-chunk-9}
\end{figure}

\begin{figure}[h]

{\centering \includegraphics[width=0.6\linewidth,]{Sup_Mat_Lanuza_et_al_2022_files/figure-latex/unnamed-chunk-10-1}

}

\caption{\textbf{Fig. S4.} Comparison of the phylogenetic informed principal component analysis for the subset of species that had information of floral rewards with data imputation and without data imputation. Panel A shows the reproductive spectrum of trait variation for the dataset with data imputation and panel B shows the reproductive spectrum for the dataset excluding species with missing trait data}\label{fig:unnamed-chunk-10}
\end{figure}

\newpage

\begin{figure}[h]
\includegraphics{Sup_Mat_Lanuza_et_al_2022_files/figure-latex/unnamed-chunk-11-1} \caption{\textbf{Fig. S5.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation. The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates.}\label{fig:unnamed-chunk-11}
\end{figure}

\newpage

\begin{figure}[h]
\includegraphics{Sup_Mat_Lanuza_et_al_2022_files/figure-latex/unnamed-chunk-12-1} \caption{\textbf{Fig. S6.} Phylogenetically informed principal component analysis (pPCA) for all plant species with the first (flower number - flower size axis) and third (style length - autonomous selfing) principal component that explained most trait variation.}\label{fig:unnamed-chunk-12}
\end{figure}

\newpage
\thispagestyle{empty}

\begin{figure}[h]
\includegraphics{Sup_Mat_Lanuza_et_al_2022_files/figure-latex/unnamed-chunk-13-1} \caption{\textbf{Fig. S7.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species. Categories that differ significantly are denoted with a different letter.}\label{fig:unnamed-chunk-13}
\end{figure}

\begin{landscape}

\begin{figure}[!H]
\includegraphics{Sup_Mat_Lanuza_et_al_2022_files/figure-latex/unnamed-chunk-14-1} \caption{\textbf{Fig. S8.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation. Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3. For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel).}\label{fig:unnamed-chunk-14}
\end{figure}

\end{landscape}

\begin{landscape}

\begin{figure}[h]
\includegraphics{Sup_Mat_Lanuza_et_al_2022_files/figure-latex/unnamed-chunk-15-1} \caption{\textbf{Fig. S9.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows). The x-axis shows the most illustrative trait extremes of the trait continuum. Note that the plots are coloured by the different network metrics.}\label{fig:unnamed-chunk-15}
\end{figure}

\end{landscape}

\end{document}

### 2023-02-10 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
Update on supp mat

@@
 - \usepackage{soul}
-- \floatplacement{figure}{H}
 - \usepackage{afterpage}
@@
 ---
-
-```{r echo=FALSE,warning=FALSE}
-knitr::opts_chunk$set(fig.pos = "h", out.extra = "")
-
-```
 
@@
 The x-axis shows the most illustrative trait extremes of the trait continuum.
-Note that the plots are coloured by the different network metrics.", fig.pos= "h"}
+Note that the plots are coloured by the different network metrics."}
 

### 2023-02-13 Manuscript/Lanuza_et_al_2022.Rmd
Trait space with pollinator guilds on it (qualitative version)

@@
 
-4. Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping networks of plant-pollinator interactions at a global scale.
+4.
+Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping plant-pollinator interactions at a macro-ecological scale.
+These findings emphasize the importance of considering reproductive traits in the global spectrum of plant form and function, and the need to explore beyond floral morphological traits to broaden our understanding of plant-pollinator interactions.
 

### 2023-02-13 Scripts/Pollinator_guild_PCA/Plot_all.Rmd
Trait space with pollinator guilds on it (qualitative version)

---
output: pdf_document
classoption: landscape

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="85%",  fig.height=12, fig.width=18,fig.align='center'}

#Create panel with all plots, qualitative version

library(ggplot2)

#Load plots
bees = readRDS("../../Data/RData/Bee_PCA.rds")
coleoptera = readRDS("../../Data/RData/Coleoptera_PCA.rds")
lepidoptera = readRDS("../../Data/RData/Lepidoptera_PCA.rds")
non_bee_hymenoptera = readRDS("../../Data/RData/Non_bee_hymenoptera_PCA.rds")
non_syrphid_diptera = readRDS("../../Data/RData/Non_syrphid_diptera_PCA.rds")
syrphids = readRDS("../../Data/RData/Syrphids_PCA.rds")

#Make plot
library(patchwork)

bees + coleoptera + lepidoptera + 
non_bee_hymenoptera + non_syrphid_diptera + syrphids

```

### 2023-02-13 Scripts/Pollinator_guild_PCA/Coleoptera_PCA.R

@@ -1,0 +1,153 @@
+#Load libraries
+#LOAD LIBRARIES
+library(phytools)
+library(ape) #for phylogenetic distance
+library(dplyr) #data processing
+library(rtrees) #for phylogenetic distancelibrary(MASS)
+library(reshape2)
+library(viridis) #COLOUR GGPLOT
+library(MASS)
+library(ggplot2)
+library(broman) #crayon colours
+library(cowplot)
+library(ggstar)
+
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(1.6)),
+           axis.text=element_text(size = rel(1.6), color = "black"),
+           legend.title=element_text(face="bold"),
+           legend.text=element_text(size = rel(1.1)),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(0.4, 'lines'),
+           panel.border=element_rect(color="black",size=1),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank(),
+           plot.title = element_text(size = rel(2.5), face="bold")
+     ))
+}
+
+#Load trait data
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
+#convert rownames to column
+dat_cleaning_5 <- setDT(dat_cleaning_5, keep.rownames = TRUE)[]
+colnames(dat_cleaning_5)[1] <- "Plant_species"
+
+#Load PCA data
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+#Load visitation data
+long_d <- read.csv("Data/Csv/long_format_quantitative_networks.csv", row.names = 1) #quantitative network data|weighted by frequency of visits per plant species
+#Select data with interaction greater than 0
+long_d_1 <- long_d[long_d$Interaction>0,]
+#Remove other orders/guilds that are not these ones
[…]

### 2023-02-13 Scripts/Pollinator_guild_PCA/Lepidoptera_PCA.R

@@ -1,0 +1,152 @@
+#Load libraries
+#LOAD LIBRARIES
+library(phytools)
+library(ape) #for phylogenetic distance
+library(dplyr) #data processing
+library(rtrees) #for phylogenetic distancelibrary(MASS)
+library(reshape2)
+library(viridis) #COLOUR GGPLOT
+library(MASS)
+library(ggplot2)
+library(broman) #crayon colours
+library(cowplot)
+library(ggstar)
+
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(1.6)),
+           axis.text=element_text(size = rel(1.6), color = "black"),
+           legend.title=element_text(face="bold"),
+           legend.text=element_text(size = rel(1.1)),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(0.4, 'lines'),
+           panel.border=element_rect(color="black",size=1),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank(),
+           plot.title = element_text(size = rel(2.5), face="bold")
+     ))
+}
+
+#Load trait data
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
+#convert rownames to column
+dat_cleaning_5 <- setDT(dat_cleaning_5, keep.rownames = TRUE)[]
+colnames(dat_cleaning_5)[1] <- "Plant_species"
+
+#Load PCA data
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+#Load visitation data
+long_d <- read.csv("Data/Csv/long_format_quantitative_networks.csv", row.names = 1) #quantitative network data|weighted by frequency of visits per plant species
+#Select data with interaction greater than 0
+long_d_1 <- long_d[long_d$Interaction>0,]
+#Remove other orders/guilds that are not these ones
[…]

### 2023-02-13 Scripts/Pollinator_guild_PCA/Non-syrphids_Diptera_PCA.R

@@ -1,0 +1,152 @@
+#Load libraries
+#LOAD LIBRARIES
+library(phytools)
+library(ape) #for phylogenetic distance
+library(dplyr) #data processing
+library(rtrees) #for phylogenetic distancelibrary(MASS)
+library(reshape2)
+library(viridis) #COLOUR GGPLOT
+library(MASS)
+library(ggplot2)
+library(broman) #crayon colours
+library(cowplot)
+library(ggstar)
+
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(1.6)),
+           axis.text=element_text(size = rel(1.6), color = "black"),
+           legend.title=element_text(face="bold"),
+           legend.text=element_text(size = rel(1.1)),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(0.4, 'lines'),
+           panel.border=element_rect(color="black",size=1),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank(),
+           plot.title = element_text(size = rel(2.5), face="bold")
+     ))
+}
+
+#Load trait data
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
+#convert rownames to column
+dat_cleaning_5 <- setDT(dat_cleaning_5, keep.rownames = TRUE)[]
+colnames(dat_cleaning_5)[1] <- "Plant_species"
+
+#Load PCA data
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+#Load visitation data
+long_d <- read.csv("Data/Csv/long_format_quantitative_networks.csv", row.names = 1) #quantitative network data|weighted by frequency of visits per plant species
+#Select data with interaction greater than 0
+long_d_1 <- long_d[long_d$Interaction>0,]
+#Remove other orders/guilds that are not these ones
[…]

### 2023-02-13 Scripts/Pollinator_guild_PCA/Syrphids_PCA.R

@@ -1,0 +1,153 @@
+#Load libraries
+#LOAD LIBRARIES
+library(phytools)
+library(ape) #for phylogenetic distance
+library(dplyr) #data processing
+library(rtrees) #for phylogenetic distancelibrary(MASS)
+library(reshape2)
+library(viridis) #COLOUR GGPLOT
+library(MASS)
+library(ggplot2)
+library(broman) #crayon colours
+library(cowplot)
+library(ggstar)
+
+# Theme for publication
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  (theme_bw(base_size = base_size, base_family = base_family)+
+     theme(text=element_text(color="black"),
+           axis.title=element_text( size = rel(1.6)),
+           axis.text=element_text(size = rel(1.6), color = "black"),
+           legend.title=element_text(face="bold"),
+           legend.text=element_text(size = rel(1.1)),
+           legend.background=element_rect(fill="transparent"),
+           legend.key.size = unit(0.4, 'lines'),
+           panel.border=element_rect(color="black",size=1),
+           panel.grid.minor.x =element_blank(),
+           panel.grid.minor.y= element_blank(),
+           panel.grid.major= element_blank(),
+           plot.title = element_text(size = rel(2.5), face="bold")
+     ))
+}
+
+#Load trait data
+dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
+#convert rownames to column
+dat_cleaning_5 <- setDT(dat_cleaning_5, keep.rownames = TRUE)[]
+colnames(dat_cleaning_5)[1] <- "Plant_species"
+
+#Load PCA data
+phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
+
+#Load visitation data
+long_d <- read.csv("Data/Csv/long_format_quantitative_networks.csv", row.names = 1) #quantitative network data|weighted by frequency of visits per plant species
+#Select data with interaction greater than 0
+long_d_1 <- long_d[long_d$Interaction>0,]
+#Remove other orders/guilds that are not these ones
[…]

### 2023-02-14 Scripts/Pollinator_guild_PCA/Syrphids_PCA.R
Pollinator guilds on trait space

@@ -26,7 +26,7 @@ theme_ms <- function(base_size=12, base_family="Helvetica") {
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
            panel.grid.major= element_blank(),
-           plot.title = element_text(size = rel(2.5), face="bold")
+           plot.title = element_text(size = rel(2.3), face="bold")
      ))
 }
 
@@ -136,8 +136,8 @@ PCbiplot <- function(PC, x="PC1", y="PC2") {
   
   #CHANGE THEME
   
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +
-    ggtitle("(a) Syrphids") + xlab(NULL)  + ylab("Autonomous selfing - Floral display axis")
+  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.11, 0.130)) +
+    ggtitle("(f) Syrphids") + xlab("Flower number - Flower size axis")  + ylab(NULL)
   
   
   plot

### 2023-02-14 Manuscript/Lanuza_et_al_2022.Rmd
Edits on code to run without the last col of nectar conc that is not finally added

@@
 
-2. Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
+2. Here, using a global dataset of 18 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
 
@@
 
-We selected a total of 19 quantitative and categorical functional traits that included reproductive traits and traits related with plant form and size (see table 1).
+We selected a total of 18 quantitative and categorical functional traits that included reproductive traits and traits related with plant form and size (see table 1).
 Reproductive traits consisted of those related to floral and reproductive biology: (i) floral traits included those related to the size of floral organs (e.g., style length), floral display size (e.g., flower number) and floral rewards (e.g., pollen quantity), while (ii) reproductive biology traits represented the plant reproductive system (i.e., the breeding, mating and compatibility system).
@@
 For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
-From a matrix comprising a total of 28,614 possible cells (considering all traits and plant species: 19 columns × 1,506 species), we were able to fill 23,354 cells (81.6% of the dataset, see figure S2 for missing value information for each trait).
+From a matrix comprising a total of 27,108 possible cells (considering all traits and plant species: 18 columns × 1,506 species), we were able to fill 22,796 cells (84.1% of the dataset, see figure S2 for missing value information for each trait).
 An extended description of each trait and how it was obtained can be found in Appendix S1.
@@
 Trait <- c("Plant height", "Flower width", "Flower length", "Inflorescence width", "Style length", "Ovules per flower",
-           "Flowers per plant", "Microliters of nectar", "Milligrams of nectar", "Nectar concentration", "Pollen grains per flower", "Autonomous selfing (fruit set)")
+           "Flowers per plant", "Microliters of nectar", "Milligrams of nectar", "Pollen grains per flower", "Autonomous selfing (fruit set)")
 
@@
 
-T.range <- c("0.01-30m", "0.50-205mm", "0.20-195mm", "0.80-300mm", "0-138mm", "1-25000", "1-1.8 x $10^5$", "0-160$\\mu$l", "0-6.1mg", "0-100$\\%$", "13-2 x $10^8$", "0-100$\\%$")
+T.range <- c("0.01-30m", "0.50-205mm", "0.20-195mm", "0.80-300mm", "0-138mm", "1-25000", "1-1.8 x $10^5$", "0-160$\\mu$l", "0-6.1mg", "13-2 x $10^8$", "0-100$\\%$")
 
@@
 kable(d, booktabs = T, linesep = "\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1.} Quantitative and categorical traits used in this study.") %>%
-  kable_styling(full_width = F,font_size = 12) %>% row_spec(0, bold=T) %>% pack_rows("Quantitative", 1, 12) %>%
-pack_rows("Categorical", 13, 19)
+  kable_styling(full_width = F,font_size = 12) %>% row_spec(0, bold=T) %>% pack_rows("Quantitative", 1, 11) %>%
+pack_rows("Categorical", 12, 18)
 
@@
 We found a strong phylogenetic signal (*P* \< 0.01) for most quantitative traits (table S5).
-The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73), number of flowers per plant ($\lambda$ = 0.69) and nectar concentration ($\lambda$ = 0.65).
+The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73) and number of flowers per plant ($\lambda$ = 0.69).
 The traits that had a moderate phylogenetic signal included inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).

### 2023-02-14 Manuscript/Lanuza_et_al_2022.tex
Edits on code to run without the last col of nectar conc that is not finally added

@@
 \item
-  Here, using a global dataset of 16 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
+  Here, using a global dataset of 18 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
 \item
@@
 \item
-  Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping networks of plant-pollinator interactions at a global scale.
+  Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping plant-pollinator interactions at a macro-ecological scale.
+These findings emphasize the importance of considering reproductive traits in the global spectrum of plant form and function, and the need to explore beyond floral morphological traits to broaden our understanding of plant-pollinator interactions.
 \end{enumerate}
@@
 \hspace{1em}Milligrams of nectar & 0-6.1mg\\
-\hspace{1em}Nectar concentration & 0-100$\%$\\
 \hspace{1em}Pollen grains per flower & 13-2 x $10^8$\\

### 2023-02-14 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
Edits on code to run without the last col of nectar conc that is not finally added

@@
 #nectar_mg <- readRDS("Data/RData/Nectar_mg_phylo.rds")
-#Nectar concentration
-nectar_con <- readRDS("Data/RData/Nectar_concentration_phylo.rds")
 
@@
 #LABELS
-label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Nectar per flower ($\\mu$l)", "Nectar concentration ($\\%$)","Pollen grains per flower")
+label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Nectar per flower ($\\mu$l)","Pollen grains per flower")
 #LAMBDA
-lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, nectar_ul$lambda, nectar_con$lambda, pollen$lambda)
+lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, nectar_ul$lambda, pollen$lambda)
 #P-VALUE
-p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P,nectar_ul$P,  nectar_con$P, pollen$P)
+p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P,nectar_ul$P, pollen$P)
 
@@
                         "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
+                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg",
                         "Pollen_per_flower")]
@@
          "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-         "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
+         "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg",
          "Pollen_per_flower")]
@@
                         "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
+                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg",
          "Pollen_per_flower")]
@@
                  "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 
-                 "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar per flower (microlitres)", "Nectar per flower (miligrames)", "Nectar concentration (%)", "Pollen grains per flower")
+                 "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar per flower (microlitres)", "Nectar per flower (miligrames)",  "Pollen grains per flower")
 

### 2023-02-14 Scripts/2_Missing_Data_Exploration.R

@@ -57,7 +57,7 @@ str(trait_filtered_2)
 t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
                         "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
                         "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
+                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg",
                         "Pollen_per_flower")]
 
 
@@ -141,7 +141,7 @@ t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c
 t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
          "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
          "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-         "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
+         "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg",
          "Pollen_per_flower")]
 
 
@@ -212,9 +212,9 @@ t <- t[!is.na(t$Genus_all),]
 
 
 t <- t[c("Breeding_system","Compatibility_system",
-         "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
+         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
          "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
[…]

### 2023-02-14 Scripts/8_Regression_Tree_All.R

@@ -1,252 +1,0 @@
-########################################################################################################################################################
-########################################################################################################################################################
-########################################################################################################################################################
-##REGRESSION TREE FOR ALL THE SPECIES
-########################################################################################################################################################
-########################################################################################################################################################
-########################################################################################################################################################
-
-#HERE I TRY TO SELECT THE MAIN EXPLANATORY TRAITS FOR EACH TRAIT 
-
-#LOAD LIBRARIES
-library(data.table) # operate with df
-library(bipartite) #calculate metrics
-library(dplyr) #data manipulation 
-library(stringr) #remove string
-library(brms)
-library(projpred)
-library(dplyr)
-library(ggplot2)
-library(bayesplot)
-library(ape)
-library(rtrees)
-library(cowplot)
-library(emmeans)
-library(tidybayes)
-library(multcomp)
-########################################################################################################################################################
-#1) LOAD NETWORK DATA
-########################################################################################################################################################
-#Set working directory to read files
-setwd("~/R_Projects/Reproductive traits/Data/Data_networks_quantitative") 
-
-#read csv files
-temp <- list.files(pattern="*.csv")
-my.list <- list(for (i in 1:length(temp)) assign(temp[i], read.csv(temp[i])))
-my_files <- list.files(pattern = "\\.csv$")
-my_data <- lapply(my_files, function(i){read.csv(i,  row.names = 1)})
-# Add id to dataframe
-names(my_data) <- stringr::str_replace(my_files, pattern = ".csv", replacement = "")
-
-########################################################################################################################################################
[…]

### 2023-02-14 Supplementary_Material/Figures/Analysis_2_Hymenoptera_Families_Separated.Rmd
organising files for what it seems it could be the final version of it

--- 2022-07-06 Supplementary_Material/Analysis_2_Hymenoptera_Families_Separated.Rmd
@@
 ggtitle("(e)") +
-annotate(geom = "text", x = -1.7, y =0.2 , label = "Low poll. depend.", size = 8) +
-annotate(geom = "text", x = -1.65, y =0.12 , label = "Small floral display", size = 8) + 
-annotate(geom = "text", x = 1.8, y =0.2 , label = "High poll. depend.", size = 8) + 
-annotate(geom = "text", x = 1.85, y =0.12 , label = "Large floral display", size = 8) +
+annotate(geom = "text", x = -1.75, y =0.2 , label = "High aut. selfing", size = 8) +
+annotate(geom = "text", x = -1.6, y =0.12 , label = "Small floral display", size = 8) + 
+annotate(geom = "text", x = 1.8, y =0.2 , label = "Low aut. selfing", size = 8) + 
+annotate(geom = "text", x = 2, y =0.12 , label = "Large floral display", size = 8) +
 xlab(NULL) +
-annotate(geom = "text", x = -0.1, y =0.35 , label = "Pollinator dependence - Floral display axis", size = 8.5, fontface =2) +
+annotate(geom = "text", x = -0.1, y =0.35 , label = "Autonomous selfing - Floral display axis", size = 8.5, fontface =2) +
 theme(panel.border=element_rect(color="black",size=1.2))
@@
 ggtitle("(f)") +
-annotate(geom = "text", x = -1.6, y =0.2 , label = "Short styles", size = 8) +
-annotate(geom = "text", x = -1.25, y =0.12 , label = "High poll. depend.", size = 8) + 
+annotate(geom = "text", x = -1.35, y =0.2 , label = "Short styles", size = 8) +
+annotate(geom = "text", x = -1.15, y =0.12 , label = "Low aut. selfing", size = 8) + 
 annotate(geom = "text", x = 1.95, y =0.2 , label = "Long styles", size = 8) + 
-annotate(geom = "text", x = 2.3, y =0.12 , label = "Low poll. depend.", size = 8) +
+annotate(geom = "text", x = 2.2, y =0.12 , label = "High aut. selfing", size = 8) +
 xlab(" \n \n  ") +
-annotate(geom = "text", x = 0.25, y =0.35 , label = "Style length - Pollinator dependence axis", size = 8.5, fontface =2) +
+annotate(geom = "text", x = 0.25, y =0.35 , label = "Style length - Autnomous selfing axis", size = 8.5, fontface =2) +
 theme(panel.border=element_rect(color="black",size=1.2))

### 2023-02-14 Supplementary_Material/Figures/Anova_Qualitative_Traits.Rmd
organising files for what it seems it could be the final version of it

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}

library(dplyr)
library(kableExtra)

setwd("~/R_Projects/Reproductive Traits")
model1 <- readRDS("Data/RData/model1_tukey_categories.rds")
model2 <- readRDS("Data/RData/model2_tukey_categories.rds")

library(dplyr)
library(kableExtra)
#CREATE TABLE WITH OUTPUT OF ANOVA MODEL

#PC1
am1 <- anova(model1) # save anova output

am1 <- as.data.frame(am1) #convert to dataframe

am2 <- am1[c(1:7),c(2,4,5)] #select columns of interest

am3 <- am2 %>% mutate(across(is.numeric, ~ round(., 2))) #select just two decimals

rownames(am3) <- c("Breeding system","Compatibility system", "Lifespan", "Life form", "Flower shape", "Flower symmetry", "Nectar provision") #rownames

am4 <- tibble::rownames_to_column(am3, "Functional traits")

am4$PC <- c(rep("PC1",7))

#NOW PC2
#PC1
an1 <- anova(model1) # save anova output

an1 <- as.data.frame(an1) #convert to dataframe

an2 <- an1[c(1:7),c(2,4,5)] #select columns of interest

an3 <- an2 %>% mutate(across(is.numeric, ~ round(., 2))) #select just two decimals

rownames(an3) <- c("Breeding system","Compatibility system", "Lifespan", "Life form", "Flower shape", "Flower symmetry", "Nectar provision") #rownames

an4 <- tibble::rownames_to_column(an3, "Functional traits")

an4$PC <- c(rep("PC2",7))

#Merge

d <- rbind(am4,an4)

saveRDS(d, "Data/RData/table_categorical_tukey_test.rds")

#Plot table
#Add latex format in markdown

kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE) %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")

```

### 2023-02-14 Supplementary_Material/Figures/Apis_Non_Apis_Presence_Absence_Bees.Rmd
organising files for what it seems it could be the final version of it

--- 2021-05-17 Supplementary_Material/Figure_Analysis_Bees_Apis_Non_Apis.Rmd
@@
 
-analysis_1_just_bees <- readRDS("results_analysis_1_just_bees.rds")
-dat_analysis <- readRDS("dat_analysis_results_analysis_1_just_bees.rds")
+analysis_1_just_bees <- readRDS("results_analysis_1_bee_families_apis_presence_absence.rds")
+dat_analysis <- readRDS("dat_analysis_results_analysis_1_bee_families_apis_presence_absence.rds")
 
@@
 
-p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis,
-  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
-  theme_ms() + theme(legend.position = "none")
+p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = dat_analysis,
+aes(x = -PC1, y = Interaction),size = 0.75, alpha=0.5) +geom_line(size=1.4, color="orange") + ylab("Absence/presence")+ xlab("PC1")+
+  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = "(a)")
 
@@
 ce_pc2 <- conditional_effects(analysis_1_just_bees, effects = "PC2",points=T) 
-ce_pc1[[1]]$guild <- "bees"
+ce_pc2[[1]]$guild <- "bees"
 
@@
 
-p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,
-  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none")  + ggtitle(my_y_title_1)+
-  theme(plot.title = element_text(size = 36, face = "bold"))
+p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = dat_analysis,
+aes(x = -PC2, y = Interaction),size = 0.75, alpha=0.5) +geom_line(size=1.4, color="orange") + ylab("Absence/presence")+ xlab("PC2")+
+  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = "(b)")
+
 #Plot nicely PC3
 ce_pc3 <- conditional_effects(analysis_1_just_bees, effects = "PC3",points=T)
-ce_pc1[[1]]$guild <- "bees"
+ce_pc3[[1]]$guild <- "bees"
 
-p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis,
-  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="orange") + geom_line(size=1.4, color="orange") + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
-  theme_ms() + theme(legend.position = "none")
-
-analysis_1_just_bees_non_apis <- readRDS("results_analysis_1_just_bees_non_apis.rds")
-dat_analysis <- readRDS("dat_analysis_results_analysis_1_just_bees.rds")
-
-ce_pc1 <- conditional_effects(analysis_1_just_bees_non_apis, effects = "PC1",points=T) 
-ce_pc1[[1]]$guild <- "bees"
-
-pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis,
-      aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4")+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
-  theme_ms() + theme(legend.position = "none")
-
-#Plot nicely PC2
-ce_pc2 <- conditional_effects(analysis_1_just_bees_non_apis, effects = "PC2",points=T) 
-ce_pc1[[1]]$guild <- "bees"
-
-my_y_title <- expression(paste(italic("Apis mellifera"), " excluded"))
-
-pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,
-                                                                          aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
-  theme_ms() + theme(legend.position = "none")  + ggtitle(my_y_title)+
-  theme(plot.title = element_text(size = 36, face = "bold"))
-#Plot nicely PC3
-ce_pc3 <- conditional_effects(analysis_1_just_bees_non_apis, effects = "PC3",points=T)
-ce_pc1[[1]]$guild <- "bees"
-
-pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis,
-                                                                          aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
-  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
-  theme_ms() + theme(legend.position = "none")
+p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = dat_analysis,
+aes(x = -PC3, y = Interaction),size = 0.75, alpha=0.5) +geom_line(size=1.4, color="orange") + ylab("Absence/presence")+ xlab("PC3")+
+  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = "(c)")
 
@@
 
-combined <- p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "right")
+combined <- p1 + p2 + p3 & theme(legend.position = "right")
 combined + plot_layout(guides = "collect", ncol=3)

### 2023-02-14 Supplementary_Material/Figures/Global_Trait_Spectrum_Nectar_Poll_No_labels.Rmd
organising files for what it seems it could be the final version of it

--- 2021-05-12 Supplementary_Material/Global_Trait_Spectrum_Nectar_Pollen.Rmd
@@
 library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
 library(reshape2)
@@
   #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height", "Nectar","Pollen" )
+  rownames(PC$L) <- c("", "", "", "", "", "", "","" )
 
@@
   plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,5.5,5.3,5.5,6.1,5.75,5.8,6)), y = (PCAloadings$PC2*c(4.8,4.8,4.65,5.65,5,5.1,5.75,5)+c(0,0,0,0,0,0,0,0)),
-                          label = PCAloadings$Variables, color="black",fontface =2,size=4)
+                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
 

### 2023-02-14 Supplementary_Material/Figures/Global_Trait_Spectrum_Nectar_Pollen.Rmd
organising files for what it seems it could be the final version of it

--- 2021-08-16 Supplementary_Material/Supplementary_Material.Rmd
@@
 ---
-title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant floral and reproductive traits determine interactions with floral visitors}
-
-output: 
-  pdf_document:
-    extra_dependencies: ["float"]
-header-includes:
-- \usepackage{pdflscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
-- \usepackage{float}
-- \usepackage{caption}
-- \usepackage{setspace}\doublespacing
-- \usepackage{soul}
-- \floatplacement{figure}{H}
-- \usepackage{afterpage}
-- \usepackage{placeins}
-- \usepackage{graphicx}
-- \usepackage{floatpag}
-
-fontsize: 12pt
-
+title: ""
+output: pdf_document
 ---
 
-```{r echo=FALSE,warning=FALSE}
-knitr::opts_chunk$set(fig.pos = "h", out.extra = "")
-
-```
-
-\captionsetup[figure]{labelformat=empty}
-\captionsetup[table]{labelformat=empty}
-\captionsetup[table]{font={stretch=1.2}}
-
-\renewcommand{\figurename}{}
-
-\singlespacing
-\vspace{-1.6cm}
-
-Jose B. Lanuza$^{1,2}*$, Romina Rader$^{1}$, Jamie Stavert$^{3}$, Liam K. Kendall$^{4}$, Manu E. Saunders$^{1}$ and Ignasi Bartomeus$^{2}$
-
-\vspace{-0.6cm}
-
-\section*{\hfil Supplementary information\hfil}
-
-# Contents:
-
-__Supplementary text__
-
-Description of the traits compiled in this study
-
-\doublespacing
-\singlespacing
-
-__Supplementary Tables__
-
-Supplementary Table S1: List of the 28 plant-pollinator studies used to build the plant trait database
-
-Supplementary Table S2: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species
-
-Supplementary Table S3: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity
-
-Supplementary Table S4: Statistical association between the different categorical variables and the fisrt three main axes of trait variation with the full set of species
-
-Supplementary Table S5: Phylogenetic signal of the different quantitative traits
-
-\doublespacing
-\singlespacing
-
-__Supplementary Figures__
-
-Supplementary Fig. S1: Percentage of present and missing values of the different traits
-
-Supplementary Fig. S2: Phylogenetic informed principal component analysis for the species that did not have missing values
-
-Supplementary Fig. S3: Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation
-
-Supplementary Fig. S4: Regression tree analyses
-
-Supplementary Fig. S5: PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species
-
-Supplementary Fig. S6: Phylogenetic informed principal component analysis for the subset of species with floral rewards.
-
-Supplementary Fig. S7: Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species
-
-Supplementary Fig. S8: Visitation rate of the main bee families on the main axes of trait variation
-
-Supplementary Fig. S9:  Plant species level metrics across the three main axes of trait variation
-
-Supplementary Fig. S10: Pearson correlation between the product of flower number-flower size and autonomous selfing level
-
-\newpage
-
-__Description of the traits compiled in this study__
-
-_Reproductive traits_
-
--	Breeding system: The different plant species were classified in hermaphrodite, dioecious and monoecious species.
-Intermediate breeding systems or more complex ones were also annotated but all the species were divided into these three main categories for simplicity of the analysis.
-
--	Selfing level: We recorded the selfing level of the different species with both quantitative and qualitative data.
-The qualitative data was divided in four main categories, high selfers, medium selfers, low selfers and none which was for the species that were unable to self-pollinate.
-In addition, quantitative data was also divided into these four categories with the following criteria: from 0% to lower than 1% ‘none’, from 1% to 25% ‘low’, from 26% to 75% ‘medium’ and from 76% to 100%  ‘high’.
-
--	Compatibility system: The different species were divided in three main categories in order to know their ability to self-pollinate.
-These categories were self-compatible, partially self-compatible and self-incompatible species.
-The field of selfing level is partly complementary to the compatibility system but is important to note that not all the self-compatible species or partially self-compatible species will self-pollinate.
-
-_Floral traits_
-
--	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape.
-We divided the flowers in 8 main different categories: open, tube, campanulate, funnelform, papilionaceous, spike and capitulum.
-
--	Flower symmetry: We also recorded if the flowers were bilaterally symmetrical “zygomorphic” or were radially symmetrical “actinomorphic”.
-
--	Flower and inflorescence size: We searched for flower length and flower and inflorescence width (mm) for all species.
-When possible, we calculated the not found measurements with the help of online images and  the software ImageJ.
-
--	Flower number per plant: We compiled information about the number of flowers per plant for all species.
-However, this field was rare to find and we also used online images of the different species in order to calculate rough numbers of flowers per plant.
-We referenced all the filled fields in order to be able to follow the images that were used for these counts.
-It is important to note, that these numbers are not pretended to be the exact number of flowers per species but an approximate indicator of the reproductive investment for the different species that allow the macroecological analysis of this field.
-
--	Ovule number: We searched for the number of ovules per flower for all the different species.
-The number of ovules of Asteraceae species are considered as the total number of ovules per capitulum.
-Many species were filled by genus or family level because the number of ovules in this taxonomic groups is considered to be mostly constant (e.g., Lamiaceae Boraginaceae or Apiaceae).
-
--	Style length: The length of the style (mm) of the different species was also included. When possible, we calculated style length from images and illustrations on the online floras.
-
-- Nectar provision: We recorded the presence and absence of nectar for all species.
-In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration.
-In general terms, nectar data was rarely present and we try to minimise the loss of information by filling some species at family level.
-For instance, Solanaceae species are described as nectarless, and species that belonged to this family were recorded with ‘absence’ of nectar.
-
-- Pollen grains per flower: We recorded pollen grains per flower for all species but this field was rarely described in the literature.
-When just the pollen:ovule ratio was found we converted it back to pollen grains by multiplying by ovule number.
-
-_Vegetative traits_
-
-- Life form, life span and plant height: We divided the different plant species in 4 main categories: herbs, vines, shrubs and trees.
-Moreover, we also divided the species between short-lived species (annual, biennial and short-lived perennials) and perennial species (long-lived).
-Finally, we also searched for the average height (m) of the different species and annotated the maximum and minimum height when possible.
-We conducted the average between the maximum and minimum height to get an approximate average height of the species when the average was not indicated.
-
-\begin{landscape}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = "left"}
-setwd("~/R_Projects/Reproductive Traits")
-library(kableExtra)
-
-#Create data.frame with references
-
-`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1", "1", "1", "1", "1", "1", "1", "3", "1",
-                          "1", "1")
-
-#`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))
-
-`Network type` <- c(rep("Weighted web",  18), rep("Unweighted web",  4), "Weighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Weighted metaweb")
-
-`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
-                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard", "Bek", "Kato", "Kevan", "Ramirez",
-                    "Inouye","McMullen", "Primack", "Ramirez", "Robertson", "Traveset")
-
-Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003,2006,2000,1970,1989,1990, 1993, 1983, 1992, 1929, 2013)
-
-#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
-#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
-#"USA", "Ecuador")
-
-DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
-"https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
-"https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
-"/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
-"https://doi.org/10.1111/j.1365-2745.2010.01732.x", "https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510",
-"https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis", "Unpublished, Master thesis", "http://hdl.handle.net/2433/156116",
-"https://doi.org/10.2307/2258569", "https://doi.org/10.2307/2388282", "http://hdl.handle.net/2433/156099", "https://biostor.org/reference/244737", "https://doi.org/10.1080/0028825X.1983.10428561",
-"https://doi.org/10.1111/j.1095-8339.1992.tb00294.x", "https://doi.org/10.5962/bhl.title.11538", "https://doi.org/10.1098/rspb.2012.3040")
-
-references <- data.frame(`First author`, Year, `Number of networks`,`Network type`,   DOI)
-
-colnames(references) <- c("First author", "Year", "Web N.",  "Network type",  "DOI")
-
-library(dplyr)
- references %>%
- arrange(`First author`)%>%
-kable("latex", longtable = T, booktabs = T,linesep = "\\addlinespace",
-             caption = "\\textbf{Supplementary Table S1 | List of the 28 plant-pollinator studies used to build the plant trait database.} Each study is shown with the first author that conducted the study, number of networks or metawebs that contains, type of information that contains (weighted or unweighted),  the structure (web or metaweb), year of publication and digital object identifier or permanent link for each study.") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, repeat_header_method="replace" ,full_width=F,position = "left")
-
-```
-
-\end{landscape}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
- kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Supplementary Table S2 | Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Microlitres of Nectar per flower" , "Pollen per flower","Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
-kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Supplementary Table S3 | Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-d <- readRDS("Data/RData/table_categorical_tukey_test.rds")
-
-#Again im getting the same error on this rmd so I run it on another one, save the dataframe and plot it here
-
-#Plot table
-#Add latex format in markdown
-
-kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Supplementary Table S4 | Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-#SELFING
-selfing <- readRDS("Data/RData/selfing_phylo.rds")
-#FLOWER NUMBER
-flower_n <- readRDS("Data/RData/flower_n_phylo.rds")
-#INFLO WIDTH
-inflow_width <- readRDS("Data/RData/inflow_width_phylo.rds")
-#FLOWER WIDTH
-flower_width <- readRDS("Data/RData/flower_width_phylo.rds")
-#FLOWER LENGHT
-flower_length <- readRDS("Data/RData/flower_length_phylo.rds")
-#STYLE LENGTH
-style_n <- readRDS("Data/RData/style_n_phylo.rds")
-#OVULE NUMBER
-ovule_n <- readRDS("Data/RData/ovule_n_phylo.rds")
-#PLANT HEIGHT
-plant_height <- readRDS("Data/RData/plant_height_phylo.rds")
-#POLLEN
-pollen <- readRDS("Data/RData/pollen_phylo.rds")
-#Nectar ul
-nectar_ul <- readRDS("Data/RData/Nectar_ul_phylo.rds")
-
-#Not included at the end
-#Nectar mg
-#nectar_mg <- readRDS("Data/RData/Nectar_mg_phylo.rds")
-#Nectar concentration
-nectar_con <- readRDS("Data/RData/Nectar_concentration_phylo.rds")
-
-#Select two decimals function
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-#LABELS
-label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Nectar per flower ($\\mu$l)", "Nectar concentration ($\\%$)","Pollen grains per flower")
-#LAMBDA
-lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, nectar_ul$lambda, nectar_con$lambda, pollen$lambda)
-#P-VALUE
-p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P,nectar_ul$P,  nectar_con$P, pollen$P)
-
-tabla <- data.frame(label, specify_decimal(lambda,2), specify_decimal(p_value,2))
-
-colnames(tabla) <- c("Functional traits", "Lambda", "P-value")
-
-kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,caption = "\\textbf{Supplementary Table S5 | Phylogenetic signal of the different quantitative traits.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Supplementary Fig. S1 | Percentage of present and missing values of the different traits.}"}
-
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-
-########################################################################################################################################################
-#SCRIPT FOR DATA IMPUTATION
-########################################################################################################################################################
-#1) READ TRAIT DATA
-
-#2) CLEAN DATA AND RENAME LEVELS
-
-#3) EXPLORE PATTERNS OF MISSING DATA
-
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-
-#5) ICLUDE EIGENVALUES IN RAWDATA TO IMPROVE IMPUTATION OURPUT
-
-#6) IMPUTE DATA
-
-#7) SAVE IMPUTED DATA 
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(missMDA) #For missing values
-library(FactoMineR) #Produce pca biplot with individuals and variables
-library(factoextra)
-library(ggpubr) 
-library(missForest) #random forst imputation
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(ape)
-library(PVR) #calculate eigen vectors and add them as a column in the imputation, seems to improve output
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-str(trait_data_1)
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-levels(as.factor(trait_filtered$Info_level)) #checking levels
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-str(trait_filtered_2)
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-                        "Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-levels(as.factor(t$Breeding_system))
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-levels(as.factor(t$Flower_morphology))
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-levels(as.factor(t$lifespan))
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-#Explore patterns of missing data
-missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)
-sort(missing_data[missing_data >= 0], decreasing=T)
-#nectar values all above 50% except presence/absence
-#then, just one cololumn with 68% missing data, then one with 35% and then 20% and 10%. The rest under 5%.
-#it is recommended to remove columns over 50% but we are particulary interested in having numeric levels of quantitative selfing 
-#we are going to work just with presence/absence of nectar
-#we will perform further analysis just with a subset with the quantitative values o nectar (very interesting data and diffciult to obtain)
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-         "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-         "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-         "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-         "Pollen_per_flower")]
-
-#check missing data now
-missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)*100
-sort(missing_data[missing_data >= 0], decreasing=T)
-
-missing_data <- unlist(lapply(t, function(x) nrow(t)-sum(is.na(x))))
-sum(missing_data)
-
-#Number of missing values on the datset
-#vis_miss(t[,c(6:20)])
-#9.9% percentage of missing values]
-
-#Checking number of filled cells/ just selecting variables used in the manuscript; nectar ul should be accounted too and it has been considered but
-#not added to run this code
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-str(t)
-
-#Impute data considering phylogenetic distance of species
-#it improves quality of imputation
-#https://doi.org/10.1111/2041-210X.12232 see ref for method comparisons with and without imputation
-
-#Multiple imputation process with phylogeny --> Missforest
-#https://doi.org/10.1111/2041-210X.12232
-#althought it does not have an option we are going to add it as a column
-
-#Before data imputation I need to calculate the phylo of the species
-#remove not found species that do not run with get tree
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-levels(factor(t$Species_all))
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-#Select just columns with traits
-t <- t[c("Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-         "Pollen_per_flower")]
-
-#################################################
-#3)SUMMARY OF THE DATA|ALL COLS CONSIDERED!
-#################################################
-##Number of filled cells
-#nrow(t) * 16 - sum(is.na(t))#[1] 20737
-##Dimension of the dataset
-#nrow(t) * 16#[1] 24096
-##Number of missing values
-#sum(is.na(t))#[1] 3359
-##Percentage of filled cells
-#sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 86.87993
-##Percentage of missing values
-#sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 13.12007
-#
-#
-
-#Function to specify number of decimals
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-no_missing <- specify_decimal(sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
-missing <- specify_decimal(sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
-
-colnames(t) <- c("Breeding system","Compatibility system",
-         "Autonomous selfing qualitative","Autonomous selfing quantitative", "Flower shape", "Flower symmetry", 
-         "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 
-         "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar per flower (microlitres)", "Nectar per flower (miligrames)", "Nectar concentration (%)", "Pollen grains per flower")
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-levels <-
-  (missing.values  %>% filter(isna == T) %>% arrange(desc(pct)))$key
-
-percentage.plot <- missing.values %>%
-  ggplot() +
-  geom_bar(aes(x = reorder(key, desc(pct)), 
-               y = pct, fill=isna), 
-           stat = 'identity', alpha=0.8) +
-  scale_x_discrete(limits = levels) + theme_bw()+
-  scale_fill_manual(name = "", 
-                    values = c('#57a340', '#d24513'), labels = c("Present values", "Missing values")) +
-  coord_flip() +
-  labs(title = "", x =
-         '', y = "")+  scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
-  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))
-
-percentage.plot
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Supplementary Fig.
-S2 |  Phylogenetic informed principal component analysis for the species that did not have missing values.}"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10}
 setwd("~/R_Projects/Reproductive Traits")
@@
       theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_complete_cases.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-#PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-pc3 <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.015, 0.03, 0.07), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,5.2,5,5.25,6.3,6)), y = -(PCAloadings$PC2*c(4,4.75,4,4.5,5,5.5)+c(0,0,0,0,-0.04,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-pc3(PC)
-
-```
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28,  fig.cap="\\textbf{Supplementary Fig.
-S3 | Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation.} The superior (plots a, b and c) and lower (plots d, e and f) panels show visitation rates on the main axes of trait variation with and without \\emph{Apis mellifera}, respectively."}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot_apis <- readRDS("Plot_apis.rds")
-
-plot_apis
-
-```
-
-\elandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Supplementary Fig.
-S4 | Regression tree analyses.} Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
-"}
-
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
-########################################################################################################################################################
-#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
-
-library(rpart.plot)
-library(rpart)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
-nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
-d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")
-
-#run  regression trees of the 3 metrics
-set.seed(1)
-tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0054559,minbucket=50)
-
-set.seed(1)
-tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0084459,minbucket=50)
-
-set.seed(1)
-tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0072192 , minbucket=50) #10
-
-#NECTAR AND POLEN DATA
-v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
-nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
-d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
-
-#Set correct colnames for plotting
-colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-set.seed(2)
-tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
-
-set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
-
-set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)
-
-par(mfrow=c(3,2))
-
-rpart.plot(tree_1, box.palette="GnOr", main="(a) Interaction frequency for all species", cex.main=1.75,tweak = 1.10) 
-rpart.plot(tree1, box.palette="GnOr", main="(b) Interaction frequency for subset with floral rewards", cex.main=1.75,tweak = 1.10)
-
-rpart.plot(tree_2, box.palette="GnOr", main="(c) Normalized degree for all species", cex.main=1.75,tweak = 1.10)
-rpart.plot(tree2, box.palette="GnOr", main="(d) Normalized degree for subset with floral rewards", cex.main=1.75,tweak = 1.10)
-
-rpart.plot(tree_3, box.palette="GnOr", main="(e) Specialization for all species", cex.main=1.75,tweak = 1.10) 
-rpart.plot(tree3, box.palette="GnOr", main="(f) Specialization for subset with floral rewards", cex.main=1.75,tweak = 1.10)
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Supplementary Fig.
-S5 | PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species.}"}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-pc3 <- function(PC, x="PC1", y="PC3") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC3 ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,4.8,7.1,5.5)), y = -(PCAloadings$PC2*c(-3.2,4.5,3.75,8.4,5,5.5)+c(0,0,0,0,-0.08,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-pc3(PC)
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Supplementary Fig.
-S6 | Phylogenetic informed principal component analysis for the subset of species with floral rewards.}"}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
+            axis.title=element_text( size = rel(1.6)),
             axis.text=element_text(size = rel(1.75), color = "black"),
@@
   #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height", "Nectar","Pollen" )
+#  rownames(PC$L) <- c("Selfing", "Flower number", "Flower #Size", "Style length", "Ovule number", "Plant height", #"Nectar","Pollen" )
+
+   rownames(PC$L) <- c("", "", "", "", "", "", "","" )
 
@@
 ```
-
-\newpage
-\thispagestyle{empty}
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Supplementary Fig.
-S7 | Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species.} Categories that differ significantly are denoted with a different letter."}
-
-########################################################################################################################################################
-#CORRELATION BETWEEN QUALITATIVE VARIABLES AND PC's
-########################################################################################################################################################
-#NOTES
-#I did not include the qualitative variables when I prepare the data for the PPCA
-#So I have to recalculate the ata here with the qualitative variables
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(emmeans)
-library(ggplot2)
-library(patchwork)
-library(dplyr)
-
-theme_ms <- function(base_size=10, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(1.3)),
-           axis.text=element_text(size = rel(1.1), color = "black"),
-           panel.border=element_rect(color="black",size=1.2),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           legend.position = "none",
-           plot.title = element_text(face = "bold",size = rel(1.45)),
-           plot.subtitle = element_text(face = "bold",size = rel(1.3))
-     ))
-}
-
-########################################################################################################################################################
-setwd("~/R_Projects/Reproductive Traits")
-
-#LOAD DATA
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-dat <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-########################################################################################################################################################
-#remove not found species, cannot do PCA with unequal numbers of rows
-cols.num <- c("Family_all","Genus_all","Species_all")
-dat[cols.num] <- sapply(dat[cols.num],as.character)
-dat$Species_all <- gsub("Species_all_", "", dat$Species_all)
-########################################################################################################################################################
-#3) REMOVE OUTLIERS, OUT OF 2.5-97.5 RANGE WHICH HELPS IMPUTATION PROCESS. SEE ARTICLE FOR REF.
-########################################################################################################################################################
-dat_cleaning <- dat[,]
-#CHECK LEVELS
-
-dat_cleaning_1 <- dat_cleaning %>%
-  filter(between(Flowers_per_plant, quantile(Flowers_per_plant, 0.025), quantile(Flowers_per_plant, 0.975)))
-
-dat_cleaning_2 <- dat_cleaning_1 %>%
-  filter(between(Corolla_diameter_mean, quantile(Corolla_diameter_mean, 0.025), quantile(Corolla_diameter_mean, 0.975)))
-
-dat_cleaning_3 <- dat_cleaning_2 %>%
-  filter(between(Style_length, quantile(Style_length, 0.025), quantile(Style_length, 0.975)))
-
-dat_cleaning_4 <- dat_cleaning_3 %>%
-  filter(between(Ovule_number, quantile(Ovule_number, 0.025), quantile(Ovule_number, 0.975)))
-
-dat_cleaning_5 <- dat_cleaning_4 %>%
-  filter(between(Plant_height_mean_m, quantile(Plant_height_mean_m, 0.025), quantile(Plant_height_mean_m, 0.975)))
-
-final_d <- dat_cleaning_5[,]
-
-pca_data <- as.data.frame(phyl_pca_forest$S)
-
-d <- cbind(final_d, pca_data)
-
-#Prepare qualitative variables
-d$Compatibility_system[d$Compatibility_system=="dioecious"] <- "Unisexual flowers"
-d$Compatibility_system[d$Compatibility_system=="monoecious"] <- "Unisexual flowers"
-d$Compatibility_system[d$Compatibility_system=="partially_self_compatible"] <- "Partially self compatible"
-d$Compatibility_system[d$Compatibility_system=="self_compatible"] <- "Self compatible"
-d$Compatibility_system[d$Compatibility_system=="self_incompatible"] <- "Self incompatible"
-d$Compatibility_system <- factor(d$Compatibility_system, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-d$life_form[d$life_form=="herb"] <- "Herb"
-d$life_form[d$life_form=="shrub"] <- "Shrub"
-d$life_form[d$life_form=="tree"] <- "Tree"
-d$life_form[d$life_form=="vine"] <- "Shrub"
-
-d$Flower_symmetry[d$Flower_symmetry=="actinomorphic"] <- "Actinomorphic"
-d$Flower_symmetry[d$Flower_symmetry=="zygomorphic"] <- "Zygomorphic"
-
-d$Flower_symmetry[d$Flower_symmetry=="Funnelform"] <- "Campanulate"
-d$Flower_symmetry[d$Flower_symmetry=="Spike"] <- "Brush"
-
-d$Flower_morphology[d$Flower_morphology=="Funnelform"] <- "Campanulate"
-d$Flower_morphology[d$Flower_morphology=="Spike"] <- "Brush"
-
-d$Nectar_presence_absence[d$Nectar_presence_absence=="yes"] <- "Yes"
-d$Nectar_presence_absence[d$Nectar_presence_absence=="no"] <- "No"
-
-#The other qualitative are ok
-
-#All principal components are normally distributed
-#Convert to factor before running model
-d[sapply(d, is.character)] <- lapply(d[sapply(d, is.character)], as.factor)
-
-#Run model
-model1 <- lm(PC1 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
-model2 <- lm(PC2 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
-
-####################################################################################################################################################################################################################################
-#1) BREEDING SYSTEM
-####################################################################################################################################################################################################################################
-model_breeding_1 <- emmeans(model1, "Breeding_system")
-breeding_1 <- as.data.frame(model_breeding_1[1:3])
-breed1 <- multcomp::cld(model_breeding_1, alpha = 0.10, Letters = LETTERS)
-
-breed_1 <- ggplot(breed1,aes(x= Breeding_system,y= emmean,
-               label = .group)) +theme_minimal()+
-  geom_point(data = breed1, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "(a) Breeding system")+
-  theme(plot.title = element_text(hjust=0.5, size=25, face="bold"))+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-model_breeding_2 <- emmeans(model2, "Breeding_system")
-breeding_2 <- as.data.frame(model_breeding_2[1:3])
-breed2 <- multcomp::cld(model_breeding_2, alpha = 0.10, Letters = LETTERS)
-
-breed_2 <- ggplot(breed2,aes(x= Breeding_system,y= emmean,
-             label = .group)) +theme_minimal()+
-  geom_point(data = breed2, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "(b) Breeding system")+
-  theme(plot.title = element_text(hjust=0.5,size=25, face="bold") )+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-########################################################################################################################################################
-#2) COMPATIBILITY
-########################################################################################################################################################
-model_com <- emmeans(model1, "Compatibility_system")
-
-d <- as.data.frame(model_com[1:4])
-comp1 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
-
-comp_1 <- ggplot(comp1,aes(x= Compatibility_system,y= emmean,
-  label = .group)) +theme_minimal()+
-  geom_point(data = comp1, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
-  width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(c) Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
-
-model_com <- emmeans(model2, "Compatibility_system")
-d <- as.data.frame(model_com[1:4])
-comp2 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
-
-comp_2 <- ggplot(comp2,aes(x= Compatibility_system,y= emmean,
-  label = .group)) +theme_minimal()+
-  geom_point(data = comp2, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
-  width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(d) Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
-
-########################################################################################################################################################
-#3) LIFESPAN
-########################################################################################################################################################
-model_lif_1 <- emmeans(model1, "lifespan")
-lif_1 <- as.data.frame(model_lif_1[1:2])
-lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
-
-lifespan_1 <- ggplot(lif_1,aes(x= lifespan,y= emmean,
-             label = .group)) +theme_minimal()+
-  geom_point(data = lif_1, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "(e) Lifespan")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-model_lif_2 <- emmeans(model2, "lifespan")
-lif_2 <- as.data.frame(model_lif_2[1:2])
-lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
-
-lifespan_2 <- ggplot(lif_2,aes(x= lifespan,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_2, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "(f) Lifespan")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")
-
-########################################################################################################################################################
-# 4) LIFE FORM
-########################################################################################################################################################
-
-model_lif_1 <- emmeans(model1, "life_form")
-lif_1 <- as.data.frame(model_lif_1[1:3])
-lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
-
-lifeform_1 <- ggplot(lif_1,aes(x= life_form,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_1, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "(g) Life form")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-model_lif_2 <- emmeans(model2, "life_form")
-lif_2 <- as.data.frame(model_lif_2[1:3])
-lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
-
-lifeform_2 <- ggplot(lif_2,aes(x= life_form,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_2, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "(h) Life form")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-########################################################################################################################################################
-# 5) FLOWER MORPHOLOGY
-########################################################################################################################################################
-model_flo_1 <- emmeans(model1, "Flower_morphology")
-flo_1 <- as.data.frame(model_flo_1[1:6])
-flo_1 <- multcomp::cld(model_flo_1, alpha = 0.10, Letters = LETTERS)
-
-shape_1 <- ggplot(flo_1,aes(x= Flower_morphology,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_1, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(i) Flower shape")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")
-
-model_flo_2 <- emmeans(model2, "Flower_morphology")
-flo_2 <- as.data.frame(model_flo_2[1:6])
-flo_2 <- multcomp::cld(model_flo_2, alpha = 0.10, Letters = LETTERS)
-
-shape_2 <- ggplot(flo_2,aes(x= Flower_morphology,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_2, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(j) Flower shape")+
-   geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
-
-########################################################################################################################################################
-#6) FLOWER SYMMETRY
-########################################################################################################################################################
-model_flo_sym_1 <- emmeans(model1, "Flower_symmetry")
-flo_sym_1 <- as.data.frame(model_flo_sym_1[1:2])
-flo_sym_1 <- multcomp::cld(model_flo_sym_1, alpha = 0.10, Letters = LETTERS)
-
-symmetry_1 <-ggplot(flo_sym_1,aes(x= Flower_symmetry,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_sym_1, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "(k) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
-
-model_flo_sym_2 <- emmeans(model2, "Flower_symmetry")
-flo_sym_2 <- as.data.frame(model_flo_sym_2[1:2])
-flo_sym_2 <- multcomp::cld(model_flo_sym_2, alpha = 0.10, Letters = LETTERS)
-
-symmetry_2 <- ggplot(flo_sym_2,aes(x= Flower_symmetry,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = flo_sym_2, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title = "(l) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-########################################################################################################################################################
-#7) NECTAR
-########################################################################################################################################################
-model_nec <- emmeans(model1, "Nectar_presence_absence")
-
-model_nec_1 <- emmeans(model1, "Nectar_presence_absence")
-nec_1 <- as.data.frame(model_nec_1[1:2])
-nec_1 <- multcomp::cld(model_nec_1, alpha = 0.10, Letters = LETTERS)
-
-nectar_1 <- ggplot(nec_1,aes(x= Nectar_presence_absence,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = nec_1, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "(m) Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-model_nec_2 <- emmeans(model2, "Nectar_presence_absence")
-nec_2 <- as.data.frame(model_nec_2[1:2])
-nec_2 <- multcomp::cld(model_nec_2, alpha = 0.10, Letters = LETTERS)
-
-nectar_2 <-ggplot(nec_2,aes(x= Nectar_presence_absence,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = nec_2, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "(n) Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")
-
-#PLOT!
-
-breed_1 + breed_2+ comp_1+ comp_2+ lifespan_1+ lifespan_2+ lifeform_1+ lifeform_2+ shape_1+ shape_2+
-symmetry_1+ symmetry_2+ nectar_1+ nectar_2 + plot_layout(ncol = 2)
-
-```
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="\\textbf{Supplementary Fig.
-S8 | Visitation rate of the main bee families on the main axes of trait variation.} Fitted posterior estimates of the visitation rate of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
-We omitted in the plotting area points over percentile 95 \\% percent due to extreme outliers."}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot <- readRDS("Plot_bee_families.rds")
-
-plot
-
-```
-
-\elandscape
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Supplementary Fig.
-S9 | Plant species level metrics across the three main axes of trait variation.}", fig.pos= "h"}
-
-library(brms) #modelling
-library(cmdstanr) #modelling
-library(cowplot) #panel of plots
-library(ggplot2) #plotting
-library(patchwork)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(3.5)),
-           axis.text=element_text(size = rel(2.75), color = "black"),
-           legend.title=element_text(face="bold"),
-           legend.text=element_text(),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(0.4, 'lines'),
-           panel.border=element_rect(color="black",size=3),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-#########
-
-setwd("~/Dropbox/PhD/R/Chapter_2")
-
-#read plot generated in other rmd, bms and stan are giving trouble here... This file is created in Species_Level_Metric_Pcs
-
-plot_metrics_pcs <- readRDS("plot_metrics_pcs.rds")
-
-plot_metrics_pcs
-
-```
-
-\elandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Supplementary Fig.
-S10 | Pearson correlation between the product of flower number-flower size and autonomous selfing level.}", fig.pos= "h"}
-
-theme_ms <- function(base_size=18, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(2.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-#LOAD LIBRARIES
-library(ggplot2)
-library(ggpubr)
-
-#LOAD DATA
-dat <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-
-#CONDUCT PRODUCT FLOWER NUMBER-FLOWER SIZE
-dat$Product <-      log(dat$Flowers_per_plant * dat$Corolla_diameter_mean+1)
-
-ggscatter(dat, x = "Autonomous_selfing_level_fruit_set", y = "Product", 
-          add = "reg.line", conf.int = TRUE,
-          cor.coef = TRUE, cor.method = "pearson",size=5,cor.coef.size=15,
-          xlab = "Autnomous selfing", ylab = "Product flower size-number") +
-  theme_ms() +ylim(0,16)
-
-```

### 2023-02-14 Supplementary_Material/Figures/Global_trait_spectrum_PC3.Rmd
organising files for what it seems it could be the final version of it

--- 2022-01-27 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
@@
 ---
-#title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant reproductive traits determine interactions with floral visitors}
-
-output: 
-  pdf_document:
-    extra_dependencies: ["float"]
-header-includes:
-- \usepackage{pdflscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
-- \usepackage{float}
-- \usepackage{caption}
-- \usepackage{setspace}\doublespacing
-- \usepackage{soul}
-- \floatplacement{figure}{H}
-- \usepackage{afterpage}
-- \usepackage{placeins}
-- \usepackage{graphicx}
-- \usepackage{floatpag}
-
-fontsize: 12pt
-
+title: ""
+output: pdf_document
 ---
 
-```{r echo=FALSE,warning=FALSE}
-knitr::opts_chunk$set(fig.pos = "h", out.extra = "")
-
-```
-
-\captionsetup[figure]{labelformat=empty}
-\captionsetup[table]{labelformat=empty}
-\captionsetup[table]{font={stretch=1.2}}
-
-\singlespacing
-
-\vspace{2cm}
-
-# Supplementary information for:
-
-## Trade-offs among plant reproductive traits determine interactions with floral visitors
-
-\textbf{Jose B. Lanuza*, Romina Rader, Jamie Stavert, Liam K. Kendall, Manu E. Saunders and Ignasi Bartomeus}
-
-\textbf{*Corresponding author}
-**E-mail: barragansljose@gmail.com**
-
-**This pdf includes:**
-
-Supplementary text
-
-Tables S1 to S5
-
-Figures S1 to S10
-
-\doublespacing
-
-<!--
-
-__Supplementary text__
-
-Description of the traits compiled in this study with an illustrative figure of the main flower morphologies (Supplementary text Fig 1)
-
-\doublespacing
-\singlespacing
-
-__Supplementary Tables__
-
-Supplementary Table S1: List of the 28 plant-pollinator studies used to build the plant trait database
-
-Supplementary Table S2: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species
-
-Supplementary Table S3: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity
-
-Supplementary Table S4: Statistical association between the different categorical variables and the fisrt three main axes of trait variation with the full set of species
-
-Supplementary Table S5: Phylogenetic signal of the different quantitative traits
-
-\doublespacing
-\singlespacing
-
-__Supplementary Figures__
-
-Supplementary Fig. S1: Percentage of present and missing values of the different plant traits
-
-Supplementary Fig. S2: Phylogenetic informed principal component analysis for the species that did not have missing values
-
-Supplementary Fig. S3: Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation
-
-Supplementary Fig. S4: Regression tree analyses
-
-Supplementary Fig. S5: PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species
-
-Supplementary Fig. S6: Phylogenetic informed principal component analysis for the subset of species with floral rewards.
-
-Supplementary Fig. S7: Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species
-
-Supplementary Fig. S8: Presence-absence of interaction and visitation rate of the main bee families on the main axes of trait variation
-
-Supplementary Fig. S9:  Plant species level metrics across the three main axes of trait variation
-
-Supplementary Fig. S10: Pearson correlation between the product of flower number-flower size and autonomous selfing level
-
--->
-
-\newpage
-
-## Supplementary Information Text
-
-__Description of the traits compiled in this study__
-
-_Reproductive traits_
-
--	Breeding system: The different plant species were classified in hermaphrodite, dioecious and monoecious species.
-Intermediate breeding systems or more complex ones were also annotated but all the species were divided into these three main categories for simplicity of the analysis.
-
--	Selfing level: We recorded the selfing level of the different species with both quantitative and qualitative data.
-The qualitative data was divided in four main categories, high selfers, medium selfers, low selfers and none which was for the species that were unable to self-pollinate.
-In addition, quantitative data was also divided into these four categories with the following criteria: from 0% to lower than 1% ‘none’, from 1% to 25% ‘low’, from 26% to 75% ‘medium’ and from 76% to 100%  ‘high’.
-
--	Compatibility system: The different species were divided in three main categories in order to know their ability to self-pollinate.
-These categories were self-compatible, partially self-compatible and self-incompatible species.
-The field of selfing level is partly complementary to the compatibility system but is important to note that not all the self-compatible species or partially self-compatible species will self-pollinate.
-
-_Floral traits_
-
--	Flower symmetry: We also recorded if the flowers were bilaterally symmetrical “zygomorphic” or were radially symmetrical “actinomorphic”.
-
--	Flower and inflorescence size: We searched for flower length and flower and inflorescence width (mm) for all species.
-When possible, we calculated the not found measurements with the help of online images and  the software ImageJ.
-
--	Flower number per plant: We compiled information about the number of flowers per plant for all species.
-However, this field was rare to find and we also used online images of the different species in order to calculate rough numbers of flowers per plant.
-We referenced all the filled fields in order to be able to follow the images that were used for these counts.
-It is important to note, that these numbers are not pretended to be the exact number of flowers per species but an approximate indicator of the reproductive investment for the different species that allow the macroecological analysis of this field.
-
--	Ovule number: We searched for the number of ovules per flower for all the different species.
-The number of ovules of Asteraceae species are considered as the total number of ovules per capitulum.
-Many species were filled by genus or family level because the number of ovules in this taxonomic groups is considered to be mostly constant (e.g., Lamiaceae Boraginaceae or Apiaceae).
-
--	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape.
-We divided the flowers in 8 main different categories: open, bowl, tube, campanulate, funnelform, papilionaceous, brush and capitulum.
-However, we ended up groupping all flowers on the following 6  morphological groups for analyses: tube, papilonaceous, open, capitulum, campanulate and brush (Supplementary Information Text Fig.
-1).
-
-```{r pressure, echo=FALSE, fig.cap="", out.width = '65%',fig.align='center', fig.cap="\\textbf{Supplementary Information Text Fig.
-1.}  Main floral morphologies considered in this study.
-All species were groupped within these categories for analysis: (a) tube, (b) papilonaceous, (c) open, (d) capitulum, (e) campanulate and (f) brush."}
-knitr::include_graphics("../Images/flower_shapes.png")
-```
-
--	Style length: The length of the style (mm) of the different species was also included. When possible, we calculated style length from images and illustrations on the online floras.
-
-- Nectar provision: We recorded the presence and absence of nectar for all species.
-In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration.
-In general terms, nectar data was rarely present and we tried to minimise the loss of information by filling some species at family level.
-For instance, Solanaceae species are described as nectarless, and species that belonged to this family were recorded with ‘absence’ of nectar.
-
-- Pollen grains per flower: We recorded pollen grains per flower for all species but this field was rarely described in the literature.
-When just the pollen:ovule ratio was found we converted it back to pollen grains by multiplying it by the average ovule number found for each species.
-
-_Vegetative traits_
-
-- Life form, life span and plant height: We divided the different plant species in 4 main categories: herbs, vines, shrubs and trees.
-Moreover, we also divided the species between short-lived species (annual, biennial and short-lived perennials) and perennial species (long-lived).
-Finally, we also searched for the average height (m) of the different species and annotated the maximum and minimum height when possible.
-We conducted the average between the maximum and minimum height to get an approximate average height of the species when the average was not indicated.
-
-\begin{landscape}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = "left"}
-setwd("~/R_Projects/Reproductive Traits")
-library(kableExtra)
-
-#Create data.frame with references
-
-`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1", "1", "1", "1", "1", "1", "1", "3", "1",
-                          "1", "1")
-
-#`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))
-
-`Network type` <- c(rep("Weighted web",  18), rep("Unweighted web",  4), "Weighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Weighted metaweb")
-
-`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
-                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard", "Bek", "Kato", "Kevan", "Ramirez",
-                    "Inouye","McMullen", "Primack", "Ramirez", "Robertson", "Traveset")
-
-Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003,2006,2000,1970,1989,1990, 1993, 1983, 1992, 1929, 2013)
-
-#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
-#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
-#"USA", "Ecuador")
-
-DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
-"https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
-"https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
-"/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
-"https://doi.org/10.1111/j.1365-2745.2010.01732.x", "https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510",
-"https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis", "Unpublished, Master thesis", "http://hdl.handle.net/2433/156116",
-"https://doi.org/10.2307/2258569", "https://doi.org/10.2307/2388282", "http://hdl.handle.net/2433/156099", "https://biostor.org/reference/244737", "https://doi.org/10.1080/0028825X.1983.10428561",
-"https://doi.org/10.1111/j.1095-8339.1992.tb00294.x", "https://doi.org/10.5962/bhl.title.11538", "https://doi.org/10.1098/rspb.2012.3040")
-
-references <- data.frame(`First author`, Year, `Number of networks`,`Network type`,   DOI)
-
-colnames(references) <- c("First author", "Year", "Web N.",  "Network type",  "DOI")
-
-library(dplyr)
- references %>%
- arrange(`First author`)%>%
-kable("latex", longtable = T, booktabs = T,linesep = "\\addlinespace",
-             caption = "\\textbf{Table S1.
-List of the 28 plant-pollinator studies used to build the plant trait database.
-Each study is shown with the first author that conducted the study, number of networks or metawebs that contains, type of information that contains (weighted or unweighted),  the structure (web or metaweb), year of publication and digital object identifier or permanent link for each study.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, repeat_header_method="replace" ,full_width=F,position = "left")
-
-```
-
-\end{landscape}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
- kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S2.
-Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Microlitres of Nectar per flower" , "Pollen per flower","Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
-kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S3.
-Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-d <- readRDS("Data/RData/table_categorical_tukey_test.rds")
-
-#Again im getting the same error on this rmd so I run it on another one, save the dataframe and plot it here
-
-#Plot table
-#Add latex format in markdown
-
-kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Table S4.
-Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-#SELFING
-selfing <- readRDS("Data/RData/selfing_phylo.rds")
-#FLOWER NUMBER
-flower_n <- readRDS("Data/RData/flower_n_phylo.rds")
-#INFLO WIDTH
-inflow_width <- readRDS("Data/RData/inflow_width_phylo.rds")
-#FLOWER WIDTH
-flower_width <- readRDS("Data/RData/flower_width_phylo.rds")
-#FLOWER LENGHT
-flower_length <- readRDS("Data/RData/flower_length_phylo.rds")
-#STYLE LENGTH
-style_n <- readRDS("Data/RData/style_n_phylo.rds")
-#OVULE NUMBER
-ovule_n <- readRDS("Data/RData/ovule_n_phylo.rds")
-#PLANT HEIGHT
-plant_height <- readRDS("Data/RData/plant_height_phylo.rds")
-#POLLEN
-pollen <- readRDS("Data/RData/pollen_phylo.rds")
-#Nectar ul
-nectar_ul <- readRDS("Data/RData/Nectar_ul_phylo.rds")
-
-#Not included at the end
-#Nectar mg
-#nectar_mg <- readRDS("Data/RData/Nectar_mg_phylo.rds")
-#Nectar concentration
-nectar_con <- readRDS("Data/RData/Nectar_concentration_phylo.rds")
-
-#Select two decimals function
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-#LABELS
-label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Nectar per flower ($\\mu$l)", "Nectar concentration ($\\%$)","Pollen grains per flower")
-#LAMBDA
-lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, nectar_ul$lambda, nectar_con$lambda, pollen$lambda)
-#P-VALUE
-p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P,nectar_ul$P,  nectar_con$P, pollen$P)
-
-tabla <- data.frame(label, specify_decimal(lambda,2), specify_decimal(p_value,2))
-
-colnames(tabla) <- c("Functional traits", "Lambda", "P-value")
-
-kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,caption = "\\textbf{Table S5. Phylogenetic signal of the different quantitative traits.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Fig. S1.} Percentage of present and missing values of the different plant traits."}
-
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-
-########################################################################################################################################################
-#SCRIPT FOR DATA IMPUTATION
-########################################################################################################################################################
-#1) READ TRAIT DATA
-
-#2) CLEAN DATA AND RENAME LEVELS
-
-#3) EXPLORE PATTERNS OF MISSING DATA
-
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-
-#5) ICLUDE EIGENVALUES IN RAWDATA TO IMPROVE IMPUTATION OURPUT
-
-#6) IMPUTE DATA
-
-#7) SAVE IMPUTED DATA 
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(missMDA) #For missing values
-library(FactoMineR) #Produce pca biplot with individuals and variables
-library(factoextra)
-library(ggpubr) 
-library(missForest) #random forst imputation
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(ape)
-library(PVR) #calculate eigen vectors and add them as a column in the imputation, seems to improve output
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-str(trait_data_1)
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-levels(as.factor(trait_filtered$Info_level)) #checking levels
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-str(trait_filtered_2)
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-                        "Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-levels(as.factor(t$Breeding_system))
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-levels(as.factor(t$Flower_morphology))
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-levels(as.factor(t$lifespan))
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-#Explore patterns of missing data
-missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)
-sort(missing_data[missing_data >= 0], decreasing=T)
-#nectar values all above 50% except presence/absence
-#then, just one cololumn with 68% missing data, then one with 35% and then 20% and 10%. The rest under 5%.
-#it is recommended to remove columns over 50% but we are particulary interested in having numeric levels of quantitative selfing 
-#we are going to work just with presence/absence of nectar
-#we will perform further analysis just with a subset with the quantitative values o nectar (very interesting data and diffciult to obtain)
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-         "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-         "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-         "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-         "Pollen_per_flower")]
-
-#check missing data now
-missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)*100
-sort(missing_data[missing_data >= 0], decreasing=T)
-
-missing_data <- unlist(lapply(t, function(x) nrow(t)-sum(is.na(x))))
-sum(missing_data)
-
-#Number of missing values on the datset
-#vis_miss(t[,c(6:20)])
-#9.9% percentage of missing values]
-
-#Checking number of filled cells/ just selecting variables used in the manuscript; nectar ul should be accounted too and it has been considered but
-#not added to run this code
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-str(t)
-
-#Impute data considering phylogenetic distance of species
-#it improves quality of imputation
-#https://doi.org/10.1111/2041-210X.12232 see ref for method comparisons with and without imputation
-
-#Multiple imputation process with phylogeny --> Missforest
-#https://doi.org/10.1111/2041-210X.12232
-#althought it does not have an option we are going to add it as a column
-
-#Before data imputation I need to calculate the phylo of the species
-#remove not found species that do not run with get tree
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-levels(factor(t$Species_all))
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-#Select just columns with traits
-t <- t[c("Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-         "Pollen_per_flower")]
-
-#################################################
-#3)SUMMARY OF THE DATA|ALL COLS CONSIDERED!
-#################################################
-##Number of filled cells
-#nrow(t) * 16 - sum(is.na(t))#[1] 20737
-##Dimension of the dataset
-#nrow(t) * 16#[1] 24096
-##Number of missing values
-#sum(is.na(t))#[1] 3359
-##Percentage of filled cells
-#sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 86.87993
-##Percentage of missing values
-#sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 13.12007
-#
-#
-
-#Function to specify number of decimals
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-no_missing <- specify_decimal(sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
-missing <- specify_decimal(sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
-
-colnames(t) <- c("Breeding system","Compatibility system",
-         "Autonomous selfing qualitative","Autonomous selfing quantitative", "Flower shape", "Flower symmetry", 
-         "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 
-         "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar per flower (microlitres)", "Nectar per flower (miligrames)", "Nectar concentration (%)", "Pollen grains per flower")
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-levels <-
-  (missing.values  %>% filter(isna == T) %>% arrange(desc(pct)))$key
-
-percentage.plot <- missing.values %>%
-  ggplot() +
-  geom_bar(aes(x = reorder(key, desc(pct)), 
-               y = pct, fill=isna), 
-           stat = 'identity', alpha=0.8) +
-  scale_x_discrete(limits = levels) + theme_bw()+
-  scale_fill_manual(name = "", 
-                    values = c('#57a340', '#d24513'), labels = c("Present values", "Missing values")) +
-  coord_flip() +
-  labs(title = "", x =
-         '', y = "")+  scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
-  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))
-
-percentage.plot
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig.
-S2.}  Phylogenetic informed principal component analysis for the species that did not have missing values."}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_complete_cases.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-#PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-pc3 <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.015, 0.03, 0.07), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,5.2,5,5.25,6.3,6)), y = -(PCAloadings$PC2*c(4,4.75,4,4.5,5,5.5)+c(0,0,0,0,-0.04,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-pc3(PC)
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24,  fig.cap="\\textbf{Fig.
-S3.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation.
-The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates."}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot_apis <- readRDS("Plot_apis_non_apis.rds")
-
-plot_apis
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig.
-S4.} Regression tree analyses.
-Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
-"}
-
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
-########################################################################################################################################################
-#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
-
-library(rpart.plot)
-library(rpart)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
-nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
-d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")
-
-#run  regression trees of the 3 metrics
-set.seed(1)
-tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0054559,minbucket=50)
-
-set.seed(1)
-tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0084459,minbucket=50)
-
-set.seed(1)
-tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0072192 , minbucket=50) #10
-
-#NECTAR AND POLEN DATA
-v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
-nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
-d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
-
-#Set correct colnames for plotting
-colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-set.seed(2)
-tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
-
-set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
-
-set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)
-
-par(mfrow=c(3,2))
-
-rpart.plot(tree_1, box.palette="GnOr", main="A Interaction frequency for all species", cex.main=1.85,tweak = 1.10) 
-rpart.plot(tree1, box.palette="GnOr", main="B Interaction frequency for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-rpart.plot(tree_2, box.palette="GnOr", main="C Normalized degree for all species", cex.main=1.85,tweak = 1.10)
-rpart.plot(tree2, box.palette="GnOr", main="D Normalized degree for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-rpart.plot(tree_3, box.palette="GnOr", main="E Specialization for all species", cex.main=1.85,tweak = 1.10) 
-rpart.plot(tree3, box.palette="GnOr", main="F Specialization for subset with floral rewards", cex.main=1.85,tweak = 1.10)
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig.
-S5.} PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10}
 setwd("~/R_Projects/Reproductive Traits")
@@
 PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
+PC$S[,3] <- -PC$S[,3]
 
@@
 ```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig.
-S6.} Phylogenetic informed principal component analysis for the subset of species with floral rewards."}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-dat_cleaning_7 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen.rds")
-
-PC <- phyl_pca_forest_nectar_pollen
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-library(magick)
-
-#Images were made by Paula Martin
-PC$S[,1] <- -PC$S[,1]
-
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
-    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-  plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw()
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height", "Nectar","Pollen" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,4.8,4.8,5.5,5,5.5,5.8,6.5)), y = -(PCAloadings$PC2*c(4.8,4.4,4.15,5.35,5,4.7,5.75,6)+c(0,0,0,0,0,0,0,0)),
-                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-all_spp(PC)
-
-```
-
-\newpage
-\thispagestyle{empty}
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig.
-S7.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species.
-Categories that differ significantly are denoted with a different letter."}
-
-########################################################################################################################################################
-#CORRELATION BETWEEN QUALITATIVE VARIABLES AND PC's
-########################################################################################################################################################
-#NOTES
-#I did not include the qualitative variables when I prepare the data for the PPCA
-#So I have to recalculate the ata here with the qualitative variables
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(emmeans)
-library(ggplot2)
-library(patchwork)
-library(dplyr)
-
-theme_ms <- function(base_size=10, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(1.3)),
-           axis.text=element_text(size = rel(1.1), color = "black"),
-           panel.border=element_rect(color="black",size=1.2),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           legend.position = "none",
-           plot.title = element_text(face = "bold",size = rel(1.55)),
-           plot.subtitle = element_text(face = "bold",size = rel(1.4))
-     ))
-}
-
-########################################################################################################################################################
-setwd("~/R_Projects/Reproductive Traits")
-
-#LOAD DATA
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-dat <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-########################################################################################################################################################
-#remove not found species, cannot do PCA with unequal numbers of rows
-cols.num <- c("Family_all","Genus_all","Species_all")
-dat[cols.num] <- sapply(dat[cols.num],as.character)
-dat$Species_all <- gsub("Species_all_", "", dat$Species_all)
-########################################################################################################################################################
-#3) REMOVE OUTLIERS, OUT OF 2.5-97.5 RANGE WHICH HELPS IMPUTATION PROCESS. SEE ARTICLE FOR REF.
-########################################################################################################################################################
-dat_cleaning <- dat[,]
-#CHECK LEVELS
-
-dat_cleaning_1 <- dat_cleaning %>%
-  filter(between(Flowers_per_plant, quantile(Flowers_per_plant, 0.025), quantile(Flowers_per_plant, 0.975)))
-
-dat_cleaning_2 <- dat_cleaning_1 %>%
-  filter(between(Corolla_diameter_mean, quantile(Corolla_diameter_mean, 0.025), quantile(Corolla_diameter_mean, 0.975)))
-
-dat_cleaning_3 <- dat_cleaning_2 %>%
-  filter(between(Style_length, quantile(Style_length, 0.025), quantile(Style_length, 0.975)))
-
-dat_cleaning_4 <- dat_cleaning_3 %>%
-  filter(between(Ovule_number, quantile(Ovule_number, 0.025), quantile(Ovule_number, 0.975)))
-
-dat_cleaning_5 <- dat_cleaning_4 %>%
-  filter(between(Plant_height_mean_m, quantile(Plant_height_mean_m, 0.025), quantile(Plant_height_mean_m, 0.975)))
-
-final_d <- dat_cleaning_5[,]
-
-pca_data <- as.data.frame(phyl_pca_forest$S)
-
-d <- cbind(final_d, pca_data)
-
-#Prepare qualitative variables
-d$Compatibility_system[d$Compatibility_system=="dioecious"] <- "Unisexual flowers"
-d$Compatibility_system[d$Compatibility_system=="monoecious"] <- "Unisexual flowers"
-d$Compatibility_system[d$Compatibility_system=="partially_self_compatible"] <- "Partially self compatible"
-d$Compatibility_system[d$Compatibility_system=="self_compatible"] <- "Self compatible"
-d$Compatibility_system[d$Compatibility_system=="self_incompatible"] <- "Self incompatible"
-d$Compatibility_system <- factor(d$Compatibility_system, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-d$life_form[d$life_form=="herb"] <- "Herb"
-d$life_form[d$life_form=="shrub"] <- "Shrub"
-d$life_form[d$life_form=="tree"] <- "Tree"
-d$life_form[d$life_form=="vine"] <- "Shrub"
-
-d$Flower_symmetry[d$Flower_symmetry=="actinomorphic"] <- "Actinomorphic"
-d$Flower_symmetry[d$Flower_symmetry=="zygomorphic"] <- "Zygomorphic"
-
-d$Flower_symmetry[d$Flower_symmetry=="Funnelform"] <- "Campanulate"
-d$Flower_symmetry[d$Flower_symmetry=="Spike"] <- "Brush"
-
-d$Flower_morphology[d$Flower_morphology=="Funnelform"] <- "Campanulate"
-d$Flower_morphology[d$Flower_morphology=="Spike"] <- "Brush"
-
-d$Nectar_presence_absence[d$Nectar_presence_absence=="yes"] <- "Yes"
-d$Nectar_presence_absence[d$Nectar_presence_absence=="no"] <- "No"
-
-#The other qualitative are ok
-
-#All principal components are normally distributed
-#Convert to factor before running model
-d[sapply(d, is.character)] <- lapply(d[sapply(d, is.character)], as.factor)
-
-#Run model
-model1 <- lm(PC1 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
-model2 <- lm(PC2 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
-
-####################################################################################################################################################################################################################################
-#1) BREEDING SYSTEM
-####################################################################################################################################################################################################################################
-model_breeding_1 <- emmeans(model1, "Breeding_system")
-breeding_1 <- as.data.frame(model_breeding_1[1:3])
-breed1 <- multcomp::cld(model_breeding_1, alpha = 0.10, Letters = LETTERS)
-
-breed_1 <- ggplot(breed1,aes(x= Breeding_system,y= emmean,
-               label = .group)) +theme_minimal()+
-  geom_point(data = breed1, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "A Breeding system")+
-  theme(plot.title = element_text(hjust=0.5, size=25, face="bold"))+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-model_breeding_2 <- emmeans(model2, "Breeding_system")
-breeding_2 <- as.data.frame(model_breeding_2[1:3])
-breed2 <- multcomp::cld(model_breeding_2, alpha = 0.10, Letters = LETTERS)
-
-breed_2 <- ggplot(breed2,aes(x= Breeding_system,y= emmean,
-             label = .group)) +theme_minimal()+
-  geom_point(data = breed2, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "B Breeding system")+
-  theme(plot.title = element_text(hjust=0.5,size=25, face="bold") )+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-########################################################################################################################################################
-#2) COMPATIBILITY
-########################################################################################################################################################
-model_com <- emmeans(model1, "Compatibility_system")
-
-d <- as.data.frame(model_com[1:4])
-comp1 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
-
-comp_1 <- ggplot(comp1,aes(x= Compatibility_system,y= emmean,
-  label = .group)) +theme_minimal()+
-  geom_point(data = comp1, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
-  width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "C Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
-
-model_com <- emmeans(model2, "Compatibility_system")
-d <- as.data.frame(model_com[1:4])
-comp2 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
-
-comp_2 <- ggplot(comp2,aes(x= Compatibility_system,y= emmean,
-  label = .group)) +theme_minimal()+
-  geom_point(data = comp2, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
-  width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "D Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
-
-########################################################################################################################################################
-#3) LIFESPAN
-########################################################################################################################################################
-model_lif_1 <- emmeans(model1, "lifespan")
-lif_1 <- as.data.frame(model_lif_1[1:2])
-lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
-
-lifespan_1 <- ggplot(lif_1,aes(x= lifespan,y= emmean,
-             label = .group)) +theme_minimal()+
-  geom_point(data = lif_1, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "E Lifespan")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-model_lif_2 <- emmeans(model2, "lifespan")
-lif_2 <- as.data.frame(model_lif_2[1:2])
-lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
-
-lifespan_2 <- ggplot(lif_2,aes(x= lifespan,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_2, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "F Lifespan")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")
-
-########################################################################################################################################################
-# 4) LIFE FORM
-########################################################################################################################################################
-
-model_lif_1 <- emmeans(model1, "life_form")
-lif_1 <- as.data.frame(model_lif_1[1:3])
-lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
-
-lifeform_1 <- ggplot(lif_1,aes(x= life_form,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_1, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "G Life form")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-model_lif_2 <- emmeans(model2, "life_form")
-lif_2 <- as.data.frame(model_lif_2[1:3])
-lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
-
-lifeform_2 <- ggplot(lif_2,aes(x= life_form,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_2, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "H Life form")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-########################################################################################################################################################
-# 5) FLOWER MORPHOLOGY
-########################################################################################################################################################
-model_flo_1 <- emmeans(model1, "Flower_morphology")
-flo_1 <- as.data.frame(model_flo_1[1:6])
-flo_1 <- multcomp::cld(model_flo_1, alpha = 0.10, Letters = LETTERS)
-
-shape_1 <- ggplot(flo_1,aes(x= Flower_morphology,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_1, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "I Flower shape")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")
-
-model_flo_2 <- emmeans(model2, "Flower_morphology")
-flo_2 <- as.data.frame(model_flo_2[1:6])
-flo_2 <- multcomp::cld(model_flo_2, alpha = 0.10, Letters = LETTERS)
-
-shape_2 <- ggplot(flo_2,aes(x= Flower_morphology,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_2, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "J Flower shape")+
-   geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
-
-########################################################################################################################################################
-#6) FLOWER SYMMETRY
-########################################################################################################################################################
-model_flo_sym_1 <- emmeans(model1, "Flower_symmetry")
-flo_sym_1 <- as.data.frame(model_flo_sym_1[1:2])
-flo_sym_1 <- multcomp::cld(model_flo_sym_1, alpha = 0.10, Letters = LETTERS)
-
-symmetry_1 <-ggplot(flo_sym_1,aes(x= Flower_symmetry,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_sym_1, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "K Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
-
-model_flo_sym_2 <- emmeans(model2, "Flower_symmetry")
-flo_sym_2 <- as.data.frame(model_flo_sym_2[1:2])
-flo_sym_2 <- multcomp::cld(model_flo_sym_2, alpha = 0.10, Letters = LETTERS)
-
-symmetry_2 <- ggplot(flo_sym_2,aes(x= Flower_symmetry,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = flo_sym_2, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title = "L Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-########################################################################################################################################################
-#7) NECTAR
-########################################################################################################################################################
-model_nec <- emmeans(model1, "Nectar_presence_absence")
-
-model_nec_1 <- emmeans(model1, "Nectar_presence_absence")
-nec_1 <- as.data.frame(model_nec_1[1:2])
-nec_1 <- multcomp::cld(model_nec_1, alpha = 0.10, Letters = LETTERS)
-
-nectar_1 <- ggplot(nec_1,aes(x= Nectar_presence_absence,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = nec_1, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "M Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-model_nec_2 <- emmeans(model2, "Nectar_presence_absence")
-nec_2 <- as.data.frame(model_nec_2[1:2])
-nec_2 <- multcomp::cld(model_nec_2, alpha = 0.10, Letters = LETTERS)
-
-nectar_2 <-ggplot(nec_2,aes(x= Nectar_presence_absence,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = nec_2, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "N Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")
-
-#PLOT!
-
-breed_1 + breed_2+ comp_1+ comp_2+ lifespan_1+ lifespan_2+ lifeform_1+ lifeform_2+ shape_1+ shape_2+
-symmetry_1+ symmetry_2+ nectar_1+ nectar_2 + plot_layout(ncol = 2)
-
-```
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Fig.
-S8.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation.
-Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
-For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)"}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot <- readRDS("Plot_bee_families.rds")
-
-plot
-
-```
-
-\elandscape
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S9.} Plant species level metrics across the three main axes of trait variation.", fig.pos= "h"}
-
-library(brms) #modelling
-library(cowplot) #panel of plots
-library(ggplot2) #plotting
-library(patchwork)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(3.5)),
-           axis.text=element_text(size = rel(2.75), color = "black"),
-           legend.title=element_text(face="bold"),
-           legend.text=element_text(),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(0.4, 'lines'),
-           panel.border=element_rect(color="black",size=3),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-#########
-
-setwd("~/Dropbox/PhD/R/Chapter_2")
-
-#read plot generated in other rmd, bms and stan are giving trouble here... This file is created in Species_Level_Metric_Pcs
-
-plot_metrics_pcs <- readRDS("plot_metrics_pcs.rds")
-
-plot_metrics_pcs
-
-```
-
-\elandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S10.} Pearson correlation between the product of flower number-flower size and autonomous selfing level.", fig.pos= "h"}
-
-theme_ms <- function(base_size=18, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(2.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-#LOAD LIBRARIES
-library(ggplot2)
-library(ggpubr)
-
-#LOAD DATA
-dat <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-
-#CONDUCT PRODUCT FLOWER NUMBER-FLOWER SIZE
-dat$Product <-      log(dat$Flowers_per_plant * dat$Corolla_diameter_mean+1)
-
-ggscatter(dat, x = "Autonomous_selfing_level_fruit_set", y = "Product", 
-          add = "reg.line", conf.int = TRUE,
-          cor.coef = TRUE, cor.method = "pearson",size=5,cor.coef.size=15,
-          xlab = "Autnomous selfing", ylab = "Product flower size-number") +
-  theme_ms() +ylim(0,16)
-
-```

### 2023-02-14 Supplementary_Material/Figures/Globlas_Trait_Spectrum_Complete_Cases.Rmd
organising files for what it seems it could be the final version of it

--- 2021-08-16 Supplementary_Material/Supplementary_Material.Rmd
@@
 
-#Load data
+PC <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")
 dat_cleaning_5 <- readRDS("Data/RData/data_complete_cases.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")
 
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-#PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-pc3 <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.015, 0.03, 0.07), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,5.2,5,5.25,6.3,6)), y = -(PCAloadings$PC2*c(4,4.75,4,4.5,5,5.5)+c(0,0,0,0,-0.04,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-pc3(PC)
-
-```
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28,  fig.cap="\\textbf{Supplementary Fig.
-S3 | Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation.} The superior (plots a, b and c) and lower (plots d, e and f) panels show visitation rates on the main axes of trait variation with and without \\emph{Apis mellifera}, respectively."}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot_apis <- readRDS("Plot_apis.rds")
-
-plot_apis
-
-```
-
-\elandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Supplementary Fig.
-S4 | Regression tree analyses.} Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
-"}
-
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
-########################################################################################################################################################
-#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
-
-library(rpart.plot)
-library(rpart)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
-nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
-d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")
-
-#run  regression trees of the 3 metrics
-set.seed(1)
-tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0054559,minbucket=50)
-
-set.seed(1)
-tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0084459,minbucket=50)
-
-set.seed(1)
-tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0072192 , minbucket=50) #10
-
-#NECTAR AND POLEN DATA
-v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
-nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
-d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
-
-#Set correct colnames for plotting
-colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-set.seed(2)
-tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
-
-set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
-
-set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)
-
-par(mfrow=c(3,2))
-
-rpart.plot(tree_1, box.palette="GnOr", main="(a) Interaction frequency for all species", cex.main=1.75,tweak = 1.10) 
-rpart.plot(tree1, box.palette="GnOr", main="(b) Interaction frequency for subset with floral rewards", cex.main=1.75,tweak = 1.10)
-
-rpart.plot(tree_2, box.palette="GnOr", main="(c) Normalized degree for all species", cex.main=1.75,tweak = 1.10)
-rpart.plot(tree2, box.palette="GnOr", main="(d) Normalized degree for subset with floral rewards", cex.main=1.75,tweak = 1.10)
-
-rpart.plot(tree_3, box.palette="GnOr", main="(e) Specialization for all species", cex.main=1.75,tweak = 1.10) 
-rpart.plot(tree3, box.palette="GnOr", main="(f) Specialization for subset with floral rewards", cex.main=1.75,tweak = 1.10)
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Supplementary Fig.
-S5 | PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species.}"}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-pc3 <- function(PC, x="PC1", y="PC3") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC3 ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,4.8,7.1,5.5)), y = -(PCAloadings$PC2*c(-3.2,4.5,3.75,8.4,5,5.5)+c(0,0,0,0,-0.08,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-pc3(PC)
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Supplementary Fig.
-S6 | Phylogenetic informed principal component analysis for the subset of species with floral rewards.}"}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-dat_cleaning_7 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen.rds")
-
-PC <- phyl_pca_forest_nectar_pollen
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-library(magick)
-
-#Images were made by Paula Martin
-
+#plot same order as the other plots
 PC$S[,2] <- -PC$S[,2]
@@
   #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height", "Nectar","Pollen" )
+  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height")
 
   PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.85,5.5,5.3,5.5,6.1,5.75,5.8,6)), y = -(PCAloadings$PC2*c(4.8,4.8,4.65,5.65,5,5.1,5.75,5)+c(0,0,0,0,0,0,0,0)),
+  plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.2,5.3,5,6.25,6.3,6.15)), y = -(PCAloadings$PC2*c(4.2,5,4,6.5,5,5.5)+c(0,0,0,0,0.25,0)),
                           label = PCAloadings$Variables, color="black",fontface =2,size=4.5)

### 2023-02-14 Supplementary_Material/Figures/Missing_Data_2_Subset_Floral_Rewards.Rmd
organising files for what it seems it could be the final version of it

---
output:
  pdf_document: default
  html_document: default

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000}

#Set working directory
setwd("~/R_Projects/Reproductive Traits")

########################################################################################################################################################
#SCRIPT FOR DATA IMPUTATION FOR THE SUBSET OF QUANTITATIVE DATA OF NECTAR
########################################################################################################################################################
#1) READ TRAIT DATA

#2) CLEAN DATA AND RENAME LEVELS

#3) EXPLORE PATTERNS OF MISSING DATA

#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION

#5) ICLUDE EIGENVALUES IN RAWDATA TO IMPROVE IMPUTATION OUTPUT

#6) IMPUTE DATA

#7) SAVE DATA
########################################################################################################################################################
#LOAD LIBRARIES
library(readxl) #read excel file (trait data)
library(dplyr) #data manipulation
library(missMDA) #For missing values
library(FactoMineR) #Produce pca biplot with individuals and variables
library(factoextra)
library(ggpubr) 
library(missForest) #random forst imputation
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(ape)
library(PVR) #calculate eigen vectors and add them as a column in the imputation, seems to improve output
library(visdat) #VISUALIZE MISSING DATA
library(tidyverse)
########################################################################################################################################################
#1) READ TRAIT DATA
########################################################################################################################################################
#load data
trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
########################################################################################################################################################
#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
########################################################################################################################################################
#####
#A) CLEAN DATA
#####
#select just filled rows
trait_data_1 <- trait_data[1:1712,]

#filter data, select species with flower level info and capitulum
trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
levels(as.factor(trait_filtered$Info_level)) #checking levels
#remove NA's and duplicated species
trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA
trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]

str(trait_filtered_2)
#select columns of interest
t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
                        "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant",  "Floral_unit_width",
                        "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
                        "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]

########################################################################################################################################################
#2 DATA PREPARATION
########################################################################################################################################################
#RENAME LEVELS 
#Breeding_system
t$Breeding_system <- as.character(t$Breeding_system)
t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
#change to capital letters
t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
levels(as.factor(t$Breeding_system))
t$Breeding_system <- as.factor(t$Breeding_system)

#Now 3 levels
#Flower_morphology
t$Flower_morphology <- as.character(t$Flower_morphology)
t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
levels(as.factor(t$Flower_morphology))
t$Flower_morphology <- as.factor(t$Flower_morphology)

#Life span
t$lifespan <- as.character(t$lifespan )
t$lifespan[t$lifespan=="annual"] <- "short_lived"
t$lifespan[t$lifespan=="biennial"] <- "short_lived"
t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
t$lifespan[t$lifespan=="perennial"] <- "Perennial"
levels(as.factor(t$lifespan))
t$lifespan <- as.factor(t$lifespan )

#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)

#Now we just select presence/absence of nectar
#select columns of interest
t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Floral_unit_width",
         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
         "Plant_height_mean_m","Nectar_presence_absence", "Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]

########################################################################################################################################################
#3) EXPLORE PATTERNS OF MISSING DATA
########################################################################################################################################################
#check missing data now
missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)*100
sort(missing_data[missing_data >= 0], decreasing=T)

#seems ok to impute, just 36% percent of missing data in this column now.

########################################################################################################################################################
#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
########################################################################################################################################################
#Convert to factor 
cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used

#remove not found species that do not run with get tree
cols.num <- c("Family_all","Genus_all","Species_all")
t[cols.num] <- sapply(t[cols.num],as.character)
t$Species_all <- gsub("Species_all_", "", t$Species_all)

t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species

#remove species that are not until species level
#ALL THE SPECIES WITH SP. ARE DELETD
t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
#CHECK LEVELS
levels(factor(t$Species_all))

#Make these NA's as NA
t$Species_all[t$Species_all=="NA"] <- NA
t$Family_all[t$Family_all=="NA"] <- NA
t$Genus_all[t$Genus_all=="NA"] <- NA
#remove NA's
t <- t[!is.na(t$Family_all),]
t <- t[!is.na(t$Species_all),]
t <- t[!is.na(t$Genus_all),]
#Explore missing data
#check missing data now
missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)*100
sort(missing_data[missing_data >= 0], decreasing=T)

#Subset species that have info for at least one of these floral traits
t_nectar <- t[!is.na(t$Nectar_concentration) | !is.na(t$Nectar_ul)| !is.na(t$Nectar_mg)| !is.na(t$Pollen_per_flower),]
nrow(t_nectar)

#Select just columns with traits
t_nectar <- t_nectar[c("Breeding_system","Compatibility_system",
                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
         "Pollen_per_flower")]
#################################################
#3)SUMMARY OF THE DATA|ALL COLS CONSIDERED!
#################################################
##Number of filled cells
#nrow(t) * 16 - sum(is.na(t))#[1] 20737
##Dimension of the dataset
#nrow(t) * 16#[1] 24096
##Number of missing values
#sum(is.na(t))#[1] 3359
##Percentage of filled cells
#sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 86.87993
##Percentage of missing values
#sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 13.12007
#
#

#Function to specify number of decimals
specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))

no_missing <- specify_decimal(sum(!is.na(t_nectar))/(sum(is.na(t_nectar))+sum(!is.na(t_nectar)))*100,2)
missing <- specify_decimal(sum(is.na(t_nectar))/(sum(is.na(t_nectar))+sum(!is.na(t_nectar)))*100,2)

colnames(t_nectar) <- c("Breeding system","Compatibility system",
         "Autonomous selfing qualitative","Autonomous selfing quantitative", "Flower shape", "Flower symmetry", 
         "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 
         "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar per flower (microlitres)", "Nectar per flower (miligrames)", "Nectar concentration (%)", "Pollen grains per flower")

missing.values <- t_nectar %>%
  gather(key = "key", value = "val") %>%
  mutate(isna = is.na(val)) %>%
  group_by(key) %>%
  mutate(total = n()) %>%
  group_by(key, total, isna) %>%
  summarise(num.isna = n()) %>%
  mutate(pct = num.isna / total * 100)

levels <-
  (missing.values  %>% filter(isna == T) %>% arrange(desc(pct)))$key

percentage.plot <- missing.values %>%
  ggplot() +
  geom_bar(aes(x = reorder(key, desc(pct)), 
               y = pct, fill=isna), 
           stat = 'identity', alpha=0.8) +
  scale_x_discrete(limits = levels) + theme_bw()+
  scale_fill_manual(name = "", 
                    values = c('#57a340', '#d24513'), labels = c("Present values", "Missing values")) +
  coord_flip() +
  labs(title = "", x =
         '', y = "")+  scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

percentage.plot

```

### 2023-02-14 Supplementary_Material/Figures/Qualitative_PCA_Associations.Rmd
organising files for what it seems it could be the final version of it

--- 2021-08-16 Supplementary_Material/Supplementary_Material.Rmd
@@
 ---
-title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant floral and reproductive traits determine interactions with floral visitors}
-
 output:
-  pdf_document:
-    extra_dependencies: ["float"]
-header-includes:
-- \usepackage{pdflscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
-- \usepackage{float}
-- \usepackage{caption}
-- \usepackage{setspace}\doublespacing
-- \usepackage{soul}
-- \floatplacement{figure}{H}
-- \usepackage{afterpage}
-- \usepackage{placeins}
-- \usepackage{graphicx}
-- \usepackage{floatpag}
-
-fontsize: 12pt
+  pdf_document: default
+  html_document: default
 
@@
 
-```{r echo=FALSE,warning=FALSE}
-knitr::opts_chunk$set(fig.pos = "h", out.extra = "")
-
-```
-
-\captionsetup[figure]{labelformat=empty}
-\captionsetup[table]{labelformat=empty}
-\captionsetup[table]{font={stretch=1.2}}
-
-\renewcommand{\figurename}{}
-
-\singlespacing
-\vspace{-1.6cm}
-
-Jose B. Lanuza$^{1,2}*$, Romina Rader$^{1}$, Jamie Stavert$^{3}$, Liam K. Kendall$^{4}$, Manu E. Saunders$^{1}$ and Ignasi Bartomeus$^{2}$
-
-\vspace{-0.6cm}
-
-\section*{\hfil Supplementary information\hfil}
-
-# Contents:
-
-__Supplementary text__
-
-Description of the traits compiled in this study
-
-\doublespacing
-\singlespacing
-
-__Supplementary Tables__
-
-Supplementary Table S1: List of the 28 plant-pollinator studies used to build the plant trait database
-
-Supplementary Table S2: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species
-
-Supplementary Table S3: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity
-
-Supplementary Table S4: Statistical association between the different categorical variables and the fisrt three main axes of trait variation with the full set of species
-
-Supplementary Table S5: Phylogenetic signal of the different quantitative traits
-
-\doublespacing
-\singlespacing
-
-__Supplementary Figures__
-
-Supplementary Fig. S1: Percentage of present and missing values of the different traits
-
-Supplementary Fig. S2: Phylogenetic informed principal component analysis for the species that did not have missing values
-
-Supplementary Fig. S3: Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation
-
-Supplementary Fig. S4: Regression tree analyses
-
-Supplementary Fig. S5: PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species
-
-Supplementary Fig. S6: Phylogenetic informed principal component analysis for the subset of species with floral rewards.
-
-Supplementary Fig. S7: Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species
-
-Supplementary Fig. S8: Visitation rate of the main bee families on the main axes of trait variation
-
-Supplementary Fig. S9:  Plant species level metrics across the three main axes of trait variation
-
-Supplementary Fig. S10: Pearson correlation between the product of flower number-flower size and autonomous selfing level
-
-\newpage
-
-__Description of the traits compiled in this study__
-
-_Reproductive traits_
-
--	Breeding system: The different plant species were classified in hermaphrodite, dioecious and monoecious species.
-Intermediate breeding systems or more complex ones were also annotated but all the species were divided into these three main categories for simplicity of the analysis.
-
--	Selfing level: We recorded the selfing level of the different species with both quantitative and qualitative data.
-The qualitative data was divided in four main categories, high selfers, medium selfers, low selfers and none which was for the species that were unable to self-pollinate.
-In addition, quantitative data was also divided into these four categories with the following criteria: from 0% to lower than 1% ‘none’, from 1% to 25% ‘low’, from 26% to 75% ‘medium’ and from 76% to 100%  ‘high’.
-
--	Compatibility system: The different species were divided in three main categories in order to know their ability to self-pollinate.
-These categories were self-compatible, partially self-compatible and self-incompatible species.
-The field of selfing level is partly complementary to the compatibility system but is important to note that not all the self-compatible species or partially self-compatible species will self-pollinate.
-
-_Floral traits_
-
--	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape.
-We divided the flowers in 8 main different categories: open, tube, campanulate, funnelform, papilionaceous, spike and capitulum.
-
--	Flower symmetry: We also recorded if the flowers were bilaterally symmetrical “zygomorphic” or were radially symmetrical “actinomorphic”.
-
--	Flower and inflorescence size: We searched for flower length and flower and inflorescence width (mm) for all species.
-When possible, we calculated the not found measurements with the help of online images and  the software ImageJ.
-
--	Flower number per plant: We compiled information about the number of flowers per plant for all species.
-However, this field was rare to find and we also used online images of the different species in order to calculate rough numbers of flowers per plant.
-We referenced all the filled fields in order to be able to follow the images that were used for these counts.
-It is important to note, that these numbers are not pretended to be the exact number of flowers per species but an approximate indicator of the reproductive investment for the different species that allow the macroecological analysis of this field.
-
--	Ovule number: We searched for the number of ovules per flower for all the different species.
-The number of ovules of Asteraceae species are considered as the total number of ovules per capitulum.
-Many species were filled by genus or family level because the number of ovules in this taxonomic groups is considered to be mostly constant (e.g., Lamiaceae Boraginaceae or Apiaceae).
-
--	Style length: The length of the style (mm) of the different species was also included. When possible, we calculated style length from images and illustrations on the online floras.
-
-- Nectar provision: We recorded the presence and absence of nectar for all species.
-In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration.
-In general terms, nectar data was rarely present and we try to minimise the loss of information by filling some species at family level.
-For instance, Solanaceae species are described as nectarless, and species that belonged to this family were recorded with ‘absence’ of nectar.
-
-- Pollen grains per flower: We recorded pollen grains per flower for all species but this field was rarely described in the literature.
-When just the pollen:ovule ratio was found we converted it back to pollen grains by multiplying by ovule number.
-
-_Vegetative traits_
-
-- Life form, life span and plant height: We divided the different plant species in 4 main categories: herbs, vines, shrubs and trees.
-Moreover, we also divided the species between short-lived species (annual, biennial and short-lived perennials) and perennial species (long-lived).
-Finally, we also searched for the average height (m) of the different species and annotated the maximum and minimum height when possible.
-We conducted the average between the maximum and minimum height to get an approximate average height of the species when the average was not indicated.
-
-\begin{landscape}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = "left"}
-setwd("~/R_Projects/Reproductive Traits")
-library(kableExtra)
-
-#Create data.frame with references
-
-`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1", "1", "1", "1", "1", "1", "1", "3", "1",
-                          "1", "1")
-
-#`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))
-
-`Network type` <- c(rep("Weighted web",  18), rep("Unweighted web",  4), "Weighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Unweighted metaweb", "Weighted metaweb")
-
-`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
-                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard", "Bek", "Kato", "Kevan", "Ramirez",
-                    "Inouye","McMullen", "Primack", "Ramirez", "Robertson", "Traveset")
-
-Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003,2006,2000,1970,1989,1990, 1993, 1983, 1992, 1929, 2013)
-
-#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
-#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
-#"USA", "Ecuador")
-
-DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
-"https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
-"https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
-"/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
-"https://doi.org/10.1111/j.1365-2745.2010.01732.x", "https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510",
-"https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis", "Unpublished, Master thesis", "http://hdl.handle.net/2433/156116",
-"https://doi.org/10.2307/2258569", "https://doi.org/10.2307/2388282", "http://hdl.handle.net/2433/156099", "https://biostor.org/reference/244737", "https://doi.org/10.1080/0028825X.1983.10428561",
-"https://doi.org/10.1111/j.1095-8339.1992.tb00294.x", "https://doi.org/10.5962/bhl.title.11538", "https://doi.org/10.1098/rspb.2012.3040")
-
-references <- data.frame(`First author`, Year, `Number of networks`,`Network type`,   DOI)
-
-colnames(references) <- c("First author", "Year", "Web N.",  "Network type",  "DOI")
-
-library(dplyr)
- references %>%
- arrange(`First author`)%>%
-kable("latex", longtable = T, booktabs = T,linesep = "\\addlinespace",
-             caption = "\\textbf{Supplementary Table S1 | List of the 28 plant-pollinator studies used to build the plant trait database.} Each study is shown with the first author that conducted the study, number of networks or metawebs that contains, type of information that contains (weighted or unweighted),  the structure (web or metaweb), year of publication and digital object identifier or permanent link for each study.") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, repeat_header_method="replace" ,full_width=F,position = "left")
-
-```
-
-\end{landscape}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
- kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Supplementary Table S2 | Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Microlitres of Nectar per flower" , "Pollen per flower","Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
-kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Supplementary Table S3 | Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-d <- readRDS("Data/RData/table_categorical_tukey_test.rds")
-
-#Again im getting the same error on this rmd so I run it on another one, save the dataframe and plot it here
-
-#Plot table
-#Add latex format in markdown
-
-kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Supplementary Table S4 | Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-#SELFING
-selfing <- readRDS("Data/RData/selfing_phylo.rds")
-#FLOWER NUMBER
-flower_n <- readRDS("Data/RData/flower_n_phylo.rds")
-#INFLO WIDTH
-inflow_width <- readRDS("Data/RData/inflow_width_phylo.rds")
-#FLOWER WIDTH
-flower_width <- readRDS("Data/RData/flower_width_phylo.rds")
-#FLOWER LENGHT
-flower_length <- readRDS("Data/RData/flower_length_phylo.rds")
-#STYLE LENGTH
-style_n <- readRDS("Data/RData/style_n_phylo.rds")
-#OVULE NUMBER
-ovule_n <- readRDS("Data/RData/ovule_n_phylo.rds")
-#PLANT HEIGHT
-plant_height <- readRDS("Data/RData/plant_height_phylo.rds")
-#POLLEN
-pollen <- readRDS("Data/RData/pollen_phylo.rds")
-#Nectar ul
-nectar_ul <- readRDS("Data/RData/Nectar_ul_phylo.rds")
-
-#Not included at the end
-#Nectar mg
-#nectar_mg <- readRDS("Data/RData/Nectar_mg_phylo.rds")
-#Nectar concentration
-nectar_con <- readRDS("Data/RData/Nectar_concentration_phylo.rds")
-
-#Select two decimals function
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-#LABELS
-label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Nectar per flower ($\\mu$l)", "Nectar concentration ($\\%$)","Pollen grains per flower")
-#LAMBDA
-lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, nectar_ul$lambda, nectar_con$lambda, pollen$lambda)
-#P-VALUE
-p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P,nectar_ul$P,  nectar_con$P, pollen$P)
-
-tabla <- data.frame(label, specify_decimal(lambda,2), specify_decimal(p_value,2))
-
-colnames(tabla) <- c("Functional traits", "Lambda", "P-value")
-
-kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,caption = "\\textbf{Supplementary Table S5 | Phylogenetic signal of the different quantitative traits.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Supplementary Fig. S1 | Percentage of present and missing values of the different traits.}"}
-
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-
-########################################################################################################################################################
-#SCRIPT FOR DATA IMPUTATION
-########################################################################################################################################################
-#1) READ TRAIT DATA
-
-#2) CLEAN DATA AND RENAME LEVELS
-
-#3) EXPLORE PATTERNS OF MISSING DATA
-
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-
-#5) ICLUDE EIGENVALUES IN RAWDATA TO IMPROVE IMPUTATION OURPUT
-
-#6) IMPUTE DATA
-
-#7) SAVE IMPUTED DATA 
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(missMDA) #For missing values
-library(FactoMineR) #Produce pca biplot with individuals and variables
-library(factoextra)
-library(ggpubr) 
-library(missForest) #random forst imputation
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(ape)
-library(PVR) #calculate eigen vectors and add them as a column in the imputation, seems to improve output
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-str(trait_data_1)
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-levels(as.factor(trait_filtered$Info_level)) #checking levels
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-str(trait_filtered_2)
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-                        "Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-levels(as.factor(t$Breeding_system))
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-levels(as.factor(t$Flower_morphology))
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-levels(as.factor(t$lifespan))
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-#Explore patterns of missing data
-missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)
-sort(missing_data[missing_data >= 0], decreasing=T)
-#nectar values all above 50% except presence/absence
-#then, just one cololumn with 68% missing data, then one with 35% and then 20% and 10%. The rest under 5%.
-#it is recommended to remove columns over 50% but we are particulary interested in having numeric levels of quantitative selfing 
-#we are going to work just with presence/absence of nectar
-#we will perform further analysis just with a subset with the quantitative values o nectar (very interesting data and diffciult to obtain)
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-         "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-         "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-         "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-         "Pollen_per_flower")]
-
-#check missing data now
-missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)*100
-sort(missing_data[missing_data >= 0], decreasing=T)
-
-missing_data <- unlist(lapply(t, function(x) nrow(t)-sum(is.na(x))))
-sum(missing_data)
-
-#Number of missing values on the datset
-#vis_miss(t[,c(6:20)])
-#9.9% percentage of missing values]
-
-#Checking number of filled cells/ just selecting variables used in the manuscript; nectar ul should be accounted too and it has been considered but
-#not added to run this code
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-str(t)
-
-#Impute data considering phylogenetic distance of species
-#it improves quality of imputation
-#https://doi.org/10.1111/2041-210X.12232 see ref for method comparisons with and without imputation
-
-#Multiple imputation process with phylogeny --> Missforest
-#https://doi.org/10.1111/2041-210X.12232
-#althought it does not have an option we are going to add it as a column
-
-#Before data imputation I need to calculate the phylo of the species
-#remove not found species that do not run with get tree
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-levels(factor(t$Species_all))
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-#Select just columns with traits
-t <- t[c("Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-         "Pollen_per_flower")]
-
-#################################################
-#3)SUMMARY OF THE DATA|ALL COLS CONSIDERED!
-#################################################
-##Number of filled cells
-#nrow(t) * 16 - sum(is.na(t))#[1] 20737
-##Dimension of the dataset
-#nrow(t) * 16#[1] 24096
-##Number of missing values
-#sum(is.na(t))#[1] 3359
-##Percentage of filled cells
-#sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 86.87993
-##Percentage of missing values
-#sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 13.12007
-#
-#
-
-#Function to specify number of decimals
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-no_missing <- specify_decimal(sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
-missing <- specify_decimal(sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
-
-colnames(t) <- c("Breeding system","Compatibility system",
-         "Autonomous selfing qualitative","Autonomous selfing quantitative", "Flower shape", "Flower symmetry", 
-         "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 
-         "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar per flower (microlitres)", "Nectar per flower (miligrames)", "Nectar concentration (%)", "Pollen grains per flower")
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-levels <-
-  (missing.values  %>% filter(isna == T) %>% arrange(desc(pct)))$key
-
-percentage.plot <- missing.values %>%
-  ggplot() +
-  geom_bar(aes(x = reorder(key, desc(pct)), 
-               y = pct, fill=isna), 
-           stat = 'identity', alpha=0.8) +
-  scale_x_discrete(limits = levels) + theme_bw()+
-  scale_fill_manual(name = "", 
-                    values = c('#57a340', '#d24513'), labels = c("Present values", "Missing values")) +
-  coord_flip() +
-  labs(title = "", x =
-         '', y = "")+  scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
-  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))
-
-percentage.plot
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Supplementary Fig.
-S2 |  Phylogenetic informed principal component analysis for the species that did not have missing values.}"}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_complete_cases.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-#PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-pc3 <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.015, 0.03, 0.07), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,5.2,5,5.25,6.3,6)), y = -(PCAloadings$PC2*c(4,4.75,4,4.5,5,5.5)+c(0,0,0,0,-0.04,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-pc3(PC)
-
-```
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=28,  fig.cap="\\textbf{Supplementary Fig.
-S3 | Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation.} The superior (plots a, b and c) and lower (plots d, e and f) panels show visitation rates on the main axes of trait variation with and without \\emph{Apis mellifera}, respectively."}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot_apis <- readRDS("Plot_apis.rds")
-
-plot_apis
-
-```
-
-\elandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Supplementary Fig.
-S4 | Regression tree analyses.} Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric.
-"}
-
-########################################################################################################################################################
-#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
-########################################################################################################################################################
-#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)
-
-library(rpart.plot)
-library(rpart)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
-nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
-d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")
-
-#run  regression trees of the 3 metrics
-set.seed(1)
-tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0054559,minbucket=50)
-
-set.seed(1)
-tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0084459,minbucket=50)
-
-set.seed(1)
-tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0072192 , minbucket=50) #10
-
-#NECTAR AND POLEN DATA
-v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
-nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
-d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")
-
-#Set correct colnames for plotting
-colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
-                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")
-
-set.seed(2)
-tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)
-
-set.seed(2)
-tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)
-
-set.seed(2)
-tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)
-
-par(mfrow=c(3,2))
-
-rpart.plot(tree_1, box.palette="GnOr", main="(a) Interaction frequency for all species", cex.main=1.75,tweak = 1.10) 
-rpart.plot(tree1, box.palette="GnOr", main="(b) Interaction frequency for subset with floral rewards", cex.main=1.75,tweak = 1.10)
-
-rpart.plot(tree_2, box.palette="GnOr", main="(c) Normalized degree for all species", cex.main=1.75,tweak = 1.10)
-rpart.plot(tree2, box.palette="GnOr", main="(d) Normalized degree for subset with floral rewards", cex.main=1.75,tweak = 1.10)
-
-rpart.plot(tree_3, box.palette="GnOr", main="(e) Specialization for all species", cex.main=1.75,tweak = 1.10) 
-rpart.plot(tree3, box.palette="GnOr", main="(f) Specialization for subset with floral rewards", cex.main=1.75,tweak = 1.10)
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Supplementary Fig.
-S5 | PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species.}"}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-pc3 <- function(PC, x="PC1", y="PC3") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC3 ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,4.8,7.1,5.5)), y = -(PCAloadings$PC2*c(-3.2,4.5,3.75,8.4,5,5.5)+c(0,0,0,0,-0.08,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-pc3(PC)
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Supplementary Fig.
-S6 | Phylogenetic informed principal component analysis for the subset of species with floral rewards.}"}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.2)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-dat_cleaning_7 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen.rds")
-
-PC <- phyl_pca_forest_nectar_pollen
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-library(magick)
-
-#Images were made by Paula Martin
-
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
-    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-  plot <- plot + geom_point(data=dat, aes(x, y),size=0.95, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw()
-
-  #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height", "Nectar","Pollen" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.85,5.5,5.3,5.5,6.1,5.75,5.8,6)), y = -(PCAloadings$PC2*c(4.8,4.8,4.65,5.65,5,5.1,5.75,5)+c(0,0,0,0,0,0,0,0)),
-                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-all_spp(PC)
-
-```
-
-\newpage
-\thispagestyle{empty}
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Supplementary Fig.
-S7 | Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species.} Categories that differ significantly are denoted with a different letter."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=14}
 
@@
 ```
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=28,  fig.cap="\\textbf{Supplementary Fig.
-S8 | Visitation rate of the main bee families on the main axes of trait variation.} Fitted posterior estimates of the visitation rate of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
-We omitted in the plotting area points over percentile 95 \\% percent due to extreme outliers."}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot <- readRDS("Plot_bee_families.rds")
-
-plot
-
-```
-
-\elandscape
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Supplementary Fig.
-S9 | Plant species level metrics across the three main axes of trait variation.}", fig.pos= "h"}
-
-library(brms) #modelling
-library(cmdstanr) #modelling
-library(cowplot) #panel of plots
-library(ggplot2) #plotting
-library(patchwork)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(3.5)),
-           axis.text=element_text(size = rel(2.75), color = "black"),
-           legend.title=element_text(face="bold"),
-           legend.text=element_text(),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(0.4, 'lines'),
-           panel.border=element_rect(color="black",size=3),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-#########
-
-setwd("~/Dropbox/PhD/R/Chapter_2")
-
-#read plot generated in other rmd, bms and stan are giving trouble here... This file is created in Species_Level_Metric_Pcs
-
-plot_metrics_pcs <- readRDS("plot_metrics_pcs.rds")
-
-plot_metrics_pcs
-
-```
-
-\elandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Supplementary Fig.
-S10 | Pearson correlation between the product of flower number-flower size and autonomous selfing level.}", fig.pos= "h"}
-
-theme_ms <- function(base_size=18, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(2.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-#LOAD LIBRARIES
-library(ggplot2)
-library(ggpubr)
-
-#LOAD DATA
-dat <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-
-#CONDUCT PRODUCT FLOWER NUMBER-FLOWER SIZE
-dat$Product <-      log(dat$Flowers_per_plant * dat$Corolla_diameter_mean+1)
-
-ggscatter(dat, x = "Autonomous_selfing_level_fruit_set", y = "Product", 
-          add = "reg.line", conf.int = TRUE,
-          cor.coef = TRUE, cor.method = "pearson",size=5,cor.coef.size=15,
-          xlab = "Autnomous selfing", ylab = "Product flower size-number") +
-  theme_ms() +ylim(0,16)
-
-```

### 2023-02-14 Supplementary_Material/Tables/Table_1_List_of_Studies.Rmd
organising files for what it seems it could be the final version of it

--- 2022-06-23 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021.Rmd
@@
 ---
-#title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Covariation among reproductive traits in flowering plants determine interactions with floral visitors}
-
+title: ""
 output:
-  pdf_document:
-    extra_dependencies: ["float"]
-header-includes:
-- \usepackage{pdflscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
-- \usepackage{float}
-- \usepackage{caption}
-- \usepackage{setspace}\doublespacing
-- \usepackage{soul}
-- \floatplacement{figure}{H}
-- \usepackage{afterpage}
-- \usepackage{placeins}
-- \usepackage{graphicx}
-- \usepackage{floatpag}
-
-fontsize: 12pt
-
+  pdf_document: default
+  html_document: default
 ---
-
-```{r echo=FALSE,warning=FALSE}
-knitr::opts_chunk$set(fig.pos = "h", out.extra = "")
-
-```
-
-\captionsetup[figure]{labelformat=empty}
-\captionsetup[table]{labelformat=empty}
-\captionsetup[table]{font={stretch=1.2}}
-
-\singlespacing
-
-\vspace{2cm}
-
-# Supplementary information for:
-
-## Covariation among reproductive traits in flowering plants determine interactions with floral visitors
-
-\textbf{Jose B. Lanuza*, Romina Rader, Jamie Stavert, Liam K. Kendall, Manu E. Saunders and Ignasi Bartomeus}
-
-\textbf{*Corresponding author}
-**E-mail: barragansljose@gmail.com**
-
-**This pdf includes:**
-
-Appendix S1 (text)
-
-Tables S1 to S5
-
-Figures S1 to S9
-
-\doublespacing
-
-<!--
-
-__Supplementary text__
-
-Description of the traits compiled in this study with an illustrative figure of the main flower morphologies (Supplementary text Fig 1)
-
-\doublespacing
-\singlespacing
-
-__Supplementary Tables__
-
-Supplementary Table S1: List of the 28 plant-pollinator studies used to build the plant trait database
-
-Supplementary Table S2: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species
-
-Supplementary Table S3: Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity
-
-Supplementary Table S4: Statistical association between the different categorical variables and the fisrt three main axes of trait variation with the full set of species
-
-Supplementary Table S5: Phylogenetic signal of the different quantitative traits
-
-\doublespacing
-\singlespacing
-
-__Supplementary Figures__
-
-Supplementary Fig. S1: Percentage of present and missing values of the different plant traits
-
-Supplementary Fig. S2: Phylogenetic informed principal component analysis for the species that did not have missing values
-
-Supplementary Fig. S3: Fitted posterior estimates of the number of visits made by bees including and exluding honey bees on the main axes of trait variation
-
-Supplementary Fig. S4: Regression tree analyses
-
-Supplementary Fig. S5: PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species
-
-Supplementary Fig. S6: Phylogenetic informed principal component analysis for the subset of species with floral rewards.
-
-Supplementary Fig. S7: Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species
-
-Supplementary Fig. S8: Presence-absence of interaction and visitation rate of the main bee families on the main axes of trait variation
-
-Supplementary Fig. S9:  Plant species level metrics across the three main axes of trait variation
-
-Supplementary Fig. S10: Pearson correlation between the product of flower number-flower size and autonomous selfing level
-
--->
-
-\newpage
-
-## Appendix S1
-
-__Description of the traits compiled in this study__
-
-Here we describe the different traits of the database used in this study to explore the reproductive spectrum of trait variation and plant-pollinator associations.
-Note that all species have references or links providing the original source of the information.
-
-_Reproductive traits_
-
--	Breeding system: The different plant species were classified in hermaphrodite, dioecious and monoecious species.
-Intermediate breeding systems or more complex ones were also annotated but all the species were divided into these three main categories for simplicity of the analysis.
-
--	Selfing level: We recorded the selfing level of the different species with both quantitative and qualitative data.
-The qualitative data was divided in four main categories, high selfers, medium selfers, low selfers and none which was for the species that were unable to self-pollinate.
-In addition, quantitative data was also divided into these four categories with the following criteria: from 0% to lower than 1% ‘none’, from 1% to 25% ‘low’, from 26% to 75% ‘medium’ and from 76% to 100%  ‘high’.
-Because quantitative selfing had a high percentage of missing values (68%), we were able to solve this by converting these four categories to representative percentages of each category 0%, 13%, 50.5% and 88%.
-This reduced the percentage of missing values for this quantitative trait from 68% to 35% and allowed the imputation of this variable.
-
--	Compatibility system: The different species were divided in three main categories in order to know their ability to self-pollinate.
-These categories were self-compatible, partially self-compatible and self-incompatible species.
-The field of selfing level is partly complementary to the compatibility system but is important to note that not all the self-compatible species or partially self-compatible species will self-pollinate.
-
-_Floral traits_
-
--	Flower symmetry: We also recorded if the flowers were bilaterally symmetrical “zygomorphic” or were radially symmetrical “actinomorphic”.
-
--	Flower and inflorescence size: We searched for flower length and flower and inflorescence width (mm) for all species.
-When possible, we calculated the not found measurements with the help of online images and the software ImageJ.
-Note that for species with compound flowers (e.g., Asteraceae) or similar floral structures with flower heads with many small flowers we considered the inflorescence as the floral unit.
-For each species this is indicated in the dataset with the field of "info_level" where the measurement level is specified as capitulum or flower level.
-Note that for some Asteraceae species information about the disc and ray floret is also provided in the database but these were not included in our analyses.
-
--	Flower number per plant: We compiled information about the number of flowers per plant for all species.
-However, this field was rare to find and we also used online images of the different species in order to calculate rough numbers of flowers per plant.
-We referenced all the filled fields in order to be able to follow the images that were used for these counts.
-It is important to note, that these numbers are not pretended to be the exact number of flowers per species but an approximate indicator of the reproductive investment for the different species that allow the macroecological analysis of this field.
-
--	Ovule number: We searched for the number of ovules per flower for all the different species.
-The number of ovules of Asteraceae species are considered as the total number of ovules per capitulum.
-Many species were filled by genus or family level because the number of ovules in this taxonomic groups is considered to be mostly constant (e.g., Lamiaceae Boraginaceae or Apiaceae).
-
--	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape.
-We divided the flowers in 8 main different categories: open, bowl, tube, campanulate, funnelform, papilionaceous, brush and capitulum.
-However, we ended up groupping all flowers on the following 6  morphological groups for analyses: tube, papilonaceous, open, capitulum, campanulate and brush (Supplementary Information Text Fig.
-1).
-
-```{r pressure, echo=FALSE, fig.cap="", out.width = '65%',fig.align='center', fig.cap="\\textbf{Supplementary Information Text Fig.
-1.}  Main floral morphologies considered in this study.
-All species were groupped within these categories for analysis: (a) tube, (b) papilonaceous, (c) open, (d) capitulum, (e) campanulate and (f) brush."}
-knitr::include_graphics("../Images/flower_shapes.png")
-```
-
--	Style length: The length of the style (mm) of the different species was also included. When possible, we calculated style length from images and illustrations on the online floras.
-
-- Nectar provision: We recorded the presence and absence of nectar for all species.
-In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration.
-For species that did not have nectar information but belonged to a family that is considered as ‘nectarless’, this trait was recorded at family level and the species was recorded with ‘absence’ of nectar.
-This was done exclusively for well documented nectarless taxonomical groups.
-For the field of microlitres of nectar, we considered single measurements of nectar standing crop.
-In general terms, the timming of the measurement and methodology differed across studies.
-For instance, some studies measured nectar in freshly opened flowers while others in flowers that were bagged for 24 hours.
-Despite the different methodologies to measure nectar provision, we believe that this is an appropriate way to collate measurements of nectar to explore trait associations at a macroecological scale.
-
-- Pollen grains per flower: We recorded pollen grains per flower for all species but this field was rarely described in the literature.
-When just the pollen:ovule ratio was found we converted it back to pollen grains by multiplying it by the average ovule number found for each species.
-
-_Vegetative traits_
-
-- Life form, life span and plant height: We divided the different plant species in 4 main categories: herbs, vines, shrubs and trees.
-Moreover, we also divided the species between short-lived species (annual, biennial and short-lived perennials) and perennial species (long-lived).
-Finally, we also searched for the average height (m) of the different species and annotated the maximum and minimum height when possible.
-We conducted the average between the maximum and minimum height to get an approximate average height of the species when the average was not indicated.
 
@@
  arrange(`First author`)%>%
-kable("latex", longtable = T, booktabs = T,linesep = "\\addlinespace",
-             caption = "\\textbf{Table S1.
-List of the 28 plant-pollinator studies used to build the plant trait database.
-Each study is shown with the first author that conducted the study, number of networks or metawebs that contains, type of information that contains (weighted or unweighted),  the structure (web or metaweb), year of publication and digital object identifier or permanent link for each study.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, repeat_header_method="replace" ,full_width=F,position = "left")
+kable("latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "left")
 
@@
 \end{landscape}
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-d <- readRDS("Data/RData/table_categorical_tukey_test.rds")
-
-#Again im getting the same error on this rmd so I run it on another one, save the dataframe and plot it here
-
-#Plot table
-#Add latex format in markdown
-
-kable(d, longtable = T,"latex" , booktabs = T,linesep = "\\addlinespace", escape=FALSE, caption = "\\textbf{Table S2.
-Statistical association between the different categorical variables and the first three main axes of trait variation with the full set of species.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
- kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S3.
-Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the full set of species.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\pagebreak
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(dplyr)
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-PC <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-
-dat <- PC$L[,c(1:3)]
-
-#Create a row to add total percentage of variance explained by PC
-
-percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-percen <- percentage[1:3]
-
-dat <- rbind(dat, percen)
-
-rownames(dat) <- c("Autonomous selfing", "Flowers per plant", "Flower width", "Style length", "Ovule number", "Plant height", "Microlitres of Nectar per flower" , "Pollen per flower","Explained variation")
-
-dat <- as.data.frame(dat)
-
-dat <- dat %>% mutate(across(is.numeric, ~ round(., 2)))
-
-kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S4.
-Loadings of the first three axes of trait variation of the phylogenetic informed principal component analysis with the subset of species with data of nectar and pollen quantity.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=10, fig.width=10, fig.align='center'}
-
-library(kableExtra)
-
-setwd("~/R_Projects/Reproductive Traits")
-
-#SELFING
-selfing <- readRDS("Data/RData/selfing_phylo.rds")
-#FLOWER NUMBER
-flower_n <- readRDS("Data/RData/flower_n_phylo.rds")
-#INFLO WIDTH
-inflow_width <- readRDS("Data/RData/inflow_width_phylo.rds")
-#FLOWER WIDTH
-flower_width <- readRDS("Data/RData/flower_width_phylo.rds")
-#FLOWER LENGHT
-flower_length <- readRDS("Data/RData/flower_length_phylo.rds")
-#STYLE LENGTH
-style_n <- readRDS("Data/RData/style_n_phylo.rds")
-#OVULE NUMBER
-ovule_n <- readRDS("Data/RData/ovule_n_phylo.rds")
-#PLANT HEIGHT
-plant_height <- readRDS("Data/RData/plant_height_phylo.rds")
-#POLLEN
-pollen <- readRDS("Data/RData/pollen_phylo.rds")
-#Nectar ul
-nectar_ul <- readRDS("Data/RData/Nectar_ul_phylo.rds")
-
-#Not included at the end
-#Nectar mg
-#nectar_mg <- readRDS("Data/RData/Nectar_mg_phylo.rds")
-#Nectar concentration
-nectar_con <- readRDS("Data/RData/Nectar_concentration_phylo.rds")
-
-#Select two decimals function
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-#LABELS
-label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Nectar per flower ($\\mu$l)", "Nectar concentration ($\\%$)","Pollen grains per flower")
-#LAMBDA
-lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, nectar_ul$lambda, nectar_con$lambda, pollen$lambda)
-#P-VALUE
-p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P,nectar_ul$P,  nectar_con$P, pollen$P)
-
-tabla <- data.frame(label, specify_decimal(lambda,2), specify_decimal(p_value,2))
-
-colnames(tabla) <- c("Functional traits", "Lambda", "P-value")
-
-kable(tabla, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,caption = "\\textbf{Table S5. Phylogenetic signal of the different quantitative traits.}") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
-
-```
-
-\newpage
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.width=12, fig.height=6, fig.cap="\\textbf{Fig.
-S1.} Map with the different locations of the plant-pollinator studies used in this work to explore woldwide patterns at the meso-scale level.
-Note that for visualization purposes studies from the same authors are shown with the same colour."}
-
-#Create coordinate dataset for plotting
-
-longitude <- c("3.296797",  #1
-               "1.575532", #2
-               "9.275556", 
-               "18.5", #4
-               "99.63806", #5
-               "148.266667",
-               "-52", 
-               "-31", "57.43", #8
-               "-75.5", #9
-               "-57.885", #10
-               "55.447778",
-               "-6.16895", #12bart
-               "55.43333", #13
-               "57.733333",
-               "-68.015892", #15
-               "-89.8968771",
-               "171.756111",
-               "10.233333",
-               "-90.35",
-               "-93.8968771",#Robertson
-               "-67.4292900",
-               "-61.71666666666667",
-               "175.756111",
-               "-71.3",
-               "129.387359", #Kevan
-               "135.75385",
-               "-93.35",
-               "10.219072")
-
-latitude <- c("42.315336", #1
-              "52.762395", #2
-              "56.0725",
-              "68.35", #4
-              "27.90139", #5
-              "-36.45", #6
-              "71", #7
-              "39.4", "-23.25", #8 #modified for visibility of ovelapping
-              "45.4", #9
-              "-21.701111", #10
-              "-7.67",#11 #modified for visibility of ovelapping
-              "37.234966", #12bart
-              "-4.666667", #13
-              "-20.4538",
-              "-32.008985", #15
-              "39.278958",
-              "-43.035889",
-              "59.066667",#18 #modified for visibility of ovelapping
-              "-0.533333",
-              "39.278958", #Robertson 
-              "8.9241600",
-              "5.5833333",
-              "-43.035889",
-              "81.8166667",
-              "28.288661", #Kevan 
-              "35.02107",
-              "-0.533333",
-              "56.069108")
-
-id <- c("Bartomeus1", #1
-        "Dicks", #2
-        "Dupont", 
-        "Elberling", #4
-        "Fang", #5
-        "Inouye1", #6
-        "Lundgren", #7
-        "Olesen", "Olesen", #8
-        "Small", #9
-        "Souza", #10
-        "Kaiser-Bunbury1", #
-        "Bartomeus2", #12
-        "Kaiser-Bunbury2", #13
-        "Kaiser-Bunbury3", #14
-        "Peralta", #15
-        "Burkle",
-        "Arroyo-Correa",
-        "Bundgaard",
-        "Traveset",
-        "Robertson",
-        "Ramirez1",
-        "Ramirez2",
-        "Primack",
-        "Kevan",
-        "Kato",
-        "Inouye2",
-        "McMullen",
-        "Baek")
-
-d <- data.frame(longitude, latitude, id)
-
-library("ggplot2")
-library("sf")
-library("rnaturalearth")
-library("rnaturalearthdata")
-
-world <- ne_countries(scale = "medium", returnclass = "sf")
-class(world)
-
-d$longitude <- as.numeric(d$longitude)
-d$latitude <- as.numeric(d$latitude)
-
-sf::sf_use_s2(FALSE)
-
-#these colors come from the library(pals)- labs = c('alphabet')
-
-colors <- c("red4", "#0075DC", "#4C005C", "#4C005C", "#993F00",  "#5EF1F2", 
-        "#005C31", "#2BCE48", "black", "lightblue", "darkorange3", "darkorange3","#8F7C00",
-        "#8F7C00","#8F7C00", "#9DCC00", "#C20088", "gold1","#FFA8BB","#426600","94FFB5","#003380",  
-         "#FF0010","#FF0010", "salmon", "seashell3","greenyellow","mediumaquamarine")
-
-set.seed(12)
-ggplot(data = world) +
-  geom_sf(fill="antiquewhite", color="grey49") +
-  xlab("Longitude") + ylab("Latitude") +
-  geom_point(data=d , aes(longitude,latitude,  color=id),  shape=10,
-           size = 4.5, stroke=1)+ 
-  theme(panel.grid.major = element_line(color = gray(.5), 
-linetype = "dashed", size = 0), panel.background = element_rect(fill = "aliceblue"))+
-  coord_sf(expand = FALSE) +  scale_y_continuous(breaks = c(-50,0, 50)) +
-  scale_x_continuous(breaks = c(-100,0, 100)) +
-  theme(legend.key.size = unit(0.6, 'cm'), legend.text = element_text(size=10),
-         legend.title = element_text(size=12)) +   scale_colour_manual(values = colors) + labs(colour="Plant-pollinator studies")
-
-```
-
-\elandscape
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,dpi=2000,  fig.cap="\\textbf{Fig. S2.} Percentage of present and missing values of the different plant traits."}
-
-#Set working directory
-setwd("~/R_Projects/Reproductive Traits")
-
-########################################################################################################################################################
-#SCRIPT FOR DATA IMPUTATION
-########################################################################################################################################################
-#1) READ TRAIT DATA
-
-#2) CLEAN DATA AND RENAME LEVELS
-
-#3) EXPLORE PATTERNS OF MISSING DATA
-
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-
-#5) ICLUDE EIGENVALUES IN RAWDATA TO IMPROVE IMPUTATION OURPUT
-
-#6) IMPUTE DATA
-
-#7) SAVE IMPUTED DATA 
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(missMDA) #For missing values
-library(FactoMineR) #Produce pca biplot with individuals and variables
-library(factoextra)
-library(ggpubr) 
-library(missForest) #random forst imputation
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(ape)
-library(PVR) #calculate eigen vectors and add them as a column in the imputation, seems to improve output
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-str(trait_data_1)
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-levels(as.factor(trait_filtered$Info_level)) #checking levels
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-str(trait_filtered_2)
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-                        "Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-levels(as.factor(t$Breeding_system))
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-levels(as.factor(t$Flower_morphology))
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-levels(as.factor(t$lifespan))
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-#Explore patterns of missing data
-missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)
-sort(missing_data[missing_data >= 0], decreasing=T)
-#nectar values all above 50% except presence/absence
-#then, just one cololumn with 68% missing data, then one with 35% and then 20% and 10%. The rest under 5%.
-#it is recommended to remove columns over 50% but we are particulary interested in having numeric levels of quantitative selfing 
-#we are going to work just with presence/absence of nectar
-#we will perform further analysis just with a subset with the quantitative values o nectar (very interesting data and diffciult to obtain)
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-         "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-         "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-         "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-         "Pollen_per_flower")]
-
-#check missing data now
-missing_data <- unlist(lapply(t, function(x) sum(is.na(x))))/nrow(t)*100
-sort(missing_data[missing_data >= 0], decreasing=T)
-
-missing_data <- unlist(lapply(t, function(x) nrow(t)-sum(is.na(x))))
-sum(missing_data)
-
-#Number of missing values on the datset
-#vis_miss(t[,c(6:20)])
-#9.9% percentage of missing values]
-
-#Checking number of filled cells/ just selecting variables used in the manuscript; nectar ul should be accounted too and it has been considered but
-#not added to run this code
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-str(t)
-
-#Impute data considering phylogenetic distance of species
-#it improves quality of imputation
-#https://doi.org/10.1111/2041-210X.12232 see ref for method comparisons with and without imputation
-
-#Multiple imputation process with phylogeny --> Missforest
-#https://doi.org/10.1111/2041-210X.12232
-#althought it does not have an option we are going to add it as a column
-
-#Before data imputation I need to calculate the phylo of the species
-#remove not found species that do not run with get tree
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-levels(factor(t$Species_all))
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-#Select just columns with traits
-t <- t[c("Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant", "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration",
-         "Pollen_per_flower")]
-
-#################################################
-#3)SUMMARY OF THE DATA|ALL COLS CONSIDERED!
-#################################################
-##Number of filled cells
-#nrow(t) * 16 - sum(is.na(t))#[1] 20737
-##Dimension of the dataset
-#nrow(t) * 16#[1] 24096
-##Number of missing values
-#sum(is.na(t))#[1] 3359
-##Percentage of filled cells
-#sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 86.87993
-##Percentage of missing values
-#sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100#[1] 13.12007
-#
-#
-
-#Function to specify number of decimals
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-no_missing <- specify_decimal(sum(!is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
-missing <- specify_decimal(sum(is.na(t))/(sum(is.na(t))+sum(!is.na(t)))*100,2)
-
-colnames(t) <- c("Breeding system","Compatibility system",
-         "Autonomous selfing qualitative","Autonomous selfing quantitative", "Flower shape", "Flower symmetry", 
-         "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 
-         "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar per flower (microlitres)", "Nectar per flower (miligrames)", "Nectar concentration (%)", "Pollen grains per flower")
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-levels <-
-  (missing.values  %>% filter(isna == T) %>% arrange(desc(pct)))$key
-
-percentage.plot <- missing.values %>%
-  ggplot() +
-  geom_bar(aes(x = reorder(key, desc(pct)), 
-               y = pct, fill=isna), 
-           stat = 'identity', alpha=0.8) +
-  scale_x_discrete(limits = levels) + theme_bw()+
-  scale_fill_manual(name = "", 
-                    values = c('#57a340', '#d24513'), labels = c("Present values", "Missing values")) +
-  coord_flip() +
-  labs(title = "", x =
-         '', y = "")+  scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
-  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))
-
-percentage.plot
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=20, fig.width=10,out.width="60%",fig.align='center',fig.cap= "\\textbf{Fig.
-S3.} Comparison of the phylogenetic informed principal component analysis for the dataset with data imputation and without data imputation.
-Panel A shows the reproductive spectrum of trait variation for the full dataset with data imputation and panel B shows the reproductive spectrum for the dataset without data imputation where the species with missing trait data were excluded from the analysis."}
-
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-library(viridis) #COLOUR GGPLOT
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(magick)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#Images were made by Paula Martin
-#Check her work on https://paulamartinart.com/
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-#ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-# plot <- plot + annotate("text", x = #(PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = #(PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0))#,
-#                         label =c("Low selfing", "Few flowers", #"Small flowers", "Short styles", "Few ovules", "Short plants" ), #color="black",fontface =2,size=4)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-p1 <- all_spp(PC)
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_complete_cases.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-#PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_complete_cases <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.015, 0.03, 0.07), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() 
-      #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,5.2,5,5.25,6.3,6)), y = -(PCAloadings$PC2*c(4,4.75,4,4.5,5,5.5)+c(0,0,0,0,-0.04,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-p2 <- all_complete_cases(PC)
-
-library(patchwork)
-
-p1 / p2 + plot_annotation(tag_levels = 'A') & 
-  theme(plot.tag = element_text(size = 24, face="bold"))
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=10,out.width="60%",fig.align='center',fig.cap="\\textbf{Fig.
-S4.} Comparison of the phylogenetic informed principal component analysis for the subset of species that had information of floral rewards with data imputation and without data imputation.
-Panel A shows the reproductive spectrum of trait variation for the dataset with data imputation and panel B shows the reproductive spectrum for the dataset excluding species with missing trait data"}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen.rds")
-dat_cleaning_7 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen.rds")
-
-PC <- phyl_pca_forest_nectar_pollen
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-library(magick)
-
-#Images were made by Paula Martin
-PC$S[,1] <- -PC$S[,1]
-
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
-    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-  plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw()
-
-  #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants", "Copious nectar","Copious pollen")
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,4.8,4.8,5.5,5.5,5.5,5.8,6.5)), y = -(PCAloadings$PC2*c(4.8,4.4,4.15,5.35,4.2,4.7,5.75,6)+c(0,0,0,0,0,0,0,0)),
-                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-p1 <- all_spp(PC)
-
-#Load data
-phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen_complete_cases.rds")
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen_complete_cases.rds")
-
-PC <- phyl_pca_forest_nectar_pollen
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_spp_complete <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
-    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.082),breaks = c(0.02, 0.035, 0.082), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-  plot <- plot + geom_point(data=dat, aes(x, y),size=0.95, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw()
-
-  #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants", "Copious nectar","Copious pollen")
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,4.8,5.4,5,4.2,5.8,3.4)+c(0,0,0,0,0,0,0,0)), y = -(PCAloadings$PC2*c(4.693,3.5,4,4,3,4.15,4.2,6.5)),
-                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-p2 <- all_spp_complete(PC)
-
-library(patchwork)
-
-p1 / p2 + plot_annotation(tag_levels = 'A') & 
-  theme(plot.tag = element_text(size = 24, face="bold"))
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24,  fig.cap="\\textbf{Fig.
-S5.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation.
-The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates."}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot_apis <- readRDS("Plot_apis_non_apis.rds")
-
-plot_apis
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig.
-S6.} Phylogenetically informed principal component analysis (pPCA) for all plant species with the first (flower number - flower size axis) and third (style length - pollinator dependence axis) principal component that explained most trait variation."}
-setwd("~/R_Projects/Reproductive Traits")
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,3] <- -PC$S[,3]
-
-pc3 <- function(PC, x="PC1", y="PC3") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("Flower number - flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Style length - pollinator dependence axis ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
- #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
- # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
- # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
- # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
- # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
- # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
- # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
- # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
- # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
- # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
- # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,4.8,7.1,5.5)), y = -(PCAloadings$PC2*c(-3.2,4.5,3.75,8.4,5,5.5)+c(0,0,0,0,-0.08,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-pc3(PC)
-
-```
-
-\newpage
-\thispagestyle{empty}
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig.
-S7.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species.
-Categories that differ significantly are denoted with a different letter."}
-
-########################################################################################################################################################
-#CORRELATION BETWEEN QUALITATIVE VARIABLES AND PC's
-########################################################################################################################################################
-#NOTES
-#I did not include the qualitative variables when I prepare the data for the PPCA
-#So I have to recalculate the ata here with the qualitative variables
-########################################################################################################################################################
-#LOAD LIBRARIES
-library(emmeans)
-library(ggplot2)
-library(patchwork)
-library(dplyr)
-
-theme_ms <- function(base_size=10, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(1.3)),
-           axis.text=element_text(size = rel(1.1), color = "black"),
-           panel.border=element_rect(color="black",size=1.2),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           legend.position = "none",
-           plot.title = element_text(face = "bold",size = rel(1.55)),
-           plot.subtitle = element_text(face = "bold",size = rel(1.4))
-     ))
-}
-
-########################################################################################################################################################
-setwd("~/R_Projects/Reproductive Traits")
-
-#LOAD DATA
-phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
-dat <- read.csv("Data/Csv/all_species_imputed_trait_data_forest_data.csv", row.names = "X")
-########################################################################################################################################################
-#remove not found species, cannot do PCA with unequal numbers of rows
-cols.num <- c("Family_all","Genus_all","Species_all")
-dat[cols.num] <- sapply(dat[cols.num],as.character)
-dat$Species_all <- gsub("Species_all_", "", dat$Species_all)
-########################################################################################################################################################
-#3) REMOVE OUTLIERS, OUT OF 2.5-97.5 RANGE WHICH HELPS IMPUTATION PROCESS. SEE ARTICLE FOR REF.
-########################################################################################################################################################
-dat_cleaning <- dat[,]
-#CHECK LEVELS
-
-dat_cleaning_1 <- dat_cleaning %>%
-  filter(between(Flowers_per_plant, quantile(Flowers_per_plant, 0.025), quantile(Flowers_per_plant, 0.975)))
-
-dat_cleaning_2 <- dat_cleaning_1 %>%
-  filter(between(Corolla_diameter_mean, quantile(Corolla_diameter_mean, 0.025), quantile(Corolla_diameter_mean, 0.975)))
-
-dat_cleaning_3 <- dat_cleaning_2 %>%
-  filter(between(Style_length, quantile(Style_length, 0.025), quantile(Style_length, 0.975)))
-
-dat_cleaning_4 <- dat_cleaning_3 %>%
-  filter(between(Ovule_number, quantile(Ovule_number, 0.025), quantile(Ovule_number, 0.975)))
-
-dat_cleaning_5 <- dat_cleaning_4 %>%
-  filter(between(Plant_height_mean_m, quantile(Plant_height_mean_m, 0.025), quantile(Plant_height_mean_m, 0.975)))
-
-final_d <- dat_cleaning_5[,]
-
-pca_data <- as.data.frame(phyl_pca_forest$S)
-
-d <- cbind(final_d, pca_data)
-
-#Prepare qualitative variables
-d$Compatibility_system[d$Compatibility_system=="dioecious"] <- "Unisexual flowers"
-d$Compatibility_system[d$Compatibility_system=="monoecious"] <- "Unisexual flowers"
-d$Compatibility_system[d$Compatibility_system=="partially_self_compatible"] <- "Partially self compatible"
-d$Compatibility_system[d$Compatibility_system=="self_compatible"] <- "Self compatible"
-d$Compatibility_system[d$Compatibility_system=="self_incompatible"] <- "Self incompatible"
-d$Compatibility_system <- factor(d$Compatibility_system, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-d$life_form[d$life_form=="herb"] <- "Herb"
-d$life_form[d$life_form=="shrub"] <- "Shrub"
-d$life_form[d$life_form=="tree"] <- "Tree"
-d$life_form[d$life_form=="vine"] <- "Shrub"
-
-d$Flower_symmetry[d$Flower_symmetry=="actinomorphic"] <- "Actinomorphic"
-d$Flower_symmetry[d$Flower_symmetry=="zygomorphic"] <- "Zygomorphic"
-
-d$Flower_symmetry[d$Flower_symmetry=="Funnelform"] <- "Campanulate"
-d$Flower_symmetry[d$Flower_symmetry=="Spike"] <- "Brush"
-
-d$Flower_morphology[d$Flower_morphology=="Funnelform"] <- "Campanulate"
-d$Flower_morphology[d$Flower_morphology=="Spike"] <- "Brush"
-
-d$Nectar_presence_absence[d$Nectar_presence_absence=="yes"] <- "Yes"
-d$Nectar_presence_absence[d$Nectar_presence_absence=="no"] <- "No"
-
-#The other qualitative are ok
-
-#All principal components are normally distributed
-#Convert to factor before running model
-d[sapply(d, is.character)] <- lapply(d[sapply(d, is.character)], as.factor)
-
-#Run model
-model1 <- lm(PC1 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
-model2 <- lm(PC2 ~ Breeding_system + Compatibility_system + lifespan + life_form + Flower_morphology + Flower_symmetry + Nectar_presence_absence, d)
-
-####################################################################################################################################################################################################################################
-#1) BREEDING SYSTEM
-####################################################################################################################################################################################################################################
-model_breeding_1 <- emmeans(model1, "Breeding_system")
-breeding_1 <- as.data.frame(model_breeding_1[1:3])
-breed1 <- multcomp::cld(model_breeding_1, alpha = 0.10, Letters = LETTERS)
-
-breed_1 <- ggplot(breed1,aes(x= Breeding_system,y= emmean,
-               label = .group)) +theme_minimal()+
-  geom_point(data = breed1, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "A Breeding system")+
-  theme(plot.title = element_text(hjust=0.5, size=26, face="bold"), plot.subtitle=element_text(size=16))+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-model_breeding_2 <- emmeans(model2, "Breeding_system")
-breeding_2 <- as.data.frame(model_breeding_2[1:3])
-breed2 <- multcomp::cld(model_breeding_2, alpha = 0.10, Letters = LETTERS)
-
-breed_2 <- ggplot(breed2,aes(x= Breeding_system,y= emmean,
-             label = .group)) +theme_minimal()+
-  geom_point(data = breed2, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "B Breeding system")+
-  theme(plot.title = element_text(hjust=0.5,size=26, face="bold"),plot.subtitle=element_text(size=16))+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-########################################################################################################################################################
-#2) COMPATIBILITY
-########################################################################################################################################################
-model_com <- emmeans(model1, "Compatibility_system")
-
-d <- as.data.frame(model_com[1:4])
-comp1 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
-
-comp_1 <- ggplot(comp1,aes(x= Compatibility_system,y= emmean,
-  label = .group)) +theme_minimal()+
-  geom_point(data = comp1, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
-  width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "C Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
-
-model_com <- emmeans(model2, "Compatibility_system")
-d <- as.data.frame(model_com[1:4])
-comp2 <- multcomp::cld(model_com, alpha = 0.10, Letters = LETTERS)
-
-comp_2 <- ggplot(comp2,aes(x= Compatibility_system,y= emmean,
-  label = .group)) +theme_minimal()+
-  geom_point(data = comp2, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
-  width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "D Compatibility system")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")
-
-########################################################################################################################################################
-#3) LIFESPAN
-########################################################################################################################################################
-model_lif_1 <- emmeans(model1, "lifespan")
-lif_1 <- as.data.frame(model_lif_1[1:2])
-lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
-
-lifespan_1 <- ggplot(lif_1,aes(x= lifespan,y= emmean,
-             label = .group)) +theme_minimal()+
-  geom_point(data = lif_1, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "E Lifespan")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-model_lif_2 <- emmeans(model2, "lifespan")
-lif_2 <- as.data.frame(model_lif_2[1:2])
-lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
-
-lifespan_2 <- ggplot(lif_2,aes(x= lifespan,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_2, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "F Lifespan")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")
-
-########################################################################################################################################################
-# 4) LIFE FORM
-########################################################################################################################################################
-
-model_lif_1 <- emmeans(model1, "life_form")
-lif_1 <- as.data.frame(model_lif_1[1:3])
-lif_1 <- multcomp::cld(model_lif_1, alpha = 0.10, Letters = LETTERS)
-
-lifeform_1 <- ggplot(lif_1,aes(x= life_form,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_1, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "G Life form")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-model_lif_2 <- emmeans(model2, "life_form")
-lif_2 <- as.data.frame(model_lif_2[1:3])
-lif_2 <- multcomp::cld(model_lif_2, alpha = 0.10, Letters = LETTERS)
-
-lifeform_2 <- ggplot(lif_2,aes(x= life_form,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = lif_2, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "H Life form")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")
-
-########################################################################################################################################################
-# 5) FLOWER MORPHOLOGY
-########################################################################################################################################################
-model_flo_1 <- emmeans(model1, "Flower_morphology")
-flo_1 <- as.data.frame(model_flo_1[1:6])
-flo_1 <- multcomp::cld(model_flo_1, alpha = 0.10, Letters = LETTERS)
-
-shape_1 <- ggplot(flo_1,aes(x= Flower_morphology,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_1, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "I Flower shape")+
-  geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")
-
-model_flo_2 <- emmeans(model2, "Flower_morphology")
-flo_2 <- as.data.frame(model_flo_2[1:6])
-flo_2 <- multcomp::cld(model_flo_2, alpha = 0.10, Letters = LETTERS)
-
-shape_2 <- ggplot(flo_2,aes(x= Flower_morphology,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_2, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "J Flower shape")+
-   geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
-
-########################################################################################################################################################
-#6) FLOWER SYMMETRY
-########################################################################################################################################################
-model_flo_sym_1 <- emmeans(model1, "Flower_symmetry")
-flo_sym_1 <- as.data.frame(model_flo_sym_1[1:2])
-flo_sym_1 <- multcomp::cld(model_flo_sym_1, alpha = 0.10, Letters = LETTERS)
-
-symmetry_1 <-ggplot(flo_sym_1,aes(x= Flower_symmetry,y= emmean,
-                 label = .group)) +theme_minimal()+
-  geom_point(data = flo_sym_1, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "K Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")
-
-model_flo_sym_2 <- emmeans(model2, "Flower_symmetry")
-flo_sym_2 <- as.data.frame(model_flo_sym_2[1:2])
-flo_sym_2 <- multcomp::cld(model_flo_sym_2, alpha = 0.10, Letters = LETTERS)
-
-symmetry_2 <- ggplot(flo_sym_2,aes(x= Flower_symmetry,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = flo_sym_2, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("sienna2","purple"))+labs(title = "L Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-########################################################################################################################################################
-#7) NECTAR
-########################################################################################################################################################
-model_nec <- emmeans(model1, "Nectar_presence_absence")
-
-model_nec_1 <- emmeans(model1, "Nectar_presence_absence")
-nec_1 <- as.data.frame(model_nec_1[1:2])
-nec_1 <- multcomp::cld(model_nec_1, alpha = 0.10, Letters = LETTERS)
-
-nectar_1 <- ggplot(nec_1,aes(x= Nectar_presence_absence,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = nec_1, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
-                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "M Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")
-
-model_nec_2 <- emmeans(model2, "Nectar_presence_absence")
-nec_2 <- as.data.frame(model_nec_2[1:2])
-nec_2 <- multcomp::cld(model_nec_2, alpha = 0.10, Letters = LETTERS)
-
-nectar_2 <-ggplot(nec_2,aes(x= Nectar_presence_absence,y= emmean,
-                     label = .group)) +theme_minimal()+
-  geom_point(data = nec_2, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
-                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
-  scale_color_manual(values=c("black","grey"))+labs(title = "N Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")
-
-#PLOT!
-
-breed_1 + breed_2+ comp_1+ comp_2+ lifespan_1+ lifespan_2+ lifeform_1+ lifeform_2+ shape_1+ shape_2+
-symmetry_1+ symmetry_2+ nectar_1+ nectar_2 + plot_layout(ncol = 2)
-
-```
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Fig.
-S8.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation.
-Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3.
-For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)"}
-
-library(Rcpp)
-library(patchwork)
-library(ggplot2)
-library(tidyr)
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2.2)),
-           axis.text=element_text(size = rel(2), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(1.8, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-
-setwd("~/Dropbox/PhD/R/Chapter_2") #DROPBOX, files too large for github
-
-#This file is produced on otehr Rmd the brms fuucntions didn't work here... Weird segfault error that I wasn't able to solve
-
-plot <- readRDS("Plot_bee_families.rds")
-
-plot
-
-```
-
-\elandscape
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S9.} Plant species level metrics across the three main axes of trait variation.", fig.pos= "h"}
-
-#library(brms) #modelling
-library(cowplot) #panel of plots
-library(ggplot2) #plotting
-library(patchwork)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(3.5)),
-           axis.text=element_text(size = rel(2.75), color = "black"),
-           legend.title=element_text(face="bold"),
-           legend.text=element_text(),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(0.4, 'lines'),
-           panel.border=element_rect(color="black",size=3),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank()
-     ))
-}
-#########
-
-setwd("~/Dropbox/PhD/R/Chapter_2")
-
-#read plot generated in other rmd, bms and stan are giving trouble here... This file is created in Species_Level_Metric_Pcs
-
-plot_metrics_pcs <- readRDS("plot_metrics_pcs.rds")
-
-plot_metrics_pcs
-
-```
-
-\elandscape

### 2023-02-14 Manuscript/Lanuza_et_al_2022.Rmd
updating ms

@@
                         "Flowers_per_plant","Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
+                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg", "Pollen_per_flower")]
 
@@
          "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
-         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg","Nectar_concentration","Pollen_per_flower")]
+         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg", "Pollen_per_flower")]
 
@@
   n_of_records$num.isna[n_of_records$key=="Flowers_per_plant"], n_of_records$num.isna[n_of_records$key=="Nectar_ul"],
-  n_of_records$num.isna[n_of_records$key=="Nectar_mg"], n_of_records$num.isna[n_of_records$key=="Nectar_concentration"], n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
+  n_of_records$num.isna[n_of_records$key=="Nectar_mg"],  n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
   n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level_fruit_set"])

### 2023-02-14 Manuscript/Lanuza_et_al_2022.tex
updating ms

@@
 For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
-From a matrix comprising a total of 28,614 possible cells (considering all traits and plant species: 19 columns × 1,506 species), we were able to fill 23,354 cells (81.6\% of the dataset, see figure S2 for missing value information for each trait).
+From a matrix comprising a total of 27,108 possible cells (considering all traits and plant species: 18 columns × 1,506 species), we were able to fill 22,796 cells (84.1\% of the dataset, see figure S2 for missing value information for each trait).
 An extended description of each trait and how it was obtained can be found in Appendix S1.
@@
 We found a strong phylogenetic signal (\emph{P} \textless{} 0.01) for most quantitative traits (table S5).
-The traits that showed the highest phylogenetic signal were ovule number (\(\lambda\) = 1), pollen grains per flower (\(\lambda\) = 1) and plant height (\(\lambda\) = 0.96), followed by flower length (\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73), number of flowers per plant (\(\lambda\) = 0.69) and nectar concentration (\(\lambda\) = 0.65).
+The traits that showed the highest phylogenetic signal were ovule number (\(\lambda\) = 1), pollen grains per flower (\(\lambda\) = 1) and plant height (\(\lambda\) = 0.96), followed by flower length (\(\lambda\) = 0.75), flower width (\(\lambda\) = 0.73) and number of flowers per plant (\(\lambda\) = 0.69).
 The traits that had a moderate phylogenetic signal included inflorescence width (\(\lambda\) = 0.57), style length (\(\lambda\) = 0.49) and autonomous selfing (\(\lambda\) = 0.34).

### 2023-02-15 Manuscript/Lanuza_et_al_2022.Rmd
adding figure pollinator guilds on trait space to main text and supp. mat.

@@
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated their position in the trait space and the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
+Similarly, we also explored for each pollinator guild (see "Visitation patterns" subsection below) the position in the trait space of the plants that interacted with them.
 We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode “covariance” because values for each variables were on the same scale following transformation [@abdi2010].
@@
 As expected, due to individual trait correlations between qualitative and quantitative traits (e.g., life form and plant height), we found that most categorical traits were clustered on the trait space and statistically associated with the first two axes of trait variation (figure s2 and table s2).
+However, the position of plants connected to each of the pollinator guilds was scattered without clear aggregation patterns on the trait space (figure s7; but see "Visitation patterns" section below for detailed results from quantitative analyses).
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed a lack of statistical association.
-In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S7).
+In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S8).
 Regarding self-compatibility, we found larger differences on PC2.
-For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S7a and figure S7b; Tukey test *P* \< 0.05).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S7c and figure S7d; Tukey test *P* \< 0.05).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f; Tukey test *P* \< 0.05).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S7g and figure S7h; Tukey test *P* \< 0.05).
-Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S7i and figure S7j; Tukey test *P* \< 0.05).
-Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S7k and figure S7l; Tukey test *P* \< 0.05).
+For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S8a and figure S8b; Tukey test *P* \< 0.05).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S8c and figure S8d; Tukey test *P* \< 0.05).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S8e and figure S8f; Tukey test *P* \< 0.05).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S8g and figure S8h; Tukey test *P* \< 0.05).
+Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S8i and figure S8j; Tukey test *P* \< 0.05).
+Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S8k and figure S8l; Tukey test *P* \< 0.05).
 
@@
 The additional models for the most represented bee families, for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and the number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03), showed that the Apidae family was the main driver of the observed patterns.
-The contrast between interaction presence/absence  and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S8).
+The contrast between interaction presence/absence  and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S9).
 
@@
 
-Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalised degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, selectivity \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
+Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S10; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalised degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, selectivity \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
 Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and selectivity.
-On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
-However, selectivity (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
-On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S9c).
-Again, selectivity showed the opposite trend to the number of visits (figure S9i).
+On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S10a).
+However, selectivity (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S10g).
+On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S10c).
+Again, selectivity showed the opposite trend to the number of visits (figure S10i).
 

### 2023-02-15 Manuscript/Lanuza_et_al_2022.tex
adding figure pollinator guilds on trait space to main text and supp. mat.

@@
 Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated their position in the trait space and the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
+Similarly, we also explored for each pollinator guild (see ``Visitation patterns'' subsection below) the position in the trait space of the plants that interacted with them.
 We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell, 2012}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode ``covariance'' because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams, 2010}).
@@
 As expected, due to individual trait correlations between qualitative and quantitative traits (e.g., life form and plant height), we found that most categorical traits were clustered on the trait space and statistically associated with the first two axes of trait variation (figure s2 and table s2).
+However, the position of plants connected to each of the pollinator guilds was scattered without clear aggregation patterns on the trait space (figure s7; but see ``Visitation patterns'' section below for detailed results from quantitative analyses).
 Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed a lack of statistical association.
-In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S7).
+In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S8).
 Regarding self-compatibility, we found larger differences on PC2.
-For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S7a and figure S7b; Tukey test \emph{P} \textless{} 0.05).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S7c and figure S7d; Tukey test \emph{P} \textless{} 0.05).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f; Tukey test \emph{P} \textless{} 0.05).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S7g and figure S7h; Tukey test \emph{P} \textless{} 0.05).
-Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S7i and figure S7j; Tukey test \emph{P} \textless{} 0.05).
-Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S7k and figure S7l; Tukey test \emph{P} \textless{} 0.05).
+For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S8a and figure S8b; Tukey test \emph{P} \textless{} 0.05).
+Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S8c and figure S8d; Tukey test \emph{P} \textless{} 0.05).
+Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S8e and figure S8f; Tukey test \emph{P} \textless{} 0.05).
+Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S8g and figure S8h; Tukey test \emph{P} \textless{} 0.05).
+Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S8i and figure S8j; Tukey test \emph{P} \textless{} 0.05).
+Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S8k and figure S8l; Tukey test \emph{P} \textless{} 0.05).
 
@@
 The additional models for the most represented bee families, for both presence-absence of interactions (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and the number of visits (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03), showed that the Apidae family was the main driver of the observed patterns.
-The contrast between interaction presence/absence and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S8).
+The contrast between interaction presence/absence and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S9).
 
@@
 
-Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalised degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, selectivity \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
+Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S10; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalised degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, selectivity \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03).
 Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and selectivity.
-On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a).
-However, selectivity (d') was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g).
-On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S9c).
-Again, selectivity showed the opposite trend to the number of visits (figure S9i).
+On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S10a).
+However, selectivity (d') was higher for plant species with large flowers but lower for plant species with small flowers (figure S10g).
+On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S10c).
+Again, selectivity showed the opposite trend to the number of visits (figure S10i).
 

### 2023-02-15 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
adding figure pollinator guilds on trait space to main text and supp. mat.

@@
 
-Figures S1 to S9
+Figures S1 to S10
 
@@
 
+\blandscape
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="85%",  fig.height=12, fig.width=18,fig.align='center',  fig.cap="\\textbf{Fig.
+S7.} Location in the trait space of the plants that were visited by each of the different pollinator guilds.
+The red square indicates that the pollinator guild has been observed in that specific plant.
+Note that the interactions used to represent the plant-pollinator guild connection are a subset of the total interactions considered in this study as indicated in the Network analysis section (see main text)."}
+
+#Create panel with all plots, qualitative version
+
+library(ggplot2)
+
+#Load plots
+bees = readRDS("../Data/RData/Bee_PCA.rds")
+coleoptera = readRDS("../Data/RData/Coleoptera_PCA.rds")
+lepidoptera = readRDS("../Data/RData/Lepidoptera_PCA.rds")
+non_bee_hymenoptera = readRDS("../Data/RData/Non_bee_hymenoptera_PCA.rds")
+non_syrphid_diptera = readRDS("../Data/RData/Non_syrphid_diptera_PCA.rds")
+syrphids = readRDS("../Data/RData/Syrphids_PCA.rds")
+
+#Make plot
+library(patchwork)
+
+bees  + lepidoptera + non_syrphid_diptera + 
+coleoptera + non_bee_hymenoptera  + syrphids
+
+```
+
+\elandscape
+
 \newpage
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig.
-S9.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows).
+S10.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows).
 The x-axis shows the most illustrative trait extremes of the trait continuum.

### 2023-02-16 Manuscript/Lanuza_et_al_2022.Rmd
brief descrp of repro traits

@@
 
-To avoid excluding species with trait missing values, we imputed trait missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of datasets with continuous and categorical variables.
+To avoid excluding species with missing trait data, we imputed missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of datasets with continuous and categorical variables.
 We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors from principal component analysis of the phylogenetic distance (PCoA), which has been shown to improve the performance of *missForest* [@penone2014].
@@
 ```
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different pollinator guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).

### 2023-02-16 Manuscript/Lanuza_et_al_2022.tex
brief descrp of repro traits

@@
 
-To avoid excluding species with trait missing values, we imputed trait missing values with the help of the function \emph{missForest} (\protect\hyperlink{ref-stekhoven2012}{Stekhoven \& Bühlmann, 2012}) which allows imputation of datasets with continuous and categorical variables.
+To avoid excluding species with missing trait data, we imputed missing values with the help of the function \emph{missForest} (\protect\hyperlink{ref-stekhoven2012}{Stekhoven \& Bühlmann, 2012}) which allows imputation of datasets with continuous and categorical variables.
 We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors from principal component analysis of the phylogenetic distance (PCoA), which has been shown to improve the performance of \emph{missForest} (\protect\hyperlink{ref-penone2014}{Penone et al., 2014}).

### 2023-02-16 Manuscript/Trial.Rmd
brief descrp of repro traits

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="80%",fig.align='center',fig.cap= "\\textbf{Figure 2.} Location of the different qualitative traits in the trait space.
-The figure panel is composed of the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
-The solid arrows indicate the direction of variation of the different quantitative traits shown in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different pollinator guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
+PC1 represents the flower number - flower size axis, PC2 represents the autonomous selfing - floral display axis and PC3 represents the style length - autonomous selfing axis.
+For visualization purposes due to large differences between number of visits from bees and the rest of the pollinator guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
 
-#Load libraries
 #LOAD LIBRARIES 
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
+#library(phytools)
+#library(ape) #for phylogenetic distance
+#library(dplyr) #data processing
+#library(rtrees) #for phylogenetic distancelibrary(MASS)
+#library(reshape2)
 library(viridis) #COLOUR GGPLOT
-library(MASS)
+#library(MASS)
 library(ggplot2)
 library(broman) #crayon colours
-library(cowplot)
-library(ggstar)
+#library(tidyverse)
+library(patchwork) #panel of plots
+#library(brms)
+#library(cmdstanr)
 
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
+#Load theme for publication
+
+theme_ms <- function(base_size=14, base_family="Helvetica") {
   (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.6)),
-            axis.text=element_text(size = rel(1.6), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(size = rel(1.1)),
+           axis.title=element_text( size = rel(2)),
+           axis.text=element_text(size = rel(1.8), color = "black"),
+           legend.title=element_text(face="bold",size=rel(2)),
+           legend.text=element_text(size=rel(1.4)),
            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.4, 'lines'),
-            panel.border=element_rect(color="black",size=1),
+           legend.key.size = unit(2, 'lines'),
+           panel.border=element_rect(color="black",size=2.4),
            panel.grid.minor.x =element_blank(),
@@
            panel.grid.major= element_blank(),
-            plot.title = element_text(size = rel(2.5), face="bold")
+           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
+           plot.subtitle = element_text(face="bold",size=rel(2))
      ))
@@
 
-#Load data
-dat_cleaning_5 <- readRDS("../Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
-phyl_pca_forest <- readRDS("../Data/RData/phyl_pca_forest.rds")
+p1 <- readRDS("../Main_Figures/figure_3_1.rds")
+p2 <- readRDS("../Main_Figures/figure_3_2.rds")
+p3 <- readRDS("../Main_Figures/figure_3_3.rds")
+pp1 <- readRDS("../Main_Figures/figure_3_4.rds")
+pp2 <- readRDS("../Main_Figures/figure_3_5.rds")
+pp3 <- readRDS("../Main_Figures/figure_3_6.rds")
 
-#CALL the output PC for simplicity
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
+library(patchwork)
 
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-Compatibility <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
+combined <- pp1 + pp2 + pp3 + p1 + p2 + p3  & theme(legend.position = "bottom") &  guides(color = guide_legend(override.aes = list(size=6.5), keywidth=1.8, keyheight=0.1,default.unit="inch"))
 
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Compatibility <- dat_cleaning_5$Compatibility_system
-  dat$Compatibility <- as.character(dat$Compatibility)
-  dat$Compatibility[dat$Compatibility=="dioecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="monoecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-  dat$Compatibility[dat$Compatibility=="self_compatible"] <- "Self compatible"
-  dat$Compatibility[dat$Compatibility=="self_incompatible"] <- "Self incompatible"
-  dat$Compatibility <- factor(dat$Compatibility, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=Compatibility, fill=Compatibility), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("deepskyblue2", "purple2","goldenrod","gray7")) +
-scale_starshape_manual(values = c(13, 15, 28, 5))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)  + ylab("Autonomous selfing - Floral display axis")
-
-  plot
-
-}
-
-#Compatibility(PC)
-
-#############################################################################################################################################################
-#Life form
-#############################################################################################################################################################
-#Load plots
-Life_form <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Life form` <- dat_cleaning_5$life_form
-  dat$`Life form` <- as.character(dat$`Life form`)
-  dat$`Life form`[dat$`Life form`=="herb"] <- "Herb"
-  dat$`Life form`[dat$`Life form`=="shrub"] <- "Shrub"
-  dat$`Life form`[dat$`Life form`=="tree"] <- "Tree"
-  dat$`Life form`[dat$`Life form`=="vine"] <- "Shrub"
-
-  dat$`Life form` <- factor( dat$`Life form`, levels = c("Herb", "Shrub", "Tree"))
-
-plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Life form`, fill=`Life form`), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("forestgreen", "darkorange2","black")) +
-scale_starshape_manual(values = c(13, 15, 28))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.090, 0.115)) + ggtitle("(b)") +
-    xlab(NULL) + ylab(NULL)
-
-  plot
-
-}
-
-#Life_form(PC)
-
-#############################################################################################################################################################
-#Life span
-#############################################################################################################################################################
-#Load plots
-Life_span <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-    dat$Lifespan <- dat_cleaning_5$lifespan
-    dat$Lifespan <- as.character(dat$Lifespan)
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=Lifespan, fill=Lifespan), size=2.25, color= NA, alpha = 0.9)+ scale_fill_manual(values=c("sienna4","forestgreen")) +
-scale_starshape_manual(values = c(13, 15))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.12, 0.1)) + ggtitle("(c)") +
-    xlab(NULL) + ylab(NULL)
-
-  plot
-
-}
-
-#Life_span(PC)
-
-#############################################################################################################################################################
-#Flower symmetry
-#############################################################################################################################################################
-#Load plots
-Flower_sym <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower symmetry` <- dat_cleaning_5$Flower_symmetry
-  dat$`Flower symmetry` <- as.character(dat$`Flower symmetry`)
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Flower symmetry`, fill=`Flower symmetry`), size=2.25, color= NA, alpha = 0.9) + scale_fill_manual(values=c("goldenrod","purple2")) +
-scale_starshape_manual(values = c(13, 15))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL) + xlab("Flower number - Flower size axis")
-
-  plot
-
-}
-
-#Flower_sym(PC)
-
-#############################################################################################################################################################
-#Flower shape
-#############################################################################################################################################################
-#Load plots
-Flower_sha <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower shape` <- dat_cleaning_5$Flower_morphology
-  dat$`Flower shape` <- as.character(dat$`Flower shape`)
-  dat$`Flower shape`[dat$`Flower shape`=="Funnelform"] <- "Campanulate"
-  dat$`Flower shape`[dat$`Flower shape`=="Spike"] <- "Brush"
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Flower shape`, fill=`Flower shape`), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("black","goldenrod", "deepskyblue2","forestgreen","purple2","darkorange2")) +
-scale_starshape_manual(values = c(13, 15, 28, 5, 9, 14))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL) + xlab("Flower number - Flower size axis")
-
-  plot
-
-}
-
-#Flower_sha(PC)
-
-#############################################################################################################################################################
-#Breeding system
-#############################################################################################################################################################
-#Load plots
-Breeding_syst <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Breeding system` <- dat_cleaning_5$Breeding_system
-  dat$`Breeding system` <- as.character(dat$`Breeding system`)
-  dat$`Breeding system` <- factor(dat$`Breeding system`, levels=c("Hermaphrodite","Monoecious" ,"Dioecious"))
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Breeding system`, fill=`Breeding system`), size=2.25, color= NA, alpha = 0.9) + scale_fill_manual(values=c("forestgreen","darkorange2", "black")) +
-scale_starshape_manual(values = c(13, 15, 28))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("(d)") +
-    xlab("Flower number - Flower size axis") +
-    ylab("Autonomous selfing - Floral display axis")
-
-  plot
-
-}
-
-#Breeding_syst(PC)
-
-#############################################################################################################################################################
-#Nectar
-#############################################################################################################################################################
-#Load plots
-#Nectar <- function(PC, x="PC1", y="PC2") {
-#  # PC being a prcomp object
-#  data <- data.frame(PC$S)
-#  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-#  dat <- data.frame(x = data[,x], y = data[,y])
-#  
-#  #######
-#  #DENSITY FUNCTION
-#  #######
-#  get_density <- function(x, y, ...) {
-#    dens <- MASS::kde2d(x, y, ...)
-#    ix <- findInterval(x, dens$x)
-#    iy <- findInterval(y, dens$y)
-#    ii <- cbind(ix, iy)
-#    return(dens$z[ii])
-#  }
-#  
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-#  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-#  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-#  plot <- plot + geom_point(data=dat, aes(-x, -y, #colour=Nectar),size=1.75)+scale_color_manual(values=c("black","grey"))
-#  
-#  ########
-#  #ADD ARROWS 
-#  ########
-#  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-#  mult <- min(
-#    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-#    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-#  )
-#  datapc <- transform(datapc,
-#                      v1 = .75 * mult * (get(x)),
-#                      v2 = .75 * mult * (get(y))
-#  )
-#  # add arrows
-#  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, #yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-#  
-#  #Add axis with perctentage
-#  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-#
-#  
-#  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, #arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-#  
-#  #ADD LABELS
-#  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-#  
-#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-#  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = #-(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-#                          label = PCAloadings$Variables, color="black",size=3)
-#  
-#  #CHANGE THEME
-#  #CHANGE THEME
-#  
-#  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)") 
-#  
-#  plot
-#  
-#}
-#
-# #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")
-
-  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),ncol=3,nrow=2,  align = "hv")
-
+combined + plot_layout(guides = "collect",ncol = 3)
 ```

### 2023-02-16 Manuscript/Lanuza_et_al_2022.Rmd
adding def of rep traits

@@
 The variety of reproductive strategies used by different plant species, from specialised reliance on a single pollinator, to full self-pollination, is incredibly rich.
-However, not all reproductive trait combinations in plants are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
+However, not all combinations of reproductive traits (i.e., morphological and physiological traits that determine a plant’s ability to reproduce) are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
 Despite recent advances in theoretical and empirical understanding of correlations between plant reproductive traits at large ecological scales [@salguero2016; @friedman2020; @paterno2020; @roddy2021; @song2022], studies typically focus on just a few traits, often in isolation.

### 2023-02-16 Manuscript/Lanuza_et_al_2022.tex
adding def of rep traits

@@
 The variety of reproductive strategies used by different plant species, from specialised reliance on a single pollinator, to full self-pollination, is incredibly rich.
-However, not all reproductive trait combinations in plants are possible due to evolutionary and ecological constraints (\protect\hyperlink{ref-agrawal2020}{Agrawal, 2020}; \protect\hyperlink{ref-stearns1989}{Stearns, 1989}).
+However, not all combinations of reproductive traits (i.e., morphological and physiological traits that determine a plant's ability to reproduce) are possible due to evolutionary and ecological constraints (\protect\hyperlink{ref-agrawal2020}{Agrawal, 2020}; \protect\hyperlink{ref-stearns1989}{Stearns, 1989}).
 Despite recent advances in theoretical and empirical understanding of correlations between plant reproductive traits at large ecological scales (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-paterno2020}{Paterno et al., 2020}; \protect\hyperlink{ref-roddy2021}{Roddy et al., 2021}; \protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}; \protect\hyperlink{ref-song2022}{Song et al., 2022}), studies typically focus on just a few traits, often in isolation.

### 2023-02-24 Manuscript/Lanuza_et_al_2022.Rmd
New two paragraphs on the discussion, much more extended now

@@
 
-Overall, plant reproductive traits explained interaction patterns among and within pollinator guilds suggesting that plant reproductive strategies partly mediate these associations across spatial large scales.
-For example, we found that all pollinator guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings [@hegland2005; @lazaro2013; @kaiser2014].
-As predicted by evolutionary life-history theory [@stebbins1970], larger investment in floral display and rewards to attract pollinators occurs when pollinator dependence is high.
-Indeed, the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different pollinator guilds [@galen1999].
-For instance, smaller flowers are visited less overall, but they are inexpensive to produce (e.g., have a low ovule number) and low visitation rate at the individual flower level can be compensated by overall visitation at the plant level by producing many flowers resulting in a larger quantity of small fruits [@kettle2011].
-In addition, we found that a substantial number of species with high autonomous selfing had large styles and were associated with a high number of interactions with bees.
-These species seem to rely on animal pollinators as indicated by their high investment in sizable styles that can help prevent pollen competition [@ramesha2011; @ashman2013; @lanuza2021] while having reproductive assurance in their absence.
-For instance, the annual herb _Scabiosa atropurpurea_ has flowers grouped in clusters with relatively long styles and a single ovule per flower that is likely to be fertilised with a single legitimate floral visit but avoids reproductive failure with autonomous self pollination.
-Similarly, zygomorphic flowers are specialised floral structures that promote precise pollen transfer [@sargent2004; @gong2009] but they were associated with high levels of autogamy.
-Our findings are consistent with the idea that reproductive assurance is not rare within specialised pollination systems [@fenster2007] and highlight the need to explore the timing (e.g., early versus delayed) and selfing mechanisms [see @goodwillie2018] in relation to other reproductive traits to better understand reproductive trait correlations and plant-pollinator interactions.
-
-Because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and pollinator guilds could indicate the existence of pollination syndromes [@fenster2004; @faegri2013; @rosas2014; @dellinger2020].
-For instance, bees had a higher number of interacting partners on plant species with large flowers but interacted more frequently with species with small flowers while syrphid flies showed the opposite trend.
-This could be reflective of differences in the ecology and behaviour between these pollinator guilds [@rader2020; @foldesi2021] that ultimately exert different selective pressures, leading divergent plant reproductive strategies.
-In any case, it is worth noting that local factors (e.g., species relative abundances or phenologies) likely contribute to the variability in the association between the plant reproductive spectrum and pollinators [@vazquez2007; @encinas2012; @bartomeus2016].
-Taking both aspects together, we suggest that while plant reproductive traits do shape their interactions with pollinators, pollinator syndromes at a macroecological scale are not distinct compartmentalised items, but form part of a multifaceted context dependent continuum.
+Overall, the main plant reproductive axes were insufficient to fully capture plant-pollinator associations.
+However, these axes helped explain, to some extent, interaction patterns among and within pollinator guilds, indicating that they partly mediate these associations across large spatial scales.
+For example, we found that all pollinator guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings [@hegland2005; @lazaro2013; @kaiser2014] and predictions from evolutionary life-history theory [@stebbins1970].
+These predictions suggest that larger investment in floral display and rewards to attract pollinators occurs when dependence on pollinators is high.
+Although pollinators play a major role in shaping plant reproductive strategies, these different strategies are also constrained by the cost of reproductive organs and trait correlations [@galen1999].
+For instance, smaller flowers tend to receive fewer visits than larger flowers, but small flowers are inexpensive to produce (e.g., have few ovules).
+Therefore, low  per-flower visitation can be compensated by overall plant-level visitation through producing many small flowers that develop into numerous small fruits [@kettle2011].
+Our results also indicate that bees interact more with plants that have higher levels of autonomous selfing and large styles, which can help with a more efficient pollen transfer and prevent pollen competition [@ashman2013; @tong2016; @lanuza2021].
+Similarly, the specialised floral structures of zygomorphic flowers promote precise pollen transfer [@sargent2004; @gong2009], although we found that they were associated with high levels of autogamy.
+The annual herb _Lathyrus clymenum_ is a clear example of this pollinator specialization - selfing strategy that may get “the best of both worlds” [@lloyd1992; @goodwillie2018].
+It has showy zygomorphic flowers with relatively long styles and few ovules per flower that are likely fertilised with a single legitimate floral visit but can avoid reproductive failure in the absence of pollinators through autonomous self pollination.
+Our findings are consistent with the hypothesis that selfing is not rare within specialised pollination systems [@fenster2007] and emphasise the need to consider different reproductive assurance mechanisms [e.g., early versus delayed selfing\; @goodwillie2018] to better understand plant reproductive trait correlations and plant-pollinator interactions.
+
+Because flowering plants can adapt to their animal pollinators to optimise pollen transfer, the correlation between distinct suites of plant reproductive traits and pollinator guilds could indicate the existence of pollination syndromes [@fenster2004; @faegri2013; @rosas2014; @dellinger2020].
+However, our work shows a weak association between the different plant reproductive strategies and pollinator guilds, which supports previous findings from a similar pollinator guild classification and spatial scale [@ollerton2009].
+Although our findings contrast with a vast amount of literature on pollinator syndromes dating back over half a century [@faegri2013; @fenster2004], the ecological scale of our study differs from the majority of floral syndrome studies that rarely consider plant-pollinator associations beyond the community scale [ca.
+3% of studies\; @dellinger2020].
+We argue that the predictive power of floral syndromes gets blurred when increasing the number of species and scale, reinforcing the view that strong specialisation may be the exception rather than the norm in plant-pollinator interactions [@jordano1987; @waser1996].
+Further, there are several factors that might have influenced our findings, (e.g., the suite of reproductive traits and type of pollinator guilds we included).
+For instance, including other key reproductive traits, such as floral scent or flower colour, could help to improve predictions of plant-pollinator interactions.
+In addition, our use of broad taxonomic pollinator guild groupings may have obscured  finer scale patterns that occur at lower taxonomic ranks (e.g., genus or species level).
+The fact that our study only accounts for insect pollinators may have also influenced the observed associations between floral traits and pollinator guilds in comparison with other studies, as some other guilds (e.g., hummingbirds or bats) generally display strong trait-matching [@wilson2004; @lagomarsino2017].
+Regardless, it is worth noting that local factors (e.g., species relative abundances, phenologies or intraspecific variation) likely contribute to the variability in interactions between the plant reproductive spectrum and pollinators [@vazquez2007; @encinas2012; @bartomeus2016; @arroyo2023].
+We suggest that while plant reproductive traits do influence which pollinators they interact with, at a macroecological scale, pollination syndromes possibly take the form of a multifaceted, context dependent continuum [e.g., ornithophilous versus entomophilous pollination of red flowers\; @leon2022].
 

### 2023-02-24 Manuscript/Lanuza_et_al_2022.tex
New two paragraphs on the discussion, much more extended now

@@
 
-Overall, plant reproductive traits explained interaction patterns among and within pollinator guilds suggesting that plant reproductive strategies partly mediate these associations across spatial large scales.
-For example, we found that all pollinator guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings (\protect\hyperlink{ref-hegland2005}{Hegland \& Totland, 2005}; \protect\hyperlink{ref-kaiser2014}{Kaiser-Bunbury et al., 2014}; \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}).
-As predicted by evolutionary life-history theory (\protect\hyperlink{ref-stebbins1970}{Stebbins, 1970}), larger investment in floral display and rewards to attract pollinators occurs when pollinator dependence is high.
-Indeed, the possible range of reproductive strategies in flowering plants is constrained by the cost of reproductive organs, trait associations and selective pressures exerted by different pollinator guilds (\protect\hyperlink{ref-galen1999}{Galen, 1999}).
-For instance, smaller flowers are visited less overall, but they are inexpensive to produce (e.g., have a low ovule number) and low visitation rate at the individual flower level can be compensated by overall visitation at the plant level by producing many flowers resulting in a larger quantity of small fruits (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}).
-In addition, we found that a substantial number of species with high autonomous selfing had large styles and were associated with a high number of interactions with bees.
-These species seem to rely on animal pollinators as indicated by their high investment in sizable styles that can help prevent pollen competition (\protect\hyperlink{ref-ashman2013}{Ashman \& Arceo-Gómez, 2013}; \protect\hyperlink{ref-lanuza2021}{Lanuza et al., 2021}; \protect\hyperlink{ref-ramesha2011}{Ramesha et al., 2011}) while having reproductive assurance in their absence.
-For instance, the annual herb \emph{Scabiosa atropurpurea} has flowers grouped in clusters with relatively long styles and a single ovule per flower that is likely to be fertilised with a single legitimate floral visit but avoids reproductive failure with autonomous self pollination.
-Similarly, zygomorphic flowers are specialised floral structures that promote precise pollen transfer (\protect\hyperlink{ref-gong2009}{Gong \& Huang, 2009}; \protect\hyperlink{ref-sargent2004}{Sargent, 2004}) but they were associated with high levels of autogamy.
-Our findings are consistent with the idea that reproductive assurance is not rare within specialised pollination systems (\protect\hyperlink{ref-fenster2007}{Fenster \& Marten-Rodriguez, 2007}) and highlight the need to explore the timing (e.g., early versus delayed) and selfing mechanisms (see \protect\hyperlink{ref-goodwillie2018}{Goodwillie \& Weber, 2018}) in relation to other reproductive traits to better understand reproductive trait correlations and plant-pollinator interactions.
-
-Because floral traits can be associated with their animal pollinators to optimise pollen transfer, the correlation between distinct suites of reproductive traits and pollinator guilds could indicate the existence of pollination syndromes (\protect\hyperlink{ref-dellinger2020}{Dellinger, 2020}; \protect\hyperlink{ref-faegri2013}{Faegri \& Van Der Pijl, 2013}; \protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero et al., 2014}).
-For instance, bees had a higher number of interacting partners on plant species with large flowers but interacted more frequently with species with small flowers while syrphid flies showed the opposite trend.
-This could be reflective of differences in the ecology and behaviour between these pollinator guilds (\protect\hyperlink{ref-foldesi2021}{Földesi et al., 2021}; \protect\hyperlink{ref-rader2020}{Rader et al., 2020}) that ultimately exert different selective pressures, leading divergent plant reproductive strategies.
-In any case, it is worth noting that local factors (e.g., species relative abundances or phenologies) likely contribute to the variability in the association between the plant reproductive spectrum and pollinators (\protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-encinas2012}{Encinas-Viso et al., 2012}; \protect\hyperlink{ref-vazquez2007}{Vázquez et al., 2007}).
-Taking both aspects together, we suggest that while plant reproductive traits do shape their interactions with pollinators, pollinator syndromes at a macroecological scale are not distinct compartmentalised items, but form part of a multifaceted context dependent continuum.
+Overall, the main plant reproductive axes were insufficient to fully capture plant-pollinator associations.
+However, these axes helped explain, to some extent, interaction patterns among and within pollinator guilds, indicating that they partly mediate these associations across large spatial scales.
+For example, we found that all pollinator guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings (\protect\hyperlink{ref-hegland2005}{Hegland \& Totland, 2005}; \protect\hyperlink{ref-kaiser2014}{Kaiser-Bunbury et al., 2014}; \protect\hyperlink{ref-lazaro2013}{Lázaro et al., 2013}) and predictions from evolutionary life-history theory (\protect\hyperlink{ref-stebbins1970}{Stebbins, 1970}).
+These predictions suggest that larger investment in floral display and rewards to attract pollinators occurs when dependence on pollinators is high.
+Although pollinators play a major role in shaping plant reproductive strategies, these different strategies are also constrained by the cost of reproductive organs and trait correlations (\protect\hyperlink{ref-galen1999}{Galen, 1999}).
+For instance, smaller flowers tend to receive fewer visits than larger flowers, but small flowers are inexpensive to produce (e.g., have few ovules).
+Therefore, low per-flower visitation can be compensated by overall plant-level visitation through producing many small flowers that develop into numerous small fruits (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}).
+Our results also indicate that bees interact more with plants that have higher levels of autonomous selfing and large styles, which can help with a more efficient pollen transfer and prevent pollen competition (\protect\hyperlink{ref-ashman2013}{Ashman \& Arceo-Gómez, 2013}; \protect\hyperlink{ref-lanuza2021}{Lanuza et al., 2021}; \protect\hyperlink{ref-tong2016}{Tong \& Huang, 2016}).
+Similarly, the specialised floral structures of zygomorphic flowers promote precise pollen transfer (\protect\hyperlink{ref-gong2009}{Gong \& Huang, 2009}; \protect\hyperlink{ref-sargent2004}{Sargent, 2004}), although we found that they were associated with high levels of autogamy.
+The annual herb \emph{Lathyrus clymenum} is a clear example of this pollinator specialization - selfing strategy that may get ``the best of both worlds'' (\protect\hyperlink{ref-goodwillie2018}{Goodwillie \& Weber, 2018}; \protect\hyperlink{ref-lloyd1992}{Lloyd \& Schoen, 1992}).
+It has showy zygomorphic flowers with relatively long styles and few ovules per flower that are likely fertilised with a single legitimate floral visit but can avoid reproductive failure in the absence of pollinators through autonomous self pollination.
+Our findings are consistent with the hypothesis that selfing is not rare within specialised pollination systems (\protect\hyperlink{ref-fenster2007}{Fenster \& Marten-Rodriguez, 2007}) and emphasise the need to consider different reproductive assurance mechanisms (e.g., early versus delayed selfing; \protect\hyperlink{ref-goodwillie2018}{Goodwillie \& Weber, 2018}) to better understand plant reproductive trait correlations and plant-pollinator interactions.
+
+Because flowering plants can adapt to their animal pollinators to optimise pollen transfer, the correlation between distinct suites of plant reproductive traits and pollinator guilds could indicate the existence of pollination syndromes (\protect\hyperlink{ref-dellinger2020}{Dellinger, 2020}; \protect\hyperlink{ref-faegri2013}{Faegri \& Van Der Pijl, 2013}; \protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}; \protect\hyperlink{ref-rosas2014}{Rosas-Guerrero et al., 2014}).
+However, our work shows a weak association between the different plant reproductive strategies and pollinator guilds, which supports previous findings from a similar pollinator guild classification and spatial scale (\protect\hyperlink{ref-ollerton2009}{Ollerton et al., 2009}).
+Although our findings contrast with a vast amount of literature on pollinator syndromes dating back over half a century (\protect\hyperlink{ref-faegri2013}{Faegri \& Van Der Pijl, 2013}; \protect\hyperlink{ref-fenster2004}{Fenster et al., 2004}), the ecological scale of our study differs from the majority of floral syndrome studies that rarely consider plant-pollinator associations beyond the community scale (ca.
+3\% of studies; \protect\hyperlink{ref-dellinger2020}{Dellinger, 2020}).
+We argue that the predictive power of floral syndromes gets blurred when increasing the number of species and scale, reinforcing the view that strong specialisation may be the exception rather than the norm in plant-pollinator interactions (\protect\hyperlink{ref-jordano1987}{Jordano, 1987}; \protect\hyperlink{ref-waser1996}{Waser et al., 1996}).
+Further, there are several factors that might have influenced our findings, (e.g., the suite of reproductive traits and type of pollinator guilds we included).
+For instance, including other key reproductive traits, such as floral scent or flower colour, could help to improve predictions of plant-pollinator interactions.
+In addition, our use of broad taxonomic pollinator guild groupings may have obscured finer scale patterns that occur at lower taxonomic ranks (e.g., genus or species level).
+The fact that our study only accounts for insect pollinators may have also influenced the observed associations between floral traits and pollinator guilds in comparison with other studies, as some other guilds (e.g., hummingbirds or bats) generally display strong trait-matching (\protect\hyperlink{ref-lagomarsino2017}{Lagomarsino et al., 2017}; \protect\hyperlink{ref-wilson2004}{Wilson et al., 2004}).
+Regardless, it is worth noting that local factors (e.g., species relative abundances, phenologies or intraspecific variation) likely contribute to the variability in interactions between the plant reproductive spectrum and pollinators (\protect\hyperlink{ref-arroyo2023}{Arroyo-Correa et al., 2023}; \protect\hyperlink{ref-bartomeus2016}{Bartomeus et al., 2016}; \protect\hyperlink{ref-encinas2012}{Encinas-Viso et al., 2012}; \protect\hyperlink{ref-vazquez2007}{Vázquez et al., 2007}).
+We suggest that while plant reproductive traits do influence which pollinators they interact with, at a macroecological scale, pollination syndromes possibly take the form of a multifaceted, context dependent continuum (e.g., ornithophilous versus entomophilous pollination of red flowers; \protect\hyperlink{ref-leon2022}{León-Osper \& Narbona, 2022}).
 
@@
 Agrawal, A. A. (2020). A scale-dependent framework for trade-offs, syndromes, and specialization in organismal biology. \emph{Ecology}, \emph{101}(2), e02924. \url{https://doi.org/10.1002/ecy.2924}
+
+\leavevmode\vadjust pre{\hypertarget{ref-arroyo2023}{}}%
+Arroyo-Correa, B., Jordano, P., \& Bartomeus, I.
+(2023).
+Intraspecific variation in species interactions promotes the feasibility of mutualistic assemblages.
+\emph{Ecology Letters}.
+\url{https://doi.org/10.1111/ele.14163}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
-Földesi, R., Howlett, B.
-G., Grass, I., \& Batáry, P.
-(2021).
-Larger pollinators deposit more pollen on stigmas across multiple plant species---a meta-analysis.
-\emph{J.
-Appl.
-Ecol.}, \emph{58}(4), 699--707.
-\url{https://doi.org/10.1111/1365-2664.13798}
-
 \leavevmode\vadjust pre{\hypertarget{ref-fortuna2010}{}}%
@@
 \url{https://doi.org/10.1111/ecog.04434}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jordano1987}{}}%
+Jordano, P.
+(1987).
+Patterns of mutualistic interactions in pollination and seed dispersal: Connectance, dependence asymmetries, and coevolution.
+\emph{The American Naturalist}, \emph{129}(5), 657--677.
+\url{https://doi.org/10.1086/284665}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-lagomarsino2017}{}}%
+Lagomarsino, L.
+P., Forrestel, E.
+J., Muchhala, N., \& Davis, C.
+C.
+(2017).
+Repeated evolution of vertebrate pollination syndromes in a recently diverged andean plant clade.
+\emph{Evolution}, \emph{71}(8), 1970--1985.
+
 \leavevmode\vadjust pre{\hypertarget{ref-lanuza2021}{}}%
@@
 Legendre, P., \& Legendre, L. (2012). \emph{Numerical ecology} ({2nd edn}). {Elsevier, Amsterdam}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-leon2022}{}}%
+León-Osper, M., \& Narbona, E.
+(2022).
+Unravelling the mystery of red flowers in the mediterranean basin: How to be conspicuous in a place dominated by hymenopteran pollinators.
+\emph{Functional Ecology}, \emph{36}(11), 2774--2790.
+\url{https://doi.org/10.1111/1365-2435.14166}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lloyd1992}{}}%
+Lloyd, D.
+G., \& Schoen, D.
+J.
+(1992).
+Self-and cross-fertilization in plants.
+I.
+Functional dimensions.
+\emph{International Journal of Plant Sciences}, \emph{153}(3, Part 1), 358--369.
+\url{https://doi.org/10.1086/297040}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ollerton2009}{}}%
+Ollerton, J., Alarcón, R., Waser, N.
+M., Price, M.
+V., Watts, S., Cranmer, L., Hingston, A., Peter, C.
+I., \& Rotenberry, J.
+(2009).
+A global test of the pollination syndrome hypothesis.
+\emph{Annals of Botany}, \emph{103}(9), 1471--1480.
+
 \leavevmode\vadjust pre{\hypertarget{ref-osnas2013}{}}%
@@
 \url{https://doi.org/10.1111/ecog.00976}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rader2020}{}}%
-Rader, R., Cunningham, S., Howlett, B., \& Inouye, D.
-(2020).
-Non-bee insects as visitors and pollinators of crops: Biology, ecology, and management.
-\emph{Annu.
-Rev.
-Entomol.}, \emph{65}, 391--407.
-\url{https://doi.org/10.1146/annurev-ento-011019-025055}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ramesha2011}{}}%
-Ramesha, B., Yetish, M., Ravikanth, G., Ganeshaiah, K., Ghazoul, J., \& Shaanker, R.
-U.
-(2011).
-Stylish lengths: Mate choice in flowers.
-\emph{Journal of Biosciences}, \emph{36}(2), 229--234.
-\url{https://doi.org/10.1007/s12038-011-9057-6}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-tong2016}{}}%
+Tong, Z.-Y., \& Huang, S.-Q.
+(2016).
+Pre-and post-pollination interaction between six co-flowering pedicularis species via heterospecific pollen transfer.
+\emph{New Phytologist}, \emph{211}(4), 1452--1461.
+\url{https://doi.org/10.1111/nph.14005}
+
 \leavevmode\vadjust pre{\hypertarget{ref-tur2013}{}}%
@@
 \url{https://doi.org/10.1111/j.1461-0248.2005.00810.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-waser1996}{}}%
+Waser, N.
+M., Chittka, L., Price, M.
+V., Williams, N.
+M., \& Ollerton, J.
+(1996).
+Generalization in pollination systems, and why it matters.
+\emph{Ecology}, \emph{77}(4), 1043--1060.
+\url{https://doi.org/10.2307/2265575}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wilson2004}{}}%
+Wilson, P., Castellanos, M.
+C., Hogue, J.
+N., Thomson, J.
+D., \& Armbruster, W.
+S.
+(2004).
+A multivariate search for pollination syndromes among penstemons.
+\emph{Oikos}, \emph{104}(2), 345--361.
+\url{https://doi.org/10.1111/j.0030-1299.2004.12819.x}
 

### 2023-02-27 Manuscript/Lanuza_et_al_2022.Rmd
Updating references and fixing style

@@
 Many of these networks are freely available either as published studies [e.g., @carvalheiro2014; @olesen2007; @fortuna2010] or in online archives [e.g., Mangal @poisot2016;  The Web of Life @fortuna2010].
-In total, our network dataset constituted 60 weighted (number of visits) and four unweighted (interaction presence-absence) networks, each sampled at a unique location and year, as well as eight meta-networks where interactions were pooled across several locations and multiple years.
+In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (interaction presence-absence) networks, each sampled at a unique location and year, as well as 8 meta-networks where interactions were pooled across several locations and multiple years.
 

### 2023-02-27 Manuscript/Lanuza_et_al_2022.tex
Updating references and fixing style

@@
 Many of these networks are freely available either as published studies (e.g., \protect\hyperlink{ref-carvalheiro2014}{Carvalheiro et al., 2014}; \protect\hyperlink{ref-fortuna2010}{Fortuna et al., 2010}; \protect\hyperlink{ref-olesen2007}{Olesen et al., 2007}) or in online archives (e.g., Mangal \protect\hyperlink{ref-poisot2016}{Poisot et al., 2016}; The Web of Life \protect\hyperlink{ref-fortuna2010}{Fortuna et al., 2010}).
-In total, our network dataset constituted 60 weighted (number of visits) and four unweighted (interaction presence-absence) networks, each sampled at a unique location and year, as well as eight meta-networks where interactions were pooled across several locations and multiple years.
+In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (interaction presence-absence) networks, each sampled at a unique location and year, as well as 8 meta-networks where interactions were pooled across several locations and multiple years.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-abdi2010}{}}%
-Abdi, H., \& Williams, L. J. (2010). Principal component analysis. \emph{WIREs Comp. Stats.}, \emph{2}(4), 433--459. \url{https://doi.org/10.1002/wics.101}
+Abdi, H., \& Williams, L. J. (2010). Principal component analysis. \emph{WIREs Computational Statistics}, \emph{2}(4), 433--459. \url{https://doi.org/10.1002/wics.101}
 
@@
 Intraspecific variation in species interactions promotes the feasibility of mutualistic assemblages.
-\emph{Ecology Letters}.
+\emph{Ecology Letters}, \emph{26}(3), 448--459.
 \url{https://doi.org/10.1111/ele.14163}
@@
 Constructing more informative plant\textendash pollinator networks: Visitation and pollen deposition networks in a heathland plant community.
-\emph{Proc.
-Royal Soc.
-B}, \emph{282}(1814), 20151130.
+\emph{Proceedings of the Royal Society B: Biological Sciences}, \emph{282}(1814), 20151130.
 \url{https://doi.org/10.1098/rspb.2015.1130}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-barrett2002}{}}%
-Barrett, S. C. H. (2002). The evolution of plant sexual diversity. \emph{Nat. Rev. Genet.}, \emph{3}(4), 274--284. \url{https://doi.org/10.1038/nrg776}
+Barrett, S. C. H. (2002). The evolution of plant sexual diversity. \emph{Nature Reviews Genetics}, \emph{3}(4), 274--284. \url{https://doi.org/10.1038/nrg776}
 
@@
 Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond.
-\emph{Philos.
-Trans.
-R.
-Soc.
-Lond.
-B Biol.
-Sci.}, \emph{358}(1434), 991--1004.
+\emph{Philosophical Transactions of the Royal Society B}, \emph{358}(1434), 991--1004.
 \url{https://doi.org/10.1098/rstb.2003.1301}
@@
 A common framework for identifying linkage rules across different types of interactions.
-\emph{Funct.
-Ecol.}, \emph{30}(12), 1894--1903.
+\emph{Functional Ecology}, \emph{30}(12), 1894--1903.
 \url{https://doi.org/10.1111/1365-2435.12666}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bluthgen2006}{}}%
-Blüthgen, N., Menzel, F., \& Blüthgen, N. (2006). Measuring specialization in species interaction networks. \emph{BMC Ecol.}, \emph{6}(1), 9. \url{https://doi.org/10.1186/1472-6785-6-9}
+Blüthgen, N., Menzel, F., \& Blüthgen, N. (2006). Measuring specialization in species interaction networks. \emph{BMC Ecology}, \emph{6}(1), 9. \url{https://doi.org/10.1186/1472-6785-6-9}
 
@@
 Global trait--environment relationships of plant communities.
-\emph{Nat.
-Ecol.
-Evol.}, \emph{2}(12), 1906--1917.
+\emph{Nature Ecology \& Evolution}, \emph{2}(12), 1906--1917.
 \url{https://doi.org/10.1038/s41559-018-0699-8}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
-Bürkner, P.-C. (2017). Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{J. Stat. Softw.}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
+Bürkner, P.-C. (2017). Brms: {An R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
 
@@
 Erosion of global functional diversity across the tree of life.
-\emph{Sci.
-Adv.}, \emph{7}(13), eabf2675.
+\emph{Science Advances}, \emph{7}(13), eabf2675.
 \url{https://doi.org/10.1126/sciadv.abf2675}
@@
 The potential for indirect effects between co-flowering plants via shared pollinators depends on resource abundance, accessibility and relatedness.
-\emph{Ecol.
-Lett.}, \emph{17}(11), 1389--1399.
+\emph{Ecology Letters}, \emph{17}(11), 1389--1399.
 \url{https://doi.org/10.1111/ele.12342}
@@
 Towards a worldwide wood economics spectrum.
-\emph{Ecol.
-Lett.}, \emph{12}(4), 351--366.
+\emph{Ecology Letters}, \emph{12}(4), 351--366.
 \url{https://doi.org/10.1111/j.1461-0248.2009.01285.x}
@@
 Linking species functional roles to their network roles.
-\emph{Ecol.
-Lett.}, \emph{19}(7), 762--770.
+\emph{Ecology Letters}, \emph{19}(7), 762--770.
 \url{https://doi.org/10.1111/ele.12612}
@@
 Morphology predicts species' functional roles and their degree of specialization in plant--frugivore interactions.
-\emph{Proc.
-Royal Soc.
-B}, \emph{283}(1823), 20152444.
+\emph{Proceedings of the Royal Society B: Biological Sciences}, \emph{283}(1823), 20152444.
 \url{https://doi.org/10.1098/rspb.2015.2444}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-dellinger2020}{}}%
-Dellinger, A. S. (2020). Pollination syndromes in the 21st century: Where do we stand and where may we go? \emph{New Phytol.}, \emph{228}(4), 1193--1213. \url{https://doi.org/10.1111/nph.16793}
+Dellinger, A. S. (2020). Pollination syndromes in the 21st century: Where do we stand and where may we go? \emph{New Phytologist}, \emph{228}(4), 1193--1213. \url{https://doi.org/10.1111/nph.16793}
 
@@
 Constraints imposed by pollinator behaviour on the ecology and evolution of plant mating systems.
-\emph{J.
-Evol.
-Biol.}, \emph{27}(7), 1413--1430.
+\emph{Journal of Evolutionary Biology}, \emph{27}(7), 1413--1430.
 \url{https://doi.org/10.1111/jeb.12380}
@@
 The dimensionality of ecological networks.
-\emph{Ecol.
-Lett.}, \emph{16}(5), 577--583.
+\emph{Ecology Letters}, \emph{16}(5), 577--583.
 \url{https://doi.org/10.1111/ele.12081}
@@
 Phenology drives mutualistic network structure and diversity.
-\emph{Ecol.
-Lett.}, \emph{15}(3), 198--208.
+\emph{Ecology Letters}, \emph{15}(3), 198--208.
 \url{https://doi.org/10.1111/j.1461-0248.2011.01726.x}
@@
 The neglected importance of floral traits in trait-based plant community assembly.
-\emph{J.
-Veg.
-Sci.}, \emph{31}(4), 529--539.
+\emph{Journal of Vegetation Science}, \emph{31}(4), 529--539.
 \url{https://doi.org/10.1111/jvs.12877}
@@
 Floral and reproductive traits are an independent dimension within the plant economic spectrum of temperate central europe.
-\emph{New Phytologist}.
+\emph{New Phytologist}, \emph{236}(5), 1964--1975.
 \url{https://doi.org/10.1111/nph.18386}
@@
 Pollination {Syndromes} and {Floral Specialization}.
-\emph{Annu.
-Rev.
-Ecol.
-Evol.
-Syst.}, \emph{35}(1), 375--403.
+\emph{Annual Review of Ecology, Evolution, and Systematics}, \emph{35}(1), 375--403.
 \url{https://doi.org/10.1146/annurev.ecolsys.34.011802.132347}
@@
 Nestedness versus modularity in ecological networks: Two sides of the same coin?
-\emph{J.
-Anim.
-Ecol.}, \emph{79}(4), 811--817.
+\emph{Journal of Animal Ecology}, \emph{79}(4), 811--817.
 \url{https://doi.org/10.1111/j.1365-2656.2010.01688.x}
@@
 The evolution of annual and perennial plant life histories: Ecological correlates and genetic mechanisms.
-\emph{Annu.
-Rev.
-Ecol.
-Evol.
-Syst.}, \emph{51}, 461--481.
+\emph{Annual Review of Ecology, Evolution, and Systematics}, \emph{51}, 461--481.
 \url{https://doi.org/10.1146/annurev-ecolsys-110218-024638}
@@
 Visualization in {Bayesian} workflow.
-\emph{J.
-R.
-Stat.
-Soc.
-Ser.
-A Stat.
-Soc.}, \emph{182}(2), 389--402.
+\emph{Journal of the Royal Statistical Society}, \emph{182}(2), 389--402.
 \url{https://doi.org/10.1111/rssa.12378}
@@
 Correlated evolution of mating system and floral display traits in flowering plants and its implications for the distribution of mating system variation.
-\emph{New Phytol.}, \emph{185}(1), 311--321.
+\emph{New Phytologist}, \emph{185}(1), 311--321.
 \url{https://doi.org/10.1111/j.1469-8137.2009.03043.x}
@@
 Animal life history is shaped by the pace of life and the distribution of age-specific mortality and reproduction.
-\emph{Nat.
-Ecol.
-Evol.}, \emph{3}(8), 1217--1224.
+\emph{Nature Ecology and Evolution}, \emph{3}(8), 1217--1224.
 \url{https://doi.org/10.1038/s41559-019-0938-7}
@@
 The worldwide importance of honey bees as pollinators in natural habitats.
-\emph{Proc.
-Royal Soc.
-B}, \emph{285}(1870), 20172140.
+\emph{Proceedings of the Royal Society B: Biological Sciences}, \emph{285}(1870), 20172140.
 \url{https://doi.org/10.1098/rspb.2017.2140}
@@
 Specialization on traits as basis for the niche-breadth of flower visitors and as structuring mechanism of ecological networks.
-\emph{Funct.
-Ecol.}, \emph{27}(2), 329--341.
+\emph{Functional Ecology}, \emph{27}(2), 329--341.
 \url{https://doi.org/10.1111/1365-2435.12005}
@@
 {TRY} \textendash{} a global database of plant traits.
-\emph{Glob.
-Chang.
-Biol.}, \emph{17}(9), 2905--2935.
+\emph{Global Change Biology}, \emph{17}(9), 2905--2935.
 \url{https://doi.org/10.1111/j.1365-2486.2011.02451.x}
@@
 \emph{Evolution}, \emph{71}(8), 1970--1985.
+\url{https://doi.org/10.1111/evo.13297}
 
@@
 Root traits explain plant species distributions along climatic gradients yet challenge the nature of ecological trade-offs.
-\emph{Nat.
-Ecol.
-Evol.}, 1--12.
+\emph{Nature Ecology and Evolution}, \emph{5}, 1123--1134.
 \url{https://doi.org/10.1038/s41559-021-01471-7}
@@
 Global biogeography of mating system variation in seed plants.
-\emph{Ecol.
-Lett.}, \emph{20}(3), 375--384.
+\emph{Ecology Letters}, \emph{20}(3), 375--384.
 \url{https://doi.org/10.1111/ele.12738}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-olesen2007}{}}%
-Olesen, J. M., Bascompte, J., Dupont, Y. L., \& Jordano, P. (2007). The modularity of pollination networks. \emph{PNAS}, \emph{104}(50), 19891--19896. \url{https://doi.org/10.1073/pnas.0706375104}
+Olesen, J.
+M., Bascompte, J., Dupont, Y.
+L., \& Jordano, P.
+(2007).
+The modularity of pollination networks.
+\emph{Proceedings of the National Academy of Sciences}, \emph{104}(50), 19891--19896.
+\url{https://doi.org/10.1073/pnas.0706375104}
 
@@
 The maleness of larger angiosperm flowers.
-\emph{Proc.
-Natl.
-Acad.
-Sci.}, \emph{117}(20), 10921--10926.
+\emph{Proceedings of the National Academy of Sciences}, \emph{117}(20), 10921--10926.
 \url{https://doi.org/10.1073/pnas.1910631117}
@@
 Imputation of missing data in life-history trait datasets: Which approach performs the best?
-\emph{Methods Ecol.
-Evol.}, \emph{5}(9), 961--970.
+\emph{Methods in Ecology and Evolution}, \emph{5}(9), 961--970.
 \url{https://doi.org/10.1111/2041-210X.12232}
@@
 Some evolutionary consequences of being a tree.
-\emph{Annu.
-Rev.
-Ecol.
-Evol.
-Syst.}, \emph{37}, 187--214.
+\emph{Annual Review of Ecology, Evolution, and Systematics}, \emph{37}, 187--214.
 \url{https://doi.org/10.1146/annurev.ecolsys.37.091305.110215}
@@
 Phytools: An {R} package for phylogenetic comparative biology (and other things).
-\emph{Methods Ecol.
-Evol.}, \emph{3}(2), 217--223.
+\emph{Methods in Ecology and Evolution}, \emph{3}(2), 217--223.
 \url{https://doi.org/10.1111/j.2041-210X.2011.00169.x}
@@
 Towards the flower economics spectrum.
-\emph{New Phytol.}, \emph{229}(2), 665--672.
+\emph{New Phytologist}, \emph{229}(2), 665--672.
 \url{https://doi.org/10.1111/nph.16823}
@@
 A quantitative review of pollination syndromes: Do floral traits predict effective pollinators?
-\emph{Ecol.
-Lett.}, \emph{17}(3), 388--400.
+\emph{Ecology Letters}, \emph{17}(3), 388--400.
 \url{https://doi.org/10.1111/ele.12224}
@@
 Beyond the fast\textendash slow continuum: Demographic dimensions structuring a tropical tree community.
-\emph{Ecol.
-Lett.}, \emph{21}(7), 1075--1084.
+\emph{Ecology Letters}, \emph{21}(7), 1075--1084.
 \url{https://doi.org/10.1111/ele.12974}
@@
 The compadre {Plant Matrix Database}: An open online repository for plant demography.
-\emph{J.
-Ecol.}, \emph{103}(1), 202--218.
+\emph{Journal of Ecology}, \emph{103}(1), 202--218.
 \url{https://doi.org/10.1111/1365-2745.12334}
@@
 Fast-slow continuum and reproductive strategies structure plant life-history variation worldwide.
-\emph{Proc.
-Natl.
-Acad.
-Sci.
-U.S.A.}, \emph{113}(1), 230--235.
+\emph{Proceedings of the National Academy of Sciences}, \emph{113}(1), 230--235.
 \url{https://doi.org/10.1073/pnas.1506215112}
@@
 Floral symmetry affects speciation rates in angiosperms.
-\emph{Proceedings of the Royal Society of London.
-Series B: Biological Sciences}, \emph{271}(1539), 603--608.
+\emph{Proceedings of the Royal Society B: Biological Sciences}, \emph{271}(1539), 603--608.
 \url{https://doi.org/10.1098/rspb.2003.2644}
@@
 Plant--pollinator interactions and the assembly of plant communities.
-\emph{Trends Ecol.
-Evol.}, \emph{23}(3), 123--130.
+\emph{Trends in Ecology \& Evolution}, \emph{23}(3), 123--130.
 \url{https://doi.org/10.1016/j.tree.2007.11.003}
@@
 Phylogenetic evidence for a flower size and number trade-off.
-\emph{Am.
-J.
-Bot.}, \emph{94}(12), 2059--2062.
+\emph{American Journal of Botany}, \emph{94}(12), 2059--2062.
 \url{https://doi.org/10.3732/ajb.94.12.2059}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-schiestl2013}{}}%
-Schiestl, F. P., \& Johnson, S. D. (2013). Pollinator-mediated evolution of floral signals. \emph{Trends Ecol. Evol.}, \emph{28}(5), 307--315. \url{https://doi.org/10.1016/j.tree.2013.01.019}
+Schiestl, F.
+P., \& Johnson, S.
+D.
+(2013).
+Pollinator-mediated evolution of floral signals.
+\emph{Trends in Ecology \& Evolution}, \emph{28}(5), 307--315.
+\url{https://doi.org/10.1016/j.tree.2013.01.019}
 
@@
 Principal component analysis for data containing outliers and missing elements.
-\emph{Comput.
-Stat.
-Data Anal.}, \emph{52}(3), 1712--1727.
+\emph{Computational Statistics \& Data Analysis}, \emph{52}(3), 1712--1727.
 \url{https://doi.org/10.1016/j.csda.2007.05.024}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-smith2018}{}}%
-Smith, S. A., \& Brown, J. W. (2018). Constructing a broadly inclusive seed plant phylogeny. \emph{Am. J. Bot.}, \emph{105}(3), 302--314. \url{https://doi.org/10.1002/ajb2.1019}
+Smith, S. A., \& Brown, J. W. (2018). Constructing a broadly inclusive seed plant phylogeny. \emph{American Journal of Botany}, \emph{105}(3), 302--314. \url{https://doi.org/10.1002/ajb2.1019}
 
@@
 Global analysis of floral longevity reveals latitudinal gradients and biotic and abiotic correlates.
-\emph{New Phytologist}.
+\emph{New Phytologist}, \emph{235}(5), 2054--2065.
 \url{https://doi.org/10.1111/nph.18271}
@@
 Size-specific interaction patterns and size matching in a plant\textendash pollinator interaction web.
-\emph{Ann.
-Bot.}, \emph{103}(9), 1459--1469.
+\emph{Annals of Botany}, \emph{103}(9), 1459--1469.
 \url{https://doi.org/10.1093/aob/mcp027}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-stearns1989}{}}%
-Stearns, S. C. (1989). Trade-offs in life-history evolution. \emph{Funct. Ecol.}, \emph{3}(3), 259--268. \url{https://doi.org/10.2307/2389364}
+Stearns, S. C. (1989). Trade-offs in life-history evolution. \emph{Functional Ecology}, \emph{3}(3), 259--268. \url{https://doi.org/10.2307/2389364}
 
@@
 Interaction frequency as a surrogate for the total effect of animal mutualists on plants.
-\emph{Ecol.
-Lett.}, \emph{8}(10), 1088--1094.
+\emph{Ecology Letters}, \emph{8}(10), 1088--1094.
 \url{https://doi.org/10.1111/j.1461-0248.2005.00810.x}
@@
 Floral display in narcissus: Variation in flower size and number at the species, population, and individual levels.
-\emph{Int.
-J.
-Plant Sci.}, \emph{161}(1), 69--79.
+\emph{International Journal of Plant Sciences}, \emph{161}(1), 69--79.
 \url{https://doi.org/10.1086/314225}

### 2023-02-27 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
Minor style edit on supplementary material

@@
 For the field of microlitres of nectar, we considered single measurements of nectar standing crop.
-Despite the timing and methodology of the different quantitative measurements of nectar differed across studies, these fields allowed us to have an approximate idea of the reproductive investment of the different plant species.
+Despite the timing and methodology of the different quantitative measurements of nectar differed across studies, these fields allowed us to have an approximate idea of the reproductive investment of the different plant species to attract pollinators.
 

### 2023-02-28 Manuscript/Lanuza_et_al_2022.Rmd
Changing one word to british style

@@
 Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping plant-pollinator interactions at a macro-ecological scale.
-These findings emphasize the importance of considering reproductive traits in the global spectrum of plant form and function, and the need to explore beyond floral morphological traits to broaden our understanding of plant-pollinator interactions.
+These findings emphasise the importance of considering reproductive traits in the global spectrum of plant form and function, and the need to explore beyond floral morphological traits to broaden our understanding of plant-pollinator interactions.
 

### 2023-02-28 Manuscript/Lanuza_et_al_2022.tex
Changing one word to british style

@@
   Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping plant-pollinator interactions at a macro-ecological scale.
-These findings emphasize the importance of considering reproductive traits in the global spectrum of plant form and function, and the need to explore beyond floral morphological traits to broaden our understanding of plant-pollinator interactions.
+These findings emphasise the importance of considering reproductive traits in the global spectrum of plant form and function, and the need to explore beyond floral morphological traits to broaden our understanding of plant-pollinator interactions.
 \end{enumerate}

### 2023-03-02 Manuscript/Lanuza_et_al_2022.Rmd
fixing typo

@@
 We found similar trends for visitation rates on the flower number - flower size axis,  but bees and syrphids visited plant species with many small flowers more frequently (figure 3d).
-On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and recieved many visits from all pollinator guilds (figure 3b and figure 3e).
+On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and received many visits from all pollinator guilds (figure 3b and figure 3e).
 Finally, on the style length - autonomous selfing axis, plant species with short styles and low autonomous selfing had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and high autonomous selfing (figure 3c).

### 2023-03-02 Manuscript/Lanuza_et_al_2022.tex
fixing typo

@@
 We found similar trends for visitation rates on the flower number - flower size axis, but bees and syrphids visited plant species with many small flowers more frequently (figure 3d).
-On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and recieved many visits from all pollinator guilds (figure 3b and figure 3e).
+On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and received many visits from all pollinator guilds (figure 3b and figure 3e).
 Finally, on the style length - autonomous selfing axis, plant species with short styles and low autonomous selfing had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and high autonomous selfing (figure 3c).

### 2023-04-13 Main_Figures/Figure_1.Rmd
edits for final sub

--- 2023-03-02 Manuscript/Lanuza_et_al_2022.Rmd
@@
 ---
-title: \singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shape their interactions with pollinators
-
-#author: 
-#  - Jose B. Lanuza^1,2^*
-#  - Romina Rader^1^
-#  - Jamie Stavert^3^
-#  - Liam K. Kendall^4^
-#  - Manu E. Saunders^1^
-#  - Ignasi Bartomeus^2^
-
-# may use lua filters for affiliations etc: see https://stackoverflow.com/a/52919256
-
-# date: '`r Sys.Date()`'
-
-output:
-  bookdown::pdf_document2:
-    fig_caption: yes
-    fig_width: 7
-    fig_height: 7
-    df_print: kable
-    keep_tex: yes
-    number_sections: no
-    extra_dependencies: ["float"]
-    toc: no
-    fig_crop: no
-    includes:
-      in_header: header.tex
-
-documentclass: article
-# classoption: twocolumn, landscape, etc
-papersize: a4
-pagestyle: plain  # plain, empty, headings
-geometry: margin=1in
-linestretch: 2
-fontfamily: mathpazo
+output: pdf_document
 fontsize: 12pt
-
-bibliography: 
-  - references.bib
-  - knitcitations.bib
-# zotero: "My shared Zotero group"
-csl: proceedingsb.csl #ecology letters
-notes-after-punctuation: false
-link-citations: yes
-linkcolor: RoyalBlue
-urlcolor: RoyalBlue
-links-as-notes: false
-subparagraph: yes
 
@@
 ---
-
-```{=tex}
-\doublespacing
-\normalsize
-```
-
-# Abstract
-
-1.
-Globally, plants display enormous variation in life history strategies and trait combinations.
-However, evidence suggests that evolutionary and physiological constraints limit the number of plant ecological strategies.
-Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with pollinators.
-
-2. Here, using a global dataset of 18 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
-
-3.
-We show that over 50% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the negative correlation between autonomous selfing and floral display size.
-In addition, these reproductive axes were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
-However, reproductive axes explain a relatively small amount of variance in pollinator interactions highlighting the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
-
-4.
-Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping plant-pollinator interactions at a macro-ecological scale.
-These findings emphasise the importance of considering reproductive traits in the global spectrum of plant form and function, and the need to explore beyond floral morphological traits to broaden our understanding of plant-pollinator interactions.
-
-\textbf{Keywords:} life-history strategies \| plant reproductive traits \| plant-pollinator interactions
-
-```{=tex}
-\doublespacing
-\vspace{5mm}
-\normalsize
-```
-```{r setup, include=FALSE, cache=FALSE, message = FALSE}
-
-library("knitr")
-
-### Chunk options: see http://yihui.name/knitr/options/ ###
-## Text results
-opts_chunk$set(echo = FALSE, warning = TRUE, message = TRUE)
-
-## Code decoration
-opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)
-
-## Cache
-# opts_chunk$set(cache = 2, cache.path = "output/cache/")
-
-## Plots
-opts_chunk$set(fig.path = "output/figures/")
-
-```
-
-```{r knitcitations, cache = FALSE}
-library(knitcitations)
-cleanbib()   
-cite_options(citation_format = "pandoc")
-
-```
-
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.pos = 'H')
-```
-
-# 1. Introduction
-
-Flowering plants display an astonishing diversity of reproductive structures [@barrett2002; @schiestl2013] that shape their interactions with animal pollinators [@fenster2004; @dellinger2020].
-The variety of reproductive strategies used by different plant species, from specialised reliance on a single pollinator, to full self-pollination, is incredibly rich.
-However, not all combinations of reproductive traits (i.e., morphological and physiological traits that determine a plant’s ability to reproduce) are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
-Despite recent advances in theoretical and empirical understanding of correlations between plant reproductive traits at large ecological scales [@salguero2016; @friedman2020; @paterno2020; @roddy2021; @song2022], studies typically focus on just a few traits, often in isolation.
-Thus, to develop a comprehensive understanding of the plant reproductive spectrum of trait variation, as done recently for root [@laughlin2021], leaf [@wright2004] and wood [@chave2009] related traits, we require a multi-trait perspective with broad geographical coverage.
-Importantly, characterization of the plant reproductive spectrum could reveal key reproductive strategies among different species [@agrawal2020] and improve knowledge of associations between specific reproductive traits and pollinators [@roddy2021].
-
-With the recent availability of large trait databases [e.g., TRY @kattge2011;  COMPADRE @salguero2015], there has been increased research on plant ecological strategies, which has produced identification of global patterns in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
-However, studies that look at multiple traits tend to overlook plant reproductive traits [@evojtko2020; @ruger2018; @roddy2021], and focus on trait correlations in other plant organs such as morphological and physiological leaf traits [@wright2004; @shipley2006; @donovan2011; @osnas2013].
-Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs such as the negative correlation between flower size and flower number [@sargent2007; @kettle2011; @vojtko2022]; the positive association between flower size and outcrossing rate [@goodwillie2010]; or the positive correlation between outcrossing rate and lifespan [@barrett2003; @munoz2016; @moeller2017].
-Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships [@roddy2021], we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
-
-Trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] are powerful for exploring the underlying mechanisms driving plant-pollinator interactions.
-For example, plant traits can define species' network roles [e.g., specialists vs generalists @tur2013] and plant species that occupy reproductive trait space extremes are likely to be more specialised and display tighter trait-matching with pollinators [@junker2013; @coux2016].
-Indeed, the degree of morphological matching between plants and pollinators often determines whether or not interactions occur, and consequently influences  the broader network structure [@stang2009; @ibanez2012].
-However, it is still unclear how specific reproductive traits (e.g., mating or compatibility system) influence plant-pollinator associations [@sargent2008; @tur2013; @devaux2014].
-For example, species with high selfing rates may evolve to invest less in floral rewards resulting in a lower number of pollinator visits [@devaux2014].
-Indeed, both morphology and mating system can determine a species' functional role within pollination networks, and the combination of several traits increases power for predicting network structure [@eklof2013].
-Because the species position within the multidimensional trait space can result in different interaction patterns or adaptations to pollinators [see @dehling2016 for a purely morphological approach], the use of the reproductive trait space to explore plant-pollinator interactions could help to identify species functional roles and associations of traits with specific pollinators (i.e., pollination syndromes).
-
-Here, we explore the spectrum of reproductive traits in flowering plants, within a global set of plant-pollinator networks, to identify reproductive trait covariation and how this influences the network of interactions between plants and pollinators.
-First, we identify the major axes of reproductive trait variation and correlations among traits for plant species.
-Then, we investigate the associations between plant species’ positions in reproductive trait space and the strength of their interactions with different pollinator guilds within networks.
-Finally, we determine how the main axes of reproductive trait variation influence plant species' functional roles within pollination networks, using a range of complementary interaction network metrics.
-
-# 2. Methods
-
-## (a) Plant-pollinator network studies
-
-We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see table S1 and figure S1).
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different ecological communities.
-The pollinators documented by these studies are primarily insect pollinators (97.8% of the total visits recorded) and the plants are characterised by a clear dominance of smaller life forms (i.e., 61% of herbs, 28% of shrubs and 11% of trees).
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to benefit, to some degree, from animal pollination.
-Many of these networks are freely available either as published studies [e.g., @carvalheiro2014; @olesen2007; @fortuna2010] or in online archives [e.g., Mangal @poisot2016;  The Web of Life @fortuna2010].
-In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (interaction presence-absence) networks, each sampled at a unique location and year, as well as 8 meta-networks where interactions were pooled across several locations and multiple years.
-
-## (b) Taxonomy of plants and pollinators
-
-All species names, genera, families and orders were retrieved and standardised from the taxonomy data sources NCBI (<https://www.ncbi.nlm.nih.gov/taxonomy>) for plants and ITIS (<https://www.itis.gov/>) for pollinators, using the R package *taxize* [@chamberlain2020].
-We filled the 'not found' searches manually using <http://www.theplantlist.org/> and <http://www.mobot.org/> for plants and <http://www.catalogueoflife.org/> for pollinators.
-
-## (c) Plant traits
-
-We selected a total of 18 quantitative and categorical functional traits that included reproductive traits and traits related with plant form and size (see table 1).
-Reproductive traits consisted of those related to floral and reproductive biology: (i) floral traits included those related to the size of floral organs (e.g., style length), floral display size (e.g., flower number) and floral rewards (e.g., pollen quantity), while (ii) reproductive biology traits represented the plant reproductive system (i.e., the breeding, mating and compatibility system).
-The remaining traits were related to plant size and form (i.e., plant height, lifespan and life form), which are commonly used to characterise the fast-slow continuum of plant trait variation [@salguero2016].
-For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
-From a matrix comprising a total of 27,108 possible cells (considering all traits and plant species: 18 columns × 1,506 species), we were able to fill 22,796 cells (84.1% of the dataset, see figure S2 for missing value information for each trait).
-An extended description of each trait and how it was obtained can be found in Appendix S1.
-
-\singlespacing
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=1, fig.width=14}
-
-library(kableExtra)
-
-library(dplyr)
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("../Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant","Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg", "Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Floral_unit_width",
-         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
-         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg", "Pollen_per_flower")]
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-n_of_records <- subset(missing.values, isna=="FALSE")
-
-Trait <- c("Plant height", "Flower width", "Flower length", "Inflorescence width", "Style length", "Ovules per flower",
-           "Flowers per plant", "Microliters of nectar", "Milligrams of nectar", "Pollen grains per flower", "Autonomous selfing (fruit set)")
-
-Trait1 <- linebreak(c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Compatibility system", "Breeding system"),align = c("l"))
-
-#T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub #\n Tree", "Brush \n Campanulate \n Capitulum \n Open \n #Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-#           "Presence \n Absence", "Self-incomp. \n Part. #self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n #Dioecious"),align = c("l"))
-#
-T.cat <- linebreak(c("Short-lived and perennial", "Herb, shrub and tree", "Brush, campanulate, capitulum,\n open, papilionaceous and tube",  "Actinomorphic and zygomorphic",
-           "Presence and absence", "Self-incompatible, partially self-compabtile \n and self-compatible", "Hermaphrodite, monoecious and dioecious"), align = c("l"))
-
-Number_of_records_quantitative <- c(n_of_records$num.isna[n_of_records$key=="Plant_height_mean_m"], n_of_records$num.isna[n_of_records$key=="Corolla_diameter_mean"],
-  n_of_records$num.isna[n_of_records$key=="Corolla_length_mean"], n_of_records$num.isna[n_of_records$key=="Floral_unit_width"],
-  n_of_records$num.isna[n_of_records$key=="Style_length"], n_of_records$num.isna[n_of_records$key=="Ovule_number"],
-  n_of_records$num.isna[n_of_records$key=="Flowers_per_plant"], n_of_records$num.isna[n_of_records$key=="Nectar_ul"],
-  n_of_records$num.isna[n_of_records$key=="Nectar_mg"],  n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
-  n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level_fruit_set"])
-
-Number_of_records_categorical <- c(n_of_records$num.isna[n_of_records$key=="lifespan"], n_of_records$num.isna[n_of_records$key=="life_form"],
-                                   n_of_records$num.isna[n_of_records$key=="Flower_morphology"], n_of_records$num.isna[n_of_records$key=="Flower_symmetry"],
-                                   n_of_records$num.isna[n_of_records$key=="Nectar_presence_absence"], n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level"],
-                                   n_of_records$num.isna[n_of_records$key=="Compatibility_system"], n_of_records$num.isna[n_of_records$key=="Breeding_system"],
-                                   rep("",4))
-
-T.range <- c("0.01-30m", "0.50-205mm", "0.20-195mm", "0.80-300mm", "0-138mm", "1-25000", "1-1.8 x $10^5$", "0-160$\\mu$l", "0-6.1mg", "13-2 x $10^8$", "0-100$\\%$")
-
-dat_1 <- data.frame(Trait,T.range)
-dat_2 <- data.frame(Trait1, T.cat)
-
-colnames(dat_1) <- c("Quantitative traits", "Numerical range")
-colnames(dat_2) <- c("Categorical traits", "Categories")
-
-#kable(list(dat_1, dat_2), booktabs = T, linesep = #"\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1 | #Quantitative and categorical traits used in this study.}") %>%
-#  kable_styling(full_width = F,font_size = 10) %>%  #column_spec(1:4, 
-#              width = "3in", 
-#              latex_valign = "m")
-#
-#
-
-colnames(dat_1) <- c("Traits", "Numerical range/Categories")
-colnames(dat_2) <- c("Traits", "Numerical range/Categories")
-
-d <- rbind(dat_1,dat_2)
-
-kable(d, booktabs = T, linesep = "\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1.} Quantitative and categorical traits used in this study.") %>%
-  kable_styling(full_width = F,font_size = 12) %>% row_spec(0, bold=T) %>% pack_rows("Quantitative", 1, 11) %>%
-pack_rows("Categorical", 12, 18)
-
-```
-
-\doublespacing
-
-## (d) Phylogenetic Distance
-
-We calculated the phylogenetic distance between all plant species considered using the function *get_tree* from the package *rtrees* (<https://github.com/daijiang/rtrees>), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
-
-## (e) Data Imputation
-
-To avoid excluding species with missing trait data, we imputed missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors from principal component analysis of the phylogenetic distance (PCoA), which has been shown to improve the performance of *missForest* [@penone2014].
-To extract the eigenvectors, we used the function *PVRdecomp* from the package *PVR* [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-We conducted two different imputations, one for the full set of species (1,506 species: 5.79% of missing values), and excluding nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and results for the two datasets were consistent (Fig S3 and Fig S4).
-
-## (f) Plant strategies analysis
-
-We explored the association between the different quantitative plant traits using a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasise flower size on the spectrum of trait variation.
-Prior to the analyses, we excluded outliers and standardised the data.
-Specifically, due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis [@legendre2012].
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated their position in the trait space and the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
-Similarly, we also explored for each pollinator guild (see "Visitation patterns" subsection below) the position in the trait space of the plants that interacted with them.
-We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode “covariance” because values for each variables were on the same scale following transformation [@abdi2010].
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity data.
-For this, we included all quantitative traits included in the main pPCA, plus pollen grains and microlitres of nectar per flower.
-
-## (g) Phylogenetic signal
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package *phytools* [@revell2012] and used Pagel's $\lambda$ as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-## (h) Network analyses
-
-### (i) Visitation patterns
-
-We used Bayesian modelling (see details below) to investigate how the different guilds of pollinators interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
-Specifically, interactions between plants and pollinators in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
-Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species [@ballantyne2015], the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination [@vazquez2005; @vazquez2012].
-Therefore, despite the fact that we do not evaluate pollinator effectiveness we refer to the different floral visitors as pollinators.
-
-We divided pollinators into six main taxonomical guilds that differ in life form, behaviour and thus likely play different ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
-Note that we excluded non-insect pollinators from our analyses as they comprised only a 2.2% of the total visits recorded in our set of studies.
-Moreover, because bees had the greatest number of occurrences in networks  (2,256 records) and the highest frequency of visits, we further broke this group down into the main bee families (Andrenidae, Apidae, Colletidae, Halictidae, and Megachilidae).
-In addition, we found that *Apis mellifera* was the pollinator with the largest proportion of occurrences in networks (7.55% of the total).
-This is consistent with previous research showing that *A.
-mellifera* was the most frequent pollinator in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
-Hence, to control for the effect of *A.
-mellifera* on observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding *A.
-mellifera*.
-We found that *A.
-mellifera*, was partly driving some of the observed trends on PC1 (figure S5).
-However, we did not detect major differences on PC2 and PC3.
-
-We used Bayesian generalised linear mixed models in the R package *brms* [@burkner2017] to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation (i.e., PC) and their interactions with pollinator guilds (i.e., PGs; e.g., number of visits \~ PC1 x PGs + PC2 x PGs + PC3 x PGs).
-Because we were interested in possible differences in visitation patterns among pollinator guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different pollinator guilds in the model.
-We added a nested random effect of networks within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence among them.
-We specified for the presence or absence of an interaction and number of visits with Bernoulli and a zero inflated negative binomial distributions, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results [@burkner2017].
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualised the posterior predictive checks with the function *pp_check* using the *bayesplot* package [@gabry2019].
-
-### (ii) Plant species network roles
-
-We also used Bayesian modelling to investigate how the main axes of trait variation determined different plant species' functional roles within pollination networks.
-For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies [@dormann2008], with clear ecological interpretations and are relevant for defining species' functional roles in networks.
-Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalised degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) selectivity (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalisation) and 1 (maximum specialisation).
-Normalised degree and selectivity were calculated with the *specieslevel* function in the R package *bipartite* [@dormann2008].
-We modelled each plant species metric (sum of visits, normalised degree and plant selectivity) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
-For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalised degree, and zero-one inflated beta for selectivity).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the 'visitation patterns' section.
-
-Our analyses were conducted on the subset of 60 weighted networks (out of a total of 64 networks) sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our network dataset (excluding meta- and non-weighted networks) included 2,256 interactions for bees, 1,768 for non-syrphid-dipterans, 845 for syrphids, 437 for lepidopterans, 432 for coleopterans, and 362 for non-bee-hymenopterans.
-Sampling methods varied across studies but this was accounted for in analyses by including study identity as a  random effect in our models.
-All analyses were conducted in R version *4.0.3*.
-
-# 3. Results
-
-## (a) Plant strategies analysis
-
-Our phylogenetically informed principal component analysis captured  51.8% and 70.97% of the reproductive trait variation in the first two and three axes, respectively (figure 1 and figure S6).
-The first principal component (PC1; the flower number - flower size axis) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; table S3) but style length also contributed moderately (loading = -0.33).
-One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-For instance, *Cornus florida* occurred at this end of the spectrum, which, on average, has approximately 10,000 flowers, is 7.5 m high, has flowers that are 3 mm wide, styles 3.5 mm long and  two ovules per flower.
-The other end of this spectrum had species that were short in height, with few large flowers that had long styles and many ovules.
-For example, *Petunia axillaris* on average, is 0.5 m high and has approximately 10 flowers per plant that are over 50 mm wide with 25 mm long styles and over 200 ovules.
-The second principal component (PC2; the autonomous selfing - floral display axis) encompassed 25.05% of the trait variation and represented variation from low to high autonomous selfing (i.e., high to low pollinator dependence).
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but all other traits (except ovule number) made moderate contributions (loadings ranging between 0.27 to 0.4; table S3).
-Generally speaking, species with low autonomous selfing had larger and many flowers with long styles, and were tall.
-*Zuccagnia punctata* occurred at this extreme of the spectrum, which is a self-incompatible species, completely dependent on animal pollination for seed production, producing  approximately 1,500 flowers per plant with an average height of 3 m and 20 mm long styles.
-In contrast, species with high autonomous selfing tended to have fewer and smaller flowers with shorter styles, and were shorter in height.
-*Veronica peregrina* occurred at this end of the spectrum, and is a self-compatible plant that requires little or no pollination by animals, it has approximately 20 flowers per plant, is 0.2 m high and has 0.25 mm long styles.
-The third principal component (PC3; the style length - autonomous selfing axis) explained a considerable amount of trait variability (19.17%) and represented a positive correlation between style length (loading = -0.66) and autonomous selfing (loading = \|-0.51\|), where species with short styles had low autonomous selfing and species with long styles high autonomous selfing.
-The remaining traits, apart from ovule number, were all positively correlated with style length and autonomous selfing (loadings from -0.23 to -0.46; table S3).
-In addition, the pPCA with the subset of species that we had nectar and pollen quantity data for showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with floral display size.
-Floral rewards were particularly strongly correlated with flower size but weakly correlated with flower number (figure S4).
-The first two principal components for this pPCA explained similar variance  (45.52%) and similar associations of traits, despite some variability in the loadings (table S4).
 
@@
 ```
-
-As expected, due to individual trait correlations between qualitative and quantitative traits (e.g., life form and plant height), we found that most categorical traits were clustered on the trait space and statistically associated with the first two axes of trait variation (figure s2 and table s2).
-However, the position of plants connected to each of the pollinator guilds was scattered without clear aggregation patterns on the trait space (figure s7; but see "Visitation patterns" section below for detailed results from quantitative analyses).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed a lack of statistical association.
-In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S8).
-Regarding self-compatibility, we found larger differences on PC2.
-For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S8a and figure S8b; Tukey test *P* \< 0.05).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S8c and figure S8d; Tukey test *P* \< 0.05).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S8e and figure S8f; Tukey test *P* \< 0.05).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S8g and figure S8h; Tukey test *P* \< 0.05).
-Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S8i and figure S8j; Tukey test *P* \< 0.05).
-Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S8k and figure S8l; Tukey test *P* \< 0.05).
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="80%",fig.align='center',fig.cap= "\\textbf{Figure 2.} Location of the different qualitative traits in the trait space.
-The figure panel is composed of the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
-The solid arrows indicate the direction of variation of the different quantitative traits shown in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S)."}
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(ggstar)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.6)),
-            axis.text=element_text(size = rel(1.6), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(size = rel(1.1)),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.4, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank(),
-            plot.title = element_text(size = rel(2.5), face="bold")
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("../Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
-phyl_pca_forest <- readRDS("../Data/RData/phyl_pca_forest.rds")
-
-#CALL the output PC for simplicity
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-Compatibility <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Compatibility <- dat_cleaning_5$Compatibility_system
-  dat$Compatibility <- as.character(dat$Compatibility)
-  dat$Compatibility[dat$Compatibility=="dioecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="monoecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-  dat$Compatibility[dat$Compatibility=="self_compatible"] <- "Self compatible"
-  dat$Compatibility[dat$Compatibility=="self_incompatible"] <- "Self incompatible"
-  dat$Compatibility <- factor(dat$Compatibility, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=Compatibility, fill=Compatibility), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("deepskyblue2", "purple2","goldenrod","gray7")) +
-scale_starshape_manual(values = c(13, 15, 28, 5))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)  + ylab("Autonomous selfing - Floral display axis")
-
-  plot
-
-}
-
-#Compatibility(PC)
-
-#############################################################################################################################################################
-#Life form
-#############################################################################################################################################################
-#Load plots
-Life_form <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Life form` <- dat_cleaning_5$life_form
-  dat$`Life form` <- as.character(dat$`Life form`)
-  dat$`Life form`[dat$`Life form`=="herb"] <- "Herb"
-  dat$`Life form`[dat$`Life form`=="shrub"] <- "Shrub"
-  dat$`Life form`[dat$`Life form`=="tree"] <- "Tree"
-  dat$`Life form`[dat$`Life form`=="vine"] <- "Shrub"
-
-  dat$`Life form` <- factor( dat$`Life form`, levels = c("Herb", "Shrub", "Tree"))
-
-plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Life form`, fill=`Life form`), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("forestgreen", "darkorange2","black")) +
-scale_starshape_manual(values = c(13, 15, 28))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.090, 0.115)) + ggtitle("(b)") +
-    xlab(NULL) + ylab(NULL)
-
-  plot
-
-}
-
-#Life_form(PC)
-
-#############################################################################################################################################################
-#Life span
-#############################################################################################################################################################
-#Load plots
-Life_span <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-    dat$Lifespan <- dat_cleaning_5$lifespan
-    dat$Lifespan <- as.character(dat$Lifespan)
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=Lifespan, fill=Lifespan), size=2.25, color= NA, alpha = 0.9)+ scale_fill_manual(values=c("sienna4","forestgreen")) +
-scale_starshape_manual(values = c(13, 15))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.12, 0.1)) + ggtitle("(c)") +
-    xlab(NULL) + ylab(NULL)
-
-  plot
-
-}
-
-#Life_span(PC)
-
-#############################################################################################################################################################
-#Flower symmetry
-#############################################################################################################################################################
-#Load plots
-Flower_sym <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower symmetry` <- dat_cleaning_5$Flower_symmetry
-  dat$`Flower symmetry` <- as.character(dat$`Flower symmetry`)
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Flower symmetry`, fill=`Flower symmetry`), size=2.25, color= NA, alpha = 0.9) + scale_fill_manual(values=c("goldenrod","purple2")) +
-scale_starshape_manual(values = c(13, 15))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL) + xlab("Flower number - Flower size axis")
-
-  plot
-
-}
-
-#Flower_sym(PC)
-
-#############################################################################################################################################################
-#Flower shape
-#############################################################################################################################################################
-#Load plots
-Flower_sha <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower shape` <- dat_cleaning_5$Flower_morphology
-  dat$`Flower shape` <- as.character(dat$`Flower shape`)
-  dat$`Flower shape`[dat$`Flower shape`=="Funnelform"] <- "Campanulate"
-  dat$`Flower shape`[dat$`Flower shape`=="Spike"] <- "Brush"
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Flower shape`, fill=`Flower shape`), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("black","goldenrod", "deepskyblue2","forestgreen","purple2","darkorange2")) +
-scale_starshape_manual(values = c(13, 15, 28, 5, 9, 14))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL) + xlab("Flower number - Flower size axis")
-
-  plot
-
-}
-
-#Flower_sha(PC)
-
-#############################################################################################################################################################
-#Breeding system
-#############################################################################################################################################################
-#Load plots
-Breeding_syst <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Breeding system` <- dat_cleaning_5$Breeding_system
-  dat$`Breeding system` <- as.character(dat$`Breeding system`)
-  dat$`Breeding system` <- factor(dat$`Breeding system`, levels=c("Hermaphrodite","Monoecious" ,"Dioecious"))
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Breeding system`, fill=`Breeding system`), size=2.25, color= NA, alpha = 0.9) + scale_fill_manual(values=c("forestgreen","darkorange2", "black")) +
-scale_starshape_manual(values = c(13, 15, 28))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("(d)") +
-    xlab("Flower number - Flower size axis") +
-    ylab("Autonomous selfing - Floral display axis")
-
-  plot
-
-}
-
-#Breeding_syst(PC)
-
-#############################################################################################################################################################
-#Nectar
-#############################################################################################################################################################
-#Load plots
-#Nectar <- function(PC, x="PC1", y="PC2") {
-#  # PC being a prcomp object
-#  data <- data.frame(PC$S)
-#  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-#  dat <- data.frame(x = data[,x], y = data[,y])
-#  
-#  #######
-#  #DENSITY FUNCTION
-#  #######
-#  get_density <- function(x, y, ...) {
-#    dens <- MASS::kde2d(x, y, ...)
-#    ix <- findInterval(x, dens$x)
-#    iy <- findInterval(y, dens$y)
-#    ii <- cbind(ix, iy)
-#    return(dens$z[ii])
-#  }
-#  
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-#  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-#  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-#  plot <- plot + geom_point(data=dat, aes(-x, -y, #colour=Nectar),size=1.75)+scale_color_manual(values=c("black","grey"))
-#  
-#  ########
-#  #ADD ARROWS 
-#  ########
-#  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-#  mult <- min(
-#    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-#    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-#  )
-#  datapc <- transform(datapc,
-#                      v1 = .75 * mult * (get(x)),
-#                      v2 = .75 * mult * (get(y))
-#  )
-#  # add arrows
-#  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, #yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-#  
-#  #Add axis with perctentage
-#  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-#
-#  
-#  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, #arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-#  
-#  #ADD LABELS
-#  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-#  
-#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-#  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = #-(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-#                          label = PCAloadings$Variables, color="black",size=3)
-#  
-#  #CHANGE THEME
-#  #CHANGE THEME
-#  
-#  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)") 
-#  
-#  plot
-#  
-#}
-#
-# #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")
-
-  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),ncol=3,nrow=2,  align = "hv")
-
-```
-
-\elandscape
-
-## (b) Phylogenetic signal
-
-We found a strong phylogenetic signal (*P* \< 0.01) for most quantitative traits (table S5).
-The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73) and number of flowers per plant ($\lambda$ = 0.69).
-The traits that had a moderate phylogenetic signal included inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all the traits we measured ($\lambda$ = 0.14).
-
-## (c) Visitation patterns
-
-The main axes of trait variation (PC1, PC2 and PC3) partly explained the presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the total number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant differences across the different pollinator guilds for both the presence-absence of interactions and number of visits (figure 3).
-On the flower number - flower size axis, we found  that plants with many small flowers tended to have interaction partners that were Coleoptera, non-bee-Hymenoptera and Diptera (figure 3a), whereas plants with few large flowers mostly had interaction partners that were bees and Lepidoptera.
-We found similar trends for visitation rates on the flower number - flower size axis,  but bees and syrphids visited plant species with many small flowers more frequently (figure 3d).
-On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and received many visits from all pollinator guilds (figure 3b and figure 3e).
-Finally, on the style length - autonomous selfing axis, plant species with short styles and low autonomous selfing had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and high autonomous selfing (figure 3c).
-Plants with long styles and high autonomous selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera (figure 3f).
-
-The additional models for the most represented bee families, for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and the number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03), showed that the Apidae family was the main driver of the observed patterns.
-The contrast between interaction presence/absence  and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S9).
-
-```{=tex}
-\vspace{5mm}
-\blandscape
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different pollinator guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
-PC1 represents the flower number - flower size axis, PC2 represents the autonomous selfing - floral display axis and PC3 represents the style length - autonomous selfing axis.
-For visualization purposes due to large differences between number of visits from bees and the rest of the pollinator guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
-
-#LOAD LIBRARIES 
-#library(phytools)
-#library(ape) #for phylogenetic distance
-#library(dplyr) #data processing
-#library(rtrees) #for phylogenetic distancelibrary(MASS)
-#library(reshape2)
-library(viridis) #COLOUR GGPLOT
-#library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-#library(tidyverse)
-library(patchwork) #panel of plots
-#library(brms)
-#library(cmdstanr)
-
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2)),
-           axis.text=element_text(size = rel(1.8), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(2, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
-           plot.subtitle = element_text(face="bold",size=rel(2))
-     ))
-}
-
-p1 <- readRDS("../Main_Figures/figure_3_1.rds")
-p2 <- readRDS("../Main_Figures/figure_3_2.rds")
-p3 <- readRDS("../Main_Figures/figure_3_3.rds")
-pp1 <- readRDS("../Main_Figures/figure_3_4.rds")
-pp2 <- readRDS("../Main_Figures/figure_3_5.rds")
-pp3 <- readRDS("../Main_Figures/figure_3_6.rds")
-
-library(patchwork)
-
-combined <- pp1 + pp2 + pp3 + p1 + p2 + p3  & theme(legend.position = "bottom") &  guides(color = guide_legend(override.aes = list(size=6.5), keywidth=1.8,
-                 keyheight=0.1,
-                 default.unit="inch"))
-
-combined + plot_layout(guides = "collect",ncol = 3)
-```
-
-\elandscape
-
-## (d) Plant species network roles
-
-Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S10; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalised degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, selectivity \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and selectivity.
-On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S10a).
-However, selectivity (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S10g).
-On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S10c).
-Again, selectivity showed the opposite trend to the number of visits (figure S10i).
-
-# 4. Discussion
-
-We found strong covariation among traits within the flowering plant reproductive spectrum, which shapes interactions with pollinators at a global scale.
-Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50% and 70% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, autonomous selfing and floral display, and style length and autonomous selfing.
-Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits [@diaz2016; @carmona2021], our results align with the two largest and most recent studies of plant life strategies that included reproductive, form and size related traits [@salguero2016; @vojtko2022].
-The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
-However, the unexplained variability found highlights the need to account for other local factors, such as species relative abundances [@bartomeus2016], along with reproductive traits, to better explain plant-pollinator associations.
-
-Our study provides strong evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1,200 species).
-Specifically, by using a multitrait approach, we are able to link the reproductive spectrum of plant trait variation with the previously described “fast-slow continuum” in plant [@salguero2016] and animal [@healy2019] life-history strategies.
-This fast-slow continuum was illustrated by the associations between reproductive traits and plant height, life form and lifespan traits.
-For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred Angiosperm species and generally lacking a multitrait perspective.
-We found support for this trait association and show that other reproductive traits (e.g., style length or ovule number) covary along this flower number - flower size axis.
-Our study also complements previous work linking plant breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers also have woody life forms and many flowers.
-Moreover, we identify the previously documented positive association between outcrossing rate and floral display size [@goodwillie2010], where species with low autonomous selfing levels also allocate large resource quantities to attract pollinators.
-
-Although we did not include floral rewards in our main analysis due to insufficient data, we did find that plant species with large floral displays and, in particular, large flowers, tended to have higher pollen and nectar quantity.
-Thus, we demonstrate that globally, reproductive trait covariation in flowering plants likely imposes constraints on the broader spectrum of plant trait variation.
-
-Overall, the main plant reproductive axes were insufficient to fully capture plant-pollinator associations.
-However, these axes helped explain, to some extent, interaction patterns among and within pollinator guilds, indicating that they partly mediate these associations across large spatial scales.
-For example, we found that all pollinator guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings [@hegland2005; @lazaro2013; @kaiser2014] and predictions from evolutionary life-history theory [@stebbins1970].
-These predictions suggest that larger investment in floral display and rewards to attract pollinators occurs when dependence on pollinators is high.
-Although pollinators play a major role in shaping plant reproductive strategies, these different strategies are also constrained by the cost of reproductive organs and trait correlations [@galen1999].
-For instance, smaller flowers tend to receive fewer visits than larger flowers, but small flowers are inexpensive to produce (e.g., have few ovules).
-Therefore, low  per-flower visitation can be compensated by overall plant-level visitation through producing many small flowers that develop into numerous small fruits [@kettle2011].
-Our results also indicate that bees interact more with plants that have higher levels of autonomous selfing and large styles, which can help with a more efficient pollen transfer and prevent pollen competition [@ashman2013; @tong2016; @lanuza2021].
-Similarly, the specialised floral structures of zygomorphic flowers promote precise pollen transfer [@sargent2004; @gong2009], although we found that they were associated with high levels of autogamy.
-The annual herb _Lathyrus clymenum_ is a clear example of this pollinator specialization - selfing strategy that may get “the best of both worlds” [@lloyd1992; @goodwillie2018].
-It has showy zygomorphic flowers with relatively long styles and few ovules per flower that are likely fertilised with a single legitimate floral visit but can avoid reproductive failure in the absence of pollinators through autonomous self pollination.
-Our findings are consistent with the hypothesis that selfing is not rare within specialised pollination systems [@fenster2007] and emphasise the need to consider different reproductive assurance mechanisms [e.g., early versus delayed selfing\; @goodwillie2018] to better understand plant reproductive trait correlations and plant-pollinator interactions.
-
-Because flowering plants can adapt to their animal pollinators to optimise pollen transfer, the correlation between distinct suites of plant reproductive traits and pollinator guilds could indicate the existence of pollination syndromes [@fenster2004; @faegri2013; @rosas2014; @dellinger2020].
-However, our work shows a weak association between the different plant reproductive strategies and pollinator guilds, which supports previous findings from a similar pollinator guild classification and spatial scale [@ollerton2009].
-Although our findings contrast with a vast amount of literature on pollinator syndromes dating back over half a century [@faegri2013; @fenster2004], the ecological scale of our study differs from the majority of floral syndrome studies that rarely consider plant-pollinator associations beyond the community scale [ca.
-3% of studies\; @dellinger2020].
-We argue that the predictive power of floral syndromes gets blurred when increasing the number of species and scale, reinforcing the view that strong specialisation may be the exception rather than the norm in plant-pollinator interactions [@jordano1987; @waser1996].
-Further, there are several factors that might have influenced our findings, (e.g., the suite of reproductive traits and type of pollinator guilds we included).
-For instance, including other key reproductive traits, such as floral scent or flower colour, could help to improve predictions of plant-pollinator interactions.
-In addition, our use of broad taxonomic pollinator guild groupings may have obscured  finer scale patterns that occur at lower taxonomic ranks (e.g., genus or species level).
-The fact that our study only accounts for insect pollinators may have also influenced the observed associations between floral traits and pollinator guilds in comparison with other studies, as some other guilds (e.g., hummingbirds or bats) generally display strong trait-matching [@wilson2004; @lagomarsino2017].
-Regardless, it is worth noting that local factors (e.g., species relative abundances, phenologies or intraspecific variation) likely contribute to the variability in interactions between the plant reproductive spectrum and pollinators [@vazquez2007; @encinas2012; @bartomeus2016; @arroyo2023].
-We suggest that while plant reproductive traits do influence which pollinators they interact with, at a macroecological scale, pollination syndromes possibly take the form of a multifaceted, context dependent continuum [e.g., ornithophilous versus entomophilous pollination of red flowers\; @leon2022].
-
-Our study provides a comprehensive assessment of  reproductive trait covariation patterns in flowering plants, using a global dataset of traits for plant species within plant-pollinator networks.
-We show the importance of pollinators in mediating reproductive trait correlations and identify the need to consider broader plant reproductive strategies, rather than just flower morphology, to understand patterns of plant-pollinator interactions.
-Further, we provide empirical evidence of reproductive trait associations that complement trait covariation studies for other plant organs, highlighting the need to include reproductive traits in the global spectrum of plant form and function.
-Future work incorporating underrepresented areas of the world and additional relevant reproductive traits (e.g., flower life span and colour) from a broader range of life forms will be valuable for enhancing our understanding of the plant reproductive spectrum and associated plant-pollinator interactions.
-
-\newpage
-
-# References
-
-::: {#refs}
-:::

### 2023-04-13 Main_Figures/Figure_2.Rmd
edits for final sub

--- 2023-03-02 Manuscript/Lanuza_et_al_2022.Rmd
@@
 ---
-title: \singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shape their interactions with pollinators
-
-#author: 
-#  - Jose B. Lanuza^1,2^*
-#  - Romina Rader^1^
-#  - Jamie Stavert^3^
-#  - Liam K. Kendall^4^
-#  - Manu E. Saunders^1^
-#  - Ignasi Bartomeus^2^
-
-# may use lua filters for affiliations etc: see https://stackoverflow.com/a/52919256
-
-# date: '`r Sys.Date()`'
-
-output:
-  bookdown::pdf_document2:
-    fig_caption: yes
-    fig_width: 7
-    fig_height: 7
-    df_print: kable
-    keep_tex: yes
-    number_sections: no
-    extra_dependencies: ["float"]
-    toc: no
-    fig_crop: no
-    includes:
-      in_header: header.tex
-
-documentclass: article
-# classoption: twocolumn, landscape, etc
-papersize: a4
-pagestyle: plain  # plain, empty, headings
-geometry: margin=1in
-linestretch: 2
-fontfamily: mathpazo
+output: pdf_document
 fontsize: 12pt
-
-bibliography: 
-  - references.bib
-  - knitcitations.bib
-# zotero: "My shared Zotero group"
-csl: proceedingsb.csl #ecology letters
-notes-after-punctuation: false
-link-citations: yes
-linkcolor: RoyalBlue
-urlcolor: RoyalBlue
-links-as-notes: false
-subparagraph: yes
+classoption: landscape
 
@@
 
-```{=tex}
-\doublespacing
-\normalsize
-```
+\pagenumbering{gobble}
 
-# Abstract
-
-1.
-Globally, plants display enormous variation in life history strategies and trait combinations.
-However, evidence suggests that evolutionary and physiological constraints limit the number of plant ecological strategies.
-Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with pollinators.
-
-2. Here, using a global dataset of 18 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
-
-3.
-We show that over 50% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the negative correlation between autonomous selfing and floral display size.
-In addition, these reproductive axes were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
-However, reproductive axes explain a relatively small amount of variance in pollinator interactions highlighting the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
-
-4.
-Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping plant-pollinator interactions at a macro-ecological scale.
-These findings emphasise the importance of considering reproductive traits in the global spectrum of plant form and function, and the need to explore beyond floral morphological traits to broaden our understanding of plant-pollinator interactions.
-
-\textbf{Keywords:} life-history strategies \| plant reproductive traits \| plant-pollinator interactions
-
-```{=tex}
-\doublespacing
-\vspace{5mm}
-\normalsize
-```
-```{r setup, include=FALSE, cache=FALSE, message = FALSE}
-
-library("knitr")
-
-### Chunk options: see http://yihui.name/knitr/options/ ###
-## Text results
-opts_chunk$set(echo = FALSE, warning = TRUE, message = TRUE)
-
-## Code decoration
-opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)
-
-## Cache
-# opts_chunk$set(cache = 2, cache.path = "output/cache/")
-
-## Plots
-opts_chunk$set(fig.path = "output/figures/")
-
-```
-
-```{r knitcitations, cache = FALSE}
-library(knitcitations)
-cleanbib()   
-cite_options(citation_format = "pandoc")
-
-```
-
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.pos = 'H')
-```
-
-# 1. Introduction
-
-Flowering plants display an astonishing diversity of reproductive structures [@barrett2002; @schiestl2013] that shape their interactions with animal pollinators [@fenster2004; @dellinger2020].
-The variety of reproductive strategies used by different plant species, from specialised reliance on a single pollinator, to full self-pollination, is incredibly rich.
-However, not all combinations of reproductive traits (i.e., morphological and physiological traits that determine a plant’s ability to reproduce) are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
-Despite recent advances in theoretical and empirical understanding of correlations between plant reproductive traits at large ecological scales [@salguero2016; @friedman2020; @paterno2020; @roddy2021; @song2022], studies typically focus on just a few traits, often in isolation.
-Thus, to develop a comprehensive understanding of the plant reproductive spectrum of trait variation, as done recently for root [@laughlin2021], leaf [@wright2004] and wood [@chave2009] related traits, we require a multi-trait perspective with broad geographical coverage.
-Importantly, characterization of the plant reproductive spectrum could reveal key reproductive strategies among different species [@agrawal2020] and improve knowledge of associations between specific reproductive traits and pollinators [@roddy2021].
-
-With the recent availability of large trait databases [e.g., TRY @kattge2011;  COMPADRE @salguero2015], there has been increased research on plant ecological strategies, which has produced identification of global patterns in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
-However, studies that look at multiple traits tend to overlook plant reproductive traits [@evojtko2020; @ruger2018; @roddy2021], and focus on trait correlations in other plant organs such as morphological and physiological leaf traits [@wright2004; @shipley2006; @donovan2011; @osnas2013].
-Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs such as the negative correlation between flower size and flower number [@sargent2007; @kettle2011; @vojtko2022]; the positive association between flower size and outcrossing rate [@goodwillie2010]; or the positive correlation between outcrossing rate and lifespan [@barrett2003; @munoz2016; @moeller2017].
-Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships [@roddy2021], we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
-
-Trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] are powerful for exploring the underlying mechanisms driving plant-pollinator interactions.
-For example, plant traits can define species' network roles [e.g., specialists vs generalists @tur2013] and plant species that occupy reproductive trait space extremes are likely to be more specialised and display tighter trait-matching with pollinators [@junker2013; @coux2016].
-Indeed, the degree of morphological matching between plants and pollinators often determines whether or not interactions occur, and consequently influences  the broader network structure [@stang2009; @ibanez2012].
-However, it is still unclear how specific reproductive traits (e.g., mating or compatibility system) influence plant-pollinator associations [@sargent2008; @tur2013; @devaux2014].
-For example, species with high selfing rates may evolve to invest less in floral rewards resulting in a lower number of pollinator visits [@devaux2014].
-Indeed, both morphology and mating system can determine a species' functional role within pollination networks, and the combination of several traits increases power for predicting network structure [@eklof2013].
-Because the species position within the multidimensional trait space can result in different interaction patterns or adaptations to pollinators [see @dehling2016 for a purely morphological approach], the use of the reproductive trait space to explore plant-pollinator interactions could help to identify species functional roles and associations of traits with specific pollinators (i.e., pollination syndromes).
-
-Here, we explore the spectrum of reproductive traits in flowering plants, within a global set of plant-pollinator networks, to identify reproductive trait covariation and how this influences the network of interactions between plants and pollinators.
-First, we identify the major axes of reproductive trait variation and correlations among traits for plant species.
-Then, we investigate the associations between plant species’ positions in reproductive trait space and the strength of their interactions with different pollinator guilds within networks.
-Finally, we determine how the main axes of reproductive trait variation influence plant species' functional roles within pollination networks, using a range of complementary interaction network metrics.
-
-# 2. Methods
-
-## (a) Plant-pollinator network studies
-
-We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see table S1 and figure S1).
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different ecological communities.
-The pollinators documented by these studies are primarily insect pollinators (97.8% of the total visits recorded) and the plants are characterised by a clear dominance of smaller life forms (i.e., 61% of herbs, 28% of shrubs and 11% of trees).
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to benefit, to some degree, from animal pollination.
-Many of these networks are freely available either as published studies [e.g., @carvalheiro2014; @olesen2007; @fortuna2010] or in online archives [e.g., Mangal @poisot2016;  The Web of Life @fortuna2010].
-In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (interaction presence-absence) networks, each sampled at a unique location and year, as well as 8 meta-networks where interactions were pooled across several locations and multiple years.
-
-## (b) Taxonomy of plants and pollinators
-
-All species names, genera, families and orders were retrieved and standardised from the taxonomy data sources NCBI (<https://www.ncbi.nlm.nih.gov/taxonomy>) for plants and ITIS (<https://www.itis.gov/>) for pollinators, using the R package *taxize* [@chamberlain2020].
-We filled the 'not found' searches manually using <http://www.theplantlist.org/> and <http://www.mobot.org/> for plants and <http://www.catalogueoflife.org/> for pollinators.
-
-## (c) Plant traits
-
-We selected a total of 18 quantitative and categorical functional traits that included reproductive traits and traits related with plant form and size (see table 1).
-Reproductive traits consisted of those related to floral and reproductive biology: (i) floral traits included those related to the size of floral organs (e.g., style length), floral display size (e.g., flower number) and floral rewards (e.g., pollen quantity), while (ii) reproductive biology traits represented the plant reproductive system (i.e., the breeding, mating and compatibility system).
-The remaining traits were related to plant size and form (i.e., plant height, lifespan and life form), which are commonly used to characterise the fast-slow continuum of plant trait variation [@salguero2016].
-For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
-From a matrix comprising a total of 27,108 possible cells (considering all traits and plant species: 18 columns × 1,506 species), we were able to fill 22,796 cells (84.1% of the dataset, see figure S2 for missing value information for each trait).
-An extended description of each trait and how it was obtained can be found in Appendix S1.
-
-\singlespacing
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=1, fig.width=14}
-
-library(kableExtra)
-
-library(dplyr)
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("../Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant","Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg", "Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Floral_unit_width",
-         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
-         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg", "Pollen_per_flower")]
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-n_of_records <- subset(missing.values, isna=="FALSE")
-
-Trait <- c("Plant height", "Flower width", "Flower length", "Inflorescence width", "Style length", "Ovules per flower",
-           "Flowers per plant", "Microliters of nectar", "Milligrams of nectar", "Pollen grains per flower", "Autonomous selfing (fruit set)")
-
-Trait1 <- linebreak(c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Compatibility system", "Breeding system"),align = c("l"))
-
-#T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub #\n Tree", "Brush \n Campanulate \n Capitulum \n Open \n #Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-#           "Presence \n Absence", "Self-incomp. \n Part. #self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n #Dioecious"),align = c("l"))
-#
-T.cat <- linebreak(c("Short-lived and perennial", "Herb, shrub and tree", "Brush, campanulate, capitulum,\n open, papilionaceous and tube",  "Actinomorphic and zygomorphic",
-           "Presence and absence", "Self-incompatible, partially self-compabtile \n and self-compatible", "Hermaphrodite, monoecious and dioecious"), align = c("l"))
-
-Number_of_records_quantitative <- c(n_of_records$num.isna[n_of_records$key=="Plant_height_mean_m"], n_of_records$num.isna[n_of_records$key=="Corolla_diameter_mean"],
-  n_of_records$num.isna[n_of_records$key=="Corolla_length_mean"], n_of_records$num.isna[n_of_records$key=="Floral_unit_width"],
-  n_of_records$num.isna[n_of_records$key=="Style_length"], n_of_records$num.isna[n_of_records$key=="Ovule_number"],
-  n_of_records$num.isna[n_of_records$key=="Flowers_per_plant"], n_of_records$num.isna[n_of_records$key=="Nectar_ul"],
-  n_of_records$num.isna[n_of_records$key=="Nectar_mg"],  n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
-  n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level_fruit_set"])
-
-Number_of_records_categorical <- c(n_of_records$num.isna[n_of_records$key=="lifespan"], n_of_records$num.isna[n_of_records$key=="life_form"],
-                                   n_of_records$num.isna[n_of_records$key=="Flower_morphology"], n_of_records$num.isna[n_of_records$key=="Flower_symmetry"],
-                                   n_of_records$num.isna[n_of_records$key=="Nectar_presence_absence"], n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level"],
-                                   n_of_records$num.isna[n_of_records$key=="Compatibility_system"], n_of_records$num.isna[n_of_records$key=="Breeding_system"],
-                                   rep("",4))
-
-T.range <- c("0.01-30m", "0.50-205mm", "0.20-195mm", "0.80-300mm", "0-138mm", "1-25000", "1-1.8 x $10^5$", "0-160$\\mu$l", "0-6.1mg", "13-2 x $10^8$", "0-100$\\%$")
-
-dat_1 <- data.frame(Trait,T.range)
-dat_2 <- data.frame(Trait1, T.cat)
-
-colnames(dat_1) <- c("Quantitative traits", "Numerical range")
-colnames(dat_2) <- c("Categorical traits", "Categories")
-
-#kable(list(dat_1, dat_2), booktabs = T, linesep = #"\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1 | #Quantitative and categorical traits used in this study.}") %>%
-#  kable_styling(full_width = F,font_size = 10) %>%  #column_spec(1:4, 
-#              width = "3in", 
-#              latex_valign = "m")
-#
-#
-
-colnames(dat_1) <- c("Traits", "Numerical range/Categories")
-colnames(dat_2) <- c("Traits", "Numerical range/Categories")
-
-d <- rbind(dat_1,dat_2)
-
-kable(d, booktabs = T, linesep = "\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1.} Quantitative and categorical traits used in this study.") %>%
-  kable_styling(full_width = F,font_size = 12) %>% row_spec(0, bold=T) %>% pack_rows("Quantitative", 1, 11) %>%
-pack_rows("Categorical", 12, 18)
-
-```
-
-\doublespacing
-
-## (d) Phylogenetic Distance
-
-We calculated the phylogenetic distance between all plant species considered using the function *get_tree* from the package *rtrees* (<https://github.com/daijiang/rtrees>), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
-
-## (e) Data Imputation
-
-To avoid excluding species with missing trait data, we imputed missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors from principal component analysis of the phylogenetic distance (PCoA), which has been shown to improve the performance of *missForest* [@penone2014].
-To extract the eigenvectors, we used the function *PVRdecomp* from the package *PVR* [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-We conducted two different imputations, one for the full set of species (1,506 species: 5.79% of missing values), and excluding nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and results for the two datasets were consistent (Fig S3 and Fig S4).
-
-## (f) Plant strategies analysis
-
-We explored the association between the different quantitative plant traits using a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasise flower size on the spectrum of trait variation.
-Prior to the analyses, we excluded outliers and standardised the data.
-Specifically, due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis [@legendre2012].
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated their position in the trait space and the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
-Similarly, we also explored for each pollinator guild (see "Visitation patterns" subsection below) the position in the trait space of the plants that interacted with them.
-We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode “covariance” because values for each variables were on the same scale following transformation [@abdi2010].
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity data.
-For this, we included all quantitative traits included in the main pPCA, plus pollen grains and microlitres of nectar per flower.
-
-## (g) Phylogenetic signal
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package *phytools* [@revell2012] and used Pagel's $\lambda$ as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-## (h) Network analyses
-
-### (i) Visitation patterns
-
-We used Bayesian modelling (see details below) to investigate how the different guilds of pollinators interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
-Specifically, interactions between plants and pollinators in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
-Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species [@ballantyne2015], the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination [@vazquez2005; @vazquez2012].
-Therefore, despite the fact that we do not evaluate pollinator effectiveness we refer to the different floral visitors as pollinators.
-
-We divided pollinators into six main taxonomical guilds that differ in life form, behaviour and thus likely play different ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
-Note that we excluded non-insect pollinators from our analyses as they comprised only a 2.2% of the total visits recorded in our set of studies.
-Moreover, because bees had the greatest number of occurrences in networks  (2,256 records) and the highest frequency of visits, we further broke this group down into the main bee families (Andrenidae, Apidae, Colletidae, Halictidae, and Megachilidae).
-In addition, we found that *Apis mellifera* was the pollinator with the largest proportion of occurrences in networks (7.55% of the total).
-This is consistent with previous research showing that *A.
-mellifera* was the most frequent pollinator in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
-Hence, to control for the effect of *A.
-mellifera* on observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding *A.
-mellifera*.
-We found that *A.
-mellifera*, was partly driving some of the observed trends on PC1 (figure S5).
-However, we did not detect major differences on PC2 and PC3.
-
-We used Bayesian generalised linear mixed models in the R package *brms* [@burkner2017] to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation (i.e., PC) and their interactions with pollinator guilds (i.e., PGs; e.g., number of visits \~ PC1 x PGs + PC2 x PGs + PC3 x PGs).
-Because we were interested in possible differences in visitation patterns among pollinator guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different pollinator guilds in the model.
-We added a nested random effect of networks within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence among them.
-We specified for the presence or absence of an interaction and number of visits with Bernoulli and a zero inflated negative binomial distributions, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results [@burkner2017].
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualised the posterior predictive checks with the function *pp_check* using the *bayesplot* package [@gabry2019].
-
-### (ii) Plant species network roles
-
-We also used Bayesian modelling to investigate how the main axes of trait variation determined different plant species' functional roles within pollination networks.
-For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies [@dormann2008], with clear ecological interpretations and are relevant for defining species' functional roles in networks.
-Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalised degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) selectivity (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalisation) and 1 (maximum specialisation).
-Normalised degree and selectivity were calculated with the *specieslevel* function in the R package *bipartite* [@dormann2008].
-We modelled each plant species metric (sum of visits, normalised degree and plant selectivity) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
-For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalised degree, and zero-one inflated beta for selectivity).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the 'visitation patterns' section.
-
-Our analyses were conducted on the subset of 60 weighted networks (out of a total of 64 networks) sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our network dataset (excluding meta- and non-weighted networks) included 2,256 interactions for bees, 1,768 for non-syrphid-dipterans, 845 for syrphids, 437 for lepidopterans, 432 for coleopterans, and 362 for non-bee-hymenopterans.
-Sampling methods varied across studies but this was accounted for in analyses by including study identity as a  random effect in our models.
-All analyses were conducted in R version *4.0.3*.
-
-# 3. Results
-
-## (a) Plant strategies analysis
-
-Our phylogenetically informed principal component analysis captured  51.8% and 70.97% of the reproductive trait variation in the first two and three axes, respectively (figure 1 and figure S6).
-The first principal component (PC1; the flower number - flower size axis) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; table S3) but style length also contributed moderately (loading = -0.33).
-One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-For instance, *Cornus florida* occurred at this end of the spectrum, which, on average, has approximately 10,000 flowers, is 7.5 m high, has flowers that are 3 mm wide, styles 3.5 mm long and  two ovules per flower.
-The other end of this spectrum had species that were short in height, with few large flowers that had long styles and many ovules.
-For example, *Petunia axillaris* on average, is 0.5 m high and has approximately 10 flowers per plant that are over 50 mm wide with 25 mm long styles and over 200 ovules.
-The second principal component (PC2; the autonomous selfing - floral display axis) encompassed 25.05% of the trait variation and represented variation from low to high autonomous selfing (i.e., high to low pollinator dependence).
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but all other traits (except ovule number) made moderate contributions (loadings ranging between 0.27 to 0.4; table S3).
-Generally speaking, species with low autonomous selfing had larger and many flowers with long styles, and were tall.
-*Zuccagnia punctata* occurred at this extreme of the spectrum, which is a self-incompatible species, completely dependent on animal pollination for seed production, producing  approximately 1,500 flowers per plant with an average height of 3 m and 20 mm long styles.
-In contrast, species with high autonomous selfing tended to have fewer and smaller flowers with shorter styles, and were shorter in height.
-*Veronica peregrina* occurred at this end of the spectrum, and is a self-compatible plant that requires little or no pollination by animals, it has approximately 20 flowers per plant, is 0.2 m high and has 0.25 mm long styles.
-The third principal component (PC3; the style length - autonomous selfing axis) explained a considerable amount of trait variability (19.17%) and represented a positive correlation between style length (loading = -0.66) and autonomous selfing (loading = \|-0.51\|), where species with short styles had low autonomous selfing and species with long styles high autonomous selfing.
-The remaining traits, apart from ovule number, were all positively correlated with style length and autonomous selfing (loadings from -0.23 to -0.46; table S3).
-In addition, the pPCA with the subset of species that we had nectar and pollen quantity data for showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with floral display size.
-Floral rewards were particularly strongly correlated with flower size but weakly correlated with flower number (figure S4).
-The first two principal components for this pPCA explained similar variance  (45.52%) and similar associations of traits, despite some variability in the loadings (table S4).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="85%", fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
-The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
-The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation.
-The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}
-
-#Load libraries
-library(viridis) #COLOUR GGPLOT
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(magick)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("../Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("../Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#Images were made by Paula Martin
-#Check her work on https://paulamartinart.com/
-
-tree <- image_read("../Images/PPCA_Plot/Tree.png")
-tree_1 <- as.raster(tree)
-
-style_l <- image_read("../Images/PPCA_Plot/Style_Long.png")
-style_l_1 <- as.raster(style_l)
-
-style_s <- image_read("../Images/PPCA_Plot/Style_Short.png")
-style_s_1 <- as.raster(style_s)
-
-ovule_h <- image_read("../Images/PPCA_Plot/Ovule_High.png")
-ovule_h_1 <- as.raster(ovule_h)
-
-ovule_l <- image_read("../Images/PPCA_Plot/Ovule_Low.png")
-ovule_l_1 <- as.raster(ovule_l)
-
-selfing_n <- image_read("../Images/PPCA_Plot/Selfing_None.png")
-selfing_n_1 <- as.raster(selfing_n)
-
-selfing_h <- image_read("../Images/PPCA_Plot/selfing.png")
-selfing_h_1 <- as.raster(selfing_h)
-
-single_flower <- image_read("../Images/PPCA_Plot/Single_Flower.png")
-single_flower_1 <- as.raster(single_flower)
-
-many_flowers <- image_read("../Images/PPCA_Plot/Inflorescencia.png")
-many_flowers_1 <- as.raster(many_flowers)
-#many_flowers_1 <- image_rotate(many_flowers, 45)
-
-large_flower <- image_read("../Images/PPCA_Plot/flower_big.png")
-large_flower_1 <- as.raster(large_flower)
-
-#"Images/PPCA_Plot/flower_short.png"
-flower_small <- image_read("../Images/PPCA_Plot/flower_big.png")
-flower_small_1 <- as.raster(flower_small)
-
-herb <- image_read("../Images/PPCA_Plot/herb.png")
-herb_1 <- as.raster(herb)
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Autonomous selfing - Floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
-    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
-    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
-    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.18, xmax = 4.13,ymin = 1.3, ymax = 2.4) +
-    annotation_raster(flower_small_1, xmin = -3.21, xmax = -2.81,ymin = -2, ymax = -1.45) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
-
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
-                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-plot_grid(all_spp(PC))
-
-```
-
-As expected, due to individual trait correlations between qualitative and quantitative traits (e.g., life form and plant height), we found that most categorical traits were clustered on the trait space and statistically associated with the first two axes of trait variation (figure s2 and table s2).
-However, the position of plants connected to each of the pollinator guilds was scattered without clear aggregation patterns on the trait space (figure s7; but see "Visitation patterns" section below for detailed results from quantitative analyses).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed a lack of statistical association.
-In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S8).
-Regarding self-compatibility, we found larger differences on PC2.
-For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S8a and figure S8b; Tukey test *P* \< 0.05).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S8c and figure S8d; Tukey test *P* \< 0.05).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S8e and figure S8f; Tukey test *P* \< 0.05).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S8g and figure S8h; Tukey test *P* \< 0.05).
-Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S8i and figure S8j; Tukey test *P* \< 0.05).
-Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S8k and figure S8l; Tukey test *P* \< 0.05).
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="80%",fig.align='center',fig.cap= "\\textbf{Figure 2.} Location of the different qualitative traits in the trait space.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="90%",fig.align='center',fig.cap= "\\textbf{Figure 2.} Location of the different qualitative traits in the trait space.
 The figure panel is composed of the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
@@
 ```
-
-\elandscape
-
-## (b) Phylogenetic signal
-
-We found a strong phylogenetic signal (*P* \< 0.01) for most quantitative traits (table S5).
-The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73) and number of flowers per plant ($\lambda$ = 0.69).
-The traits that had a moderate phylogenetic signal included inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all the traits we measured ($\lambda$ = 0.14).
-
-## (c) Visitation patterns
-
-The main axes of trait variation (PC1, PC2 and PC3) partly explained the presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the total number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant differences across the different pollinator guilds for both the presence-absence of interactions and number of visits (figure 3).
-On the flower number - flower size axis, we found  that plants with many small flowers tended to have interaction partners that were Coleoptera, non-bee-Hymenoptera and Diptera (figure 3a), whereas plants with few large flowers mostly had interaction partners that were bees and Lepidoptera.
-We found similar trends for visitation rates on the flower number - flower size axis,  but bees and syrphids visited plant species with many small flowers more frequently (figure 3d).
-On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and received many visits from all pollinator guilds (figure 3b and figure 3e).
-Finally, on the style length - autonomous selfing axis, plant species with short styles and low autonomous selfing had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and high autonomous selfing (figure 3c).
-Plants with long styles and high autonomous selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera (figure 3f).
-
-The additional models for the most represented bee families, for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and the number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03), showed that the Apidae family was the main driver of the observed patterns.
-The contrast between interaction presence/absence  and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S9).
-
-```{=tex}
-\vspace{5mm}
-\blandscape
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different pollinator guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
-PC1 represents the flower number - flower size axis, PC2 represents the autonomous selfing - floral display axis and PC3 represents the style length - autonomous selfing axis.
-For visualization purposes due to large differences between number of visits from bees and the rest of the pollinator guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
-
-#LOAD LIBRARIES 
-#library(phytools)
-#library(ape) #for phylogenetic distance
-#library(dplyr) #data processing
-#library(rtrees) #for phylogenetic distancelibrary(MASS)
-#library(reshape2)
-library(viridis) #COLOUR GGPLOT
-#library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-#library(tidyverse)
-library(patchwork) #panel of plots
-#library(brms)
-#library(cmdstanr)
-
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2)),
-           axis.text=element_text(size = rel(1.8), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(2, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
-           plot.subtitle = element_text(face="bold",size=rel(2))
-     ))
-}
-
-p1 <- readRDS("../Main_Figures/figure_3_1.rds")
-p2 <- readRDS("../Main_Figures/figure_3_2.rds")
-p3 <- readRDS("../Main_Figures/figure_3_3.rds")
-pp1 <- readRDS("../Main_Figures/figure_3_4.rds")
-pp2 <- readRDS("../Main_Figures/figure_3_5.rds")
-pp3 <- readRDS("../Main_Figures/figure_3_6.rds")
-
-library(patchwork)
-
-combined <- pp1 + pp2 + pp3 + p1 + p2 + p3  & theme(legend.position = "bottom") &  guides(color = guide_legend(override.aes = list(size=6.5), keywidth=1.8,
-                 keyheight=0.1,
-                 default.unit="inch"))
-
-combined + plot_layout(guides = "collect",ncol = 3)
-```
-
-\elandscape
-
-## (d) Plant species network roles
-
-Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S10; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalised degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, selectivity \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and selectivity.
-On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S10a).
-However, selectivity (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S10g).
-On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S10c).
-Again, selectivity showed the opposite trend to the number of visits (figure S10i).
-
-# 4. Discussion
-
-We found strong covariation among traits within the flowering plant reproductive spectrum, which shapes interactions with pollinators at a global scale.
-Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50% and 70% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, autonomous selfing and floral display, and style length and autonomous selfing.
-Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits [@diaz2016; @carmona2021], our results align with the two largest and most recent studies of plant life strategies that included reproductive, form and size related traits [@salguero2016; @vojtko2022].
-The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
-However, the unexplained variability found highlights the need to account for other local factors, such as species relative abundances [@bartomeus2016], along with reproductive traits, to better explain plant-pollinator associations.
-
-Our study provides strong evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1,200 species).
-Specifically, by using a multitrait approach, we are able to link the reproductive spectrum of plant trait variation with the previously described “fast-slow continuum” in plant [@salguero2016] and animal [@healy2019] life-history strategies.
-This fast-slow continuum was illustrated by the associations between reproductive traits and plant height, life form and lifespan traits.
-For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred Angiosperm species and generally lacking a multitrait perspective.
-We found support for this trait association and show that other reproductive traits (e.g., style length or ovule number) covary along this flower number - flower size axis.
-Our study also complements previous work linking plant breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers also have woody life forms and many flowers.
-Moreover, we identify the previously documented positive association between outcrossing rate and floral display size [@goodwillie2010], where species with low autonomous selfing levels also allocate large resource quantities to attract pollinators.
-
-Although we did not include floral rewards in our main analysis due to insufficient data, we did find that plant species with large floral displays and, in particular, large flowers, tended to have higher pollen and nectar quantity.
-Thus, we demonstrate that globally, reproductive trait covariation in flowering plants likely imposes constraints on the broader spectrum of plant trait variation.
-
-Overall, the main plant reproductive axes were insufficient to fully capture plant-pollinator associations.
-However, these axes helped explain, to some extent, interaction patterns among and within pollinator guilds, indicating that they partly mediate these associations across large spatial scales.
-For example, we found that all pollinator guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings [@hegland2005; @lazaro2013; @kaiser2014] and predictions from evolutionary life-history theory [@stebbins1970].
-These predictions suggest that larger investment in floral display and rewards to attract pollinators occurs when dependence on pollinators is high.
-Although pollinators play a major role in shaping plant reproductive strategies, these different strategies are also constrained by the cost of reproductive organs and trait correlations [@galen1999].
-For instance, smaller flowers tend to receive fewer visits than larger flowers, but small flowers are inexpensive to produce (e.g., have few ovules).
-Therefore, low  per-flower visitation can be compensated by overall plant-level visitation through producing many small flowers that develop into numerous small fruits [@kettle2011].
-Our results also indicate that bees interact more with plants that have higher levels of autonomous selfing and large styles, which can help with a more efficient pollen transfer and prevent pollen competition [@ashman2013; @tong2016; @lanuza2021].
-Similarly, the specialised floral structures of zygomorphic flowers promote precise pollen transfer [@sargent2004; @gong2009], although we found that they were associated with high levels of autogamy.
-The annual herb _Lathyrus clymenum_ is a clear example of this pollinator specialization - selfing strategy that may get “the best of both worlds” [@lloyd1992; @goodwillie2018].
-It has showy zygomorphic flowers with relatively long styles and few ovules per flower that are likely fertilised with a single legitimate floral visit but can avoid reproductive failure in the absence of pollinators through autonomous self pollination.
-Our findings are consistent with the hypothesis that selfing is not rare within specialised pollination systems [@fenster2007] and emphasise the need to consider different reproductive assurance mechanisms [e.g., early versus delayed selfing\; @goodwillie2018] to better understand plant reproductive trait correlations and plant-pollinator interactions.
-
-Because flowering plants can adapt to their animal pollinators to optimise pollen transfer, the correlation between distinct suites of plant reproductive traits and pollinator guilds could indicate the existence of pollination syndromes [@fenster2004; @faegri2013; @rosas2014; @dellinger2020].
-However, our work shows a weak association between the different plant reproductive strategies and pollinator guilds, which supports previous findings from a similar pollinator guild classification and spatial scale [@ollerton2009].
-Although our findings contrast with a vast amount of literature on pollinator syndromes dating back over half a century [@faegri2013; @fenster2004], the ecological scale of our study differs from the majority of floral syndrome studies that rarely consider plant-pollinator associations beyond the community scale [ca.
-3% of studies\; @dellinger2020].
-We argue that the predictive power of floral syndromes gets blurred when increasing the number of species and scale, reinforcing the view that strong specialisation may be the exception rather than the norm in plant-pollinator interactions [@jordano1987; @waser1996].
-Further, there are several factors that might have influenced our findings, (e.g., the suite of reproductive traits and type of pollinator guilds we included).
-For instance, including other key reproductive traits, such as floral scent or flower colour, could help to improve predictions of plant-pollinator interactions.
-In addition, our use of broad taxonomic pollinator guild groupings may have obscured  finer scale patterns that occur at lower taxonomic ranks (e.g., genus or species level).
-The fact that our study only accounts for insect pollinators may have also influenced the observed associations between floral traits and pollinator guilds in comparison with other studies, as some other guilds (e.g., hummingbirds or bats) generally display strong trait-matching [@wilson2004; @lagomarsino2017].
-Regardless, it is worth noting that local factors (e.g., species relative abundances, phenologies or intraspecific variation) likely contribute to the variability in interactions between the plant reproductive spectrum and pollinators [@vazquez2007; @encinas2012; @bartomeus2016; @arroyo2023].
-We suggest that while plant reproductive traits do influence which pollinators they interact with, at a macroecological scale, pollination syndromes possibly take the form of a multifaceted, context dependent continuum [e.g., ornithophilous versus entomophilous pollination of red flowers\; @leon2022].
-
-Our study provides a comprehensive assessment of  reproductive trait covariation patterns in flowering plants, using a global dataset of traits for plant species within plant-pollinator networks.
-We show the importance of pollinators in mediating reproductive trait correlations and identify the need to consider broader plant reproductive strategies, rather than just flower morphology, to understand patterns of plant-pollinator interactions.
-Further, we provide empirical evidence of reproductive trait associations that complement trait covariation studies for other plant organs, highlighting the need to include reproductive traits in the global spectrum of plant form and function.
-Future work incorporating underrepresented areas of the world and additional relevant reproductive traits (e.g., flower life span and colour) from a broader range of life forms will be valuable for enhancing our understanding of the plant reproductive spectrum and associated plant-pollinator interactions.
-
-\newpage
-
-# References
-
-::: {#refs}
-:::

### 2023-04-13 Main_Figures/Figure_3.Rmd
edits for final sub

--- 2023-03-02 Manuscript/Lanuza_et_al_2022.Rmd
@@
 
-```{=tex}
-\doublespacing
-\normalsize
-```
-
-# Abstract
-
-1.
-Globally, plants display enormous variation in life history strategies and trait combinations.
-However, evidence suggests that evolutionary and physiological constraints limit the number of plant ecological strategies.
-Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with pollinators.
-
-2. Here, using a global dataset of 18 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
-
-3.
-We show that over 50% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the negative correlation between autonomous selfing and floral display size.
-In addition, these reproductive axes were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
-However, reproductive axes explain a relatively small amount of variance in pollinator interactions highlighting the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
-
-4.
-Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping plant-pollinator interactions at a macro-ecological scale.
-These findings emphasise the importance of considering reproductive traits in the global spectrum of plant form and function, and the need to explore beyond floral morphological traits to broaden our understanding of plant-pollinator interactions.
-
-\textbf{Keywords:} life-history strategies \| plant reproductive traits \| plant-pollinator interactions
-
-```{=tex}
-\doublespacing
-\vspace{5mm}
-\normalsize
-```
-```{r setup, include=FALSE, cache=FALSE, message = FALSE}
-
-library("knitr")
-
-### Chunk options: see http://yihui.name/knitr/options/ ###
-## Text results
-opts_chunk$set(echo = FALSE, warning = TRUE, message = TRUE)
-
-## Code decoration
-opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)
-
-## Cache
-# opts_chunk$set(cache = 2, cache.path = "output/cache/")
-
-## Plots
-opts_chunk$set(fig.path = "output/figures/")
-
-```
-
-```{r knitcitations, cache = FALSE}
-library(knitcitations)
-cleanbib()   
-cite_options(citation_format = "pandoc")
-
-```
-
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.pos = 'H')
-```
-
-# 1. Introduction
-
-Flowering plants display an astonishing diversity of reproductive structures [@barrett2002; @schiestl2013] that shape their interactions with animal pollinators [@fenster2004; @dellinger2020].
-The variety of reproductive strategies used by different plant species, from specialised reliance on a single pollinator, to full self-pollination, is incredibly rich.
-However, not all combinations of reproductive traits (i.e., morphological and physiological traits that determine a plant’s ability to reproduce) are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
-Despite recent advances in theoretical and empirical understanding of correlations between plant reproductive traits at large ecological scales [@salguero2016; @friedman2020; @paterno2020; @roddy2021; @song2022], studies typically focus on just a few traits, often in isolation.
-Thus, to develop a comprehensive understanding of the plant reproductive spectrum of trait variation, as done recently for root [@laughlin2021], leaf [@wright2004] and wood [@chave2009] related traits, we require a multi-trait perspective with broad geographical coverage.
-Importantly, characterization of the plant reproductive spectrum could reveal key reproductive strategies among different species [@agrawal2020] and improve knowledge of associations between specific reproductive traits and pollinators [@roddy2021].
-
-With the recent availability of large trait databases [e.g., TRY @kattge2011;  COMPADRE @salguero2015], there has been increased research on plant ecological strategies, which has produced identification of global patterns in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
-However, studies that look at multiple traits tend to overlook plant reproductive traits [@evojtko2020; @ruger2018; @roddy2021], and focus on trait correlations in other plant organs such as morphological and physiological leaf traits [@wright2004; @shipley2006; @donovan2011; @osnas2013].
-Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs such as the negative correlation between flower size and flower number [@sargent2007; @kettle2011; @vojtko2022]; the positive association between flower size and outcrossing rate [@goodwillie2010]; or the positive correlation between outcrossing rate and lifespan [@barrett2003; @munoz2016; @moeller2017].
-Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships [@roddy2021], we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
-
-Trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] are powerful for exploring the underlying mechanisms driving plant-pollinator interactions.
-For example, plant traits can define species' network roles [e.g., specialists vs generalists @tur2013] and plant species that occupy reproductive trait space extremes are likely to be more specialised and display tighter trait-matching with pollinators [@junker2013; @coux2016].
-Indeed, the degree of morphological matching between plants and pollinators often determines whether or not interactions occur, and consequently influences  the broader network structure [@stang2009; @ibanez2012].
-However, it is still unclear how specific reproductive traits (e.g., mating or compatibility system) influence plant-pollinator associations [@sargent2008; @tur2013; @devaux2014].
-For example, species with high selfing rates may evolve to invest less in floral rewards resulting in a lower number of pollinator visits [@devaux2014].
-Indeed, both morphology and mating system can determine a species' functional role within pollination networks, and the combination of several traits increases power for predicting network structure [@eklof2013].
-Because the species position within the multidimensional trait space can result in different interaction patterns or adaptations to pollinators [see @dehling2016 for a purely morphological approach], the use of the reproductive trait space to explore plant-pollinator interactions could help to identify species functional roles and associations of traits with specific pollinators (i.e., pollination syndromes).
-
-Here, we explore the spectrum of reproductive traits in flowering plants, within a global set of plant-pollinator networks, to identify reproductive trait covariation and how this influences the network of interactions between plants and pollinators.
-First, we identify the major axes of reproductive trait variation and correlations among traits for plant species.
-Then, we investigate the associations between plant species’ positions in reproductive trait space and the strength of their interactions with different pollinator guilds within networks.
-Finally, we determine how the main axes of reproductive trait variation influence plant species' functional roles within pollination networks, using a range of complementary interaction network metrics.
-
-# 2. Methods
-
-## (a) Plant-pollinator network studies
-
-We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see table S1 and figure S1).
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different ecological communities.
-The pollinators documented by these studies are primarily insect pollinators (97.8% of the total visits recorded) and the plants are characterised by a clear dominance of smaller life forms (i.e., 61% of herbs, 28% of shrubs and 11% of trees).
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to benefit, to some degree, from animal pollination.
-Many of these networks are freely available either as published studies [e.g., @carvalheiro2014; @olesen2007; @fortuna2010] or in online archives [e.g., Mangal @poisot2016;  The Web of Life @fortuna2010].
-In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (interaction presence-absence) networks, each sampled at a unique location and year, as well as 8 meta-networks where interactions were pooled across several locations and multiple years.
-
-## (b) Taxonomy of plants and pollinators
-
-All species names, genera, families and orders were retrieved and standardised from the taxonomy data sources NCBI (<https://www.ncbi.nlm.nih.gov/taxonomy>) for plants and ITIS (<https://www.itis.gov/>) for pollinators, using the R package *taxize* [@chamberlain2020].
-We filled the 'not found' searches manually using <http://www.theplantlist.org/> and <http://www.mobot.org/> for plants and <http://www.catalogueoflife.org/> for pollinators.
-
-## (c) Plant traits
-
-We selected a total of 18 quantitative and categorical functional traits that included reproductive traits and traits related with plant form and size (see table 1).
-Reproductive traits consisted of those related to floral and reproductive biology: (i) floral traits included those related to the size of floral organs (e.g., style length), floral display size (e.g., flower number) and floral rewards (e.g., pollen quantity), while (ii) reproductive biology traits represented the plant reproductive system (i.e., the breeding, mating and compatibility system).
-The remaining traits were related to plant size and form (i.e., plant height, lifespan and life form), which are commonly used to characterise the fast-slow continuum of plant trait variation [@salguero2016].
-For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
-From a matrix comprising a total of 27,108 possible cells (considering all traits and plant species: 18 columns × 1,506 species), we were able to fill 22,796 cells (84.1% of the dataset, see figure S2 for missing value information for each trait).
-An extended description of each trait and how it was obtained can be found in Appendix S1.
-
-\singlespacing
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=1, fig.width=14}
-
-library(kableExtra)
-
-library(dplyr)
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("../Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant","Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg", "Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Floral_unit_width",
-         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
-         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg", "Pollen_per_flower")]
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-n_of_records <- subset(missing.values, isna=="FALSE")
-
-Trait <- c("Plant height", "Flower width", "Flower length", "Inflorescence width", "Style length", "Ovules per flower",
-           "Flowers per plant", "Microliters of nectar", "Milligrams of nectar", "Pollen grains per flower", "Autonomous selfing (fruit set)")
-
-Trait1 <- linebreak(c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Compatibility system", "Breeding system"),align = c("l"))
-
-#T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub #\n Tree", "Brush \n Campanulate \n Capitulum \n Open \n #Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-#           "Presence \n Absence", "Self-incomp. \n Part. #self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n #Dioecious"),align = c("l"))
-#
-T.cat <- linebreak(c("Short-lived and perennial", "Herb, shrub and tree", "Brush, campanulate, capitulum,\n open, papilionaceous and tube",  "Actinomorphic and zygomorphic",
-           "Presence and absence", "Self-incompatible, partially self-compabtile \n and self-compatible", "Hermaphrodite, monoecious and dioecious"), align = c("l"))
-
-Number_of_records_quantitative <- c(n_of_records$num.isna[n_of_records$key=="Plant_height_mean_m"], n_of_records$num.isna[n_of_records$key=="Corolla_diameter_mean"],
-  n_of_records$num.isna[n_of_records$key=="Corolla_length_mean"], n_of_records$num.isna[n_of_records$key=="Floral_unit_width"],
-  n_of_records$num.isna[n_of_records$key=="Style_length"], n_of_records$num.isna[n_of_records$key=="Ovule_number"],
-  n_of_records$num.isna[n_of_records$key=="Flowers_per_plant"], n_of_records$num.isna[n_of_records$key=="Nectar_ul"],
-  n_of_records$num.isna[n_of_records$key=="Nectar_mg"],  n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
-  n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level_fruit_set"])
-
-Number_of_records_categorical <- c(n_of_records$num.isna[n_of_records$key=="lifespan"], n_of_records$num.isna[n_of_records$key=="life_form"],
-                                   n_of_records$num.isna[n_of_records$key=="Flower_morphology"], n_of_records$num.isna[n_of_records$key=="Flower_symmetry"],
-                                   n_of_records$num.isna[n_of_records$key=="Nectar_presence_absence"], n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level"],
-                                   n_of_records$num.isna[n_of_records$key=="Compatibility_system"], n_of_records$num.isna[n_of_records$key=="Breeding_system"],
-                                   rep("",4))
-
-T.range <- c("0.01-30m", "0.50-205mm", "0.20-195mm", "0.80-300mm", "0-138mm", "1-25000", "1-1.8 x $10^5$", "0-160$\\mu$l", "0-6.1mg", "13-2 x $10^8$", "0-100$\\%$")
-
-dat_1 <- data.frame(Trait,T.range)
-dat_2 <- data.frame(Trait1, T.cat)
-
-colnames(dat_1) <- c("Quantitative traits", "Numerical range")
-colnames(dat_2) <- c("Categorical traits", "Categories")
-
-#kable(list(dat_1, dat_2), booktabs = T, linesep = #"\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1 | #Quantitative and categorical traits used in this study.}") %>%
-#  kable_styling(full_width = F,font_size = 10) %>%  #column_spec(1:4, 
-#              width = "3in", 
-#              latex_valign = "m")
-#
-#
-
-colnames(dat_1) <- c("Traits", "Numerical range/Categories")
-colnames(dat_2) <- c("Traits", "Numerical range/Categories")
-
-d <- rbind(dat_1,dat_2)
-
-kable(d, booktabs = T, linesep = "\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1.} Quantitative and categorical traits used in this study.") %>%
-  kable_styling(full_width = F,font_size = 12) %>% row_spec(0, bold=T) %>% pack_rows("Quantitative", 1, 11) %>%
-pack_rows("Categorical", 12, 18)
-
-```
-
-\doublespacing
-
-## (d) Phylogenetic Distance
-
-We calculated the phylogenetic distance between all plant species considered using the function *get_tree* from the package *rtrees* (<https://github.com/daijiang/rtrees>), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
-
-## (e) Data Imputation
-
-To avoid excluding species with missing trait data, we imputed missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors from principal component analysis of the phylogenetic distance (PCoA), which has been shown to improve the performance of *missForest* [@penone2014].
-To extract the eigenvectors, we used the function *PVRdecomp* from the package *PVR* [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-We conducted two different imputations, one for the full set of species (1,506 species: 5.79% of missing values), and excluding nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and results for the two datasets were consistent (Fig S3 and Fig S4).
-
-## (f) Plant strategies analysis
-
-We explored the association between the different quantitative plant traits using a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasise flower size on the spectrum of trait variation.
-Prior to the analyses, we excluded outliers and standardised the data.
-Specifically, due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis [@legendre2012].
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated their position in the trait space and the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
-Similarly, we also explored for each pollinator guild (see "Visitation patterns" subsection below) the position in the trait space of the plants that interacted with them.
-We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode “covariance” because values for each variables were on the same scale following transformation [@abdi2010].
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity data.
-For this, we included all quantitative traits included in the main pPCA, plus pollen grains and microlitres of nectar per flower.
-
-## (g) Phylogenetic signal
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package *phytools* [@revell2012] and used Pagel's $\lambda$ as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-## (h) Network analyses
-
-### (i) Visitation patterns
-
-We used Bayesian modelling (see details below) to investigate how the different guilds of pollinators interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
-Specifically, interactions between plants and pollinators in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
-Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species [@ballantyne2015], the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination [@vazquez2005; @vazquez2012].
-Therefore, despite the fact that we do not evaluate pollinator effectiveness we refer to the different floral visitors as pollinators.
-
-We divided pollinators into six main taxonomical guilds that differ in life form, behaviour and thus likely play different ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
-Note that we excluded non-insect pollinators from our analyses as they comprised only a 2.2% of the total visits recorded in our set of studies.
-Moreover, because bees had the greatest number of occurrences in networks  (2,256 records) and the highest frequency of visits, we further broke this group down into the main bee families (Andrenidae, Apidae, Colletidae, Halictidae, and Megachilidae).
-In addition, we found that *Apis mellifera* was the pollinator with the largest proportion of occurrences in networks (7.55% of the total).
-This is consistent with previous research showing that *A.
-mellifera* was the most frequent pollinator in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
-Hence, to control for the effect of *A.
-mellifera* on observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding *A.
-mellifera*.
-We found that *A.
-mellifera*, was partly driving some of the observed trends on PC1 (figure S5).
-However, we did not detect major differences on PC2 and PC3.
-
-We used Bayesian generalised linear mixed models in the R package *brms* [@burkner2017] to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation (i.e., PC) and their interactions with pollinator guilds (i.e., PGs; e.g., number of visits \~ PC1 x PGs + PC2 x PGs + PC3 x PGs).
-Because we were interested in possible differences in visitation patterns among pollinator guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different pollinator guilds in the model.
-We added a nested random effect of networks within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence among them.
-We specified for the presence or absence of an interaction and number of visits with Bernoulli and a zero inflated negative binomial distributions, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results [@burkner2017].
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualised the posterior predictive checks with the function *pp_check* using the *bayesplot* package [@gabry2019].
-
-### (ii) Plant species network roles
-
-We also used Bayesian modelling to investigate how the main axes of trait variation determined different plant species' functional roles within pollination networks.
-For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies [@dormann2008], with clear ecological interpretations and are relevant for defining species' functional roles in networks.
-Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalised degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) selectivity (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalisation) and 1 (maximum specialisation).
-Normalised degree and selectivity were calculated with the *specieslevel* function in the R package *bipartite* [@dormann2008].
-We modelled each plant species metric (sum of visits, normalised degree and plant selectivity) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
-For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalised degree, and zero-one inflated beta for selectivity).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the 'visitation patterns' section.
-
-Our analyses were conducted on the subset of 60 weighted networks (out of a total of 64 networks) sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our network dataset (excluding meta- and non-weighted networks) included 2,256 interactions for bees, 1,768 for non-syrphid-dipterans, 845 for syrphids, 437 for lepidopterans, 432 for coleopterans, and 362 for non-bee-hymenopterans.
-Sampling methods varied across studies but this was accounted for in analyses by including study identity as a  random effect in our models.
-All analyses were conducted in R version *4.0.3*.
-
-# 3. Results
-
-## (a) Plant strategies analysis
-
-Our phylogenetically informed principal component analysis captured  51.8% and 70.97% of the reproductive trait variation in the first two and three axes, respectively (figure 1 and figure S6).
-The first principal component (PC1; the flower number - flower size axis) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; table S3) but style length also contributed moderately (loading = -0.33).
-One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-For instance, *Cornus florida* occurred at this end of the spectrum, which, on average, has approximately 10,000 flowers, is 7.5 m high, has flowers that are 3 mm wide, styles 3.5 mm long and  two ovules per flower.
-The other end of this spectrum had species that were short in height, with few large flowers that had long styles and many ovules.
-For example, *Petunia axillaris* on average, is 0.5 m high and has approximately 10 flowers per plant that are over 50 mm wide with 25 mm long styles and over 200 ovules.
-The second principal component (PC2; the autonomous selfing - floral display axis) encompassed 25.05% of the trait variation and represented variation from low to high autonomous selfing (i.e., high to low pollinator dependence).
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but all other traits (except ovule number) made moderate contributions (loadings ranging between 0.27 to 0.4; table S3).
-Generally speaking, species with low autonomous selfing had larger and many flowers with long styles, and were tall.
-*Zuccagnia punctata* occurred at this extreme of the spectrum, which is a self-incompatible species, completely dependent on animal pollination for seed production, producing  approximately 1,500 flowers per plant with an average height of 3 m and 20 mm long styles.
-In contrast, species with high autonomous selfing tended to have fewer and smaller flowers with shorter styles, and were shorter in height.
-*Veronica peregrina* occurred at this end of the spectrum, and is a self-compatible plant that requires little or no pollination by animals, it has approximately 20 flowers per plant, is 0.2 m high and has 0.25 mm long styles.
-The third principal component (PC3; the style length - autonomous selfing axis) explained a considerable amount of trait variability (19.17%) and represented a positive correlation between style length (loading = -0.66) and autonomous selfing (loading = \|-0.51\|), where species with short styles had low autonomous selfing and species with long styles high autonomous selfing.
-The remaining traits, apart from ovule number, were all positively correlated with style length and autonomous selfing (loadings from -0.23 to -0.46; table S3).
-In addition, the pPCA with the subset of species that we had nectar and pollen quantity data for showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with floral display size.
-Floral rewards were particularly strongly correlated with flower size but weakly correlated with flower number (figure S4).
-The first two principal components for this pPCA explained similar variance  (45.52%) and similar associations of traits, despite some variability in the loadings (table S4).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="85%", fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
-The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
-The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation.
-The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}
-
-#Load libraries
-library(viridis) #COLOUR GGPLOT
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(magick)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("../Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("../Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#Images were made by Paula Martin
-#Check her work on https://paulamartinart.com/
-
-tree <- image_read("../Images/PPCA_Plot/Tree.png")
-tree_1 <- as.raster(tree)
-
-style_l <- image_read("../Images/PPCA_Plot/Style_Long.png")
-style_l_1 <- as.raster(style_l)
-
-style_s <- image_read("../Images/PPCA_Plot/Style_Short.png")
-style_s_1 <- as.raster(style_s)
-
-ovule_h <- image_read("../Images/PPCA_Plot/Ovule_High.png")
-ovule_h_1 <- as.raster(ovule_h)
-
-ovule_l <- image_read("../Images/PPCA_Plot/Ovule_Low.png")
-ovule_l_1 <- as.raster(ovule_l)
-
-selfing_n <- image_read("../Images/PPCA_Plot/Selfing_None.png")
-selfing_n_1 <- as.raster(selfing_n)
-
-selfing_h <- image_read("../Images/PPCA_Plot/selfing.png")
-selfing_h_1 <- as.raster(selfing_h)
-
-single_flower <- image_read("../Images/PPCA_Plot/Single_Flower.png")
-single_flower_1 <- as.raster(single_flower)
-
-many_flowers <- image_read("../Images/PPCA_Plot/Inflorescencia.png")
-many_flowers_1 <- as.raster(many_flowers)
-#many_flowers_1 <- image_rotate(many_flowers, 45)
-
-large_flower <- image_read("../Images/PPCA_Plot/flower_big.png")
-large_flower_1 <- as.raster(large_flower)
-
-#"Images/PPCA_Plot/flower_short.png"
-flower_small <- image_read("../Images/PPCA_Plot/flower_big.png")
-flower_small_1 <- as.raster(flower_small)
-
-herb <- image_read("../Images/PPCA_Plot/herb.png")
-herb_1 <- as.raster(herb)
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Autonomous selfing - Floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
-    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
-    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
-    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.18, xmax = 4.13,ymin = 1.3, ymax = 2.4) +
-    annotation_raster(flower_small_1, xmin = -3.21, xmax = -2.81,ymin = -2, ymax = -1.45) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
-
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
-                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-plot_grid(all_spp(PC))
-
-```
-
-As expected, due to individual trait correlations between qualitative and quantitative traits (e.g., life form and plant height), we found that most categorical traits were clustered on the trait space and statistically associated with the first two axes of trait variation (figure s2 and table s2).
-However, the position of plants connected to each of the pollinator guilds was scattered without clear aggregation patterns on the trait space (figure s7; but see "Visitation patterns" section below for detailed results from quantitative analyses).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed a lack of statistical association.
-In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S8).
-Regarding self-compatibility, we found larger differences on PC2.
-For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S8a and figure S8b; Tukey test *P* \< 0.05).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S8c and figure S8d; Tukey test *P* \< 0.05).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S8e and figure S8f; Tukey test *P* \< 0.05).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S8g and figure S8h; Tukey test *P* \< 0.05).
-Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S8i and figure S8j; Tukey test *P* \< 0.05).
-Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S8k and figure S8l; Tukey test *P* \< 0.05).
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="80%",fig.align='center',fig.cap= "\\textbf{Figure 2.} Location of the different qualitative traits in the trait space.
-The figure panel is composed of the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
-The solid arrows indicate the direction of variation of the different quantitative traits shown in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S)."}
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(ggstar)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.6)),
-            axis.text=element_text(size = rel(1.6), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(size = rel(1.1)),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.4, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank(),
-            plot.title = element_text(size = rel(2.5), face="bold")
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("../Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
-phyl_pca_forest <- readRDS("../Data/RData/phyl_pca_forest.rds")
-
-#CALL the output PC for simplicity
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-Compatibility <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Compatibility <- dat_cleaning_5$Compatibility_system
-  dat$Compatibility <- as.character(dat$Compatibility)
-  dat$Compatibility[dat$Compatibility=="dioecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="monoecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-  dat$Compatibility[dat$Compatibility=="self_compatible"] <- "Self compatible"
-  dat$Compatibility[dat$Compatibility=="self_incompatible"] <- "Self incompatible"
-  dat$Compatibility <- factor(dat$Compatibility, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=Compatibility, fill=Compatibility), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("deepskyblue2", "purple2","goldenrod","gray7")) +
-scale_starshape_manual(values = c(13, 15, 28, 5))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)  + ylab("Autonomous selfing - Floral display axis")
-
-  plot
-
-}
-
-#Compatibility(PC)
-
-#############################################################################################################################################################
-#Life form
-#############################################################################################################################################################
-#Load plots
-Life_form <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Life form` <- dat_cleaning_5$life_form
-  dat$`Life form` <- as.character(dat$`Life form`)
-  dat$`Life form`[dat$`Life form`=="herb"] <- "Herb"
-  dat$`Life form`[dat$`Life form`=="shrub"] <- "Shrub"
-  dat$`Life form`[dat$`Life form`=="tree"] <- "Tree"
-  dat$`Life form`[dat$`Life form`=="vine"] <- "Shrub"
-
-  dat$`Life form` <- factor( dat$`Life form`, levels = c("Herb", "Shrub", "Tree"))
-
-plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Life form`, fill=`Life form`), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("forestgreen", "darkorange2","black")) +
-scale_starshape_manual(values = c(13, 15, 28))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.090, 0.115)) + ggtitle("(b)") +
-    xlab(NULL) + ylab(NULL)
-
-  plot
-
-}
-
-#Life_form(PC)
-
-#############################################################################################################################################################
-#Life span
-#############################################################################################################################################################
-#Load plots
-Life_span <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-    dat$Lifespan <- dat_cleaning_5$lifespan
-    dat$Lifespan <- as.character(dat$Lifespan)
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=Lifespan, fill=Lifespan), size=2.25, color= NA, alpha = 0.9)+ scale_fill_manual(values=c("sienna4","forestgreen")) +
-scale_starshape_manual(values = c(13, 15))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.12, 0.1)) + ggtitle("(c)") +
-    xlab(NULL) + ylab(NULL)
-
-  plot
-
-}
-
-#Life_span(PC)
-
-#############################################################################################################################################################
-#Flower symmetry
-#############################################################################################################################################################
-#Load plots
-Flower_sym <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower symmetry` <- dat_cleaning_5$Flower_symmetry
-  dat$`Flower symmetry` <- as.character(dat$`Flower symmetry`)
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Flower symmetry`, fill=`Flower symmetry`), size=2.25, color= NA, alpha = 0.9) + scale_fill_manual(values=c("goldenrod","purple2")) +
-scale_starshape_manual(values = c(13, 15))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL) + xlab("Flower number - Flower size axis")
-
-  plot
-
-}
-
-#Flower_sym(PC)
-
-#############################################################################################################################################################
-#Flower shape
-#############################################################################################################################################################
-#Load plots
-Flower_sha <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower shape` <- dat_cleaning_5$Flower_morphology
-  dat$`Flower shape` <- as.character(dat$`Flower shape`)
-  dat$`Flower shape`[dat$`Flower shape`=="Funnelform"] <- "Campanulate"
-  dat$`Flower shape`[dat$`Flower shape`=="Spike"] <- "Brush"
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Flower shape`, fill=`Flower shape`), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("black","goldenrod", "deepskyblue2","forestgreen","purple2","darkorange2")) +
-scale_starshape_manual(values = c(13, 15, 28, 5, 9, 14))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL) + xlab("Flower number - Flower size axis")
-
-  plot
-
-}
-
-#Flower_sha(PC)
-
-#############################################################################################################################################################
-#Breeding system
-#############################################################################################################################################################
-#Load plots
-Breeding_syst <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Breeding system` <- dat_cleaning_5$Breeding_system
-  dat$`Breeding system` <- as.character(dat$`Breeding system`)
-  dat$`Breeding system` <- factor(dat$`Breeding system`, levels=c("Hermaphrodite","Monoecious" ,"Dioecious"))
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Breeding system`, fill=`Breeding system`), size=2.25, color= NA, alpha = 0.9) + scale_fill_manual(values=c("forestgreen","darkorange2", "black")) +
-scale_starshape_manual(values = c(13, 15, 28))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("(d)") +
-    xlab("Flower number - Flower size axis") +
-    ylab("Autonomous selfing - Floral display axis")
-
-  plot
-
-}
-
-#Breeding_syst(PC)
-
-#############################################################################################################################################################
-#Nectar
-#############################################################################################################################################################
-#Load plots
-#Nectar <- function(PC, x="PC1", y="PC2") {
-#  # PC being a prcomp object
-#  data <- data.frame(PC$S)
-#  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-#  dat <- data.frame(x = data[,x], y = data[,y])
-#  
-#  #######
-#  #DENSITY FUNCTION
-#  #######
-#  get_density <- function(x, y, ...) {
-#    dens <- MASS::kde2d(x, y, ...)
-#    ix <- findInterval(x, dens$x)
-#    iy <- findInterval(y, dens$y)
-#    ii <- cbind(ix, iy)
-#    return(dens$z[ii])
-#  }
-#  
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-#  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-#  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-#  plot <- plot + geom_point(data=dat, aes(-x, -y, #colour=Nectar),size=1.75)+scale_color_manual(values=c("black","grey"))
-#  
-#  ########
-#  #ADD ARROWS 
-#  ########
-#  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-#  mult <- min(
-#    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-#    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-#  )
-#  datapc <- transform(datapc,
-#                      v1 = .75 * mult * (get(x)),
-#                      v2 = .75 * mult * (get(y))
-#  )
-#  # add arrows
-#  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, #yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-#  
-#  #Add axis with perctentage
-#  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-#
-#  
-#  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, #arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-#  
-#  #ADD LABELS
-#  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-#  
-#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-#  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = #-(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-#                          label = PCAloadings$Variables, color="black",size=3)
-#  
-#  #CHANGE THEME
-#  #CHANGE THEME
-#  
-#  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)") 
-#  
-#  plot
-#  
-#}
-#
-# #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")
-
-  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),ncol=3,nrow=2,  align = "hv")
-
-```
-
-\elandscape
-
-## (b) Phylogenetic signal
-
-We found a strong phylogenetic signal (*P* \< 0.01) for most quantitative traits (table S5).
-The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73) and number of flowers per plant ($\lambda$ = 0.69).
-The traits that had a moderate phylogenetic signal included inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all the traits we measured ($\lambda$ = 0.14).
-
-## (c) Visitation patterns
-
-The main axes of trait variation (PC1, PC2 and PC3) partly explained the presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the total number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant differences across the different pollinator guilds for both the presence-absence of interactions and number of visits (figure 3).
-On the flower number - flower size axis, we found  that plants with many small flowers tended to have interaction partners that were Coleoptera, non-bee-Hymenoptera and Diptera (figure 3a), whereas plants with few large flowers mostly had interaction partners that were bees and Lepidoptera.
-We found similar trends for visitation rates on the flower number - flower size axis,  but bees and syrphids visited plant species with many small flowers more frequently (figure 3d).
-On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and received many visits from all pollinator guilds (figure 3b and figure 3e).
-Finally, on the style length - autonomous selfing axis, plant species with short styles and low autonomous selfing had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and high autonomous selfing (figure 3c).
-Plants with long styles and high autonomous selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera (figure 3f).
-
-The additional models for the most represented bee families, for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and the number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03), showed that the Apidae family was the main driver of the observed patterns.
-The contrast between interaction presence/absence  and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S9).
-
-```{=tex}
-\vspace{5mm}
-\blandscape
-```
-
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different pollinator guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
@@
            legend.key.size = unit(2, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
+           panel.border=element_rect(color="black",size=2.5),
            panel.grid.minor.x =element_blank(),
@@
 
-p1 <- readRDS("../Main_Figures/figure_3_1.rds")
-p2 <- readRDS("../Main_Figures/figure_3_2.rds")
-p3 <- readRDS("../Main_Figures/figure_3_3.rds")
-pp1 <- readRDS("../Main_Figures/figure_3_4.rds")
-pp2 <- readRDS("../Main_Figures/figure_3_5.rds")
-pp3 <- readRDS("../Main_Figures/figure_3_6.rds")
+p1 <- readRDS("../Main_Figures/Other_figs/figure_3_1.rds")
+p2 <- readRDS("../Main_Figures/Other_figs/figure_3_2.rds")
+p3 <- readRDS("../Main_Figures/Other_figs/figure_3_3.rds")
+pp1 <- readRDS("../Main_Figures/Other_figs/figure_3_4.rds")
+pp2 <- readRDS("../Main_Figures/Other_figs/figure_3_5.rds")
+pp3 <- readRDS("../Main_Figures/Other_figs/figure_3_6.rds")
 
@@
 ```
-
-\elandscape
-
-## (d) Plant species network roles
-
-Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S10; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalised degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, selectivity \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and selectivity.
-On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S10a).
-However, selectivity (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S10g).
-On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S10c).
-Again, selectivity showed the opposite trend to the number of visits (figure S10i).
-
-# 4. Discussion
-
-We found strong covariation among traits within the flowering plant reproductive spectrum, which shapes interactions with pollinators at a global scale.
-Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50% and 70% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, autonomous selfing and floral display, and style length and autonomous selfing.
-Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits [@diaz2016; @carmona2021], our results align with the two largest and most recent studies of plant life strategies that included reproductive, form and size related traits [@salguero2016; @vojtko2022].
-The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
-However, the unexplained variability found highlights the need to account for other local factors, such as species relative abundances [@bartomeus2016], along with reproductive traits, to better explain plant-pollinator associations.
-
-Our study provides strong evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1,200 species).
-Specifically, by using a multitrait approach, we are able to link the reproductive spectrum of plant trait variation with the previously described “fast-slow continuum” in plant [@salguero2016] and animal [@healy2019] life-history strategies.
-This fast-slow continuum was illustrated by the associations between reproductive traits and plant height, life form and lifespan traits.
-For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred Angiosperm species and generally lacking a multitrait perspective.
-We found support for this trait association and show that other reproductive traits (e.g., style length or ovule number) covary along this flower number - flower size axis.
-Our study also complements previous work linking plant breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers also have woody life forms and many flowers.
-Moreover, we identify the previously documented positive association between outcrossing rate and floral display size [@goodwillie2010], where species with low autonomous selfing levels also allocate large resource quantities to attract pollinators.
-
-Although we did not include floral rewards in our main analysis due to insufficient data, we did find that plant species with large floral displays and, in particular, large flowers, tended to have higher pollen and nectar quantity.
-Thus, we demonstrate that globally, reproductive trait covariation in flowering plants likely imposes constraints on the broader spectrum of plant trait variation.
-
-Overall, the main plant reproductive axes were insufficient to fully capture plant-pollinator associations.
-However, these axes helped explain, to some extent, interaction patterns among and within pollinator guilds, indicating that they partly mediate these associations across large spatial scales.
-For example, we found that all pollinator guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings [@hegland2005; @lazaro2013; @kaiser2014] and predictions from evolutionary life-history theory [@stebbins1970].
-These predictions suggest that larger investment in floral display and rewards to attract pollinators occurs when dependence on pollinators is high.
-Although pollinators play a major role in shaping plant reproductive strategies, these different strategies are also constrained by the cost of reproductive organs and trait correlations [@galen1999].
-For instance, smaller flowers tend to receive fewer visits than larger flowers, but small flowers are inexpensive to produce (e.g., have few ovules).
-Therefore, low  per-flower visitation can be compensated by overall plant-level visitation through producing many small flowers that develop into numerous small fruits [@kettle2011].
-Our results also indicate that bees interact more with plants that have higher levels of autonomous selfing and large styles, which can help with a more efficient pollen transfer and prevent pollen competition [@ashman2013; @tong2016; @lanuza2021].
-Similarly, the specialised floral structures of zygomorphic flowers promote precise pollen transfer [@sargent2004; @gong2009], although we found that they were associated with high levels of autogamy.
-The annual herb _Lathyrus clymenum_ is a clear example of this pollinator specialization - selfing strategy that may get “the best of both worlds” [@lloyd1992; @goodwillie2018].
-It has showy zygomorphic flowers with relatively long styles and few ovules per flower that are likely fertilised with a single legitimate floral visit but can avoid reproductive failure in the absence of pollinators through autonomous self pollination.
-Our findings are consistent with the hypothesis that selfing is not rare within specialised pollination systems [@fenster2007] and emphasise the need to consider different reproductive assurance mechanisms [e.g., early versus delayed selfing\; @goodwillie2018] to better understand plant reproductive trait correlations and plant-pollinator interactions.
-
-Because flowering plants can adapt to their animal pollinators to optimise pollen transfer, the correlation between distinct suites of plant reproductive traits and pollinator guilds could indicate the existence of pollination syndromes [@fenster2004; @faegri2013; @rosas2014; @dellinger2020].
-However, our work shows a weak association between the different plant reproductive strategies and pollinator guilds, which supports previous findings from a similar pollinator guild classification and spatial scale [@ollerton2009].
-Although our findings contrast with a vast amount of literature on pollinator syndromes dating back over half a century [@faegri2013; @fenster2004], the ecological scale of our study differs from the majority of floral syndrome studies that rarely consider plant-pollinator associations beyond the community scale [ca.
-3% of studies\; @dellinger2020].
-We argue that the predictive power of floral syndromes gets blurred when increasing the number of species and scale, reinforcing the view that strong specialisation may be the exception rather than the norm in plant-pollinator interactions [@jordano1987; @waser1996].
-Further, there are several factors that might have influenced our findings, (e.g., the suite of reproductive traits and type of pollinator guilds we included).
-For instance, including other key reproductive traits, such as floral scent or flower colour, could help to improve predictions of plant-pollinator interactions.
-In addition, our use of broad taxonomic pollinator guild groupings may have obscured  finer scale patterns that occur at lower taxonomic ranks (e.g., genus or species level).
-The fact that our study only accounts for insect pollinators may have also influenced the observed associations between floral traits and pollinator guilds in comparison with other studies, as some other guilds (e.g., hummingbirds or bats) generally display strong trait-matching [@wilson2004; @lagomarsino2017].
-Regardless, it is worth noting that local factors (e.g., species relative abundances, phenologies or intraspecific variation) likely contribute to the variability in interactions between the plant reproductive spectrum and pollinators [@vazquez2007; @encinas2012; @bartomeus2016; @arroyo2023].
-We suggest that while plant reproductive traits do influence which pollinators they interact with, at a macroecological scale, pollination syndromes possibly take the form of a multifaceted, context dependent continuum [e.g., ornithophilous versus entomophilous pollination of red flowers\; @leon2022].
-
-Our study provides a comprehensive assessment of  reproductive trait covariation patterns in flowering plants, using a global dataset of traits for plant species within plant-pollinator networks.
-We show the importance of pollinators in mediating reproductive trait correlations and identify the need to consider broader plant reproductive strategies, rather than just flower morphology, to understand patterns of plant-pollinator interactions.
-Further, we provide empirical evidence of reproductive trait associations that complement trait covariation studies for other plant organs, highlighting the need to include reproductive traits in the global spectrum of plant form and function.
-Future work incorporating underrepresented areas of the world and additional relevant reproductive traits (e.g., flower life span and colour) from a broader range of life forms will be valuable for enhancing our understanding of the plant reproductive spectrum and associated plant-pollinator interactions.
-
-\newpage
-
-# References
-
-::: {#refs}
-:::

### 2023-04-13 Main_Figures/Other_figs/Analysis_1_Separated.Rmd
edits for final sub

--- 2021-08-02 Main_Figures/Analysis_1_Separated.Rmd
@@
 
-combined <- p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "right")
+combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
 combined + plot_layout(guides = "collect",ncol = 3)
 
+setwd("~/R_Projects/Reproductive Traits")
+
+saveRDS(p1,"Main_Figures/figure_2_1.rds")
+saveRDS(p2,"Main_Figures/figure_2_2.rds")
+saveRDS(p3,"Main_Figures/figure_2_3.rds")
+saveRDS(pp1,"Main_Figures/figure_2_4.rds")
+saveRDS(pp2,"Main_Figures/figure_2_5.rds")
+saveRDS(pp3,"Main_Figures/figure_2_6.rds")
+
 ```

### 2023-04-13 Main_Figures/Other_figs/Figure3.Rmd
edits for final sub

---
output:
  pdf_document: default
  html_document: default
classoption: landscape

---

\pagenumbering{gobble}

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27}

#LOAD LIBRARIES 
#library(phytools)
#library(ape) #for phylogenetic distance
#library(dplyr) #data processing
#library(rtrees) #for phylogenetic distancelibrary(MASS)
#library(reshape2)
library(viridis) #COLOUR GGPLOT
#library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(tidyverse)
library(patchwork) #panel of plots
library(brms)

#Load theme for publication

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2)),
           axis.text=element_text(size = rel(1.8), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.7)),
           legend.background=element_rect(fill="transparent"),
           legend.key = element_rect(size = 10),
           legend.key.size = unit(4.2, 'lines'),
           legend.box.margin=margin(20,20,20,20),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank(),
           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
           plot.margin = margin(1,1,1,1, unit = "cm"),
           plot.subtitle = element_text(face="bold",size=rel(2.5)),
           legend.spacing = unit(0.01, "cm")

     ))
}

#decimal places for ggplot

scaleFUN <- function(x) sprintf("%.1f", x)

#Prepare plot with presence absence and interaction frequency
#Plot nicely PC1
analysis_1 <- readRDS("../Data/Large_files/results_analysis_1_presence_absence.rds")
dat_analysis <- readRDS("../Data/Large_files/dat_analysis_results_analysis_presence_absence.rds")

ce_pc1 <- conditional_effects(analysis_1, effects = "PC1:guild",points=T)

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=guild)) + 
geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction, colour=guild),size = 2.5, alpha=0.15) + 
geom_line(aes(colour=guild, linetype=guild, size=guild))  + 
ylab("Interaction") + 
xlab(NULL) +
theme_ms() + 
theme(legend.position = "none") + 
scale_color_manual(name="Functional groups",values=c("orange", "limegreen", "black","#E7298A","cyan4","blueviolet"),  labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera","Non-syrphid-Diptera", "Syrphids")) + 
ggtitle("PC1", subtitle = "(a)") + 
scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes")) +
scale_linetype_manual(values=c("solid","twodash", "dotted", "longdash", "dashed", "dotdash"), labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphid-Diptera", "Syrphids"), name="Functional groups")+
scale_size_manual(values=c(1.75, 1.75, 1.5, 1.75, 1.75, 1.75), labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphid-Diptera", "Syrphids"), name="Functional groups")

ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:guild",points=T)

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=guild)) + geom_point(data = dat_analysis, aes(x = -PC2, y = Interaction, colour=guild),size = 2.5, alpha=0.15) + 
geom_line(aes(colour=guild, linetype=guild,  size=guild))  + 
ylab(NULL)+ 
xlab(NULL)+
theme_ms() + 
theme(legend.position = "none") + 
scale_color_manual(name="Functional groups",values=c("orange", "limegreen", "black","#E7298A",        "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids")) + 
ggtitle("PC2", subtitle = "(b)") + 
scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes")) +
scale_linetype_manual(values=c("solid","twodash", "dotted", "longdash", "dashed", "dotdash"), labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphid-Diptera", "Syrphids"), name="Functional groups")+
scale_size_manual(values=c(1.75, 1.75, 1.5, 1.75, 1.75, 1.75), labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphid-Diptera", "Syrphids"),name="Functional groups")

ce_pc3 <- conditional_effects(analysis_1, effects = "PC3:guild",points=T)

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__), group=guild)) + geom_point(data = dat_analysis, aes(x = -PC3, y = Interaction, colour=guild),size = 2.5, alpha=0.15) + 
geom_line(aes(colour=guild, linetype=guild, size=guild))  + ylab(NULL)+ xlab(NULL)+
theme_ms() +
theme(legend.position = "none") + 
scale_color_manual(name="Functional groups",values=c("orange", "limegreen", "black","#E7298A",            "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
        "Non-syrphid-Diptera", "Syrphids")) + 
ggtitle("PC3", subtitle = "(c)") + 
scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes")) +
scale_linetype_manual(values=c("solid","twodash", "dotted", "longdash", "dashed", "dotdash"), labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphid-Diptera", "Syrphids"), name="Functional groups")+
scale_size_manual(values=c(1.75, 1.75, 1.5, 1.75, 1.75, 1.75), labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphid-Diptera", "Syrphids"), name="Functional groups")

#Plot nicely PC1
analysis_1 <- readRDS("../Data/Large_files/results_analysis_1.rds")
dat_analysis <- readRDS("../Data/Large_files/dat_analysis_results_analysis_1.rds")
########################################################################################################################

########################################################################################################################
ce_pc1 <- conditional_effects(analysis_1, effects = "PC1:guild",points=T)

dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild)) + 
geom_point(data = dat_analysis, aes(x = -PC1, y = Interaction, colour=guild),size = 2.5, alpha=0.15) + 
geom_line(aes(colour=guild, linetype=guild, size=guild)) + 
coord_cartesian(ylim=c(1,100),clip="off") + 
ylab("Number of visits") +  
theme_ms() +
scale_color_manual(name="Functional groups",values=c("orange", "limegreen", "black","#E7298A",            "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
        "Non-syrphid-Diptera", "Syrphids")) +
scale_y_log10() +
ggtitle(NULL, subtitle = "(d)") +
annotate(geom = "text", x = -1.7, y =0.2 , label = "High flower N.", size = 8) +
annotate(geom = "text", x = -1.75, y =0.12 , label = "Small flowers", size = 8) + 
annotate(geom = "text", x = 1.8, y =0.2 , label = "Low flower N.", size = 8) + 
annotate(geom = "text", x = 1.8, y =0.12 , label = "Large flowers", size = 8) +
xlab("") +
annotate(geom = "text", x = -0.1, y =0.35 , label = "Flower number - Flower size axis", size = 8.5, fontface =2) + 
xlab("") + 
theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold"),panel.border=element_rect(color="black",size=1.2))  +
scale_linetype_manual(values=c("solid","twodash", "dotted", "longdash", "dashed", "dotdash"), labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphid-Diptera", "Syrphids"), name="Functional groups")+
scale_size_manual(values=c(1.75, 1.75, 1.5, 1.75, 1.75, 1.75), labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphid-Diptera", "Syrphids"), name="Functional groups")

#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:guild",points=T)

dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild)) + 
geom_point(data = dat_analysis, aes(x = -PC2, y = Interaction, colour=guild),size = 2.5, alpha=0.15) + 
geom_line(aes(colour=guild, linetype=guild, size=guild))+ 
coord_cartesian(ylim=c(1,100),clip="off") + 
ylab(NULL)  +
theme_ms() + 
scale_color_manual(name="Functional groups",values=c("orange", "limegreen", "black","#E7298A",            "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
        "Non-syrphid-Diptera", "Syrphids")) + scale_y_log10()+
ggtitle(NULL, subtitle = "(e)") +
annotate(geom = "text", x = -1.78, y =0.2 , label = "High aut. selfing", size = 8) +
annotate(geom = "text", x = -1.65, y =0.12 , label = "Small floral display", size = 8) + 
annotate(geom = "text", x = 1.665, y =0.2 , label = "Low aut. selfing", size = 8) + 
annotate(geom = "text", x = 1.85, y =0.12 , label = "Large floral display", size = 8) +
xlab("") +
annotate(geom = "text", x = -0.1, y =0.35 , label = "Autonomous selfing - Floral display axis", size = 8.5, fontface =2) +
theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold"), panel.border=element_rect(color="black",size=1.2)) +
scale_linetype_manual(values=c("solid","twodash", "dotted", "longdash", "dashed", "dotdash"), labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphid-Diptera", "Syrphids"), name="Functional groups")+
scale_size_manual(values=c(1.75, 1.75, 1.5, 1.75, 1.75, 1.75), labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphid-Diptera", "Syrphids"), name="Functional groups")

#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1, effects = "PC3:guild",points=T)

dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)

p3 <-  ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=guild)) + 
geom_point(data = dat_analysis, aes(x = -PC3, y = Interaction, colour=guild),size = 2.5, alpha=0.15) + 
geom_line(aes(colour=guild, linetype=guild, size=guild))+ 
coord_cartesian(ylim=c(1,100),clip="off") + 
ylab(NULL)  +
theme_ms() + 
scale_color_manual(name="Functional groups",values=c("orange", "limegreen", "black","#E7298A",            "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
        "Non-syrphid-Diptera", "Syrphids")) + scale_y_log10()+
ggtitle(NULL, subtitle = "(f)") +
annotate(geom = "text", x = -1.48, y =0.2 , label = "Short styles", size = 8) +
annotate(geom = "text", x = -1.25, y =0.12 , label = "Low aut. selfing", size = 8) + 
annotate(geom = "text", x = 2.24, y =0.2 , label = "Long styles", size = 8) + 
annotate(geom = "text", x = 2.5, y =0.12 , label = "High aut. selfing", size = 8) +
xlab(" \n \n  ")  +
  annotate(geom = "text", x = 0.25, y =0.35 , label = "Style length - Autonomous selfing axis", size = 8.5, fontface =2) +
theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold"), panel.border=element_rect(color="black",size=1.2)) +
scale_linetype_manual(values=c("solid","twodash", "dotted", "longdash", "dashed", "dotdash"), labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphid-Diptera", "Syrphids"), name="Functional groups")+
scale_size_manual(values=c(1.75, 1.75, 1.5, 1.75, 1.75, 1.75), labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera", "Non-syrphid-Diptera", "Syrphids"), name="Functional groups")

combined <- pp1 + pp2 + pp3 + p1 + p2 + p3  & theme(legend.position = "bottom") &  guides(color = guide_legend(override.aes = list(size=6.5), keywidth=1.8,
                 keyheight=0.1,
                 default.unit="inch"))

combined + plot_layout(guides = "collect",ncol = 3)

saveRDS(p1, "../Main_Figures/figure_3_1.rds")
saveRDS(p2, "../Main_Figures/figure_3_2.rds")
saveRDS(p3, "../Main_Figures/figure_3_3.rds")
saveRDS(pp1, "../Main_Figures/figure_3_4.rds")
saveRDS(pp2, "../Main_Figures/figure_3_5.rds")
saveRDS(pp3, "../Main_Figures/figure_3_6.rds")

```

### 2023-04-13 Main_Figures/Other_figs/Traits_Table.Rmd
edits for final sub

--- 2021-12-16 Main_Figures/Traits_Table.Rmd
@@
 Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
-           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")
+           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing")
 
@@
   kable_styling(full_width = F,font_size = 10) %>%
-  add_header_above(c("Quantitative traits" = 1,"Qualitative traits" = 2),bold=T)   %>% row_spec(0, bold=T)
+  add_header_above(c("Quantitative traits" = 1,"Qualitative traits" = 2),bold=T)   %>% row_spec(0:12, bold=T) %>% save_kable(file = "table_1.png",density = 700)
 

### 2023-04-13 Main_Figures/Table_1.Rmd
edits for final sub

--- 2023-03-02 Manuscript/Lanuza_et_al_2022.Rmd
@@
 ---
-
-```{=tex}
-\doublespacing
-\normalsize
-```
-
-# Abstract
-
-1.
-Globally, plants display enormous variation in life history strategies and trait combinations.
-However, evidence suggests that evolutionary and physiological constraints limit the number of plant ecological strategies.
-Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with pollinators.
-
-2. Here, using a global dataset of 18 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
-
-3.
-We show that over 50% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the negative correlation between autonomous selfing and floral display size.
-In addition, these reproductive axes were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
-However, reproductive axes explain a relatively small amount of variance in pollinator interactions highlighting the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
-
-4.
-Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping plant-pollinator interactions at a macro-ecological scale.
-These findings emphasise the importance of considering reproductive traits in the global spectrum of plant form and function, and the need to explore beyond floral morphological traits to broaden our understanding of plant-pollinator interactions.
-
-\textbf{Keywords:} life-history strategies \| plant reproductive traits \| plant-pollinator interactions
-
-```{=tex}
-\doublespacing
-\vspace{5mm}
-\normalsize
-```
-```{r setup, include=FALSE, cache=FALSE, message = FALSE}
-
-library("knitr")
-
-### Chunk options: see http://yihui.name/knitr/options/ ###
-## Text results
-opts_chunk$set(echo = FALSE, warning = TRUE, message = TRUE)
-
-## Code decoration
-opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)
-
-## Cache
-# opts_chunk$set(cache = 2, cache.path = "output/cache/")
-
-## Plots
-opts_chunk$set(fig.path = "output/figures/")
-
-```
-
-```{r knitcitations, cache = FALSE}
-library(knitcitations)
-cleanbib()   
-cite_options(citation_format = "pandoc")
-
-```
-
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.pos = 'H')
-```
-
-# 1. Introduction
-
-Flowering plants display an astonishing diversity of reproductive structures [@barrett2002; @schiestl2013] that shape their interactions with animal pollinators [@fenster2004; @dellinger2020].
-The variety of reproductive strategies used by different plant species, from specialised reliance on a single pollinator, to full self-pollination, is incredibly rich.
-However, not all combinations of reproductive traits (i.e., morphological and physiological traits that determine a plant’s ability to reproduce) are possible due to evolutionary and ecological constraints [@stearns1989; @agrawal2020].
-Despite recent advances in theoretical and empirical understanding of correlations between plant reproductive traits at large ecological scales [@salguero2016; @friedman2020; @paterno2020; @roddy2021; @song2022], studies typically focus on just a few traits, often in isolation.
-Thus, to develop a comprehensive understanding of the plant reproductive spectrum of trait variation, as done recently for root [@laughlin2021], leaf [@wright2004] and wood [@chave2009] related traits, we require a multi-trait perspective with broad geographical coverage.
-Importantly, characterization of the plant reproductive spectrum could reveal key reproductive strategies among different species [@agrawal2020] and improve knowledge of associations between specific reproductive traits and pollinators [@roddy2021].
-
-With the recent availability of large trait databases [e.g., TRY @kattge2011;  COMPADRE @salguero2015], there has been increased research on plant ecological strategies, which has produced identification of global patterns in plant form and function [@salguero2016; @diaz2016; @bruelheide2018; @carmona2021].
-However, studies that look at multiple traits tend to overlook plant reproductive traits [@evojtko2020; @ruger2018; @roddy2021], and focus on trait correlations in other plant organs such as morphological and physiological leaf traits [@wright2004; @shipley2006; @donovan2011; @osnas2013].
-Despite the lack of a holistic understanding that depicts reproductive trait covariation patterns, there are widely recognized associations between plant reproductive trait pairs such as the negative correlation between flower size and flower number [@sargent2007; @kettle2011; @vojtko2022]; the positive association between flower size and outcrossing rate [@goodwillie2010]; or the positive correlation between outcrossing rate and lifespan [@barrett2003; @munoz2016; @moeller2017].
-Although identification of these trait correlations has allowed progress toward a conceptual framework that integrates different floral trait relationships [@roddy2021], we still lack empirical understanding of how these associations among floral and other reproductive traits (e.g., reproductive biology) shape plant life history strategies.
-
-Trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] are powerful for exploring the underlying mechanisms driving plant-pollinator interactions.
-For example, plant traits can define species' network roles [e.g., specialists vs generalists @tur2013] and plant species that occupy reproductive trait space extremes are likely to be more specialised and display tighter trait-matching with pollinators [@junker2013; @coux2016].
-Indeed, the degree of morphological matching between plants and pollinators often determines whether or not interactions occur, and consequently influences  the broader network structure [@stang2009; @ibanez2012].
-However, it is still unclear how specific reproductive traits (e.g., mating or compatibility system) influence plant-pollinator associations [@sargent2008; @tur2013; @devaux2014].
-For example, species with high selfing rates may evolve to invest less in floral rewards resulting in a lower number of pollinator visits [@devaux2014].
-Indeed, both morphology and mating system can determine a species' functional role within pollination networks, and the combination of several traits increases power for predicting network structure [@eklof2013].
-Because the species position within the multidimensional trait space can result in different interaction patterns or adaptations to pollinators [see @dehling2016 for a purely morphological approach], the use of the reproductive trait space to explore plant-pollinator interactions could help to identify species functional roles and associations of traits with specific pollinators (i.e., pollination syndromes).
-
-Here, we explore the spectrum of reproductive traits in flowering plants, within a global set of plant-pollinator networks, to identify reproductive trait covariation and how this influences the network of interactions between plants and pollinators.
-First, we identify the major axes of reproductive trait variation and correlations among traits for plant species.
-Then, we investigate the associations between plant species’ positions in reproductive trait space and the strength of their interactions with different pollinator guilds within networks.
-Finally, we determine how the main axes of reproductive trait variation influence plant species' functional roles within pollination networks, using a range of complementary interaction network metrics.
-
-# 2. Methods
-
-## (a) Plant-pollinator network studies
-
-We selected 28 studies from 18 different countries that constituted a total of 64 plant-pollinator networks (see table S1 and figure S1).
-These studies recorded plant-pollinator interactions in natural systems and were selected so that we had broad geographical representation across different ecological communities.
-The pollinators documented by these studies are primarily insect pollinators (97.8% of the total visits recorded) and the plants are characterised by a clear dominance of smaller life forms (i.e., 61% of herbs, 28% of shrubs and 11% of trees).
-Although these studies differ in sampling effort and methodology, all studies provided information about plant-pollinator interactions (weighted and non-weighted), which we used to build a database of plant species that are likely to benefit, to some degree, from animal pollination.
-Many of these networks are freely available either as published studies [e.g., @carvalheiro2014; @olesen2007; @fortuna2010] or in online archives [e.g., Mangal @poisot2016;  The Web of Life @fortuna2010].
-In total, our network dataset constituted 60 weighted (number of visits) and 4 unweighted (interaction presence-absence) networks, each sampled at a unique location and year, as well as 8 meta-networks where interactions were pooled across several locations and multiple years.
-
-## (b) Taxonomy of plants and pollinators
-
-All species names, genera, families and orders were retrieved and standardised from the taxonomy data sources NCBI (<https://www.ncbi.nlm.nih.gov/taxonomy>) for plants and ITIS (<https://www.itis.gov/>) for pollinators, using the R package *taxize* [@chamberlain2020].
-We filled the 'not found' searches manually using <http://www.theplantlist.org/> and <http://www.mobot.org/> for plants and <http://www.catalogueoflife.org/> for pollinators.
-
-## (c) Plant traits
-
-We selected a total of 18 quantitative and categorical functional traits that included reproductive traits and traits related with plant form and size (see table 1).
-Reproductive traits consisted of those related to floral and reproductive biology: (i) floral traits included those related to the size of floral organs (e.g., style length), floral display size (e.g., flower number) and floral rewards (e.g., pollen quantity), while (ii) reproductive biology traits represented the plant reproductive system (i.e., the breeding, mating and compatibility system).
-The remaining traits were related to plant size and form (i.e., plant height, lifespan and life form), which are commonly used to characterise the fast-slow continuum of plant trait variation [@salguero2016].
-For each plant species, we undertook an extensive literature and online search for all traits across a wide range of resources (plant databases, online floras, books, journals and images).
-From a matrix comprising a total of 27,108 possible cells (considering all traits and plant species: 18 columns × 1,506 species), we were able to fill 22,796 cells (84.1% of the dataset, see figure S2 for missing value information for each trait).
-An extended description of each trait and how it was obtained can be found in Appendix S1.
 
@@
 \doublespacing
-
-## (d) Phylogenetic Distance
-
-We calculated the phylogenetic distance between all plant species considered using the function *get_tree* from the package *rtrees* (<https://github.com/daijiang/rtrees>), which downloads phylogenetic distances from the extended R implementation of the Open Tree of Life [@smith2018; @jin2019].
-
-## (e) Data Imputation
-
-To avoid excluding species with missing trait data, we imputed missing values with the help of the function *missForest* [@stekhoven2012] which allows imputation of datasets with continuous and categorical variables.
-We accounted for the phylogenetic distance among species on the imputation process by including the eigenvectors from principal component analysis of the phylogenetic distance (PCoA), which has been shown to improve the performance of *missForest* [@penone2014].
-To extract the eigenvectors, we used the function *PVRdecomp* from the package *PVR* [@santos2018] based on a previous conceptual framework that considers phylogenetic eigenvectors [@diniz-filho2012].
-We conducted two different imputations, one for the full set of species (1,506 species: 5.79% of missing values), and excluding nectar and pollen traits because of the high percentage of missing values (figure S2), and a second one for the subset of species with data for pollen per flower and microliters of nectar (755 species: 8.01% of missing values).
-To corroborate that our imputation of missing values did not affect our results, we evaluated the reproductive spectrum (see section below) with and without imputed values and results for the two datasets were consistent (Fig S3 and Fig S4).
-
-## (f) Plant strategies analysis
-
-We explored the association between the different quantitative plant traits using a phylogenetically informed Principal Component Analysis (pPCA).
-We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasise flower size on the spectrum of trait variation.
-Prior to the analyses, we excluded outliers and standardised the data.
-Specifically, due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species.
-Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis [@legendre2012].
-Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated their position in the trait space and the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test.
-Similarly, we also explored for each pollinator guild (see "Visitation patterns" subsection below) the position in the trait space of the plants that interacted with them.
-We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode “covariance” because values for each variables were on the same scale following transformation [@abdi2010].
-Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity data.
-For this, we included all quantitative traits included in the main pPCA, plus pollen grains and microlitres of nectar per flower.
-
-## (g) Phylogenetic signal
-
-We calculated the phylogenetic signal of the different quantitative traits on the imputed dataset with the full set of species (N = 1,506) with the package *phytools* [@revell2012] and used Pagel's $\lambda$ as a measurement of the phylogenetic signal.
-However, for pollen and nectar traits, phylogenetic signal was calculated only on the subset of species that had quantitative information for these traits (N = 755).
-
-## (h) Network analyses
-
-### (i) Visitation patterns
-
-We used Bayesian modelling (see details below) to investigate how the different guilds of pollinators interacted along the main axes of reproductive trait variation using qualitative and quantitative measures of plant-pollinator interactions.
-Specifically, interactions between plants and pollinators in binary networks were defined as the presence or absence of floral visitation, while in weighted networks, interactions were measured as the the number of visits from each insect species to different plant species.
-Although floral visitors are not always pollinators and the number of visits does not consider the pollination efficiency of each species [@ballantyne2015], the number of visits does provide valuable information about the relative contributions different floral visitors make to pollination [@vazquez2005; @vazquez2012].
-Therefore, despite the fact that we do not evaluate pollinator effectiveness we refer to the different floral visitors as pollinators.
-
-We divided pollinators into six main taxonomical guilds that differ in life form, behaviour and thus likely play different ecological roles: (i) bees (Hymenoptera-Anthophila), (ii) non-bee-Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Diptera-Syrphidae), (iv) non-syrphid-Diptera (Diptera-non-Syrphidae), (v) Lepidoptera, and (vi) Coleoptera.
-Note that we excluded non-insect pollinators from our analyses as they comprised only a 2.2% of the total visits recorded in our set of studies.
-Moreover, because bees had the greatest number of occurrences in networks  (2,256 records) and the highest frequency of visits, we further broke this group down into the main bee families (Andrenidae, Apidae, Colletidae, Halictidae, and Megachilidae).
-In addition, we found that *Apis mellifera* was the pollinator with the largest proportion of occurrences in networks (7.55% of the total).
-This is consistent with previous research showing that *A.
-mellifera* was the most frequent pollinator in a similar dataset of 80 plant-pollinator networks in natural ecosystems [@hung2018].
-Hence, to control for the effect of *A.
-mellifera* on observed visitation patterns of bees, we conducted an analogous analysis with presence-absence of the interaction and number of visits excluding *A.
-mellifera*.
-We found that *A.
-mellifera*, was partly driving some of the observed trends on PC1 (figure S5).
-However, we did not detect major differences on PC2 and PC3.
-
-We used Bayesian generalised linear mixed models in the R package *brms* [@burkner2017] to model the presence-absence of observed interactions and number of visits as a function of the main axes of plant trait variation (i.e., PC) and their interactions with pollinator guilds (i.e., PGs; e.g., number of visits \~ PC1 x PGs + PC2 x PGs + PC3 x PGs).
-Because we were interested in possible differences in visitation patterns among pollinator guilds to plants with different reproductive strategies, we included interactions between the main axes of trait variation (PC1, PC2 and PC3) and the different pollinator guilds in the model.
-We added a nested random effect of networks within the study system to capture the variation in networks among studies and within networks.
-Moreover, we included the phylogenetic covariance matrix as a random factor due to the possible shared evolutionary histories of species and therefore lack of independence among them.
-We specified for the presence or absence of an interaction and number of visits with Bernoulli and a zero inflated negative binomial distributions, respectively.
-The models were run with 3,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results [@burkner2017].
-We set delta ($\Delta$) to 0.99 to avoid divergent transitions and visualised the posterior predictive checks with the function *pp_check* using the *bayesplot* package [@gabry2019].
-
-### (ii) Plant species network roles
-
-We also used Bayesian modelling to investigate how the main axes of trait variation determined different plant species' functional roles within pollination networks.
-For this, we selected complementary species-level network metrics, commonly applied in bipartite network studies [@dormann2008], with clear ecological interpretations and are relevant for defining species' functional roles in networks.
-Specifically, the species-level metrics we included were: (i) sum of visits per plant species; (ii) normalised degree, calculated as the number of links per plant species divided by the total possible number of partners; and (iii) selectivity (d') [@bluthgen2006], which measures the deviation of an expected random choice of the available interaction partners and ranges between 0 (maximum generalisation) and 1 (maximum specialisation).
-Normalised degree and selectivity were calculated with the *specieslevel* function in the R package *bipartite* [@dormann2008].
-We modelled each plant species metric (sum of visits, normalised degree and plant selectivity) as a function of the three main axes of trait variation (plant species level metric \~ PC1 + PC2 + PC3).
-For the different response variables in each model (i.e., each plant species level metric), we used different distribution families (zero inflated negative binomial for the sum of visits, weibull for normalised degree, and zero-one inflated beta for selectivity).
-Finally, we used the same random factors, model settings and conducted the same posterior predictive checks for each model as detailed above in the 'visitation patterns' section.
-
-Our analyses were conducted on the subset of 60 weighted networks (out of a total of 64 networks) sampled in a unique flowering season and site, which included 556 plant and 1,126 pollinator species.
-In total, our network dataset (excluding meta- and non-weighted networks) included 2,256 interactions for bees, 1,768 for non-syrphid-dipterans, 845 for syrphids, 437 for lepidopterans, 432 for coleopterans, and 362 for non-bee-hymenopterans.
-Sampling methods varied across studies but this was accounted for in analyses by including study identity as a  random effect in our models.
-All analyses were conducted in R version *4.0.3*.
-
-# 3. Results
-
-## (a) Plant strategies analysis
-
-Our phylogenetically informed principal component analysis captured  51.8% and 70.97% of the reproductive trait variation in the first two and three axes, respectively (figure 1 and figure S6).
-The first principal component (PC1; the flower number - flower size axis) represented 26.72% of the trait variation and indicated a negative correlation between flower number and flower size.
-The main contributing traits to PC1 were plant height, flower number, ovule number and flower size (loadings \> \|0.5\|; table S3) but style length also contributed moderately (loading = -0.33).
-One end of this axis comprised species with high investment in flower number and plant height but small flower size, short style length and low ovule number.
-For instance, *Cornus florida* occurred at this end of the spectrum, which, on average, has approximately 10,000 flowers, is 7.5 m high, has flowers that are 3 mm wide, styles 3.5 mm long and  two ovules per flower.
-The other end of this spectrum had species that were short in height, with few large flowers that had long styles and many ovules.
-For example, *Petunia axillaris* on average, is 0.5 m high and has approximately 10 flowers per plant that are over 50 mm wide with 25 mm long styles and over 200 ovules.
-The second principal component (PC2; the autonomous selfing - floral display axis) encompassed 25.05% of the trait variation and represented variation from low to high autonomous selfing (i.e., high to low pollinator dependence).
-The main driver of trait variation on PC2 was autonomous selfing (loading = 0.85) but all other traits (except ovule number) made moderate contributions (loadings ranging between 0.27 to 0.4; table S3).
-Generally speaking, species with low autonomous selfing had larger and many flowers with long styles, and were tall.
-*Zuccagnia punctata* occurred at this extreme of the spectrum, which is a self-incompatible species, completely dependent on animal pollination for seed production, producing  approximately 1,500 flowers per plant with an average height of 3 m and 20 mm long styles.
-In contrast, species with high autonomous selfing tended to have fewer and smaller flowers with shorter styles, and were shorter in height.
-*Veronica peregrina* occurred at this end of the spectrum, and is a self-compatible plant that requires little or no pollination by animals, it has approximately 20 flowers per plant, is 0.2 m high and has 0.25 mm long styles.
-The third principal component (PC3; the style length - autonomous selfing axis) explained a considerable amount of trait variability (19.17%) and represented a positive correlation between style length (loading = -0.66) and autonomous selfing (loading = \|-0.51\|), where species with short styles had low autonomous selfing and species with long styles high autonomous selfing.
-The remaining traits, apart from ovule number, were all positively correlated with style length and autonomous selfing (loadings from -0.23 to -0.46; table S3).
-In addition, the pPCA with the subset of species that we had nectar and pollen quantity data for showed that nectar quantity (microlitres of nectar per flower) and pollen grains per flower were positively associated with floral display size.
-Floral rewards were particularly strongly correlated with flower size but weakly correlated with flower number (figure S4).
-The first two principal components for this pPCA explained similar variance  (45.52%) and similar associations of traits, despite some variability in the loadings (table S4).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="85%", fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
-The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
-The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation.
-The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}
-
-#Load libraries
-library(viridis) #COLOUR GGPLOT
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(magick)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("../Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("../Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#Images were made by Paula Martin
-#Check her work on https://paulamartinart.com/
-
-tree <- image_read("../Images/PPCA_Plot/Tree.png")
-tree_1 <- as.raster(tree)
-
-style_l <- image_read("../Images/PPCA_Plot/Style_Long.png")
-style_l_1 <- as.raster(style_l)
-
-style_s <- image_read("../Images/PPCA_Plot/Style_Short.png")
-style_s_1 <- as.raster(style_s)
-
-ovule_h <- image_read("../Images/PPCA_Plot/Ovule_High.png")
-ovule_h_1 <- as.raster(ovule_h)
-
-ovule_l <- image_read("../Images/PPCA_Plot/Ovule_Low.png")
-ovule_l_1 <- as.raster(ovule_l)
-
-selfing_n <- image_read("../Images/PPCA_Plot/Selfing_None.png")
-selfing_n_1 <- as.raster(selfing_n)
-
-selfing_h <- image_read("../Images/PPCA_Plot/selfing.png")
-selfing_h_1 <- as.raster(selfing_h)
-
-single_flower <- image_read("../Images/PPCA_Plot/Single_Flower.png")
-single_flower_1 <- as.raster(single_flower)
-
-many_flowers <- image_read("../Images/PPCA_Plot/Inflorescencia.png")
-many_flowers_1 <- as.raster(many_flowers)
-#many_flowers_1 <- image_rotate(many_flowers, 45)
-
-large_flower <- image_read("../Images/PPCA_Plot/flower_big.png")
-large_flower_1 <- as.raster(large_flower)
-
-#"Images/PPCA_Plot/flower_short.png"
-flower_small <- image_read("../Images/PPCA_Plot/flower_big.png")
-flower_small_1 <- as.raster(flower_small)
-
-herb <- image_read("../Images/PPCA_Plot/herb.png")
-herb_1 <- as.raster(herb)
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Autonomous selfing - Floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
-    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
-    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
-    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.18, xmax = 4.13,ymin = 1.3, ymax = 2.4) +
-    annotation_raster(flower_small_1, xmin = -3.21, xmax = -2.81,ymin = -2, ymax = -1.45) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
-
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
-                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-plot_grid(all_spp(PC))
-
-```
-
-As expected, due to individual trait correlations between qualitative and quantitative traits (e.g., life form and plant height), we found that most categorical traits were clustered on the trait space and statistically associated with the first two axes of trait variation (figure s2 and table s2).
-However, the position of plants connected to each of the pollinator guilds was scattered without clear aggregation patterns on the trait space (figure s7; but see "Visitation patterns" section below for detailed results from quantitative analyses).
-Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed a lack of statistical association.
-In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S8).
-Regarding self-compatibility, we found larger differences on PC2.
-For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S8a and figure S8b; Tukey test *P* \< 0.05).
-Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S8c and figure S8d; Tukey test *P* \< 0.05).
-Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S8e and figure S8f; Tukey test *P* \< 0.05).
-Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S8g and figure S8h; Tukey test *P* \< 0.05).
-Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S8i and figure S8j; Tukey test *P* \< 0.05).
-Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S8k and figure S8l; Tukey test *P* \< 0.05).
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="80%",fig.align='center',fig.cap= "\\textbf{Figure 2.} Location of the different qualitative traits in the trait space.
-The figure panel is composed of the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
-The solid arrows indicate the direction of variation of the different quantitative traits shown in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S)."}
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(ggstar)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.6)),
-            axis.text=element_text(size = rel(1.6), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(size = rel(1.1)),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.4, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank(),
-            plot.title = element_text(size = rel(2.5), face="bold")
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("../Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
-phyl_pca_forest <- readRDS("../Data/RData/phyl_pca_forest.rds")
-
-#CALL the output PC for simplicity
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-Compatibility <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Compatibility <- dat_cleaning_5$Compatibility_system
-  dat$Compatibility <- as.character(dat$Compatibility)
-  dat$Compatibility[dat$Compatibility=="dioecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="monoecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-  dat$Compatibility[dat$Compatibility=="self_compatible"] <- "Self compatible"
-  dat$Compatibility[dat$Compatibility=="self_incompatible"] <- "Self incompatible"
-  dat$Compatibility <- factor(dat$Compatibility, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=Compatibility, fill=Compatibility), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("deepskyblue2", "purple2","goldenrod","gray7")) +
-scale_starshape_manual(values = c(13, 15, 28, 5))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)  + ylab("Autonomous selfing - Floral display axis")
-
-  plot
-
-}
-
-#Compatibility(PC)
-
-#############################################################################################################################################################
-#Life form
-#############################################################################################################################################################
-#Load plots
-Life_form <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Life form` <- dat_cleaning_5$life_form
-  dat$`Life form` <- as.character(dat$`Life form`)
-  dat$`Life form`[dat$`Life form`=="herb"] <- "Herb"
-  dat$`Life form`[dat$`Life form`=="shrub"] <- "Shrub"
-  dat$`Life form`[dat$`Life form`=="tree"] <- "Tree"
-  dat$`Life form`[dat$`Life form`=="vine"] <- "Shrub"
-
-  dat$`Life form` <- factor( dat$`Life form`, levels = c("Herb", "Shrub", "Tree"))
-
-plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Life form`, fill=`Life form`), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("forestgreen", "darkorange2","black")) +
-scale_starshape_manual(values = c(13, 15, 28))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.090, 0.115)) + ggtitle("(b)") +
-    xlab(NULL) + ylab(NULL)
-
-  plot
-
-}
-
-#Life_form(PC)
-
-#############################################################################################################################################################
-#Life span
-#############################################################################################################################################################
-#Load plots
-Life_span <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-    dat$Lifespan <- dat_cleaning_5$lifespan
-    dat$Lifespan <- as.character(dat$Lifespan)
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=Lifespan, fill=Lifespan), size=2.25, color= NA, alpha = 0.9)+ scale_fill_manual(values=c("sienna4","forestgreen")) +
-scale_starshape_manual(values = c(13, 15))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.12, 0.1)) + ggtitle("(c)") +
-    xlab(NULL) + ylab(NULL)
-
-  plot
-
-}
-
-#Life_span(PC)
-
-#############################################################################################################################################################
-#Flower symmetry
-#############################################################################################################################################################
-#Load plots
-Flower_sym <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower symmetry` <- dat_cleaning_5$Flower_symmetry
-  dat$`Flower symmetry` <- as.character(dat$`Flower symmetry`)
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Flower symmetry`, fill=`Flower symmetry`), size=2.25, color= NA, alpha = 0.9) + scale_fill_manual(values=c("goldenrod","purple2")) +
-scale_starshape_manual(values = c(13, 15))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL) + xlab("Flower number - Flower size axis")
-
-  plot
-
-}
-
-#Flower_sym(PC)
-
-#############################################################################################################################################################
-#Flower shape
-#############################################################################################################################################################
-#Load plots
-Flower_sha <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower shape` <- dat_cleaning_5$Flower_morphology
-  dat$`Flower shape` <- as.character(dat$`Flower shape`)
-  dat$`Flower shape`[dat$`Flower shape`=="Funnelform"] <- "Campanulate"
-  dat$`Flower shape`[dat$`Flower shape`=="Spike"] <- "Brush"
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Flower shape`, fill=`Flower shape`), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("black","goldenrod", "deepskyblue2","forestgreen","purple2","darkorange2")) +
-scale_starshape_manual(values = c(13, 15, 28, 5, 9, 14))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL) + xlab("Flower number - Flower size axis")
-
-  plot
-
-}
-
-#Flower_sha(PC)
-
-#############################################################################################################################################################
-#Breeding system
-#############################################################################################################################################################
-#Load plots
-Breeding_syst <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Breeding system` <- dat_cleaning_5$Breeding_system
-  dat$`Breeding system` <- as.character(dat$`Breeding system`)
-  dat$`Breeding system` <- factor(dat$`Breeding system`, levels=c("Hermaphrodite","Monoecious" ,"Dioecious"))
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Breeding system`, fill=`Breeding system`), size=2.25, color= NA, alpha = 0.9) + scale_fill_manual(values=c("forestgreen","darkorange2", "black")) +
-scale_starshape_manual(values = c(13, 15, 28))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("(d)") +
-    xlab("Flower number - Flower size axis") +
-    ylab("Autonomous selfing - Floral display axis")
-
-  plot
-
-}
-
-#Breeding_syst(PC)
-
-#############################################################################################################################################################
-#Nectar
-#############################################################################################################################################################
-#Load plots
-#Nectar <- function(PC, x="PC1", y="PC2") {
-#  # PC being a prcomp object
-#  data <- data.frame(PC$S)
-#  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-#  dat <- data.frame(x = data[,x], y = data[,y])
-#  
-#  #######
-#  #DENSITY FUNCTION
-#  #######
-#  get_density <- function(x, y, ...) {
-#    dens <- MASS::kde2d(x, y, ...)
-#    ix <- findInterval(x, dens$x)
-#    iy <- findInterval(y, dens$y)
-#    ii <- cbind(ix, iy)
-#    return(dens$z[ii])
-#  }
-#  
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-#  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-#  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-#  plot <- plot + geom_point(data=dat, aes(-x, -y, #colour=Nectar),size=1.75)+scale_color_manual(values=c("black","grey"))
-#  
-#  ########
-#  #ADD ARROWS 
-#  ########
-#  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-#  mult <- min(
-#    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-#    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-#  )
-#  datapc <- transform(datapc,
-#                      v1 = .75 * mult * (get(x)),
-#                      v2 = .75 * mult * (get(y))
-#  )
-#  # add arrows
-#  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, #yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-#  
-#  #Add axis with perctentage
-#  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-#
-#  
-#  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, #arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-#  
-#  #ADD LABELS
-#  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-#  
-#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-#  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = #-(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-#                          label = PCAloadings$Variables, color="black",size=3)
-#  
-#  #CHANGE THEME
-#  #CHANGE THEME
-#  
-#  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)") 
-#  
-#  plot
-#  
-#}
-#
-# #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")
-
-  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),ncol=3,nrow=2,  align = "hv")
-
-```
-
-\elandscape
-
-## (b) Phylogenetic signal
-
-We found a strong phylogenetic signal (*P* \< 0.01) for most quantitative traits (table S5).
-The traits that showed the highest phylogenetic signal were ovule number ($\lambda$ = 1), pollen grains per flower ($\lambda$ = 1) and plant height ($\lambda$ = 0.96), followed by flower length ($\lambda$ = 0.75), flower width ($\lambda$ = 0.73) and number of flowers per plant ($\lambda$ = 0.69).
-The traits that had a moderate phylogenetic signal included inflorescence width ($\lambda$ = 0.57), style length ($\lambda$ = 0.49) and autonomous selfing ($\lambda$ = 0.34).
-Finally, microliters of nectar per flower showed the lowest phylogenetic signal of all the traits we measured ($\lambda$ = 0.14).
-
-## (c) Visitation patterns
-
-The main axes of trait variation (PC1, PC2 and PC3) partly explained the presence-absence of interaction partners (conditional $R^{2}$ = 0.26; marginal $R^{2}$ = 0.20) but little of the total number of visits (conditional $R^{2}$ = 0.31; marginal $R^{2}$ = 0.06).
-However, we found relevant differences across the different pollinator guilds for both the presence-absence of interactions and number of visits (figure 3).
-On the flower number - flower size axis, we found  that plants with many small flowers tended to have interaction partners that were Coleoptera, non-bee-Hymenoptera and Diptera (figure 3a), whereas plants with few large flowers mostly had interaction partners that were bees and Lepidoptera.
-We found similar trends for visitation rates on the flower number - flower size axis,  but bees and syrphids visited plant species with many small flowers more frequently (figure 3d).
-On the autonomous selfing - floral display axis, we found that all plant species with lower autonomous selfing had many interaction partners and received many visits from all pollinator guilds (figure 3b and figure 3e).
-Finally, on the style length - autonomous selfing axis, plant species with short styles and low autonomous selfing had more interaction partners for all guilds, except bees which interacted more frequently with plant species with long styles and high autonomous selfing (figure 3c).
-Plants with long styles and high autonomous selfing interacted more frequently with Lepidoptera and non-bee-Hymenoptera (figure 3f).
-
-The additional models for the most represented bee families, for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and the number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03), showed that the Apidae family was the main driver of the observed patterns.
-The contrast between interaction presence/absence  and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S9).
-
-```{=tex}
-\vspace{5mm}
-\blandscape
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different pollinator guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
-PC1 represents the flower number - flower size axis, PC2 represents the autonomous selfing - floral display axis and PC3 represents the style length - autonomous selfing axis.
-For visualization purposes due to large differences between number of visits from bees and the rest of the pollinator guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
-
-#LOAD LIBRARIES 
-#library(phytools)
-#library(ape) #for phylogenetic distance
-#library(dplyr) #data processing
-#library(rtrees) #for phylogenetic distancelibrary(MASS)
-#library(reshape2)
-library(viridis) #COLOUR GGPLOT
-#library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-#library(tidyverse)
-library(patchwork) #panel of plots
-#library(brms)
-#library(cmdstanr)
-
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2)),
-           axis.text=element_text(size = rel(1.8), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(2, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
-           plot.subtitle = element_text(face="bold",size=rel(2))
-     ))
-}
-
-p1 <- readRDS("../Main_Figures/figure_3_1.rds")
-p2 <- readRDS("../Main_Figures/figure_3_2.rds")
-p3 <- readRDS("../Main_Figures/figure_3_3.rds")
-pp1 <- readRDS("../Main_Figures/figure_3_4.rds")
-pp2 <- readRDS("../Main_Figures/figure_3_5.rds")
-pp3 <- readRDS("../Main_Figures/figure_3_6.rds")
-
-library(patchwork)
-
-combined <- pp1 + pp2 + pp3 + p1 + p2 + p3  & theme(legend.position = "bottom") &  guides(color = guide_legend(override.aes = list(size=6.5), keywidth=1.8,
-                 keyheight=0.1,
-                 default.unit="inch"))
-
-combined + plot_layout(guides = "collect",ncol = 3)
-```
-
-\elandscape
-
-## (d) Plant species network roles
-
-Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S10; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalised degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, selectivity \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03).
-Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and selectivity.
-On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S10a).
-However, selectivity (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S10g).
-On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S10c).
-Again, selectivity showed the opposite trend to the number of visits (figure S10i).
-
-# 4. Discussion
-
-We found strong covariation among traits within the flowering plant reproductive spectrum, which shapes interactions with pollinators at a global scale.
-Despite the enormous variability in plant reproductive structures, the first two and three axes captured over 50% and 70% of trait variation, respectively, and these axes encapsulated correlations among flower number and flower size, autonomous selfing and floral display, and style length and autonomous selfing.
-Although explained trait variation on the first two axes was less than previous studies of morphological and physiological traits [@diaz2016; @carmona2021], our results align with the two largest and most recent studies of plant life strategies that included reproductive, form and size related traits [@salguero2016; @vojtko2022].
-The different plant reproductive axes that we identified were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
-However, the unexplained variability found highlights the need to account for other local factors, such as species relative abundances [@bartomeus2016], along with reproductive traits, to better explain plant-pollinator associations.
-
-Our study provides strong evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1,200 species).
-Specifically, by using a multitrait approach, we are able to link the reproductive spectrum of plant trait variation with the previously described “fast-slow continuum” in plant [@salguero2016] and animal [@healy2019] life-history strategies.
-This fast-slow continuum was illustrated by the associations between reproductive traits and plant height, life form and lifespan traits.
-For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred Angiosperm species and generally lacking a multitrait perspective.
-We found support for this trait association and show that other reproductive traits (e.g., style length or ovule number) covary along this flower number - flower size axis.
-Our study also complements previous work linking plant breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers also have woody life forms and many flowers.
-Moreover, we identify the previously documented positive association between outcrossing rate and floral display size [@goodwillie2010], where species with low autonomous selfing levels also allocate large resource quantities to attract pollinators.
-
-Although we did not include floral rewards in our main analysis due to insufficient data, we did find that plant species with large floral displays and, in particular, large flowers, tended to have higher pollen and nectar quantity.
-Thus, we demonstrate that globally, reproductive trait covariation in flowering plants likely imposes constraints on the broader spectrum of plant trait variation.
-
-Overall, the main plant reproductive axes were insufficient to fully capture plant-pollinator associations.
-However, these axes helped explain, to some extent, interaction patterns among and within pollinator guilds, indicating that they partly mediate these associations across large spatial scales.
-For example, we found that all pollinator guilds interacted more frequently with species with large floral displays and low ability to self pollinate, which aligns with previous findings [@hegland2005; @lazaro2013; @kaiser2014] and predictions from evolutionary life-history theory [@stebbins1970].
-These predictions suggest that larger investment in floral display and rewards to attract pollinators occurs when dependence on pollinators is high.
-Although pollinators play a major role in shaping plant reproductive strategies, these different strategies are also constrained by the cost of reproductive organs and trait correlations [@galen1999].
-For instance, smaller flowers tend to receive fewer visits than larger flowers, but small flowers are inexpensive to produce (e.g., have few ovules).
-Therefore, low  per-flower visitation can be compensated by overall plant-level visitation through producing many small flowers that develop into numerous small fruits [@kettle2011].
-Our results also indicate that bees interact more with plants that have higher levels of autonomous selfing and large styles, which can help with a more efficient pollen transfer and prevent pollen competition [@ashman2013; @tong2016; @lanuza2021].
-Similarly, the specialised floral structures of zygomorphic flowers promote precise pollen transfer [@sargent2004; @gong2009], although we found that they were associated with high levels of autogamy.
-The annual herb _Lathyrus clymenum_ is a clear example of this pollinator specialization - selfing strategy that may get “the best of both worlds” [@lloyd1992; @goodwillie2018].
-It has showy zygomorphic flowers with relatively long styles and few ovules per flower that are likely fertilised with a single legitimate floral visit but can avoid reproductive failure in the absence of pollinators through autonomous self pollination.
-Our findings are consistent with the hypothesis that selfing is not rare within specialised pollination systems [@fenster2007] and emphasise the need to consider different reproductive assurance mechanisms [e.g., early versus delayed selfing\; @goodwillie2018] to better understand plant reproductive trait correlations and plant-pollinator interactions.
-
-Because flowering plants can adapt to their animal pollinators to optimise pollen transfer, the correlation between distinct suites of plant reproductive traits and pollinator guilds could indicate the existence of pollination syndromes [@fenster2004; @faegri2013; @rosas2014; @dellinger2020].
-However, our work shows a weak association between the different plant reproductive strategies and pollinator guilds, which supports previous findings from a similar pollinator guild classification and spatial scale [@ollerton2009].
-Although our findings contrast with a vast amount of literature on pollinator syndromes dating back over half a century [@faegri2013; @fenster2004], the ecological scale of our study differs from the majority of floral syndrome studies that rarely consider plant-pollinator associations beyond the community scale [ca.
-3% of studies\; @dellinger2020].
-We argue that the predictive power of floral syndromes gets blurred when increasing the number of species and scale, reinforcing the view that strong specialisation may be the exception rather than the norm in plant-pollinator interactions [@jordano1987; @waser1996].
-Further, there are several factors that might have influenced our findings, (e.g., the suite of reproductive traits and type of pollinator guilds we included).
-For instance, including other key reproductive traits, such as floral scent or flower colour, could help to improve predictions of plant-pollinator interactions.
-In addition, our use of broad taxonomic pollinator guild groupings may have obscured  finer scale patterns that occur at lower taxonomic ranks (e.g., genus or species level).
-The fact that our study only accounts for insect pollinators may have also influenced the observed associations between floral traits and pollinator guilds in comparison with other studies, as some other guilds (e.g., hummingbirds or bats) generally display strong trait-matching [@wilson2004; @lagomarsino2017].
-Regardless, it is worth noting that local factors (e.g., species relative abundances, phenologies or intraspecific variation) likely contribute to the variability in interactions between the plant reproductive spectrum and pollinators [@vazquez2007; @encinas2012; @bartomeus2016; @arroyo2023].
-We suggest that while plant reproductive traits do influence which pollinators they interact with, at a macroecological scale, pollination syndromes possibly take the form of a multifaceted, context dependent continuum [e.g., ornithophilous versus entomophilous pollination of red flowers\; @leon2022].
-
-Our study provides a comprehensive assessment of  reproductive trait covariation patterns in flowering plants, using a global dataset of traits for plant species within plant-pollinator networks.
-We show the importance of pollinators in mediating reproductive trait correlations and identify the need to consider broader plant reproductive strategies, rather than just flower morphology, to understand patterns of plant-pollinator interactions.
-Further, we provide empirical evidence of reproductive trait associations that complement trait covariation studies for other plant organs, highlighting the need to include reproductive traits in the global spectrum of plant form and function.
-Future work incorporating underrepresented areas of the world and additional relevant reproductive traits (e.g., flower life span and colour) from a broader range of life forms will be valuable for enhancing our understanding of the plant reproductive spectrum and associated plant-pollinator interactions.
-
-\newpage
-
-# References
-
-::: {#refs}
-:::

### 2023-04-13 Manuscript/Main_text_word.Rmd
edits for final sub

--- 2023-03-02 Manuscript/Lanuza_et_al_2022.Rmd
@@
 ---
-title: \singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shape their interactions with pollinators
-
-#author: 
-#  - Jose B. Lanuza^1,2^*
-#  - Romina Rader^1^
-#  - Jamie Stavert^3^
-#  - Liam K. Kendall^4^
-#  - Manu E. Saunders^1^
-#  - Ignasi Bartomeus^2^
-
-# may use lua filters for affiliations etc: see https://stackoverflow.com/a/52919256
-
-# date: '`r Sys.Date()`'
-
+title: "\\singlespacing \\vspace{-1.6cm} \\LARGE Covariation among reproductive traits
+  in flowering plants shape their interactions with pollinators"
 output:
-  bookdown::pdf_document2:
-    fig_caption: yes
-    fig_width: 7
-    fig_height: 7
-    df_print: kable
-    keep_tex: yes
-    number_sections: no
-    extra_dependencies: ["float"]
-    toc: no
-    fig_crop: no
-    includes:
-      in_header: header.tex
-
-documentclass: article
-# classoption: twocolumn, landscape, etc
-papersize: a4
-pagestyle: plain  # plain, empty, headings
-geometry: margin=1in
-linestretch: 2
-fontfamily: mathpazo
-fontsize: 12pt
-
+  word_document: default
+  html_document: default
+date: "2023-04-13"
 bibliography:
@@
 - knitcitations.bib
-# zotero: "My shared Zotero group"
-csl: proceedingsb.csl #ecology letters
-notes-after-punctuation: false
+csl: proceedingsb.csl
+notes-after-punctuation: no
+always_allow_html: true
 link-citations: yes
@@
 urlcolor: RoyalBlue
-links-as-notes: false
+links-as-notes: no
 subparagraph: yes
-
 header-includes:
@@
 - \usepackage{titlesec}
-- \titlespacing{\title}{0pt}{\parskip}{-\parskip}
+- "\\titlespacing{\\title}{0pt}{\\parskip}{-\\parskip}"
 - \usepackage[style=nature]{biblatex}
@@
 ---
-
-```{=tex}
-\doublespacing
-\normalsize
-```
 
@@
 We show that over 50% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the negative correlation between autonomous selfing and floral display size.
-In addition, these reproductive axes were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds.
+In addition, these reproductive axes were associated with the identity and number of visits of the distinct pollinator guilds.
 However, reproductive axes explain a relatively small amount of variance in pollinator interactions highlighting the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
@@
 An extended description of each trait and how it was obtained can be found in Appendix S1.
-
-\singlespacing
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=1, fig.width=14}
-
-library(kableExtra)
-
-library(dplyr)
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-#load data
-trait_data <- read_excel("../Data/Trait_data_raw/Trait_data_final.xlsx",na = "NA")
-########################################################################################################################################################
-#2) A) CLEAN DATA AND B) RENAME LEVELS FOR IMPUTATION 
-########################################################################################################################################################
-#####
-#A) CLEAN DATA
-#####
-#select just filled rows
-trait_data_1 <- trait_data[1:1712,] #It may be a more elegant way but this does the job, 1712 rows of data
-
-#filter data, select species with flower level info and capitulum
-trait_filtered <- filter(trait_data_1, Info_level == "flower" |  Info_level == "capitulum")
-#remove NA's and duplicated species|Some spp are repeated once the spp names are standardize with taxize
-trait_filtered$Species_all[trait_filtered$Species_all=="NA"]<-NA 
-trait_filtered_1 <- trait_filtered[!is.na(trait_filtered$Species_all),]
-trait_filtered_2 <- trait_filtered_1[!duplicated(trait_filtered_1$Species_all),]
-
-#Select columns to work with
-t <- trait_filtered_2[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system",
-                        "Autonomous_selfing_level","Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", 
-                        "Flowers_per_plant","Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean","Style_length", "Ovule_number", 
-                        "life_form", "lifespan","Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg", "Pollen_per_flower")]
-
-########################################################################################################################################################
-#####
-#B) RENAME LEVELS FOR IMPUTATION
-#####
-#Breeding_system| For the purpose of this study we are not going to consider other complex breeding systems and just focus on 
-#Hermaphroditism, dioecy and monoecy, the closest levels are grouped within each category
-t$Breeding_system <- as.character(t$Breeding_system)
-t$Breeding_system[t$Breeding_system=="androdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="androgynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="andromonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynodioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="gynoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="gynomonoecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="monoecious_dioecious"] <- "monoecious"
-t$Breeding_system[t$Breeding_system=="polygamo-dioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="protandrous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="protogynous"] <- "hermaphrodite"
-t$Breeding_system[t$Breeding_system=="subdioecious"] <- "dioecious"
-t$Breeding_system[t$Breeding_system=="submonoecious"] <- "monoecious"
-#Change to capital letters| There are already levels with lower case
-t$Breeding_system[t$Breeding_system=="monoecious"] <- "Monoecious"
-t$Breeding_system[t$Breeding_system=="dioecious"] <- "Dioecious"
-t$Breeding_system[t$Breeding_system=="hermaphrodite"] <- "Hermaphrodite"
-t$Breeding_system <- as.factor(t$Breeding_system)
-
-#Now 3 levels
-#Flower_morphology
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="bowl"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="dish"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="exposed"] <- "open"
-t$Flower_morphology[t$Flower_morphology=="spadix"] <- "spike"
-t$Flower_morphology[t$Flower_morphology=="open"] <- "Open"
-t$Flower_morphology[t$Flower_morphology=="brush"] <- "Brush"
-t$Flower_morphology[t$Flower_morphology=="campanulate"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="capitulum"] <- "Capitulum"
-t$Flower_morphology[t$Flower_morphology=="funnelform"] <- "Funnelform"
-t$Flower_morphology[t$Flower_morphology=="papilionaceous"] <- "Papilionaceous"
-t$Flower_morphology[t$Flower_morphology=="spike"] <- "Spike"
-t$Flower_morphology[t$Flower_morphology=="tube"] <- "Tube"
-t$Flower_morphology <- as.factor(t$Flower_morphology)
-
-#Life span
-t$lifespan <- as.character(t$lifespan )
-t$lifespan[t$lifespan=="annual"] <- "short_lived"
-t$lifespan[t$lifespan=="biennial"] <- "short_lived"
-t$lifespan[t$lifespan=="short_lived"] <- "Short lived"
-t$lifespan[t$lifespan=="perennial"] <- "Perennial"
-t$lifespan <- as.factor(t$lifespan )
-
-########################################################################################################################################################
-#3) EXPLORE PATTERNS OF MISSING DATA
-########################################################################################################################################################
-
-#We convert cualitative data to quantitative to reduce missing data on this column and hence conduct the imputation 
-#use ifelse base r does not work with these NA'S Even with work around. base r does not like the na option of read excel
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("high") & is.na(t$Autonomous_selfing_level_fruit_set), 88, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("medium") & is.na(t$Autonomous_selfing_level_fruit_set), 50.5, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("low") & is.na(t$Autonomous_selfing_level_fruit_set), 13, t$Autonomous_selfing_level_fruit_set)
-t$Autonomous_selfing_level_fruit_set <- ifelse(t$Autonomous_selfing_level %in% c("none") & is.na(t$Autonomous_selfing_level_fruit_set), 0, t$Autonomous_selfing_level_fruit_set)
-
-#t$Nectar_ul adding it here just to see how many cells 
-#Now we just select presence/absence of nectar
-#select columns of interest
-t <- t[c("Species_geonet","Order_all","Family_all","Genus_all","Species_all","Breeding_system","Compatibility_system","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Floral_unit_width",
-         "Corolla_diameter_mean", "Corolla_length_mean", "Style_length", "Ovule_number", "life_form", "lifespan",
-         "Plant_height_mean_m","Nectar_presence_absence","Nectar_ul","Nectar_mg", "Pollen_per_flower")]
-
-########################################################################################################################################################
-#4) CALCULATE PHYLOGENETIC DISTANCE TO CORRECT WITH EIGENVALUES IN THE IMPUTATION
-########################################################################################################################################################
-#Convert to factor 
-cols <- c("Order_all", "Family_all", "Genus_all", "Species_all", "Compatibility_system", "Autonomous_selfing_level", "Flower_morphology",
-          "Flower_symmetry", "life_form", "lifespan","Nectar_presence_absence")
-t[cols] <- lapply(t[cols], factor)  ## as.factor() could also be used
-
-cols.num <- c("Family_all","Genus_all","Species_all")
-t[cols.num] <- sapply(t[cols.num],as.character)
-t$Species_all <- gsub("Species_all_", "", t$Species_all)
-
-t <- t[!t$Species_all == "Pinus luchuensis", ]   # remove gymnosperm species
-
-#remove species that are not until species level
-#ALL THE SPECIES WITH SP. ARE DELETD
-t$Species_geonet <- gsub("M_PL_.*","",t$Species_geonet) #subsitute partial string for nothing
-t$Species_geonet <- gsub(" $","", t$Species_geonet, perl=T) #remove trailing spaces
-t$Species_geonet <-  sub('sp.1$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp.2$', 'sp.', t$Species_geonet)#PREPARE ALL SP TO SP.
-t$Species_geonet <- sub('sp$', 'sp.', t$Species_geonet) #PREPARE ALL SP TO SP.
-t$Species_geonet <- sub("sp.$", "DELETE", t$Species_geonet) #change all sp. for DELETE
-t <- t[- grep("DELETE",  t$Species_geonet),] #remove species with "DELETE"
-#CHECK LEVELS
-
-#Make these NA's as NA
-t$Species_all[t$Species_all=="NA"] <- NA
-t$Family_all[t$Family_all=="NA"] <- NA
-t$Genus_all[t$Genus_all=="NA"] <- NA
-#remove NA's
-t <- t[!is.na(t$Family_all),]
-t <- t[!is.na(t$Species_all),]
-t <- t[!is.na(t$Genus_all),]
-
-missing.values <- t %>%
-  gather(key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  group_by(key) %>%
-  mutate(total = n()) %>%
-  group_by(key, total, isna) %>%
-  summarise(num.isna = n()) %>%
-  mutate(pct = num.isna / total * 100)
-
-n_of_records <- subset(missing.values, isna=="FALSE")
-
-Trait <- c("Plant height", "Flower width", "Flower length", "Inflorescence width", "Style length", "Ovules per flower",
-           "Flowers per plant", "Microliters of nectar", "Milligrams of nectar", "Pollen grains per flower", "Autonomous selfing (fruit set)")
-
-Trait1 <- linebreak(c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Nectar", "Compatibility system", "Breeding system"),align = c("l"))
-
-#T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub #\n Tree", "Brush \n Campanulate \n Capitulum \n Open \n #Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",
-#           "Presence \n Absence", "Self-incomp. \n Part. #self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n #Dioecious"),align = c("l"))
-#
-T.cat <- linebreak(c("Short-lived and perennial", "Herb, shrub and tree", "Brush, campanulate, capitulum,\n open, papilionaceous and tube",  "Actinomorphic and zygomorphic",
-           "Presence and absence", "Self-incompatible, partially self-compabtile \n and self-compatible", "Hermaphrodite, monoecious and dioecious"), align = c("l"))
-
-Number_of_records_quantitative <- c(n_of_records$num.isna[n_of_records$key=="Plant_height_mean_m"], n_of_records$num.isna[n_of_records$key=="Corolla_diameter_mean"],
-  n_of_records$num.isna[n_of_records$key=="Corolla_length_mean"], n_of_records$num.isna[n_of_records$key=="Floral_unit_width"],
-  n_of_records$num.isna[n_of_records$key=="Style_length"], n_of_records$num.isna[n_of_records$key=="Ovule_number"],
-  n_of_records$num.isna[n_of_records$key=="Flowers_per_plant"], n_of_records$num.isna[n_of_records$key=="Nectar_ul"],
-  n_of_records$num.isna[n_of_records$key=="Nectar_mg"],  n_of_records$num.isna[n_of_records$key=="Pollen_per_flower"],
-  n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level_fruit_set"])
-
-Number_of_records_categorical <- c(n_of_records$num.isna[n_of_records$key=="lifespan"], n_of_records$num.isna[n_of_records$key=="life_form"],
-                                   n_of_records$num.isna[n_of_records$key=="Flower_morphology"], n_of_records$num.isna[n_of_records$key=="Flower_symmetry"],
-                                   n_of_records$num.isna[n_of_records$key=="Nectar_presence_absence"], n_of_records$num.isna[n_of_records$key=="Autonomous_selfing_level"],
-                                   n_of_records$num.isna[n_of_records$key=="Compatibility_system"], n_of_records$num.isna[n_of_records$key=="Breeding_system"],
-                                   rep("",4))
-
-T.range <- c("0.01-30m", "0.50-205mm", "0.20-195mm", "0.80-300mm", "0-138mm", "1-25000", "1-1.8 x $10^5$", "0-160$\\mu$l", "0-6.1mg", "13-2 x $10^8$", "0-100$\\%$")
-
-dat_1 <- data.frame(Trait,T.range)
-dat_2 <- data.frame(Trait1, T.cat)
-
-colnames(dat_1) <- c("Quantitative traits", "Numerical range")
-colnames(dat_2) <- c("Categorical traits", "Categories")
-
-#kable(list(dat_1, dat_2), booktabs = T, linesep = #"\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1 | #Quantitative and categorical traits used in this study.}") %>%
-#  kable_styling(full_width = F,font_size = 10) %>%  #column_spec(1:4, 
-#              width = "3in", 
-#              latex_valign = "m")
-#
-#
-
-colnames(dat_1) <- c("Traits", "Numerical range/Categories")
-colnames(dat_2) <- c("Traits", "Numerical range/Categories")
-
-d <- rbind(dat_1,dat_2)
-
-kable(d, booktabs = T, linesep = "\\addlinespace", escape = FALSE,caption = "\\textbf{Table 1.} Quantitative and categorical traits used in this study.") %>%
-  kable_styling(full_width = F,font_size = 12) %>% row_spec(0, bold=T) %>% pack_rows("Quantitative", 1, 11) %>%
-pack_rows("Categorical", 12, 18)
-
-```
-
-\doublespacing
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="85%", fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies.
-The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation.
-The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation.
-The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}
-
-#Load libraries
-library(viridis) #COLOUR GGPLOT
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(magick)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.75)),
-            axis.text=element_text(size = rel(1.75), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(1.2, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank()
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("../Data/RData/data_all_species_PPCA.rds")
-phyl_pca_forest <- readRDS("../Data/RData/phyl_pca_forest.rds")
-
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#Images were made by Paula Martin
-#Check her work on https://paulamartinart.com/
-
-tree <- image_read("../Images/PPCA_Plot/Tree.png")
-tree_1 <- as.raster(tree)
-
-style_l <- image_read("../Images/PPCA_Plot/Style_Long.png")
-style_l_1 <- as.raster(style_l)
-
-style_s <- image_read("../Images/PPCA_Plot/Style_Short.png")
-style_s_1 <- as.raster(style_s)
-
-ovule_h <- image_read("../Images/PPCA_Plot/Ovule_High.png")
-ovule_h_1 <- as.raster(ovule_h)
-
-ovule_l <- image_read("../Images/PPCA_Plot/Ovule_Low.png")
-ovule_l_1 <- as.raster(ovule_l)
-
-selfing_n <- image_read("../Images/PPCA_Plot/Selfing_None.png")
-selfing_n_1 <- as.raster(selfing_n)
-
-selfing_h <- image_read("../Images/PPCA_Plot/selfing.png")
-selfing_h_1 <- as.raster(selfing_h)
-
-single_flower <- image_read("../Images/PPCA_Plot/Single_Flower.png")
-single_flower_1 <- as.raster(single_flower)
-
-many_flowers <- image_read("../Images/PPCA_Plot/Inflorescencia.png")
-many_flowers_1 <- as.raster(many_flowers)
-#many_flowers_1 <- image_rotate(many_flowers, 45)
-
-large_flower <- image_read("../Images/PPCA_Plot/flower_big.png")
-large_flower_1 <- as.raster(large_flower)
-
-#"Images/PPCA_Plot/flower_short.png"
-flower_small <- image_read("../Images/PPCA_Plot/flower_big.png")
-flower_small_1 <- as.raster(flower_small)
-
-herb <- image_read("../Images/PPCA_Plot/herb.png")
-herb_1 <- as.raster(herb)
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-
-#Invert axes
-PC$S[,1] <- -PC$S[,1]
-PC$S[,2] <- -PC$S[,2]
-
-all_spp <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-
-  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
-  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
-    scale_alpha(guide = 'none')
-
-    plot <- plot + geom_point(data=dat, aes(x, y),size=1.3, color="black")
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .7 * mult * (get(x)),
-                      v2 = .7 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))
-
-   #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
-  plot <- plot + ylab(paste("Autonomous selfing - Floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
-
-  #CHANGE THEME
-
-  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
-     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
-    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
-    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
-    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
-    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
-    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
-    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
-    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
-    annotation_raster(large_flower_1, xmin = 3.18, xmax = 4.13,ymin = 1.3, ymax = 2.4) +
-    annotation_raster(flower_small_1, xmin = -3.21, xmax = -2.81,ymin = -2, ymax = -1.45) +
-    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)
-
-      #ADD LABELS
-  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
- plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
-                         label = PCAloadings$Variables, color="black",fontface =2,size=4)
-
- plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
-                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("")
-
-  plot
-
-}
-
-plot_grid(all_spp(PC))
-
-```
-
 As expected, due to individual trait correlations between qualitative and quantitative traits (e.g., life form and plant height), we found that most categorical traits were clustered on the trait space and statistically associated with the first two axes of trait variation (figure s2 and table s2).
@@
 Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S8k and figure S8l; Tukey test *P* \< 0.05).
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="80%",fig.align='center',fig.cap= "\\textbf{Figure 2.} Location of the different qualitative traits in the trait space.
-The figure panel is composed of the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f).
-The solid arrows indicate the direction of variation of the different quantitative traits shown in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S)."}
-
-#Load libraries
-#LOAD LIBRARIES
-library(phytools)
-library(ape) #for phylogenetic distance
-library(dplyr) #data processing
-library(rtrees) #for phylogenetic distancelibrary(MASS)
-library(reshape2)
-library(viridis) #COLOUR GGPLOT
-library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-library(cowplot)
-library(ggstar)
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.6)),
-            axis.text=element_text(size = rel(1.6), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(size = rel(1.1)),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.4, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_blank(),
-            panel.grid.minor.y= element_blank(),
-             panel.grid.major= element_blank(),
-            plot.title = element_text(size = rel(2.5), face="bold")
-      ))
-}
-
-#Load data
-dat_cleaning_5 <- readRDS("../Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
-phyl_pca_forest <- readRDS("../Data/RData/phyl_pca_forest.rds")
-
-#CALL the output PC for simplicity
-PC <- phyl_pca_forest
-#CHECK CONTENT
-#EIGENVALUES
-PC$Eval
-#PC score (POINTS)
-PC$S
-#PC loadings (ARROWS)
-PC$L
-
-#############################################################################################################################################################
-#COMPATIBILITY
-#############################################################################################################################################################
-#Load plots
-Compatibility <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$Compatibility <- dat_cleaning_5$Compatibility_system
-  dat$Compatibility <- as.character(dat$Compatibility)
-  dat$Compatibility[dat$Compatibility=="dioecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="monoecious"] <- "Unisexual flowers"
-  dat$Compatibility[dat$Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-  dat$Compatibility[dat$Compatibility=="self_compatible"] <- "Self compatible"
-  dat$Compatibility[dat$Compatibility=="self_incompatible"] <- "Self incompatible"
-  dat$Compatibility <- factor(dat$Compatibility, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=Compatibility, fill=Compatibility), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("deepskyblue2", "purple2","goldenrod","gray7")) +
-scale_starshape_manual(values = c(13, 15, 28, 5))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)  + ylab("Autonomous selfing - Floral display axis")
-
-  plot
-
-}
-
-#Compatibility(PC)
-
-#############################################################################################################################################################
-#Life form
-#############################################################################################################################################################
-#Load plots
-Life_form <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Life form` <- dat_cleaning_5$life_form
-  dat$`Life form` <- as.character(dat$`Life form`)
-  dat$`Life form`[dat$`Life form`=="herb"] <- "Herb"
-  dat$`Life form`[dat$`Life form`=="shrub"] <- "Shrub"
-  dat$`Life form`[dat$`Life form`=="tree"] <- "Tree"
-  dat$`Life form`[dat$`Life form`=="vine"] <- "Shrub"
-
-  dat$`Life form` <- factor( dat$`Life form`, levels = c("Herb", "Shrub", "Tree"))
-
-plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Life form`, fill=`Life form`), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("forestgreen", "darkorange2","black")) +
-scale_starshape_manual(values = c(13, 15, 28))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.090, 0.115)) + ggtitle("(b)") +
-    xlab(NULL) + ylab(NULL)
-
-  plot
-
-}
-
-#Life_form(PC)
-
-#############################################################################################################################################################
-#Life span
-#############################################################################################################################################################
-#Load plots
-Life_span <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-    dat$Lifespan <- dat_cleaning_5$lifespan
-    dat$Lifespan <- as.character(dat$Lifespan)
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=Lifespan, fill=Lifespan), size=2.25, color= NA, alpha = 0.9)+ scale_fill_manual(values=c("sienna4","forestgreen")) +
-scale_starshape_manual(values = c(13, 15))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.12, 0.1)) + ggtitle("(c)") +
-    xlab(NULL) + ylab(NULL)
-
-  plot
-
-}
-
-#Life_span(PC)
-
-#############################################################################################################################################################
-#Flower symmetry
-#############################################################################################################################################################
-#Load plots
-Flower_sym <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower symmetry` <- dat_cleaning_5$Flower_symmetry
-  dat$`Flower symmetry` <- as.character(dat$`Flower symmetry`)
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
-  dat$`Flower symmetry`[dat$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Flower symmetry`, fill=`Flower symmetry`), size=2.25, color= NA, alpha = 0.9) + scale_fill_manual(values=c("goldenrod","purple2")) +
-scale_starshape_manual(values = c(13, 15))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL) + xlab("Flower number - Flower size axis")
-
-  plot
-
-}
-
-#Flower_sym(PC)
-
-#############################################################################################################################################################
-#Flower shape
-#############################################################################################################################################################
-#Load plots
-Flower_sha <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Flower shape` <- dat_cleaning_5$Flower_morphology
-  dat$`Flower shape` <- as.character(dat$`Flower shape`)
-  dat$`Flower shape`[dat$`Flower shape`=="Funnelform"] <- "Campanulate"
-  dat$`Flower shape`[dat$`Flower shape`=="Spike"] <- "Brush"
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Flower shape`, fill=`Flower shape`), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("black","goldenrod", "deepskyblue2","forestgreen","purple2","darkorange2")) +
-scale_starshape_manual(values = c(13, 15, 28, 5, 9, 14))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL) + xlab("Flower number - Flower size axis")
-
-  plot
-
-}
-
-#Flower_sha(PC)
-
-#############################################################################################################################################################
-#Breeding system
-#############################################################################################################################################################
-#Load plots
-Breeding_syst <- function(PC, x="PC1", y="PC2") {
-  # PC being a prcomp object
-  data <- data.frame(PC$S)
-  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-  dat <- data.frame(x = data[,x], y = data[,y])
-
-  #######
-  #DENSITY FUNCTION
-  #######
-  get_density <- function(x, y, ...) {
-    dens <- MASS::kde2d(x, y, ...)
-    ix <- findInterval(x, dens$x)
-    iy <- findInterval(y, dens$y)
-    ii <- cbind(ix, iy)
-    return(dens$z[ii])
-  }
-
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-  dat$`Breeding system` <- dat_cleaning_5$Breeding_system
-  dat$`Breeding system` <- as.character(dat$`Breeding system`)
-  dat$`Breeding system` <- factor(dat$`Breeding system`, levels=c("Hermaphrodite","Monoecious" ,"Dioecious"))
-
-  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Breeding system`, fill=`Breeding system`), size=2.25, color= NA, alpha = 0.9) + scale_fill_manual(values=c("forestgreen","darkorange2", "black")) +
-scale_starshape_manual(values = c(13, 15, 28))
-
-  ########
-  #ADD ARROWS 
-  ########
-  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-  mult <- min(
-    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-  )
-  datapc <- transform(datapc,
-                      v1 = .75 * mult * (get(x)),
-                      v2 = .75 * mult * (get(y))
-  )
-  # add arrows
-  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-
-  #Add axis with perctentage
-  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-
-  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-
-  #ADD LABELS
-  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )
-
-  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
-                          label = PCAloadings$Variables, color="black",size=6, fontface=2)
-
-  #CHANGE THEME
-  #CHANGE THEME
-
-  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("(d)") +
-    xlab("Flower number - Flower size axis") +
-    ylab("Autonomous selfing - Floral display axis")
-
-  plot
-
-}
-
-#Breeding_syst(PC)
-
-#############################################################################################################################################################
-#Nectar
-#############################################################################################################################################################
-#Load plots
-#Nectar <- function(PC, x="PC1", y="PC2") {
-#  # PC being a prcomp object
-#  data <- data.frame(PC$S)
-#  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
-#  dat <- data.frame(x = data[,x], y = data[,y])
-#  
-#  #######
-#  #DENSITY FUNCTION
-#  #######
-#  get_density <- function(x, y, ...) {
-#    dens <- MASS::kde2d(x, y, ...)
-#    ix <- findInterval(x, dens$x)
-#    iy <- findInterval(y, dens$y)
-#    ii <- cbind(ix, iy)
-#    return(dens$z[ii])
-#  }
-#  
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
-#  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
-#  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
-#  dat$Nectar[dat$Nectar=="no"] <- "Absence"
-#  plot <- plot + geom_point(data=dat, aes(-x, -y, #colour=Nectar),size=1.75)+scale_color_manual(values=c("black","grey"))
-#  
-#  ########
-#  #ADD ARROWS 
-#  ########
-#  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
-#  mult <- min(
-#    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
-#    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
-#  )
-#  datapc <- transform(datapc,
-#                      v1 = .75 * mult * (get(x)),
-#                      v2 = .75 * mult * (get(y))
-#  )
-#  # add arrows
-#  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, #yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
-#  
-#  #Add axis with perctentage
-#  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
-#
-#  
-#  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
-#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, #arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
-#  
-#  #ADD LABELS
-#  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
-#  
-#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
-#  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = #-(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
-#                          label = PCAloadings$Variables, color="black",size=3)
-#  
-#  #CHANGE THEME
-#  #CHANGE THEME
-#  
-#  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)") 
-#  
-#  plot
-#  
-#}
-#
-# #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")
-
-  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),ncol=3,nrow=2,  align = "hv")
-
-```
-
-\elandscape
 
@@
 The contrast between interaction presence/absence  and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S9).
-
-```{=tex}
-\vspace{5mm}
-\blandscape
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different pollinator guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3).
-PC1 represents the flower number - flower size axis, PC2 represents the autonomous selfing - floral display axis and PC3 represents the style length - autonomous selfing axis.
-For visualization purposes due to large differences between number of visits from bees and the rest of the pollinator guilds, the number of visits was log-transformed (Y-axis of lower panel)."}
-
-#LOAD LIBRARIES 
-#library(phytools)
-#library(ape) #for phylogenetic distance
-#library(dplyr) #data processing
-#library(rtrees) #for phylogenetic distancelibrary(MASS)
-#library(reshape2)
-library(viridis) #COLOUR GGPLOT
-#library(MASS)
-library(ggplot2)
-library(broman) #crayon colours
-#library(tidyverse)
-library(patchwork) #panel of plots
-#library(brms)
-#library(cmdstanr)
-
-#Load theme for publication
-
-theme_ms <- function(base_size=14, base_family="Helvetica") {
-  (theme_bw(base_size = base_size, base_family = base_family)+
-     theme(text=element_text(color="black"),
-           axis.title=element_text( size = rel(2)),
-           axis.text=element_text(size = rel(1.8), color = "black"),
-           legend.title=element_text(face="bold",size=rel(2)),
-           legend.text=element_text(size=rel(1.4)),
-           legend.background=element_rect(fill="transparent"),
-           legend.key.size = unit(2, 'lines'),
-           panel.border=element_rect(color="black",size=2.4),
-           panel.grid.minor.x =element_blank(),
-           panel.grid.minor.y= element_blank(),
-           panel.grid.major= element_blank(),
-           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
-           plot.subtitle = element_text(face="bold",size=rel(2))
-     ))
-}
-
-p1 <- readRDS("../Main_Figures/figure_3_1.rds")
-p2 <- readRDS("../Main_Figures/figure_3_2.rds")
-p3 <- readRDS("../Main_Figures/figure_3_3.rds")
-pp1 <- readRDS("../Main_Figures/figure_3_4.rds")
-pp2 <- readRDS("../Main_Figures/figure_3_5.rds")
-pp3 <- readRDS("../Main_Figures/figure_3_6.rds")
-
-library(patchwork)
-
-combined <- pp1 + pp2 + pp3 + p1 + p2 + p3  & theme(legend.position = "bottom") &  guides(color = guide_legend(override.aes = list(size=6.5), keywidth=1.8,
-                 keyheight=0.1,
-                 default.unit="inch"))
-
-combined + plot_layout(guides = "collect",ncol = 3)
-```
-
-\elandscape
 

### 2023-04-13 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
edits for final sub

@@
 We divided the flowers in 8 main different categories: open, bowl, tube, campanulate, funnelform, papilionaceous, brush and capitulum.
-However, we ended up groupping all flowers on the following 6  morphological groups for analyses: tube, papilonaceous, open, capitulum, campanulate and brush (Supplementary Information Text Fig.
+However, we ended up grouping all flowers on the following 6  morphological groups for analyses: tube, papilonaceous, open, capitulum, campanulate and brush (Supplementary Information Text Fig.
 1).
@@
 1.}  Main floral morphologies considered in this study.
-All species were groupped within these categories for analysis: (a) tube, (b) papilonaceous, (c) open, (d) capitulum, (e) campanulate and (f) brush."}
+All species were grouped within these categories for analysis: (a) tube, (b) papilonaceous, (c) open, (d) capitulum, (e) campanulate and (f) brush."}
 knitr::include_graphics("../Images/flower_shapes.png")

### 2023-04-14 Main_Figures/Table_1.Rmd
Final updates for publishing

@@
 ---
-output: pdf_document
+output:
+  word_document: default
+  pdf_document: default
 fontsize: 12pt
+always_allow_html: true
 
